# Identifying subjects

The TBI information of the ABCD dataset is split across a few files:

* `abcd_otbi01.txt`: the raw, modified Ohio State TBI screen given at baseline
* `abcd_tbi01.txt`: summary scores of abcd_otbi01.txt
* `abcd_lpohstbi01.txt`: all longitudinal follow-ups of the baseline screen
* `abcd_lsstbi01.txt`: summary scores of abcd_lpohstbi01.txt

All information required for identifying children at a chronic stage following mTBI as of baseline data collection is available in the `abcd_otbi01.txt` file.


## Renaming the mTBI data


```{r child="wheeler-lab/abcd/prashanth-proj/00-rename-data/rename_abcd_otbi01.Rmd", eval=TRUE}

```


Note that all variables with the same prefix (or number originally) are referring to the same injury or set of injuries.


## Identifying subjects at a chronic stage post-mTBI

To identify subjects at a chronic stage post-mTBI, two intermediate pieces of information must be calculated from the original dataset:

* identifying which head injuries were mTBIs
* identifying the time since the most recent mTBI

The structure of the Ohio State TBI screen as used for ABCD data collection was not completely compatible with the most commonly used definition of mTBI @blennow_traumatic_2016:

At least one of the following:

* Any period of loss of consciousness
* Any loss of memory
* Any alteration in mental state
* Focal neurological deficits

but where the severity does not exceed:

* LOC over 30 minutes
* A Glasgow Coma Scale score below 13
* Post-traumatic amnesia (PTA) greater than 24 hours

A few aspects of the data collection process in the ABCD study precluded the usage of this definition:

* No information was collected regarding the GCS
* Feeling dazed and PTA were combined into a single variable, making it unclear which combination of symptoms was present
* No information was collected regarding the duration of feeling dazed or experiencing PTA

Consequently, I used the following definition to identify mTBIs:

Any child who experienced at least one injury where that injury resulted in either:

1. Less than 30 minutes of LOC (including 0 minutes) **AND** any duration of memory loss / feeling dazed
2. LOC that is greater than 0 minutes but less than 30 minutes.

The fixed nature of the questionnaire also meant that some information about multiple mTBIs sustained in the same way or about a very large number of mTBIs throughout a child's life could have been lost (see the previous section on identifying children with a history of mTBI).
For my analyses, I assume these edge cases are not common enough to meaningfully change any obtained conclusions.

The code below generates a new file which adds the following columns to the TBI screen data:

1. if a subject has experienced an mTBI prior to baseline
2. which of the reported head injuries were mTBIs
3. the time since a subject's most recent mTBI


```{r child="wheeler-lab/abcd/prashanth-proj/01-process-data/generate_abcd_otbi01_detailed.Rmd", eval=TRUE}

```


A few types of injuries were handled differently from the rest in the above code:

* for `other_loc`, the questionnaire asked for a total number of injuries with LOC as well as a total number of injuries with LOC above 30 minutes.
    * If their difference was above 0, they were labeled as having had an mTBI.
* for `other_multi` and `other_other_multi`, insufficient information was provided to determine the severity of the associated injuries.

For my analyses, I consider 3 months to be the threshold at which an mTBI patient enters a chronic stage post-injury.
The subject list was then defined in the following code:

```{r child="wheeler-lab/abcd/prashanth-proj/02-get-subjects/get_baseline_mtbi_subjects.Rmd", eval=TRUE}

```

## Some participant demographics

## Handling twins

## Identifying matched and non-matched control groups
