# Data extraction

## Subjects

All information required for identifying children at a chronic stage following mTBI as of baseline data collection is available in the `abcd_otbi01.txt` file, and in the `abcd_lpohstbi01.txt` file for longitudinal data.
To identify subjects at a chronic stage post-mTBI, two intermediate pieces of information must be calculated from the original dataset:

* identifying which head injuries were mTBIs
* identifying the time since the most recent mTBI

The structure of the Ohio State TBI screen as used for ABCD data collection was not completely compatible with the most commonly used definition of mTBI @WYA25C6X#Blennow_Etal_2016, which requires at least one of the following:

* Any period of loss of consciousness
* Any loss of memory
* Any alteration in mental state
* Focal neurological deficits

but none of the following:

* LOC over 30 minutes
* A Glasgow Coma Scale score below 13
* Post-traumatic amnesia (PTA) greater than 24 hours

A few aspects of the data collection process in the ABCD study precluded the usage of this definition:

* No information was collected regarding the GCS
* Feeling dazed and PTA were combined into a single variable, making it unclear which combination of symptoms was present
* No information was collected regarding the duration of feeling dazed or experiencing PTA

Consequently, I defined mTBI as any injury that resulted in **either**:

1. LOC for less than 30 minutes (including 0 minutes) **AND** any duration of memory loss / feeling dazed
2. LOC for less than 30 minutes but greater than 0 minutes

The fixed nature of the questionnaire also meant that some information about multiple mTBIs sustained in the same way or about a very large number of mTBIs throughout a child's life could have been lost (see the previous section on identifying children with a history of mTBI).
For my analyses, I assume these edge cases are not common enough to meaningfully change any obtained conclusions.

```{r}

library(ggplot2)
library(readr)
library(dplyr)
library(here)
library(knitr)
library(abcdutils)

core_path <- path_maker(here(paste0("data/abcd/core")))
input_path <- path_maker(here(paste0("data/abcd/inputs")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

# Loading data
## TBI
ph_p_otbi <- abcd_load(core_path("physical-health/ph_p_otbi.csv"))

## Age
abcd_y_lt <- abcd_load(core_path("abcd-general/abcd_y_lt.csv"))

# mTBI subjects
## Baseline at chronic stage post-mTBI (> 3 months) for analyses
(mtbi_subjects_0 <- get_mtbi_subjects(ph_p_otbi, abcd_y_lt, min_mpi = 3, t = 0))

write_csv(
    mtbi_subjects_0,
    sub_path("mtbi_subjects_0.csv", date = TRUE)
)

## Baseline including recent mTBIs to exclude from longitudinal data
(mtbi_subjects_0_no_min <- get_mtbi_subjects(ph_p_otbi, abcd_y_lt, t = 0))

## Year 1 follow-up - assessments will just be taken from 2 yr follow up time
(mtbi_subjects_1 <- get_mtbi_subjects(ph_p_otbi, abcd_y_lt, t = 1))

write_csv(
    mtbi_subjects_1,
    sub_path("mtbi_subjects_1.csv", date = TRUE)
)

## Year 2 follow-up
(mtbi_subjects_2 <- get_mtbi_subjects(ph_p_otbi, abcd_y_lt, min_mpi = 3, t = 2))

write_csv(
    mtbi_subjects_2,
    sub_path("mtbi_subjects_2.csv", date = TRUE)
)

## Those with injuries in year 1 + 2
mtbi_subjects_1_2 <-
    dplyr::full_join(mtbi_subjects_1, mtbi_subjects_2, by = "subjectkey")

write_csv(
    mtbi_subjects_1_2,
    sub_path("mtbi_subjects_1_2.csv", date = TRUE)
)

## Those with injuries in year 1 + 2, but not year 0 (exclusively longitudinal)
mtbi_subjects_l <- mtbi_subjects_1_2[which(!(
    mtbi_subjects_1_2$"subjectkey" %in%
        mtbi_subjects_0_no_min$"subjectkey")), ]

mtbi_subjects_l <- data.frame("subjectkey" = mtbi_subjects_l)

write_csv(
    mtbi_subjects_l,
    sub_path("mtbi_subjects_l.csv", date = TRUE)
)

# Control subjects (those with no injuries in year 1, 2, or 3)
uninjured_subjects <- get_uninjured_subjects(
    ph_p_otbi,
    abcd_y_lt
)

write_csv(
    uninjured_subjects,
    sub_path("uninjured_subjects.csv", date = TRUE)
)

# Within mtbi_subjects xl, I need to keep track of which subjects had their
#  latest injury in year 1 and which ones had their latest injury in year 2.
#  This is only so that the mTBI specific variables, like memory loss, are
#  recorded for the most recent injury.
mtbi_subjects_1_not_0 <- dplyr::semi_join(
    mtbi_subjects_1,
    mtbi_subjects_l,
    by = "subjectkey"
)

write_csv(
    mtbi_subjects_1_not_0,
    sub_path("mtbi_subjects_1_not_0.csv", date = TRUE)
)

mtbi_subjects_2_not_0 <- dplyr::semi_join(
    mtbi_subjects_2,
    mtbi_subjects_l,
    by = "subjectkey"
)

write_csv(
    mtbi_subjects_2_not_0,
    sub_path("mtbi_subjects_2_not_0.csv", date = TRUE)
)

# Note that the longitudinal subjects have not been filtered in any way based on
#  whether or not they also had an mTBI at bsaeline or another timepoint
mtbi_subjects_0 <- read_csv(
    sub_path("2023_09_20_mtbi_subjects_0.csv")
)
mtbi_subjects_1 <- read_csv(
    sub_path("2023_09_20_mtbi_subjects_1.csv")
)
mtbi_subjects_2 <- read_csv(
    sub_path("2023_09_20_mtbi_subjects_2.csv")
)
mtbi_subjects_l <- read_csv(
    sub_path("2023_09_20_mtbi_subjects_l.csv")
)
mtbi_subjects_1_not_0 <- read_csv(
    sub_path("2023_09_20_mtbi_subjects_1_not_0.csv")
)
mtbi_subjects_2_not_0 <- read_csv(
    sub_path("2023_09_20_mtbi_subjects_2_not_0.csv")
)
uninjured_subjects <- read_csv(
    sub_path("2023_09_20_uninjured_subjects.csv")
)

```

A few types of injuries were handled differently from the rest in the above code.
For the `other_loc` injury type, the questionnaire asked for a total number of injuries with LOC as well as a total number of injuries with LOC above 30 minutes.
If their difference was above 0, they were labelled as having had an mTBI.
For the `other_multi` and `other_other_multi` injury types, insufficient information was provided to determine the severity of the associated injuries.

For my analyses, I consider 3 months to be the threshold at which an mTBI patient enters a chronic stage post-injury.

## Input variables

Notation for organizing baseline and longitudinal data:

variable_name + (when subject had mTBI) + (when data was collected from)

Fields in brackets could be 0 (baseline) or 1 or 2 for 1yfu or 2yfu.

For example, `as_mtbi_mem_daze_l_0` would describe baseline mem/daze data for children who had their mTBIs at a longitudinal timepoint.

For baseline analyses, I collect baseline data for those who had their mTBI prior to baseline data collection.

For my longitudinal analysis #1 (does clustering at baseline data predict post-concussion change in impairment?), I collect baseline (non-injury) data for longitudinal subjects, with the exception of CBCL outcome measures, which get baseline and 2yfu time points collected. This analysis does leave the question: is this pattern concussion specific? Or general to all children?

To address the concussion-specific question, we need to examine a matched cohort of uninjured children.

I collect mtbi-specific data at the first post-mTBI timepoint (e.g., if the injury was between baseline and 1yfu, mtbi data is collected at 1yfu rather than 2yfu).


### Acute symptoms

The acute symptom data is found within the TBI dataset.
We are interesed in the following acute symptoms:

* mechanism of injury
* age
* LOC information
* Feeling dazed or having memory loss

A few more intermediate columns need to be added to isolate these variables for the most recent mTBIs of the subjects.

#### Feeling dazed

```{r}

# Baseline values of subjects with injuries prior to baseline
as_mtbi_mem_daze_0_0 <-
    get_mtbi_mem_daze(ph_p_otbi, abcd_y_lt, mtbi_subjects_0, t = 0)

write_csv(
    as_mtbi_mem_daze_0_0,
    input_path("as_mtbi_mem_daze_0_0.csv", date = TRUE)
)

# Baseline values of subjects who received injuries between baseline and 2yfu
# This should just be a lot of NA values, as they haven't had their injuries yet
as_mtbi_mem_daze_l_0 <-
    get_mtbi_mem_daze(ph_p_otbi, abcd_y_lt, mtbi_subjects_l, t = 0)

write_csv(
    as_mtbi_mem_daze_l_0,
    input_path("as_mtbi_mem_daze_l_0.csv", date = TRUE)
)

# Longitudinal values of subjects who received injuries between bl and 2yfu
as_mtbi_mem_daze_l_l <- get_mtbi_mem_daze_l(
    ph_p_otbi,
    abcd_y_lt,
    mtbi_subjects_l,
    mtbi_subjects_1,
    mtbi_subjects_2
)

write_csv(
    as_mtbi_mem_daze_l_l,
    input_path("as_mtbi_mem_daze_l_l.csv", date = TRUE)
)

```

#### Mechanism of injury

```{r}

# Baseline values of subjects with injuries prior to baseline
as_mtbi_mechanism_0_0 <-
    get_mtbi_mechanism(ph_p_otbi, abcd_y_lt, mtbi_subjects_0, t = 0)

write_csv(
    as_mtbi_mechanism_0_0,
    input_path("as_mtbi_mechanism_0_0.csv", date = TRUE)
)

# Baseline values of subjects who received injuries between baseline and 2yfu
# This should just be a lot of NA values, as they haven't had their injuries yet
as_mtbi_mechanism_l_0 <-
    get_mtbi_mechanism(ph_p_otbi, abcd_y_lt, mtbi_subjects_l, t = 0)

write_csv(
    as_mtbi_mechanism_l_0,
    input_path("as_mtbi_mechanism_l_0.csv", date = TRUE)
)

# Longitudinal values of subjects who received injuries between bl and 2yfu
as_mtbi_mechanism_l_l <- get_mtbi_mechanism_l(
    ph_p_otbi,
    abcd_y_lt,
    mtbi_subjects_l,
    mtbi_subjects_1,
    mtbi_subjects_2
)

write_csv(
    as_mtbi_mechanism_l_l,
    input_path("as_mtbi_mechanism_l_l.csv", date = TRUE)
)

```

#### Loss of consciousness

```{r}

# Baseline values of subjects with injuries prior to baseline
as_mtbi_loc_0_0 <-
    get_mtbi_loc(ph_p_otbi, abcd_y_lt, mtbi_subjects_0, t = 0)

write_csv(
    as_mtbi_loc_0_0,
    input_path("as_mtbi_loc_0_0.csv", date = TRUE)
)

# Baseline values of subjects who received injuries between baseline and 2yfu
# This should just be a lot of NA values, as they haven't had their injuries yet
as_mtbi_loc_l_0 <-
    get_mtbi_loc(ph_p_otbi, abcd_y_lt, mtbi_subjects_l, t = 0)

write_csv(
    as_mtbi_loc_l_0,
    input_path("as_mtbi_loc_l_0.csv", date = TRUE)
)

# Longitudinal values of subjects who received injuries between bl and 2yfu
as_mtbi_loc_l_l <- get_mtbi_loc_l(
    ph_p_otbi,
    abcd_y_lt,
    mtbi_subjects_l,
    mtbi_subjects_1,
    mtbi_subjects_2
)

write_csv(
    as_mtbi_loc_l_l,
    input_path("as_mtbi_loc_l_l.csv", date = TRUE)
)

```

### Demographics

Demographic variables included in the analyses are:

Aspects of the NIH Toolbox probe different forms of IQ @7HIU42K2#Zhao_Etal_2022 and are used in this study as an out-of-model outcome measure rather than as an input.

Age and sex are commonly included in the ABCD study's data files.

* Age
* Sex
* Race
* Household income
* Pubertal development status

#### Pubertal status

```{r}

ph_y_pds <- abcd_load(core_path("physical-health/ph_y_pds.csv"))
ph_p_pds <- abcd_load(core_path("physical-health/ph_p_pds.csv"))

d_pubertal_status_0_0 <-
    get_pubertal_status(ph_p_pds, ph_y_pds, mtbi_subjects_0, t = 0)

write_csv(d_pubertal_status_0_0, input_path("d_pubertal_status_0_0.csv", TRUE))

d_pubertal_status_l_0 <-
    get_pubertal_status(ph_p_pds, ph_y_pds, mtbi_subjects_l, t = 0)

write_csv(d_pubertal_status_l_0, input_path("d_pubertal_status_l_0.csv", TRUE))

d_pubertal_status_u_0 <-
    get_pubertal_status(ph_p_pds, ph_y_pds, uninjured_subjects, t = 0)

write_csv(d_pubertal_status_u_0, input_path("d_pubertal_status_u_0.csv", TRUE))

```

#### Interview age

```{r}

(d_interview_age_0_0 <- get_interview_age(abcd_y_lt, mtbi_subjects_0, t = 0))

write_csv(d_interview_age_0_0, input_path("d_interview_age_0_0.csv", TRUE))

(d_interview_age_l_0 <- get_interview_age(abcd_y_lt, mtbi_subjects_l, t = 0))

write_csv(d_interview_age_l_0, input_path("d_interview_age_l_0.csv", TRUE))

(d_interview_age_u_0 <- get_interview_age(abcd_y_lt, uninjured_subjects, t = 0))

write_csv(d_interview_age_u_0, input_path("d_interview_age_u_0.csv", TRUE))

```

#### Injury age

I will also collect here the age of the children at their latest injury.
For some of these children, that means their age should be collected at the 1-year-follow-up.
For others, it is the 2-year-follow-up.
I'll start by creating a dataframe containing the longitudinal subjects and leaving an empty column for age.
The column will first get populated by the 1 year values, followed by the 2 year values.
This way, children who have injuries from both the 1 year and 2 year timepoints will have their 1-year injury ages overwritten by their 2-year injury ages.

For an analysis that uses baseline data of longitudinally injured children to predict their outcomes, this variable would not be necessary; there is no baseline injury data (including when they were injured) for those who were injured longitudinally.
This would primarily be used for an analysis in which we examined all the 2yfu data we have access to in the same way that we have already done for the baseline data.

```{r}

## Age on injury
(d_mtbi_age_0_0 <- get_mtbi_age(ph_p_otbi, abcd_y_lt, mtbi_subjects_0, t = 0))

write_csv(d_mtbi_age_0_0, input_path("d_mtbi_age_0_0.csv", TRUE))


# The age of latest mTBI as of 1 years
d_mtbi_age_1_l <- get_mtbi_age(
    ph_p_otbi,
    abcd_y_lt,
    mtbi_subjects_1_not_0,
    t = 1
)

# The age of latest mTBI as of 2 years
d_mtbi_age_2_l <- get_mtbi_age(
    ph_p_otbi,
    abcd_y_lt,
    mtbi_subjects_2_not_0,
    t = 2
)

# Where all longitudinal ages will be stored
d_mtbi_age_l_l <- data.frame(
    subjectkey = mtbi_subjects_l$subjectkey
)

# Change the names from these dataframes to keep track of where each column
#  came from
d_mtbi_age_1_l <- d_mtbi_age_1_l |>
    dplyr::rename("latest_mtbi_age_1" = "latest_mtbi_age")
d_mtbi_age_2_l <- d_mtbi_age_2_l |>
    dplyr::rename("latest_mtbi_age_2" = "latest_mtbi_age")

# Merge everything into one dataframe
d_mtbi_age_l_l <- dplyr::full_join(
    d_mtbi_age_l_l,
    d_mtbi_age_1_l,
    by = "subjectkey"
)
d_mtbi_age_l_l <- dplyr::full_join(
    d_mtbi_age_l_l,
    d_mtbi_age_2_l,
    by = "subjectkey"
)

# If the 2-year timepoint does not have an mTBI age, the latest mtbi must have
#  happened at the 1-year timepoint. In the case, take the age from that time.
#  Otherwise if the 2-year timepoint does have an age, use that age as the
#  latest mTBI age.
d_mtbi_age_l_l <- d_mtbi_age_l_l |> dplyr::mutate(
    latest_mtbi_age = dplyr::case_when(
        is.na(latest_mtbi_age_2) ~ latest_mtbi_age_1,
        TRUE ~ latest_mtbi_age_2
    ),
    .keep = "unused"
)

write_csv(d_mtbi_age_l_l, input_path("d_mtbi_age_l_l.csv", TRUE))

# As this is one of the mTBI injury variables, it is not needed for the
#  longitudinal analysis checking to see if baseline pre-injury data predicts
#  post-injury change in behavioural scores.

```

#### Sex at birth

```{r}

gish_p_gi <- abcd_load(core_path("gender-identity-sexual-health/gish_p_gi.csv"))

(d_sex_0_0 <- get_sex(gish_p_gi, mtbi_subjects_0, t = 0))

write_csv(d_sex_0_0, input_path("d_sex_0_0.csv", TRUE))

(d_sex_l_0 <- get_sex(gish_p_gi, mtbi_subjects_l, t = 0))

write_csv(d_sex_l_0, input_path("d_sex_l_0.csv", TRUE))

(d_sex_u_0 <- get_sex(gish_p_gi, uninjured_subjects, t = 0))

write_csv(d_sex_u_0, input_path("d_sex_u_0.csv", TRUE))

```

#### Parent report of gender

```{r}

gish_y_gi <- abcd_load(core_path("gender-identity-sexual-health/gish_y_gi.csv"))

# Gender identity - only parent reports are available at baseline. 4 year data
#  is the earliest timepoint where child reports are available.
(d_p_gender_0_0 <- get_p_gender(gish_p_gi, mtbi_subjects_0, t = 0))

write_csv(d_p_gender_0_0, input_path("d_p_gender_0_0.csv", TRUE))

(d_y_gender_0_4 <- get_y_gender(gish_y_gi, mtbi_subjects_0, t = 4))

write_csv(d_y_gender_0_4, input_path("d_y_gender_0_4.csv", TRUE))

(d_p_gender_l_0 <- get_p_gender(gish_p_gi, mtbi_subjects_l, t = 0))

write_csv(d_p_gender_l_0, input_path("d_p_gender_l_0.csv", TRUE))

(d_y_gender_l_4 <- get_y_gender(gish_y_gi, mtbi_subjects_l, t = 4))

write_csv(d_y_gender_l_4, input_path("d_y_gender_l_4.csv", TRUE))

(d_p_gender_u_0 <- get_p_gender(gish_p_gi, uninjured_subjects, t = 0))

write_csv(d_p_gender_u_0, input_path("d_p_gender_u_0.csv", TRUE))

(d_y_gender_u_4 <- get_y_gender(gish_y_gi, uninjured_subjects, t = 4))

write_csv(d_y_gender_u_4, input_path("d_y_gender_u_4.csv", TRUE))

```

#### Household income

```{r}

abcd_p_demo <- abcd_load(core_path("abcd-general/abcd_p_demo.csv"))

(d_income_0_0 <- get_income(abcd_p_demo, mtbi_subjects_0, t = 0))

write_csv(d_income_0_0, input_path("d_income_0_0.csv", TRUE))

(d_income_l_0 <- get_income(abcd_p_demo, mtbi_subjects_l, t = 0))

write_csv(d_income_l_0, input_path("d_income_l_0.csv", TRUE))

(d_income_u_0 <- get_income(abcd_p_demo, uninjured_subjects, t = 0))

write_csv(d_income_u_0, input_path("d_income_u_0.csv", TRUE))

```

#### Race

```{r}

d_race_0_0 <- get_race(
    abcd_p_demo,
    mtbi_subjects_0,
    "condensed_undummied",
    t = 0
)

write_csv(d_race_0_0, input_path("d_race_0_0.csv", TRUE))

d_race_l_0 <- get_race(
    abcd_p_demo,
    mtbi_subjects_l,
    "condensed_undummied",
    t = 0
)

write_csv(d_race_l_0, input_path("d_race_l_0.csv", TRUE))

d_race_u_0 <- get_race(
    abcd_p_demo,
    uninjured_subjects,
    "condensed_undummied",
    t = 0
)

write_csv(d_race_u_0, input_path("d_race_u_0.csv", TRUE))

```

### Medical history

Medical history variables of interest include:

1. Number of previous head injuries
    * discrete variable `mtbi_count` from the processed file `abcd_otbi01_detailed.csv`
2. History of headaches
    * binary variable `medhx_2q` from the file ABCD Parent Medical History Questionnaire (`abcd_mx01.txt`; category Med History; release 2.0)
        * checks if subject has ever gone to doctor for bad headaches

Unfortunately, information on pain (the file `abcd_pq01.txt`), a factor noted as an important covariate by the original A-CAP study (@8VF7JUXL##Yeates_Etal_2017), was not a part of ABCD's baseline data collection.

#### History of headaches

```{r}

ph_p_mhx <- abcd_load(core_path("physical-health/ph_p_mhx.csv"))

(mh_headaches_0_0 <- get_headaches(ph_p_mhx, mtbi_subjects_0, t = 0))

write_csv(mh_headaches_0_0, input_path("mh_headaches_0_0.csv", date = TRUE))

(mh_headaches_l_0 <- get_headaches(ph_p_mhx, mtbi_subjects_l, t = 0))

write_csv(mh_headaches_l_0, input_path("mh_headaches_l_0.csv", date = TRUE))

(mh_headaches_u_0 <- get_headaches(ph_p_mhx, uninjured_subjects, t = 0))

write_csv(mh_headaches_u_0, input_path("mh_headaches_u_0.csv", date = TRUE))

```

#### Number of previous mTBIs

```{r}

mh_mtbi_count_0_0 <- get_mtbi_count(ph_p_otbi,
    abcd_y_lt,
    mtbi_subjects_0,
    t = 0
)

write_csv(mh_mtbi_count_0_0, input_path("mh_mtbi_count_0_0.csv", date = TRUE))

mh_mtbi_count_l_0 <- get_mtbi_count(ph_p_otbi,
    abcd_y_lt,
    mtbi_subjects_l,
    t = 0
)

write_csv(mh_mtbi_count_l_0, input_path("mh_mtbi_count_l_0.csv", date = TRUE))

mh_mtbi_count_u_0 <- get_mtbi_count(ph_p_otbi,
    abcd_y_lt,
    uninjured_subjects,
    t = 0
)

write_csv(mh_mtbi_count_u_0, input_path("mh_mtbi_count_u_0.csv", date = TRUE))

```

### Neuroimaging

Variables of interest related to brain structure and function include:

* Structural: T1-weighted multishell diffusion-weighted MRI data
* Diffusion: Neurite density (restricted spectrum imaging)
* Functional: resting-state functional MRI data

The 2019 publication by Hagler et al. @UD6THTQZ##Hagler_Etal_2019 outlines the neuroimaging data present in the ABCD dataset in detail.

#### Structural MRI

The sMRI variables of interest include subcortical volumes, and cortical thicknesses, and cortical surface areas.

For cortical surface areas, the relevant file is abcd_mrisdp10201, which contains the cortical surface areas of ~150 regions (variables `mrisdp_*` where * ranges from 1 to 151).

For cortical thicknesses, the relevant file is abcd_mrisdp10201, which contains the cortical thickness of ~150 regions (variables `mrisdp_*` where * ranges from 303 to 453).

##### Subcortical volume

```{r}

mri_y_smr_vol_aseg <- abcd_load(core_path("imaging/mri_y_smr_vol_aseg.csv"))

sm_subc_v_0_0 <- abcdutils::get_subc_v(
    mri_y_smr_vol_aseg,
    mtbi_subjects_0,
    t = 0
)

write_csv(sm_subc_v_0_0, input_path("sm_subc_v_0_0.csv", date = TRUE))

sm_subc_v_l_0 <- abcdutils::get_subc_v(
    mri_y_smr_vol_aseg,
    mtbi_subjects_l,
    t = 0
)

write_csv(sm_subc_v_l_0, input_path("sm_subc_v_l_0.csv", date = TRUE))

sm_subc_v_u_0 <- abcdutils::get_subc_v(
    mri_y_smr_vol_aseg,
    uninjured_subjects,
    t = 0
)

write_csv(sm_subc_v_u_0, input_path("sm_subc_v_u_0.csv", date = TRUE))

```

##### Cortical thickness

```{r}

mri_y_smr_thk_dst <- abcd_load(core_path("imaging/mri_y_smr_thk_dst.csv"))

## Cortical thickness
sm_cort_t_0_0 <- abcdutils::get_cort_t(
    mri_y_smr_thk_dst,
    mtbi_subjects_0,
    t = 0
)

write_csv(sm_cort_t_0_0, input_path("sm_cort_t_0_0.csv", date = TRUE))

sm_cort_t_l_0 <- abcdutils::get_cort_t(
    mri_y_smr_thk_dst,
    mtbi_subjects_l,
    t = 0
)

write_csv(sm_cort_t_l_0, input_path("sm_cort_t_l_0.csv", date = TRUE))

sm_cort_t_u_0 <- abcdutils::get_cort_t(
    mri_y_smr_thk_dst,
    uninjured_subjects,
    t = 0
)

write_csv(sm_cort_t_u_0, input_path("sm_cort_t_u_0.csv", date = TRUE))

```

##### Cortical surface areas

```{r}

mri_y_smr_area_dst <- abcd_load(core_path("imaging/mri_y_smr_area_dst.csv"))

sm_cort_sa_0_0 <- abcdutils::get_cort_sa(
    mri_y_smr_area_dst, mtbi_subjects_0, t = 0
)

write_csv(sm_cort_sa_0_0, input_path("sm_cort_sa_0_0.csv", date = TRUE))

sm_cort_sa_l_0 <- abcdutils::get_cort_sa(
    mri_y_smr_area_dst, mtbi_subjects_l, t = 0
)

write_csv(sm_cort_sa_l_0, input_path("sm_cort_sa_l_0.csv", date = TRUE))

sm_cort_sa_u_0 <- abcdutils::get_cort_sa(
    mri_y_smr_area_dst, uninjured_subjects, t = 0
)

write_csv(sm_cort_sa_u_0, input_path("sm_cort_sa_u_0.csv", date = TRUE))

```

#### Diffusion MRI

We are interested in the neurite density measures of white matter regions in the brain.
Previously, these measures were found in variables containing the string "rsindwm_cdk" within the file `mri_rsi_p102.txt`.
A change anounced in the ABCD 4.0 MRI release notes indicates that neurite density is now referred to as "restricted normalized directional" and that the relevant white matter variables contain the string "rsirndwm" within the file `abcd_drsip201.txt`.

See diffusion MRI chapter in appendix for full details.

##### White matter neurite densities

```{r}

# DMRI dataframe
mri_y_rsi_rnd_at <- abcd_load(core_path("imaging/mri_y_rsi_rnd_at.csv"))
mri_y_rsi_rnd_wm_dsk <- abcd_load(core_path("imaging/mri_y_rsi_rnd_wm_dsk.csv"))
mri_y_rsi_rnd_wm_dst <- abcd_load(core_path("imaging/mri_y_rsi_rnd_wm_dst.csv"))

# White matter neurite densities
dm_all_wmnd_0_0 <- get_all_wmnd(
    mri_y_rsi_rnd_at,
    mri_y_rsi_rnd_wm_dst,
    mri_y_rsi_rnd_wm_dsk,
    subjects = mtbi_subjects_0,
    t = 0
)
write_csv(dm_all_wmnd_0_0, input_path("dm_all_wmnd_0_0.csv", date = TRUE))

dm_all_wmnd_l_0 <- get_all_wmnd(
    mri_y_rsi_rnd_at,
    mri_y_rsi_rnd_wm_dst,
    mri_y_rsi_rnd_wm_dsk,
    subjects = mtbi_subjects_l,
    t = 0
)
write_csv(dm_all_wmnd_l_0, input_path("dm_all_wmnd_l_0.csv", date = TRUE))

dm_all_wmnd_u_0 <- get_all_wmnd(
    mri_y_rsi_rnd_at,
    mri_y_rsi_rnd_wm_dst,
    mri_y_rsi_rnd_wm_dsk,
    subjects = uninjured_subjects,
    t = 0
)
write_csv(dm_all_wmnd_u_0, input_path("dm_all_wmnd_u_0.csv", date = TRUE))

```

#### Resting-state functional MRI

We are interested in the following rs-fMRI measures:

- Gordon network (cortical) correlations
- Subcortical correlations
- Gordon and subcortical temporal variances

##### Cortical parcellation network correlations

```{r}

mri_y_rsfmr_cor_gp_gp <- abcd_load(
    core_path("imaging/mri_y_rsfmr_cor_gp_gp.csv")
)

rm_gord_cor_0_0 <- get_gord_cor(
    mri_y_rsfmr_cor_gp_gp,
    mtbi_subjects_0,
    t = 0
)

write_csv(rm_gord_cor_0_0, input_path("rm_gord_cor_0_0.csv", date = TRUE))

rm_gord_cor_l_0 <- get_gord_cor(
    mri_y_rsfmr_cor_gp_gp,
    mtbi_subjects_l,
    t = 0
)

write_csv(rm_gord_cor_l_0, input_path("rm_gord_cor_l_0.csv", date = TRUE))

rm_gord_cor_u_0 <- get_gord_cor(
    mri_y_rsfmr_cor_gp_gp,
    uninjured_subjects,
    t = 0
)

write_csv(rm_gord_cor_u_0, input_path("rm_gord_cor_u_0.csv", date = TRUE))

```

##### Subcortical parcellation network correlations

```{r}

mri_y_rsfmr_cor_gp_aseg <- abcd_load(
    core_path("imaging/mri_y_rsfmr_cor_gp_aseg.csv")
)

rm_subc_cor_0_0 <- get_subc_cor(
    mri_y_rsfmr_cor_gp_aseg,
    mtbi_subjects_0,
    t = 0
)

write_csv(rm_subc_cor_0_0, input_path("rm_subc_cor_0_0.csv", date = TRUE))

rm_subc_cor_l_0 <- get_subc_cor(
    mri_y_rsfmr_cor_gp_aseg,
    mtbi_subjects_l,
    t = 0
)

write_csv(rm_subc_cor_l_0, input_path("rm_subc_cor_l_0.csv", date = TRUE))

rm_subc_cor_u_0 <- get_subc_cor(
    mri_y_rsfmr_cor_gp_aseg,
    uninjured_subjects,
    t = 0
)

write_csv(rm_subc_cor_u_0, input_path("rm_subc_cor_u_0.csv", date = TRUE))

```

##### Cortical parcellation temporal variances

```{r}

mri_y_rsfmr_var_gp <- abcd_load(core_path("imaging/mri_y_rsfmr_var_gp.csv"))

rm_gord_var_0_0 <- get_gord_var(mri_y_rsfmr_var_gp, mtbi_subjects_0, t = 0)

write_csv(rm_gord_var_0_0, input_path("rm_gord_var_0_0.csv", date = TRUE))

rm_gord_var_l_0 <- get_gord_var(mri_y_rsfmr_var_gp, mtbi_subjects_l, t = 0)

write_csv(rm_gord_var_l_0, input_path("rm_gord_var_l_0.csv", date = TRUE))

rm_gord_var_u_0 <- get_gord_var(mri_y_rsfmr_var_gp, uninjured_subjects, t = 0)

write_csv(rm_gord_var_u_0, input_path("rm_gord_var_u_0.csv", date = TRUE))

```

##### Subcortical parcellation temporal variances

```{r}

mri_y_rsfmr_var_aseg <- abcd_load(core_path("imaging/mri_y_rsfmr_var_aseg.csv"))

rm_subc_var_0_0 <- get_subc_var(mri_y_rsfmr_var_aseg, mtbi_subjects_0, t = 0)

write_csv(rm_subc_var_0_0, input_path("rm_subc_var_0_0.csv", date = TRUE))

rm_subc_var_l_0 <- get_subc_var(mri_y_rsfmr_var_aseg, mtbi_subjects_l, t = 0)

write_csv(rm_subc_var_l_0, input_path("rm_subc_var_l_0.csv", date = TRUE))

rm_subc_var_u_0 <- get_subc_var(mri_y_rsfmr_var_aseg, uninjured_subjects, t = 0)

write_csv(rm_subc_var_u_0, input_path("rm_subc_var_u_0.csv", date = TRUE))

```

### Psychosocial resilience

Psychosocial factors of interest include:

#### Loneliness

```{r}

mh_y_or <- abcd_load(core_path("mental-health/mh_y_or.csv"))

p_loneliness_0_0 <- get_loneliness(
    mh_y_or,
    gish_p_gi,
    mtbi_subjects_0,
    t = 0
)
write_csv(p_loneliness_0_0, input_path("p_loneliness_0_0.csv", date = TRUE))

p_loneliness_l_0 <- get_loneliness(
    mh_y_or,
    gish_p_gi,
    mtbi_subjects_l,
    t = 0
)
write_csv(p_loneliness_l_0, input_path("p_loneliness_l_0.csv", date = TRUE))

p_loneliness_u_0 <- get_loneliness(
    mh_y_or,
    gish_p_gi,
    uninjured_subjects,
    t = 0
)
write_csv(p_loneliness_u_0, input_path("p_loneliness_u_0.csv", date = TRUE))

```

#### Healthy behaviours

##### Screen time

```{r}

nt_p_stq <- abcd_load(core_path("novel-technologies/nt_p_stq.csv"))

p_screen_time_0_0 <- get_screen_time(
    nt_p_stq,
    mtbi_subjects_0,
    t = 0
)
write_csv(p_screen_time_0_0, input_path("p_screen_time_0_0.csv", date = TRUE))

p_screen_time_l_0 <- get_screen_time(
    nt_p_stq,
    mtbi_subjects_l,
    t = 0
)
write_csv(p_screen_time_l_0, input_path("p_screen_time_l_0.csv", date = TRUE))

p_screen_time_u_0 <- get_screen_time(
    nt_p_stq,
    uninjured_subjects,
    t = 0
)
write_csv(p_screen_time_u_0, input_path("p_screen_time_u_0.csv", date = TRUE))

```

##### Sports and activities participation

```{r}

ph_p_saiq <- abcd_load(core_path("physical-health/ph_p_saiq.csv"))

p_sports_0_0 <- get_sports_and_activities(
    ph_p_saiq,
    mtbi_subjects_0,
    t = 0
)
write_csv(p_sports_0_0, input_path("p_sports_0_0.csv", date = TRUE))

p_sports_l_0 <- get_sports_and_activities(
    ph_p_saiq,
    mtbi_subjects_l,
    t = 0
)
write_csv(p_sports_l_0, input_path("p_sports_l_0.csv", date = TRUE))

p_sports_u_0 <- get_sports_and_activities(
    ph_p_saiq,
    uninjured_subjects,
    t = 0
)
write_csv(p_sports_u_0, input_path("p_sports_u_0.csv", date = TRUE))

```

##### Exercise habits

```{r}

ph_y_yrb <- abcd_load(core_path("physical-health/ph_y_yrb.csv"))

p_exercise_0_0 <- get_exercise(
    ph_y_yrb,
    mtbi_subjects_0,
    t = 0
)
write_csv(p_exercise_0_0, input_path("p_exercise_0_0.csv", date = TRUE))

p_exercise_l_0 <- get_exercise(
    ph_y_yrb,
    mtbi_subjects_l,
    t = 0
)
write_csv(p_exercise_l_0, input_path("p_exercise_l_0.csv", date = TRUE))

p_exercise_u_0 <- get_exercise(
    ph_y_yrb,
    uninjured_subjects,
    t = 0
)
write_csv(p_exercise_u_0, input_path("p_exercise_u_0.csv", date = TRUE))

```

#### Prosocial behaviour

```{r}

ce_y_psb <- abcd_load(core_path("culture-environment/ce_y_psb.csv"))
ce_p_psb <- abcd_load(core_path("culture-environment/ce_p_psb.csv"))

p_prosocial_0_0 <- get_prosocial_behaviour(
    ce_p_psb,
    ce_y_psb,
    mtbi_subjects_0,
    t = 0
)
write_csv(p_prosocial_0_0, input_path("p_prosocial_0_0.csv", date = TRUE))

p_prosocial_l_0 <- get_prosocial_behaviour(
    ce_p_psb,
    ce_y_psb,
    mtbi_subjects_l,
    t = 0
)
write_csv(p_prosocial_l_0, input_path("p_prosocial_l_0.csv", date = TRUE))

p_prosocial_u_0 <- get_prosocial_behaviour(
    ce_p_psb,
    ce_y_psb,
    uninjured_subjects,
    t = 0
)
write_csv(p_prosocial_u_0, input_path("p_prosocial_u_0.csv", date = TRUE))

```

#### Family function

```{r}

ce_y_fes <- abcd_load(core_path("culture-environment/ce_y_fes.csv"))
ce_p_fes <- abcd_load(core_path("culture-environment/ce_p_fes.csv"))

p_family_function_0_0 <- get_family_function(
    ce_y_fes,
    ce_p_fes,
    mtbi_subjects_0,
    t = 0
)
write_csv(
    p_family_function_0_0,
    input_path("p_family_function_0_0.csv", date = TRUE)
)

p_family_function_l_0 <- get_family_function(
    ce_y_fes,
    ce_p_fes,
    mtbi_subjects_l,
    t = 0
)
write_csv(
    p_family_function_l_0,
    input_path("p_family_function_l_0.csv", date = TRUE)
)

p_family_function_u_0 <- get_family_function(
    ce_y_fes,
    ce_p_fes,
    uninjured_subjects,
    t = 0
)
write_csv(
    p_family_function_u_0,
    input_path("p_family_function_u_0.csv", date = TRUE)
)

```

#### Parent psychopathology

```{r}

mh_p_asr <- abcd_load(core_path("mental-health/mh_p_asr.csv"))

p_parent_psych_0_0 <- get_parent_psychopathology(
    mh_p_asr,
    mtbi_subjects_0,
    t = 0
)
write_csv(
    p_parent_psych_0_0,
    input_path("p_parent_psych_0_0.csv", date = TRUE)
)

p_parent_psych_l_0 <- get_parent_psychopathology(
    mh_p_asr,
    mtbi_subjects_l,
    t = 0
)
write_csv(p_parent_psych_l_0, input_path("p_parent_psych_l_0.csv", date = TRUE))

p_parent_psych_u_0 <- get_parent_psychopathology(
    mh_p_asr,
    uninjured_subjects,
    t = 0
)
write_csv(p_parent_psych_u_0, input_path("p_parent_psych_u_0.csv", date = TRUE))

```

## Output variables

### Child behaviour checklist

These are collected at both baseline and longitudinal timepoints.

#### Anxious-depressed

```{r}

mh_p_asr <- abcd_load(core_path("mental-health/mh_p_asr.csv"))
mh_p_cbcl <- abcd_load(core_path("mental-health/mh_p_cbcl.csv"))

get_cbcl_syndrome_scale(
    syndrome = "anxdep",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_0,
    t = 1
) |>
    na.omit() |>
    dim()

get_cbcl_syndrome_scale(
    syndrome = "withdep",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_0,
    t = 1
) |>
    na.omit() |>
    dim()


## At baseline
cbcl_anxdep_ss_0_0 <- get_cbcl_syndrome_scale(
    syndrome = "anxdep",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_0,
    t = 0
)
write_csv(
    cbcl_anxdep_ss_0_0,
    input_path("cbcl_anxdep_ss_0_0.csv", date = TRUE)
)

cbcl_anxdep_ss_l_0 <- get_cbcl_syndrome_scale(
    syndrome = "anxdep",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_l,
    t = 0
)
write_csv(
    cbcl_anxdep_ss_l_0,
    input_path("cbcl_anxdep_ss_l_0.csv", date = TRUE)
)

cbcl_anxdep_ss_u_0 <- get_cbcl_syndrome_scale(
    syndrome = "anxdep",
    mh_p_cbcl,
    raw = TRUE,
    subjects = uninjured_subjects,
    t = 0
)
write_csv(
    cbcl_anxdep_ss_u_0,
    input_path("cbcl_anxdep_ss_u_0.csv", date = TRUE)
)

## At 2yfu
cbcl_anxdep_ss_0_l <- get_cbcl_syndrome_scale(
    syndrome = "anxdep",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_0,
    t = 2
)
write_csv(
    cbcl_anxdep_ss_0_l,
    input_path("cbcl_anxdep_ss_0_l.csv", date = TRUE)
)

cbcl_anxdep_ss_l_l <- get_cbcl_syndrome_scale(
    syndrome = "anxdep",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_l,
    t = 2
)
write_csv(
    cbcl_anxdep_ss_l_l,
    input_path("cbcl_anxdep_ss_l_l.csv", date = TRUE)
)

cbcl_anxdep_ss_u_l <- get_cbcl_syndrome_scale(
    syndrome = "anxdep",
    mh_p_cbcl,
    raw = TRUE,
    subjects = uninjured_subjects,
    t = 2
)
write_csv(
    cbcl_anxdep_ss_u_l,
    input_path("cbcl_anxdep_ss_u_l.csv", date = TRUE)
)

```

#### Withdrawn-depressed

```{r}

## At baseline
cbcl_withdep_ss_0_0 <- get_cbcl_syndrome_scale(
    syndrome = "withdep",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_0,
    t = 0
)
write_csv(
    cbcl_withdep_ss_0_0,
    input_path("cbcl_withdep_ss_0_0.csv", date = TRUE)
)

cbcl_withdep_ss_l_0 <- get_cbcl_syndrome_scale(
    syndrome = "withdep",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_l,
    t = 0
)
write_csv(
    cbcl_withdep_ss_l_0,
    input_path("cbcl_withdep_ss_l_0.csv", date = TRUE)
)

cbcl_withdep_ss_u_0 <- get_cbcl_syndrome_scale(
    syndrome = "withdep",
    mh_p_cbcl,
    raw = TRUE,
    subjects = uninjured_subjects,
    t = 0
)
write_csv(
    cbcl_withdep_ss_u_0,
    input_path("cbcl_withdep_ss_u_0.csv", date = TRUE)
)

## At 2yfu
cbcl_withdep_ss_0_l <- get_cbcl_syndrome_scale(
    syndrome = "withdep",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_0,
    t = 2
)
write_csv(
    cbcl_withdep_ss_0_l,
    input_path("cbcl_withdep_ss_0_l.csv", date = TRUE)
)

cbcl_withdep_ss_l_l <- get_cbcl_syndrome_scale(
    syndrome = "withdep",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_l,
    t = 2
)
write_csv(
    cbcl_withdep_ss_l_l,
    input_path("cbcl_withdep_ss_l_l.csv", date = TRUE)
)

cbcl_withdep_ss_u_l <- get_cbcl_syndrome_scale(
    syndrome = "withdep",
    mh_p_cbcl,
    raw = TRUE,
    subjects = uninjured_subjects,
    t = 2
)
write_csv(
    cbcl_withdep_ss_u_l,
    input_path("cbcl_withdep_ss_u_l.csv", date = TRUE)
)

```

#### Somatic complaints

```{r}

## At baseline
cbcl_somatic_ss_0_0 <- get_cbcl_syndrome_scale(
    syndrome = "somatic",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_0,
    t = 0
)
write_csv(
    cbcl_somatic_ss_0_0,
    input_path("cbcl_somatic_ss_0_0.csv", date = TRUE)
)

cbcl_somatic_ss_l_0 <- get_cbcl_syndrome_scale(
    syndrome = "somatic",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_l,
    t = 0
)
write_csv(
    cbcl_somatic_ss_l_0,
    input_path("cbcl_somatic_ss_l_0.csv", date = TRUE)
)

cbcl_somatic_ss_u_0 <- get_cbcl_syndrome_scale(
    syndrome = "somatic",
    mh_p_cbcl,
    raw = TRUE,
    subjects = uninjured_subjects,
    t = 0
)
write_csv(
    cbcl_somatic_ss_u_0,
    input_path("cbcl_somatic_ss_u_0.csv", date = TRUE)
)

## At 2yfu
cbcl_somatic_ss_0_l <- get_cbcl_syndrome_scale(
    syndrome = "somatic",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_0,
    t = 2
)
write_csv(
    cbcl_somatic_ss_0_l,
    input_path("cbcl_somatic_ss_0_l.csv", date = TRUE)
)

cbcl_somatic_ss_l_l <- get_cbcl_syndrome_scale(
    syndrome = "somatic",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_l,
    t = 2
)
write_csv(
    cbcl_somatic_ss_l_l,
    input_path("cbcl_somatic_ss_l_l.csv", date = TRUE)
)

cbcl_somatic_ss_u_l <- get_cbcl_syndrome_scale(
    syndrome = "somatic",
    mh_p_cbcl,
    raw = TRUE,
    subjects = uninjured_subjects,
    t = 2
)
write_csv(
    cbcl_somatic_ss_u_l,
    input_path("cbcl_somatic_ss_u_l.csv", date = TRUE)
)

```

#### Social complaints

```{r}

## At baseline
cbcl_social_ss_0_0 <- get_cbcl_syndrome_scale(
    syndrome = "social",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_0,
    t = 0
)
write_csv(
    cbcl_social_ss_0_0,
    input_path("cbcl_social_ss_0_0.csv", date = TRUE)
)

cbcl_social_ss_l_0 <- get_cbcl_syndrome_scale(
    syndrome = "social",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_l,
    t = 0
)
write_csv(
    cbcl_social_ss_l_0,
    input_path("cbcl_social_ss_l_0.csv", date = TRUE)
)

cbcl_social_ss_u_0 <- get_cbcl_syndrome_scale(
    syndrome = "social",
    mh_p_cbcl,
    raw = TRUE,
    subjects = uninjured_subjects,
    t = 0
)
write_csv(
    cbcl_social_ss_u_0,
    input_path("cbcl_social_ss_u_0.csv", date = TRUE)
)

## At 2yfu
cbcl_social_ss_0_l <- get_cbcl_syndrome_scale(
    syndrome = "social",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_0,
    t = 2
)
write_csv(
    cbcl_social_ss_0_l,
    input_path("cbcl_social_ss_0_l.csv", date = TRUE)
)

cbcl_social_ss_l_l <- get_cbcl_syndrome_scale(
    syndrome = "social",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_l,
    t = 2
)
write_csv(
    cbcl_social_ss_l_l,
    input_path("cbcl_social_ss_l_l.csv", date = TRUE)
)

cbcl_social_ss_u_l <- get_cbcl_syndrome_scale(
    syndrome = "social",
    mh_p_cbcl,
    raw = TRUE,
    subjects = uninjured_subjects,
    t = 2
)
write_csv(
    cbcl_social_ss_u_l,
    input_path("cbcl_social_ss_u_l.csv", date = TRUE)
)

```

#### Thought complaints

```{r}

## At baseline
cbcl_thought_ss_0_0 <- get_cbcl_syndrome_scale(
    syndrome = "thought",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_0,
    t = 0
)
write_csv(
    cbcl_thought_ss_0_0,
    input_path("cbcl_thought_ss_0_0.csv", date = TRUE)
)

cbcl_thought_ss_l_0 <- get_cbcl_syndrome_scale(
    syndrome = "thought",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_l,
    t = 0
)
write_csv(
    cbcl_thought_ss_l_0,
    input_path("cbcl_thought_ss_l_0.csv", date = TRUE)
)

cbcl_thought_ss_u_0 <- get_cbcl_syndrome_scale(
    syndrome = "thought",
    mh_p_cbcl,
    raw = TRUE,
    subjects = uninjured_subjects,
    t = 0
)
write_csv(
    cbcl_thought_ss_u_0,
    input_path("cbcl_thought_ss_u_0.csv", date = TRUE)
)

## At 2yfu
cbcl_thought_ss_0_l <- get_cbcl_syndrome_scale(
    syndrome = "thought",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_0,
    t = 2
)
write_csv(
    cbcl_thought_ss_0_l,
    input_path("cbcl_thought_ss_0_l.csv", date = TRUE)
)

cbcl_thought_ss_l_l <- get_cbcl_syndrome_scale(
    syndrome = "thought",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_l,
    t = 2
)
write_csv(
    cbcl_thought_ss_l_l,
    input_path("cbcl_thought_ss_l_l.csv", date = TRUE)
)

cbcl_thought_ss_u_l <- get_cbcl_syndrome_scale(
    syndrome = "thought",
    mh_p_cbcl,
    raw = TRUE,
    subjects = uninjured_subjects,
    t = 2
)
write_csv(
    cbcl_thought_ss_u_l,
    input_path("cbcl_thought_ss_u_l.csv", date = TRUE)
)

```

#### Attention complaints

```{r}

## At baseline
cbcl_attention_ss_0_0 <- get_cbcl_syndrome_scale(
    syndrome = "attention",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_0,
    t = 0
)
write_csv(
    cbcl_attention_ss_0_0,
    input_path("cbcl_attention_ss_0_0.csv", date = TRUE)
)

cbcl_attention_ss_l_0 <- get_cbcl_syndrome_scale(
    syndrome = "attention",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_l,
    t = 0
)
write_csv(
    cbcl_attention_ss_l_0,
    input_path("cbcl_attention_ss_l_0.csv", date = TRUE)
)

cbcl_attention_ss_u_0 <- get_cbcl_syndrome_scale(
    syndrome = "attention",
    mh_p_cbcl,
    raw = TRUE,
    subjects = uninjured_subjects,
    t = 0
)
write_csv(
    cbcl_attention_ss_u_0,
    input_path("cbcl_attention_ss_u_0.csv", date = TRUE)
)

## At 2yfu
cbcl_attention_ss_0_l <- get_cbcl_syndrome_scale(
    syndrome = "attention",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_0,
    t = 2
)
write_csv(
    cbcl_attention_ss_0_l,
    input_path("cbcl_attention_ss_0_l.csv", date = TRUE)
)

cbcl_attention_ss_l_l <- get_cbcl_syndrome_scale(
    syndrome = "attention",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_l,
    t = 2
)
write_csv(
    cbcl_attention_ss_l_l,
    input_path("cbcl_attention_ss_l_l.csv", date = TRUE)
)

cbcl_attention_ss_u_l <- get_cbcl_syndrome_scale(
    syndrome = "attention",
    mh_p_cbcl,
    raw = TRUE,
    subjects = uninjured_subjects,
    t = 2
)
write_csv(
    cbcl_attention_ss_u_l,
    input_path("cbcl_attention_ss_u_l.csv", date = TRUE)
)

```

#### Rulebreak complaints

```{r}

## At baseline
cbcl_rulebreak_ss_0_0 <- get_cbcl_syndrome_scale(
    syndrome = "rulebreak",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_0,
    t = 0
)
write_csv(
    cbcl_rulebreak_ss_0_0,
    input_path("cbcl_rulebreak_ss_0_0.csv", date = TRUE)
)

cbcl_rulebreak_ss_l_0 <- get_cbcl_syndrome_scale(
    syndrome = "rulebreak",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_l,
    t = 0
)
write_csv(
    cbcl_rulebreak_ss_l_0,
    input_path("cbcl_rulebreak_ss_l_0.csv", date = TRUE)
)

cbcl_rulebreak_ss_u_0 <- get_cbcl_syndrome_scale(
    syndrome = "rulebreak",
    mh_p_cbcl,
    raw = TRUE,
    subjects = uninjured_subjects,
    t = 0
)
write_csv(
    cbcl_rulebreak_ss_u_0,
    input_path("cbcl_rulebreak_ss_u_0.csv", date = TRUE)
)

## At 2yfu
cbcl_rulebreak_ss_0_l <- get_cbcl_syndrome_scale(
    syndrome = "rulebreak",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_0,
    t = 2
)
write_csv(
    cbcl_rulebreak_ss_0_l,
    input_path("cbcl_rulebreak_ss_0_l.csv", date = TRUE)
)

cbcl_rulebreak_ss_l_l <- get_cbcl_syndrome_scale(
    syndrome = "rulebreak",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_l,
    t = 2
)
write_csv(
    cbcl_rulebreak_ss_l_l,
    input_path("cbcl_rulebreak_ss_l_l.csv", date = TRUE)
)

cbcl_rulebreak_ss_u_l <- get_cbcl_syndrome_scale(
    syndrome = "rulebreak",
    mh_p_cbcl,
    raw = TRUE,
    subjects = uninjured_subjects,
    t = 2
)
write_csv(
    cbcl_rulebreak_ss_u_l,
    input_path("cbcl_rulebreak_ss_u_l.csv", date = TRUE)
)

```

#### Aggressive complaints

```{r}

## At baseline
cbcl_aggressive_ss_0_0 <- get_cbcl_syndrome_scale(
    syndrome = "aggressive",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_0,
    t = 0
)
write_csv(
    cbcl_aggressive_ss_0_0,
    input_path("cbcl_aggressive_ss_0_0.csv", date = TRUE)
)

cbcl_aggressive_ss_l_0 <- get_cbcl_syndrome_scale(
    syndrome = "aggressive",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_l,
    t = 0
)
write_csv(
    cbcl_aggressive_ss_l_0,
    input_path("cbcl_aggressive_ss_l_0.csv", date = TRUE)
)

cbcl_aggressive_ss_u_0 <- get_cbcl_syndrome_scale(
    syndrome = "aggressive",
    mh_p_cbcl,
    raw = TRUE,
    subjects = uninjured_subjects,
    t = 0
)
write_csv(
    cbcl_aggressive_ss_u_0,
    input_path("cbcl_aggressive_ss_u_0.csv", date = TRUE)
)

## At 2yfu
cbcl_aggressive_ss_0_l <- get_cbcl_syndrome_scale(
    syndrome = "aggressive",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_0,
    t = 2
)
write_csv(
    cbcl_aggressive_ss_0_l,
    input_path("cbcl_aggressive_ss_0_l.csv", date = TRUE)
)

cbcl_aggressive_ss_l_l <- get_cbcl_syndrome_scale(
    syndrome = "aggressive",
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subjects_l,
    t = 2
)
write_csv(
    cbcl_aggressive_ss_l_l,
    input_path("cbcl_aggressive_ss_l_l.csv", date = TRUE)
)

cbcl_aggressive_ss_u_l <- get_cbcl_syndrome_scale(
    syndrome = "aggressive",
    mh_p_cbcl,
    raw = TRUE,
    subjects = uninjured_subjects,
    t = 2
)
write_csv(
    cbcl_aggressive_ss_u_l,
    input_path("cbcl_aggressive_ss_u_l.csv", date = TRUE)
)

```

#### No need for CBCL imputation

```{r}

#missing_cbcl <- mh_p_cbcl |>
#    dplyr::select(
#        "subjectkey",
#        dplyr::contains("cbcl_scr_syn"),
#    ) |>
#    dplyr::select(
#        dplyr::ends_with("r")
#    )
#
#
#colnames(missing_cbcl)
#
#missing_cbcl$"nas" <- rowSums(is.na(missing_cbcl))
#
#hist(missing_cbcl$"nas")

# Next steps: DON'T IMPUTE THE CBCL!

## Save this analysis for later - it requires post-imputed data
# calc_delta <- function(df0, df2) {
#    # Reduce dataframes to only those subjects in common
#    common_subs <- common_subjects(list(df0, df2))
#    df0 <- df0 |>
#        dplyr::filter(df0$"subjectkey" %in% common_subs) |>
#        col_to_num_all_possible()
#    df2 <- df2 |>
#        dplyr::filter(df2$"subjectkey" %in% common_subs) |>
#        col_to_num_all_possible()
#    df_delta <- df0
#    features <- colnames(df0)[-1]
#    for (feature in features) {
#        df_delta[, feature] <- df2[, feature] - df0[, feature]
#    }
#    colnames(df_delta) <-
#        c("subjectkey", paste0(colnames(df_delta[-1]), "_delta"))
#    return(df_delta)
# }
#
# calc_delta(cbcl_rulebreak_ss_0_0, cbcl_rulebreak_ss_0_l)
#
#
## Quick and dirty check to see how these measures change for the l subjects
# a <- list(
#    cbcl_headaches_delta_l,
#    cbcl_nausea_delta_l,
#    cbcl_vomiting_delta_l,
#    cbcl_dizzy_delta_l,
#    cbcl_overtired_delta_l,
#    cbcl_sleeping_more_delta_l,
#    cbcl_sleeping_less_delta_l,
#    cbcl_depress_r_delta_l,
#    cbcl_anxiety_r_delta_l,
#    cbcl_attention_r_delta_l,
#    cbcl_aggressive_r_delta_l,
#    cbcl_depress_delta_l,
#    cbcl_anxiety_delta_l,
#    cbcl_attention_delta_l,
#    cbcl_aggressive_delta_l)
#
# b <- merge_df_list(a) |>
#    na.omit() |>
#    dplyr::select(-dplyr::contains(c("subjectkey", "r")))
#
# pheatmap::pheatmap(b)

```

### Sleep disturbance scale

```{r}
ph_p_sds <- abcd_load(core_path("physical-health/ph_p_sds.csv"))

# Baseline
sds_total_probs_0_0 <- get_sds_total_probs(
    ph_p_sds,
    mtbi_subjects_0,
    t = 0
)
write_csv(
    sds_total_probs_0_0,
    input_path(
        "sds_total_probs_0_0.csv",
        date = TRUE
    )
sds_total_probs_l_0 <- get_sds_total_probs(
    ph_p_sds,
    mtbi_subjects_l,
    t = 0
)
write_csv(
    sds_total_probs_l_0,
    input_path(
        "sds_total_probs_l_0.csv",
        date = TRUE
    )
)

sds_total_probs_u_0 <- get_sds_total_probs(
    ph_p_sds,
    uninjured_subjects,
    t = 0
)
write_csv(
    sds_total_probs_u_0,
    input_path(
        "sds_total_probs_u_0.csv",
        date = TRUE
    )
)


# 2yfu
sds_total_probs_0_l <- get_sds_total_probs(
    ph_p_sds,
    mtbi_subjects_0,
    t = 2
)
write_csv(
    sds_total_probs_0_l,
    input_path(
        "sds_total_probs_0_l.csv",
        date = TRUE
    )
)

sds_total_probs_l_l <- get_sds_total_probs(
    ph_p_sds,
    mtbi_subjects_l,
    t = 2
)
write_csv(
    sds_total_probs_l_l,
    input_path(
        "sds_total_probs_l_l.csv",
        date = TRUE
    )
)

sds_total_probs_u_l <- get_sds_total_probs(
    ph_p_sds,
    uninjured_subjects,
    t = 2
)
write_csv(
    sds_total_probs_u_l,
    input_path(
        "sds_total_probs_u_l.csv",
        date = TRUE
    )
)
```

# R Session Information

The analysis in this script were last completed on September 20th, 2023, under the following conditions:

R version 4.3.1 (2023-06-16)
Platform: x86_64-pc-linux-gnu (64-bit)
Running under: CentOS Linux 7 (Core)

Matrix products: default
BLAS:   /hpf/tools/centos7/R/4.3.1/lib64/R/lib/libRblas.so
LAPACK: /hpf/tools/centos7/R/4.3.1/lib64/R/lib/libRlapack.so;  LAPACK version 3.11.0

locale:
 [1] LC_CTYPE=en_US.UTF-8       LC_NUMERIC=C
 [3] LC_TIME=en_US.UTF-8        LC_COLLATE=en_US.UTF-8
 [5] LC_MONETARY=en_US.UTF-8    LC_MESSAGES=en_US.UTF-8
 [7] LC_PAPER=en_US.UTF-8       LC_NAME=C
 [9] LC_ADDRESS=C               LC_TELEPHONE=C
[11] LC_MEASUREMENT=en_US.UTF-8 LC_IDENTIFICATION=C

time zone: America/Toronto
tzcode source: system (glibc)

attached base packages:
[1] stats     graphics  grDevices utils     datasets  methods   base

other attached packages:
[1] abcdutils_0.1.1 knitr_1.43      here_1.0.1      dplyr_1.1.2
[5] readr_2.1.4     ggplot2_3.4.2   colorout_1.2-2

loaded via a namespace (and not attached):
 [1] crayon_1.5.2      vctrs_0.6.3       cli_3.6.1         xfun_0.39
 [5] rlang_1.1.1       purrr_1.0.1       generics_0.1.3    data.table_1.14.8
 [9] bit_4.0.5         glue_1.6.2        colorspace_2.1-0  rprojroot_2.0.3
[13] hms_1.1.3         scales_1.2.1      fansi_1.0.4       grid_4.3.1
[17] munsell_0.5.0     tibble_3.2.1      tzdb_0.4.0        lifecycle_1.0.3
[21] compiler_4.3.1    pkgconfig_2.0.3   R6_2.5.1          tidyselect_1.2.0
[25] utf8_1.2.3        parallel_4.3.1    vroom_1.6.3       pillar_1.9.0
[29] magrittr_2.0.3    bit64_4.0.5       tools_4.3.1       withr_2.5.0
[33] gtable_0.3.3

Output obtained from the following command:

```{r eval = FALSE}
writeLines(capture.output(sessionInfo()), "sessionInfo.txt")
```

From: https://stackoverflow.com/a/21967272/16626788
