# Data extraction

## Libraries, path names, and importing of raw data

```{r}
library(ggplot2)
library(readr)
library(dplyr)
library(here)
library(knitr)
library(abcdutils)

core_path <- path_maker(here(paste0("data/abcd/core")))
input_path <- path_maker(here(paste0("data/abcd/inputs")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))

# Ohio TBI screen
ph_p_otbi <- abcd_load(
    core_path("physical-health/ph_p_otbi.csv")
)

# Age
abcd_y_lt <- abcd_load(
    core_path("abcd-general/abcd_y_lt.csv")
)

# Pubertal development scale, youth report
ph_y_pds <- abcd_load(
    core_path("physical-health/ph_y_pds.csv")
)

# Pubertal development scale, parent report
ph_p_pds <- abcd_load(
    core_path("physical-health/ph_p_pds.csv")
)

# Parent report of gender identity
gish_p_gi <- abcd_load(
    core_path("gender-identity-sexual-health/gish_p_gi.csv")
)

# Youth report of gender identity
gish_y_gi <- abcd_load(
    core_path("gender-identity-sexual-health/gish_y_gi.csv")
)

# Demographic data
abcd_p_demo <- abcd_load(
    core_path("abcd-general/abcd_p_demo.csv")
)

# Medical history
ph_p_mhx <- abcd_load(
    core_path("physical-health/ph_p_mhx.csv")
)

# Subcortical volumes (ASEG)
mri_y_smr_vol_aseg <- abcd_load(
    core_path("imaging/mri_y_smr_vol_aseg.csv")
)

# Desikan cortical thicknesses
mri_y_smr_thk_dsk <- abcd_load(
    core_path("imaging/mri_y_smr_thk_dsk.csv")
)

# Desikan cortical surface areas
mri_y_smr_area_dsk <- abcd_load(
    core_path("imaging/mri_y_smr_area_dsk.csv")
)

# Neurite density (AtlasTrack, all fibers)
mri_y_rsi_rnd_at <- abcd_load(
    core_path("imaging/mri_y_rsi_rnd_at.csv")
)

# Neurite density (Desikan, peri-cortical WM)
mri_y_rsi_rnd_wm_dsk <- abcd_load(
    core_path("imaging/mri_y_rsi_rnd_wm_dsk.csv")
)

# Neurite density (Destriux, peri-cortical WM)
mri_y_rsi_rnd_wm_dst <- abcd_load(
    core_path("imaging/mri_y_rsi_rnd_wm_dst.csv")
)

# rs-fMRI cortical-cortical correlations
mri_y_rsfmr_cor_gp_gp <- abcd_load(
    core_path("imaging/mri_y_rsfmr_cor_gp_gp.csv")
)

# rs-fMRI cortical-subcortical correlations
mri_y_rsfmr_cor_gp_aseg <- abcd_load(
    core_path("imaging/mri_y_rsfmr_cor_gp_aseg.csv")
)

# Loneliness
mh_y_or <- abcd_load(
    core_path("mental-health/mh_y_or.csv")
)

# Screen time
nt_p_stq <- abcd_load(
    core_path("novel-technologies/nt_p_stq.csv")
)

# Participation in sports and activities
ph_p_saiq <- abcd_load(
    core_path("physical-health/ph_p_saiq.csv")
)

# Exercise habits
ph_y_yrb <- abcd_load(
    core_path("physical-health/ph_y_yrb.csv")
)

# Youth report of prosocial behaviour
ce_y_psb <- abcd_load(
    core_path("culture-environment/ce_y_psb.csv")
)

# Parent report of prosocial behaviour
ce_p_psb <- abcd_load(
    core_path("culture-environment/ce_p_psb.csv")
)

# Youth report of family function
ce_y_fes <- abcd_load(
    core_path("culture-environment/ce_y_fes.csv")
)

# Parent report of family function
ce_p_fes <- abcd_load(
    core_path("culture-environment/ce_p_fes.csv")
)

# Parent ASEBA self-report (psychopathology)
mh_p_asr <- abcd_load(
    core_path("mental-health/mh_p_asr.csv")
)

# Parent report of child behaviour (CBCL)
mh_p_cbcl <- abcd_load(
    core_path("mental-health/mh_p_cbcl.csv")
)

# Sleep disturbance scale
ph_p_sds <- abcd_load(
    core_path("physical-health/ph_p_sds.csv")
)
```

## Subjects

All information required for identifying children at a chronic stage following mTBI as of baseline data collection is available in the `abcd_otbi01.txt` file, and in the `abcd_lpohstbi01.txt` file for longitudinal data.
To identify subjects at a chronic stage post-mTBI, two intermediate pieces of information must be calculated from the original dataset:

* identifying which head injuries were mTBIs
* identifying the time since the most recent mTBI

The structure of the Ohio State TBI screen as used for ABCD data collection was not completely compatible with the most commonly used definition of mTBI @WYA25C6X#Blennow_Etal_2016, which requires at least one of the following:

* Any period of loss of consciousness
* Any loss of memory
* Any alteration in mental state
* Focal neurological deficits

but none of the following:

* LOC over 30 minutes
* A Glasgow Coma Scale score below 13
* Post-traumatic amnesia (PTA) greater than 24 hours

A few aspects of the data collection process in the ABCD study precluded the usage of this definition:

* No information was collected regarding the GCS
* Feeling dazed and PTA were combined into a single variable, making it unclear which combination of symptoms was present
* No information was collected regarding the duration of feeling dazed or experiencing PTA

Consequently, I defined mTBI as any injury that resulted in **either**:

1. LOC for less than 30 minutes (including 0 minutes) **AND** any duration of memory loss / feeling dazed
2. LOC for less than 30 minutes but greater than 0 minutes

The fixed nature of the questionnaire also meant that some information about multiple mTBIs sustained in the same way or about a very large number of mTBIs throughout a child's life could have been lost (see the previous section on identifying children with a history of mTBI).
For my analyses, I assume these edge cases are not common enough to meaningfully change any obtained conclusions.

```{r}
# mTBI subjects (latest mTBI at least 3 months prior to baseline collection
mtbi_subjects <- get_mtbi_subjects(ph_p_otbi, abcd_y_lt, min_mpi = 3, t = 0)

# Uninjured subjects (those with no injuries as of baseline collection)
uninjured_subjects <- get_uninjured_subjects(ph_p_otbi, abcd_y_lt, t = 0)

write_csv(mtbi_subjects, sub_path("mtbi_subjects.csv", date = TRUE))
write_csv(uninjured_subjects, sub_path("uninjured_subjects.csv", date = TRUE))

# Note that the longitudinal subjects have not been filtered in any way based on
#  whether or not they also had an mTBI at baseline or another timepoint
mtbi_subjects <- read_csv(sub_path("2024_02_13_mtbi_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2024_02_13_uninjured_subjects.csv"))
```

A few types of injuries were handled differently from the rest in the above code.
For the `other_loc` injury type, the questionnaire asked for a total number of injuries with LOC as well as a total number of injuries with LOC above 30 minutes.
If their difference was above 0, they were labelled as having had an mTBI.
For the `other_multi` and `other_other_multi` injury types, insufficient information was provided to determine the severity of the associated injuries.

For my analyses, I consider 3 months to be the threshold at which an mTBI patient enters a chronic stage post-injury.

## Input variables

### Acute symptoms

The acute symptom data is found within the TBI dataset.
We are interesed in the following acute symptoms:

* mechanism of injury
* age
* LOC information
* Feeling dazed or having memory loss

A few more intermediate columns need to be added to isolate these variables for the most recent mTBIs of the subjects.

#### Feeling dazed

```{r}
as_mtbi_mem_daze_mtbi <- get_mtbi_mem_daze(
    ph_p_otbi,
    abcd_y_lt,
    mtbi_subjects,
    t = 0
)

write_csv(
    as_mtbi_mem_daze_mtbi,
    input_path("as_mem_daze_mtbi.csv", date = TRUE)
)
```

#### Mechanism of injury

```{r}
as_mechanism_mtbi <- get_mtbi_mechanism(
    ph_p_otbi,
    abcd_y_lt,
    mtbi_subjects,
    t = 0
)

write_csv(
    as_mechanism_mtbi,
    input_path("as_mechanism_mtbi.csv", date = TRUE)
)
```

#### Loss of consciousness

```{r}
# Baseline values of subjects with injuries prior to baseline
as_loc_mtbi <-
    get_mtbi_loc(ph_p_otbi, abcd_y_lt, mtbi_subjects, t = 0)

write_csv(
    as_loc_mtbi,
    input_path("as_loc_mtbi.csv", date = TRUE)
)
```

### Demographics

Demographic variables included in the analyses are:

* Interview age
* Injury age
* Sex
* Race
* Household income
* Pubertal status

#### Interview age

```{r}
d_interview_age_mtbi <- get_interview_age(
    abcd_y_lt,
    mtbi_subjects,
    t = 0
)

write_csv(
    d_interview_age_mtbi,
    input_path("d_interview_age_mtbi.csv", TRUE)
)

d_interview_age_uninj <- get_interview_age(
    abcd_y_lt,
    uninjured_subjects,
    t = 0
)

write_csv(
    d_interview_age_uninj,
    input_path("d_interview_age_uninj.csv", TRUE)
)
```

#### Injury age

```{r}
d_mtbi_age_mtbi <- get_mtbi_age(ph_p_otbi, abcd_y_lt, mtbi_subjects, t = 0)

write_csv(
    d_mtbi_age_mtbi,
    input_path("d_mtbi_age_mtbi.csv", TRUE)
)
```

#### Sex at birth

```{r}
d_sex_mtbi <- get_sex(
    gish_p_gi,
    mtbi_subjects,
    t = 0,
    as_numeric = TRUE
)

write_csv(
    d_sex_mtbi,
    input_path("d_sex_mtbi.csv", TRUE)
)

d_sex_uninj <- get_sex(
    gish_p_gi,
    uninjured_subjects,
    t = 0,
    as_numeric = TRUE
)

write_csv(
    d_sex_uninj,
    input_path("d_sex_uninj.csv", TRUE)
)
```

#### Household income

```{r}
d_income_mtbi <- get_income(abcd_p_demo, mtbi_subjects, t = 0)

write_csv(
    d_income_mtbi,
    input_path("d_income_mtbi.csv", TRUE)
)

d_income_uninj <- get_income(abcd_p_demo, uninjured_subjects, t = 0)

write_csv(
    d_income_uninj,
    input_path("d_income_uninj.csv", TRUE)
)
```

#### Race

```{r}

abcd_p_demo$"race_ethnicity"

race_data <- abcd_p_demo |>
    dplyr::select(
        "subjectkey",
        "demo_ethn_v2",
        "demo_race_a_p___10", # white
        "demo_race_a_p___11", # black/african american
        "demo_race_a_p___12", # american indian
        "demo_race_a_p___13", # alaskan native
        "demo_race_a_p___14", # native hawaiian
        "demo_race_a_p___15", # guamanian
        "demo_race_a_p___16", # samoan
        "demo_race_a_p___17", # other pacific islander
        "demo_race_a_p___18", # asian indian
        "demo_race_a_p___19", # chinese
        "demo_race_a_p___20", # filipino
        "demo_race_a_p___21", # japanese
        "demo_race_a_p___22", # korean
        "demo_race_a_p___23", # vietnamese
        "demo_race_a_p___24", # other asian
        "demo_race_a_p___25", # other race
        "demo_race_a_p___99", # refuse to answer
        "demo_race_a_p___77"  # don't know
    )

# This approach will preserve NAs
race_data$"white" <- ifelse(
    race_data$"demo_race_a_p___10" == 1,
    yes = 1, no = 0
)

race_data$"black" <- ifelse(
    race_data$"demo_race_a_p___11" == 1,
    yes = 1, no = 0
)

race_data$"asian" <- ifelse(
    race_data$"demo_race_a_p___18" == 1 |
    race_data$"demo_race_a_p___19" == 1 |
    race_data$"demo_race_a_p___20" == 1 |
    race_data$"demo_race_a_p___21" == 1 |
    race_data$"demo_race_a_p___22" == 1 |
    race_data$"demo_race_a_p___23" == 1 |
    race_data$"demo_race_a_p___24" == 1,
    yes = 1, no = 0
)

# american indian / alaskan native
race_data$"aian" <- ifelse(
    race_data$"demo_race_a_p___12" == 1 |
    race_data$"demo_race_a_p___13" == 1,
    yes = 1, no = 0
)

# native hawaiian / pacific islander
race_data$"nhpi" <- ifelse(
    race_data$"demo_race_a_p___14" == 1 |
    race_data$"demo_race_a_p___15" == 1 |
    race_data$"demo_race_a_p___16" == 1 |
    race_data$"demo_race_a_p___17" == 1,
    yes = 1, no = 0
)

# hispanic
race_data$"hispanic" <- ifelse(
    race_data$"demo_ethn_v2" == 1,
    yes = 1, no = 0
)

# other races
race_data$"oth" <- ifelse(
    race_data$"demo_race_a_p___25" == 1,
    yes = 1, no = 0
)

race_data$"race_eth" <- NA
race_data$"race_eth"[race_data$"white" == 1] <- 1 # non-hispanic white
race_data$"race_eth"[race_data$"black" == 1] <- 2 # non-hispanic black
race_data$"race_eth"[race_data$"aian" == 1] <- 5 # am. indian, al. native
race_data$"race_eth"[race_data$"nhpi" == 1] <- 6 # nat. hawaii, pac. isl
race_data$"race_eth"[race_data$"asian" == 1] <- 4 # asian
race_data$"race_eth"[race_data$"other" == 1] <- 8 # other
race_data$"race_eth"[race_data$"demo_race_a_p___77" == 1] <- NA # don't know
race_data$"race_eth"[race_data$"demo_race_a_p___99" == 1] <- NA # no answer

race_data$"race_eth"[race_data$"mixed" == 1] <- NA # no answer

race_data

race_data

race_data <- race_data |>
    dplyr::select(
        "subjectkey",
        "white",
        "black",
        "asian",
        "aian",
        "nhpi",
        "oth"
    )

race_data$"count" <- race_data$"white" +
    race_data$"black" +
    race_data$"asian" +
    race_data$"aian" +
    race_data$"nhpi" +
    race_data$"oth"

race_data$"mixed" <- ifelse(
    race_data$"count" > 1,
    yes = 1, no = 0
)

d_race_mtbi <- get_race(
    abcd_p_demo,
    mtbi_subjects,
    "condensed_undummied",
    t = 0
)

race_data <- race_data |>
    dplyr::select(
        "white",
        "black",
        "asian",
        "aian",
        "nhpi",
        "oth"
    )

race_data[is.na(race_data)] <- 0



















head(race_data)






write_csv(
    d_race_mtbi,
    input_path("d_race_mtbi.csv", TRUE)
)


d_race_uninj <- get_race(
    abcd_p_demo,
    uninjured_subjects,
    "condensed_undummied",
    t = 0
)

write_csv(d_race_uninj, input_path("d_race_uninj.csv", TRUE))
```

#### Pubertal status

```{r}
d_pubertal_status_mtbi <- get_pubertal_status(
    ph_p_pds,
    ph_y_pds,
    mtbi_subjects,
    t = 0
)

write_csv(
    d_pubertal_status_mtbi,
    input_path("d_pubertal_status_mtbi.csv", TRUE)
)

d_pubertal_status_uninj <- get_pubertal_status(
    ph_p_pds,
    ph_y_pds,
    uninjured_subjects,
    t = 0
)

write_csv(
    d_pubertal_status_uninj,
    input_path("d_pubertal_status_uninj.csv", TRUE)
)
```

### Medical history

Medical history variables of interest include:

1. Number of previous head injuries
2. History of headaches (binary)

#### History of headaches

```{r}
mh_headaches_mtbi <- get_headaches(
    ph_p_mhx,
    mtbi_subjects,
    t = 0
)

write_csv(
    mh_headaches_mtbi, input_path("mh_headaches_mtbi.csv", date = TRUE)
)

mh_headaches_uninj <- get_headaches(
    ph_p_mhx,
    uninjured_subjects,
    t = 0
)

write_csv(
    mh_headaches_uninj, input_path("mh_headaches_uninj.csv", date = TRUE)
)
```

#### Number of previous mTBIs

```{r}
mh_mtbi_count_mtbi <- get_mtbi_count(ph_p_otbi,
    abcd_y_lt,
    mtbi_subjects,
    t = 0
)

write_csv(
    mh_mtbi_count_mtbi, input_path("mh_mtbi_count_mtbi.csv", date = TRUE)
)

mh_mtbi_count_uninj <- get_mtbi_count(ph_p_otbi,
    abcd_y_lt,
    uninjured_subjects,
    t = 0
)

write_csv(
    mh_mtbi_count_uninj, input_path("mh_mtbi_count_uninj.csv", date = TRUE)
)
```

### Neuroimaging

Variables of interest related to brain structure and function include:

* Structural: T1-weighted multishell diffusion-weighted MRI data
* Diffusion: Neurite density (restricted spectrum imaging)
* Functional: resting-state functional MRI data

The 2019 publication by Hagler et al. @UD6THTQZ##Hagler_Etal_2019 outlines the neuroimaging data present in the ABCD dataset in detail.

#### Structural MRI

The sMRI variables of interest include subcortical volumes, and cortical thicknesses, and cortical surface areas.

For cortical surface areas, the relevant file is abcd_mrisdp10201, which contains the cortical surface areas of ~150 regions (variables `mrisdp_*` where * ranges from 1 to 151).

For cortical thicknesses, the relevant file is abcd_mrisdp10201, which contains the cortical thickness of ~150 regions (variables `mrisdp_*` where * ranges from 303 to 453).

##### Subcortical volume

```{r}
sm_subc_v_mtbi <- get_subc_v(
    mri_y_smr_vol_aseg,
    mtbi_subjects,
    t = 0
)

write_csv(
    sm_subc_v_mtbi, input_path("sm_subc_v_mtbi.csv", date = TRUE)
)

sm_subc_v_uninj <- get_subc_v(
    mri_y_smr_vol_aseg,
    uninjured_subjects,
    t = 0
)

write_csv(
    sm_subc_v_uninj, input_path("sm_subc_v_uninj.csv", date = TRUE)
)
```

##### Cortical thickness

Both the Desikan and Destrieux cortical parcellations could have been used for the cortical imaging data collected below.
A comparison between the two can be found in the appendix.
Because there happens to be a few more participants with calculated Desikan parcellations, that is what is used here.

```{r}
sm_cort_t_mtbi <- get_cort_t(
    mri_y_smr_thk_dsk,
    mtbi_subjects,
    t = 0
)

write_csv(
    sm_cort_t_mtbi, input_path("sm_cort_t_mtbi.csv", date = TRUE)
)

sm_cort_t_uninj <- get_cort_t(
    mri_y_smr_thk_dsk,
    uninjured_subjects,
    t = 0
)

write_csv(
    sm_cort_t_uninj, input_path("sm_cort_t_uninj.csv", date = TRUE)
)
```

##### Cortical surface areas

```{r}
sm_cort_sa_mtbi <- get_cort_sa(
    mri_y_smr_area_dsk, mtbi_subjects, t = 0
)

write_csv(
    sm_cort_sa_mtbi, input_path("sm_cort_sa_mtbi.csv", date = TRUE)
)

sm_cort_sa_uninj <- get_cort_sa(
    mri_y_smr_area_dsk, uninjured_subjects, t = 0
)

write_csv(
    sm_cort_sa_uninj, input_path("sm_cort_sa_uninj.csv", date = TRUE)
)
```

#### Diffusion MRI

We are interested in the neurite density measures of white matter regions in the brain.
Previously, these measures were found in variables containing the string "rsindwm_cdk" within the file `mri_rsi_p102.txt`.
A change anounced in the ABCD 4.0 MRI release notes indicates that neurite density is now referred to as "restricted normalized directional" and that the relevant white matter variables contain the string "rsirndwm" within the file `abcd_drsip201.txt`.

See diffusion MRI chapter in appendix for full details.

##### White matter neurite densities

Some potential summary neurite density meeasures:

* dmri_rsirnd_fib_allfib (AtlasTrack fiber segmentation, all fibers)
* dmri_rsirndwm_cdk_mean (Desikan cortical parcellation peri-cortical white matter mean)

```{r}
# White matter neurite densities
dm_all_wmnd_mtbi <- get_all_wmnd(
    mri_y_rsi_rnd_at,
    mri_y_rsi_rnd_wm_dsk,
    subjects = mtbi_subjects,
    t = 0
)

write_csv(
    dm_all_wmnd_mtbi, input_path("dm_all_wmnd_mtbi.csv", date = TRUE)
)

dm_all_wmnd_uninj <- get_all_wmnd(
    mri_y_rsi_rnd_at,
    mri_y_rsi_rnd_wm_dsk,
    subjects = uninjured_subjects,
    t = 0
)

write_csv(
    dm_all_wmnd_uninj, input_path("dm_all_wmnd_uninj.csv", date = TRUE)
)
```

#### Resting-state functional MRI

We are interested in the following rs-fMRI measures:

- Gordon network (cortical) correlations
- Subcortical correlations

##### Cortical parcellation network correlations

```{r}
rm_gord_cor_mtbi <- get_gord_cor(
    mri_y_rsfmr_cor_gp_gp,
    mtbi_subjects,
    t = 0
)

write_csv(
    rm_gord_cor_mtbi, input_path("rm_gord_cor_mtbi.csv", date = TRUE)
)

rm_gord_cor_uninj <- get_gord_cor(
    mri_y_rsfmr_cor_gp_gp,
    uninjured_subjects,
    t = 0
)

write_csv(
    rm_gord_cor_uninj, input_path("rm_gord_cor_uninj.csv", date = TRUE)
)
```

##### Subcortical parcellation network correlations

```{r}
rm_subc_cor_mtbi <- get_subc_cor(
    mri_y_rsfmr_cor_gp_aseg,
    mtbi_subjects,
    t = 0
)

write_csv(
    rm_subc_cor_mtbi, input_path("rm_subc_cor_mtbi.csv", date = TRUE)
)

rm_subc_cor_uninj <- get_subc_cor(
    mri_y_rsfmr_cor_gp_aseg,
    uninjured_subjects,
    t = 0
)

write_csv(
    rm_subc_cor_uninj, input_path("rm_subc_cor_uninj.csv", date = TRUE)
)
```

### Psychosocial resilience

Psychosocial factors of interest include:

#### Loneliness

```{r}
p_loneliness_mtbi <- get_loneliness(
    mh_y_or,
    gish_p_gi,
    mtbi_subjects,
    t = 0
)

write_csv(
    p_loneliness_mtbi, input_path("p_loneliness_mtbi.csv", date = TRUE)
)

p_loneliness_uninj <- get_loneliness(
    mh_y_or,
    gish_p_gi,
    uninjured_subjects,
    t = 0
)

write_csv(
    p_loneliness_uninj, input_path("p_loneliness_uninj.csv", date = TRUE)
)
```

#### Healthy behaviours

##### Screen time

```{r}
p_screen_time_mtbi <- get_screen_time(
    nt_p_stq,
    mtbi_subjects,
    t = 0
)

write_csv(
    p_screen_time_mtbi, input_path("p_screen_time_mtbi.csv", date = TRUE)
)

p_screen_time_uninj <- get_screen_time(
    nt_p_stq,
    uninjured_subjects,
    t = 0
)

write_csv(
    p_screen_time_uninj, input_path("p_screen_time_uninj.csv", date = TRUE)
)
```

##### Sports and activities participation

```{r}
p_sports_mtbi <- get_sports_and_activities(
    ph_p_saiq,
    mtbi_subjects,
    t = 0
)

write_csv(
    p_sports_mtbi, input_path("p_sports_mtbi.csv", date = TRUE)
)

p_sports_uninj <- get_sports_and_activities(
    ph_p_saiq,
    uninjured_subjects,
    t = 0
)

write_csv(
    p_sports_uninj, input_path("p_sports_uninj.csv", date = TRUE)
)
```

##### Exercise habits

```{r}
p_exercise_mtbi <- get_exercise(
    ph_y_yrb,
    mtbi_subjects,
    t = 0
)

write_csv(
    p_exercise_mtbi, input_path("p_exercise_mtbi.csv", date = TRUE)
)

p_exercise_uninj <- get_exercise(
    ph_y_yrb,
    uninjured_subjects,
    t = 0
)

write_csv(
    p_exercise_uninj, input_path("p_exercise_uninj.csv", date = TRUE)
)
```

#### Prosocial behaviour

```{r}
p_prosocial_mtbi <- get_prosocial_behaviour(
    ce_p_psb,
    ce_y_psb,
    mtbi_subjects,
    t = 0
)

write_csv(
    p_prosocial_mtbi, input_path("p_prosocial_mtbi.csv", date = TRUE)
)

p_prosocial_uninj <- get_prosocial_behaviour(
    ce_p_psb,
    ce_y_psb,
    uninjured_subjects,
    t = 0
)

write_csv(
    p_prosocial_uninj, input_path("p_prosocial_uninj.csv", date = TRUE)
)
```

#### Family function

```{r}
p_fam_fn_mtbi <- get_family_function(
    ce_y_fes,
    ce_p_fes,
    mtbi_subjects,
    t = 0
)
write_csv(
    p_fam_fn_mtbi,
    input_path("p_fam_fn_mtbi.csv", date = TRUE)
)

p_fam_fn_uninj <- get_family_function(
    ce_y_fes,
    ce_p_fes,
    uninjured_subjects,
    t = 0
)

write_csv(
    p_fam_fn_uninj,
    input_path("p_fam_fn_uninj.csv", date = TRUE)
)
```

#### Parent psychopathology

```{r}
p_parent_psych_mtbi <- get_parent_psychopathology(
    mh_p_asr,
    mtbi_subjects,
    t = 0,
    raw = FALSE
)

write_csv(
    p_parent_psych_mtbi,
    input_path("p_parent_psych_mtbi.csv", date = TRUE)
)

p_parent_psych_uninj <- get_parent_psychopathology(
    mh_p_asr,
    uninjured_subjects,
    t = 0,
    raw = FALSE
)

write_csv(
    p_parent_psych_uninj, input_path("p_parent_psych_uninj.csv", date = TRUE)
)
```

## Output variables

### Child Behaviour Checklist

These are collected at both baseline and longitudinal timepoints.

#### Anxious-depressed

```{r}
cbcl_anxdep_mtbi <- get_cbcl_syndrome_scale(
    syndrome = "anxdep",
    mh_p_cbcl,
    raw = FALSE,
    subjects = mtbi_subjects,
    t = 0
)

write_csv(
    cbcl_anxdep_mtbi,
    input_path("cbcl_anxdep_mtbi.csv", date = TRUE)
)

cbcl_anxdep_uninj <- get_cbcl_syndrome_scale(
    syndrome = "anxdep",
    mh_p_cbcl,
    raw = FALSE,
    subjects = uninjured_subjects,
    t = 0
)
write_csv(
    cbcl_anxdep_uninj,
    input_path("cbcl_anxdep_uninj.csv", date = TRUE)
)
```

#### Withdrawn-depressed

```{r}
cbcl_withdep_mtbi <- get_cbcl_syndrome_scale(
    syndrome = "withdep",
    mh_p_cbcl,
    raw = FALSE,
    subjects = mtbi_subjects,
    t = 0
)
write_csv(
    cbcl_withdep_mtbi,
    input_path("cbcl_withdep_mtbi.csv", date = TRUE)
)

cbcl_withdep_uninj <- get_cbcl_syndrome_scale(
    syndrome = "withdep",
    mh_p_cbcl,
    raw = FALSE,
    subjects = uninjured_subjects,
    t = 0
)
write_csv(
    cbcl_withdep_uninj,
    input_path("cbcl_withdep_uninj.csv", date = TRUE)
)
```

#### Somatic complaints

```{r}
cbcl_somatic_mtbi <- get_cbcl_syndrome_scale(
    syndrome = "somatic",
    mh_p_cbcl,
    raw = FALSE,
    subjects = mtbi_subjects,
    t = 0
)

write_csv(
    cbcl_somatic_mtbi,
    input_path("cbcl_somatic_mtbi.csv", date = TRUE)
)

cbcl_somatic_uninj <- get_cbcl_syndrome_scale(
    syndrome = "somatic",
    mh_p_cbcl,
    raw = FALSE,
    subjects = uninjured_subjects,
    t = 0
)

write_csv(
    cbcl_somatic_uninj,
    input_path("cbcl_somatic_uninj.csv", date = TRUE)
)
```

#### Social complaints

```{r}
cbcl_social_mtbi <- get_cbcl_syndrome_scale(
    syndrome = "social",
    mh_p_cbcl,
    raw = FALSE,
    subjects = mtbi_subjects,
    t = 0
)

write_csv(
    cbcl_social_mtbi,
    input_path("cbcl_social_mtbi.csv", date = TRUE)
)

cbcl_social_uninj <- get_cbcl_syndrome_scale(
    syndrome = "social",
    mh_p_cbcl,
    raw = FALSE,
    subjects = uninjured_subjects,
    t = 0
)

write_csv(
    cbcl_social_uninj,
    input_path("cbcl_social_uninj.csv", date = TRUE)
)
```

#### Thought complaints

```{r}
cbcl_thought_mtbi <- get_cbcl_syndrome_scale(
    syndrome = "thought",
    mh_p_cbcl,
    raw = FALSE,
    subjects = mtbi_subjects,
    t = 0
)
write_csv(
    cbcl_thought_mtbi,
    input_path("cbcl_thought_mtbi.csv", date = TRUE)
)

cbcl_thought_uninj <- get_cbcl_syndrome_scale(
    syndrome = "thought",
    mh_p_cbcl,
    raw = FALSE,
    subjects = uninjured_subjects,
    t = 0
)
write_csv(
    cbcl_thought_uninj,
    input_path("cbcl_thought_uninj.csv", date = TRUE)
)
```

#### Attention complaints

```{r}
cbcl_attention_mtbi <- get_cbcl_syndrome_scale(
    syndrome = "attention",
    mh_p_cbcl,
    raw = FALSE,
    subjects = mtbi_subjects,
    t = 0
)
write_csv(
    cbcl_attention_mtbi,
    input_path("cbcl_attention_mtbi.csv", date = TRUE)
)

cbcl_attention_uninj <- get_cbcl_syndrome_scale(
    syndrome = "attention",
    mh_p_cbcl,
    raw = FALSE,
    subjects = uninjured_subjects,
    t = 0
)
write_csv(
    cbcl_attention_uninj,
    input_path("cbcl_attention_uninj.csv", date = TRUE)
)
```

#### Rulebreak complaints

```{r}
cbcl_rulebreak_mtbi <- get_cbcl_syndrome_scale(
    syndrome = "rulebreak",
    mh_p_cbcl,
    raw = FALSE,
    subjects = mtbi_subjects,
    t = 0
)
write_csv(
    cbcl_rulebreak_mtbi,
    input_path("cbcl_rulebreak_mtbi.csv", date = TRUE)
)

cbcl_rulebreak_uninj <- get_cbcl_syndrome_scale(
    syndrome = "rulebreak",
    mh_p_cbcl,
    raw = FALSE,
    subjects = uninjured_subjects,
    t = 0
)
write_csv(
    cbcl_rulebreak_uninj,
    input_path("cbcl_rulebreak_uninj.csv", date = TRUE)
)
```

#### Aggressive complaints

```{r}
cbcl_aggressive_mtbi <- get_cbcl_syndrome_scale(
    syndrome = "aggressive",
    mh_p_cbcl,
    raw = FALSE,
    subjects = mtbi_subjects,
    t = 0
)

write_csv(
    cbcl_aggressive_mtbi,
    input_path("cbcl_aggressive_mtbi.csv", date = TRUE)
)

cbcl_aggressive_uninj <- get_cbcl_syndrome_scale(
    syndrome = "aggressive",
    mh_p_cbcl,
    raw = FALSE,
    subjects = uninjured_subjects,
    t = 0
)

write_csv(
    cbcl_aggressive_uninj,
    input_path("cbcl_aggressive_uninj.csv", date = TRUE)
)
```

### Sleep disturbance scale

```{r}
sds_total_probs_mtbi <- get_sds_total_probs(
    ph_p_sds,
    mtbi_subjects,
    t = 0
)

write_csv(
    sds_total_probs_mtbi,
    input_path(
        "sds_total_probs_mtbi.csv",
        date = TRUE
    )
)

sds_total_probs_uninj <- get_sds_total_probs(
    ph_p_sds,
    uninjured_subjects,
    t = 0
)
write_csv(
    sds_total_probs_uninj,
    input_path(
        "sds_total_probs_uninj.csv",
        date = TRUE
    )
)
```

# R Session Information

The analysis in this script were last completed on September 20th, 2023, under the following conditions:

R version 4.3.1 (2023-06-16)
Platform: x86_64-pc-linux-gnu (64-bit)
Running under: CentOS Linux 7 (Core)

Matrix products: default
BLAS:   /hpf/tools/centos7/R/4.3.1/lib64/R/lib/libRblas.so
LAPACK: /hpf/tools/centos7/R/4.3.1/lib64/R/lib/libRlapack.so;  LAPACK version 3.11.0

locale:
 [1] LC_CTYPE=en_US.UTF-8       LC_NUMERIC=C
 [3] LC_TIME=en_US.UTF-8        LC_COLLATE=en_US.UTF-8
 [5] LC_MONETARY=en_US.UTF-8    LC_MESSAGES=en_US.UTF-8
 [7] LC_PAPER=en_US.UTF-8       LC_NAME=C
 [9] LC_ADDRESS=C               LC_TELEPHONE=C
[11] LC_MEASUREMENT=en_US.UTF-8 LC_IDENTIFICATION=C

time zone: America/Toronto
tzcode source: system (glibc)

attached base packages:
[1] stats     graphics  grDevices utils     datasets  methods   base

other attached packages:
[1] abcdutils_0.1.1 knitr_1.43      here_1.0.1      dplyr_1.1.2
[5] readr_2.1.4     ggplot2_3.4.2   colorout_1.2-2

loaded via a namespace (and not attached):
 [1] crayon_1.5.2      vctrs_0.6.3       cli_3.6.1         xfun_0.39
 [5] rlang_1.1.1       purrr_1.0.1       generics_0.1.3    data.table_1.14.8
 [9] bit_4.0.5         glue_1.6.2        colorspace_2.1-0  rprojroot_2.0.3
[13] hms_1.1.3         scales_1.2.1      fansi_1.0.4       grid_4.3.1
[17] munsell_0.5.0     tibble_3.2.1      tzdb_0.4.0        lifecycle_1.0.3
[21] compiler_4.3.1    pkgconfig_2.0.3   R6_2.5.1          tidyselect_1.2.0
[25] utf8_1.2.3        parallel_4.3.1    vroom_1.6.3       pillar_1.9.0
[29] magrittr_2.0.3    bit64_4.0.5       tools_4.3.1       withr_2.5.0
[33] gtable_0.3.3

Output obtained from the following command:

```{r eval = FALSE}
writeLines(capture.output(sessionInfo()), "sessionInfo.txt")
```

From: https://stackoverflow.com/a/21967272/16626788
