# R Session Information

The analysis in this script were last completed on August 9th, 2023, under the following conditions:

- R version 4.3.1 (2023-06-16)
- Platform: x86_64-pc-linux-gnu (64-bit)
- OS: CentOS Linux 7 (Core)
- Packages:
    - attached base packages:
        - stats
        - graphics
        - grDevices
        - utils
        - datasets
        - methods
        - base
    - other attached packages:
        - abcdutils_0.1.1
        - knitr_1.43
        - here_1.0.1
        - dplyr_1.1.2
        - readr_2.1.4
        - ggplot2_3.4.2
    - loaded via a namespace:
        - crayon_1.5.2
        - vctrs_0.6.3
        - cli_3.6.1
        - rlang_1.1.1
        - xfun_0.39
        - generics_0.1.3
        - data.table_1.14.8
        - bit_4.0.5
        - glue_1.6.2
        - colorspace_2.1-0
        - rprojroot_2.0.3
        - hms_1.1.3
        - scales_1.2.1
        - fansi_1.0.4
        - grid_4.3.1
        - munsell_0.5.0
        - tibble_3.2.1
        - tzdb_0.4.0
        - lifecycle_1.0.3
        - compiler_4.3.1
        - pkgconfig_2.0.3
        - R6_2.5.1
        - tidyselect_1.2.0
        - utf8_1.2.3
        - parallel_4.3.1
        - vroom_1.6.3
        - pillar_1.9.0
        - magrittr_2.0.3
        - bit64_4.0.5
        - tools_4.3.1
        - withr_2.5.0
        - gtable_0.3.3

# Data extraction

## Subjects

All information required for identifying children at a chronic stage following mTBI as of baseline data collection is available in the `abcd_otbi01.txt` file, and in the `abcd_lpohstbi01.txt` file for longitudinal data.
To identify subjects at a chronic stage post-mTBI, two intermediate pieces of information must be calculated from the original dataset:

* identifying which head injuries were mTBIs
* identifying the time since the most recent mTBI

The structure of the Ohio State TBI screen as used for ABCD data collection was not completely compatible with the most commonly used definition of mTBI @WYA25C6X#Blennow_Etal_2016, which requires at least one of the following:

* Any period of loss of consciousness
* Any loss of memory
* Any alteration in mental state
* Focal neurological deficits

but none of the following:

* LOC over 30 minutes
* A Glasgow Coma Scale score below 13
* Post-traumatic amnesia (PTA) greater than 24 hours

A few aspects of the data collection process in the ABCD study precluded the usage of this definition:

* No information was collected regarding the GCS
* Feeling dazed and PTA were combined into a single variable, making it unclear which combination of symptoms was present
* No information was collected regarding the duration of feeling dazed or experiencing PTA

Consequently, I defined mTBI as any injury that resulted in **either**:

1. LOC for less than 30 minutes (including 0 minutes) **AND** any duration of memory loss / feeling dazed
2. LOC for less than 30 minutes but greater than 0 minutes

The fixed nature of the questionnaire also meant that some information about multiple mTBIs sustained in the same way or about a very large number of mTBIs throughout a child's life could have been lost (see the previous section on identifying children with a history of mTBI).
For my analyses, I assume these edge cases are not common enough to meaningfully change any obtained conclusions.

```{r}

library(ggplot2)
library(readr)
library(dplyr)
library(here)
library(knitr)
library(abcdutils)

core_path <- path_maker(here(paste0("data/abcd/core")))
input_path <- path_maker(here(paste0("data/abcd/inputs")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

# Loading data
## TBI
ph_p_otbi <- abcd_load(core_path("physical-health/ph_p_otbi.csv"))

## Age
abcd_y_lt <- abcd_load(core_path("abcd-general/abcd_y_lt.csv"))

# mTBI subjects
## Baseline at chronic stage post-mTBI (> 3 months) for analyses
(mtbi_subjects_0 <- get_mtbi_subjects(ph_p_otbi, abcd_y_lt, min_mpi = 3, t = 0))

## Baseline including recent mTBIs to exclude from longitudinal data
(mtbi_subjects_0_no_min <- get_mtbi_subjects(ph_p_otbi, abcd_y_lt, t = 0))

## Year 1 follow-up - assessments will just be taken from 2 yr follow up time
(mtbi_subjects_1 <- get_mtbi_subjects(ph_p_otbi, abcd_y_lt, t = 1))

## Year 2 follow-up
(mtbi_subjects_2 <- get_mtbi_subjects(ph_p_otbi, abcd_y_lt, min_mpi = 3, t = 2))

## Those with injuries in year 1 + 2
(mtbi_subjects_1_2 <-
    dplyr::full_join(mtbi_subjects_1, mtbi_subjects_2, by = "subjectkey"))

## Those with injuries in year 1 + 2, but not year 0 (exclusively longitudinal)
mtbi_subjects_l <- mtbi_subjects_1_2[which(!(
    mtbi_subjects_1_2$"subjectkey" %in%
        mtbi_subjects_0_no_min$"subjectkey")), ]

mtbi_subjects_l <- data.frame("subjectkey" = mtbi_subjects_l)

# Control subjects (those with no injuries in year 1, 2, or 3)
uninjured_subjects <- get_uninjured_subjects(
    ph_p_otbi,
    abcd_y_lt
)

# Within mtbi_subjects xl, I need to keep track of which subjects had their
#  latest injury in year 1 and which ones had their latest injury in year 2.
#  This is only so that the mTBI specific variables, like memory loss, are
#  recorded for the most recent injury.
mtbi_subjects_1_not_0 <- dplyr::semi_join(
    mtbi_subjects_1,
    mtbi_subjects_l,
    by = "subjectkey"
)
mtbi_subjects_2_not_0 <- dplyr::semi_join(
    mtbi_subjects_2,
    mtbi_subjects_l,
    by = "subjectkey"
)


# Note that the longitudinal subjects have not been filtered in any way based on
#  whether or not they also had an mTBI at bsaeline or another timepoint
write_csv(mtbi_subjects_0, sub_path("mtbi_subjects_0.csv", date = TRUE))
write_csv(mtbi_subjects_1, sub_path("mtbi_subjects_1.csv", date = TRUE))
write_csv(mtbi_subjects_2, sub_path("mtbi_subjects_2.csv", date = TRUE))
write_csv(mtbi_subjects_1_2, sub_path("mtbi_subjects_1_2.csv", date = TRUE))
write_csv(mtbi_subjects_1_not_0, sub_path("mtbi_subjects_1_not_0.csv", date = TRUE))
write_csv(mtbi_subjects_2_not_0, sub_path("mtbi_subjects_2_not_0.csv", date = TRUE))
write_csv(mtbi_subjects_l, sub_path("mtbi_subjects_l.csv", date = TRUE))
write_csv(uninjured_subjects, sub_path("uninjured_subjects.csv", date = TRUE))

mtbi_subjects_0 <- read_csv(sub_path("2023_08_09_mtbi_subjects_0.csv"))
mtbi_subjects_1 <- read_csv(sub_path("2023_08_09_mtbi_subjects_1.csv"))
mtbi_subjects_2 <- read_csv(sub_path("2023_08_09_mtbi_subjects_2.csv"))
mtbi_subjects_l <- read_csv(sub_path("2023_08_09_mtbi_subjects_l.csv"))
mtbi_subjects_1_not_0 <- read_csv(sub_path("2023_08_09_mtbi_subjects_1_not_0.csv"))
mtbi_subjects_2_not_0 <- read_csv(sub_path("2023_08_09_mtbi_subjects_2_not_0.csv"))
uninjured_subjects <- read_csv(sub_path("2023_08_09_uninjured_subjects.csv"))

```


A few types of injuries were handled differently from the rest in the above code.
For the `other_loc` injury type, the questionnaire asked for a total number of injuries with LOC as well as a total number of injuries with LOC above 30 minutes.
If their difference was above 0, they were labelled as having had an mTBI.
For the `other_multi` and `other_other_multi` injury types, insufficient information was provided to determine the severity of the associated injuries.

For my analyses, I consider 3 months to be the threshold at which an mTBI patient enters a chronic stage post-injury.

## Input variables

Notation for organizing baseline and longitudinal data:

variable_name + (when subject had mTBI) + (when data was collected from)

Fields in brackets could be 0 (baseline) or 1 or 2 for 1yfu or 2yfu.

For example, `as_mtbi_mem_daze_l_0` would describe baseline mem/daze data for children who had their mTBIs at a longitudinal timepoint.

For baseline analyses, I collect baseline data for those who had their mTBI prior to baseline data collection.

For my longitudinal analysis #1 (does clustering at baseline data predict post-concussion change in impairment?), I collect baseline (non-injury) data for longitudinal subjects, with the exception of CBCL outcome measures, which get baseline and 2yfu time points collected. This analysis does leave the question: is this pattern concussion specific? Or general to all children?

To address the concussion-specific question, we need to examine a matched cohort of uninjured children.

I collect mtbi-specific data at the first post-mTBI timepoint (e.g., if the injury was between baseline and 1yfu, mtbi data is collected at 1yfu rather than 2yfu).


### Acute symptoms

The acute symptom data is found within the TBI dataset.
We are interesed in the following acute symptoms:

* mechanism of injury
* age
* LOC information
* Feeling dazed or having memory loss

A few more intermediate columns need to be added to isolate these variables for the most recent mTBIs of the subjects.

```{r}
# Baseline values of subjects with injuries prior to baseline
as_mtbi_mem_daze_0_0 <-
    get_mtbi_mem_daze(ph_p_otbi, abcd_y_lt, mtbi_subjects_0, t = 0)
as_mtbi_mechanism_0_0 <-
    get_mtbi_mechanism(ph_p_otbi, abcd_y_lt, mtbi_subjects_0, t = 0)
as_mtbi_loc_0_0 <-
    get_mtbi_loc(ph_p_otbi, abcd_y_lt, mtbi_subjects_0, t = 0)

# Baseline values of subjects who received injuries between baseline and 2yfu
# This should just be a lot of NA values, as they haven't had their injuries yet
as_mtbi_mem_daze_l_0 <-
    get_mtbi_mem_daze(ph_p_otbi, abcd_y_lt, mtbi_subjects_l, t = 0)
as_mtbi_mechanism_l_0 <-
    get_mtbi_mechanism(ph_p_otbi, abcd_y_lt, mtbi_subjects_l, t = 0)
as_mtbi_loc_l_0 <-
    get_mtbi_loc(ph_p_otbi, abcd_y_lt, mtbi_subjects_l, t = 0)

# Longitudinal values of subjects who received injuries between bl and 2yfu
as_mtbi_mem_daze_l_l <- get_mtbi_mem_daze_l(
                    ph_p_otbi,
                    abcd_y_lt,
                    mtbi_subjects_l,
                    mtbi_subjects_1,
                    mtbi_subjects_2)

as_mtbi_mechanism_l_l <- get_mtbi_mechanism_l(
                    ph_p_otbi,
                    abcd_y_lt,
                    mtbi_subjects_l,
                    mtbi_subjects_1,
                    mtbi_subjects_2)

as_mtbi_loc_l_l <- get_mtbi_loc_l(
                    ph_p_otbi,
                    abcd_y_lt,
                    mtbi_subjects_l,
                    mtbi_subjects_1,
                    mtbi_subjects_2)

# Baseline subjects, baseline data
write_csv(as_mtbi_mem_daze_0_0,
    input_path("as_mtbi_mem_daze_0_0.csv", date = TRUE))
write_csv(as_mtbi_mechanism_0_0,
    input_path("as_mtbi_mechanism_0_0.csv", date = TRUE))
write_csv(as_mtbi_loc_0_0,
    input_path("as_mtbi_loc_0_0.csv", date = TRUE))

# Longitudinal subjects, baseline data
write_csv(as_mtbi_mem_daze_l_0,
    input_path("as_mtbi_mem_daze_l_0.csv", date = TRUE))
write_csv(as_mtbi_mechanism_l_0,
    input_path("as_mtbi_mechanism_l_0.csv", date = TRUE))
write_csv(as_mtbi_loc_l_0,
    input_path("as_mtbi_loc_l_0.csv", date = TRUE))

# Longitudinal subjects, longitudinal data
write_csv(as_mtbi_mem_daze_l_l,
    input_path("as_mtbi_mem_daze_l_l.csv", date = TRUE))
write_csv(as_mtbi_mechanism_l_l,
    input_path("as_mtbi_mechanism_l_l.csv", date = TRUE))
write_csv(as_mtbi_loc_l_l,
    input_path("as_mtbi_loc_l_l.csv", date = TRUE))

```


### Demographics

Demographic variables included in the analyses are:

Aspects of the NIH Toolbox probe different forms of IQ @7HIU42K2#Zhao_Etal_2022 and are used in this study as an out-of-model outcome measure rather than as an input.

Age and sex are commonly included in the ABCD study's data files.

* Age
* Sex
* Race
* Household income
* Pubertal development status

```{r}

## Demographic dataframes
ph_y_pds <- abcd_load(core_path("physical-health/ph_y_pds.csv"))
ph_p_pds <- abcd_load(core_path("physical-health/ph_p_pds.csv"))
gish_p_gi <- abcd_load(core_path("gender-identity-sexual-health/gish_p_gi.csv"))
gish_y_gi <- abcd_load(core_path("gender-identity-sexual-health/gish_y_gi.csv"))
abcd_p_demo <- abcd_load(core_path("abcd-general/abcd_p_demo.csv"))


## Pubertal status
(d_pubertal_status_0_0 <-
    get_pubertal_status(ph_p_pds, ph_y_pds, mtbi_subjects_0, t = 0))
(d_pubertal_status_l_0 <-
    get_pubertal_status(ph_p_pds, ph_y_pds, mtbi_subjects_l, t = 0))
(d_pubertal_status_u_0 <-
    get_pubertal_status(ph_p_pds, ph_y_pds, uninjured_subjects, t = 0))

## Age on interview
(d_interview_age_0_0 <- get_interview_age(abcd_y_lt, mtbi_subjects_0, t = 0))
(d_interview_age_l_0 <- get_interview_age(abcd_y_lt, mtbi_subjects_l, t = 0))
(d_interview_age_u_0 <- get_interview_age(abcd_y_lt, uninjured_subjects, t = 0))

## Age on injury
(d_mtbi_age_0_0 <- get_mtbi_age(ph_p_otbi, abcd_y_lt, mtbi_subjects_0, t = 0))

```

I will also collect here the age of the children at their latest injury.
For some of these children, that means their age should be collected at the 1-year-follow-up.
For others, it is the 2-year-follow-up.
I'll start by creating a dataframe containing the longitudinal subjects and leaving an empty column for age.
The column will first get populated by the 1 year values, followed by the 2 year values.
This way, children who have injuries from both the 1 year and 2 year timepoints will have their 1-year injury ages overwritten by their 2-year injury ages.

For an analysis that uses baseline data of longitudinally injured children to predict their outcomes, this variable would not be necessary; there is no baseline injury data (including when they were injured) for those who were injured longitudinally.
This would primarily be used for an analysis in which we examined all the 2yfu data we have access to in the same way that we have already done for the baseline data.

```{r}

(d_mtbi_age_1_l <- get_mtbi_age(ph_p_otbi, abcd_y_lt, mtbi_subjects_1_not_0, t = 1))
(d_mtbi_age_2_l <- get_mtbi_age(ph_p_otbi, abcd_y_lt, mtbi_subjects_2_not_0, t = 2))
d_mtbi_age_l_l <- data.frame(
    subjectkey = mtbi_subjects_l$subjectkey
)
d_mtbi_age_l_l <- (dplyr::full_join(d_mtbi_age_l_l, d_mtbi_age_1_l, by = "subjectkey"))
d_mtbi_age_l_l <- (dplyr::full_join(q, d_mtbi_age_2_l, by = "subjectkey"))
d_mtbi_age_l_l <- d_mtbi_age_l_l |> dplyr::mutate(
    latest_mtbi_age = dplyr::case_when(
        is.na(latest_mtbi_age.y) ~ latest_mtbi_age.x,
        TRUE ~ latest_mtbi_age.y
    ),
    .keep = "unused"
)


# As this is one of the mTBI injury variables, it is not needed for the
#  longitudinal analysis checking to see if baseline pre-injury data predicts
#  post-injury change in behavioural scores.

## Sex assigned at birth
(d_sex_0_0 <- get_sex(gish_p_gi, mtbi_subjects_0, t = 0))
(d_sex_l_0 <- get_sex(gish_p_gi, mtbi_subjects_l, t = 0))
(d_sex_u_0 <- get_sex(gish_p_gi, uninjured_subjects, t = 0))


## Gender identity - only parent reports are available at baseline
(d_p_gender_0_0 <- get_p_gender(gish_p_gi, mtbi_subjects_0, t = 0))
(d_y_gender_0_4 <- get_y_gender(gish_y_gi, mtbi_subjects_0, t = 4))
(d_p_gender_l_0 <- get_p_gender(gish_p_gi, mtbi_subjects_l, t = 0))
(d_y_gender_l_4 <- get_y_gender(gish_y_gi, mtbi_subjects_l, t = 4))
(d_p_gender_u_0 <- get_p_gender(gish_p_gi, uninjured_subjects, t = 0))
(d_y_gender_u_4 <- get_y_gender(gish_y_gi, uninjured_subjects, t = 4))


## Household income
(d_income_0_0 <- get_income(abcd_p_demo, mtbi_subjects_0, t = 0))
(d_income_l_0 <- get_income(abcd_p_demo, mtbi_subjects_l, t = 0))
(d_income_u_0 <- get_income(abcd_p_demo, uninjured_subjects, t = 0))


## Race
d_race_0_0 <- get_race(
    abcd_p_demo,
    mtbi_subjects_0,
    "condensed_undummied",
    t = 0
)
d_race_l_0 <- get_race(
    abcd_p_demo,
    mtbi_subjects_l,
    "condensed_undummied",
    t = 0
)
d_race_u_0 <- get_race(
    abcd_p_demo,
    uninjured_subjects,
    "condensed_undummied",
    t = 0
)

```

Subset and export the demographic input variables:

```{r}

# Last run July 14th, 2023
write_csv(d_pubertal_status_0_0, input_path("d_pubertal_status_0_0.csv", TRUE))
write_csv(d_interview_age_0_0, input_path("d_interview_age_0_0.csv", TRUE))
write_csv(d_mtbi_age_0_0, input_path("d_mtbi_age_0_0.csv", TRUE))
write_csv(d_sex_0_0, input_path("d_sex_0_0.csv", TRUE))
write_csv(d_p_gender_0_0, input_path("d_p_gender_0_0", TRUE))
write_csv(d_y_gender_0_4, input_path("d_y_gender_0_4", TRUE))
write_csv(d_income_0_0, input_path("d_income_0_0.csv", TRUE))
write_csv(d_race_0_0, input_path("d_race_0_0.csv", TRUE))

write_csv(d_pubertal_status_l_0, input_path("d_pubertal_status_l_0.csv", TRUE))
write_csv(d_interview_age_l_0, input_path("d_interview_age_l_0.csv", TRUE))
write_csv(d_mtbi_age_l_l, input_path("d_mtbi_age_l_l.csv", TRUE))
write_csv(d_sex_l_0, input_path("d_sex_l_0.csv", TRUE))
write_csv(d_p_gender_l_0, input_path("d_p_gender_l_0", TRUE))
write_csv(d_y_gender_l_4, input_path("d_y_gender_l_4", TRUE))
write_csv(d_income_l_0, input_path("d_income_l_0.csv", TRUE))
write_csv(d_race_l_0, input_path("d_race_l_0.csv", TRUE))

write_csv(d_pubertal_status_u_0, input_path("d_pubertal_status_u_0.csv", TRUE))
write_csv(d_interview_age_u_0, input_path("d_interview_age_u_0.csv", TRUE))
write_csv(d_sex_u_0, input_path("d_sex_u_0.csv", TRUE))
write_csv(d_p_gender_u_0, input_path("d_p_gender_u_0", TRUE))
write_csv(d_y_gender_u_4, input_path("d_y_gender_u_4", TRUE))
write_csv(d_income_u_0, input_path("d_income_u_0.csv", TRUE))
write_csv(d_race_u_0, input_path("d_race_u_0.csv", TRUE))


```


### Medical history

Medical history variables of interest include:

1. Number of previous head injuries
    * discrete variable `mtbi_count` from the processed file `abcd_otbi01_detailed.csv`
2. History of headaches
    * binary variable `medhx_2q` from the file ABCD Parent Medical History Questionnaire (`abcd_mx01.txt`; category Med History; release 2.0)
        * checks if subject has ever gone to doctor for bad headaches

Unfortunately, information on pain (the file `abcd_pq01.txt`), a factor noted as an important covariate by the original A-CAP study (@8VF7JUXL##Yeates_Etal_2017), was not a part of ABCD's baseline data collection.

```{r}
ph_p_mhx <- abcd_load(core_path("physical-health/ph_p_mhx.csv"))

## History of headaches
(mh_headaches_0_0 <- get_headaches(ph_p_mhx, mtbi_subjects_0, t = 0))
(mh_headaches_l_0 <- get_headaches(ph_p_mhx, mtbi_subjects_l, t = 0))
(mh_headaches_u_0 <- get_headaches(ph_p_mhx, uninjured_subjects, t = 0))

## Number of previous mTBIs
(mh_mtbi_count_0_0 <- get_mtbi_count(ph_p_otbi,
    abcd_y_lt,
    mtbi_subjects_0,
    t = 0))
(mh_mtbi_count_l_0 <- get_mtbi_count(ph_p_otbi,
    abcd_y_lt,
    mtbi_subjects_l,
    t = 0))
(mh_mtbi_count_u_0 <- get_mtbi_count(ph_p_otbi,
    abcd_y_lt,
    uninjured_subjects,
    t = 0))

```

Subset and export the medical history variables:

```{r}

write_csv(mh_headaches_0_0, input_path("mh_headaches_0_0.csv", date = TRUE))
write_csv(mh_mtbi_count_0_0, input_path("mh_mtbi_count_0_0.csv", date = TRUE))
write_csv(mh_headaches_l_0, input_path("mh_headaches_l_0.csv", date = TRUE))
write_csv(mh_mtbi_count_l_0, input_path("mh_mtbi_count_l_0.csv", date = TRUE))
write_csv(mh_headaches_u_0, input_path("mh_headaches_u_0.csv", date = TRUE))
write_csv(mh_mtbi_count_u_0, input_path("mh_mtbi_count_u_0.csv", date = TRUE))

```


### Neuroimaging

Variables of interest related to brain structure and function include:

* Structural: T1-weighted multishell diffusion-weighted MRI data
* Diffusion: Neurite density (restricted spectrum imaging)
* Functional: resting-state functional MRI data

The 2019 publication by Hagler et al. @UD6THTQZ##Hagler_Etal_2019 outlines the neuroimaging data present in the ABCD dataset in detail.


#### Structural MRI

The sMRI variables of interest include subcortical volumes, and cortical thicknesses, and cortical surface areas.

For cortical surface areas, the relevant file is abcd_mrisdp10201, which contains the cortical surface areas of ~150 regions (variables `mrisdp_*` where * ranges from 1 to 151).

For cortical thicknesses, the relevant file is abcd_mrisdp10201, which contains the cortical thickness of ~150 regions (variables `mrisdp_*` where * ranges from 303 to 453).


```{r}

## SMRI dataframes
mri_y_smr_vol_aseg <- abcd_load(core_path("imaging/mri_y_smr_vol_aseg.csv"))
mri_y_smr_thk_dst <- abcd_load(core_path("imaging/mri_y_smr_thk_dst.csv"))
mri_y_smr_area_dst <- abcd_load(core_path("imaging/mri_y_smr_area_dst.csv"))

## Subcortical volumes
sm_subc_v_0_0 <- abcdutils::get_subc_v(mri_y_smr_vol_aseg, mtbi_subjects_0, t = 0)
sm_subc_v_l_0 <- abcdutils::get_subc_v(mri_y_smr_vol_aseg, mtbi_subjects_l, t = 0)
sm_subc_v_u_0 <- abcdutils::get_subc_v(mri_y_smr_vol_aseg, uninjured_subjects, t = 0)

## Cortical thickness
sm_cort_t_0_0 <- abcdutils::get_cort_t(mri_y_smr_thk_dst, mtbi_subjects_0, t = 0)
sm_cort_t_l_0 <- abcdutils::get_cort_t(mri_y_smr_thk_dst, mtbi_subjects_l, t = 0)
sm_cort_t_u_0 <- abcdutils::get_cort_t(mri_y_smr_thk_dst, uninjured_subjects, t = 0)

## Cortical surface areas
sm_cort_sa_0_0 <- abcdutils::get_cort_sa(mri_y_smr_area_dst, mtbi_subjects_0, t = 0)
sm_cort_sa_l_0 <- abcdutils::get_cort_sa(mri_y_smr_area_dst, mtbi_subjects_l, t = 0)
sm_cort_sa_u_0 <- abcdutils::get_cort_sa(mri_y_smr_area_dst, uninjured_subjects, t = 0)

```

```{r}

write_csv(sm_subc_v_0_0, input_path("sm_subc_v_0_0.csv", date = TRUE))
write_csv(sm_cort_t_0_0, input_path("sm_cort_t_0_0.csv", date = TRUE))
write_csv(sm_cort_sa_0_0, input_path("sm_cort_sa_0_0.csv", date = TRUE))

write_csv(sm_subc_v_l_0, input_path("sm_subc_v_l_0.csv", date = TRUE))
write_csv(sm_cort_t_l_0, input_path("sm_cort_t_l_0.csv", date = TRUE))
write_csv(sm_cort_sa_l_0, input_path("sm_cort_sa_l_0.csv", date = TRUE))

write_csv(sm_subc_v_u_0, input_path("sm_subc_v_u_0.csv", date = TRUE))
write_csv(sm_cort_t_u_0, input_path("sm_cort_t_u_0.csv", date = TRUE))
write_csv(sm_cort_sa_u_0, input_path("sm_cort_sa_u_0.csv", date = TRUE))

```


#### Diffusion MRI

We are interested in the neurite density measures of white matter regions in the brain.
Previously, these measures were found in variables containing the string "rsindwm_cdk" within the file `mri_rsi_p102.txt`.
A change anounced in the ABCD 4.0 MRI release notes indicates that neurite density is now referred to as "restricted normalized directional" and that the relevant white matter variables contain the string "rsirndwm" within the file `abcd_drsip201.txt`.

See diffusion MRI chapter in appendix for full details.

```{r}

# DMRI dataframe
mri_y_rsi_rnd_at <- abcd_load(core_path("imaging/mri_y_rsi_rnd_at.csv"))
mri_y_rsi_rnd_wm_dsk <- abcd_load(core_path("imaging/mri_y_rsi_rnd_wm_dsk.csv"))
mri_y_rsi_rnd_wm_dst <- abcd_load(core_path("imaging/mri_y_rsi_rnd_wm_dst.csv"))

# White matter neurite densities
dm_all_wmnd_0_0 <- get_all_wmnd(
    mri_y_rsi_rnd_at,
    mri_y_rsi_rnd_wm_dst,
    mri_y_rsi_rnd_wm_dsk,
    subjects = mtbi_subjects_0,
    t = 0
)

dm_all_wmnd_l_0 <- get_all_wmnd(
    mri_y_rsi_rnd_at,
    mri_y_rsi_rnd_wm_dst,
    mri_y_rsi_rnd_wm_dsk,
    subjects = mtbi_subjects_l,
    t = 0
)

dm_all_wmnd_u_0 <- get_all_wmnd(
    mri_y_rsi_rnd_at,
    mri_y_rsi_rnd_wm_dst,
    mri_y_rsi_rnd_wm_dsk,
    subjects = uninjured_subjects,
    t = 0
)


write_csv(dm_all_wmnd_0_0, input_path("dm_all_wmnd_0_0.csv", date = TRUE))
write_csv(dm_all_wmnd_l_0, input_path("dm_all_wmnd_l_0.csv", date = TRUE))
write_csv(dm_all_wmnd_u_0, input_path("dm_all_wmnd_l_0.csv", date = TRUE))

```


#### Resting-state functional MRI

We are interested in the following rs-fMRI measures:

- Gordon network (cortical) correlations
- Subcortical correlations
- Gordon and subcortical temporal variances

```{r}

mri_y_rsfmr_cor_gp_gp <- abcd_load(core_path("imaging/mri_y_rsfmr_cor_gp_gp.csv"))
mri_y_rsfmr_cor_gp_aseg <- abcd_load(core_path("imaging/mri_y_rsfmr_cor_gp_aseg.csv"))
mri_y_rsfmr_var_gp <- abcd_load(core_path("imaging/mri_y_rsfmr_var_gp.csv"))
mri_y_rsfmr_var_aseg <- abcd_load(core_path("imaging/mri_y_rsfmr_var_aseg.csv"))

## Cortical parcellation network correlations
rm_gord_cor_0_0 <- get_gord_cor(mri_y_rsfmr_cor_gp_gp, mtbi_subjects_0, t = 0)
rm_gord_cor_l_0 <- get_gord_cor(mri_y_rsfmr_cor_gp_gp, mtbi_subjects_l, t = 0)
rm_gord_cor_u_0 <- get_gord_cor(mri_y_rsfmr_cor_gp_gp, uninjured_subjects, t = 0)
## Subcortical parcellation network correlations
rm_subc_cor_0_0 <- get_subc_cor(mri_y_rsfmr_cor_gp_aseg, mtbi_subjects_0, t = 0)
rm_subc_cor_l_0 <- get_subc_cor(mri_y_rsfmr_cor_gp_aseg, mtbi_subjects_l, t = 0)
rm_subc_cor_u_0 <- get_subc_cor(mri_y_rsfmr_cor_gp_aseg, uninjured_subjects, t = 0)
## Temporal variances - cortical parcellations
rm_gord_var_0_0 <- get_gord_var(mri_y_rsfmr_var_gp, mtbi_subjects_0, t = 0)
rm_gord_var_l_0 <- get_gord_var(mri_y_rsfmr_var_gp, mtbi_subjects_l, t = 0)
rm_gord_var_u_0 <- get_gord_var(mri_y_rsfmr_var_gp, uninjured_subjects, t = 0)
## Subcortical temporal variances
rm_subc_var_0_0 <- get_subc_var(mri_y_rsfmr_var_aseg, mtbi_subjects_0, t = 0)
rm_subc_var_l_0 <- get_subc_var(mri_y_rsfmr_var_aseg, mtbi_subjects_l, t = 0)
rm_subc_var_u_0 <- get_subc_var(mri_y_rsfmr_var_aseg, uninjured_subjects, t = 0)

```

```{r}

write_csv(rm_gord_cor_0_0, input_path("rm_gord_cor_0_0.csv", date = TRUE))
write_csv(rm_subc_cor_0_0, input_path("rm_subc_cor_0_0.csv", date = TRUE))
write_csv(rm_subc_var_0_0, input_path("rm_subc_var_0_0.csv", date = TRUE))
write_csv(rm_gord_var_0_0, input_path("rm_gord_var_0_0.csv", date = TRUE))
write_csv(rm_gord_cor_l_0, input_path("rm_gord_cor_l_0.csv", date = TRUE))
write_csv(rm_subc_cor_l_0, input_path("rm_subc_cor_l_0.csv", date = TRUE))
write_csv(rm_subc_var_l_0, input_path("rm_subc_var_l_0.csv", date = TRUE))
write_csv(rm_gord_var_l_0, input_path("rm_gord_var_l_0.csv", date = TRUE))
write_csv(rm_gord_cor_u_0, input_path("rm_gord_cor_u_0.csv", date = TRUE))
write_csv(rm_subc_cor_u_0, input_path("rm_subc_cor_u_0.csv", date = TRUE))
write_csv(rm_subc_var_u_0, input_path("rm_subc_var_u_0.csv", date = TRUE))
write_csv(rm_gord_var_u_0, input_path("rm_gord_var_u_0.csv", date = TRUE))

```


### Psychosocial resilience

Psychosocial factors of interest include:

* loneliness
* healthy behaviours
* family function
* prosocial behaviour
* parent psychopathology

```{r}

mh_y_or <- abcd_load(core_path("mental-health/mh_y_or.csv"))
nt_p_stq <- abcd_load(core_path("novel-technologies/nt_p_stq.csv"))
ce_y_fes <- abcd_load(core_path("culture-environment/ce_y_fes.csv"))
ce_p_fes <- abcd_load(core_path("culture-environment/ce_p_fes.csv"))
ph_p_saiq <- abcd_load(core_path("physical-health/ph_p_saiq.csv"))
ce_y_psb <- abcd_load(core_path("culture-environment/ce_y_psb.csv"))
ce_p_psb <- abcd_load(core_path("culture-environment/ce_p_psb.csv"))
mh_p_asr <- abcd_load(core_path("mental-health/mh_p_asr.csv"))
ph_y_yrb <- abcd_load(core_path("physical-health/ph_y_yrb.csv"))

p_loneliness_0_0 <- get_loneliness(
    mh_y_or,
    gish_p_gi,
    mtbi_subjects_0,
    t = 0
)
p_loneliness_l_0 <- get_loneliness(
    mh_y_or,
    gish_p_gi,
    mtbi_subjects_l,
    t = 0
)
p_loneliness_u_0 <- get_loneliness(
    mh_y_or,
    gish_p_gi,
    uninjured_subjects,
    t = 0
)

p_screen_time_0_0 <- get_screen_time(
    nt_p_stq,
    mtbi_subjects_0,
    t = 0
)
p_screen_time_l_0 <- get_screen_time(
    nt_p_stq,
    mtbi_subjects_l,
    t = 0
)
p_screen_time_u_0 <- get_screen_time(
    nt_p_stq,
    uninjured_subjects,
    t = 0
)

p_family_function_0_0 <- get_family_function(
    ce_y_fes,
    ce_p_fes,
    mtbi_subjects_0,
    t = 0
)
p_family_function_l_0 <- get_family_function(
    ce_y_fes,
    ce_p_fes,
    mtbi_subjects_l,
    t = 0
)
p_family_function_u_0 <- get_family_function(
    ce_y_fes,
    ce_p_fes,
    uninjured_subjects,
    t = 0
)
p_sports_0_0 <- get_sports_and_activities(
    ph_p_saiq,
    mtbi_subjects_0,
    t = 0
)
p_sports_l_0 <- get_sports_and_activities(
    ph_p_saiq,
    mtbi_subjects_l,
    t = 0
)
p_sports_u_0 <- get_sports_and_activities(
    ph_p_saiq,
    uninjured_subjects,
    t = 0
)
p_prosocial_0_0 <- get_prosocial_behaviour(
    ce_p_psb,
    ce_y_psb,
    mtbi_subjects_0,
    t = 0
)
p_prosocial_l_0 <- get_prosocial_behaviour(
    ce_p_psb,
    ce_y_psb,
    mtbi_subjects_l,
    t = 0
)
p_prosocial_u_0 <- get_prosocial_behaviour(
    ce_p_psb,
    ce_y_psb,
    uninjured_subjects,
    t = 0
)
p_parent_psych_0_0 <- get_parent_psychopathology(
    mh_p_asr,
    mtbi_subjects_0,
    t = 0
)
p_parent_psych_l_0 <- get_parent_psychopathology(
    mh_p_asr,
    mtbi_subjects_l,
    t = 0
)
p_parent_psych_u_0 <- get_parent_psychopathology(
    mh_p_asr,
    uninjured_subjects,
    t = 0
)
p_exercise_0_0 <- get_exercise(
    ph_y_yrb,
    mtbi_subjects_0,
    t = 0
)
p_exercise_l_0 <- get_exercise(
    ph_y_yrb,
    mtbi_subjects_l,
    t = 0
)
p_exercise_u_0 <- get_exercise(
    ph_y_yrb,
    uninjured_subjects,
    t = 0
)

```

Subset and export the psychosocial resilience variables:

```{r}

write_csv(p_loneliness_0_0, input_path("p_loneliness_0_0.csv", date = TRUE))
write_csv(p_screen_time_0_0, input_path("p_screen_time_0_0.csv", date = TRUE))
write_csv(p_family_function_0_0, input_path("p_family_function_0_0.csv", date = TRUE))
write_csv(p_sports_0_0, input_path("p_sports_0_0.csv", date = TRUE))
write_csv(p_prosocial_0_0, input_path("p_prosocial_0_0.csv", date = TRUE))
write_csv(p_parent_psych_0_0, input_path("p_parent_psych_0_0.csv", date = TRUE))
write_csv(p_exercise_0_0, input_path("p_exercise_0_0.csv", date = TRUE))

write_csv(p_loneliness_l_0, input_path("p_loneliness_l_0.csv", date = TRUE))
write_csv(p_screen_time_l_0, input_path("p_screen_time_l_0.csv", date = TRUE))
write_csv(p_family_function_l_0, input_path("p_family_function_l_0.csv", date = TRUE))
write_csv(p_sports_l_0, input_path("p_sports_l_0.csv", date = TRUE))
write_csv(p_prosocial_l_0, input_path("p_prosocial_l_0.csv", date = TRUE))
write_csv(p_parent_psych_l_0, input_path("p_parent_psych_l_0.csv", date = TRUE))
write_csv(p_exercise_l_0, input_path("p_exercise_l_0.csv", date = TRUE))

write_csv(p_loneliness_u_0, input_path("p_loneliness_u_0.csv", date = TRUE))
write_csv(p_screen_time_u_0, input_path("p_screen_time_u_0.csv", date = TRUE))
write_csv(p_family_function_u_0, input_path("p_family_function_u_0.csv", date = TRUE))
write_csv(p_sports_u_0, input_path("p_sports_u_0.csv", date = TRUE))
write_csv(p_prosocial_u_0, input_path("p_prosocial_u_0.csv", date = TRUE))
write_csv(p_parent_psych_u_0, input_path("p_parent_psych_u_0.csv", date = TRUE))
write_csv(p_exercise_u_0, input_path("p_exercise_u_0.csv", date = TRUE))

```


## Output variables

### Child behaviour checklist

These are needed at both baseline and longitudinal timepoints.

```{r}

# LEFT OFF HERE

mh_p_asr <- abcd_load(core_path("mental-health/mh_p_asr.csv"))
mh_p_cbcl <- abcd_load(core_path("mental-health/mh_p_cbcl.csv"))

# Baseline subjects, baseline time point
cbcl_headaches_0_0 <-
    get_cbcl_headaches(mh_p_cbcl, mtbi_subjects_0, t = 0)
cbcl_nausea_0_0 <-
    get_cbcl_nausea(mh_p_cbcl, mtbi_subjects_0, t = 0)
cbcl_vomiting_0_0 <-
    get_cbcl_vomiting(mh_p_cbcl, mtbi_subjects_0, t = 0)
cbcl_dizzy_0_0 <-
    get_cbcl_dizzy(mh_p_cbcl, mtbi_subjects_0, t = 0)
cbcl_overtired_0_0 <-
    get_cbcl_overtired(mh_p_cbcl, mtbi_subjects_0, t = 0)
cbcl_sleeping_more_0_0 <-
    get_cbcl_sleeping_more(mh_p_cbcl, mtbi_subjects_0, t = 0)
cbcl_sleeping_less_0_0 <-
    get_cbcl_sleeping_less(mh_p_cbcl, mtbi_subjects_0, t = 0)
cbcl_depress_r_0_0 <-
    get_cbcl_depress(mh_p_cbcl, mtbi_subjects_0, t = 0)
cbcl_anxiety_r_0_0 <-
    get_cbcl_anxiety(mh_p_cbcl, mtbi_subjects_0, t = 0)
cbcl_attention_r_0_0 <-
    get_cbcl_attention(mh_p_cbcl, mtbi_subjects_0, t = 0)
cbcl_aggressive_r_0_0 <-
    get_cbcl_aggressive(mh_p_cbcl, mtbi_subjects_0, t = 0)
# Borderline/clinical thresholded instead of raw scores
cbcl_depress_0_0 <-
    get_cbcl_depress(mh_p_cbcl, mtbi_subjects_0, t = 0, raw = FALSE)
cbcl_anxiety_0_0 <-
    get_cbcl_anxiety(mh_p_cbcl, mtbi_subjects_0, t = 0, raw = FALSE)
cbcl_attention_0_0 <-
    get_cbcl_attention(mh_p_cbcl, mtbi_subjects_0, t = 0, raw = FALSE)
cbcl_aggressive_0_0 <-
    get_cbcl_aggressive(mh_p_cbcl, mtbi_subjects_0, t = 0, raw = FALSE)

# Baseline subjects, longitudinal time point
cbcl_headaches_0_l <-
    get_cbcl_headaches(mh_p_cbcl, mtbi_subjects_0, t = 2)
cbcl_nausea_0_l <-
    get_cbcl_nausea(mh_p_cbcl, mtbi_subjects_0, t = 2)
cbcl_vomiting_0_l <-
    get_cbcl_vomiting(mh_p_cbcl, mtbi_subjects_0, t = 2)
cbcl_dizzy_0_l <-
    get_cbcl_dizzy(mh_p_cbcl, mtbi_subjects_0, t = 2)
cbcl_overtired_0_l <-
    get_cbcl_overtired(mh_p_cbcl, mtbi_subjects_0, t = 2)
cbcl_sleeping_more_0_l <-
    get_cbcl_sleeping_more(mh_p_cbcl, mtbi_subjects_0, t = 2)
cbcl_sleeping_less_0_l <-
    get_cbcl_sleeping_less(mh_p_cbcl, mtbi_subjects_0, t = 2)
cbcl_depress_r_0_l <-
    get_cbcl_depress(mh_p_cbcl, mtbi_subjects_0, t = 2)
cbcl_anxiety_r_0_l <-
    get_cbcl_anxiety(mh_p_cbcl, mtbi_subjects_0, t = 2)
cbcl_attention_r_0_l <-
    get_cbcl_attention(mh_p_cbcl, mtbi_subjects_0, t = 2)
cbcl_aggressive_r_0_l <-
    get_cbcl_aggressive(mh_p_cbcl, mtbi_subjects_0, t = 2)
# Borderline/clinical thresholded instead of raw scores
cbcl_depress_0_l <-
    get_cbcl_depress(mh_p_cbcl, mtbi_subjects_0, t = 2, raw = FALSE)
cbcl_anxiety_0_l <-
    get_cbcl_anxiety(mh_p_cbcl, mtbi_subjects_0, t = 2, raw = FALSE)
cbcl_attention_0_l <-
    get_cbcl_attention(mh_p_cbcl, mtbi_subjects_0, t = 2, raw = FALSE)
cbcl_aggressive_0_l <-
    get_cbcl_aggressive(mh_p_cbcl, mtbi_subjects_0, t = 2, raw = FALSE)

# Longitudinal subjects, baseline time point
cbcl_headaches_l_0 <-
    get_cbcl_headaches(mh_p_cbcl, mtbi_subjects_l, t = 0)
cbcl_nausea_l_0 <-
    get_cbcl_nausea(mh_p_cbcl, mtbi_subjects_l, t = 0)
cbcl_vomiting_l_0 <-
    get_cbcl_vomiting(mh_p_cbcl, mtbi_subjects_l, t = 0)
cbcl_dizzy_l_0 <-
    get_cbcl_dizzy(mh_p_cbcl, mtbi_subjects_l, t = 0)
cbcl_overtired_l_0 <-
    get_cbcl_overtired(mh_p_cbcl, mtbi_subjects_l, t = 0)
cbcl_sleeping_more_l_0 <-
    get_cbcl_sleeping_more(mh_p_cbcl, mtbi_subjects_l, t = 0)
cbcl_sleeping_less_l_0 <-
    get_cbcl_sleeping_less(mh_p_cbcl, mtbi_subjects_l, t = 0)
cbcl_depress_r_l_0 <-
    get_cbcl_depress(mh_p_cbcl, mtbi_subjects_l, t = 0)
cbcl_anxiety_r_l_0 <-
    get_cbcl_anxiety(mh_p_cbcl, mtbi_subjects_l, t = 0)
cbcl_attention_r_l_0 <-
    get_cbcl_attention(mh_p_cbcl, mtbi_subjects_l, t = 0)
cbcl_aggressive_r_l_0 <-
    get_cbcl_aggressive(mh_p_cbcl, mtbi_subjects_l, t = 0)
# Borderline/clinical thresholded instead of raw scores
cbcl_depress_l_0 <-
    get_cbcl_depress(mh_p_cbcl, mtbi_subjects_l, t = 0, raw = FALSE)
cbcl_anxiety_l_0 <-
    get_cbcl_anxiety(mh_p_cbcl, mtbi_subjects_l, t = 0, raw = FALSE)
cbcl_attention_l_0 <-
    get_cbcl_attention(mh_p_cbcl, mtbi_subjects_l, t = 0, raw = FALSE)
cbcl_aggressive_l_0 <-
    get_cbcl_aggressive(mh_p_cbcl, mtbi_subjects_l, t = 0, raw = FALSE)

# Longitudinal subjects, 2yfu time point
cbcl_headaches_l_2 <-
    get_cbcl_headaches(mh_p_cbcl, mtbi_subjects_l, t = 2)
cbcl_nausea_l_2 <-
    get_cbcl_nausea(mh_p_cbcl, mtbi_subjects_l, t = 2)
cbcl_vomiting_l_2 <-
    get_cbcl_vomiting(mh_p_cbcl, mtbi_subjects_l, t = 2)
cbcl_dizzy_l_2 <-
    get_cbcl_dizzy(mh_p_cbcl, mtbi_subjects_l, t = 2)
cbcl_overtired_l_2 <-
    get_cbcl_overtired(mh_p_cbcl, mtbi_subjects_l, t = 2)
cbcl_sleeping_more_l_2 <-
    get_cbcl_sleeping_more(mh_p_cbcl, mtbi_subjects_l, t = 2)
cbcl_sleeping_less_l_2 <-
    get_cbcl_sleeping_less(mh_p_cbcl, mtbi_subjects_l, t = 2)
cbcl_depress_r_l_2 <-
    get_cbcl_depress(mh_p_cbcl, mtbi_subjects_l, t = 2)
cbcl_anxiety_r_l_2 <-
    get_cbcl_anxiety(mh_p_cbcl, mtbi_subjects_l, t = 2)
cbcl_attention_r_l_2 <-
    get_cbcl_attention(mh_p_cbcl, mtbi_subjects_l, t = 2)
cbcl_aggressive_r_l_2 <-
    get_cbcl_aggressive(mh_p_cbcl, mtbi_subjects_l, t = 2)
# Borderline/clinical thresholded instead of raw scores
cbcl_depress_l_2 <-
    get_cbcl_depress(mh_p_cbcl, mtbi_subjects_l, t = 2, raw = FALSE)
cbcl_anxiety_l_2 <-
    get_cbcl_anxiety(mh_p_cbcl, mtbi_subjects_l, t = 2, raw = FALSE)
cbcl_attention_l_2 <-
    get_cbcl_attention(mh_p_cbcl, mtbi_subjects_l, t = 2, raw = FALSE)
cbcl_aggressive_l_2 <-
    get_cbcl_aggressive(mh_p_cbcl, mtbi_subjects_l, t = 2, raw = FALSE)


calc_delta <- function(df0, df2) {
    common_subs <- common_subjects(list(df0, df2))
    df0 <- df0 |> dplyr::filter(df0$"subjectkey" %in% common_subs) |>
        col_to_num_all_possible()
    df2 <- df2 |> dplyr::filter(df2$"subjectkey" %in% common_subs) |>
        col_to_num_all_possible()
    df_delta <- df0
    features <- colnames(df0)[-1]
    for (feature in features) {
        df_delta[, feature] <- df2[, feature] - df0[, feature]
    }
    colnames(df_delta) <-
        c("subjectkey", paste0(colnames(df_delta[-1]), "_delta"))
    return(df_delta)
}


# Calculating change in CBCL score from pre-injury to post-injury time points
cbcl_headaches_delta_l <-
    calc_delta(cbcl_headaches_l_0, cbcl_headaches_l_2)
cbcl_nausea_delta_l <-
    calc_delta(cbcl_nausea_l_0, cbcl_nausea_l_2)
cbcl_vomiting_delta_l <-
    calc_delta(cbcl_vomiting_l_0, cbcl_vomiting_l_2)
cbcl_dizzy_delta_l <-
    calc_delta(cbcl_dizzy_l_0, cbcl_dizzy_l_2)
cbcl_overtired_delta_l <-
    calc_delta(cbcl_overtired_l_0, cbcl_overtired_l_2)
cbcl_sleeping_more_delta_l <-
    calc_delta(cbcl_sleeping_more_l_0, cbcl_sleeping_more_l_2)
cbcl_sleeping_less_delta_l <-
    calc_delta(cbcl_sleeping_less_l_0, cbcl_sleeping_less_l_2)
cbcl_depress_r_delta_l <-
    calc_delta(cbcl_depress_r_l_0, cbcl_depress_r_l_2)
cbcl_anxiety_r_delta_l <-
    calc_delta(cbcl_anxiety_r_l_0, cbcl_anxiety_r_l_2)
cbcl_attention_r_delta_l <-
    calc_delta(cbcl_attention_r_l_0, cbcl_attention_r_l_2)
cbcl_aggressive_r_delta_l <-
    calc_delta(cbcl_aggressive_r_l_0, cbcl_aggressive_r_l_2)
cbcl_depress_delta_l <-
    calc_delta(cbcl_depress_l_0, cbcl_depress_l_2)
cbcl_anxiety_delta_l <-
    calc_delta(cbcl_anxiety_l_0, cbcl_anxiety_l_2)
cbcl_attention_delta_l <-
    calc_delta(cbcl_attention_l_0, cbcl_attention_l_2)
cbcl_aggressive_delta_l <-
    calc_delta(cbcl_aggressive_l_0, cbcl_aggressive_l_2)


# Quick and dirty check to see how these measures change for the l subjects
a <- list(
    cbcl_headaches_delta_l,
    cbcl_nausea_delta_l,
    cbcl_vomiting_delta_l,
    cbcl_dizzy_delta_l,
    cbcl_overtired_delta_l,
    cbcl_sleeping_more_delta_l,
    cbcl_sleeping_less_delta_l,
    cbcl_depress_r_delta_l,
    cbcl_anxiety_r_delta_l,
    cbcl_attention_r_delta_l,
    cbcl_aggressive_r_delta_l,
    cbcl_depress_delta_l,
    cbcl_anxiety_delta_l,
    cbcl_attention_delta_l,
    cbcl_aggressive_delta_l)

b <- merge_df_list(a) |>
    na.omit() |>
    dplyr::select(-dplyr::contains(c("subjectkey", "r")))

pheatmap::pheatmap(b)

write_csv(cbcl_headaches_0_0,
    input_path("cbcl_headaches_0_0.csv", date = TRUE))
write_csv(cbcl_nausea_0_0,
    input_path("cbcl_nausea_0_0.csv", date = TRUE))
write_csv(cbcl_vomiting_0_0,
    input_path("cbcl_vomiting_0_0.csv", date = TRUE))
write_csv(cbcl_dizzy_0_0,
    input_path("cbcl_dizzy_0_0.csv", date = TRUE))
write_csv(cbcl_overtired_0_0,
    input_path("cbcl_overtired_0_0.csv", date = TRUE))
write_csv(cbcl_sleeping_more_0_0,
    input_path("cbcl_sleeping_more_0_0.csv", date = TRUE))
write_csv(cbcl_sleeping_less_0_0,
    input_path("cbcl_sleeping_less_0_0.csv", date = TRUE))
write_csv(cbcl_depress_r_0_0,
    input_path("cbcl_depress_r_0_0.csv", date = TRUE))
write_csv(cbcl_anxiety_r_0_0,
    input_path("cbcl_anxiety_r_0_0.csv", date = TRUE))
write_csv(cbcl_attention_r_0_0,
    input_path("cbcl_attention_r_0_0.csv", date = TRUE))
write_csv(cbcl_aggressive_r_0_0,
    input_path("cbcl_aggressive_r_0_0.csv", date = TRUE))
write_csv(cbcl_depress_0_0,
    input_path("cbcl_depress_0_0.csv", date = TRUE))
write_csv(cbcl_anxiety_0_0,
    input_path("cbcl_anxiety_0_0.csv", date = TRUE))
write_csv(cbcl_attention_0_0,
    input_path("cbcl_attention_0_0.csv", date = TRUE))
write_csv(cbcl_aggressive_0_0,
    input_path("cbcl_aggressive_0_0.csv", date = TRUE))

write_csv(cbcl_headaches_l_0,
    input_path("cbcl_headaches_l_0.csv", date = TRUE))
write_csv(cbcl_nausea_l_0,
    input_path("cbcl_nausea_l_0.csv", date = TRUE))
write_csv(cbcl_vomiting_l_0,
    input_path("cbcl_vomiting_l_0.csv", date = TRUE))
write_csv(cbcl_dizzy_l_0,
    input_path("cbcl_dizzy_l_0.csv", date = TRUE))
write_csv(cbcl_overtired_l_0,
    input_path("cbcl_overtired_l_0.csv", date = TRUE))
write_csv(cbcl_sleeping_more_l_0,
    input_path("cbcl_sleeping_more_l_0.csv", date = TRUE))
write_csv(cbcl_sleeping_less_l_0,
    input_path("cbcl_sleeping_less_l_0.csv", date = TRUE))
write_csv(cbcl_depress_r_l_0,
    input_path("cbcl_depress_r_l_0.csv", date = TRUE))
write_csv(cbcl_anxiety_r_l_0,
    input_path("cbcl_anxiety_r_l_0.csv", date = TRUE))
write_csv(cbcl_attention_r_l_0,
    input_path("cbcl_attention_r_l_0.csv", date = TRUE))
write_csv(cbcl_aggressive_r_l_0,
    input_path("cbcl_aggressive_r_l_0.csv", date = TRUE))
write_csv(cbcl_depress_l_0,
    input_path("cbcl_depress_l_0.csv", date = TRUE))
write_csv(cbcl_anxiety_l_0,
    input_path("cbcl_anxiety_l_0.csv", date = TRUE))
write_csv(cbcl_attention_l_0,
    input_path("cbcl_attention_l_0.csv", date = TRUE))
write_csv(cbcl_aggressive_l_0,
    input_path("cbcl_aggressive_l_0.csv", date = TRUE))

write_csv(cbcl_headaches_l_2,
    input_path("cbcl_headaches_l_2.csv", date = TRUE))
write_csv(cbcl_nausea_l_2,
    input_path("cbcl_nausea_l_2.csv", date = TRUE))
write_csv(cbcl_vomiting_l_2,
    input_path("cbcl_vomiting_l_2.csv", date = TRUE))
write_csv(cbcl_dizzy_l_2,
    input_path("cbcl_dizzy_l_2.csv", date = TRUE))
write_csv(cbcl_overtired_l_2,
    input_path("cbcl_overtired_l_2.csv", date = TRUE))
write_csv(cbcl_sleeping_more_l_2,
    input_path("cbcl_sleeping_more_l_2.csv", date = TRUE))
write_csv(cbcl_sleeping_less_l_2,
    input_path("cbcl_sleeping_less_l_2.csv", date = TRUE))
write_csv(cbcl_depress_r_l_2,
    input_path("cbcl_depress_r_l_2.csv", date = TRUE))
write_csv(cbcl_anxiety_r_l_2,
    input_path("cbcl_anxiety_r_l_2.csv", date = TRUE))
write_csv(cbcl_attention_r_l_2,
    input_path("cbcl_attention_r_l_2.csv", date = TRUE))
write_csv(cbcl_aggressive_r_l_2,
    input_path("cbcl_aggressive_r_l_2.csv", date = TRUE))
write_csv(cbcl_depress_l_2,
    input_path("cbcl_depress_l_2.csv", date = TRUE))
write_csv(cbcl_anxiety_l_2,
    input_path("cbcl_anxiety_l_2.csv", date = TRUE))
write_csv(cbcl_attention_l_2,
    input_path("cbcl_attention_l_2.csv", date = TRUE))
write_csv(cbcl_aggressive_l_2,
    input_path("cbcl_aggressive_l_2.csv", date = TRUE))

write_csv(cbcl_headaches_delta_l,
    input_path("cbcl_headaches_delta_l.csv", date = TRUE))
write_csv(cbcl_nausea_delta_l,
    input_path("cbcl_nausea_delta_l.csv", date = TRUE))
write_csv(cbcl_vomiting_delta_l,
    input_path("cbcl_vomiting_delta_l.csv", date = TRUE))
write_csv(cbcl_dizzy_delta_l,
    input_path("cbcl_dizzy_delta_l.csv", date = TRUE))
write_csv(cbcl_overtired_delta_l,
    input_path("cbcl_overtired_delta_l.csv", date = TRUE))
write_csv(cbcl_sleeping_more_delta_l,
    input_path("cbcl_sleeping_more_delta_l.csv", date = TRUE))
write_csv(cbcl_sleeping_less_delta_l,
    input_path("cbcl_sleeping_less_delta_l.csv", date = TRUE))
write_csv(cbcl_depress_r_delta_l,
    input_path("cbcl_depress_r_delta_l.csv", date = TRUE))
write_csv(cbcl_anxiety_r_delta_l,
    input_path("cbcl_anxiety_r_delta_l.csv", date = TRUE))
write_csv(cbcl_attention_r_delta_l,
    input_path("cbcl_attention_r_delta_l.csv", date = TRUE))
write_csv(cbcl_aggressive_r_delta_l,
    input_path("cbcl_aggressive_r_delta_l.csv", date = TRUE))
write_csv(cbcl_depress_delta_l,
    input_path("cbcl_depress_delta_l.csv", date = TRUE))
write_csv(cbcl_anxiety_delta_l,
    input_path("cbcl_anxiety_delta_l.csv", date = TRUE))
write_csv(cbcl_attention_delta_l,
    input_path("cbcl_attention_delta_l.csv", date = TRUE))
write_csv(cbcl_aggressive_delta_l,
    input_path("cbcl_aggressive_delta_l.csv", date = TRUE))
```

### NIH Toolbox

```{r}
nc_y_nihtb <- abcd_load(core_path("neurocognition/nc_y_nihtb.csv"))


# Baseline subjects, baseline data
nihtbx_list_fc_0_0 <-
    get_nihtbx_list_fc(nc_y_nihtb, mtbi_subjects_0, t = 0)
nihtbx_pattern_fc_0_0 <-
    get_nihtbx_pattern_fc(nc_y_nihtb, mtbi_subjects_0, t = 0)
nihtbx_cardsort_fc_0_0 <-
    get_nihtbx_cardsort_fc(nc_y_nihtb, mtbi_subjects_0, t = 0)

# Longitudinal subjects, baseline data
(nihtbx_list_fc_l_0 <-
    get_nihtbx_list_fc(nc_y_nihtb, mtbi_subjects_l, t = 0))
(nihtbx_pattern_fc_l_0 <-
    get_nihtbx_pattern_fc(nc_y_nihtb, mtbi_subjects_l, t = 0))
(nihtbx_cardsort_fc_l_0 <-
    get_nihtbx_cardsort_fc(nc_y_nihtb, mtbi_subjects_l, t = 0))

# Longitudinal subjects, longitudinal data - only pattern test is present
(nihtbx_pattern_fc_l_2 <-
    get_nihtbx_pattern_fc(nc_y_nihtb, mtbi_subjects_l, t = 2))

# Change in pattern test score:
nihtbx_pattern_fc_delta_l <-
    calc_delta(nihtbx_pattern_fc_l_0, nihtbx_pattern_fc_l_2)

write_csv(nihtbx_list_fc_0_0, input_path("nihtbx_list_fc_0_0.csv", 1))
write_csv(nihtbx_pattern_fc_0_0, input_path("nihtbx_pattern_fc_0_0.csv", 1))
write_csv(nihtbx_cardsort_fc_0_0, input_path("nihtbx_cardsort_fc_0_0.csv", 1))

write_csv(nihtbx_list_fc_l_0, input_path("nihtbx_list_fc_l_0.csv", 1))
write_csv(nihtbx_pattern_fc_l_0, input_path("nihtbx_pattern_fc_l_0.csv", 1))
write_csv(nihtbx_cardsort_fc_l_0, input_path("nihtbx_cardsort_fc_l_0.csv", 1))

write_csv(nihtbx_pattern_fc_l_2, input_path("nihtbx_pattern_fc_l_2.csv", 1))

write_csv(nihtbx_pattern_fc_delta_l,
          input_path("nihtbx_pattern_fc_delta_l.csv", 1))
```


### Sleep disturbance scale

```{r}
ph_p_sds <- abcd_load(core_path("physical-health/ph_p_sds.csv"))

(sds_sleep_df_0_0 <- get_full_sleep_df(ph_p_sds, mtbi_subjects_0, t = 0))

(sds_sleep_df_l_0 <- get_full_sleep_df(ph_p_sds, mtbi_subjects_l, t = 0))

(sds_sleep_df_l_2 <- get_full_sleep_df(ph_p_sds, mtbi_subjects_l, t = 2))

sds_sleep_df_delta_l <- calc_delta(sds_sleep_df_l_0, sds_sleep_df_l_2)

write_csv(sds_sleep_df_0_0, input_path("sds_sleep_df_0_0.csv", date = TRUE))
write_csv(sds_sleep_df_l_0, input_path("sds_sleep_df_l_0.csv", date = TRUE))
write_csv(sds_sleep_df_l_2, input_path("sds_sleep_df_l_2.csv", date = TRUE))
write_csv(sds_sleep_df_delta_l, input_path("sds_sleep_df_delta_l.csv", TRUE))
```
