# Baseline Data Extraction

This file achieves the following goals:

1. Identification of concussion and uninjured children as of the baseline timepoint
2. Extraction of features values for those children

## Loading packages

The `abcdutils` package can be installed from GitHub using the command: `devtools::install_github("BRANCHlab/abcdutils")`.

```{r}
library(ggplot2)
library(readr)
library(dplyr)
library(here)
library(abcdutils)
library(visdat)
```

## Path set-up

The `path_maker()` function returns other functions that can turn relative paths into absolute ones.
The functions returned by `path_maker()` also have a `date` parameter which attach as a prefix the current date to a file name.

```{r}
core_path <- path_maker(here("data/abcd/core"))
input_path <- path_maker(here("data/abcd/inputs"))
sub_path <- path_maker(here("data/abcd/subjects"))
fig_path <- path_maker(here("data/abcd/results/figures"))

core_path <- path_maker(here("data/abcd/core"))
import <- function(path) {
    return(abcd_load(core_path(path)))
}
```

## Import raw data

This chunk loads in raw ABCD 5.1 CSVs into data frames.

```{r}
# Ohio TBI screen
ph_p_otbi <- import("physical-health/ph_p_otbi.csv")
# Age, family ID, site ID
abcd_y_lt <- import("abcd-general/abcd_y_lt.csv")
# Pubertal development scale, youth report
ph_y_pds <- import("physical-health/ph_y_pds.csv")
# Pubertal development scale, parent report
ph_p_pds <- import("physical-health/ph_p_pds.csv")
# Parent report of gender identity
gish_p_gi <- import("gender-identity-sexual-health/gish_p_gi.csv")
# Demographic data
abcd_p_demo <- import("abcd-general/abcd_p_demo.csv")
# Medical history
ph_p_mhx <- import("physical-health/ph_p_mhx.csv")
# Subcortical volumes (ASEG)
mri_y_smr_vol_aseg <- import("imaging/mri_y_smr_vol_aseg.csv")
# Desikan cortical thicknesses
mri_y_smr_thk_dsk <- import("imaging/mri_y_smr_thk_dsk.csv")
# Desikan cortical surface areas
mri_y_smr_area_dsk <- import("imaging/mri_y_smr_area_dsk.csv")
# Neurite density (AtlasTrack, all fibers)
mri_y_rsi_rnd_at <- import("imaging/mri_y_rsi_rnd_at.csv")
# Neurite density (Desikan, peri-cortical WM)
mri_y_rsi_rnd_wm_dsk <- import("imaging/mri_y_rsi_rnd_wm_dsk.csv")
# Neurite density (Destriux, peri-cortical WM)
mri_y_rsi_rnd_wm_dst <- import("imaging/mri_y_rsi_rnd_wm_dst.csv")
# rs-fMRI cortical-cortical correlations
mri_y_rsfmr_cor_gp_gp <- import("imaging/mri_y_rsfmr_cor_gp_gp.csv")
# rs-fMRI cortical-subcortical correlations
mri_y_rsfmr_cor_gp_aseg <- import("imaging/mri_y_rsfmr_cor_gp_aseg.csv")
# Number of friends
mh_y_or <- import("mental-health/mh_y_or.csv")
# Screen time
nt_p_stq <- import("novel-technologies/nt_p_stq.csv")
# Participation in sports and activities
ph_p_saiq <- import("physical-health/ph_p_saiq.csv")
# Exercise habits
ph_y_yrb <- import("physical-health/ph_y_yrb.csv")
# Youth report of prosocial behaviour
ce_y_psb <- import("culture-environment/ce_y_psb.csv")
# Parent report of prosocial behaviour
ce_p_psb <- import("culture-environment/ce_p_psb.csv")
# Youth report of family function
ce_y_fes <- import("culture-environment/ce_y_fes.csv")
# Parent report of family function
ce_p_fes <- import("culture-environment/ce_p_fes.csv")
# Parent ASEBA self-report (psychopathology)
mh_p_asr <- import("mental-health/mh_p_asr.csv")
# Parent report of child behaviour (CBCL)
mh_p_cbcl <- import("mental-health/mh_p_cbcl.csv")
# Sleep disturbance scale
ph_p_sds <- import("physical-health/ph_p_sds.csv")
# Scanner ID
mri_y_adm_info <- import("imaging/mri_y_adm_info.csv")
```

## Sample identification

All information required for identifying children following mTBI as of baseline data collection is available in the `ph_p_otbi.csv` file.
The structure of the Ohio State TBI screen as used for ABCD data collection was not completely compatible with the most commonly used definition of mTBI [@blennow_traumatic_2016], which requires at least one of the following:

* Any period of loss of consciousness
* Any loss of memory
* Any alteration in mental state
* Focal neurological deficits

But none of the following:

* LOC over 30 minutes
* A Glasgow Coma Scale score below 13
* Post-traumatic amnesia (PTA) greater than 24 hours

A few aspects of the data collection process in the ABCD study precluded the usage of this definition:

* No information was collected regarding the GCS
* Feeling dazed and PTA were combined into a single variable, making it unclear which combination of symptoms was present
* No information was collected regarding the duration of feeling dazed or experiencing PTA

Consequently, I defined mTBI as any injury that resulted in **either**:

1. LOC for less than 30 minutes (including 0 minutes) **AND** any duration of memory loss / feeling dazed
2. LOC for less than 30 minutes but greater than 0 minutes

The fixed nature of the questionnaire also meant that some information about multiple mTBIs sustained in the same way or about a very large number of mTBIs throughout a child's life could have been lost (see the previous section on identifying children with a history of mTBI).
For my analyses, I assume these edge cases are not common enough to meaningfully change any obtained conclusions.

```{r}
# 11864 total children included in baseline TBI data
ph_p_otbi |>
    filter_timepoint(0) |>
    nrow()

# mTBI subjects
# N = 442
mtbi_subs <- get_mtbi_subjects(
    ph_p_otbi,
    abcd_y_lt,
    min_mpi = 0,
    t = 0
)

# Later analyses show some unusual data for subject: NDAR_INVBU31791C.
# They are removed from the uninjured subjects list.

# Uninjured subjects (those with no injuries as of baseline collection)
# N = 9302
unij_subs <- get_uninjured_subjects(
    ph_p_otbi,
    abcd_y_lt,
    t = 0
)

write_csv(mtbi_subs, sub_path("mtbi_subs.csv", date = TRUE))
write_csv(unij_subs, sub_path("unij_subs.csv", date = TRUE))
```

Throughout this and subsequent files, I make an effort to export intermediate data objects and re-import them in a following chunk.
This is done both to serve as a reproducibility check as well as to serve as a checkpoint to resume work without tracking gigantic session files.

```{r}
# CHECKPOINT
mtbi_subs <- read_subjects(sub_path("2025_09_11_mtbi_subs.csv"))
unij_subs <- read_subjects(sub_path("2025_09_11_unij_subs.csv"))

length(mtbi_subs)
length(unij_subs)
```

An overview of the types of injuries considered in the `ph_p_otbi` file can be examined by calling `abcdutils::original_tbi_names()`.
A few types of injuries were handled differently from the rest in the above code.
For the `other_loc` injury type, the questionnaire asked for a total number of injuries with LOC as well as a total number of injuries with LOC above 30 minutes.
If their difference was above 0, they were labelled as having had an mTBI.
For the `other_multi` and `other_other_multi` injury types, insufficient information was provided to determine the severity of the associated injuries.

## Extracting input variables

### Acute symptoms

The acute symptom data is found within the TBI dataset.
We are interesed in the following acute symptoms:

* mechanism of injury (categorical)
* LOC information (ordinal)
* Feeling dazed or having memory loss (binary)

A few more intermediate columns need to be added to isolate these variables for the most recent mTBIs of the subjects.

#### Feeling dazed

```{r}
mtbi_as_mem_daze <- get_mtbi_mem_daze(
    ph_p_otbi,
    abcd_y_lt,
    mtbi_subs,
    t = 0
)

dplyr::tibble(mtbi_as_mem_daze)

readr::write_csv(
    mtbi_as_mem_daze,
    input_path("mtbi_as_mem_daze.csv", date = TRUE)
)
```

#### Mechanism of injury

```{r}
mtbi_as_mechanism <- get_mtbi_mechanism(
    ph_p_otbi,
    abcd_y_lt,
    mtbi_subs,
    t = 0
)

tibble(mtbi_as_mechanism)

readr::write_csv(
    mtbi_as_mechanism,
    input_path("mtbi_as_mechanism.csv", date = TRUE)
)
```

#### Loss of consciousness

```{r}
mtbi_as_loc <- get_mtbi_loc(
    ph_p_otbi,
    abcd_y_lt,
    mtbi_subs,
    t = 0
)

dplyr::tibble(mtbi_as_loc)

readr::write_csv(
    mtbi_as_loc,
    input_path("mtbi_as_loc.csv", date = TRUE)
)
```

### Demographics

Demographic variables included in the analyses are:

* Interview age (numeric, months)
* Injury age (numeric, years)
* Sex (binary)
* Race (categorical)
* Household income (ordinal)
* Pubertal status (ordinal)

#### Interview age

```{r}
mtbi_d_interview_age <- get_interview_age(
    abcd_y_lt = abcd_y_lt,
    subjects = mtbi_subs,
    t = 0,
    as_years = FALSE
)

dplyr::tibble(mtbi_d_interview_age)

readr::write_csv(
    mtbi_d_interview_age,
    input_path("mtbi_d_interview_age.csv", TRUE)
)

unij_d_interview_age <- get_interview_age(
    abcd_y_lt = abcd_y_lt,
    subjects = unij_subs,
    t = 0,
    as_years = FALSE
)

dplyr::tibble(unij_d_interview_age)

readr::write_csv(
    unij_d_interview_age,
    input_path("unij_d_interview_age.csv", TRUE)
)
```

#### Injury age

```{r}
mtbi_d_mtbi_age <- get_mtbi_age(
    ph_p_otbi = ph_p_otbi,
    abcd_y_lt = abcd_y_lt,
    subjects = mtbi_subs,
    t = 0,
    as_years = FALSE
)

dplyr::tibble(mtbi_d_mtbi_age)

readr::write_csv(
    mtbi_d_mtbi_age,
    input_path("mtbi_d_mtbi_age.csv", TRUE)
)
```

#### Sex at birth

```{r}
mtbi_d_sex <- get_sex(
    gish_p_gi,
    mtbi_subs,
    t = 0,
    as_numeric = TRUE,
    only_m_f = TRUE
)

dplyr::tibble(mtbi_d_sex)

readr::write_csv(
    mtbi_d_sex,
    input_path("mtbi_d_sex.csv", TRUE)
)

unij_d_sex <- get_sex(
    gish_p_gi,
    unij_subs,
    t = 0,
    as_numeric = TRUE,
    only_m_f = TRUE
)

dplyr::tibble(unij_d_sex)

readr::write_csv(
    unij_d_sex,
    input_path("unij_d_sex.csv", TRUE)
)
```

#### Household income

Income was coded as a 3-level variable. 
Here are some other ABCD studies looking at income:

- 10-levels
    - Tomasi 2021 (https://pubmed.ncbi.nlm.nih.gov/33990770/)
    - Rakesh 2021 (https://pubmed.ncbi.nlm.nih.gov/34419766/)
    - Guberman 2022 (https://pubmed.ncbi.nlm.nih.gov/35579325/)
- 6-levels
    - Nagata 2024 (https://pubmed.ncbi.nlm.nih.gov/38323959/)
- 3-levels
    - Nishat 2023 (https://pubmed.ncbi.nlm.nih.gov/37441978/)
    - Nishat 2024 (https://pubmed.ncbi.nlm.nih.gov/38237797/)
    - Cook 2021 (https://pubmed.ncbi.nlm.nih.gov/34790165/)
    - Veliz 2023 (https://pubmed.ncbi.nlm.nih.gov/36689685/)

```{r}
mtbi_d_income <- get_income(
    abcd_p_demo,
    mtbi_subs,
    t = 0
)

dplyr::tibble(mtbi_d_income)

readr::write_csv(
    mtbi_d_income,
    input_path("mtbi_d_income.csv", TRUE)
)

unij_d_income <- get_income(abcd_p_demo, unij_subs, t = 0)

dplyr::tibble(unij_d_income)

readr::write_csv(
    unij_d_income,
    input_path("unij_d_income.csv", TRUE)
)
```

#### Race

```{r}
# distinct Asian category only has N = 4
mtbi_d_race <- get_race(
    abcd_p_demo,
    mtbi_subs,
    asian_as_other = TRUE,
    t = 0
)

dplyr::tibble(mtbi_d_race)

readr::write_csv(
    mtbi_d_race,
    input_path("mtbi_d_race.csv", TRUE)
)

unij_d_race <- get_race(
    abcd_p_demo,
    unij_subs,
    asian_as_other = TRUE,
    t = 0
)

dplyr::tibble(unij_d_race)

readr::write_csv(
    unij_d_race,
    input_path("unij_d_race.csv", TRUE)
)
```

#### Pubertal status

We take both reports as they aren't super correlated

```{r}
# General proportions of the PDS values
p0 <- get_pubertal_status_p(ph_p_pds, max_value = 3, t = 0)
y0 <- get_pubertal_status_y(ph_y_pds, max_value = 3, t = 0)
p1 <- get_pubertal_status_p(ph_p_pds, max_value = 99, t = 0)
y1 <- get_pubertal_status_y(ph_y_pds, max_value = 99, t = 0)

table(p0[, 2]) |> prop.table() |> signif(2) * 100
table(p1[, 2]) |> prop.table() |> signif(2) * 100 # 1.588 % of parent reports are 4 or 5
table(y0[, 2]) |> prop.table() |> signif(2) * 100
table(y1[, 2]) |> prop.table() |> signif(2) * 100 # 2.53 % of youth reports are 4 or 5


p0 <- get_pubertal_status_p(ph_p_pds, max_value = 4, t = 2)
y0 <- get_pubertal_status_y(ph_y_pds, max_value = 4, t = 2)
p1 <- get_pubertal_status_p(ph_p_pds, max_value = 99, t = 2)
y1 <- get_pubertal_status_y(ph_y_pds, max_value = 99, t = 2)

table(p0[, 2]) |> prop.table() |> signif(2) * 100
table(p1[, 2]) |> prop.table() |> signif(2) * 100 # 1.588 % of parent reports are 4 or 5
table(y0[, 2]) |> prop.table() |> signif(2) * 100
table(y1[, 2]) |> prop.table() |> signif(2) * 100 # 2.53 % of youth reports are 4 or 5

# there are four 4s here
mtbi_d_pubertal_status_p <- get_pubertal_status_p(
    ph_p_pds,
    mtbi_subs,
    max_value = 3,
    t = 0
)

# there are seven 4s here
mtbi_d_pubertal_status_y <- get_pubertal_status_y(
    ph_y_pds,
    mtbi_subs,
    max_value = 3,
    t = 0
)

mtbi_d_pubertal_status <- dplyr::inner_join(
    mtbi_d_pubertal_status_p,
    mtbi_d_pubertal_status_y
)

dplyr::tibble(mtbi_d_pubertal_status)

readr::write_csv(
    mtbi_d_pubertal_status,
    input_path("mtbi_d_pubertal_status.csv", TRUE)
)

unij_d_pubertal_status_p <- get_pubertal_status_p(
    ph_p_pds,
    unij_subs,
    max_value = 3,
    t = 0
)

unij_d_pubertal_status_y <- get_pubertal_status_y(
    ph_y_pds,
    unij_subs,
    max_value = 3,
    t = 0
)

unij_d_pubertal_status <- dplyr::inner_join(
    unij_d_pubertal_status_p,
    unij_d_pubertal_status_y
)

dplyr::tibble(unij_d_pubertal_status)

readr::write_csv(
    unij_d_pubertal_status,
    input_path("unij_d_pubertal_status.csv", TRUE)
)
```

### Medical history

Medical history variables of interest include:

1. Number of previous head injuries (discrete)
2. History of headaches (binary)

#### History of headaches

```{r}
mtbi_mh_headaches <- get_headaches(ph_p_mhx, mtbi_subs, t = 0)

dplyr::tibble(mtbi_mh_headaches)

readr::write_csv(
    mtbi_mh_headaches,
    input_path("mtbi_mh_headaches.csv", date = TRUE)
)

unij_mh_headaches <- get_headaches(ph_p_mhx, unij_subs, t = 0)

dplyr::tibble(unij_mh_headaches)

readr::write_csv(
    unij_mh_headaches,
    input_path("unij_mh_headaches.csv", date = TRUE)
)
```

#### Number of previous mTBIs

```{r}
 # N = 4 and 5 only occur once
mtbi_mh_mtbi_count <- get_mtbi_count(
    ph_p_otbi,
    abcd_y_lt,
    mtbi_subs,
    cutoff = 3,
    t = 0
)

dplyr::tibble(mtbi_mh_mtbi_count)

readr::write_csv(
    mtbi_mh_mtbi_count,
    input_path("mtbi_mh_mtbi_count.csv", date = TRUE)
)
```

### Neuroimaging

Variables of interest related to brain structure and function include:

* Structural: T1-weighted multishell diffusion-weighted MRI data
* Diffusion: Neurite density (restricted spectrum imaging)
* Functional: resting-state functional MRI data

[@hagler_image_2019] outlines the neuroimaging data present in the ABCD dataset in detail.

#### Structural MRI

The sMRI variables of interest include subcortical volumes, and cortical thicknesses, and cortical surface areas.
For cortical surface areas, the relevant file is abcd_mrisdp10201, which contains the cortical surface areas of ~150 regions (variables `mrisdp_*` where * ranges from 1 to 151).
For cortical thicknesses, the relevant file is abcd_mrisdp10201, which contains the cortical thickness of ~150 regions (variables `mrisdp_*` where * ranges from 303 to 453).

##### Subcortical volume

```{r}
mtbi_sm_subc_v <- get_subc_v(
    mri_y_smr_vol_aseg,
    mtbi_subs,
    t = 0
)

dplyr::tibble(mtbi_sm_subc_v)

readr::write_csv(
    mtbi_sm_subc_v,
    input_path("mtbi_sm_subc_v.csv", date = TRUE)
)

unij_sm_subc_v <- get_subc_v(
    mri_y_smr_vol_aseg,
    unij_subs,
    t = 0
)

dplyr::tibble(unij_sm_subc_v)

readr::write_csv(
    unij_sm_subc_v,
    input_path("unij_sm_subc_v.csv", date = TRUE)
)
```

##### Cortical thickness

Both the Desikan and Destrieux cortical parcellations could have been used for the cortical imaging data collected below.
A comparison between the two can be found in the appendix.
Because there happens to be a few more participants with calculated Desikan parcellations, that is what is used here.

```{r}
mtbi_sm_cort_t <- get_cort_t(
    mri_y_smr_thk_dsk,
    mtbi_subs,
    t = 0
)

dplyr::tibble(mtbi_sm_cort_t)

readr::write_csv(
    mtbi_sm_cort_t,
    input_path("mtbi_sm_cort_t.csv", date = TRUE)
)

unij_sm_cort_t <- get_cort_t(
    mri_y_smr_thk_dsk,
    unij_subs,
    t = 0
)

dplyr::tibble(unij_sm_cort_t)

readr::write_csv(
    unij_sm_cort_t,
    input_path("unij_sm_cort_t.csv", date = TRUE)
)
```

##### Cortical surface areas

```{r}
mtbi_sm_cort_sa <- get_cort_sa(
    mri_y_smr_area_dsk,
    mtbi_subs,
    t = 0
)

dplyr::tibble(mtbi_sm_cort_sa)

readr::write_csv(
    mtbi_sm_cort_sa,
    input_path("mtbi_sm_cort_sa.csv", date = TRUE)
)

unij_sm_cort_sa <- get_cort_sa(
    mri_y_smr_area_dsk,
    unij_subs,
    t = 0
)

dplyr::tibble(unij_sm_cort_sa)

readr::write_csv(
    unij_sm_cort_sa,
    input_path("unij_sm_cort_sa.csv", date = TRUE)
)

```

#### Diffusion MRI

We are interested in the neurite density measures of white matter regions in the brain.
Previously, these measures were found in variables containing the string "rsindwm_cdk" within the file `mri_rsi_p102.txt`.
A change anounced in the ABCD 4.0 MRI release notes indicates that neurite density is now referred to as "restricted normalized directional" and that the relevant white matter variables contain the string "rsirndwm" within the file `abcd_drsip201.txt`.

##### White matter neurite densities

Some potential summary neurite density meeasures:

* dmri_rsirnd_fib_allfib (AtlasTrack fiber segmentation, all fibers)
* dmri_rsirndwm_cdk_mean (Desikan cortical parcellation peri-cortical white matter mean)

```{r}
# White matter neurite densities
mtbi_dm_wmnd <- get_wmnd(
    mri_y_rsi_rnd_at,
    mri_y_rsi_rnd_wm_dsk,
    subjects = mtbi_subs,
    t = 0
)

dplyr::tibble(mtbi_dm_wmnd)

readr::write_csv(
    mtbi_dm_wmnd,
    input_path("mtbi_dm_wmnd.csv", date = TRUE)
)

unij_dm_wmnd <- get_wmnd(
    mri_y_rsi_rnd_at,
    mri_y_rsi_rnd_wm_dsk,
    subjects = unij_subs,
    t = 0
)

dplyr::tibble(unij_dm_wmnd)

readr::write_csv(
    unij_dm_wmnd,
    input_path("unij_dm_wmnd.csv", date = TRUE)
)
```

#### Resting-state functional MRI

We are interested in the following rs-fMRI measures that have been associated with post-concussion outcomes:

- Gordon network (cortical) correlations
    - default mode network
    - dorsal attention network
    - frontoparietal network
    - salience network
    - DMN-FPN
- Subcortical correlations
    - FPN-amygdala

##### Cortical parcellation network correlations

```{r}
mtbi_rm_gord_cor <- get_gord_cor(
    mri_y_rsfmr_cor_gp_gp,
    mtbi_subs,
    t = 0,
    roi_pairs = list(
        c("default", "default"), 
        c("dorsal_attention", "dorsal_attention"),
        c("fronto_parietal", "fronto_parietal"),
        c("salience", "salience"),
        c("default", "fronto_parietal")
    )
)

dplyr::tibble(mtbi_rm_gord_cor)

readr::write_csv(
    mtbi_rm_gord_cor,
    input_path("mtbi_rm_gord_cor.csv", date = TRUE)
)

unij_rm_gord_cor <- get_gord_cor(
    mri_y_rsfmr_cor_gp_gp,
    unij_subs,
    t = 0,
    roi_pairs = list(
        c("default", "default"), 
        c("dorsal_attention", "dorsal_attention"),
        c("fronto_parietal", "fronto_parietal"),
        c("salience", "salience"),
        c("default", "fronto_parietal")
    )
)

dplyr::tibble(unij_rm_gord_cor)

readr::write_csv(
    unij_rm_gord_cor,
    input_path("unij_rm_gord_cor.csv", date = TRUE)
)
```

##### Subcortical parcellation network correlations

```{r}
mtbi_rm_subc_cor <- get_subc_cor(
    mri_y_rsfmr_cor_gp_aseg,
    mtbi_subs,
    t = 0,
    roi_pairs = list(
        c("fronto_parietal", "left_amygdala"),
        c("fronto_parietal", "right_amygdala")
    )
)

dplyr::tibble(mtbi_rm_subc_cor)

readr::write_csv(
    mtbi_rm_subc_cor,
    input_path("mtbi_rm_subc_cor.csv", date = TRUE)
)

unij_rm_subc_cor <- get_subc_cor(
    mri_y_rsfmr_cor_gp_aseg,
    unij_subs,
    t = 0,
    roi_pairs = list(
        c("fronto_parietal", "left_amygdala"),
        c("fronto_parietal", "right_amygdala")
    )
)

dplyr::tibble(unij_rm_subc_cor)

readr::write_csv(
    unij_rm_subc_cor,
    input_path("unij_rm_subc_cor.csv", date = TRUE)
)
```

### Psychosocial resilience

Psychosocial factors of interest include:

- total number of friends (discretized into quartiles)
- screen time (hours)
- participation in sports and activities (discretized into quartiles)
- time spent exercising (discretized into quartiles)
- prosocial behaviour (ordinal responses indicating agreement to child demonstrating prosocial attributes including not true (0), somewhat true (1), and certainly true (2))
- family environment/function (similar ordinal responses to family environment questions)
- parent psychopathology scores (raw scores from aseba parent self report)

#### Number of friends

```{r}
mtbi_p_friends <- get_friends(
    mh_y_or,
    gish_p_gi,
    mtbi_subs,
    discretize = TRUE,
    t = 0
)

dplyr::tibble(mtbi_p_friends)

readr::write_csv(
    mtbi_p_friends,
    input_path("mtbi_p_friends.csv", date = TRUE)
)

unij_p_friends <- get_friends(
    mh_y_or,
    gish_p_gi,
    unij_subs,
    discretize = TRUE,
    t = 0
)

dplyr::tibble(unij_p_friends)

readr::write_csv(
    unij_p_friends,
    input_path("unij_p_friends.csv", date = TRUE)
)
```

#### Healthy behaviours

##### Screen time

```{r}
mtbi_p_screen_time <- get_screen_time(
    nt_p_stq,
    mtbi_subs,
    t = 0
)

dplyr::tibble(mtbi_p_screen_time)

readr::write_csv(
    mtbi_p_screen_time,
    input_path("mtbi_p_screen_time.csv", date = TRUE)
)

unij_p_screen_time <- get_screen_time(
    nt_p_stq,
    unij_subs,
    t = 0
)

dplyr::tibble(unij_p_screen_time)

readr::write_csv(
    unij_p_screen_time,
    input_path("unij_p_screen_time.csv", date = TRUE)
)
```

##### Sports and activities participation

```{r}
mtbi_p_sports <- get_sports_and_activities(
    ph_p_saiq,
    mtbi_subs,
    t = 0,
    discretize = TRUE
)

dplyr::tibble(mtbi_p_sports)
skimr::skim(mtbi_p_sports)

readr::write_csv(
    mtbi_p_sports,
    input_path("mtbi_p_sports.csv", date = TRUE)
)

unij_p_sports <- get_sports_and_activities(
    ph_p_saiq,
    unij_subs,
    t = 0,
    discretize = TRUE
)

dplyr::tibble(unij_p_sports)
skimr::skim(unij_p_sports)

readr::write_csv(
    unij_p_sports,
    input_path("unij_p_sports.csv", date = TRUE)
)
```

##### Exercise habits

```{r}
mtbi_p_exercise <- get_exercise(
    ph_y_yrb,
    mtbi_subs,
    t = 0
)

dplyr::tibble(mtbi_p_exercise)

readr::write_csv(
    mtbi_p_exercise,
    input_path("mtbi_p_exercise.csv", date = TRUE)
)

unij_p_exercise <- get_exercise(
    ph_y_yrb,
    unij_subs,
    t = 0
)

dplyr::tibble(unij_p_exercise)

readr::write_csv(
    unij_p_exercise,
    input_path("unij_p_exercise.csv", date = TRUE)
)
```

#### Prosocial behaviour

```{r}
mtbi_p_prosocial_p <- get_prosocial_behaviour_p(
    ce_p_psb,
    mtbi_subs,
    no_zero = TRUE,
    t = 0
)

mtbi_p_prosocial_y <- get_prosocial_behaviour_y(
    ce_y_psb,
    mtbi_subs,
    no_zero = TRUE,
    t = 0
)

mtbi_p_prosocial <- dplyr::inner_join(
    mtbi_p_prosocial_y,
    mtbi_p_prosocial_p
)

dplyr::tibble(mtbi_p_prosocial)

readr::write_csv(
    mtbi_p_prosocial,
    input_path("mtbi_p_prosocial.csv", date = TRUE)
)

unij_p_prosocial_p <- get_prosocial_behaviour_p(
    ce_p_psb,
    unij_subs,
    no_zero = TRUE,
    t = 0
)

unij_p_prosocial_y <- get_prosocial_behaviour_y(
    ce_y_psb,
    unij_subs,
    no_zero = TRUE,
    t = 0
)

unij_p_prosocial <- dplyr::inner_join(
    unij_p_prosocial_p,
    unij_p_prosocial_y
)

dplyr::tibble(unij_p_prosocial)

readr::write_csv(
    unij_p_prosocial,
    input_path("unij_p_prosocial.csv", date = TRUE)
)
```

#### Family function

Another feature where we take parent and youth reports on the basis of them not being very similar.

```{r}
mtbi_p_fam_fn <- get_family_function(
    ce_y_fes,
    ce_p_fes,
    mtbi_subs,
    t = 0
)

dplyr::tibble(mtbi_p_fam_fn)

readr::write_csv(
    mtbi_p_fam_fn,
    input_path("mtbi_p_fam_fn.csv", date = TRUE)
)

unij_p_fam_fn <- get_family_function(
    ce_y_fes,
    ce_p_fes,
    unij_subs,
    t = 0
)

dplyr::tibble(unij_p_fam_fn)

readr::write_csv(
    unij_p_fam_fn,
    input_path("unij_p_fam_fn.csv", date = TRUE)
)
```

#### Parent psychopathology

Raw scores for:
    
- personal strength,
- anxious/depressed problems,
- withdrawn problems,
- somatic complaints,
- thought problems,
- attention problems,
- aggressive behaviour,
- intrusive thoughts,
- depressive problems
- anxiety problems
- avoidant problems,
- antisocial problems,
- hyperactive problems


search_dd("asr_scr_") |>
    dplyr::select(-notes, -table_name_nda, -table_name) |>
    data.frame()

```{r}
mtbi_p_parent_psych <- get_parent_psychopathology(
    mh_p_asr,
    mtbi_subs,
    t = 0,
    raw = TRUE
)

colnames(mtbi_p_parent_psych)

dplyr::tibble(mtbi_p_parent_psych)

readr::write_csv(
    mtbi_p_parent_psych,
    input_path("mtbi_p_parent_psych.csv", date = TRUE)
)

unij_p_parent_psych <- get_parent_psychopathology(
    mh_p_asr,
    unij_subs,
    t = 0,
    raw = TRUE
)

dplyr::tibble(unij_p_parent_psych)

readr::write_csv(
    unij_p_parent_psych,
    input_path("unij_p_parent_psych.csv", date = TRUE)
)
```

## Output variables

### Child Behaviour Checklist

CBCL syndrom subscales include anxious-depressed withdrawn-depressed, somatic complaints, social complaints, thought complaints, attention complaints, rulebreak complaints, and aggressive complaints.

```{r}
mtbi_cbcl <- get_cbcl_syndrome_scale(
    mh_p_cbcl,
    raw = TRUE,
    subjects = mtbi_subs,
    t = 0
)

dplyr::tibble(mtbi_cbcl)

readr::write_csv(
    mtbi_cbcl,
    input_path("mtbi_cbcl.csv", date = TRUE)
)

unij_cbcl <- get_cbcl_syndrome_scale(
    mh_p_cbcl,
    raw = TRUE,
    subjects = unij_subs,
    t = 0
)

dplyr::tibble(unij_cbcl)

readr::write_csv(
    unij_cbcl,
    input_path("unij_cbcl.csv", date = TRUE)
)
```

### Sleep disturbance scale

```{r}
mtbi_sds <- get_sleep_disturbance(
    ph_p_sds,
    mtbi_subs,
    t = 0
)

dplyr::tibble(mtbi_sds)

readr::write_csv(
    mtbi_sds,
    input_path("mtbi_sds.csv", date = TRUE)
)

unij_sds <- get_sleep_disturbance(
    ph_p_sds,
    unij_subs,
    t = 0
)

dplyr::tibble(unij_sds)

readr::write_csv(
    unij_sds,
    input_path("unij_sds.csv", date = TRUE)
)
```

## Other covariates

### Scanner information

Note that there are 22 unique site values: https://neurostars.org/t/abcd-family-nested-within-site-or-scanner-id-how-to-deal-with-inaccuracies/18664

```{r}
set.seed(42)
mtbi_scanner <- get_scanner_id(
    mri_y_adm_info = mri_y_adm_info,
    subjects = mtbi_subs,
    t = 0,
    abcd_y_lt = abcd_y_lt,
    sample_missing = TRUE
)

dplyr::tibble(mtbi_scanner)

readr::write_csv(
    mtbi_scanner,
    input_path("mtbi_scanner.csv", date = TRUE)
)

set.seed(42)
unij_scanner <- get_scanner_id(
    mri_y_adm_info = mri_y_adm_info,
    subjects = unij_subs,
    t = 0,
    abcd_y_lt = abcd_y_lt,
    sample_missing = TRUE
)

dplyr::tibble(unij_scanner)

readr::write_csv(
    unij_scanner,
    input_path("unij_scanner.csv", date = TRUE)
)
```

### Family ID

What family the child belonged to to account for sibling exclusions.

```{r}
mtbi_family <- get_family_id(
    abcd_y_lt,
    mtbi_subs,
    t = 0
)

dplyr::tibble(mtbi_family)

readr::write_csv(
    mtbi_family,
    input_path("mtbi_family.csv", date = TRUE)
)

unij_family <- get_family_id(
    abcd_y_lt,
    unij_subs,
    t = 0
)

dplyr::tibble(unij_family)

readr::write_csv(
    unij_family,
    input_path("unij_family.csv", date = TRUE)
)
```

### Site ID

Site ID provides information for scanner when imputing neuroimaging data and running combat harmonization.

```{r}
mtbi_site <- get_site_id(
    abcd_y_lt,
    mtbi_subs,
    t = 0
)

dplyr::tibble(mtbi_site)

readr::write_csv(
    mtbi_site,
    input_path("mtbi_site.csv", date = TRUE)
)

unij_site <- get_site_id(
    abcd_y_lt,
    unij_subs,
    t = 0
)

dplyr::tibble(unij_site)

readr::write_csv(
    unij_site,
    input_path("unij_site.csv", date = TRUE)
)
```
