# Data Preprocessing

In this chapter, I

1. Assign train and test sets of the data
2. Remove neuroimaging data for participants who do not meet ABCD's QC
3. Use mice imputation to impute missing data
4. Organize and export all data as nested lists

## Importing Extracted Data

```{r}
library(abcdutils)
library(here)
library(dplyr)
library(readr)
library(metasnf)
library(mice)
library(rlist)

source("abcd/helper_functions.R")

input_path <- path_maker(here(paste0("data/abcd/inputs")))
raw_path <- path_maker(here(paste0("data/abcd/raw")))
core_path <- path_maker(here(paste0("data/abcd/core")))
misc_path <- path_maker(here(paste0("data/abcd/misc")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))

# Subjects
mtbi_subjects <- read_subjects(
    sub_path("2024_04_17_mtbi_subjects.csv")
)
uninj_subjects <- read_subjects(
    sub_path("2024_04_17_uninjured_subjects.csv")
)

read <- function(path) {
    read_csv(input_path(path))
}
```

```{r}
# mTBI data
as_mem_daze_mtbi <- read("2024_04_17_as_mem_daze_mtbi.csv")
as_mechanism_mtbi <- read("2024_04_17_as_mechanism_mtbi.csv")
as_loc_mtbi <- read("2024_04_17_as_loc_mtbi.csv")
d_interview_age_mtbi <- read("2024_04_17_d_interview_age_mtbi.csv")
d_mtbi_age_mtbi <- read("2024_04_17_d_mtbi_age_mtbi.csv")
d_sex_mtbi <- read("2024_04_17_d_sex_mtbi.csv")
d_income_mtbi <- read("2024_04_17_d_income_mtbi.csv")
d_race_mtbi <- read("2024_04_17_d_race_mtbi.csv")
d_pubertal_status_mtbi <- read("2024_04_17_d_pubertal_status_mtbi.csv")
mh_headaches_mtbi <- read("2024_04_17_mh_headaches_mtbi.csv")
mh_mtbi_count_mtbi <- read("2024_04_17_mh_mtbi_count_mtbi.csv")
sm_subc_v_mtbi <- read("2024_04_17_sm_subc_v_mtbi.csv")
sm_cort_t_mtbi <- read("2024_04_17_sm_cort_t_mtbi.csv")
sm_cort_sa_mtbi <- read("2024_04_17_sm_cort_sa_mtbi.csv")
dm_all_wmnd_mtbi <- read("2024_04_17_dm_all_wmnd_mtbi.csv")
rm_gord_cor_mtbi <- read("2024_04_17_rm_gord_cor_mtbi.csv")
rm_subc_cor_mtbi <- read("2024_04_17_rm_subc_cor_mtbi.csv")
p_loneliness_mtbi <- read("2024_04_17_p_loneliness_mtbi.csv")
p_screen_time_mtbi <- read("2024_04_17_p_screen_time_mtbi.csv")
p_sports_mtbi <- read("2024_04_17_p_sports_mtbi.csv")
p_exercise_mtbi <- read("2024_04_17_p_exercise_mtbi.csv")
p_prosocial_mtbi <- read("2024_04_17_p_prosocial_mtbi.csv")
p_fam_fn_mtbi <- read("2024_04_17_p_fam_fn_mtbi.csv")
p_parent_psych_mtbi <- read("2024_04_17_p_parent_psych_mtbi.csv")
cbcl_anxdep_mtbi <- read("2024_04_17_cbcl_anxdep_mtbi.csv")
cbcl_withdep_mtbi <- read("2024_04_17_cbcl_withdep_mtbi.csv")
cbcl_somatic_mtbi <- read("2024_04_17_cbcl_somatic_mtbi.csv")
cbcl_social_mtbi <- read("2024_04_17_cbcl_social_mtbi.csv")
cbcl_thought_mtbi <- read("2024_04_17_cbcl_thought_mtbi.csv")
cbcl_attention_mtbi <- read("2024_04_17_cbcl_attention_mtbi.csv")
cbcl_rulebreak_mtbi <- read("2024_04_17_cbcl_rulebreak_mtbi.csv")
cbcl_aggressive_mtbi <- read("2024_04_17_cbcl_aggressive_mtbi.csv")
sds_total_probs_mtbi <- read("2024_04_17_sds_total_probs_mtbi.csv")

# Uninjured subjects
d_interview_age_uninj <- read("2024_04_17_d_interview_age_uninj.csv")
d_sex_uninj <- read("2024_04_17_d_sex_uninj.csv")
d_income_uninj <- read("2024_04_17_d_income_uninj.csv")
d_race_uninj <- read("2024_04_17_d_race_uninj.csv")
d_pubertal_status_uninj <- read("2024_04_17_d_pubertal_status_uninj.csv")
mh_headaches_uninj <- read("2024_04_17_mh_headaches_uninj.csv")
sm_subc_v_uninj <- read("2024_04_17_sm_subc_v_uninj.csv")
sm_cort_t_uninj <- read("2024_04_17_sm_cort_t_uninj.csv")
sm_cort_sa_uninj <- read("2024_04_17_sm_cort_sa_uninj.csv")
dm_all_wmnd_uninj <- read("2024_04_17_dm_all_wmnd_uninj.csv")
rm_gord_cor_uninj <- read("2024_04_17_rm_gord_cor_uninj.csv")
rm_subc_cor_uninj <- read("2024_04_17_rm_subc_cor_uninj.csv")
p_loneliness_uninj <- read("2024_04_17_p_loneliness_uninj.csv")
p_screen_time_uninj <- read("2024_04_17_p_screen_time_uninj.csv")
p_sports_uninj <- read("2024_04_17_p_sports_uninj.csv")
p_exercise_uninj <- read("2024_04_17_p_exercise_uninj.csv")
p_prosocial_uninj <- read("2024_04_17_p_prosocial_uninj.csv")
p_fam_fn_uninj <- read("2024_04_17_p_fam_fn_uninj.csv")
p_parent_psych_uninj <- read("2024_04_17_p_parent_psych_uninj.csv")
cbcl_anxdep_uninj <- read("2024_04_17_cbcl_anxdep_uninj.csv")
cbcl_withdep_uninj <- read("2024_04_17_cbcl_withdep_uninj.csv")
cbcl_somatic_uninj <- read("2024_04_17_cbcl_somatic_uninj.csv")
cbcl_social_uninj <- read("2024_04_17_cbcl_social_uninj.csv")
cbcl_thought_uninj <- read("2024_04_17_cbcl_thought_uninj.csv")
cbcl_attention_uninj <- read("2024_04_17_cbcl_attention_uninj.csv")
cbcl_rulebreak_uninj <- read("2024_04_17_cbcl_rulebreak_uninj.csv")
cbcl_aggressive_uninj <- read("2024_04_17_cbcl_aggressive_uninj.csv")
sds_total_probs_uninj <- read("2024_04_17_sds_total_probs_uninj.csv")




cbcl_anxdep_mtbi
cbcl_withdep_mtbi
cbcl_somatic_mtbi
cbcl_social_mtbi
cbcl_thought_mtbi
cbcl_attention_mtbi
cbcl_rulebreak_mtbi
cbcl_aggressive_mtbi
sds_total_probs_mtbi








```

## mTBI vs. Uninj Initial Comparisons

```{r}

mtbi_initial_df_list <- list(
    as_mem_daze_mtbi,
    as_mechanism_mtbi,
    as_loc_mtbi,
    d_interview_age_mtbi,
    d_mtbi_age_mtbi,
    d_sex_mtbi,
    d_income_mtbi,
    d_race_mtbi,
    d_pubertal_status_mtbi,
    mh_headaches_mtbi,
    mh_mtbi_count_mtbi,
    sm_subc_v_mtbi,
    sm_cort_t_mtbi,
    sm_cort_sa_mtbi,
    dm_all_wmnd_mtbi,
    rm_gord_cor_mtbi,
    rm_subc_cor_mtbi,
    p_loneliness_mtbi,
    p_screen_time_mtbi,
    p_sports_mtbi,
    p_exercise_mtbi,
    p_prosocial_mtbi,
    p_fam_fn_mtbi,
    p_parent_psych_mtbi,
    cbcl_anxdep_mtbi,
    cbcl_withdep_mtbi,
    cbcl_somatic_mtbi,
    cbcl_social_mtbi,
    cbcl_thought_mtbi,
    cbcl_attention_mtbi,
    cbcl_rulebreak_mtbi,
    cbcl_aggressive_mtbi,
    sds_total_probs_mtbi
)

uninj_initial_df_list <- list(
    d_interview_age_uninj,
    d_sex_uninj,
    d_income_uninj,
    d_race_uninj,
    d_pubertal_status_uninj,
    mh_headaches_uninj,
    sm_subc_v_uninj,
    sm_cort_t_uninj,
    sm_cort_sa_uninj,
    dm_all_wmnd_uninj,
    rm_gord_cor_uninj,
    rm_subc_cor_uninj,
    p_loneliness_uninj,
    p_screen_time_uninj,
    p_sports_uninj,
    p_exercise_uninj,
    p_prosocial_uninj,
    p_fam_fn_uninj,
    p_parent_psych_uninj,
    cbcl_anxdep_uninj,
    cbcl_withdep_uninj,
    cbcl_somatic_uninj,
    cbcl_social_uninj,
    cbcl_thought_uninj,
    cbcl_attention_uninj,
    cbcl_rulebreak_uninj,
    cbcl_aggressive_uninj,
    sds_total_probs_uninj
)

mtbi_initial_df <- merge_df_list(mtbi_initial_df_list, join = "full")
uninj_initial_df <- merge_df_list(uninj_initial_df_list, join = "full")

nrow(mtbi_initial_df)

baseline_initial_df <- bind_rows(mtbi_initial_df, uninj_initial_df)


```

## Neuroimaging quality control

Subset neuroimaging data to those subjects who pass neuroimaging QC and PC.

```{r}
mri_y_qc_raw_smr_t1 <- abcd_load(core_path("imaging/mri_y_qc_raw_smr_t1.csv"))
mri_y_qc_raw_smr_t2 <- abcd_load(core_path("imaging/mri_y_qc_raw_smr_t2.csv"))
mri_y_qc_raw_rsfmr <- abcd_load(core_path("imaging/mri_y_qc_raw_rsfmr.csv"))
mri_y_qc_raw_dmr <- abcd_load(core_path("imaging/mri_y_qc_raw_dmr.csv"))

# sMRI
smri_qc_mtbi <- abcdutils::qc_smri(
    mri_y_qc_raw_smr_t1,
    t = 0,
    subjects = mtbi_subjects,
    metric = "qc"
)
smri_pc_mtbi <- abcdutils::qc_smri(
    mri_y_qc_raw_smr_t1,
    t = 0,
    subjects = mtbi_subjects,
    metric = "pc"
)
smri_qc_uninj <- abcdutils::qc_smri(
    mri_y_qc_raw_smr_t1,
    t = 0,
    subjects = uninj_subjects,
    metric = "qc"
)
smri_pc_uninj <- abcdutils::qc_smri(
    mri_y_qc_raw_smr_t1,
    t = 0,
    subjects = uninj_subjects,
    metric = "pc"
)

# dMRI
dmri_qc_mtbi <- abcdutils::qc_dmri(
    mri_y_qc_raw_dmr,
    t = 0,
    subjects = mtbi_subjects,
    metric = "qc"
)
dmri_pc_mtbi <- abcdutils::qc_dmri(
    mri_y_qc_raw_dmr,
    t = 0,
    subjects = mtbi_subjects,
    metric = "pc"
)
dmri_qc_uninj <- abcdutils::qc_dmri(
    mri_y_qc_raw_dmr,
    t = 0,
    subjects = uninj_subjects,
    metric = "qc"
)
dmri_pc_uninj <- abcdutils::qc_dmri(
    mri_y_qc_raw_dmr,
    t = 0,
    subjects = uninj_subjects,
    metric = "pc"
)

# rs-fMRI
rsfmri_qc_mtbi <- qc_rsfmri(
    mri_y_qc_raw_rsfmr,
    t = 0,
    subjects = mtbi_subjects,
    metric = "qc"
)
rsfmri_pc_mtbi <- qc_rsfmri(
    mri_y_qc_raw_rsfmr,
    t = 0,
    subjects = mtbi_subjects,
    metric = "pc"
)
rsfmri_qc_uninj <- qc_rsfmri(
    mri_y_qc_raw_rsfmr,
    t = 0,
    subjects = uninj_subjects,
    metric = "qc"
)
rsfmri_pc_uninj <- qc_rsfmri(
    mri_y_qc_raw_rsfmr,
    t = 0,
    subjects = uninj_subjects,
    metric = "pc"
)

smri_pass <- c(
    intersect(smri_qc_mtbi$"pass", smri_pc_mtbi$"pass"),
    intersect(smri_qc_uninj$"pass", smri_pc_uninj$"pass")
)

dmri_pass <- c(
    intersect(dmri_qc_mtbi$"pass", dmri_pc_mtbi$"pass"),
    intersect(dmri_qc_uninj$"pass", dmri_pc_uninj$"pass")
)

rsfmri_pass <- c(
    intersect(rsfmri_qc_mtbi$"pass", rsfmri_pc_mtbi$"pass"),
    intersect(rsfmri_qc_uninj$"pass", rsfmri_pc_uninj$"pass")
)

sm_subc_v_qc_mtbi <- filter(sm_subc_v_mtbi, subjectkey %in% smri_pass)
sm_cort_t_qc_mtbi <- filter(sm_cort_t_mtbi, subjectkey %in% smri_pass)
sm_cort_sa_qc_mtbi <- filter(sm_cort_sa_mtbi, subjectkey %in% smri_pass)
sm_subc_v_qc_uninj <- filter(sm_subc_v_uninj, subjectkey %in% smri_pass)
sm_cort_t_qc_uninj <- filter(sm_cort_t_uninj, subjectkey %in% smri_pass)
sm_cort_sa_qc_uninj <- filter(sm_cort_sa_uninj, subjectkey %in% smri_pass)
dm_all_wmnd_qc_mtbi <- filter(dm_all_wmnd_mtbi, subjectkey %in% dmri_pass)
dm_all_wmnd_qc_uninj <- filter(dm_all_wmnd_uninj, subjectkey %in% dmri_pass)
rm_gord_cor_qc_mtbi <- filter(rm_gord_cor_mtbi, subjectkey %in% rsfmri_pass)
rm_subc_cor_qc_mtbi <- filter(rm_subc_cor_mtbi, subjectkey %in% rsfmri_pass)
rm_gord_cor_qc_uninj <- filter(rm_gord_cor_uninj, subjectkey %in% rsfmri_pass)
rm_subc_cor_qc_uninj <- filter(rm_subc_cor_uninj, subjectkey %in% rsfmri_pass)

write_csv(sm_cort_sa_qc_mtbi, input_path("sm_cort_sa_qc_mtbi.csv", TRUE))
write_csv(sm_cort_t_qc_mtbi, input_path("sm_cort_t_qc_mtbi.csv", TRUE))
write_csv(sm_subc_v_qc_mtbi, input_path("sm_subc_v_qc_mtbi.csv", TRUE))
write_csv(sm_cort_sa_qc_uninj, input_path("sm_cort_sa_qc_uninj.csv", TRUE))
write_csv(sm_cort_t_qc_uninj, input_path("sm_cort_t_qc_uninj.csv", TRUE))
write_csv(sm_subc_v_qc_uninj, input_path("sm_subc_v_qc_uninj.csv", TRUE))
write_csv(dm_all_wmnd_qc_mtbi, input_path("dm_all_wmnd_qc_mtbi.csv", TRUE))
write_csv(dm_all_wmnd_qc_uninj, input_path("dm_all_wmnd_qc_uninj.csv", TRUE))
write_csv(rm_gord_cor_qc_mtbi, input_path("rm_gord_cor_qc_mtbi.csv", TRUE))
write_csv(rm_subc_cor_qc_mtbi, input_path("rm_subc_cor_qc_mtbi.csv", TRUE))
write_csv(rm_gord_cor_qc_uninj, input_path("rm_gord_cor_qc_uninj.csv", TRUE))
write_csv(rm_subc_cor_qc_uninj, input_path("rm_subc_cor_qc_uninj.csv", TRUE))
```

```{r}
sm_cort_sa_qc_mtbi <- read("2024_04_17_sm_cort_sa_qc_mtbi.csv")
sm_cort_t_qc_mtbi <- read("2024_04_17_sm_cort_t_qc_mtbi.csv")
sm_subc_v_qc_mtbi <- read("2024_04_17_sm_subc_v_qc_mtbi.csv")
sm_cort_sa_qc_uninj <- read("2024_04_17_sm_cort_sa_qc_uninj.csv")
sm_cort_t_qc_uninj <- read("2024_04_17_sm_cort_t_qc_uninj.csv")
sm_subc_v_qc_uninj <- read("2024_04_17_sm_subc_v_qc_uninj.csv")
dm_all_wmnd_qc_mtbi <- read("2024_04_17_dm_all_wmnd_qc_mtbi.csv")
dm_all_wmnd_qc_uninj <- read("2024_04_17_dm_all_wmnd_qc_uninj.csv")
rm_gord_cor_qc_mtbi <- read("2024_04_17_rm_gord_cor_qc_mtbi.csv")
rm_subc_cor_qc_mtbi <- read("2024_04_17_rm_subc_cor_qc_mtbi.csv")
rm_gord_cor_qc_uninj <- read("2024_04_17_rm_gord_cor_qc_uninj.csv")
rm_subc_cor_qc_uninj <- read("2024_04_17_rm_subc_cor_qc_uninj.csv")
```

## Train/Test Split

To avoid having training and testing data inform each other during imputation, we assign the splits prior to the imputation.
This is only done in our primary analysis group (baseline mTBI).

```{r}
mtbi_split <- train_test_assign(
    train_frac = 0.8,
    subjects = mtbi_subjects
)

mtbi_train <- mtbi_split$"train"
mtbi_test <- mtbi_split$"test"

write_subjects(mtbi_train, sub_path("mtbi_train_subjects.csv", TRUE))
write_subjects(mtbi_test, sub_path("mtbi_test_subjects.csv", TRUE))

mtbi_train <- read_subjects(sub_path("2024_04_18_mtbi_train_subjects.csv"))
mtbi_test <- read_subjects(sub_path("2024_04_18_mtbi_test_subjects.csv"))

train_filter <- function(df) {
    filtered_df <- dplyr::filter(
        df,
        df$"subjectkey" %in% mtbi_train
    )
    return(filtered_df)
}

test_filter <- function(df) {
    filtered_df <- dplyr::filter(
        df,
        df$"subjectkey" %in% mtbi_test
    )
    return(filtered_df)
}

mtbi_dfs <- list(
    "subjects" = data.frame(subjectkey = mtbi_subjects),
    "as_mem_daze_mtbi" = as_mem_daze_mtbi,
    "as_mechanism_mtbi" = as_mechanism_mtbi,
    "as_loc_mtbi" = as_loc_mtbi,
    "d_interview_age_mtbi" = d_interview_age_mtbi,
    "d_mtbi_age_mtbi" = d_mtbi_age_mtbi,
    "d_sex_mtbi" = d_sex_mtbi,
    "d_income_mtbi" = d_income_mtbi,
    "d_race_mtbi" = d_race_mtbi,
    "d_pubertal_status_mtbi" = d_pubertal_status_mtbi,
    "mh_headaches_mtbi" = mh_headaches_mtbi,
    "mh_mtbi_count_mtbi" = mh_mtbi_count_mtbi,
    "sm_subc_v_qc_mtbi" = sm_subc_v_qc_mtbi,
    "sm_cort_t_qc_mtbi" = sm_cort_t_qc_mtbi,
    "sm_cort_sa_qc_mtbi" = sm_cort_sa_qc_mtbi,
    "dm_all_wmnd_qc_mtbi" = dm_all_wmnd_qc_mtbi,
    "rm_gord_cor_qc_mtbi" = rm_gord_cor_qc_mtbi,
    "rm_subc_cor_qc_mtbi" = rm_subc_cor_qc_mtbi,
    "p_loneliness_mtbi" = p_loneliness_mtbi,
    "p_screen_time_mtbi" = p_screen_time_mtbi,
    "p_sports_mtbi" = p_sports_mtbi,
    "p_exercise_mtbi" = p_exercise_mtbi,
    "p_prosocial_mtbi" = p_prosocial_mtbi,
    "p_fam_fn_mtbi" = p_fam_fn_mtbi,
    "p_parent_psych_mtbi" = p_parent_psych_mtbi,
    "cbcl_anxdep_mtbi" = cbcl_anxdep_mtbi,
    "cbcl_withdep_mtbi" = cbcl_withdep_mtbi,
    "cbcl_somatic_mtbi" = cbcl_somatic_mtbi,
    "cbcl_social_mtbi" = cbcl_social_mtbi,
    "cbcl_thought_mtbi" = cbcl_thought_mtbi,
    "cbcl_attention_mtbi" = cbcl_attention_mtbi,
    "cbcl_rulebreak_mtbi" = cbcl_rulebreak_mtbi,
    "cbcl_aggressive_mtbi" = cbcl_aggressive_mtbi,
    "sds_total_probs_mtbi" = sds_total_probs_mtbi
)

uninj_dfs <- list(
    "subjects" = data.frame(subjectkey = uninj_subjects),
    "d_interview_age_uninj" = d_interview_age_uninj,
    "d_sex_uninj" = d_sex_uninj,
    "d_income_uninj" = d_income_uninj,
    "d_race_uninj" = d_race_uninj,
    "d_pubertal_status_uninj" = d_pubertal_status_uninj,
    "mh_headaches_uninj" = mh_headaches_uninj,
    "sm_subc_v_qc_uninj" = sm_subc_v_qc_uninj,
    "sm_cort_t_qc_uninj" = sm_cort_t_qc_uninj,
    "sm_cort_sa_qc_uninj" = sm_cort_sa_qc_uninj,
    "dm_all_wmnd_qc_uninj" = dm_all_wmnd_qc_uninj,
    "rm_gord_cor_qc_uninj" = rm_gord_cor_qc_uninj,
    "rm_subc_cor_qc_uninj" = rm_subc_cor_qc_uninj,
    "p_loneliness_uninj" = p_loneliness_uninj,
    "p_screen_time_uninj" = p_screen_time_uninj,
    "p_sports_uninj" = p_sports_uninj,
    "p_exercise_uninj" = p_exercise_uninj,
    "p_prosocial_uninj" = p_prosocial_uninj,
    "p_fam_fn_uninj" = p_fam_fn_uninj,
    "p_parent_psych_uninj" = p_parent_psych_uninj,
    "cbcl_anxdep_uninj" = cbcl_anxdep_uninj,
    "cbcl_withdep_uninj" = cbcl_withdep_uninj,
    "cbcl_somatic_uninj" = cbcl_somatic_uninj,
    "cbcl_social_uninj" = cbcl_social_uninj,
    "cbcl_thought_uninj" = cbcl_thought_uninj,
    "cbcl_attention_uninj" = cbcl_attention_uninj,
    "cbcl_rulebreak_uninj" = cbcl_rulebreak_uninj,
    "cbcl_aggressive_uninj" = cbcl_aggressive_uninj,
    "sds_total_probs_uninj" = sds_total_probs_uninj
)

mtbi_train_dfs <- lapply(mtbi_dfs, train_filter)
mtbi_test_dfs <- lapply(mtbi_dfs, test_filter)
```

## Imputation

SNF requires complete data as input for integration.

Data will be imputed under the following schemes:

- 5 imputations of mTBI data alone
- 5 imputations of uninjured data alone
- 5 imputations of mTBI + uninjured data together

Resulting in 10 versions of the mTBI data and 10 versions of the uninjured data.

First, each group has their extracted dataframes merged into a single one for imputation.

```{r}
mtbi_train_df <- merge_df_list(mtbi_train_dfs, join = "full")
mtbi_test_df <- merge_df_list(mtbi_test_dfs, join = "full")
uninj_df <- merge_df_list(uninj_dfs, join = "full")
```

A check of which columns have missing data.

```{r}
missing_colnames_mtbi <- names(which(colSums(is.na(mtbi_train_df)) > 0))
missing_colnames_mtbi

missing_colnames_uninj <- names(which(colSums(is.na(uninj_df)) > 0))
missing_colnames_uninj

# Remove the subjectkey variable
mtbi_train_df_no_subs <- char_to_fac(mtbi_train_df[, -1])
mtbi_test_df_no_subs <- char_to_fac(mtbi_test_df[, -1])
uninj_df_no_subs <- char_to_fac(uninj_df[, -1])

# Function that checks which variables have the biggest correlations
pairwise_correlations <- function(df, threshold = 0) {
    # Remove missing data to help calculate correlations
    df <- na.omit(df)
    # Remove non-numeric columns
    non_numeric_cols <- sapply(df, function(x) !is.numeric(x))
    df <- df[, !non_numeric_cols]
    # Calculate correlations
    correlations <- cor(df)
    # Ignore self-correlations
    diag(correlations) <- 0
    # Take absolute value of the correlations, as strong anti-correlations also
    # lead to strong linear dependence
    abs_cor <- abs(correlations)
    # Create dataframe of all pairs of correlations
    pairs <- t(combn(colnames(abs_cor), 2))
    paired_cors <- data.frame(pairs, cor = abs_cor[pairs])
    # Filter to only correlations bigger than a specified threshold
    paired_cors <- paired_cors[paired_cors$"cor" > threshold, ]
    return(paired_cors)
}

# Function to help sort variables by pairwise correlations
top_correlating_vars <- function(df, threshold = 0) {
    # Dataframe highlighting strongest correlations
    df <- pairwise_correlations(df, threshold)
    # Iteratively build up an ordered correlations matrix by:
    #   - Record one of the two variables contributing to the largest
    #     pairwise correlation
    #   - Remove that variables from the list of all pairs of correlations
    #   - Repeat until all variables have been removed
    max_cor_df <- data.frame(
        variable = as.character(),
        max_cor = as.numeric()
    )
    i <- 0
    while (nrow(df) > 0) {
        i <- i + 1
        row_with_max_cor <- which(df$"cor" == max(df$"cor"))[1]
        var_with_max_cor <- df[row_with_max_cor, "X1"]
        max_cor <- df[row_with_max_cor, "cor"]
        max_cor_df <- rbind(
            max_cor_df,
            data.frame(
                variable = var_with_max_cor,
                max_cor = max_cor
            )
        )
        df <- dplyr::filter(
            df,
            df$"X1" != var_with_max_cor & df$"X2" != var_with_max_cor
        )
    }
    return(max_cor_df)
}

# Prediction matrix construction
build_pred_mat <- function(df, n_predictors = 1) {
    pred_mat <- matrix(
        nrow = ncol(df),
        ncol = ncol(df),
        data = 1
    )
    colnames(pred_mat) <- colnames(df)
    rownames(pred_mat) <- colnames(df)
    diag(pred_mat) <- 0
    pred_mat_vars <- top_correlating_vars(df)
    vars_to_drop <- pred_mat_vars$"variable"[seq_len(n_predictors)]
    print(paste0("Dropping: ", paste(vars_to_drop, collapse = ", ")))
    pred_mat[, vars_to_drop] <- 0
    return(pred_mat)
}

###############################################################################
# Imputation - mTBI train
###############################################################################
# Doesn't run (system is computationally singular)
imputed_mtbi <- futuremice(
    mtbi_train_df_no_subs,
    m = 5,
    maxit = 10,
    parallelseed = 42
)

mtbi_train_pred_mat <- build_pred_mat(mtbi_train_df_no_subs, 1)

# Write and recover
write.table(mtbi_train_pred_mat, proc_path("mtbi_train_pred_mat.txt", TRUE))

mtbi_train_pred_mat <- as.matrix(
    read.table(proc_path("2024_04_18_mtbi_train_pred_mat.txt"))
)
storage.mode(mtbi_train_pred_mat) <- "double"

# Runs
imputed_mtbi_train <- futuremice(
    mtbi_train_df_no_subs,
    m = 5,
    n.core = 5,
    maxit = 10,
    parallelseed = 42,
    predictorMatrix = mtbi_train_pred_mat
)

# mTBI solo imputed data
five_imputed_mtbi_train <- complete(
    imputed_mtbi_train,
    action = "long",
    include = TRUE
)

# Write and recover
write_csv(
    five_imputed_mtbi_train,
    input_path("five_imputed_mtbi_train.csv", TRUE)
)

five_imputed_mtbi_train <- read_csv(
    input_path("2024_04_18_five_imputed_mtbi_train.csv")
)

###############################################################################
# Imputation - mTBI test
###############################################################################
mtbi_test_pred_mat <- build_pred_mat(mtbi_test_df_no_subs, 9)
write.table(mtbi_test_pred_mat, proc_path("mtbi_test_pred_mat.txt", TRUE))
mtbi_test_pred_mat <- as.matrix(
    read.table(proc_path("2024_04_19_mtbi_test_pred_mat.txt"))
)
storage.mode(mtbi_test_pred_mat) <- "double"
imputed_mtbi_test <- futuremice(
    mtbi_test_df_no_subs,
    m = 5,
    n.core = 5,
    maxit = 10,
    parallelseed = 42,
    predictorMatrix = mtbi_test_pred_mat
)

# mTBI solo imputed data
five_imputed_mtbi_test <- complete(
    imputed_mtbi_test,
    action = "long",
    include = TRUE
)

# Write and recover
write_csv(
    five_imputed_mtbi_test,
    input_path("five_imputed_mtbi_test.csv", TRUE)
)

five_imputed_mtbi_test <- read_csv(
    input_path("2024_04_19_five_imputed_mtbi_test.csv")
)


###############################################################################
# Imputation - only uninjured
###############################################################################
uninj_pred_mat <- build_pred_mat(uninj_df_no_subs, 1)

# Write and recover
write.table(uninj_pred_mat, proc_path("uninj_pred_mat.txt", TRUE))

uninj_pred_mat <- as.matrix(
    read.table(proc_path("2024_04_18_uninj_pred_mat.txt"))
)
storage.mode(uninj_pred_mat) <- "double"

imputed_uninj <- futuremice(
    uninj_df_no_subs,
    m = 5,
    n.core = 5,
    maxit = 10,
    parallelseed = 42,
    predictorMatrix = uninj_pred_mat
)

# Uninjured solo imputed data
five_imputed_uninj <- complete(
    imputed_uninj,
    action = "long",
    include = TRUE
)

# Write and recover
write_csv(
    five_imputed_uninj,
    input_path("five_imputed_uninj.csv", TRUE)
)

five_imputed_uninj <- read_csv(
    input_path("2024_04_18_five_imputed_uninj.csv")
) # 68448 rows (11408 subjects * 6 imputations)

###############################################################################
# Imputation - mTBI and uninjured data stacked on top of each other
# This will only look at the variables shared between the two groups
###############################################################################
mtbi_train_df_u_vars <- mtbi_train_df_no_subs[, colnames(uninj_df_no_subs)]
pooled_df <- rbind(mtbi_train_df_u_vars, uninj_df_no_subs)
pooled_df <- char_to_fac(pooled_df)

pooled_pred_mat <- build_pred_mat(pooled_df, 1)

# Write and recover
write.table(pooled_pred_mat, proc_path("pooled_pred_mat.txt", TRUE))
pooled_pred_mat <- as.matrix(
    read.table(proc_path("2024_04_18_pooled_pred_mat.txt"))
)
storage.mode(pooled_pred_mat) <- "double"

imputed_pooled <- futuremice(
    pooled_df,
    m = 5,
    n.core = 5,
    maxit = 10,
    parallelseed = 42,
    predictorMatrix = pooled_pred_mat
)

# mTBI solo imputed data
five_imputed_pooled <- complete(
    imputed_pooled,
    action = "long",
    include = TRUE
)

# Write and recover
write_csv(five_imputed_pooled, input_path("five_imputed_pooled.csv", TRUE))
five_imputed_pooled <- read_csv(
    input_path("2024_04_18_five_imputed_pooled.csv")
)
```

Formatting the imputed data:

```{r}
five_imputed_mtbi_train$"subjectkey" <- rep(mtbi_train, 6)

five_imputed_mtbi_test$"subjectkey" <- rep(mtbi_test, 6)

five_imputed_uninj$"subjectkey" <- rep(uninj_subjects, 6)

pooled_subjects <- c(mtbi_train, uninj_subjects)
five_imputed_pooled$"subjectkey" <- rep(pooled_subjects, 6)

write_csv(
    five_imputed_mtbi_train,
    input_path("five_imputed_mtbi_train_named.csv", TRUE)
)
write_csv(
    five_imputed_mtbi_test,
    input_path("five_imputed_mtbi_test_named.csv", TRUE)
)
write_csv(
    five_imputed_uninj,
    input_path("five_imputed_uninj_named.csv", TRUE)
)
write_csv(
    five_imputed_pooled,
    input_path("five_imputed_pooled_named.csv", TRUE)
)
```

```{r}
# Write and recover
five_imputed_mtbi_train <- read_csv(
    input_path("2024_04_18_five_imputed_mtbi_train_named.csv")
)

five_imputed_mtbi_test <- read_csv(
    input_path("2024_04_19_five_imputed_mtbi_test_named.csv")
)

five_imputed_uninj <- read_csv(
    input_path("2024_04_18_five_imputed_uninj_named.csv")
)

five_imputed_pooled <- read_csv(
    input_path("2024_04_18_five_imputed_pooled_named.csv")
)

```

# mTBI subsetting

```{r}
mtbi_train_parsed_imputations <- parse_imputations(
    mtbi_train_dfs,
    five_imputed_mtbi_train,
    6
)

mtbi_test_parsed_imputations <- parse_imputations(
    mtbi_test_dfs,
    five_imputed_mtbi_test,
    6
)

uninj_parsed_imputations <- parse_imputations(
    uninj_dfs,
    five_imputed_uninj,
    6
)

pooled_parsed_imputations <- parse_imputations(
    uninj_dfs,
    five_imputed_pooled,
    6
)

pooled_parsed_imputations |> names()

mtbi_pooled_parsed_imputations <- pooled_parsed_imputations |>
    lapply(
        function(variable) {
            lapply(
                variable,
                function(imputed_df) {
                    keep_rows <- imputed_df$"subjectkey" %in% mtbi_train
                    filtered_df <- imputed_df[keep_rows, ]
                    return(filtered_df)
                }
            )
        }
    )

uninj_pooled_parsed_imps <- pooled_parsed_imputations |>
    lapply(
        function(variable) {
            lapply(
                variable,
                function(imputed_df) {
                    keep_rows <- imputed_df$"subjectkey" %in% uninj_subjects
                    filtered_df <- imputed_df[keep_rows, ]
                    return(filtered_df)
                }
            )
        }
    )

list.save(
    mtbi_train_parsed_imputations,
    input_path("mtbi_train_parsed_imputations.rds", TRUE)
)
list.save(
    mtbi_test_parsed_imputations,
    input_path("mtbi_test_parsed_imputations.rds", TRUE)
)
list.save(
    mtbi_pooled_parsed_imputations,
    input_path("mtbi_pooled_parsed_imputations.rds", TRUE)
)
list.save(
    uninj_parsed_imputations,
    input_path("uninj_parsed_imputations.rds", TRUE)
)
list.save(
    uninj_pooled_parsed_imps,
    input_path("uninj_pooled_parsed_imputations.rds", TRUE)
)
```

Re-reading:

```{r}
mtbi_train_parsed_imputations <- list.load(
    input_path("2024_04_19_mtbi_train_parsed_imputations.rds")
)
mtbi_test_parsed_imputations <- list.load(
    input_path("2024_04_19_mtbi_test_parsed_imputations.rds")
)
mtbi_pooled_parsed_imputations <- list.load(
    input_path("2024_04_19_mtbi_pooled_parsed_imputations.rds")
)
uninj_parsed_imputations <- list.load(
    input_path("2024_04_19_uninj_parsed_imputations.rds")
)
uninj_pooled_parsed_imps <- list.load(
    input_path("2024_04_19_uninj_pooled_parsed_imputations.rds")
)
```


## Constructing data_lists

We have:

* 1 original unimputed mTBI dataset
* 1 original unimputed uninjured dataset
* 5 imputed mTBI datasets
* 5 imputed uninjured datasets
* 5 imputed mTBI + uninjured datasets

For the sake of brevity, these will be referred to with the following notation:

* m = mTBI
* u = uninjured
* p = pooled
* 0 = original (unimputed)
* 1-5 = imputed dataset number

```{r}
mtbi_train_data_lists <- build_dls(mtbi_train_parsed_imputations)
mtbi_train_oom_lists <- build_ols(mtbi_train_parsed_imputations)
mtbi_test_data_lists <- build_dls(mtbi_test_parsed_imputations)
mtbi_test_oom_lists <- build_ols(mtbi_test_parsed_imputations)
mtbi_pooled_data_lists <- build_dls(mtbi_pooled_parsed_imputations)
mtbi_pooled_oom_lists <- build_ols(mtbi_pooled_parsed_imputations)
uninj_data_lists <- build_dls(uninj_parsed_imputations)
uninj_oom_lists <- build_ols(uninj_parsed_imputations)
uninj_pooled_data_lists <- build_dls(uninj_pooled_parsed_imps)
uninj_pooled_oom_lists <- build_ols(uninj_pooled_parsed_imps)

all_dls <- list(
    "mtbi_train_data_lists" = mtbi_train_data_lists,
    "mtbi_train_oom_lists" = mtbi_train_oom_lists,
    "mtbi_test_data_lists" = mtbi_test_data_lists,
    "mtbi_test_oom_lists" = mtbi_test_oom_lists,
    "mtbi_pooled_data_lists" = mtbi_pooled_data_lists,
    "mtbi_pooled_oom_lists" = mtbi_pooled_oom_lists,
    "uninj_data_lists" = uninj_data_lists,
    "uninj_oom_lists" = uninj_oom_lists,
    "uninj_pooled_data_lists" = uninj_pooled_data_lists,
    "uninj_pooled_oom_lists" = uninj_pooled_oom_lists
)

```

## Renaming the initial data

```{r}
name_changes <- c(
    "mtbi_mechanism" = "latest_mtbi_mechanism",
    "mtbi_mem_daze" = "latest_mtbi_mem_daze",
    "mtbi_loc" = "latest_mtbi_loc",
    "mtbi_age" = "latest_mtbi_age",
    "age" = "interview_age",
    "parent_thought" = "asr_scr_thought_t",
    "parent_aggressive" = "asr_scr_aggressive_t",
    "parent_antisocial" = "asr_scr_antisocial_t",
    "parent_hyperactive" = "asr_scr_hyperactive_t",
    "parent_attention" = "asr_scr_attention_t",
    "parent_anxdep" = "asr_scr_anxdep_t",
    "parent_depress" = "asr_scr_depress_t",
    "parent_withdrawn" = "asr_scr_withdrawn_t",
    "parent_avoidant" = "asr_scr_avoidant_t",
    "parent_anxdisord" = "asr_scr_anxdisord_t",
    "parent_somatic" = "asr_scr_somatic_t",
    "parent_intrusive" = "asr_scr_intrusive_t",
    "parent_perstr" = "asr_scr_perstr_t",
    "sds_sleep" = "sds_p_ss_total",
    "cbcl_somatic" = "cbcl_scr_syn_somatic_t",
    "cbcl_social" = "cbcl_scr_syn_social_t",
    "cbcl_anxdep" = "cbcl_scr_syn_anxdep_t",
    "cbcl_thought" = "cbcl_scr_syn_thought_t",
    "cbcl_attention" = "cbcl_scr_syn_attention_t",
    "cbcl_withdep" = "cbcl_scr_syn_withdep_t",
    "cbcl_aggressive" = "cbcl_scr_syn_aggressive_t",
    "cbcl_rulebreak" = "cbcl_scr_syn_rulebreak_t",
    "family_fight" = "q1_fight",
    "family_angry" = "q2_angry",
    "family_throw" = "q3_throw",
    "family_temper" = "q4_temper",
    "family_criticize" = "q5_criticize",
    "family_hit" = "q6_hit",
    "family_peaceful" = "q7_peaceful",
    "family_outdo" = "q8_outdo",
    "family_yell" = "q9_yell",
    "prosocial_considerate" = "q1",
    "prosocial_helps_hurt" = "q2",
    "prosocial_helpful" = "q3",
    "headache_history" = "headache",
    "previous_mtbis" = "mtbi_count",
    "brain_volume" = "smri_vol_scs_wholeb",
    "cortical_thickness" = "smri_thick_cdk_mean",
    "cortical_sa" = "smri_area_cdk_total",
    "major_wm_ndi" = "dmri_rsirnd_fib_allfib",
    "pericortical_wm_ndi" = "dmri_rsirndwm_cdk_mean",
    "fmri_cort_cors" = "avg_gord_cor",
    "fmri_cort_subcort_cors" = "avg_subc_cor",
    "same_sex_friend" = "ss_friend",
    "opp_sex_friend" = "os_friend",
    "same_sex_close_friend" = "ss_close_friend",
    "opp_sex_close_friend" = "os_close_friend",
    "weekend_screentime" = "screentime_wknd_hrs",
    "weekday_screentime" = "screentime_wkday_hrs",
    "school_programs" = "organized_school_activities",
    "non_school_programs" = "organized_outside_activities",
    "private_instruction" = "private_instruction_activities",
    "programs_this_year" = "p12_activities",
    "exercise_time" = "physical_activity"
)

all_dls <- all_dls |>
    lapply(
        function(data_lists_of_group) {
            lapply(
                data_lists_of_group,
                function(data_list) {
                    data_list <- rename_dl(data_list, name_changes)
                }
            )
        }
    )

list.save(all_dls, input_path("all_dls.rds", TRUE))
```

# R Session Information

This script was last run on April 19th, 2024, in the following environment:

R version 4.3.2 (2023-10-31)
Platform: x86_64-pc-linux-gnu (64-bit)
Running under: Ubuntu 22.04.4 LTS

Matrix products: default
BLAS:   /usr/lib/x86_64-linux-gnu/openblas-pthread/libblas.so.3
LAPACK: /usr/lib/x86_64-linux-gnu/openblas-pthread/libopenblasp-r0.3.20.so;  LAPACK version 3.10.0

locale:
 [1] LC_CTYPE=en_US.UTF-8       LC_NUMERIC=C
 [3] LC_TIME=en_US.UTF-8        LC_COLLATE=en_US.UTF-8
 [5] LC_MONETARY=en_US.UTF-8    LC_MESSAGES=en_US.UTF-8
 [7] LC_PAPER=en_US.UTF-8       LC_NAME=C
 [9] LC_ADDRESS=C               LC_TELEPHONE=C
[11] LC_MEASUREMENT=en_US.UTF-8 LC_IDENTIFICATION=C

time zone: America/New_York
tzcode source: system (glibc)

attached base packages:
[1] stats     graphics  grDevices utils     datasets  methods   base

other attached packages:
[1] gt_0.9.0        abcdutils_0.1.1 here_1.0.1      dplyr_1.1.4
[5] readr_2.1.5     ggplot2_3.5.0

loaded via a namespace (and not attached):
 [1] bit_4.0.5         gtable_0.3.4      compiler_4.3.2    crayon_1.5.2
 [5] tidyselect_1.2.1  xml2_1.3.4        parallel_4.3.2    scales_1.3.0
 [9] fastmap_1.1.1     R6_2.5.1          generics_0.1.3    tibble_3.2.1
[13] munsell_0.5.1     rprojroot_2.0.3   pillar_1.9.0      tzdb_0.4.0
[17] rlang_1.1.3       utf8_1.2.4        bit64_4.0.5       cli_3.6.2
[21] withr_3.0.0       magrittr_2.0.3    digest_0.6.35     grid_4.3.2
[25] vroom_1.6.5       hms_1.1.3         lifecycle_1.0.4   vctrs_0.6.5
[29] glue_1.7.0        data.table_1.15.4 fansi_1.0.6       colorspace_2.1-0
[33] purrr_1.0.2       tools_4.3.2       pkgconfig_2.0.3   htmltools_0.5.5

```{r}
writeLines(capture.output(sessionInfo()), "01_preprocessing_session_info.txt")
```
