# Imputation, QCing, and CBCL thresholding

This script is used to:

1. Assign train and test sets of the data
2. Remove neuroimaging data for participants who do not meet ABCD's QC
3. Impute missing data
4. Threshold CBCL behaviour measures (raw scores into normal (0), borderline (1), and clinical (2))

## Loading in data

```{r}
# Chunk needed for re-running
library(abcdutils)
library(here)
library(readr)
library(metasnf)
library(mice)
#library(dplyr)
#library(purrr)
#library(pheatmap)
#library(ggplot2)

# The path_maker function helps with managing and date stamping long paths. The
#  functions are just used here to help with reading and writing data. See
#  ?path_maker for more information.
input_path <- path_maker(here(paste0("data/abcd/inputs")))
raw_path <- path_maker(here(paste0("data/abcd/raw")))
core_path <- path_maker(here(paste0("data/abcd/core")))
misc_path <- path_maker(here(paste0("data/abcd/misc")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))

# Subjects
mtbi_subjects <- read_csv(sub_path("2023_11_07_mtbi_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2023_11_07_uninjured_subjects.csv"))

# mTBI data
as_mem_daze_mtbi <- read_csv(
    input_path("2023_11_07_as_mem_daze_mtbi.csv")
)
as_mechanism_mtbi <- read_csv(
    input_path("2023_11_07_as_mechanism_mtbi.csv")
)
as_loc_mtbi <- read_csv(
    input_path("2023_11_07_as_loc_mtbi.csv")
)
d_interview_age_mtbi <- read_csv(
    input_path("2023_11_07_d_interview_age_mtbi.csv")
)
d_mtbi_age_mtbi <- read_csv(
    input_path("2023_11_07_d_mtbi_age_mtbi.csv")
)
d_sex_mtbi <- read_csv(
    input_path("2023_11_07_d_sex_mtbi.csv")
)
d_income_mtbi <- read_csv(
    input_path("2023_11_07_d_income_mtbi.csv")
)
d_race_mtbi <- read_csv(
    input_path("2023_11_07_d_race_mtbi.csv")
)
d_pubertal_status_mtbi <- read_csv(
    input_path("2023_11_07_d_pubertal_status_mtbi.csv")
)
mh_headaches_mtbi <- read_csv(
    input_path("2023_11_07_mh_headaches_mtbi.csv")
)
mh_mtbi_count_mtbi <- read_csv(
    input_path("2023_11_07_mh_mtbi_count_mtbi.csv")
)
sm_subc_v_mtbi <- read_csv(
    input_path("2023_11_07_sm_subc_v_mtbi.csv")
)
sm_cort_t_mtbi <- read_csv(
    input_path("2023_11_07_sm_cort_t_mtbi.csv")
)
sm_cort_sa_mtbi <- read_csv(
    input_path("2023_11_07_sm_cort_sa_mtbi.csv")
)
dm_all_wmnd_mtbi <- read_csv(
    input_path("2023_11_07_dm_all_wmnd_mtbi.csv")
)
rm_gord_cor_mtbi <- read_csv(
    input_path("2023_11_07_rm_gord_cor_mtbi.csv")
)
rm_subc_cor_mtbi <- read_csv(
    input_path("2023_11_07_rm_subc_cor_mtbi.csv")
)
p_loneliness_mtbi <- read_csv(
    input_path("2023_11_07_p_loneliness_mtbi.csv")
)
p_screen_time_mtbi <- read_csv(
    input_path("2023_11_07_p_screen_time_mtbi.csv")
)
p_sports_mtbi <- read_csv(
    input_path("2023_11_07_p_sports_mtbi.csv")
)
p_exercise_mtbi <- read_csv(
    input_path("2023_11_07_p_exercise_mtbi.csv")
)
p_prosocial_mtbi <- read_csv(
    input_path("2023_11_07_p_prosocial_mtbi.csv")
)
p_fam_fn_mtbi <- read_csv(
    input_path("2023_11_07_p_fam_fn_mtbi.csv")
)
p_parent_psych_mtbi <- read_csv(
    input_path("2023_11_07_p_parent_psych_mtbi.csv")
)
cbcl_anxdep_mtbi <- read_csv(
    input_path("2023_11_07_cbcl_anxdep_mtbi.csv")
)
cbcl_withdep_mtbi <- read_csv(
    input_path("2023_11_07_cbcl_withdep_mtbi.csv")
)
cbcl_somatic_mtbi <- read_csv(
    input_path("2023_11_07_cbcl_somatic_mtbi.csv")
)
cbcl_social_mtbi <- read_csv(
    input_path("2023_11_07_cbcl_social_mtbi.csv")
)
cbcl_thought_mtbi <- read_csv(
    input_path("2023_11_07_cbcl_thought_mtbi.csv")
)
cbcl_attention_mtbi <- read_csv(
    input_path("2023_11_07_cbcl_attention_mtbi.csv")
)
cbcl_rulebreak_mtbi <- read_csv(
    input_path("2023_11_07_cbcl_rulebreak_mtbi.csv")
)
cbcl_aggressive_mtbi <- read_csv(
    input_path("2023_11_07_cbcl_aggressive_mtbi.csv")
)
sds_total_probs_mtbi <- read_csv(
    input_path("2023_11_07_sds_total_probs_mtbi.csv")
)

# Uninjured subjects
d_interview_age_uninj <- read_csv(
    input_path("2023_11_07_d_interview_age_uninj.csv")
)
d_sex_uninj <- read_csv(
    input_path("2023_11_07_d_sex_uninj.csv")
)
d_income_uninj <- read_csv(
    input_path("2023_11_07_d_income_uninj.csv")
)
d_race_uninj <- read_csv(
    input_path("2023_11_07_d_race_uninj.csv")
)
d_pubertal_status_uninj <- read_csv(
    input_path("2023_11_07_d_pubertal_status_uninj.csv")
)
mh_headaches_uninj <- read_csv(
    input_path("2023_11_07_mh_headaches_uninj.csv")
)
sm_subc_v_uninj <- read_csv(
    input_path("2023_11_07_sm_subc_v_uninj.csv")
)
sm_cort_t_uninj <- read_csv(
    input_path("2023_11_07_sm_cort_t_uninj.csv")
)
sm_cort_sa_uninj <- read_csv(
    input_path("2023_11_07_sm_cort_sa_uninj.csv")
)
dm_all_wmnd_uninj <- read_csv(
    input_path("2023_11_07_dm_all_wmnd_uninj.csv")
)
rm_gord_cor_uninj <- read_csv(
    input_path("2023_11_07_rm_gord_cor_uninj.csv")
)
rm_subc_cor_uninj <- read_csv(
    input_path("2023_11_07_rm_subc_cor_uninj.csv")
)
p_loneliness_uninj <- read_csv(
    input_path("2023_11_07_p_loneliness_uninj.csv")
)
p_screen_time_uninj <- read_csv(
    input_path("2023_11_07_p_screen_time_uninj.csv")
)
p_sports_uninj <- read_csv(
    input_path("2023_11_07_p_sports_uninj.csv")
)
p_exercise_uninj <- read_csv(
    input_path("2023_11_07_p_exercise_uninj.csv")
)
p_prosocial_uninj <- read_csv(
    input_path("2023_11_07_p_prosocial_uninj.csv")
)
p_fam_fn_uninj <- read_csv(
    input_path("2023_11_07_p_fam_fn_uninj.csv")
)
p_parent_psych_uninj <- read_csv(
    input_path("2023_11_07_p_parent_psych_uninj.csv")
)
cbcl_anxdep_uninj <- read_csv(
    input_path("2023_11_07_cbcl_anxdep_uninj.csv")
)
cbcl_withdep_uninj <- read_csv(
    input_path("2023_11_07_cbcl_withdep_uninj.csv")
)
cbcl_somatic_uninj <- read_csv(
    input_path("2023_11_07_cbcl_somatic_uninj.csv")
)
cbcl_social_uninj <- read_csv(
    input_path("2023_11_07_cbcl_social_uninj.csv")
)
cbcl_thought_uninj <- read_csv(
    input_path("2023_11_07_cbcl_thought_uninj.csv")
)
cbcl_attention_uninj <- read_csv(
    input_path("2023_11_07_cbcl_attention_uninj.csv")
)
cbcl_rulebreak_uninj <- read_csv(
    input_path("2023_11_07_cbcl_rulebreak_uninj.csv")
)
cbcl_aggressive_uninj <- read_csv(
    input_path("2023_11_07_cbcl_aggressive_uninj.csv")
)
sds_total_probs_uninj <- read_csv(
    input_path("2023_11_07_sds_total_probs_uninj.csv")
)
```

## Neuroimaging quality control

First identify which subjects have valid neuroimaging data.

```{r eval = FALSE}
mri_y_qc_raw_smr_t1 <- abcd_load(core_path("imaging/mri_y_qc_raw_smr_t1.csv"))
mri_y_qc_raw_smr_t2 <- abcd_load(core_path("imaging/mri_y_qc_raw_smr_t2.csv"))
mri_y_qc_raw_rsfmr <- abcd_load(core_path("imaging/mri_y_qc_raw_rsfmr.csv"))
mri_y_qc_raw_dmr <- abcd_load(core_path("imaging/mri_y_qc_raw_dmr.csv"))

# Obtaining the QC'd subjects with complete neuroimaging data

## Baseline mTBI
rm_gord_cor_qc_mtbi <- abcdutils::qc_rsfmri(
    rm_gord_cor_mtbi,
    mri_y_qc_raw_rsfmr,
    t = 0,
    no_na = TRUE
)

rm_subc_cor_qc_mtbi <- abcdutils::qc_rsfmri(
    rm_subc_cor_mtbi,
    mri_y_qc_raw_rsfmr,
    t = 0,
    no_na = TRUE
)

dm_all_wmnd_qc_mtbi <- abcdutils::qc_dmri(
    dm_all_wmnd_mtbi,
    mri_y_qc_raw_dmr,
    t = 0,
    no_na = TRUE
)

sm_cort_sa_qc_mtbi <- abcdutils::qc_smri(
    sm_cort_sa_mtbi,
    mri_y_qc_raw_smr_t1,
    mri_y_qc_raw_smr_t2,
    t = 0,
    no_na = TRUE
)

sm_cort_t_qc_mtbi <- abcdutils::qc_smri(
    sm_cort_t_mtbi,
    mri_y_qc_raw_smr_t1,
    mri_y_qc_raw_smr_t2,
    t = 0,
    no_na = TRUE
)

sm_subc_v_qc_mtbi <- abcdutils::qc_smri(
    sm_subc_v_mtbi,
    mri_y_qc_raw_smr_t1,
    mri_y_qc_raw_smr_t2,
    t = 0,
    no_na = TRUE
)

## Uninjured
rm_gord_cor_qc_uninj <- abcdutils::qc_rsfmri(
    rm_gord_cor_uninj,
    mri_y_qc_raw_rsfmr,
    t = 0,
    no_na = TRUE
)

rm_subc_cor_qc_uninj <- abcdutils::qc_rsfmri(
    rm_subc_cor_uninj,
    mri_y_qc_raw_rsfmr,
    t = 0,
    no_na = TRUE
)

dm_all_wmnd_qc_uninj <- abcdutils::qc_dmri(
    dm_all_wmnd_uninj,
    mri_y_qc_raw_dmr,
    t = 0,
    no_na = TRUE
)

sm_cort_sa_qc_uninj <- abcdutils::qc_smri(
    sm_cort_sa_uninj,
    mri_y_qc_raw_smr_t1,
    mri_y_qc_raw_smr_t2,
    t = 0,
    no_na = TRUE
)

sm_cort_t_qc_uninj <- abcdutils::qc_smri(
    sm_cort_t_uninj,
    mri_y_qc_raw_smr_t1,
    mri_y_qc_raw_smr_t2,
    t = 0,
    no_na = TRUE
)

sm_subc_v_qc_uninj <- abcdutils::qc_smri(
    sm_subc_v_uninj,
    mri_y_qc_raw_smr_t1,
    mri_y_qc_raw_smr_t2,
    t = 0,
    no_na = TRUE
)

write_csv(rm_gord_cor_qc_mtbi, input_path("rm_gord_cor_qc_mtbi.csv", TRUE))
write_csv(rm_subc_cor_qc_mtbi, input_path("rm_subc_cor_qc_mtbi.csv", TRUE))
write_csv(dm_all_wmnd_qc_mtbi, input_path("dm_all_wmnd_qc_mtbi.csv", TRUE))
write_csv(sm_cort_sa_qc_mtbi, input_path("sm_cort_sa_qc_mtbi.csv", TRUE))
write_csv(sm_cort_t_qc_mtbi, input_path("sm_cort_t_qc_mtbi.csv", TRUE))
write_csv(sm_subc_v_qc_mtbi, input_path("sm_subc_v_qc_mtbi.csv", TRUE))

write_csv(rm_gord_cor_qc_uninj, input_path("rm_gord_cor_qc_uninj.csv", TRUE))
write_csv(rm_subc_cor_qc_uninj, input_path("rm_subc_cor_qc_uninj.csv", TRUE))
write_csv(dm_all_wmnd_qc_uninj, input_path("dm_all_wmnd_qc_uninj.csv", TRUE))
write_csv(sm_cort_sa_qc_uninj, input_path("sm_cort_sa_qc_uninj.csv", TRUE))
write_csv(sm_cort_t_qc_uninj, input_path("sm_cort_t_qc_uninj.csv", TRUE))
write_csv(sm_subc_v_qc_uninj, input_path("sm_subc_v_qc_uninj.csv", TRUE))
```


```{r}
# Chunk needed for re-running
rm_gord_cor_qc_mtbi <- read_csv(
    input_path("2023_11_07_rm_gord_cor_qc_mtbi.csv")
)
rm_subc_cor_qc_mtbi <- read_csv(
    input_path("2023_11_07_rm_subc_cor_qc_mtbi.csv")
)
dm_all_wmnd_qc_mtbi <- read_csv(
    input_path("2023_11_07_dm_all_wmnd_qc_mtbi.csv")
)
sm_cort_sa_qc_mtbi <- read_csv(
    input_path("2023_11_07_sm_cort_sa_qc_mtbi.csv")
)
sm_cort_t_qc_mtbi <- read_csv(
    input_path("2023_11_07_sm_cort_t_qc_mtbi.csv")
)
sm_subc_v_qc_mtbi <- read_csv(
    input_path("2023_11_07_sm_subc_v_qc_mtbi.csv")
)
rm_gord_cor_qc_uninj <- read_csv(
    input_path("2023_11_07_rm_gord_cor_qc_uninj.csv")
)
rm_subc_cor_qc_uninj <- read_csv(
    input_path("2023_11_07_rm_subc_cor_qc_uninj.csv")
)
dm_all_wmnd_qc_uninj <- read_csv(
    input_path("2023_11_07_dm_all_wmnd_qc_uninj.csv")
)
sm_cort_sa_qc_uninj <- read_csv(
    input_path("2023_11_07_sm_cort_sa_qc_uninj.csv")
)
sm_cort_t_qc_uninj <- read_csv(
    input_path("2023_11_07_sm_cort_t_qc_uninj.csv")
)
sm_subc_v_qc_uninj <- read_csv(
    input_path("2023_11_07_sm_subc_v_qc_uninj.csv")
)
```

## Train/Test split

To avoid having training and testing data inform each other during imputation, we assign the splits prior to the imputation.

```{r}
mtbi_split <- train_test_assign(
    train_frac = 0.8,
    subjects = mtbi_subjects$"subjectkey"
)

as_mem_daze_mtbi_train <- metasnf::keep_split(
    as_mem_daze_mtbi,
    mtbi_split,
    "train"
)

as_mechanism_mtbi_train <- metasnf::keep_split(
    as_mechanism_mtbi,
    mtbi_split,
    "train"
)

as_loc_mtbi_train <- metasnf::keep_split(
    as_loc_mtbi,
    mtbi_split,
    "train"
)

d_pubertal_status_mtbi_train <- metasnf::keep_split(
    d_pubertal_status_mtbi,
    mtbi_split,
    "train"
)

d_interview_age_mtbi_train <- metasnf::keep_split(
    d_interview_age_mtbi,
    mtbi_split,
    "train"
)

d_mtbi_age_mtbi_train <- metasnf::keep_split(
    d_mtbi_age_mtbi,
    mtbi_split,
    "train"
)

d_sex_mtbi_train <- metasnf::keep_split(
    d_sex_mtbi,
    mtbi_split,
    "train"
)

d_income_mtbi_train <- metasnf::keep_split(
    d_income_mtbi,
    mtbi_split,
    "train"
)

d_race_mtbi_train <- metasnf::keep_split(
    d_race_mtbi,
    mtbi_split,
    "train"
)

mh_headaches_mtbi_train <- metasnf::keep_split(
    mh_headaches_mtbi,
    mtbi_split,
    "train"
)

mh_mtbi_count_mtbi_train <- metasnf::keep_split(
    mh_mtbi_count_mtbi,
    mtbi_split,
    "train"
)

sm_subc_v_qc_mtbi_train <- metasnf::keep_split(
    sm_subc_v_qc_mtbi,
    mtbi_split,
    "train"
)

sm_cort_t_qc_mtbi_train <- metasnf::keep_split(
    sm_cort_t_qc_mtbi,
    mtbi_split,
    "train"
)

sm_cort_sa_qc_mtbi_train <- metasnf::keep_split(
    sm_cort_sa_qc_mtbi,
    mtbi_split,
    "train"
)

dm_all_wmnd_qc_mtbi_train <- metasnf::keep_split(
    dm_all_wmnd_qc_mtbi,
    mtbi_split,
    "train"
)

rm_gord_cor_qc_mtbi_train <- metasnf::keep_split(
    rm_gord_cor_qc_mtbi,
    mtbi_split,
    "train"
)

rm_subc_cor_qc_mtbi_train <- metasnf::keep_split(
    rm_subc_cor_qc_mtbi,
    mtbi_split,
    "train"
)

p_loneliness_mtbi_train <- metasnf::keep_split(
    p_loneliness_mtbi,
    mtbi_split,
    "train"
)

p_screen_time_mtbi_train <- metasnf::keep_split(
    p_screen_time_mtbi,
    mtbi_split,
    "train"
)

p_sports_mtbi_train <- metasnf::keep_split(
    p_sports_mtbi,
    mtbi_split,
    "train"
)

p_exercise_mtbi_train <- metasnf::keep_split(
    p_exercise_mtbi,
    mtbi_split,
    "train"
)

p_prosocial_mtbi_train <- metasnf::keep_split(
    p_prosocial_mtbi,
    mtbi_split,
    "train"
)

p_fam_fn_mtbi_train <- metasnf::keep_split(
    p_fam_fn_mtbi,
    mtbi_split,
    "train"
)

p_parent_psych_mtbi_train <- metasnf::keep_split(
    p_parent_psych_mtbi,
    mtbi_split,
    "train"
)

cbcl_anxdep_mtbi_train <- metasnf::keep_split(
    cbcl_anxdep_mtbi,
    mtbi_split,
    "train"
)

cbcl_withdep_mtbi_train <- metasnf::keep_split(
    cbcl_withdep_mtbi,
    mtbi_split,
    "train"
)

cbcl_somatic_mtbi_train <- metasnf::keep_split(
    cbcl_somatic_mtbi,
    mtbi_split,
    "train"
)

cbcl_social_mtbi_train <- metasnf::keep_split(
    cbcl_social_mtbi,
    mtbi_split,
    "train"
)

cbcl_thought_mtbi_train <- metasnf::keep_split(
    cbcl_thought_mtbi,
    mtbi_split,
    "train"
)

cbcl_attention_mtbi_train <- metasnf::keep_split(
    cbcl_attention_mtbi,
    mtbi_split,
    "train"
)

cbcl_rulebreak_mtbi_train <- metasnf::keep_split(
    cbcl_rulebreak_mtbi,
    mtbi_split,
    "train"
)

cbcl_aggressive_mtbi_train <- metasnf::keep_split(
    cbcl_aggressive_mtbi,
    mtbi_split,
    "train"
)

sds_total_probs_mtbi_train <- metasnf::keep_split(
    sds_total_probs_mtbi,
    mtbi_split,
    "train"
)

# Test set - mTBI
as_mem_daze_mtbi_test <- metasnf::keep_split(
    as_mem_daze_mtbi,
    mtbi_split,
    "test"
)

as_mechanism_mtbi_test <- metasnf::keep_split(
    as_mechanism_mtbi,
    mtbi_split,
    "test"
)

as_loc_mtbi_test <- metasnf::keep_split(
    as_loc_mtbi,
    mtbi_split,
    "test"
)

d_pubertal_status_mtbi_test <- metasnf::keep_split(
    d_pubertal_status_mtbi,
    mtbi_split,
    "test"
)

d_interview_age_mtbi_test <- metasnf::keep_split(
    d_interview_age_mtbi,
    mtbi_split,
    "test"
)

d_mtbi_age_mtbi_test <- metasnf::keep_split(
    d_mtbi_age_mtbi,
    mtbi_split,
    "test"
)

d_sex_mtbi_test <- metasnf::keep_split(
    d_sex_mtbi,
    mtbi_split,
    "test"
)

d_income_mtbi_test <- metasnf::keep_split(
    d_income_mtbi,
    mtbi_split,
    "test"
)

d_race_mtbi_test <- metasnf::keep_split(
    d_race_mtbi,
    mtbi_split,
    "test"
)

mh_headaches_mtbi_test <- metasnf::keep_split(
    mh_headaches_mtbi,
    mtbi_split,
    "test"
)

mh_mtbi_count_mtbi_test <- metasnf::keep_split(
    mh_mtbi_count_mtbi,
    mtbi_split,
    "test"
)

sm_subc_v_qc_mtbi_test <- metasnf::keep_split(
    sm_subc_v_qc_mtbi,
    mtbi_split,
    "test"
)

sm_cort_t_qc_mtbi_test <- metasnf::keep_split(
    sm_cort_t_qc_mtbi,
    mtbi_split,
    "test"
)

sm_cort_sa_qc_mtbi_test <- metasnf::keep_split(
    sm_cort_sa_qc_mtbi,
    mtbi_split,
    "test"
)

dm_all_wmnd_qc_mtbi_test <- metasnf::keep_split(
    dm_all_wmnd_qc_mtbi,
    mtbi_split,
    "test"
)

rm_gord_cor_qc_mtbi_test <- metasnf::keep_split(
    rm_gord_cor_qc_mtbi,
    mtbi_split,
    "test"
)

rm_subc_cor_qc_mtbi_test <- metasnf::keep_split(
    rm_subc_cor_qc_mtbi,
    mtbi_split,
    "test"
)

p_loneliness_mtbi_test <- metasnf::keep_split(
    p_loneliness_mtbi,
    mtbi_split,
    "test"
)

p_screen_time_mtbi_test <- metasnf::keep_split(
    p_screen_time_mtbi,
    mtbi_split,
    "test"
)

p_sports_mtbi_test <- metasnf::keep_split(
    p_sports_mtbi,
    mtbi_split,
    "test"
)

p_exercise_mtbi_test <- metasnf::keep_split(
    p_exercise_mtbi,
    mtbi_split,
    "test"
)

p_prosocial_mtbi_test <- metasnf::keep_split(
    p_prosocial_mtbi,
    mtbi_split,
    "test"
)

p_fam_fn_mtbi_test <- metasnf::keep_split(
    p_fam_fn_mtbi,
    mtbi_split,
    "test"
)

p_parent_psych_mtbi_test <- metasnf::keep_split(
    p_parent_psych_mtbi,
    mtbi_split,
    "test"
)

cbcl_anxdep_mtbi_test <- metasnf::keep_split(
    cbcl_anxdep_mtbi,
    mtbi_split,
    "test"
)

cbcl_withdep_mtbi_test <- metasnf::keep_split(
    cbcl_withdep_mtbi,
    mtbi_split,
    "test"
)

cbcl_somatic_mtbi_test <- metasnf::keep_split(
    cbcl_somatic_mtbi,
    mtbi_split,
    "test"
)

cbcl_social_mtbi_test <- metasnf::keep_split(
    cbcl_social_mtbi,
    mtbi_split,
    "test"
)

cbcl_thought_mtbi_test <- metasnf::keep_split(
    cbcl_thought_mtbi,
    mtbi_split,
    "test"
)

cbcl_attention_mtbi_test <- metasnf::keep_split(
    cbcl_attention_mtbi,
    mtbi_split,
    "test"
)

cbcl_rulebreak_mtbi_test <- metasnf::keep_split(
    cbcl_rulebreak_mtbi,
    mtbi_split,
    "test"
)

cbcl_aggressive_mtbi_test <- metasnf::keep_split(
    cbcl_aggressive_mtbi,
    mtbi_split,
    "test"
)

sds_total_probs_mtbi_test <- metasnf::keep_split(
    sds_total_probs_mtbi,
    mtbi_split,
    "test"
)

```

# Imputation

Data will be imputed under the following schemes:
- 5 imputations of mTBI data alone
- 5 imputations of uninjured data alone
- 5 imputations of mTBI + uninjured data together

Resulting in 10 versions of the mTBI data and 10 versions of the uninjured data.

# Imputing missing data

SNF requires complete data as input for integration.

We face a few oddities that may impact the validity of using a multiple imputation approach:

Neuroimaging data, which accounts for the majority of the individual features, are either completely removed or completely present for most subjects.
We proceed by not including those subjects who are missing neuroimaging data or who have neuroimaging data that did not pass checks for quality control.

Though this work is an exploratory clustering analysis that is designed to reveal insights about patterns across all variables, the experimental design used focuses on those insights particular relevant to better understanding behavioural impairments following concussion.
Our post-concussion assessments of behavioural impairment come from the CBCL and SDS.
CBCL data, which comprises a wide set of features, is either completely missing or completely present.

```{r}

mtbi_train_df <- list(
    "as_mem_daze_mtbi" = as_mem_daze_mtbi_train,
    "as_mechanism_mtbi" = as_mechanism_mtbi_train,
    "as_loc_mtbi" = as_loc_mtbi_train,
    "d_interview_age_mtbi" = d_interview_age_mtbi_train,
    "d_mtbi_age_mtbi" = d_mtbi_age_mtbi_train,
    "d_sex_mtbi" = d_sex_mtbi_train,
    "d_income_mtbi" = d_income_mtbi_train,
    "d_race_mtbi" = d_race_mtbi_train,
    "d_pubertal_status_mtbi" = d_pubertal_status_mtbi_train,
    "mh_headaches_mtbi" = mh_headaches_mtbi_train,
    "mh_mtbi_count_mtbi" = mh_mtbi_count_mtbi_train,
    "sm_subc_v_qc_mtbi" = sm_subc_v_qc_mtbi_train,
    "sm_cort_t_qc_mtbi" = sm_cort_t_qc_mtbi_train,
    "sm_cort_sa_qc_mtbi" = sm_cort_sa_qc_mtbi_train,
    "dm_all_wmnd_qc_mtbi" = dm_all_wmnd_qc_mtbi_train,
    "rm_gord_cor_qc_mtbi" = rm_gord_cor_qc_mtbi_train,
    "rm_subc_cor_qc_mtbi" = rm_subc_cor_qc_mtbi_train,
    "p_loneliness_mtbi" = p_loneliness_mtbi_train,
    "p_screen_time_mtbi" = p_screen_time_mtbi_train,
    "p_sports_mtbi" = p_sports_mtbi_train,
    "p_exercise_mtbi" = p_exercise_mtbi_train,
    "p_prosocial_mtbi" = p_prosocial_mtbi_train,
    "p_fam_fn_mtbi" = p_fam_fn_mtbi_train,
    "p_parent_psych_mtbi" = p_parent_psych_mtbi_train,
    "cbcl_anxdep_mtbi" = cbcl_anxdep_mtbi_train,
    "cbcl_withdep_mtbi" = cbcl_withdep_mtbi_train,
    "cbcl_somatic_mtbi" = cbcl_somatic_mtbi_train,
    "cbcl_social_mtbi" = cbcl_social_mtbi_train,
    "cbcl_thought_mtbi" = cbcl_thought_mtbi_train,
    "cbcl_attention_mtbi" = cbcl_attention_mtbi_train,
    "cbcl_rulebreak_mtbi" = cbcl_rulebreak_mtbi_train,
    "cbcl_aggressive_mtbi" = cbcl_aggressive_mtbi_train,
    "sds_total_probs_mtbi" = sds_total_probs_mtbi_train
) |>
    abcdutils::merge_df_list(join = "full")

uninj_df <- list(
    "d_pubertal_status_uninj" = d_pubertal_status_uninj,
    "d_interview_age_uninj" = d_interview_age_uninj,
    "d_sex_uninj" = d_sex_uninj,
    "d_income_uninj" = d_income_uninj,
    "d_race_uninj" = d_race_uninj,
    "mh_headaches_uninj" = mh_headaches_uninj,
    "sm_subc_v_qc_uninj" = sm_subc_v_qc_uninj,
    "sm_cort_t_qc_uninj" = sm_cort_t_qc_uninj,
    "sm_cort_sa_qc_uninj" = sm_cort_sa_qc_uninj,
    "dm_all_wmnd_qc_uninj" = dm_all_wmnd_qc_uninj,
    "rm_gord_cor_qc_uninj" = rm_gord_cor_qc_uninj,
    "rm_subc_cor_qc_uninj" = rm_subc_cor_qc_uninj,
    "p_loneliness_uninj" = p_loneliness_uninj,
    "p_screen_time_uninj" = p_screen_time_uninj,
    "p_sports_uninj" = p_sports_uninj,
    "p_exercise_uninj" = p_exercise_uninj,
    "p_prosocial_uninj" = p_prosocial_uninj,
    "p_fam_fn_uninj" = p_fam_fn_uninj,
    "p_parent_psych_uninj" = p_parent_psych_uninj,
    "cbcl_anxdep_uninj" = cbcl_anxdep_uninj,
    "cbcl_withdep_uninj" = cbcl_withdep_uninj,
    "cbcl_somatic_uninj" = cbcl_somatic_uninj,
    "cbcl_social_uninj" = cbcl_social_uninj,
    "cbcl_thought_uninj" = cbcl_thought_uninj,
    "cbcl_attention_uninj" = cbcl_attention_uninj,
    "cbcl_rulebreak_uninj" = cbcl_rulebreak_uninj,
    "cbcl_aggressive_uninj" = cbcl_aggressive_uninj,
    "sds_total_probs_uninj" = sds_total_probs_uninj
) |>
    abcdutils::merge_df_list(join = "full")

```

Adjusting variables to numeric format

```{r}

classes <- sapply(mtbi_df, class) |> as.vector()
mtbi_df[, classes == "character"]

mtbi_train_df_numeric <- mtbi_train_df |>
    dplyr::mutate(
        sex = dplyr::case_when(
            sex == "F" ~ 0,
            sex == "M" ~ 1
        ),
        race = dplyr::case_when(
            race == "white" ~ 0,
            race == "mixed_or_other" ~ 1,
            race == "black" ~ 1
        )
    ) |> abcdutils::char_to_fac()

uninj_df_numeric <- uninj_df |>
    dplyr::mutate(
        sex = dplyr::case_when(
            sex == "F" ~ 0,
            sex == "M" ~ 1
        ),
        race = dplyr::case_when(
            race == "white" ~ 0,
            race == "mixed_or_other" ~ 1,
            race == "black" ~ 1
        )
    ) |> abcdutils::char_to_fac()

```

## Checking for excessive collinearity

```{r}
# Restrict to only shared variables
mtbi_train_reduced <- mtbi_train_df_numeric[, colnames(uninj_df_numeric)]

mtbi_train_dl <- generate_data_list(
    list(mtbi_train_reduced, "mtbi", "mtbi", "mixed")
)

uninj_dl <- generate_data_list(
    list(uninj_df_numeric, "uninj", "uninj", "mixed")
)

keep_numeric <- function(df) {
    df <- numcol_to_numeric(df)
    classes <- as.vector(sapply(df, class))
    df <- df[, classes == "numeric", drop = FALSE]
    return(df)
}

correlation_heatmap <- function(data_list, order = NULL) {
    dl_df <- collapse_dl(data_list)
    numeric_dl_df <- keep_numeric(dl_df)
    correlation_matrix <- cor(numeric_dl_df)
    if (is.null(order)) {
        heatmap <- ComplexHeatmap::Heatmap(correlation_matrix)
    } else {
        heatmap <- ComplexHeatmap::Heatmap(
            correlation_matrix[order, order],
            cluster_rows = FALSE,
            cluster_columns = FALSE
        )
    }
    drawn_heatmap <- ComplexHeatmap::draw(heatmap)
    order <- ComplexHeatmap::row_order(drawn_heatmap)
    results <- list(
        "correlation_matrix" = correlation_matrix,
        "heatmap" = heatmap,
        "order" = order
    )
    return(results)
}

# First pass to extract the order of columns
mtbi_correlation_data_initial <- correlation_heatmap(
    mtbi_train_dl
)

mtbi_order <- mtbi_correlation_data_initial$"order"

mtbi_correlation_data <- correlation_heatmap(
    mtbi_train_dl,
    order = mtbi_order
)

uninj_correlation_data <- correlation_heatmap(
    uninj_dl,
    order = mtbi_order
)

mtbi_correlation_matrix <- mtbi_correlation_data$"correlation_matrix"
mtbi_correlation_heatmap <- mtbi_correlation_data$"heatmap"
uninj_correlation_matrix <- uninj_correlation_data$"correlation_matrix"
uninj_correlation_heatmap <- uninj_correlation_data$"heatmap"

png(
    fig_path("uninjured_correlations.png", TRUE),
    width = 250,
    height = 220,
    units = "mm",
    res = 300
)
uninj_correlation_heatmap
dev.off()

png(
    fig_path("mtbi_correlations.png", TRUE),
    width = 250,
    height = 220,
    units = "mm",
    res = 300
)
mtbi_correlation_heatmap
dev.off()

diff_matrix <- uninj_correlation_matrix - mtbi_correlation_matrix

png(
    fig_path("difference_in_correlations.png", TRUE),
    width = 250,
    height = 220,
    units = "mm",
    res = 300
)
ComplexHeatmap::Heatmap(
    diff_matrix,
    cluster_rows = FALSE,
    cluster_columns = FALSE
)
dev.off()


abs_diff_matrix <- abs(diff_matrix)
col_fun <- circlize::colorRamp2(c(0, max(abs_diff_matrix)), c("white", "purple"))


png(
    fig_path("abs_difference_in_correlations.png", TRUE),
    width = 250,
    height = 220,
    units = "mm",
    res = 300
)
ComplexHeatmap::Heatmap(
    abs_diff_matrix,
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    col = col_fun
)
dev.off()

```

## Imputing missing data

Generating three different sets of 5:

- Imputing mTBI alone (5 datasets)
- Imputing uninjured alone (5 datasets)
- Imputing mTBI and uninjured together (5 datasets)

```{r eval = FALSE}

missing_colnames_mtbi <- names(which(colSums(is.na(mtbi_train_df_numeric)) > 0))
missing_colnames_mtbi

missing_colnames_uninj <- names(which(colSums(is.na(uninj_df_numeric)) > 0))
missing_colnames_uninj

# Remove the subjectkey variable
mtbi_df_no_subs <- mtbi_train_df_numeric |>
    dplyr::select(-"subjectkey") |>
    data.frame()

uninj_df_no_subs <- uninj_df_numeric |>
    dplyr::select(-"subjectkey") |>
    data.frame()

###############################################################################
# Functions to check the biggest correlations
big_correlations <- function(df, threshold = 0) {
    df <- na.omit(df)
    correlations <- cor(df)
    diag(correlations) <- 0
    abs_cor <- abs(correlations)
    pairs <- t(combn(colnames(abs_cor), 2))
    paired_cors <- data.frame(pairs, cor = abs_cor[pairs])
    paired_cors <- paired_cors[paired_cors$"cor" > threshold, ]
    return(paired_cors)
}

predictor_candidates <- function(df, threshold = 0) {
    df <- big_correlations(df, threshold)
    variables <- c(df$"X1", df$"X2") |> unique()
    max_cor_df <- data.frame(
        variable = as.character(),
        max_cor = as.numeric()
    )
    i <- 0
    while (nrow(df) > 0) {
        i <- i + 1
        print(i)
        row_with_max_cor <- which(df$"cor" == max(df$"cor"))[1]
        var_with_max_cor <- df[row_with_max_cor, "X1"]
        max_cor <- df[row_with_max_cor, "cor"]
        max_cor_df <- rbind(
            max_cor_df,
            data.frame(
                variable = var_with_max_cor,
                max_cor = max_cor
            )
        )
        df <- df |>
            dplyr::filter(X1 != var_with_max_cor & X2 != var_with_max_cor)
    }
    return(max_cor_df)
}
###############################################################################
# Imputation - only mTBI
###############################################################################
# Doesn't run
imputed_mtbi <- mice(
    mtbi_df_no_subs,
    m = 5,
    maxit = 10,
    seed = 42
)

# Prediction matrix construction
mtbi_predmat <- matrix(nrow = ncol(mtbi_df_no_subs), ncol = ncol(mtbi_df_no_subs), 1)
colnames(mtbi_predmat) <- colnames(mtbi_df_no_subs)
rownames(mtbi_predmat) <- colnames(mtbi_df_no_subs)
diag(mtbi_predmat) <- 0
pred_mat_vars <- predictor_candidates(mtbi_df_no_subs[, -2])
mtbi_predmat[, pred_mat_vars$"variable"[1]] <- 0
ComplexHeatmap::Heatmap(
    mtbi_predmat,
    cluster_rows = FALSE,
    cluster_columns = FALSE
)

# Write and recover
write.table(mtbi_predmat, proc_path("mtbi_predmat.txt", TRUE))
mtbi_predmat <- as.matrix(read.table(proc_path("2023_11_29_mtbi_predmat.txt")))
storage.mode(mtbi_predmat) <- "double"

# Runs
imputed_mtbi <- mice(
    mtbi_df_no_subs,
    m = 5,
    maxit = 10,
    seed = 42,
    predictorMatrix = mtbi_predmat
)

# mTBI solo imputed data
five_imputed_mtbi_train <- complete(
    imputed_mtbi,
    action = "long",
    include = TRUE
)

# Write and recover
write_csv(
    five_imputed_mtbi_train,
    input_path("five_imputed_mtbi_train.csv", TRUE)
)
five_imputed_mtbi_train <- read_csv(
    input_path("2023_11_29_five_imputed_mtbi_train.csv")
)

###############################################################################
# Imputation - only uninjured
###############################################################################

# Doesn't run
imputed_uninj <- mice(
    uninj_df_no_subs,
    m = 5,
    maxit = 10,
    seed = 42
)

# Prediction matrix construction
uninj_predmat <- matrix(nrow = ncol(uninj_df_no_subs), ncol = ncol(uninj_df_no_subs), 1)
colnames(uninj_predmat) <- colnames(uninj_df_no_subs)
rownames(uninj_predmat) <- colnames(uninj_df_no_subs)
diag(uninj_predmat) <- 0
pred_mat_vars <- predictor_candidates(uninj_df_no_subs[, -2])
uninj_predmat[, pred_mat_vars$"variable"[1]] <- 0
ComplexHeatmap::Heatmap(
    uninj_predmat,
    cluster_rows = FALSE,
    cluster_columns = FALSE
)

# Write and recover
write.table(uninj_predmat, proc_path("uninj_predmat.txt", TRUE))
uninj_predmat <- as.matrix(read.table(proc_path("2023_11_29_uninj_predmat.txt")))
storage.mode(uninj_predmat) <- "double"


# Runs
imputed_uninj <- mice(
    uninj_df_no_subs,
    m = 5,
    maxit = 10,
    seed = 42,
    predictorMatrix = uninj_predmat
)


# Uninjured solo imputed data
five_imputed_uninj <- complete(
    imputed_uninj,
    action = "long",
    include = TRUE
)

# Write and recover
write_csv(
    five_imputed_uninj,
    input_path("five_imputed_uninj.csv", TRUE)
)
five_imputed_uninj <- read_csv(
    input_path("2023_11_29_five_imputed_uninj.csv")
)

###############################################################################
# Imputation - mTBI and uninjured data stacked on top of each other
# This will only look at the variables shared between the two groups
###############################################################################

mtbi_df_no_subs_limited_vars <- mtbi_df_no_subs[, colnames(uninj_df_no_subs)]

colnames(uninj_df_no_subs)

pooled_df <- rbind(mtbi_df_no_subs_limited_vars, uninj_df_no_subs)

# Doesn't run
imputed_pooled <- mice(
    pooled_df,
    m = 5,
    maxit = 10,
    seed = 42
)

# Prediction matrix construction
pooled_predmat <- matrix(nrow = ncol(pooled_df), ncol = ncol(pooled_df), 1)
colnames(pooled_predmat) <- colnames(pooled_df)
rownames(pooled_predmat) <- colnames(pooled_df)
diag(pooled_predmat) <- 0
pred_mat_vars <- predictor_candidates(pooled_df)
pooled_predmat[, pred_mat_vars$"variable"[1]] <- 0
ComplexHeatmap::Heatmap(
    pooled_predmat,
    cluster_rows = FALSE,
    cluster_columns = FALSE
)

# Write and recover
write.table(pooled_predmat, proc_path("pooled_predmat.txt", TRUE))
pooled_predmat <- as.matrix(read.table(proc_path("2023_11_29_pooled_predmat.txt")))
storage.mode(pooled_predmat) <- "double"

# Runs
imputed_pooled <- mice(
    pooled_df,
    m = 5,
    maxit = 10,
    seed = 42,
    predictorMatrix = pooled_predmat
)

# mTBI solo imputed data
five_imputed_pooled <- complete(
    imputed_pooled,
    action = "long",
    include = TRUE
)

# Write and recover
write_csv(
    five_imputed_pooled,
    input_path("five_imputed_pooled.csv", TRUE)
)
five_imputed_pooled <- read_csv(
    input_path("2023_11_29_five_imputed_pooled.csv")
)
```


Formatting the imputed data:


```{r}

five_imputed_mtbi_train$"subjectkey" <- rep(
    mtbi_train_df_numeric$"subjectkey",
    6
)

five_imputed_uninj$"subjectkey" <- rep(
    uninj_df_numeric$"subjectkey",
    6
)

pooled_subjects <- c(
    mtbi_train_df_numeric$"subjectkey",
    uninj_df_numeric$"subjectkey"
)

five_imputed_pooled$"subjectkey" <- rep(
    pooled_subjects,
    6
)

write_csv(
    five_imputed_mtbi_train,
    input_path("five_imputed_mtbi_train_named.csv", TRUE)
)
write_csv(
    five_imputed_uninj,
    input_path("five_imputed_uninj_named.csv", TRUE)
)
write_csv(
    five_imputed_pooled,
    input_path("five_imputed_pooled_named.csv", TRUE)
)
```

```{r}
# Write and recover
five_imputed_mtbi_train <- read_csv(
    input_path("2023_11_29_five_imputed_mtbi_train_named.csv")
)

# Write and recover
five_imputed_uninj <- read_csv(
    input_path("2023_11_29_five_imputed_uninj_named.csv")
)

five_imputed_pooled <- read_csv(
    input_path("2023_11_29_five_imputed_pooled_named.csv")
)
```

```{r}

pull_imputed_vars <- function(original_df, imputed_df, partition = NULL) {
    if (!is.null(partition)) {
        original_rows <- nrow(original_df)
        start <- original_rows * partition + 1
        end <- original_rows * (partition + 1)
        partitioned_df <- imputed_df[start:end, colnames(original_df)]
        return(partitioned_df)
    } else {
        df <- imputed_df[, colnames(original_df)]
        return(df)
    }
}

as_mem_daze_mtbi_train_imp_0 <- pull_imputed_vars(as_mem_daze_mtbi_train, five_imputed_mtbi_train, 0)
as_mem_daze_mtbi_train_imp_1 <- pull_imputed_vars(as_mem_daze_mtbi_train, five_imputed_mtbi_train, 1)
as_mem_daze_mtbi_train_imp_2 <- pull_imputed_vars(as_mem_daze_mtbi_train, five_imputed_mtbi_train, 2)
as_mem_daze_mtbi_train_imp_3 <- pull_imputed_vars(as_mem_daze_mtbi_train, five_imputed_mtbi_train, 3)
as_mem_daze_mtbi_train_imp_4 <- pull_imputed_vars(as_mem_daze_mtbi_train, five_imputed_mtbi_train, 4)
as_mem_daze_mtbi_train_imp_5 <- pull_imputed_vars(as_mem_daze_mtbi_train, five_imputed_mtbi_train, 5)

# HERE I AM!!!!!



as_mem_daze_mtbi_imp <- five_imputed_mtbi_train[, colnames(as_mem_daze_mtbi)]

as_mechanism_mtbi
as_loc_mtbi
d_interview_age_mtbi
d_mtbi_age_mtbi
d_sex_mtbi
d_income_mtbi
d_race_mtbi
d_pubertal_status_mtbi
mh_headaches_mtbi
mh_mtbi_count_mtbi
sm_subc_v_mtbi
sm_cort_t_mtbi
sm_cort_sa_mtbi
dm_all_wmnd_mtbi
rm_gord_cor_mtbi
rm_subc_cor_mtbi
p_loneliness_mtbi
p_screen_time_mtbi
p_sports_mtbi
p_exercise_mtbi
p_prosocial_mtbi
p_fam_fn_mtbi
p_parent_psych_mtbi
cbcl_anxdep_mtbi
cbcl_withdep_mtbi
cbcl_somatic_mtbi
cbcl_social_mtbi
cbcl_thought_mtbi
cbcl_attention_mtbi
cbcl_rulebreak_mtbi
cbcl_aggressive_mtbi
sds_total_probs_mtbi




```

```{r}
# The features that were missing data
missing_data_colnames

as_mtbi_mem_daze_imp_mtbi <- complete_imputed_mtbi |>
    dplyr::select("subjectkey", "latest_mtbi_mem_daze")
d_income_imp_mtbi <- complete_imputed_mtbi |>
    dplyr::select("subjectkey", "household_income")
d_pubertal_status_imp_mtbi <- complete_imputed_mtbi |>
    dplyr::select("subjectkey", "pubertal_status")
d_race_imp_mtbi <- complete_imputed_mtbi |>
    dplyr::select("subjectkey", "race")
p_screen_time_imp_mtbi <- complete_imputed_mtbi |>
    dplyr::select("subjectkey", dplyr::contains("screentime"))
p_exercise_imp_mtbi <- complete_imputed_mtbi |>
    dplyr::select("subjectkey", "physical_activity")
nihtbx_list_fc_imp_mtbi <- complete_imputed_mtbi |>
    dplyr::select("subjectkey", "nihtbx_list_fc")
nihtbx_pattern_fc_imp_mtbi <- complete_imputed_mtbi |>
    dplyr::select("subjectkey", "nihtbx_pattern_fc")
nihtbx_cardsort_fc_imp_mtbi <- complete_imputed_mtbi |>
    dplyr::select("subjectkey", "nihtbx_cardsort_fc")

# Features that had no NAs to begin with
as_mtbi_loc_imp_mtbi <- as_mtbi_loc_mtbi
as_mtbi_mechanism_imp_mtbi <- as_mtbi_mechanism_mtbi
d_interview_age_imp_mtbi <- d_interview_age_mtbi
d_mtbi_age_imp_mtbi <- d_mtbi_age_mtbi
d_sex_imp_mtbi <- d_sex_mtbi
mh_headaches_imp_mtbi <- mh_headaches_mtbi
mh_mtbi_count_imp_mtbi <- mh_mtbi_count_mtbi
p_loneliness_imp_mtbi <- p_loneliness_mtbi
p_fam_fn_imp_mtbi <- p_fam_fn_mtbi
p_sports_imp_mtbi <- p_sports_mtbi
p_prosocial_imp_mtbi <- p_prosocial_mtbi
p_parent_psych_imp_mtbi <- p_parent_psych_mtbi
cbcl_headaches_imp_mtbi <- cbcl_headaches_mtbi
cbcl_nausea_imp_mtbi <- cbcl_nausea_mtbi
cbcl_vomiting_imp_mtbi <- cbcl_vomiting_mtbi
cbcl_dizzy_imp_mtbi <- cbcl_dizzy_mtbi
cbcl_overtired_imp_mtbi <- cbcl_overtired_mtbi
cbcl_sleeping_more_imp_mtbi <- cbcl_sleeping_more_mtbi
cbcl_sleeping_less_imp_mtbi <- cbcl_sleeping_less_mtbi
cbcl_depress_r_imp_mtbi <- cbcl_depress_r_mtbi
cbcl_anxiety_r_imp_mtbi <- cbcl_anxiety_r_mtbi
cbcl_attention_r_imp_mtbi <- cbcl_attention_r_mtbi
cbcl_aggressive_r_imp_mtbi <- cbcl_aggressive_r_mtbi
sds_sleep_imp_mtbi <- sds_sleep_mtbi

# Export imputed results
write_csv(as_mtbi_loc_imp_mtbi,
    input_path("as_mtbi_loc_imp_mtbi.csv", date = TRUE))
write_csv(as_mtbi_mechanism_imp_mtbi,
    input_path("as_mtbi_mechanism_imp_mtbi.csv", date = TRUE))
write_csv(as_mtbi_mem_daze_imp_mtbi,
    input_path("as_mtbi_mem_daze_imp_mtbi.csv", date = TRUE))
write_csv(d_income_imp_mtbi,
    input_path("d_income_imp_mtbi.csv", date = TRUE))
write_csv(d_interview_age_imp_mtbi,
    input_path("d_interview_age_imp_mtbi.csv", date = TRUE))
write_csv(d_mtbi_age_imp_mtbi,
    input_path("d_mtbi_age_imp_mtbi.csv", date = TRUE))
write_csv(d_pubertal_status_imp_mtbi,
    input_path("d_pubertal_status_imp_mtbi.csv", date = TRUE))
write_csv(d_race_imp_mtbi,
    input_path("d_race_imp_mtbi.csv", date = TRUE))
write_csv(d_sex_imp_mtbi,
    input_path("d_sex_imp_mtbi.csv", date = TRUE))
write_csv(mh_headaches_imp_mtbi,
    input_path("mh_headaches_imp_mtbi.csv", date = TRUE))
write_csv(mh_mtbi_count_imp_mtbi,
    input_path("mh_mtbi_count_imp_mtbi.csv", date = TRUE))
write_csv(p_loneliness_imp_mtbi,
    input_path("p_loneliness_imp_mtbi.csv", date = TRUE))
write_csv(p_screen_time_imp_mtbi,
    input_path("p_screen_time_imp_mtbi.csv", date = TRUE))
write_csv(p_fam_fn_imp_mtbi,
    input_path("p_fam_fn_imp_mtbi.csv", date = TRUE))
write_csv(p_sports_imp_mtbi,
    input_path("p_sports_imp_mtbi.csv", date = TRUE))
write_csv(p_prosocial_imp_mtbi,
    input_path("p_prosocial_imp_mtbi.csv", date = TRUE))
write_csv(p_parent_psych_imp_mtbi,
    input_path("p_parent_psych_imp_mtbi.csv", date = TRUE))
write_csv(p_exercise_imp_mtbi,
    input_path("p_exercise_imp_mtbi.csv", date = TRUE))
write_csv(cbcl_headaches_imp_mtbi,
    input_path("cbcl_headaches_imp_mtbi.csv", date = TRUE))
write_csv(cbcl_nausea_imp_mtbi,
    input_path("cbcl_nausea_imp_mtbi.csv", date = TRUE))
write_csv(cbcl_vomiting_imp_mtbi,
    input_path("cbcl_vomiting_imp_mtbi.csv", date = TRUE))
write_csv(cbcl_dizzy_imp_mtbi,
    input_path("cbcl_dizzy_imp_mtbi.csv", date = TRUE))
write_csv(cbcl_overtired_imp_mtbi,
    input_path("cbcl_overtired_imp_mtbi.csv", date = TRUE))
write_csv(cbcl_sleeping_more_imp_mtbi,
    input_path("cbcl_sleeping_more_imp_mtbi.csv", date = TRUE))
write_csv(cbcl_sleeping_less_imp_mtbi,
    input_path("cbcl_sleeping_less_imp_mtbi.csv", date = TRUE))
write_csv(cbcl_depress_r_imp_mtbi,
    input_path("cbcl_depress_r_imp_mtbi.csv", date = TRUE))
write_csv(cbcl_anxiety_r_imp_mtbi,
    input_path("cbcl_anxiety_r_imp_mtbi.csv", date = TRUE))
write_csv(cbcl_attention_r_imp_mtbi,
    input_path("cbcl_attention_r_imp_mtbi.csv", date = TRUE))
write_csv(cbcl_aggressive_r_imp_mtbi,
    input_path("cbcl_aggressive_r_imp_mtbi.csv", date = TRUE))
write_csv(sds_sleep_imp_mtbi,
    input_path("sds_sleep_imp_mtbi.csv", date = TRUE))
write_csv(nihtbx_list_fc_imp_mtbi,
    input_path("nihtbx_list_fc_imp_mtbi.csv", date = TRUE))
write_csv(nihtbx_pattern_fc_imp_mtbi,
    input_path("nihtbx_pattern_fc_imp_mtbi.csv", date = TRUE))
write_csv(nihtbx_cardsort_fc_imp_mtbi,
    input_path("nihtbx_cardsort_fc_imp_mtbi.csv", date = TRUE))
```

## Convert the raw CBCL scores into thresholded ones

```{r}
cbcl_depress_r_imp_mtbi <-
    read_csv(input_path("2023_07_17_cbcl_depress_r_imp_mtbi.csv"))
cbcl_anxiety_r_imp_mtbi <-
    read_csv(input_path("2023_07_17_cbcl_anxiety_r_imp_mtbi.csv"))
cbcl_attention_r_imp_mtbi <-
    read_csv(input_path("2023_07_17_cbcl_attention_r_imp_mtbi.csv"))
cbcl_aggressive_r_imp_mtbi <-
    read_csv(input_path("2023_07_17_cbcl_aggressive_r_imp_mtbi.csv"))

cbcl_depress_imp_mtbi <-
    abcdutils::cbcl_raw_to_thresh(cbcl_depress_r_imp_mtbi)
cbcl_anxiety_imp_mtbi <-
    abcdutils::cbcl_raw_to_thresh(cbcl_anxiety_r_imp_mtbi)
cbcl_attention_imp_mtbi <-
    abcdutils::cbcl_raw_to_thresh(cbcl_attention_r_imp_mtbi)
cbcl_aggressive_imp_mtbi <-
    abcdutils::cbcl_raw_to_thresh(cbcl_aggressive_r_imp_mtbi)

write_csv(cbcl_depress_imp_mtbi,
    input_path("cbcl_depress_imp_mtbi.csv", date = TRUE))
write_csv(cbcl_anxiety_imp_mtbi,
    input_path("cbcl_anxiety_imp_mtbi.csv", date = TRUE))
write_csv(cbcl_attention_imp_mtbi,
    input_path("cbcl_attention_imp_mtbi.csv", date = TRUE))
write_csv(cbcl_aggressive_imp_mtbi,
    input_path("cbcl_aggressive_imp_mtbi.csv", date = TRUE))
```


## Training and testing data splits

```{r eval = FALSE}
library(abcdutils)
library(readr)
library(here)

# Functions to import data from carbon
input_path <- abcdutils::path_maker(here(paste0("data/abcd/inputs")))
proc_path <- abcdutils::path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- abcdutils::path_maker(here(paste0("data/abcd/results/figures")))

# Importing data
as_mtbi_loc_mtbi <-
    read_csv(input_path("2023_07_17_as_mtbi_loc_imp_mtbi.csv"))
as_mtbi_mechanism_mtbi <-
    read_csv(input_path("2023_07_17_as_mtbi_mechanism_imp_mtbi.csv"))
as_mtbi_mem_daze_mtbi <-
    read_csv(input_path("2023_07_17_as_mtbi_mem_daze_imp_mtbi.csv"))
d_income_mtbi <-
    read_csv(input_path("2023_07_17_d_income_imp_mtbi.csv"))
d_interview_age_mtbi <-
    read_csv(input_path("2023_07_17_d_interview_age_imp_mtbi.csv"))
d_mtbi_age_mtbi <-
    read_csv(input_path("2023_07_17_d_mtbi_age_imp_mtbi.csv"))
d_pubertal_status_mtbi <-
    read_csv(input_path("2023_07_17_d_pubertal_status_imp_mtbi.csv"))
d_race_mtbi <-
    read_csv(input_path("2023_07_17_d_race_imp_mtbi.csv"))
d_sex_mtbi <-
    read_csv(input_path("2023_07_17_d_sex_imp_mtbi.csv"))
mh_headaches_mtbi <-
    read_csv(input_path("2023_07_17_mh_headaches_imp_mtbi.csv"))
mh_mtbi_count_mtbi <-
    read_csv(input_path("2023_07_17_mh_mtbi_count_imp_mtbi.csv"))
dm_all_wmnd_mtbi <-
    read_csv(input_path("2023_07_17_dm_all_wmnd_qc_mtbi.csv"))
rm_gord_cor_mtbi <-
    read_csv(input_path("2023_07_17_rm_gord_cor_qc_mtbi.csv"))
rm_subc_cor_mtbi <-
    read_csv(input_path("2023_07_17_rm_subc_cor_qc_mtbi.csv"))
sm_cort_sa_mtbi <-
    read_csv(input_path("2023_07_17_sm_cort_sa_qc_mtbi.csv"))
sm_cort_t_mtbi <-
    read_csv(input_path("2023_07_17_sm_cort_t_qc_mtbi.csv"))
sm_subc_v_mtbi <-
    read_csv(input_path("2023_07_17_sm_subc_v_qc_mtbi.csv"))
p_loneliness_mtbi <-
    read_csv(input_path("2023_07_17_p_loneliness_imp_mtbi.csv"))
p_screen_time_mtbi <-
    read_csv(input_path("2023_07_17_p_screen_time_imp_mtbi.csv"))
p_fam_fn_mtbi <-
    read_csv(input_path("2023_07_17_p_fam_fn_imp_mtbi.csv"))
p_sports_mtbi <-
    read_csv(input_path("2023_07_17_p_sports_imp_mtbi.csv"))
p_prosocial_mtbi <-
    read_csv(input_path("2023_07_17_p_prosocial_imp_mtbi.csv"))
p_parent_psych_mtbi <-
    read_csv(input_path("2023_07_17_p_parent_psych_imp_mtbi.csv"))
p_exercise_mtbi <-
    read_csv(input_path("2023_07_17_p_exercise_imp_mtbi.csv"))
cbcl_headaches_mtbi <-
    read_csv(input_path("2023_07_17_cbcl_headaches_imp_mtbi.csv"))
cbcl_nausea_mtbi <-
    read_csv(input_path("2023_07_17_cbcl_nausea_imp_mtbi.csv"))
cbcl_vomiting_mtbi <-
    read_csv(input_path("2023_07_17_cbcl_vomiting_imp_mtbi.csv"))
cbcl_dizzy_mtbi <-
    read_csv(input_path("2023_07_17_cbcl_dizzy_imp_mtbi.csv"))
cbcl_overtired_mtbi <-
    read_csv(input_path("2023_07_17_cbcl_overtired_imp_mtbi.csv"))
cbcl_sleeping_more_mtbi <-
    read_csv(input_path("2023_07_17_cbcl_sleeping_more_imp_mtbi.csv"))
cbcl_sleeping_less_mtbi <-
    read_csv(input_path("2023_07_17_cbcl_sleeping_less_imp_mtbi.csv"))
cbcl_depress_mtbi <-
    read_csv(input_path("2023_07_17_cbcl_depress_imp_mtbi.csv"))
cbcl_anxiety_mtbi <-
    read_csv(input_path("2023_07_17_cbcl_anxiety_imp_mtbi.csv"))
cbcl_attention_mtbi <-
    read_csv(input_path("2023_07_17_cbcl_attention_imp_mtbi.csv"))
cbcl_aggressive_mtbi <-
    read_csv(input_path("2023_07_17_cbcl_aggressive_imp_mtbi.csv"))
sds_sleep_mtbi <-
    read_csv(input_path("2023_07_17_sds_sleep_imp_mtbi.csv"))
nihtbx_list_fc_mtbi <-
    read_csv(input_path("2023_07_17_nihtbx_list_fc_imp_mtbi.csv"))
nihtbx_pattern_fc_mtbi <-
    read_csv(input_path("2023_07_17_nihtbx_pattern_fc_imp_mtbi.csv"))
nihtbx_cardsort_fc_mtbi <-
    read_csv(input_path("2023_07_17_nihtbx_cardsort_fc_imp_mtbi.csv"))


# Filtering to common subjects
common_subs <- common_subjects(list(
    as_mtbi_loc_mtbi,
    as_mtbi_mechanism_mtbi,
    as_mtbi_mem_daze_mtbi,
    d_income_mtbi,
    d_interview_age_mtbi,
    d_mtbi_age_mtbi,
    d_pubertal_status_mtbi,
    d_race_mtbi,
    d_sex_mtbi,
    mh_headaches_mtbi,
    mh_mtbi_count_mtbi,
    dm_all_wmnd_mtbi,
    rm_gord_cor_mtbi,
    rm_subc_cor_mtbi,
    sm_cort_sa_mtbi,
    sm_cort_t_mtbi,
    sm_subc_v_mtbi,
    p_loneliness_mtbi,
    p_screen_time_mtbi,
    p_fam_fn_mtbi,
    p_sports_mtbi,
    p_prosocial_mtbi,
    p_parent_psych_mtbi,
    p_exercise_mtbi,
    cbcl_headaches_mtbi,
    cbcl_nausea_mtbi,
    cbcl_vomiting_mtbi,
    cbcl_dizzy_mtbi,
    cbcl_overtired_mtbi,
    cbcl_sleeping_more_mtbi,
    cbcl_sleeping_less_mtbi,
    cbcl_depress_mtbi,
    cbcl_anxiety_mtbi,
    cbcl_attention_mtbi,
    cbcl_aggressive_mtbi,
    sds_sleep_mtbi))

# Assigning common subjects into training and testing sets
assigned_df_0 <- train_test_assign(train_frac = 0.8, subjects = common_subs)

# Generate training set
as_mtbi_loc_mtbi_train <-
    keep_split(as_mtbi_loc_mtbi, assigned_df_0, "train")
as_mtbi_mechanism_mtbi_train <-
    keep_split(as_mtbi_mechanism_mtbi, assigned_df_0, "train")
as_mtbi_mem_daze_mtbi_train <-
    keep_split(as_mtbi_mem_daze_mtbi, assigned_df_0, "train")
d_income_mtbi_train <-
    keep_split(d_income_mtbi, assigned_df_0, "train")
d_interview_age_mtbi_train <-
    keep_split(d_interview_age_mtbi, assigned_df_0, "train")
d_mtbi_age_mtbi_train <-
    keep_split(d_mtbi_age_mtbi, assigned_df_0, "train")
d_pubertal_status_mtbi_train <-
    keep_split(d_pubertal_status_mtbi, assigned_df_0, "train")
d_race_mtbi_train <-
    keep_split(d_race_mtbi, assigned_df_0, "train")
d_sex_mtbi_train <-
    keep_split(d_sex_mtbi, assigned_df_0, "train")
mh_headaches_mtbi_train <-
    keep_split(mh_headaches_mtbi, assigned_df_0, "train")
mh_mtbi_count_mtbi_train <-
    keep_split(mh_mtbi_count_mtbi, assigned_df_0, "train")
dm_all_wmnd_mtbi_train <-
    keep_split(dm_all_wmnd_mtbi, assigned_df_0, "train")
rm_gord_cor_mtbi_train <-
    keep_split(rm_gord_cor_mtbi, assigned_df_0, "train")
rm_subc_cor_mtbi_train <-
    keep_split(rm_subc_cor_mtbi, assigned_df_0, "train")
sm_cort_sa_mtbi_train <-
    keep_split(sm_cort_sa_mtbi, assigned_df_0, "train")
sm_cort_t_mtbi_train <-
    keep_split(sm_cort_t_mtbi, assigned_df_0, "train")
sm_subc_v_mtbi_train <-
    keep_split(sm_subc_v_mtbi, assigned_df_0, "train")
p_loneliness_mtbi_train <-
    keep_split(p_loneliness_mtbi, assigned_df_0, "train")
p_screen_time_mtbi_train <-
    keep_split(p_screen_time_mtbi, assigned_df_0, "train")
p_fam_fn_mtbi_train <-
    keep_split(p_fam_fn_mtbi, assigned_df_0, "train")
p_sports_mtbi_train <-
    keep_split(p_sports_mtbi, assigned_df_0, "train")
p_prosocial_mtbi_train <-
    keep_split(p_prosocial_mtbi, assigned_df_0, "train")
p_parent_psych_mtbi_train <-
    keep_split(p_parent_psych_mtbi, assigned_df_0, "train")
p_exercise_mtbi_train <-
    keep_split(p_exercise_mtbi, assigned_df_0, "train")
cbcl_headaches_mtbi_train <-
    keep_split(cbcl_headaches_mtbi, assigned_df_0, "train")
cbcl_nausea_mtbi_train <-
    keep_split(cbcl_nausea_mtbi, assigned_df_0, "train")
cbcl_vomiting_mtbi_train <-
    keep_split(cbcl_vomiting_mtbi, assigned_df_0, "train")
cbcl_dizzy_mtbi_train <-
    keep_split(cbcl_dizzy_mtbi, assigned_df_0, "train")
cbcl_overtired_mtbi_train <-
    keep_split(cbcl_overtired_mtbi, assigned_df_0, "train")
cbcl_sleeping_more_mtbi_train <-
    keep_split(cbcl_sleeping_more_mtbi, assigned_df_0, "train")
cbcl_sleeping_less_mtbi_train <-
    keep_split(cbcl_sleeping_less_mtbi, assigned_df_0, "train")
cbcl_depress_mtbi_train <-
    keep_split(cbcl_depress_mtbi, assigned_df_0, "train")
cbcl_anxiety_mtbi_train <-
    keep_split(cbcl_anxiety_mtbi, assigned_df_0, "train")
cbcl_attention_mtbi_train <-
    keep_split(cbcl_attention_mtbi, assigned_df_0, "train")
cbcl_aggressive_mtbi_train <-
    keep_split(cbcl_aggressive_mtbi, assigned_df_0, "train")
sds_sleep_mtbi_train <-
    keep_split(sds_sleep_mtbi, assigned_df_0, "train")

# Generate testing set
as_mtbi_loc_mtbi_test <-
    keep_split(as_mtbi_loc_mtbi, assigned_df_0, "test")
as_mtbi_mechanism_mtbi_test <-
    keep_split(as_mtbi_mechanism_mtbi, assigned_df_0, "test")
as_mtbi_mem_daze_mtbi_test <-
    keep_split(as_mtbi_mem_daze_mtbi, assigned_df_0, "test")
d_income_mtbi_test <-
    keep_split(d_income_mtbi, assigned_df_0, "test")
d_interview_age_mtbi_test <-
    keep_split(d_interview_age_mtbi, assigned_df_0, "test")
d_mtbi_age_mtbi_test <-
    keep_split(d_mtbi_age_mtbi, assigned_df_0, "test")
d_pubertal_status_mtbi_test <-
    keep_split(d_pubertal_status_mtbi, assigned_df_0, "test")
d_race_mtbi_test <-
    keep_split(d_race_mtbi, assigned_df_0, "test")
d_sex_mtbi_test <-
    keep_split(d_sex_mtbi, assigned_df_0, "test")
mh_headaches_mtbi_test <-
    keep_split(mh_headaches_mtbi, assigned_df_0, "test")
mh_mtbi_count_mtbi_test <-
    keep_split(mh_mtbi_count_mtbi, assigned_df_0, "test")
dm_all_wmnd_mtbi_test <-
    keep_split(dm_all_wmnd_mtbi, assigned_df_0, "test")
rm_gord_cor_mtbi_test <-
    keep_split(rm_gord_cor_mtbi, assigned_df_0, "test")
rm_subc_cor_mtbi_test <-
    keep_split(rm_subc_cor_mtbi, assigned_df_0, "test")
sm_cort_sa_mtbi_test <-
    keep_split(sm_cort_sa_mtbi, assigned_df_0, "test")
sm_cort_t_mtbi_test <-
    keep_split(sm_cort_t_mtbi, assigned_df_0, "test")
sm_subc_v_mtbi_test <-
    keep_split(sm_subc_v_mtbi, assigned_df_0, "test")
p_loneliness_mtbi_test <-
    keep_split(p_loneliness_mtbi, assigned_df_0, "test")
p_screen_time_mtbi_test <-
    keep_split(p_screen_time_mtbi, assigned_df_0, "test")
p_fam_fn_mtbi_test <-
    keep_split(p_fam_fn_mtbi, assigned_df_0, "test")
p_sports_mtbi_test <-
    keep_split(p_sports_mtbi, assigned_df_0, "test")
p_prosocial_mtbi_test <-
    keep_split(p_prosocial_mtbi, assigned_df_0, "test")
p_parent_psych_mtbi_test <-
    keep_split(p_parent_psych_mtbi, assigned_df_0, "test")
p_exercise_mtbi_test <-
    keep_split(p_exercise_mtbi, assigned_df_0, "test")
cbcl_headaches_mtbi_test <-
    keep_split(cbcl_headaches_mtbi, assigned_df_0, "test")
cbcl_nausea_mtbi_test <-
    keep_split(cbcl_nausea_mtbi, assigned_df_0, "test")
cbcl_vomiting_mtbi_test <-
    keep_split(cbcl_vomiting_mtbi, assigned_df_0, "test")
cbcl_dizzy_mtbi_test <-
    keep_split(cbcl_dizzy_mtbi, assigned_df_0, "test")
cbcl_overtired_mtbi_test <-
    keep_split(cbcl_overtired_mtbi, assigned_df_0, "test")
cbcl_sleeping_more_mtbi_test <-
    keep_split(cbcl_sleeping_more_mtbi, assigned_df_0, "test")
cbcl_sleeping_less_mtbi_test <-
    keep_split(cbcl_sleeping_less_mtbi, assigned_df_0, "test")
cbcl_depress_mtbi_test <-
    keep_split(cbcl_depress_mtbi, assigned_df_0, "test")
cbcl_anxiety_mtbi_test <-
    keep_split(cbcl_anxiety_mtbi, assigned_df_0, "test")
cbcl_attention_mtbi_test <-
    keep_split(cbcl_attention_mtbi, assigned_df_0, "test")
cbcl_aggressive_mtbi_test <-
    keep_split(cbcl_aggressive_mtbi, assigned_df_0, "test")
sds_sleep_mtbi_test <-
    keep_split(sds_sleep_mtbi, assigned_df_0, "test")

# Generate full set (note that this is structured specifically in row order of
#  training subjects followed by testing subjects)
as_mtbi_loc_mtbi_full <-
    rbind(as_mtbi_loc_mtbi_train, as_mtbi_loc_mtbi_test)
as_mtbi_mechanism_mtbi_full <-
    rbind(as_mtbi_mechanism_mtbi_train, as_mtbi_mechanism_mtbi_test)
as_mtbi_mem_daze_mtbi_full <-
    rbind(as_mtbi_mem_daze_mtbi_train, as_mtbi_mem_daze_mtbi_test)
d_income_mtbi_full <-
    rbind(d_income_mtbi_train, d_income_mtbi_test)
d_interview_age_mtbi_full <-
    rbind(d_interview_age_mtbi_train, d_interview_age_mtbi_test)
d_mtbi_age_mtbi_full <-
    rbind(d_mtbi_age_mtbi_train, d_mtbi_age_mtbi_test)
d_pubertal_status_mtbi_full <-
    rbind(d_pubertal_status_mtbi_train, d_pubertal_status_mtbi_test)
d_race_mtbi_full <-
    rbind(d_race_mtbi_train, d_race_mtbi_test)
d_sex_mtbi_full <-
    rbind(d_sex_mtbi_train, d_sex_mtbi_test)
mh_headaches_mtbi_full <-
    rbind(mh_headaches_mtbi_train, mh_headaches_mtbi_test)
mh_mtbi_count_mtbi_full <-
    rbind(mh_mtbi_count_mtbi_train, mh_mtbi_count_mtbi_test)
dm_all_wmnd_mtbi_full <-
    rbind(dm_all_wmnd_mtbi_train, dm_all_wmnd_mtbi_test)
rm_gord_cor_mtbi_full <-
    rbind(rm_gord_cor_mtbi_train, rm_gord_cor_mtbi_test)
rm_subc_cor_mtbi_full <-
    rbind(rm_subc_cor_mtbi_train, rm_subc_cor_mtbi_test)
sm_cort_sa_mtbi_full <-
    rbind(sm_cort_sa_mtbi_train, sm_cort_sa_mtbi_test)
sm_cort_t_mtbi_full <-
    rbind(sm_cort_t_mtbi_train, sm_cort_t_mtbi_test)
sm_subc_v_mtbi_full <-
    rbind(sm_subc_v_mtbi_train, sm_subc_v_mtbi_test)
p_loneliness_mtbi_full <-
    rbind(p_loneliness_mtbi_train, p_loneliness_mtbi_test)
p_screen_time_mtbi_full <-
    rbind(p_screen_time_mtbi_train, p_screen_time_mtbi_test)
p_fam_fn_mtbi_full <-
    rbind(p_fam_fn_mtbi_train, p_fam_fn_mtbi_test)
p_sports_mtbi_full <-
    rbind(p_sports_mtbi_train, p_sports_mtbi_test)
p_prosocial_mtbi_full <-
    rbind(p_prosocial_mtbi_train, p_prosocial_mtbi_test)
p_parent_psych_mtbi_full <-
    rbind(p_parent_psych_mtbi_train, p_parent_psych_mtbi_test)
p_exercise_mtbi_full <-
    rbind(p_exercise_mtbi_train, p_exercise_mtbi_test)
cbcl_headaches_mtbi_full <-
    rbind(cbcl_headaches_mtbi_train, cbcl_headaches_mtbi_test)
cbcl_nausea_mtbi_full <-
    rbind(cbcl_nausea_mtbi_train, cbcl_nausea_mtbi_test)
cbcl_vomiting_mtbi_full <-
    rbind(cbcl_vomiting_mtbi_train, cbcl_vomiting_mtbi_test)
cbcl_dizzy_mtbi_full <-
    rbind(cbcl_dizzy_mtbi_train, cbcl_dizzy_mtbi_test)
cbcl_overtired_mtbi_full <-
    rbind(cbcl_overtired_mtbi_train, cbcl_overtired_mtbi_test)
cbcl_sleeping_more_mtbi_full <-
    rbind(cbcl_sleeping_more_mtbi_train, cbcl_sleeping_more_mtbi_test)
cbcl_sleeping_less_mtbi_full <-
    rbind(cbcl_sleeping_less_mtbi_train, cbcl_sleeping_less_mtbi_test)
cbcl_depress_mtbi_full <-
    rbind(cbcl_depress_mtbi_train, cbcl_depress_mtbi_test)
cbcl_anxiety_mtbi_full <-
    rbind(cbcl_anxiety_mtbi_train, cbcl_anxiety_mtbi_test)
cbcl_attention_mtbi_full <-
    rbind(cbcl_attention_mtbi_train, cbcl_attention_mtbi_test)
cbcl_aggressive_mtbi_full <-
    rbind(cbcl_aggressive_mtbi_train, cbcl_aggressive_mtbi_test)


# Export training set
write_csv(as_mtbi_loc_mtbi_train,
    proc_path("as_mtbi_loc_mtbi_train.csv", date = TRUE))
write_csv(as_mtbi_mechanism_mtbi_train,
    proc_path("as_mtbi_mechanism_mtbi_train.csv", date = TRUE))
write_csv(as_mtbi_mem_daze_mtbi_train,
    proc_path("as_mtbi_mem_daze_mtbi_train.csv", date = TRUE))
write_csv(d_income_mtbi_train,
    proc_path("d_income_mtbi_train.csv", date = TRUE))
write_csv(d_interview_age_mtbi_train,
    proc_path("d_interview_age_mtbi_train.csv", date = TRUE))
write_csv(d_mtbi_age_mtbi_train,
    proc_path("d_mtbi_age_mtbi_train.csv", date = TRUE))
write_csv(d_pubertal_status_mtbi_train,
    proc_path("d_pubertal_status_mtbi_train.csv", date = TRUE))
write_csv(d_race_mtbi_train,
    proc_path("d_race_mtbi_train.csv", date = TRUE))
write_csv(d_sex_mtbi_train,
    proc_path("d_sex_mtbi_train.csv", date = TRUE))
write_csv(mh_headaches_mtbi_train,
    proc_path("mh_headaches_mtbi_train.csv", date = TRUE))
write_csv(mh_mtbi_count_mtbi_train,
    proc_path("mh_mtbi_count_mtbi_train.csv", date = TRUE))
write_csv(dm_all_wmnd_mtbi_train,
    proc_path("dm_all_wmnd_mtbi_train.csv", date = TRUE))
write_csv(rm_gord_cor_mtbi_train,
    proc_path("rm_gord_cor_mtbi_train.csv", date = TRUE))
write_csv(rm_subc_cor_mtbi_train,
    proc_path("rm_subc_cor_mtbi_train.csv", date = TRUE))
write_csv(sm_cort_sa_mtbi_train,
    proc_path("sm_cort_sa_mtbi_train.csv", date = TRUE))
write_csv(sm_cort_t_mtbi_train,
    proc_path("sm_cort_t_mtbi_train.csv", date = TRUE))
write_csv(sm_subc_v_mtbi_train,
    proc_path("sm_subc_v_mtbi_train.csv", date = TRUE))
write_csv(p_loneliness_mtbi_train,
    proc_path("p_loneliness_mtbi_train.csv", date = TRUE))
write_csv(p_screen_time_mtbi_train,
    proc_path("p_screen_time_mtbi_train.csv", date = TRUE))
write_csv(p_fam_fn_mtbi_train,
    proc_path("p_fam_fn_mtbi_train.csv", date = TRUE))
write_csv(p_sports_mtbi_train,
    proc_path("p_sports_mtbi_train.csv", date = TRUE))
write_csv(p_prosocial_mtbi_train,
    proc_path("p_prosocial_mtbi_train.csv", date = TRUE))
write_csv(p_parent_psych_mtbi_train,
    proc_path("p_parent_psych_mtbi_train.csv", date = TRUE))
write_csv(p_exercise_mtbi_train,
    proc_path("p_exercise_mtbi_train.csv", date = TRUE))
write_csv(cbcl_headaches_mtbi_train,
    proc_path("cbcl_headaches_mtbi_train.csv", date = TRUE))
write_csv(cbcl_nausea_mtbi_train,
    proc_path("cbcl_nausea_mtbi_train.csv", date = TRUE))
write_csv(cbcl_vomiting_mtbi_train,
    proc_path("cbcl_vomiting_mtbi_train.csv", date = TRUE))
write_csv(cbcl_dizzy_mtbi_train,
    proc_path("cbcl_dizzy_mtbi_train.csv", date = TRUE))
write_csv(cbcl_overtired_mtbi_train,
    proc_path("cbcl_overtired_mtbi_train.csv", date = TRUE))
write_csv(cbcl_sleeping_more_mtbi_train,
    proc_path("cbcl_sleeping_more_mtbi_train.csv", date = TRUE))
write_csv(cbcl_sleeping_less_mtbi_train,
    proc_path("cbcl_sleeping_less_mtbi_train.csv", date = TRUE))
write_csv(cbcl_depress_mtbi_train,
    proc_path("cbcl_depress_mtbi_train.csv", date = TRUE))
write_csv(cbcl_anxiety_mtbi_train,
    proc_path("cbcl_anxiety_mtbi_train.csv", date = TRUE))
write_csv(cbcl_attention_mtbi_train,
    proc_path("cbcl_attention_mtbi_train.csv", date = TRUE))
write_csv(cbcl_aggressive_mtbi_train,
    proc_path("cbcl_aggressive_mtbi_train.csv", date = TRUE))
write_csv(sds_sleep_mtbi_train,
    proc_path("sds_sleep_mtbi_train.csv", date = TRUE))

# Export testing set
write_csv(as_mtbi_loc_mtbi_test,
    proc_path("as_mtbi_loc_mtbi_test.csv", date = TRUE))
write_csv(as_mtbi_mechanism_mtbi_test,
    proc_path("as_mtbi_mechanism_mtbi_test.csv", date = TRUE))
write_csv(as_mtbi_mem_daze_mtbi_test,
    proc_path("as_mtbi_mem_daze_mtbi_test.csv", date = TRUE))
write_csv(d_income_mtbi_test,
    proc_path("d_income_mtbi_test.csv", date = TRUE))
write_csv(d_interview_age_mtbi_test,
    proc_path("d_interview_age_mtbi_test.csv", date = TRUE))
write_csv(d_mtbi_age_mtbi_test,
    proc_path("d_mtbi_age_mtbi_test.csv", date = TRUE))
write_csv(d_pubertal_status_mtbi_test,
    proc_path("d_pubertal_status_mtbi_test.csv", date = TRUE))
write_csv(d_race_mtbi_test,
    proc_path("d_race_mtbi_test.csv", date = TRUE))
write_csv(d_sex_mtbi_test,
    proc_path("d_sex_mtbi_test.csv", date = TRUE))
write_csv(mh_headaches_mtbi_test,
    proc_path("mh_headaches_mtbi_test.csv", date = TRUE))
write_csv(mh_mtbi_count_mtbi_test,
    proc_path("mh_mtbi_count_mtbi_test.csv", date = TRUE))
write_csv(dm_all_wmnd_mtbi_test,
    proc_path("dm_all_wmnd_mtbi_test.csv", date = TRUE))
write_csv(rm_gord_cor_mtbi_test,
    proc_path("rm_gord_cor_mtbi_test.csv", date = TRUE))
write_csv(rm_subc_cor_mtbi_test,
    proc_path("rm_subc_cor_mtbi_test.csv", date = TRUE))
write_csv(sm_cort_sa_mtbi_test,
    proc_path("sm_cort_sa_mtbi_test.csv", date = TRUE))
write_csv(sm_cort_t_mtbi_test,
    proc_path("sm_cort_t_mtbi_test.csv", date = TRUE))
write_csv(sm_subc_v_mtbi_test,
    proc_path("sm_subc_v_mtbi_test.csv", date = TRUE))
write_csv(p_loneliness_mtbi_test,
    proc_path("p_loneliness_mtbi_test.csv", date = TRUE))
write_csv(p_screen_time_mtbi_test,
    proc_path("p_screen_time_mtbi_test.csv", date = TRUE))
write_csv(p_fam_fn_mtbi_test,
    proc_path("p_fam_fn_mtbi_test.csv", date = TRUE))
write_csv(p_sports_mtbi_test,
    proc_path("p_sports_mtbi_test.csv", date = TRUE))
write_csv(p_prosocial_mtbi_test,
    proc_path("p_prosocial_mtbi_test.csv", date = TRUE))
write_csv(p_parent_psych_mtbi_test,
    proc_path("p_parent_psych_mtbi_test.csv", date = TRUE))
write_csv(p_exercise_mtbi_test,
    proc_path("p_exercise_mtbi_test.csv", date = TRUE))
write_csv(cbcl_headaches_mtbi_test,
    proc_path("cbcl_headaches_mtbi_test.csv", date = TRUE))
write_csv(cbcl_nausea_mtbi_test,
    proc_path("cbcl_nausea_mtbi_test.csv", date = TRUE))
write_csv(cbcl_vomiting_mtbi_test,
    proc_path("cbcl_vomiting_mtbi_test.csv", date = TRUE))
write_csv(cbcl_dizzy_mtbi_test,
    proc_path("cbcl_dizzy_mtbi_test.csv", date = TRUE))
write_csv(cbcl_overtired_mtbi_test,
    proc_path("cbcl_overtired_mtbi_test.csv", date = TRUE))
write_csv(cbcl_sleeping_more_mtbi_test,
    proc_path("cbcl_sleeping_more_mtbi_test.csv", date = TRUE))
write_csv(cbcl_sleeping_less_mtbi_test,
    proc_path("cbcl_sleeping_less_mtbi_test.csv", date = TRUE))
write_csv(cbcl_depress_mtbi_test,
    proc_path("cbcl_depress_mtbi_test.csv", date = TRUE))
write_csv(cbcl_anxiety_mtbi_test,
    proc_path("cbcl_anxiety_mtbi_test.csv", date = TRUE))
write_csv(cbcl_attention_mtbi_test,
    proc_path("cbcl_attention_mtbi_test.csv", date = TRUE))
write_csv(cbcl_aggressive_mtbi_test,
    proc_path("cbcl_aggressive_mtbi_test.csv", date = TRUE))
write_csv(sds_sleep_mtbi_test,
    proc_path("sds_sleep_mtbi_test.csv", date = TRUE))

# Full data
write_csv(as_mtbi_loc_mtbi_full,
    proc_path("as_mtbi_loc_mtbi_full.csv", date = TRUE))
write_csv(as_mtbi_mechanism_mtbi_full,
    proc_path("as_mtbi_mechanism_mtbi_full.csv", date = TRUE))
write_csv(as_mtbi_mem_daze_mtbi_full,
    proc_path("as_mtbi_mem_daze_mtbi_full.csv", date = TRUE))
write_csv(d_income_mtbi_full,
    proc_path("d_income_mtbi_full.csv", date = TRUE))
write_csv(d_interview_age_mtbi_full,
    proc_path("d_interview_age_mtbi_full.csv", date = TRUE))
write_csv(d_mtbi_age_mtbi_full,
    proc_path("d_mtbi_age_mtbi_full.csv", date = TRUE))
write_csv(d_pubertal_status_mtbi_full,
    proc_path("d_pubertal_status_mtbi_full.csv", date = TRUE))
write_csv(d_race_mtbi_full,
    proc_path("d_race_mtbi_full.csv", date = TRUE))
write_csv(d_sex_mtbi_full,
    proc_path("d_sex_mtbi_full.csv", date = TRUE))
write_csv(mh_headaches_mtbi_full,
    proc_path("mh_headaches_mtbi_full.csv", date = TRUE))
write_csv(mh_mtbi_count_mtbi_full,
    proc_path("mh_mtbi_count_mtbi_full.csv", date = TRUE))
write_csv(dm_all_wmnd_mtbi_full,
    proc_path("dm_all_wmnd_mtbi_full.csv", date = TRUE))
write_csv(rm_gord_cor_mtbi_full,
    proc_path("rm_gord_cor_mtbi_full.csv", date = TRUE))
write_csv(rm_subc_cor_mtbi_full,
    proc_path("rm_subc_cor_mtbi_full.csv", date = TRUE))
write_csv(sm_cort_sa_mtbi_full,
    proc_path("sm_cort_sa_mtbi_full.csv", date = TRUE))
write_csv(sm_cort_t_mtbi_full,
    proc_path("sm_cort_t_mtbi_full.csv", date = TRUE))
write_csv(sm_subc_v_mtbi_full,
    proc_path("sm_subc_v_mtbi_full.csv", date = TRUE))
write_csv(p_loneliness_mtbi_full,
    proc_path("p_loneliness_mtbi_full.csv", date = TRUE))
write_csv(p_screen_time_mtbi_full,
    proc_path("p_screen_time_mtbi_full.csv", date = TRUE))
write_csv(p_fam_fn_mtbi_full,
    proc_path("p_fam_fn_mtbi_full.csv", date = TRUE))
write_csv(p_sports_mtbi_full,
    proc_path("p_sports_mtbi_full.csv", date = TRUE))
write_csv(p_prosocial_mtbi_full,
    proc_path("p_prosocial_mtbi_full.csv", date = TRUE))
write_csv(p_parent_psych_mtbi_full,
    proc_path("p_parent_psych_mtbi_full.csv", date = TRUE))
write_csv(p_exercise_mtbi_full,
    proc_path("p_exercise_mtbi_full.csv", date = TRUE))
write_csv(cbcl_headaches_mtbi_full,
    proc_path("cbcl_headaches_mtbi_full.csv", date = TRUE))
write_csv(cbcl_nausea_mtbi_full,
    proc_path("cbcl_nausea_mtbi_full.csv", date = TRUE))
write_csv(cbcl_vomiting_mtbi_full,
    proc_path("cbcl_vomiting_mtbi_full.csv", date = TRUE))
write_csv(cbcl_dizzy_mtbi_full,
    proc_path("cbcl_dizzy_mtbi_full.csv", date = TRUE))
write_csv(cbcl_overtired_mtbi_full,
    proc_path("cbcl_overtired_mtbi_full.csv", date = TRUE))
write_csv(cbcl_sleeping_more_mtbi_full,
    proc_path("cbcl_sleeping_more_mtbi_full.csv", date = TRUE))
write_csv(cbcl_sleeping_less_mtbi_full,
    proc_path("cbcl_sleeping_less_mtbi_full.csv", date = TRUE))
write_csv(cbcl_depress_mtbi_full,
    proc_path("cbcl_depress_mtbi_full.csv", date = TRUE))
write_csv(cbcl_anxiety_mtbi_full,
    proc_path("cbcl_anxiety_mtbi_full.csv", date = TRUE))
write_csv(cbcl_attention_mtbi_full,
    proc_path("cbcl_attention_mtbi_full.csv", date = TRUE))
write_csv(cbcl_aggressive_mtbi_full,
    proc_path("cbcl_aggressive_mtbi_full.csv", date = TRUE))
```


## Data and outcome lists

Subsequent analyses make use of custom `data_list` and `outcome_list` objects that store information about all input variables and outcome (CBCL) measures used for SNF and cluster characterization.
I also store make use of a `cbcl_list` object, which is simply a list of cbcl dataframes and does not keep a track of the same amount of metadata as used in the highly nested `outcome_list` object.
Instead of loading each individual file and building these lists, we can build the lists here and export them for later use.

```{r}
library(metasnf)
library(rlist)

# Importing the data
as_mtbi_loc_mtbi_train <-
    read_csv(proc_path("2023_07_17_as_mtbi_loc_mtbi_train.csv"))
as_mtbi_mechanism_mtbi_train <-
    read_csv(proc_path("2023_07_17_as_mtbi_mechanism_mtbi_train.csv"))
as_mtbi_mem_daze_mtbi_train <-
    read_csv(proc_path("2023_07_17_as_mtbi_mem_daze_mtbi_train.csv"))
d_income_mtbi_train <-
    read_csv(proc_path("2023_07_17_d_income_mtbi_train.csv"))
d_interview_age_mtbi_train <-
    read_csv(proc_path("2023_07_17_d_interview_age_mtbi_train.csv"))
d_mtbi_age_mtbi_train <-
    read_csv(proc_path("2023_07_17_d_mtbi_age_mtbi_train.csv"))
d_pubertal_status_mtbi_train <-
    read_csv(proc_path("2023_07_17_d_pubertal_status_mtbi_train.csv"))
d_race_mtbi_train <-
    read_csv(proc_path("2023_07_17_d_race_mtbi_train.csv"))
d_sex_mtbi_train <-
    read_csv(proc_path("2023_07_17_d_sex_mtbi_train.csv"))
mh_headaches_mtbi_train <-
    read_csv(proc_path("2023_07_17_mh_headaches_mtbi_train.csv"))
mh_mtbi_count_mtbi_train <-
    read_csv(proc_path("2023_07_17_mh_mtbi_count_mtbi_train.csv"))
dm_all_wmnd_mtbi_train <-
    read_csv(proc_path("2023_07_17_dm_all_wmnd_mtbi_train.csv"))
rm_gord_cor_mtbi_train <-
    read_csv(proc_path("2023_07_17_rm_gord_cor_mtbi_train.csv"))
rm_subc_cor_mtbi_train <-
    read_csv(proc_path("2023_07_17_rm_subc_cor_mtbi_train.csv"))
sm_cort_sa_mtbi_train <-
    read_csv(proc_path("2023_07_17_sm_cort_sa_mtbi_train.csv"))
sm_cort_t_mtbi_train <-
    read_csv(proc_path("2023_07_17_sm_cort_t_mtbi_train.csv"))
sm_subc_v_mtbi_train <-
    read_csv(proc_path("2023_07_17_sm_subc_v_mtbi_train.csv"))
p_loneliness_mtbi_train <-
    read_csv(proc_path("2023_07_17_p_loneliness_mtbi_train.csv"))
p_screen_time_mtbi_train <-
    read_csv(proc_path("2023_07_17_p_screen_time_mtbi_train.csv"))
p_fam_fn_mtbi_train <-
    read_csv(proc_path("2023_07_17_p_fam_fn_mtbi_train.csv"))
p_sports_mtbi_train <-
    read_csv(proc_path("2023_07_17_p_sports_mtbi_train.csv"))
p_prosocial_mtbi_train <-
    read_csv(proc_path("2023_07_17_p_prosocial_mtbi_train.csv"))
p_parent_psych_mtbi_train <-
    read_csv(proc_path("2023_07_17_p_parent_psych_mtbi_train.csv"))
p_exercise_mtbi_train <-
    read_csv(proc_path("2023_07_17_p_exercise_mtbi_train.csv"))
cbcl_headaches_mtbi_train <-
    read_csv(proc_path("2023_07_17_cbcl_headaches_mtbi_train.csv"))
cbcl_nausea_mtbi_train <-
    read_csv(proc_path("2023_07_17_cbcl_nausea_mtbi_train.csv"))
cbcl_vomiting_mtbi_train <-
    read_csv(proc_path("2023_07_17_cbcl_vomiting_mtbi_train.csv"))
cbcl_dizzy_mtbi_train <-
    read_csv(proc_path("2023_07_17_cbcl_dizzy_mtbi_train.csv"))
cbcl_overtired_mtbi_train <-
    read_csv(proc_path("2023_07_17_cbcl_overtired_mtbi_train.csv"))
cbcl_sleeping_more_mtbi_train <-
    read_csv(proc_path("2023_07_17_cbcl_sleeping_more_mtbi_train.csv"))
cbcl_sleeping_less_mtbi_train <-
    read_csv(proc_path("2023_07_17_cbcl_sleeping_less_mtbi_train.csv"))
cbcl_depress_mtbi_train <-
    read_csv(proc_path("2023_07_17_cbcl_depress_mtbi_train.csv"))
cbcl_anxiety_mtbi_train <-
    read_csv(proc_path("2023_07_17_cbcl_anxiety_mtbi_train.csv"))
cbcl_attention_mtbi_train <-
    read_csv(proc_path("2023_07_17_cbcl_attention_mtbi_train.csv"))
cbcl_aggressive_mtbi_train <-
    read_csv(proc_path("2023_07_17_cbcl_aggressive_mtbi_train.csv"))

as_mtbi_loc_mtbi_test <-
    read_csv(proc_path("2023_07_17_as_mtbi_loc_mtbi_test.csv"))
as_mtbi_mechanism_mtbi_test <-
    read_csv(proc_path("2023_07_17_as_mtbi_mechanism_mtbi_test.csv"))
as_mtbi_mem_daze_mtbi_test <-
    read_csv(proc_path("2023_07_17_as_mtbi_mem_daze_mtbi_test.csv"))
d_income_mtbi_test <-
    read_csv(proc_path("2023_07_17_d_income_mtbi_test.csv"))
d_interview_age_mtbi_test <-
    read_csv(proc_path("2023_07_17_d_interview_age_mtbi_test.csv"))
d_mtbi_age_mtbi_test <-
    read_csv(proc_path("2023_07_17_d_mtbi_age_mtbi_test.csv"))
d_pubertal_status_mtbi_test <-
    read_csv(proc_path("2023_07_17_d_pubertal_status_mtbi_test.csv"))
d_race_mtbi_test <-
    read_csv(proc_path("2023_07_17_d_race_mtbi_test.csv"))
d_sex_mtbi_test <-
    read_csv(proc_path("2023_07_17_d_sex_mtbi_test.csv"))
mh_headaches_mtbi_test <-
    read_csv(proc_path("2023_07_17_mh_headaches_mtbi_test.csv"))
mh_mtbi_count_mtbi_test <-
    read_csv(proc_path("2023_07_17_mh_mtbi_count_mtbi_test.csv"))
dm_all_wmnd_mtbi_test <-
    read_csv(proc_path("2023_07_17_dm_all_wmnd_mtbi_test.csv"))
rm_gord_cor_mtbi_test <-
    read_csv(proc_path("2023_07_17_rm_gord_cor_mtbi_test.csv"))
rm_subc_cor_mtbi_test <-
    read_csv(proc_path("2023_07_17_rm_subc_cor_mtbi_test.csv"))
sm_cort_sa_mtbi_test <-
    read_csv(proc_path("2023_07_17_sm_cort_sa_mtbi_test.csv"))
sm_cort_t_mtbi_test <-
    read_csv(proc_path("2023_07_17_sm_cort_t_mtbi_test.csv"))
sm_subc_v_mtbi_test <-
    read_csv(proc_path("2023_07_17_sm_subc_v_mtbi_test.csv"))
p_loneliness_mtbi_test <-
    read_csv(proc_path("2023_07_17_p_loneliness_mtbi_test.csv"))
p_screen_time_mtbi_test <-
    read_csv(proc_path("2023_07_17_p_screen_time_mtbi_test.csv"))
p_fam_fn_mtbi_test <-
    read_csv(proc_path("2023_07_17_p_fam_fn_mtbi_test.csv"))
p_sports_mtbi_test <-
    read_csv(proc_path("2023_07_17_p_sports_mtbi_test.csv"))
p_prosocial_mtbi_test <-
    read_csv(proc_path("2023_07_17_p_prosocial_mtbi_test.csv"))
p_parent_psych_mtbi_test <-
    read_csv(proc_path("2023_07_17_p_parent_psych_mtbi_test.csv"))
p_exercise_mtbi_test <-
    read_csv(proc_path("2023_07_17_p_exercise_mtbi_test.csv"))
cbcl_headaches_mtbi_test <-
    read_csv(proc_path("2023_07_17_cbcl_headaches_mtbi_test.csv"))
cbcl_nausea_mtbi_test <-
    read_csv(proc_path("2023_07_17_cbcl_nausea_mtbi_test.csv"))
cbcl_vomiting_mtbi_test <-
    read_csv(proc_path("2023_07_17_cbcl_vomiting_mtbi_test.csv"))
cbcl_dizzy_mtbi_test <-
    read_csv(proc_path("2023_07_17_cbcl_dizzy_mtbi_test.csv"))
cbcl_overtired_mtbi_test <-
    read_csv(proc_path("2023_07_17_cbcl_overtired_mtbi_test.csv"))
cbcl_sleeping_more_mtbi_test <-
    read_csv(proc_path("2023_07_17_cbcl_sleeping_more_mtbi_test.csv"))
cbcl_sleeping_less_mtbi_test <-
    read_csv(proc_path("2023_07_17_cbcl_sleeping_less_mtbi_test.csv"))
cbcl_depress_mtbi_test <-
    read_csv(proc_path("2023_07_17_cbcl_depress_mtbi_test.csv"))
cbcl_anxiety_mtbi_test <-
    read_csv(proc_path("2023_07_17_cbcl_anxiety_mtbi_test.csv"))
cbcl_attention_mtbi_test <-
    read_csv(proc_path("2023_07_17_cbcl_attention_mtbi_test.csv"))
cbcl_aggressive_mtbi_test <-
    read_csv(proc_path("2023_07_17_cbcl_aggressive_mtbi_test.csv"))

as_mtbi_loc_mtbi_full <-
    read_csv(proc_path("2023_07_17_as_mtbi_loc_mtbi_full.csv"))
as_mtbi_mechanism_mtbi_full <-
    read_csv(proc_path("2023_07_17_as_mtbi_mechanism_mtbi_full.csv"))
as_mtbi_mem_daze_mtbi_full <-
    read_csv(proc_path("2023_07_17_as_mtbi_mem_daze_mtbi_full.csv"))
d_income_mtbi_full <-
    read_csv(proc_path("2023_07_17_d_income_mtbi_full.csv"))
d_interview_age_mtbi_full <-
    read_csv(proc_path("2023_07_17_d_interview_age_mtbi_full.csv"))
d_mtbi_age_mtbi_full <-
    read_csv(proc_path("2023_07_17_d_mtbi_age_mtbi_full.csv"))
d_pubertal_status_mtbi_full <-
    read_csv(proc_path("2023_07_17_d_pubertal_status_mtbi_full.csv"))
d_race_mtbi_full <-
    read_csv(proc_path("2023_07_17_d_race_mtbi_full.csv"))
d_sex_mtbi_full <-
    read_csv(proc_path("2023_07_17_d_sex_mtbi_full.csv"))
mh_headaches_mtbi_full <-
    read_csv(proc_path("2023_07_17_mh_headaches_mtbi_full.csv"))
mh_mtbi_count_mtbi_full <-
    read_csv(proc_path("2023_07_17_mh_mtbi_count_mtbi_full.csv"))
dm_all_wmnd_mtbi_full <-
    read_csv(proc_path("2023_07_17_dm_all_wmnd_mtbi_full.csv"))
rm_gord_cor_mtbi_full <-
    read_csv(proc_path("2023_07_17_rm_gord_cor_mtbi_full.csv"))
rm_subc_cor_mtbi_full <-
    read_csv(proc_path("2023_07_17_rm_subc_cor_mtbi_full.csv"))
sm_cort_sa_mtbi_full <-
    read_csv(proc_path("2023_07_17_sm_cort_sa_mtbi_full.csv"))
sm_cort_t_mtbi_full <-
    read_csv(proc_path("2023_07_17_sm_cort_t_mtbi_full.csv"))
sm_subc_v_mtbi_full <-
    read_csv(proc_path("2023_07_17_sm_subc_v_mtbi_full.csv"))
p_loneliness_mtbi_full <-
    read_csv(proc_path("2023_07_17_p_loneliness_mtbi_full.csv"))
p_screen_time_mtbi_full <-
    read_csv(proc_path("2023_07_17_p_screen_time_mtbi_full.csv"))
p_fam_fn_mtbi_full <-
    read_csv(proc_path("2023_07_17_p_fam_fn_mtbi_full.csv"))
p_sports_mtbi_full <-
    read_csv(proc_path("2023_07_17_p_sports_mtbi_full.csv"))
p_prosocial_mtbi_full <-
    read_csv(proc_path("2023_07_17_p_prosocial_mtbi_full.csv"))
p_parent_psych_mtbi_full <-
    read_csv(proc_path("2023_07_17_p_parent_psych_mtbi_full.csv"))
p_exercise_mtbi_full <-
    read_csv(proc_path("2023_07_17_p_exercise_mtbi_full.csv"))
cbcl_headaches_mtbi_full <-
    read_csv(proc_path("2023_07_17_cbcl_headaches_mtbi_full.csv"))
cbcl_nausea_mtbi_full <-
    read_csv(proc_path("2023_07_17_cbcl_nausea_mtbi_full.csv"))
cbcl_vomiting_mtbi_full <-
    read_csv(proc_path("2023_07_17_cbcl_vomiting_mtbi_full.csv"))
cbcl_dizzy_mtbi_full <-
    read_csv(proc_path("2023_07_17_cbcl_dizzy_mtbi_full.csv"))
cbcl_overtired_mtbi_full <-
    read_csv(proc_path("2023_07_17_cbcl_overtired_mtbi_full.csv"))
cbcl_sleeping_more_mtbi_full <-
    read_csv(proc_path("2023_07_17_cbcl_sleeping_more_mtbi_full.csv"))
cbcl_sleeping_less_mtbi_full <-
    read_csv(proc_path("2023_07_17_cbcl_sleeping_less_mtbi_full.csv"))
cbcl_depress_mtbi_full <-
    read_csv(proc_path("2023_07_17_cbcl_depress_mtbi_full.csv"))
cbcl_anxiety_mtbi_full <-
    read_csv(proc_path("2023_07_17_cbcl_anxiety_mtbi_full.csv"))
cbcl_attention_mtbi_full <-
    read_csv(proc_path("2023_07_17_cbcl_attention_mtbi_full.csv"))
cbcl_aggressive_mtbi_full <-
    read_csv(proc_path("2023_07_17_cbcl_aggressive_mtbi_full.csv"))


# Training data list
data_list_mtbi_train <- generate_data_list(
    list(as_mtbi_loc_mtbi_train, "mtbi_loc", "as", "categorical"),
    list(as_mtbi_mechanism_mtbi_train, "mtbi_mechanism", "as", "categorical"),
    list(as_mtbi_mem_daze_mtbi_train, "mtbi_mem_daze", "as", "categorical"),
    list(d_income_mtbi_train, "income", "d", "numeric"),
    list(d_interview_age_mtbi_train, "interview_age", "d", "numeric"),
    list(d_mtbi_age_mtbi_train, "mtbi_age", "d", "numeric"),
    list(d_pubertal_status_mtbi_train, "pubertal_status", "d", "numeric"),
    list(d_race_mtbi_train, "race", "d", "categorical"),
    list(d_sex_mtbi_train, "sex", "d", "categorical"),
    list(mh_headaches_mtbi_train, "headaches", "mh", "categorical"),
    list(mh_mtbi_count_mtbi_train, "mtbi_count", "mh", "numeric"),
    list(dm_all_wmnd_mtbi_train, "wmndf", "n", "numeric"),
    list(rm_gord_cor_mtbi_train, "gord_cor", "n", "numeric"),
    list(rm_subc_cor_mtbi_train, "subc_cor", "n", "numeric"),
    list(sm_cort_sa_mtbi_train, "cort_sa", "n", "numeric"),
    list(sm_cort_t_mtbi_train, "cort_t", "n", "numeric"),
    list(sm_subc_v_mtbi_train, "subc_v", "n", "numeric"),
    list(p_loneliness_mtbi_train, "loneliness", "p", "numeric"),
    list(p_screen_time_mtbi_train, "screen_time", "p", "numeric"),
    list(p_fam_fn_mtbi_train, "fam_fn", "p", "numeric"),
    list(p_sports_mtbi_train, "sports", "p", "numeric"),
    list(p_prosocial_mtbi_train, "prosocial", "p", "numeric"),
    list(p_parent_psych_mtbi_train, "parent_psych", "p", "numeric"),
    list(p_exercise_mtbi_train, "exercise", "p", "numeric")
)

list.save(data_list_mtbi_train,
          proc_path("data_list_mtbi_train.rdata", date = TRUE))

# Testing
data_list_mtbi_test <- generate_data_list(
    list(as_mtbi_loc_mtbi_test, "mtbi_loc", "as", "categorical"),
    list(as_mtbi_mechanism_mtbi_test, "mtbi_mechanism", "as", "categorical"),
    list(as_mtbi_mem_daze_mtbi_test, "mtbi_mem_daze", "as", "categorical"),
    list(d_income_mtbi_test, "income", "d", "numeric"),
    list(d_interview_age_mtbi_test, "interview_age", "d", "numeric"),
    list(d_mtbi_age_mtbi_test, "mtbi_age", "d", "numeric"),
    list(d_pubertal_status_mtbi_test, "pubertal_status", "d", "numeric"),
    list(d_race_mtbi_test, "race", "d", "categorical"),
    list(d_sex_mtbi_test, "sex", "d", "categorical"),
    list(mh_headaches_mtbi_test, "headaches", "mh", "categorical"),
    list(mh_mtbi_count_mtbi_test, "mtbi_count", "mh", "numeric"),
    list(dm_all_wmnd_mtbi_test, "wmndf", "n", "numeric"),
    list(rm_gord_cor_mtbi_test, "gord_cor", "n", "numeric"),
    list(rm_subc_cor_mtbi_test, "subc_cor", "n", "numeric"),
    list(sm_cort_sa_mtbi_test, "cort_sa", "n", "numeric"),
    list(sm_cort_t_mtbi_test, "cort_t", "n", "numeric"),
    list(sm_subc_v_mtbi_test, "subc_v", "n", "numeric"),
    list(p_loneliness_mtbi_test, "loneliness", "p", "numeric"),
    list(p_screen_time_mtbi_test, "screen_time", "p", "numeric"),
    list(p_fam_fn_mtbi_test, "fam_fn", "p", "numeric"),
    list(p_sports_mtbi_test, "sports", "p", "numeric"),
    list(p_prosocial_mtbi_test, "prosocial", "p", "numeric"),
    list(p_parent_psych_mtbi_test, "parent_psych", "p", "numeric"),
    list(p_exercise_mtbi_test, "exercise", "p", "numeric")
)

list.save(data_list_mtbi_test,
          proc_path("data_list_mtbi_test.rdata", date = TRUE))


data_list_mtbi_full <- generate_data_list(
    list(as_mtbi_loc_mtbi_full, "mtbi_loc", "as", "categorical"),
    list(as_mtbi_mechanism_mtbi_full, "mtbi_mechanism", "as", "categorical"),
    list(as_mtbi_mem_daze_mtbi_full, "mtbi_mem_daze", "as", "categorical"),
    list(d_income_mtbi_full, "income", "d", "numeric"),
    list(d_interview_age_mtbi_full, "interview_age", "d", "numeric"),
    list(d_mtbi_age_mtbi_full, "mtbi_age", "d", "numeric"),
    list(d_pubertal_status_mtbi_full, "pubertal_status", "d", "numeric"),
    list(d_race_mtbi_full, "race", "d", "categorical"),
    list(d_sex_mtbi_full, "sex", "d", "categorical"),
    list(mh_headaches_mtbi_full, "headaches", "mh", "categorical"),
    list(mh_mtbi_count_mtbi_full, "mtbi_count", "mh", "numeric"),
    list(dm_all_wmnd_mtbi_full, "wmndf", "n", "numeric"),
    list(rm_gord_cor_mtbi_full, "gord_cor", "n", "numeric"),
    list(rm_subc_cor_mtbi_full, "subc_cor", "n", "numeric"),
    list(sm_cort_sa_mtbi_full, "cort_sa", "n", "numeric"),
    list(sm_cort_t_mtbi_full, "cort_t", "n", "numeric"),
    list(sm_subc_v_mtbi_full, "subc_v", "n", "numeric"),
    list(p_loneliness_mtbi_full, "loneliness", "p", "numeric"),
    list(p_screen_time_mtbi_full, "screen_time", "p", "numeric"),
    list(p_fam_fn_mtbi_full, "fam_fn", "p", "numeric"),
    list(p_sports_mtbi_full, "sports", "p", "numeric"),
    list(p_prosocial_mtbi_full, "prosocial", "p", "numeric"),
    list(p_parent_psych_mtbi_full, "parent_psych", "p", "numeric"),
    list(p_exercise_mtbi_full, "exercise", "p", "numeric")
)

list.save(data_list_mtbi_full,
          proc_path("data_list_mtbi_full.rdata", date = TRUE))


# Training CBCL list
cbcl_list_mtbi_train <- list(
    cbcl_nausea_mtbi_train,
    cbcl_vomiting_mtbi_train,
    cbcl_dizzy_mtbi_train,
    cbcl_overtired_mtbi_train,
    cbcl_sleeping_more_mtbi_train,
    cbcl_sleeping_less_mtbi_train,
    cbcl_depress_mtbi_train,
    cbcl_anxiety_mtbi_train,
    cbcl_attention_mtbi_train,
    cbcl_aggressive_mtbi_train
)

list.save(cbcl_list_mtbi_train,
          proc_path("cbcl_list_mtbi_train.rdata", date = TRUE))


# The outcome list should be an optional structure
outcome_list_mtbi_train <- generate_outcome_list(
    list(cbcl_nausea_mtbi_train, "cbcl_nausea", "ordinal"),
    list(cbcl_vomiting_mtbi_train, "cbcl_vomiting", "ordinal"),
    list(cbcl_dizzy_mtbi_train, "cbcl_dizzy", "ordinal"),
    list(cbcl_overtired_mtbi_train, "cbcl_overtired", "ordinal"),
    list(cbcl_sleeping_more_mtbi_train, "cbcl_sleeping_more", "ordinal"),
    list(cbcl_sleeping_less_mtbi_train, "cbcl_sleeping_less", "ordinal"),
    list(cbcl_depress_mtbi_train, "cbcl_depress", "ordinal"),
    list(cbcl_anxiety_mtbi_train, "cbcl_anxiety", "ordinal"),
    list(cbcl_attention_mtbi_train, "cbcl_attention", "ordinal"),
    list(cbcl_aggressive_mtbi_train, "cbcl_aggressive", "ordinal")
)

list.save(outcome_list_mtbi_train,
          proc_path("outcome_list_mtbi_train.rdata", date = TRUE))

cbcl_list_mtbi_full <- list(
    cbcl_nausea_mtbi_full,
    cbcl_vomiting_mtbi_full,
    cbcl_dizzy_mtbi_full,
    cbcl_overtired_mtbi_full,
    cbcl_sleeping_more_mtbi_full,
    cbcl_sleeping_less_mtbi_full,
    cbcl_depress_mtbi_full,
    cbcl_anxiety_mtbi_full,
    cbcl_attention_mtbi_full,
    cbcl_aggressive_mtbi_full
)

list.save(cbcl_list_mtbi_full,
          proc_path("cbcl_list_mtbi_full.rdata", date = TRUE))
```
