# Imputation, QCing, and CBCL thresholding

This script is used to:

1. Impute missing data for non-neuroimaging input variables
2. Remove neuroimaging data for participants who do not meet ABCD's QC
3. Threshold CBCL behaviour measures (raw scores into normal (0), borderline (1), and clinical (2))

1. Load in the extracted data
2. Assign train and test sets of the data

3. Within the training data:
    - Explore the percentage of missingness
    - Impute missing data

2. Remove subjects who are missing neuroimaging data - we are not going to impute that
4. sdfasd

The longitudinal analysis will ultimately involve checking to see if the subtypes found can predict change scores in CBCL or SDS measures.
Which means we'll also need longitudinal CBCL and SDS measures.


## Loading in data

```{r}

library(mice)
library(dplyr)
library(abcdutils)
library(readr)
library(purrr)
library(here)

# The path_maker function helps with managing and date stamping long paths. The
#  functions are just used here to help with reading and writing data. See
#  ?path_maker for more information.
input_path <- abcdutils::path_maker(here::here(paste0("data/abcd/inputs")))
raw_path <- abcdutils::path_maker(here::here(paste0("data/abcd/raw")))
core_path <- abcdutils::path_maker(here::here(paste0("data/abcd/core")))
misc_path <- abcdutils::path_maker(here::here(paste0("data/abcd/misc")))

# Baseline inputs
as_mtbi_mem_daze_0_0 <-
    read_csv(input_path("2023_09_19_as_mtbi_mem_daze_0_0.csv"))
as_mtbi_mechanism_0_0 <-
    read_csv(input_path("2023_09_19_as_mtbi_mechanism_0_0.csv"))
as_mtbi_loc_0_0 <-
    read_csv(input_path("2023_09_19_as_mtbi_loc_0_0.csv"))
d_pubertal_status_0_0 <-
    read_csv(input_path("2023_09_19_d_pubertal_status_0_0.csv"))
d_interview_age_0_0 <-
    read_csv(input_path("2023_09_19_d_interview_age_0_0.csv"))
d_mtbi_age_0_0 <-
    read_csv(input_path("2023_09_19_d_mtbi_age_0_0.csv"))
d_sex_0_0 <-
    read_csv(input_path("2023_09_19_d_sex_0_0.csv"))
d_gender_0_0 <-
    read_csv(input_path("2023_09_19_d_p_gender_0_0.csv"))
d_income_0_0 <-
    read_csv(input_path("2023_09_19_d_income_0_0.csv"))
d_race_0_0 <-
    read_csv(input_path("2023_09_19_d_race_0_0.csv"))
mh_headaches_0_0 <-
    read_csv(input_path("2023_09_19_mh_headaches_0_0.csv"))
mh_mtbi_count_0_0 <-
    read_csv(input_path("2023_09_19_mh_mtbi_count_0_0.csv"))
sm_subc_v_0_0 <-
    read_csv(input_path("2023_09_19_sm_subc_v_0_0.csv"))
sm_cort_t_0_0 <-
    read_csv(input_path("2023_09_19_sm_cort_t_0_0.csv"))
sm_cort_sa_0_0 <-
    read_csv(input_path("2023_09_19_sm_cort_sa_0_0.csv"))
dm_all_wmnd_0_0 <-
    read_csv(input_path("2023_09_19_dm_all_wmnd_0_0.csv"))
rm_gord_cor_0_0 <-
    read_csv(input_path("2023_09_19_rm_gord_cor_0_0.csv"))
rm_subc_cor_0_0 <-
    read_csv(input_path("2023_09_19_rm_subc_cor_0_0.csv"))
rm_gord_var_0_0 <-
    read_csv(input_path("2023_09_19_rm_gord_var_0_0.csv"))
rm_subc_var_0_0 <-
    read_csv(input_path("2023_09_19_rm_subc_var_0_0.csv"))
p_loneliness_0_0 <-
    read_csv(input_path("2023_09_19_p_loneliness_0_0.csv"))
p_screen_time_0_0 <-
    read_csv(input_path("2023_09_19_p_screen_time_0_0.csv"))
p_sports_0_0 <-
    read_csv(input_path("2023_09_19_p_sports_0_0.csv"))
p_exercise_0_0 <-
    read_csv(input_path("2023_09_19_p_exercise_0_0.csv"))
p_prosocial_0_0 <-
    read_csv(input_path("2023_09_19_p_prosocial_0_0.csv"))
p_family_function_0_0 <-
    read_csv(input_path("2023_09_19_p_family_function_0_0.csv"))
p_parent_psych_0_0 <-
    read_csv(input_path("2023_09_19_p_parent_psych_0_0.csv"))
cbcl_anxdep_ss_0_0 <- read_csv(
    input_path("2023_09_19_cbcl_anxdep_ss_0_0.csv")
)
cbcl_withdep_ss_0_0 <- read_csv(
    input_path("2023_09_19_cbcl_withdep_ss_0_0.csv")
)
cbcl_somatic_ss_0_0 <- read_csv(
    input_path("2023_09_19_cbcl_somatic_ss_0_0.csv")
)
cbcl_social_ss_0_0 <- read_csv(
    input_path("2023_09_19_cbcl_social_ss_0_0.csv")
)
cbcl_thought_ss_0_0 <- read_csv(
    input_path("2023_09_19_cbcl_thought_ss_0_0.csv")
)
cbcl_attention_ss_0_0 <- read_csv(
    input_path("2023_09_19_cbcl_attention_ss_0_0.csv")
)
cbcl_rulebreak_ss_0_0 <- read_csv(
    input_path("2023_09_19_cbcl_rulebreak_ss_0_0.csv")
)
cbcl_aggressive_ss_0_0 <- read_csv(
    input_path("2023_09_19_cbcl_aggressive_ss_0_0.csv")
)
sds_total_probs_0_0 <- read_csv(
    input_path("2023_09_19_sds_total_probs_0_0.csv")
)
nihtbx_list_fc_0_0 <- read_csv(
    input_path("2023_09_19_nihtbx_list_fc_0_0.csv")
)
nihtbx_pattern_fc_0_0 <- read_csv(
    input_path("2023_09_19_nihtbx_pattern_fc_0_0.csv")
)
nihtbx_cardsort_fc_0_0 <- read_csv(
    input_path("2023_09_19_nihtbx_cardsort_fc_0_0.csv")
)

```

## Neuroimaging quality control

First identify which subjects have valid neuroimaging data.

```{r eval = FALSE}

mri_y_qc_raw_smr_t1 <- abcd_load(core_path("imaging/mri_y_qc_raw_smr_t1.csv"))
mri_y_qc_raw_smr_t2 <- abcd_load(core_path("imaging/mri_y_qc_raw_smr_t2.csv"))
mri_y_qc_raw_rsfmr <- abcd_load(core_path("imaging/mri_y_qc_raw_rsfmr.csv"))
mri_y_qc_raw_dmr <- abcd_load(core_path("imaging/mri_y_qc_raw_dmr.csv"))

# Obtaining the QC'd subjects with complete neuroimaging data
rm_gord_cor_qc_0_0 <- abcdutils::qc_rsfmri(
    rm_gord_cor_0_0,
    mri_y_qc_raw_rsfmr,
    t = 0,
    no_na = TRUE
)
rm_gord_var_qc_0_0 <- abcdutils::qc_rsfmri(
    rm_gord_var_0_0,
    mri_y_qc_raw_rsfmr,
    t = 0,
    no_na = TRUE
)
rm_subc_cor_qc_0_0 <- abcdutils::qc_rsfmri(
    rm_subc_cor_0_0,
    mri_y_qc_raw_rsfmr,
    t = 0,
    no_na = TRUE
)
rm_subc_var_qc_0_0 <- abcdutils::qc_rsfmri(
    rm_subc_var_0_0,
    mri_y_qc_raw_rsfmr,
    t = 0,
    no_na = TRUE
)
dm_all_wmnd_qc_0_0 <- abcdutils::qc_dmri(
    dm_all_wmnd_0_0,
    mri_y_qc_raw_dmr,
    t = 0,
    no_na = TRUE
)
sm_cort_sa_qc_0_0 <- abcdutils::qc_smri(
    sm_cort_sa_0_0,
    mri_y_qc_raw_smr_t1,
    mri_y_qc_raw_smr_t2,
    t = 0,
    no_na = TRUE
)
sm_cort_t_qc_0_0 <- abcdutils::qc_smri(
    sm_cort_t_0_0,
    mri_y_qc_raw_smr_t1,
    mri_y_qc_raw_smr_t2,
    t = 0,
    no_na = TRUE
)
sm_subc_v_qc_0_0 <- abcdutils::qc_smri(
    sm_subc_v_0_0,
    mri_y_qc_raw_smr_t1,
    mri_y_qc_raw_smr_t2,
    t = 0,
    no_na = TRUE
)

write_csv(rm_gord_cor_qc_0_0, input_path("rm_gord_cor_qc_0_0.csv", TRUE))
write_csv(rm_gord_var_qc_0_0, input_path("rm_gord_var_qc_0_0.csv", TRUE))
write_csv(rm_subc_cor_qc_0_0, input_path("rm_subc_cor_qc_0_0.csv", TRUE))
write_csv(rm_subc_var_qc_0_0, input_path("rm_subc_var_qc_0_0.csv", TRUE))
write_csv(dm_all_wmnd_qc_0_0, input_path("dm_all_wmnd_qc_0_0.csv", TRUE))
write_csv(sm_cort_sa_qc_0_0, input_path("sm_cort_sa_qc_0_0.csv", TRUE))
write_csv(sm_cort_t_qc_0_0, input_path("sm_cort_t_qc_0_0.csv", TRUE))
write_csv(sm_subc_v_qc_0_0, input_path("sm_subc_v_qc_0_0.csv", TRUE))

rm_gord_cor_qc_0_0 <- read_csv(input_path("2023_09_18_rm_gord_cor_qc_0_0.csv"))
rm_gord_var_qc_0_0 <- read_csv(input_path("2023_09_18_rm_gord_var_qc_0_0.csv"))
rm_subc_cor_qc_0_0 <- read_csv(input_path("2023_09_18_rm_subc_cor_qc_0_0.csv"))
rm_subc_var_qc_0_0 <- read_csv(input_path("2023_09_18_rm_subc_var_qc_0_0.csv"))
dm_all_wmnd_qc_0_0 <- read_csv(input_path("2023_09_18_dm_all_wmnd_qc_0_0.csv"))
sm_cort_sa_qc_0_0 <- read_csv(input_path("2023_09_18_sm_cort_sa_qc_0_0.csv"))
sm_cort_t_qc_0_0 <- read_csv(input_path("2023_09_18_sm_cort_t_qc_0_0.csv"))
sm_subc_v_qc_0_0 <- read_csv(input_path("2023_09_18_sm_subc_v_qc_0_0.csv"))

```

# Assigning train and test splits

To avoid having training and testing data inform each other during imputation, we assign the splits prior to the imputation.

```{r}



```




# Imputing missing data

SNF requires complete data as input for integration.

We face a few oddities that may impact the validity of using a multiple imputation approach:

Neuroimaging data, which accounts for the majority of the individual features, are either completely removed or completely present for most subjects.
We proceed by not including those subjects who are missing neuroimaging data or who have neuroimaging data that did not pass checks for quality control.

Though this work is an exploratory clustering analysis that is designed to reveal insights about patterns across all variables, the experimental design used focuses on those insights particular relevant to better understanding behavioural impairments following concussion.
Our post-concussion assessments of behavioural impairment come from the CBCL and SDS.
CBCL data, which comprises a wide set of features, is either completely missing or completely present.

```{r}

full_baseline_df_list <- list(
    as_mtbi_mem_daze_0_0,
    as_mtbi_mechanism_0_0,
    as_mtbi_loc_0_0,
    d_pubertal_status_0_0,
    d_interview_age_0_0,
    d_mtbi_age_0_0,
    d_sex_0_0,
    d_gender_0_0,
    d_income_0_0,
    d_race_0_0,
    mh_headaches_0_0,
    mh_mtbi_count_0_0,
    sm_subc_v_qc_0_0,
    sm_cort_t_qc_0_0,
    sm_cort_sa_qc_0_0,
    dm_all_wmnd_qc_0_0,
    rm_gord_cor_qc_0_0,
    rm_subc_cor_qc_0_0,
    rm_gord_var_qc_0_0,
    rm_subc_var_qc_0_0,
    p_loneliness_0_0,
    p_screen_time_0_0,
    p_sports_0_0,
    p_exercise_0_0,
    p_prosocial_0_0,
    p_family_function_0_0,
    p_parent_psych_0_0,
    cbcl_anxdep_ss_0_0,
    cbcl_withdep_ss_0_0,
    cbcl_somatic_ss_0_0,
    cbcl_social_ss_0_0,
    cbcl_thought_ss_0_0,
    cbcl_attention_ss_0_0,
    cbcl_rulebreak_ss_0_0,
    cbcl_aggressive_ss_0_0,
    sds_total_probs_0_0,
    nihtbx_list_fc_0_0,
    nihtbx_pattern_fc_0_0,
    nihtbx_cardsort_fc_0_0
)

full_baseline_df <- abcdutils::merge_df_list(
    full_baseline_df_list,
    join = "full"
)

no_imaging_baseline_df_list <- list(
    as_mtbi_mem_daze_0_0,
    as_mtbi_mechanism_0_0,
    as_mtbi_loc_0_0,
    d_pubertal_status_0_0,
    d_interview_age_0_0,
    d_mtbi_age_0_0,
    d_sex_0_0,
    d_gender_0_0,
    d_income_0_0,
    d_race_0_0,
    mh_headaches_0_0,
    mh_mtbi_count_0_0,
    p_loneliness_0_0,
    p_screen_time_0_0,
    p_sports_0_0,
    p_exercise_0_0,
    p_prosocial_0_0,
    p_family_function_0_0,
    p_parent_psych_0_0,
    cbcl_anxdep_ss_0_0,
    cbcl_withdep_ss_0_0,
    cbcl_somatic_ss_0_0,
    cbcl_social_ss_0_0,
    cbcl_thought_ss_0_0,
    cbcl_attention_ss_0_0,
    cbcl_rulebreak_ss_0_0,
    cbcl_aggressive_ss_0_0,
    sds_total_probs_0_0,
    nihtbx_list_fc_0_0,
    nihtbx_pattern_fc_0_0,
    nihtbx_cardsort_fc_0_0
)

no_imaging_baseline_df <- abcdutils::merge_df_list(
    no_imaging_baseline_df_list,
    join = "full"
)


colnames(no_imaging_baseline_df)[colSums(is.na(no_imaging_baseline_df)) > 0]

na.omit(no_imaging_baseline_df)


na.omit(no_imaging_baseline_df)

imaging_baseline_df_list <- list(
    sm_subc_v_qc_0_0,
    sm_cort_t_qc_0_0,
    sm_cort_sa_qc_0_0,
    dm_all_wmnd_qc_0_0,
    rm_gord_cor_qc_0_0,
    rm_subc_cor_qc_0_0,
    rm_gord_var_qc_0_0,
    rm_subc_var_qc_0_0,
    cbcl_anxdep_ss_0_0,
    cbcl_withdep_ss_0_0,
    cbcl_somatic_ss_0_0,
    cbcl_social_ss_0_0,
    cbcl_thought_ss_0_0,
    cbcl_attention_ss_0_0,
    cbcl_rulebreak_ss_0_0,
    cbcl_aggressive_ss_0_0,
    sds_total_probs_0_0,
    nihtbx_cardsort_fc_0_0
)
#
imaging_baseline_df <- abcdutils::merge_df_list(
    imaging_baseline_df_list,
    join = "full"
)
# 362 subjects have complete imaging data post-QC
na.omit(imaging_baseline_df)




# Size of baseline data:
dim(full_baseline_df) # 440 * 1435





# Create and format a dataframe that stores the number of missing entries for
#  each feature
missing_baseline_df <- data.frame(colSums(is.na(full_baseline_df)))
missing_baseline_df$"feature" <- rownames(missing_baseline_df)
missing_baseline_df <- missing_baseline_df[, c(2, 1)]
colnames(missing_baseline_df) <- c("feature", "missing")
rownames(missing_baseline_df) <- NULL

head(missing_baseline_df)

number_of_cols_missing_data <- missing_baseline_df |>
    dplyr::filter(missing > 0) |>
    nrow()

number_of_cols_missing_data # 1377

hist(missing_baseline_df$missing)

# Create and format a dataframe that stores the number of missing entries for
#  each subject
hist(rowSums(is.na(full_baseline_df)))

```



## Imputing missing data

Here, I only impute the non-neuroimaging data.

Code is based on Eman's imputation script.
Thanks Eman!

While this choice was made largely for the sake of time, it was also partially because imputing neuroimaging data doesn't seem to be a common practice.

Imputation notes:

1. I'm imputing prior to train/test split (limits generalizability)
2. I'm imputing uninjured controls with the injured group

```{r eval = FALSE}

## put all data frames into a named list
#df_list_no_neuroimaging_0_0 <- list(
#    "loss of consciousness" = as_mtbi_loc_0_0,
#    "mechanism of injury" = as_mtbi_mechanism_0_0,
#    "memory loss / dazed" = as_mtbi_mem_daze_0_0,
#    "income" = d_income_0_0,
#    "interview_age" = d_interview_age_0_0,
#    "mtbi_age" = d_mtbi_age_0_0,
#    "pubertal_status" = d_pubertal_status_0_0,
#    "race" = d_race_0_0,
#    "sex" = d_sex_0_0,
#    "headaches" = mh_headaches_0_0,
#    "mtbi_count" = mh_mtbi_count_0_0,
#    "loneliness" = p_loneliness_0_0,
#    "screen time" = p_screen_time_0_0,
#    "family function" = p_family_function_0_0,
#    "sports" = p_sports_0_0,
#    "prosocial" = p_prosocial_0_0,
#    "parent psych" = p_parent_psych_0_0,
#    "exercise" = p_exercise_0_0,
#    "nihtbx list fc" = nihtbx_list_fc_0_0,
#    "nihtbx pattern fc" = nihtbx_pattern_fc_0_0,
#    "nihtbx cardsort fc" = nihtbx_cardsort_fc_0_0
#)
#
#a <- abcdutils::vis_missing_by_df(full_baseline_df_list)[[1]]
#
#a + ggplot2::theme(text = ggplot2::element_text(size=20))
#
## Visualize missing data
#abcdutils::vis_missing_by_df(df_list_no_neuroimaging_0_0)
#
#full_df_0_0 <- df_list_no_neuroimaging_0_0 |>
#    purrr::reduce(dplyr::full_join, by = "subjectkey")
#
#dim(full_df_0_0)
## 440 subjects
#
#dim(na.omit(full_df_0_0))
## 368 subjects with complete non-neuroimaging data
#
## Not imputing the neuroimaging data
#neuroimaging_df <- abcdutils::merge_df_list(list(rm_gord_cor_qc_0_0,
#    rm_gord_var_qc_0_0,
#    rm_subc_cor_qc_0_0,
#    rm_subc_var_qc_0_0,
#    dm_all_wmnd_qc_0_0,
#    sm_cort_sa_qc_0_0,
#    sm_cort_t_qc_0_0,
#    sm_subc_v_qc_0_0,
#    full_df_0_0))
#na.omit(neuroimaging_df)
## Only 308 children remain if missing data is excluded
#
## Excluding NIHTBX out-of-model measure
#full_df_0_0_no_nihtbx <- full_df_0_0 |>
#    dplyr::select(-dplyr::starts_with("nih"))
#
#no_imputation_no_nihtbx <- abcdutils::merge_df_list(list(rm_gord_cor_qc_0_0,
#    rm_gord_var_qc_0_0,
#    rm_subc_cor_qc_0_0,
#    rm_subc_var_qc_0_0,
#    dm_all_wmnd_qc_0_0,
#    sm_cort_sa_qc_0_0,
#    sm_cort_t_qc_0_0,
#    sm_subc_v_qc_0_0,
#    full_df_0_0_no_nihtbx))
#na.omit(no_imputation_no_nihtbx)
# 321 children - still many are lost

# Columns with missing data

(missing_data_colnames <- names(which(colSums(is.na(full_df_0_0)) > 0)))

# Missing:
# mem/daze,
# household_income,
# pubertal_status,
# race,
# screentime,
# exercise,
# nihtbx measures

# Throwing in the following variables to assist with imputation:
#   M (sex), latest_mtbi_loc, latest_mtbi_mechanism, mtbi_count
missing_data_cols <- full_df_0_0[, c(missing_data_colnames,
                                     "sex",
                                     "latest_mtbi_mechanism",
                                     "latest_mtbi_loc",
                                     "mtbi_count")]

# Only treat race and latest_mtbi_mechanism as factors
missing_data_cols$race <- as.factor(missing_data_cols$race)
missing_data_cols$latest_mtbi_mechanism <-
    as.factor(missing_data_cols$latest_mtbi_mechanism)
missing_data_cols$household_income <-
    as.numeric(missing_data_cols$household_income)

str(missing_data_cols)

imputed_0_0 <- mice(missing_data_cols, m = 20, maxit = 10, seed = 42)

# Isolate the imputed data
complete_imputed_0_0 <- cbind(subjectkey = full_df_0_0$"subjectkey",
                              complete(imputed_0_0))

# The features that were missing data
missing_data_colnames

as_mtbi_mem_daze_imp_0_0 <- complete_imputed_0_0 |>
    dplyr::select("subjectkey", "latest_mtbi_mem_daze")
d_income_imp_0_0 <- complete_imputed_0_0 |>
    dplyr::select("subjectkey", "household_income")
d_pubertal_status_imp_0_0 <- complete_imputed_0_0 |>
    dplyr::select("subjectkey", "pubertal_status")
d_race_imp_0_0 <- complete_imputed_0_0 |>
    dplyr::select("subjectkey", "race")
p_screen_time_imp_0_0 <- complete_imputed_0_0 |>
    dplyr::select("subjectkey", dplyr::contains("screentime"))
p_exercise_imp_0_0 <- complete_imputed_0_0 |>
    dplyr::select("subjectkey", "physical_activity")
nihtbx_list_fc_imp_0_0 <- complete_imputed_0_0 |>
    dplyr::select("subjectkey", "nihtbx_list_fc")
nihtbx_pattern_fc_imp_0_0 <- complete_imputed_0_0 |>
    dplyr::select("subjectkey", "nihtbx_pattern_fc")
nihtbx_cardsort_fc_imp_0_0 <- complete_imputed_0_0 |>
    dplyr::select("subjectkey", "nihtbx_cardsort_fc")

# Features that had no NAs to begin with
as_mtbi_loc_imp_0_0 <- as_mtbi_loc_0_0
as_mtbi_mechanism_imp_0_0 <- as_mtbi_mechanism_0_0
d_interview_age_imp_0_0 <- d_interview_age_0_0
d_mtbi_age_imp_0_0 <- d_mtbi_age_0_0
d_sex_imp_0_0 <- d_sex_0_0
mh_headaches_imp_0_0 <- mh_headaches_0_0
mh_mtbi_count_imp_0_0 <- mh_mtbi_count_0_0
p_loneliness_imp_0_0 <- p_loneliness_0_0
p_family_function_imp_0_0 <- p_family_function_0_0
p_sports_imp_0_0 <- p_sports_0_0
p_prosocial_imp_0_0 <- p_prosocial_0_0
p_parent_psych_imp_0_0 <- p_parent_psych_0_0
cbcl_headaches_imp_0_0 <- cbcl_headaches_0_0
cbcl_nausea_imp_0_0 <- cbcl_nausea_0_0
cbcl_vomiting_imp_0_0 <- cbcl_vomiting_0_0
cbcl_dizzy_imp_0_0 <- cbcl_dizzy_0_0
cbcl_overtired_imp_0_0 <- cbcl_overtired_0_0
cbcl_sleeping_more_imp_0_0 <- cbcl_sleeping_more_0_0
cbcl_sleeping_less_imp_0_0 <- cbcl_sleeping_less_0_0
cbcl_depress_r_imp_0_0 <- cbcl_depress_r_0_0
cbcl_anxiety_r_imp_0_0 <- cbcl_anxiety_r_0_0
cbcl_attention_r_imp_0_0 <- cbcl_attention_r_0_0
cbcl_aggressive_r_imp_0_0 <- cbcl_aggressive_r_0_0
sds_sleep_imp_0_0 <- sds_sleep_0_0


# Visualize missing data post-imputation
df_list_no_neuroimaging_post_imp_0_0 <- list(
    "loss of consciousness" = as_mtbi_loc_0_0,
    "mechanism of injury" = as_mtbi_mechanism_0_0,
    "memory loss / dazed" = as_mtbi_mem_daze_imp_0_0,
    "income" = d_income_imp_0_0,
    "interview_age" = d_interview_age_0_0,
    "mtbi_age" = d_mtbi_age_0_0,
    "pubertal_status" = d_pubertal_status_imp_0_0,
    "race" = d_race_imp_0_0,
    "sex" = d_sex_0_0,
    "headaches" = mh_headaches_0_0,
    "mtbi_count" = mh_mtbi_count_0_0,
    "loneliness" = p_loneliness_0_0,
    "screen time" = p_screen_time_imp_0_0,
    "family function" = p_family_function_0_0,
    "sports" = p_sports_0_0,
    "prosocial" = p_prosocial_0_0,
    "parent psych" = p_parent_psych_0_0,
    "exercise" = p_exercise_imp_0_0,
    "cbcl headaches" = cbcl_headaches_0_0,
    "cbcl nausea" = cbcl_nausea_0_0,
    "cbcl vomiting" = cbcl_vomiting_0_0,
    "cbcl dizzy" = cbcl_dizzy_0_0,
    "cbcl overtired" = cbcl_overtired_0_0,
    "cbcl sleeping more" = cbcl_sleeping_more_0_0,
    "cbcl sleeping less" = cbcl_sleeping_less_0_0,
    "cbcl depress r" = cbcl_depress_r_0_0,
    "cbcl anxiety r" = cbcl_anxiety_r_0_0,
    "cbcl attention r" = cbcl_attention_r_0_0,
    "cbcl aggressive r" = cbcl_aggressive_r_0_0,
    "sds sleep" = sds_sleep_0_0,
    "nihtbx list fc" = nihtbx_list_fc_imp_0_0,
    "nihtbx pattern fc" = nihtbx_pattern_fc_imp_0_0,
    "nihtbx cardsort fc" = nihtbx_cardsort_fc_imp_0_0
)
vis_missing_by_df(df_list_no_neuroimaging_post_imp_0_0)


# Export imputed results
write_csv(as_mtbi_loc_imp_0_0,
    input_path("as_mtbi_loc_imp_0_0.csv", date = TRUE))
write_csv(as_mtbi_mechanism_imp_0_0,
    input_path("as_mtbi_mechanism_imp_0_0.csv", date = TRUE))
write_csv(as_mtbi_mem_daze_imp_0_0,
    input_path("as_mtbi_mem_daze_imp_0_0.csv", date = TRUE))
write_csv(d_income_imp_0_0,
    input_path("d_income_imp_0_0.csv", date = TRUE))
write_csv(d_interview_age_imp_0_0,
    input_path("d_interview_age_imp_0_0.csv", date = TRUE))
write_csv(d_mtbi_age_imp_0_0,
    input_path("d_mtbi_age_imp_0_0.csv", date = TRUE))
write_csv(d_pubertal_status_imp_0_0,
    input_path("d_pubertal_status_imp_0_0.csv", date = TRUE))
write_csv(d_race_imp_0_0,
    input_path("d_race_imp_0_0.csv", date = TRUE))
write_csv(d_sex_imp_0_0,
    input_path("d_sex_imp_0_0.csv", date = TRUE))
write_csv(mh_headaches_imp_0_0,
    input_path("mh_headaches_imp_0_0.csv", date = TRUE))
write_csv(mh_mtbi_count_imp_0_0,
    input_path("mh_mtbi_count_imp_0_0.csv", date = TRUE))
write_csv(p_loneliness_imp_0_0,
    input_path("p_loneliness_imp_0_0.csv", date = TRUE))
write_csv(p_screen_time_imp_0_0,
    input_path("p_screen_time_imp_0_0.csv", date = TRUE))
write_csv(p_family_function_imp_0_0,
    input_path("p_family_function_imp_0_0.csv", date = TRUE))
write_csv(p_sports_imp_0_0,
    input_path("p_sports_imp_0_0.csv", date = TRUE))
write_csv(p_prosocial_imp_0_0,
    input_path("p_prosocial_imp_0_0.csv", date = TRUE))
write_csv(p_parent_psych_imp_0_0,
    input_path("p_parent_psych_imp_0_0.csv", date = TRUE))
write_csv(p_exercise_imp_0_0,
    input_path("p_exercise_imp_0_0.csv", date = TRUE))
write_csv(cbcl_headaches_imp_0_0,
    input_path("cbcl_headaches_imp_0_0.csv", date = TRUE))
write_csv(cbcl_nausea_imp_0_0,
    input_path("cbcl_nausea_imp_0_0.csv", date = TRUE))
write_csv(cbcl_vomiting_imp_0_0,
    input_path("cbcl_vomiting_imp_0_0.csv", date = TRUE))
write_csv(cbcl_dizzy_imp_0_0,
    input_path("cbcl_dizzy_imp_0_0.csv", date = TRUE))
write_csv(cbcl_overtired_imp_0_0,
    input_path("cbcl_overtired_imp_0_0.csv", date = TRUE))
write_csv(cbcl_sleeping_more_imp_0_0,
    input_path("cbcl_sleeping_more_imp_0_0.csv", date = TRUE))
write_csv(cbcl_sleeping_less_imp_0_0,
    input_path("cbcl_sleeping_less_imp_0_0.csv", date = TRUE))
write_csv(cbcl_depress_r_imp_0_0,
    input_path("cbcl_depress_r_imp_0_0.csv", date = TRUE))
write_csv(cbcl_anxiety_r_imp_0_0,
    input_path("cbcl_anxiety_r_imp_0_0.csv", date = TRUE))
write_csv(cbcl_attention_r_imp_0_0,
    input_path("cbcl_attention_r_imp_0_0.csv", date = TRUE))
write_csv(cbcl_aggressive_r_imp_0_0,
    input_path("cbcl_aggressive_r_imp_0_0.csv", date = TRUE))
write_csv(sds_sleep_imp_0_0,
    input_path("sds_sleep_imp_0_0.csv", date = TRUE))
write_csv(nihtbx_list_fc_imp_0_0,
    input_path("nihtbx_list_fc_imp_0_0.csv", date = TRUE))
write_csv(nihtbx_pattern_fc_imp_0_0,
    input_path("nihtbx_pattern_fc_imp_0_0.csv", date = TRUE))
write_csv(nihtbx_cardsort_fc_imp_0_0,
    input_path("nihtbx_cardsort_fc_imp_0_0.csv", date = TRUE))

```

## Convert the raw CBCL scores into thresholded ones

```{r}
cbcl_depress_r_imp_0_0 <-
    read_csv(input_path("2023_07_17_cbcl_depress_r_imp_0_0.csv"))
cbcl_anxiety_r_imp_0_0 <-
    read_csv(input_path("2023_07_17_cbcl_anxiety_r_imp_0_0.csv"))
cbcl_attention_r_imp_0_0 <-
    read_csv(input_path("2023_07_17_cbcl_attention_r_imp_0_0.csv"))
cbcl_aggressive_r_imp_0_0 <-
    read_csv(input_path("2023_07_17_cbcl_aggressive_r_imp_0_0.csv"))

cbcl_depress_imp_0_0 <-
    abcdutils::cbcl_raw_to_thresh(cbcl_depress_r_imp_0_0)
cbcl_anxiety_imp_0_0 <-
    abcdutils::cbcl_raw_to_thresh(cbcl_anxiety_r_imp_0_0)
cbcl_attention_imp_0_0 <-
    abcdutils::cbcl_raw_to_thresh(cbcl_attention_r_imp_0_0)
cbcl_aggressive_imp_0_0 <-
    abcdutils::cbcl_raw_to_thresh(cbcl_aggressive_r_imp_0_0)

write_csv(cbcl_depress_imp_0_0,
    input_path("cbcl_depress_imp_0_0.csv", date = TRUE))
write_csv(cbcl_anxiety_imp_0_0,
    input_path("cbcl_anxiety_imp_0_0.csv", date = TRUE))
write_csv(cbcl_attention_imp_0_0,
    input_path("cbcl_attention_imp_0_0.csv", date = TRUE))
write_csv(cbcl_aggressive_imp_0_0,
    input_path("cbcl_aggressive_imp_0_0.csv", date = TRUE))
```


## Training and testing data splits

```{r eval = FALSE}
library(abcdutils)
library(readr)
library(here)


# Functions to import data from carbon
input_path <- abcdutils::path_maker(here(paste0("data/abcd/inputs")))
proc_path <- abcdutils::path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- abcdutils::path_maker(here(paste0("data/abcd/results/figures")))


# Importing data
as_mtbi_loc_0_0 <-
    read_csv(input_path("2023_07_17_as_mtbi_loc_imp_0_0.csv"))
as_mtbi_mechanism_0_0 <-
    read_csv(input_path("2023_07_17_as_mtbi_mechanism_imp_0_0.csv"))
as_mtbi_mem_daze_0_0 <-
    read_csv(input_path("2023_07_17_as_mtbi_mem_daze_imp_0_0.csv"))
d_income_0_0 <-
    read_csv(input_path("2023_07_17_d_income_imp_0_0.csv"))
d_interview_age_0_0 <-
    read_csv(input_path("2023_07_17_d_interview_age_imp_0_0.csv"))
d_mtbi_age_0_0 <-
    read_csv(input_path("2023_07_17_d_mtbi_age_imp_0_0.csv"))
d_pubertal_status_0_0 <-
    read_csv(input_path("2023_07_17_d_pubertal_status_imp_0_0.csv"))
d_race_0_0 <-
    read_csv(input_path("2023_07_17_d_race_imp_0_0.csv"))
d_sex_0_0 <-
    read_csv(input_path("2023_07_17_d_sex_imp_0_0.csv"))
mh_headaches_0_0 <-
    read_csv(input_path("2023_07_17_mh_headaches_imp_0_0.csv"))
mh_mtbi_count_0_0 <-
    read_csv(input_path("2023_07_17_mh_mtbi_count_imp_0_0.csv"))
dm_all_wmnd_0_0 <-
    read_csv(input_path("2023_07_17_dm_all_wmnd_qc_0_0.csv"))
rm_gord_cor_0_0 <-
    read_csv(input_path("2023_07_17_rm_gord_cor_qc_0_0.csv"))
rm_gord_var_0_0 <-
    read_csv(input_path("2023_07_17_rm_gord_var_qc_0_0.csv"))
rm_subc_cor_0_0 <-
    read_csv(input_path("2023_07_17_rm_subc_cor_qc_0_0.csv"))
rm_subc_var_0_0 <-
    read_csv(input_path("2023_07_17_rm_subc_var_qc_0_0.csv"))
sm_cort_sa_0_0 <-
    read_csv(input_path("2023_07_17_sm_cort_sa_qc_0_0.csv"))
sm_cort_t_0_0 <-
    read_csv(input_path("2023_07_17_sm_cort_t_qc_0_0.csv"))
sm_subc_v_0_0 <-
    read_csv(input_path("2023_07_17_sm_subc_v_qc_0_0.csv"))
p_loneliness_0_0 <-
    read_csv(input_path("2023_07_17_p_loneliness_imp_0_0.csv"))
p_screen_time_0_0 <-
    read_csv(input_path("2023_07_17_p_screen_time_imp_0_0.csv"))
p_family_function_0_0 <-
    read_csv(input_path("2023_07_17_p_family_function_imp_0_0.csv"))
p_sports_0_0 <-
    read_csv(input_path("2023_07_17_p_sports_imp_0_0.csv"))
p_prosocial_0_0 <-
    read_csv(input_path("2023_07_17_p_prosocial_imp_0_0.csv"))
p_parent_psych_0_0 <-
    read_csv(input_path("2023_07_17_p_parent_psych_imp_0_0.csv"))
p_exercise_0_0 <-
    read_csv(input_path("2023_07_17_p_exercise_imp_0_0.csv"))
cbcl_headaches_0_0 <-
    read_csv(input_path("2023_07_17_cbcl_headaches_imp_0_0.csv"))
cbcl_nausea_0_0 <-
    read_csv(input_path("2023_07_17_cbcl_nausea_imp_0_0.csv"))
cbcl_vomiting_0_0 <-
    read_csv(input_path("2023_07_17_cbcl_vomiting_imp_0_0.csv"))
cbcl_dizzy_0_0 <-
    read_csv(input_path("2023_07_17_cbcl_dizzy_imp_0_0.csv"))
cbcl_overtired_0_0 <-
    read_csv(input_path("2023_07_17_cbcl_overtired_imp_0_0.csv"))
cbcl_sleeping_more_0_0 <-
    read_csv(input_path("2023_07_17_cbcl_sleeping_more_imp_0_0.csv"))
cbcl_sleeping_less_0_0 <-
    read_csv(input_path("2023_07_17_cbcl_sleeping_less_imp_0_0.csv"))
cbcl_depress_0_0 <-
    read_csv(input_path("2023_07_17_cbcl_depress_imp_0_0.csv"))
cbcl_anxiety_0_0 <-
    read_csv(input_path("2023_07_17_cbcl_anxiety_imp_0_0.csv"))
cbcl_attention_0_0 <-
    read_csv(input_path("2023_07_17_cbcl_attention_imp_0_0.csv"))
cbcl_aggressive_0_0 <-
    read_csv(input_path("2023_07_17_cbcl_aggressive_imp_0_0.csv"))
sds_sleep_0_0 <-
    read_csv(input_path("2023_07_17_sds_sleep_imp_0_0.csv"))
nihtbx_list_fc_0_0 <-
    read_csv(input_path("2023_07_17_nihtbx_list_fc_imp_0_0.csv"))
nihtbx_pattern_fc_0_0 <-
    read_csv(input_path("2023_07_17_nihtbx_pattern_fc_imp_0_0.csv"))
nihtbx_cardsort_fc_0_0 <-
    read_csv(input_path("2023_07_17_nihtbx_cardsort_fc_imp_0_0.csv"))


# Filtering to common subjects
common_subs <- common_subjects(list(
    as_mtbi_loc_0_0,
    as_mtbi_mechanism_0_0,
    as_mtbi_mem_daze_0_0,
    d_income_0_0,
    d_interview_age_0_0,
    d_mtbi_age_0_0,
    d_pubertal_status_0_0,
    d_race_0_0,
    d_sex_0_0,
    mh_headaches_0_0,
    mh_mtbi_count_0_0,
    dm_all_wmnd_0_0,
    rm_gord_cor_0_0,
    rm_gord_var_0_0,
    rm_subc_cor_0_0,
    rm_subc_var_0_0,
    sm_cort_sa_0_0,
    sm_cort_t_0_0,
    sm_subc_v_0_0,
    p_loneliness_0_0,
    p_screen_time_0_0,
    p_family_function_0_0,
    p_sports_0_0,
    p_prosocial_0_0,
    p_parent_psych_0_0,
    p_exercise_0_0,
    cbcl_headaches_0_0,
    cbcl_nausea_0_0,
    cbcl_vomiting_0_0,
    cbcl_dizzy_0_0,
    cbcl_overtired_0_0,
    cbcl_sleeping_more_0_0,
    cbcl_sleeping_less_0_0,
    cbcl_depress_0_0,
    cbcl_anxiety_0_0,
    cbcl_attention_0_0,
    cbcl_aggressive_0_0,
    sds_sleep_0_0))

# Assigning common subjects into training and testing sets
assigned_df_0 <- train_test_assign(train_frac = 0.8, subjects = common_subs)

# Generate training set
as_mtbi_loc_0_0_train <-
    keep_split(as_mtbi_loc_0_0, assigned_df_0, "train")
as_mtbi_mechanism_0_0_train <-
    keep_split(as_mtbi_mechanism_0_0, assigned_df_0, "train")
as_mtbi_mem_daze_0_0_train <-
    keep_split(as_mtbi_mem_daze_0_0, assigned_df_0, "train")
d_income_0_0_train <-
    keep_split(d_income_0_0, assigned_df_0, "train")
d_interview_age_0_0_train <-
    keep_split(d_interview_age_0_0, assigned_df_0, "train")
d_mtbi_age_0_0_train <-
    keep_split(d_mtbi_age_0_0, assigned_df_0, "train")
d_pubertal_status_0_0_train <-
    keep_split(d_pubertal_status_0_0, assigned_df_0, "train")
d_race_0_0_train <-
    keep_split(d_race_0_0, assigned_df_0, "train")
d_sex_0_0_train <-
    keep_split(d_sex_0_0, assigned_df_0, "train")
mh_headaches_0_0_train <-
    keep_split(mh_headaches_0_0, assigned_df_0, "train")
mh_mtbi_count_0_0_train <-
    keep_split(mh_mtbi_count_0_0, assigned_df_0, "train")
dm_all_wmnd_0_0_train <-
    keep_split(dm_all_wmnd_0_0, assigned_df_0, "train")
rm_gord_cor_0_0_train <-
    keep_split(rm_gord_cor_0_0, assigned_df_0, "train")
rm_gord_var_0_0_train <-
    keep_split(rm_gord_var_0_0, assigned_df_0, "train")
rm_subc_cor_0_0_train <-
    keep_split(rm_subc_cor_0_0, assigned_df_0, "train")
rm_subc_var_0_0_train <-
    keep_split(rm_subc_var_0_0, assigned_df_0, "train")
sm_cort_sa_0_0_train <-
    keep_split(sm_cort_sa_0_0, assigned_df_0, "train")
sm_cort_t_0_0_train <-
    keep_split(sm_cort_t_0_0, assigned_df_0, "train")
sm_subc_v_0_0_train <-
    keep_split(sm_subc_v_0_0, assigned_df_0, "train")
p_loneliness_0_0_train <-
    keep_split(p_loneliness_0_0, assigned_df_0, "train")
p_screen_time_0_0_train <-
    keep_split(p_screen_time_0_0, assigned_df_0, "train")
p_family_function_0_0_train <-
    keep_split(p_family_function_0_0, assigned_df_0, "train")
p_sports_0_0_train <-
    keep_split(p_sports_0_0, assigned_df_0, "train")
p_prosocial_0_0_train <-
    keep_split(p_prosocial_0_0, assigned_df_0, "train")
p_parent_psych_0_0_train <-
    keep_split(p_parent_psych_0_0, assigned_df_0, "train")
p_exercise_0_0_train <-
    keep_split(p_exercise_0_0, assigned_df_0, "train")
cbcl_headaches_0_0_train <-
    keep_split(cbcl_headaches_0_0, assigned_df_0, "train")
cbcl_nausea_0_0_train <-
    keep_split(cbcl_nausea_0_0, assigned_df_0, "train")
cbcl_vomiting_0_0_train <-
    keep_split(cbcl_vomiting_0_0, assigned_df_0, "train")
cbcl_dizzy_0_0_train <-
    keep_split(cbcl_dizzy_0_0, assigned_df_0, "train")
cbcl_overtired_0_0_train <-
    keep_split(cbcl_overtired_0_0, assigned_df_0, "train")
cbcl_sleeping_more_0_0_train <-
    keep_split(cbcl_sleeping_more_0_0, assigned_df_0, "train")
cbcl_sleeping_less_0_0_train <-
    keep_split(cbcl_sleeping_less_0_0, assigned_df_0, "train")
cbcl_depress_0_0_train <-
    keep_split(cbcl_depress_0_0, assigned_df_0, "train")
cbcl_anxiety_0_0_train <-
    keep_split(cbcl_anxiety_0_0, assigned_df_0, "train")
cbcl_attention_0_0_train <-
    keep_split(cbcl_attention_0_0, assigned_df_0, "train")
cbcl_aggressive_0_0_train <-
    keep_split(cbcl_aggressive_0_0, assigned_df_0, "train")
sds_sleep_0_0_train <-
    keep_split(sds_sleep_0_0, assigned_df_0, "train")

# Generate testing set
as_mtbi_loc_0_0_test <-
    keep_split(as_mtbi_loc_0_0, assigned_df_0, "test")
as_mtbi_mechanism_0_0_test <-
    keep_split(as_mtbi_mechanism_0_0, assigned_df_0, "test")
as_mtbi_mem_daze_0_0_test <-
    keep_split(as_mtbi_mem_daze_0_0, assigned_df_0, "test")
d_income_0_0_test <-
    keep_split(d_income_0_0, assigned_df_0, "test")
d_interview_age_0_0_test <-
    keep_split(d_interview_age_0_0, assigned_df_0, "test")
d_mtbi_age_0_0_test <-
    keep_split(d_mtbi_age_0_0, assigned_df_0, "test")
d_pubertal_status_0_0_test <-
    keep_split(d_pubertal_status_0_0, assigned_df_0, "test")
d_race_0_0_test <-
    keep_split(d_race_0_0, assigned_df_0, "test")
d_sex_0_0_test <-
    keep_split(d_sex_0_0, assigned_df_0, "test")
mh_headaches_0_0_test <-
    keep_split(mh_headaches_0_0, assigned_df_0, "test")
mh_mtbi_count_0_0_test <-
    keep_split(mh_mtbi_count_0_0, assigned_df_0, "test")
dm_all_wmnd_0_0_test <-
    keep_split(dm_all_wmnd_0_0, assigned_df_0, "test")
rm_gord_cor_0_0_test <-
    keep_split(rm_gord_cor_0_0, assigned_df_0, "test")
rm_gord_var_0_0_test <-
    keep_split(rm_gord_var_0_0, assigned_df_0, "test")
rm_subc_cor_0_0_test <-
    keep_split(rm_subc_cor_0_0, assigned_df_0, "test")
rm_subc_var_0_0_test <-
    keep_split(rm_subc_var_0_0, assigned_df_0, "test")
sm_cort_sa_0_0_test <-
    keep_split(sm_cort_sa_0_0, assigned_df_0, "test")
sm_cort_t_0_0_test <-
    keep_split(sm_cort_t_0_0, assigned_df_0, "test")
sm_subc_v_0_0_test <-
    keep_split(sm_subc_v_0_0, assigned_df_0, "test")
p_loneliness_0_0_test <-
    keep_split(p_loneliness_0_0, assigned_df_0, "test")
p_screen_time_0_0_test <-
    keep_split(p_screen_time_0_0, assigned_df_0, "test")
p_family_function_0_0_test <-
    keep_split(p_family_function_0_0, assigned_df_0, "test")
p_sports_0_0_test <-
    keep_split(p_sports_0_0, assigned_df_0, "test")
p_prosocial_0_0_test <-
    keep_split(p_prosocial_0_0, assigned_df_0, "test")
p_parent_psych_0_0_test <-
    keep_split(p_parent_psych_0_0, assigned_df_0, "test")
p_exercise_0_0_test <-
    keep_split(p_exercise_0_0, assigned_df_0, "test")
cbcl_headaches_0_0_test <-
    keep_split(cbcl_headaches_0_0, assigned_df_0, "test")
cbcl_nausea_0_0_test <-
    keep_split(cbcl_nausea_0_0, assigned_df_0, "test")
cbcl_vomiting_0_0_test <-
    keep_split(cbcl_vomiting_0_0, assigned_df_0, "test")
cbcl_dizzy_0_0_test <-
    keep_split(cbcl_dizzy_0_0, assigned_df_0, "test")
cbcl_overtired_0_0_test <-
    keep_split(cbcl_overtired_0_0, assigned_df_0, "test")
cbcl_sleeping_more_0_0_test <-
    keep_split(cbcl_sleeping_more_0_0, assigned_df_0, "test")
cbcl_sleeping_less_0_0_test <-
    keep_split(cbcl_sleeping_less_0_0, assigned_df_0, "test")
cbcl_depress_0_0_test <-
    keep_split(cbcl_depress_0_0, assigned_df_0, "test")
cbcl_anxiety_0_0_test <-
    keep_split(cbcl_anxiety_0_0, assigned_df_0, "test")
cbcl_attention_0_0_test <-
    keep_split(cbcl_attention_0_0, assigned_df_0, "test")
cbcl_aggressive_0_0_test <-
    keep_split(cbcl_aggressive_0_0, assigned_df_0, "test")
sds_sleep_0_0_test <-
    keep_split(sds_sleep_0_0, assigned_df_0, "test")

# Generate full set (note that this is structured specifically in row order of
#  training subjects followed by testing subjects)
as_mtbi_loc_0_0_full <-
    rbind(as_mtbi_loc_0_0_train, as_mtbi_loc_0_0_test)
as_mtbi_mechanism_0_0_full <-
    rbind(as_mtbi_mechanism_0_0_train, as_mtbi_mechanism_0_0_test)
as_mtbi_mem_daze_0_0_full <-
    rbind(as_mtbi_mem_daze_0_0_train, as_mtbi_mem_daze_0_0_test)
d_income_0_0_full <-
    rbind(d_income_0_0_train, d_income_0_0_test)
d_interview_age_0_0_full <-
    rbind(d_interview_age_0_0_train, d_interview_age_0_0_test)
d_mtbi_age_0_0_full <-
    rbind(d_mtbi_age_0_0_train, d_mtbi_age_0_0_test)
d_pubertal_status_0_0_full <-
    rbind(d_pubertal_status_0_0_train, d_pubertal_status_0_0_test)
d_race_0_0_full <-
    rbind(d_race_0_0_train, d_race_0_0_test)
d_sex_0_0_full <-
    rbind(d_sex_0_0_train, d_sex_0_0_test)
mh_headaches_0_0_full <-
    rbind(mh_headaches_0_0_train, mh_headaches_0_0_test)
mh_mtbi_count_0_0_full <-
    rbind(mh_mtbi_count_0_0_train, mh_mtbi_count_0_0_test)
dm_all_wmnd_0_0_full <-
    rbind(dm_all_wmnd_0_0_train, dm_all_wmnd_0_0_test)
rm_gord_cor_0_0_full <-
    rbind(rm_gord_cor_0_0_train, rm_gord_cor_0_0_test)
rm_gord_var_0_0_full <-
    rbind(rm_gord_var_0_0_train, rm_gord_var_0_0_test)
rm_subc_cor_0_0_full <-
    rbind(rm_subc_cor_0_0_train, rm_subc_cor_0_0_test)
rm_subc_var_0_0_full <-
    rbind(rm_subc_var_0_0_train, rm_subc_var_0_0_test)
sm_cort_sa_0_0_full <-
    rbind(sm_cort_sa_0_0_train, sm_cort_sa_0_0_test)
sm_cort_t_0_0_full <-
    rbind(sm_cort_t_0_0_train, sm_cort_t_0_0_test)
sm_subc_v_0_0_full <-
    rbind(sm_subc_v_0_0_train, sm_subc_v_0_0_test)
p_loneliness_0_0_full <-
    rbind(p_loneliness_0_0_train, p_loneliness_0_0_test)
p_screen_time_0_0_full <-
    rbind(p_screen_time_0_0_train, p_screen_time_0_0_test)
p_family_function_0_0_full <-
    rbind(p_family_function_0_0_train, p_family_function_0_0_test)
p_sports_0_0_full <-
    rbind(p_sports_0_0_train, p_sports_0_0_test)
p_prosocial_0_0_full <-
    rbind(p_prosocial_0_0_train, p_prosocial_0_0_test)
p_parent_psych_0_0_full <-
    rbind(p_parent_psych_0_0_train, p_parent_psych_0_0_test)
p_exercise_0_0_full <-
    rbind(p_exercise_0_0_train, p_exercise_0_0_test)
cbcl_headaches_0_0_full <-
    rbind(cbcl_headaches_0_0_train, cbcl_headaches_0_0_test)
cbcl_nausea_0_0_full <-
    rbind(cbcl_nausea_0_0_train, cbcl_nausea_0_0_test)
cbcl_vomiting_0_0_full <-
    rbind(cbcl_vomiting_0_0_train, cbcl_vomiting_0_0_test)
cbcl_dizzy_0_0_full <-
    rbind(cbcl_dizzy_0_0_train, cbcl_dizzy_0_0_test)
cbcl_overtired_0_0_full <-
    rbind(cbcl_overtired_0_0_train, cbcl_overtired_0_0_test)
cbcl_sleeping_more_0_0_full <-
    rbind(cbcl_sleeping_more_0_0_train, cbcl_sleeping_more_0_0_test)
cbcl_sleeping_less_0_0_full <-
    rbind(cbcl_sleeping_less_0_0_train, cbcl_sleeping_less_0_0_test)
cbcl_depress_0_0_full <-
    rbind(cbcl_depress_0_0_train, cbcl_depress_0_0_test)
cbcl_anxiety_0_0_full <-
    rbind(cbcl_anxiety_0_0_train, cbcl_anxiety_0_0_test)
cbcl_attention_0_0_full <-
    rbind(cbcl_attention_0_0_train, cbcl_attention_0_0_test)
cbcl_aggressive_0_0_full <-
    rbind(cbcl_aggressive_0_0_train, cbcl_aggressive_0_0_test)


# Export training set
write_csv(as_mtbi_loc_0_0_train,
    proc_path("as_mtbi_loc_0_0_train.csv", date = TRUE))
write_csv(as_mtbi_mechanism_0_0_train,
    proc_path("as_mtbi_mechanism_0_0_train.csv", date = TRUE))
write_csv(as_mtbi_mem_daze_0_0_train,
    proc_path("as_mtbi_mem_daze_0_0_train.csv", date = TRUE))
write_csv(d_income_0_0_train,
    proc_path("d_income_0_0_train.csv", date = TRUE))
write_csv(d_interview_age_0_0_train,
    proc_path("d_interview_age_0_0_train.csv", date = TRUE))
write_csv(d_mtbi_age_0_0_train,
    proc_path("d_mtbi_age_0_0_train.csv", date = TRUE))
write_csv(d_pubertal_status_0_0_train,
    proc_path("d_pubertal_status_0_0_train.csv", date = TRUE))
write_csv(d_race_0_0_train,
    proc_path("d_race_0_0_train.csv", date = TRUE))
write_csv(d_sex_0_0_train,
    proc_path("d_sex_0_0_train.csv", date = TRUE))
write_csv(mh_headaches_0_0_train,
    proc_path("mh_headaches_0_0_train.csv", date = TRUE))
write_csv(mh_mtbi_count_0_0_train,
    proc_path("mh_mtbi_count_0_0_train.csv", date = TRUE))
write_csv(dm_all_wmnd_0_0_train,
    proc_path("dm_all_wmnd_0_0_train.csv", date = TRUE))
write_csv(rm_gord_cor_0_0_train,
    proc_path("rm_gord_cor_0_0_train.csv", date = TRUE))
write_csv(rm_gord_var_0_0_train,
    proc_path("rm_gord_var_0_0_train.csv", date = TRUE))
write_csv(rm_subc_cor_0_0_train,
    proc_path("rm_subc_cor_0_0_train.csv", date = TRUE))
write_csv(rm_subc_var_0_0_train,
    proc_path("rm_subc_var_0_0_train.csv", date = TRUE))
write_csv(sm_cort_sa_0_0_train,
    proc_path("sm_cort_sa_0_0_train.csv", date = TRUE))
write_csv(sm_cort_t_0_0_train,
    proc_path("sm_cort_t_0_0_train.csv", date = TRUE))
write_csv(sm_subc_v_0_0_train,
    proc_path("sm_subc_v_0_0_train.csv", date = TRUE))
write_csv(p_loneliness_0_0_train,
    proc_path("p_loneliness_0_0_train.csv", date = TRUE))
write_csv(p_screen_time_0_0_train,
    proc_path("p_screen_time_0_0_train.csv", date = TRUE))
write_csv(p_family_function_0_0_train,
    proc_path("p_family_function_0_0_train.csv", date = TRUE))
write_csv(p_sports_0_0_train,
    proc_path("p_sports_0_0_train.csv", date = TRUE))
write_csv(p_prosocial_0_0_train,
    proc_path("p_prosocial_0_0_train.csv", date = TRUE))
write_csv(p_parent_psych_0_0_train,
    proc_path("p_parent_psych_0_0_train.csv", date = TRUE))
write_csv(p_exercise_0_0_train,
    proc_path("p_exercise_0_0_train.csv", date = TRUE))
write_csv(cbcl_headaches_0_0_train,
    proc_path("cbcl_headaches_0_0_train.csv", date = TRUE))
write_csv(cbcl_nausea_0_0_train,
    proc_path("cbcl_nausea_0_0_train.csv", date = TRUE))
write_csv(cbcl_vomiting_0_0_train,
    proc_path("cbcl_vomiting_0_0_train.csv", date = TRUE))
write_csv(cbcl_dizzy_0_0_train,
    proc_path("cbcl_dizzy_0_0_train.csv", date = TRUE))
write_csv(cbcl_overtired_0_0_train,
    proc_path("cbcl_overtired_0_0_train.csv", date = TRUE))
write_csv(cbcl_sleeping_more_0_0_train,
    proc_path("cbcl_sleeping_more_0_0_train.csv", date = TRUE))
write_csv(cbcl_sleeping_less_0_0_train,
    proc_path("cbcl_sleeping_less_0_0_train.csv", date = TRUE))
write_csv(cbcl_depress_0_0_train,
    proc_path("cbcl_depress_0_0_train.csv", date = TRUE))
write_csv(cbcl_anxiety_0_0_train,
    proc_path("cbcl_anxiety_0_0_train.csv", date = TRUE))
write_csv(cbcl_attention_0_0_train,
    proc_path("cbcl_attention_0_0_train.csv", date = TRUE))
write_csv(cbcl_aggressive_0_0_train,
    proc_path("cbcl_aggressive_0_0_train.csv", date = TRUE))
write_csv(sds_sleep_0_0_train,
    proc_path("sds_sleep_0_0_train.csv", date = TRUE))

# Export testing set
write_csv(as_mtbi_loc_0_0_test,
    proc_path("as_mtbi_loc_0_0_test.csv", date = TRUE))
write_csv(as_mtbi_mechanism_0_0_test,
    proc_path("as_mtbi_mechanism_0_0_test.csv", date = TRUE))
write_csv(as_mtbi_mem_daze_0_0_test,
    proc_path("as_mtbi_mem_daze_0_0_test.csv", date = TRUE))
write_csv(d_income_0_0_test,
    proc_path("d_income_0_0_test.csv", date = TRUE))
write_csv(d_interview_age_0_0_test,
    proc_path("d_interview_age_0_0_test.csv", date = TRUE))
write_csv(d_mtbi_age_0_0_test,
    proc_path("d_mtbi_age_0_0_test.csv", date = TRUE))
write_csv(d_pubertal_status_0_0_test,
    proc_path("d_pubertal_status_0_0_test.csv", date = TRUE))
write_csv(d_race_0_0_test,
    proc_path("d_race_0_0_test.csv", date = TRUE))
write_csv(d_sex_0_0_test,
    proc_path("d_sex_0_0_test.csv", date = TRUE))
write_csv(mh_headaches_0_0_test,
    proc_path("mh_headaches_0_0_test.csv", date = TRUE))
write_csv(mh_mtbi_count_0_0_test,
    proc_path("mh_mtbi_count_0_0_test.csv", date = TRUE))
write_csv(dm_all_wmnd_0_0_test,
    proc_path("dm_all_wmnd_0_0_test.csv", date = TRUE))
write_csv(rm_gord_cor_0_0_test,
    proc_path("rm_gord_cor_0_0_test.csv", date = TRUE))
write_csv(rm_gord_var_0_0_test,
    proc_path("rm_gord_var_0_0_test.csv", date = TRUE))
write_csv(rm_subc_cor_0_0_test,
    proc_path("rm_subc_cor_0_0_test.csv", date = TRUE))
write_csv(rm_subc_var_0_0_test,
    proc_path("rm_subc_var_0_0_test.csv", date = TRUE))
write_csv(sm_cort_sa_0_0_test,
    proc_path("sm_cort_sa_0_0_test.csv", date = TRUE))
write_csv(sm_cort_t_0_0_test,
    proc_path("sm_cort_t_0_0_test.csv", date = TRUE))
write_csv(sm_subc_v_0_0_test,
    proc_path("sm_subc_v_0_0_test.csv", date = TRUE))
write_csv(p_loneliness_0_0_test,
    proc_path("p_loneliness_0_0_test.csv", date = TRUE))
write_csv(p_screen_time_0_0_test,
    proc_path("p_screen_time_0_0_test.csv", date = TRUE))
write_csv(p_family_function_0_0_test,
    proc_path("p_family_function_0_0_test.csv", date = TRUE))
write_csv(p_sports_0_0_test,
    proc_path("p_sports_0_0_test.csv", date = TRUE))
write_csv(p_prosocial_0_0_test,
    proc_path("p_prosocial_0_0_test.csv", date = TRUE))
write_csv(p_parent_psych_0_0_test,
    proc_path("p_parent_psych_0_0_test.csv", date = TRUE))
write_csv(p_exercise_0_0_test,
    proc_path("p_exercise_0_0_test.csv", date = TRUE))
write_csv(cbcl_headaches_0_0_test,
    proc_path("cbcl_headaches_0_0_test.csv", date = TRUE))
write_csv(cbcl_nausea_0_0_test,
    proc_path("cbcl_nausea_0_0_test.csv", date = TRUE))
write_csv(cbcl_vomiting_0_0_test,
    proc_path("cbcl_vomiting_0_0_test.csv", date = TRUE))
write_csv(cbcl_dizzy_0_0_test,
    proc_path("cbcl_dizzy_0_0_test.csv", date = TRUE))
write_csv(cbcl_overtired_0_0_test,
    proc_path("cbcl_overtired_0_0_test.csv", date = TRUE))
write_csv(cbcl_sleeping_more_0_0_test,
    proc_path("cbcl_sleeping_more_0_0_test.csv", date = TRUE))
write_csv(cbcl_sleeping_less_0_0_test,
    proc_path("cbcl_sleeping_less_0_0_test.csv", date = TRUE))
write_csv(cbcl_depress_0_0_test,
    proc_path("cbcl_depress_0_0_test.csv", date = TRUE))
write_csv(cbcl_anxiety_0_0_test,
    proc_path("cbcl_anxiety_0_0_test.csv", date = TRUE))
write_csv(cbcl_attention_0_0_test,
    proc_path("cbcl_attention_0_0_test.csv", date = TRUE))
write_csv(cbcl_aggressive_0_0_test,
    proc_path("cbcl_aggressive_0_0_test.csv", date = TRUE))
write_csv(sds_sleep_0_0_test,
    proc_path("sds_sleep_0_0_test.csv", date = TRUE))

# Full data
write_csv(as_mtbi_loc_0_0_full,
    proc_path("as_mtbi_loc_0_0_full.csv", date = TRUE))
write_csv(as_mtbi_mechanism_0_0_full,
    proc_path("as_mtbi_mechanism_0_0_full.csv", date = TRUE))
write_csv(as_mtbi_mem_daze_0_0_full,
    proc_path("as_mtbi_mem_daze_0_0_full.csv", date = TRUE))
write_csv(d_income_0_0_full,
    proc_path("d_income_0_0_full.csv", date = TRUE))
write_csv(d_interview_age_0_0_full,
    proc_path("d_interview_age_0_0_full.csv", date = TRUE))
write_csv(d_mtbi_age_0_0_full,
    proc_path("d_mtbi_age_0_0_full.csv", date = TRUE))
write_csv(d_pubertal_status_0_0_full,
    proc_path("d_pubertal_status_0_0_full.csv", date = TRUE))
write_csv(d_race_0_0_full,
    proc_path("d_race_0_0_full.csv", date = TRUE))
write_csv(d_sex_0_0_full,
    proc_path("d_sex_0_0_full.csv", date = TRUE))
write_csv(mh_headaches_0_0_full,
    proc_path("mh_headaches_0_0_full.csv", date = TRUE))
write_csv(mh_mtbi_count_0_0_full,
    proc_path("mh_mtbi_count_0_0_full.csv", date = TRUE))
write_csv(dm_all_wmnd_0_0_full,
    proc_path("dm_all_wmnd_0_0_full.csv", date = TRUE))
write_csv(rm_gord_cor_0_0_full,
    proc_path("rm_gord_cor_0_0_full.csv", date = TRUE))
write_csv(rm_gord_var_0_0_full,
    proc_path("rm_gord_var_0_0_full.csv", date = TRUE))
write_csv(rm_subc_cor_0_0_full,
    proc_path("rm_subc_cor_0_0_full.csv", date = TRUE))
write_csv(rm_subc_var_0_0_full,
    proc_path("rm_subc_var_0_0_full.csv", date = TRUE))
write_csv(sm_cort_sa_0_0_full,
    proc_path("sm_cort_sa_0_0_full.csv", date = TRUE))
write_csv(sm_cort_t_0_0_full,
    proc_path("sm_cort_t_0_0_full.csv", date = TRUE))
write_csv(sm_subc_v_0_0_full,
    proc_path("sm_subc_v_0_0_full.csv", date = TRUE))
write_csv(p_loneliness_0_0_full,
    proc_path("p_loneliness_0_0_full.csv", date = TRUE))
write_csv(p_screen_time_0_0_full,
    proc_path("p_screen_time_0_0_full.csv", date = TRUE))
write_csv(p_family_function_0_0_full,
    proc_path("p_family_function_0_0_full.csv", date = TRUE))
write_csv(p_sports_0_0_full,
    proc_path("p_sports_0_0_full.csv", date = TRUE))
write_csv(p_prosocial_0_0_full,
    proc_path("p_prosocial_0_0_full.csv", date = TRUE))
write_csv(p_parent_psych_0_0_full,
    proc_path("p_parent_psych_0_0_full.csv", date = TRUE))
write_csv(p_exercise_0_0_full,
    proc_path("p_exercise_0_0_full.csv", date = TRUE))
write_csv(cbcl_headaches_0_0_full,
    proc_path("cbcl_headaches_0_0_full.csv", date = TRUE))
write_csv(cbcl_nausea_0_0_full,
    proc_path("cbcl_nausea_0_0_full.csv", date = TRUE))
write_csv(cbcl_vomiting_0_0_full,
    proc_path("cbcl_vomiting_0_0_full.csv", date = TRUE))
write_csv(cbcl_dizzy_0_0_full,
    proc_path("cbcl_dizzy_0_0_full.csv", date = TRUE))
write_csv(cbcl_overtired_0_0_full,
    proc_path("cbcl_overtired_0_0_full.csv", date = TRUE))
write_csv(cbcl_sleeping_more_0_0_full,
    proc_path("cbcl_sleeping_more_0_0_full.csv", date = TRUE))
write_csv(cbcl_sleeping_less_0_0_full,
    proc_path("cbcl_sleeping_less_0_0_full.csv", date = TRUE))
write_csv(cbcl_depress_0_0_full,
    proc_path("cbcl_depress_0_0_full.csv", date = TRUE))
write_csv(cbcl_anxiety_0_0_full,
    proc_path("cbcl_anxiety_0_0_full.csv", date = TRUE))
write_csv(cbcl_attention_0_0_full,
    proc_path("cbcl_attention_0_0_full.csv", date = TRUE))
write_csv(cbcl_aggressive_0_0_full,
    proc_path("cbcl_aggressive_0_0_full.csv", date = TRUE))
```


## Data and outcome lists

Subsequent analyses make use of custom `data_list` and `outcome_list` objects that store information about all input variables and outcome (CBCL) measures used for SNF and cluster characterization.
I also store make use of a `cbcl_list` object, which is simply a list of cbcl dataframes and does not keep a track of the same amount of metadata as used in the highly nested `outcome_list` object.
Instead of loading each individual file and building these lists, we can build the lists here and export them for later use.

```{r}
library(metasnf)
library(rlist)

# Importing the data
as_mtbi_loc_0_0_train <-
    read_csv(proc_path("2023_07_17_as_mtbi_loc_0_0_train.csv"))
as_mtbi_mechanism_0_0_train <-
    read_csv(proc_path("2023_07_17_as_mtbi_mechanism_0_0_train.csv"))
as_mtbi_mem_daze_0_0_train <-
    read_csv(proc_path("2023_07_17_as_mtbi_mem_daze_0_0_train.csv"))
d_income_0_0_train <-
    read_csv(proc_path("2023_07_17_d_income_0_0_train.csv"))
d_interview_age_0_0_train <-
    read_csv(proc_path("2023_07_17_d_interview_age_0_0_train.csv"))
d_mtbi_age_0_0_train <-
    read_csv(proc_path("2023_07_17_d_mtbi_age_0_0_train.csv"))
d_pubertal_status_0_0_train <-
    read_csv(proc_path("2023_07_17_d_pubertal_status_0_0_train.csv"))
d_race_0_0_train <-
    read_csv(proc_path("2023_07_17_d_race_0_0_train.csv"))
d_sex_0_0_train <-
    read_csv(proc_path("2023_07_17_d_sex_0_0_train.csv"))
mh_headaches_0_0_train <-
    read_csv(proc_path("2023_07_17_mh_headaches_0_0_train.csv"))
mh_mtbi_count_0_0_train <-
    read_csv(proc_path("2023_07_17_mh_mtbi_count_0_0_train.csv"))
dm_all_wmnd_0_0_train <-
    read_csv(proc_path("2023_07_17_dm_all_wmnd_0_0_train.csv"))
rm_gord_cor_0_0_train <-
    read_csv(proc_path("2023_07_17_rm_gord_cor_0_0_train.csv"))
rm_gord_var_0_0_train <-
    read_csv(proc_path("2023_07_17_rm_gord_var_0_0_train.csv"))
rm_subc_cor_0_0_train <-
    read_csv(proc_path("2023_07_17_rm_subc_cor_0_0_train.csv"))
rm_subc_var_0_0_train <-
    read_csv(proc_path("2023_07_17_rm_subc_var_0_0_train.csv"))
sm_cort_sa_0_0_train <-
    read_csv(proc_path("2023_07_17_sm_cort_sa_0_0_train.csv"))
sm_cort_t_0_0_train <-
    read_csv(proc_path("2023_07_17_sm_cort_t_0_0_train.csv"))
sm_subc_v_0_0_train <-
    read_csv(proc_path("2023_07_17_sm_subc_v_0_0_train.csv"))
p_loneliness_0_0_train <-
    read_csv(proc_path("2023_07_17_p_loneliness_0_0_train.csv"))
p_screen_time_0_0_train <-
    read_csv(proc_path("2023_07_17_p_screen_time_0_0_train.csv"))
p_family_function_0_0_train <-
    read_csv(proc_path("2023_07_17_p_family_function_0_0_train.csv"))
p_sports_0_0_train <-
    read_csv(proc_path("2023_07_17_p_sports_0_0_train.csv"))
p_prosocial_0_0_train <-
    read_csv(proc_path("2023_07_17_p_prosocial_0_0_train.csv"))
p_parent_psych_0_0_train <-
    read_csv(proc_path("2023_07_17_p_parent_psych_0_0_train.csv"))
p_exercise_0_0_train <-
    read_csv(proc_path("2023_07_17_p_exercise_0_0_train.csv"))
cbcl_headaches_0_0_train <-
    read_csv(proc_path("2023_07_17_cbcl_headaches_0_0_train.csv"))
cbcl_nausea_0_0_train <-
    read_csv(proc_path("2023_07_17_cbcl_nausea_0_0_train.csv"))
cbcl_vomiting_0_0_train <-
    read_csv(proc_path("2023_07_17_cbcl_vomiting_0_0_train.csv"))
cbcl_dizzy_0_0_train <-
    read_csv(proc_path("2023_07_17_cbcl_dizzy_0_0_train.csv"))
cbcl_overtired_0_0_train <-
    read_csv(proc_path("2023_07_17_cbcl_overtired_0_0_train.csv"))
cbcl_sleeping_more_0_0_train <-
    read_csv(proc_path("2023_07_17_cbcl_sleeping_more_0_0_train.csv"))
cbcl_sleeping_less_0_0_train <-
    read_csv(proc_path("2023_07_17_cbcl_sleeping_less_0_0_train.csv"))
cbcl_depress_0_0_train <-
    read_csv(proc_path("2023_07_17_cbcl_depress_0_0_train.csv"))
cbcl_anxiety_0_0_train <-
    read_csv(proc_path("2023_07_17_cbcl_anxiety_0_0_train.csv"))
cbcl_attention_0_0_train <-
    read_csv(proc_path("2023_07_17_cbcl_attention_0_0_train.csv"))
cbcl_aggressive_0_0_train <-
    read_csv(proc_path("2023_07_17_cbcl_aggressive_0_0_train.csv"))

as_mtbi_loc_0_0_test <-
    read_csv(proc_path("2023_07_17_as_mtbi_loc_0_0_test.csv"))
as_mtbi_mechanism_0_0_test <-
    read_csv(proc_path("2023_07_17_as_mtbi_mechanism_0_0_test.csv"))
as_mtbi_mem_daze_0_0_test <-
    read_csv(proc_path("2023_07_17_as_mtbi_mem_daze_0_0_test.csv"))
d_income_0_0_test <-
    read_csv(proc_path("2023_07_17_d_income_0_0_test.csv"))
d_interview_age_0_0_test <-
    read_csv(proc_path("2023_07_17_d_interview_age_0_0_test.csv"))
d_mtbi_age_0_0_test <-
    read_csv(proc_path("2023_07_17_d_mtbi_age_0_0_test.csv"))
d_pubertal_status_0_0_test <-
    read_csv(proc_path("2023_07_17_d_pubertal_status_0_0_test.csv"))
d_race_0_0_test <-
    read_csv(proc_path("2023_07_17_d_race_0_0_test.csv"))
d_sex_0_0_test <-
    read_csv(proc_path("2023_07_17_d_sex_0_0_test.csv"))
mh_headaches_0_0_test <-
    read_csv(proc_path("2023_07_17_mh_headaches_0_0_test.csv"))
mh_mtbi_count_0_0_test <-
    read_csv(proc_path("2023_07_17_mh_mtbi_count_0_0_test.csv"))
dm_all_wmnd_0_0_test <-
    read_csv(proc_path("2023_07_17_dm_all_wmnd_0_0_test.csv"))
rm_gord_cor_0_0_test <-
    read_csv(proc_path("2023_07_17_rm_gord_cor_0_0_test.csv"))
rm_gord_var_0_0_test <-
    read_csv(proc_path("2023_07_17_rm_gord_var_0_0_test.csv"))
rm_subc_cor_0_0_test <-
    read_csv(proc_path("2023_07_17_rm_subc_cor_0_0_test.csv"))
rm_subc_var_0_0_test <-
    read_csv(proc_path("2023_07_17_rm_subc_var_0_0_test.csv"))
sm_cort_sa_0_0_test <-
    read_csv(proc_path("2023_07_17_sm_cort_sa_0_0_test.csv"))
sm_cort_t_0_0_test <-
    read_csv(proc_path("2023_07_17_sm_cort_t_0_0_test.csv"))
sm_subc_v_0_0_test <-
    read_csv(proc_path("2023_07_17_sm_subc_v_0_0_test.csv"))
p_loneliness_0_0_test <-
    read_csv(proc_path("2023_07_17_p_loneliness_0_0_test.csv"))
p_screen_time_0_0_test <-
    read_csv(proc_path("2023_07_17_p_screen_time_0_0_test.csv"))
p_family_function_0_0_test <-
    read_csv(proc_path("2023_07_17_p_family_function_0_0_test.csv"))
p_sports_0_0_test <-
    read_csv(proc_path("2023_07_17_p_sports_0_0_test.csv"))
p_prosocial_0_0_test <-
    read_csv(proc_path("2023_07_17_p_prosocial_0_0_test.csv"))
p_parent_psych_0_0_test <-
    read_csv(proc_path("2023_07_17_p_parent_psych_0_0_test.csv"))
p_exercise_0_0_test <-
    read_csv(proc_path("2023_07_17_p_exercise_0_0_test.csv"))
cbcl_headaches_0_0_test <-
    read_csv(proc_path("2023_07_17_cbcl_headaches_0_0_test.csv"))
cbcl_nausea_0_0_test <-
    read_csv(proc_path("2023_07_17_cbcl_nausea_0_0_test.csv"))
cbcl_vomiting_0_0_test <-
    read_csv(proc_path("2023_07_17_cbcl_vomiting_0_0_test.csv"))
cbcl_dizzy_0_0_test <-
    read_csv(proc_path("2023_07_17_cbcl_dizzy_0_0_test.csv"))
cbcl_overtired_0_0_test <-
    read_csv(proc_path("2023_07_17_cbcl_overtired_0_0_test.csv"))
cbcl_sleeping_more_0_0_test <-
    read_csv(proc_path("2023_07_17_cbcl_sleeping_more_0_0_test.csv"))
cbcl_sleeping_less_0_0_test <-
    read_csv(proc_path("2023_07_17_cbcl_sleeping_less_0_0_test.csv"))
cbcl_depress_0_0_test <-
    read_csv(proc_path("2023_07_17_cbcl_depress_0_0_test.csv"))
cbcl_anxiety_0_0_test <-
    read_csv(proc_path("2023_07_17_cbcl_anxiety_0_0_test.csv"))
cbcl_attention_0_0_test <-
    read_csv(proc_path("2023_07_17_cbcl_attention_0_0_test.csv"))
cbcl_aggressive_0_0_test <-
    read_csv(proc_path("2023_07_17_cbcl_aggressive_0_0_test.csv"))

as_mtbi_loc_0_0_full <-
    read_csv(proc_path("2023_07_17_as_mtbi_loc_0_0_full.csv"))
as_mtbi_mechanism_0_0_full <-
    read_csv(proc_path("2023_07_17_as_mtbi_mechanism_0_0_full.csv"))
as_mtbi_mem_daze_0_0_full <-
    read_csv(proc_path("2023_07_17_as_mtbi_mem_daze_0_0_full.csv"))
d_income_0_0_full <-
    read_csv(proc_path("2023_07_17_d_income_0_0_full.csv"))
d_interview_age_0_0_full <-
    read_csv(proc_path("2023_07_17_d_interview_age_0_0_full.csv"))
d_mtbi_age_0_0_full <-
    read_csv(proc_path("2023_07_17_d_mtbi_age_0_0_full.csv"))
d_pubertal_status_0_0_full <-
    read_csv(proc_path("2023_07_17_d_pubertal_status_0_0_full.csv"))
d_race_0_0_full <-
    read_csv(proc_path("2023_07_17_d_race_0_0_full.csv"))
d_sex_0_0_full <-
    read_csv(proc_path("2023_07_17_d_sex_0_0_full.csv"))
mh_headaches_0_0_full <-
    read_csv(proc_path("2023_07_17_mh_headaches_0_0_full.csv"))
mh_mtbi_count_0_0_full <-
    read_csv(proc_path("2023_07_17_mh_mtbi_count_0_0_full.csv"))
dm_all_wmnd_0_0_full <-
    read_csv(proc_path("2023_07_17_dm_all_wmnd_0_0_full.csv"))
rm_gord_cor_0_0_full <-
    read_csv(proc_path("2023_07_17_rm_gord_cor_0_0_full.csv"))
rm_gord_var_0_0_full <-
    read_csv(proc_path("2023_07_17_rm_gord_var_0_0_full.csv"))
rm_subc_cor_0_0_full <-
    read_csv(proc_path("2023_07_17_rm_subc_cor_0_0_full.csv"))
rm_subc_var_0_0_full <-
    read_csv(proc_path("2023_07_17_rm_subc_var_0_0_full.csv"))
sm_cort_sa_0_0_full <-
    read_csv(proc_path("2023_07_17_sm_cort_sa_0_0_full.csv"))
sm_cort_t_0_0_full <-
    read_csv(proc_path("2023_07_17_sm_cort_t_0_0_full.csv"))
sm_subc_v_0_0_full <-
    read_csv(proc_path("2023_07_17_sm_subc_v_0_0_full.csv"))
p_loneliness_0_0_full <-
    read_csv(proc_path("2023_07_17_p_loneliness_0_0_full.csv"))
p_screen_time_0_0_full <-
    read_csv(proc_path("2023_07_17_p_screen_time_0_0_full.csv"))
p_family_function_0_0_full <-
    read_csv(proc_path("2023_07_17_p_family_function_0_0_full.csv"))
p_sports_0_0_full <-
    read_csv(proc_path("2023_07_17_p_sports_0_0_full.csv"))
p_prosocial_0_0_full <-
    read_csv(proc_path("2023_07_17_p_prosocial_0_0_full.csv"))
p_parent_psych_0_0_full <-
    read_csv(proc_path("2023_07_17_p_parent_psych_0_0_full.csv"))
p_exercise_0_0_full <-
    read_csv(proc_path("2023_07_17_p_exercise_0_0_full.csv"))
cbcl_headaches_0_0_full <-
    read_csv(proc_path("2023_07_17_cbcl_headaches_0_0_full.csv"))
cbcl_nausea_0_0_full <-
    read_csv(proc_path("2023_07_17_cbcl_nausea_0_0_full.csv"))
cbcl_vomiting_0_0_full <-
    read_csv(proc_path("2023_07_17_cbcl_vomiting_0_0_full.csv"))
cbcl_dizzy_0_0_full <-
    read_csv(proc_path("2023_07_17_cbcl_dizzy_0_0_full.csv"))
cbcl_overtired_0_0_full <-
    read_csv(proc_path("2023_07_17_cbcl_overtired_0_0_full.csv"))
cbcl_sleeping_more_0_0_full <-
    read_csv(proc_path("2023_07_17_cbcl_sleeping_more_0_0_full.csv"))
cbcl_sleeping_less_0_0_full <-
    read_csv(proc_path("2023_07_17_cbcl_sleeping_less_0_0_full.csv"))
cbcl_depress_0_0_full <-
    read_csv(proc_path("2023_07_17_cbcl_depress_0_0_full.csv"))
cbcl_anxiety_0_0_full <-
    read_csv(proc_path("2023_07_17_cbcl_anxiety_0_0_full.csv"))
cbcl_attention_0_0_full <-
    read_csv(proc_path("2023_07_17_cbcl_attention_0_0_full.csv"))
cbcl_aggressive_0_0_full <-
    read_csv(proc_path("2023_07_17_cbcl_aggressive_0_0_full.csv"))


# Training data list
data_list_0_0_train <- generate_data_list(
    list(as_mtbi_loc_0_0_train, "mtbi_loc", "as", "categorical"),
    list(as_mtbi_mechanism_0_0_train, "mtbi_mechanism", "as", "categorical"),
    list(as_mtbi_mem_daze_0_0_train, "mtbi_mem_daze", "as", "categorical"),
    list(d_income_0_0_train, "income", "d", "numeric"),
    list(d_interview_age_0_0_train, "interview_age", "d", "numeric"),
    list(d_mtbi_age_0_0_train, "mtbi_age", "d", "numeric"),
    list(d_pubertal_status_0_0_train, "pubertal_status", "d", "numeric"),
    list(d_race_0_0_train, "race", "d", "categorical"),
    list(d_sex_0_0_train, "sex", "d", "categorical"),
    list(mh_headaches_0_0_train, "headaches", "mh", "categorical"),
    list(mh_mtbi_count_0_0_train, "mtbi_count", "mh", "numeric"),
    list(dm_all_wmnd_0_0_train, "wmndf", "n", "numeric"),
    list(rm_gord_cor_0_0_train, "gord_cor", "n", "numeric"),
    list(rm_gord_var_0_0_train, "gord_var", "n", "numeric"),
    list(rm_subc_cor_0_0_train, "subc_cor", "n", "numeric"),
    list(rm_subc_var_0_0_train, "subc_var", "n", "numeric"),
    list(sm_cort_sa_0_0_train, "cort_sa", "n", "numeric"),
    list(sm_cort_t_0_0_train, "cort_t", "n", "numeric"),
    list(sm_subc_v_0_0_train, "subc_v", "n", "numeric"),
    list(p_loneliness_0_0_train, "loneliness", "p", "numeric"),
    list(p_screen_time_0_0_train, "screen_time", "p", "numeric"),
    list(p_family_function_0_0_train, "family_function", "p", "numeric"),
    list(p_sports_0_0_train, "sports", "p", "numeric"),
    list(p_prosocial_0_0_train, "prosocial", "p", "numeric"),
    list(p_parent_psych_0_0_train, "parent_psych", "p", "numeric"),
    list(p_exercise_0_0_train, "exercise", "p", "numeric")
)

list.save(data_list_0_0_train,
          proc_path("data_list_0_0_train.rdata", date = TRUE))

# Testing
data_list_0_0_test <- generate_data_list(
    list(as_mtbi_loc_0_0_test, "mtbi_loc", "as", "categorical"),
    list(as_mtbi_mechanism_0_0_test, "mtbi_mechanism", "as", "categorical"),
    list(as_mtbi_mem_daze_0_0_test, "mtbi_mem_daze", "as", "categorical"),
    list(d_income_0_0_test, "income", "d", "numeric"),
    list(d_interview_age_0_0_test, "interview_age", "d", "numeric"),
    list(d_mtbi_age_0_0_test, "mtbi_age", "d", "numeric"),
    list(d_pubertal_status_0_0_test, "pubertal_status", "d", "numeric"),
    list(d_race_0_0_test, "race", "d", "categorical"),
    list(d_sex_0_0_test, "sex", "d", "categorical"),
    list(mh_headaches_0_0_test, "headaches", "mh", "categorical"),
    list(mh_mtbi_count_0_0_test, "mtbi_count", "mh", "numeric"),
    list(dm_all_wmnd_0_0_test, "wmndf", "n", "numeric"),
    list(rm_gord_cor_0_0_test, "gord_cor", "n", "numeric"),
    list(rm_gord_var_0_0_test, "gord_var", "n", "numeric"),
    list(rm_subc_cor_0_0_test, "subc_cor", "n", "numeric"),
    list(rm_subc_var_0_0_test, "subc_var", "n", "numeric"),
    list(sm_cort_sa_0_0_test, "cort_sa", "n", "numeric"),
    list(sm_cort_t_0_0_test, "cort_t", "n", "numeric"),
    list(sm_subc_v_0_0_test, "subc_v", "n", "numeric"),
    list(p_loneliness_0_0_test, "loneliness", "p", "numeric"),
    list(p_screen_time_0_0_test, "screen_time", "p", "numeric"),
    list(p_family_function_0_0_test, "family_function", "p", "numeric"),
    list(p_sports_0_0_test, "sports", "p", "numeric"),
    list(p_prosocial_0_0_test, "prosocial", "p", "numeric"),
    list(p_parent_psych_0_0_test, "parent_psych", "p", "numeric"),
    list(p_exercise_0_0_test, "exercise", "p", "numeric")
)

list.save(data_list_0_0_test,
          proc_path("data_list_0_0_test.rdata", date = TRUE))


data_list_0_0_full <- generate_data_list(
    list(as_mtbi_loc_0_0_full, "mtbi_loc", "as", "categorical"),
    list(as_mtbi_mechanism_0_0_full, "mtbi_mechanism", "as", "categorical"),
    list(as_mtbi_mem_daze_0_0_full, "mtbi_mem_daze", "as", "categorical"),
    list(d_income_0_0_full, "income", "d", "numeric"),
    list(d_interview_age_0_0_full, "interview_age", "d", "numeric"),
    list(d_mtbi_age_0_0_full, "mtbi_age", "d", "numeric"),
    list(d_pubertal_status_0_0_full, "pubertal_status", "d", "numeric"),
    list(d_race_0_0_full, "race", "d", "categorical"),
    list(d_sex_0_0_full, "sex", "d", "categorical"),
    list(mh_headaches_0_0_full, "headaches", "mh", "categorical"),
    list(mh_mtbi_count_0_0_full, "mtbi_count", "mh", "numeric"),
    list(dm_all_wmnd_0_0_full, "wmndf", "n", "numeric"),
    list(rm_gord_cor_0_0_full, "gord_cor", "n", "numeric"),
    list(rm_gord_var_0_0_full, "gord_var", "n", "numeric"),
    list(rm_subc_cor_0_0_full, "subc_cor", "n", "numeric"),
    list(rm_subc_var_0_0_full, "subc_var", "n", "numeric"),
    list(sm_cort_sa_0_0_full, "cort_sa", "n", "numeric"),
    list(sm_cort_t_0_0_full, "cort_t", "n", "numeric"),
    list(sm_subc_v_0_0_full, "subc_v", "n", "numeric"),
    list(p_loneliness_0_0_full, "loneliness", "p", "numeric"),
    list(p_screen_time_0_0_full, "screen_time", "p", "numeric"),
    list(p_family_function_0_0_full, "family_function", "p", "numeric"),
    list(p_sports_0_0_full, "sports", "p", "numeric"),
    list(p_prosocial_0_0_full, "prosocial", "p", "numeric"),
    list(p_parent_psych_0_0_full, "parent_psych", "p", "numeric"),
    list(p_exercise_0_0_full, "exercise", "p", "numeric")
)

list.save(data_list_0_0_full,
          proc_path("data_list_0_0_full.rdata", date = TRUE))


# Training CBCL list
cbcl_list_0_0_train <- list(
    cbcl_nausea_0_0_train,
    cbcl_vomiting_0_0_train,
    cbcl_dizzy_0_0_train,
    cbcl_overtired_0_0_train,
    cbcl_sleeping_more_0_0_train,
    cbcl_sleeping_less_0_0_train,
    cbcl_depress_0_0_train,
    cbcl_anxiety_0_0_train,
    cbcl_attention_0_0_train,
    cbcl_aggressive_0_0_train
)

list.save(cbcl_list_0_0_train,
          proc_path("cbcl_list_0_0_train.rdata", date = TRUE))


# The outcome list should be an optional structure
outcome_list_0_0_train <- generate_outcome_list(
    list(cbcl_nausea_0_0_train, "cbcl_nausea", "ordinal"),
    list(cbcl_vomiting_0_0_train, "cbcl_vomiting", "ordinal"),
    list(cbcl_dizzy_0_0_train, "cbcl_dizzy", "ordinal"),
    list(cbcl_overtired_0_0_train, "cbcl_overtired", "ordinal"),
    list(cbcl_sleeping_more_0_0_train, "cbcl_sleeping_more", "ordinal"),
    list(cbcl_sleeping_less_0_0_train, "cbcl_sleeping_less", "ordinal"),
    list(cbcl_depress_0_0_train, "cbcl_depress", "ordinal"),
    list(cbcl_anxiety_0_0_train, "cbcl_anxiety", "ordinal"),
    list(cbcl_attention_0_0_train, "cbcl_attention", "ordinal"),
    list(cbcl_aggressive_0_0_train, "cbcl_aggressive", "ordinal")
)

list.save(outcome_list_0_0_train,
          proc_path("outcome_list_0_0_train.rdata", date = TRUE))

cbcl_list_0_0_full <- list(
    cbcl_nausea_0_0_full,
    cbcl_vomiting_0_0_full,
    cbcl_dizzy_0_0_full,
    cbcl_overtired_0_0_full,
    cbcl_sleeping_more_0_0_full,
    cbcl_sleeping_less_0_0_full,
    cbcl_depress_0_0_full,
    cbcl_anxiety_0_0_full,
    cbcl_attention_0_0_full,
    cbcl_aggressive_0_0_full
)

list.save(cbcl_list_0_0_full,
          proc_path("cbcl_list_0_0_full.rdata", date = TRUE))
```
