# Imputation, QCing, and CBCL thresholding

This script is used to:

1. Impute missing data for non-neuroimaging input variables
2. Remove neuroimaging data for participants who do not meet ABCD's QC
3. Threshold CBCL behaviour measures (raw scores into normal (0), borderline (1), and clinical (2))

next step is to figure out what needs to be reverted here

## Loading in data

```{r}
library(mice)
library(dplyr)
library(abcdutils)
library(readr)
library(purrr)
library(here)


# Place the location of your input data here
input_path <- path_maker(here(paste0("data/abcd/inputs")))
raw_path <- path_maker(here(paste0("data/abcd/raw")))
misc_path <- path_maker(here(paste0("data/abcd/misc")))


# Baseline inputs
as_mtbi_loc_0_0 <- read_csv(input_path("2023_04_13_as_mtbi_loc_0_0.csv"))
as_mtbi_mechanism_0_0 <- read_csv(input_path("2023_04_13_as_mtbi_mechanism_0_0.csv"))
as_mtbi_mem_daze_0_0 <- read_csv(input_path("2023_04_13_as_mtbi_mem_daze_0_0.csv"))
d_income_0_0 <- read_csv(input_path("2023_04_13_d_income_0_0.csv"))
d_interview_age_0_0 <- read_csv(input_path("2023_04_13_d_interview_age_0_0.csv"))
d_mtbi_age_0_0 <- read_csv(input_path("2023_04_13_d_mtbi_age_0_0.csv"))
d_pubertal_status_0_0 <- read_csv(input_path("2023_04_13_d_pubertal_status_0_0.csv"))
d_race_0_0 <- read_csv(input_path("2023_04_13_d_race_0_0.csv"))
d_sex_0_0 <- read_csv(input_path("2023_04_13_d_sex_0_0.csv"))
mh_headaches_0_0 <- read_csv(input_path("2023_04_13_mh_headaches_0_0.csv"))
mh_mtbi_count_0_0 <- read_csv(input_path("2023_04_13_mh_mtbi_count_0_0.csv"))
dm_all_wmnd_0_0 <- read_csv(input_path("2023_04_13_dm_all_wmnd_0_0.csv"))
rm_gord_cor_0_0 <- read_csv(input_path("2023_04_13_rm_gord_cor_0_0.csv"))
rm_gord_var_0_0 <- read_csv(input_path("2023_04_13_rm_gord_var_0_0.csv"))
rm_subc_cor_0_0 <- read_csv(input_path("2023_04_13_rm_subc_cor_0_0.csv"))
rm_subc_var_0_0 <- read_csv(input_path("2023_04_13_rm_subc_var_0_0.csv"))
sm_cort_sa_0_0 <- read_csv(input_path("2023_04_13_sm_cort_sa_0_0.csv"))
sm_cort_t_0_0 <- read_csv(input_path("2023_04_13_sm_cort_t_0_0.csv"))
sm_subc_v_0_0 <- read_csv(input_path("2023_04_13_sm_subc_v_0_0.csv"))
p_loneliness_0_0 <- read_csv(input_path("2023_04_13_p_loneliness_0_0.csv"))
p_screen_time_0_0 <- read_csv(input_path("2023_04_13_p_screen_time_0_0.csv"))
p_family_function_0_0 <- read_csv(input_path("2023_04_13_p_family_function_0_0.csv"))
p_sports_0_0 <- read_csv(input_path("2023_04_13_p_sports_0_0.csv"))
p_prosocial_0_0 <- read_csv(input_path("2023_04_13_p_prosocial_0_0.csv"))
p_parent_psych_0_0 <- read_csv(input_path("2023_04_13_p_parent_psych_0_0.csv"))
p_exercise_0_0 <- read_csv(input_path("2023_04_13_p_exercise_0_0.csv"))
cbcl_headaches_0_0 <- read_csv(input_path("2023_04_13_cbcl_headaches_0_0.csv"))
cbcl_nausea_0_0 <- read_csv(input_path("2023_04_13_cbcl_nausea_0_0.csv"))
cbcl_vomiting_0_0 <- read_csv(input_path("2023_04_13_cbcl_vomiting_0_0.csv"))
cbcl_dizzy_0_0 <- read_csv(input_path("2023_04_13_cbcl_dizzy_0_0.csv"))
cbcl_overtired_0_0 <- read_csv(input_path("2023_04_13_cbcl_overtired_0_0.csv"))
cbcl_sleeping_more_0_0 <- read_csv(input_path("2023_04_13_cbcl_sleeping_more_0_0.csv"))
cbcl_sleeping_less_0_0 <- read_csv(input_path("2023_04_13_cbcl_sleeping_less_0_0.csv"))
cbcl_depress_r_0_0 <- read_csv(input_path("2023_04_13_cbcl_depress_r_0_0.csv"))
cbcl_anxiety_r_0_0 <- read_csv(input_path("2023_04_13_cbcl_anxiety_r_0_0.csv"))
cbcl_attention_r_0_0 <- read_csv(input_path("2023_04_13_cbcl_attention_r_0_0.csv"))
cbcl_aggressive_r_0_0 <- read_csv(input_path("2023_04_13_cbcl_aggressive_r_0_0.csv"))
sds_sleep_0_0 <- read_csv(input_path("2023_04_13_sds_sleep_df_0_0.csv"))
nihtbx_list_fc_0_0 <- read_csv(input_path("2023_04_13_nihtbx_list_fc_0_0.csv"))
nihtbx_pattern_fc_0_0 <- read_csv(input_path("2023_04_13_nihtbx_pattern_fc_0_0.csv"))
nihtbx_cardsort_fc_0_0 <- read_csv(input_path("2023_04_13_nihtbx_cardsort_fc_0_0.csv"))
```


## Neuroimaging quality control

```{r eval = FALSE}
mriqcrp10301 <- read_delim(raw_path("mriqcrp10301.txt"))

# Obtaining the QC'd subjects with complete neuroimaging data
rm_gord_cor_qc_0_0 <- qc_rsfmri(rm_gord_cor_0_0, mriqcrp10301, t = 0, no_na = TRUE)
rm_gord_var_qc_0_0 <- qc_rsfmri(rm_gord_var_0_0, mriqcrp10301, t = 0, no_na = TRUE)
rm_subc_cor_qc_0_0 <- qc_rsfmri(rm_subc_cor_0_0, mriqcrp10301, t = 0, no_na = TRUE)
rm_subc_var_qc_0_0 <- qc_rsfmri(rm_subc_var_0_0, mriqcrp10301, t = 0, no_na = TRUE)
dm_all_wmnd_qc_0_0 <- qc_dmri(dm_all_wmnd_0_0, mriqcrp10301, t = 0, no_na = TRUE)
sm_cort_sa_qc_0_0 <- qc_smri(sm_cort_sa_0_0, mriqcrp10301, t = 0, no_na = TRUE)
sm_cort_t_qc_0_0 <- qc_smri(sm_cort_t_0_0, mriqcrp10301, t = 0, no_na = TRUE)
sm_subc_v_qc_0_0 <- qc_smri(sm_subc_v_0_0, mriqcrp10301, t = 0, no_na = TRUE)

write_csv(rm_gord_cor_qc_0_0, input_path("rm_gord_cor_qc_0_0.csv", TRUE))
write_csv(rm_gord_var_qc_0_0, input_path("rm_gord_var_qc_0_0.csv", TRUE))
write_csv(rm_subc_cor_qc_0_0, input_path("rm_subc_cor_qc_0_0.csv", TRUE))
write_csv(rm_subc_var_qc_0_0, input_path("rm_subc_var_qc_0_0.csv", TRUE))
write_csv(dm_all_wmnd_qc_0_0, input_path("dm_all_wmnd_qc_0_0.csv", TRUE))
write_csv(sm_cort_sa_qc_0_0, input_path("sm_cort_sa_qc_0_0.csv", TRUE))
write_csv(sm_cort_t_qc_0_0, input_path("sm_cort_t_qc_0_0.csv", TRUE))
write_csv(sm_subc_v_qc_0_0, input_path("sm_subc_v_qc_0_0.csv", TRUE))
```


## Imputing missing data 

Here, I only impute the non-neuroimaging data.

Code is based on Eman's imputation script.
Thanks Eman!

While this choice was made largely for the sake of time, it was also partially because imputing neuroimaging data doesn't seem to be a common practice.


```{r eval = FALSE}
# put all data frames into a named list
df_list_no_neuroimaging_0_0 <- list(
    "loss of consciousness" = as_mtbi_loc_0_0,
    "mechanism of injury" = as_mtbi_mechanism_0_0,
    "memory loss / dazed" = as_mtbi_mem_daze_0_0,
    "income" = d_income_0_0,
    "interview_age" = d_interview_age_0_0,
    "mtbi_age" = d_mtbi_age_0_0,
    "pubertal_status" = d_pubertal_status_0_0,
    "race" = d_race_0_0,
    "sex" = d_sex_0_0,
    "headaches" = mh_headaches_0_0,
    "mtbi_count" = mh_mtbi_count_0_0,
    "loneliness" = p_loneliness_0_0,
    "screen time" = p_screen_time_0_0,
    "family function" = p_family_function_0_0,
    "sports" = p_sports_0_0,
    "prosocial" = p_prosocial_0_0,
    "parent psych" = p_parent_psych_0_0,
    "exercise" = p_exercise_0_0,
    "cbcl headaches" = cbcl_headaches_0_0,
    "cbcl nausea" = cbcl_nausea_0_0,
    "cbcl vomiting" = cbcl_vomiting_0_0,
    "cbcl dizzy" = cbcl_dizzy_0_0,
    "cbcl overtired" = cbcl_overtired_0_0,
    "cbcl sleeping more" = cbcl_sleeping_more_0_0,
    "cbcl sleeping less" = cbcl_sleeping_less_0_0,
    "cbcl depress r" = cbcl_depress_r_0_0,
    "cbcl anxiety r" = cbcl_anxiety_r_0_0,
    "cbcl attention r" = cbcl_attention_r_0_0,
    "cbcl aggressive r" = cbcl_aggressive_r_0_0,
    "sds sleep" = sds_sleep_0_0,
    "nihtbx list fc" = nihtbx_list_fc_0_0,
    "nihtbx pattern fc" = nihtbx_pattern_fc_0_0,
    "nihtbx cardsort fc" = nihtbx_cardsort_fc_0_0
)

vis_missing_by_df(df_list_no_neuroimaging_0_0)

full_df_0_0 <- df_list_no_neuroimaging_0_0 |>
    purrr::reduce(dplyr::full_join, by = "subjectkey")

str(full_df_0_0)


dim(full_df_0_0) # 424 subjects

dim(na.omit(full_df_0_0)) # 356 subjects


# the 0-imputation group
a <- merge_df_list(list(rm_gord_cor_qc_0_0,
rm_gord_var_qc_0_0,
rm_subc_cor_qc_0_0,
rm_subc_var_qc_0_0,
dm_all_wmnd_qc_0_0,
sm_cort_sa_qc_0_0,
sm_cort_t_qc_0_0,
sm_subc_v_qc_0_0,
full_df_0_0))
na.omit(a)


# These do not need to be converted into factors
latest_mtbi_mechanism
race

full_df_0_0$household_income <- as.factor(full_df_0_0$household_income)
full_df_0_0$race <- as.factor(full_df_0_0$race)


# m = 5 and maxit = 10 are default settings
imputed_0_0 <- mice(full_df_0_0, m = 5, maxit = 10, seed = 42, remove.collinear = FALSE)


(full_df_0_0_ns <- full_df_0_0[, -1])

sum(is.na(full_df_0_0_ns[, 1]))



# Columns with missing data
a <- names(which(colSums(is.na(full_df_0_0_ns)) > 0))

b <- full_df_0_0[, a]



vis_missing_by_df(df_list_no_neuroimaging_0_0)


b |>
    dplyr::select(-dplyr::starts_with("nih")) |>
    na.omit() |>
    dim()

q <- b |> dplyr::select(dplyr::starts_with("latest"))

q <- detail_mtbi(abcd_otbi01, subjects = mtbi_subjects_0)

sum(is.na(q$"latest_mtbi_mechanism"))

sum(is.na(q$"latest_mtbi_age"))

q

# There is a lot to unravel here - seems like the TBI extraction functions are
#  still not correct.




colnames(full_df_0_0_ns)


imputed_0_0 <- mice(full_df_0_0_ns, m = 1, maxit = 1, seed = 42)

imputed_0_0$loggedEvents

colnames(full_df_0_0_ns)



all.equal(full_df_0_0, full_df, check.attributes = FALSE)

all.equal(imputed_0_0, imputed, check.attributes = FALSE)


# Now running imputed^

# View a summary of which variables were added by the imputation
imputed_0_0$imp

# Isolate the imputed data
imputed_non_imaging_0_0 <- complete(imputed_0_0)

as_mtbi_loc_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", "latest_mtbi_loc")
as_mtbi_mechanism_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", "latest_mtbi_mechanism")
as_mtbi_mem_daze_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", "latest_mtbi_mem_daze")
d_income_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", "household_income")
d_interview_age_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", "interview_age")
d_mtbi_age_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", "latest_mtbi_age")
d_pubertal_status_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", "pubertal_status")
d_race_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", "race")
d_sex_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", "M")
mh_headaches_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", "headache")
mh_mtbi_count_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", "mtbi_count")
p_loneliness_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", "ss_friend":"os_close_friend")
p_screen_time_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", dplyr::contains("screentime"))
p_family_function_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", "q1_fight":"q9_yell")
p_sports_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", dplyr::contains("activities"))
p_prosocial_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", "q1":"q3")
p_parent_psych_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", dplyr::contains("asr_scr"))
p_exercise_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", dplyr::contains("physical_activity"))
cbcl_headaches_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", "cbcl_headaches")
cbcl_nausea_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", "cbcl_nausea")
cbcl_vomiting_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", "cbcl_vomiting")
cbcl_dizzy_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", "cbcl_dizzy")
cbcl_overtired_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", "cbcl_overtired")
cbcl_sleeping_more_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", "cbcl_sleeping_more")
cbcl_sleeping_less_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", "cbcl_sleeping_less")
cbcl_depress_r_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", "cbcl_depress_r")
cbcl_anxiety_r_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", "cbcl_anxiety_r")
cbcl_attention_r_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", "cbcl_attention_r")
cbcl_aggressive_r_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", "cbcl_aggressive_r")
sds_sleep_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", dplyr::starts_with("sleep"))
nihtbx_list_fc_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", "nihtbx_list_fc")
nihtbx_pattern_fc_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", "nihtbx_pattern_fc")
nihtbx_cardsort_fc_imp_0_0 <- imputed_non_imaging_0_0 |> dplyr::select("subjectkey", "nihtbx_cardsort_fc")

#as_mtbi_loc_imp <- read_csv(input_data("as_mtbi_loc_imp.csv"))
#as_mtbi_mechanism_imp <- read_csv(input_data("as_mtbi_mechanism_imp.csv"))
#as_mtbi_mem_daze_imp <- read_csv(input_data("as_mtbi_mem_daze_imp.csv"))
#d_income_imp <- read_csv(input_data("d_income_imp.csv"))
#d_interview_age_imp <- read_csv(input_data("d_interview_age_imp.csv"))
#d_mtbi_age_imp <- read_csv(input_data("d_mtbi_age_imp.csv"))
#d_pubertal_status_imp <- read_csv(input_data("d_pubertal_status_imp.csv"))
#d_race_imp <- read_csv(input_data("d_race_imp.csv"))
#d_sex_imp <- read_csv(input_data("d_sex_imp.csv"))
#mh_headaches_imp <- read_csv(input_data("mh_headaches_imp.csv"))
#mh_mtbi_count_imp <- read_csv(input_data("mh_mtbi_count_imp.csv"))
#p_loneliness_imp <- read_csv(input_data("p_loneliness_imp.csv"))
#p_screen_time_imp <- read_csv(input_data("p_screen_time_imp.csv"))
#p_family_function_imp <- read_csv(input_data("p_family_function_imp.csv"))
#p_sports_imp <- read_csv(input_data("p_sports_imp.csv"))
#p_prosocial_imp <- read_csv(input_data("p_prosocial_imp.csv"))
#p_parent_psych_imp <- read_csv(input_data("p_parent_psych_imp.csv"))
#p_exercise_imp <- read_csv(input_data("p_exercise_imp.csv"))
#cbcl_headaches_imp <- read_csv(input_data("cbcl_headaches_imp.csv"))
#cbcl_nausea_imp <- read_csv(input_data("cbcl_nausea_imp.csv"))
#cbcl_vomiting_imp <- read_csv(input_data("cbcl_vomiting_imp.csv"))
#cbcl_dizzy_imp <- read_csv(input_data("cbcl_dizzy_imp.csv"))
#cbcl_overtired_imp <- read_csv(input_data("cbcl_overtired_imp.csv"))
#cbcl_sleeping_more_imp <- read_csv(input_data("cbcl_sleeping_more_imp.csv"))
#cbcl_sleeping_less_imp <- read_csv(input_data("cbcl_sleeping_less_imp.csv"))
#cbcl_depress_r_imp <- read_csv(input_data("cbcl_depress_r_imp.csv"))
#cbcl_anxiety_r_imp <- read_csv(input_data("cbcl_anxiety_r_imp.csv"))
#cbcl_attention_r_imp <- read_csv(input_data("cbcl_attention_r_imp.csv"))
#cbcl_aggressive_r_imp <- read_csv(input_data("cbcl_aggressive_r_imp.csv"))
#sds_sleep_imp <- read_csv(input_data("sds_sleep_imp.csv"))
#nihtbx_list_fc_imp <- read_csv(input_data("nihtbx_list_fc_imp.csv"))
#nihtbx_pattern_fc_imp <- read_csv(input_data("nihtbx_pattern_fc_imp.csv"))
#nihtbx_cardsort_fc_imp <- read_csv(input_data("nihtbx_cardsort_fc_imp.csv"))
#
#
## All pass!
#ae(as_mtbi_loc_imp, as_mtbi_loc_imp_0_0)
#ae(d_interview_age_imp, d_interview_age_imp_0_0)
#ae(d_mtbi_age_imp, d_mtbi_age_imp_0_0)
#all_equal(as_mtbi_mechanism_imp, as_mtbi_mechanism_imp_0_0, check.attributes = FALSE, convert = TRUE)
#ae2(as_mtbi_mechanism_imp, as_mtbi_mechanism_imp_0_0)
#
#ae2 <- function(x, y) {
#    return(all_equal(x, y, check.attributes = FALSE, convert = TRUE))
#}
#
#ae2(as_mtbi_mem_daze_imp, as_mtbi_mem_daze_imp_0_0)
#ae2(d_income_imp, col_to_num_all_possible(d_income_imp_0_0))
#ae(d_pubertal_status_imp, d_pubertal_status_imp_0_0)
#
#d_race_imp_0_0$race <- as.character(d_race_imp_0_0$race)
#ae(d_race_imp, d_race_imp_0_0)
#ae(d_sex_imp, d_sex_imp_0_0)
#ae(mh_headaches_imp, mh_headaches_imp_0_0)
#ae(mh_mtbi_count_imp, mh_mtbi_count_imp_0_0)
#ae(p_loneliness_imp, p_loneliness_imp_0_0)
#ae(p_screen_time_imp, p_screen_time_imp_0_0)
#ae(p_family_function_imp, p_family_function_imp_0_0)
#ae(p_sports_imp, p_sports_imp_0_0)
#ae(p_prosocial_imp, p_prosocial_imp_0_0)
#ae(p_parent_psych_imp, p_parent_psych_imp_0_0)
#ae(p_exercise_imp, p_exercise_imp_0_0)
#ae(cbcl_headaches_imp, cbcl_headaches_imp_0_0)
#ae(cbcl_nausea_imp, cbcl_nausea_imp_0_0)
#ae(cbcl_vomiting_imp, cbcl_vomiting_imp_0_0)
#ae(cbcl_dizzy_imp, cbcl_dizzy_imp_0_0)
#ae(cbcl_overtired_imp, cbcl_overtired_imp_0_0)
#ae(cbcl_sleeping_more_imp, cbcl_sleeping_more_imp_0_0)
#ae(cbcl_sleeping_less_imp, cbcl_sleeping_less_imp_0_0)
#ae(cbcl_depress_r_imp, cbcl_depress_r_imp_0_0)
#ae(cbcl_anxiety_r_imp, cbcl_anxiety_r_imp_0_0)
#ae(cbcl_attention_r_imp, cbcl_attention_r_imp_0_0)
#ae(cbcl_aggressive_r_imp, cbcl_aggressive_r_imp_0_0)
#ae(sds_sleep_imp, sds_sleep_imp_0_0)
#ae(nihtbx_list_fc_imp, nihtbx_list_fc_imp_0_0)
#ae(nihtbx_pattern_fc_imp, nihtbx_pattern_fc_imp_0_0)
#ae(nihtbx_cardsort_fc_imp, nihtbx_cardsort_fc_imp_0_0)

write_csv(as_mtbi_loc_imp_0_0, input_path("as_mtbi_loc_imp_0_0.csv", date = TRUE))
write_csv(as_mtbi_mechanism_imp_0_0, input_path("as_mtbi_mechanism_imp_0_0.csv", date = TRUE))
write_csv(as_mtbi_mem_daze_imp_0_0, input_path("as_mtbi_mem_daze_imp_0_0.csv", date = TRUE))
write_csv(d_income_imp_0_0, input_path("d_income_imp_0_0.csv", date = TRUE))
write_csv(d_interview_age_imp_0_0, input_path("d_interview_age_imp_0_0.csv", date = TRUE))
write_csv(d_mtbi_age_imp_0_0, input_path("d_mtbi_age_imp_0_0.csv", date = TRUE))
write_csv(d_pubertal_status_imp_0_0, input_path("d_pubertal_status_imp_0_0.csv", date = TRUE))
write_csv(d_race_imp_0_0, input_path("d_race_imp_0_0.csv", date = TRUE))
write_csv(d_sex_imp_0_0, input_path("d_sex_imp_0_0.csv", date = TRUE))
write_csv(mh_headaches_imp_0_0, input_path("mh_headaches_imp_0_0.csv", date = TRUE))
write_csv(mh_mtbi_count_imp_0_0, input_path("mh_mtbi_count_imp_0_0.csv", date = TRUE))
write_csv(p_loneliness_imp_0_0, input_path("p_loneliness_imp_0_0.csv", date = TRUE))
write_csv(p_screen_time_imp_0_0, input_path("p_screen_time_imp_0_0.csv", date = TRUE))
write_csv(p_family_function_imp_0_0, input_path("p_family_function_imp_0_0.csv", date = TRUE))
write_csv(p_sports_imp_0_0, input_path("p_sports_imp_0_0.csv", date = TRUE))
write_csv(p_prosocial_imp_0_0, input_path("p_prosocial_imp_0_0.csv", date = TRUE))
write_csv(p_parent_psych_imp_0_0, input_path("p_parent_psych_imp_0_0.csv", date = TRUE))
write_csv(p_exercise_imp_0_0, input_path("p_exercise_imp_0_0.csv", date = TRUE))
write_csv(cbcl_headaches_imp_0_0, input_path("cbcl_headaches_imp_0_0.csv", date = TRUE))
write_csv(cbcl_nausea_imp_0_0, input_path("cbcl_nausea_imp_0_0.csv", date = TRUE))
write_csv(cbcl_vomiting_imp_0_0, input_path("cbcl_vomiting_imp_0_0.csv", date = TRUE))
write_csv(cbcl_dizzy_imp_0_0, input_path("cbcl_dizzy_imp_0_0.csv", date = TRUE))
write_csv(cbcl_overtired_imp_0_0, input_path("cbcl_overtired_imp_0_0.csv", date = TRUE))
write_csv(cbcl_sleeping_more_imp_0_0, input_path("cbcl_sleeping_more_imp_0_0.csv", date = TRUE))
write_csv(cbcl_sleeping_less_imp_0_0, input_path("cbcl_sleeping_less_imp_0_0.csv", date = TRUE))
write_csv(cbcl_depress_r_imp_0_0, input_path("cbcl_depress_r_imp_0_0.csv", date = TRUE))
write_csv(cbcl_anxiety_r_imp_0_0, input_path("cbcl_anxiety_r_imp_0_0.csv", date = TRUE))
write_csv(cbcl_attention_r_imp_0_0, input_path("cbcl_attention_r_imp_0_0.csv", date = TRUE))
write_csv(cbcl_aggressive_r_imp_0_0, input_path("cbcl_aggressive_r_imp_0_0.csv", date = TRUE))
write_csv(sds_sleep_imp_0_0, input_path("sds_sleep_imp_0_0.csv", date = TRUE))
write_csv(nihtbx_list_fc_imp_0_0, input_path("nihtbx_list_fc_imp_0_0.csv", date = TRUE))
write_csv(nihtbx_pattern_fc_imp_0_0, input_path("nihtbx_pattern_fc_imp_0_0.csv", date = TRUE))
write_csv(nihtbx_cardsort_fc_imp_0_0, input_path("nihtbx_cardsort_fc_imp_0_0.csv", date = TRUE))
```

## Convert the raw CBCL scores into thresholded ones
```{r}
cbcl_depress_r_imp_0_0 <- read_csv(input_path("2023_04_06_cbcl_depress_r_imp_0_0.csv"))
cbcl_anxiety_r_imp_0_0 <- read_csv(input_path("2023_04_06_cbcl_anxiety_r_imp_0_0.csv"))
cbcl_attention_r_imp_0_0 <- read_csv(input_path("2023_04_06_cbcl_attention_r_imp_0_0.csv"))
cbcl_aggressive_r_imp_0_0 <- read_csv(input_path("2023_04_06_cbcl_aggressive_r_imp_0_0.csv"))

cbcl_depress_imp_0_0 <- cbcl_raw_to_thresh(cbcl_depress_r_imp_0_0)
cbcl_anxiety_imp_0_0 <- cbcl_raw_to_thresh(cbcl_anxiety_r_imp_0_0)
cbcl_attention_imp_0_0 <- cbcl_raw_to_thresh(cbcl_attention_r_imp_0_0)
cbcl_aggressive_imp_0_0 <- cbcl_raw_to_thresh(cbcl_aggressive_r_imp_0_0)

write_csv(cbcl_depress_imp_0_0, input_path("cbcl_depress_imp_0_0.csv", date = TRUE))
write_csv(cbcl_anxiety_imp_0_0, input_path("cbcl_anxiety_imp_0_0.csv", date = TRUE))
write_csv(cbcl_attention_imp_0_0, input_path("cbcl_attention_imp_0_0.csv", date = TRUE))
write_csv(cbcl_aggressive_imp_0_0, input_path("cbcl_aggressive_imp_0_0.csv", date = TRUE))
```


## Training and testing data splits

```{r eval = FALSE}
library(abcdutils)
library(scabcd)
library(readr)
library(here)


# Functions to import data from carbon
input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))


# Importing data
as_mtbi_loc_0_0 <- read_csv(input_path("2023_04_06_as_mtbi_loc_imp_0_0.csv"))
as_mtbi_mechanism_0_0 <- read_csv(input_path("2023_04_06_as_mtbi_mechanism_imp_0_0.csv"))
as_mtbi_mem_daze_0_0 <- read_csv(input_path("2023_04_06_as_mtbi_mem_daze_imp_0_0.csv"))
d_income_0_0 <- read_csv(input_path("2023_04_06_d_income_imp_0_0.csv"))
d_interview_age_0_0 <- read_csv(input_path("2023_04_06_d_interview_age_imp_0_0.csv"))
d_mtbi_age_0_0 <- read_csv(input_path("2023_04_06_d_mtbi_age_imp_0_0.csv"))
d_pubertal_status_0_0 <- read_csv(input_path("2023_04_06_d_pubertal_status_imp_0_0.csv"))
d_race_0_0 <- read_csv(input_path("2023_04_06_d_race_imp_0_0.csv"))
d_sex_0_0 <- read_csv(input_path("2023_04_06_d_sex_imp_0_0.csv"))
mh_headaches_0_0 <- read_csv(input_path("2023_04_06_mh_headaches_imp_0_0.csv"))
mh_mtbi_count_0_0 <- read_csv(input_path("2023_04_06_mh_mtbi_count_imp_0_0.csv"))
dm_all_wmnd_0_0 <- read_csv(input_path("2023_04_06_dm_all_wmnd_qc_0_0.csv"))
rm_gord_cor_0_0 <- read_csv(input_path("2023_04_06_rm_gord_cor_qc_0_0.csv"))
rm_gord_var_0_0 <- read_csv(input_path("2023_04_06_rm_gord_var_qc_0_0.csv"))
rm_subc_cor_0_0 <- read_csv(input_path("2023_04_06_rm_subc_cor_qc_0_0.csv"))
rm_subc_var_0_0 <- read_csv(input_path("2023_04_06_rm_subc_var_qc_0_0.csv"))
sm_cort_sa_0_0 <- read_csv(input_path("2023_04_06_sm_cort_sa_qc_0_0.csv"))
sm_cort_t_0_0 <- read_csv(input_path("2023_04_06_sm_cort_t_qc_0_0.csv"))
sm_subc_v_0_0 <- read_csv(input_path("2023_04_06_sm_subc_v_qc_0_0.csv"))
p_loneliness_0_0 <- read_csv(input_path("2023_04_06_p_loneliness_imp_0_0.csv"))
p_screen_time_0_0 <- read_csv(input_path("2023_04_06_p_screen_time_imp_0_0.csv"))
p_family_function_0_0 <- read_csv(input_path("2023_04_06_p_family_function_imp_0_0.csv"))
p_sports_0_0 <- read_csv(input_path("2023_04_06_p_sports_imp_0_0.csv"))
p_prosocial_0_0 <- read_csv(input_path("2023_04_06_p_prosocial_imp_0_0.csv"))
p_parent_psych_0_0 <- read_csv(input_path("2023_04_06_p_parent_psych_imp_0_0.csv"))
p_exercise_0_0 <- read_csv(input_path("2023_04_06_p_exercise_imp_0_0.csv"))
cbcl_headaches_0_0 <- read_csv(input_path("2023_04_06_cbcl_headaches_imp_0_0.csv"))
cbcl_nausea_0_0 <- read_csv(input_path("2023_04_06_cbcl_nausea_imp_0_0.csv"))
cbcl_vomiting_0_0 <- read_csv(input_path("2023_04_06_cbcl_vomiting_imp_0_0.csv"))
cbcl_dizzy_0_0 <- read_csv(input_path("2023_04_06_cbcl_dizzy_imp_0_0.csv"))
cbcl_overtired_0_0 <- read_csv(input_path("2023_04_06_cbcl_overtired_imp_0_0.csv"))
cbcl_sleeping_more_0_0 <- read_csv(input_path("2023_04_06_cbcl_sleeping_more_imp_0_0.csv"))
cbcl_sleeping_less_0_0 <- read_csv(input_path("2023_04_06_cbcl_sleeping_less_imp_0_0.csv"))
cbcl_depress_0_0 <- read_csv(input_path("2023_04_06_cbcl_depress_imp_0_0.csv"))
cbcl_anxiety_0_0 <- read_csv(input_path("2023_04_06_cbcl_anxiety_imp_0_0.csv"))
cbcl_attention_0_0 <- read_csv(input_path("2023_04_06_cbcl_attention_imp_0_0.csv"))
cbcl_aggressive_0_0 <- read_csv(input_path("2023_04_06_cbcl_aggressive_imp_0_0.csv"))
sds_sleep_0_0 <- read_csv(input_path("2023_04_06_sds_sleep_imp_0_0.csv"))
nihtbx_list_fc_0_0 <- read_csv(input_path("2023_04_06_nihtbx_list_fc_imp_0_0.csv"))
nihtbx_pattern_fc_0_0 <- read_csv(input_path("2023_04_06_nihtbx_pattern_fc_imp_0_0.csv"))
nihtbx_cardsort_fc_0_0 <- read_csv(input_path("2023_04_06_nihtbx_cardsort_fc_imp_0_0.csv"))


# Filtering to common subjects
common_subs <- common_subjects(list(
    as_mtbi_loc_0_0,
    as_mtbi_mechanism_0_0,
    as_mtbi_mem_daze_0_0,
    d_income_0_0,
    d_interview_age_0_0,
    d_mtbi_age_0_0,
    d_pubertal_status_0_0,
    d_race_0_0,
    d_sex_0_0,
    mh_headaches_0_0,
    mh_mtbi_count_0_0,
    dm_all_wmnd_0_0,
    rm_gord_cor_0_0,
    rm_gord_var_0_0,
    rm_subc_cor_0_0,
    rm_subc_var_0_0,
    sm_cort_sa_0_0,
    sm_cort_t_0_0,
    sm_subc_v_0_0,
    p_loneliness_0_0,
    p_screen_time_0_0,
    p_family_function_0_0,
    p_sports_0_0,
    p_prosocial_0_0,
    p_parent_psych_0_0,
    p_exercise_0_0,
    cbcl_headaches_0_0,
    cbcl_nausea_0_0,
    cbcl_vomiting_0_0,
    cbcl_dizzy_0_0,
    cbcl_overtired_0_0,
    cbcl_sleeping_more_0_0,
    cbcl_sleeping_less_0_0,
    cbcl_depress_0_0,
    cbcl_anxiety_0_0,
    cbcl_attention_0_0,
    cbcl_aggressive_0_0,
    sds_sleep_0_0))

# Assigning common subjects into training and testing sets
assigned_df_0 <- train_test_assign(train_frac = 0.8, subjects = common_subs)

# Generate training set
as_mtbi_loc_0_0_train <- keep_split(as_mtbi_loc_0_0, assigned_df_0, "train")
as_mtbi_mechanism_0_0_train <- keep_split(as_mtbi_mechanism_0_0, assigned_df_0, "train")
as_mtbi_mem_daze_0_0_train <- keep_split(as_mtbi_mem_daze_0_0, assigned_df_0, "train")
d_income_0_0_train <- keep_split(d_income_0_0, assigned_df_0, "train")
d_interview_age_0_0_train <- keep_split(d_interview_age_0_0, assigned_df_0, "train")
d_mtbi_age_0_0_train <- keep_split(d_mtbi_age_0_0, assigned_df_0, "train")
d_pubertal_status_0_0_train <- keep_split(d_pubertal_status_0_0, assigned_df_0, "train")
d_race_0_0_train <- keep_split(d_race_0_0, assigned_df_0, "train")
d_sex_0_0_train <- keep_split(d_sex_0_0, assigned_df_0, "train")
mh_headaches_0_0_train <- keep_split(mh_headaches_0_0, assigned_df_0, "train")
mh_mtbi_count_0_0_train <- keep_split(mh_mtbi_count_0_0, assigned_df_0, "train")
dm_all_wmnd_0_0_train <- keep_split(dm_all_wmnd_0_0, assigned_df_0, "train")
rm_gord_cor_0_0_train <- keep_split(rm_gord_cor_0_0, assigned_df_0, "train")
rm_gord_var_0_0_train <-
    keep_split(rm_gord_var_0_0, assigned_df_0, "train")
rm_subc_cor_0_0_train <- keep_split(rm_subc_cor_0_0, assigned_df_0, "train")
rm_subc_var_0_0_train <- keep_split(rm_subc_var_0_0, assigned_df_0, "train")
sm_cort_sa_0_0_train <- keep_split(sm_cort_sa_0_0, assigned_df_0, "train")
sm_cort_t_0_0_train <- keep_split(sm_cort_t_0_0, assigned_df_0, "train")
sm_subc_v_0_0_train <- keep_split(sm_subc_v_0_0, assigned_df_0, "train")
p_loneliness_0_0_train <- keep_split(p_loneliness_0_0, assigned_df_0, "train")
p_screen_time_0_0_train <- keep_split(p_screen_time_0_0, assigned_df_0, "train")
p_family_function_0_0_train <- keep_split(p_family_function_0_0, assigned_df_0, "train")
p_sports_0_0_train <- keep_split(p_sports_0_0, assigned_df_0, "train")
p_prosocial_0_0_train <- keep_split(p_prosocial_0_0, assigned_df_0, "train")
p_parent_psych_0_0_train <- keep_split(p_parent_psych_0_0, assigned_df_0, "train")
p_exercise_0_0_train <- keep_split(p_exercise_0_0, assigned_df_0, "train")
cbcl_headaches_0_0_train <- keep_split(cbcl_headaches_0_0, assigned_df_0, "train")
cbcl_nausea_0_0_train <- keep_split(cbcl_nausea_0_0, assigned_df_0, "train")
cbcl_vomiting_0_0_train <- keep_split(cbcl_vomiting_0_0, assigned_df_0, "train")
cbcl_dizzy_0_0_train <- keep_split(cbcl_dizzy_0_0, assigned_df_0, "train")
cbcl_overtired_0_0_train <- keep_split(cbcl_overtired_0_0, assigned_df_0, "train")
cbcl_sleeping_more_0_0_train <- keep_split(cbcl_sleeping_more_0_0, assigned_df_0, "train")
cbcl_sleeping_less_0_0_train <- keep_split(cbcl_sleeping_less_0_0, assigned_df_0, "train")
cbcl_depress_0_0_train <- keep_split(cbcl_depress_0_0, assigned_df_0, "train")
cbcl_anxiety_0_0_train <- keep_split(cbcl_anxiety_0_0, assigned_df_0, "train")
cbcl_attention_0_0_train <- keep_split(cbcl_attention_0_0, assigned_df_0, "train")
cbcl_aggressive_0_0_train <- keep_split(cbcl_aggressive_0_0, assigned_df_0, "train")
sds_sleep_0_0_train <- keep_split(sds_sleep_0_0, assigned_df_0, "train")

# Generate testing set
as_mtbi_loc_0_0_test <- keep_split(as_mtbi_loc_0_0, assigned_df_0, "test")
as_mtbi_mechanism_0_0_test <- keep_split(as_mtbi_mechanism_0_0, assigned_df_0, "test")
as_mtbi_mem_daze_0_0_test <- keep_split(as_mtbi_mem_daze_0_0, assigned_df_0, "test")
d_income_0_0_test <- keep_split(d_income_0_0, assigned_df_0, "test")
d_interview_age_0_0_test <- keep_split(d_interview_age_0_0, assigned_df_0, "test")
d_mtbi_age_0_0_test <- keep_split(d_mtbi_age_0_0, assigned_df_0, "test")
d_pubertal_status_0_0_test <- keep_split(d_pubertal_status_0_0, assigned_df_0, "test")
d_race_0_0_test <- keep_split(d_race_0_0, assigned_df_0, "test")
d_sex_0_0_test <- keep_split(d_sex_0_0, assigned_df_0, "test")
mh_headaches_0_0_test <- keep_split(mh_headaches_0_0, assigned_df_0, "test")
mh_mtbi_count_0_0_test <- keep_split(mh_mtbi_count_0_0, assigned_df_0, "test")
dm_all_wmnd_0_0_test <- keep_split(dm_all_wmnd_0_0, assigned_df_0, "test")
rm_gord_cor_0_0_test <- keep_split(rm_gord_cor_0_0, assigned_df_0, "test")
rm_gord_var_0_0_test <- keep_split(rm_gord_var_0_0, assigned_df_0, "test")
rm_subc_cor_0_0_test <- keep_split(rm_subc_cor_0_0, assigned_df_0, "test")
rm_subc_var_0_0_test <- keep_split(rm_subc_var_0_0, assigned_df_0, "test")
sm_cort_sa_0_0_test <- keep_split(sm_cort_sa_0_0, assigned_df_0, "test")
sm_cort_t_0_0_test <- keep_split(sm_cort_t_0_0, assigned_df_0, "test")
sm_subc_v_0_0_test <- keep_split(sm_subc_v_0_0, assigned_df_0, "test")
p_loneliness_0_0_test <- keep_split(p_loneliness_0_0, assigned_df_0, "test")
p_screen_time_0_0_test <- keep_split(p_screen_time_0_0, assigned_df_0, "test")
p_family_function_0_0_test <- keep_split(p_family_function_0_0, assigned_df_0, "test")
p_sports_0_0_test <- keep_split(p_sports_0_0, assigned_df_0, "test")
p_prosocial_0_0_test <- keep_split(p_prosocial_0_0, assigned_df_0, "test")
p_parent_psych_0_0_test <- keep_split(p_parent_psych_0_0, assigned_df_0, "test")
p_exercise_0_0_test <- keep_split(p_exercise_0_0, assigned_df_0, "test")
cbcl_headaches_0_0_test <- keep_split(cbcl_headaches_0_0, assigned_df_0, "test")
cbcl_nausea_0_0_test <- keep_split(cbcl_nausea_0_0, assigned_df_0, "test")
cbcl_vomiting_0_0_test <- keep_split(cbcl_vomiting_0_0, assigned_df_0, "test")
cbcl_dizzy_0_0_test <- keep_split(cbcl_dizzy_0_0, assigned_df_0, "test")
cbcl_overtired_0_0_test <- keep_split(cbcl_overtired_0_0, assigned_df_0, "test")
cbcl_sleeping_more_0_0_test <- keep_split(cbcl_sleeping_more_0_0, assigned_df_0, "test")
cbcl_sleeping_less_0_0_test <- keep_split(cbcl_sleeping_less_0_0, assigned_df_0, "test")
cbcl_depress_0_0_test <- keep_split(cbcl_depress_0_0, assigned_df_0, "test")
cbcl_anxiety_0_0_test <- keep_split(cbcl_anxiety_0_0, assigned_df_0, "test")
cbcl_attention_0_0_test <- keep_split(cbcl_attention_0_0, assigned_df_0, "test")
cbcl_aggressive_0_0_test <- keep_split(cbcl_aggressive_0_0, assigned_df_0, "test")
sds_sleep_0_0_test <- keep_split(sds_sleep_0_0, assigned_df_0, "test")

# Generate full set (note that this is structured specifically in row order of
#  training subjects followed by testing subjects)
as_mtbi_loc_0_0_full <- rbind(as_mtbi_loc_0_0_train, as_mtbi_loc_0_0_test)
as_mtbi_mechanism_0_0_full <- rbind(as_mtbi_mechanism_0_0_train, as_mtbi_mechanism_0_0_test)
as_mtbi_mem_daze_0_0_full <- rbind(as_mtbi_mem_daze_0_0_train, as_mtbi_mem_daze_0_0_test)
d_income_0_0_full <- rbind(d_income_0_0_train, d_income_0_0_test)
d_interview_age_0_0_full <- rbind(d_interview_age_0_0_train, d_interview_age_0_0_test)
d_mtbi_age_0_0_full <- rbind(d_mtbi_age_0_0_train, d_mtbi_age_0_0_test)
d_pubertal_status_0_0_full <- rbind(d_pubertal_status_0_0_train, d_pubertal_status_0_0_test)
d_race_0_0_full <- rbind(d_race_0_0_train, d_race_0_0_test)
d_sex_0_0_full <- rbind(d_sex_0_0_train, d_sex_0_0_test)
mh_headaches_0_0_full <- rbind(mh_headaches_0_0_train, mh_headaches_0_0_test)
mh_mtbi_count_0_0_full <- rbind(mh_mtbi_count_0_0_train, mh_mtbi_count_0_0_test)
dm_all_wmnd_0_0_full <- rbind(dm_all_wmnd_0_0_train, dm_all_wmnd_0_0_test)
rm_gord_cor_0_0_full <- rbind(rm_gord_cor_0_0_train, rm_gord_cor_0_0_test)
rm_gord_var_0_0_full <- rbind(rm_gord_var_0_0_train, rm_gord_var_0_0_test)
rm_subc_cor_0_0_full <- rbind(rm_subc_cor_0_0_train, rm_subc_cor_0_0_test)
rm_subc_var_0_0_full <- rbind(rm_subc_var_0_0_train, rm_subc_var_0_0_test)
sm_cort_sa_0_0_full <- rbind(sm_cort_sa_0_0_train, sm_cort_sa_0_0_test)
sm_cort_t_0_0_full <- rbind(sm_cort_t_0_0_train, sm_cort_t_0_0_test)
sm_subc_v_0_0_full <- rbind(sm_subc_v_0_0_train, sm_subc_v_0_0_test)
p_loneliness_0_0_full <- rbind(p_loneliness_0_0_train, p_loneliness_0_0_test)
p_screen_time_0_0_full <- rbind(p_screen_time_0_0_train, p_screen_time_0_0_test)
p_family_function_0_0_full <- rbind(p_family_function_0_0_train, p_family_function_0_0_test)
p_sports_0_0_full <- rbind(p_sports_0_0_train, p_sports_0_0_test)
p_prosocial_0_0_full <- rbind(p_prosocial_0_0_train, p_prosocial_0_0_test)
p_parent_psych_0_0_full <- rbind(p_parent_psych_0_0_train, p_parent_psych_0_0_test)
p_exercise_0_0_full <- rbind(p_exercise_0_0_train, p_exercise_0_0_test)
cbcl_headaches_0_0_full <- rbind(cbcl_headaches_0_0_train, cbcl_headaches_0_0_test)
cbcl_nausea_0_0_full <- rbind(cbcl_nausea_0_0_train, cbcl_nausea_0_0_test)
cbcl_vomiting_0_0_full <- rbind(cbcl_vomiting_0_0_train, cbcl_vomiting_0_0_test)
cbcl_dizzy_0_0_full <- rbind(cbcl_dizzy_0_0_train, cbcl_dizzy_0_0_test)
cbcl_overtired_0_0_full <- rbind(cbcl_overtired_0_0_train, cbcl_overtired_0_0_test)
cbcl_sleeping_more_0_0_full <- rbind(cbcl_sleeping_more_0_0_train, cbcl_sleeping_more_0_0_test)
cbcl_sleeping_less_0_0_full <- rbind(cbcl_sleeping_less_0_0_train, cbcl_sleeping_less_0_0_test)
cbcl_depress_0_0_full <- rbind(cbcl_depress_0_0_train, cbcl_depress_0_0_test)
cbcl_anxiety_0_0_full <- rbind(cbcl_anxiety_0_0_train, cbcl_anxiety_0_0_test)
cbcl_attention_0_0_full <- rbind(cbcl_attention_0_0_train, cbcl_attention_0_0_test)
cbcl_aggressive_0_0_full <- rbind(cbcl_aggressive_0_0_train, cbcl_aggressive_0_0_test)


# Export training set
write_csv(as_mtbi_loc_0_0_train, proc_path("as_mtbi_loc_0_0_train.csv", date = TRUE))
write_csv(as_mtbi_mechanism_0_0_train, proc_path("as_mtbi_mechanism_0_0_train.csv", date = TRUE))
write_csv(as_mtbi_mem_daze_0_0_train, proc_path("as_mtbi_mem_daze_0_0_train.csv", date = TRUE))
write_csv(d_income_0_0_train, proc_path("d_income_0_0_train.csv", date = TRUE))
write_csv(d_interview_age_0_0_train, proc_path("d_interview_age_0_0_train.csv", date = TRUE))
write_csv(d_mtbi_age_0_0_train, proc_path("d_mtbi_age_0_0_train.csv", date = TRUE))
write_csv(d_pubertal_status_0_0_train, proc_path("d_pubertal_status_0_0_train.csv", date = TRUE))
write_csv(d_race_0_0_train, proc_path("d_race_0_0_train.csv", date = TRUE))
write_csv(d_sex_0_0_train, proc_path("d_sex_0_0_train.csv", date = TRUE))
write_csv(mh_headaches_0_0_train, proc_path("mh_headaches_0_0_train.csv", date = TRUE))
write_csv(mh_mtbi_count_0_0_train, proc_path("mh_mtbi_count_0_0_train.csv", date = TRUE))
write_csv(dm_all_wmnd_0_0_train, proc_path("dm_all_wmnd_0_0_train.csv", date = TRUE))
write_csv(rm_gord_cor_0_0_train, proc_path("rm_gord_cor_0_0_train.csv", date = TRUE))
write_csv(rm_gord_var_0_0_train, proc_path("rm_gord_var_0_0_train.csv", date = TRUE))
write_csv(rm_subc_cor_0_0_train, proc_path("rm_subc_cor_0_0_train.csv", date = TRUE))
write_csv(rm_subc_var_0_0_train, proc_path("rm_subc_var_0_0_train.csv", date = TRUE))
write_csv(sm_cort_sa_0_0_train, proc_path("sm_cort_sa_0_0_train.csv", date = TRUE))
write_csv(sm_cort_t_0_0_train, proc_path("sm_cort_t_0_0_train.csv", date = TRUE))
write_csv(sm_subc_v_0_0_train, proc_path("sm_subc_v_0_0_train.csv", date = TRUE))
write_csv(p_loneliness_0_0_train, proc_path("p_loneliness_0_0_train.csv", date = TRUE))
write_csv(p_screen_time_0_0_train, proc_path("p_screen_time_0_0_train.csv", date = TRUE))
write_csv(p_family_function_0_0_train, proc_path("p_family_function_0_0_train.csv", date = TRUE))
write_csv(p_sports_0_0_train, proc_path("p_sports_0_0_train.csv", date = TRUE))
write_csv(p_prosocial_0_0_train, proc_path("p_prosocial_0_0_train.csv", date = TRUE))
write_csv(p_parent_psych_0_0_train, proc_path("p_parent_psych_0_0_train.csv", date = TRUE))
write_csv(p_exercise_0_0_train, proc_path("p_exercise_0_0_train.csv", date = TRUE))
write_csv(cbcl_headaches_0_0_train, proc_path("cbcl_headaches_0_0_train.csv", date = TRUE))
write_csv(cbcl_nausea_0_0_train, proc_path("cbcl_nausea_0_0_train.csv", date = TRUE))
write_csv(cbcl_vomiting_0_0_train, proc_path("cbcl_vomiting_0_0_train.csv", date = TRUE))
write_csv(cbcl_dizzy_0_0_train, proc_path("cbcl_dizzy_0_0_train.csv", date = TRUE))
write_csv(cbcl_overtired_0_0_train, proc_path("cbcl_overtired_0_0_train.csv", date = TRUE))
write_csv(cbcl_sleeping_more_0_0_train, proc_path("cbcl_sleeping_more_0_0_train.csv", date = TRUE))
write_csv(cbcl_sleeping_less_0_0_train, proc_path("cbcl_sleeping_less_0_0_train.csv", date = TRUE))
write_csv(cbcl_depress_0_0_train, proc_path("cbcl_depress_0_0_train.csv", date = TRUE))
write_csv(cbcl_anxiety_0_0_train, proc_path("cbcl_anxiety_0_0_train.csv", date = TRUE))
write_csv(cbcl_attention_0_0_train, proc_path("cbcl_attention_0_0_train.csv", date = TRUE))
write_csv(cbcl_aggressive_0_0_train, proc_path("cbcl_aggressive_0_0_train.csv", date = TRUE))
write_csv(sds_sleep_0_0_train, proc_path("sds_sleep_0_0_train.csv", date = TRUE))

# Export testing set
write_csv(as_mtbi_loc_0_0_test, proc_path("as_mtbi_loc_0_0_test.csv", date = TRUE))
write_csv(as_mtbi_mechanism_0_0_test, proc_path("as_mtbi_mechanism_0_0_test.csv", date = TRUE))
write_csv(as_mtbi_mem_daze_0_0_test, proc_path("as_mtbi_mem_daze_0_0_test.csv", date = TRUE))
write_csv(d_income_0_0_test, proc_path("d_income_0_0_test.csv", date = TRUE))
write_csv(d_interview_age_0_0_test, proc_path("d_interview_age_0_0_test.csv", date = TRUE))
write_csv(d_mtbi_age_0_0_test, proc_path("d_mtbi_age_0_0_test.csv", date = TRUE))
write_csv(d_pubertal_status_0_0_test, proc_path("d_pubertal_status_0_0_test.csv", date = TRUE))
write_csv(d_race_0_0_test, proc_path("d_race_0_0_test.csv", date = TRUE))
write_csv(d_sex_0_0_test, proc_path("d_sex_0_0_test.csv", date = TRUE))
write_csv(mh_headaches_0_0_test, proc_path("mh_headaches_0_0_test.csv", date = TRUE))
write_csv(mh_mtbi_count_0_0_test, proc_path("mh_mtbi_count_0_0_test.csv", date = TRUE))
write_csv(dm_all_wmnd_0_0_test, proc_path("dm_all_wmnd_0_0_test.csv", date = TRUE))
write_csv(rm_gord_cor_0_0_test, proc_path("rm_gord_cor_0_0_test.csv", date = TRUE))
write_csv(rm_gord_var_0_0_test, proc_path("rm_gord_var_0_0_test.csv", date = TRUE))
write_csv(rm_subc_cor_0_0_test, proc_path("rm_subc_cor_0_0_test.csv", date = TRUE))
write_csv(rm_subc_var_0_0_test, proc_path("rm_subc_var_0_0_test.csv", date = TRUE))
write_csv(sm_cort_sa_0_0_test, proc_path("sm_cort_sa_0_0_test.csv", date = TRUE))
write_csv(sm_cort_t_0_0_test, proc_path("sm_cort_t_0_0_test.csv", date = TRUE))
write_csv(sm_subc_v_0_0_test, proc_path("sm_subc_v_0_0_test.csv", date = TRUE))
write_csv(p_loneliness_0_0_test, proc_path("p_loneliness_0_0_test.csv", date = TRUE))
write_csv(p_screen_time_0_0_test, proc_path("p_screen_time_0_0_test.csv", date = TRUE))
write_csv(p_family_function_0_0_test, proc_path("p_family_function_0_0_test.csv", date = TRUE))
write_csv(p_sports_0_0_test, proc_path("p_sports_0_0_test.csv", date = TRUE))
write_csv(p_prosocial_0_0_test, proc_path("p_prosocial_0_0_test.csv", date = TRUE))
write_csv(p_parent_psych_0_0_test, proc_path("p_parent_psych_0_0_test.csv", date = TRUE))
write_csv(p_exercise_0_0_test, proc_path("p_exercise_0_0_test.csv", date = TRUE))
write_csv(cbcl_headaches_0_0_test, proc_path("cbcl_headaches_0_0_test.csv", date = TRUE))
write_csv(cbcl_nausea_0_0_test, proc_path("cbcl_nausea_0_0_test.csv", date = TRUE))
write_csv(cbcl_vomiting_0_0_test, proc_path("cbcl_vomiting_0_0_test.csv", date = TRUE))
write_csv(cbcl_dizzy_0_0_test, proc_path("cbcl_dizzy_0_0_test.csv", date = TRUE))
write_csv(cbcl_overtired_0_0_test, proc_path("cbcl_overtired_0_0_test.csv", date = TRUE))
write_csv(cbcl_sleeping_more_0_0_test, proc_path("cbcl_sleeping_more_0_0_test.csv", date = TRUE))
write_csv(cbcl_sleeping_less_0_0_test, proc_path("cbcl_sleeping_less_0_0_test.csv", date = TRUE))
write_csv(cbcl_depress_0_0_test, proc_path("cbcl_depress_0_0_test.csv", date = TRUE))
write_csv(cbcl_anxiety_0_0_test, proc_path("cbcl_anxiety_0_0_test.csv", date = TRUE))
write_csv(cbcl_attention_0_0_test, proc_path("cbcl_attention_0_0_test.csv", date = TRUE))
write_csv(cbcl_aggressive_0_0_test, proc_path("cbcl_aggressive_0_0_test.csv", date = TRUE))
write_csv(sds_sleep_0_0_test, proc_path("sds_sleep_0_0_test.csv", date = TRUE))

# Full data
write_csv(as_mtbi_loc_0_0_full, proc_path("as_mtbi_loc_0_0_full.csv", date = TRUE))
write_csv(as_mtbi_mechanism_0_0_full, proc_path("as_mtbi_mechanism_0_0_full.csv", date = TRUE))
write_csv(as_mtbi_mem_daze_0_0_full, proc_path("as_mtbi_mem_daze_0_0_full.csv", date = TRUE))
write_csv(d_income_0_0_full, proc_path("d_income_0_0_full.csv", date = TRUE))
write_csv(d_interview_age_0_0_full, proc_path("d_interview_age_0_0_full.csv", date = TRUE))
write_csv(d_mtbi_age_0_0_full, proc_path("d_mtbi_age_0_0_full.csv", date = TRUE))
write_csv(d_pubertal_status_0_0_full, proc_path("d_pubertal_status_0_0_full.csv", date = TRUE))
write_csv(d_race_0_0_full, proc_path("d_race_0_0_full.csv", date = TRUE))
write_csv(d_sex_0_0_full, proc_path("d_sex_0_0_full.csv", date = TRUE))
write_csv(mh_headaches_0_0_full, proc_path("mh_headaches_0_0_full.csv", date = TRUE))
write_csv(mh_mtbi_count_0_0_full, proc_path("mh_mtbi_count_0_0_full.csv", date = TRUE))
write_csv(dm_all_wmnd_0_0_full, proc_path("dm_all_wmnd_0_0_full.csv", date = TRUE))
write_csv(rm_gord_cor_0_0_full, proc_path("rm_gord_cor_0_0_full.csv", date = TRUE))
write_csv(rm_gord_var_0_0_full, proc_path("rm_gord_var_0_0_full.csv", date = TRUE))
write_csv(rm_subc_cor_0_0_full, proc_path("rm_subc_cor_0_0_full.csv", date = TRUE))
write_csv(rm_subc_var_0_0_full, proc_path("rm_subc_var_0_0_full.csv", date = TRUE))
write_csv(sm_cort_sa_0_0_full, proc_path("sm_cort_sa_0_0_full.csv", date = TRUE))
write_csv(sm_cort_t_0_0_full, proc_path("sm_cort_t_0_0_full.csv", date = TRUE))
write_csv(sm_subc_v_0_0_full, proc_path("sm_subc_v_0_0_full.csv", date = TRUE))
write_csv(p_loneliness_0_0_full, proc_path("p_loneliness_0_0_full.csv", date = TRUE))
write_csv(p_screen_time_0_0_full, proc_path("p_screen_time_0_0_full.csv", date = TRUE))
write_csv(p_family_function_0_0_full, proc_path("p_family_function_0_0_full.csv", date = TRUE))
write_csv(p_sports_0_0_full, proc_path("p_sports_0_0_full.csv", date = TRUE))
write_csv(p_prosocial_0_0_full, proc_path("p_prosocial_0_0_full.csv", date = TRUE))
write_csv(p_parent_psych_0_0_full, proc_path("p_parent_psych_0_0_full.csv", date = TRUE))
write_csv(p_exercise_0_0_full, proc_path("p_exercise_0_0_full.csv", date = TRUE))
write_csv(cbcl_headaches_0_0_full, proc_path("cbcl_headaches_0_0_full.csv", date = TRUE))
write_csv(cbcl_nausea_0_0_full, proc_path("cbcl_nausea_0_0_full.csv", date = TRUE))
write_csv(cbcl_vomiting_0_0_full, proc_path("cbcl_vomiting_0_0_full.csv", date = TRUE))
write_csv(cbcl_dizzy_0_0_full, proc_path("cbcl_dizzy_0_0_full.csv", date = TRUE))
write_csv(cbcl_overtired_0_0_full, proc_path("cbcl_overtired_0_0_full.csv", date = TRUE))
write_csv(cbcl_sleeping_more_0_0_full, proc_path("cbcl_sleeping_more_0_0_full.csv", date = TRUE))
write_csv(cbcl_sleeping_less_0_0_full, proc_path("cbcl_sleeping_less_0_0_full.csv", date = TRUE))
write_csv(cbcl_depress_0_0_full, proc_path("cbcl_depress_0_0_full.csv", date = TRUE))
write_csv(cbcl_anxiety_0_0_full, proc_path("cbcl_anxiety_0_0_full.csv", date = TRUE))
write_csv(cbcl_attention_0_0_full, proc_path("cbcl_attention_0_0_full.csv", date = TRUE))
write_csv(cbcl_aggressive_0_0_full, proc_path("cbcl_aggressive_0_0_full.csv", date = TRUE))
```


## Data and outcome lists

Subsequent analyses make use of custom `data_list` and `outcome_list` objects that store information about all input variables and outcome (CBCL) measures used for SNF and cluster characterization.
I also store make use of a `cbcl_list` object, which is simply a list of cbcl dataframes and does not keep a track of the same amount of metadata as used in the highly nested `outcome_list` object.
Instead of loading each individual file and building these lists, we can build the lists here and export them for later use.

```{r}
library(rlist)

# Training data list
data_list_0_0_train <- generate_data_list(
    mtbi_loc = as_mtbi_loc_0_0_train,
    mtbi_mechanism = as_mtbi_mechanism_0_0_train,
    mtbi_mem_daze = as_mtbi_mem_daze_0_0_train,
    income = d_income_0_0_train,
    interview_age = d_interview_age_0_0_train,
    mtbi_age = d_mtbi_age_0_0_train,
    pubertal_status = d_pubertal_status_0_0_train,
    race = d_race_0_0_train,
    sex = d_sex_0_0_train,
    headaches = mh_headaches_0_0_train,
    mtbi_count = mh_mtbi_count_0_0_train,
    wmndf = dm_all_wmnd_0_0_train,
    gord_cor = rm_gord_cor_0_0_train,
    gord_var = rm_gord_var_0_0_train,
    subc_cor = rm_subc_cor_0_0_train,
    subc_var = rm_subc_var_0_0_train,
    cort_sa = sm_cort_sa_0_0_train,
    cort_t = sm_cort_t_0_0_train,
    subc_v = sm_subc_v_0_0_train,
    loneliness = p_loneliness_0_0_train,
    screen_time = p_screen_time_0_0_train,
    family_function = p_family_function_0_0_train,
    sports = p_sports_0_0_train,
    prosocial = p_prosocial_0_0_train,
    parent_psych = p_parent_psych_0_0_train,
    exercise = p_exercise_0_0_train
)

list.save(data_list_0_0_train,
          proc_path("data_list_0_0_train.rdata", date = TRUE))


# Testing data list
data_list_0_0_test <- generate_data_list(
    mtbi_loc = as_mtbi_loc_0_0_test,
    mtbi_mechanism = as_mtbi_mechanism_0_0_test,
    mtbi_mem_daze = as_mtbi_mem_daze_0_0_test,
    income = d_income_0_0_test,
    interview_age = d_interview_age_0_0_test,
    mtbi_age = d_mtbi_age_0_0_test,
    pubertal_status = d_pubertal_status_0_0_test,
    race = d_race_0_0_test,
    sex = d_sex_0_0_test,
    headaches = mh_headaches_0_0_test,
    mtbi_count = mh_mtbi_count_0_0_test,
    wmndf = dm_all_wmnd_0_0_test,
    gord_cor = rm_gord_cor_0_0_test,
    gord_var = rm_gord_var_0_0_test,
    subc_cor = rm_subc_cor_0_0_test,
    subc_var = rm_subc_var_0_0_test,
    cort_sa = sm_cort_sa_0_0_test,
    cort_t = sm_cort_t_0_0_test,
    subc_v = sm_subc_v_0_0_test,
    loneliness = p_loneliness_0_0_test,
    screen_time = p_screen_time_0_0_test,
    family_function = p_family_function_0_0_test,
    sports = p_sports_0_0_test,
    prosocial = p_prosocial_0_0_test,
    parent_psych = p_parent_psych_0_0_test,
    exercise = p_exercise_0_0_test
)

list.save(data_list_0_0_test,
          proc_path("data_list_0_0_test.rdata", date = TRUE))





# Full data list
data_list_0_0_full <- generate_data_list(
    mtbi_loc = as_mtbi_loc_0_0_full,
    mtbi_mechanism = as_mtbi_mechanism_0_0_full,
    mtbi_mem_daze = as_mtbi_mem_daze_0_0_full,
    income = d_income_0_0_full,
    interview_age = d_interview_age_0_0_full,
    mtbi_age = d_mtbi_age_0_0_full,
    pubertal_status = d_pubertal_status_0_0_full,
    race = d_race_0_0_full,
    sex = d_sex_0_0_full,
    headaches = mh_headaches_0_0_full,
    mtbi_count = mh_mtbi_count_0_0_full,
    wmndf = dm_all_wmnd_0_0_full,
    gord_cor = rm_gord_cor_0_0_full,
    gord_var = rm_gord_var_0_0_full,
    subc_cor = rm_subc_cor_0_0_full,
    subc_var = rm_subc_var_0_0_full,
    cort_sa = sm_cort_sa_0_0_full,
    cort_t = sm_cort_t_0_0_full,
    subc_v = sm_subc_v_0_0_full,
    loneliness = p_loneliness_0_0_full,
    screen_time = p_screen_time_0_0_full,
    family_function = p_family_function_0_0_full,
    sports = p_sports_0_0_full,
    prosocial = p_prosocial_0_0_full,
    parent_psych = p_parent_psych_0_0_full,
    exercise = p_exercise_0_0_full
)

list.save(data_list_0_0_full,
          proc_path("data_list_0_0_full.rdata", date = TRUE))


# Training CBCL list
cbcl_list_0_0_train <- list(
    cbcl_nausea_0_0_train,
    cbcl_vomiting_0_0_train,
    cbcl_dizzy_0_0_train,
    cbcl_overtired_0_0_train,
    cbcl_sleeping_more_0_0_train,
    cbcl_sleeping_less_0_0_train,
    cbcl_depress_0_0_train,
    cbcl_anxiety_0_0_train,
    cbcl_attention_0_0_train,
    cbcl_aggressive_0_0_train
)

list.save(cbcl_list_0_0_train,
          proc_path("cbcl_list_0_0_train.rdata", date = TRUE))

outcome_list_0_0_train <- generate_outcome_list(
    cbcl_nausea = cbcl_nausea_0_0_train,
    cbcl_vomiting = cbcl_vomiting_0_0_train,
    cbcl_dizzy = cbcl_dizzy_0_0_train,
    cbcl_overtired = cbcl_overtired_0_0_train,
    cbcl_sleeping_more = cbcl_sleeping_more_0_0_train,
    cbcl_sleeping_less = cbcl_sleeping_less_0_0_train,
    cbcl_depress = cbcl_depress_0_0_train,
    cbcl_anxiety = cbcl_anxiety_0_0_train,
    cbcl_attention = cbcl_attention_0_0_train,
    cbcl_aggressive = cbcl_aggressive_0_0_train)

list.save(outcome_list_0_0_train,
          proc_path("outcome_list_0_0_train.rdata", date = TRUE))


cbcl_list_0_0_full <- list(
    cbcl_nausea_0_0_full,
    cbcl_vomiting_0_0_full,
    cbcl_dizzy_0_0_full,
    cbcl_overtired_0_0_full,
    cbcl_sleeping_more_0_0_full,
    cbcl_sleeping_less_0_0_full,
    cbcl_depress_0_0_full,
    cbcl_anxiety_0_0_full,
    cbcl_attention_0_0_full,
    cbcl_aggressive_0_0_full
)

list.save(cbcl_list_0_0_full,
          proc_path("cbcl_list_0_0_full.rdata", date = TRUE))
```
