# Data Preprocessing

This chapter contains:
1. Removal of neuroimaging data failing QC
2. Random removal of siblings
3. Train/test split
4. Mice imputation of missing data
5. Organization of imputed data into `data_list` class objects (from the `metasnf` package)

## Importing Extracted Data

```{r}
library(abcdutils)
library(here)
library(dplyr)
library(readr)
library(metasnf)
library(mice)
library(rlist)

#source("abcd/helper_functions.R")

input_path <- path_maker(here("data/abcd/inputs"))
core_path <- path_maker(here("data/abcd/core"))
sub_path <- path_maker(here("data/abcd/subjects"))
fig_path <- path_maker(here("data/abcd/results/figures"))
proc_path <- path_maker(here("data/abcd/results/processed"))

# Subjects
mtbi_subs <- read_subjects(sub_path("2025_05_22_mtbi_subs.csv"))
unij_subs <- read_subjects(sub_path("2025_05_22_unij_subs.csv"))

read <- function(path) {
    read_csv(input_path(path))
}
```

```{r}
# CHECKPOINT
# mTBI subjects
mtbi_as_loc            <- read("2025_05_22_mtbi_as_loc.csv")
mtbi_as_mechanism      <- read("2025_05_22_mtbi_as_mechanism.csv")
mtbi_as_mem_daze       <- read("2025_05_22_mtbi_as_mem_daze.csv")
mtbi_cbcl              <- read("2025_05_22_mtbi_cbcl.csv")
mtbi_d_income          <- read("2025_05_22_mtbi_d_income.csv")
mtbi_d_interview_age   <- read("2025_05_22_mtbi_d_interview_age.csv")
mtbi_d_mtbi_age        <- read("2025_05_22_mtbi_d_mtbi_age.csv")
mtbi_d_pubertal_status <- read("2025_05_22_mtbi_d_pubertal_status.csv")
mtbi_d_race            <- read("2025_05_22_mtbi_d_race.csv")
mtbi_d_sex             <- read("2025_05_22_mtbi_d_sex.csv")
mtbi_dm_wmnd           <- read("2025_05_22_mtbi_dm_wmnd.csv")
mtbi_mh_headaches      <- read("2025_05_22_mtbi_mh_headaches.csv")
mtbi_mh_mtbi_count     <- read("2025_05_22_mtbi_mh_mtbi_count.csv")
mtbi_p_exercise        <- read("2025_05_22_mtbi_p_exercise.csv")
mtbi_p_fam_fn          <- read("2025_05_22_mtbi_p_fam_fn.csv")
mtbi_p_friends         <- read("2025_05_22_mtbi_p_friends.csv")
mtbi_p_parent_psych    <- read("2025_05_22_mtbi_p_parent_psych.csv")
mtbi_p_prosocial       <- read("2025_05_22_mtbi_p_prosocial.csv")
mtbi_p_screen_time     <- read("2025_05_22_mtbi_p_screen_time.csv")
mtbi_p_sports          <- read("2025_05_22_mtbi_p_sports.csv")
mtbi_rm_gord_cor       <- read("2025_05_22_mtbi_rm_gord_cor.csv")
mtbi_rm_subc_cor       <- read("2025_05_22_mtbi_rm_subc_cor.csv")
mtbi_sds               <- read("2025_05_22_mtbi_sds.csv")
mtbi_sm_cort_sa        <- read("2025_05_22_mtbi_sm_cort_sa.csv")
mtbi_sm_cort_t         <- read("2025_05_22_mtbi_sm_cort_t.csv")
mtbi_sm_subc_v         <- read("2025_05_22_mtbi_sm_subc_v.csv")
mtbi_family            <- read("2025_05_22_mtbi_family.csv")
mtbi_scanner           <- read("2025_05_22_mtbi_scanner.csv")

# Uninjured subjects
unij_cbcl              <- read("2025_05_22_unij_cbcl.csv")
unij_d_income          <- read("2025_05_22_unij_d_income.csv")
unij_d_interview_age   <- read("2025_05_22_unij_d_interview_age.csv")
unij_d_pubertal_status <- read("2025_05_22_unij_d_pubertal_status.csv")
unij_d_race            <- read("2025_05_22_unij_d_race.csv")
unij_d_sex             <- read("2025_05_22_unij_d_sex.csv")
unij_dm_wmnd           <- read("2025_05_22_unij_dm_wmnd.csv")
unij_mh_headaches      <- read("2025_05_22_unij_mh_headaches.csv")
unij_p_exercise        <- read("2025_05_22_unij_p_exercise.csv")
unij_p_fam_fn          <- read("2025_05_22_unij_p_fam_fn.csv")
unij_p_friends         <- read("2025_05_22_unij_p_friends.csv")
unij_p_parent_psych    <- read("2025_05_22_unij_p_parent_psych.csv")
unij_p_prosocial       <- read("2025_05_22_unij_p_prosocial.csv")
unij_p_screen_time     <- read("2025_05_22_unij_p_screen_time.csv")
unij_p_sports          <- read("2025_05_22_unij_p_sports.csv")
unij_rm_gord_cor       <- read("2025_05_22_unij_rm_gord_cor.csv")
unij_rm_subc_cor       <- read("2025_05_22_unij_rm_subc_cor.csv")
unij_sds               <- read("2025_05_22_unij_sds.csv")
unij_sm_cort_sa        <- read("2025_05_22_unij_sm_cort_sa.csv")
unij_sm_cort_t         <- read("2025_05_22_unij_sm_cort_t.csv")
unij_sm_subc_v         <- read("2025_05_22_unij_sm_subc_v.csv")
unij_family            <- read("2025_05_22_unij_family.csv")
unij_scanner           <- read("2025_05_22_unij_scanner.csv")
```

## Neuroimaging quality control

Subset neuroimaging data to those subjects who pass neuroimaging QC and PC.
The QC and PC functions used below, such as `qc_smri()`, return a named list containing vectors of subjects who passed, explicitly failed, or failed by having missing values.

```{r}
# QC data
mri_y_qc_raw_smr_t1 <- abcd_load(core_path("imaging/mri_y_qc_raw_smr_t1.csv"))
mri_y_qc_raw_smr_t2 <- abcd_load(core_path("imaging/mri_y_qc_raw_smr_t2.csv"))
mri_y_qc_raw_rsfmr  <- abcd_load(core_path("imaging/mri_y_qc_raw_rsfmr.csv"))
mri_y_qc_raw_dmr    <- abcd_load(core_path("imaging/mri_y_qc_raw_dmr.csv"))

# sMRI
mtbi_smri_qc <- qc_smri(mri_y_qc_raw_smr_t1, t = 0, mtbi_subs, "qc")
mtbi_smri_pc <- qc_smri(mri_y_qc_raw_smr_t1, t = 0, mtbi_subs, "pc")
unij_smri_qc <- qc_smri(mri_y_qc_raw_smr_t1, t = 0, unij_subs, "qc")
unij_smri_pc <- qc_smri(mri_y_qc_raw_smr_t1, t = 0, unij_subs, "pc")

# dMRI
mtbi_dmri_qc <- qc_dmri(mri_y_qc_raw_dmr, t = 0, mtbi_subs, "qc")
mtbi_dmri_pc <- qc_dmri(mri_y_qc_raw_dmr, t = 0, mtbi_subs, "pc")
unij_dmri_qc <- qc_dmri(mri_y_qc_raw_dmr, t = 0, unij_subs, "qc")
unij_dmri_pc <- qc_dmri(mri_y_qc_raw_dmr, t = 0, unij_subs, "pc")

# rs-fMRI
mtbi_rsfmri_qc <- qc_rsfmri(mri_y_qc_raw_rsfmr, t = 0, mtbi_subs, "qc")
mtbi_rsfmri_pc <- qc_rsfmri(mri_y_qc_raw_rsfmr, t = 0, mtbi_subs, "pc")
unij_rsfmri_qc <- qc_rsfmri(mri_y_qc_raw_rsfmr, t = 0, unij_subs, "qc")
unij_rsfmri_pc <- qc_rsfmri(mri_y_qc_raw_rsfmr, t = 0, unij_subs, "pc")

# Vectors of those who passed QC and PC
dmri_pass <- c(
    intersect(mtbi_dmri_qc$"pass", mtbi_dmri_pc$"pass"),
    intersect(unij_dmri_qc$"pass", unij_dmri_pc$"pass")
)

smri_pass <- c(
    intersect(mtbi_smri_qc$"pass", mtbi_smri_pc$"pass"),
    intersect(unij_smri_qc$"pass", unij_smri_pc$"pass")
)

rsfmri_pass <- c(
    intersect(mtbi_rsfmri_qc$"pass", mtbi_rsfmri_pc$"pass"),
    intersect(unij_rsfmri_qc$"pass", unij_rsfmri_pc$"pass")
)

# Reducing extracted data to just those who passed QC and PC
mtbi_dm_wmnd_qc     <- filter(mtbi_dm_wmnd,     subjectkey %in% dmri_pass)
unij_dm_wmnd_qc     <- filter(unij_dm_wmnd,     subjectkey %in% dmri_pass)
mtbi_rm_gord_cor_qc <- filter(mtbi_rm_gord_cor, subjectkey %in% rsfmri_pass)
unij_rm_gord_cor_qc <- filter(unij_rm_gord_cor, subjectkey %in% rsfmri_pass)
mtbi_rm_subc_cor_qc <- filter(mtbi_rm_subc_cor, subjectkey %in% rsfmri_pass)
unij_rm_subc_cor_qc <- filter(unij_rm_subc_cor, subjectkey %in% rsfmri_pass)
mtbi_sm_cort_sa_qc  <- filter(mtbi_sm_cort_sa,  subjectkey %in% smri_pass)
unij_sm_cort_sa_qc  <- filter(unij_sm_cort_sa,  subjectkey %in% smri_pass)
mtbi_sm_cort_t_qc   <- filter(mtbi_sm_cort_t,   subjectkey %in% smri_pass)
unij_sm_cort_t_qc   <- filter(unij_sm_cort_t,   subjectkey %in% smri_pass)
mtbi_sm_subc_v_qc   <- filter(mtbi_sm_subc_v,   subjectkey %in% smri_pass)
unij_sm_subc_v_qc   <- filter(unij_sm_subc_v,   subjectkey %in% smri_pass)

write_csv(mtbi_dm_wmnd_qc,     input_path("mtbi_dm_wmnd_qc.csv", TRUE))
write_csv(mtbi_rm_gord_cor_qc, input_path("mtbi_rm_gord_cor_qc.csv", TRUE))
write_csv(mtbi_rm_subc_cor_qc, input_path("mtbi_rm_subc_cor_qc.csv", TRUE))
write_csv(mtbi_sm_cort_sa_qc,  input_path("mtbi_sm_cort_sa_qc.csv", TRUE))
write_csv(mtbi_sm_cort_t_qc,   input_path("mtbi_sm_cort_t_qc.csv", TRUE))
write_csv(mtbi_sm_subc_v_qc,   input_path("mtbi_sm_subc_v_qc.csv", TRUE))
write_csv(unij_dm_wmnd_qc,     input_path("unij_dm_wmnd_qc.csv", TRUE))
write_csv(unij_rm_gord_cor_qc, input_path("unij_rm_gord_cor_qc.csv", TRUE))
write_csv(unij_rm_subc_cor_qc, input_path("unij_rm_subc_cor_qc.csv", TRUE))
write_csv(unij_sm_cort_sa_qc,  input_path("unij_sm_cort_sa_qc.csv", TRUE))
write_csv(unij_sm_cort_t_qc,   input_path("unij_sm_cort_t_qc.csv", TRUE))
write_csv(unij_sm_subc_v_qc,   input_path("unij_sm_subc_v_qc.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_dm_wmnd_qc     <- read_csv(input_path("2025_05_22_mtbi_dm_wmnd_qc.csv"))
mtbi_rm_gord_cor_qc <- read_csv(input_path("2025_05_22_mtbi_rm_gord_cor_qc.csv"))
mtbi_rm_subc_cor_qc <- read_csv(input_path("2025_05_22_mtbi_rm_subc_cor_qc.csv"))
mtbi_sm_cort_sa_qc  <- read_csv(input_path("2025_05_22_mtbi_sm_cort_sa_qc.csv"))
mtbi_sm_cort_t_qc   <- read_csv(input_path("2025_05_22_mtbi_sm_cort_t_qc.csv"))
mtbi_sm_subc_v_qc   <- read_csv(input_path("2025_05_22_mtbi_sm_subc_v_qc.csv"))
unij_dm_wmnd_qc     <- read_csv(input_path("2025_05_22_unij_dm_wmnd_qc.csv"))
unij_rm_gord_cor_qc <- read_csv(input_path("2025_05_22_unij_rm_gord_cor_qc.csv"))
unij_rm_subc_cor_qc <- read_csv(input_path("2025_05_22_unij_rm_subc_cor_qc.csv"))
unij_sm_cort_sa_qc  <- read_csv(input_path("2025_05_22_unij_sm_cort_sa_qc.csv"))
unij_sm_cort_t_qc   <- read_csv(input_path("2025_05_22_unij_sm_cort_t_qc.csv"))
unij_sm_subc_v_qc   <- read_csv(input_path("2025_05_22_unij_sm_subc_v_qc.csv"))
```

```{r}

library(mice)
# 1. Create a simple toy dataset
set.seed(123)
data <- data.frame(
  age = c(10, 11, 12, NA, 10, 11, 12, NA, 11, 10),
  iq  = c(100, 105, 110, 115, NA, 102, NA, 108, 111, 100),
  scanner_id = c("S1", "S1", "S2", NA, "S2", "S1", NA, "S2", "S1", NA)
)
# Turn scanner_id into a factor (common in MICE usage)
data$scanner_id <- as.factor(data$scanner_id)
# View missing data summary
ini <- mice(data, maxit = 0)
meth <- ini$method
pred <- ini$predictorMatrix
# Don't impute scanner_id
meth["scanner_id"] <- ""
# Predict age and iq using each other (you could add scanner_id if desired)
pred["age", ] <- c(0, 1, 0)  # Predict age using iq only
pred["iq", ]  <- c(1, 0, 0)  # Predict iq using age only
imp <- mice(data, method = meth, predictorMatrix = pred, m = 5, seed = 42)
completed_data <- complete(imp, action = "long", include = TRUE)
# View completed data
print(completed_data)
# Compare original and completed data side-by-side
cbind(original = data$scanner_id, imputed = completed_data$scanner_id)
```

## Train/Test Split

To avoid having training and testing data inform each other during imputation, we assign the splits prior to the imputation.
This is only done in our primary analysis group (baseline mTBI).

```{r}
mtbi_split <- train_test_assign(
    train_frac = 0.8,
    uids = mtbi_subs
)

mtbi_train_subs <- mtbi_split$"train"
mtbi_test_subs <- mtbi_split$"test"

write_subjects(mtbi_train_subs, sub_path("mtbi_train_subs.csv", TRUE))
write_subjects(mtbi_test_subs, sub_path("mtbi_test_subs.csv", TRUE))
```

```{r}
mtbi_train_subs <- read_subjects(sub_path("2025_05_22_mtbi_train_subs.csv"))
mtbi_test_subs  <- read_subjects(sub_path("2025_05_22_mtbi_test_subs.csv"))

# Storing all mTBI data frames in a list
mtbi_df_list <- list(
    "mtbi_as_loc"            = mtbi_as_loc,
    "mtbi_as_mechanism"      = mtbi_as_mechanism,
    "mtbi_as_mem_daze"       = mtbi_as_mem_daze,
    "mtbi_cbcl"              = mtbi_cbcl,
    "mtbi_d_income"          = mtbi_d_income,
    "mtbi_d_interview_age"   = mtbi_d_interview_age,
    "mtbi_d_mtbi_age"        = mtbi_d_mtbi_age,
    "mtbi_d_pubertal_status" = mtbi_d_pubertal_status,
    "mtbi_d_race"            = mtbi_d_race,
    "mtbi_d_sex"             = mtbi_d_sex,
    "mtbi_dm_wmnd_qc"        = mtbi_dm_wmnd_qc,
    "mtbi_mh_headaches"      = mtbi_mh_headaches,
    "mtbi_mh_mtbi_count"     = mtbi_mh_mtbi_count,
    "mtbi_p_exercise"        = mtbi_p_exercise,
    "mtbi_p_fam_fn"          = mtbi_p_fam_fn,
    "mtbi_p_friends"         = mtbi_p_friends,
    "mtbi_p_parent_psych"    = mtbi_p_parent_psych,
    "mtbi_p_prosocial"       = mtbi_p_prosocial,
    "mtbi_p_screen_time"     = mtbi_p_screen_time,
    "mtbi_p_sports"          = mtbi_p_sports,
    "mtbi_rm_gord_cor_qc"    = mtbi_rm_gord_cor_qc,
    "mtbi_rm_subc_cor_qc"    = mtbi_rm_subc_cor_qc,
    #"mtbi_scanner"           = mtbi_scanner,
    "mtbi_sds"               = mtbi_sds,
    "mtbi_sm_cort_sa_qc"     = mtbi_sm_cort_sa_qc,
    "mtbi_sm_cort_t_qc"      = mtbi_sm_cort_t_qc,
    "mtbi_sm_subc_v_qc"      = mtbi_sm_subc_v_qc
)

# Storing all uninjured data frames in a list
unij_df_list <- list(
    "unij_cbcl"              = unij_cbcl,
    "unij_d_income"          = unij_d_income,
    "unij_d_interview_age"   = unij_d_interview_age,
    "unij_d_pubertal_status" = unij_d_pubertal_status,
    "unij_d_race"            = unij_d_race,
    "unij_d_sex"             = unij_d_sex,
    "unij_dm_wmnd_qc"        = unij_dm_wmnd_qc,
    "unij_mh_headaches"      = unij_mh_headaches,
    "unij_p_exercise"        = unij_p_exercise,
    "unij_p_fam_fn"          = unij_p_fam_fn,
    "unij_p_friends"         = unij_p_friends,
    "unij_p_parent_psych"    = unij_p_parent_psych,
    "unij_p_prosocial"       = unij_p_prosocial,
    "unij_p_screen_time"     = unij_p_screen_time,
    "unij_p_sports"          = unij_p_sports,
    "unij_rm_gord_cor_qc"    = unij_rm_gord_cor_qc,
    "unij_rm_subc_cor_qc"    = unij_rm_subc_cor_qc,
    #"unij_scanner"           = unij_scanner,
    "unij_sds"               = unij_sds,
    "unij_sm_cort_sa_qc"     = unij_sm_cort_sa_qc,
    "unij_sm_cort_t_qc"      = unij_sm_cort_t_qc,
    "unij_sm_subc_v_qc"      = unij_sm_subc_v_qc
)

# Splitting the mTBI list of data frames into training and test set versions
train_filter <- function(df) {
    filtered_df <- dplyr::filter(df, df$"subjectkey" %in% mtbi_train_subs)
    return(filtered_df)
}

test_filter <- function(df) {
    filtered_df <- dplyr::filter(df, df$"subjectkey" %in% mtbi_test_subs)
    return(filtered_df)
}

mtbi_train_df_list <- lapply(mtbi_df_list, train_filter)
mtbi_test_df_list <- lapply(mtbi_df_list, test_filter)
```

## Imputation

SNF requires complete data as input for integration.

Data will be imputed under the following schemes:

- 5 imputations of mTBI data alone
- 5 imputations of unijured data alone
- 5 imputations of mTBI + unijured data together

Resulting in 10 versions of the mTBI data and 10 versions of the unijured data.

First, each group has their extracted dataframes merged into a single one for imputation.

```{r}
# `merge_df_list()` converts lists of data frames into a single data frame
mtbi_train_df <- metasnf::merge_df_list(
    mtbi_train_df_list,
    uid = "subjectkey",
    join = "full"
)

mtbi_test_df <- metasnf::merge_df_list(
    mtbi_test_df_list,
    uid = "subjectkey",
    join = "full"
)

unij_df <- metasnf::merge_df_list(
    unij_df_list,
    uid = "subjectkey",
    join = "full"
)

write_csv(mtbi_test_df, proc_path("mtbi_test_df.csv", TRUE))
write_csv(mtbi_train_df, proc_path("mtbi_train_df.csv", TRUE))
write_csv(unij_df, proc_path("unij_df.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_train_df <- data.frame(read_csv(proc_path("2025_05_23_mtbi_train_df.csv")))
mtbi_test_df <- data.frame(read_csv(proc_path("2025_05_23_mtbi_test_df.csv")))
unij_df <- data.frame(read_csv(proc_path("2025_05_23_unij_df.csv")))
```

A preliminary check of which columns have missing data.

```{r}
missing_colnames_mtbi <- names(which(colSums(is.na(mtbi_train_df)) > 0))
missing_colnames_mtbi

missing_colnames_unij <- names(which(colSums(is.na(unij_df)) > 0))
missing_colnames_unij

# Remove the subjectkey variable and convert character features into factors
mtbi_train_df_no_subs <- char_to_fac(mtbi_train_df[, -1])
mtbi_test_df_no_subs <- char_to_fac(mtbi_test_df[, -1])
unij_df_no_subs <- char_to_fac(unij_df[, -1])

# Set family ID and scanner ID also as factors
mtbi_train_df_no_subs$"scanner_id" <- as.factor(mtbi_train_df_no_subs$"scanner_id")

mtbi_test_df_no_subs$"scanner_id" <- as.factor(mtbi_test_df_no_subs$"scanner_id")

unij_df_no_subs$"scanner_id" <- as.factor(unij_df_no_subs$"scanner_id")
```

```{r}
# Function that checks which variables have the biggest correlations
pairwise_correlations <- function(df, threshold = 0) {
    # Remove missing data to help calculate correlations
    df <- na.omit(df)
    # Remove non-numeric columns
    non_numeric_cols <- sapply(df, function(x) !is.numeric(x))
    df <- df[, !non_numeric_cols]
    # Calculate correlations
    correlations <- cor(df)
    # Ignore self-correlations
    diag(correlations) <- 0
    # Take absolute value of the correlations, as strong anti-correlations also
    # lead to strong linear dependence
    abs_cor <- abs(correlations)
    # Create dataframe of all pairs of correlations
    pairs <- t(combn(colnames(abs_cor), 2))
    paired_cors <- data.frame(pairs, cor = abs_cor[pairs])
    # Filter to only correlations bigger than a specified threshold
    paired_cors <- paired_cors[paired_cors$"cor" > threshold, ]
    return(paired_cors)
}

# Function to help sort variables by pairwise correlations
top_correlating_vars <- function(df, threshold = 0) {
    # Dataframe highlighting strongest correlations
    df <- pairwise_correlations(df, threshold)
    # Iteratively build up an ordered correlations matrix by:
    #   - Record one of the two variables contributing to the largest
    #     pairwise correlation
    #   - Remove that variables from the list of all pairs of correlations
    #   - Repeat until all variables have been removed
    max_cor_df <- data.frame(
        variable = as.character(),
        max_cor = as.numeric()
    )
    i <- 0
    while (nrow(df) > 0) {
        i <- i + 1
        row_with_max_cor <- which(df$"cor" == max(df$"cor"))[1]
        var_with_max_cor <- df[row_with_max_cor, "X1"]
        max_cor <- df[row_with_max_cor, "cor"]
        max_cor_df <- rbind(
            max_cor_df,
            data.frame(
                variable = var_with_max_cor,
                max_cor = max_cor
            )
        )
        df <- dplyr::filter(
            df,
            df$"X1" != var_with_max_cor & df$"X2" != var_with_max_cor
        )
    }
    return(max_cor_df)
}

# Prediction matrix construction
build_pred_mat <- function(df, n_predictors = 1) {
    pred_mat <- matrix(
        nrow = ncol(df),
        ncol = ncol(df),
        data = 1
    )
    colnames(pred_mat) <- colnames(df)
    rownames(pred_mat) <- colnames(df)
    diag(pred_mat) <- 0
    pred_mat_vars <- top_correlating_vars(df)
    vars_to_drop <- pred_mat_vars$"variable"[seq_len(n_predictors)]
    print(paste0("Dropping: ", paste(vars_to_drop, collapse = ", ")))
    pred_mat[, vars_to_drop] <- 0
    return(pred_mat)
}

###############################################################################
# Imputation - mTBI train
###############################################################################
mtbi_train_pred_mat <- build_pred_mat(mtbi_train_df_no_subs, 1)
#mtbi_train_pred_mat["scanner_id", ] <- 0
write.table(mtbi_train_pred_mat, proc_path("mtbi_train_pred_mat.txt", TRUE))
mtbi_train_pred_mat <- as.matrix(read.table(proc_path("2025_05_23_mtbi_train_pred_mat.txt")))
storage.mode(mtbi_train_pred_mat) <- "double"
#ini <- mice(mtbi_train_df_no_subs, maxit = 0)
#meth <- ini$"method"
#meth["scanner_id"] <- ""

# Runs

colnames(mtbi_train_df_no_subs)[66]

ComplexHeatmap::Heatmap(mtbi_train_pred_mat)

mtbi_train_df_no_subs

mtbi_train_pred_mat <- build_pred_mat(mtbi_train_df_no_subs, 60)
start <- Sys.time()
#mtbi_train_imputed <- futuremice(
mtbi_train_imputed <- mice(
    mtbi_train_df_no_subs,
    m = 5,
    #n.core = 5,
    maxit = 10,
    #method = meth,
    #parallelseed = 42,
    predictorMatrix = mtbi_train_pred_mat
)
print(Sys.time() - start)


mtbi_train_df_no_subs$"scanner_id" |> table(useNA = "always")

complete(mtbi_train_imputed, action = "long")$"scanner_id" |> table(useNA = "always")

saveRDS(mtbi_train_imputed, file = proc_path("mtbi_train_imputed_0.rds", TRUE))
mtbi_train_imputed <- readRDS(proc_path("2025_05_23_mtbi_train_imputed_0.rds"))
```

```{r}
#
# mTBI solo imputed data
five_imputed_mtbi_train <- complete(
    imputed_mtbi_train,
    action = "long",
    include = TRUE
)
#
# Write and recover
write_csv(
    five_imputed_mtbi_train,
    input_path("five_imputed_mtbi_train.csv", TRUE)
)
# CHECKPOINT
five_imputed_mtbi_train <- read_csv(
    input_path("2025_02_07_five_imputed_mtbi_train.csv")
)
```

```{r}
###############################################################################
# Imputation - mTBI test
###############################################################################
mtbi_test_pred_mat <- build_pred_mat(mtbi_test_df_no_subs, 28)
write.table(mtbi_test_pred_mat, proc_path("mtbi_test_pred_mat.txt", TRUE))
mtbi_test_pred_mat <- as.matrix(read.table(proc_path("2025_02_07_mtbi_test_pred_mat.txt")))
storage.mode(mtbi_test_pred_mat) <- "double"
imputed_mtbi_test <- futuremice(
    mtbi_test_df_no_subs,
    m = 5,
    n.core = 5,
    maxit = 10,
    parallelseed = 42,
    predictorMatrix = mtbi_test_pred_mat
)

saveRDS(imputed_mtbi_test, file = proc_path("baseline_imputed_mtbi_test.rds", TRUE))
imputed_mtbi_test <- readRDS(proc_path("2025_02_07_baseline_imputed_mtbi_test.rds"))

# mTBI solo imputed data
five_imputed_mtbi_test <- complete(
    imputed_mtbi_test,
    action = "long",
    include = TRUE
)
#
# Write and recover
write_csv(
    five_imputed_mtbi_test,
    input_path("five_imputed_mtbi_test.csv", TRUE)
)
# CHECKPOINT
five_imputed_mtbi_test <- read_csv(
    input_path("2025_02_07_five_imputed_mtbi_test.csv")
)

###############################################################################
# Imputation - only unijured
###############################################################################
unij_pred_mat <- build_pred_mat(unij_df_no_subs, 1)
# Write and recover
write.table(unij_pred_mat, proc_path("unij_pred_mat.txt", TRUE))
unij_pred_mat <- as.matrix(read.table(proc_path("2025_02_07_unij_pred_mat.txt")))
storage.mode(unij_pred_mat) <- "double"
imputed_unij <- futuremice(
    unij_df_no_subs,
    m = 5,
    n.core = 5,
    maxit = 10,
    parallelseed = 42,
    predictorMatrix = unij_pred_mat
)

saveRDS(imputed_unij, file = proc_path("baseline_imputed_unij.rds", TRUE))
imputed_unij <- readRDS(proc_path("2025_02_07_baseline_imputed_unij.rds"))
```

```{r}
# unijured solo imputed data
five_imputed_unij <- complete(
    imputed_unij,
    action = "long",
    include = TRUE
)
#
# Write and recover
write_csv(
    five_imputed_unij,
    input_path("five_imputed_unij.csv", TRUE)
)
#
five_imputed_unij <- read_csv(
    input_path("2025_02_07_five_imputed_unij.csv")
) # 68448 rows (11408 subjects * 6 imputations)

###############################################################################
# Imputation - mTBI and unijured data stacked on top of each other
# This will only look at the variables shared between the two groups
###############################################################################
mtbi_train_df_u_vars <- mtbi_train_df_no_subs[, colnames(unij_df_no_subs)]
pooled_df <- rbind(mtbi_train_df_u_vars, unij_df_no_subs)
pooled_df <- char_to_fac(pooled_df)

pooled_pred_mat <- build_pred_mat(pooled_df, 1)
# Write and recover
write.table(pooled_pred_mat, proc_path("pooled_pred_mat.txt", TRUE))
pooled_pred_mat <- as.matrix(
    read.table(proc_path("2025_02_07_pooled_pred_mat.txt"))
)
storage.mode(pooled_pred_mat) <- "double"
imputed_pooled <- futuremice(
    pooled_df,
    m = 5,
    n.core = 5,
    maxit = 10,
    parallelseed = 42,
    predictorMatrix = pooled_pred_mat
)

saveRDS(imputed_pooled, file = proc_path("baseline_imputed_pooled.rds", TRUE))
imputed_pooled <- readRDS(proc_path("2025_02_07_baseline_imputed_pooled.rds"))

# mTBI solo imputed data
five_imputed_pooled <- complete(
    imputed_pooled,
    action = "long",
    include = TRUE
)
#
# Write and recover
write_csv(five_imputed_pooled, input_path("five_imputed_pooled.csv", TRUE))
five_imputed_pooled <- read_csv(
    input_path("2025_02_07_five_imputed_pooled.csv")
)
```

Formatting the imputed data:

```{r}
five_imputed_mtbi_train$"subjectkey" <- rep(mtbi_train_subs, 6)
five_imputed_mtbi_test$"subjectkey" <- rep(mtbi_test_subs, 6)
five_imputed_unij$"subjectkey" <- rep(unij_subs, 6)

pooled_subs <- c(mtbi_train_subs, unij_subs)
five_imputed_pooled$"subjectkey" <- rep(pooled_subs, 6)

write_csv(
    five_imputed_mtbi_train,
    input_path("five_imputed_mtbi_train_named.csv", TRUE)
)
write_csv(
    five_imputed_mtbi_test,
    input_path("five_imputed_mtbi_test_named.csv", TRUE)
)
write_csv(
    five_imputed_unij,
    input_path("five_imputed_unij_named.csv", TRUE)
)
write_csv(
    five_imputed_pooled,
    input_path("five_imputed_pooled_named.csv", TRUE)
)
```

```{r}
# Write and recover
five_imputed_mtbi_train <- read_csv(
    input_path("2025_02_07_five_imputed_mtbi_train_named.csv")
)

five_imputed_mtbi_test <- read_csv(
    input_path("2025_02_07_five_imputed_mtbi_test_named.csv")
)

five_imputed_unij <- read_csv(
    input_path("2025_02_07_five_imputed_unij_named.csv")
)

five_imputed_pooled <- read_csv(
    input_path("2025_02_07_five_imputed_pooled_named.csv")
)
```

# mTBI subsetting

```{r}
extract_imputed <- function(original_df, imputed_df, partition) {
    return(imputed_df[imputed_df$".imp" == partition, colnames(original_df)])
}

parse_imputations <- function(original_df_list, complete_imputed_df, imps) {
    parsed_imputations <- original_df_list |>
        lapply(
            function(x) {
                imputations <- list()
                for (i in seq_len(imps)) {
                    imputations[[i]] <- extract_imputed(
                        x,
                        complete_imputed_df,
                        i - 1
                    )
                }
                names(imputations) <- paste0("imp_", seq_len(imps) - 1)
                return(imputations)
            }
        )
    names(parsed_imputations) <- gsub("_mtbi$", "", names(parsed_imputations))
    names(parsed_imputations) <- gsub("_unij$", "", names(parsed_imputations))
    return(parsed_imputations)
}

mtbi_train_parsed_imputations <- parse_imputations(
    mtbi_train_df_list,
    five_imputed_mtbi_train,
    6
)

mtbi_test_parsed_imputations <- parse_imputations(
    mtbi_test_df_list,
    five_imputed_mtbi_test,
    6
)

unij_parsed_imputations <- parse_imputations(
    unij_df_list,
    five_imputed_unij,
    6
)

pooled_parsed_imputations <- parse_imputations(
    unij_df_list,
    five_imputed_pooled,
    6
)

mtbi_pooled_parsed_imputations <- pooled_parsed_imputations |>
    lapply(
        function(variable) {
            lapply(
                variable,
                function(imputed_df) {
                    keep_rows <- imputed_df$"subjectkey" %in% mtbi_train_subs
                    filtered_df <- imputed_df[keep_rows, ]
                    return(filtered_df)
                }
            )
        }
    )

unij_pooled_parsed_imps <- pooled_parsed_imputations |>
    lapply(
        function(variable) {
            lapply(
                variable,
                function(imputed_df) {
                    keep_rows <- imputed_df$"subjectkey" %in% unij_subs
                    filtered_df <- imputed_df[keep_rows, ]
                    return(filtered_df)
                }
            )
        }
    )

list.save(
    mtbi_train_parsed_imputations,
    input_path("mtbi_train_parsed_imputations.rds", TRUE)
)
list.save(
    mtbi_test_parsed_imputations,
    input_path("mtbi_test_parsed_imputations.rds", TRUE)
)
list.save(
    mtbi_pooled_parsed_imputations,
    input_path("mtbi_pooled_parsed_imputations.rds", TRUE)
)
list.save(
    unij_parsed_imputations,
    input_path("unij_parsed_imputations.rds", TRUE)
)
list.save(
    unij_pooled_parsed_imps,
    input_path("unij_pooled_parsed_imputations.rds", TRUE)
)
```

Re-reading:

```{r}
mtbi_train_parsed_imputations <- list.load(
    input_path("2025_02_07_mtbi_train_parsed_imputations.rds")
)
mtbi_test_parsed_imputations <- list.load(
    input_path("2025_02_07_mtbi_test_parsed_imputations.rds")
)
mtbi_pooled_parsed_imputations <- list.load(
    input_path("2025_02_07_mtbi_pooled_parsed_imputations.rds")
)
unij_parsed_imputations <- list.load(
    input_path("2025_02_07_unij_parsed_imputations.rds")
)
unij_pooled_parsed_imps <- list.load(
    input_path("2025_02_07_unij_pooled_parsed_imputations.rds")
)

names(mtbi_train_parsed_imputations)
```


## Constructing data_lists

We have:

* 1 original unimputed mTBI dataset
* 1 original unimputed unijured dataset
* 5 imputed mTBI datasets
* 5 imputed unijured datasets
* 5 imputed mTBI + unijured datasets

For the sake of brevity, these will be referred to with the following notation:

* m = mTBI
* u = unijured
* p = pooled
* 0 = original (unimputed)
* 1-5 = imputed dataset number

```{r}
mtbi_train_data_lists <- build_dls(mtbi_train_parsed_imputations)
mtbi_train_oom_lists <- build_ols(mtbi_train_parsed_imputations)
mtbi_test_data_lists <- build_dls(mtbi_test_parsed_imputations)
mtbi_test_oom_lists <- build_ols(mtbi_test_parsed_imputations)
mtbi_pooled_data_lists <- build_unij_dls(mtbi_pooled_parsed_imputations)
mtbi_pooled_oom_lists <- build_ols(mtbi_pooled_parsed_imputations)
unij_data_lists <- build_unij_dls(unij_parsed_imputations)
unij_oom_lists <- build_ols(unij_parsed_imputations)
unij_pooled_data_lists <- build_unij_dls(unij_pooled_parsed_imps)
unij_pooled_oom_lists <- build_ols(unij_pooled_parsed_imps)

all_dls <- list(
    "mtbi_train_data_lists" = mtbi_train_data_lists,
    "mtbi_train_oom_lists" = mtbi_train_oom_lists,
    "mtbi_test_data_lists" = mtbi_test_data_lists,
    "mtbi_test_oom_lists" = mtbi_test_oom_lists,
    "mtbi_pooled_data_lists" = mtbi_pooled_data_lists,
    "mtbi_pooled_oom_lists" = mtbi_pooled_oom_lists,
    "unij_data_lists" = unij_data_lists,
    "unij_oom_lists" = unij_oom_lists,
    "unij_pooled_data_lists" = unij_pooled_data_lists,
    "unij_pooled_oom_lists" = unij_pooled_oom_lists
)

```

## Renaming the initial data

```{r}
name_changes <- c(
    "mtbi_mechanism" = "latest_mtbi_mechanism",
    "mtbi_mem_daze" = "latest_mtbi_mem_daze",
    "mtbi_loc" = "latest_mtbi_loc",
    "mtbi_age" = "latest_mtbi_age",
    "age" = "interview_age",
    "parent_thought" = "asr_scr_thought_r",
    "parent_aggressive" = "asr_scr_aggressive_r",
    "parent_antisocial" = "asr_scr_antisocial_r",
    "parent_hyperactive" = "asr_scr_hyperactive_r",
    "parent_attention" = "asr_scr_attention_r",
    "parent_anxdep" = "asr_scr_anxdep_r",
    "parent_depress" = "asr_scr_depress_r",
    "parent_withdrawn" = "asr_scr_withdrawn_r",
    "parent_avoidant" = "asr_scr_avoidant_r",
    "parent_anxdisord" = "asr_scr_anxdisord_r",
    "parent_somatic" = "asr_scr_somatic_r",
    "parent_intrusive" = "asr_scr_intrusive_r",
    "parent_perstr" = "asr_scr_perstr_r",
    "sds_sleep" = "sds_p_ss_total",
    "cbcl_somatic" = "cbcl_scr_syn_somatic_r",
    "cbcl_social" = "cbcl_scr_syn_social_r",
    "cbcl_anxdep" = "cbcl_scr_syn_anxdep_r",
    "cbcl_thought" = "cbcl_scr_syn_thought_r",
    "cbcl_attention" = "cbcl_scr_syn_attention_r",
    "cbcl_withdep" = "cbcl_scr_syn_withdep_r",
    "cbcl_aggressive" = "cbcl_scr_syn_aggressive_r",
    "cbcl_rulebreak" = "cbcl_scr_syn_rulebreak_r",
    "family_fight_y" = "q1_fight_y",
    "family_angry_y" = "q2_angry_y",
    "family_throw_y" = "q3_throw_y",
    "family_temper_y" = "q4_temper_y",
    "family_criticize_y" = "q5_criticize_y",
    "family_hit_y" = "q6_hit_y",
    "family_peaceful_y" = "q7_peaceful_y",
    "family_outdo_y" = "q8_outdo_y",
    "family_yell_y" = "q9_yell_y",
    "family_fight_p" = "q1_fight_p",
    "family_angry_p" = "q2_angry_p",
    "family_throw_p" = "q3_throw_p",
    "family_temper_p" = "q4_temper_p",
    "family_criticize_p" = "q5_criticize_p",
    "family_hit_p" = "q6_hit_p",
    "family_peaceful_p" = "q7_peaceful_p",
    "family_outdo_p" = "q8_outdo_p",
    "family_yell_p" = "q9_yell_p",
    "headache_history" = "headache",
    "previous_mtbis" = "mtbi_count",
    "brain_volume" = "smri_vol_scs_wholeb",
    "cortical_thickness" = "smri_thick_cdk_mean",
    "cortical_sa" = "smri_area_cdk_total",
    "major_wm_ndi" = "dmri_rsirnd_fib_allfib",
    "pericortical_wm_ndi" = "dmri_rsirndwm_cdk_mean",
    "fmri_cort_cors" = "avg_gord_cor",
    "fmri_cort_subcort_cors" = "avg_subc_cor",
    "same_sex_friend" = "ss_friend",
    "opp_sex_friend" = "os_friend",
    "same_sex_close_friend" = "ss_close_friend",
    "opp_sex_close_friend" = "os_close_friend",
    "weekend_screentime" = "screentime_wknd_hrs",
    "weekday_screentime" = "screentime_wkday_hrs"
)

all_dls <- all_dls |>
    lapply(
        function(data_lists_of_group) {
            lapply(
                data_lists_of_group,
                function(data_list) {
                    data_list <- as_data_list(rename_dl(data_list, name_changes))
                }
            )
        }
    )

saveRDS(all_dls, input_path("all_dls.rds", TRUE))
```

## Density plots

- Can re-run later

```{r}
imputed_mtbi_test <- readRDS(proc_path("2025_02_07_baseline_imputed_mtbi_test.rds"))
imputed_mtbi_train <- readRDS(proc_path("2025_02_07_baseline_imputed_mtbi_train.rds"))
imputed_unij <- readRDS(proc_path("2025_02_07_baseline_imputed_unij.rds"))
imputed_pooled <- readRDS(proc_path("2025_02_07_baseline_imputed_pooled.rds"))

mtbi_test_densityplot <- densityplot(imputed_mtbi_test)
mtbi_train_densityplot <- densityplot(imputed_mtbi_train)
unij_densityplot <- densityplot(imputed_unij)

png_save(unij_densityplot, fig_path("unij_densityplot.png", TRUE))

pooled_densityplot <- densityplot(imputed_pooled)
```
