# MetaSNF

In this chapter, I use the metaSNF package to generate and characterize meta clusters of the extracted data.

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)
library(ggplot2)
library(patchwork)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subjects <- read_csv(sub_path("2024_04_17_mtbi_subjects.csv"))
mtbi_train_subjects <- read_csv(sub_path("2024_04_18_mtbi_train_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2024_04_17_uninjured_subjects.csv"))
```

## Importing data

```{r}
all_dls <- list.load(input_path("2024_04_19_all_dls.rds"))
```

## Generating custom distance measures

```{r}
###############################################################################
# 2. Add standard normalized variations to the distance metrics list (also
# achievable through toggling automatic_standard_normalize parameter in
# `batch_snf`)
###############################################################################
my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

summarize_dml(my_distance_metrics)
```

## Generating the settings matrix

```{r}
mtbi_settings_matrix <- generate_settings_matrix(
    all_dls$"mtbi_train_data_lists"$"imp_1",
    nrow = 200,
    seed = 42,
    distance_metrics_list = my_distance_metrics
)

write_csv(mtbi_settings_matrix, proc_path("mtbi_settings_matrix.csv", TRUE))

mtbi_settings_matrix <- read_csv(
    proc_path("2024_04_19_mtbi_settings_matrix.csv")
)
```

## Running SNF for each of the imputations

```{r}
mtbi_train_dls <- c(
    all_dls$"mtbi_train_data_lists",
    all_dls$"mtbi_pooled_data_lists"
)

names(mtbi_train_dls) <- c(paste0("imp_", 1:5), paste0("pooled_imp_", 1:5))

mtbi_train_solutions_matrices <- lapply(
    mtbi_train_dls,
    function(imputed_dl) {
        summarize_dl(imputed_dl)
        solutions_matrix <- batch_snf(
            data_list = imputed_dl,
            settings_matrix = mtbi_settings_matrix,
            distance_metrics_list = my_distance_metrics,
            processes = "max"
        )
    }
)

list.save(
    mtbi_train_solutions_matrices,
    input_path("mtbi_train_solutions_matrices.rds", TRUE)
)

mtbi_train_solutions_matrices <- list.load(
    input_path("2024_04_22_mtbi_train_solutions_matrices.rds")
)

mtbi_sm <- do.call(
    "rbind",
    mtbi_train_solutions_matrices
)

write_csv(data.frame(mtbi_sm), proc_path("mtbi_sm.csv", TRUE))

mtbi_ari <- calc_aris(mtbi_sm, processes = "max")

write_csv(data.frame(mtbi_ari), proc_path("mtbi_ari.csv", TRUE))

mtbi_ari_order <- get_matrix_order(mtbi_ari)

write_csv(data.frame(mtbi_ari_order), proc_path("mtbi_ari_order.csv", TRUE))
```

## Re-importing data

```{r}
mtbi_sm <- read_csv(proc_path("2024_04_23_mtbi_sm.csv"))

mtbi_ari <- as.matrix(read_csv(proc_path("2024_04_23_mtbi_ari.csv")))

mtbi_ari_order <- unlist(read_csv(proc_path("2024_05_27_mtbi_ari_order.csv")))
names(mtbi_ari_order) <- NULL
```

## Calculating associations between cluster solutions and features

```{r}
imputation_labels <- data.frame(
    "imputation" = c(
        rep("m1", 200),
        rep("m2", 200),
        rep("m3", 200),
        rep("m4", 200),
        rep("m5", 200),
        rep("pm1", 200),
        rep("pm2", 200),
        rep("pm3", 200),
        rep("pm4", 200),
        rep("pm5", 200)
    ),
    "pooled" = c(
        rep("no", 1000),
        rep("yes", 1000)
    )
)

mtbi_sm_l <- cbind(mtbi_sm, imputation_labels)

mtbi_esm_m1 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "m1", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_1",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_1",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_m2 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "m2", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_2",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_2",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_m3 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "m3", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_3",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_3",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_m4 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "m4", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_4",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_4",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_m5 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "m5", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_5",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_5",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_pm1 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "pm1", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_1",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_1",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_pm2 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "pm2", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_2",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_2",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_pm3 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "pm3", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_3",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_3",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_pm4 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "pm4", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_4",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_4",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_pm5 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "pm5", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_5",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_5",
    min_pval = 1e-10,
    processes = "max"
)

mtbi_esm <- dplyr::bind_rows(
    mtbi_esm_m1,
    mtbi_esm_m2,
    mtbi_esm_m3,
    mtbi_esm_m4,
    mtbi_esm_m5,
    mtbi_esm_pm1,
    mtbi_esm_pm2,
    mtbi_esm_pm3,
    mtbi_esm_pm4,
    mtbi_esm_pm5
)

mtbi_esm$"impairment_separation" <- -log10(mtbi_esm$"mean_pval")

write_csv(mtbi_esm, proc_path("mtbi_esm.csv", TRUE))
```

```{r}
mtbi_esm <- read_csv(proc_path("2024_05_29_mtbi_esm.csv"))
```

## Identifying and visualizing meta clusters

```{r}
base_ari_hm <- adjusted_rand_index_heatmap(
    mtbi_ari,
    order = mtbi_ari_order
)

shiny_annotator(base_ari_hm)

mtbi_split_vec <- c(
    60,
    137,
    275,
    490,
    580,
    940,
    1086,
    1175,
    1435,
    1660
)
write_csv(data.frame(mtbi_split_vec), proc_path("mtbi_split_vec.csv", TRUE))
```

```{r}
mtbi_split_vec <- read_csv(proc_path("2024_05_27_mtbi_split_vec.csv")) |>
    unlist() |>
    as.numeric()
```

```{r}
divergent_colours <- function(column)  {
    values <- unique(column)
    colours <- RColorBrewer::brewer.pal(n = length(values), name = "Set3")
    names(colours) <- values
    return(colours)
}

full_mtbi_ari_hm <- adjusted_rand_index_heatmap(
    aris = mtbi_ari,
    order = mtbi_ari_order,
    data = mtbi_esm,
    min_colour = "black",
    split_vector = mtbi_split_vec,
    top_hm = list(
        "Impairment Separation" = "impairment_separation"
    ),
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    left_hm = list(
        "Pooled" = "pooled",
        "Imputation" = "imputation"
    ),
    annotation_colours = list(
        "Impairment Separation" = colour_scale(
            mtbi_esm$"impairment_separation",
            min_colour = "gray7",
            max_colour = "limegreen"
        ),
        "Imputation" = divergent_colours(mtbi_esm$"imputation"),
        "Pooled" = c(
            "yes" = "orange",
            "no" = "purple"
        )
    )
)

save_heatmap(
    heatmap = full_mtbi_ari_hm,
    path = fig_path("full_mtbi_ari_hm.png", TRUE),
    width = 950,
    height = 900,
    res = 100
)

# Another heatmap without the imputation-related columns
lite_mtbi_ari_hm <- adjusted_rand_index_heatmap(
    aris = mtbi_ari,
    order = mtbi_ari_order,
    data = mtbi_esm,
    min_colour = "black",
    split_vector = mtbi_split_vec,
    top_hm = list(
        "Impairment Separation" = "impairment_separation"
    ),
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    annotation_colours = list(
        "Impairment Separation" = colour_scale(
            mtbi_esm$"impairment_separation",
            min_colour = "gray7",
            max_colour = "limegreen"
        )
    )
)

save_heatmap(
    heatmap = lite_mtbi_ari_hm,
    path = fig_path("lite_mtbi_ari_hm.png", TRUE),
    width = 900,
    height = 700,
    res = 100
)
```

When picking out representative solutions, I'd like to preferentially go for solutions that derived from solo rather than pooled imputations, as those solutions have values for all features.

```{r}
# Function to try to lean on mTBI-including solutions when possible.
# This function will pick from solo solutions unless over 70% of the meta
# cluster is pooled.
restrict_fn <- function(x, threshold = 0.3) {
    x_solo_ind <- x$"imputation" %in% c("m1", "m2", "m3", "m4", "m5")
    x_pool_ind <- x$"imputation" %in% c("pm1", "pm2", "pm3", "pm4", "pm5")
    x_solo <- x[x_solo_ind, ]
    x_pool <- x[x_pool_ind, ]
    frac_solo <- nrow(x_solo) / (nrow(x_solo) + nrow(x_pool))
    if (frac_solo < threshold) {
        return(x[x_pool_ind, ])
    } else {
        return(x[x_solo_ind, ])
    }
}

mtbi_rep_solutions <- get_representative_solutions(
    mtbi_ari,
    split_vector = mtbi_split_vec,
    order = mtbi_ari_order,
    filter_fn = restrict_fn,
    mtbi_esm
)

# Based on the heatmap, we'll remove B, E, H, K (unstable meta clusters)
mtbi_rep_solutions <- dplyr::filter(
    mtbi_rep_solutions,
    !label %in% c("B", "E", "H", "K")
)

write_csv(mtbi_rep_solutions, proc_path("mtbi_rep_solutions.csv", TRUE))
```

```{r}
mtbi_rep_solutions <- read_csv(proc_path("2024_05_29_mtbi_rep_solutions.csv"))

mtbi_manhattan <- mc_manhattan_plot(
    mtbi_rep_solutions,
    data_list = all_dls$"mtbi_train_data_lists"$"imp_1",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_1",
    domain_colours = c(
        "AS" = "#85929e",
        "D" = "#bb8fce",
        "N" = "#e59866",
        "MH" = "#7fb3d5",
        "P" = "#52be80",
        "S" = "#d98880",
        "B" = "#ff3131"
    )
)

ggsave(
    plot = mtbi_manhattan,
    filename = fig_path("mtbi_manhattan.png", TRUE),
    width = 18,
    height = 14,
    dpi = 120
)

# The most robust solution
mtbi_mc_d_esm <- mtbi_rep_solutions |>
    dplyr::filter(label == "D")

write_csv(mtbi_mc_d_esm, proc_path("mtbi_mc_d_esm.csv", TRUE))

mtbi_mc_d_esm <- read_csv(proc_path("2024_05_30_mtbi_mc_d_esm.csv"))

# Feature plot generation
plot_list <- auto_plot(
    solutions_matrix_row = mtbi_mc_d_esm,
    data_list = all_dls$"mtbi_train_data_lists"$"imp_3",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_3",
    save = fig_path("mtbi_mc_d", TRUE)
)

# No save version:
plot_list <- auto_plot(
    solutions_matrix_row = mtbi_mc_d_esm,
    data_list = all_dls$"mtbi_train_data_lists"$"imp_3",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_3"
)

all_plots <- wrap_plots(plot_list)

# Good enough as a snapshot
ggsave(
    fig_path("mtbi_mc_d_all_plots.png", TRUE),
    all_plots,
    width = 35,
    height = 30,
    dpi = 50
)
```

## Key attributes of the cluster solution

Doesn't seem to be a big difference:

- mtbi_mem_daze: 1 = 2 = 3
- mtbi_loc: 1 = 2 = 3
- mtbi_age: 1 = 2 = 3
- previous_mtbis: 1 = 2 = 3
- major_wm_ndi: 1 = 2 = 3
- pericortical_wm_ndi: 1 = 2 = 3
- fmri_cort_cors: 1 = 2 = 3
- school_programs: 1 = 2 = 3

Small difference:

- mtbi_mechanism 1 < 2 = 3
- age 1 = 2 < 3
- headache_history: 3 < 1 = 2
- fmri_cort_subcort_cors: 1 < 3 < 2
- cortical_thickness: 1 < 2 = 3
- school_programs: 1 < 2 < 3
- same_sex_friend: 3 > 1 = 2
- opp_sex_friend: 1 > 2 = 3

Seems to be a big difference:

- sex (n_female): 3 >> 1 > 2
- household_income: 1 << 2 = 3
- race (minority groups): 1 >> 2 = 3
- pubertal_status: 2 < 1 = 3
- brain_volume: 2 >> 1 > 3
- cortical thickness: 1 < 2 = 3
- cortical_sa: 2 >> 1 > 3
- same_sex_close_friend: 3 >> 2 > 1
- opp_sex_close_friend: 1 > 2 = 3
- weekend_screentime: 1 > 2 = 3
- weekday_screentime: 1 > 2 = 3
- non_school_programs: 1 << 2 = 3
- private_instruction: 1 < 2 < 3
- programs_this_year: 1 << 2 = 3
- exercise_time: 1 < 2 = 3
- considerate: 1 < 2 < 3
- helps_hurt: 3 > 1 = 2
- helpful: 3 > 1 = 2
- family_fight: 1 > 2 = 3
- family_angry: 1 > 2 = 3
- family_throw: 1 > 2 = 3
- family_temper: 1 > 2 = 3
- family_criticize: 1 > 2 = 3
- family_hit: 1 > 2 = 3
- family_peaceful: 1 > 2 > 3
- family_outdo: 1 > 2 = 3
- family_yell: 1 > 2 > 3
- parent_perstr: 1 < 2 < 3
- parent_anxdep: 1 >> 2 = 3
- parent_withdrawn: 1 > 2 = 3
- parent_somatic: 1 > 2 = 3
- parent_thought: 1 > 2 = 3
- parent_attention: 1 > 2 = 3
- parent_aggressive: 1 > 2 = 3
- parent_intrusive: 1 > 2 = 3
- parent_depress: 1 > 2 = 3
- parent_anxdisord: 1 > 2 = 3
- parent_avoidant: 1 > 2 > 3
- parent_antisocial: 1 > 2 = 3
- parent_hyperactive: 1 > 2 = 3
- cbcl_anxdep: 1 > 2 = 3
- cbcl_withdep: 1 > 2 = 3
- cbcl_somatic: 1 > 2 = 3
- cbcl_social: 1 > 2 = 3
- cbcl_thought: 1 > 2 = 3
- cbcl_attention: 1 > 2 = 3
- cbcl_rulebreak: 1 > 2 = 3
- cbcl_aggressive: 1 > 2 = 3
- sds_sleep: 1 > 2 = 3

Dennis, E., Manza, P. & Volkow, N.D. Socioeconomic status, BMI, and brain development in children. Transl Psychiatry 12, 33 (2022). https://doi.org/10.1038/s41398-022-01779-3

In the study above, they looked at SES based on household income, highest level of parental education, and area deprivation.
They also found that BMI played a role in brain development.

Orben, A., Meier, A., Dalgleish, T. et al. Mechanisms linking social media use to adolescent mental health vulnerability. Nat Rev Psychol (2024). https://doi.org/10.1038/s44159-024-00307-y

```{r}
# Calculating feature importances
nmis <- batch_nmi(
    all_dls$"mtbi_train_data_lists"$"imp_3",
    mtbi_mc_d_esm,
    distance_metrics_list = my_distance_metrics
)

nmi_order <- sort(
    nmis$"row_id_67",
    decreasing = TRUE,
    index.return = TRUE
)

nmis <- nmis[nmi_order$ix, ]

write_csv(nmis, proc_path("mtbi_mc_d_nmis.csv", TRUE))
```

```{r}
mtbi_mc_d_nmis <- read_csv(proc_path("2024_05_29_mtbi_mc_d_nmis.csv"))
```

NMI order:

                  feature   row_id_67
1                     sex 0.243209963
2            brain_volume 0.191430570
3             cortical_sa 0.176465863
4        household_income 0.173650190
5                    race 0.106974328
6     non_school_programs 0.089535118
7      programs_this_year 0.085778912
8         pubertal_status 0.073815053
9      weekend_screentime 0.068591085
10         parent_thought 0.065605239
11         parent_somatic 0.063379204
12 fmri_cort_subcort_cors 0.062316738
13      parent_aggressive 0.061766652
14        parent_avoidant 0.061007979
15    private_instruction 0.060788001
16       parent_withdrawn 0.058834958
17      parent_antisocial 0.058439486
18     weekday_screentime 0.052901237
19       parent_anxdisord 0.047661089
20     parent_hyperactive 0.046030868
21        family_peaceful 0.045456812
22       parent_intrusive 0.044010345
23         fmri_cort_cors 0.041913000
24          parent_anxdep 0.041754962
25          parent_perstr 0.037575118
26         parent_depress 0.036061882
27          family_temper 0.034659741
28            considerate 0.034615358
29             helps_hurt 0.034538988
30       headache_history 0.033912559
31          exercise_time 0.033209402
32           family_outdo 0.031435016
33  same_sex_close_friend 0.029747204
34           family_angry 0.029313684
35           family_fight 0.028924925
36       parent_attention 0.028905738
37         mtbi_mechanism 0.028635369
38    pericortical_wm_ndi 0.028290869
39     cortical_thickness 0.025146517
40       family_criticize 0.024516708
41                    age 0.024484370
42        school_programs 0.023241074
43                helpful 0.022037230
44           major_wm_ndi 0.020916865
45               mtbi_age 0.018499859
46           family_throw 0.018149749
47          mtbi_mem_daze 0.015706414
48             family_hit 0.014753237
49        same_sex_friend 0.012166623
50               mtbi_loc 0.011030747
51         previous_mtbis 0.009733142
52            family_yell 0.009473181
53         opp_sex_friend 0.003748435
54   opp_sex_close_friend 0.003587654

## NMIs vs. p-values

```{r}
pvals <- get_pvals(
    mtbi_mc_d_esm,
    keep_summaries = FALSE
)
pvals <- data.frame(
    "feature" = gsub("_pval", "", names(pvals)),
    "neg_log_pval" = -log10(as.numeric(unlist(pvals)))
)
pvals <- pvals[-1, ]
pvals_order <- sort(
    pvals$"neg_log_pval",
    decreasing = TRUE,
    index.return = TRUE
)
pvals <- pvals[pvals_order$ix, ]

mtbi_mc_d_nmi_pval <- dplyr::full_join(mtbi_mc_d_nmis, pvals, by = "feature")

var_metadata <- dl_variable_summary(
    c(
        all_dls$"mtbi_train_data_lists"$"imp_3",
        all_dls$"mtbi_train_oom_lists"$"imp_3"
    )
)

mtbi_mc_d_nmi_pval <- dplyr::full_join(
    mtbi_mc_d_nmi_pval,
    var_metadata,
    by = c("feature" = "name")
)

colnames(mtbi_mc_d_nmi_pval) <- c(
    "feature",
    "nmi",
    "neg_log_pval",
    "type",
    "domain"
)

r2 <- function(df) {
    df <- na.omit(df)
    return(round(cor(df$"nmi", df$"neg_log_pval")^2, 3))
}

mtbi_mc_d_nmi_pval_r2 <- mtbi_mc_d_nmi_pval |>
    dplyr::filter(neg_log_pval < 10) |>
    dplyr::filter(domain != "B") |>
    r2()

no_diff <- data.frame(
    vis_diff = "none",
    feature = c(
        "mtbi_mem_daze",
        "mtbi_loc",
        "previous_mtbis",
        "cortical thickness",
        "major_wm_ndi",
        "pericortical_wm_ndi",
        "fmri_cort_cors",
        "opp_sex_close_friend",
        "school_programs"
    )
)

small_diff <- data.frame(
    vis_diff = "small",
    feature = c(
        "mtbi_mechanism",
        "age",
        "mtbi_age",
        "fmri_cort_subcort_cors",
        "cortical_thickness",
        "school_programs",
        "headache_history",
        "same_sex_friend",
        "opp_sex_friend",
        "exercise_time",
        "helpful",
        "family_yell",
        "parent_intrusive",
        "weekend_screentime"
    )
)

big_diff <- data.frame(
    vis_diff = "big",
    feature = c(
        "sex",
        "household_income",
        "race",
        "pubertal_status",
        "brain_volume",
        "cortical_sa",
        "same_sex_close_friend",
        "weekday_screentime",
        "non_school_programs",
        "private_instruction",
        "programs_this_year",
        "considerate",
        "helps_hurt",
        "family_fight",
        "family_angry",
        "family_throw",
        "family_temper",
        "family_criticize",
        "family_hit",
        "family_peaceful",
        "family_outdo",
        "parent_perstr",
        "parent_anxdep",
        "parent_withdrawn",
        "parent_somatic",
        "parent_thought",
        "parent_attention",
        "parent_aggressive",
        "parent_depress",
        "parent_anxdisord",
        "parent_avoidant",
        "parent_antisocial",
        "parent_hyperactive",
        "cbcl_anxdep",
        "cbcl_withdep",
        "cbcl_somatic",
        "cbcl_social",
        "cbcl_thought",
        "cbcl_attention",
        "cbcl_rulebreak",
        "cbcl_aggressive",
        "sds_sleep"
    )
)

vis_diff <- dplyr::bind_rows(
    no_diff,
    small_diff,
    big_diff
)

mtbi_mc_d_nmi_pval_vis <- dplyr::full_join(
    mtbi_mc_d_nmi_pval,
    vis_diff,
    by = "feature"
)

write_csv(
    mtbi_mc_d_nmi_pval_vis,
    proc_path("mtbi_mc_d_nmi_pval_vis.csv", TRUE)
)

```

```{r}
mtbi_mc_d_nmi_pval_vis <- read_csv(
    proc_path("2024_05_31_mtbi_mc_d_nmi_pval_vis.csv")
)
```

```{r}
mtbi_mc_d_nmi_vs_pval_thresh <- mtbi_mc_d_nmi_pval_vis |>
    dplyr::filter(neg_log_pval < 10) |>
    dplyr::filter(domain != "B") |>
    na.omit() |>
    ggplot(
        aes(
            x = nmi,
            y = neg_log_pval,
            label = feature
        )
    ) +
    labs(
        x = "Normalized Mutual Information",
        y = expression("-log"[10] * "(p)")
    ) +
    geom_point(
        aes(
            colour = domain,
            shape = type
        ),
        size = 2
    ) +
    geom_smooth(
        aes(
            x = nmi,
            y = neg_log_pval
        ),
        colour = "gray",
        alpha = 0.1,
        method = "lm"
    ) +
    xlim(0, 0.08) +
    annotate(
        "text",
        x = 0.02,
        y = 7.5,
        size = 6,
        label = parse(text = paste0("R^2 == ", mtbi_mc_d_nmi_pval_r2))
    ) +
    theme_bw() +
    theme(
        text = element_text(size = 16)
    ) +
    scale_colour_manual(
        values = c(
            "AS" = "#85929e",
            "D" = "#bb8fce",
            "N" = "#e59866",
            "MH" = "#7fb3d5",
            "P" = "#52be80",
            "S" = "#d98880",
            "B" = "#ff3131"
        )
    ) +
    ggrepel::geom_text_repel(
        aes(
            colour = domain
        )
    )
mtbi_mc_d_nmi_vs_pval_thresh

ggsave(
    fig_path("mtbi_mc_d_nmi_vs_pval_thresh.png", TRUE),
    mtbi_mc_d_nmi_vs_pval_thresh,
    width = 14,
    height = 7,
    dpi = 100
)

mtbi_mc_d_nmi_vs_pval <- mtbi_mc_d_nmi_pval_vis |>
    dplyr::filter(domain != "B") |>
    na.omit() |>
    ggplot(
        aes(
            x = nmi,
            y = neg_log_pval,
            colour = domain,
            shape = type,
            label = feature
        )
    ) +
    labs(
        x = "Normalized Mutual Information",
        y = expression("-log"[10] * "(p)")
    ) +
    geom_point(
        size = 2
    ) +
    ggrepel::geom_text_repel(
        vjust = 2,
        hjust = 1.2,
        max.overlaps = 11,
        size = 3
    ) +
    theme_bw() +
    theme(
        text = element_text(size = 12)
    ) +
    scale_colour_manual(
        values = c(
            "AS" = "#85929e",
            "D" = "#bb8fce",
            "N" = "#e59866",
            "MH" = "#7fb3d5",
            "P" = "#52be80",
            "S" = "#d98880",
            "B" = "#ff3131"
        )
    )
mtbi_mc_d_nmi_vs_pval

ggsave(
    fig_path("mtbi_mc_d_nmi_vs_pval.png", TRUE),
    mtbi_mc_d_nmi_vs_pval,
    width = 10,
    height = 10,
    dpi = 100
)

mtbi_mc_d_nmi_pval_vis$"vis_diff" <- factor(
    mtbi_mc_d_nmi_pval_vis$"vis_diff",
    levels = c("none", "small", "big")
)

mtbi_mc_d_nmi_vs_pval_vs_vis <- mtbi_mc_d_nmi_pval_vis |>
    dplyr::filter(domain != "B") |>
    na.omit() |>
    ggplot(
        aes(
            x = nmi,
            y = neg_log_pval,
            colour = vis_diff,
            label = feature
        )
    ) +
    labs(
        x = "Normalized Mutual Information",
        y = expression("-log"[10] * "(p)"),
        colour = "Perceived\nSeparation\n"
    ) +
    geom_point(
        size = 2
    ) +
    ggrepel::geom_text_repel(
        vjust = 2,
        hjust = 1.2,
        max.overlaps = 11,
        size = 3
    ) +
    theme_bw() +
    theme(
        text = element_text(size = 12)
    ) +
    scale_colour_manual(
        values = c(
            "none" = "red",
            "small" = "#c79c26",
            "big" = "#41ad2f"
        )
    )
mtbi_mc_d_nmi_vs_pval_vs_vis

ggsave(
    fig_path("mtbi_mc_d_nmi_vs_pval_vs_vis.png", TRUE),
    mtbi_mc_d_nmi_vs_pval_vs_vis,
    width = 10,
    height = 10,
    dpi = 100
)

###############################################################################
# Key variable identification
###############################################################################
mtbi_mc_d_nmi_vs_pval_vs_vis_t <- mtbi_mc_d_nmi_pval_vis |>
    dplyr::filter(neg_log_pval < 10) |>
    dplyr::filter(domain != "B") |>
    na.omit() |>
    ggplot(
        aes(
            x = nmi,
            y = neg_log_pval,
            colour = vis_diff,
            label = feature
        )
    ) +
    labs(
        x = "Normalized Mutual Information",
        y = expression("-log"[10] * "(p)"),
        colour = "Perceived\nSeparation\n"
    ) +
    geom_point(
        size = 2
    ) +
    ggrepel::geom_text_repel(
        vjust = 2,
        hjust = 1.2,
        max.overlaps = 11,
        size = 3
    ) +
    theme_bw() +
    theme(
        text = element_text(size = 12)
    ) +
    scale_colour_manual(
        values = c(
            "none" = "red",
            "small" = "#c79c26",
            "big" = "#41ad2f"
        )
    ) +
    geom_segment(
        aes(x = 0.04, xend = 0.04, y = 0, yend = 2.75),
        linetype = "dashed",
        color = "red"
    ) +
    geom_segment(
        aes(x = 0, xend = 0.04, y = 2.75, yend = 2.75),
        linetype = "dashed",
        color = "red"
    ) +
    coord_cartesian(ylim = c(0.1, 10), expand = FALSE)
mtbi_mc_d_nmi_vs_pval_vs_vis_t

ggsave(
    fig_path("mtbi_mc_d_nmi_vs_pval_vs_vis_t.png", TRUE),
    mtbi_mc_d_nmi_vs_pval_vs_vis_t,
    width = 12,
    height = 7,
    dpi = 100
)
```

## Key variables

These are the variables that, based on NMI score, p-values, and visual inspection, appear to be more important in characterizing our cluster solution.

```{r}
mtbi_mc_d_nmi_pval_vis_key <- mtbi_mc_d_nmi_pval_vis |>
    dplyr::filter(nmi > 0.04 | neg_log_pval > 2.75)

write_csv(
    mtbi_mc_d_nmi_pval_vis_key,
    proc_path("mtbi_mc_d_nmi_pval_vis_key.csv", TRUE)
)

mtbi_mc_d_nmi_pval_vis_key <- read_csv(
    proc_path("2024_05_31_mtbi_mc_d_nmi_pval_vis_key.csv")
)

mtbi_mc_d_nmi_pval_vis_key$"feature"
```

The key features appear to be:

- [x] sex
- [ ] brain_volume
- [ ] cortical_sa
- [ ] household_income
- [ ] race
- [ ] non_school_programs
- [ ] programs_this_year
- [ ] pubertal_status
- [ ] weekend_screentime
- [ ] parent_thought
- [ ] parent_somatic
- [ ] fmri_cort_subcort_cors
- [ ] parent_aggressive
- [ ] parent_avoidant
- [ ] private_instruction
- [ ] parent_withdrawn
- [ ] parent_antisocial
- [ ] weekday_screentime
- [ ] parent_anxdisord
- [ ] parent_hyperactive
- [ ] family_peaceful
- [ ] parent_intrusive
- [ ] fmri_cort_cors
- [ ] parent_anxdep
- [ ] parent_perstr
- [ ] parent_depress
- [ ] family_temper
- [ ] considerate
- [ ] helps_hurt
- [ ] family_outdo
- [ ] same_sex_close_friend
- [ ] family_angry
- [ ] family_fight
- [ ] parent_attention
- [ ] family_criticize

In the next sections, I'll step through exactly how each of these key features differ.

## Sex

```{r}
sex_plot <- plot_list$"sex" +
    ggplot2::labs(
        fill = "Sex",
        x = "Cluster"
    ) +
    ggplot2::scale_fill_hue(
        labels = c(
            "1" = "F",
            "0" = "M"
        )
    )

ggsave(
    plot = sex_plot,
    filename = fig_path("mtbi_mc_d_sex_plot_clean.png", TRUE)
)
```

Clusters 1 and 2 appear to be primarily male, while cluster 3 appears to be primarily female.

## Neuroimaging measures

HERE I AM

```{r}

plot_list$"brain_volume" +
    ggplot2::labs(
        x = "Cluster",
        y = "Brain Volume"
    )

plot_list$"cortical_sa"

plot_list$"fmri_cort_subcort_cors"

```


# Label propagation

This top solution specifically came from the third imputed dataset, so that's what we'll label propagate off of.

```{r}

all_dls |> names()

train_data_list_m3 <- all_dls$"mtbi_train_data_lists"$"imp_3"

test_data_list_m1 <- all_dls$"mtbi_test_data_lists"$"imp_1"

full_data_list <- merge_data_lists(train_data_list_m3, test_data_list_m1)

my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

mtbi_mc_a <- mtbi_rep[1, ]

set.seed(42)
mtbi_mc_a_lp <- lp_solutions_matrix(
    mtbi_mc_a,
    full_data_list,
    distance_metrics_list = my_distance_metrics
)
colnames(mtbi_mc_a_lp) <- c("subjectkey", "group", "cluster")

mtbi_mc_a_lp <- mtbi_mc_a_lp |>
    dplyr::filter(group == "test") |>
    dplyr::select(-group)

write_csv(mtbi_mc_a_lp, proc_path("mtbi_mc_a_lp.csv", TRUE))

mtbi_mc_a_lp <- read_csv(proc_path("2024_04_23_mtbi_mc_a_lp.csv"))

mtbi_mc_a_lp_plots <- characterize_solution(
    cluster_df = mtbi_mc_a_lp,
    data_list = c(
        all_dls$"mtbi_test_data_lists"$"imp_1",
        all_dls$"mtbi_test_oom_lists"$"imp_1"
    ),
    plotname = fig_path("mtbi_mc_a_lp", TRUE),
    individual_plots = TRUE,
    group_plots = TRUE
)

```

(Leave below for later)

# Longitudinal analyses

```{r}

#mtbi_train <- read_csv(sub_path("2024_03_12_mtbi_train_subjects.csv"))

core_path <- path_maker(here(paste0("data/abcd/core")))

import <- function(path) {
    return(abcd_load(core_path(path)))
}

mh_p_cbcl <- import("mental-health/mh_p_cbcl.csv")
ph_p_sds <- import("physical-health/ph_p_sds.csv")

mc_d_cluster_df <- get_cluster_df(mtbi_mc_d_esm)

mc_d_subs <- gsub("subject_", "", mc_d_cluster_df$"subjectkey")

syndromes <- c(
    "anxdep",
    #"withdep",
    #"somatic",
    #"social",
    #"thought",
    #"attention",
    #"rulebreak",
    "aggressive"
)

tps <- c(0, 1, 2, 3)

get_syndrome_long <- function(syndrome, timepoints, subs) {
    full_df <- NULL
    for (tp in timepoints) {
        outcomes <- get_cbcl_syndrome_scale(
            syndrome = syndrome,
            mh_p_cbcl,
            raw = FALSE,
            subjects = subs,
            t = tp
        )
        outcomes$"tp" <- tp
        if (is.null(full_df)) {
            full_df <- outcomes
        } else {
            full_df <- rbind(full_df, outcomes)
        }
    }
    return(full_df)
}



# make change score plots where you plot time on x-axis and visualize change
# by absolute t-score differences for 2 year and 3 year follow up

# Option 1
z <- get_syndrome_long("anxdep", tps, mc_d_subs)
z$"subjectkey" <- paste0("subject_", z$"subjectkey")
z_long <- dplyr::full_join(z, mc_d_cluster_df, by = "subjectkey")
z_long$"cluster" <- factor(z_long$"cluster")
anxdep <- ggplot(
    na.omit(z_long),
    aes(x = tp, y = cbcl_scr_syn_anxdep_t, colour = cluster, group = subjectkey)
) +
    geom_point() +
    geom_line() +
    facet_grid(cluster ~ .) +
    theme_bw()
ggsave("anxdep.png", anxdep)

z <- get_syndrome_long("withdep", tps, mc_d_subs)
z$"subjectkey" <- paste0("subject_", z$"subjectkey")
z_long <- dplyr::full_join(z, mc_d_cluster_df, by = "subjectkey")
z_long$"cluster" <- factor(z_long$"cluster")
withdep <- ggplot(
    na.omit(z_long),
    aes(x = tp, y = cbcl_scr_syn_withdep_t, colour = cluster, group = subjectkey)
) +
    geom_point() +
    geom_line() +
    facet_grid(cluster ~ .) +
    theme_bw()
ggsave("withdep.png", withdep)

z <- get_syndrome_long("aggressive", tps, mc_d_subs)
z$"subjectkey" <- paste0("subject_", z$"subjectkey")
z_long <- dplyr::full_join(z, mc_d_cluster_df, by = "subjectkey")
z_long$"cluster" <- factor(z_long$"cluster")
aggressive <- ggplot(
    na.omit(z_long),
    aes(x = tp, y = cbcl_scr_syn_aggressive_t, colour = cluster, group = subjectkey)
) +
    geom_point() +
    geom_line() +
    facet_grid(cluster ~ .) +
    theme_bw()
ggsave("aggressive.png", aggressive)



qq <- get_syndrome_long("anxdep", tps, mc_d_subs)
qq$"subjectkey" <- paste0("subject_", qq$"subjectkey")
qq_long <- dplyr::full_join(qq, mc_d_cluster_df, by = "subjectkey")
qq_long$"cluster" <- factor(qq_long$"cluster")
qq_long <- na.omit(qq_long)
for (subject in unique(qq_long$"subjectkey")) {
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 3, "cbcl_scr_syn_anxdep_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 3, "cbcl_scr_syn_anxdep_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_anxdep_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 2, "cbcl_scr_syn_anxdep_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 2, "cbcl_scr_syn_anxdep_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_anxdep_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 1, "cbcl_scr_syn_anxdep_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 1, "cbcl_scr_syn_anxdep_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_anxdep_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_anxdep_t"] <- 0
}
anxdep2 <- ggplot(
    na.omit(qq_long),
    aes(x = tp, y = cbcl_scr_syn_anxdep_t, colour = cluster, group = subjectkey)
) +
    geom_point() +
    geom_line() +
    facet_grid(cluster ~ .) +
    theme_bw()
ggsave("anxdep2.png", anxdep2)

qq <- get_syndrome_long("aggressive", tps, mc_d_subs)
qq$"subjectkey" <- paste0("subject_", qq$"subjectkey")
qq_long <- dplyr::full_join(qq, mc_d_cluster_df, by = "subjectkey")
qq_long$"cluster" <- factor(qq_long$"cluster")
qq_long <- na.omit(qq_long)
for (subject in unique(qq_long$"subjectkey")) {
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 3, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 3, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 2, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 2, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 1, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 1, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"] <- 0
}
aggressive2 <- ggplot(
    na.omit(qq_long),
    aes(x = tp, y = cbcl_scr_syn_aggressive_t, colour = cbcl_scr_syn_aggressive_t > 0, group = subjectkey)
) +
    geom_point() +
    geom_line() +
    facet_grid(cluster ~ .) +
    theme_bw()
ggsave("aggressive3.png", aggressive2)


qq <- get_syndrome_long("aggressive", tps, mc_d_subs)
qq$"subjectkey" <- paste0("subject_", qq$"subjectkey")
qq_long <- dplyr::full_join(qq, mc_d_cluster_df, by = "subjectkey")
qq_long$"cluster" <- factor(qq_long$"cluster")
for (subject in unique(qq_long$"subjectkey")) {
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 3, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 3, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 2, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 2, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 1, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 1, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"] <- 0
}
unique(qq_long$"subjectkey")
parent <- all_dls$"mtbi_train_data_lists"$"imp_1"[[24]]$"data"
summarize_dl(all_dls$"mtbi_train_data_lists"$"imp_1")
qq_long <- dplyr::full_join(qq_long, parent, by = "subjectkey")
aggressive4 <- ggplot(
    na.omit(qq_long),
    aes(x = tp, y = cbcl_scr_syn_aggressive_t, colour = parent_aggressive > 60, group = subjectkey)
) +
    geom_point() +
    geom_line() +
    facet_grid(cluster ~ .) +
    theme_bw()
aggressive4
ggsave("aggressive4.png", aggressive4)

qq <- get_syndrome_long("aggressive", tps, mc_d_subs)
qq$"subjectkey" <- paste0("subject_", qq$"subjectkey")
qq_long <- dplyr::full_join(qq, mc_d_cluster_df, by = "subjectkey")
qq_long$"cluster" <- factor(qq_long$"cluster")
for (subject in unique(qq_long$"subjectkey")) {
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 3, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 3, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 2, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 2, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 1, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 1, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"] <- 0
}
unique(qq_long$"subjectkey")
income <- all_dls$"mtbi_train_data_lists"$"imp_1"[[7]]$"data"
qq_long <- dplyr::full_join(qq_long, income, by = "subjectkey")
aggressive5 <- ggplot(
    na.omit(qq_long),
    aes(x = tp, y = cbcl_scr_syn_aggressive_t, colour = household_income, group = subjectkey)
) +
    geom_point() +
    geom_line() +
    facet_grid(cluster ~ .) +
    theme_bw()
aggressive5
ggsave("aggressive5.png", aggressive5)


qq <- get_syndrome_long("aggressive", tps, mc_d_subs)
qq$"subjectkey" <- paste0("subject_", qq$"subjectkey")
qq_long <- dplyr::full_join(qq, mc_d_cluster_df, by = "subjectkey")
qq_long$"cluster" <- factor(qq_long$"cluster")
for (subject in unique(qq_long$"subjectkey")) {
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 3, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 3, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 2, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 2, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 1, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 1, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"] <- 0
}
unique(qq_long$"subjectkey")
data <- collapse_dl(all_dls$"mtbi_train_data_lists"$"imp_1")
qq_long <- dplyr::full_join(qq_long, data, by = "subjectkey")
aggressive6 <- ggplot(
    na.omit(qq_long),
    aes(x = tp, y = cbcl_scr_syn_aggressive_t, colour = sex, group = subjectkey)
) +
    geom_point() +
    geom_line() +
    facet_grid(cluster ~ .) +
    theme_bw()
aggressive6
ggsave("aggressive6.png", aggressive6)

for (tp in c(1, 2, 3)) {
    long_outcomes <- NULL
    for (syndrome in syndromes) {
        if (is.null(long_outcomes)) {
            long_outcomes <- get_cbcl_syndrome_scale(
                syndrome = syndrome,
                mh_p_cbcl,
                raw = FALSE,
                subjects = mtbi_train,
                t = tp
            )
        } else {
            long_outcomes <- dplyr::inner_join(
                long_outcomes,
                get_cbcl_syndrome_scale(
                    syndrome = syndrome,
                    mh_p_cbcl,
                    raw = FALSE,
                    subjects = mtbi_train,
                    t = tp
                ),
                by = "subjectkey"
            )
        }
    }
    long_outcomes <- dplyr::inner_join(
        long_outcomes,
        get_sds_total_probs(
            ph_p_sds,
            mtbi_train,
            t = tp
        ),
        by = "subjectkey"
    )
    long_outcomes$"subjectkey" <- paste0("subject_", long_outcomes$"subjectkey")
    colnames(long_outcomes) <- c(
        "subjectkey",
        paste0("cbcl_", syndromes),
        "sds_sleep"
    )
    baseline_outcomes <- collapse_dl(oom_list_m3)
    d_outcomes <- NULL
    for (outcome in colnames(baseline_outcomes[-1])) {
        t0 <- dplyr::select(baseline_outcomes, "subjectkey", outcome)
        tn <- dplyr::select(long_outcomes, "subjectkey", outcome)
        colnames(t0) <- c("subjectkey", paste0(outcome, "_0"))
        colnames(tn) <- c("subjectkey", paste0(outcome, "_", tp))
        both_t <- dplyr::inner_join(t0, tn, by = "subjectkey")
        both_t[, 4] <- both_t[, 3] - both_t[, 2]
        colnames(both_t)[4] <- paste0("d_", outcome)
        both_t <- both_t[, c(1, 4)]
        if (is.null(d_outcomes)) {
            d_outcomes <- both_t
        } else {
            d_outcomes <- dplyr::full_join(d_outcomes, both_t, by = "subjectkey")
        }
    }
    mtbi_mc_a <- mtbi_rep[1, ]
    mtbi_mc_a <- get_cluster_df(mtbi_mc_a)
    mtbi_mc_a <- dplyr::full_join(
        mtbi_mc_a,
        d_outcomes,
        by = "subjectkey"
    )
    mtbi_mc_a$"cluster" <- factor(mtbi_mc_a$"cluster")
    d_plots <- list()
    for (outcome in colnames(d_outcomes)[-1]) {
        plot <- mtbi_mc_a |>
            ggplot(
                aes(
                    x = cluster,
                    y = !!sym(outcome),
                    colour = cluster
                )
            ) +
            geom_violin(alpha = 0.4) +
            geom_jitter(width = 0.2, height = 0.2) +
            stat_summary(
                fun = "mean",
                geom = "point",
                colour = "black",
                size = 2
            ) +
            labs(
                x = "Cluster",
                y = gsub("d_", "Δ", outcome)
            ) +
            theme_bw() +
            theme(
                legend.position = "none"
            )
        d_plots[[length(d_plots) + 1]] <- plot
    }
    d_plots <- d_plots |>
        wrap_plots() +
        plot_annotation(
            paste0("CBCL/SDS Outcomes, ", tp, "-year Follow-Up Minus Baseline"),
            theme = theme(plot.title=element_text(hjust=0.5))
        )
    # Looks like cluster 1 has the higher variance, indicating potential for intervention?
    ggsave(
        plot = d_plots,
        filename = fig_path(
            paste0("mtbi_mc_a_outcomes_t", tp, "_plots.png"),
            TRUE
        ),
        width = 8,
        height = 8,
        dpi = 120
    )
}

full_df <- NULL
for (tp in c(0, 1, 2, 3, 4)) {
    long_outcomes <- NULL
    for (syndrome in syndromes) {
        if (is.null(long_outcomes)) {
            long_outcomes <- get_cbcl_syndrome_scale(
                syndrome = syndrome,
                mh_p_cbcl,
                raw = FALSE,
                subjects = mtbi_train,
                t = tp
            )
            colnames(long_outcomes) <- c("subjectkey", syndrome)
        } else {
            new_df <- get_cbcl_syndrome_scale(
                syndrome = syndrome,
                mh_p_cbcl,
                raw = FALSE,
                subjects = mtbi_train,
                t = tp
            )
            colnames(new_df) <- c("subjectkey", syndrome)
            long_outcomes <- dplyr::full_join(
                long_outcomes,
                new_df,
                by = "subjectkey"
            )
        }
    }
    long_outcomes$"tp" <- tp
    if (is.null(full_df)) {
        full_df <- long_outcomes
    } else {
        full_df <- rbind(full_df, long_outcomes)
    }
}
full_df$"subjectkey" <- paste0("subject_", full_df$"subjectkey")
mtbi_mc_a <- mtbi_rep[1, ]
mtbi_mc_a <- get_cluster_df(mtbi_mc_a)
mtbi_mc_a$"cluster" <- factor(mtbi_mc_a$"cluster")
full_df <- dplyr::full_join(full_df, mtbi_mc_a, by = "subjectkey")
full_df$"tp" <- factor(full_df$"tp")
full_df |>
    dplyr::filter(cluster == 1) |>
    na.omit() |>
    ggplot(
        aes(
            x = tp,
            y = aggressive,
            group = subjectkey,
            colour = cluster
        )
    ) +
    geom_line() +
    geom_point() +
    theme_bw()

nrow(mtbi_mc_a)

head(mtbi_mc_a)

head(long_outcomes)
```


## A deeper dive at feature separation

```{r}
dl_df <- auto_plot(
    solutions_matrix_row = mtbi_mc_d_esm,
    data_list = all_dls$"mtbi_train_data_lists"$"imp_3",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_3",
    return_plots = FALSE
)

dl_df |>
    dplyr::filter(sex == 0) |>
    ggplot(
        aes(
            x = race,
            y = brain_volume,
            colour = race,
            group = race
        )
    ) +
    geom_point() +
    theme_bw() +
    facet_grid(household_income ~ .)

dl_df$"household_income" <- factor(dl_df$"household_income")
dl_df$"sex" <- factor(dl_df$"sex")

dl_df |>
    ggplot(
        aes(
            x = household_income,
            y = cbcl_aggressive,
            colour = race,
            group = interaction(race, household_income)
        )
    ) +
    geom_violin(position = position_dodge(width = 0.75)) +
    geom_jitter(
        position = position_jitterdodge(
            jitter.width = 0,
            jitter.height = 0.5
        ),
    ) +
    theme_bw()

dl_df |>
    ggplot(
        aes(
            x = sex,
            y = cbcl_aggressive,
            colour = race,
            group = interaction(race, sex)
        )
    ) +
    geom_boxplot(position = position_dodge(width = 0.75), width = 0.4) +
    geom_jitter(
        position = position_jitterdodge(
            jitter.width = 0,
            jitter.height = 0.5
        ),
    ) +
    theme_bw()
```



