# Data Preprocessing

This chapter contains:
1. Removal of neuroimaging data failing QC
2. Train/test split
3. Mice imputation
4. Organization of imputed data into exported R lists

## Importing Extracted Data

```{r}
library(abcdutils)
library(here)
library(dplyr)
library(readr)
library(metasnf)
library(mice)
library(rlist)

#source("abcd/helper_functions.R")

input_path <- path_maker(here(paste0("data/abcd/inputs")))
core_path <- path_maker(here(paste0("data/abcd/core")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))

# Subjects
mtbi_subs <- read_subjects(sub_path("2025_02_07_mtbi_subs.csv"))
unij_subs <- read_subjects(sub_path("2025_02_07_unij_subs.csv"))

read <- function(path) {
    read_csv(input_path(path))
}
```

```{r}
# CHECKPOINT
# mTBI subjects
as_mem_daze_mtbi <- read("2025_02_07_as_mem_daze_mtbi.csv")
as_mechanism_mtbi <- read("2025_02_07_as_mechanism_mtbi.csv")
as_loc_mtbi <- read("2025_02_07_as_loc_mtbi.csv")
d_interview_age_mtbi <- read("2025_02_07_d_interview_age_mtbi.csv")
d_mtbi_age_mtbi <- read("2025_02_07_d_mtbi_age_mtbi.csv")
d_sex_mtbi <- read("2025_02_07_d_sex_mtbi.csv")
d_income_mtbi <- read("2025_02_07_d_income_mtbi.csv")
d_race_mtbi <- read("2025_02_07_d_race_mtbi.csv")
d_pubertal_status_mtbi <- read("2025_02_07_d_pubertal_status_mtbi.csv")
mh_headaches_mtbi <- read("2025_02_07_mh_headaches_mtbi.csv")
mh_mtbi_count_mtbi <- read("2025_02_07_mh_mtbi_count_mtbi.csv")
sm_subc_v_mtbi <- read("2025_02_07_sm_subc_v_mtbi.csv")
sm_cort_t_mtbi <- read("2025_02_07_sm_cort_t_mtbi.csv")
sm_cort_sa_mtbi <- read("2025_02_07_sm_cort_sa_mtbi.csv")
dm_all_wmnd_mtbi <- read("2025_02_07_dm_all_wmnd_mtbi.csv")
rm_gord_cor_mtbi <- read("2025_02_07_rm_gord_cor_mtbi.csv")
rm_subc_cor_mtbi <- read("2025_02_07_rm_subc_cor_mtbi.csv")
p_friends_mtbi <- read("2025_02_07_p_friends_mtbi.csv")
p_screen_time_mtbi <- read("2025_02_07_p_screen_time_mtbi.csv")
p_sports_mtbi <- read("2025_02_07_p_sports_mtbi.csv")
p_exercise_mtbi <- read("2025_02_07_p_exercise_mtbi.csv")
p_prosocial_mtbi <- read("2025_02_07_p_prosocial_mtbi.csv")
p_fam_fn_mtbi <- read("2025_02_07_p_fam_fn_mtbi.csv")
p_parent_psych_mtbi <- read("2025_02_07_p_parent_psych_mtbi.csv")
cbcl_mtbi <- read("2025_02_07_cbcl_mtbi.csv")
sds_mtbi <- read("2025_02_07_sds_mtbi.csv")

# unijured subjects
d_interview_age_unij <- read("2025_02_07_d_interview_age_unij.csv")
d_sex_unij <- read("2025_02_07_d_sex_unij.csv")
d_income_unij <- read("2025_02_07_d_income_unij.csv")
d_race_unij <- read("2025_02_07_d_race_unij.csv")
d_pubertal_status_unij <- read("2025_02_07_d_pubertal_status_unij.csv")
mh_headaches_unij <- read("2025_02_07_mh_headaches_unij.csv")
sm_subc_v_unij <- read("2025_02_07_sm_subc_v_unij.csv")
sm_cort_t_unij <- read("2025_02_07_sm_cort_t_unij.csv")
sm_cort_sa_unij <- read("2025_02_07_sm_cort_sa_unij.csv")
dm_all_wmnd_unij <- read("2025_02_07_dm_all_wmnd_unij.csv")
rm_gord_cor_unij <- read("2025_02_07_rm_gord_cor_unij.csv")
rm_subc_cor_unij <- read("2025_02_07_rm_subc_cor_unij.csv")
p_friends_unij <- read("2025_02_07_p_friends_unij.csv")
p_screen_time_unij <- read("2025_02_07_p_screen_time_unij.csv")
p_sports_unij <- read("2025_02_07_p_sports_unij.csv")
p_exercise_unij <- read("2025_02_07_p_exercise_unij.csv")
p_prosocial_unij <- read("2025_02_07_p_prosocial_unij.csv")
p_fam_fn_unij <- read("2025_02_07_p_fam_fn_unij.csv")
p_parent_psych_unij <- read("2025_02_07_p_parent_psych_unij.csv")
cbcl_unij <- read("2025_02_07_cbcl_unij.csv")
sds_unij <- read("2025_02_07_sds_unij.csv")
```

## Neuroimaging quality control

Subset neuroimaging data to those subjects who pass neuroimaging QC and PC.

```{r}
# QC data
mri_y_qc_raw_smr_t1 <- abcd_load(core_path("imaging/mri_y_qc_raw_smr_t1.csv"))
mri_y_qc_raw_smr_t2 <- abcd_load(core_path("imaging/mri_y_qc_raw_smr_t2.csv"))
mri_y_qc_raw_rsfmr <- abcd_load(core_path("imaging/mri_y_qc_raw_rsfmr.csv"))
mri_y_qc_raw_dmr <- abcd_load(core_path("imaging/mri_y_qc_raw_dmr.csv"))

# sMRI
smri_qc_mtbi <- qc_smri(mri_y_qc_raw_smr_t1, t = 0, subjects = mtbi_subs, metric = "qc")
smri_pc_mtbi <- qc_smri(mri_y_qc_raw_smr_t1, t = 0, subjects = mtbi_subs, metric = "pc")
smri_qc_unij <- qc_smri(mri_y_qc_raw_smr_t1, t = 0, subjects = unij_subs, metric = "qc")
smri_pc_unij <- qc_smri(mri_y_qc_raw_smr_t1, t = 0, subjects = unij_subs, metric = "pc")

# dMRI
dmri_qc_mtbi <- qc_dmri(mri_y_qc_raw_dmr, t = 0, subjects = mtbi_subs, metric = "qc")
dmri_pc_mtbi <- qc_dmri(mri_y_qc_raw_dmr, t = 0, subjects = mtbi_subs, metric = "pc")
dmri_qc_unij <- qc_dmri(mri_y_qc_raw_dmr, t = 0, subjects = unij_subs, metric = "qc")
dmri_pc_unij <- qc_dmri(mri_y_qc_raw_dmr, t = 0, subjects = unij_subs, metric = "pc")

# rs-fMRI
rsfmri_qc_mtbi <- qc_rsfmri(mri_y_qc_raw_rsfmr, t = 0, subjects = mtbi_subs, metric = "qc")
rsfmri_pc_mtbi <- qc_rsfmri(mri_y_qc_raw_rsfmr, t = 0, subjects = mtbi_subs, metric = "pc")
rsfmri_qc_unij <- qc_rsfmri(mri_y_qc_raw_rsfmr, t = 0, subjects = unij_subs, metric = "qc")
rsfmri_pc_unij <- qc_rsfmri(mri_y_qc_raw_rsfmr, t = 0, subjects = unij_subs, metric = "pc")

smri_pass <- c(
    intersect(smri_qc_mtbi$"pass", smri_pc_mtbi$"pass"),
    intersect(smri_qc_unij$"pass", smri_pc_unij$"pass")
)

dmri_pass <- c(
    intersect(dmri_qc_mtbi$"pass", dmri_pc_mtbi$"pass"),
    intersect(dmri_qc_unij$"pass", dmri_pc_unij$"pass")
)

rsfmri_pass <- c(
    intersect(rsfmri_qc_mtbi$"pass", rsfmri_pc_mtbi$"pass"),
    intersect(rsfmri_qc_unij$"pass", rsfmri_pc_unij$"pass")
)

sm_subc_v_qc_mtbi <- filter(sm_subc_v_mtbi, subjectkey %in% smri_pass)
sm_cort_t_qc_mtbi <- filter(sm_cort_t_mtbi, subjectkey %in% smri_pass)
sm_cort_sa_qc_mtbi <- filter(sm_cort_sa_mtbi, subjectkey %in% smri_pass)
sm_subc_v_qc_unij <- filter(sm_subc_v_unij, subjectkey %in% smri_pass)
sm_cort_t_qc_unij <- filter(sm_cort_t_unij, subjectkey %in% smri_pass)
sm_cort_sa_qc_unij <- filter(sm_cort_sa_unij, subjectkey %in% smri_pass)
dm_all_wmnd_qc_mtbi <- filter(dm_all_wmnd_mtbi, subjectkey %in% dmri_pass)
dm_all_wmnd_qc_unij <- filter(dm_all_wmnd_unij, subjectkey %in% dmri_pass)
rm_gord_cor_qc_mtbi <- filter(rm_gord_cor_mtbi, subjectkey %in% rsfmri_pass)
rm_subc_cor_qc_mtbi <- filter(rm_subc_cor_mtbi, subjectkey %in% rsfmri_pass)
rm_gord_cor_qc_unij <- filter(rm_gord_cor_unij, subjectkey %in% rsfmri_pass)
rm_subc_cor_qc_unij <- filter(rm_subc_cor_unij, subjectkey %in% rsfmri_pass)

write_csv(sm_cort_sa_qc_mtbi, input_path("sm_cort_sa_qc_mtbi.csv", TRUE))
write_csv(sm_cort_t_qc_mtbi, input_path("sm_cort_t_qc_mtbi.csv", TRUE))
write_csv(sm_subc_v_qc_mtbi, input_path("sm_subc_v_qc_mtbi.csv", TRUE))
write_csv(sm_cort_sa_qc_unij, input_path("sm_cort_sa_qc_unij.csv", TRUE))
write_csv(sm_cort_t_qc_unij, input_path("sm_cort_t_qc_unij.csv", TRUE))
write_csv(sm_subc_v_qc_unij, input_path("sm_subc_v_qc_unij.csv", TRUE))
write_csv(dm_all_wmnd_qc_mtbi, input_path("dm_all_wmnd_qc_mtbi.csv", TRUE))
write_csv(dm_all_wmnd_qc_unij, input_path("dm_all_wmnd_qc_unij.csv", TRUE))
write_csv(rm_gord_cor_qc_mtbi, input_path("rm_gord_cor_qc_mtbi.csv", TRUE))
write_csv(rm_subc_cor_qc_mtbi, input_path("rm_subc_cor_qc_mtbi.csv", TRUE))
write_csv(rm_gord_cor_qc_unij, input_path("rm_gord_cor_qc_unij.csv", TRUE))
write_csv(rm_subc_cor_qc_unij, input_path("rm_subc_cor_qc_unij.csv", TRUE))
```

```{r}
# CHECKPOINT
sm_cort_sa_qc_mtbi <- read("2025_02_07_sm_cort_sa_qc_mtbi.csv")
sm_cort_t_qc_mtbi <- read("2025_02_07_sm_cort_t_qc_mtbi.csv")
sm_subc_v_qc_mtbi <- read("2025_02_07_sm_subc_v_qc_mtbi.csv")
sm_cort_sa_qc_unij <- read("2025_02_07_sm_cort_sa_qc_unij.csv")
sm_cort_t_qc_unij <- read("2025_02_07_sm_cort_t_qc_unij.csv")
sm_subc_v_qc_unij <- read("2025_02_07_sm_subc_v_qc_unij.csv")
dm_all_wmnd_qc_mtbi <- read("2025_02_07_dm_all_wmnd_qc_mtbi.csv")
dm_all_wmnd_qc_unij <- read("2025_02_07_dm_all_wmnd_qc_unij.csv")
rm_gord_cor_qc_mtbi <- read("2025_02_07_rm_gord_cor_qc_mtbi.csv")
rm_subc_cor_qc_mtbi <- read("2025_02_07_rm_subc_cor_qc_mtbi.csv")
rm_gord_cor_qc_unij <- read("2025_02_07_rm_gord_cor_qc_unij.csv")
rm_subc_cor_qc_unij <- read("2025_02_07_rm_subc_cor_qc_unij.csv")
```

## Train/Test Split

To avoid having training and testing data inform each other during imputation, we assign the splits prior to the imputation.
This is only done in our primary analysis group (baseline mTBI).

```{r}
mtbi_split <- train_test_assign(train_frac = 0.8, uids = mtbi_subs)

mtbi_train <- mtbi_split$"train"
mtbi_test <- mtbi_split$"test"

write_subjects(mtbi_train, sub_path("mtbi_train_subs.csv", TRUE))
write_subjects(mtbi_test, sub_path("mtbi_test_subs.csv", TRUE))

mtbi_train_subs <- read_subjects(sub_path("2025_02_07_mtbi_train_subs.csv"))
mtbi_test_subs <- read_subjects(sub_path("2025_02_07_mtbi_test_subs.csv"))

train_filter <- function(df) {
    filtered_df <- dplyr::filter(df, df$"subjectkey" %in% mtbi_train_subs)
    return(filtered_df)
}

test_filter <- function(df) {
    filtered_df <- dplyr::filter(df, df$"subjectkey" %in% mtbi_test_subs)
    return(filtered_df)
}

mtbi_df_list <- list(
    "as_mem_daze_mtbi" = as_mem_daze_mtbi,
    "as_mechanism_mtbi" = as_mechanism_mtbi,
    "as_loc_mtbi" = as_loc_mtbi,
    "d_interview_age_mtbi" = d_interview_age_mtbi,
    "d_mtbi_age_mtbi" = d_mtbi_age_mtbi,
    "d_sex_mtbi" = d_sex_mtbi,
    "d_income_mtbi" = d_income_mtbi,
    "d_race_mtbi" = d_race_mtbi,
    "d_pubertal_status_mtbi" = d_pubertal_status_mtbi,
    "mh_headaches_mtbi" = mh_headaches_mtbi,
    "mh_mtbi_count_mtbi" = mh_mtbi_count_mtbi,
    "sm_subc_v_qc_mtbi" = sm_subc_v_qc_mtbi,
    "sm_cort_t_qc_mtbi" = sm_cort_t_qc_mtbi,
    "sm_cort_sa_qc_mtbi" = sm_cort_sa_qc_mtbi,
    "dm_all_wmnd_qc_mtbi" = dm_all_wmnd_qc_mtbi,
    "rm_gord_cor_qc_mtbi" = rm_gord_cor_qc_mtbi,
    "rm_subc_cor_qc_mtbi" = rm_subc_cor_qc_mtbi,
    "p_friends_mtbi" = p_friends_mtbi,
    "p_screen_time_mtbi" = p_screen_time_mtbi,
    "p_sports_mtbi" = p_sports_mtbi,
    "p_exercise_mtbi" = p_exercise_mtbi,
    "p_prosocial_mtbi" = p_prosocial_mtbi,
    "p_fam_fn_mtbi" = p_fam_fn_mtbi,
    "p_parent_psych_mtbi" = p_parent_psych_mtbi,
    "cbcl_mtbi" = cbcl_mtbi,
    "sds_mtbi" = sds_mtbi
)

unij_df_list <- list(
    "d_interview_age_unij" = d_interview_age_unij,
    "d_sex_unij" = d_sex_unij,
    "d_income_unij" = d_income_unij,
    "d_race_unij" = d_race_unij,
    "d_pubertal_status_unij" = d_pubertal_status_unij,
    "mh_headaches_unij" = mh_headaches_unij,
    "sm_subc_v_qc_unij" = sm_subc_v_qc_unij,
    "sm_cort_t_qc_unij" = sm_cort_t_qc_unij,
    "sm_cort_sa_qc_unij" = sm_cort_sa_qc_unij,
    "dm_all_wmnd_qc_unij" = dm_all_wmnd_qc_unij,
    "rm_gord_cor_qc_unij" = rm_gord_cor_qc_unij,
    "rm_subc_cor_qc_unij" = rm_subc_cor_qc_unij,
    "p_friends_unij" = p_friends_unij,
    "p_screen_time_unij" = p_screen_time_unij,
    "p_sports_unij" = p_sports_unij,
    "p_exercise_unij" = p_exercise_unij,
    "p_prosocial_unij" = p_prosocial_unij,
    "p_fam_fn_unij" = p_fam_fn_unij,
    "p_parent_psych_unij" = p_parent_psych_unij,
    "cbcl_unij" = cbcl_unij,
    "sds_unij" = sds_unij
)

mtbi_train_df_list <- lapply(mtbi_df_list, train_filter)
mtbi_test_df_list <- lapply(mtbi_df_list, test_filter)
```

## Imputation

SNF requires complete data as input for integration.

Data will be imputed under the following schemes:

- 5 imputations of mTBI data alone
- 5 imputations of unijured data alone
- 5 imputations of mTBI + unijured data together

Resulting in 10 versions of the mTBI data and 10 versions of the unijured data.

First, each group has their extracted dataframes merged into a single one for imputation.

```{r}
mtbi_train_df <- metasnf::merge_df_list(
    mtbi_train_df_list,
    uid = "subjectkey",
    join = "full"
)

mtbi_test_df <- metasnf::merge_df_list(
    mtbi_test_df_list,
    uid = "subjectkey",
    join = "full"
)

unij_df <- metasnf::merge_df_list(
    unij_df_list,
    uid = "subjectkey",
    join = "full"
)

write_csv(mtbi_test_df, proc_path("mtbi_test_df.csv", TRUE))
write_csv(mtbi_train_df, proc_path("mtbi_train_df.csv", TRUE))
write_csv(unij_df, proc_path("unij_df.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_train_df <- data.frame(read_csv(proc_path("2025_02_07_mtbi_train_df.csv")))
mtbi_test_df <- data.frame(read_csv(proc_path("2025_02_07_mtbi_test_df.csv")))
unij_df <- data.frame(read_csv(proc_path("2025_02_07_unij_df.csv")))
```


A check of which columns have missing data.

```{r}
missing_colnames_mtbi <- names(which(colSums(is.na(mtbi_train_df)) > 0))
missing_colnames_mtbi

missing_colnames_unij <- names(which(colSums(is.na(unij_df)) > 0))
missing_colnames_unij

# Remove the subjectkey variable
mtbi_train_df_no_subs <- char_to_fac(mtbi_train_df[, -1])
mtbi_test_df_no_subs <- char_to_fac(mtbi_test_df[, -1])
unij_df_no_subs <- char_to_fac(unij_df[, -1])

# Function that checks which variables have the biggest correlations
pairwise_correlations <- function(df, threshold = 0) {
    # Remove missing data to help calculate correlations
    df <- na.omit(df)
    # Remove non-numeric columns
    non_numeric_cols <- sapply(df, function(x) !is.numeric(x))
    df <- df[, !non_numeric_cols]
    # Calculate correlations
    correlations <- cor(df)
    # Ignore self-correlations
    diag(correlations) <- 0
    # Take absolute value of the correlations, as strong anti-correlations also
    # lead to strong linear dependence
    abs_cor <- abs(correlations)
    # Create dataframe of all pairs of correlations
    pairs <- t(combn(colnames(abs_cor), 2))
    paired_cors <- data.frame(pairs, cor = abs_cor[pairs])
    # Filter to only correlations bigger than a specified threshold
    paired_cors <- paired_cors[paired_cors$"cor" > threshold, ]
    return(paired_cors)
}

# Function to help sort variables by pairwise correlations
top_correlating_vars <- function(df, threshold = 0) {
    # Dataframe highlighting strongest correlations
    df <- pairwise_correlations(df, threshold)
    # Iteratively build up an ordered correlations matrix by:
    #   - Record one of the two variables contributing to the largest
    #     pairwise correlation
    #   - Remove that variables from the list of all pairs of correlations
    #   - Repeat until all variables have been removed
    max_cor_df <- data.frame(
        variable = as.character(),
        max_cor = as.numeric()
    )
    i <- 0
    while (nrow(df) > 0) {
        i <- i + 1
        row_with_max_cor <- which(df$"cor" == max(df$"cor"))[1]
        var_with_max_cor <- df[row_with_max_cor, "X1"]
        max_cor <- df[row_with_max_cor, "cor"]
        max_cor_df <- rbind(
            max_cor_df,
            data.frame(
                variable = var_with_max_cor,
                max_cor = max_cor
            )
        )
        df <- dplyr::filter(
            df,
            df$"X1" != var_with_max_cor & df$"X2" != var_with_max_cor
        )
    }
    return(max_cor_df)
}

# Prediction matrix construction
build_pred_mat <- function(df, n_predictors = 1) {
    pred_mat <- matrix(
        nrow = ncol(df),
        ncol = ncol(df),
        data = 1
    )
    colnames(pred_mat) <- colnames(df)
    rownames(pred_mat) <- colnames(df)
    diag(pred_mat) <- 0
    pred_mat_vars <- top_correlating_vars(df)
    vars_to_drop <- pred_mat_vars$"variable"[seq_len(n_predictors)]
    print(paste0("Dropping: ", paste(vars_to_drop, collapse = ", ")))
    pred_mat[, vars_to_drop] <- 0
    return(pred_mat)
}

###############################################################################
# Imputation - mTBI train
###############################################################################
# Doesn't run (system is computationally singular)
imputed_mtbi <- futuremice(
    mtbi_train_df_no_subs,
    m = 5,
    maxit = 10,
    parallelseed = 42
)

mtbi_train_pred_mat <- build_pred_mat(mtbi_train_df_no_subs, 1)

write.table(mtbi_train_pred_mat, proc_path("mtbi_train_pred_mat.txt", TRUE))

mtbi_train_pred_mat <- as.matrix(read.table(proc_path("2025_02_07_mtbi_train_pred_mat.txt")))
storage.mode(mtbi_train_pred_mat) <- "double"

# Runs
imputed_mtbi_train <- futuremice(
    mtbi_train_df_no_subs,
    m = 5,
    n.core = 5,
    maxit = 10,
    parallelseed = 42,
    predictorMatrix = mtbi_train_pred_mat
)

saveRDS(imputed_mtbi_train, file = proc_path("baseline_imputed_mtbi_train.rds", TRUE))
imputed_mtbi_train <- readRDS(proc_path("2025_02_07_baseline_imputed_mtbi_train.rds"))

#
# mTBI solo imputed data
five_imputed_mtbi_train <- complete(
    imputed_mtbi_train,
    action = "long",
    include = TRUE
)
#
# Write and recover
write_csv(
    five_imputed_mtbi_train,
    input_path("five_imputed_mtbi_train.csv", TRUE)
)
# CHECKPOINT
five_imputed_mtbi_train <- read_csv(
    input_path("2025_02_07_five_imputed_mtbi_train.csv")
)
```

```{r}
###############################################################################
# Imputation - mTBI test
###############################################################################
mtbi_test_pred_mat <- build_pred_mat(mtbi_test_df_no_subs, 28)
write.table(mtbi_test_pred_mat, proc_path("mtbi_test_pred_mat.txt", TRUE))
mtbi_test_pred_mat <- as.matrix(read.table(proc_path("2025_02_07_mtbi_test_pred_mat.txt")))
storage.mode(mtbi_test_pred_mat) <- "double"
imputed_mtbi_test <- futuremice(
    mtbi_test_df_no_subs,
    m = 5,
    n.core = 5,
    maxit = 10,
    parallelseed = 42,
    predictorMatrix = mtbi_test_pred_mat
)

saveRDS(imputed_mtbi_test, file = proc_path("baseline_imputed_mtbi_test.rds", TRUE))
imputed_mtbi_test <- readRDS(proc_path("2025_02_07_baseline_imputed_mtbi_test.rds"))

# mTBI solo imputed data
five_imputed_mtbi_test <- complete(
    imputed_mtbi_test,
    action = "long",
    include = TRUE
)
#
# Write and recover
write_csv(
    five_imputed_mtbi_test,
    input_path("five_imputed_mtbi_test.csv", TRUE)
)
# CHECKPOINT
five_imputed_mtbi_test <- read_csv(
    input_path("2025_02_07_five_imputed_mtbi_test.csv")
)

###############################################################################
# Imputation - only unijured
###############################################################################
unij_pred_mat <- build_pred_mat(unij_df_no_subs, 1)
# Write and recover
write.table(unij_pred_mat, proc_path("unij_pred_mat.txt", TRUE))
unij_pred_mat <- as.matrix(read.table(proc_path("2025_02_07_unij_pred_mat.txt")))
storage.mode(unij_pred_mat) <- "double"
imputed_unij <- futuremice(
    unij_df_no_subs,
    m = 5,
    n.core = 5,
    maxit = 10,
    parallelseed = 42,
    predictorMatrix = unij_pred_mat
)

saveRDS(imputed_unij, file = proc_path("baseline_imputed_unij.rds", TRUE))
imputed_unij <- readRDS(proc_path("2025_02_07_baseline_imputed_unij.rds"))
```

```{r}
# unijured solo imputed data
five_imputed_unij <- complete(
    imputed_unij,
    action = "long",
    include = TRUE
)
#
# Write and recover
write_csv(
    five_imputed_unij,
    input_path("five_imputed_unij.csv", TRUE)
)
#
five_imputed_unij <- read_csv(
    input_path("2025_02_07_five_imputed_unij.csv")
) # 68448 rows (11408 subjects * 6 imputations)

###############################################################################
# Imputation - mTBI and unijured data stacked on top of each other
# This will only look at the variables shared between the two groups
###############################################################################
mtbi_train_df_u_vars <- mtbi_train_df_no_subs[, colnames(unij_df_no_subs)]
pooled_df <- rbind(mtbi_train_df_u_vars, unij_df_no_subs)
pooled_df <- char_to_fac(pooled_df)

pooled_pred_mat <- build_pred_mat(pooled_df, 1)
# Write and recover
write.table(pooled_pred_mat, proc_path("pooled_pred_mat.txt", TRUE))
pooled_pred_mat <- as.matrix(
    read.table(proc_path("2025_02_07_pooled_pred_mat.txt"))
)
storage.mode(pooled_pred_mat) <- "double"
imputed_pooled <- futuremice(
    pooled_df,
    m = 5,
    n.core = 5,
    maxit = 10,
    parallelseed = 42,
    predictorMatrix = pooled_pred_mat
)

saveRDS(imputed_pooled, file = proc_path("baseline_imputed_pooled.rds", TRUE))
imputed_pooled <- readRDS(proc_path("2025_02_07_baseline_imputed_pooled.rds"))

# mTBI solo imputed data
five_imputed_pooled <- complete(
    imputed_pooled,
    action = "long",
    include = TRUE
)
#
# Write and recover
write_csv(five_imputed_pooled, input_path("five_imputed_pooled.csv", TRUE))
five_imputed_pooled <- read_csv(
    input_path("2025_02_07_five_imputed_pooled.csv")
)
```

Formatting the imputed data:

```{r}
five_imputed_mtbi_train$"subjectkey" <- rep(mtbi_train_subs, 6)
five_imputed_mtbi_test$"subjectkey" <- rep(mtbi_test_subs, 6)
five_imputed_unij$"subjectkey" <- rep(unij_subs, 6)

pooled_subs <- c(mtbi_train_subs, unij_subs)
five_imputed_pooled$"subjectkey" <- rep(pooled_subs, 6)

write_csv(
    five_imputed_mtbi_train,
    input_path("five_imputed_mtbi_train_named.csv", TRUE)
)
write_csv(
    five_imputed_mtbi_test,
    input_path("five_imputed_mtbi_test_named.csv", TRUE)
)
write_csv(
    five_imputed_unij,
    input_path("five_imputed_unij_named.csv", TRUE)
)
write_csv(
    five_imputed_pooled,
    input_path("five_imputed_pooled_named.csv", TRUE)
)
```

```{r}
# Write and recover
five_imputed_mtbi_train <- read_csv(
    input_path("2025_02_07_five_imputed_mtbi_train_named.csv")
)

five_imputed_mtbi_test <- read_csv(
    input_path("2025_02_07_five_imputed_mtbi_test_named.csv")
)

five_imputed_unij <- read_csv(
    input_path("2025_02_07_five_imputed_unij_named.csv")
)

five_imputed_pooled <- read_csv(
    input_path("2025_02_07_five_imputed_pooled_named.csv")
)
```

# mTBI subsetting

```{r}
extract_imputed <- function(original_df, imputed_df, partition) {
    return(imputed_df[imputed_df$".imp" == partition, colnames(original_df)])
}

parse_imputations <- function(original_df_list, complete_imputed_df, imps) {
    parsed_imputations <- original_df_list |>
        lapply(
            function(x) {
                imputations <- list()
                for (i in seq_len(imps)) {
                    imputations[[i]] <- extract_imputed(
                        x,
                        complete_imputed_df,
                        i - 1
                    )
                }
                names(imputations) <- paste0("imp_", seq_len(imps) - 1)
                return(imputations)
            }
        )
    names(parsed_imputations) <- gsub("_mtbi$", "", names(parsed_imputations))
    names(parsed_imputations) <- gsub("_unij$", "", names(parsed_imputations))
    return(parsed_imputations)
}

mtbi_train_parsed_imputations <- parse_imputations(
    mtbi_train_df_list,
    five_imputed_mtbi_train,
    6
)

mtbi_test_parsed_imputations <- parse_imputations(
    mtbi_test_df_list,
    five_imputed_mtbi_test,
    6
)

unij_parsed_imputations <- parse_imputations(
    unij_df_list,
    five_imputed_unij,
    6
)

pooled_parsed_imputations <- parse_imputations(
    unij_df_list,
    five_imputed_pooled,
    6
)

mtbi_pooled_parsed_imputations <- pooled_parsed_imputations |>
    lapply(
        function(variable) {
            lapply(
                variable,
                function(imputed_df) {
                    keep_rows <- imputed_df$"subjectkey" %in% mtbi_train_subs
                    filtered_df <- imputed_df[keep_rows, ]
                    return(filtered_df)
                }
            )
        }
    )

unij_pooled_parsed_imps <- pooled_parsed_imputations |>
    lapply(
        function(variable) {
            lapply(
                variable,
                function(imputed_df) {
                    keep_rows <- imputed_df$"subjectkey" %in% unij_subs
                    filtered_df <- imputed_df[keep_rows, ]
                    return(filtered_df)
                }
            )
        }
    )

list.save(
    mtbi_train_parsed_imputations,
    input_path("mtbi_train_parsed_imputations.rds", TRUE)
)
list.save(
    mtbi_test_parsed_imputations,
    input_path("mtbi_test_parsed_imputations.rds", TRUE)
)
list.save(
    mtbi_pooled_parsed_imputations,
    input_path("mtbi_pooled_parsed_imputations.rds", TRUE)
)
list.save(
    unij_parsed_imputations,
    input_path("unij_parsed_imputations.rds", TRUE)
)
list.save(
    unij_pooled_parsed_imps,
    input_path("unij_pooled_parsed_imputations.rds", TRUE)
)
```

Re-reading:

```{r}
mtbi_train_parsed_imputations <- list.load(
    input_path("2025_02_07_mtbi_train_parsed_imputations.rds")
)
mtbi_test_parsed_imputations <- list.load(
    input_path("2025_02_07_mtbi_test_parsed_imputations.rds")
)
mtbi_pooled_parsed_imputations <- list.load(
    input_path("2025_02_07_mtbi_pooled_parsed_imputations.rds")
)
unij_parsed_imputations <- list.load(
    input_path("2025_02_07_unij_parsed_imputations.rds")
)
unij_pooled_parsed_imps <- list.load(
    input_path("2025_02_07_unij_pooled_parsed_imputations.rds")
)

names(mtbi_train_parsed_imputations)
```


## Constructing data_lists

We have:

* 1 original unimputed mTBI dataset
* 1 original unimputed unijured dataset
* 5 imputed mTBI datasets
* 5 imputed unijured datasets
* 5 imputed mTBI + unijured datasets

For the sake of brevity, these will be referred to with the following notation:

* m = mTBI
* u = unijured
* p = pooled
* 0 = original (unimputed)
* 1-5 = imputed dataset number

```{r}
mtbi_train_data_lists <- build_dls(mtbi_train_parsed_imputations)
mtbi_train_oom_lists <- build_ols(mtbi_train_parsed_imputations)
mtbi_test_data_lists <- build_dls(mtbi_test_parsed_imputations)
mtbi_test_oom_lists <- build_ols(mtbi_test_parsed_imputations)
mtbi_pooled_data_lists <- build_unij_dls(mtbi_pooled_parsed_imputations)
mtbi_pooled_oom_lists <- build_ols(mtbi_pooled_parsed_imputations)
unij_data_lists <- build_unij_dls(unij_parsed_imputations)
unij_oom_lists <- build_ols(unij_parsed_imputations)
unij_pooled_data_lists <- build_unij_dls(unij_pooled_parsed_imps)
unij_pooled_oom_lists <- build_ols(unij_pooled_parsed_imps)

all_dls <- list(
    "mtbi_train_data_lists" = mtbi_train_data_lists,
    "mtbi_train_oom_lists" = mtbi_train_oom_lists,
    "mtbi_test_data_lists" = mtbi_test_data_lists,
    "mtbi_test_oom_lists" = mtbi_test_oom_lists,
    "mtbi_pooled_data_lists" = mtbi_pooled_data_lists,
    "mtbi_pooled_oom_lists" = mtbi_pooled_oom_lists,
    "unij_data_lists" = unij_data_lists,
    "unij_oom_lists" = unij_oom_lists,
    "unij_pooled_data_lists" = unij_pooled_data_lists,
    "unij_pooled_oom_lists" = unij_pooled_oom_lists
)

```

## Renaming the initial data

```{r}
name_changes <- c(
    "mtbi_mechanism" = "latest_mtbi_mechanism",
    "mtbi_mem_daze" = "latest_mtbi_mem_daze",
    "mtbi_loc" = "latest_mtbi_loc",
    "mtbi_age" = "latest_mtbi_age",
    "age" = "interview_age",
    "parent_thought" = "asr_scr_thought_r",
    "parent_aggressive" = "asr_scr_aggressive_r",
    "parent_antisocial" = "asr_scr_antisocial_r",
    "parent_hyperactive" = "asr_scr_hyperactive_r",
    "parent_attention" = "asr_scr_attention_r",
    "parent_anxdep" = "asr_scr_anxdep_r",
    "parent_depress" = "asr_scr_depress_r",
    "parent_withdrawn" = "asr_scr_withdrawn_r",
    "parent_avoidant" = "asr_scr_avoidant_r",
    "parent_anxdisord" = "asr_scr_anxdisord_r",
    "parent_somatic" = "asr_scr_somatic_r",
    "parent_intrusive" = "asr_scr_intrusive_r",
    "parent_perstr" = "asr_scr_perstr_r",
    "sds_sleep" = "sds_p_ss_total",
    "cbcl_somatic" = "cbcl_scr_syn_somatic_r",
    "cbcl_social" = "cbcl_scr_syn_social_r",
    "cbcl_anxdep" = "cbcl_scr_syn_anxdep_r",
    "cbcl_thought" = "cbcl_scr_syn_thought_r",
    "cbcl_attention" = "cbcl_scr_syn_attention_r",
    "cbcl_withdep" = "cbcl_scr_syn_withdep_r",
    "cbcl_aggressive" = "cbcl_scr_syn_aggressive_r",
    "cbcl_rulebreak" = "cbcl_scr_syn_rulebreak_r",
    "family_fight_y" = "q1_fight_y",
    "family_angry_y" = "q2_angry_y",
    "family_throw_y" = "q3_throw_y",
    "family_temper_y" = "q4_temper_y",
    "family_criticize_y" = "q5_criticize_y",
    "family_hit_y" = "q6_hit_y",
    "family_peaceful_y" = "q7_peaceful_y",
    "family_outdo_y" = "q8_outdo_y",
    "family_yell_y" = "q9_yell_y",
    "family_fight_p" = "q1_fight_p",
    "family_angry_p" = "q2_angry_p",
    "family_throw_p" = "q3_throw_p",
    "family_temper_p" = "q4_temper_p",
    "family_criticize_p" = "q5_criticize_p",
    "family_hit_p" = "q6_hit_p",
    "family_peaceful_p" = "q7_peaceful_p",
    "family_outdo_p" = "q8_outdo_p",
    "family_yell_p" = "q9_yell_p",
    "headache_history" = "headache",
    "previous_mtbis" = "mtbi_count",
    "brain_volume" = "smri_vol_scs_wholeb",
    "cortical_thickness" = "smri_thick_cdk_mean",
    "cortical_sa" = "smri_area_cdk_total",
    "major_wm_ndi" = "dmri_rsirnd_fib_allfib",
    "pericortical_wm_ndi" = "dmri_rsirndwm_cdk_mean",
    "fmri_cort_cors" = "avg_gord_cor",
    "fmri_cort_subcort_cors" = "avg_subc_cor",
    "same_sex_friend" = "ss_friend",
    "opp_sex_friend" = "os_friend",
    "same_sex_close_friend" = "ss_close_friend",
    "opp_sex_close_friend" = "os_close_friend",
    "weekend_screentime" = "screentime_wknd_hrs",
    "weekday_screentime" = "screentime_wkday_hrs"
)

all_dls[[1]][[1]] |> features()

all_dls <- all_dls |>
    lapply(
        function(data_lists_of_group) {
            lapply(
                data_lists_of_group,
                function(data_list) {
                    data_list <- rename_dl(data_list, name_changes)
                }
            )
        }
    )

list.save(all_dls, input_path("all_dls.rds", TRUE))
```
