# Data Preprocessing

This chapter contains:
1. Removal of neuroimaging data failing QC
2. Random removal of siblings
3. Train/test split
4. Mice imputation of missing data
5. Organization of imputed data into `data_list` class objects (from the `metasnf` package)

## Importing Extracted Data

```{r}
library(abcdutils)
library(here)
library(dplyr)
library(readr)
library(metasnf)
library(mice)
library(rlist)
library(ggplot2)

input_path <- path_maker(here("data/abcd/inputs"))
core_path <- path_maker(here("data/abcd/core"))
sub_path <- path_maker(here("data/abcd/subjects"))
fig_path <- path_maker(here("data/abcd/results/figures"))
proc_path <- path_maker(here("data/abcd/results/processed"))

# Subjects
mtbi_subs <- read_subjects(sub_path("2025_09_11_mtbi_subs.csv"))
unij_subs <- read_subjects(sub_path("2025_09_11_unij_subs.csv"))

import <- function(path) {
    return(abcdutils::abcd_load(core_path(path)))
}

iread <- function(path) {
    read_csv(input_path(path))
}

iwrite <- function(data, path) {
    write_csv(data, input_path(path, date = TRUE))
}
```

```{r}
# CHECKPOINT
# mTBI subjects
mtbi_as_loc            <- iread("2025_09_11_mtbi_as_loc.csv")
mtbi_as_mechanism      <- iread("2025_09_11_mtbi_as_mechanism.csv")
mtbi_as_mem_daze       <- iread("2025_09_11_mtbi_as_mem_daze.csv")
mtbi_cbcl              <- iread("2025_09_11_mtbi_cbcl.csv")
mtbi_d_income          <- iread("2025_09_11_mtbi_d_income.csv")
mtbi_d_interview_age   <- iread("2025_09_11_mtbi_d_interview_age.csv")
mtbi_d_mtbi_age        <- iread("2025_09_11_mtbi_d_mtbi_age.csv")
mtbi_d_pubertal_status <- iread("2025_09_11_mtbi_d_pubertal_status.csv")
mtbi_d_race            <- iread("2025_09_11_mtbi_d_race.csv")
mtbi_d_sex             <- iread("2025_09_11_mtbi_d_sex.csv")
mtbi_dm_wmnd           <- iread("2025_09_11_mtbi_dm_wmnd.csv")
mtbi_mh_headaches      <- iread("2025_09_11_mtbi_mh_headaches.csv")
mtbi_mh_mtbi_count     <- iread("2025_09_11_mtbi_mh_mtbi_count.csv")
mtbi_p_exercise        <- iread("2025_09_11_mtbi_p_exercise.csv")
mtbi_p_fam_fn          <- iread("2025_09_11_mtbi_p_fam_fn.csv")
mtbi_p_friends         <- iread("2025_09_11_mtbi_p_friends.csv")
mtbi_p_parent_psych    <- iread("2025_09_11_mtbi_p_parent_psych.csv")
mtbi_p_prosocial       <- iread("2025_09_11_mtbi_p_prosocial.csv")
mtbi_p_screen_time     <- iread("2025_09_11_mtbi_p_screen_time.csv")
mtbi_p_sports          <- iread("2025_09_11_mtbi_p_sports.csv")
mtbi_rm_gord_cor       <- iread("2025_09_11_mtbi_rm_gord_cor.csv")
mtbi_rm_subc_cor       <- iread("2025_09_11_mtbi_rm_subc_cor.csv")
mtbi_sds               <- iread("2025_09_11_mtbi_sds.csv")
mtbi_sm_cort_sa        <- iread("2025_09_11_mtbi_sm_cort_sa.csv")
mtbi_sm_cort_t         <- iread("2025_09_11_mtbi_sm_cort_t.csv")
mtbi_sm_subc_v         <- iread("2025_09_11_mtbi_sm_subc_v.csv")
mtbi_family            <- iread("2025_09_11_mtbi_family.csv")
mtbi_scanner           <- iread("2025_09_11_mtbi_scanner.csv")
mtbi_site              <- iread("2025_09_11_mtbi_site.csv")

# Uninjured subjects
unij_cbcl              <- iread("2025_09_11_unij_cbcl.csv")
unij_d_income          <- iread("2025_09_11_unij_d_income.csv")
unij_d_interview_age   <- iread("2025_09_11_unij_d_interview_age.csv")
unij_d_pubertal_status <- iread("2025_09_11_unij_d_pubertal_status.csv")
unij_d_race            <- iread("2025_09_11_unij_d_race.csv")
unij_d_sex             <- iread("2025_09_11_unij_d_sex.csv")
unij_dm_wmnd           <- iread("2025_09_11_unij_dm_wmnd.csv")
unij_mh_headaches      <- iread("2025_09_11_unij_mh_headaches.csv")
unij_p_exercise        <- iread("2025_09_11_unij_p_exercise.csv")
unij_p_fam_fn          <- iread("2025_09_11_unij_p_fam_fn.csv")
unij_p_friends         <- iread("2025_09_11_unij_p_friends.csv")
unij_p_parent_psych    <- iread("2025_09_11_unij_p_parent_psych.csv")
unij_p_prosocial       <- iread("2025_09_11_unij_p_prosocial.csv")
unij_p_screen_time     <- iread("2025_09_11_unij_p_screen_time.csv")
unij_p_sports          <- iread("2025_09_11_unij_p_sports.csv")
unij_rm_gord_cor       <- iread("2025_09_11_unij_rm_gord_cor.csv")
unij_rm_subc_cor       <- iread("2025_09_11_unij_rm_subc_cor.csv")
unij_sds               <- iread("2025_09_11_unij_sds.csv")
unij_sm_cort_sa        <- iread("2025_09_11_unij_sm_cort_sa.csv")
unij_sm_cort_t         <- iread("2025_09_11_unij_sm_cort_t.csv")
unij_sm_subc_v         <- iread("2025_09_11_unij_sm_subc_v.csv")
unij_family            <- iread("2025_09_11_unij_family.csv")
unij_scanner           <- iread("2025_09_11_unij_scanner.csv")
unij_site              <- iread("2025_09_11_unij_site.csv")
```

## Neuroimaging quality control

Subset neuroimaging data to those subjects who pass neuroimaging QC and PC.
The QC and PC functions used below, such as `qc_smri()`, return a named list containing vectors of subjects who passed, explicitly failed, or failed by having missing values.

```{r}
# QC data
mri_y_qc_incl <- abcd_load(core_path("imaging/mri_y_qc_incl.csv"))

# Vectors of those who passed QC
smri_pass <- get_qc_data(
    mri_y_qc_incl,
    t = 0,
    subjects = c(mtbi_subs, unij_subs),
    type = "t1w"
)$"pass"

dmri_pass <- get_qc_data(
    mri_y_qc_incl,
    t = 0,
    subjects = c(mtbi_subs, unij_subs),
    type = "dmri"
)$"pass"

rsfmri_pass <- get_qc_data(
    mri_y_qc_incl,
    t = 0,
    subjects = c(mtbi_subs, unij_subs),
    type = "rsfmri"
)$"pass"

# Reducing extracted data to just those who passed QC and PC
mtbi_dm_wmnd_qc     <- filter(mtbi_dm_wmnd,     subjectkey %in% dmri_pass)
unij_dm_wmnd_qc     <- filter(unij_dm_wmnd,     subjectkey %in% dmri_pass)
mtbi_rm_gord_cor_qc <- filter(mtbi_rm_gord_cor, subjectkey %in% rsfmri_pass)
unij_rm_gord_cor_qc <- filter(unij_rm_gord_cor, subjectkey %in% rsfmri_pass)
mtbi_rm_subc_cor_qc <- filter(mtbi_rm_subc_cor, subjectkey %in% rsfmri_pass)
unij_rm_subc_cor_qc <- filter(unij_rm_subc_cor, subjectkey %in% rsfmri_pass)
mtbi_sm_cort_sa_qc  <- filter(mtbi_sm_cort_sa,  subjectkey %in% smri_pass)
unij_sm_cort_sa_qc  <- filter(unij_sm_cort_sa,  subjectkey %in% smri_pass)
mtbi_sm_cort_t_qc   <- filter(mtbi_sm_cort_t,   subjectkey %in% smri_pass)
unij_sm_cort_t_qc   <- filter(unij_sm_cort_t,   subjectkey %in% smri_pass)
mtbi_sm_subc_v_qc   <- filter(mtbi_sm_subc_v,   subjectkey %in% smri_pass)
unij_sm_subc_v_qc   <- filter(unij_sm_subc_v,   subjectkey %in% smri_pass)

iwrite(mtbi_dm_wmnd_qc, "mtbi_dm_wmnd_qc.csv")
iwrite(mtbi_rm_gord_cor_qc, "mtbi_rm_gord_cor_qc.csv")
iwrite(mtbi_rm_subc_cor_qc, "mtbi_rm_subc_cor_qc.csv")
iwrite(mtbi_sm_cort_sa_qc, "mtbi_sm_cort_sa_qc.csv")
iwrite(mtbi_sm_cort_t_qc, "mtbi_sm_cort_t_qc.csv")
iwrite(mtbi_sm_subc_v_qc, "mtbi_sm_subc_v_qc.csv")
iwrite(unij_dm_wmnd_qc, "unij_dm_wmnd_qc.csv")
iwrite(unij_rm_gord_cor_qc, "unij_rm_gord_cor_qc.csv")
iwrite(unij_rm_subc_cor_qc, "unij_rm_subc_cor_qc.csv")
iwrite(unij_sm_cort_sa_qc, "unij_sm_cort_sa_qc.csv")
iwrite(unij_sm_cort_t_qc, "unij_sm_cort_t_qc.csv")
iwrite(unij_sm_subc_v_qc, "unij_sm_subc_v_qc.csv")
```

```{r}
# CHECKPOINT
mtbi_dm_wmnd_qc     <- iread("2025_09_11_mtbi_dm_wmnd_qc.csv")
mtbi_rm_gord_cor_qc <- iread("2025_09_11_mtbi_rm_gord_cor_qc.csv")
mtbi_rm_subc_cor_qc <- iread("2025_09_11_mtbi_rm_subc_cor_qc.csv")
mtbi_sm_cort_sa_qc  <- iread("2025_09_11_mtbi_sm_cort_sa_qc.csv")
mtbi_sm_cort_t_qc   <- iread("2025_09_11_mtbi_sm_cort_t_qc.csv")
mtbi_sm_subc_v_qc   <- iread("2025_09_11_mtbi_sm_subc_v_qc.csv")
unij_dm_wmnd_qc     <- iread("2025_09_11_unij_dm_wmnd_qc.csv")
unij_rm_gord_cor_qc <- iread("2025_09_11_unij_rm_gord_cor_qc.csv")
unij_rm_subc_cor_qc <- iread("2025_09_11_unij_rm_subc_cor_qc.csv")
unij_sm_cort_sa_qc  <- iread("2025_09_11_unij_sm_cort_sa_qc.csv")
unij_sm_cort_t_qc   <- iread("2025_09_11_unij_sm_cort_t_qc.csv")
unij_sm_subc_v_qc   <- iread("2025_09_11_unij_sm_subc_v_qc.csv")
```

```{r}
library(mice)
# 1. Create a simple toy dataset
set.seed(123)
data <- data.frame(
  age = c(10, 11, 12, NA, 10, 11, 12, NA, 11, 10),
  iq  = c(100, 105, 110, 115, NA, 102, NA, 108, 111, 100),
  scanner_id = c("S1", "S1", "S2", NA, "S2", "S1", NA, "S2", "S1", NA)
)
# Turn scanner_id into a factor (common in MICE usage)
data$scanner_id <- as.factor(data$scanner_id)
# View missing data summary
ini <- mice(data, maxit = 0)
meth <- ini$method
pred <- ini$predictorMatrix
# Don't impute scanner_id
meth["scanner_id"] <- ""
# Predict age and iq using each other (you could add scanner_id if desired)
pred["age", ] <- c(0, 1, 0)  # Predict age using iq only
pred["iq", ]  <- c(1, 0, 0)  # Predict iq using age only
imp <- mice(data, method = meth, predictorMatrix = pred, m = 5, seed = 42)
completed_data <- complete(imp, action = "long", include = TRUE)
# View completed data
print(completed_data)
# Compare original and completed data side-by-side
cbind(original = data$scanner_id, imputed = completed_data$scanner_id)
```

## Train/Test Split

To avoid having training and testing data inform each other during imputation, we assign the splits prior to the imputation.
This is only done in our primary analysis group (baseline mTBI).

```{r}
mtbi_split <- train_test_assign(
    train_frac = 0.8,
    uids = mtbi_subs
)

mtbi_train_subs <- mtbi_split$"train"
mtbi_test_subs <- mtbi_split$"test"

write_subjects(mtbi_train_subs, sub_path("mtbi_train_subs.csv", TRUE))
write_subjects(mtbi_test_subs, sub_path("mtbi_test_subs.csv", TRUE))
```

```{r}
mtbi_train_subs <- read_subjects(sub_path("2025_09_11_mtbi_train_subs.csv"))
mtbi_test_subs  <- read_subjects(sub_path("2025_09_11_mtbi_test_subs.csv"))

# Storing all mTBI data frames in a list
mtbi_df_list <- list(
    "mtbi_as_loc"            = mtbi_as_loc,
    "mtbi_as_mechanism"      = mtbi_as_mechanism,
    "mtbi_as_mem_daze"       = mtbi_as_mem_daze,
    "mtbi_cbcl"              = mtbi_cbcl,
    "mtbi_d_income"          = mtbi_d_income,
    "mtbi_d_interview_age"   = mtbi_d_interview_age,
    "mtbi_d_mtbi_age"        = mtbi_d_mtbi_age,
    "mtbi_d_pubertal_status" = mtbi_d_pubertal_status,
    "mtbi_d_race"            = mtbi_d_race,
    "mtbi_d_sex"             = mtbi_d_sex,
    "mtbi_dm_wmnd_qc"        = mtbi_dm_wmnd_qc,
    "mtbi_mh_headaches"      = mtbi_mh_headaches,
    "mtbi_mh_mtbi_count"     = mtbi_mh_mtbi_count,
    "mtbi_p_exercise"        = mtbi_p_exercise,
    "mtbi_p_fam_fn"          = mtbi_p_fam_fn,
    "mtbi_p_friends"         = mtbi_p_friends,
    "mtbi_p_parent_psych"    = mtbi_p_parent_psych,
    "mtbi_p_prosocial"       = mtbi_p_prosocial,
    "mtbi_p_screen_time"     = mtbi_p_screen_time,
    "mtbi_p_sports"          = mtbi_p_sports,
    "mtbi_rm_gord_cor_qc"    = mtbi_rm_gord_cor_qc,
    "mtbi_rm_subc_cor_qc"    = mtbi_rm_subc_cor_qc,
    "mtbi_scanner"           = mtbi_scanner,
    "mtbi_sds"               = mtbi_sds,
    "mtbi_sm_cort_sa_qc"     = mtbi_sm_cort_sa_qc,
    "mtbi_sm_cort_t_qc"      = mtbi_sm_cort_t_qc,
    "mtbi_sm_subc_v_qc"      = mtbi_sm_subc_v_qc
)

# Storing all uninjured data frames in a list
unij_df_list <- list(
    "unij_cbcl"              = unij_cbcl,
    "unij_d_income"          = unij_d_income,
    "unij_d_interview_age"   = unij_d_interview_age,
    "unij_d_pubertal_status" = unij_d_pubertal_status,
    "unij_d_race"            = unij_d_race,
    "unij_d_sex"             = unij_d_sex,
    "unij_dm_wmnd_qc"        = unij_dm_wmnd_qc,
    "unij_mh_headaches"      = unij_mh_headaches,
    "unij_p_exercise"        = unij_p_exercise,
    "unij_p_fam_fn"          = unij_p_fam_fn,
    "unij_p_friends"         = unij_p_friends,
    "unij_p_parent_psych"    = unij_p_parent_psych,
    "unij_p_prosocial"       = unij_p_prosocial,
    "unij_p_screen_time"     = unij_p_screen_time,
    "unij_p_sports"          = unij_p_sports,
    "unij_rm_gord_cor_qc"    = unij_rm_gord_cor_qc,
    "unij_rm_subc_cor_qc"    = unij_rm_subc_cor_qc,
    "unij_scanner"           = unij_scanner,
    "unij_sds"               = unij_sds,
    "unij_sm_cort_sa_qc"     = unij_sm_cort_sa_qc,
    "unij_sm_cort_t_qc"      = unij_sm_cort_t_qc,
    "unij_sm_subc_v_qc"      = unij_sm_subc_v_qc
)

# Splitting the mTBI list of data frames into training and test set versions
train_filter <- function(df) {
    filtered_df <- dplyr::filter(df, df$"subjectkey" %in% mtbi_train_subs)
    return(filtered_df)
}

test_filter <- function(df) {
    filtered_df <- dplyr::filter(df, df$"subjectkey" %in% mtbi_test_subs)
    return(filtered_df)
}

mtbi_train_df_list <- lapply(mtbi_df_list, train_filter)
mtbi_test_df_list <- lapply(mtbi_df_list, test_filter)
```

## Imputation

SNF requires complete data as input for integration.

Data will be imputed under the following schemes:

- 5 imputations of mTBI data alone
- 5 imputations of unijured data alone
- 5 imputations of mTBI + unijured data together

Resulting in 10 versions of the mTBI data and 10 versions of the unijured data.

First, each group has their extracted dataframes merged into a single one for imputation.

```{r}
# `merge_df_list()` converts lists of data frames into a single data frame
mtbi_train_df <- metasnf::merge_df_list(
    mtbi_train_df_list,
    uid = "subjectkey",
    join = "full"
)

mtbi_test_df <- metasnf::merge_df_list(
    mtbi_test_df_list,
    uid = "subjectkey",
    join = "full"
)

unij_df <- metasnf::merge_df_list(
    unij_df_list,
    uid = "subjectkey",
    join = "full"
)

write_csv(mtbi_test_df, proc_path("mtbi_test_df.csv", TRUE))
write_csv(mtbi_train_df, proc_path("mtbi_train_df.csv", TRUE))
write_csv(unij_df, proc_path("unij_df.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_train_df <- data.frame(read_csv(proc_path("2025_09_11_mtbi_train_df.csv")))
mtbi_test_df <- data.frame(read_csv(proc_path("2025_09_11_mtbi_test_df.csv")))
unij_df <- data.frame(read_csv(proc_path("2025_09_11_unij_df.csv")))
```

A preliminary check of which columns have missing data:

```{r}
missing_columns(mtbi_train_df)
missing_columns(unij_df)
```

```{r}

# Function that checks which variables have the biggest correlations# {{{
pairwise_correlations <- function(df, threshold = 0) {
    # Remove missing data to help calculate correlations
    df <- na.omit(df)
    # Remove non-numeric columns
    non_numeric_cols <- sapply(df, function(x) !is.numeric(x))
    df <- df[, !non_numeric_cols]
    # Calculate correlations
    correlations <- cor(df)
    # Ignore self-correlations
    diag(correlations) <- 0
    # Take absolute value of the correlations, as strong anti-correlations also
    # lead to strong linear dependence
    abs_cor <- abs(correlations)
    # Create dataframe of all pairs of correlations
    pairs <- t(combn(colnames(abs_cor), 2))
    paired_cors <- data.frame(pairs, cor = abs_cor[pairs])
    # Filter to only correlations bigger than a specified threshold
    paired_cors <- paired_cors[paired_cors$"cor" > threshold, ]
    return(paired_cors)
}

# Function to help sort variables by pairwise correlations
top_correlating_vars <- function(df, threshold = 0) {
    # Dataframe highlighting strongest correlations
    df <- pairwise_correlations(df, threshold)
    # Iteratively build up an ordered correlations matrix by:
    #   - Record one of the two variables contributing to the largest
    #     pairwise correlation
    #   - Remove that variables from the list of all pairs of correlations
    #   - Repeat until all variables have been removed
    max_cor_df <- data.frame(
        variable = as.character(),
        max_cor = as.numeric()
    )
    i <- 0
    while (nrow(df) > 0) {
        i <- i + 1
        row_with_max_cor <- which(df$"cor" == max(df$"cor"))[1]
        var_with_max_cor <- df[row_with_max_cor, "X1"]
        max_cor <- df[row_with_max_cor, "cor"]
        max_cor_df <- rbind(
            max_cor_df,
            data.frame(
                variable = var_with_max_cor,
                max_cor = max_cor
            )
        )
        df <- dplyr::filter(
            df,
            df$"X1" != var_with_max_cor & df$"X2" != var_with_max_cor
        )
    }
    return(max_cor_df)
}

# Prediction matrix construction
build_pred_mat <- function(df, n_predictors = 1) {
    pred_mat <- matrix(
        nrow = ncol(df),
        ncol = ncol(df),
        data = 1
    )
    colnames(pred_mat) <- colnames(df)
    rownames(pred_mat) <- colnames(df)
    diag(pred_mat) <- 0
    pred_mat_vars <- top_correlating_vars(df)
    vars_to_drop <- pred_mat_vars$"variable"[seq_len(n_predictors)]
    print(paste0("Dropping: ", paste(vars_to_drop, collapse = ", ")))
    pred_mat[, vars_to_drop] <- 0
    return(pred_mat)
}# }}}
# pred_mat_exclusions controls how many of the top most correlated variables
# are excluded as predictors from the predictor matrix.
run_imputation <- function(df,
                           pred_mat_exclusions = 0,
                           visit_sequence = NULL,
                           parallel = FALSE,
                           ...) {
    df <- dplyr::select(df, -"subjectkey")
    df <- char_to_fac(df)
    if (!is.null(visit_sequence)) {
        df <- df[, visit_sequence[visit_sequence %in% colnames(df)]]
    } else {
        df <- df[, sample(colnames(df))]
    }
    # Construct predictor matrix
    pred_mat <- build_pred_mat(df, pred_mat_exclusions)
    # Construct methods vector and set scanner_id to ""
    if (!parallel) {
        imputed <- mice(
            df,
            m = 5,
            maxit = 10,
            predictorMatrix = pred_mat,
            ...
        )
    } else {
        imputed <- futuremice(
            df,
            m = 5,
            maxit = 10,
            parallelseed = 42,
            n.core = 5,
            predictorMatrix = pred_mat,
            ...
        )
    }
    return(
        list(
            visit_sequence = colnames(df),
            pred_mat = pred_mat,
            imputed = imputed
        )
    )
}

# mTBI train
set.seed(42)
mtbi_train_imputed <- run_imputation(mtbi_train_df, 1)
saveRDS(mtbi_train_imputed, proc_path("mtbi_train_imputed.rds", TRUE))
complete(mtbi_train_imputed$"imputed", action = "long", include = FALSE) |>
    missing_columns()

# Copy visit sequence
mtbi_train_imputed <- readRDS(proc_path("2025_09_11_mtbi_train_imputed.rds"))
vs <- mtbi_train_imputed$"visit_sequence"

#mTBI test
set.seed(42)
mtbi_test_imputed <- run_imputation(mtbi_test_df, 48, vs)
saveRDS(mtbi_test_imputed, proc_path("mtbi_test_imputed.rds", TRUE))
complete(mtbi_test_imputed$"imputed", action = "long", include = FALSE) |>
    missing_columns()

# HERE 2025-09-11

#Uninjured
set.seed(42)
start <- Sys.time()
unij_imputed <- run_imputation(unij_df, 1, vs, FALSE)
print(Sys.time() - start)
saveRDS(unij_imputed, proc_path("unij_imputed.rds", TRUE))
complete(unij_imputed$"imputed", action = "long", include = FALSE) |>
    missing_columns()

# mTBI/uninjured pooled
mtbi_unij_vars_df <- mtbi_train_df[, colnames(unij_df)]
pool_df <- rbind(mtbi_unij_vars_df, unij_df)
pool_imputed <- run_imputation(pool_df, 1, vs)
saveRDS(pool_imputed, file = proc_path("pool_imputed.rds", TRUE))
```

```{r}
mtbi_train_imputed <- readRDS(proc_path("2025_09_11_mtbi_train_imputed.rds"))
mtbi_test_imputed <- readRDS(proc_path("2025_09_11_mtbi_test_imputed.rds"))
unij_imputed <- readRDS(proc_path("2025_09_11_unij_imputed.rds"))
pool_imputed <- readRDS(proc_path("2025_09_11_pool_imputed.rds"))
```

```{r}
save_density_plots(
    missing_columns(mtbi_train_df),
    mtbi_train_imputed$"imputed",
    "mtbi_train_"
)

save_density_plots(
    missing_columns(mtbi_test_df),
    mtbi_test_imputed$"imputed",
    "mtbi_test_"
)

save_density_plots(
    missing_columns(unij_df),
    unij_imputed$"imputed",
    "unij_"
)

save_density_plots(
    missing_columns(pool_df),
    pool_imputed$"imputed",
    "pool_"
)
```

```{r}
mtbi_train_complete <- complete(
    mtbi_train_imputed$"imputed",
    action = "long",
    include = TRUE
)
mtbi_test_complete <- complete(
    mtbi_test_imputed$"imputed",
    action = "long",
    include = TRUE
)
unij_complete <- complete(
    unij_imputed$"imputed",
    action = "long",
    include = TRUE
)
pool_complete <- complete(
    pool_imputed$"imputed",
    action = "long",
    include = TRUE
)
```

```{r}
mtbi_train_complete$"subjectkey" <- rep(mtbi_train_subs, 6)
mtbi_test_complete$"subjectkey" <- rep(mtbi_test_subs, 6)
unij_complete$"subjectkey" <- rep(unij_subs, 6)
pool_subs <- c(mtbi_train_subs, unij_subs)
pool_complete$"subjectkey" <- rep(pool_subs, 6)

write_csv(
    mtbi_train_complete,
    input_path("mtbi_train_complete.csv", TRUE)
)
write_csv(
    mtbi_test_complete,
    input_path("mtbi_test_complete.csv", TRUE)
)
write_csv(
    unij_complete,
    input_path("unij_complete.csv", TRUE)
)
write_csv(
    pool_complete,
    input_path("pool_complete.csv", TRUE)
)
```

```{r}
# CHECKPOINT
mtbi_train_complete <- read_csv(
    input_path("2025_09_11_mtbi_train_complete.csv")
)
mtbi_test_complete <- read_csv(
    input_path("2025_09_11_mtbi_test_complete.csv")
)
unij_complete <- read_csv(
    input_path("2025_09_11_unij_complete.csv")
)
pool_complete <- read_csv(
    input_path("2025_09_11_pool_complete.csv")
)
```

# mTBI subsetting

```{r}
extract_imputed <- function(original_df, imputed_df, partition) {
    return(imputed_df[imputed_df$".imp" == partition, colnames(original_df)])
}

parse_imputations <- function(original_df_list, complete_imputed_df, imps) {
    parsed_imputations <- original_df_list |>
        lapply(
            function(x) {
                imputations <- list()
                for (i in seq_len(imps)) {
                    imputations[[i]] <- extract_imputed(
                        x,
                        complete_imputed_df,
                        i - 1
                    )
                }
                names(imputations) <- paste0("imp_", seq_len(imps) - 1)
                return(imputations)
            }
        )
    names(parsed_imputations) <- gsub("_mtbi$", "", names(parsed_imputations))
    names(parsed_imputations) <- gsub("_unij$", "", names(parsed_imputations))
    return(parsed_imputations)
}

mtbi_train_parsed_imputations <- parse_imputations(
    mtbi_train_df_list,
    mtbi_train_complete,
    6
)

mtbi_test_parsed_imputations <- parse_imputations(
    mtbi_test_df_list,
    mtbi_test_complete,
    6
)

unij_parsed_imputations <- parse_imputations(
    unij_df_list,
    unij_complete,
    6
)

pool_parsed_imputations <- parse_imputations(
    unij_df_list,
    pool_complete,
    6
)

mtbi_pool_parsed_imputations <- pool_parsed_imputations |>
    lapply(
        function(variable) {
            lapply(
                variable,
                function(imputed_df) {
                    keep_rows <- imputed_df$"subjectkey" %in% mtbi_train_subs
                    filtered_df <- imputed_df[keep_rows, ]
                    return(filtered_df)
                }
            )
        }
    )

unij_pool_parsed_imps <- pool_parsed_imputations |>
    lapply(
        function(variable) {
            lapply(
                variable,
                function(imputed_df) {
                    keep_rows <- imputed_df$"subjectkey" %in% unij_subs
                    filtered_df <- imputed_df[keep_rows, ]
                    return(filtered_df)
                }
            )
        }
    )

list.save(
    mtbi_train_parsed_imputations,
    input_path("mtbi_train_parsed_imputations.rds", TRUE)
)
list.save(
    mtbi_test_parsed_imputations,
    input_path("mtbi_test_parsed_imputations.rds", TRUE)
)
list.save(
    mtbi_pool_parsed_imputations,
    input_path("mtbi_pool_parsed_imputations.rds", TRUE)
)
list.save(
    unij_parsed_imputations,
    input_path("unij_parsed_imputations.rds", TRUE)
)
list.save(
    unij_pool_parsed_imps,
    input_path("unij_pool_parsed_imputations.rds", TRUE)
)
```

Re-reading:

```{r}
mtbi_train_parsed_imputations <- list.load(
    input_path("2025_09_11_mtbi_train_parsed_imputations.rds")
)
mtbi_test_parsed_imputations <- list.load(
    input_path("2025_09_11_mtbi_test_parsed_imputations.rds")
)

mtbi_pool_parsed_imputations <- list.load(
    input_path("2025_09_11_mtbi_pool_parsed_imputations.rds")
)

unij_parsed_imputations <- list.load(
    input_path("2025_09_11_unij_parsed_imputations.rds")
)
unij_pool_parsed_imps <- list.load(
    input_path("2025_09_11_unij_pool_parsed_imputations.rds")
)

names(mtbi_train_parsed_imputations)
```


## Constructing data_lists

We have:

* 1 original unimputed mTBI dataset
* 1 original unimputed unijured dataset
* 5 imputed mTBI datasets
* 5 imputed unijured datasets
* 5 imputed mTBI + unijured datasets

For the sake of brevity, these will be referred to with the following notation:

* m = mTBI
* u = unijured
* p = pool
* 0 = original (unimputed)
* 1-5 = imputed dataset number

```{r}
source("abcd/helper_functions.R")

mtbi_train_parsed_imputations[[1]]


names(mtbi_train_parsed_imputations) <- gsub("^mtbi_", "", names(mtbi_train_parsed_imputations))
names(mtbi_test_parsed_imputations) <- gsub("^mtbi_", "", names(mtbi_test_parsed_imputations))
names(mtbi_pool_parsed_imputations) <- gsub("^unij_", "", names(mtbi_pool_parsed_imputations))
names(unij_parsed_imputations) <- gsub("^unij_", "", names(unij_parsed_imputations))
names(unij_pool_parsed_imps) <- gsub("^unij_", "", names(unij_pool_parsed_imps))

mtbi_train_data_lists <- build_mtbi_dls(mtbi_train_parsed_imputations)
mtbi_train_oom_lists  <- build_ols(mtbi_train_parsed_imputations)
mtbi_test_data_lists  <- build_mtbi_dls(mtbi_test_parsed_imputations)
mtbi_test_oom_lists   <- build_ols(mtbi_test_parsed_imputations)
mtbi_pool_data_lists  <- build_unij_dls(mtbi_pool_parsed_imputations)
mtbi_pool_oom_lists   <- build_ols(mtbi_pool_parsed_imputations)
unij_data_lists       <- build_unij_dls(unij_parsed_imputations)
unij_oom_lists        <- build_ols(unij_parsed_imputations)
unij_pool_data_lists  <- build_unij_dls(unij_pool_parsed_imps)
unij_pool_oom_lists   <- build_ols(unij_pool_parsed_imps)

all_dls <- list(
    "mtbi_train_data_lists" = mtbi_train_data_lists,
    "mtbi_train_oom_lists"  = mtbi_train_oom_lists,
    "mtbi_test_data_lists"  = mtbi_test_data_lists,
    "mtbi_test_oom_lists"   = mtbi_test_oom_lists,
    "mtbi_pool_data_lists"  = mtbi_pool_data_lists,
    "mtbi_pool_oom_lists"   = mtbi_pool_oom_lists,
    "unij_data_lists"       = unij_data_lists,
    "unij_oom_lists"        = unij_oom_lists,
    "unij_pool_data_lists"  = unij_pool_data_lists,
    "unij_pool_oom_lists"   = unij_pool_oom_lists
)

```

## Renaming the initial data

```{r}
name_changes <- c(
    "age"                    = "interview_age",
    "brain_volume"           = "smri_vol_scs_wholeb",
    "cbcl_aggressive"        = "cbcl_scr_syn_aggressive_r",
    "cbcl_anxdep"            = "cbcl_scr_syn_anxdep_r",
    "cbcl_attention"         = "cbcl_scr_syn_attention_r",
    "cbcl_rulebreak"         = "cbcl_scr_syn_rulebreak_r",
    "cbcl_social"            = "cbcl_scr_syn_social_r",
    "cbcl_somatic"           = "cbcl_scr_syn_somatic_r",
    "cbcl_thought"           = "cbcl_scr_syn_thought_r",
    "cbcl_withdep"           = "cbcl_scr_syn_withdep_r",
    "cortical_sa"            = "smri_area_cdk_total",
    "cortical_t"             = "smri_thick_cdk_mean",
    "family_angry_p"         = "q2_angry_p",
    "family_angry_y"         = "q2_angry_y",
    "family_criticize_p"     = "q5_criticize_p",
    "family_criticize_y"     = "q5_criticize_y",
    "family_fight_p"         = "q1_fight_p",
    "family_fight_y"         = "q1_fight_y",
    "family_hit_p"           = "q6_hit_p",
    "family_hit_y"           = "q6_hit_y",
    "family_outdo_p"         = "q8_outdo_p",
    "family_outdo_y"         = "q8_outdo_y",
    "family_peaceful_p"      = "q7_peaceful_p",
    "family_peaceful_y"      = "q7_peaceful_y",
    "family_temper_p"        = "q4_temper_p",
    "family_temper_y"        = "q4_temper_y",
    "family_throw_p"         = "q3_throw_p",
    "family_throw_y"         = "q3_throw_y",
    "family_yell_p"          = "q9_yell_p",
    "family_yell_y"          = "q9_yell_y",
    "fmri_dmn_within_cor"    = "rsfmri_c_ngd_dt_ngd_dt",
    "fmri_dan_within_cor"    = "rsfmri_c_ngd_dla_ngd_dla",
    "fmri_fpn_within_cor"    = "rsfmri_c_ngd_fo_ngd_fo",
    "fmri_san_within_cor"    = "rsfmri_c_ngd_sa_ngd_sa",
    "fmri_dmn_fpn_cor"       = "rsfmri_c_ngd_dt_ngd_fo",
    "fmri_fpn_lamyg_cor"     = "rsfmri_cor_ngd_fopa_scs_aglh",
    "fmri_fpn_ramyg_cor"     = "rsfmri_cor_ngd_fopa_scs_agrh",
    "headache_history"       = "headache",
    "major_wm_ndi"           = "dmri_rsirnd_fib_allfib",
    "mtbi_age"               = "latest_mtbi_age",
    "mtbi_loc"               = "latest_mtbi_loc",
    "mtbi_mechanism"         = "latest_mtbi_mechanism",
    "mtbi_mem_daze"          = "latest_mtbi_mem_daze",
    "opp_sex_close_friend"   = "os_close_friend",
    "opp_sex_friend"         = "os_friend",
    "parent_aggressive"      = "asr_scr_aggressive_r",
    "parent_antisocial"      = "asr_scr_antisocial_r",
    "parent_anxdep"          = "asr_scr_anxdep_r",
    "parent_anxdisord"       = "asr_scr_anxdisord_r",
    "parent_attention"       = "asr_scr_attention_r",
    "parent_avoidant"        = "asr_scr_avoidant_r",
    "parent_depress"         = "asr_scr_depress_r",
    "parent_hyperactive"     = "asr_scr_hyperactive_r",
    "parent_intrusive"       = "asr_scr_intrusive_r",
    "parent_perstr"          = "asr_scr_perstr_r",
    "parent_somatic"         = "asr_scr_somatic_r",
    "parent_thought"         = "asr_scr_thought_r",
    "parent_withdrawn"       = "asr_scr_withdrawn_r",
    "pericortical_wm_ndi"    = "dmri_rsirndwm_cdk_mean",
    "previous_mtbis"         = "mtbi_count",
    "same_sex_close_friend"  = "ss_close_friend",
    "same_sex_friend"        = "ss_friend",
    "sds_sleep"              = "sds_p_ss_total",
    "weekday_screentime"     = "screentime_wkday_hrs",
    "weekend_screentime"     = "screentime_wknd_hrs"
)

names(all_dls[[1]][[1]])

all_dls <- all_dls |>
    lapply(
        function(data_lists_of_group) {
            lapply(
                data_lists_of_group,
                function(data_list) {
                    data_list <- as_data_list(rename_dl(data_list, name_changes))
                }
            )
        }
    )

saveRDS(all_dls, input_path("all_dls.rds", TRUE))
```

# Combat harmonization

```{r}
all_dls <- readRDS(input_path("2025_09_11_all_dls.rds"))
```

```{r echo = FALSE}
library(neuroCombat)

dl <- all_dls$"mtbi_train_data_lists"$"imp_1"
ol <- all_dls$"mtbi_train_oom_lists"$"imp_1"

combat_dl <- function(dl, ol, site_df, mean.only = FALSE) {
    neuro_components <- c(
        "n_subc_v",
        "n_cort_t",
        "n_cort_sa",
        "n_wmnd",
        "n_gord_cor",
        "n_subc_cor"
    )
    covariate_components <- c(
        "d_age",
        "d_sex",
        "d_income",
        "d_race",
        "d_pubertal"
    )
    neuro_fts <- c(
        "brain_volume",
        "cortical_t",
        "cortical_sa",
        "major_wm_ndi",
        "pericortical_wm_ndi",
        "fmri_dmn_within_cor",
        "fmri_dan_within_cor",
        "fmri_fpn_within_cor",
        "fmri_san_within_cor",
        "fmri_dmn_fpn_cor",
        "fmri_fpn_lamyg_cor",
        "fmri_fpn_ramyg_cor"
    )
    neuroimaging_df <- as.data.frame(dl[neuro_components])
    covariate_df <- as.data.frame(c(dl[covariate_components], ol))
    site_df <- site_df |>
        dplyr::mutate(
            uid = paste0("uid_", subjectkey)
        ) |>
        dplyr::select(
            -subjectkey
        )
    all_data <- dplyr::inner_join(neuroimaging_df, covariate_df, by = "uid")
    all_data <- dplyr::inner_join(all_data, site_df, by = "uid")
    # 1. data to be harmonized (dat param)
    # 3. covariates
    my_mod <- dplyr::select(all_data[, colnames(covariate_df)], -uid)
    data_harmonized <- neuroCombat(
        dat = t(
            as.matrix(all_data[, neuro_fts])
        ),
        batch = all_data$"site_id",
        mod = model.matrix(
            ~ .,
            data = my_mod
        ),
        mean.only = mean.only
    )
    data_harmonized <- data.frame(t(data_harmonized$"dat.combat"))
    data_harmonized$"uid" <- all_data$"uid"
    #--------------------------------------------------------------------------
    # Updating data list
    harmonized_dl <- dlapply(
        dl,
        function(x) {
            if (any(neuro_fts %in% colnames(x$"data"))) {
                neuro_idx <- which(neuro_fts %in% colnames(x$"data")) 
                neuro_fts_in_x <- neuro_fts[neuro_idx]
                x$"data"[, neuro_fts_in_x] <- data_harmonized[, neuro_fts_in_x]
            }
            return(x)
        }
    )
    return(harmonized_dl)
}

visualize_combat <- function(initial_dl, harmonized_dl, site_df) {
    site_df <- site_df |>
        dplyr::mutate(uid = paste0("uid_", subjectkey)) |>
        dplyr::select(-subjectkey)
    neuro_fts <- c(
        "brain_volume",
        "cortical_t",
        "cortical_sa",
        "major_wm_ndi",
        "pericortical_wm_ndi",
        "fmri_dmn_within_cor",
        "fmri_dan_within_cor",
        "fmri_fpn_within_cor",
        "fmri_san_within_cor",
        "fmri_dmn_fpn_cor",
        "fmri_fpn_lamyg_cor",
        "fmri_fpn_ramyg_cor"
    )
    initial_df <- as.data.frame(initial_dl)
    harmonized_df <- as.data.frame(harmonized_dl)
    if (!all(initial_df$"uid" == harmonized_dl$"uid")) {
        stop("Mismatched UIDs.")
    }
    initial_df$"group" <- "initial"
    initial_df <- dplyr::inner_join(initial_df, site_df, by = "uid")
    harmonized_df$"group" <- "harmonized"
    harmonized_df <- dplyr::inner_join(harmonized_df, site_df, by = "uid")
    df <- dplyr::bind_rows(initial_df, harmonized_df)
    plot_list <- vector("list", length = length(neuro_fts))
    for (i in seq_along(neuro_fts)) {
        ft <- neuro_fts[i]
        plot <- df |>
            ggplot(
                aes(
                    x = .data[["site_id"]],
                    y = .data[[ft]],
                    color = .data[["group"]]
                )
            ) + 
            geom_boxplot(
                outlier.shape = NA,
                position = position_dodge(width = 0.8)
            ) +
            geom_point(
                position = position_dodge(width = 0.8),
                alpha = 0.6,
                size = 1.5
            ) +
            labs(
                x = "Site ID",
                color = "Group"
            ) +
            theme_minimal()
        plot_list[[i]] <- plot
    }
    return(plot_list)
}

dl_harmonized <- combat_dl(dl, ol, mtbi_site)

pl <- visualize_combat(dl, dl_harmonized, mtbi_site)

names(all_dls)

all_dls$"mtbi_der_sh_data_lists"$"imp_1" <-  combat_dl(all_dls$"mtbi_train_data_lists"$"imp_1", all_dls$"mtbi_train_oom_lists"$"imp_1", mtbi_site)
all_dls$"mtbi_der_sh_data_lists"$"imp_2" <-  combat_dl(all_dls$"mtbi_train_data_lists"$"imp_2", all_dls$"mtbi_train_oom_lists"$"imp_2", mtbi_site)
all_dls$"mtbi_der_sh_data_lists"$"imp_3" <-  combat_dl(all_dls$"mtbi_train_data_lists"$"imp_3", all_dls$"mtbi_train_oom_lists"$"imp_3", mtbi_site)
all_dls$"mtbi_der_sh_data_lists"$"imp_4" <-  combat_dl(all_dls$"mtbi_train_data_lists"$"imp_4", all_dls$"mtbi_train_oom_lists"$"imp_4", mtbi_site)
all_dls$"mtbi_der_sh_data_lists"$"imp_5" <-  combat_dl(all_dls$"mtbi_train_data_lists"$"imp_5", all_dls$"mtbi_train_oom_lists"$"imp_5", mtbi_site)

all_dls$"mtbi_val_sh_data_lists"$"imp_1" <-  combat_dl(all_dls$"mtbi_test_data_lists"$"imp_1", all_dls$"mtbi_test_oom_lists"$"imp_1", mtbi_site, mean.only = TRUE)
all_dls$"mtbi_val_sh_data_lists"$"imp_2" <-  combat_dl(all_dls$"mtbi_test_data_lists"$"imp_2", all_dls$"mtbi_test_oom_lists"$"imp_2", mtbi_site, mean.only = TRUE)
all_dls$"mtbi_val_sh_data_lists"$"imp_3" <-  combat_dl(all_dls$"mtbi_test_data_lists"$"imp_3", all_dls$"mtbi_test_oom_lists"$"imp_3", mtbi_site, mean.only = TRUE)
all_dls$"mtbi_val_sh_data_lists"$"imp_4" <-  combat_dl(all_dls$"mtbi_test_data_lists"$"imp_4", all_dls$"mtbi_test_oom_lists"$"imp_4", mtbi_site, mean.only = TRUE)
all_dls$"mtbi_val_sh_data_lists"$"imp_5" <-  combat_dl(all_dls$"mtbi_test_data_lists"$"imp_5", all_dls$"mtbi_test_oom_lists"$"imp_5", mtbi_site, mean.only = TRUE)

all_dls$"mtbi_der_ph_data_lists"$"imp_1" <-  combat_dl(all_dls$"mtbi_pool_data_lists"$"imp_1", all_dls$"mtbi_pool_oom_lists"$"imp_1", mtbi_site)
all_dls$"mtbi_der_ph_data_lists"$"imp_2" <-  combat_dl(all_dls$"mtbi_pool_data_lists"$"imp_2", all_dls$"mtbi_pool_oom_lists"$"imp_2", mtbi_site)
all_dls$"mtbi_der_ph_data_lists"$"imp_3" <-  combat_dl(all_dls$"mtbi_pool_data_lists"$"imp_3", all_dls$"mtbi_pool_oom_lists"$"imp_3", mtbi_site)
all_dls$"mtbi_der_ph_data_lists"$"imp_4" <-  combat_dl(all_dls$"mtbi_pool_data_lists"$"imp_4", all_dls$"mtbi_pool_oom_lists"$"imp_4", mtbi_site)
all_dls$"mtbi_der_ph_data_lists"$"imp_5" <-  combat_dl(all_dls$"mtbi_pool_data_lists"$"imp_5", all_dls$"mtbi_pool_oom_lists"$"imp_5", mtbi_site)

all_dls$"unij_sh_data_lists"$"imp_1" <-  combat_dl(all_dls$"unij_data_lists"$"imp_1", all_dls$"unij_oom_lists"$"imp_1", unij_site)
all_dls$"unij_sh_data_lists"$"imp_2" <-  combat_dl(all_dls$"unij_data_lists"$"imp_2", all_dls$"unij_oom_lists"$"imp_2", unij_site)
all_dls$"unij_sh_data_lists"$"imp_3" <-  combat_dl(all_dls$"unij_data_lists"$"imp_3", all_dls$"unij_oom_lists"$"imp_3", unij_site)
all_dls$"unij_sh_data_lists"$"imp_4" <-  combat_dl(all_dls$"unij_data_lists"$"imp_4", all_dls$"unij_oom_lists"$"imp_4", unij_site)
all_dls$"unij_sh_data_lists"$"imp_5" <-  combat_dl(all_dls$"unij_data_lists"$"imp_5", all_dls$"unij_oom_lists"$"imp_5", unij_site)

all_dls$"unij_ph_data_lists"$"imp_1" <-  combat_dl(all_dls$"unij_pool_data_lists"$"imp_1", all_dls$"unij_pool_oom_lists"$"imp_1", unij_site)
all_dls$"unij_ph_data_lists"$"imp_2" <-  combat_dl(all_dls$"unij_pool_data_lists"$"imp_2", all_dls$"unij_pool_oom_lists"$"imp_2", unij_site)
all_dls$"unij_ph_data_lists"$"imp_3" <-  combat_dl(all_dls$"unij_pool_data_lists"$"imp_3", all_dls$"unij_pool_oom_lists"$"imp_3", unij_site)
all_dls$"unij_ph_data_lists"$"imp_4" <-  combat_dl(all_dls$"unij_pool_data_lists"$"imp_4", all_dls$"unij_pool_oom_lists"$"imp_4", unij_site)
all_dls$"unij_ph_data_lists"$"imp_5" <-  combat_dl(all_dls$"unij_pool_data_lists"$"imp_5", all_dls$"unij_pool_oom_lists"$"imp_5", unij_site)

all_dls_h <- all_dls

keep_comps <- c(
    "mtbi_der_sh_data_lists",
    "mtbi_train_oom_lists",
    "mtbi_val_sh_data_lists",
    "mtbi_test_oom_lists",
    "mtbi_der_ph_data_lists",
    "mtbi_pool_oom_lists",
    "unij_sh_data_lists",
    "unij_oom_lists",
    "unij_ph_data_lists",
    "unij_pool_oom_lists"
)

all_dls_h <- all_dls_h[keep_comps]

names(all_dls_h) <- c(
    "mtbi_der_u_dls",
    "mtbi_der_u_ols",
    "mtbi_val_u_dls",
    "mtbi_val_u_ols",
    "mtbi_der_p_dls",
    "mtbi_der_p_ols",
    "unij_all_u_dls",
    "unij_all_u_ols",
    "unij_all_p_dls",
    "unij_all_p_ols"
)

saveRDS(all_dls_h, proc_path("all_dls_h.rds", TRUE))
```

# Siblings drop

```{r}
import <- function(path) {
    return(abcdutils::abcd_load(core_path(path)))
}

abcd_y_lt <- import("abcd-general/abcd_y_lt.csv")

drop_random_siblings <- function(abcd_y_lt, subjects) {
    sibling_df <- abcd_y_lt |>
        filter_timepoint(t = 0) |>
        dplyr::select(subjectkey, rel_family_id) |>
        filter_subjects(subjects)
    sibling_df <- sibling_df[sample(nrow(sibling_df)), ]
    is_dup_family <- duplicated(sibling_df$"rel_family_id")
    siblings_removed <- sibling_df[!is_dup_family, ]
    return(siblings_removed$"subjectkey")
}

set.seed(42)
mtbi_no_sibs_subs <- drop_random_siblings(abcd_y_lt, mtbi_subs)

mtbi_der_no_sibs_subs <- mtbi_train_subs[mtbi_train_subs %in% mtbi_no_sibs_subs]
mtbi_val_no_sibs_subs <- mtbi_test_subs[mtbi_test_subs %in% mtbi_no_sibs_subs]

set.seed(42)
unij_no_sibs_subs <- drop_random_siblings(abcd_y_lt, unij_subs)

length(mtbi_train_subs)       # N = 359 originally
length(mtbi_der_no_sibs_subs) # N = 356 after sibling removal

length(mtbi_test_subs)        # N = 83 originally
length(mtbi_val_no_sibs_subs) # N = 82 after sibling removal

length(unij_subs)         # N = 9302 originally
length(unij_no_sibs_subs) # N = 7905 after sibling removal

saveRDS(mtbi_no_sibs_subs,     sub_path("mtbi_no_sibs_subs.rds", TRUE))
saveRDS(mtbi_der_no_sibs_subs, sub_path("mtbi_der_no_sibs_subs.rds", TRUE))
saveRDS(mtbi_val_no_sibs_subs, sub_path("mtbi_val_no_sibs_subs.rds", TRUE))
saveRDS(unij_no_sibs_subs,     sub_path("unij_no_sibs_subs.rds", TRUE))

mtbi_no_sibs_subs <- readRDS(sub_path("2025_09_11_mtbi_no_sibs_subs.rds"))
mtbi_der_no_sibs_subs <- readRDS(sub_path("2025_09_11_mtbi_der_no_sibs_subs.rds"))
mtbi_val_no_sibs_subs <- readRDS(sub_path("2025_09_11_mtbi_val_no_sibs_subs.rds"))
unij_no_sibs_subs <- readRDS(sub_path("2025_09_11_unij_no_sibs_subs.rds"))
all_dls_h <- readRDS(proc_path("2025_09_11_all_dls_h.rds"))

names(all_dls_h)

mtbi_der_no_sibs_subs

batch_uid_replace <- function(list_of_dls, uids) {
    uids <- paste0("uid_", uids)
    list_of_dls_new <- lapply(
        list_of_dls,
        function(dl) {
            new_dl <- dlapply(
                dl,
                function(x) {
                    x$"data" <- x$"data"[x$"data"$"uid" %in% uids, ]
                    return(x)
                }
            )
            return(new_dl)
        }
    )
    return(list_of_dls_new)
}

all_dls_h_no_sibs <- all_dls_h

all_dls_h_no_sibs[["mtbi_der_u_dls"]] <- batch_uid_replace(all_dls_h_no_sibs[["mtbi_der_u_dls"]], mtbi_der_no_sibs_subs)
all_dls_h_no_sibs[["mtbi_der_u_ols"]] <- batch_uid_replace(all_dls_h_no_sibs[["mtbi_der_u_ols"]], mtbi_der_no_sibs_subs)

all_dls_h_no_sibs[["mtbi_val_u_dls"]] <- batch_uid_replace(all_dls_h_no_sibs[["mtbi_val_u_dls"]], mtbi_val_no_sibs_subs)
all_dls_h_no_sibs[["mtbi_val_u_ols"]] <- batch_uid_replace(all_dls_h_no_sibs[["mtbi_val_u_ols"]], mtbi_val_no_sibs_subs)

all_dls_h_no_sibs[["mtbi_der_p_dls"]] <- batch_uid_replace(all_dls_h_no_sibs[["mtbi_der_p_dls"]], mtbi_der_no_sibs_subs)
all_dls_h_no_sibs[["mtbi_der_p_ols"]] <- batch_uid_replace(all_dls_h_no_sibs[["mtbi_der_p_ols"]], mtbi_der_no_sibs_subs)

all_dls_h_no_sibs[["unij_all_u_dls"]] <- batch_uid_replace(all_dls_h_no_sibs[["unij_all_u_dls"]], unij_no_sibs_subs)
all_dls_h_no_sibs[["unij_all_u_ols"]] <- batch_uid_replace(all_dls_h_no_sibs[["unij_all_u_ols"]], unij_no_sibs_subs)

all_dls_h_no_sibs[["unij_all_p_dls"]] <- batch_uid_replace(all_dls_h_no_sibs[["unij_all_p_dls"]], unij_no_sibs_subs)
all_dls_h_no_sibs[["unij_all_p_ols"]] <- batch_uid_replace(all_dls_h_no_sibs[["unij_all_p_ols"]], unij_no_sibs_subs)

saveRDS(all_dls_h_no_sibs, proc_path("all_dls_h_no_sibs.rds", TRUE))
```
