# Similarity Network Fusion

In this chapter, I generate heatmaps to visit some of the broad correlations between data being used for this subtyping analysis.

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)

source(here("abcd/functions.R"))

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subjects <- read_csv(sub_path("2023_11_07_mtbi_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2023_11_07_uninjured_subjects.csv"))
```

## Loading data and out of model lists

```{r}
data_list_m1 <- list.load(input_path("2023_12_14_data_list_m1.rds"))
data_list_m2 <- list.load(input_path("2023_12_14_data_list_m2.rds"))
data_list_m3 <- list.load(input_path("2023_12_14_data_list_m3.rds"))
data_list_m4 <- list.load(input_path("2023_12_14_data_list_m4.rds"))
data_list_m5 <- list.load(input_path("2023_12_14_data_list_m5.rds"))
data_list_pm1 <- list.load(input_path("2023_12_14_data_list_pm1.rds"))
data_list_pm2 <- list.load(input_path("2023_12_14_data_list_pm2.rds"))
data_list_pm3 <- list.load(input_path("2023_12_14_data_list_pm3.rds"))
data_list_pm4 <- list.load(input_path("2023_12_14_data_list_pm4.rds"))
data_list_pm5 <- list.load(input_path("2023_12_14_data_list_pm5.rds"))
oom_list_m1 <- list.load(input_path("2023_12_14_oom_list_m1.rds"))
oom_list_m2 <- list.load(input_path("2023_12_14_oom_list_m2.rds"))
oom_list_m3 <- list.load(input_path("2023_12_14_oom_list_m3.rds"))
oom_list_m4 <- list.load(input_path("2023_12_14_oom_list_m4.rds"))
oom_list_m5 <- list.load(input_path("2023_12_14_oom_list_m5.rds"))
oom_list_pm1 <- list.load(input_path("2023_12_14_oom_list_pm1.rds"))
oom_list_pm2 <- list.load(input_path("2023_12_14_oom_list_pm2.rds"))
oom_list_pm3 <- list.load(input_path("2023_12_14_oom_list_pm3.rds"))
oom_list_pm4 <- list.load(input_path("2023_12_14_oom_list_pm4.rds"))
oom_list_pm5 <- list.load(input_path("2023_12_14_oom_list_pm5.rds"))
```

## Some pairwise variable correlations

Examining some of the pairwise associations between all the included (numeric) variables within the first imputed dataset.

```{r}
# Merging all the variables into a single data list
all_var_dl_m1 <- c(data_list_m1, oom_list_m1)

# First pass to extract the order of columns
# correlation_data function contains the correlation matrix, heatmap, and order
correlation_data_m1 <- correlation_data(all_var_dl_m1)

# Pulling just the correlation matrix
correlation_matrix_m1 <- correlation_data_m1$"correlation_matrix"

# The absolute values of all correlations with race
race_cors_m1 <- abs(correlation_matrix_m1[, "race"])
# The variables sorted by their absolute value of correlation with race
race_order_m1 <- sort(race_cors_m1, index.return = TRUE, decreasing = TRUE)$"ix"

# Same values, but for the sex variable
sex_cors_m1 <- abs(correlation_matrix_m1[, "sex"])
sex_order_m1 <- sort(sex_cors_m1, index.return = TRUE, decreasing = TRUE)$"ix"

# 1. Heatmap of all correlations
correlation_data_m1$"heatmap"
save_png(
    correlation_data_m1$"heatmap",
    fig_path("correlation_heatmap_m1.png", TRUE),
    width = 3500,
    height = 3500
)

# 2. Heatmap of all correlations, sorted by abs(correlation with race)
correlation_data_m1_race <- correlation_data(
    all_var_dl_m1,
    order = race_order_m1
)
save_png(
    correlation_data_m1_race$"heatmap",
    fig_path("correlation_heatmap_m1_race.png", TRUE),
    width = 3500,
    height = 3500
)

# 3. Heatmap of race correlations, sorted by abs(correlation with race)
correlation_heatmap_m1_race_only <- ComplexHeatmap::Heatmap(
    correlation_matrix_m1[race_order_m1, "race"],
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    show_column_names = FALSE
)
save_png(
    correlation_heatmap_m1_race_only,
    fig_path("correlation_heatmap_m1_race_only.png", TRUE),
    width = 3500,
    height = 3500
)

# 4. Heatmap of all correlations, sorted by abs(correlation with sex)
correlation_data_m1_sex <- correlation_data(
    all_var_dl_m1,
    order = sex_order_m1
)
save_png(
    correlation_data_m1_sex$"heatmap",
    fig_path("correlation_heatmap_m1_sex.png", TRUE),
    width = 3500,
    height = 3500
)

# 5. Heatmap of sex correlations, sorted by abs(correlation with sex)
correlation_heatmap_m1_sex_only <- ComplexHeatmap::Heatmap(
    correlation_matrix_m1[sex_order_m1, "sex"],
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    show_column_names = FALSE
)
save_png(
    correlation_heatmap_m1_sex_only,
    fig_path("correlation_heatmap_m1_sex_only.png", TRUE),
    width = 3500,
    height = 3500
)

```

## Replications across the other imputations

To get a sense of how the imputation process affects the correlations between variables, I repeat the above process for the other imputations.

```{r}

all_var_dl_m2 <- c(data_list_m2, oom_list_m2)
all_var_dl_m3 <- c(data_list_m3, oom_list_m3)
all_var_dl_m4 <- c(data_list_m4, oom_list_m4)
all_var_dl_m5 <- c(data_list_m5, oom_list_m5)
all_var_dl_pm1 <- c(data_list_pm1, oom_list_pm1)
all_var_dl_pm2 <- c(data_list_pm2, oom_list_pm2)
all_var_dl_pm3 <- c(data_list_pm3, oom_list_pm3)
all_var_dl_pm4 <- c(data_list_pm4, oom_list_pm4)
all_var_dl_pm5 <- c(data_list_pm5, oom_list_pm5)

correlation_data_m2 <- correlation_data(all_var_dl_m2)
correlation_data_m3 <- correlation_data(all_var_dl_m3)
correlation_data_m4 <- correlation_data(all_var_dl_m4)
correlation_data_m5 <- correlation_data(all_var_dl_m5)
correlation_data_pm1 <- correlation_data(all_var_dl_pm1)
correlation_data_pm2 <- correlation_data(all_var_dl_pm2)
correlation_data_pm3 <- correlation_data(all_var_dl_pm3)
correlation_data_pm4 <- correlation_data(all_var_dl_pm4)
correlation_data_pm5 <- correlation_data(all_var_dl_pm5)

# A consistent order making use of the restricted variables found in the pooled matrix
var_order <- colnames(correlation_data_pm1$"correlation_matrix")

canonical_m1 <- correlation_data_m1$"correlation_matrix"[var_order, var_order]
canonical_m2 <- correlation_data_m2$"correlation_matrix"[var_order, var_order]
canonical_m3 <- correlation_data_m3$"correlation_matrix"[var_order, var_order]
canonical_m4 <- correlation_data_m4$"correlation_matrix"[var_order, var_order]
canonical_m5 <- correlation_data_m5$"correlation_matrix"[var_order, var_order]
canonical_pm1 <- correlation_data_pm1$"correlation_matrix"[var_order, var_order]
canonical_pm2 <- correlation_data_pm2$"correlation_matrix"[var_order, var_order]
canonical_pm3 <- correlation_data_pm3$"correlation_matrix"[var_order, var_order]
canonical_pm4 <- correlation_data_pm4$"correlation_matrix"[var_order, var_order]
canonical_pm5 <- correlation_data_pm5$"correlation_matrix"[var_order, var_order]

m_matrices <- array(
    c(
        canonical_m1,
        canonical_m2,
        canonical_m3,
        canonical_m4,
        canonical_m5
    ),
    dim = c(dim(canonical_m1), 5)
)
# Element-wise means and variances
m_means <- apply(m_matrices, c(1, 2), mean)
m_vars <- apply(m_matrices, c(1, 2), var)
colnames(m_means) <- colnames(canonical_m1)
rownames(m_means) <- rownames(canonical_m1)
colnames(m_vars) <- colnames(canonical_m1)
rownames(m_vars) <- rownames(canonical_m1)

pm_matrices <- array(
    c(
        canonical_pm1,
        canonical_pm2,
        canonical_pm3,
        canonical_pm4,
        canonical_pm5
    ),
    dim = c(dim(canonical_pm1), 5)
)
pm_means <- apply(pm_matrices, c(1, 2), mean)
pm_vars <- apply(pm_matrices, c(1, 2), var)
colnames(pm_means) <- colnames(canonical_pm1)
rownames(pm_means) <- rownames(canonical_pm1)
colnames(pm_vars) <- colnames(canonical_pm1)
rownames(pm_vars) <- rownames(canonical_pm1)

# Average of the mtbi correlations
save_png(
    ComplexHeatmap::Heatmap(m_means),
    fig_path("correlation_heatmap_m_means.png", TRUE),
    width = 3500,
    height = 3500
)

# Average of the pooled correlations
save_png(
    ComplexHeatmap::Heatmap(pm_means),
    fig_path("correlation_heatmap_pm_means.png", TRUE),
    width = 3500,
    height = 3500
)

# Very small difference in correlations
max(abs(m_means - pm_means)) # 0.0610264

# Very small variances
max(m_vars) # 0.002426604
max(pm_vars) # 0.02360992
```
