# Similarity Network Fusion

In this chapter, I generate heatmaps to visit some of the broad correlations between data being used for this subtyping analysis.

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subjects <- read_csv(sub_path("2023_11_07_mtbi_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2023_11_07_uninjured_subjects.csv"))
```

## Utility functions

```{r}
divergent_colours <- function(column)  {
    values <- unique(column)
    colours <- RColorBrewer::brewer.pal(n = length(values), name = "Set3")
    names(colours) <- values
    return(colours)
}

data_list_metadata <- function(data_list) {
    merged_df <- metasnf::collapse_dl(data_list)
    merged_df <- merged_df[, colnames(merged_df) != "subjectkey"]
    ###########################################################################
    # Build data.frame containing the types of variables in merged_df
    ###########################################################################
    types <- data_list |>
        lapply(
            function(x) {
                rep(x$"type", ncol(x$"data") - 1)
            }
        ) |>
        unlist()
    domains <- data_list |>
        lapply(
            function(x) {
                rep(x$"domain", ncol(x$"data") - 1)
            }
        ) |>
        unlist()
    var_names <- colnames(merged_df[, colnames(merged_df) != "subjectkey"])
    metadata <- data.frame(
        name = var_names,
        type = types,
        domain = domains
    )
    return(metadata)
}

keep_numeric <- function(df) {
    df <- metasnf::numcol_to_numeric(df)
    classes <- as.vector(sapply(df, class))
    df <- df[, classes == "numeric", drop = FALSE]
    return(df)
}

hm_colours <- function(data, max_red = TRUE) {
    if (max_red) {
        colours <- circlize::colorRamp2(
            c(min(data), max(data)),
            c("black", "red")
        )
    } else {
        colours <- circlize::colorRamp2(
            c(min(data), max(data)),
            c("red", "black")
        )
    }
    return(colours)
}

correlation_data <- function(data_list, order = NULL) {
    dl_df <- metasnf::collapse_dl(data_list)
    numeric_dl_df <- keep_numeric(dl_df)
    correlation_matrix <- cor(numeric_dl_df)
    if (is.null(order)) {
        heatmap <- ComplexHeatmap::Heatmap(correlation_matrix)
    } else {
        heatmap <- ComplexHeatmap::Heatmap(
            correlation_matrix[order, order],
            cluster_rows = FALSE,
            cluster_columns = FALSE
        )
    }
    drawn_heatmap <- ComplexHeatmap::draw(heatmap)
    order <- ComplexHeatmap::row_order(drawn_heatmap)
    results <- list(
        "correlation_matrix" = correlation_matrix,
        "heatmap" = heatmap,
        "order" = order
    )
    return(results)
}

pval_select <- function(extended_solutions_matrix,
                        keep_summary = TRUE,
                        negative_log = FALSE,
                        recalculate_summary = TRUE) {
    pval_df <- extended_solutions_matrix |>
        dplyr::select(
            "row_id",
            dplyr::ends_with("_p"),
            dplyr::contains("p_val")
        ) |>
        data.frame() |>
        metasnf::numcol_to_numeric()
    if (!keep_summary) {
        pval_df <- pval_df |>
            dplyr::select(-c("min_p_val", "mean_p_val"))
    }
    if (negative_log) {
        neg_log_pval_df <- -log(pval_df)
        neg_log_pval_df$"row_id" <- pval_df$"row_id"
        pval_df <- neg_log_pval_df
        if (recalculate_summary) {
            mini_df <- pval_df |> dplyr::select(
                dplyr::ends_with("_p")
            )
            pval_df$"mean_neglog_p" <- apply(mini_df, 1, FUN = mean)
            pval_df$"max_neglog_p" <- apply(mini_df, 1, FUN = max)
        }
    }
    return(pval_df)
}

pval_heatmap <- function(pval_df, order, max_red = FALSE) {
    pval_df <- pval_df |> dplyr::select(-"row_id")
    pval_matrix <- as.matrix(pval_df[order, ])
    hm <- ComplexHeatmap::Heatmap(
        pval_matrix,
        cluster_rows = FALSE,
        cluster_columns = FALSE,
        show_row_names = FALSE,
        col = hm_colours(pval_matrix, max_red)
    )
    return(hm)
}

split_at <- function(vector, nrow) {
    split_vec <- rep("A", nrow)
    if (vector[length(vector)] != nrow) {
        vector <- c(vector, nrow)
    }
    for (i in 1:(length(vector) - 1)) {
        start <- vector[i]
        end <- vector[i + 1]
        split_vec[start:end] <- LETTERS[i + 1]
    }
    return(split_vec)
}

save_pdf <- function(heatmap, path, width, height) {
    grDevices::pdf(
        path,
        width,
        height
    )
    heatmap
    grDevices::dev.off()
}

save_png <- function(heatmap, path, width, height, res = 300) {
    tryCatch(
        {
            grDevices::png(
                filename = path,
                width = width,
                height = height,
                res = res
            )
            ComplexHeatmap::draw(heatmap)
            grDevices::dev.off()
        }, error = function(err) {
            message("Error saving png - does the heatmap exist?")
            grDevices::dev.off()
        }
    )
}

read_matrix <- function(path) {
    mat <- read_csv(path, col_names = TRUE) |> as.matrix()
    rownames(mat) <- mat[, 1]
    mat <- mat[, -1]
    mat <- mat |>
        data.frame() |>
        numcol_to_numeric() |>
        as.matrix()
    return(mat)
}
```

## Loading data and out of model lists

```{r}
data_list_m1 <- list.load(input_path("2023_12_14_data_list_m1.rds"))
data_list_m2 <- list.load(input_path("2023_12_14_data_list_m2.rds"))
data_list_m3 <- list.load(input_path("2023_12_14_data_list_m3.rds"))
data_list_m4 <- list.load(input_path("2023_12_14_data_list_m4.rds"))
data_list_m5 <- list.load(input_path("2023_12_14_data_list_m5.rds"))
data_list_pm1 <- list.load(input_path("2023_12_14_data_list_pm1.rds"))
data_list_pm2 <- list.load(input_path("2023_12_14_data_list_pm2.rds"))
data_list_pm3 <- list.load(input_path("2023_12_14_data_list_pm3.rds"))
data_list_pm4 <- list.load(input_path("2023_12_14_data_list_pm4.rds"))
data_list_pm5 <- list.load(input_path("2023_12_14_data_list_pm5.rds"))
oom_list_m1 <- list.load(input_path("2023_12_14_oom_list_m1.rds"))
oom_list_m2 <- list.load(input_path("2023_12_14_oom_list_m2.rds"))
oom_list_m3 <- list.load(input_path("2023_12_14_oom_list_m3.rds"))
oom_list_m4 <- list.load(input_path("2023_12_14_oom_list_m4.rds"))
oom_list_m5 <- list.load(input_path("2023_12_14_oom_list_m5.rds"))
oom_list_pm1 <- list.load(input_path("2023_12_14_oom_list_pm1.rds"))
oom_list_pm2 <- list.load(input_path("2023_12_14_oom_list_pm2.rds"))
oom_list_pm3 <- list.load(input_path("2023_12_14_oom_list_pm3.rds"))
oom_list_pm4 <- list.load(input_path("2023_12_14_oom_list_pm4.rds"))
oom_list_pm5 <- list.load(input_path("2023_12_14_oom_list_pm5.rds"))
```

## Some pairwise variable correlations

Examining some of the pairwise associations between all the included (numeric) variables within the first imputed dataset.

```{r}
# Merging all the variables into a single data list
all_var_dl_m1 <- c(data_list_m1, oom_list_m1)

# First pass to extract the order of columns
# correlation_data function contains the correlation matrix, heatmap, and order
correlation_data_m1 <- correlation_data(all_var_dl_m1)

# Pulling just the correlation matrix
correlation_matrix_m1 <- correlation_data_m1$"correlation_matrix"

# The absolute values of all correlations with race
race_cors_m1 <- abs(correlation_matrix_m1[, "race"])
# The variables sorted by their absolute value of correlation with race
race_order_m1 <- sort(race_cors_m1, index.return = TRUE, decreasing = TRUE)$"ix"

# Same values, but for the sex variable
sex_cors_m1 <- abs(correlation_matrix_m1[, "sex"])
sex_order_m1 <- sort(sex_cors_m1, index.return = TRUE, decreasing = TRUE)$"ix"

# 1. Heatmap of all correlations
correlation_data_m1$"heatmap"
save_png(
    correlation_data_m1$"heatmap",
    fig_path("correlation_heatmap_m1.png", TRUE),
    width = 2500,
    height = 2500
)

# 2. Heatmap of all correlations, sorted by abs(correlation with race)
correlation_data_m1_race <- correlation_data(
    all_var_dl_m1,
    order = race_order_m1
)
save_png(
    correlation_data_m1_race$"heatmap",
    fig_path("correlation_heatmap_m1_race.png", TRUE),
    width = 2500,
    height = 2500
)

# 3. Heatmap of race correlations, sorted by abs(correlation with race)
correlation_heatmap_m1_race_only <- ComplexHeatmap::Heatmap(
    correlation_matrix_m1[race_order_m1, "race"],
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    show_column_names = FALSE
)
save_png(
    correlation_heatmap_m1_race_only,
    fig_path("correlation_heatmap_m1_race_only.png", TRUE),
    width = 2000,
    height = 2000
)

# 4. Heatmap of all correlations, sorted by abs(correlation with sex)
correlation_data_m1_sex <- correlation_data(
    all_var_dl_m1,
    order = sex_order_m1
)
save_png(
    correlation_data_m1_sex$"heatmap",
    fig_path("correlation_heatmap_m1_sex.png", TRUE),
    width = 2500,
    height = 2500
)

# 5. Heatmap of sex correlations, sorted by abs(correlation with sex)
correlation_heatmap_m1_sex_only <- ComplexHeatmap::Heatmap(
    correlation_matrix_m1[sex_order_m1, "sex"],
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    show_column_names = FALSE
)
save_png(
    correlation_heatmap_m1_sex_only,
    fig_path("correlation_heatmap_m1_sex_only.png", TRUE),
    width = 2000,
    height = 2000
)

```

## Replications across the other imputations

To get a sense of how the imputation process affects the correlations between variables, I repeat the above process for the other imputations.

```{r}

all_var_dl_m2 <- c(data_list_m2, oom_list_m2)
all_var_dl_m3 <- c(data_list_m3, oom_list_m3)
all_var_dl_m4 <- c(data_list_m4, oom_list_m4)
all_var_dl_m5 <- c(data_list_m5, oom_list_m5)
all_var_dl_pm1 <- c(data_list_pm1, oom_list_pm1)
all_var_dl_pm2 <- c(data_list_pm2, oom_list_pm2)
all_var_dl_pm3 <- c(data_list_pm3, oom_list_pm3)
all_var_dl_pm4 <- c(data_list_pm4, oom_list_pm4)
all_var_dl_pm5 <- c(data_list_pm5, oom_list_pm5)

correlation_data_m2 <- correlation_data(all_var_dl_m2)
correlation_data_m3 <- correlation_data(all_var_dl_m3)
correlation_data_m4 <- correlation_data(all_var_dl_m4)
correlation_data_m5 <- correlation_data(all_var_dl_m5)
correlation_data_pm1 <- correlation_data(all_var_dl_pm1)
correlation_data_pm2 <- correlation_data(all_var_dl_pm2)
correlation_data_pm3 <- correlation_data(all_var_dl_pm3)
correlation_data_pm4 <- correlation_data(all_var_dl_pm4)
correlation_data_pm5 <- correlation_data(all_var_dl_pm5)

# A consistent order making use of the restricted variables found in the pooled matrix
var_order <- colnames(correlation_data_pm1$"correlation_matrix")

write.csv(var_order, proc_path("var_order.csv", TRUE))
write.csv(
    data.frame(correlation_data_m1$"correlation_matrix"),
    proc_path("correlation_matrix_m1.csv", TRUE)
)
write.csv(
    data.frame(correlation_data_m2$"correlation_matrix"),
    proc_path("correlation_matrix_m2.csv", TRUE)
)
write.csv(
    data.frame(correlation_data_m3$"correlation_matrix"),
    proc_path("correlation_matrix_m3.csv", TRUE)
)
write.csv(
    data.frame(correlation_data_m4$"correlation_matrix"),
    proc_path("correlation_matrix_m4.csv", TRUE)
)
write.csv(
    data.frame(correlation_data_m5$"correlation_matrix"),
    proc_path("correlation_matrix_m5.csv", TRUE)
)
write.csv(
    data.frame(correlation_data_pm1$"correlation_matrix"),
    proc_path("correlation_matrix_pm1.csv", TRUE)
)
write.csv(
    data.frame(correlation_data_pm2$"correlation_matrix"),
    proc_path("correlation_matrix_pm2.csv", TRUE)
)
write.csv(
    data.frame(correlation_data_pm3$"correlation_matrix"),
    proc_path("correlation_matrix_pm3.csv", TRUE)
)
write.csv(
    data.frame(correlation_data_pm4$"correlation_matrix"),
    proc_path("correlation_matrix_pm4.csv", TRUE)
)
write.csv(
    data.frame(correlation_data_pm5$"correlation_matrix"),
    proc_path("correlation_matrix_pm5.csv", TRUE)
)
```

```{r}
var_order <- read_csv(proc_path("2024_01_13_var_order.csv"))$"x"
correlation_matrix_m1 <- read_matrix(
    proc_path("2024_01_13_correlation_matrix_m1.csv")
)
correlation_matrix_m2 <- read_matrix(
    proc_path("2024_01_13_correlation_matrix_m2.csv")
)
correlation_matrix_m3 <- read_matrix(
    proc_path("2024_01_13_correlation_matrix_m3.csv")
)
correlation_matrix_m4 <- read_matrix(
    proc_path("2024_01_13_correlation_matrix_m4.csv")
)
correlation_matrix_m5 <- read_matrix(
    proc_path("2024_01_13_correlation_matrix_m5.csv")
)
correlation_matrix_pm1 <- read_matrix(
    proc_path("2024_01_13_correlation_matrix_pm1.csv")
)
correlation_matrix_pm2 <- read_matrix(
    proc_path("2024_01_13_correlation_matrix_pm2.csv")
)
correlation_matrix_pm3 <- read_matrix(
    proc_path("2024_01_13_correlation_matrix_pm3.csv")
)
correlation_matrix_pm4 <- read_matrix(
    proc_path("2024_01_13_correlation_matrix_pm4.csv")
)
correlation_matrix_pm5 <- read_matrix(
    proc_path("2024_01_13_correlation_matrix_pm5.csv")
)

canonical_m1 <- correlation_matrix_m1[var_order, var_order]
canonical_m2 <- correlation_matrix_m2[var_order, var_order]
canonical_m3 <- correlation_matrix_m3[var_order, var_order]
canonical_m4 <- correlation_matrix_m4[var_order, var_order]
canonical_m5 <- correlation_matrix_m5[var_order, var_order]
canonical_pm1 <- correlation_matrix_pm1[var_order, var_order]
canonical_pm2 <- correlation_matrix_pm2[var_order, var_order]
canonical_pm3 <- correlation_matrix_pm3[var_order, var_order]
canonical_pm4 <- correlation_matrix_pm4[var_order, var_order]
canonical_pm5 <- correlation_matrix_pm5[var_order, var_order]

m_matrices <- array(
    c(
        canonical_m1,
        canonical_m2,
        canonical_m3,
        canonical_m4,
        canonical_m5
    ),
    dim = c(dim(canonical_m1), 5)
)
# Element-wise means and variances
m_means <- apply(m_matrices, c(1, 2), mean)
m_vars <- apply(m_matrices, c(1, 2), var)
colnames(m_means) <- colnames(canonical_m1)
rownames(m_means) <- rownames(canonical_m1)
colnames(m_vars) <- colnames(canonical_m1)
rownames(m_vars) <- rownames(canonical_m1)

pm_matrices <- array(
    c(
        canonical_pm1,
        canonical_pm2,
        canonical_pm3,
        canonical_pm4,
        canonical_pm5
    ),
    dim = c(dim(canonical_pm1), 5)
)
pm_means <- apply(pm_matrices, c(1, 2), mean)
pm_vars <- apply(pm_matrices, c(1, 2), var)
colnames(pm_means) <- colnames(canonical_pm1)
rownames(pm_means) <- rownames(canonical_pm1)
colnames(pm_vars) <- colnames(canonical_pm1)
rownames(pm_vars) <- rownames(canonical_pm1)

# Average of the mtbi correlations
save_png(
    ComplexHeatmap::Heatmap(m_means),
    fig_path("correlation_heatmap_m_means.png", TRUE),
    width = 2500,
    height = 2500
)

# Average of the pooled correlations
save_png(
    ComplexHeatmap::Heatmap(pm_means),
    fig_path("correlation_heatmap_pm_means.png", TRUE),
    width = 2500,
    height = 2500
)

# Very small difference in correlations
max(abs(m_means - pm_means)) # 0.0610264

# Very small variances
max(abs(m_vars)) # 0.002426604
max(abs(pm_vars)) # 0.02360992

# Difference in correlations between the two groups
save_png(
    ComplexHeatmap::Heatmap(m_means - pm_means),
    fig_path("difference_in_correlations_m_vs_pm.png", TRUE),
    width = 2500,
    height = 2500
)

# Difference in absolute correlations between the two groups
save_png(
    ComplexHeatmap::Heatmap(abs(m_means) - abs(pm_means)),
    fig_path("difference_in_abs_correlations_m_vs_pm.png", TRUE),
    width = 2500,
    height = 2500
)

```
