# Pre-imputation Data Exploration

```{r}
library(ggplot2)
library(readr)
library(dplyr)
library(here)
library(abcdutils)
library(ComplexUpset)
library(fastDummies)
library(patchwork)

core_path <- path_maker(here(paste0("data/abcd/core")))
input_path <- path_maker(here(paste0("data/abcd/inputs")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))

import <- function(path) {
    return(abcd_load(core_path(path)))
}

mtbi_subjects <- read_subjects(sub_path("2024_07_31_mtbi_subjects.csv"))
uninjured_subjects <- read_subjects(sub_path("2024_07_31_uninjured_subjects.csv"))
```

## Sex and Gender

The purpose of this subsection is to examine the distribution of children by their parent-reported genders and sexes at baseline with their own self-reported genders and sexes at the 3-year follow-up timepoint.

```{r}
gish_p_gi <- import("gender-identity-sexual-health/gish_p_gi.csv")
gish_y_gi <- import("gender-identity-sexual-health/gish_y_gi.csv")

mtbi_y_sex <- gish_y_gi |>
    filter_subjects(mtbi_subjects) |>
    filter_timepoint(t = 3) |>
    dplyr::select(
        subjectkey,
        kbi_sex_assigned_at_birth
    ) |>
    dplyr::rename(
        "y_sex" = "kbi_sex_assigned_at_birth"
    ) |>
    dplyr::mutate(group = "mtbi", t = 3) |>
    dplyr::mutate(
        y_sex = dplyr::case_when(
            y_sex == 1 ~ "M",
            y_sex == 2 ~ "F",
            TRUE ~ NA
        )
    )

uninj_y_sex <- gish_y_gi |>
    filter_subjects(uninjured_subjects) |>
    filter_timepoint(t = 3) |>
    dplyr::select(
        subjectkey,
        kbi_sex_assigned_at_birth
    ) |>
    dplyr::rename(
        "y_sex" = "kbi_sex_assigned_at_birth"
    ) |>
    dplyr::mutate(group = "uninj", t = 3) |>
    dplyr::mutate(
        y_sex = dplyr::case_when(
            y_sex == 1 ~ "M",
            y_sex == 2 ~ "F",
            TRUE ~ NA
        )
    )

mtbi_p_sex <- get_sex(
    gish_p_gi,
    mtbi_subjects,
    t = 0,
    as_numeric = FALSE,
    only_m_f = FALSE
) |>
    dplyr::mutate(group = "mtbi", t = 0)

uninj_p_sex <- get_sex(
    gish_p_gi,
    uninjured_subjects,
    t = 0,
    as_numeric = FALSE,
    only_m_f = FALSE
) |>
    dplyr::mutate(group = "uninj", t = 0)

mtbi_y_gender <- get_y_gender(
    gish_y_gi,
    mtbi_subjects,
    t = 3
) |>
    dplyr::mutate(group = "mtbi", t = 3)

uninj_y_gender <- get_y_gender(
    gish_y_gi,
    uninjured_subjects,
    t = 3
) |>
    dplyr::mutate(group = "uninj", t = 3)

mtbi_p_gender <- get_p_gender(
    gish_p_gi,
    mtbi_subjects,
    t = 0,
    match_y_report = TRUE
) |>
    dplyr::mutate(group = "mtbi", t = 0)

uninj_p_gender <- get_p_gender(
    gish_p_gi,
    uninjured_subjects,
    t = 0,
    match_y_report = TRUE
) |>
    dplyr::mutate(group = "uninj", t = 0)

y_sex <- rbind(mtbi_y_sex, uninj_y_sex)
y_gender <- rbind(mtbi_y_gender, uninj_y_gender)
p_sex <- rbind(mtbi_p_sex, uninj_p_sex)
p_gender <- rbind(mtbi_p_gender, uninj_p_gender)

y_report <- dplyr::full_join(y_sex, y_gender) |>
    dplyr::select(-t)

p_report <- dplyr::full_join(p_sex, p_gender) |>
    dplyr::rename("p_sex" = "sex") |>
    dplyr::select(-t)

sex_and_gender <- dplyr::full_join(
    y_report,
    p_report
)

sex_and_gender[is.na(sex_and_gender)] <- "NA"

sex_and_gender <- sex_and_gender |>
    dummy_cols(
        select_columns = c("y_sex", "y_gender", "p_sex", "p_gender"),
        remove_selected_columns = TRUE
    ) |>
    tibble()

sex_and_gender_mtbi <- sex_and_gender |>
    dplyr::filter(group == "mtbi")  |>
    dplyr::select(-group)

sex_and_gender_uninj <- sex_and_gender |>
    dplyr::filter(group == "uninj")  |>
    dplyr::select(-group)
```

### Gender Upset Plots

```{r}
gender_sets <- c(
    "p_gender_NB",
    "p_gender_NA",
    "y_gender_NB",
    "y_gender_NA",
    "y_gender_F",
    "y_gender_M",
    "p_gender_F",
    "p_gender_M"
)

gender_ints <- list(
    c("p_gender_M", "y_gender_M"),
    c("p_gender_F", "y_gender_F"),
    c("p_gender_F", "y_gender_NA"),
    c("p_gender_M", "y_gender_NA"),
    c("p_gender_F", "y_gender_NB"),
    c("p_gender_F", "y_gender_M"),
    c("p_gender_M", "y_gender_NB"),
    c("p_gender_M", "y_gender_F"),
    c("p_gender_NA", "y_gender_F"),
    c("p_gender_NA", "y_gender_M"),
    c("p_gender_NA", "y_gender_NB"),
    c("p_gender_NA", "y_gender_NA"),
    c("p_gender_NB", "y_gender_F"),
    c("p_gender_NB", "y_gender_NA"),
    c("p_gender_NB", "y_gender_NB")
)

uninj_gender_upset <- upset(
    sex_and_gender_uninj,
    gender_sets,
    intersections = gender_ints,
    name = "",
    sort_sets = FALSE,
    sort_intersections = FALSE
) +
    ggtitle("Uninjured") +
    theme(text = element_text(size = 14))

mtbi_gender_upset <- upset(
    sex_and_gender_mtbi,
    gender_sets,
    intersections = gender_ints,
    name = "Gender Identity",
    sort_sets = FALSE,
    sort_intersections = FALSE
) +
    ggtitle("mTBI") +
    theme(text = element_text(size = 14))

gender_upset_plots <- uninj_gender_upset / mtbi_gender_upset

gender_upset_plots

pdf(fig_path("gender_upset_plots.pdf", TRUE), width = 10, height = 10)
print(gender_upset_plots)
dev.off()
```

### Sex Upset Plots

```{r}
sex_sets <- c(
    "p_sex_IM",
    "y_sex_NA",
    "y_sex_F",
    "y_sex_M",
    "p_sex_F",
    "p_sex_M"
)

sex_ints <- list(
    c("p_sex_M", "y_sex_M"),
    c("p_sex_F", "y_sex_F"),
    c("p_sex_M", "y_sex_NA"),
    c("p_sex_F", "y_sex_NA"),
    c("p_sex_M", "y_sex_F"),
    c("p_sex_F", "y_sex_M"),
    c("y_sex_M", "p_sex_IM")
)

mtbi_sex_upset <- upset(
    sex_and_gender_mtbi,
    sex_sets,
    intersections = sex_ints,
    name = "Sex at Birth",
    sort_sets = FALSE,
    sort_intersections = FALSE
) +
    ggtitle("mTBI") +
    theme(text = element_text(size = 14))
uninj_sex_upset <- upset(
    sex_and_gender_uninj,
    sex_sets,
    intersections = sex_ints,
    name = "Sex at Birth",
    sort_sets = FALSE,
    sort_intersections = FALSE
) +
    ggtitle("Uninjured") +
    theme(text = element_text(size = 14))
sex_upset_plots <- uninj_sex_upset / mtbi_sex_upset

sex_upset_plots

pdf(fig_path("sex_upset_plots.pdf", TRUE), width = 10, height = 10)
print(sex_upset_plots)
dev.off()
```

### Parent Report Upset Plots

```{r}

parent_sets <- c(
    "p_gender_NB",
    "p_gender_NA",
    "p_gender_F",
    "p_gender_M",
    "p_sex_IM",
    "p_sex_F",
    "p_sex_M"
)

parent_ints <- list(
    c("p_sex_M", "p_gender_M"),
    c("p_sex_F", "p_gender_F"),
    c("p_sex_F", "p_gender_NA"),
    c("p_sex_M", "p_gender_NB"),
    c("p_sex_F", "p_gender_NB"),
    c("p_gender_M", "p_sex_IM"),
    c("p_sex_M", "p_gender_F"), 
    c("p_sex_M", "p_gender_NA"), 
    c("p_gender_M", "p_sex_F")
)

mtbi_parent_sag <- upset(
    sex_and_gender_mtbi,
    intersect = parent_sets,
    intersections = parent_ints,
    set_sizes = FALSE,
    sort_sets = FALSE,
    sort_intersections = FALSE
) +
    ggtitle("mTBI") +
    theme(text = element_text(size = 14))

uninj_parent_sag <- upset(
    sex_and_gender_uninj,
    intersect = parent_sets,
    intersections = parent_ints,
    set_sizes = FALSE,
    sort_sets = FALSE,
    sort_intersections = FALSE
) +
    ggtitle("Uninjured") +
    theme(text = element_text(size = 14))

parent_sag <- wrap_plots(
    list(
        uninj_parent_sag,
        mtbi_parent_sag
    ),
    ncol = 1
)

pdf(fig_path("parent_sag", TRUE), width = 10, height = 10)
print(parent_sag)
dev.off()

```

```{r}

youth_sets <- c(
    "y_gender_NB",
    "y_gender_NA",
    "y_gender_F",
    "y_gender_M",
    "y_sex_NA",
    "y_sex_F",
    "y_sex_M"
)

youth_ints <- list(
    c("y_sex_M", "y_gender_M"),
    c("y_sex_F", "y_gender_F"),
    c("y_sex_NA", "y_gender_NA"), 
    c("y_sex_F", "y_gender_NB"),
    c("y_gender_M", "y_sex_NA"),
    c("y_gender_F", "y_sex_NA"),
    c("y_sex_F", "y_gender_NA"),
    c("y_gender_M", "y_sex_F"),
    c("y_sex_M", "y_gender_NA"),
    c("y_sex_M", "y_gender_NB"),
    c("y_sex_M", "y_gender_F")
)

mtbi_youth_sag <- upset(
    sex_and_gender_mtbi,
    intersect = youth_sets,
    intersections = youth_ints,
    set_sizes = FALSE,
    sort_sets = FALSE,
    sort_intersections = FALSE
) +
    ggtitle("mTBI") +
    theme(text = element_text(size = 14))

uninj_youth_sag <- upset(
    sex_and_gender_uninj,
    intersect = youth_sets,
    intersections = youth_ints,
    set_sizes = FALSE,
    sort_sets = FALSE,
    sort_intersections = FALSE
) +
    ggtitle("Uninjured") +
    theme(text = element_text(size = 14))

youth_sag <- wrap_plots(
    list(
        uninj_youth_sag,
        mtbi_youth_sag
    ),
    ncol = 1
)

age_split_sag <- wrap_plots(
    list(parent_sag, youth_sag),
    nrow = 2, ncol = 2
)

pdf(fig_path("age_split_sag.pdf", TRUE), width = 20, height = 20)
print(age_split_sag)
dev.off()
```

## Other features

```{r}
as_mem_daze_mtbi <- read("2024_07_31_as_mem_daze_mtbi.csv")
as_mechanism_mtbi <- read("2024_07_31_as_mechanism_mtbi.csv")
as_loc_mtbi <- read("2024_07_31_as_loc_mtbi.csv")
d_interview_age_mtbi <- read("2024_07_31_d_interview_age_mtbi.csv")
d_mtbi_age_mtbi <- read("2024_07_31_d_mtbi_age_mtbi.csv")
d_sex_mtbi <- read("2024_07_31_d_sex_mtbi.csv")
d_income_mtbi <- read("2024_07_31_d_income_mtbi.csv")
d_race_mtbi <- read("2024_07_31_d_race_mtbi.csv")
d_pubertal_status_mtbi <- read("2024_07_31_d_pubertal_status_mtbi.csv")
mh_headaches_mtbi <- read("2024_07_31_mh_headaches_mtbi.csv")
mh_mtbi_count_mtbi <- read("2024_07_31_mh_mtbi_count_mtbi.csv")
sm_subc_v_mtbi <- read("2024_07_31_sm_subc_v_mtbi.csv")
sm_cort_t_mtbi <- read("2024_07_31_sm_cort_t_mtbi.csv")
sm_cort_sa_mtbi <- read("2024_07_31_sm_cort_sa_mtbi.csv")
dm_all_wmnd_mtbi <- read("2024_07_31_dm_all_wmnd_mtbi.csv")
rm_gord_cor_mtbi <- read("2024_07_31_rm_gord_cor_mtbi.csv")
rm_subc_cor_mtbi <- read("2024_07_31_rm_subc_cor_mtbi.csv")
p_loneliness_mtbi <- read("2024_07_31_p_loneliness_mtbi.csv")
p_screen_time_mtbi <- read("2024_07_31_p_screen_time_mtbi.csv")
p_sports_mtbi <- read("2024_07_31_p_sports_mtbi.csv")
p_exercise_mtbi <- read("2024_07_31_p_exercise_mtbi.csv")
p_prosocial_mtbi <- read("2024_07_31_p_prosocial_mtbi.csv")
p_fam_fn_mtbi <- read("2024_07_31_p_fam_fn_mtbi.csv")
p_parent_psych_mtbi <- read("2024_07_31_p_parent_psych_mtbi.csv")
cbcl_anxdep_mtbi <- read("2024_07_31_cbcl_anxdep_mtbi.csv")
cbcl_withdep_mtbi <- read("2024_07_31_cbcl_withdep_mtbi.csv")
cbcl_somatic_mtbi <- read("2024_07_31_cbcl_somatic_mtbi.csv")
cbcl_social_mtbi <- read("2024_07_31_cbcl_social_mtbi.csv")
cbcl_thought_mtbi <- read("2024_07_31_cbcl_thought_mtbi.csv")
cbcl_attention_mtbi <- read("2024_07_31_cbcl_attention_mtbi.csv")
cbcl_rulebreak_mtbi <- read("2024_07_31_cbcl_rulebreak_mtbi.csv")
cbcl_aggressive_mtbi <- read("2024_07_31_cbcl_aggressive_mtbi.csv")
sds_total_probs_mtbi <- read("2024_07_31_sds_total_probs_mtbi.csv")

# Uninjured subjects
d_interview_age_uninj <- read("2024_07_31_d_interview_age_uninj.csv")
d_sex_uninj <- read("2024_07_31_d_sex_uninj.csv")
d_income_uninj <- read("2024_07_31_d_income_uninj.csv")
d_race_uninj <- read("2024_07_31_d_race_uninj.csv")
d_pubertal_status_uninj <- read("2024_07_31_d_pubertal_status_uninj.csv")
mh_headaches_uninj <- read("2024_07_31_mh_headaches_uninj.csv")
sm_subc_v_uninj <- read("2024_07_31_sm_subc_v_uninj.csv")
sm_cort_t_uninj <- read("2024_07_31_sm_cort_t_uninj.csv")
sm_cort_sa_uninj <- read("2024_07_31_sm_cort_sa_uninj.csv")
dm_all_wmnd_uninj <- read("2024_07_31_dm_all_wmnd_uninj.csv")
rm_gord_cor_uninj <- read("2024_07_31_rm_gord_cor_uninj.csv")
rm_subc_cor_uninj <- read("2024_07_31_rm_subc_cor_uninj.csv")
p_loneliness_uninj <- read("2024_07_31_p_loneliness_uninj.csv")
p_screen_time_uninj <- read("2024_07_31_p_screen_time_uninj.csv")
p_sports_uninj <- read("2024_07_31_p_sports_uninj.csv")
p_exercise_uninj <- read("2024_07_31_p_exercise_uninj.csv")
p_prosocial_uninj <- read("2024_07_31_p_prosocial_uninj.csv")
p_fam_fn_uninj <- read("2024_07_31_p_fam_fn_uninj.csv")
p_parent_psych_uninj <- read("2024_07_31_p_parent_psych_uninj.csv")
cbcl_anxdep_uninj <- read("2024_07_31_cbcl_anxdep_uninj.csv")
cbcl_withdep_uninj <- read("2024_07_31_cbcl_withdep_uninj.csv")
cbcl_somatic_uninj <- read("2024_07_31_cbcl_somatic_uninj.csv")
cbcl_social_uninj <- read("2024_07_31_cbcl_social_uninj.csv")
cbcl_thought_uninj <- read("2024_07_31_cbcl_thought_uninj.csv")
cbcl_attention_uninj <- read("2024_07_31_cbcl_attention_uninj.csv")
cbcl_rulebreak_uninj <- read("2024_07_31_cbcl_rulebreak_uninj.csv")
cbcl_aggressive_uninj <- read("2024_07_31_cbcl_aggressive_uninj.csv")
sds_total_probs_uninj <- read("2024_07_31_sds_total_probs_uninj.csv")
```

## mTBI vs. Uninj Initial Comparisons

```{r}
mtbi_initial_df_list <- list(
    as_mem_daze_mtbi,
    as_mechanism_mtbi,
    as_loc_mtbi,
    d_interview_age_mtbi,
    d_mtbi_age_mtbi,
    d_sex_mtbi,
    d_income_mtbi,
    d_race_mtbi,
    d_pubertal_status_mtbi,
    mh_headaches_mtbi,
    mh_mtbi_count_mtbi,
    sm_subc_v_mtbi,
    sm_cort_t_mtbi,
    sm_cort_sa_mtbi,
    dm_all_wmnd_mtbi,
    rm_gord_cor_mtbi,
    rm_subc_cor_mtbi,
    p_loneliness_mtbi,
    p_screen_time_mtbi,
    p_sports_mtbi,
    p_exercise_mtbi,
    p_prosocial_mtbi,
    p_fam_fn_mtbi,
    p_parent_psych_mtbi,
    cbcl_anxdep_mtbi,
    cbcl_withdep_mtbi,
    cbcl_somatic_mtbi,
    cbcl_social_mtbi,
    cbcl_thought_mtbi,
    cbcl_attention_mtbi,
    cbcl_rulebreak_mtbi,
    cbcl_aggressive_mtbi,
    sds_total_probs_mtbi
)

uninj_initial_df_list <- list(
    d_interview_age_uninj,
    d_sex_uninj,
    d_income_uninj,
    d_race_uninj,
    d_pubertal_status_uninj,
    mh_headaches_uninj,
    sm_subc_v_uninj,
    sm_cort_t_uninj,
    sm_cort_sa_uninj,
    dm_all_wmnd_uninj,
    rm_gord_cor_uninj,
    rm_subc_cor_uninj,
    p_loneliness_uninj,
    p_screen_time_uninj,
    p_sports_uninj,
    p_exercise_uninj,
    p_prosocial_uninj,
    p_fam_fn_uninj,
    p_parent_psych_uninj,
    cbcl_anxdep_uninj,
    cbcl_withdep_uninj,
    cbcl_somatic_uninj,
    cbcl_social_uninj,
    cbcl_thought_uninj,
    cbcl_attention_uninj,
    cbcl_rulebreak_uninj,
    cbcl_aggressive_uninj,
    sds_total_probs_uninj
)

mtbi_initial_df <- merge_df_list(mtbi_initial_df_list, join = "full")
uninj_initial_df <- merge_df_list(uninj_initial_df_list, join = "full")

nrow(mtbi_initial_df)

baseline_initial_df <- bind_rows(mtbi_initial_df, uninj_initial_df)

expect it is all diffuse global is fine
```
