# Similarity Network Fusion

In this chapter, I use the `metasnf` package to generate many diverse subtyping solutions with SNF.

## Data set-up

In the previous chapter, we set up the following datasets:

* 1 original unimputed mTBI dataset
* 1 original unimputed uninjured dataset
* 5 imputed mTBI datasets
* 5 imputed uninjured datasets
* 5 imputed mTBI + uninjured datasets

To keep track of what data we're working with, variables will have the following notation: (m/u/p)(0-5), where m represented mTBI data, u represents uninjured data, p for pooled data, 0 indicating original (unimputed) data, and 1-5 indicating the imputed dataset number.

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subjects <- read_csv(sub_path("2023_11_07_mtbi_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2023_11_07_uninjured_subjects.csv"))

as_mem_daze_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_as_mem_daze_mtbi_train_imp_1.csv"))
as_mechanism_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_as_mechanism_mtbi_train_imp_1.csv"))
as_loc_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_as_loc_mtbi_train_imp_1.csv"))
d_interview_age_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_d_interview_age_mtbi_train_imp_1.csv"))
d_mtbi_age_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_d_mtbi_age_mtbi_train_imp_1.csv"))
d_sex_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_d_sex_mtbi_train_imp_1.csv"))
d_income_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_d_income_mtbi_train_imp_1.csv"))
d_race_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_d_race_mtbi_train_imp_1.csv"))
d_pubertal_status_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_d_pubertal_status_mtbi_train_imp_1.csv"))
mh_headaches_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_mh_headaches_mtbi_train_imp_1.csv"))
mh_mtbi_count_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_mh_mtbi_count_mtbi_train_imp_1.csv"))
sm_subc_v_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_sm_subc_v_mtbi_train_imp_1.csv"))
sm_cort_t_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_sm_cort_t_mtbi_train_imp_1.csv"))
sm_cort_sa_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_sm_cort_sa_mtbi_train_imp_1.csv"))
dm_all_wmnd_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_dm_all_wmnd_mtbi_train_imp_1.csv"))
rm_gord_cor_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_rm_gord_cor_mtbi_train_imp_1.csv"))
rm_subc_cor_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_rm_subc_cor_mtbi_train_imp_1.csv"))
p_loneliness_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_p_loneliness_mtbi_train_imp_1.csv"))
p_screen_time_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_p_screen_time_mtbi_train_imp_1.csv"))
p_sports_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_p_sports_mtbi_train_imp_1.csv"))
p_exercise_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_p_exercise_mtbi_train_imp_1.csv"))
p_prosocial_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_p_prosocial_mtbi_train_imp_1.csv"))
p_fam_fn_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_p_fam_fn_mtbi_train_imp_1.csv"))
p_parent_psych_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_p_parent_psych_mtbi_train_imp_1.csv"))
t_cbcl_anxdep_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_t_cbcl_anxdep_mtbi_train_imp_1.csv"))
t_cbcl_withdep_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_t_cbcl_withdep_mtbi_train_imp_1.csv"))
t_cbcl_somatic_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_t_cbcl_somatic_mtbi_train_imp_1.csv"))
t_cbcl_social_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_t_cbcl_social_mtbi_train_imp_1.csv"))
t_cbcl_thought_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_t_cbcl_thought_mtbi_train_imp_1.csv"))
t_cbcl_attention_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_t_cbcl_attention_mtbi_train_imp_1.csv"))
t_cbcl_rulebreak_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_t_cbcl_rulebreak_mtbi_train_imp_1.csv"))
t_cbcl_aggressive_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_t_cbcl_aggressive_mtbi_train_imp_1.csv"))
sds_total_probs_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_sds_total_probs_mtbi_train_imp_1.csv"))

as_mem_daze_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_as_mem_daze_mtbi_train_imp_2.csv"))
as_mechanism_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_as_mechanism_mtbi_train_imp_2.csv"))
as_loc_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_as_loc_mtbi_train_imp_2.csv"))
d_interview_age_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_d_interview_age_mtbi_train_imp_2.csv"))
d_mtbi_age_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_d_mtbi_age_mtbi_train_imp_2.csv"))
d_sex_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_d_sex_mtbi_train_imp_2.csv"))
d_income_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_d_income_mtbi_train_imp_2.csv"))
d_race_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_d_race_mtbi_train_imp_2.csv"))
d_pubertal_status_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_d_pubertal_status_mtbi_train_imp_2.csv"))
mh_headaches_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_mh_headaches_mtbi_train_imp_2.csv"))
mh_mtbi_count_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_mh_mtbi_count_mtbi_train_imp_2.csv"))
sm_subc_v_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_sm_subc_v_mtbi_train_imp_2.csv"))
sm_cort_t_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_sm_cort_t_mtbi_train_imp_2.csv"))
sm_cort_sa_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_sm_cort_sa_mtbi_train_imp_2.csv"))
dm_all_wmnd_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_dm_all_wmnd_mtbi_train_imp_2.csv"))
rm_gord_cor_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_rm_gord_cor_mtbi_train_imp_2.csv"))
rm_subc_cor_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_rm_subc_cor_mtbi_train_imp_2.csv"))
p_loneliness_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_p_loneliness_mtbi_train_imp_2.csv"))
p_screen_time_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_p_screen_time_mtbi_train_imp_2.csv"))
p_sports_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_p_sports_mtbi_train_imp_2.csv"))
p_exercise_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_p_exercise_mtbi_train_imp_2.csv"))
p_prosocial_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_p_prosocial_mtbi_train_imp_2.csv"))
p_fam_fn_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_p_fam_fn_mtbi_train_imp_2.csv"))
p_parent_psych_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_p_parent_psych_mtbi_train_imp_2.csv"))
t_cbcl_anxdep_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_t_cbcl_anxdep_mtbi_train_imp_2.csv"))
t_cbcl_withdep_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_t_cbcl_withdep_mtbi_train_imp_2.csv"))
t_cbcl_somatic_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_t_cbcl_somatic_mtbi_train_imp_2.csv"))
t_cbcl_social_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_t_cbcl_social_mtbi_train_imp_2.csv"))
t_cbcl_thought_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_t_cbcl_thought_mtbi_train_imp_2.csv"))
t_cbcl_attention_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_t_cbcl_attention_mtbi_train_imp_2.csv"))
t_cbcl_rulebreak_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_t_cbcl_rulebreak_mtbi_train_imp_2.csv"))
t_cbcl_aggressive_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_t_cbcl_aggressive_mtbi_train_imp_2.csv"))
sds_total_probs_mtbi_train_imp_2 <- read_csv(input_path("2023_12_01_sds_total_probs_mtbi_train_imp_2.csv"))

as_mem_daze_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_as_mem_daze_mtbi_train_imp_3.csv"))
as_mechanism_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_as_mechanism_mtbi_train_imp_3.csv"))
as_loc_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_as_loc_mtbi_train_imp_3.csv"))
d_interview_age_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_d_interview_age_mtbi_train_imp_3.csv"))
d_mtbi_age_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_d_mtbi_age_mtbi_train_imp_3.csv"))
d_sex_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_d_sex_mtbi_train_imp_3.csv"))
d_income_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_d_income_mtbi_train_imp_3.csv"))
d_race_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_d_race_mtbi_train_imp_3.csv"))
d_pubertal_status_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_d_pubertal_status_mtbi_train_imp_3.csv"))
mh_headaches_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_mh_headaches_mtbi_train_imp_3.csv"))
mh_mtbi_count_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_mh_mtbi_count_mtbi_train_imp_3.csv"))
sm_subc_v_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_sm_subc_v_mtbi_train_imp_3.csv"))
sm_cort_t_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_sm_cort_t_mtbi_train_imp_3.csv"))
sm_cort_sa_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_sm_cort_sa_mtbi_train_imp_3.csv"))
dm_all_wmnd_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_dm_all_wmnd_mtbi_train_imp_3.csv"))
rm_gord_cor_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_rm_gord_cor_mtbi_train_imp_3.csv"))
rm_subc_cor_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_rm_subc_cor_mtbi_train_imp_3.csv"))
p_loneliness_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_p_loneliness_mtbi_train_imp_3.csv"))
p_screen_time_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_p_screen_time_mtbi_train_imp_3.csv"))
p_sports_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_p_sports_mtbi_train_imp_3.csv"))
p_exercise_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_p_exercise_mtbi_train_imp_3.csv"))
p_prosocial_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_p_prosocial_mtbi_train_imp_3.csv"))
p_fam_fn_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_p_fam_fn_mtbi_train_imp_3.csv"))
p_parent_psych_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_p_parent_psych_mtbi_train_imp_3.csv"))
t_cbcl_anxdep_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_t_cbcl_anxdep_mtbi_train_imp_3.csv"))
t_cbcl_withdep_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_t_cbcl_withdep_mtbi_train_imp_3.csv"))
t_cbcl_somatic_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_t_cbcl_somatic_mtbi_train_imp_3.csv"))
t_cbcl_social_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_t_cbcl_social_mtbi_train_imp_3.csv"))
t_cbcl_thought_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_t_cbcl_thought_mtbi_train_imp_3.csv"))
t_cbcl_attention_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_t_cbcl_attention_mtbi_train_imp_3.csv"))
t_cbcl_rulebreak_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_t_cbcl_rulebreak_mtbi_train_imp_3.csv"))
t_cbcl_aggressive_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_t_cbcl_aggressive_mtbi_train_imp_3.csv"))
sds_total_probs_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_sds_total_probs_mtbi_train_imp_3.csv"))

as_mem_daze_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_as_mem_daze_mtbi_train_imp_3.csv"))
as_mechanism_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_as_mechanism_mtbi_train_imp_3.csv"))
as_loc_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_as_loc_mtbi_train_imp_3.csv"))
d_interview_age_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_d_interview_age_mtbi_train_imp_3.csv"))
d_mtbi_age_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_d_mtbi_age_mtbi_train_imp_3.csv"))
d_sex_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_d_sex_mtbi_train_imp_3.csv"))
d_income_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_d_income_mtbi_train_imp_3.csv"))
d_race_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_d_race_mtbi_train_imp_3.csv"))
d_pubertal_status_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_d_pubertal_status_mtbi_train_imp_3.csv"))
mh_headaches_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_mh_headaches_mtbi_train_imp_3.csv"))
mh_mtbi_count_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_mh_mtbi_count_mtbi_train_imp_3.csv"))
sm_subc_v_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_sm_subc_v_mtbi_train_imp_3.csv"))
sm_cort_t_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_sm_cort_t_mtbi_train_imp_3.csv"))
sm_cort_sa_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_sm_cort_sa_mtbi_train_imp_3.csv"))
dm_all_wmnd_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_dm_all_wmnd_mtbi_train_imp_3.csv"))
rm_gord_cor_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_rm_gord_cor_mtbi_train_imp_3.csv"))
rm_subc_cor_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_rm_subc_cor_mtbi_train_imp_3.csv"))
p_loneliness_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_p_loneliness_mtbi_train_imp_3.csv"))
p_screen_time_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_p_screen_time_mtbi_train_imp_3.csv"))
p_sports_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_p_sports_mtbi_train_imp_3.csv"))
p_exercise_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_p_exercise_mtbi_train_imp_3.csv"))
p_prosocial_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_p_prosocial_mtbi_train_imp_3.csv"))
p_fam_fn_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_p_fam_fn_mtbi_train_imp_3.csv"))
p_parent_psych_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_p_parent_psych_mtbi_train_imp_3.csv"))
t_cbcl_anxdep_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_t_cbcl_anxdep_mtbi_train_imp_3.csv"))
t_cbcl_withdep_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_t_cbcl_withdep_mtbi_train_imp_3.csv"))
t_cbcl_somatic_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_t_cbcl_somatic_mtbi_train_imp_3.csv"))
t_cbcl_social_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_t_cbcl_social_mtbi_train_imp_3.csv"))
t_cbcl_thought_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_t_cbcl_thought_mtbi_train_imp_3.csv"))
t_cbcl_attention_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_t_cbcl_attention_mtbi_train_imp_3.csv"))
t_cbcl_rulebreak_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_t_cbcl_rulebreak_mtbi_train_imp_3.csv"))
t_cbcl_aggressive_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_t_cbcl_aggressive_mtbi_train_imp_3.csv"))
sds_total_probs_mtbi_train_imp_3 <- read_csv(input_path("2023_12_01_sds_total_probs_mtbi_train_imp_3.csv"))

as_mem_daze_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_as_mem_daze_mtbi_train_imp_4.csv"))
as_mechanism_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_as_mechanism_mtbi_train_imp_4.csv"))
as_loc_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_as_loc_mtbi_train_imp_4.csv"))
d_interview_age_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_d_interview_age_mtbi_train_imp_4.csv"))
d_mtbi_age_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_d_mtbi_age_mtbi_train_imp_4.csv"))
d_sex_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_d_sex_mtbi_train_imp_4.csv"))
d_income_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_d_income_mtbi_train_imp_4.csv"))
d_race_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_d_race_mtbi_train_imp_4.csv"))
d_pubertal_status_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_d_pubertal_status_mtbi_train_imp_4.csv"))
mh_headaches_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_mh_headaches_mtbi_train_imp_4.csv"))
mh_mtbi_count_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_mh_mtbi_count_mtbi_train_imp_4.csv"))
sm_subc_v_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_sm_subc_v_mtbi_train_imp_4.csv"))
sm_cort_t_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_sm_cort_t_mtbi_train_imp_4.csv"))
sm_cort_sa_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_sm_cort_sa_mtbi_train_imp_4.csv"))
dm_all_wmnd_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_dm_all_wmnd_mtbi_train_imp_4.csv"))
rm_gord_cor_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_rm_gord_cor_mtbi_train_imp_4.csv"))
rm_subc_cor_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_rm_subc_cor_mtbi_train_imp_4.csv"))
p_loneliness_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_p_loneliness_mtbi_train_imp_4.csv"))
p_screen_time_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_p_screen_time_mtbi_train_imp_4.csv"))
p_sports_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_p_sports_mtbi_train_imp_4.csv"))
p_exercise_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_p_exercise_mtbi_train_imp_4.csv"))
p_prosocial_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_p_prosocial_mtbi_train_imp_4.csv"))
p_fam_fn_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_p_fam_fn_mtbi_train_imp_4.csv"))
p_parent_psych_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_p_parent_psych_mtbi_train_imp_4.csv"))
t_cbcl_anxdep_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_t_cbcl_anxdep_mtbi_train_imp_4.csv"))
t_cbcl_withdep_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_t_cbcl_withdep_mtbi_train_imp_4.csv"))
t_cbcl_somatic_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_t_cbcl_somatic_mtbi_train_imp_4.csv"))
t_cbcl_social_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_t_cbcl_social_mtbi_train_imp_4.csv"))
t_cbcl_thought_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_t_cbcl_thought_mtbi_train_imp_4.csv"))
t_cbcl_attention_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_t_cbcl_attention_mtbi_train_imp_4.csv"))
t_cbcl_rulebreak_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_t_cbcl_rulebreak_mtbi_train_imp_4.csv"))
t_cbcl_aggressive_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_t_cbcl_aggressive_mtbi_train_imp_4.csv"))
sds_total_probs_mtbi_train_imp_4 <- read_csv(input_path("2023_12_01_sds_total_probs_mtbi_train_imp_4.csv"))

as_mem_daze_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_as_mem_daze_mtbi_train_imp_5.csv"))
as_mechanism_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_as_mechanism_mtbi_train_imp_5.csv"))
as_loc_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_as_loc_mtbi_train_imp_5.csv"))
d_interview_age_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_d_interview_age_mtbi_train_imp_5.csv"))
d_mtbi_age_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_d_mtbi_age_mtbi_train_imp_5.csv"))
d_sex_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_d_sex_mtbi_train_imp_5.csv"))
d_income_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_d_income_mtbi_train_imp_5.csv"))
d_race_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_d_race_mtbi_train_imp_5.csv"))
d_pubertal_status_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_d_pubertal_status_mtbi_train_imp_5.csv"))
mh_headaches_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_mh_headaches_mtbi_train_imp_5.csv"))
mh_mtbi_count_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_mh_mtbi_count_mtbi_train_imp_5.csv"))
sm_subc_v_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_sm_subc_v_mtbi_train_imp_5.csv"))
sm_cort_t_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_sm_cort_t_mtbi_train_imp_5.csv"))
sm_cort_sa_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_sm_cort_sa_mtbi_train_imp_5.csv"))
dm_all_wmnd_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_dm_all_wmnd_mtbi_train_imp_5.csv"))
rm_gord_cor_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_rm_gord_cor_mtbi_train_imp_5.csv"))
rm_subc_cor_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_rm_subc_cor_mtbi_train_imp_5.csv"))
p_loneliness_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_p_loneliness_mtbi_train_imp_5.csv"))
p_screen_time_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_p_screen_time_mtbi_train_imp_5.csv"))
p_sports_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_p_sports_mtbi_train_imp_5.csv"))
p_exercise_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_p_exercise_mtbi_train_imp_5.csv"))
p_prosocial_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_p_prosocial_mtbi_train_imp_5.csv"))
p_fam_fn_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_p_fam_fn_mtbi_train_imp_5.csv"))
p_parent_psych_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_p_parent_psych_mtbi_train_imp_5.csv"))
t_cbcl_anxdep_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_t_cbcl_anxdep_mtbi_train_imp_5.csv"))
t_cbcl_withdep_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_t_cbcl_withdep_mtbi_train_imp_5.csv"))
t_cbcl_somatic_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_t_cbcl_somatic_mtbi_train_imp_5.csv"))
t_cbcl_social_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_t_cbcl_social_mtbi_train_imp_5.csv"))
t_cbcl_thought_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_t_cbcl_thought_mtbi_train_imp_5.csv"))
t_cbcl_attention_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_t_cbcl_attention_mtbi_train_imp_5.csv"))
t_cbcl_rulebreak_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_t_cbcl_rulebreak_mtbi_train_imp_5.csv"))
t_cbcl_aggressive_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_t_cbcl_aggressive_mtbi_train_imp_5.csv"))
sds_total_probs_mtbi_train_imp_5 <- read_csv(input_path("2023_12_01_sds_total_probs_mtbi_train_imp_5.csv"))

###############################################################################
# Pooled imputed
###############################################################################

d_interview_age_pooled_mtbi_imp_1 <- read_csv(input_path("2023_12_01_d_interview_age_pooled_imp_1.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
d_sex_pooled_mtbi_imp_1 <- read_csv(input_path("2023_12_01_d_sex_pooled_imp_1.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
d_income_pooled_mtbi_imp_1 <- read_csv(input_path("2023_12_01_d_income_pooled_imp_1.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
d_race_pooled_mtbi_imp_1 <- read_csv(input_path("2023_12_01_d_race_pooled_imp_1.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
d_pubertal_status_pooled_mtbi_imp_1 <- read_csv(input_path("2023_12_01_d_pubertal_status_pooled_imp_1.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
mh_headaches_pooled_mtbi_imp_1 <- read_csv(input_path("2023_12_01_mh_headaches_pooled_imp_1.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
sm_subc_v_pooled_mtbi_imp_1 <- read_csv(input_path("2023_12_01_sm_subc_v_pooled_imp_1.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
sm_cort_t_pooled_mtbi_imp_1 <- read_csv(input_path("2023_12_01_sm_cort_t_pooled_imp_1.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
sm_cort_sa_pooled_mtbi_imp_1 <- read_csv(input_path("2023_12_01_sm_cort_sa_pooled_imp_1.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
dm_all_wmnd_pooled_mtbi_imp_1 <- read_csv(input_path("2023_12_01_dm_all_wmnd_pooled_imp_1.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
rm_gord_cor_pooled_mtbi_imp_1 <- read_csv(input_path("2023_12_01_rm_gord_cor_pooled_imp_1.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
rm_subc_cor_pooled_mtbi_imp_1 <- read_csv(input_path("2023_12_01_rm_subc_cor_pooled_imp_1.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_loneliness_pooled_mtbi_imp_1 <- read_csv(input_path("2023_12_01_p_loneliness_pooled_imp_1.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_screen_time_pooled_mtbi_imp_1 <- read_csv(input_path("2023_12_01_p_screen_time_pooled_imp_1.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_sports_pooled_mtbi_imp_1 <- read_csv(input_path("2023_12_01_p_sports_pooled_imp_1.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_exercise_pooled_mtbi_imp_1 <- read_csv(input_path("2023_12_01_p_exercise_pooled_imp_1.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_prosocial_pooled_mtbi_imp_1 <- read_csv(input_path("2023_12_01_p_prosocial_pooled_imp_1.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_fam_fn_pooled_mtbi_imp_1 <- read_csv(input_path("2023_12_01_p_fam_fn_pooled_imp_1.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_parent_psych_pooled_mtbi_imp_1 <- read_csv(input_path("2023_12_01_p_parent_psych_pooled_imp_1.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_anxdep_pooled_mtbi_imp_1 <- read_csv(input_path("2023_12_01_t_cbcl_anxdep_pooled_imp_1.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_withdep_pooled_mtbi_imp_1 <- read_csv(input_path("2023_12_01_t_cbcl_withdep_pooled_imp_1.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_somatic_pooled_mtbi_imp_1 <- read_csv(input_path("2023_12_01_t_cbcl_somatic_pooled_imp_1.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_social_pooled_mtbi_imp_1 <- read_csv(input_path("2023_12_01_t_cbcl_social_pooled_imp_1.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_thought_pooled_mtbi_imp_1 <- read_csv(input_path("2023_12_01_t_cbcl_thought_pooled_imp_1.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_attention_pooled_mtbi_imp_1 <- read_csv(input_path("2023_12_01_t_cbcl_attention_pooled_imp_1.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_rulebreak_pooled_mtbi_imp_1 <- read_csv(input_path("2023_12_01_t_cbcl_rulebreak_pooled_imp_1.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_aggressive_pooled_mtbi_imp_1 <- read_csv(input_path("2023_12_01_t_cbcl_aggressive_pooled_imp_1.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
sds_total_probs_pooled_mtbi_imp_1 <- read_csv(input_path("2023_12_01_sds_total_probs_pooled_imp_1.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
#
d_interview_age_pooled_mtbi_imp_2 <- read_csv(input_path("2023_12_01_d_interview_age_pooled_imp_2.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
d_sex_pooled_mtbi_imp_2 <- read_csv(input_path("2023_12_01_d_sex_pooled_imp_2.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
d_income_pooled_mtbi_imp_2 <- read_csv(input_path("2023_12_01_d_income_pooled_imp_2.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
d_race_pooled_mtbi_imp_2 <- read_csv(input_path("2023_12_01_d_race_pooled_imp_2.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
d_pubertal_status_pooled_mtbi_imp_2 <- read_csv(input_path("2023_12_01_d_pubertal_status_pooled_imp_2.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
mh_headaches_pooled_mtbi_imp_2 <- read_csv(input_path("2023_12_01_mh_headaches_pooled_imp_2.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
sm_subc_v_pooled_mtbi_imp_2 <- read_csv(input_path("2023_12_01_sm_subc_v_pooled_imp_2.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
sm_cort_t_pooled_mtbi_imp_2 <- read_csv(input_path("2023_12_01_sm_cort_t_pooled_imp_2.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
sm_cort_sa_pooled_mtbi_imp_2 <- read_csv(input_path("2023_12_01_sm_cort_sa_pooled_imp_2.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
dm_all_wmnd_pooled_mtbi_imp_2 <- read_csv(input_path("2023_12_01_dm_all_wmnd_pooled_imp_2.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
rm_gord_cor_pooled_mtbi_imp_2 <- read_csv(input_path("2023_12_01_rm_gord_cor_pooled_imp_2.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
rm_subc_cor_pooled_mtbi_imp_2 <- read_csv(input_path("2023_12_01_rm_subc_cor_pooled_imp_2.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_loneliness_pooled_mtbi_imp_2 <- read_csv(input_path("2023_12_01_p_loneliness_pooled_imp_2.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_screen_time_pooled_mtbi_imp_2 <- read_csv(input_path("2023_12_01_p_screen_time_pooled_imp_2.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_sports_pooled_mtbi_imp_2 <- read_csv(input_path("2023_12_01_p_sports_pooled_imp_2.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_exercise_pooled_mtbi_imp_2 <- read_csv(input_path("2023_12_01_p_exercise_pooled_imp_2.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_prosocial_pooled_mtbi_imp_2 <- read_csv(input_path("2023_12_01_p_prosocial_pooled_imp_2.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_fam_fn_pooled_mtbi_imp_2 <- read_csv(input_path("2023_12_01_p_fam_fn_pooled_imp_2.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_parent_psych_pooled_mtbi_imp_2 <- read_csv(input_path("2023_12_01_p_parent_psych_pooled_imp_2.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_anxdep_pooled_mtbi_imp_2 <- read_csv(input_path("2023_12_01_t_cbcl_anxdep_pooled_imp_2.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_withdep_pooled_mtbi_imp_2 <- read_csv(input_path("2023_12_01_t_cbcl_withdep_pooled_imp_2.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_somatic_pooled_mtbi_imp_2 <- read_csv(input_path("2023_12_01_t_cbcl_somatic_pooled_imp_2.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_social_pooled_mtbi_imp_2 <- read_csv(input_path("2023_12_01_t_cbcl_social_pooled_imp_2.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_thought_pooled_mtbi_imp_2 <- read_csv(input_path("2023_12_01_t_cbcl_thought_pooled_imp_2.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_attention_pooled_mtbi_imp_2 <- read_csv(input_path("2023_12_01_t_cbcl_attention_pooled_imp_2.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_rulebreak_pooled_mtbi_imp_2 <- read_csv(input_path("2023_12_01_t_cbcl_rulebreak_pooled_imp_2.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_aggressive_pooled_mtbi_imp_2 <- read_csv(input_path("2023_12_01_t_cbcl_aggressive_pooled_imp_2.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
sds_total_probs_pooled_mtbi_imp_2 <- read_csv(input_path("2023_12_01_sds_total_probs_pooled_imp_2.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
#
d_interview_age_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_d_interview_age_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
d_sex_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_d_sex_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
d_income_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_d_income_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
d_race_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_d_race_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
d_pubertal_status_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_d_pubertal_status_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
mh_headaches_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_mh_headaches_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
sm_subc_v_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_sm_subc_v_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
sm_cort_t_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_sm_cort_t_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
sm_cort_sa_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_sm_cort_sa_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
dm_all_wmnd_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_dm_all_wmnd_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
rm_gord_cor_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_rm_gord_cor_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
rm_subc_cor_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_rm_subc_cor_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_loneliness_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_p_loneliness_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_screen_time_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_p_screen_time_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_sports_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_p_sports_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_exercise_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_p_exercise_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_prosocial_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_p_prosocial_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_fam_fn_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_p_fam_fn_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_parent_psych_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_p_parent_psych_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_anxdep_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_t_cbcl_anxdep_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_withdep_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_t_cbcl_withdep_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_somatic_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_t_cbcl_somatic_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_social_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_t_cbcl_social_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_thought_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_t_cbcl_thought_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_attention_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_t_cbcl_attention_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_rulebreak_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_t_cbcl_rulebreak_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_aggressive_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_t_cbcl_aggressive_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
sds_total_probs_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_sds_total_probs_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
#
d_interview_age_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_d_interview_age_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
d_sex_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_d_sex_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
d_income_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_d_income_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
d_race_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_d_race_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
d_pubertal_status_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_d_pubertal_status_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
mh_headaches_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_mh_headaches_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
sm_subc_v_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_sm_subc_v_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
sm_cort_t_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_sm_cort_t_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
sm_cort_sa_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_sm_cort_sa_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
dm_all_wmnd_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_dm_all_wmnd_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
rm_gord_cor_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_rm_gord_cor_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
rm_subc_cor_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_rm_subc_cor_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_loneliness_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_p_loneliness_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_screen_time_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_p_screen_time_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_sports_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_p_sports_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_exercise_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_p_exercise_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_prosocial_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_p_prosocial_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_fam_fn_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_p_fam_fn_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_parent_psych_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_p_parent_psych_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_anxdep_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_t_cbcl_anxdep_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_withdep_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_t_cbcl_withdep_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_somatic_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_t_cbcl_somatic_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_social_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_t_cbcl_social_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_thought_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_t_cbcl_thought_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_attention_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_t_cbcl_attention_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_rulebreak_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_t_cbcl_rulebreak_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_aggressive_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_t_cbcl_aggressive_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
sds_total_probs_pooled_mtbi_imp_3 <- read_csv(input_path("2023_12_01_sds_total_probs_pooled_imp_3.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
#
d_interview_age_pooled_mtbi_imp_4 <- read_csv(input_path("2023_12_01_d_interview_age_pooled_imp_4.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
d_sex_pooled_mtbi_imp_4 <- read_csv(input_path("2023_12_01_d_sex_pooled_imp_4.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
d_income_pooled_mtbi_imp_4 <- read_csv(input_path("2023_12_01_d_income_pooled_imp_4.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
d_race_pooled_mtbi_imp_4 <- read_csv(input_path("2023_12_01_d_race_pooled_imp_4.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
d_pubertal_status_pooled_mtbi_imp_4 <- read_csv(input_path("2023_12_01_d_pubertal_status_pooled_imp_4.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
mh_headaches_pooled_mtbi_imp_4 <- read_csv(input_path("2023_12_01_mh_headaches_pooled_imp_4.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
sm_subc_v_pooled_mtbi_imp_4 <- read_csv(input_path("2023_12_01_sm_subc_v_pooled_imp_4.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
sm_cort_t_pooled_mtbi_imp_4 <- read_csv(input_path("2023_12_01_sm_cort_t_pooled_imp_4.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
sm_cort_sa_pooled_mtbi_imp_4 <- read_csv(input_path("2023_12_01_sm_cort_sa_pooled_imp_4.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
dm_all_wmnd_pooled_mtbi_imp_4 <- read_csv(input_path("2023_12_01_dm_all_wmnd_pooled_imp_4.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
rm_gord_cor_pooled_mtbi_imp_4 <- read_csv(input_path("2023_12_01_rm_gord_cor_pooled_imp_4.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
rm_subc_cor_pooled_mtbi_imp_4 <- read_csv(input_path("2023_12_01_rm_subc_cor_pooled_imp_4.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_loneliness_pooled_mtbi_imp_4 <- read_csv(input_path("2023_12_01_p_loneliness_pooled_imp_4.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_screen_time_pooled_mtbi_imp_4 <- read_csv(input_path("2023_12_01_p_screen_time_pooled_imp_4.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_sports_pooled_mtbi_imp_4 <- read_csv(input_path("2023_12_01_p_sports_pooled_imp_4.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_exercise_pooled_mtbi_imp_4 <- read_csv(input_path("2023_12_01_p_exercise_pooled_imp_4.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_prosocial_pooled_mtbi_imp_4 <- read_csv(input_path("2023_12_01_p_prosocial_pooled_imp_4.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_fam_fn_pooled_mtbi_imp_4 <- read_csv(input_path("2023_12_01_p_fam_fn_pooled_imp_4.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_parent_psych_pooled_mtbi_imp_4 <- read_csv(input_path("2023_12_01_p_parent_psych_pooled_imp_4.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_anxdep_pooled_mtbi_imp_4 <- read_csv(input_path("2023_12_01_t_cbcl_anxdep_pooled_imp_4.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_withdep_pooled_mtbi_imp_4 <- read_csv(input_path("2023_12_01_t_cbcl_withdep_pooled_imp_4.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_somatic_pooled_mtbi_imp_4 <- read_csv(input_path("2023_12_01_t_cbcl_somatic_pooled_imp_4.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_social_pooled_mtbi_imp_4 <- read_csv(input_path("2023_12_01_t_cbcl_social_pooled_imp_4.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_thought_pooled_mtbi_imp_4 <- read_csv(input_path("2023_12_01_t_cbcl_thought_pooled_imp_4.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_attention_pooled_mtbi_imp_4 <- read_csv(input_path("2023_12_01_t_cbcl_attention_pooled_imp_4.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_rulebreak_pooled_mtbi_imp_4 <- read_csv(input_path("2023_12_01_t_cbcl_rulebreak_pooled_imp_4.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_aggressive_pooled_mtbi_imp_4 <- read_csv(input_path("2023_12_01_t_cbcl_aggressive_pooled_imp_4.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
sds_total_probs_pooled_mtbi_imp_4 <- read_csv(input_path("2023_12_01_sds_total_probs_pooled_imp_4.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
#
d_interview_age_pooled_mtbi_imp_5 <- read_csv(input_path("2023_12_01_d_interview_age_pooled_imp_5.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
d_sex_pooled_mtbi_imp_5 <- read_csv(input_path("2023_12_01_d_sex_pooled_imp_5.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
d_income_pooled_mtbi_imp_5 <- read_csv(input_path("2023_12_01_d_income_pooled_imp_5.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
d_race_pooled_mtbi_imp_5 <- read_csv(input_path("2023_12_01_d_race_pooled_imp_5.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
d_pubertal_status_pooled_mtbi_imp_5 <- read_csv(input_path("2023_12_01_d_pubertal_status_pooled_imp_5.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
mh_headaches_pooled_mtbi_imp_5 <- read_csv(input_path("2023_12_01_mh_headaches_pooled_imp_5.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
sm_subc_v_pooled_mtbi_imp_5 <- read_csv(input_path("2023_12_01_sm_subc_v_pooled_imp_5.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
sm_cort_t_pooled_mtbi_imp_5 <- read_csv(input_path("2023_12_01_sm_cort_t_pooled_imp_5.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
sm_cort_sa_pooled_mtbi_imp_5 <- read_csv(input_path("2023_12_01_sm_cort_sa_pooled_imp_5.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
dm_all_wmnd_pooled_mtbi_imp_5 <- read_csv(input_path("2023_12_01_dm_all_wmnd_pooled_imp_5.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
rm_gord_cor_pooled_mtbi_imp_5 <- read_csv(input_path("2023_12_01_rm_gord_cor_pooled_imp_5.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
rm_subc_cor_pooled_mtbi_imp_5 <- read_csv(input_path("2023_12_01_rm_subc_cor_pooled_imp_5.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_loneliness_pooled_mtbi_imp_5 <- read_csv(input_path("2023_12_01_p_loneliness_pooled_imp_5.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_screen_time_pooled_mtbi_imp_5 <- read_csv(input_path("2023_12_01_p_screen_time_pooled_imp_5.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_sports_pooled_mtbi_imp_5 <- read_csv(input_path("2023_12_01_p_sports_pooled_imp_5.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_exercise_pooled_mtbi_imp_5 <- read_csv(input_path("2023_12_01_p_exercise_pooled_imp_5.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_prosocial_pooled_mtbi_imp_5 <- read_csv(input_path("2023_12_01_p_prosocial_pooled_imp_5.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_fam_fn_pooled_mtbi_imp_5 <- read_csv(input_path("2023_12_01_p_fam_fn_pooled_imp_5.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
p_parent_psych_pooled_mtbi_imp_5 <- read_csv(input_path("2023_12_01_p_parent_psych_pooled_imp_5.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_anxdep_pooled_mtbi_imp_5 <- read_csv(input_path("2023_12_01_t_cbcl_anxdep_pooled_imp_5.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_withdep_pooled_mtbi_imp_5 <- read_csv(input_path("2023_12_01_t_cbcl_withdep_pooled_imp_5.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_somatic_pooled_mtbi_imp_5 <- read_csv(input_path("2023_12_01_t_cbcl_somatic_pooled_imp_5.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_social_pooled_mtbi_imp_5 <- read_csv(input_path("2023_12_01_t_cbcl_social_pooled_imp_5.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_thought_pooled_mtbi_imp_5 <- read_csv(input_path("2023_12_01_t_cbcl_thought_pooled_imp_5.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_attention_pooled_mtbi_imp_5 <- read_csv(input_path("2023_12_01_t_cbcl_attention_pooled_imp_5.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_rulebreak_pooled_mtbi_imp_5 <- read_csv(input_path("2023_12_01_t_cbcl_rulebreak_pooled_imp_5.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
t_cbcl_aggressive_pooled_mtbi_imp_5 <- read_csv(input_path("2023_12_01_t_cbcl_aggressive_pooled_imp_5.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
sds_total_probs_pooled_mtbi_imp_5 <- read_csv(input_path("2023_12_01_sds_total_probs_pooled_imp_5.csv")) |> dplyr::filter(subjectkey %in% mtbi_subjects$"subjectkey")
```


```{r}
###############################################################################
# 1. Load the input features and out-of-model features into data_lists
###############################################################################
data_list_m1 <- generate_data_list(
    list(as_mem_daze_mtbi_train_imp_1, "as_mem_daze", "AS", "discrete"),
    list(as_mechanism_mtbi_train_imp_1, "as_mechanism", "AS", "categorical"),
    list(as_loc_mtbi_train_imp_1, "as_loc", "AS", "discrete"),
    list(d_interview_age_mtbi_train_imp_1, "d_age", "D", "discrete"),
    list(d_mtbi_age_mtbi_train_imp_1, "d_mtbi_age", "D", "discrete"),
    list(d_sex_mtbi_train_imp_1, "d_sex", "D", "discrete"),
    list(d_income_mtbi_train_imp_1, "d_income", "D", "ordinal"),
    list(d_race_mtbi_train_imp_1, "d_race", "D", "discrete"),
    list(d_pubertal_status_mtbi_train_imp_1, "d_pubertal", "D", "discrete"),
    list(mh_headaches_mtbi_train_imp_1, "mh_headaches", "MH", "discrete"),
    list(mh_mtbi_count_mtbi_train_imp_1, "mh_mtbi_count", "MH", "discrete"),
    list(sm_subc_v_mtbi_train_imp_1, "sm_subc_v", "N", "continuous"),
    list(sm_cort_t_mtbi_train_imp_1, "sm_cort_t", "N", "continuous"),
    list(sm_cort_sa_mtbi_train_imp_1, "sm_cort_sa", "N", "continuous"),
    list(dm_all_wmnd_mtbi_train_imp_1, "dm_all_wmnd", "N", "continuous"),
    list(rm_gord_cor_mtbi_train_imp_1, "rm_gord_cor", "N", "continuous"),
    list(rm_subc_cor_mtbi_train_imp_1, "rm_subc_cor", "N", "continuous"),
    list(p_loneliness_mtbi_train_imp_1, "p_loneliness", "P", "discrete"),
    list(p_screen_time_mtbi_train_imp_1, "p_screen_time", "P", "discrete"),
    list(p_sports_mtbi_train_imp_1, "p_sports", "P", "discrete"),
    list(p_exercise_mtbi_train_imp_1, "p_exercise", "P", "discrete"),
    list(p_prosocial_mtbi_train_imp_1, "p_prosocial", "P", "discrete"),
    list(p_fam_fn_mtbi_train_imp_1, "p_fam_fn", "P", "discrete"),
    list(p_parent_psych_mtbi_train_imp_1, "p_parent_psych", "P", "discrete"),
    uid = "subjectkey"
)
#
data_list_m2 <- generate_data_list(
    list(as_mem_daze_mtbi_train_imp_2, "as_mem_daze", "AS", "discrete"),
    list(as_mechanism_mtbi_train_imp_2, "as_mechanism", "AS", "categorical"),
    list(as_loc_mtbi_train_imp_2, "as_loc", "AS", "discrete"),
    list(d_interview_age_mtbi_train_imp_2, "d_age", "D", "discrete"),
    list(d_mtbi_age_mtbi_train_imp_2, "d_mtbi_age", "D", "discrete"),
    list(d_sex_mtbi_train_imp_2, "d_sex", "D", "discrete"),
    list(d_income_mtbi_train_imp_2, "d_income", "D", "ordinal"),
    list(d_race_mtbi_train_imp_2, "d_race", "D", "discrete"),
    list(d_pubertal_status_mtbi_train_imp_2, "d_pubertal", "D", "discrete"),
    list(mh_headaches_mtbi_train_imp_2, "mh_headaches", "MH", "discrete"),
    list(mh_mtbi_count_mtbi_train_imp_2, "mh_mtbi_count", "MH", "discrete"),
    list(sm_subc_v_mtbi_train_imp_2, "sm_subc_v", "N", "continuous"),
    list(sm_cort_t_mtbi_train_imp_2, "sm_cort_t", "N", "continuous"),
    list(sm_cort_sa_mtbi_train_imp_2, "sm_cort_sa", "N", "continuous"),
    list(dm_all_wmnd_mtbi_train_imp_2, "dm_all_wmnd", "N", "continuous"),
    list(rm_gord_cor_mtbi_train_imp_2, "rm_gord_cor", "N", "continuous"),
    list(rm_subc_cor_mtbi_train_imp_2, "rm_subc_cor", "N", "continuous"),
    list(p_loneliness_mtbi_train_imp_2, "p_loneliness", "P", "discrete"),
    list(p_screen_time_mtbi_train_imp_2, "p_screen_time", "P", "discrete"),
    list(p_sports_mtbi_train_imp_2, "p_sports", "P", "discrete"),
    list(p_exercise_mtbi_train_imp_2, "p_exercise", "P", "discrete"),
    list(p_prosocial_mtbi_train_imp_2, "p_prosocial", "P", "discrete"),
    list(p_fam_fn_mtbi_train_imp_2, "p_fam_fn", "P", "discrete"),
    list(p_parent_psych_mtbi_train_imp_2, "p_parent_psych", "P", "discrete"),
    uid = "subjectkey"
)
#
data_list_m3 <- generate_data_list(
    list(as_mem_daze_mtbi_train_imp_3, "as_mem_daze", "AS", "discrete"),
    list(as_mechanism_mtbi_train_imp_3, "as_mechanism", "AS", "categorical"),
    list(as_loc_mtbi_train_imp_3, "as_loc", "AS", "discrete"),
    list(d_interview_age_mtbi_train_imp_3, "d_age", "D", "discrete"),
    list(d_mtbi_age_mtbi_train_imp_3, "d_mtbi_age", "D", "discrete"),
    list(d_sex_mtbi_train_imp_3, "d_sex", "D", "discrete"),
    list(d_income_mtbi_train_imp_3, "d_income", "D", "ordinal"),
    list(d_race_mtbi_train_imp_3, "d_race", "D", "discrete"),
    list(d_pubertal_status_mtbi_train_imp_3, "d_pubertal", "D", "discrete"),
    list(mh_headaches_mtbi_train_imp_3, "mh_headaches", "MH", "discrete"),
    list(mh_mtbi_count_mtbi_train_imp_3, "mh_mtbi_count", "MH", "discrete"),
    list(sm_subc_v_mtbi_train_imp_3, "sm_subc_v", "N", "continuous"),
    list(sm_cort_t_mtbi_train_imp_3, "sm_cort_t", "N", "continuous"),
    list(sm_cort_sa_mtbi_train_imp_3, "sm_cort_sa", "N", "continuous"),
    list(dm_all_wmnd_mtbi_train_imp_3, "dm_all_wmnd", "N", "continuous"),
    list(rm_gord_cor_mtbi_train_imp_3, "rm_gord_cor", "N", "continuous"),
    list(rm_subc_cor_mtbi_train_imp_3, "rm_subc_cor", "N", "continuous"),
    list(p_loneliness_mtbi_train_imp_3, "p_loneliness", "P", "discrete"),
    list(p_screen_time_mtbi_train_imp_3, "p_screen_time", "P", "discrete"),
    list(p_sports_mtbi_train_imp_3, "p_sports", "P", "discrete"),
    list(p_exercise_mtbi_train_imp_3, "p_exercise", "P", "discrete"),
    list(p_prosocial_mtbi_train_imp_3, "p_prosocial", "P", "discrete"),
    list(p_fam_fn_mtbi_train_imp_3, "p_fam_fn", "P", "discrete"),
    list(p_parent_psych_mtbi_train_imp_3, "p_parent_psych", "P", "discrete"),
    uid = "subjectkey"
)
#
data_list_m4 <- generate_data_list(
    list(as_mem_daze_mtbi_train_imp_4, "as_mem_daze", "AS", "discrete"),
    list(as_mechanism_mtbi_train_imp_4, "as_mechanism", "AS", "categorical"),
    list(as_loc_mtbi_train_imp_4, "as_loc", "AS", "discrete"),
    list(d_interview_age_mtbi_train_imp_4, "d_age", "D", "discrete"),
    list(d_mtbi_age_mtbi_train_imp_4, "d_mtbi_age", "D", "discrete"),
    list(d_sex_mtbi_train_imp_4, "d_sex", "D", "discrete"),
    list(d_income_mtbi_train_imp_4, "d_income", "D", "ordinal"),
    list(d_race_mtbi_train_imp_4, "d_race", "D", "discrete"),
    list(d_pubertal_status_mtbi_train_imp_4, "d_pubertal", "D", "discrete"),
    list(mh_headaches_mtbi_train_imp_4, "mh_headaches", "MH", "discrete"),
    list(mh_mtbi_count_mtbi_train_imp_4, "mh_mtbi_count", "MH", "discrete"),
    list(sm_subc_v_mtbi_train_imp_4, "sm_subc_v", "N", "continuous"),
    list(sm_cort_t_mtbi_train_imp_4, "sm_cort_t", "N", "continuous"),
    list(sm_cort_sa_mtbi_train_imp_4, "sm_cort_sa", "N", "continuous"),
    list(dm_all_wmnd_mtbi_train_imp_4, "dm_all_wmnd", "N", "continuous"),
    list(rm_gord_cor_mtbi_train_imp_4, "rm_gord_cor", "N", "continuous"),
    list(rm_subc_cor_mtbi_train_imp_4, "rm_subc_cor", "N", "continuous"),
    list(p_loneliness_mtbi_train_imp_4, "p_loneliness", "P", "discrete"),
    list(p_screen_time_mtbi_train_imp_4, "p_screen_time", "P", "discrete"),
    list(p_sports_mtbi_train_imp_4, "p_sports", "P", "discrete"),
    list(p_exercise_mtbi_train_imp_4, "p_exercise", "P", "discrete"),
    list(p_prosocial_mtbi_train_imp_4, "p_prosocial", "P", "discrete"),
    list(p_fam_fn_mtbi_train_imp_4, "p_fam_fn", "P", "discrete"),
    list(p_parent_psych_mtbi_train_imp_4, "p_parent_psych", "P", "discrete"),
    uid = "subjectkey"
)
#
data_list_m5 <- generate_data_list(
    list(as_mem_daze_mtbi_train_imp_5, "as_mem_daze", "AS", "discrete"),
    list(as_mechanism_mtbi_train_imp_5, "as_mechanism", "AS", "categorical"),
    list(as_loc_mtbi_train_imp_5, "as_loc", "AS", "discrete"),
    list(d_interview_age_mtbi_train_imp_5, "d_age", "D", "discrete"),
    list(d_mtbi_age_mtbi_train_imp_5, "d_mtbi_age", "D", "discrete"),
    list(d_sex_mtbi_train_imp_5, "d_sex", "D", "discrete"),
    list(d_income_mtbi_train_imp_5, "d_income", "D", "ordinal"),
    list(d_race_mtbi_train_imp_5, "d_race", "D", "discrete"),
    list(d_pubertal_status_mtbi_train_imp_5, "d_pubertal", "D", "discrete"),
    list(mh_headaches_mtbi_train_imp_5, "mh_headaches", "MH", "discrete"),
    list(mh_mtbi_count_mtbi_train_imp_5, "mh_mtbi_count", "MH", "discrete"),
    list(sm_subc_v_mtbi_train_imp_5, "sm_subc_v", "N", "continuous"),
    list(sm_cort_t_mtbi_train_imp_5, "sm_cort_t", "N", "continuous"),
    list(sm_cort_sa_mtbi_train_imp_5, "sm_cort_sa", "N", "continuous"),
    list(dm_all_wmnd_mtbi_train_imp_5, "dm_all_wmnd", "N", "continuous"),
    list(rm_gord_cor_mtbi_train_imp_5, "rm_gord_cor", "N", "continuous"),
    list(rm_subc_cor_mtbi_train_imp_5, "rm_subc_cor", "N", "continuous"),
    list(p_loneliness_mtbi_train_imp_5, "p_loneliness", "P", "discrete"),
    list(p_screen_time_mtbi_train_imp_5, "p_screen_time", "P", "discrete"),
    list(p_sports_mtbi_train_imp_5, "p_sports", "P", "discrete"),
    list(p_exercise_mtbi_train_imp_5, "p_exercise", "P", "discrete"),
    list(p_prosocial_mtbi_train_imp_5, "p_prosocial", "P", "discrete"),
    list(p_fam_fn_mtbi_train_imp_5, "p_fam_fn", "P", "discrete"),
    list(p_parent_psych_mtbi_train_imp_5, "p_parent_psych", "P", "discrete"),
    uid = "subjectkey"
)

#
data_list_pm1 <- generate_data_list(
    list(d_interview_age_pooled_mtbi_imp_1, "d_age", "D", "discrete"),
    list(d_sex_pooled_mtbi_imp_1, "d_sex", "D", "discrete"),
    list(d_income_pooled_mtbi_imp_1, "d_income", "D", "ordinal"),
    list(d_race_pooled_mtbi_imp_1, "d_race", "D", "discrete"),
    list(d_pubertal_status_pooled_mtbi_imp_1, "d_pubertal", "D", "discrete"),
    list(mh_headaches_pooled_mtbi_imp_1, "mh_headaches", "MH", "discrete"),
    list(sm_subc_v_pooled_mtbi_imp_1, "sm_subc_v", "N", "continuous"),
    list(sm_cort_t_pooled_mtbi_imp_1, "sm_cort_t", "N", "continuous"),
    list(sm_cort_sa_pooled_mtbi_imp_1, "sm_cort_sa", "N", "continuous"),
    list(dm_all_wmnd_pooled_mtbi_imp_1, "dm_all_wmnd", "N", "continuous"),
    list(rm_gord_cor_pooled_mtbi_imp_1, "rm_gord_cor", "N", "continuous"),
    list(rm_subc_cor_pooled_mtbi_imp_1, "rm_subc_cor", "N", "continuous"),
    list(p_loneliness_pooled_mtbi_imp_1, "p_loneliness", "P", "discrete"),
    list(p_screen_time_pooled_mtbi_imp_1, "p_screen_time", "P", "discrete"),
    list(p_sports_pooled_mtbi_imp_1, "p_sports", "P", "discrete"),
    list(p_exercise_pooled_mtbi_imp_1, "p_exercise", "P", "discrete"),
    list(p_prosocial_pooled_mtbi_imp_1, "p_prosocial", "P", "discrete"),
    list(p_fam_fn_pooled_mtbi_imp_1, "p_fam_fn", "P", "discrete"),
    list(p_parent_psych_pooled_mtbi_imp_1, "p_parent_psych", "P", "discrete"),
    uid = "subjectkey"
)
#
data_list_pm2 <- generate_data_list(
    list(d_interview_age_pooled_mtbi_imp_2, "d_age", "D", "discrete"),
    list(d_sex_pooled_mtbi_imp_2, "d_sex", "D", "discrete"),
    list(d_income_pooled_mtbi_imp_2, "d_income", "D", "ordinal"),
    list(d_race_pooled_mtbi_imp_2, "d_race", "D", "discrete"),
    list(d_pubertal_status_pooled_mtbi_imp_2, "d_pubertal", "D", "discrete"),
    list(mh_headaches_pooled_mtbi_imp_2, "mh_headaches", "MH", "discrete"),
    list(sm_subc_v_pooled_mtbi_imp_2, "sm_subc_v", "N", "continuous"),
    list(sm_cort_t_pooled_mtbi_imp_2, "sm_cort_t", "N", "continuous"),
    list(sm_cort_sa_pooled_mtbi_imp_2, "sm_cort_sa", "N", "continuous"),
    list(dm_all_wmnd_pooled_mtbi_imp_2, "dm_all_wmnd", "N", "continuous"),
    list(rm_gord_cor_pooled_mtbi_imp_2, "rm_gord_cor", "N", "continuous"),
    list(rm_subc_cor_pooled_mtbi_imp_2, "rm_subc_cor", "N", "continuous"),
    list(p_loneliness_pooled_mtbi_imp_2, "p_loneliness", "P", "discrete"),
    list(p_screen_time_pooled_mtbi_imp_2, "p_screen_time", "P", "discrete"),
    list(p_sports_pooled_mtbi_imp_2, "p_sports", "P", "discrete"),
    list(p_exercise_pooled_mtbi_imp_2, "p_exercise", "P", "discrete"),
    list(p_prosocial_pooled_mtbi_imp_2, "p_prosocial", "P", "discrete"),
    list(p_fam_fn_pooled_mtbi_imp_2, "p_fam_fn", "P", "discrete"),
    list(p_parent_psych_pooled_mtbi_imp_2, "p_parent_psych", "P", "discrete"),
    uid = "subjectkey"
)
#
data_list_pm3 <- generate_data_list(
    list(d_interview_age_pooled_mtbi_imp_3, "d_age", "D", "discrete"),
    list(d_sex_pooled_mtbi_imp_3, "d_sex", "D", "discrete"),
    list(d_income_pooled_mtbi_imp_3, "d_income", "D", "ordinal"),
    list(d_race_pooled_mtbi_imp_3, "d_race", "D", "discrete"),
    list(d_pubertal_status_pooled_mtbi_imp_3, "d_pubertal", "D", "discrete"),
    list(mh_headaches_pooled_mtbi_imp_3, "mh_headaches", "MH", "discrete"),
    list(sm_subc_v_pooled_mtbi_imp_3, "sm_subc_v", "N", "continuous"),
    list(sm_cort_t_pooled_mtbi_imp_3, "sm_cort_t", "N", "continuous"),
    list(sm_cort_sa_pooled_mtbi_imp_3, "sm_cort_sa", "N", "continuous"),
    list(dm_all_wmnd_pooled_mtbi_imp_3, "dm_all_wmnd", "N", "continuous"),
    list(rm_gord_cor_pooled_mtbi_imp_3, "rm_gord_cor", "N", "continuous"),
    list(rm_subc_cor_pooled_mtbi_imp_3, "rm_subc_cor", "N", "continuous"),
    list(p_loneliness_pooled_mtbi_imp_3, "p_loneliness", "P", "discrete"),
    list(p_screen_time_pooled_mtbi_imp_3, "p_screen_time", "P", "discrete"),
    list(p_sports_pooled_mtbi_imp_3, "p_sports", "P", "discrete"),
    list(p_exercise_pooled_mtbi_imp_3, "p_exercise", "P", "discrete"),
    list(p_prosocial_pooled_mtbi_imp_3, "p_prosocial", "P", "discrete"),
    list(p_fam_fn_pooled_mtbi_imp_3, "p_fam_fn", "P", "discrete"),
    list(p_parent_psych_pooled_mtbi_imp_3, "p_parent_psych", "P", "discrete"),
    uid = "subjectkey"
)
#
data_list_pm4 <- generate_data_list(
    list(d_interview_age_pooled_mtbi_imp_4, "d_age", "D", "discrete"),
    list(d_sex_pooled_mtbi_imp_4, "d_sex", "D", "discrete"),
    list(d_income_pooled_mtbi_imp_4, "d_income", "D", "ordinal"),
    list(d_race_pooled_mtbi_imp_4, "d_race", "D", "discrete"),
    list(d_pubertal_status_pooled_mtbi_imp_4, "d_pubertal", "D", "discrete"),
    list(mh_headaches_pooled_mtbi_imp_4, "mh_headaches", "MH", "discrete"),
    list(sm_subc_v_pooled_mtbi_imp_4, "sm_subc_v", "N", "continuous"),
    list(sm_cort_t_pooled_mtbi_imp_4, "sm_cort_t", "N", "continuous"),
    list(sm_cort_sa_pooled_mtbi_imp_4, "sm_cort_sa", "N", "continuous"),
    list(dm_all_wmnd_pooled_mtbi_imp_4, "dm_all_wmnd", "N", "continuous"),
    list(rm_gord_cor_pooled_mtbi_imp_4, "rm_gord_cor", "N", "continuous"),
    list(rm_subc_cor_pooled_mtbi_imp_4, "rm_subc_cor", "N", "continuous"),
    list(p_loneliness_pooled_mtbi_imp_4, "p_loneliness", "P", "discrete"),
    list(p_screen_time_pooled_mtbi_imp_4, "p_screen_time", "P", "discrete"),
    list(p_sports_pooled_mtbi_imp_4, "p_sports", "P", "discrete"),
    list(p_exercise_pooled_mtbi_imp_4, "p_exercise", "P", "discrete"),
    list(p_prosocial_pooled_mtbi_imp_4, "p_prosocial", "P", "discrete"),
    list(p_fam_fn_pooled_mtbi_imp_4, "p_fam_fn", "P", "discrete"),
    list(p_parent_psych_pooled_mtbi_imp_4, "p_parent_psych", "P", "discrete"),
    uid = "subjectkey"
)
#
data_list_pm5 <- generate_data_list(
    list(d_interview_age_pooled_mtbi_imp_5, "d_age", "D", "discrete"),
    list(d_sex_pooled_mtbi_imp_5, "d_sex", "D", "discrete"),
    list(d_income_pooled_mtbi_imp_5, "d_income", "D", "ordinal"),
    list(d_race_pooled_mtbi_imp_5, "d_race", "D", "discrete"),
    list(d_pubertal_status_pooled_mtbi_imp_5, "d_pubertal", "D", "discrete"),
    list(mh_headaches_pooled_mtbi_imp_5, "mh_headaches", "MH", "discrete"),
    list(sm_subc_v_pooled_mtbi_imp_5, "sm_subc_v", "N", "continuous"),
    list(sm_cort_t_pooled_mtbi_imp_5, "sm_cort_t", "N", "continuous"),
    list(sm_cort_sa_pooled_mtbi_imp_5, "sm_cort_sa", "N", "continuous"),
    list(dm_all_wmnd_pooled_mtbi_imp_5, "dm_all_wmnd", "N", "continuous"),
    list(rm_gord_cor_pooled_mtbi_imp_5, "rm_gord_cor", "N", "continuous"),
    list(rm_subc_cor_pooled_mtbi_imp_5, "rm_subc_cor", "N", "continuous"),
    list(p_loneliness_pooled_mtbi_imp_5, "p_loneliness", "P", "discrete"),
    list(p_screen_time_pooled_mtbi_imp_5, "p_screen_time", "P", "discrete"),
    list(p_sports_pooled_mtbi_imp_5, "p_sports", "P", "discrete"),
    list(p_exercise_pooled_mtbi_imp_5, "p_exercise", "P", "discrete"),
    list(p_prosocial_pooled_mtbi_imp_5, "p_prosocial", "P", "discrete"),
    list(p_fam_fn_pooled_mtbi_imp_5, "p_fam_fn", "P", "discrete"),
    list(p_parent_psych_pooled_mtbi_imp_5, "p_parent_psych", "P", "discrete"),
    uid = "subjectkey"
)

oom_list_m1 <- generate_data_list(
    list(t_cbcl_anxdep_mtbi_train_imp_1, "t_cbcl_anxdep", "B", "ordinal"),
    list(t_cbcl_withdep_mtbi_train_imp_1, "t_cbcl_withdep", "B", "ordinal"),
    list(t_cbcl_somatic_mtbi_train_imp_1, "t_cbcl_somatic", "B", "ordinal"),
    list(t_cbcl_social_mtbi_train_imp_1, "t_cbcl_social", "B", "ordinal"),
    list(t_cbcl_thought_mtbi_train_imp_1, "t_cbcl_thought", "B", "ordinal"),
    list(t_cbcl_attention_mtbi_train_imp_1, "t_cbcl_attention", "B", "ordinal"),
    list(t_cbcl_rulebreak_mtbi_train_imp_1, "t_cbcl_rulebreak", "B", "ordinal"),
    list(t_cbcl_aggressive_mtbi_train_imp_1, "t_cbcl_aggressive", "B", "ordinal"),
    list(sds_total_probs_mtbi_train_imp_1, "sds_total_probs", "S", "discrete")
)
#
oom_list_m2 <- generate_data_list(
    list(t_cbcl_anxdep_mtbi_train_imp_2, "t_cbcl_anxdep", "B", "ordinal"),
    list(t_cbcl_withdep_mtbi_train_imp_2, "t_cbcl_withdep", "B", "ordinal"),
    list(t_cbcl_somatic_mtbi_train_imp_2, "t_cbcl_somatic", "B", "ordinal"),
    list(t_cbcl_social_mtbi_train_imp_2, "t_cbcl_social", "B", "ordinal"),
    list(t_cbcl_thought_mtbi_train_imp_2, "t_cbcl_thought", "B", "ordinal"),
    list(t_cbcl_attention_mtbi_train_imp_2, "t_cbcl_attention", "B", "ordinal"),
    list(t_cbcl_rulebreak_mtbi_train_imp_2, "t_cbcl_rulebreak", "B", "ordinal"),
    list(t_cbcl_aggressive_mtbi_train_imp_2, "t_cbcl_aggressive", "B", "ordinal"),
    list(sds_total_probs_mtbi_train_imp_2, "sds_total_probs", "S", "discrete")
)
#
oom_list_m3 <- generate_data_list(
    list(t_cbcl_anxdep_mtbi_train_imp_3, "t_cbcl_anxdep", "B", "ordinal"),
    list(t_cbcl_withdep_mtbi_train_imp_3, "t_cbcl_withdep", "B", "ordinal"),
    list(t_cbcl_somatic_mtbi_train_imp_3, "t_cbcl_somatic", "B", "ordinal"),
    list(t_cbcl_social_mtbi_train_imp_3, "t_cbcl_social", "B", "ordinal"),
    list(t_cbcl_thought_mtbi_train_imp_3, "t_cbcl_thought", "B", "ordinal"),
    list(t_cbcl_attention_mtbi_train_imp_3, "t_cbcl_attention", "B", "ordinal"),
    list(t_cbcl_rulebreak_mtbi_train_imp_3, "t_cbcl_rulebreak", "B", "ordinal"),
    list(t_cbcl_aggressive_mtbi_train_imp_3, "t_cbcl_aggressive", "B", "ordinal"),
    list(sds_total_probs_mtbi_train_imp_3, "sds_total_probs", "S", "discrete")
)
#
oom_list_m4 <- generate_data_list(
    list(t_cbcl_anxdep_mtbi_train_imp_4, "t_cbcl_anxdep", "B", "ordinal"),
    list(t_cbcl_withdep_mtbi_train_imp_4, "t_cbcl_withdep", "B", "ordinal"),
    list(t_cbcl_somatic_mtbi_train_imp_4, "t_cbcl_somatic", "B", "ordinal"),
    list(t_cbcl_social_mtbi_train_imp_4, "t_cbcl_social", "B", "ordinal"),
    list(t_cbcl_thought_mtbi_train_imp_4, "t_cbcl_thought", "B", "ordinal"),
    list(t_cbcl_attention_mtbi_train_imp_4, "t_cbcl_attention", "B", "ordinal"),
    list(t_cbcl_rulebreak_mtbi_train_imp_4, "t_cbcl_rulebreak", "B", "ordinal"),
    list(t_cbcl_aggressive_mtbi_train_imp_4, "t_cbcl_aggressive", "B", "ordinal"),
    list(sds_total_probs_mtbi_train_imp_4, "sds_total_probs", "S", "discrete")
)
#
oom_list_m5 <- generate_data_list(
    list(t_cbcl_anxdep_mtbi_train_imp_5, "t_cbcl_anxdep", "B", "ordinal"),
    list(t_cbcl_withdep_mtbi_train_imp_5, "t_cbcl_withdep", "B", "ordinal"),
    list(t_cbcl_somatic_mtbi_train_imp_5, "t_cbcl_somatic", "B", "ordinal"),
    list(t_cbcl_social_mtbi_train_imp_5, "t_cbcl_social", "B", "ordinal"),
    list(t_cbcl_thought_mtbi_train_imp_5, "t_cbcl_thought", "B", "ordinal"),
    list(t_cbcl_attention_mtbi_train_imp_5, "t_cbcl_attention", "B", "ordinal"),
    list(t_cbcl_rulebreak_mtbi_train_imp_5, "t_cbcl_rulebreak", "B", "ordinal"),
    list(t_cbcl_aggressive_mtbi_train_imp_5, "t_cbcl_aggressive", "B", "ordinal"),
    list(sds_total_probs_mtbi_train_imp_5, "sds_total_probs", "S", "discrete")
)


oom_list_pm1 <- generate_data_list(
    list(t_cbcl_anxdep_pooled_mtbi_imp_1, "t_cbcl_anxdep", "B", "ordinal"),
    list(t_cbcl_withdep_pooled_mtbi_imp_1, "t_cbcl_withdep", "B", "ordinal"),
    list(t_cbcl_somatic_pooled_mtbi_imp_1, "t_cbcl_somatic", "B", "ordinal"),
    list(t_cbcl_social_pooled_mtbi_imp_1, "t_cbcl_social", "B", "ordinal"),
    list(t_cbcl_thought_pooled_mtbi_imp_1, "t_cbcl_thought", "B", "ordinal"),
    list(t_cbcl_attention_pooled_mtbi_imp_1, "t_cbcl_attention", "B", "ordinal"),
    list(t_cbcl_rulebreak_pooled_mtbi_imp_1, "t_cbcl_rulebreak", "B", "ordinal"),
    list(t_cbcl_aggressive_pooled_mtbi_imp_1, "t_cbcl_aggressive", "B", "ordinal"),
    list(sds_total_probs_pooled_mtbi_imp_1, "sds_total_probs", "S", "discrete")
)
#
oom_list_pm2 <- generate_data_list(
    list(t_cbcl_anxdep_pooled_mtbi_imp_2, "t_cbcl_anxdep", "B", "ordinal"),
    list(t_cbcl_withdep_pooled_mtbi_imp_2, "t_cbcl_withdep", "B", "ordinal"),
    list(t_cbcl_somatic_pooled_mtbi_imp_2, "t_cbcl_somatic", "B", "ordinal"),
    list(t_cbcl_social_pooled_mtbi_imp_2, "t_cbcl_social", "B", "ordinal"),
    list(t_cbcl_thought_pooled_mtbi_imp_2, "t_cbcl_thought", "B", "ordinal"),
    list(t_cbcl_attention_pooled_mtbi_imp_2, "t_cbcl_attention", "B", "ordinal"),
    list(t_cbcl_rulebreak_pooled_mtbi_imp_2, "t_cbcl_rulebreak", "B", "ordinal"),
    list(t_cbcl_aggressive_pooled_mtbi_imp_2, "t_cbcl_aggressive", "B", "ordinal"),
    list(sds_total_probs_pooled_mtbi_imp_2, "sds_total_probs", "S", "discrete")
)
#
oom_list_pm3 <- generate_data_list(
    list(t_cbcl_anxdep_pooled_mtbi_imp_3, "t_cbcl_anxdep", "B", "ordinal"),
    list(t_cbcl_withdep_pooled_mtbi_imp_3, "t_cbcl_withdep", "B", "ordinal"),
    list(t_cbcl_somatic_pooled_mtbi_imp_3, "t_cbcl_somatic", "B", "ordinal"),
    list(t_cbcl_social_pooled_mtbi_imp_3, "t_cbcl_social", "B", "ordinal"),
    list(t_cbcl_thought_pooled_mtbi_imp_3, "t_cbcl_thought", "B", "ordinal"),
    list(t_cbcl_attention_pooled_mtbi_imp_3, "t_cbcl_attention", "B", "ordinal"),
    list(t_cbcl_rulebreak_pooled_mtbi_imp_3, "t_cbcl_rulebreak", "B", "ordinal"),
    list(t_cbcl_aggressive_pooled_mtbi_imp_3, "t_cbcl_aggressive", "B", "ordinal"),
    list(sds_total_probs_pooled_mtbi_imp_3, "sds_total_probs", "S", "discrete")
)
#
oom_list_pm4 <- generate_data_list(
    list(t_cbcl_anxdep_pooled_mtbi_imp_4, "t_cbcl_anxdep", "B", "ordinal"),
    list(t_cbcl_withdep_pooled_mtbi_imp_4, "t_cbcl_withdep", "B", "ordinal"),
    list(t_cbcl_somatic_pooled_mtbi_imp_4, "t_cbcl_somatic", "B", "ordinal"),
    list(t_cbcl_social_pooled_mtbi_imp_4, "t_cbcl_social", "B", "ordinal"),
    list(t_cbcl_thought_pooled_mtbi_imp_4, "t_cbcl_thought", "B", "ordinal"),
    list(t_cbcl_attention_pooled_mtbi_imp_4, "t_cbcl_attention", "B", "ordinal"),
    list(t_cbcl_rulebreak_pooled_mtbi_imp_4, "t_cbcl_rulebreak", "B", "ordinal"),
    list(t_cbcl_aggressive_pooled_mtbi_imp_4, "t_cbcl_aggressive", "B", "ordinal"),
    list(sds_total_probs_pooled_mtbi_imp_4, "sds_total_probs", "S", "discrete")
)
#
oom_list_pm5 <- generate_data_list(
    list(t_cbcl_anxdep_pooled_mtbi_imp_5, "t_cbcl_anxdep", "B", "ordinal"),
    list(t_cbcl_withdep_pooled_mtbi_imp_5, "t_cbcl_withdep", "B", "ordinal"),
    list(t_cbcl_somatic_pooled_mtbi_imp_5, "t_cbcl_somatic", "B", "ordinal"),
    list(t_cbcl_social_pooled_mtbi_imp_5, "t_cbcl_social", "B", "ordinal"),
    list(t_cbcl_thought_pooled_mtbi_imp_5, "t_cbcl_thought", "B", "ordinal"),
    list(t_cbcl_attention_pooled_mtbi_imp_5, "t_cbcl_attention", "B", "ordinal"),
    list(t_cbcl_rulebreak_pooled_mtbi_imp_5, "t_cbcl_rulebreak", "B", "ordinal"),
    list(t_cbcl_aggressive_pooled_mtbi_imp_5, "t_cbcl_aggressive", "B", "ordinal"),
    list(sds_total_probs_pooled_mtbi_imp_5, "sds_total_probs", "S", "discrete")
)

###############################################################################
# 2. Add standard normalized variations to the distance metrics list (also
# achievable through toggling automatic_standard_normalize parameter in
# `batch_snf`)
###############################################################################
my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

summarize_distance_metrics_list(my_distance_metrics)
```

## A utility function to give our variables some better names

```{r}


heart_rate_df <- data.frame(
    patient_id = c("1", "2", "3"),
    var1 = c(0.04, 0.1, 0.3),
    var2 = c(30, 2, 0.3)
)

personality_test_df <- data.frame(
    patient_id = c("1", "2", "3"),
    var3 = c(900, 1990, 373),
    var4 = c(509, 2209, 83)
)

survey_response_df <- data.frame(
    patient_id = c("1", "2", "3"),
    var5 = c(1, 3, 3),
    var6 = c(2, 3, 3)
)

city_df <- data.frame(
    patient_id = c("1", "2", "3"),
    var7 = c("toronto", "montreal", "vancouver")
)

dl <- generate_data_list(
    list(heart_rate_df, "heart_rate", "clinical", "continuous"),
    list(personality_test_df, "personality_test", "surveys", "continuous"),
    list(survey_response_df, "survey_response", "surveys", "ordinal"),
    list(city_df, "city", "location", "categorical"),
    uid = "patient_id"
)

name_changes <- c(
    "persons_city" = "var7",
    "heart_measure1"= "var1",
    "heart_measure2" = "var2"
)

rename_data_list <- function(data_list, name_mapping) {
    data_list <- data_list |> lapply(
        function(x) {
            old_colnames <- colnames(x$"data")
            new_colnames <- old_colnames |> lapply(
                function(old_name) {
                    if (old_name %in% name_mapping) {
                        new_name <- names(name_mapping)[which(name_mapping == old_name)]
                    } else {
                        new_name <- old_name
                    }
                    return(new_name)
                }
            )
            colnames(x$"data") <- new_colnames
            return(x)
        }
    )
    return(data_list)
}

rename_data_list(dl, name_changes)

```

## Initial visualizations

Visualizing correlations among variables

```{r}

keep_numeric <- function(df) {
    df <- numcol_to_numeric(df)
    classes <- as.vector(sapply(df, class))
    df <- df[, classes == "numeric", drop = FALSE]
    return(df)
}

hm_colours <- function(data, max_red = TRUE) {
    if (max_red) {
        colours <- circlize::colorRamp2(
            c(min(data), max(data)),
            c("black", "red")
        )
    } else {
        colours <- circlize::colorRamp2(
            c(min(data), max(data)),
            c("red", "black")
        )
    }
    return(colours)
}

correlation_heatmap <- function(data_list, order = NULL) {
    dl_df <- collapse_dl(data_list)
    numeric_dl_df <- keep_numeric(dl_df)
    correlation_matrix <- cor(numeric_dl_df)
    if (is.null(order)) {
        heatmap <- ComplexHeatmap::Heatmap(correlation_matrix)
    } else {
        heatmap <- ComplexHeatmap::Heatmap(
            correlation_matrix[order, order],
            cluster_rows = FALSE,
            cluster_columns = FALSE
        )
    }
    drawn_heatmap <- ComplexHeatmap::draw(heatmap)
    order <- ComplexHeatmap::row_order(drawn_heatmap)
    results <- list(
        "correlation_matrix" = correlation_matrix,
        "heatmap" = heatmap,
        "order" = order
    )
    return(results)
}

###############################################################################
# Imputation 1
###############################################################################
# First pass to extract the order of columns
correlation_heatmap_data_m1 <- correlation_heatmap(c(data_list_m1, oom_list_m1))
correlation_matrix_m1 <- correlation_heatmap_data_m1$"correlation_matrix"
race_cors_m1 <- abs(correlation_matrix_m1[, "race"])
race_order_m1 <- sort(race_cors_m1, index.return = TRUE, decreasing = TRUE)$"ix"
sex_cors_m1 <- abs(correlation_matrix_m1[, "sex"])
sex_order_m1 <- sort(sex_cors_m1, index.return = TRUE, decreasing = TRUE)$"ix"

# All correlations, sorted by abs(cor-race)
ComplexHeatmap::Heatmap(
    correlation_matrix_m1[race_order_m1, race_order_m1],
    cluster_rows = FALSE,
    cluster_columns = FALSE
)

# Race correlations, sorted by abs(cor-race)
ComplexHeatmap::Heatmap(
    correlation_matrix_m1[race_order_m1, "race"],
    cluster_rows = FALSE,
    cluster_columns = FALSE
)

# All correlations, sorted by abs(cor-sex)
ComplexHeatmap::Heatmap(
    correlation_matrix_m1[sex_order_m1, sex_order_m1],
    cluster_rows = FALSE,
    cluster_columns = FALSE
)

# Sex correlations, sorted by abs(cor-race)
ComplexHeatmap::Heatmap(
    correlation_matrix_m1[sex_order_m1, "sex"],
    cluster_rows = FALSE,
    cluster_columns = FALSE
)

###############################################################################
# Similarity matrix visualizations
###############################################################################

all_vars_associations <- calculate_associations(all_vars_dl_m1)

race_cors <- all_vars_associations[, "race"]
race_order <- sort(race_cors, index.return = TRUE)$"ix"

correlation_pval_heatmap(
    all_vars_associations[race_order, race_order],
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    significance_stars = FALSE
)

sex_cors <- all_vars_associations[, "sex"]
sex_order <- sort(sex_cors, index.return = TRUE)$"ix"

correlation_pval_heatmap(
    all_vars_associations[sex_order, sex_order],
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    significance_stars = FALSE
)
```

Now for the actual subtyping.

Some of the heavier functions are in the next chunk:

```{r}
###############################################################################
# 3. Generate the settings matrix
###############################################################################
settings_matrix <- generate_settings_matrix(
    data_list_m1,
    nrow = 200,
    seed = 42,
    distance_metrics_list = my_distance_metrics
)

write_csv(settings_matrix, proc_path("settings_matrix.csv", TRUE))

settings_matrix <- read_csv(
    proc_path(
        "2023_12_01_settings_matrix.csv"
    )
)

###############################################################################
# 4. SNF
###############################################################################
# mTBI only imputed
# Imputation 1
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m1 <- batch_snf(
        data_list = data_list_m1,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m1, proc_path("solutions_matrix_m1.csv", TRUE))
# Imputation 2
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m2 <- batch_snf(
        data_list = data_list_m2,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m2, proc_path("solutions_matrix_m2.csv", TRUE))
# Imputation 3
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m3 <- batch_snf(
        data_list = data_list_m3,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m3, proc_path("solutions_matrix_m3.csv", TRUE))
# Imputation 4
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m4 <- batch_snf(
        data_list = data_list_m4,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m4, proc_path("solutions_matrix_m4.csv", TRUE))
# Imputation 5
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m5 <- batch_snf(
        data_list = data_list_m5,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m5, proc_path("solutions_matrix_m5.csv", TRUE))

# mTBI and uninjured pooled imputed
# Imputation 1
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm1 <- batch_snf(
        data_list = data_list_pm1,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm1, proc_path("solutions_matrix_pm1.csv", TRUE))
# Imputation 2
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm2 <- batch_snf(
        data_list = data_list_pm2,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm2, proc_path("solutions_matrix_pm2.csv", TRUE))
# Imputation 3
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm3 <- batch_snf(
        data_list = data_list_pm3,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm3, proc_path("solutions_matrix_pm3.csv", TRUE))
# Imputation 4
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm4 <- batch_snf(
        data_list = data_list_pm4,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm4, proc_path("solutions_matrix_pm4.csv", TRUE))
# Imputation 5
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm5 <- batch_snf(
        data_list = data_list_pm5,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm5, proc_path("solutions_matrix_pm5.csv", TRUE))
```

That covers 10 different imputed mTBI datasets: 5 that were imputed with only the mTBI subjects, and 5 that were imputed with both mTBI and uninjured subjects.

Now a check to see how much the clusters varied by imputation.

```{r}

solutions_matrix_m1 <- read_csv(proc_path("2023_12_07_solutions_matrix_m1.csv"))
solutions_matrix_m2 <- read_csv(proc_path("2023_12_07_solutions_matrix_m2.csv"))
solutions_matrix_m3 <- read_csv(proc_path("2023_12_07_solutions_matrix_m3.csv"))
solutions_matrix_m4 <- read_csv(proc_path("2023_12_07_solutions_matrix_m4.csv"))
solutions_matrix_m5 <- read_csv(proc_path("2023_12_07_solutions_matrix_m5.csv"))
solutions_matrix_pm1 <- read_csv(proc_path("2023_12_07_solutions_matrix_pm1.csv"))
solutions_matrix_pm2 <- read_csv(proc_path("2023_12_07_solutions_matrix_pm2.csv"))
solutions_matrix_pm3 <- read_csv(proc_path("2023_12_07_solutions_matrix_pm3.csv"))
solutions_matrix_pm4 <- read_csv(proc_path("2023_12_07_solutions_matrix_pm4.csv"))
solutions_matrix_pm5 <- read_csv(proc_path("2023_12_07_solutions_matrix_pm5.csv"))

aris_m1 <- calc_om_aris(solutions_matrix_m1)
write_csv(data.frame(aris_m1), proc_path("aris_m1.csv", TRUE))
aris_m2 <- calc_om_aris(solutions_matrix_m2)
write_csv(data.frame(aris_m2), proc_path("aris_m2.csv", TRUE))
aris_m3 <- calc_om_aris(solutions_matrix_m3)
write_csv(data.frame(aris_m3), proc_path("aris_m3.csv", TRUE))
aris_m4 <- calc_om_aris(solutions_matrix_m4)
write_csv(data.frame(aris_m4), proc_path("aris_m4.csv", TRUE))
aris_m5 <- calc_om_aris(solutions_matrix_m5)
write_csv(data.frame(aris_m5), proc_path("aris_m5.csv", TRUE))
aris_pm1 <- calc_om_aris(solutions_matrix_pm1)
write_csv(data.frame(aris_pm1), proc_path("aris_pm1.csv", TRUE))
aris_pm2 <- calc_om_aris(solutions_matrix_pm2)
write_csv(data.frame(aris_pm2), proc_path("aris_pm2.csv", TRUE))
aris_pm3 <- calc_om_aris(solutions_matrix_pm3)
write_csv(data.frame(aris_pm3), proc_path("aris_pm3.csv", TRUE))
aris_pm4 <- calc_om_aris(solutions_matrix_pm4)
write_csv(data.frame(aris_pm4), proc_path("aris_pm4.csv", TRUE))
aris_pm5 <- calc_om_aris(solutions_matrix_pm5)
write_csv(data.frame(aris_pm5), proc_path("aris_pm5.csv", TRUE))
all_mtbi_imputations <- do.call(
    "rbind",
    list(
        solutions_matrix_m1,
        solutions_matrix_m2,
        solutions_matrix_m3,
        solutions_matrix_m4,
        solutions_matrix_m5,
        solutions_matrix_pm1,
        solutions_matrix_pm2,
        solutions_matrix_pm3,
        solutions_matrix_pm4,
        solutions_matrix_pm5
    )
)
aris_all_mtbi_imputations <- calc_om_aris(all_mtbi_imputations)
write_csv(data.frame(aris_all_mtbi_imputations), proc_path("aris_all_mtbi_imputations.csv", TRUE))

aris_m1 <- read_csv(proc_path("2023_12_07_aris_m1.csv")) |> as.matrix()
aris_m2 <- read_csv(proc_path("2023_12_07_aris_m2.csv")) |> as.matrix()
aris_m3 <- read_csv(proc_path("2023_12_07_aris_m3.csv")) |> as.matrix()
aris_m4 <- read_csv(proc_path("2023_12_07_aris_m4.csv")) |> as.matrix()
aris_m5 <- read_csv(proc_path("2023_12_07_aris_m5.csv")) |> as.matrix()
aris_pm1 <- read_csv(proc_path("2023_12_07_aris_pm1.csv")) |> as.matrix()
aris_pm2 <- read_csv(proc_path("2023_12_07_aris_pm2.csv")) |> as.matrix()
aris_pm3 <- read_csv(proc_path("2023_12_07_aris_pm3.csv")) |> as.matrix()
aris_pm4 <- read_csv(proc_path("2023_12_07_aris_pm4.csv")) |> as.matrix()
aris_pm5 <- read_csv(proc_path("2023_12_07_aris_pm5.csv")) |> as.matrix()
aris_all_mtbi_imputations <- read_csv(proc_path("2023_12_07_aris_all_mtbi_imputations.csv")) |> as.matrix()


aris_all_mtbi_imputations_heatmap <- similarity_matrix_heatmap(
    aris_all_mtbi_imputations,
    log_graph = FALSE,
    cluster_rows = TRUE,
    cluster_columns = TRUE
)

aris_all_mtbi_imputations_heatmap <- ComplexHeatmap::draw(aris_all_mtbi_imputations_heatmap)

aris_all_mtbi_imputations_order <- ComplexHeatmap::row_order(aris_all_mtbi_imputations_heatmap)

aris_all_mtbi_imputations_order

write_csv(data.frame(aris_all_mtbi_imputations_order), proc_path("aris_all_mtbi_imputations_order.csv", TRUE))

aris_all_mtbi_imputations_order <- unlist(read_csv(proc_path("2023_12_07_aris_all_mtbi_imputations_order.csv")))

names(aris_all_mtbi_imputations_order) <- NULL

imputation_labels <- data.frame(
    "imputation" = c(
        rep("m1", 200),
        rep("m2", 200),
        rep("m3", 200),
        rep("m4", 200),
        rep("m5", 200),
        rep("pm1", 200),
        rep("pm2", 200),
        rep("pm3", 200),
        rep("pm4", 200),
        rep("pm5", 200)
    ),
    "pooled" = c(
        rep("yes", 1000),
        rep("no", 1000)
    )
)

head(imputation_labels)

colnames(imputation_labels)

"imputation"

aris_all_mtbi_imputations

aris_all_mtbi_imputations_order

imputation_labels

aris_all_mtbi_imputations_annotated_heatmap <- similarity_matrix_heatmap(
    aris_all_mtbi_imputations,
    order = aris_all_mtbi_imputations_order,
    log_graph = FALSE,
    data = imputation_labels,
    top_hm = list(
        "imputation" = "imputation"
    ),
    left_hm = list(
        "pooled" = "pooled"
    ),
    scale_diag = "none",
    #heatmap_height = grid::unit(19, "cm"),
    #heatmap_width = grid::unit(19, "cm"),
    annotation_colours = list(
        "pooled" = c(
            "yes" = "orange",
            "no" = "purple"
        )
    ),
    col = circlize::colorRamp2(
        c(min(aris_all_mtbi_imputations), max(aris_all_mtbi_imputations)),
        c("navy", "red")
    )
)

aris_all_mtbi_imputations_annotated_heatmap


# PNG export
grDevices::png(
    fig_path("aris_all_mtbi_imputations_annotated_heatmap.png", TRUE),
    width = 4000,
    height = 3000,
    res = 400
)
aris_all_mtbi_imputations_annotated_heatmap
grDevices::dev.off()


```


```{r}
###############################################################################
# 4. Calculate pairwise solution similarities
###############################################################################
aris_m1 <- calc_om_aris(solutions_matrix_m1)

write_csv(data.frame(aris_m1), proc_path("aris_m1.csv", TRUE))

aris_m1 <- read_csv(proc_path("2023_12_01_aris_m1.csv"))
aris_m1 <- as.matrix(aris_m1)
colnames(aris_m1) <- 1:nrow(aris_m1)
rownames(aris_m1) <- 1:nrow(aris_m1)
```

Back to more lightweight functions:

```{r}
###############################################################################
# 5. Extract order of pairwise solution similarities
###############################################################################
aris_m1_heatmap <- similarity_matrix_heatmap(
    aris_m1,
    log_graph = FALSE,
    cluster_rows = TRUE,
    cluster_columns = TRUE,
)

aris_m1_heatmap <- ComplexHeatmap::draw(aris_m1_heatmap)

aris_m1_order <- ComplexHeatmap::row_order(aris_m1_heatmap)

write_csv(data.frame(aris_m1_order), proc_path("aris_m1_order.csv", TRUE))

aris_m1_order <- unlist(read_csv(proc_path("2023_12_01_aris_m1_order.csv")))

###############################################################################
# 5. Visualize reordered settings matrix and similarity matrix
###############################################################################
# No saving
settings_matrix_heatmap(
    settings_matrix,
    order = aris_m1_order,
    show_rownames = FALSE
)

settings_matrix_heatmap(
    settings_matrix,
    order = aris_m1_order,
    show_rownames = FALSE,
    save = fig_path("aris_m1_ordered_settings_matrix_heatmap.png", TRUE)
)
```

By visual inspection, there appears to be non-random organization based on the parameters k, and snf_scheme.
Below is the actual adjusted rand index heatmap with these hyperparameters highlighted.

```{r}

aris_m1_annotated_heatmap <- similarity_matrix_heatmap(
    aris_m1,
    order = aris_m1_order,
    log_graph = FALSE,
    data = solutions_matrix_m1,
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    top_hm = list(
        "Scheme" = "snf_scheme"
    ),
    bottom_bar = list(
        "K" = "k"
    ),
    scale_diag = "none",
    heatmap_height = grid::unit(19, "cm"),
    heatmap_width = grid::unit(19, "cm"),
    annotation_colours = list(
        "Scheme" = c(
            "1" = "#7FC97F",
            "2" = "#BEAED4",
            "3" = "#FDC086"
        )
    ),
    col = circlize::colorRamp2(
        c(min(aris_m1), max(aris_m1)),
        c("navy", "red")
    )
)

# No saving
aris_m1_annotated_heatmap

# PDF export
grDevices::pdf(
    fig_path("aris_m1_annotated_heatmap.pdf", TRUE),
    width = 10,
    height = 10
)
aris_m1_annotated_heatmap
grDevices::dev.off()

# PNG export
grDevices::png(
    fig_path("aris_m1_annotated_heatmap.png", TRUE),
    width = 4000,
    height = 3000,
    res = 400
)
aris_m1_annotated_heatmap
grDevices::dev.off()
```

A few "meta clusters" are visible in the pairwise ARI heatmap.

Let's see how they associate with the out of model measures:

```{r}

extended_solutions_matrix_m1 <- extend_solutions(
    solutions_matrix_m1,
    oom_list_m1
)

write_csv(
    extended_solutions_matrix_m1,
    proc_path(
        "extended_solutions_matrix_m1.csv",
        TRUE
    )
)

extended_solutions_matrix_m1 <- read_csv(
    proc_path(
        "2023_12_04_extended_solutions_matrix_m1.csv"
    )
)

pval_select <- function(extended_solutions_matrix,
                        keep_summary = TRUE,
                        negative_log = FALSE,
                        recalculate_summary = TRUE) {
    pval_df <- extended_solutions_matrix |>
        dplyr::select(
            "row_id",
            dplyr::ends_with("_p"),
            dplyr::contains("p_val")
        ) |>
        data.frame() |>
        numcol_to_numeric()
    if (!keep_summary) {
        pval_df <- pval_df |>
            dplyr::select(-c("min_p_val", "mean_p_val"))
    }
    if (negative_log) {
        neg_log_pval_df <- -log(pval_df)
        neg_log_pval_df$"row_id" <- pval_df$"row_id"
        pval_df <- neg_log_pval_df
        if (recalculate_summary) {
            mini_df <- pval_df |> dplyr::select(
                dplyr::ends_with("_p")
            )
            pval_df$"mean_neglog_p" <- apply(mini_df, 1, FUN = mean)
            pval_df$"max_neglog_p" <- apply(mini_df, 1, FUN = max)
        }
    }
    return(pval_df)
}

oom_m1_pvals <- pval_select(
    extended_solutions_matrix_m1,
    negative_log = TRUE
)


pval_heatmap <- function(pval_df, order, max_red = FALSE) {
    pval_df <- pval_df |> dplyr::select(-"row_id")
    pval_matrix <- as.matrix(pval_df[order, ])
    hm <- ComplexHeatmap::Heatmap(
        pval_matrix,
        cluster_rows = FALSE,
        cluster_columns = FALSE,
        show_row_names = FALSE,
        col = hm_colours(pval_matrix, max_red)
    )
    return(hm)
}
pval_hm_m1 <- pval_heatmap(oom_m1_pvals, order = aris_m1_order, max_red = TRUE)

# No saving
pval_hm_m1

# PNG export
grDevices::png(
    fig_path("pval_hm_m1.png", TRUE),
    width = 4000,
    height = 3000,
    res = 400
)
pval_hm_m1
grDevices::dev.off()

extended_solutions_matrix_m1$"mean_neglog_p" <- oom_m1_pvals$"mean_neglog_p"

aris_m1_extended_annotated_heatmap <- similarity_matrix_heatmap(
    aris_m1,
    order = aris_m1_order,
    log_graph = FALSE,
    data = extended_solutions_matrix_m1,
    bottom_hm = list(
        "SNF Scheme" = "snf_scheme"
    ),
    top_hm = list(
        "Impairment Separation" = "mean_neglog_p"
    ),
    bottom_bar = list(
        "K" = "k",
        "Number of Clusters" = "nclust"
    ),
    scale_diag = "none",
    heatmap_height = grid::unit(19, "cm"),
    heatmap_width = grid::unit(19, "cm"),
    annotation_colours = list(
        "SNF Scheme" = c(
            "1" = "orange",
            "2" = "purple",
            "3" = "turquoise"
        ),
        "Impairment Separation" = hm_colours(oom_m1_pvals$"mean_neglog_p")
    ),
    col = circlize::colorRamp2(
        c(min(aris_m1), max(aris_m1)),
        c("navy", "red")
    )
)

# No saving
aris_m1_extended_annotated_heatmap

# PNG export
grDevices::png(
    fig_path("aris_m1_extended_annotated_heatmap.png", TRUE),
    width = 4000,
    height = 3000,
    res = 400
)
aris_m1_extended_annotated_heatmap
grDevices::dev.off()
```

Next steps:

- repeat for the other imputations and see how well the structure holds.
