# SNF in mTBI

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subjects <- read_csv(sub_path("2024_04_17_mtbi_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2024_04_17_uninjured_subjects.csv"))

mtbi_train_subjects <- read_csv(sub_path("2024_04_18_mtbi_train_subjects.csv"))

source("abcd/functions.R")
```

## Loading data and out of model lists

```{r}
all_dls <- list.load(input_path("2024_04_19_all_dls.rds"))
```

## Generating custom distance measures

```{r}
###############################################################################
# 2. Add standard normalized variations to the distance metrics list (also
# achievable through toggling automatic_standard_normalize parameter in
# `batch_snf`)
###############################################################################
my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

summarize_distance_metrics_list(my_distance_metrics)
```

## Generating the settings matrix

```{r}
mtbi_settings_matrix <- generate_settings_matrix(
    all_dls$"mtbi_train_data_lists"$"imp_1",
    nrow = 200,
    seed = 42,
    distance_metrics_list = my_distance_metrics
)

write_csv(mtbi_settings_matrix, proc_path("mtbi_settings_matrix.csv", TRUE))

mtbi_settings_matrix <- read_csv(
    proc_path("2024_04_19_mtbi_settings_matrix.csv")
)
```

## SNF for each of the imputations

```{r}
mtbi_train_dls <- c(
    all_dls$"mtbi_train_data_lists",
    all_dls$"mtbi_pooled_data_lists"
)

names(mtbi_train_dls) <- c(paste0("imp_", 1:5), paste0("pooled_imp_", 1:5))

mtbi_train_solutions_matrices <- lapply(
    mtbi_train_dls,
    function(imputed_dl) {
        summarize_dl(imputed_dl)
        solutions_matrix <- batch_snf(
            data_list = imputed_dl,
            settings_matrix = mtbi_settings_matrix,
            distance_metrics_list = my_distance_metrics,
            processes = "max"
        )
    }
)

list.save(
    mtbi_train_solutions_matrices,
    input_path("mtbi_train_solutions_matrices.rds", TRUE)
)

mtbi_train_solutions_matrices <- list.load(
    input_path("2024_04_22_mtbi_train_solutions_matrices.rds")
)

mtbi_sm <- do.call(
    "rbind",
    mtbi_train_solutions_matrices
)

write_csv(data.frame(mtbi_sm), proc_path("mtbi_sm.csv", TRUE))
```

## Re-importing the generated solutions

```{r}

mtbi_ari <- calc_om_aris(mtbi_sm, processes = "max")
write_csv(data.frame(mtbi_ari), proc_path("mtbi_ari.csv", TRUE))

mtbi_ari_order <- ari_order(mtbi_ari)
write_csv(data.frame(mtbi_ari_order), proc_path("mtbi_ari_order.csv", TRUE))
```

```{r}
mtbi_sm <- read_csv(proc_path("2024_04_23_mtbi_sm.csv"))
mtbi_ari <- as.matrix(read_csv(proc_path("2024_04_23_mtbi_ari.csv")))
mtbi_ari_order <- unlist(read_csv(proc_path("2024_04_23_mtbi_ari_order.csv")))
names(mtbi_ari_order) <- NULL
```

## Full imputation meta clustering plot with impairment levels

```{r}

imputation_labels <- data.frame(
    "imputation" = c(
        rep("m1", 200),
        rep("m2", 200),
        rep("m3", 200),
        rep("m4", 200),
        rep("m5", 200),
        rep("pm1", 200),
        rep("pm2", 200),
        rep("pm3", 200),
        rep("pm4", 200),
        rep("pm5", 200)
    ),
    "pooled" = c(
        rep("yes", 1000),
        rep("no", 1000)
    )
)

###############################################################################
# Setting up merged data lists and outcome lists for visualizing p-values over
# inputs and outputs.
###############################################################################
mtbi_train_dls <- c(
    all_dls$"mtbi_train_data_lists",
    all_dls$"mtbi_pooled_data_lists"
)

mtbi_train_ols <- c(
    all_dls$"mtbi_train_oom_lists",
    all_dls$"mtbi_pooled_oom_lists"
)

mtbi_train_dls_ols <- lapply(
    1:10,
    function(x) {
        c(mtbi_train_dls[[x]], mtbi_train_ols[[x]])
    }
)

names(mtbi_train_dls_ols) <- c(
    paste0("m", 1:5),
    paste0("pm", 1:5)
)

mtbi_sm_l <- cbind(mtbi_sm, imputation_labels)

mtbi_esm <- extend_solutions_imp(
    mtbi_sm_l,
    imputed_targets = mtbi_train_dls_ols,
    min_pval = 1e-10,
    calculate_summaries = FALSE,
    processes = "max"
)
write_csv(mtbi_esm, proc_path("mtbi_esm.csv", TRUE))
```

```{r}
mtbi_esm <- read_csv(proc_path("2024_04_23_mtbi_esm.csv"))
```

```{r}
library(plotly)
library(ComplexHeatmap)
library(InteractiveComplexHeatmap)

mtbi_mc_heatmap <- lite_similarity_matrix_heatmap(
    aris = mtbi_ari,
    aris_order = mtbi_ari_order,
    extended_solutions = mtbi_esm
)

# Plot the heatmap
ht_plot <- draw(mtbi_mc_heatmap)

htShiny(
    ht_plot,
    response = "click",
    title = "Meta Cluster Identification",
    description = paste0(
        "Click on the heatmap to identify the indices of the meta cluster",
        " boundaries. You can recreate the similarity matrix heatmap",
        " passing these values as the `split_vector` argument to have the",
        " meta clusters visually separated and labeled. For example,",
        " if the boundaries of the meta clusters were at row/column indices",
        " 150, 300, and 313, use the argument",
        " `split_vector = c(150, 300, 313) when recreating the heatmap."
    )
)

mtbi_split_vec <- c(
    233,
    380,
    672,
    830,
    978,
    1240,
    1465
)

mtbi_mc_heatmap_lite <- lite_similarity_matrix_heatmap(
    aris = mtbi_ari,
    aris_order = mtbi_ari_order,
    extended_solutions = mtbi_esm,
    split_vector = mtbi_split_vec
)
mtbi_mc_heatmap_lite

mc_heatmap_save(
    mtbi_mc_heatmap_lite,
    fig_path("mtbi_mc_heatmap_lite.png", TRUE)
)

write_csv(data.frame(mtbi_split_vec), proc_path("mtbi_split_vec.csv", TRUE))

mtbi_split_vec <- read_csv(proc_path("2024_04_23_mtbi_split_vec.csv")) |>
    unlist() |>
    as.numeric()

```

```{r}

# Function to try to lean on mTBI-including solutions when possible.
restrict_fn <- function(x, threshold = 0.1) {
    x_solo_ind <- x$"imputation" %in% c("m1", "m2", "m3", "m4", "m5")
    x_pool_ind <- x$"imputation" %in% c("pm1", "pm2", "pm3", "pm4", "pm5")
    x_solo <- x[x_solo_ind, ]
    x_pool <- x[x_pool_ind, ]
    frac_solo <- nrow(x_solo) / (nrow(x_solo) + nrow(x_pool))
    if (frac_solo < threshold) {
        return(x_pool_ind)
    } else {
        return(x_solo_ind)
    }
}

# Representative solutions
mtbi_rep <- get_rep_solutions(
    ari = mtbi_ari,
    split_vector = mtbi_split_vec,
    ari_order = mtbi_ari_order,
    solutions_matrix = mtbi_esm,
    exclude_mcs = "G",
    restriction_function = restrict_fn
)

write_csv(mtbi_rep, proc_path("mtbi_rep.csv", TRUE))

mtbi_rep <- read_csv(proc_path("2024_04_23_mtbi_rep.csv"))



mtbi_train_ols[[1]]

mtbi_manhattan <- manhattan_plot2(
    mtbi_rep,
    data_list = mtbi_train_dls[[1]],
    target_list = mtbi_train_ols[[1]],
    threshold = 0.05
)
mtbi_manhattan

ggsave(
    plot = mtbi_manhattan,
    filename = fig_path("mtbi_manhattan.png", TRUE),
    width = 18,
    height = 7 * 2,
    dpi = 120
)

mtbi_mc_a_manhattan <- mtbi_rep |>
    dplyr::filter(mc == "A") |>
    manhattan_plot2(
        data_list = mtbi_train_dls[[1]],
        target_list = mtbi_train_ols[[1]],
        threshold = 0.05
    )
mtbi_mc_a_manhattan

ggsave(
    plot = mtbi_mc_a_manhattan,
    filename = fig_path("mtbi_mc_a_manhattan.png", TRUE),
    width = 18,
    height = 6,
    dpi = 100
)

plot_solutions_matrix

mc_a_cluster_df <- mtbi_rep |>
    dplyr::filter(mc == "A") |>
    get_cluster_df()

mtbi_mc_a_plots <- characterize_solution(
    cluster_df = mc_a_cluster_df,
    data_list = c(
        all_dls$"mtbi_train_data_lists"$"imp_3",
        all_dls$"mtbi_train_oom_lists"$"imp_3"
    ),
    plotname = fig_path("mtbi_mc_a", TRUE),
    individual_plots = TRUE,
    group_plots = TRUE
)

mtbi_rep |>
    dplyr::filter(mc == "A") |>
    plot_solutions_matrix(
        "mtbi",
        possible_data = mtbi_train_dls_ols,
        individual_plots = TRUE,
        group_plots = TRUE
    )

```

# Label propagation

This top solution specifically came from the third imputed dataset, so that's what we'll label propagate off of.

```{r}

all_dls |> names()

train_data_list_m3 <- all_dls$"mtbi_train_data_lists"$"imp_3"

test_data_list_m1 <- all_dls$"mtbi_test_data_lists"$"imp_1"

full_data_list <- merge_data_lists(train_data_list_m3, test_data_list_m1)

#full_data_list_m3 <- list.load(input_path("2024_03_17_full_data_list_m3.rds"))
#test_data_list_m3 <- list.load(input_path("2024_03_17_test_data_list_m3.rds"))
#test_oom_list_m3 <- list.load(input_path("2024_03_17_test_oom_list_m3.rds"))

my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

mtbi_mc_a <- mtbi_rep[1, ]

set.seed(42)
mtbi_mc_a_lp <- lp_solutions_matrix(
    mtbi_mc_a,
    full_data_list,
    distance_metrics_list = my_distance_metrics
)
colnames(mtbi_mc_a_lp) <- c("subjectkey", "group", "cluster")

mtbi_mc_a_lp <- mtbi_mc_a_lp |>
    dplyr::filter(group == "test") |>
    dplyr::select(-group)

write_csv(mtbi_mc_a_lp, proc_path("mtbi_mc_a_lp.csv", TRUE))

mtbi_mc_a_lp <- read_csv(proc_path("2024_04_23_mtbi_mc_a_lp.csv"))

mtbi_mc_a_lp_plots <- characterize_solution(
    cluster_df = mtbi_mc_a_lp,
    data_list = c(
        all_dls$"mtbi_test_data_lists"$"imp_1",
        all_dls$"mtbi_test_oom_lists"$"imp_1"
    ),
    plotname = fig_path("mtbi_mc_a_lp", TRUE),
    individual_plots = TRUE,
    group_plots = TRUE
)

```

(Leave below for later)

# Longitudinal analyses

```{r}

mtbi_train <- read_csv(sub_path("2024_03_12_mtbi_train_subjects.csv"))

core_path <- path_maker(here(paste0("data/abcd/core")))

import <- function(path) {
    return(abcd_load(core_path(path)))
}

mh_p_cbcl <- import("mental-health/mh_p_cbcl.csv")
ph_p_sds <- import("physical-health/ph_p_sds.csv")

syndromes <- c(
    "anxdep",
    "withdep",
    "somatic",
    "social",
    "thought",
    "attention",
    "rulebreak",
    "aggressive"
)

for (tp in c(1, 2, 3)) {
    long_outcomes <- NULL
    for (syndrome in syndromes) {
        if (is.null(long_outcomes)) {
            long_outcomes <- get_cbcl_syndrome_scale(
                syndrome = syndrome,
                mh_p_cbcl,
                raw = FALSE,
                subjects = mtbi_train,
                t = tp
            )
        } else {
            long_outcomes <- dplyr::inner_join(
                long_outcomes,
                get_cbcl_syndrome_scale(
                    syndrome = syndrome,
                    mh_p_cbcl,
                    raw = FALSE,
                    subjects = mtbi_train,
                    t = tp
                ),
                by = "subjectkey"
            )
        }
    }
    long_outcomes <- dplyr::inner_join(
        long_outcomes,
        get_sds_total_probs(
            ph_p_sds,
            mtbi_train,
            t = tp
        ),
        by = "subjectkey"
    )
    long_outcomes$"subjectkey" <- paste0("subject_", long_outcomes$"subjectkey")
    colnames(long_outcomes) <- c(
        "subjectkey",
        paste0("cbcl_", syndromes),
        "sds_sleep"
    )
    baseline_outcomes <- collapse_dl(oom_list_m3)
    d_outcomes <- NULL
    for (outcome in colnames(baseline_outcomes[-1])) {
        t0 <- dplyr::select(baseline_outcomes, "subjectkey", outcome)
        tn <- dplyr::select(long_outcomes, "subjectkey", outcome)
        colnames(t0) <- c("subjectkey", paste0(outcome, "_0"))
        colnames(tn) <- c("subjectkey", paste0(outcome, "_", tp))
        both_t <- dplyr::inner_join(t0, tn, by = "subjectkey")
        both_t[, 4] <- both_t[, 3] - both_t[, 2]
        colnames(both_t)[4] <- paste0("d_", outcome)
        both_t <- both_t[, c(1, 4)]
        if (is.null(d_outcomes)) {
            d_outcomes <- both_t
        } else {
            d_outcomes <- dplyr::full_join(d_outcomes, both_t, by = "subjectkey")
        }
    }
    mtbi_mc_a <- mtbi_rep[1, ]
    mtbi_mc_a <- get_cluster_df(mtbi_mc_a)
    mtbi_mc_a <- dplyr::full_join(
        mtbi_mc_a,
        d_outcomes,
        by = "subjectkey"
    )
    mtbi_mc_a$"cluster" <- factor(mtbi_mc_a$"cluster")
    d_plots <- list()
    for (outcome in colnames(d_outcomes)[-1]) {
        plot <- mtbi_mc_a |>
            ggplot(
                aes(
                    x = cluster,
                    y = !!sym(outcome),
                    colour = cluster
                )
            ) +
            geom_violin(alpha = 0.4) +
            geom_jitter(width = 0.2, height = 0.2) +
            stat_summary(
                fun = "mean",
                geom = "point",
                colour = "black",
                size = 2
            ) +
            labs(
                x = "Cluster",
                y = gsub("d_", "Δ", outcome)
            ) +
            theme_bw() +
            theme(
                legend.position = "none"
            )
        d_plots[[length(d_plots) + 1]] <- plot
    }
    d_plots <- d_plots |>
        wrap_plots() +
        plot_annotation(
            paste0("CBCL/SDS Outcomes, ", tp, "-year Follow-Up Minus Baseline"),
            theme = theme(plot.title=element_text(hjust=0.5))
        )
    # Looks like cluster 1 has the higher variance, indicating potential for intervention?
    ggsave(
        plot = d_plots,
        filename = fig_path(
            paste0("mtbi_mc_a_outcomes_t", tp, "_plots.png"),
            TRUE
        ),
        width = 8,
        height = 8,
        dpi = 120
    )
}

full_df <- NULL
for (tp in c(0, 1, 2, 3, 4)) {
    long_outcomes <- NULL
    for (syndrome in syndromes) {
        if (is.null(long_outcomes)) {
            long_outcomes <- get_cbcl_syndrome_scale(
                syndrome = syndrome,
                mh_p_cbcl,
                raw = FALSE,
                subjects = mtbi_train,
                t = tp
            )
            colnames(long_outcomes) <- c("subjectkey", syndrome)
        } else {
            new_df <- get_cbcl_syndrome_scale(
                syndrome = syndrome,
                mh_p_cbcl,
                raw = FALSE,
                subjects = mtbi_train,
                t = tp
            )
            colnames(new_df) <- c("subjectkey", syndrome)
            long_outcomes <- dplyr::full_join(
                long_outcomes,
                new_df,
                by = "subjectkey"
            )
        }
    }
    long_outcomes$"tp" <- tp
    if (is.null(full_df)) {
        full_df <- long_outcomes
    } else {
        full_df <- rbind(full_df, long_outcomes)
    }
}
full_df$"subjectkey" <- paste0("subject_", full_df$"subjectkey")
mtbi_mc_a <- mtbi_rep[1, ]
mtbi_mc_a <- get_cluster_df(mtbi_mc_a)
mtbi_mc_a$"cluster" <- factor(mtbi_mc_a$"cluster")
full_df <- dplyr::full_join(full_df, mtbi_mc_a, by = "subjectkey")
full_df$"tp" <- factor(full_df$"tp")
full_df |>
    dplyr::filter(cluster == 1) |>
    na.omit() |>
    ggplot(
        aes(
            x = tp,
            y = aggressive,
            group = subjectkey,
            colour = cluster
        )
    ) +
    geom_line() +
    geom_point() +
    theme_bw()

nrow(mtbi_mc_a)

head(mtbi_mc_a)

head(long_outcomes)

#for (tp in c(1, 2, 3)) {
#    for (syndrome in syndromes) {
#        if (is.null(long_outcomes)) {
#            long_outcomes <- get_cbcl_syndrome_scale(
#                syndrome = syndrome,
#                mh_p_cbcl,
#                raw = FALSE,
#                subjects = mtbi_train,
#                t = tp
#            )
#        } else {
#            long_outcomes <- dplyr::inner_join(
#                long_outcomes,
#                get_cbcl_syndrome_scale(
#                    syndrome = syndrome,
#                    mh_p_cbcl,
#                    raw = FALSE,
#                    subjects = mtbi_train,
#                    t = tp
#                ),
#                by = "subjectkey"
#            )
#        }
#    }
#    long_outcomes <- dplyr::inner_join(
#        long_outcomes,
#        get_sds_total_probs(
#            ph_p_sds,
#            mtbi_train,
#            t = tp
#        ),
#        by = "subjectkey"
#    )
#    long_outcomes$"subjectkey" <- paste0("subject_", long_outcomes$"subjectkey")
#    colnames(long_outcomes) <- c(
#        "subjectkey",
#        paste0("cbcl_", syndromes),
#        "sds_sleep"
#    )
#    baseline_outcomes <- collapse_dl(oom_list_m3)
#    d_outcomes <- NULL
#    for (outcome in colnames(baseline_outcomes[-1])) {
#        t0 <- dplyr::select(baseline_outcomes, "subjectkey", outcome)
#        tn <- dplyr::select(long_outcomes, "subjectkey", outcome)
#        colnames(t0) <- c("subjectkey", paste0(outcome, "_0"))
#        colnames(tn) <- c("subjectkey", paste0(outcome, "_", tp))
#        both_t <- dplyr::inner_join(t0, tn, by = "subjectkey")
#        both_t[, 4] <- both_t[, 3] - both_t[, 2]
#        colnames(both_t)[4] <- paste0("d_", outcome)
#        both_t <- both_t[, c(1, 4)]
#        if (is.null(d_outcomes)) {
#            d_outcomes <- both_t
#        } else {
#            d_outcomes <- dplyr::full_join(d_outcomes, both_t, by = "subjectkey")
#        }
#    }
#    mtbi_mc_a <- mtbi_rep[1, ]
#    mtbi_mc_a <- get_cluster_df(mtbi_mc_a)
#    mtbi_mc_a <- dplyr::full_join(
#        mtbi_mc_a,
#        d_outcomes,
#        by = "subjectkey"
#    )
#    mtbi_mc_a$"cluster" <- factor(mtbi_mc_a$"cluster")
#    d_plots <- list()
#    for (outcome in colnames(d_outcomes)[-1]) {
#        plot <- mtbi_mc_a |>
#            ggplot(
#                aes(
#                    x = cluster,
#                    y = !!sym(outcome),
#                    colour = cluster
#                )
#            ) +
#            geom_violin(alpha = 0.4) +
#            geom_jitter(width = 0.2, height = 0.2) +
#            stat_summary(
#                fun = "mean",
#                geom = "point",
#                colour = "black",
#                size = 2
#            ) +
#            labs(
#                x = "Cluster",
#                y = gsub("d_", "Δ", outcome)
#            ) +
#            theme_bw() +
#            theme(
#                legend.position = "none"
#            )
#        d_plots[[length(d_plots) + 1]] <- plot
#    }
#    d_plots <- d_plots |>
#        wrap_plots() +
#        plot_annotation(
#            paste0("CBCL/SDS Outcomes, ", tp, "-year Follow-Up Minus Baseline"),
#            theme = theme(plot.title=element_text(hjust=0.5))
#        )
#    # Looks like cluster 1 has the higher variance, indicating potential for intervention?
#    ggsave(
#        plot = d_plots,
#        filename = fig_path(
#            paste0("mtbi_mc_a_outcomes_t", tp, "_plots.png"),
#            TRUE
#        ),
#        width = 8,
#        height = 8,
#        dpi = 120
#    )
#}

```
