# SNF in mTBI

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subjects <- read_csv(sub_path("2024_04_17_mtbi_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2024_04_17_uninjured_subjects.csv"))

mtbi_train_subjects <- read_csv(sub_path("2024_04_18_mtbi_train_subjects.csv"))
```

## Loading data and out of model lists

```{r}
all_dls <- list.load(input_path("2024_04_19_all_dls.rds"))
```

## Generating custom distance measures

```{r}
###############################################################################
# 2. Add standard normalized variations to the distance metrics list (also
# achievable through toggling automatic_standard_normalize parameter in
# `batch_snf`)
###############################################################################
my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

summarize_distance_metrics_list(my_distance_metrics)
```

## Generating the settings matrix

```{r}
mtbi_settings_matrix <- generate_settings_matrix(
    all_dls$"mtbi_train_data_lists"$"imp_1",
    nrow = 200,
    seed = 42,
    distance_metrics_list = my_distance_metrics
)

write_csv(mtbi_settings_matrix, proc_path("mtbi_settings_matrix.csv", TRUE))

mtbi_settings_matrix <- read_csv(
    proc_path("2024_04_19_mtbi_settings_matrix.csv")
)
```

## SNF for each of the imputations

```{r}
mtbi_train_dls <- c(
    all_dls$"mtbi_train_data_lists",
    all_dls$"mtbi_pooled_data_lists"
)

names(mtbi_train_dls) <- c(paste0("imp_", 1:5), paste0("pooled_imp_", 1:5))

mtbi_train_solutions_matrices <- lapply(
    mtbi_train_dls,
    function(imputed_dl) {
        summarize_dl(imputed_dl)
        solutions_matrix <- batch_snf(
            data_list = imputed_dl,
            settings_matrix = mtbi_settings_matrix,
            distance_metrics_list = my_distance_metrics,
            processes = "max"
        )
    }
)

list.save(
    mtbi_train_solutions_matrices,
    input_path("mtbi_train_solutions_matrices.rds", TRUE)
)

mtbi_train_solutions_matrices <- list.load(
    input_path("2024_04_22_mtbi_train_solutions_matrices.rds")
)

mtbi_sm <- do.call(
    "rbind",
    mtbi_train_solutions_matrices
)

write_csv(data.frame(mtbi_sm), proc_path("mtbi_sm.csv", TRUE))
```

## Re-importing the generated solutions

```{r}
mtbi_ari <- calc_aris(mtbi_sm, processes = "max")
write_csv(data.frame(mtbi_ari), proc_path("mtbi_ari.csv", TRUE))

mtbi_ari_order <- get_matrix_order(mtbi_ari)

write_csv(data.frame(mtbi_ari_order), proc_path("mtbi_ari_order.csv", TRUE))
```

```{r}
mtbi_sm <- read_csv(proc_path("2024_04_23_mtbi_sm.csv"))

mtbi_ari <- as.matrix(read_csv(proc_path("2024_04_23_mtbi_ari.csv")))

mtbi_ari_order <- unlist(read_csv(proc_path("2024_05_27_mtbi_ari_order.csv")))
names(mtbi_ari_order) <- NULL
```

## Full imputation meta clustering plot with impairment levels

```{r}
imputation_labels <- data.frame(
    "imputation" = c(
        rep("m1", 200),
        rep("m2", 200),
        rep("m3", 200),
        rep("m4", 200),
        rep("m5", 200),
        rep("pm1", 200),
        rep("pm2", 200),
        rep("pm3", 200),
        rep("pm4", 200),
        rep("pm5", 200)
    ),
    "pooled" = c(
        rep("yes", 1000),
        rep("no", 1000)
    )
)

mtbi_sm_l <- cbind(mtbi_sm, imputation_labels)

mtbi_sm_solo <- mtbi_sm_l |>
    dplyr::filter(pooled == "no")

mtbi_sm_pooled <- mtbi_sm_l |>
    dplyr::filter(pooled == "yes")

mtbi_esm_m1 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "m1", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_1",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_1",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_m2 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "m2", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_2",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_2",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_m3 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "m3", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_3",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_3",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_m4 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "m4", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_4",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_4",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_m5 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "m5", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_5",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_5",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_pm1 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "pm1", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_1",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_1",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_pm2 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "pm2", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_2",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_2",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_pm3 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "pm3", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_3",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_3",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_pm4 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "pm4", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_4",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_4",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_pm5 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "pm5", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_5",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_5",
    min_pval = 1e-10,
    processes = "max"
)

mtbi_esm <- dplyr::bind_rows(
    mtbi_esm_m1,
    mtbi_esm_m2,
    mtbi_esm_m3,
    mtbi_esm_m4,
    mtbi_esm_m5,
    mtbi_esm_pm1,
    mtbi_esm_pm2,
    mtbi_esm_pm3,
    mtbi_esm_pm4,
    mtbi_esm_pm5
)

mtbi_esm$"impairment_separation" <- -log10(mtbi_esm$"mean_pval")

write_csv(mtbi_esm, proc_path("mtbi_esm.csv", TRUE))
```

```{r}
mtbi_esm <- read_csv(proc_path("2024_05_27_mtbi_esm.csv"))
```

```{r}
base_ari_hm <- adjusted_rand_index_heatmap(
    mtbi_ari,
    order = mtbi_ari_order
)

shiny_annotator(base_ari_hm)

mtbi_split_vec <- c(
    60,
    137,
    275,
    490,
    580,
    940,
    1086,
    1175,
    1435,
    1660
)

write_csv(data.frame(mtbi_split_vec), proc_path("mtbi_split_vec.csv", TRUE))
mtbi_split_vec <- read_csv(proc_path("2024_05_27_mtbi_split_vec.csv")) |>
    unlist() |>
    as.numeric()

divergent_colours <- function(column)  {
    values <- unique(column)
    colours <- RColorBrewer::brewer.pal(n = length(values), name = "Set3")
    names(colours) <- values
    return(colours)
}

full_mtbi_ari_hm <- adjusted_rand_index_heatmap(
    aris = mtbi_ari,
    order = mtbi_ari_order,
    data = mtbi_esm,
    min_colour = "black",
    split_vector = mtbi_split_vec,
    top_hm = list(
        "Impairment Separation" = "impairment_separation"
    ),
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    left_hm = list(
        "Pooled" = "pooled",
        "Imputation" = "imputation"
    ),
    annotation_colours = list(
        "Impairment Separation" = colour_scale(
            mtbi_esm$"impairment_separation",
            min_colour = "gray7",
            max_colour = "limegreen"
        ),
        "Imputation" = divergent_colours(mtbi_esm$"imputation"),
        "Pooled" = c(
            "yes" = "orange",
            "no" = "purple"
        )
    )
)

save_heatmap(
    heatmap = full_mtbi_ari_hm,
    path = fig_path("full_mtbi_ari_hm.png", TRUE),
    width = 950,
    height = 900,
    res = 100
)

lite_mtbi_ari_hm <- adjusted_rand_index_heatmap(
    aris = mtbi_ari,
    order = mtbi_ari_order,
    data = mtbi_esm,
    min_colour = "black",
    split_vector = mtbi_split_vec,
    top_hm = list(
        "Impairment Separation" = "impairment_separation"
    ),
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    annotation_colours = list(
        "Impairment Separation" = colour_scale(
            mtbi_esm$"impairment_separation",
            min_colour = "gray7",
            max_colour = "limegreen"
        )
    )
)

save_heatmap(
    heatmap = lite_mtbi_ari_hm,
    path = fig_path("lite_mtbi_ari_hm.png", TRUE),
    width = 900,
    height = 700,
    res = 100
)
```

When picking out representative solutions, I'd like to preferentially go for solutions that derived from solo rather than pooled imputations, as those solutions have
values for all features.

```{r}

z <- mtbi_esm

z[mtbi_ari_order, "label"] <- label_splits(mtbi_split_vec, 2000)

z$"label"

###############################################################################
# Here i am
###############################################################################

mtbi_rep_solutions <- get_representative_solutions(
    mtbi_ari,
    split_vector = mtbi_split_vec,
    order = mtbi_ari_order,
    mtbi_esm
)
```

```{r}
mtbi_rep_solutions$"imputation"

write_csv(mtbi_rep, proc_path("mtbi_rep.csv", TRUE))

# Solutions B, E, H, K are relatively unstable



mtbi_rep <- read_csv(proc_path("2024_04_23_mtbi_rep.csv"))

        #ggplot2::scale_colour_manual(
        #    values = c(
        #        "I-AS" = "#85929e",
        #        "I-D" = "#bb8fce",
        #        "I-N" = "#e59866",
        #        "I-MH" = "#7fb3d5",
        #        "I-P" = "#52be80",
        #        "O-S" = "#d98880",
        #        "O-B" = "#ff3131"
        #    )
        #) +

mtbi_manhattan <- manhattan_plot2(
    mtbi_rep,
    data_list = mtbi_train_dls[[1]],
    target_list = mtbi_train_ols[[1]],
    threshold = 0.05
)
mtbi_manhattan

ggsave(
    plot = mtbi_manhattan,
    filename = fig_path("mtbi_manhattan.png", TRUE),
    width = 18,
    height = 7 * 2,
    dpi = 120
)

mtbi_mc_a_manhattan <- mtbi_rep |>
    dplyr::filter(mc == "A") |>
    manhattan_plot2(
        data_list = mtbi_train_dls[[1]],
        target_list = mtbi_train_ols[[1]],
        threshold = 0.05
    )
mtbi_mc_a_manhattan

ggsave(
    plot = mtbi_mc_a_manhattan,
    filename = fig_path("mtbi_mc_a_manhattan.png", TRUE),
    width = 18,
    height = 6,
    dpi = 100
)

plot_solutions_matrix

mc_a_cluster_df <- mtbi_rep |>
    dplyr::filter(mc == "A") |>
    get_cluster_df()

mtbi_mc_a_plots <- characterize_solution(
    cluster_df = mc_a_cluster_df,
    data_list = c(
        all_dls$"mtbi_train_data_lists"$"imp_3",
        all_dls$"mtbi_train_oom_lists"$"imp_3"
    ),
    plotname = fig_path("mtbi_mc_a", TRUE),
    individual_plots = TRUE,
    group_plots = TRUE
)

#mtbi_rep |>
#    dplyr::filter(mc == "A") |>
#    plot_solutions_matrix(
#        "mtbi",
#        possible_data = mtbi_train_dls_ols,
#        individual_plots = TRUE,
#        group_plots = TRUE
#    )

mtbi_rep_a <- mtbi_rep |> dplyr::filter(mc == "A")

pvals <- unlist(get_pvals(mtbi_rep_a))

options(scipen = 999)

p.adjust(pvals, method = "holm")

mtbi_train_dls_ols

pval_df <- c(
    all_dls$"mtbi_train_data_lists"$"imp_3",
    all_dls$"mtbi_train_oom_lists"$"imp_3"
)

pval_df <- collapse_dl(pval_df)

pval_df$

a_clusters <- get_cluster_df(mtbi_rep_a)

pval_df <- dplyr::inner_join(a_clusters, pval_df, by = "subjectkey") |>
    tibble::tibble()

pval_df |> colnames()

t.test(
    pval_df$"sds_sleep"[pval_df$cluster == 1],
    pval_df$"sds_sleep"[pval_df$cluster == 2]
)

pval_df$"sds_sleep"[pval_df$cluster == 1]

pval_df$"sds_sleep"[pval_df$cluster == 2]


```

# Label propagation

This top solution specifically came from the third imputed dataset, so that's what we'll label propagate off of.

```{r}

all_dls |> names()

train_data_list_m3 <- all_dls$"mtbi_train_data_lists"$"imp_3"

test_data_list_m1 <- all_dls$"mtbi_test_data_lists"$"imp_1"

full_data_list <- merge_data_lists(train_data_list_m3, test_data_list_m1)

#full_data_list_m3 <- list.load(input_path("2024_03_17_full_data_list_m3.rds"))
#test_data_list_m3 <- list.load(input_path("2024_03_17_test_data_list_m3.rds"))
#test_oom_list_m3 <- list.load(input_path("2024_03_17_test_oom_list_m3.rds"))

my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

mtbi_mc_a <- mtbi_rep[1, ]

set.seed(42)
mtbi_mc_a_lp <- lp_solutions_matrix(
    mtbi_mc_a,
    full_data_list,
    distance_metrics_list = my_distance_metrics
)
colnames(mtbi_mc_a_lp) <- c("subjectkey", "group", "cluster")

mtbi_mc_a_lp <- mtbi_mc_a_lp |>
    dplyr::filter(group == "test") |>
    dplyr::select(-group)

write_csv(mtbi_mc_a_lp, proc_path("mtbi_mc_a_lp.csv", TRUE))

mtbi_mc_a_lp <- read_csv(proc_path("2024_04_23_mtbi_mc_a_lp.csv"))

mtbi_mc_a_lp_plots <- characterize_solution(
    cluster_df = mtbi_mc_a_lp,
    data_list = c(
        all_dls$"mtbi_test_data_lists"$"imp_1",
        all_dls$"mtbi_test_oom_lists"$"imp_1"
    ),
    plotname = fig_path("mtbi_mc_a_lp", TRUE),
    individual_plots = TRUE,
    group_plots = TRUE
)

```

(Leave below for later)

# Longitudinal analyses

```{r}

mtbi_train <- read_csv(sub_path("2024_03_12_mtbi_train_subjects.csv"))

core_path <- path_maker(here(paste0("data/abcd/core")))

import <- function(path) {
    return(abcd_load(core_path(path)))
}

mh_p_cbcl <- import("mental-health/mh_p_cbcl.csv")
ph_p_sds <- import("physical-health/ph_p_sds.csv")

syndromes <- c(
    "anxdep",
    "withdep",
    "somatic",
    "social",
    "thought",
    "attention",
    "rulebreak",
    "aggressive"
)

for (tp in c(1, 2, 3)) {
    long_outcomes <- NULL
    for (syndrome in syndromes) {
        if (is.null(long_outcomes)) {
            long_outcomes <- get_cbcl_syndrome_scale(
                syndrome = syndrome,
                mh_p_cbcl,
                raw = FALSE,
                subjects = mtbi_train,
                t = tp
            )
        } else {
            long_outcomes <- dplyr::inner_join(
                long_outcomes,
                get_cbcl_syndrome_scale(
                    syndrome = syndrome,
                    mh_p_cbcl,
                    raw = FALSE,
                    subjects = mtbi_train,
                    t = tp
                ),
                by = "subjectkey"
            )
        }
    }
    long_outcomes <- dplyr::inner_join(
        long_outcomes,
        get_sds_total_probs(
            ph_p_sds,
            mtbi_train,
            t = tp
        ),
        by = "subjectkey"
    )
    long_outcomes$"subjectkey" <- paste0("subject_", long_outcomes$"subjectkey")
    colnames(long_outcomes) <- c(
        "subjectkey",
        paste0("cbcl_", syndromes),
        "sds_sleep"
    )
    baseline_outcomes <- collapse_dl(oom_list_m3)
    d_outcomes <- NULL
    for (outcome in colnames(baseline_outcomes[-1])) {
        t0 <- dplyr::select(baseline_outcomes, "subjectkey", outcome)
        tn <- dplyr::select(long_outcomes, "subjectkey", outcome)
        colnames(t0) <- c("subjectkey", paste0(outcome, "_0"))
        colnames(tn) <- c("subjectkey", paste0(outcome, "_", tp))
        both_t <- dplyr::inner_join(t0, tn, by = "subjectkey")
        both_t[, 4] <- both_t[, 3] - both_t[, 2]
        colnames(both_t)[4] <- paste0("d_", outcome)
        both_t <- both_t[, c(1, 4)]
        if (is.null(d_outcomes)) {
            d_outcomes <- both_t
        } else {
            d_outcomes <- dplyr::full_join(d_outcomes, both_t, by = "subjectkey")
        }
    }
    mtbi_mc_a <- mtbi_rep[1, ]
    mtbi_mc_a <- get_cluster_df(mtbi_mc_a)
    mtbi_mc_a <- dplyr::full_join(
        mtbi_mc_a,
        d_outcomes,
        by = "subjectkey"
    )
    mtbi_mc_a$"cluster" <- factor(mtbi_mc_a$"cluster")
    d_plots <- list()
    for (outcome in colnames(d_outcomes)[-1]) {
        plot <- mtbi_mc_a |>
            ggplot(
                aes(
                    x = cluster,
                    y = !!sym(outcome),
                    colour = cluster
                )
            ) +
            geom_violin(alpha = 0.4) +
            geom_jitter(width = 0.2, height = 0.2) +
            stat_summary(
                fun = "mean",
                geom = "point",
                colour = "black",
                size = 2
            ) +
            labs(
                x = "Cluster",
                y = gsub("d_", "Δ", outcome)
            ) +
            theme_bw() +
            theme(
                legend.position = "none"
            )
        d_plots[[length(d_plots) + 1]] <- plot
    }
    d_plots <- d_plots |>
        wrap_plots() +
        plot_annotation(
            paste0("CBCL/SDS Outcomes, ", tp, "-year Follow-Up Minus Baseline"),
            theme = theme(plot.title=element_text(hjust=0.5))
        )
    # Looks like cluster 1 has the higher variance, indicating potential for intervention?
    ggsave(
        plot = d_plots,
        filename = fig_path(
            paste0("mtbi_mc_a_outcomes_t", tp, "_plots.png"),
            TRUE
        ),
        width = 8,
        height = 8,
        dpi = 120
    )
}

full_df <- NULL
for (tp in c(0, 1, 2, 3, 4)) {
    long_outcomes <- NULL
    for (syndrome in syndromes) {
        if (is.null(long_outcomes)) {
            long_outcomes <- get_cbcl_syndrome_scale(
                syndrome = syndrome,
                mh_p_cbcl,
                raw = FALSE,
                subjects = mtbi_train,
                t = tp
            )
            colnames(long_outcomes) <- c("subjectkey", syndrome)
        } else {
            new_df <- get_cbcl_syndrome_scale(
                syndrome = syndrome,
                mh_p_cbcl,
                raw = FALSE,
                subjects = mtbi_train,
                t = tp
            )
            colnames(new_df) <- c("subjectkey", syndrome)
            long_outcomes <- dplyr::full_join(
                long_outcomes,
                new_df,
                by = "subjectkey"
            )
        }
    }
    long_outcomes$"tp" <- tp
    if (is.null(full_df)) {
        full_df <- long_outcomes
    } else {
        full_df <- rbind(full_df, long_outcomes)
    }
}
full_df$"subjectkey" <- paste0("subject_", full_df$"subjectkey")
mtbi_mc_a <- mtbi_rep[1, ]
mtbi_mc_a <- get_cluster_df(mtbi_mc_a)
mtbi_mc_a$"cluster" <- factor(mtbi_mc_a$"cluster")
full_df <- dplyr::full_join(full_df, mtbi_mc_a, by = "subjectkey")
full_df$"tp" <- factor(full_df$"tp")
full_df |>
    dplyr::filter(cluster == 1) |>
    na.omit() |>
    ggplot(
        aes(
            x = tp,
            y = aggressive,
            group = subjectkey,
            colour = cluster
        )
    ) +
    geom_line() +
    geom_point() +
    theme_bw()

nrow(mtbi_mc_a)

head(mtbi_mc_a)

head(long_outcomes)

#for (tp in c(1, 2, 3)) {
#    for (syndrome in syndromes) {
#        if (is.null(long_outcomes)) {
#            long_outcomes <- get_cbcl_syndrome_scale(
#                syndrome = syndrome,
#                mh_p_cbcl,
#                raw = FALSE,
#                subjects = mtbi_train,
#                t = tp
#            )
#        } else {
#            long_outcomes <- dplyr::inner_join(
#                long_outcomes,
#                get_cbcl_syndrome_scale(
#                    syndrome = syndrome,
#                    mh_p_cbcl,
#                    raw = FALSE,
#                    subjects = mtbi_train,
#                    t = tp
#                ),
#                by = "subjectkey"
#            )
#        }
#    }
#    long_outcomes <- dplyr::inner_join(
#        long_outcomes,
#        get_sds_total_probs(
#            ph_p_sds,
#            mtbi_train,
#            t = tp
#        ),
#        by = "subjectkey"
#    )
#    long_outcomes$"subjectkey" <- paste0("subject_", long_outcomes$"subjectkey")
#    colnames(long_outcomes) <- c(
#        "subjectkey",
#        paste0("cbcl_", syndromes),
#        "sds_sleep"
#    )
#    baseline_outcomes <- collapse_dl(oom_list_m3)
#    d_outcomes <- NULL
#    for (outcome in colnames(baseline_outcomes[-1])) {
#        t0 <- dplyr::select(baseline_outcomes, "subjectkey", outcome)
#        tn <- dplyr::select(long_outcomes, "subjectkey", outcome)
#        colnames(t0) <- c("subjectkey", paste0(outcome, "_0"))
#        colnames(tn) <- c("subjectkey", paste0(outcome, "_", tp))
#        both_t <- dplyr::inner_join(t0, tn, by = "subjectkey")
#        both_t[, 4] <- both_t[, 3] - both_t[, 2]
#        colnames(both_t)[4] <- paste0("d_", outcome)
#        both_t <- both_t[, c(1, 4)]
#        if (is.null(d_outcomes)) {
#            d_outcomes <- both_t
#        } else {
#            d_outcomes <- dplyr::full_join(d_outcomes, both_t, by = "subjectkey")
#        }
#    }
#    mtbi_mc_a <- mtbi_rep[1, ]
#    mtbi_mc_a <- get_cluster_df(mtbi_mc_a)
#    mtbi_mc_a <- dplyr::full_join(
#        mtbi_mc_a,
#        d_outcomes,
#        by = "subjectkey"
#    )
#    mtbi_mc_a$"cluster" <- factor(mtbi_mc_a$"cluster")
#    d_plots <- list()
#    for (outcome in colnames(d_outcomes)[-1]) {
#        plot <- mtbi_mc_a |>
#            ggplot(
#                aes(
#                    x = cluster,
#                    y = !!sym(outcome),
#                    colour = cluster
#                )
#            ) +
#            geom_violin(alpha = 0.4) +
#            geom_jitter(width = 0.2, height = 0.2) +
#            stat_summary(
#                fun = "mean",
#                geom = "point",
#                colour = "black",
#                size = 2
#            ) +
#            labs(
#                x = "Cluster",
#                y = gsub("d_", "Δ", outcome)
#            ) +
#            theme_bw() +
#            theme(
#                legend.position = "none"
#            )
#        d_plots[[length(d_plots) + 1]] <- plot
#    }
#    d_plots <- d_plots |>
#        wrap_plots() +
#        plot_annotation(
#            paste0("CBCL/SDS Outcomes, ", tp, "-year Follow-Up Minus Baseline"),
#            theme = theme(plot.title=element_text(hjust=0.5))
#        )
#    # Looks like cluster 1 has the higher variance, indicating potential for intervention?
#    ggsave(
#        plot = d_plots,
#        filename = fig_path(
#            paste0("mtbi_mc_a_outcomes_t", tp, "_plots.png"),
#            TRUE
#        ),
#        width = 8,
#        height = 8,
#        dpi = 120
#    )
#}

```
