# Similarity Network Fusion

In this chapter, I use the `metasnf` package to generate many diverse subtyping solutions with SNF.

In the previous chapter, we set up the following datasets:

* 1 original unimputed mTBI dataset
* 1 original unimputed uninjured dataset
* 5 imputed mTBI datasets
* 5 imputed uninjured datasets
* 5 imputed mTBI + uninjured datasets

To keep track of what data we're working with, variables will have the following notation: (m/u/p)(0-5), where m represented mTBI data, u represents uninjured data, p for pooled data, 0 indicating original (unimputed) data, and 1-5 indicating the imputed dataset number.

## Utility functions

```{r}
divergent_colours <- function(column)  {
    values <- unique(column)
    colours <- RColorBrewer::brewer.pal(n = length(values), name = "Set3")
    names(colours) <- values
    return(colours)
}

data_list_metadata <- function(data_list) {
    merged_df <- collapse_dl(data_list)
    merged_df <- merged_df[, colnames(merged_df) != "subjectkey"]
    ###########################################################################
    # Build data.frame containing the types of variables in merged_df
    ###########################################################################
    types <- data_list |> lapply(
        function(x) {
            rep(x$"type", ncol(x$"data") - 1)
        }
    ) |> unlist()
    domains <- data_list |> lapply(
        function(x) {
            rep(x$"domain", ncol(x$"data") - 1)
        }
    ) |> unlist()
    var_names <- colnames(merged_df[, colnames(merged_df) != "subjectkey"])
    metadata <- data.frame(
        name = var_names,
        type = types,
        domain = domains
    )
    return(metadata)
}

rename_data_list <- function(data_list, name_mapping) {
    data_list <- data_list |> lapply(
        function(x) {
            old_colnames <- colnames(x$"data")
            new_colnames <- old_colnames |> lapply(
                function(old_name) {
                    if (old_name %in% name_mapping) {
                        new_name <- names(name_mapping)[which(name_mapping == old_name)]
                    } else {
                        new_name <- old_name
                    }
                    return(new_name)
                }
            )
            colnames(x$"data") <- new_colnames
            return(x)
        }
    )
    return(data_list)
}

keep_numeric <- function(df) {
    df <- numcol_to_numeric(df)
    classes <- as.vector(sapply(df, class))
    df <- df[, classes == "numeric", drop = FALSE]
    return(df)
}

hm_colours <- function(data, max_red = TRUE) {
    if (max_red) {
        colours <- circlize::colorRamp2(
            c(min(data), max(data)),
            c("black", "red")
        )
    } else {
        colours <- circlize::colorRamp2(
            c(min(data), max(data)),
            c("red", "black")
        )
    }
    return(colours)
}

correlation_heatmap <- function(data_list, order = NULL) {
    dl_df <- collapse_dl(data_list)
    numeric_dl_df <- keep_numeric(dl_df)
    correlation_matrix <- cor(numeric_dl_df)
    if (is.null(order)) {
        heatmap <- ComplexHeatmap::Heatmap(correlation_matrix)
    } else {
        heatmap <- ComplexHeatmap::Heatmap(
            correlation_matrix[order, order],
            cluster_rows = FALSE,
            cluster_columns = FALSE
        )
    }
    drawn_heatmap <- ComplexHeatmap::draw(heatmap)
    order <- ComplexHeatmap::row_order(drawn_heatmap)
    results <- list(
        "correlation_matrix" = correlation_matrix,
        "heatmap" = heatmap,
        "order" = order
    )
    return(results)
}

pval_select <- function(extended_solutions_matrix,
                        keep_summary = TRUE,
                        negative_log = FALSE,
                        recalculate_summary = TRUE) {
    pval_df <- extended_solutions_matrix |>
        dplyr::select(
            "row_id",
            dplyr::ends_with("_p"),
            dplyr::contains("p_val")
        ) |>
        data.frame() |>
        numcol_to_numeric()
    if (!keep_summary) {
        pval_df <- pval_df |>
            dplyr::select(-c("min_p_val", "mean_p_val"))
    }
    if (negative_log) {
        neg_log_pval_df <- -log(pval_df)
        neg_log_pval_df$"row_id" <- pval_df$"row_id"
        pval_df <- neg_log_pval_df
        if (recalculate_summary) {
            mini_df <- pval_df |> dplyr::select(
                dplyr::ends_with("_p")
            )
            pval_df$"mean_neglog_p" <- apply(mini_df, 1, FUN = mean)
            pval_df$"max_neglog_p" <- apply(mini_df, 1, FUN = max)
        }
    }
    return(pval_df)
}

pval_heatmap <- function(pval_df, order, max_red = FALSE) {
    pval_df <- pval_df |> dplyr::select(-"row_id")
    pval_matrix <- as.matrix(pval_df[order, ])
    hm <- ComplexHeatmap::Heatmap(
        pval_matrix,
        cluster_rows = FALSE,
        cluster_columns = FALSE,
        show_row_names = FALSE,
        col = hm_colours(pval_matrix, max_red)
    )
    return(hm)
}

split_at <- function(vector, nrow) {
    split_vec <- rep("A", nrow)
    if (vector[length(vector)] != nrow) {
        vector <- c(vector, nrow)
    }
    for (i in 1:(length(vector) - 1)) {
        start <- vector[i]
        end <- vector[i + 1]
        split_vec[start:end] <- LETTERS[i + 1]
    }
    return(split_vec)
}

save_pdf <- function(heatmap, path, width, height) {
    grDevices::pdf(
        path,
        width,
        height
    )
    heatmap
    grDevices::dev.off()
}

save_png <- function(heatmap, path, width, height, res) {
    grDevices::png(
        filename = path,
        width = width,
        height = height,
        res = res
    )
    ComplexHeatmap::draw(heatmap)
    grDevices::dev.off()
}
```

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subjects <- read_csv(sub_path("2023_11_07_mtbi_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2023_11_07_uninjured_subjects.csv"))
```

## Loading data and out of model lists

```{r}
data_list_m1 <- list.load(input_path("2023_12_14_data_list_m1.rds"))
data_list_m2 <- list.load(input_path("2023_12_14_data_list_m2.rds"))
data_list_m3 <- list.load(input_path("2023_12_14_data_list_m3.rds"))
data_list_m4 <- list.load(input_path("2023_12_14_data_list_m4.rds"))
data_list_m5 <- list.load(input_path("2023_12_14_data_list_m5.rds"))
data_list_pm1 <- list.load(input_path("2023_12_14_data_list_pm1.rds"))
data_list_pm2 <- list.load(input_path("2023_12_14_data_list_pm2.rds"))
data_list_pm3 <- list.load(input_path("2023_12_14_data_list_pm3.rds"))
data_list_pm4 <- list.load(input_path("2023_12_14_data_list_pm4.rds"))
data_list_pm5 <- list.load(input_path("2023_12_14_data_list_pm5.rds"))
oom_list_m1 <- list.load(input_path("2023_12_14_oom_list_m1.rds"))
oom_list_m2 <- list.load(input_path("2023_12_14_oom_list_m2.rds"))
oom_list_m3 <- list.load(input_path("2023_12_14_oom_list_m3.rds"))
oom_list_m4 <- list.load(input_path("2023_12_14_oom_list_m4.rds"))
oom_list_m5 <- list.load(input_path("2023_12_14_oom_list_m5.rds"))
oom_list_pm1 <- list.load(input_path("2023_12_14_oom_list_pm1.rds"))
oom_list_pm2 <- list.load(input_path("2023_12_14_oom_list_pm2.rds"))
oom_list_pm3 <- list.load(input_path("2023_12_14_oom_list_pm3.rds"))
oom_list_pm4 <- list.load(input_path("2023_12_14_oom_list_pm4.rds"))
oom_list_pm5 <- list.load(input_path("2023_12_14_oom_list_pm5.rds"))
```

## Some pairwise variable correlations

Examining some of the pairwise associations between all the included (numeric) variables within the first imputed dataset.

```{r}
all_var_dl_m1 <- c(data_list_m1, oom_list_m1)

# First pass to extract the order of columns
correlation_heatmap_data_m1 <- correlation_heatmap(all_var_dl_m1)
correlation_matrix_m1 <- correlation_heatmap_data_m1$"correlation_matrix"
race_cors_m1 <- abs(correlation_matrix_m1[, "race"])
race_order_m1 <- sort(race_cors_m1, index.return = TRUE, decreasing = TRUE)$"ix"
sex_cors_m1 <- abs(correlation_matrix_m1[, "sex"])
sex_order_m1 <- sort(sex_cors_m1, index.return = TRUE, decreasing = TRUE)$"ix"

correlation_heatmap_data_m1$"heatmap"

# All correlations, sorted by abs(cor-race)
save_png(
    correlation_heatmap_data_m1$"heatmap",
    fig_path("correlation_matrix_m1.png", TRUE),
    width = 3500,
    height = 3500,
    res = 300
)

correlation_heatmap_data_m1_race <- correlation_heatmap(
    c(data_list_m1, oom_list_m1),
    order = race_order_m1
)

save_png(
    correlation_heatmap_data_m1_race$"heatmap",
    fig_path("correlation_matrix_m1_race.png", TRUE),
    width = 3500,
    height = 3500,
    res = 300
)

# Race correlations, sorted by abs(cor-race)
grDevices::png(
    fig_path("correlation_matrix_m1_race_only.png", TRUE),
    width = 3500,
    height = 3500
)

ComplexHeatmap::Heatmap(
    correlation_matrix_m1[race_order_m1, "race"],
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    show_column_names = FALSE
)

grDevices::dev.off()

# All correlations, sorted by abs(cor-sex)
grDevices::png(
    fig_path("correlation_matrix_m1_sex.png", TRUE),
    width = 3500,
    height = 3500
)
ComplexHeatmap::Heatmap(
    correlation_matrix_m1[sex_order_m1, sex_order_m1],
    cluster_rows = FALSE,
    cluster_columns = FALSE
)
grDevices::dev.off()

# Sex correlations, sorted by abs(cor-race)
grDevices::png(
    fig_path("correlation_matrix_m1_sex_only.png", TRUE),
    width = 3500,
    height = 3500
)
ComplexHeatmap::Heatmap(
    correlation_matrix_m1[sex_order_m1, "sex"],
    cluster_rows = FALSE,
    cluster_columns = FALSE
)
grDevices::dev.off()
```

## Generating custom distance measures

```{r}
###############################################################################
# 2. Add standard normalized variations to the distance metrics list (also
# achievable through toggling automatic_standard_normalize parameter in
# `batch_snf`)
###############################################################################
my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

summarize_distance_metrics_list(my_distance_metrics)
```

## Generating the settings matrix

```{r}
###############################################################################
# 3. Generate the settings matrix
###############################################################################
settings_matrix <- generate_settings_matrix(
    data_list_m1,
    nrow = 200,
    seed = 42,
    distance_metrics_list = my_distance_metrics
)

write_csv(settings_matrix, proc_path("settings_matrix.csv", TRUE))

settings_matrix <- read_csv(
    proc_path(
        "2023_12_01_settings_matrix.csv"
    )
)
```

## SNF for each of the imputations

```{r}
# mTBI only imputed
# Imputation 1
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m1 <- batch_snf(
        data_list = data_list_m1,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m1, proc_path("solutions_matrix_m1.csv", TRUE))
# Imputation 2
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m2 <- batch_snf(
        data_list = data_list_m2,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m2, proc_path("solutions_matrix_m2.csv", TRUE))
# Imputation 3
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m3 <- batch_snf(
        data_list = data_list_m3,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m3, proc_path("solutions_matrix_m3.csv", TRUE))
# Imputation 4
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m4 <- batch_snf(
        data_list = data_list_m4,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m4, proc_path("solutions_matrix_m4.csv", TRUE))
# Imputation 5
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m5 <- batch_snf(
        data_list = data_list_m5,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m5, proc_path("solutions_matrix_m5.csv", TRUE))

# mTBI and uninjured pooled imputed
# Imputation 1
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm1 <- batch_snf(
        data_list = data_list_pm1,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm1, proc_path("solutions_matrix_pm1.csv", TRUE))
# Imputation 2
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm2 <- batch_snf(
        data_list = data_list_pm2,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm2, proc_path("solutions_matrix_pm2.csv", TRUE))
# Imputation 3
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm3 <- batch_snf(
        data_list = data_list_pm3,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm3, proc_path("solutions_matrix_pm3.csv", TRUE))
# Imputation 4
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm4 <- batch_snf(
        data_list = data_list_pm4,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm4, proc_path("solutions_matrix_pm4.csv", TRUE))
# Imputation 5
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm5 <- batch_snf(
        data_list = data_list_pm5,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm5, proc_path("solutions_matrix_pm5.csv", TRUE))
```

## Re-importing the generated solutions

```{r}
solutions_matrix_m1 <- read_csv(proc_path("2023_12_07_solutions_matrix_m1.csv"))
solutions_matrix_m2 <- read_csv(proc_path("2023_12_07_solutions_matrix_m2.csv"))
solutions_matrix_m3 <- read_csv(proc_path("2023_12_07_solutions_matrix_m3.csv"))
solutions_matrix_m4 <- read_csv(proc_path("2023_12_07_solutions_matrix_m4.csv"))
solutions_matrix_m5 <- read_csv(proc_path("2023_12_07_solutions_matrix_m5.csv"))
solutions_matrix_pm1 <- read_csv(proc_path("2023_12_07_solutions_matrix_pm1.csv"))
solutions_matrix_pm2 <- read_csv(proc_path("2023_12_07_solutions_matrix_pm2.csv"))
solutions_matrix_pm3 <- read_csv(proc_path("2023_12_07_solutions_matrix_pm3.csv"))
solutions_matrix_pm4 <- read_csv(proc_path("2023_12_07_solutions_matrix_pm4.csv"))
solutions_matrix_pm5 <- read_csv(proc_path("2023_12_07_solutions_matrix_pm5.csv"))

all_mtbi_imputations <- do.call(
    "rbind",
    list(
        solutions_matrix_m1,
        solutions_matrix_m2,
        solutions_matrix_m3,
        solutions_matrix_m4,
        solutions_matrix_m5,
        solutions_matrix_pm1,
        solutions_matrix_pm2,
        solutions_matrix_pm3,
        solutions_matrix_pm4,
        solutions_matrix_pm5
    )
)
```

## Calculating pairwise ARIs

```{r}
aris_m1 <- calc_om_aris(solutions_matrix_m1)
write_csv(data.frame(aris_m1), proc_path("aris_m1.csv", TRUE))
aris_m2 <- calc_om_aris(solutions_matrix_m2)
write_csv(data.frame(aris_m2), proc_path("aris_m2.csv", TRUE))
aris_m3 <- calc_om_aris(solutions_matrix_m3)
write_csv(data.frame(aris_m3), proc_path("aris_m3.csv", TRUE))
aris_m4 <- calc_om_aris(solutions_matrix_m4)
write_csv(data.frame(aris_m4), proc_path("aris_m4.csv", TRUE))
aris_m5 <- calc_om_aris(solutions_matrix_m5)
write_csv(data.frame(aris_m5), proc_path("aris_m5.csv", TRUE))
aris_pm1 <- calc_om_aris(solutions_matrix_pm1)
write_csv(data.frame(aris_pm1), proc_path("aris_pm1.csv", TRUE))
aris_pm2 <- calc_om_aris(solutions_matrix_pm2)
write_csv(data.frame(aris_pm2), proc_path("aris_pm2.csv", TRUE))
aris_pm3 <- calc_om_aris(solutions_matrix_pm3)
write_csv(data.frame(aris_pm3), proc_path("aris_pm3.csv", TRUE))
aris_pm4 <- calc_om_aris(solutions_matrix_pm4)
write_csv(data.frame(aris_pm4), proc_path("aris_pm4.csv", TRUE))
aris_pm5 <- calc_om_aris(solutions_matrix_pm5)
write_csv(data.frame(aris_pm5), proc_path("aris_pm5.csv", TRUE))
aris_all_mtbi_imputations <- calc_om_aris(all_mtbi_imputations)
write_csv(data.frame(aris_all_mtbi_imputations), proc_path("aris_all_mtbi_imputations.csv", TRUE))
```

## Re-importing the ARIs

```{r}
aris_m1 <- read_csv(proc_path("2023_12_07_aris_m1.csv")) |> as.matrix()
aris_m2 <- read_csv(proc_path("2023_12_07_aris_m2.csv")) |> as.matrix()
aris_m3 <- read_csv(proc_path("2023_12_07_aris_m3.csv")) |> as.matrix()
aris_m4 <- read_csv(proc_path("2023_12_07_aris_m4.csv")) |> as.matrix()
aris_m5 <- read_csv(proc_path("2023_12_07_aris_m5.csv")) |> as.matrix()
aris_pm1 <- read_csv(proc_path("2023_12_07_aris_pm1.csv")) |> as.matrix()
aris_pm2 <- read_csv(proc_path("2023_12_07_aris_pm2.csv")) |> as.matrix()
aris_pm3 <- read_csv(proc_path("2023_12_07_aris_pm3.csv")) |> as.matrix()
aris_pm4 <- read_csv(proc_path("2023_12_07_aris_pm4.csv")) |> as.matrix()
aris_pm5 <- read_csv(proc_path("2023_12_07_aris_pm5.csv")) |> as.matrix()

aris_all_mtbi_imputations <- read_csv(proc_path("2023_12_07_aris_all_mtbi_imputations.csv")) |> as.matrix()
```

## Plotting the ARIs

### Initial plot across all ARIs to extract order

```{r}
aris_all_mtbi_imputations_heatmap <- similarity_matrix_heatmap(
    aris_all_mtbi_imputations,
    log_graph = FALSE,
    cluster_rows = TRUE,
    cluster_columns = TRUE
)

aris_all_mtbi_imputations_heatmap <- ComplexHeatmap::draw(aris_all_mtbi_imputations_heatmap)
aris_all_mtbi_imputations_order <- ComplexHeatmap::row_order(aris_all_mtbi_imputations_heatmap)
write_csv(data.frame(aris_all_mtbi_imputations_order), proc_path("aris_all_mtbi_imputations_order.csv", TRUE))
```

### Re-importing the order

```{r}
aris_all_mtbi_imputations_order <- unlist(read_csv(proc_path("2023_12_07_aris_all_mtbi_imputations_order.csv")))
names(aris_all_mtbi_imputations_order) <- NULL
```

## Full imputation meta clustering plot with impairment levels

```{r}
imputation_labels <- data.frame(
    "imputation" = c(
        rep("m1", 200),
        rep("m2", 200),
        rep("m3", 200),
        rep("m4", 200),
        rep("m5", 200),
        rep("pm1", 200),
        rep("pm2", 200),
        rep("pm3", 200),
        rep("pm4", 200),
        rep("pm5", 200)
    ),
    "pooled" = c(
        rep("yes", 1000),
        rep("no", 1000)
    )
)

full_solutions_matrix <- cbind(all_mtbi_imputations, imputation_labels)

full_solutions_matrix$"nclust2" <- full_solutions_matrix$"nclust" - 2

full_extended_solutions_matrix <- extend_solutions(
    full_solutions_matrix,
    oom_list_m1
)

write_csv(
    full_extended_solutions_matrix,
    proc_path("full_mtbi_extended_solutions_matrix.csv", TRUE)
)

full_extended_solutions_matrix <- read_csv(proc_path("2023_12_12_full_mtbi_extended_solutions_matrix.csv"))

full_oom_pvals <- pval_select(
    full_extended_solutions_matrix,
    negative_log = TRUE
)

full_extended_solutions_matrix$"mean_neglog_p" <- full_oom_pvals$"mean_neglog_p"

aris_all_mtbi_imputations_annotated_heatmap <- similarity_matrix_heatmap(
    aris_all_mtbi_imputations,
    order = aris_all_mtbi_imputations_order,
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    log_graph = FALSE,
    data = full_extended_solutions_matrix,
    top_hm = list(
        "Scheme" = "snf_scheme",
        "Impairment Separation" = "mean_neglog_p"
    ),
    left_hm = list(
        "Pooled" = "pooled",
        "Imputation" = "imputation"
    ),
    top_bar = list(
        "Number of Clusters - 2" = "nclust2"
    ),
    scale_diag = "none",
    heatmap_height = grid::unit(19, "cm"),
    heatmap_width = grid::unit(19, "cm"),
    annotation_colours = list(
        "Pooled" = c(
            "yes" = "orange",
            "no" = "purple"
        ),
        "Imputation" = divergent_colours(full_extended_solutions_matrix$"imputation"),
        "Scheme" = c(
            "1" = "#7FC97F",
            "2" = "#BEAED4",
            "3" = "#FDC086"
        ),
        "Impairment Separation" = hm_colours(full_extended_solutions_matrix$"mean_neglog_p")
    ),
    col = circlize::colorRamp2(
        c(min(aris_all_mtbi_imputations), max(aris_all_mtbi_imputations)),
        c("navy", "red")
    )
)

aris_all_mtbi_imputations_annotated_heatmap

# PNG export
grDevices::png(
    fig_path("aris_all_mtbi_imputations_annotated_heatmap.png", TRUE),
    width = 4000,
    height = 4000,
    res = 400
)
aris_all_mtbi_imputations_annotated_heatmap
grDevices::dev.off()

```

## Identifying meta clusters

```{r}

aris_all_mtbi_imputations_chopped_heatmap <- similarity_matrix_heatmap(
    aris_all_mtbi_imputations,
    order = aris_all_mtbi_imputations_order,
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    log_graph = FALSE,
    data = full_extended_solutions_matrix,
    top_hm = list(
        "Scheme" = "snf_scheme",
        "Impairment Separation" = "mean_neglog_p"
    ),
    left_hm = list(
        "Pooled" = "pooled",
        "Imputation" = "imputation"
    ),
    top_bar = list(
        "Number of Clusters - 2" = "nclust2"
    ),
    scale_diag = "none",
    heatmap_height = grid::unit(19, "cm"),
    heatmap_width = grid::unit(19, "cm"),
    annotation_colours = list(
        "Pooled" = c(
            "yes" = "orange",
            "no" = "purple"
        ),
        "Imputation" = divergent_colours(full_extended_solutions_matrix$"imputation"),
        "Scheme" = c(
            "1" = "#7FC97F",
            "2" = "#BEAED4",
            "3" = "#FDC086"
        ),
        "Impairment Separation" = hm_colours(full_extended_solutions_matrix$"mean_neglog_p")
    ),
    col = circlize::colorRamp2(
        c(min(aris_all_mtbi_imputations), max(aris_all_mtbi_imputations)),
        c("navy", "red")
    ),
    row_split = split_at(
        vector = c(
            500,
            806,
            956,
            1227,
            1441
        ),
        nrow = 2000
    ),
    column_split = split_at(
        vector = c(
            500,
            806,
            956,
            1227,
            1441
        ),
        nrow = 2000
    )
)

aris_all_mtbi_imputations_chopped_heatmap


# PNG export
grDevices::png(
    fig_path("aris_all_mtbi_imputations_chopped_heatmap.png", TRUE),
    width = 4000,
    height = 4000,
    res = 400
)
aris_all_mtbi_imputations_chopped_heatmap
grDevices::dev.off()


# A deeper zoom on some of the small heatmaps

zoomed_mc_f <- aris_all_mtbi_imputations[aris_all_mtbi_imputations_order, aris_all_mtbi_imputations_order]

zoomed_mc_f <- zoomed_mc_f[1441:2000, 1441:2000]

nrow(zoomed_mc_f)

aris_all_mtbi_zoomed_mc_f_chopped_heatmap <- similarity_matrix_heatmap(
    zoomed_mc_f,
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    log_graph = FALSE,
    scale_diag = "none",
    heatmap_height = grid::unit(19, "cm"),
    heatmap_width = grid::unit(19, "cm"),
    col = circlize::colorRamp2(
        c(min(aris_all_mtbi_imputations), max(aris_all_mtbi_imputations)),
        c("navy", "red")
    ),
    row_split = paste0(
        "F-",
        split_at(
            vector = c(
                78,
                253,
                290,
                336,
                400,
                438,
                462,
                496,
                513
            ),
            nrow = 560
        )
    ),
    column_split = paste0(
        "F-",
        split_at(
            vector = c(
                78,
                253,
                290,
                336,
                400,
                438,
                462,
                496,
                513
            ),
            nrow = 560
        )
    )
)
aris_all_mtbi_zoomed_mc_f_chopped_heatmap

# PNG export
grDevices::png(
    fig_path("aris_all_mtbi_zoomed_mc_f_chopped_heatmap.png", TRUE),
    width = 4000,
    height = 4000,
    res = 400
)
aris_all_mtbi_zoomed_mc_f_chopped_heatmap
grDevices::dev.off()

aris_all_mtbi_zoomed_mc_f_chopped_heatmap
```

## One-MC-at-a-time

```{r}

# Indices as they appear in the plots
mc_reordered_indices <- list(
    "A" = c(1, 500),
    "B" = c(501, 806),
    "C" = c(807, 956),
    "D" = c(957, 1227),
    "E" = c(1228, 1441),
    "F-A" = c(1442, 1442 + 78),
    "F-B" = c(1442 + 79, 1442 + 253),
    "F-C" = c(1442 + 254, 1442 + 290),
    "F-D" = c(1442 + 291, 1442 + 336),
    "F-E" = c(1442 + 337, 1442 + 400),
    "F-F" = c(1442 + 401, 1442 + 438),
    "F-G" = c(1442 + 439, 1442 + 462),
    "F-H" = c(1442 + 463, 1442 + 496),
    "F-I" = c(1442 + 497, 1442 + 513),
    "F-J" = c(1442 + 514, 2000)
)

mc_reordered_labels <- split_at(
    c(
        500,
        806,
        956,
        1227,
        1441,
        1442 + 78,
        1442 + 253,
        1442 + 290,
        1442 + 336,
        1442 + 400,
        1442 + 438,
        1442 + 462,
        1442 + 496,
        1442 + 513
    ),
    2000
)
mc_reordered_labels <- gsub("F", "F-A", mc_reordered_labels)
mc_reordered_labels <- gsub("G", "F-B", mc_reordered_labels)
mc_reordered_labels <- gsub("H", "F-C", mc_reordered_labels)
mc_reordered_labels <- gsub("I", "F-D", mc_reordered_labels)
mc_reordered_labels <- gsub("J", "F-E", mc_reordered_labels)
mc_reordered_labels <- gsub("K", "F-F", mc_reordered_labels)
mc_reordered_labels <- gsub("L", "F-G", mc_reordered_labels)
mc_reordered_labels <- gsub("M", "F-H", mc_reordered_labels)
mc_reordered_labels <- gsub("N", "F-I", mc_reordered_labels)
mc_reordered_labels <- gsub("O", "F-J", mc_reordered_labels)

names(aris_all_mtbi_imputations_order) <- mc_reordered_labels

sorted_mc_labels <- sort(aris_all_mtbi_imputations_order)

full_input_characterization_m1 <- extend_solutions(
    full_solutions_matrix,
    data_list_m1
)

write_csv(full_input_characterization_m1, proc_path("full_input_characterization_m1.csv", TRUE))

full_input_characterization_m1 <- read_csv(proc_path("2023_12_14_full_input_characterization_m1.csv"))

target_pvals <- full_input_characterization_m1 |>
    p_val_select()

target_pvals$"mc_label" <- names(sorted_mc_labels)

manhattan_plot <- function(data,
                           key_mode = FALSE,
                           threshold = NULL,
                           bonferroni_line = FALSE,
                           data_list) {
    row_id <- ""
    variable <- ""
    pval <- ""
    var_cols <- colnames(data)[endsWith(colnames(data), "_p")]
    data[, var_cols] <- data[, var_cols] |>
        apply(
            MARGIN = 2,
            FUN = function(x) {
                -log10(x)
                raw_p <- -log10(x)
                new_x <- dplyr::case_when(
                    raw_p > 5 ~ 5,
                    raw_p > 4 ~ 4,
                    raw_p > 3 ~ 3,
                    raw_p > 2 ~ 2,
                    raw_p > 1 ~ 1,
                    raw_p > 0 ~ 0,
                )
                new_x
            }
        )
    data$"row_id" <- factor(data$"row_id")
    data$"mc_label" <- factor(data$"mc_label")
    data <- data |>
        tidyr::pivot_longer(
            !(c(row_id, mc_label)),
            names_to = "variable",
            values_to = "pval"
        ) |>
        data.frame()
    summary_data <- data |>
        dplyr::group_by(
            mc_label,
            variable
        ) |>
        dplyr::summarize(
            mean_p = mean(pval),
            sd_p = sd(pval),
            se_p = sd_p / sqrt(dplyr::n()),
            .groups = "drop"
        )
    summary_data$"variable" <- sub("_p$", "", summary_data$"variable")
    ###########################################################################
    # Merge the summmary plot with domain information from the data_list
    ###########################################################################
    dl_metadata <- data_list_metadata(data_list) |> dplyr::select(-"type")
    summary_data <- merge(
        summary_data,
        dl_metadata,
        by.x = "variable",
        by.y = "name",
        all.x = TRUE
    )
    summary_data <- summary_data |> dplyr::arrange(domain)
    summary_data$"variable" <- factor(
        summary_data$"variable",
        levels = unique(summary_data$"variable")
    )
    plot <- summary_data |>
        ggplot2::ggplot(ggplot2::aes(x = domain, y = mean_p)) +
        #ggplot2::geom_errorbar(
        #    mapping = ggplot2::aes(
        #        x = variable,
        #        ymin = mean_p - se_p,
        #        ymax = mean_p + se_p,
        #        colour = mc_label
        #    )
        #) +
        ggplot2::geom_jitter(
            mapping = ggplot2::aes(
                group = domain,
                x = variable,
                y = mean_p,
                colour = domain
            ),
            height = 0,
            width = 0,
            alpha = 0.8,
            size = 5
        ) +
        ggplot2::labs(
            x = "Variable",
            y = expression("-log"[10]*"(p)"),
            colour = "Solution"
        ) +
        ggplot2::ylim(-log10(0.05), 5) +
        ggplot2::theme_bw() +
        ggplot2::labs(y = "Discretized -log10(p)") +
        ggplot2::theme(
            axis.text.x = ggplot2::element_text(
                angle = 90,
                vjust = 0.5,
                hjust = 1
            ),
            plot.title = ggplot2::element_text(hjust = 0.5)
        ) +
        ggplot2::facet_wrap(~ mc_label)
    if (!is.null(threshold)) {
        plot <- plot + ggplot2::geom_hline(
            yintercept = -log10(threshold),
            linetype = "dashed",
            colour = "red"
        )
        if (bonferroni_line) {
            plot <- plot + ggplot2::geom_hline(
                yintercept = -log10(threshold / nrow(data)),
                linetype = "dashed",
                colour = "black"
            )
        }
    } else if (bonferroni_line) {
        stop(
            "Please specify threshold p-value which will be used",
            " for calculting the Bonferroni-corrected line."
        )
    }
    return(plot)
}

manhattan_plot(
    target_pvals,
    threshold = 0.05,
    bonferroni_line = FALSE,
    data_list = data_list_m1
)

library(ggplot2)

ggsave(
    fig_path("all_mtbi_imputations_all_mc_input_associations.png", TRUE),
    width = 20,
    height = 20
)

target_pvals2 <- target_pvals |>
    dplyr::select()


```



```{r}
mc_c_rows <- aris_all_mtbi_imputations_order[956:1227]
colnames(target_pvals)


nrow(target_pvals)

# Who are those solutions?
mc_b_rows <- aris_all_mtbi_imputations_order[501:806]
mc_b_solutions <- full_extended_solutions_matrix[mc_b_rows, ]

mc_b_solutions

nrow(full_solutions_matrix)
data_list_m1[[1]]$"data"$"clusters" <- get_clusters(mc_b_solutions[20, ])

key_associations_df <- calculate_associations(
    data_list_m1,
    key_association = "clusters"
)

manhattan_plot(
    key_associations_df,
    key_mode = TRUE,
    threshold = 0.05,
    bonferroni_line = TRUE
)

-log10(0.00001)

library(ggplot2)
ggsave(fig_path("mc_b_associations.png", TRUE))
extended_solutions_matrix <- extend_solutions(solutions_matrix, target_list)

# Who are those solutions?
mc_c_rows <- aris_all_mtbi_imputations_order[956:1227]
mc_c_solutions <- full_extended_solutions_matrix[mc_c_rows, ]
mc_c_solutions
nrow(full_solutions_matrix)
data_list_m1[[1]]$"data"$"clusters" <- get_clusters(mc_c_solutions[20, ])
data_list_m1
key_associations_df <- calculate_associations(
    data_list_m1,
    key_association = "clusters"
)
manhattan_plot(
    key_associations_df,
    key_mode = TRUE,
    threshold = 0.05,
    bonferroni_line = TRUE
)
library(ggplot2)
ggsave(fig_path("mc_c_associations.png", TRUE))

# Who are those solutions?
mc_d_rows <- aris_all_mtbi_imputations_order[1227:1441]
mc_d_solutions <- full_extended_solutions_matrix[mc_d_rows, ]
mc_d_solutions
nrow(full_solutions_matrix)
data_list_m1[[1]]$"data"$"clusters" <- get_clusters(mc_d_solutions[20, ])
data_list_m1
key_associations_df <- calculate_associations(
    data_list_m1,
    key_association = "clusters"
)
manhattan_plot(
    key_associations_df,
    key_mode = TRUE,
    threshold = 0.05,
    bonferroni_line = TRUE
)
library(ggplot2)
ggsave(fig_path("mc_d_associations.png", TRUE))

```


```{r}
###############################################################################
# 4. Calculate pairwise solution similarities
###############################################################################
aris_m1 <- calc_om_aris(solutions_matrix_m1)

write_csv(data.frame(aris_m1), proc_path("aris_m1.csv", TRUE))

aris_m1 <- read_csv(proc_path("2023_12_01_aris_m1.csv"))
aris_m1 <- as.matrix(aris_m1)
colnames(aris_m1) <- 1:nrow(aris_m1)
rownames(aris_m1) <- 1:nrow(aris_m1)
```

Back to more lightweight functions:

```{r}
###############################################################################
# 5. Extract order of pairwise solution similarities
###############################################################################
aris_m1_heatmap <- similarity_matrix_heatmap(
    aris_m1,
    log_graph = FALSE,
    cluster_rows = TRUE,
    cluster_columns = TRUE,
)

aris_m1_heatmap <- ComplexHeatmap::draw(aris_m1_heatmap)

aris_m1_order <- ComplexHeatmap::row_order(aris_m1_heatmap)

write_csv(data.frame(aris_m1_order), proc_path("aris_m1_order.csv", TRUE))

aris_m1_order <- unlist(read_csv(proc_path("2023_12_01_aris_m1_order.csv")))

###############################################################################
# 5. Visualize reordered settings matrix and similarity matrix
###############################################################################
# No saving
settings_matrix_heatmap(
    settings_matrix,
    order = aris_m1_order,
    show_rownames = FALSE
)

settings_matrix_heatmap(
    settings_matrix,
    order = aris_m1_order,
    show_rownames = FALSE,
    save = fig_path("aris_m1_ordered_settings_matrix_heatmap.png", TRUE)
)
```

By visual inspection, there appears to be non-random organization based on the parameters k, and snf_scheme.
Below is the actual adjusted rand index heatmap with these hyperparameters highlighted.

```{r}

aris_m1_annotated_heatmap <- similarity_matrix_heatmap(
    aris_m1,
    order = aris_m1_order,
    log_graph = FALSE,
    data = solutions_matrix_m1,
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    top_hm = list(
        "Scheme" = "snf_scheme"
    ),
    bottom_bar = list(
        "K" = "k"
    ),
    scale_diag = "none",
    heatmap_height = grid::unit(19, "cm"),
    heatmap_width = grid::unit(19, "cm"),
    annotation_colours = list(
        "Scheme" = c(
            "1" = "#7FC97F",
            "2" = "#BEAED4",
            "3" = "#FDC086"
        )
    ),
    col = circlize::colorRamp2(
        c(min(aris_m1), max(aris_m1)),
        c("navy", "red")
    )
)

# No saving
aris_m1_annotated_heatmap

# PDF export
grDevices::pdf(
    fig_path("aris_m1_annotated_heatmap.pdf", TRUE),
    width = 10,
    height = 10
)
aris_m1_annotated_heatmap
grDevices::dev.off()

# PNG export
grDevices::png(
    fig_path("aris_m1_annotated_heatmap.png", TRUE),
    width = 4000,
    height = 3000,
    res = 400
)
aris_m1_annotated_heatmap
grDevices::dev.off()
```

A few "meta clusters" are visible in the pairwise ARI heatmap.

Let's see how they associate with the out of model measures:

```{r}

extended_solutions_matrix_m1 <- extend_solutions(
    solutions_matrix_m1,
    oom_list_m1
)

write_csv(
    extended_solutions_matrix_m1,
    proc_path(
        "extended_solutions_matrix_m1.csv",
        TRUE
    )
)

extended_solutions_matrix_m1 <- read_csv(
    proc_path(
        "2023_12_04_extended_solutions_matrix_m1.csv"
    )
)


oom_m1_pvals <- pval_select(
    extended_solutions_matrix_m1,
    negative_log = TRUE
)


pval_hm_m1 <- pval_heatmap(oom_m1_pvals, order = aris_m1_order, max_red = TRUE)

# No saving
pval_hm_m1

# PNG export
grDevices::png(
    fig_path("pval_hm_m1.png", TRUE),
    width = 4000,
    height = 3000,
    res = 400
)
pval_hm_m1
grDevices::dev.off()

extended_solutions_matrix_m1$"mean_neglog_p" <- oom_m1_pvals$"mean_neglog_p"

aris_m1_extended_annotated_heatmap <- similarity_matrix_heatmap(
    aris_m1,
    order = aris_m1_order,
    log_graph = FALSE,
    data = extended_solutions_matrix_m1,
    bottom_hm = list(
        "SNF Scheme" = "snf_scheme"
    ),
    top_hm = list(
        "Impairment Separation" = "mean_neglog_p"
    ),
    bottom_bar = list(
        "K" = "k",
        "Number of Clusters" = "nclust"
    ),
    scale_diag = "none",
    heatmap_height = grid::unit(19, "cm"),
    heatmap_width = grid::unit(19, "cm"),
    annotation_colours = list(
        "SNF Scheme" = c(
            "1" = "orange",
            "2" = "purple",
            "3" = "turquoise"
        ),
        "Impairment Separation" = hm_colours(oom_m1_pvals$"mean_neglog_p")
    ),
    col = circlize::colorRamp2(
        c(min(aris_m1), max(aris_m1)),
        c("navy", "red")
    )
)

# No saving
aris_m1_extended_annotated_heatmap

# PNG export
grDevices::png(
    fig_path("aris_m1_extended_annotated_heatmap.png", TRUE),
    width = 4000,
    height = 3000,
    res = 400
)
aris_m1_extended_annotated_heatmap
grDevices::dev.off()
```

Next steps:

- repeat for the other imputations and see how well the structure holds.
