# Similarity Network Fusion

In this chapter, I use the `metasnf` package to generate many diverse subtyping solutions with SNF.

## Data set-up

In the previous chapter, we set up the following datasets:

* 1 original unimputed mTBI dataset
* 1 original unimputed uninjured dataset
* 5 imputed mTBI datasets
* 5 imputed uninjured datasets
* 5 imputed mTBI + uninjured datasets

For the sake of simplicity, let's start just by exploring the first of the imputed mTBI datasets.

To keep track of what data we're working with, variables will have the following notation: (m/u/p)(0-5), where m represented mTBI data, u represents uninjured data, p for pooled data, 0 indicating original (unimputed) data, and 1-5 indicating the imputed dataset number.

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))

as_mem_daze_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_as_mem_daze_mtbi_train_imp_1.csv"))
as_mechanism_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_as_mechanism_mtbi_train_imp_1.csv"))
as_loc_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_as_loc_mtbi_train_imp_1.csv"))
d_interview_age_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_d_interview_age_mtbi_train_imp_1.csv"))
d_mtbi_age_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_d_mtbi_age_mtbi_train_imp_1.csv"))
d_sex_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_d_sex_mtbi_train_imp_1.csv"))
d_income_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_d_income_mtbi_train_imp_1.csv"))
d_race_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_d_race_mtbi_train_imp_1.csv"))
d_pubertal_status_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_d_pubertal_status_mtbi_train_imp_1.csv"))
mh_headaches_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_mh_headaches_mtbi_train_imp_1.csv"))
mh_mtbi_count_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_mh_mtbi_count_mtbi_train_imp_1.csv"))
sm_subc_v_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_sm_subc_v_mtbi_train_imp_1.csv"))
sm_cort_t_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_sm_cort_t_mtbi_train_imp_1.csv"))
sm_cort_sa_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_sm_cort_sa_mtbi_train_imp_1.csv"))
dm_all_wmnd_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_dm_all_wmnd_mtbi_train_imp_1.csv"))
rm_gord_cor_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_rm_gord_cor_mtbi_train_imp_1.csv"))
rm_subc_cor_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_rm_subc_cor_mtbi_train_imp_1.csv"))
p_loneliness_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_p_loneliness_mtbi_train_imp_1.csv"))
p_screen_time_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_p_screen_time_mtbi_train_imp_1.csv"))
p_sports_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_p_sports_mtbi_train_imp_1.csv"))
p_exercise_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_p_exercise_mtbi_train_imp_1.csv"))
p_prosocial_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_p_prosocial_mtbi_train_imp_1.csv"))
p_fam_fn_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_p_fam_fn_mtbi_train_imp_1.csv"))
p_parent_psych_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_p_parent_psych_mtbi_train_imp_1.csv"))
t_cbcl_anxdep_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_t_cbcl_anxdep_mtbi_train_imp_1.csv"))
t_cbcl_withdep_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_t_cbcl_withdep_mtbi_train_imp_1.csv"))
t_cbcl_somatic_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_t_cbcl_somatic_mtbi_train_imp_1.csv"))
t_cbcl_social_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_t_cbcl_social_mtbi_train_imp_1.csv"))
t_cbcl_thought_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_t_cbcl_thought_mtbi_train_imp_1.csv"))
t_cbcl_attention_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_t_cbcl_attention_mtbi_train_imp_1.csv"))
t_cbcl_rulebreak_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_t_cbcl_rulebreak_mtbi_train_imp_1.csv"))
t_cbcl_aggressive_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_t_cbcl_aggressive_mtbi_train_imp_1.csv"))
sds_total_probs_mtbi_train_imp_1 <- read_csv(input_path("2023_12_01_sds_total_probs_mtbi_train_imp_1.csv"))
```


```{r}
###############################################################################
# 1. Load the input features and out-of-model features into data_lists
###############################################################################
data_list_m1 <- generate_data_list(
    list(as_mem_daze_mtbi_train_imp_1, "as_mem_daze", "AS", "discrete"),
    list(as_mechanism_mtbi_train_imp_1, "as_mechanism", "AS", "categorical"),
    list(as_loc_mtbi_train_imp_1, "as_loc", "AS", "discrete"),
    list(d_interview_age_mtbi_train_imp_1, "d_age", "D", "discrete"),
    list(d_mtbi_age_mtbi_train_imp_1, "d_mtbi_age", "D", "discrete"),
    list(d_sex_mtbi_train_imp_1, "d_sex", "D", "discrete"),
    list(d_income_mtbi_train_imp_1, "d_income", "D", "ordinal"),
    list(d_race_mtbi_train_imp_1, "d_race", "D", "discrete"),
    list(d_pubertal_status_mtbi_train_imp_1, "d_pubertal", "D", "discrete"),
    list(mh_headaches_mtbi_train_imp_1, "mh_headaches", "MH", "discrete"),
    list(mh_mtbi_count_mtbi_train_imp_1, "mh_mtbi_count", "MH", "discrete"),
    list(sm_subc_v_mtbi_train_imp_1, "sm_subc_v", "N", "continuous"),
    list(sm_cort_t_mtbi_train_imp_1, "sm_cort_t", "N", "continuous"),
    list(sm_cort_sa_mtbi_train_imp_1, "sm_cort_sa", "N", "continuous"),
    list(dm_all_wmnd_mtbi_train_imp_1, "dm_all_wmnd", "N", "continuous"),
    list(rm_gord_cor_mtbi_train_imp_1, "rm_gord_cor", "N", "continuous"),
    list(rm_subc_cor_mtbi_train_imp_1, "rm_subc_cor", "N", "continuous"),
    list(p_loneliness_mtbi_train_imp_1, "p_loneliness", "P", "discrete"),
    list(p_screen_time_mtbi_train_imp_1, "p_screen_time", "P", "discrete"),
    list(p_sports_mtbi_train_imp_1, "p_sports", "P", "discrete"),
    list(p_exercise_mtbi_train_imp_1, "p_exercise", "P", "discrete"),
    list(p_prosocial_mtbi_train_imp_1, "p_prosocial", "P", "discrete"),
    list(p_fam_fn_mtbi_train_imp_1, "p_fam_fn", "P", "discrete"),
    list(p_parent_psych_mtbi_train_imp_1, "p_parent_psych", "P", "discrete"),
    uid = "subjectkey"
)

oom_list_m1 <- generate_data_list(
    list(t_cbcl_anxdep_mtbi_train_imp_1, "t_cbcl_anxdep", "B", "ordinal"),
    list(t_cbcl_withdep_mtbi_train_imp_1, "t_cbcl_withdep", "B", "ordinal"),
    list(t_cbcl_somatic_mtbi_train_imp_1, "t_cbcl_somatic", "B", "ordinal"),
    list(t_cbcl_social_mtbi_train_imp_1, "t_cbcl_social", "B", "ordinal"),
    list(t_cbcl_thought_mtbi_train_imp_1, "t_cbcl_thought", "B", "ordinal"),
    list(t_cbcl_attention_mtbi_train_imp_1, "t_cbcl_attention", "B", "ordinal"),
    list(t_cbcl_rulebreak_mtbi_train_imp_1, "t_cbcl_rulebreak", "B", "ordinal"),
    list(t_cbcl_aggressive_mtbi_train_imp_1, "t_cbcl_aggressive", "B", "ordinal"),
    list(sds_total_probs_mtbi_train_imp_1, "sds_total_probs", "S", "discrete")
)

all_vars_dl_m1 <- c(data_list_m1, oom_list_m1)
summarize_dl(all_vars_dl_m1)

###############################################################################
# 2. Add standard normalized variations to the distance metrics list (also
# achievable through toggling automatic_standard_normalize parameter in
# `batch_snf`)
###############################################################################
my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

summarize_distance_metrics_list(my_distance_metrics)
```

Some of the heavier functions are in the next chunk:

```{r}
###############################################################################
# 3. Generate the settings matrix
###############################################################################
settings_matrix <- generate_settings_matrix(
    data_list_m1,
    nrow = 200,
    seed = 42,
    distance_metrics_list = my_distance_metrics
)

write_csv(settings_matrix, proc_path("settings_matrix.csv", TRUE))

settings_matrix <- read_csv(
    proc_path(
        "2023_12_01_settings_matrix.csv"
    )
)

solutions_matrix_m1 <- batch_snf(
    data_list = data_list_m1,
    settings_matrix = settings_matrix,
    distance_metrics_list = my_distance_metrics
)

write_csv(solutions_matrix_m1, proc_path("solutions_matrix_m1.csv", TRUE))

solutions_matrix_m1 <- read_csv(
    proc_path(
        "2023_12_01_solutions_matrix_m1.csv"
    )
)

###############################################################################
# 4. Calculate pairwise solution similarities
###############################################################################
aris_m1 <- calc_om_aris(solutions_matrix_m1)

write_csv(data.frame(aris_m1), proc_path("aris_m1.csv", TRUE))

aris_m1 <- read_csv(proc_path("2023_12_01_aris_m1.csv"))
aris_m1 <- as.matrix(aris_m1)
colnames(aris_m1) <- 1:nrow(aris_m1)
rownames(aris_m1) <- 1:nrow(aris_m1)
```

Back to more lightweight functions:

```{r}
###############################################################################
# 5. Extract order of pairwise solution similarities
###############################################################################
aris_m1_heatmap <- similarity_matrix_heatmap(
    aris_m1,
    log_graph = FALSE,
    cluster_rows = TRUE,
    cluster_columns = TRUE,
)

aris_m1_heatmap <- ComplexHeatmap::draw(aris_m1_heatmap)

aris_m1_order <- ComplexHeatmap::row_order(aris_m1_heatmap)

write_csv(data.frame(aris_m1_order), proc_path("aris_m1_order.csv", TRUE))

aris_m1_order <- unlist(read_csv(proc_path("2023_12_01_aris_m1_order.csv")))

###############################################################################
# 5. Visualize reordered settings matrix and similarity matrix
###############################################################################
# No saving
settings_matrix_heatmap(
    settings_matrix,
    order = aris_m1_order,
    show_rownames = FALSE
)

settings_matrix_heatmap(
    settings_matrix,
    order = aris_m1_order,
    show_rownames = FALSE,
    save = fig_path("aris_m1_ordered_settings_matrix_heatmap.png", TRUE)
)
```

By visual inspection, there appears to be non-random organization based on the parameters k, and snf_scheme.
Below is the actual adjusted rand index heatmap with these hyperparameters highlighted.

```{r}
formatted_solutions_matrix_m1 <- solutions_matrix_m1 |>
    dplyr::mutate(
        "snf_scheme" = dplyr::case_when(
            snf_scheme == 1 ~ "Individual",
            snf_scheme == 2 ~ "Two-step",
            snf_scheme == 3 ~ "Domain"
        )
    )

aris_m1_annotated_heatmap <- similarity_matrix_heatmap(
    aris_m1,
    order = aris_m1_order,
    log_graph = FALSE,
    cluster_rows = TRUE,
    cluster_columns = TRUE,
    data = formatted_solutions_matrix_m1,
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    top_hm = list(
        "Scheme" = "snf_scheme"
    ),
    bottom_bar = list(
        "K" = "k"
    ),
    scale_diag = "none",
    heatmap_height = grid::unit(19, "cm"),
    heatmap_width = grid::unit(19, "cm"),
    annotation_colours = list(
        "Scheme" = c(
            "Domain" = "#7FC97F",
            "Individual" = "#BEAED4",
            "Two-step" = "#FDC086"
        )
    ),
    col = circlize::colorRamp2(
        c(min(aris_m1), max(aris_m1)),
        c("navy", "red")
    )
)

# No saving
aris_m1_annotated_heatmap

# PDF export
grDevices::pdf(
    fig_path("aris_m1_annotated_heatmap.pdf", TRUE),
    width = 10,
    height = 10
)
aris_m1_annotated_heatmap
grDevices::dev.off()

# PNG export
grDevices::png(
    fig_path("aris_m1_annotated_heatmap.png", TRUE),
    width = 4000,
    height = 3000,
    res = 400
)
aris_m1_annotated_heatmap
grDevices::dev.off()
```

A few "meta clusters" are visible in the pairwise ARI heatmap.

Let's see how they associate with the out of model measures:

```{r}


aris_m1_annotated_heatmap

extended_solutions_matrix_m1 <- extend_solutions(
    solutions_matrix_m1,
    oom_list_m1
)

oom_m1_pvals <- p_val_select(extended_solutions_matrix_m1)

colnames(oom_m1_pvals)

impairment_separation <- -log(oom_m1_pvals)

impairment_separation$"row_id" <- oom_m1_pvals$"row_id"

pvals_heatmap(
    oom_m1_pvals,
    order = aris_m1_order,
    cluster_cols = FALSE,
    reverse_colours = TRUE,
    save = fig_path("aris_ordered_oom_pvals_m1.png", TRUE)
)

pvals_heatmap(
    impairment_separation,
    order = aris_m1_order,
    cluster_cols = FALSE
)

dim(impairment_separation)

as.matrix(impairment_separation[aris_m1_order, -1]) |>
    ComplexHeatmap::Heatmap(cluster_rows = FALSE, cluster_columns = FALSE)

```


```{r}

extended_solutions_matrix_m1


# Looking at the newly added columns
head(no_subs(extended_solutions_matrix))

formatted_extended_solutions_matrix_m1 <- extended_solutions_matrix_m1 |>
    dplyr::mutate(
        "snf_scheme" = dplyr::case_when(
            snf_scheme == 1 ~ "Individual",
            snf_scheme == 2 ~ "Two-step",
            snf_scheme == 3 ~ "Domain"
        ),
        "minus_log_mean_p" = -log(mean_p_val)
    )

colnames(no_subs(extended_solutions_matrix_m1))

colnames(formatted_extended_solutions_matrix_m1)

neg_log <- formatted_extended_solutions_matrix_m1 |>
    no_subs() |>
    dplyr::select(dplyr::ends_with("_p") | dplyr::ends_with("_val")) |>
    numcol_to_numeric() |>
    dplyr::select(-"minus_log_mean_p")
neg_log <- -log(neg_log)
better_names <- gsub("cbcl_scr_syn_", "", colnames(neg_log))
better_names <- gsub("_r_p", "", better_names)
better_names <- gsub("sds_p_ss_total_p", "sleep", better_names)
better_names <- gsub("_p_val", "_sep", better_names)
better_names
colnames(neg_log) <- better_names
neg_log$"row_id" <- formatted_extended_solutions_matrix_m1$"row_id"
separation_df <- dplyr::inner_join(neg_log, formatted_extended_solutions_matrix_m1, by = "row_id")
separation_df <- separation_df |> numcol_to_numeric()

colnames(separation_df |> no_subs())

hm_colours <- function(vector) {
    colours <- circlize::colorRamp2(
        c(min(vector), max(vector)),
        c("black", "red")
    )
    return(colours)
}

aris_m1_extended_annotated_heatmap <- similarity_matrix_heatmap(
    aris_m1,
    order = aris_m1_order,
    log_graph = FALSE,
    data = separation_df,
    bottom_hm = list(
        "SNF Scheme" = "snf_scheme"
    ),
    top_hm = list(
        "Impairment Separation" = "mean_sep"
    ),
    bottom_bar = list(
        "K" = "k",
        "Number of Clusters" = "nclust"
    ),
    scale_diag = "none",
    heatmap_height = grid::unit(19, "cm"),
    heatmap_width = grid::unit(19, "cm"),
    annotation_colours = list(
        "SNF Scheme" = c(
            "Domain" = "orange",
            "Individual" = "purple",
            "Two-step" = "turquoise"
        ),
        "Impairment Separation" = hm_colours(separation_df$"mean_sep")
    ),
    col = circlize::colorRamp2(
        c(min(aris_m1), max(aris_m1)),
        c("navy", "red")
    )
)
# No saving
aris_m1_extended_annotated_heatmap



aris_m1_extended_annotated_heatmap <- similarity_matrix_heatmap(
    aris_m1,
    order = aris_m1_order,
    log_graph = FALSE,
    data = formatted_extended_solutions_matrix_m1,
    bottom_hm = list(
        "SNF Scheme" = "snf_scheme"
    ),
    top_bar = list(
        "Impairment Separation" = "minus_log_mean_p"
    ),
    left_bar = list(
        "WithdrawnDepressed" = "cbcl_scr_syn_withdep_r_p"
    ),
    bottom_bar = list(
        "K" = "k",
        "Number of Clusters" = "nclust"
    ),
    scale_diag = "none",
    heatmap_height = grid::unit(19, "cm"),
    heatmap_width = grid::unit(19, "cm"),
    annotation_colours = list(
        "SNF Scheme" = c(
            "Domain" = "orange",
            "Individual" = "purple",
            "Two-step" = "turquoise"
        )
    ),
    col = circlize::colorRamp2(
        c(min(aris_m1), max(aris_m1)),
        c("navy", "red")
    )
)
# No saving
aris_m1_extended_annotated_heatmap

# PDF export
grDevices::pdf(
    fig_path("aris_m1_extended_annotated_heatmap.pdf", TRUE),
    width = 10,
    height = 10
)
aris_m1_extended_annotated_heatmap
grDevices::dev.off()

# PNG export
grDevices::png(
    fig_path("aris_m1_extended_annotated_heatmap.png", TRUE),
    width = 4000,
    height = 3000,
    res = 400
)
aris_m1_extended_annotated_heatmap
grDevices::dev.off()
```

Loose exploring

```{r}

all_vars_dl_m1

summarize_dl(all_vars_dl_m1)


keep_numeric <- function(df) {
    df <- numcol_to_numeric(df)
    classes <- as.vector(sapply(df, class))
    df <- df[, classes == "numeric", drop = FALSE]
    return(df)
}

correlation_heatmap <- function(data_list, order = NULL) {
    dl_df <- collapse_dl(data_list)
    numeric_dl_df <- keep_numeric(dl_df)
    correlation_matrix <- cor(numeric_dl_df)
    if (is.null(order)) {
        heatmap <- ComplexHeatmap::Heatmap(correlation_matrix)
    } else {
        heatmap <- ComplexHeatmap::Heatmap(
            correlation_matrix[order, order],
            cluster_rows = FALSE,
            cluster_columns = FALSE
        )
    }
    drawn_heatmap <- ComplexHeatmap::draw(heatmap)
    order <- ComplexHeatmap::row_order(drawn_heatmap)
    results <- list(
        "correlation_matrix" = correlation_matrix,
        "heatmap" = heatmap,
        "order" = order
    )
    return(results)
}

# First pass to extract the order of columns
correlation_heatmap(
    all_vars_dl_m1
)

all_vars_associations <- calculate_associations(all_vars_dl_m1)

race_cors <- all_vars_associations[, "race"]
race_order <- sort(race_cors, index.return = TRUE)$"ix"

correlation_pval_heatmap(
    all_vars_associations[race_order, race_order],
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    significance_stars = FALSE
)

sex_cors <- all_vars_associations[, "sex"]
sex_order <- sort(sex_cors, index.return = TRUE)$"ix"

correlation_pval_heatmap(
    all_vars_associations[sex_order, sex_order],
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    significance_stars = FALSE
)

```
