# Similarity Network Fusion

In this chapter, I use the `metasnf` package to generate many diverse subtyping solutions with SNF.

In the previous chapter, we set up the following datasets:

* 1 original unimputed mTBI dataset
* 1 original unimputed uninjured dataset
* 5 imputed mTBI datasets
* 5 imputed uninjured datasets
* 5 imputed mTBI + uninjured datasets

To keep track of what data we're working with, variables will have the following notation: (m/u/p)(0-5), where m represented mTBI data, u represents uninjured data, p for pooled data, 0 indicating original (unimputed) data, and 1-5 indicating the imputed dataset number.

## Utility functions

```{r}
rename_data_list <- function(data_list, name_mapping) {
    data_list <- data_list |> lapply(
        function(x) {
            old_colnames <- colnames(x$"data")
            new_colnames <- old_colnames |> lapply(
                function(old_name) {
                    if (old_name %in% name_mapping) {
                        new_name <- names(name_mapping)[which(name_mapping == old_name)]
                    } else {
                        new_name <- old_name
                    }
                    return(new_name)
                }
            )
            colnames(x$"data") <- new_colnames
            return(x)
        }
    )
    return(data_list)
}

keep_numeric <- function(df) {
    df <- numcol_to_numeric(df)
    classes <- as.vector(sapply(df, class))
    df <- df[, classes == "numeric", drop = FALSE]
    return(df)
}

hm_colours <- function(data, max_red = TRUE) {
    if (max_red) {
        colours <- circlize::colorRamp2(
            c(min(data), max(data)),
            c("black", "red")
        )
    } else {
        colours <- circlize::colorRamp2(
            c(min(data), max(data)),
            c("red", "black")
        )
    }
    return(colours)
}

correlation_heatmap <- function(data_list, order = NULL) {
    dl_df <- collapse_dl(data_list)
    numeric_dl_df <- keep_numeric(dl_df)
    correlation_matrix <- cor(numeric_dl_df)
    if (is.null(order)) {
        heatmap <- ComplexHeatmap::Heatmap(correlation_matrix)
    } else {
        heatmap <- ComplexHeatmap::Heatmap(
            correlation_matrix[order, order],
            cluster_rows = FALSE,
            cluster_columns = FALSE
        )
    }
    drawn_heatmap <- ComplexHeatmap::draw(heatmap)
    order <- ComplexHeatmap::row_order(drawn_heatmap)
    results <- list(
        "correlation_matrix" = correlation_matrix,
        "heatmap" = heatmap,
        "order" = order
    )
    return(results)
}

pval_select <- function(extended_solutions_matrix,
                        keep_summary = TRUE,
                        negative_log = FALSE,
                        recalculate_summary = TRUE) {
    pval_df <- extended_solutions_matrix |>
        dplyr::select(
            "row_id",
            dplyr::ends_with("_p"),
            dplyr::contains("p_val")
        ) |>
        data.frame() |>
        numcol_to_numeric()
    if (!keep_summary) {
        pval_df <- pval_df |>
            dplyr::select(-c("min_p_val", "mean_p_val"))
    }
    if (negative_log) {
        neg_log_pval_df <- -log(pval_df)
        neg_log_pval_df$"row_id" <- pval_df$"row_id"
        pval_df <- neg_log_pval_df
        if (recalculate_summary) {
            mini_df <- pval_df |> dplyr::select(
                dplyr::ends_with("_p")
            )
            pval_df$"mean_neglog_p" <- apply(mini_df, 1, FUN = mean)
            pval_df$"max_neglog_p" <- apply(mini_df, 1, FUN = max)
        }
    }
    return(pval_df)
}

pval_heatmap <- function(pval_df, order, max_red = FALSE) {
    pval_df <- pval_df |> dplyr::select(-"row_id")
    pval_matrix <- as.matrix(pval_df[order, ])
    hm <- ComplexHeatmap::Heatmap(
        pval_matrix,
        cluster_rows = FALSE,
        cluster_columns = FALSE,
        show_row_names = FALSE,
        col = hm_colours(pval_matrix, max_red)
    )
    return(hm)
}

split_at <- function(vector, nrow) {
    split_vec <- rep("A", nrow)
    if (vector[length(vector)] != nrow) {
        vector <- c(vector, nrow)
    }
    for (i in 1:(length(vector) - 1)) {
        start <- vector[i]
        end <- vector[i + 1]
        split_vec[start:end] <- LETTERS[i + 1]
    }
    return(split_vec)
}


```

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subjects <- read_csv(sub_path("2023_11_07_mtbi_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2023_11_07_uninjured_subjects.csv"))
```

## Loading data and out of model lists

```{r}
data_list_m1 <- list.load(input_path("2023_12_11_data_list_m1.rds"))
data_list_m2 <- list.load(input_path("2023_12_11_data_list_m2.rds"))
data_list_m3 <- list.load(input_path("2023_12_11_data_list_m3.rds"))
data_list_m4 <- list.load(input_path("2023_12_11_data_list_m4.rds"))
data_list_m5 <- list.load(input_path("2023_12_11_data_list_m5.rds"))
data_list_pm1 <- list.load(input_path("2023_12_11_data_list_pm1.rds"))
data_list_pm2 <- list.load(input_path("2023_12_11_data_list_pm2.rds"))
data_list_pm3 <- list.load(input_path("2023_12_11_data_list_pm3.rds"))
data_list_pm4 <- list.load(input_path("2023_12_11_data_list_pm4.rds"))
data_list_pm5 <- list.load(input_path("2023_12_11_data_list_pm5.rds"))
oom_list_m1 <- list.load(input_path("2023_12_11_oom_list_m1.rds"))
oom_list_m2 <- list.load(input_path("2023_12_11_oom_list_m2.rds"))
oom_list_m3 <- list.load(input_path("2023_12_11_oom_list_m3.rds"))
oom_list_m4 <- list.load(input_path("2023_12_11_oom_list_m4.rds"))
oom_list_m5 <- list.load(input_path("2023_12_11_oom_list_m5.rds"))
oom_list_pm1 <- list.load(input_path("2023_12_11_oom_list_pm1.rds"))
oom_list_pm2 <- list.load(input_path("2023_12_11_oom_list_pm2.rds"))
oom_list_pm3 <- list.load(input_path("2023_12_11_oom_list_pm3.rds"))
oom_list_pm4 <- list.load(input_path("2023_12_11_oom_list_pm4.rds"))
oom_list_pm5 <- list.load(input_path("2023_12_11_oom_list_pm5.rds"))
```

## Initial visualizations

Examining some of the pairwise associations between all the included (numeric) variables within the first imputed dataset.

```{r}
###############################################################################
# Imputation 1
###############################################################################
all_var_dl_m1 <- c(data_list_m1, oom_list_m1)

# First pass to extract the order of columns
correlation_heatmap_data_m1 <- correlation_heatmap(all_var_dl_m1)
correlation_matrix_m1 <- correlation_heatmap_data_m1$"correlation_matrix"
race_cors_m1 <- abs(correlation_matrix_m1[, "race"])
race_order_m1 <- sort(race_cors_m1, index.return = TRUE, decreasing = TRUE)$"ix"
sex_cors_m1 <- abs(correlation_matrix_m1[, "sex"])
sex_order_m1 <- sort(sex_cors_m1, index.return = TRUE, decreasing = TRUE)$"ix"

correlation_heatmap_data_m1 <- correlation_heatmap(c(data_list_m1, oom_list_m1), order = race_order_m1)

# All correlations, sorted by abs(cor-race)

grDevices::pdf(
    fig_path("correlation_matrix_m1_race.png", TRUE),
    width = 10,
    height = 10
)

ComplexHeatmap::Heatmap(
    correlation_matrix_m1[race_order_m1, race_order_m1],
    cluster_rows = FALSE,
    cluster_columns = FALSE
)

grDevices::dev.off()

# Race correlations, sorted by abs(cor-race)
grDevices::pdf(
    fig_path("correlation_matrix_m1_race_only.png", TRUE),
    width = 10,
    height = 10
)
ComplexHeatmap::Heatmap(
    correlation_matrix_m1[race_order_m1, "race"],
    cluster_rows = FALSE,
    cluster_columns = FALSE
)
grDevices::dev.off()

# All correlations, sorted by abs(cor-sex)
grDevices::pdf(
    fig_path("correlation_matrix_m1_sex.png", TRUE),
    width = 10,
    height = 10
)
ComplexHeatmap::Heatmap(
    correlation_matrix_m1[sex_order_m1, sex_order_m1],
    cluster_rows = FALSE,
    cluster_columns = FALSE
)
grDevices::dev.off()

# Sex correlations, sorted by abs(cor-race)
grDevices::pdf(
    fig_path("correlation_matrix_m1_sex_only.png", TRUE),
    width = 10,
    height = 10
)
ComplexHeatmap::Heatmap(
    correlation_matrix_m1[sex_order_m1, "sex"],
    cluster_rows = FALSE,
    cluster_columns = FALSE
)
grDevices::dev.off()
```

## Establishing custom distance measures

```{r}
###############################################################################
# 2. Add standard normalized variations to the distance metrics list (also
# achievable through toggling automatic_standard_normalize parameter in
# `batch_snf`)
###############################################################################
my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

summarize_distance_metrics_list(my_distance_metrics)
```

## SNF calculations

Now for the actual subtyping.

Some of the heavier functions are in the next chunk:

```{r}
###############################################################################
# 3. Generate the settings matrix
###############################################################################
settings_matrix <- generate_settings_matrix(
    data_list_m1,
    nrow = 200,
    seed = 42,
    distance_metrics_list = my_distance_metrics
)

write_csv(settings_matrix, proc_path("settings_matrix.csv", TRUE))

settings_matrix <- read_csv(
    proc_path(
        "2023_12_01_settings_matrix.csv"
    )
)

###############################################################################
# 4. SNF
###############################################################################
# mTBI only imputed
# Imputation 1
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m1 <- batch_snf(
        data_list = data_list_m1,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m1, proc_path("solutions_matrix_m1.csv", TRUE))
# Imputation 2
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m2 <- batch_snf(
        data_list = data_list_m2,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m2, proc_path("solutions_matrix_m2.csv", TRUE))
# Imputation 3
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m3 <- batch_snf(
        data_list = data_list_m3,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m3, proc_path("solutions_matrix_m3.csv", TRUE))
# Imputation 4
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m4 <- batch_snf(
        data_list = data_list_m4,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m4, proc_path("solutions_matrix_m4.csv", TRUE))
# Imputation 5
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m5 <- batch_snf(
        data_list = data_list_m5,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m5, proc_path("solutions_matrix_m5.csv", TRUE))

# mTBI and uninjured pooled imputed
# Imputation 1
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm1 <- batch_snf(
        data_list = data_list_pm1,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm1, proc_path("solutions_matrix_pm1.csv", TRUE))
# Imputation 2
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm2 <- batch_snf(
        data_list = data_list_pm2,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm2, proc_path("solutions_matrix_pm2.csv", TRUE))
# Imputation 3
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm3 <- batch_snf(
        data_list = data_list_pm3,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm3, proc_path("solutions_matrix_pm3.csv", TRUE))
# Imputation 4
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm4 <- batch_snf(
        data_list = data_list_pm4,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm4, proc_path("solutions_matrix_pm4.csv", TRUE))
# Imputation 5
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm5 <- batch_snf(
        data_list = data_list_pm5,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm5, proc_path("solutions_matrix_pm5.csv", TRUE))
```

That covers 10 different imputed mTBI datasets: 5 that were imputed with only the mTBI subjects, and 5 that were imputed with both mTBI and uninjured subjects.

Now a check to see how much the clusters varied by imputation.

```{r}

solutions_matrix_m1 <- read_csv(proc_path("2023_12_07_solutions_matrix_m1.csv"))
solutions_matrix_m2 <- read_csv(proc_path("2023_12_07_solutions_matrix_m2.csv"))
solutions_matrix_m3 <- read_csv(proc_path("2023_12_07_solutions_matrix_m3.csv"))
solutions_matrix_m4 <- read_csv(proc_path("2023_12_07_solutions_matrix_m4.csv"))
solutions_matrix_m5 <- read_csv(proc_path("2023_12_07_solutions_matrix_m5.csv"))
solutions_matrix_pm1 <- read_csv(proc_path("2023_12_07_solutions_matrix_pm1.csv"))
solutions_matrix_pm2 <- read_csv(proc_path("2023_12_07_solutions_matrix_pm2.csv"))
solutions_matrix_pm3 <- read_csv(proc_path("2023_12_07_solutions_matrix_pm3.csv"))
solutions_matrix_pm4 <- read_csv(proc_path("2023_12_07_solutions_matrix_pm4.csv"))
solutions_matrix_pm5 <- read_csv(proc_path("2023_12_07_solutions_matrix_pm5.csv"))

aris_m1 <- calc_om_aris(solutions_matrix_m1)
write_csv(data.frame(aris_m1), proc_path("aris_m1.csv", TRUE))
aris_m2 <- calc_om_aris(solutions_matrix_m2)
write_csv(data.frame(aris_m2), proc_path("aris_m2.csv", TRUE))
aris_m3 <- calc_om_aris(solutions_matrix_m3)
write_csv(data.frame(aris_m3), proc_path("aris_m3.csv", TRUE))
aris_m4 <- calc_om_aris(solutions_matrix_m4)
write_csv(data.frame(aris_m4), proc_path("aris_m4.csv", TRUE))
aris_m5 <- calc_om_aris(solutions_matrix_m5)
write_csv(data.frame(aris_m5), proc_path("aris_m5.csv", TRUE))
aris_pm1 <- calc_om_aris(solutions_matrix_pm1)
write_csv(data.frame(aris_pm1), proc_path("aris_pm1.csv", TRUE))
aris_pm2 <- calc_om_aris(solutions_matrix_pm2)
write_csv(data.frame(aris_pm2), proc_path("aris_pm2.csv", TRUE))
aris_pm3 <- calc_om_aris(solutions_matrix_pm3)
write_csv(data.frame(aris_pm3), proc_path("aris_pm3.csv", TRUE))
aris_pm4 <- calc_om_aris(solutions_matrix_pm4)
write_csv(data.frame(aris_pm4), proc_path("aris_pm4.csv", TRUE))
aris_pm5 <- calc_om_aris(solutions_matrix_pm5)
write_csv(data.frame(aris_pm5), proc_path("aris_pm5.csv", TRUE))

all_mtbi_imputations <- do.call(
    "rbind",
    list(
        solutions_matrix_m1,
        solutions_matrix_m2,
        solutions_matrix_m3,
        solutions_matrix_m4,
        solutions_matrix_m5,
        solutions_matrix_pm1,
        solutions_matrix_pm2,
        solutions_matrix_pm3,
        solutions_matrix_pm4,
        solutions_matrix_pm5
    )
)

aris_all_mtbi_imputations <- calc_om_aris(all_mtbi_imputations)
write_csv(data.frame(aris_all_mtbi_imputations), proc_path("aris_all_mtbi_imputations.csv", TRUE))
```

```{r}
aris_m1 <- read_csv(proc_path("2023_12_07_aris_m1.csv")) |> as.matrix()
aris_m2 <- read_csv(proc_path("2023_12_07_aris_m2.csv")) |> as.matrix()
aris_m3 <- read_csv(proc_path("2023_12_07_aris_m3.csv")) |> as.matrix()
aris_m4 <- read_csv(proc_path("2023_12_07_aris_m4.csv")) |> as.matrix()
aris_m5 <- read_csv(proc_path("2023_12_07_aris_m5.csv")) |> as.matrix()
aris_pm1 <- read_csv(proc_path("2023_12_07_aris_pm1.csv")) |> as.matrix()
aris_pm2 <- read_csv(proc_path("2023_12_07_aris_pm2.csv")) |> as.matrix()
aris_pm3 <- read_csv(proc_path("2023_12_07_aris_pm3.csv")) |> as.matrix()
aris_pm4 <- read_csv(proc_path("2023_12_07_aris_pm4.csv")) |> as.matrix()
aris_pm5 <- read_csv(proc_path("2023_12_07_aris_pm5.csv")) |> as.matrix()

aris_all_mtbi_imputations <- read_csv(proc_path("2023_12_07_aris_all_mtbi_imputations.csv")) |> as.matrix()

aris_all_mtbi_imputations_heatmap <- similarity_matrix_heatmap(
    aris_all_mtbi_imputations,
    log_graph = FALSE,
    cluster_rows = TRUE,
    cluster_columns = TRUE
)

aris_all_mtbi_imputations_heatmap <- ComplexHeatmap::draw(aris_all_mtbi_imputations_heatmap)

aris_all_mtbi_imputations_order <- ComplexHeatmap::row_order(aris_all_mtbi_imputations_heatmap)

aris_all_mtbi_imputations_order

write_csv(data.frame(aris_all_mtbi_imputations_order), proc_path("aris_all_mtbi_imputations_order.csv", TRUE))

aris_all_mtbi_imputations_order <- unlist(read_csv(proc_path("2023_12_07_aris_all_mtbi_imputations_order.csv")))

names(aris_all_mtbi_imputations_order) <- NULL

imputation_labels <- data.frame(
    "imputation" = c(
        rep("m1", 200),
        rep("m2", 200),
        rep("m3", 200),
        rep("m4", 200),
        rep("m5", 200),
        rep("pm1", 200),
        rep("pm2", 200),
        rep("pm3", 200),
        rep("pm4", 200),
        rep("pm5", 200)
    ),
    "pooled" = c(
        rep("yes", 1000),
        rep("no", 1000)
    )
)

full_solutions_matrix <- cbind(all_mtbi_imputations, imputation_labels)

full_solutions_matrix$"nclust2" <- full_solutions_matrix$"nclust" - 2

full_extended_solutions_matrix <- extend_solutions(
    full_solutions_matrix,
    oom_list_m1
)

full_oom_pvals <- pval_select(
    full_extended_solutions_matrix,
    negative_log = TRUE
)

full_extended_solutions_matrix$"mean_neglog_p" <- full_oom_pvals$"mean_neglog_p"

divergent_colours <- function(column)  {
    values <- unique(column)
    colours <- RColorBrewer::brewer.pal(n = length(values), name = "Set3")
    names(colours) <- values
    return(colours)
}

aris_all_mtbi_imputations_annotated_heatmap <- similarity_matrix_heatmap(
    aris_all_mtbi_imputations,
    order = aris_all_mtbi_imputations_order,
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    log_graph = FALSE,
    data = full_extended_solutions_matrix,
    top_hm = list(
        "Scheme" = "snf_scheme",
        "Impairment Separation" = "mean_neglog_p"
    ),
    left_hm = list(
        "Pooled?" = "pooled",
        "Imputation" = "imputation"
    ),
    top_bar = list(
        "Number of Clusters - 2" = "nclust2"
    ),
    scale_diag = "none",
    heatmap_height = grid::unit(19, "cm"),
    heatmap_width = grid::unit(19, "cm"),
    annotation_colours = list(
        "Pooled?" = c(
            "yes" = "orange",
            "no" = "purple"
        ),
        "Imputation" = divergent_colours(full_extended_solutions_matrix$"imputation"),
        "Scheme" = c(
            "1" = "#7FC97F",
            "2" = "#BEAED4",
            "3" = "#FDC086"
        ),
        "Impairment Separation" = hm_colours(full_extended_solutions_matrix$"mean_neglog_p")
    ),
    col = circlize::colorRamp2(
        c(min(aris_all_mtbi_imputations), max(aris_all_mtbi_imputations)),
        c("navy", "red")
    )
)

aris_all_mtbi_imputations_annotated_heatmap

# PNG export
grDevices::png(
    fig_path("aris_all_mtbi_imputations_annotated_heatmap.png", TRUE),
    width = 4000,
    height = 4000,
    res = 400
)
aris_all_mtbi_imputations_annotated_heatmap
grDevices::dev.off()
```

What are those clusters?

```{r}

aris_all_mtbi_imputations_chopped_heatmap <- similarity_matrix_heatmap(
    aris_all_mtbi_imputations,
    order = aris_all_mtbi_imputations_order,
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    log_graph = FALSE,
    data = full_extended_solutions_matrix,
    top_hm = list(
        "Scheme" = "snf_scheme",
        "Impairment Separation" = "mean_neglog_p"
    ),
    left_hm = list(
        "Pooled?" = "pooled",
        "Imputation" = "imputation"
    ),
    top_bar = list(
        "Number of Clusters - 2" = "nclust2"
    ),
    scale_diag = "none",
    heatmap_height = grid::unit(19, "cm"),
    heatmap_width = grid::unit(19, "cm"),
    annotation_colours = list(
        "Pooled?" = c(
            "yes" = "orange",
            "no" = "purple"
        ),
        "Imputation" = divergent_colours(full_extended_solutions_matrix$"imputation"),
        "Scheme" = c(
            "1" = "#7FC97F",
            "2" = "#BEAED4",
            "3" = "#FDC086"
        ),
        "Impairment Separation" = hm_colours(full_extended_solutions_matrix$"mean_neglog_p")
    ),
    col = circlize::colorRamp2(
        c(min(aris_all_mtbi_imputations), max(aris_all_mtbi_imputations)),
        c("navy", "red")
    ),
    row_split = split_at(
        vector = c(
            500,
            806,
            956,
            1227,
            1441
        ),
        nrow = 2000
    ),
    column_split = split_at(
        vector = c(
            500,
            806,
            956,
            1227,
            1441
        ),
        nrow = 2000
    )
)

aris_all_mtbi_imputations_chopped_heatmap


# PNG export
grDevices::png(
    fig_path("aris_all_mtbi_imputations_chopped_heatmap.png", TRUE),
    width = 4000,
    height = 4000,
    res = 400
)
aris_all_mtbi_imputations_chopped_heatmap
grDevices::dev.off()


# A deeper zoom on some of the small heatmaps

zoomed_mc_f <- aris_all_mtbi_imputations[aris_all_mtbi_imputations_order, aris_all_mtbi_imputations_order]

zoomed_mc_f <- zoomed_mc_f[1441:2000, 1441:2000]

nrow(zoomed_mc_f)

aris_all_mtbi_zoomed_mc_f_chopped_heatmap <- similarity_matrix_heatmap(
    zoomed_mc_f,
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    log_graph = FALSE,
    scale_diag = "none",
    heatmap_height = grid::unit(19, "cm"),
    heatmap_width = grid::unit(19, "cm"),
    col = circlize::colorRamp2(
        c(min(aris_all_mtbi_imputations), max(aris_all_mtbi_imputations)),
        c("navy", "red")
    ),
    row_split = paste0(
        "F-",
        split_at(
            vector = c(
                78,
                253,
                290,
                336,
                400,
                520
            ),
            nrow = 560
        )
    ),
    column_split = paste0(
        "F-",
        split_at(
            vector = c(
                78,
                253,
                290,
                336,
                400,
                520
            ),
            nrow = 560
        )
    )
)
aris_all_mtbi_zoomed_mc_f_chopped_heatmap


# PNG export
grDevices::png(
    fig_path("aris_all_mtbi_zoomed_mc_f_chopped_heatmap.png", TRUE),
    width = 4000,
    height = 4000,
    res = 400
)
aris_all_mtbi_zoomed_mc_f_chopped_heatmap
grDevices::dev.off()


zoomed_mc_f_chopped_heatmap


# HERE I AM!

aris_all_mtbi_imputations_chopped_heatmap

# Who are those solutions?
mc_b_rows <- aris_all_mtbi_imputations_order[500:806]
mc_b_solutions <- full_extended_solutions_matrix[mc_b_rows, ]
mc_b_solutions
nrow(full_solutions_matrix)
data_list_m1[[1]]$"data"$"clusters" <- get_clusters(mc_b_solutions[20, ])
data_list_m1
key_associations_df <- calculate_associations(
    data_list_m1,
    key_association = "clusters"
)
manhattan_plot(
    key_associations_df,
    key_mode = TRUE,
    threshold = 0.05,
    bonferroni_line = TRUE
)
library(ggplot2)
ggsave(fig_path("mc_b_associations.png", TRUE))
extended_solutions_matrix <- extend_solutions(solutions_matrix, target_list)

# Who are those solutions?
mc_c_rows <- aris_all_mtbi_imputations_order[956:1227]
mc_c_solutions <- full_extended_solutions_matrix[mc_c_rows, ]
mc_c_solutions
nrow(full_solutions_matrix)
data_list_m1[[1]]$"data"$"clusters" <- get_clusters(mc_c_solutions[20, ])
data_list_m1
key_associations_df <- calculate_associations(
    data_list_m1,
    key_association = "clusters"
)
manhattan_plot(
    key_associations_df,
    key_mode = TRUE,
    threshold = 0.05,
    bonferroni_line = TRUE
)
library(ggplot2)
ggsave(fig_path("mc_c_associations.png", TRUE))

# Who are those solutions?
mc_d_rows <- aris_all_mtbi_imputations_order[1227:1441]
mc_d_solutions <- full_extended_solutions_matrix[mc_d_rows, ]
mc_d_solutions
nrow(full_solutions_matrix)
data_list_m1[[1]]$"data"$"clusters" <- get_clusters(mc_d_solutions[20, ])
data_list_m1
key_associations_df <- calculate_associations(
    data_list_m1,
    key_association = "clusters"
)
manhattan_plot(
    key_associations_df,
    key_mode = TRUE,
    threshold = 0.05,
    bonferroni_line = TRUE
)
library(ggplot2)
ggsave(fig_path("mc_d_associations.png", TRUE))

```


```{r}
###############################################################################
# 4. Calculate pairwise solution similarities
###############################################################################
aris_m1 <- calc_om_aris(solutions_matrix_m1)

write_csv(data.frame(aris_m1), proc_path("aris_m1.csv", TRUE))

aris_m1 <- read_csv(proc_path("2023_12_01_aris_m1.csv"))
aris_m1 <- as.matrix(aris_m1)
colnames(aris_m1) <- 1:nrow(aris_m1)
rownames(aris_m1) <- 1:nrow(aris_m1)
```

Back to more lightweight functions:

```{r}
###############################################################################
# 5. Extract order of pairwise solution similarities
###############################################################################
aris_m1_heatmap <- similarity_matrix_heatmap(
    aris_m1,
    log_graph = FALSE,
    cluster_rows = TRUE,
    cluster_columns = TRUE,
)

aris_m1_heatmap <- ComplexHeatmap::draw(aris_m1_heatmap)

aris_m1_order <- ComplexHeatmap::row_order(aris_m1_heatmap)

write_csv(data.frame(aris_m1_order), proc_path("aris_m1_order.csv", TRUE))

aris_m1_order <- unlist(read_csv(proc_path("2023_12_01_aris_m1_order.csv")))

###############################################################################
# 5. Visualize reordered settings matrix and similarity matrix
###############################################################################
# No saving
settings_matrix_heatmap(
    settings_matrix,
    order = aris_m1_order,
    show_rownames = FALSE
)

settings_matrix_heatmap(
    settings_matrix,
    order = aris_m1_order,
    show_rownames = FALSE,
    save = fig_path("aris_m1_ordered_settings_matrix_heatmap.png", TRUE)
)
```

By visual inspection, there appears to be non-random organization based on the parameters k, and snf_scheme.
Below is the actual adjusted rand index heatmap with these hyperparameters highlighted.

```{r}

aris_m1_annotated_heatmap <- similarity_matrix_heatmap(
    aris_m1,
    order = aris_m1_order,
    log_graph = FALSE,
    data = solutions_matrix_m1,
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    top_hm = list(
        "Scheme" = "snf_scheme"
    ),
    bottom_bar = list(
        "K" = "k"
    ),
    scale_diag = "none",
    heatmap_height = grid::unit(19, "cm"),
    heatmap_width = grid::unit(19, "cm"),
    annotation_colours = list(
        "Scheme" = c(
            "1" = "#7FC97F",
            "2" = "#BEAED4",
            "3" = "#FDC086"
        )
    ),
    col = circlize::colorRamp2(
        c(min(aris_m1), max(aris_m1)),
        c("navy", "red")
    )
)

# No saving
aris_m1_annotated_heatmap

# PDF export
grDevices::pdf(
    fig_path("aris_m1_annotated_heatmap.pdf", TRUE),
    width = 10,
    height = 10
)
aris_m1_annotated_heatmap
grDevices::dev.off()

# PNG export
grDevices::png(
    fig_path("aris_m1_annotated_heatmap.png", TRUE),
    width = 4000,
    height = 3000,
    res = 400
)
aris_m1_annotated_heatmap
grDevices::dev.off()
```

A few "meta clusters" are visible in the pairwise ARI heatmap.

Let's see how they associate with the out of model measures:

```{r}

extended_solutions_matrix_m1 <- extend_solutions(
    solutions_matrix_m1,
    oom_list_m1
)

write_csv(
    extended_solutions_matrix_m1,
    proc_path(
        "extended_solutions_matrix_m1.csv",
        TRUE
    )
)

extended_solutions_matrix_m1 <- read_csv(
    proc_path(
        "2023_12_04_extended_solutions_matrix_m1.csv"
    )
)


oom_m1_pvals <- pval_select(
    extended_solutions_matrix_m1,
    negative_log = TRUE
)


pval_hm_m1 <- pval_heatmap(oom_m1_pvals, order = aris_m1_order, max_red = TRUE)

# No saving
pval_hm_m1

# PNG export
grDevices::png(
    fig_path("pval_hm_m1.png", TRUE),
    width = 4000,
    height = 3000,
    res = 400
)
pval_hm_m1
grDevices::dev.off()

extended_solutions_matrix_m1$"mean_neglog_p" <- oom_m1_pvals$"mean_neglog_p"

aris_m1_extended_annotated_heatmap <- similarity_matrix_heatmap(
    aris_m1,
    order = aris_m1_order,
    log_graph = FALSE,
    data = extended_solutions_matrix_m1,
    bottom_hm = list(
        "SNF Scheme" = "snf_scheme"
    ),
    top_hm = list(
        "Impairment Separation" = "mean_neglog_p"
    ),
    bottom_bar = list(
        "K" = "k",
        "Number of Clusters" = "nclust"
    ),
    scale_diag = "none",
    heatmap_height = grid::unit(19, "cm"),
    heatmap_width = grid::unit(19, "cm"),
    annotation_colours = list(
        "SNF Scheme" = c(
            "1" = "orange",
            "2" = "purple",
            "3" = "turquoise"
        ),
        "Impairment Separation" = hm_colours(oom_m1_pvals$"mean_neglog_p")
    ),
    col = circlize::colorRamp2(
        c(min(aris_m1), max(aris_m1)),
        c("navy", "red")
    )
)

# No saving
aris_m1_extended_annotated_heatmap

# PNG export
grDevices::png(
    fig_path("aris_m1_extended_annotated_heatmap.png", TRUE),
    width = 4000,
    height = 3000,
    res = 400
)
aris_m1_extended_annotated_heatmap
grDevices::dev.off()
```

Next steps:

- repeat for the other imputations and see how well the structure holds.
