# metaSNF of Baseline mTBI Subjects

This chapter contains:

1. Derivation of baseline mTBI subtypes with metasnf
2. Characterization of those subtypes

## Importing packages and establishing file paths

```{r}
# CHECKPOINT 
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(ggplot2)
library(patchwork)
library(xtable)
library(compute.es)
library(dplyr)
library(fastDummies)
library(tidyr)
library(nnet)
library(ComplexHeatmap)

input_path      <- path_maker(here(paste0("data/abcd/inputs")))
proc_path       <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path        <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path        <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_ns_der_subs <- readRDS(sub_path("2025_09_11_mtbi_der_no_sibs_subs.rds"))
mtbi_ns_val_subs <- readRDS(sub_path("2025_09_11_mtbi_val_no_sibs_subs.rds"))

mtbi_ns_subs     <- readRDS(sub_path("2025_09_11_mtbi_no_sibs_subs.rds"))
```

## Importing data

`all_dls` contains all the imputed data lists (including out of model data lists) for the mTBI derivation (train) and validation (test) splits, as well as for the uninjured subjects.

```{r}
all_dls_h <- readRDS(proc_path("2025_09_11_all_dls_h.rds"))
all_dls_h_ns <- readRDS(proc_path("2025_09_11_all_dls_h_no_sibs.rds"))

names(all_dls_h_ns)
```

## Generating the SNF config

```{r}
set.seed(42)
mtbi_config <- snf_config(
    all_dls_h_ns$"mtbi_der_u_dls"$"imp_1",
    n_solutions = 200,
    cnt_dist_fns = list("standard_norm_euclidean" = sn_euclidean_distance),
    dsc_dist_fns = list("standard_norm_euclidean" = sn_euclidean_distance),
    ord_dist_fns = list("standard_norm_euclidean" = sn_euclidean_distance),
    use_default_dist_fns = TRUE
)

saveRDS(mtbi_config, proc_path("mtbi_config.rds", TRUE))
```

## Running SNF for each of the imputations

```{r}
# CHECKPOINT
mtbi_config <- readRDS(proc_path("2025_09_15_mtbi_config.rds"))

run_mtbi_der_u_batch_snf <- function(x) {
    progressr::with_progress({
        batch_snf(
            dl = all_dls_h_ns$"mtbi_der_u_dls"[[x]],
            sc = mtbi_config,
            processes = "max"
        )
    })
}

run_mtbi_der_p_batch_snf <- function(x) {
    progressr::with_progress({
        batch_snf(
            dl = all_dls_h_ns$"mtbi_der_p_dls"[[x]],
            sc = mtbi_config,
            processes = "max"
        )
    })
}
```

```{r}
# mtbi derivation set unpooled sample
mtbi_der_sol_df_u1 <- run_mtbi_der_u_batch_snf(1)
saveRDS(mtbi_der_sol_df_u1, proc_path("mtbi_der_sol_df_u1.rds", TRUE))

mtbi_der_sol_df_u2 <- run_mtbi_der_u_batch_snf(2)
saveRDS(mtbi_der_sol_df_u2, proc_path("mtbi_der_sol_df_u2.rds", TRUE))
```

```{r}
mtbi_der_sol_df_u3 <- run_mtbi_der_u_batch_snf(3)
saveRDS(mtbi_der_sol_df_u3, proc_path("mtbi_der_sol_df_u3.rds", TRUE))

mtbi_der_sol_df_u4 <- run_mtbi_der_u_batch_snf(4)
saveRDS(mtbi_der_sol_df_u4, proc_path("mtbi_der_sol_df_u4.rds", TRUE))

mtbi_der_sol_df_u5 <- run_mtbi_der_u_batch_snf(5)
saveRDS(mtbi_der_sol_df_u5, proc_path("mtbi_der_sol_df_u5.rds", TRUE))
```

```{r}
# mtbi derivation set pooled sample
mtbi_der_sol_df_p1 <- run_mtbi_der_p_batch_snf(1)
saveRDS(mtbi_der_sol_df_p1, proc_path("mtbi_der_sol_df_p1.rds", TRUE))
#
mtbi_der_sol_df_p2 <- run_mtbi_der_p_batch_snf(2)
saveRDS(mtbi_der_sol_df_p2, proc_path("mtbi_der_sol_df_p2.rds", TRUE))
```

```{r}
mtbi_der_sol_df_p3 <- run_mtbi_der_p_batch_snf(3)
saveRDS(mtbi_der_sol_df_p3, proc_path("mtbi_der_sol_df_p3.rds", TRUE))
#
mtbi_der_sol_df_p4 <- run_mtbi_der_p_batch_snf(4)
saveRDS(mtbi_der_sol_df_p4, proc_path("mtbi_der_sol_df_p4.rds", TRUE))
#
mtbi_der_sol_df_p5 <- run_mtbi_der_p_batch_snf(5)
saveRDS(mtbi_der_sol_df_p5, proc_path("mtbi_der_sol_df_p5.rds", TRUE))
```

```{r}
mtbi_der_sol_df_u1 <- readRDS(proc_path("2025_09_15_mtbi_der_sol_df_u1.rds"))
mtbi_der_sol_df_u2 <- readRDS(proc_path("2025_09_15_mtbi_der_sol_df_u2.rds"))
mtbi_der_sol_df_u3 <- readRDS(proc_path("2025_09_15_mtbi_der_sol_df_u3.rds"))
mtbi_der_sol_df_u4 <- readRDS(proc_path("2025_09_15_mtbi_der_sol_df_u4.rds"))
mtbi_der_sol_df_u5 <- readRDS(proc_path("2025_09_15_mtbi_der_sol_df_u5.rds"))

mtbi_der_sol_df_p1 <- readRDS(proc_path("2025_09_15_mtbi_der_sol_df_p1.rds"))
mtbi_der_sol_df_p2 <- readRDS(proc_path("2025_09_15_mtbi_der_sol_df_p2.rds"))
mtbi_der_sol_df_p3 <- readRDS(proc_path("2025_09_15_mtbi_der_sol_df_p3.rds"))
mtbi_der_sol_df_p4 <- readRDS(proc_path("2025_09_15_mtbi_der_sol_df_p4.rds"))
mtbi_der_sol_df_p5 <- readRDS(proc_path("2025_09_15_mtbi_der_sol_df_p5.rds"))
```

```{r}
mtbi_der_sol_df <- do.call(
    "rbind",
    c(
        list(
            mtbi_der_sol_df_u1,
            mtbi_der_sol_df_u2,
            mtbi_der_sol_df_u3,
            mtbi_der_sol_df_u4,
            mtbi_der_sol_df_u5,
            mtbi_der_sol_df_p1,
            mtbi_der_sol_df_p2,
            mtbi_der_sol_df_p3,
            mtbi_der_sol_df_p4,
            mtbi_der_sol_df_p5
        ),
        list(reset_indices = TRUE)
    )
)
saveRDS(mtbi_der_sol_df, proc_path("mtbi_der_sol_df.rds", TRUE))

mtbi_der_ari <- calc_aris(mtbi_der_sol_df, processes = "max")
saveRDS(mtbi_der_ari, proc_path("mtbi_der_ari.rds", TRUE))
```

```{r}
mtbi_der_ari_order <- get_matrix_order(mtbi_der_ari)
saveRDS(mtbi_der_ari_order, proc_path("mtbi_der_ari_order.rds", TRUE))
```

## Re-importing data

```{r}
# CHECKPOINT
mtbi_der_sol_df    <- readRDS(proc_path("2025_09_15_mtbi_der_sol_df.rds"))
mtbi_der_ari       <- readRDS(proc_path("2025_09_15_mtbi_der_ari.rds"))
mtbi_der_ari_order <- readRDS(proc_path("2025_09_15_mtbi_der_ari_order.rds"))
```

## Calculating associations between cluster solutions and features

```{r}
run_extend_solutions <- function(name, x) {
    imp <- paste0("imp_", if (max(x %% 5) > 0) max(x %% 5) else 5)
    cat(
        "Extending rows: ", 
        (200*(x-1) + 1),
        " to ",
        (200*x),
        " for imputation ",
        imp,
        ".\n",
        sep = ""
    )
    extend_solutions(
        mtbi_der_sol_df[(200*(x-1) + 1):(200*x), ],
        dl = all_dls_h_ns[[paste0(name, "_dls")]][[imp]],
        target_dl = all_dls_h_ns[[paste0(name, "_ols")]][[imp]],
        min_pval = 1e-10,
        processes = "max"
    )
}
```

```{r}
# Unpooled imputations
mtbi_der_ext_sol_df_u1 <- run_extend_solutions("mtbi_der_u", 1)
saveRDS(mtbi_der_ext_sol_df_u1, proc_path("mtbi_der_ext_sol_df_u1.rds", TRUE))
mtbi_der_ext_sol_df_u2 <- run_extend_solutions("mtbi_der_u", 2)
saveRDS(mtbi_der_ext_sol_df_u2, proc_path("mtbi_der_ext_sol_df_u2.rds", TRUE))
mtbi_der_ext_sol_df_u3 <- run_extend_solutions("mtbi_der_u", 3)
saveRDS(mtbi_der_ext_sol_df_u3, proc_path("mtbi_der_ext_sol_df_u3.rds", TRUE))
mtbi_der_ext_sol_df_u4 <- run_extend_solutions("mtbi_der_u", 4)
saveRDS(mtbi_der_ext_sol_df_u4, proc_path("mtbi_der_ext_sol_df_u4.rds", TRUE))
mtbi_der_ext_sol_df_u5 <- run_extend_solutions("mtbi_der_u", 5)
saveRDS(mtbi_der_ext_sol_df_u5, proc_path("mtbi_der_ext_sol_df_u5.rds", TRUE))
```

```{r}
mtbi_der_ext_sol_df_p1 <- run_extend_solutions("mtbi_der_p", 6)
saveRDS(mtbi_der_ext_sol_df_p1, proc_path("mtbi_der_ext_sol_df_p1.rds", TRUE))
mtbi_der_ext_sol_df_p2 <- run_extend_solutions("mtbi_der_p", 7)
saveRDS(mtbi_der_ext_sol_df_p2, proc_path("mtbi_der_ext_sol_df_p2.rds", TRUE))
mtbi_der_ext_sol_df_p3 <- run_extend_solutions("mtbi_der_p", 8)
saveRDS(mtbi_der_ext_sol_df_p3, proc_path("mtbi_der_ext_sol_df_p3.rds", TRUE))
mtbi_der_ext_sol_df_p4 <- run_extend_solutions("mtbi_der_p", 9)
saveRDS(mtbi_der_ext_sol_df_p4, proc_path("mtbi_der_ext_sol_df_p4.rds", TRUE))
mtbi_der_ext_sol_df_p5 <- run_extend_solutions("mtbi_der_p", 10)
saveRDS(mtbi_der_ext_sol_df_p5, proc_path("mtbi_der_ext_sol_df_p5.rds", TRUE))
```

```{r}
mtbi_der_ext_sol_df_u1 <- readRDS(proc_path("2025_09_15_mtbi_der_ext_sol_df_u1.rds"))
mtbi_der_ext_sol_df_u2 <- readRDS(proc_path("2025_09_15_mtbi_der_ext_sol_df_u2.rds"))
mtbi_der_ext_sol_df_u3 <- readRDS(proc_path("2025_09_15_mtbi_der_ext_sol_df_u3.rds"))
mtbi_der_ext_sol_df_u4 <- readRDS(proc_path("2025_09_15_mtbi_der_ext_sol_df_u4.rds"))
mtbi_der_ext_sol_df_u5 <- readRDS(proc_path("2025_09_15_mtbi_der_ext_sol_df_u5.rds"))
mtbi_der_ext_sol_df_p1 <- readRDS(proc_path("2025_09_15_mtbi_der_ext_sol_df_p1.rds"))
mtbi_der_ext_sol_df_p2 <- readRDS(proc_path("2025_09_15_mtbi_der_ext_sol_df_p2.rds"))
mtbi_der_ext_sol_df_p3 <- readRDS(proc_path("2025_09_15_mtbi_der_ext_sol_df_p3.rds"))
mtbi_der_ext_sol_df_p4 <- readRDS(proc_path("2025_09_15_mtbi_der_ext_sol_df_p4.rds"))
mtbi_der_ext_sol_df_p5 <- readRDS(proc_path("2025_09_15_mtbi_der_ext_sol_df_p5.rds"))

drop_mtbi_cols <- function(x) {
    x[, !grepl("mtbi", colnames(x))]
}

# To be able to vertically stack all the pooled and unpooled solutions data frames
mtbi_der_ext_sol_df_u1_no_mtbi <- drop_mtbi_cols(mtbi_der_ext_sol_df_u1)
mtbi_der_ext_sol_df_u2_no_mtbi <- drop_mtbi_cols(mtbi_der_ext_sol_df_u2)
mtbi_der_ext_sol_df_u3_no_mtbi <- drop_mtbi_cols(mtbi_der_ext_sol_df_u3)
mtbi_der_ext_sol_df_u4_no_mtbi <- drop_mtbi_cols(mtbi_der_ext_sol_df_u4)
mtbi_der_ext_sol_df_u5_no_mtbi <- drop_mtbi_cols(mtbi_der_ext_sol_df_u5)

mtbi_der_ext_sol_df <- do.call(
    "rbind",
    c(
        list(
            mtbi_der_ext_sol_df_u1_no_mtbi,
            mtbi_der_ext_sol_df_u2_no_mtbi,
            mtbi_der_ext_sol_df_u3_no_mtbi,
            mtbi_der_ext_sol_df_u4_no_mtbi,
            mtbi_der_ext_sol_df_u5_no_mtbi,
            mtbi_der_ext_sol_df_p1,
            mtbi_der_ext_sol_df_p2,
            mtbi_der_ext_sol_df_p3,
            mtbi_der_ext_sol_df_p4,
            mtbi_der_ext_sol_df_p5
        ),
        list(reset_indices = TRUE)
    )
)

mtbi_der_ext_sol_df   

saveRDS(mtbi_der_ext_sol_df, proc_path("mtbi_der_ext_sol_df.rds", TRUE))
```

```{r}
# CHECKPOINT
mtbi_der_ext_sol_df <- readRDS(proc_path("2025_09_15_mtbi_der_ext_sol_df.rds"))
```

## Identifying and visualizing meta clusters

```{r}
mtbi_der_ari_hm <- meta_cluster_heatmap(
    mtbi_der_ari,
    order = mtbi_der_ari_order
)

divergent_colours <- function(column)  {
    values <- unique(column)
    colours <- RColorBrewer::brewer.pal(n = length(values), name = "Set3")
    names(colours) <- values
    return(colours)
}

mtbi_der_esdf <- as.data.frame(mtbi_der_ext_sol_df)

mtbi_der_esdf$"impairment_separation" <- -log10(mtbi_der_esdf$"mean_pval")

mtbi_der_esdf$"pool" <- c(rep("no", 1000), rep("yes", 1000))

mtbi_der_esdf$"imputation" <- c(
    rep("u1", 200),
    rep("u2", 200),
    rep("u3", 200),
    rep("u4", 200),
    rep("u5", 200),
    rep("p1", 200),
    rep("p2", 200),
    rep("p3", 200),
    rep("p4", 200),
    rep("p5", 200)
)

write_csv(mtbi_der_esdf, proc_path("mtbi_der_esdf.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_der_esdf <- read_csv(proc_path("2025_09_15_mtbi_der_esdf.csv"))
```


```{r}
mtbi_der_split_vec <- c(
    163,
    538,
    695,
    #800,
    915,
    1175,
    1275,
    1550
)
saveRDS(mtbi_der_split_vec, proc_path("mtbi_split_vec.rds", TRUE))
mtbi_der_split_vec <- readRDS(proc_path("2025_09_15_mtbi_split_vec.rds"))
mtbi_der_ari_hm <- meta_cluster_heatmap(
    x = mtbi_der_ari,
    order = mtbi_der_ari_order,
    data = mtbi_der_esdf,
    min_colour = "black",
    split_vector = mtbi_der_split_vec,
    top_hm = list(
        "Impairment Separation" = "impairment_separation"
    ),
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    left_hm = list(
        "Pooled" = "pool",
        "Imputation" = "imputation"
    ),
    annotation_colours = list(
        "Impairment Separation" = colour_scale(
            mtbi_der_esdf$"impairment_separation",
            min_colour = "gray7",
            max_colour = "limegreen"
        ),
        "Imputation" = divergent_colours(mtbi_der_esdf$"imputation"),
        "Pooled" = c(
            "yes" = "orange",
            "no" = "purple"
        )
    )
)
mtbi_der_ari_hm

save_heatmap(
    heatmap = mtbi_der_ari_hm,
    path = fig_path("mtbi_der_ari_hm.png", TRUE),
    width = 950,
    height = 900,
    res = 100
)
```

```{r}
mtbi_der_mc_sol_df <- label_meta_clusters(
    mtbi_der_ext_sol_df,
    order = mtbi_der_ari_order,
    split_vector = mtbi_der_split_vec
)

saveRDS(mtbi_der_mc_sol_df, proc_path("mtbi_der_mc_sol_df.rds", TRUE))
```

```{r}
# CHECKPOINT
mtbi_der_mc_sol_df <- readRDS(proc_path("2025_09_15_mtbi_der_mc_sol_df.rds"))


as.data.frame(mtbi_der_mc_sol_df) |>
    dplyr::filter(mc == "D") |>
    nrow()

as.data.frame(mtbi_der_mc_sol_df) |>
    dplyr::filter(mc == "D") |>
    dplyr::filter(mean_pval < 0.001 & nclust == 3) |>
    nrow()

as.data.frame(mtbi_der_mc_sol_df) |>
    dplyr::filter(mc == "D") |>
    dplyr::filter(nclust == 3) |>
    dplyr::select(mean_pval) |>
    unlist() |> 
    log10() |>
    as.numeric() |>
    saveRDS(proc_path("mtbi_der_mc_d_pvals.rds", TRUE))

```

When picking out representative solutions, I'd like to preferentially go for solutions that derived from solo rather than pooled imputations, as those solutions have values for all features.

```{r}
# Function to try to lean on mTBI-including solutions when possible.
# This function will pick from solo solutions unless over 70% of the meta
# cluster is pooled.
restrict_fn <- function(x, threshold = 0.5) {
    x_solo_ind <- x$"solution" %in% 1:1000
    x_pool_ind <- x$"solution" %in% 1001:2000
    x_solo <- x[x_solo_ind, ]
    x_pool <- x[x_pool_ind, ]
    frac_solo <- nrow(x_solo) / (nrow(x_solo) + nrow(x_pool))
    if (frac_solo < threshold) {
        return(x[x_pool_ind, ])
    } else {
        return(x[x_solo_ind, ])
    }
}

mtbi_der_rep_solutions <- get_representative_solutions(
    mtbi_der_ari,
    mtbi_der_mc_sol_df,
    filter_fn = restrict_fn
)

saveRDS(mtbi_der_rep_solutions, proc_path("mtbi_der_rep_solutions.rds", TRUE))
```

```{r}
mtbi_der_rep_solutions <- readRDS(
    proc_path("2025_09_15_mtbi_der_rep_solutions.rds")
)

mtbi_der_rep_solutions

# Top solution is meta cluster D, represented by solution 881
mtbi_der_top_solution <- mtbi_der_ext_sol_df_u5[mtbi_der_ext_sol_df_u5$"solution" == 881, ]

mtbi_der_top_solution$"mc" <- "D"

saveRDS(mtbi_der_top_solution, proc_path("mtbi_der_top_solution.rds", TRUE))
```

```{r}
# CHECKPOINT
mtbi_der_top_solution <- readRDS(
    proc_path("2025_09_15_mtbi_der_top_solution.rds")
)

mtbi_der_top_solution$"mc" <- "Derivation MC D"

mtbi_der_manhattan <- mc_manhattan_plot(
    mtbi_der_top_solution,
    dl = all_dls_h_ns$"mtbi_der_u_dls"$"imp_5",
    target_dl = all_dls_h_ns$"mtbi_der_u_ols"$"imp_5",
    domain_colours = c(
        "AS" = "#85929e",
        "D" = "#bb8fce",
        "N" = "#e59866",
        "MH" = "#7fb3d5",
        "P" = "#52be80",
        "S" = "#d98880",
        "B" = "#ff3131"
    )
)
mtbi_der_manhattan

ggsave(
    plot = mtbi_der_manhattan,
    filename = fig_path("mtbi_der_manhattan.png", TRUE),
    width = 18,
    height = 5,
    dpi = 120
)
```

```{r}
# Initial visualizations
plot_list <- auto_plot(
    sol_df_row = mtbi_der_top_solution,
    dl = c(
        all_dls_h_ns$"mtbi_der_u_dls"$"imp_5",
        all_dls_h_ns$"mtbi_der_u_ols"$"imp_5"
    ),
    verbose = TRUE
)

plot_list$"sex"

plot_list$"race"

plot_list$"household_income"

# In anticipation of the upcoming cluster swaps
cluster_label_swap <- function(solutions_matrix, c_a, c_b) {
    swapped_sm <- dplyr::mutate(
        solutions_matrix,
        across(
            dplyr::starts_with("uid"),
            ~ ifelse(. == c_a, c_b, ifelse(. == c_b, c_a, .))
        )
    )
    return(swapped_sm)
}

mtbi_der_top_solution_swp <- cluster_label_swap(mtbi_der_top_solution, 2, 3)

saveRDS(
    mtbi_der_top_solution_swp,
    proc_path("mtbi_der_top_solution_swp.rds", TRUE)
)
```

```{r}
# CHECKPOINT
mtbi_der_top_solution_swp <- readRDS(
    proc_path("2025_09_15_mtbi_der_top_solution_swp.rds")
)
```

```{r}
plot_list <- auto_plot(
    sol_df_row = mtbi_der_top_solution_swp,
    dl = c(
        all_dls_h_ns$"mtbi_der_u_dls"$"imp_5",
        all_dls_h_ns$"mtbi_der_u_ols"$"imp_5"
    ),
    verbose = TRUE
)

saveRDS(plot_list, fig_path("mtbi_der_top_solution_pl.rds", TRUE))
```

```{r}
# CHECKPOINT
der_dl_u5 <- all_dls_h_ns$"mtbi_der_u_dls"$"imp_5"
der_ol_u5 <- all_dls_h_ns$"mtbi_der_u_ols"$"imp_5" 
der_io_dl_u5 <- c(der_dl_u5, der_ol_u5)
```

## Feature importance

### Rank by NMI

```{r}
progressr::with_progress({
    nmis <- calc_nmis(der_dl_u5, mtbi_der_top_solution_swp)
})

nmi_order <- sort(nmis$"s881", decreasing = TRUE, index.return = TRUE)
ordered_nmis <- nmis[nmi_order$ix, ]
ordered_nmis$"nmi_rank" <- rank(-ordered_nmis$"s881", ties.method = "min")
```

I also calculate p-value related ranks, however NMI scores are what are used in the manuscript.

```{r}
pvals <- get_pvals(mtbi_der_top_solution_swp, keep_summaries = FALSE)
pvals <- data.frame(
    "feature" = gsub("_pval", "", names(pvals)),
    "neg_log_pval" = -log10(as.numeric(unlist(pvals)))
)
pvals <- pvals[-1, ]
pvals_order <- sort(
    pvals$"neg_log_pval",
    decreasing = TRUE,
    index.return = TRUE
)
ordered_pvals <- pvals[pvals_order$ix, ]
ordered_pvals <- dplyr::filter(
    ordered_pvals,
    !grepl("^cbcl|^sds", feature)
)
ordered_pvals$"pval_rank" <- rank(
    -ordered_pvals$"neg_log_pval",
    ties.method = "min"
)
```

```{r}
mtbi_der_top_solution_nmi_v_pval <- dplyr::full_join(
    ordered_nmis,
    ordered_pvals,
    by = "feature"
)

domain_df <- der_dl_u5 |>
    summary("feature") |>
    dplyr::select(name, domain) |>
    dplyr::rename("feature" = "name")

domain_df

mtbi_der_top_solution_nmi_v_pval <- dplyr::inner_join(
    mtbi_der_top_solution_nmi_v_pval,
    domain_df,
    by = "feature"
)

mtbi_der_top_solution_nmi_v_pval <- dplyr::mutate(
    mtbi_der_top_solution_nmi_v_pval,
    nmi_plus_pval = nmi_rank + pval_rank
)

mtbi_der_top_solution_nmi_v_pval$"joint_rank" <- rank(
    mtbi_der_top_solution_nmi_v_pval$"nmi_plus_pval",
    ties.method = "min"
)

mtbi_der_top_solution_nmi_v_pval

mtbi_der_top_solution_nmi_v_pval_rank <- dplyr::rename(
    mtbi_der_top_solution_nmi_v_pval,
    "nmi" = "s881"
)

mtbi_der_top_solution_nmi_v_pval_rank <- dplyr::select(
    mtbi_der_top_solution_nmi_v_pval_rank,
    feature,
    domain,
    nmi,
    nmi_rank,
    neg_log_pval,
    pval_rank,
    joint_rank
)

write_csv(
    mtbi_der_top_solution_nmi_v_pval_rank,
    proc_path("mtbi_der_top_solution_nmi_v_pval_rank.csv", TRUE)
)
```

```{r}
# CHECKPOINT
mtbi_der_top_solution_nmi_v_pval_rank <- read_csv(
    proc_path("2025_09_15_mtbi_der_top_solution_nmi_v_pval_rank.csv")
)

options(width=200)
data.frame(mtbi_der_top_solution_nmi_v_pval_rank)
```

```{r}
# 2025-09-15
# Export input feature ranks
mtbi_der_top_solution_nmi_v_pval_rank |>
    dplyr::select(nmi_rank, dplyr::everything()) |>
    dplyr::select(-joint_rank, -pval_rank, -neg_log_pval) |>
    knitr::kable(format = "markdown", digits = 4) |>
    writeLines(proc_path("mtbi_der_top_solution_ift_ranks.txt", TRUE))

mtbi_der_top_solution_nmi_v_pval_rank

# Input features
ifts <- mtbi_der_top_solution_nmi_v_pval_rank$"feature"

# Output features
ofts <- features(der_ol_u5)

# All features
afts <- c(ifts, ofts)

saveRDS(ifts, proc_path("ifts.rds", TRUE))
saveRDS(afts, proc_path("afts.rds", TRUE))
saveRDS(ofts, proc_path("ofts.rds", TRUE))
```

```{r}
# CHECKPOINT
ifts <- readRDS(proc_path("2025_09_15_ifts.rds"))
afts <- readRDS(proc_path("2025_09_15_afts.rds"))
ofts <- readRDS(proc_path("2025_09_15_ofts.rds"))
```

```{r}
# Some file renaming
mtbi_der_top_solution_swp <- readRDS(
    proc_path("2025_09_15_mtbi_der_top_solution_swp.rds")
)

saveRDS(
    mtbi_der_top_solution_swp,
    proc_path("mtbi_der_solution.rds", TRUE)
)
```

```{r}
# CHECKPOINT 
mtbi_der_solution <- readRDS(proc_path("2025_09_15_mtbi_der_solution.rds"))
```

```{r}
# Feature plot generation
mtbi_der_plot_list <- auto_plot(
    sol_df_row = mtbi_der_solution,
    dl = c(der_dl_u5, der_ol_u5),
    save = fig_path("ap_mtbi_der_mc_d", TRUE),
    verbose = TRUE
)

# No save version:
mtbi_der_plot_list <- auto_plot(
    sol_df_row = mtbi_der_solution,
    dl = c(der_dl_u5, der_ol_u5),
    verbose = TRUE
)

saveRDS(mtbi_der_plot_list, fig_path("mtbi_der_plot_list.rds", TRUE))
```

```{r}
# CHECKPOINT
mtbi_der_plot_list <- readRDS(fig_path("2025_09_15_mtbi_der_plot_list.rds"))
```

### Visualizing top features

```{r}
mtbi_der_ranked_plot_list <- mtbi_der_plot_list[afts]

saveRDS(
    mtbi_der_ranked_plot_list,
    fig_path("mtbi_der_ranked_plot_list.rds", TRUE)
)

mtbi_der_ranked_plot_list <- readRDS(
    fig_path("2025_09_15_mtbi_der_ranked_plot_list.rds")
)

#mtbi_der_ranked_plots <- wrap_plots(mtbi_der_ranked_plot_list)
#ggsave(
#    fig_path("mtbi_der_ranked_plots.png", TRUE),
#    mtbi_der_ranked_plots,
#    width = 45,
#    height = 30,
#    dpi = 50
#)
```

```{r}
## Building a patchwork of the 20 plots
#top_pl <- mtbi_der_ranked_plot_list[1:20]
#for (i in seq_along(top_pl)) {
#    print(paste0(i, ": ", names(top_pl)[i]))
#}
#top_pl$"sex"                    <- top_pl$"sex"                    + labs(fill = "Sex") + scale_fill_discrete(labels = c("F", "M"))
#top_pl$"brain_volume"           <- top_pl$"brain_volume"           + labs(y = expression(paste("Brain Volume ", (mm^3))))
#top_pl$"cortical_sa"            <- top_pl$"cortical_sa"            + labs(y = expression(paste("Cortical Area ", (mm^2))))
#top_pl$"household_income"       <- top_pl$"household_income"       + labs(y = "Household Income")
#top_pl$"race"                   <- top_pl$"race"                   + labs(fill = "Race") + scale_fill_discrete(labels = c("Black", "Hispanic", "Other", "White"))
#top_pl$"pubertal_status_p"      <- top_pl$"pubertal_status_p"      + labs(y = "Pubertal Status\n(Parent Report)")
#top_pl$"activities_last_year"   <- top_pl$"activities_last_year"   + labs(y = "Total Activities\nthis Year")
#top_pl$"private_instruction"    <- top_pl$"private_instruction"    + labs(y = "Private Activities")
#top_pl$"extracurriculars"       <- top_pl$"extracurriculars"       + labs(y = "Lifetime\nExtracurriculars")
#top_pl$"parent_thought"         <- top_pl$"parent_thought"         + labs(y = "Parent Thought\nProblems")
#top_pl$"parent_somatic"         <- top_pl$"parent_somatic"         + labs(y = "Parent Somatic\nProblems")
#top_pl$"parent_antisocial"      <- top_pl$"parent_antisocial"      + labs(y = "Parent Antisocial\nProblems")
#top_pl$"weekday_screentime"     <- top_pl$"weekday_screentime"     + labs(y = "Weekday Screentime")
#top_pl$"fmri_cort_subcort_cors" <- top_pl$"fmri_cort_subcort_cors" + labs(y = "Cortical-Subcortical\nNetwork Correlation")
#top_pl$"parent_avoidant"        <- top_pl$"parent_avoidant"        + labs(y = "Parent Avoidant\nProblems")
#top_pl$"weekend_screentime"     <- top_pl$"weekend_screentime"     + labs(y = "Weekend\nScreentime")
#top_pl$"fmri_cort_cors"         <- top_pl$"fmri_cort_cors"         + labs(y = "Cortical-Cortical\nNetwork Correlation")
#top_pl$"parent_aggressive"      <- top_pl$"parent_aggressive"      + labs(y = "Parent Aggressive\nProblems")
#top_pl$"parent_withdrawn"       <- top_pl$"parent_withdrawn"       + labs(y = "Parent Withdrawn\nProblems")
#top_pl$"parent_anxdisord"       <- top_pl$"parent_anxdisord"       + labs(y = "Parent Anxiety\nProblems")
#top_p <- (wrap_plots(top_pl) & labs(x = "Cluster") & theme(plot.margin = unit(c(0.5, 1.5, 0.5, 2), "cm"))) + plot_annotation(tag_levels = '1')
#ggsave(
#    fig_path("mtbi_der_solution_top_20_ifts.png", TRUE),
#    top_p,
#    width = 25,
#    height = 15,
#    dpi = 150
#)
```

```{r}
# Data frame used to generate the auto plots
mtbi_der_solution_plot_df <- auto_plot(
    sol_df_row = mtbi_der_solution,
    dl = der_io_dl_u5,
    return_plots = FALSE
)

saveRDS(mtbi_der_solution_plot_df, proc_path("mtbi_der_solution_plot_df.rds", TRUE))
```

```{r}
# CHECKPOINT
mtbi_der_solution_plot_df <- readRDS(proc_path("2025_09_16_mtbi_der_solution_plot_df.rds"))
```

```{r}
#ofts_pl <- mtbi_der_ranked_plot_list[ofts]
#
#names(ofts_pl)
#
#clean_names <- c(
#    "CBCL\nAnxious-Depressed",
#    "CBCL\nWithdrawn-Depressed",
#    "CBCL\nSomatic Problems",
#    "CBCL\nSocial Problems",
#    "CBCL\nThought Problems",
#    "CBCL\nAttention Problems",
#    "CBCL\nRule-breaking Problems",
#    "CBCL\nAggression Problems",
#    "SDS Total\nSleeping Problems"
#)
#
#for (i in seq_along(ofts_pl)) {
#    ofts_pl[[i]] <- ofts_pl[[i]] + labs(y = clean_names[[i]], x = "Cluster")
#}
#
#ofts_p <- wrap_plots(ofts_pl) &
#          theme(plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), "cm"))
#
#ofts_p <- ofts_p + plot_annotation(tag_levels = '1')
#
#ggsave(
#    fig_path("mtbi_der_solution_ofts.png", TRUE),
#    ofts_p,
#    width = 14,
#    height = 14,
#    dpi = 150
#)
```

# Validation

```{r}
# CHECKPOINT
# The first test data set, for example
val_dl_u1 <- all_dls_h_ns$"mtbi_val_u_dls"$"imp_1"
val_dl_u2 <- all_dls_h_ns$"mtbi_val_u_dls"$"imp_2"
val_dl_u3 <- all_dls_h_ns$"mtbi_val_u_dls"$"imp_3"
val_dl_u4 <- all_dls_h_ns$"mtbi_val_u_dls"$"imp_4"
val_dl_u5 <- all_dls_h_ns$"mtbi_val_u_dls"$"imp_5"
val_ol_u1 <- all_dls_h_ns$"mtbi_val_u_ols"$"imp_1"
val_ol_u2 <- all_dls_h_ns$"mtbi_val_u_ols"$"imp_2"
val_ol_u3 <- all_dls_h_ns$"mtbi_val_u_ols"$"imp_3"
val_ol_u4 <- all_dls_h_ns$"mtbi_val_u_ols"$"imp_4"
val_ol_u5 <- all_dls_h_ns$"mtbi_val_u_ols"$"imp_5"
```

```{r}
mtbi_dl_1 <- merge(der_dl_u5, val_dl_u1)
mtbi_dl_2 <- merge(der_dl_u5, val_dl_u2)
mtbi_dl_3 <- merge(der_dl_u5, val_dl_u3)
mtbi_dl_4 <- merge(der_dl_u5, val_dl_u4)
mtbi_dl_5 <- merge(der_dl_u5, val_dl_u5)

mtbi_ol_1 <- merge(der_ol_u5, val_ol_u1)
mtbi_ol_2 <- merge(der_ol_u5, val_ol_u2)
mtbi_ol_3 <- merge(der_ol_u5, val_ol_u3)
mtbi_ol_4 <- merge(der_ol_u5, val_ol_u4)
mtbi_ol_5 <- merge(der_ol_u5, val_ol_u5)

saveRDS(mtbi_dl_1, input_path("mtbi_dl_1.rds", TRUE))
saveRDS(mtbi_dl_2, input_path("mtbi_dl_2.rds", TRUE))
saveRDS(mtbi_dl_3, input_path("mtbi_dl_3.rds", TRUE))
saveRDS(mtbi_dl_4, input_path("mtbi_dl_4.rds", TRUE))
saveRDS(mtbi_dl_5, input_path("mtbi_dl_5.rds", TRUE))

saveRDS(mtbi_ol_1, input_path("mtbi_ol_1.rds", TRUE))
saveRDS(mtbi_ol_2, input_path("mtbi_ol_2.rds", TRUE))
saveRDS(mtbi_ol_3, input_path("mtbi_ol_3.rds", TRUE))
saveRDS(mtbi_ol_4, input_path("mtbi_ol_4.rds", TRUE))
saveRDS(mtbi_ol_5, input_path("mtbi_ol_5.rds", TRUE))
```

```{r}
# CHECKPOINT
mtbi_dl_1 <- readRDS(input_path("2025_09_15_mtbi_dl_1.rds"))
mtbi_dl_2 <- readRDS(input_path("2025_09_15_mtbi_dl_2.rds"))
mtbi_dl_3 <- readRDS(input_path("2025_09_15_mtbi_dl_3.rds"))
mtbi_dl_4 <- readRDS(input_path("2025_09_15_mtbi_dl_4.rds"))
mtbi_dl_5 <- readRDS(input_path("2025_09_15_mtbi_dl_5.rds"))

mtbi_ol_1 <- readRDS(input_path("2025_09_15_mtbi_ol_1.rds"))
mtbi_ol_2 <- readRDS(input_path("2025_09_15_mtbi_ol_2.rds"))
mtbi_ol_3 <- readRDS(input_path("2025_09_15_mtbi_ol_3.rds"))
mtbi_ol_4 <- readRDS(input_path("2025_09_15_mtbi_ol_4.rds"))
mtbi_ol_5 <- readRDS(input_path("2025_09_15_mtbi_ol_5.rds"))
```

```{r}
mtbi_config <- readRDS(proc_path("2025_09_15_mtbi_config.rds"))

mtbi_sol_df <- batch_snf(
    dl = mtbi_dl_1,
    sc = mtbi_config,
    processes = 20
)

saveRDS(mtbi_sol_df, proc_path("mtbi_sol_df.rds", TRUE))
```

```{r}
mtbi_sol_df <- readRDS(proc_path("2025_09_16_mtbi_sol_df.rds"))
```

```{r}
mtbi_ext_sol_df <- extend_solutions(
    mtbi_sol_df,
    dl = mtbi_dl_1,
    target_dl = mtbi_ol_1,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(mtbi_ext_sol_df, proc_path("mtbi_ext_sol_df.rds", TRUE))
```

```{r}
# CHECKPOINT
mtbi_ext_sol_df <- readRDS(proc_path("2025_09_16_mtbi_ext_sol_df.rds"))
```

```{r}
# Filtering down to only 3 cluster solutions
mtbi_ext_sol_df_3c <- mtbi_ext_sol_df |>
    dplyr::filter(nclust == 3)

saveRDS(mtbi_ext_sol_df_3c, proc_path("mtbi_ext_sol_df_3c.rds", TRUE))

mtbi_ext_sol_df_3c <- readRDS(proc_path("2025_09_16_mtbi_ext_sol_df_3c.rds"))

nrow(mtbi_ext_sol_df_3c) # 43 of them

mtbi_ari_3c <- calc_aris(mtbi_ext_sol_df_3c, processes = "max")
saveRDS(mtbi_ari_3c, proc_path("mtbi_ari_3c.rds", TRUE))
```

```{r}
# CHECKPOINT
mtbi_ext_sol_df_3c <- readRDS(proc_path("2025_09_16_mtbi_ext_sol_df_3c.rds"))
mtbi_ari_3c <- readRDS(proc_path("2025_09_16_mtbi_ari_3c.rds"))
mtbi_der_solution <- readRDS(proc_path("2025_09_15_mtbi_der_solution.rds"))
```

Here I identify the cluster solution from the derivation + validation samples that is the most similar to the derivation sample solution in terms of its distribution of derivation sample observations.

```{r}
mtbi_ari_order_3c <- get_matrix_order(mtbi_ari_3c)
mtbi_esdf_3c <- as.data.frame(mtbi_ext_sol_df_3c)

drop_subs <- function(ext_solutions_df, subjects) {
    ext_solutions_df[, !colnames(ext_solutions_df) %in% subjects]
}

mtbi_ext_sol_df_3c_der_subs <- drop_subs(
    mtbi_ext_sol_df_3c,
    paste0("uid_", mtbi_ns_val_subs)
)

der_and_new_aris <- rbind(
    mtbi_ext_sol_df_3c_der_subs,
    mtbi_der_solution
) |> 
    calc_aris()

validation_order <- sort(der_and_new_aris["881", ], index.return = TRUE)$"ix"

# 3 cluster solutions sorted 
validation_heatmap <- meta_cluster_heatmap(
    der_and_new_aris,
    order = validation_order,
    show_row_names = TRUE
)
validation_heatmap

save_heatmap(
    heatmap = validation_heatmap,
    path = fig_path("validation_heatmap.png", TRUE),
    width = 650,
    height = 550,
    res = 75
)

validation_heatmap

# 117 is the most similar solution to the top derivation set solution
mtbi_top_solution <- mtbi_ext_sol_df_3c[mtbi_ext_sol_df_3c$"solution" == 117, ]

mtbi_top_solution <- cluster_label_swap(mtbi_top_solution, 2, 3)

saveRDS(mtbi_top_solution, proc_path("mtbi_top_solution.rds", TRUE))
```

```{r}
mtbi_top_solution <- readRDS(proc_path("2025_09_16_mtbi_top_solution.rds"))

mtbi_top_pl <- auto_plot(
    mtbi_top_solution,
    dl = c(mtbi_dl_1, mtbi_ol_1),
    verbose = TRUE
)

mtbi_top_pl$"sex"

saveRDS(mtbi_top_pl, proc_path("mtbi_top_pl.rds", TRUE))

mtbi_top_pl <- readRDS(proc_path("2025_09_16_mtbi_top_pl.rds"))
```

```{r}
mtbi_top_solution$"mc" <- "Pooled"

mtbi_top_manhattan <- mc_manhattan_plot(
    mtbi_top_solution,
    dl = mtbi_dl_1,
    target_dl = mtbi_ol_1,
    domain_colours = c(
        "AS" = "#85929e",
        "D" = "#bb8fce",
        "N" = "#e59866",
        "MH" = "#7fb3d5",
        "P" = "#52be80",
        "S" = "#d98880",
        "B" = "#ff3131"
    )
)
mtbi_top_manhattan

ggsave(
    plot = mtbi_top_manhattan,
    filename = fig_path("mtbi_top_manhattan.png", TRUE),
    width = 18,
    height = 5,
    dpi = 120
)

mtbi_der_numerator <- mtbi_der_manhattan + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

mtbi_manhattan_der_and_pool <- mtbi_der_numerator / mtbi_top_manhattan

ggsave(
    plot = mtbi_manhattan_der_and_pool,
    filename = fig_path("mtbi_manhattan_der_and_pool.png", TRUE),
    width = 18,
    height = 8,
    dpi = 200
)
```

Checking to see if there are site effects:

```{r}
mtbi_site <- read_csv(input_path("2025_09_11_mtbi_site.csv"))
mtbi_site$"uid" <- paste0("uid_", mtbi_site$"subjectkey")
mtbi_top_pl_df <- auto_plot(
    mtbi_top_solution,
    dl = c(mtbi_dl_1, mtbi_ol_1),
    verbose = TRUE,
    return_plots = FALSE
) |> as.data.frame()
mtbi_top_pl_df_w_site <- dplyr::inner_join(
    mtbi_top_pl_df,
    mtbi_site,
    by = "uid"
)

mtbi_top_pl_df_w_site$"site_id" <- factor(mtbi_top_pl_df_w_site$"site_id")

# Demonstration that site is not a significant predictor of cluster membership
# using multinomial logistic regression of only 3 features
df <- mtbi_top_pl_df_w_site

covariates <- "sex + brain_volume + household_income"

formula_no_site <- as.formula(paste("cluster ~", covariates))
formula_with_site <- as.formula(paste("cluster ~", covariates, "+ site_id"))

mod_no_site <- multinom(formula_no_site, data = df)
mod_with_site <- multinom(formula_with_site, data = df)
anova(mod_no_site, mod_with_site, test = "Chisq") # N.S.
```

Concordance between the derivation and full samples:

```{r}
mtbi_der_df <- auto_plot(
    mtbi_der_solution,
    dl = c(der_dl_u5, der_ol_u5),
    return_plots = FALSE
)

mtbi_ful_df <- auto_plot(
    mtbi_top_solution,
    dl = c(mtbi_dl_1, mtbi_ol_1),
    return_plots = FALSE
)

mtbi_top_solution

val_cluster_df <- mtbi_top_solution |>
    t() |>
    dplyr::rename(
        "cluster" = "s117"
    ) |>
    dplyr::filter(
        uid %in% paste0("uid_", mtbi_ns_val_subs)
    )

mtbi_val_df <- auto_plot(
    cluster_df = val_cluster_df,
    dl = c(val_dl_u1, val_ol_u1),
    return_plots = FALSE
)

saveRDS(mtbi_val_df, proc_path("mtbi_val_df.rds", TRUE))
saveRDS(mtbi_der_df, proc_path("mtbi_der_df.rds", TRUE))
saveRDS(mtbi_ful_df, proc_path("mtbi_ful_df.rds", TRUE))

mtbi_val_df <- readRDS(proc_path("2025_09_16_mtbi_val_df.rds"))
mtbi_der_df <- readRDS(proc_path("2025_09_16_mtbi_der_df.rds"))
mtbi_ful_df <- readRDS(proc_path("2025_09_16_mtbi_ful_df.rds"))
```

```{r}
# Regular plot lists:
mtbi_der_df_pl <- auto_plot(
    mtbi_der_solution,
    dl = c(der_dl_u5, der_ol_u5)
)
mtbi_ful_df_pl <- auto_plot(
    mtbi_top_solution,
    dl = c(mtbi_dl_1, mtbi_ol_1)
)
mtbi_val_df_pl <- auto_plot(
    cluster_df = val_cluster_df,
    dl = c(val_dl_u1, val_ol_u1)
)

saveRDS(mtbi_der_df_pl, proc_path("mtbi_der_df_pl.rds", TRUE))
saveRDS(mtbi_val_df_pl, proc_path("mtbi_val_df_pl.rds", TRUE))
saveRDS(mtbi_ful_df_pl, proc_path("mtbi_ful_df_pl.rds", TRUE))

mtbi_der_df_pl <- readRDS(proc_path("2025_09_16_mtbi_der_df_pl.rds"))
mtbi_val_df_pl <- readRDS(proc_path("2025_09_16_mtbi_val_df_pl.rds"))
mtbi_ful_df_pl <- readRDS(proc_path("2025_09_16_mtbi_ful_df_pl.rds"))
```

```{r}
source("abcd/helper_functions.R")

mtbi_val_tops <- topologizer(mtbi_val_df)
mtbi_der_tops <- topologizer(mtbi_der_df)
mtbi_ful_tops <- topologizer(mtbi_ful_df)

write_csv(mtbi_der_tops, proc_path("mtbi_der_tops.csv", TRUE))
write_csv(mtbi_ful_tops, proc_path("mtbi_ful_tops.csv", TRUE))
write_csv(mtbi_val_tops, proc_path("mtbi_val_tops.csv", TRUE))

# CHECKPOINT
mtbi_der_tops <- read_csv(proc_path("2025_09_22_mtbi_der_tops.csv"))
mtbi_ful_tops <- read_csv(proc_path("2025_09_22_mtbi_ful_tops.csv"))
mtbi_val_tops <- read_csv(proc_path("2025_09_22_mtbi_val_tops.csv"))
```

```{r}
f_der_tops <- format_tops(mtbi_der_tops)
f_val_tops <- format_tops(mtbi_val_tops)
f_ful_tops <- format_tops(mtbi_ful_tops)

f_der_tops$"set" <- "D"
f_val_tops$"set" <- "V"
f_ful_tops$"set" <- "F"

all_tops <- do.call(rbind, list(f_der_tops2, f_val_tops2, f_ful_tops2)) |>
    dplyr::rename("feature" = "Feature")

mtbi_der_top_solution_nmi_v_pval_rank <- read_csv(
    proc_path("2025_09_15_mtbi_der_top_solution_nmi_v_pval_rank.csv")
)

print(mtbi_der_top_solution_nmi_v_pval_rank, n = Inf)

# Constructing a data frame of feature ranks that accounts for how
# mechanism and race were dummied
nmi_ranks <- mtbi_der_top_solution_nmi_v_pval_rank |>
    data.frame() |>
    dplyr::select(feature, nmi_rank)
nmi_ranks <- rbind(
    nmi_ranks,
    data.frame(
        feature = c("race_black", "race_white", "race_hispanic", "race_other"),
        nmi_rank = nmi_ranks[nmi_ranks$"feature" == "race", "nmi_rank"]
    )
)
nmi_ranks <- rbind(
    nmi_ranks,
    data.frame(
        feature = c(
            "mtbi_mechanism_fall_hit",
            "mtbi_mechanism_hosp_er",
            "mtbi_mechanism_multi",
            "mtbi_mechanism_other_loc",
            "mtbi_mechanism_vehicle",
            "mtbi_mechanism_violent"
        ),
        nmi_rank = nmi_ranks[nmi_ranks$"feature" == "mtbi_mechanism", "nmi_rank"]
    )
)
nmi_ranks <- dplyr::filter(nmi_ranks, !feature %in% c("mtbi_mechanism", "race"))
nmi_ranks <- arrange(nmi_ranks, nmi_rank)
nmi_ranks <- rbind(
    data.frame(feature = ofts, nmi_rank = nrow(nmi_ranks) + 1),
    nmi_ranks
) |> data.frame()
nmi_ranks
write_csv(nmi_ranks, proc_path("nmi_ranks.csv", TRUE))

nmi_ranks <- read_csv(proc_path("2025_09_22_nmi_ranks.csv"))

sorted_tops <- dplyr::full_join(all_tops, nmi_ranks) |>
    dplyr::mutate(set = factor(set, levels = c("D", "V", "F"))) |>
    dplyr::arrange(nmi_rank, feature, set)

write_csv(sorted_tops, proc_path("sorted_tops.csv", TRUE))

sorted_tops <- read_csv(proc_path("2025_09_22_sorted_tops.csv"))

knitr::kable(
    sorted_tops,
    format = "markdown",
    digits = 3, format.args = list(scientific = FALSE)
) |>
    writeLines(proc_path("mtbi_sorted_tops.txt", TRUE)) # 2025-09-22

sorted_tops |>
    dplyr::select(feature, set, Summary, ES, "C1 vs. C2", "C1 vs. C3", "C2 vs. C3") |>
    dplyr::rename("Feature" = "feature", "Set" = "set") |>
    dplyr::mutate(
        `C1 vs. C2` = gsub("textbf\\{", "*", `C1 vs. C2`),
        `C1 vs. C3` = gsub("textbf\\{", "*", `C1 vs. C3`),
        `C2 vs. C3` = gsub("textbf\\{", "*", `C2 vs. C3`)
    ) |>
    dplyr::mutate(
        `C1 vs. C2` = gsub("}", "*", `C1 vs. C2`),
        `C1 vs. C3` = gsub("}", "*", `C1 vs. C3`),
        `C2 vs. C3` = gsub("}", "*", `C2 vs. C3`),
        ES = toupper(ES)
    ) |>
    knitr::kable(
        format = "markdown",
        digits = 3, format.args = list(scientific = FALSE)
    ) |>
    writeLines(proc_path("mtbi_sorted_tops_clean.txt", TRUE)) # 2025-10-01

mtbi_der_tops$"set" <- "D"
mtbi_val_tops$"set" <- "V"
mtbi_ful_tops$"set" <- "F"

all_tops_raw <- do.call(
    rbind,
    list(mtbi_der_tops, mtbi_ful_tops, mtbi_val_tops)
)

all_der_tops_raw <- dplyr::full_join(
    nmi_ranks,
    mtbi_der_tops,
    by = "feature"
)
all_val_tops_raw <- dplyr::full_join(
    nmi_ranks,
    mtbi_val_tops,
    by = "feature"
)
all_ful_tops_raw <- dplyr::full_join(
    nmi_ranks,
    mtbi_ful_tops,
    by = "feature"
)
all_tops_raw <- do.call(
    rbind,
    list(all_der_tops_raw, all_val_tops_raw, all_ful_tops_raw)
) |>
    dplyr::mutate(set = factor(set, levels = c("D", "V", "F"))) |>
    dplyr::arrange(nmi_rank, feature, set)
```

Here, I manually adjust those with 0 ES.
The confidence intervals are left at NA.

```{r}
all_tops_raw_manual_adj <- all_tops_raw
#all_tops_raw_manual_adj$"row" <- rownames(all_tops_raw_manual_adj)
## Similar situation for mtbi mechanism multi
#all_tops_raw_manual_adj[196, "c12_es"] <- 0
#all_tops_raw_manual_adj[197, "c13_es"] <- 0
## Missing "V" set label
#all_tops_raw_manual_adj[201, "set"] <- "V"
# mtbi mechanism other loc simply not present in V
all_tops_raw_manual_adj[180, c("c12_es", "c13_es", "c23_es")] <- 1
all_tops_raw_manual_adj[180, "es"] <- "or"
## summary missing for all empty cell other loc 
#all_tops_raw_manual_adj[201, "summary"] <- "1 = 2 = 3"
## mtbi mechanism violent
#all_tops_raw_manual_adj[206, "c23_es"] <- 0
all_tops_raw_manual_adj |>
    #dplyr::select(-dplyr::contains("_l"), -dplyr::contains("_u")) |>
    dplyr::filter(dplyr::if_any(dplyr::everything(), is.na))

```

```{r}
saveRDS(all_tops_raw_manual_adj, proc_path("all_tops_raw_manual_adj.rds", TRUE))
```

```{r}
all_tops_raw_manual_adj <- readRDS(proc_path("2025_09_22_all_tops_raw_manual_adj.rds"))

all_tops_raw_manual_adj |> head()

all_tops_raw_manual_adj |>
    format_tops2() |>
    dplyr::mutate(
        ES = toupper(ES)
    ) |>
    knitr::kable(
        format = "markdown",
        digits = 3, format.args = list(scientific = FALSE)
    ) |>
    writeLines(proc_path("mtbi_sorted_adj_tops_clean.txt", TRUE)) # 2025-09-22

mtbi_gen_fts_table <- generalizable_features(all_tops_raw_manual_adj, compare_fn_a, 0.2)
saveRDS(mtbi_gen_fts_table, proc_path("mtbi_gen_fts_table.rds", TRUE))

```

```{r}
mtbi_gen_fts_table <- readRDS(proc_path("2025_09_22_mtbi_gen_fts_table.rds"))

mtbi_gen_fts_table |>
    dplyr::mutate(
        c1v2 = dplyr::case_when(is.na(c1v2) ~ "n.g.", c1v2 == "=" ~ "n.g.", c1v2 == "<" ~ "$lt$", c1v2 == ">" ~ "$gt$", TRUE ~ c1v2),
        c1v3 = dplyr::case_when(is.na(c1v3) ~ "n.g.", c1v3 == "=" ~ "n.g.", c1v3 == "<" ~ "$lt$", c1v3 == ">" ~ "$gt$", TRUE ~ c1v3),
        c2v3 = dplyr::case_when(is.na(c2v3) ~ "n.g.", c2v3 == "=" ~ "n.g.", c2v3 == "<" ~ "$lt$", c2v3 == ">" ~ "$gt$", TRUE ~ c2v3)
    ) |>
    dplyr::rename(
        "Feature" = "feature",
        "C1v2" = "c1v2",
        "C1v3" = "c1v3",
        "C2v3" = "c2v3"
    ) |>
    knitr::kable(
        format = "markdown",
        digits = 3, format.args = list(scientific = FALSE)
    ) |>
    writeLines(proc_path("mtbi_gen_fts_table.txt", TRUE)) # 2025-09-22

```

```{r}
mtbi_der_df_pl <- readRDS(proc_path("2025_09_16_mtbi_der_df_pl.rds"))
mtbi_val_df_pl <- readRDS(proc_path("2025_09_16_mtbi_val_df_pl.rds"))
mtbi_ful_df_pl <- readRDS(proc_path("2025_09_16_mtbi_ful_df_pl.rds"))

dvf_plots <- list(
    mtbi_der_df_pl[afts],
    mtbi_val_df_pl[afts],
    mtbi_ful_df_pl[afts]
)
```

```{r}
# image export helper function
quick_save <- function(plot, path, w = 12, h = 4, dpi = 300) {
    path <- paste0("mtbi_dvf_", path, ".png")
    ggsave(
        fig_path(path, TRUE),
        plot,
        width = w,
        height = h,
        dpi = dpi,
        limitsize = FALSE
    )
}
```

```{r}
# Not necessarily in ranked order:
activities_last_year_plot   <- tri_plot(dvf_plots, "activities_last_year",   "Programs Last\nYear (Quartile)")#; activities_last_year_plot; Sys.sleep(1)
age_plot                    <- tri_plot(dvf_plots, "age",                    "Age") #; age_plot; Sys.sleep(1)
brain_volume_plot           <- tri_plot(dvf_plots, "brain_volume",           "Brain Volume\n(mm³)", ylims = c(900000, 1650000)) #; brain_volume_plot; Sys.sleep(1)
considerate_p_plot          <- tri_plot(dvf_plots, "considerate_p",          "Considerate\n(Parent Report)", c("No", "Yes")) #; considerate_p_plot ; Sys.sleep(1)
considerate_y_plot          <- tri_plot(dvf_plots, "considerate_y",          "Considerate\n(Youth Report)", c("No", "Yes")) #; considerate_y_plot ; Sys.sleep(1)
cort_sa_plot                <- tri_plot(dvf_plots, "cortical_sa",            "Cortical Surface\nArea (mm²)", ylims = c(140000, 250000)) #; cort_sa_plot ; Sys.sleep(1)
cortical_t_plot             <- tri_plot(dvf_plots, "cortical_t",             "Cortical\nThickness (mm)", ylims = c(2.35, 3.05)) #; cortical_t_plot ; Sys.sleep(1)
extracurriculars_plot       <- tri_plot(dvf_plots, "extracurriculars",       "Extracurriculars\n(Quartile)") #; extracurriculars_plot ; Sys.sleep(1)
family_angry_p_plot         <- tri_plot(dvf_plots, "family_angry_p",         "Family Angry\n(Parent Report)", c("No", "Yes")) #; family_angry_p_plot ; Sys.sleep(1)
family_angry_y_plot         <- tri_plot(dvf_plots, "family_angry_y",         "Family Angry\n(Youth Report)", c("No", "Yes")) #; family_angry_y_plot ; Sys.sleep(1)
family_criticize_p_plot     <- tri_plot(dvf_plots, "family_criticize_p",     "Family Criticizes\n(Parent Report)", c("No", "Yes")) #; family_criticize_p_plot ; Sys.sleep(1)
family_criticize_y_plot     <- tri_plot(dvf_plots, "family_criticize_y",     "Family Criticizes\n(Youth Report)", c("No", "Yes")) #; family_criticize_y_plot ; Sys.sleep(1)
family_fight_p_plot         <- tri_plot(dvf_plots, "family_fight_p",         "Family Fights\n(Parent Report)", scale_fill_labels = c("No", "Yes")) #; family_fight_p_plot ; Sys.sleep(1)
family_fight_y_plot         <- tri_plot(dvf_plots, "family_fight_y",         "Family Fights\n(Youth Report)", c("No", "Yes")) #; family_fight_y_plot ; Sys.sleep(1)
family_hit_p_plot           <- tri_plot(dvf_plots, "family_hit_p",           "Family Hitting\n(Parent Report)", c("No", "Yes")) #; family_hit_p_plot ; Sys.sleep(1)
family_hit_y_plot           <- tri_plot(dvf_plots, "family_hit_y",           "Family Hitting\n(Youth Report)", c("No", "Yes")) #; family_hit_y_plot ; Sys.sleep(1)
family_outdo_p_plot         <- tri_plot(dvf_plots, "family_outdo_p",         "Family Outdo\n(Parent Report)", c("No", "Yes")) #; family_outdo_p_plot ; Sys.sleep(1)
family_outdo_y_plot         <- tri_plot(dvf_plots, "family_outdo_y",         "Family Outdoing\n(Youth Report)", c("No", "Yes")) #; family_outdo_y_plot ; Sys.sleep(1)
family_peaceful_p_plot      <- tri_plot(dvf_plots, "family_peaceful_p",      "Family Not Peaceful\n(Parent Report)", c("No", "Yes")) #; family_peaceful_p_plot ; Sys.sleep(1)
family_peaceful_y_plot      <- tri_plot(dvf_plots, "family_peaceful_y",      "Family Not Peaceful\n(Youth Report)", c("No", "Yes")) #; family_peaceful_y_plot ; Sys.sleep(1)
family_temper_p_plot        <- tri_plot(dvf_plots, "family_temper_p",        "Family Temper\n(Parent Report)", scale_fill_labels = c("No", "Yes")) #; family_temper_p_plot ; Sys.sleep(1)
family_temper_y_plot        <- tri_plot(dvf_plots, "family_temper_y",        "Family Temper\n(Youth Report)", c("No", "Yes")) #; family_temper_y_plot ; Sys.sleep(1)
family_throw_p_plot         <- tri_plot(dvf_plots, "family_throw_p",         "Family Throwing\n(Parent Report)", c("No", "Yes")) #; family_throw_p_plot ; Sys.sleep(1)
family_throw_y_plot         <- tri_plot(dvf_plots, "family_throw_y",         "Family Throwing\n(Youth Report)", c("No", "Yes")) #; family_throw_y_plot ; Sys.sleep(1)
family_yell_p_plot          <- tri_plot(dvf_plots, "family_yell_p",          "Family Yells\n(Parent Report)", c("No", "Yes")) #; family_yell_p_plot ; Sys.sleep(1)
family_yell_y_plot          <- tri_plot(dvf_plots, "family_yell_y",          "Family Yells\n(Youth Report)", c("No", "Yes")) #; family_yell_y_plot ; Sys.sleep(1)
fmri_dan_within_cor_plot    <- tri_plot(dvf_plots, "fmri_dan_within_cor",    "fMRI DAN Corrs", ylims = c(0, 0.6)) #; fmri_dan_within_cor_plot; Sys.sleep(1)
fmri_dmn_fpn_cor_plot       <- tri_plot(dvf_plots, "fmri_dmn_fpn_cor",       "fMRI DAN-FPN\nCorrs", ylims = c(-0.2, 0.3)) #; fmri_dmn_fpn_cor_plot; Sys.sleep(1)
fmri_dmn_within_cor_plot    <- tri_plot(dvf_plots, "fmri_dmn_within_cor",    "fMRI DMN Corrs", ylims = c(0, 0.5)) #; fmri_dmn_within_cor_plot; Sys.sleep(1)
fmri_fpn_lamyg_cor_plot     <- tri_plot(dvf_plots, "fmri_fpn_lamyg_cor",     "fMRI FPN-lAmyg\nCorrs", ylims = c(-0.2, 0.35)) #; fmri_fpn_lamyg_cor_plot; Sys.sleep(1)
fmri_fpn_ramyg_cor_plot     <- tri_plot(dvf_plots, "fmri_fpn_ramyg_cor",     "fMRI FPN-rAmyg\nCorrs", ylims = c(-0.35, 0.4)) #; fmri_fpn_ramyg_cor_plot; Sys.sleep(1)
fmri_fpn_within_cor_plot    <- tri_plot(dvf_plots, "fmri_fpn_within_cor",    "fMRI FPN Corrs", ylims = c(0, 0.5)) #; fmri_fpn_within_cor_plot; Sys.sleep(1)
fmri_san_within_cor_plot    <- tri_plot(dvf_plots, "fmri_san_within_cor",    "fMRI SAN Corrs", ylims = c(0, 0.8)) #; fmri_san_within_cor_plot; Sys.sleep(1)
headache_history_plot       <- tri_plot(dvf_plots, "headache_history",       "Headache\nHistory", c("No", "Yes")) #; headache_history_plot ; Sys.sleep(1)
helpful_p_plot              <- tri_plot(dvf_plots, "helpful_p",              "Helpful\n(Parent Report)", c("No", "Yes")) #; helpful_p_plot ; Sys.sleep(1)
helpful_y_plot              <- tri_plot(dvf_plots, "helpful_y",              "Helpful\n(Youth Report)", c("No", "Yes")) #; helpful_y_plot ; Sys.sleep(1)
helps_hurt_p_plot           <- tri_plot(dvf_plots, "helps_hurt_p",           "Helps Hurt\n(Parent Report)", c("No", "Yes")) #; helps_hurt_p_plot ; Sys.sleep(1)
helps_hurt_y_plot           <- tri_plot(dvf_plots, "helps_hurt_y",           "Helps Hurt\n(Youth Report)", c("No", "Yes")) #; helps_hurt_y_plot ; Sys.sleep(1)
household_income_plot       <- tri_plot(dvf_plots, "household_income",       "Household\nIncome") #; household_income_plot ; Sys.sleep(1)
major_wm_ndi_plot           <- tri_plot(dvf_plots, "major_wm_ndi",           "Major WM\nNeurite Density", ylims = c(0.45, 0.85)) #; major_wm_ndi_plot ; Sys.sleep(1)
mtbi_age_plot               <- tri_plot(dvf_plots, "mtbi_age",               "mTBI Age\n(months)") #; mtbi_age_plot ; Sys.sleep(1)
mtbi_loc_plot               <- tri_plot(dvf_plots, "mtbi_loc",               "mTBI LOC", c("No", "Yes")) #; mtbi_loc_plot ; Sys.sleep(1)
mtbi_mechanism_plot         <- tri_plot(dvf_plots, "mtbi_mechanism",         "mTBI Mechanism", c("Fall/Hit", "Hospital/ER", "Multiple Injuries", "Other", "Vehicle", "Violent")) #; mtbi_mechanism_plot ; Sys.sleep(1)
mtbi_mem_daze_plot          <- tri_plot(dvf_plots, "mtbi_mem_daze",          "mTBI mem_daze", c("No", "Yes")) #; mtbi_mem_daze_plot ; Sys.sleep(1)
opp_sex_close_friend_plot   <- tri_plot(dvf_plots, "opp_sex_close_friend",   "Opposite-Sex\nClose Friends (Quartile)") #; opp_sex_close_friend_plot ; Sys.sleep(1)
opp_sex_friend_plot         <- tri_plot(dvf_plots, "opp_sex_friend",         "Opposite-Sex\nFriends (Quartile)") #; opp_sex_friend_plot ; Sys.sleep(1)
parent_aggressive_plot      <- tri_plot(dvf_plots, "parent_aggressive",      "Parent\nAggressive", ylims = c(-0.5, 25)) #; parent_aggressive_plot ; Sys.sleep(1)
parent_antisocial_plot      <- tri_plot(dvf_plots, "parent_antisocial",      "Parent\nAntisocial", ylims = c(-0.5, 20)) #; parent_antisocial_plot ; Sys.sleep(1)
parent_anxdep_plot          <- tri_plot(dvf_plots, "parent_anxdep",          "Parent\nAnxious-Depressed", ylims = c(-0.5, 30)) #; parent_anxdep_plot ; Sys.sleep(1)
parent_anxdisord_plot       <- tri_plot(dvf_plots, "parent_anxdisord",       "Parent\nAnxious", ylims = c(-0.5, 13)) #; parent_anxdisord_plot ; Sys.sleep(1)
parent_attention_plot       <- tri_plot(dvf_plots, "parent_attention",       "Parent Attention", ylims = c(-0.5, 25)) #; parent_attention_plot ; Sys.sleep(1)
parent_avoidant_plot        <- tri_plot(dvf_plots, "parent_avoidant",        "Parent\nAvoidant", ylims = c(-0.5, 13)) #; parent_avoidant_plot ; Sys.sleep(1)
parent_depress_plot         <- tri_plot(dvf_plots, "parent_depress",         "Parent\nDepress", ylims = c(-0.5, 25)) #; parent_depress_plot ; Sys.sleep(1)
parent_hyperactive_plot     <- tri_plot(dvf_plots, "parent_hyperactive",     "Parent\nHyperactive", ylims = c(-0.5, 12)) #; parent_hyperactive_plot ; Sys.sleep(1)
parent_intrusive_plot       <- tri_plot(dvf_plots, "parent_intrusive",       "Parent Intrusive", ylims = c(-0.5, 12)) #; parent_intrusive_plot ; Sys.sleep(1)
parent_perstr_plot          <- tri_plot(dvf_plots, "parent_perstr",          "Parent\nPersonal Strength") #; parent_perstr_plot ; Sys.sleep(1)
parent_somatic_plot         <- tri_plot(dvf_plots, "parent_somatic",         "Parent\nSomatic", ylims = c(-0.5, 25)) #; parent_somatic_plot ; Sys.sleep(1)
parent_thought_plot         <- tri_plot(dvf_plots, "parent_thought",         "Parent\nThought", ylims = c(-0.5, 13.5)) #; parent_thought_plot ; Sys.sleep(1)
parent_withdrawn_plot       <- tri_plot(dvf_plots, "parent_withdrawn",       "Parent\nWithdrawn", ylims = c(-0.5, 17)) #; parent_withdrawn_plot ; Sys.sleep(1)
pericortical_wm_ndi_plot    <- tri_plot(dvf_plots, "pericortical_wm_ndi",    "Pericortical WM\nNeurite Density", ylims = c(0.25, 0.6)) #; pericortical_wm_ndi_plot ; Sys.sleep(1)
physical_activity_plot      <- tri_plot(dvf_plots, "physical_activity",      "Physical Activity", ylims = c(0, 1.1)) #; physical_activity_plot ; Sys.sleep(1)
previous_mtbis_plot         <- tri_plot(dvf_plots, "previous_mtbis",         "Previous mTBIs") #; previous_mtbis_plot ; Sys.sleep(1)
private_instruction_plot    <- tri_plot(dvf_plots, "private_instruction",    "Private Activities\n(Quartile)") #; private_instruction_plot ; Sys.sleep(1)
pubertal_status_p_plot      <- tri_plot(dvf_plots, "pubertal_status_p",      "Pubertal Status\n(Parent Report)") #; pubertal_status_p_plot ; Sys.sleep(1)
pubertal_status_y_plot      <- tri_plot(dvf_plots, "pubertal_status_y",      "Pubertal Status\n(Youth Report)") #; pubertal_status_y_plot ; Sys.sleep(1)
race_plot                   <- tri_plot(dvf_plots, "race",                   "Race", scale_fill_labels = c("Black", "Hispanic", "Other", "White")) #; race_plot ; Sys.sleep(1)
same_sex_close_friend_plot  <- tri_plot(dvf_plots, "same_sex_close_friend",  "Same-Sex Close\nFriends (Quartile)") #; same_sex_close_friend_plot ; Sys.sleep(1)
same_sex_friend_plot        <- tri_plot(dvf_plots, "same_sex_friend",        "Same-Sex Friends\n(Quartile)") #; same_sex_friend_plot ; Sys.sleep(1)
school_activities_plot      <- tri_plot(dvf_plots, "school_activities",      "School Activities") #; school_activities_plot ; Sys.sleep(1)
sex_plot                    <- tri_plot(dvf_plots, "sex",                    "Sex", c("F", "M")) #; sex_plot ; Sys.sleep(1)
weekday_screentime_plot     <- tri_plot(dvf_plots, "weekday_screentime",     "Weekday\nScreentime (hours)", ylims = c(-0.5, 21)) #; weekday_screentime_plot ; Sys.sleep(1)
weekend_screentime_plot     <- tri_plot(dvf_plots, "weekend_screentime",     "Weekend\nScreentime (hours)", ylims = c(-0.5, 21)) #; weekend_screentime_plot ; Sys.sleep(1)
# Outcome trip-plots#; # ; Sys.sleep(1)
cbcl_anxdep_plot            <- tri_plot(dvf_plots, "cbcl_anxdep",            "Anxious-\nDepressed", ylims = c(-0.5, 30))#; cbcl_anxdep_plot ; Sys.sleep(1)
cbcl_withdep_plot           <- tri_plot(dvf_plots, "cbcl_withdep",           "Withdrawn-\nDepressed", ylims = c(-0.5, 15))#; cbcl_withdep_plot ; Sys.sleep(1)
cbcl_somatic_plot           <- tri_plot(dvf_plots, "cbcl_somatic",           "Somatic", ylims = c(-0.5, 17))#; cbcl_somatic_plot ; Sys.sleep(1)
cbcl_social_plot            <- tri_plot(dvf_plots, "cbcl_social",            "Social", ylims = c(-0.5, 20))#; cbcl_social_plot ; Sys.sleep(1)
cbcl_thought_plot           <- tri_plot(dvf_plots, "cbcl_thought",           "Thought", ylims = c(-0.5, 20))#; cbcl_thought_plot ; Sys.sleep(1)
cbcl_attention_plot         <- tri_plot(dvf_plots, "cbcl_attention",         "Attention", ylims = c(-0.5, 22))#; cbcl_attention_plot ; Sys.sleep(1)
cbcl_rulebreak_plot         <- tri_plot(dvf_plots, "cbcl_rulebreak",         "Rule-Breaking", ylims = c(-0.5, 22))#; cbcl_rulebreak_plot ; Sys.sleep(1)
cbcl_aggressive_plot        <- tri_plot(dvf_plots, "cbcl_aggressive",        "Aggression", ylims = c(-0.5, 32))#; cbcl_aggressive_plot ; Sys.sleep(1)
sds_sleep_plot              <- tri_plot(dvf_plots, "sds_sleep",              "Total Sleep\nProblems", ylims = c(20, 100))#; sds_sleep_plot ; Sys.sleep(1)

generalizing_plots <- list(
    "activities_last_year"   = activities_last_year_plot,
    "age"                    = age_plot,
    "brain_volume"           = brain_volume_plot,
    "cbcl_aggressive"        = cbcl_aggressive_plot,
    "cbcl_anxdep"            = cbcl_anxdep_plot,
    "cbcl_attention"         = cbcl_attention_plot,
    "cbcl_rulebreak"         = cbcl_rulebreak_plot,
    "cbcl_social"            = cbcl_social_plot,
    "cbcl_somatic"           = cbcl_somatic_plot,
    "cbcl_thought"           = cbcl_thought_plot,
    "cbcl_withdep"           = cbcl_withdep_plot,
    "considerate_p"          = considerate_p_plot,
    "considerate_y"          = considerate_y_plot,
    "cortical_sa"            = cort_sa_plot,
    "cortical_t"             = cortical_t_plot,
    "extracurriculars"       = extracurriculars_plot,
    "family_angry_p"         = family_angry_p_plot,
    "family_angry_y"         = family_angry_y_plot,
    "family_criticize_p"     = family_criticize_p_plot,
    "family_criticize_y"     = family_criticize_y_plot,
    "family_fight_p"         = family_fight_p_plot,
    "family_fight_y"         = family_fight_y_plot,
    "family_hit_p"           = family_hit_p_plot,
    "family_hit_y"           = family_hit_y_plot,
    "family_outdo_p"         = family_outdo_p_plot,
    "family_outdo_y"         = family_outdo_y_plot,
    "family_peaceful_p"      = family_peaceful_p_plot,
    "family_peaceful_y"      = family_peaceful_y_plot,
    "family_temper_p"        = family_temper_p_plot,
    "family_temper_y"        = family_temper_y_plot,
    "family_throw_p"         = family_throw_p_plot,
    "family_throw_y"         = family_throw_y_plot,
    "family_yell_p"          = family_yell_p_plot,
    "family_yell_y"          = family_yell_y_plot,
    "fmri_dan_within_cor"    = fmri_dan_within_cor_plot,
    "fmri_dmn_fpn_cor"       = fmri_dmn_fpn_cor_plot,
    "fmri_dmn_within_cor"    = fmri_dmn_within_cor_plot,
    "fmri_fpn_lamyg_cor"     = fmri_fpn_lamyg_cor_plot,
    "fmri_fpn_ramyg_cor"     = fmri_fpn_ramyg_cor_plot,
    "fmri_fpn_within_cor"    = fmri_fpn_within_cor_plot,
    "fmri_san_within_cor"    = fmri_san_within_cor_plot,
    "headache_history"       = headache_history_plot,
    "helpful_p"              = helpful_p_plot,
    "helpful_y"              = helpful_y_plot,
    "helps_hurt_p"           = helps_hurt_p_plot,
    "helps_hurt_y"           = helps_hurt_y_plot,
    "household_income"       = household_income_plot,
    "major_wm_ndi"           = major_wm_ndi_plot,
    "mtbi_age"               = mtbi_age_plot,
    "mtbi_loc"               = mtbi_loc_plot,
    "mtbi_mechanism"         = mtbi_mechanism_plot,
    "mtbi_mem_daze"          = mtbi_mem_daze_plot,
    "opp_sex_close_friend"   = opp_sex_close_friend_plot,
    "opp_sex_friend"         = opp_sex_friend_plot,
    "parent_aggressive"      = parent_aggressive_plot,
    "parent_antisocial"      = parent_antisocial_plot,
    "parent_anxdep"          = parent_anxdep_plot,
    "parent_anxdisord"       = parent_anxdisord_plot,
    "parent_attention"       = parent_attention_plot,
    "parent_avoidant"        = parent_avoidant_plot,
    "parent_depress"         = parent_depress_plot,
    "parent_hyperactive"     = parent_hyperactive_plot,
    "parent_intrusive"       = parent_intrusive_plot,
    "parent_perstr"          = parent_perstr_plot,
    "parent_somatic"         = parent_somatic_plot,
    "parent_thought"         = parent_thought_plot,
    "parent_withdrawn"       = parent_withdrawn_plot,
    "pericortical_wm_ndi"    = pericortical_wm_ndi_plot,
    "physical_activity"      = physical_activity_plot,
    "previous_mtbis"         = previous_mtbis_plot,
    "private_instruction"    = private_instruction_plot,
    "pubertal_status_p"      = pubertal_status_p_plot,
    "pubertal_status_y"      = pubertal_status_y_plot,
    "race"                   = race_plot,
    "same_sex_close_friend"  = same_sex_close_friend_plot,
    "same_sex_friend"        = same_sex_friend_plot,
    "school_activities"      = school_activities_plot,
    "sds_sleep"              = sds_sleep_plot,
    "sex"                    = sex_plot,
    "weekday_screentime"     = weekday_screentime_plot,
    "weekend_screentime"     = weekend_screentime_plot
) |> lapply(
    function(x) {
        theme_comps <- theme(
            axis.title.x = element_blank(),
            legend.title = element_text(size = 14),
            legend.text = element_text(size = 14)
        )
        x[[1]] <- x[[1]] + theme_comps
        x[[2]] <- x[[2]] + theme_comps
        x[[3]] <- x[[3]] + theme_comps
        return(x)
    }
)

iplots <- generalizing_plots[ifts]
oplots <- generalizing_plots[ofts]
#

saveRDS(iplots, proc_path("mtbi_iplots.rds", TRUE))
saveRDS(oplots, proc_path("mtbi_oplots.rds", TRUE))

iplots <- readRDS(proc_path("2025_09_30_mtbi_iplots.rds"))
oplots <- readRDS(proc_path("2025_09_30_mtbi_oplots.rds"))

iplots[[1]]


wp_1 <- wrap_plots(iplots[1:9], ncol = 1)
quick_save(wp_1, "wp_1", w = 7.5, h = 20, dpi = 100)
wp_2 <- wrap_plots(iplots[10:18], ncol = 1)
quick_save(wp_2, "wp_2", w = 5.5, h = 20, dpi = 100)
wp_3 <- wrap_plots(iplots[19:27], ncol = 1)
quick_save(wp_3, "wp_3", w = 7.5, h = 20, dpi = 100)
wp_4 <- wrap_plots(iplots[28:36], ncol = 1)
quick_save(wp_4, "wp_4", w = 7.5, h = 20, dpi = 100)
wp_5 <- wrap_plots(iplots[37:45], ncol = 1)
quick_save(wp_5, "wp_5", w = 7.5, h = 20, dpi = 100)
wp_6 <- wrap_plots(iplots[46:54], ncol = 1)
quick_save(wp_6, "wp_6", w = 7.5, h = 20, dpi = 100)
wp_7 <- wrap_plots(iplots[55:63], ncol = 1)
quick_save(wp_7, "wp_7", w = 7.5, h = 20, dpi = 100)
wp_8 <- wrap_plots(iplots[64:72], ncol = 1)
quick_save(wp_8, "wp_8", w = 7.5, h = 20, dpi = 100)
wp_o <- wrap_plots(oplots, ncol = 1)
quick_save(wp_o, "wp_o", w = 5.5, h = 20, dpi = 100)
```


Variation with only the full plots:

```{r}

# Not necessarily in ranked order:
activities_last_year_uniplot   <- uni_plot(dvf_plots, "activities_last_year",   "Programs Last\nYear (Quartile)")#; activities_last_year_plot; Sys.sleep(1)
age_uniplot                    <- uni_plot(dvf_plots, "age",                    "Age") #; age_plot; Sys.sleep(1)
brain_volume_uniplot           <- uni_plot(dvf_plots, "brain_volume",           "Brain Volume\n(mm³)", ylims = c(900000, 1650000)) #; brain_volume_plot; Sys.sleep(1)
considerate_p_uniplot          <- uni_plot(dvf_plots, "considerate_p",          "Considerate\n(Parent Report)", c("No", "Yes")) #; considerate_p_plot ; Sys.sleep(1)
considerate_y_uniplot          <- uni_plot(dvf_plots, "considerate_y",          "Considerate\n(Youth Report)", c("No", "Yes")) #; considerate_y_plot ; Sys.sleep(1)
cort_sa_uniplot                <- uni_plot(dvf_plots, "cortical_sa",            "Cortical Surface\nArea (mm²)", ylims = c(140000, 250000)) #; cort_sa_plot ; Sys.sleep(1)
cortical_t_uniplot             <- uni_plot(dvf_plots, "cortical_t",             "Cortical\nThickness (mm)", ylims = c(2.35, 3.05)) #; cortical_t_plot ; Sys.sleep(1)
extracurriculars_uniplot       <- uni_plot(dvf_plots, "extracurriculars",       "Extracurriculars\n(Quartile)") #; extracurriculars_plot ; Sys.sleep(1)
family_angry_p_uniplot         <- uni_plot(dvf_plots, "family_angry_p",         "Family Angry\n(Parent Report)", c("No", "Yes")) #; family_angry_p_plot ; Sys.sleep(1)
family_angry_y_uniplot         <- uni_plot(dvf_plots, "family_angry_y",         "Family Angry\n(Youth Report)", c("No", "Yes")) #; family_angry_y_plot ; Sys.sleep(1)
family_criticize_p_uniplot     <- uni_plot(dvf_plots, "family_criticize_p",     "Family Criticizes\n(Parent Report)", c("No", "Yes")) #; family_criticize_p_plot ; Sys.sleep(1)
family_criticize_y_uniplot     <- uni_plot(dvf_plots, "family_criticize_y",     "Family Criticizes\n(Youth Report)", c("No", "Yes")) #; family_criticize_y_plot ; Sys.sleep(1)
family_fight_p_uniplot         <- uni_plot(dvf_plots, "family_fight_p",         "Family Fights\n(Parent Report)", scale_fill_labels = c("No", "Yes")) #; family_fight_p_plot ; Sys.sleep(1)
family_fight_y_uniplot         <- uni_plot(dvf_plots, "family_fight_y",         "Family Fights\n(Youth Report)", c("No", "Yes")) #; family_fight_y_plot ; Sys.sleep(1)
family_hit_p_uniplot           <- uni_plot(dvf_plots, "family_hit_p",           "Family Hitting\n(Parent Report)", c("No", "Yes")) #; family_hit_p_plot ; Sys.sleep(1)
family_hit_y_uniplot           <- uni_plot(dvf_plots, "family_hit_y",           "Family Hitting\n(Youth Report)", c("No", "Yes")) #; family_hit_y_plot ; Sys.sleep(1)
family_outdo_p_uniplot         <- uni_plot(dvf_plots, "family_outdo_p",         "Family Outdo\n(Parent Report)", c("No", "Yes")) #; family_outdo_p_plot ; Sys.sleep(1)
family_outdo_y_uniplot         <- uni_plot(dvf_plots, "family_outdo_y",         "Family Outdoing\n(Youth Report)", c("No", "Yes")) #; family_outdo_y_plot ; Sys.sleep(1)
family_peaceful_p_uniplot      <- uni_plot(dvf_plots, "family_peaceful_p",      "Family Not Peaceful\n(Parent Report)", c("No", "Yes")) #; family_peaceful_p_plot ; Sys.sleep(1)
family_peaceful_y_uniplot      <- uni_plot(dvf_plots, "family_peaceful_y",      "Family Not Peaceful\n(Youth Report)", c("No", "Yes")) #; family_peaceful_y_plot ; Sys.sleep(1)
family_temper_p_uniplot        <- uni_plot(dvf_plots, "family_temper_p",        "Family Temper\n(Parent Report)", scale_fill_labels = c("No", "Yes")) #; family_temper_p_plot ; Sys.sleep(1)
family_temper_y_uniplot        <- uni_plot(dvf_plots, "family_temper_y",        "Family Temper\n(Youth Report)", c("No", "Yes")) #; family_temper_y_plot ; Sys.sleep(1)
family_throw_p_uniplot         <- uni_plot(dvf_plots, "family_throw_p",         "Family Throwing\n(Parent Report)", c("No", "Yes")) #; family_throw_p_plot ; Sys.sleep(1)
family_throw_y_uniplot         <- uni_plot(dvf_plots, "family_throw_y",         "Family Throwing\n(Youth Report)", c("No", "Yes")) #; family_throw_y_plot ; Sys.sleep(1)
family_yell_p_uniplot          <- uni_plot(dvf_plots, "family_yell_p",          "Family Yells\n(Parent Report)", c("No", "Yes")) #; family_yell_p_plot ; Sys.sleep(1)
family_yell_y_uniplot          <- uni_plot(dvf_plots, "family_yell_y",          "Family Yells\n(Youth Report)", c("No", "Yes")) #; family_yell_y_plot ; Sys.sleep(1)
fmri_dan_within_cor_uniplot    <- uni_plot(dvf_plots, "fmri_dan_within_cor",    "fMRI DAN Corrs", ylims = c(0, 0.6)) #; fmri_dan_within_cor_plot; Sys.sleep(1)
fmri_dmn_fpn_cor_uniplot       <- uni_plot(dvf_plots, "fmri_dmn_fpn_cor",       "fMRI DAN-FPN\nCorrs", ylims = c(-0.2, 0.3)) #; fmri_dmn_fpn_cor_plot; Sys.sleep(1)
fmri_dmn_within_cor_uniplot    <- uni_plot(dvf_plots, "fmri_dmn_within_cor",    "fMRI DMN Corrs", ylims = c(0, 0.5)) #; fmri_dmn_within_cor_plot; Sys.sleep(1)
fmri_fpn_lamyg_cor_uniplot     <- uni_plot(dvf_plots, "fmri_fpn_lamyg_cor",     "fMRI FPN-lAmyg\nCorrs", ylims = c(-0.2, 0.35)) #; fmri_fpn_lamyg_cor_plot; Sys.sleep(1)
fmri_fpn_ramyg_cor_uniplot     <- uni_plot(dvf_plots, "fmri_fpn_ramyg_cor",     "fMRI FPN-rAmyg\nCorrs", ylims = c(-0.35, 0.4)) #; fmri_fpn_ramyg_cor_plot; Sys.sleep(1)
fmri_fpn_within_cor_uniplot    <- uni_plot(dvf_plots, "fmri_fpn_within_cor",    "fMRI FPN Corrs", ylims = c(0, 0.5)) #; fmri_fpn_within_cor_plot; Sys.sleep(1)
fmri_san_within_cor_uniplot    <- uni_plot(dvf_plots, "fmri_san_within_cor",    "fMRI SAN Corrs", ylims = c(0, 0.8)) #; fmri_san_within_cor_plot; Sys.sleep(1)
headache_history_uniplot       <- uni_plot(dvf_plots, "headache_history",       "Headache\nHistory", c("No", "Yes")) #; headache_history_plot ; Sys.sleep(1)
helpful_p_uniplot              <- uni_plot(dvf_plots, "helpful_p",              "Helpful\n(Parent Report)", c("No", "Yes")) #; helpful_p_plot ; Sys.sleep(1)
helpful_y_uniplot              <- uni_plot(dvf_plots, "helpful_y",              "Helpful\n(Youth Report)", c("No", "Yes")) #; helpful_y_plot ; Sys.sleep(1)
helps_hurt_p_uniplot           <- uni_plot(dvf_plots, "helps_hurt_p",           "Helps Hurt\n(Parent Report)", c("No", "Yes")) #; helps_hurt_p_plot ; Sys.sleep(1)
helps_hurt_y_uniplot           <- uni_plot(dvf_plots, "helps_hurt_y",           "Helps Hurt\n(Youth Report)", c("No", "Yes")) #; helps_hurt_y_plot ; Sys.sleep(1)
household_income_uniplot       <- uni_plot(dvf_plots, "household_income",       "Household\nIncome") #; household_income_plot ; Sys.sleep(1)
major_wm_ndi_uniplot           <- uni_plot(dvf_plots, "major_wm_ndi",           "Major WM\nNeurite Density", ylims = c(0.45, 0.85)) #; major_wm_ndi_plot ; Sys.sleep(1)
mtbi_age_uniplot               <- uni_plot(dvf_plots, "mtbi_age",               "mTBI Age\n(months)") #; mtbi_age_plot ; Sys.sleep(1)
mtbi_loc_uniplot               <- uni_plot(dvf_plots, "mtbi_loc",               "mTBI LOC", c("No", "Yes")) #; mtbi_loc_plot ; Sys.sleep(1)
mtbi_mechanism_uniplot         <- uni_plot(dvf_plots, "mtbi_mechanism",         "mTBI Mechanism", c("Fall/Hit", "Hospital/ER", "Multiple Injuries", "Other", "Vehicle", "Violent")) #; mtbi_mechanism_plot ; Sys.sleep(1)
mtbi_mem_daze_uniplot          <- uni_plot(dvf_plots, "mtbi_mem_daze",          "mTBI mem_daze", c("No", "Yes")) #; mtbi_mem_daze_plot ; Sys.sleep(1)
opp_sex_close_friend_uniplot   <- uni_plot(dvf_plots, "opp_sex_close_friend",   "Opposite-Sex\nClose Friends (Quartile)") #; opp_sex_close_friend_plot ; Sys.sleep(1)
opp_sex_friend_uniplot         <- uni_plot(dvf_plots, "opp_sex_friend",         "Opposite-Sex\nFriends (Quartile)") #; opp_sex_friend_plot ; Sys.sleep(1)
parent_aggressive_uniplot      <- uni_plot(dvf_plots, "parent_aggressive",      "Parent\nAggressive", ylims = c(-0.5, 25)) #; parent_aggressive_plot ; Sys.sleep(1)
parent_antisocial_uniplot      <- uni_plot(dvf_plots, "parent_antisocial",      "Parent\nAntisocial", ylims = c(-0.5, 20)) #; parent_antisocial_plot ; Sys.sleep(1)
parent_anxdep_uniplot          <- uni_plot(dvf_plots, "parent_anxdep",          "Parent\nAnxious-Depressed", ylims = c(-0.5, 30)) #; parent_anxdep_plot ; Sys.sleep(1)
parent_anxdisord_uniplot       <- uni_plot(dvf_plots, "parent_anxdisord",       "Parent\nAnxious", ylims = c(-0.5, 13)) #; parent_anxdisord_plot ; Sys.sleep(1)
parent_attention_uniplot       <- uni_plot(dvf_plots, "parent_attention",       "Parent Attention", ylims = c(-0.5, 25)) #; parent_attention_plot ; Sys.sleep(1)
parent_avoidant_uniplot        <- uni_plot(dvf_plots, "parent_avoidant",        "Parent\nAvoidant", ylims = c(-0.5, 13)) #; parent_avoidant_plot ; Sys.sleep(1)
parent_depress_uniplot         <- uni_plot(dvf_plots, "parent_depress",         "Parent\nDepress", ylims = c(-0.5, 25)) #; parent_depress_plot ; Sys.sleep(1)
parent_hyperactive_uniplot     <- uni_plot(dvf_plots, "parent_hyperactive",     "Parent\nHyperactive", ylims = c(-0.5, 12)) #; parent_hyperactive_plot ; Sys.sleep(1)
parent_intrusive_uniplot       <- uni_plot(dvf_plots, "parent_intrusive",       "Parent Intrusive", ylims = c(-0.5, 12)) #; parent_intrusive_plot ; Sys.sleep(1)
parent_perstr_uniplot          <- uni_plot(dvf_plots, "parent_perstr",          "Parent\nPersonal Strength") #; parent_perstr_plot ; Sys.sleep(1)
parent_somatic_uniplot         <- uni_plot(dvf_plots, "parent_somatic",         "Parent\nSomatic", ylims = c(-0.5, 25)) #; parent_somatic_plot ; Sys.sleep(1)
parent_thought_uniplot         <- uni_plot(dvf_plots, "parent_thought",         "Parent\nThought", ylims = c(-0.5, 13.5)) #; parent_thought_plot ; Sys.sleep(1)
parent_withdrawn_uniplot       <- uni_plot(dvf_plots, "parent_withdrawn",       "Parent\nWithdrawn", ylims = c(-0.5, 17)) #; parent_withdrawn_plot ; Sys.sleep(1)
pericortical_wm_ndi_uniplot    <- uni_plot(dvf_plots, "pericortical_wm_ndi",    "Pericortical WM\nNeurite Density", ylims = c(0.25, 0.6)) #; pericortical_wm_ndi_plot ; Sys.sleep(1)
physical_activity_uniplot      <- uni_plot(dvf_plots, "physical_activity",      "Physical Activity", ylims = c(0, 1.1)) #; physical_activity_plot ; Sys.sleep(1)
previous_mtbis_uniplot         <- uni_plot(dvf_plots, "previous_mtbis",         "Previous mTBIs") #; previous_mtbis_plot ; Sys.sleep(1)
private_instruction_uniplot    <- uni_plot(dvf_plots, "private_instruction",    "Private Activities\n(Quartile)") #; private_instruction_plot ; Sys.sleep(1)
pubertal_status_p_uniplot      <- uni_plot(dvf_plots, "pubertal_status_p",      "Pubertal Status\n(Parent Report)") #; pubertal_status_p_plot ; Sys.sleep(1)
pubertal_status_y_uniplot      <- uni_plot(dvf_plots, "pubertal_status_y",      "Pubertal Status\n(Youth Report)") #; pubertal_status_y_plot ; Sys.sleep(1)
race_uniplot                   <- uni_plot(dvf_plots, "race",                   "Race", scale_fill_labels = c("Black", "Hispanic", "Other", "White")) #; race_plot ; Sys.sleep(1)
same_sex_close_friend_uniplot  <- uni_plot(dvf_plots, "same_sex_close_friend",  "Same-Sex Close\nFriends (Quartile)") #; same_sex_close_friend_plot ; Sys.sleep(1)
same_sex_friend_uniplot        <- uni_plot(dvf_plots, "same_sex_friend",        "Same-Sex Friends\n(Quartile)") #; same_sex_friend_plot ; Sys.sleep(1)
school_activities_uniplot      <- uni_plot(dvf_plots, "school_activities",      "School Activities") #; school_activities_plot ; Sys.sleep(1)
sex_uniplot                    <- uni_plot(dvf_plots, "sex",                    "Sex", c("F", "M")) #; sex_plot ; Sys.sleep(1)
weekday_screentime_uniplot     <- uni_plot(dvf_plots, "weekday_screentime",     "Weekday\nScreentime (hours)", ylims = c(-0.5, 21)) #; weekday_screentime_plot ; Sys.sleep(1)
weekend_screentime_uniplot     <- uni_plot(dvf_plots, "weekend_screentime",     "Weekend\nScreentime (hours)", ylims = c(-0.5, 21)) #; weekend_screentime_plot ; Sys.sleep(1)
# Outcome unip-uniplots#; # ; Sys.sleep(1)
cbcl_anxdep_uniplot            <- uni_plot(dvf_plots, "cbcl_anxdep",            "Anxious-\nDepressed", ylims = c(-0.5, 30))#; cbcl_anxdep_plot ; Sys.sleep(1)
cbcl_withdep_uniplot           <- uni_plot(dvf_plots, "cbcl_withdep",           "Withdrawn-\nDepressed", ylims = c(-0.5, 15))#; cbcl_withdep_plot ; Sys.sleep(1)
cbcl_somatic_uniplot           <- uni_plot(dvf_plots, "cbcl_somatic",           "Somatic", ylims = c(-0.5, 17))#; cbcl_somatic_plot ; Sys.sleep(1)
cbcl_social_uniplot            <- uni_plot(dvf_plots, "cbcl_social",            "Social", ylims = c(-0.5, 20))#; cbcl_social_plot ; Sys.sleep(1)
cbcl_thought_uniplot           <- uni_plot(dvf_plots, "cbcl_thought",           "Thought", ylims = c(-0.5, 20))#; cbcl_thought_plot ; Sys.sleep(1)
cbcl_attention_uniplot         <- uni_plot(dvf_plots, "cbcl_attention",         "Attention", ylims = c(-0.5, 22))#; cbcl_attention_plot ; Sys.sleep(1)
cbcl_rulebreak_uniplot         <- uni_plot(dvf_plots, "cbcl_rulebreak",         "Rule-Breaking", ylims = c(-0.5, 22))#; cbcl_rulebreak_plot ; Sys.sleep(1)
cbcl_aggressive_uniplot        <- uni_plot(dvf_plots, "cbcl_aggressive",        "Aggression", ylims = c(-0.5, 32))#; cbcl_aggressive_plot ; Sys.sleep(1)
sds_sleep_uniplot              <- uni_plot(dvf_plots, "sds_sleep",              "Total Sleep\nProblems", ylims = c(20, 100))#; sds_sleep_plot ; Sys.sleep(1)

generalizing_uniplots <- list(
    "activities_last_year"   = activities_last_year_uniplot,
    "age"                    = age_uniplot,
    "brain_volume"           = brain_volume_uniplot,
    "cbcl_aggressive"        = cbcl_aggressive_uniplot,
    "cbcl_anxdep"            = cbcl_anxdep_uniplot,
    "cbcl_attention"         = cbcl_attention_uniplot,
    #"cbcl_rulebreak"         = cbcl_rulebreak_uniplot,
    #"cbcl_social"            = cbcl_social_uniplot,
    "cbcl_somatic"           = cbcl_somatic_uniplot,
    #"cbcl_thought"           = cbcl_thought_uniplot,
    #"cbcl_withdep"           = cbcl_withdep_uniplot,
    #"considerate_p"          = considerate_p_uniplot,
    #"considerate_y"          = considerate_y_uniplot,
    #"cortical_sa"            = cort_sa_uniplot,
    #"cortical_t"             = cortical_t_uniplot,
    "extracurriculars"       = extracurriculars_uniplot,
    #"family_angry_p"         = family_angry_p_uniplot,
    #"family_angry_y"         = family_angry_y_uniplot,
    #"family_criticize_p"     = family_criticize_p_uniplot,
    #"family_criticize_y"     = family_criticize_y_uniplot,
    "family_fight_p"         = family_fight_p_uniplot,
    #"family_fight_y"         = family_fight_y_uniplot,
    #"family_hit_p"           = family_hit_p_uniplot,
    #"family_hit_y"           = family_hit_y_uniplot,
    #"family_outdo_p"         = family_outdo_p_uniplot,
    #"family_outdo_y"         = family_outdo_y_uniplot,
    #"family_peaceful_p"      = family_peaceful_p_uniplot,
    #"family_peaceful_y"      = family_peaceful_y_uniplot,
    #"family_temper_p"        = family_temper_p_uniplot,
    #"family_temper_y"        = family_temper_y_uniplot,
    #"family_throw_p"         = family_throw_p_uniplot,
    #"family_throw_y"         = family_throw_y_uniplot,
    #"family_yell_p"          = family_yell_p_uniplot,
    #"family_yell_y"          = family_yell_y_uniplot,
    #"fmri_dan_within_cor"    = fmri_dan_within_cor_uniplot,
    #"fmri_dmn_fpn_cor"       = fmri_dmn_fpn_cor_uniplot,
    #"fmri_dmn_within_cor"    = fmri_dmn_within_cor_uniplot,
    "fmri_fpn_lamyg_cor"     = fmri_fpn_lamyg_cor_uniplot,
    #"fmri_fpn_ramyg_cor"     = fmri_fpn_ramyg_cor_uniplot,
    #"fmri_fpn_within_cor"    = fmri_fpn_within_cor_uniplot,
    #"fmri_san_within_cor"    = fmri_san_within_cor_uniplot,
    "headache_history"       = headache_history_uniplot,
    #"helpful_p"              = helpful_p_uniplot,
    #"helpful_y"              = helpful_y_uniplot,
    "helps_hurt_p"           = helps_hurt_p_uniplot,
    #"helps_hurt_y"           = helps_hurt_y_uniplot,
    "household_income"       = household_income_uniplot,
    "major_wm_ndi"           = major_wm_ndi_uniplot,
    "mtbi_age"               = mtbi_age_uniplot,
    "mtbi_loc"               = mtbi_loc_uniplot,
    "mtbi_mechanism"         = mtbi_mechanism_uniplot,
    "mtbi_mem_daze"          = mtbi_mem_daze_uniplot,
    "opp_sex_close_friend"   = opp_sex_close_friend_uniplot,
    "opp_sex_friend"         = opp_sex_friend_uniplot,
    "parent_somatic"         = parent_somatic_uniplot,
    "parent_anxdep"          = parent_anxdep_uniplot,
    #"parent_aggressive"      = parent_aggressive_uniplot,
    #"parent_antisocial"      = parent_antisocial_uniplot,
    #"parent_anxdisord"       = parent_anxdisord_uniplot,
    #"parent_attention"       = parent_attention_uniplot,
    #"parent_avoidant"        = parent_avoidant_uniplot,
    #"parent_depress"         = parent_depress_uniplot,
    #"parent_hyperactive"     = parent_hyperactive_uniplot,
    #"parent_intrusive"       = parent_intrusive_uniplot,
    #"parent_perstr"          = parent_perstr_uniplot,
    #"parent_thought"         = parent_thought_uniplot,
    #"parent_withdrawn"       = parent_withdrawn_uniplot,
    "pericortical_wm_ndi"    = pericortical_wm_ndi_uniplot,
    "physical_activity"      = physical_activity_uniplot,
    "previous_mtbis"         = previous_mtbis_uniplot,
    "private_instruction"    = private_instruction_uniplot,
    "pubertal_status_p"      = pubertal_status_p_uniplot,
    #"pubertal_status_y"      = pubertal_status_y_uniplot,
    "race"                   = race_uniplot,
    "same_sex_close_friend"  = same_sex_close_friend_uniplot,
    "same_sex_friend"        = same_sex_friend_uniplot,
    "school_activities"      = school_activities_uniplot,
    "sds_sleep"              = sds_sleep_uniplot,
    "sex"                    = sex_uniplot,
    "weekday_screentime"     = weekday_screentime_uniplot
    #"weekend_screentime"     = weekend_screentime_uniplot
) |> lapply(
    function(x) {
        x + theme(
            axis.title.x = element_blank(),
            legend.title = element_text(size = 14),
            legend.text = element_text(size = 14)
        )
    }
)

generalizing_uniplots <- generalizing_uniplots[afts[afts %in% names(generalizing_uniplots)]]

saveRDS(generalizing_uniplots, proc_path("generalizing_uniplots.rds", TRUE))

generalizing_uniplots <- readRDS(proc_path("2026_01_22_generalizing_uniplots.rds"))
generalizing_uniplots$"brain_volume" <- generalizing_uniplots$"brain_volume" +
    scale_y_continuous(labels = scales::label_number(scale = 1e-3, suffix = "")) +
    labs(y = "Brain Volume\n(cm3)")
generalizing_uniplots$"cbcl_anxdep" <- generalizing_uniplots$"cbcl_anxdep" +
    labs(y = "CBCL Anxious-\nDepressed")
generalizing_uniplots$"cbcl_attention" <- generalizing_uniplots$"cbcl_attention" +
    labs(y = "CBCL Attention")
generalizing_uniplots$"cbcl_aggressive" <- generalizing_uniplots$"cbcl_aggressive" +
    labs(y = "CBCL Aggression")

generalizing_uniplots <- lapply(
    generalizing_uniplots,
    function(x) {
        x + theme(axis.title.y = element_text(size = 14))
    }
)

name_order <- c(
    "cbcl_anxdep",
    "cbcl_attention",
    "cbcl_aggressive",
    "sds_sleep",
    "sex",
    #
    "brain_volume",
    "fmri_fpn_lamyg_cor",
    "pericortical_wm_ndi",
    "major_wm_ndi",
    "race",
    #
    "weekday_screentime",
    "private_instruction",
    "parent_somatic",
    "parent_anxdep",
    "family_fight_p",
    #
    "age",
    "pubertal_status_p",
    "school_activities",
    "same_sex_close_friend",
    "helps_hurt_p",
    #
    "household_income",
    "physical_activity",
    "same_sex_friend",
    "opp_sex_friend",
    "mtbi_mechanism",
    #
    "mtbi_age",
    "activities_last_year",
    "extracurriculars",
    "previous_mtbis",
    "mtbi_loc"
)

generalizing_uniplots <- lapply(
    generalizing_uniplots,
    function(x) {
        if ("stat_summary" %in% names(x$"layers")) {
            x$"layers"$"stat_summary" <- NULL
            x + stat_summary(geom = "point", size = 4, colour = "black")
        } else {
            x
        }
    }
)

ggsave(
    fig_path("uniplots.png", TRUE),
    generalizing_uniplots_wrapped,
    width = 15,
    height = 14,
    dpi = 300,
    limitsize = FALSE
)





generalizing_uniplots[[2]] |> attributes()

generalizing_uniplots[[2]]$"theme"$"geom"$"pointsize" <- 1.5

generalizing_uniplots[[2]]$"theme"$"polygon"

generalizing_uniplots[[2]]$"theme"$"point"$"stroke" <- 0.

generalizing_uniplots[[2]] |> attributes()


generalizing_uniplots[[2]]$"layers"$"stat_summary"


generalizing_uniplots[[2]]$"layers"$"properties"

generalizing_uniplots[[2]]$"theme"$"point"$"colour" <- "blue"

generalizing_uniplots[[2]]$"theme"$"point"$"colour" <- 3

generalizing_uniplots[[2]]

args(wrap_plots)

```



```{r}
all_plots <- c(iplots, oplots)

light_fts <- c(
    "sex", # 1 (cat)
    "brain_volume", # 2
    "household_income",
    "race", # 6 (cat)
    "parent_antisocial",
    "weekday_screentime",
    "activities_last_year",
    "cbcl_aggressive",
    "sds_sleep"
)
all_light_plots <- all_plots[light_fts]
newsize <- 3

all_light_plots <- lapply(
    seq_along(all_light_plots),
    function(x) {
        all_light_plots[[x]] <- all_light_plots[[x]] + theme(
            legend.title = element_text(size = 14),
            legend.text = element_text(size = 14)
        )
        if (x %in% c(2, 3, 5, 6, 7, 8, 9)) {
            # Categorical features
            all_light_plots[[x]][[3]]$"layers"[[3]]$"aes_params"$"size" <- 3
        }
        if (x %in% c(1, 4)) {
            # Continuous / numeric features
            all_light_plots[[x]][[3]]$"layers"[[2]]$"aes_params"$"size" <- 5
        }
        all_light_plots[[x]][[3]]
    }
)
names(all_light_plots) <- light_fts
axis_fs <- 14
all_light_plots$"sex" <- all_light_plots$"sex" + labs(fill = "Sex", y = "%") + theme(axis.title.y = ggplot2::element_text(size = axis_fs, angle = 90), legend.position = "left")
all_light_plots$"brain_volume" <- all_light_plots$"brain_volume" + labs(y = "Brain\nVolume (cm³)") + theme(axis.title.y = ggplot2::element_text(angle = 90, size = axis_fs)) + scale_y_continuous(labels = function(x) x / 1000)
all_light_plots$"household_income" <- all_light_plots$"household_income" + labs(y = "Household\nIncome") + theme(axis.title.y = ggplot2::element_text(angle = 90, size = axis_fs))
all_light_plots$"activities_last_year" <- all_light_plots$"activities_last_year" + labs(y = "Activities Last\nYear (Quartile)") + theme(axis.title.y = ggplot2::element_text(angle = 90, size = axis_fs))
all_light_plots$"parent_antisocial" <- all_light_plots$"parent_antisocial" + labs(y = "Parent\nAntisocial") + theme(axis.title.y = ggplot2::element_text(angle = 90, size = axis_fs))
all_light_plots$"race" <- all_light_plots$"race" + labs(fill = "Race", y = "%") + theme(axis.title.y = ggplot2::element_text(angle = 90, size = axis_fs), legend.position = "left")
all_light_plots$"weekday_screentime" <- all_light_plots$"weekday_screentime" + labs(y = "Weekday\nScreentime\n(hours)") + theme(axis.title.y = ggplot2::element_text(angle = 90, size = axis_fs))
all_light_plots$"cbcl_aggressive" <- all_light_plots$"cbcl_aggressive" + labs(y = "CBCL\nAggressive") + theme(axis.title.y = ggplot2::element_text(angle = 90, size = axis_fs))
all_light_plots$"sds_sleep" <- all_light_plots$"sds_sleep" + labs(y = "Total Sleeping\nProblems") + theme(axis.title.y = ggplot2::element_text(angle = 90, size = axis_fs), legend.position = "none")
all_light_plots |>
    wrap_plots() |>
    quick_save(
        "light",
        w = 10,
        h = 6,
        dpi = 300
    )

```

# Summary of the validation (table)

```{r}
mtbi_gen_fts_table <- readRDS(proc_path("2025_09_22_mtbi_gen_fts_table.rds"))
rownames(mtbi_gen_fts_table) <- mtbi_gen_fts_table$"feature"

mtbi_gen_fts_table

afts_dummy <- afts
afts_dummy <- append(afts_dummy, "race_black", after = 9)
afts_dummy <- append(afts_dummy, "race_hispanic", after = 9)
afts_dummy <- append(afts_dummy, "race_other", after = 9)
afts_dummy <- append(afts_dummy, "race_white", after = 9)
afts_dummy <- append(afts_dummy, "mtbi_mechanism_fall_hit", after = 58)
afts_dummy <- append(afts_dummy, "mtbi_mechanism_hosp_er", after = 58)
afts_dummy <- append(afts_dummy, "mtbi_mechanism_multi", after = 58)
afts_dummy <- append(afts_dummy, "mtbi_mechanism_other_loc", after = 58)
afts_dummy <- append(afts_dummy, "mtbi_mechanism_vehicle", after = 58)
afts_dummy <- append(afts_dummy, "mtbi_mechanism_violent", after = 58)
afts_dummy <- afts_dummy[-c(9, 58)] # remove race and mtbi_mechanism
afts_dummy
for (ft in seq_along(afts_dummy)) {
    print(paste0(ft, ": ", afts_dummy[ft]))
}

mtbi_gen_fts_table_hits <- mtbi_gen_fts_table[afts_dummy, ] |>
    dplyr::filter(
        c1v2 %in% c(">", "<") | c1v3 %in% c(">", "<") | c2v3 %in% c(">", "<")
    )
mtbi_gen_fts_table_hits

write_csv(mtbi_gen_fts_table_hits, proc_path("mtbi_gen_fts_table_hits.csv", TRUE))
```

```{r}
mtbi_gen_fts_table_hits <- read_csv(proc_path("2025_09_22_mtbi_gen_fts_table_hits.csv"))

mtbi_gen_fts_table_hits

mtbi_gen_fts_table_hits_t <- mtbi_gen_fts_table_hits |>
    pivot_longer(
        cols = -feature,
        names_to = "comparison",
        values_to = "order"
    )

write_csv(mtbi_gen_fts_table_hits_t, proc_path("mtbi_gen_fts_table_hits_t.csv", TRUE))

mtbi_gen_fts_table_hits_t <- read_csv(proc_path("2025_09_22_mtbi_gen_fts_table_hits_t.csv"))

mtbi_gen_fts_table_hits_t |>
    knitr::kable(format = "markdown", align = "lccc") |>
    writeLines(proc_path("mtbi_gen_fts_table_hits_t.txt", TRUE))

# 2025-09-30
mtbi_gen_fts_table_hits |>
    dplyr::mutate(
        c1v2 = dplyr::case_when(is.na(c1v2) ~ "-", c1v2 == "=" ~ "-", c1v2 == "<" ~ "$lt$", c1v2 == ">" ~ "$gt$", TRUE ~ c1v2),
        c1v3 = dplyr::case_when(is.na(c1v3) ~ "-", c1v3 == "=" ~ "-", c1v3 == "<" ~ "$lt$", c1v3 == ">" ~ "$gt$", TRUE ~ c1v3),
        c2v3 = dplyr::case_when(is.na(c2v3) ~ "-", c2v3 == "=" ~ "-", c2v3 == "<" ~ "$lt$", c2v3 == ">" ~ "$gt$", TRUE ~ c2v3)
    ) |>
    dplyr::rename(
        "Feature" = "feature",
        "C1v2" = "c1v2",
        "C1v3" = "c1v3",
        "C2v3" = "c2v3"
    ) |>
    knitr::kable(format = "markdown", align = "lccc") |>
    writeLines(proc_path("mtbi_gen_fts_table_hits.txt", TRUE))
```

## How would the process go in demographic adjusted data?

The outcomes (and inputs) appear heavily associated with demographic variables pubertal status, sex, income, and race.
How would correcting for those variables influence the meta clustering results?

```{r}
mtbi_dl_1 <- readRDS(input_path("2025_09_15_mtbi_dl_1.rds"))
mtbi_ol_1 <- readRDS(input_path("2025_09_15_mtbi_ol_1.rds"))

# excluding mTBI mechanism from analysis, as it is an unadjustable categorical
# feature
dl_no_demo <- mtbi_dl_1[-c(2, 4, 6:9)] 
dl_demo <- mtbi_dl_1[c(4, 6:9)]

saveRDS(dl_demo, proc_path("dl_demo.rds", TRUE))
saveRDS(dl_no_demo, proc_path("dl_no_demo.rds", TRUE))

dl_demo <- readRDS(proc_path("2025_09_23_dl_demo.rds"))
dl_no_demo <- readRDS(proc_path("2025_09_23_dl_no_demo.rds"))

dl_demo

dl_corrected <- linear_adjust(dl_no_demo, dl_demo)

saveRDS(dl_corrected, proc_path("dl_corrected.rds", TRUE))
```

```{r}
# CHECKPOINT
dl_corrected <- readRDS(proc_path("2025_09_23_dl_corrected.rds"))

names(dl_corrected)

as.data.frame(c(dl_corrected, dl_demo)) |>
    ggplot(aes(x = sex, y = mtbi_mem_daze)) +
    geom_point() +
    geom_smooth(method = "lm", se = FALSE)

as.data.frame(c(dl_corrected, dl_demo)) |>
    ggplot(aes(x = sex, y = brain_volume)) +
    geom_point() +
    geom_smooth(method = "lm", se = FALSE) +
    theme_bw()
```

```{r}
set.seed(42)
corrected_config <- snf_config(
    dl_corrected,
    n_solutions = 400,
    cnt_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    dsc_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ord_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    use_default_dist_fns = TRUE
)
saveRDS(corrected_config, proc_path("corrected_config.rds", TRUE))

corrected_config <- readRDS(proc_path("2025_09_23_corrected_config.rds"))

correction_heatmap <- c(dl_corrected, dl_demo) |>
    as.data.frame() |>
    dummy_cols(
        select_columns = c("race", "mtbi_mechanism"),
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = FALSE
    ) |>
    dplyr::select(-"uid") |>
    dplyr::relocate(
        "race_white",
        "race_black",
        "race_hispanic",
        "race_other",
        "age",
        "pubertal_status_p",
        "pubertal_status_y",
        "household_income",
        "sex",
        .after = last_col()
    ) |>
    cor() |>
    Heatmap(cluster_rows = FALSE, cluster_columns = FALSE)

save_heatmap(
    heatmap = correction_heatmap,
    path = fig_path("correction_heatmap.png", TRUE),
    width = 950,
    height = 700,
    res = 100
)
```


```{r}
# CHECKPOINT
dl_corrected <- readRDS(proc_path("2025_09_23_dl_corrected.rds"))
corrected_config <- readRDS(proc_path("2025_09_23_corrected_config.rds"))
```

Meta clustering using the demographic adjusted data list.

```{r}
progressr::with_progress({
demo_adj_sol_df <- batch_snf(
    dl = dl_corrected,
    sc = corrected_config,
    processes = "max"
)
})
saveRDS(demo_adj_sol_df, proc_path("demo_adj_sol_df.rds", TRUE))
```

```{r}
# CHECKPOINT
demo_adj_sol_df <- readRDS(proc_path("2025_09_23_demo_adj_sol_df.rds"))
demo_adj_ari <- calc_aris(demo_adj_sol_df, verbose = TRUE, processes = "max")
saveRDS(demo_adj_ari, proc_path("demo_adj_ari.rds", TRUE))
```

```{r}
demo_adj_ari_order <- get_matrix_order(demo_adj_ari)
saveRDS(demo_adj_ari_order, proc_path("demo_adj_ari_order.rds", TRUE))
```

```{r}
# CHECKPOINT
demo_adj_sol_df <- readRDS(proc_path("2025_09_23_demo_adj_sol_df.rds"))
demo_adj_ari <- readRDS(proc_path("2025_09_23_demo_adj_ari.rds"))
demo_adj_ari_order <- readRDS(proc_path("2025_09_23_demo_adj_ari_order.rds"))
```

Creating a demographic adjusted outcome list to extend against.

```{r}
adj_oom_list <- linear_adjust(mtbi_ol_1, dl_demo)
saveRDS(adj_oom_list, proc_path("adj_oom_list.rds", TRUE))
```

```{r}
adj_oom_list <- readRDS(proc_path("2025_09_23_adj_oom_list.rds"))
```

```{r}
# Extend solutions from adjusted inputs to adjusted outcomes
demo_double_adj_ext_sol_df <- extend_solutions(
    demo_adj_sol_df,
    dl = dl_corrected,
    target_dl = adj_oom_list,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(
    demo_double_adj_ext_sol_df,
    proc_path("demo_double_adj_ext_sol_df.rds", TRUE)
)
```

```{r}
demo_double_adj_ext_sol_df <- readRDS(
    proc_path("2025_09_23_demo_double_adj_ext_sol_df.rds")
)

base_adj_ari_hm <- meta_cluster_heatmap(
    demo_adj_ari,
    order = demo_adj_ari_order
)

demo_double_adj_esdf <- as.data.frame(demo_double_adj_ext_sol_df)
demo_double_adj_esdf$"impairment_separation" <- -log10(demo_double_adj_esdf$"mean_pval")

demo_adj_split_vec <- c(30, 65, 183, 236, 281, 361, 375)

saveRDS(demo_adj_split_vec, proc_path("demo_adj_split_vec.rds", TRUE))

demo_adj_split_vec <- readRDS(proc_path("2025_09_23_demo_adj_split_vec.rds"))

# The double adjustment does not yield and interesting meta clusters
full_demo_double_adj_ari_hm <- meta_cluster_heatmap(
    x = demo_adj_ari,
    order = demo_adj_ari_order,
    data = demo_double_adj_esdf,
    min_colour = "black",
    split_vector = demo_adj_split_vec,
    top_hm = list(
        "Impairment Separation" = "impairment_separation"
    ),
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    annotation_colours = list(
        "Impairment Separation" = colour_scale(
            # Using the separation scale of the original derivation clustering
            demo_double_adj_esdf$"impairment_separation",
            min_colour = "gray7",
            max_colour = "limegreen"
        )
    )
)
full_demo_double_adj_ari_hm

save_heatmap(
    heatmap = full_demo_double_adj_ari_hm,
    path = fig_path("full_demo_double_adj_ari_hm.png", TRUE),
    width = 950,
    height = 700,
    res = 100
)

double_demo_adj_mc_sol_df <- label_meta_clusters(
    demo_double_adj_ext_sol_df,
    order = demo_adj_ari_order,
    split_vector = demo_adj_split_vec
)

double_demo_adj_rep_solutions <- get_representative_solutions(
    demo_adj_ari,
    double_demo_adj_mc_sol_df
)

min(double_demo_adj_rep_solutions$"mean_pval") # The lowest mean p-value is 0.2156412
```
