# metaSNF of Baseline mTBI Subjects

This chapter contains:

1. Derivation of baseline mTBI subtypes with metasnf
2. Characterization of those subtypes

## Importing packages and establishing file paths

```{r}
# CHECKPOINT 
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)
library(ggplot2)
library(patchwork)
library(xtable)
library(compute.es)
library(dplyr)
library(fastDummies)
library(tidyr)

input_path      <- path_maker(here(paste0("data/abcd/inputs")))
proc_path       <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path        <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path        <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subs       <- read_csv(sub_path("2025_05_22_mtbi_subs.csv"))
mtbi_train_subs <- read_csv(sub_path("2025_05_22_mtbi_train_subs.csv"))
mtbi_test_subs  <- read_csv(sub_path("2025_05_22_mtbi_test_subs.csv"))

mtbi_ns_subs     <- readRDS(sub_path("2025_06_11_mtbi_no_sibs_subs.rds"))
mtbi_ns_der_subs <- readRDS(sub_path("2025_06_11_mtbi_der_no_sibs_subs.rds"))
mtbi_ns_val_subs <- readRDS(sub_path("2025_06_11_mtbi_val_no_sibs_subs.rds"))
unij_ns_subs     <- readRDS(sub_path("2025_06_11_unij_no_sibs_subs.rds"))
```

## Importing data

`all_dls` contains all the imputed data lists (including out of model data lists) for the mTBI derivation (train) and validation (test) splits, as well as for the uninjured subjects.

```{r}
#all_dls <- readRDS(input_path("2025_05_27_all_dls.rds"))
#all_dls_h <- readRDS(proc_path("2025_06_11_all_dls_h.rds"))
all_dls_h_ns <- readRDS(proc_path("2025_06_11_all_dls_h_no_sibs.rds"))

names(all_dls_h_ns)
```

## Generating the SNF config

```{r}
set.seed(42)
mtbi_config <- snf_config(
    all_dls_h_ns$"mtbi_der_u_dls"$"imp_1",
    n_solutions = 200,
    cnt_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    dsc_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ord_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    use_default_dist_fns = TRUE
)

saveRDS(mtbi_config, proc_path("mtbi_config.rds", TRUE))
```

## Running SNF for each of the imputations

```{r}
# CHECKPOINT
mtbi_config <- readRDS(proc_path("2025_06_11_mtbi_config.rds"))
all_dls_h_ns <- readRDS(proc_path("2025_06_11_all_dls_h_no_sibs.rds"))

run_mtbi_der_u_batch_snf <- function(x) {
    progressr::with_progress({
        batch_snf(
            dl = all_dls_h_ns$"mtbi_der_u_dls"[[x]],
            sc = mtbi_config,
            processes = "max"
        )
    })
}

run_mtbi_der_p_batch_snf <- function(x) {
    progressr::with_progress({
        batch_snf(
            dl = all_dls_h_ns$"mtbi_der_p_dls"[[x]],
            sc = mtbi_config,
            processes = "max"
        )
    })
}
```

```{r}
# mtbi derivation set unpooled sample
mtbi_der_sol_df_u1 <- run_mtbi_der_u_batch_snf(1)
saveRDS(mtbi_der_sol_df_u1, proc_path("mtbi_der_sol_df_u1.rds", TRUE))

mtbi_der_sol_df_u2 <- run_mtbi_der_u_batch_snf(2)
saveRDS(mtbi_der_sol_df_u2, proc_path("mtbi_der_sol_df_u2.rds", TRUE))
```

```{r}
mtbi_der_sol_df_u3 <- run_mtbi_der_u_batch_snf(3)
saveRDS(mtbi_der_sol_df_u3, proc_path("mtbi_der_sol_df_u3.rds", TRUE))

mtbi_der_sol_df_u4 <- run_mtbi_der_u_batch_snf(4)
saveRDS(mtbi_der_sol_df_u4, proc_path("mtbi_der_sol_df_u4.rds", TRUE))

mtbi_der_sol_df_u5 <- run_mtbi_der_u_batch_snf(5)
saveRDS(mtbi_der_sol_df_u5, proc_path("mtbi_der_sol_df_u5.rds", TRUE))
```

```{r}
# mtbi derivation set pooled sample
mtbi_der_sol_df_p1 <- run_mtbi_der_p_batch_snf(1)
saveRDS(mtbi_der_sol_df_p1, proc_path("mtbi_der_sol_df_p1.rds", TRUE))
#
mtbi_der_sol_df_p2 <- run_mtbi_der_p_batch_snf(2)
saveRDS(mtbi_der_sol_df_p2, proc_path("mtbi_der_sol_df_p2.rds", TRUE))
```

```{r}
mtbi_der_sol_df_p3 <- run_mtbi_der_p_batch_snf(3)
saveRDS(mtbi_der_sol_df_p3, proc_path("mtbi_der_sol_df_p3.rds", TRUE))
#
mtbi_der_sol_df_p4 <- run_mtbi_der_p_batch_snf(4)
saveRDS(mtbi_der_sol_df_p4, proc_path("mtbi_der_sol_df_p4.rds", TRUE))
#
mtbi_der_sol_df_p5 <- run_mtbi_der_p_batch_snf(5)
saveRDS(mtbi_der_sol_df_p5, proc_path("mtbi_der_sol_df_p5.rds", TRUE))
```

```{r}
mtbi_der_sol_df_u1 <- readRDS(proc_path("2025_06_11_mtbi_der_sol_df_u1.rds"))
mtbi_der_sol_df_u2 <- readRDS(proc_path("2025_06_11_mtbi_der_sol_df_u2.rds"))
mtbi_der_sol_df_u3 <- readRDS(proc_path("2025_06_11_mtbi_der_sol_df_u3.rds"))
mtbi_der_sol_df_u4 <- readRDS(proc_path("2025_06_11_mtbi_der_sol_df_u4.rds"))
mtbi_der_sol_df_u5 <- readRDS(proc_path("2025_06_11_mtbi_der_sol_df_u5.rds"))

mtbi_der_sol_df_p1 <- readRDS(proc_path("2025_06_11_mtbi_der_sol_df_p1.rds"))
mtbi_der_sol_df_p2 <- readRDS(proc_path("2025_06_11_mtbi_der_sol_df_p2.rds"))
mtbi_der_sol_df_p3 <- readRDS(proc_path("2025_06_11_mtbi_der_sol_df_p3.rds"))
mtbi_der_sol_df_p4 <- readRDS(proc_path("2025_06_11_mtbi_der_sol_df_p4.rds"))
mtbi_der_sol_df_p5 <- readRDS(proc_path("2025_06_11_mtbi_der_sol_df_p5.rds"))
```

```{r}
mtbi_der_sol_df <- do.call(
    "rbind",
    c(
        list(
            mtbi_der_sol_df_u1,
            mtbi_der_sol_df_u2,
            mtbi_der_sol_df_u3,
            mtbi_der_sol_df_u4,
            mtbi_der_sol_df_u5,
            mtbi_der_sol_df_p1,
            mtbi_der_sol_df_p2,
            mtbi_der_sol_df_p3,
            mtbi_der_sol_df_p4,
            mtbi_der_sol_df_p5
        ),
        list(reset_indices = TRUE)
    )
)
saveRDS(mtbi_der_sol_df, proc_path("mtbi_der_sol_df.rds", TRUE))

mtbi_der_ari <- calc_aris(mtbi_der_sol_df, processes = "max")
saveRDS(mtbi_der_ari, proc_path("mtbi_der_ari.rds", TRUE))

mtbi_der_ari_order <- get_matrix_order(mtbi_der_ari)
saveRDS(mtbi_der_ari_order, proc_path("mtbi_der_ari_order.rds", TRUE))
```

## Re-importing data

```{r}
# CHECKPOINT
mtbi_der_sol_df    <- readRDS(proc_path("2025_06_11_mtbi_der_sol_df.rds"))
mtbi_der_ari       <- readRDS(proc_path("2025_06_11_mtbi_der_ari.rds"))
mtbi_der_ari_order <- readRDS(proc_path("2025_06_11_mtbi_der_ari_order.rds"))
```

## Calculating associations between cluster solutions and features

```{r}
run_extend_solutions <- function(name, x) {
    imp <- paste0("imp_", if (max(x %% 5) > 0) max(x %% 5) else 5)
    cat(
        "Extending rows: ", 
        (200*(x-1) + 1),
        " to ",
        (200*x),
        " for imputation ",
        imp,
        ".\n",
        sep = ""
    )
    extend_solutions(
        mtbi_der_sol_df[(200*(x-1) + 1):(200*x), ],
        dl = all_dls[[paste0(name, "_dls")]][[imp]],
        target_dl = all_dls[[paste0(name, "_ols")]][[imp]],
        min_pval = 1e-10,
        processes = "max"
    )
}

# Unpooled imputations
mtbi_der_ext_sol_df_u1 <- run_extend_solutions("mtbi_der_u", 1)
saveRDS(mtbi_der_ext_sol_df_u1, proc_path("mtbi_der_ext_sol_df_u1.rds", TRUE))
mtbi_der_ext_sol_df_u2 <- run_extend_solutions("mtbi_der_u", 2)
saveRDS(mtbi_der_ext_sol_df_u2, proc_path("mtbi_der_ext_sol_df_u2.rds", TRUE))
mtbi_der_ext_sol_df_u3 <- run_extend_solutions("mtbi_der_u", 3)
saveRDS(mtbi_der_ext_sol_df_u3, proc_path("mtbi_der_ext_sol_df_u3.rds", TRUE))
mtbi_der_ext_sol_df_u4 <- run_extend_solutions("mtbi_der_u", 4)
saveRDS(mtbi_der_ext_sol_df_u4, proc_path("mtbi_der_ext_sol_df_u4.rds", TRUE))
mtbi_der_ext_sol_df_u5 <- run_extend_solutions("mtbi_der_u", 5)
saveRDS(mtbi_der_ext_sol_df_u5, proc_path("mtbi_der_ext_sol_df_u5.rds", TRUE))

mtbi_der_ext_sol_df_p1 <- run_extend_solutions("mtbi_der_p", 6)
saveRDS(mtbi_der_ext_sol_df_p1, proc_path("mtbi_der_ext_sol_df_p1.rds", TRUE))
mtbi_der_ext_sol_df_p2 <- run_extend_solutions("mtbi_der_p", 7)
saveRDS(mtbi_der_ext_sol_df_p2, proc_path("mtbi_der_ext_sol_df_p2.rds", TRUE))
mtbi_der_ext_sol_df_p3 <- run_extend_solutions("mtbi_der_p", 8)
saveRDS(mtbi_der_ext_sol_df_p3, proc_path("mtbi_der_ext_sol_df_p3.rds", TRUE))
mtbi_der_ext_sol_df_p4 <- run_extend_solutions("mtbi_der_p", 9)
saveRDS(mtbi_der_ext_sol_df_p4, proc_path("mtbi_der_ext_sol_df_p4.rds", TRUE))
mtbi_der_ext_sol_df_p5 <- run_extend_solutions("mtbi_der_p", 10)
saveRDS(mtbi_der_ext_sol_df_p5, proc_path("mtbi_der_ext_sol_df_p5.rds", TRUE))
```

```{r}
mtbi_der_ext_sol_df_u1 <- readRDS(proc_path("2025_06_11_mtbi_der_ext_sol_df_u1.rds"))
mtbi_der_ext_sol_df_u2 <- readRDS(proc_path("2025_06_11_mtbi_der_ext_sol_df_u2.rds"))
mtbi_der_ext_sol_df_u3 <- readRDS(proc_path("2025_06_11_mtbi_der_ext_sol_df_u3.rds"))
mtbi_der_ext_sol_df_u4 <- readRDS(proc_path("2025_06_11_mtbi_der_ext_sol_df_u4.rds"))
mtbi_der_ext_sol_df_u5 <- readRDS(proc_path("2025_06_11_mtbi_der_ext_sol_df_u5.rds"))
mtbi_der_ext_sol_df_p1 <- readRDS(proc_path("2025_06_11_mtbi_der_ext_sol_df_p1.rds"))
mtbi_der_ext_sol_df_p2 <- readRDS(proc_path("2025_06_11_mtbi_der_ext_sol_df_p2.rds"))
mtbi_der_ext_sol_df_p3 <- readRDS(proc_path("2025_06_11_mtbi_der_ext_sol_df_p3.rds"))
mtbi_der_ext_sol_df_p4 <- readRDS(proc_path("2025_06_11_mtbi_der_ext_sol_df_p4.rds"))
mtbi_der_ext_sol_df_p5 <- readRDS(proc_path("2025_06_11_mtbi_der_ext_sol_df_p5.rds"))

drop_mtbi_cols <- function(x) {
    x[, !grepl("mtbi", colnames(x))]
}

# To be able to vertically stack all the pooled and unpooled solutions data frames
mtbi_der_ext_sol_df_u1_no_mtbi <- drop_mtbi_cols(mtbi_der_ext_sol_df_u1)
mtbi_der_ext_sol_df_u2_no_mtbi <- drop_mtbi_cols(mtbi_der_ext_sol_df_u2)
mtbi_der_ext_sol_df_u3_no_mtbi <- drop_mtbi_cols(mtbi_der_ext_sol_df_u3)
mtbi_der_ext_sol_df_u4_no_mtbi <- drop_mtbi_cols(mtbi_der_ext_sol_df_u4)
mtbi_der_ext_sol_df_u5_no_mtbi <- drop_mtbi_cols(mtbi_der_ext_sol_df_u5)

mtbi_der_ext_sol_df <- do.call(
    "rbind",
    c(
        list(
            mtbi_der_ext_sol_df_u1_no_mtbi,
            mtbi_der_ext_sol_df_u2_no_mtbi,
            mtbi_der_ext_sol_df_u3_no_mtbi,
            mtbi_der_ext_sol_df_u4_no_mtbi,
            mtbi_der_ext_sol_df_u5_no_mtbi,
            mtbi_der_ext_sol_df_p1,
            mtbi_der_ext_sol_df_p2,
            mtbi_der_ext_sol_df_p3,
            mtbi_der_ext_sol_df_p4,
            mtbi_der_ext_sol_df_p5
        ),
        list(reset_indices = TRUE)
    )
)

mtbi_der_ext_sol_df   

saveRDS(mtbi_der_ext_sol_df, proc_path("mtbi_der_ext_sol_df.rds", TRUE))
```

```{r}
# CHECKPOINT
#mtbi_ext_sol_df <- readRDS(proc_path("2025_02_11_mtbi_ext_sol_df.rds"))
mtbi_der_ext_sol_df <- readRDS(proc_path("2025_06_11_mtbi_der_ext_sol_df.rds"))
```

## Identifying and visualizing meta clusters

```{r}
mtbi_der_ari_hm <- meta_cluster_heatmap(
    mtbi_der_ari,
    order = mtbi_der_ari_order
)

divergent_colours <- function(column)  {
    values <- unique(column)
    colours <- RColorBrewer::brewer.pal(n = length(values), name = "Set3")
    names(colours) <- values
    return(colours)
}

mtbi_der_esdf <- as.data.frame(mtbi_der_ext_sol_df)

mtbi_der_esdf$"impairment_separation" <- -log10(mtbi_der_esdf$"mean_pval")

mtbi_der_esdf$"pool" <- c(rep("no", 1000), rep("yes", 1000))

mtbi_der_esdf$"imputation" <- c(
    rep("u1", 200),
    rep("u2", 200),
    rep("u3", 200),
    rep("u4", 200),
    rep("u5", 200),
    rep("p1", 200),
    rep("p2", 200),
    rep("p3", 200),
    rep("p4", 200),
    rep("p5", 200)
)

write_csv(mtbi_der_esdf, proc_path("mtbi_der_esdf.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_der_esdf <- read_csv(proc_path("2025_06_11_mtbi_der_esdf.csv"))
```



```{r}
mtbi_der_split_vec <- c(
    170,
    497,
    538,
    690,
    758,
    895,
    1149,
    1215,
    1415,
    1630
)
saveRDS(mtbi_der_split_vec, proc_path("mtbi_split_vec.rds", TRUE))
mtbi_der_split_vec <- readRDS(proc_path("2025_06_11_mtbi_split_vec.rds"))
mtbi_der_ari_hm <- meta_cluster_heatmap(
    x = mtbi_der_ari,
    order = mtbi_der_ari_order,
    data = mtbi_der_esdf,
    min_colour = "black",
    split_vector = mtbi_der_split_vec,
    top_hm = list(
        "Impairment Separation" = "impairment_separation"
    ),
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    left_hm = list(
        "Pooled" = "pool",
        "Imputation" = "imputation"
    ),
    annotation_colours = list(
        "Impairment Separation" = colour_scale(
            mtbi_der_esdf$"impairment_separation",
            min_colour = "gray7",
            max_colour = "limegreen"
        ),
        "Imputation" = divergent_colours(mtbi_der_esdf$"imputation"),
        "Pooled" = c(
            "yes" = "orange",
            "no" = "purple"
        )
    )
)
mtbi_der_ari_hm

save_heatmap(
    heatmap = mtbi_der_ari_hm,
    path = fig_path("mtbi_der_ari_hm.png", TRUE),
    width = 950,
    height = 900,
    res = 100
)
```

```{r}
mtbi_der_mc_sol_df <- label_meta_clusters(
    mtbi_der_ext_sol_df,
    order = mtbi_der_ari_order,
    split_vector = mtbi_der_split_vec
)

saveRDS(mtbi_der_mc_sol_df, proc_path("mtbi_der_mc_sol_df.rds", TRUE))
```

```{r}
# CHECKPOINT
mtbi_der_mc_sol_df <- readRDS(proc_path("2025_05_27_mtbi_der_mc_sol_df.rds"))
```

When picking out representative solutions, I'd like to preferentially go for solutions that derived from solo rather than pooled imputations, as those solutions have values for all features.

```{r}
# Function to try to lean on mTBI-including solutions when possible.
# This function will pick from solo solutions unless over 70% of the meta
# cluster is pooled.
restrict_fn <- function(x, threshold = 0.3) {
    x_solo_ind <- x$"solution" %in% 1:1000
    x_pool_ind <- x$"solution" %in% 1001:2000
    x_solo <- x[x_solo_ind, ]
    x_pool <- x[x_pool_ind, ]
    frac_solo <- nrow(x_solo) / (nrow(x_solo) + nrow(x_pool))
    if (frac_solo < threshold) {
        return(x[x_pool_ind, ])
    } else {
        return(x[x_solo_ind, ])
    }
}

mtbi_der_rep_solutions <- get_representative_solutions(
    mtbi_der_ari,
    mtbi_der_mc_sol_df,
    filter_fn = restrict_fn
)

saveRDS(mtbi_der_rep_solutions, proc_path("mtbi_der_rep_solutions.rds", TRUE))
```

```{r}
mtbi_der_rep_solutions <- readRDS(
    proc_path("2025_05_27_mtbi_der_rep_solutions.rds")
)

mtbi_der_rep_solutions

# Top solution is meta cluster F, represented by solution 776
mtbi_der_top_solution <- mtbi_der_ext_sol_df_u4[mtbi_der_ext_sol_df_u4$"solution" == 776, ]

mtbi_der_top_solution$"mc" <- "F"

saveRDS(mtbi_der_top_solution, proc_path("mtbi_der_top_solution.rds", TRUE))
```

```{r}
# CHECKPOINT
mtbi_der_top_solution <- readRDS(
    proc_path("2025_05_27_mtbi_der_top_solution.rds")
)

mtbi_der_top_solution$"mc" <- "Derivation MC F"

mtbi_der_manhattan <- mc_manhattan_plot(
    mtbi_der_top_solution,
    dl = all_dls$"mtbi_train_data_lists"$"imp_4",
    target_dl = all_dls$"mtbi_train_oom_lists"$"imp_4",
    domain_colours = c(
        "AS" = "#85929e",
        "D" = "#bb8fce",
        "N" = "#e59866",
        "MH" = "#7fb3d5",
        "P" = "#52be80",
        "S" = "#d98880",
        "B" = "#ff3131"
    )
)
mtbi_der_manhattan

ggsave(
    plot = mtbi_der_manhattan,
    filename = fig_path("mtbi_der_manhattan.png", TRUE),
    width = 18,
    height = 5,
    dpi = 120
)
```

```{r}

# Initial visualizations
plot_list <- auto_plot(
    sol_df_row = mtbi_der_top_solution,
    dl = c(
        all_dls$"mtbi_train_data_lists"$"imp_4",
        all_dls$"mtbi_train_oom_lists"$"imp_4"
    ),
    verbose = TRUE
)

plot_list$"sex"

plot_list$"race"

# In anticipation of the upcoming cluster swaps
cluster_label_swap <- function(solutions_matrix, c_a, c_b) {
    swapped_sm <- dplyr::mutate(
        solutions_matrix,
        across(
            dplyr::starts_with("uid"),
            ~ ifelse(
                . == c_a,
                c_b,
                ifelse(
                    . == c_b,
                    c_a,
                    .
                )
            )
        )
    )
    return(swapped_sm)
}

mtbi_der_top_solution_swp <- cluster_label_swap(mtbi_der_top_solution, 1, 3)
mtbi_der_top_solution_swp <- cluster_label_swap(mtbi_der_top_solution_swp, 2, 3)

saveRDS(
    mtbi_der_top_solution_swp,
    proc_path("mtbi_der_top_solution_swp.rds", TRUE)
)
```

```{r}
# CHECKPOINT
mtbi_der_top_solution_swp <- readRDS(
    proc_path("2025_05_27_mtbi_der_top_solution_swp.rds")
)
```

```{r}
plot_list <- auto_plot(
    sol_df_row = mtbi_der_top_solution_swp,
    dl = c(
        all_dls$"mtbi_train_data_lists"$"imp_4",
        all_dls$"mtbi_train_oom_lists"$"imp_4"
    ),
    verbose = TRUE
)

saveRDS(plot_list, fig_path("mtbi_der_top_solution_pl.rds", TRUE))
```

```{r}
# CHECKPOINT
train_dl_u4 <- all_dls$"mtbi_train_data_lists"$"imp_4"
train_ol_u4 <- all_dls$"mtbi_train_oom_lists"$"imp_4"
train_io_dl_u4 <- c(train_dl_u4, train_ol_u4)
```

## Feature importance

### Rank by NMI

```{r}
progressr::with_progress({
    nmis <- calc_nmis(train_dl_u4, mtbi_der_top_solution_swp)
})

nmi_order <- sort(nmis$"s776", decreasing = TRUE, index.return = TRUE)
ordered_nmis <- nmis[nmi_order$ix, ]
ordered_nmis$"nmi_rank" <- rank(-ordered_nmis$"s776", ties.method = "min")
```

### Rank by p-values

```{r}
pvals <- get_pvals(mtbi_der_top_solution_swp, keep_summaries = FALSE)
pvals <- data.frame(
    "feature" = gsub("_pval", "", names(pvals)),
    "neg_log_pval" = -log10(as.numeric(unlist(pvals)))
)
pvals <- pvals[-1, ]
pvals_order <- sort(
    pvals$"neg_log_pval",
    decreasing = TRUE,
    index.return = TRUE
)
ordered_pvals <- pvals[pvals_order$ix, ]
ordered_pvals <- dplyr::filter(
    ordered_pvals,
    !grepl("^cbcl|^sds", feature)
)
ordered_pvals$"pval_rank" <- rank(
    -ordered_pvals$"neg_log_pval",
    ties.method = "min"
)
```

### Joint rank

```{r}
mtbi_der_top_solution_nmi_v_pval <- dplyr::full_join(
    ordered_nmis,
    ordered_pvals,
    by = "feature"
)

domain_df <- train_dl_u4 |>
    summary("feature") |>
    dplyr::select(name, domain) |>
    dplyr::rename("feature" = "name")

domain_df

mtbi_der_top_solution_nmi_v_pval <- dplyr::inner_join(
    mtbi_der_top_solution_nmi_v_pval,
    domain_df,
    by = "feature"
)

mtbi_der_top_solution_nmi_v_pval <- dplyr::mutate(
    mtbi_der_top_solution_nmi_v_pval,
    nmi_plus_pval = nmi_rank + pval_rank
)

mtbi_der_top_solution_nmi_v_pval$"joint_rank" <- rank(
    mtbi_der_top_solution_nmi_v_pval$"nmi_plus_pval",
    ties.method = "min"
)

joint_order <- sort(
    mtbi_der_top_solution_nmi_v_pval$"joint_rank",
    decreasing = FALSE,
    index.return = TRUE
)

mtbi_der_top_solution_nmi_v_pval_rank <-
    mtbi_der_top_solution_nmi_v_pval[joint_order$ix, ]

mtbi_der_top_solution_nmi_v_pval_rank <- dplyr::rename(
    mtbi_der_top_solution_nmi_v_pval_rank,
    "nmi" = "s776"
)

mtbi_der_top_solution_nmi_v_pval_rank <- dplyr::select(
    mtbi_der_top_solution_nmi_v_pval_rank,
    feature,
    domain,
    nmi,
    nmi_rank,
    neg_log_pval,
    pval_rank,
    joint_rank
)

write_csv(
    mtbi_der_top_solution_nmi_v_pval_rank,
    proc_path("mtbi_der_top_solution_nmi_v_pval_rank.csv", TRUE)
)
```

```{r}
# CHECKPOINT
mtbi_der_top_solution_nmi_v_pval_rank <- read_csv(
    proc_path("2025_05_27_mtbi_der_top_solution_nmi_v_pval_rank.csv")
)

options(width=200)
data.frame(mtbi_der_top_solution_nmi_v_pval_rank)
```

```{r}
# 2025-05-28
# Export input feature ranks
mtbi_der_top_solution_nmi_v_pval_rank |>
    dplyr::select(joint_rank, dplyr::everything()) |>
    dplyr::select(-nmi_rank, -pval_rank) |>
    knitr::kable(format = "markdown", digits = 4) |>
    writeLines(proc_path("mtbi_der_top_solution_ift_ranks.txt", TRUE))

# Input features
ifts <- mtbi_der_top_solution_nmi_v_pval_rank$"feature"

# Output features
ofts <- features(train_ol_u4)

# All features
afts <- c(ifts, ofts)

saveRDS(ifts, proc_path("ifts.rds", TRUE))
saveRDS(afts, proc_path("afts.rds", TRUE))
saveRDS(ofts, proc_path("ofts.rds", TRUE))
```

```{r}
# CHECKPOINT
ifts <- readRDS(proc_path("2025_05_28_ifts.rds"))
afts <- readRDS(proc_path("2025_05_28_afts.rds"))
ofts <- readRDS(proc_path("2025_05_28_ofts.rds"))
```

### Correlation of NMI and p-value

Checking association between the two feature importance ranking methods.

```{r}
nmi_v_p_rho <- cor(
    mtbi_der_top_solution_nmi_v_pval_rank$"nmi_rank",
    mtbi_der_top_solution_nmi_v_pval_rank$"pval_rank",
    method = "spearman"
)

nmi_v_pval_plot <- mtbi_der_top_solution_nmi_v_pval_rank |>
    ggplot(
        aes(x = nmi_rank, y = pval_rank, label = feature, colour = domain)
    ) +
    geom_point(size = 2) + 
    scale_colour_manual(
        values = c(
            "AS" = "#85929e",
            "D" = "#bb8fce",
            "N" = "#e59866",
            "MH" = "#7fb3d5",
            "P" = "#52be80"
        )
    ) +
    theme_bw() +
    labs(x = "Rank by NMI", y = "Rank by Association p-value") +
    ggrepel::geom_text_repel(
        force = 1,
        max.overlaps = 35,
        size = 4
    ) +
    annotate(
        "text",
        x = 4,
        y = 50,
        size = 5,
        label = paste("Spearman's ρ =", round(nmi_v_p_rho, 2)),
        hjust = 0
    ) + 
    theme(text = element_text(size = 20))
nmi_v_pval_plot

ggsave(
    fig_path("nmi_v_pval_plot.png", TRUE),
    nmi_v_pval_plot,
    width = 14,
    height = 12
)
```

```{r}
# Some file renaming
mtbi_der_top_solution_swp <- readRDS(
    proc_path("2025_05_27_mtbi_der_top_solution_swp.rds")
)

saveRDS(
    mtbi_der_top_solution_swp,
    proc_path("mtbi_der_solution.rds", TRUE)
)
```

```{r}
# CHECKPOINT 
mtbi_der_solution <- readRDS(proc_path("2025_05_28_mtbi_der_solution.rds"))
```

```{r}
# Feature plot generation
mtbi_der_plot_list <- auto_plot(
    sol_df_row = mtbi_der_solution,
    dl = c(train_dl_u4, train_ol_u4),
    save = fig_path("ap_mtbi_der_mc_f", TRUE),
    verbose = TRUE
)

# No save version:
mtbi_der_plot_list <- auto_plot(
    sol_df_row = mtbi_der_solution,
    dl = c(train_dl_u4, train_ol_u4),
    verbose = TRUE
)

saveRDS(mtbi_der_plot_list, fig_path("mtbi_der_plot_list.rds", TRUE))
```

```{r}
# CHECKPOINT
mtbi_der_plot_list <- readRDS(fig_path("2025_05_28_mtbi_der_plot_list.rds"))
```

### Visualizing top features

```{r}
mtbi_der_ranked_plot_list <- mtbi_der_plot_list[afts]

saveRDS(
    mtbi_der_ranked_plot_list,
    fig_path("mtbi_der_ranked_plot_list.rds", TRUE)
)

mtbi_der_ranked_plot_list <- readRDS(
    fig_path("2025_05_28_mtbi_der_ranked_plot_list.rds")
)

mtbi_der_ranked_plots <- wrap_plots(mtbi_der_ranked_plot_list)

ggsave(
    fig_path("mtbi_der_ranked_plots.png", TRUE),
    mtbi_der_ranked_plots,
    width = 45,
    height = 30,
    dpi = 50
)
```

```{r}
# Building a patchwork of the 20 plots

top_pl <- mtbi_der_ranked_plot_list[1:20]
for (i in seq_along(top_pl)) {
    print(paste0(i, ": ", names(top_pl)[i]))
}
top_pl$"sex"                    <- top_pl$"sex"                    + labs(fill = "Sex") + scale_fill_discrete(labels = c("F", "M"))
top_pl$"brain_volume"           <- top_pl$"brain_volume"           + labs(y = expression(paste("Brain Volume ", (mm^3))))
top_pl$"cortical_sa"            <- top_pl$"cortical_sa"            + labs(y = expression(paste("Cortical Area ", (mm^2))))
top_pl$"household_income"       <- top_pl$"household_income"       + labs(y = "Household Income")
top_pl$"race"                   <- top_pl$"race"                   + labs(fill = "Race") + scale_fill_discrete(labels = c("Black", "Hispanic", "Other", "White"))
top_pl$"pubertal_status_p"      <- top_pl$"pubertal_status_p"      + labs(y = "Pubertal Status\n(Parent Report)")
top_pl$"activities_last_year"   <- top_pl$"activities_last_year"   + labs(y = "Total Activities\nthis Year")
top_pl$"private_instruction"    <- top_pl$"private_instruction"    + labs(y = "Private Activities")
top_pl$"extracurriculars"       <- top_pl$"extracurriculars"       + labs(y = "Lifetime\nExtracurriculars")
top_pl$"parent_thought"         <- top_pl$"parent_thought"         + labs(y = "Parent Thought\nProblems")
top_pl$"parent_somatic"         <- top_pl$"parent_somatic"         + labs(y = "Parent Somatic\nProblems")
top_pl$"parent_antisocial"      <- top_pl$"parent_antisocial"      + labs(y = "Parent Antisocial\nProblems")
top_pl$"weekday_screentime"     <- top_pl$"weekday_screentime"     + labs(y = "Weekday Screentime")
top_pl$"fmri_cort_subcort_cors" <- top_pl$"fmri_cort_subcort_cors" + labs(y = "Cortical-Subcortical\nNetwork Correlation")
top_pl$"parent_avoidant"        <- top_pl$"parent_avoidant"        + labs(y = "Parent Avoidant\nProblems")
top_pl$"weekend_screentime"     <- top_pl$"weekend_screentime"     + labs(y = "Weekend\nScreentime")
top_pl$"fmri_cort_cors"         <- top_pl$"fmri_cort_cors"         + labs(y = "Cortical-Cortical\nNetwork Correlation")
top_pl$"parent_aggressive"      <- top_pl$"parent_aggressive"      + labs(y = "Parent Aggressive\nProblems")
top_pl$"parent_withdrawn"       <- top_pl$"parent_withdrawn"       + labs(y = "Parent Withdrawn\nProblems")
top_pl$"parent_anxdisord"       <- top_pl$"parent_anxdisord"       + labs(y = "Parent Anxiety\nProblems")
top_p <- (wrap_plots(top_pl) & labs(x = "Cluster") & theme(plot.margin = unit(c(0.5, 1.5, 0.5, 2), "cm"))) + plot_annotation(tag_levels = '1')
ggsave(
    fig_path("mtbi_der_solution_top_20_ifts.png", TRUE),
    top_p,
    width = 25,
    height = 15,
    dpi = 150
)
```

```{r}
# Data frame used to generate the auto plots
mtbi_der_solution_plot_df <- auto_plot(
    sol_df_row = mtbi_der_solution,
    dl = train_io_dl_u4,
    return_plots = FALSE
)

saveRDS(mtbi_der_solution_plot_df, proc_path("mtbi_der_solution_plot_df.rds", TRUE))
```

```{r}
# CHECKPOINT
mtbi_der_solution_plot_df <- readRDS(proc_path("2025_05_29_mtbi_der_solution_plot_df.rds"))
```

```{r}
ofts_pl <- mtbi_der_ranked_plot_list[ofts]

names(ofts_pl)

clean_names <- c(
    "CBCL\nAnxious-Depressed",
    "CBCL\nWithdrawn-Depressed",
    "CBCL\nSomatic Problems",
    "CBCL\nSocial Problems",
    "CBCL\nThought Problems",
    "CBCL\nAttention Problems",
    "CBCL\nRule-breaking Problems",
    "CBCL\nAggression Problems",
    "SDS Total\nSleeping Problems"
)

for (i in seq_along(ofts_pl)) {
    ofts_pl[[i]] <- ofts_pl[[i]] + labs(y = clean_names[[i]], x = "Cluster")
}

ofts_p <- wrap_plots(ofts_pl) &
          theme(plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), "cm"))

ofts_p <- ofts_p + plot_annotation(tag_levels = '1')

ggsave(
    fig_path("mtbi_der_solution_ofts.png", TRUE),
    ofts_p,
    width = 14,
    height = 14,
    dpi = 150
)
```

# Validation

```{r}
# CHECKPOINT
# The data list that generated the top solution

# The first test data set, for example
test_dl_u1 <- all_dls$"mtbi_test_data_lists"$"imp_1"
test_dl_u2 <- all_dls$"mtbi_test_data_lists"$"imp_2"
test_dl_u3 <- all_dls$"mtbi_test_data_lists"$"imp_3"
test_dl_u4 <- all_dls$"mtbi_test_data_lists"$"imp_4"
test_dl_u5 <- all_dls$"mtbi_test_data_lists"$"imp_5"

test_ol_u1 <- all_dls$"mtbi_test_oom_lists"$"imp_1"
test_ol_u2 <- all_dls$"mtbi_test_oom_lists"$"imp_2"
test_ol_u3 <- all_dls$"mtbi_test_oom_lists"$"imp_3"
test_ol_u4 <- all_dls$"mtbi_test_oom_lists"$"imp_4"
test_ol_u5 <- all_dls$"mtbi_test_oom_lists"$"imp_5"
```

```{r}
mtbi_dl_1 <- merge(train_dl_u4, test_dl_u1)
mtbi_dl_2 <- merge(train_dl_u4, test_dl_u2)
mtbi_dl_3 <- merge(train_dl_u4, test_dl_u3)
mtbi_dl_4 <- merge(train_dl_u4, test_dl_u4)
mtbi_dl_5 <- merge(train_dl_u4, test_dl_u5)

mtbi_ol_1 <- merge(train_ol_u4, test_ol_u1)
mtbi_ol_2 <- merge(train_ol_u4, test_ol_u2)
mtbi_ol_3 <- merge(train_ol_u4, test_ol_u3)
mtbi_ol_4 <- merge(train_ol_u4, test_ol_u4)
mtbi_ol_5 <- merge(train_ol_u4, test_ol_u5)

saveRDS(mtbi_dl_1, input_path("mtbi_dl_1.rds", TRUE))
saveRDS(mtbi_dl_2, input_path("mtbi_dl_2.rds", TRUE))
saveRDS(mtbi_dl_3, input_path("mtbi_dl_3.rds", TRUE))
saveRDS(mtbi_dl_4, input_path("mtbi_dl_4.rds", TRUE))
saveRDS(mtbi_dl_5, input_path("mtbi_dl_5.rds", TRUE))

saveRDS(mtbi_ol_1, input_path("mtbi_ol_1.rds", TRUE))
saveRDS(mtbi_ol_2, input_path("mtbi_ol_2.rds", TRUE))
saveRDS(mtbi_ol_3, input_path("mtbi_ol_3.rds", TRUE))
saveRDS(mtbi_ol_4, input_path("mtbi_ol_4.rds", TRUE))
saveRDS(mtbi_ol_5, input_path("mtbi_ol_5.rds", TRUE))
```

```{r}
# CHECKPOINT
mtbi_dl_1 <- readRDS(input_path("2025_05_29_mtbi_dl_1.rds"))
mtbi_dl_2 <- readRDS(input_path("2025_05_29_mtbi_dl_2.rds"))
mtbi_dl_3 <- readRDS(input_path("2025_05_29_mtbi_dl_3.rds"))
mtbi_dl_4 <- readRDS(input_path("2025_05_29_mtbi_dl_4.rds"))
mtbi_dl_5 <- readRDS(input_path("2025_05_29_mtbi_dl_5.rds"))

mtbi_ol_1 <- readRDS(input_path("2025_05_29_mtbi_ol_1.rds"))
mtbi_ol_2 <- readRDS(input_path("2025_05_29_mtbi_ol_2.rds"))
mtbi_ol_3 <- readRDS(input_path("2025_05_29_mtbi_ol_3.rds"))
mtbi_ol_4 <- readRDS(input_path("2025_05_29_mtbi_ol_4.rds"))
mtbi_ol_5 <- readRDS(input_path("2025_05_29_mtbi_ol_5.rds"))
```

```{r}
mtbi_config <- readRDS(proc_path("2025_05_27_mtbi_config.rds"))

progressr::with_progress({
    mtbi_sol_df <- batch_snf(
        dl = mtbi_dl_1,
        sc = mtbi_config,
        processes = "max"
    )
})

saveRDS(mtbi_sol_df, proc_path("mtbi_sol_df.rds", TRUE))

mtbi_sol_df <- readRDS(proc_path("2025_05_29_mtbi_sol_df.rds"))
```

```{r}
mtbi_ext_sol_df <- extend_solutions(
    mtbi_sol_df,
    dl = mtbi_dl_1,
    target_dl = mtbi_ol_1,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(mtbi_ext_sol_df, proc_path("mtbi_ext_sol_df.rds", TRUE))
```

```{r}
# CHECKPOINT
mtbi_ext_sol_df <- readRDS(proc_path("2025_05_29_mtbi_ext_sol_df.rds"))
```

```{r}
# Filtering down to only 3 cluster solutions
mtbi_ext_sol_df_3c <- mtbi_ext_sol_df |>
    dplyr::filter(nclust == 3)

saveRDS(mtbi_ext_sol_df_3c, proc_path("mtbi_ext_sol_df_3c.rds", TRUE))

mtbi_ext_sol_df_3c <- readRDS(proc_path("2025_05_29_mtbi_ext_sol_df_3c.rds"))

nrow(mtbi_ext_sol_df_3c) # 52 of them

mtbi_ari_3c <- calc_aris(mtbi_ext_sol_df_3c)

saveRDS(mtbi_ari_3c, proc_path("mtbi_ari_3c.rds", TRUE))
```

```{r}
# CHECKPOINT
mtbi_ext_sol_df_3c <- readRDS(proc_path("2025_05_29_mtbi_ext_sol_df_3c.rds"))
mtbi_ari_3c <- readRDS(proc_path("2025_05_29_mtbi_ari_3c.rds"))
mtbi_der_solution <- readRDS(proc_path("2025_05_28_mtbi_der_solution.rds"))
```

Here I identify the cluster solution from the derivation + validation samples that is the most similar to the derivation sample solution in terms of its distribution of derivation sample observations.

```{r}
mtbi_ari_order_3c <- get_matrix_order(mtbi_ari_3c)
mtbi_esdf_3c <- as.data.frame(mtbi_ext_sol_df_3c)

drop_subs <- function(ext_solutions_df, subjects) {
    ext_solutions_df[, !colnames(ext_solutions_df) %in% subjects]
}

mtbi_ext_sol_df_3c_der_subs <- drop_subs(
    mtbi_ext_sol_df_3c,
    paste0("uid_", mtbi_test_subs$"subjectkey")
)

der_and_new_aris <- rbind(
    mtbi_ext_sol_df_3c_der_subs,
    mtbi_der_solution
) |> 
    calc_aris()

validation_order <- sort(der_and_new_aris["776", ], index.return = TRUE)$"ix"

# 3 cluster solutions sorted 
validation_heatmap <- meta_cluster_heatmap(
    der_and_new_aris,
    order = validation_order,
    show_row_names = TRUE
)
validation_heatmap

save_heatmap(
    heatmap = validation_heatmap,
    path = fig_path("validation_heatmap.png", TRUE),
    width = 650,
    height = 550,
    res = 75
)

validation_heatmap

# 117 is the most similar solution to the top derivation set solution
mtbi_top_solution <- mtbi_ext_sol_df_3c[mtbi_ext_sol_df_3c$"solution" == 117, ]
mtbi_top_solution <- cluster_label_swap(mtbi_top_solution, 2, 3)
mtbi_top_solution <- cluster_label_swap(mtbi_top_solution, 1, 2)

saveRDS(mtbi_top_solution, proc_path("mtbi_top_solution.rds", TRUE))
```

```{r}
mtbi_top_solution <- readRDS(proc_path("2025_05_30_mtbi_top_solution.rds"))

mtbi_top_pl <- auto_plot(
    mtbi_top_solution,
    dl = c(mtbi_dl_1, mtbi_ol_1),
    verbose = TRUE
)

saveRDS(mtbi_top_pl, proc_path("mtbi_top_pl.rds", TRUE))

mtbi_top_pl <- readRDS(proc_path("2025_05_30_mtbi_top_pl.rds"))
```

```{r}

mtbi_top_solution$"mc" <- "Pooled"

mtbi_top_manhattan <- mc_manhattan_plot(
    mtbi_top_solution,
    dl = mtbi_dl_1,
    target_dl = mtbi_ol_1,
    domain_colours = c(
        "AS" = "#85929e",
        "D" = "#bb8fce",
        "N" = "#e59866",
        "MH" = "#7fb3d5",
        "P" = "#52be80",
        "S" = "#d98880",
        "B" = "#ff3131"
    )
)
mtbi_top_manhattan

ggsave(
    plot = mtbi_top_manhattan,
    filename = fig_path("mtbi_top_manhattan.png", TRUE),
    width = 18,
    height = 5,
    dpi = 120
)

mtbi_der_numerator <- mtbi_der_manhattan + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

mtbi_manhattan_der_and_pool <- mtbi_der_numerator / mtbi_top_manhattan

ggsave(
    plot = mtbi_manhattan_der_and_pool,
    filename = fig_path("mtbi_manhattan_der_and_pool.png", TRUE),
    width = 18,
    height = 8,
    dpi = 200
)
```

Checking to see if there are site effects:

```{r}
mtbi_site <- read_csv(input_path("2025_05_23_mtbi_site.csv"))
mtbi_site$"uid" <- paste0("uid_", mtbi_site$"subjectkey")
mtbi_top_pl_df <- auto_plot(
    mtbi_top_solution,
    dl = c(mtbi_dl_1, mtbi_ol_1),
    verbose = TRUE,
    return_plots = FALSE
) |> as.data.frame()
mtbi_top_pl_df_w_site <- dplyr::inner_join(
    mtbi_top_pl_df,
    mtbi_site,
    by = "uid"
)

mtbi_top_pl_df_w_site$"site_id" <- factor(mtbi_top_pl_df_w_site$"site_id")

# Demonstration that site is not a significant predictor of cluster membership
# using multinomial logistic regression of only 3 features
df <- mtbi_top_pl_df_w_site
covariates <- "sex + brain_volume + household_income"
formula_no_site <- as.formula(paste("cluster ~", covariates))
formula_with_site <- as.formula(paste("cluster ~", covariates, "+ site_id"))
mod_no_site <- multinom(formula_no_site, data = df)
mod_with_site <- multinom(formula_with_site, data = df)
anova(mod_no_site, mod_with_site, test = "Chisq")
```

Concordance between the derivation and full samples:

```{r}
mtbi_der_df <- auto_plot(
    mtbi_der_solution,
    dl = c(train_dl_u4, train_ol_u4),
    return_plots = FALSE
)

mtbi_ful_df <- auto_plot(
    mtbi_top_solution,
    dl = c(mtbi_dl_1, mtbi_ol_1),
    return_plots = FALSE
)

val_cluster_df <- mtbi_top_solution |>
    t() |>
    dplyr::rename(
        "cluster" = "s117"
    ) |>
    dplyr::filter(
        uid %in% paste0("uid_", mtbi_test_subs$"subjectkey")
    )

mtbi_val_df <- auto_plot(
    cluster_df = val_cluster_df,
    dl = c(test_dl_u1, test_ol_u1),
    return_plots = FALSE
)

saveRDS(mtbi_val_df, proc_path("mtbi_val_df.rds", TRUE))
saveRDS(mtbi_der_df, proc_path("mtbi_der_df.rds", TRUE))
saveRDS(mtbi_ful_df, proc_path("mtbi_ful_df.rds", TRUE))

mtbi_val_df <- readRDS(proc_path("2025_05_30_mtbi_val_df.rds"))
mtbi_der_df <- readRDS(proc_path("2025_05_30_mtbi_der_df.rds"))
mtbi_ful_df <- readRDS(proc_path("2025_05_30_mtbi_ful_df.rds"))
```

```{r}
# Regular plot lists:
mtbi_der_df_pl <- auto_plot(
    mtbi_der_solution,
    dl = c(train_dl_u4, train_ol_u4)
)
mtbi_ful_df_pl <- auto_plot(
    mtbi_top_solution,
    dl = c(mtbi_dl_1, mtbi_ol_1)
)
mtbi_val_df_pl <- auto_plot(
    cluster_df = val_cluster_df,
    dl = c(test_dl_u1, test_ol_u1)
)

saveRDS(mtbi_der_df_pl, proc_path("mtbi_der_df_pl.rds", TRUE))
saveRDS(mtbi_val_df_pl, proc_path("mtbi_val_df_pl.rds", TRUE))
saveRDS(mtbi_ful_df_pl, proc_path("mtbi_ful_df_pl.rds", TRUE))

mtbi_der_df_pl <- readRDS(proc_path("2025_06_03_mtbi_der_df_pl.rds"))
mtbi_val_df_pl <- readRDS(proc_path("2025_06_03_mtbi_val_df_pl.rds"))
mtbi_ful_df_pl <- readRDS(proc_path("2025_06_03_mtbi_ful_df_pl.rds"))
```

```{r}
source("abcd/helper_functions.R")

mtbi_val_tops <- topologizer(mtbi_val_df)
mtbi_der_tops <- topologizer(mtbi_der_df)
mtbi_ful_tops <- topologizer(mtbi_ful_df)

write_csv(mtbi_der_tops, proc_path("mtbi_der_tops.csv", TRUE))
write_csv(mtbi_ful_tops, proc_path("mtbi_ful_tops.csv", TRUE))
write_csv(mtbi_val_tops, proc_path("mtbi_val_tops.csv", TRUE))

```

```{r}
# CHECKPOINT
mtbi_der_tops <- read_csv(proc_path("2025_05_30_mtbi_der_tops.csv"))
mtbi_ful_tops <- read_csv(proc_path("2025_05_30_mtbi_ful_tops.csv"))
mtbi_val_tops <- read_csv(proc_path("2025_05_30_mtbi_val_tops.csv"))
```

```{r}
f_der_tops <- format_tops(mtbi_der_tops)
f_val_tops <- format_tops(mtbi_val_tops)
f_ful_tops <- format_tops(mtbi_ful_tops)

head(joint_ranks_with_out)

f_der_tops$"set" <- "D"
f_val_tops$"set" <- "V"
f_ful_tops$"set" <- "F"

all_tops <- do.call(rbind, list(f_der_tops, f_val_tops, f_ful_tops)) |>
    dplyr::rename("feature" = "Feature")

mtbi_der_top_solution_nmi_v_pval_rank <- read_csv(
    proc_path("2025_05_27_mtbi_der_top_solution_nmi_v_pval_rank.csv")
)

# Constructing a data frame of feature ranks that accounts for how
# mechanism and race were dummied
joint_ranks <- mtbi_der_top_solution_nmi_v_pval_rank |>
    data.frame() |>
    dplyr::select(feature, joint_rank)
joint_ranks <- rbind(
    joint_ranks,
    data.frame(
        feature = c("race_black", "race_white", "race_hispanic", "race_other"),
        joint_rank = joint_ranks[joint_ranks$"feature" == "race", "joint_rank"]
    )
)
joint_ranks <- rbind(
    joint_ranks,
    data.frame(
        feature = c(
            "mtbi_mechanism_fall_hit",
            "mtbi_mechanism_hosp_er",
            "mtbi_mechanism_multi",
            "mtbi_mechanism_other_loc",
            "mtbi_mechanism_vehicle",
            "mtbi_mechanism_violent"
        ),
        joint_rank = joint_ranks[joint_ranks$"feature" == "mtbi_mechanism", "joint_rank"]
    )
)
joint_ranks <- dplyr::filter(joint_ranks, !feature %in% c("mtbi_mechanism", "race"))
joint_ranks <- arrange(joint_ranks, joint_rank)
joint_ranks <- rbind(
    data.frame(feature = ofts, joint_rank = nrow(joint_ranks) + 1),
    joint_ranks
) |> data.frame()
joint_ranks

write_csv(joint_ranks, proc_path("joint_ranks.csv", TRUE))

joint_ranks <- read_csv(proc_path("2025_05_30_joint_ranks.csv"))

sorted_tops <- dplyr::full_join(all_tops, joint_ranks) |>
    dplyr::mutate(set = factor(set, levels = c("D", "V", "F"))) |>
    dplyr::arrange(joint_rank, feature, set)

write_csv(sorted_tops, proc_path("sorted_tops.csv", TRUE))

sorted_tops <- read_csv(proc_path("2025_05_30_sorted_tops.csv"))

knitr::kable(
    sorted_tops,
    format = "markdown",
    digits = 3, format.args = list(scientific = FALSE)
) |>
    writeLines(proc_path("mtbi_sorted_tops.txt", TRUE)) # 2025-05-30

mtbi_der_tops <- read_csv(proc_path("2025_05_30_mtbi_der_tops.csv"))
mtbi_ful_tops <- read_csv(proc_path("2025_05_30_mtbi_ful_tops.csv"))
mtbi_val_tops <- read_csv(proc_path("2025_05_30_mtbi_val_tops.csv"))

mtbi_der_tops$"set" <- "D"
mtbi_val_tops$"set" <- "V"
mtbi_ful_tops$"set" <- "F"

all_tops_raw <- do.call(
    rbind,
    list(mtbi_der_tops, mtbi_ful_tops, mtbi_val_tops)
)

all_der_tops_raw <- dplyr::full_join(
    joint_ranks,
    mtbi_der_tops,
    by = "feature"
)

all_val_tops_raw <- dplyr::full_join(
    joint_ranks,
    mtbi_val_tops,
    by = "feature"
)

all_ful_tops_raw <- dplyr::full_join(
    joint_ranks,
    mtbi_ful_tops,
    by = "feature"
)

all_tops_raw <- do.call(
    rbind,
    list(all_der_tops_raw, all_val_tops_raw, all_ful_tops_raw)
) |>
    dplyr::mutate(set = factor(set, levels = c("D", "V", "F"))) |>
    dplyr::arrange(joint_rank, feature, set)

all_tops_raw
```

Some of the 

```{r}
all_tops_raw_manual_adj <- all_tops_raw
all_tops_raw_manual_adj$"row" <- rownames(all_tops_raw_manual_adj)
# This entry has NA ES between C2 and C3 race_black, but both clusters are
# have 0 membership race_black membership
all_tops_raw_manual_adj[14, "c23_es"] <- 0
# Similar situation for mtbi mechanism multi
all_tops_raw_manual_adj[127, "c12_es"] <- 0
all_tops_raw_manual_adj[128, "c13_es"] <- 0
# Missing "V" set label
all_tops_raw_manual_adj[132, "set"] <- "V"
# mtbi mechanism other loc simply not present in V
all_tops_raw_manual_adj[132, c("c12_es", "c13_es", "c23_es")] <- 0
all_tops_raw_manual_adj[132, "es"] <- "or"
all_tops_raw_manual_adj[132, "summary"] <- "1 = 2 = 3"
# mtbi mechanism violent
all_tops_raw_manual_adj[137, "c13_es"] <- 0
all_tops_raw_manual_adj |>
    dplyr::select(-dplyr::contains("_l"), -dplyr::contains("_u")) |>
    dplyr::filter(dplyr::if_any(dplyr::everything(), is.na))

saveRDS(all_tops_raw_manual_adj, proc_path("all_tops_raw_manual_adj.rds", TRUE))
```

```{r}
all_tops_raw_manual_adj <- readRDS(proc_path("2025_05_30_all_tops_raw_manual_adj.rds"))

mtbi_gen_fts_table <- generalizable_features(all_tops_raw_manual_adj, compare_fn_a, 0.2)
saveRDS(mtbi_gen_fts_table, proc_path("mtbi_gen_fts_table.rds", TRUE))
```

```{r}
mtbi_gen_fts_table <- readRDS(proc_path("2025_05_30_mtbi_gen_fts_table.rds"))
mtbi_gen_fts_table
```

```{r}
mtbi_der_df_pl <- readRDS(proc_path("2025_06_03_mtbi_der_df_pl.rds"))
mtbi_val_df_pl <- readRDS(proc_path("2025_06_03_mtbi_val_df_pl.rds"))
mtbi_ful_df_pl <- readRDS(proc_path("2025_06_03_mtbi_ful_df_pl.rds"))

dvf_plots <- list(
    mtbi_der_df_pl[afts],
    mtbi_val_df_pl[afts],
    mtbi_ful_df_pl[afts]
)
```

```{r}
# image export helper function
quick_save <- function(plot, path, w = 12, h = 4, dpi = 300) {
    path <- paste0("mtbi_dvf_", path, ".png")
    ggsave(
        fig_path(path, TRUE),
        plot,
        width = w,
        height = h,
        dpi = dpi,
        limitsize = FALSE
    )
}
```

```{r}
# Not necessarily in ranked order:
activities_last_year_plot   <- tri_plot(dvf_plots, "activities_last_year",   "Programs Last\nYear (Quartile)") 
age_plot                    <- tri_plot(dvf_plots, "age",                    "Age") 
brain_volume_plot           <- tri_plot(dvf_plots, "brain_volume",           "Brain Volume\n(mm³)", ylims = c(900000, 1650000)) 
considerate_p_plot          <- tri_plot(dvf_plots, "considerate_p",          "Considerate\n(Parent Report)", c("No", "Yes")) 
considerate_y_plot          <- tri_plot(dvf_plots, "considerate_y",          "Considerate\n(Youth Report)", c("No", "Yes")) 
cort_sa_plot                <- tri_plot(dvf_plots, "cortical_sa",            "Cortical Surface\nArea (mm²)", ylims = c(140000, 260000)) 
cortical_thickness_plot     <- tri_plot(dvf_plots, "cortical_thickness",     "Cortical\nThickness (mm)", ylims = c(2.3, 3.1)) 
extracurriculars_plot       <- tri_plot(dvf_plots, "extracurriculars",       "Extracurriculars\n(Quartile)") 
family_angry_p_plot         <- tri_plot(dvf_plots, "family_angry_p",         "Family Angry\n(Parent Report)", c("No", "Yes")) 
family_angry_y_plot         <- tri_plot(dvf_plots, "family_angry_y",         "Family Angry\n(Youth Report)", c("No", "Yes")) 
family_criticize_p_plot     <- tri_plot(dvf_plots, "family_criticize_p",     "Family Criticizes\n(Parent Report)", c("No", "Yes")) 
family_criticize_y_plot     <- tri_plot(dvf_plots, "family_criticize_y",     "Family Criticizes\n(Youth Report)", c("No", "Yes")) 
family_fight_p_plot         <- tri_plot(dvf_plots, "family_fight_p",         "Family Fights\n(Parent Report)", scale_fill_labels = c("No", "Yes")) 
family_fight_y_plot         <- tri_plot(dvf_plots, "family_fight_y",         "Family Fights\n(Youth Report)", c("No", "Yes")) 
family_hit_p_plot           <- tri_plot(dvf_plots, "family_hit_p",           "Family Hitting\n(Parent Report)", c("No", "Yes")) 
family_hit_y_plot           <- tri_plot(dvf_plots, "family_hit_y",           "Family Hitting\n(Youth Report)", c("No", "Yes")) 
family_outdo_p_plot         <- tri_plot(dvf_plots, "family_outdo_p",         "Family Outdo\n(Parent Report)", c("No", "Yes")) 
family_outdo_y_plot         <- tri_plot(dvf_plots, "family_outdo_y",         "Family Outdoing\n(Youth Report)", c("No", "Yes")) 
family_peaceful_p_plot      <- tri_plot(dvf_plots, "family_peaceful_p",      "Family Peaceful\n(Parent Report)", c("No", "Yes")) 
family_peaceful_y_plot      <- tri_plot(dvf_plots, "family_peaceful_y",      "Family Peaceful\n(Youth Report)", c("No", "Yes")) 
family_temper_p_plot        <- tri_plot(dvf_plots, "family_temper_p",        "Family Temper\n(Parent Report)", scale_fill_labels = c("No", "Yes")) 
family_temper_y_plot        <- tri_plot(dvf_plots, "family_temper_y",        "Family Temper\n(Youth Report)", c("No", "Yes")) 
family_throw_p_plot         <- tri_plot(dvf_plots, "family_throw_p",         "Family Throwing\n(Parent Report)", c("No", "Yes")) 
family_throw_y_plot         <- tri_plot(dvf_plots, "family_throw_y",         "Family Throwing\n(Youth Report)", c("No", "Yes")) 
family_yell_p_plot          <- tri_plot(dvf_plots, "family_yell_p",          "Family Yells\n(Parent Report)", c("No", "Yes")) 
family_yell_y_plot          <- tri_plot(dvf_plots, "family_yell_y",          "Family Yells\n(Youth Report)", c("No", "Yes")) 
fmri_cort_cors_plot         <- tri_plot(dvf_plots, "fmri_cort_cors",         "fMRI Cort-\nCort Corrs", ylims = c(-0.1, 0.16)) 
fmri_cort_subcort_cors_plot <- tri_plot(dvf_plots, "fmri_cort_subcort_cors", "fMRI Cort-\nSubcort Corrs", ylims = c(-0.15, 0.2)) 
headache_history_plot       <- tri_plot(dvf_plots, "headache_history",       "Headache\nHistory", c("No", "Yes")) 
helpful_p_plot              <- tri_plot(dvf_plots, "helpful_p",              "Helpful\n(Parent Report)", c("No", "Yes")) 
helpful_y_plot              <- tri_plot(dvf_plots, "helpful_y",              "Helpful\n(Youth Report)", c("No", "Yes")) 
helps_hurt_p_plot           <- tri_plot(dvf_plots, "helps_hurt_p",           "Helps Hurt\n(Parent Report)", c("No", "Yes")) 
helps_hurt_y_plot           <- tri_plot(dvf_plots, "helps_hurt_y",           "Helps Hurt\n(Youth Report)", c("No", "Yes")) 
household_income_plot       <- tri_plot(dvf_plots, "household_income",       "Household Income") 
major_wm_ndi_plot           <- tri_plot(dvf_plots, "major_wm_ndi",           "Major WM\nNeurite Density", ylims = c(0.45, 0.85)) 
mtbi_age_plot               <- tri_plot(dvf_plots, "mtbi_age",               "mTBI Age\n(months)") 
mtbi_loc_plot               <- tri_plot(dvf_plots, "mtbi_loc",               "mTBI LOC", c("No", "Yes")) 
mtbi_mechanism_plot         <- tri_plot(dvf_plots, "mtbi_mechanism",         "mTBI Mechanism", c("Fall/Hit", "Hospital/ER", "Multiple Injuries", "Other", "Vehicle", "Violent")) 
mtbi_mem_daze_plot          <- tri_plot(dvf_plots, "mtbi_mem_daze",          "mTBI mem_daze", c("No", "Yes")) 
opp_sex_close_friend_plot   <- tri_plot(dvf_plots, "opp_sex_close_friend",   "Opposite-Sex\nClose Friends (Quartile)") 
opp_sex_friend_plot         <- tri_plot(dvf_plots, "opp_sex_friend",         "Opposite-Sex\nFriends (Quartile)") 
parent_aggressive_plot      <- tri_plot(dvf_plots, "parent_aggressive",      "Parent\nAggressive", ylims = c(-0.5, 25)) 
parent_antisocial_plot      <- tri_plot(dvf_plots, "parent_antisocial",      "Parent\nAntisocial", ylims = c(-0.5, 20)) 
parent_anxdep_plot          <- tri_plot(dvf_plots, "parent_anxdep",          "Parent\nAnxious-Depressed", ylims = c(-0.5, 30)) 
parent_anxdisord_plot       <- tri_plot(dvf_plots, "parent_anxdisord",       "Parent\nAnxious", ylims = c(-0.5, 13)) 
parent_attention_plot       <- tri_plot(dvf_plots, "parent_attention",       "Parent Attention", ylims = c(-0.5, 25)) 
parent_avoidant_plot        <- tri_plot(dvf_plots, "parent_avoidant",        "Parent\nAvoidant", ylims = c(-0.5, 13)) 
parent_depress_plot         <- tri_plot(dvf_plots, "parent_depress",         "Parent\nDepress", ylims = c(-0.5, 25)) 
parent_hyperactive_plot     <- tri_plot(dvf_plots, "parent_hyperactive",     "Parent\nHyperactive", ylims = c(-0.5, 12)) 
parent_intrusive_plot       <- tri_plot(dvf_plots, "parent_intrusive",       "Parent Intrusive", ylims = c(-0.5, 12)) 
parent_perstr_plot          <- tri_plot(dvf_plots, "parent_perstr",          "Parent\nPersonal Strength") 
parent_somatic_plot         <- tri_plot(dvf_plots, "parent_somatic",         "Parent\nSomatic", ylims = c(-0.5, 25)) 
parent_thought_plot         <- tri_plot(dvf_plots, "parent_thought",         "Parent\nThought", ylims = c(-0.5, 13.5)) 
parent_withdrawn_plot       <- tri_plot(dvf_plots, "parent_withdrawn",       "Parent\nWithdrawn", ylims = c(-0.5, 17)) 
pericortical_wm_ndi_plot    <- tri_plot(dvf_plots, "pericortical_wm_ndi",    "Pericortical WM\nNeurite Density", ylims = c(0.25, 0.6)) 
physical_activity_plot      <- tri_plot(dvf_plots, "physical_activity",      "Physical Activity", ylims = c(0, 1.1)) 
previous_mtbis_plot         <- tri_plot(dvf_plots, "previous_mtbis",         "Previous mTBIs") 
private_instruction_plot    <- tri_plot(dvf_plots, "private_instruction",    "Private Activities\n(Quartile)") 
pubertal_status_p_plot      <- tri_plot(dvf_plots, "pubertal_status_p",      "Pubertal Status\n(Parent Report)") 
pubertal_status_y_plot      <- tri_plot(dvf_plots, "pubertal_status_y",      "Pubertal Status\n(Youth Report)") 
race_plot                   <- tri_plot(dvf_plots, "race",                   "Race", scale_fill_labels = c("Black", "Hispanic", "Other", "White")) 
same_sex_close_friend_plot  <- tri_plot(dvf_plots, "same_sex_close_friend",  "Same-Sex Close\nFriends (Quartile)") 
same_sex_friend_plot        <- tri_plot(dvf_plots, "same_sex_friend",        "Same-Sex Friends\n(Quartile)") 
school_activities_plot      <- tri_plot(dvf_plots, "school_activities",      "School Activities") 
sex_plot                    <- tri_plot(dvf_plots, "sex",                    "Sex", c("F", "M")) 
weekday_screentime_plot     <- tri_plot(dvf_plots, "weekday_screentime",     "Weekday\nScreentime (hours)", ylims = c(-0.5, 21)) 
weekend_screentime_plot     <- tri_plot(dvf_plots, "weekend_screentime",     "Weekend\nScreentime (hours)", ylims = c(-0.5, 21)) 
# Outcome trip-plots
cbcl_anxdep_plot            <- tri_plot(dvf_plots, "cbcl_anxdep",            "Anxious-\nDepressed", ylims = c(-0.5, 30))
cbcl_withdep_plot           <- tri_plot(dvf_plots, "cbcl_withdep",           "Withdrawn-\nDepressed", ylims = c(-0.5, 15))
cbcl_somatic_plot           <- tri_plot(dvf_plots, "cbcl_somatic",           "Somatic", ylims = c(-0.5, 17))
cbcl_social_plot            <- tri_plot(dvf_plots, "cbcl_social",            "Social", ylims = c(-0.5, 20))
cbcl_thought_plot           <- tri_plot(dvf_plots, "cbcl_thought",           "Thought", ylims = c(-0.5, 20))
cbcl_attention_plot         <- tri_plot(dvf_plots, "cbcl_attention",         "Attention", ylims = c(-0.5, 22))
cbcl_rulebreak_plot         <- tri_plot(dvf_plots, "cbcl_rulebreak",         "Rule-Breaking", ylims = c(-0.5, 22))
cbcl_aggressive_plot        <- tri_plot(dvf_plots, "cbcl_aggressive",        "Aggression", ylims = c(-0.5, 32))
sds_sleep_plot              <- tri_plot(dvf_plots, "sds_sleep",              "Total Sleep\nProblems", ylims = c(20, 100))
#

generalizing_plots <- list(
    "activities_last_year"   = activities_last_year_plot,
    "age"                    = age_plot,
    "brain_volume"           = brain_volume_plot,
    "cbcl_aggressive"        = cbcl_aggressive_plot,
    "cbcl_anxdep"            = cbcl_anxdep_plot,
    "cbcl_attention"         = cbcl_attention_plot,
    "cbcl_rulebreak"         = cbcl_rulebreak_plot,
    "cbcl_social"            = cbcl_social_plot,
    "cbcl_somatic"           = cbcl_somatic_plot,
    "cbcl_thought"           = cbcl_thought_plot,
    "cbcl_withdep"           = cbcl_withdep_plot,
    "considerate_p"          = considerate_p_plot,
    "considerate_y"          = considerate_y_plot,
    "cortical_sa"            = cort_sa_plot,
    "cortical_thickness"     = cortical_thickness_plot,
    "extracurriculars"       = extracurriculars_plot,
    "family_angry_p"         = family_angry_p_plot,
    "family_angry_y"         = family_angry_y_plot,
    "family_criticize_p"     = family_criticize_p_plot,
    "family_criticize_y"     = family_criticize_y_plot,
    "family_fight_p"         = family_fight_p_plot,
    "family_fight_y"         = family_fight_y_plot,
    "family_hit_p"           = family_hit_p_plot,
    "family_hit_y"           = family_hit_y_plot,
    "family_outdo_p"         = family_outdo_p_plot,
    "family_outdo_y"         = family_outdo_y_plot,
    "family_peaceful_p"      = family_peaceful_p_plot,
    "family_peaceful_y"      = family_peaceful_y_plot,
    "family_temper_p"        = family_temper_p_plot,
    "family_temper_y"        = family_temper_y_plot,
    "family_throw_p"         = family_throw_p_plot,
    "family_throw_y"         = family_throw_y_plot,
    "family_yell_p"          = family_yell_p_plot,
    "family_yell_y"          = family_yell_y_plot,
    "fmri_cort_cors"         = fmri_cort_cors_plot,
    "fmri_cort_subcort_cors" = fmri_cort_subcort_cors_plot,
    "headache_history"       = headache_history_plot,
    "helpful_p"              = helpful_p_plot,
    "helpful_y"              = helpful_y_plot,
    "helps_hurt_p"           = helps_hurt_p_plot,
    "helps_hurt_y"           = helps_hurt_y_plot,
    "household_income"       = household_income_plot,
    "major_wm_ndi"           = major_wm_ndi_plot,
    "mtbi_age"               = mtbi_age_plot,
    "mtbi_loc"               = mtbi_loc_plot,
    "mtbi_mechanism"         = mtbi_mechanism_plot,
    "mtbi_mem_daze"          = mtbi_mem_daze_plot,
    "opp_sex_close_friend"   = opp_sex_close_friend_plot,
    "opp_sex_friend"         = opp_sex_friend_plot,
    "parent_aggressive"      = parent_aggressive_plot,
    "parent_antisocial"      = parent_antisocial_plot,
    "parent_anxdep"          = parent_anxdep_plot,
    "parent_anxdisord"       = parent_anxdisord_plot,
    "parent_attention"       = parent_attention_plot,
    "parent_avoidant"        = parent_avoidant_plot,
    "parent_depress"         = parent_depress_plot,
    "parent_hyperactive"     = parent_hyperactive_plot,
    "parent_intrusive"       = parent_intrusive_plot,
    "parent_perstr"          = parent_perstr_plot,
    "parent_somatic"         = parent_somatic_plot,
    "parent_thought"         = parent_thought_plot,
    "parent_withdrawn"       = parent_withdrawn_plot,
    "pericortical_wm_ndi"    = pericortical_wm_ndi_plot,
    "physical_activity"      = physical_activity_plot,
    "previous_mtbis"         = previous_mtbis_plot,
    "private_instruction"    = private_instruction_plot,
    "pubertal_status_p"      = pubertal_status_p_plot,
    "pubertal_status_y"      = pubertal_status_y_plot,
    "race"                   = race_plot,
    "same_sex_close_friend"  = same_sex_close_friend_plot,
    "same_sex_friend"        = same_sex_friend_plot,
    "school_activities"      = school_activities_plot,
    "sds_sleep"              = sds_sleep_plot,
    "sex"                    = sex_plot,
    "weekday_screentime"     = weekday_screentime_plot,
    "weekend_screentime"     = weekend_screentime_plot
) |> lapply(
    function(x) {
        x[[1]] <- x[[1]] + theme(axis.title.x = element_blank()) 
        x[[2]] <- x[[2]] + theme(axis.title.x = element_blank()) 
        x[[3]] <- x[[3]] + theme(axis.title.x = element_blank()) 
        return(x)
    }
)

iplots <- generalizing_plots[ifts]
oplots <- generalizing_plots[ofts]
#

saveRDS(iplots, proc_path("mtbi_iplots.rds", TRUE))
saveRDS(oplots, proc_path("mtbi_oplots.rds", TRUE))
iplots <- readRDS(proc_path("2025_06_10_mtbi_iplots.rds"))
oplots <- readRDS(proc_path("2025_06_10_mtbi_oplots.rds"))

wp_1 <- wrap_plots(iplots[1:10], ncol = 1)
quick_save(wp_1, "wp_1", w = 8, h = 20, dpi = 100)
wp_2 <- wrap_plots(iplots[11:20], ncol = 1)
quick_save(wp_2, "wp_2", w = 5.5, h = 20, dpi = 100)
wp_3 <- wrap_plots(iplots[21:30], ncol = 1)
quick_save(wp_3, "wp_3", w = 8, h = 20, dpi = 100)
wp_4 <- wrap_plots(iplots[31:40], ncol = 1)
quick_save(wp_4, "wp_4", w = 8, h = 20, dpi = 100)
wp_5 <- wrap_plots(iplots[41:50], ncol = 1)
quick_save(wp_5, "wp_5", w = 8, h = 20, dpi = 100)
wp_6 <- wrap_plots(iplots[51:60], ncol = 1)
quick_save(wp_6, "wp_6", w = 8, h = 20, dpi = 100)
wp_7 <- wrap_plots(iplots[61:67], ncol = 1)
quick_save(wp_7, "wp_7", w = 8, h = 14, dpi = 100)

wp_o <- wrap_plots(oplots, ncol = 1)
quick_save(wp_o, "wp_o", w = 5.5, h = 18)
```

# Summary of the validation (table)

```{r}
mtbi_gen_fts_table <- readRDS(proc_path("2025_05_30_mtbi_gen_fts_table.rds"))
rownames(mtbi_gen_fts_table) <- mtbi_gen_fts_table$"feature"

mtbi_gen_fts_table

mtbi_gen_fts_table_hits <- mtbi_gen_fts_table[afts, ] |>
    dplyr::filter(
        c1v2 %in% c(">", "<") | c1v3 %in% c(">", "<") | c2v3 %in% c(">", "<")
    )
mtbi_gen_fts_table_hits

write_csv(mtbi_gen_fts_table_hits, proc_path("mtbi_gen_fts_table_hits.csv", TRUE))
```

```{r}
mtbi_gen_fts_table_hits <- read_csv(proc_path("2025_06_03_mtbi_gen_fts_table_hits.csv"))

mtbi_gen_fts_table_hits

mtbi_gen_fts_table_hits_t <- mtbi_gen_fts_table_hits |>
    pivot_longer(
        cols = -feature,
        names_to = "comparison",
        values_to = "order"
    )

write_csv(mtbi_gen_fts_table_hits_t, proc_path("mtbi_gen_fts_table_hits_t.csv", TRUE))

mtbi_gen_fts_table_hits_t <- read_csv(proc_path("2025_06_03_mtbi_gen_fts_table_hits_t.csv"))

mtbi_gen_fts_table_hits_t |>
    knitr::kable(format = "markdown", align = "lccc") |>
    writeLines(proc_path("mtbi_gen_fts_table_hits_t.txt", TRUE))

mtbi_gen_fts_table_hits |>
    knitr::kable(format = "markdown", align = "lccc") |>
    writeLines(proc_path("mtbi_gen_fts_table_hits.txt", TRUE))
```

## How would the process go in demographic adjusted data?

The outcomes (and inputs) appear heavily associated with demographic variables pubertal status, sex, income, and race.
How would correcting for those variables influence the meta clustering results?

```{r}
mtbi_dl_1 <- readRDS(input_path("2025_05_29_mtbi_dl_1.rds"))
mtbi_ol_1 <- readRDS(input_path("2025_05_29_mtbi_ol_1.rds"))

# excluding mTBI mechanism from analysis, as it is an unadjustable categorical
# feature
dl_no_demo <- mtbi_dl_1[-c(2, 4, 6:9)] 
dl_demo <- mtbi_dl_1[c(4, 6:9)]

saveRDS(dl_demo, proc_path("dl_demo.rds", TRUE))
saveRDS(dl_no_demo, proc_path("dl_no_demo.rds", TRUE))

dl_demo <- readRDS(proc_path("2025_06_06_dl_demo.rds"))
dl_no_demo <- readRDS(proc_path("2025_06_06_dl_no_demo.rds"))

dl_demo

dl_corrected <- linear_adjust(dl_no_demo, dl_demo)

saveRDS(dl_corrected, proc_path("dl_corrected.rds", TRUE))
```

```{r}
# CHECKPOINT
dl_corrected <- readRDS(proc_path("2025_06_03_dl_corrected.rds"))

names(dl_corrected)

as.data.frame(c(dl_corrected, dl_demo)) |>
    ggplot(aes(x = sex, y = mtbi_mem_daze)) +
    geom_point() +
    geom_smooth(method = "lm", se = FALSE)

as.data.frame(c(dl_corrected, dl_demo)) |>
    ggplot(aes(x = sex, y = brain_volume)) +
    geom_point() +
    geom_smooth(method = "lm", se = FALSE) +
    theme_bw()
```

```{r}
set.seed(42)
corrected_config <- snf_config(
    dl_corrected,
    n_solutions = 400,
    cnt_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    dsc_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ord_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    use_default_dist_fns = TRUE
)

saveRDS(corrected_config, proc_path("corrected_config.rds", TRUE))

corrected_config <- readRDS(proc_path("2025_06_03_corrected_config.rds"))

c(dl_corrected, dl_demo) |>
    as.data.frame() |>
    dummy_cols(
        select_columns = c("race", "mtbi_mechanism"),
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = FALSE
    ) |>
    dplyr::select(-"uid") |>
    dplyr::relocate(
        "race_white",
        "race_black",
        "race_hispanic",
        "race_other",
        "age",
        "pubertal_status_p",
        "pubertal_status_y",
        "household_income",
        "sex",
        .after = last_col()
    ) |>
    cor() |>
    Heatmap(cluster_rows = FALSE, cluster_columns = FALSE)
```


```{r}
# CHECKPOINT
dl_corrected <- readRDS(proc_path("2025_06_03_dl_corrected.rds"))
corrected_config <- readRDS(proc_path("2025_06_03_corrected_config.rds"))
```

Meta clustering using the demographic adjusted data list.

```{r}
# HERE 2025-06-03
progressr::with_progress({
demo_adj_sol_df <- batch_snf(
    dl = dl_corrected,
    sc = corrected_config,
    processes = "max"
)
})
saveRDS(demo_adj_sol_df, proc_path("demo_adj_sol_df.rds", TRUE))
```

```{r}
# CHECKPOINT
demo_adj_sol_df <- readRDS(proc_path("2025_06_03_demo_adj_sol_df.rds"))
demo_adj_ari <- calc_aris(demo_adj_sol_df, verbose = TRUE, processes = "max")
saveRDS(demo_adj_ari, proc_path("demo_adj_ari.rds", TRUE))
```

```{r}
demo_adj_ari_order <- get_matrix_order(demo_adj_ari)
saveRDS(demo_adj_ari_order, proc_path("demo_adj_ari_order.rds", TRUE))
```

```{r}
# CHECKPOINT
demo_adj_sol_df <- readRDS(proc_path("2025_06_03_demo_adj_sol_df.rds"))
demo_adj_ari <- readRDS(proc_path("2025_06_03_demo_adj_ari.rds"))
demo_adj_ari_order <- readRDS(proc_path("2025_06_06_demo_adj_ari_order.rds"))
```

Creating a demographic adjusted outcome list to extend against.

```{r}
adj_oom_list <- linear_adjust(mtbi_ol_1, dl_demo)
saveRDS(adj_oom_list, proc_path("adj_oom_list.rds", TRUE))
```

```{r}
adj_oom_list <- readRDS(proc_path("2025_06_06_adj_oom_list.rds"))
```

```{r}
# Extend solutions from adjusted inputs to adjusted outcomes
demo_double_adj_ext_sol_df <- extend_solutions(
    demo_adj_sol_df,
    dl = dl_corrected,
    target_dl = adj_oom_list,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(demo_double_adj_ext_sol_df, proc_path("demo_double_adj_ext_sol_df.rds", TRUE))
```

```{r}
demo_adj_ext_sol_df <- readRDS(proc_path("2025_06_06_demo_adj_ext_sol_df.rds"))
demo_double_adj_ext_sol_df <- readRDS(proc_path("2025_06_06_demo_double_adj_ext_sol_df.rds"))

base_adj_ari_hm <- meta_cluster_heatmap(
    demo_adj_ari,
    order = demo_adj_ari_order
)

demo_adj_esdf <- as.data.frame(demo_adj_ext_sol_df)
demo_adj_esdf$"impairment_separation" <- -log10(demo_adj_esdf$"mean_pval")

demo_double_adj_esdf <- as.data.frame(demo_double_adj_ext_sol_df)
demo_double_adj_esdf$"impairment_separation" <- -log10(demo_double_adj_esdf$"mean_pval")

demo_adj_split_vec <- c(
    17,
    82,
    133,
    189,
    244
)
saveRDS(demo_adj_split_vec, proc_path("demo_adj_split_vec.rds", TRUE))
demo_adj_split_vec <- readRDS(proc_path("2025_06_06_demo_adj_split_vec.rds"))

# The double adjustment does not yield and interesting meta clusters
full_demo_double_adj_ari_hm <- meta_cluster_heatmap(
    x = demo_adj_ari,
    order = demo_adj_ari_order,
    data = demo_double_adj_esdf,
    min_colour = "black",
    split_vector = demo_adj_split_vec,
    top_hm = list(
        "Impairment Separation" = "impairment_separation"
    ),
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    annotation_colours = list(
        "Impairment Separation" = colour_scale(
            # Using the separation scale of the original derivation clustering
            mtbi_der_esdf$"impairment_separation",
            min_colour = "gray7",
            max_colour = "limegreen"
        )
    )
)
full_demo_double_adj_ari_hm

save_heatmap(
    heatmap = full_demo_double_adj_ari_hm,
    path = fig_path("full_demo_double_adj_ari_hm.png", TRUE),
    width = 950,
    height = 700,
    res = 100
)

double_demo_adj_mc_sol_df <- label_meta_clusters(
    demo_double_adj_ext_sol_df,
    order = demo_adj_ari_order,
    split_vector = demo_adj_split_vec
)

double_demo_adj_rep_solutions <- get_representative_solutions(
    demo_adj_ari,
    double_demo_adj_mc_sol_df
)

double_demo_adj_rep_solutions$"mean_pval" # The lowest mean p-value is 0.06
```
