# Initial correlations

In this chapter, I generate heatmaps to visit some of the broad correlations between data being used for this subtyping analysis.

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subjects <- read_csv(sub_path("2023_11_07_mtbi_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2023_11_07_uninjured_subjects.csv"))
matched_uninjured <- read_csv(sub_path("2024_01_15_matched_uninjured.csv"))
```

## Utility functions

```{r}
divergent_colours <- function(column)  {
    values <- unique(column)
    colours <- RColorBrewer::brewer.pal(n = length(values), name = "Set3")
    names(colours) <- values
    return(colours)
}

data_list_metadata <- function(data_list) {
    merged_df <- metasnf::collapse_dl(data_list)
    merged_df <- merged_df[, colnames(merged_df) != "subjectkey"]
    ###########################################################################
    # Build data.frame containing the types of variables in merged_df
    ###########################################################################
    types <- data_list |>
        lapply(
            function(x) {
                rep(x$"type", ncol(x$"data") - 1)
            }
        ) |>
        unlist()
    domains <- data_list |>
        lapply(
            function(x) {
                rep(x$"domain", ncol(x$"data") - 1)
            }
        ) |>
        unlist()
    var_names <- colnames(merged_df[, colnames(merged_df) != "subjectkey"])
    metadata <- data.frame(
        name = var_names,
        type = types,
        domain = domains
    )
    return(metadata)
}

keep_numeric <- function(df) {
    df <- metasnf::numcol_to_numeric(df)
    classes <- as.vector(sapply(df, class))
    df <- df[, classes == "numeric", drop = FALSE]
    return(df)
}

hm_colours <- function(data, max_red = TRUE) {
    if (max_red) {
        colours <- circlize::colorRamp2(
            c(min(data), max(data)),
            c("black", "red")
        )
    } else {
        colours <- circlize::colorRamp2(
            c(min(data), max(data)),
            c("red", "black")
        )
    }
    return(colours)
}

correlation_data <- function(data_list, order = NULL) {
    dl_df <- metasnf::collapse_dl(data_list)
    numeric_dl_df <- keep_numeric(dl_df)
    correlation_matrix <- cor(numeric_dl_df)
    if (is.null(order)) {
        heatmap <- ComplexHeatmap::Heatmap(
            correlation_matrix,
            heatmap_legend_param = list(
                title = "Corr"
            )
        )
    } else {
        heatmap <- ComplexHeatmap::Heatmap(
            correlation_matrix[order, order],
            cluster_rows = FALSE,
            cluster_columns = FALSE,
            heatmap_legend_param = list(
                title = "Corr"
            )
        )
    }
    drawn_heatmap <- ComplexHeatmap::draw(heatmap)
    order <- ComplexHeatmap::row_order(drawn_heatmap)
    results <- list(
        "correlation_matrix" = correlation_matrix,
        "heatmap" = heatmap,
        "order" = order
    )
    return(results)
}

pval_select <- function(extended_solutions_matrix,
                        keep_summary = TRUE,
                        negative_log = FALSE,
                        recalculate_summary = TRUE) {
    pval_df <- extended_solutions_matrix |>
        dplyr::select(
            "row_id",
            dplyr::ends_with("_p"),
            dplyr::contains("p_val")
        ) |>
        data.frame() |>
        metasnf::numcol_to_numeric()
    if (!keep_summary) {
        pval_df <- pval_df |>
            dplyr::select(-c("min_p_val", "mean_p_val"))
    }
    if (negative_log) {
        neg_log_pval_df <- -log(pval_df)
        neg_log_pval_df$"row_id" <- pval_df$"row_id"
        pval_df <- neg_log_pval_df
        if (recalculate_summary) {
            mini_df <- pval_df |> dplyr::select(
                dplyr::ends_with("_p")
            )
            pval_df$"mean_neglog_p" <- apply(mini_df, 1, FUN = mean)
            pval_df$"max_neglog_p" <- apply(mini_df, 1, FUN = max)
        }
    }
    return(pval_df)
}

pval_heatmap <- function(pval_df, order, max_red = FALSE) {
    pval_df <- pval_df |> dplyr::select(-"row_id")
    pval_matrix <- as.matrix(pval_df[order, ])
    hm <- ComplexHeatmap::Heatmap(
        pval_matrix,
        cluster_rows = FALSE,
        cluster_columns = FALSE,
        show_row_names = FALSE,
        col = hm_colours(pval_matrix, max_red)
    )
    return(hm)
}

split_at <- function(vector, nrow) {
    split_vec <- rep("A", nrow)
    if (vector[length(vector)] != nrow) {
        vector <- c(vector, nrow)
    }
    for (i in 1:(length(vector) - 1)) {
        start <- vector[i]
        end <- vector[i + 1]
        split_vec[start:end] <- LETTERS[i + 1]
    }
    return(split_vec)
}

save_pdf <- function(heatmap, path, width, height) {
    grDevices::pdf(
        path,
        width,
        height
    )
    heatmap
    grDevices::dev.off()
}

save_png <- function(heatmap, path, width, height, res = 300) {
    tryCatch(
        {
            grDevices::png(
                filename = path,
                width = width,
                height = height,
                res = res
            )
            ComplexHeatmap::draw(heatmap)
            grDevices::dev.off()
        }, error = function(err) {
            message("Error saving png - does the heatmap exist?")
            grDevices::dev.off()
        }
    )
}

read_matrix <- function(path) {
    mat <- read_csv(path, col_names = TRUE) |> as.matrix()
    rownames(mat) <- mat[, 1]
    mat <- mat[, -1]
    mat <- mat |>
        data.frame() |>
        numcol_to_numeric() |>
        as.matrix()
    return(mat)
}
```

## Loading data and out of model lists

```{r}
data_list_m1 <- list.load(input_path("2024_01_15_data_list_m1.rds"))
data_list_m2 <- list.load(input_path("2024_01_15_data_list_m2.rds"))
data_list_m3 <- list.load(input_path("2024_01_15_data_list_m3.rds"))
data_list_m4 <- list.load(input_path("2024_01_15_data_list_m4.rds"))
data_list_m5 <- list.load(input_path("2024_01_15_data_list_m5.rds"))
data_list_pm1 <- list.load(input_path("2024_01_15_data_list_pm1.rds"))
data_list_pm2 <- list.load(input_path("2024_01_15_data_list_pm2.rds"))
data_list_pm3 <- list.load(input_path("2024_01_15_data_list_pm3.rds"))
data_list_pm4 <- list.load(input_path("2024_01_15_data_list_pm4.rds"))
data_list_pm5 <- list.load(input_path("2024_01_15_data_list_pm5.rds"))

oom_list_m1 <- list.load(input_path("2024_01_24_oom_list_m1.rds"))
oom_list_m2 <- list.load(input_path("2024_01_24_oom_list_m2.rds"))
oom_list_m3 <- list.load(input_path("2024_01_24_oom_list_m3.rds"))
oom_list_m4 <- list.load(input_path("2024_01_24_oom_list_m4.rds"))
oom_list_m5 <- list.load(input_path("2024_01_24_oom_list_m5.rds"))
oom_list_pm1 <- list.load(input_path("2024_01_24_oom_list_pm1.rds"))
oom_list_pm2 <- list.load(input_path("2024_01_24_oom_list_pm2.rds"))
oom_list_pm3 <- list.load(input_path("2024_01_24_oom_list_pm3.rds"))
oom_list_pm4 <- list.load(input_path("2024_01_24_oom_list_pm4.rds"))
oom_list_pm5 <- list.load(input_path("2024_01_24_oom_list_pm5.rds"))

data_list_mu1 <- list.load(input_path("2024_01_15_data_list_mu1.rds"))
data_list_mu2 <- list.load(input_path("2024_01_15_data_list_mu2.rds"))
data_list_mu3 <- list.load(input_path("2024_01_15_data_list_mu3.rds"))
data_list_mu4 <- list.load(input_path("2024_01_15_data_list_mu4.rds"))
data_list_mu5 <- list.load(input_path("2024_01_15_data_list_mu5.rds"))
data_list_mpu1 <- list.load(input_path("2024_01_15_data_list_mpu1.rds"))
data_list_mpu2 <- list.load(input_path("2024_01_15_data_list_mpu2.rds"))
data_list_mpu3 <- list.load(input_path("2024_01_15_data_list_mpu3.rds"))
data_list_mpu4 <- list.load(input_path("2024_01_15_data_list_mpu4.rds"))
data_list_mpu5 <- list.load(input_path("2024_01_15_data_list_mpu5.rds"))

oom_list_mu1 <- list.load(input_path("2024_01_24_oom_list_mu1.rds"))
oom_list_mu2 <- list.load(input_path("2024_01_24_oom_list_mu2.rds"))
oom_list_mu3 <- list.load(input_path("2024_01_24_oom_list_mu3.rds"))
oom_list_mu4 <- list.load(input_path("2024_01_24_oom_list_mu4.rds"))
oom_list_mu5 <- list.load(input_path("2024_01_24_oom_list_mu5.rds"))
oom_list_mpu1 <- list.load(input_path("2024_01_24_oom_list_mpu1.rds"))
oom_list_mpu2 <- list.load(input_path("2024_01_24_oom_list_mpu2.rds"))
oom_list_mpu3 <- list.load(input_path("2024_01_24_oom_list_mpu3.rds"))
oom_list_mpu4 <- list.load(input_path("2024_01_24_oom_list_mpu4.rds"))
oom_list_mpu5 <- list.load(input_path("2024_01_24_oom_list_mpu5.rds"))
```

## Some pairwise variable correlations

Examining some of the pairwise associations between all the included (numeric) variables within the first imputed dataset.

```{r}
# Merging all the variables into a single data list
all_var_dl_m1 <- c(data_list_m1, oom_list_m1)

# First pass to extract the order of columns
# correlation_data function contains the correlation matrix, heatmap, and order
correlation_data_m1 <- correlation_data(all_var_dl_m1)

# Pulling just the correlation matrix
correlation_matrix_m1 <- correlation_data_m1$"correlation_matrix"

# The absolute values of all correlations with race
race_cors_m1 <- abs(correlation_matrix_m1[, "race"])
# The variables sorted by their absolute value of correlation with race
race_order_m1 <- sort(race_cors_m1, index.return = TRUE, decreasing = TRUE)$"ix"

# Same values, but for the sex variable
sex_cors_m1 <- abs(correlation_matrix_m1[, "sex"])
sex_order_m1 <- sort(sex_cors_m1, index.return = TRUE, decreasing = TRUE)$"ix"

# 1. Heatmap of all correlations
correlation_data_m1$"heatmap"
save_png(
    correlation_data_m1$"heatmap",
    fig_path("correlation_heatmap_m1.png", TRUE),
    width = 3500,
    height = 3500
)

# 2. Heatmap of all correlations, sorted by abs(correlation with race)
correlation_data_m1_race <- correlation_data(
    all_var_dl_m1,
    order = race_order_m1
)
save_png(
    correlation_data_m1_race$"heatmap",
    fig_path("correlation_heatmap_m1_race.png", TRUE),
    width = 2500,
    height = 2500
)

# 3. Heatmap of race correlations, sorted by abs(correlation with race)
correlation_heatmap_m1_race_only <- ComplexHeatmap::Heatmap(
    correlation_matrix_m1[race_order_m1, "race"],
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    show_column_names = FALSE,
    heatmap_legend_param = list(
        title = "Corr"
    )
)
save_png(
    correlation_heatmap_m1_race_only,
    fig_path("correlation_heatmap_m1_race_only.png", TRUE),
    width = 2000,
    height = 3000
)

# 4. Heatmap of all correlations, sorted by abs(correlation with sex)
correlation_data_m1_sex <- correlation_data(
    all_var_dl_m1,
    order = sex_order_m1
)
save_png(
    correlation_data_m1_sex$"heatmap",
    fig_path("correlation_heatmap_m1_sex.png", TRUE),
    width = 2500,
    height = 2500
)

# 5. Heatmap of sex correlations, sorted by abs(correlation with sex)
correlation_heatmap_m1_sex_only <- ComplexHeatmap::Heatmap(
    correlation_matrix_m1[sex_order_m1, "sex"],
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    show_column_names = FALSE,
    heatmap_legend_param = list(
        title = "Corr"
    )
)
save_png(
    correlation_heatmap_m1_sex_only,
    fig_path("correlation_heatmap_m1_sex_only.png", TRUE),
    width = 2000,
    height = 3000
)

```

## Replications across the other imputations

To get a sense of how the imputation process affects the correlations between variables, I repeat the above process for the other imputations.

```{r}

all_var_dl_m2 <- c(data_list_m2, oom_list_m2)
all_var_dl_m3 <- c(data_list_m3, oom_list_m3)
all_var_dl_m4 <- c(data_list_m4, oom_list_m4)
all_var_dl_m5 <- c(data_list_m5, oom_list_m5)
all_var_dl_pm1 <- c(data_list_pm1, oom_list_pm1)
all_var_dl_pm2 <- c(data_list_pm2, oom_list_pm2)
all_var_dl_pm3 <- c(data_list_pm3, oom_list_pm3)
all_var_dl_pm4 <- c(data_list_pm4, oom_list_pm4)
all_var_dl_pm5 <- c(data_list_pm5, oom_list_pm5)

all_var_dl_mu1 <- c(data_list_mu1, oom_list_mu1)
all_var_dl_mu2 <- c(data_list_mu2, oom_list_mu2)
all_var_dl_mu3 <- c(data_list_mu3, oom_list_mu3)
all_var_dl_mu4 <- c(data_list_mu4, oom_list_mu4)
all_var_dl_mu5 <- c(data_list_mu5, oom_list_mu5)
all_var_dl_mpu1 <- c(data_list_mpu1, oom_list_mpu1)
all_var_dl_mpu2 <- c(data_list_mpu2, oom_list_mpu2)
all_var_dl_mpu3 <- c(data_list_mpu3, oom_list_mpu3)
all_var_dl_mpu4 <- c(data_list_mpu4, oom_list_mpu4)
all_var_dl_mpu5 <- c(data_list_mpu5, oom_list_mpu5)

correlation_data_m1 <- correlation_data(all_var_dl_m1)
correlation_data_m2 <- correlation_data(all_var_dl_m2)
correlation_data_m3 <- correlation_data(all_var_dl_m3)
correlation_data_m4 <- correlation_data(all_var_dl_m4)
correlation_data_m5 <- correlation_data(all_var_dl_m5)
correlation_data_pm1 <- correlation_data(all_var_dl_pm1)
correlation_data_pm2 <- correlation_data(all_var_dl_pm2)
correlation_data_pm3 <- correlation_data(all_var_dl_pm3)
correlation_data_pm4 <- correlation_data(all_var_dl_pm4)
correlation_data_pm5 <- correlation_data(all_var_dl_pm5)
correlation_data_mu1 <- correlation_data(all_var_dl_mu1)
correlation_data_mu2 <- correlation_data(all_var_dl_mu2)
correlation_data_mu3 <- correlation_data(all_var_dl_mu3)
correlation_data_mu4 <- correlation_data(all_var_dl_mu4)
correlation_data_mu5 <- correlation_data(all_var_dl_mu5)
correlation_data_mpu1 <- correlation_data(all_var_dl_mpu1)
correlation_data_mpu2 <- correlation_data(all_var_dl_mpu2)
correlation_data_mpu3 <- correlation_data(all_var_dl_mpu3)
correlation_data_mpu4 <- correlation_data(all_var_dl_mpu4)
correlation_data_mpu5 <- correlation_data(all_var_dl_mpu5)

# A consistent order making use of the restricted variables found in the pooled matrix
drawn_pm1 <- ComplexHeatmap::draw(correlation_data_pm1$"heatmap")
var_order <- ComplexHeatmap::row_order(drawn_pm1)
var_order <- colnames(correlation_data_pm1$"correlation_matrix")[var_order]

write.csv(var_order, proc_path("var_order.csv", TRUE))

var_order <- read_csv(proc_path("2024_01_24_var_order.csv"))$"x"

var_order

correlation_data_list <- list(
    "correlation_data_m1" = correlation_data_m1,
    "correlation_data_m2" = correlation_data_m2,
    "correlation_data_m3" = correlation_data_m3,
    "correlation_data_m4" = correlation_data_m4,
    "correlation_data_m5" = correlation_data_m5,
    "correlation_data_pm1" = correlation_data_pm1,
    "correlation_data_pm2" = correlation_data_pm2,
    "correlation_data_pm3" = correlation_data_pm3,
    "correlation_data_pm4" = correlation_data_pm4,
    "correlation_data_pm5" = correlation_data_pm5,
    "correlation_data_mu1" = correlation_data_mu1,
    "correlation_data_mu2" = correlation_data_mu2,
    "correlation_data_mu3" = correlation_data_mu3,
    "correlation_data_mu4" = correlation_data_mu4,
    "correlation_data_mu5" = correlation_data_mu5,
    "correlation_data_mpu1" = correlation_data_mpu1,
    "correlation_data_mpu2" = correlation_data_mpu2,
    "correlation_data_mpu3" = correlation_data_mpu3,
    "correlation_data_mpu4" = correlation_data_mpu4,
    "correlation_data_mpu5" = correlation_data_mpu5
)

for (i in 1:length(correlation_data_list)) {
    suffix <- names(correlation_data_list)[[i]]
    suffix <- gsub("correlation_data_", "", suffix)
    corr_matrix <- data.frame(correlation_data_list[[i]]$"correlation_matrix")
    # Save the correlation matrix to file
    write.csv(
        corr_matrix,
        proc_path(paste0("correlation_matrix_", suffix, ".csv"), TRUE)
    )
    # Plot the correlation heatmaps
    canon_matrix <- corr_matrix[var_order, var_order]
    canon_hm <- ComplexHeatmap::Heatmap(
        canon_matrix,
        cluster_rows = FALSE,
        cluster_columns = FALSE,
        heatmap_legend_param = list(
            title = "Corr"
        )
    )
    print(canon_hm)
    hm_name <- paste0("correlation_heatmap_", suffix, ".png")
    save_png(
        canon_hm,
        fig_path(hm_name, TRUE),
        width = 3000,
        height = 3000
    )
}

# Difference between mTBI alone and pooled mtbi
mtbi_alone <- (correlation_data_m1$"correlation_matrix"[var_order, var_order] +
    correlation_data_m2$"correlation_matrix"[var_order, var_order] +
    correlation_data_m3$"correlation_matrix"[var_order, var_order] +
    correlation_data_m4$"correlation_matrix"[var_order, var_order] +
    correlation_data_m5$"correlation_matrix"[var_order, var_order]) / 5

mtbi_pooled <- (correlation_data_pm1$"correlation_matrix"[var_order, var_order] +
    correlation_data_pm2$"correlation_matrix"[var_order, var_order] +
    correlation_data_pm3$"correlation_matrix"[var_order, var_order] +
    correlation_data_pm4$"correlation_matrix"[var_order, var_order] +
    correlation_data_pm5$"correlation_matrix"[var_order, var_order]) / 5

m_alone_v_pool <- ComplexHeatmap::Heatmap(
    mtbi_alone - mtbi_pooled,
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    heatmap_legend_param = list(
        title = "Corr"
    )
)

save_png(
    m_alone_v_pool,
    fig_path("mtbi_alone_vs_pooled.png", TRUE),
    width = 3000,
    height = 3000
)

# Difference between uninjured alone and pooled uninjured
uninjured_alone <- (correlation_data_mu1$"correlation_matrix"[var_order, var_order] +
    correlation_data_mu2$"correlation_matrix"[var_order, var_order] +
    correlation_data_mu3$"correlation_matrix"[var_order, var_order] +
    correlation_data_mu4$"correlation_matrix"[var_order, var_order] +
    correlation_data_mu5$"correlation_matrix"[var_order, var_order]) / 5

uninjured_pooled <- (correlation_data_mpu1$"correlation_matrix"[var_order, var_order] +
    correlation_data_mpu2$"correlation_matrix"[var_order, var_order] +
    correlation_data_mpu3$"correlation_matrix"[var_order, var_order] +
    correlation_data_mpu4$"correlation_matrix"[var_order, var_order] +
    correlation_data_mpu5$"correlation_matrix"[var_order, var_order]) / 5

u_alone_v_pool <- ComplexHeatmap::Heatmap(
    uninjured_alone - uninjured_pooled,
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    heatmap_legend_param = list(
        title = "Corr"
    )
)

save_png(
    u_alone_v_pool,
    fig_path("uninjured_alone_vs_pooled.png", TRUE),
    width = 3000,
    height = 3000
)

# Difference between all mTBI and all uninjured
mtbi_all <- (
    correlation_data_m1$"correlation_matrix"[var_order, var_order] +
    correlation_data_m2$"correlation_matrix"[var_order, var_order] +
    correlation_data_m3$"correlation_matrix"[var_order, var_order] +
    correlation_data_m4$"correlation_matrix"[var_order, var_order] +
    correlation_data_m5$"correlation_matrix"[var_order, var_order] +
    correlation_data_pm1$"correlation_matrix"[var_order, var_order] +
    correlation_data_pm2$"correlation_matrix"[var_order, var_order] +
    correlation_data_pm3$"correlation_matrix"[var_order, var_order] +
    correlation_data_pm4$"correlation_matrix"[var_order, var_order] +
    correlation_data_pm5$"correlation_matrix"[var_order, var_order]
) / 10

uninjured_all <- (
    correlation_data_mu1$"correlation_matrix"[var_order, var_order] +
    correlation_data_mu2$"correlation_matrix"[var_order, var_order] +
    correlation_data_mu3$"correlation_matrix"[var_order, var_order] +
    correlation_data_mu4$"correlation_matrix"[var_order, var_order] +
    correlation_data_mu5$"correlation_matrix"[var_order, var_order] +
    correlation_data_mpu1$"correlation_matrix"[var_order, var_order] +
    correlation_data_mpu2$"correlation_matrix"[var_order, var_order] +
    correlation_data_mpu3$"correlation_matrix"[var_order, var_order] +
    correlation_data_mpu4$"correlation_matrix"[var_order, var_order] +
    correlation_data_mpu5$"correlation_matrix"[var_order, var_order]
) / 10

mtbi_vs_uninjured <- ComplexHeatmap::Heatmap(
    mtbi_all - uninjured_all,
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    heatmap_legend_param = list(
        title = "Corr"
    )
)

save_png(
    mtbi_vs_uninjured,
    fig_path("mtbi_vs_uninjured.png", TRUE),
    width = 3000,
    height = 3000
)

# Difference between mTBI-solo and uninjured-solo
mtbi_solo_vs_uninjured_solo <- ComplexHeatmap::Heatmap(
    mtbi_alone - uninjured_alone,
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    heatmap_legend_param = list(
        title = "Corr"
    )
)

save_png(
    mtbi_solo_vs_uninjured_solo,
    fig_path("mtbi_solo_vs_uninjured_solo.png", TRUE),
    width = 3000,
    height = 3000
)
```
