# Data extraction

Load libraries and establish paths.

```{r}
library(ggplot2)
library(readr)
library(dplyr)
library(here)
library(abcdutils)
library(visdat)
library(tibble)

core_path <- path_maker(here(paste0("data/abcd/core")))
input_path <- path_maker(here(paste0("data/abcd/inputs")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))

read <- function(path) {
    return(abcd_load(core_path(path)))
}
```

Import raw data.

```{r}
ph_p_otbi <- read("physical-health/ph_p_otbi.csv")
abcd_y_lt <- read("abcd-general/abcd_y_lt.csv")
ph_y_pds <- read("physical-health/ph_y_pds.csv")
ph_p_pds <- read("physical-health/ph_p_pds.csv")
gish_p_gi <- read("gender-identity-sexual-health/gish_p_gi.csv")
abcd_p_demo <- read("abcd-general/abcd_p_demo.csv")
ph_p_mhx <- read("physical-health/ph_p_mhx.csv")
mri_y_smr_vol_aseg <- read("imaging/mri_y_smr_vol_aseg.csv")
mri_y_smr_thk_dsk <- read("imaging/mri_y_smr_thk_dsk.csv")
mri_y_smr_area_dsk <- read("imaging/mri_y_smr_area_dsk.csv")
mri_y_rsi_rnd_at <- read("imaging/mri_y_rsi_rnd_at.csv")
mri_y_rsi_rnd_wm_dsk <- read("imaging/mri_y_rsi_rnd_wm_dsk.csv")
mri_y_rsi_rnd_wm_dst <- read("imaging/mri_y_rsi_rnd_wm_dst.csv")
mri_y_rsfmr_cor_gp_gp <- read("imaging/mri_y_rsfmr_cor_gp_gp.csv")
mri_y_rsfmr_cor_gp_aseg <- read("imaging/mri_y_rsfmr_cor_gp_aseg.csv")
mh_y_or <- read("mental-health/mh_y_or.csv")
nt_p_stq <- read("novel-technologies/nt_p_stq.csv")
ph_p_saiq <- read("physical-health/ph_p_saiq.csv")
ph_y_yrb <- read("physical-health/ph_y_yrb.csv")
ce_y_psb <- read("culture-environment/ce_y_psb.csv")
ce_p_psb <- read("culture-environment/ce_p_psb.csv")
ce_y_fes <- read("culture-environment/ce_y_fes.csv")
ce_p_fes <- read("culture-environment/ce_p_fes.csv")
mh_p_asr <- read("mental-health/mh_p_asr.csv")
mh_p_cbcl <- read("mental-health/mh_p_cbcl.csv")
ph_p_sds <- read("physical-health/ph_p_sds.csv")
```

## Subjects

There are three broad subject groups:

- baseline mtbi: those who have had an mTBI pre-baseline (we could just collect outcome data)
- longitudinal mtbi: those who have had only an mTBI post-baseline but pre-2yfu
- baseline uninjured: those who have had no mTBI or worse as of baseline, including:
    - matched uninjured
    - longitudinal uninjured (those who have had no mTBI or worse as of 2yfu)

so the total combos of data needed are:

- base mtbi base [x]
- base mtbi long
- long mtbi base 
- long mtbi long
- base uninj base [x]
- base uninj long

We will now look at:


1. (A: "mtbi_subjects.csv") longitudinal data for baseline mTBI subjects
    - What happened to them after 2 years?
    - How informative was the baseline clustering?

2. (B: "uninjured_subjects.csv" that are NOT in C) longitudinal data for *some* baseline uninj subjects. It's okay if they had injuries.
    - used as context for #3

3. (C) longitudinal data for baseline outcome matched uninjured subjects. It's okay if they had injuries.
    - did they experience more mTBIs than the other uninjured subjects (#2)?

4. (D: longitudinal mTBI / "mtbi_subjects_0_to_2.csv") baseline data for longitudinal mTBI subjects
    - Does the baseline clustering assignment predict their long term outcomes?
    - Did they have bad outcomes right out of the gates compared to baseline matched uninjured controls?

5. (D: longitudinal mTBI / "mtbi_subjects_0_to_2.csv") longitudinal data for longitudinal mTBI subjects
    - used as context for #1

6. (E: longitudinal uninjured / "uninjured_subjects_0_to_2.csv") baseline data for longitudinal uninjured subjects
    - with #4, used as context for #1 and #2?

7. (E: "uninjured_subjects_0_to_2.csv") Long uninj subjects, long
    - with #3, used as context for #1 and #2?

The relevant times already collected for these longitudinal analyses are:
1. baseline mTBI subjects, baseline (already collected)
2. baseline uninj subjects, baseline (already collected)
3. baseline outcome matched uninj subjects, baseline (already collected)

And in later chapters, if clustering results are good, I'll make a classifier to predict cluster from raw data.

```{r}
# subs who had an mTBI as of baseline timepoint (regardless of chronic tp)
mtbi_subs_t0 <- get_mtbi_subjects(
    ph_p_otbi,
    abcd_y_lt,
    min_mpi = 0,
    t = 0
) |>
    dplyr::select(subjectkey) |>
    unlist() |>
    as.character()

# subs who had an mTBI as of the year 1 follow up data
mtbi_subs_t1 <- get_mtbi_subjects(
    ph_p_otbi,
    abcd_y_lt,
    min_mpi = 0,
    t = 1
) |>
    dplyr::select(subjectkey) |>
    unlist() |>
    as.character()

# subs who had an mTBI as of the year 2 follow up data
mtbi_subs_t2 <- get_mtbi_subjects(
    ph_p_otbi,
    abcd_y_lt,
    min_mpi = 0,
    t = 2
) |>
    dplyr::select(subjectkey) |>
    unlist() |>
    as.character()

# subs who had an mtbi pre-1yfu, but not pre-baseline
mtbi_subs_t1o <- mtbi_subs_t1[!mtbi_subs_t1 %in% mtbi_subs_t0]

# subs who had an mtbi between 1yfu and 2yfu, but not pre-baseline
mtbi_subs_t2o <- mtbi_subs_t2[!mtbi_subs_t2 %in% mtbi_subs_t0]

# subs who had an mtbi pre-2yfu but not pre-baseline
mtbi_subs_0_to_2 <- unique(c(mtbi_subs_t1o, mtbi_subs_t2o))

length(mtbi_subs_0_to_2) #219

write_subjects(
    mtbi_subs_t1,
    sub_path("mtbi_subs_t1.csv", TRUE)
)

write_subjects(
    mtbi_subs_t2,
    sub_path("mtbi_subs_t2.csv", TRUE)
)

write_subjects(
    mtbi_subs_0_to_2,
    sub_path("mtbi_subs_0_to_2.csv", TRUE)
)

# Subjects who had no mtbi or worse pre-baseline
unij_subs_t0 <- get_uninjured_subjects(ph_p_otbi, abcd_y_lt, t = 0) |>
    dplyr::select(subjectkey) |>
    unlist() |>
    as.character()

# Subjects who had no mtbi or worse between baseline and 1yfu
unij_subs_t1 <- get_uninjured_subjects(ph_p_otbi, abcd_y_lt, t = 1) |>
    dplyr::select(subjectkey) |>
    unlist() |>
    as.character()

# Subjects who had no mtbi or worse between 1yfu and 2yfu
unij_subs_t2 <- get_uninjured_subjects(ph_p_otbi, abcd_y_lt, t = 2) |>
    dplyr::select(subjectkey) |>
    unlist() |>
    as.character()

# Subjects who had no mtbi or worse as of 2yfu
unij_subs_0_to_2 <- Reduce(
    intersect,
    list(
        unij_subs_t0,
        unij_subs_t1,
        unij_subs_t2
    )
)

# Exporting those subjects
write_subjects(
    unij_subs_0_to_2,
    sub_path("unij_subs_0_to_2.csv", TRUE)
)
```

```{r}
# CHECKPOINT
mtbi_subs_t1 <- read_subjects(
    sub_path("2024_11_18_mtbi_subs_t1.csv")
)

mtbi_subs_t2 <- read_subjects(
    sub_path("2024_11_18_mtbi_subs_t2.csv")
)

long_mtbi_subs <- read_subjects(
    sub_path("2024_11_18_mtbi_subs_0_to_2.csv")
)

long_unij_subs <- read_subjects(
    sub_path("2024_11_18_unij_subs_0_to_2.csv")
)

# The original baseline sample:
base_mtbi_subs <- read_subjects(sub_path("2024_11_18_mtbi_subs.csv"))
base_unij_subs <- read_subjects(sub_path("2024_11_18_unij_subs.csv"))
```

Checking when each injured subject should have their injury info collected:

```{r}
# subs who should have their injury information collected from t1
t1_latest <- long_mtbi_subs[!long_mtbi_subs %in% mtbi_subs_t2]

# subs who should have their injury information collected from t2
t2_latest <- long_mtbi_subs[long_mtbi_subs %in% mtbi_subs_t2]
```

Note that for data only present at baseline, I only collect that data for the longitudinal mTBI sample at the T0 timepoint.
It has already been collected for the baseline mTBI and unijured samples, and the longitudinal unijured sample is just a subset of the baseline unijured sample.

## Input variables

### Acute symptoms

#### Feeling dazed

```{r}
as_mem_daze_long_mtbi_l1 <- get_mtbi_mem_daze(
    ph_p_otbi,
    abcd_y_lt,
    t1_latest,
    t = 1
)

as_mem_daze_long_mtbi_l2 <- get_mtbi_mem_daze(
    ph_p_otbi,
    abcd_y_lt,
    t2_latest,
    t = 2
)

as_mem_daze_long_mtbi_l <- rbind(
    as_mem_daze_long_mtbi_l1,
    as_mem_daze_long_mtbi_l2
)

tibble(as_mem_daze_long_mtbi_l)
write_csv(
    as_mem_daze_long_mtbi_l,
    input_path("as_mem_daze_long_mtbi_l.csv", date = TRUE)
)
```

#### Mechanism of injury

```{r}
as_mechanism_long_mtbi_l1 <- get_mtbi_mechanism(
    ph_p_otbi,
    abcd_y_lt,
    t1_latest,
    t = 1
)

as_mechanism_long_mtbi_l2 <- get_mtbi_mechanism(
    ph_p_otbi,
    abcd_y_lt,
    t2_latest,
    t = 2
)

as_mechanism_long_mtbi_l <- rbind(
    as_mechanism_long_mtbi_l1,
    as_mechanism_long_mtbi_l2
)

tibble(as_mechanism_long_mtbi_l)
write_csv(
    as_mechanism_long_mtbi_l,
    input_path("as_mechanism_long_mtbi_l.csv", date = TRUE)
)
```

#### Loss of consciousness

```{r}
as_loc_long_mtbi_l1 <- get_mtbi_loc(
    ph_p_otbi,
    abcd_y_lt,
    t1_latest,
    t = 1
)

as_loc_long_mtbi_l2 <- get_mtbi_loc(
    ph_p_otbi,
    abcd_y_lt,
    t2_latest,
    t = 2
)

as_loc_long_mtbi_l <- rbind(
    as_loc_long_mtbi_l1,
    as_loc_long_mtbi_l2
)

tibble(as_loc_long_mtbi_l)
write_csv(
    as_loc_long_mtbi_l,
    input_path("as_loc_long_mtbi_l.csv", date = TRUE)
)
```

Now we move on to (mostly) features that are present among all subjects.

Checklist of extraction points I should be collecting (see line 57):

Previously:
- [x] baseline mtbi, baseline
- [x] baseline unijured, baseline
    - this includes the matched subjects

Now:
- [ ] baseline subjects, 2yfu
- [ ] baseline unijured, 2yfu
    - this includes the longitudinal unijured
- [ ] longitudinal mtbi, baseline
- [ ] longitudinal mtbi, 2yfu

### Demographics

Demographic variables included in the analyses are:

* Interview age
* Injury age
* Sex
* Race
* Household income
* Pubertal status

#### Interview age

1. A: long_mtbi_0
2. B: long_mtbi_l
3. C: base_mtbi_l
4. D: base_unij_l

```{r}
# A 
d_interview_age_long_mtbi_0 <- get_interview_age(abcd_y_lt, long_mtbi_subs, t = 0, as_years = FALSE)
tibble(d_interview_age_long_mtbi_0)
write_csv(d_interview_age_long_mtbi_0, input_path("d_interview_age_long_mtbi_0.csv", TRUE))

# B
d_interview_age_long_mtbi_l <- get_interview_age(abcd_y_lt, long_mtbi_subs, t = 2, as_years = FALSE)
tibble(d_interview_age_long_mtbi_l)
write_csv(d_interview_age_long_mtbi_l, input_path("d_interview_age_long_mtbi_l.csv", TRUE))

# C
d_interview_age_base_mtbi_l <- get_interview_age(abcd_y_lt, base_mtbi_subs, t = 2, as_years = FALSE)
tibble(d_interview_age_base_mtbi_l)
write_csv(d_interview_age_base_mtbi_l, input_path("d_interview_age_mtbi_l.csv", TRUE))

# D
d_interview_age_base_unij_l <- get_interview_age(abcd_y_lt, base_unij_subs, t = 2, as_years = FALSE)
tibble(d_interview_age_base_unij_l)
write_csv(d_interview_age_base_unij_l, input_path("d_interview_age_base_unij_l.csv", TRUE))
```


#### Injury age

This is only relevant for the longitudinal mTBI group.

```{r}
d_mtbi_age_mtbi_l1 <- get_mtbi_age(ph_p_otbi, abcd_y_lt, t1_latest, t = 1, as_years = FALSE)
d_mtbi_age_mtbi_l2 <- get_mtbi_age(ph_p_otbi, abcd_y_lt, t2_latest, t = 2, as_years = FALSE)
d_mtbi_age_long_mtbi_l <- rbind(d_mtbi_age_mtbi_l1, d_mtbi_age_mtbi_l2)

tibble(d_mtbi_age_long_mtbi_l)
write_csv(d_mtbi_age_long_mtbi_l, input_path("d_mtbi_age_long_mtbi_l.csv", TRUE))
```

#### Sex at birth

Data only present at baseline.
We already have sex for the baseline mTBI and baseline unijured groups.

```{r}
d_sex_long_mtbi_0 <- get_sex(gish_p_gi, long_mtbi_subs, t = 0, as_numeric = TRUE)
tibble(d_sex_long_mtbi_0)
write_csv(d_sex_long_mtbi_0, input_path("d_sex_long_mtbi_0.csv", TRUE))
```

#### Household income

```{r}
# A
d_income_long_mtbi_0 <- get_income(abcd_p_demo, long_mtbi_subs, t = 0)
tibble(d_income_long_mtbi_0)
write_csv(d_income_long_mtbi_0, input_path("d_income_long_mtbi_0.csv", TRUE))

# B
d_income_long_mtbi_l <- get_income(abcd_p_demo, long_mtbi_subs, t = 2)
tibble(d_income_long_mtbi_l)
write_csv(d_income_long_mtbi_l, input_path("d_income_long_mtbi_l.csv", TRUE))

# C
d_income_base_mtbi_l <- get_income(abcd_p_demo, base_mtbi_subs, t = 2)
tibble(d_income_base_mtbi_l)
write_csv(d_income_base_mtbi_l, input_path("d_income_mtbi_l.csv", TRUE))

# D
d_income_base_unij_l <- get_income(abcd_p_demo, base_unij_subs, t = 2)
tibble(d_income_base_unij_l)
write_csv(d_income_base_unij_l, input_path("d_income_base_unij_l.csv", TRUE))
```

#### Race

Data only present at baseline.

```{r}
d_race_long_mtbi_0 <- get_race(abcd_p_demo, long_mtbi_subs, asian_as_other = TRUE, t = 0)
tibble(d_race_long_mtbi_0)
write_csv(d_race_long_mtbi_0, input_path("d_race_long_mtbi_0.csv", TRUE))
```

#### Pubertal status

```{r}
d_pubertal_status_p_long_mtbi_0 <- get_pubertal_status_p(ph_p_pds, long_mtbi_subs, max_value = 3, t = 0)
d_pubertal_status_y_long_mtbi_0 <- get_pubertal_status_y(ph_y_pds, long_mtbi_subs, max_value = 3, t = 0)
d_pubertal_status_long_mtbi_0 <- dplyr::inner_join(d_pubertal_status_p_long_mtbi_0, d_pubertal_status_y_long_mtbi_0)
tibble(d_pubertal_status_long_mtbi_0)
write_csv(d_pubertal_status_long_mtbi_0, input_path("d_pubertal_status_long_mtbi_0.csv", TRUE))

d_pubertal_status_p_long_mtbi_l <- get_pubertal_status_p(ph_p_pds, long_mtbi_subs, max_value = 4, t = 2)
d_pubertal_status_y_long_mtbi_l <- get_pubertal_status_y(ph_y_pds, long_mtbi_subs, max_value = 4, t = 2)
d_pubertal_status_long_mtbi_l <- dplyr::inner_join(d_pubertal_status_p_long_mtbi_l, d_pubertal_status_y_long_mtbi_l)
tibble(d_pubertal_status_long_mtbi_l)
write_csv(d_pubertal_status_long_mtbi_l, input_path("d_pubertal_status_long_mtbi_l.csv", TRUE))

d_pubertal_status_p_base_mtbi_l <- get_pubertal_status_p(ph_p_pds, base_mtbi_subs, max_value = 4, t = 2)
d_pubertal_status_y_base_mtbi_l <- get_pubertal_status_y(ph_y_pds, base_mtbi_subs, max_value = 4, t = 2)
d_pubertal_status_base_mtbi_l <- dplyr::inner_join(d_pubertal_status_p_base_mtbi_l, d_pubertal_status_y_base_mtbi_l)
tibble(d_pubertal_status_base_mtbi_l)
write_csv(d_pubertal_status_base_mtbi_l, input_path("d_pubertal_status_base_mtbi_l.csv", TRUE))

d_pubertal_status_p_base_unij_l <- get_pubertal_status_p(ph_p_pds, base_unij_subs, max_value = 4, t = 2)
d_pubertal_status_y_base_unij_l <- get_pubertal_status_y(ph_y_pds, base_unij_subs, max_value = 4, t = 2)
d_pubertal_status_base_unij_l <- dplyr::inner_join(d_pubertal_status_p_base_unij_l, d_pubertal_status_y_base_unij_l)
tibble(d_pubertal_status_base_unij_l)
write_csv(d_pubertal_status_base_unij_l, input_path("d_pubertal_status_base_unij_l.csv", TRUE))
```

### Medical history

Medical history variables of interest include:

1. Number of previous head injuries
2. History of headaches (binary)

#### History of headaches

```{r}
mh_headaches_long_mtbi_0 <- get_headaches(ph_p_mhx, long_mtbi_subs, t = 0)
tibble(mh_headaches_long_mtbi_0)
write_csv(mh_headaches_long_mtbi_0, input_path("mh_headaches_long_mtbi_0.csv", TRUE))

mh_headaches_long_mtbi_l <- get_headaches(ph_p_mhx, long_mtbi_subs, t = 2)
tibble(mh_headaches_long_mtbi_l)
write_csv(mh_headaches_long_mtbi_l, input_path("mh_headaches_long_mtbi_l.csv", TRUE))

mh_headaches_base_mtbi_l <- get_headaches(ph_p_mhx, base_mtbi_subs, t = 2)
tibble(mh_headaches_base_mtbi_l)
write_csv(mh_headaches_base_mtbi_l, input_path("mh_headaches_base_mtbi_l.csv", TRUE))

mh_headaches_base_unij_l <- get_headaches(ph_p_mhx, base_unij_subs, t = 2)
tibble(mh_headaches_base_unij_l)
write_csv(mh_headaches_base_unij_l, input_path("mh_headaches_base_unij_l.csv", TRUE))
```

#### Number of previous mTBIs

```{r}
# N = 4 and 5 only occur once
mh_mtbi_count_long_mtbi_t1 <- get_mtbi_count(ph_p_otbi, abcd_y_lt, long_mtbi_subs, cutoff = 6, t = 1)

# N = 4 and 5 only occur once
mh_mtbi_count_long_mtbi_t2 <- get_mtbi_count(ph_p_otbi, abcd_y_lt, long_mtbi_subs, cutoff = 6, t = 2)

mh_mtbi_count_long_mtbi_l <- dplyr::full_join(
    mh_mtbi_count_long_mtbi_t1,
    mh_mtbi_count_long_mtbi_t2,
    by = "subjectkey"
) |>
    dplyr::rowwise() |>
    dplyr::mutate(
        mtbi_count = sum(mtbi_count.x, mtbi_count.y, na.rm = TRUE),
        .keep = "unused"
    ) |>
    dplyr::ungroup()

head(mh_mtbi_count_long_mtbi_l)
write_csv(
    mh_mtbi_count_long_mtbi_l,
    input_path("mh_mtbi_count_long_mtbi_l.csv", date = TRUE)
)
```

### Neuroimaging

#### Structural MRI

##### Subcortical volume

```{r}
sm_subc_v_long_mtbi_0 <- get_subc_v(mri_y_smr_vol_aseg, long_mtbi_subs, t = 0)
tibble(sm_subc_v_long_mtbi_0)
write_csv(sm_subc_v_long_mtbi_0, input_path("sm_subc_v_long_mtbi_0.csv", date = TRUE))

sm_subc_v_long_mtbi_l <- get_subc_v(mri_y_smr_vol_aseg, long_mtbi_subs, t = 2)
tibble(sm_subc_v_long_mtbi_l)
write_csv(sm_subc_v_long_mtbi_l, input_path("sm_subc_v_long_mtbi_l.csv", date = TRUE))

sm_subc_v_base_mtbi_l <- get_subc_v(mri_y_smr_vol_aseg, base_mtbi_subs, t = 2)
tibble(sm_subc_v_base_mtbi_l)
write_csv(sm_subc_v_base_mtbi_l, input_path("sm_subc_v_base_mtbi_l.csv", date = TRUE))

sm_subc_v_base_unij_l <- get_subc_v(mri_y_smr_vol_aseg, base_unij_subs, t = 2)
tibble(sm_subc_v_base_unij_l)
write_csv(sm_subc_v_base_unij_l, input_path("sm_subc_v_base_unij_l.csv", date = TRUE))
```

##### Cortical thickness

Both the Desikan and Destrieux cortical parcellations could have been used for the cortical imaging data collected below.
A comparison between the two can be found in the appendix.
Because there happens to be a few more participants with calculated Desikan parcellations, that is what is used here.

```{r}
sm_cort_t_long_mtbi_0 <- get_cort_t(mri_y_smr_thk_dsk, long_mtbi_subs, t = 0)
tibble(sm_cort_t_long_mtbi_0)
write_csv(sm_cort_t_long_mtbi_0, input_path("sm_cort_t_long_mtbi_0.csv", date = TRUE))

sm_cort_t_long_mtbi_l <- get_cort_t(mri_y_smr_thk_dsk, long_mtbi_subs, t = 2)
tibble(sm_cort_t_long_mtbi_l)
write_csv(sm_cort_t_long_mtbi_l, input_path("sm_cort_t_long_mtbi_l.csv", date = TRUE))

sm_cort_t_base_mtbi_l <- get_cort_t(mri_y_smr_thk_dsk, base_mtbi_subs, t = 2)
tibble(sm_cort_t_base_mtbi_l)
write_csv(sm_cort_t_base_mtbi_l, input_path("sm_cort_t_base_mtbi_l.csv", date = TRUE))

sm_cort_t_base_unij_l <- get_cort_t(mri_y_smr_thk_dsk, base_unij_subs, t = 2)
tibble(sm_cort_t_base_unij_l)
write_csv(sm_cort_t_base_unij_l, input_path("sm_cort_t_base_unij_l.csv", date = TRUE))
```

##### Cortical surface areas

```{r}
sm_cort_sa_long_mtbi_0 <- get_cort_sa(mri_y_smr_area_dsk, long_mtbi_subs, t = 0)
tibble(sm_cort_sa_long_mtbi_0)
write_csv(sm_cort_sa_long_mtbi_0, input_path("sm_cort_sa_long_mtbi_0.csv", date = TRUE))

sm_cort_sa_long_mtbi_l <- get_cort_sa(mri_y_smr_area_dsk, long_mtbi_subs, t = 2)
tibble(sm_cort_sa_long_mtbi_l)
write_csv(sm_cort_sa_long_mtbi_l, input_path("sm_cort_sa_long_mtbi_l.csv", date = TRUE))

sm_cort_sa_base_mtbi_l <- get_cort_sa(mri_y_smr_area_dsk, base_mtbi_subs, t = 2)
tibble(sm_cort_sa_base_mtbi_l)
write_csv(sm_cort_sa_base_mtbi_l, input_path("sm_cort_sa_base_mtbi_l.csv", date = TRUE))

sm_cort_sa_base_unij_l <- get_cort_sa(mri_y_smr_area_dsk, base_unij_subs, t = 2)
tibble(sm_cort_sa_base_unij_l)
write_csv(sm_cort_sa_base_unij_l, input_path("sm_cort_sa_base_unij_l.csv", date = TRUE))
```

#### Diffusion MRI

##### White matter neurite densities

```{r}
dm_all_wmnd_long_mtbi_0 <- get_all_wmnd(mri_y_rsi_rnd_at, mri_y_rsi_rnd_wm_dsk, long_mtbi_subs, t = 0)
tibble(dm_all_wmnd_long_mtbi_0)
write_csv(dm_all_wmnd_long_mtbi_0, input_path("dm_all_wmnd_long_mtbi_0.csv", date = TRUE))

dm_all_wmnd_long_mtbi_l <- get_all_wmnd(mri_y_rsi_rnd_at, mri_y_rsi_rnd_wm_dsk, long_mtbi_subs, t = 2)
tibble(dm_all_wmnd_long_mtbi_l)
write_csv(dm_all_wmnd_long_mtbi_l, input_path("dm_all_wmnd_long_mtbi_l.csv", date = TRUE))

dm_all_wmnd_base_mtbi_l <- get_all_wmnd(mri_y_rsi_rnd_at, mri_y_rsi_rnd_wm_dsk, base_mtbi_subs, t = 2)
tibble(dm_all_wmnd_base_mtbi_l)
write_csv(dm_all_wmnd_base_mtbi_l, input_path("dm_all_wmnd_base_mtbi_l.csv", date = TRUE))

dm_all_wmnd_base_unij_l <- get_all_wmnd(mri_y_rsi_rnd_at, mri_y_rsi_rnd_wm_dsk, base_unij_subs, t = 2)
tibble(dm_all_wmnd_base_unij_l)
write_csv(dm_all_wmnd_base_unij_l, input_path("dm_all_wmnd_base_unij_l.csv", date = TRUE))
```

#### Resting-state functional MRI

We are interested in the following rs-fMRI measures:

- Gordon network (cortical) correlations
- Subcortical correlations

##### Cortical parcellation network correlations

```{r}
rm_gord_cor_long_mtbi_0 <- get_gord_cor(mri_y_rsfmr_cor_gp_gp, long_mtbi_subs, t = 0)
tibble(rm_gord_cor_long_mtbi_0)
write_csv(rm_gord_cor_long_mtbi_0, input_path("rm_gord_cor_long_mtbi_0.csv", date = TRUE))

rm_gord_cor_long_mtbi_l <- get_gord_cor(mri_y_rsfmr_cor_gp_gp, long_mtbi_subs, t = 2)
tibble(rm_gord_cor_long_mtbi_l)
write_csv(rm_gord_cor_long_mtbi_l, input_path("rm_gord_cor_long_mtbi_l.csv", date = TRUE))

rm_gord_cor_base_mtbi_l <- get_gord_cor(mri_y_rsfmr_cor_gp_gp, base_mtbi_subs, t = 2)
tibble(rm_gord_cor_base_mtbi_l)
write_csv(rm_gord_cor_base_mtbi_l, input_path("rm_gord_cor_base_mtbi_l.csv", date = TRUE))

rm_gord_cor_base_unij_l <- get_gord_cor(mri_y_rsfmr_cor_gp_gp, base_unij_subs, t = 2)
tibble(rm_gord_cor_base_unij_l)
write_csv(rm_gord_cor_base_unij_l, input_path("rm_gord_cor_base_unij_l.csv", date = TRUE))
```

##### Subcortical parcellation network correlations

```{r}
rm_subc_cor_long_mtbi_0 <- get_subc_cor(mri_y_rsfmr_cor_gp_aseg, long_mtbi_subs, t = 0)
tibble(rm_subc_cor_long_mtbi_0)
write_csv(rm_subc_cor_long_mtbi_0, input_path("rm_subc_cor_long_mtbi_0.csv", date = TRUE))

rm_subc_cor_long_mtbi_l <- get_subc_cor(mri_y_rsfmr_cor_gp_aseg, long_mtbi_subs, t = 2)
tibble(rm_subc_cor_long_mtbi_l)
write_csv(rm_subc_cor_long_mtbi_l, input_path("rm_subc_cor_long_mtbi_l.csv", date = TRUE))

rm_subc_cor_base_mtbi_l <- get_subc_cor(mri_y_rsfmr_cor_gp_aseg, base_mtbi_subs, t = 2)
tibble(rm_subc_cor_base_mtbi_l)
write_csv(rm_subc_cor_base_mtbi_l, input_path("rm_subc_cor_base_mtbi_l.csv", date = TRUE))

rm_subc_cor_base_unij_l <- get_subc_cor(mri_y_rsfmr_cor_gp_aseg, base_unij_subs, t = 2)
tibble(rm_subc_cor_base_unij_l)
write_csv(rm_subc_cor_base_unij_l, input_path("rm_subc_cor_base_unij_l.csv", date = TRUE))
```

### Psychosocial resilience

Psychosocial factors of interest include:

#### Loneliness

```{r}
p_friends_long_mtbi_0 <- get_friends(mh_y_or, gish_p_gi, long_mtbi_subs, discretize = TRUE, t = 0)
tibble(p_friends_long_mtbi_0)
write_csv(p_friends_long_mtbi_0, input_path("p_friends_long_mtbi_0.csv", TRUE))

p_friends_long_mtbi_l <- get_friends(mh_y_or, gish_p_gi, long_mtbi_subs, discretize = TRUE, t = 2)
tibble(p_friends_long_mtbi_l)
write_csv(p_friends_long_mtbi_l, input_path("p_friends_long_mtbi_l.csv", TRUE))

p_friends_base_mtbi_l <- get_friends(mh_y_or, gish_p_gi, base_mtbi_subs, discretize = TRUE, t = 2)
tibble(p_friends_base_mtbi_l)
write_csv(p_friends_base_mtbi_l, input_path("p_friends_base_mtbi_l.csv", TRUE))

p_friends_base_unij_l <- get_friends(mh_y_or, gish_p_gi, base_unij_subs, discretize = TRUE, t = 2)
tibble(p_friends_base_unij_l)
write_csv(p_friends_base_unij_l, input_path("p_friends_base_unij_l.csv", TRUE))
```

#### Healthy behaviours

##### Screen time

```{r}
p_screen_time_long_mtbi_0 <- get_screen_time(nt_p_stq, long_mtbi_subs, t = 0)
tibble(p_screen_time_long_mtbi_0)
write_csv(p_screen_time_long_mtbi_0, input_path("p_screen_time_long_mtbi_0.csv", TRUE))

p_screen_time_long_mtbi_l <- get_screen_time(nt_p_stq, long_mtbi_subs, t = 2)
tibble(p_screen_time_long_mtbi_l)
write_csv(p_screen_time_long_mtbi_l, input_path("p_screen_time_long_mtbi_l.csv", TRUE))

p_screen_time_base_mtbi_l <- get_screen_time(nt_p_stq, base_mtbi_subs, t = 2)
tibble(p_screen_time_base_mtbi_l)
write_csv(p_screen_time_base_mtbi_l, input_path("p_screen_time_base_mtbi_l.csv", TRUE))

p_screen_time_base_unij_l <- get_screen_time(nt_p_stq, base_unij_subs, t = 2)
tibble(p_screen_time_base_unij_l)
write_csv(p_screen_time_base_unij_l, input_path("p_screen_time_base_unij_l.csv", TRUE))
```

##### Sports and activities participation

```{r}
p_sports_long_mtbi_0 <- get_sports_and_activities(ph_p_saiq, long_mtbi_subs, t = 0, discretize = TRUE)
tibble(p_sports_long_mtbi_0)
write_csv(p_sports_long_mtbi_0, input_path("p_sports_long_mtbi_0.csv", TRUE))

p_sports_long_mtbi_l <- get_sports_and_activities(ph_p_saiq, long_mtbi_subs, t = 2, discretize = TRUE)
tibble(p_sports_long_mtbi_l)
write_csv(p_sports_long_mtbi_l, input_path("p_sports_long_mtbi_l.csv", TRUE))

p_sports_base_mtbi_l <- get_sports_and_activities(ph_p_saiq, base_mtbi_subs, t = 2, discretize = TRUE)
tibble(p_sports_base_mtbi_l)
write_csv(p_sports_base_mtbi_l, input_path("p_sports_base_mtbi_l.csv", TRUE))

p_sports_base_unij_l <- get_sports_and_activities(ph_p_saiq, base_unij_subs, t = 2, discretize = TRUE)
tibble(p_sports_base_unij_l)
write_csv(p_sports_base_unij_l, input_path("p_sports_base_unij_l.csv", TRUE))
```

##### Exercise habits

```{r}
p_exercise_long_mtbi_0 <- get_exercise(ph_y_yrb, long_mtbi_subs, t = 0)
tibble(p_exercise_long_mtbi_0)
write_csv(p_exercise_long_mtbi_0, input_path("p_exercise_long_mtbi_0.csv", date = TRUE))

p_exercise_long_mtbi_l <- get_exercise(ph_y_yrb, long_mtbi_subs, t = 2)
tibble(p_exercise_long_mtbi_l)
write_csv(p_exercise_long_mtbi_l, input_path("p_exercise_long_mtbi_l.csv", date = TRUE))

p_exercise_base_mtbi_l <- get_exercise(ph_y_yrb, base_mtbi_subs, t = 2)
tibble(p_exercise_base_mtbi_l)
write_csv(p_exercise_base_mtbi_l, input_path("p_exercise_base_mtbi_l.csv", date = TRUE))

p_exercise_base_unij_l <- get_exercise(ph_y_yrb, base_unij_subs, t = 2)
tibble(p_exercise_base_unij_l)
write_csv(p_exercise_base_unij_l, input_path("p_exercise_base_unij_l.csv", date = TRUE))
```

#### Prosocial behaviour

```{r}
p_prosocial_p_long_mtbi_0 <- get_prosocial_behaviour_p(ce_p_psb, long_mtbi_subs, t = 0)
p_prosocial_y_long_mtbi_0 <- get_prosocial_behaviour_y(ce_y_psb, long_mtbi_subs, t = 0)
p_prosocial_long_mtbi_0 <- dplyr::inner_join(p_prosocial_p_long_mtbi_0, p_prosocial_y_long_mtbi_0)
tibble(p_prosocial_long_mtbi_0)
write_csv(p_prosocial_long_mtbi_0, input_path("p_prosocial_long_mtbi_0.csv", date = TRUE))

p_prosocial_p_long_mtbi_l <- get_prosocial_behaviour_p(ce_p_psb, long_mtbi_subs, t = 2)
p_prosocial_y_long_mtbi_l <- get_prosocial_behaviour_y(ce_y_psb, long_mtbi_subs, t = 2)
p_prosocial_long_mtbi_l <- dplyr::inner_join(p_prosocial_p_long_mtbi_l, p_prosocial_y_long_mtbi_l)
tibble(p_prosocial_long_mtbi_l)
write_csv(p_prosocial_long_mtbi_l, input_path("p_prosocial_long_mtbi_l.csv", date = TRUE))

p_prosocial_p_base_mtbi_l <- get_prosocial_behaviour_p(ce_p_psb, base_mtbi_subs, t = 2)
p_prosocial_y_base_mtbi_l <- get_prosocial_behaviour_y(ce_y_psb, base_mtbi_subs, t = 2)
p_prosocial_base_mtbi_l <- dplyr::inner_join(p_prosocial_p_base_mtbi_l, p_prosocial_y_base_mtbi_l)
tibble(p_prosocial_base_mtbi_l)
write_csv(p_prosocial_base_mtbi_l, input_path("p_prosocial_base_mtbi_l.csv", date = TRUE))

p_prosocial_p_base_unij_l <- get_prosocial_behaviour_p(ce_p_psb, base_unij_subs, t = 2)
p_prosocial_y_base_unij_l <- get_prosocial_behaviour_y(ce_y_psb, base_unij_subs, t = 2)
p_prosocial_base_unij_l <- dplyr::inner_join(p_prosocial_p_base_unij_l, p_prosocial_y_base_unij_l)
tibble(p_prosocial_base_unij_l)
write_csv(p_prosocial_base_unij_l, input_path("p_prosocial_base_unij_l.csv", date = TRUE))
```

#### Family function

```{r}
p_fam_fn_long_mtbi_0 <- get_family_function(ce_y_fes, ce_p_fes, long_mtbi_subs, t = 0)
tibble(p_fam_fn_long_mtbi_0)
write_csv(p_fam_fn_long_mtbi_0, input_path("p_fam_fn_long_mtbi_0.csv", date = TRUE))

p_fam_fn_long_mtbi_l <- get_family_function(ce_y_fes, ce_p_fes, long_mtbi_subs, t = 2)
tibble(p_fam_fn_long_mtbi_l)
write_csv(p_fam_fn_long_mtbi_l, input_path("p_fam_fn_long_mtbi_l.csv", date = TRUE))

p_fam_fn_base_mtbi_l <- get_family_function(ce_y_fes, ce_p_fes, base_mtbi_subs, t = 2)
tibble(p_fam_fn_base_mtbi_l)
write_csv(p_fam_fn_base_mtbi_l, input_path("p_fam_fn_base_mtbi_l.csv", date = TRUE))

p_fam_fn_base_unij_l <- get_family_function(ce_y_fes, ce_p_fes, base_unij_subs, t = 2)
tibble(p_fam_fn_base_unij_l)
write_csv(p_fam_fn_base_unij_l, input_path("p_fam_fn_base_unij_l.csv", date = TRUE))
```

#### Parent psychopathology

```{r}
p_parent_psych_long_mtbi_0 <- get_parent_psychopathology(mh_p_asr, long_mtbi_subs, t = 0, raw = TRUE)
tibble(p_parent_psych_long_mtbi_0)

write_csv(p_parent_psych_long_mtbi_0, input_path("p_parent_psych_long_mtbi_0.csv", date = TRUE))

p_parent_psych_long_mtbi_l <- get_parent_psychopathology(mh_p_asr, long_mtbi_subs, t = 2, raw = TRUE)
tibble(p_parent_psych_long_mtbi_l)

write_csv(p_parent_psych_long_mtbi_l, input_path("p_parent_psych_long_mtbi_l.csv", date = TRUE))

p_parent_psych_base_mtbi_l <- get_parent_psychopathology(mh_p_asr, base_mtbi_subs, t = 2, raw = TRUE)
tibble(p_parent_psych_base_mtbi_l)

write_csv(p_parent_psych_base_mtbi_l, input_path("p_parent_psych_base_mtbi_l.csv", date = TRUE))

p_parent_psych_base_unij_l <- get_parent_psychopathology(mh_p_asr, base_unij_subs, t = 2, raw = TRUE)
tibble(p_parent_psych_base_unij_l)

write_csv(p_parent_psych_base_unij_l, input_path("p_parent_psych_base_unij_l.csv", date = TRUE))
```

## Output variables

### Child Behaviour Checklist

These are collected at both baseline and longitudinal timepoints.

```{r}
cbcl_long_mtbi_0 <- get_cbcl_syndrome_scale(mh_p_cbcl, long_mtbi_subs, t = 0, raw = TRUE)
tibble(cbcl_long_mtbi_0)
write_csv(cbcl_long_mtbi_0, input_path("cbcl_long_mtbi_0.csv", date = TRUE))

cbcl_long_mtbi_l <- get_cbcl_syndrome_scale(mh_p_cbcl, long_mtbi_subs, t = 2, raw = TRUE)
tibble(cbcl_long_mtbi_l)
write_csv(cbcl_long_mtbi_l, input_path("cbcl_long_mtbi_l.csv", date = TRUE))

cbcl_base_mtbi_l <- get_cbcl_syndrome_scale(mh_p_cbcl, base_mtbi_subs, t = 2, raw = TRUE)
tibble(cbcl_base_mtbi_l)
write_csv(cbcl_base_mtbi_l, input_path("cbcl_base_mtbi_l.csv", date = TRUE))

cbcl_base_unij_l <- get_cbcl_syndrome_scale(mh_p_cbcl, base_unij_subs, t = 2, raw = TRUE)
tibble(cbcl_base_unij_l)
write_csv(cbcl_base_unij_l, input_path("cbcl_base_unij_l.csv", date = TRUE))
```

### Sleep disturbance scale


```{r}
sds_long_mtbi_0 <- get_sds_total_probs(ph_p_sds, long_mtbi_subs, t = 0)
tibble(sds_long_mtbi_0)
write_csv(sds_long_mtbi_0, input_path("sds_long_mtbi_0.csv", date = TRUE))

sds_long_mtbi_l <- get_sds_total_probs(ph_p_sds, long_mtbi_subs, t = 2)
tibble(sds_long_mtbi_l)
write_csv(sds_long_mtbi_l, input_path("sds_long_mtbi_l.csv", date = TRUE))

sds_base_mtbi_l <- get_sds_total_probs(ph_p_sds, base_mtbi_subs, t = 2)
tibble(sds_base_mtbi_l)
write_csv(sds_base_mtbi_l, input_path("sds_base_mtbi_l.csv", date = TRUE))

sds_base_unij_l <- get_sds_total_probs(ph_p_sds, base_unij_subs, t = 2)
tibble(sds_base_unij_l)
write_csv(sds_base_unij_l, input_path("sds_base_unij_l.csv", date = TRUE))
```
