# metasnf over imputaions

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subjects <- read_csv(sub_path("2024_03_12_mtbi_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2024_03_12_uninjured_subjects.csv"))
mtbi_subjects_train <- read_csv(sub_path("2024_03_12_mtbi_train_subjects.csv"))

source("abcd/functions.R")
```

## Loading data and out of model lists

```{r}
data_list_m1 <- list.load(input_path("2024_03_12_data_list_m1.rds"))
data_list_m2 <- list.load(input_path("2024_03_12_data_list_m2.rds"))
data_list_m3 <- list.load(input_path("2024_03_12_data_list_m3.rds"))
data_list_m4 <- list.load(input_path("2024_03_12_data_list_m4.rds"))
data_list_m5 <- list.load(input_path("2024_03_12_data_list_m5.rds"))
data_list_pm1 <- list.load(input_path("2024_03_12_data_list_pm1.rds"))
data_list_pm2 <- list.load(input_path("2024_03_12_data_list_pm2.rds"))
data_list_pm3 <- list.load(input_path("2024_03_12_data_list_pm3.rds"))
data_list_pm4 <- list.load(input_path("2024_03_12_data_list_pm4.rds"))
data_list_pm5 <- list.load(input_path("2024_03_12_data_list_pm5.rds"))
oom_list_m1 <- list.load(input_path("2024_03_12_oom_list_m1.rds"))
oom_list_m2 <- list.load(input_path("2024_03_12_oom_list_m2.rds"))
oom_list_m3 <- list.load(input_path("2024_03_12_oom_list_m3.rds"))
oom_list_m4 <- list.load(input_path("2024_03_12_oom_list_m4.rds"))
oom_list_m5 <- list.load(input_path("2024_03_12_oom_list_m5.rds"))
oom_list_pm1 <- list.load(input_path("2024_03_12_oom_list_pm1.rds"))
oom_list_pm2 <- list.load(input_path("2024_03_12_oom_list_pm2.rds"))
oom_list_pm3 <- list.load(input_path("2024_03_12_oom_list_pm3.rds"))
oom_list_pm4 <- list.load(input_path("2024_03_12_oom_list_pm4.rds"))
oom_list_pm5 <- list.load(input_path("2024_03_12_oom_list_pm5.rds"))
```

## Generating custom distance measures

```{r}
###############################################################################
# 2. Add standard normalized variations to the distance metrics list (also
# achievable through toggling automatic_standard_normalize parameter in
# `batch_snf`)
###############################################################################
my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

summarize_distance_metrics_list(my_distance_metrics)
```

## Generating the settings matrix

```{r}

mtbi_settings_matrix <- generate_settings_matrix(
    data_list_m1,
    nrow = 200,
    seed = 42,
    distance_metrics_list = my_distance_metrics
)

write_csv(mtbi_settings_matrix, proc_path("mtbi_settings_matrix.csv", TRUE))

mtbi_settings_matrix <- read_csv(
    proc_path("2024_03_12_mtbi_settings_matrix.csv")
)

```

## SNF for each of the imputations

```{r}
# mTBI only imputed
# Imputation 1
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m1 <- batch_snf(
        data_list = data_list_m1,
        settings_matrix = mtbi_settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m1, proc_path("solutions_matrix_m1.csv", TRUE))
# Imputation 2
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m2 <- batch_snf(
        data_list = data_list_m2,
        settings_matrix = mtbi_settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m2, proc_path("solutions_matrix_m2.csv", TRUE))
# Imputation 3
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m3 <- batch_snf(
        data_list = data_list_m3,
        settings_matrix = mtbi_settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m3, proc_path("solutions_matrix_m3.csv", TRUE))
# Imputation 4
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m4 <- batch_snf(
        data_list = data_list_m4,
        settings_matrix = mtbi_settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m4, proc_path("solutions_matrix_m4.csv", TRUE))
# Imputation 5
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m5 <- batch_snf(
        data_list = data_list_m5,
        settings_matrix = mtbi_settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m5, proc_path("solutions_matrix_m5.csv", TRUE))
#
# mTBI and uninjured pooled imputed
# Imputation 1
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm1 <- batch_snf(
        data_list = data_list_pm1,
        settings_matrix = mtbi_settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm1, proc_path("solutions_matrix_pm1.csv", TRUE))
# Imputation 2
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm2 <- batch_snf(
        data_list = data_list_pm2,
        settings_matrix = mtbi_settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm2, proc_path("solutions_matrix_pm2.csv", TRUE))
# Imputation 3
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm3 <- batch_snf(
        data_list = data_list_pm3,
        settings_matrix = mtbi_settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm3, proc_path("solutions_matrix_pm3.csv", TRUE))
# Imputation 4
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm4 <- batch_snf(
        data_list = data_list_pm4,
        settings_matrix = mtbi_settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm4, proc_path("solutions_matrix_pm4.csv", TRUE))
# Imputation 5
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm5 <- batch_snf(
        data_list = data_list_pm5,
        settings_matrix = mtbi_settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm5, proc_path("solutions_matrix_pm5.csv", TRUE))
```

## Re-importing the generated solutions

```{r}
solutions_matrix_m1 <- read_csv(proc_path("2024_03_12_solutions_matrix_m1.csv"))
solutions_matrix_m2 <- read_csv(proc_path("2024_03_12_solutions_matrix_m2.csv"))
solutions_matrix_m3 <- read_csv(proc_path("2024_03_12_solutions_matrix_m3.csv"))
solutions_matrix_m4 <- read_csv(proc_path("2024_03_12_solutions_matrix_m4.csv"))
solutions_matrix_m5 <- read_csv(proc_path("2024_03_12_solutions_matrix_m5.csv"))
solutions_matrix_pm1 <- read_csv(proc_path("2024_03_12_solutions_matrix_pm1.csv"))
solutions_matrix_pm2 <- read_csv(proc_path("2024_03_12_solutions_matrix_pm2.csv"))
solutions_matrix_pm3 <- read_csv(proc_path("2024_03_12_solutions_matrix_pm3.csv"))
solutions_matrix_pm4 <- read_csv(proc_path("2024_03_12_solutions_matrix_pm4.csv"))
solutions_matrix_pm5 <- read_csv(proc_path("2024_03_12_solutions_matrix_pm5.csv"))

mtbi_sm <- do.call(
    "rbind",
    list(
        solutions_matrix_m1,
        solutions_matrix_m2,
        solutions_matrix_m3,
        solutions_matrix_m4,
        solutions_matrix_m5,
        solutions_matrix_pm1,
        solutions_matrix_pm2,
        solutions_matrix_pm3,
        solutions_matrix_pm4,
        solutions_matrix_pm5
    )
)

mtbi_ari <- calc_om_aris(mtbi_sm, processes = "max")
write_csv(data.frame(mtbi_ari), proc_path("mtbi_ari.csv", TRUE))
```

## Re-importing the ARIs

```{r}
mtbi_ari <- as.matrix(read_csv(proc_path("2024_03_12_mtbi_ari.csv")))
```

## Plotting the ARIs

### Initial plot across all ARIs to extract order

```{r}
mtbi_ari_order <- ari_order(mtbi_ari)
write_csv(data.frame(mtbi_ari_order), proc_path("mtbi_ari_order.csv", TRUE))
```

```{r}
mtbi_ari_order <- unlist(read_csv(proc_path("2024_03_12_mtbi_ari_order.csv")))
names(mtbi_ari_order) <- NULL
```

## Full imputation meta clustering plot with impairment levels

```{r}

imputation_labels <- data.frame(
    "imputation" = c(
        rep("m1", 200),
        rep("m2", 200),
        rep("m3", 200),
        rep("m4", 200),
        rep("m5", 200),
        rep("pm1", 200),
        rep("pm2", 200),
        rep("pm3", 200),
        rep("pm4", 200),
        rep("pm5", 200)
    ),
    "pooled" = c(
        rep("yes", 1000),
        rep("no", 1000)
    )
)

mtbi_sm <- cbind(mtbi_sm, imputation_labels)
```

```{r}
mtbi_o_esm <- extend_solutions(
    mtbi_sm,
    oom_list_m1,
    min_pval = 1e-10,
    processes = "max"
)
write_csv(mtbi_o_esm, proc_path("mtbi_o_esm.csv", TRUE))

mtbi_io_esm <- extend_solutions(
    mtbi_sm,
    target_list = c(data_list_m1, oom_list_m1),
    min_pval = 1e-10,
    processes = "max"
)
write_csv(mtbi_io_esm, proc_path("mtbi_io_esm.csv", TRUE))
```

The "o" is for just extending on the output variables (CBCL/SDS), while the "io" is for both input and output variables.

```{r}
mtbi_o_esm <- read_csv(proc_path("2024_03_12_mtbi_io_esm.csv"))
mtbi_io_esm <- read_csv(proc_path("2024_03_12_mtbi_io_esm.csv"))
```

```{r}

mtbi_split_vec <- c(280, 420, 850, 1115, 1780)

write_csv(data.frame(mtbi_split_vec), proc_path("mtbi_split_vec.csv", TRUE))
mtbi_split_vec <- read_csv(proc_path("2024_03_12_mtbi_split_vec.csv")) |>
    unlist() |>
    as.numeric()

mtbi_mc_heatmap <- my_similarity_matrix_heatmap(
    aris = mtbi_ari,
    aris_order = mtbi_ari_order,
    extended_solutions = mtbi_o_esm,
    split_vector = split_vec
)
mtbi_mc_heatmap

mc_heatmap_save(mtbi_mc_heatmap, fig_path("mtbi_mc_heatmap.png", TRUE))
```

## One-MC-at-a-time

```{r}
my_manhattan_bulk_save(
    solutions_matrix = mtbi_io_esm,
    ari_order = mtbi_ari_order,
    split_vector = mtbi_split_vec,
    data_list = data_list_m1,
    target_list = oom_list_m1,
    prefix = "mtbi"
)
```

## Replication in demographic-corrected data

```{r}

data_list_m1 <- list.load(input_path("2024_03_12_data_list_m1.rds"))
data_list_m2 <- list.load(input_path("2024_03_12_data_list_m2.rds"))
data_list_m3 <- list.load(input_path("2024_03_12_data_list_m3.rds"))
data_list_m4 <- list.load(input_path("2024_03_12_data_list_m4.rds"))
data_list_m5 <- list.load(input_path("2024_03_12_data_list_m5.rds"))
data_list_pm1 <- list.load(input_path("2024_03_12_data_list_pm1.rds"))
data_list_pm2 <- list.load(input_path("2024_03_12_data_list_pm2.rds"))
data_list_pm3 <- list.load(input_path("2024_03_12_data_list_pm3.rds"))
data_list_pm4 <- list.load(input_path("2024_03_12_data_list_pm4.rds"))
data_list_pm5 <- list.load(input_path("2024_03_12_data_list_pm5.rds"))
oom_list_m1 <- list.load(input_path("2024_03_12_oom_list_m1.rds"))
oom_list_m2 <- list.load(input_path("2024_03_12_oom_list_m2.rds"))
oom_list_m3 <- list.load(input_path("2024_03_12_oom_list_m3.rds"))
oom_list_m4 <- list.load(input_path("2024_03_12_oom_list_m4.rds"))
oom_list_m5 <- list.load(input_path("2024_03_12_oom_list_m5.rds"))
oom_list_pm1 <- list.load(input_path("2024_03_12_oom_list_pm1.rds"))
oom_list_pm2 <- list.load(input_path("2024_03_12_oom_list_pm2.rds"))
oom_list_pm3 <- list.load(input_path("2024_03_12_oom_list_pm3.rds"))
oom_list_pm4 <- list.load(input_path("2024_03_12_oom_list_pm4.rds"))
oom_list_pm5 <- list.load(input_path("2024_03_12_oom_list_pm5.rds"))

# demo_lists just contain the demographic variables
demo_list_m1 <- data_list_m1[summarize_dl(data_list_m1)$"domain" == "D"]
demo_list_m2 <- data_list_m2[summarize_dl(data_list_m2)$"domain" == "D"]
demo_list_m3 <- data_list_m3[summarize_dl(data_list_m3)$"domain" == "D"]
demo_list_m4 <- data_list_m4[summarize_dl(data_list_m4)$"domain" == "D"]
demo_list_m5 <- data_list_m5[summarize_dl(data_list_m5)$"domain" == "D"]
demo_list_pm1 <- data_list_pm1[summarize_dl(data_list_pm1)$"domain" == "D"]
demo_list_pm2 <- data_list_pm2[summarize_dl(data_list_pm2)$"domain" == "D"]
demo_list_pm3 <- data_list_pm3[summarize_dl(data_list_pm3)$"domain" == "D"]
demo_list_pm4 <- data_list_pm4[summarize_dl(data_list_pm4)$"domain" == "D"]
demo_list_pm5 <- data_list_pm5[summarize_dl(data_list_pm5)$"domain" == "D"]

# categorical lists just contain the categorical variables
cat_list_m1 <- data_list_m1[summarize_dl(data_list_m1)$"type" == "categorical"]
cat_list_m2 <- data_list_m2[summarize_dl(data_list_m2)$"type" == "categorical"]
cat_list_m3 <- data_list_m3[summarize_dl(data_list_m3)$"type" == "categorical"]
cat_list_m4 <- data_list_m4[summarize_dl(data_list_m4)$"type" == "categorical"]
cat_list_m5 <- data_list_m5[summarize_dl(data_list_m5)$"type" == "categorical"]
cat_list_pm1 <- data_list_pm1[summarize_dl(data_list_pm1)$"type" == "categorical"]
cat_list_pm2 <- data_list_pm2[summarize_dl(data_list_pm2)$"type" == "categorical"]
cat_list_pm3 <- data_list_pm3[summarize_dl(data_list_pm3)$"type" == "categorical"]
cat_list_pm4 <- data_list_pm4[summarize_dl(data_list_pm4)$"type" == "categorical"]
cat_list_pm5 <- data_list_pm5[summarize_dl(data_list_pm5)$"type" == "categorical"]

# copies of the data_lists
data_list_nd_m1 <- data_list_m1
data_list_nd_m2 <- data_list_m2
data_list_nd_m3 <- data_list_m3
data_list_nd_m4 <- data_list_m4
data_list_nd_m5 <- data_list_m5
data_list_nd_pm1 <- data_list_pm1
data_list_nd_pm2 <- data_list_pm2
data_list_nd_pm3 <- data_list_pm3
data_list_nd_pm4 <- data_list_pm4
data_list_nd_pm5 <- data_list_pm5
oom_list_nd_m1 <- oom_list_m1
oom_list_nd_m2 <- oom_list_m2
oom_list_nd_m3 <- oom_list_m3
oom_list_nd_m4 <- oom_list_m4
oom_list_nd_m5 <- oom_list_m5
oom_list_nd_pm1 <- oom_list_pm1
oom_list_nd_pm2 <- oom_list_pm2
oom_list_nd_pm3 <- oom_list_pm3
oom_list_nd_pm4 <- oom_list_pm4
oom_list_nd_pm5 <- oom_list_pm5

# Removing the demographic variables from the copies of the data lists
data_list_nd_m1[summarize_dl(data_list_nd_m1)$"domain" == "D"] <- NULL
data_list_nd_m2[summarize_dl(data_list_nd_m2)$"domain" == "D"] <- NULL
data_list_nd_m3[summarize_dl(data_list_nd_m3)$"domain" == "D"] <- NULL
data_list_nd_m4[summarize_dl(data_list_nd_m4)$"domain" == "D"] <- NULL
data_list_nd_m5[summarize_dl(data_list_nd_m5)$"domain" == "D"] <- NULL
data_list_nd_pm1[summarize_dl(data_list_nd_pm1)$"domain" == "D"] <- NULL
data_list_nd_pm2[summarize_dl(data_list_nd_pm2)$"domain" == "D"] <- NULL
data_list_nd_pm3[summarize_dl(data_list_nd_pm3)$"domain" == "D"] <- NULL
data_list_nd_pm4[summarize_dl(data_list_nd_pm4)$"domain" == "D"] <- NULL
data_list_nd_pm5[summarize_dl(data_list_nd_pm5)$"domain" == "D"] <- NULL

# Remove any categorical variables from the copies of the data lists
data_list_nd_m1[summarize_dl(data_list_nd_m1)$"type" == "categorical"] <- NULL
data_list_nd_m2[summarize_dl(data_list_nd_m2)$"type" == "categorical"] <- NULL
data_list_nd_m3[summarize_dl(data_list_nd_m3)$"type" == "categorical"] <- NULL
data_list_nd_m4[summarize_dl(data_list_nd_m4)$"type" == "categorical"] <- NULL
data_list_nd_m5[summarize_dl(data_list_nd_m5)$"type" == "categorical"] <- NULL
data_list_nd_pm1[summarize_dl(data_list_nd_pm1)$"type" == "categorical"] <- NULL
data_list_nd_pm2[summarize_dl(data_list_nd_pm2)$"type" == "categorical"] <- NULL
data_list_nd_pm3[summarize_dl(data_list_nd_pm3)$"type" == "categorical"] <- NULL
data_list_nd_pm4[summarize_dl(data_list_nd_pm4)$"type" == "categorical"] <- NULL
data_list_nd_pm5[summarize_dl(data_list_nd_pm5)$"type" == "categorical"] <- NULL

data_list_nd_m1 <- remove_signal(data_list_nd_m1, demo_list_m1, sig_digs = 3)
data_list_nd_m2 <- remove_signal(data_list_nd_m2, demo_list_m2, sig_digs = 3)
data_list_nd_m3 <- remove_signal(data_list_nd_m3, demo_list_m3, sig_digs = 3)
data_list_nd_m4 <- remove_signal(data_list_nd_m4, demo_list_m4, sig_digs = 3)
data_list_nd_m5 <- remove_signal(data_list_nd_m5, demo_list_m5, sig_digs = 3)
data_list_nd_pm1 <- remove_signal(data_list_nd_pm1, demo_list_pm1, sig_digs = 3)
data_list_nd_pm2 <- remove_signal(data_list_nd_pm2, demo_list_pm2, sig_digs = 3)
data_list_nd_pm3 <- remove_signal(data_list_nd_pm3, demo_list_pm3, sig_digs = 3)
data_list_nd_pm4 <- remove_signal(data_list_nd_pm4, demo_list_pm4, sig_digs = 3)
data_list_nd_pm5 <- remove_signal(data_list_nd_pm5, demo_list_pm5, sig_digs = 3)
oom_list_nd_m1 <- remove_signal(oom_list_nd_m1, demo_list_m1, sig_digs = 3)
oom_list_nd_m2 <- remove_signal(oom_list_nd_m2, demo_list_m2, sig_digs = 3)
oom_list_nd_m3 <- remove_signal(oom_list_nd_m3, demo_list_m3, sig_digs = 3)
oom_list_nd_m4 <- remove_signal(oom_list_nd_m4, demo_list_m4, sig_digs = 3)
oom_list_nd_m5 <- remove_signal(oom_list_nd_m5, demo_list_m5, sig_digs = 3)
oom_list_nd_pm1 <- remove_signal(oom_list_nd_pm1, demo_list_pm1, sig_digs = 3)
oom_list_nd_pm2 <- remove_signal(oom_list_nd_pm2, demo_list_pm2, sig_digs = 3)
oom_list_nd_pm3 <- remove_signal(oom_list_nd_pm3, demo_list_pm3, sig_digs = 3)
oom_list_nd_pm4 <- remove_signal(oom_list_nd_pm4, demo_list_pm4, sig_digs = 3)
oom_list_nd_pm5 <- remove_signal(oom_list_nd_pm5, demo_list_pm5, sig_digs = 3)

# Adding back the demographic variables post-correction
data_list_rd_m1 <- unique(c(data_list_nd_m1, demo_list_m1, cat_list_m1))
data_list_rd_m2 <- unique(c(data_list_nd_m2, demo_list_m2, cat_list_m2))
data_list_rd_m3 <- unique(c(data_list_nd_m3, demo_list_m3, cat_list_m3))
data_list_rd_m4 <- unique(c(data_list_nd_m4, demo_list_m4, cat_list_m4))
data_list_rd_m5 <- unique(c(data_list_nd_m5, demo_list_m5, cat_list_m5))
data_list_rd_pm1 <- unique(c(data_list_nd_pm1, demo_list_pm1, cat_list_pm1))
data_list_rd_pm2 <- unique(c(data_list_nd_pm2, demo_list_pm2, cat_list_pm2))
data_list_rd_pm3 <- unique(c(data_list_nd_pm3, demo_list_pm3, cat_list_pm3))
data_list_rd_pm4 <- unique(c(data_list_nd_pm4, demo_list_pm4, cat_list_pm4))
data_list_rd_pm5 <- unique(c(data_list_nd_pm5, demo_list_pm5, cat_list_pm5))


list.save(data_list_nd_m1, input_path("data_list_nd_m1.rds", TRUE))
list.save(data_list_nd_m2, input_path("data_list_nd_m2.rds", TRUE))
list.save(data_list_nd_m3, input_path("data_list_nd_m3.rds", TRUE))
list.save(data_list_nd_m4, input_path("data_list_nd_m4.rds", TRUE))
list.save(data_list_nd_m5, input_path("data_list_nd_m5.rds", TRUE))
list.save(data_list_nd_pm1, input_path("data_list_nd_pm1.rds", TRUE))
list.save(data_list_nd_pm2, input_path("data_list_nd_pm2.rds", TRUE))
list.save(data_list_nd_pm3, input_path("data_list_nd_pm3.rds", TRUE))
list.save(data_list_nd_pm4, input_path("data_list_nd_pm4.rds", TRUE))
list.save(data_list_nd_pm5, input_path("data_list_nd_pm5.rds", TRUE))

list.save(data_list_rd_m1, input_path("data_list_rd_m1.rds", TRUE))
list.save(data_list_rd_m2, input_path("data_list_rd_m2.rds", TRUE))
list.save(data_list_rd_m3, input_path("data_list_rd_m3.rds", TRUE))
list.save(data_list_rd_m4, input_path("data_list_rd_m4.rds", TRUE))
list.save(data_list_rd_m5, input_path("data_list_rd_m5.rds", TRUE))
list.save(data_list_rd_pm1, input_path("data_list_rd_pm1.rds", TRUE))
list.save(data_list_rd_pm2, input_path("data_list_rd_pm2.rds", TRUE))
list.save(data_list_rd_pm3, input_path("data_list_rd_pm3.rds", TRUE))
list.save(data_list_rd_pm4, input_path("data_list_rd_pm4.rds", TRUE))
list.save(data_list_rd_pm5, input_path("data_list_rd_pm5.rds", TRUE))

list.save(oom_list_nd_m1, input_path("oom_list_nd_m1.rds", TRUE))
list.save(oom_list_nd_m2, input_path("oom_list_nd_m2.rds", TRUE))
list.save(oom_list_nd_m3, input_path("oom_list_nd_m3.rds", TRUE))
list.save(oom_list_nd_m4, input_path("oom_list_nd_m4.rds", TRUE))
list.save(oom_list_nd_m5, input_path("oom_list_nd_m5.rds", TRUE))
list.save(oom_list_nd_pm1, input_path("oom_list_nd_pm1.rds", TRUE))
list.save(oom_list_nd_pm2, input_path("oom_list_nd_pm2.rds", TRUE))
list.save(oom_list_nd_pm3, input_path("oom_list_nd_pm3.rds", TRUE))
list.save(oom_list_nd_pm4, input_path("oom_list_nd_pm4.rds", TRUE))
list.save(oom_list_nd_pm5, input_path("oom_list_nd_pm5.rds", TRUE))

```


```{r}
data_list_nd_m1 <- list.load(input_path("2024_03_14_data_list_nd_m1.rds"))
data_list_nd_m2 <- list.load(input_path("2024_03_14_data_list_nd_m2.rds"))
data_list_nd_m3 <- list.load(input_path("2024_03_14_data_list_nd_m3.rds"))
data_list_nd_m4 <- list.load(input_path("2024_03_14_data_list_nd_m4.rds"))
data_list_nd_m5 <- list.load(input_path("2024_03_14_data_list_nd_m5.rds"))
data_list_nd_pm1 <- list.load(input_path("2024_03_14_data_list_nd_pm1.rds"))
data_list_nd_pm2 <- list.load(input_path("2024_03_14_data_list_nd_pm2.rds"))
data_list_nd_pm3 <- list.load(input_path("2024_03_14_data_list_nd_pm3.rds"))
data_list_nd_pm4 <- list.load(input_path("2024_03_14_data_list_nd_pm4.rds"))
data_list_nd_pm5 <- list.load(input_path("2024_03_14_data_list_nd_pm5.rds"))

data_list_rd_m1 <- list.load(input_path("2024_03_14_data_list_rd_m1.rds"))
data_list_rd_m2 <- list.load(input_path("2024_03_14_data_list_rd_m2.rds"))
data_list_rd_m3 <- list.load(input_path("2024_03_14_data_list_rd_m3.rds"))
data_list_rd_m4 <- list.load(input_path("2024_03_14_data_list_rd_m4.rds"))
data_list_rd_m5 <- list.load(input_path("2024_03_14_data_list_rd_m5.rds"))
data_list_rd_pm1 <- list.load(input_path("2024_03_14_data_list_rd_pm1.rds"))
data_list_rd_pm2 <- list.load(input_path("2024_03_14_data_list_rd_pm2.rds"))
data_list_rd_pm3 <- list.load(input_path("2024_03_14_data_list_rd_pm3.rds"))
data_list_rd_pm4 <- list.load(input_path("2024_03_14_data_list_rd_pm4.rds"))
data_list_rd_pm5 <- list.load(input_path("2024_03_14_data_list_rd_pm5.rds"))

oom_list_nd_m1 <- list.load(input_path("2024_03_14_oom_list_nd_m1.rds"))
oom_list_nd_m2 <- list.load(input_path("2024_03_14_oom_list_nd_m2.rds"))
oom_list_nd_m3 <- list.load(input_path("2024_03_14_oom_list_nd_m3.rds"))
oom_list_nd_m4 <- list.load(input_path("2024_03_14_oom_list_nd_m4.rds"))
oom_list_nd_m5 <- list.load(input_path("2024_03_14_oom_list_nd_m5.rds"))
oom_list_nd_pm1 <- list.load(input_path("2024_03_14_oom_list_nd_pm1.rds"))
oom_list_nd_pm2 <- list.load(input_path("2024_03_14_oom_list_nd_pm2.rds"))
oom_list_nd_pm3 <- list.load(input_path("2024_03_14_oom_list_nd_pm3.rds"))
oom_list_nd_pm4 <- list.load(input_path("2024_03_14_oom_list_nd_pm4.rds"))
oom_list_nd_pm5 <- list.load(input_path("2024_03_14_oom_list_nd_pm5.rds"))
```

Showing that the demographic variables have been removed from the data list.

Chunk below should be re-run outside of HPC

```{r}

fdl <- c(data_list_m1, oom_list_m1)

race_pos <- which(summarize_dl(fdl)$"name" == "d_race")
mech_pos <- which(summarize_dl(fdl)$"name" == "as_mechanism")

fdl[[race_pos]]$"data" <- fdl[[race_pos]]$"data" |>
    fastDummies::dummy_cols(
        "race",
        remove_first_dummy = TRUE,
        remove_selected_columns = TRUE
    )

fdl[[mech_pos]]$"data" <- fdl[[mech_pos]]$"data" |>
    fastDummies::dummy_cols(
        "mtbi_mechanism",
        remove_first_dummy = TRUE,
        remove_selected_columns = TRUE
    )

m1_corr_data <- correlation_data(fdl)
m1_corr_mat <- m1_corr_data$"correlation_matrix"
corr_order <- colnames(m1_corr_mat)[m1_corr_data$"order"]
write_csv(data.frame(corr_order), proc_path("mtbi_corr_order.csv", TRUE))

corr_order <- read_csv(proc_path("2024_03_14_mtbi_corr_order.csv"))

m_corr <- my_corr_plot(
    data_list_m1,
    oom_list_m1,
    order = corr_order
)

save_png(
    m_corr$"heatmap",
    fig_path("m_corr_heatmap.png", TRUE),
    width = 2000,
    height = 2000
)

pm_corr <- my_corr_plot(
    data_list_pm2,
    oom_list_pm2,
    order = corr_order
)
save_png(
    pm_corr$"heatmap",
    fig_path("pm_corr_heatmap.png", TRUE),
    width = 2000,
    height = 2000
)

# m vs. pm
m_vs_pm_corr_hm <- diff_heatmap(
    m_corr$"correlation_matrix",
    pm_corr$"correlation_matrix"
)
save_png(
    m_vs_pm_corr_hm,
    fig_path("m_vs_pm_corr_heatmap.png", TRUE),
    width = 2000,
    height = 2000
)

abs_m_vs_pm_corr_hm <- diff_heatmap(
    m_corr$"correlation_matrix",
    pm_corr$"correlation_matrix",
    abs = TRUE
)

save_png(
    abs_m_vs_pm_corr_hm,
    fig_path("abs_m_vs_pm_corr_heatmap.png", TRUE),
    width = 2000,
    height = 2000
)
nd_m_corr <- my_corr_plot(
    data_list_rd_m1,
    oom_list_no_demo_m1,
    order = corr_order
)
save_png(
    nd_m_corr$"heatmap",
    fig_path("nd_m_corr_heatmap.png", TRUE),
    width = 2000,
    height = 2000
)

```

```{r}

nd_settings_matrix <- generate_settings_matrix(
    data_list_nd_m1,
    nrow = 200,
    seed = 42,
    distance_metrics_list = my_distance_metrics
)

write_csv(nd_settings_matrix, proc_path("nd_settings_matrix.csv", TRUE))

nd_settings_matrix <- read_csv(proc_path("2024_03_14_nd_settings_matrix.csv"))
```

```{r}
# Imputation 1
start <- proc.time()
progressr::with_progress({
    solutions_matrix_nd_m1 <- batch_snf(
        data_list = data_list_nd_m1,
        settings_matrix = nd_settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_nd_m1,
    proc_path("solutions_matrix_nd_m1.csv", TRUE)
)
# Imputation 2
start <- proc.time()
progressr::with_progress({
    solutions_matrix_nd_m2 <- batch_snf(
        data_list = data_list_nd_m2,
        settings_matrix = nd_settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_nd_m2,
    proc_path("solutions_matrix_nd_m2.csv", TRUE)
)
# Imputation 3
start <- proc.time()
progressr::with_progress({
    solutions_matrix_nd_m3 <- batch_snf(
        data_list = data_list_nd_m3,
        settings_matrix = nd_settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_nd_m3,
    proc_path("solutions_matrix_nd_m3.csv", TRUE)
)
# Imputation 4
start <- proc.time()
progressr::with_progress({
    solutions_matrix_nd_m4 <- batch_snf(
        data_list = data_list_nd_m4,
        settings_matrix = nd_settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_nd_m4,
    proc_path("solutions_matrix_nd_m4.csv", TRUE)
)
# Imputation 5
start <- proc.time()
progressr::with_progress({
    solutions_matrix_nd_m5 <- batch_snf(
        data_list = data_list_nd_m5,
        settings_matrix = nd_settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_nd_m5,
    proc_path("solutions_matrix_nd_m5.csv", TRUE)
)
# mTBI and uninjured pooled imputed
# Imputation 1
start <- proc.time()
progressr::with_progress({
    solutions_matrix_nd_pm1 <- batch_snf(
        data_list = data_list_nd_pm1,
        settings_matrix = nd_settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_nd_pm1,
    proc_path("solutions_matrix_nd_pm1.csv", TRUE)
)
# Imputation 2
start <- proc.time()
progressr::with_progress({
    solutions_matrix_nd_pm2 <- batch_snf(
        data_list = data_list_nd_pm2,
        settings_matrix = nd_settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_nd_pm2,
    proc_path("solutions_matrix_nd_pm2.csv", TRUE)
)
# Imputation 3
start <- proc.time()
progressr::with_progress({
    solutions_matrix_nd_pm3 <- batch_snf(
        data_list = data_list_nd_pm3,
        settings_matrix = nd_settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_nd_pm3,
    proc_path("solutions_matrix_nd_pm3.csv", TRUE)
)
# Imputation 4
start <- proc.time()
progressr::with_progress({
    solutions_matrix_nd_pm4 <- batch_snf(
        data_list = data_list_nd_pm4,
        settings_matrix = nd_settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_nd_pm4,
    proc_path("solutions_matrix_nd_pm4.csv", TRUE)
)
# Imputation 5
start <- proc.time()
progressr::with_progress({
    solutions_matrix_nd_pm5 <- batch_snf(
        data_list = data_list_nd_pm5,
        settings_matrix = nd_settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_nd_pm5,
    proc_path("solutions_matrix_nd_pm5.csv", TRUE)
)
```

```{r}
solutions_matrix_nd_m1 <- read_csv(proc_path("2024_03_14_solutions_matrix_nd_m1.csv"))
solutions_matrix_nd_m2 <- read_csv(proc_path("2024_03_14_solutions_matrix_nd_m2.csv"))
solutions_matrix_nd_m3 <- read_csv(proc_path("2024_03_14_solutions_matrix_nd_m3.csv"))
solutions_matrix_nd_m4 <- read_csv(proc_path("2024_03_14_solutions_matrix_nd_m4.csv"))
solutions_matrix_nd_m5 <- read_csv(proc_path("2024_03_14_solutions_matrix_nd_m5.csv"))
solutions_matrix_nd_pm1 <- read_csv(proc_path("2024_03_14_solutions_matrix_nd_pm1.csv"))
solutions_matrix_nd_pm2 <- read_csv(proc_path("2024_03_14_solutions_matrix_nd_pm2.csv"))
solutions_matrix_nd_pm3 <- read_csv(proc_path("2024_03_14_solutions_matrix_nd_pm3.csv"))
solutions_matrix_nd_pm4 <- read_csv(proc_path("2024_03_14_solutions_matrix_nd_pm4.csv"))
solutions_matrix_nd_pm5 <- read_csv(proc_path("2024_03_14_solutions_matrix_nd_pm5.csv"))

mtbi_nd_sm <- do.call(
    "rbind",
    list(
        solutions_matrix_nd_m1,
        solutions_matrix_nd_m2,
        solutions_matrix_nd_m3,
        solutions_matrix_nd_m4,
        solutions_matrix_nd_m5,
        solutions_matrix_nd_pm1,
        solutions_matrix_nd_pm2,
        solutions_matrix_nd_pm3,
        solutions_matrix_nd_pm4,
        solutions_matrix_nd_pm5
    )
)

```

```{r}
mtbi_nd_ari <- calc_om_aris(mtbi_nd_sm, processes = "max")
write_csv(data.frame(mtbi_nd_ari), proc_path("mtbi_nd_ari.csv", TRUE))
```

```{r}
mtbi_nd_ari <- read_csv(proc_path("2024_03_14_mtbi_nd_ari.csv")) |> as.matrix()
```

```{r}
mtbi_nd_ari_order <- ari_order(mtbi_nd_ari)
write_csv(data.frame(mtbi_nd_ari_order), proc_path("mtbi_nd_ari_order.csv", TRUE))
```

```{r}
mtbi_nd_ari_order <- unlist(read_csv(proc_path("2024_03_14_mtbi_nd_ari_order.csv")))
names(mtbi_nd_ari_order) <- NULL
```

## Full imputation meta clustering plot with impairment levels

```{r}
imputation_labels <- data.frame(
    "imputation" = c(
        rep("m1", 200),
        rep("m2", 200),
        rep("m3", 200),
        rep("m4", 200),
        rep("m5", 200),
        rep("pm1", 200),
        rep("pm2", 200),
        rep("pm3", 200),
        rep("pm4", 200),
        rep("pm5", 200)
    ),
    "pooled" = c(
        rep("yes", 1000),
        rep("no", 1000)
    )
)

mtbi_nd_sm <- cbind(mtbi_nd_sm, imputation_labels)
```

```{r}

mtbi_nd_i_esm <- extend_solutions(
    mtbi_nd_sm,
    data_list_nd_m1,
    min_pval = 1e-10,
    processes = "max"
)
write_csv(mtbi_nd_i_esm, proc_path("mtbi_nd_i_esm.csv", TRUE))

mtbi_nd_o_esm <- extend_solutions(
    mtbi_nd_sm,
    oom_list_nd_m1,
    min_pval = 1e-10,
    processes = "max"
)
write_csv(mtbi_nd_o_esm, proc_path("mtbi_nd_o_esm.csv", TRUE))


colnames(mtbi_nd_sm)

summarize_dl(data_list_rd_m1)

mtbi_nd_io_esm <- extend_solutions(
    mtbi_nd_sm,
    target_list = c(data_list_rd_m1, oom_list_nd_m1),
    min_pval = 1e-10,
    processes = "max"
)
write_csv(mtbi_nd_io_esm, proc_path("mtbi_nd_io_esm.csv", TRUE))

```

```{r}
mtbi_nd_i_esm <- read_csv(proc_path("2024_03_14_mtbi_nd_i_esm.csv"))
mtbi_nd_o_esm <- read_csv(proc_path("2024_03_14_mtbi_nd_o_esm.csv"))
mtbi_nd_io_esm <- read_csv(proc_path("2024_03_14_mtbi_nd_io_esm.csv"))
```

```{r}

mtbi_nd_split_vec <- c(
    340,
    520,
    725,
    770,
    1030,
    1175,
    1770
)
mtbi_nd_mc_heatmap <- my_similarity_matrix_heatmap(
    aris = mtbi_nd_ari,
    aris_order = mtbi_nd_ari_order,
    extended_solutions = mtbi_nd_o_esm,
    split_vector = mtbi_nd_split_vec
)

mtbi_nd_mc_heatmap

mc_heatmap_save(mtbi_nd_mc_heatmap, fig_path("mtbi_nd_mc_heatmap.png", TRUE))

```

MCs A, B, D, F, and H look most robust.

```{r}
write_csv(data.frame(mtbi_nd_split_vec), proc_path("mtbi_nd_split_vec.csv", TRUE))
mtbi_nd_split_vec <- read_csv(proc_path("2024_03_14_mtbi_nd_split_vec.csv")) |>
    unlist() |>
    as.numeric()
```


## One-MC-at-a-time

```{r}

mtbi_nd_manhattan <- my_manhattan_plot(
    solutions_matrix = mtbi_nd_io_esm,
    aris_order = mtbi_nd_ari_order,
    split_vector = mtbi_nd_split_vec,
    data_list = data_list_rd_m1,
    target_list = oom_list_nd_m1,
    colours = c(
        "I-AS" = "#1B9E77",
        "I-D" = "#D95F02",
        "I-N" = "#7570B3",
        "I-MH" = "#E7298A",
        "I-P" = "#66A61E",
        "O-S" = "#E6AB02",
        "O-B" = "#A6761D"
    )
)
mtbi_nd_manhattan

rep_solutions <- get_rep_solutions(
    mtbi_nd_split_vec,
    mtbi_nd_ari,
    mtbi_nd_ari_order,
    mtbi_nd_io_esm
)

rep_solutions$"label" <- rep_solutions$"mc"

manhattan_plot2(
    rep_solutions,
    data_list = c(data_list_rd_m1, oom_list_nd_m1)
)

rep_solutions

q <- collapse_dl(data_list_rd_m1)


q |>
    ggplot(aes(x = age, y = mtbi_age)) +
    geom_jitter() +
    geom_smooth(method = "lm", se = FALSE, color = "red")

ggplot(df, aes(x = x, y = y)) +
  geom_point() +  # Scatter plot

a_df <- get_cluster_df(rep_solutions[1, ])
rd_dl <- collapse_dl(data_list_rd_m1)

eval_df <- dplyr::inner_join(a_df, rd_dl, by = "subjectkey")
eval_df$"cluster" <- factor(eval_df$"cluster")

eval_df |>
    ggplot(aes(x = cluster, y = age)) +
    geom_boxplot()

get_cluster_pval(
    a_df,
    rd_dl,
    "discrete",
    "age"
)

mtbi_nd_manhattan <- my_manhattan_plot(
    solutions_matrix = mtbi_nd_io_esm,
    aris_order = mtbi_nd_ari_order,
    mcs = "A",
    split_vector = mtbi_nd_split_vec,
    data_list = data_list_rd_m1,
    target_list = oom_list_nd_m1,
    colours = c(
        "I-AS" = "#1B9E77",
        "I-D" = "#D95F02",
        "I-N" = "#7570B3",
        "I-MH" = "#E7298A",
        "I-P" = "#66A61E",
        "O-S" = "#E6AB02",
        "O-B" = "#A6761D"
    )
)

mtbi_nd_manhattan

select_solution(mtbi_nd_io_esm, 139, "m3") |>
    pval_select()

which(mtbi_nd_io_esm$"opp_sex_friend_p" == min(mtbi_nd_io_esm$"opp_sex_friend_p"))

z <- mtbi_nd_io_esm[c(204, 205),  ]

z$"mc_label" <- "A"
manhattan_plot(
    z,
    data_list = data_list_rd_m1
)

my_manhattan_bulk_save(
    split_vector = mtbi_nd_split_vec,
    solutions_matrix = mtbi_nd_io_esm,
    ari_order = mtbi_nd_ari_order,
    data_list = data_list_rd_m1,
    target_list = oom_list_nd_m1,
    "mtbi_nd"
)

data_list_rd_m1 |> summarize_dl()


mtbi_nd_io_esm <- read_csv(proc_path("2024_03_14_mtbi_nd_io_esm.csv"))
mtbi_nd_ari <- read_csv(proc_path("2024_03_14_mtbi_nd_ari.csv"))
mtbi_nd_ari_order <- read_csv(proc_path("2024_03_14_mtbi_nd_ari_order.csv"))
mtbi_nd_split_vec <- read_csv(proc_path("2024_03_14_mtbi_nd_split_vec.csv")) |>
    unlist() |>
    as.numeric()

# MTBI-ND
representative_mc(
    split_vector = mtbi_nd_split_vec,
    aris = mtbi_nd_ari,
    ari_order = mtbi_nd_ari_order,
    solutions_matrix = mtbi_nd_io_esm,
    group_name = "mtbi_nd",
    possible_data = list(
        "m1" = c(data_list_rd_m1, oom_list_nd_m1),
        "m2" = c(data_list_rd_m2, oom_list_nd_m2),
        "m3" = c(data_list_rd_m3, oom_list_nd_m3),
        "m4" = c(data_list_rd_m4, oom_list_nd_m4),
        "m5" = c(data_list_rd_m5, oom_list_nd_m5),
        "pm5" = c(data_list_rd_pm5, oom_list_nd_pm5),
        "pm1" = c(data_list_rd_pm1, oom_list_nd_pm1),
        "pm2" = c(data_list_rd_pm2, oom_list_nd_pm2),
        "pm3" = c(data_list_rd_pm3, oom_list_nd_pm3),
        "pm4" = c(data_list_rd_pm4, oom_list_nd_pm4),
        "pm5" = c(data_list_rd_pm5, oom_list_nd_pm5)
    ),
    individual_plots = FALSE,
    group_plots = FALSE
)

```
