# metaSNF of Baseline mTBI Subjects

In this chapter, I use the metaSNF package to generate and characterize meta clusters of the extracted data.

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)
library(ggplot2)
library(patchwork)
library(xtable)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subjects <- read_csv(sub_path("2024_07_31_mtbi_subjects.csv"))
mtbi_train_subjects <- read_csv(sub_path("2024_07_31_mtbi_train_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2024_07_31_uninjured_subjects.csv"))
```

## Importing data

```{r}
# CHECKMARK
all_dls <- list.load(input_path("2024_07_31_all_dls.rds"))

```

## Generating custom distance measures

```{r}
###############################################################################
# 2. Add standard normalized variations to the distance metrics list (also
# achievable through toggling automatic_standard_normalize parameter in
# `batch_snf`)
###############################################################################
my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

summarize_dml(my_distance_metrics)
```

## Generating the settings matrix

```{r}
mtbi_settings_matrix <- generate_settings_matrix(
    all_dls$"mtbi_train_data_lists"$"imp_1",
    nrow = 200,
    seed = 42,
    distance_metrics_list = my_distance_metrics
)

write_csv(mtbi_settings_matrix, proc_path("mtbi_settings_matrix.csv", TRUE))

mtbi_settings_matrix <- read_csv(
    proc_path("2024_07_31_mtbi_settings_matrix.csv")
)
```

## Running SNF for each of the imputations

```{r}
mtbi_train_dls <- c(
    all_dls$"mtbi_train_data_lists",
    all_dls$"mtbi_pooled_data_lists"
)

names(mtbi_train_dls) <- c(paste0("imp_", 1:5), paste0("pooled_imp_", 1:5))

mtbi_train_solutions_matrices <- lapply(
    mtbi_train_dls,
    function(imputed_dl) {
        summarize_dl(imputed_dl)
        solutions_matrix <- batch_snf(
            data_list = imputed_dl,
            settings_matrix = mtbi_settings_matrix,
            distance_metrics_list = my_distance_metrics,
            processes = "max"
        )
    }
)

#
list.save(
    mtbi_train_solutions_matrices,
    input_path("mtbi_train_solutions_matrices.rds", TRUE)
)
#
mtbi_train_solutions_matrices <- list.load(
    input_path("2024_07_31_mtbi_train_solutions_matrices.rds")
)
#
mtbi_sm <- do.call(
    "rbind",
    mtbi_train_solutions_matrices
)
#
write_csv(data.frame(mtbi_sm), proc_path("mtbi_sm.csv", TRUE))
#
mtbi_ari <- calc_aris(mtbi_sm, processes = "max")
#
write_csv(data.frame(mtbi_ari), proc_path("mtbi_ari.csv", TRUE))
#
mtbi_ari_order <- get_matrix_order(mtbi_ari)
#
write_csv(data.frame(mtbi_ari_order), proc_path("mtbi_ari_order.csv", TRUE))
```

## Re-importing data

```{r}
# CHECKMARK
mtbi_sm <- read_csv(proc_path("2024_07_31_mtbi_sm.csv"))

mtbi_ari <- as.matrix(read_csv(proc_path("2024_07_31_mtbi_ari.csv")))

mtbi_ari_order <- unlist(read_csv(proc_path("2024_07_31_mtbi_ari_order.csv")))
names(mtbi_ari_order) <- NULL
```

## Calculating associations between cluster solutions and features

```{r}
imputation_labels <- data.frame(
    "imputation" = c(
        rep("m1", 200),
        rep("m2", 200),
        rep("m3", 200),
        rep("m4", 200),
        rep("m5", 200),
        rep("pm1", 200),
        rep("pm2", 200),
        rep("pm3", 200),
        rep("pm4", 200),
        rep("pm5", 200)
    ),
    "pooled" = c(
        rep("no", 1000),
        rep("yes", 1000)
    )
)

mtbi_sm_l <- cbind(mtbi_sm, imputation_labels)

mtbi_esm_m1 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "m1", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_1",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_1",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_m2 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "m2", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_2",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_2",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_m3 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "m3", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_3",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_3",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_m4 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "m4", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_4",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_4",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_m5 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "m5", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_5",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_5",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_pm1 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "pm1", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_1",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_1",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_pm2 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "pm2", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_2",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_2",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_pm3 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "pm3", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_3",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_3",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_pm4 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "pm4", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_4",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_4",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_pm5 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "pm5", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_5",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_5",
    min_pval = 1e-10,
    processes = "max"
)

mtbi_esm <- dplyr::bind_rows(
    mtbi_esm_m1,
    mtbi_esm_m2,
    mtbi_esm_m3,
    mtbi_esm_m4,
    mtbi_esm_m5,
    mtbi_esm_pm1,
    mtbi_esm_pm2,
    mtbi_esm_pm3,
    mtbi_esm_pm4,
    mtbi_esm_pm5
)

mtbi_esm$"impairment_separation" <- -log10(mtbi_esm$"mean_pval")

write_csv(mtbi_esm, proc_path("mtbi_esm.csv", TRUE))
```

```{r}
# CHECKMARK
mtbi_esm <- read_csv(proc_path("2024_07_31_mtbi_esm.csv"))
```

## Identifying and visualizing meta clusters

```{r}
base_ari_hm <- adjusted_rand_index_heatmap(
    mtbi_ari,
    order = mtbi_ari_order
)

shiny_annotator(base_ari_hm)

mtbi_split_vec <- c(
    206,
    230,
    466,
    555,
    797,
    959,
    1247,
    1490
)

write_csv(data.frame(mtbi_split_vec), proc_path("mtbi_split_vec.csv", TRUE))
```

```{r}
# CHECKMARK
mtbi_split_vec <- read_csv(proc_path("2024_07_31_mtbi_split_vec.csv")) |>
    unlist() |>
    as.numeric()
```

```{r}
divergent_colours <- function(column)  {
    values <- unique(column)
    colours <- RColorBrewer::brewer.pal(n = length(values), name = "Set3")
    names(colours) <- values
    return(colours)
}

full_mtbi_ari_hm <- adjusted_rand_index_heatmap(
    aris = mtbi_ari,
    order = mtbi_ari_order,
    data = mtbi_esm,
    min_colour = "black",
    split_vector = mtbi_split_vec,
    top_hm = list(
        "Impairment Separation" = "impairment_separation"
    ),
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    left_hm = list(
        "Pooled" = "pooled",
        "Imputation" = "imputation"
    ),
    annotation_colours = list(
        "Impairment Separation" = colour_scale(
            mtbi_esm$"impairment_separation",
            min_colour = "gray7",
            max_colour = "limegreen"
        ),
        "Imputation" = divergent_colours(mtbi_esm$"imputation"),
        "Pooled" = c(
            "yes" = "orange",
            "no" = "purple"
        )
    )
)
full_mtbi_ari_hm

save_heatmap(
    heatmap = full_mtbi_ari_hm,
    path = fig_path("full_mtbi_ari_hm.png", TRUE),
    width = 950,
    height = 900,
    res = 100
)

# Another heatmap without the imputation-related columns
lite_mtbi_ari_hm <- adjusted_rand_index_heatmap(
    aris = mtbi_ari,
    order = mtbi_ari_order,
    data = mtbi_esm,
    min_colour = "black",
    split_vector = mtbi_split_vec,
    top_hm = list(
        "Impairment Separation" = "impairment_separation"
    ),
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    annotation_colours = list(
        "Impairment Separation" = colour_scale(
            mtbi_esm$"impairment_separation",
            min_colour = "gray7",
            max_colour = "limegreen"
        )
    )
)

save_heatmap(
    heatmap = lite_mtbi_ari_hm,
    path = fig_path("lite_mtbi_ari_hm.png", TRUE),
    width = 900,
    height = 700,
    res = 100
)
```

When picking out representative solutions, I'd like to preferentially go for solutions that derived from solo rather than pooled imputations, as those solutions have values for all features.

```{r}
# Function to try to lean on mTBI-including solutions when possible.
# This function will pick from solo solutions unless over 70% of the meta
# cluster is pooled.
restrict_fn <- function(x, threshold = 0.3) {
    x_solo_ind <- x$"imputation" %in% c("m1", "m2", "m3", "m4", "m5")
    x_pool_ind <- x$"imputation" %in% c("pm1", "pm2", "pm3", "pm4", "pm5")
    x_solo <- x[x_solo_ind, ]
    x_pool <- x[x_pool_ind, ]
    frac_solo <- nrow(x_solo) / (nrow(x_solo) + nrow(x_pool))
    if (frac_solo < threshold) {
        return(x[x_pool_ind, ])
    } else {
        return(x[x_solo_ind, ])
    }
}

mtbi_rep_solutions <- get_representative_solutions(
    mtbi_ari,
    split_vector = mtbi_split_vec,
    order = mtbi_ari_order,
    filter_fn = restrict_fn,
    mtbi_esm
)

mtbi_rep_solutions

# Based on the heatmap, we'll remove B, E, H, K (unstable meta clusters)
mtbi_rep_solutions <- dplyr::filter(
    mtbi_rep_solutions,
    !label %in% c("B", "D", "I")
)

write_csv(mtbi_rep_solutions, proc_path("mtbi_rep_solutions.csv", TRUE))
```

```{r}
# CHECKMARK
mtbi_rep_solutions <- read_csv(proc_path("2024_08_08_mtbi_rep_solutions.csv"))
```

```{r}
mtbi_manhattan <- mc_manhattan_plot(
    mtbi_rep_solutions,
    data_list = all_dls$"mtbi_train_data_lists"$"imp_1",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_1",
    domain_colours = c(
        "AS" = "#85929e",
        "D" = "#bb8fce",
        "N" = "#e59866",
        "MH" = "#7fb3d5",
        "P" = "#52be80",
        "S" = "#d98880",
        "B" = "#ff3131"
    )
)
mtbi_manhattan

ggsave(
    plot = mtbi_manhattan,
    filename = fig_path("mtbi_manhattan.png", TRUE),
    width = 18,
    height = 14,
    dpi = 120
)

# The most robust solution
mtbi_mc_e_esm <- mtbi_rep_solutions |>
    dplyr::filter(label == "E")

write_csv(mtbi_mc_e_esm, proc_path("mtbi_mc_e_esm.csv", TRUE))
```

```{r}
# CHECKMARK
mtbi_mc_e_esm <- read_csv(proc_path("2024_08_08_mtbi_mc_e_esm.csv"))
```

```{r}
mtbi_mc_e_esm$"imputation"

# Feature plot generation
plot_list <- auto_plot(
    solutions_matrix_row = mtbi_mc_e_esm,
    data_list = all_dls$"mtbi_train_data_lists"$"imp_1",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_1",
    save = fig_path("mtbi_mc_e", TRUE)
)

# No save version:
plot_list <- auto_plot(
    solutions_matrix_row = mtbi_mc_e_esm,
    data_list = all_dls$"mtbi_train_data_lists"$"imp_1",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_1"
)

all_plots <- wrap_plots(plot_list)

# Good enough as a snapshot
ggsave(
    fig_path("mtbi_mc_e_all_plots.png", TRUE),
    all_plots,
    width = 35,
    height = 30,
    dpi = 50
)
```

## Characterization of meta cluster E representative solution

### NMI

```{r}
# Calculating feature importances
nmis <- batch_nmi(
    all_dls$"mtbi_train_data_lists"$"imp_1",
    mtbi_mc_e_esm,
    distance_metrics_list = my_distance_metrics
)
nmi_order <- sort(
    nmis$"row_id_81",
    decreasing = TRUE,
    index.return = TRUE
)
nmis <- nmis[nmi_order$ix, ]
nmis

write_csv(nmis, proc_path("mtbi_mc_e_nmis.csv", TRUE))

mtbi_mc_e_nmis <- read_csv(proc_path("2024_08_08_mtbi_mc_e_nmis.csv"))

data.frame(mtbi_mc_e_nmis)
```

NMI order:

                  feature   row_id_81 nmi_rank
1                     sex 0.275526597        1
2            brain_volume 0.210296415        2
3             cortical_sa 0.184404762        3
4        household_income 0.166172559        4
5       pubertal_status_p 0.122584831        5
6                    race 0.088071636        6
7      programs_this_year 0.084278633        7
8     non_school_programs 0.081924484        8
9          parent_somatic 0.076984578        9
10     weekend_screentime 0.069927358       10
11     weekday_screentime 0.069889352       11
12 fmri_cort_subcort_cors 0.063850773       12
13    private_instruction 0.054050497       13
14         parent_thought 0.043251992       14
15         fmri_cort_cors 0.040882414       15
16          parent_anxdep 0.040648766       16
17       headache_history 0.040265567       17
18          parent_perstr 0.039215874       18
19      parent_antisocial 0.038275871       19
20         parent_depress 0.038094711       20
21      parent_aggressive 0.035884445       21
22            considerate 0.035052610       22
23       parent_anxdisord 0.034747645       23
24           family_outdo 0.032472213       24
25           major_wm_ndi 0.031484982       25
26             helps_hurt 0.031050319       26
27     parent_hyperactive 0.030866031       27
28        parent_avoidant 0.028372879       28
29          exercise_time 0.028298248       29
30       parent_withdrawn 0.028166332       30
31          family_temper 0.027048041       31
32     cortical_thickness 0.025519804       32
33           family_fight 0.024800636       33
34       parent_attention 0.024588368       34
35        family_peaceful 0.023107261       35
36           family_throw 0.023093326       36
37       family_criticize 0.021713654       37
38           family_angry 0.020785098       38
39      pubertal_status_y 0.020067468       39
40       parent_intrusive 0.019630108       40
41                helpful 0.019391479       41
42  same_sex_close_friend 0.018634682       42
43               mtbi_age 0.015366885       43
44    pericortical_wm_ndi 0.014752662       44
45        school_programs 0.012770795       45
46                    age 0.012249243       46
47        same_sex_friend 0.009985895       47
48             family_hit 0.009825276       48
49            family_yell 0.009790276       49
50         mtbi_mechanism 0.008265686       50
51          mtbi_mem_daze 0.007403597       51
52               mtbi_loc 0.007210643       52
53         previous_mtbis 0.007052524       53
54         opp_sex_friend 0.005411475       54
55   opp_sex_close_friend 0.002462148       55

### p-values

```{r}
pvals <- get_pvals(
    mtbi_mc_e_esm,
    keep_summaries = FALSE
)
pvals <- data.frame(
    "feature" = gsub("_pval", "", names(pvals)),
    "neg_log_pval" = -log10(as.numeric(unlist(pvals)))
)
pvals <- pvals[-1, ]
pvals_order <- sort(
    pvals$"neg_log_pval",
    decreasing = TRUE,
    index.return = TRUE
)
pvals <- pvals[pvals_order$ix, ]
pvals <- dplyr::filter(
    pvals,
    !grepl("^cbcl|^sds", feature)
)

write_csv(pvals, proc_path("mtbi_mc_e_pvals.csv", TRUE))

mtbi_mc_e_pvals <- read_csv(proc_path("2024_08_08_mtbi_mc_e_pvals.csv"))

data.frame(mtbi_mc_e_pvals)
```
                  feature neg_log_pval pval_rank
1                     sex   10.0000000         1
2        household_income   10.0000000         1
3       pubertal_status_p   10.0000000         1
4            brain_volume   10.0000000         1
5             cortical_sa   10.0000000         1
6      weekday_screentime   10.0000000         1
7     non_school_programs   10.0000000         1
8      programs_this_year   10.0000000         1
9          parent_somatic   10.0000000         1
10                   race    9.9851428        10
11         parent_depress    7.5227388        11
12      parent_aggressive    7.3540555        12
13          parent_anxdep    7.3173966        13
14         parent_thought    7.0034199        14
15      parent_antisocial    6.9312020        15
16    private_instruction    6.5096860        16
17       parent_anxdisord    6.1157933        17
18         fmri_cort_cors    6.0233908        18
19 fmri_cort_subcort_cors    5.8557565        19
20            considerate    5.2459699        20
21           family_outdo    5.1282293        21
22     parent_hyperactive    4.9567045        22
23             helps_hurt    4.6600296        23
24       parent_withdrawn    4.6593934        24
25       parent_attention    4.4443911        25
26           major_wm_ndi    4.2191702        26
27        parent_avoidant    4.2128400        27
28       headache_history    3.8034048        28
29     weekend_screentime    3.7372043        29
30     cortical_thickness    3.7210189        30
31           family_fight    3.4858695        31
32           family_angry    3.2580565        32
33       family_criticize    3.2132658        33
34          family_temper    3.2085406        34
35          exercise_time    3.1548592        35
36        family_peaceful    3.0518592        36
37  same_sex_close_friend    3.0112434        37
38                helpful    2.8425081        38
39       parent_intrusive    2.8120690        39
40           family_throw    2.6673169        40
41          parent_perstr    2.1950143        41
42    pericortical_wm_ndi    1.9417773        42
43                    age    1.6206383        43
44      pubertal_status_y    1.5321973        44
45        school_programs    1.4410232        45
46            family_yell    1.3552800        46
47        same_sex_friend    1.0351215        47
48         mtbi_mechanism    0.8948445        48
49         previous_mtbis    0.8892980        49
50               mtbi_loc    0.8849865        50
51             family_hit    0.8523426        51
52          mtbi_mem_daze    0.7441445        52
53               mtbi_age    0.3763523        53
54         opp_sex_friend    0.1345863        54
55   opp_sex_close_friend    0.0505548        55

### Correlation of NMI and p-value

```{r}
mtbi_mc_e_pvals$"pval_rank" <- rank(
    -mtbi_mc_e_pvals$"neg_log_pval",
    ties.method = "min"
)

mtbi_mc_e_nmis$"nmi_rank" <- rank(
    -mtbi_mc_e_nmis$"row_id_81",
    ties.method = "min"
)

mtbi_mc_e_nmi_v_pval <- dplyr::full_join(
    mtbi_mc_e_nmis,
    mtbi_mc_e_pvals,
    by = "feature"
)

domain_df <- dl_variable_summary(all_dls$"mtbi_train_data_lists"$"imp_1") |>
    dplyr::select(name, domain) |>
    dplyr::rename("feature" = "name")

mtbi_mc_e_nmi_v_pval <- mtbi_mc_e_nmi_v_pval |>
    dplyr::inner_join(domain_df, by = "feature")

write_csv(mtbi_mc_e_nmi_v_pval, proc_path("mtbi_mc_e_nmi_v_pval.csv", TRUE))
```

```{r}
# CHECKMARK
mtbi_mc_e_nmi_v_pval <- read_csv(
    proc_path("2024_08_08_mtbi_mc_e_nmi_v_pval.csv")
)
```

```{r}
nmi_v_p_rho <- cor(
    mtbi_mc_e_nmi_v_pval$"nmi_rank",
    mtbi_mc_e_nmi_v_pval$"pval_rank",
    method = "spearman"
)

nmi_v_pval_plot <- mtbi_mc_e_nmi_v_pval |>
    ggplot(
        aes(x = nmi_rank, y = pval_rank, label = feature, colour = domain)
    ) +
    geom_point(size = 2) + 
    scale_colour_manual(
        values = c(
            "AS" = "#85929e",
            "D" = "#bb8fce",
            "N" = "#e59866",
            "MH" = "#7fb3d5",
            "P" = "#52be80"
        )
    ) +
    theme_bw() +
    labs(x = "Rank by NMI", y = "Rank by p-value") +
    ggrepel::geom_text_repel(
        #vjust = 3,
        #hjust = 1,
        force = 1,
        max.overlaps = 20,
        size = 4
    ) +
    annotate(
        "text",
        x = 4,
        y = 50,
        size = 5,
        label = paste("Spearman's ρ =", round(nmi_v_p_rho, 2)),
        hjust = 0
    ) + 
    theme(text = element_text(size = 16))
nmi_v_pval_plot

ggsave(
    fig_path("nmi_v_pval_plot.png", TRUE),
    nmi_v_pval_plot,
    width = 12,
    height = 12
)
```

### Joint rankings

```{r}
mtbi_mc_e_nmi_v_pval$"joint_rank" <- rank(
    mtbi_mc_e_nmi_v_pval$"nmi_rank" + mtbi_mc_e_nmi_v_pval$"pval_rank",
    ties.method = "min"
)

joint_order <- sort(
    mtbi_mc_e_nmi_v_pval$"joint_rank",
    decreasing = FALSE,
    index.return = TRUE
)
mtbi_mc_e_nmi_v_pval_rank <- mtbi_mc_e_nmi_v_pval[joint_order$ix, ]

mtbi_mc_e_nmi_v_pval_rank <- mtbi_mc_e_nmi_v_pval_rank |>
    dplyr::select("feature", dplyr::contains("rank"))

write_csv(
    mtbi_mc_e_nmi_v_pval_rank,
    proc_path("mtbi_mc_e_nmi_v_pval_rank.csv", TRUE)
)
```

```{r}
# CHECKMARK
mtbi_mc_e_nmi_v_pval_rank <- read_csv(
    proc_path("2024_08_09_mtbi_mc_e_nmi_v_pval_rank.csv")
)
```

```{r}
data.frame(mtbi_mc_e_nmi_v_pval_rank)

# Latex table
xtable(data.frame(mtbi_mc_e_nmi_v_pval_rank))
```

### Visualizing top 10 features

```{r}
sorted_features <- mtbi_mc_e_nmi_v_pval_rank$"feature"

names(plot_list)

ranked_plot_list <- plot_list[sorted_features]

ranked_all_plots <- wrap_plots(ranked_plot_list)

ggsave(
    fig_path("mtbi_mc_e_ranked_all_plots.png", TRUE),
    ranked_all_plots,
    width = 35,
    height = 30,
    dpi = 50
)

saveRDS(
    ranked_all_plots,
    file = fig_path("mtbi_mc_e_ranked_all_plots.rds", TRUE)
)

mtbi_mc_e_ranked_all_plots <- readRDS(
    fig_path("2024_08_09_mtbi_mc_e_ranked_all_plots.rds")
)

###############################################################################
# Building the top 10 plot list
###############################################################################

mc_e_top_ten_pl <- ranked_plot_list[1:10]

names(mc_e_top_ten_pl) <- sorted_features[1:10]

names(mc_e_top_ten_pl)

#
mc_e_top_ten_pl$"sex" <- mc_e_top_ten_pl$"sex" +
    labs(fill = "Sex") +
    scale_fill_discrete(labels = c("F", "M"))
#
mc_e_top_ten_pl$"brain_volume" <- mc_e_top_ten_pl$"brain_volume" +
    labs(y = expression(paste("Brain Volume ", (mm^3))))
#
mc_e_top_ten_pl$"cortical_sa" <- mc_e_top_ten_pl$"cortical_sa" +
    labs(y = expression(paste("Cortical Area ", (mm^2))))
#
mc_e_top_ten_pl$"household_income" <- mc_e_top_ten_pl$"household_income" +
    labs(y = "Household Income")
#
mc_e_top_ten_pl$"pubertal_status_p" <- mc_e_top_ten_pl$"pubertal_status_p" +
    labs(y = "Pubertal Status - P")
#
mc_e_top_ten_pl$"pubertal_status_p" <- mc_e_top_ten_pl$"pubertal_status_p" +
    labs(y = "Pubertal Status - P")
#
mc_e_top_ten_pl$"programs_this_year" <- mc_e_top_ten_pl$"programs_this_year" +
    labs(y = "Total Activities this Year")
#
mc_e_top_ten_pl$"non_school_programs" <- mc_e_top_ten_pl$"non_school_programs" +
    labs(y = "Lifetime Extracurriculars")
#
mc_e_top_ten_pl$"parent_somatic" <- mc_e_top_ten_pl$"parent_somatic" +
    labs(y = "Parent Somatic Problems")
#
mc_e_top_ten_pl$"weekday_screentime" <- mc_e_top_ten_pl$"weekday_screentime" +
    labs(y = "Weekday Screentime")
#
mc_e_top_ten_pl$"race" <- mc_e_top_ten_pl$"race" +
    labs(fill = "Race") +
    scale_fill_discrete(labels = c("Black", "Hispanic", "Other", "White"))
#
mc_e_top_ten_p <- wrap_plots(
    mc_e_top_ten_pl,
    ncol = 2
) & labs(x = "Cluster") & theme(plot.margin = unit(c(0.5, 1.5, 0.5, 2), "cm"))
#
ggsave(
    fig_path("mtbi_mc_e_ranked_all_plots_ten.png", TRUE),
    mc_e_top_ten_p,
    width = 15,
    height = 20,
    dpi = 150
)

# PDF equivalent
pdf(
    fig_path("mtbi_mc_e_ranked_all_plots_ten.pdf", TRUE),
    width = 15,
    height = 20
)
print(mc_e_top_ten_p)
dev.off()

```

just show top 10 clusters by similarity

                  feature nmi_rank pval_rank joint_rank
1                     sex        1         1          1
2            brain_volume        2         1          2
3             cortical_sa        3         1          3
4        household_income        4         1          4
5       pubertal_status_p        5         1          5
6      programs_this_year        7         1          6
7     non_school_programs        8         1          7
8          parent_somatic        9         1          8
9      weekday_screentime       11         1          9
10                   race        6        10         10
11         parent_thought       14        14         11
12    private_instruction       13        16         12
13          parent_anxdep       16        13         12
14 fmri_cort_subcort_cors       12        19         14
15         parent_depress       20        11         14
16         fmri_cort_cors       15        18         16
17      parent_aggressive       21        12         16
18      parent_antisocial       19        15         18
19     weekend_screentime       10        29         19
20       parent_anxdisord       23        17         20
21            considerate       22        20         21
22       headache_history       17        28         22
23           family_outdo       24        21         22
24             helps_hurt       26        23         24
25     parent_hyperactive       27        22         24
26           major_wm_ndi       25        26         26
27       parent_withdrawn       30        24         27
28        parent_avoidant       28        27         28
29          parent_perstr       18        41         29
30       parent_attention       34        25         29
31     cortical_thickness       32        30         31
32          exercise_time       29        35         32
33           family_fight       33        31         32
34          family_temper       31        34         34
35       family_criticize       37        33         35
36           family_angry       38        32         35
37        family_peaceful       35        36         37
38           family_throw       36        40         38
39       parent_intrusive       40        39         39
40                helpful       41        38         39
41  same_sex_close_friend       42        37         39
42      pubertal_status_y       39        44         42
43    pericortical_wm_ndi       44        42         43
44                    age       46        43         44
45        school_programs       45        45         45
46        same_sex_friend       47        47         46
47            family_yell       49        46         47
48               mtbi_age       43        53         48
49         mtbi_mechanism       50        48         49
50             family_hit       48        51         50
51               mtbi_loc       52        50         51
52         previous_mtbis       53        49         51
53          mtbi_mem_daze       51        52         53
54         opp_sex_friend       54        54         54
55   opp_sex_close_friend       55        55         55

### Detailed cluster topologies

Can come back to this later.

```{r}# {{{

mtbi_mc_e_esm_plot_df <- auto_plot(
    solutions_matrix_row = mtbi_mc_e_esm,
    data_list = all_dls$"mtbi_train_data_lists"$"imp_1",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_1",
    return_plots = FALSE
)

mtbi_mc_e_ranked_all_plots[[2]]

outcome_plot_list <- auto_plot(
    solutions_matrix_row = mtbi_mc_e_esm,
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_1"
)

names(outcome_plot_list)

clean_names <- c(
    "CBCL\nAnxious-Depressed",
    "CBCL\nWithdrawn-Depressed",
    "CBCL\nSomatic Problems",
    "CBCL\nSocial Problems",
    "CBCL\nThought Problems",
    "CBCL\nAttention Problems",
    "CBCL\nRule-breaking Problems",
    "CBCL\nAggression Problems",
    "SDS Total\nSleeping Problems"
)
for (i in seq_along(outcome_plot_list)) {
    outcome_plot_list[[i]] <- outcome_plot_list[[i]] +
        labs(y = clean_names[[i]], x = "Cluster")
}

outcome_plot_wrap <- wrap_plots(outcome_plot_list) &
    theme(plot.margin = unit(c(0, 1, 1, 0), "cm"))

ggsave(
    fig_path("mtbi_mc_e_outcome_plot_wrap.png", TRUE),
    outcome_plot_wrap,
    width = 14,
    height = 14,
    dpi = 150
)

proptable <- function(df, ft) {
    tab <- prop.table(
        table(df[, ft], df$"cluster"),
        margin = 2
    ) * 100
    return(tab)
}

proptable(mtbi_mc_e_esm_plot_df, "sex")

proptable(mtbi_mc_e_esm_plot_df, "sex")

tstat <- function(d, n1, n2) {
    t <- d * sqrt((n1 * n2) / (n1 + n2))
    return(t)
}
pooled_sd <- function(n1, s1, n2, s2) {
    numerator <- ((n1 - 1) * (s1^2)) + ((n2 - 1) * (s2^2))
    denominator <- n1 + n2 - 2
    s <- sqrt(numerator / denominator)
    return(s)
}
cohens_d <- function(mean1, mean2, pooled_sd) {
    d <- (mean1 - mean2) / pooled_sd
    return(d)
}

calc_es <- function(x1, x2) {
    n1 <- length(x1)
    n2 <- length(x2)
    s1 <- sd(x1)
    s2 <- sd(x2)
    s <- pooled_sd(n1, s1, n2, s2)
    mean1 <- mean(x1)
    mean2 <- mean(x2)
    d <- cohens_d(mean1, mean2, s)
    d_full <- des(d, n1, n2, verbose = FALSE)
    return(
        list(
            "d" = d_full$"d",
            
        )
    )
}

mc_e_c1 <- mtbi_mc_e_esm_plot_df |> dplyr::filter(cluster == 1)
mc_e_c2 <- mtbi_mc_e_esm_plot_df |> dplyr::filter(cluster == 2)
mc_e_c3 <- mtbi_mc_e_esm_plot_df |> dplyr::filter(cluster == 3)

n1 <- nrow(mc_e_c1)
n2 <- nrow(mc_e_c2)
n3 <- nrow(mc_e_c3)

d <- calc_es(
    mc_e_c1$"brain_volume",
    mc_e_c2$"brain_volume"
)

d

z2 <- des(d, n1, n2, verbose = FALSE)

z2

library(compute.es)

table(mc_e_c1$"sex")
table(mc_e_c3$"sex")




z <- propes(
    0.1214953,
    0.8225806,
    nrow(mc_e_c1),
    nrow(mc_e_c3)
)

z$"OR"

es_bound(d, nrow(mc_e_c1), nrow(mc_e_c2))


```


sex:  Cluster 1 and 2 were primarily male (87.9% and 83.9% male respectively), while cluster 3 was primarily female (82.3%). 


brain_volume
cortical_sa
household_income
pubertal_status_p
programs_this_year
non_school_programs
parent_somatic
weekday_screentime
race
parent_thought
private_instruction
parent_anxdep
fmri_cort_subcort_cors
parent_depress
fmri_cort_cors
parent_aggressive
parent_antisocial
weekend_screentime
parent_anxdisord
considerate
headache_history
family_outdo
helps_hurt
parent_hyperactive
major_wm_ndi
parent_withdrawn
parent_avoidant
parent_perstr
parent_attention
cortical_thickness
exercise_time
family_fight
family_temper
family_criticize
family_angry
family_peaceful
family_throw
parent_intrusive
helpful
same_sex_close_friend
pubertal_status_y
pericortical_wm_ndi
age
school_programs
same_sex_friend
family_yell
mtbi_age
mtbi_mechanism
family_hit
mtbi_loc
previous_mtbis
mtbi_mem_daze
opp_sex_friend
opp_sex_close_friend


```{r}



binary_or <- function(df, feature, ca, cb) {
    ca_values <- df[df$"cluster" == ca, feature]
    cb_values <- df[df$"cluster" == cb, feature]
    print(ca_values)
    print(".")
    print(cb_values)
}
binary_or(
    mtbi_mc_e_esm_plot_df,
    feature = "sex",
    ca = 1,
    cb = 2
)

sorted_features

# OR calculations
or_from_table <- function(table, exposed_c, ctrl_c, outcome_cat, nothing_cat) {
    df <- data.frame(table)
    colnames(df) <- c("cluster", "event", "freq")
    exposed_outcome <- dplyr::filter(
        df,
        cluster == exposed_c & event == outcome_cat
    )$"freq"
    ctrl_outcome <- dplyr::filter( df,
        cluster == ctrl_c & event == outcome_cat
    )$"freq"
    exposed_nothing <- dplyr::filter(
        df,
        cluster == exposed_c & event == nothing_cat
    )$"freq"
    ctrl_nothing <- dplyr::filter( df,
        cluster == ctrl_c & event == nothing_cat
    )$"freq"
    or_num <- exposed_outcome / ctrl_outcome
    or_den <- exposed_nothing / ctrl_nothing
    or <- or_num / or_den
    d <- ln()
    return(or_num / or_den)
}

# Race
race_df <- mtbi_mc_e_esm_plot_df |>
    dplyr::select(cluster, race)

race_df$"race"[race_df$"race" != "white"] <- "minority"

race_tab <- table(race_df)

for (i in 1:3) {
    for (j in 1:3) {
        if (i != j) {
            or <- or_from_table(race_tab, i, j, "minority", "white")
            print(paste0("Cluster ", i, " vs. ", j, ": ", round(or, 2)))
            d <- 
            cat("\n")
        }
    }
}

or_from_table(race_tab, 1, 2, "minority", "white")

or_from_table(race_tab, 1, 3, "minority", "white")

or_from_table(race_tab, 1, 3, "minority", "white")

race_tab


metadata_df

sorted_features

mtbi_mc_e_esm_plot_df |> head()

odds_ratio <- function(de, he, dn, hn) {
    numerator <- de / he
    denominator <- dn / hn
    return(numerator / denominator)
}



```

ordinal variable -> cohen's d
continuous variable -> cohen's d
discrete variable -> cohen's d
categorical variable -> odd's ratio -> cohen's d
binary variable -> odd's ratio -> cohen's d

log odds * sqrt(3)/pi}}}

# Label propagation

This top solution specifically came from the first imputed dataset, so that's what we'll label propagate off of.

```{r}
mtbi_mc_e_esm$"imputation"

all_dls |> names()

train_data_list_m1 <- all_dls$"mtbi_train_data_lists"$"imp_1"

test_data_list_m1 <- all_dls$"mtbi_test_data_lists"$"imp_1"
test_data_list_m2 <- all_dls$"mtbi_test_data_lists"$"imp_2"
test_data_list_m3 <- all_dls$"mtbi_test_data_lists"$"imp_3"
test_data_list_m4 <- all_dls$"mtbi_test_data_lists"$"imp_4"
test_data_list_m5 <- all_dls$"mtbi_test_data_lists"$"imp_5"

full_data_list_1 <- merge_data_lists(train_data_list_m1, test_data_list_m1)
full_data_list_2 <- merge_data_lists(train_data_list_m1, test_data_list_m2)
full_data_list_3 <- merge_data_lists(train_data_list_m1, test_data_list_m3)
full_data_list_4 <- merge_data_lists(train_data_list_m1, test_data_list_m4)
full_data_list_5 <- merge_data_lists(train_data_list_m1, test_data_list_m5)

my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

my_clust_algs_list <- generate_clust_algs_list(
    "three_cluster_spectral" = spectral_three,
    disable_base = TRUE
)

mtbi_mc_e_lp_1 <- lp_solutions_matrix(
    mtbi_mc_e_esm,
    full_data_list_1,
    distance_metrics_list = my_distance_metrics,
    clust_algs_list = my_clust_algs_list
)

dplyr::filter(mtbi_mc_d_lp_1, group == "test")$"subjectkey"

collapse_dl(train_data_list_m1)$"household_income"

collapse_dl(test_data_list_m1)$"household_income"

mtbi_mc_d_lp_1 <- read_csv(proc_path("2024_07_21_mtbi_mc_d_lp_1.csv"))

dplyr::filter(mtbi_mc_e_lp_1, group == "test")$"81"

#
mtbi_mc_e_lp_2 <- lp_solutions_matrix(
    mtbi_mc_e_esm,
    full_data_list_2,
    distance_metrics_list = my_distance_metrics
)
#
mtbi_mc_e_lp_3 <- lp_solutions_matrix(
    mtbi_mc_e_esm,
    full_data_list_3,
    distance_metrics_list = my_distance_metrics
)
#
mtbi_mc_e_lp_4 <- lp_solutions_matrix(
    mtbi_mc_e_esm,
    full_data_list_4,
    distance_metrics_list = my_distance_metrics
)
#
mtbi_mc_e_lp_5 <- lp_solutions_matrix(
    mtbi_mc_e_esm,
    full_data_list_5,
    distance_metrics_list = my_distance_metrics
)

# HERE I AM!

colnames(mtbi_mc_e_lp_1) <- c("subjectkey", "group", "cluster")
colnames(mtbi_mc_e_lp_2) <- c("subjectkey", "group", "cluster")
colnames(mtbi_mc_e_lp_3) <- c("subjectkey", "group", "cluster")
colnames(mtbi_mc_e_lp_4) <- c("subjectkey", "group", "cluster")
colnames(mtbi_mc_e_lp_5) <- c("subjectkey", "group", "cluster")

mtbi_mc_d_lp_1 <- read_csv(proc_path("2024_07_21_mtbi_mc_d_lp_1.csv"))
mtbi_mc_d_lp_2 <- read_csv(proc_path("2024_07_21_mtbi_mc_d_lp_2.csv"))
mtbi_mc_d_lp_3 <- read_csv(proc_path("2024_07_21_mtbi_mc_d_lp_3.csv"))
mtbi_mc_d_lp_4 <- read_csv(proc_path("2024_07_21_mtbi_mc_d_lp_4.csv"))
mtbi_mc_d_lp_5 <- read_csv(proc_path("2024_07_21_mtbi_mc_d_lp_5.csv"))
```

How similar are the label propagated results across imputations?

```{r}

lp1_vec <- dplyr::filter(mtbi_mc_e_lp_1, group == "test")$"cluster"
lp2_vec <- dplyr::filter(mtbi_mc_e_lp_2, group == "test")$"cluster"
lp3_vec <- dplyr::filter(mtbi_mc_e_lp_3, group == "test")$"cluster"
lp4_vec <- dplyr::filter(mtbi_mc_e_lp_4, group == "test")$"cluster"
lp5_vec <- dplyr::filter(mtbi_mc_e_lp_5, group == "test")$"cluster"

lp_vecs <- list(
    lp1_vec,
    lp2_vec,
    lp3_vec,
    lp4_vec,
    lp5_vec
)

lp_ari_mat <- matrix(1, 5, 5)
for (i in seq_along(lp_vecs)) {
    for (j in seq_along(lp_vecs)) {
        lp_ari_mat[i, j] <- mclust::adjustedRandIndex(
            lp_vecs[[i]],
            lp_vecs[[j]]
        )
    }
}

rownames(lp_ari_mat) <- paste0("lp_imp_", 1:5)
colnames(lp_ari_mat) <- paste0("lp_imp_", 1:5)

lp_ari_hm <- adjusted_rand_index_heatmap(
    lp_ari_mat,
    show_row_names = TRUE,
    show_column_names = TRUE
)

save_heatmap(
    lp_ari_hm,
    fig_path("lp_ari_hm.png", TRUE),
    width = 450,
    height = 350,
    res = 100
)

(lp_ari_mat)

lp_ari_mat == min(lp_ari_mat)

sum(lp_vecs[[1]] != lp_vecs[[2]])

sum(lp_vecs[[1]] != lp_vecs[[2]]) / length(lp_vecs[[2]])

lp1_vec

```

The label propagated results were extremely similar across imputations.
The most dissimilar results differed by assignment of 1 (out of 85) children.

The "full" suffix below refers to the original + label propagated subjects, together

```{r}
mtbi_mc_d_lp_1 <- read_csv(proc_path("2024_07_21_mtbi_mc_d_lp_1.csv"))


mtbi_mc_d_full <- mtbi_mc_d_lp_1 |>
    dplyr::select(-group)

mtbi_mc_d_lp_only <- mtbi_mc_d_lp_1 |>
    dplyr::filter(group == "test") |>
    dplyr::select(-group)

write_csv(mtbi_mc_d_full, proc_path("mtbi_mc_d_full.csv", TRUE))
write_csv(mtbi_mc_d_lp_only, proc_path("mtbi_mc_d_lp_only.csv", TRUE))

mtbi_mc_d_full <- read_csv(proc_path("2024_07_22_mtbi_mc_d_full.csv"))
mtbi_mc_d_lp_only <- read_csv(proc_path("2024_07_22_mtbi_mc_d_lp_only.csv"))

train_oom_list_m3 <- all_dls$"mtbi_train_oom_lists"$"imp_3"
test_oom_list_m1 <- all_dls$"mtbi_test_oom_lists"$"imp_1"

mtbi_mc_d_data_list <- merge_data_lists(
    train_data_list_m3,
    test_data_list_m1
)

mtbi_mc_d_oom_list <- merge_data_lists(
    train_oom_list_m3,
    test_oom_list_m1
)

list.save(
    mtbi_mc_d_data_list, 
    proc_path("mtbi_mc_d_full_data_list.rds", TRUE)
)
list.save(
    mtbi_mc_d_oom_list, 
    proc_path("mtbi_mc_d_full_oom_list.rds", TRUE)
)


mtbi_mc_d_full_data_list <- list.load(
    proc_path(
        "2024_07_22_mtbi_mc_d_full_data_list.rds"
    )
)
mtbi_mc_d_full_oom_list <- list.load(
    proc_path(
        "2024_07_22_mtbi_mc_d_full_oom_list.rds"
    )
)


mtbi_mc_d_full_plot_list <- auto_plot(
    cluster_df = mtbi_mc_d_full,
    data_list = mtbi_mc_d_full_data_list,
    target_list = mtbi_mc_d_full_oom_list,
    save = fig_path("mtbi_mc_d_full", TRUE)
)

mtbi_mc_d_lp_only_plot_list <- auto_plot(
    cluster_df = mtbi_mc_d_lp_only,
    data_list = test_data_list_m1,
    target_list = test_oom_list_m1,
    save = fig_path("mtbi_mc_d_lp_only", TRUE)
)

mtbi_mc_d_full_wrap <- wrap_plots(mtbi_mc_d_full_plot_list)
mtbi_mc_d_lp_only_wrap <- wrap_plots(mtbi_mc_d_lp_only_plot_list)

ggsave(
    fig_path("mtbi_mc_d_full_wrap.png", TRUE),
    mtbi_mc_d_full_wrap,
    width = 35,
    height = 30,
    dpi = 50
)

ggsave(
    fig_path("mtbi_mc_d_lp_only_wrap.png", TRUE),
    mtbi_mc_d_lp_only_wrap,
    width = 35,
    height = 30,
    dpi = 50
)

# Creating ESM formatted full solution
mtbi_mc_d_full_sm <- mtbi_mc_d_esm |>
    dplyr::select(
        -dplyr::contains("pval"),
        -dplyr::contains("impairment"),
        -label,
        -imputation,
        -pooled
    )
mtbi_mc_d_lp_only_sm_row <- data.frame(
    t(mtbi_mc_d_lp_only$"cluster")
)
colnames(mtbi_mc_d_lp_only_sm_row) <- mtbi_mc_d_lp_only$"subjectkey"
mtbi_mc_d_full_sm <- cbind(
    mtbi_mc_d_full_sm,
    mtbi_mc_d_lp_only_sm_row
)

mtbi_mc_d_full_esm <- extend_solutions(
    mtbi_mc_d_full_sm,
    data_list = mtbi_mc_d_full_data_list,
    target_list = mtbi_mc_d_full_oom_list,
    min_pval = 1e-10,
    processes = "max"
)

write_csv(mtbi_mc_d_full_esm, proc_path("mtbi_mc_d_full_esm.csv", TRUE))
mtbi_mc_d_full_esm <- read_csv(proc_path("2024_07_22_mtbi_mc_d_full_esm.csv"))

```

(Leave below for later)

# Longitudinal analyses

```{r}

#mtbi_train <- read_csv(sub_path("2024_03_12_mtbi_train_subjects.csv"))

core_path <- path_maker(here(paste0("data/abcd/core")))

import <- function(path) {
    return(abcd_load(core_path(path)))
}

mh_p_cbcl <- import("mental-health/mh_p_cbcl.csv")
ph_p_sds <- import("physical-health/ph_p_sds.csv")

mc_d_cluster_df <- get_cluster_df(mtbi_mc_d_esm)

mc_d_subs <- gsub("subject_", "", mc_d_cluster_df$"subjectkey")

syndromes <- c(
    "anxdep",
    #"withdep",
    #"somatic",
    #"social",
    #"thought",
    #"attention",
    #"rulebreak",
    "aggressive"
)

tps <- c(0, 1, 2, 3)

get_syndrome_long <- function(syndrome, timepoints, subs) {
    full_df <- NULL
    for (tp in timepoints) {
        outcomes <- get_cbcl_syndrome_scale(
            syndrome = syndrome,
            mh_p_cbcl,
            raw = FALSE,
            subjects = subs,
            t = tp
        )
        outcomes$"tp" <- tp
        if (is.null(full_df)) {
            full_df <- outcomes
        } else {
            full_df <- rbind(full_df, outcomes)
        }
    }
    return(full_df)
}



# make change score plots where you plot time on x-axis and visualize change
# by absolute t-score differences for 2 year and 3 year follow up

# Option 1
z <- get_syndrome_long("anxdep", tps, mc_d_subs)
z$"subjectkey" <- paste0("subject_", z$"subjectkey")
z_long <- dplyr::full_join(z, mc_d_cluster_df, by = "subjectkey")
z_long$"cluster" <- factor(z_long$"cluster")
anxdep <- ggplot(
    na.omit(z_long),
    aes(x = tp, y = cbcl_scr_syn_anxdep_t, colour = cluster, group = subjectkey)
) +
    geom_point() +
    geom_line() +
    facet_grid(cluster ~ .) +
    theme_bw()
ggsave("anxdep.png", anxdep)

z <- get_syndrome_long("withdep", tps, mc_d_subs)
z$"subjectkey" <- paste0("subject_", z$"subjectkey")
z_long <- dplyr::full_join(z, mc_d_cluster_df, by = "subjectkey")
z_long$"cluster" <- factor(z_long$"cluster")
withdep <- ggplot(
    na.omit(z_long),
    aes(x = tp, y = cbcl_scr_syn_withdep_t, colour = cluster, group = subjectkey)
) +
    geom_point() +
    geom_line() +
    facet_grid(cluster ~ .) +
    theme_bw()
ggsave("withdep.png", withdep)

z <- get_syndrome_long("aggressive", tps, mc_d_subs)
z$"subjectkey" <- paste0("subject_", z$"subjectkey")
z_long <- dplyr::full_join(z, mc_d_cluster_df, by = "subjectkey")
z_long$"cluster" <- factor(z_long$"cluster")
aggressive <- ggplot(
    na.omit(z_long),
    aes(x = tp, y = cbcl_scr_syn_aggressive_t, colour = cluster, group = subjectkey)
) +
    geom_point() +
    geom_line() +
    facet_grid(cluster ~ .) +
    theme_bw()
ggsave("aggressive.png", aggressive)



qq <- get_syndrome_long("anxdep", tps, mc_d_subs)
qq$"subjectkey" <- paste0("subject_", qq$"subjectkey")
qq_long <- dplyr::full_join(qq, mc_d_cluster_df, by = "subjectkey")
qq_long$"cluster" <- factor(qq_long$"cluster")
qq_long <- na.omit(qq_long)
for (subject in unique(qq_long$"subjectkey")) {
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 3, "cbcl_scr_syn_anxdep_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 3, "cbcl_scr_syn_anxdep_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_anxdep_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 2, "cbcl_scr_syn_anxdep_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 2, "cbcl_scr_syn_anxdep_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_anxdep_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 1, "cbcl_scr_syn_anxdep_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 1, "cbcl_scr_syn_anxdep_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_anxdep_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_anxdep_t"] <- 0
}
anxdep2 <- ggplot(
    na.omit(qq_long),
    aes(x = tp, y = cbcl_scr_syn_anxdep_t, colour = cluster, group = subjectkey)
) +
    geom_point() +
    geom_line() +
    facet_grid(cluster ~ .) +
    theme_bw()
ggsave("anxdep2.png", anxdep2)

qq <- get_syndrome_long("aggressive", tps, mc_d_subs)
qq$"subjectkey" <- paste0("subject_", qq$"subjectkey")
qq_long <- dplyr::full_join(qq, mc_d_cluster_df, by = "subjectkey")
qq_long$"cluster" <- factor(qq_long$"cluster")
qq_long <- na.omit(qq_long)
for (subject in unique(qq_long$"subjectkey")) {
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 3, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 3, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 2, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 2, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 1, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 1, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"] <- 0
}
aggressive2 <- ggplot(
    na.omit(qq_long),
    aes(x = tp, y = cbcl_scr_syn_aggressive_t, colour = cbcl_scr_syn_aggressive_t > 0, group = subjectkey)
) +
    geom_point() +
    geom_line() +
    facet_grid(cluster ~ .) +
    theme_bw()
ggsave("aggressive3.png", aggressive2)


qq <- get_syndrome_long("aggressive", tps, mc_d_subs)
qq$"subjectkey" <- paste0("subject_", qq$"subjectkey")
qq_long <- dplyr::full_join(qq, mc_d_cluster_df, by = "subjectkey")
qq_long$"cluster" <- factor(qq_long$"cluster")
for (subject in unique(qq_long$"subjectkey")) {
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 3, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 3, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 2, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 2, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 1, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 1, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"] <- 0
}
unique(qq_long$"subjectkey")
parent <- all_dls$"mtbi_train_data_lists"$"imp_1"[[24]]$"data"
summarize_dl(all_dls$"mtbi_train_data_lists"$"imp_1")
qq_long <- dplyr::full_join(qq_long, parent, by = "subjectkey")
aggressive4 <- ggplot(
    na.omit(qq_long),
    aes(x = tp, y = cbcl_scr_syn_aggressive_t, colour = parent_aggressive > 60, group = subjectkey)
) +
    geom_point() +
    geom_line() +
    facet_grid(cluster ~ .) +
    theme_bw()
aggressive4
ggsave("aggressive4.png", aggressive4)

qq <- get_syndrome_long("aggressive", tps, mc_d_subs)
qq$"subjectkey" <- paste0("subject_", qq$"subjectkey")
qq_long <- dplyr::full_join(qq, mc_d_cluster_df, by = "subjectkey")
qq_long$"cluster" <- factor(qq_long$"cluster")
for (subject in unique(qq_long$"subjectkey")) {
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 3, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 3, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 2, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 2, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 1, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 1, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"] <- 0
}
unique(qq_long$"subjectkey")
income <- all_dls$"mtbi_train_data_lists"$"imp_1"[[7]]$"data"
qq_long <- dplyr::full_join(qq_long, income, by = "subjectkey")
aggressive5 <- ggplot(
    na.omit(qq_long),
    aes(x = tp, y = cbcl_scr_syn_aggressive_t, colour = household_income, group = subjectkey)
) +
    geom_point() +
    geom_line() +
    facet_grid(cluster ~ .) +
    theme_bw()
aggressive5
ggsave("aggressive5.png", aggressive5)


qq <- get_syndrome_long("aggressive", tps, mc_d_subs)
qq$"subjectkey" <- paste0("subject_", qq$"subjectkey")
qq_long <- dplyr::full_join(qq, mc_d_cluster_df, by = "subjectkey")
qq_long$"cluster" <- factor(qq_long$"cluster")
for (subject in unique(qq_long$"subjectkey")) {
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 3, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 3, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 2, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 2, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 1, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 1, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"] <- 0
}
unique(qq_long$"subjectkey")
data <- collapse_dl(all_dls$"mtbi_train_data_lists"$"imp_1")
qq_long <- dplyr::full_join(qq_long, data, by = "subjectkey")
aggressive6 <- ggplot(
    na.omit(qq_long),
    aes(x = tp, y = cbcl_scr_syn_aggressive_t, colour = sex, group = subjectkey)
) +
    geom_point() +
    geom_line() +
    facet_grid(cluster ~ .) +
    theme_bw()
aggressive6
ggsave("aggressive6.png", aggressive6)

for (tp in c(1, 2, 3)) {
    long_outcomes <- NULL
    for (syndrome in syndromes) {
        if (is.null(long_outcomes)) {
            long_outcomes <- get_cbcl_syndrome_scale(
                syndrome = syndrome,
                mh_p_cbcl,
                raw = FALSE,
                subjects = mtbi_train,
                t = tp
            )
        } else {
            long_outcomes <- dplyr::inner_join(
                long_outcomes,
                get_cbcl_syndrome_scale(
                    syndrome = syndrome,
                    mh_p_cbcl,
                    raw = FALSE,
                    subjects = mtbi_train,
                    t = tp
                ),
                by = "subjectkey"
            )
        }
    }
    long_outcomes <- dplyr::inner_join(
        long_outcomes,
        get_sds_total_probs(
            ph_p_sds,
            mtbi_train,
            t = tp
        ),
        by = "subjectkey"
    )
    long_outcomes$"subjectkey" <- paste0("subject_", long_outcomes$"subjectkey")
    colnames(long_outcomes) <- c(
        "subjectkey",
        paste0("cbcl_", syndromes),
        "sds_sleep"
    )
    baseline_outcomes <- collapse_dl(oom_list_m3)
    d_outcomes <- NULL
    for (outcome in colnames(baseline_outcomes[-1])) {
        t0 <- dplyr::select(baseline_outcomes, "subjectkey", outcome)
        tn <- dplyr::select(long_outcomes, "subjectkey", outcome)
        colnames(t0) <- c("subjectkey", paste0(outcome, "_0"))
        colnames(tn) <- c("subjectkey", paste0(outcome, "_", tp))
        both_t <- dplyr::inner_join(t0, tn, by = "subjectkey")
        both_t[, 4] <- both_t[, 3] - both_t[, 2]
        colnames(both_t)[4] <- paste0("d_", outcome)
        both_t <- both_t[, c(1, 4)]
        if (is.null(d_outcomes)) {
            d_outcomes <- both_t
        } else {
            d_outcomes <- dplyr::full_join(d_outcomes, both_t, by = "subjectkey")
        }
    }
    mtbi_mc_a <- mtbi_rep[1, ]
    mtbi_mc_a <- get_cluster_df(mtbi_mc_a)
    mtbi_mc_a <- dplyr::full_join(
        mtbi_mc_a,
        d_outcomes,
        by = "subjectkey"
    )
    mtbi_mc_a$"cluster" <- factor(mtbi_mc_a$"cluster")
    d_plots <- list()
    for (outcome in colnames(d_outcomes)[-1]) {
        plot <- mtbi_mc_a |>
            ggplot(
                aes(
                    x = cluster,
                    y = !!sym(outcome),
                    colour = cluster
                )
            ) +
            geom_violin(alpha = 0.4) +
            geom_jitter(width = 0.2, height = 0.2) +
            stat_summary(
                fun = "mean",
                geom = "point",
                colour = "black",
                size = 2
            ) +
            labs(
                x = "Cluster",
                y = gsub("d_", "Δ", outcome)
            ) +
            theme_bw() +
            theme(
                legend.position = "none"
            )
        d_plots[[length(d_plots) + 1]] <- plot
    }
    d_plots <- d_plots |>
        wrap_plots() +
        plot_annotation(
            paste0("CBCL/SDS Outcomes, ", tp, "-year Follow-Up Minus Baseline"),
            theme = theme(plot.title=element_text(hjust=0.5))
        )
    # Looks like cluster 1 has the higher variance, indicating potential for intervention?
    ggsave(
        plot = d_plots,
        filename = fig_path(
            paste0("mtbi_mc_a_outcomes_t", tp, "_plots.png"),
            TRUE
        ),
        width = 8,
        height = 8,
        dpi = 120
    )
}

full_df <- NULL
for (tp in c(0, 1, 2, 3, 4)) {
    long_outcomes <- NULL
    for (syndrome in syndromes) {
        if (is.null(long_outcomes)) {
            long_outcomes <- get_cbcl_syndrome_scale(
                syndrome = syndrome,
                mh_p_cbcl,
                raw = FALSE,
                subjects = mtbi_train,
                t = tp
            )
            colnames(long_outcomes) <- c("subjectkey", syndrome)
        } else {
            new_df <- get_cbcl_syndrome_scale(
                syndrome = syndrome,
                mh_p_cbcl,
                raw = FALSE,
                subjects = mtbi_train,
                t = tp
            )
            colnames(new_df) <- c("subjectkey", syndrome)
            long_outcomes <- dplyr::full_join(
                long_outcomes,
                new_df,
                by = "subjectkey"
            )
        }
    }
    long_outcomes$"tp" <- tp
    if (is.null(full_df)) {
        full_df <- long_outcomes
    } else {
        full_df <- rbind(full_df, long_outcomes)
    }
}
full_df$"subjectkey" <- paste0("subject_", full_df$"subjectkey")
mtbi_mc_a <- mtbi_rep[1, ]
mtbi_mc_a <- get_cluster_df(mtbi_mc_a)
mtbi_mc_a$"cluster" <- factor(mtbi_mc_a$"cluster")
full_df <- dplyr::full_join(full_df, mtbi_mc_a, by = "subjectkey")
full_df$"tp" <- factor(full_df$"tp")
full_df |>
    dplyr::filter(cluster == 1) |>
    na.omit() |>
    ggplot(
        aes(
            x = tp,
            y = aggressive,
            group = subjectkey,
            colour = cluster
        )
    ) +
    geom_line() +
    geom_point() +
    theme_bw()

nrow(mtbi_mc_a)

head(mtbi_mc_a)

head(long_outcomes)
```


## A deeper dive at feature separation

```{r}
dl_df <- auto_plot(
    solutions_matrix_row = mtbi_mc_d_esm,
    data_list = all_dls$"mtbi_train_data_lists"$"imp_3",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_3",
    return_plots = FALSE
)

dl_df |>
    dplyr::filter(sex == 0) |>
    ggplot(
        aes(
            x = race,
            y = brain_volume,
            colour = race,
            group = race
        )
    ) +
    geom_point() +
    theme_bw() +
    facet_grid(household_income ~ .)

dl_df$"household_income" <- factor(dl_df$"household_income")
dl_df$"sex" <- factor(dl_df$"sex")

dl_df |>
    ggplot(
        aes(
            x = household_income,
            y = cbcl_aggressive,
            colour = race,
            group = interaction(race, household_income)
        )
    ) +
    geom_violin(position = position_dodge(width = 0.75)) +
    geom_jitter(
        position = position_jitterdodge(
            jitter.width = 0,
            jitter.height = 0.5
        ),
    ) +
    theme_bw()

dl_df |>
    ggplot(
        aes(
            x = sex,
            y = cbcl_aggressive,
            colour = race,
            group = interaction(race, sex)
        )
    ) +
    geom_boxplot(position = position_dodge(width = 0.75), width = 0.4) +
    geom_jitter(
        position = position_jitterdodge(
            jitter.width = 0,
            jitter.height = 0.5
        ),
    ) +
    theme_bw()
```



