# metaSNF of Baseline mTBI Subjects

In this chapter, I use the metaSNF package to generate and characterize meta clusters of the extracted data.

## Importing packages and establishing file paths


```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)
library(ggplot2)
library(patchwork)
library(xtable)
library(compute.es)
library(dplyr)
library(fastDummies)
library(tidyr)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subjects <- read_csv(sub_path("2024_09_13_mtbi_subjects.csv"))
mtbi_train_subjects <- read_csv(sub_path("2024_09_13_mtbi_train_subjects.csv"))
mtbi_test_subjects <- read_csv(sub_path("2024_09_13_mtbi_test_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2024_09_13_uninjured_subjects.csv"))
```


## Importing data


```{r}
# CHECKPOINT
all_dls <- list.load(input_path("2024_09_13_all_dls.rds"))
```


## Generating custom distance measures


```{r}
# CHECKPOINT
###############################################################################
# 2. Add standard normalized variations to the distance metrics list (also
# achievable through toggling automatic_standard_normalize parameter in
# `batch_snf`)
###############################################################################
my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

summarize_dml(my_distance_metrics)
```


## Generating the settings matrix


```{r}
mtbi_settings_matrix <- generate_settings_matrix(
    all_dls$"mtbi_train_data_lists"$"imp_1",
    nrow = 200,
    seed = 42,
    distance_metrics_list = my_distance_metrics
)

write_csv(mtbi_settings_matrix, proc_path("mtbi_settings_matrix.csv", TRUE))

mtbi_settings_matrix <- read_csv(
    proc_path("2024_09_13_mtbi_settings_matrix.csv")
)
```


## Running SNF for each of the imputations


```{r}
mtbi_solutions_matrix_s1 <- batch_snf(
    data_list = all_dls$"mtbi_train_data_lists"[[1]],
    settings_matrix = mtbi_settings_matrix,
    distance_metrics_list = my_distance_metrics,
    processes = "max"
)
write_csv(mtbi_solutions_matrix_s1, proc_path("mtbi_solutions_matrix_s1.csv", TRUE))
#
mtbi_solutions_matrix_s2 <- batch_snf(
    data_list = all_dls$"mtbi_train_data_lists"[[2]],
    settings_matrix = mtbi_settings_matrix,
    distance_metrics_list = my_distance_metrics,
    processes = "max"
)
write_csv(mtbi_solutions_matrix_s2, proc_path("mtbi_solutions_matrix_s2.csv", TRUE))
#
mtbi_solutions_matrix_s3 <- batch_snf(
    data_list = all_dls$"mtbi_train_data_lists"[[3]],
    settings_matrix = mtbi_settings_matrix,
    distance_metrics_list = my_distance_metrics,
    processes = "max"
)
write_csv(mtbi_solutions_matrix_s3, proc_path("mtbi_solutions_matrix_s3.csv", TRUE))
#
mtbi_solutions_matrix_s4 <- batch_snf(
    data_list = all_dls$"mtbi_train_data_lists"[[4]],
    settings_matrix = mtbi_settings_matrix,
    distance_metrics_list = my_distance_metrics,
    processes = "max"
)
write_csv(mtbi_solutions_matrix_s4, proc_path("mtbi_solutions_matrix_s4.csv", TRUE))
#
mtbi_solutions_matrix_s5 <- batch_snf(
    data_list = all_dls$"mtbi_train_data_lists"[[5]],
    settings_matrix = mtbi_settings_matrix,
    distance_metrics_list = my_distance_metrics,
    processes = "max"
)
write_csv(mtbi_solutions_matrix_s5, proc_path("mtbi_solutions_matrix_s5.csv", TRUE))
#
mtbi_solutions_matrix_p1 <- batch_snf(
    data_list = all_dls$"mtbi_pooled_data_lists"[[1]],
    settings_matrix = mtbi_settings_matrix,
    distance_metrics_list = my_distance_metrics,
    processes = "max"
)
write_csv(mtbi_solutions_matrix_p1, proc_path("mtbi_solutions_matrix_p1.csv", TRUE))
#
mtbi_solutions_matrix_p2 <- batch_snf(
    data_list = all_dls$"mtbi_pooled_data_lists"[[2]],
    settings_matrix = mtbi_settings_matrix,
    distance_metrics_list = my_distance_metrics,
    processes = "max"
)
write_csv(mtbi_solutions_matrix_p2, proc_path("mtbi_solutions_matrix_p2.csv", TRUE))
#
mtbi_solutions_matrix_p3 <- batch_snf(
    data_list = all_dls$"mtbi_pooled_data_lists"[[3]],
    settings_matrix = mtbi_settings_matrix,
    distance_metrics_list = my_distance_metrics,
    processes = "max"
)
write_csv(mtbi_solutions_matrix_p3, proc_path("mtbi_solutions_matrix_p3.csv", TRUE))
#
mtbi_solutions_matrix_p4 <- batch_snf(
    data_list = all_dls$"mtbi_pooled_data_lists"[[4]],
    settings_matrix = mtbi_settings_matrix,
    distance_metrics_list = my_distance_metrics,
    processes = "max"
)
write_csv(mtbi_solutions_matrix_p4, proc_path("mtbi_solutions_matrix_p4.csv", TRUE))
#
mtbi_solutions_matrix_p5 <- batch_snf(
    data_list = all_dls$"mtbi_pooled_data_lists"[[5]],
    settings_matrix = mtbi_settings_matrix,
    distance_metrics_list = my_distance_metrics,
    processes = "max"
)
write_csv(mtbi_solutions_matrix_p5, proc_path("mtbi_solutions_matrix_p5.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_solutions_matrix_s1 <- read_csv(proc_path("2024_09_13_mtbi_solutions_matrix_s1.csv"))
mtbi_solutions_matrix_s2 <- read_csv(proc_path("2024_09_13_mtbi_solutions_matrix_s2.csv"))
mtbi_solutions_matrix_s3 <- read_csv(proc_path("2024_09_13_mtbi_solutions_matrix_s3.csv"))
mtbi_solutions_matrix_s4 <- read_csv(proc_path("2024_09_13_mtbi_solutions_matrix_s4.csv"))
mtbi_solutions_matrix_s5 <- read_csv(proc_path("2024_09_13_mtbi_solutions_matrix_s5.csv"))
mtbi_solutions_matrix_p1 <- read_csv(proc_path("2024_09_13_mtbi_solutions_matrix_p1.csv"))
mtbi_solutions_matrix_p2 <- read_csv(proc_path("2024_09_13_mtbi_solutions_matrix_p2.csv"))
mtbi_solutions_matrix_p3 <- read_csv(proc_path("2024_09_13_mtbi_solutions_matrix_p3.csv"))
mtbi_solutions_matrix_p4 <- read_csv(proc_path("2024_09_13_mtbi_solutions_matrix_p4.csv"))
mtbi_solutions_matrix_p5 <- read_csv(proc_path("2024_09_13_mtbi_solutions_matrix_p5.csv"))

mtbi_sm <- do.call(
    "rbind",
    list(
        mtbi_solutions_matrix_s1,
        mtbi_solutions_matrix_s2,
        mtbi_solutions_matrix_s3,
        mtbi_solutions_matrix_s4,
        mtbi_solutions_matrix_s5,
        mtbi_solutions_matrix_p1,
        mtbi_solutions_matrix_p2,
        mtbi_solutions_matrix_p3,
        mtbi_solutions_matrix_p4,
        mtbi_solutions_matrix_p5
    )
)
write_csv(data.frame(mtbi_sm), proc_path("mtbi_sm.csv", TRUE))

mtbi_ari <- calc_aris(mtbi_sm, processes = "max")
#
write_csv(data.frame(mtbi_ari), proc_path("mtbi_ari.csv", TRUE))
#
mtbi_ari_order <- get_matrix_order(mtbi_ari)
#
write_csv(data.frame(mtbi_ari_order), proc_path("mtbi_ari_order.csv", TRUE))
```

## Re-importing data

```{r}
# CHECKPOINT
mtbi_sm <- read_csv(proc_path("2024_09_13_mtbi_sm.csv"))
mtbi_ari <- as.matrix(read_csv(proc_path("2024_09_13_mtbi_ari.csv")))
mtbi_ari_order <- unlist(read_csv(proc_path("2024_09_13_mtbi_ari_order.csv")))
names(mtbi_ari_order) <- NULL
```

## Calculating associations between cluster solutions and features

```{r}
imputation_labels <- data.frame(
    "imputation" = c(
        rep("s1", 200),
        rep("s2", 200),
        rep("s3", 200),
        rep("s4", 200),
        rep("s5", 200),
        rep("p1", 200),
        rep("p2", 200),
        rep("p3", 200),
        rep("p4", 200),
        rep("p5", 200)
    ),
    "pooled" = c(
        rep("no", 1000),
        rep("yes", 1000)
    )
)

mtbi_sm_l <- cbind(mtbi_sm, imputation_labels)

mtbi_esm_s1 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "s1", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_1",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_1",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_s2 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "s2", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_2",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_2",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_s3 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "s3", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_3",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_3",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_s4 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "s4", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_4",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_4",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_s5 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "s5", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_5",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_5",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_p1 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "p1", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_1",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_1",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_p2 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "p2", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_2",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_2",
    min_pval = 1e-10,
    processes = 1
)

mtbi_esm_p3 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "p3", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_3",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_3",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_p4 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "p4", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_4",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_4",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_p5 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "p5", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_5",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_5",
    min_pval = 1e-10,
    processes = "max"
)

mtbi_esm <- dplyr::bind_rows(
    mtbi_esm_s1,
    mtbi_esm_s2,
    mtbi_esm_s3,
    mtbi_esm_s4,
    mtbi_esm_s5,
    mtbi_esm_p1,
    mtbi_esm_p2,
    mtbi_esm_p3,
    mtbi_esm_p4,
    mtbi_esm_p5
)

#
mtbi_esm$"impairment_separation" <- -log10(mtbi_esm$"mean_pval")
#
write_csv(mtbi_esm, proc_path("mtbi_esm.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_esm <- read_csv(proc_path("2024_09_13_mtbi_esm.csv"))
```


## Identifying and visualizing meta clusters


```{r}
base_ari_hm <- adjusted_rand_index_heatmap(
    mtbi_ari,
    order = mtbi_ari_order
)

shiny_annotator(base_ari_hm)

mtbi_split_vec <- c(
    178,
    324,
    397,
    570,
    681,
    1652,
    1861,
    1961
)

write_csv(data.frame(mtbi_split_vec), proc_path("mtbi_split_vec.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_split_vec <- read_csv(proc_path("2024_09_13_mtbi_split_vec.csv")) |>
    unlist() |>
    as.numeric()
```

```{r}
divergent_colours <- function(column)  {
    values <- unique(column)
    colours <- RColorBrewer::brewer.pal(n = length(values), name = "Set3")
    names(colours) <- values
    return(colours)
}

full_mtbi_ari_hm <- adjusted_rand_index_heatmap(
    aris = mtbi_ari,
    order = mtbi_ari_order,
    data = mtbi_esm,
    min_colour = "black",
    split_vector = mtbi_split_vec,
    top_hm = list(
        "Impairment Separation" = "impairment_separation"
    ),
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    left_hm = list(
        "Pooled" = "pooled",
        "Imputation" = "imputation"
    ),
    annotation_colours = list(
        "Impairment Separation" = colour_scale(
            mtbi_esm$"impairment_separation",
            min_colour = "gray7",
            max_colour = "limegreen"
        ),
        "Imputation" = divergent_colours(mtbi_esm$"imputation"),
        "Pooled" = c(
            "yes" = "orange",
            "no" = "purple"
        )
    )
)
full_mtbi_ari_hm

save_heatmap(
    heatmap = full_mtbi_ari_hm,
    path = fig_path("full_mtbi_ari_hm.png", TRUE),
    width = 950,
    height = 900,
    res = 100
)

# Another heatmap without the imputation-related columns
lite_mtbi_ari_hm <- adjusted_rand_index_heatmap(
    aris = mtbi_ari,
    order = mtbi_ari_order,
    data = mtbi_esm,
    min_colour = "black",
    split_vector = mtbi_split_vec,
    top_hm = list(
        "Impairment Separation" = "impairment_separation"
    ),
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    annotation_colours = list(
        "Impairment Separation" = colour_scale(
            mtbi_esm$"impairment_separation",
            min_colour = "gray7",
            max_colour = "limegreen"
        )
    )
)

save_heatmap(
    heatmap = lite_mtbi_ari_hm,
    path = fig_path("lite_mtbi_ari_hm.png", TRUE),
    width = 900,
    height = 700,
    res = 100
)
```

When picking out representative solutions, I'd like to preferentially go for solutions that derived from solo rather than pooled imputations, as those solutions have values for all features.

```{r}
# Function to try to lean on mTBI-including solutions when possible.
# This function will pick from solo solutions unless over 70% of the meta
# cluster is pooled.
restrict_fn <- function(x, threshold = 0.3) {
    x_solo_ind <- x$"imputation" %in% c("s1", "s2", "s3", "s4", "s5")
    x_pool_ind <- x$"imputation" %in% c("p1", "p2", "p3", "p4", "p5")
    x_solo <- x[x_solo_ind, ]
    x_pool <- x[x_pool_ind, ]
    frac_solo <- nrow(x_solo) / (nrow(x_solo) + nrow(x_pool))
    if (frac_solo < threshold) {
        return(x[x_pool_ind, ])
    } else {
        return(x[x_solo_ind, ])
    }
}

mtbi_rep_solutions <- get_representative_solutions(
    mtbi_ari,
    split_vector = mtbi_split_vec,
    order = mtbi_ari_order,
    filter_fn = restrict_fn,
    mtbi_esm
)

# Based on the heatmap, we'll remove B, E, H, K (unstable meta clusters)
mtbi_rep_solutions <- dplyr::filter(
    mtbi_rep_solutions,
    !label %in% c("B", "F", "I")
)

write_csv(mtbi_rep_solutions, proc_path("mtbi_rep_solutions.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_rep_solutions <- read_csv(proc_path("2024_09_13_mtbi_rep_solutions.csv"))
```

```{r}
# D (s3) is the top looking solution
mtbi_rep_solutions$"imputation"
mtbi_rep_solutions$"label"

mtbi_manhattan <- mc_manhattan_plot(
    mtbi_rep_solutions,
    data_list = all_dls$"mtbi_train_data_lists"$"imp_3",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_3",
    domain_colours = c(
        "AS" = "#85929e",
        "D" = "#bb8fce",
        "N" = "#e59866",
        "MH" = "#7fb3d5",
        "P" = "#52be80",
        "S" = "#d98880",
        "B" = "#ff3131"
    )
)
mtbi_manhattan

ggsave(
    plot = mtbi_manhattan,
    filename = fig_path("mtbi_manhattan.png", TRUE),
    width = 18,
    height = 14,
    dpi = 120
)

# The most robust solution
mtbi_mc_d_esm <- mtbi_rep_solutions |>
    dplyr::filter(label == "D")

write_csv(mtbi_mc_d_esm, proc_path("mtbi_mc_d_esm.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_mc_d_esm <- read_csv(proc_path("2024_09_13_mtbi_mc_d_esm.csv"))
```

```{r}
# Feature plot generation
plot_list <- auto_plot(
    solutions_matrix_row = mtbi_mc_d_esm,
    data_list = all_dls$"mtbi_train_data_lists"$"imp_2",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_2",
    save = fig_path("mtbi_mc_d", TRUE)
)

# No save version:
plot_list <- auto_plot(
    solutions_matrix_row = mtbi_mc_d_esm,
    data_list = all_dls$"mtbi_train_data_lists"$"imp_2",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_2"
)

#all_plots <- wrap_plots(plot_list)
#
## Good enough as a snapshot
#ggsave(
#    fig_path("mtbi_mc_d_all_plots.png", TRUE),
#    all_plots,
#    width = 45,
#    height = 30,
#    dpi = 50
#)
```


## Characterization of meta cluster D representative solution

### NMI


```{r}
nmis <- batch_nmi(
    all_dls$"mtbi_train_data_lists"$"imp_3",
    mtbi_mc_d_esm,
    distance_metrics_list = my_distance_metrics
)

nmi_order <- sort(
    nmis$"row_id_16",
    decreasing = TRUE,
    index.return = TRUE
)

ordered_nmis <- nmis[nmi_order$ix, ]

ordered_nmis$"nmi_rank" <- rank(
    -ordered_nmis$"row_id_16",
    ties.method = "min"
)
```


### p-values


```{r}
pvals <- get_pvals(
    mtbi_mc_d_esm,
    keep_summaries = FALSE
)
pvals <- data.frame(
    "feature" = gsub("_pval", "", names(pvals)),
    "neg_log_pval" = -log10(as.numeric(unlist(pvals)))
)
pvals <- pvals[-1, ]
pvals_order <- sort(
    pvals$"neg_log_pval",
    decreasing = TRUE,
    index.return = TRUE
)
ordered_pvals <- pvals[pvals_order$ix, ]
ordered_pvals <- dplyr::filter(
    ordered_pvals,
    !grepl("^cbcl|^sds", feature)
)

ordered_pvals$"pval_rank" <- rank(
    -ordered_pvals$"neg_log_pval",
    ties.method = "min"
)
```


### Joint rank


```{r}
mtbi_mc_d_nmi_v_pval <- dplyr::full_join(
    ordered_nmis,
    ordered_pvals,
    by = "feature"
)

domain_df <- dl_variable_summary(all_dls$"mtbi_train_data_lists"$"imp_3") |>
    dplyr::select(name, domain) |>
    dplyr::rename("feature" = "name")

mtbi_mc_d_nmi_v_pval <- mtbi_mc_d_nmi_v_pval |>
    dplyr::inner_join(domain_df, by = "feature")

mtbi_mc_d_nmi_v_pval$"joint_rank" <- rank(
    mtbi_mc_d_nmi_v_pval$"nmi_rank" + mtbi_mc_d_nmi_v_pval$"pval_rank",
    ties.method = "min"
)

joint_order <- sort(
    mtbi_mc_d_nmi_v_pval$"joint_rank",
    decreasing = FALSE,
    index.return = TRUE
)

mtbi_mc_d_nmi_v_pval_rank <- mtbi_mc_d_nmi_v_pval[joint_order$ix, ]

mtbi_mc_d_nmi_v_pval_rank <- mtbi_mc_d_nmi_v_pval_rank |>
    dplyr::rename("nmi" = "row_id_16")

mtbi_mc_d_nmi_v_pval_rank <- mtbi_mc_d_nmi_v_pval_rank |>
    dplyr::select(
        feature,
        domain,
        nmi,
        nmi_rank,
        neg_log_pval,
        pval_rank,
        joint_rank
    )

write_csv(
    mtbi_mc_d_nmi_v_pval_rank,
    proc_path("mtbi_mc_d_nmi_v_pval_rank.csv", TRUE)
)

data.frame(mtbi_mc_d_nmi_v_pval_rank)
options(width=200)

# Latex table
xtable(data.frame(mtbi_mc_d_nmi_v_pval_rank))
```
                  feature domain          nmi nmi_rank neg_log_pval pval_rank joint_rank
1            brain_volume      N 0.2776266197        1   10.0000000         1          1
2                     sex      D 0.2581508525        2   10.0000000         1          2
3             cortical_sa      N 0.2111381159        3   10.0000000         1          3
4        household_income      D 0.1810385126        4   10.0000000         1          4
5       pubertal_status_p      D 0.1051259234        5   10.0000000         1          5
7      programs_this_year      P 0.0823618086        7   10.0000000         1          6
8     non_school_programs      P 0.0817780853        8   10.0000000         1          7
10         parent_thought      P 0.0733320070       10   10.0000000         1          8
11         parent_somatic      P 0.0696680813       11   10.0000000         1          9
12     weekday_screentime      P 0.0627533945       12   10.0000000         1         10
14      parent_antisocial      P 0.0594433093       14   10.0000000         1         11
16      parent_aggressive      P 0.0522685698       16   10.0000000         1         12
17         parent_depress      P 0.0511940884       17   10.0000000         1         13
19          parent_anxdep      P 0.0462568187       19   10.0000000         1         14
6                    race      D 0.0860664419        6    9.7494599        15         15
15       parent_anxdisord      P 0.0528332239       15    9.6413802        16         16
13    private_instruction      P 0.0597443003       13    6.7568611        19         17
9      weekend_screentime      P 0.0747239075        9    3.5264398        26         18
18       parent_withdrawn      P 0.0485413864       18    7.8853004        17         18
20        parent_avoidant      P 0.0379034983       20    6.4518066        20         20
22     parent_hyperactive      P 0.0364016053       22    7.8190730        18         20
23         fmri_cort_cors      N 0.0341594597       23    4.5742846        22         22
21 fmri_cort_subcort_cors      N 0.0370401297       21    3.8043159        25         23
26       parent_attention      P 0.0293624701       26    6.1498796        21         24
24          parent_perstr      P 0.0326454993       24    3.9439718        24         25
29       parent_intrusive      P 0.0276512455       29    3.9832227        23         26
27         family_fight_p      P 0.0285074289       27    3.2882631        28         27
30           major_wm_ndi      N 0.0272209994       30    3.4384221        27         28
25       headache_history     MH 0.0312518787       25    2.7519873        35         29
28          exercise_time      P 0.0279864497       28    2.7879585        33         30
31          considerate_y      P 0.0250763392       31    3.1525180        30         30
32        family_temper_p      P 0.0241724255       32    3.2329566        29         30
33         family_outdo_p      P 0.0233301963       33    2.8196567        32         33
36     cortical_thickness      N 0.0216520750       36    2.9266173        31         34
35           helps_hurt_p      P 0.0228312639       35    2.6913532        36         35
38  same_sex_close_friend      P 0.0208609812       38    2.7876879        34         36
34      family_peaceful_p      P 0.0230310265       34    2.2618231        40         37
40         family_outdo_y      P 0.0190255962       40    2.3996813        37         38
41               mtbi_loc     AS 0.0184840348       41    2.3170946        38         39
42     family_criticize_p      P 0.0176136782       42    2.2883720        39         40
37        school_programs      P 0.0210050174       37    1.8728170        47         41
39           family_hit_p      P 0.0194387480       39    1.9557489        45         41
43         family_angry_p      P 0.0167580033       43    2.2435830        41         41
45              helpful_y      P 0.0164386095       45    2.2068772        42         44
47              helpful_p      P 0.0160051496       47    1.9782105        44         45
48         family_angry_y      P 0.0157444270       48    2.0861456        43         45
46    pericortical_wm_ndi      N 0.0160571592       46    1.7563647        49         47
49          family_yell_y      P 0.0155392309       49    1.9524668        46         47
44      pubertal_status_y      D 0.0166271749       44    1.2701631        53         49
51           helps_hurt_y      P 0.0151843347       51    1.8356762        48         50
50                    age      D 0.0153915661       50    1.3306869        52         51
53     family_criticize_y      P 0.0125839242       53    1.5379514        50         52
54         family_throw_p      P 0.0123127601       54    1.3409601        51         53
55          mtbi_mem_daze     AS 0.0117825584       55    1.2001902        54         54
56        same_sex_friend      P 0.0113222522       56    1.0984904        55         55
52               mtbi_age      D 0.0149382443       52    0.4121475        61         56
57         previous_mtbis     MH 0.0076714561       57    0.8698083        57         57
58          considerate_p      P 0.0071864214       58    0.9115176        56         57
59      family_peaceful_y      P 0.0071260923       59    0.6692267        59         59
61         mtbi_mechanism     AS 0.0038511030       61    0.7045122        58         60
60         family_fight_y      P 0.0055963070       60    0.6475604        60         61
62           family_hit_y      P 0.0033438213       62    0.3744418        62         62
64         family_throw_y      P 0.0024088317       64    0.2388636        64         63
65        family_temper_y      P 0.0023806944       65    0.3098676        63         63
63   opp_sex_close_friend      P 0.0025380247       63    0.1711698        66         65
66         opp_sex_friend      P 0.0021859169       66    0.1820859        65         66
67          family_yell_p      P 0.0007776271       67    0.1036635        67         67


```{r}
# CHECKPOINT
mtbi_mc_d_nmi_v_pval_rank <- read_csv(
    proc_path("2024_09_13_mtbi_mc_d_nmi_v_pval_rank.csv")
)

sorted_features <- mtbi_mc_d_nmi_v_pval_rank$"feature"
```


### Correlation of NMI and p-value


```{r}
nmi_v_p_rho <- cor(
    mtbi_mc_d_nmi_v_pval_rank$"nmi_rank",
    mtbi_mc_d_nmi_v_pval_rank$"pval_rank",
    method = "spearman"
)

nmi_v_pval_plot <- mtbi_mc_d_nmi_v_pval_rank |>
    ggplot(
        aes(x = nmi_rank, y = pval_rank, label = feature, colour = domain)
    ) +
    geom_point(size = 2) + 
    scale_colour_manual(
        values = c(
            "AS" = "#85929e",
            "D" = "#bb8fce",
            "N" = "#e59866",
            "MH" = "#7fb3d5",
            "P" = "#52be80"
        )
    ) +
    theme_bw() +
    labs(x = "Rank by NMI", y = "Rank by Association p-value") +
    ggrepel::geom_text_repel(
        #vjust = 3,
        #hjust = 1,
        force = 1,
        max.overlaps = 35,
        size = 4
    ) +
    annotate(
        "text",
        x = 4,
        y = 50,
        size = 5,
        label = paste("Spearman's ρ =", round(nmi_v_p_rho, 2)),
        hjust = 0
    ) + 
    theme(text = element_text(size = 16))
nmi_v_pval_plot

ggsave(
    fig_path("nmi_v_pval_plot.png", TRUE),
    nmi_v_pval_plot,
    width = 12,
    height = 12
)
```

<!-- {{{ -->
### Visualizing top 12 features

```{r}
#names(plot_list)
#
#ranked_plot_list <- plot_list[sorted_features]
#
#ranked_all_plots <- wrap_plots(ranked_plot_list)
#
#ggsave(
#    fig_path("mtbi_mc_d_ranked_all_plots.png", TRUE),
#    ranked_all_plots,
#    width = 45,
#    height = 30,
#    dpi = 50
#)
#
#saveRDS(
#    ranked_all_plots,
#    file = fig_path("mtbi_mc_d_ranked_all_plots.rds", TRUE)
#)
#
#mtbi_mc_e_ranked_all_plots <- readRDS(
#    fig_path("2024_09_13_mtbi_mc_d_ranked_all_plots.rds")
#)
#
################################################################################
## Building the top 12 plot list
################################################################################
#
#mc_d_top_pl <- ranked_plot_list[1:12]
#
#names(mc_d_top_pl) <- sorted_features[1:12]
#
#names(mc_d_top_pl)
#
##
#mc_d_top_pl$"sex" <- mc_d_top_pl$"sex" +
#    labs(fill = "Sex") +
#    scale_fill_discrete(labels = c("F", "M"))
##
#mc_d_top_pl$"brain_volume" <- mc_d_top_pl$"brain_volume" +
#    labs(y = expression(paste("Brain Volume ", (mm^3))))
##
#mc_d_top_pl$"cortical_sa" <- mc_d_top_pl$"cortical_sa" +
#    labs(y = expression(paste("Cortical Area ", (mm^2))))
##
#mc_d_top_pl$"household_income" <- mc_d_top_pl$"household_income" +
#    labs(y = "Household Income")
##
#mc_d_top_pl$"pubertal_status_p" <- mc_d_top_pl$"pubertal_status_p" +
#    labs(y = "Pubertal Status - P")
##
#mc_d_top_pl$"programs_this_year" <- mc_d_top_pl$"programs_this_year" +
#    labs(y = "Total Activities this Year")
##
#mc_d_top_pl$"non_school_programs" <- mc_d_top_pl$"non_school_programs" +
#    labs(y = "Lifetime Extracurriculars")
##
#mc_d_top_pl$"parent_somatic" <- mc_d_top_pl$"parent_somatic" +
#    labs(y = "Parent Somatic Problems")
##
#mc_d_top_pl$"weekday_screentime" <- mc_d_top_pl$"weekday_screentime" +
#    labs(y = "Weekday Screentime")
##
#mc_d_top_pl$"race" <- mc_d_top_pl$"race" +
#    labs(fill = "Race") +
#    scale_fill_discrete(labels = c("Black", "Hispanic", "Other", "White"))
##
#mc_d_top_pl$"parent_depress" <- mc_d_top_pl$"parent_depress" +
#    labs(y = "Parent Depression Problems")
##
#mc_d_top_pl$"parent_thought" <- mc_d_top_pl$"parent_thought" +
#    labs(y = "Parent Thought Problems")
##
#
#mc_d_top_p <- wrap_plots(
#    mc_d_top_pl,
#) & labs(x = "Cluster") & theme(plot.margin = unit(c(0.5, 1.5, 0.5, 2), "cm"))
#ggsave(
#    fig_path("mtbi_mc_d_ranked_all_plots_12.png", TRUE),
#    mc_d_top_p,
#    width = 25,
#    height = 15,
#    dpi = 150
#)
#
#
################################################################################
## Outcomes
################################################################################
#
#mtbi_mc_d_esm_plot_df <- auto_plot(
#    solutions_matrix_row = mtbi_mc_d_esm,
#    data_list = all_dls$"mtbi_train_data_lists"$"imp_2",
#    target_list = all_dls$"mtbi_train_oom_lists"$"imp_2",
#    return_plots = FALSE
#)
#
#write_csv(mtbi_mc_d_esm_plot_df, proc_path("mtbi_mc_d_esm_plot_df.csv", TRUE))
```

```{r}
#mtbi_mc_d_esm_plot_df <- read_csv(proc_path("2024_09_03_mtbi_mc_d_esm_plot_df.csv"))
```

```{r}
#mtbi_mc_d_ranked_all_plots[[2]]
#
#outcome_plot_list <- auto_plot(
#    solutions_matrix_row = mtbi_mc_d_esm,
#    target_list = all_dls$"mtbi_train_oom_lists"$"imp_2"
#)
#
#names(outcome_plot_list)
#
#clean_names <- c(
#    "CBCL\nAnxious-Depressed",
#    "CBCL\nWithdrawn-Depressed",
#    "CBCL\nSomatic Problems",
#    "CBCL\nSocial Problems",
#    "CBCL\nThought Problems",
#    "CBCL\nAttention Problems",
#    "CBCL\nRule-breaking Problems",
#    "CBCL\nAggression Problems",
#    "SDS Total\nSleeping Problems"
#)
#for (i in seq_along(outcome_plot_list)) {
#    outcome_plot_list[[i]] <- outcome_plot_list[[i]] +
#        labs(y = clean_names[[i]], x = "Cluster")
#}
#
#outcome_plot_wrap <- wrap_plots(outcome_plot_list) &
#    theme(plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), "cm"))
#
#ggsave(
#    fig_path("mtbi_mc_d_outcome_plot_wrap.png", TRUE),
#    outcome_plot_wrap,
#    width = 14,
#    height = 14,
#    dpi = 150
#)
```
<!-- }}} -->

### Detailed cluster topologies

Can come back to this later.

```{r}
tstat <- function(d, n1, n2) {
    t <- d * sqrt((n1 * n2) / (n1 + n2))
    return(t)
}
pooled_sd <- function(n1, s1, n2, s2) {
    numerator <- ((n1 - 1) * (s1^2)) + ((n2 - 1) * (s2^2))
    denominator <- n1 + n2 - 2
    s <- sqrt(numerator / denominator)
    return(s)
}
cohens_d <- function(mean1, mean2, pooled_sd) {
    d <- (mean1 - mean2) / pooled_sd
    return(d)
}

calc_des <- function(x1, x2) {
    n1 <- length(x1)
    n2 <- length(x2)
    s1 <- sd(x1)
    s2 <- sd(x2)
    s <- pooled_sd(n1, s1, n2, s2)
    mean1 <- mean(x1)
    mean2 <- mean(x2)
    d <- cohens_d(mean1, mean2, s)
    d_full <- compute.es::des(
        d,
        n1,
        n2,
        verbose = FALSE
    )
    return(
        list(
            "es" = d_full$"d",
            "l" = d_full$"l.d",
            "u" = d_full$"u.d"
        )
    )
}

calc_propes <- function(x1, x2) {
    d_full <- compute.es::propes(
        mean(x1),
        mean(x2),
        length(x1),
        length(x2),
        verbose = FALSE
    )
    return(
        list(
            "es" = d_full$"OR",
            "l" = d_full$"l.or",
            "u" = d_full$"u.or"
        )
    )
}

dummy_non_numeric <- function(df) {
    to_dummy <- colnames(df)[!sapply(df, is.numeric)]
    dummied_df <- dummy_cols(
        df,
        select_columns = to_dummy,
        remove_selected_columns = TRUE
    )
    return(dummied_df)
}

is_binary <- function(x) {
    return(isTRUE(all.equal(sort(unique(x)), c(0, 1))))
}

topologizer <- function(df) {
    df <- data.frame(df)
    df <- numcol_to_numeric(df)
    df <- dummy_non_numeric(dplyr::select(df, -"subjectkey"))
    summary_df <- data.frame(
        "feature" = as.character(),
        "type" = as.character(),
        "summary" = as.character(),
        "c1_mean" = as.numeric(),
        "c2_mean" = as.numeric(),
        "c3_mean" = as.numeric(),
        "c1_c2_es" = as.numeric(),
        "c1_c2_l" = as.numeric(),
        "c1_c2_u" = as.numeric(),
        "c1_c3_es" = as.numeric(),
        "c1_c3_l" = as.numeric(),
        "c1_c3_u" = as.numeric(),
        "c2_c3_es" = as.numeric(),
        "c2_c3_l" = as.numeric(),
        "c2_c3_u" = as.numeric()
    )
    c1 <- df[df$"cluster" == 1, ]
    c2 <- df[df$"cluster" == 2, ]
    c3 <- df[df$"cluster" == 3, ]
    features <- df |>
        dplyr::select(-"cluster") |>
        colnames()
    ###########################################################################
    # Check if features are binary (unique values are 0 and 1) or not
    ###########################################################################
    for (feature in features) {
        f1 <- c1[, feature]
        f2 <- c2[, feature]
        f3 <- c3[, feature]
        means <- c("1" = mean(f1), "2" = mean(f2), "3" = mean(f3))
        full_summary <- paste(
            names(sort(means, decreasing = TRUE)),
            collapse = " > "
        )
        if (is_binary(df[, feature])) {
            sum_1_v_2 <- calc_propes(f1, f2)
            sum_1_v_3 <- calc_propes(f1, f3)
            sum_2_v_3 <- calc_propes(f2, f3)
            type <- "or"
        } else {
            sum_1_v_2 <- calc_des(f1, f2)
            sum_1_v_3 <- calc_des(f1, f3)
            sum_2_v_3 <- calc_des(f2, f3)
            type <- "d"
        }
        summary_df <- rbind(
            summary_df,
            data.frame(
                "feature" = feature,
                "summary" = full_summary,
                "c1" = signif(mean(f1), 3),
                "c2" = signif(mean(f2), 3),
                "c3" = signif(mean(f3), 3),
                "es" = type,
                "c12_es" = sum_1_v_2$"es",
                "c12_l" = sum_1_v_2$"l",
                "c12_u" = sum_1_v_2$"u",
                "c13_es" = sum_1_v_3$"es",
                "c13_l" = sum_1_v_3$"l",
                "c13_u" = sum_1_v_3$"u",
                "c23_es" = sum_2_v_3$"es",
                "c23_l" = sum_2_v_3$"l",
                "c23_u" = sum_2_v_3$"u"
            )
        )
    }
    return(summary_df)
}
```

# Validation

```{r}
# CHECKPOINT
# The data list that generated the top solution
train_data_list_s3 <- all_dls$"mtbi_train_data_lists"$"imp_3"
train_oom_list_s3 <- all_dls$"mtbi_train_oom_lists"$"imp_3"

# The first test data set, for example
test_data_list_s1 <- all_dls$"mtbi_test_data_lists"$"imp_1"
test_data_list_s2 <- all_dls$"mtbi_test_data_lists"$"imp_2"
test_data_list_s3 <- all_dls$"mtbi_test_data_lists"$"imp_3"
test_data_list_s4 <- all_dls$"mtbi_test_data_lists"$"imp_4"
test_data_list_s5 <- all_dls$"mtbi_test_data_lists"$"imp_5"

test_oom_list_s1 <- all_dls$"mtbi_test_oom_lists"$"imp_1"
test_oom_list_s2 <- all_dls$"mtbi_test_oom_lists"$"imp_2"
test_oom_list_s3 <- all_dls$"mtbi_test_oom_lists"$"imp_3"
test_oom_list_s4 <- all_dls$"mtbi_test_oom_lists"$"imp_4"
test_oom_list_s5 <- all_dls$"mtbi_test_oom_lists"$"imp_5"
```

```{r}
full_data_list_1 <- merge_data_lists(train_data_list_s3, test_data_list_s1)
full_data_list_2 <- merge_data_lists(train_data_list_s3, test_data_list_s2)
full_data_list_3 <- merge_data_lists(train_data_list_s3, test_data_list_s3)
full_data_list_4 <- merge_data_lists(train_data_list_s3, test_data_list_s4)
full_data_list_5 <- merge_data_lists(train_data_list_s3, test_data_list_s5)

full_oom_list_1 <- merge_data_lists(train_oom_list_s3, test_oom_list_s1)
full_oom_list_2 <- merge_data_lists(train_oom_list_s3, test_oom_list_s2)
full_oom_list_3 <- merge_data_lists(train_oom_list_s3, test_oom_list_s3)
full_oom_list_4 <- merge_data_lists(train_oom_list_s3, test_oom_list_s4)
full_oom_list_5 <- merge_data_lists(train_oom_list_s3, test_oom_list_s5)

list.save(full_data_list_1, input_path("mtbi_full_data_list_1.rds", TRUE))
list.save(full_data_list_2, input_path("mtbi_full_data_list_2.rds", TRUE))
list.save(full_data_list_3, input_path("mtbi_full_data_list_3.rds", TRUE))
list.save(full_data_list_4, input_path("mtbi_full_data_list_4.rds", TRUE))
list.save(full_data_list_5, input_path("mtbi_full_data_list_5.rds", TRUE))

list.save(full_oom_list_1, input_path("mtbi_full_oom_list_1.rds", TRUE))
list.save(full_oom_list_2, input_path("mtbi_full_oom_list_2.rds", TRUE))
list.save(full_oom_list_3, input_path("mtbi_full_oom_list_3.rds", TRUE))
list.save(full_oom_list_4, input_path("mtbi_full_oom_list_4.rds", TRUE))
list.save(full_oom_list_5, input_path("mtbi_full_oom_list_5.rds", TRUE))
```

```{r}
# CHECKPOINT
full_data_list_1 <- list.load(input_path("2024_09_13_mtbi_full_data_list_1.rds"))
full_data_list_2 <- list.load(input_path("2024_09_13_mtbi_full_data_list_2.rds"))
full_data_list_3 <- list.load(input_path("2024_09_13_mtbi_full_data_list_3.rds"))
full_data_list_4 <- list.load(input_path("2024_09_13_mtbi_full_data_list_4.rds"))
full_data_list_5 <- list.load(input_path("2024_09_13_mtbi_full_data_list_5.rds"))

full_oom_list_1 <- list.load(input_path("2024_09_13_mtbi_full_oom_list_1.rds"))
full_oom_list_2 <- list.load(input_path("2024_09_13_mtbi_full_oom_list_2.rds"))
full_oom_list_3 <- list.load(input_path("2024_09_13_mtbi_full_oom_list_3.rds"))
full_oom_list_4 <- list.load(input_path("2024_09_13_mtbi_full_oom_list_4.rds"))
full_oom_list_5 <- list.load(input_path("2024_09_13_mtbi_full_oom_list_5.rds"))
```

```{r}
my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

mtbi_settings_matrix <- read_csv(
    proc_path("2024_09_13_mtbi_settings_matrix.csv")
)

mtbi_full_sm <- batch_snf(
    data_list = full_data_list_1,
    settings_matrix = mtbi_settings_matrix,
    distance_metrics_list = my_distance_metrics,
    processes = "max"
)
write_csv(mtbi_full_sm, proc_path("mtbi_full_sm.csv", TRUE))

mtbi_full_sm <- read_csv(proc_path("2024_09_13_mtbi_full_sm.csv"))

mtbi_full_esm <- extend_solutions(
    mtbi_full_sm,
    data_list = full_data_list_1,
    target_list = full_oom_list_1,
    min_pval = 1e-10,
    processes = "max"
)
mtbi_full_esm$"impairment_separation" <- -log10(mtbi_full_esm$"mean_pval")
write_csv(mtbi_full_esm, proc_path("mtbi_full_esm.csv", TRUE))
```

```{r}
mtbi_full_esm <- read_csv(proc_path("2024_09_13_mtbi_full_esm.csv"))
```

```{r}
# In anticipation of the upcoming cluster swaps
cluster_label_swap <- function(solutions_matrix, c_a, c_b) {
    swapped_sm <- dplyr::mutate(
        solutions_matrix,
        across(
            dplyr::starts_with("subject"),
            ~ ifelse(
                . == c_a,
                c_b,
                ifelse(
                    . == c_b,
                    c_a,
                    .
                )
            )
        )
    )
    return(swapped_sm)
}
```



What does the full 3-cluster solution look like?

```{r}
# The full solutions with 3 clusters that have big outcome separation
mtbi_full_3c <- mtbi_full_esm |>
    dplyr::filter(
        nclust == 3,
        impairment_separation > 4
    )

mtbi_full_3c_manhattan <- mc_manhattan_plot(
    mtbi_full_3c,
    data_list = full_data_list_1,
    target_list = full_oom_list_1,
    domain_colours = c(
        "AS" = "#85929e",
        "D" = "#bb8fce",
        "N" = "#e59866",
        "MH" = "#7fb3d5",
        "P" = "#52be80",
        "S" = "#d98880",
        "B" = "#ff3131"
    )
)

mtbi_full_3c_manhattan

ggsave(
    plot = mtbi_full_3c_manhattan,
    filename = fig_path("mtbi_full_3c_manhattan.png", TRUE),
    width = 18,
    height = 14,
    dpi = 120
)

# The second one is very similar to the derivation set version
mtbi_full_top_3c <- mtbi_full_3c[2, ]
mtbi_full_top_3c <- cluster_label_swap(mtbi_full_top_3c, 1, 3)
mtbi_full_top_3c$"label" <- "Full Top 3C Solution"

write_csv(mtbi_full_top_3c, proc_path("mtbi_full_top_3c.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_full_top_3c <- read_csv(proc_path("2024_09_13_mtbi_full_top_3c.csv"))
```

```{r}
mtbi_derivation_plot_list <- auto_plot(
    solutions_matrix_row = mtbi_mc_d_esm,
    data_list = all_dls$"mtbi_train_data_lists"$"imp_2",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_2"
)

mtbi_full_plot_list <- auto_plot(
    mtbi_full_top_3c,
    data_list = full_data_list_1,
    target_list = full_oom_list_1
)

val_cluster_df <- mtbi_full_top_3c |>
    get_cluster_df() |>
    dplyr::filter(
        subjectkey %in% paste0("subject_", mtbi_test_subjects$"subjectkey")
    )

mtbi_val_plot_list <- auto_plot(
    cluster_df = val_cluster_df,
    data_list = test_data_list_s1,
    target_list = test_oom_list_s1
)

mtbi_val_plot_list$"mtbi_mechanism"[[1]]$"keycol" <- factor(
    mtbi_val_plot_list$"mtbi_mechanism"[[1]]$"keycol",
    levels = c("fall_hit", "hosp_er", "multi", "other_loc", "vehicle", "violent")
)

bar_colors <- scales::hue_pal()(6)
names(bar_colors) <- c("fall_hit", "hosp_er", "multi", "other_loc", "vehicle", "violent")

mtbi_val_plot_list$"mtbi_mechanism" <- mtbi_val_plot_list$"mtbi_mechanism" +
    scale_fill_manual(values = bar_colors, drop = FALSE)

```

How are all the test features distributed?
How are all the features distributed?

I'd like to have a table along the lines of,

| DERIVATION | IN DERIVATION + VALIDATION | IN VALIDATION |
C1 max F | True | Almost  true|

Something like that, which will require a side-by-side comparison of these features through visual inspection and through the topologizer function in the supplementary section for those who wish to look at the crunched numbers.

Up to 3 should be sufficient for determining which attributes should play a key role in validating the subsequent investigations.

```{r}
outcome_idx <- !names(mtbi_full_plot_list) %in% sorted_features
outcome_features <- names(mtbi_full_plot_list)[outcome_idx]

# Full input feature plots
pli_sort_d <- mtbi_derivation_plot_list[sorted_features]
pli_sort_v <- mtbi_val_plot_list[sorted_features]
pli_sort_f <- mtbi_full_plot_list[sorted_features]
plo_d <- mtbi_derivation_plot_list[outcome_features]
plo_v <- mtbi_val_plot_list[outcome_features]
plo_f <- mtbi_full_plot_list[outcome_features]

# Let's manually assemble these puppies!
input_plots <- list(pli_sort_d, pli_sort_v, pli_sort_f)
outcome_plots <- list(plo_d, plo_v, plo_f)

list.save(input_plots, proc_path("input_tri_plots.rds", TRUE))
list.save(outcome_plots, proc_path("outcome_tri_plots.rds", TRUE))
```

```{r}
# CHECKPOINT
input_plots <- list.load(proc_path("2024_09_16_input_tri_plots.rds"))
outcome_plots <- list.load(proc_path("2024_09_13_outcome_tri_plots.rds"))
```

```{r}
# qs image export helper function# {{{
qs <- function(plot, path, w = 12, h = 4) {
    path <- paste0("mtbi_dvf_", path, ".png")
    ggsave(fig_path(path, TRUE), plot, width = w, height = h)
}
# }}}

# tri-plot helper function# {{{
tri_plot <- function(pl,
                     feature,
                     ft_name,
                     scale_fill_labels = NULL,
                     ylims = NULL) {
    ###########################################################################
    p1 <- pl[[1]][[feature]] +
        theme(
            legend.position = "none",
            axis.title.y = element_text(size = 16)
        )
    ###########################################################################
    p2 <- pl[[2]][[feature]] +
        theme(
            legend.position = "none",
            axis.title.y = element_blank()
        ) 
    ###########################################################################
    p3 <- pl[[3]][[feature]] +
        theme(
            axis.title.y = element_blank()
        )
    ###########################################################################
    if (class(pl[[3]][[feature]]$layers[[1]]$geom)[[1]] == "GeomBar") {
        p3 <- p3 + labs(fill = ft_name)
    } else {
        p1 <- p1 + labs(y = ft_name)
    }
    if (!is.null(scale_fill_labels)) {
        p3 <- p3 + scale_fill_discrete(labels = scale_fill_labels)
    }
    if (!is.null(ylims)) {
        p1 <- p1 + ylim(ylims[[1]], ylims[[2]])
        p2 <- p2 + ylim(ylims[[1]], ylims[[2]])
        p3 <- p3 + ylim(ylims[[1]], ylims[[2]])
    }
    ###########################################################################
    patch_plot <- list(p1, p2, p3)
    patch_plot <- lapply(
        patch_plot,
        function(x) {
            x <- x + labs(x = "Cluster") + theme(text = element_text(size = 16))
        }
    )
    names(patch_plot) <- c("derivation", "validation", "full")
    return(wrap_plots(patch_plot))
}
# }}}
```

```{r}
# Input tri-plots# {{{
# Brain volumes
brain_volume_plot <- tri_plot(input_plots, "brain_volume", expression("Brain Volume "(mm^3)), ylims = c(900000, 1650000))
brain_volume_plot
qs(brain_volume_plot, "brain_volume")

# Sex
sex_plot <- tri_plot(input_plots, "sex", "Sex", c("F", "M"))
sex_plot
qs(sex_plot, "sex")

# cort sa
cort_sa_plot <- tri_plot(input_plots, "cortical_sa", expression("Cortical Surface Area "(mm^2)), ylims = c(140000, 260000))
cort_sa_plot
qs(cort_sa_plot, "cort_sa")

# Income
household_income_plot <- tri_plot(input_plots, "household_income", "Household Income")
household_income_plot
qs(household_income_plot, "household_income")

# Pubertal Status - Parent Report
pubertal_status_p_plot <- tri_plot(input_plots, "pubertal_status_p", "Pubertal Status\n(Parent Report)")
pubertal_status_p_plot
qs(pubertal_status_p_plot, "pubertal_status_p")

# Programs this year
programs_this_year_plot <- tri_plot(input_plots, "programs_this_year", "Programs This Year")
programs_this_year_plot
qs(programs_this_year_plot, "programs_this_year")

# Non school programs
non_school_programs_plot <- tri_plot(input_plots, "non_school_programs", "Non-School Programs This Year", ylims= c(-0.5, 12))
non_school_programs_plot
qs(non_school_programs_plot, "non_school_programs")

# parent_thought
parent_thought_plot <- tri_plot(input_plots, "parent_thought", "Parent Thought", ylims = c(-0.5, 13.5))
parent_thought_plot
qs(parent_thought_plot, "parent_thought")

# Parent Somatic
parent_somatic_plot <- tri_plot(input_plots, "parent_somatic", "Parent Somatic", ylims = c(-0.5, 25))
parent_somatic_plot
qs(parent_somatic_plot, "parent_somatic")

# Weekday screentime
weekday_screentime_plot <- tri_plot(input_plots, "weekday_screentime", "Weekday Screentime (hours)", ylims = c(-0.5, 21))
weekday_screentime_plot
qs(weekday_screentime_plot, "weekday_screentime")

# parent_antisocial
parent_antisocial_plot <- tri_plot(input_plots, "parent_antisocial", "Parent Antisocial", ylims = c(-0.5, 20))
parent_antisocial_plot
qs(parent_antisocial_plot, "parent_antisocial")

# parent_aggressive
parent_aggressive_plot <- tri_plot(input_plots, "parent_aggressive", "Parent Aggressive", ylims = c(-0.5, 25))
parent_aggressive_plot
qs(parent_aggressive_plot, "parent_aggressive")

# Parent depress
parent_depress_plot <- tri_plot(input_plots, "parent_depress", "Parent Depress", ylims = c(-0.5, 25))
parent_depress_plot
qs(parent_depress_plot, "parent_depress")

# parent_anxdep
parent_anxdep_plot <- tri_plot(input_plots, "parent_anxdep", "Parent Anxious-Depressed", ylims = c(-0.5, 30))
parent_anxdep_plot
qs(parent_anxdep_plot, "parent_anxdep")

# Race
race_plot <- tri_plot(input_plots, "race", "Race", scale_fill_labels = c("Black", "Hispanic", "Other", "White"))
race_plot
qs(race_plot, "race")

# parent_anxdisord
parent_anxdisord_plot <- tri_plot(input_plots, "parent_anxdisord", "Parent Anxious", ylims = c(-0.5, 13))
parent_anxdisord_plot
qs(parent_anxdisord_plot, "parent_anxdisord")

# private_instruction
private_instruction_plot <- tri_plot(input_plots, "private_instruction", "Private Activities", ylims = c(-0.5, 9.5))
private_instruction_plot
qs(private_instruction_plot, "private_instruction")

# weekend_screentime
weekend_screentime_plot <- tri_plot(input_plots, "weekend_screentime", "Weekend Screentime (hours)", ylims = c(-0.5, 21))
weekend_screentime_plot
qs(weekend_screentime_plot, "weekend_screentime")

# parent_withdrawn
parent_withdrawn_plot <- tri_plot(input_plots, "parent_withdrawn", "Parent Withdrawn", ylims = c(-0.5, 17))
parent_withdrawn_plot
qs(parent_withdrawn_plot, "parent_withdrawn")

# parent_avoidant
parent_avoidant_plot <- tri_plot(input_plots, "parent_avoidant", "Parent Avoidant", ylims = c(-0.5, 13))
parent_avoidant_plot
qs(parent_avoidant_plot, "parent_avoidant")

# parent_hyperactive
parent_hyperactive_plot <- tri_plot(input_plots, "parent_hyperactive", "Parent Hyperactive", ylims = c(-0.5, 12))
parent_hyperactive_plot
qs(parent_hyperactive_plot, "parent_hyperactive")

# fmri_cort_cors
fmri_cort_cors_plot <- tri_plot(input_plots, "fmri_cort_cors", "fMRI Cort-Cort Corrs", ylims = c(-0.1, 0.16))
fmri_cort_cors_plot
qs(fmri_cort_cors_plot, "fmri_cort_cors")

# fmri_cort_subcort_cors
fmri_cort_subcort_cors_plot <- tri_plot(input_plots, "fmri_cort_subcort_cors", "fMRI Cort-Subcort Corrs", ylims = c(-0.15, 0.2))
fmri_cort_subcort_cors_plot
qs(fmri_cort_subcort_cors_plot, "fmri_cort_subcort_cors")

# Parent attention
parent_attention_plot <- tri_plot(input_plots, "parent_attention", "Parent Attention", ylims = c(-0.5, 25))
parent_attention_plot
qs(parent_attention_plot, "parent_attention")

# parent_perstr
parent_perstr_plot <- tri_plot(input_plots, "parent_perstr", "Parent Personal Strength")
parent_perstr_plot
qs(parent_perstr_plot, "parent_perstr")

# parent_intrusive
parent_intrusive_plot <- tri_plot(input_plots, "parent_intrusive", "Parent Intrusive", ylims = c(-0.5, 12))
parent_intrusive_plot
qs(parent_intrusive_plot, "parent_intrusive")

# family_fight_p
family_fight_p_plot <- tri_plot(input_plots, "family_fight_p", "Family Fights\n(Parent Report)", scale_fill_labels = c("No", "Yes"))
family_fight_p_plot
qs(family_fight_p_plot, "family_fight_p")

# major_wm_ndi
major_wm_ndi_plot <- tri_plot(input_plots, "major_wm_ndi", "Major WM Neurite Density", ylims = c(0.45, 0.85))
major_wm_ndi_plot
qs(major_wm_ndi_plot, "major_wm_ndi")

# headache_history
headache_history_plot <- tri_plot(input_plots, "headache_history", "Headache\nHistory", c("No", "Yes"))
headache_history_plot
qs(headache_history_plot, "headache_history")

# exercise_time
exercise_time_plot <- tri_plot(input_plots, "exercise_time", "Exercise Score", ylims = c(0, 1.1))
exercise_time_plot
qs(exercise_time_plot, "exercise_time")

# considerate_y
considerate_y_plot <- tri_plot(input_plots, "considerate_y", "Considerate\n(Youth Report)", c("No", "Yes"))
considerate_y_plot
qs(considerate_y_plot, "considerate_y")

# family_temper_p
family_temper_p_plot <- tri_plot(input_plots, "family_temper_p", "Family Temper\n(Parent Report)", scale_fill_labels = c("No", "Yes"))
family_temper_p_plot
qs(family_temper_p_plot, "family_temper_p")

# family_outdo_p
family_outdo_p_plot <- tri_plot(input_plots, "family_outdo_p", "Family Outdo\n(Parent Report)", c("No", "Yes"))
family_outdo_p_plot
qs(family_outdo_p_plot, "family_outdo_p")

# cortical_thickness
cortical_thickness_plot <- tri_plot(input_plots, "cortical_thickness", "Cortical Thickness (mm)", ylims = c(2.3, 3.1))
cortical_thickness_plot
qs(cortical_thickness_plot, "cortical_thickness")

# helps_hurt_p
helps_hurt_p_plot <- tri_plot(input_plots, "helps_hurt_p", "Helps Hurt\n(Parent Report)", c("No", "Yes"))
helps_hurt_p_plot
qs(helps_hurt_p_plot, "helps_hurt_p")

# same_sex_close_friend
same_sex_close_friend_plot <- tri_plot(input_plots, "same_sex_close_friend", "Same-Sex Close Friends (Quartile)")
same_sex_close_friend_plot
qs(same_sex_close_friend_plot, "same_sex_close_friend")

# family_peaceful_p
family_peaceful_p_plot <- tri_plot(input_plots, "family_peaceful_p", "Family Peaceful\n(Parent Report)", c("No", "Yes"))
family_peaceful_p_plot
qs(family_peaceful_p_plot, "family_peaceful_p")

# family_outdo_y
family_outdo_y_plot <- tri_plot(input_plots, "family_outdo_y", "Family Outdoing\n(Youth Report)", c("No", "Yes"))
family_outdo_y_plot
qs(family_outdo_y_plot, "family_outdo_y")

# mtbi_loc
mtbi_loc_plot <- tri_plot(input_plots, "mtbi_loc", "mTBI LOC", c("No", "Yes"))
mtbi_loc_plot
qs(mtbi_loc_plot, "mtbi_loc")

# family_criticize_p
family_criticize_p_plot <- tri_plot(input_plots, "family_criticize_p", "Family Criticizes\n(Parent Report)", c("No", "Yes"))
family_criticize_p_plot
qs(family_criticize_p_plot, "family_criticize_p")

# school_programs
school_programs_plot <- tri_plot(input_plots, "school_programs", "School Programs", ylims = c(-0.5, 18))
school_programs_plot
qs(school_programs_plot, "school_programs")

# family_hit_p
family_hit_p_plot <- tri_plot(input_plots, "family_hit_p", "Family Hitting\n(Parent Report)", c("No", "Yes"))
family_hit_p_plot
qs(family_hit_p_plot, "family_hit_p")

# family_angry_p
family_angry_p_plot <- tri_plot(input_plots, "family_angry_p", "Family Angry\n(Parent Report)", c("No", "Yes"))
family_angry_p_plot
qs(family_angry_p_plot, "family_angry_p")

# helpful_y
helpful_y_plot <- tri_plot(input_plots, "helpful_y", "Helpful\n(Youth Report)", c("No", "Yes"))
helpful_y_plot
qs(helpful_y_plot, "helpful_y")

# helpful_p
helpful_p_plot <- tri_plot(input_plots, "helpful_p", "Helpful\n(Parent Report)", c("No", "Yes"))
helpful_p_plot
qs(helpful_p_plot, "helpful_p")

# family_angry_y
family_angry_y_plot <- tri_plot(input_plots, "family_angry_y", "Family Angry\n(Youth Report)", c("No", "Yes"))
family_angry_y_plot
qs(family_angry_y_plot, "family_angry_y")

# pericortical_wm_ndi
pericortical_wm_ndi_plot <- tri_plot(input_plots, "pericortical_wm_ndi", "Pericortical WM Neurite Density", ylims = c(0.25, 0.6))
pericortical_wm_ndi_plot
qs(pericortical_wm_ndi_plot, "pericortical_wm_ndi")

# family_yell_y
family_yell_y_plot <- tri_plot(input_plots, "family_yell_y", "Family Yells\n(Youth Report)", c("No", "Yes"))
family_yell_y_plot
qs(family_yell_y_plot, "family_yell_y")

# pubertal_status_y
pubertal_status_y_plot <- tri_plot(input_plots, "pubertal_status_y", "Pubertal Status (Youth Report)")
pubertal_status_y_plot
qs(pubertal_status_y_plot, "pubertal_status_y")

# helps_hurt_y
helps_hurt_y_plot <- tri_plot(input_plots, "helps_hurt_y", "Helps Hurt\n(Youth Report)", c("No", "Yes"))
helps_hurt_y_plot
qs(helps_hurt_y_plot, "helps_hurt_y")

# age
age_plot <- tri_plot(input_plots, "age", "age")
age_plot
qs(age_plot, "age")

# family_criticize_y
family_criticize_y_plot <- tri_plot(input_plots, "family_criticize_y", "Family Criticizes\n(Youth Report)", c("No", "Yes"))
family_criticize_y_plot
qs(family_criticize_y_plot, "family_criticize_y")

# family_throw_p
family_throw_p_plot <- tri_plot(input_plots, "family_throw_p", "Family Throwing\n(Parent Report)", c("No", "Yes"))
family_throw_p_plot
qs(family_throw_p_plot, "family_throw_p")

# mtbi_mem_daze
mtbi_mem_daze_plot <- tri_plot(input_plots, "mtbi_mem_daze", "mTBI mem_daze", c("No", "Yes"))
mtbi_mem_daze_plot
qs(mtbi_mem_daze_plot, "mtbi_mem_daze")

# same_sex_friend
same_sex_friend_plot <- tri_plot(input_plots, "same_sex_friend", "Same-Sex Friends\n(Quartile)")
same_sex_friend_plot
qs(same_sex_friend_plot, "same_sex_friend")

# mtbi_age
mtbi_age_plot <- tri_plot(input_plots, "mtbi_age", "mTBI Age (months)")
mtbi_age_plot
qs(mtbi_age_plot, "mtbi_age")

# previous_mtbis
previous_mtbis_plot <- tri_plot(input_plots, "previous_mtbis", "Previous mTBIs")
previous_mtbis_plot
qs(previous_mtbis_plot, "previous_mtbis")

# considerate_p
considerate_p_plot <- tri_plot(input_plots, "considerate_p", "Considerate\n(Parent Report)", c("No", "Yes"))
considerate_p_plot
qs(considerate_p_plot, "considerate_p")

# family_peaceful_y
family_peaceful_y_plot <- tri_plot(input_plots, "family_peaceful_y", "Family Peaceful\n(Youth Report)", c("No", "Yes"))
family_peaceful_y_plot
qs(family_peaceful_y_plot, "family_peaceful_y")

# mtbi_mechanism
mtbi_mechanism_plot <- tri_plot(
    input_plots,
    "mtbi_mechanism",
    "mTBI Mechanism",
    c("Fall/Hit", "Hospital/ER", "Multiple Injuries", "Other", "Vehicle", "Violent")
)
mtbi_mechanism_plot
qs(mtbi_mechanism_plot, "mtbi_mechanism")

# family_fight_y
family_fight_y_plot <- tri_plot(input_plots, "family_fight_y", "Family Fights\n(Youth Report)", c("No", "Yes"))
family_fight_y_plot
qs(family_fight_y_plot, "family_fight_y")

# family_hit_y
family_hit_y_plot <- tri_plot(input_plots, "family_hit_y", "Family Hitting\n(Youth Report)", c("No", "Yes"))
family_hit_y_plot
qs(family_hit_y_plot, "family_hit_y")

# family_throw_y
family_throw_y_plot <- tri_plot(input_plots, "family_throw_y", "Family Throwing\n(Youth Report)", c("No", "Yes"))
family_throw_y_plot
qs(family_throw_y_plot, "family_throw_y")

# family_temper_y
family_temper_y_plot <- tri_plot(input_plots, "family_temper_y", "Family Temper\n(Youth Report)", c("No", "Yes"))
family_temper_y_plot
qs(family_temper_y_plot, "family_temper_y")

# opp_sex_close_friend
opp_sex_close_friend_plot <- tri_plot(input_plots, "opp_sex_close_friend", "Opposite-Sex Close Friends\n(Quartile)")
opp_sex_close_friend_plot
qs(opp_sex_close_friend_plot, "opp_sex_close_friend")

# opp_sex_friend
opp_sex_friend_plot <- tri_plot(input_plots, "opp_sex_friend", "Opposite-Sex Friends (Quartile)")
opp_sex_friend_plot
qs(opp_sex_friend_plot, "opp_sex_friend")

# family_yell_p
family_yell_p_plot <- tri_plot(input_plots, "family_yell_p", "Family Yells\n(Parent Report)", c("No", "Yes"))
family_yell_p_plot
qs(family_yell_p_plot, "family_yell_p")
# }}}

# Outcome trip-plots# {{{
cbcl_anxdep_plot <- tri_plot(outcome_plots, "cbcl_anxdep", "Anxious-Depressed", ylims = c(-0.5, 30))
cbcl_withdep_plot <- tri_plot(outcome_plots, "cbcl_withdep", "Withdrawn-Depressed", ylims = c(-0.5, 15))
cbcl_somatic_plot <- tri_plot(outcome_plots, "cbcl_somatic", "Somatic Problems", ylims = c(-0.5, 17))
cbcl_social_plot <- tri_plot(outcome_plots, "cbcl_social", "Social Problems", ylims = c(-0.5, 20))
cbcl_thought_plot <- tri_plot(outcome_plots, "cbcl_thought", "Thought Problems", ylims = c(-0.5, 20))
cbcl_attention_plot <- tri_plot(outcome_plots, "cbcl_attention", "Attention Problems", ylims = c(-0.5, 22))
cbcl_rulebreak_plot <- tri_plot(outcome_plots, "cbcl_rulebreak", "Rule-Breaking Problems", ylims = c(-0.5, 22))
cbcl_aggressive_plot <- tri_plot(outcome_plots, "cbcl_aggressive", "Aggression Problems", ylims = c(-0.5, 32))
sds_sleep_plot <- tri_plot(outcome_plots, "sds_sleep", "Total Sleep Problems", ylims = c(20, 100))
# }}}
```

```{r}
generalizing_plots <- list(
    "brain_volume" = brain_volume_plot,
    "sex" = sex_plot,
    "cort_sa" = cort_sa_plot,
    "household_income" = household_income_plot,
    "pubertal_status_p" = pubertal_status_p_plot,
    "programs_this_year" = programs_this_year_plot,
    "non_school_programs" = non_school_programs_plot,
    "parent_thought" = parent_thought_plot,
    "parent_somatic" = parent_somatic_plot,
    "weekday_screentime" = weekday_screentime_plot,
    "parent_antisocial" = parent_antisocial_plot,
    "parent_aggressive" = parent_aggressive_plot,
    "parent_depress" = parent_depress_plot,
    "parent_anxdep" = parent_anxdep_plot,
    "race" = race_plot,
    "parent_anxdisord" = parent_anxdisord_plot,
    "private_instruction" = private_instruction_plot,
    "weekend_screentime" = weekend_screentime_plot,
    "parent_withdrawn" = parent_withdrawn_plot,
    "parent_avoidant" = parent_avoidant_plot,
    "parent_hyperactive" = parent_hyperactive_plot,
    "fmri_cort_cors" = fmri_cort_cors_plot,
    "fmri_cort_subcort_cors" = fmri_cort_subcort_cors_plot,
    "parent_attention" = parent_attention_plot,
    "parent_perstr" = parent_perstr_plot,
    "parent_intrusive" = parent_intrusive_plot,
    "family_fight_p" = family_fight_p_plot,
    "major_wm_ndi" = major_wm_ndi_plot,
    "headache_history" = headache_history_plot,
    "exercise_time" = exercise_time_plot,
    "considerate_y" = considerate_y_plot,
    "family_temper_p" = family_temper_p_plot,
    "family_outdo_p" = family_outdo_p_plot,
    "cortical_thickness" = cortical_thickness_plot,
    "helps_hurt_p" = helps_hurt_p_plot,
    "same_sex_close_friend" = same_sex_close_friend_plot,
    "family_peaceful_p" = family_peaceful_p_plot,
    "family_outdo_y" = family_outdo_y_plot,
    "mtbi_loc" = mtbi_loc_plot,
    "family_criticize_p" = family_criticize_p_plot,
    "school_programs" = school_programs_plot,
    "family_hit_p" = family_hit_p_plot,
    "family_angry_p" = family_angry_p_plot,
    "helpful_y" = helpful_y_plot,
    "helpful_p" = helpful_p_plot,
    "family_angry_y" = family_angry_y_plot,
    "pericortical_wm_ndi" = pericortical_wm_ndi_plot,
    "family_yell_y" = family_yell_y_plot,
    "pubertal_status_y" = pubertal_status_y_plot,
    "helps_hurt_y" = helps_hurt_y_plot,
    "age" = age_plot,
    "family_criticize_y" = family_criticize_y_plot,
    "family_throw_p" = family_throw_p_plot,
    "mtbi_mem_daze" = mtbi_mem_daze_plot,
    "same_sex_friend" = same_sex_friend_plot,
    "mtbi_age" = mtbi_age_plot,
    "previous_mtbis" = previous_mtbis_plot,
    "considerate_p" = considerate_p_plot,
    "family_peaceful_y" = family_peaceful_y_plot,
    "mtbi_mechanism" = mtbi_mechanism_plot,
    "family_fight_y" = family_fight_y_plot,
    "family_hit_y" = family_hit_y_plot,
    "family_throw_y" = family_throw_y_plot,
    "family_temper_y" = family_temper_y_plot,
    "opp_sex_close_friend" = opp_sex_close_friend_plot,
    "opp_sex_friend" = opp_sex_friend_plot,
    "family_yell_p" = family_yell_p_plot
)

generalizing_outcome_plots <- list(
    "cbcl_anxdep" = cbcl_anxdep_plot,
    "cbcl_withdep" = cbcl_withdep_plot,
    "cbcl_somatic" = cbcl_somatic_plot,
    "cbcl_social" = cbcl_social_plot,
    "cbcl_thought" = cbcl_thought_plot,
    "cbcl_attention" = cbcl_attention_plot,
    "cbcl_rulebreak" = cbcl_rulebreak_plot,
    "cbcl_aggressive" = cbcl_aggressive_plot,
    "sds_sleep" = sds_sleep_plot
)

generalizing_plots <- lapply(
    generalizing_plots,
    function(x) {
        x[[1]] <- x[[1]] + theme(axis.title.x = element_blank()) 
        x[[2]] <- x[[2]] + theme(axis.title.x = element_blank()) 
        x[[3]] <- x[[3]] + theme(axis.title.x = element_blank()) 
        return(x)
    }
)

generalizing_outcome_plots <- lapply(
    generalizing_outcome_plots,
    function(x) {
        x[[1]] <- x[[1]] + theme(axis.title.x = element_blank()) 
        x[[2]] <- x[[2]] + theme(axis.title.x = element_blank()) 
        x[[3]] <- x[[3]] + theme(axis.title.x = element_blank()) 
        return(x)
    }
)

```

```{r}
wp_1 <- wrap_plots(generalizing_plots[1:10], ncol = 1)
qs(wp_1, "wp_1", w = 10, h = 30)

wp_2 <- wrap_plots(generalizing_plots[11:20], ncol = 1)
qs(wp_2, "wp_2", w = 10, h = 30)

wp_3 <- wrap_plots(generalizing_plots[21:30], ncol = 1)
qs(wp_3, "wp_3", w = 10, h = 30)

wp_4 <- wrap_plots(generalizing_plots[31:40], ncol = 1)
qs(wp_4, "wp_4", w = 10, h = 30)

wp_5 <- wrap_plots(generalizing_plots[41:50], ncol = 1)
qs(wp_5, "wp_5", w = 10, h = 30)

wp_6 <- wrap_plots(generalizing_plots[51:60], ncol = 1)
qs(wp_6, "wp_6", w = 10, h = 30)

wp_7 <- wrap_plots(generalizing_plots[61:67], ncol = 1)
qs(wp_7, "wp_7", w = 10, h = 21)
```

```{r}
wpo <- wrap_plots(generalizing_outcome_plots, ncol = 1)

qs(wpo, "wpo", w = 7, h = 22)
```

# Summary of the validation (table)

# Topologies go here, save actually for later.

```{r}
mtbi_derivation_df <- auto_plot(
    solutions_matrix_row = mtbi_mc_d_esm,
    data_list = all_dls$"mtbi_train_data_lists"$"imp_2",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_2",
    return_plots = FALSE
)

mtbi_full_df <- auto_plot(
    mtbi_full_top_3c,
    data_list = full_data_list_1,
    target_list = full_oom_list_1,
    return_plots = FALSE
)

mtbi_val_df <- auto_plot(
    cluster_df = val_cluster_df,
    data_list = test_data_list_s1,
    target_list = test_oom_list_s1,
    return_plots = FALSE
) 

write_csv(mtbi_derivation_df, proc_path("mtbi_derivation_df.csv", TRUE))
write_csv(mtbi_full_df, proc_path("mtbi_full_df.csv", TRUE))
write_csv(mtbi_val_df, proc_path("mtbi_val_df.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_derivation_df <- read_csv(proc_path("2024_09_18_mtbi_derivation_df.csv"))
mtbi_full_df <- read_csv(proc_path("2024_09_18_mtbi_full_df.csv"))
mtbi_val_df <- read_csv(proc_path("2024_09_18_mtbi_val_df.csv"))
```

```{r}
mtbi_derivation_tops <- topologizer(mtbi_derivation_df)
mtbi_full_tops <- topologizer(mtbi_full_df)
mtbi_val_tops <- topologizer(mtbi_val_df)

write_csv(mtbi_derivation_tops, proc_path("mtbi_derivation_tops.csv", TRUE))
write_csv(mtbi_full_tops, proc_path("mtbi_full_tops.csv", TRUE))
write_csv(mtbi_val_tops, proc_path("mtbi_val_tops.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_derivation_tops <- read_csv(proc_path("2024_09_19_mtbi_derivation_tops.csv"))
mtbi_full_tops <- read_csv(proc_path("2024_09_19_mtbi_full_tops.csv"))
mtbi_val_tops <- read_csv(proc_path("2024_09_19_mtbi_val_tops.csv"))
```

```{r}
# FUNCTION: Calculate if an ES is significant# {{{
significant_es <- function(type, l, u) {
    thresh <- as.numeric(type %in% c("or", "OR"))
    return(as.numeric(thresh < l | thresh > u))
}
# }}}

# FUNCTION: Format topologies# {{{
format_tops <- function(tops) {
    tops <- data.frame(tops) |> mutate(
        c12_sig = significant_es(es, c12_l, c12_u),
        c13_sig = significant_es(es, c13_l, c13_u),
        c23_sig = significant_es(es, c23_l, c23_u)
    )
    # Strips whitespace by converting number columns to numeric format
    tops <- numcol_to_numeric(tops)
    tops <- tops |> mutate(
        "C1 vs. C2" = paste0(c12_es, " [", c12_l, ", ", c12_u, "]"),
        "C1 vs. C3" = paste0(c13_es, " [", c13_l, ", ", c13_u, "]"),
        "C2 vs. C3" = paste0(c23_es, " [", c23_l, ", ", c23_u, "]"),
        .keep = "unused"
    )
    tops <- tops |> mutate(
        "C1 vs. C2" = ifelse(c12_sig == 1, paste0("textbf{", `C1 vs. C2`, "}"), `C1 vs. C2`),
        "C1 vs. C3" = ifelse(c13_sig == 1, paste0("textbf{", `C1 vs. C3`, "}"), `C1 vs. C3`),
        "C2 vs. C3" = ifelse(c23_sig == 1, paste0("textbf{", `C2 vs. C3`, "}"), `C2 vs. C3`),
        .keep = "unused"
    )
    # Remove scientific notation and trailing zeros
    tops <- format(data.frame(tops), scientific = FALSE, drop0trailing = TRUE)
    colnames(tops) <- c("Feature", "Summary", "C1", "C2", "C3", "ES", "C1 vs. C2", "C1 vs. C3", "C2 vs. C3")
    return(tops)
}
# }}}
```

```{r}
# Prepping the ordering of the tops features
mtbi_mc_d_nmi_v_pval_rank <- read_csv(
    proc_path("2024_09_13_mtbi_mc_d_nmi_v_pval_rank.csv")
)

joint_ranks <- mtbi_mc_d_nmi_v_pval_rank |>
    data.frame() |>
    dplyr::select(feature, joint_rank)
joint_ranks <- rbind(
    joint_ranks,
    data.frame(
        feature = c(
            "race_black",
            "race_white",
            "race_hispanic",
            "race_other"
        ),
        joint_rank = joint_ranks[joint_ranks$"feature" == "race", "joint_rank"]
    )
)
joint_ranks <- rbind(
    joint_ranks,
    data.frame(
        feature = c(
            "mtbi_mechanism_fall_hit",
            "mtbi_mechanism_hosp_er",
            "mtbi_mechanism_multi",
            "mtbi_mechanism_other_loc",
            "mtbi_mechanism_vehicle",
            "mtbi_mechanism_violent"
        ),
        joint_rank = joint_ranks[joint_ranks$"feature" == "mtbi_mechanism", "joint_rank"]
    )
)
joint_ranks <- dplyr::filter(joint_ranks, !feature %in% c("mtbi_mechanism", "race"))

joint_ranks <- arrange(joint_ranks, joint_rank)

write_csv(joint_ranks, proc_path("joint_ranks.csv", TRUE))
```

```{r}
# CHECKPOINT
joint_ranks <- read_csv(proc_path("2024_09_19_joint_ranks.csv"))
```


```{r}
outcomes <- summarize_dl(test_oom_list_s1, scope = "feature")$"name"

joint_ranks_with_out <- rbind(
    data.frame(
        feature = outcomes,
        joint_rank = nrow(joint_ranks) + 1
    ),
    joint_ranks
) |> data.frame()

f_derivation_tops <- data.frame(format_tops(mtbi_derivation_tops))
f_val_tops <- data.frame(format_tops(mtbi_val_tops))
f_full_tops <- data.frame(format_tops(mtbi_full_tops))

all_der_tops <- dplyr::full_join(
    joint_ranks_with_out,
    f_derivation_tops,
    by = join_by("feature" == "Feature")
) |>
    dplyr::select(-joint_rank) |>
    dplyr::rename("Feature" = "feature")

all_val_tops <- dplyr::full_join(
    joint_ranks_with_out,
    f_val_tops,
    by = join_by("feature" == "Feature")
) |>
    dplyr::select(-joint_rank) |>
    dplyr::rename("Feature" = "feature")

all_full_tops <- dplyr::full_join(
    joint_ranks_with_out,
    f_full_tops,
    by = join_by("feature" == "Feature")
) |>
    dplyr::select(-joint_rank) |>
    dplyr::rename("Feature" = "feature")

write_csv(all_der_tops, proc_path("mtbi_all_der_tops.csv", TRUE))
write_csv(all_val_tops, proc_path("mtbi_all_val_tops.csv", TRUE))
write_csv(all_full_tops, proc_path("mtbi_all_full_tops.csv", TRUE))
```

```{r}
# CHECKPOINT
all_der_tops <- read_csv(proc_path("2024_09_19_mtbi_all_der_tops.csv"))
all_val_tops <- read_csv(proc_path("2024_09_19_mtbi_all_val_tops.csv"))
all_full_tops <- read_csv(proc_path("2024_09_19_mtbi_all_full_tops.csv"))
```

```{r}
all_der_tops$"Set" <- "D"
all_val_tops$"Set" <- "V"
all_full_tops$"Set" <- "F"

all_der_tops$rank <- seq_len(nrow(all_der_tops))
all_val_tops$rank <- seq_len(nrow(all_val_tops))
all_full_tops$rank <- seq_len(nrow(all_full_tops))

all_tops <- do.call(rbind, list(all_der_tops, all_val_tops, all_full_tops))

all_tops <- arrange(all_tops, rank) |>
    relocate(Set, .after = "Feature") |>
    dplyr::select(-rank)

write_csv(all_tops, proc_path("all_tops.csv", TRUE))

all_tops <- read_csv(proc_path("2024_09_19_all_tops.csv"))

xtable(all_tops)
```

```{r}
mtbi_derivation_tops$"set" <- "D"
mtbi_full_tops$"set" <- "V"
mtbi_val_tops$"set" <- "F"


all_der_tops_raw <- dplyr::full_join(
    joint_ranks_with_out,
    mtbi_derivation_tops,
    by = "feature"
) |>
    dplyr::select(-joint_rank)

all_val_tops_raw <- dplyr::full_join(
    joint_ranks_with_out,
    mtbi_val_tops,
    by = "feature"
) |>
    dplyr::select(-joint_rank)

all_full_tops_raw <- dplyr::full_join(
    joint_ranks_with_out,
    mtbi_full_tops,
    by = "feature"
) |>
    dplyr::select(-joint_rank)

all_der_tops_raw$rank <- seq_len(nrow(all_der_tops_raw))
all_val_tops_raw$rank <- seq_len(nrow(all_val_tops_raw))
all_full_tops_raw$rank <- seq_len(nrow(all_full_tops_raw))

all_tops_raw <- do.call(
    rbind,
    list(all_der_tops_raw, all_val_tops_raw, all_full_tops_raw)
)

all_tops_raw$"set" <- factor(all_tops_raw$"set", levels = c("D", "V", "F"))

options(width = 200)

all_tops_raw <- all_tops_raw |>
    arrange(rank, set)

write_csv(all_tops_raw, proc_path("all_tops_raw.csv", TRUE))
```

```{r}
all_tops_raw <- read_csv(proc_path("2024_09_23_all_tops_raw.csv"))

# Comparison based purely on effect size
compare_fn_a <- function(d, sig, thresh = 0.2) {
    order <- case_when(
        d >= thresh ~ ">",
        d <= -thresh ~ "<",
        abs(d) < thresh ~ "=",
        TRUE ~ NA
    )
    return(order)
}

# Comparison based on effect size and significance
compare_fn_b <- function(d, sig, thresh = 0.2) {
    order <- case_when(
        d >= thresh ~ ">",
        d <= -thresh ~ "<",
        d > 0 & sig ~ ">",
        d < 0 & sig ~ "<",
        abs(d) < thresh & !sig ~ "=",
        TRUE ~ NA
    )
}

generalizable_features <- function(tops_df, comparison_fn, t = 0.2) {
    # Remove unnecessary columns
    if ("rank" %in% colnames(tops_df)) {
        tops_df <- dplyr::select(tops_df, -rank)
    }
    if ("summary" %in% colnames(tops_df)) {
        tops_df <- dplyr::select(tops_df, -summary)
    }
    # Calculate significance for every row
    tops_df <- tops_df |>
        mutate(
            c12_sig = as.logical(significant_es(es, c12_l, c12_u)),
            c13_sig = as.logical(significant_es(es, c13_l, c13_u)),
            c23_sig = as.logical(significant_es(es, c23_l, c23_u))
        )
    # Create d-values for every row
    tops_df <- tops_df |>
        dplyr::mutate(
            c12_d = dplyr::case_when(
                es == "d" ~ c12_es,
                es == "or" ~ suppressWarnings(log(c12_es)) * sqrt(3) / pi
            ),
            c13_d = dplyr::case_when(
                es == "d" ~ c13_es,
                es == "or" ~ suppressWarnings(log(c13_es)) * sqrt(3) / pi
            ),
            c23_d = dplyr::case_when(
                es == "d" ~ c23_es,
                es == "or" ~ suppressWarnings(log(c23_es)) * sqrt(3) / pi
            )
        )
    # Calculate orderings
    tops_df <- tops_df |>
        dplyr::mutate(
            c12_order = comparison_fn(c12_d, c12_sig, thresh = t),
            c13_order = comparison_fn(c13_d, c13_sig, thresh = t),
            c23_order = comparison_fn(c23_d, c23_sig, thresh = t)
        )
    # Now find conistency across D, V, F for each feature
    features <- unique(tops_df$"feature")
    gen_df <- data.frame()
    for (ft in features) {
        feature_df <- dplyr::filter(tops_df, feature == ft)
        c12 <- feature_df$"c12_order"
        c13 <- feature_df$"c13_order"
        c23 <- feature_df$"c23_order"
        if (any(is.na(c12)) | length(unique(c12)) > 1) {
            c12o <- NA
        } else {
            c12o <- unique(c12)
        }
        if (any(is.na(c13)) | length(unique(c13)) > 1) {
            c13o <- NA
        } else {
            c13o <- unique(c13)
        }
        if (any(is.na(c23)) | length(unique(c23)) > 1) {
            c23o <- NA
        } else {
            c23o <- unique(c23)
        }
        gen_df <- rbind(
            gen_df,
            data.frame(
                feature = ft,
                c1v2 = c12o,
                c1v3 = c13o,
                c2v3 = c23o
            )
        )
    }
    return(gen_df)
}

gen_df_a <- generalizable_features(all_tops_raw, compare_fn_a, 0.2)
gen_df_b <- generalizable_features(all_tops_raw, compare_fn_b)

# The generalizable features appear identical by both means
identical(gen_df_a, gen_df_b)

write_csv(gen_df_a, proc_path("mtbi_gen_fts.csv", TRUE))

mtbi_gen_fts <- data.frame(read_csv(proc_path("2024_09_23_mtbi_gen_fts.csv")))

mtbi_gen_fts_in <- mtbi_gen_fts |>
    dplyr::filter(
        c1v2 %in% c(">", "<") | c1v3 %in% c(">", "<") | c2v3 %in% c(">", "<")
    ) |>
    dplyr::filter(
        !feature %in% outcomes
    )

mtbi_gen_fts_out <- mtbi_gen_fts |>
    dplyr::filter(
        c1v2 %in% c(">", "<") | c1v3 %in% c(">", "<") | c2v3 %in% c(">", "<")
    ) |>
    dplyr::filter(
        feature %in% outcomes
    )

write_csv(mtbi_gen_fts_in, proc_path("mtbi_gen_fts_in.csv", TRUE))
write_csv(mtbi_gen_fts_out, proc_path("mtbi_gen_fts_out.csv", TRUE))

mtbi_gen_fts_in <- read_csv(proc_path("2024_09_23_mtbi_gen_fts_in.csv"))
mtbi_gen_fts_out <- read_csv(proc_path("2024_09_23_mtbi_gen_fts_out.csv"))

mtbi_gen_fts_in_long <- mtbi_gen_fts_in |>
    pivot_longer(
        cols = -feature,
        names_to = "comparison",
        values_to = "order"
    )

mtbi_gen_fts_out_long <- mtbi_gen_fts_out |>
    pivot_longer(
        cols = -feature,
        names_to = "comparison",
        values_to = "order"
    )

write_csv(mtbi_gen_fts_in_long, proc_path("mtbi_gen_fts_in_long.csv", TRUE))
write_csv(mtbi_gen_fts_out_long, proc_path("mtbi_gen_fts_out_long.csv", TRUE))

mtbi_gen_fts_in_long <- read_csv(proc_path("2024_09_23_mtbi_gen_fts_in_long.csv"))
mtbi_gen_fts_out_long <- read_csv(proc_path("2024_09_23_mtbi_gen_fts_out_long.csv"))

xtable(mtbi_gen_fts_out)
xtable(mtbi_gen_fts_in)
```
