# metaSNF of Baseline mTBI Subjects

In this chapter, I use the metaSNF package to generate and characterize meta clusters of the extracted data.

## Importing packages and establishing file paths


```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)
library(ggplot2)
library(patchwork)
library(xtable)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subjects <- read_csv(sub_path("2024_08_17_mtbi_subjects.csv"))
mtbi_train_subjects <- read_csv(sub_path("2024_08_17_mtbi_train_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2024_08_17_uninjured_subjects.csv"))
```


## Importing data


```{r}
# CHECKPOINT
all_dls <- list.load(input_path("2024_08_17_all_dls.rds"))
```


## Generating custom distance measures


```{r}
# CHECKPOINT
###############################################################################
# 2. Add standard normalized variations to the distance metrics list (also
# achievable through toggling automatic_standard_normalize parameter in
# `batch_snf`)
###############################################################################
my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

summarize_dml(my_distance_metrics)
```


## Generating the settings matrix


```{r}
mtbi_settings_matrix <- generate_settings_matrix(
    all_dls$"mtbi_train_data_lists"$"imp_1",
    nrow = 200,
    seed = 42,
    distance_metrics_list = my_distance_metrics
)

write_csv(mtbi_settings_matrix, proc_path("mtbi_settings_matrix.csv", TRUE))

mtbi_settings_matrix <- read_csv(
    proc_path("2024_08_17_mtbi_settings_matrix.csv")
)
```


## Running SNF for each of the imputations


```{r}
mtbi_train_dls <- c(
    all_dls$"mtbi_train_data_lists",
    all_dls$"mtbi_pooled_data_lists"
)

names(mtbi_train_dls) <- c(paste0("imp_", 1:5), paste0("pooled_imp_", 1:5))

mtbi_train_solutions_matrices <- lapply(
    mtbi_train_dls,
    function(imputed_dl) {
        summarize_dl(imputed_dl)
        solutions_matrix <- batch_snf(
            data_list = imputed_dl,
            settings_matrix = mtbi_settings_matrix,
            distance_metrics_list = my_distance_metrics,
            processes = "max"
        )
    }
)

#
list.save(
    mtbi_train_solutions_matrices,
    input_path("mtbi_train_solutions_matrices.rds", TRUE)
)
#
mtbi_train_solutions_matrices <- list.load(
    input_path("2024_08_17_mtbi_train_solutions_matrices.rds")
)
#
mtbi_sm <- do.call(
    "rbind",
    mtbi_train_solutions_matrices
)
#
write_csv(data.frame(mtbi_sm), proc_path("mtbi_sm.csv", TRUE))
#
mtbi_ari <- calc_aris(mtbi_sm, processes = "max")
#
write_csv(data.frame(mtbi_ari), proc_path("mtbi_ari.csv", TRUE))
#
mtbi_ari_order <- get_matrix_order(mtbi_ari)
#
write_csv(data.frame(mtbi_ari_order), proc_path("mtbi_ari_order.csv", TRUE))
```


## Re-importing data


```{r}
# CHECKPOINT
mtbi_sm <- read_csv(proc_path("2024_08_17_mtbi_sm.csv"))

mtbi_ari <- as.matrix(read_csv(proc_path("2024_08_17_mtbi_ari.csv")))

mtbi_ari_order <- unlist(read_csv(proc_path("2024_08_17_mtbi_ari_order.csv")))
names(mtbi_ari_order) <- NULL
```



## Calculating associations between cluster solutions and features


```{r}
imputation_labels <- data.frame(
    "imputation" = c(
        rep("m1", 200),
        rep("m2", 200),
        rep("m3", 200),
        rep("m4", 200),
        rep("m5", 200),
        rep("pm1", 200),
        rep("pm2", 200),
        rep("pm3", 200),
        rep("pm4", 200),
        rep("pm5", 200)
    ),
    "pooled" = c(
        rep("no", 1000),
        rep("yes", 1000)
    )
)

mtbi_sm_l <- cbind(mtbi_sm, imputation_labels)

mtbi_esm_m1 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "m1", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_1",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_1",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_m2 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "m2", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_2",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_2",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_m3 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "m3", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_3",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_3",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_m4 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "m4", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_4",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_4",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_m5 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "m5", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_5",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_5",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_pm1 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "pm1", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_1",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_1",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_pm2 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "pm2", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_2",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_2",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_pm3 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "pm3", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_3",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_3",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_pm4 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "pm4", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_4",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_4",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_pm5 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "pm5", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_5",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_5",
    min_pval = 1e-10,
    processes = "max"
)

mtbi_esm <- dplyr::bind_rows(
    mtbi_esm_m1,
    mtbi_esm_m2,
    mtbi_esm_m3,
    mtbi_esm_m4,
    mtbi_esm_m5,
    mtbi_esm_pm1,
    mtbi_esm_pm2,
    mtbi_esm_pm3,
    mtbi_esm_pm4,
    mtbi_esm_pm5
)

mtbi_esm$"impairment_separation" <- -log10(mtbi_esm$"mean_pval")

write_csv(mtbi_esm, proc_path("mtbi_esm.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_esm <- read_csv(proc_path("2024_08_17_mtbi_esm.csv"))
```


## Identifying and visualizing meta clusters


```{r}
base_ari_hm <- adjusted_rand_index_heatmap(
    mtbi_ari,
    order = mtbi_ari_order
)

shiny_annotator(base_ari_hm)

mtbi_split_vec <- c(
    190,
    514,
    646,
    845,
    1192,
    1442,
    1474,
    1710
)

write_csv(data.frame(mtbi_split_vec), proc_path("mtbi_split_vec.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_split_vec <- read_csv(proc_path("2024_08_18_mtbi_split_vec.csv")) |>
    unlist() |>
    as.numeric()
```

```{r}
divergent_colours <- function(column)  {
    values <- unique(column)
    colours <- RColorBrewer::brewer.pal(n = length(values), name = "Set3")
    names(colours) <- values
    return(colours)
}

full_mtbi_ari_hm <- adjusted_rand_index_heatmap(
    aris = mtbi_ari,
    order = mtbi_ari_order,
    data = mtbi_esm,
    min_colour = "black",
    split_vector = mtbi_split_vec,
    top_hm = list(
        "Impairment Separation" = "impairment_separation"
    ),
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    left_hm = list(
        "Pooled" = "pooled",
        "Imputation" = "imputation"
    ),
    annotation_colours = list(
        "Impairment Separation" = colour_scale(
            mtbi_esm$"impairment_separation",
            min_colour = "gray7",
            max_colour = "limegreen"
        ),
        "Imputation" = divergent_colours(mtbi_esm$"imputation"),
        "Pooled" = c(
            "yes" = "orange",
            "no" = "purple"
        )
    )
)
full_mtbi_ari_hm

save_heatmap(
    heatmap = full_mtbi_ari_hm,
    path = fig_path("full_mtbi_ari_hm.png", TRUE),
    width = 950,
    height = 900,
    res = 100
)

# Another heatmap without the imputation-related columns
lite_mtbi_ari_hm <- adjusted_rand_index_heatmap(
    aris = mtbi_ari,
    order = mtbi_ari_order,
    data = mtbi_esm,
    min_colour = "black",
    split_vector = mtbi_split_vec,
    top_hm = list(
        "Impairment Separation" = "impairment_separation"
    ),
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    annotation_colours = list(
        "Impairment Separation" = colour_scale(
            mtbi_esm$"impairment_separation",
            min_colour = "gray7",
            max_colour = "limegreen"
        )
    )
)

save_heatmap(
    heatmap = lite_mtbi_ari_hm,
    path = fig_path("lite_mtbi_ari_hm.png", TRUE),
    width = 900,
    height = 700,
    res = 100
)
```

When picking out representative solutions, I'd like to preferentially go for solutions that derived from solo rather than pooled imputations, as those solutions have values for all features.

```{r}
# Function to try to lean on mTBI-including solutions when possible.
# This function will pick from solo solutions unless over 70% of the meta
# cluster is pooled.
restrict_fn <- function(x, threshold = 0.3) {
    x_solo_ind <- x$"imputation" %in% c("m1", "m2", "m3", "m4", "m5")
    x_pool_ind <- x$"imputation" %in% c("pm1", "pm2", "pm3", "pm4", "pm5")
    x_solo <- x[x_solo_ind, ]
    x_pool <- x[x_pool_ind, ]
    frac_solo <- nrow(x_solo) / (nrow(x_solo) + nrow(x_pool))
    if (frac_solo < threshold) {
        return(x[x_pool_ind, ])
    } else {
        return(x[x_solo_ind, ])
    }
}

mtbi_rep_solutions <- get_representative_solutions(
    mtbi_ari,
    split_vector = mtbi_split_vec,
    order = mtbi_ari_order,
    filter_fn = restrict_fn,
    mtbi_esm
)

mtbi_rep_solutions

# Based on the heatmap, we'll remove B, E, H, K (unstable meta clusters)
mtbi_rep_solutions <- dplyr::filter(
    mtbi_rep_solutions,
    !label %in% c("E", "G", "I")
)

write_csv(mtbi_rep_solutions, proc_path("mtbi_rep_solutions.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_rep_solutions <- read_csv(proc_path("2024_08_18_mtbi_rep_solutions.csv"))
```

```{r}
mtbi_manhattan <- mc_manhattan_plot(
    mtbi_rep_solutions,
    data_list = all_dls$"mtbi_train_data_lists"$"imp_2",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_2",
    domain_colours = c(
        "AS" = "#85929e",
        "D" = "#bb8fce",
        "N" = "#e59866",
        "MH" = "#7fb3d5",
        "P" = "#52be80",
        "S" = "#d98880",
        "B" = "#ff3131"
    )
)
mtbi_manhattan

ggsave(
    plot = mtbi_manhattan,
    filename = fig_path("mtbi_manhattan.png", TRUE),
    width = 18,
    height = 14,
    dpi = 120
)

# The most robust solution
mtbi_mc_d_esm <- mtbi_rep_solutions |>
    dplyr::filter(label == "D")

write_csv(mtbi_mc_d_esm, proc_path("mtbi_mc_d_esm.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_mc_d_esm <- read_csv(proc_path("2024_08_18_mtbi_mc_d_esm.csv"))
```

```{r}
mtbi_mc_d_esm$"imputation"

# Feature plot generation
plot_list <- auto_plot(
    solutions_matrix_row = mtbi_mc_d_esm,
    data_list = all_dls$"mtbi_train_data_lists"$"imp_2",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_2",
    save = fig_path("mtbi_mc_d", TRUE)
)

# No save version:
plot_list <- auto_plot(
    solutions_matrix_row = mtbi_mc_d_esm,
    data_list = all_dls$"mtbi_train_data_lists"$"imp_2",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_2"
)

all_plots <- wrap_plots(plot_list)

# Good enough as a snapshot
ggsave(
    fig_path("mtbi_mc_d_all_plots.png", TRUE),
    all_plots,
    width = 45,
    height = 30,
    dpi = 50
)
```


## Characterization of meta cluster D representative solution

### NMI


```{r}
nmis <- batch_nmi(
    all_dls$"mtbi_train_data_lists"$"imp_2",
    mtbi_mc_d_esm,
    distance_metrics_list = my_distance_metrics
)

nmi_order <- sort(
    nmis$"row_id_81",
    decreasing = TRUE,
    index.return = TRUE
)

ordered_nmis <- nmis[nmi_order$ix, ]

ordered_nmis$"nmi_rank" <- rank(
    -ordered_nmis$"row_id_81",
    ties.method = "min"
)
```


### p-values


```{r}
pvals <- get_pvals(
    mtbi_mc_d_esm,
    keep_summaries = FALSE
)
pvals <- data.frame(
    "feature" = gsub("_pval", "", names(pvals)),
    "neg_log_pval" = -log10(as.numeric(unlist(pvals)))
)
pvals <- pvals[-1, ]
pvals_order <- sort(
    pvals$"neg_log_pval",
    decreasing = TRUE,
    index.return = TRUE
)
ordered_pvals <- pvals[pvals_order$ix, ]
ordered_pvals <- dplyr::filter(
    ordered_pvals,
    !grepl("^cbcl|^sds", feature)
)

ordered_pvals$"pval_rank" <- rank(
    -ordered_pvals$"neg_log_pval",
    ties.method = "min"
)
```


### Joint rank


```{r}
mtbi_mc_d_nmi_v_pval <- dplyr::full_join(
    ordered_nmis,
    ordered_pvals,
    by = "feature"
)

domain_df <- dl_variable_summary(all_dls$"mtbi_train_data_lists"$"imp_2") |>
    dplyr::select(name, domain) |>
    dplyr::rename("feature" = "name")

mtbi_mc_d_nmi_v_pval <- mtbi_mc_d_nmi_v_pval |>
    dplyr::inner_join(domain_df, by = "feature")

mtbi_mc_d_nmi_v_pval$"joint_rank" <- rank(
    mtbi_mc_d_nmi_v_pval$"nmi_rank" + mtbi_mc_d_nmi_v_pval$"pval_rank",
    ties.method = "min"
)

joint_order <- sort(
    mtbi_mc_d_nmi_v_pval$"joint_rank",
    decreasing = FALSE,
    index.return = TRUE
)

mtbi_mc_d_nmi_v_pval_rank <- mtbi_mc_d_nmi_v_pval[joint_order$ix, ]

mtbi_mc_d_nmi_v_pval_rank <- mtbi_mc_d_nmi_v_pval_rank |>
    dplyr::rename("nmi" = "row_id_81")

mtbi_mc_d_nmi_v_pval_rank <- mtbi_mc_d_nmi_v_pval_rank |>
    dplyr::select(
        feature,
        domain,
        nmi,
        nmi_rank,
        neg_log_pval,
        pval_rank,
        joint_rank
    )

write_csv(
    mtbi_mc_d_nmi_v_pval_rank,
    proc_path("mtbi_mc_d_nmi_v_pval_rank.csv", TRUE)
)

data.frame(mtbi_mc_d_nmi_v_pval_rank)

# Latex table
xtable(data.frame(mtbi_mc_d_nmi_v_pval_rank))
```

                  feature domain          nmi nmi_rank neg_log_pval pval_rank joint_rank
1                     sex      D 0.2985873838        1   10.0000000         1          1
2            brain_volume      N 0.2217644212        2   10.0000000         1          2
3             cortical_sa      N 0.2032265446        3   10.0000000         1          3
4        household_income      D 0.1451227069        4   10.0000000         1          4
5       pubertal_status_p      D 0.1085711605        5   10.0000000         1          5
6      programs_this_year      P 0.0931335524        6   10.0000000         1          6
8     non_school_programs      P 0.0747381192        8   10.0000000         1          7
10         parent_somatic      P 0.0662651869       10   10.0000000         1          8
11     weekday_screentime      P 0.0632396705       11   10.0000000         1          9
7                    race      D 0.0774583581        7    8.1140944        13         10
13         parent_depress      P 0.0477022183       13    8.8134915        11         11
14         parent_thought      P 0.0466989872       14    9.7334076        10         11
17          parent_anxdep      P 0.0425659370       17    8.1884295        12         13
12    private_instruction      P 0.0584871743       12    6.1573351        18         14
15      parent_antisocial      P 0.0452306056       15    7.9663295        15         14
18         fmri_cort_cors      N 0.0417425220       18    7.3756235        16         16
20      parent_aggressive      P 0.0393519079       20    8.0811853        14         16
9      weekend_screentime      P 0.0721706141        9    3.1658276        29         18
22       parent_anxdisord      P 0.0361093706       22    6.7082660        17         19
16          exercise_time      P 0.0443959675       16    3.9952204        25         20
19         family_fight_p      P 0.0401472888       19    4.6992767        22         20
25     cortical_thickness      N 0.0298916659       25    5.1290506        20         22
21 fmri_cort_subcort_cors      N 0.0386767628       21    3.7192756        26         23
23        parent_avoidant      P 0.0336032086       23    4.2825992        24         23
28     parent_hyperactive      P 0.0279453604       28    5.1692320        19         23
27       parent_attention      P 0.0284097681       27    4.9589901        21         26
31       parent_withdrawn      P 0.0265018835       31    4.3490583        23         27
29           helps_hurt_p      P 0.0274069997       29    3.2958551        28         28
30          considerate_y      P 0.0273993871       30    3.4709959        27         28
26           major_wm_ndi      N 0.0291007627       26    2.9070615        33         30
32           helps_hurt_y      P 0.0249872491       32    2.9882885        30         31
33              helpful_p      P 0.0235618961       33    2.9102231        32         32
34           family_hit_p      P 0.0234408323       34    2.3935444        36         33
37         family_outdo_p      P 0.0220122681       37    2.6341984        34         34
41       parent_intrusive      P 0.0201717654       41    2.9516614        31         35
35       headache_history     MH 0.0230578288       35    2.2107514        40         36
40               mtbi_loc     AS 0.0206061192       40    2.6059292        35         36
38      family_peaceful_y      P 0.0210522209       38    1.9503586        43         38
39      family_peaceful_p      P 0.0209353039       39    2.0765066        42         38
24          parent_perstr      P 0.0320081639       24    0.7881771        58         40
44          considerate_p      P 0.0183202410       44    2.3796597        38         40
45    pericortical_wm_ndi      N 0.0173340830       45    2.3815893        37         40
46        family_temper_p      P 0.0166428482       46    2.2273051        39         43
43                    age      D 0.0187117914       43    1.8421893        45         44
47     family_criticize_p      P 0.0166052825       47    2.1272289        41         44
48         family_outdo_y      P 0.0152259886       48    1.9141442        44         46
42        school_programs      P 0.0192015706       42    1.3088942        51         47
36               mtbi_age      D 0.0224022854       36    0.7780819        59         48
49          family_yell_y      P 0.0141902908       49    1.7358388        47         49
50  same_sex_close_friend      P 0.0122821681       50    1.7657008        46         49
51     family_criticize_y      P 0.0119354939       51    1.4455761        49         51
52         family_angry_y      P 0.0114856671       52    1.5162493        48         51
55         family_angry_p      P 0.0107022991       55    1.4270912        50         53
54         family_throw_p      P 0.0107519383       54    1.0998158        53         54
58              helpful_y      P 0.0088325050       58    1.1753101        52         55
56      pubertal_status_y      D 0.0102883494       56    0.9463089        55         56
57          mtbi_mem_daze     AS 0.0093869868       57    0.9614631        54         56
53        same_sex_friend      P 0.0110132368       53    0.6322198        60         58
59         previous_mtbis     MH 0.0066352548       59    0.8213008        57         59
60         mtbi_mechanism     AS 0.0049358228       60    0.8696554        56         59
61         family_fight_y      P 0.0041952645       61    0.4873173        61         61
63         opp_sex_friend      P 0.0028603637       63    0.3800571        62         62
62         family_throw_y      P 0.0033013525       62    0.3367914        64         63
64        family_temper_y      P 0.0028015716       64    0.3633989        63         64
65           family_hit_y      P 0.0016846994       65    0.1883945        65         65
66   opp_sex_close_friend      P 0.0011695472       66    0.1606693        66         66
67          family_yell_p      P 0.0009946099       67    0.1322986        67         67

```{r}
# CHECKPOINT
mtbi_mc_d_nmi_v_pval_rank <- read_csv(
    proc_path("2024_08_20_mtbi_mc_d_nmi_v_pval_rank.csv")
)
```


### Correlation of NMI and p-value


```{r}
nmi_v_p_rho <- cor(
    mtbi_mc_d_nmi_v_pval_rank$"nmi_rank",
    mtbi_mc_d_nmi_v_pval_rank$"pval_rank",
    method = "spearman"
)

nmi_v_pval_plot <- mtbi_mc_d_nmi_v_pval_rank |>
    ggplot(
        aes(x = nmi_rank, y = pval_rank, label = feature, colour = domain)
    ) +
    geom_point(size = 2) + 
    scale_colour_manual(
        values = c(
            "AS" = "#85929e",
            "D" = "#bb8fce",
            "N" = "#e59866",
            "MH" = "#7fb3d5",
            "P" = "#52be80"
        )
    ) +
    theme_bw() +
    labs(x = "Rank by NMI", y = "Rank by Association p-value") +
    ggrepel::geom_text_repel(
        #vjust = 3,
        #hjust = 1,
        force = 1,
        max.overlaps = 20,
        size = 4
    ) +
    annotate(
        "text",
        x = 4,
        y = 50,
        size = 5,
        label = paste("Spearman's ρ =", round(nmi_v_p_rho, 2)),
        hjust = 0
    ) + 
    theme(text = element_text(size = 16))
nmi_v_pval_plot

ggsave(
    fig_path("nmi_v_pval_plot.png", TRUE),
    nmi_v_pval_plot,
    width = 12,
    height = 12
)
```


### Visualizing top 10 features


```{r}
sorted_features <- mtbi_mc_d_nmi_v_pval_rank$"feature"

names(plot_list)

ranked_plot_list <- plot_list[sorted_features]

ranked_all_plots <- wrap_plots(ranked_plot_list)

ggsave(
    fig_path("mtbi_mc_d_ranked_all_plots.png", TRUE),
    ranked_all_plots,
    width = 45,
    height = 30,
    dpi = 50
)

saveRDS(
    ranked_all_plots,
    file = fig_path("mtbi_mc_d_ranked_all_plots.rds", TRUE)
)

mtbi_mc_e_ranked_all_plots <- readRDS(
    fig_path("2024_08_21_mtbi_mc_d_ranked_all_plots.rds")
)

###############################################################################
# Building the top 12 plot list
###############################################################################

mc_d_top_pl <- ranked_plot_list[1:12]

names(mc_d_top_pl) <- sorted_features[1:12]

names(mc_d_top_pl)

#
mc_d_top_pl$"sex" <- mc_d_top_pl$"sex" +
    labs(fill = "Sex") +
    scale_fill_discrete(labels = c("F", "M"))
#
mc_d_top_pl$"brain_volume" <- mc_d_top_pl$"brain_volume" +
    labs(y = expression(paste("Brain Volume ", (mm^3))))
#
mc_d_top_pl$"cortical_sa" <- mc_d_top_pl$"cortical_sa" +
    labs(y = expression(paste("Cortical Area ", (mm^2))))
#
mc_d_top_pl$"household_income" <- mc_d_top_pl$"household_income" +
    labs(y = "Household Income")
#
mc_d_top_pl$"pubertal_status_p" <- mc_d_top_pl$"pubertal_status_p" +
    labs(y = "Pubertal Status - P")
#
mc_d_top_pl$"programs_this_year" <- mc_d_top_pl$"programs_this_year" +
    labs(y = "Total Activities this Year")
#
mc_d_top_pl$"non_school_programs" <- mc_d_top_pl$"non_school_programs" +
    labs(y = "Lifetime Extracurriculars")
#
mc_d_top_pl$"parent_somatic" <- mc_d_top_pl$"parent_somatic" +
    labs(y = "Parent Somatic Problems")
#
mc_d_top_pl$"weekday_screentime" <- mc_d_top_pl$"weekday_screentime" +
    labs(y = "Weekday Screentime")
#
mc_d_top_pl$"race" <- mc_d_top_pl$"race" +
    labs(fill = "Race") +
    scale_fill_discrete(labels = c("Black", "Hispanic", "Other", "White"))
#
mc_d_top_pl$"parent_depress" <- mc_d_top_pl$"parent_depress" +
    labs(y = "Parent Depression Problems")
#
mc_d_top_pl$"parent_thought" <- mc_d_top_pl$"parent_thought" +
    labs(y = "Parent Thought Problems")
#

mc_d_top_p <- wrap_plots(
    mc_d_top_pl,
) & labs(x = "Cluster") & theme(plot.margin = unit(c(0.5, 1.5, 0.5, 2), "cm"))
ggsave(
    fig_path("mtbi_mc_d_ranked_all_plots_12.png", TRUE),
    mc_d_top_p,
    width = 25,
    height = 15,
    dpi = 150
)


###############################################################################
# Outcomes
###############################################################################

mtbi_mc_d_esm_plot_df <- auto_plot(
    solutions_matrix_row = mtbi_mc_d_esm,
    data_list = all_dls$"mtbi_train_data_lists"$"imp_2",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_2",
    return_plots = FALSE
)

mtbi_mc_d_ranked_all_plots[[2]]

outcome_plot_list <- auto_plot(
    solutions_matrix_row = mtbi_mc_d_esm,
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_2"
)

names(outcome_plot_list)

clean_names <- c(
    "CBCL\nAnxious-Depressed",
    "CBCL\nWithdrawn-Depressed",
    "CBCL\nSomatic Problems",
    "CBCL\nSocial Problems",
    "CBCL\nThought Problems",
    "CBCL\nAttention Problems",
    "CBCL\nRule-breaking Problems",
    "CBCL\nAggression Problems",
    "SDS Total\nSleeping Problems"
)
for (i in seq_along(outcome_plot_list)) {
    outcome_plot_list[[i]] <- outcome_plot_list[[i]] +
        labs(y = clean_names[[i]], x = "Cluster")
}

outcome_plot_wrap <- wrap_plots(outcome_plot_list) &
    theme(plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), "cm"))

ggsave(
    fig_path("mtbi_mc_d_outcome_plot_wrap.png", TRUE),
    outcome_plot_wrap,
    width = 14,
    height = 14,
    dpi = 150
)
```


### Detailed cluster topologies

Can come back to this later.

```{r}# 

proptable <- function(df, ft) {
    tab <- prop.table(
        table(df[, ft], df$"cluster"),
        margin = 2
    ) * 100
    return(tab)
}

proptable(mtbi_mc_e_esm_plot_df, "sex")

proptable(mtbi_mc_e_esm_plot_df, "sex")

tstat <- function(d, n1, n2) {
    t <- d * sqrt((n1 * n2) / (n1 + n2))
    return(t)
}
pooled_sd <- function(n1, s1, n2, s2) {
    numerator <- ((n1 - 1) * (s1^2)) + ((n2 - 1) * (s2^2))
    denominator <- n1 + n2 - 2
    s <- sqrt(numerator / denominator)
    return(s)
}
cohens_d <- function(mean1, mean2, pooled_sd) {
    d <- (mean1 - mean2) / pooled_sd
    return(d)
}

calc_es <- function(x1, x2) {
    n1 <- length(x1)
    n2 <- length(x2)
    s1 <- sd(x1)
    s2 <- sd(x2)
    s <- pooled_sd(n1, s1, n2, s2)
    mean1 <- mean(x1)
    mean2 <- mean(x2)
    d <- cohens_d(mean1, mean2, s)
    d_full <- des(d, n1, n2, verbose = FALSE)
    return(
        list(
            "d" = d_full$"d",
            
        )
    )
}

mc_e_c1 <- mtbi_mc_e_esm_plot_df |> dplyr::filter(cluster == 1)
mc_e_c2 <- mtbi_mc_e_esm_plot_df |> dplyr::filter(cluster == 2)
mc_e_c3 <- mtbi_mc_e_esm_plot_df |> dplyr::filter(cluster == 3)

n1 <- nrow(mc_e_c1)
n2 <- nrow(mc_e_c2)
n3 <- nrow(mc_e_c3)

d <- calc_es(
    mc_e_c1$"brain_volume",
    mc_e_c2$"brain_volume"
)

d

z2 <- des(d, n1, n2, verbose = FALSE)

z2

library(compute.es)

table(mc_e_c1$"sex")
table(mc_e_c3$"sex")




z <- propes(
    0.1214953,
    0.8225806,
    nrow(mc_e_c1),
    nrow(mc_e_c3)
)

z$"OR"

es_bound(d, nrow(mc_e_c1), nrow(mc_e_c2))


```


sex:  Cluster 1 and 2 were primarily male (87.9% and 83.9% male respectively), while cluster 3 was primarily female (82.3%). 


brain_volume
cortical_sa
household_income
pubertal_status_p
programs_this_year
non_school_programs
parent_somatic
weekday_screentime
race
parent_thought
private_instruction
parent_anxdep
fmri_cort_subcort_cors
parent_depress
fmri_cort_cors
parent_aggressive
parent_antisocial
weekend_screentime
parent_anxdisord
considerate
headache_history
family_outdo
helps_hurt
parent_hyperactive
major_wm_ndi
parent_withdrawn
parent_avoidant
parent_perstr
parent_attention
cortical_thickness
exercise_time
family_fight
family_temper
family_criticize
family_angry
family_peaceful
family_throw
parent_intrusive
helpful
same_sex_close_friend
pubertal_status_y
pericortical_wm_ndi
age
school_programs
same_sex_friend
family_yell
mtbi_age
mtbi_mechanism
family_hit
mtbi_loc
previous_mtbis
mtbi_mem_daze
opp_sex_friend
opp_sex_close_friend


```{r}



binary_or <- function(df, feature, ca, cb) {
    ca_values <- df[df$"cluster" == ca, feature]
    cb_values <- df[df$"cluster" == cb, feature]
    print(ca_values)
    print(".")
    print(cb_values)
}
binary_or(
    mtbi_mc_e_esm_plot_df,
    feature = "sex",
    ca = 1,
    cb = 2
)

sorted_features

# OR calculations
or_from_table <- function(table, exposed_c, ctrl_c, outcome_cat, nothing_cat) {
    df <- data.frame(table)
    colnames(df) <- c("cluster", "event", "freq")
    exposed_outcome <- dplyr::filter(
        df,
        cluster == exposed_c & event == outcome_cat
    )$"freq"
    ctrl_outcome <- dplyr::filter( df,
        cluster == ctrl_c & event == outcome_cat
    )$"freq"
    exposed_nothing <- dplyr::filter(
        df,
        cluster == exposed_c & event == nothing_cat
    )$"freq"
    ctrl_nothing <- dplyr::filter( df,
        cluster == ctrl_c & event == nothing_cat
    )$"freq"
    or_num <- exposed_outcome / ctrl_outcome
    or_den <- exposed_nothing / ctrl_nothing
    or <- or_num / or_den
    d <- ln()
    return(or_num / or_den)
}

# Race
race_df <- mtbi_mc_e_esm_plot_df |>
    dplyr::select(cluster, race)

race_df$"race"[race_df$"race" != "white"] <- "minority"

race_tab <- table(race_df)

for (i in 1:3) {
    for (j in 1:3) {
        if (i != j) {
            or <- or_from_table(race_tab, i, j, "minority", "white")
            print(paste0("Cluster ", i, " vs. ", j, ": ", round(or, 2)))
            d <- 
            cat("\n")
        }
    }
}

or_from_table(race_tab, 1, 2, "minority", "white")

or_from_table(race_tab, 1, 3, "minority", "white")

or_from_table(race_tab, 1, 3, "minority", "white")

race_tab


metadata_df

sorted_features

mtbi_mc_e_esm_plot_df |> head()

odds_ratio <- function(de, he, dn, hn) {
    numerator <- de / he
    denominator <- dn / hn
    return(numerator / denominator)
}



```

ordinal variable -> cohen's d
continuous variable -> cohen's d
discrete variable -> cohen's d
categorical variable -> odd's ratio -> cohen's d
binary variable -> odd's ratio -> cohen's d

log odds * sqrt(3)/pi

# Label propagation

## Attempt 1: Propagation with the full data list

A label propagation attempt using the full data list.

```{r}
mtbi_mc_d_esm$"imputation"

# The data list that generated the top solution
train_data_list_m2 <- all_dls$"mtbi_train_data_lists"$"imp_2"
train_oom_list_m2 <- all_dls$"mtbi_train_oom_lists"$"imp_2"

# The first test data set, for example
test_data_list_m1 <- all_dls$"mtbi_test_data_lists"$"imp_1"
test_data_list_m2 <- all_dls$"mtbi_test_data_lists"$"imp_2"
test_data_list_m3 <- all_dls$"mtbi_test_data_lists"$"imp_3"
test_data_list_m4 <- all_dls$"mtbi_test_data_lists"$"imp_4"
test_data_list_m5 <- all_dls$"mtbi_test_data_lists"$"imp_5"

test_oom_list_m1 <- all_dls$"mtbi_test_oom_lists"$"imp_1"
test_oom_list_m2 <- all_dls$"mtbi_test_oom_lists"$"imp_2"
test_oom_list_m3 <- all_dls$"mtbi_test_oom_lists"$"imp_3"
test_oom_list_m4 <- all_dls$"mtbi_test_oom_lists"$"imp_4"
test_oom_list_m5 <- all_dls$"mtbi_test_oom_lists"$"imp_5"

full_data_list_1 <- merge_data_lists(train_data_list_m2, test_data_list_m1)
full_data_list_2 <- merge_data_lists(train_data_list_m2, test_data_list_m2)
full_data_list_3 <- merge_data_lists(train_data_list_m2, test_data_list_m3)
full_data_list_4 <- merge_data_lists(train_data_list_m2, test_data_list_m4)
full_data_list_5 <- merge_data_lists(train_data_list_m2, test_data_list_m5)

full_oom_list_1 <- merge_data_lists(train_oom_list_m2, test_oom_list_m1)
full_oom_list_2 <- merge_data_lists(train_oom_list_m2, test_oom_list_m2)
full_oom_list_3 <- merge_data_lists(train_oom_list_m2, test_oom_list_m3)
full_oom_list_4 <- merge_data_lists(train_oom_list_m2, test_oom_list_m4)
full_oom_list_5 <- merge_data_lists(train_oom_list_m2, test_oom_list_m5)

mtbi_mc_d_fdl_lp_1 <- lp_solutions_matrix(
    mtbi_mc_d_esm,
    full_data_list_1,
    distance_metrics_list = my_distance_metrics
)

colnames(mtbi_mc_d_fdl_lp_1) <- c("subjectkey", "group", "cluster")

mtbi_mc_d_fdl_lp_only_1 <- mtbi_mc_d_fdl_lp_1 |>
    dplyr::filter(group == "test") |>
    dplyr::select(-group)

mtbi_mc_d_fdl_lp_plot_list_1 <- auto_plot(
    cluster_df = mtbi_mc_d_fdl_lp_only_1,
    data_list = test_data_list_m1,
    target_list = test_oom_list_m1
)

fdl_lp_plots_1 <- wrap_plots(mtbi_mc_d_fdl_lp_plot_list_1)

ggsave(
    fig_path("mtbi_mc_d_fdl_lp_plots_1.png", TRUE),
    fdl_lp_plots_1,
    width = 45,
    height = 30,
    dpi = 50
)
```

That attempt leads to 2 cluster propagation driven almost exclusively by sex.

## Attempt 2: Top features, no reliance on sex

```{r}

names(mc_d_top_pl)

# This is the list that actually worked most recently
#top_12_non_sex <- c(
#    "d_income",
#    "p_parent_psych",
#    "d_race"
#)

top_full_dl_1 |> collapse_dl()

top_12_0 <- c(
    "d_income",
    "d_race"
)

top_12_1 <- c(
    "d_income",
    "p_parent_psych",
    "d_race"
)

top_12_2 <- c(
    "d_income",
    "p_parent_psych",
    "p_fam_fn",
    "d_race"
)

top_12_3 <- c(
    "d_income",
    "p_sports",
    "p_parent_psych",
    "p_screen_time",
    "d_race"
)

# Trim down the data list to just those top features
get_top_full_dl_a <- function(full_data_list, top_list) {
    return(full_data_list[top_list])
}

# Trim down the data list to just those top features
get_top_full_dl_b <- function(full_data_list, top_list) {
    top_full_dl <- lapply(
        full_data_list[top_list],
        function(x) {
            x$"data" <- x$"data"[, colnames(x$"data") %in% c("subjectkey", names(mc_d_top_pl))]
            return(x)
        }
    )
    return(top_full_dl)
}
```

Attempt summary

- fn_a
    - top_0
        - 21 in C1
        - good on income, race, and CBCL. decent on parent psych (see 4th plot)
        - bad on rationale
    - top_1
        - actually really good 4th plot
    - top_2
        - good on most things
        - bad 
        - eh honestly kind of mid. parent psych and cbcl seems to be pretty rough
    - top_3
        - bad
- fn_b
    - top_0
        - bad
    - top_1
        - bad
    - top_2
        - eh
    - top_3
        - bad

```{r}
top_full_dl_1 <- get_top_full_dl_a(full_data_list_1, top_12_3)
top_full_dl_2 <- get_top_full_dl_a(full_data_list_2, top_12_3)
top_full_dl_3 <- get_top_full_dl_a(full_data_list_3, top_12_3)
top_full_dl_4 <- get_top_full_dl_a(full_data_list_4, top_12_3)
top_full_dl_5 <- get_top_full_dl_a(full_data_list_5, top_12_3)

summarize_dl(top_full_dl_1)

mtbi_mc_d_lp_1 <- lp_solutions_matrix(
    mtbi_mc_d_esm,
    top_full_dl_1,
    distance_metrics_list = my_distance_metrics
)
#
mtbi_mc_d_lp_2 <- lp_solutions_matrix(
    mtbi_mc_d_esm,
    top_full_dl_2,
    distance_metrics_list = my_distance_metrics
)
#
mtbi_mc_d_lp_3 <- lp_solutions_matrix(
    mtbi_mc_d_esm,
    top_full_dl_3,
    distance_metrics_list = my_distance_metrics
)
#
mtbi_mc_d_lp_4 <- lp_solutions_matrix(
    mtbi_mc_d_esm,
    top_full_dl_4,
    distance_metrics_list = my_distance_metrics
)
#
mtbi_mc_d_lp_5 <- lp_solutions_matrix(
    mtbi_mc_d_esm,
    top_full_dl_5,
    distance_metrics_list = my_distance_metrics
)

sum(mtbi_mc_d_lp_1$"81" != mtbi_mc_d_lp_2$"81") #2
sum(mtbi_mc_d_lp_1$"81" != mtbi_mc_d_lp_3$"81") #2
sum(mtbi_mc_d_lp_1$"81" != mtbi_mc_d_lp_4$"81") #1
sum(mtbi_mc_d_lp_1$"81" != mtbi_mc_d_lp_5$"81") #2
sum(mtbi_mc_d_lp_2$"81" != mtbi_mc_d_lp_3$"81") #2
sum(mtbi_mc_d_lp_2$"81" != mtbi_mc_d_lp_4$"81") #3
sum(mtbi_mc_d_lp_2$"81" != mtbi_mc_d_lp_5$"81") #2
sum(mtbi_mc_d_lp_3$"81" != mtbi_mc_d_lp_4$"81") #1
sum(mtbi_mc_d_lp_3$"81" != mtbi_mc_d_lp_5$"81") #2
sum(mtbi_mc_d_lp_4$"81" != mtbi_mc_d_lp_5$"81") #1

colnames(mtbi_mc_d_lp_1) <- c("subjectkey", "group", "cluster")
colnames(mtbi_mc_d_lp_2) <- c("subjectkey", "group", "cluster")
colnames(mtbi_mc_d_lp_3) <- c("subjectkey", "group", "cluster")
colnames(mtbi_mc_d_lp_4) <- c("subjectkey", "group", "cluster")
colnames(mtbi_mc_d_lp_5) <- c("subjectkey", "group", "cluster")

table(dplyr::filter(mtbi_mc_d_lp_1, group == "test")$"cluster")
# 13 in 1, 63 in 2, 9 in 3


#write_csv(mtbi_mc_d_lp_1, proc_path("mtbi_mc_d_lp_1.csv", TRUE))
#write_csv(mtbi_mc_d_lp_2, proc_path("mtbi_mc_d_lp_2.csv", TRUE))
#write_csv(mtbi_mc_d_lp_3, proc_path("mtbi_mc_d_lp_3.csv", TRUE))
#write_csv(mtbi_mc_d_lp_4, proc_path("mtbi_mc_d_lp_4.csv", TRUE))
#write_csv(mtbi_mc_d_lp_5, proc_path("mtbi_mc_d_lp_5.csv", TRUE))
#
#mtbi_mc_d_lp_1 <- read_csv(proc_path("2024_08_21_mtbi_mc_d_lp_1.csv"))
#mtbi_mc_d_lp_2 <- read_csv(proc_path("2024_08_21_mtbi_mc_d_lp_2.csv"))
#mtbi_mc_d_lp_3 <- read_csv(proc_path("2024_08_21_mtbi_mc_d_lp_3.csv"))
#mtbi_mc_d_lp_4 <- read_csv(proc_path("2024_08_21_mtbi_mc_d_lp_4.csv"))
#mtbi_mc_d_lp_5 <- read_csv(proc_path("2024_08_21_mtbi_mc_d_lp_5.csv"))

#mtbi_mc_d_full_1 <- dplyr::select(mtbi_mc_d_lp_1, -group)
#mtbi_mc_d_full_2 <- dplyr::select(mtbi_mc_d_lp_2, -group)
#mtbi_mc_d_full_3 <- dplyr::select(mtbi_mc_d_lp_3, -group)
#mtbi_mc_d_full_4 <- dplyr::select(mtbi_mc_d_lp_4, -group)
#mtbi_mc_d_full_5 <- dplyr::select(mtbi_mc_d_lp_5, -group)

mtbi_mc_d_lp_only_1 <- dplyr::filter(mtbi_mc_d_lp_1, group == "test") |> dplyr::select(-group)
mtbi_mc_d_lp_only_2 <- dplyr::filter(mtbi_mc_d_lp_2, group == "test") |> dplyr::select(-group)
mtbi_mc_d_lp_only_3 <- dplyr::filter(mtbi_mc_d_lp_3, group == "test") |> dplyr::select(-group)
mtbi_mc_d_lp_only_4 <- dplyr::filter(mtbi_mc_d_lp_4, group == "test") |> dplyr::select(-group)
mtbi_mc_d_lp_only_5 <- dplyr::filter(mtbi_mc_d_lp_5, group == "test") |> dplyr::select(-group)

#write_csv(mtbi_mc_d_full_1, proc_path("mtbi_mc_d_full_1.csv", TRUE))
#write_csv(mtbi_mc_d_full_2, proc_path("mtbi_mc_d_full_2.csv", TRUE))
#write_csv(mtbi_mc_d_full_3, proc_path("mtbi_mc_d_full_3.csv", TRUE))
#write_csv(mtbi_mc_d_full_4, proc_path("mtbi_mc_d_full_4.csv", TRUE))
#write_csv(mtbi_mc_d_full_5, proc_path("mtbi_mc_d_full_5.csv", TRUE))
#
#write_csv(mtbi_mc_d_lp_only_1, proc_path("mtbi_mc_d_lp_only_1.csv", TRUE))
#write_csv(mtbi_mc_d_lp_only_2, proc_path("mtbi_mc_d_lp_only_2.csv", TRUE))
#write_csv(mtbi_mc_d_lp_only_3, proc_path("mtbi_mc_d_lp_only_3.csv", TRUE))
#write_csv(mtbi_mc_d_lp_only_4, proc_path("mtbi_mc_d_lp_only_4.csv", TRUE))
#write_csv(mtbi_mc_d_lp_only_5, proc_path("mtbi_mc_d_lp_only_5.csv", TRUE))
#
## CHECKPOINT
#mtbi_mc_d_full_1 <- read_csv(proc_path("2024_08_21_mtbi_mc_d_full_1.csv"))
#mtbi_mc_d_full_2 <- read_csv(proc_path("2024_08_21_mtbi_mc_d_full_2.csv"))
#mtbi_mc_d_full_3 <- read_csv(proc_path("2024_08_21_mtbi_mc_d_full_3.csv"))
#mtbi_mc_d_full_4 <- read_csv(proc_path("2024_08_21_mtbi_mc_d_full_4.csv"))
#mtbi_mc_d_full_5 <- read_csv(proc_path("2024_08_21_mtbi_mc_d_full_5.csv"))
#
#mtbi_mc_d_lp_only_1 <- read_csv(proc_path("2024_08_21_mtbi_mc_d_lp_only_1.csv"))
#mtbi_mc_d_lp_only_2 <- read_csv(proc_path("2024_08_21_mtbi_mc_d_lp_only_2.csv"))
#mtbi_mc_d_lp_only_3 <- read_csv(proc_path("2024_08_21_mtbi_mc_d_lp_only_3.csv"))
#mtbi_mc_d_lp_only_4 <- read_csv(proc_path("2024_08_21_mtbi_mc_d_lp_only_4.csv"))
#mtbi_mc_d_lp_only_5 <- read_csv(proc_path("2024_08_21_mtbi_mc_d_lp_only_5.csv"))

mtbi_mc_d_lp_only_plot_list_1 <- auto_plot(
    cluster_df = mtbi_mc_d_lp_only_1,
    data_list = test_data_list_m1,
    target_list = test_oom_list_m1
)

mtbi_mc_d_lp_only_plot_list_2 <- auto_plot(
    cluster_df = mtbi_mc_d_lp_only_2,
    data_list = test_data_list_m2,
    target_list = test_oom_list_m2
)

mtbi_mc_d_lp_only_plot_list_3 <- auto_plot(
    cluster_df = mtbi_mc_d_lp_only_3,
    data_list = test_data_list_m3,
    target_list = test_oom_list_m3
)

mtbi_mc_d_lp_only_plot_list_4 <- auto_plot(
    cluster_df = mtbi_mc_d_lp_only_4,
    data_list = test_data_list_m4,
    target_list = test_oom_list_m4
)

mtbi_mc_d_lp_only_plot_list_5 <- auto_plot(
    cluster_df = mtbi_mc_d_lp_only_5,
    data_list = test_data_list_m5,
    target_list = test_oom_list_m5
)

mtbi_mc_d_lp_only_all_plots_1 <- wrap_plots(mtbi_mc_d_lp_only_plot_list_1)
mtbi_mc_d_lp_only_all_plots_2 <- wrap_plots(mtbi_mc_d_lp_only_plot_list_2)
mtbi_mc_d_lp_only_all_plots_3 <- wrap_plots(mtbi_mc_d_lp_only_plot_list_3)
mtbi_mc_d_lp_only_all_plots_4 <- wrap_plots(mtbi_mc_d_lp_only_plot_list_4)
mtbi_mc_d_lp_only_all_plots_5 <- wrap_plots(mtbi_mc_d_lp_only_plot_list_5)

# It isn't quite a perfect match.
ggsave(
    fig_path("mtbi_mc_d_lp_only_all_plots_1.png", TRUE),
    mtbi_mc_d_lp_only_all_plots_1,
    width = 45,
    height = 30,
    dpi = 50
)
#
ggsave(
    fig_path("mtbi_mc_d_lp_only_all_plots_2.png", TRUE),
    mtbi_mc_d_lp_only_all_plots_2,
    width = 45,
    height = 30,
    dpi = 50
)
#
ggsave(
    fig_path("mtbi_mc_d_lp_only_all_plots_3.png", TRUE),
    mtbi_mc_d_lp_only_all_plots_3,
    width = 45,
    height = 30,
    dpi = 50
)
#
ggsave(
    fig_path("mtbi_mc_d_lp_only_all_plots_4.png", TRUE),
    mtbi_mc_d_lp_only_all_plots_4,
    width = 45,
    height = 30,
    dpi = 50
)
#
ggsave(
    fig_path("mtbi_mc_d_lp_only_all_plots_5.png", TRUE),
    mtbi_mc_d_lp_only_all_plots_5,
    width = 45,
    height = 30,
    dpi = 50
)
```

```{r}
top_lp_plots <- wrap_plots(mtbi_mc_d_lp_plot_list_1[names(mc_d_top_pl)]) &
    labs(x = "Cluster") &
    theme(plot.margin = unit(c(0.5, 1.5, 0.5, 2), "cm"))

ggsave(
    fig_path("mtbi_mc_d_ranked_all_plots_lp_12_1.png", TRUE),
    top_lp_plots,
    width = 25,
    height = 15,
    dpi = 150
)

mtbi_mc_d_full_plot_list <- auto_plot(
    cluster_df = mtbi_mc_d_full_1,
    data_list = full_data_list_1,
    target_list = full_oom_list_1
)

## HERE I AM 

#mtbi_mc_d_full_plot_list <- auto_plot(
#    cluster_df = mtbi_mc_d_full,
#    data_list = mtbi_mc_d_full_data_list,
#    target_list = mtbi_mc_d_full_oom_list,
#    save = fig_path("mtbi_mc_d_full", TRUE)
#)

mtbi_mc_e_lp_only_plot_list <- auto_plot(
    cluster_df = mtbi_mc_e_lp_only,
    data_list = test_data_list_m1,
    target_list = test_oom_list_m1
)

mtbi_mc_e_full_wrap <- wrap_plots(mtbi_mc_e_full_plot_list)

mtbi_mc_e_lp_only_wrap <- wrap_plots(mtbi_mc_e_lp_only_plot_list)

ggsave(
    fig_path("mtbi_mc_d_full_wrap.png", TRUE),
    mtbi_mc_d_full_wrap,
    width = 35,
    height = 30,
    dpi = 50
)

ggsave(
    fig_path("mtbi_mc_e_lp_only_wrap.png", TRUE),
    mtbi_mc_e_lp_only_wrap,
    width = 35,
    height = 30,
    dpi = 50
)

# Creating ESM formatted full solution
mtbi_mc_d_full_sm <- mtbi_mc_d_esm |>
    dplyr::select(
        -dplyr::contains("pval"),
        -dplyr::contains("impairment"),
        -label,
        -imputation,
        -pooled
    )
mtbi_mc_d_lp_only_sm_row <- data.frame(
    t(mtbi_mc_d_lp_only$"cluster")
)
colnames(mtbi_mc_d_lp_only_sm_row) <- mtbi_mc_d_lp_only$"subjectkey"
mtbi_mc_d_full_sm <- cbind(
    mtbi_mc_d_full_sm,
    mtbi_mc_d_lp_only_sm_row
)

mtbi_mc_d_full_esm <- extend_solutions(
    mtbi_mc_d_full_sm,
    data_list = mtbi_mc_d_full_data_list,
    target_list = mtbi_mc_d_full_oom_list,
    min_pval = 1e-10,
    processes = "max"
)

write_csv(mtbi_mc_d_full_esm, proc_path("mtbi_mc_d_full_esm.csv", TRUE))
mtbi_mc_d_full_esm <- read_csv(proc_path("2024_07_22_mtbi_mc_d_full_esm.csv"))

```

(Leave below for later)

# Longitudinal analyses

```{r}

#mtbi_train <- read_csv(sub_path("2024_03_12_mtbi_train_subjects.csv"))

core_path <- path_maker(here(paste0("data/abcd/core")))

import <- function(path) {
    return(abcd_load(core_path(path)))
}

mh_p_cbcl <- import("mental-health/mh_p_cbcl.csv")
ph_p_sds <- import("physical-health/ph_p_sds.csv")

mc_d_cluster_df <- get_cluster_df(mtbi_mc_d_esm)

mc_d_subs <- gsub("subject_", "", mc_d_cluster_df$"subjectkey")

syndromes <- c(
    "anxdep",
    #"withdep",
    #"somatic",
    #"social",
    #"thought",
    #"attention",
    #"rulebreak",
    "aggressive"
)

tps <- c(0, 1, 2, 3)

get_syndrome_long <- function(syndrome, timepoints, subs) {
    full_df <- NULL
    for (tp in timepoints) {
        outcomes <- get_cbcl_syndrome_scale(
            syndrome = syndrome,
            mh_p_cbcl,
            raw = FALSE,
            subjects = subs,
            t = tp
        )
        outcomes$"tp" <- tp
        if (is.null(full_df)) {
            full_df <- outcomes
        } else {
            full_df <- rbind(full_df, outcomes)
        }
    }
    return(full_df)
}



# make change score plots where you plot time on x-axis and visualize change
# by absolute t-score differences for 2 year and 3 year follow up

# Option 1
z <- get_syndrome_long("anxdep", tps, mc_d_subs)
z$"subjectkey" <- paste0("subject_", z$"subjectkey")
z_long <- dplyr::full_join(z, mc_d_cluster_df, by = "subjectkey")
z_long$"cluster" <- factor(z_long$"cluster")
anxdep <- ggplot(
    na.omit(z_long),
    aes(x = tp, y = cbcl_scr_syn_anxdep_t, colour = cluster, group = subjectkey)
) +
    geom_point() +
    geom_line() +
    facet_grid(cluster ~ .) +
    theme_bw()
ggsave("anxdep.png", anxdep)

z <- get_syndrome_long("withdep", tps, mc_d_subs)
z$"subjectkey" <- paste0("subject_", z$"subjectkey")
z_long <- dplyr::full_join(z, mc_d_cluster_df, by = "subjectkey")
z_long$"cluster" <- factor(z_long$"cluster")
withdep <- ggplot(
    na.omit(z_long),
    aes(x = tp, y = cbcl_scr_syn_withdep_t, colour = cluster, group = subjectkey)
) +
    geom_point() +
    geom_line() +
    facet_grid(cluster ~ .) +
    theme_bw()
ggsave("withdep.png", withdep)

z <- get_syndrome_long("aggressive", tps, mc_d_subs)
z$"subjectkey" <- paste0("subject_", z$"subjectkey")
z_long <- dplyr::full_join(z, mc_d_cluster_df, by = "subjectkey")
z_long$"cluster" <- factor(z_long$"cluster")
aggressive <- ggplot(
    na.omit(z_long),
    aes(x = tp, y = cbcl_scr_syn_aggressive_t, colour = cluster, group = subjectkey)
) +
    geom_point() +
    geom_line() +
    facet_grid(cluster ~ .) +
    theme_bw()
ggsave("aggressive.png", aggressive)



qq <- get_syndrome_long("anxdep", tps, mc_d_subs)
qq$"subjectkey" <- paste0("subject_", qq$"subjectkey")
qq_long <- dplyr::full_join(qq, mc_d_cluster_df, by = "subjectkey")
qq_long$"cluster" <- factor(qq_long$"cluster")
qq_long <- na.omit(qq_long)
for (subject in unique(qq_long$"subjectkey")) {
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 3, "cbcl_scr_syn_anxdep_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 3, "cbcl_scr_syn_anxdep_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_anxdep_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 2, "cbcl_scr_syn_anxdep_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 2, "cbcl_scr_syn_anxdep_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_anxdep_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 1, "cbcl_scr_syn_anxdep_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 1, "cbcl_scr_syn_anxdep_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_anxdep_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_anxdep_t"] <- 0
}
anxdep2 <- ggplot(
    na.omit(qq_long),
    aes(x = tp, y = cbcl_scr_syn_anxdep_t, colour = cluster, group = subjectkey)
) +
    geom_point() +
    geom_line() +
    facet_grid(cluster ~ .) +
    theme_bw()
ggsave("anxdep2.png", anxdep2)

qq <- get_syndrome_long("aggressive", tps, mc_d_subs)
qq$"subjectkey" <- paste0("subject_", qq$"subjectkey")
qq_long <- dplyr::full_join(qq, mc_d_cluster_df, by = "subjectkey")
qq_long$"cluster" <- factor(qq_long$"cluster")
qq_long <- na.omit(qq_long)
for (subject in unique(qq_long$"subjectkey")) {
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 3, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 3, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 2, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 2, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 1, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 1, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"] <- 0
}
aggressive2 <- ggplot(
    na.omit(qq_long),
    aes(x = tp, y = cbcl_scr_syn_aggressive_t, colour = cbcl_scr_syn_aggressive_t > 0, group = subjectkey)
) +
    geom_point() +
    geom_line() +
    facet_grid(cluster ~ .) +
    theme_bw()
ggsave("aggressive3.png", aggressive2)


qq <- get_syndrome_long("aggressive", tps, mc_d_subs)
qq$"subjectkey" <- paste0("subject_", qq$"subjectkey")
qq_long <- dplyr::full_join(qq, mc_d_cluster_df, by = "subjectkey")
qq_long$"cluster" <- factor(qq_long$"cluster")
for (subject in unique(qq_long$"subjectkey")) {
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 3, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 3, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 2, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 2, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 1, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 1, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"] <- 0
}
unique(qq_long$"subjectkey")
parent <- all_dls$"mtbi_train_data_lists"$"imp_1"[[24]]$"data"
summarize_dl(all_dls$"mtbi_train_data_lists"$"imp_1")
qq_long <- dplyr::full_join(qq_long, parent, by = "subjectkey")
aggressive4 <- ggplot(
    na.omit(qq_long),
    aes(x = tp, y = cbcl_scr_syn_aggressive_t, colour = parent_aggressive > 60, group = subjectkey)
) +
    geom_point() +
    geom_line() +
    facet_grid(cluster ~ .) +
    theme_bw()
aggressive4
ggsave("aggressive4.png", aggressive4)

qq <- get_syndrome_long("aggressive", tps, mc_d_subs)
qq$"subjectkey" <- paste0("subject_", qq$"subjectkey")
qq_long <- dplyr::full_join(qq, mc_d_cluster_df, by = "subjectkey")
qq_long$"cluster" <- factor(qq_long$"cluster")
for (subject in unique(qq_long$"subjectkey")) {
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 3, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 3, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 2, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 2, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 1, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 1, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"] <- 0
}
unique(qq_long$"subjectkey")
income <- all_dls$"mtbi_train_data_lists"$"imp_1"[[7]]$"data"
qq_long <- dplyr::full_join(qq_long, income, by = "subjectkey")
aggressive5 <- ggplot(
    na.omit(qq_long),
    aes(x = tp, y = cbcl_scr_syn_aggressive_t, colour = household_income, group = subjectkey)
) +
    geom_point() +
    geom_line() +
    facet_grid(cluster ~ .) +
    theme_bw()
aggressive5
ggsave("aggressive5.png", aggressive5)


qq <- get_syndrome_long("aggressive", tps, mc_d_subs)
qq$"subjectkey" <- paste0("subject_", qq$"subjectkey")
qq_long <- dplyr::full_join(qq, mc_d_cluster_df, by = "subjectkey")
qq_long$"cluster" <- factor(qq_long$"cluster")
for (subject in unique(qq_long$"subjectkey")) {
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 3, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 3, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 2, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 2, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 1, "cbcl_scr_syn_aggressive_t"] <-
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 1, "cbcl_scr_syn_aggressive_t"] -
        qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"]
    qq_long[qq_long$"subjectkey" == subject & qq_long$"tp" == 0, "cbcl_scr_syn_aggressive_t"] <- 0
}
unique(qq_long$"subjectkey")
data <- collapse_dl(all_dls$"mtbi_train_data_lists"$"imp_1")
qq_long <- dplyr::full_join(qq_long, data, by = "subjectkey")
aggressive6 <- ggplot(
    na.omit(qq_long),
    aes(x = tp, y = cbcl_scr_syn_aggressive_t, colour = sex, group = subjectkey)
) +
    geom_point() +
    geom_line() +
    facet_grid(cluster ~ .) +
    theme_bw()
aggressive6
ggsave("aggressive6.png", aggressive6)

for (tp in c(1, 2, 3)) {
    long_outcomes <- NULL
    for (syndrome in syndromes) {
        if (is.null(long_outcomes)) {
            long_outcomes <- get_cbcl_syndrome_scale(
                syndrome = syndrome,
                mh_p_cbcl,
                raw = FALSE,
                subjects = mtbi_train,
                t = tp
            )
        } else {
            long_outcomes <- dplyr::inner_join(
                long_outcomes,
                get_cbcl_syndrome_scale(
                    syndrome = syndrome,
                    mh_p_cbcl,
                    raw = FALSE,
                    subjects = mtbi_train,
                    t = tp
                ),
                by = "subjectkey"
            )
        }
    }
    long_outcomes <- dplyr::inner_join(
        long_outcomes,
        get_sds_total_probs(
            ph_p_sds,
            mtbi_train,
            t = tp
        ),
        by = "subjectkey"
    )
    long_outcomes$"subjectkey" <- paste0("subject_", long_outcomes$"subjectkey")
    colnames(long_outcomes) <- c(
        "subjectkey",
        paste0("cbcl_", syndromes),
        "sds_sleep"
    )
    baseline_outcomes <- collapse_dl(oom_list_m3)
    d_outcomes <- NULL
    for (outcome in colnames(baseline_outcomes[-1])) {
        t0 <- dplyr::select(baseline_outcomes, "subjectkey", outcome)
        tn <- dplyr::select(long_outcomes, "subjectkey", outcome)
        colnames(t0) <- c("subjectkey", paste0(outcome, "_0"))
        colnames(tn) <- c("subjectkey", paste0(outcome, "_", tp))
        both_t <- dplyr::inner_join(t0, tn, by = "subjectkey")
        both_t[, 4] <- both_t[, 3] - both_t[, 2]
        colnames(both_t)[4] <- paste0("d_", outcome)
        both_t <- both_t[, c(1, 4)]
        if (is.null(d_outcomes)) {
            d_outcomes <- both_t
        } else {
            d_outcomes <- dplyr::full_join(d_outcomes, both_t, by = "subjectkey")
        }
    }
    mtbi_mc_a <- mtbi_rep[1, ]
    mtbi_mc_a <- get_cluster_df(mtbi_mc_a)
    mtbi_mc_a <- dplyr::full_join(
        mtbi_mc_a,
        d_outcomes,
        by = "subjectkey"
    )
    mtbi_mc_a$"cluster" <- factor(mtbi_mc_a$"cluster")
    d_plots <- list()
    for (outcome in colnames(d_outcomes)[-1]) {
        plot <- mtbi_mc_a |>
            ggplot(
                aes(
                    x = cluster,
                    y = !!sym(outcome),
                    colour = cluster
                )
            ) +
            geom_violin(alpha = 0.4) +
            geom_jitter(width = 0.2, height = 0.2) +
            stat_summary(
                fun = "mean",
                geom = "point",
                colour = "black",
                size = 2
            ) +
            labs(
                x = "Cluster",
                y = gsub("d_", "Δ", outcome)
            ) +
            theme_bw() +
            theme(
                legend.position = "none"
            )
        d_plots[[length(d_plots) + 1]] <- plot
    }
    d_plots <- d_plots |>
        wrap_plots() +
        plot_annotation(
            paste0("CBCL/SDS Outcomes, ", tp, "-year Follow-Up Minus Baseline"),
            theme = theme(plot.title=element_text(hjust=0.5))
        )
    # Looks like cluster 1 has the higher variance, indicating potential for intervention?
    ggsave(
        plot = d_plots,
        filename = fig_path(
            paste0("mtbi_mc_a_outcomes_t", tp, "_plots.png"),
            TRUE
        ),
        width = 8,
        height = 8,
        dpi = 120
    )
}

full_df <- NULL
for (tp in c(0, 1, 2, 3, 4)) {
    long_outcomes <- NULL
    for (syndrome in syndromes) {
        if (is.null(long_outcomes)) {
            long_outcomes <- get_cbcl_syndrome_scale(
                syndrome = syndrome,
                mh_p_cbcl,
                raw = FALSE,
                subjects = mtbi_train,
                t = tp
            )
            colnames(long_outcomes) <- c("subjectkey", syndrome)
        } else {
            new_df <- get_cbcl_syndrome_scale(
                syndrome = syndrome,
                mh_p_cbcl,
                raw = FALSE,
                subjects = mtbi_train,
                t = tp
            )
            colnames(new_df) <- c("subjectkey", syndrome)
            long_outcomes <- dplyr::full_join(
                long_outcomes,
                new_df,
                by = "subjectkey"
            )
        }
    }
    long_outcomes$"tp" <- tp
    if (is.null(full_df)) {
        full_df <- long_outcomes
    } else {
        full_df <- rbind(full_df, long_outcomes)
    }
}
full_df$"subjectkey" <- paste0("subject_", full_df$"subjectkey")
mtbi_mc_a <- mtbi_rep[1, ]
mtbi_mc_a <- get_cluster_df(mtbi_mc_a)
mtbi_mc_a$"cluster" <- factor(mtbi_mc_a$"cluster")
full_df <- dplyr::full_join(full_df, mtbi_mc_a, by = "subjectkey")
full_df$"tp" <- factor(full_df$"tp")
full_df |>
    dplyr::filter(cluster == 1) |>
    na.omit() |>
    ggplot(
        aes(
            x = tp,
            y = aggressive,
            group = subjectkey,
            colour = cluster
        )
    ) +
    geom_line() +
    geom_point() +
    theme_bw()

nrow(mtbi_mc_a)

head(mtbi_mc_a)

head(long_outcomes)
```


## A deeper dive at feature separation

```{r}
dl_df <- auto_plot(
    solutions_matrix_row = mtbi_mc_d_esm,
    data_list = all_dls$"mtbi_train_data_lists"$"imp_3",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_3",
    return_plots = FALSE
)

dl_df |>
    dplyr::filter(sex == 0) |>
    ggplot(
        aes(
            x = race,
            y = brain_volume,
            colour = race,
            group = race
        )
    ) +
    geom_point() +
    theme_bw() +
    facet_grid(household_income ~ .)

dl_df$"household_income" <- factor(dl_df$"household_income")
dl_df$"sex" <- factor(dl_df$"sex")

dl_df |>
    ggplot(
        aes(
            x = household_income,
            y = cbcl_aggressive,
            colour = race,
            group = interaction(race, household_income)
        )
    ) +
    geom_violin(position = position_dodge(width = 0.75)) +
    geom_jitter(
        position = position_jitterdodge(
            jitter.width = 0,
            jitter.height = 0.5
        ),
    ) +
    theme_bw()

dl_df |>
    ggplot(
        aes(
            x = sex,
            y = cbcl_aggressive,
            colour = race,
            group = interaction(race, sex)
        )
    ) +
    geom_boxplot(position = position_dodge(width = 0.75), width = 0.4) +
    geom_jitter(
        position = position_jitterdodge(
            jitter.width = 0,
            jitter.height = 0.5
        ),
    ) +
    theme_bw()
```



