# metaSNF of Baseline mTBI Subjects

In this chapter, I use the metaSNF package to generate and characterize meta clusters of the extracted data.

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)
library(ggplot2)
library(patchwork)
library(xtable)
library(compute.es)
library(dplyr)
library(fastDummies)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subjects <- read_csv(sub_path("2024_08_17_mtbi_subjects.csv"))
mtbi_train_subjects <- read_csv(sub_path("2024_08_17_mtbi_train_subjects.csv"))
mtbi_test_subjects <- read_csv(sub_path("2024_08_17_mtbi_test_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2024_08_17_uninjured_subjects.csv"))
```


## Importing data


```{r}
# CHECKPOINT
all_dls <- list.load(input_path("2024_08_17_all_dls.rds"))
```


## Generating custom distance measures


```{r}
# CHECKPOINT
###############################################################################
# 2. Add standard normalized variations to the distance metrics list (also
# achievable through toggling automatic_standard_normalize parameter in
# `batch_snf`)
###############################################################################
my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

summarize_dml(my_distance_metrics)
```


## Generating the settings matrix


```{r}
mtbi_settings_matrix <- generate_settings_matrix(
    all_dls$"mtbi_train_data_lists"$"imp_1",
    nrow = 200,
    seed = 42,
    distance_metrics_list = my_distance_metrics
)

write_csv(mtbi_settings_matrix, proc_path("mtbi_settings_matrix.csv", TRUE))

mtbi_settings_matrix <- read_csv(
    proc_path("2024_08_17_mtbi_settings_matrix.csv")
)
```


## Running SNF for each of the imputations


```{r}
mtbi_train_dls <- c(
    all_dls$"mtbi_train_data_lists",
    all_dls$"mtbi_pooled_data_lists"
)

names(mtbi_train_dls) <- c(paste0("imp_", 1:5), paste0("pooled_imp_", 1:5))

mtbi_train_solutions_matrices <- lapply(
    mtbi_train_dls,
    function(imputed_dl) {
        summarize_dl(imputed_dl)
        solutions_matrix <- batch_snf(
            data_list = imputed_dl,
            settings_matrix = mtbi_settings_matrix,
            distance_metrics_list = my_distance_metrics,
            processes = "max"
        )
    }
)

#
list.save(
    mtbi_train_solutions_matrices,
    input_path("mtbi_train_solutions_matrices.rds", TRUE)
)
#
mtbi_train_solutions_matrices <- list.load(
    input_path("2024_08_17_mtbi_train_solutions_matrices.rds")
)
#
mtbi_sm <- do.call(
    "rbind",
    mtbi_train_solutions_matrices
)
#
write_csv(data.frame(mtbi_sm), proc_path("mtbi_sm.csv", TRUE))
#
mtbi_ari <- calc_aris(mtbi_sm, processes = "max")
#
write_csv(data.frame(mtbi_ari), proc_path("mtbi_ari.csv", TRUE))
#
mtbi_ari_order <- get_matrix_order(mtbi_ari)
#
write_csv(data.frame(mtbi_ari_order), proc_path("mtbi_ari_order.csv", TRUE))
```

## Re-importing data

```{r}
# CHECKPOINT
mtbi_sm <- read_csv(proc_path("2024_08_17_mtbi_sm.csv"))

mtbi_ari <- as.matrix(read_csv(proc_path("2024_08_17_mtbi_ari.csv")))

mtbi_ari_order <- unlist(read_csv(proc_path("2024_08_17_mtbi_ari_order.csv")))
names(mtbi_ari_order) <- NULL
```

## Calculating associations between cluster solutions and features

```{r}
imputation_labels <- data.frame(
    "imputation" = c(
        rep("m1", 200),
        rep("m2", 200),
        rep("m3", 200),
        rep("m4", 200),
        rep("m5", 200),
        rep("pm1", 200),
        rep("pm2", 200),
        rep("pm3", 200),
        rep("pm4", 200),
        rep("pm5", 200)
    ),
    "pooled" = c(
        rep("no", 1000),
        rep("yes", 1000)
    )
)

mtbi_sm_l <- cbind(mtbi_sm, imputation_labels)

mtbi_esm_m1 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "m1", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_1",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_1",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_m2 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "m2", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_2",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_2",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_m3 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "m3", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_3",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_3",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_m4 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "m4", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_4",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_4",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_m5 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "m5", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_5",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_5",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_pm1 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "pm1", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_1",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_1",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_pm2 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "pm2", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_2",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_2",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_pm3 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "pm3", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_3",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_3",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_pm4 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "pm4", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_4",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_4",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_pm5 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "pm5", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_5",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_5",
    min_pval = 1e-10,
    processes = "max"
)

mtbi_esm <- dplyr::bind_rows(
    mtbi_esm_m1,
    mtbi_esm_m2,
    mtbi_esm_m3,
    mtbi_esm_m4,
    mtbi_esm_m5,
    mtbi_esm_pm1,
    mtbi_esm_pm2,
    mtbi_esm_pm3,
    mtbi_esm_pm4,
    mtbi_esm_pm5
)

mtbi_esm$"impairment_separation" <- -log10(mtbi_esm$"mean_pval")

write_csv(mtbi_esm, proc_path("mtbi_esm.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_esm <- read_csv(proc_path("2024_08_17_mtbi_esm.csv"))
```


## Identifying and visualizing meta clusters


```{r}
base_ari_hm <- adjusted_rand_index_heatmap(
    mtbi_ari,
    order = mtbi_ari_order
)

shiny_annotator(base_ari_hm)

mtbi_split_vec <- c(
    190,
    514,
    646,
    845,
    1192,
    1442,
    1474,
    1710
)

write_csv(data.frame(mtbi_split_vec), proc_path("mtbi_split_vec.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_split_vec <- read_csv(proc_path("2024_08_18_mtbi_split_vec.csv")) |>
    unlist() |>
    as.numeric()
```

```{r}
divergent_colours <- function(column)  {
    values <- unique(column)
    colours <- RColorBrewer::brewer.pal(n = length(values), name = "Set3")
    names(colours) <- values
    return(colours)
}

full_mtbi_ari_hm <- adjusted_rand_index_heatmap(
    aris = mtbi_ari,
    order = mtbi_ari_order,
    data = mtbi_esm,
    min_colour = "black",
    split_vector = mtbi_split_vec,
    top_hm = list(
        "Impairment Separation" = "impairment_separation"
    ),
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    left_hm = list(
        "Pooled" = "pooled",
        "Imputation" = "imputation"
    ),
    annotation_colours = list(
        "Impairment Separation" = colour_scale(
            mtbi_esm$"impairment_separation",
            min_colour = "gray7",
            max_colour = "limegreen"
        ),
        "Imputation" = divergent_colours(mtbi_esm$"imputation"),
        "Pooled" = c(
            "yes" = "orange",
            "no" = "purple"
        )
    )
)
full_mtbi_ari_hm

save_heatmap(
    heatmap = full_mtbi_ari_hm,
    path = fig_path("full_mtbi_ari_hm.png", TRUE),
    width = 950,
    height = 900,
    res = 100
)

# Another heatmap without the imputation-related columns
lite_mtbi_ari_hm <- adjusted_rand_index_heatmap(
    aris = mtbi_ari,
    order = mtbi_ari_order,
    data = mtbi_esm,
    min_colour = "black",
    split_vector = mtbi_split_vec,
    top_hm = list(
        "Impairment Separation" = "impairment_separation"
    ),
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    annotation_colours = list(
        "Impairment Separation" = colour_scale(
            mtbi_esm$"impairment_separation",
            min_colour = "gray7",
            max_colour = "limegreen"
        )
    )
)

save_heatmap(
    heatmap = lite_mtbi_ari_hm,
    path = fig_path("lite_mtbi_ari_hm.png", TRUE),
    width = 900,
    height = 700,
    res = 100
)
```

When picking out representative solutions, I'd like to preferentially go for solutions that derived from solo rather than pooled imputations, as those solutions have values for all features.

```{r}
# Function to try to lean on mTBI-including solutions when possible.
# This function will pick from solo solutions unless over 70% of the meta
# cluster is pooled.
restrict_fn <- function(x, threshold = 0.3) {
    x_solo_ind <- x$"imputation" %in% c("m1", "m2", "m3", "m4", "m5")
    x_pool_ind <- x$"imputation" %in% c("pm1", "pm2", "pm3", "pm4", "pm5")
    x_solo <- x[x_solo_ind, ]
    x_pool <- x[x_pool_ind, ]
    frac_solo <- nrow(x_solo) / (nrow(x_solo) + nrow(x_pool))
    if (frac_solo < threshold) {
        return(x[x_pool_ind, ])
    } else {
        return(x[x_solo_ind, ])
    }
}

mtbi_rep_solutions <- get_representative_solutions(
    mtbi_ari,
    split_vector = mtbi_split_vec,
    order = mtbi_ari_order,
    filter_fn = restrict_fn,
    mtbi_esm
)

mtbi_rep_solutions

# Based on the heatmap, we'll remove B, E, H, K (unstable meta clusters)
mtbi_rep_solutions <- dplyr::filter(
    mtbi_rep_solutions,
    !label %in% c("E", "G", "I")
)

write_csv(mtbi_rep_solutions, proc_path("mtbi_rep_solutions.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_rep_solutions <- read_csv(proc_path("2024_08_18_mtbi_rep_solutions.csv"))
```

```{r}
mtbi_manhattan <- mc_manhattan_plot(
    mtbi_rep_solutions,
    data_list = all_dls$"mtbi_train_data_lists"$"imp_2",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_2",
    domain_colours = c(
        "AS" = "#85929e",
        "D" = "#bb8fce",
        "N" = "#e59866",
        "MH" = "#7fb3d5",
        "P" = "#52be80",
        "S" = "#d98880",
        "B" = "#ff3131"
    )
)
mtbi_manhattan

ggsave(
    plot = mtbi_manhattan,
    filename = fig_path("mtbi_manhattan.png", TRUE),
    width = 18,
    height = 14,
    dpi = 120
)

# The most robust solution
mtbi_mc_d_esm <- mtbi_rep_solutions |>
    dplyr::filter(label == "D")

write_csv(mtbi_mc_d_esm, proc_path("mtbi_mc_d_esm.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_mc_d_esm <- read_csv(proc_path("2024_08_18_mtbi_mc_d_esm.csv"))
```

```{r}
# Feature plot generation
plot_list <- auto_plot(
    solutions_matrix_row = mtbi_mc_d_esm,
    data_list = all_dls$"mtbi_train_data_lists"$"imp_2",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_2",
    save = fig_path("mtbi_mc_d", TRUE)
)

# No save version:
plot_list <- auto_plot(
    solutions_matrix_row = mtbi_mc_d_esm,
    data_list = all_dls$"mtbi_train_data_lists"$"imp_2",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_2"
)

all_plots <- wrap_plots(plot_list)

# Good enough as a snapshot
ggsave(
    fig_path("mtbi_mc_d_all_plots.png", TRUE),
    all_plots,
    width = 45,
    height = 30,
    dpi = 50
)
```


## Characterization of meta cluster D representative solution

### NMI


```{r}
nmis <- batch_nmi(
    all_dls$"mtbi_train_data_lists"$"imp_2",
    mtbi_mc_d_esm,
    distance_metrics_list = my_distance_metrics
)

nmi_order <- sort(
    nmis$"row_id_81",
    decreasing = TRUE,
    index.return = TRUE
)

ordered_nmis <- nmis[nmi_order$ix, ]

ordered_nmis$"nmi_rank" <- rank(
    -ordered_nmis$"row_id_81",
    ties.method = "min"
)
```


### p-values


```{r}
pvals <- get_pvals(
    mtbi_mc_d_esm,
    keep_summaries = FALSE
)
pvals <- data.frame(
    "feature" = gsub("_pval", "", names(pvals)),
    "neg_log_pval" = -log10(as.numeric(unlist(pvals)))
)
pvals <- pvals[-1, ]
pvals_order <- sort(
    pvals$"neg_log_pval",
    decreasing = TRUE,
    index.return = TRUE
)
ordered_pvals <- pvals[pvals_order$ix, ]
ordered_pvals <- dplyr::filter(
    ordered_pvals,
    !grepl("^cbcl|^sds", feature)
)

ordered_pvals$"pval_rank" <- rank(
    -ordered_pvals$"neg_log_pval",
    ties.method = "min"
)
```


### Joint rank


```{r}
mtbi_mc_d_nmi_v_pval <- dplyr::full_join(
    ordered_nmis,
    ordered_pvals,
    by = "feature"
)

domain_df <- dl_variable_summary(all_dls$"mtbi_train_data_lists"$"imp_2") |>
    dplyr::select(name, domain) |>
    dplyr::rename("feature" = "name")

mtbi_mc_d_nmi_v_pval <- mtbi_mc_d_nmi_v_pval |>
    dplyr::inner_join(domain_df, by = "feature")

mtbi_mc_d_nmi_v_pval$"joint_rank" <- rank(
    mtbi_mc_d_nmi_v_pval$"nmi_rank" + mtbi_mc_d_nmi_v_pval$"pval_rank",
    ties.method = "min"
)

joint_order <- sort(
    mtbi_mc_d_nmi_v_pval$"joint_rank",
    decreasing = FALSE,
    index.return = TRUE
)

mtbi_mc_d_nmi_v_pval_rank <- mtbi_mc_d_nmi_v_pval[joint_order$ix, ]

mtbi_mc_d_nmi_v_pval_rank <- mtbi_mc_d_nmi_v_pval_rank |>
    dplyr::rename("nmi" = "row_id_81")

mtbi_mc_d_nmi_v_pval_rank <- mtbi_mc_d_nmi_v_pval_rank |>
    dplyr::select(
        feature,
        domain,
        nmi,
        nmi_rank,
        neg_log_pval,
        pval_rank,
        joint_rank
    )

write_csv(
    mtbi_mc_d_nmi_v_pval_rank,
    proc_path("mtbi_mc_d_nmi_v_pval_rank.csv", TRUE)
)

data.frame(mtbi_mc_d_nmi_v_pval_rank)

# Latex table
xtable(data.frame(mtbi_mc_d_nmi_v_pval_rank))
```

                  feature domain          nmi nmi_rank neg_log_pval pval_rank joint_rank
1                     sex      D 0.2985873838        1   10.0000000         1          1
2            brain_volume      N 0.2217644212        2   10.0000000         1          2
3             cortical_sa      N 0.2032265446        3   10.0000000         1          3
4        household_income      D 0.1451227069        4   10.0000000         1          4
5       pubertal_status_p      D 0.1085711605        5   10.0000000         1          5
6      programs_this_year      P 0.0931335524        6   10.0000000         1          6
8     non_school_programs      P 0.0747381192        8   10.0000000         1          7
10         parent_somatic      P 0.0662651869       10   10.0000000         1          8
11     weekday_screentime      P 0.0632396705       11   10.0000000         1          9
7                    race      D 0.0774583581        7    8.1140944        13         10
13         parent_depress      P 0.0477022183       13    8.8134915        11         11
14         parent_thought      P 0.0466989872       14    9.7334076        10         11
17          parent_anxdep      P 0.0425659370       17    8.1884295        12         13
12    private_instruction      P 0.0584871743       12    6.1573351        18         14
15      parent_antisocial      P 0.0452306056       15    7.9663295        15         14
18         fmri_cort_cors      N 0.0417425220       18    7.3756235        16         16
20      parent_aggressive      P 0.0393519079       20    8.0811853        14         16
9      weekend_screentime      P 0.0721706141        9    3.1658276        29         18
22       parent_anxdisord      P 0.0361093706       22    6.7082660        17         19
16          exercise_time      P 0.0443959675       16    3.9952204        25         20
19         family_fight_p      P 0.0401472888       19    4.6992767        22         20
25     cortical_thickness      N 0.0298916659       25    5.1290506        20         22
21 fmri_cort_subcort_cors      N 0.0386767628       21    3.7192756        26         23
23        parent_avoidant      P 0.0336032086       23    4.2825992        24         23
28     parent_hyperactive      P 0.0279453604       28    5.1692320        19         23
27       parent_attention      P 0.0284097681       27    4.9589901        21         26
31       parent_withdrawn      P 0.0265018835       31    4.3490583        23         27
29           helps_hurt_p      P 0.0274069997       29    3.2958551        28         28
30          considerate_y      P 0.0273993871       30    3.4709959        27         28
26           major_wm_ndi      N 0.0291007627       26    2.9070615        33         30
32           helps_hurt_y      P 0.0249872491       32    2.9882885        30         31
33              helpful_p      P 0.0235618961       33    2.9102231        32         32
34           family_hit_p      P 0.0234408323       34    2.3935444        36         33
37         family_outdo_p      P 0.0220122681       37    2.6341984        34         34
41       parent_intrusive      P 0.0201717654       41    2.9516614        31         35
35       headache_history     MH 0.0230578288       35    2.2107514        40         36
40               mtbi_loc     AS 0.0206061192       40    2.6059292        35         36
38      family_peaceful_y      P 0.0210522209       38    1.9503586        43         38
39      family_peaceful_p      P 0.0209353039       39    2.0765066        42         38
24          parent_perstr      P 0.0320081639       24    0.7881771        58         40
44          considerate_p      P 0.0183202410       44    2.3796597        38         40
45    pericortical_wm_ndi      N 0.0173340830       45    2.3815893        37         40
46        family_temper_p      P 0.0166428482       46    2.2273051        39         43
43                    age      D 0.0187117914       43    1.8421893        45         44
47     family_criticize_p      P 0.0166052825       47    2.1272289        41         44
48         family_outdo_y      P 0.0152259886       48    1.9141442        44         46
42        school_programs      P 0.0192015706       42    1.3088942        51         47
36               mtbi_age      D 0.0224022854       36    0.7780819        59         48
49          family_yell_y      P 0.0141902908       49    1.7358388        47         49
50  same_sex_close_friend      P 0.0122821681       50    1.7657008        46         49
51     family_criticize_y      P 0.0119354939       51    1.4455761        49         51
52         family_angry_y      P 0.0114856671       52    1.5162493        48         51
55         family_angry_p      P 0.0107022991       55    1.4270912        50         53
54         family_throw_p      P 0.0107519383       54    1.0998158        53         54
58              helpful_y      P 0.0088325050       58    1.1753101        52         55
56      pubertal_status_y      D 0.0102883494       56    0.9463089        55         56
57          mtbi_mem_daze     AS 0.0093869868       57    0.9614631        54         56
53        same_sex_friend      P 0.0110132368       53    0.6322198        60         58
59         previous_mtbis     MH 0.0066352548       59    0.8213008        57         59
60         mtbi_mechanism     AS 0.0049358228       60    0.8696554        56         59
61         family_fight_y      P 0.0041952645       61    0.4873173        61         61
63         opp_sex_friend      P 0.0028603637       63    0.3800571        62         62
62         family_throw_y      P 0.0033013525       62    0.3367914        64         63
64        family_temper_y      P 0.0028015716       64    0.3633989        63         64
65           family_hit_y      P 0.0016846994       65    0.1883945        65         65
66   opp_sex_close_friend      P 0.0011695472       66    0.1606693        66         66
67          family_yell_p      P 0.0009946099       67    0.1322986        67         67

```{r}
# CHECKPOINT
mtbi_mc_d_nmi_v_pval_rank <- read_csv(
    proc_path("2024_08_20_mtbi_mc_d_nmi_v_pval_rank.csv")
)

sorted_features <- mtbi_mc_d_nmi_v_pval_rank$"feature"
```


### Correlation of NMI and p-value


```{r}
nmi_v_p_rho <- cor(
    mtbi_mc_d_nmi_v_pval_rank$"nmi_rank",
    mtbi_mc_d_nmi_v_pval_rank$"pval_rank",
    method = "spearman"
)

nmi_v_pval_plot <- mtbi_mc_d_nmi_v_pval_rank |>
    ggplot(
        aes(x = nmi_rank, y = pval_rank, label = feature, colour = domain)
    ) +
    geom_point(size = 2) + 
    scale_colour_manual(
        values = c(
            "AS" = "#85929e",
            "D" = "#bb8fce",
            "N" = "#e59866",
            "MH" = "#7fb3d5",
            "P" = "#52be80"
        )
    ) +
    theme_bw() +
    labs(x = "Rank by NMI", y = "Rank by Association p-value") +
    ggrepel::geom_text_repel(
        #vjust = 3,
        #hjust = 1,
        force = 1,
        max.overlaps = 20,
        size = 4
    ) +
    annotate(
        "text",
        x = 4,
        y = 50,
        size = 5,
        label = paste("Spearman's ρ =", round(nmi_v_p_rho, 2)),
        hjust = 0
    ) + 
    theme(text = element_text(size = 16))
nmi_v_pval_plot

ggsave(
    fig_path("nmi_v_pval_plot.png", TRUE),
    nmi_v_pval_plot,
    width = 12,
    height = 12
)
```


### Visualizing top 10 features


```{r}
names(plot_list)

ranked_plot_list <- plot_list[sorted_features]

ranked_all_plots <- wrap_plots(ranked_plot_list)

ggsave(
    fig_path("mtbi_mc_d_ranked_all_plots.png", TRUE),
    ranked_all_plots,
    width = 45,
    height = 30,
    dpi = 50
)

saveRDS(
    ranked_all_plots,
    file = fig_path("mtbi_mc_d_ranked_all_plots.rds", TRUE)
)

mtbi_mc_e_ranked_all_plots <- readRDS(
    fig_path("2024_08_21_mtbi_mc_d_ranked_all_plots.rds")
)

###############################################################################
# Building the top 12 plot list
###############################################################################

mc_d_top_pl <- ranked_plot_list[1:12]

names(mc_d_top_pl) <- sorted_features[1:12]

names(mc_d_top_pl)

#
mc_d_top_pl$"sex" <- mc_d_top_pl$"sex" +
    labs(fill = "Sex") +
    scale_fill_discrete(labels = c("F", "M"))
#
mc_d_top_pl$"brain_volume" <- mc_d_top_pl$"brain_volume" +
    labs(y = expression(paste("Brain Volume ", (mm^3))))
#
mc_d_top_pl$"cortical_sa" <- mc_d_top_pl$"cortical_sa" +
    labs(y = expression(paste("Cortical Area ", (mm^2))))
#
mc_d_top_pl$"household_income" <- mc_d_top_pl$"household_income" +
    labs(y = "Household Income")
#
mc_d_top_pl$"pubertal_status_p" <- mc_d_top_pl$"pubertal_status_p" +
    labs(y = "Pubertal Status - P")
#
mc_d_top_pl$"programs_this_year" <- mc_d_top_pl$"programs_this_year" +
    labs(y = "Total Activities this Year")
#
mc_d_top_pl$"non_school_programs" <- mc_d_top_pl$"non_school_programs" +
    labs(y = "Lifetime Extracurriculars")
#
mc_d_top_pl$"parent_somatic" <- mc_d_top_pl$"parent_somatic" +
    labs(y = "Parent Somatic Problems")
#
mc_d_top_pl$"weekday_screentime" <- mc_d_top_pl$"weekday_screentime" +
    labs(y = "Weekday Screentime")
#
mc_d_top_pl$"race" <- mc_d_top_pl$"race" +
    labs(fill = "Race") +
    scale_fill_discrete(labels = c("Black", "Hispanic", "Other", "White"))
#
mc_d_top_pl$"parent_depress" <- mc_d_top_pl$"parent_depress" +
    labs(y = "Parent Depression Problems")
#
mc_d_top_pl$"parent_thought" <- mc_d_top_pl$"parent_thought" +
    labs(y = "Parent Thought Problems")
#

mc_d_top_p <- wrap_plots(
    mc_d_top_pl,
) & labs(x = "Cluster") & theme(plot.margin = unit(c(0.5, 1.5, 0.5, 2), "cm"))
ggsave(
    fig_path("mtbi_mc_d_ranked_all_plots_12.png", TRUE),
    mc_d_top_p,
    width = 25,
    height = 15,
    dpi = 150
)


###############################################################################
# Outcomes
###############################################################################

mtbi_mc_d_esm_plot_df <- auto_plot(
    solutions_matrix_row = mtbi_mc_d_esm,
    data_list = all_dls$"mtbi_train_data_lists"$"imp_2",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_2",
    return_plots = FALSE
)

write_csv(mtbi_mc_d_esm_plot_df, proc_path("mtbi_mc_d_esm_plot_df.csv", TRUE))
```

```{r}
mtbi_mc_d_esm_plot_df <- read_csv(proc_path("2024_09_03_mtbi_mc_d_esm_plot_df.csv"))
```

```{r}
mtbi_mc_d_ranked_all_plots[[2]]

outcome_plot_list <- auto_plot(
    solutions_matrix_row = mtbi_mc_d_esm,
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_2"
)

names(outcome_plot_list)

clean_names <- c(
    "CBCL\nAnxious-Depressed",
    "CBCL\nWithdrawn-Depressed",
    "CBCL\nSomatic Problems",
    "CBCL\nSocial Problems",
    "CBCL\nThought Problems",
    "CBCL\nAttention Problems",
    "CBCL\nRule-breaking Problems",
    "CBCL\nAggression Problems",
    "SDS Total\nSleeping Problems"
)
for (i in seq_along(outcome_plot_list)) {
    outcome_plot_list[[i]] <- outcome_plot_list[[i]] +
        labs(y = clean_names[[i]], x = "Cluster")
}

outcome_plot_wrap <- wrap_plots(outcome_plot_list) &
    theme(plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), "cm"))

ggsave(
    fig_path("mtbi_mc_d_outcome_plot_wrap.png", TRUE),
    outcome_plot_wrap,
    width = 14,
    height = 14,
    dpi = 150
)
```

### Detailed cluster topologies

Can come back to this later.

```{r}
tstat <- function(d, n1, n2) {
    t <- d * sqrt((n1 * n2) / (n1 + n2))
    return(t)
}
pooled_sd <- function(n1, s1, n2, s2) {
    numerator <- ((n1 - 1) * (s1^2)) + ((n2 - 1) * (s2^2))
    denominator <- n1 + n2 - 2
    s <- sqrt(numerator / denominator)
    return(s)
}
cohens_d <- function(mean1, mean2, pooled_sd) {
    d <- (mean1 - mean2) / pooled_sd
    return(d)
}

calc_des <- function(x1, x2) {
    n1 <- length(x1)
    n2 <- length(x2)
    s1 <- sd(x1)
    s2 <- sd(x2)
    s <- pooled_sd(n1, s1, n2, s2)
    mean1 <- mean(x1)
    mean2 <- mean(x2)
    d <- cohens_d(mean1, mean2, s)
    d_full <- compute.es::des(
        d,
        n1,
        n2,
        verbose = FALSE
    )
    return(
        list(
            "es" = d_full$"d",
            "l" = d_full$"l.d",
            "u" = d_full$"u.d"
        )
    )
}

calc_propes <- function(x1, x2) {
    d_full <- compute.es::propes(
        mean(x1),
        mean(x2),
        length(x1),
        length(x2),
        verbose = FALSE
    )
    return(
        list(
            "es" = d_full$"OR",
            "l" = d_full$"l.or",
            "u" = d_full$"u.or"
        )
    )
}

dummy_non_numeric <- function(df) {
    to_dummy <- colnames(df)[!sapply(df, is.numeric)]
    dummied_df <- dummy_cols(
        df,
        select_columns = to_dummy,
        remove_selected_columns = TRUE
    )
    return(dummied_df)
}

is_binary <- function(x) {
    return(isTRUE(all.equal(sort(unique(x)), c(0, 1))))
}

topologizer <- function(df) {
    df <- data.frame(df)
    df <- dummy_non_numeric(dplyr::select(df, -"subjectkey"))
    summary_df <- data.frame(
        "feature" = as.character(),
        "type" = as.character(),
        "summary" = as.character(),
        "c1_mean" = as.numeric(),
        "c2_mean" = as.numeric(),
        "c3_mean" = as.numeric(),
        "c1_c2_es" = as.numeric(),
        "c1_c2_l" = as.numeric(),
        "c1_c2_u" = as.numeric(),
        "c1_c3_es" = as.numeric(),
        "c1_c3_l" = as.numeric(),
        "c1_c3_u" = as.numeric(),
        "c2_c3_es" = as.numeric(),
        "c2_c3_l" = as.numeric(),
        "c2_c3_u" = as.numeric()
    )
    c1 <- df[df$"cluster" == 1, ]
    c2 <- df[df$"cluster" == 2, ]
    c3 <- df[df$"cluster" == 3, ]
    features <- df |>
        dplyr::select(-"cluster") |>
        colnames()
    ###########################################################################
    # Check if features are binary (unique values are 0 and 1) or not
    ###########################################################################
    for (feature in features) {
        f1 <- c1[, feature]
        f2 <- c2[, feature]
        f3 <- c3[, feature]
        means <- c("1" = mean(f1), "2" = mean(f2), "3" = mean(f3))
        full_summary <- paste(
            names(sort(means, decreasing = TRUE)),
            collapse = " > "
        )
        if (is_binary(df[, feature])) {
            sum_1_v_2 <- calc_propes(f1, f2)
            sum_1_v_3 <- calc_propes(f1, f3)
            sum_2_v_3 <- calc_propes(f2, f3)
            type <- "or"
        } else {
            sum_1_v_2 <- calc_des(f1, f2)
            sum_1_v_3 <- calc_des(f1, f3)
            sum_2_v_3 <- calc_des(f2, f3)
            type <- "d"
        }
        summary_df <- rbind(
            summary_df,
            data.frame(
                "feature" = feature,
                "summary" = full_summary,
                "c1" = signif(mean(f1), 2),
                "c2" = signif(mean(f2), 2),
                "c3" = signif(mean(f3), 2),
                "es" = type,
                "c12_es" = sum_1_v_2$"es",
                "c12_l" = sum_1_v_2$"l",
                "c12_u" = sum_1_v_2$"u",
                "c13_es" = sum_1_v_3$"es",
                "c13_l" = sum_1_v_3$"l",
                "c13_u" = sum_1_v_3$"u",
                "c23_es" = sum_2_v_3$"es",
                "c23_l" = sum_2_v_3$"l",
                "c23_u" = sum_2_v_3$"u"
            )
        )
    }
    return(summary_df)
}
```


```{r}
d_df <- read_csv(proc_path("2024_09_03_mtbi_mc_d_esm_plot_df.csv"))

topology_df <- topologizer(d_df)

mtbi_mc_d_outcome_tops <- topology_df |> dplyr::filter(grepl("cbcl|sds", feature))
mtbi_mc_d_input_tops <- topology_df |> dplyr::filter(!grepl("cbcl|sds", feature))

joint_ranks <- mtbi_mc_d_nmi_v_pval_rank |>
    dplyr::select(feature, joint_rank)
joint_ranks <- rbind(
    joint_ranks,
    data.frame(
        feature = c(
            "race_black",
            "race_white",
            "race_hispanic",
            "race_other"
        ),
        joint_rank = joint_ranks[joint_ranks$"feature" == "race", "joint_rank"]
    )
)
joint_ranks <- rbind(
    joint_ranks,
    data.frame(
        feature = c(
            "mtbi_mechanism_fall_hit",
            "mtbi_mechanism_hosp_er",
            "mtbi_mechanism_multi",
            "mtbi_mechanism_other_loc",
            "mtbi_mechanism_vehicle",
            "mtbi_mechanism_violent"
        ),
        joint_rank = joint_ranks[joint_ranks$"feature" == "mtbi_mechanism", "joint_rank"]
    )
)
joint_ranks <- dplyr::filter(joint_ranks, !feature %in% c("mtbi_mechanism", "race"))

mtbi_mc_d_input_tops <- dplyr::inner_join(mtbi_mc_d_input_tops, joint_ranks, by = "feature")

mtbi_mc_d_input_tops <- dplyr::arrange(mtbi_mc_d_input_tops, joint_rank)

write_csv(mtbi_mc_d_input_tops, proc_path("mtbi_mc_d_input_tops.csv", TRUE))
write_csv(mtbi_mc_d_outcome_tops, proc_path("mtbi_mc_d_outcome_tops.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_mc_d_input_tops <- read_csv(proc_path("2024_09_11_mtbi_mc_d_input_tops.csv"))
mtbi_mc_d_outcome_tops <- read_csv(proc_path("2024_09_11_mtbi_mc_d_outcome_tops.csv"))
```

# Label propagation

## Attempt 1: Propagation with the full data list

A label propagation attempt using the full data list.

```{r}
# CHECKPOINT
# The data list that generated the top solution
train_data_list_m2 <- all_dls$"mtbi_train_data_lists"$"imp_2"
train_oom_list_m2 <- all_dls$"mtbi_train_oom_lists"$"imp_2"

# The first test data set, for example
test_data_list_m1 <- all_dls$"mtbi_test_data_lists"$"imp_1"
test_data_list_m2 <- all_dls$"mtbi_test_data_lists"$"imp_2"
test_data_list_m3 <- all_dls$"mtbi_test_data_lists"$"imp_3"
test_data_list_m4 <- all_dls$"mtbi_test_data_lists"$"imp_4"
test_data_list_m5 <- all_dls$"mtbi_test_data_lists"$"imp_5"

test_oom_list_m1 <- all_dls$"mtbi_test_oom_lists"$"imp_1"
test_oom_list_m2 <- all_dls$"mtbi_test_oom_lists"$"imp_2"
test_oom_list_m3 <- all_dls$"mtbi_test_oom_lists"$"imp_3"
test_oom_list_m4 <- all_dls$"mtbi_test_oom_lists"$"imp_4"
test_oom_list_m5 <- all_dls$"mtbi_test_oom_lists"$"imp_5"
```

```{r}
full_data_list_1 <- merge_data_lists(train_data_list_m2, test_data_list_m1)
full_data_list_2 <- merge_data_lists(train_data_list_m2, test_data_list_m2)
full_data_list_3 <- merge_data_lists(train_data_list_m2, test_data_list_m3)
full_data_list_4 <- merge_data_lists(train_data_list_m2, test_data_list_m4)
full_data_list_5 <- merge_data_lists(train_data_list_m2, test_data_list_m5)

full_oom_list_1 <- merge_data_lists(train_oom_list_m2, test_oom_list_m1)
full_oom_list_2 <- merge_data_lists(train_oom_list_m2, test_oom_list_m2)
full_oom_list_3 <- merge_data_lists(train_oom_list_m2, test_oom_list_m3)
full_oom_list_4 <- merge_data_lists(train_oom_list_m2, test_oom_list_m4)
full_oom_list_5 <- merge_data_lists(train_oom_list_m2, test_oom_list_m5)

list.save(full_data_list_1, input_path("mtbi_full_data_list_1.rds", TRUE))
list.save(full_data_list_2, input_path("mtbi_full_data_list_2.rds", TRUE))
list.save(full_data_list_3, input_path("mtbi_full_data_list_3.rds", TRUE))
list.save(full_data_list_4, input_path("mtbi_full_data_list_4.rds", TRUE))
list.save(full_data_list_5, input_path("mtbi_full_data_list_5.rds", TRUE))

list.save(full_oom_list_1, input_path("mtbi_full_oom_list_1.rds", TRUE))
list.save(full_oom_list_2, input_path("mtbi_full_oom_list_2.rds", TRUE))
list.save(full_oom_list_3, input_path("mtbi_full_oom_list_3.rds", TRUE))
list.save(full_oom_list_4, input_path("mtbi_full_oom_list_4.rds", TRUE))
list.save(full_oom_list_5, input_path("mtbi_full_oom_list_5.rds", TRUE))
```

```{r}
# CHECKPOINT
full_data_list_1 <- list.load(input_path("2024_08_22_mtbi_full_data_list_1.rds"))
full_data_list_2 <- list.load(input_path("2024_08_22_mtbi_full_data_list_2.rds"))
full_data_list_3 <- list.load(input_path("2024_08_22_mtbi_full_data_list_3.rds"))
full_data_list_4 <- list.load(input_path("2024_08_22_mtbi_full_data_list_4.rds"))
full_data_list_5 <- list.load(input_path("2024_08_22_mtbi_full_data_list_5.rds"))

full_oom_list_1 <- list.load(input_path("2024_08_22_mtbi_full_oom_list_1.rds"))
full_oom_list_2 <- list.load(input_path("2024_08_22_mtbi_full_oom_list_2.rds"))
full_oom_list_3 <- list.load(input_path("2024_08_22_mtbi_full_oom_list_3.rds"))
full_oom_list_4 <- list.load(input_path("2024_08_22_mtbi_full_oom_list_4.rds"))
full_oom_list_5 <- list.load(input_path("2024_08_22_mtbi_full_oom_list_5.rds"))
```

## Mixing in the Validation Set

```{r}
my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

mtbi_settings_matrix <- read_csv(
    proc_path("2024_08_17_mtbi_settings_matrix.csv")
)

mtbi_full_sm <- batch_snf(
    data_list = full_data_list_1,
    settings_matrix = mtbi_settings_matrix,
    distance_metrics_list = my_distance_metrics,
    processes = "max"
)
write_csv(mtbi_full_sm, proc_path("mtbi_full_sm.csv", TRUE))

mtbi_full_sm <- read_csv(proc_path("2024_08_30_mtbi_full_sm.csv"))

mtbi_full_esm <- extend_solutions(
    mtbi_full_sm,
    data_list = mtbi_full_data_list_1,
    target_list = mtbi_full_oom_list_1,
    min_pval = 1e-10,
    processes = "max"
)
write_csv(mtbi_full_esm, proc_path("mtbi_full_esm.csv", TRUE))

mtbi_full_ari <- calc_aris(mtbi_full_esm, processes = "max")
mtbi_full_order <- get_matrix_order(mtbi_full_ari)

write_csv(data.frame(mtbi_full_ari), proc_path("mtbi_full_ari.csv", TRUE))
write_csv(data.frame(mtbi_full_order), proc_path("mtbi_full_order.csv", TRUE))

mtbi_full_esm$"impairment_separation" <- -log10(mtbi_full_esm$"mean_pval")

write_csv(mtbi_full_esm, proc_path("mtbi_full_esm.csv", TRUE))

```

```{r}
mtbi_full_esm <- read_csv(proc_path("2024_09_12_mtbi_full_esm.csv"))
mtbi_full_ari <- read_csv(proc_path("2024_09_03_mtbi_full_ari.csv"))
mtbi_full_order <- unlist(read_csv(proc_path("2024_09_03_mtbi_full_order.csv")))
```

What does the full 3-cluster solution look like?

```{r}
# The full solutions with 3 clusters that have outcome separation
mtbi_full_3c <- mtbi_full_esm |> dplyr::filter(nclust == 3)

max_sep <- max(mtbi_full_3c$"impairment_separation")

mtbi_full_top_3c <- mtbi_full_3c |>
    dplyr::filter(impairment_separation == max_sep)

mtbi_full_top_3c$"label" <- "Full Top 3C Solution"
```

```{r}
cluster_label_swap <- function(solutions_matrix, c_a, c_b) {
    swapped_sm <- dplyr::mutate(
        solutions_matrix,
        across(
            dplyr::starts_with("subject"),
            ~ ifelse(
                . == c_a,
                c_b,
                ifelse(
                    . == c_b,
                    c_a,
                    .
                )
            )
        )
    )
    return(swapped_sm)
}
```

```{r}
mtbi_full_top_3c <- cluster_label_swap(mtbi_full_top_3c, 1, 2)
mtbi_full_top_3c <- cluster_label_swap(mtbi_full_top_3c, 2, 3)
write_csv(mtbi_full_top_3c, proc_path("mtbi_full_top_3c.csv", TRUE))
```

```{r}
mtbi_full_top_3c <- read_csv(proc_path("2024_09_12_mtbi_full_top_3c.csv"))
```

```{r}
mtbi_full_top_3c_manhattan <- mc_manhattan_plot(
    mtbi_full_top_3c,
    data_list = full_data_list_1,
    target_list = full_oom_list_1,
    domain_colours = c(
        "AS" = "#85929e",
        "D" = "#bb8fce",
        "N" = "#e59866",
        "MH" = "#7fb3d5",
        "P" = "#52be80",
        "S" = "#d98880",
        "B" = "#ff3131"
    )
)

mtbi_full_top_3c_manhattan

ggsave(
    plot = mtbi_full_top_3c_manhattan,
    filename = fig_path("mtbi_full_top_3c_manhattan.png", TRUE),
    width = 18,
    height = 6,
    dpi = 120
)
```

How are all the test features distributed?
How are all the features distributed?

I'd like to have a table along the lines of,

| DERIVATION | IN DERIVATION + VALIDATION | IN VALIDATION |
C1 max F | True | Almost  true|

Something like that, which will require a side-by-side comparison of these features through visual inspection and through the topologizer function in the supplementary section for those who wish to look at the crunched numbers.

So my objectives here are:

1. [ ] The auto-plot of the full dataset.
2. [ ] The auto-plot of the validation dataset.
3. [ ] The qualitative table.
4. [ ] The topologized table of the derivation dataset.
5. [ ] The topologized table of the derivation + validation dataset.
6. [ ] The topologized table of the validation dataset.

Up to 3 should be sufficient for determining which attributes should play a key role in validating the subsequent investigations.

```{r}

mtbi_derivation_plot_list <- plot_list

mtbi_full_plot_list <- auto_plot(
    mtbi_full_top_3c,
    data_list = full_data_list_1,
    target_list = full_oom_list_1
)

outcome_idx <- !names(mtbi_full_plot_list) %in% sorted_features
outcome_features <- names(mtbi_full_plot_list)[outcome_idx]

val_cluster_df <- mtbi_full_top_3c |>
    get_cluster_df() |>
    dplyr::filter(
        subjectkey %in% paste0("subject_", mtbi_test_subjects$"subjectkey")
    )

mtbi_val_plot_list <- auto_plot(
    cluster_df = val_cluster_df,
    data_list = test_data_list_m1,
    target_list = test_oom_list_m1
)

# Full input feature plots
pli_sort_d <- mtbi_derivation_plot_list[sorted_features]
pli_sort_v <- mtbi_val_plot_list[sorted_features]
pli_sort_f <- mtbi_full_plot_list[sorted_features]

plo_d <- mtbi_derivation_plot_list[outcome_features]
plo_v <- mtbi_val_plot_list[outcome_features]
plo_f <- mtbi_full_plot_list[outcome_features]

# Let's manually assemble these puppies!

input_plots <- list(pli_sort_d, pli_sort_v, pli_sort_f)
outcome_plots <- list(plo_d, plo_v, plo_f)

list.save(input_plots, proc_path("input_tri_plots.rds", TRUE))
list.save(outcome_plots, proc_path("outcome_tri_plots.rds", TRUE))
```

```{r}
# CHECKPOINT
input_plots <- list.load(proc_path("2024_09_13_input_tri_plots.rds"))
outcome_plots <- list.load(proc_path("2024_09_13_outcome_tri_plots.rds"))
```

```{r}
qs <- function(plot, path, w = 12, h = 4) {
    path <- paste0("mtbi_dvf_", path, ".png")
    ggsave(fig_path(path, TRUE), plot, width = w, height = h)
}

tri_plot <- function(pl,
                     feature,
                     ft_name,
                     scale_fill_labels = NULL,
                     ylims = NULL) {
    ###########################################################################
    p1 <- pl[[1]][[feature]] +
        theme(
            legend.position = "none",
            axis.title.y = element_text(size = 16)
        )
    ###########################################################################
    p2 <- pl[[2]][[feature]] +
        theme(
            legend.position = "none",
            axis.title.y = element_blank()
        ) 
    ###########################################################################
    p3 <- pl[[3]][[feature]] +
        theme(
            axis.title.y = element_blank()
        )
    ###########################################################################
    if (class(pl[[3]][[feature]]$layers[[1]]$geom)[[1]] == "GeomBar") {
        p3 <- p3 + labs(fill = ft_name)
    } else {
        p1 <- p1 + labs(y = ft_name)
    }
    if (!is.null(scale_fill_labels)) {
        p3 <- p3 + scale_fill_discrete(labels = scale_fill_labels)
    }
    if (!is.null(ylims)) {
        p1 <- p1 + ylim(ylims[[1]], ylims[[2]])
        p2 <- p2 + ylim(ylims[[1]], ylims[[2]])
        p3 <- p3 + ylim(ylims[[1]], ylims[[2]])
    }
    ###########################################################################
    patch_plot <- list(p1, p2, p3)
    patch_plot <- lapply(
        patch_plot,
        function(x) {
            x <- x + labs(x = "Cluster") + theme(text = element_text(size = 16))
        }
    )
    names(patch_plot) <- c("derivation", "validation", "full")
    return(wrap_plots(patch_plot))
}
```

```{r}
# 1. Sex
sorted_features[1]
sex_plot <- tri_plot(input_plots, "sex", "Sex", c("F", "M"))
qs(sex_plot, "sex")

# 2. Brain volumes
sorted_features[2]
brain_volume_plot <- tri_plot(input_plots, "brain_volume", expression("Brain Volume "(mm^3)), ylims = c(900000, 1650000))
qs(brain_volume_plot, "brain_volume")

# 3. Surface Areas
sorted_features[3]
cort_sa_plot <- tri_plot(input_plots, "cortical_sa", expression("Cortical Surface Area "(mm^2)), ylims = c(140000, 260000))
cort_sa_plot
qs(cort_sa_plot, "cort_sa")

# 4. Income
sorted_features[4]
household_income_plot <- tri_plot(input_plots, "household_income", "Household Income")
household_income_plot
qs(household_income_plot, "household_income")

# 5. Pubertal Status - Parent Report
sorted_features[5]
pubertal_status_p_plot <- tri_plot(input_plots, "pubertal_status_p", "Pubertal Status (Parent)")
pubertal_status_p_plot
qs(pubertal_status_p_plot, "pubertal_status_p")

# 6. Programs this year
sorted_features[6]
programs_this_year_plot <- tri_plot(input_plots, "programs_this_year", "Programs This Year")
programs_this_year_plot
qs(programs_this_year_plot, "programs_this_year")

# 7. Non school programs
sorted_features[7]
non_school_programs_plot <- tri_plot(input_plots, "non_school_programs", "Non-School Programs This Year")
non_school_programs_plot
qs(non_school_programs_plot, "non_school_programs")

# 8. Parent Somatic
sorted_features[8]
parent_somatic_plot <- tri_plot(input_plots, "parent_somatic", "Parent Somatic (T)", ylims = c(49, 95))
parent_somatic_plot
qs(parent_somatic_plot, "parent_somatic")

# 9. Parent Somatic
sorted_features[9]
weekday_screentime_plot <- tri_plot(input_plots, "weekday_screentime", "Weekday Screentime (hours)", ylims = c(-0.5, 21))
weekday_screentime_plot
qs(weekday_screentime_plot, "weekday_screentime")

# 10. Race
sorted_features[10]
race_plot <- tri_plot(input_plots, "race", "Race")
race_plot
qs(race_plot, "race")

# 11. Parent depress
sorted_features[11]
parent_depress_plot <- tri_plot(input_plots, "parent_depress", "Parent Depress (T)", ylims = c(49, 95))
parent_depress_plot
qs(parent_depress_plot, "parent_depress")

# parent_thought
sorted_features[12]
parent_thought_plot <- tri_plot(input_plots, "parent_thought", "Parent Thought (T)", ylims = c(49, 95))
parent_thought_plot
qs(parent_thought_plot, "parent_thought")

# parent_anxdep
sorted_features[13]
parent_anxdep_plot <- tri_plot(input_plots, "parent_anxdep", "Parent Anxious-Depressed (T)", ylims = c(49, 95))
parent_anxdep_plot
qs(parent_anxdep_plot, "parent_anxdep")


# private_instruction
sorted_features[14]
private_instruction_plot <- tri_plot(input_plots, "private_instruction", "Private Activities", ylims = c(-0.5, 9.5))
private_instruction_plot
qs(private_instruction_plot, "private_instruction")

# parent_antisocial
sorted_features[15]
parent_antisocial_plot <- tri_plot(input_plots, "parent_antisocial", "Parent Antisocial (T)", ylims = c(49, 95))
parent_antisocial_plot
qs(parent_antisocial_plot, "parent_antisocial")


# fmri_cort_cors
sorted_features[16]
fmri_cort_cors_plot <- tri_plot(input_plots, "fmri_cort_cors", "fMRI Cort-Cort Corrs", ylims = c(-0.1, 0.16))
fmri_cort_cors_plot
qs(fmri_cort_cors_plot, "fmri_cort_cors")


# parent_aggressive
sorted_features[17]
parent_aggressive_plot <- tri_plot(input_plots, "parent_aggressive", "Parent Aggressive (T)", ylims = c(49, 95))
parent_aggressive_plot
qs(parent_aggressive_plot, "parent_aggressive")


# weekend_screentime
sorted_features[18]
weekend_screentime_plot <- tri_plot(input_plots, "weekend_screentime", "Weekend Screentime (hours)", ylims = c(-0.5, 21))
weekend_screentime_plot
qs(weekend_screentime_plot, "weekend_screentime")

# parent_anxdisord
sorted_features[19]
parent_anxdisord_plot <- tri_plot(input_plots, "parent_anxdisord", "Parent Anxious (T)", ylims = c(49, 95))
parent_anxdisord_plot
qs(parent_anxdisord_plot, "parent_anxdisord")

# exercise_time
sorted_features[20]
exercise_time_plot <- tri_plot(input_plots, "exercise_time", "Exercise Score", ylims = c(0, 1))
exercise_time_plot
qs(exercise_time_plot, "exercise_time")

# family_fight_p
sorted_features[21]
family_fight_p_plot <- tri_plot(input_plots, "family_fight_p", "Family Fights\n(Parent Report)", scale_fill_labels = c("No", "Yes"))
family_fight_p_plot
qs(family_fight_p_plot, "family_fight_p")

# cortical_thickness
sorted_features[22]
cortical_thickness_plot <- tri_plot(input_plots, "cortical_thickness", "Cortical Thickness (mm)", ylims = c(2.3, 3.1))
cortical_thickness_plot
qs(cortical_thickness_plot, "cortical_thickness")

# fmri_cort_subcort_cors
sorted_features[23]
fmri_cort_subcort_cors_plot <- tri_plot(input_plots, "fmri_cort_subcort_cors", "fMRI Cort-Subcort Corrs", ylims = c(-0.15, 0.2))
qs(fmri_cort_subcort_cors_plot, "fmri_cort_subcort_cors")

# parent_avoidant
sorted_features[24]
parent_avoidant_plot <- tri_plot(input_plots, "parent_avoidant", "Parent Avoidant (T)", ylims = c(49, 95))
parent_avoidant_plot
qs(parent_avoidant_plot, "parent_avoidant")


# parent_hyperactive
sorted_features[25]
parent_hyperactive_plot <- tri_plot(input_plots, "parent_hyperactive", "Parent Hyperactive (T)", ylims = c(49, 95))
qs(parent_hyperactive_plot, "parent_hyperactive")


# Parent attention
sorted_features[26]
parent_attention_plot <- tri_plot(input_plots, "parent_attention", "Parent Attention (T)", ylims = c(49, 95))
parent_attention_plot
qs(parent_attention_plot, "parent_attention")

# parent_withdrawn
sorted_features[27]
parent_withdrawn_plot <- tri_plot(input_plots, "parent_withdrawn", "Parent Withdrawn (T)")
parent_withdrawn_plot

qs(parent_withdrawn_plot, "parent_withdrawn")

# helps_hurt_p
sorted_features[28]
helps_hurt_p_plot <- tri_plot(input_plots, "helps_hurt_p", "Helps Hurt\n(Parent Report)", c("No", "Yes"))
helps_hurt_p_plot

qs(helps_hurt_p_plot, "helps_hurt_p")

# considerate_y
sorted_features[29]
considerate_y_plot <- tri_plot(input_plots, "considerate_y", "Considerate\n(Youth Report)", c("No", "Yes"))
considerate_y_plot
qs(considerate_y_plot, "considerate_y")


# major_wm_ndi
sorted_features[30]
major_wm_ndi_plot <- tri_plot(input_plots, "major_wm_ndi", "Major WM Neurite Density", ylims = c(0.45, 0.85))
major_wm_ndi_plot
qs(major_wm_ndi_plot, "major_wm_ndi")

# helps_hurt_y
sorted_features[31]
helps_hurt_y_plot <- tri_plot(input_plots, "helps_hurt_y", "Helps Hurt\n(Youth Report)", c("No", "Yes"))
helps_hurt_y_plot
qs(helps_hurt_y_plot, "helps_hurt_y")

# helpful_p
sorted_features[32]
helpful_p_plot <- tri_plot(input_plots, "helpful_p", "Helpful\n(Parent Report)", c("No", "Yes"))
helpful_p_plot
qs(helpful_p_plot, "helpful_p")

# family_hit_p
sorted_features[33]
family_hit_p_plot <- tri_plot(input_plots, "family_hit_p", "Family Hitting\n(Parent Report)", c("No", "Yes"))
family_hit_p_plot
qs(family_hit_p_plot, "family_hit_p")

# family_outdo_p
sorted_features[34]
family_outdo_p_plot <- tri_plot(input_plots, "family_outdo_p", "Family Outdo\n(Parent Report)", c("No", "Yes"))
family_outdo_p_plot
qs(family_outdo_p_plot, "family_outdo_p")

# parent_intrusive
sorted_features[35]
parent_intrusive_plot <- tri_plot(input_plots, "parent_intrusive", "Parent Intrusive (T)", ylims = c(49, 95))
parent_intrusive_plot
qs(parent_intrusive_plot, "parent_intrusive")

###############################################################################

# parent_intrusive
parent_intrusive_plot <- tri_plot(input_plots, "parent_intrusive", "parent_intrusive (T)", ylims = c(49, 95))
parent_intrusive_plot
qs(parent_intrusive_plot, "parent_intrusive")

# headache_history
headache_history_plot <- tri_plot(input_plots, "headache_history", "Headache\nHistory", c("No", "Yes"))
headache_history_plot
qs(headache_history_plot, "headache_history")

# mtbi_loc
mtbi_loc_plot <- tri_plot(input_plots, "mtbi_loc", "mTBI LOC", c("No", "Yes"))
mtbi_loc_plot
qs(mtbi_loc_plot, "mtbi_loc")

# family_peaceful_y
family_peaceful_y_plot <- tri_plot(input_plots, "family_peaceful_y", "Family Peaceful\n(Youth Report)", c("No", "Yes"))
family_peaceful_y_plot
qs(family_peaceful_y_plot, "family_peaceful_y")

# family_peaceful_p
family_peaceful_p_plot <- tri_plot(input_plots, "family_peaceful_p", "Family Peaceful\n(Parent Report)", c("No", "Yes"))
family_peaceful_p_plot
qs(family_peaceful_p_plot, "family_peaceful_p")

# parent_perstr
parent_perstr_plot <- tri_plot(input_plots, "parent_perstr", "parent_perstr")
parent_perstr_plot
qs(parent_perstr_plot, "parent_perstr")

# considerate_p
considerate_p_plot <- tri_plot(input_plots, "considerate_p", "considerate_p")
considerate_p_plot
qs(considerate_p_plot, "considerate_p")

# pericortical_wm_ndi
pericortical_wm_ndi_plot <- tri_plot(input_plots, "pericortical_wm_ndi", "pericortical_wm_ndi")
pericortical_wm_ndi_plot
qs(pericortical_wm_ndi_plot, "pericortical_wm_ndi")

# family_temper_p
family_temper_p_plot <- tri_plot(input_plots, "family_temper_p", "family_temper_p")
family_temper_p_plot
qs(family_temper_p_plot, "family_temper_p")

# age
age_plot <- tri_plot(input_plots, "age", "age")
age_plot
qs(age_plot, "age")

# family_criticize_p
family_criticize_p_plot <- tri_plot(input_plots, "family_criticize_p", "family_criticize_p")
family_criticize_p_plot
qs(family_criticize_p_plot, "family_criticize_p")

# family_outdo_y
family_outdo_y_plot <- tri_plot(input_plots, "family_outdo_y", "family_outdo_y")
family_outdo_y_plot
qs(family_outdo_y_plot, "family_outdo_y")

# school_programs
school_programs_plot <- tri_plot(input_plots, "school_programs", "school_programs")
school_programs_plot
qs(school_programs_plot, "school_programs")

# mtbi_age
mtbi_age_plot <- tri_plot(input_plots, "mtbi_age", "mtbi_age")
mtbi_age_plot
qs(mtbi_age_plot, "mtbi_age")

# family_yell_y
family_yell_y_plot <- tri_plot(input_plots, "family_yell_y", "family_yell_y")
family_yell_y_plot
qs(family_yell_y_plot, "family_yell_y")

# same_sex_close_friend
same_sex_close_friend_plot <- tri_plot(input_plots, "same_sex_close_friend", "same_sex_close_friend")
same_sex_close_friend_plot
qs(same_sex_close_friend_plot, "same_sex_close_friend")

# family_criticize_y
family_criticize_y_plot <- tri_plot(input_plots, "family_criticize_y", "family_criticize_y")
family_criticize_y_plot
qs(family_criticize_y_plot, "family_criticize_y")

# family_angry_y
family_angry_y_plot <- tri_plot(input_plots, "family_angry_y", "family_angry_y")
family_angry_y_plot
qs(family_angry_y_plot, "family_angry_y")

# family_angry_p
family_angry_p_plot <- tri_plot(input_plots, "family_angry_p", "family_angry_p")
family_angry_p_plot
qs(family_angry_p_plot, "family_angry_p")

# family_throw_p
family_throw_p_plot <- tri_plot(input_plots, "family_throw_p", "family_throw_p")
family_throw_p_plot
qs(family_throw_p_plot, "family_throw_p")

# helpful_y
helpful_y_plot <- tri_plot(input_plots, "helpful_y", "helpful_y")
helpful_y_plot
qs(helpful_y_plot, "helpful_y")

# pubertal_status_y
pubertal_status_y_plot <- tri_plot(input_plots, "pubertal_status_y", "pubertal_status_y")
pubertal_status_y_plot
qs(pubertal_status_y_plot, "pubertal_status_y")

# mtbi_mem_daze
mtbi_mem_daze_plot <- tri_plot(input_plots, "mtbi_mem_daze", "mtbi_mem_daze")
mtbi_mem_daze_plot
qs(mtbi_mem_daze_plot, "mtbi_mem_daze")

# same_sex_friend
same_sex_friend_plot <- tri_plot(input_plots, "same_sex_friend", "same_sex_friend")
same_sex_friend_plot
qs(same_sex_friend_plot, "same_sex_friend")

# previous_mtbis
previous_mtbis_plot <- tri_plot(input_plots, "previous_mtbis", "previous_mtbis")
previous_mtbis_plot
qs(previous_mtbis_plot, "previous_mtbis")

# mtbi_mechanism
mtbi_mechanism_plot <- tri_plot(input_plots, "mtbi_mechanism", "mtbi_mechanism")
mtbi_mechanism_plot
qs(mtbi_mechanism_plot, "mtbi_mechanism")

# family_fight_y
family_fight_y_plot <- tri_plot(input_plots, "family_fight_y", "family_fight_y")
family_fight_y_plot
qs(family_fight_y_plot, "family_fight_y")

# opp_sex_friend
opp_sex_friend_plot <- tri_plot(input_plots, "opp_sex_friend", "opp_sex_friend")
opp_sex_friend_plot
qs(opp_sex_friend_plot, "opp_sex_friend")

# family_throw_y
family_throw_y_plot <- tri_plot(input_plots, "family_throw_y", "family_throw_y")
family_throw_y_plot
qs(family_throw_y_plot, "family_throw_y")

# family_temper_y
family_temper_y_plot <- tri_plot(input_plots, "family_temper_y", "family_temper_y")
family_temper_y_plot
qs(family_temper_y_plot, "family_temper_y")

# family_hit_y
family_hit_y_plot <- tri_plot(input_plots, "family_hit_y", "family_hit_y")
family_hit_y_plot
qs(family_hit_y_plot, "family_hit_y")

# opp_sex_close_friend
opp_sex_close_friend_plot <- tri_plot(input_plots, "opp_sex_close_friend", "opp_sex_close_friend")
opp_sex_close_friend_plot
qs(opp_sex_close_friend_plot, "opp_sex_close_friend")

# family_yell_p
family_yell_p_plot <- tri_plot(input_plots, "family_yell_p", "family_yell_p")
family_yell_p_plot
qs(family_yell_p_plot, "family_yell_p")


```

```{r}











```
