# Cluster characterization

## Load libraries and data

```{r}
library(metasnf)
library(rlist)
library(abcdutils)
library(here)
library(readr)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
od_path <- path_maker("/home/prashanth/onedrive/images")
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))

proc_writer <- make_writer(proc_path)
proc_reader <- make_reader(proc_path)
input_reader <- make_reader(input_path)

data_list_train <- list.load(proc_path("2023_04_27_data_list_0_0_train.rdata"))
data_list_test <- list.load(proc_path("2023_04_27_data_list_0_0_test.rdata"))
data_list_full <- list.load(proc_path("2023_04_27_data_list_0_0_full.rdata"))
cbcl_list_train <- list.load(proc_path("2023_04_27_cbcl_list_0_0_train.rdata"))
cbcl_list_full <- list.load(proc_path("2023_04_27_cbcl_list_0_0_full.rdata"))

nihtbx_pattern <- input_reader("2023_04_27_nihtbx_pattern_fc_imp_0_0.csv")
nihtbx_list <- input_reader("2023_04_27_nihtbx_list_fc_imp_0_0.csv")
nihtbx_cardsort <- input_reader("2023_04_27_nihtbx_cardsort_fc_imp_0_0.csv")
sds_sleep_df <- input_reader("2023_04_26_sds_sleep_df_0_0.csv")


top_oms_0_0_train <- read_csv(proc_path("2023_04_27_top_oms_0_0_train.csv"))
```

## Summary of the ABCD sample

```{r}
#library(gt)
#library(gtExtras)
#library(webshot2)
#
#sdl(data_list_full)
#
#
##Base tables
#table1 <- data.frame(
#  Measure = LETTERS[1:2],
#  n = runif(2))
#table2 <- data.frame(
#  Measure = LETTERS[3:5],
#  n = runif(3))
##Merge tables by row
#fulltable <- rbind(table1, table2)
##Create the gt object again for the merged table
#gttable <- gt(fulltable) |>
#  tab_row_group(label = "Race", rows = 1:2) |>
#  tab_row_group(label = "Injury Mechanism", rows = 3:5) |>
#  tab_options(table.width = 250)
#gttable
#
#
#
#make_summary_tables <- function(data_list_full, fig_path) {
#    race <- ""
#    # Give the data list accessible names
#    names(data_list_full) <- sdl(data_list_full)$"name"
#    # Race table# {~
#    race_table <- data_list_full$"race"$"data" |>
#        dplyr::group_by(race) |>
#        dplyr::summarize(n = dplyr::n()) |>
#        dplyr::mutate(Percent = round(n / sum(n) * 100, 1)) |>
#        dplyr::mutate(race = dplyr::case_when(
#            race == "black" ~ "Black",
#            race == "white" ~ "White",
#            race == "mixed_or_other" ~ "Mixed/Other")) |>
#        `colnames<-`(c("Measure", "n (total = 320)", "%"))# ~}
#    # Mechanism table# {~
#    mechanism_table <- data_list_full$"mtbi_mechanism"$"data" |>
#        dplyr::mutate(latest_mtbi_mechanism = dplyr::case_when(
#            latest_mtbi_mechanism == "multi" ~ "other_loc",
#            TRUE ~ latest_mtbi_mechanism))
#    print(unique(mechanism_table$latest_mtbi_mechanism))
#    mechanism_table <- mechanism_table |>
#        dplyr::group_by(latest_mtbi_mechanism) |>
#        dplyr::summarize(n = dplyr::n()) |>
#        dplyr::mutate(Percent = round(n / sum(n) * 100, 1))
#    mechanism_table <- mechanism_table |>
#        dplyr::group_by(latest_mtbi_mechanism) |>
#        dplyr::mutate(latest_mtbi_mechanism = dplyr::case_when(
#            latest_mtbi_mechanism == "fall_hit" ~ "Fall",
#            latest_mtbi_mechanism == "hosp_er" ~ "ER visit",
#            latest_mtbi_mechanism == "vehicle" ~ "Vehicle accident",
#            latest_mtbi_mechanism == "violent" ~ "Violent attack",
#            latest_mtbi_mechanism == "other_loc" ~ "Other injury",
#            TRUE ~ latest_mtbi_mechanism)) |>
#        `colnames<-`(c("Measure", "n (total = 320)", "%"))# ~}
#    # Sex table    # {~
#    sex_table <- data_list_full$"sex"$"data" |>
#        dplyr::group_by(M) |>
#        dplyr::summarize(n = dplyr::n()) |>
#        dplyr::mutate(Percent = round(n / sum(n) * 100, 1)) |>
#        dplyr::mutate(M = dplyr::case_when(
#            M == 0 ~ "F",
#            M == 1 ~ "M")) |>
#        `colnames<-`(c("Measure", "n (total = 320)", "%"))# ~}
#    # Loc table# {~
#    loc_table <- data_list_full$"mtbi_loc"$"data" |>
#        dplyr::group_by(latest_mtbi_loc) |>
#        dplyr::summarize(n = dplyr::n()) |>
#        dplyr::mutate(Percent = round(n / sum(n) * 100, 1)) |>
#        dplyr::mutate(latest_mtbi_loc = dplyr::case_when(
#            latest_mtbi_loc == 0 ~ "No",
#            latest_mtbi_loc == 1 ~ "Yes")) |>
#        `colnames<-`(c("Measure", "n (total = 320)", "%"))# ~}
#    # Mem daze table# {~
#    mem_daze_table <- data_list_full$"mtbi_mem_daze"$"data" |>
#        dplyr::group_by(latest_mtbi_mem_daze) |>
#        dplyr::summarize(n = dplyr::n()) |>
#        dplyr::mutate(Percent = round(n / sum(n) * 100, 1)) |>
#        dplyr::mutate(latest_mtbi_mem_daze = dplyr::case_when(
#            latest_mtbi_mem_daze == 0 ~ "No",
#            latest_mtbi_mem_daze == 1 ~ "Yes")) |>
#        `colnames<-`(c("Measure", "n (total = 320)", "%"))# ~}
#    # Putting it all together# {~
#    idx1 <- 1
#    idx2 <- nrow(race_table)
#    idx3 <- idx2 + 1
#    idx4 <- idx2 + nrow(mechanism_table)
#    idx5 <- idx4 + 1
#    idx6 <- idx4 + nrow(sex_table)
#    idx7 <- idx6 + 1
#    idx8 <- idx6 + nrow(loc_table)
#    idx9 <- idx8 + 1
#    idx10 <- idx8 + nrow(loc_table)
#    full_table <- do.call(rbind, list(race_table,
#                                      mechanism_table,
#                                      mem_daze_table,
#                                      loc_table,
#                                      sex_table
#                                      ))
#    full_table |>
#        gt::gt() |>
#        gt::cols_align(align = "center", columns = "n (total = 320)") |>
#        gt::tab_row_group(label = "Race", rows = idx1:idx2) |>
#        gt::tab_row_group(label = "Injury mechanism", rows = idx3:idx4) |>
#        gt::tab_row_group(label = "Memory loss / Feeling dazed", rows = idx5:idx6) |>
#        gt::tab_row_group(label = "LOC", rows = idx7:idx8) |>
#        gt::tab_row_group(label = "Sex", rows = idx9:idx10) |>
#        gt::tab_options(
#            table.width = 400,
#            data_row.padding = px(2),
#            column_labels.padding = px(8),
#            row_group.padding = px(3),
#            table.font.size = "20px",
#            column_labels.font.size = "24px"
#            ) |>
#        gt::tab_style(
#            style = list(
#                gt::cell_text(weight = "bold")),
#            locations = list(
#                cells_row_groups(),
#                cells_column_labels()
#            )) |>
#    gtsave(fig_path("abcd_mtbi_summary_table_0_0.png", date = TRUE))# ~}
#}
#make_summary_tables(data_list_full, fig_path)
#
#
#
#data_list_full$"mtbi_age"$"data"$"latest_mtbi_age" |> mean()
#data_list_full$"mtbi_age"$"data"$"latest_mtbi_age" |> sd()
#
#
#    gt() |>
#    cols_align(align = "center") |>
#    gt_theme_538() |>
#    gtsave(od_path("abcd_mtbi_loc_table_0_0.png", date = TRUE))
#
```



## CBCL plotting in the training subjects

The function below generates a grid of CBCL impairment plots for each cluster solution and saves them using a provided `path_maker` function.

```{r}
# Last generated on 2023-04-06
plot_all_cbcl(top_oms_0_0_train, cbcl_list_train, fig_path)

top_oms_0_0_train$significance

# The two clust mean solution
top_om_uhn <- top_oms_0_0_train[2, ]

# All solutions, all cbcl vars
plot_all_cbcl(
    top_oms_0_0_train,
    cbcl_list_train,
    fig_path,
    save_suffix = "_cbcl_train"
)

# Top solution, depress, anxiety, attention, and aggression
plot_all_cbcl(
    top_om_uhn,
    cbcl_list_train,
    fig_path,
    include = c(
        "depress",
        "anxiety",
        "attention",
        "aggressive"
    ),
    save_suffix = "_cbcl_short_train",
    h = 8,
    w = 15
)
```


## NMI calculations

I have found that the `om_to_nmi_df` function can yield different results across different machines.
I believe this is due to to hardware-specific differences in handling floating point arithmetic during the SNFTool package's implementation of spectral clustering.
Moving forward, I use results generated by my machine at SickKids (Intel(R) Core(TM) i5-10400 CPU @ 2.90 GHz).
Some notable file versions are `2023_03_13_nmi_df.csv` (the first run of the `om_to_nmi_df` function, calculated at the SickKids machine) and `2023_03_15_nmi_df.csv` (run from my home machine, yielding distinct results).


```{r}
library(metasnf)# {~
library(abcdutils)
library(here)
library(readr)
library(gt)
library(gtExtras)
library(webshot2)
library(rlist)

nmi_df <- om_to_nmi_df(top_oms_0_0_train, data_list_train)

write_csv(nmi_df, proc_path("nmi_df_0_0_train.csv", date = TRUE))

nmi_df <- data.frame(read_csv(proc_path("2023_04_05_nmi_df_0_0_train.csv")))

# Saving a pretty table png of each row's NMIs
for (row in seq_len(nrow(top_oms_0_0_train))) {
    calc_nmi(top_oms_0_0_train[row, ], data_list_train) |>
        gt() |>
        gt_theme_538() |>
        gtsave(fig_path(paste0(top_oms_0_0_train[row, ]$"significance",
                               "_nmis.png"), date = TRUE))
}# ~}
```


## Label propagation

```{r}
propagated_labels <- lp_om(top_oms_0_0_train, data_list_full)

write_csv(propagated_labels, proc_path("top_oms_0_0_lp.csv", date = TRUE))

propagated_labels <- proc_reader("2023_05_08_top_oms_0_0_lp.csv")

top_oms_0_0_train |>
    dplyr::select("row_id", "significance")
```

## CBCL plotting in the label propagated group

```{r}
#### NEW STUFF
propagated_labels

test_labels <- propagated_labels |>
    dplyr::filter(group == "test") |>
    dplyr::select(-"group")

outcomes_and_eval_df <- append(list(test_labels), cbcl_list_full)

test_eval_df <- merge_df_list(outcomes_and_eval_df)

#' Convert a propagated label structure to an output-matrix like structure
#'
#' @param pl a propagated label dataframe row
#' @param significance a label for the row
#'
#' @return pl_om the converted row
#'
#' @export
pl_to_om <- function(pl, original_om) {
    pl_om <- pl |>
        dplyr::filter(group == "test") |>
        t() |>
        data.frame()
    colnames(pl_om) <- pl_om[1, ]
    pl_om <- pl_om[3:nrow(pl_om), ]
    pl_om <- cbind(rownames(pl_om), pl_om)
    pl_om <- cbind(original_om$"row_id", pl_om)
    colnames(pl_om) <- c("row_id", "significance", colnames(pl_om)[3:length(colnames(pl_om))])
    rownames(pl_om) <- NULL
    pl_om <- pl_om |>
        dplyr::mutate(
            nclust = dplyr::case_when(
                grepl("two", pl_om$"significance") ~ 2,
                grepl("three", pl_om$"significance") ~ 3,
                grepl("four", pl_om$"significance") ~ 4,
                grepl("five", pl_om$"significance") ~ 5,
                TRUE ~ NA
            )
        )
    return(pl_om)
}

pl_om <- pl_to_om(propagated_labels, top_oms_0_0_train)

plot_all_cbcl(
    pl_om,
    cbcl_list_full,
    fig_path,
    save_suffix = "_cbcl_test"
)

#### 2023_05_08 left off here
# Need to do some uninjured subject comparisons
# Also seek out solutions that are driven by mTBI variables (see their NMIs)
```

## NMI characterization
```{r}
nmi_df

# How NMIs are distributed
plot_nmis(nmi_df, fig_path)
```


## Input variable characterization
```{r}
plot_om_bar <- function(om_row, input_df, feature, featname, save = NULL) {
    if (is.null(input_df)) {
        return(NULL)
    }
    cluster_df <- get_cluster_df(om_row)
    characterization_df <-
        dplyr::inner_join(cluster_df, input_df, by = "subjectkey")
    cluster <- ""
    percent <- ""
    n <- ""
    keycol <- ""
    n_thresh <- ""
    characterization_df <- characterization_df |>
        dplyr::rename("keycol" = !!feature) # wizardry
    summary <- characterization_df |>
        dplyr::group_by(cluster) |>
        dplyr::count(keycol) |>
        dplyr::mutate(percent = round(n / sum(n) * 100))
    if (is.numeric(summary$"keycol")) {
        lvl <- as.character(rev(sort(unique(summary$"keycol"))))
        summary$"keycol" <- factor(summary$"keycol", levels = lvl)
    } else {
        summary$"keycol" <- factor(summary$"keycol")
    }
    summary$"cluster" <-
        factor(summary$"cluster", levels = as.character(1:om_row$"nclust"))
    summary <- summary |>
        dplyr::mutate(n_thresh = dplyr::case_when(
            n < 5 ~ "",
            TRUE ~ as.character(n)))
    print(summary)
    plot <- ggplot2::ggplot(
        summary,
        ggplot2::aes(
            x = cluster,
            y = percent,
            fill = keycol)) +
        ggplot2::geom_bar(
            stat = "identity",
            position = ggplot2::position_stack(),
            width = 0.8) +
        ggplot2::geom_text(
            #data = subset(summary, percent > 10),
            mapping = ggplot2::aes(
                #label = n_thresh,
                label = n,
                y = percent),
            size = 8,
            position = ggplot2::position_stack(vjust = 0.5)) +
        ggplot2::scale_y_continuous(
            expand = ggplot2::expansion(mult = c(0, .1))) +
        ggplot2::scale_x_discrete(drop = FALSE) +
        ggplot2::labs(
            x = "Cluster",
            y = "Percentage",
            fill = featname) +
        ggplot2::theme_bw() +
        ggplot2::theme(
            text = ggplot2::element_text(size = 30),
            plot.margin = ggplot2::margin(l = 0, r = 2, t = 1, b = 1, "cm"))
    if (!is.null(save)) {
        ggplot2::ggsave(file = save, plot, width = 10, height = 10)
    } else {
        return(plot)
    }
}

pheatmap_om_matrix <- function(om_row, input_df, binary = FALSE, save = NULL,
                               main = "", show_row = FALSE, legend = TRUE,
                               cw = 100, ch = 2) {
    if (is.null(input_df)) {
        return(NULL)
    }
    cluster <- ""
    cluster_df <- get_cluster_df(om_row)
    characterization_df <-
        dplyr::inner_join(input_df, cluster_df, by = "subjectkey")
    cluster_names <- characterization_df |>
        dplyr::group_by(cluster) |>
        dplyr::select(-"subjectkey") |>
        dplyr::summarize_all(mean) |>
        dplyr::select("cluster") |>
        unlist() |>
        names()
    cluster_names <- as.character(sort(unique(characterization_df$"cluster")))
    matrix <- characterization_df |>
        dplyr::group_by(cluster) |>
        dplyr::select(-"subjectkey") |>
        dplyr::summarize_all(mean) |>
        dplyr::select(-"cluster") |>
        t()
    colnames(matrix) <- cluster_names
    if (binary == TRUE) {
    # This for loop ensures that the lowest value in each row becomes 0
        for (i in seq_len(nrow(matrix))) {
            matrix[i, ] <- matrix[i, ] - min(matrix[i, ])
        }
    }
    # This for loop ensures that the highest value in each row becomes 1
    matrix_row_max <- apply(matrix, 1, max)
    for (i in seq_len(nrow(matrix))) {
        matrix[i, ] <- (matrix[i, ] / matrix_row_max[i])
    }
    if (!(is.null(grDevices::dev.list())) && !(is.null(save))) {
        grDevices::dev.off()
    }
    if (!(is.null(save))) {
        pheatmap::pheatmap(matrix,
                           cluster_cols = FALSE,
                           filename = save,
                           main = main,
                           fontsize = 25,
                           show_rownames = show_row)
    } else {
        return(pheatmap::pheatmap(matrix, cluster_cols = FALSE, main = main,
                                  fontsize = 25,
                                  show_rownames = show_row,
                                  legend = legend,
                                  angle_col = "0",
                                  cellwidth = cw,
                                  cellheight = ch,
                                  border_color = NA))
    }
}

plot_om_cont <- function(om_row, input_df, feature, featname, save = NULL) {
    if (is.null(input_df)) {
        return(NULL)
    }
    cluster_df <- get_cluster_df(om_row)
    cluster <- ""
    keycol <- ""
    characterization_df <-
        dplyr::inner_join(cluster_df, input_df, by = "subjectkey")
    characterization_df <- characterization_df |>
        dplyr::rename("keycol" = !!feature) # wizardry
    characterization_df$"cluster" <- factor(characterization_df$"cluster")
    plot <- ggplot2::ggplot(
        characterization_df,
        ggplot2::aes(
            x = cluster,
            y = keycol,
            fill = cluster,
            color = cluster)) +
        ggplot2::geom_violin(alpha = 0.4) +
        ggplot2::geom_jitter(height = 0, size = 3, alpha = 1) +
        ggplot2::scale_y_continuous(
            expand = ggplot2::expansion(mult = c(0, .1))) +
        ggplot2::scale_x_discrete(limits = as.character(1:om_row$"nclust")) +
        ggplot2::labs(
            x = "Cluster",
            y = featname) +
        ggplot2::theme_bw() +
        ggplot2::theme(
            text = ggplot2::element_text(size = 30),
            plot.margin = ggplot2::margin(l = 0, r = 2, t = 1, b = 1, "cm"),
            legend.position = "none")
    if (!is.null(save)) {
        print(save)
        ggplot2::ggsave(file = save, plot, width = 10, height = 10)
    } else {
        return(plot)
    }
}

train_dfs <- lapply(data_list_train, function(x) x$"data")

input_characterization_plots_g <- function(om,
                                         loc = NULL,
                                         mechanism = NULL,
                                         dazed = NULL,
                                         income = NULL,
                                         interview_age = NULL,
                                         mtbi_age = NULL,
                                         pubertal = NULL,
                                         race = NULL,
                                         sex = NULL,
                                         headache = NULL,
                                         mtbi_count = NULL,
                                         wmnd = NULL,
                                         gord_cor = NULL,
                                         gord_var = NULL,
                                         subc_cor = NULL,
                                         subc_var = NULL,
                                         cort_sa = NULL,
                                         cort_t = NULL,
                                         subc_v = NULL,
                                         loneliness = NULL,
                                         screentime = NULL,
                                         fam_fn = NULL,
                                         sports = NULL,
                                         prosocial = NULL,
                                         parent_psych = NULL,
                                         exercise = NULL,
                                         pattern = NULL,
                                         cardsort = NULL,
                                         list = NULL,
                                         general_inp_path,
                                         rsfmri_path,
                                         other_mri_path,
                                         other_heatmap_path) {
    for (i in seq_len(nrow(om))) {
        row_i <- om[i, ]
        sig <- row_i$"significance"
        id <- row_i$"row_id"
        prefix <- paste0("row_", id, "_", sig)
        g_path <- gsub("gen", paste0(prefix, "_gen"), general_inp_path)
        r_path <- gsub("rsfmri", paste0(prefix, "_rsfmri"), rsfmri_path)
        om_path <- gsub("other_mri",
                        paste0(prefix, "_other_mri"), other_mri_path)
        o_path <- gsub("other_in",
                       paste0(prefix, "_other_in"), other_heatmap_path)
        # LOC
        loc_p <- plot_om_bar(row_i, loc, "latest_mtbi_loc", "LOC")
        # Mechanism
        mech_p <- plot_om_bar(row_i, mechanism, "latest_mtbi_mechanism", "MOI")
        # Dazed
        dazed_p <- plot_om_bar(row_i, dazed, "latest_mtbi_mem_daze", "Dazed")
        # Income
        income_p <- plot_om_bar(row_i, income, "household_income", "Income")
        # Age at interview
        interview_age_p <- plot_om_cont(row_i, interview_age, "interview_age",
                               "Interview Age")
        # Age at injury
        injury_age_p <- plot_om_cont(row_i, mtbi_age, "latest_mtbi_age",
                                     "Injury Age")
        # Pubertal status
        pubertal_p <- plot_om_cont(row_i, pubertal, "pubertal_status",
                                   "Pubertal\nStage")
        # Race
        race_p <- plot_om_bar(row_i, race, "race", "Race")
        # Sex
        sex_p <- plot_om_bar(row_i, sex, "M", "Male")
        # Headaches
        headache_p <- plot_om_bar(row_i, headache, "headache", "Headaches")
        # Number of injuries
        mtbi_count_p <- plot_om_bar(row_i, mtbi_count, "mtbi_count",
                                     "mTBI\nCount")
        # Loneliness
        friend_p1 <- plot_om_cont(row_i, loneliness, "ss_friend",
                     "Same Sex\nFriends")
        friend_p2 <- plot_om_cont(row_i, loneliness, "ss_close_friend",
                     "Same Sex\nClose Friends")
        friend_p3 <- plot_om_cont(row_i, loneliness, "os_friend",
                     "Opposite Sex\nFriends")
        friend_p4 <- plot_om_cont(row_i, loneliness, "os_close_friend",
                     "Opposite Sex\nClose Friends")
        # Screentime
        wknd_screen_p <- plot_om_cont(row_i, screentime, "screentime_wknd_hrs",
                     "Weekend\nScreentime")
        wkd_screen_p <- plot_om_cont(row_i, screentime, "screentime_wkday_hrs",
                     "Weekday\nScreentime")
        # Exercise
        exercise_p <- plot_om_cont(row_i, exercise, "physical_activity",
            "Exercise level")
        # NIHTBX
        pattern_p <- plot_om_cont(row_i, pattern, "nihtbx_pattern_fc",
                     "NIHTBX\nPattern Comparison")
        # NIH Cardsort
        card_p <- plot_om_cont(row_i, cardsort, "nihtbx_cardsort_fc",
                     "NIHTBX\nCard Sort")
        # NIH List
        list_p <- plot_om_cont(row_i, list, "nihtbx_list_fc",
                     "NIHTBX\nList Sort")
        ## Sports and Activities
        sa_p1 <- plot_om_cont(row_i, sports, "organized_school_activities",
                     "Activities organized\nwithin school")
        sa_p2 <- plot_om_cont(row_i, sports, "organized_outside_activities",
                     "Activities organized\noutside of school")
        sa_p3 <- plot_om_cont(row_i, sports, "private_instruction_activities",
                     "Activities with\nprivate instruction")
        sa_p4 <- plot_om_cont(row_i, sports, "p12_activities",
                     "Activities in\nthe last year")
        # Prosocial behaviour
        proso_p1 <- plot_om_bar(row_i, prosocial, "q1",
                    "Care about \nothers'\nfeelings")
        proso_p2 <- plot_om_bar(row_i, prosocial, "q2",
                    "Help hurt, upset, \nor sick people")
        proso_p3 <- plot_om_bar(row_i, prosocial, "q3",
                    "Often offer\nto help")
        # rsFMRI
        # gord_cor
        gord_cor_p <- pheatmap_om_matrix(row_i, gord_cor, binary = TRUE,
            legend = FALSE,
            cw = 50,
            ch = 3,
            main = "Cortical correlations (rs-fMRI)")[[4]]
        ## gord_var
        gord_var_p <- pheatmap_om_matrix(row_i, gord_var,
            legend = FALSE,
            cw = 50,
            ch = 3,
            main = "Cortical variations (rs-fMRI))")[[4]]
        ### subc_cor
        subc_cor_p <- pheatmap_om_matrix(row_i, subc_cor, binary = TRUE,
            legend = FALSE,
            cw = 50,
            ch = 3,
            main = "Subcortical correlations (rs-fMRI)")[[4]]
        ## subc_var
        subc_var_p <- pheatmap_om_matrix(row_i, subc_var,
            legend = FALSE,
            cw = 50,
            ch = 3,
            main = "Subcortical variations (rs-fMRI)")[[4]]
        # Other MRI
        ## dMRI
        wmnd_p <- pheatmap_om_matrix(
            row_i, wmnd, binary = FALSE,
            legend = FALSE,
            cw = 50,
            ch = 2,
            main = "White Matter Neurite Densities")[[4]]
        ## cort_sa
        cort_sa_p <- pheatmap_om_matrix(row_i, cort_sa,
            legend = FALSE,
            cw = 50,
            ch = 3,
            main = "Cortical Surface Area")[[4]]
        ## cort_t
        cort_t_p <- pheatmap_om_matrix(row_i, cort_t,
            legend = FALSE,
            cw = 50,
            ch = 3,
            main = "Cortical Thickness")[[4]]
        ## subc_v
        subc_v_p <- pheatmap_om_matrix(row_i, subc_v,
            legend = FALSE,
            cw = 50,
            ch = 3,
            main = "Subcortical Volume")[[4]]
        # Non-imaging
        ## Family function
        fam_fn_p <- pheatmap_om_matrix(row_i, fam_fn,
            legend = FALSE,
            cw = 50,
            ch = 30,
            show_row = TRUE,
            main = "Family Function")[[4]]
        ## Parent psychopathology
        parent_p <- pheatmap_om_matrix(row_i, parent_psych,
            legend = FALSE,
            cw = 50,
            ch = 30,
            show_row = TRUE,
            main = "Parent Psychopathology")[[4]]
        ## SDS
        sleep_p <- pheatmap_om_matrix(row_i, sds_sleep_df,
            legend = FALSE,
            cw = 50,
            ch = 30,
            show_row = TRUE,
            main = "Sleeping issues")[[4]]
        ## Sports and Activities
        sports_p <- pheatmap_om_matrix(row_i, sports,
            legend = FALSE,
            cw = 50,
            ch = 30,
            show_row = TRUE,
            main = "Sports and Activities")[[4]]
        #
        # Grid creation
        #
        grid_rsfmri <- gridExtra::arrangeGrob(
            gord_var_p,
            subc_cor_p,
            gord_cor_p,
            subc_var_p)
        ggplot2::ggsave(file = r_path,
                        grid_rsfmri,
                        width = 20,
                        height = 30)
        grid_other_mri <- gridExtra::arrangeGrob(
            wmnd_p,
            cort_sa_p,
            cort_t_p,
            subc_v_p)
        ggplot2::ggsave(file = om_path,
                        grid_other_mri,
                        width = 20,
                        height = 20)
        grid_non_imaging <- gridExtra::arrangeGrob(
            fam_fn_p,
            parent_p,
            sleep_p,
            sports_p)
        ggplot2::ggsave(file = o_path,
                        grid_non_imaging,
                        width = 20,
                        height = 30)
        grid <- gridExtra::arrangeGrob(
                abcdutils::clean_plot(loc_p, c("x")),
                abcdutils::clean_plot(mech_p, c("x")),
                abcdutils::clean_plot(dazed_p, c("x")),
                abcdutils::clean_plot(income_p, c("x")),
                abcdutils::clean_plot(race_p, c("x")),
                abcdutils::clean_plot(sex_p, c("x")),
                abcdutils::clean_plot(headache_p, c("x")),
                abcdutils::clean_plot(mtbi_count_p, c("x")),
                abcdutils::clean_plot(proso_p1, c("x")),
                abcdutils::clean_plot(proso_p2, c("x")),
                abcdutils::clean_plot(proso_p3, c("x")),
                abcdutils::clean_plot(sa_p1, c("x")),
                abcdutils::clean_plot(sa_p2, c("x")),
                abcdutils::clean_plot(sa_p3, c("x")),
                abcdutils::clean_plot(sa_p4, c("x")),
                abcdutils::clean_plot(exercise_p, c("x")),
                abcdutils::clean_plot(interview_age_p, c("x")),
                abcdutils::clean_plot(injury_age_p, c("x")),
                abcdutils::clean_plot(friend_p1, c("x")),
                abcdutils::clean_plot(friend_p2, c("x")),
                abcdutils::clean_plot(friend_p3, c("x")),
                abcdutils::clean_plot(friend_p4, c("x")),
                abcdutils::clean_plot(wknd_screen_p, c("x")),
                abcdutils::clean_plot(wkd_screen_p, c("x")),
                abcdutils::clean_plot(pattern_p, c("x")),
                abcdutils::clean_plot(card_p, c("x")),
                abcdutils::clean_plot(list_p, c("x")),
                abcdutils::clean_plot(pubertal_p, c("x")))
        ggplot2::ggsave(file = g_path, grid, width = 45, height = 30)
    }
}


input_characterization_plots_g(top_oms_0_0_train,
    loc = train_dfs[[1]],
    mechanism = train_dfs[[2]],
    dazed = train_dfs[[3]],
    income = train_dfs[[4]],
    interview_age = train_dfs[[5]],
    mtbi_age = train_dfs[[6]],
    pubertal = train_dfs[[7]],
    race = train_dfs[[8]],
    sex = train_dfs[[9]],
    headache = train_dfs[[10]],
    mtbi_count = train_dfs[[11]],
    wmnd = train_dfs[[12]],
    gord_cor = train_dfs[[13]],
    gord_var = train_dfs[[14]],
    subc_cor = train_dfs[[15]],
    subc_var = train_dfs[[16]],
    cort_sa = train_dfs[[17]],
    cort_t = train_dfs[[18]],
    subc_v = train_dfs[[19]],
    loneliness = train_dfs[[20]],
    screentime = train_dfs[[21]],
    fam_fn = train_dfs[[22]],
    sports = train_dfs[[23]],
    prosocial = train_dfs[[24]],
    parent_psych = train_dfs[[25]],
    exercise = train_dfs[[26]],
    pattern = nihtbx_pattern,
    cardsort = nihtbx_cardsort,
    list = nihtbx_list,
    general_inp_path = fig_path("general_inputs_train.png", date = TRUE),
    rsfmri_path = fig_path("rsfmri_inputs_train.png", date = TRUE),
    other_mri_path = fig_path("other_mri_train.png", date = TRUE),
    other_heatmap_path = fig_path("other_input_train.png", date = TRUE))

test_dfs <- lapply(data_list_test, function(x) x$"data")

#### OLD
## Conversion of propagated labels into an om format
#propagated_om <- propagated_labels |>
#    dplyr::select(-"group") |>
#    t()
#colnames(propagated_om) <- propagated_om[1, ]
#propagated_om <- data.frame(propagated_om[-1, ])
#propagated_om$"significance" <- propagated_labels |>
#    dplyr::select(-c("subjectkey", "group")) |>
#    colnames()
#rownames(propagated_om) <- NULL
#top_oms$"row_id"
#if (all(top_oms$"significance" == propagated_om$"significance")) {
#    propagated_om$"row_id" <- top_oms$"row_id"
#    propagated_om$"nclust" <- top_oms$"nclust"
#}
#propagated_om <- col_to_num_all_possible(propagated_om)
#### END OF OLD
#
#library(tibble)


pl_new <- propagated_labels
pl_new <- pl_new |>
    dplyr::filter(group == "test") |>
    dplyr::select(-"group") |>
    t()
colnames(pl_new) <- pl_new[1, ]
pl_new <- tibble(data.frame(pl_new[-1, ]))
pl_new$"significance" <- propagated_labels |>
    dplyr::select(-c("subjectkey", "group")) |>
    colnames()
rownames(pl_new) <- NULL
top_oms_0_0_train$"row_id"
if (all(top_oms_0_0_train$"significance" == pl_new$"significance")) {
    pl_new$"row_id" <- top_oms_0_0_train$"row_id"
    pl_new$"nclust" <- top_oms_0_0_train$"nclust"
}
pl_new <- col_to_num_all_possible(pl_new)
# Just added 04-18
pl_new <- pl_new[2, ]


pl_new$significance

colnames(pl_new)

colnames(pl_om)

#
#input_characterization_plots_g(pl_new,
#    loc = test_dfs[[1]],
#    mechanism = test_dfs[[2]],
#    dazed = test_dfs[[3]],
#    income = test_dfs[[4]],
#    interview_age = test_dfs[[5]],
#    mtbi_age = test_dfs[[6]],
#    pubertal = test_dfs[[7]],
#    race = test_dfs[[8]],
#    sex = test_dfs[[9]],
#    headache = test_dfs[[10]],
#    mtbi_count = test_dfs[[11]],
#    wmnd = test_dfs[[12]],
#    gord_cor = test_dfs[[13]],
#    gord_var = test_dfs[[14]],
#    subc_cor = test_dfs[[15]],
#    subc_var = test_dfs[[16]],
#    cort_sa = test_dfs[[17]],
#    cort_t = test_dfs[[18]],
#    subc_v = test_dfs[[19]],
#    loneliness = test_dfs[[20]],
#    screentime = test_dfs[[21]],
#    fam_fn = test_dfs[[22]],
#    sports = test_dfs[[23]],
#    prosocial = test_dfs[[24]],
#    parent_psych = test_dfs[[25]],
#    exercise = test_dfs[[26]],
#    pattern = nihtbx_pattern,
#    cardsort = nihtbx_cardsort,
#    list = nihtbx_list,
#    general_inp_path = fig_path("general_inputs_test.png", date = TRUE),
#    rsfmri_path = fig_path("rsfmri_inputs_test.png", date = TRUE),
#    other_mri_path = fig_path("other_mri_test.png", date = TRUE),
#    other_heatmap_path = fig_path("other_input_test.png", date = TRUE))



input_characterization_plots_g(pl_om,
    loc = test_dfs[[1]],
    mechanism = test_dfs[[2]],
    dazed = test_dfs[[3]],
    income = test_dfs[[4]],
    interview_age = test_dfs[[5]],
    mtbi_age = test_dfs[[6]],
    pubertal = test_dfs[[7]],
    race = test_dfs[[8]],
    sex = test_dfs[[9]],
    headache = test_dfs[[10]],
    mtbi_count = test_dfs[[11]],
    wmnd = test_dfs[[12]],
    gord_cor = test_dfs[[13]],
    gord_var = test_dfs[[14]],
    subc_cor = test_dfs[[15]],
    subc_var = test_dfs[[16]],
    cort_sa = test_dfs[[17]],
    cort_t = test_dfs[[18]],
    subc_v = test_dfs[[19]],
    loneliness = test_dfs[[20]],
    screentime = test_dfs[[21]],
    fam_fn = test_dfs[[22]],
    sports = test_dfs[[23]],
    prosocial = test_dfs[[24]],
    parent_psych = test_dfs[[25]],
    exercise = test_dfs[[26]],
    pattern = nihtbx_pattern,
    cardsort = nihtbx_cardsort,
    list = nihtbx_list,
    general_inp_path = fig_path("general_inputs_test.png", date = TRUE),
    rsfmri_path = fig_path("rsfmri_inputs_test.png", date = TRUE),
    other_mri_path = fig_path("other_mri_test.png", date = TRUE),
    other_heatmap_path = fig_path("other_input_test.png", date = TRUE))


plot_om_bar(pl_new, test_dfs[[1]], "latest_mtbi_loc", "LOC")


pl_new

plot_om_bar(pl_new, test_dfs[[9]], "M", "Male")

tibble(test_dfs[[9]])

sex_df <- dplyr::inner_join(get_cluster_df(pl_new), test_dfs[[9]], by = "subjectkey")

sex_df_summary <- sex_df |>
    dplyr::group_by(cluster, M) |>
    dplyr::summarize(count = dplyr::n())

chisq_table <- data.frame(cluster = c(1, 2), M = c(3, 35), F = c(3, 26))

sex_df$cluster <- as.factor(sex_df$cluster)
sex_df$M <- as.factor(sex_df$M)

# n.s.
chisq.test(sex_df$cluster, sex_df$M, correct=FALSE)



lapply(test_dfs, function(x) colnames(x)[2])


pl_new |>
    dplyr::select("significance", "row_id")


sex_df_train <- dplyr::inner_join(get_cluster_df(top_om_uhn), train_dfs[[9]], by = "subjectkey")

sex_df_train

chisq.test(sex_df_train$cluster, sex_df_train$M, correct=FALSE)

# N.S. for sex

# Income
income_df <- dplyr::inner_join(get_cluster_df(pl_new), test_dfs[[4]], by = "subjectkey")

chisq.test(income_df$cluster, income_df$household_income) # p = 1.137e-06


# Pubertal stage
pubertal_df <- dplyr::inner_join(get_cluster_df(pl_new), test_dfs[[7]], by = "subjectkey")

head(pubertal_df)

t.test(pubertal_df$pubertal_status[pubertal_df$cluster == 1], pubertal_df$pubertal_status[pubertal_df$cluster == 2]) # uncorrected p-value of 0.024

# Acitivites in the last year
activities_df <- dplyr::inner_join(get_cluster_df(pl_new), test_dfs[[23]], by = "subjectkey")

head(activities_df)

t.test(activities_df$p12_activities[activities_df$cluster == 1], activities_df$p12_activities[activities_df$cluster == 2]) # uncorrected p-value of 0.00056


cort_sa_df <- dplyr::inner_join(tibble(test_dfs[[17]]), get_cluster_df(pl_new), by = "subjectkey")

cort_sas <- cort_sa_df |>
    dplyr::select(dplyr::starts_with("mrisd")) |>
    rowMeans()

cortsadf <- cbind(get_cluster_df(pl_new), cort_sas)

t_test <- function(df, key_var, group_col, group_1, group_2) {
    group_1_vals <- df[, key_var][df[, group_col] == group_1]
    group_2_vals <- df[, key_var][df[, group_col] == group_2]
    t.test(group_1_vals, group_2_vals)
}

t_test(cortsadf, "cort_sas", "cluster", 1, 2)

library(ggplot2)

cortsadf$cluster <- as.factor(cortsadf$cluster)

ggplot(cortsadf, mapping = aes(x = cluster, y = cort_sas)) +
    geom_violin() +
    geom_jitter(height = 0, width = 0.1)


# subcv

cort_sa_df <- dplyr::inner_join(tibble(test_dfs[[19]]), get_cluster_df(pl_new), by = "subjectkey")


cort_sas <- cort_sa_df |>
    dplyr::select(dplyr::starts_with("smri")) |>
    rowMeans()

cortsadf <- cbind(get_cluster_df(pl_new), cort_sas)

t_test <- function(df, key_var, group_col, group_1, group_2) {
    group_1_vals <- df[, key_var][df[, group_col] == group_1]
    group_2_vals <- df[, key_var][df[, group_col] == group_2]
    t.test(group_1_vals, group_2_vals)
}

t_test(cortsadf, "cort_sas", "cluster", 1, 2)

cortsadf$cluster <- as.factor(cortsadf$cluster)

ggplot(cortsadf, mapping = aes(x = cluster, y = cort_sas)) +
    geom_violin() +
    geom_jitter(height = 0, width = 0.1)

```

Here is a summary of the plots derived above:

- Two-cluster, lowest mean (10):
    - cluster one is consistently worse, but has 3 subjects in impaired cluster
    - general patterns found in previous solutions are still present
- Two-cluster, lowest min (1):
    - same as before, but has 5 subjects in impaired cluster
- Three-cluster, lowest min & mean (60):
    - Only clusters 2 and 3 were predicted in the propagated group
    - **discard this solution**
- Four-cluster, lowest min p-value (71):
    - doesn't seem to generalize well (2 is worst in train, 4 is worst in test)
    - **discard this solution**
- Four-cluster, lowest mean p-value (92):
    - doesn't generalize well, only clusters 2 and 4 were in propagated group
    - **discard this solution**
- Five-cluster, lowest min and mean (98)
    - doesn't generalize well
    - **discard this solution**

So we are left with the 2-cluster solutions only.

The cluster-comparison-tool paper can revisit this and try to select a solution based on optimal generalization. That would lead into cross-validation for clustering quite well!

## Significance testing

```{r}
# Training subjects
cbcl_pvals_0_0_train <- cbcl_ord_reg_from_om(top_oms_0_0_train, cbcl_list_train)


# Testing subjects
cbcl_ord_reg_from_om(pl_new, cbcl_list_full)
```

Because the sample sizes in the allocated test groups are so small, traditional significance testing approaches don't work very well. I use permutation testing moving forward.


```{r}
library(dplyr)

# The solutions of interest based on plots:
two_clust_min <- propagated_labels |>
    dplyr::filter(propagated_labels$"group" == "test") |>
    dplyr::select(-"group") |>
    dplyr::select("subjectkey", "two_clust_min")
colnames(two_clust_min) <- c("subjectkey", "cluster")

two_clust_mean <- propagated_labels |>
    dplyr::filter(propagated_labels$"group" == "test") |>
    dplyr::select(-"group") |>
    dplyr::select("subjectkey", "two_clust_mean")
colnames(two_clust_mean) <- c("subjectkey", "cluster")



two_clust_perm_test_lp <- function(cluster_df, cbcl_list) {
    df_list <- append(list(data.frame(cluster_df)), cbcl_list)
    merged_df <- tibble(merge_df_list(df_list))
    return(merged_df)
}

a <- two_clust_perm_test_lp(two_clust_min, cbcl_list_full)
b <- two_clust_perm_test_lp(two_clust_mean, cbcl_list_full)

# good ~ Healthy
# bad ~ Diseased
# C1 ~ Exposed
# C2 ~ Not exposed

he_good_c1 <- length(which(a$cluster == 1 & a$cbcl_nausea == 0))
de_bad_c1 <- length(which(a$cluster == 1 & a$cbcl_nausea > 0))
hn_good_c2 <- length(which(a$cluster == 2 & a$cbcl_nausea == 0))
dn_bad_c2 <- length(which(a$cluster == 2 & a$cbcl_nausea > 0))

odds_ratio(de = de_bad_c1,
           he = he_good_c1,
           dn = dn_bad_c2,
           hn = hn_good_c2)

odds_ratio <- function(de, he, dn, hn) { # {~
    numerator <- de / he
    denominator <- dn / hn
    return(numerator / denominator)
}
cbcl_or <- function(evaluation_df) {
    cluster <- ""
    bad_outcome <- ""
    or_df <- data.frame(outcome = as.character(),
                        or = as.numeric(),
                        ci_low = as.numeric(),
                        ci_high = as.numeric())
    outcome_names <- evaluation_df |>
        dplyr::select(dplyr::starts_with("cbcl")) |>
        colnames()
    for (i in seq_along(outcome_names)) {
        current_outcome <- outcome_names[i]
        or_summary <- evaluation_df |>
            dplyr::group_by(cluster) |>
            dplyr::count(evaluation_df[, current_outcome] > 0)
        colnames(or_summary) <- c("cluster", "bad_outcome", "n")
        # Calculating odds ratios
        de_bad_c1 <- or_summary |>
            dplyr::filter(cluster == 1 & bad_outcome == TRUE) |>
            dplyr::ungroup() |>
            dplyr::select("n") |>
            as.numeric()
        he_good_c1 <- or_summary |>
            dplyr::filter(cluster == 1 & bad_outcome == FALSE) |>
            dplyr::ungroup() |>
            dplyr::select("n") |>
            as.numeric()
        dn_bad_c2 <- or_summary |>
            dplyr::filter(cluster == 2 & bad_outcome == TRUE) |>
            dplyr::ungroup() |>
            dplyr::select("n") |>
            as.numeric()
        hn_good_c2 <- or_summary |>
            dplyr::filter(cluster == 2 & bad_outcome == FALSE) |>
            dplyr::ungroup() |>
            dplyr::select("n") |>
            as.numeric()
        or <- odds_ratio(de = de_bad_c1,
            he = he_good_c1,
            dn = dn_bad_c2,
            hn = hn_good_c2)
        # Calculating upper and lower bounds
        a_val <- de_bad_c1
        c_val <- dn_bad_c2
        b_val <- he_good_c1
        d_val <- hn_good_c2
        num <- a_val / b_val
        den <- c_val / d_val
        se_ln_or <- sqrt((1 / a_val + 1 / b_val + 1 / c_val + 1 / d_val))
        ln_or <- log(num / den)
        lower <- exp(ln_or - 1.96 * se_ln_or)
        upper <- exp(ln_or + 1.96 * se_ln_or)
        current_df <- data.frame(outcome = current_outcome,
                              or = or,
                              ci_low = lower,
                              ci_high = upper)
        or_df <- rbind(or_df, current_df)
    }
    return(or_df)
} # ~}

# Two clust min
cbcl_or(a)

# Two clust mean
cbcl_or(b)


# Now let's try the permutation testing way

permutation_test <- function(df, param, title = "", save_plot = FALSE) {
    vals1 <- df[, param][df[, "cluster"] == 1]
    vals2 <- df[, param][df[, "cluster"] == 2]
    true_diff <- mean(vals1) - mean(vals2)
    results <- c()
    all_vals <- c(vals1, vals2)
    set.seed(42)
    for (i in 1:10000) {
        number_in_c1 <- 6
        c1_indices <- sample(67, size = number_in_c1)
        c2_indices <- which(!(1:67 %in% c1_indices))
        mock_c1 <- all_vals[c1_indices]
        mock_c2 <- all_vals[c2_indices]
        mean_difference <- mean(mock_c1) - mean(mock_c2)
        results <- c(results, mean_difference)
    }
    print(paste0("The true mean difference: ", signif(true_diff, 2)))
    print("The 5% and 95% percentiles:")
    print(quantile(results, probs = c(0.05, 0.95)))
    p_value <- length(which(results >= true_diff)) / (length(results))
    print(paste0("p-value: ", p_value))
    if (save_plot) {
        png(fig_path(paste0("lp_ptest_", param, ".png"), date = TRUE),
            height = 5,
            width = 5,
            units = "in",
            res = 300)
        par(mar=c(5,6,4,1)+.1)
        hist(results,
             cex.lab = 2,
             cex.axis = 2,
             cex.main = 2,
             cex.sub = 2,
             xlab = "Mean Difference",
             main = title)
        abline(v = true_diff,
            col = "red")
        dev.off()
    } else {
        par(mar=c(5,6,4,1)+.1)
        hist(results,
             cex.lab = 2,
             cex.axis = 2,
             cex.main = 2,
             cex.sub = 2,
             xlab = "Mean Difference",
             main = title)
        abline(v = true_diff,
            col = "red")
    }
}

permutation_test_prop <- function(df, param, title = "", save_plot = FALSE,
                                  prop = FALSE, detail = FALSE) {
    number_in_c1 <- length(which(df$"cluster" == 1))
    vals1 <- df[, param][df[, "cluster"] == 1]
    vals2 <- df[, param][df[, "cluster"] == 2]
    if (prop) {
        prop1 <- (length(which(vals1 > 0))) / (length(vals1))
        prop2 <- (length(which(vals2 > 0))) / (length(vals2))
        true_diff <- prop1 - prop2
    } else {
        true_diff <- mean(vals1) - mean(vals2)
    }
    results <- c()
    all_vals <- c(vals1, vals2)
    set.seed(42)
    for (i in 1:10000) {
        c1_indices <- sample(67, size = number_in_c1)
        c2_indices <- which(!(1:67 %in% c1_indices))
        mock_c1 <- all_vals[c1_indices]
        mock_c2 <- all_vals[c2_indices]
        if (prop) {
            mock_prop1 <- (length(which(mock_c1 > 0))) / (length(mock_c1))
            mock_prop2 <- (length(which(mock_c2 > 0))) / (length(mock_c2))
            mean_difference <- mock_prop1 - mock_prop2
        } else {
            mean_difference <- mean(mock_c1) - mean(mock_c2)
        }
        results <- c(results, mean_difference)
    }
    p_value <- length(which(results >= true_diff)) / (length(results))
    print(paste0("p-value: ", p_value))
    if (detail == TRUE) {
        print(paste0("The true mean difference: ", signif(true_diff, 2)))
        print("The 5% and 95% percentiles:")
        print(quantile(results, probs = c(0.05, 0.95)))
    }
    if (save_plot) {
        png(fig_path(paste0("lp_ptest_", param, ".png"), date = TRUE),
            height = 5,
            width = 5,
            units = "in",
            res = 300)
        par(mar=c(5,6,4,1)+.1)
        hist(results,
             cex.lab = 2,
             cex.axis = 2,
             cex.main = 2,
             cex.sub = 2,
             xlab = "Mean Difference",
             main = title)
        abline(v = true_diff,
            col = "red")
        dev.off()
    } else {
        par(mar=c(5,6,4,1)+.1)
        hist(results,
             cex.lab = 2,
             cex.axis = 2,
             cex.main = 2,
             cex.sub = 2,
             xlab = "Mean Difference",
             main = title)
        abline(v = true_diff,
            col = "red")
    }
    return(p_value)
}

perm_test_all_cbcl <- function(df, prop, detail = FALSE) {
    cbcl_names <- colnames(df)[-c(1, 2)]
    nsig <- 0
    for (name in cbcl_names) {
        print(name)
        pval <- permutation_test_prop(df, name, prop = prop)
        if (pval < 0.05) nsig <- nsig + 1
        cat("\n")
    }
    print(nsig)
}

perm_test_all_cbcl(a, TRUE)

perm_test_all_cbcl(b, TRUE)

perm_test_all_cbcl(a, FALSE)

# Best so far
perm_test_all_cbcl(b, FALSE)

# sleeping more
main_vec <- c(rep(0, 65), rep(1, 2))

all_diffs <- vector()
for (i in 1:10000) {
    this_sample <- sample(main_vec)
    c1 <- this_sample[1:3]
    c2 <- this_sample[4:67]
    l1 <- length(which(c1 > 0)) / length(c1)
    l2 <- length(which(c2 > 0)) / length(c2)
    all_diffs <- c(all_diffs, l1 - l2)
}

length(which(all_diffs > 0)) / length(all_diffs)

all_diffs



this_sample <- sample(main_vec)
c1 <- this_sample[1:3]
c2 <- this_sample[4:67]


l1 - l2


permutation_test_prop(a, "cbcl_aggressive", prop = TRUE)
```
