# Data extraction

Load libraries and establish paths.

```{r}
library(ggplot2)
library(readr)
library(dplyr)
library(here)
library(abcdutils)
library(visdat)
library(tibble)

core_path <- path_maker(here(paste0("data/abcd/core")))
input_path <- path_maker(here(paste0("data/abcd/inputs")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))

read <- function(path) {
    return(abcd_load(core_path(path)))
}

iwrite <- function(data, path) {
    write_csv(data, input_path(path, date = TRUE))
}
```

Import raw data.

```{r}
abcd_p_demo             <- read("abcd-general/abcd_p_demo.csv")
abcd_y_lt               <- read("abcd-general/abcd_y_lt.csv")
ce_p_fes                <- read("culture-environment/ce_p_fes.csv")
ce_p_psb                <- read("culture-environment/ce_p_psb.csv")
ce_y_fes                <- read("culture-environment/ce_y_fes.csv")
ce_y_psb                <- read("culture-environment/ce_y_psb.csv")
gish_p_gi               <- read("gender-identity-sexual-health/gish_p_gi.csv")
mh_p_asr                <- read("mental-health/mh_p_asr.csv")
mh_p_cbcl               <- read("mental-health/mh_p_cbcl.csv")
mh_y_or                 <- read("mental-health/mh_y_or.csv")
mri_y_adm_info          <- read("imaging/mri_y_adm_info.csv")
mri_y_rsfmr_cor_gp_aseg <- read("imaging/mri_y_rsfmr_cor_gp_aseg.csv")
mri_y_rsfmr_cor_gp_gp   <- read("imaging/mri_y_rsfmr_cor_gp_gp.csv")
mri_y_rsi_rnd_at        <- read("imaging/mri_y_rsi_rnd_at.csv")
mri_y_rsi_rnd_wm_dsk    <- read("imaging/mri_y_rsi_rnd_wm_dsk.csv")
mri_y_rsi_rnd_wm_dst    <- read("imaging/mri_y_rsi_rnd_wm_dst.csv")
mri_y_smr_area_dsk      <- read("imaging/mri_y_smr_area_dsk.csv")
mri_y_smr_thk_dsk       <- read("imaging/mri_y_smr_thk_dsk.csv")
mri_y_smr_vol_aseg      <- read("imaging/mri_y_smr_vol_aseg.csv")
nt_p_stq                <- read("novel-technologies/nt_p_stq.csv")
ph_p_mhx                <- read("physical-health/ph_p_mhx.csv")
ph_p_otbi               <- read("physical-health/ph_p_otbi.csv")
ph_p_pds                <- read("physical-health/ph_p_pds.csv")
ph_p_saiq               <- read("physical-health/ph_p_saiq.csv")
ph_p_sds                <- read("physical-health/ph_p_sds.csv")
ph_y_pds                <- read("physical-health/ph_y_pds.csv")
ph_y_yrb                <- read("physical-health/ph_y_yrb.csv")
```

## Subjects

There are three broad subject groups:

- base mtbi: those who have had an mTBI pre-baseline (we could just collect outcome data)
- long mtbi: those who have had only an mTBI post-baseline but pre-2yfu
- base unij: those who have had no mTBI or worse as of baseline, including:
    - matched uninjured
    - longitudinal uninjured (those who have had no mTBI or worse as of 2yfu)

We will now look at:

1. (A: "mtbi_subjects.csv") longitudinal data for baseline mTBI subjects
    - What happened to them after 2 years?
    - How informative was the baseline clustering?

2. (B: "uninjured_subjects.csv" that are NOT in C) longitudinal data for *some* baseline uninj subjects. It's okay if they had injuries.
    - used as context for #3

3. (C) longitudinal data for baseline outcome matched uninjured subjects. It's okay if they had injuries.
    - did they experience more mTBIs than the other uninjured subjects (#2)?

4. (D: longitudinal mTBI / "mtbi_subjects_0_to_2.csv") baseline data for longitudinal mTBI subjects
    - Does the baseline clustering assignment predict their long term outcomes?
    - Did they have bad outcomes right out of the gates compared to baseline matched uninjured controls?

5. (D: longitudinal mTBI / "mtbi_subjects_0_to_2.csv") longitudinal data for longitudinal mTBI subjects
    - used as context for #1

6. (E: longitudinal uninjured / "uninjured_subjects_0_to_2.csv") baseline data for longitudinal uninjured subjects
    - with #4, used as context for #1 and #2?

7. (E: "uninjured_subjects_0_to_2.csv") Long uninj subjects, long
    - with #3, used as context for #1 and #2?

The relevant times already collected for these longitudinal analyses are:
1. baseline mTBI subjects, baseline (already collected)
2. baseline uninj subjects, baseline (already collected)
3. baseline outcome matched uninj subjects, baseline (already collected)

And in later chapters, if clustering results are good, I'll make a classifier to predict cluster from raw data.

```{r}
# subs who had an mTBI as of baseline timepoint (regardless of chronic tp)
mtbi_subs_t0 <- get_mtbi_subjects(
    ph_p_otbi,
    abcd_y_lt,
    min_mpi = 0,
    t = 0
) |>
    dplyr::select(subjectkey) |>
    unlist() |>
    as.character()

mtbi_subs_t0 # 446 kids

# subs who had an mTBI based on year 1 follow up data
mtbi_subs_t1 <- get_mtbi_subjects(
    ph_p_otbi,
    abcd_y_lt,
    min_mpi = 0,
    t = 1
) |>
    dplyr::select(subjectkey) |>
    unlist() |>
    as.character()

mtbi_subs_t1 # 133

sum(mtbi_subs_t1 %in% mtbi_subs_t0)
sum(mtbi_subs_t0 %in% mtbi_subs_t1)

# subs who had an mTBI based on the year 2 follow up data
mtbi_subs_t2 <- get_mtbi_subjects(
    ph_p_otbi,
    abcd_y_lt,
    min_mpi = 0,
    t = 2
) |>
    dplyr::select(subjectkey) |>
    unlist() |>
    as.character()

mtbi_subs_t2 # 143

# subs who had an mtbi pre-1yfu, but not pre-baseline (t1 only)
mtbi_subs_t1o <- mtbi_subs_t1[!mtbi_subs_t1 %in% mtbi_subs_t0]

# subs who had an mtbi between 1yfu and 2yfu, but not pre-baseline (t2 only)
mtbi_subs_t2o <- mtbi_subs_t2[!mtbi_subs_t2 %in% mtbi_subs_t0]

# subs who had an mtbi pre-2yfu but not pre-baseline
mtbi_subs_0_to_2 <- unique(c(mtbi_subs_t1o, mtbi_subs_t2o))

write_subjects(
    mtbi_subs_t1,
    sub_path("mtbi_subs_t1.csv", TRUE)
)

write_subjects(
    mtbi_subs_t2,
    sub_path("mtbi_subs_t2.csv", TRUE)
)

write_subjects(
    mtbi_subs_0_to_2,
    sub_path("mtbi_subs_0_to_2.csv", TRUE)
)

# Subjects who had no mtbi or worse pre-baseline
unij_subs_t0 <- get_uninjured_subjects(ph_p_otbi, abcd_y_lt, t = 0) |>
    dplyr::select(subjectkey) |>
    unlist() |>
    as.character()

# Subjects who had no mtbi or worse between baseline and 1yfu
unij_subs_t1 <- get_uninjured_subjects(ph_p_otbi, abcd_y_lt, t = 1) |>
    dplyr::select(subjectkey) |>
    unlist() |>
    as.character()

# Subjects who had no mtbi or worse between 1yfu and 2yfu
unij_subs_t2 <- get_uninjured_subjects(ph_p_otbi, abcd_y_lt, t = 2) |>
    dplyr::select(subjectkey) |>
    unlist() |>
    as.character()

# Subjects who had no mtbi or worse as of 2yfu
unij_subs_0_to_2 <- Reduce(
    intersect,
    list(
        unij_subs_t0,
        unij_subs_t1,
        unij_subs_t2
    )
)

# Exporting those subjects
write_subjects(
    unij_subs_0_to_2,
    sub_path("unij_subs_0_to_2.csv", TRUE)
)
```

```{r}
# CHECKPOINT
mtbi_subs_t1 <- read_subjects(
    sub_path("2025_06_09_mtbi_subs_t1.csv")
)

mtbi_subs_t2 <- read_subjects(
    sub_path("2025_06_09_mtbi_subs_t2.csv")
)

# Longitudinal mTBI subjects
lmtb_subs <- read_subjects(
    sub_path("2025_06_09_mtbi_subs_0_to_2.csv")
)

# Longitudinal uninjured subjects
lunj_subs <- read_subjects(
    sub_path("2025_06_09_unij_subs_0_to_2.csv")
)

# The original baseline sample:
mtbi_subs <- read_subjects(sub_path("2025_05_22_mtbi_subs.csv"))
unij_subs <- read_subjects(sub_path("2025_05_22_unij_subs.csv"))
```

Checking when each injured subject should have their injury info collected:

```{r}
# subs who should have their injury information collected from t1
t1_latest <- lmtb_subs[!lmtb_subs %in% mtbi_subs_t2]
length(t1_latest) # N = 92

# subs who should have their injury information collected from t2
t2_latest <- lmtb_subs[lmtb_subs %in% mtbi_subs_t2]
length(t2_latest) # N = 128
```

Note that for data only present at baseline, I only collect that data for the longitudinal mTBI sample at the T0 timepoint.
It has already been collected for the baseline mTBI and unijured samples, and the longitudinal unijured sample is just a subset of the baseline unijured sample.

## Input variables

### Acute symptoms

#### Feeling dazed

```{r}
lmtb_as_mem_daze_l1 <- get_mtbi_mem_daze(
    ph_p_otbi,
    abcd_y_lt,
    t1_latest,
    t = 1
)

lmtb_as_mem_daze_l2 <- get_mtbi_mem_daze(
    ph_p_otbi,
    abcd_y_lt,
    t2_latest,
    t = 2
)

lmtb_as_mem_daze_l <- rbind(
    lmtb_as_mem_daze_l1,
    lmtb_as_mem_daze_l2
)
tibble(lmtb_as_mem_daze_l)
iwrite(lmtb_as_mem_daze_l, "lmtb_as_mem_daze_l.csv")
```

#### Mechanism of injury

```{r}
lmtb_as_mechanism_l1 <- get_mtbi_mechanism(
    ph_p_otbi,
    abcd_y_lt,
    t1_latest,
    t = 1
)

lmtb_as_mechanism_l2 <- get_mtbi_mechanism(
    ph_p_otbi,
    abcd_y_lt,
    t2_latest,
    t = 2
)

lmtb_as_mechanism_l <- rbind(
    lmtb_as_mechanism_l1,
    lmtb_as_mechanism_l2
)
tibble(lmtb_as_mechanism_l)
iwrite(lmtb_as_mechanism_l, "lmtb_as_mechanism_l.csv")
```

#### Loss of consciousness

```{r}
lmtb_as_loc_l1 <- get_mtbi_loc(
    ph_p_otbi,
    abcd_y_lt,
    t1_latest,
    t = 1
)

lmtb_as_loc_l2 <- get_mtbi_loc(
    ph_p_otbi,
    abcd_y_lt,
    t2_latest,
    t = 2
)

lmtb_as_loc_l <- rbind(
    lmtb_as_loc_l1,
    lmtb_as_loc_l2
)
tibble(lmtb_as_loc_l)
iwrite(lmtb_as_loc_l, "lmtb_as_loc_l.csv")
```

Now we move on to (mostly) features that are present among all subjects.

Checklist of extraction points I should be collecting (see line 57):

Previously:
- [x] baseline mtbi, baseline
- [x] baseline unijured, baseline
    - this includes the matched subjects

Now:
- [ ] baseline subjects, 2yfu
- [ ] baseline unijured, 2yfu
    - this includes the longitudinal unijured
- [ ] longitudinal mtbi, baseline
- [ ] longitudinal mtbi, 2yfu

### Demographics

Demographic variables included in the analyses are:

* Interview age
* Injury age
* Sex
* Race
* Household income
* Pubertal status

#### Interview age

1. A: long_mtbi_0
2. B: long_mtbi_l
3. C: base_mtbi_l
4. D: base_unij_l

```{r}
# A: longitudinal mTBI, baseline timepoint
lmtb_d_interview_age_0 <- get_interview_age(
    abcd_y_lt,
    lmtb_subs,
    t = 0,
    as_years = FALSE
)
tibble(lmtb_d_interview_age_0)
iwrite(lmtb_d_interview_age_0, "lmtb_d_interview_age_0.csv")

# B: longitudinal mTBI, longitudinal timepoint
lmtb_d_interview_age_l <- get_interview_age(
    abcd_y_lt,
    lmtb_subs,
    t = 2,
    as_years = FALSE
)
tibble(lmtb_d_interview_age_l)
iwrite(lmtb_d_interview_age_l, "lmtb_d_interview_age_l.csv")

# C: baseline mTBI, longitudinal timepoint
mtbi_d_interview_age_l <- get_interview_age(
    abcd_y_lt,
    mtbi_subs,
    t = 2,
    as_years = FALSE
)
tibble(mtbi_d_interview_age_l)
iwrite(mtbi_d_interview_age_l, "mtbi_d_interview_age_l.csv")

# baseline uninjured, longitudinal timepoint
unij_d_interview_age_l <- get_interview_age(
    abcd_y_lt,
    unij_subs,
    t = 2,
    as_years = FALSE
)
tibble(unij_d_interview_age_l)
iwrite(unij_d_interview_age_l, "unij_d_interview_age_l.csv")
```


#### Injury age

This is only relevant for the longitudinal mTBI group.

```{r}
mtbi_d_mtbi_age_l1 <- get_mtbi_age(
    ph_p_otbi,
    abcd_y_lt,
    t1_latest,
    t = 1,
    as_years = FALSE
)

mtbi_d_mtbi_age_l2 <- get_mtbi_age(
    ph_p_otbi,
    abcd_y_lt,
    t2_latest,
    t = 2,
    as_years = FALSE
)

# B: longitudinal mTBI, longitudinal timepoint
lmtb_d_mtbi_age_l <- rbind(mtbi_d_mtbi_age_l1, mtbi_d_mtbi_age_l2)
tibble(lmtb_d_mtbi_age_l)
iwrite(lmtb_d_mtbi_age_l, "lmtb_d_mtbi_age_l.csv")
```

#### Sex at birth

Data only present at baseline.
We already have sex for the baseline mTBI and baseline unijured groups.

```{r}
# A: longitudinal mTBI, baseline timepoint
lmtb_d_sex_0 <- get_sex(gish_p_gi, lmtb_subs, t = 0, as_numeric = TRUE)
tibble(lmtb_d_sex_0)
iwrite(lmtb_d_sex_0, "lmtb_d_sex_0.csv")
```

#### Household income

```{r}
# A: longitudinal mTBI, baseline timepoint
lmtb_d_income_0 <- get_income(abcd_p_demo, lmtb_subs, t = 0)
tibble(lmtb_d_income_0)
iwrite(lmtb_d_income_0, "lmtb_d_income_0.csv")

# B: longitudinal mTBI, longitudinal timepoint
lmtb_d_income_l <- get_income(abcd_p_demo, lmtb_subs, t = 2)
tibble(lmtb_d_income_l)
iwrite(lmtb_d_income_l, "lmtb_d_income_l.csv")

# C: baseline mTBI, longitudinal timepoint
mtbi_d_income_l <- get_income(abcd_p_demo, mtbi_subs, t = 2)
tibble(mtbi_d_income_l)
iwrite(mtbi_d_income_l, "mtbi_d_income_l.csv")

# D: baseline uninjured, longitudinal timepoint
unij_d_income_l <- get_income(abcd_p_demo, unij_subs, t = 2)
tibble(unij_d_income_l)
iwrite(unij_d_income_l, "unij_d_income_l.csv")
```

#### Race

Data only present at baseline.

```{r}
# A: longitudinal mTBI, baseline timepoint
lmtb_d_race_0 <- get_race(
    abcd_p_demo,
    lmtb_subs,
    asian_as_other = TRUE,
    t = 0
)
tibble(lmtb_d_race_0)
iwrite(lmtb_d_race_0, "lmtb_d_race_0.csv")
```

#### Pubertal status

```{r}
lmtb_d_pubertal_status_p_0 <- get_pubertal_status_p(
    ph_p_pds,
    lmtb_subs,
    max_value = 3,
    t = 0
)

lmtb_d_pubertal_status_y_0 <- get_pubertal_status_y(
    ph_y_pds,
    lmtb_subs,
    max_value = 3,
    t = 0
)

# A: longitudinal mTBI, baseline timepoint
lmtb_d_pubertal_status_0 <- dplyr::inner_join(
    lmtb_d_pubertal_status_p_0,
    lmtb_d_pubertal_status_y_0
)
tibble(lmtb_d_pubertal_status_0)
iwrite(lmtb_d_pubertal_status_0, "lmtb_d_pubertal_status_0.csv")

lmtb_d_pubertal_status_p_l <- get_pubertal_status_p(
    ph_p_pds,
    lmtb_subs,
    max_value = 4,
    t = 2
)
lmtb_d_pubertal_status_y_l <- get_pubertal_status_y(
    ph_y_pds,
    lmtb_subs,
    max_value = 4,
    t = 2
)

# B: longitudinal mTBI, longitudinal timepoint
lmtb_d_pubertal_status_l <- dplyr::inner_join(
    lmtb_d_pubertal_status_p_l,
    lmtb_d_pubertal_status_y_l
)
tibble(lmtb_d_pubertal_status_l)
iwrite(lmtb_d_pubertal_status_l, "lmtb_d_pubertal_status_l.csv")

mtbi_d_pubertal_status_p_l <- get_pubertal_status_p(
    ph_p_pds,
    mtbi_subs,
    max_value = 4,
    t = 2
)

mtbi_d_pubertal_status_y_l <- get_pubertal_status_y(
    ph_y_pds,
    mtbi_subs,
    max_value = 4,
    t = 2
)

# C: baseline mTBI, longitudinal timepoint
mtbi_d_pubertal_status_l <- dplyr::inner_join(
    mtbi_d_pubertal_status_p_l,
    mtbi_d_pubertal_status_y_l
)
tibble(mtbi_d_pubertal_status_l)
iwrite(mtbi_d_pubertal_status_l, "mtbi_d_pubertal_status_l.csv")

unij_d_pubertal_status_p_l <- get_pubertal_status_p(
    ph_p_pds,
    unij_subs,
    max_value = 4,
    t = 2
)

unij_d_pubertal_status_y_l <- get_pubertal_status_y(
    ph_y_pds,
    unij_subs,
    max_value = 4,
    t = 2
)

# D: baseline uninjured, longitudinal timepoint
unij_d_pubertal_status_l <- dplyr::inner_join(
    unij_d_pubertal_status_p_l,
    unij_d_pubertal_status_y_l
)
tibble(unij_d_pubertal_status_l)
iwrite(unij_d_pubertal_status_l, "unij_d_pubertal_status_l.csv")
```

### Medical history

Medical history variables of interest include:

1. Number of previous head injuries
2. History of headaches (binary)

#### History of headaches

```{r}
# A: longitudinal mTBI, baseline timepoint
lmtb_mh_headaches_0 <- get_headaches(ph_p_mhx, lmtb_subs, t = 0)
tibble(lmtb_mh_headaches_0)
iwrite(lmtb_mh_headaches_0, "lmtb_mh_headaches_0.csv")

# B: longitudinal mTBI, longitudinal timepoint
lmtb_mh_headaches_l <- get_headaches(ph_p_mhx, lmtb_subs, t = 2)
tibble(lmtb_mh_headaches_l)
iwrite(lmtb_mh_headaches_l, "lmtb_mh_headaches_l.csv")

# C: baseline mTBI, longitudinal timepoint
mtbi_mh_headaches_l <- get_headaches(ph_p_mhx, mtbi_subs, t = 2)
tibble(mtbi_mh_headaches_l)
iwrite(mtbi_mh_headaches_l, "mtbi_mh_headaches_l.csv")

# D: baseline uninjured, longitudinal timepoint
unij_mh_headaches_l <- get_headaches(ph_p_mhx, unij_subs, t = 2)
tibble(unij_mh_headaches_l)
iwrite(unij_mh_headaches_l, "unij_mh_headaches_l.csv")
```

#### Number of previous mTBIs

```{r}
# N = 4 and 5 only occur once
lmtb_mh_mtbi_count_t1 <- get_mtbi_count(
    ph_p_otbi,
    abcd_y_lt,
    lmtb_subs,
    cutoff = 6,
    t = 1
)

# N = 4 and 5 only occur once
lmtb_mh_mtbi_count_t2 <- get_mtbi_count(
    ph_p_otbi,
    abcd_y_lt,
    lmtb_subs,
    cutoff = 6,
    t = 2
)

# B: longitudinal mTBI, longitudinal timepoint
lmtb_mh_mtbi_count_l <- dplyr::full_join(
    lmtb_mh_mtbi_count_t1,
    lmtb_mh_mtbi_count_t2,
    by = "subjectkey"
) |>
    dplyr::rowwise() |>
    dplyr::mutate(
        mtbi_count = sum(mtbi_count.x, mtbi_count.y, na.rm = TRUE),
        .keep = "unused"
    ) |>
    dplyr::ungroup()
head(lmtb_mh_mtbi_count_l)
iwrite(lmtb_mh_mtbi_count_l, "lmtb_mh_mtbi_count_l.csv")
```

### Neuroimaging

#### Structural MRI

##### Subcortical volume

```{r}
# A: longitudinal mTBI, baseline timepoint
lmtb_sm_subc_v_0 <- get_subc_v(mri_y_smr_vol_aseg, lmtb_subs, t = 0)
tibble(lmtb_sm_subc_v_0)
iwrite(lmtb_sm_subc_v_0, "lmtb_sm_subc_v_0.csv")

# B: longitudinal mTBI, longitudinal timepoint
lmtb_sm_subc_v_l <- get_subc_v(mri_y_smr_vol_aseg, lmtb_subs, t = 2)
tibble(lmtb_sm_subc_v_l)
iwrite(lmtb_sm_subc_v_l, "lmtb_sm_subc_v_l.csv")

# C: baseline mTBI, longitudinal timepoint
mtbi_sm_subc_v_l <- get_subc_v(mri_y_smr_vol_aseg, mtbi_subs, t = 2)
tibble(mtbi_sm_subc_v_l)
iwrite(mtbi_sm_subc_v_l, "mtbi_sm_subc_v_l.csv")

# D: baseline uninjured, longitudinal timepoint
unij_sm_subc_v_l <- get_subc_v(mri_y_smr_vol_aseg, unij_subs, t = 2)
tibble(unij_sm_subc_v_l)
iwrite(unij_sm_subc_v_l, "unij_sm_subc_v_l.csv")
```

##### Cortical thickness

Both the Desikan and Destrieux cortical parcellations could have been used for the cortical imaging data collected below.
A comparison between the two can be found in the appendix.
Because there happens to be a few more participants with calculated Desikan parcellations, that is what is used here.

```{r}
# A: longitudinal mTBI, baseline timepoint
lmtb_sm_cort_t_0 <- get_cort_t(mri_y_smr_thk_dsk, lmtb_subs, t = 0)
tibble(lmtb_sm_cort_t_0)
iwrite(lmtb_sm_cort_t_0, "lmtb_sm_cort_t_0.csv")

# B: longitudinal mTBI, longitudinal timepoint
lmtb_sm_cort_t_l <- get_cort_t(mri_y_smr_thk_dsk, lmtb_subs, t = 2)
tibble(lmtb_sm_cort_t_l)
iwrite(lmtb_sm_cort_t_l, "lmtb_sm_cort_t_l.csv")

# C: baseline mTBI, longitudinal timepoint
mtbi_sm_cort_t_l <- get_cort_t(mri_y_smr_thk_dsk, mtbi_subs, t = 2)
tibble(mtbi_sm_cort_t_l)
iwrite(mtbi_sm_cort_t_l, "mtbi_sm_cort_t_l.csv")

# D: baseline uninjured, longitudinal timepoint
unij_sm_cort_t_l <- get_cort_t(mri_y_smr_thk_dsk, unij_subs, t = 2)
tibble(unij_sm_cort_t_l)
iwrite(unij_sm_cort_t_l, "unij_sm_cort_t_l.csv")
```

##### Cortical surface areas

```{r}
# A: longitudinal mTBI, baseline timepoint
lmtb_sm_cort_sa_0 <- get_cort_sa(mri_y_smr_area_dsk, lmtb_subs, t = 0)
tibble(lmtb_sm_cort_sa_0)
iwrite(lmtb_sm_cort_sa_0, "lmtb_sm_cort_sa_0.csv")

# B: longitudinal mTBI, longitudinal timepoint
lmtb_sm_cort_sa_l <- get_cort_sa(mri_y_smr_area_dsk, lmtb_subs, t = 2)
tibble(lmtb_sm_cort_sa_l)
iwrite(lmtb_sm_cort_sa_l, "lmtb_sm_cort_sa_l.csv")

# C: baseline mTBI, longitudinal timepoint
mtbi_sm_cort_sa_l <- get_cort_sa(mri_y_smr_area_dsk, mtbi_subs, t = 2)
tibble(mtbi_sm_cort_sa_l)
iwrite(mtbi_sm_cort_sa_l, "mtbi_sm_cort_sa_l.csv")

# D: baseline uninjured, longitudinal timepoint
unij_sm_cort_sa_l <- get_cort_sa(mri_y_smr_area_dsk, unij_subs, t = 2)
tibble(unij_sm_cort_sa_l)
iwrite(unij_sm_cort_sa_l, "unij_sm_cort_sa_l.csv")
```

#### Diffusion MRI

##### White matter neurite densities

```{r}
# A: longitudinal mTBI, baseline timepoint
lmtb_dm_wmnd_0 <- get_wmnd(
    mri_y_rsi_rnd_at,
    mri_y_rsi_rnd_wm_dsk,
    lmtb_subs,
    t = 0
)
tibble(lmtb_dm_wmnd_0)
iwrite(lmtb_dm_wmnd_0, "lmtb_dm_wmnd_0.csv")

# B: longitudinal mTBI, longitudinal timepoint
lmtb_dm_wmnd_l <- get_wmnd(
    mri_y_rsi_rnd_at,
    mri_y_rsi_rnd_wm_dsk,
    lmtb_subs,
    t = 2
)
tibble(lmtb_dm_wmnd_l)
iwrite(lmtb_dm_wmnd_l, "lmtb_dm_wmnd_l.csv")

# C: baseline mTBI, longitudinal timepoint
mtbi_dm_wmnd_l <- get_wmnd(
    mri_y_rsi_rnd_at,
    mri_y_rsi_rnd_wm_dsk,
    mtbi_subs,
    t = 2
)
tibble(mtbi_dm_wmnd_l)
iwrite(mtbi_dm_wmnd_l, "mtbi_dm_wmnd_l.csv")

# D: baseline uninjured, longitudinal timepoint
unij_dm_wmnd_l <- get_wmnd(
    mri_y_rsi_rnd_at,
    mri_y_rsi_rnd_wm_dsk,
    unij_subs,
    t = 2
)
tibble(unij_dm_wmnd_l)
iwrite(unij_dm_wmnd_l, "unij_dm_wmnd_l.csv")
```

#### Resting-state functional MRI

We are interested in the following rs-fMRI measures:

- Gordon network (cortical) correlations
- Subcortical correlations

##### Cortical parcellation network correlations

```{r}
# A: longitudinal mTBI, baseline timepoint
lmtb_rm_gord_cor_0 <- get_gord_cor(mri_y_rsfmr_cor_gp_gp, lmtb_subs, t = 0)
tibble(lmtb_rm_gord_cor_0)
iwrite(lmtb_rm_gord_cor_0, "lmtb_rm_gord_cor_0.csv")

#: B: longitudinal mTBI, longitudinal timepoint
lmtb_rm_gord_cor_l <- get_gord_cor(mri_y_rsfmr_cor_gp_gp, lmtb_subs, t = 2)
tibble(lmtb_rm_gord_cor_l)
iwrite(lmtb_rm_gord_cor_l, "lmtb_rm_gord_cor_l.csv")

# C: baseline mTBI, longitudinal timepoint
mtbi_rm_gord_cor_l <- get_gord_cor(mri_y_rsfmr_cor_gp_gp, mtbi_subs, t = 2)
tibble(mtbi_rm_gord_cor_l)
iwrite(mtbi_rm_gord_cor_l, "mtbi_rm_gord_cor_l.csv")

# D: baseline uninjured, longitudinal timepoint
unij_rm_gord_cor_l <- get_gord_cor(mri_y_rsfmr_cor_gp_gp, unij_subs, t = 2)
tibble(unij_rm_gord_cor_l)
iwrite(unij_rm_gord_cor_l, "unij_rm_gord_cor_l.csv")
```

##### Subcortical parcellation network correlations

```{r}
# A: longitudinal mTBI, baseline timepoint
lmtb_rm_subc_cor_0 <- get_subc_cor(mri_y_rsfmr_cor_gp_aseg, lmtb_subs, t = 0)
tibble(lmtb_rm_subc_cor_0)
iwrite(lmtb_rm_subc_cor_0, "lmtb_rm_subc_cor_0.csv")

# B: longitudinal mTBI, longitudinal timepoint
lmtb_rm_subc_cor_l <- get_subc_cor(mri_y_rsfmr_cor_gp_aseg, lmtb_subs, t = 2)
tibble(lmtb_rm_subc_cor_l)
iwrite(lmtb_rm_subc_cor_l, "lmtb_rm_subc_cor_l.csv")

# C: baseline mTBI, longitudinal timepoint
mtbi_rm_subc_cor_l <- get_subc_cor(mri_y_rsfmr_cor_gp_aseg, mtbi_subs, t = 2)
tibble(mtbi_rm_subc_cor_l)
iwrite(mtbi_rm_subc_cor_l, "mtbi_rm_subc_cor_l.csv")

# D: baseline uninjured, longitudinal timepoint
unij_rm_subc_cor_l <- get_subc_cor(mri_y_rsfmr_cor_gp_aseg, unij_subs, t = 2)
tibble(unij_rm_subc_cor_l)
iwrite(unij_rm_subc_cor_l, "unij_rm_subc_cor_l.csv")
```

### Psychosocial resilience

Psychosocial factors of interest include:

#### Loneliness

```{r}
# A: longitudinal mTBI, baseline timepoint
lmtb_p_friends_0 <- get_friends(
    mh_y_or,
    gish_p_gi,
    lmtb_subs,
    discretize = TRUE,
    t = 0
)
tibble(lmtb_p_friends_0)
iwrite(lmtb_p_friends_0, "lmtb_p_friends_0.csv")

# B: longitudinal mTBI, longitudinal timepoint
lmtb_p_friends_l <- get_friends(
    mh_y_or,
    gish_p_gi,
    lmtb_subs,
    discretize = TRUE,
    t = 2
)
tibble(lmtb_p_friends_l)
iwrite(lmtb_p_friends_l, "lmtb_p_friends_l.csv")

# C: baseline mTBI, longitudinal timepoint
mtbi_p_friends_l <- get_friends(
    mh_y_or,
    gish_p_gi,
    mtbi_subs,
    discretize = TRUE,
    t = 2
)
tibble(mtbi_p_friends_l)
iwrite(mtbi_p_friends_l, "mtbi_p_friends_l.csv")

# D: baseline uninjured, longitudinal timepoint
unij_p_friends_l <- get_friends(
    mh_y_or,
    gish_p_gi,
    unij_subs,
    discretize = TRUE,
    t = 2
)
tibble(unij_p_friends_l)
iwrite(unij_p_friends_l, "unij_p_friends_l.csv")
```

#### Healthy behaviours

##### Screen time

```{r}
# A: longitudinal mTBI, baseline timepoint
lmtb_p_screen_time_0 <- get_screen_time(nt_p_stq, lmtb_subs, t = 0)
tibble(lmtb_p_screen_time_0)
iwrite(lmtb_p_screen_time_0, "lmtb_p_screen_time_0.csv")

# B: longitudinal mTBI, longitudinal timepoint
lmtb_p_screen_time_l <- get_screen_time(nt_p_stq, lmtb_subs, t = 2)
tibble(lmtb_p_screen_time_l)
iwrite(lmtb_p_screen_time_l, "lmtb_p_screen_time_l.csv")

# C: baseline mTBI, longitudinal timepoint
mtbi_p_screen_time_l <- get_screen_time(nt_p_stq, mtbi_subs, t = 2)
tibble(mtbi_p_screen_time_l)
iwrite(mtbi_p_screen_time_l, "mtbi_p_screen_time_l.csv")

# D: baseline uninjured, longitudinal timepoint
unij_p_screen_time_l <- get_screen_time(nt_p_stq, unij_subs, t = 2)
tibble(unij_p_screen_time_l)
iwrite(unij_p_screen_time_l, "unij_p_screen_time_l.csv")
```

##### Sports and activities participation

```{r}
# A: longitudinal mTBI, baseline timepoint
lmtb_p_sports_0 <- get_sports_and_activities(
    ph_p_saiq,
    lmtb_subs,
    t = 0,
    discretize = TRUE
)
tibble(lmtb_p_sports_0)
iwrite(lmtb_p_sports_0, "lmtb_p_sports_0.csv")

# B: longitudinal mTBI, longitudinal timepoint
lmtb_p_sports_l <- get_sports_and_activities(
    ph_p_saiq,
    lmtb_subs,
    t = 2,
    discretize = TRUE
)
tibble(lmtb_p_sports_l)
iwrite(lmtb_p_sports_l, "lmtb_p_sports_l.csv")

# C: baseline mTBI, longitudinal timepoint
mtbi_p_sports_l <- get_sports_and_activities(
    ph_p_saiq,
    mtbi_subs,
    t = 2,
    discretize = TRUE
)
tibble(mtbi_p_sports_l)
iwrite(mtbi_p_sports_l, "mtbi_p_sports_l.csv")

# D: baseline uninjured, longitudinal timepoint
unij_p_sports_l <- get_sports_and_activities(
    ph_p_saiq,
    unij_subs,
    t = 2,
    discretize = TRUE
)
tibble(unij_p_sports_l)
iwrite(unij_p_sports_l, "unij_p_sports_l.csv")
```

##### Exercise habits

```{r}
# A: longitudinal mTBI, baseline timepoint
lmtb_p_exercise_0 <- get_exercise(ph_y_yrb, lmtb_subs, t = 0)
tibble(lmtb_p_exercise_0)
iwrite(lmtb_p_exercise_0, "lmtb_p_exercise_0.csv")

# B: longitudinal mTBI, longitudinal timepoint
lmtb_p_exercise_l <- get_exercise(ph_y_yrb, lmtb_subs, t = 2)
tibble(lmtb_p_exercise_l)
iwrite(lmtb_p_exercise_l, "lmtb_p_exercise_l.csv")

# C: baseline mTBI, longitudinal timepoint
mtbi_p_exercise_l <- get_exercise(ph_y_yrb, mtbi_subs, t = 2)
tibble(mtbi_p_exercise_l)
iwrite(mtbi_p_exercise_l, "mtbi_p_exercise_l.csv")

# D: baseline uninjured, longitudinal timepoint
unij_p_exercise_l <- get_exercise(ph_y_yrb, unij_subs, t = 2)
tibble(unij_p_exercise_l)
iwrite(unij_p_exercise_l, "unij_p_exercise_l.csv")
```

#### Prosocial behaviour

```{r}
# A: longitudinal mTBI, baseline timepoint
lmtb_p_prosocial_p_0 <- get_prosocial_behaviour_p(ce_p_psb, lmtb_subs, t = 0)
lmtb_p_prosocial_y_0 <- get_prosocial_behaviour_y(ce_y_psb, lmtb_subs, t = 0)
lmtb_p_prosocial_0 <- dplyr::inner_join(
    lmtb_p_prosocial_p_0,
    lmtb_p_prosocial_y_0
)
tibble(lmtb_p_prosocial_0)
iwrite(lmtb_p_prosocial_0, "lmtb_p_prosocial_0.csv")

# B: longitudinal mTBI, longitudinal timepoint
lmtb_p_prosocial_p_l <- get_prosocial_behaviour_p(ce_p_psb, lmtb_subs, t = 2)
lmtb_p_prosocial_y_l <- get_prosocial_behaviour_y(ce_y_psb, lmtb_subs, t = 2)
lmtb_p_prosocial_l <- dplyr::inner_join(
    lmtb_p_prosocial_p_l,
    lmtb_p_prosocial_y_l
)
tibble(lmtb_p_prosocial_l)
iwrite(lmtb_p_prosocial_l, "lmtb_p_prosocial_l.csv")

# C: baseline mTBI, longitudinal timepoint
mtbi_p_prosocial_p_l <- get_prosocial_behaviour_p(ce_p_psb, mtbi_subs, t = 2)
mtbi_p_prosocial_y_l <- get_prosocial_behaviour_y(ce_y_psb, mtbi_subs, t = 2)
mtbi_p_prosocial_l <- dplyr::inner_join(
    mtbi_p_prosocial_p_l,
    mtbi_p_prosocial_y_l
)
tibble(mtbi_p_prosocial_l)
iwrite(mtbi_p_prosocial_l, "mtbi_p_prosocial_l.csv")

# D: baseline uninjured, longitudinal timepoint
unij_p_prosocial_p_l <- get_prosocial_behaviour_p(ce_p_psb, unij_subs, t = 2)
unij_p_prosocial_y_l <- get_prosocial_behaviour_y(ce_y_psb, unij_subs, t = 2)
unij_p_prosocial_l <- dplyr::inner_join(
    unij_p_prosocial_p_l,
    unij_p_prosocial_y_l
)
tibble(unij_p_prosocial_l)
iwrite(unij_p_prosocial_l, "unij_p_prosocial_l.csv")
```

#### Family function

```{r}
# A: longitudinal mTBI, baseline timepoint
lmtb_p_fam_fn_0 <- get_family_function(ce_y_fes, ce_p_fes, lmtb_subs, t = 0)
tibble(lmtb_p_fam_fn_0)
iwrite(lmtb_p_fam_fn_0, "lmtb_p_fam_fn_0.csv")

# B: longitudinal mTBI, longitudinal timepoint
lmtb_p_fam_fn_l <- get_family_function(ce_y_fes, ce_p_fes, lmtb_subs, t = 2)
tibble(lmtb_p_fam_fn_l)
iwrite(lmtb_p_fam_fn_l, "lmtb_p_fam_fn_l.csv")

# C: baseline mTBI, longitudinal timepoint
mtbi_p_fam_fn_l <- get_family_function(ce_y_fes, ce_p_fes, mtbi_subs, t = 2)
tibble(mtbi_p_fam_fn_l)
iwrite(mtbi_p_fam_fn_l, "mtbi_p_fam_fn_l.csv")

# D: baseline uninjured, longitudinal timepoint
unij_p_fam_fn_l <- get_family_function(ce_y_fes, ce_p_fes, unij_subs, t = 2)
tibble(unij_p_fam_fn_l)
iwrite(unij_p_fam_fn_l, "unij_p_fam_fn_l.csv")
```

#### Parent psychopathology

```{r}
# A: longitudinal mTBI, baseline timepoint
lmtb_p_parent_psych_0 <- get_parent_psychopathology(
    mh_p_asr,
    lmtb_subs,
    t = 0,
    raw = TRUE
)
tibble(lmtb_p_parent_psych_0)
iwrite(lmtb_p_parent_psych_0, "lmtb_p_parent_psych_0.csv")

# B: longitudinal mTBI, longitudinal timepoint
lmtb_p_parent_psych_l <- get_parent_psychopathology(
    mh_p_asr,
    lmtb_subs,
    t = 2,
    raw = TRUE
)
tibble(lmtb_p_parent_psych_l)
iwrite(lmtb_p_parent_psych_l, "lmtb_p_parent_psych_l.csv")

# C: baseline mTBI, longitudinal timepoint
mtbi_p_parent_psych_l <- get_parent_psychopathology(
    mh_p_asr,
    mtbi_subs,
    t = 2,
    raw = TRUE
)
tibble(mtbi_p_parent_psych_l)
iwrite(mtbi_p_parent_psych_l, "mtbi_p_parent_psych_l.csv")

# D: baseline uninjured, longitudinal timepoint
unij_p_parent_psych_l <- get_parent_psychopathology(
    mh_p_asr,
    unij_subs,
    t = 2,
    raw = TRUE
)
tibble(unij_p_parent_psych_l)
iwrite(unij_p_parent_psych_l, "unij_p_parent_psych_l.csv")
```

## Output variables

### Child Behaviour Checklist

These are collected at both baseline and longitudinal timepoints.

```{r}
# A: longitudinal mTBI, baseline timepoint
lmtb_cbcl_0 <- get_cbcl_syndrome_scale(mh_p_cbcl, lmtb_subs, t = 0, raw = TRUE)
tibble(lmtb_cbcl_0)
iwrite(lmtb_cbcl_0, "lmtb_cbcl_0.csv")

# B: longitudinal mTBI, longitudinal timepoint
lmtb_cbcl_l <- get_cbcl_syndrome_scale(mh_p_cbcl, lmtb_subs, t = 2, raw = TRUE)
tibble(lmtb_cbcl_l)
iwrite(lmtb_cbcl_l, "lmtb_cbcl_l.csv")

# C: baseline mTBI, longitudinal timepoint
mtbi_cbcl_l <- get_cbcl_syndrome_scale(mh_p_cbcl, mtbi_subs, t = 2, raw = TRUE)
tibble(mtbi_cbcl_l)
iwrite(mtbi_cbcl_l, "mtbi_cbcl_l.csv")

# D: baseline uninjured, longitudinal timepoint
unij_cbcl_l <- get_cbcl_syndrome_scale(mh_p_cbcl, unij_subs, t = 2, raw = TRUE)
tibble(unij_cbcl_l)
iwrite(unij_cbcl_l, "unij_cbcl_l.csv")
```

### Sleep disturbance scale


```{r}
# A: longitudinal mTBI, baseline timepoint
lmtb_sds_0 <- get_sleep_disturbance(ph_p_sds, lmtb_subs, t = 0)
tibble(lmtb_sds_0)
iwrite(lmtb_sds_0, "lmtb_sds_0.csv")

# B: longitudinal mTBI, longitudinal timepoint
lmtb_sds_l <- get_sleep_disturbance(ph_p_sds, lmtb_subs, t = 2)
tibble(lmtb_sds_l)
iwrite(lmtb_sds_l, "lmtb_sds_l.csv")

# C: baseline mTBI, longitudinal timepoint
mtbi_sds_l <- get_sleep_disturbance(ph_p_sds, mtbi_subs, t = 2)
tibble(mtbi_sds_l)
iwrite(mtbi_sds_l, "mtbi_sds_l.csv")

# D: baseline uninjured, longitudinal timepoint
unij_sds_l <- get_sleep_disturbance(ph_p_sds, unij_subs, t = 2)
tibble(unij_sds_l)
iwrite(unij_sds_l, "unij_sds_l.csv")
```

## Other covariates

### Scanner information

```{r}
# A: longitudinal mTBI, baseline timepoint
set.seed(42)
lmtb_scanner_0 <- get_scanner_id(
    mri_y_adm_info = mri_y_adm_info,
    subjects = lmtb_subs,
    t = 0,
    abcd_y_lt = abcd_y_lt,
    sample_missing = TRUE
)
tibble(lmtb_scanner_0)
iwrite(lmtb_scanner_0, "lmtb_scanner_0.csv")

# B: longitudinal mTBI, longitudinal timepoint
set.seed(42)
lmtb_scanner_l <- get_scanner_id(
    mri_y_adm_info = mri_y_adm_info,
    subjects = lmtb_subs,
    t = 2,
    abcd_y_lt = abcd_y_lt,
    sample_missing = TRUE
)
tibble(lmtb_scanner_l)
iwrite(lmtb_scanner_l, "lmtb_scanner_l.csv")

# C: baseline mTBI, longitudinal timepoint
set.seed(42)
mtbi_scanner_l <- get_scanner_id(
    mri_y_adm_info = mri_y_adm_info,
    subjects = mtbi_subs,
    t = 2,
    abcd_y_lt = abcd_y_lt,
    sample_missing = TRUE
)
tibble(mtbi_scanner_l)
iwrite(mtbi_scanner_l, "mtbi_scanner_l.csv")

# D: baseline uninjured, longitudinal timepoint
set.seed(42)
unij_scanner_l <- get_scanner_id(
    mri_y_adm_info = mri_y_adm_info,
    subjects = unij_subs,
    t = 2,
    abcd_y_lt = abcd_y_lt,
    sample_missing = TRUE
)
tibble(unij_scanner_l)
iwrite(unij_scanner_l, "unij_scanner_l.csv")
```

### Family ID

Timepoint does not apply to family ID.

```{r}
# A: longitudinal mTBI, baseline timepoint
lmtb_family <- get_family_id(abcd_y_lt, lmtb_subs, t = 0)
tibble(lmtb_family)
iwrite(lmtb_family, "lmtb_family.csv")
```

### Site ID

```{r}
# A: longitudinal mTBI, baseline timepoint
lmtb_site_0 <- get_site_id(abcd_y_lt, lmtb_subs, t = 0)
tibble(lmtb_site_0)
iwrite(lmtb_site_0, "lmtb_site_0.csv")

# B: longitudinal mTBI, longitudinal timepoint
lmtb_site_l <- get_site_id(abcd_y_lt, lmtb_subs, t = 2)
tibble(lmtb_site_l)
iwrite(lmtb_site_l, "lmtb_site_l.csv")

# C: baseline mTBI, longitudinal timepoint
mtbi_site_l <- get_site_id(abcd_y_lt, mtbi_subs, t = 2)
tibble(mtbi_site_l)
iwrite(mtbi_site_l, "mtbi_site_l.csv")

# D: baseline uninjured, longitudinal timepoint
unij_site_l <- get_site_id(abcd_y_lt, unij_subs, t = 2)
tibble(unij_site_l)
iwrite(unij_site_l, "unij_site_l.csv")
```
