# SNF in Uninjured Controls

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)
library(MatchIt)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subjects <- read_csv(sub_path("2023_11_07_mtbi_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2023_11_07_uninjured_subjects.csv"))
```

## Matching

Finding matched uninjured controls for each mtbi subject based on demographic variables.

```{r}
d_interview_age_mtbi_train_imp_1 <- read_csv(input_path("2024_01_15_d_interview_age_mtbi_train_imp_1.csv"))
d_sex_mtbi_train_imp_1 <- read_csv(input_path("2024_01_15_d_sex_mtbi_train_imp_1.csv"))
d_income_mtbi_train_imp_1 <- read_csv(input_path("2024_01_15_d_income_mtbi_train_imp_1.csv"))
d_race_mtbi_train_imp_1 <- read_csv(input_path("2024_01_15_d_race_mtbi_train_imp_1.csv"))

d_interview_age_uninj_imp_1 <- read_csv(input_path("2024_01_15_d_interview_age_uninj_imp_1.csv"))
d_sex_uninj_imp_1 <- read_csv(input_path("2024_01_15_d_sex_uninj_imp_1.csv"))
d_income_uninj_imp_1 <- read_csv(input_path("2024_01_15_d_income_uninj_imp_1.csv"))
d_race_uninj_imp_1 <- read_csv(input_path("2024_01_15_d_race_uninj_imp_1.csv"))


mtbi_matching_df <- list(
    d_interview_age_mtbi_train_imp_1,
    d_sex_mtbi_train_imp_1,
    d_income_mtbi_train_imp_1,
    d_race_mtbi_train_imp_1
) |> merge_df_list()

mtbi_matching_df$"mtbi" <- 1

uninjured_matching_df <- list(
    d_interview_age_uninj_imp_1,
    d_sex_uninj_imp_1,
    d_income_uninj_imp_1,
    d_race_uninj_imp_1
) |> merge_df_list()

uninjured_matching_df$"mtbi" <- 0

matching_df <- rbind(mtbi_matching_df, uninjured_matching_df)

matching_df

# Create a formula for matching

# Use the nearest neighbor matching method (you can explore other methods)
matching_results <- matchit(
    formula(mtbi ~ household_income + race + interview_age + sex),
    data = matching_df,
    method = "nearest"
)

# Print summary information about the matching
summary(matching_results)

# Obtain the matched data
matched_data <- match.data(matching_results)

# Extract the control group from the matched data
matched_uninjured <- matched_data |> 
    dplyr::filter(mtbi == 0) |> 
    dplyr::select(subjectkey)

write_csv(matched_uninjured, sub_path("matched_uninjured.csv", TRUE))
```

## Loading data and out of model lists

```{r}
matched_uninjured <- read_csv(sub_path("2024_01_15_matched_uninjured.csv"))

data_list_u1 <- list.load(input_path("2024_01_15_data_list_u1.rds"))
data_list_u2 <- list.load(input_path("2024_01_15_data_list_u2.rds"))
data_list_u3 <- list.load(input_path("2024_01_15_data_list_u3.rds"))
data_list_u4 <- list.load(input_path("2024_01_15_data_list_u4.rds"))
data_list_u5 <- list.load(input_path("2024_01_15_data_list_u5.rds"))
data_list_pu1 <- list.load(input_path("2024_01_15_data_list_pu1.rds"))
data_list_pu2 <- list.load(input_path("2024_01_15_data_list_pu2.rds"))
data_list_pu3 <- list.load(input_path("2024_01_15_data_list_pu3.rds"))
data_list_pu4 <- list.load(input_path("2024_01_15_data_list_pu4.rds"))
data_list_pu5 <- list.load(input_path("2024_01_15_data_list_pu5.rds"))
oom_list_u1 <- list.load(input_path("2024_01_15_oom_list_u1.rds"))
oom_list_u2 <- list.load(input_path("2024_01_15_oom_list_u2.rds"))
oom_list_u3 <- list.load(input_path("2024_01_15_oom_list_u3.rds"))
oom_list_u4 <- list.load(input_path("2024_01_15_oom_list_u4.rds"))
oom_list_u5 <- list.load(input_path("2024_01_15_oom_list_u5.rds"))
oom_list_pu1 <- list.load(input_path("2024_01_15_oom_list_pu1.rds"))
oom_list_pu2 <- list.load(input_path("2024_01_15_oom_list_pu2.rds"))
oom_list_pu3 <- list.load(input_path("2024_01_15_oom_list_pu3.rds"))
oom_list_pu4 <- list.load(input_path("2024_01_15_oom_list_pu4.rds"))
oom_list_pu5 <- list.load(input_path("2024_01_15_oom_list_pu5.rds"))

subject_filter_dl <- function(data_list, subject_vector) {
    subject_vector <- paste0("subject_", subject_vector)
    data_list <- data_list |>
        lapply(
            function(x) {
                x$"data" <- x$"data"[x$"data"$"subjectkey" %in% subject_vector, ]
                return(x)
            }
        )
    return(data_list)
}

# The matched data lists
data_list_mu1 <- data_list_u1 |> subject_filter_dl(matched_uninjured$"subjectkey")
data_list_mu2 <- data_list_u2 |> subject_filter_dl(matched_uninjured$"subjectkey")
data_list_mu3 <- data_list_u3 |> subject_filter_dl(matched_uninjured$"subjectkey")
data_list_mu4 <- data_list_u4 |> subject_filter_dl(matched_uninjured$"subjectkey")
data_list_mu5 <- data_list_u5 |> subject_filter_dl(matched_uninjured$"subjectkey")
data_list_mpu1 <- data_list_pu1 |> subject_filter_dl(matched_uninjured$"subjectkey")
data_list_mpu2 <- data_list_pu2 |> subject_filter_dl(matched_uninjured$"subjectkey")
data_list_mpu3 <- data_list_pu3 |> subject_filter_dl(matched_uninjured$"subjectkey")
data_list_mpu4 <- data_list_pu4 |> subject_filter_dl(matched_uninjured$"subjectkey")
data_list_mpu5 <- data_list_pu5 |> subject_filter_dl(matched_uninjured$"subjectkey")
oom_list_mu1 <- oom_list_u1 |> subject_filter_dl(matched_uninjured$"subjectkey")
oom_list_mu2 <- oom_list_u2 |> subject_filter_dl(matched_uninjured$"subjectkey")
oom_list_mu3 <- oom_list_u3 |> subject_filter_dl(matched_uninjured$"subjectkey")
oom_list_mu4 <- oom_list_u4 |> subject_filter_dl(matched_uninjured$"subjectkey")
oom_list_mu5 <- oom_list_u5 |> subject_filter_dl(matched_uninjured$"subjectkey")
oom_list_mpu1 <- oom_list_pu1 |> subject_filter_dl(matched_uninjured$"subjectkey")
oom_list_mpu2 <- oom_list_pu2 |> subject_filter_dl(matched_uninjured$"subjectkey")
oom_list_mpu3 <- oom_list_pu3 |> subject_filter_dl(matched_uninjured$"subjectkey")
oom_list_mpu4 <- oom_list_pu4 |> subject_filter_dl(matched_uninjured$"subjectkey")
oom_list_mpu5 <- oom_list_pu5 |> subject_filter_dl(matched_uninjured$"subjectkey")

list.save(data_list_mu1, input_path("data_list_mu1.rds", TRUE))
list.save(data_list_mu2, input_path("data_list_mu2.rds", TRUE))
list.save(data_list_mu3, input_path("data_list_mu3.rds", TRUE))
list.save(data_list_mu4, input_path("data_list_mu4.rds", TRUE))
list.save(data_list_mu5, input_path("data_list_mu5.rds", TRUE))
list.save(data_list_mpu1, input_path("data_list_mpu1.rds", TRUE))
list.save(data_list_mpu2, input_path("data_list_mpu2.rds", TRUE))
list.save(data_list_mpu3, input_path("data_list_mpu3.rds", TRUE))
list.save(data_list_mpu4, input_path("data_list_mpu4.rds", TRUE))
list.save(data_list_mpu5, input_path("data_list_mpu5.rds", TRUE))
list.save(oom_list_mu1, input_path("oom_list_mu1.rds", TRUE))
list.save(oom_list_mu2, input_path("oom_list_mu2.rds", TRUE))
list.save(oom_list_mu3, input_path("oom_list_mu3.rds", TRUE))
list.save(oom_list_mu4, input_path("oom_list_mu4.rds", TRUE))
list.save(oom_list_mu5, input_path("oom_list_mu5.rds", TRUE))
list.save(oom_list_mpu1, input_path("oom_list_mpu1.rds", TRUE))
list.save(oom_list_mpu2, input_path("oom_list_mpu2.rds", TRUE))
list.save(oom_list_mpu3, input_path("oom_list_mpu3.rds", TRUE))
list.save(oom_list_mpu4, input_path("oom_list_mpu4.rds", TRUE))
list.save(oom_list_mpu5, input_path("oom_list_mpu5.rds", TRUE))

data_list_mu1 <- list.load(input_path("2024_01_15_data_list_mu1.rds"))
data_list_mu2 <- list.load(input_path("2024_01_15_data_list_mu2.rds"))
data_list_mu3 <- list.load(input_path("2024_01_15_data_list_mu3.rds"))
data_list_mu4 <- list.load(input_path("2024_01_15_data_list_mu4.rds"))
data_list_mu5 <- list.load(input_path("2024_01_15_data_list_mu5.rds"))
data_list_mpu1 <- list.load(input_path("2024_01_15_data_list_mpu1.rds"))
data_list_mpu2 <- list.load(input_path("2024_01_15_data_list_mpu2.rds"))
data_list_mpu3 <- list.load(input_path("2024_01_15_data_list_mpu3.rds"))
data_list_mpu4 <- list.load(input_path("2024_01_15_data_list_mpu4.rds"))
data_list_mpu5 <- list.load(input_path("2024_01_15_data_list_mpu5.rds"))
oom_list_mu1 <- list.load(input_path("2024_01_15_oom_list_mu1.rds"))
oom_list_mu2 <- list.load(input_path("2024_01_15_oom_list_mu2.rds"))
oom_list_mu3 <- list.load(input_path("2024_01_15_oom_list_mu3.rds"))
oom_list_mu4 <- list.load(input_path("2024_01_15_oom_list_mu4.rds"))
oom_list_mu5 <- list.load(input_path("2024_01_15_oom_list_mu5.rds"))
oom_list_mpu1 <- list.load(input_path("2024_01_15_oom_list_mpu1.rds"))
oom_list_mpu2 <- list.load(input_path("2024_01_15_oom_list_mpu2.rds"))
oom_list_mpu3 <- list.load(input_path("2024_01_15_oom_list_mpu3.rds"))
oom_list_mpu4 <- list.load(input_path("2024_01_15_oom_list_mpu4.rds"))
oom_list_mpu5 <- list.load(input_path("2024_01_15_oom_list_mpu5.rds"))
```

## Generating custom distance measures

```{r}
my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

summarize_distance_metrics_list(my_distance_metrics)
```

## Generating the settings matrix

```{r}
###############################################################################
# 3. Generate the settings matrix
###############################################################################
settings_matrix <- generate_settings_matrix(
    data_list_mu1,
    nrow = 200,
    seed = 42,
    distance_metrics_list = my_distance_metrics
)

write_csv(settings_matrix, proc_path("settings_matrix_mu.csv", TRUE))

settings_matrix <- read_csv(
    proc_path(
        "2024_01_15_settings_matrix_mu.csv"
    )
)
```

## SNF for each of the imputations

```{r}

# Uninjured only imputed
# Imputation 1
start <- proc.time()
progressr::with_progress({
    solutions_matrix_mu1 <- batch_snf(
        data_list = data_list_mu1,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_mu1, proc_path("solutions_matrix_mu1.csv", TRUE))
# Imputation 2
start <- proc.time()
progressr::with_progress({
    solutions_matrix_mu2 <- batch_snf(
        data_list = data_list_mu2,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_mu2, proc_path("solutions_matrix_mu2.csv", TRUE))
# Imputation 3
start <- proc.time()
progressr::with_progress({
    solutions_matrix_mu3 <- batch_snf(
        data_list = data_list_mu3,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_mu3, proc_path("solutions_matrix_mu3.csv", TRUE))
# Imputation 4
start <- proc.time()
progressr::with_progress({
    solutions_matrix_mu4 <- batch_snf(
        data_list = data_list_mu4,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_mu4, proc_path("solutions_matrix_mu4.csv", TRUE))
# Imputation 5
start <- proc.time()
progressr::with_progress({
    solutions_matrix_mu5 <- batch_snf(
        data_list = data_list_mu5,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_mu5, proc_path("solutions_matrix_mu5.csv", TRUE))
#
# Uninjured pooled imputed
# Imputation 1
start <- proc.time()
progressr::with_progress({
    solutions_matrix_mpu1 <- batch_snf(
        data_list = data_list_mpu1,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_mpu1, proc_path("solutions_matrix_mpu1.csv", TRUE))
# Imputation 2
start <- proc.time()
progressr::with_progress({
    solutions_matrix_mpu2 <- batch_snf(
        data_list = data_list_mpu2,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_mpu2, proc_path("solutions_matrix_mpu2.csv", TRUE))
# Imputation 3
start <- proc.time()
progressr::with_progress({
    solutions_matrix_mpu3 <- batch_snf(
        data_list = data_list_mpu3,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_mpu3, proc_path("solutions_matrix_mpu3.csv", TRUE))
# Imputation 4
start <- proc.time()
progressr::with_progress({
    solutions_matrix_mpu4 <- batch_snf(
        data_list = data_list_mpu4,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_mpu4, proc_path("solutions_matrix_mpu4.csv", TRUE))
# Imputation 5
start <- proc.time()
progressr::with_progress({
    solutions_matrix_mpu5 <- batch_snf(
        data_list = data_list_mpu5,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_mpu5, proc_path("solutions_matrix_mpu5.csv", TRUE))

```

code below is yet to be run

## Re-importing the generated solutions

```{r}
solutions_matrix_mu1 <- read_csv(proc_path("2024_01_15_solutions_matrix_mu1.csv"))
solutions_matrix_mu2 <- read_csv(proc_path("2024_01_15_solutions_matrix_mu2.csv"))
solutions_matrix_mu3 <- read_csv(proc_path("2024_01_15_solutions_matrix_mu3.csv"))
solutions_matrix_mu4 <- read_csv(proc_path("2024_01_15_solutions_matrix_mu4.csv"))
solutions_matrix_mu5 <- read_csv(proc_path("2024_01_15_solutions_matrix_mu5.csv"))
solutions_matrix_mpu1 <- read_csv(proc_path("2024_01_15_solutions_matrix_mpu1.csv"))
solutions_matrix_mpu2 <- read_csv(proc_path("2024_01_15_solutions_matrix_mpu2.csv"))
solutions_matrix_mpu3 <- read_csv(proc_path("2024_01_15_solutions_matrix_mpu3.csv"))
solutions_matrix_mpu4 <- read_csv(proc_path("2024_01_15_solutions_matrix_mpu4.csv"))
solutions_matrix_mpu5 <- read_csv(proc_path("2024_01_15_solutions_matrix_mpu5.csv"))

all_uninjured_imputations <- do.call(
    "rbind",
    list(
        solutions_matrix_mu1,
        solutions_matrix_mu2,
        solutions_matrix_mu3,
        solutions_matrix_mu4,
        solutions_matrix_mu5,
        solutions_matrix_mpu1,
        solutions_matrix_mpu2,
        solutions_matrix_mpu3,
        solutions_matrix_mpu4,
        solutions_matrix_mpu5
    )
)
```

## Calculating pairwise ARIs

```{r}
# Completed
aris_mu1 <- calc_om_aris(solutions_matrix_mu1)
write_csv(data.frame(aris_mu1), proc_path("aris_mu1.csv", TRUE))
aris_mu2 <- calc_om_aris(solutions_matrix_mu2)
write_csv(data.frame(aris_mu2), proc_path("aris_mu2.csv", TRUE))
aris_mu3 <- calc_om_aris(solutions_matrix_mu3)
write_csv(data.frame(aris_mu3), proc_path("aris_mu3.csv", TRUE))
aris_mu4 <- calc_om_aris(solutions_matrix_mu4)
write_csv(data.frame(aris_mu4), proc_path("aris_mu4.csv", TRUE))
aris_mu5 <- calc_om_aris(solutions_matrix_mu5)
write_csv(data.frame(aris_mu5), proc_path("aris_mu5.csv", TRUE))
aris_mpu1 <- calc_om_aris(solutions_matrix_mpu1)
write_csv(data.frame(aris_mpu1), proc_path("aris_mpu1.csv", TRUE))
aris_mpu2 <- calc_om_aris(solutions_matrix_mpu2)
write_csv(data.frame(aris_mpu2), proc_path("aris_mpu2.csv", TRUE))
aris_mpu3 <- calc_om_aris(solutions_matrix_mpu3)
write_csv(data.frame(aris_mpu3), proc_path("aris_mpu3.csv", TRUE))
aris_mpu4 <- calc_om_aris(solutions_matrix_mpu4)
write_csv(data.frame(aris_mpu4), proc_path("aris_mpu4.csv", TRUE))
aris_mpu5 <- calc_om_aris(solutions_matrix_mpu5)
write_csv(data.frame(aris_mpu5), proc_path("aris_mpu5.csv", TRUE))

aris_all_uninjured_imputations <- calc_om_aris(all_uninjured_imputations)

write_csv(
    data.frame(aris_all_uninjured_imputations),
    proc_path("aris_all_uninjured_imputations.csv", TRUE)
)
```

## Re-importing the ARIs

```{r}
aris_mu1 <- read_csv(proc_path("2024_01_15_aris_mu1.csv")) |> as.matrix()
aris_mu2 <- read_csv(proc_path("2024_01_15_aris_mu2.csv")) |> as.matrix()
aris_mu3 <- read_csv(proc_path("2024_01_15_aris_mu3.csv")) |> as.matrix()
aris_mu4 <- read_csv(proc_path("2024_01_15_aris_mu4.csv")) |> as.matrix()
aris_mu5 <- read_csv(proc_path("2024_01_15_aris_mu5.csv")) |> as.matrix()
aris_mpu1 <- read_csv(proc_path("2024_01_15_aris_mpu1.csv")) |> as.matrix()
aris_mpu2 <- read_csv(proc_path("2024_01_15_aris_mpu2.csv")) |> as.matrix()
aris_mpu3 <- read_csv(proc_path("2024_01_15_aris_mpu3.csv")) |> as.matrix()
aris_mpu4 <- read_csv(proc_path("2024_01_15_aris_mpu4.csv")) |> as.matrix()
aris_mpu5 <- read_csv(proc_path("2024_01_15_aris_mpu5.csv")) |> as.matrix()

aris_all_uninjured_imputations <- read_csv(
    proc_path("2024_01_15_aris_all_uninjured_imputations.csv")
) |>
    as.matrix()
```
