# metasnf over imputaions

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subjects <- read_csv(sub_path("2024_02_13_mtbi_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2024_02_13_uninjured_subjects.csv"))
mtbi_subjects_train <- read_csv(sub_path("2024_02_13_mtbi_train_subjects.csv"))
```

## Loading data and out of model lists

```{r}
data_list_m1 <- list.load(input_path("2024_02_14_data_list_m1.rds"))
data_list_m2 <- list.load(input_path("2024_02_14_data_list_m2.rds"))
data_list_m3 <- list.load(input_path("2024_02_14_data_list_m3.rds"))
data_list_m4 <- list.load(input_path("2024_02_14_data_list_m4.rds"))
data_list_m5 <- list.load(input_path("2024_02_14_data_list_m5.rds"))
data_list_pm1 <- list.load(input_path("2024_02_14_data_list_pm1.rds"))
data_list_pm2 <- list.load(input_path("2024_02_14_data_list_pm2.rds"))
data_list_pm3 <- list.load(input_path("2024_02_14_data_list_pm3.rds"))
data_list_pm4 <- list.load(input_path("2024_02_14_data_list_pm4.rds"))
data_list_pm5 <- list.load(input_path("2024_02_14_data_list_pm5.rds"))
oom_list_m1 <- list.load(input_path("2024_02_14_oom_list_m1.rds"))
oom_list_m2 <- list.load(input_path("2024_02_14_oom_list_m2.rds"))
oom_list_m3 <- list.load(input_path("2024_02_14_oom_list_m3.rds"))
oom_list_m4 <- list.load(input_path("2024_02_14_oom_list_m4.rds"))
oom_list_m5 <- list.load(input_path("2024_02_14_oom_list_m5.rds"))
oom_list_pm1 <- list.load(input_path("2024_02_14_oom_list_pm1.rds"))
oom_list_pm2 <- list.load(input_path("2024_02_14_oom_list_pm2.rds"))
oom_list_pm3 <- list.load(input_path("2024_02_14_oom_list_pm3.rds"))
oom_list_pm4 <- list.load(input_path("2024_02_14_oom_list_pm4.rds"))
oom_list_pm5 <- list.load(input_path("2024_02_14_oom_list_pm5.rds"))
```

## Generating custom distance measures

```{r}
###############################################################################
# 2. Add standard normalized variations to the distance metrics list (also
# achievable through toggling automatic_standard_normalize parameter in
# `batch_snf`)
###############################################################################
my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

summarize_distance_metrics_list(my_distance_metrics)
```

## Generating the settings matrix

```{r}
###############################################################################
# 3. Generate the settings matrix
###############################################################################
settings_matrix <- generate_settings_matrix(
    data_list_m1,
    nrow = 200,
    seed = 42,
    distance_metrics_list = my_distance_metrics
)

write_csv(settings_matrix, proc_path("settings_matrix.csv", TRUE))

settings_matrix <- read_csv(
    proc_path(
        "2024_02_14_settings_matrix.csv"
    )
)
```

## SNF for each of the imputations

```{r}
# mTBI only imputed
# Imputation 1
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m1 <- batch_snf(
        data_list = data_list_m1,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m1, proc_path("solutions_matrix_m1.csv", TRUE))
# Imputation 2
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m2 <- batch_snf(
        data_list = data_list_m2,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m2, proc_path("solutions_matrix_m2.csv", TRUE))
# Imputation 3
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m3 <- batch_snf(
        data_list = data_list_m3,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m3, proc_path("solutions_matrix_m3.csv", TRUE))
# Imputation 4
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m4 <- batch_snf(
        data_list = data_list_m4,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m4, proc_path("solutions_matrix_m4.csv", TRUE))
# Imputation 5
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m5 <- batch_snf(
        data_list = data_list_m5,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m5, proc_path("solutions_matrix_m5.csv", TRUE))
#
# mTBI and uninjured pooled imputed
# Imputation 1
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm1 <- batch_snf(
        data_list = data_list_pm1,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm1, proc_path("solutions_matrix_pm1.csv", TRUE))
# Imputation 2
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm2 <- batch_snf(
        data_list = data_list_pm2,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm2, proc_path("solutions_matrix_pm2.csv", TRUE))
# Imputation 3
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm3 <- batch_snf(
        data_list = data_list_pm3,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm3, proc_path("solutions_matrix_pm3.csv", TRUE))
# Imputation 4
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm4 <- batch_snf(
        data_list = data_list_pm4,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm4, proc_path("solutions_matrix_pm4.csv", TRUE))
# Imputation 5
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm5 <- batch_snf(
        data_list = data_list_pm5,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm5, proc_path("solutions_matrix_pm5.csv", TRUE))
```


## Re-importing the generated solutions

```{r}
solutions_matrix_m1 <- read_csv(proc_path("2024_02_14_solutions_matrix_m1.csv"))
solutions_matrix_m2 <- read_csv(proc_path("2024_02_14_solutions_matrix_m2.csv"))
solutions_matrix_m3 <- read_csv(proc_path("2024_02_14_solutions_matrix_m3.csv"))
solutions_matrix_m4 <- read_csv(proc_path("2024_02_14_solutions_matrix_m4.csv"))
solutions_matrix_m5 <- read_csv(proc_path("2024_02_14_solutions_matrix_m5.csv"))
solutions_matrix_pm1 <- read_csv(proc_path("2024_02_14_solutions_matrix_pm1.csv"))
solutions_matrix_pm2 <- read_csv(proc_path("2024_02_14_solutions_matrix_pm2.csv"))
solutions_matrix_pm3 <- read_csv(proc_path("2024_02_14_solutions_matrix_pm3.csv"))
solutions_matrix_pm4 <- read_csv(proc_path("2024_02_14_solutions_matrix_pm4.csv"))
solutions_matrix_pm5 <- read_csv(proc_path("2024_02_14_solutions_matrix_pm5.csv"))
#
all_mtbi_imputations <- do.call(
    "rbind",
    list(
        solutions_matrix_m1,
        solutions_matrix_m2,
        solutions_matrix_m3,
        solutions_matrix_m4,
        solutions_matrix_m5,
        solutions_matrix_pm1,
        solutions_matrix_pm2,
        solutions_matrix_pm3,
        solutions_matrix_pm4,
        solutions_matrix_pm5
    )
)

aris_m1 <- calc_om_aris(solutions_matrix_m1, verbose = TRUE)
write_csv(data.frame(aris_m1), proc_path("aris_m1.csv", TRUE))
aris_m2 <- calc_om_aris(solutions_matrix_m2, verbose = TRUE)
write_csv(data.frame(aris_m2), proc_path("aris_m2.csv", TRUE))
aris_m3 <- calc_om_aris(solutions_matrix_m3, verbose = TRUE)
write_csv(data.frame(aris_m3), proc_path("aris_m3.csv", TRUE))
aris_m4 <- calc_om_aris(solutions_matrix_m4, verbose = TRUE)
write_csv(data.frame(aris_m4), proc_path("aris_m4.csv", TRUE))
aris_m5 <- calc_om_aris(solutions_matrix_m5, verbose = TRUE)
write_csv(data.frame(aris_m5), proc_path("aris_m5.csv", TRUE))
aris_pm1 <- calc_om_aris(solutions_matrix_pm1, verbose = TRUE)
write_csv(data.frame(aris_pm1), proc_path("aris_pm1.csv", TRUE))
aris_pm2 <- calc_om_aris(solutions_matrix_pm2, verbose = TRUE)
write_csv(data.frame(aris_pm2), proc_path("aris_pm2.csv", TRUE))
aris_pm3 <- calc_om_aris(solutions_matrix_pm3, verbose = TRUE)
write_csv(data.frame(aris_pm3), proc_path("aris_pm3.csv", TRUE))
aris_pm4 <- calc_om_aris(solutions_matrix_pm4, verbose = TRUE)
write_csv(data.frame(aris_pm4), proc_path("aris_pm4.csv", TRUE))
aris_pm5 <- calc_om_aris(solutions_matrix_pm5, verbose = TRUE)
write_csv(data.frame(aris_pm5), proc_path("aris_pm5.csv", TRUE))

aris_all_mtbi_imputations <- calc_om_aris(all_mtbi_imputations, verbose = TRUE)
write_csv(
    data.frame(aris_all_mtbi_imputations),
    proc_path("aris_all_mtbi_imputations.csv", TRUE)
)

```

2024-02-15 This meta-calcs is done

## Re-importing the ARIs

```{r}
aris_m1 <- read_csv(proc_path("2024_02_15_aris_m1.csv")) |> as.matrix()
aris_m2 <- read_csv(proc_path("2024_02_15_aris_m2.csv")) |> as.matrix()
aris_m3 <- read_csv(proc_path("2024_02_15_aris_m3.csv")) |> as.matrix()
aris_m4 <- read_csv(proc_path("2024_02_15_aris_m4.csv")) |> as.matrix()
aris_m5 <- read_csv(proc_path("2024_02_15_aris_m5.csv")) |> as.matrix()
aris_pm1 <- read_csv(proc_path("2024_02_15_aris_pm1.csv")) |> as.matrix()
aris_pm2 <- read_csv(proc_path("2024_02_15_aris_pm2.csv")) |> as.matrix()
aris_pm3 <- read_csv(proc_path("2024_02_15_aris_pm3.csv")) |> as.matrix()
aris_pm4 <- read_csv(proc_path("2024_02_15_aris_pm4.csv")) |> as.matrix()
aris_pm5 <- read_csv(proc_path("2024_02_15_aris_pm5.csv")) |> as.matrix()

aris_all_mtbi_imputations <- read_csv(
    proc_path("2024_02_15_aris_all_mtbi_imputations.csv")
) |>
    as.matrix()
```

## Plotting the ARIs

### Initial plot across all ARIs to extract order

```{r}
aris_all_mtbi_imputations_heatmap <- similarity_matrix_heatmap(
    aris_all_mtbi_imputations,
    log_graph = FALSE,
    cluster_rows = TRUE,
    cluster_columns = TRUE
)

aris_all_mtbi_imputations_heatmap <- ComplexHeatmap::draw(
    aris_all_mtbi_imputations_heatmap
)
aris_all_mtbi_imputations_order <- ComplexHeatmap::row_order(
    aris_all_mtbi_imputations_heatmap
)

write_csv(
    data.frame(aris_all_mtbi_imputations_order),
    proc_path("aris_all_mtbi_imputations_order.csv", TRUE)
)
```

### Re-importing the order

```{r}
aris_all_mtbi_imputations_order <- unlist(
    read_csv(proc_path("2024_02_16_aris_all_mtbi_imputations_order.csv"))
)

names(aris_all_mtbi_imputations_order) <- NULL
```

## Full imputation meta clustering plot with impairment levels

```{r}
imputation_labels <- data.frame(
    "imputation" = c(
        rep("m1", 200),
        rep("m2", 200),
        rep("m3", 200),
        rep("m4", 200),
        rep("m5", 200),
        rep("pm1", 200),
        rep("pm2", 200),
        rep("pm3", 200),
        rep("pm4", 200),
        rep("pm5", 200)
    ),
    "pooled" = c(
        rep("yes", 1000),
        rep("no", 1000)
    )
)

full_solutions_matrix <- cbind(all_mtbi_imputations, imputation_labels)

full_solutions_matrix$"nclust2" <- full_solutions_matrix$"nclust" - 2

z <- extend_solutions(
    full_solutions_matrix[1:3, ],
    target_list = c(data_list_m1, oom_list_m1),
    verbose = TRUE,
    min_pval = 1e-10
)

pval_cols <- z[, endsWith(colnames(z), "_p")]

pval_cols[pval_cols < 1e-10]

pval_cols



ncol(z)

my_df <- z[1:3, 400:410]

z[1:3, 400:410] |>
    numcol_to_numeric() |>
    dplyr::mutate(
        dplyr::across(
            dplyr::ends_with("_p"),
            ~ ifelse(
                . < 1e-10,
                999,
                .
            )
        )
    )


pval_summaries(z)$"sex_p" < 1e-10

full_mtbi_io_extended_solutions_matrix

write_csv(
    full_mtbi_io_extended_solutions_matrix,
    proc_path("full_mtbi_io_extended_solutions_matrix.csv", TRUE)
)

full_mtbi_o_extended_solutions_matrix <- extend_solutions(
    full_solutions_matrix,
    oom_list_m1,
    verbose = TRUE,
    min_pval = 1e-10
)

write_csv(
    full_mtbi_i_extended_solutions_matrix,
    proc_path("full_mtbi_i_extended_solutions_matrix.csv", TRUE)
)
```

```{r}


mini1 <- extend_solutions(
    full_solutions_matrix[1:3, ],
    oom_list_m1,
    verbose = TRUE
)

mini2 <- extend_solutions(
    full_solutions_matrix[1:3, ],
    oom_list_m1,
    verbose = TRUE
)

identical(mini1, mini2)

df

identical(mini1, mini2)

p_columns <- grep("_p$", names(mini1), value = TRUE)

mini1[p_columns][mini1[p_columns] < 0.05] <- 0.05

mini1


z <- pval_summaries(mini2)

```

HERE

Re-reading the extended solutions matrices

```{r}
full_mtbi_i_extended_solutions_matrix <- read_csv(
    proc_path("2024_02_23_full_mtbi_i_extended_solutions_matrix.csv")
)

full_mtbi_io_extended_solutions_matrix <- read_csv(
    proc_path("2024_02_23_full_mtbi_io_extended_solutions_matrix.csv")
)
```

```{r}

full_mtbi_io_extended_solutions_matrix |> colnames()

full_mtbi_io_extended_solutions_matrix[1:5, ]

#pval_select <- function(extended_solutions_matrix,
#                        negative_log = FALSE) {
#    # Select p-value columns and convert to numeric
#    pval_df <- extended_solutions_matrix |>
#        dplyr::select(
#            "row_id",
#            dplyr::ends_with("_p"),
#            dplyr::contains("p_val")
#        ) |>
#        data.frame() |>
#        metasnf::numcol_to_numeric()
#    # Convert p-values to negative log p-values if requested
#    if (negative_log) {
#        # Remove summary columns from non-negative log p-value calculations
#        pval_df <- dplyr::select(pval_df, -c("min_p_val", "mean_p_val"))
#        # Negative log conversions
#        neg_log_pval_df <- -log(pval_df)
#        neg_log_pval_df$"row_id" <- pval_df$"row_id"
#        pval_df <- neg_log_pval_df
#        mini_df <- pval_df |> dplyr::select(
#            dplyr::ends_with("_p")
#        )
#        pval_df$"mean_neglog_p" <- apply(mini_df, 1, FUN = mean)
#        pval_df$"max_neglog_p" <- apply(mini_df, 1, FUN = max)
#    }
#    return(pval_df)
#}

full_oom_pvals <- pval_select(
    full_mtbi_io_extended_solutions_matrix,
    negative_log = TRUE
)

data.frame(full_mtbi_io_extended_solutions_matrix) |> head()

full_oom_pvals |> head()



full_mtbi_io_extended_solutions_matrix


full_mtbi_io_extended_solutions_matrix$"mean_neglog_p" <-
    full_oom_pvals$"mean_neglog_p"

head(full_oom_pvals)

aris_all_mtbi_imputations_annotated_heatmap <- similarity_matrix_heatmap(
    aris_all_mtbi_imputations,
    order = aris_all_mtbi_imputations_order,
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    log_graph = FALSE,
    data = data.frame(full_mtbi_io_extended_solutions_matrix),
    top_hm = list(
        "Scheme" = "snf_scheme",
        "Impairment Separation" = "mean_neglog_p"
    ),
    left_hm = list(
        "Pooled" = "pooled",
        "Imputation" = "imputation"
    ),
    top_bar = list(
        "Number of Clusters - 2" = "nclust2"
    ),
    scale_diag = "none",
    heatmap_height = grid::unit(19, "cm"),
    heatmap_width = grid::unit(19, "cm"),
    annotation_colours = list(
        "Pooled" = c(
            "yes" = "orange",
            "no" = "purple"
        ),
        "Imputation" = divergent_colours(
            full_mtbi_io_extended_solutions_matrix$"imputation"
        ),
        "Scheme" = c(
            "1" = "#7FC97F",
            "2" = "#BEAED4",
            "3" = "#FDC086"
        ),
        "Impairment Separation" = hm_colours(
            full_mtbi_io_extended_solutions_matrix$"mean_neglog_p"
        )
    ),
    col = circlize::colorRamp2(
        c(min(aris_all_mtbi_imputations), max(aris_all_mtbi_imputations)),
        c("navy", "red")
    )
)
aris_all_mtbi_imputations_annotated_heatmap
```

```{r}
# PNG export
grDevices::png(
    fig_path("aris_all_mtbi_imputations_annotated_heatmap.png", TRUE),
    width = 3000,
    height = 3000,
    res = 300
)
aris_all_mtbi_imputations_annotated_heatmap
grDevices::dev.off()
```

## Identifying meta clusters

```{r}
split_at <- function(vector, nrow) {
    split_vec <- rep("A", nrow)
    if (vector[length(vector)] != nrow) {
        vector <- c(vector, nrow)
    }
    for (i in 1:(length(vector) - 1)) {
        start <- vector[i]
        end <- vector[i + 1]
        split_vec[start:end] <- LETTERS[i + 1]
    }
    return(split_vec)
}

split_vec = c(
    233,
    723,
    1405,
    1685,
    1900
)
aris_all_mtbi_imputations_chopped_heatmap <- similarity_matrix_heatmap(
    aris_all_mtbi_imputations,
    order = aris_all_mtbi_imputations_order,
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    log_graph = FALSE,
    data = full_extended_solutions_matrix,
    top_hm = list(
        "Scheme" = "snf_scheme",
        "Impairment Separation" = "mean_neglog_p"
    ),
    left_hm = list(
        "Pooled" = "pooled",
        "Imputation" = "imputation"
    ),
    top_bar = list(
        "Number of Clusters - 2" = "nclust2"
    ),
    scale_diag = "none",
    heatmap_height = grid::unit(19, "cm"),
    heatmap_width = grid::unit(19, "cm"),
    annotation_colours = list(
        "Pooled" = c(
            "yes" = "orange",
            "no" = "purple"
        ),
        "Imputation" = divergent_colours(full_extended_solutions_matrix$"imputation"),
        "Scheme" = c(
            "1" = "#7FC97F",
            "2" = "#BEAED4",
            "3" = "#FDC086"
        ),
        "Impairment Separation" = hm_colours(full_extended_solutions_matrix$"mean_neglog_p")
    ),
    col = circlize::colorRamp2(
        c(min(aris_all_mtbi_imputations), max(aris_all_mtbi_imputations)),
        c("navy", "red")
    ),
    row_split = split_at(
        vector = split_vec,
        nrow = 2000
    ),
    column_split = split_at(
        vector = split_vec,
        nrow = 2000
    )
)

aris_all_mtbi_imputations_chopped_heatmap

# PNG export
grDevices::png(
    fig_path("aris_all_mtbi_imputations_chopped_heatmap.png", TRUE),
    width = 3000,
    height = 3000,
    res = 300
)
aris_all_mtbi_imputations_chopped_heatmap
grDevices::dev.off()
```

## One-MC-at-a-time

```{r}
library(ggplot2)

mc_reordered_labels <- split_at(split_vec, 2000)
names(aris_all_mtbi_imputations_order) <- mc_reordered_labels
sorted_mc_labels <- sort(aris_all_mtbi_imputations_order)

full_mtbi_io_extended_solutions_matrix <- read_csv(
    proc_path("2024_02_16_full_mtbi_io_extended_solutions_matrix.csv")
)

target_pvals <- p_val_select(full_mtbi_io_extended_solutions_matrix)
target_pvals$"mc_label" <- names(sorted_mc_labels)
target_pvals <- dplyr::select(target_pvals, -dplyr::starts_with("mean"))

my_manhattan_plot <- function(io_solutions_matrix,
                              sorted_labels,
                              mcs,
                              data_list) {
    target_pvals <- p_val_select(io_solutions_matrix)
    target_pvals$"mc_label" <- names(sorted_labels)
    target_pvals <- dplyr::select(target_pvals, -dplyr::starts_with("mean"))
    mc_associations <- manhattan_plot(
        target_pvals,
        threshold = 0.05,
        bonferroni_line = FALSE,
        data_list = data_list,
        mc_labels = mcs,
        colours = sample(gg_color_hue(7))
    )
    return(mc_associations)
}

gg_color_hue <- function(n) {
  hues = seq(15, 375, length = n + 1)
  hcl(h = hues, l = 65, c = 100)[1:n]
}

colorz <- gg_color_hue(7)

df <- data.frame(color = colorz)

# 2024-02-16 HERE I AM!

# Plot the colors using ggplot2
ggplot(df, aes(x = 1, y = seq_along(color), fill = color)) +
  geom_tile() +
  scale_fill_identity() +
  theme_void() +
  theme(legend.position = "none") +
  labs(title = "Visualization of Color Codes")

dl_m1_renamed <- data_list_m1 |> lapply(
    function(x) {
        x$"domain" <- paste0("I-", x$"domain")
        return(x)
    }
)
oom_m1_renamed <- oom_list_m1 |> lapply(
    function(x) {
        x$"domain" <- paste0("O-", x$"domain")
        return(x)
    }
)

my_manhattan_plot(
    full_mtbi_io_extended_solutions_matrix,
    sorted_mc_labels,
    c("A", "B", "D", "E"),
    data_list = c(dl_m1_renamed, oom_m1_renamed)
)



ggsave(
    plot = all_mtbi_imputations_main_mc_associations,
    fig_path("all_mtbi_imputations_main_mc_associations.png", TRUE),
    width = 8,
    height = 10
)

all_mtbi_imputations_f_mc_associations <- manhattan_plot(
    target_pvals,
    threshold = 0.05,
    bonferroni_line = FALSE,
    data_list = data_list_m1,
    mc_labels = c("F-A", "F-B", "F-C", "F-D", "F-E")
)

all_mtbi_imputations_f_mc_associations

ggsave(
    plot = all_mtbi_imputations_f_mc_associations,
    fig_path("all_mtbi_imputations_f_mc_associations.png", TRUE),
    width = 8,
    height = 10
)

all_mtbi_imputations_all_mc_associations <- manhattan_plot(
    target_pvals,
    threshold = 0.05,
    bonferroni_line = FALSE,
    data_list = data_list_m1
)
ggsave(
    plot = all_mtbi_imputations_all_mc_associations,
    fig_path("all_mtbi_imputations_all_mc_associations.png", TRUE),
    width = 8,
    height = 20
)

# Bulk export each MC individually
for (mc in names(mc_reordered_indices)) {
    mc_plot <- manhattan_plot(
        target_pvals,
        threshold = 0.05,
        bonferroni_line = FALSE,
        data_list = data_list_m1,
        mc_label = mc
    )
    mc_path <- paste0(
        "all_mtbi_imputations_mc_",
        gsub("-", "_", tolower(mc)),
        "_associations.png"
    )
    ggsave(
        plot = mc_plot,
        fig_path(mc_path, TRUE),
        width = 10,
        height = 3
    )
}
```
