# metasnf over imputaions

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subjects <- read_csv(sub_path("2024_02_13_mtbi_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2024_02_13_uninjured_subjects.csv"))
mtbi_subjects_train <- read_csv(sub_path("2024_02_13_mtbi_train_subjects.csv"))

source("abcd/functions.R")
```

## Loading data and out of model lists

```{r}
data_list_m1 <- list.load(input_path("2024_02_14_data_list_m1.rds"))
data_list_m2 <- list.load(input_path("2024_02_14_data_list_m2.rds"))
data_list_m3 <- list.load(input_path("2024_02_14_data_list_m3.rds"))
data_list_m4 <- list.load(input_path("2024_02_14_data_list_m4.rds"))
data_list_m5 <- list.load(input_path("2024_02_14_data_list_m5.rds"))
data_list_pm1 <- list.load(input_path("2024_02_14_data_list_pm1.rds"))
data_list_pm2 <- list.load(input_path("2024_02_14_data_list_pm2.rds"))
data_list_pm3 <- list.load(input_path("2024_02_14_data_list_pm3.rds"))
data_list_pm4 <- list.load(input_path("2024_02_14_data_list_pm4.rds"))
data_list_pm5 <- list.load(input_path("2024_02_14_data_list_pm5.rds"))
oom_list_m1 <- list.load(input_path("2024_02_14_oom_list_m1.rds"))
oom_list_m2 <- list.load(input_path("2024_02_14_oom_list_m2.rds"))
oom_list_m3 <- list.load(input_path("2024_02_14_oom_list_m3.rds"))
oom_list_m4 <- list.load(input_path("2024_02_14_oom_list_m4.rds"))
oom_list_m5 <- list.load(input_path("2024_02_14_oom_list_m5.rds"))
oom_list_pm1 <- list.load(input_path("2024_02_14_oom_list_pm1.rds"))
oom_list_pm2 <- list.load(input_path("2024_02_14_oom_list_pm2.rds"))
oom_list_pm3 <- list.load(input_path("2024_02_14_oom_list_pm3.rds"))
oom_list_pm4 <- list.load(input_path("2024_02_14_oom_list_pm4.rds"))
oom_list_pm5 <- list.load(input_path("2024_02_14_oom_list_pm5.rds"))
```

## Generating custom distance measures

```{r}
###############################################################################
# 2. Add standard normalized variations to the distance metrics list (also
# achievable through toggling automatic_standard_normalize parameter in
# `batch_snf`)
###############################################################################
my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

summarize_distance_metrics_list(my_distance_metrics)
```

## Generating the settings matrix

```{r}
###############################################################################
# 3. Generate the settings matrix
###############################################################################
settings_matrix <- generate_settings_matrix(
    data_list_m1,
    nrow = 200,
    seed = 42,
    distance_metrics_list = my_distance_metrics
)

write_csv(settings_matrix, proc_path("settings_matrix.csv", TRUE))

settings_matrix <- read_csv(
    proc_path(
        "2024_02_14_settings_matrix.csv"
    )
)
```

## SNF for each of the imputations

```{r}
# mTBI only imputed
# Imputation 1
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m1 <- batch_snf(
        data_list = data_list_m1,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m1, proc_path("solutions_matrix_m1.csv", TRUE))
# Imputation 2
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m2 <- batch_snf(
        data_list = data_list_m2,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m2, proc_path("solutions_matrix_m2.csv", TRUE))
# Imputation 3
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m3 <- batch_snf(
        data_list = data_list_m3,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m3, proc_path("solutions_matrix_m3.csv", TRUE))
# Imputation 4
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m4 <- batch_snf(
        data_list = data_list_m4,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m4, proc_path("solutions_matrix_m4.csv", TRUE))
# Imputation 5
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m5 <- batch_snf(
        data_list = data_list_m5,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m5, proc_path("solutions_matrix_m5.csv", TRUE))
#
# mTBI and uninjured pooled imputed
# Imputation 1
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm1 <- batch_snf(
        data_list = data_list_pm1,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm1, proc_path("solutions_matrix_pm1.csv", TRUE))
# Imputation 2
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm2 <- batch_snf(
        data_list = data_list_pm2,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm2, proc_path("solutions_matrix_pm2.csv", TRUE))
# Imputation 3
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm3 <- batch_snf(
        data_list = data_list_pm3,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm3, proc_path("solutions_matrix_pm3.csv", TRUE))
# Imputation 4
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm4 <- batch_snf(
        data_list = data_list_pm4,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm4, proc_path("solutions_matrix_pm4.csv", TRUE))
# Imputation 5
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm5 <- batch_snf(
        data_list = data_list_pm5,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm5, proc_path("solutions_matrix_pm5.csv", TRUE))
```


## Re-importing the generated solutions

```{r}
solutions_matrix_m1 <- read_csv(proc_path("2024_02_14_solutions_matrix_m1.csv"))
solutions_matrix_m2 <- read_csv(proc_path("2024_02_14_solutions_matrix_m2.csv"))
solutions_matrix_m3 <- read_csv(proc_path("2024_02_14_solutions_matrix_m3.csv"))
solutions_matrix_m4 <- read_csv(proc_path("2024_02_14_solutions_matrix_m4.csv"))
solutions_matrix_m5 <- read_csv(proc_path("2024_02_14_solutions_matrix_m5.csv"))
solutions_matrix_pm1 <- read_csv(proc_path("2024_02_14_solutions_matrix_pm1.csv"))
solutions_matrix_pm2 <- read_csv(proc_path("2024_02_14_solutions_matrix_pm2.csv"))
solutions_matrix_pm3 <- read_csv(proc_path("2024_02_14_solutions_matrix_pm3.csv"))
solutions_matrix_pm4 <- read_csv(proc_path("2024_02_14_solutions_matrix_pm4.csv"))
solutions_matrix_pm5 <- read_csv(proc_path("2024_02_14_solutions_matrix_pm5.csv"))
#
all_mtbi_imputations <- do.call(
    "rbind",
    list(
        solutions_matrix_m1,
        solutions_matrix_m2,
        solutions_matrix_m3,
        solutions_matrix_m4,
        solutions_matrix_m5,
        solutions_matrix_pm1,
        solutions_matrix_pm2,
        solutions_matrix_pm3,
        solutions_matrix_pm4,
        solutions_matrix_pm5
    )
)

aris_m1 <- calc_om_aris(solutions_matrix_m1, verbose = TRUE)
write_csv(data.frame(aris_m1), proc_path("aris_m1.csv", TRUE))
aris_m2 <- calc_om_aris(solutions_matrix_m2, verbose = TRUE)
write_csv(data.frame(aris_m2), proc_path("aris_m2.csv", TRUE))
aris_m3 <- calc_om_aris(solutions_matrix_m3, verbose = TRUE)
write_csv(data.frame(aris_m3), proc_path("aris_m3.csv", TRUE))
aris_m4 <- calc_om_aris(solutions_matrix_m4, verbose = TRUE)
write_csv(data.frame(aris_m4), proc_path("aris_m4.csv", TRUE))
aris_m5 <- calc_om_aris(solutions_matrix_m5, verbose = TRUE)
write_csv(data.frame(aris_m5), proc_path("aris_m5.csv", TRUE))
aris_pm1 <- calc_om_aris(solutions_matrix_pm1, verbose = TRUE)
write_csv(data.frame(aris_pm1), proc_path("aris_pm1.csv", TRUE))
aris_pm2 <- calc_om_aris(solutions_matrix_pm2, verbose = TRUE)
write_csv(data.frame(aris_pm2), proc_path("aris_pm2.csv", TRUE))
aris_pm3 <- calc_om_aris(solutions_matrix_pm3, verbose = TRUE)
write_csv(data.frame(aris_pm3), proc_path("aris_pm3.csv", TRUE))
aris_pm4 <- calc_om_aris(solutions_matrix_pm4, verbose = TRUE)
write_csv(data.frame(aris_pm4), proc_path("aris_pm4.csv", TRUE))
aris_pm5 <- calc_om_aris(solutions_matrix_pm5, verbose = TRUE)
write_csv(data.frame(aris_pm5), proc_path("aris_pm5.csv", TRUE))

aris_all_mtbi_imputations <- calc_om_aris(all_mtbi_imputations, verbose = TRUE)
write_csv(
    data.frame(aris_all_mtbi_imputations),
    proc_path("aris_all_mtbi_imputations.csv", TRUE)
)

```

## Re-importing the ARIs

```{r}
aris_m1 <- read_csv(proc_path("2024_02_15_aris_m1.csv")) |> as.matrix()
aris_m2 <- read_csv(proc_path("2024_02_15_aris_m2.csv")) |> as.matrix()
aris_m3 <- read_csv(proc_path("2024_02_15_aris_m3.csv")) |> as.matrix()
aris_m4 <- read_csv(proc_path("2024_02_15_aris_m4.csv")) |> as.matrix()
aris_m5 <- read_csv(proc_path("2024_02_15_aris_m5.csv")) |> as.matrix()
aris_pm1 <- read_csv(proc_path("2024_02_15_aris_pm1.csv")) |> as.matrix()
aris_pm2 <- read_csv(proc_path("2024_02_15_aris_pm2.csv")) |> as.matrix()
aris_pm3 <- read_csv(proc_path("2024_02_15_aris_pm3.csv")) |> as.matrix()
aris_pm4 <- read_csv(proc_path("2024_02_15_aris_pm4.csv")) |> as.matrix()
aris_pm5 <- read_csv(proc_path("2024_02_15_aris_pm5.csv")) |> as.matrix()

aris_all_mtbi_imputations <- read_csv(
    proc_path("2024_02_15_aris_all_mtbi_imputations.csv")
) |>
    as.matrix()
```

## Plotting the ARIs

### Initial plot across all ARIs to extract order

```{r}
aris_all_mtbi_imputations_heatmap <- similarity_matrix_heatmap(
    aris_all_mtbi_imputations,
    log_graph = FALSE,
    cluster_rows = TRUE,
    cluster_columns = TRUE
)

aris_all_mtbi_imputations_heatmap <- ComplexHeatmap::draw(
    aris_all_mtbi_imputations_heatmap
)
aris_all_mtbi_imputations_order <- ComplexHeatmap::row_order(
    aris_all_mtbi_imputations_heatmap
)

write_csv(
    data.frame(aris_all_mtbi_imputations_order),
    proc_path("aris_all_mtbi_imputations_order.csv", TRUE)
)
```

### Re-importing the order

```{r}
aris_all_mtbi_imputations_order <- unlist(
    read_csv(proc_path("2024_02_16_aris_all_mtbi_imputations_order.csv"))
)

names(aris_all_mtbi_imputations_order) <- NULL
```

## Full imputation meta clustering plot with impairment levels

```{r}
imputation_labels <- data.frame(
    "imputation" = c(
        rep("m1", 200),
        rep("m2", 200),
        rep("m3", 200),
        rep("m4", 200),
        rep("m5", 200),
        rep("pm1", 200),
        rep("pm2", 200),
        rep("pm3", 200),
        rep("pm4", 200),
        rep("pm5", 200)
    ),
    "pooled" = c(
        rep("yes", 1000),
        rep("no", 1000)
    )
)

full_solutions_matrix <- cbind(all_mtbi_imputations, imputation_labels)

full_solutions_matrix$"nclust2" <- full_solutions_matrix$"nclust" - 2

full_mtbi_o_extended_solutions_matrix <- extend_solutions(
    full_solutions_matrix,
    oom_list_m1,
    verbose = TRUE,
    min_pval = 1e-10
)

write_csv(
    full_mtbi_o_extended_solutions_matrix,
    proc_path("full_mtbi_o_extended_solutions_matrix.csv", TRUE)
)

full_mtbi_io_extended_solutions_matrix <- extend_solutions(
    full_solutions_matrix,
    target_list = c(data_list_m1, oom_list_m1),
    verbose = TRUE,
    min_pval = 1e-10
)

full_mtbi_io_extended_solutions_matrix

write_csv(
    full_mtbi_io_extended_solutions_matrix,
    proc_path("full_mtbi_io_extended_solutions_matrix.csv", TRUE)
)

```

The "o" is for just extending on the output variables (CBCL/SDS), while the "io" is for both input and output variables.

```{r}
full_mtbi_o_extended_solutions_matrix <- read_csv(
    proc_path("2024_02_24_full_mtbi_o_extended_solutions_matrix.csv")
)

full_mtbi_io_extended_solutions_matrix <- read_csv(
    proc_path("2024_02_24_full_mtbi_io_extended_solutions_matrix.csv")
)
```

```{r}

split_vec = c(
    233,
    500,
    723,
    830,
    1404,
    1685,
    1900
)
mtbi_mc_heatmap <- my_similarity_matrix_heatmap(
    aris = aris_all_mtbi_imputations,
    aris_order = aris_all_mtbi_imputations_order,
    extended_solutions = full_mtbi_o_extended_solutions_matrix,
    split_vector = split_vec
)

mtbi_mc_heatmap

# PNG export
grDevices::png(
    fig_path("mtbi_mc_heatmap.png", TRUE),
    width = 3000,
    height = 3000,
    res = 300
)
mtbi_mc_heatmap
grDevices::dev.off()
```

## One-MC-at-a-time

```{r}

mtbi_manhattan <- my_manhattan_plot(
    solutions_matrix = full_mtbi_io_extended_solutions_matrix,
    aris_order = aris_all_mtbi_imputations_order,
    split_vector = split_vec,
    data_list = data_list_m1,
    target_list = oom_list_m1,
    colours = c(
        "I-AS" = "#1B9E77",
        "I-D" = "#D95F02",
        "I-N" = "#7570B3",
        "I-MH" = "#E7298A",
        "I-P" = "#66A61E",
        "O-S" = "#E6AB02",
        "O-B" = "#A6761D"
    )
)
mtbi_manhattan

ggsave(
    plot = mtbi_manhattan,
    fig_path("mtbi_manhattan.png", TRUE),
    width = 15,
    height = 8 * 2.5
)

# Bulk export each MC individually
for (mc in c("A", "B", "C", "D", "E")) {
    mc_plot <- my_manhattan_plot(
        solutions_matrix = full_mtbi_io_extended_solutions_matrix,
        aris_order = aris_all_mtbi_imputations_order,
        split_vector = split_vec,
        data_list = data_list_m1,
        target_list = oom_list_m1,
        mcs = mc,
        colours = c(
            "I-AS" = "#1B9E77",
            "I-D" = "#D95F02",
            "I-N" = "#7570B3",
            "I-MH" = "#E7298A",
            "I-P" = "#66A61E",
            "O-S" = "#E6AB02",
            "O-B" = "#A6761D"
        )
    )
    mc_path <- paste0(
        "mtbi_mc_",
        gsub("-", "_", tolower(mc)),
        "_manhattan.png"
    )
    ggsave(
        plot = mc_plot,
        fig_path(mc_path, TRUE),
        width = 15,
        height = 5
    )
}
```

## Replication in demographic-corrected data

```{r}
data_list_m1 <- list.load(input_path("2024_02_14_data_list_m1.rds"))
data_list_m2 <- list.load(input_path("2024_02_14_data_list_m2.rds"))
data_list_m3 <- list.load(input_path("2024_02_14_data_list_m3.rds"))
data_list_m4 <- list.load(input_path("2024_02_14_data_list_m4.rds"))
data_list_m5 <- list.load(input_path("2024_02_14_data_list_m5.rds"))
data_list_pm1 <- list.load(input_path("2024_02_14_data_list_pm1.rds"))
data_list_pm2 <- list.load(input_path("2024_02_14_data_list_pm2.rds"))
data_list_pm3 <- list.load(input_path("2024_02_14_data_list_pm3.rds"))
data_list_pm4 <- list.load(input_path("2024_02_14_data_list_pm4.rds"))
data_list_pm5 <- list.load(input_path("2024_02_14_data_list_pm5.rds"))
oom_list_m1 <- list.load(input_path("2024_02_14_oom_list_m1.rds"))
oom_list_m2 <- list.load(input_path("2024_02_14_oom_list_m2.rds"))
oom_list_m3 <- list.load(input_path("2024_02_14_oom_list_m3.rds"))
oom_list_m4 <- list.load(input_path("2024_02_14_oom_list_m4.rds"))
oom_list_m5 <- list.load(input_path("2024_02_14_oom_list_m5.rds"))
oom_list_pm1 <- list.load(input_path("2024_02_14_oom_list_pm1.rds"))
oom_list_pm2 <- list.load(input_path("2024_02_14_oom_list_pm2.rds"))
oom_list_pm3 <- list.load(input_path("2024_02_14_oom_list_pm3.rds"))
oom_list_pm4 <- list.load(input_path("2024_02_14_oom_list_pm4.rds"))
oom_list_pm5 <- list.load(input_path("2024_02_14_oom_list_pm5.rds"))

data_list_no_demo_m1 <- data_list_m1
data_list_no_demo_m2 <- data_list_m2
data_list_no_demo_m3 <- data_list_m3
data_list_no_demo_m4 <- data_list_m4
data_list_no_demo_m5 <- data_list_m5
data_list_no_demo_pm1 <- data_list_pm1
data_list_no_demo_pm2 <- data_list_pm2
data_list_no_demo_pm3 <- data_list_pm3
data_list_no_demo_pm4 <- data_list_pm4
data_list_no_demo_pm5 <- data_list_pm5
oom_list_no_demo_m1 <- oom_list_m1
oom_list_no_demo_m2 <- oom_list_m2
oom_list_no_demo_m3 <- oom_list_m3
oom_list_no_demo_m4 <- oom_list_m4
oom_list_no_demo_m5 <- oom_list_m5
oom_list_no_demo_pm1 <- oom_list_pm1
oom_list_no_demo_pm2 <- oom_list_pm2
oom_list_no_demo_pm3 <- oom_list_pm3
oom_list_no_demo_pm4 <- oom_list_pm4
oom_list_no_demo_pm5 <- oom_list_pm5

demo_list_m1 <- data_list_no_demo_m1[c(4, 6, 7, 8)]
demo_list_m2 <- data_list_no_demo_m2[c(4, 6, 7, 8)]
demo_list_m3 <- data_list_no_demo_m3[c(4, 6, 7, 8)]
demo_list_m4 <- data_list_no_demo_m4[c(4, 6, 7, 8)]
demo_list_m5 <- data_list_no_demo_m5[c(4, 6, 7, 8)]

demo_list_pm1 <- data_list_no_demo_pm1[c(1, 2, 3, 4)]
demo_list_pm2 <- data_list_no_demo_pm2[c(1, 2, 3, 4)]
demo_list_pm3 <- data_list_no_demo_pm3[c(1, 2, 3, 4)]
demo_list_pm4 <- data_list_no_demo_pm4[c(1, 2, 3, 4)]
demo_list_pm5 <- data_list_no_demo_pm5[c(1, 2, 3, 4)]

data_list_no_demo_m1[c(4, 6, 7, 8)] <- NULL
data_list_no_demo_m2[c(4, 6, 7, 8)] <- NULL
data_list_no_demo_m3[c(4, 6, 7, 8)] <- NULL
data_list_no_demo_m4[c(4, 6, 7, 8)] <- NULL
data_list_no_demo_m5[c(4, 6, 7, 8)] <- NULL

data_list_no_demo_pm1[c(1, 2, 3, 4)] <- NULL
data_list_no_demo_pm2[c(1, 2, 3, 4)] <- NULL
data_list_no_demo_pm3[c(1, 2, 3, 4)] <- NULL
data_list_no_demo_pm4[c(1, 2, 3, 4)] <- NULL
data_list_no_demo_pm5[c(1, 2, 3, 4)] <- NULL

data_list_no_demo_m1 <- remove_signal(data_list_no_demo_m1, demo_list_m1)
data_list_no_demo_m2 <- remove_signal(data_list_no_demo_m2, demo_list_m2)
data_list_no_demo_m3 <- remove_signal(data_list_no_demo_m3, demo_list_m3)
data_list_no_demo_m4 <- remove_signal(data_list_no_demo_m4, demo_list_m4)
data_list_no_demo_m5 <- remove_signal(data_list_no_demo_m5, demo_list_m5)
data_list_no_demo_pm1 <- remove_signal(data_list_no_demo_pm1, demo_list_pm1)
data_list_no_demo_pm2 <- remove_signal(data_list_no_demo_pm2, demo_list_pm2)
data_list_no_demo_pm3 <- remove_signal(data_list_no_demo_pm3, demo_list_pm3)
data_list_no_demo_pm4 <- remove_signal(data_list_no_demo_pm4, demo_list_pm4)
data_list_no_demo_pm5 <- remove_signal(data_list_no_demo_pm5, demo_list_pm5)
oom_list_no_demo_m1 <- remove_signal(oom_list_no_demo_m1, demo_list_m1)
oom_list_no_demo_m2 <- remove_signal(oom_list_no_demo_m2, demo_list_m2)
oom_list_no_demo_m3 <- remove_signal(oom_list_no_demo_m3, demo_list_m3)
oom_list_no_demo_m4 <- remove_signal(oom_list_no_demo_m4, demo_list_m4)
oom_list_no_demo_m5 <- remove_signal(oom_list_no_demo_m5, demo_list_m5)
oom_list_no_demo_pm1 <- remove_signal(oom_list_no_demo_pm1, demo_list_pm1)
oom_list_no_demo_pm2 <- remove_signal(oom_list_no_demo_pm2, demo_list_pm2)
oom_list_no_demo_pm3 <- remove_signal(oom_list_no_demo_pm3, demo_list_pm3)
oom_list_no_demo_pm4 <- remove_signal(oom_list_no_demo_pm4, demo_list_pm4)
oom_list_no_demo_pm5 <- remove_signal(oom_list_no_demo_pm5, demo_list_pm5)

list.save(data_list_no_demo_m1, input_path("data_list_no_demo_m1.rds", TRUE))
list.save(data_list_no_demo_m2, input_path("data_list_no_demo_m2.rds", TRUE))
list.save(data_list_no_demo_m3, input_path("data_list_no_demo_m3.rds", TRUE))
list.save(data_list_no_demo_m4, input_path("data_list_no_demo_m4.rds", TRUE))
list.save(data_list_no_demo_m5, input_path("data_list_no_demo_m5.rds", TRUE))
list.save(data_list_no_demo_pm1, input_path("data_list_no_demo_pm1.rds", TRUE))
list.save(data_list_no_demo_pm2, input_path("data_list_no_demo_pm2.rds", TRUE))
list.save(data_list_no_demo_pm3, input_path("data_list_no_demo_pm3.rds", TRUE))
list.save(data_list_no_demo_pm4, input_path("data_list_no_demo_pm4.rds", TRUE))
list.save(data_list_no_demo_pm5, input_path("data_list_no_demo_pm5.rds", TRUE))
list.save(oom_list_no_demo_m1, input_path("oom_list_no_demo_m1.rds", TRUE))
list.save(oom_list_no_demo_m2, input_path("oom_list_no_demo_m2.rds", TRUE))
list.save(oom_list_no_demo_m3, input_path("oom_list_no_demo_m3.rds", TRUE))
list.save(oom_list_no_demo_m4, input_path("oom_list_no_demo_m4.rds", TRUE))
list.save(oom_list_no_demo_m5, input_path("oom_list_no_demo_m5.rds", TRUE))
list.save(oom_list_no_demo_pm1, input_path("oom_list_no_demo_pm1.rds", TRUE))
list.save(oom_list_no_demo_pm2, input_path("oom_list_no_demo_pm2.rds", TRUE))
list.save(oom_list_no_demo_pm3, input_path("oom_list_no_demo_pm3.rds", TRUE))
list.save(oom_list_no_demo_pm4, input_path("oom_list_no_demo_pm4.rds", TRUE))
list.save(oom_list_no_demo_pm5, input_path("oom_list_no_demo_pm5.rds", TRUE))

data_list_no_demo_m1 <- list.load(
    input_path(
        "2024_02_25_data_list_no_demo_m1.rds"
    )
)
data_list_no_demo_m2 <- list.load(
    input_path(
        "2024_02_25_data_list_no_demo_m2.rds"
    )
)
data_list_no_demo_m3 <- list.load(
    input_path(
        "2024_02_25_data_list_no_demo_m3.rds"
    )
)
data_list_no_demo_m4 <- list.load(
    input_path(
        "2024_02_25_data_list_no_demo_m4.rds"
    )
)
data_list_no_demo_m5 <- list.load(
    input_path(
        "2024_02_25_data_list_no_demo_m5.rds"
    )
)
data_list_no_demo_pm1 <- list.load(
    input_path(
        "2024_02_25_data_list_no_demo_pm1.rds"
    )
)
data_list_no_demo_pm2 <- list.load(
    input_path(
        "2024_02_25_data_list_no_demo_pm2.rds"
    )
)
data_list_no_demo_pm3 <- list.load(
    input_path(
        "2024_02_25_data_list_no_demo_pm3.rds"
    )
)
data_list_no_demo_pm4 <- list.load(
    input_path(
        "2024_02_25_data_list_no_demo_pm4.rds"
    )
)
data_list_no_demo_pm5 <- list.load(
    input_path(
        "2024_02_25_data_list_no_demo_pm5.rds"
    )
)
oom_list_no_demo_m1 <- list.load(
    input_path(
        "2024_02_25_oom_list_no_demo_m1.rds"
    )
)
oom_list_no_demo_m2 <- list.load(
    input_path(
        "2024_02_25_oom_list_no_demo_m2.rds"
    )
)
oom_list_no_demo_m3 <- list.load(
    input_path(
        "2024_02_25_oom_list_no_demo_m3.rds"
    )
)
oom_list_no_demo_m4 <- list.load(
    input_path(
        "2024_02_25_oom_list_no_demo_m4.rds"
    )
)
oom_list_no_demo_m5 <- list.load(
    input_path(
        "2024_02_25_oom_list_no_demo_m5.rds"
    )
)
oom_list_no_demo_pm1 <- list.load(
    input_path(
        "2024_02_25_oom_list_no_demo_pm1.rds"
    )
)
oom_list_no_demo_pm2 <- list.load(
    input_path(
        "2024_02_25_oom_list_no_demo_pm2.rds"
    )
)
oom_list_no_demo_pm3 <- list.load(
    input_path(
        "2024_02_25_oom_list_no_demo_pm3.rds"
    )
)
oom_list_no_demo_pm4 <- list.load(
    input_path(
        "2024_02_25_oom_list_no_demo_pm4.rds"
    )
)
oom_list_no_demo_pm5 <- list.load(
    input_path(
        "2024_02_25_oom_list_no_demo_pm5.rds"
    )
)

settings_matrix_no_demo <- generate_settings_matrix(
    data_list_no_demo_m1,
    nrow = 200,
    seed = 42,
    distance_metrics_list = my_distance_metrics
)

write_csv(
    settings_matrix_no_demo,
    proc_path("settings_matrix_no_demo.csv", TRUE)
)

settings_matrix_no_demo <- read_csv(
    proc_path("2024_02_25_settings_matrix_no_demo.csv")
)

###############################################################################
# SNF!
###############################################################################

# mTBI only imputed
# Imputation 1
start <- proc.time()
progressr::with_progress({
    solutions_matrix_no_demo_m1 <- batch_snf(
        data_list = data_list_no_demo_m1,
        settings_matrix = settings_matrix_no_demo,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_no_demo_m1,
    proc_path("solutions_matrix_no_demo_m1.csv", TRUE)
)
# Imputation 2
start <- proc.time()
progressr::with_progress({
    solutions_matrix_no_demo_m2 <- batch_snf(
        data_list = data_list_no_demo_m2,
        settings_matrix = settings_matrix_no_demo,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_no_demo_m2,
    proc_path("solutions_matrix_no_demo_m2.csv", TRUE)
)
# Imputation 3
start <- proc.time()
progressr::with_progress({
    solutions_matrix_no_demo_m3 <- batch_snf(
        data_list = data_list_no_demo_m3,
        settings_matrix = settings_matrix_no_demo,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_no_demo_m3,
    proc_path("solutions_matrix_no_demo_m3.csv", TRUE)
)
# Imputation 4
start <- proc.time()
progressr::with_progress({
    solutions_matrix_no_demo_m4 <- batch_snf(
        data_list = data_list_no_demo_m4,
        settings_matrix = settings_matrix_no_demo,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_no_demo_m4,
    proc_path("solutions_matrix_no_demo_m4.csv", TRUE)
)
# Imputation 5
start <- proc.time()
progressr::with_progress({
    solutions_matrix_no_demo_m5 <- batch_snf(
        data_list = data_list_no_demo_m5,
        settings_matrix = settings_matrix_no_demo,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_no_demo_m5,
    proc_path("solutions_matrix_no_demo_m5.csv", TRUE)
)

# mTBI and uninjured pooled imputed
# Imputation 1
start <- proc.time()
progressr::with_progress({
    solutions_matrix_no_demo_pm1 <- batch_snf(
        data_list = data_list_no_demo_pm1,
        settings_matrix = settings_matrix_no_demo,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_no_demo_pm1,
    proc_path("solutions_matrix_no_demo_pm1.csv", TRUE)
)
# Imputation 2
start <- proc.time()
progressr::with_progress({
    solutions_matrix_no_demo_pm2 <- batch_snf(
        data_list = data_list_no_demo_pm2,
        settings_matrix = settings_matrix_no_demo,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_no_demo_pm2,
    proc_path("solutions_matrix_no_demo_pm2.csv", TRUE)
)
# Imputation 3
start <- proc.time()
progressr::with_progress({
    solutions_matrix_no_demo_pm3 <- batch_snf(
        data_list = data_list_no_demo_pm3,
        settings_matrix = settings_matrix_no_demo,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_no_demo_pm3,
    proc_path("solutions_matrix_no_demo_pm3.csv", TRUE)
)
# Imputation 4
start <- proc.time()
progressr::with_progress({
    solutions_matrix_no_demo_pm4 <- batch_snf(
        data_list = data_list_no_demo_pm4,
        settings_matrix = settings_matrix_no_demo,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_no_demo_pm4,
    proc_path("solutions_matrix_no_demo_pm4.csv", TRUE)
)
# Imputation 5
start <- proc.time()
progressr::with_progress({
    solutions_matrix_no_demo_pm5 <- batch_snf(
        data_list = data_list_no_demo_pm5,
        settings_matrix = settings_matrix_no_demo,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_no_demo_pm5,
    proc_path("solutions_matrix_no_demo_pm5.csv", TRUE)
)

solutions_matrix_no_demo_m1 <- read_csv(proc_path("2024_02_25_solutions_matrix_no_demo_m1.csv"))
solutions_matrix_no_demo_m2 <- read_csv(proc_path("2024_02_25_solutions_matrix_no_demo_m2.csv"))
solutions_matrix_no_demo_m3 <- read_csv(proc_path("2024_02_25_solutions_matrix_no_demo_m3.csv"))
solutions_matrix_no_demo_m4 <- read_csv(proc_path("2024_02_25_solutions_matrix_no_demo_m4.csv"))
solutions_matrix_no_demo_m5 <- read_csv(proc_path("2024_02_25_solutions_matrix_no_demo_m5.csv"))
solutions_matrix_no_demo_pm1 <- read_csv(proc_path("2024_02_25_solutions_matrix_no_demo_pm1.csv"))
solutions_matrix_no_demo_pm2 <- read_csv(proc_path("2024_02_25_solutions_matrix_no_demo_pm2.csv"))
solutions_matrix_no_demo_pm3 <- read_csv(proc_path("2024_02_25_solutions_matrix_no_demo_pm3.csv"))
solutions_matrix_no_demo_pm4 <- read_csv(proc_path("2024_02_25_solutions_matrix_no_demo_pm4.csv"))
solutions_matrix_no_demo_pm5 <- read_csv(proc_path("2024_02_25_solutions_matrix_no_demo_pm5.csv"))

all_mtbi_imputations_no_demo <- do.call(
    "rbind",
    list(
        solutions_matrix_no_demo_m1,
        solutions_matrix_no_demo_m2,
        solutions_matrix_no_demo_m3,
        solutions_matrix_no_demo_m4,
        solutions_matrix_no_demo_m5,
        solutions_matrix_no_demo_pm1,
        solutions_matrix_no_demo_pm2,
        solutions_matrix_no_demo_pm3,
        solutions_matrix_no_demo_pm4,
        solutions_matrix_no_demo_pm5
    )
)

aris_m1_no_demo <- calc_om_aris(solutions_matrix_no_demo_m1, verbose = TRUE)
write_csv(data.frame(aris_m1_no_demo), proc_path("aris_m1_no_demo.csv", TRUE))
aris_m2_no_demo <- calc_om_aris(solutions_matrix_no_demo_m2, verbose = TRUE)
write_csv(data.frame(aris_m2_no_demo), proc_path("aris_m2_no_demo.csv", TRUE))
aris_m3_no_demo <- calc_om_aris(solutions_matrix_no_demo_m3, verbose = TRUE)
write_csv(data.frame(aris_m3_no_demo), proc_path("aris_m3_no_demo.csv", TRUE))
aris_m4_no_demo <- calc_om_aris(solutions_matrix_no_demo_m4, verbose = TRUE)
write_csv(data.frame(aris_m4_no_demo), proc_path("aris_m4_no_demo.csv", TRUE))
aris_m5_no_demo <- calc_om_aris(solutions_matrix_no_demo_m5, verbose = TRUE)
write_csv(data.frame(aris_m5_no_demo), proc_path("aris_m5_no_demo.csv", TRUE))
aris_pm1_no_demo <- calc_om_aris(solutions_matrix_no_demo_pm1, verbose = TRUE)
write_csv(data.frame(aris_pm1_no_demo), proc_path("aris_pm1_no_demo.csv", TRUE))
aris_pm2_no_demo <- calc_om_aris(solutions_matrix_no_demo_pm2, verbose = TRUE)
write_csv(data.frame(aris_pm2_no_demo), proc_path("aris_pm2_no_demo.csv", TRUE))
aris_pm3_no_demo <- calc_om_aris(solutions_matrix_no_demo_pm3, verbose = TRUE)
write_csv(data.frame(aris_pm3_no_demo), proc_path("aris_pm3_no_demo.csv", TRUE))
aris_pm4_no_demo <- calc_om_aris(solutions_matrix_no_demo_pm4, verbose = TRUE)
write_csv(data.frame(aris_pm4_no_demo), proc_path("aris_pm4_no_demo.csv", TRUE))
aris_pm5_no_demo <- calc_om_aris(solutions_matrix_no_demo_pm5, verbose = TRUE)
write_csv(data.frame(aris_pm5_no_demo), proc_path("aris_pm5_no_demo.csv", TRUE))

aris_all_mtbi_imputations_no_demo <- calc_om_aris(
    all_mtbi_imputations_no_demo,
    verbose = TRUE
)
write_csv(
    data.frame(aris_all_mtbi_imputations_no_demo),
    proc_path("aris_all_mtbi_imputations_no_demo.csv", TRUE)
)

```

## Re-importing the ARIs

```{r}
aris_m1_no_demo <- read_csv(proc_path("2024_02_25_aris_m1_no_demo.csv")) |> as.matrix()
aris_m2_no_demo <- read_csv(proc_path("2024_02_25_aris_m2_no_demo.csv")) |> as.matrix()
aris_m3_no_demo <- read_csv(proc_path("2024_02_25_aris_m3_no_demo.csv")) |> as.matrix()
aris_m4_no_demo <- read_csv(proc_path("2024_02_25_aris_m4_no_demo.csv")) |> as.matrix()
aris_m5_no_demo <- read_csv(proc_path("2024_02_25_aris_m5_no_demo.csv")) |> as.matrix()
aris_pm1_no_demo <- read_csv(proc_path("2024_02_25_aris_pm1_no_demo.csv")) |> as.matrix()
aris_pm2_no_demo <- read_csv(proc_path("2024_02_25_aris_pm2_no_demo.csv")) |> as.matrix()
aris_pm3_no_demo <- read_csv(proc_path("2024_02_25_aris_pm3_no_demo.csv")) |> as.matrix()
aris_pm4_no_demo <- read_csv(proc_path("2024_02_25_aris_pm4_no_demo.csv")) |> as.matrix()
aris_pm5_no_demo <- read_csv(proc_path("2024_02_25_aris_pm5_no_demo.csv")) |> as.matrix()

aris_all_mtbi_imputations_no_demo <- read_csv(
    proc_path("2024_02_25_aris_all_mtbi_imputations_no_demo.csv")
) |>
    as.matrix()
```

## Plotting the ARIs

### Initial plot across all ARIs to extract order

```{r}
aris_all_mtbi_imputations_no_demo_heatmap <- similarity_matrix_heatmap(
    aris_all_mtbi_imputations_no_demo,
    log_graph = FALSE,
    cluster_rows = TRUE,
    cluster_columns = TRUE
)

aris_all_mtbi_imputations_no_demo_heatmap <- ComplexHeatmap::draw(
    aris_all_mtbi_imputations_no_demo_heatmap
)
aris_all_mtbi_imputations_order_no_demo <- ComplexHeatmap::row_order(
    aris_all_mtbi_imputations_no_demo_heatmap
)

write_csv(
    data.frame(aris_all_mtbi_imputations_order_no_demo),
    proc_path("aris_all_mtbi_imputations_order_no_demo.csv", TRUE)
)
```

### Re-importing the order

```{r}
aris_all_mtbi_imputations_order_no_demo <- unlist(
    read_csv(
        proc_path("2024_02_25_aris_all_mtbi_imputations_order_no_demo.csv")
    )
)

names(aris_all_mtbi_imputations_order_no_demo) <- NULL
```

## Full imputation meta clustering plot with impairment levels

```{r}
imputation_labels <- data.frame(
    "imputation" = c(
        rep("m1", 200),
        rep("m2", 200),
        rep("m3", 200),
        rep("m4", 200),
        rep("m5", 200),
        rep("pm1", 200),
        rep("pm2", 200),
        rep("pm3", 200),
        rep("pm4", 200),
        rep("pm5", 200)
    ),
    "pooled" = c(
        rep("yes", 1000),
        rep("no", 1000)
    )
)

full_solutions_matrix_no_demo <- cbind(
    all_mtbi_imputations_no_demo,
    imputation_labels
)

full_solutions_matrix_no_demo$"nclust2" <-
    full_solutions_matrix_no_demo$"nclust" - 2

full_mtbi_o_extended_solutions_matrix_no_demo <- extend_solutions(
    full_solutions_matrix_no_demo,
    oom_list_no_demo_m1,
    verbose = TRUE,
    min_pval = 1e-10
)

write_csv(
    full_mtbi_o_extended_solutions_matrix_no_demo,
    proc_path("full_mtbi_o_extended_solutions_matrix_no_demo.csv", TRUE)
)

full_mtbi_io_extended_solutions_matrix_no_demo <- extend_solutions(
    full_solutions_matrix_no_demo,
    target_list = c(data_list_no_demo_m1, oom_list_no_demo_m1),
    verbose = TRUE,
    min_pval = 1e-10
)
write_csv(
    full_mtbi_io_extended_solutions_matrix_no_demo,
    proc_path("full_mtbi_io_extended_solutions_matrix_no_demo.csv", TRUE)
)

```

```{r}
full_mtbi_o_extended_solutions_matrix_no_demo <- read_csv(
    proc_path("2024_02_25_full_mtbi_o_extended_solutions_matrix_no_demo.csv")
)

full_mtbi_io_extended_solutions_matrix_no_demo <- read_csv(
    proc_path("2024_02_25_full_mtbi_io_extended_solutions_matrix_no_demo.csv")
)
```

```{r}
split_vec = c(
    417,
    683,
    750,
    830,
    964,
    1150,
    1300,
    1510,
    1890
)

mtbi_nd_mc_heatmap <- my_similarity_matrix_heatmap(
    aris = aris_all_mtbi_imputations_no_demo,
    aris_order = aris_all_mtbi_imputations_order_no_demo,
    extended_solutions = full_mtbi_o_extended_solutions_matrix_no_demo,
    split_vector = split_vec
)
mtbi_nd_mc_heatmap

# PNG export
grDevices::png(
    fig_path("mtbi_nd_mc_heatmap.png", TRUE),
    width = 3000,
    height = 3000,
    res = 300
)
mtbi_nd_mc_heatmap
grDevices::dev.off()
```

## One-MC-at-a-time

```{r}
#mc_reordered_labels_no_demo <- split_at(split_vec, 2000)
#names(aris_all_mtbi_imputations_order_no_demo) <- mc_reordered_labels_no_demo
#sorted_mc_labels_no_demo <- sort(aris_all_mtbi_imputations_order_no_demo)

#dl_no_demo_m1_renamed <- data_list_no_demo_m1 |> lapply(
#    function(x) {
#        x$"domain" <- paste0("I-", x$"domain")
#        return(x)
#    }
#)
#
#oom_no_demo_m1_renamed <- oom_list_no_demo_m1 |> lapply(
#    function(x) {
#        x$"domain" <- paste0("O-", x$"domain")
#        return(x)
#    }
#)

#my_manhattan_plot <- function(solutions_matrix,
#                              sorted_labels,
#                              mcs,
#                              data_list,
#                              colours) {
#    target_pvals <- pval_select(solutions_matrix)
#    target_pvals$"mc_label" <- names(sorted_labels)
#    target_pvals <- dplyr::select(
#        target_pvals,
#        -dplyr::starts_with(c("mean", "min"))
#    )
#    mc_associations <- manhattan_plot(
#        target_pvals,
#        threshold = 0.05,
#        bonferroni_line = FALSE,
#        data_list = data_list,
#        mc_labels = mcs,
#        colours = colours
#    )
#    return(mc_associations)
#}

# Candidates are A, B, C, D, E, F, H, J

mtbi_nd_manhattan <- my_manhattan_plot(
    solutions_matrix = full_mtbi_io_extended_solutions_matrix_no_demo,
    aris_order = aris_all_mtbi_imputations_order_no_demo,
    split_vector = split_vec,
    data_list = data_list_no_demo_m1,
    target_list = oom_list_no_demo_m1,
    colours = c(
        "I-AS" = "#1B9E77",
        "I-D" = "#D95F02",
        "I-N" = "#7570B3",
        "I-MH" = "#E7298A",
        "I-P" = "#66A61E",
        "O-S" = "#E6AB02",
        "O-B" = "#A6761D"
    )
)
mtbi_nd_manhattan

ggsave(
    plot = mtbi_nd_manhattan,
    fig_path("mtbi_nd_manhattan.png", TRUE),
    width = 15,
    height = 10*2.5
)

split_vec |>
    split_at(2000) |>
    unique()

# Bulk export each MC individually
for (mc in unique(split_at(split_vec, 2000))) {
    print(mc)
    mc_plot <- my_manhattan_plot(
        solutions_matrix = full_mtbi_io_extended_solutions_matrix,
        aris_order = aris_all_mtbi_imputations_order,
        split_vector = split_vec,
        data_list = data_list_m1,
        target_list = oom_list_m1,
        mcs = mc,
        colours = c(
            "I-AS" = "#1B9E77",
            "I-D" = "#D95F02",
            "I-N" = "#7570B3",
            "I-MH" = "#E7298A",
            "I-P" = "#66A61E",
            "O-S" = "#E6AB02",
            "O-B" = "#A6761D"
        )
    )
    mc_path <- paste0(
        "mtbi_nd_mc_",
        gsub("-", "_", tolower(mc)),
        "_manhattan.png"
    )
    ggsave(
        plot = mc_plot,
        fig_path(mc_path, TRUE),
        width = 15,
        height = 5
    )
}
```

