# metasnf over imputaions

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subjects <- read_csv(sub_path("2023_11_07_mtbi_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2023_11_07_uninjured_subjects.csv"))
mtbi_subjects_train <- read_csv(sub_path("2024_01_15_mtbi_subjects_train.csv"))
```

## Loading data and out of model lists

```{r}
data_list_m1 <- list.load(input_path("2024_01_15_data_list_m1.rds"))
data_list_m2 <- list.load(input_path("2024_01_15_data_list_m2.rds"))
data_list_m3 <- list.load(input_path("2024_01_15_data_list_m3.rds"))
data_list_m4 <- list.load(input_path("2024_01_15_data_list_m4.rds"))
data_list_m5 <- list.load(input_path("2024_01_15_data_list_m5.rds"))
data_list_pm1 <- list.load(input_path("2024_01_15_data_list_pm1.rds"))
data_list_pm2 <- list.load(input_path("2024_01_15_data_list_pm2.rds"))
data_list_pm3 <- list.load(input_path("2024_01_15_data_list_pm3.rds"))
data_list_pm4 <- list.load(input_path("2024_01_15_data_list_pm4.rds"))
data_list_pm5 <- list.load(input_path("2024_01_15_data_list_pm5.rds"))
oom_list_m1 <- list.load(input_path("2024_01_24_oom_list_m1.rds"))
oom_list_m2 <- list.load(input_path("2024_01_24_oom_list_m2.rds"))
oom_list_m3 <- list.load(input_path("2024_01_24_oom_list_m3.rds"))
oom_list_m4 <- list.load(input_path("2024_01_24_oom_list_m4.rds"))
oom_list_m5 <- list.load(input_path("2024_01_24_oom_list_m5.rds"))
oom_list_pm1 <- list.load(input_path("2024_01_24_oom_list_pm1.rds"))
oom_list_pm2 <- list.load(input_path("2024_01_24_oom_list_pm2.rds"))
oom_list_pm3 <- list.load(input_path("2024_01_24_oom_list_pm3.rds"))
oom_list_pm4 <- list.load(input_path("2024_01_24_oom_list_pm4.rds"))
oom_list_pm5 <- list.load(input_path("2024_01_24_oom_list_pm5.rds"))
```

## Generating custom distance measures

```{r}
###############################################################################
# 2. Add standard normalized variations to the distance metrics list (also
# achievable through toggling automatic_standard_normalize parameter in
# `batch_snf`)
###############################################################################
my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

summarize_distance_metrics_list(my_distance_metrics)
```

## Generating the settings matrix

```{r}
###############################################################################
# 3. Generate the settings matrix
###############################################################################
settings_matrix <- generate_settings_matrix(
    data_list_m1,
    nrow = 200,
    seed = 42,
    distance_metrics_list = my_distance_metrics
)

write_csv(settings_matrix, proc_path("settings_matrix.csv", TRUE))

settings_matrix <- read_csv(
    proc_path(
        "2024_01_15_settings_matrix.csv"
    )
)
```

## SNF for each of the imputations

```{r}
# mTBI only imputed
# Imputation 1
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m1 <- batch_snf(
        data_list = data_list_m1,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m1, proc_path("solutions_matrix_m1.csv", TRUE))
# Imputation 2
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m2 <- batch_snf(
        data_list = data_list_m2,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m2, proc_path("solutions_matrix_m2.csv", TRUE))
# Imputation 3
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m3 <- batch_snf(
        data_list = data_list_m3,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m3, proc_path("solutions_matrix_m3.csv", TRUE))
# Imputation 4
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m4 <- batch_snf(
        data_list = data_list_m4,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m4, proc_path("solutions_matrix_m4.csv", TRUE))
# Imputation 5
start <- proc.time()
progressr::with_progress({
    solutions_matrix_m5 <- batch_snf(
        data_list = data_list_m5,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_m5, proc_path("solutions_matrix_m5.csv", TRUE))

# mTBI and uninjured pooled imputed
# Imputation 1
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm1 <- batch_snf(
        data_list = data_list_pm1,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm1, proc_path("solutions_matrix_pm1.csv", TRUE))
# Imputation 2
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm2 <- batch_snf(
        data_list = data_list_pm2,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm2, proc_path("solutions_matrix_pm2.csv", TRUE))
# Imputation 3
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm3 <- batch_snf(
        data_list = data_list_pm3,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm3, proc_path("solutions_matrix_pm3.csv", TRUE))
# Imputation 4
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm4 <- batch_snf(
        data_list = data_list_pm4,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm4, proc_path("solutions_matrix_pm4.csv", TRUE))
# Imputation 5
start <- proc.time()
progressr::with_progress({
    solutions_matrix_pm5 <- batch_snf(
        data_list = data_list_pm5,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_pm5, proc_path("solutions_matrix_pm5.csv", TRUE))
```

## Re-importing the generated solutions

```{r}
solutions_matrix_m1 <- read_csv(proc_path("2024_01_15_solutions_matrix_m1.csv"))
solutions_matrix_m2 <- read_csv(proc_path("2024_01_15_solutions_matrix_m2.csv"))
solutions_matrix_m3 <- read_csv(proc_path("2024_01_15_solutions_matrix_m3.csv"))
solutions_matrix_m4 <- read_csv(proc_path("2024_01_15_solutions_matrix_m4.csv"))
solutions_matrix_m5 <- read_csv(proc_path("2024_01_15_solutions_matrix_m5.csv"))
solutions_matrix_pm1 <- read_csv(proc_path("2024_01_15_solutions_matrix_pm1.csv"))
solutions_matrix_pm2 <- read_csv(proc_path("2024_01_15_solutions_matrix_pm2.csv"))
solutions_matrix_pm3 <- read_csv(proc_path("2024_01_15_solutions_matrix_pm3.csv"))
solutions_matrix_pm4 <- read_csv(proc_path("2024_01_15_solutions_matrix_pm4.csv"))
solutions_matrix_pm5 <- read_csv(proc_path("2024_01_15_solutions_matrix_pm5.csv"))

all_mtbi_imputations <- do.call(
    "rbind",
    list(
        solutions_matrix_m1,
        solutions_matrix_m2,
        solutions_matrix_m3,
        solutions_matrix_m4,
        solutions_matrix_m5,
        solutions_matrix_pm1,
        solutions_matrix_pm2,
        solutions_matrix_pm3,
        solutions_matrix_pm4,
        solutions_matrix_pm5
    )
)
```

## Calculating pairwise ARIs

```{r}
aris_m1 <- calc_om_aris(solutions_matrix_m1)
write_csv(data.frame(aris_m1), proc_path("aris_m1.csv", TRUE))
aris_m2 <- calc_om_aris(solutions_matrix_m2)
write_csv(data.frame(aris_m2), proc_path("aris_m2.csv", TRUE))
aris_m3 <- calc_om_aris(solutions_matrix_m3)
write_csv(data.frame(aris_m3), proc_path("aris_m3.csv", TRUE))
aris_m4 <- calc_om_aris(solutions_matrix_m4)
write_csv(data.frame(aris_m4), proc_path("aris_m4.csv", TRUE))
aris_m5 <- calc_om_aris(solutions_matrix_m5)
write_csv(data.frame(aris_m5), proc_path("aris_m5.csv", TRUE))
aris_pm1 <- calc_om_aris(solutions_matrix_pm1)
write_csv(data.frame(aris_pm1), proc_path("aris_pm1.csv", TRUE))
aris_pm2 <- calc_om_aris(solutions_matrix_pm2)
write_csv(data.frame(aris_pm2), proc_path("aris_pm2.csv", TRUE))
aris_pm3 <- calc_om_aris(solutions_matrix_pm3)
write_csv(data.frame(aris_pm3), proc_path("aris_pm3.csv", TRUE))
aris_pm4 <- calc_om_aris(solutions_matrix_pm4)
write_csv(data.frame(aris_pm4), proc_path("aris_pm4.csv", TRUE))
aris_pm5 <- calc_om_aris(solutions_matrix_pm5)
write_csv(data.frame(aris_pm5), proc_path("aris_pm5.csv", TRUE))
aris_all_mtbi_imputations <- calc_om_aris(all_mtbi_imputations)
write_csv(
    data.frame(aris_all_mtbi_imputations),
    proc_path("aris_all_mtbi_imputations.csv", TRUE)
)
```


## Re-importing the ARIs

```{r}
aris_m1 <- read_csv(proc_path("2024_01_15_aris_m1.csv")) |> as.matrix()
aris_m2 <- read_csv(proc_path("2024_01_15_aris_m2.csv")) |> as.matrix()
aris_m3 <- read_csv(proc_path("2024_01_15_aris_m3.csv")) |> as.matrix()
aris_m4 <- read_csv(proc_path("2024_01_15_aris_m4.csv")) |> as.matrix()
aris_m5 <- read_csv(proc_path("2024_01_15_aris_m5.csv")) |> as.matrix()
aris_pm1 <- read_csv(proc_path("2024_01_15_aris_pm1.csv")) |> as.matrix()
aris_pm2 <- read_csv(proc_path("2024_01_15_aris_pm2.csv")) |> as.matrix()
aris_pm3 <- read_csv(proc_path("2024_01_15_aris_pm3.csv")) |> as.matrix()
aris_pm4 <- read_csv(proc_path("2024_01_15_aris_pm4.csv")) |> as.matrix()
aris_pm5 <- read_csv(proc_path("2024_01_15_aris_pm5.csv")) |> as.matrix()

aris_all_mtbi_imputations <- read_csv(
    proc_path("2024_01_15_aris_all_mtbi_imputations.csv")
) |>
    as.matrix()
```

## Plotting the ARIs

### Initial plot across all ARIs to extract order

```{r}
aris_all_mtbi_imputations_heatmap <- similarity_matrix_heatmap(
    aris_all_mtbi_imputations,
    log_graph = FALSE,
    cluster_rows = TRUE,
    cluster_columns = TRUE
)

aris_all_mtbi_imputations_heatmap <- ComplexHeatmap::draw(
    aris_all_mtbi_imputations_heatmap
)
aris_all_mtbi_imputations_order <- ComplexHeatmap::row_order(
    aris_all_mtbi_imputations_heatmap
)

write_csv(
    data.frame(aris_all_mtbi_imputations_order),
    proc_path("aris_all_mtbi_imputations_order.csv", TRUE)
)
```

### Re-importing the order

```{r}
aris_all_mtbi_imputations_order <- unlist(
    read_csv(proc_path("2024_01_15_aris_all_mtbi_imputations_order.csv"))
)

names(aris_all_mtbi_imputations_order) <- NULL
```

## Full imputation meta clustering plot with impairment levels

```{r}
imputation_labels <- data.frame(
    "imputation" = c(
        rep("m1", 200),
        rep("m2", 200),
        rep("m3", 200),
        rep("m4", 200),
        rep("m5", 200),
        rep("pm1", 200),
        rep("pm2", 200),
        rep("pm3", 200),
        rep("pm4", 200),
        rep("pm5", 200)
    ),
    "pooled" = c(
        rep("yes", 1000),
        rep("no", 1000)
    )
)

full_solutions_matrix <- cbind(all_mtbi_imputations, imputation_labels)

full_solutions_matrix$"nclust2" <- full_solutions_matrix$"nclust" - 2

full_extended_solutions_matrix <- extend_solutions(
    full_solutions_matrix,
    oom_list_m1
)

write_csv(
    full_extended_solutions_matrix,
    proc_path("full_mtbi_extended_solutions_matrix.csv", TRUE)
)

full_extended_solutions_matrix <- read_csv(
    proc_path("2024_01_24_full_mtbi_extended_solutions_matrix.csv")
)

pval_select <- function(extended_solutions_matrix,
                        keep_summary = TRUE,
                        negative_log = FALSE,
                        recalculate_summary = TRUE) {
    pval_df <- extended_solutions_matrix |>
        dplyr::select(
            "row_id",
            dplyr::ends_with("_p"),
            dplyr::contains("p_val")
        ) |>
        data.frame() |>
        metasnf::numcol_to_numeric()
    if (!keep_summary) {
        pval_df <- pval_df |>
            dplyr::select(-c("min_p_val", "mean_p_val"))
    }
    if (negative_log) {
        neg_log_pval_df <- -log(pval_df)
        neg_log_pval_df$"row_id" <- pval_df$"row_id"
        pval_df <- neg_log_pval_df
        if (recalculate_summary) {
            mini_df <- pval_df |> dplyr::select(
                dplyr::ends_with("_p")
            )
            pval_df$"mean_neglog_p" <- apply(mini_df, 1, FUN = mean)
            pval_df$"max_neglog_p" <- apply(mini_df, 1, FUN = max)
        }
    }
    return(pval_df)
}

full_oom_pvals <- pval_select(
    full_extended_solutions_matrix,
    negative_log = TRUE
)

full_extended_solutions_matrix$"mean_neglog_p" <- full_oom_pvals$"mean_neglog_p"

divergent_colours <- function(column)  {
    values <- unique(column)
    colours <- RColorBrewer::brewer.pal(n = length(values), name = "Set3")
    names(colours) <- values
    return(colours)
}

hm_colours <- function(data, max_red = TRUE) {
    if (max_red) {
        colours <- circlize::colorRamp2(
            c(min(data), max(data)),
            c("black", "red")
        )
    } else {
        colours <- circlize::colorRamp2(
            c(min(data), max(data)),
            c("red", "black")
        )
    }
    return(colours)
}

aris_all_mtbi_imputations_annotated_heatmap <- similarity_matrix_heatmap(
    aris_all_mtbi_imputations,
    order = aris_all_mtbi_imputations_order,
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    log_graph = FALSE,
    data = data.frame(full_extended_solutions_matrix),
    top_hm = list(
        "Scheme" = "snf_scheme",
        "Impairment Separation" = "mean_neglog_p"
    ),
    left_hm = list(
        "Pooled" = "pooled",
        "Imputation" = "imputation"
    ),
    top_bar = list(
        "Number of Clusters - 2" = "nclust2"
    ),
    scale_diag = "none",
    heatmap_height = grid::unit(19, "cm"),
    heatmap_width = grid::unit(19, "cm"),
    annotation_colours = list(
        "Pooled" = c(
            "yes" = "orange",
            "no" = "purple"
        ),
        "Imputation" = divergent_colours(full_extended_solutions_matrix$"imputation"),
        "Scheme" = c(
            "1" = "#7FC97F",
            "2" = "#BEAED4",
            "3" = "#FDC086"
        ),
        "Impairment Separation" = hm_colours(full_extended_solutions_matrix$"mean_neglog_p")
    ),
    col = circlize::colorRamp2(
        c(min(aris_all_mtbi_imputations), max(aris_all_mtbi_imputations)),
        c("navy", "red")
    )
)

aris_all_mtbi_imputations_annotated_heatmap

# PNG export
grDevices::png(
    fig_path("aris_all_mtbi_imputations_annotated_heatmap.png", TRUE),
    width = 2000,
    height = 2000,
)
aris_all_mtbi_imputations_annotated_heatmap
grDevices::dev.off()

```

## Identifying meta clusters

```{r}
split_at <- function(vector, nrow) {
    split_vec <- rep("A", nrow)
    if (vector[length(vector)] != nrow) {
        vector <- c(vector, nrow)
    }
    for (i in 1:(length(vector) - 1)) {
        start <- vector[i]
        end <- vector[i + 1]
        split_vec[start:end] <- LETTERS[i + 1]
    }
    return(split_vec)
}

aris_all_mtbi_imputations_chopped_heatmap <- similarity_matrix_heatmap(
    aris_all_mtbi_imputations,
    order = aris_all_mtbi_imputations_order,
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    log_graph = FALSE,
    data = full_extended_solutions_matrix,
    top_hm = list(
        "Scheme" = "snf_scheme",
        "Impairment Separation" = "mean_neglog_p"
    ),
    left_hm = list(
        "Pooled" = "pooled",
        "Imputation" = "imputation"
    ),
    top_bar = list(
        "Number of Clusters - 2" = "nclust2"
    ),
    scale_diag = "none",
    heatmap_height = grid::unit(19, "cm"),
    heatmap_width = grid::unit(19, "cm"),
    annotation_colours = list(
        "Pooled" = c(
            "yes" = "orange",
            "no" = "purple"
        ),
        "Imputation" = divergent_colours(full_extended_solutions_matrix$"imputation"),
        "Scheme" = c(
            "1" = "#7FC97F",
            "2" = "#BEAED4",
            "3" = "#FDC086"
        ),
        "Impairment Separation" = hm_colours(full_extended_solutions_matrix$"mean_neglog_p")
    ),
    col = circlize::colorRamp2(
        c(min(aris_all_mtbi_imputations), max(aris_all_mtbi_imputations)),
        c("navy", "red")
    ),
    row_split = split_at(
        vector = c(
            500,
            806,
            956,
            1227,
            1441
        ),
        nrow = 2000
    ),
    column_split = split_at(
        vector = c(
            500,
            806,
            956,
            1227,
            1441
        ),
        nrow = 2000
    )
)

aris_all_mtbi_imputations_chopped_heatmap

# PNG export
grDevices::png(
    fig_path("aris_all_mtbi_imputations_chopped_heatmap.png", TRUE),
    width = 3000,
    height = 3000,
    res = 300
)
aris_all_mtbi_imputations_chopped_heatmap
grDevices::dev.off()

# A deeper zoom on the smaller heatmaps (manual inspection, trial and error)
aamio <- aris_all_mtbi_imputations_order

mc_f <- aris_all_mtbi_imputations[aamio, aamio]
mc_f <- mc_f[1441:2000, 1441:2000]

aris_all_mtbi_mc_f_chopped_heatmap <- similarity_matrix_heatmap(
    mc_f,
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    log_graph = FALSE,
    scale_diag = "none",
    heatmap_height = grid::unit(19, "cm"),
    heatmap_width = grid::unit(19, "cm"),
    col = circlize::colorRamp2(
        c(min(aris_all_mtbi_imputations), max(aris_all_mtbi_imputations)),
        c("navy", "red")
    ),
    row_split = paste0(
        "F-",
        split_at(
            vector = c(
                78,
                253,
                290,
                336,
                400,
                438,
                462,
                496,
                513
            ),
            nrow = nrow(mc_f)
        )
    ),
    column_split = paste0(
        "F-",
        split_at(
            vector = c(
                78,
                253,
                290,
                336,
                400,
                438,
                462,
                496,
                513
            ),
            nrow = nrow(mc_f)
        )
    )
)
aris_all_mtbi_mc_f_chopped_heatmap

# PNG export
grDevices::png(
    fig_path("aris_all_mtbi_mc_f_chopped_heatmap.png", TRUE),
    width = 2500,
    height = 2500,
    res = 300
)
aris_all_mtbi_mc_f_chopped_heatmap
grDevices::dev.off()
```

## One-MC-at-a-time

```{r}
# Indices as they appear in the plots
mc_reordered_indices <- list(
    "A" = c(1, 500),
    "B" = c(501, 806),
    "C" = c(807, 956),
    "D" = c(957, 1227),
    "E" = c(1228, 1441),
    "F-A" = c(1442, 1442 + 78),
    "F-B" = c(1442 + 79, 1442 + 253),
    "F-C" = c(1442 + 254, 1442 + 290),
    "F-D" = c(1442 + 291, 1442 + 336),
    "F-E" = c(1442 + 337, 1442 + 400),
    "F-F" = c(1442 + 401, 1442 + 438),
    "F-G" = c(1442 + 439, 1442 + 462),
    "F-H" = c(1442 + 463, 1442 + 496),
    "F-I" = c(1442 + 497, 1442 + 513),
    "F-J" = c(1442 + 514, 2000)
)

mc_reordered_labels <- split_at(
    c(
        500,
        806,
        956,
        1227,
        1441,
        1442 + 78,
        1442 + 253,
        1442 + 290,
        1442 + 336,
        1442 + 400,
        1442 + 438,
        1442 + 462,
        1442 + 496,
        1442 + 513
    ),
    2000
)
mc_reordered_labels <- gsub("F", "F-A", mc_reordered_labels)
mc_reordered_labels <- gsub("G", "F-B", mc_reordered_labels)
mc_reordered_labels <- gsub("H", "F-C", mc_reordered_labels)
mc_reordered_labels <- gsub("I", "F-D", mc_reordered_labels)
mc_reordered_labels <- gsub("J", "F-E", mc_reordered_labels)
mc_reordered_labels <- gsub("K", "F-F", mc_reordered_labels)
mc_reordered_labels <- gsub("L", "F-G", mc_reordered_labels)
mc_reordered_labels <- gsub("M", "F-H", mc_reordered_labels)
mc_reordered_labels <- gsub("N", "F-I", mc_reordered_labels)
mc_reordered_labels <- gsub("O", "F-J", mc_reordered_labels)

names(aris_all_mtbi_imputations_order) <- mc_reordered_labels

# Here I am - revised edition

sorted_mc_labels <- sort(aris_all_mtbi_imputations_order)

full_input_characterization_m1 <- extend_solutions(
    full_solutions_matrix,
    data_list_m1
)

write_csv(
    full_input_characterization_m1,
    proc_path("full_input_characterization_m1.csv", TRUE)
)

full_input_characterization_m1 <- read_csv(
    proc_path(
        "2024_01_18_full_input_characterization_m1.csv"
    )
)

target_pvals <- full_input_characterization_m1 |>
    p_val_select()
target_pvals$"mc_label" <- names(sorted_mc_labels)

manhattan_plot <- function(data,
                           key_mode = FALSE,
                           threshold = NULL,
                           bonferroni_line = FALSE,
                           data_list,
                           mc_labels = NULL) {
    row_id <- ""
    variable <- ""
    pval <- ""
    var_cols <- colnames(data)[endsWith(colnames(data), "_p")]
    data[, var_cols] <- data[, var_cols] |>
        apply(
            MARGIN = 2,
            FUN = function(x) {
                -log10(x)
                raw_p <- -log10(x)
                new_x <- dplyr::case_when(
                    raw_p > 5 ~ 5,
                    raw_p > 4 ~ 4,
                    raw_p > 3 ~ 3,
                    raw_p > 2 ~ 2,
                    raw_p > 1 ~ 1,
                    raw_p > 0 ~ 0,
                )
                new_x
            }
        )
    data$"row_id" <- factor(data$"row_id")
    data$"mc_label" <- factor(data$"mc_label")
    data <- data |>
        tidyr::pivot_longer(
            !(c(row_id, mc_label)),
            names_to = "variable",
            values_to = "pval"
        ) |>
        data.frame()
    summary_data <- data |>
        dplyr::group_by(
            mc_label,
            variable
        ) |>
        dplyr::summarize(
            mean_p = mean(pval),
            sd_p = sd(pval),
            se_p = sd_p / sqrt(dplyr::n()),
            .groups = "drop"
        )
    summary_data$"variable" <- sub("_p$", "", summary_data$"variable")
    ###########################################################################
    # Merge the summmary plot with domain information from the data_list
    ###########################################################################
    dl_metadata <- data_list_metadata(data_list) |> dplyr::select(-"type")
    summary_data <- merge(
        summary_data,
        dl_metadata,
        by.x = "variable",
        by.y = "name",
        all.x = TRUE
    )
    summary_data <- summary_data |> dplyr::arrange(domain)
    summary_data$"variable" <- factor(
        summary_data$"variable",
        levels = unique(summary_data$"variable")
    )
    if (!is.null(mc_labels)) {
        summary_data <- summary_data[summary_data$"mc_label" %in% mc_labels, ]
        summary_data$"mc_label" <- factor(
            summary_data$"mc_label",
            levels = mc_labels
        )
    }
    plot <- summary_data |>
        ggplot2::ggplot(ggplot2::aes(x = domain, y = mean_p)) +
        ggplot2::geom_jitter(
            mapping = ggplot2::aes(
                group = domain,
                x = variable,
                y = mean_p,
                colour = domain
            ),
            height = 0,
            width = 0,
            size = 5
        ) +
        ggplot2::labs(
            x = "Variable",
            y = expression("-log"[10]*"(p)"),
            colour = "Domain"
        ) +
        ggplot2::ylim(-log10(0.05), 5) +
        ggplot2::theme_bw() +
        ggplot2::labs(y = "Discretized -log10(p)") +
        ggplot2::theme(
            axis.text.x = ggplot2::element_text(
                angle = 90,
                vjust = 0.5,
                hjust = 1
            ),
            plot.title = ggplot2::element_text(hjust = 0.5)
        )
    plot <- plot + ggplot2::facet_grid(mc_label ~ .)
    if (!is.null(threshold)) {
        plot <- plot + ggplot2::geom_hline(
            yintercept = -log10(threshold),
            linetype = "dashed",
            colour = "red"
        )
        if (bonferroni_line) {
            plot <- plot + ggplot2::geom_hline(
                yintercept = -log10(threshold / nrow(data)),
                linetype = "dashed",
                colour = "black"
            )
        }
    } else if (bonferroni_line) {
        stop(
            "Please specify threshold p-value which will be used",
            " for calculting the Bonferroni-corrected line."
        )
    }
    return(plot)
}

library(ggplot2)
# Here I am

all_mtbi_imputations_main_mc_associations <- manhattan_plot(
    target_pvals,
    threshold = 0.05,
    bonferroni_line = FALSE,
    data_list = data_list_m1,
    mc_labels = c("A", "B", "C", "D", "E")
)

ggsave(
    plot = all_mtbi_imputations_main_mc_associations,
    fig_path("all_mtbi_imputations_main_mc_associations.png", TRUE),
    width = 8,
    height = 10
)

all_mtbi_imputations_f_mc_associations <- manhattan_plot(
    target_pvals,
    threshold = 0.05,
    bonferroni_line = FALSE,
    data_list = data_list_m1,
    mc_labels = c("F-A", "F-C", "F-E", "F-F", "F-J")
)

all_mtbi_imputations_f_mc_associations

ggsave(
    plot = all_mtbi_imputations_f_mc_associations,
    fig_path("all_mtbi_imputations_f_mc_associations.png", TRUE),
    width = 8,
    height = 10
)

all_mtbi_imputations_all_mc_associations <- manhattan_plot(
    target_pvals,
    threshold = 0.05,
    bonferroni_line = FALSE,
    data_list = data_list_m1
)
ggsave(
    plot = all_mtbi_imputations_all_mc_associations,
    fig_path("all_mtbi_imputations_all_mc_associations.png", TRUE),
    width = 8,
    height = 20
)



# Bulk export each MC individually
for (mc in names(mc_reordered_indices)) {
    mc_plot <- manhattan_plot(
        target_pvals,
        threshold = 0.05,
        bonferroni_line = FALSE,
        data_list = data_list_m1,
        mc_label = mc
    )
    mc_path <- paste0(
        "all_mtbi_imputations_mc_",
        gsub("-", "_", tolower(mc)),
        "_associations.png"
    )
    ggsave(
        plot = mc_plot,
        fig_path(mc_path, TRUE),
        width = 10,
        height = 3
    )
}
```
