# Matching

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)
library(MatchIt)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subjects <- read_csv(sub_path("2024_08_17_mtbi_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2024_08_17_uninjured_subjects.csv"))
```

## Importing data

```{r}
all_dls <- list.load(input_path("2024_08_17_all_dls.rds"))
```

```{r}
mtbi_full_data_list_1 <- list.load(input_path("2024_08_22_mtbi_full_data_list_1.rds"))
mtbi_full_oom_list_1 <- list.load(input_path("2024_08_22_mtbi_full_oom_list_1.rds"))

uninj_dl_imp_1 <- all_dls$"uninj_data_lists"$"imp_1"
uninj_dl_imp_2 <- all_dls$"uninj_data_lists"$"imp_2"
uninj_dl_imp_3 <- all_dls$"uninj_data_lists"$"imp_3"
uninj_dl_imp_4 <- all_dls$"uninj_data_lists"$"imp_4"
uninj_dl_imp_5 <- all_dls$"uninj_data_lists"$"imp_5"

uninj_ol_imp_1 <- all_dls$"uninj_oom_lists"$"imp_1"
uninj_ol_imp_2 <- all_dls$"uninj_oom_lists"$"imp_2"
uninj_ol_imp_3 <- all_dls$"uninj_oom_lists"$"imp_3"
uninj_ol_imp_4 <- all_dls$"uninj_oom_lists"$"imp_4"
uninj_ol_imp_5 <- all_dls$"uninj_oom_lists"$"imp_5"
```

## Matching

Finding matched uninjured controls for each mtbi subject based on a variety of variables.
Matching will be done based on the first imputed dataset of the baseline data.

```{r}
names(mtbi_full_data_list_1)

# 5 different combinations for the dl matching
# Could have included pooled imputations here as well...

mtbi_matching_df <- c(mtbi_full_data_list_1, mtbi_full_oom_list_1) |> collapse_dl()
uninj_matching_df_imp_1 <- c(uninj_dl_imp_1, uninj_ol_imp_1) |> collapse_dl()
uninj_matching_df_imp_2 <- c(uninj_dl_imp_2, uninj_ol_imp_2) |> collapse_dl()
uninj_matching_df_imp_3 <- c(uninj_dl_imp_3, uninj_ol_imp_3) |> collapse_dl()
uninj_matching_df_imp_4 <- c(uninj_dl_imp_4, uninj_ol_imp_4) |> collapse_dl()
uninj_matching_df_imp_5 <- c(uninj_dl_imp_5, uninj_ol_imp_5) |> collapse_dl()

mtbi_matching_df$"mtbi" <- 1
uninj_matching_df_imp_1$"mtbi" <- 0
uninj_matching_df_imp_2$"mtbi" <- 0
uninj_matching_df_imp_3$"mtbi" <- 0
uninj_matching_df_imp_4$"mtbi" <- 0
uninj_matching_df_imp_5$"mtbi" <- 0

mtbi_matching_df <- dplyr::select(
    mtbi_matching_df,
    colnames(uninj_matching_df_imp_1)
)

mtbi_matching_df |> colnames()

matching_df_imp_1 <- rbind(mtbi_matching_df, uninj_matching_df_imp_1)
matching_df_imp_2 <- rbind(mtbi_matching_df, uninj_matching_df_imp_2)
matching_df_imp_3 <- rbind(mtbi_matching_df, uninj_matching_df_imp_3)
matching_df_imp_4 <- rbind(mtbi_matching_df, uninj_matching_df_imp_4)
matching_df_imp_5 <- rbind(mtbi_matching_df, uninj_matching_df_imp_5)

###############################################################################
# Total parent psych
###############################################################################
matching_df_imp_1$"total_parent_psych" <- matching_df_imp_1 |>
    dplyr::select(dplyr::starts_with("parent")) |>
    rowSums()

matching_df_imp_2$"total_parent_psych" <- matching_df_imp_2 |>
    dplyr::select(dplyr::starts_with("parent")) |>
    rowSums()

matching_df_imp_3$"total_parent_psych" <- matching_df_imp_3 |>
    dplyr::select(dplyr::starts_with("parent")) |>
    rowSums()

matching_df_imp_4$"total_parent_psych" <- matching_df_imp_4 |>
    dplyr::select(dplyr::starts_with("parent")) |>
    rowSums()

matching_df_imp_5$"total_parent_psych" <- matching_df_imp_5 |>
    dplyr::select(dplyr::starts_with("parent")) |>
    rowSums()

###############################################################################
# Total CBCL
###############################################################################
matching_df_imp_1$"total_impairments" <- matching_df_imp_1 |>
    dplyr::select(dplyr::starts_with("cbcl"), dplyr::starts_with("sds")) |>
    rowSums()
matching_df_imp_2$"total_impairments" <- matching_df_imp_2 |>
    dplyr::select(dplyr::starts_with("cbcl"), dplyr::starts_with("sds")) |>
    rowSums()

matching_df_imp_3$"total_impairments" <- matching_df_imp_3 |>
    dplyr::select(dplyr::starts_with("cbcl"), dplyr::starts_with("sds")) |>
    rowSums()

matching_df_imp_4$"total_impairments" <- matching_df_imp_4 |>
    dplyr::select(dplyr::starts_with("cbcl"), dplyr::starts_with("sds")) |>
    rowSums()

matching_df_imp_5$"total_impairments" <- matching_df_imp_5 |>
    dplyr::select(dplyr::starts_with("cbcl"), dplyr::starts_with("sds")) |>
    rowSums()
```

We'll try a few different matching schemes:

```{r}
colnames(matching_df_imp_5)

# Matching by income, race, parent psych
matching_results_1_imp_1 <- matchit(
    formula(mtbi ~ household_income + race + total_parent_psych),
    data = matching_df_imp_1,
    method = "nearest"
)
matching_summary_1_imp_1 <- capture.output(print(summary(matching_results_1_imp_1)))
matching_summary_1_imp_1

# Matching by demographic variables
matching_results_2_imp_1 <- matchit(
    formula(mtbi ~ household_income + race + sex + pubertal_status_p + pubertal_status_y),
    data = matching_df_imp_1,
    method = "nearest"
)
matching_summary_2_imp_1 <- capture.output(print(summary(matching_results_2_imp_1)))
matching_summary_2_imp_1

# Matching by parent psych alone
matching_results_3_imp_1 <- matchit(
    formula(mtbi ~ total_parent_psych),
    data = matching_df_imp_1,
    method = "nearest"
)
matching_summary_3_imp_1 <- capture.output(print(summary(matching_results_3_imp_1)))
matching_summary_3_imp_1

# Matching by CBCL alone
matching_results_4_imp_1 <- matchit(
    formula(mtbi ~ total_impairments),
    data = matching_df_imp_1,
    method = "nearest"
)
matching_summary_4_imp_1 <- capture.output(print(summary(matching_results_4_imp_1)))
matching_summary_4_imp_1

saveRDS(matching_summary_1_imp_1, proc_path("matching_summary_1_imp_1.rds", TRUE))
saveRDS(matching_summary_2_imp_1, proc_path("matching_summary_2_imp_1.rds", TRUE))
saveRDS(matching_summary_3_imp_1, proc_path("matching_summary_3_imp_1.rds", TRUE))
saveRDS(matching_summary_4_imp_1, proc_path("matching_summary_4_imp_1.rds", TRUE))
```

```{r}
# CHECKPOINT
matching_summary_1_imp_1 <- readRDS(proc_path("2024_08_23_matching_summary_1_imp_1.rds"))
matching_summary_2_imp_1 <- readRDS(proc_path("2024_08_23_matching_summary_2_imp_1.rds"))
matching_summary_3_imp_1 <- readRDS(proc_path("2024_08_23_matching_summary_3_imp_1.rds"))
matching_summary_4_imp_1 <- readRDS(proc_path("2024_08_23_matching_summary_4_imp_1.rds"))
```

```{r}
grDevices::png(
    filename = fig_path("matching_results_1_imp_1.png", TRUE),
    width = 1000,
    height = 500,
    res = 100
)
plot(
    matching_results_1_imp_1,
    type = "density",
    interactive = FALSE
)
grDevices::dev.off()

grDevices::png(
    filename = fig_path("matching_results_2_imp_1.png", TRUE),
    width = 1000,
    height = 500,
    res = 100
)
plot(
    matching_results_2_imp_1,
    type = "density",
    interactive = FALSE
)
grDevices::dev.off()

grDevices::png(
    filename = fig_path("matching_results_3_imp_1.png", TRUE),
    width = 1000,
    height = 500,
    res = 100
)
plot(
    matching_results_3_imp_1,
    type = "density",
    interactive = FALSE
)
grDevices::dev.off()

grDevices::png(
    filename = fig_path("matching_results_4_imp_1.png", TRUE),
    width = 1000,
    height = 500,
    res = 100
)
plot(
    matching_results_4_imp_1,
    type = "density",
    interactive = FALSE
)
grDevices::dev.off()
```

```{r}
matched_data_1_imp_1 <- match.data(matching_results_1_imp_1)
matched_data_2_imp_1 <- match.data(matching_results_2_imp_1)
matched_data_3_imp_1 <- match.data(matching_results_3_imp_1)
matched_data_4_imp_1 <- match.data(matching_results_4_imp_1)
```

```{r}
# Extract the control group from the matched data
matched_uninj_1_imp_1 <- dplyr::filter(matched_data_1_imp_1, mtbi == 0)$"subjectkey"
matched_uninj_2_imp_1 <- dplyr::filter(matched_data_2_imp_1, mtbi == 0)$"subjectkey"
matched_uninj_3_imp_1 <- dplyr::filter(matched_data_3_imp_1, mtbi == 0)$"subjectkey"
matched_uninj_4_imp_1 <- dplyr::filter(matched_data_4_imp_1, mtbi == 0)$"subjectkey"

write_csv(data.frame(subjectkey = matched_uninj_1_imp_1), sub_path("matched_uninj_1_imp_1.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_2_imp_1), sub_path("matched_uninj_2_imp_1.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_3_imp_1), sub_path("matched_uninj_3_imp_1.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_4_imp_1), sub_path("matched_uninj_4_imp_1.csv", TRUE))
```

```{r}
matched_uninj_1_imp_1 <- read_subjects(sub_path("2024_08_23_matched_uninj_1_imp_1.csv"))
matched_uninj_2_imp_1 <- read_subjects(sub_path("2024_08_23_matched_uninj_2_imp_1.csv"))
matched_uninj_3_imp_1 <- read_subjects(sub_path("2024_08_23_matched_uninj_3_imp_1.csv"))
matched_uninj_4_imp_1 <- read_subjects(sub_path("2024_08_23_matched_uninj_4_imp_1.csv"))
```

For the sake of simplicity, we did our matching off of just 1 of the imputed uninjured datasets.
So matched uninj 1, matched uninj 2, 3, and 4 are all based on solo imputed 1 data.

## Loading data and out of model lists

```{r}
all_dls |> names()

uninj_dls <- all_dls[
    c(
        "uninj_data_lists",
        "uninj_pooled_data_lists",
        "uninj_oom_lists",
        "uninj_pooled_oom_lists"
    )
]

subject_filter_dl <- function(data_list, subject_vector) {
    data_list <- data_list |>
        lapply(
            function(x) {
                keep_subs <- x$"data"$"subjectkey" %in% subject_vector
                x$"data" <- x$"data"[keep_subs, ]
                return(x)
            }
        )
    return(data_list)
}

dl_matcher <- function(list_of_dls, matching_subs) {
    matched_list_of_dls <- lapply(
        list_of_dls,
        function(x) {
            lapply(
                x,
                function(y) {
                    subject_filter_dl(y, matching_subs)
                }
            )
        }
    )
    return(matched_list_of_dls)
}

matched_uninj_dls_1 <- dl_matcher(uninj_dls, matched_uninj_1_imp_1)
matched_uninj_dls_2 <- dl_matcher(uninj_dls, matched_uninj_2_imp_1)
matched_uninj_dls_3 <- dl_matcher(uninj_dls, matched_uninj_3_imp_1)
matched_uninj_dls_4 <- dl_matcher(uninj_dls, matched_uninj_4_imp_1)

list.save(matched_uninj_dls_1, input_path("matched_uninj_dls_1.rds", TRUE))
list.save(matched_uninj_dls_2, input_path("matched_uninj_dls_2.rds", TRUE))
list.save(matched_uninj_dls_3, input_path("matched_uninj_dls_3.rds", TRUE))
list.save(matched_uninj_dls_4, input_path("matched_uninj_dls_4.rds", TRUE))
```

```{r}
# CHECKPOINT
matched_uninj_dls_1 <- list.load(input_path("2024_08_23_matched_uninj_dls_1.rds"))
matched_uninj_dls_2 <- list.load(input_path("2024_08_23_matched_uninj_dls_2.rds"))
matched_uninj_dls_3 <- list.load(input_path("2024_08_23_matched_uninj_dls_3.rds"))
matched_uninj_dls_4 <- list.load(input_path("2024_08_23_matched_uninj_dls_4.rds"))
```

## metaSNF

```{r}
my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

names(matched_uninj_dls_1[[1]])

matched_settings_matrix <- generate_settings_matrix(
    matched_uninj_dls_1$"uninj_data_lists"$"imp_1",
    nrow = 200,
    seed = 42,
    distance_metrics_list = my_distance_metrics
)

write_csv(matched_settings_matrix, proc_path("matched_settings_matrix.csv", TRUE))
```

```{r}
# CHECKPOINT
matched_settings_matrix <- read_csv(proc_path("2024_08_23_matched_settings_matrix.csv"))
```

The goal now is to actually run the SNF.

I have 4 different "sets" of data list / oom list combinations.

Consider just the first set.

This covers 10 different imputed datasets (right?) the 5 pooled and 5 solo uninjured.
So, I'll create 2000 SNF solutions using all of those 10 sets.

Then, repeat that process 4x.

```{r}
bulk_batch_snf <- function(dls, sm, dml) {
    solutions_matrices <- lapply(
        dls,
        function(dl) {
            solutions_matrix <- batch_snf(
                data_list = dl,
                settings_matrix = sm,
                distance_metrics_list = dml,
                processes = "max"
            ) 
        }
    )
    names(solutions_matrices) <- c("s1", "s2", "s3", "s4", "s5", "p1", "p2", "p3", "p4", "p5")
    return(solutions_matrices)
}
```

```{r}
matched_uninj_solutions_matrix_1 <- bulk_batch_snf(
    dls = c(matched_uninj_dls_1$"uninj_data_lists", matched_uninj_dls_1$"uninj_data_lists"),
    sm = matched_settings_matrix,
    dml = my_distance_metrics 
)
list.save(matched_uninj_solutions_matrix_1, input_path("matched_uninj_solutions_matrix_1.rds", TRUE))

matched_uninj_solutions_matrix_2 <- bulk_batch_snf(
    dls = c(matched_uninj_dls_2$"uninj_data_lists", matched_uninj_dls_2$"uninj_data_lists"),
    sm = matched_settings_matrix,
    dml = my_distance_metrics 
)
list.save(matched_uninj_solutions_matrix_2, input_path("matched_uninj_solutions_matrix_2.rds", TRUE))

matched_uninj_solutions_matrix_3 <- bulk_batch_snf(
    dls = c(matched_uninj_dls_3$"uninj_data_lists", matched_uninj_dls_3$"uninj_data_lists"),
    sm = matched_settings_matrix,
    dml = my_distance_metrics 
)
list.save(matched_uninj_solutions_matrix_3, input_path("matched_uninj_solutions_matrix_3.rds", TRUE))

matched_uninj_solutions_matrix_4 <- bulk_batch_snf(
    dls = c(matched_uninj_dls_4$"uninj_data_lists", matched_uninj_dls_4$"uninj_data_lists"),
    sm = matched_settings_matrix,
    dml = my_distance_metrics 
)
list.save(matched_uninj_solutions_matrix_4, input_path("matched_uninj_solutions_matrix_4.rds", TRUE))
```

Even though the matching was done through 1 imputation of the data, the actual SNF was done across all the imputed datasets.

```{r}
matched_uninj_solutions_matrix_1 <- list.load(input_path("2024_08_25_matched_uninj_solutions_matrix_1.rds"))
matched_uninj_solutions_matrix_2 <- list.load(input_path("2024_08_25_matched_uninj_solutions_matrix_2.rds"))
matched_uninj_solutions_matrix_3 <- list.load(input_path("2024_08_26_matched_uninj_solutions_matrix_3.rds"))
matched_uninj_solutions_matrix_4 <- list.load(input_path("2024_08_26_matched_uninj_solutions_matrix_4.rds"))
```

```{r}
matched_uninj_sm_1 <- do.call("rbind", matched_uninj_solutions_matrix_1)
matched_uninj_sm_2 <- do.call("rbind", matched_uninj_solutions_matrix_2)
matched_uninj_sm_3 <- do.call("rbind", matched_uninj_solutions_matrix_3)
matched_uninj_sm_4 <- do.call("rbind", matched_uninj_solutions_matrix_4)

write_csv(data.frame(matched_uninj_sm_1), proc_path("matched_uninj_sm_1.csv", TRUE))
write_csv(data.frame(matched_uninj_sm_2), proc_path("matched_uninj_sm_2.csv", TRUE))
write_csv(data.frame(matched_uninj_sm_3), proc_path("matched_uninj_sm_3.csv", TRUE))
write_csv(data.frame(matched_uninj_sm_4), proc_path("matched_uninj_sm_4.csv", TRUE))
```

```{r}
# CHECKPOINT
matched_uninj_sm_1 <- read_csv(proc_path("2024_08_26_matched_uninj_sm_1.csv"))
matched_uninj_sm_2 <- read_csv(proc_path("2024_08_26_matched_uninj_sm_2.csv"))
matched_uninj_sm_3 <- read_csv(proc_path("2024_08_26_matched_uninj_sm_3.csv"))
matched_uninj_sm_4 <- read_csv(proc_path("2024_08_26_matched_uninj_sm_4.csv"))
```

```{r}
matched_uninj_ari_1 <- calc_aris(matched_uninj_sm_1, processes = "max")
write_csv(data.frame(matched_uninj_ari_1), proc_path("matched_uninj_ari_1.csv", TRUE))
matched_uninj_ari_2 <- calc_aris(matched_uninj_sm_2, processes = "max")
write_csv(data.frame(matched_uninj_ari_2), proc_path("matched_uninj_ari_2.csv", TRUE))
matched_uninj_ari_3 <- calc_aris(matched_uninj_sm_3, processes = "max")
write_csv(data.frame(matched_uninj_ari_3), proc_path("matched_uninj_ari_3.csv", TRUE))
matched_uninj_ari_4 <- calc_aris(matched_uninj_sm_4, processes = "max")
write_csv(data.frame(matched_uninj_ari_4), proc_path("matched_uninj_ari_4.csv", TRUE))
```

```{r}
matched_uninj_ari_order_1 <- get_matrix_order(matched_uninj_ari_1)
matched_uninj_ari_order_2 <- get_matrix_order(matched_uninj_ari_2)
matched_uninj_ari_order_3 <- get_matrix_order(matched_uninj_ari_3)
matched_uninj_ari_order_4 <- get_matrix_order(matched_uninj_ari_4)

write_csv(data.frame(matched_uninj_ari_order_1), proc_path("matched_uninj_ari_order_1.csv", TRUE))
write_csv(data.frame(matched_uninj_ari_order_2), proc_path("matched_uninj_ari_order_2.csv", TRUE))
write_csv(data.frame(matched_uninj_ari_order_3), proc_path("matched_uninj_ari_order_3.csv", TRUE))
write_csv(data.frame(matched_uninj_ari_order_4), proc_path("matched_uninj_ari_order_4.csv", TRUE))
```

```{r}
# CHECKPOINT
matched_uninj_ari_1 <- read_csv(proc_path("2024_08_26_matched_uninj_ari_1.csv"))
matched_uninj_ari_2 <- read_csv(proc_path("2024_08_26_matched_uninj_ari_2.csv"))
matched_uninj_ari_3 <- read_csv(proc_path("2024_08_26_matched_uninj_ari_3.csv"))
matched_uninj_ari_4 <- read_csv(proc_path("2024_08_26_matched_uninj_ari_4.csv"))

matched_uninj_ari_order_1 <- read_csv(proc_path("2024_08_26_matched_uninj_ari_order_1.csv"))
matched_uninj_ari_order_2 <- read_csv(proc_path("2024_08_26_matched_uninj_ari_order_2.csv"))
matched_uninj_ari_order_3 <- read_csv(proc_path("2024_08_26_matched_uninj_ari_order_3.csv"))
matched_uninj_ari_order_4 <- read_csv(proc_path("2024_08_26_matched_uninj_ari_order_4.csv"))
```

```{r}

matched_uninj_dl_1_s1 <- matched_uninj_dls_1$"uninj_data_lists"$"imp_1"
matched_uninj_dl_1_s2 <- matched_uninj_dls_1$"uninj_data_lists"$"imp_2"
matched_uninj_dl_1_s3 <- matched_uninj_dls_1$"uninj_data_lists"$"imp_3"
matched_uninj_dl_1_s4 <- matched_uninj_dls_1$"uninj_data_lists"$"imp_4"
matched_uninj_dl_1_s5 <- matched_uninj_dls_1$"uninj_data_lists"$"imp_5"

identical(matched_uninj_dl_1_s1_subs, matched_uninj_dl_1_s2_subs)
identical(matched_uninj_dl_1_s1_subs, matched_uninj_dl_1_s3_subs)
identical(matched_uninj_dl_1_s1_subs, matched_uninj_dl_1_s4_subs)
identical(matched_uninj_dl_1_s1_subs, matched_uninj_dl_1_s5_subs)
identical(matched_uninj_dl_1_s2_subs, matched_uninj_dl_1_s3_subs)
identical(matched_uninj_dl_1_s2_subs, matched_uninj_dl_1_s4_subs)
identical(matched_uninj_dl_1_s2_subs, matched_uninj_dl_1_s5_subs)

length(matched_uninj_solutions_matrix_1) # 10, one for each imputation

collapse_dl(matched_uninj_dls_1[[1]][[1]])$"subjectkey"[1:10]

z <- collapse_dl(matched_uninj_dls_1[[2]][[2]])$"subjectkey"
z2 <- collapse_dl(matched_uninj_dls_1[[1]][[2]])$"subjectkey"

names(matched_uninj_dls_2)

matched_uninj_dls_3
matched_uninj_dls_4

uninj_dl_s1 <- all_dls$"uninj_data_lists"$"imp_1"
uninj_dl_s2 <- all_dls$"uninj_data_lists"$"imp_2"
uninj_dl_s3 <- all_dls$"uninj_data_lists"$"imp_3"
uninj_dl_s4 <- all_dls$"uninj_data_lists"$"imp_4"
uninj_dl_s5 <- all_dls$"uninj_data_lists"$"imp_5"
uninj_dl_p1 <- all_dls$"uninj_pooled_data_lists"$"imp_1"
uninj_dl_p2 <- all_dls$"uninj_pooled_data_lists"$"imp_2"
uninj_dl_p3 <- all_dls$"uninj_pooled_data_lists"$"imp_3"
uninj_dl_p4 <- all_dls$"uninj_pooled_data_lists"$"imp_4"
uninj_dl_p5 <- all_dls$"uninj_pooled_data_lists"$"imp_5"

uninj_ol_s1 <- all_dls$"uninj_oom_lists"$"imp_1"
uninj_ol_s2 <- all_dls$"uninj_oom_lists"$"imp_2"
uninj_ol_s3 <- all_dls$"uninj_oom_lists"$"imp_3"
uninj_ol_s4 <- all_dls$"uninj_oom_lists"$"imp_4"
uninj_ol_s5 <- all_dls$"uninj_oom_lists"$"imp_5"
uninj_ol_p1 <- all_dls$"uninj_pooled_oom_lists"$"imp_1"
uninj_ol_p2 <- all_dls$"uninj_pooled_oom_lists"$"imp_2"
uninj_ol_p3 <- all_dls$"uninj_pooled_oom_lists"$"imp_3"
uninj_ol_p4 <- all_dls$"uninj_pooled_oom_lists"$"imp_4"
uninj_ol_p5 <- all_dls$"uninj_pooled_oom_lists"$"imp_5"

```

```{r}

matched_uninj_esm_1_s1 <- extend_solutions(matched_uninj_solutions_matrix_1$"s1", data_list = uninj_dl_s1, target_list = uninj_ol_s1, min_pval = 1e-10, processes = "max")

names(matched_uninj_dls_1[[1]])

write_csv(proc_path("matched_uninj_esm_1_s1.csv", TRUE))
matched_uninj_esm_1_s2 <- extend_solutions(matched_uninj_solutions_matrix_1$"s2", data_list = uninj_dl_s2, target_list = uninj_ol_s2, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_1_s2.csv", TRUE))
matched_uninj_esm_1_s3 <- extend_solutions(matched_uninj_solutions_matrix_1$"s3", data_list = uninj_dl_s3, target_list = uninj_ol_s3, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_1_s3.csv", TRUE))
matched_uninj_esm_1_s4 <- extend_solutions(matched_uninj_solutions_matrix_1$"s4", data_list = uninj_dl_s4, target_list = uninj_ol_s4, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_1_s4.csv", TRUE))
matched_uninj_esm_1_s5 <- extend_solutions(matched_uninj_solutions_matrix_1$"s5", data_list = uninj_dl_s5, target_list = uninj_ol_s5, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_1_s5.csv", TRUE))
matched_uninj_esm_1_p1 <- extend_solutions(matched_uninj_solutions_matrix_1$"p1", data_list = uninj_dl_p1, target_list = uninj_ol_p1, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_1_p1.csv", TRUE))
matched_uninj_esm_1_p2 <- extend_solutions(matched_uninj_solutions_matrix_1$"p2", data_list = uninj_dl_p2, target_list = uninj_ol_p2, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_1_p2.csv", TRUE))
matched_uninj_esm_1_p3 <- extend_solutions(matched_uninj_solutions_matrix_1$"p3", data_list = uninj_dl_p3, target_list = uninj_ol_p3, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_1_p3.csv", TRUE))
matched_uninj_esm_1_p4 <- extend_solutions(matched_uninj_solutions_matrix_1$"p4", data_list = uninj_dl_p4, target_list = uninj_ol_p4, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_1_p4.csv", TRUE))
matched_uninj_esm_1_p5 <- extend_solutions(matched_uninj_solutions_matrix_1$"p5", data_list = uninj_dl_p5, target_list = uninj_ol_p5, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_1_p5.csv", TRUE))

matched_uninj_esm_2_s1 <- extend_solutions(matched_uninj_solutions_matrix_2$"s1", data_list = uninj_dl_s1, target_list = uninj_ol_s1, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_2_s2.csv", TRUE))
matched_uninj_esm_2_s2 <- extend_solutions(matched_uninj_solutions_matrix_2$"s2", data_list = uninj_dl_s2, target_list = uninj_ol_s2, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_2_s2.csv", TRUE))
matched_uninj_esm_2_s3 <- extend_solutions(matched_uninj_solutions_matrix_2$"s3", data_list = uninj_dl_s3, target_list = uninj_ol_s3, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_2_s3.csv", TRUE))
matched_uninj_esm_2_s4 <- extend_solutions(matched_uninj_solutions_matrix_2$"s4", data_list = uninj_dl_s4, target_list = uninj_ol_s4, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_2_s4.csv", TRUE))
matched_uninj_esm_2_s5 <- extend_solutions(matched_uninj_solutions_matrix_2$"s5", data_list = uninj_dl_s5, target_list = uninj_ol_s5, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_2_s5.csv", TRUE))
matched_uninj_esm_2_p1 <- extend_solutions(matched_uninj_solutions_matrix_2$"p1", data_list = uninj_dl_p1, target_list = uninj_ol_p1, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_2_p1.csv", TRUE))
matched_uninj_esm_2_p2 <- extend_solutions(matched_uninj_solutions_matrix_2$"p2", data_list = uninj_dl_p2, target_list = uninj_ol_p2, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_2_p2.csv", TRUE))
matched_uninj_esm_2_p3 <- extend_solutions(matched_uninj_solutions_matrix_2$"p3", data_list = uninj_dl_p3, target_list = uninj_ol_p3, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_2_p3.csv", TRUE))
matched_uninj_esm_2_p4 <- extend_solutions(matched_uninj_solutions_matrix_2$"p4", data_list = uninj_dl_p4, target_list = uninj_ol_p4, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_2_p4.csv", TRUE))
matched_uninj_esm_2_p5 <- extend_solutions(matched_uninj_solutions_matrix_2$"p5", data_list = uninj_dl_p5, target_list = uninj_ol_p5, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_2_p5.csv", TRUE))

matched_uninj_esm_3_s1 <- extend_solutions(matched_uninj_solutions_matrix_3$"s1", data_list = uninj_dl_s1, target_list = uninj_ol_s1, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_3_s1.csv", TRUE))
matched_uninj_esm_3_s2 <- extend_solutions(matched_uninj_solutions_matrix_3$"s2", data_list = uninj_dl_s2, target_list = uninj_ol_s2, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_3_s2.csv", TRUE))
matched_uninj_esm_3_s3 <- extend_solutions(matched_uninj_solutions_matrix_3$"s3", data_list = uninj_dl_s3, target_list = uninj_ol_s3, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_3_s3.csv", TRUE))
matched_uninj_esm_3_s4 <- extend_solutions(matched_uninj_solutions_matrix_3$"s4", data_list = uninj_dl_s4, target_list = uninj_ol_s4, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_3_s4.csv", TRUE))
matched_uninj_esm_3_s5 <- extend_solutions(matched_uninj_solutions_matrix_3$"s5", data_list = uninj_dl_s5, target_list = uninj_ol_s5, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_3_s5.csv", TRUE))
matched_uninj_esm_3_p1 <- extend_solutions(matched_uninj_solutions_matrix_3$"p1", data_list = uninj_dl_p1, target_list = uninj_ol_p1, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_3_p1.csv", TRUE))
matched_uninj_esm_3_p2 <- extend_solutions(matched_uninj_solutions_matrix_3$"p2", data_list = uninj_dl_p2, target_list = uninj_ol_p2, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_3_p2.csv", TRUE))
matched_uninj_esm_3_p3 <- extend_solutions(matched_uninj_solutions_matrix_3$"p3", data_list = uninj_dl_p3, target_list = uninj_ol_p3, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_3_p3.csv", TRUE))
matched_uninj_esm_3_p4 <- extend_solutions(matched_uninj_solutions_matrix_3$"p4", data_list = uninj_dl_p4, target_list = uninj_ol_p4, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_3_p4.csv", TRUE))
matched_uninj_esm_3_p5 <- extend_solutions(matched_uninj_solutions_matrix_3$"p5", data_list = uninj_dl_p5, target_list = uninj_ol_p5, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_3_p5.csv", TRUE))

matched_uninj_esm_4_s1 <- extend_solutions(matched_uninj_solutions_matrix_4$"s1", data_list = uninj_dl_s1, target_list = uninj_ol_s1, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_4_s1.csv", TRUE))
matched_uninj_esm_4_s2 <- extend_solutions(matched_uninj_solutions_matrix_4$"s2", data_list = uninj_dl_s2, target_list = uninj_ol_s2, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_4_s2.csv", TRUE))
matched_uninj_esm_4_s3 <- extend_solutions(matched_uninj_solutions_matrix_4$"s3", data_list = uninj_dl_s3, target_list = uninj_ol_s3, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_4_s3.csv", TRUE))
matched_uninj_esm_4_s4 <- extend_solutions(matched_uninj_solutions_matrix_4$"s4", data_list = uninj_dl_s4, target_list = uninj_ol_s4, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_4_s4.csv", TRUE))
matched_uninj_esm_4_s5 <- extend_solutions(matched_uninj_solutions_matrix_4$"s5", data_list = uninj_dl_s5, target_list = uninj_ol_s5, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_4_s5.csv", TRUE))
matched_uninj_esm_4_p1 <- extend_solutions(matched_uninj_solutions_matrix_4$"p1", data_list = uninj_dl_p1, target_list = uninj_ol_p1, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_4_p1.csv", TRUE))
matched_uninj_esm_4_p2 <- extend_solutions(matched_uninj_solutions_matrix_4$"p2", data_list = uninj_dl_p2, target_list = uninj_ol_p2, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_4_p2.csv", TRUE))
matched_uninj_esm_4_p3 <- extend_solutions(matched_uninj_solutions_matrix_4$"p3", data_list = uninj_dl_p3, target_list = uninj_ol_p3, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_4_p3.csv", TRUE))
matched_uninj_esm_4_p4 <- extend_solutions(matched_uninj_solutions_matrix_4$"p4", data_list = uninj_dl_p4, target_list = uninj_ol_p4, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_4_p4.csv", TRUE))
matched_uninj_esm_4_p5 <- extend_solutions(matched_uninj_solutions_matrix_4$"p5", data_list = uninj_dl_p5, target_list = uninj_ol_p5, min_pval = 1e-10, processes = "max")
write_csv(proc_path("matched_uninj_esm_4_p5.csv", TRUE))
```
