# Matching

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)
library(MatchIt)
library(tibble)
library(ggplot2)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subjects <- read_csv(sub_path("2024_09_13_mtbi_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2024_09_13_uninjured_subjects.csv"))
```

## Importing data

```{r}
all_dls <- list.load(input_path("2024_09_13_all_dls.rds"))

# Aye, this requires the validation set solution too...
mtbi_full_data_list_1 <- list.load(input_path("2024_09_13_mtbi_full_data_list_1.rds"))
mtbi_full_oom_list_1 <- list.load(input_path("2024_09_13_mtbi_full_oom_list_1.rds"))

mtbi_full_top_3c <- read_csv(proc_path("2024_09_13_mtbi_full_top_3c.csv"))

uninj_dl_s1 <- all_dls$"uninj_data_lists"$"imp_1"
uninj_dl_p1 <- all_dls$"uninj_pooled_data_lists"$"imp_1"
uninj_ol_s1 <- all_dls$"uninj_oom_lists"$"imp_1"
uninj_ol_p1 <- all_dls$"uninj_pooled_oom_lists"$"imp_1"
```


## Matching

Finding matched uninjured controls for each mtbi subject based on a variety of variables.
Matching will be done based on the first imputed dataset of the baseline data.

```{r}
mtbi_matching_df <- c(mtbi_full_data_list_1, mtbi_full_oom_list_1) |> collapse_dl()

uninj_matching_df_s1 <- c(uninj_dl_s1, uninj_ol_s1) |> collapse_dl()
uninj_matching_df_p1 <- c(uninj_dl_p1, uninj_ol_p1) |> collapse_dl()

mtbi_matching_df$"mtbi" <- 1
uninj_matching_df_s1$"mtbi" <- 0
uninj_matching_df_p1$"mtbi" <- 0

mtbi_matching_df <- dplyr::select(
    mtbi_matching_df,
    colnames(uninj_matching_df_s1)
)

matching_df_s1 <- rbind(mtbi_matching_df, uninj_matching_df_s1)
matching_df_p1 <- rbind(mtbi_matching_df, uninj_matching_df_p1)

# Total parent psych
matching_df_s1$"total_parent_psych" <- matching_df_s1 |> dplyr::select(dplyr::starts_with("parent")) |> rowSums()
matching_df_p1$"total_parent_psych" <- matching_df_p1 |> dplyr::select(dplyr::starts_with("parent")) |> rowSums()

# Total CBCL
matching_df_s1$"total_impairments" <- matching_df_s1 |> dplyr::select(dplyr::starts_with("cbcl"), dplyr::starts_with("sds")) |> rowSums()
matching_df_p1$"total_impairments" <- matching_df_p1 |> dplyr::select(dplyr::starts_with("cbcl"), dplyr::starts_with("sds")) |> rowSums()
```

We'll try a few different matching schemes:

```{r}
# Matching by income, race, parent psych
matching_results_a_s1 <- matchit(formula(mtbi ~ household_income + race + total_parent_psych), data = matching_df_s1, method = "nearest")
matching_results_a_p1 <- matchit(formula(mtbi ~ household_income + race + total_parent_psych), data = matching_df_p1, method = "nearest")
matching_summary_a_s1 <- capture.output(print(summary(matching_results_a_s1)))
matching_summary_a_p1 <- capture.output(print(summary(matching_results_a_p1)))
matched_data_a_s1 <- match.data(matching_results_a_s1)
matched_data_a_p1 <- match.data(matching_results_a_p1)

###############################################################################
# Matching by demographic variables
###############################################################################
matching_results_b_s1 <- matchit(formula(mtbi ~ household_income + race + sex + pubertal_status_p + pubertal_status_y), data = matching_df_s1, method = "nearest")
matching_results_b_p1 <- matchit(formula(mtbi ~ household_income + race + sex + pubertal_status_p + pubertal_status_y), data = matching_df_p1, method = "nearest")
matching_summary_b_s1 <- capture.output(print(summary(matching_results_b_s1)))
matching_summary_b_p1 <- capture.output(print(summary(matching_results_b_p1)))
matched_data_b_s1 <- match.data(matching_results_b_s1)
matched_data_b_p1 <- match.data(matching_results_b_p1)

###############################################################################
# Matching by parent psych alone
###############################################################################
matching_results_c_s1 <- matchit(formula(mtbi ~ total_parent_psych), data = matching_df_s1, method = "nearest")
matching_results_c_p1 <- matchit(formula(mtbi ~ total_parent_psych), data = matching_df_p1, method = "nearest")
matching_summary_c_s1 <- capture.output(print(summary(matching_results_c_s1)))
matching_summary_c_p1 <- capture.output(print(summary(matching_results_c_p1)))
matched_data_c_s1 <- match.data(matching_results_c_s1)
matched_data_c_p1 <- match.data(matching_results_c_p1)

###############################################################################
# Matching by CBCL alone
###############################################################################
matching_results_d_s1 <- matchit(formula(mtbi ~ total_impairments), data = matching_df_s1, method = "nearest")
matching_results_d_p1 <- matchit(formula(mtbi ~ total_impairments), data = matching_df_p1, method = "nearest")
matching_summary_d_s1 <- capture.output(print(summary(matching_results_d_s1)))
matching_summary_d_p1 <- capture.output(print(summary(matching_results_d_p1)))
matched_data_d_s1 <- match.data(matching_results_d_s1)
matched_data_d_p1 <- match.data(matching_results_d_p1)

saveRDS(matching_summary_a_s1, proc_path("matching_summary_a_s1.rds", TRUE))
saveRDS(matching_summary_a_p1, proc_path("matching_summary_a_p1.rds", TRUE))
saveRDS(matching_summary_b_s1, proc_path("matching_summary_b_s1.rds", TRUE))
saveRDS(matching_summary_b_p1, proc_path("matching_summary_b_p1.rds", TRUE))
saveRDS(matching_summary_c_s1, proc_path("matching_summary_c_s1.rds", TRUE))
saveRDS(matching_summary_c_p1, proc_path("matching_summary_c_p1.rds", TRUE))
saveRDS(matching_summary_d_s1, proc_path("matching_summary_d_s1.rds", TRUE))
saveRDS(matching_summary_d_p1, proc_path("matching_summary_d_p1.rds", TRUE))
```

```{r}
## CHECKPOINT
#matching_summary_1_imp_1 <- readRDS(proc_path("2024_09_13_matching_summary_1_imp_1.rds"))
#matching_summary_2_imp_1 <- readRDS(proc_path("2024_09_13_matching_summary_2_imp_1.rds"))
#matching_summary_3_imp_1 <- readRDS(proc_path("2024_09_13_matching_summary_3_imp_1.rds"))
#matching_summary_4_imp_1 <- readRDS(proc_path("2024_09_13_matching_summary_4_imp_1.rds"))

#grDevices::png(filename = fig_path("matching_results_1_imp_1.png", TRUE), width = 1000, height = 500, res = 100)
#plot(matching_results_1_imp_1, type = "density", interactive = FALSE)
#grDevices::dev.off()
#
#grDevices::png(filename = fig_path("matching_results_2_imp_1.png", TRUE), width = 1000, height = 500, res = 100)
#plot(matching_results_2_imp_1, type = "density", interactive = FALSE)
#grDevices::dev.off()
#
#grDevices::png(filename = fig_path("matching_results_3_imp_1.png", TRUE), width = 1000, height = 500, res = 100)
#plot(matching_results_3_imp_1, type = "density", interactive = FALSE)
#grDevices::dev.off()
#
#grDevices::png(filename = fig_path("matching_results_4_imp_1.png", TRUE), width = 1000, height = 500, res = 100)
#plot(matching_results_4_imp_1, type = "density", interactive = FALSE)
#grDevices::dev.off()
```

```{r}
matched_uninj_a_s1 <- dplyr::filter(matched_data_a_s1, mtbi == 0)$"subjectkey"
matched_uninj_a_p1 <- dplyr::filter(matched_data_a_p1, mtbi == 0)$"subjectkey"
matched_uninj_b_s1 <- dplyr::filter(matched_data_b_s1, mtbi == 0)$"subjectkey"
matched_uninj_b_p1 <- dplyr::filter(matched_data_b_p1, mtbi == 0)$"subjectkey"
matched_uninj_c_s1 <- dplyr::filter(matched_data_c_s1, mtbi == 0)$"subjectkey"
matched_uninj_c_p1 <- dplyr::filter(matched_data_c_p1, mtbi == 0)$"subjectkey"
matched_uninj_d_s1 <- dplyr::filter(matched_data_d_s1, mtbi == 0)$"subjectkey"
matched_uninj_d_p1 <- dplyr::filter(matched_data_d_p1, mtbi == 0)$"subjectkey"

# Extract the control group from the matched data
write_csv(data.frame(subjectkey = matched_uninj_a_s1), sub_path("matched_uninj_a_s1.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_a_p1), sub_path("matched_uninj_a_p1.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_b_s1), sub_path("matched_uninj_b_s1.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_b_p1), sub_path("matched_uninj_b_p1.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_c_s1), sub_path("matched_uninj_c_s1.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_c_p1), sub_path("matched_uninj_c_p1.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_d_s1), sub_path("matched_uninj_d_s1.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_d_p1), sub_path("matched_uninj_d_p1.csv", TRUE))
```

```{r}
matched_uninj_a_s1 <- read_subjects(sub_path("2024_09_16_matched_uninj_a_s1.csv"))
matched_uninj_a_p1 <- read_subjects(sub_path("2024_09_16_matched_uninj_a_p1.csv"))
matched_uninj_b_s1 <- read_subjects(sub_path("2024_09_16_matched_uninj_b_s1.csv"))
matched_uninj_b_p1 <- read_subjects(sub_path("2024_09_16_matched_uninj_b_p1.csv"))
matched_uninj_c_s1 <- read_subjects(sub_path("2024_09_16_matched_uninj_c_s1.csv"))
matched_uninj_c_p1 <- read_subjects(sub_path("2024_09_16_matched_uninj_c_p1.csv"))
matched_uninj_d_s1 <- read_subjects(sub_path("2024_09_16_matched_uninj_d_s1.csv"))
matched_uninj_d_p1 <- read_subjects(sub_path("2024_09_16_matched_uninj_d_p1.csv"))

sub_list <- list(
    "a_s1" = matched_uninj_a_s1,
    "a_p1" = matched_uninj_a_p1,
    "b_s1" = matched_uninj_b_s1,
    "b_p1" = matched_uninj_b_p1,
    "c_s1" = matched_uninj_c_s1,
    "c_p1" = matched_uninj_c_p1,
    "d_s1" = matched_uninj_d_s1,
    "d_p1" = matched_uninj_d_p1
)
```

## Subsetting matched uninjured data and out of model lists

```{r}
subject_filter_dl <- function(data_list, subject_vector) {
    data_list <- data_list |>
        lapply(
            function(x) {
                keep_subs <- x$"data"$"subjectkey" %in% subject_vector
                x$"data" <- x$"data"[keep_subs, ]
                return(x)
            }
        )
    return(data_list)
}

matched_uninj_dl_a_s1 <- subject_filter_dl(uninj_dl_s1, matched_uninj_a_s1)
matched_uninj_dl_a_p1 <- subject_filter_dl(uninj_dl_p1, matched_uninj_a_p1)
matched_uninj_ol_a_s1 <- subject_filter_dl(uninj_ol_s1, matched_uninj_a_s1)
matched_uninj_ol_a_p1 <- subject_filter_dl(uninj_ol_p1, matched_uninj_a_p1)

matched_uninj_dl_b_s1 <- subject_filter_dl(uninj_dl_s1, matched_uninj_b_s1)
matched_uninj_dl_b_p1 <- subject_filter_dl(uninj_dl_p1, matched_uninj_b_p1)
matched_uninj_ol_b_s1 <- subject_filter_dl(uninj_ol_s1, matched_uninj_b_s1)
matched_uninj_ol_b_p1 <- subject_filter_dl(uninj_ol_p1, matched_uninj_b_p1)

matched_uninj_dl_c_s1 <- subject_filter_dl(uninj_dl_s1, matched_uninj_c_s1)
matched_uninj_dl_c_p1 <- subject_filter_dl(uninj_dl_p1, matched_uninj_c_p1)
matched_uninj_ol_c_s1 <- subject_filter_dl(uninj_ol_s1, matched_uninj_c_s1)
matched_uninj_ol_c_p1 <- subject_filter_dl(uninj_ol_p1, matched_uninj_c_p1)

matched_uninj_dl_d_s1 <- subject_filter_dl(uninj_dl_s1, matched_uninj_d_s1)
matched_uninj_dl_d_p1 <- subject_filter_dl(uninj_dl_p1, matched_uninj_d_p1)
matched_uninj_ol_d_s1 <- subject_filter_dl(uninj_ol_s1, matched_uninj_d_s1)
matched_uninj_ol_d_p1 <- subject_filter_dl(uninj_ol_p1, matched_uninj_d_p1)

###############################################################################

list.save(matched_uninj_dl_a_s1, proc_path("matched_uninj_dl_a_s1.rds", TRUE))
list.save(matched_uninj_dl_a_p1, proc_path("matched_uninj_dl_a_p1.rds", TRUE))
list.save(matched_uninj_ol_a_s1, proc_path("matched_uninj_ol_a_s1.rds", TRUE))
list.save(matched_uninj_ol_a_p1, proc_path("matched_uninj_ol_a_p1.rds", TRUE))
list.save(matched_uninj_dl_b_s1, proc_path("matched_uninj_dl_b_s1.rds", TRUE))
list.save(matched_uninj_dl_b_p1, proc_path("matched_uninj_dl_b_p1.rds", TRUE))
list.save(matched_uninj_ol_b_s1, proc_path("matched_uninj_ol_b_s1.rds", TRUE))
list.save(matched_uninj_ol_b_p1, proc_path("matched_uninj_ol_b_p1.rds", TRUE))
list.save(matched_uninj_dl_c_s1, proc_path("matched_uninj_dl_c_s1.rds", TRUE))
list.save(matched_uninj_dl_c_p1, proc_path("matched_uninj_dl_c_p1.rds", TRUE))
list.save(matched_uninj_ol_c_s1, proc_path("matched_uninj_ol_c_s1.rds", TRUE))
list.save(matched_uninj_ol_c_p1, proc_path("matched_uninj_ol_c_p1.rds", TRUE))
list.save(matched_uninj_dl_d_s1, proc_path("matched_uninj_dl_d_s1.rds", TRUE))
list.save(matched_uninj_dl_d_p1, proc_path("matched_uninj_dl_d_p1.rds", TRUE))
list.save(matched_uninj_ol_d_s1, proc_path("matched_uninj_ol_d_s1.rds", TRUE))
list.save(matched_uninj_ol_d_p1, proc_path("matched_uninj_ol_d_p1.rds", TRUE))
```

```{r}
# CHECKPOINT
matched_uninj_dl_a_s1 <- list.load(proc_path("2024_09_16_matched_uninj_dl_a_s1.rds"))
matched_uninj_dl_a_p1 <- list.load(proc_path("2024_09_16_matched_uninj_dl_a_p1.rds"))
matched_uninj_ol_a_s1 <- list.load(proc_path("2024_09_16_matched_uninj_ol_a_s1.rds"))
matched_uninj_ol_a_p1 <- list.load(proc_path("2024_09_16_matched_uninj_ol_a_p1.rds"))
matched_uninj_dl_b_s1 <- list.load(proc_path("2024_09_16_matched_uninj_dl_b_s1.rds"))
matched_uninj_dl_b_p1 <- list.load(proc_path("2024_09_16_matched_uninj_dl_b_p1.rds"))
matched_uninj_ol_b_s1 <- list.load(proc_path("2024_09_16_matched_uninj_ol_b_s1.rds"))
matched_uninj_ol_b_p1 <- list.load(proc_path("2024_09_16_matched_uninj_ol_b_p1.rds"))
matched_uninj_dl_c_s1 <- list.load(proc_path("2024_09_16_matched_uninj_dl_c_s1.rds"))
matched_uninj_dl_c_p1 <- list.load(proc_path("2024_09_16_matched_uninj_dl_c_p1.rds"))
matched_uninj_ol_c_s1 <- list.load(proc_path("2024_09_16_matched_uninj_ol_c_s1.rds"))
matched_uninj_ol_c_p1 <- list.load(proc_path("2024_09_16_matched_uninj_ol_c_p1.rds"))
matched_uninj_dl_d_s1 <- list.load(proc_path("2024_09_16_matched_uninj_dl_d_s1.rds"))
matched_uninj_dl_d_p1 <- list.load(proc_path("2024_09_16_matched_uninj_dl_d_p1.rds"))
matched_uninj_ol_d_s1 <- list.load(proc_path("2024_09_16_matched_uninj_ol_d_s1.rds"))
matched_uninj_ol_d_p1 <- list.load(proc_path("2024_09_16_matched_uninj_ol_d_p1.rds"))
```

## metaSNF

```{r}
my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

matched_settings_matrix <- generate_settings_matrix(
    matched_uninj_dl_a_s1,
    nrow = 200,
    seed = 42,
    distance_metrics_list = my_distance_metrics
)

write_csv(matched_settings_matrix, proc_path("matched_settings_matrix.csv", TRUE))
```

```{r}
# CHECKPOINT
matched_settings_matrix <- read_csv(proc_path("2024_09_16_matched_settings_matrix.csv"))
```

The goal now is to actually run the SNF.

I have 4 different "sets" of data list / oom list combinations.

Consider just the first set.

This covers 10 different imputed datasets (right?) the 5 pooled and 5 solo uninjured.
So, I'll create 2000 SNF solutions using all of those 10 sets.

Then, repeat that process 4x.

```{r}
uninj_sm_a_s1 <- batch_snf(matched_uninj_dl_a_s1, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_a_s1, proc_path("uninj_sm_a_s1.csv", TRUE))
uninj_sm_a_p1 <- batch_snf(matched_uninj_dl_a_p1, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_a_p1, proc_path("uninj_sm_a_p1.csv", TRUE))
uninj_sm_b_s1 <- batch_snf(matched_uninj_dl_b_s1, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_b_s1, proc_path("uninj_sm_b_s1.csv", TRUE))
uninj_sm_b_p1 <- batch_snf(matched_uninj_dl_b_p1, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_b_p1, proc_path("uninj_sm_b_p1.csv", TRUE))
uninj_sm_c_s1 <- batch_snf(matched_uninj_dl_c_s1, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_c_s1, proc_path("uninj_sm_c_s1.csv", TRUE))
uninj_sm_c_p1 <- batch_snf(matched_uninj_dl_c_p1, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_c_p1, proc_path("uninj_sm_c_p1.csv", TRUE))
uninj_sm_d_s1 <- batch_snf(matched_uninj_dl_d_s1, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_d_s1, proc_path("uninj_sm_d_s1.csv", TRUE))
uninj_sm_d_p1 <- batch_snf(matched_uninj_dl_d_p1, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_d_p1, proc_path("uninj_sm_d_p1.csv", TRUE))
```

```{r}
uninj_sm_a_s1 <- read_csv(proc_path("2024_09_16_uninj_sm_a_s1.csv"))
uninj_sm_a_p1 <- read_csv(proc_path("2024_09_16_uninj_sm_a_p1.csv"))
uninj_sm_b_s1 <- read_csv(proc_path("2024_09_16_uninj_sm_b_s1.csv"))
uninj_sm_b_p1 <- read_csv(proc_path("2024_09_16_uninj_sm_b_p1.csv"))
uninj_sm_c_s1 <- read_csv(proc_path("2024_09_16_uninj_sm_c_s1.csv"))
uninj_sm_c_p1 <- read_csv(proc_path("2024_09_16_uninj_sm_c_p1.csv"))
uninj_sm_d_s1 <- read_csv(proc_path("2024_09_16_uninj_sm_d_s1.csv"))
uninj_sm_d_p1 <- read_csv(proc_path("2024_09_16_uninj_sm_d_p1.csv"))
```

```{r}
matched_uninj_esm_a_s1 <- extend_solutions(uninj_sm_a_s1, data_list = matched_uninj_dl_a_s1, target_list = matched_uninj_ol_a_s1, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_a_s1, proc_path("matched_uninj_esm_a_s1.csv", TRUE))
matched_uninj_esm_a_p1 <- extend_solutions(uninj_sm_a_p1, data_list = matched_uninj_dl_a_p1, target_list = matched_uninj_ol_a_p1, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_a_p1, proc_path("matched_uninj_esm_a_p1.csv", TRUE))
matched_uninj_esm_b_s1 <- extend_solutions(uninj_sm_b_s1, data_list = matched_uninj_dl_b_s1, target_list = matched_uninj_ol_b_s1, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_b_s1, proc_path("matched_uninj_esm_b_s1.csv", TRUE))
matched_uninj_esm_b_p1 <- extend_solutions(uninj_sm_b_p1, data_list = matched_uninj_dl_b_p1, target_list = matched_uninj_ol_b_p1, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_b_p1, proc_path("matched_uninj_esm_b_p1.csv", TRUE))
matched_uninj_esm_c_s1 <- extend_solutions(uninj_sm_c_s1, data_list = matched_uninj_dl_c_s1, target_list = matched_uninj_ol_c_s1, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_c_s1, proc_path("matched_uninj_esm_c_s1.csv", TRUE))
matched_uninj_esm_c_p1 <- extend_solutions(uninj_sm_c_p1, data_list = matched_uninj_dl_c_p1, target_list = matched_uninj_ol_c_p1, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_c_p1, proc_path("matched_uninj_esm_c_p1.csv", TRUE))
matched_uninj_esm_d_s1 <- extend_solutions(uninj_sm_d_s1, data_list = matched_uninj_dl_d_s1, target_list = matched_uninj_ol_d_s1, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_d_s1, proc_path("matched_uninj_esm_d_s1.csv", TRUE))
matched_uninj_esm_d_p1 <- extend_solutions(uninj_sm_d_p1, data_list = matched_uninj_dl_d_p1, target_list = matched_uninj_ol_d_p1, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_d_p1, proc_path("matched_uninj_esm_d_p1.csv", TRUE))
```

```{r}
matched_uninj_esm_a_s1 <- read_csv(proc_path("2024_09_16_matched_uninj_esm_a_s1.csv"))
matched_uninj_esm_a_p1 <- read_csv(proc_path("2024_09_16_matched_uninj_esm_a_p1.csv"))
matched_uninj_esm_b_s1 <- read_csv(proc_path("2024_09_16_matched_uninj_esm_b_s1.csv"))
matched_uninj_esm_b_p1 <- read_csv(proc_path("2024_09_16_matched_uninj_esm_b_p1.csv"))
matched_uninj_esm_c_s1 <- read_csv(proc_path("2024_09_16_matched_uninj_esm_c_s1.csv"))
matched_uninj_esm_c_p1 <- read_csv(proc_path("2024_09_16_matched_uninj_esm_c_p1.csv"))
matched_uninj_esm_d_s1 <- read_csv(proc_path("2024_09_16_matched_uninj_esm_d_s1.csv"))
matched_uninj_esm_d_p1 <- read_csv(proc_path("2024_09_16_matched_uninj_esm_d_p1.csv"))

matched_uninj_esm_list <- list(
    "a_s1" = matched_uninj_esm_a_s1,
    "a_p1" = matched_uninj_esm_a_p1,
    "b_s1" = matched_uninj_esm_b_s1,
    "b_p1" = matched_uninj_esm_b_p1,
    "c_s1" = matched_uninj_esm_c_s1,
    "c_p1" = matched_uninj_esm_c_p1,
    "d_s1" = matched_uninj_esm_d_s1,
    "d_p1" = matched_uninj_esm_d_p1
)

names(matched_uninj_esm_list)  <- c(
    "a_s1",
    "a_p1",
    "b_s1",
    "b_p1",
    "c_s1",
    "c_p1",
    "d_s1",
    "d_p1"
)

list.save(matched_uninj_esm_list, proc_path("matched_uninj_esm_list.rds", TRUE))
```

```{r}
matched_uninj_esm_list <- list.load(proc_path("2024_09_16_matched_uninj_esm_list.rds"))
```

```{r}
matched_uninj_esm_3c_list <- lapply(
    matched_uninj_esm_list,
    function(x) {
        x$"impairment_separation" <- -log10(x$"mean_pval")
        x <- dplyr::filter(x, nclust == 3, impairment_separation > 1)
        return(x)
    }
)

list.save(
    matched_uninj_esm_3c_list,
    proc_path("matched_uninj_esm_3c_list.rds", TRUE)
)
```

```{r}
# CHECKPOINT
matched_uninj_esm_3c_list <- list.load(
    proc_path("2024_09_17_matched_uninj_esm_3c_list.rds")
)
```

```{r}
# Pretty small impairment separations
lapply(
    matched_uninj_esm_3c_list,
    function(x) {
        x$"impairment_separation"
    }
)

dcols <- c(
    "AS" = "#85929e",
    "D" = "#bb8fce",
    "N" = "#e59866",
    "MH" = "#7fb3d5",
    "P" = "#52be80",
    "S" = "#d98880",
    "B" = "#ff3131"
)

matched_uninj_a_s1 <- mc_manhattan_plot(
    matched_uninj_esm_3c_list$"a_s1",
    data_list = matched_uninj_dl_a_s1,
    target_list = matched_uninj_ol_a_s1,
    domain_colours = dcols
)

matched_uninj_a_p1 <- mc_manhattan_plot(
    matched_uninj_esm_3c_list$"a_p1",
    data_list = matched_uninj_dl_a_p1,
    target_list = matched_uninj_ol_a_p1,
    domain_colours = dcols
)

matched_uninj_b_s1 <- mc_manhattan_plot(
    matched_uninj_esm_3c_list$"b_s1",
    data_list = matched_uninj_dl_b_s1,
    target_list = matched_uninj_ol_b_s1,
    domain_colours = dcols
)

matched_uninj_b_p1 <- mc_manhattan_plot(
    matched_uninj_esm_3c_list$"b_p1",
    data_list = matched_uninj_dl_b_p1,
    target_list = matched_uninj_ol_b_p1,
    domain_colours = dcols
)

matched_uninj_c_s1 <- mc_manhattan_plot(
    matched_uninj_esm_3c_list$"c_s1",
    data_list = matched_uninj_dl_c_s1,
    target_list = matched_uninj_ol_c_s1,
    domain_colours = dcols
)

matched_uninj_c_p1 <- mc_manhattan_plot(
    matched_uninj_esm_3c_list$"c_p1",
    data_list = matched_uninj_dl_c_p1,
    target_list = matched_uninj_ol_c_p1,
    domain_colours = dcols
)

matched_uninj_d_s1 <- mc_manhattan_plot(
    matched_uninj_esm_3c_list$"d_s1",
    data_list = matched_uninj_dl_d_s1,
    target_list = matched_uninj_ol_d_s1,
    domain_colours = dcols
)

matched_uninj_d_p1 <- mc_manhattan_plot(
    matched_uninj_esm_3c_list$"d_p1",
    data_list = matched_uninj_dl_d_p1,
    target_list = matched_uninj_ol_d_p1,
    domain_colours = dcols
)

# Good rows 1 and 4
matched_uninj_a_s1

# Good row 1
matched_uninj_a_p1

# Bad
matched_uninj_b_s1

# Bad
matched_uninj_b_p1

# Bad
matched_uninj_c_s1

# Bad
matched_uninj_c_p1

# Bad
matched_uninj_d_s1

# So-so
matched_uninj_d_p1

matched_uninj_manhattan_plots <- list(
    matched_uninj_a_s1,
    matched_uninj_a_p1,
    matched_uninj_b_s1,
    matched_uninj_b_p1,
    matched_uninj_c_s1,
    matched_uninj_c_p1,
    matched_uninj_d_s1,
    matched_uninj_d_p1
)

names(matched_uninj_manhattan_plots) <- c(
    "a_s1",
    "a_p1",
    "b_s1",
    "b_p1",
    "c_s1",
    "c_p1",
    "d_s1",
    "d_p1"
)

list.save(
    matched_uninj_manhattan_plots,
    fig_path("matched_uninj_manhattan_plots.rds", TRUE)
)
```

```{r}
# CHECKPOINT
matched_uninj_manhattan_plots <- list.load(
    fig_path("2024_09_16_matched_uninj_manhattan_plots.rds")
)
```

Exporting the manhattan plots

```{r}
qs2 <- function(plot, path, w = 18, h = 14, d = 120) {    
    path <- paste0("matched_uninj_", path, "_manhattan.png")
    ggsave(
        fig_path(path, TRUE),
        plot,
        width = w,
        height = h,
        dpi = d
    )
}

qs2(matched_uninj_manhattan_plots$"a_s1", "a_s1", h = 10)
qs2(matched_uninj_manhattan_plots$"a_p1", "a_p1", h = 10)
#
qs2(matched_uninj_manhattan_plots$"b_s1", "b_s1", h = 5)
qs2(matched_uninj_manhattan_plots$"b_p1", "b_p1", h = 5)
#
qs2(matched_uninj_manhattan_plots$"c_s1", "c_s1", h = 10)
qs2(matched_uninj_manhattan_plots$"c_p1", "c_p1", h = 5)
#
qs2(matched_uninj_manhattan_plots$"d_s1", "d_s1", h = 5)
qs2(matched_uninj_manhattan_plots$"d_p1", "d_p1", h = 7)
```

```{r}
matched_uninj_dls <- list(
    "a_s1" = matched_uninj_dl_a_s1,
    "a_p1" = matched_uninj_dl_a_p1,
    "b_s1" = matched_uninj_dl_b_s1,
    "b_p1" = matched_uninj_dl_b_p1,
    "c_s1" = matched_uninj_dl_c_s1,
    "c_p1" = matched_uninj_dl_c_p1,
    "d_s1" = matched_uninj_dl_d_s1,
    "d_p1" = matched_uninj_dl_d_p1
)

matched_uninj_ols <- list(
    "a_s1" = matched_uninj_ol_a_s1,
    "a_p1" = matched_uninj_ol_a_p1,
    "b_s1" = matched_uninj_ol_b_s1,
    "b_p1" = matched_uninj_ol_b_p1,
    "c_s1" = matched_uninj_ol_c_s1,
    "c_p1" = matched_uninj_ol_c_p1,
    "d_s1" = matched_uninj_ol_d_s1,
    "d_p1" = matched_uninj_ol_d_p1
)


a_s1_1_pl

names(matched_uninj_esm_3c_list)[1]
names(matched_uninj_esm_3c_list)[1:2]
names(matched_uninj_esm_3c_list)[3]

matched_pls <- lapply(
    names(matched_uninj_esm_3c_list),
    function(match) {
        pl <- list()
        nrows <- nrow(matched_uninj_esm_3c_list[[match]])
        for (row in seq_len(nrows)) {
            p <- auto_plot(
                matched_uninj_esm_3c_list[[match]][row, ],
                data_list = matched_uninj_dls[[match]],
                target_list = matched_uninj_ols[[match]]
            )
            pl[[length(pl) + 1]] <- p
        }
        names(pl) <- paste0("row_", seq_len(nrows))
        return(pl)
    }
)

names(matched_pls) <- names(matched_uninj_esm_3c_list)

list.save(matched_pls, fig_path("matched_pls.rds", TRUE))
```


```{r}
# CHECKPOINT
matched_pls <- list.load(fig_path("2024_09_17_matched_pls.rds"))


matched_pls$"a_s1"

```




```{r}
## CHECKPOINT
#matched_uninj_esm_list <- list.load(proc_path("2024_09_13_matched_uninj_esm_list.rds"))
#matched_uninj_aris <- list.load(proc_path("2024_09_13_matched_uninj_aris.rds"))
#matched_uninj_ari_orders <- list.load(proc_path("2024_09_13_matched_uninj_ari_orders.rds"))
```


```{r}
uninj_dl_s1 <- all_dls$"uninj_data_lists"$"imp_1"
uninj_dl_s2 <- all_dls$"uninj_data_lists"$"imp_2"
uninj_dl_s3 <- all_dls$"uninj_data_lists"$"imp_3"
uninj_dl_s4 <- all_dls$"uninj_data_lists"$"imp_4"
uninj_dl_s5 <- all_dls$"uninj_data_lists"$"imp_5"
uninj_dl_p1 <- all_dls$"uninj_pooled_data_lists"$"imp_1"
uninj_dl_p2 <- all_dls$"uninj_pooled_data_lists"$"imp_2"
uninj_dl_p3 <- all_dls$"uninj_pooled_data_lists"$"imp_3"
uninj_dl_p4 <- all_dls$"uninj_pooled_data_lists"$"imp_4"
uninj_dl_p5 <- all_dls$"uninj_pooled_data_lists"$"imp_5"

uninj_ol_s1 <- all_dls$"uninj_oom_lists"$"imp_1"
uninj_ol_s2 <- all_dls$"uninj_oom_lists"$"imp_2"
uninj_ol_s3 <- all_dls$"uninj_oom_lists"$"imp_3"
uninj_ol_s4 <- all_dls$"uninj_oom_lists"$"imp_4"
uninj_ol_s5 <- all_dls$"uninj_oom_lists"$"imp_5"
uninj_ol_p1 <- all_dls$"uninj_pooled_oom_lists"$"imp_1"
uninj_ol_p2 <- all_dls$"uninj_pooled_oom_lists"$"imp_2"
uninj_ol_p3 <- all_dls$"uninj_pooled_oom_lists"$"imp_3"
uninj_ol_p4 <- all_dls$"uninj_pooled_oom_lists"$"imp_4"
uninj_ol_p5 <- all_dls$"uninj_pooled_oom_lists"$"imp_5"
```
