# Matching

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)
library(MatchIt)
library(tibble)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subjects <- read_csv(sub_path("2024_09_13_mtbi_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2024_09_13_uninjured_subjects.csv"))
```

## Importing data

```{r}
all_dls <- list.load(input_path("2024_09_13_all_dls.rds"))

# Aye, this requires the validation set solution too...
mtbi_full_data_list_1 <- list.load(input_path("2024_09_13_mtbi_full_data_list_1.rds"))
mtbi_full_oom_list_1 <- list.load(input_path("2024_09_13_mtbi_full_oom_list_1.rds"))

uninj_dl_s1 <- all_dls$"uninj_data_lists"$"imp_1"
uninj_dl_s2 <- all_dls$"uninj_data_lists"$"imp_2"
uninj_dl_s3 <- all_dls$"uninj_data_lists"$"imp_3"
uninj_dl_s4 <- all_dls$"uninj_data_lists"$"imp_4"
uninj_dl_s5 <- all_dls$"uninj_data_lists"$"imp_5"
uninj_dl_p1 <- all_dls$"uninj_pooled_data_lists"$"imp_1"
uninj_dl_p2 <- all_dls$"uninj_pooled_data_lists"$"imp_2"
uninj_dl_p3 <- all_dls$"uninj_pooled_data_lists"$"imp_3"
uninj_dl_p4 <- all_dls$"uninj_pooled_data_lists"$"imp_4"
uninj_dl_p5 <- all_dls$"uninj_pooled_data_lists"$"imp_5"
uninj_ol_s1 <- all_dls$"uninj_oom_lists"$"imp_1"
uninj_ol_s2 <- all_dls$"uninj_oom_lists"$"imp_2"
uninj_ol_s3 <- all_dls$"uninj_oom_lists"$"imp_3"
uninj_ol_s4 <- all_dls$"uninj_oom_lists"$"imp_4"
uninj_ol_s5 <- all_dls$"uninj_oom_lists"$"imp_5"
uninj_ol_p1 <- all_dls$"uninj_pooled_oom_lists"$"imp_1"
uninj_ol_p2 <- all_dls$"uninj_pooled_oom_lists"$"imp_2"
uninj_ol_p3 <- all_dls$"uninj_pooled_oom_lists"$"imp_3"
uninj_ol_p4 <- all_dls$"uninj_pooled_oom_lists"$"imp_4"
uninj_ol_p5 <- all_dls$"uninj_pooled_oom_lists"$"imp_5"
```


## Matching

Finding matched uninjured controls for each mtbi subject based on a variety of variables.
Matching will be done based on the first imputed dataset of the baseline data.

```{r}
mtbi_matching_df <- c(mtbi_full_data_list_1, mtbi_full_oom_list_1) |> collapse_dl()

uninj_matching_df_s1 <- c(uninj_dl_s1, uninj_ol_s1) |> collapse_dl()
uninj_matching_df_s2 <- c(uninj_dl_s2, uninj_ol_s2) |> collapse_dl()
uninj_matching_df_s3 <- c(uninj_dl_s3, uninj_ol_s3) |> collapse_dl()
uninj_matching_df_s4 <- c(uninj_dl_s4, uninj_ol_s4) |> collapse_dl()
uninj_matching_df_s5 <- c(uninj_dl_s5, uninj_ol_s5) |> collapse_dl()

uninj_matching_df_p1 <- c(uninj_dl_p1, uninj_ol_p1) |> collapse_dl()
uninj_matching_df_p2 <- c(uninj_dl_p2, uninj_ol_p2) |> collapse_dl()
uninj_matching_df_p3 <- c(uninj_dl_p3, uninj_ol_p3) |> collapse_dl()
uninj_matching_df_p4 <- c(uninj_dl_p4, uninj_ol_p4) |> collapse_dl()
uninj_matching_df_p5 <- c(uninj_dl_p5, uninj_ol_p5) |> collapse_dl()

mtbi_matching_df$"mtbi" <- 1

uninj_matching_df_s1$"mtbi" <- 0
uninj_matching_df_s2$"mtbi" <- 0
uninj_matching_df_s3$"mtbi" <- 0
uninj_matching_df_s4$"mtbi" <- 0
uninj_matching_df_s5$"mtbi" <- 0

uninj_matching_df_p1$"mtbi" <- 0
uninj_matching_df_p2$"mtbi" <- 0
uninj_matching_df_p3$"mtbi" <- 0
uninj_matching_df_p4$"mtbi" <- 0
uninj_matching_df_p5$"mtbi" <- 0

mtbi_matching_df <- dplyr::select(
    mtbi_matching_df,
    colnames(uninj_matching_df_s1)
)

matching_df_s1 <- rbind(mtbi_matching_df, uninj_matching_df_s1)
matching_df_s2 <- rbind(mtbi_matching_df, uninj_matching_df_s2)
matching_df_s3 <- rbind(mtbi_matching_df, uninj_matching_df_s3)
matching_df_s4 <- rbind(mtbi_matching_df, uninj_matching_df_s4)
matching_df_s5 <- rbind(mtbi_matching_df, uninj_matching_df_s5)

matching_df_p1 <- rbind(mtbi_matching_df, uninj_matching_df_p1)
matching_df_p2 <- rbind(mtbi_matching_df, uninj_matching_df_p2)
matching_df_p3 <- rbind(mtbi_matching_df, uninj_matching_df_p3)
matching_df_p4 <- rbind(mtbi_matching_df, uninj_matching_df_p4)
matching_df_p5 <- rbind(mtbi_matching_df, uninj_matching_df_p5)

###############################################################################
# Total parent psych
###############################################################################
matching_df_s1$"total_parent_psych" <- matching_df_s1 |> dplyr::select(dplyr::starts_with("parent")) |> rowSums()
matching_df_s2$"total_parent_psych" <- matching_df_s2 |> dplyr::select(dplyr::starts_with("parent")) |> rowSums()
matching_df_s3$"total_parent_psych" <- matching_df_s3 |> dplyr::select(dplyr::starts_with("parent")) |> rowSums()
matching_df_s4$"total_parent_psych" <- matching_df_s4 |> dplyr::select(dplyr::starts_with("parent")) |> rowSums()
matching_df_s5$"total_parent_psych" <- matching_df_s5 |> dplyr::select(dplyr::starts_with("parent")) |> rowSums()
matching_df_p1$"total_parent_psych" <- matching_df_p1 |> dplyr::select(dplyr::starts_with("parent")) |> rowSums()
matching_df_p2$"total_parent_psych" <- matching_df_p2 |> dplyr::select(dplyr::starts_with("parent")) |> rowSums()
matching_df_p3$"total_parent_psych" <- matching_df_p3 |> dplyr::select(dplyr::starts_with("parent")) |> rowSums()
matching_df_p4$"total_parent_psych" <- matching_df_p4 |> dplyr::select(dplyr::starts_with("parent")) |> rowSums()
matching_df_p5$"total_parent_psych" <- matching_df_p5 |> dplyr::select(dplyr::starts_with("parent")) |> rowSums()

###############################################################################
# Total CBCL
###############################################################################
matching_df_s1$"total_impairments" <- matching_df_s1 |> dplyr::select(dplyr::starts_with("cbcl"), dplyr::starts_with("sds")) |> rowSums()
matching_df_s2$"total_impairments" <- matching_df_s2 |> dplyr::select(dplyr::starts_with("cbcl"), dplyr::starts_with("sds")) |> rowSums()
matching_df_s3$"total_impairments" <- matching_df_s3 |> dplyr::select(dplyr::starts_with("cbcl"), dplyr::starts_with("sds")) |> rowSums()
matching_df_s4$"total_impairments" <- matching_df_s4 |> dplyr::select(dplyr::starts_with("cbcl"), dplyr::starts_with("sds")) |> rowSums()
matching_df_s5$"total_impairments" <- matching_df_s5 |> dplyr::select(dplyr::starts_with("cbcl"), dplyr::starts_with("sds")) |> rowSums()
matching_df_p1$"total_impairments" <- matching_df_p1 |> dplyr::select(dplyr::starts_with("cbcl"), dplyr::starts_with("sds")) |> rowSums()
matching_df_p2$"total_impairments" <- matching_df_p2 |> dplyr::select(dplyr::starts_with("cbcl"), dplyr::starts_with("sds")) |> rowSums()
matching_df_p3$"total_impairments" <- matching_df_p3 |> dplyr::select(dplyr::starts_with("cbcl"), dplyr::starts_with("sds")) |> rowSums()
matching_df_p4$"total_impairments" <- matching_df_p4 |> dplyr::select(dplyr::starts_with("cbcl"), dplyr::starts_with("sds")) |> rowSums()
matching_df_p5$"total_impairments" <- matching_df_p5 |> dplyr::select(dplyr::starts_with("cbcl"), dplyr::starts_with("sds")) |> rowSums()
```

We'll try a few different matching schemes:

```{r}
###############################################################################
# Matching by income, race, parent psych
###############################################################################
matching_results_a_s1 <- matchit(formula(mtbi ~ household_income + race + total_parent_psych), data = matching_df_s1, method = "nearest")
matching_results_a_s2 <- matchit(formula(mtbi ~ household_income + race + total_parent_psych), data = matching_df_s2, method = "nearest")
matching_results_a_s3 <- matchit(formula(mtbi ~ household_income + race + total_parent_psych), data = matching_df_s3, method = "nearest")
matching_results_a_s4 <- matchit(formula(mtbi ~ household_income + race + total_parent_psych), data = matching_df_s4, method = "nearest")
matching_results_a_s5 <- matchit(formula(mtbi ~ household_income + race + total_parent_psych), data = matching_df_s5, method = "nearest")
matching_results_a_p1 <- matchit(formula(mtbi ~ household_income + race + total_parent_psych), data = matching_df_p1, method = "nearest")
matching_results_a_p2 <- matchit(formula(mtbi ~ household_income + race + total_parent_psych), data = matching_df_p2, method = "nearest")
matching_results_a_p3 <- matchit(formula(mtbi ~ household_income + race + total_parent_psych), data = matching_df_p3, method = "nearest")
matching_results_a_p4 <- matchit(formula(mtbi ~ household_income + race + total_parent_psych), data = matching_df_p4, method = "nearest")
matching_results_a_p5 <- matchit(formula(mtbi ~ household_income + race + total_parent_psych), data = matching_df_p5, method = "nearest")

matching_summary_a_s1 <- capture.output(print(summary(matching_results_a_s1)))
matching_summary_a_s2 <- capture.output(print(summary(matching_results_a_s2)))
matching_summary_a_s3 <- capture.output(print(summary(matching_results_a_s3)))
matching_summary_a_s4 <- capture.output(print(summary(matching_results_a_s4)))
matching_summary_a_s5 <- capture.output(print(summary(matching_results_a_s5)))
matching_summary_a_p1 <- capture.output(print(summary(matching_results_a_p1)))
matching_summary_a_p2 <- capture.output(print(summary(matching_results_a_p2)))
matching_summary_a_p3 <- capture.output(print(summary(matching_results_a_p3)))
matching_summary_a_p4 <- capture.output(print(summary(matching_results_a_p4)))
matching_summary_a_p5 <- capture.output(print(summary(matching_results_a_p5)))

matched_data_a_s1 <- match.data(matching_results_a_s1)
matched_data_a_s2 <- match.data(matching_results_a_s2)
matched_data_a_s3 <- match.data(matching_results_a_s3)
matched_data_a_s4 <- match.data(matching_results_a_s4)
matched_data_a_s5 <- match.data(matching_results_a_s5)
matched_data_a_p1 <- match.data(matching_results_a_p1)
matched_data_a_p2 <- match.data(matching_results_a_p2)
matched_data_a_p3 <- match.data(matching_results_a_p3)
matched_data_a_p4 <- match.data(matching_results_a_p4)
matched_data_a_p5 <- match.data(matching_results_a_p5)

###############################################################################
# Matching by demographic variables
###############################################################################
matching_results_b_s1 <- matchit(formula(mtbi ~ household_income + race + sex + pubertal_status_p + pubertal_status_y), data = matching_df_s1, method = "nearest")
matching_results_b_s2 <- matchit(formula(mtbi ~ household_income + race + sex + pubertal_status_p + pubertal_status_y), data = matching_df_s2, method = "nearest")
matching_results_b_s3 <- matchit(formula(mtbi ~ household_income + race + sex + pubertal_status_p + pubertal_status_y), data = matching_df_s3, method = "nearest")
matching_results_b_s4 <- matchit(formula(mtbi ~ household_income + race + sex + pubertal_status_p + pubertal_status_y), data = matching_df_s4, method = "nearest")
matching_results_b_s5 <- matchit(formula(mtbi ~ household_income + race + sex + pubertal_status_p + pubertal_status_y), data = matching_df_s5, method = "nearest")
matching_results_b_p1 <- matchit(formula(mtbi ~ household_income + race + sex + pubertal_status_p + pubertal_status_y), data = matching_df_p1, method = "nearest")
matching_results_b_p2 <- matchit(formula(mtbi ~ household_income + race + sex + pubertal_status_p + pubertal_status_y), data = matching_df_p2, method = "nearest")
matching_results_b_p3 <- matchit(formula(mtbi ~ household_income + race + sex + pubertal_status_p + pubertal_status_y), data = matching_df_p3, method = "nearest")
matching_results_b_p4 <- matchit(formula(mtbi ~ household_income + race + sex + pubertal_status_p + pubertal_status_y), data = matching_df_p4, method = "nearest")
matching_results_b_p5 <- matchit(formula(mtbi ~ household_income + race + sex + pubertal_status_p + pubertal_status_y), data = matching_df_p5, method = "nearest")

matching_summary_b_s1 <- capture.output(print(summary(matching_results_b_s1)))
matching_summary_b_s2 <- capture.output(print(summary(matching_results_b_s2)))
matching_summary_b_s3 <- capture.output(print(summary(matching_results_b_s3)))
matching_summary_b_s4 <- capture.output(print(summary(matching_results_b_s4)))
matching_summary_b_s5 <- capture.output(print(summary(matching_results_b_s5)))
matching_summary_b_p1 <- capture.output(print(summary(matching_results_b_p1)))
matching_summary_b_p2 <- capture.output(print(summary(matching_results_b_p2)))
matching_summary_b_p3 <- capture.output(print(summary(matching_results_b_p3)))
matching_summary_b_p4 <- capture.output(print(summary(matching_results_b_p4)))
matching_summary_b_p5 <- capture.output(print(summary(matching_results_b_p5)))

matched_data_b_s1 <- match.data(matching_results_b_s1)
matched_data_b_s2 <- match.data(matching_results_b_s2)
matched_data_b_s3 <- match.data(matching_results_b_s3)
matched_data_b_s4 <- match.data(matching_results_b_s4)
matched_data_b_s5 <- match.data(matching_results_b_s5)
matched_data_b_p1 <- match.data(matching_results_b_p1)
matched_data_b_p2 <- match.data(matching_results_b_p2)
matched_data_b_p3 <- match.data(matching_results_b_p3)
matched_data_b_p4 <- match.data(matching_results_b_p4)
matched_data_b_p5 <- match.data(matching_results_b_p5)


###############################################################################
# Matching by parent psych alone
###############################################################################
matching_results_c_s1 <- matchit(formula(mtbi ~ total_parent_psych), data = matching_df_s1, method = "nearest")
matching_results_c_s2 <- matchit(formula(mtbi ~ total_parent_psych), data = matching_df_s2, method = "nearest")
matching_results_c_s3 <- matchit(formula(mtbi ~ total_parent_psych), data = matching_df_s3, method = "nearest")
matching_results_c_s4 <- matchit(formula(mtbi ~ total_parent_psych), data = matching_df_s4, method = "nearest")
matching_results_c_s5 <- matchit(formula(mtbi ~ total_parent_psych), data = matching_df_s5, method = "nearest")
matching_results_c_p1 <- matchit(formula(mtbi ~ total_parent_psych), data = matching_df_p1, method = "nearest")
matching_results_c_p2 <- matchit(formula(mtbi ~ total_parent_psych), data = matching_df_p2, method = "nearest")
matching_results_c_p3 <- matchit(formula(mtbi ~ total_parent_psych), data = matching_df_p3, method = "nearest")
matching_results_c_p4 <- matchit(formula(mtbi ~ total_parent_psych), data = matching_df_p4, method = "nearest")
matching_results_c_p5 <- matchit(formula(mtbi ~ total_parent_psych), data = matching_df_p5, method = "nearest")

matching_summary_c_s1 <- capture.output(print(summary(matching_results_c_s1)))
matching_summary_c_s2 <- capture.output(print(summary(matching_results_c_s2)))
matching_summary_c_s3 <- capture.output(print(summary(matching_results_c_s3)))
matching_summary_c_s4 <- capture.output(print(summary(matching_results_c_s4)))
matching_summary_c_s5 <- capture.output(print(summary(matching_results_c_s5)))
matching_summary_c_p1 <- capture.output(print(summary(matching_results_c_p1)))
matching_summary_c_p2 <- capture.output(print(summary(matching_results_c_p2)))
matching_summary_c_p3 <- capture.output(print(summary(matching_results_c_p3)))
matching_summary_c_p4 <- capture.output(print(summary(matching_results_c_p4)))
matching_summary_c_p5 <- capture.output(print(summary(matching_results_c_p5)))

matched_data_c_s1 <- match.data(matching_results_c_s1)
matched_data_c_s2 <- match.data(matching_results_c_s2)
matched_data_c_s3 <- match.data(matching_results_c_s3)
matched_data_c_s4 <- match.data(matching_results_c_s4)
matched_data_c_s5 <- match.data(matching_results_c_s5)
matched_data_c_p1 <- match.data(matching_results_c_p1)
matched_data_c_p2 <- match.data(matching_results_c_p2)
matched_data_c_p3 <- match.data(matching_results_c_p3)
matched_data_c_p4 <- match.data(matching_results_c_p4)
matched_data_c_p5 <- match.data(matching_results_c_p5)

###############################################################################
# Matching by CBCL alone
###############################################################################
matching_results_d_s1 <- matchit(formula(mtbi ~ total_impairments), data = matching_df_s1, method = "nearest")
matching_results_d_s2 <- matchit(formula(mtbi ~ total_impairments), data = matching_df_s2, method = "nearest")
matching_results_d_s3 <- matchit(formula(mtbi ~ total_impairments), data = matching_df_s3, method = "nearest")
matching_results_d_s4 <- matchit(formula(mtbi ~ total_impairments), data = matching_df_s4, method = "nearest")
matching_results_d_s5 <- matchit(formula(mtbi ~ total_impairments), data = matching_df_s5, method = "nearest")
matching_results_d_p1 <- matchit(formula(mtbi ~ total_impairments), data = matching_df_p1, method = "nearest")
matching_results_d_p2 <- matchit(formula(mtbi ~ total_impairments), data = matching_df_p2, method = "nearest")
matching_results_d_p3 <- matchit(formula(mtbi ~ total_impairments), data = matching_df_p3, method = "nearest")
matching_results_d_p4 <- matchit(formula(mtbi ~ total_impairments), data = matching_df_p4, method = "nearest")
matching_results_d_p5 <- matchit(formula(mtbi ~ total_impairments), data = matching_df_p5, method = "nearest")

matching_summary_d_s1 <- capture.output(print(summary(matching_results_d_s1)))
matching_summary_d_s2 <- capture.output(print(summary(matching_results_d_s2)))
matching_summary_d_s3 <- capture.output(print(summary(matching_results_d_s3)))
matching_summary_d_s4 <- capture.output(print(summary(matching_results_d_s4)))
matching_summary_d_s5 <- capture.output(print(summary(matching_results_d_s5)))
matching_summary_d_p1 <- capture.output(print(summary(matching_results_d_p1)))
matching_summary_d_p2 <- capture.output(print(summary(matching_results_d_p2)))
matching_summary_d_p3 <- capture.output(print(summary(matching_results_d_p3)))
matching_summary_d_p4 <- capture.output(print(summary(matching_results_d_p4)))
matching_summary_d_p5 <- capture.output(print(summary(matching_results_d_p5)))

matched_data_d_s1 <- match.data(matching_results_d_s1)
matched_data_d_s2 <- match.data(matching_results_d_s2)
matched_data_d_s3 <- match.data(matching_results_d_s3)
matched_data_d_s4 <- match.data(matching_results_d_s4)
matched_data_d_s5 <- match.data(matching_results_d_s5)
matched_data_d_p1 <- match.data(matching_results_d_p1)
matched_data_d_p2 <- match.data(matching_results_d_p2)
matched_data_d_p3 <- match.data(matching_results_d_p3)
matched_data_d_p4 <- match.data(matching_results_d_p4)
matched_data_d_p5 <- match.data(matching_results_d_p5)

saveRDS(matching_summary_a_s1, proc_path("matching_summary_a_s1.rds", TRUE))
saveRDS(matching_summary_a_s2, proc_path("matching_summary_a_s2.rds", TRUE))
saveRDS(matching_summary_a_s3, proc_path("matching_summary_a_s3.rds", TRUE))
saveRDS(matching_summary_a_s4, proc_path("matching_summary_a_s4.rds", TRUE))
saveRDS(matching_summary_a_s5, proc_path("matching_summary_a_s5.rds", TRUE))
saveRDS(matching_summary_a_p1, proc_path("matching_summary_a_p1.rds", TRUE))
saveRDS(matching_summary_a_p2, proc_path("matching_summary_a_p2.rds", TRUE))
saveRDS(matching_summary_a_p3, proc_path("matching_summary_a_p3.rds", TRUE))
saveRDS(matching_summary_a_p4, proc_path("matching_summary_a_p4.rds", TRUE))
saveRDS(matching_summary_a_p5, proc_path("matching_summary_a_p5.rds", TRUE))
saveRDS(matching_summary_b_s1, proc_path("matching_summary_b_s1.rds", TRUE))
saveRDS(matching_summary_b_s2, proc_path("matching_summary_b_s2.rds", TRUE))
saveRDS(matching_summary_b_s3, proc_path("matching_summary_b_s3.rds", TRUE))
saveRDS(matching_summary_b_s4, proc_path("matching_summary_b_s4.rds", TRUE))
saveRDS(matching_summary_b_s5, proc_path("matching_summary_b_s5.rds", TRUE))
saveRDS(matching_summary_b_p1, proc_path("matching_summary_b_p1.rds", TRUE))
saveRDS(matching_summary_b_p2, proc_path("matching_summary_b_p2.rds", TRUE))
saveRDS(matching_summary_b_p3, proc_path("matching_summary_b_p3.rds", TRUE))
saveRDS(matching_summary_b_p4, proc_path("matching_summary_b_p4.rds", TRUE))
saveRDS(matching_summary_b_p5, proc_path("matching_summary_b_p5.rds", TRUE))
saveRDS(matching_summary_c_s1, proc_path("matching_summary_c_s1.rds", TRUE))
saveRDS(matching_summary_c_s2, proc_path("matching_summary_c_s2.rds", TRUE))
saveRDS(matching_summary_c_s3, proc_path("matching_summary_c_s3.rds", TRUE))
saveRDS(matching_summary_c_s4, proc_path("matching_summary_c_s4.rds", TRUE))
saveRDS(matching_summary_c_s5, proc_path("matching_summary_c_s5.rds", TRUE))
saveRDS(matching_summary_c_p1, proc_path("matching_summary_c_p1.rds", TRUE))
saveRDS(matching_summary_c_p2, proc_path("matching_summary_c_p2.rds", TRUE))
saveRDS(matching_summary_c_p3, proc_path("matching_summary_c_p3.rds", TRUE))
saveRDS(matching_summary_c_p4, proc_path("matching_summary_c_p4.rds", TRUE))
saveRDS(matching_summary_c_p5, proc_path("matching_summary_c_p5.rds", TRUE))
saveRDS(matching_summary_d_s1, proc_path("matching_summary_d_s1.rds", TRUE))
saveRDS(matching_summary_d_s2, proc_path("matching_summary_d_s2.rds", TRUE))
saveRDS(matching_summary_d_s3, proc_path("matching_summary_d_s3.rds", TRUE))
saveRDS(matching_summary_d_s4, proc_path("matching_summary_d_s4.rds", TRUE))
saveRDS(matching_summary_d_s5, proc_path("matching_summary_d_s5.rds", TRUE))
saveRDS(matching_summary_d_p1, proc_path("matching_summary_d_p1.rds", TRUE))
saveRDS(matching_summary_d_p2, proc_path("matching_summary_d_p2.rds", TRUE))
saveRDS(matching_summary_d_p3, proc_path("matching_summary_d_p3.rds", TRUE))
saveRDS(matching_summary_d_p4, proc_path("matching_summary_d_p4.rds", TRUE))
saveRDS(matching_summary_d_p5, proc_path("matching_summary_d_p5.rds", TRUE))
```

```{r}
## CHECKPOINT
#matching_summary_1_imp_1 <- readRDS(proc_path("2024_09_13_matching_summary_1_imp_1.rds"))
#matching_summary_2_imp_1 <- readRDS(proc_path("2024_09_13_matching_summary_2_imp_1.rds"))
#matching_summary_3_imp_1 <- readRDS(proc_path("2024_09_13_matching_summary_3_imp_1.rds"))
#matching_summary_4_imp_1 <- readRDS(proc_path("2024_09_13_matching_summary_4_imp_1.rds"))

#grDevices::png(filename = fig_path("matching_results_1_imp_1.png", TRUE), width = 1000, height = 500, res = 100)
#plot(matching_results_1_imp_1, type = "density", interactive = FALSE)
#grDevices::dev.off()
#
#grDevices::png(filename = fig_path("matching_results_2_imp_1.png", TRUE), width = 1000, height = 500, res = 100)
#plot(matching_results_2_imp_1, type = "density", interactive = FALSE)
#grDevices::dev.off()
#
#grDevices::png(filename = fig_path("matching_results_3_imp_1.png", TRUE), width = 1000, height = 500, res = 100)
#plot(matching_results_3_imp_1, type = "density", interactive = FALSE)
#grDevices::dev.off()
#
#grDevices::png(filename = fig_path("matching_results_4_imp_1.png", TRUE), width = 1000, height = 500, res = 100)
#plot(matching_results_4_imp_1, type = "density", interactive = FALSE)
#grDevices::dev.off()
```

```{r}
matched_uninj_a_s1 <- dplyr::filter(matched_data_a_s1, mtbi == 0)$"subjectkey"
matched_uninj_a_s2 <- dplyr::filter(matched_data_a_s2, mtbi == 0)$"subjectkey"
matched_uninj_a_s3 <- dplyr::filter(matched_data_a_s3, mtbi == 0)$"subjectkey"
matched_uninj_a_s4 <- dplyr::filter(matched_data_a_s4, mtbi == 0)$"subjectkey"
matched_uninj_a_s5 <- dplyr::filter(matched_data_a_s5, mtbi == 0)$"subjectkey"
matched_uninj_a_p1 <- dplyr::filter(matched_data_a_p1, mtbi == 0)$"subjectkey"
matched_uninj_a_p2 <- dplyr::filter(matched_data_a_p2, mtbi == 0)$"subjectkey"
matched_uninj_a_p3 <- dplyr::filter(matched_data_a_p3, mtbi == 0)$"subjectkey"
matched_uninj_a_p4 <- dplyr::filter(matched_data_a_p4, mtbi == 0)$"subjectkey"
matched_uninj_a_p5 <- dplyr::filter(matched_data_a_p5, mtbi == 0)$"subjectkey"
matched_uninj_b_s1 <- dplyr::filter(matched_data_b_s1, mtbi == 0)$"subjectkey"
matched_uninj_b_s2 <- dplyr::filter(matched_data_b_s2, mtbi == 0)$"subjectkey"
matched_uninj_b_s3 <- dplyr::filter(matched_data_b_s3, mtbi == 0)$"subjectkey"
matched_uninj_b_s4 <- dplyr::filter(matched_data_b_s4, mtbi == 0)$"subjectkey"
matched_uninj_b_s5 <- dplyr::filter(matched_data_b_s5, mtbi == 0)$"subjectkey"
matched_uninj_b_p1 <- dplyr::filter(matched_data_b_p1, mtbi == 0)$"subjectkey"
matched_uninj_b_p2 <- dplyr::filter(matched_data_b_p2, mtbi == 0)$"subjectkey"
matched_uninj_b_p3 <- dplyr::filter(matched_data_b_p3, mtbi == 0)$"subjectkey"
matched_uninj_b_p4 <- dplyr::filter(matched_data_b_p4, mtbi == 0)$"subjectkey"
matched_uninj_b_p5 <- dplyr::filter(matched_data_b_p5, mtbi == 0)$"subjectkey"
matched_uninj_c_s1 <- dplyr::filter(matched_data_c_s1, mtbi == 0)$"subjectkey"
matched_uninj_c_s2 <- dplyr::filter(matched_data_c_s2, mtbi == 0)$"subjectkey"
matched_uninj_c_s3 <- dplyr::filter(matched_data_c_s3, mtbi == 0)$"subjectkey"
matched_uninj_c_s4 <- dplyr::filter(matched_data_c_s4, mtbi == 0)$"subjectkey"
matched_uninj_c_s5 <- dplyr::filter(matched_data_c_s5, mtbi == 0)$"subjectkey"
matched_uninj_c_p1 <- dplyr::filter(matched_data_c_p1, mtbi == 0)$"subjectkey"
matched_uninj_c_p2 <- dplyr::filter(matched_data_c_p2, mtbi == 0)$"subjectkey"
matched_uninj_c_p3 <- dplyr::filter(matched_data_c_p3, mtbi == 0)$"subjectkey"
matched_uninj_c_p4 <- dplyr::filter(matched_data_c_p4, mtbi == 0)$"subjectkey"
matched_uninj_c_p5 <- dplyr::filter(matched_data_c_p5, mtbi == 0)$"subjectkey"
matched_uninj_d_s1 <- dplyr::filter(matched_data_d_s1, mtbi == 0)$"subjectkey"
matched_uninj_d_s2 <- dplyr::filter(matched_data_d_s2, mtbi == 0)$"subjectkey"
matched_uninj_d_s3 <- dplyr::filter(matched_data_d_s3, mtbi == 0)$"subjectkey"
matched_uninj_d_s4 <- dplyr::filter(matched_data_d_s4, mtbi == 0)$"subjectkey"
matched_uninj_d_s5 <- dplyr::filter(matched_data_d_s5, mtbi == 0)$"subjectkey"
matched_uninj_d_p1 <- dplyr::filter(matched_data_d_p1, mtbi == 0)$"subjectkey"
matched_uninj_d_p2 <- dplyr::filter(matched_data_d_p2, mtbi == 0)$"subjectkey"
matched_uninj_d_p3 <- dplyr::filter(matched_data_d_p3, mtbi == 0)$"subjectkey"
matched_uninj_d_p4 <- dplyr::filter(matched_data_d_p4, mtbi == 0)$"subjectkey"
matched_uninj_d_p5 <- dplyr::filter(matched_data_d_p5, mtbi == 0)$"subjectkey"

# Extract the control group from the matched data
write_csv(data.frame(subjectkey = matched_uninj_a_s1), sub_path("matched_uninj_a_s1.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_a_s2), sub_path("matched_uninj_a_s2.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_a_s3), sub_path("matched_uninj_a_s3.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_a_s4), sub_path("matched_uninj_a_s4.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_a_s5), sub_path("matched_uninj_a_s5.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_a_p1), sub_path("matched_uninj_a_p1.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_a_p2), sub_path("matched_uninj_a_p2.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_a_p3), sub_path("matched_uninj_a_p3.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_a_p4), sub_path("matched_uninj_a_p4.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_a_p5), sub_path("matched_uninj_a_p5.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_b_s1), sub_path("matched_uninj_b_s1.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_b_s2), sub_path("matched_uninj_b_s2.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_b_s3), sub_path("matched_uninj_b_s3.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_b_s4), sub_path("matched_uninj_b_s4.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_b_s5), sub_path("matched_uninj_b_s5.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_b_p1), sub_path("matched_uninj_b_p1.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_b_p2), sub_path("matched_uninj_b_p2.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_b_p3), sub_path("matched_uninj_b_p3.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_b_p4), sub_path("matched_uninj_b_p4.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_b_p5), sub_path("matched_uninj_b_p5.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_c_s1), sub_path("matched_uninj_c_s1.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_c_s2), sub_path("matched_uninj_c_s2.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_c_s3), sub_path("matched_uninj_c_s3.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_c_s4), sub_path("matched_uninj_c_s4.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_c_s5), sub_path("matched_uninj_c_s5.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_c_p1), sub_path("matched_uninj_c_p1.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_c_p2), sub_path("matched_uninj_c_p2.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_c_p3), sub_path("matched_uninj_c_p3.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_c_p4), sub_path("matched_uninj_c_p4.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_c_p5), sub_path("matched_uninj_c_p5.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_d_s1), sub_path("matched_uninj_d_s1.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_d_s2), sub_path("matched_uninj_d_s2.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_d_s3), sub_path("matched_uninj_d_s3.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_d_s4), sub_path("matched_uninj_d_s4.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_d_s5), sub_path("matched_uninj_d_s5.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_d_p1), sub_path("matched_uninj_d_p1.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_d_p2), sub_path("matched_uninj_d_p2.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_d_p3), sub_path("matched_uninj_d_p3.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_d_p4), sub_path("matched_uninj_d_p4.csv", TRUE))
write_csv(data.frame(subjectkey = matched_uninj_d_p5), sub_path("matched_uninj_d_p5.csv", TRUE))
```

```{r}
matched_uninj_a_s1 <- read_subjects(sub_path("2024_09_13_matched_uninj_a_s1.csv"))
matched_uninj_a_s2 <- read_subjects(sub_path("2024_09_13_matched_uninj_a_s2.csv"))
matched_uninj_a_s3 <- read_subjects(sub_path("2024_09_13_matched_uninj_a_s3.csv"))
matched_uninj_a_s4 <- read_subjects(sub_path("2024_09_13_matched_uninj_a_s4.csv"))
matched_uninj_a_s5 <- read_subjects(sub_path("2024_09_13_matched_uninj_a_s5.csv"))
matched_uninj_a_p1 <- read_subjects(sub_path("2024_09_13_matched_uninj_a_p1.csv"))
matched_uninj_a_p2 <- read_subjects(sub_path("2024_09_13_matched_uninj_a_p2.csv"))
matched_uninj_a_p3 <- read_subjects(sub_path("2024_09_13_matched_uninj_a_p3.csv"))
matched_uninj_a_p4 <- read_subjects(sub_path("2024_09_13_matched_uninj_a_p4.csv"))
matched_uninj_a_p5 <- read_subjects(sub_path("2024_09_13_matched_uninj_a_p5.csv"))
matched_uninj_b_s1 <- read_subjects(sub_path("2024_09_13_matched_uninj_b_s1.csv"))
matched_uninj_b_s2 <- read_subjects(sub_path("2024_09_13_matched_uninj_b_s2.csv"))
matched_uninj_b_s3 <- read_subjects(sub_path("2024_09_13_matched_uninj_b_s3.csv"))
matched_uninj_b_s4 <- read_subjects(sub_path("2024_09_13_matched_uninj_b_s4.csv"))
matched_uninj_b_s5 <- read_subjects(sub_path("2024_09_13_matched_uninj_b_s5.csv"))
matched_uninj_b_p1 <- read_subjects(sub_path("2024_09_13_matched_uninj_b_p1.csv"))
matched_uninj_b_p2 <- read_subjects(sub_path("2024_09_13_matched_uninj_b_p2.csv"))
matched_uninj_b_p3 <- read_subjects(sub_path("2024_09_13_matched_uninj_b_p3.csv"))
matched_uninj_b_p4 <- read_subjects(sub_path("2024_09_13_matched_uninj_b_p4.csv"))
matched_uninj_b_p5 <- read_subjects(sub_path("2024_09_13_matched_uninj_b_p5.csv"))
matched_uninj_c_s1 <- read_subjects(sub_path("2024_09_13_matched_uninj_c_s1.csv"))
matched_uninj_c_s2 <- read_subjects(sub_path("2024_09_13_matched_uninj_c_s2.csv"))
matched_uninj_c_s3 <- read_subjects(sub_path("2024_09_13_matched_uninj_c_s3.csv"))
matched_uninj_c_s4 <- read_subjects(sub_path("2024_09_13_matched_uninj_c_s4.csv"))
matched_uninj_c_s5 <- read_subjects(sub_path("2024_09_13_matched_uninj_c_s5.csv"))
matched_uninj_c_p1 <- read_subjects(sub_path("2024_09_13_matched_uninj_c_p1.csv"))
matched_uninj_c_p2 <- read_subjects(sub_path("2024_09_13_matched_uninj_c_p2.csv"))
matched_uninj_c_p3 <- read_subjects(sub_path("2024_09_13_matched_uninj_c_p3.csv"))
matched_uninj_c_p4 <- read_subjects(sub_path("2024_09_13_matched_uninj_c_p4.csv"))
matched_uninj_c_p5 <- read_subjects(sub_path("2024_09_13_matched_uninj_c_p5.csv"))
matched_uninj_d_s1 <- read_subjects(sub_path("2024_09_13_matched_uninj_d_s1.csv"))
matched_uninj_d_s2 <- read_subjects(sub_path("2024_09_13_matched_uninj_d_s2.csv"))
matched_uninj_d_s3 <- read_subjects(sub_path("2024_09_13_matched_uninj_d_s3.csv"))
matched_uninj_d_s4 <- read_subjects(sub_path("2024_09_13_matched_uninj_d_s4.csv"))
matched_uninj_d_s5 <- read_subjects(sub_path("2024_09_13_matched_uninj_d_s5.csv"))
matched_uninj_d_p1 <- read_subjects(sub_path("2024_09_13_matched_uninj_d_p1.csv"))
matched_uninj_d_p2 <- read_subjects(sub_path("2024_09_13_matched_uninj_d_p2.csv"))
matched_uninj_d_p3 <- read_subjects(sub_path("2024_09_13_matched_uninj_d_p3.csv"))
matched_uninj_d_p4 <- read_subjects(sub_path("2024_09_13_matched_uninj_d_p4.csv"))
matched_uninj_d_p5 <- read_subjects(sub_path("2024_09_13_matched_uninj_d_p5.csv"))

sub_list <- list(
    "a_s1" = matched_uninj_a_s1,
    "a_s2" = matched_uninj_a_s2,
    "a_s3" = matched_uninj_a_s3,
    "a_s4" = matched_uninj_a_s4,
    "a_s5" = matched_uninj_a_s5,
    "a_p1" = matched_uninj_a_p1,
    "a_p2" = matched_uninj_a_p2,
    "a_p3" = matched_uninj_a_p3,
    "a_p4" = matched_uninj_a_p4,
    "a_p5" = matched_uninj_a_p5,
    "b_s1" = matched_uninj_b_s1,
    "b_s2" = matched_uninj_b_s2,
    "b_s3" = matched_uninj_b_s3,
    "b_s4" = matched_uninj_b_s4,
    "b_s5" = matched_uninj_b_s5,
    "b_p1" = matched_uninj_b_p1,
    "b_p2" = matched_uninj_b_p2,
    "b_p3" = matched_uninj_b_p3,
    "b_p4" = matched_uninj_b_p4,
    "b_p5" = matched_uninj_b_p5,
    "c_s1" = matched_uninj_c_s1,
    "c_s2" = matched_uninj_c_s2,
    "c_s3" = matched_uninj_c_s3,
    "c_s4" = matched_uninj_c_s4,
    "c_s5" = matched_uninj_c_s5,
    "c_p1" = matched_uninj_c_p1,
    "c_p2" = matched_uninj_c_p2,
    "c_p3" = matched_uninj_c_p3,
    "c_p4" = matched_uninj_c_p4,
    "c_p5" = matched_uninj_c_p5,
    "d_s1" = matched_uninj_d_s1,
    "d_s2" = matched_uninj_d_s2,
    "d_s3" = matched_uninj_d_s3,
    "d_s4" = matched_uninj_d_s4,
    "d_s5" = matched_uninj_d_s5,
    "d_p1" = matched_uninj_d_p1,
    "d_p2" = matched_uninj_d_p2,
    "d_p3" = matched_uninj_d_p3,
    "d_p4" = matched_uninj_d_p4,
    "d_p5" = matched_uninj_d_p5
)
```

## Subsetting matched uninjured data and out of model lists

```{r}
subject_filter_dl <- function(data_list, subject_vector) {
    data_list <- data_list |>
        lapply(
            function(x) {
                keep_subs <- x$"data"$"subjectkey" %in% subject_vector
                x$"data" <- x$"data"[keep_subs, ]
                return(x)
            }
        )
    return(data_list)
}

matched_uninj_dl_a_s1 <- subject_filter_dl(uninj_dl_s1, matched_uninj_a_s1)
matched_uninj_dl_a_s2 <- subject_filter_dl(uninj_dl_s2, matched_uninj_a_s2)
matched_uninj_dl_a_s3 <- subject_filter_dl(uninj_dl_s3, matched_uninj_a_s3)
matched_uninj_dl_a_s4 <- subject_filter_dl(uninj_dl_s4, matched_uninj_a_s4)
matched_uninj_dl_a_s5 <- subject_filter_dl(uninj_dl_s5, matched_uninj_a_s5)
matched_uninj_dl_a_p1 <- subject_filter_dl(uninj_dl_p1, matched_uninj_a_p1)
matched_uninj_dl_a_p2 <- subject_filter_dl(uninj_dl_p2, matched_uninj_a_p2)
matched_uninj_dl_a_p3 <- subject_filter_dl(uninj_dl_p3, matched_uninj_a_p3)
matched_uninj_dl_a_p4 <- subject_filter_dl(uninj_dl_p4, matched_uninj_a_p4)
matched_uninj_dl_a_p5 <- subject_filter_dl(uninj_dl_p5, matched_uninj_a_p5)
matched_uninj_ol_a_s1 <- subject_filter_dl(uninj_ol_s1, matched_uninj_a_s1)
matched_uninj_ol_a_s2 <- subject_filter_dl(uninj_ol_s2, matched_uninj_a_s2)
matched_uninj_ol_a_s3 <- subject_filter_dl(uninj_ol_s3, matched_uninj_a_s3)
matched_uninj_ol_a_s4 <- subject_filter_dl(uninj_ol_s4, matched_uninj_a_s4)
matched_uninj_ol_a_s5 <- subject_filter_dl(uninj_ol_s5, matched_uninj_a_s5)
matched_uninj_ol_a_p1 <- subject_filter_dl(uninj_ol_p1, matched_uninj_a_p1)
matched_uninj_ol_a_p2 <- subject_filter_dl(uninj_ol_p2, matched_uninj_a_p2)
matched_uninj_ol_a_p3 <- subject_filter_dl(uninj_ol_p3, matched_uninj_a_p3)
matched_uninj_ol_a_p4 <- subject_filter_dl(uninj_ol_p4, matched_uninj_a_p4)
matched_uninj_ol_a_p5 <- subject_filter_dl(uninj_ol_p5, matched_uninj_a_p5)

matched_uninj_dl_b_s1 <- subject_filter_dl(uninj_dl_s1, matched_uninj_b_s1)
matched_uninj_dl_b_s2 <- subject_filter_dl(uninj_dl_s2, matched_uninj_b_s2)
matched_uninj_dl_b_s3 <- subject_filter_dl(uninj_dl_s3, matched_uninj_b_s3)
matched_uninj_dl_b_s4 <- subject_filter_dl(uninj_dl_s4, matched_uninj_b_s4)
matched_uninj_dl_b_s5 <- subject_filter_dl(uninj_dl_s5, matched_uninj_b_s5)
matched_uninj_dl_b_p1 <- subject_filter_dl(uninj_dl_p1, matched_uninj_b_p1)
matched_uninj_dl_b_p2 <- subject_filter_dl(uninj_dl_p2, matched_uninj_b_p2)
matched_uninj_dl_b_p3 <- subject_filter_dl(uninj_dl_p3, matched_uninj_b_p3)
matched_uninj_dl_b_p4 <- subject_filter_dl(uninj_dl_p4, matched_uninj_b_p4)
matched_uninj_dl_b_p5 <- subject_filter_dl(uninj_dl_p5, matched_uninj_b_p5)
matched_uninj_ol_b_s1 <- subject_filter_dl(uninj_ol_s1, matched_uninj_b_s1)
matched_uninj_ol_b_s2 <- subject_filter_dl(uninj_ol_s2, matched_uninj_b_s2)
matched_uninj_ol_b_s3 <- subject_filter_dl(uninj_ol_s3, matched_uninj_b_s3)
matched_uninj_ol_b_s4 <- subject_filter_dl(uninj_ol_s4, matched_uninj_b_s4)
matched_uninj_ol_b_s5 <- subject_filter_dl(uninj_ol_s5, matched_uninj_b_s5)
matched_uninj_ol_b_p1 <- subject_filter_dl(uninj_ol_p1, matched_uninj_b_p1)
matched_uninj_ol_b_p2 <- subject_filter_dl(uninj_ol_p2, matched_uninj_b_p2)
matched_uninj_ol_b_p3 <- subject_filter_dl(uninj_ol_p3, matched_uninj_b_p3)
matched_uninj_ol_b_p4 <- subject_filter_dl(uninj_ol_p4, matched_uninj_b_p4)
matched_uninj_ol_b_p5 <- subject_filter_dl(uninj_ol_p5, matched_uninj_b_p5)

matched_uninj_dl_c_s1 <- subject_filter_dl(uninj_dl_s1, matched_uninj_c_s1)
matched_uninj_dl_c_s2 <- subject_filter_dl(uninj_dl_s2, matched_uninj_c_s2)
matched_uninj_dl_c_s3 <- subject_filter_dl(uninj_dl_s3, matched_uninj_c_s3)
matched_uninj_dl_c_s4 <- subject_filter_dl(uninj_dl_s4, matched_uninj_c_s4)
matched_uninj_dl_c_s5 <- subject_filter_dl(uninj_dl_s5, matched_uninj_c_s5)
matched_uninj_dl_c_p1 <- subject_filter_dl(uninj_dl_p1, matched_uninj_c_p1)
matched_uninj_dl_c_p2 <- subject_filter_dl(uninj_dl_p2, matched_uninj_c_p2)
matched_uninj_dl_c_p3 <- subject_filter_dl(uninj_dl_p3, matched_uninj_c_p3)
matched_uninj_dl_c_p4 <- subject_filter_dl(uninj_dl_p4, matched_uninj_c_p4)
matched_uninj_dl_c_p5 <- subject_filter_dl(uninj_dl_p5, matched_uninj_c_p5)
matched_uninj_ol_c_s1 <- subject_filter_dl(uninj_ol_s1, matched_uninj_c_s1)
matched_uninj_ol_c_s2 <- subject_filter_dl(uninj_ol_s2, matched_uninj_c_s2)
matched_uninj_ol_c_s3 <- subject_filter_dl(uninj_ol_s3, matched_uninj_c_s3)
matched_uninj_ol_c_s4 <- subject_filter_dl(uninj_ol_s4, matched_uninj_c_s4)
matched_uninj_ol_c_s5 <- subject_filter_dl(uninj_ol_s5, matched_uninj_c_s5)
matched_uninj_ol_c_p1 <- subject_filter_dl(uninj_ol_p1, matched_uninj_c_p1)
matched_uninj_ol_c_p2 <- subject_filter_dl(uninj_ol_p2, matched_uninj_c_p2)
matched_uninj_ol_c_p3 <- subject_filter_dl(uninj_ol_p3, matched_uninj_c_p3)
matched_uninj_ol_c_p4 <- subject_filter_dl(uninj_ol_p4, matched_uninj_c_p4)
matched_uninj_ol_c_p5 <- subject_filter_dl(uninj_ol_p5, matched_uninj_c_p5)

matched_uninj_dl_d_s1 <- subject_filter_dl(uninj_dl_s1, matched_uninj_d_s1)
matched_uninj_dl_d_s2 <- subject_filter_dl(uninj_dl_s2, matched_uninj_d_s2)
matched_uninj_dl_d_s3 <- subject_filter_dl(uninj_dl_s3, matched_uninj_d_s3)
matched_uninj_dl_d_s4 <- subject_filter_dl(uninj_dl_s4, matched_uninj_d_s4)
matched_uninj_dl_d_s5 <- subject_filter_dl(uninj_dl_s5, matched_uninj_d_s5)
matched_uninj_dl_d_p1 <- subject_filter_dl(uninj_dl_p1, matched_uninj_d_p1)
matched_uninj_dl_d_p2 <- subject_filter_dl(uninj_dl_p2, matched_uninj_d_p2)
matched_uninj_dl_d_p3 <- subject_filter_dl(uninj_dl_p3, matched_uninj_d_p3)
matched_uninj_dl_d_p4 <- subject_filter_dl(uninj_dl_p4, matched_uninj_d_p4)
matched_uninj_dl_d_p5 <- subject_filter_dl(uninj_dl_p5, matched_uninj_d_p5)
matched_uninj_ol_d_s1 <- subject_filter_dl(uninj_ol_s1, matched_uninj_d_s1)
matched_uninj_ol_d_s2 <- subject_filter_dl(uninj_ol_s2, matched_uninj_d_s2)
matched_uninj_ol_d_s3 <- subject_filter_dl(uninj_ol_s3, matched_uninj_d_s3)
matched_uninj_ol_d_s4 <- subject_filter_dl(uninj_ol_s4, matched_uninj_d_s4)
matched_uninj_ol_d_s5 <- subject_filter_dl(uninj_ol_s5, matched_uninj_d_s5)
matched_uninj_ol_d_p1 <- subject_filter_dl(uninj_ol_p1, matched_uninj_d_p1)
matched_uninj_ol_d_p2 <- subject_filter_dl(uninj_ol_p2, matched_uninj_d_p2)
matched_uninj_ol_d_p3 <- subject_filter_dl(uninj_ol_p3, matched_uninj_d_p3)
matched_uninj_ol_d_p4 <- subject_filter_dl(uninj_ol_p4, matched_uninj_d_p4)
matched_uninj_ol_d_p5 <- subject_filter_dl(uninj_ol_p5, matched_uninj_d_p5)

###############################################################################

list.save(matched_uninj_dl_a_s1, proc_path("matched_uninj_dl_a_s1.rds", TRUE))
list.save(matched_uninj_dl_a_s2, proc_path("matched_uninj_dl_a_s2.rds", TRUE))
list.save(matched_uninj_dl_a_s3, proc_path("matched_uninj_dl_a_s3.rds", TRUE))
list.save(matched_uninj_dl_a_s4, proc_path("matched_uninj_dl_a_s4.rds", TRUE))
list.save(matched_uninj_dl_a_s5, proc_path("matched_uninj_dl_a_s5.rds", TRUE))
list.save(matched_uninj_dl_a_p1, proc_path("matched_uninj_dl_a_p1.rds", TRUE))
list.save(matched_uninj_dl_a_p2, proc_path("matched_uninj_dl_a_p2.rds", TRUE))
list.save(matched_uninj_dl_a_p3, proc_path("matched_uninj_dl_a_p3.rds", TRUE))
list.save(matched_uninj_dl_a_p4, proc_path("matched_uninj_dl_a_p4.rds", TRUE))
list.save(matched_uninj_dl_a_p5, proc_path("matched_uninj_dl_a_p5.rds", TRUE))
list.save(matched_uninj_ol_a_s1, proc_path("matched_uninj_ol_a_s1.rds", TRUE))
list.save(matched_uninj_ol_a_s2, proc_path("matched_uninj_ol_a_s2.rds", TRUE))
list.save(matched_uninj_ol_a_s3, proc_path("matched_uninj_ol_a_s3.rds", TRUE))
list.save(matched_uninj_ol_a_s4, proc_path("matched_uninj_ol_a_s4.rds", TRUE))
list.save(matched_uninj_ol_a_s5, proc_path("matched_uninj_ol_a_s5.rds", TRUE))
list.save(matched_uninj_ol_a_p1, proc_path("matched_uninj_ol_a_p1.rds", TRUE))
list.save(matched_uninj_ol_a_p2, proc_path("matched_uninj_ol_a_p2.rds", TRUE))
list.save(matched_uninj_ol_a_p3, proc_path("matched_uninj_ol_a_p3.rds", TRUE))
list.save(matched_uninj_ol_a_p4, proc_path("matched_uninj_ol_a_p4.rds", TRUE))
list.save(matched_uninj_ol_a_p5, proc_path("matched_uninj_ol_a_p5.rds", TRUE))
list.save(matched_uninj_dl_b_s1, proc_path("matched_uninj_dl_b_s1.rds", TRUE))
list.save(matched_uninj_dl_b_s2, proc_path("matched_uninj_dl_b_s2.rds", TRUE))
list.save(matched_uninj_dl_b_s3, proc_path("matched_uninj_dl_b_s3.rds", TRUE))
list.save(matched_uninj_dl_b_s4, proc_path("matched_uninj_dl_b_s4.rds", TRUE))
list.save(matched_uninj_dl_b_s5, proc_path("matched_uninj_dl_b_s5.rds", TRUE))
list.save(matched_uninj_dl_b_p1, proc_path("matched_uninj_dl_b_p1.rds", TRUE))
list.save(matched_uninj_dl_b_p2, proc_path("matched_uninj_dl_b_p2.rds", TRUE))
list.save(matched_uninj_dl_b_p3, proc_path("matched_uninj_dl_b_p3.rds", TRUE))
list.save(matched_uninj_dl_b_p4, proc_path("matched_uninj_dl_b_p4.rds", TRUE))
list.save(matched_uninj_dl_b_p5, proc_path("matched_uninj_dl_b_p5.rds", TRUE))
list.save(matched_uninj_ol_b_s1, proc_path("matched_uninj_ol_b_s1.rds", TRUE))
list.save(matched_uninj_ol_b_s2, proc_path("matched_uninj_ol_b_s2.rds", TRUE))
list.save(matched_uninj_ol_b_s3, proc_path("matched_uninj_ol_b_s3.rds", TRUE))
list.save(matched_uninj_ol_b_s4, proc_path("matched_uninj_ol_b_s4.rds", TRUE))
list.save(matched_uninj_ol_b_s5, proc_path("matched_uninj_ol_b_s5.rds", TRUE))
list.save(matched_uninj_ol_b_p1, proc_path("matched_uninj_ol_b_p1.rds", TRUE))
list.save(matched_uninj_ol_b_p2, proc_path("matched_uninj_ol_b_p2.rds", TRUE))
list.save(matched_uninj_ol_b_p3, proc_path("matched_uninj_ol_b_p3.rds", TRUE))
list.save(matched_uninj_ol_b_p4, proc_path("matched_uninj_ol_b_p4.rds", TRUE))
list.save(matched_uninj_ol_b_p5, proc_path("matched_uninj_ol_b_p5.rds", TRUE))
list.save(matched_uninj_dl_c_s1, proc_path("matched_uninj_dl_c_s1.rds", TRUE))
list.save(matched_uninj_dl_c_s2, proc_path("matched_uninj_dl_c_s2.rds", TRUE))
list.save(matched_uninj_dl_c_s3, proc_path("matched_uninj_dl_c_s3.rds", TRUE))
list.save(matched_uninj_dl_c_s4, proc_path("matched_uninj_dl_c_s4.rds", TRUE))
list.save(matched_uninj_dl_c_s5, proc_path("matched_uninj_dl_c_s5.rds", TRUE))
list.save(matched_uninj_dl_c_p1, proc_path("matched_uninj_dl_c_p1.rds", TRUE))
list.save(matched_uninj_dl_c_p2, proc_path("matched_uninj_dl_c_p2.rds", TRUE))
list.save(matched_uninj_dl_c_p3, proc_path("matched_uninj_dl_c_p3.rds", TRUE))
list.save(matched_uninj_dl_c_p4, proc_path("matched_uninj_dl_c_p4.rds", TRUE))
list.save(matched_uninj_dl_c_p5, proc_path("matched_uninj_dl_c_p5.rds", TRUE))
list.save(matched_uninj_ol_c_s1, proc_path("matched_uninj_ol_c_s1.rds", TRUE))
list.save(matched_uninj_ol_c_s2, proc_path("matched_uninj_ol_c_s2.rds", TRUE))
list.save(matched_uninj_ol_c_s3, proc_path("matched_uninj_ol_c_s3.rds", TRUE))
list.save(matched_uninj_ol_c_s4, proc_path("matched_uninj_ol_c_s4.rds", TRUE))
list.save(matched_uninj_ol_c_s5, proc_path("matched_uninj_ol_c_s5.rds", TRUE))
list.save(matched_uninj_ol_c_p1, proc_path("matched_uninj_ol_c_p1.rds", TRUE))
list.save(matched_uninj_ol_c_p2, proc_path("matched_uninj_ol_c_p2.rds", TRUE))
list.save(matched_uninj_ol_c_p3, proc_path("matched_uninj_ol_c_p3.rds", TRUE))
list.save(matched_uninj_ol_c_p4, proc_path("matched_uninj_ol_c_p4.rds", TRUE))
list.save(matched_uninj_ol_c_p5, proc_path("matched_uninj_ol_c_p5.rds", TRUE))
list.save(matched_uninj_dl_d_s1, proc_path("matched_uninj_dl_d_s1.rds", TRUE))
list.save(matched_uninj_dl_d_s2, proc_path("matched_uninj_dl_d_s2.rds", TRUE))
list.save(matched_uninj_dl_d_s3, proc_path("matched_uninj_dl_d_s3.rds", TRUE))
list.save(matched_uninj_dl_d_s4, proc_path("matched_uninj_dl_d_s4.rds", TRUE))
list.save(matched_uninj_dl_d_s5, proc_path("matched_uninj_dl_d_s5.rds", TRUE))
list.save(matched_uninj_dl_d_p1, proc_path("matched_uninj_dl_d_p1.rds", TRUE))
list.save(matched_uninj_dl_d_p2, proc_path("matched_uninj_dl_d_p2.rds", TRUE))
list.save(matched_uninj_dl_d_p3, proc_path("matched_uninj_dl_d_p3.rds", TRUE))
list.save(matched_uninj_dl_d_p4, proc_path("matched_uninj_dl_d_p4.rds", TRUE))
list.save(matched_uninj_dl_d_p5, proc_path("matched_uninj_dl_d_p5.rds", TRUE))
list.save(matched_uninj_ol_d_s1, proc_path("matched_uninj_ol_d_s1.rds", TRUE))
list.save(matched_uninj_ol_d_s2, proc_path("matched_uninj_ol_d_s2.rds", TRUE))
list.save(matched_uninj_ol_d_s3, proc_path("matched_uninj_ol_d_s3.rds", TRUE))
list.save(matched_uninj_ol_d_s4, proc_path("matched_uninj_ol_d_s4.rds", TRUE))
list.save(matched_uninj_ol_d_s5, proc_path("matched_uninj_ol_d_s5.rds", TRUE))
list.save(matched_uninj_ol_d_p1, proc_path("matched_uninj_ol_d_p1.rds", TRUE))
list.save(matched_uninj_ol_d_p2, proc_path("matched_uninj_ol_d_p2.rds", TRUE))
list.save(matched_uninj_ol_d_p3, proc_path("matched_uninj_ol_d_p3.rds", TRUE))
list.save(matched_uninj_ol_d_p4, proc_path("matched_uninj_ol_d_p4.rds", TRUE))
list.save(matched_uninj_ol_d_p5, proc_path("matched_uninj_ol_d_p5.rds", TRUE))
```

```{r}
# CHECKPOINT
matched_uninj_dl_a_s1 <- list.load(proc_path("2024_09_13_matched_uninj_dl_a_s1.rds"))
matched_uninj_dl_a_s2 <- list.load(proc_path("2024_09_13_matched_uninj_dl_a_s2.rds"))
matched_uninj_dl_a_s3 <- list.load(proc_path("2024_09_13_matched_uninj_dl_a_s3.rds"))
matched_uninj_dl_a_s4 <- list.load(proc_path("2024_09_13_matched_uninj_dl_a_s4.rds"))
matched_uninj_dl_a_s5 <- list.load(proc_path("2024_09_13_matched_uninj_dl_a_s5.rds"))
matched_uninj_dl_a_p1 <- list.load(proc_path("2024_09_13_matched_uninj_dl_a_p1.rds"))
matched_uninj_dl_a_p2 <- list.load(proc_path("2024_09_13_matched_uninj_dl_a_p2.rds"))
matched_uninj_dl_a_p3 <- list.load(proc_path("2024_09_13_matched_uninj_dl_a_p3.rds"))
matched_uninj_dl_a_p4 <- list.load(proc_path("2024_09_13_matched_uninj_dl_a_p4.rds"))
matched_uninj_dl_a_p5 <- list.load(proc_path("2024_09_13_matched_uninj_dl_a_p5.rds"))
matched_uninj_ol_a_s1 <- list.load(proc_path("2024_09_13_matched_uninj_ol_a_s1.rds"))
matched_uninj_ol_a_s2 <- list.load(proc_path("2024_09_13_matched_uninj_ol_a_s2.rds"))
matched_uninj_ol_a_s3 <- list.load(proc_path("2024_09_13_matched_uninj_ol_a_s3.rds"))
matched_uninj_ol_a_s4 <- list.load(proc_path("2024_09_13_matched_uninj_ol_a_s4.rds"))
matched_uninj_ol_a_s5 <- list.load(proc_path("2024_09_13_matched_uninj_ol_a_s5.rds"))
matched_uninj_ol_a_p1 <- list.load(proc_path("2024_09_13_matched_uninj_ol_a_p1.rds"))
matched_uninj_ol_a_p2 <- list.load(proc_path("2024_09_13_matched_uninj_ol_a_p2.rds"))
matched_uninj_ol_a_p3 <- list.load(proc_path("2024_09_13_matched_uninj_ol_a_p3.rds"))
matched_uninj_ol_a_p4 <- list.load(proc_path("2024_09_13_matched_uninj_ol_a_p4.rds"))
matched_uninj_ol_a_p5 <- list.load(proc_path("2024_09_13_matched_uninj_ol_a_p5.rds"))
matched_uninj_dl_b_s1 <- list.load(proc_path("2024_09_13_matched_uninj_dl_b_s1.rds"))
matched_uninj_dl_b_s2 <- list.load(proc_path("2024_09_13_matched_uninj_dl_b_s2.rds"))
matched_uninj_dl_b_s3 <- list.load(proc_path("2024_09_13_matched_uninj_dl_b_s3.rds"))
matched_uninj_dl_b_s4 <- list.load(proc_path("2024_09_13_matched_uninj_dl_b_s4.rds"))
matched_uninj_dl_b_s5 <- list.load(proc_path("2024_09_13_matched_uninj_dl_b_s5.rds"))
matched_uninj_dl_b_p1 <- list.load(proc_path("2024_09_13_matched_uninj_dl_b_p1.rds"))
matched_uninj_dl_b_p2 <- list.load(proc_path("2024_09_13_matched_uninj_dl_b_p2.rds"))
matched_uninj_dl_b_p3 <- list.load(proc_path("2024_09_13_matched_uninj_dl_b_p3.rds"))
matched_uninj_dl_b_p4 <- list.load(proc_path("2024_09_13_matched_uninj_dl_b_p4.rds"))
matched_uninj_dl_b_p5 <- list.load(proc_path("2024_09_13_matched_uninj_dl_b_p5.rds"))
matched_uninj_ol_b_s1 <- list.load(proc_path("2024_09_13_matched_uninj_ol_b_s1.rds"))
matched_uninj_ol_b_s2 <- list.load(proc_path("2024_09_13_matched_uninj_ol_b_s2.rds"))
matched_uninj_ol_b_s3 <- list.load(proc_path("2024_09_13_matched_uninj_ol_b_s3.rds"))
matched_uninj_ol_b_s4 <- list.load(proc_path("2024_09_13_matched_uninj_ol_b_s4.rds"))
matched_uninj_ol_b_s5 <- list.load(proc_path("2024_09_13_matched_uninj_ol_b_s5.rds"))
matched_uninj_ol_b_p1 <- list.load(proc_path("2024_09_13_matched_uninj_ol_b_p1.rds"))
matched_uninj_ol_b_p2 <- list.load(proc_path("2024_09_13_matched_uninj_ol_b_p2.rds"))
matched_uninj_ol_b_p3 <- list.load(proc_path("2024_09_13_matched_uninj_ol_b_p3.rds"))
matched_uninj_ol_b_p4 <- list.load(proc_path("2024_09_13_matched_uninj_ol_b_p4.rds"))
matched_uninj_ol_b_p5 <- list.load(proc_path("2024_09_13_matched_uninj_ol_b_p5.rds"))
matched_uninj_dl_c_s1 <- list.load(proc_path("2024_09_13_matched_uninj_dl_c_s1.rds"))
matched_uninj_dl_c_s2 <- list.load(proc_path("2024_09_13_matched_uninj_dl_c_s2.rds"))
matched_uninj_dl_c_s3 <- list.load(proc_path("2024_09_13_matched_uninj_dl_c_s3.rds"))
matched_uninj_dl_c_s4 <- list.load(proc_path("2024_09_13_matched_uninj_dl_c_s4.rds"))
matched_uninj_dl_c_s5 <- list.load(proc_path("2024_09_13_matched_uninj_dl_c_s5.rds"))
matched_uninj_dl_c_p1 <- list.load(proc_path("2024_09_13_matched_uninj_dl_c_p1.rds"))
matched_uninj_dl_c_p2 <- list.load(proc_path("2024_09_13_matched_uninj_dl_c_p2.rds"))
matched_uninj_dl_c_p3 <- list.load(proc_path("2024_09_13_matched_uninj_dl_c_p3.rds"))
matched_uninj_dl_c_p4 <- list.load(proc_path("2024_09_13_matched_uninj_dl_c_p4.rds"))
matched_uninj_dl_c_p5 <- list.load(proc_path("2024_09_13_matched_uninj_dl_c_p5.rds"))
matched_uninj_ol_c_s1 <- list.load(proc_path("2024_09_13_matched_uninj_ol_c_s1.rds"))
matched_uninj_ol_c_s2 <- list.load(proc_path("2024_09_13_matched_uninj_ol_c_s2.rds"))
matched_uninj_ol_c_s3 <- list.load(proc_path("2024_09_13_matched_uninj_ol_c_s3.rds"))
matched_uninj_ol_c_s4 <- list.load(proc_path("2024_09_13_matched_uninj_ol_c_s4.rds"))
matched_uninj_ol_c_s5 <- list.load(proc_path("2024_09_13_matched_uninj_ol_c_s5.rds"))
matched_uninj_ol_c_p1 <- list.load(proc_path("2024_09_13_matched_uninj_ol_c_p1.rds"))
matched_uninj_ol_c_p2 <- list.load(proc_path("2024_09_13_matched_uninj_ol_c_p2.rds"))
matched_uninj_ol_c_p3 <- list.load(proc_path("2024_09_13_matched_uninj_ol_c_p3.rds"))
matched_uninj_ol_c_p4 <- list.load(proc_path("2024_09_13_matched_uninj_ol_c_p4.rds"))
matched_uninj_ol_c_p5 <- list.load(proc_path("2024_09_13_matched_uninj_ol_c_p5.rds"))
matched_uninj_dl_d_s1 <- list.load(proc_path("2024_09_13_matched_uninj_dl_d_s1.rds"))
matched_uninj_dl_d_s2 <- list.load(proc_path("2024_09_13_matched_uninj_dl_d_s2.rds"))
matched_uninj_dl_d_s3 <- list.load(proc_path("2024_09_13_matched_uninj_dl_d_s3.rds"))
matched_uninj_dl_d_s4 <- list.load(proc_path("2024_09_13_matched_uninj_dl_d_s4.rds"))
matched_uninj_dl_d_s5 <- list.load(proc_path("2024_09_13_matched_uninj_dl_d_s5.rds"))
matched_uninj_dl_d_p1 <- list.load(proc_path("2024_09_13_matched_uninj_dl_d_p1.rds"))
matched_uninj_dl_d_p2 <- list.load(proc_path("2024_09_13_matched_uninj_dl_d_p2.rds"))
matched_uninj_dl_d_p3 <- list.load(proc_path("2024_09_13_matched_uninj_dl_d_p3.rds"))
matched_uninj_dl_d_p4 <- list.load(proc_path("2024_09_13_matched_uninj_dl_d_p4.rds"))
matched_uninj_dl_d_p5 <- list.load(proc_path("2024_09_13_matched_uninj_dl_d_p5.rds"))
matched_uninj_ol_d_s1 <- list.load(proc_path("2024_09_13_matched_uninj_ol_d_s1.rds"))
matched_uninj_ol_d_s2 <- list.load(proc_path("2024_09_13_matched_uninj_ol_d_s2.rds"))
matched_uninj_ol_d_s3 <- list.load(proc_path("2024_09_13_matched_uninj_ol_d_s3.rds"))
matched_uninj_ol_d_s4 <- list.load(proc_path("2024_09_13_matched_uninj_ol_d_s4.rds"))
matched_uninj_ol_d_s5 <- list.load(proc_path("2024_09_13_matched_uninj_ol_d_s5.rds"))
matched_uninj_ol_d_p1 <- list.load(proc_path("2024_09_13_matched_uninj_ol_d_p1.rds"))
matched_uninj_ol_d_p2 <- list.load(proc_path("2024_09_13_matched_uninj_ol_d_p2.rds"))
matched_uninj_ol_d_p3 <- list.load(proc_path("2024_09_13_matched_uninj_ol_d_p3.rds"))
matched_uninj_ol_d_p4 <- list.load(proc_path("2024_09_13_matched_uninj_ol_d_p4.rds"))
matched_uninj_ol_d_p5 <- list.load(proc_path("2024_09_13_matched_uninj_ol_d_p5.rds"))
```

## metaSNF

```{r}
my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

matched_settings_matrix <- generate_settings_matrix(
    matched_uninj_dl_a_s1,
    nrow = 200,
    seed = 42,
    distance_metrics_list = my_distance_metrics
)

write_csv(matched_settings_matrix, proc_path("matched_settings_matrix.csv", TRUE))
```

```{r}
# CHECKPOINT
matched_settings_matrix <- read_csv(proc_path("2024_09_13_matched_settings_matrix.csv"))
```

The goal now is to actually run the SNF.

I have 4 different "sets" of data list / oom list combinations.

Consider just the first set.

This covers 10 different imputed datasets (right?) the 5 pooled and 5 solo uninjured.
So, I'll create 2000 SNF solutions using all of those 10 sets.

Then, repeat that process 4x.

```{r}
uninj_sm_a_s1 <- batch_snf(matched_uninj_dl_a_s1, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_a_s1, proc_path("uninj_sm_a_s1.csv", TRUE))
uninj_sm_a_s2 <- batch_snf(matched_uninj_dl_a_s2, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_a_s2, proc_path("uninj_sm_a_s2.csv", TRUE))
uninj_sm_a_s3 <- batch_snf(matched_uninj_dl_a_s3, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_a_s3, proc_path("uninj_sm_a_s3.csv", TRUE))
uninj_sm_a_s4 <- batch_snf(matched_uninj_dl_a_s4, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_a_s4, proc_path("uninj_sm_a_s4.csv", TRUE))
uninj_sm_a_s5 <- batch_snf(matched_uninj_dl_a_s5, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_a_s5, proc_path("uninj_sm_a_s5.csv", TRUE))
uninj_sm_a_p1 <- batch_snf(matched_uninj_dl_a_p1, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_a_p1, proc_path("uninj_sm_a_p1.csv", TRUE))
uninj_sm_a_p2 <- batch_snf(matched_uninj_dl_a_p2, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_a_p2, proc_path("uninj_sm_a_p2.csv", TRUE))
uninj_sm_a_p3 <- batch_snf(matched_uninj_dl_a_p3, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_a_p3, proc_path("uninj_sm_a_p3.csv", TRUE))
uninj_sm_a_p4 <- batch_snf(matched_uninj_dl_a_p4, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_a_p4, proc_path("uninj_sm_a_p4.csv", TRUE))
uninj_sm_a_p5 <- batch_snf(matched_uninj_dl_a_p5, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_a_p5, proc_path("uninj_sm_a_p5.csv", TRUE))
uninj_sm_b_s1 <- batch_snf(matched_uninj_dl_b_s1, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_b_s1, proc_path("uninj_sm_b_s1.csv", TRUE))
uninj_sm_b_s2 <- batch_snf(matched_uninj_dl_b_s2, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_b_s2, proc_path("uninj_sm_b_s2.csv", TRUE))
uninj_sm_b_s3 <- batch_snf(matched_uninj_dl_b_s3, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_b_s3, proc_path("uninj_sm_b_s3.csv", TRUE))
uninj_sm_b_s4 <- batch_snf(matched_uninj_dl_b_s4, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_b_s4, proc_path("uninj_sm_b_s4.csv", TRUE))
uninj_sm_b_s5 <- batch_snf(matched_uninj_dl_b_s5, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_b_s5, proc_path("uninj_sm_b_s5.csv", TRUE))
uninj_sm_b_p1 <- batch_snf(matched_uninj_dl_b_p1, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_b_p1, proc_path("uninj_sm_b_p1.csv", TRUE))
uninj_sm_b_p2 <- batch_snf(matched_uninj_dl_b_p2, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_b_p2, proc_path("uninj_sm_b_p2.csv", TRUE))
uninj_sm_b_p3 <- batch_snf(matched_uninj_dl_b_p3, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_b_p3, proc_path("uninj_sm_b_p3.csv", TRUE))
uninj_sm_b_p4 <- batch_snf(matched_uninj_dl_b_p4, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_b_p4, proc_path("uninj_sm_b_p4.csv", TRUE))
uninj_sm_b_p5 <- batch_snf(matched_uninj_dl_b_p5, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_b_p5, proc_path("uninj_sm_b_p5.csv", TRUE))
uninj_sm_c_s1 <- batch_snf(matched_uninj_dl_c_s1, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_c_s1, proc_path("uninj_sm_c_s1.csv", TRUE))
uninj_sm_c_s2 <- batch_snf(matched_uninj_dl_c_s2, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_c_s2, proc_path("uninj_sm_c_s2.csv", TRUE))
uninj_sm_c_s3 <- batch_snf(matched_uninj_dl_c_s3, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_c_s3, proc_path("uninj_sm_c_s3.csv", TRUE))
uninj_sm_c_s4 <- batch_snf(matched_uninj_dl_c_s4, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_c_s4, proc_path("uninj_sm_c_s4.csv", TRUE))
uninj_sm_c_s5 <- batch_snf(matched_uninj_dl_c_s5, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_c_s5, proc_path("uninj_sm_c_s5.csv", TRUE))
uninj_sm_c_p1 <- batch_snf(matched_uninj_dl_c_p1, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_c_p1, proc_path("uninj_sm_c_p1.csv", TRUE))
uninj_sm_c_p2 <- batch_snf(matched_uninj_dl_c_p2, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_c_p2, proc_path("uninj_sm_c_p2.csv", TRUE))
uninj_sm_c_p3 <- batch_snf(matched_uninj_dl_c_p3, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_c_p3, proc_path("uninj_sm_c_p3.csv", TRUE))
uninj_sm_c_p4 <- batch_snf(matched_uninj_dl_c_p4, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_c_p4, proc_path("uninj_sm_c_p4.csv", TRUE))
uninj_sm_c_p5 <- batch_snf(matched_uninj_dl_c_p5, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_c_p5, proc_path("uninj_sm_c_p5.csv", TRUE))
uninj_sm_d_s1 <- batch_snf(matched_uninj_dl_d_s1, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_d_s1, proc_path("uninj_sm_d_s1.csv", TRUE))
uninj_sm_d_s2 <- batch_snf(matched_uninj_dl_d_s2, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_d_s2, proc_path("uninj_sm_d_s2.csv", TRUE))
uninj_sm_d_s3 <- batch_snf(matched_uninj_dl_d_s3, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_d_s3, proc_path("uninj_sm_d_s3.csv", TRUE))
uninj_sm_d_s4 <- batch_snf(matched_uninj_dl_d_s4, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_d_s4, proc_path("uninj_sm_d_s4.csv", TRUE))
uninj_sm_d_s5 <- batch_snf(matched_uninj_dl_d_s5, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_d_s5, proc_path("uninj_sm_d_s5.csv", TRUE))
uninj_sm_d_p1 <- batch_snf(matched_uninj_dl_d_p1, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_d_p1, proc_path("uninj_sm_d_p1.csv", TRUE))
uninj_sm_d_p2 <- batch_snf(matched_uninj_dl_d_p2, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_d_p2, proc_path("uninj_sm_d_p2.csv", TRUE))
uninj_sm_d_p3 <- batch_snf(matched_uninj_dl_d_p3, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_d_p3, proc_path("uninj_sm_d_p3.csv", TRUE))
uninj_sm_d_p4 <- batch_snf(matched_uninj_dl_d_p4, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_d_p4, proc_path("uninj_sm_d_p4.csv", TRUE))
uninj_sm_d_p5 <- batch_snf(matched_uninj_dl_d_p5, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(uninj_sm_d_p5, proc_path("uninj_sm_d_p5.csv", TRUE))
```

```{r}
uninj_sm_a_s1 <- read_csv(proc_path("2024_09_13_uninj_sm_a_s1.csv"))
uninj_sm_a_s2 <- read_csv(proc_path("2024_09_13_uninj_sm_a_s2.csv"))
uninj_sm_a_s3 <- read_csv(proc_path("2024_09_13_uninj_sm_a_s3.csv"))
uninj_sm_a_s4 <- read_csv(proc_path("2024_09_13_uninj_sm_a_s4.csv"))
uninj_sm_a_s5 <- read_csv(proc_path("2024_09_13_uninj_sm_a_s5.csv"))
uninj_sm_a_p1 <- read_csv(proc_path("2024_09_13_uninj_sm_a_p1.csv"))
uninj_sm_a_p2 <- read_csv(proc_path("2024_09_13_uninj_sm_a_p2.csv"))
uninj_sm_a_p3 <- read_csv(proc_path("2024_09_13_uninj_sm_a_p3.csv"))
uninj_sm_a_p4 <- read_csv(proc_path("2024_09_13_uninj_sm_a_p4.csv"))
uninj_sm_a_p5 <- read_csv(proc_path("2024_09_13_uninj_sm_a_p5.csv"))
uninj_sm_b_s1 <- read_csv(proc_path("2024_09_13_uninj_sm_b_s1.csv"))
uninj_sm_b_s2 <- read_csv(proc_path("2024_09_13_uninj_sm_b_s2.csv"))
uninj_sm_b_s3 <- read_csv(proc_path("2024_09_13_uninj_sm_b_s3.csv"))
uninj_sm_b_s4 <- read_csv(proc_path("2024_09_13_uninj_sm_b_s4.csv"))
uninj_sm_b_s5 <- read_csv(proc_path("2024_09_13_uninj_sm_b_s5.csv"))
uninj_sm_b_p1 <- read_csv(proc_path("2024_09_13_uninj_sm_b_p1.csv"))
uninj_sm_b_p2 <- read_csv(proc_path("2024_09_13_uninj_sm_b_p2.csv"))
uninj_sm_b_p3 <- read_csv(proc_path("2024_09_13_uninj_sm_b_p3.csv"))
uninj_sm_b_p4 <- read_csv(proc_path("2024_09_13_uninj_sm_b_p4.csv"))
uninj_sm_b_p5 <- read_csv(proc_path("2024_09_13_uninj_sm_b_p5.csv"))
uninj_sm_c_s1 <- read_csv(proc_path("2024_09_13_uninj_sm_c_s1.csv"))
uninj_sm_c_s2 <- read_csv(proc_path("2024_09_13_uninj_sm_c_s2.csv"))
uninj_sm_c_s3 <- read_csv(proc_path("2024_09_13_uninj_sm_c_s3.csv"))
uninj_sm_c_s4 <- read_csv(proc_path("2024_09_13_uninj_sm_c_s4.csv"))
uninj_sm_c_s5 <- read_csv(proc_path("2024_09_13_uninj_sm_c_s5.csv"))
uninj_sm_c_p1 <- read_csv(proc_path("2024_09_13_uninj_sm_c_p1.csv"))
uninj_sm_c_p2 <- read_csv(proc_path("2024_09_13_uninj_sm_c_p2.csv"))
uninj_sm_c_p3 <- read_csv(proc_path("2024_09_13_uninj_sm_c_p3.csv"))
uninj_sm_c_p4 <- read_csv(proc_path("2024_09_13_uninj_sm_c_p4.csv"))
uninj_sm_c_p5 <- read_csv(proc_path("2024_09_13_uninj_sm_c_p5.csv"))
uninj_sm_d_s1 <- read_csv(proc_path("2024_09_13_uninj_sm_d_s1.csv"))
uninj_sm_d_s2 <- read_csv(proc_path("2024_09_13_uninj_sm_d_s2.csv"))
uninj_sm_d_s3 <- read_csv(proc_path("2024_09_13_uninj_sm_d_s3.csv"))
uninj_sm_d_s4 <- read_csv(proc_path("2024_09_13_uninj_sm_d_s4.csv"))
uninj_sm_d_s5 <- read_csv(proc_path("2024_09_13_uninj_sm_d_s5.csv"))
uninj_sm_d_p1 <- read_csv(proc_path("2024_09_13_uninj_sm_d_p1.csv"))
uninj_sm_d_p2 <- read_csv(proc_path("2024_09_13_uninj_sm_d_p2.csv"))
uninj_sm_d_p3 <- read_csv(proc_path("2024_09_13_uninj_sm_d_p3.csv"))
uninj_sm_d_p4 <- read_csv(proc_path("2024_09_13_uninj_sm_d_p4.csv"))
uninj_sm_d_p5 <- read_csv(proc_path("2024_09_13_uninj_sm_d_p5.csv"))
```

```{r}
matched_uninj_esm_a_s1 <- extend_solutions(uninj_sm_a_s1, data_list = matched_uninj_dl_a_s1, target_list = matched_uninj_ol_a_s1, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_a_s1, proc_path("matched_uninj_esm_a_s1.csv", TRUE))
matched_uninj_esm_a_s2 <- extend_solutions(uninj_sm_a_s2, data_list = matched_uninj_dl_a_s2, target_list = matched_uninj_ol_a_s2, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_a_s2, proc_path("matched_uninj_esm_a_s2.csv", TRUE))
matched_uninj_esm_a_s3 <- extend_solutions(uninj_sm_a_s3, data_list = matched_uninj_dl_a_s3, target_list = matched_uninj_ol_a_s3, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_a_s3, proc_path("matched_uninj_esm_a_s3.csv", TRUE))
matched_uninj_esm_a_s4 <- extend_solutions(uninj_sm_a_s4, data_list = matched_uninj_dl_a_s4, target_list = matched_uninj_ol_a_s4, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_a_s4, proc_path("matched_uninj_esm_a_s4.csv", TRUE))
matched_uninj_esm_a_s5 <- extend_solutions(uninj_sm_a_s5, data_list = matched_uninj_dl_a_s5, target_list = matched_uninj_ol_a_s5, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_a_s5, proc_path("matched_uninj_esm_a_s5.csv", TRUE))
matched_uninj_esm_a_p1 <- extend_solutions(uninj_sm_a_p1, data_list = matched_uninj_dl_a_p1, target_list = matched_uninj_ol_a_p1, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_a_p1, proc_path("matched_uninj_esm_a_p1.csv", TRUE))
matched_uninj_esm_a_p2 <- extend_solutions(uninj_sm_a_p2, data_list = matched_uninj_dl_a_p2, target_list = matched_uninj_ol_a_p2, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_a_p2, proc_path("matched_uninj_esm_a_p2.csv", TRUE))
matched_uninj_esm_a_p3 <- extend_solutions(uninj_sm_a_p3, data_list = matched_uninj_dl_a_p3, target_list = matched_uninj_ol_a_p3, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_a_p3, proc_path("matched_uninj_esm_a_p3.csv", TRUE))
matched_uninj_esm_a_p4 <- extend_solutions(uninj_sm_a_p4, data_list = matched_uninj_dl_a_p4, target_list = matched_uninj_ol_a_p4, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_a_p4, proc_path("matched_uninj_esm_a_p4.csv", TRUE))
matched_uninj_esm_a_p5 <- extend_solutions(uninj_sm_a_p5, data_list = matched_uninj_dl_a_p5, target_list = matched_uninj_ol_a_p5, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_a_p5, proc_path("matched_uninj_esm_a_p5.csv", TRUE))
matched_uninj_esm_b_s1 <- extend_solutions(uninj_sm_b_s1, data_list = matched_uninj_dl_b_s1, target_list = matched_uninj_ol_b_s1, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_b_s1, proc_path("matched_uninj_esm_b_s1.csv", TRUE))
matched_uninj_esm_b_s2 <- extend_solutions(uninj_sm_b_s2, data_list = matched_uninj_dl_b_s2, target_list = matched_uninj_ol_b_s2, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_b_s2, proc_path("matched_uninj_esm_b_s2.csv", TRUE))
matched_uninj_esm_b_s3 <- extend_solutions(uninj_sm_b_s3, data_list = matched_uninj_dl_b_s3, target_list = matched_uninj_ol_b_s3, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_b_s3, proc_path("matched_uninj_esm_b_s3.csv", TRUE))
matched_uninj_esm_b_s4 <- extend_solutions(uninj_sm_b_s4, data_list = matched_uninj_dl_b_s4, target_list = matched_uninj_ol_b_s4, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_b_s4, proc_path("matched_uninj_esm_b_s4.csv", TRUE))
matched_uninj_esm_b_s5 <- extend_solutions(uninj_sm_b_s5, data_list = matched_uninj_dl_b_s5, target_list = matched_uninj_ol_b_s5, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_b_s5, proc_path("matched_uninj_esm_b_s5.csv", TRUE))
matched_uninj_esm_b_p1 <- extend_solutions(uninj_sm_b_p1, data_list = matched_uninj_dl_b_p1, target_list = matched_uninj_ol_b_p1, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_b_p1, proc_path("matched_uninj_esm_b_p1.csv", TRUE))
matched_uninj_esm_b_p2 <- extend_solutions(uninj_sm_b_p2, data_list = matched_uninj_dl_b_p2, target_list = matched_uninj_ol_b_p2, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_b_p2, proc_path("matched_uninj_esm_b_p2.csv", TRUE))
matched_uninj_esm_b_p3 <- extend_solutions(uninj_sm_b_p3, data_list = matched_uninj_dl_b_p3, target_list = matched_uninj_ol_b_p3, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_b_p3, proc_path("matched_uninj_esm_b_p3.csv", TRUE))
matched_uninj_esm_b_p4 <- extend_solutions(uninj_sm_b_p4, data_list = matched_uninj_dl_b_p4, target_list = matched_uninj_ol_b_p4, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_b_p4, proc_path("matched_uninj_esm_b_p4.csv", TRUE))
matched_uninj_esm_b_p5 <- extend_solutions(uninj_sm_b_p5, data_list = matched_uninj_dl_b_p5, target_list = matched_uninj_ol_b_p5, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_b_p5, proc_path("matched_uninj_esm_b_p5.csv", TRUE))
matched_uninj_esm_c_s1 <- extend_solutions(uninj_sm_c_s1, data_list = matched_uninj_dl_c_s1, target_list = matched_uninj_ol_c_s1, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_c_s1, proc_path("matched_uninj_esm_c_s1.csv", TRUE))
matched_uninj_esm_c_s2 <- extend_solutions(uninj_sm_c_s2, data_list = matched_uninj_dl_c_s2, target_list = matched_uninj_ol_c_s2, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_c_s2, proc_path("matched_uninj_esm_c_s2.csv", TRUE))
matched_uninj_esm_c_s3 <- extend_solutions(uninj_sm_c_s3, data_list = matched_uninj_dl_c_s3, target_list = matched_uninj_ol_c_s3, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_c_s3, proc_path("matched_uninj_esm_c_s3.csv", TRUE))
matched_uninj_esm_c_s4 <- extend_solutions(uninj_sm_c_s4, data_list = matched_uninj_dl_c_s4, target_list = matched_uninj_ol_c_s4, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_c_s4, proc_path("matched_uninj_esm_c_s4.csv", TRUE))
matched_uninj_esm_c_s5 <- extend_solutions(uninj_sm_c_s5, data_list = matched_uninj_dl_c_s5, target_list = matched_uninj_ol_c_s5, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_c_s5, proc_path("matched_uninj_esm_c_s5.csv", TRUE))
matched_uninj_esm_c_p1 <- extend_solutions(uninj_sm_c_p1, data_list = matched_uninj_dl_c_p1, target_list = matched_uninj_ol_c_p1, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_c_p1, proc_path("matched_uninj_esm_c_p1.csv", TRUE))
matched_uninj_esm_c_p2 <- extend_solutions(uninj_sm_c_p2, data_list = matched_uninj_dl_c_p2, target_list = matched_uninj_ol_c_p2, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_c_p2, proc_path("matched_uninj_esm_c_p2.csv", TRUE))
matched_uninj_esm_c_p3 <- extend_solutions(uninj_sm_c_p3, data_list = matched_uninj_dl_c_p3, target_list = matched_uninj_ol_c_p3, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_c_p3, proc_path("matched_uninj_esm_c_p3.csv", TRUE))
matched_uninj_esm_c_p4 <- extend_solutions(uninj_sm_c_p4, data_list = matched_uninj_dl_c_p4, target_list = matched_uninj_ol_c_p4, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_c_p4, proc_path("matched_uninj_esm_c_p4.csv", TRUE))
matched_uninj_esm_c_p5 <- extend_solutions(uninj_sm_c_p5, data_list = matched_uninj_dl_c_p5, target_list = matched_uninj_ol_c_p5, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_c_p5, proc_path("matched_uninj_esm_c_p5.csv", TRUE))
matched_uninj_esm_d_s1 <- extend_solutions(uninj_sm_d_s1, data_list = matched_uninj_dl_d_s1, target_list = matched_uninj_ol_d_s1, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_d_s1, proc_path("matched_uninj_esm_d_s1.csv", TRUE))
matched_uninj_esm_d_s2 <- extend_solutions(uninj_sm_d_s2, data_list = matched_uninj_dl_d_s2, target_list = matched_uninj_ol_d_s2, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_d_s2, proc_path("matched_uninj_esm_d_s2.csv", TRUE))
matched_uninj_esm_d_s3 <- extend_solutions(uninj_sm_d_s3, data_list = matched_uninj_dl_d_s3, target_list = matched_uninj_ol_d_s3, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_d_s3, proc_path("matched_uninj_esm_d_s3.csv", TRUE))
matched_uninj_esm_d_s4 <- extend_solutions(uninj_sm_d_s4, data_list = matched_uninj_dl_d_s4, target_list = matched_uninj_ol_d_s4, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_d_s4, proc_path("matched_uninj_esm_d_s4.csv", TRUE))
matched_uninj_esm_d_s5 <- extend_solutions(uninj_sm_d_s5, data_list = matched_uninj_dl_d_s5, target_list = matched_uninj_ol_d_s5, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_d_s5, proc_path("matched_uninj_esm_d_s5.csv", TRUE))
matched_uninj_esm_d_p1 <- extend_solutions(uninj_sm_d_p1, data_list = matched_uninj_dl_d_p1, target_list = matched_uninj_ol_d_p1, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_d_p1, proc_path("matched_uninj_esm_d_p1.csv", TRUE))
matched_uninj_esm_d_p2 <- extend_solutions(uninj_sm_d_p2, data_list = matched_uninj_dl_d_p2, target_list = matched_uninj_ol_d_p2, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_d_p2, proc_path("matched_uninj_esm_d_p2.csv", TRUE))
matched_uninj_esm_d_p3 <- extend_solutions(uninj_sm_d_p3, data_list = matched_uninj_dl_d_p3, target_list = matched_uninj_ol_d_p3, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_d_p3, proc_path("matched_uninj_esm_d_p3.csv", TRUE))
matched_uninj_esm_d_p4 <- extend_solutions(uninj_sm_d_p4, data_list = matched_uninj_dl_d_p4, target_list = matched_uninj_ol_d_p4, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_d_p4, proc_path("matched_uninj_esm_d_p4.csv", TRUE))
matched_uninj_esm_d_p5 <- extend_solutions(uninj_sm_d_p5, data_list = matched_uninj_dl_d_p5, target_list = matched_uninj_ol_d_p5, min_pval = 1e-10, processes = "max")
write_csv(matched_uninj_esm_d_p5, proc_path("matched_uninj_esm_d_p5.csv", TRUE))
# HERE I AM
```

```{r}

matched_uninj_esm_a_s1 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_a_s1.csv"))
matched_uninj_esm_a_s2 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_a_s2.csv"))
matched_uninj_esm_a_s3 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_a_s3.csv"))
matched_uninj_esm_a_s4 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_a_s4.csv"))
matched_uninj_esm_a_s5 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_a_s5.csv"))
matched_uninj_esm_a_p1 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_a_p1.csv"))
matched_uninj_esm_a_p2 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_a_p2.csv"))
matched_uninj_esm_a_p3 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_a_p3.csv"))
matched_uninj_esm_a_p4 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_a_p4.csv"))
matched_uninj_esm_a_p5 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_a_p5.csv"))
matched_uninj_esm_b_s1 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_b_s1.csv"))
matched_uninj_esm_b_s2 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_b_s2.csv"))
matched_uninj_esm_b_s3 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_b_s3.csv"))
matched_uninj_esm_b_s4 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_b_s4.csv"))
matched_uninj_esm_b_s5 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_b_s5.csv"))
matched_uninj_esm_b_p1 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_b_p1.csv"))
matched_uninj_esm_b_p2 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_b_p2.csv"))
matched_uninj_esm_b_p3 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_b_p3.csv"))
matched_uninj_esm_b_p4 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_b_p4.csv"))
matched_uninj_esm_b_p5 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_b_p5.csv"))
matched_uninj_esm_c_s1 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_c_s1.csv"))
matched_uninj_esm_c_s2 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_c_s2.csv"))
matched_uninj_esm_c_s3 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_c_s3.csv"))
matched_uninj_esm_c_s4 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_c_s4.csv"))
matched_uninj_esm_c_s5 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_c_s5.csv"))
matched_uninj_esm_c_p1 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_c_p1.csv"))
matched_uninj_esm_c_p2 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_c_p2.csv"))
matched_uninj_esm_c_p3 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_c_p3.csv"))
matched_uninj_esm_c_p4 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_c_p4.csv"))
matched_uninj_esm_c_p5 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_c_p5.csv"))
matched_uninj_esm_d_s1 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_d_s1.csv"))
matched_uninj_esm_d_s2 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_d_s2.csv"))
matched_uninj_esm_d_s3 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_d_s3.csv"))
matched_uninj_esm_d_s4 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_d_s4.csv"))
matched_uninj_esm_d_s5 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_d_s5.csv"))
matched_uninj_esm_d_p1 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_d_p1.csv"))
matched_uninj_esm_d_p2 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_d_p2.csv"))
matched_uninj_esm_d_p3 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_d_p3.csv"))
matched_uninj_esm_d_p4 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_d_p4.csv"))
matched_uninj_esm_d_p5 <- read_csv(proc_path("2024_09_13_matched_uninj_esm_d_p5.csv"))

matched_uninj_esm_list <- list(
    "a_s1" = matched_uninj_esm_a_s1,
    "a_s2" = matched_uninj_esm_a_s2,
    "a_s3" = matched_uninj_esm_a_s3,
    "a_s4" = matched_uninj_esm_a_s4,
    "a_s5" = matched_uninj_esm_a_s5,
    "a_p1" = matched_uninj_esm_a_p1,
    "a_p2" = matched_uninj_esm_a_p2,
    "a_p3" = matched_uninj_esm_a_p3,
    "a_p4" = matched_uninj_esm_a_p4,
    "a_p5" = matched_uninj_esm_a_p5,
    "b_s1" = matched_uninj_esm_b_s1,
    "b_s2" = matched_uninj_esm_b_s2,
    "b_s3" = matched_uninj_esm_b_s3,
    "b_s4" = matched_uninj_esm_b_s4,
    "b_s5" = matched_uninj_esm_b_s5,
    "b_p1" = matched_uninj_esm_b_p1,
    "b_p2" = matched_uninj_esm_b_p2,
    "b_p3" = matched_uninj_esm_b_p3,
    "b_p4" = matched_uninj_esm_b_p4,
    "b_p5" = matched_uninj_esm_b_p5,
    "c_s1" = matched_uninj_esm_c_s1,
    "c_s2" = matched_uninj_esm_c_s2,
    "c_s3" = matched_uninj_esm_c_s3,
    "c_s4" = matched_uninj_esm_c_s4,
    "c_s5" = matched_uninj_esm_c_s5,
    "c_p1" = matched_uninj_esm_c_p1,
    "c_p2" = matched_uninj_esm_c_p2,
    "c_p3" = matched_uninj_esm_c_p3,
    "c_p4" = matched_uninj_esm_c_p4,
    "c_p5" = matched_uninj_esm_c_p5,
    "d_s1" = matched_uninj_esm_d_s1,
    "d_s2" = matched_uninj_esm_d_s2,
    "d_s3" = matched_uninj_esm_d_s3,
    "d_s4" = matched_uninj_esm_d_s4,
    "d_s5" = matched_uninj_esm_d_s5,
    "d_p1" = matched_uninj_esm_d_p1,
    "d_p2" = matched_uninj_esm_d_p2,
    "d_p3" = matched_uninj_esm_d_p3,
    "d_p4" = matched_uninj_esm_d_p4,
    "d_p5" = matched_uninj_esm_d_p5
)

list.save(matched_uninj_esm_list, proc_path("matched_uninj_esm_list.rds", TRUE))
```

```{r}
matched_uninj_esm_list <- list.load(proc_path("2024_09_13_matched_uninj_esm_list.rds"))

names(matched_uninj_esm_list)  <- c(
    "a_s1",
    "a_s2",
    "a_s3",
    "a_s4",
    "a_s5",
    "a_p1",
    "a_p2",
    "a_p3",
    "a_p4",
    "a_p5",
    "b_s1",
    "b_s2",
    "b_s3",
    "b_s4",
    "b_s5",
    "b_p1",
    "b_p2",
    "b_p3",
    "b_p4",
    "b_p5",
    "c_s1",
    "c_s2",
    "c_s3",
    "c_s4",
    "c_s5",
    "c_p1",
    "c_p2",
    "c_p3",
    "c_p4",
    "c_p5",
    "d_s1",
    "d_s2",
    "d_s3",
    "d_s4",
    "d_s5",
    "d_p1",
    "d_p2",
    "d_p3",
    "d_p4",
    "d_p5"
)

list.save(matched_uninj_esm_list, proc_path("matched_uninj_esm_list.rds", TRUE))

matched_uninj_aris <- lapply(
    matched_uninj_esm_list,
    function(x) {
        calc_aris(x, processes = "max")
    }
)
list.save(matched_uninj_aris, proc_path("matched_uninj_aris.rds", TRUE))


```

```{r}

matched_uninj_aris <- list.load(proc_path("2024_09_13_matched_uninj_aris.rds"))

matched_uninj_ari_orders <- lapply(
    matched_uninj_aris,
    get_matrix_order
)

list.save(matched_uninj_ari_orders, proc_path("matched_uninj_ari_orders.rds", TRUE))

matched_uninj_ari_orders <- list.load(proc_path("2024_09_13_matched_uninj_ari_orders.rds"))
```

Then I just look to see, in each of these, what evidence do we have for a 3 cluster solution that has those traits I've observed already?



```{r}
## CHECKPOINT
matched_uninj_esm_list <- list.load(proc_path("2024_09_13_matched_uninj_esm_list.rds"))
matched_uninj_aris <- list.load(proc_path("2024_09_13_matched_uninj_aris.rds"))
matched_uninj_ari_orders <- list.load(proc_path("2024_09_13_matched_uninj_ari_orders.rds"))
```


```{r}
uninj_dl_s1 <- all_dls$"uninj_data_lists"$"imp_1"
uninj_dl_s2 <- all_dls$"uninj_data_lists"$"imp_2"
uninj_dl_s3 <- all_dls$"uninj_data_lists"$"imp_3"
uninj_dl_s4 <- all_dls$"uninj_data_lists"$"imp_4"
uninj_dl_s5 <- all_dls$"uninj_data_lists"$"imp_5"
uninj_dl_p1 <- all_dls$"uninj_pooled_data_lists"$"imp_1"
uninj_dl_p2 <- all_dls$"uninj_pooled_data_lists"$"imp_2"
uninj_dl_p3 <- all_dls$"uninj_pooled_data_lists"$"imp_3"
uninj_dl_p4 <- all_dls$"uninj_pooled_data_lists"$"imp_4"
uninj_dl_p5 <- all_dls$"uninj_pooled_data_lists"$"imp_5"

uninj_ol_s1 <- all_dls$"uninj_oom_lists"$"imp_1"
uninj_ol_s2 <- all_dls$"uninj_oom_lists"$"imp_2"
uninj_ol_s3 <- all_dls$"uninj_oom_lists"$"imp_3"
uninj_ol_s4 <- all_dls$"uninj_oom_lists"$"imp_4"
uninj_ol_s5 <- all_dls$"uninj_oom_lists"$"imp_5"
uninj_ol_p1 <- all_dls$"uninj_pooled_oom_lists"$"imp_1"
uninj_ol_p2 <- all_dls$"uninj_pooled_oom_lists"$"imp_2"
uninj_ol_p3 <- all_dls$"uninj_pooled_oom_lists"$"imp_3"
uninj_ol_p4 <- all_dls$"uninj_pooled_oom_lists"$"imp_4"
uninj_ol_p5 <- all_dls$"uninj_pooled_oom_lists"$"imp_5"
```


```{r}

matched_uninj_esm_list <- lapply(
    matched_uninj_esm_list,
    function(x) {
        x$"impairment_separation" <- -log10(x$"mean_pval")
        return(x)
    }
)




my_ari_hm <- function(a, o, e) {
    plot <- adjusted_rand_index_heatmap(
        aris = a,
        order = o,
        data = e,
        min_colour = "black",
        top_hm = list(
            "Impairment Separation" = "impairment_separation"
        ),
        top_bar = list(
            "Number of Clusters" = "nclust"
        ),
        annotation_colours = list(
            "Impairment Separation" = colour_scale(
                e$"impairment_separation",
                min_colour = "gray7",
                max_colour = "limegreen"
            )
        )
    )
    return(plot)
}

my_ari_hm(
    a = matched_uninj_aris$"a_s1",
    e = matched_uninj_esm_list$"a_s1",
    o = matched_uninj_ari_orders$"a_s1"
)

my_ari_hm(
    a = matched_uninj_aris$"b_s1",
    e = matched_uninj_esm_list$"b_s1",
    o = matched_uninj_ari_orders$"b_s1"
)

# Define the lists
a <- list(1, 2, 3)
b <- list(2, 1, 2)
c <- list(10, 100, 1000)

# Define a function that uses elements from each list
combine_function <- function(a, o, e) {
    return(my_ari_hm(a, o, e))
}

# Use mapply to apply the function element-wise across the three lists
d <- mapply(combine_function, matched_uninj_aris, matched_uninj_ari_orders, matched_uninj_esm_list)

d[[2]]

d


```
