# Data Exploration

## Establishing paths

```{r}
library(ggplot2)
library(readr)
library(dplyr)
library(here)
library(abcdutils)
library(ComplexUpset)
library(fastDummies)
library(patchwork)
library(visdat)
library(mice)
library(circlize)
library(ComplexHeatmap)

core_path <- path_maker(here(paste0("data/abcd/core")))
input_path <- path_maker(here(paste0("data/abcd/inputs")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))

long_mtbi_subs <- read_subjects(sub_path("2024_11_04_mtbi_subjects_0_to_2.csv"))
long_uninj_subs <- read_subjects(sub_path("2024_11_04_uninjured_subjects_0_to_2.csv"))
base_mtbi_subs <- read_subjects(sub_path("2024_10_29_mtbi_subs.csv"))
base_uninj_subs <- read_subjects(sub_path("2024_10_29_uninj_subs.csv"))
```

## Importing data

```{r}
# Baseline-related data frames, pre-imputation
mtbi_train_df <- read_csv(proc_path("2024_11_15_mtbi_train_df.csv"))
mtbi_test_df <- read_csv(proc_path("2024_11_15_mtbi_test_df.csv"))
mtbi_df <- rbind(mtbi_train_df, mtbi_test_df)
uninj_df <- read_csv(proc_path("2024_11_15_uninj_df.csv"))
```

```{r}
# Baseline-related pre-QC neuroimaging data
sm_subc_v_mtbi <- read("2024_10_29_sm_subc_v_mtbi.csv")
sm_cort_t_mtbi <- read("2024_10_29_sm_cort_t_mtbi.csv")
sm_cort_sa_mtbi <- read("2024_10_29_sm_cort_sa_mtbi.csv")
dm_all_wmnd_mtbi <- read("2024_10_29_dm_all_wmnd_mtbi.csv")
rm_gord_cor_mtbi <- read("2024_10_29_rm_gord_cor_mtbi.csv")
rm_subc_cor_mtbi <- read("2024_10_29_rm_subc_cor_mtbi.csv")

sm_subc_v_uninj <- read("2024_10_29_sm_subc_v_uninj.csv")
sm_cort_t_uninj <- read("2024_10_29_sm_cort_t_uninj.csv")
sm_cort_sa_uninj <- read("2024_10_29_sm_cort_sa_uninj.csv")
dm_all_wmnd_uninj <- read("2024_10_29_dm_all_wmnd_uninj.csv")
rm_gord_cor_uninj <- read("2024_10_29_rm_gord_cor_uninj.csv")
rm_subc_cor_uninj <- read("2024_10_29_rm_subc_cor_uninj.csv")

# Baseline related post-QC neuroimaging data
sm_cort_sa_qc_mtbi <- read("2024_10_29_sm_cort_sa_qc_mtbi.csv")
sm_cort_t_qc_mtbi <- read("2024_10_29_sm_cort_t_qc_mtbi.csv")
sm_subc_v_qc_mtbi <- read("2024_10_29_sm_subc_v_qc_mtbi.csv")
sm_cort_sa_qc_uninj <- read("2024_10_29_sm_cort_sa_qc_uninj.csv")
sm_cort_t_qc_uninj <- read("2024_10_29_sm_cort_t_qc_uninj.csv")
sm_subc_v_qc_uninj <- read("2024_10_29_sm_subc_v_qc_uninj.csv")
dm_all_wmnd_qc_mtbi <- read("2024_10_29_dm_all_wmnd_qc_mtbi.csv")
dm_all_wmnd_qc_uninj <- read("2024_10_29_dm_all_wmnd_qc_uninj.csv")
rm_gord_cor_qc_mtbi <- read("2024_10_29_rm_gord_cor_qc_mtbi.csv")
rm_subc_cor_qc_mtbi <- read("2024_10_29_rm_subc_cor_qc_mtbi.csv")
rm_gord_cor_qc_uninj <- read("2024_10_29_rm_gord_cor_qc_uninj.csv")
rm_subc_cor_qc_uninj <- read("2024_10_29_rm_subc_cor_qc_uninj.csv")

# Longitudinal-related data frames, pre-imputation
long_mtbi_0_df <- read_csv(input_path("2024_11_06_long_mtbi_0_df.csv"))
long_mtbi_l_df <- read_csv(input_path("2024_11_06_long_mtbi_l_df.csv"))
base_mtbi_l_df <- read_csv(input_path("2024_11_06_base_mtbi_l_df.csv"))
base_uninj_l_df <- read_csv(input_path("2024_11_06_base_uninj_l_df.csv"))

# Longitudinal-related pre-QC neuroimaging data
sm_subc_v_long_mtbi_0 <- read_csv(input_path("2024_11_06_sm_subc_v_long_mtbi_0.csv"))
sm_cort_t_long_mtbi_0 <- read_csv(input_path("2024_11_06_sm_cort_t_long_mtbi_0.csv"))
sm_cort_sa_long_mtbi_0 <- read_csv(input_path("2024_11_06_sm_cort_sa_long_mtbi_0.csv"))
dm_all_wmnd_long_mtbi_0 <- read_csv(input_path("2024_11_06_dm_all_wmnd_long_mtbi_0.csv"))
rm_gord_cor_long_mtbi_0 <- read_csv(input_path("2024_11_06_rm_gord_cor_long_mtbi_0.csv"))
rm_subc_cor_long_mtbi_0 <- read_csv(input_path("2024_11_06_rm_subc_cor_long_mtbi_0.csv"))

sm_subc_v_long_mtbi_l <- read_csv(input_path("2024_11_06_sm_subc_v_long_mtbi_l.csv"))
sm_cort_t_long_mtbi_l <- read_csv(input_path("2024_11_06_sm_cort_t_long_mtbi_l.csv"))
sm_cort_sa_long_mtbi_l <- read_csv(input_path("2024_11_06_sm_cort_sa_long_mtbi_l.csv"))
dm_all_wmnd_long_mtbi_l <- read_csv(input_path("2024_11_06_dm_all_wmnd_long_mtbi_l.csv"))
rm_gord_cor_long_mtbi_l <- read_csv(input_path("2024_11_06_rm_gord_cor_long_mtbi_l.csv"))
rm_subc_cor_long_mtbi_l <- read_csv(input_path("2024_11_06_rm_subc_cor_long_mtbi_l.csv"))

sm_subc_v_base_mtbi_l <- read_csv(input_path("2024_11_06_sm_subc_v_base_mtbi_l.csv"))
sm_cort_t_base_mtbi_l <- read_csv(input_path("2024_11_06_sm_cort_t_base_mtbi_l.csv"))
sm_cort_sa_base_mtbi_l <- read_csv(input_path("2024_11_06_sm_cort_sa_base_mtbi_l.csv"))
dm_all_wmnd_base_mtbi_l <- read_csv(input_path("2024_11_06_dm_all_wmnd_base_mtbi_l.csv"))
rm_gord_cor_base_mtbi_l <- read_csv(input_path("2024_11_06_rm_gord_cor_base_mtbi_l.csv"))
rm_subc_cor_base_mtbi_l <- read_csv(input_path("2024_11_06_rm_subc_cor_base_mtbi_l.csv"))

sm_subc_v_base_uninj_l <- read_csv(input_path("2024_11_06_sm_subc_v_base_uninj_l.csv"))
sm_cort_t_base_uninj_l <- read_csv(input_path("2024_11_06_sm_cort_t_base_uninj_l.csv"))
sm_cort_sa_base_uninj_l <- read_csv(input_path("2024_11_06_sm_cort_sa_base_uninj_l.csv"))
dm_all_wmnd_base_uninj_l <- read_csv(input_path("2024_11_06_dm_all_wmnd_base_uninj_l.csv"))
rm_gord_cor_base_uninj_l <- read_csv(input_path("2024_11_06_rm_gord_cor_base_uninj_l.csv"))
rm_subc_cor_base_uninj_l <- read_csv(input_path("2024_11_06_rm_subc_cor_base_uninj_l.csv"))

# Longitudinal-related post-QC neuroimaging data
sm_subc_v_qc_long_mtbi_0 <- read_csv(input_path("2024_11_06_sm_subc_v_qc_long_mtbi_0.csv"))
sm_cort_t_qc_long_mtbi_0 <- read_csv(input_path("2024_11_06_sm_cort_t_qc_long_mtbi_0.csv"))
sm_cort_sa_qc_long_mtbi_0 <- read_csv(input_path("2024_11_06_sm_cort_sa_qc_long_mtbi_0.csv"))
dm_all_wmnd_qc_long_mtbi_0 <- read_csv(input_path("2024_11_06_dm_all_wmnd_qc_long_mtbi_0.csv"))
rm_gord_cor_qc_long_mtbi_0 <- read_csv(input_path("2024_11_06_rm_gord_cor_qc_long_mtbi_0.csv"))
rm_subc_cor_qc_long_mtbi_0 <- read_csv(input_path("2024_11_06_rm_subc_cor_qc_long_mtbi_0.csv"))
sm_subc_v_qc_long_mtbi_l <- read_csv(input_path("2024_11_06_sm_subc_v_qc_long_mtbi_l.csv"))
sm_cort_t_qc_long_mtbi_l <- read_csv(input_path("2024_11_06_sm_cort_t_qc_long_mtbi_l.csv"))
sm_cort_sa_qc_long_mtbi_l <- read_csv(input_path("2024_11_06_sm_cort_sa_qc_long_mtbi_l.csv"))
dm_all_wmnd_qc_long_mtbi_l <- read_csv(input_path("2024_11_06_dm_all_wmnd_qc_long_mtbi_l.csv"))
rm_gord_cor_qc_long_mtbi_l <- read_csv(input_path("2024_11_06_rm_gord_cor_qc_long_mtbi_l.csv"))
rm_subc_cor_qc_long_mtbi_l <- read_csv(input_path("2024_11_06_rm_subc_cor_qc_long_mtbi_l.csv"))
sm_subc_v_qc_base_mtbi_l <- read_csv(input_path("2024_11_06_sm_subc_v_qc_base_mtbi_l.csv"))
sm_cort_t_qc_base_mtbi_l <- read_csv(input_path("2024_11_06_sm_cort_t_qc_base_mtbi_l.csv"))
sm_cort_sa_qc_base_mtbi_l <- read_csv(input_path("2024_11_06_sm_cort_sa_qc_base_mtbi_l.csv"))
dm_all_wmnd_qc_base_mtbi_l <- read_csv(input_path("2024_11_06_dm_all_wmnd_qc_base_mtbi_l.csv"))
rm_gord_cor_qc_base_mtbi_l <- read_csv(input_path("2024_11_06_rm_gord_cor_qc_base_mtbi_l.csv"))
rm_subc_cor_qc_base_mtbi_l <- read_csv(input_path("2024_11_06_rm_subc_cor_qc_base_mtbi_l.csv"))
sm_subc_v_qc_base_uninj_l <- read_csv(input_path("2024_11_06_sm_subc_v_qc_base_uninj_l.csv"))
sm_cort_t_qc_base_uninj_l <- read_csv(input_path("2024_11_06_sm_cort_t_qc_base_uninj_l.csv"))
sm_cort_sa_qc_base_uninj_l <- read_csv(input_path("2024_11_06_sm_cort_sa_qc_base_uninj_l.csv"))
dm_all_wmnd_qc_base_uninj_l <- read_csv(input_path("2024_11_06_dm_all_wmnd_qc_base_uninj_l.csv"))
rm_gord_cor_qc_base_uninj_l <- read_csv(input_path("2024_11_06_rm_gord_cor_qc_base_uninj_l.csv"))
rm_subc_cor_qc_base_uninj_l <- read_csv(input_path("2024_11_06_rm_subc_cor_qc_base_uninj_l.csv"))
```

## Who failed QC?

```{r}
qc_fails <- function(df_list_1, df_list_2) {
    df_1 <- merge_df_list(df_list_1)
    df_2 <- merge_df_list(df_list_2)
    subs_1 <- na.omit(df_1)$"subjectkey"
    subs_2 <- na.omit(df_2)$"subjectkey"
    return(subs_1[which(!subs_1 %in% subs_2)])
}

###############################################################################
# Baseline mTBI, T = 0
###############################################################################
base_mtbi_0_s_qcf <- qc_fails(
    list(sm_subc_v_mtbi, sm_cort_t_mtbi, sm_cort_sa_mtbi),
    list(sm_cort_sa_qc_mtbi, sm_cort_t_qc_mtbi, sm_subc_v_qc_mtbi)
)
base_mtbi_0_s_qcf

base_mtbi_0_d_qcf <- qc_fails(
    list(dm_all_wmnd_mtbi),
    list(dm_all_wmnd_qc_mtbi)
)
base_mtbi_0_d_qcf

base_mtbi_0_r_qcf <- qc_fails(
    list(rm_gord_cor_mtbi),
    list(rm_gord_cor_qc_mtbi)
)
base_mtbi_0_r_qcf

###############################################################################
# Baseline uninj, T = 0
###############################################################################
base_uninj_0_s_qcf <- qc_fails(
    list(sm_subc_v_uninj, sm_cort_t_uninj, sm_cort_sa_uninj),
    list(sm_cort_sa_qc_uninj, sm_cort_t_qc_uninj, sm_subc_v_qc_uninj)
)
base_uninj_0_s_qcf

base_uninj_0_d_qcf <- qc_fails(
    list(dm_all_wmnd_uninj),
    list(dm_all_wmnd_qc_uninj)
)
base_uninj_0_d_qcf

base_uninj_0_r_qcf <- qc_fails(
    list(rm_gord_cor_uninj),
    list(rm_gord_cor_qc_uninj)
)
base_uninj_0_r_qcf

###############################################################################
# Baseline mtbi, T = 2
###############################################################################
base_mtbi_l_s_qcf <- qc_fails(
    list(sm_subc_v_base_mtbi_l, sm_cort_t_base_mtbi_l, sm_cort_sa_base_mtbi_l),
    list(sm_cort_sa_qc_base_mtbi_l, sm_cort_t_qc_base_mtbi_l, sm_subc_v_qc_base_mtbi_l)
)
base_mtbi_l_s_qcf

base_mtbi_l_d_qcf <- qc_fails(
    list(dm_all_wmnd_base_mtbi_l),
    list(dm_all_wmnd_qc_base_mtbi_l)
)
base_mtbi_l_d_qcf

base_mtbi_l_r_qcf <- qc_fails(
    list(rm_gord_cor_base_mtbi_l),
    list(rm_gord_cor_qc_base_mtbi_l)
)
base_mtbi_l_r_qcf

###############################################################################
# Baseline uninj, T = 2
###############################################################################
base_uninj_l_s_qcf <- qc_fails(
    list(sm_subc_v_base_uninj_l, sm_cort_t_base_uninj_l, sm_cort_sa_base_uninj_l),
    list(sm_cort_sa_qc_base_uninj_l, sm_cort_t_qc_base_uninj_l, sm_subc_v_qc_base_uninj_l)
)
base_uninj_l_s_qcf

base_uninj_l_d_qcf <- qc_fails(
    list(dm_all_wmnd_base_uninj_l),
    list(dm_all_wmnd_qc_base_uninj_l)
)
base_uninj_l_d_qcf

base_uninj_l_r_qcf <- qc_fails(
    list(rm_gord_cor_base_uninj_l),
    list(rm_gord_cor_qc_base_uninj_l)
)
base_uninj_l_r_qcf

###############################################################################
# Longitudinal mtbi, T = 0
###############################################################################
long_mtbi_0_s_qcf <- qc_fails(
    list(sm_subc_v_long_mtbi_0, sm_cort_t_long_mtbi_0, sm_cort_sa_long_mtbi_0),
    list(sm_cort_sa_qc_long_mtbi_0, sm_cort_t_qc_long_mtbi_0, sm_subc_v_qc_long_mtbi_0)
)
long_mtbi_0_s_qcf

long_mtbi_0_d_qcf <- qc_fails(
    list(dm_all_wmnd_long_mtbi_0),
    list(dm_all_wmnd_qc_long_mtbi_0)
)
long_mtbi_0_d_qcf

long_mtbi_0_r_qcf <- qc_fails(
    list(rm_gord_cor_long_mtbi_0),
    list(rm_gord_cor_qc_long_mtbi_0)
)
long_mtbi_0_r_qcf

###############################################################################
# Longitudinal mtbi, T = 2
###############################################################################
long_mtbi_l_s_qcf <- qc_fails(
    list(sm_subc_v_long_mtbi_l, sm_cort_t_long_mtbi_l, sm_cort_sa_long_mtbi_l),
    list(sm_cort_sa_qc_long_mtbi_l, sm_cort_t_qc_long_mtbi_l, sm_subc_v_qc_long_mtbi_l)
)
long_mtbi_l_s_qcf

long_mtbi_l_d_qcf <- qc_fails(
    list(dm_all_wmnd_long_mtbi_l),
    list(dm_all_wmnd_qc_long_mtbi_l)
)
long_mtbi_l_d_qcf

long_mtbi_l_r_qcf <- qc_fails(
    list(rm_gord_cor_long_mtbi_l),
    list(rm_gord_cor_qc_long_mtbi_l)
)
long_mtbi_l_r_qcf
```

```{r}
flag_missing <- function(df) {
    for (col in colnames(df)) {
        if (any(is.na(df[, col]))) {
            newcol <- paste0("X_", col)
            df <- df |>
                dplyr::mutate(
                    newcol = as.numeric(is.na(.data[[col]]))
                )
            colnames(df)[ncol(df)] <- newcol
        }
    }
    return(df)
}
```

## MAR/MCAR check

```{r}
mtbi_df$"group" <- "base_mtbi"
mtbi_df$"t" <- 0

uninj_df$"group" <- "base_uninj"
uninj_df$"t" <- 0

long_mtbi_0_df$"group" <- "long_mtbi"
long_mtbi_0_df$"t" <- 0

long_mtbi_l_df$"group" <- "long_mtbi"
long_mtbi_l_df$"t" <- 2

base_mtbi_l_df$"group" <- "base_mtbi"
base_mtbi_l_df$"t" <- 2

base_uninj_l_df$"group" <- "base_uninj"
base_uninj_l_df$"t" <- 2

pre_imputation_df <- bind_rows(
    mtbi_df,
    uninj_df,
    long_mtbi_0_df,
    long_mtbi_l_df,
    base_mtbi_l_df,
    base_uninj_l_df
)

pre_imputation_df <- pre_imputation_df |>
    dplyr::mutate(
        X_s_qc = dplyr::case_when(
            t == 0 & group == "base_mtbi" & subjectkey %in% base_mtbi_0_s_qcf ~ 1,
            t == 2 & group == "base_mtbi" & subjectkey %in% base_mtbi_l_s_qcf ~ 1,
            t == 0 & group == "base_uninj" & subjectkey %in% base_uninj_0_s_qcf ~ 1,
            t == 2 & group == "base_uninj" & subjectkey %in% base_uninj_l_s_qcf ~ 1,
            t == 0 & group == "long_mtbi" & subjectkey %in% long_mtbi_0_s_qcf ~ 1,
            t == 2 & group == "long_mtbi" & subjectkey %in% long_mtbi_l_s_qcf ~ 1,
            TRUE ~ 0
        ),
        X_d_qc = dplyr::case_when(
            t == 0 & group == "base_mtbi" & subjectkey %in% base_mtbi_0_d_qcf ~ 1,
            t == 2 & group == "base_mtbi" & subjectkey %in% base_mtbi_l_d_qcf ~ 1,
            t == 0 & group == "base_uninj" & subjectkey %in% base_uninj_0_d_qcf ~ 1,
            t == 2 & group == "base_uninj" & subjectkey %in% base_uninj_l_d_qcf ~ 1,
            t == 0 & group == "long_mtbi" & subjectkey %in% long_mtbi_0_d_qcf ~ 1,
            t == 2 & group == "long_mtbi" & subjectkey %in% long_mtbi_l_d_qcf ~ 1,
            TRUE ~ 0
        ),
        X_r_qc = dplyr::case_when(
            t == 0 & group == "base_mtbi" & subjectkey %in% base_mtbi_0_r_qcf ~ 1,
            t == 2 & group == "base_mtbi" & subjectkey %in% base_mtbi_l_r_qcf ~ 1,
            t == 0 & group == "base_uninj" & subjectkey %in% base_uninj_0_r_qcf ~ 1,
            t == 2 & group == "base_uninj" & subjectkey %in% base_uninj_l_r_qcf ~ 1,
            t == 0 & group == "long_mtbi" & subjectkey %in% long_mtbi_0_r_qcf ~ 1,
            t == 2 & group == "long_mtbi" & subjectkey %in% long_mtbi_l_r_qcf ~ 1,
            TRUE ~ 0
        ) 
    )

pre_imputation_df <- pre_imputation_df |>
    dummy_cols(
        select_columns = c("latest_mtbi_mechanism", "race"),
        remove_most_frequent_dummy = TRUE,
        remove_selected_columns = TRUE
    )

pre_imputation_df <- flag_missing(pre_imputation_df)

write_csv(pre_imputation_df, proc_path("pre_imputation_df.csv", TRUE))

pre_imputation_df <- read_csv(proc_path("2024_11_15_pre_imputation_df.csv"))
```


```{r}

saiq_cols <- c("school_activities", "extracurriculars", "private_instruction", "activities_last_year")

mtbi_train_df |> dplyr::select(all_of(saiq_cols))

missing_mat <- pre_imputation_df |>
    dplyr::select(-subjectkey, -group, -t) |>
    cor(use = "pairwise.complete.obs") |>
    as.matrix()

missing_indicator_cols <- grepl("X_", colnames(missing_mat))

# For checking MCAR vs. MAR
missing_cor_mat_1 <- missing_mat[missing_indicator_cols, !missing_indicator_cols]

# For checking patterns of missingness
missing_cor_mat_2 <- missing_mat[missing_indicator_cols, missing_indicator_cols]

x_map <- matrix(
    c(
        "X_s_qc", "N (QC)",
        "X_d_qc", "N (QC)",
        "X_r_qc", "N (QC)",
        "X_latest_mtbi_mem_daze", "AS",
        "X_latest_mtbi_loc", "AS",
        "X_interview_age", "D",
        "X_latest_mtbi_age", "AS",
        "X_sex", "D",
        "X_household_income", "D",
        "X_pubertal_status_p", "D",
        "X_pubertal_status_y", "D",
        "X_headache", "MH",
        "X_mtbi_count", "MH",
        "X_smri_vol_scs_wholeb", "N",
        "X_smri_thick_cdk_mean", "N",
        "X_smri_area_cdk_total", "N",
        "X_dmri_rsirnd_fib_allfib", "N",
        "X_dmri_rsirndwm_cdk_mean", "N",
        "X_avg_gord_cor", "N",
        "X_avg_subc_cor", "N",
        "X_ss_friend", "P",
        "X_os_friend", "P",
        "X_ss_close_friend", "P",
        "X_os_close_friend", "P",
        "X_screentime_wknd_hrs", "P",
        "X_screentime_wkday_hrs", "P",
        "X_physical_activity", "P",
        "X_considerate_y", "P",
        "X_helps_hurt_y", "P",
        "X_helpful_y", "P",
        "X_considerate_p", "P",
        "X_helps_hurt_p", "P",
        "X_helpful_p", "P",
        "X_q1_fight_y", "P (FE)",
        "X_q2_angry_y", "P (FE)",
        "X_q3_throw_y", "P (FE)",
        "X_q4_temper_y", "P (FE)",
        "X_q5_criticize_y", "P (FE)",
        "X_q6_hit_y", "P (FE)",
        "X_q7_peaceful_y", "P (FE)",
        "X_q8_outdo_y", "P (FE)",
        "X_q9_yell_y", "P (FE)",
        "X_q1_fight_p", "P (FE)",
        "X_q2_angry_p", "P (FE)",
        "X_q3_throw_p", "P (FE)",
        "X_q4_temper_p", "P (FE)",
        "X_q5_criticize_p", "P (FE)",
        "X_q6_hit_p", "P (FE)",
        "X_q7_peaceful_p", "P (FE)",
        "X_q8_outdo_p", "P (FE)",
        "X_q9_yell_p", "P (FE)",
        "X_asr_scr_perstr_r", "P (ASR)",
        "X_asr_scr_anxdep_r", "P (ASR)",
        "X_asr_scr_withdrawn_r", "P (ASR)",
        "X_asr_scr_somatic_r", "P (ASR)",
        "X_asr_scr_thought_r", "P (ASR)",
        "X_asr_scr_attention_r", "P (ASR)",
        "X_asr_scr_aggressive_r", "P (ASR)",
        "X_asr_scr_intrusive_r", "P (ASR)",
        "X_asr_scr_depress_r", "P (ASR)",
        "X_asr_scr_anxdisord_r", "P (ASR)",
        "X_asr_scr_avoidant_r", "P (ASR)",
        "X_asr_scr_antisocial_r", "P (ASR)",
        "X_asr_scr_hyperactive_r", "P (ASR)",
        "X_cbcl_scr_syn_anxdep_r", "B",
        "X_cbcl_scr_syn_withdep_r", "B",
        "X_cbcl_scr_syn_somatic_r", "B",
        "X_cbcl_scr_syn_social_r", "B",
        "X_cbcl_scr_syn_thought_r", "B",
        "X_cbcl_scr_syn_attention_r", "B",
        "X_cbcl_scr_syn_rulebreak_r", "B",
        "X_cbcl_scr_syn_aggressive_r", "B",
        "X_sds_p_ss_total", "B (SDS)",
        "X_latest_mtbi_mechanism_fall_hit", "AS",
        "X_latest_mtbi_mechanism_multi", "AS",
        "X_latest_mtbi_mechanism_other_loc", "AS",
        "X_latest_mtbi_mechanism_vehicle", "AS",
        "X_latest_mtbi_mechanism_violent", "AS",
        "X_race_black", "D",
        "X_race_hispanic", "D",
        "X_race_other", "D"
    ),
    ncol = 2,
    byrow = TRUE
)


# Here i am! - Interesting missingness plots
ComplexHeatmap::Heatmap(
    missing_cor_mat_1,
    cluster_rows = FALSE,
    cluster_columns = FALSE
)

nrow(missing_cor_mat_1)

ncol(missing_cor_mat_1)

z <- paste0("X_", colnames(missing_cor_mat_1)) %in% x_map[, 1]

ncol(missing_cor_mat_2)

ncol(missing_cor_mat_2)

for (i in colnames(missing_cor_mat_2)) {
    print(i)
}

ComplexHeatmap::Heatmap(
    missing_cor_mat_2,
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    col = circlize::colorRamp2(
        c(-1, 0, 1),
        c("blue", "white", "red")
    ),
    column_split = x_map[, 2]
)

ComplexHeatmap::Heatmap(missing_cor_mat_2)

# Also need to do actual correlation structure plots across the imputations

library(reshape2)

# Example pairwise matrix
mat <- matrix(c(0, 1, 2,
                1, 0, 3,
                2, 3, 0), 
              nrow = 3, byrow = TRUE)
rownames(mat) <- colnames(mat) <- c("A", "B", "C")

mat

# Convert to a 2-column dataframe
df <- melt(
    missing_correlation_matrix,
    varnames = c("missing", "feature"), value.name = "correlation") |>
    arrange(-abs(correlation))

df[1:100, ]

# Exclude redundant pairs (if symmetric)
df <- df[df$Item1 < df$Item2, ]

print(df)
```






## Sex and Gender

The purpose of this subsection is to examine the distribution of children by their parent-reported genders and sexes at baseline with their own self-reported genders and sexes at the 3-year follow-up timepoint.

```{r}
gish_p_gi <- import("gender-identity-sexual-health/gish_p_gi.csv")
gish_y_gi <- import("gender-identity-sexual-health/gish_y_gi.csv")

mtbi_y_sex <- gish_y_gi |>
    filter_subjects(mtbi_subjects) |>
    filter_timepoint(t = 3) |>
    dplyr::select(
        subjectkey,
        kbi_sex_assigned_at_birth
    ) |>
    dplyr::rename(
        "y_sex" = "kbi_sex_assigned_at_birth"
    ) |>
    dplyr::mutate(group = "mtbi", t = 3) |>
    dplyr::mutate(
        y_sex = dplyr::case_when(
            y_sex == 1 ~ "M",
            y_sex == 2 ~ "F",
            TRUE ~ NA
        )
    )

uninj_y_sex <- gish_y_gi |>
    filter_subjects(uninjured_subjects) |>
    filter_timepoint(t = 3) |>
    dplyr::select(
        subjectkey,
        kbi_sex_assigned_at_birth
    ) |>
    dplyr::rename(
        "y_sex" = "kbi_sex_assigned_at_birth"
    ) |>
    dplyr::mutate(group = "uninj", t = 3) |>
    dplyr::mutate(
        y_sex = dplyr::case_when(
            y_sex == 1 ~ "M",
            y_sex == 2 ~ "F",
            TRUE ~ NA
        )
    )

mtbi_p_sex <- get_sex(
    gish_p_gi,
    mtbi_subjects,
    t = 0,
    as_numeric = FALSE,
    only_m_f = FALSE
) |>
    dplyr::mutate(group = "mtbi", t = 0)

uninj_p_sex <- get_sex(
    gish_p_gi,
    uninjured_subjects,
    t = 0,
    as_numeric = FALSE,
    only_m_f = FALSE
) |>
    dplyr::mutate(group = "uninj", t = 0)

mtbi_y_gender <- get_y_gender(
    gish_y_gi,
    mtbi_subjects,
    t = 3
) |>
    dplyr::mutate(group = "mtbi", t = 3)

uninj_y_gender <- get_y_gender(
    gish_y_gi,
    uninjured_subjects,
    t = 3
) |>
    dplyr::mutate(group = "uninj", t = 3)

mtbi_p_gender <- get_p_gender(
    gish_p_gi,
    mtbi_subjects,
    t = 0,
    match_y_report = TRUE
) |>
    dplyr::mutate(group = "mtbi", t = 0)

uninj_p_gender <- get_p_gender(
    gish_p_gi,
    uninjured_subjects,
    t = 0,
    match_y_report = TRUE
) |>
    dplyr::mutate(group = "uninj", t = 0)

y_sex <- rbind(mtbi_y_sex, uninj_y_sex)
y_gender <- rbind(mtbi_y_gender, uninj_y_gender)
p_sex <- rbind(mtbi_p_sex, uninj_p_sex)
p_gender <- rbind(mtbi_p_gender, uninj_p_gender)

y_report <- dplyr::full_join(y_sex, y_gender) |>
    dplyr::select(-t)

p_report <- dplyr::full_join(p_sex, p_gender) |>
    dplyr::rename("p_sex" = "sex") |>
    dplyr::select(-t)

sex_and_gender <- dplyr::full_join(
    y_report,
    p_report
)

sex_and_gender[is.na(sex_and_gender)] <- "NA"

sex_and_gender <- sex_and_gender |>
    dummy_cols(
        select_columns = c("y_sex", "y_gender", "p_sex", "p_gender"),
        remove_selected_columns = TRUE
    ) |>
    tibble()

sex_and_gender_mtbi <- sex_and_gender |>
    dplyr::filter(group == "mtbi")  |>
    dplyr::select(-group)

sex_and_gender_uninj <- sex_and_gender |>
    dplyr::filter(group == "uninj")  |>
    dplyr::select(-group)
```

### Gender Upset Plots

```{r}
gender_sets <- c(
    "p_gender_NB",
    "p_gender_NA",
    "y_gender_NB",
    "y_gender_NA",
    "y_gender_F",
    "y_gender_M",
    "p_gender_F",
    "p_gender_M"
)

gender_ints <- list(
    c("p_gender_M", "y_gender_M"),
    c("p_gender_F", "y_gender_F"),
    c("p_gender_F", "y_gender_NA"),
    c("p_gender_M", "y_gender_NA"),
    c("p_gender_F", "y_gender_NB"),
    c("p_gender_F", "y_gender_M"),
    c("p_gender_M", "y_gender_NB"),
    c("p_gender_M", "y_gender_F"),
    c("p_gender_NA", "y_gender_F"),
    c("p_gender_NA", "y_gender_M"),
    c("p_gender_NA", "y_gender_NB"),
    c("p_gender_NA", "y_gender_NA"),
    c("p_gender_NB", "y_gender_F"),
    c("p_gender_NB", "y_gender_NA"),
    c("p_gender_NB", "y_gender_NB")
)

uninj_gender_upset <- upset(
    sex_and_gender_uninj,
    gender_sets,
    intersections = gender_ints,
    name = "",
    sort_sets = FALSE,
    sort_intersections = FALSE
) +
    ggtitle("Uninjured") +
    theme(text = element_text(size = 14))

mtbi_gender_upset <- upset(
    sex_and_gender_mtbi,
    gender_sets,
    intersections = gender_ints,
    name = "Gender Identity",
    sort_sets = FALSE,
    sort_intersections = FALSE
) +
    ggtitle("mTBI") +
    theme(text = element_text(size = 14))

gender_upset_plots <- uninj_gender_upset / mtbi_gender_upset

gender_upset_plots

pdf(fig_path("gender_upset_plots.pdf", TRUE), width = 10, height = 10)
print(gender_upset_plots)
dev.off()
```

### Sex Upset Plots

```{r}
sex_sets <- c(
    "p_sex_IM",
    "y_sex_NA",
    "y_sex_F",
    "y_sex_M",
    "p_sex_F",
    "p_sex_M"
)

sex_ints <- list(
    c("p_sex_M", "y_sex_M"),
    c("p_sex_F", "y_sex_F"),
    c("p_sex_M", "y_sex_NA"),
    c("p_sex_F", "y_sex_NA"),
    c("p_sex_M", "y_sex_F"),
    c("p_sex_F", "y_sex_M"),
    c("y_sex_M", "p_sex_IM")
)

mtbi_sex_upset <- upset(
    sex_and_gender_mtbi,
    sex_sets,
    intersections = sex_ints,
    name = "Sex at Birth",
    sort_sets = FALSE,
    sort_intersections = FALSE
) +
    ggtitle("mTBI") +
    theme(text = element_text(size = 14))
uninj_sex_upset <- upset(
    sex_and_gender_uninj,
    sex_sets,
    intersections = sex_ints,
    name = "Sex at Birth",
    sort_sets = FALSE,
    sort_intersections = FALSE
) +
    ggtitle("Uninjured") +
    theme(text = element_text(size = 14))
sex_upset_plots <- uninj_sex_upset / mtbi_sex_upset

sex_upset_plots

pdf(fig_path("sex_upset_plots.pdf", TRUE), width = 10, height = 10)
print(sex_upset_plots)
dev.off()
```

### Parent Report Upset Plots

```{r}

parent_sets <- c(
    "p_gender_NB",
    "p_gender_NA",
    "p_gender_F",
    "p_gender_M",
    "p_sex_IM",
    "p_sex_F",
    "p_sex_M"
)

parent_ints <- list(
    c("p_sex_M", "p_gender_M"),
    c("p_sex_F", "p_gender_F"),
    c("p_sex_F", "p_gender_NA"),
    c("p_sex_M", "p_gender_NB"),
    c("p_sex_F", "p_gender_NB"),
    c("p_gender_M", "p_sex_IM"),
    c("p_sex_M", "p_gender_F"), 
    c("p_sex_M", "p_gender_NA"), 
    c("p_gender_M", "p_sex_F")
)

mtbi_parent_sag <- upset(
    sex_and_gender_mtbi,
    intersect = parent_sets,
    intersections = parent_ints,
    set_sizes = FALSE,
    sort_sets = FALSE,
    sort_intersections = FALSE
) +
    ggtitle("mTBI") +
    theme(text = element_text(size = 14))

uninj_parent_sag <- upset(
    sex_and_gender_uninj,
    intersect = parent_sets,
    intersections = parent_ints,
    set_sizes = FALSE,
    sort_sets = FALSE,
    sort_intersections = FALSE
) +
    ggtitle("Uninjured") +
    theme(text = element_text(size = 14))

parent_sag <- wrap_plots(
    list(
        uninj_parent_sag,
        mtbi_parent_sag
    ),
    ncol = 1
)

pdf(fig_path("parent_sag", TRUE), width = 10, height = 10)
print(parent_sag)
dev.off()

```

```{r}

youth_sets <- c(
    "y_gender_NB",
    "y_gender_NA",
    "y_gender_F",
    "y_gender_M",
    "y_sex_NA",
    "y_sex_F",
    "y_sex_M"
)

youth_ints <- list(
    c("y_sex_M", "y_gender_M"),
    c("y_sex_F", "y_gender_F"),
    c("y_sex_NA", "y_gender_NA"), 
    c("y_sex_F", "y_gender_NB"),
    c("y_gender_M", "y_sex_NA"),
    c("y_gender_F", "y_sex_NA"),
    c("y_sex_F", "y_gender_NA"),
    c("y_gender_M", "y_sex_F"),
    c("y_sex_M", "y_gender_NA"),
    c("y_sex_M", "y_gender_NB"),
    c("y_sex_M", "y_gender_F")
)

mtbi_youth_sag <- upset(
    sex_and_gender_mtbi,
    intersect = youth_sets,
    intersections = youth_ints,
    set_sizes = FALSE,
    sort_sets = FALSE,
    sort_intersections = FALSE
) +
    ggtitle("mTBI") +
    theme(text = element_text(size = 14))

uninj_youth_sag <- upset(
    sex_and_gender_uninj,
    intersect = youth_sets,
    intersections = youth_ints,
    set_sizes = FALSE,
    sort_sets = FALSE,
    sort_intersections = FALSE
) +
    ggtitle("Uninjured") +
    theme(text = element_text(size = 14))

youth_sag <- wrap_plots(
    list(
        uninj_youth_sag,
        mtbi_youth_sag
    ),
    ncol = 1
)

age_split_sag <- wrap_plots(
    list(parent_sag, youth_sag),
    nrow = 2, ncol = 2
)

pdf(fig_path("age_split_sag.pdf", TRUE), width = 20, height = 20)
print(age_split_sag)
dev.off()
```

## Other features

```{r}
as_mem_daze_mtbi <- read("2024_07_31_as_mem_daze_mtbi.csv")
as_mechanism_mtbi <- read("2024_07_31_as_mechanism_mtbi.csv")
as_loc_mtbi <- read("2024_07_31_as_loc_mtbi.csv")
d_interview_age_mtbi <- read("2024_07_31_d_interview_age_mtbi.csv")
d_mtbi_age_mtbi <- read("2024_07_31_d_mtbi_age_mtbi.csv")
d_sex_mtbi <- read("2024_07_31_d_sex_mtbi.csv")
d_income_mtbi <- read("2024_07_31_d_income_mtbi.csv")
d_race_mtbi <- read("2024_07_31_d_race_mtbi.csv")
d_pubertal_status_mtbi <- read("2024_07_31_d_pubertal_status_mtbi.csv")
mh_headaches_mtbi <- read("2024_07_31_mh_headaches_mtbi.csv")
mh_mtbi_count_mtbi <- read("2024_07_31_mh_mtbi_count_mtbi.csv")
sm_subc_v_mtbi <- read("2024_07_31_sm_subc_v_mtbi.csv")
sm_cort_t_mtbi <- read("2024_07_31_sm_cort_t_mtbi.csv")
sm_cort_sa_mtbi <- read("2024_07_31_sm_cort_sa_mtbi.csv")
dm_all_wmnd_mtbi <- read("2024_07_31_dm_all_wmnd_mtbi.csv")
rm_gord_cor_mtbi <- read("2024_07_31_rm_gord_cor_mtbi.csv")
rm_subc_cor_mtbi <- read("2024_07_31_rm_subc_cor_mtbi.csv")
p_loneliness_mtbi <- read("2024_07_31_p_loneliness_mtbi.csv")
p_screen_time_mtbi <- read("2024_07_31_p_screen_time_mtbi.csv")
p_sports_mtbi <- read("2024_07_31_p_sports_mtbi.csv")
p_exercise_mtbi <- read("2024_07_31_p_exercise_mtbi.csv")
p_prosocial_mtbi <- read("2024_07_31_p_prosocial_mtbi.csv")
p_fam_fn_mtbi <- read("2024_07_31_p_fam_fn_mtbi.csv")
p_parent_psych_mtbi <- read("2024_07_31_p_parent_psych_mtbi.csv")
cbcl_anxdep_mtbi <- read("2024_07_31_cbcl_anxdep_mtbi.csv")
cbcl_withdep_mtbi <- read("2024_07_31_cbcl_withdep_mtbi.csv")
cbcl_somatic_mtbi <- read("2024_07_31_cbcl_somatic_mtbi.csv")
cbcl_social_mtbi <- read("2024_07_31_cbcl_social_mtbi.csv")
cbcl_thought_mtbi <- read("2024_07_31_cbcl_thought_mtbi.csv")
cbcl_attention_mtbi <- read("2024_07_31_cbcl_attention_mtbi.csv")
cbcl_rulebreak_mtbi <- read("2024_07_31_cbcl_rulebreak_mtbi.csv")
cbcl_aggressive_mtbi <- read("2024_07_31_cbcl_aggressive_mtbi.csv")
sds_total_probs_mtbi <- read("2024_07_31_sds_total_probs_mtbi.csv")

# Uninjured subjects
d_interview_age_uninj <- read("2024_07_31_d_interview_age_uninj.csv")
d_sex_uninj <- read("2024_07_31_d_sex_uninj.csv")
d_income_uninj <- read("2024_07_31_d_income_uninj.csv")
d_race_uninj <- read("2024_07_31_d_race_uninj.csv")
d_pubertal_status_uninj <- read("2024_07_31_d_pubertal_status_uninj.csv")
mh_headaches_uninj <- read("2024_07_31_mh_headaches_uninj.csv")
sm_subc_v_uninj <- read("2024_07_31_sm_subc_v_uninj.csv")
sm_cort_t_uninj <- read("2024_07_31_sm_cort_t_uninj.csv")
sm_cort_sa_uninj <- read("2024_07_31_sm_cort_sa_uninj.csv")
dm_all_wmnd_uninj <- read("2024_07_31_dm_all_wmnd_uninj.csv")
rm_gord_cor_uninj <- read("2024_07_31_rm_gord_cor_uninj.csv")
rm_subc_cor_uninj <- read("2024_07_31_rm_subc_cor_uninj.csv")
p_loneliness_uninj <- read("2024_07_31_p_loneliness_uninj.csv")
p_screen_time_uninj <- read("2024_07_31_p_screen_time_uninj.csv")
p_sports_uninj <- read("2024_07_31_p_sports_uninj.csv")
p_exercise_uninj <- read("2024_07_31_p_exercise_uninj.csv")
p_prosocial_uninj <- read("2024_07_31_p_prosocial_uninj.csv")
p_fam_fn_uninj <- read("2024_07_31_p_fam_fn_uninj.csv")
p_parent_psych_uninj <- read("2024_07_31_p_parent_psych_uninj.csv")
cbcl_anxdep_uninj <- read("2024_07_31_cbcl_anxdep_uninj.csv")
cbcl_withdep_uninj <- read("2024_07_31_cbcl_withdep_uninj.csv")
cbcl_somatic_uninj <- read("2024_07_31_cbcl_somatic_uninj.csv")
cbcl_social_uninj <- read("2024_07_31_cbcl_social_uninj.csv")
cbcl_thought_uninj <- read("2024_07_31_cbcl_thought_uninj.csv")
cbcl_attention_uninj <- read("2024_07_31_cbcl_attention_uninj.csv")
cbcl_rulebreak_uninj <- read("2024_07_31_cbcl_rulebreak_uninj.csv")
cbcl_aggressive_uninj <- read("2024_07_31_cbcl_aggressive_uninj.csv")
sds_total_probs_uninj <- read("2024_07_31_sds_total_probs_uninj.csv")
```

## mTBI vs. Uninj Initial Comparisons

```{r}
mtbi_initial_df_list <- list(
    as_mem_daze_mtbi,
    as_mechanism_mtbi,
    as_loc_mtbi,
    d_interview_age_mtbi,
    d_mtbi_age_mtbi,
    d_sex_mtbi,
    d_income_mtbi,
    d_race_mtbi,
    d_pubertal_status_mtbi,
    mh_headaches_mtbi,
    mh_mtbi_count_mtbi,
    sm_subc_v_mtbi,
    sm_cort_t_mtbi,
    sm_cort_sa_mtbi,
    dm_all_wmnd_mtbi,
    rm_gord_cor_mtbi,
    rm_subc_cor_mtbi,
    p_loneliness_mtbi,
    p_screen_time_mtbi,
    p_sports_mtbi,
    p_exercise_mtbi,
    p_prosocial_mtbi,
    p_fam_fn_mtbi,
    p_parent_psych_mtbi,
    cbcl_anxdep_mtbi,
    cbcl_withdep_mtbi,
    cbcl_somatic_mtbi,
    cbcl_social_mtbi,
    cbcl_thought_mtbi,
    cbcl_attention_mtbi,
    cbcl_rulebreak_mtbi,
    cbcl_aggressive_mtbi,
    sds_total_probs_mtbi
)

uninj_initial_df_list <- list(
    d_interview_age_uninj,
    d_sex_uninj,
    d_income_uninj,
    d_race_uninj,
    d_pubertal_status_uninj,
    mh_headaches_uninj,
    sm_subc_v_uninj,
    sm_cort_t_uninj,
    sm_cort_sa_uninj,
    dm_all_wmnd_uninj,
    rm_gord_cor_uninj,
    rm_subc_cor_uninj,
    p_loneliness_uninj,
    p_screen_time_uninj,
    p_sports_uninj,
    p_exercise_uninj,
    p_prosocial_uninj,
    p_fam_fn_uninj,
    p_parent_psych_uninj,
    cbcl_anxdep_uninj,
    cbcl_withdep_uninj,
    cbcl_somatic_uninj,
    cbcl_social_uninj,
    cbcl_thought_uninj,
    cbcl_attention_uninj,
    cbcl_rulebreak_uninj,
    cbcl_aggressive_uninj,
    sds_total_probs_uninj
)

mtbi_initial_df <- merge_df_list(mtbi_initial_df_list, join = "full")
uninj_initial_df <- merge_df_list(uninj_initial_df_list, join = "full")

nrow(mtbi_initial_df)

baseline_initial_df <- bind_rows(mtbi_initial_df, uninj_initial_df)

expect it is all diffuse global is fine
```
