# Imputation, QCing, and CBCL thresholding

To keep things simple, I keep the longitudinal imputation separate from the baseline imputation.
In some ways, the longitudinal analyses are validating steps to the clustering.
That provides some further rationale for keeping them separate.

Questions I'm trying to answer with the longitudinal data:

1. Was the baseline clustering informative for long-term outcomes?
2. Do matched unij subjects to the mTBI group experience more mTBIs by T2 than the other unij subjects?
3. Is the clustering of the longitudinal sample using their baseline (pre-injury) equally informative as using their longitudinal (post-injury) data?

## Loading in data

```{r}
library(abcdutils)
library(here)
library(readr)
library(metasnf)
library(mice)
library(rlist)
library(visdat)

# The path_maker function helps with managing and date stamping long paths. The
# functions are just used here to help with reading and writing data. See
# ?path_maker for more information.
input_path <- path_maker(here(paste0("data/abcd/inputs")))
core_path <- path_maker(here(paste0("data/abcd/core")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))

iread <- function(path) {
    return(read_csv(input_path(path)))
}

iwrite <- function(path) {
    return(read_csv(input_path(path)))
}
```

```{r}
# CHECKPOINT
lmtb_subs <- read_subjects(sub_path("2025_06_09_mtbi_subs_0_to_2.csv"))
lunj_subs <- read_subjects(sub_path("2025_06_09_unij_subs_0_to_2.csv"))
mtbi_subs <- read_subjects(sub_path("2025_05_22_mtbi_subs.csv"))
unij_subs <- read_subjects(sub_path("2025_05_22_unij_subs.csv"))
```

```{r}
# Just use 1st imputation.
all_dls <- readRDS(input_path("2025_05_27_all_dls.rds"))

# Baseline data
unij_dl <- all_dls$"unij_data_lists"$"imp_1"
mtbi_dl <- merge(
    all_dls$"mtbi_train_data_lists"$"imp_4",
    all_dls$"mtbi_test_data_lists"$"imp_1"
)
```

```{r}
strip_sub_prefix <- function(df) {
    df <- df |>
        dplyr::mutate(uid = gsub("uid_", "", uid)) |>
        dplyr::rename("subjectkey" = "uid") |>
        tibble::tibble()
    return(tibble::tibble(df))
}

# LONG MTBI 0
# as_loc not existent
# as_mechanism not existent
# as_mem_daze not existent
# mtbi_age not existent
# mtbi_count not existent
lmtb_cbcl_0              <- iread("2025_06_09_lmtb_cbcl_0.csv")
lmtb_d_income_0          <- iread("2025_06_09_lmtb_d_income_0.csv")
lmtb_d_interview_age_0   <- iread("2025_06_09_lmtb_d_interview_age_0.csv")
lmtb_d_pubertal_status_0 <- iread("2025_06_09_lmtb_d_pubertal_status_0.csv")
lmtb_d_race_0            <- iread("2025_06_09_lmtb_d_race_0.csv")
lmtb_d_sex_0             <- iread("2025_06_09_lmtb_d_sex_0.csv")
lmtb_dm_wmnd_0           <- iread("2025_06_09_lmtb_dm_wmnd_0.csv")
lmtb_mh_headaches_0      <- iread("2025_06_09_lmtb_mh_headaches_0.csv")
lmtb_p_exercise_0        <- iread("2025_06_09_lmtb_p_exercise_0.csv")
lmtb_p_fam_fn_0          <- iread("2025_06_09_lmtb_p_fam_fn_0.csv")
lmtb_p_friends_0         <- iread("2025_06_09_lmtb_p_friends_0.csv")
lmtb_p_parent_psych_0    <- iread("2025_06_09_lmtb_p_parent_psych_0.csv")
lmtb_p_prosocial_0       <- iread("2025_06_09_lmtb_p_prosocial_0.csv")
lmtb_p_screen_time_0     <- iread("2025_06_09_lmtb_p_screen_time_0.csv")
lmtb_p_sports_0          <- iread("2025_06_09_lmtb_p_sports_0.csv")
lmtb_rm_gord_cor_0       <- iread("2025_06_09_lmtb_rm_gord_cor_0.csv")
lmtb_rm_subc_cor_0       <- iread("2025_06_09_lmtb_rm_subc_cor_0.csv")
lmtb_sds_0               <- iread("2025_06_09_lmtb_sds_0.csv")
lmtb_sm_cort_sa_0        <- iread("2025_06_09_lmtb_sm_cort_sa_0.csv")
lmtb_sm_cort_t_0         <- iread("2025_06_09_lmtb_sm_cort_t_0.csv")
lmtb_sm_subc_v_0         <- iread("2025_06_09_lmtb_sm_subc_v_0.csv")
lmtb_family              <- iread("2025_06_09_lmtb_family.csv")
lmtb_scanner_0           <- iread("2025_06_09_lmtb_scanner_0.csv")
lmtb_site_0              <- iread("2025_06_09_lmtb_site_0.csv")

# LONG MTBI L
lmtb_as_loc_l            <- iread("2025_06_09_lmtb_as_loc_l.csv")
lmtb_as_mechanism_l      <- iread("2025_06_09_lmtb_as_mechanism_l.csv")
lmtb_as_mem_daze_l       <- iread("2025_06_09_lmtb_as_mem_daze_l.csv")
lmtb_cbcl_l              <- iread("2025_06_09_lmtb_cbcl_l.csv")
lmtb_d_income_l          <- iread("2025_06_09_lmtb_d_income_l.csv")
lmtb_d_interview_age_l   <- iread("2025_06_09_lmtb_d_interview_age_l.csv")
lmtb_d_mtbi_age_l        <- iread("2025_06_09_lmtb_d_mtbi_age_l.csv")
lmtb_d_pubertal_status_l <- iread("2025_06_09_lmtb_d_pubertal_status_l.csv")
lmtb_d_race_l            <- iread("2025_06_09_lmtb_d_race_0.csv")
lmtb_d_sex_l             <- iread("2025_06_09_lmtb_d_sex_0.csv")
lmtb_dm_wmnd_l           <- iread("2025_06_09_lmtb_dm_wmnd_l.csv")
lmtb_mh_headaches_l      <- iread("2025_06_09_lmtb_mh_headaches_l.csv")
lmtb_mh_mtbi_count_l     <- iread("2025_06_09_lmtb_mh_mtbi_count_l.csv")
lmtb_p_exercise_l        <- iread("2025_06_09_lmtb_p_exercise_l.csv")
lmtb_p_fam_fn_l          <- iread("2025_06_09_lmtb_p_fam_fn_l.csv")
lmtb_p_friends_l         <- iread("2025_06_09_lmtb_p_friends_l.csv")
lmtb_p_parent_psych_l    <- iread("2025_06_09_lmtb_p_parent_psych_l.csv")
lmtb_p_prosocial_l       <- iread("2025_06_09_lmtb_p_prosocial_l.csv")
lmtb_p_screen_time_l     <- iread("2025_06_09_lmtb_p_screen_time_l.csv")
lmtb_p_sports_l          <- iread("2025_06_09_lmtb_p_sports_l.csv")
lmtb_rm_gord_cor_l       <- iread("2025_06_09_lmtb_rm_gord_cor_l.csv")
lmtb_rm_subc_cor_l       <- iread("2025_06_09_lmtb_rm_subc_cor_l.csv")
lmtb_sds_l               <- iread("2025_06_09_lmtb_sds_l.csv")
lmtb_sm_cort_sa_l        <- iread("2025_06_09_lmtb_sm_cort_sa_l.csv")
lmtb_sm_cort_t_l         <- iread("2025_06_09_lmtb_sm_cort_t_l.csv")
lmtb_sm_subc_v_l         <- iread("2025_06_09_lmtb_sm_subc_v_l.csv")
lmtb_scanner_l           <- iread("2025_06_09_lmtb_scanner_l.csv")
lmtb_site_l              <- iread("2025_06_09_lmtb_site_l.csv")

# BASE MTBI L
# as_loc not extracted
# as_mechanism not extracted
# as_mem_daze not extracted
# mtbi_age not extracted
# mtbi_count not extracted
mtbi_cbcl_l              <- iread("2025_06_09_mtbi_cbcl_l.csv")
mtbi_d_income_l          <- iread("2025_06_09_mtbi_d_income_mtbi_l.csv")
mtbi_d_interview_age_l   <- iread("2025_06_09_mtbi_d_interview_age_mtbi_l.csv")
mtbi_d_pubertal_status_l <- iread("2025_06_09_mtbi_d_pubertal_status_l.csv")
mtbi_dm_wmnd_l           <- iread("2025_06_09_mtbi_dm_wmnd_l.csv")
mtbi_mh_headaches_l      <- iread("2025_06_09_mtbi_mh_headaches_l.csv")
mtbi_p_exercise_l        <- iread("2025_06_09_mtbi_p_exercise_l.csv")
mtbi_p_fam_fn_l          <- iread("2025_06_09_mtbi_p_fam_fn_l.csv")
mtbi_p_friends_l         <- iread("2025_06_09_mtbi_p_friends_l.csv")
mtbi_p_parent_psych_l    <- iread("2025_06_09_mtbi_p_parent_psych_l.csv")
mtbi_p_prosocial_l       <- iread("2025_06_09_mtbi_p_prosocial_l.csv")
mtbi_p_screen_time_l     <- iread("2025_06_09_mtbi_p_screen_time_l.csv")
mtbi_p_sports_l          <- iread("2025_06_09_mtbi_p_sports_l.csv")
mtbi_rm_gord_cor_l       <- iread("2025_06_09_mtbi_rm_gord_cor_l.csv")
mtbi_rm_subc_cor_l       <- iread("2025_06_09_mtbi_rm_subc_cor_l.csv")
mtbi_sds_l               <- iread("2025_06_09_mtbi_sds_l.csv")
mtbi_sm_cort_sa_l        <- iread("2025_06_09_mtbi_sm_cort_sa_l.csv")
mtbi_sm_cort_t_l         <- iread("2025_06_09_mtbi_sm_cort_t_l.csv")
mtbi_sm_subc_v_l         <- iread("2025_06_09_mtbi_sm_subc_v_l.csv")
mtbi_scanner_l           <- iread("2025_06_09_mtbi_scanner_l.csv")
mtbi_site_l              <- iread("2025_06_09_mtbi_site_l.csv")

# BASE unij L
# as_loc not existent
# as_mechanism not existent
# as_mem_daze not existent
# mtbi_age not existent
# mtbi_count not existent
unij_cbcl_l              <- iread("2025_06_09_unij_cbcl_l.csv")
unij_d_income_l          <- iread("2025_06_09_unij_d_income_l.csv")
unij_d_interview_age_l   <- iread("2025_06_09_unij_d_interview_age_l.csv")
unij_d_pubertal_status_l <- iread("2025_06_09_unij_d_pubertal_status_l.csv")
unij_dm_wmnd_l           <- iread("2025_06_09_unij_dm_wmnd_l.csv")
unij_mh_headaches_l      <- iread("2025_06_09_unij_mh_headaches_l.csv")
unij_p_exercise_l        <- iread("2025_06_09_unij_p_exercise_l.csv")
unij_p_fam_fn_l          <- iread("2025_06_09_unij_p_fam_fn_l.csv")
unij_p_friends_l         <- iread("2025_06_09_unij_p_friends_l.csv")
unij_p_parent_psych_l    <- iread("2025_06_09_unij_p_parent_psych_l.csv")
unij_p_prosocial_l       <- iread("2025_06_09_unij_p_prosocial_l.csv")
unij_p_screen_time_l     <- iread("2025_06_09_unij_p_screen_time_l.csv")
unij_p_sports_l          <- iread("2025_06_09_unij_p_sports_l.csv")
unij_rm_gord_cor_l       <- iread("2025_06_09_unij_rm_gord_cor_l.csv")
unij_rm_subc_cor_l       <- iread("2025_06_09_unij_rm_subc_cor_l.csv")
unij_sds_l               <- iread("2025_06_09_unij_sds_l.csv")
unij_sm_cort_sa_l        <- iread("2025_06_09_unij_sm_cort_sa_l.csv")
unij_sm_cort_t_l         <- iread("2025_06_09_unij_sm_cort_t_l.csv")
unij_sm_subc_v_l         <- iread("2025_06_09_unij_sm_subc_v_l.csv")
unij_scanner_l           <- iread("2025_06_09_unij_scanner_l.csv")
unij_site_l              <- iread("2025_06_09_unij_site_l.csv")

# Race and sex are extracted from pre-imputed data
mtbi_d_race_l <- strip_sub_prefix(mtbi_dl$"d_race"$"data")
mtbi_d_sex_l  <- strip_sub_prefix(mtbi_dl$"d_sex"$"data")
mtbi_d_race_l <- strip_sub_prefix(unij_dl$"d_race"$"data")
mtbi_d_sex_l  <- strip_sub_prefix(unij_dl$"d_sex"$"data")
```

# QC

```{r}
# QC data
mri_y_qc_raw_smr_t1 <- abcd_load(core_path("imaging/mri_y_qc_raw_smr_t1.csv"))
mri_y_qc_raw_smr_t2 <- abcd_load(core_path("imaging/mri_y_qc_raw_smr_t2.csv"))
mri_y_qc_raw_rsfmr <- abcd_load(core_path("imaging/mri_y_qc_raw_rsfmr.csv"))
mri_y_qc_raw_dmr <- abcd_load(core_path("imaging/mri_y_qc_raw_dmr.csv"))

qc_pc_helper <- function(t, subjects, type) {
    qc_fns = list(
        "smri"   = qc_smri,
        "dmri"   = qc_dmri,
        "rsfmri" = qc_rsfmri
    )
    qc_dfs = list(
        "smri"   = mri_y_qc_raw_smr_t1,
        "dmri"   = mri_y_qc_raw_dmr,
        "rsfmri" = mri_y_qc_raw_rsfmr
    )
    qc_fn <- qc_fns[[type]]
    qc_df <- qc_dfs[[type]]
    qc_pass <- qc_fn(qc_df, t = t, subjects = subjects, metric = "qc")
    pc_pass <- qc_fn(qc_df, t = t, subjects = subjects, metric = "pc")
    pass <- intersect(qc_pass$"pass", pc_pass$"pass")
    return(pass)
}

lmtb_smri_pass_0 <- qc_pc_helper(t = 0, subjects = lmtb_subs, "smri")
lmtb_smri_pass_l <- qc_pc_helper(t = 2, subjects = lmtb_subs, "smri")
mtbi_smri_pass_l <- qc_pc_helper(t = 2, subjects = mtbi_subs, "smri")
unij_smri_pass_l <- qc_pc_helper(t = 2, subjects = unij_subs, "smri")

lmtb_dmri_pass_0 <- qc_pc_helper(t = 0, subjects = lmtb_subs, "dmri")
lmtb_dmri_pass_l <- qc_pc_helper(t = 2, subjects = lmtb_subs, "dmri")
mtbi_dmri_pass_l <- qc_pc_helper(t = 2, subjects = mtbi_subs, "dmri")
unij_dmri_pass_l <- qc_pc_helper(t = 2, subjects = unij_subs, "dmri")

lmtb_rmri_pass_0 <- qc_pc_helper(t = 0, subjects = lmtb_subs, "rsfmri")
lmtb_rmri_pass_l <- qc_pc_helper(t = 2, subjects = lmtb_subs, "rsfmri")
mtbi_rmri_pass_l <- qc_pc_helper(t = 2, subjects = mtbi_subs, "rsfmri")
unij_rmri_pass_l <- qc_pc_helper(t = 2, subjects = unij_subs, "rsfmri")

# rs-fMRI
lmtb_sm_subc_v_qc_0   <- filter(lmtb_sm_subc_v_0,   subjectkey %in% lmtb_smri_pass_0)
lmtb_sm_cort_t_qc_0   <- filter(lmtb_sm_cort_t_0,   subjectkey %in% lmtb_smri_pass_0)
lmtb_sm_cort_sa_qc_0  <- filter(lmtb_sm_cort_sa_0,  subjectkey %in% lmtb_smri_pass_0)
lmtb_dm_wmnd_qc_0     <- filter(lmtb_dm_wmnd_0,     subjectkey %in% lmtb_dmri_pass_0)
lmtb_rm_gord_cor_qc_0 <- filter(lmtb_rm_gord_cor_0, subjectkey %in% lmtb_rmri_pass_0)
lmtb_rm_subc_cor_qc_0 <- filter(lmtb_rm_subc_cor_0, subjectkey %in% lmtb_rmri_pass_0)

lmtb_sm_subc_v_qc_l   <- filter(lmtb_sm_subc_v_l,   subjectkey %in% lmtb_smri_pass_l)
lmtb_sm_cort_t_qc_l   <- filter(lmtb_sm_cort_t_l,   subjectkey %in% lmtb_smri_pass_l)
lmtb_sm_cort_sa_qc_l  <- filter(lmtb_sm_cort_sa_l,  subjectkey %in% lmtb_smri_pass_l)
lmtb_dm_wmnd_qc_l     <- filter(lmtb_dm_wmnd_l,     subjectkey %in% lmtb_dmri_pass_l)
lmtb_rm_gord_cor_qc_l <- filter(lmtb_rm_gord_cor_l, subjectkey %in% lmtb_rmri_pass_l)
lmtb_rm_subc_cor_qc_l <- filter(lmtb_rm_subc_cor_l, subjectkey %in% lmtb_rmri_pass_l)

mtbi_sm_subc_v_qc_l   <- filter(mtbi_sm_subc_v_l,   subjectkey %in% mtbi_smri_pass_l)
mtbi_sm_cort_t_qc_l   <- filter(mtbi_sm_cort_t_l,   subjectkey %in% mtbi_smri_pass_l)
mtbi_sm_cort_sa_qc_l  <- filter(mtbi_sm_cort_sa_l,  subjectkey %in% mtbi_smri_pass_l)
mtbi_dm_wmnd_qc_l     <- filter(mtbi_dm_wmnd_l,     subjectkey %in% mtbi_dmri_pass_l)
mtbi_rm_gord_cor_qc_l <- filter(mtbi_rm_gord_cor_l, subjectkey %in% mtbi_rmri_pass_l)
mtbi_rm_subc_cor_qc_l <- filter(mtbi_rm_subc_cor_l, subjectkey %in% mtbi_rmri_pass_l)

unij_sm_subc_v_qc_l   <- filter(unij_sm_subc_v_l,   subjectkey %in% smri_unij_pass_l)
unij_sm_cort_t_qc_l   <- filter(unij_sm_cort_t_l,   subjectkey %in% smri_unij_pass_l)
unij_sm_cort_sa_qc_l  <- filter(unij_sm_cort_sa_l,  subjectkey %in% smri_unij_pass_l)
unij_dm_wmnd_qc_l     <- filter(unij_dm_wmnd_l,     subjectkey %in% dmri_unij_pass_l)
unij_rm_gord_cor_qc_l <- filter(unij_rm_gord_cor_l, subjectkey %in% rmri_unij_pass_l)
unij_rm_subc_cor_qc_l <- filter(unij_rm_subc_cor_l, subjectkey %in% rmri_unij_pass_l)

iwrite(lmtb_sm_subc_v_qc_0, "lmtb_sm_subc_v_qc_0.csv")
iwrite(lmtb_sm_cort_t_qc_0, "lmtb_sm_cort_t_qc_0.csv")
iwrite(lmtb_sm_cort_sa_qc_0, "lmtb_sm_cort_sa_qc_0.csv")
iwrite(lmtb_dm_wmnd_qc_0, "lmtb_dm_wmnd_qc_0.csv")
iwrite(lmtb_rm_gord_cor_qc_0, "lmtb_rm_gord_cor_qc_0.csv")
iwrite(lmtb_rm_subc_cor_qc_0, "lmtb_rm_subc_cor_qc_0.csv")
iwrite(lmtb_sm_subc_v_qc_l, "lmtb_sm_subc_v_qc_l.csv")
iwrite(lmtb_sm_cort_t_qc_l, "lmtb_sm_cort_t_qc_l.csv")
iwrite(lmtb_sm_cort_sa_qc_l, "lmtb_sm_cort_sa_qc_l.csv")
iwrite(lmtb_dm_wmnd_qc_l, "lmtb_dm_wmnd_qc_l.csv")
iwrite(lmtb_rm_gord_cor_qc_l, "lmtb_rm_gord_cor_qc_l.csv")
iwrite(lmtb_rm_subc_cor_qc_l, "lmtb_rm_subc_cor_qc_l.csv")
iwrite(sm_subc_v_qc_base_mtbi_l, "sm_subc_v_qc_base_mtbi_l.csv")
iwrite(sm_cort_t_qc_base_mtbi_l, "sm_cort_t_qc_base_mtbi_l.csv")
iwrite(sm_cort_sa_qc_base_mtbi_l, "sm_cort_sa_qc_base_mtbi_l.csv")
iwrite(dm_wmnd_qc_base_mtbi_l, "dm_wmnd_qc_base_mtbi_l.csv")
iwrite(rm_gord_cor_qc_base_mtbi_l, "rm_gord_cor_qc_base_mtbi_l.csv")
iwrite(rm_subc_cor_qc_base_mtbi_l, "rm_subc_cor_qc_base_mtbi_l.csv")
iwrite(sm_subc_v_qc_base_unij_l, "sm_subc_v_qc_base_unij_l.csv")
iwrite(sm_cort_t_qc_base_unij_l, "sm_cort_t_qc_base_unij_l.csv")
iwrite(sm_cort_sa_qc_base_unij_l, "sm_cort_sa_qc_base_unij_l.csv")
iwrite(dm_wmnd_qc_base_unij_l, "dm_wmnd_qc_base_unij_l.csv")
iwrite(rm_gord_cor_qc_base_unij_l, "rm_gord_cor_qc_base_unij_l.csv")
iwrite(rm_subc_cor_qc_base_unij_l, "rm_subc_cor_qc_base_unij_l.csv")
```

```{r}
lmtb_sm_subc_v_qc_0   <- iread("2025_02_13_lmtb_sm_subc_v_qc_0.csv")
lmtb_sm_cort_t_qc_0   <- iread("2025_02_13_lmtb_sm_cort_t_qc_0.csv")
lmtb_sm_cort_sa_qc_0  <- iread("2025_02_13_lmtb_sm_cort_sa_qc_0.csv")
lmtb_dm_wmnd_qc_0 <- iread("2025_03_10_lmtb_dm_wmnd_qc_0.csv")
lmtb_rm_gord_cor_qc_0 <- iread("2025_02_13_lmtb_rm_gord_cor_qc_0.csv")
lmtb_rm_subc_cor_qc_0 <- iread("2025_02_13_lmtb_rm_subc_cor_qc_0.csv")

lmtb_sm_subc_v_qc_l   <- iread("2025_02_13_lmtb_sm_subc_v_qc_l.csv")
lmtb_sm_cort_t_qc_l   <- iread("2025_02_13_lmtb_sm_cort_t_qc_l.csv")
lmtb_sm_cort_sa_qc_l  <- iread("2025_02_13_lmtb_sm_cort_sa_qc_l.csv")
lmtb_dm_wmnd_qc_l <- iread("2025_02_13_lmtb_dm_wmnd_qc_l.csv")
lmtb_rm_gord_cor_qc_l <- iread("2025_02_13_lmtb_rm_gord_cor_qc_l.csv")
lmtb_rm_subc_cor_qc_l <- iread("2025_02_13_lmtb_rm_subc_cor_qc_l.csv")

mtbi_sm_subc_v_qc_l   <- iread("2025_02_13_mtbi_sm_subc_v_qc_l.csv")
mtbi_sm_cort_t_qc_l   <- iread("2025_02_13_mtbi_sm_cort_t_qc_l.csv")
mtbi_sm_cort_sa_qc_l  <- iread("2025_02_13_mtbi_sm_cort_sa_qc_l.csv")
mtbi_dm_wmnd_qc_l <- iread("2025_02_13_mtbi_dm_wmnd_qc_l.csv")
mtbi_rm_gord_cor_qc_l <- iread("2025_02_13_mtbi_rm_gord_cor_qc_l.csv")
mtbi_rm_subc_cor_qc_l <- iread("2025_02_13_mtbi_rm_subc_cor_qc_l.csv")

unij_sm_subc_v_qc_l   <- iread("2025_02_13_unij_sm_subc_v_qc_l.csv")
unij_sm_cort_t_qc_l   <- iread("2025_02_13_unij_sm_cort_t_qc_l.csv")
unij_sm_cort_sa_qc_l  <- iread("2025_02_13_unij_sm_cort_sa_qc_l.csv")
unij_dm_wmnd_qc_l <- iread("2025_02_13_unij_dm_wmnd_qc_l.csv")
unij_rm_gord_cor_qc_l <- iread("2025_02_13_unij_rm_gord_cor_qc_l.csv")
unij_rm_subc_cor_qc_l <- iread("2025_02_13_unij_rm_subc_cor_qc_l.csv")
```

Building dataframes for imputation:

```{r}
long_mtbi_0_list <- list(
    d_interview_age_long_mtbi_0,
    d_sex_long_mtbi_0,
    d_income_long_mtbi_0,
    d_race_long_mtbi_0,
    d_pubertal_status_long_mtbi_0,
    mh_headaches_long_mtbi_0,
    sm_subc_v_qc_long_mtbi_0,
    sm_cort_t_qc_long_mtbi_0,
    sm_cort_sa_qc_long_mtbi_0,
    dm_wmnd_qc_long_mtbi_0,
    rm_gord_cor_qc_long_mtbi_0,
    rm_subc_cor_qc_long_mtbi_0,
    p_friends_long_mtbi_0,
    p_screen_time_long_mtbi_0,
    p_sports_long_mtbi_0,
    p_exercise_long_mtbi_0,
    p_prosocial_long_mtbi_0,
    p_fam_fn_long_mtbi_0,
    p_parent_psych_long_mtbi_0,
    cbcl_long_mtbi_0,
    sds_long_mtbi_0
)
long_mtbi_0_df <- merge_df_list(long_mtbi_0_list, join = "full", uid = "subjectkey")
long_mtbi_0_df

long_mtbi_l_list <- list(
    as_mem_daze_long_mtbi_l,
    as_mechanism_long_mtbi_l,
    as_loc_long_mtbi_l,
    d_interview_age_long_mtbi_l,
    d_mtbi_age_long_mtbi_l,
    d_sex_long_mtbi_l,
    d_income_long_mtbi_l,
    d_race_long_mtbi_l,
    d_pubertal_status_long_mtbi_l,
    mh_headaches_long_mtbi_l,
    mh_mtbi_count_long_mtbi_l,
    sm_subc_v_qc_long_mtbi_l,
    sm_cort_t_qc_long_mtbi_l,
    sm_cort_sa_qc_long_mtbi_l,
    dm_wmnd_qc_long_mtbi_l,
    rm_gord_cor_qc_long_mtbi_l,
    rm_subc_cor_qc_long_mtbi_l,
    p_friends_long_mtbi_l,
    p_screen_time_long_mtbi_l,
    p_sports_long_mtbi_l,
    p_exercise_long_mtbi_l,
    p_prosocial_long_mtbi_l,
    p_fam_fn_long_mtbi_l,
    p_parent_psych_long_mtbi_l,
    cbcl_long_mtbi_l,
    sds_long_mtbi_l
)
long_mtbi_l_df <- merge_df_list(long_mtbi_l_list, join = "full", uid = "subjectkey")
long_mtbi_l_df

base_mtbi_l_list <- list(
    d_interview_age_base_mtbi_l,
    d_sex_base_mtbi_l,
    d_income_base_mtbi_l,
    d_race_base_mtbi_l,
    d_pubertal_status_base_mtbi_l,
    mh_headaches_base_mtbi_l,
    sm_subc_v_qc_base_mtbi_l,
    sm_cort_t_qc_base_mtbi_l,
    sm_cort_sa_qc_base_mtbi_l,
    dm_wmnd_qc_base_mtbi_l,
    rm_gord_cor_qc_base_mtbi_l,
    rm_subc_cor_qc_base_mtbi_l,
    p_friends_base_mtbi_l,
    p_screen_time_base_mtbi_l,
    p_sports_base_mtbi_l,
    p_exercise_base_mtbi_l,
    p_prosocial_base_mtbi_l,
    p_fam_fn_base_mtbi_l,
    p_parent_psych_base_mtbi_l,
    cbcl_base_mtbi_l,
    sds_base_mtbi_l
)
base_mtbi_l_df <- merge_df_list(base_mtbi_l_list, join = "full", uid = "subjectkey")
base_mtbi_l_df


base_unij_l_list <- list(
    d_interview_age_base_unij_l,
    d_sex_base_unij_l,
    d_income_base_unij_l,
    d_race_base_unij_l,
    d_pubertal_status_base_unij_l,
    mh_headaches_base_unij_l,
    sm_subc_v_qc_base_unij_l,
    sm_cort_t_qc_base_unij_l,
    sm_cort_sa_qc_base_unij_l,
    dm_wmnd_qc_base_unij_l,
    rm_gord_cor_qc_base_unij_l,
    rm_subc_cor_qc_base_unij_l,
    p_friends_base_unij_l,
    p_screen_time_base_unij_l,
    p_sports_base_unij_l,
    p_exercise_base_unij_l,
    p_prosocial_base_unij_l,
    p_fam_fn_base_unij_l,
    p_parent_psych_base_unij_l,
    cbcl_base_unij_l,
    sds_base_unij_l
)
base_unij_l_df <- merge_df_list(base_unij_l_list, join = "full", uid = "subjectkey")
base_unij_l_df

write_csv(long_mtbi_0_df, input_path("long_mtbi_0_df.csv", TRUE))
write_csv(long_mtbi_l_df, input_path("long_mtbi_l_df.csv", TRUE))
write_csv(base_mtbi_l_df, input_path("base_mtbi_l_df.csv", TRUE))
write_csv(base_unij_l_df, input_path("base_unij_l_df.csv", TRUE))
```

```{r}
# CHECKPOINT
long_mtbi_0_df <- data.frame(read_csv(input_path("2025_03_10_long_mtbi_0_df.csv")))
long_mtbi_l_df <- data.frame(read_csv(input_path("2025_02_13_long_mtbi_l_df.csv")))
base_mtbi_l_df <- data.frame(read_csv(input_path("2025_02_13_base_mtbi_l_df.csv")))
base_unij_l_df <- data.frame(read_csv(input_path("2025_02_13_base_unij_l_df.csv")))
```

```{r}
# Remove the subjectkey variable
long_mtbi_0_df_no_subs <- char_to_fac(long_mtbi_0_df[, -1])
long_mtbi_l_df_no_subs <- char_to_fac(long_mtbi_l_df[, -1])
base_mtbi_l_df_no_subs <- char_to_fac(base_mtbi_l_df[, -1])
base_unij_l_df_no_subs <- char_to_fac(base_unij_l_df[, -1])
```

Imputation functions (from ch03):

```{r}
pairwise_correlations <- function(df, threshold = 0) {
    df <- na.omit(df)
    non_numeric_cols <- sapply(df, function(x) !is.numeric(x))
    df <- df[, !non_numeric_cols]
    correlations <- cor(df)
    diag(correlations) <- 0
    abs_cor <- abs(correlations)
    pairs <- t(combn(colnames(abs_cor), 2))
    paired_cors <- data.frame(pairs, cor = abs_cor[pairs])
    paired_cors <- paired_cors[paired_cors$"cor" > threshold, ]
    return(paired_cors)
}

top_correlating_vars <- function(df, threshold = 0) {
    df <- pairwise_correlations(df, threshold)
    max_cor_df <- data.frame(
        variable = as.character(),
        max_cor = as.numeric()
    )
    i <- 0
    while (nrow(df) > 0) {
        i <- i + 1
        row_with_max_cor <- which(df$"cor" == max(df$"cor"))[1]
        var_with_max_cor <- df[row_with_max_cor, "X1"]
        max_cor <- df[row_with_max_cor, "cor"]
        max_cor_df <- rbind(
            max_cor_df,
            data.frame(
                variable = var_with_max_cor,
                max_cor = max_cor
            )
        )
        df <- dplyr::filter(
            df,
            df$"X1" != var_with_max_cor & df$"X2" != var_with_max_cor
        )
    }
    return(max_cor_df)
}

build_pred_mat <- function(df, n_predictors = 1) {
    pred_mat <- matrix(
        nrow = ncol(df),
        ncol = ncol(df),
        data = 1
    )
    colnames(pred_mat) <- colnames(df)
    rownames(pred_mat) <- colnames(df)
    diag(pred_mat) <- 0
    pred_mat_vars <- top_correlating_vars(df)
    vars_to_drop <- pred_mat_vars$"variable"[seq_len(n_predictors)]
    print(paste0("Dropping: ", paste(vars_to_drop, collapse = ", ")))
    pred_mat[, vars_to_drop] <- 0
    return(pred_mat)
}
```

```{r}
imputed_long_mtbi_0 <- futuremice(
    long_mtbi_0_df_no_subs,
    m = 5,
    maxit = 10,
    parallelseed = 42
)

long_mtbi_0_pred_mat <- build_pred_mat(long_mtbi_0_df_no_subs, 1)
write.table(long_mtbi_0_pred_mat, proc_path("long_mtbi_0_pred_mat.txt", TRUE))
long_mtbi_0_pred_mat <- as.matrix(read.table(proc_path("2025_03_10_long_mtbi_0_pred_mat.txt")))
storage.mode(long_mtbi_0_pred_mat) <- "double"
imputed_long_mtbi_0 <- futuremice(
    long_mtbi_0_df_no_subs,
    m = 5,
    maxit = 10,
    parallelseed = 42,
    predictorMatrix = long_mtbi_0_pred_mat
)
#
saveRDS(imputed_long_mtbi_0, file = proc_path("long_mtbi_0_imputed.rds", TRUE))
imputed_long_mtbi_0 <- readRDS(proc_path("2025_03_10_long_mtbi_0_imputed.rds"))
#
five_imputed_long_mtbi_0 <- complete(imputed_long_mtbi_0, action = "long", include = TRUE)
write_csv(five_imputed_long_mtbi_0, input_path("five_imputed_long_mtbi_0.csv", TRUE))
five_imputed_long_mtbi_0 <- read_csv(input_path("2025_03_10_five_imputed_long_mtbi_0.csv"))
```

```{r}
long_mtbi_l_pred_mat <- build_pred_mat(long_mtbi_l_df_no_subs, 1)
write.table(long_mtbi_l_pred_mat, proc_path("long_mtbi_l_pred_mat.txt", TRUE))
long_mtbi_l_pred_mat <- as.matrix(read.table(proc_path("2025_02_13_long_mtbi_l_pred_mat.txt")))
storage.mode(long_mtbi_l_pred_mat) <- "double"

imputed_long_mtbi_l <- futuremice(
    long_mtbi_l_df_no_subs,
    m = 5,
    maxit = 10,
    parallelseed = 42,
    predictorMatrix = long_mtbi_l_pred_mat
)

saveRDS(imputed_long_mtbi_l, file = proc_path("long_mtbi_l_imputed.rds", TRUE))
imputed_long_mtbi_l <- readRDS(proc_path("2025_02_13_long_mtbi_l_imputed.rds"))
five_imputed_long_mtbi_l <- complete(imputed_long_mtbi_l, action = "long", include = TRUE)
write_csv(five_imputed_long_mtbi_l, input_path("five_imputed_long_mtbi_l.csv", TRUE))
five_imputed_long_mtbi_l <- read_csv(input_path("2025_02_13_five_imputed_long_mtbi_l.csv"))
```


```{r}
base_mtbi_l_pred_mat <- build_pred_mat(base_mtbi_l_df_no_subs, 1)
write.table(base_mtbi_l_pred_mat, proc_path("base_mtbi_l_pred_mat.txt", TRUE))
base_mtbi_l_pred_mat <- as.matrix(read.table(proc_path("2025_02_13_base_mtbi_l_pred_mat.txt")))
storage.mode(base_mtbi_l_pred_mat) <- "double"

imputed_base_mtbi_l <- futuremice(
    base_mtbi_l_df_no_subs,
    m = 5,
    maxit = 10,
    parallelseed = 42,
    predictorMatrix = base_mtbi_l_pred_mat
)

saveRDS(imputed_base_mtbi_l, file = proc_path("base_mtbi_l_imputed.rds", TRUE))
imputed_base_mtbi_l <- readRDS(proc_path("2025_02_13_base_mtbi_l_imputed.rds"))

five_imputed_base_mtbi_l <- complete(imputed_base_mtbi_l, action = "long", include = TRUE)
write_csv(five_imputed_base_mtbi_l, input_path("five_imputed_base_mtbi_l.csv", TRUE))
five_imputed_base_mtbi_l <- read_csv(input_path("2025_02_13_five_imputed_base_mtbi_l.csv"))

base_unij_l_pred_mat <- build_pred_mat(base_unij_l_df_no_subs, 1)
write.table(base_unij_l_pred_mat, proc_path("base_unij_l_pred_mat.txt", TRUE))
base_unij_l_pred_mat <- as.matrix(read.table(proc_path("2025_02_13_base_unij_l_pred_mat.txt")))
storage.mode(base_unij_l_pred_mat) <- "double"

imputed_base_unij_l <- futuremice(
    base_unij_l_df_no_subs,
    m = 5,
    maxit = 10,
    parallelseed = 42,
    predictorMatrix = base_unij_l_pred_mat
)

saveRDS(imputed_base_unij_l, file = proc_path("base_unij_l_imputed.rds", TRUE))
imputed_base_unij_l <- readRDS(proc_path("2025_02_13_base_unij_l_imputed.rds"))

five_imputed_base_unij_l <- complete(imputed_base_unij_l, action = "long", include = TRUE)
write_csv(five_imputed_base_unij_l, input_path("five_imputed_base_unij_l.csv", TRUE))
five_imputed_base_unij_l <- read_csv(input_path("2025_02_13_five_imputed_base_unij_l.csv"))
```

```{r}
five_imputed_long_mtbi_0 <- read_csv(input_path("2025_03_10_five_imputed_long_mtbi_0.csv"))
five_imputed_long_mtbi_l <- read_csv(input_path("2025_02_13_five_imputed_long_mtbi_l.csv"))
five_imputed_base_mtbi_l <- read_csv(input_path("2025_02_13_five_imputed_base_mtbi_l.csv"))
five_imputed_base_unij_l <- read_csv(input_path("2025_02_13_five_imputed_base_unij_l.csv"))

named_imputed_long_mtbi_0 <- dplyr::mutate(five_imputed_long_mtbi_0, "subjectkey" = rep(long_mtbi_subs, 6))
named_imputed_long_mtbi_l <- dplyr::mutate(five_imputed_long_mtbi_l, "subjectkey" = rep(long_mtbi_subs, 6))
named_imputed_base_mtbi_l <- dplyr::mutate(five_imputed_base_mtbi_l, "subjectkey" = rep(base_mtbi_subs, 6))
named_imputed_base_unij_l <- dplyr::mutate(five_imputed_base_unij_l, "subjectkey" = rep(base_unij_subs, 6))

write_csv(named_imputed_long_mtbi_0, input_path("named_imputed_long_mtbi_0.csv", TRUE))
write_csv(named_imputed_long_mtbi_l, input_path("named_imputed_long_mtbi_l.csv", TRUE))
write_csv(named_imputed_base_mtbi_l, input_path("named_imputed_base_mtbi_l.csv", TRUE))
write_csv(named_imputed_base_unij_l, input_path("named_imputed_base_unij_l.csv", TRUE))
```

```{r}
# CHECKPOINT
named_imputed_long_mtbi_0 <- read_csv(input_path("2025_03_10_named_imputed_long_mtbi_0.csv"))
named_imputed_long_mtbi_l <- read_csv(input_path("2025_02_13_named_imputed_long_mtbi_l.csv"))
named_imputed_base_mtbi_l <- read_csv(input_path("2025_02_13_named_imputed_base_mtbi_l.csv"))
named_imputed_base_unij_l <- read_csv(input_path("2025_02_13_named_imputed_base_unij_l.csv"))
```

# mTBI subsetting

```{r}
extract_imputed <- function(original_df, imputed_df, partition) {
    return(imputed_df[imputed_df$".imp" == partition, colnames(original_df)])
}

parse_imputations <- function(original_df_list, complete_imputed_df, imps) {
    parsed_imputations <- original_df_list |>
        lapply(
            function(x) {
                imputations <- list()
                for (i in seq_len(imps)) {
                    imputations[[i]] <- extract_imputed(
                        x,
                        complete_imputed_df,
                        i - 1
                    )
                }
                names(imputations) <- paste0("imp_", seq_len(imps) - 1)
                return(imputations)
            }
        )
    names(parsed_imputations) <- gsub("_mtbi$", "", names(parsed_imputations))
    names(parsed_imputations) <- gsub("_unij$", "", names(parsed_imputations))
    return(parsed_imputations)
}

names(long_mtbi_0_list) <- c(
    "d_interview_age",
    "d_sex",
    "d_income",
    "d_race",
    "d_pubertal_status",
    "mh_headaches",
    "sm_subc_v_qc",
    "sm_cort_t_qc",
    "sm_cort_sa_qc",
    "dm_wmnd_qc",
    "rm_gord_cor_qc",
    "rm_subc_cor_qc",
    "p_friends",
    "p_screen_time",
    "p_sports",
    "p_exercise",
    "p_prosocial",
    "p_fam_fn",
    "p_parent_psych",
    "cbcl",
    "sds"
)

names(long_mtbi_l_list) <- c(
    "as_mem_daze",
    "as_mechanism",
    "as_loc",
    "d_interview_age",
    "d_mtbi_age",
    "d_sex",
    "d_income",
    "d_race",
    "d_pubertal_status",
    "mh_headaches",
    "mh_mtbi_count",
    "sm_subc_v_qc",
    "sm_cort_t_qc",
    "sm_cort_sa_qc",
    "dm_wmnd_qc",
    "rm_gord_cor_qc",
    "rm_subc_cor_qc",
    "p_friends",
    "p_screen_time",
    "p_sports",
    "p_exercise",
    "p_prosocial",
    "p_fam_fn",
    "p_parent_psych",
    "cbcl",
    "sds"
)

names(base_mtbi_l_list) <- c(
    "d_interview_age",
    "d_sex",
    "d_income",
    "d_race",
    "d_pubertal_status",
    "mh_headaches",
    "sm_subc_v_qc",
    "sm_cort_t_qc",
    "sm_cort_sa_qc",
    "dm_wmnd_qc",
    "rm_gord_cor_qc",
    "rm_subc_cor_qc",
    "p_friends",
    "p_screen_time",
    "p_sports",
    "p_exercise",
    "p_prosocial",
    "p_fam_fn",
    "p_parent_psych",
    "cbcl",
    "sds"
)

names(base_unij_l_list) <- c(
    "d_interview_age",
    "d_sex",
    "d_income",
    "d_race",
    "d_pubertal_status",
    "mh_headaches",
    "sm_subc_v_qc",
    "sm_cort_t_qc",
    "sm_cort_sa_qc",
    "dm_wmnd_qc",
    "rm_gord_cor_qc",
    "rm_subc_cor_qc",
    "p_friends",
    "p_screen_time",
    "p_sports",
    "p_exercise",
    "p_prosocial",
    "p_fam_fn",
    "p_parent_psych",
    "cbcl",
    "sds"
)

long_mtbi_0_pi <- parse_imputations(long_mtbi_0_list, named_imputed_long_mtbi_0, 6)
long_mtbi_l_pi <- parse_imputations(long_mtbi_l_list, named_imputed_long_mtbi_l, 6)
base_mtbi_l_pi <- parse_imputations(base_mtbi_l_list, named_imputed_base_mtbi_l, 6)
base_unij_l_pi <- parse_imputations(base_unij_l_list, named_imputed_base_unij_l, 6)

list.save(long_mtbi_0_pi, input_path("long_mtbi_0_pi.rds", TRUE))
list.save(long_mtbi_l_pi, input_path("long_mtbi_l_pi.rds", TRUE))
list.save(base_mtbi_l_pi, input_path("base_mtbi_l_pi.rds", TRUE))
list.save(base_unij_l_pi, input_path("base_unij_l_pi.rds", TRUE))
```

Re-reading:

```{r}
long_mtbi_0_pi <- list.load(input_path("2025_03_10_long_mtbi_0_pi.rds"))
long_mtbi_l_pi <- list.load(input_path("2025_02_13_long_mtbi_l_pi.rds"))
base_mtbi_l_pi <- list.load(input_path("2025_02_13_base_mtbi_l_pi.rds"))
base_unij_l_pi <- list.load(input_path("2025_02_13_base_unij_l_pi.rds"))
```

## Constructing data_lists

```{r}
long_mtbi_0_dls <- build_unij_dls(long_mtbi_0_pi)
long_mtbi_l_dls <- build_dls(long_mtbi_l_pi)
base_mtbi_l_dls <- build_unij_dls(base_mtbi_l_pi)
base_unij_l_dls <- build_unij_dls(base_unij_l_pi)
long_mtbi_0_ols <- build_ols(long_mtbi_0_pi)
long_mtbi_l_ols <- build_ols(long_mtbi_l_pi)
base_mtbi_l_ols <- build_ols(base_mtbi_l_pi)
base_unij_l_ols <- build_ols(base_unij_l_pi)

all_long_dls <- list(
    "long_mtbi_0_dls" = long_mtbi_0_dls,
    "long_mtbi_l_dls" = long_mtbi_l_dls,
    "base_mtbi_l_dls" = base_mtbi_l_dls,
    "base_unij_l_dls" = base_unij_l_dls,
    "long_mtbi_0_ols" = long_mtbi_0_ols,
    "long_mtbi_l_ols" = long_mtbi_l_ols,
    "base_mtbi_l_ols" = base_mtbi_l_ols,
    "base_unij_l_ols" = base_unij_l_ols
)
```

## Renaming the initial data

```{r}
name_changes <- c(
    "mtbi_mechanism" = "latest_mtbi_mechanism",
    "mtbi_mem_daze" = "latest_mtbi_mem_daze",
    "mtbi_loc" = "latest_mtbi_loc",
    "mtbi_age" = "latest_mtbi_age",
    "age" = "interview_age",
    "parent_thought" = "asr_scr_thought_r",
    "parent_aggressive" = "asr_scr_aggressive_r",
    "parent_antisocial" = "asr_scr_antisocial_r",
    "parent_hyperactive" = "asr_scr_hyperactive_r",
    "parent_attention" = "asr_scr_attention_r",
    "parent_anxdep" = "asr_scr_anxdep_r",
    "parent_depress" = "asr_scr_depress_r",
    "parent_withdrawn" = "asr_scr_withdrawn_r",
    "parent_avoidant" = "asr_scr_avoidant_r",
    "parent_anxdisord" = "asr_scr_anxdisord_r",
    "parent_somatic" = "asr_scr_somatic_r",
    "parent_intrusive" = "asr_scr_intrusive_r",
    "parent_perstr" = "asr_scr_perstr_r",
    "sds_sleep" = "sds_p_ss_total",
    "cbcl_somatic" = "cbcl_scr_syn_somatic_r",
    "cbcl_social" = "cbcl_scr_syn_social_r",
    "cbcl_anxdep" = "cbcl_scr_syn_anxdep_r",
    "cbcl_thought" = "cbcl_scr_syn_thought_r",
    "cbcl_attention" = "cbcl_scr_syn_attention_r",
    "cbcl_withdep" = "cbcl_scr_syn_withdep_r",
    "cbcl_aggressive" = "cbcl_scr_syn_aggressive_r",
    "cbcl_rulebreak" = "cbcl_scr_syn_rulebreak_r",
    "family_fight_y" = "q1_fight_y",
    "family_angry_y" = "q2_angry_y",
    "family_throw_y" = "q3_throw_y",
    "family_temper_y" = "q4_temper_y",
    "family_criticize_y" = "q5_criticize_y",
    "family_hit_y" = "q6_hit_y",
    "family_peaceful_y" = "q7_peaceful_y",
    "family_outdo_y" = "q8_outdo_y",
    "family_yell_y" = "q9_yell_y",
    "family_fight_p" = "q1_fight_p",
    "family_angry_p" = "q2_angry_p",
    "family_throw_p" = "q3_throw_p",
    "family_temper_p" = "q4_temper_p",
    "family_criticize_p" = "q5_criticize_p",
    "family_hit_p" = "q6_hit_p",
    "family_peaceful_p" = "q7_peaceful_p",
    "family_outdo_p" = "q8_outdo_p",
    "family_yell_p" = "q9_yell_p",
    "headache_history" = "headache",
    "previous_mtbis" = "mtbi_count",
    "brain_volume" = "smri_vol_scs_wholeb",
    "cortical_thickness" = "smri_thick_cdk_mean",
    "cortical_sa" = "smri_area_cdk_total",
    "major_wm_ndi" = "dmri_rsirnd_fib_allfib",
    "pericortical_wm_ndi" = "dmri_rsirndwm_cdk_mean",
    "fmri_cort_cors" = "avg_gord_cor",
    "fmri_cort_subcort_cors" = "avg_subc_cor",
    "same_sex_friend" = "ss_friend",
    "opp_sex_friend" = "os_friend",
    "same_sex_close_friend" = "ss_close_friend",
    "opp_sex_close_friend" = "os_close_friend",
    "weekend_screentime" = "screentime_wknd_hrs",
    "weekday_screentime" = "screentime_wkday_hrs"
)

all_long_dls <- all_long_dls |>
    lapply(
        function(data_lists_of_group) {
            lapply(
                data_lists_of_group,
                function(data_list) {
                    data_list <- as_data_list(rename_dl(data_list, name_changes))
                }
            )
        }
    )

# 2025-03-10
saveRDS(all_long_dls, input_path("all_long_dls.rds", TRUE))
```
