# Data extraction

Load libraries and establish paths.

```{r}
library(ggplot2)
library(readr)
library(dplyr)
library(here)
library(abcdutils)

core_path <- path_maker(here(paste0("data/abcd/core")))
input_path <- path_maker(here(paste0("data/abcd/inputs")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))

read <- function(path) {
    return(abcd_load(core_path(path)))
}
```

Import raw data.

```{r}
ph_p_otbi <- read("physical-health/ph_p_otbi.csv")
abcd_y_lt <- read("abcd-general/abcd_y_lt.csv")
ph_y_pds <- read("physical-health/ph_y_pds.csv")
ph_p_pds <- read("physical-health/ph_p_pds.csv")
gish_p_gi <- read("gender-identity-sexual-health/gish_p_gi.csv")
abcd_p_demo <- read("abcd-general/abcd_p_demo.csv")
ph_p_mhx <- read("physical-health/ph_p_mhx.csv")
mri_y_smr_vol_aseg <- read("imaging/mri_y_smr_vol_aseg.csv")
mri_y_smr_thk_dsk <- read("imaging/mri_y_smr_thk_dsk.csv")
mri_y_smr_area_dsk <- read("imaging/mri_y_smr_area_dsk.csv")
mri_y_rsi_rnd_at <- read("imaging/mri_y_rsi_rnd_at.csv")
mri_y_rsi_rnd_wm_dsk <- read("imaging/mri_y_rsi_rnd_wm_dsk.csv")
mri_y_rsi_rnd_wm_dst <- read("imaging/mri_y_rsi_rnd_wm_dst.csv")
mri_y_rsfmr_cor_gp_gp <- read("imaging/mri_y_rsfmr_cor_gp_gp.csv")
mri_y_rsfmr_cor_gp_aseg <- read("imaging/mri_y_rsfmr_cor_gp_aseg.csv")
mh_y_or <- read("mental-health/mh_y_or.csv")
nt_p_stq <- read("novel-technologies/nt_p_stq.csv")
ph_p_saiq <- read("physical-health/ph_p_saiq.csv")
ph_y_yrb <- read("physical-health/ph_y_yrb.csv")
ce_y_psb <- read("culture-environment/ce_y_psb.csv")
ce_p_psb <- read("culture-environment/ce_p_psb.csv")
ce_y_fes <- read("culture-environment/ce_y_fes.csv")
ce_p_fes <- read("culture-environment/ce_p_fes.csv")
mh_p_asr <- read("mental-health/mh_p_asr.csv")
mh_p_cbcl <- read("mental-health/mh_p_cbcl.csv")
ph_p_sds <- read("physical-health/ph_p_sds.csv")
```

## Subjects

We will now look at:

1. (A: "mtbi_subjects.csv") baseline mTBI subjects, long
    - What happened to them after 2 years?
    - How predictive was the baseline clustering?

2. (B: "uninjured_subjects.csv" that are NOT in C) baseline uninj subjects, long. It's okay if they had injuries.
    - used as context for #3
3. (C: ) baseline outcome matched uninj subjects, long. It's okay if they had injuries.
    - did they experience more mTBIs than #2?

4. (D: "mtbi_subjects_0_to_2.csv") Long mTBI subjects, baseline
    - Does the baseline clustering predict their long term outcomes?
    - Did they have bad outcomes right out of the gates compared to baseline matched uninjured controls?
5. (D: "mtbi_subjects_0_to_2.csv") Long mTBI subjects, long
    - used as context for #1
6. (E: "uninjured_subjects_0_to_2.csv") Long uninj subjects, baseline
    - with #4, used as context for #1 and #2?
7. (E: "uninjured_subjects_0_to_2.csv") Long uninj subjects, long
    - with #3, used as context for #1 and #2?

The relevant times already collected for these longitudinal analyses are:
1. baseline mTBI subjects, baseline (already collected)
2. baseline uninj subjects, baseline (already collected)
3. baseline outcome matched uninj subjects, baseline (already collected)

And in later chapters, if clustering results are good, I'll make a classifier to predict cluster from raw data.

```{r}
mtbi_subjects_t0 <- get_mtbi_subjects(
    ph_p_otbi,
    abcd_y_lt,
    min_mpi = 0,
    t = 0
) |>
    dplyr::select(subjectkey) |>
    unlist() |>
    as.character()

mtbi_subjects_t1 <- get_mtbi_subjects(
    ph_p_otbi,
    abcd_y_lt,
    min_mpi = 0,
    t = 1
) |>
    dplyr::select(subjectkey) |>
    unlist() |>
    as.character()

mtbi_subjects_t2 <- get_mtbi_subjects(
    ph_p_otbi,
    abcd_y_lt,
    min_mpi = 0,
    t = 2
) |>
    dplyr::select(subjectkey) |>
    unlist() |>
    as.character()

mtbi_subjects_t1

mtbi_subjects_t1o <- mtbi_subjects_t1[!mtbi_subjects_t1 %in% mtbi_subjects_t0]
mtbi_subjects_t2o <- mtbi_subjects_t2[!mtbi_subjects_t2 %in% mtbi_subjects_t0]

mtbi_subjects_0_to_2 <- unique(c(mtbi_subjects_t1o, mtbi_subjects_t2o))

length(mtbi_subjects_0_to_2) #219

write_subjects(
    mtbi_subjects_t1,
    sub_path("mtbi_subjects_t1.csv", TRUE)
)

write_subjects(
    mtbi_subjects_t2,
    sub_path("mtbi_subjects_t2.csv", TRUE)
)

write_subjects(
    mtbi_subjects_0_to_2,
    sub_path("mtbi_subjects_0_to_2.csv", TRUE)
)

uninjured_subjects_t0 <- get_uninjured_subjects(ph_p_otbi, abcd_y_lt, t = 0) |>
    dplyr::select(subjectkey) |>
    unlist() |>
    as.character()

uninjured_subjects_t1 <- get_uninjured_subjects(ph_p_otbi, abcd_y_lt, t = 1) |>
    dplyr::select(subjectkey) |>
    unlist() |>
    as.character()

uninjured_subjects_t2 <- get_uninjured_subjects(ph_p_otbi, abcd_y_lt, t = 2) |>
    dplyr::select(subjectkey) |>
    unlist() |>
    as.character()

uninjured_subjects_0_to_2 <- Reduce(
    intersect,
    list(
        uninjured_subjects_t0,
        uninjured_subjects_t1,
        uninjured_subjects_t2
    )
)

# Exporting those subjects
write_subjects(
    uninjured_subjects_0_to_2,
    sub_path("uninjured_subjects_0_to_2.csv", TRUE)
)
```

```{r}
mtbi_subjects_t1 <- read_subjects(
    sub_path("2024_05_06_mtbi_subjects_t1.csv")
)

mtbi_subjects_t2 <- read_subjects(
    sub_path("2024_05_06_mtbi_subjects_t2.csv")
)

mtbi_subjects_0_to_2 <- read_subjects(
    sub_path("2024_05_06_mtbi_subjects_0_to_2.csv")
)

uninjured_subjects_0_to_2 <- read_subjects(
    sub_path("2024_05_06_uninjured_subjects_0_to_2.csv")
)

# Baseline
mtbi_subjects_0 <- read_subjects(
    sub_path("2024_04_17_mtbi_subjects.csv")
)

uninjured_subjects_0 <- read_subjects(
    sub_path("2024_04_17_uninjured_subjects.csv")
)

```

## Input variables

### Acute symptoms

#### Feeling dazed

```{r}
# Subjects who should have their injury information collected from t1
t1_latest <- mtbi_subjects_0_to_2[!mtbi_subjects_0_to_2 %in% mtbi_subjects_t2]

# Subjects who should have their injury information collected from t2
t2_latest <- mtbi_subjects_0_to_2[!mtbi_subjects_0_to_2 %in% t1_latest]

as_mem_daze_mtbi_l1 <- get_mtbi_mem_daze(
    ph_p_otbi,
    abcd_y_lt,
    t1_latest,
    t = 1
)

as_mem_daze_mtbi_l2 <- get_mtbi_mem_daze(
    ph_p_otbi,
    abcd_y_lt,
    t2_latest,
    t = 2
)

as_mem_daze_mtbi_l <- rbind(
    as_mem_daze_mtbi_l1,
    as_mem_daze_mtbi_l2
)

write_csv(
    as_mem_daze_mtbi_l,
    input_path("as_mem_daze_mtbi_l.csv", date = TRUE)
)
```

#### Mechanism of injury

```{r}
as_mechanism_mtbi_l1 <- get_mtbi_mechanism(
    ph_p_otbi,
    abcd_y_lt,
    t1_latest,
    t = 1
)

as_mechanism_mtbi_l2 <- get_mtbi_mechanism(
    ph_p_otbi,
    abcd_y_lt,
    t2_latest,
    t = 2
)

as_mechanism_mtbi_l <- rbind(
    as_mechanism_mtbi_l1,
    as_mechanism_mtbi_l2
)

write_csv(
    as_mechanism_mtbi_l,
    input_path("as_mechanism_mtbi_l.csv", date = TRUE)
)
```

#### Loss of consciousness

```{r}
as_loc_mtbi_l1 <- get_mtbi_loc(
    ph_p_otbi,
    abcd_y_lt,
    t1_latest,
    t = 1
)

as_loc_mtbi_l2 <- get_mtbi_loc(
    ph_p_otbi,
    abcd_y_lt,
    t2_latest,
    t = 2
)

as_loc_mtbi_l <- rbind(
    as_loc_mtbi_l1,
    as_loc_mtbi_l2
)

write_csv(
    as_loc_mtbi_l,
    input_path("as_loc_mtbi_l.csv", date = TRUE)
)
```

### Demographics

Demographic variables included in the analyses are:

* Interview age
* Injury age
* Sex
* Race
* Household income
* Pubertal status

#### Interview age

```{r}
d_interview_age_mtbi_l0 <- get_interview_age(
    abcd_y_lt,
    mtbi_subjects_0_to_2,
    t = 0,
    as_years = FALSE
)

write_csv(
    d_interview_age_l0,
    input_path("d_interview_age_mtbi_l0.csv", TRUE)
)

d_interview_age_uninj_l0 <- get_interview_age(
    abcd_y_lt,
    uninjured_subjects_0_to_2,
    t = 0,
    as_years = FALSE
)

write_csv(
    d_interview_age_uninj_l0,
    input_path("d_interview_age_uninj_l0.csv", TRUE)
)

d_interview_age_mtbi_l2 <- get_interview_age(
    abcd_y_lt,
    mtbi_subjects_0_to_2,
    t = 2,
    as_years = FALSE
)

write_csv(
    d_interview_age_mtbi_l2,
    input_path("d_interview_age_mtbi_l2.csv", TRUE)
)

d_interview_age_uninj_l2 <- get_interview_age(
    abcd_y_lt,
    uninjured_subjects_0_to_2,
    t = 2,
    as_years = FALSE
)

write_csv(
    d_interview_age_uninj_l2,
    input_path("d_interview_age_uninj_l2.csv", TRUE)
)
```

#### Injury age

```{r}
d_mtbi_age_mtbi_l1 <- get_mtbi_age(
    ph_p_otbi,
    abcd_y_lt,
    t1_latest,
    t = 1,
    as_years = FALSE
)

d_mtbi_age_mtbi_l2 <- get_mtbi_age(
    ph_p_otbi,
    abcd_y_lt,
    t2_latest,
    t = 2,
    as_years = FALSE
)

d_mtbi_age_mtbi_l <- rbind(
    d_mtbi_age_mtbi_l1,
    d_mtbi_age_mtbi_l2
)

write_csv(
    d_mtbi_age_mtbi_l,
    input_path("d_mtbi_age_mtbi_l.csv", TRUE)
)
```

#### Sex at birth

Data only present at baseline.

```{r}
d_sex_mtbi_l0 <- get_sex(
    gish_p_gi,
    mtbi_subjects_0_to_2,
    t = 0,
    as_numeric = TRUE
)

write_csv(
    d_sex_mtbi_l0,
    input_path("d_sex_mtbi_l0.csv", TRUE)
)

d_sex_uninj_l0 <- get_sex(
    gish_p_gi,
    uninjured_subjects_0_to_2,
    t = 0,
    as_numeric = TRUE
)

write_csv(
    d_sex_uninj_l0,
    input_path("d_sex_uninj_l0.csv", TRUE)
)
```

#### Household income

Data only present at baseline.

```{r}
d_income_mtbi_l0 <- get_income(
    abcd_p_demo,
    mtbi_subjects_0_to_2,
    t = 0
)

write_csv(
    d_income_mtbi_l0,
    input_path("d_income_mtbi_l0.csv", TRUE)
)

d_income_uninj_l0 <- get_income(
    abcd_p_demo,
    uninjured_subjects_0_to_2,
    t = 0
)

write_csv(
    d_income_uninj_l0,
    input_path("d_income_uninj_l0.csv", TRUE)
)
```

#### Race

Data only present at baseline.

```{r}
d_race_mtbi_l0 <- get_race(
    abcd_p_demo,
    mtbi_subjects_0_to_2,
    asian_as_other = TRUE, # distinct Asian category only has N = 4
    t = 0
)

write_csv(
    d_race_mtbi_l0,
    input_path("d_race_mtbi_l0.csv", TRUE)
)

d_race_uninj_l0 <- get_race(
    abcd_p_demo,
    uninjured_subjects_0_to_2,
    asian_as_other = TRUE,
    t = 0
)

write_csv(
    d_race_uninj_l0,
    input_path("d_race_uninj_l0.csv", TRUE)
)
```

#### Pubertal status

```{r}
d_pubertal_status_mtbi_l0 <- get_pubertal_status(
    ph_p_pds,
    ph_y_pds,
    mtbi_subjects_0_to_2,
    max_value = 3,
    t = 0
)

write_csv(
    d_pubertal_status_mtbi_l0,
    input_path("d_pubertal_status_mtbi_l0.csv", TRUE)
)

d_pubertal_status_uninj_l0 <- get_pubertal_status(
    ph_p_pds,
    ph_y_pds,
    uninjured_subjects_0_to_2,
    max_value = 3,
    t = 0
)

write_csv(
    d_pubertal_status_uninj_l0,
    input_path("d_pubertal_status_uninj_l0.csv", TRUE)
)

d_pubertal_status_mtbi_l2 <- get_pubertal_status(
    ph_p_pds,
    ph_y_pds,
    mtbi_subjects_0_to_2,
    max_value = 5,
    t = 2
)

write_csv(
    d_pubertal_status_mtbi_l2,
    input_path("d_pubertal_status_mtbi_l2.csv", TRUE)
)

d_pubertal_status_uninj_l2 <- get_pubertal_status(
    ph_p_pds,
    ph_y_pds,
    uninjured_subjects_0_to_2,
    max_value = 5,
    t = 2
)

write_csv(
    d_pubertal_status_uninj_l2,
    input_path("d_pubertal_status_uninj_l2.csv", TRUE)
)
```

### Medical history

Medical history variables of interest include:

1. Number of previous head injuries
2. History of headaches (binary)

#### History of headaches

Data only present at baseline.

```{r}
mh_headaches_mtbi_l0 <- get_headaches(
    ph_p_mhx,
    mtbi_subjects_0_to_2,
    t = 0
)

write_csv(
    mh_headaches_mtbi_l0,
    input_path("mh_headaches_mtbi_l0.csv", date = TRUE)
)

mh_headaches_uninj_l0 <- get_headaches(
    ph_p_mhx,
    uninjured_subjects_0_to_2,
    t = 0
)

write_csv(
    mh_headaches_uninj_l0,
    input_path("mh_headaches_uninj_l0.csv", date = TRUE)
)
```

#### Number of previous mTBIs

```{r}
mh_mtbi_count_mtbi_0_to_2_t1 <- get_mtbi_count(
    ph_p_otbi,
    abcd_y_lt,
    mtbi_subjects_0_to_2,
    cutoff = 6, # N = 4 and 5 only occur once
    t = 1
)

mh_mtbi_count_mtbi_0_to_2_t2 <- get_mtbi_count(
    ph_p_otbi,
    abcd_y_lt,
    mtbi_subjects_0_to_2,
    cutoff = 6, # N = 4 and 5 only occur once
    t = 2
)

mh_mtbi_count_mtbi_l2 <- dplyr::full_join(
    mh_mtbi_count_mtbi_0_to_2_t1,
    mh_mtbi_count_mtbi_0_to_2_t2,
    by = "subjectkey"
) |>
    dplyr::rowwise() |>
    dplyr::mutate(
        mtbi_count = sum(mtbi_count.x, mtbi_count.y, na.rm = TRUE),
        .keep = "unused"
    ) |>
    dplyr::ungroup()

write_csv(
    mh_mtbi_count_mtbi_l2,
    input_path("mh_mtbi_count_mtbi_l2.csv", date = TRUE)
)
```

### Neuroimaging

#### Structural MRI

##### Subcortical volume

```{r}
sm_subc_v_mtbi_l0 <- get_subc_v(
    mri_y_smr_vol_aseg,
    mtbi_subjects_0_to_2,
    t = 0
)

write_csv(
    sm_subc_v_mtbi_l0,
    input_path("sm_subc_v_mtbi_l0.csv", date = TRUE)
)

sm_subc_v_uninj_l0 <- get_subc_v(
    mri_y_smr_vol_aseg,
    uninjured_subjects_0_to_2,
    t = 0
)

write_csv(
    sm_subc_v_uninj_l0,
    input_path("sm_subc_v_uninj_l0.csv", date = TRUE)
)

sm_subc_v_mtbi_l2 <- get_subc_v(
    mri_y_smr_vol_aseg,
    mtbi_subjects_0_to_2,
    t = 2
)

write_csv(
    sm_subc_v_mtbi_l2,
    input_path("sm_subc_v_mtbi_l2.csv", date = TRUE)
)

sm_subc_v_uninj_l2 <- get_subc_v(
    mri_y_smr_vol_aseg,
    uninjured_subjects_0_to_2,
    t = 2
)

write_csv(
    sm_subc_v_uninj_l2,
    input_path("sm_subc_v_uninj_l2.csv", date = TRUE)
)
```

##### Cortical thickness

Both the Desikan and Destrieux cortical parcellations could have been used for the cortical imaging data collected below.
A comparison between the two can be found in the appendix.
Because there happens to be a few more participants with calculated Desikan parcellations, that is what is used here.

```{r}
sm_cort_t_mtbi_l0 <- get_cort_t(
    mri_y_smr_thk_dsk,
    mtbi_subjects_0_to_2,
    t = 0
)

write_csv(
    sm_cort_t_mtbi_l0,
    input_path("sm_cort_t_mtbi_l0.csv", date = TRUE)
)

sm_cort_t_uninj_l0 <- get_cort_t(
    mri_y_smr_thk_dsk,
    uninjured_subjects_0_to_2,
    t = 0
)

write_csv(
    sm_cort_t_uninj_l0,
    input_path("sm_cort_t_uninj_l0.csv", date = TRUE)
)

sm_cort_t_mtbi_l2 <- get_cort_t(
    mri_y_smr_thk_dsk,
    mtbi_subjects_0_to_2,
    t = 2
)

write_csv(
    sm_cort_t_mtbi_l2,
    input_path("sm_cort_t_mtbi_l2.csv", date = TRUE)
)

sm_cort_t_uninj_l2 <- get_cort_t(
    mri_y_smr_thk_dsk,
    uninjured_subjects_0_to_2,
    t = 2
)

write_csv(
    sm_cort_t_uninj_l2,
    input_path("sm_cort_t_uninj_l2.csv", date = TRUE)
)
```

##### Cortical surface areas

```{r}
sm_cort_sa_mtbi_l0 <- get_cort_sa(
    mri_y_smr_area_dsk,
    mtbi_subjects_0_to_2,
    t = 0
)

write_csv(
    sm_cort_sa_mtbi_l0,
    input_path("sm_cort_sa_mtbi_l0.csv", date = TRUE)
)

sm_cort_sa_uninj_l0 <- get_cort_sa(
    mri_y_smr_area_dsk,
    uninjured_subjects_0_to_2,
    t = 0
)

write_csv(
    sm_cort_sa_uninj_l0,
    input_path("sm_cort_sa_uninj_l0.csv", date = TRUE)
)

sm_cort_sa_mtbi_l2 <- get_cort_sa(
    mri_y_smr_area_dsk,
    mtbi_subjects_0_to_2,
    t = 2
)

write_csv(
    sm_cort_sa_mtbi_l2,
    input_path("sm_cort_sa_mtbi_l2.csv", date = TRUE)
)

sm_cort_sa_uninj_l2 <- get_cort_sa(
    mri_y_smr_area_dsk,
    uninjured_subjects_0_to_2,
    t = 2
)

write_csv(
    sm_cort_sa_uninj_l2,
    input_path("sm_cort_sa_uninj_l2.csv", date = TRUE)
)
```

#### Diffusion MRI

##### White matter neurite densities

```{r}
dm_all_wmnd_mtbi_l0 <- get_all_wmnd(
    mri_y_rsi_rnd_at,
    mri_y_rsi_rnd_wm_dsk,
    subjects = mtbi_subjects_0_to_2,
    t = 0
)

write_csv(
    dm_all_wmnd_mtbi_l0,
    input_path("dm_all_wmnd_mtbi_l0.csv", date = TRUE)
)

dm_all_wmnd_uninj_l0 <- get_all_wmnd(
    mri_y_rsi_rnd_at,
    mri_y_rsi_rnd_wm_dsk,
    subjects = uninjured_subjects_0_to_2,
    t = 0
)

write_csv(
    dm_all_wmnd_uninj_l0,
    input_path("dm_all_wmnd_uninj_l0.csv", date = TRUE)
)

dm_all_wmnd_mtbi_l2 <- get_all_wmnd(
    mri_y_rsi_rnd_at,
    mri_y_rsi_rnd_wm_dsk,
    subjects = mtbi_subjects_0_to_2,
    t = 2
)

write_csv(
    dm_all_wmnd_mtbi_l2,
    input_path("dm_all_wmnd_mtbi_l2.csv", date = TRUE)
)

dm_all_wmnd_uninj_l2 <- get_all_wmnd(
    mri_y_rsi_rnd_at,
    mri_y_rsi_rnd_wm_dsk,
    subjects = uninjured_subjects_0_to_2,
    t = 2
)

write_csv(
    dm_all_wmnd_uninj_l2,
    input_path("dm_all_wmnd_uninj_l2.csv", date = TRUE)
)
```

#### Resting-state functional MRI

We are interested in the following rs-fMRI measures:

- Gordon network (cortical) correlations
- Subcortical correlations

##### Cortical parcellation network correlations

```{r}
rm_gord_cor_mtbi_l0 <- get_gord_cor(
    mri_y_rsfmr_cor_gp_gp,
    mtbi_subjects_0_to_2,
    t = 0
)

write_csv(
    rm_gord_cor_mtbi_l0,
    input_path("rm_gord_cor_mtbi_l0.csv", date = TRUE)
)

rm_gord_cor_uninj_l0 <- get_gord_cor(
    mri_y_rsfmr_cor_gp_gp,
    uninjured_subjects_0_to_2,
    t = 0
)

write_csv(
    rm_gord_cor_uninj_l0,
    input_path("rm_gord_cor_uninj_l0.csv", date = TRUE)
)

rm_gord_cor_mtbi_l2 <- get_gord_cor(
    mri_y_rsfmr_cor_gp_gp,
    mtbi_subjects_0_to_2,
    t = 2
)

write_csv(
    rm_gord_cor_mtbi_l2,
    input_path("rm_gord_cor_mtbi_l2.csv", date = TRUE)
)

rm_gord_cor_uninj_l2 <- get_gord_cor(
    mri_y_rsfmr_cor_gp_gp,
    uninjured_subjects_0_to_2,
    t = 2
)

write_csv(
    rm_gord_cor_uninj_l2,
    input_path("rm_gord_cor_uninj_l2.csv", date = TRUE)
)
```

##### Subcortical parcellation network correlations

```{r}
rm_subc_cor_mtbi_l0 <- get_subc_cor(
    mri_y_rsfmr_cor_gp_aseg,
    mtbi_subjects_0_to_2,
    t = 0
)
write_csv(
    rm_subc_cor_mtbi_l0,
    input_path("rm_subc_cor_mtbi_l0.csv", date = TRUE)
)

rm_subc_cor_uninj_l0 <- get_subc_cor(
    mri_y_rsfmr_cor_gp_aseg,
    uninjured_subjects_0_to_2,
    t = 0
)
write_csv(
    rm_subc_cor_uninj_l0,
    input_path("rm_subc_cor_uninj_l0.csv", date = TRUE)
)

rm_subc_cor_mtbi_l2 <- get_subc_cor(
    mri_y_rsfmr_cor_gp_aseg,
    mtbi_subjects_0_to_2,
    t = 2
)
write_csv(
    rm_subc_cor_mtbi_l2,
    input_path("rm_subc_cor_mtbi_l2.csv", date = TRUE)
)

rm_subc_cor_uninj_l2 <- get_subc_cor(
    mri_y_rsfmr_cor_gp_aseg,
    uninjured_subjects_0_to_2,
    t = 2
)
write_csv(
    rm_subc_cor_uninj_l2,
    input_path("rm_subc_cor_uninj_l2.csv", date = TRUE)
)
```

### Psychosocial resilience

Psychosocial factors of interest include:

#### Loneliness

Data only present at baseline.

```{r}
p_loneliness_mtbi_l0 <- get_loneliness(
    mh_y_or,
    gish_p_gi,
    mtbi_subjects_0_to_2,
    discretize = TRUE,
    t = 0
)
write_csv(
    p_loneliness_mtbi_l0,
    input_path("p_loneliness_mtbi_l0.csv", date = TRUE)
)

p_loneliness_uninj_l0 <- get_loneliness(
    mh_y_or,
    gish_p_gi,
    uninjured_subjects_0_to_2,
    discretize = TRUE,
    t = 0
)
write_csv(
    p_loneliness_uninj_l0,
    input_path("p_loneliness_uninj_l0.csv", date = TRUE)
)
```

#### Healthy behaviours

##### Screen time

Data only present at baseline.

```{r}
p_screen_time_mtbi_l0 <- get_screen_time(
    nt_p_stq,
    mtbi_subjects_0_to_2,
    t = 0
)

write_csv(
    p_screen_time_mtbi_l0,
    input_path("p_screen_time_mtbi_l0.csv", date = TRUE)
)

p_screen_time_uninj_l0 <- get_screen_time(
    nt_p_stq,
    uninjured_subjects_0_to_2,
    t = 0
)

write_csv(
    p_screen_time_uninj_l0,
    input_path("p_screen_time_uninj_l0.csv", date = TRUE)
)
```

##### Sports and activities participation

```{r}
p_sports_mtbi_l0 <- get_sports_and_activities(
    ph_p_saiq,
    mtbi_subjects_0_to_2,
    t = 0
)
write_csv(
    p_sports_mtbi_l0,
    input_path("p_sports_mtbi_l0.csv", date = TRUE)
)

p_sports_uninj_l0 <- get_sports_and_activities(
    ph_p_saiq,
    uninjured_subjects_0_to_2,
    t = 0
)
write_csv(
    p_sports_uninj_l0,
    input_path("p_sports_uninj_l0.csv", date = TRUE)
)

p_sports_mtbi_l2 <- get_sports_and_activities(
    ph_p_saiq,
    mtbi_subjects_0_to_2,
    t = 2
)
write_csv(
    p_sports_mtbi_l2,
    input_path("p_sports_mtbi_l2.csv", date = TRUE)
)

p_sports_uninj_l2 <- get_sports_and_activities(
    ph_p_saiq,
    uninjured_subjects_0_to_2,
    t = 2
)
write_csv(
    p_sports_uninj_l2,
    input_path("p_sports_uninj_l2.csv", date = TRUE)
)
```

##### Exercise habits

```{r}
p_exercise_mtbi_l0 <- get_exercise(
    ph_y_yrb,
    mtbi_subjects_0_to_2,
    t = 0
)
write_csv(
    p_exercise_mtbi_l0,
    input_path("p_exercise_mtbi_l0.csv", date = TRUE)
)

p_exercise_uninj_l0 <- get_exercise(
    ph_y_yrb,
    uninjured_subjects_0_to_2,
    t = 0
)
write_csv(
    p_exercise_uninj_l0,
    input_path("p_exercise_uninj_l0.csv", date = TRUE)
)

p_exercise_mtbi_l2 <- get_exercise(
    ph_y_yrb,
    mtbi_subjects_0_to_2,
    t = 2
)
write_csv(
    p_exercise_mtbi_l2,
    input_path("p_exercise_mtbi_l2.csv", date = TRUE)
)

p_exercise_uninj_l2 <- get_exercise(
    ph_y_yrb,
    uninjured_subjects_0_to_2,
    t = 2
)
write_csv(
    p_exercise_uninj_l2,
    input_path("p_exercise_uninj_l2.csv", date = TRUE)
)
```

#### Prosocial behaviour

```{r}
p_prosocial_mtbi_l0 <- get_prosocial_behaviour(
    ce_p_psb,
    ce_y_psb,
    mtbi_subjects_0_to_2,
    no_zero = TRUE,
    t = 0
)
write_csv(
    p_prosocial_mtbi_l0,
    input_path("p_prosocial_mtbi_l0.csv", date = TRUE)
)

p_prosocial_uninj_l0 <- get_prosocial_behaviour(
    ce_p_psb,
    ce_y_psb,
    uninjured_subjects_0_to_2,
    no_zero = TRUE,
    t = 0
)
write_csv(
    p_prosocial_uninj_l0,
    input_path("p_prosocial_uninj_l0.csv", date = TRUE)
)

p_prosocial_mtbi_l2 <- get_prosocial_behaviour(
    ce_p_psb,
    ce_y_psb,
    mtbi_subjects_0_to_2,
    no_zero = TRUE,
    t = 2
)
write_csv(
    p_prosocial_mtbi_l2,
    input_path("p_prosocial_mtbi_l2.csv", date = TRUE)
)

p_prosocial_uninj_l2 <- get_prosocial_behaviour(
    ce_p_psb,
    ce_y_psb,
    uninjured_subjects_0_to_2,
    no_zero = TRUE,
    t = 2
)
write_csv(
    p_prosocial_uninj_l2,
    input_path("p_prosocial_uninj_l2.csv", date = TRUE)
)
```

#### Family function

```{r}
p_fam_fn_mtbi_l0 <- get_family_function(
    ce_y_fes,
    ce_p_fes,
    mtbi_subjects_0_to_2,
    t = 0
)
write_csv(
    p_fam_fn_mtbi_l0,
    input_path("p_fam_fn_mtbi_l0.csv", date = TRUE)
)

p_fam_fn_uninj_l0 <- get_family_function(
    ce_y_fes,
    ce_p_fes,
    uninjured_subjects_0_to_2,
    t = 0
)
write_csv(
    p_fam_fn_uninj_l0,
    input_path("p_fam_fn_uninj_l0.csv", date = TRUE)
)

p_fam_fn_mtbi_l2 <- get_family_function(
    ce_y_fes,
    ce_p_fes,
    mtbi_subjects_0_to_2,
    t = 2
)
write_csv(
    p_fam_fn_mtbi_l2,
    input_path("p_fam_fn_mtbi_l2.csv", date = TRUE)
)

p_fam_fn_uninj_l2 <- get_family_function(
    ce_y_fes,
    ce_p_fes,
    uninjured_subjects_0_to_2,
    t = 2
)
write_csv(
    p_fam_fn_uninj_l2,
    input_path("p_fam_fn_uninj_l2.csv", date = TRUE)
)

```

#### Parent psychopathology

```{r}
p_parent_psych_mtbi_l0 <- get_parent_psychopathology(
    mh_p_asr,
    mtbi_subjects_0_to_2,
    t = 0,
    raw = FALSE
)
write_csv(
    p_parent_psych_mtbi_l0,
    input_path("p_parent_psych_mtbi_l0.csv", date = TRUE)
)

p_parent_psych_uninj_l0 <- get_parent_psychopathology(
    mh_p_asr,
    uninjured_subjects_0_to_2,
    t = 0,
    raw = FALSE
)
write_csv(
    p_parent_psych_uninj_l0,
    input_path("p_parent_psych_uninj_l0.csv", date = TRUE)
)

p_parent_psych_mtbi_l2 <- get_parent_psychopathology(
    mh_p_asr,
    mtbi_subjects_0_to_2,
    t = 2,
    raw = FALSE
)
write_csv(
    p_parent_psych_mtbi_l2,
    input_path("p_parent_psych_mtbi_l2.csv", date = TRUE)
)

p_parent_psych_uninj_l2 <- get_parent_psychopathology(
    mh_p_asr,
    uninjured_subjects_0_to_2,
    t = 2,
    raw = FALSE
)
write_csv(
    p_parent_psych_uninj_l2,
    input_path("p_parent_psych_uninj_l2.csv", date = TRUE)
)
```

## Output variables

### Child Behaviour Checklist

These are collected at both baseline and longitudinal timepoints.

#### Anxious-depressed

```{r}
cbcl_anxdep_mtbi_l0 <- get_cbcl_syndrome_scale(
    syndrome = "anxdep",
    mh_p_cbcl,
    raw = FALSE,
    subjects = mtbi_subjects_0_to_2,
    t = 0
)
write_csv(
    cbcl_anxdep_mtbi_l0,
    input_path("cbcl_anxdep_mtbi_l0.csv", date = TRUE)
)

cbcl_anxdep_uninj_l0 <- get_cbcl_syndrome_scale(
    syndrome = "anxdep",
    mh_p_cbcl,
    raw = FALSE,
    subjects = uninjured_subjects_0_to_2,
    t = 0
)
write_csv(
    cbcl_anxdep_uninj_l0,
    input_path("cbcl_anxdep_uninj_l0.csv", date = TRUE)
)

cbcl_anxdep_mtbi_l2 <- get_cbcl_syndrome_scale(
    syndrome = "anxdep",
    mh_p_cbcl,
    raw = FALSE,
    subjects = mtbi_subjects_0_to_2,
    t = 2
)
write_csv(
    cbcl_anxdep_mtbi_l2,
    input_path("cbcl_anxdep_mtbi_l2.csv", date = TRUE)
)

cbcl_anxdep_uninj_l2 <- get_cbcl_syndrome_scale(
    syndrome = "anxdep",
    mh_p_cbcl,
    raw = FALSE,
    subjects = uninjured_subjects_0_to_2,
    t = 2
)
write_csv(
    cbcl_anxdep_uninj_l2,
    input_path("cbcl_anxdep_uninj_l2.csv", date = TRUE)
)
```

#### Withdrawn-depressed

```{r}
cbcl_withdep_mtbi_l0 <- get_cbcl_syndrome_scale(
    syndrome = "withdep",
    mh_p_cbcl,
    raw = FALSE,
    subjects = mtbi_subjects_0_to_2,
    t = 0
)
write_csv(
    cbcl_withdep_mtbi_l0,
    input_path("cbcl_withdep_mtbi_l0.csv", date = TRUE)
)

cbcl_withdep_uninj_l0 <- get_cbcl_syndrome_scale(
    syndrome = "withdep",
    mh_p_cbcl,
    raw = FALSE,
    subjects = uninjured_subjects_0_to_2,
    t = 0
)
write_csv(
    cbcl_withdep_uninj_l0,
    input_path("cbcl_withdep_uninj_l0.csv", date = TRUE)
)

cbcl_withdep_mtbi_l2 <- get_cbcl_syndrome_scale(
    syndrome = "withdep",
    mh_p_cbcl,
    raw = FALSE,
    subjects = mtbi_subjects_0_to_2,
    t = 2
)
write_csv(
    cbcl_withdep_mtbi_l2,
    input_path("cbcl_withdep_mtbi_l2.csv", date = TRUE)
)

cbcl_withdep_uninj_l2 <- get_cbcl_syndrome_scale(
    syndrome = "withdep",
    mh_p_cbcl,
    raw = FALSE,
    subjects = uninjured_subjects_0_to_2,
    t = 2
)
write_csv(
    cbcl_withdep_uninj_l2,
    input_path("cbcl_withdep_uninj_l2.csv", date = TRUE)
)
```

#### Somatic complaints

```{r}
cbcl_somatic_mtbi_l0 <- get_cbcl_syndrome_scale(
    syndrome = "somatic",
    mh_p_cbcl,
    raw = FALSE,
    subjects = mtbi_subjects_0_to_2,
    t = 0
)
write_csv(
    cbcl_somatic_mtbi_l0,
    input_path("cbcl_somatic_mtbi_l0.csv", date = TRUE)
)

cbcl_somatic_uninj_l0 <- get_cbcl_syndrome_scale(
    syndrome = "somatic",
    mh_p_cbcl,
    raw = FALSE,
    subjects = uninjured_subjects_0_to_2,
    t = 0
)
write_csv(
    cbcl_somatic_uninj_l0,
    input_path("cbcl_somatic_uninj_l0.csv", date = TRUE)
)

cbcl_somatic_mtbi_l2 <- get_cbcl_syndrome_scale(
    syndrome = "somatic",
    mh_p_cbcl,
    raw = FALSE,
    subjects = mtbi_subjects_0_to_2,
    t = 2
)
write_csv(
    cbcl_somatic_mtbi_l2,
    input_path("cbcl_somatic_mtbi_l2.csv", date = TRUE)
)

cbcl_somatic_uninj_l2 <- get_cbcl_syndrome_scale(
    syndrome = "somatic",
    mh_p_cbcl,
    raw = FALSE,
    subjects = uninjured_subjects_0_to_2,
    t = 2
)
write_csv(
    cbcl_somatic_uninj_l2,
    input_path("cbcl_somatic_uninj_l2.csv", date = TRUE)
)
```

#### Social complaints

```{r}
cbcl_social_mtbi_l0 <- get_cbcl_syndrome_scale(
    syndrome = "social",
    mh_p_cbcl,
    raw = FALSE,
    subjects = mtbi_subjects_0_to_2,
    t = 0
)
write_csv(
    cbcl_social_mtbi_l0,
    input_path("cbcl_social_mtbi_l0.csv", date = TRUE)
)

cbcl_social_uninj_l0 <- get_cbcl_syndrome_scale(
    syndrome = "social",
    mh_p_cbcl,
    raw = FALSE,
    subjects = uninjured_subjects_0_to_2,
    t = 0
)
write_csv(
    cbcl_social_uninj_l0,
    input_path("cbcl_social_uninj_l0.csv", date = TRUE)
)

cbcl_social_mtbi_l2 <- get_cbcl_syndrome_scale(
    syndrome = "social",
    mh_p_cbcl,
    raw = FALSE,
    subjects = mtbi_subjects_0_to_2,
    t = 2
)
write_csv(
    cbcl_social_mtbi_l2,
    input_path("cbcl_social_mtbi_l2.csv", date = TRUE)
)

cbcl_social_uninj_l2 <- get_cbcl_syndrome_scale(
    syndrome = "social",
    mh_p_cbcl,
    raw = FALSE,
    subjects = uninjured_subjects_0_to_2,
    t = 2
)
write_csv(
    cbcl_social_uninj_l2,
    input_path("cbcl_social_uninj_l2.csv", date = TRUE)
)
```

#### Thought complaints

```{r}
cbcl_thought_mtbi_l0 <- get_cbcl_syndrome_scale(
    syndrome = "thought",
    mh_p_cbcl,
    raw = FALSE,
    subjects = mtbi_subjects_0_to_2,
    t = 0
)
write_csv(
    cbcl_thought_mtbi_l0,
    input_path("cbcl_thought_mtbi_l0.csv", date = TRUE)
)

cbcl_thought_uninj_l0 <- get_cbcl_syndrome_scale(
    syndrome = "thought",
    mh_p_cbcl,
    raw = FALSE,
    subjects = uninjured_subjects_0_to_2,
    t = 0
)
write_csv(
    cbcl_thought_uninj_l0,
    input_path("cbcl_thought_uninj_l0.csv", date = TRUE)
)

cbcl_thought_mtbi_l2 <- get_cbcl_syndrome_scale(
    syndrome = "thought",
    mh_p_cbcl,
    raw = FALSE,
    subjects = mtbi_subjects_0_to_2,
    t = 2
)
write_csv(
    cbcl_thought_mtbi_l2,
    input_path("cbcl_thought_mtbi_l2.csv", date = TRUE)
)

cbcl_thought_uninj_l2 <- get_cbcl_syndrome_scale(
    syndrome = "thought",
    mh_p_cbcl,
    raw = FALSE,
    subjects = uninjured_subjects_0_to_2,
    t = 2
)
write_csv(
    cbcl_thought_uninj_l2,
    input_path("cbcl_thought_uninj_l2.csv", date = TRUE)
)

```

#### Attention complaints

```{r}
cbcl_attention_mtbi_l0 <- get_cbcl_syndrome_scale(
    syndrome = "attention",
    mh_p_cbcl,
    raw = FALSE,
    subjects = mtbi_subjects_0_to_2,
    t = 0
)
write_csv(
    cbcl_attention_mtbi_l0,
    input_path("cbcl_attention_mtbi_l0.csv", date = TRUE)
)

cbcl_attention_uninj_l0 <- get_cbcl_syndrome_scale(
    syndrome = "attention",
    mh_p_cbcl,
    raw = FALSE,
    subjects = uninjured_subjects_0_to_2,
    t = 0
)
write_csv(
    cbcl_attention_uninj_l0,
    input_path("cbcl_attention_uninj_l0.csv", date = TRUE)
)

cbcl_attention_mtbi_l2 <- get_cbcl_syndrome_scale(
    syndrome = "attention",
    mh_p_cbcl,
    raw = FALSE,
    subjects = mtbi_subjects_0_to_2,
    t = 2
)
write_csv(
    cbcl_attention_mtbi_l2,
    input_path("cbcl_attention_mtbi_l2.csv", date = TRUE)
)

cbcl_attention_uninj_l2 <- get_cbcl_syndrome_scale(
    syndrome = "attention",
    mh_p_cbcl,
    raw = FALSE,
    subjects = uninjured_subjects_0_to_2,
    t = 2
)
write_csv(
    cbcl_attention_uninj_l2,
    input_path("cbcl_attention_uninj_l2.csv", date = TRUE)
)
```

#### Rulebreak complaints

```{r}
cbcl_rulebreak_mtbi_l0 <- get_cbcl_syndrome_scale(
    syndrome = "rulebreak",
    mh_p_cbcl,
    raw = FALSE,
    subjects = mtbi_subjects_0_to_2,
    t = 0
)
write_csv(
    cbcl_rulebreak_mtbi_l0,
    input_path("cbcl_rulebreak_mtbi_l0.csv", date = TRUE)
)

cbcl_rulebreak_uninj_l0 <- get_cbcl_syndrome_scale(
    syndrome = "rulebreak",
    mh_p_cbcl,
    raw = FALSE,
    subjects = uninjured_subjects_0_to_2,
    t = 0
)
write_csv(
    cbcl_rulebreak_uninj_l0,
    input_path("cbcl_rulebreak_uninj_l0.csv", date = TRUE)
)

cbcl_rulebreak_mtbi_l2 <- get_cbcl_syndrome_scale(
    syndrome = "rulebreak",
    mh_p_cbcl,
    raw = FALSE,
    subjects = mtbi_subjects_0_to_2,
    t = 2
)
write_csv(
    cbcl_rulebreak_mtbi_l2,
    input_path("cbcl_rulebreak_mtbi_l2.csv", date = TRUE)
)

cbcl_rulebreak_uninj_l2 <- get_cbcl_syndrome_scale(
    syndrome = "rulebreak",
    mh_p_cbcl,
    raw = FALSE,
    subjects = uninjured_subjects_0_to_2,
    t = 2
)
write_csv(
    cbcl_rulebreak_uninj_l2,
    input_path("cbcl_rulebreak_uninj_l2.csv", date = TRUE)
)
```

#### Aggressive complaints

```{r}
cbcl_aggressive_mtbi_l0 <- get_cbcl_syndrome_scale(
    syndrome = "aggressive",
    mh_p_cbcl,
    raw = FALSE,
    subjects = mtbi_subjects_0_to_2,
    t = 0
)
write_csv(
    cbcl_aggressive_mtbi_l0,
    input_path("cbcl_aggressive_mtbi_l0.csv", date = TRUE)
)

cbcl_aggressive_uninj_l0 <- get_cbcl_syndrome_scale(
    syndrome = "aggressive",
    mh_p_cbcl,
    raw = FALSE,
    subjects = uninjured_subjects_0_to_2,
    t = 0
)
write_csv(
    cbcl_aggressive_uninj_l0,
    input_path("cbcl_aggressive_uninj_l0.csv", date = TRUE)
)

cbcl_aggressive_mtbi_l2 <- get_cbcl_syndrome_scale(
    syndrome = "aggressive",
    mh_p_cbcl,
    raw = FALSE,
    subjects = mtbi_subjects_0_to_2,
    t = 2
)
write_csv(
    cbcl_aggressive_mtbi_l2,
    input_path("cbcl_aggressive_mtbi_l2.csv", date = TRUE)
)

cbcl_aggressive_uninj_l2 <- get_cbcl_syndrome_scale(
    syndrome = "aggressive",
    mh_p_cbcl,
    raw = FALSE,
    subjects = uninjured_subjects_0_to_2,
    t = 2
)
write_csv(
    cbcl_aggressive_uninj_l2,
    input_path("cbcl_aggressive_uninj_l2.csv", date = TRUE)
)
```

### Sleep disturbance scale

```{r}
sds_total_probs_mtbi_l0 <- get_sds_total_probs(
    ph_p_sds,
    mtbi_subjects_0_to_2,
    t = 0
)
write_csv(
    sds_total_probs_mtbi_l0,
    input_path("sds_total_probs_mtbi_l0.csv", date = TRUE)
)

sds_total_probs_uninj_l0 <- get_sds_total_probs(
    ph_p_sds,
    uninjured_subjects_0_to_2,
    t = 0
)
write_csv(
    sds_total_probs_uninj_l0,
    input_path("sds_total_probs_uninj_l0.csv", date = TRUE)
)

sds_total_probs_mtbi_l2 <- get_sds_total_probs(
    ph_p_sds,
    mtbi_subjects_0_to_2,
    t = 2
)
write_csv(
    sds_total_probs_mtbi_l2,
    input_path("sds_total_probs_mtbi_l2.csv", date = TRUE)
)

sds_total_probs_uninj_l2 <- get_sds_total_probs(
    ph_p_sds,
    uninjured_subjects_0_to_2,
    t = 2
)
write_csv(
    sds_total_probs_uninj_l2,
    input_path("sds_total_probs_uninj_l2.csv", date = TRUE)
)
```
