# SNF in Uninjured Controls

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)
library(MatchIt)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subjects <- read_csv(sub_path("2024_02_13_mtbi_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2024_02_13_uninjured_subjects.csv"))
mtbi_subjects_train <- read_csv(sub_path("2024_02_13_mtbi_train_subjects.csv"))

source("abcd/functions.R")

```

## Loading data and out of model lists

```{r}
data_list_mu1 <- list.load(input_path("2024_02_14_data_list_mu1.rds"))
data_list_mu2 <- list.load(input_path("2024_02_14_data_list_mu2.rds"))
data_list_mu3 <- list.load(input_path("2024_02_14_data_list_mu3.rds"))
data_list_mu4 <- list.load(input_path("2024_02_14_data_list_mu4.rds"))
data_list_mu5 <- list.load(input_path("2024_02_14_data_list_mu5.rds"))
data_list_mpu1 <- list.load(input_path("2024_02_14_data_list_mpu1.rds"))
data_list_mpu2 <- list.load(input_path("2024_02_14_data_list_mpu2.rds"))
data_list_mpu3 <- list.load(input_path("2024_02_14_data_list_mpu3.rds"))
data_list_mpu4 <- list.load(input_path("2024_02_14_data_list_mpu4.rds"))
data_list_mpu5 <- list.load(input_path("2024_02_14_data_list_mpu5.rds"))
oom_list_mu1 <- list.load(input_path("2024_02_14_oom_list_mu1.rds"))
oom_list_mu2 <- list.load(input_path("2024_02_14_oom_list_mu2.rds"))
oom_list_mu3 <- list.load(input_path("2024_02_14_oom_list_mu3.rds"))
oom_list_mu4 <- list.load(input_path("2024_02_14_oom_list_mu4.rds"))
oom_list_mu5 <- list.load(input_path("2024_02_14_oom_list_mu5.rds"))
oom_list_mpu1 <- list.load(input_path("2024_02_14_oom_list_mpu1.rds"))
oom_list_mpu2 <- list.load(input_path("2024_02_14_oom_list_mpu2.rds"))
oom_list_mpu3 <- list.load(input_path("2024_02_14_oom_list_mpu3.rds"))
oom_list_mpu4 <- list.load(input_path("2024_02_14_oom_list_mpu4.rds"))
oom_list_mpu5 <- list.load(input_path("2024_02_14_oom_list_mpu5.rds"))
```

## Generating custom distance measures

```{r}
my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

summarize_distance_metrics_list(my_distance_metrics)
```

## Generating the settings matrix

```{r}
###############################################################################
# 3. Generate the settings matrix
###############################################################################
settings_matrix <- generate_settings_matrix(
    data_list_mu1,
    nrow = 200,
    seed = 42,
    distance_metrics_list = my_distance_metrics
)

write_csv(settings_matrix, proc_path("settings_matrix_mu.csv", TRUE))

settings_matrix <- read_csv(
    proc_path(
        "2024_02_14_settings_matrix_mu.csv"
    )
)
```

## SNF for each of the imputations

```{r}

# Uninjured only imputed
# Imputation 1
start <- proc.time()
progressr::with_progress({
    solutions_matrix_mu1 <- batch_snf(
        data_list = data_list_mu1,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_mu1, proc_path("solutions_matrix_mu1.csv", TRUE))
# Imputation 2
start <- proc.time()
progressr::with_progress({
    solutions_matrix_mu2 <- batch_snf(
        data_list = data_list_mu2,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_mu2, proc_path("solutions_matrix_mu2.csv", TRUE))
# Imputation 3
start <- proc.time()
progressr::with_progress({
    solutions_matrix_mu3 <- batch_snf(
        data_list = data_list_mu3,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_mu3, proc_path("solutions_matrix_mu3.csv", TRUE))
# Imputation 4
start <- proc.time()
progressr::with_progress({
    solutions_matrix_mu4 <- batch_snf(
        data_list = data_list_mu4,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_mu4, proc_path("solutions_matrix_mu4.csv", TRUE))
# Imputation 5
start <- proc.time()
progressr::with_progress({
    solutions_matrix_mu5 <- batch_snf(
        data_list = data_list_mu5,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_mu5, proc_path("solutions_matrix_mu5.csv", TRUE))
#
# Uninjured pooled imputed
# Imputation 1
start <- proc.time()
progressr::with_progress({
    solutions_matrix_mpu1 <- batch_snf(
        data_list = data_list_mpu1,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_mpu1, proc_path("solutions_matrix_mpu1.csv", TRUE))
# Imputation 2
start <- proc.time()
progressr::with_progress({
    solutions_matrix_mpu2 <- batch_snf(
        data_list = data_list_mpu2,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_mpu2, proc_path("solutions_matrix_mpu2.csv", TRUE))
# Imputation 3
start <- proc.time()
progressr::with_progress({
    solutions_matrix_mpu3 <- batch_snf(
        data_list = data_list_mpu3,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_mpu3, proc_path("solutions_matrix_mpu3.csv", TRUE))
# Imputation 4
start <- proc.time()
progressr::with_progress({
    solutions_matrix_mpu4 <- batch_snf(
        data_list = data_list_mpu4,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_mpu4, proc_path("solutions_matrix_mpu4.csv", TRUE))
# Imputation 5
start <- proc.time()
progressr::with_progress({
    solutions_matrix_mpu5 <- batch_snf(
        data_list = data_list_mpu5,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_mpu5, proc_path("solutions_matrix_mpu5.csv", TRUE))
```

## Re-importing the generated solutions

```{r}
solutions_matrix_mu1 <- read_csv(proc_path("2024_02_14_solutions_matrix_mu1.csv"))
solutions_matrix_mu2 <- read_csv(proc_path("2024_02_14_solutions_matrix_mu2.csv"))
solutions_matrix_mu3 <- read_csv(proc_path("2024_02_14_solutions_matrix_mu3.csv"))
solutions_matrix_mu4 <- read_csv(proc_path("2024_02_14_solutions_matrix_mu4.csv"))
solutions_matrix_mu5 <- read_csv(proc_path("2024_02_14_solutions_matrix_mu5.csv"))
solutions_matrix_mpu1 <- read_csv(proc_path("2024_02_14_solutions_matrix_mpu1.csv"))
solutions_matrix_mpu2 <- read_csv(proc_path("2024_02_14_solutions_matrix_mpu2.csv"))
solutions_matrix_mpu3 <- read_csv(proc_path("2024_02_14_solutions_matrix_mpu3.csv"))
solutions_matrix_mpu4 <- read_csv(proc_path("2024_02_14_solutions_matrix_mpu4.csv"))
solutions_matrix_mpu5 <- read_csv(proc_path("2024_02_14_solutions_matrix_mpu5.csv"))

all_uninjured_imputations <- do.call(
    "rbind",
    list(
        solutions_matrix_mu1,
        solutions_matrix_mu2,
        solutions_matrix_mu3,
        solutions_matrix_mu4,
        solutions_matrix_mu5,
        solutions_matrix_mpu1,
        solutions_matrix_mpu2,
        solutions_matrix_mpu3,
        solutions_matrix_mpu4,
        solutions_matrix_mpu5
    )
)
```

## Calculating pairwise ARIs

```{r}
# Completed
aris_mu1 <- calc_om_aris(solutions_matrix_mu1, verbose = TRUE)
write_csv(data.frame(aris_mu1), proc_path("aris_mu1.csv", TRUE))
aris_mu2 <- calc_om_aris(solutions_matrix_mu2, verbose = TRUE)
write_csv(data.frame(aris_mu2), proc_path("aris_mu2.csv", TRUE))
aris_mu3 <- calc_om_aris(solutions_matrix_mu3, verbose = TRUE)
write_csv(data.frame(aris_mu3), proc_path("aris_mu3.csv", TRUE))
aris_mu4 <- calc_om_aris(solutions_matrix_mu4, verbose = TRUE)
write_csv(data.frame(aris_mu4), proc_path("aris_mu4.csv", TRUE))
aris_mu5 <- calc_om_aris(solutions_matrix_mu5, verbose = TRUE)
write_csv(data.frame(aris_mu5), proc_path("aris_mu5.csv", TRUE))
aris_mpu1 <- calc_om_aris(solutions_matrix_mpu1, verbose = TRUE)
write_csv(data.frame(aris_mpu1), proc_path("aris_mpu1.csv", TRUE))
aris_mpu2 <- calc_om_aris(solutions_matrix_mpu2, verbose = TRUE)
write_csv(data.frame(aris_mpu2), proc_path("aris_mpu2.csv", TRUE))
aris_mpu3 <- calc_om_aris(solutions_matrix_mpu3, verbose = TRUE)
write_csv(data.frame(aris_mpu3), proc_path("aris_mpu3.csv", TRUE))
aris_mpu4 <- calc_om_aris(solutions_matrix_mpu4, verbose = TRUE)
write_csv(data.frame(aris_mpu4), proc_path("aris_mpu4.csv", TRUE))
aris_mpu5 <- calc_om_aris(solutions_matrix_mpu5, verbose = TRUE)
write_csv(data.frame(aris_mpu5), proc_path("aris_mpu5.csv", TRUE))
aris_all_uninjured_imputations <- calc_om_aris(
    all_uninjured_imputations,
    verbose = TRUE
)
write_csv(
    data.frame(aris_all_uninjured_imputations),
    proc_path("aris_all_uninjured_imputations.csv", TRUE)
)
```

## Re-importing the ARIs

```{r}
aris_mu1 <- read_csv(proc_path("2024_02_15_aris_mu1.csv")) |> as.matrix()
aris_mu2 <- read_csv(proc_path("2024_02_15_aris_mu2.csv")) |> as.matrix()
aris_mu3 <- read_csv(proc_path("2024_02_15_aris_mu3.csv")) |> as.matrix()
aris_mu4 <- read_csv(proc_path("2024_02_15_aris_mu4.csv")) |> as.matrix()
aris_mu5 <- read_csv(proc_path("2024_02_15_aris_mu5.csv")) |> as.matrix()
aris_mpu1 <- read_csv(proc_path("2024_02_15_aris_mpu1.csv")) |> as.matrix()
aris_mpu2 <- read_csv(proc_path("2024_02_15_aris_mpu2.csv")) |> as.matrix()
aris_mpu3 <- read_csv(proc_path("2024_02_15_aris_mpu3.csv")) |> as.matrix()
aris_mpu4 <- read_csv(proc_path("2024_02_15_aris_mpu4.csv")) |> as.matrix()
aris_mpu5 <- read_csv(proc_path("2024_02_15_aris_mpu5.csv")) |> as.matrix()

aris_all_uninjured_imputations <- read_csv(
    proc_path("2024_02_15_aris_all_uninjured_imputations.csv")
) |>
    as.matrix()
```

## Plotting the ARIs

### Initial plot across all ARIs to extract order

```{r}
aris_all_uninjured_imputations_heatmap <- similarity_matrix_heatmap(
    aris_all_uninjured_imputations,
    log_graph = FALSE,
    cluster_rows = TRUE,
    cluster_columns = TRUE
)

aris_all_uninjured_imputations_heatmap <- ComplexHeatmap::draw(
    aris_all_uninjured_imputations_heatmap
)
aris_all_uninjured_imputations_order <- ComplexHeatmap::row_order(
    aris_all_uninjured_imputations_heatmap
)

write_csv(
    data.frame(aris_all_uninjured_imputations_order),
    proc_path("aris_all_uninjured_imputations_order.csv", TRUE)
)
```

### Re-importing the order

```{r}
aris_all_uninjured_imputations_order <- unlist(
    read_csv(proc_path("2024_02_25_aris_all_uninjured_imputations_order.csv"))
)

names(aris_all_uninjured_imputations_order) <- NULL
```

## Full imputation meta clustering plot with impairment levels

```{r}
imputation_labels <- data.frame(
    "imputation" = c(
        rep("u1", 200),
        rep("u2", 200),
        rep("u3", 200),
        rep("u4", 200),
        rep("u5", 200),
        rep("pu1", 200),
        rep("pu2", 200),
        rep("pu3", 200),
        rep("pu4", 200),
        rep("pu5", 200)
    ),
    "pooled" = c(
        rep("yes", 1000),
        rep("no", 1000)
    )
)

full_solutions_matrix <- cbind(all_uninjured_imputations, imputation_labels)

#full_solutions_matrix$"nclust2" <- full_solutions_matrix$"nclust" - 2

#full_extended_solutions_matrix <- extend_solutions(
#    full_solutions_matrix,
#    oom_list_mu1
#)
#write_csv(
#    full_extended_solutions_matrix,
#    proc_path("full_uninjured_extended_solutions_matrix.csv", TRUE)
#)
#full_extended_solutions_matrix <- read_csv(
#    proc_path("2024_02_14_full_uninjured_extended_solutions_matrix.csv")
#)
#full_oom_pvals <- pval_select(
#    full_extended_solutions_matrix,
#    negative_log = TRUE
#)
#full_extended_solutions_matrix$"mean_neglog_p" <- full_oom_pvals$"mean_neglog_p"

full_mu_o_extended_solutions_matrix <- extend_solutions(
    full_solutions_matrix,
    oom_list_mu1,
    verbose = TRUE,
    min_pval = 1e-10
)
write_csv(
    full_mu_o_extended_solutions_matrix,
    proc_path("full_mu_o_extended_solutions_matrix.csv", TRUE)
)
full_mu_io_extended_solutions_matrix <- extend_solutions(
    full_solutions_matrix,
    target_list = c(data_list_mu1, oom_list_mu1),
    verbose = TRUE,
    min_pval = 1e-10
)
full_mu_io_extended_solutions_matrix
write_csv(
    full_mu_io_extended_solutions_matrix,
    proc_path("full_mu_io_extended_solutions_matrix.csv", TRUE)
)
```

```{r}
full_mu_o_extended_solutions_matrix <- read_csv(
    proc_path("2024_02_25_full_mu_o_extended_solutions_matrix.csv")
)

full_mu_io_extended_solutions_matrix <- read_csv(
    proc_path("2024_02_25_full_mu_io_extended_solutions_matrix.csv")
)
```

```{r}

split_vec <- c(
    682,
    1070,
    1555
)
mu_mc_heatmap <- my_similarity_matrix_heatmap(
    aris = aris_all_uninjured_imputations,
    aris_order = aris_all_uninjured_imputations_order,
    extended_solutions = full_mu_o_extended_solutions_matrix,
    split_vector = split_vec
)
mu_mc_heatmap

# PNG export
grDevices::png(
    fig_path("mu_mc_heatmap.png", TRUE),
    width = 3000,
    height = 3000,
    res = 300
)
mu_mc_heatmap
grDevices::dev.off()
```

## One-MC-at-a-time

```{r}

mu_manhattan <- my_manhattan_plot(
    solutions_matrix = full_mu_io_extended_solutions_matrix,
    aris_order = aris_all_uninjured_imputations_order,
    split_vector = split_vec,
    data_list = data_list_mu1,
    target_list = oom_list_mu1,
    colours = c(
        "I-D" = "#D95F02",
        "I-N" = "#7570B3",
        "I-MH" = "#E7298A",
        "I-P" = "#66A61E",
        "O-S" = "#E6AB02",
        "O-B" = "#A6761D"
    )
)
mu_manhattan

ggsave(
    plot = mu_manhattan,
    fig_path("mu_manhattan.png", TRUE),
    width = 15,
    height = 4 * 2.5
)

# Bulk export each MC individually
for (mc in c("A", "B", "C", "D")) {
    mc_plot <- my_manhattan_plot(
        solutions_matrix = full_mu_io_extended_solutions_matrix,
        aris_order = aris_all_uninjured_imputations_order,
        split_vector = split_vec,
        mcs = mc,
        data_list = data_list_mu1,
        target_list = oom_list_mu1,
        colours = c(
            "I-D" = "#D95F02",
            "I-N" = "#7570B3",
            "I-MH" = "#E7298A",
            "I-P" = "#66A61E",
            "O-S" = "#E6AB02",
            "O-B" = "#A6761D"
        )
    )
    mc_path <- paste0(
        "mu_mc_",
        gsub("-", "_", tolower(mc)),
        "_manhattan.png"
    )
    ggsave(
        plot = mc_plot,
        fig_path(mc_path, TRUE),
        width = 15,
        height = 5
    )
}

```

## Replication in demographic-corrected data

```{r}
data_list_mu1 <- list.load(input_path("2024_02_14_data_list_mu1.rds"))
data_list_mu2 <- list.load(input_path("2024_02_14_data_list_mu2.rds"))
data_list_mu3 <- list.load(input_path("2024_02_14_data_list_mu3.rds"))
data_list_mu4 <- list.load(input_path("2024_02_14_data_list_mu4.rds"))
data_list_mu5 <- list.load(input_path("2024_02_14_data_list_mu5.rds"))
data_list_mpu1 <- list.load(input_path("2024_02_14_data_list_mpu1.rds"))
data_list_mpu2 <- list.load(input_path("2024_02_14_data_list_mpu2.rds"))
data_list_mpu3 <- list.load(input_path("2024_02_14_data_list_mpu3.rds"))
data_list_mpu4 <- list.load(input_path("2024_02_14_data_list_mpu4.rds"))
data_list_mpu5 <- list.load(input_path("2024_02_14_data_list_mpu5.rds"))
oom_list_mu1 <- list.load(input_path("2024_02_14_oom_list_mu1.rds"))
oom_list_mu2 <- list.load(input_path("2024_02_14_oom_list_mu2.rds"))
oom_list_mu3 <- list.load(input_path("2024_02_14_oom_list_mu3.rds"))
oom_list_mu4 <- list.load(input_path("2024_02_14_oom_list_mu4.rds"))
oom_list_mu5 <- list.load(input_path("2024_02_14_oom_list_mu5.rds"))
oom_list_mpu1 <- list.load(input_path("2024_02_14_oom_list_mpu1.rds"))
oom_list_mpu2 <- list.load(input_path("2024_02_14_oom_list_mpu2.rds"))
oom_list_mpu3 <- list.load(input_path("2024_02_14_oom_list_mpu3.rds"))
oom_list_mpu4 <- list.load(input_path("2024_02_14_oom_list_mpu4.rds"))
oom_list_mpu5 <- list.load(input_path("2024_02_14_oom_list_mpu5.rds"))

data_list_no_demo_mu1 <- data_list_mu1
data_list_no_demo_mu2 <- data_list_mu2
data_list_no_demo_mu3 <- data_list_mu3
data_list_no_demo_mu4 <- data_list_mu4
data_list_no_demo_mu5 <- data_list_mu5
data_list_no_demo_mpu1 <- data_list_mpu1
data_list_no_demo_mpu2 <- data_list_mpu2
data_list_no_demo_mpu3 <- data_list_mpu3
data_list_no_demo_mpu4 <- data_list_mpu4
data_list_no_demo_mpu5 <- data_list_mpu5
oom_list_no_demo_mu1 <- oom_list_mu1
oom_list_no_demo_mu2 <- oom_list_mu2
oom_list_no_demo_mu3 <- oom_list_mu3
oom_list_no_demo_mu4 <- oom_list_mu4
oom_list_no_demo_mu5 <- oom_list_mu5
oom_list_no_demo_mpu1 <- oom_list_mpu1
oom_list_no_demo_mpu2 <- oom_list_mpu2
oom_list_no_demo_mpu3 <- oom_list_mpu3
oom_list_no_demo_mpu4 <- oom_list_mpu4
oom_list_no_demo_mpu5 <- oom_list_mpu5

demo_list_mu1 <- data_list_no_demo_mu1[c(1, 2, 3, 4)]
demo_list_mu2 <- data_list_no_demo_mu2[c(1, 2, 3, 4)]
demo_list_mu3 <- data_list_no_demo_mu3[c(1, 2, 3, 4)]
demo_list_mu4 <- data_list_no_demo_mu4[c(1, 2, 3, 4)]
demo_list_mu5 <- data_list_no_demo_mu5[c(1, 2, 3, 4)]
demo_list_mpu1 <- data_list_no_demo_mpu1[c(1, 2, 3, 4)]
demo_list_mpu2 <- data_list_no_demo_mpu2[c(1, 2, 3, 4)]
demo_list_mpu3 <- data_list_no_demo_mpu3[c(1, 2, 3, 4)]
demo_list_mpu4 <- data_list_no_demo_mpu4[c(1, 2, 3, 4)]
demo_list_mpu5 <- data_list_no_demo_mpu5[c(1, 2, 3, 4)]
data_list_no_demo_mu1[c(1, 2, 3, 4)] <- NULL
data_list_no_demo_mu2[c(1, 2, 3, 4)] <- NULL
data_list_no_demo_mu3[c(1, 2, 3, 4)] <- NULL
data_list_no_demo_mu4[c(1, 2, 3, 4)] <- NULL
data_list_no_demo_mu5[c(1, 2, 3, 4)] <- NULL
data_list_no_demo_mpu1[c(1, 2, 3, 4)] <- NULL
data_list_no_demo_mpu2[c(1, 2, 3, 4)] <- NULL
data_list_no_demo_mpu3[c(1, 2, 3, 4)] <- NULL
data_list_no_demo_mpu4[c(1, 2, 3, 4)] <- NULL
data_list_no_demo_mpu5[c(1, 2, 3, 4)] <- NULL

data_list_no_demo_mu1 <- remove_signal(data_list_no_demo_mu1, demo_list_mu1)
data_list_no_demo_mu2 <- remove_signal(data_list_no_demo_mu2, demo_list_mu2)
data_list_no_demo_mu3 <- remove_signal(data_list_no_demo_mu3, demo_list_mu3)
data_list_no_demo_mu4 <- remove_signal(data_list_no_demo_mu4, demo_list_mu4)
data_list_no_demo_mu5 <- remove_signal(data_list_no_demo_mu5, demo_list_mu5)
data_list_no_demo_mpu1 <- remove_signal(data_list_no_demo_mpu1, demo_list_mpu1)
data_list_no_demo_mpu2 <- remove_signal(data_list_no_demo_mpu2, demo_list_mpu2)
data_list_no_demo_mpu3 <- remove_signal(data_list_no_demo_mpu3, demo_list_mpu3)
data_list_no_demo_mpu4 <- remove_signal(data_list_no_demo_mpu4, demo_list_mpu4)
data_list_no_demo_mpu5 <- remove_signal(data_list_no_demo_mpu5, demo_list_mpu5)
oom_list_no_demo_mu1 <- remove_signal(oom_list_no_demo_mu1, demo_list_mu1)
oom_list_no_demo_mu2 <- remove_signal(oom_list_no_demo_mu2, demo_list_mu2)
oom_list_no_demo_mu3 <- remove_signal(oom_list_no_demo_mu3, demo_list_mu3)
oom_list_no_demo_mu4 <- remove_signal(oom_list_no_demo_mu4, demo_list_mu4)
oom_list_no_demo_mu5 <- remove_signal(oom_list_no_demo_mu5, demo_list_mu5)
oom_list_no_demo_mpu1 <- remove_signal(oom_list_no_demo_mpu1, demo_list_mpu1)
oom_list_no_demo_mpu2 <- remove_signal(oom_list_no_demo_mpu2, demo_list_mpu2)
oom_list_no_demo_mpu3 <- remove_signal(oom_list_no_demo_mpu3, demo_list_mpu3)
oom_list_no_demo_mpu4 <- remove_signal(oom_list_no_demo_mpu4, demo_list_mpu4)
oom_list_no_demo_mpu5 <- remove_signal(oom_list_no_demo_mpu5, demo_list_mpu5)

list.save(data_list_no_demo_mu1, input_path("data_list_no_demo_mu1.rds", TRUE))
list.save(data_list_no_demo_mu2, input_path("data_list_no_demo_mu2.rds", TRUE))
list.save(data_list_no_demo_mu3, input_path("data_list_no_demo_mu3.rds", TRUE))
list.save(data_list_no_demo_mu4, input_path("data_list_no_demo_mu4.rds", TRUE))
list.save(data_list_no_demo_mu5, input_path("data_list_no_demo_mu5.rds", TRUE))
list.save(
    data_list_no_demo_mpu1,
    input_path("data_list_no_demo_mpu1.rds", TRUE)
)
list.save(
    data_list_no_demo_mpu2,
    input_path("data_list_no_demo_mpu2.rds", TRUE)
)
list.save(
    data_list_no_demo_mpu3,
    input_path("data_list_no_demo_mpu3.rds", TRUE)
)
list.save(
    data_list_no_demo_mpu4,
    input_path("data_list_no_demo_mpu4.rds", TRUE)
)
list.save(
    data_list_no_demo_mpu5,
    input_path("data_list_no_demo_mpu5.rds", TRUE)
)
list.save(oom_list_no_demo_mu1, input_path("oom_list_no_demo_mu1.rds", TRUE))
list.save(oom_list_no_demo_mu2, input_path("oom_list_no_demo_mu2.rds", TRUE))
list.save(oom_list_no_demo_mu3, input_path("oom_list_no_demo_mu3.rds", TRUE))
list.save(oom_list_no_demo_mu4, input_path("oom_list_no_demo_mu4.rds", TRUE))
list.save(oom_list_no_demo_mu5, input_path("oom_list_no_demo_mu5.rds", TRUE))
list.save(oom_list_no_demo_mpu1, input_path("oom_list_no_demo_mpu1.rds", TRUE))
list.save(oom_list_no_demo_mpu2, input_path("oom_list_no_demo_mpu2.rds", TRUE))
list.save(oom_list_no_demo_mpu3, input_path("oom_list_no_demo_mpu3.rds", TRUE))
list.save(oom_list_no_demo_mpu4, input_path("oom_list_no_demo_mpu4.rds", TRUE))
list.save(oom_list_no_demo_mpu5, input_path("oom_list_no_demo_mpu5.rds", TRUE))

data_list_no_demo_mu1 <- list.load(
    input_path(
        "2024_02_25_data_list_no_demo_mu1.rds"
    )
)
data_list_no_demo_mu2 <- list.load(
    input_path(
        "2024_02_25_data_list_no_demo_mu2.rds"
    )
)
data_list_no_demo_mu3 <- list.load(
    input_path(
        "2024_02_25_data_list_no_demo_mu3.rds"
    )
)
data_list_no_demo_mu4 <- list.load(
    input_path(
        "2024_02_25_data_list_no_demo_mu4.rds"
    )
)
data_list_no_demo_mu5 <- list.load(
    input_path(
        "2024_02_25_data_list_no_demo_mu5.rds"
    )
)
data_list_no_demo_mpu1 <- list.load(
    input_path(
        "2024_02_25_data_list_no_demo_mpu1.rds"
    )
)
data_list_no_demo_mpu2 <- list.load(
    input_path(
        "2024_02_25_data_list_no_demo_mpu2.rds"
    )
)
data_list_no_demo_mpu3 <- list.load(
    input_path(
        "2024_02_25_data_list_no_demo_mpu3.rds"
    )
)
data_list_no_demo_mpu4 <- list.load(
    input_path(
        "2024_02_25_data_list_no_demo_mpu4.rds"
    )
)
data_list_no_demo_mpu5 <- list.load(
    input_path(
        "2024_02_25_data_list_no_demo_mpu5.rds"
    )
)

oom_list_no_demo_mu1 <- list.load(
    input_path(
        "2024_02_27_oom_list_no_demo_mu1.rds"
    )
)
oom_list_no_demo_mu2 <- list.load(
    input_path(
        "2024_02_27_oom_list_no_demo_mu2.rds"
    )
)
oom_list_no_demo_mu3 <- list.load(
    input_path(
        "2024_02_27_oom_list_no_demo_mu3.rds"
    )
)
oom_list_no_demo_mu4 <- list.load(
    input_path(
        "2024_02_27_oom_list_no_demo_mu4.rds"
    )
)
oom_list_no_demo_mu5 <- list.load(
    input_path(
        "2024_02_27_oom_list_no_demo_mu5.rds"
    )
)
oom_list_no_demo_mpu1 <- list.load(
    input_path(
        "2024_02_27_oom_list_no_demo_mpu1.rds"
    )
)
oom_list_no_demo_mpu2 <- list.load(
    input_path(
        "2024_02_27_oom_list_no_demo_mpu2.rds"
    )
)
oom_list_no_demo_mpu3 <- list.load(
    input_path(
        "2024_02_27_oom_list_no_demo_mpu3.rds"
    )
)
oom_list_no_demo_mpu4 <- list.load(
    input_path(
        "2024_02_27_oom_list_no_demo_mpu4.rds"
    )
)
oom_list_no_demo_mpu5 <- list.load(
    input_path(
        "2024_02_27_oom_list_no_demo_mpu5.rds"
    )
)

settings_matrix_no_demo_mu1 <- generate_settings_matrix(
    data_list_no_demo_mu1,
    nrow = 200,
    seed = 42,
    distance_metrics_list = my_distance_metrics
)

write_csv(
    settings_matrix_no_demo_mu1,
    proc_path("settings_matrix_no_demo_mu1.csv", TRUE)
)

settings_matrix_no_demo_mu1 <- read_csv(
    proc_path("2024_02_25_settings_matrix_no_demo_mu1.csv")
)

###############################################################################
# SNF!
###############################################################################

# Uninjured only imputed
# Imputation 1
start <- proc.time()
progressr::with_progress({
    solutions_matrix_no_demo_mu1 <- batch_snf(
        data_list = data_list_no_demo_mu1,
        settings_matrix = settings_matrix_no_demo_mu1,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_no_demo_mu1,
    proc_path("solutions_matrix_no_demo_mu1.csv", TRUE)
)
# Imputation 2
start <- proc.time()
progressr::with_progress({
    solutions_matrix_no_demo_mu2 <- batch_snf(
        data_list = data_list_no_demo_mu2,
        settings_matrix = settings_matrix_no_demo_mu1,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_no_demo_mu2,
    proc_path("solutions_matrix_no_demo_mu2.csv", TRUE)
)
# Imputation 3
start <- proc.time()
progressr::with_progress({
    solutions_matrix_no_demo_mu3 <- batch_snf(
        data_list = data_list_no_demo_mu3,
        settings_matrix = settings_matrix_no_demo_mu1,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_no_demo_mu3,
    proc_path("solutions_matrix_no_demo_mu3.csv", TRUE)
)
# Imputation 4
start <- proc.time()
progressr::with_progress({
    solutions_matrix_no_demo_mu4 <- batch_snf(
        data_list = data_list_no_demo_mu4,
        settings_matrix = settings_matrix_no_demo_mu1,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_no_demo_mu4,
    proc_path("solutions_matrix_no_demo_mu4.csv", TRUE)
)
# Imputation 5
start <- proc.time()
progressr::with_progress({
    solutions_matrix_no_demo_mu5 <- batch_snf(
        data_list = data_list_no_demo_mu5,
        settings_matrix = settings_matrix_no_demo_mu1,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_no_demo_mu5,
    proc_path("solutions_matrix_no_demo_mu5.csv", TRUE)
)
# mTBI and uninjured pooled imputed
# Imputation 1
start <- proc.time()
progressr::with_progress({
    solutions_matrix_no_demo_mpu1 <- batch_snf(
        data_list = data_list_no_demo_mpu1,
        settings_matrix = settings_matrix_no_demo_mu1,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_no_demo_mpu1,
    proc_path("solutions_matrix_no_demo_mpu1.csv", TRUE)
)
# Imputation 2
start <- proc.time()
progressr::with_progress({
    solutions_matrix_no_demo_mpu2 <- batch_snf(
        data_list = data_list_no_demo_mpu2,
        settings_matrix = settings_matrix_no_demo_mu1,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_no_demo_mpu2,
    proc_path("solutions_matrix_no_demo_mpu2.csv", TRUE)
)
# Imputation 3
start <- proc.time()
progressr::with_progress({
    solutions_matrix_no_demo_mpu3 <- batch_snf(
        data_list = data_list_no_demo_mpu3,
        settings_matrix = settings_matrix_no_demo_mu1,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_no_demo_mpu3,
    proc_path("solutions_matrix_no_demo_mpu3.csv", TRUE)
)
# Imputation 4
start <- proc.time()
progressr::with_progress({
    solutions_matrix_no_demo_mpu4 <- batch_snf(
        data_list = data_list_no_demo_mpu4,
        settings_matrix = settings_matrix_no_demo_mu1,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_no_demo_mpu4,
    proc_path("solutions_matrix_no_demo_mpu4.csv", TRUE)
)
# Imputation 5
start <- proc.time()
progressr::with_progress({
    solutions_matrix_no_demo_mpu5 <- batch_snf(
        data_list = data_list_no_demo_mpu5,
        settings_matrix = settings_matrix_no_demo_mu1,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_no_demo_mpu5,
    proc_path("solutions_matrix_no_demo_mpu5.csv", TRUE)
)
```

```{r}
solutions_matrix_no_demo_mu1 <- read_csv(proc_path("2024_02_25_solutions_matrix_no_demo_mu1.csv"))
solutions_matrix_no_demo_mu2 <- read_csv(proc_path("2024_02_25_solutions_matrix_no_demo_mu2.csv"))
solutions_matrix_no_demo_mu3 <- read_csv(proc_path("2024_02_25_solutions_matrix_no_demo_mu3.csv"))
solutions_matrix_no_demo_mu4 <- read_csv(proc_path("2024_02_25_solutions_matrix_no_demo_mu4.csv"))
solutions_matrix_no_demo_mu5 <- read_csv(proc_path("2024_02_25_solutions_matrix_no_demo_mu5.csv"))
solutions_matrix_no_demo_mpu1 <- read_csv(proc_path("2024_02_25_solutions_matrix_no_demo_mpu1.csv"))
solutions_matrix_no_demo_mpu2 <- read_csv(proc_path("2024_02_25_solutions_matrix_no_demo_mpu2.csv"))
solutions_matrix_no_demo_mpu3 <- read_csv(proc_path("2024_02_25_solutions_matrix_no_demo_mpu3.csv"))
solutions_matrix_no_demo_mpu4 <- read_csv(proc_path("2024_02_25_solutions_matrix_no_demo_mpu4.csv"))
solutions_matrix_no_demo_mpu5 <- read_csv(proc_path("2024_02_25_solutions_matrix_no_demo_mpu5.csv"))

all_mu_imputations_no_demo <- do.call(
    "rbind",
    list(
        solutions_matrix_no_demo_mu1,
        solutions_matrix_no_demo_mu2,
        solutions_matrix_no_demo_mu3,
        solutions_matrix_no_demo_mu4,
        solutions_matrix_no_demo_mu5,
        solutions_matrix_no_demo_mpu1,
        solutions_matrix_no_demo_mpu2,
        solutions_matrix_no_demo_mpu3,
        solutions_matrix_no_demo_mpu4,
        solutions_matrix_no_demo_mpu5
    )
)
```

```{r}
aris_mu1_no_demo <- calc_om_aris(solutions_matrix_no_demo_mu1, verbose = TRUE)
write_csv(data.frame(aris_mu1_no_demo), proc_path("aris_mu1_no_demo.csv", TRUE))
aris_mu2_no_demo <- calc_om_aris(solutions_matrix_no_demo_mu2, verbose = TRUE)
write_csv(data.frame(aris_mu2_no_demo), proc_path("aris_mu2_no_demo.csv", TRUE))
aris_mu3_no_demo <- calc_om_aris(solutions_matrix_no_demo_mu3, verbose = TRUE)
write_csv(data.frame(aris_mu3_no_demo), proc_path("aris_mu3_no_demo.csv", TRUE))
aris_mu4_no_demo <- calc_om_aris(solutions_matrix_no_demo_mu4, verbose = TRUE)
write_csv(data.frame(aris_mu4_no_demo), proc_path("aris_mu4_no_demo.csv", TRUE))
aris_mu5_no_demo <- calc_om_aris(solutions_matrix_no_demo_mu5, verbose = TRUE)
write_csv(data.frame(aris_mu5_no_demo), proc_path("aris_mu5_no_demo.csv", TRUE))
aris_mpu1_no_demo <- calc_om_aris(solutions_matrix_no_demo_mpu1, verbose = TRUE)
write_csv(data.frame(aris_mpu1_no_demo), proc_path("aris_mpu1_no_demo.csv", TRUE))
aris_mpu2_no_demo <- calc_om_aris(solutions_matrix_no_demo_mpu2, verbose = TRUE)
write_csv(data.frame(aris_mpu2_no_demo), proc_path("aris_mpu2_no_demo.csv", TRUE))
aris_mpu3_no_demo <- calc_om_aris(solutions_matrix_no_demo_mpu3, verbose = TRUE)
write_csv(data.frame(aris_mpu3_no_demo), proc_path("aris_mpu3_no_demo.csv", TRUE))
aris_mpu4_no_demo <- calc_om_aris(solutions_matrix_no_demo_mpu4, verbose = TRUE)
write_csv(data.frame(aris_mpu4_no_demo), proc_path("aris_mpu4_no_demo.csv", TRUE))
aris_mpu5_no_demo <- calc_om_aris(solutions_matrix_no_demo_mpu5, verbose = TRUE)
write_csv(data.frame(aris_mpu5_no_demo), proc_path("aris_mpu5_no_demo.csv", TRUE))
aris_all_mu_imputations_no_demo <- calc_om_aris(
    all_mu_imputations_no_demo,
    verbose = TRUE
)
write_csv(
    data.frame(aris_all_mu_imputations_no_demo),
    proc_path("aris_all_mu_imputations_no_demo.csv", TRUE)
)

```

## Re-importing the ARIs

```{r}
aris_mu1_no_demo <- read_csv(proc_path("2024_02_25_aris_mu1_no_demo.csv")) |>
    as.matrix()
aris_mu2_no_demo <- read_csv(proc_path("2024_02_25_aris_mu2_no_demo.csv")) |>
    as.matrix()
aris_mu3_no_demo <- read_csv(proc_path("2024_02_25_aris_mu3_no_demo.csv")) |>
    as.matrix()
aris_mu4_no_demo <- read_csv(proc_path("2024_02_25_aris_mu4_no_demo.csv")) |>
    as.matrix()
aris_mu5_no_demo <- read_csv(proc_path("2024_02_25_aris_mu5_no_demo.csv")) |>
    as.matrix()
aris_mpu1_no_demo <- read_csv(proc_path("2024_02_25_aris_mpu1_no_demo.csv")) |>
    as.matrix()
aris_mpu2_no_demo <- read_csv(proc_path("2024_02_25_aris_mpu2_no_demo.csv")) |>
    as.matrix()
aris_mpu3_no_demo <- read_csv(proc_path("2024_02_25_aris_mpu3_no_demo.csv")) |>
    as.matrix()
aris_mpu4_no_demo <- read_csv(proc_path("2024_02_25_aris_mpu4_no_demo.csv")) |>
    as.matrix()
aris_mpu5_no_demo <- read_csv(proc_path("2024_02_25_aris_mpu5_no_demo.csv")) |>
    as.matrix()

aris_all_mu_imputations_no_demo <- read_csv(
    proc_path("2024_02_25_aris_all_mu_imputations_no_demo.csv")
) |>
    as.matrix()
```


## Plotting the ARIs

### Initial plot across all ARIs to extract order

```{r}
aris_all_mu_imputations_no_demo_heatmap <- similarity_matrix_heatmap(
    aris_all_mu_imputations_no_demo,
    log_graph = FALSE,
    cluster_rows = TRUE,
    cluster_columns = TRUE
)

aris_all_mu_imputations_no_demo_heatmap <- ComplexHeatmap::draw(
    aris_all_mu_imputations_no_demo_heatmap
)
aris_all_mu_imputations_order_no_demo <- ComplexHeatmap::row_order(
    aris_all_mu_imputations_no_demo_heatmap
)

write_csv(
    data.frame(aris_all_mu_imputations_order_no_demo),
    proc_path("aris_all_mu_imputations_order_no_demo.csv", TRUE)
)
```

### Re-importing the order

```{r}
aris_all_mu_imputations_order_no_demo <- unlist(
    read_csv(
        proc_path("2024_02_25_aris_all_mu_imputations_order_no_demo.csv")
    )
)

names(aris_all_mu_imputations_order_no_demo) <- NULL
```

## Full imputation meta clustering plot with impairment levels

```{r}

imputation_labels <- data.frame(
    "imputation" = c(
        rep("u1", 200),
        rep("u2", 200),
        rep("u3", 200),
        rep("u4", 200),
        rep("u5", 200),
        rep("pu1", 200),
        rep("pu2", 200),
        rep("pu3", 200),
        rep("pu4", 200),
        rep("pu5", 200)
    ),
    "pooled" = c(
        rep("yes", 1000),
        rep("no", 1000)
    )
)

full_solutions_matrix_no_demo <- cbind(
    all_mu_imputations_no_demo,
    imputation_labels
)

#full_solutions_matrix_no_demo$"nclust2" <-
#    full_solutions_matrix_no_demo$"nclust" - 2

full_mu_o_extended_solutions_matrix_no_demo <- extend_solutions(
    full_solutions_matrix_no_demo,
    oom_list_no_demo_mu1,
    verbose = TRUE,
    min_pval = 1e-10
)
write_csv(
    full_mu_o_extended_solutions_matrix_no_demo,
    proc_path("full_mu_o_extended_solutions_matrix_no_demo.csv", TRUE)
)
full_mu_io_extended_solutions_matrix_no_demo <- extend_solutions(
    full_solutions_matrix_no_demo,
    target_list = c(data_list_no_demo_mu1, oom_list_no_demo_mu1),
    verbose = TRUE,
    min_pval = 1e-10
)
write_csv(
    full_mu_io_extended_solutions_matrix_no_demo,
    proc_path("full_mu_io_extended_solutions_matrix_no_demo.csv", TRUE)
)
```

Here 2024-02-27 14:47

```{r}
full_mu_o_extended_solutions_matrix_no_demo <- read_csv(
    proc_path("2024_02_27_full_mu_o_extended_solutions_matrix_no_demo.csv")
)

full_mu_io_extended_solutions_matrix_no_demo <- read_csv(
    proc_path("2024_02_27_full_mu_io_extended_solutions_matrix_no_demo.csv")
)
```

```{r}

split_vec = c(
    329,
    520,
    823,
    928,
    1030,
    1090,
    1470,
    1700,
    1840,
    1920
)
mu_nd_mc_heatmap <- my_similarity_matrix_heatmap(
    aris = aris_all_mu_imputations_no_demo,
    aris_order = aris_all_mu_imputations_order_no_demo,
    extended_solutions = full_mu_o_extended_solutions_matrix_no_demo,
    split_vector = split_vec
)
mu_nd_mc_heatmap


# PNG export
grDevices::png(
    fig_path("mu_nd_mc_heatmap.png", TRUE),
    width = 3000,
    height = 3000,
    res = 300
)
mu_nd_mc_heatmap
grDevices::dev.off()
```

## One-MC-at-a-time

```{r}

mu_nd_manhattan <- my_manhattan_plot(
    solutions_matrix = full_mu_io_extended_solutions_matrix_no_demo,
    aris_order = aris_all_mu_imputations_order_no_demo,
    split_vector = split_vec,
    data_list = data_list_no_demo_mu1,
    target_list = oom_list_no_demo_mu1,
    colours = c(
        "I-AS" = "#1B9E77",
        "I-D" = "#D95F02",
        "I-N" = "#7570B3",
        "I-MH" = "#E7298A",
        "I-P" = "#66A61E",
        "O-S" = "#E6AB02",
        "O-B" = "#A6761D"
    )
)
mu_nd_manhattan

ggsave(
    plot = mu_nd_manhattan,
    fig_path("mu_nd_manhattan.png", TRUE),
    width = 15,
    height = 11*2.5
)

# Bulk export each MC individually
for (mc in split_letters(split_vec)) {
    print(mc)
    mc_plot <- my_manhattan_plot(
        solutions_matrix = full_mu_io_extended_solutions_matrix_no_demo,
        aris_order = aris_all_mu_imputations_order_no_demo,
        split_vector = split_vec,
        data_list = data_list_no_demo_mu1,
        target_list = oom_list_no_demo_mu1,
        colours = c(
            "I-AS" = "#1B9E77",
            "I-D" = "#D95F02",
            "I-N" = "#7570B3",
            "I-MH" = "#E7298A",
            "I-P" = "#66A61E",
            "O-S" = "#E6AB02",
            "O-B" = "#A6761D"
        )
    )
    mc_path <- paste0(
        "mu_nd_mc_",
        gsub("-", "_", tolower(mc)),
        "_manhattan.png"
    )
    ggsave(
        plot = mc_plot,
        fig_path(mc_path, TRUE),
        width = 15,
        height = 5
    )
}

```
