```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(rlist)
library(ggplot2)
library(patchwork)
library(dplyr)
library(fastDummies)
library(tidyr)
library(ggpubr)
library(ComplexHeatmap)
library(Hmisc)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subs <- read_csv(sub_path("2025_02_07_mtbi_subs.csv"))
mtbi_train_subs <- read_csv(sub_path("2025_02_07_mtbi_train_subs.csv"))
mtbi_test_subs <- read_csv(sub_path("2025_02_07_mtbi_test_subs.csv"))
unij_subs <- read_csv(sub_path("2025_02_07_unij_subs.csv"))
```


```{r}
# Data frame of all the features, observations, and cluster assignments
mtbi_ful_df <- as.data.frame(readRDS(proc_path("2025_02_13_mtbi_ful_df.rds")))

all_dls <- readRDS(input_path("2025_02_10_all_dls.rds"))

# An uninjured data frame
unij_dl_s1 <- c(all_dls$"unij_data_lists"[[1]], all_dls$"unij_oom_lists"[[1]])
unij_df <- as.data.frame(unij_dl_s1)
unij_df$"cluster" <- "ctrl"

# A compatible comparison mTBI data frame
mtbi_df <- mtbi_ful_df[, colnames(unij_df)]

# A joint data frame
df <- rbind(mtbi_df, unij_df)

```

```{r}

# Input features adjusted for demographics
dl_corrected <- readRDS(proc_path("2025_02_13_dl_corrected.rds"))

# Outcome features adjusted for demographics
adj_oom_list <- readRDS(proc_path("2025_03_17_adj_oom_list.rds"))

dl_corrected

full_oom_list_1 <- readRDS(input_path("2025_02_12_mtbi_full_oom_list_1.rds"))
full_data_list_1 <- readRDS(input_path("2025_02_12_mtbi_full_data_list_1.rds"))

dl_no_demo <- full_data_list_1[-c(6:9)] 
dl_demo <- full_data_list_1[c(6:9)]

mtbi_demo_dl <- c(dl_corrected, adj_oom_list)
mtbi_demo_dl <- c(mtbi_demo_dl, dl_demo)

mtbi_demo_df <- as.data.frame(mtbi_demo_dl)
mtbi_demo_df$"cluster" <- mtbi_ful_df$"cluster"

mtbi_raw_dl <- c(full_data_list_1, full_oom_list_1)
mtbi_raw_df <- as.data.frame(mtbi_raw_dl)
mtbi_raw_df$"cluster" <- mtbi_ful_df$"cluster"

fdr_matrix <- function(mat) {
    pvals <- mat[upper.tri(mat)]
    p_adjusted <- p.adjust(pvals, method = "fdr")
    adj_mat <- mat
    adj_mat[upper.tri(adj_mat)] <- p_adjusted
    adj_mat[lower.tri(adj_mat)] <- t(adj_mat)[lower.tri(adj_mat)]
    return(adj_mat)
}

raw_mtbi_cmat <- mtbi_raw_df |>
    dplyr::mutate(minority = as.numeric(race != "white")) |>
    dplyr::select(-cluster, -uid, -race, -mtbi_mechanism) |>
    cor()
raw_mtbi_order <- get_matrix_order(raw_mtbi_cmat)
raw_mtbi_cmat <- raw_mtbi_cmat[raw_mtbi_order, raw_mtbi_order]
raw_mtbi_hm <- Heatmap(raw_mtbi_cmat, cluster_rows = FALSE, cluster_columns = FALSE)
#
raw_mtbi_cmat_1 <- mtbi_raw_df |>
    dplyr::filter(cluster == 1) |>
    dplyr::mutate(minority = as.numeric(race != "white")) |>
    dplyr::select(-cluster, -uid, -race, -mtbi_mechanism) |>
    cor()
raw_mtbi_cmat_1 <- raw_mtbi_cmat_1[colnames(raw_mtbi_cmat), colnames(raw_mtbi_cmat)]
raw_mtbi_hm_1 <- Heatmap(raw_mtbi_cmat_1, cluster_rows = FALSE, cluster_columns = FALSE)
#
raw_mtbi_cmat_2 <- mtbi_raw_df |>
    dplyr::filter(cluster == 2) |>
    dplyr::mutate(minority = as.numeric(race != "white")) |>
    dplyr::select(-cluster, -uid, -race, -mtbi_mechanism) |>
    cor()
raw_mtbi_cmat_2 <- raw_mtbi_cmat_2[colnames(raw_mtbi_cmat), colnames(raw_mtbi_cmat)]
raw_mtbi_hm_2 <- Heatmap(raw_mtbi_cmat_2, cluster_rows = FALSE, cluster_columns = FALSE)
#
raw_mtbi_cmat_3 <- mtbi_raw_df |>
    dplyr::filter(cluster == 3) |>
    dplyr::mutate(minority = as.numeric(race != "white")) |>
    dplyr::select(-cluster, -uid, -race, -mtbi_mechanism) |>
    cor()
raw_mtbi_cmat_3 <- raw_mtbi_cmat_3[colnames(raw_mtbi_cmat), colnames(raw_mtbi_cmat)]
raw_mtbi_hm_3 <- Heatmap(raw_mtbi_cmat_3, cluster_rows = FALSE, cluster_columns = FALSE)
#
raw_mtbi_cmat_12 <- mtbi_raw_df |>
    dplyr::filter(cluster == 3) |>
    dplyr::mutate(minority = as.numeric(race != "white")) |>
    dplyr::select(-cluster, -uid, -race, -mtbi_mechanism) |>
    cor()
raw_mtbi_cmat_12 <- raw_mtbi_cmat_12[colnames(raw_mtbi_cmat), colnames(raw_mtbi_cmat)]
raw_mtbi_hm_12 <- Heatmap(raw_mtbi_cmat_12, cluster_rows = FALSE, cluster_columns = FALSE)
#
raw_mtbi_cmat_m <- mtbi_raw_df |>
    dplyr::filter(sex == 0) |>
    dplyr::mutate(minority = as.numeric(race != "white")) |>
    dplyr::select(-cluster, -uid, -race, -mtbi_mechanism) |>
    cor()
raw_mtbi_cmat_m <- raw_mtbi_cmat_m[colnames(raw_mtbi_cmat), colnames(raw_mtbi_cmat)]
raw_mtbi_hm_m <- Heatmap(raw_mtbi_cmat_m, cluster_rows = FALSE, cluster_columns = FALSE)
#
raw_mtbi_cmat_f <- mtbi_raw_df |>
    dplyr::filter(sex == 1) |>
    dplyr::mutate(minority = as.numeric(race != "white")) |>
    dplyr::select(-cluster, -uid, -race, -mtbi_mechanism) |>
    cor()
raw_mtbi_cmat_f <- raw_mtbi_cmat_f[colnames(raw_mtbi_cmat), colnames(raw_mtbi_cmat)]
raw_mtbi_hm_f <- Heatmap(raw_mtbi_cmat_f, cluster_rows = FALSE, cluster_columns = FALSE)
#
#------------------------------------------------------------------------------
#
demo_mtbi_cmat <- mtbi_demo_df |>
    dplyr::mutate(minority = as.numeric(race != "white")) |>
    dplyr::select(-cluster, -uid, -race, -mtbi_mechanism) |>
    cor()
demo_mtbi_cmat <- demo_mtbi_cmat[colnames(raw_mtbi_cmat), colnames(raw_mtbi_cmat)]
demo_mtbi_hm <- Heatmap(demo_mtbi_cmat, cluster_rows = FALSE, cluster_columns = FALSE)
#
demo_mtbi_cmat_1 <- mtbi_demo_df |>
    dplyr::filter(cluster == 1) |>
    dplyr::mutate(minority = as.numeric(race != "white")) |>
    dplyr::select(-cluster, -uid, -race, -mtbi_mechanism) |>
    cor()
demo_mtbi_cmat_1 <- demo_mtbi_cmat_1[colnames(raw_mtbi_cmat), colnames(raw_mtbi_cmat)]
demo_mtbi_hm_1 <- Heatmap(demo_mtbi_cmat_1, cluster_rows = FALSE, cluster_columns = FALSE)
#
demo_mtbi_cmat_2 <- mtbi_demo_df |>
    dplyr::filter(cluster == 2) |>
    dplyr::mutate(minority = as.numeric(race != "white")) |>
    dplyr::select(-cluster, -uid, -race, -mtbi_mechanism) |>
    cor()
demo_mtbi_cmat_2 <- demo_mtbi_cmat_2[colnames(raw_mtbi_cmat), colnames(raw_mtbi_cmat)]
demo_mtbi_hm_2 <- Heatmap(demo_mtbi_cmat_2, cluster_rows = FALSE, cluster_columns = FALSE)
#
demo_mtbi_cmat_3 <- mtbi_demo_df |>
    dplyr::filter(cluster == 3) |>
    dplyr::mutate(minority = as.numeric(race != "white")) |>
    dplyr::select(-cluster, -uid, -race, -mtbi_mechanism) |>
    cor()
demo_mtbi_cmat_3 <- demo_mtbi_cmat_3[colnames(raw_mtbi_cmat), colnames(raw_mtbi_cmat)]
demo_mtbi_hm_3 <- Heatmap(demo_mtbi_cmat_3, cluster_rows = FALSE, cluster_columns = FALSE)
#
demo_mtbi_cmat_12 <- mtbi_demo_df |>
    dplyr::filter(cluster == 3) |>
    dplyr::mutate(minority = as.numeric(race != "white")) |>
    dplyr::select(-cluster, -uid, -race, -mtbi_mechanism) |>
    cor()
demo_mtbi_cmat_12 <- demo_mtbi_cmat_12[colnames(raw_mtbi_cmat), colnames(raw_mtbi_cmat)]
demo_mtbi_hm_12 <- Heatmap(demo_mtbi_cmat_12, cluster_rows = FALSE, cluster_columns = FALSE)
#
demo_mtbi_cmat_m <- mtbi_demo_df |>
    dplyr::filter(sex == 0) |>
    dplyr::mutate(minority = as.numeric(race != "white")) |>
    dplyr::select(-cluster, -uid, -race, -mtbi_mechanism) |>
    cor()
demo_mtbi_cmat_m <- demo_mtbi_cmat_m[colnames(raw_mtbi_cmat), colnames(raw_mtbi_cmat)]
demo_mtbi_hm_m <- Heatmap(demo_mtbi_cmat_m, cluster_rows = FALSE, cluster_columns = FALSE)
#
demo_mtbi_cmat_f <- mtbi_demo_df |>
    dplyr::filter(sex == 1) |>
    dplyr::mutate(minority = as.numeric(race != "white")) |>
    dplyr::select(-cluster, -uid, -race, -mtbi_mechanism) |>
    cor()
demo_mtbi_cmat_f <- demo_mtbi_cmat_f[colnames(raw_mtbi_cmat), colnames(raw_mtbi_cmat)]
demo_mtbi_hm_f <- Heatmap(demo_mtbi_cmat_f, cluster_rows = FALSE, cluster_columns = FALSE)

save_heatmap(
    raw_mtbi_hm,
    fig_path("raw_mtbi_hm.png", TRUE),
    width = 1500,
    height = 1300,
    res = 130
)

hm_save_fn <- function(hm, name) {
    save_heatmap(
        hm,
        fig_path(name, TRUE),
        width = 1500,
        height = 1300,
        res = 100
    )
}

hm_save_fn(raw_mtbi_hm_1, "raw_mtbi_hm_1.png")
hm_save_fn(raw_mtbi_hm_2, "raw_mtbi_hm_2.png")
hm_save_fn(raw_mtbi_hm_3, "raw_mtbi_hm_3.png")
hm_save_fn(raw_mtbi_hm_12, "raw_mtbi_hm_12.png")
hm_save_fn(raw_mtbi_hm_m, "raw_mtbi_hm_m.png")
hm_save_fn(raw_mtbi_hm_f, "raw_mtbi_hm_f.png")

hm_save_fn(demo_mtbi_hm_1, "demo_mtbi_hm_1.png")
hm_save_fn(demo_mtbi_hm_2, "demo_mtbi_hm_2.png")
hm_save_fn(demo_mtbi_hm_3, "demo_mtbi_hm_3.png")
hm_save_fn(demo_mtbi_hm_12, "demo_mtbi_hm_12.png")
hm_save_fn(demo_mtbi_hm_m, "demo_mtbi_hm_m.png")
hm_save_fn(demo_mtbi_hm_f, "demo_mtbi_hm_f.png")

#------------------------------------------------------------------------------

abs_hm_fn <- function(mat1, mat2, thresh = 0) {
    breaks <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5)
    colors <- RColorBrewer::brewer.pal(n = 6, name = "BuPu")
    col_fun <- circlize::colorRamp2(breaks, colors)  # Maps discrete ranges to colors
    mat <- abs(mat1 - mat2)
    mat <- ifelse(mat > thresh, mat, 0)
    Heatmap(
        mat,
        cluster_rows = FALSE,
        cluster_columns = FALSE,
        col = col_fun
    )
}

raw_vs_demo <- abs_hm_fn(raw_mtbi_cmat, demo_mtbi_cmat, thresh = 0.2)
raw_vs_raw1 <- abs_hm_fn(raw_mtbi_cmat, raw_mtbi_cmat_1, thresh = 0.2)
raw_vs_raw2 <- abs_hm_fn(raw_mtbi_cmat, raw_mtbi_cmat_2, thresh = 0.2)
raw_vs_raw3 <- abs_hm_fn(raw_mtbi_cmat, raw_mtbi_cmat_3, thresh = 0.2)
raw1_vs_raw2 <- abs_hm_fn(raw_mtbi_cmat_1, raw_mtbi_cmat_2, thresh = 0.3)
raw2_vs_raw3 <- abs_hm_fn(raw_mtbi_cmat_2, raw_mtbi_cmat_3, thresh = 0.3)
rawm_vs_rawf <- abs_hm_fn(raw_mtbi_cmat_m, raw_mtbi_cmat_f, thresh = 0.3)
demo_vs_demo1 <-  abs_hm_fn(demo_mtbi_cmat, demo_mtbi_cmat_1, thresh = 0.2)
demo_vs_demo2 <- abs_hm_fn(demo_mtbi_cmat, demo_mtbi_cmat_2, thresh = 0.3)
demo_vs_demo3 <- abs_hm_fn(demo_mtbi_cmat, demo_mtbi_cmat_3, thresh = 0.3)
demo1_vs_demo2 <- abs_hm_fn(demo_mtbi_cmat_1, demo_mtbi_cmat_2, thresh = 0.4)
demo2_vs_demo3 <- abs_hm_fn(demo_mtbi_cmat_2, demo_mtbi_cmat_3, thresh = 0.35)
demom_vs_demof <- abs_hm_fn(demo_mtbi_cmat_m, demo_mtbi_cmat_f, thresh = 0.3)

hm_save_fn(raw_vs_demo, "raw_vs_demo.png")
hm_save_fn(raw_vs_raw1, "raw_vs_raw1.png")
hm_save_fn(raw_vs_raw2, "raw_vs_raw2.png")
hm_save_fn(raw_vs_raw3, "raw_vs_raw3.png")
hm_save_fn(raw1_vs_raw2, "raw1_vs_raw2.png")
hm_save_fn(raw2_vs_raw3, "raw2_vs_raw3.png")
hm_save_fn(rawm_vs_rawf, "rawm_vs_rawf.png")
hm_save_fn(demo_vs_demo1, "demo_vs_demo1.png")
hm_save_fn(demo_vs_demo2, "demo_vs_demo2.png")
hm_save_fn(demo_vs_demo3, "demo_vs_demo3.png")
hm_save_fn(demo1_vs_demo2, "demo1_vs_demo2.png")
hm_save_fn(demo2_vs_demo3, "demo2_vs_demo3.png")
hm_save_fn(demom_vs_demof, "demom_vs_demof.png")
```

```{r}
demo_mtbi_cmat <- mtbi_demo_df |>
    dummy_cols(
        select_columns = c("race", "mtbi_mechanism"),
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = FALSE
    ) |>
    dplyr::select(-cluster, -uid) |>
    cor()
demo_mtbi_cmat <- demo_mtbi_cmat[colnames(raw_mtbi_cmat), colnames(raw_mtbi_cmat)]
Heatmap(demo_mtbi_cmat, cluster_rows = FALSE, cluster_columns = FALSE)

#send anne the thick cbcl plots page 6
#unique thing ive shown is the inference
#unique structure of the mtbi group
#correlation matrices of TBI vs. matched group
#vulnerability of mTBI grooup
#as kids get older these correlations make sense to matter less
#resilient kids

cmat <- all_corrected_df |>
    dplyr::filter(cluster == 1) |>
    dummy_cols(
        select_columns = "race",
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = FALSE
    ) |>
    dplyr::select(-cluster, -uid, -mtbi_mechanism) |>
    cor()
cmat <- ifelse(abs(cmat) > 0.2, abs(cmat), 0)
Heatmap(cmat)

cmat <- all_corrected_df |>
    dplyr::mutate(minority = as.numeric(race != "white")) |>
    dummy_cols(
        select_columns = "race",
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = FALSE
    ) |>
    dplyr::select(-cluster, -uid, -mtbi_mechanism) |>
    cor()
cmat <- ifelse(abs(cmat) > 0.2, abs(cmat), 0)
Heatmap(cmat)

cmat <- all_corrected_df |>
    dplyr::filter(cluster == 3) |>
    dplyr::mutate(minority = as.numeric(race != "white")) |>
    dummy_cols(
        select_columns = "race",
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = FALSE
    ) |>
    dplyr::select(-cluster, -uid, -mtbi_mechanism) |>
    cor()
cmat <- ifelse(abs(cmat) > 0.2, abs(cmat), abs(cmat))
Heatmap(cmat)

all_corrected_df |>
    dplyr::filter(cluster == 3) |>
    dplyr::mutate(minority = as.numeric(race != "white")) |>
    dplyr::select(-cluster, -uid, -race, -mtbi_mechanism) |>
    cor() |>
    Heatmap()

corrected_assoc_mat <- calc_assoc_pval_matrix(mtbi_demo_dl)
fdr_demo_mat <- fdr_matrix(corrected_assoc_mat)

uncorrected_assoc_mat <- calc_assoc_pval_matrix(all_uncorrected_dl)
fdr_raw_mat <- fdr_matrix(uncorrected_assoc_mat)

fdr_raw_mat["fmri_cort_subcort_cors", ] |>
    ComplexHeatmap::Heatmap()

fdr_raw_mat["cortical_sa", !grepl("cortical_sa|brain_volume|sex|pubertal_status_p|race|cortical_thickness", rownames(fdr_raw_mat))] |>
    log() |>
    ComplexHeatmap::Heatmap()

fdr_raw_mat["pericortical_wm_ndi", ] |>
    ComplexHeatmap::Heatmap()

fdr_demo_mat["fmri_cort_subcort_cors", !grepl("fmri_cort_subcort_cors", rownames(fdr_demo_mat))] |>
    as.data.frame() |>
    rename_with(~ if_else(seq_along(.) == 1, "p", .)) |>
    dplyr::filter(p <= 0.05) |>
    dplyr::mutate(p = -log10(p)) |>
    as.matrix() |>
    ComplexHeatmap::Heatmap()

top_cor_check <- function(mat, ft) {
    mat[ft, !grepl(ft, rownames(mat))] |>
        as.data.frame() |>
        rename_with(~ if_else(seq_along(.) == 1, "p", .)) |>
        dplyr::filter(p <= 0.05) |>
        dplyr::mutate(p = -log10(p)) |>
        as.matrix()
        as.matrix() |>
        ComplexHeatmap::Heatmap()
}

top_cor_check(fdr_demo_mat, "fmri_cort_subcort_cors")

top_cor_check(fdr_demo_mat, "cortical_sa")

top_cor_check(fdr_demo_mat, "cortical_thickness")

top_cor_check(fdr_demo_mat, "brain_volume")

top_cor_check(fdr_demo_mat, "cbcl_aggressive")

# Do this kind of plot for all the features

fdr_demo_mat["cortical_sa", !grepl("cortical_sa|brain_volume|sex|pubertal_status_p|race|cortical_thickness", rownames(fdr_demo_mat))] |>
    log() |>
    ComplexHeatmap::Heatmap()

fdr_demo_mat["pericortical_wm_ndi", ] |>
    ComplexHeatmap::Heatmap()

# No demographic adjustment, correlations of features
# after FDR
raw_assoc_hm <- assoc_pval_heatmap(
    fdr_raw_mat,
    dl = all_uncorrected_dl,
    scale_diag = "none",
    significance_stars = FALSE,
    split_by_domain = TRUE
)
raw_assoc_hm

save_heatmap(
    raw_assoc_hm,
    fig_path(
        "explr_raw_fdr_assoc_hm.png",
        TRUE
    ),
    width = 1500,
    height = 1300,
    res = 130
)

# Demographic adjustment, correlations of features
# after FDR
demo_assoc_hm <- assoc_pval_heatmap(
    fd = fdr_demo_mat,
    dl = mtbi_demo_dl,
    scale_diag = "none",
    significance_stars = FALSE,
    split_by_domain = TRUE
)
demo_assoc_hm

save_heatmap(
    demo_assoc_hm,
    fig_path(
        "explr_demo_fdr_assoc_hm.png",
        TRUE
    ),
    width = 1500,
    height = 1300,
    res = 130
)

fdr_raw_mat2 <- fdr_raw_mat[!grepl("cbcl|sds", colnames(fdr_raw_mat)), grepl("cbcl|sds", colnames(fdr_raw_mat))]
#fdr_raw_mat2 <- fdr_raw_mat2[apply(fdr_raw_mat2, 1, min) <= 0.05, ]
fdr_raw_hm_out <- ComplexHeatmap::Heatmap(
    fdr_raw_mat2,
    col = circlize::colorRamp2(
        c(0, 0.0005, 0.005, 0.05, 1),
        c(
            "black",
            "navy",
            "blue",
            "royalblue",
            "steelblue2"
        )
    ),
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    heatmap_legend_param = list(
        color_bar = "continuous",
        at = c(0, 0.0005, 0.005, 0.05, 1),
        title = "FDR Corrected\np-value",
        break_dist = 1
    )
)
fdr_raw_hm_out

save_heatmap(
    fdr_raw_hm_out,
    fig_path(
        "fdr_raw_hm_out.png",
        TRUE
    ),
    width = 800,
    height = 1300
)

fdr_demo_mat2 <- fdr_demo_mat[!grepl("cbcl|sds", colnames(fdr_demo_mat)), grepl("cbcl|sds", colnames(fdr_demo_mat))]
fdr_demo_mat2 <- fdr_demo_mat2[rownames(fdr_raw_mat2), ]
fdr_demo_hm_out <- ComplexHeatmap::Heatmap(
    fdr_demo_mat2,
    col = circlize::colorRamp2(
        c(0, 0.0005, 0.005, 0.05, 1),
        c(
            "black",
            "navy",
            "blue",
            "royalblue",
            "steelblue2"
        )
    ),
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    heatmap_legend_param = list(
        color_bar = "continuous",
        at = c(0, 0.0005, 0.005, 0.05, 1),
        title = "FDR Corrected\np-value",
        break_dist = 1
    )
)
fdr_demo_hm_out

save_heatmap(
    fdr_demo_hm_out,
    fig_path(
        "fdr_demo_hm_out.png",
        TRUE
    ),
    width = 800,
    height = 1300
)

max(-log10(fdr_demo_mat2))

-log10(0.05)

-log10(1)

-log10(1e-10)

pval_heatmap

ComplexHeatmap::Heatmap(
    -log10(fdr_demo_mat2),
    col = circlize::colorRamp2(
        c(0, -log10(0.05) , -log10(0.01), -log10(0.001), -log10(0.0001)),
        c(
            "steelblue2",
            "royalblue",
            "blue",
            "navy",
            "black"
        )
    ),
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    heatmap_legend_param = list(
        color_bar = "continuous",
        at = c(0, signif(-log10(0.05), 2), -log10(0.01), -log10(0.001), -log10(0.0001)),
        title = "Negative log10\nFDR Corrected\np-value",
        break_dist = 1
    )
)

ComplexHeatmap::Heatmap(
    -log10(fdr_raw_mat2),
    col = circlize::colorRamp2(
        c(0, -log10(0.05) , -log10(0.01), -log10(0.001), -log10(0.0001)),
        c(
            "steelblue2",
            "royalblue",
            "blue",
            "navy",
            "black"
        )
    ),
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    heatmap_legend_param = list(
        color_bar = "continuous",
        at = c(0, signif(-log10(0.05), 2), -log10(0.01), -log10(0.001), -log10(0.0001)),
        title = "Negative log10\nFDR Corrected\np-value",
        break_dist = 1
    )
)

log_pval_hm <- function(mat, colours = NULL) {
    if (is.null(colours)) {
        colours <- c(
            "steelblue2",
            "royalblue",
            "blue",
            "navy",
            "black"
        )
    }
    ComplexHeatmap::Heatmap(
        -log10(mat),
        col = circlize::colorRamp2(
            c(0, -log10(0.05) , -log10(0.01), -log10(0.001), -log10(0.0001)),
            colours
        ),
        cluster_rows = FALSE,
        cluster_columns = FALSE,
        heatmap_legend_param = list(
            color_bar = "continuous",
            at = c(0, signif(-log10(0.05), 2), -log10(0.01), -log10(0.001), -log10(0.0001)),
            title = "Negative log10\nFDR Corrected\np-value",
            break_dist = 1
        )
    )
}

neuro_fts <- c(
    "brain_volume",
    "cortical_thickness",
    "cortical_sa",
    "major_wm_ndi",
    "pericortical_wm_ndi",
    "fmri_cort_cors",
    "fmri_cort_subcort_cors"
)

rownames(fdr_raw_mat2)

log_pval_hm(
    fdr_demo_mat2[neuro_fts, ],
    colours = c(
        "white",
        "orange",
        "red",
        "black",
        "white"
    )
)

log_pval_hm(
    fdr_raw_mat2[neuro_fts, ],
    colours = c(
        "white",
        "orange",
        "red",
        "black",
        "white"
    )
)

log_pval_hm(
    fdr_raw_mat2[neuro_fts, ]
)

log_pval_hm(
    fdr_demo_mat2[neuro_fts, ]
)

fdr_raw_mat3 <- ifelse(fdr_raw_mat2 <= 0.05, 1, 0)

fdr_demo_mat2[neuro_fts, ]

ComplexHeatmap::Heatmap(fdr_raw_mat3[neuro_fts, ])
```

These heatmaps serve as the starting point for which specific associations to dig deeper into.


Probably would be valuable to really zoom in on the effect of the concussion itself.

## Physiological characterization

```{r}
mtbi_ful_df <- as.data.frame(readRDS(proc_path("2025_02_13_mtbi_ful_df.rds")))

# Seems to still persist after demographic correction?
z1 <- all_corrected_df |>
    ggplot(
        aes(x = cluster, y = fmri_cort_subcort_cors)
    ) +
    geom_boxplot() + 
    geom_jitter(height = 0, width = 0.1, alpha = 0.4) 
z1

ggsave(fig_path("z1.png"), z1)

z2 <- all_corrected_df |>
    ggplot(
        aes(y = cbcl_attention, x = fmri_cort_subcort_cors)
    ) +
    geom_smooth(method = "lm") +
    geom_point()

ggsave(fig_path("z2.png"), z2)


z3 <- all_corrected_df |>
    ggplot(
        aes(y = cbcl_somatic, x = pericortical_wm_ndi)
    ) +
    geom_smooth(method = "lm") +
    geom_point()


ggsave(fig_path("z3.png"), z3)


# value in looking at thise within subgroups
all_corrected_df |>
    ggplot(
        aes(x = weekday_screentime, y = cbcl_aggressive)
    ) +
    geom_point() 


# Appears to be quite a substantial difference in cort-subcort fMRI
mtbi_ful_df |>
    ggplot(
        aes(x = mtbi_mechanism, y = cbcl_somatic)
    ) +
    geom_violin() + 
    geom_jitter() 

# Is this really correlated with outcomes directly?

mtbi_ful_df |>
    dplyr::mutate(
        cbcl_total = rowSums(across(starts_with("cbcl")))
    ) |>
    ggplot(
        aes(y = fmri_cort_subcort_cors, x = race)
    ) +
    geom_boxplot() +
    geom_point() 

colnames(mtbi_ful_df)

full_data_list_1 <- readRDS(
    input_path(
        "2025_02_12_mtbi_full_data_list_1.rds"
    )
)

der_pl <- readRDS(fig_path("2025_02_12_ap_mtbi_mc_f_plot_list.rds"))

der_pl$"fmri_cort_cors"

der_pl$"fmri_cort_subcort_cors"

my_ttest <- function(df, ft, c1 = 1, c2 = 2) {
    group_1 <- df |>
        dplyr::filter(cluster == c1) |>
        dplyr::select(dplyr::all_of(ft)) |>
        unlist()
        as.numeric()
    group_2 <- df |>
        dplyr::filter(cluster == c2) |>
        dplyr::select(dplyr::all_of(ft)) |>
        unlist()
        as.numeric()
    return(t.test(group_1, group_2))
}

my_ttest(mtbi_ful_df, "fmri_cort_subcort_cors")

my_ttest(all_corrected_df, "fmri_cort_subcort_cors")

```

### Sleep?

```{r}
import <- function(path) {
    return(abcd_load(core_path(path)))
}

ph_p_sds <- import("physical-health/ph_p_sds.csv")

mtbi_subs <- read_subjects(sub_path("2025_02_07_mtbi_subs.csv"))
unij_subs <- read_subjects(sub_path("2025_02_07_unij_subs.csv"))
```

```{r}
sleep <- ph_p_sds |>
    filter_timepoint(t = 0) |>
    filter_subjects(mtbi_subs)

sleep$"uid" <- paste0("uid_", sleep$"subjectkey") 

q <- search_dd("ph_p_sds") |>
    dplyr::filter(grepl("sds_p_ss", var_name))

q$"var_label"

print(search_dd("ph_p_sds"), n= 50)

sleep_df <- dplyr::inner_join(
    mtbi_ful_df,
    sleep
)

colnames(sleep)

jitter_plot(sleep_df, "sds_p_ss_dims") + labs(y = "Disorders of starting/maintaining sleep")

jitter_plot(sleep_df, "sds_p_ss_sbd") + labs(y = "Sleep breathing disorders")

jitter_plot(sleep_df, "sds_p_ss_da") + labs(y = "Disorders of arousal")

jitter_plot(sleep_df, "sds_p_ss_swtd") + labs(y = "Disorders of sleep-wake transition")

jitter_plot(sleep_df, "sds_p_ss_does") + labs(y = "Excessive Somnolence")

jitter_plot(sleep_df, "sds_p_ss_shy") + labs(y = "Hyperhydrosis")

```

```{r}

mtbi_subs

df |>
    ggplot(
        aes(x = cluster, y = cbcl_aggressive)
    ) +
    geom_jitter(height = 0) +
    geom_violin(alpha = 0.8)

c1 <- df |>
    dplyr::filter(cluster == 1)

c1 |>
    dplyr::select(-uid, -cluster, -race) |>
    cor() |>
    ComplexHeatmap::Heatmap()

df |>
    dplyr::mutate(sex = as.factor(sex)) |>
    dplyr::group_by(cluster, sex) |>
    dplyr::summarize(fmri_cor = cor(cbcl_attention, fmri_cort_subcort_cors)) |>
    ggplot(aes(x = cluster, y = fmri_cor, fill = sex)) +
      geom_bar(stat = "identity", position = position_dodge()) +
      labs(x = "Cluster", y = "fMRI Correlation", fill = "Sex") +
      theme_minimal()

df$"sex" <- as.factor(df$"sex")

df |>
    dplyr::mutate(sex = dplyr::case_when(sex == 1 ~ "M", TRUE ~ "F")) |>
    ggplot(aes(x = fmri_cort_subcort_cors, y = cbcl_attention, colour = sex)) +
    geom_point() +
    geom_smooth(method = "lm") +
    facet_wrap(~cluster + sex, nrow = 2)
    

m_df <- df |>
    dplyr::filter(sex == 1, cluster == 1)
cor.test(m_df$"cbcl_somatic", m_df$"pericortical_wm_ndi")

colnames(m_df)

df |>
    ggplot()
```

### What's different between the clusters, physiolocially? A closer look at neuroimaging

```{r}

df$"parent"


mtbi_ful_df |>
    dplyr::mutate(
        parent_total = rowSums(across(starts_with("parent"))),
        cbcl_total = rowSums(across(starts_with("cbcl")))
    ) |>
    ggplot(
        aes(x = parent_total, y = cbcl_aggressive)
    ) +
    geom_point() +
    geom_smooth(method = "lm")

z2 <- mtbi_ful_df |>
    dplyr::mutate(
        parent_total = rowSums(across(starts_with("parent"))),
        cbcl_total = rowSums(across(starts_with("cbcl")))
    )

summary(lm(cbcl_total ~ parent_total + sex + race + brain_volume + cluster + household_income, z2))
summary(lm(cbcl_attention ~ fmri_cort_subcort_cors * cluster, mtbi_ful_df))
summary(lm(cbcl_attention ~ fmri_cort_subcort_cors, data = subset(mtbi_ful_df, cluster == 1)))
summary(lm(cbcl_attention ~ fmri_cort_subcort_cors, data = subset(mtbi_ful_df, cluster == 2)))
summary(lm(cbcl_attention ~ fmri_cort_subcort_cors, data = subset(mtbi_ful_df, cluster == 3)))
summary(lm(cbcl_attention ~ fmri_cort_subcort_cors * race, data = mtbi_ful_df))

summary(model_cluster1)

summary(model_cluster2)

summary(model_cluster3)

mtbi_ful_df |>
    ggplot(
        aes(
            x = fmri_cort_subcort_cors,
            y = cbcl_attention,
            group = race,
            colour = race
        )
    ) +
    geom_point() +
    geom_smooth(method = "lm") +
    theme_bw() +
    facet_wrap("race")

df |>
    ggplot(
        aes(
            x = fmri_cort_subcort_cors,
            y = cbcl_attention,
            group = race,
            colour = race
        )
    ) +
    geom_point() +
    geom_smooth(method = "lm") +
    theme_bw() +
    facet_wrap("race")

```

```{r}
my_jitter <- function(plot_data, ft, name) {
    ggplot(
        plot_data,
        aes(
            x = cluster,
            y = .data[[ft]],
        )
    ) +
    geom_violin(
        data = plot_data,
        alpha = 0.1,
        aes(colour = cluster)
    ) +
    geom_jitter(
        height = 0,
        width = 0.1,
        alpha = 0.1
    ) +
    ggplot2::stat_summary(
        data = plot_data,
        aes(colour = cluster),
        fun = "mean",
        geom = "crossbar",
        fatten = 4,
        width = 0.6
    ) +
    labs(
        x = "Cluster",
        y = name
    ) +
    theme_classic() +
    theme(legend.position = "none") +
    theme(text = element_text(size = 16))
}
# Generalizable: C1 < C2, C1 > C3, C2 > C3
mtbi_0_volume_plot <- my_jitter(
    mtbi_ful_df,
    "brain_volume",
    "Brain\nVolume"
)
mtbi_0_volume_plot
#ggsave(
#    fig_path("mtbi_0_volume_plot.png", TRUE),
#    mtbi_0_volume_plot,
#    width = 7,
#    height = 5
#)

# Generalizable: C1 < C2, C1 > C3, C2 > C3
mtbi_0_cortsa_plot <- my_jitter( 
    mtbi_ful_df,
    "cortical_sa",
    "Cortical SA"
)
mtbi_0_cortsa_plot
#ggsave(
#    fig_path("mtbi_0_cortsa_plot.png", TRUE),
#    mtbi_0_cortsa_plot,
#    width = 7,
#    height = 5
#)

# Generalizable: C1 < C2
mtbi_0_fmri_subc_c_plot <- my_jitter(
    mtbi_ful_df,
    "fmri_cort_subcort_cors",
    "fMRI Cort-Subcort\nCorr"
)
mtbi_0_fmri_subc_c_plot
#ggsave(
#    fig_path("mtbi_0_fmri_subc_c_plot.png", TRUE),
#    mtbi_0_fmri_subc_c_plot,
#    width = 7,
#    height = 5
#)

# Generalizable: C1 < C3
# Qualitatively: C1 < C2 and C1 < C3
mtbi_0_cortt_plot <-  my_jitter( 
    mtbi_ful_df,
    "cortical_thickness",
    "Cortical\nthickness"
)
mtbi_0_cortt_plot
#ggsave(
#    fig_path("mtbi_0_cortt_plot.png", TRUE),
#    mtbi_0_cortt_plot,
#    width = 7,
#    height = 5
#)

# Outcomes

mtbi_0_aggressive_plot <- my_jitter(
    mtbi_ful_df,
    "cbcl_aggressive",
    "Aggressive"
)
mtbi_0_aggressive_plot
#ggsave(
#    fig_path("mtbi_0_aggressive_plot.png", TRUE),
#    mtbi_0_aggressive_plot,
#    width = 7,
#    height = 5
#)

mtbi_0_anxdep_plot <- my_jitter(
    mtbi_ful_df,
    "cbcl_anxdep",
    "Anxious\nDepressed"
)
mtbi_0_anxdep_plot
#ggsave(
#    fig_path("mtbi_0_anxdep_plot.png", TRUE),
#    mtbi_0_anxdep_plot,
#    width = 7,
#    height = 5
#)

mtbi_0_attention_plot <- my_jitter(
    mtbi_ful_df,
    "cbcl_attention",
    "Attention"
)
mtbi_0_attention_plot
#ggsave(
#    fig_path("mtbi_0_attention_plot.png", TRUE),
#    mtbi_0_attention_plot,
#    width = 7,
#    height = 5
#)

mtbi_0_rulebreak_plot <- my_jitter(
    mtbi_ful_df,
    "cbcl_rulebreak",
    "Rule-Breaking"
)
mtbi_0_rulebreak_plot
#ggsave(
#    fig_path("mtbi_0_rulebreak_plot.png", TRUE),
#    mtbi_0_rulebreak_plot,
#    width = 7,
#    height = 5
#)

mtbi_0_social_plot <- my_jitter(
    mtbi_ful_df,
    "cbcl_social",
    "Social"
)
mtbi_0_social_plot
#ggsave(
#    fig_path("mtbi_0_social_plot.png", TRUE),
#    mtbi_0_social_plot,
#    width = 7,
#    height = 5
#)

mtbi_0_somatic_plot <- my_jitter(
    mtbi_ful_df,
    "cbcl_somatic",
    "Somatic"
)
mtbi_0_somatic_plot
#ggsave(
#    fig_path("mtbi_0_somatic_plot.png", TRUE),
#    mtbi_0_somatic_plot,
#    width = 7,
#    height = 5
#)

mtbi_0_thought_plot <- my_jitter(
    mtbi_ful_df,
    "cbcl_thought",
    "Thought"
)
mtbi_0_thought_plot
#ggsave(
#    fig_path("mtbi_0_thought_plot.png", TRUE),
#    mtbi_0_thought_plot,
#    width = 7,
#    height = 5
#)

mtbi_0_withdep_plot <- my_jitter(
    mtbi_ful_df,
    "cbcl_withdep",
    "Withdrawn\nDepressed"
)
mtbi_0_withdep_plot
#ggsave(
#    fig_path("mtbi_0_withdep_plot.png", TRUE),
#    mtbi_0_withdep_plot,
#    width = 7,
#    height = 5
#)

mtbi_0_sleep_plot <- my_jitter(
    mtbi_ful_df,
    "sds_sleep",
    "Sleep\nDisorders"
)
mtbi_0_sleep_plot
#ggsave(
#    fig_path("mtbi_0_sleep_plot.png", TRUE),
#    mtbi_0_sleep_plot,
#    width = 7,
#    height = 5
#)

# Patchwork assembly of those plots

jitters_neuro_behav <- (mtbi_0_sleep_plot + mtbi_0_withdep_plot + mtbi_0_thought_plot + mtbi_0_somatic_plot + mtbi_0_social_plot + mtbi_0_rulebreak_plot + mtbi_0_attention_plot + mtbi_0_anxdep_plot + mtbi_0_aggressive_plot) |
(mtbi_0_cortt_plot + mtbi_0_fmri_subc_c_plot + mtbi_0_cortsa_plot + mtbi_0_volume_plot)
jitters_neuro_behav

ggsave(
    fig_path(
        "jitters_neuro_behav.png",
        TRUE
    ),
    jitters_neuro_behav,
    width = 15,
    height = 7
)
```

```{r}
my_bar <- function(plot_data, ft, name) {
    plot_data$"cluster" <- as.factor(plot_data$"cluster")
    plot_data <- plot_data |>
        dplyr::rename("keycol" = !!ft) |>
        dplyr::select(
            "cluster",
            "keycol"
        ) |>
        dplyr::group_by(cluster) |>
        dplyr::count(keycol) |>
        dplyr::mutate(percent = n / sum(n) * 100)
    plot_data$"keycol" <- factor(plot_data$"keycol")
    if (all(plot_data$"keycol" %in% c(0, 1))) {
        levels(plot_data$"keycol") <- c("1", "0")
    }
    plot <- plot_data |>
        ggplot2::ggplot(
            ggplot2::aes(
                x = cluster,
                y = percent,
                fill = keycol
            )
        ) +
        ggplot2::geom_bar(
            stat = "identity",
            position = ggplot2::position_stack(),
            show.legend = TRUE
        ) +
        ggplot2::geom_text(
            ggplot2::aes(
                label = n,
                y = percent
            ),
            size = 6,
            position = ggplot2::position_stack(vjust = 0.5)
        ) +
        ggplot2::labs(
            x = "cluster",
            y = "%",
            fill = ft
        ) +
        ggplot2::theme_bw() +
        ggplot2::theme(
            text = ggplot2::element_text(size = 20),
            legend.text = ggplot2::element_text(size = 20),
            legend.title = ggplot2::element_text(size = 20),
            legend.position = "right",
            panel.grid.major.x = ggplot2::element_blank()
        )
    return(plot)
}

mtbi_0_race_plot <- my_bar(
    mtbi_ful_df,
    "race",
    "Race"
)
mtbi_0_race_plot

mtbi_0_sex_plot <- my_bar(
    mtbi_ful_df,
    "sex",
    "Sex"
)
mtbi_0_sex_plot

mtbi_0_income_plot <- my_bar(
    mtbi_ful_df,
    "household_income",
    "Income"
)
mtbi_0_income_plot

mtbi_0_pds_p_plot <- my_bar(
    mtbi_ful_df,
    "pubertal_status_p",
    "pds_p"
)
mtbi_0_pds_p_plot

mtbi_0_parent_thought_plot <- my_jitter(
    mtbi_ful_df,
    "parent_thought",
    "Parent Thought"
)
mtbi_0_parent_thought_plot
```

```{r}
my_scatter <- function(plot_data, ft1, ft2) {
    ggplot(
        plot_data,
        aes(
            x = .data[[ft1]],
            y = .data[[ft2]],
        )
    ) +
    geom_point() +
    geom_smooth(method = "lm") +
    theme_classic() +
    theme(legend.position = "none") +
    theme(text = element_text(size = 16)) +
    stat_cor(
        aes(
            label = paste(
                after_stat(r.label), 
                after_stat(rr.label), 
                after_stat(p.label),
                sep = "~`,`~"
            )
        ), 
        label.x.npc = "left",
        label.y.npc = "top",
        size = 5
    )
}

# No need to keep using cortical SA AND brain volume?
my_scatter(
    mtbi_ful_df,
    "cortical_sa",
    "brain_volume"
)

my_scatter(
    dplyr::filter(mtbi_ful_df, sex == 1),
    "cbcl_attention",
    "fmri_cort_subcort_cors"
)

my_scatter(
    dplyr::filter(mtbi_ful_df, sex == 0),
    "brain_volume",
    "cbcl_somatic"
)

my_scatter(
    mtbi_ful_df,
    "parent_thought",
    "fmri_cort_subcort_cors"
)

# Interesting
my_scatter(
    mtbi_ful_df,
    "weekday_screentime",
    "cbcl_attention"
)

my_scatter(
    mtbi_ful_df,
    "physical_activity",
    "fmri_cort_subcort_cors"
)

my_scatter(
    mtbi_ful_df,
    "parent_antisocial",
    "fmri_cort_subcort_cors"
)

my_scatter(
    mtbi_ful_df,
    "pubertal_status_p",
    "fmri_cort_subcort_cors"
)

ggplot(
    mtbi_ful_df,
    aes(
        x = factor(extracurriculars),
        y = cortical_sa
    )
) +
    geom_point()

my_scatter(
    mtbi_ful_df,
    "cortical_sa",
    "extracurriculars"
)


my_scatter(
    mtbi_ful_df,
    "pericortical_wm_ndi",
    "cbcl_somatic"
)

summary(lm(cbcl_attention ~ race + cluster, data = mtbi_ful_df))


my_scatter(mtbi_ful_df, "brain_volume", "cbcl_somatic")

my_scatter(mtbi_ful_df, "brain_volume", "cbcl_aggressive")

z_mtbi <- mtbi_ful_df |>
    dplyr::mutate(
        cbcl_total = rowSums(across(starts_with("cbcl")))
    )

z_all <- df |>
    dplyr::mutate(
        cbcl_total = rowSums(across(starts_with("cbcl")))
    )

dfs <- list(
    #z_mtbi,
    #dplyr::filter(z_mtbi, cluster == 1),
    #dplyr::filter(z_mtbi, cluster == 2),
    #dplyr::filter(z_mtbi, cluster == 3),
    #dplyr::filter(z_mtbi, cluster != 3),
    #dplyr::filter(z_mtbi, sex == 0),
    #dplyr::filter(z_mtbi, sex == 1),
    #dplyr::filter(z_mtbi, race == "white"),
    dplyr::filter(z_mtbi, race == "other"),
    #dplyr::filter(z_mtbi, race != "white"),
    #z_all,
    #dplyr::filter(z_all, cluster == 1),
    #dplyr::filter(z_all, cluster == 2),
    #dplyr::filter(z_all, cluster == 3),
    #dplyr::filter(z_all, cluster != 3),
    #dplyr::filter(z_all, sex == 0),
    #dplyr::filter(z_all, sex == 1),
    #dplyr::filter(z_all, race == "white"),
    #dplyr::filter(z_all, race == "other"),
    dplyr::filter(z_all, race != "white")
)
neuro_fts <- c(
    #"brain_volume",
    "fmri_cort_subcort_cors"
    #"cortical_sa",
    #"cortical_thickness",
    #"pericortical_wm_ndi",
    #"major_wm_ndi",
    #"fmri_cort_cors"
)
behav_fts <- c(
    #"cbcl_anxdep",
    #"cbcl_withdep",
    #"cbcl_somatic",
    #"cbcl_social",
    #"cbcl_thought",
    #"cbcl_attention",
    #"cbcl_rulebreak",
    #"cbcl_aggressive",
    #"cbcl_total",
    "sds_sleep"
)
cor_data <- data.frame()
for (x in dfs) {
    for (neuro_ft in neuro_fts) {
        for (behav_ft in behav_fts) {
            cor_data <- rbind(
                cor_data,
                data.frame(
                    neuro_ft = neuro_ft,
                    behav_ft = behav_ft,
                    cor = cor(x[[neuro_ft]], x[[behav_ft]])
                )
            )
        }
    }
}
max(abs(cor_data$"cor"))

which(cor_data$"cor" == min(cor_data$"cor"))

cor_data[580, ]

mtbi_ful_df |>
    dplyr::filter(race == "other") |>
    my_scatter("fmri_cort_subcort_cors", "sds_sleep")

neuro_fts <- c(
    "brain_volume",
    "fmri_cort_subcort_cors",
    "cortical_sa",
    "cortical_thickness"
)

behav_fts <- c(
    "cbcl_anxdep",
    "cbcl_withdep",
    "cbcl_somatic",
    "cbcl_social",
    "cbcl_thought",
    "cbcl_attention",
    "cbcl_rulebreak",
    "cbcl_aggressive",
    "sds_sleep"
)

parent_fts <- colnames(mtbi_ful_df)[grepl("parent", colnames(mtbi_ful_df))]

parent_pca <- prcomp(
    dplyr::select(mtbi_ful_df, dplyr::all_of(neuro_fts)),
    center = TRUE,
    scale. = TRUE
)
summary(parent_pca)

neuro_pca <- prcomp(
    dplyr::select(mtbi_ful_df, dplyr::all_of(neuro_fts)),
    center = TRUE,
    scale. = TRUE
)
summary(neuro_pca)

neuro_pca <- prcomp(
    dplyr::select(mtbi_ful_df, dplyr::all_of(neuro_fts)),
    center = TRUE,
    scale. = TRUE
)
summary(neuro_pca)

outcome_pca <- prcomp(
    dplyr::select(mtbi_ful_df, dplyr::all_of(behav_fts)),
    center = TRUE,
    scale. = TRUE
)
summary(outcome_pca)

neuro_pca_df <- as.data.frame(neuro_pca$x)[, 1:3]  # First few PCs for reduced dimensions
behav_pca_df <- as.data.frame(outcome_pca$x)[, 1:4]  # First few PCs for reduced dimensions

colnames(neuro_pca_df) <- c("neuro1", "neuro2", "neuro3")
colnames(behav_pca_df) <- c("behav1", "behav2", "behav3", "behav4")


z_mtbi <- mtbi_ful_df |>
    dplyr::mutate(
        cbcl_total = rowSums(across(starts_with("cbcl")))
    )
z_mtbi <- cbind(z_mtbi, neuro_pca_df)
z_mtbi <- cbind(z_mtbi, behav_pca_df)

neuro_and_pca_fts <- c(
    "brain_volume",
    "fmri_cort_subcort_cors",
    "cortical_sa",
    "cortical_thickness",
    "neuro1",
    "neuro2",
    "neuro3"
)
behav_and_pca_fts <- c(
    "cbcl_anxdep",
    "cbcl_withdep",
    "cbcl_somatic",
    "cbcl_social",
    "cbcl_thought",
    "cbcl_attention",
    "cbcl_rulebreak",
    "cbcl_aggressive",
    "sds_sleep",
    "behav1",
    "behav2",
    "behav3",
    "behav4"
)
dfs <- list(
    "all_obs" = z_mtbi,
    "c1_only" = dplyr::filter(z_mtbi, cluster == 1),
    "c2_only" = dplyr::filter(z_mtbi, cluster == 2),
    "c3_only" = dplyr::filter(z_mtbi, cluster == 3),
    "c1_and_c2" = dplyr::filter(z_mtbi, cluster != 3),
    "only_f" = dplyr::filter(z_mtbi, sex == 0),
    "only_m" = dplyr::filter(z_mtbi, sex == 1),
    "only_white" = dplyr::filter(z_mtbi, race == "white"),
    "only_non_white" = dplyr::filter(z_mtbi, race != "white"),
    "only_other" = dplyr::filter(z_mtbi, race == "other")
)
cor_data <- data.frame()
for (x in names(dfs)) {
    for (neuro_ft in neuro_and_pca_fts) {
        for (behav_ft in behav_and_pca_fts) {
            temp_df <- dfs[[x]]
            test <- cor.test(temp_df[[neuro_ft]], temp_df[[behav_ft]])
            cor_data <- rbind(
                cor_data,
                data.frame(
                    n = nrow(temp_df),
                    subset = x,
                    neuro_ft = neuro_ft,
                    behav_ft = behav_ft,
                    cor = signif(test$"estimate", 3),
                    p = signif(test$"p.value", 3)
                )
            )
        }
    }
}
max(abs(cor_data$"cor"))
cor_data$"abs_cor" <- abs(cor_data$"cor")
cor_data$"p.adj" <- p.adjust(cor_data$"p", method = "fdr")
cor_data |>
    dplyr::arrange(-cor)

?p.adjust

my_scatter(
    dplyr::filter(z_mtbi, cluster == 1),
    "neuro2",
    "cbcl_social"
)

my_scatter(
    dplyr::filter(z_mtbi, cluster == 3),
    "neuro2",
    "cbcl_social"
)
```

```{r}
summary(lm(cbcl_attention ~ fmri_cort_subcort_cors, mtbi_df))

# Nothing was generalizable...
my_jitter( 
    mtbi_ful_df,
    "pericortical_wm_ndi",
    "Pericortical WM NDI"
)

mtbi_ful_df |> colnames()

q <- mtbi_ful_df |>
    dplyr::filter(cluster == 3) |>
    dplyr::select(
        dplyr::starts_with("cbcl"),
        dplyr::starts_with("sds"),
        fmri_cort_subcort_cors
    ) |>
    cor()
q2 <- q[, "fmri_cort_subcort_cors"] |>
    data.frame()
colnames(q2) <- "cor"
q2$"feature" <- rownames(q)
q2[-10, ] |>
    ggplot(
        aes(x = feature, y = cor)
    ) +
    geom_bar(stat = "identity")
    

mtbi_ful_df$"sex"

dplyr::filter()

dplyr::filter(mtbi_ful_df, cluster == 1)$"sex" |> table()

z <- mtbi_ful_df |> 
    dplyr::filter(sex == 1, cluster == 1) |>
    dplyr::select(fmri_cort_subcort_cors, cbcl_aggressive)

z |> cor()

# Interesting: high corr between withdep and fmri in cluster 3
q <- mtbi_ful_df |>
#q <- df |>
    #dplyr::filter(sex == 1, cluster == 1) |>
    dplyr::filter(cluster == 3) |>
    dplyr::select(
        dplyr::starts_with("cbcl"),
        dplyr::starts_with("sds"),
        fmri_cort_subcort_cors
    ) |>
    cor()
q2 <- q[, "fmri_cort_subcort_cors"] |>
    data.frame()
colnames(q2) <- "cor"
q2$"feature" <- rownames(q)
q2[-10, ] |>
    ggplot(
        aes(x = feature, y = cor)
    ) +
    ylim(-0.3, 0.3) +
    geom_bar(stat = "identity") +
    theme_bw()
    
q <- mtbi_ful_df |>
#q <- df |>
    #dplyr::filter(sex == 1, cluster == 1) |>
    dplyr::filter(cluster == 1) |>
    dplyr::select(
        dplyr::starts_with("cbcl"),
        dplyr::starts_with("sds"),
        fmri_cort_subcort_cors
    ) |>
    cor()
q2 <- q[, "fmri_cort_subcort_cors"] |>
    data.frame()
colnames(q2) <- "cor"
q2$"feature" <- rownames(q)
q2[-10, ] |>
    ggplot(
        aes(x = feature, y = cor)
    ) +
    ylim(-0.3, 0.3) +
    geom_bar(stat = "identity") +
    theme_bw()
    
q <- mtbi_ful_df |>
#q <- df |>
    #dplyr::filter(sex == 1, cluster == 1) |>
    dplyr::select(
        dplyr::starts_with("cbcl"),
        dplyr::starts_with("sds"),
        brain_volume
    ) |>
    cor()
q2 <- q[, "brain_volume"] |>
    data.frame()
colnames(q2) <- "cor"
q2$"feature" <- rownames(q)
q2[-10, ] |>
    ggplot(
        aes(x = feature, y = cor)
    ) +
    ylim(-0.3, 0.3) +
    geom_bar(stat = "identity") +
    theme_bw()
```

```{r}

neuro_fts <- c(
    "brain_volume",
    "cortical_thickness",
    "cortical_sa",
    "fmri_cort_subcort_cors"
)



give_cors <- function(data_df) {
    cor_results <- sapply(
        2:ncol(data_df),
        function(i) {
            test <- cor.test(data_df[[1]], data_df[[i]])
            c(correlation = test$estimate, p_value = test$p.value)
        }
    )
    # Convert results to a dataframe
    cor_results_df <- as.data.frame(t(cor_results))
    rownames(cor_results_df) <- colnames(data_df)[2:10]
    return(cor_results_df)
}

give_cors(z1)


```

```{r}


z1 <- mtbi_ful_df |>
    dplyr::select(
        dplyr::all_of(neuro_fts),
        dplyr::starts_with("cbcl"),
        dplyr::starts_with("sds")
    ) |>
    cor()
z1[!grepl("cbcl|sds", rownames(z1)), grepl("cbcl|sds", colnames(z1))] |>
    abs() |>
    ComplexHeatmap::Heatmap(
        col = circlize::colorRamp2(
            c(0, 0.1),
            c(
                "white",
                "black"
            )
        ),
    )


z2 <- mtbi_ful_df |>
    dplyr::filter(cluster == 1) |>
    dplyr::select(
        dplyr::all_of(neuro_fts),
        dplyr::starts_with("cbcl"),
        dplyr::starts_with("sds")
    ) |>
    cor()
z2[!grepl("cbcl|sds", rownames(z2)), grepl("cbcl|sds", colnames(z2))] |>
    abs() |>
    ComplexHeatmap::Heatmap(
        col = circlize::colorRamp2(
            c(0, 0.5),
            c(
                "white",
                "black"
            )
        ),
    )

z3 <- mtbi_ful_df |>
    dplyr::filter(cluster == 1) |>
    dplyr::select(
        dplyr::all_of(neuro_fts),
        dplyr::starts_with("cbcl"),
        dplyr::starts_with("sds")
    ) |>
    cor()
z3 <- z3[!grepl("cbcl|sds", rownames(z3)), grepl("cbcl|sds", colnames(z3))]

z3["fmri_cort_subcort_cors", ] |> min()
z3["fmri_cort_subcort_cors", ] |> max()

z3["brain_volume", ] |> min()
z3["brain_volume", ] |> max()

z3["cortical_thickness", ] |> min()
z3["cortical_thickness", ] |> max()

z3["cortical_thickness", ]

z3["cortical_sa", ] |> min()
z3["cortical_sa", ] |> max()

neuro_fts

mtbi_ful_df |>
    dplyr::filter(cluster == 1) |>
    ggplot(aes(x = fmri_cort_subcort_cors, y = cbcl_attention)) +
    geom_point() +
    geom_smooth(method = "lm") +
    stat_cor(
        aes(label = paste(after_stat(rr.label), after_stat(p.label), sep = "~`,`~")), 
        label.x.npc = "left", label.y.npc = "top", size = 5
    )

mtbi_df |>
    dplyr::filter(sex == 1) |>
    ggplot(aes(x = fmri_cort_subcort_cors, y = cbcl_somatic)) +
    geom_point() +
    geom_smooth(method = "lm") +
stat_cor(aes(label = paste(after_stat(rr.label), after_stat(p.label), sep = "~`,`~")), 
    label.x.npc = "left", label.y.npc = "top", size = 5)

# keep looking...
```

```{r}

# feature ranks
mtbi_gen_fts_in <- read_csv(proc_path("2025_02_13_mtbi_gen_fts_in.csv"))
mtbi_gen_fts_out <- read_csv(proc_path("2025_02_13_mtbi_gen_fts_out.csv"))

mtbi_gen_fts_in$"feature" %in% colnames(oom_raw_pl_data)

setdiff(mtbi_gen_fts_in$"feature", colnames(oom_raw_pl_data))


# A combination of the raw inputs, but adjusted outputs
mtbi_all_adj <- c(dl_corrected, dl_demo, adj_oom_list)
mtbi_only_adj_out <- c(dl_no_demo, dl_demo, adj_oom_list)
mtbi_raw_dl <- c(full_data_list_1, full_oom_list_1)

mtbi_full_top_3c <- readRDS(proc_path("2025_02_13_mtbi_full_top_3c.rds"))

all_raw_pl_data <- auto_plot(mtbi_full_top_3c, mtbi_raw_dl, return_plots = FALSE)
oom_adj_pl_data <- auto_plot(mtbi_full_top_3c, mtbi_only_adj_out, return_plots = FALSE)
all_adj_pl_data <- auto_plot(mtbi_full_top_3c, mtbi_all_adj, return_plots = FALSE)

all_raw_pl_data <- as.data.frame(all_raw_pl_data)
oom_adj_pl_data <- as.data.frame(oom_adj_pl_data) |> dplyr::select(dplyr::all_of(colnames(all_raw_pl_data)))
all_adj_pl_data <- as.data.frame(all_adj_pl_data) |> dplyr::select(dplyr::all_of(colnames(all_raw_pl_data)))

write_csv(all_raw_pl_data, proc_path("all_raw_pl_data.csv", TRUE))
write_csv(oom_adj_pl_data, proc_path("oom_adj_pl_data.csv", TRUE))
write_csv(all_adj_pl_data, proc_path("all_adj_pl_data.csv", TRUE))

all_raw_pl_data <- read_csv(proc_path("2025_03_26_all_raw_pl_data.csv"))
oom_adj_pl_data <- read_csv(proc_path("2025_03_26_oom_adj_pl_data.csv"))
all_adj_pl_data <- read_csv(proc_path("2025_03_26_all_adj_pl_data.csv"))

oom_adj_pl <- auto_plot(mtbi_full_top_3c, mtbi_only_adj_out)
all_adj_pl <- auto_plot(mtbi_full_top_3c, mtbi_all_adj)
all_raw_pl <- auto_plot(mtbi_full_top_3c, mtbi_raw_dl)

# Plot shows that clusters still explain outcome measures beyond 
# demographic variables
adjusted_vs_unadjusted_plots <-
    wrap_plots(all_raw_pl[grepl("cbcl|sds", names(all_raw_pl))], nrow = 1) /
    wrap_plots(oom_adj_pl[grepl("cbcl|sds", names(all_raw_pl))], nrow = 1)

ggsave(
    fig_path("adjusted_vs_unadjusted_plots.png", TRUE),
    adjusted_vs_unadjusted_plots,
    width = 30,
    height = 7
)

# ALSO HERE 2025_04_02

```

- Make the cmats below
- Check what (if anything) significantly correlated with the outcome measures
- check most recent chatgpt convo (particularly #4): https://chatgpt.com/c/67eda298-677c-8005-bb6a-c959ead198a2
- repeat it all in the demo adjusted and demo unadjusted data.
    - may need to consider doing the demo adjustment off of the entire dataset? Talk to Anne about this
- better get some systematic review extractions done!

```{r}

# Are these new adjusted outcomes correlated with anything?
outcome_cmat <- function(df) {
    cmat <- df |>
        dplyr::select(-uid, -mtbi_mechanism) |>
        dummy_cols(
            c("cluster", "race"),
            remove_selected_columns = TRUE
        ) |>
        cor()
    out_idx <- grepl("^cbcl|^sds", rownames(cmat))
    cmat <- cmat[out_idx, !out_idx] |>
        abs()
    return(cmat)
}

outcome_hm <- function(cmat) {
    ComplexHeatmap::Heatmap(
        cmat,
        cluster_rows = FALSE,
        cluster_columns = FALSE,
        col = circlize::colorRamp2(
            c(0, 0.1, 0.2, 0.3, 0.4, 0.5),
            RColorBrewer::brewer.pal(n = 6, name = "BuPu")
        ),
        heatmap_legend_param = list(
            title = "|Cor|"
        )
    )
}

all_raw_cmat <- outcome_cmat(all_raw_pl_data)
oom_adj_cmat <- outcome_cmat(oom_adj_pl_data)
all_adj_cmat <- outcome_cmat(all_adj_pl_data)

outcome_hm(all_raw_cmat)

outcome_hm(all_adj_cmat)

outcome_hm(all_raw_cmat - all_adj_cmat)


# Compute correlations and p-values
outcome_cmat_hmisc <- function(df, thresh = 0.05) {
    cmat <- df |>
        dplyr::select(-uid, -mtbi_mechanism) |>
        dummy_cols(
            c("cluster", "race"),
            remove_selected_columns = TRUE
        ) |>
        as.matrix() |>
        rcorr()
    cmat <- cmat$P
    out_idx <- grepl("^cbcl|^sds", rownames(cmat))
    in_model_colours <- c(
        "black",
        "blue"
    )
    cmat_out <- cmat[out_idx, !out_idx]
        #fdr_matrix()
    #cmat_out <- cmat[out_idx, !out_idx] |>
    #    fdr_matrix()
    cmat_out[cmat_out <= thresh] <- 0  # Set values ≤ 0.05 to 1
    cmat_out[cmat_out > thresh] <- 1   # Set values > 0.05 to 0
    cmat_out[cmat_out == 0] <- 99
    cmat_out[cmat_out == 1] <- 0
    cmat_out[cmat_out == 99] <- 1
    col <- function(x) {
      ifelse(x == 1, in_model_colours[2], in_model_colours[1])
    }
    hm <- cmat_out |>
        ComplexHeatmap::Heatmap(
            cluster_rows = FALSE,
            cluster_columns = FALSE,
            col = col,
            heatmap_legend_param = list(
                at = c(0, 1),
                color_bar = "discrete",
                title = paste0("p < ", thresh),
                labels = c("No", "Yes")
            )
        )
    hm
}
#outcome_cmat(oom_adj_pl_data)
#outcome_cmat_hmisc(all_adj_pl_data, 0.00000000000000000000000000000000000000000000000000000000001)

outcome_cmat_hmisc(all_adj_pl_data, 0.05)

outcome_cmat_hmisc(oom_adj_pl_data, 0.05)

outcome_cmat_hmisc(all_raw_pl_data, 0.05)

result <- rcorr(as.matrix(df))

# Extract correlation matrix
cor_matrix <- result$r

# Extract p-value matrix
p_matrix <- result$P

print(cor_matrix)
print(p_matrix)




all_adj_pl_data |>
    dplyr::select(-uid, -mtbi_mechanism, -race) |>
    cor()

pl |>
    ggplot(aes(x = pubertal_status_p, y = cbcl_aggressive)) +
    geom_point() +
    geom_smooth(method = "lm")

pl$"cbcl_aggressive"

mtbi_only_adj_out_df <- as.data.frame(mtbi_only_adj_out)

mtbi_only_adj_out_cor <- mtbi_only_adj_out_df |>
    dplyr::select(-uid, -mtbi_mechanism, -race) |>
    cor()

out_idx <- grepl("^cbcl|^sds", rownames(mtbi_only_adj_out_cor))

mtbi_only_adj_out_cor[out_idx, !out_idx] |>
    abs() |>
    ComplexHeatmap::Heatmap()


```
