# metaSNF of Baseline mTBI Subjects

This chapter contains:

1. Derivation of baseline mTBI subtypes with metasnf
2. Characterization of those subtypes

## Importing packages and establishing file paths


```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)
library(ggplot2)
library(patchwork)
library(xtable)
library(compute.es)
library(dplyr)
library(fastDummies)
library(tidyr)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subs <- read_csv(sub_path("2024_10_29_mtbi_subs.csv"))
mtbi_train_subs <- read_csv(sub_path("2024_10_29_mtbi_train_subs.csv"))
mtbi_test_subs <- read_csv(sub_path("2024_10_29_mtbi_test_subs.csv"))
uninj_subs <- read_csv(sub_path("2024_10_29_uninj_subs.csv"))
```


## Importing data


```{r}
# CHECKPOINT
all_dls <- list.load(input_path("2024_10_29_all_dls.rds"))
```

## Generating custom distance measures

```{r}
# CHECKPOINT
###############################################################################
# 2. Add standard normalized variations to the distance metrics list (also
# achievable through toggling automatic_standard_normalize parameter in
# `batch_snf`)
###############################################################################
my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

summarize_dml(my_distance_metrics)
```


## Generating the settings matrix


```{r}
set.seed(42)
mtbi_settings_matrix <- generate_settings_matrix(
    all_dls$"mtbi_train_data_lists"$"imp_1",
    nrow = 200,
    distance_metrics_list = my_distance_metrics
)
write_csv(mtbi_settings_matrix, proc_path("mtbi_settings_matrix.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_settings_matrix <- read_csv(proc_path("2024_10_29_mtbi_settings_matrix.csv"))
```


## Running SNF for each of the imputations


```{r}
mtbi_solutions_matrix_s1 <- batch_snf(
    data_list = all_dls$"mtbi_train_data_lists"[[1]],
    settings_matrix = mtbi_settings_matrix,
    distance_metrics_list = my_distance_metrics,
    processes = "max"
)
write_csv(mtbi_solutions_matrix_s1, proc_path("mtbi_solutions_matrix_s1.csv", TRUE))
#
mtbi_solutions_matrix_s2 <- batch_snf(
    data_list = all_dls$"mtbi_train_data_lists"[[2]],
    settings_matrix = mtbi_settings_matrix,
    distance_metrics_list = my_distance_metrics,
    processes = "max"
)
write_csv(mtbi_solutions_matrix_s2, proc_path("mtbi_solutions_matrix_s2.csv", TRUE))
#
mtbi_solutions_matrix_s3 <- batch_snf(
    data_list = all_dls$"mtbi_train_data_lists"[[3]],
    settings_matrix = mtbi_settings_matrix,
    distance_metrics_list = my_distance_metrics,
    processes = "max"
)
write_csv(mtbi_solutions_matrix_s3, proc_path("mtbi_solutions_matrix_s3.csv", TRUE))
#
mtbi_solutions_matrix_s4 <- batch_snf(
    data_list = all_dls$"mtbi_train_data_lists"[[4]],
    settings_matrix = mtbi_settings_matrix,
    distance_metrics_list = my_distance_metrics,
    processes = "max"
)
write_csv(mtbi_solutions_matrix_s4, proc_path("mtbi_solutions_matrix_s4.csv", TRUE))
#
mtbi_solutions_matrix_s5 <- batch_snf(
    data_list = all_dls$"mtbi_train_data_lists"[[5]],
    settings_matrix = mtbi_settings_matrix,
    distance_metrics_list = my_distance_metrics,
    processes = "max"
)
write_csv(mtbi_solutions_matrix_s5, proc_path("mtbi_solutions_matrix_s5.csv", TRUE))
#
mtbi_solutions_matrix_p1 <- batch_snf(
    data_list = all_dls$"mtbi_pooled_data_lists"[[1]],
    settings_matrix = mtbi_settings_matrix,
    distance_metrics_list = my_distance_metrics,
    processes = "max"
)
write_csv(mtbi_solutions_matrix_p1, proc_path("mtbi_solutions_matrix_p1.csv", TRUE))
#
mtbi_solutions_matrix_p2 <- batch_snf(
    data_list = all_dls$"mtbi_pooled_data_lists"[[2]],
    settings_matrix = mtbi_settings_matrix,
    distance_metrics_list = my_distance_metrics,
    processes = "max"
)
write_csv(mtbi_solutions_matrix_p2, proc_path("mtbi_solutions_matrix_p2.csv", TRUE))
#
mtbi_solutions_matrix_p3 <- batch_snf(
    data_list = all_dls$"mtbi_pooled_data_lists"[[3]],
    settings_matrix = mtbi_settings_matrix,
    distance_metrics_list = my_distance_metrics,
    processes = "max"
)
write_csv(mtbi_solutions_matrix_p3, proc_path("mtbi_solutions_matrix_p3.csv", TRUE))
#
mtbi_solutions_matrix_p4 <- batch_snf(
    data_list = all_dls$"mtbi_pooled_data_lists"[[4]],
    settings_matrix = mtbi_settings_matrix,
    distance_metrics_list = my_distance_metrics,
    processes = "max"
)
write_csv(mtbi_solutions_matrix_p4, proc_path("mtbi_solutions_matrix_p4.csv", TRUE))
#
mtbi_solutions_matrix_p5 <- batch_snf(
    data_list = all_dls$"mtbi_pooled_data_lists"[[5]],
    settings_matrix = mtbi_settings_matrix,
    distance_metrics_list = my_distance_metrics,
    processes = "max"
)
write_csv(mtbi_solutions_matrix_p5, proc_path("mtbi_solutions_matrix_p5.csv", TRUE))
```

```{r}
mtbi_solutions_matrix_s1 <- read_csv(proc_path("2024_10_29_mtbi_solutions_matrix_s1.csv"))
mtbi_solutions_matrix_s2 <- read_csv(proc_path("2024_10_29_mtbi_solutions_matrix_s2.csv"))
mtbi_solutions_matrix_s3 <- read_csv(proc_path("2024_10_29_mtbi_solutions_matrix_s3.csv"))
mtbi_solutions_matrix_s4 <- read_csv(proc_path("2024_10_29_mtbi_solutions_matrix_s4.csv"))
mtbi_solutions_matrix_s5 <- read_csv(proc_path("2024_10_29_mtbi_solutions_matrix_s5.csv"))
mtbi_solutions_matrix_p1 <- read_csv(proc_path("2024_10_29_mtbi_solutions_matrix_p1.csv"))
mtbi_solutions_matrix_p2 <- read_csv(proc_path("2024_10_29_mtbi_solutions_matrix_p2.csv"))
mtbi_solutions_matrix_p3 <- read_csv(proc_path("2024_10_29_mtbi_solutions_matrix_p3.csv"))
mtbi_solutions_matrix_p4 <- read_csv(proc_path("2024_10_29_mtbi_solutions_matrix_p4.csv"))
mtbi_solutions_matrix_p5 <- read_csv(proc_path("2024_10_29_mtbi_solutions_matrix_p5.csv"))

mtbi_sm <- do.call(
    "rbind",
    list(
        mtbi_solutions_matrix_s1,
        mtbi_solutions_matrix_s2,
        mtbi_solutions_matrix_s3,
        mtbi_solutions_matrix_s4,
        mtbi_solutions_matrix_s5,
        mtbi_solutions_matrix_p1,
        mtbi_solutions_matrix_p2,
        mtbi_solutions_matrix_p3,
        mtbi_solutions_matrix_p4,
        mtbi_solutions_matrix_p5
    )
)
write_csv(data.frame(mtbi_sm), proc_path("mtbi_sm.csv", TRUE))
#
mtbi_ari <- calc_aris(mtbi_sm, processes = "max")
#
write_csv(data.frame(mtbi_ari), proc_path("mtbi_ari.csv", TRUE))
#
mtbi_ari_order <- get_matrix_order(mtbi_ari)
#
write_csv(data.frame(mtbi_ari_order), proc_path("mtbi_ari_order.csv", TRUE))
```

## Re-importing data

```{r}
# CHECKPOINT
mtbi_sm <- read_csv(proc_path("2024_10_29_mtbi_sm.csv"))
mtbi_ari <- as.matrix(read_csv(proc_path("2024_10_29_mtbi_ari.csv")))
mtbi_ari_order <- unlist(read_csv(proc_path("2024_10_29_mtbi_ari_order.csv")))
names(mtbi_ari_order) <- NULL
```

## Calculating associations between cluster solutions and features

```{r}
imputation_labels <- data.frame(
    "imputation" = c(
        rep("s1", 200),
        rep("s2", 200),
        rep("s3", 200),
        rep("s4", 200),
        rep("s5", 200),
        rep("p1", 200),
        rep("p2", 200),
        rep("p3", 200),
        rep("p4", 200),
        rep("p5", 200)
    ),
    "pooled" = c(
        rep("no", 1000),
        rep("yes", 1000)
    )
)

mtbi_sm_l <- cbind(mtbi_sm, imputation_labels)

mtbi_esm_s1 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "s1", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_1",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_1",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_s2 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "s2", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_2",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_2",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_s3 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "s3", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_3",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_3",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_s4 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "s4", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_4",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_4",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_s5 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "s5", ],
    data_list = all_dls$"mtbi_train_data_lists"$"imp_5",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_5",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_p1 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "p1", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_1",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_1",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_p2 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "p2", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_2",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_2",
    min_pval = 1e-10,
    processes = "max"
)

mtbi_esm_p3 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "p3", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_3",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_3",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_p4 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "p4", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_4",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_4",
    min_pval = 1e-10,
    processes = "max"
)
#
mtbi_esm_p5 <- extend_solutions(
    mtbi_sm_l[mtbi_sm_l$"imputation" == "p5", ],
    data_list = all_dls$"mtbi_pooled_data_lists"$"imp_5",
    target_list = all_dls$"mtbi_pooled_oom_lists"$"imp_5",
    min_pval = 1e-10,
    processes = "max"
)

mtbi_esm <- dplyr::bind_rows(
    mtbi_esm_s1,
    mtbi_esm_s2,
    mtbi_esm_s3,
    mtbi_esm_s4,
    mtbi_esm_s5,
    mtbi_esm_p1,
    mtbi_esm_p2,
    mtbi_esm_p3,
    mtbi_esm_p4,
    mtbi_esm_p5
)

#
mtbi_esm$"impairment_separation" <- -log10(mtbi_esm$"mean_pval")
#
write_csv(mtbi_esm, proc_path("mtbi_esm.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_esm <- read_csv(proc_path("2024_10_29_mtbi_esm.csv"))
```

## Identifying and visualizing meta clusters


```{r}
base_ari_hm <- adjusted_rand_index_heatmap(
    mtbi_ari,
    order = mtbi_ari_order
)

shiny_annotator(base_ari_hm)

mtbi_split_vec <- c(
    170,
    430,
    580,
    644,
    790,
    810,
    963,
    1220,
    1450
)

write_csv(data.frame(mtbi_split_vec), proc_path("mtbi_split_vec.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_split_vec <- read_csv(proc_path("2024_11_04_mtbi_split_vec.csv")) |>
    unlist() |>
    as.numeric()
```

```{r}
divergent_colours <- function(column)  {
    values <- unique(column)
    colours <- RColorBrewer::brewer.pal(n = length(values), name = "Set3")
    names(colours) <- values
    return(colours)
}

full_mtbi_ari_hm <- adjusted_rand_index_heatmap(
    aris = mtbi_ari,
    order = mtbi_ari_order,
    data = mtbi_esm,
    min_colour = "black",
    split_vector = mtbi_split_vec,
    top_hm = list(
        "Impairment Separation" = "impairment_separation"
    ),
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    left_hm = list(
        "Pooled" = "pooled",
        "Imputation" = "imputation"
    ),
    annotation_colours = list(
        "Impairment Separation" = colour_scale(
            mtbi_esm$"impairment_separation",
            min_colour = "gray7",
            max_colour = "limegreen"
        ),
        "Imputation" = divergent_colours(mtbi_esm$"imputation"),
        "Pooled" = c(
            "yes" = "orange",
            "no" = "purple"
        )
    )
)
full_mtbi_ari_hm

save_heatmap(
    heatmap = full_mtbi_ari_hm,
    path = fig_path("full_mtbi_ari_hm.png", TRUE),
    width = 950,
    height = 900,
    res = 100
)

# Another heatmap without the imputation-related columns
lite_mtbi_ari_hm <- adjusted_rand_index_heatmap(
    aris = mtbi_ari,
    order = mtbi_ari_order,
    data = mtbi_esm,
    min_colour = "black",
    split_vector = mtbi_split_vec,
    top_hm = list(
        "Impairment Separation" = "impairment_separation"
    ),
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    annotation_colours = list(
        "Impairment Separation" = colour_scale(
            mtbi_esm$"impairment_separation",
            min_colour = "gray7",
            max_colour = "limegreen"
        )
    )
)
lite_mtbi_ari_hm

save_heatmap(
    heatmap = lite_mtbi_ari_hm,
    path = fig_path("lite_mtbi_ari_hm.png", TRUE),
    width = 900,
    height = 700,
    res = 100
)
```

When picking out representative solutions, I'd like to preferentially go for solutions that derived from solo rather than pooled imputations, as those solutions have values for all features.

```{r}
# Function to try to lean on mTBI-including solutions when possible.
# This function will pick from solo solutions unless over 70% of the meta
# cluster is pooled.
restrict_fn <- function(x, threshold = 0.3) {
    x_solo_ind <- x$"imputation" %in% c("s1", "s2", "s3", "s4", "s5")
    x_pool_ind <- x$"imputation" %in% c("p1", "p2", "p3", "p4", "p5")
    x_solo <- x[x_solo_ind, ]
    x_pool <- x[x_pool_ind, ]
    frac_solo <- nrow(x_solo) / (nrow(x_solo) + nrow(x_pool))
    if (frac_solo < threshold) {
        return(x[x_pool_ind, ])
    } else {
        return(x[x_solo_ind, ])
    }
}

mtbi_rep_solutions <- get_representative_solutions(
    mtbi_ari,
    split_vector = mtbi_split_vec,
    order = mtbi_ari_order,
    filter_fn = restrict_fn,
    mtbi_esm
)

# Based on the heatmap, we'll remove B, E, H, K (unstable meta clusters)
mtbi_rep_solutions <- dplyr::filter(
    mtbi_rep_solutions,
    !label %in% c("C", "F", "J")
)

write_csv(mtbi_rep_solutions, proc_path("mtbi_rep_solutions.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_rep_solutions <- read_csv(proc_path("2024_11_04_mtbi_rep_solutions.csv"))

mtbi_rep_solutions |>
    dplyr::filter(label == "E") |>
    dplyr::select(imputation)
```

```{r}
# E (s3) is the top looking solution
mtbi_rep_solutions$"imputation"
mtbi_rep_solutions$"label"

mtbi_manhattan <- mc_manhattan_plot(
    mtbi_rep_solutions,
    data_list = all_dls$"mtbi_train_data_lists"$"imp_3",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_3",
    domain_colours = c(
        "AS" = "#85929e",
        "D" = "#bb8fce",
        "N" = "#e59866",
        "MH" = "#7fb3d5",
        "P" = "#52be80",
        "S" = "#d98880",
        "B" = "#ff3131"
    )
)
mtbi_manhattan

ggsave(
    plot = mtbi_manhattan,
    filename = fig_path("mtbi_manhattan.png", TRUE),
    width = 18,
    height = 14,
    dpi = 120
)

# The most robust solution, best outcome p-values
mtbi_mc_e_esm <- mtbi_rep_solutions |>
    dplyr::filter(label == "E")

write_csv(mtbi_mc_e_esm, proc_path("mtbi_mc_e_esm.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_mc_e_esm <- read_csv(proc_path("2024_11_04_mtbi_mc_e_esm.csv"))
```

```{r}
# Feature plot generation
plot_list <- auto_plot(
    solutions_matrix_row = mtbi_mc_e_esm,
    data_list = all_dls$"mtbi_train_data_lists"$"imp_3",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_3",
    save = fig_path("mtbi_mc_e", TRUE)
)

# No save version:
plot_list <- auto_plot(
    solutions_matrix_row = mtbi_mc_e_esm,
    data_list = all_dls$"mtbi_train_data_lists"$"imp_3",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_3"
)

all_plots <- wrap_plots(plot_list)

# Good enough as a snapshot
ggsave(
    fig_path("mtbi_mc_e_all_plots.png", TRUE),
    all_plots,
    width = 45,
    height = 30,
    dpi = 50
)
```


## Characterization of meta cluster D representative solution

### NMI


```{r}
nmis <- batch_nmi(
    all_dls$"mtbi_train_data_lists"$"imp_3",
    mtbi_mc_e_esm,
    distance_metrics_list = my_distance_metrics
)

nmi_order <- sort(
    nmis$"row_id_176",
    decreasing = TRUE,
    index.return = TRUE
)

ordered_nmis <- nmis[nmi_order$ix, ]

ordered_nmis$"nmi_rank" <- rank(
    -ordered_nmis$"row_id_176",
    ties.method = "min"
)
```


### p-values


```{r}
pvals <- get_pvals(
    mtbi_mc_e_esm,
    keep_summaries = FALSE
)
pvals <- data.frame(
    "feature" = gsub("_pval", "", names(pvals)),
    "neg_log_pval" = -log10(as.numeric(unlist(pvals)))
)
pvals <- pvals[-1, ]
pvals_order <- sort(
    pvals$"neg_log_pval",
    decreasing = TRUE,
    index.return = TRUE
)
ordered_pvals <- pvals[pvals_order$ix, ]
ordered_pvals <- dplyr::filter(
    ordered_pvals,
    !grepl("^cbcl|^sds", feature)
)

ordered_pvals$"pval_rank" <- rank(
    -ordered_pvals$"neg_log_pval",
    ties.method = "min"
)
```


### Joint rank


```{r}
mtbi_mc_e_nmi_v_pval <- dplyr::full_join(
    ordered_nmis,
    ordered_pvals,
    by = "feature"
)

domain_df <- dl_variable_summary(all_dls$"mtbi_train_data_lists"$"imp_3") |>
    dplyr::select(name, domain) |>
    dplyr::rename("feature" = "name")

mtbi_mc_e_nmi_v_pval <- mtbi_mc_e_nmi_v_pval |>
    dplyr::inner_join(domain_df, by = "feature")

mtbi_mc_e_nmi_v_pval$"joint_rank" <- rank(
    mtbi_mc_e_nmi_v_pval$"nmi_rank" + mtbi_mc_e_nmi_v_pval$"pval_rank",
    ties.method = "min"
)

joint_order <- sort(
    mtbi_mc_e_nmi_v_pval$"joint_rank",
    decreasing = FALSE,
    index.return = TRUE
)

mtbi_mc_e_nmi_v_pval_rank <- mtbi_mc_e_nmi_v_pval[joint_order$ix, ]

mtbi_mc_e_nmi_v_pval_rank <- mtbi_mc_e_nmi_v_pval_rank |>
    dplyr::rename("nmi" = "row_id_176")

mtbi_mc_e_nmi_v_pval_rank <- mtbi_mc_e_nmi_v_pval_rank |>
    dplyr::select(
        feature,
        domain,
        nmi,
        nmi_rank,
        neg_log_pval,
        pval_rank,
        joint_rank
    )

write_csv(
    mtbi_mc_e_nmi_v_pval_rank,
    proc_path("mtbi_mc_e_nmi_v_pval_rank.csv", TRUE)
)

options(width=200)
data.frame(mtbi_mc_e_nmi_v_pval_rank)


# Latex table
xtable(data.frame(mtbi_mc_e_nmi_v_pval_rank))
```
                  feature domain         nmi nmi_rank neg_log_pval pval_rank joint_rank
1                     sex      D 0.266450388        1  10.00000000         1          1
2        household_income      D 0.214062038        2  10.00000000         1          2
3            brain_volume      N 0.208832026        3  10.00000000         1          3
4             cortical_sa      N 0.195323534        4  10.00000000         1          4
5       pubertal_status_p      D 0.126620804        5  10.00000000         1          5
6                    race      D 0.111029667        6  10.00000000         1          6
7        extracurriculars      P 0.089055592        7  10.00000000         1          7
8    activities_last_year      P 0.084071266        8  10.00000000         1          8
10         parent_somatic      P 0.063399374       10  10.00000000         1          9
12         parent_thought      P 0.060204542       12  10.00000000         1         10
15      parent_antisocial      P 0.049054017       15  10.00000000         1         11
11     weekday_screentime      P 0.060229955       11   8.20541359        15         12
14       parent_withdrawn      P 0.054934271       14   8.29206777        14         13
16      parent_aggressive      P 0.042967817       16   8.78749168        12         13
13    private_instruction      P 0.057833287       13   5.66299037        20         15
18         parent_depress      P 0.042333377       18   7.82735788        16         16
22          parent_anxdep      P 0.036900610       22   8.47611082        13         17
19       parent_anxdisord      P 0.041512366       19   7.69198332        17         18
9      weekend_screentime      P 0.067482408        9   3.08121259        29         19
17 fmri_cort_subcort_cors      N 0.042338248       17   4.80224201        21         19
20        parent_avoidant      P 0.041445998       20   6.91225993        18         19
21     parent_hyperactive      P 0.039952441       21   6.79437106        19         22
23  same_sex_close_friend      P 0.032744663       23   3.69042975        23         23
26         family_fight_p      P 0.029311048       26   3.65345056        24         24
24          parent_perstr      P 0.032334666       24   3.12387333        28         25
27         fmri_cort_cors      N 0.027737173       27   3.35886427        27         26
28         family_outdo_p      P 0.027715638       28   3.38952404        26         26
32       parent_attention      P 0.025855623       32   4.58809828        22         26
33       parent_intrusive      P 0.024595692       33   3.57556708        25         29
25      physical_activity      P 0.031941455       25   2.36349599        34         30
30       headache_history     MH 0.026443636       30   2.21442846        37         31
34           helps_hurt_p      P 0.022131531       34   2.45500954        33         31
36               mtbi_loc     AS 0.021362651       36   2.73112580        31         31
37     cortical_thickness      N 0.020776206       37   2.94218855        30         31
29      school_activities      P 0.027507930       29   1.84669951        42         35
41              helpful_y      P 0.018687180       41   2.46508291        32         36
35      family_peaceful_p      P 0.022128724       35   2.12534556        39         37
39          mtbi_mem_daze     AS 0.019892887       39   2.21775376        36         38
40          considerate_y      P 0.019296280       40   2.34253195        35         38
31         mtbi_mechanism     AS 0.026159051       31   1.00569279        52         40
43           helps_hurt_y      P 0.017319048       43   2.09970078        40         40
45     family_criticize_p      P 0.016379109       45   2.18258927        38         40
42           major_wm_ndi      N 0.017634538       42   1.68291444        44         43
46        family_temper_p      P 0.014915158       46   1.98395716        41         44
47         family_outdo_y      P 0.014032545       47   1.76792929        43         45
48     family_criticize_y      P 0.013265709       48   1.62553381        45         46
49                    age      D 0.012847040       49   1.56599180        46         47
38    pericortical_wm_ndi      N 0.020170141       38   0.45520665        60         48
51        same_sex_friend      P 0.011309740       51   1.44876735        47         48
53         family_angry_p      P 0.009687300       53   1.29165475        48         50
44               mtbi_age      D 0.016918706       44   0.52174893        58         51
54              helpful_p      P 0.009475231       54   1.14117225        50         52
52         previous_mtbis     MH 0.009939187       52   1.00059775        53         53
56         family_angry_y      P 0.009178946       56   1.18416461        49         53
55         family_throw_p      P 0.009417238       55   1.07085434        51         55
50      pubertal_status_y      D 0.012826525       50   0.50607417        59         56
57           family_hit_p      P 0.007505127       57   0.79393949        54         57
58          family_yell_y      P 0.006111359       58   0.74064960        55         58
59      family_peaceful_y      P 0.005606331       59   0.52515385        56         59
60         family_throw_y      P 0.005434001       60   0.52309282        57         60
61         opp_sex_friend      P 0.004067152       61   0.44119902        61         61
63         family_fight_y      P 0.003431208       63   0.39960433        62         62
62   opp_sex_close_friend      P 0.003677979       62   0.23120558        64         63
64          considerate_p      P 0.002723307       64   0.33773181        63         64
65        family_temper_y      P 0.001554551       65   0.19870410        65         65
66          family_yell_p      P 0.001140392       66   0.15177144        66         66
67           family_hit_y      P 0.000406684       67   0.04542819        67         67

```{r}
# CHECKPOINT
mtbi_mc_e_nmi_v_pval_rank <- read_csv(
    proc_path("2024_11_04_mtbi_mc_e_nmi_v_pval_rank.csv")
)

sorted_features <- mtbi_mc_e_nmi_v_pval_rank$"feature"
```


### Correlation of NMI and p-value


```{r}
nmi_v_p_rho <- cor(
    mtbi_mc_e_nmi_v_pval_rank$"nmi_rank",
    mtbi_mc_e_nmi_v_pval_rank$"pval_rank",
    method = "spearman"
)

nmi_v_pval_plot <- mtbi_mc_e_nmi_v_pval_rank |>
    ggplot(
        aes(x = nmi_rank, y = pval_rank, label = feature, colour = domain)
    ) +
    geom_point(size = 2) + 
    scale_colour_manual(
        values = c(
            "AS" = "#85929e",
            "D" = "#bb8fce",
            "N" = "#e59866",
            "MH" = "#7fb3d5",
            "P" = "#52be80"
        )
    ) +
    theme_bw() +
    labs(x = "Rank by NMI", y = "Rank by Association p-value") +
    ggrepel::geom_text_repel(
        #vjust = 3,
        #hjust = 1,
        force = 1,
        max.overlaps = 35,
        size = 4
    ) +
    annotate(
        "text",
        x = 4,
        y = 50,
        size = 5,
        label = paste("Spearman's ρ =", round(nmi_v_p_rho, 2)),
        hjust = 0
    ) + 
    theme(text = element_text(size = 16))
nmi_v_pval_plot

ggsave(
    fig_path("nmi_v_pval_plot.png", TRUE),
    nmi_v_pval_plot,
    width = 12,
    height = 12
)
```

### Visualizing top features

Ranked plots

```{r}
names(plot_list)

input_plot_list <- plot_list[sorted_features]
input_plots <- wrap_plots(input_plot_list)

input_plot_list2 <- plot_list[c(sorted_features, outcomes)]
input_plots2 <- wrap_plots(input_plot_list2)

ggsave(
    fig_path("mtbi_mc_e_input_plots.png", TRUE),
    input_plots,
    width = 45,
    height = 30,
    dpi = 50
)

saveRDS(
    input_plots,
    file = fig_path("mtbi_mc_e_input_plots.rds", TRUE)
)

mtbi_mc_e_input_plots <- readRDS(
    fig_path("2024_11_07_mtbi_mc_e_input_plots.rds")
)

summary <- summarize_dl(c(full_data_list_1, full_oom_list_1), scope = "feature")
outcomes <- summary$"name"[!summary$"name" %in% sorted_features]

ranked_all_plot_list <- plot_list[c(sorted_features, outcomes)]
ranked_all_plots <- wrap_plots(ranked_all_plot_list)

ggsave(
    fig_path("mtbi_mc_e_ranked_all_plots.png", TRUE),
    ranked_all_plots,
    width = 45,
    height = 30,
    dpi = 50
)

saveRDS(
    ranked_all_plots,
    file = fig_path("mtbi_mc_e_ranked_all_plots.rds", TRUE)
)

mtbi_mc_e_ranked_all_plots <- readRDS(
    fig_path("2024_11_07_mtbi_mc_e_ranked_all_plots.rds")
)
```

```{r}
################################################################################
## Building the top 12 plot list
################################################################################
mc_e_top_pl <- ranked_plot_list[1:12]

names(mc_e_top_pl) <- sorted_features[1:12]
names(mc_e_top_pl)

mc_e_top_pl$"sex" <- mc_e_top_pl$"sex" +
    labs(fill = "Sex") +
    scale_fill_discrete(labels = c("F", "M"))

mc_e_top_pl$"household_income" <- mc_e_top_pl$"household_income" +
    labs(y = "Household Income")

mc_e_top_pl$"brain_volume" <- mc_e_top_pl$"brain_volume" +
    labs(y = expression(paste("Brain Volume ", (mm^3))))

mc_e_top_pl$"cortical_sa" <- mc_e_top_pl$"cortical_sa" +
    labs(y = expression(paste("Cortical Area ", (mm^2))))

mc_e_top_pl$"pubertal_status_p" <- mc_e_top_pl$"pubertal_status_p" +
    labs(y = "Pubertal Status - P")

mc_e_top_pl$"race" <- mc_e_top_pl$"race" +
    labs(fill = "Race") +
    scale_fill_discrete(labels = c("Black", "Hispanic", "Other", "White"))

mc_e_top_pl$"extracurriculars" <- mc_e_top_pl$"extracurriculars" +
    labs(y = "Lifetime Extracurriculars")

mc_e_top_pl$"activities_last_year" <- mc_e_top_pl$"activities_last_year" +
    labs(y = "Total Activities this Year")

mc_e_top_pl$"parent_somatic" <- mc_e_top_pl$"parent_somatic" +
    labs(y = "Parent Somatic Problems")

mc_e_top_pl$"parent_thought" <- mc_e_top_pl$"parent_thought" +
    labs(y = "Parent Thought Problems")

mc_e_top_pl$"parent_antisocial" <- mc_e_top_pl$"parent_antisocial" +
    labs(y = "Parent Antisocial Problems")

mc_e_top_pl$"weekday_screentime" <- mc_e_top_pl$"weekday_screentime" +
    labs(y = "Weekday Screentime")

mc_e_top_p <- wrap_plots(
    mc_e_top_pl,
) & labs(x = "Cluster") & theme(plot.margin = unit(c(0.5, 1.5, 0.5, 2), "cm"))

ggsave(
    fig_path("mtbi_mc_e_input_plots_12.png", TRUE),
    mc_e_top_p,
    width = 25,
    height = 15,
    dpi = 150
)
```

```{r}
################################################################################
## Outcomes
################################################################################
mtbi_mc_e_esm_plot_df <- auto_plot(
    solutions_matrix_row = mtbi_mc_e_esm,
    data_list = all_dls$"mtbi_train_data_lists"$"imp_3",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_3",
    return_plots = FALSE
)

write_csv(mtbi_mc_e_esm_plot_df, proc_path("mtbi_mc_e_esm_plot_df.csv", TRUE))
```

```{r}
mtbi_mc_e_esm_plot_df <- read_csv(proc_path("2024_11_07_mtbi_mc_e_esm_plot_df.csv"))
```

```{r}
outcome_plot_list <- auto_plot(
    solutions_matrix_row = mtbi_mc_e_esm,
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_3"
)
names(outcome_plot_list)

clean_names <- c(
    "CBCL\nAnxious-Depressed",
    "CBCL\nWithdrawn-Depressed",
    "CBCL\nSomatic Problems",
    "CBCL\nSocial Problems",
    "CBCL\nThought Problems",
    "CBCL\nAttention Problems",
    "CBCL\nRule-breaking Problems",
    "CBCL\nAggression Problems",
    "SDS Total\nSleeping Problems"
)

for (i in seq_along(outcome_plot_list)) {
    outcome_plot_list[[i]] <- outcome_plot_list[[i]] +
        labs(y = clean_names[[i]], x = "Cluster")
}

outcome_plot_wrap <- wrap_plots(outcome_plot_list) &
    theme(plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), "cm"))

ggsave(
    fig_path("mtbi_mc_e_outcome_plots.png", TRUE),
    outcome_plot_wrap,
    width = 14,
    height = 14,
    dpi = 150
)
```

### Detailed cluster topologies

Can come back to this later.

```{r}
tstat <- function(d, n1, n2) {
    t <- d * sqrt((n1 * n2) / (n1 + n2))
    return(t)
}
pooled_sd <- function(n1, s1, n2, s2) {
    numerator <- ((n1 - 1) * (s1^2)) + ((n2 - 1) * (s2^2))
    denominator <- n1 + n2 - 2
    s <- sqrt(numerator / denominator)
    return(s)
}
cohens_d <- function(mean1, mean2, pooled_sd) {
    d <- (mean1 - mean2) / pooled_sd
    return(d)
}

calc_des <- function(x1, x2) {
    n1 <- length(x1)
    n2 <- length(x2)
    s1 <- sd(x1)
    s2 <- sd(x2)
    s <- pooled_sd(n1, s1, n2, s2)
    mean1 <- mean(x1)
    mean2 <- mean(x2)
    d <- cohens_d(mean1, mean2, s)
    d_full <- compute.es::des(
        d,
        n1,
        n2,
        verbose = FALSE
    )
    return(
        list(
            "es" = d_full$"d",
            "l" = d_full$"l.d",
            "u" = d_full$"u.d"
        )
    )
}

calc_propes <- function(x1, x2) {
    d_full <- compute.es::propes(
        mean(x1),
        mean(x2),
        length(x1),
        length(x2),
        verbose = FALSE
    )
    return(
        list(
            "es" = d_full$"OR",
            "l" = d_full$"l.or",
            "u" = d_full$"u.or"
        )
    )
}

dummy_non_numeric <- function(df) {
    to_dummy <- colnames(df)[!sapply(df, is.numeric)]
    dummied_df <- dummy_cols(
        df,
        select_columns = to_dummy,
        remove_selected_columns = TRUE
    )
    return(dummied_df)
}

is_binary <- function(x) {
    return(isTRUE(all.equal(sort(unique(x)), c(0, 1))))
}

topologizer <- function(df) {
    df <- data.frame(df)
    df <- numcol_to_numeric(df)
    df <- dummy_non_numeric(dplyr::select(df, -"subjectkey"))
    summary_df <- data.frame(
        "feature" = as.character(),
        "type" = as.character(),
        "summary" = as.character(),
        "c1_mean" = as.numeric(),
        "c2_mean" = as.numeric(),
        "c3_mean" = as.numeric(),
        "c1_c2_es" = as.numeric(),
        "c1_c2_l" = as.numeric(),
        "c1_c2_u" = as.numeric(),
        "c1_c3_es" = as.numeric(),
        "c1_c3_l" = as.numeric(),
        "c1_c3_u" = as.numeric(),
        "c2_c3_es" = as.numeric(),
        "c2_c3_l" = as.numeric(),
        "c2_c3_u" = as.numeric()
    )
    c1 <- df[df$"cluster" == 1, ]
    c2 <- df[df$"cluster" == 2, ]
    c3 <- df[df$"cluster" == 3, ]
    features <- df |>
        dplyr::select(-"cluster") |>
        colnames()
    ###########################################################################
    # Check if features are binary (unique values are 0 and 1) or not
    ###########################################################################
    for (feature in features) {
        f1 <- c1[, feature]
        f2 <- c2[, feature]
        f3 <- c3[, feature]
        means <- c("1" = mean(f1), "2" = mean(f2), "3" = mean(f3))
        full_summary <- paste(
            names(sort(means, decreasing = TRUE)),
            collapse = " > "
        )
        if (is_binary(df[, feature])) {
            sum_1_v_2 <- calc_propes(f1, f2)
            sum_1_v_3 <- calc_propes(f1, f3)
            sum_2_v_3 <- calc_propes(f2, f3)
            type <- "or"
        } else {
            sum_1_v_2 <- calc_des(f1, f2)
            sum_1_v_3 <- calc_des(f1, f3)
            sum_2_v_3 <- calc_des(f2, f3)
            type <- "d"
        }
        summary_df <- rbind(
            summary_df,
            data.frame(
                "feature" = feature,
                "summary" = full_summary,
                "c1" = signif(mean(f1), 3),
                "c2" = signif(mean(f2), 3),
                "c3" = signif(mean(f3), 3),
                "es" = type,
                "c12_es" = sum_1_v_2$"es",
                "c12_l" = sum_1_v_2$"l",
                "c12_u" = sum_1_v_2$"u",
                "c13_es" = sum_1_v_3$"es",
                "c13_l" = sum_1_v_3$"l",
                "c13_u" = sum_1_v_3$"u",
                "c23_es" = sum_2_v_3$"es",
                "c23_l" = sum_2_v_3$"l",
                "c23_u" = sum_2_v_3$"u"
            )
        )
    }
    return(summary_df)
}
```

# Validation

```{r}
# CHECKPOINT
# The data list that generated the top solution
train_data_list_s3 <- all_dls$"mtbi_train_data_lists"$"imp_3"
train_oom_list_s3 <- all_dls$"mtbi_train_oom_lists"$"imp_3"

# The first test data set, for example
test_data_list_s1 <- all_dls$"mtbi_test_data_lists"$"imp_1"
test_data_list_s2 <- all_dls$"mtbi_test_data_lists"$"imp_2"
test_data_list_s3 <- all_dls$"mtbi_test_data_lists"$"imp_3"
test_data_list_s4 <- all_dls$"mtbi_test_data_lists"$"imp_4"
test_data_list_s5 <- all_dls$"mtbi_test_data_lists"$"imp_5"

test_oom_list_s1 <- all_dls$"mtbi_test_oom_lists"$"imp_1"
test_oom_list_s2 <- all_dls$"mtbi_test_oom_lists"$"imp_2"
test_oom_list_s3 <- all_dls$"mtbi_test_oom_lists"$"imp_3"
test_oom_list_s4 <- all_dls$"mtbi_test_oom_lists"$"imp_4"
test_oom_list_s5 <- all_dls$"mtbi_test_oom_lists"$"imp_5"
```

```{r}
full_data_list_1 <- merge_data_lists(train_data_list_s3, test_data_list_s1)
full_data_list_2 <- merge_data_lists(train_data_list_s3, test_data_list_s2)
full_data_list_3 <- merge_data_lists(train_data_list_s3, test_data_list_s3)
full_data_list_4 <- merge_data_lists(train_data_list_s3, test_data_list_s4)
full_data_list_5 <- merge_data_lists(train_data_list_s3, test_data_list_s5)

full_oom_list_1 <- merge_data_lists(train_oom_list_s3, test_oom_list_s1)
full_oom_list_2 <- merge_data_lists(train_oom_list_s3, test_oom_list_s2)
full_oom_list_3 <- merge_data_lists(train_oom_list_s3, test_oom_list_s3)
full_oom_list_4 <- merge_data_lists(train_oom_list_s3, test_oom_list_s4)
full_oom_list_5 <- merge_data_lists(train_oom_list_s3, test_oom_list_s5)

list.save(full_data_list_1, input_path("mtbi_full_data_list_1.rds", TRUE))
list.save(full_data_list_2, input_path("mtbi_full_data_list_2.rds", TRUE))
list.save(full_data_list_3, input_path("mtbi_full_data_list_3.rds", TRUE))
list.save(full_data_list_4, input_path("mtbi_full_data_list_4.rds", TRUE))
list.save(full_data_list_5, input_path("mtbi_full_data_list_5.rds", TRUE))

list.save(full_oom_list_1, input_path("mtbi_full_oom_list_1.rds", TRUE))
list.save(full_oom_list_2, input_path("mtbi_full_oom_list_2.rds", TRUE))
list.save(full_oom_list_3, input_path("mtbi_full_oom_list_3.rds", TRUE))
list.save(full_oom_list_4, input_path("mtbi_full_oom_list_4.rds", TRUE))
list.save(full_oom_list_5, input_path("mtbi_full_oom_list_5.rds", TRUE))
```

```{r}
# CHECKPOINT
full_data_list_1 <- list.load(input_path("2024_11_04_mtbi_full_data_list_1.rds"))
full_data_list_2 <- list.load(input_path("2024_11_04_mtbi_full_data_list_2.rds"))
full_data_list_3 <- list.load(input_path("2024_11_04_mtbi_full_data_list_3.rds"))
full_data_list_4 <- list.load(input_path("2024_11_04_mtbi_full_data_list_4.rds"))
full_data_list_5 <- list.load(input_path("2024_11_04_mtbi_full_data_list_5.rds"))

full_oom_list_1 <- list.load(input_path("2024_11_04_mtbi_full_oom_list_1.rds"))
full_oom_list_2 <- list.load(input_path("2024_11_04_mtbi_full_oom_list_2.rds"))
full_oom_list_3 <- list.load(input_path("2024_11_04_mtbi_full_oom_list_3.rds"))
full_oom_list_4 <- list.load(input_path("2024_11_04_mtbi_full_oom_list_4.rds"))
full_oom_list_5 <- list.load(input_path("2024_11_04_mtbi_full_oom_list_5.rds"))
```

```{r}
my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

mtbi_settings_matrix <- read_csv(proc_path("2024_10_29_mtbi_settings_matrix.csv"))

mtbi_full_sm <- batch_snf(
    data_list = full_data_list_1,
    settings_matrix = mtbi_settings_matrix,
    distance_metrics_list = my_distance_metrics,
    processes = "max"
)
write_csv(mtbi_full_sm, proc_path("mtbi_full_sm.csv", TRUE))

mtbi_full_sm <- read_csv(proc_path("2024_11_04_mtbi_full_sm.csv"))

mtbi_full_esm <- extend_solutions(
    mtbi_full_sm,
    data_list = full_data_list_1,
    target_list = full_oom_list_1,
    min_pval = 1e-10,
    processes = "max"
)
mtbi_full_esm$"impairment_separation" <- -log10(mtbi_full_esm$"mean_pval")
write_csv(mtbi_full_esm, proc_path("mtbi_full_esm.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_full_esm <- read_csv(proc_path("2024_11_04_mtbi_full_esm.csv"))
```

```{r}
# In anticipation of the upcoming cluster swaps
cluster_label_swap <- function(solutions_matrix, c_a, c_b) {
    swapped_sm <- dplyr::mutate(
        solutions_matrix,
        across(
            dplyr::starts_with("subject"),
            ~ ifelse(
                . == c_a,
                c_b,
                ifelse(
                    . == c_b,
                    c_a,
                    .
                )
            )
        )
    )
    return(swapped_sm)
}
```

What does the full 3-cluster solution look like?

```{r}
# The full solutions with 3 clusters that have big outcome separation
mtbi_full_3c <- mtbi_full_esm |>
    dplyr::filter(
        nclust == 3,
        impairment_separation > 4
    )

mtbi_full_3c_manhattan <- mc_manhattan_plot(
    mtbi_full_3c,
    data_list = full_data_list_1,
    target_list = full_oom_list_1,
    domain_colours = c(
        "AS" = "#85929e",
        "D" = "#bb8fce",
        "N" = "#e59866",
        "MH" = "#7fb3d5",
        "P" = "#52be80",
        "S" = "#d98880",
        "B" = "#ff3131"
    )
)

mtbi_full_3c_manhattan

ggsave(
    plot = mtbi_full_3c_manhattan,
    filename = fig_path("mtbi_full_3c_manhattan.png", TRUE),
    width = 18,
    height = 14,
    dpi = 120
)

mtbi_full_3c

summary <- summarize_dl(c(full_data_list_1, full_oom_list_1), scope = "feature")
outcome_features <- summary$"name"[!summary$"name" %in% sorted_features]
summary$"name"

for (i in seq_len(nrow(mtbi_full_3c))) {
    print(i)
    current_row <- mtbi_full_3c[i, ]
    if (i %in% c(1, 2, 5)) {
        current_row <- cluster_label_swap(current_row, 1, 3)
        current_row <- cluster_label_swap(current_row, 1, 2)
    }
    if (i %in% c(3, 4, 6, 7, 8)) {
        current_row <- cluster_label_swap(current_row, 1, 3)
    }
    plot_list <- auto_plot(
        current_row,
        data_list = full_data_list_1,
        target_list = full_oom_list_1
    )
    names(plot_list) <- summary$"name"
    plot_list <- plot_list[c(sorted_features, outcome_features)]
    full_3c_plot <- wrap_plots(plot_list)
    ggsave(
        fig_path(paste0("mtbi_full_3c_all_plots_", i, ".png"), TRUE),
        full_3c_plot,
        width = 45,
        height = 30,
        dpi = 50
    )
}

# The second one is very similar to the derivation set version
mtbi_full_top_3c <- mtbi_full_3c[5, ]
mtbi_full_top_3c <- cluster_label_swap(mtbi_full_top_3c, 1, 3)
mtbi_full_top_3c <- cluster_label_swap(mtbi_full_top_3c, 1, 2)
mtbi_full_top_3c$"label" <- "Full Top 3C Solution"

write_csv(mtbi_full_top_3c, proc_path("mtbi_full_top_3c.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_full_top_3c <- read_csv(proc_path("2024_11_07_mtbi_full_top_3c.csv"))
```

```{r}
mtbi_der_plot_list <- auto_plot(
    solutions_matrix_row = mtbi_mc_e_esm,
    data_list = all_dls$"mtbi_train_data_lists"$"imp_3",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_3"
)

mtbi_ful_plot_list <- auto_plot(
    mtbi_full_top_3c,
    data_list = full_data_list_1,
    target_list = full_oom_list_1
)

val_cluster_df <- mtbi_full_top_3c |>
    get_cluster_df() |>
    dplyr::filter(
        subjectkey %in% paste0("subject_", mtbi_test_subs$"subjectkey")
    )

mtbi_val_plot_list <- auto_plot(
    cluster_df = val_cluster_df,
    data_list = test_data_list_s1,
    target_list = test_oom_list_s1
)

#mtbi_val_plot_list$"mtbi_mechanism"[[1]]$"keycol" <- factor(
#    mtbi_val_plot_list$"mtbi_mechanism"[[1]]$"keycol",
#    levels = c("fall_hit", "hosp_er", "multi", "other_loc", "vehicle", "violent")
#)
#
#bar_colors <- scales::hue_pal()(6)
#names(bar_colors) <- c("fall_hit", "hosp_er", "multi", "other_loc", "vehicle", "violent")
#
#mtbi_val_plot_list$"mtbi_mechanism" <- mtbi_val_plot_list$"mtbi_mechanism" +
#    scale_fill_manual(values = bar_colors, drop = FALSE)

```

How are all the test features distributed?
How are all the features distributed?

I'd like to have a table along the lines of,

| DERIVATION | IN DERIVATION + VALIDATION | IN VALIDATION |
C1 max F | True | Almost  true|

Something like that, which will require a side-by-side comparison of these features through visual inspection and through the topologizer function in the supplementary section for those who wish to look at the crunched numbers.

Up to 3 should be sufficient for determining which attributes should play a key role in validating the subsequent investigations.

```{r}
outcome_idx <- !names(mtbi_full_plot_list) %in% sorted_features
outcome_features <- names(mtbi_full_plot_list)[outcome_idx]

# Full input feature plots
pli_sort_d <- mtbi_der_plot_list[sorted_features]
pli_sort_v <- mtbi_val_plot_list[sorted_features]
pli_sort_f <- mtbi_ful_plot_list[sorted_features]
plo_d <- mtbi_der_plot_list[outcome_features]
plo_v <- mtbi_val_plot_list[outcome_features]
plo_f <- mtbi_ful_plot_list[outcome_features]

# Let's manually assemble these puppies!
input_plots <- list(pli_sort_d, pli_sort_v, pli_sort_f)
outcome_plots <- list(plo_d, plo_v, plo_f)

list.save(input_plots, proc_path("input_tri_plots.rds", TRUE))
list.save(outcome_plots, proc_path("outcome_tri_plots.rds", TRUE))
```

```{r}
# CHECKPOINT
input_plots <- list.load(proc_path("2024_11_07_input_tri_plots.rds"))
outcome_plots <- list.load(proc_path("2024_11_07_outcome_tri_plots.rds"))
```

```{r}
# image export helper function
quick_save <- function(plot, path, w = 12, h = 4) {
    path <- paste0("mtbi_dvf_", path, ".png")
    ggsave(fig_path(path, TRUE), plot, width = w, height = h)
}

# tri-plot helper function
tri_plot <- function(pl,
                     feature,
                     ft_name,
                     scale_fill_labels = NULL,
                     ylims = NULL) {
    ###########################################################################
    p1 <- pl[[1]][[feature]] +
        theme(
            legend.position = "none",
            axis.title.y = element_text(size = 16)
        )
    ###########################################################################
    p2 <- pl[[2]][[feature]] +
        theme(
            legend.position = "none",
            axis.title.y = element_blank()
        ) 
    ###########################################################################
    p3 <- pl[[3]][[feature]] +
        theme(
            axis.title.y = element_blank()
        )
    ###########################################################################
    if (class(pl[[3]][[feature]]$layers[[1]]$geom)[[1]] == "GeomBar") {
        p3 <- p3 + labs(fill = ft_name)
    } else {
        p1 <- p1 + labs(y = ft_name)
    }
    if (!is.null(scale_fill_labels)) {
        p3 <- p3 + scale_fill_discrete(labels = scale_fill_labels)
    }
    if (!is.null(ylims)) {
        p1 <- p1 + ylim(ylims[[1]], ylims[[2]])
        p2 <- p2 + ylim(ylims[[1]], ylims[[2]])
        p3 <- p3 + ylim(ylims[[1]], ylims[[2]])
    }
    ###########################################################################
    patch_plot <- list(p1, p2, p3)
    patch_plot <- lapply(
        patch_plot,
        function(x) {
            x <- x + labs(x = "Cluster") + theme(text = element_text(size = 16))
        }
    )
    names(patch_plot) <- c("derivation", "validation", "full")
    return(wrap_plots(patch_plot))
}

```

```{r}
# Input tri-plots

# 1. Sex
sex_plot <- tri_plot(input_plots, "sex", "Sex", c("F", "M"))
sex_plot
quick_save(sex_plot, "sex")

# 2. Income
household_income_plot <- tri_plot(input_plots, "household_income", "Household Income")
household_income_plot
quick_save(household_income_plot, "household_income")

# 3. Brain volumes
brain_volume_plot <- tri_plot(input_plots, "brain_volume", expression("Brain Volume "(mm^3)), ylims = c(900000, 1650000))
brain_volume_plot
quick_save(brain_volume_plot, "brain_volume")

# 4. cort sa
cort_sa_plot <- tri_plot(input_plots, "cortical_sa", expression("Cortical Surface Area "(mm^2)), ylims = c(140000, 260000))
cort_sa_plot
quick_save(cort_sa_plot, "cort_sa")

# 5. Pubertal Status - Parent Report
pubertal_status_p_plot <- tri_plot(input_plots, "pubertal_status_p", "Pubertal Status\n(Parent Report)")
pubertal_status_p_plot
quick_save(pubertal_status_p_plot, "pubertal_status_p")

# 6. Race
race_plot <- tri_plot(input_plots, "race", "Race", scale_fill_labels = c("Black", "Hispanic", "Other", "White"))
race_plot
quick_save(race_plot, "race")

# 7. Extracurriculars
extracurriculars_plot <- tri_plot(input_plots, "extracurriculars", "Extracurriculars", ylims= c(-0.5, 12))
extracurriculars_plot
quick_save(extracurriculars_plot, "extracurriculars")

# 8. activities this year
activities_last_year_plot <- tri_plot(input_plots, "activities_last_year", "Programs Last Year")
activities_last_year_plot
quick_save(activities_last_year_plot, "activities_last_year")

# 9. Parent Somatic
parent_somatic_plot <- tri_plot(input_plots, "parent_somatic", "Parent Somatic", ylims = c(-0.5, 25))
parent_somatic_plot
quick_save(parent_somatic_plot, "parent_somatic")

# 10. parent_thought
parent_thought_plot <- tri_plot(input_plots, "parent_thought", "Parent Thought", ylims = c(-0.5, 13.5))
parent_thought_plot
quick_save(parent_thought_plot, "parent_thought")

# 11. parent_antisocial
parent_antisocial_plot <- tri_plot(input_plots, "parent_antisocial", "Parent Antisocial", ylims = c(-0.5, 20))
parent_antisocial_plot
quick_save(parent_antisocial_plot, "parent_antisocial")

# 12. Weekday screentime
weekday_screentime_plot <- tri_plot(input_plots, "weekday_screentime", "Weekday Screentime (hours)", ylims = c(-0.5, 21))
weekday_screentime_plot
quick_save(weekday_screentime_plot, "weekday_screentime")

# 13. parent_withdrawn
parent_withdrawn_plot <- tri_plot(input_plots, "parent_withdrawn", "Parent Withdrawn", ylims = c(-0.5, 17))
parent_withdrawn_plot
quick_save(parent_withdrawn_plot, "parent_withdrawn")

# 14. parent_aggressive
parent_aggressive_plot <- tri_plot(input_plots, "parent_aggressive", "Parent Aggressive", ylims = c(-0.5, 25))
parent_aggressive_plot
quick_save(parent_aggressive_plot, "parent_aggressive")

# 15. private_instruction
private_instruction_plot <- tri_plot(input_plots, "private_instruction", "Private Activities", ylims = c(-0.5, 9.5))
private_instruction_plot
quick_save(private_instruction_plot, "private_instruction")

# 16. Parent depress
parent_depress_plot <- tri_plot(input_plots, "parent_depress", "Parent Depress", ylims = c(-0.5, 25))
parent_depress_plot
quick_save(parent_depress_plot, "parent_depress")

# 17. parent_anxdep
parent_anxdep_plot <- tri_plot(input_plots, "parent_anxdep", "Parent Anxious-Depressed", ylims = c(-0.5, 30))
parent_anxdep_plot
quick_save(parent_anxdep_plot, "parent_anxdep")

# 18. parent_anxdisord
parent_anxdisord_plot <- tri_plot(input_plots, "parent_anxdisord", "Parent Anxious", ylims = c(-0.5, 13))
parent_anxdisord_plot
quick_save(parent_anxdisord_plot, "parent_anxdisord")

# 19. weekend_screentime
weekend_screentime_plot <- tri_plot(input_plots, "weekend_screentime", "Weekend Screentime (hours)", ylims = c(-0.5, 21))
weekend_screentime_plot
quick_save(weekend_screentime_plot, "weekend_screentime")

# 20. fmri_cort_subcort_cors
fmri_cort_subcort_cors_plot <- tri_plot(input_plots, "fmri_cort_subcort_cors", "fMRI Cort-Subcort Corrs", ylims = c(-0.15, 0.2))
fmri_cort_subcort_cors_plot
quick_save(fmri_cort_subcort_cors_plot, "fmri_cort_subcort_cors")

# 21. parent_avoidant
parent_avoidant_plot <- tri_plot(input_plots, "parent_avoidant", "Parent Avoidant", ylims = c(-0.5, 13))
parent_avoidant_plot
quick_save(parent_avoidant_plot, "parent_avoidant")

# 22. parent_hyperactive
parent_hyperactive_plot <- tri_plot(input_plots, "parent_hyperactive", "Parent Hyperactive", ylims = c(-0.5, 12))
parent_hyperactive_plot
quick_save(parent_hyperactive_plot, "parent_hyperactive")

# 23. same_sex_close_friend
same_sex_close_friend_plot <- tri_plot(input_plots, "same_sex_close_friend", "Same-Sex Close Friends (Quartile)")
same_sex_close_friend_plot
quick_save(same_sex_close_friend_plot, "same_sex_close_friend")

# 24. family_fight_p
family_fight_p_plot <- tri_plot(input_plots, "family_fight_p", "Family Fights\n(Parent Report)", scale_fill_labels = c("No", "Yes"))
family_fight_p_plot
quick_save(family_fight_p_plot, "family_fight_p")

# 25. parent_perstr
parent_perstr_plot <- tri_plot(input_plots, "parent_perstr", "Parent Personal Strength")
parent_perstr_plot
quick_save(parent_perstr_plot, "parent_perstr")

# 26. fmri_cort_cors
fmri_cort_cors_plot <- tri_plot(input_plots, "fmri_cort_cors", "fMRI Cort-Cort Corrs", ylims = c(-0.1, 0.16))
fmri_cort_cors_plot
quick_save(fmri_cort_cors_plot, "fmri_cort_cors")

# 27. family_outdo_p
family_outdo_p_plot <- tri_plot(input_plots, "family_outdo_p", "Family Outdo\n(Parent Report)", c("No", "Yes"))
family_outdo_p_plot
quick_save(family_outdo_p_plot, "family_outdo_p")

# 28. Parent attention
parent_attention_plot <- tri_plot(input_plots, "parent_attention", "Parent Attention", ylims = c(-0.5, 25))
parent_attention_plot
quick_save(parent_attention_plot, "parent_attention")

# 29. parent_intrusive
parent_intrusive_plot <- tri_plot(input_plots, "parent_intrusive", "Parent Intrusive", ylims = c(-0.5, 12))
parent_intrusive_plot
quick_save(parent_intrusive_plot, "parent_intrusive")

# 30. physical_activity
physical_activity_plot <- tri_plot(input_plots, "physical_activity", "Physical Activity", ylims = c(0, 1.1))
physical_activity_plot
quick_save(physical_activity_plot, "physical_activity")

# 31. headache_history
headache_history_plot <- tri_plot(input_plots, "headache_history", "Headache\nHistory", c("No", "Yes"))
headache_history_plot
quick_save(headache_history_plot, "headache_history")

# 32. helps_hurt_p
helps_hurt_p_plot <- tri_plot(input_plots, "helps_hurt_p", "Helps Hurt\n(Parent Report)", c("No", "Yes"))
helps_hurt_p_plot
quick_save(helps_hurt_p_plot, "helps_hurt_p")

# 33. mtbi_loc
mtbi_loc_plot <- tri_plot(input_plots, "mtbi_loc", "mTBI LOC", c("No", "Yes"))
mtbi_loc_plot
quick_save(mtbi_loc_plot, "mtbi_loc")

# 34. cortical_thickness
cortical_thickness_plot <- tri_plot(input_plots, "cortical_thickness", "Cortical Thickness (mm)", ylims = c(2.3, 3.1))
cortical_thickness_plot
quick_save(cortical_thickness_plot, "cortical_thickness")

# 35. school_programs
school_activities_plot <- tri_plot(input_plots, "school_activities", "School Activities", ylims = c(-0.5, 18))
school_activities_plot
quick_save(school_activities_plot, "school_activities")

# 36. helpful_y
helpful_y_plot <- tri_plot(input_plots, "helpful_y", "Helpful\n(Youth Report)", c("No", "Yes"))
helpful_y_plot
quick_save(helpful_y_plot, "helpful_y")

# 37. family_peaceful_p
family_peaceful_p_plot <- tri_plot(input_plots, "family_peaceful_p", "Family Peaceful\n(Parent Report)", c("No", "Yes"))
family_peaceful_p_plot
quick_save(family_peaceful_p_plot, "family_peaceful_p")

# 38. mtbi_mem_daze
mtbi_mem_daze_plot <- tri_plot(input_plots, "mtbi_mem_daze", "mTBI mem_daze", c("No", "Yes"))
mtbi_mem_daze_plot
quick_save(mtbi_mem_daze_plot, "mtbi_mem_daze")

# 39. considerate_y
considerate_y_plot <- tri_plot(input_plots, "considerate_y", "Considerate\n(Youth Report)", c("No", "Yes"))
considerate_y_plot
quick_save(considerate_y_plot, "considerate_y")

# 40. mtbi_mechanism
mtbi_mechanism_plot <- tri_plot(
    input_plots,
    "mtbi_mechanism",
    "mTBI Mechanism",
    c("Fall/Hit", "Hospital/ER", "Multiple Injuries", "Other", "Vehicle", "Violent")
)
mtbi_mechanism_plot
quick_save(mtbi_mechanism_plot, "mtbi_mechanism")

# 41. helps_hurt_y
helps_hurt_y_plot <- tri_plot(input_plots, "helps_hurt_y", "Helps Hurt\n(Youth Report)", c("No", "Yes"))
helps_hurt_y_plot
quick_save(helps_hurt_y_plot, "helps_hurt_y")

# 42. family_criticize_p
family_criticize_p_plot <- tri_plot(input_plots, "family_criticize_p", "Family Criticizes\n(Parent Report)", c("No", "Yes"))
family_criticize_p_plot
quick_save(family_criticize_p_plot, "family_criticize_p")

# 43. major_wm_ndi
major_wm_ndi_plot <- tri_plot(input_plots, "major_wm_ndi", "Major WM Neurite Density", ylims = c(0.45, 0.85))
major_wm_ndi_plot
quick_save(major_wm_ndi_plot, "major_wm_ndi")

# 44. family_temper_p
family_temper_p_plot <- tri_plot(input_plots, "family_temper_p", "Family Temper\n(Parent Report)", scale_fill_labels = c("No", "Yes"))
family_temper_p_plot
quick_save(family_temper_p_plot, "family_temper_p")

# 45. family_outdo_y
family_outdo_y_plot <- tri_plot(input_plots, "family_outdo_y", "Family Outdoing\n(Youth Report)", c("No", "Yes"))
family_outdo_y_plot
quick_save(family_outdo_y_plot, "family_outdo_y")

# 46. family_criticize_y
family_criticize_y_plot <- tri_plot(input_plots, "family_criticize_y", "Family Criticizes\n(Youth Report)", c("No", "Yes"))
family_criticize_y_plot
quick_save(family_criticize_y_plot, "family_criticize_y")

# 47. age
age_plot <- tri_plot(input_plots, "age", "age")
age_plot
quick_save(age_plot, "age")

# 48. pericortical_wm_ndi
pericortical_wm_ndi_plot <- tri_plot(input_plots, "pericortical_wm_ndi", "Pericortical WM Neurite Density", ylims = c(0.25, 0.6))
pericortical_wm_ndi_plot
quick_save(pericortical_wm_ndi_plot, "pericortical_wm_ndi")

# 49. same_sex_friend
same_sex_friend_plot <- tri_plot(input_plots, "same_sex_friend", "Same-Sex Friends\n(Quartile)")
same_sex_friend_plot
quick_save(same_sex_friend_plot, "same_sex_friend")

# 50. family_angry_p
family_angry_p_plot <- tri_plot(input_plots, "family_angry_p", "Family Angry\n(Parent Report)", c("No", "Yes"))
family_angry_p_plot
quick_save(family_angry_p_plot, "family_angry_p")

# 51. mtbi_age
mtbi_age_plot <- tri_plot(input_plots, "mtbi_age", "mTBI Age (months)")
mtbi_age_plot
quick_save(mtbi_age_plot, "mtbi_age")

# 52. helpful_p
helpful_p_plot <- tri_plot(input_plots, "helpful_p", "Helpful\n(Parent Report)", c("No", "Yes"))
helpful_p_plot
quick_save(helpful_p_plot, "helpful_p")

# 53. previous_mtbis
previous_mtbis_plot <- tri_plot(input_plots, "previous_mtbis", "Previous mTBIs")
previous_mtbis_plot
quick_save(previous_mtbis_plot, "previous_mtbis")

# 54. family_angry_y
family_angry_y_plot <- tri_plot(input_plots, "family_angry_y", "Family Angry\n(Youth Report)", c("No", "Yes"))
family_angry_y_plot
quick_save(family_angry_y_plot, "family_angry_y")

# 55. family_throw_p
family_throw_p_plot <- tri_plot(input_plots, "family_throw_p", "Family Throwing\n(Parent Report)", c("No", "Yes"))
family_throw_p_plot
quick_save(family_throw_p_plot, "family_throw_p")

# 56. pubertal_status_y
pubertal_status_y_plot <- tri_plot(input_plots, "pubertal_status_y", "Pubertal Status (Youth Report)")
pubertal_status_y_plot
quick_save(pubertal_status_y_plot, "pubertal_status_y")

# 57. family_hit_p
family_hit_p_plot <- tri_plot(input_plots, "family_hit_p", "Family Hitting\n(Parent Report)", c("No", "Yes"))
family_hit_p_plot
quick_save(family_hit_p_plot, "family_hit_p")

# 58. family_yell_y
family_yell_y_plot <- tri_plot(input_plots, "family_yell_y", "Family Yells\n(Youth Report)", c("No", "Yes"))
family_yell_y_plot
quick_save(family_yell_y_plot, "family_yell_y")

# 59. family_peaceful_y
family_peaceful_y_plot <- tri_plot(input_plots, "family_peaceful_y", "Family Peaceful\n(Youth Report)", c("No", "Yes"))
family_peaceful_y_plot
quick_save(family_peaceful_y_plot, "family_peaceful_y")

# 60. family_throw_y
family_throw_y_plot <- tri_plot(input_plots, "family_throw_y", "Family Throwing\n(Youth Report)", c("No", "Yes"))
family_throw_y_plot
quick_save(family_throw_y_plot, "family_throw_y")

# 61. opp_sex_friend
opp_sex_friend_plot <- tri_plot(input_plots, "opp_sex_friend", "Opposite-Sex Friends (Quartile)")
opp_sex_friend_plot
quick_save(opp_sex_friend_plot, "opp_sex_friend")

# 62. family_fight_y
family_fight_y_plot <- tri_plot(input_plots, "family_fight_y", "Family Fights\n(Youth Report)", c("No", "Yes"))
family_fight_y_plot
quick_save(family_fight_y_plot, "family_fight_y")

# 63. opp_sex_close_friend
opp_sex_close_friend_plot <- tri_plot(input_plots, "opp_sex_close_friend", "Opposite-Sex Close Friends\n(Quartile)")
opp_sex_close_friend_plot
quick_save(opp_sex_close_friend_plot, "opp_sex_close_friend")

# 64. considerate_p
considerate_p_plot <- tri_plot(input_plots, "considerate_p", "Considerate\n(Parent Report)", c("No", "Yes"))
considerate_p_plot
quick_save(considerate_p_plot, "considerate_p")

# 65. family_temper_y
family_temper_y_plot <- tri_plot(input_plots, "family_temper_y", "Family Temper\n(Youth Report)", c("No", "Yes"))
family_temper_y_plot
quick_save(family_temper_y_plot, "family_temper_y")

# 66. family_yell_p
family_yell_p_plot <- tri_plot(input_plots, "family_yell_p", "Family Yells\n(Parent Report)", c("No", "Yes"))
family_yell_p_plot
quick_save(family_yell_p_plot, "family_yell_p")

# 67. family_hit_y
family_hit_y_plot <- tri_plot(input_plots, "family_hit_y", "Family Hitting\n(Youth Report)", c("No", "Yes"))
family_hit_y_plot
quick_save(family_hit_y_plot, "family_hit_y")

# Outcome trip-plots
cbcl_anxdep_plot <- tri_plot(outcome_plots, "cbcl_anxdep", "Anxious-Depressed", ylims = c(-0.5, 30))
cbcl_withdep_plot <- tri_plot(outcome_plots, "cbcl_withdep", "Withdrawn-Depressed", ylims = c(-0.5, 15))
cbcl_somatic_plot <- tri_plot(outcome_plots, "cbcl_somatic", "Somatic Problems", ylims = c(-0.5, 17))
cbcl_social_plot <- tri_plot(outcome_plots, "cbcl_social", "Social Problems", ylims = c(-0.5, 20))
cbcl_thought_plot <- tri_plot(outcome_plots, "cbcl_thought", "Thought Problems", ylims = c(-0.5, 20))
cbcl_attention_plot <- tri_plot(outcome_plots, "cbcl_attention", "Attention Problems", ylims = c(-0.5, 22))
cbcl_rulebreak_plot <- tri_plot(outcome_plots, "cbcl_rulebreak", "Rule-Breaking Problems", ylims = c(-0.5, 22))
cbcl_aggressive_plot <- tri_plot(outcome_plots, "cbcl_aggressive", "Aggression Problems", ylims = c(-0.5, 32))
sds_sleep_plot <- tri_plot(outcome_plots, "sds_sleep", "Total Sleep Problems", ylims = c(20, 100))
```

```{r}

generalizing_plots <- list(
    "sex" = sex_plot,
    "household_income" = household_income_plot,
    "brain_volume" = brain_volume_plot,
    "cort_sa" = cort_sa_plot,
    "pubertal_status_p" = pubertal_status_p_plot,
    "race" = race_plot,
    "extracurriculars" = extracurriculars_plot,
    "activities_last_year" = activities_last_year_plot,
    "parent_somatic" = parent_somatic_plot,
    "parent_thought" = parent_thought_plot,
    "parent_antisocial" = parent_antisocial_plot,
    "weekday_screentime" = weekday_screentime_plot,
    "parent_withdrawn" = parent_withdrawn_plot,
    "parent_aggressive" = parent_aggressive_plot,
    "private_instruction" = private_instruction_plot,
    "parent_depress" = parent_depress_plot,
    "parent_anxdep" = parent_anxdep_plot,
    "parent_anxdisord" = parent_anxdisord_plot,
    "weekend_screentime" = weekend_screentime_plot,
    "fmri_cort_subcort_cors" = fmri_cort_subcort_cors_plot,
    "parent_avoidant" = parent_avoidant_plot,
    "parent_hyperactive" = parent_hyperactive_plot,
    "same_sex_close_friend" = same_sex_close_friend_plot,
    "family_fight_p" = family_fight_p_plot,
    "parent_perstr" = parent_perstr_plot,
    "fmri_cort_cors" = fmri_cort_cors_plot,
    "family_outdo_p" = family_outdo_p_plot,
    "parent_attention" = parent_attention_plot,
    "parent_intrusive" = parent_intrusive_plot,
    "physical_activity" = physical_activity_plot,
    "headache_history" = headache_history_plot,
    "helps_hurt_p" = helps_hurt_p_plot,
    "mtbi_loc" = mtbi_loc_plot,
    "cortical_thickness" = cortical_thickness_plot,
    "school_activities" = school_activities_plot,
    "helpful_y" = helpful_y_plot,
    "family_peaceful_p" = family_peaceful_p_plot,
    "mtbi_mem_daze" = mtbi_mem_daze_plot,
    "considerate_y" = considerate_y_plot,
    "mtbi_mechanism" = mtbi_mechanism_plot,
    "helps_hurt_y" = helps_hurt_y_plot,
    "family_criticize_p" = family_criticize_p_plot,
    "major_wm_ndi" = major_wm_ndi_plot,
    "family_temper_p" = family_temper_p_plot,
    "family_outdo_y" = family_outdo_y_plot,
    "family_criticize_y" = family_criticize_y_plot,
    "age" = age_plot,
    "pericortical_wm_ndi" = pericortical_wm_ndi_plot,
    "same_sex_friend" = same_sex_friend_plot,
    "family_angry_p" = family_angry_p_plot,
    "mtbi_age" = mtbi_age_plot,
    "helpful_p" = helpful_p_plot,
    "previous_mtbis" = previous_mtbis_plot,
    "family_angry_y" = family_angry_y_plot,
    "family_throw_p" = family_throw_p_plot,
    "pubertal_status_y" = pubertal_status_y_plot,
    "family_hit_p" = family_hit_p_plot,
    "family_yell_y" = family_yell_y_plot,
    "family_peaceful_y" = family_peaceful_y_plot,
    "family_throw_y" = family_throw_y_plot,
    "opp_sex_friend" = opp_sex_friend_plot,
    "family_fight_y" = family_fight_y_plot,
    "opp_sex_close_friend" = opp_sex_close_friend_plot,
    "considerate_p" = considerate_p_plot,
    "family_temper_y" = family_temper_y_plot,
    "family_yell_p" = family_yell_p_plot,
    "family_hit_y" = family_hit_y_plot
)

generalizing_outcome_plots <- list(
    "cbcl_anxdep" = cbcl_anxdep_plot,
    "cbcl_withdep" = cbcl_withdep_plot,
    "cbcl_somatic" = cbcl_somatic_plot,
    "cbcl_social" = cbcl_social_plot,
    "cbcl_thought" = cbcl_thought_plot,
    "cbcl_attention" = cbcl_attention_plot,
    "cbcl_rulebreak" = cbcl_rulebreak_plot,
    "cbcl_aggressive" = cbcl_aggressive_plot,
    "sds_sleep" = sds_sleep_plot
)

generalizing_plots <- lapply(
    generalizing_plots,
    function(x) {
        x[[1]] <- x[[1]] + theme(axis.title.x = element_blank()) 
        x[[2]] <- x[[2]] + theme(axis.title.x = element_blank()) 
        x[[3]] <- x[[3]] + theme(axis.title.x = element_blank()) 
        return(x)
    }
)

generalizing_outcome_plots <- lapply(
    generalizing_outcome_plots,
    function(x) {
        x[[1]] <- x[[1]] + theme(axis.title.x = element_blank()) 
        x[[2]] <- x[[2]] + theme(axis.title.x = element_blank()) 
        x[[3]] <- x[[3]] + theme(axis.title.x = element_blank()) 
        return(x)
    }
)
```

```{r}
wp_1 <- wrap_plots(generalizing_plots[1:10], ncol = 1)
quick_save(wp_1, "wp_1", w = 10, h = 30)

wp_2 <- wrap_plots(generalizing_plots[11:20], ncol = 1)
quick_save(wp_2, "wp_2", w = 10, h = 30)

wp_3 <- wrap_plots(generalizing_plots[21:30], ncol = 1)
quick_save(wp_3, "wp_3", w = 10, h = 30)

wp_4 <- wrap_plots(generalizing_plots[31:40], ncol = 1)
quick_save(wp_4, "wp_4", w = 10, h = 30)

wp_5 <- wrap_plots(generalizing_plots[41:50], ncol = 1)
quick_save(wp_5, "wp_5", w = 10, h = 30)

wp_6 <- wrap_plots(generalizing_plots[51:60], ncol = 1)
quick_save(wp_6, "wp_6", w = 10, h = 30)

wp_7 <- wrap_plots(generalizing_plots[61:67], ncol = 1)
quick_save(wp_7, "wp_7", w = 10, h = 21)
```

```{r}
wpo <- wrap_plots(generalizing_outcome_plots, ncol = 1)

quick_save(wpo, "wpo", w = 7, h = 22)
```

# Summary of the validation (table)

# Topologies go here, save actually for later.

```{r}
mtbi_der_df <- auto_plot(
    solutions_matrix_row = mtbi_mc_e_esm,
    data_list = all_dls$"mtbi_train_data_lists"$"imp_3",
    target_list = all_dls$"mtbi_train_oom_lists"$"imp_3",
    return_plots = FALSE
)

mtbi_ful_df <- auto_plot(
    mtbi_full_top_3c,
    data_list = full_data_list_1,
    target_list = full_oom_list_1,
    return_plots = FALSE
)

mtbi_val_df <- auto_plot(
    cluster_df = val_cluster_df,
    data_list = test_data_list_s1,
    target_list = test_oom_list_s1,
    return_plots = FALSE
) 

write_csv(mtbi_der_df, proc_path("mtbi_der_df.csv", TRUE))
write_csv(mtbi_ful_df, proc_path("mtbi_ful_df.csv", TRUE))
write_csv(mtbi_val_df, proc_path("mtbi_val_df.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_der_df <- read_csv(proc_path("2024_11_07_mtbi_der_df.csv"))
mtbi_ful_df <- read_csv(proc_path("2024_11_07_mtbi_ful_df.csv"))
mtbi_val_df <- read_csv(proc_path("2024_11_07_mtbi_val_df.csv"))
```

```{r}
mtbi_der_tops <- topologizer(mtbi_der_df)
mtbi_ful_tops <- topologizer(mtbi_ful_df)
mtbi_val_tops <- topologizer(mtbi_val_df)

write_csv(mtbi_der_tops, proc_path("mtbi_der_tops.csv", TRUE))
write_csv(mtbi_ful_tops, proc_path("mtbi_ful_tops.csv", TRUE))
write_csv(mtbi_val_tops, proc_path("mtbi_val_tops.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_der_tops <- read_csv(proc_path("2024_11_07_mtbi_der_tops.csv"))
mtbi_ful_tops <- read_csv(proc_path("2024_11_07_mtbi_ful_tops.csv"))
mtbi_val_tops <- read_csv(proc_path("2024_11_07_mtbi_val_tops.csv"))
```

```{r}
# FUNCTION: Calculate if an ES is significant
significant_es <- function(type, l, u) {
    thresh <- as.numeric(type %in% c("or", "OR"))
    return(as.numeric(thresh < l | thresh > u))
}


# FUNCTION: Format topologies
format_tops <- function(tops) {
    tops <- data.frame(tops) |> mutate(
        c12_sig = significant_es(es, c12_l, c12_u),
        c13_sig = significant_es(es, c13_l, c13_u),
        c23_sig = significant_es(es, c23_l, c23_u)
    )
    # Strips whitespace by converting number columns to numeric format
    tops <- numcol_to_numeric(tops)
    tops <- tops |> mutate(
        "C1 vs. C2" = paste0(c12_es, " [", c12_l, ", ", c12_u, "]"),
        "C1 vs. C3" = paste0(c13_es, " [", c13_l, ", ", c13_u, "]"),
        "C2 vs. C3" = paste0(c23_es, " [", c23_l, ", ", c23_u, "]"),
        .keep = "unused"
    )
    tops <- tops |> mutate(
        "C1 vs. C2" = ifelse(c12_sig == 1, paste0("textbf{", `C1 vs. C2`, "}"), `C1 vs. C2`),
        "C1 vs. C3" = ifelse(c13_sig == 1, paste0("textbf{", `C1 vs. C3`, "}"), `C1 vs. C3`),
        "C2 vs. C3" = ifelse(c23_sig == 1, paste0("textbf{", `C2 vs. C3`, "}"), `C2 vs. C3`),
        .keep = "unused"
    )
    # Remove scientific notation and trailing zeros
    tops <- format(data.frame(tops), scientific = FALSE, drop0trailing = TRUE)
    colnames(tops) <- c("Feature", "Summary", "C1", "C2", "C3", "ES", "C1 vs. C2", "C1 vs. C3", "C2 vs. C3")
    return(tops)
}

```

```{r}
# Prepping the ordering of the tops features
mtbi_mc_e_nmi_v_pval_rank <- read_csv(
    proc_path("2024_11_04_mtbi_mc_e_nmi_v_pval_rank.csv")
)

joint_ranks <- mtbi_mc_e_nmi_v_pval_rank |>
    data.frame() |>
    dplyr::select(feature, joint_rank)
joint_ranks <- rbind(
    joint_ranks,
    data.frame(
        feature = c(
            "race_black",
            "race_white",
            "race_hispanic",
            "race_other"
        ),
        joint_rank = joint_ranks[joint_ranks$"feature" == "race", "joint_rank"]
    )
)
joint_ranks <- rbind(
    joint_ranks,
    data.frame(
        feature = c(
            "mtbi_mechanism_fall_hit",
            "mtbi_mechanism_hosp_er",
            "mtbi_mechanism_multi",
            "mtbi_mechanism_other_loc",
            "mtbi_mechanism_vehicle",
            "mtbi_mechanism_violent"
        ),
        joint_rank = joint_ranks[joint_ranks$"feature" == "mtbi_mechanism", "joint_rank"]
    )
)
joint_ranks <- dplyr::filter(joint_ranks, !feature %in% c("mtbi_mechanism", "race"))

joint_ranks <- arrange(joint_ranks, joint_rank)

write_csv(joint_ranks, proc_path("joint_ranks.csv", TRUE))
```

```{r}
# CHECKPOINT
joint_ranks <- read_csv(proc_path("2024_11_07_joint_ranks.csv"))
```


```{r}
outcomes <- summarize_dl(test_oom_list_s1, scope = "feature")$"name"

joint_ranks_with_out <- rbind(
    data.frame(
        feature = outcomes,
        joint_rank = nrow(joint_ranks) + 1
    ),
    joint_ranks
) |> data.frame()

f_der_tops <- data.frame(format_tops(mtbi_der_tops))
f_val_tops <- data.frame(format_tops(mtbi_val_tops))
f_ful_tops <- data.frame(format_tops(mtbi_ful_tops))

all_der_tops <- dplyr::full_join(
    joint_ranks_with_out,
    f_der_tops,
    by = join_by("feature" == "Feature")
) |>
    dplyr::select(-joint_rank) |>
    dplyr::rename("Feature" = "feature")

all_val_tops <- dplyr::full_join(
    joint_ranks_with_out,
    f_val_tops,
    by = join_by("feature" == "Feature")
) |>
    dplyr::select(-joint_rank) |>
    dplyr::rename("Feature" = "feature")

all_ful_tops <- dplyr::full_join(
    joint_ranks_with_out,
    f_ful_tops,
    by = join_by("feature" == "Feature")
) |>
    dplyr::select(-joint_rank) |>
    dplyr::rename("Feature" = "feature")

write_csv(all_der_tops, proc_path("mtbi_all_der_tops.csv", TRUE))
write_csv(all_val_tops, proc_path("mtbi_all_val_tops.csv", TRUE))
write_csv(all_ful_tops, proc_path("mtbi_all_ful_tops.csv", TRUE))
```

```{r}
# CHECKPOINT
all_der_tops <- read_csv(proc_path("2024_11_07_mtbi_all_der_tops.csv"))
all_val_tops <- read_csv(proc_path("2024_11_07_mtbi_all_val_tops.csv"))
all_ful_tops <- read_csv(proc_path("2024_11_07_mtbi_all_ful_tops.csv"))
```

```{r}
all_der_tops$"Set" <- "D"
all_val_tops$"Set" <- "V"
all_ful_tops$"Set" <- "F"

all_der_tops$rank <- seq_len(nrow(all_der_tops))
all_val_tops$rank <- seq_len(nrow(all_val_tops))
all_ful_tops$rank <- seq_len(nrow(all_ful_tops))

all_tops <- do.call(rbind, list(all_der_tops, all_val_tops, all_ful_tops))

all_tops <- arrange(all_tops, rank) |>
    relocate(Set, .after = "Feature") |>
    dplyr::select(-rank)

write_csv(all_tops, proc_path("all_tops.csv", TRUE))

all_tops <- read_csv(proc_path("2024_11_07_all_tops.csv"))

xtable(all_tops)
```

```{r}
mtbi_der_tops$"set" <- "D"
mtbi_ful_tops$"set" <- "V"
mtbi_val_tops$"set" <- "F"

all_der_tops_raw <- dplyr::full_join(
    joint_ranks_with_out,
    mtbi_der_tops,
    by = "feature"
) |>
    dplyr::select(-joint_rank)

all_val_tops_raw <- dplyr::full_join(
    joint_ranks_with_out,
    mtbi_val_tops,
    by = "feature"
) |>
    dplyr::select(-joint_rank)

all_ful_tops_raw <- dplyr::full_join(
    joint_ranks_with_out,
    mtbi_ful_tops,
    by = "feature"
) |>
    dplyr::select(-joint_rank)

all_der_tops_raw$rank <- seq_len(nrow(all_der_tops_raw))
all_val_tops_raw$rank <- seq_len(nrow(all_val_tops_raw))
all_ful_tops_raw$rank <- seq_len(nrow(all_ful_tops_raw))

all_tops_raw <- do.call(
    rbind,
    list(
        all_der_tops_raw,
        all_val_tops_raw,
        all_ful_tops_raw
    )
)

all_tops_raw$"set" <- factor(
    all_tops_raw$"set",
    levels = c("D", "V", "F")
)

options(width = 200)

all_tops_raw <- all_tops_raw |> arrange(rank, set)

write_csv(all_tops_raw, proc_path("all_tops_raw.csv", TRUE))
```

```{r}
all_tops_raw <- read_csv(proc_path("2024_11_07_all_tops_raw.csv"))

# Comparison based purely on effect size
compare_fn_a <- function(d, sig, thresh = 0.2) {
    order <- case_when(
        d >= thresh ~ ">",
        d <= -thresh ~ "<",
        abs(d) < thresh ~ "=",
        TRUE ~ NA
    )
    return(order)
}

# Comparison based on effect size and significance
compare_fn_b <- function(d, sig, thresh = 0.2) {
    order <- case_when(
        d >= thresh ~ ">",
        d <= -thresh ~ "<",
        d > 0 & sig ~ ">",
        d < 0 & sig ~ "<",
        abs(d) < thresh & !sig ~ "=",
        TRUE ~ NA
    )
}

generalizable_features <- function(tops_df, comparison_fn, t = 0.2) {
    # Remove unnecessary columns
    if ("rank" %in% colnames(tops_df)) {
        tops_df <- dplyr::select(tops_df, -rank)
    }
    if ("summary" %in% colnames(tops_df)) {
        tops_df <- dplyr::select(tops_df, -summary)
    }
    # Calculate significance for every row
    tops_df <- tops_df |>
        mutate(
            c12_sig = as.logical(significant_es(es, c12_l, c12_u)),
            c13_sig = as.logical(significant_es(es, c13_l, c13_u)),
            c23_sig = as.logical(significant_es(es, c23_l, c23_u))
        )
    # Create d-values for every row
    tops_df <- tops_df |>
        dplyr::mutate(
            c12_d = dplyr::case_when(
                es == "d" ~ c12_es,
                es == "or" ~ suppressWarnings(log(c12_es)) * sqrt(3) / pi
            ),
            c13_d = dplyr::case_when(
                es == "d" ~ c13_es,
                es == "or" ~ suppressWarnings(log(c13_es)) * sqrt(3) / pi
            ),
            c23_d = dplyr::case_when(
                es == "d" ~ c23_es,
                es == "or" ~ suppressWarnings(log(c23_es)) * sqrt(3) / pi
            )
        )
    # Calculate orderings
    tops_df <- tops_df |>
        dplyr::mutate(
            c12_order = comparison_fn(c12_d, c12_sig, thresh = t),
            c13_order = comparison_fn(c13_d, c13_sig, thresh = t),
            c23_order = comparison_fn(c23_d, c23_sig, thresh = t)
        )
    # Now find conistency across D, V, F for each feature
    features <- unique(tops_df$"feature")
    gen_df <- data.frame()
    for (ft in features) {
        feature_df <- dplyr::filter(tops_df, feature == ft)
        c12 <- feature_df$"c12_order"
        c13 <- feature_df$"c13_order"
        c23 <- feature_df$"c23_order"
        if (any(is.na(c12)) | length(unique(c12)) > 1) {
            c12o <- NA
        } else {
            c12o <- unique(c12)
        }
        if (any(is.na(c13)) | length(unique(c13)) > 1) {
            c13o <- NA
        } else {
            c13o <- unique(c13)
        }
        if (any(is.na(c23)) | length(unique(c23)) > 1) {
            c23o <- NA
        } else {
            c23o <- unique(c23)
        }
        gen_df <- rbind(
            gen_df,
            data.frame(
                feature = ft,
                c1v2 = c12o,
                c1v3 = c13o,
                c2v3 = c23o
            )
        )
    }
    return(gen_df)
}

gen_df_a <- generalizable_features(all_tops_raw, compare_fn_a, 0.2)
gen_df_b <- generalizable_features(all_tops_raw, compare_fn_b)

# The generalizable features appear identical by both means
identical(gen_df_a, gen_df_b)

write_csv(gen_df_a, proc_path("mtbi_gen_fts.csv", TRUE))

mtbi_gen_fts <- data.frame(read_csv(proc_path("2024_11_07_mtbi_gen_fts.csv")))

mtbi_gen_fts_in <- mtbi_gen_fts |>
    dplyr::filter(
        c1v2 %in% c(">", "<") | c1v3 %in% c(">", "<") | c2v3 %in% c(">", "<")
    ) |>
    dplyr::filter(
        !feature %in% outcomes
    )

mtbi_gen_fts_out <- mtbi_gen_fts |>
    dplyr::filter(
        c1v2 %in% c(">", "<") | c1v3 %in% c(">", "<") | c2v3 %in% c(">", "<")
    ) |>
    dplyr::filter(
        feature %in% outcomes
    )

write_csv(mtbi_gen_fts_in, proc_path("mtbi_gen_fts_in.csv", TRUE))
write_csv(mtbi_gen_fts_out, proc_path("mtbi_gen_fts_out.csv", TRUE))

mtbi_gen_fts_in <- read_csv(proc_path("2024_11_07_mtbi_gen_fts_in.csv"))
mtbi_gen_fts_out <- read_csv(proc_path("2024_11_07_mtbi_gen_fts_out.csv"))

mtbi_gen_fts_in_long <- mtbi_gen_fts_in |>
    pivot_longer(
        cols = -feature,
        names_to = "comparison",
        values_to = "order"
    )

mtbi_gen_fts_out_long <- mtbi_gen_fts_out |>
    pivot_longer(
        cols = -feature,
        names_to = "comparison",
        values_to = "order"
    )

write_csv(mtbi_gen_fts_in_long, proc_path("mtbi_gen_fts_in_long.csv", TRUE))
write_csv(mtbi_gen_fts_out_long, proc_path("mtbi_gen_fts_out_long.csv", TRUE))

mtbi_gen_fts_in_long <- read_csv(proc_path("2024_11_07_mtbi_gen_fts_in_long.csv"))
mtbi_gen_fts_out_long <- read_csv(proc_path("2024_11_07_mtbi_gen_fts_out_long.csv"))

xtable(mtbi_gen_fts_out)

xtable(mtbi_gen_fts_in)


mtbi_gen_fts_in_long

mtbi_gen_fts_in




```
