# metaSNF of Baseline mTBI Subjects

This chapter contains:

1. Derivation of baseline mTBI subtypes with metasnf
2. Characterization of those subtypes

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)
library(ggplot2)
library(patchwork)
library(xtable)
library(compute.es)
library(dplyr)
library(fastDummies)
library(tidyr)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subs <- read_csv(sub_path("2025_02_07_mtbi_subs.csv"))
mtbi_train_subs <- read_csv(sub_path("2025_02_07_mtbi_train_subs.csv"))
mtbi_test_subs <- read_csv(sub_path("2025_02_07_mtbi_test_subs.csv"))
unij_subs <- read_csv(sub_path("2025_02_07_unij_subs.csv"))
```

## Importing data

```{r}
# CHECKPOINT
all_dls <- readRDS(input_path("2025_02_10_all_dls.rds"))
```

## Generating the SNF config

```{r}
set.seed(42)
mtbi_config <- snf_config(
    all_dls$"mtbi_train_data_lists"$"imp_1",
    n_solutions = 200,
    cnt_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    dsc_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ord_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    use_default_dist_fns = TRUE
)

mtbi_config$"clust_fns_list"[[1]]

saveRDS(mtbi_config, proc_path("mtbi_config.rds", TRUE))
```

```{r}
# CHECKPOINT
mtbi_config <- readRDS(proc_path("2025_02_10_mtbi_config.rds"))
```

## Running SNF for each of the imputations

```{r}

mtbi_config[176]

mtbi_sol_df_s1 <- batch_snf(
    dl = all_dls$"mtbi_train_data_lists"[[1]],
    sc = mtbi_config[176],
    processes = 1,
    return_sim_mats = TRUE
)

sim_mats_list(mtbi_sol_df_s1)[[1]]

saveRDS(mtbi_sol_df_s1, proc_path("mtbi_sol_df_s1.rds", TRUE))
#
mtbi_sol_df_s2 <- batch_snf(
    dl = all_dls$"mtbi_train_data_lists"[[2]],
    sc = mtbi_config,
    processes = "max"
)
saveRDS(mtbi_sol_df_s2, proc_path("mtbi_sol_df_s2.rds", TRUE))
#
mtbi_sol_df_s3 <- batch_snf(
    dl = all_dls$"mtbi_train_data_lists"[[3]],
    sc = mtbi_config,
    processes = "max"
)
saveRDS(mtbi_sol_df_s3, proc_path("mtbi_sol_df_s3.rds", TRUE))
#
mtbi_sol_df_s4 <- batch_snf(
    dl = all_dls$"mtbi_train_data_lists"[[4]],
    sc = mtbi_config,
    processes = "max"
)
saveRDS(mtbi_sol_df_s4, proc_path("mtbi_sol_df_s4.rds", TRUE))
#
mtbi_sol_df_s5 <- batch_snf(
    dl = all_dls$"mtbi_train_data_lists"[[5]],
    sc = mtbi_config,
    processes = "max"
)
saveRDS(mtbi_sol_df_s5, proc_path("mtbi_sol_df_s5.rds", TRUE))
#
mtbi_sol_df_p1 <- batch_snf(
    dl = all_dls$"mtbi_pooled_data_lists"[[1]],
    sc = mtbi_config,
    processes = "max"
)
saveRDS(mtbi_sol_df_p1, proc_path("mtbi_sol_df_p1.rds", TRUE))
#
mtbi_sol_df_p2 <- batch_snf(
    dl = all_dls$"mtbi_pooled_data_lists"[[2]],
    sc = mtbi_config,
    processes = "max"
)
saveRDS(mtbi_sol_df_p2, proc_path("mtbi_sol_df_p2.rds", TRUE))
#
mtbi_sol_df_p3 <- batch_snf(
    dl = all_dls$"mtbi_pooled_data_lists"[[3]],
    sc = mtbi_config,
    processes = "max"
)
saveRDS(mtbi_sol_df_p3, proc_path("mtbi_sol_df_p3.rds", TRUE))
#
mtbi_sol_df_p4 <- batch_snf(
    dl = all_dls$"mtbi_pooled_data_lists"[[4]],
    sc = mtbi_config,
    processes = "max"
)
saveRDS(mtbi_sol_df_p4, proc_path("mtbi_sol_df_p4.rds", TRUE))
#
mtbi_sol_df_p5 <- batch_snf(
    dl = all_dls$"mtbi_pooled_data_lists"[[5]],
    sc = mtbi_config,
    processes = "max"
)
saveRDS(mtbi_sol_df_p5, proc_path("mtbi_sol_df_p5.rds", TRUE))
```

```{r}
mtbi_sol_df_s1 <- readRDS(proc_path("2025_02_10_mtbi_sol_df_s1.rds"))
mtbi_sol_df_s2 <- readRDS(proc_path("2025_02_10_mtbi_sol_df_s2.rds"))
mtbi_sol_df_s3 <- readRDS(proc_path("2025_02_10_mtbi_sol_df_s3.rds"))
mtbi_sol_df_s4 <- readRDS(proc_path("2025_02_10_mtbi_sol_df_s4.rds"))
mtbi_sol_df_s5 <- readRDS(proc_path("2025_02_10_mtbi_sol_df_s5.rds"))
mtbi_sol_df_p1 <- readRDS(proc_path("2025_02_10_mtbi_sol_df_p1.rds"))
mtbi_sol_df_p2 <- readRDS(proc_path("2025_02_10_mtbi_sol_df_p2.rds"))
mtbi_sol_df_p3 <- readRDS(proc_path("2025_02_10_mtbi_sol_df_p3.rds"))
mtbi_sol_df_p4 <- readRDS(proc_path("2025_02_10_mtbi_sol_df_p4.rds"))
mtbi_sol_df_p5 <- readRDS(proc_path("2025_02_10_mtbi_sol_df_p5.rds"))

mtbi_sol_df <- do.call(
    "rbind",
    c(
        list(
            mtbi_sol_df_s1,
            mtbi_sol_df_s2,
            mtbi_sol_df_s3,
            mtbi_sol_df_s4,
            mtbi_sol_df_s5,
            mtbi_sol_df_p1,
            mtbi_sol_df_p2,
            mtbi_sol_df_p3,
            mtbi_sol_df_p4,
            mtbi_sol_df_p5
        ),
        list(reset_indices = TRUE)
    )
)
saveRDS(mtbi_sol_df, proc_path("mtbi_sol_df.rds", TRUE))

mtbi_ari <- calc_aris(mtbi_sol_df, processes = "max")
saveRDS(mtbi_ari, proc_path("mtbi_ari.rds", TRUE))

mtbi_ari_order <- get_matrix_order(mtbi_ari)
write_csv(data.frame(mtbi_ari_order), proc_path("mtbi_ari_order.csv", TRUE))
```

## Re-importing data

```{r}
# CHECKPOINT
mtbi_sol_df <- readRDS(proc_path("2025_02_10_mtbi_sol_df.rds"))
mtbi_ari <- readRDS(proc_path("2025_02_10_mtbi_ari.rds"))
mtbi_ari_order <- unlist(read_csv(proc_path("2025_02_10_mtbi_ari_order.csv")))
names(mtbi_ari_order) <- NULL
```

## Calculating associations between cluster solutions and features

```{r}
# Solo imputation 1
mtbi_ext_sol_df_s1 <- extend_solutions(
    mtbi_sol_df[1:200, ],
    dl = all_dls$"mtbi_train_data_lists"$"imp_1",
    target_dl = all_dls$"mtbi_train_oom_lists"$"imp_1",
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(mtbi_ext_sol_df_s1, proc_path("mtbi_ext_sol_df_s1.rds", TRUE))
# Solo imputation 2
mtbi_ext_sol_df_s2 <- extend_solutions(
    mtbi_sol_df[201:400, ],
    dl = all_dls$"mtbi_train_data_lists"$"imp_2",
    target_dl = all_dls$"mtbi_train_oom_lists"$"imp_2",
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(mtbi_ext_sol_df_s2, proc_path("mtbi_ext_sol_df_s2.rds", TRUE))
# Solo imputation 3
mtbi_ext_sol_df_s3 <- extend_solutions(
    mtbi_sol_df[401:600, ],
    dl = all_dls$"mtbi_train_data_lists"$"imp_3",
    target_dl = all_dls$"mtbi_train_oom_lists"$"imp_3",
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(mtbi_ext_sol_df_s3, proc_path("mtbi_ext_sol_df_s3.rds", TRUE))
# Solo imputation 4
mtbi_ext_sol_df_s4 <- extend_solutions(
    mtbi_sol_df[601:800, ],
    dl = all_dls$"mtbi_train_data_lists"$"imp_4",
    target_dl = all_dls$"mtbi_train_oom_lists"$"imp_4",
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(mtbi_ext_sol_df_s4, proc_path("mtbi_ext_sol_df_s4.rds", TRUE))
# Solo imputation 5
mtbi_ext_sol_df_s5 <- extend_solutions(
    mtbi_sol_df[801:1000, ],
    dl = all_dls$"mtbi_train_data_lists"$"imp_5",
    target_dl = all_dls$"mtbi_train_oom_lists"$"imp_5",
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(mtbi_ext_sol_df_s5, proc_path("mtbi_ext_sol_df_s5.rds", TRUE))
# Pooled imputation 1
mtbi_ext_sol_df_p1 <- extend_solutions(
    mtbi_sol_df[1001:1200, ],
    dl = all_dls$"mtbi_pooled_data_lists"$"imp_1",
    target_dl = all_dls$"mtbi_pooled_oom_lists"$"imp_1",
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(mtbi_ext_sol_df_p1, proc_path("mtbi_ext_sol_df_p1.rds", TRUE))
# Pooled imputation 2
mtbi_ext_sol_df_p2 <- extend_solutions(
    mtbi_sol_df[1201:1400, ],
    dl = all_dls$"mtbi_pooled_data_lists"$"imp_2",
    target_dl = all_dls$"mtbi_pooled_oom_lists"$"imp_2",
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(mtbi_ext_sol_df_p2, proc_path("mtbi_ext_sol_df_p2.rds", TRUE))
# Pooled imputation 3
mtbi_ext_sol_df_p3 <- extend_solutions(
    mtbi_sol_df[1401:1600, ],
    dl = all_dls$"mtbi_pooled_data_lists"$"imp_3",
    target_dl = all_dls$"mtbi_pooled_oom_lists"$"imp_3",
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(mtbi_ext_sol_df_p3, proc_path("mtbi_ext_sol_df_p3.rds", TRUE))
# Pooled imputation 4
mtbi_ext_sol_df_p4 <- extend_solutions(
    mtbi_sol_df[1601:1800, ],
    dl = all_dls$"mtbi_pooled_data_lists"$"imp_4",
    target_dl = all_dls$"mtbi_pooled_oom_lists"$"imp_4",
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(mtbi_ext_sol_df_p4, proc_path("mtbi_ext_sol_df_p4.rds", TRUE))
# Pooled imputation 5
mtbi_ext_sol_df_p5 <- extend_solutions(
    mtbi_sol_df[1801:2000, ],
    dl = all_dls$"mtbi_pooled_data_lists"$"imp_5",
    target_dl = all_dls$"mtbi_pooled_oom_lists"$"imp_5",
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(mtbi_ext_sol_df_p5, proc_path("mtbi_ext_sol_df_p5.rds", TRUE))

mtbi_ext_sol_df_s1 <- readRDS(proc_path("2025_02_10_mtbi_ext_sol_df_s1.rds"))
mtbi_ext_sol_df_s2 <- readRDS(proc_path("2025_02_10_mtbi_ext_sol_df_s2.rds"))
mtbi_ext_sol_df_s3 <- readRDS(proc_path("2025_02_10_mtbi_ext_sol_df_s3.rds"))
mtbi_ext_sol_df_s4 <- readRDS(proc_path("2025_02_10_mtbi_ext_sol_df_s4.rds"))
mtbi_ext_sol_df_s5 <- readRDS(proc_path("2025_02_10_mtbi_ext_sol_df_s5.rds"))
mtbi_ext_sol_df_p1 <- readRDS(proc_path("2025_02_10_mtbi_ext_sol_df_p1.rds"))
mtbi_ext_sol_df_p2 <- readRDS(proc_path("2025_02_10_mtbi_ext_sol_df_p2.rds"))
mtbi_ext_sol_df_p3 <- readRDS(proc_path("2025_02_10_mtbi_ext_sol_df_p3.rds"))
mtbi_ext_sol_df_p4 <- readRDS(proc_path("2025_02_10_mtbi_ext_sol_df_p4.rds"))
mtbi_ext_sol_df_p5 <- readRDS(proc_path("2025_02_10_mtbi_ext_sol_df_p5.rds"))

mtbi_ext_sol_df_s1_no_mtbi <- mtbi_ext_sol_df_s1 |> dplyr::select(-dplyr::contains("mtbi"))
mtbi_ext_sol_df_s2_no_mtbi <- mtbi_ext_sol_df_s2 |> dplyr::select(-dplyr::contains("mtbi"))
mtbi_ext_sol_df_s3_no_mtbi <- mtbi_ext_sol_df_s3 |> dplyr::select(-dplyr::contains("mtbi"))
mtbi_ext_sol_df_s4_no_mtbi <- mtbi_ext_sol_df_s4 |> dplyr::select(-dplyr::contains("mtbi"))
mtbi_ext_sol_df_s5_no_mtbi <- mtbi_ext_sol_df_s5 |> dplyr::select(-dplyr::contains("mtbi"))

mtbi_ext_sol_df <- do.call(
    "rbind",
    c(
        list(
            mtbi_ext_sol_df_s1_no_mtbi,
            mtbi_ext_sol_df_s2_no_mtbi,
            mtbi_ext_sol_df_s3_no_mtbi,
            mtbi_ext_sol_df_s4_no_mtbi,
            mtbi_ext_sol_df_s5_no_mtbi,
            mtbi_ext_sol_df_p1,
            mtbi_ext_sol_df_p2,
            mtbi_ext_sol_df_p3,
            mtbi_ext_sol_df_p4,
            mtbi_ext_sol_df_p5
        ),
        list(reset_indices = TRUE)
    )
)

mtbi_ext_sol_df   

saveRDS(mtbi_ext_sol_df, proc_path("mtbi_ext_sol_df.rds", TRUE))
```

```{r}
# CHECKPOINT
mtbi_ext_sol_df <- readRDS(proc_path("2025_02_11_mtbi_ext_sol_df.rds"))
```

## Identifying and visualizing meta clusters

```{r}
base_ari_hm <- meta_cluster_heatmap(
    mtbi_ari,
    order = mtbi_ari_order
)

shiny_annotator(base_ari_hm)

mtbi_split_vec <- c(
    167,
    225,
    390,
    487,
    635,
    821,
    960,
    1234,
    1626,
    1848
)

write_csv(data.frame(mtbi_split_vec), proc_path("mtbi_split_vec.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_split_vec <- read_csv(proc_path("2025_02_10_mtbi_split_vec.csv")) |>
    unlist() |>
    as.numeric()
```

```{r}
divergent_colours <- function(column)  {
    values <- unique(column)
    colours <- RColorBrewer::brewer.pal(n = length(values), name = "Set3")
    names(colours) <- values
    return(colours)
}

mtbi_esdf <- as.data.frame(mtbi_ext_sol_df)

mtbi_esdf$"impairment_separation" <- -log10(mtbi_esdf$"mean_pval")

mtbi_esdf$"pooled" <- c(rep("no", 1000), rep("yes", 1000))

mtbi_esdf$"imputation" <- c(
    rep("s1", 200),
    rep("s2", 200),
    rep("s3", 200),
    rep("s4", 200),
    rep("s5", 200),
    rep("p1", 200),
    rep("p2", 200),
    rep("p3", 200),
    rep("p4", 200),
    rep("p5", 200)
)
write_csv(mtbi_esdf, proc_path("mtbi_esdf.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_esdf <- read_csv(proc_path("2025_02_10_mtbi_esdf.csv"))
```

```{r}
full_mtbi_ari_hm <- meta_cluster_heatmap(
    aris = mtbi_ari,
    order = mtbi_ari_order,
    data = mtbi_esdf,
    min_colour = "black",
    split_vector = mtbi_split_vec,
    top_hm = list(
        "Impairment Separation" = "impairment_separation"
    ),
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    left_hm = list(
        "Pooled" = "pooled",
        "Imputation" = "imputation"
    ),
    annotation_colours = list(
        "Impairment Separation" = colour_scale(
            mtbi_esdf$"impairment_separation",
            min_colour = "gray7",
            max_colour = "limegreen"
        ),
        "Imputation" = divergent_colours(mtbi_esdf$"imputation"),
        "Pooled" = c(
            "yes" = "orange",
            "no" = "purple"
        )
    )
)
full_mtbi_ari_hm

save_heatmap(
    heatmap = full_mtbi_ari_hm,
    path = fig_path("full_mtbi_ari_hm.png", TRUE),
    width = 950,
    height = 900,
    res = 100
)

# Another heatmap without the imputation-related columns
lite_mtbi_ari_hm <- meta_cluster_heatmap(
    aris = mtbi_ari,
    order = mtbi_ari_order,
    data = mtbi_esdf,
    min_colour = "black",
    split_vector = mtbi_split_vec,
    top_hm = list(
        "Impairment Separation" = "impairment_separation"
    ),
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    annotation_colours = list(
        "Impairment Separation" = colour_scale(
            mtbi_esdf$"impairment_separation",
            min_colour = "gray7",
            max_colour = "limegreen"
        )
    )
)
lite_mtbi_ari_hm

save_heatmap(
    heatmap = lite_mtbi_ari_hm,
    path = fig_path("lite_mtbi_ari_hm.png", TRUE),
    width = 900,
    height = 700,
    res = 100
)
```

```{r}
mtbi_mc_sol_df <- label_meta_clusters(
    mtbi_ext_sol_df,
    order = mtbi_ari_order,
    split_vector = mtbi_split_vec
)

saveRDS(mtbi_mc_sol_df, proc_path("mtbi_mc_sol_df.rds", TRUE))
```

```{r}
# CHECKPOINT
mtbi_mc_sol_df <- readRDS(proc_path("2025_02_11_mtbi_mc_sol_df.rds"))

e_pvals <- mtbi_mc_sol_df |>
    dplyr::filter(mc == "E") |>
    as.data.frame() |>
    dplyr::select(mean_pval) |>
    unlist() |>
    as.numeric()

length(e_pvals)

mean(-log10(e_pvals) > 4)

```

When picking out representative solutions, I'd like to preferentially go for solutions that derived from solo rather than pooled imputations, as those solutions have values for all features.

```{r}
# Function to try to lean on mTBI-including solutions when possible.
# This function will pick from solo solutions unless over 70% of the meta
# cluster is pooled.
restrict_fn <- function(x, threshold = 0.3) {
    x_solo_ind <- x$"solution" %in% 1:1000
    x_pool_ind <- x$"solution" %in% 1001:2000
    x_solo <- x[x_solo_ind, ]
    x_pool <- x[x_pool_ind, ]
    frac_solo <- nrow(x_solo) / (nrow(x_solo) + nrow(x_pool))
    if (frac_solo < threshold) {
        return(x[x_pool_ind, ])
    } else {
        return(x[x_solo_ind, ])
    }
}

mtbi_rep_solutions <- get_representative_solutions(
    mtbi_ari,
    mtbi_mc_sol_df,
    filter_fn = restrict_fn
)

saveRDS(mtbi_rep_solutions, proc_path("mtbi_rep_solutions.rds", TRUE))
```

```{r}
mtbi_rep_solutions <- readRDS(proc_path("2025_02_11_mtbi_rep_solutions.rds"))

mtbi_rep_solutions

# Top solution is meta cluster F, represented by solution 576
mtbi_top_solution <- mtbi_ext_sol_df_s3[mtbi_ext_sol_df_s3$"solution" == 576, ]

mtbi_top_solution$"mc" <- "F"

saveRDS(mtbi_top_solution, proc_path("mtbi_top_solution.rds", TRUE))
```

```{r}
# CHECKPOINT
mtbi_top_solution <- readRDS(proc_path("2025_02_11_mtbi_top_solution.rds"))

# Note that MC E came from imputation s3 (401:600 range) and MC F came from
#  imputation p2 (1201:1400 range).
mtbi_manhattan <- mc_manhattan_plot(
    mtbi_top_solution,
    dl = all_dls$"mtbi_train_data_lists"$"imp_3",
    target_dl = all_dls$"mtbi_train_oom_lists"$"imp_3",
    domain_colours = c(
        "AS" = "#85929e",
        "D" = "#bb8fce",
        "N" = "#e59866",
        "MH" = "#7fb3d5",
        "P" = "#52be80",
        "S" = "#d98880",
        "B" = "#ff3131"
    )
)
mtbi_manhattan

ggsave(
    plot = mtbi_manhattan,
    filename = fig_path("mtbi_manhattan.png", TRUE),
    width = 18,
    height = 5,
    dpi = 120
)
```

```{r}
# In anticipation of the upcoming cluster swaps
cluster_label_swap <- function(solutions_matrix, c_a, c_b) {
    swapped_sm <- dplyr::mutate(
        solutions_matrix,
        across(
            dplyr::starts_with("uid"),
            ~ ifelse(
                . == c_a,
                c_b,
                ifelse(
                    . == c_b,
                    c_a,
                    .
                )
            )
        )
    )
    return(swapped_sm)
}

mtbi_top_solution_swp <- cluster_label_swap(mtbi_top_solution, 2, 3)

saveRDS(mtbi_top_solution_swp, proc_path("mtbi_top_solution_swp.rds", TRUE))
```

```{r}
# CHECKPOINT
mtbi_top_solution_swp <- readRDS(proc_path("2025_02_12_mtbi_top_solution_swp.rds"))
```

## Feature importance

### NMI

```{r}
nmis <- calc_nmis(
    all_dls$"mtbi_train_data_lists"$"imp_3",
    mtbi_top_solution_swp,
    verbose = TRUE
)

nmi_order <- sort(
    nmis$"s576",
    decreasing = TRUE,
    index.return = TRUE
)

ordered_nmis <- nmis[nmi_order$ix, ]

ordered_nmis$"nmi_rank" <- rank(
    -ordered_nmis$"s576",
    ties.method = "min"
)
```


### p-values


```{r}
pvals <- get_pvals(
    mtbi_top_solution_swp,
    keep_summaries = FALSE
)
pvals <- data.frame(
    "feature" = gsub("_pval", "", names(pvals)),
    "neg_log_pval" = -log10(as.numeric(unlist(pvals)))
)
pvals <- pvals[-1, ]
pvals_order <- sort(
    pvals$"neg_log_pval",
    decreasing = TRUE,
    index.return = TRUE
)
ordered_pvals <- pvals[pvals_order$ix, ]
ordered_pvals <- dplyr::filter(
    ordered_pvals,
    !grepl("^cbcl|^sds", feature)
)
ordered_pvals$"pval_rank" <- rank(
    -ordered_pvals$"neg_log_pval",
    ties.method = "min"
)
```


### Joint rank


```{r}
mtbi_top_solution_nmi_v_pval <- dplyr::full_join(
    ordered_nmis,
    ordered_pvals,
    by = "feature"
)

domain_df <- all_dls$"mtbi_train_data_lists"$"imp_3" |>
    summary("feature") |>
    dplyr::select(name, domain) |>
    dplyr::rename("feature" = "name")

domain_df

mtbi_top_solution_nmi_v_pval <- mtbi_top_solution_nmi_v_pval |>
    dplyr::inner_join(domain_df, by = "feature")

mtbi_top_solution_nmi_v_pval$"joint_rank" <- rank(
    mtbi_top_solution_nmi_v_pval$"nmi_rank" + mtbi_top_solution_nmi_v_pval$"pval_rank",
    ties.method = "min"
)

joint_order <- sort(
    mtbi_top_solution_nmi_v_pval$"joint_rank",
    decreasing = FALSE,
    index.return = TRUE
)

mtbi_top_solution_nmi_v_pval_rank <- mtbi_top_solution_nmi_v_pval[joint_order$ix, ]

mtbi_top_solution_nmi_v_pval_rank <- mtbi_top_solution_nmi_v_pval_rank |>
    dplyr::rename("nmi" = "s576")

mtbi_top_solution_nmi_v_pval_rank <- mtbi_top_solution_nmi_v_pval_rank |>
    dplyr::select(
        feature,
        domain,
        nmi,
        nmi_rank,
        neg_log_pval,
        pval_rank,
        joint_rank
    )

write_csv(
    mtbi_top_solution_nmi_v_pval_rank,
    proc_path("mtbi_top_solution_nmi_v_pval_rank.csv", TRUE)
)

options(width=200)
data.frame(mtbi_top_solution_nmi_v_pval_rank)

# Latex table
xtable(data.frame(mtbi_top_solution_nmi_v_pval_rank))
```

```{r}
# CHECKPOINT
mtbi_top_solution_nmi_v_pval_rank <- read_csv(
    proc_path("2025_02_12_mtbi_top_solution_nmi_v_pval_rank.csv")
)

mtbi_top_solution_nmi_v_pval_rank

mtbi_top_solution_nmi_v_pval_rank |>
    dplyr::select(joint_rank, dplyr::everything()) |>
    dplyr::select(-nmi_rank, -pval_rank) |>
    knitr::kable(format = "markdown", digits = 4) |>
    writeLines(proc_path("mtbi_top_solution_input_ranks.txt", TRUE)) # 2025-02-12

outputs <- summary(
    all_dls$"mtbi_train_oom_lists"$"imp_3",
    scope = "feature"
) |>
    dplyr::select(name) |>
    unlist() |>
    as.character()

sorted_inputs <- mtbi_top_solution_nmi_v_pval_rank$"feature"
sorted_in_and_out <- c(sorted_inputs, outputs)

saveRDS(sorted_inputs, proc_path("sorted_inputs.rds", TRUE))
saveRDS(sorted_in_and_out, proc_path("sorted_in_and_out.rds", TRUE))
saveRDS(outputs, proc_path("outputs.rds", TRUE))
```

```{r}
# CHECKPOINT
sorted_inputs <- readRDS(proc_path("2025_02_12_sorted_inputs.rds"))
sorted_in_and_out <- readRDS(proc_path("2025_02_12_sorted_in_and_out.rds"))
outputs <- readRDS(proc_path("2025_02_13_outputs.rds"))

data.frame(
    Rank = 1:length(sorted_inputs),
    Feature = sorted_inputs
)

```

### Correlation of NMI and p-value

```{r}
nmi_v_p_rho <- cor(
    mtbi_top_solution_nmi_v_pval_rank$"nmi_rank",
    mtbi_top_solution_nmi_v_pval_rank$"pval_rank",
    method = "spearman"
)

nmi_v_pval_plot <- mtbi_top_solution_nmi_v_pval_rank |>
    ggplot(
        aes(x = nmi_rank, y = pval_rank, label = feature, colour = domain)
    ) +
    geom_point(size = 2) + 
    scale_colour_manual(
        values = c(
            "AS" = "#85929e",
            "D" = "#bb8fce",
            "N" = "#e59866",
            "MH" = "#7fb3d5",
            "P" = "#52be80"
        )
    ) +
    theme_bw() +
    labs(x = "Rank by NMI", y = "Rank by Association p-value") +
    ggrepel::geom_text_repel(
        force = 1,
        max.overlaps = 35,
        size = 4
    ) +
    annotate(
        "text",
        x = 4,
        y = 50,
        size = 5,
        label = paste("Spearman's ρ =", round(nmi_v_p_rho, 2)),
        hjust = 0
    ) + 
    theme(text = element_text(size = 20))
nmi_v_pval_plot

ggsave(
    fig_path("nmi_v_pval_plot.png", TRUE),
    nmi_v_pval_plot,
    width = 14,
    height = 12
)
```

```{r}
# Feature plot generation
plot_list <- auto_plot(
    sol_df_row = mtbi_top_solution_swp,
    dl = c(
        all_dls$"mtbi_train_data_lists"$"imp_3",
        all_dls$"mtbi_train_oom_lists"$"imp_3"
    ),
    save = fig_path("ap_mtbi_mc_f", TRUE),
    verbose = TRUE
)

# No save version:
plot_list <- auto_plot(
    sol_df_row = mtbi_top_solution_swp,
    dl = c(
        all_dls$"mtbi_train_data_lists"$"imp_3",
        all_dls$"mtbi_train_oom_lists"$"imp_3"
    ),
    verbose = TRUE
)

saveRDS(plot_list, fig_path("ap_mtbi_mc_f_plot_list.rds", TRUE))
```

```{r}
# CHECKPOINT
plot_list <- readRDS(fig_path("2025_02_12_ap_mtbi_mc_f_plot_list.rds"))
```


### Visualizing top features

Ranked plots

```{r}
ranked_plot_list <- plot_list[sorted_in_and_out]

ranked_plot_list[[1]]

ranked_plots <- wrap_plots(ranked_plot_list)

ggsave(
    fig_path("mtbi_top_solution_ranked_plots.png", TRUE),
    ranked_plots,
    width = 45,
    height = 30,
    dpi = 50
)
```

```{r}
################################################################################
## Building the top 12 plot list
################################################################################
top_pl <- ranked_plot_list[1:12]

for (i in names(top_pl)) {
    print(i)
}

top_pl$"sex" <- top_pl$"sex" + labs(fill = "Sex") + scale_fill_discrete(labels = c("F", "M"))
top_pl$"brain_volume" <- top_pl$"brain_volume" + labs(y = expression(paste("Brain Volume ", (mm^3))))
top_pl$"cortical_sa" <- top_pl$"cortical_sa" + labs(y = expression(paste("Cortical Area ", (mm^2))))
top_pl$"household_income" <- top_pl$"household_income" + labs(y = "Household Income")
top_pl$"pubertal_status_p" <- top_pl$"pubertal_status_p" + labs(y = "Pubertal Status - P")
top_pl$"race" <- top_pl$"race" + labs(fill = "Race") + scale_fill_discrete(labels = c("Black", "Hispanic", "Other", "White"))
top_pl$"activities_last_year" <- top_pl$"activities_last_year" + labs(y = "Total Activities this Year")
top_pl$"private_instruction" <- top_pl$"private_instruction" + labs(y = "Private Activities")
top_pl$"extracurriculars" <- top_pl$"extracurriculars" + labs(y = "Lifetime Extracurriculars")
top_pl$"parent_thought" <- top_pl$"parent_thought" + labs(y = "Parent Thought Problems")
top_pl$"weekday_screentime" <- top_pl$"weekday_screentime" + labs(y = "Weekday Screentime")
top_pl$"parent_somatic" <- top_pl$"parent_somatic" + labs(y = "Parent Somatic Problems")

top_p <- wrap_plots(top_pl) & labs(x = "Cluster") & theme(plot.margin = unit(c(0.5, 1.5, 0.5, 2), "cm"))

ggsave(
    fig_path("mtbi_top_solution_input_plots_12.png", TRUE),
    top_p,
    width = 25,
    height = 15,
    dpi = 150
)
```

```{r}
# Plot-related DF -------------------------------------------------------------
mtbi_top_solution_plot_df <- auto_plot(
    sol_df_row = mtbi_top_solution_swp,
    dl = c(
        all_dls$"mtbi_train_data_lists"$"imp_3",
        all_dls$"mtbi_train_oom_lists"$"imp_3"
    ),
    return_plots = FALSE
)

saveRDS(mtbi_top_solution_plot_df, proc_path("mtbi_top_solution_plot_df.rds", TRUE))
```

```{r}
# CHECKPOINT
mtbi_top_solution_plot_df <- readRDS(proc_path("2025_02_12_mtbi_top_solution_plot_df.rds"))
```

```{r}
outcome_plot_list <- ranked_plot_list[68:76]

outcome_plot_list

clean_names <- c(
    "CBCL\nAnxious-Depressed",
    "CBCL\nWithdrawn-Depressed",
    "CBCL\nSomatic Problems",
    "CBCL\nSocial Problems",
    "CBCL\nThought Problems",
    "CBCL\nAttention Problems",
    "CBCL\nRule-breaking Problems",
    "CBCL\nAggression Problems",
    "SDS Total\nSleeping Problems"
)

for (i in seq_along(outcome_plot_list)) {
    outcome_plot_list[[i]] <- outcome_plot_list[[i]] +
        labs(y = clean_names[[i]], x = "Cluster")
}

outcome_plot_wrap <- wrap_plots(outcome_plot_list) &
    theme(plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), "cm"))

ggsave(
    fig_path("mtbi_top_solution_outcome_plots.png", TRUE),
    outcome_plot_wrap,
    width = 14,
    height = 14,
    dpi = 150
)
```

# Validation

```{r}
# CHECKPOINT
# The data list that generated the top solution
train_data_list_s3 <- all_dls$"mtbi_train_data_lists"$"imp_3"
train_oom_list_s3 <- all_dls$"mtbi_train_oom_lists"$"imp_3"

# The first test data set, for example
test_data_list_s1 <- all_dls$"mtbi_test_data_lists"$"imp_1"
test_data_list_s2 <- all_dls$"mtbi_test_data_lists"$"imp_2"
test_data_list_s3 <- all_dls$"mtbi_test_data_lists"$"imp_3"
test_data_list_s4 <- all_dls$"mtbi_test_data_lists"$"imp_4"
test_data_list_s5 <- all_dls$"mtbi_test_data_lists"$"imp_5"

test_oom_list_s1 <- all_dls$"mtbi_test_oom_lists"$"imp_1"
test_oom_list_s2 <- all_dls$"mtbi_test_oom_lists"$"imp_2"
test_oom_list_s3 <- all_dls$"mtbi_test_oom_lists"$"imp_3"
test_oom_list_s4 <- all_dls$"mtbi_test_oom_lists"$"imp_4"
test_oom_list_s5 <- all_dls$"mtbi_test_oom_lists"$"imp_5"
```

```{r}
full_data_list_1 <- merge(train_data_list_s3, test_data_list_s1)
full_data_list_2 <- merge(train_data_list_s3, test_data_list_s2)
full_data_list_3 <- merge(train_data_list_s3, test_data_list_s3)
full_data_list_4 <- merge(train_data_list_s3, test_data_list_s4)
full_data_list_5 <- merge(train_data_list_s3, test_data_list_s5)

full_oom_list_1 <- merge(train_oom_list_s3, test_oom_list_s1)
full_oom_list_2 <- merge(train_oom_list_s3, test_oom_list_s2)
full_oom_list_3 <- merge(train_oom_list_s3, test_oom_list_s3)
full_oom_list_4 <- merge(train_oom_list_s3, test_oom_list_s4)
full_oom_list_5 <- merge(train_oom_list_s3, test_oom_list_s5)

saveRDS(full_data_list_1, input_path("mtbi_full_data_list_1.rds", TRUE))
saveRDS(full_data_list_2, input_path("mtbi_full_data_list_2.rds", TRUE))
saveRDS(full_data_list_3, input_path("mtbi_full_data_list_3.rds", TRUE))
saveRDS(full_data_list_4, input_path("mtbi_full_data_list_4.rds", TRUE))
saveRDS(full_data_list_5, input_path("mtbi_full_data_list_5.rds", TRUE))

saveRDS(full_oom_list_1, input_path("mtbi_full_oom_list_1.rds", TRUE))
saveRDS(full_oom_list_2, input_path("mtbi_full_oom_list_2.rds", TRUE))
saveRDS(full_oom_list_3, input_path("mtbi_full_oom_list_3.rds", TRUE))
saveRDS(full_oom_list_4, input_path("mtbi_full_oom_list_4.rds", TRUE))
saveRDS(full_oom_list_5, input_path("mtbi_full_oom_list_5.rds", TRUE))
```

```{r}
# CHECKPOINT
full_data_list_1 <- readRDS(input_path("2025_02_12_mtbi_full_data_list_1.rds"))
full_data_list_2 <- readRDS(input_path("2025_02_12_mtbi_full_data_list_2.rds"))
full_data_list_3 <- readRDS(input_path("2025_02_12_mtbi_full_data_list_3.rds"))
full_data_list_4 <- readRDS(input_path("2025_02_12_mtbi_full_data_list_4.rds"))
full_data_list_5 <- readRDS(input_path("2025_02_12_mtbi_full_data_list_5.rds"))

full_oom_list_1 <- readRDS(input_path("2025_02_12_mtbi_full_oom_list_1.rds"))
full_oom_list_2 <- readRDS(input_path("2025_02_12_mtbi_full_oom_list_2.rds"))
full_oom_list_3 <- readRDS(input_path("2025_02_12_mtbi_full_oom_list_3.rds"))
full_oom_list_4 <- readRDS(input_path("2025_02_12_mtbi_full_oom_list_4.rds"))
full_oom_list_5 <- readRDS(input_path("2025_02_12_mtbi_full_oom_list_5.rds"))
```

```{r}
mtbi_config <- readRDS(proc_path("2025_02_10_mtbi_config.rds"))

mtbi_full_sol_df <- batch_snf(
    dl = full_data_list_1,
    sc = mtbi_config,
    processes = "max"
)
saveRDS(mtbi_full_sol_df, proc_path("mtbi_full_sol_df.rds", TRUE))

mtbi_full_sol_df <- readRDS(proc_path("2025_02_12_mtbi_full_sol_df.rds"))

mtbi_full_sol_df

mtbi_full_ext_sol_df <- extend_solutions(
    mtbi_full_sol_df,
    dl = full_data_list_1,
    target_dl = full_oom_list_1,
    min_pval = 1e-10,
    processes = "max"
)
#mtbi_full_esm$"impairment_separation" <- -log10(mtbi_full_esm$"mean_pval")
saveRDS(mtbi_full_ext_sol_df, proc_path("mtbi_full_ext_sol_df.rds", TRUE))
```

```{r}
# CHECKPOINT
mtbi_full_ext_sol_df <- readRDS(proc_path("2025_02_12_mtbi_full_ext_sol_df.rds"))
```

What does the full 3-cluster solution look like?

```{r}
# The full solutions with 3 clusters that have big outcome separation
mtbi_full_ext_sol_df_3c <- mtbi_full_ext_sol_df |>
    dplyr::filter(
        nclust == 3,
        -log10(mean_pval) > 4
    )
mtbi_full_ext_sol_df_3c_ari <- calc_aris(mtbi_full_ext_sol_df_3c)
full_3c_ari_order <- get_matrix_order(mtbi_full_ext_sol_df_3c_ari)
mtbi_full_split_vec <- c(2, 4, 8, 16, 20)

mtbi_full_ext_sol_df_3c_ari_hm <- meta_cluster_heatmap(
    mtbi_full_ext_sol_df_3c_ari,
    split_vector = mtbi_full_split_vec,
    order = full_3c_ari_order
)

save_heatmap(
    heatmap = mtbi_full_ext_sol_df_3c_ari_hm,
    path = fig_path("full_mtbi_full_ari_hm.png", TRUE),
    width = 950,
    height = 900,
    res = 100
)

mtbi_full_mc_sol_df_3c <- label_meta_clusters(
    mtbi_full_ext_sol_df_3c,
    order = full_3c_ari_order,
    split_vector = mtbi_full_split_vec
)

saveRDS(mtbi_full_mc_sol_df_3c, proc_path("mtbi_full_mc_sol_df_3c.rds", TRUE))
mtbi_full_mc_sol_df_3c <- readRDS(proc_path("2025_02_12_mtbi_full_mc_sol_df_3c.rds"))

mtbi_full_mc_3c_rep_solutions <- get_representative_solutions(
    mtbi_full_ext_sol_df_3c_ari,
    mtbi_full_mc_sol_df_3c
)

saveRDS(mtbi_full_mc_3c_rep_solutions, proc_path("mtbi_full_mc_3c_rep_solutions.rds", TRUE))
mtbi_full_mc_3c_rep_solutions <- readRDS(proc_path("2025_02_12_mtbi_full_mc_3c_rep_solutions.rds"))

mtbi_full_3c_manhattan <- mc_manhattan_plot(
    mtbi_full_mc_3c_rep_solutions,
    dl = full_data_list_1,
    target_dl = full_oom_list_1,
    domain_colours = c(
        "AS" = "#85929e",
        "D" = "#bb8fce",
        "N" = "#e59866",
        "MH" = "#7fb3d5",
        "P" = "#52be80",
        "S" = "#d98880",
        "B" = "#ff3131"
    )
)

mtbi_full_3c_manhattan

ggsave(
    plot = mtbi_full_3c_manhattan,
    filename = fig_path("mtbi_full_3c_manhattan.png", TRUE),
    width = 18,
    height = 14,
    dpi = 120
)

for (i in seq_along(sorted_inputs)) {
    cat(i, ": ", sorted_inputs[i], "\n", sep = "")
}

mtbi_full_mc_3c_rep_solutions

for (i in seq_len(nrow(mtbi_full_mc_3c_rep_solutions))) {
    print(i)
    current_row <- mtbi_full_mc_3c_rep_solutions[i, ]
    if (i %in% c(1, 3, 4)) {
        current_row <- cluster_label_swap(current_row, 2, 3)
    }
    if (i == 2) {
        current_row <- cluster_label_swap(current_row, 1, 3)
        current_row <- cluster_label_swap(current_row, 2, 3)
    }
    plot_list <- auto_plot(
        current_row,
        dl = c(full_data_list_1, full_oom_list_1)
    )
    plot_list <- plot_list[sorted_in_and_out]
    full_mc_3c_rep_solutions_plot <- wrap_plots(plot_list)
    ggsave(
        fig_path(paste0("mtbi_full_mc_3c_rep_solutions_all_plots_", i, ".png"), TRUE),
        full_mc_3c_rep_solutions_plot,
        width = 45,
        height = 30,
        dpi = 50
    )
}

# The first one (MC E) is very similar to the derivation set version
mtbi_full_top_3c <- mtbi_full_mc_3c_rep_solutions[1, ]
mtbi_full_top_3c <- cluster_label_swap(mtbi_full_top_3c, 2, 3)
mtbi_full_top_3c$"mc" <- "Full"

saveRDS(mtbi_full_top_3c, proc_path("mtbi_full_top_3c.rds", TRUE))
```

```{r}
# CHECKPOINT
mtbi_full_top_3c <- readRDS(proc_path("2025_02_13_mtbi_full_top_3c.rds"))
```

```{r}
mtbi_full_top_3c_manhattan <- mc_manhattan_plot(
    mtbi_full_top_3c,
    dl = full_data_list_1,
    target_dl = full_oom_list_1,
    domain_colours = c(
        "AS" = "#85929e",
        "D" = "#bb8fce",
        "N" = "#e59866",
        "MH" = "#7fb3d5",
        "P" = "#52be80",
        "S" = "#d98880",
        "B" = "#ff3131"
    )
)

mtbi_full_top_3c_manhattan

# Last run on February 13th, 2025
ggsave(
    plot = mtbi_full_top_3c_manhattan,
    filename = fig_path("mtbi_full_top_3c_manhattan.png", TRUE),
    width = 18,
    height = 5,
    dpi = 120
)

mtbi_der_plot_list <- readRDS(fig_path("2025_02_12_ap_mtbi_mc_f_plot_list.rds"))

mtbi_ful_plot_list <- auto_plot(
    mtbi_full_top_3c,
    dl = c(full_data_list_1, full_oom_list_1)
)

val_cluster_df <- mtbi_full_top_3c |>
    t() |>
    dplyr::filter(
        uid %in% paste0("uid_", mtbi_test_subs$"subjectkey")
    )

mtbi_val_plot_list <- auto_plot(
    cluster_df = val_cluster_df,
    dl = c(test_data_list_s1, test_oom_list_s1)
)

mtbi_val_plot_list$"mtbi_mechanism"[[1]]$"keycol" <- factor(
    mtbi_val_plot_list$"mtbi_mechanism"[[1]]$"keycol",
    levels = c("fall_hit", "hosp_er", "multi", "other_loc", "vehicle", "violent")
)

bar_colors <- scales::hue_pal()(6)
names(bar_colors) <- c("fall_hit", "hosp_er", "multi", "other_loc", "vehicle", "violent")

mtbi_val_plot_list$"mtbi_mechanism" <- mtbi_val_plot_list$"mtbi_mechanism" +
    scale_fill_manual(values = bar_colors, drop = FALSE)

saveRDS(mtbi_der_plot_list, proc_path("mtbi_der_plot_list.rds", TRUE))
saveRDS(mtbi_val_plot_list, proc_path("mtbi_val_plot_list.rds", TRUE))
saveRDS(mtbi_ful_plot_list, proc_path("mtbi_ful_plot_list.rds", TRUE))
```

```{r}
# CHECKPOINT
mtbi_der_plot_list <- readRDS(proc_path("2025_02_13_mtbi_der_plot_list.rds"))
mtbi_val_plot_list <- readRDS(proc_path("2025_02_13_mtbi_val_plot_list.rds"))
mtbi_ful_plot_list <- readRDS(proc_path("2025_02_13_mtbi_ful_plot_list.rds"))
```

How are all the test features distributed?
How are all the features distributed?

I'd like to have a table along the lines of,

| DERIVATION | IN DERIVATION + VALIDATION | IN VALIDATION |
C1 max F | True | Almost  true|

Something like that, which will require a side-by-side comparison of these features through visual inspection and through the topologizer function in the supplementary section for those who wish to look at the crunched numbers.

Up to 3 should be sufficient for determining which attributes should play a key role in validating the subsequent investigations.

```{r}
#outcome_idx <- !names(mtbi_full_plot_list) %in% sorted_features
#outcome_features <- names(mtbi_full_plot_list)[outcome_idx]

# Full input feature plots
pli_sort_d <- mtbi_der_plot_list[sorted_inputs]
pli_sort_v <- mtbi_val_plot_list[sorted_inputs]
pli_sort_f <- mtbi_ful_plot_list[sorted_inputs]

plo_d <- mtbi_der_plot_list[outputs]
plo_v <- mtbi_val_plot_list[outputs]
plo_f <- mtbi_ful_plot_list[outputs]

# Manually assemble plots
input_plots <- list(pli_sort_d, pli_sort_v, pli_sort_f)
outcome_plots <- list(plo_d, plo_v, plo_f)

list.save(input_plots, proc_path("input_tri_plots.rds", TRUE))
list.save(outcome_plots, proc_path("outcome_tri_plots.rds", TRUE))
```

```{r}
# CHECKPOINT
input_plots <- list.load(proc_path("2025_02_13_input_tri_plots.rds"))
outcome_plots <- list.load(proc_path("2025_02_13_outcome_tri_plots.rds"))
```

```{r}
# image export helper function
quick_save <- function(plot, path, w = 12, h = 4) {
    path <- paste0("mtbi_dvf_", path, ".png")
    ggsave(fig_path(path, TRUE), plot, width = w, height = h)
}

# tri-plot helper function
tri_plot <- function(pl,
                     feature,
                     ft_name,
                     scale_fill_labels = NULL,
                     ylims = NULL) {
    ###########################################################################
    p1 <- pl[[1]][[feature]] +
        theme(
            legend.position = "none",
            axis.title.y = element_text(size = 16)
        )
    ###########################################################################
    p2 <- pl[[2]][[feature]] +
        theme(
            legend.position = "none",
            axis.title.y = element_blank()
        ) 
    ###########################################################################
    p3 <- pl[[3]][[feature]] +
        theme(
            axis.title.y = element_blank()
        )
    ###########################################################################
    if (class(pl[[3]][[feature]]$layers[[1]]$geom)[[1]] == "GeomBar") {
        p3 <- p3 + labs(fill = ft_name)
    } else {
        p1 <- p1 + labs(y = ft_name)
    }
    if (!is.null(scale_fill_labels)) {
        p3 <- p3 + scale_fill_discrete(labels = scale_fill_labels)
    }
    if (!is.null(ylims)) {
        p1 <- p1 + ylim(ylims[[1]], ylims[[2]])
        p2 <- p2 + ylim(ylims[[1]], ylims[[2]])
        p3 <- p3 + ylim(ylims[[1]], ylims[[2]])
    }
    ###########################################################################
    patch_plot <- list(p1, p2, p3)
    patch_plot <- lapply(
        patch_plot,
        function(x) {
            x <- x + labs(x = "Cluster") + theme(text = element_text(size = 16))
        }
    )
    names(patch_plot) <- c("derivation", "validation", "full")
    return(wrap_plots(patch_plot))
}

```

```{r}
# Not necessarily in ranked order:
brain_volume_plot <- tri_plot(input_plots, "brain_volume", expression("Brain Volume "(mm^3)), ylims = c(900000, 1650000)) #; brain_volume_plot; quick_save(brain_volume_plot, "brain_volume")
sex_plot <- tri_plot(input_plots, "sex", "Sex", c("F", "M")) #; sex_plot; quick_save(sex_plot, "sex")
household_income_plot <- tri_plot(input_plots, "household_income", "Household Income") #; household_income_plot; quick_save(household_income_plot, "household_income")
cort_sa_plot <- tri_plot(input_plots, "cortical_sa", expression("Cortical Surface Area "(mm^2)), ylims = c(140000, 260000)) #; cort_sa_plot; quick_save(cort_sa_plot, "cort_sa")
pubertal_status_p_plot <- tri_plot(input_plots, "pubertal_status_p", "Pubertal Status\n(Parent Report)") #; pubertal_status_p_plot; quick_save(pubertal_status_p_plot, "pubertal_status_p")
race_plot <- tri_plot(input_plots, "race", "Race", scale_fill_labels = c("Black", "Hispanic", "Other", "White")) #; race_plot; quick_save(race_plot, "race")
extracurriculars_plot <- tri_plot(input_plots, "extracurriculars", "Extracurriculars (Quartile)") #; extracurriculars_plot; quick_save(extracurriculars_plot, "extracurriculars")
activities_last_year_plot <- tri_plot(input_plots, "activities_last_year", "Programs Last Year (Quartile)") #; activities_last_year_plot; quick_save(activities_last_year_plot, "activities_last_year")
parent_somatic_plot <- tri_plot(input_plots, "parent_somatic", "Parent Somatic", ylims = c(-0.5, 25)) #; parent_somatic_plot; quick_save(parent_somatic_plot, "parent_somatic")
parent_thought_plot <- tri_plot(input_plots, "parent_thought", "Parent Thought", ylims = c(-0.5, 13.5)) #; parent_thought_plot; quick_save(parent_thought_plot, "parent_thought")
parent_antisocial_plot <- tri_plot(input_plots, "parent_antisocial", "Parent Antisocial", ylims = c(-0.5, 20)) #; parent_antisocial_plot; quick_save(parent_antisocial_plot, "parent_antisocial")
weekday_screentime_plot <- tri_plot(input_plots, "weekday_screentime", "Weekday Screentime (hours)", ylims = c(-0.5, 21)) #; weekday_screentime_plot; quick_save(weekday_screentime_plot, "weekday_screentime")
parent_withdrawn_plot <- tri_plot(input_plots, "parent_withdrawn", "Parent Withdrawn", ylims = c(-0.5, 17)) #; parent_withdrawn_plot; quick_save(parent_withdrawn_plot, "parent_withdrawn")
parent_aggressive_plot <- tri_plot(input_plots, "parent_aggressive", "Parent Aggressive", ylims = c(-0.5, 25)) #; parent_aggressive_plot; quick_save(parent_aggressive_plot, "parent_aggressive")
private_instruction_plot <- tri_plot(input_plots, "private_instruction", "Private Activities (Quartile)") #; private_instruction_plot; quick_save(private_instruction_plot, "private_instruction")
parent_depress_plot <- tri_plot(input_plots, "parent_depress", "Parent Depress", ylims = c(-0.5, 25)) #; parent_depress_plot; quick_save(parent_depress_plot, "parent_depress")
parent_anxdep_plot <- tri_plot(input_plots, "parent_anxdep", "Parent Anxious-Depressed", ylims = c(-0.5, 30)) #; parent_anxdep_plot; quick_save(parent_anxdep_plot, "parent_anxdep")
parent_anxdisord_plot <- tri_plot(input_plots, "parent_anxdisord", "Parent Anxious", ylims = c(-0.5, 13)) #; parent_anxdisord_plot; quick_save(parent_anxdisord_plot, "parent_anxdisord")
weekend_screentime_plot <- tri_plot(input_plots, "weekend_screentime", "Weekend Screentime (hours)", ylims = c(-0.5, 21)) #; weekend_screentime_plot; quick_save(weekend_screentime_plot, "weekend_screentime")
fmri_cort_subcort_cors_plot <- tri_plot(input_plots, "fmri_cort_subcort_cors", "fMRI Cort-Subcort Corrs", ylims = c(-0.15, 0.2)) #; fmri_cort_subcort_cors_plot; quick_save(fmri_cort_subcort_cors_plot, "fmri_cort_subcort_cors")
parent_avoidant_plot <- tri_plot(input_plots, "parent_avoidant", "Parent Avoidant", ylims = c(-0.5, 13)) #; parent_avoidant_plot; quick_save(parent_avoidant_plot, "parent_avoidant")
parent_hyperactive_plot <- tri_plot(input_plots, "parent_hyperactive", "Parent Hyperactive", ylims = c(-0.5, 12)) #; parent_hyperactive_plot; quick_save(parent_hyperactive_plot, "parent_hyperactive")
same_sex_close_friend_plot <- tri_plot(input_plots, "same_sex_close_friend", "Same-Sex Close Friends (Quartile)") #; same_sex_close_friend_plot; quick_save(same_sex_close_friend_plot, "same_sex_close_friend")
family_fight_p_plot <- tri_plot(input_plots, "family_fight_p", "Family Fights\n(Parent Report)", scale_fill_labels = c("No", "Yes")) #; family_fight_p_plot; quick_save(family_fight_p_plot, "family_fight_p")
parent_perstr_plot <- tri_plot(input_plots, "parent_perstr", "Parent Personal Strength") #; parent_perstr_plot; quick_save(parent_perstr_plot, "parent_perstr")
fmri_cort_cors_plot <- tri_plot(input_plots, "fmri_cort_cors", "fMRI Cort-Cort Corrs", ylims = c(-0.1, 0.16)) #; fmri_cort_cors_plot; quick_save(fmri_cort_cors_plot, "fmri_cort_cors")
family_outdo_p_plot <- tri_plot(input_plots, "family_outdo_p", "Family Outdo\n(Parent Report)", c("No", "Yes")) #; family_outdo_p_plot; quick_save(family_outdo_p_plot, "family_outdo_p")
parent_attention_plot <- tri_plot(input_plots, "parent_attention", "Parent Attention", ylims = c(-0.5, 25)) #; parent_attention_plot; quick_save(parent_attention_plot, "parent_attention")
parent_intrusive_plot <- tri_plot(input_plots, "parent_intrusive", "Parent Intrusive", ylims = c(-0.5, 12)) #; parent_intrusive_plot; quick_save(parent_intrusive_plot, "parent_intrusive")
physical_activity_plot <- tri_plot(input_plots, "physical_activity", "Physical Activity", ylims = c(0, 1.1)) #; physical_activity_plot; quick_save(physical_activity_plot, "physical_activity")
headache_history_plot <- tri_plot(input_plots, "headache_history", "Headache\nHistory", c("No", "Yes")) #; headache_history_plot; quick_save(headache_history_plot, "headache_history")
helps_hurt_p_plot <- tri_plot(input_plots, "helps_hurt_p", "Helps Hurt\n(Parent Report)", c("No", "Yes")) #; helps_hurt_p_plot; quick_save(helps_hurt_p_plot, "helps_hurt_p")
mtbi_loc_plot <- tri_plot(input_plots, "mtbi_loc", "mTBI LOC", c("No", "Yes")) #; mtbi_loc_plot; quick_save(mtbi_loc_plot, "mtbi_loc")
cortical_thickness_plot <- tri_plot(input_plots, "cortical_thickness", "Cortical Thickness (mm)", ylims = c(2.3, 3.1)) #; cortical_thickness_plot; quick_save(cortical_thickness_plot, "cortical_thickness")
school_activities_plot <- tri_plot(input_plots, "school_activities", "School Activities") #; school_activities_plot; quick_save(school_activities_plot, "school_activities")
helpful_y_plot <- tri_plot(input_plots, "helpful_y", "Helpful\n(Youth Report)", c("No", "Yes")) #; helpful_y_plot; quick_save(helpful_y_plot, "helpful_y")
family_peaceful_p_plot <- tri_plot(input_plots, "family_peaceful_p", "Family Peaceful\n(Parent Report)", c("No", "Yes")) #; family_peaceful_p_plot; quick_save(family_peaceful_p_plot, "family_peaceful_p")
mtbi_mem_daze_plot <- tri_plot(input_plots, "mtbi_mem_daze", "mTBI mem_daze", c("No", "Yes")) #; mtbi_mem_daze_plot; quick_save(mtbi_mem_daze_plot, "mtbi_mem_daze")
considerate_y_plot <- tri_plot(input_plots, "considerate_y", "Considerate\n(Youth Report)", c("No", "Yes")) #; considerate_y_plot; quick_save(considerate_y_plot, "considerate_y")
mtbi_mechanism_plot <- tri_plot(input_plots, "mtbi_mechanism", "mTBI Mechanism", c("Fall/Hit", "Hospital/ER", "Multiple Injuries", "Other", "Vehicle", "Violent")) #; mtbi_mechanism_plot; quick_save(mtbi_mechanism_plot, "mtbi_mechanism")
helps_hurt_y_plot <- tri_plot(input_plots, "helps_hurt_y", "Helps Hurt\n(Youth Report)", c("No", "Yes")) #; helps_hurt_y_plot; quick_save(helps_hurt_y_plot, "helps_hurt_y")
family_criticize_p_plot <- tri_plot(input_plots, "family_criticize_p", "Family Criticizes\n(Parent Report)", c("No", "Yes")) #; family_criticize_p_plot; quick_save(family_criticize_p_plot, "family_criticize_p")
major_wm_ndi_plot <- tri_plot(input_plots, "major_wm_ndi", "Major WM Neurite Density", ylims = c(0.45, 0.85)) #; major_wm_ndi_plot; quick_save(major_wm_ndi_plot, "major_wm_ndi")
family_temper_p_plot <- tri_plot(input_plots, "family_temper_p", "Family Temper\n(Parent Report)", scale_fill_labels = c("No", "Yes")) #; family_temper_p_plot; quick_save(family_temper_p_plot, "family_temper_p")
family_outdo_y_plot <- tri_plot(input_plots, "family_outdo_y", "Family Outdoing\n(Youth Report)", c("No", "Yes")) #; family_outdo_y_plot; quick_save(family_outdo_y_plot, "family_outdo_y")
family_criticize_y_plot <- tri_plot(input_plots, "family_criticize_y", "Family Criticizes\n(Youth Report)", c("No", "Yes")) #; family_criticize_y_plot; quick_save(family_criticize_y_plot, "family_criticize_y")
age_plot <- tri_plot(input_plots, "age", "Age") #; age_plot; quick_save(age_plot, "age")
pericortical_wm_ndi_plot <- tri_plot(input_plots, "pericortical_wm_ndi", "Pericortical WM Neurite Density", ylims = c(0.25, 0.6)) #; pericortical_wm_ndi_plot; quick_save(pericortical_wm_ndi_plot, "pericortical_wm_ndi")
same_sex_friend_plot <- tri_plot(input_plots, "same_sex_friend", "Same-Sex Friends\n(Quartile)") #; same_sex_friend_plot; quick_save(same_sex_friend_plot, "same_sex_friend")
family_angry_p_plot <- tri_plot(input_plots, "family_angry_p", "Family Angry\n(Parent Report)", c("No", "Yes")) #; family_angry_p_plot; quick_save(family_angry_p_plot, "family_angry_p")
mtbi_age_plot <- tri_plot(input_plots, "mtbi_age", "mTBI Age (months)") #; mtbi_age_plot; quick_save(mtbi_age_plot, "mtbi_age")
helpful_p_plot <- tri_plot(input_plots, "helpful_p", "Helpful\n(Parent Report)", c("No", "Yes")) #; helpful_p_plot; quick_save(helpful_p_plot, "helpful_p")
previous_mtbis_plot <- tri_plot(input_plots, "previous_mtbis", "Previous mTBIs") #; previous_mtbis_plot; quick_save(previous_mtbis_plot, "previous_mtbis")
family_angry_y_plot <- tri_plot(input_plots, "family_angry_y", "Family Angry\n(Youth Report)", c("No", "Yes")) #; family_angry_y_plot; quick_save(family_angry_y_plot, "family_angry_y")
family_throw_p_plot <- tri_plot(input_plots, "family_throw_p", "Family Throwing\n(Parent Report)", c("No", "Yes")) #; family_throw_p_plot; quick_save(family_throw_p_plot, "family_throw_p")
pubertal_status_y_plot <- tri_plot(input_plots, "pubertal_status_y", "Pubertal Status (Youth Report)") #; pubertal_status_y_plot; quick_save(pubertal_status_y_plot, "pubertal_status_y")
family_hit_p_plot <- tri_plot(input_plots, "family_hit_p", "Family Hitting\n(Parent Report)", c("No", "Yes")) #; family_hit_p_plot; quick_save(family_hit_p_plot, "family_hit_p")
family_yell_y_plot <- tri_plot(input_plots, "family_yell_y", "Family Yells\n(Youth Report)", c("No", "Yes")) #; family_yell_y_plot; quick_save(family_yell_y_plot, "family_yell_y")
family_peaceful_y_plot <- tri_plot(input_plots, "family_peaceful_y", "Family Peaceful\n(Youth Report)", c("No", "Yes")) #; family_peaceful_y_plot; quick_save(family_peaceful_y_plot, "family_peaceful_y")
family_throw_y_plot <- tri_plot(input_plots, "family_throw_y", "Family Throwing\n(Youth Report)", c("No", "Yes")) #; family_throw_y_plot; quick_save(family_throw_y_plot, "family_throw_y")
opp_sex_friend_plot <- tri_plot(input_plots, "opp_sex_friend", "Opposite-Sex Friends\n(Quartile)") #; opp_sex_friend_plot; quick_save(opp_sex_friend_plot, "opp_sex_friend")
family_fight_y_plot <- tri_plot(input_plots, "family_fight_y", "Family Fights\n(Youth Report)", c("No", "Yes")) #; family_fight_y_plot; quick_save(family_fight_y_plot, "family_fight_y")
opp_sex_close_friend_plot <- tri_plot(input_plots, "opp_sex_close_friend", "Opposite-Sex Close Friends\n(Quartile)") #; opp_sex_close_friend_plot; quick_save(opp_sex_close_friend_plot, "opp_sex_close_friend")
considerate_p_plot <- tri_plot(input_plots, "considerate_p", "Considerate\n(Parent Report)", c("No", "Yes")) #; considerate_p_plot; quick_save(considerate_p_plot, "considerate_p")
family_temper_y_plot <- tri_plot(input_plots, "family_temper_y", "Family Temper\n(Youth Report)", c("No", "Yes")) #; family_temper_y_plot; quick_save(family_temper_y_plot, "family_temper_y")
family_yell_p_plot <- tri_plot(input_plots, "family_yell_p", "Family Yells\n(Parent Report)", c("No", "Yes")) #; family_yell_p_plot; quick_save(family_yell_p_plot, "family_yell_p")
family_hit_y_plot <- tri_plot(input_plots, "family_hit_y", "Family Hitting\n(Youth Report)", c("No", "Yes")) #; family_hit_y_plot; quick_save(family_hit_y_plot, "family_hit_y")

# Outcome trip-plots
cbcl_anxdep_plot <- tri_plot(outcome_plots, "cbcl_anxdep", "Anxious-Depressed", ylims = c(-0.5, 30))
cbcl_withdep_plot <- tri_plot(outcome_plots, "cbcl_withdep", "Withdrawn-Depressed", ylims = c(-0.5, 15))
cbcl_somatic_plot <- tri_plot(outcome_plots, "cbcl_somatic", "Somatic Problems", ylims = c(-0.5, 17))
cbcl_social_plot <- tri_plot(outcome_plots, "cbcl_social", "Social Problems", ylims = c(-0.5, 20))
cbcl_thought_plot <- tri_plot(outcome_plots, "cbcl_thought", "Thought Problems", ylims = c(-0.5, 20))
cbcl_attention_plot <- tri_plot(outcome_plots, "cbcl_attention", "Attention Problems", ylims = c(-0.5, 22))
cbcl_rulebreak_plot <- tri_plot(outcome_plots, "cbcl_rulebreak", "Rule-Breaking Problems", ylims = c(-0.5, 22))
cbcl_aggressive_plot <- tri_plot(outcome_plots, "cbcl_aggressive", "Aggression Problems", ylims = c(-0.5, 32))
sds_sleep_plot <- tri_plot(outcome_plots, "sds_sleep", "Total Sleep Problems", ylims = c(20, 100))
```

```{r}
generalizing_plots <- list(
    "brain_volume" = brain_volume_plot,
    "sex" = sex_plot,
    "cortical_sa" = cort_sa_plot,
    "household_income" = household_income_plot,
    "pubertal_status_p" = pubertal_status_p_plot,
    "race" = race_plot,
    "activities_last_year" = activities_last_year_plot,
    "private_instruction" = private_instruction_plot,
    "extracurriculars" = extracurriculars_plot,
    "weekday_screentime" = weekday_screentime_plot,
    "parent_somatic" = parent_somatic_plot,
    "parent_thought" = parent_thought_plot,
    "parent_antisocial" = parent_antisocial_plot,
    "parent_withdrawn" = parent_withdrawn_plot,
    "parent_aggressive" = parent_aggressive_plot,
    "parent_depress" = parent_depress_plot,
    "parent_anxdep" = parent_anxdep_plot,
    "parent_anxdisord" = parent_anxdisord_plot,
    "weekend_screentime" = weekend_screentime_plot,
    "fmri_cort_subcort_cors" = fmri_cort_subcort_cors_plot,
    "parent_avoidant" = parent_avoidant_plot,
    "parent_hyperactive" = parent_hyperactive_plot,
    "same_sex_close_friend" = same_sex_close_friend_plot,
    "family_fight_p" = family_fight_p_plot,
    "parent_perstr" = parent_perstr_plot,
    "fmri_cort_cors" = fmri_cort_cors_plot,
    "family_outdo_p" = family_outdo_p_plot,
    "parent_attention" = parent_attention_plot,
    "parent_intrusive" = parent_intrusive_plot,
    "physical_activity" = physical_activity_plot,
    "headache_history" = headache_history_plot,
    "helps_hurt_p" = helps_hurt_p_plot,
    "mtbi_loc" = mtbi_loc_plot,
    "cortical_thickness" = cortical_thickness_plot,
    "school_activities" = school_activities_plot,
    "helpful_y" = helpful_y_plot,
    "family_peaceful_p" = family_peaceful_p_plot,
    "mtbi_mem_daze" = mtbi_mem_daze_plot,
    "considerate_y" = considerate_y_plot,
    "mtbi_mechanism" = mtbi_mechanism_plot,
    "helps_hurt_y" = helps_hurt_y_plot,
    "family_criticize_p" = family_criticize_p_plot,
    "major_wm_ndi" = major_wm_ndi_plot,
    "family_temper_p" = family_temper_p_plot,
    "family_outdo_y" = family_outdo_y_plot,
    "family_criticize_y" = family_criticize_y_plot,
    "age" = age_plot,
    "pericortical_wm_ndi" = pericortical_wm_ndi_plot,
    "same_sex_friend" = same_sex_friend_plot,
    "family_angry_p" = family_angry_p_plot,
    "mtbi_age" = mtbi_age_plot,
    "helpful_p" = helpful_p_plot,
    "previous_mtbis" = previous_mtbis_plot,
    "family_angry_y" = family_angry_y_plot,
    "family_throw_p" = family_throw_p_plot,
    "pubertal_status_y" = pubertal_status_y_plot,
    "family_hit_p" = family_hit_p_plot,
    "family_yell_y" = family_yell_y_plot,
    "family_peaceful_y" = family_peaceful_y_plot,
    "family_throw_y" = family_throw_y_plot,
    "opp_sex_friend" = opp_sex_friend_plot,
    "family_fight_y" = family_fight_y_plot,
    "opp_sex_close_friend" = opp_sex_close_friend_plot,
    "considerate_p" = considerate_p_plot,
    "family_temper_y" = family_temper_y_plot,
    "family_yell_p" = family_yell_p_plot,
    "family_hit_y" = family_hit_y_plot
)

generalizing_plots <- generalizing_plots[sorted_inputs]

generalizing_outcome_plots <- list(
    "cbcl_anxdep" = cbcl_anxdep_plot,
    "cbcl_withdep" = cbcl_withdep_plot,
    "cbcl_somatic" = cbcl_somatic_plot,
    "cbcl_social" = cbcl_social_plot,
    "cbcl_thought" = cbcl_thought_plot,
    "cbcl_attention" = cbcl_attention_plot,
    "cbcl_rulebreak" = cbcl_rulebreak_plot,
    "cbcl_aggressive" = cbcl_aggressive_plot,
    "sds_sleep" = sds_sleep_plot
)

generalizing_plots <- lapply(
    generalizing_plots,
    function(x) {
        x[[1]] <- x[[1]] + theme(axis.title.x = element_blank()) 
        x[[2]] <- x[[2]] + theme(axis.title.x = element_blank()) 
        x[[3]] <- x[[3]] + theme(axis.title.x = element_blank()) 
        return(x)
    }
)

generalizing_outcome_plots <- lapply(
    generalizing_outcome_plots,
    function(x) {
        x[[1]] <- x[[1]] + theme(axis.title.x = element_blank()) 
        x[[2]] <- x[[2]] + theme(axis.title.x = element_blank()) 
        x[[3]] <- x[[3]] + theme(axis.title.x = element_blank()) 
        return(x)
    }
)
```

```{r}
wp_1 <- wrap_plots(generalizing_plots[1:10], ncol = 1)
quick_save(wp_1, "wp_1", w = 10, h = 30)

wp_2 <- wrap_plots(generalizing_plots[11:20], ncol = 1)
quick_save(wp_2, "wp_2", w = 10, h = 30)

wp_3 <- wrap_plots(generalizing_plots[21:30], ncol = 1)
quick_save(wp_3, "wp_3", w = 10, h = 30)

wp_4 <- wrap_plots(generalizing_plots[31:40], ncol = 1)
quick_save(wp_4, "wp_4", w = 10, h = 30)

wp_5 <- wrap_plots(generalizing_plots[41:50], ncol = 1)
quick_save(wp_5, "wp_5", w = 10, h = 30)

wp_6 <- wrap_plots(generalizing_plots[51:60], ncol = 1)
quick_save(wp_6, "wp_6", w = 10, h = 30)

wp_7 <- wrap_plots(generalizing_plots[61:67], ncol = 1)
quick_save(wp_7, "wp_7", w = 10, h = 21)
```

```{r}
wpo <- wrap_plots(generalizing_outcome_plots, ncol = 1)

quick_save(wpo, "wpo", w = 7, h = 22)
```

# Summary of the validation (table)

```{r}
mtbi_der_df <- readRDS(proc_path("2025_02_12_mtbi_top_solution_plot_df.rds"))

mtbi_ful_df <- auto_plot(
    mtbi_full_top_3c,
    dl = c(full_data_list_1, full_oom_list_1),
    return_plots = FALSE
)

mtbi_val_df <- auto_plot(
    cluster_df = val_cluster_df,
    dl = c(test_data_list_s1, test_oom_list_s1),
    return_plots = FALSE
) 

colnames(mtbi_der_df)
colnames(mtbi_val_df)
colnames(mtbi_ful_df)

mtbi_der_df <- mtbi_der_df[, -2]
mtbi_val_df <- mtbi_val_df[, -2]
mtbi_ful_df <- mtbi_ful_df[, -2]

saveRDS(mtbi_der_df, proc_path("mtbi_der_df.rds", TRUE))
saveRDS(mtbi_ful_df, proc_path("mtbi_ful_df.rds", TRUE))
saveRDS(mtbi_val_df, proc_path("mtbi_val_df.rds", TRUE))
```

```{r}
# CHECKPOINT
mtbi_der_df <- readRDS(proc_path("2025_02_13_mtbi_der_df.rds"))

mtbi_ful_df <- readRDS(proc_path("2025_02_13_mtbi_ful_df.rds"))

mtbi_ful_df$"cluster" |> table()

mtbi_val_df <- readRDS(proc_path("2025_02_13_mtbi_val_df.rds"))
```

```{r}
mtbi_der_tops <- topologizer(mtbi_der_df)
mtbi_ful_tops <- topologizer(mtbi_ful_df)
mtbi_val_tops <- topologizer(mtbi_val_df)

write_csv(mtbi_der_tops, proc_path("mtbi_der_tops.csv", TRUE))
write_csv(mtbi_ful_tops, proc_path("mtbi_ful_tops.csv", TRUE))
write_csv(mtbi_val_tops, proc_path("mtbi_val_tops.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_der_tops <- read_csv(proc_path("2024_11_26_mtbi_der_tops.csv"))
mtbi_ful_tops <- read_csv(proc_path("2024_11_26_mtbi_ful_tops.csv"))
mtbi_val_tops <- read_csv(proc_path("2024_11_26_mtbi_val_tops.csv"))
```

```{r}
# Prepping the ordering of the tops features
mtbi_top_solution_nmi_v_pval_rank <- read_csv(
    proc_path("2025_02_12_mtbi_top_solution_nmi_v_pval_rank.csv")
)

joint_ranks <- mtbi_top_solution_nmi_v_pval_rank |>
    data.frame() |>
    dplyr::select(feature, joint_rank)
joint_ranks <- rbind(
    joint_ranks,
    data.frame(
        feature = c(
            "race_black",
            "race_white",
            "race_hispanic",
            "race_other"
        ),
        joint_rank = joint_ranks[joint_ranks$"feature" == "race", "joint_rank"]
    )
)
joint_ranks <- rbind(
    joint_ranks,
    data.frame(
        feature = c(
            "mtbi_mechanism_fall_hit",
            "mtbi_mechanism_hosp_er",
            "mtbi_mechanism_multi",
            "mtbi_mechanism_other_loc",
            "mtbi_mechanism_vehicle",
            "mtbi_mechanism_violent"
        ),
        joint_rank = joint_ranks[joint_ranks$"feature" == "mtbi_mechanism", "joint_rank"]
    )
)
joint_ranks <- dplyr::filter(joint_ranks, !feature %in% c("mtbi_mechanism", "race"))

joint_ranks <- arrange(joint_ranks, joint_rank)

joint_ranks

write_csv(joint_ranks, proc_path("joint_ranks.csv", TRUE))
```

```{r}
# CHECKPOINT
joint_ranks <- read_csv(proc_path("2025_02_13_joint_ranks.csv"))
```


```{r}
joint_ranks_with_out <- rbind(
    data.frame(
        feature = outputs,
        joint_rank = nrow(joint_ranks) + 1
    ),
    joint_ranks
) |> data.frame()

f_der_tops <- data.frame(format_tops(mtbi_der_tops))
f_val_tops <- data.frame(format_tops(mtbi_val_tops))
f_ful_tops <- data.frame(format_tops(mtbi_ful_tops))

all_der_tops <- dplyr::full_join(
    joint_ranks_with_out,
    f_der_tops,
    by = join_by("feature" == "Feature")
) |>
    dplyr::select(-joint_rank) |>
    dplyr::rename("Feature" = "feature")

all_val_tops <- dplyr::full_join(
    joint_ranks_with_out,
    f_val_tops,
    by = join_by("feature" == "Feature")
) |>
    dplyr::select(-joint_rank) |>
    dplyr::rename("Feature" = "feature")

all_ful_tops <- dplyr::full_join(
    joint_ranks_with_out,
    f_ful_tops,
    by = join_by("feature" == "Feature")
) |>
    dplyr::select(-joint_rank) |>
    dplyr::rename("Feature" = "feature")

write_csv(all_der_tops, proc_path("mtbi_all_der_tops.csv", TRUE))
write_csv(all_val_tops, proc_path("mtbi_all_val_tops.csv", TRUE))
write_csv(all_ful_tops, proc_path("mtbi_all_ful_tops.csv", TRUE))
```

```{r}
# CHECKPOINT
all_der_tops <- read_csv(proc_path("2025_02_13_mtbi_all_der_tops.csv"))
all_val_tops <- read_csv(proc_path("2025_02_13_mtbi_all_val_tops.csv"))
all_ful_tops <- read_csv(proc_path("2025_02_13_mtbi_all_ful_tops.csv"))
```

```{r}
all_der_tops$"Set" <- "D"
all_val_tops$"Set" <- "V"
all_ful_tops$"Set" <- "F"

all_der_tops$rank <- seq_len(nrow(all_der_tops))
all_val_tops$rank <- seq_len(nrow(all_val_tops))
all_ful_tops$rank <- seq_len(nrow(all_ful_tops))

all_tops <- do.call(rbind, list(all_der_tops, all_val_tops, all_ful_tops))

all_tops <- arrange(all_tops, rank) |>
    relocate(Set, .after = "Feature") |>
    dplyr::select(-rank)

write_csv(all_tops, proc_path("all_tops.csv", TRUE))

all_tops <- read_csv(proc_path("2025_02_13_all_tops.csv"))

knitr::kable(all_tops, format = "markdown", digits = 3, format.args = list(scientific = FALSE)) |>
    writeLines(proc_path("mtbi_full_tops.txt", TRUE)) # 2025-02-13

xtable(all_tops)
```

```{r}
mtbi_der_tops$"set" <- "D"
mtbi_ful_tops$"set" <- "V"
mtbi_val_tops$"set" <- "F"

all_der_tops_raw <- dplyr::full_join(
    joint_ranks_with_out,
    mtbi_der_tops,
    by = "feature"
) |>
    dplyr::select(-joint_rank)

all_val_tops_raw <- dplyr::full_join(
    joint_ranks_with_out,
    mtbi_val_tops,
    by = "feature"
) |>
    dplyr::select(-joint_rank)

all_ful_tops_raw <- dplyr::full_join(
    joint_ranks_with_out,
    mtbi_ful_tops,
    by = "feature"
) |>
    dplyr::select(-joint_rank)

all_der_tops_raw$rank <- seq_len(nrow(all_der_tops_raw))
all_val_tops_raw$rank <- seq_len(nrow(all_val_tops_raw))
all_ful_tops_raw$rank <- seq_len(nrow(all_ful_tops_raw))

all_tops_raw <- do.call(
    rbind,
    list(
        all_der_tops_raw,
        all_val_tops_raw,
        all_ful_tops_raw
    )
)

all_tops_raw$"set" <- factor(
    all_tops_raw$"set",
    levels = c("D", "V", "F")
)

options(width = 200)

all_tops_raw <- all_tops_raw |> arrange(rank, set)

write_csv(all_tops_raw, proc_path("all_tops_raw.csv", TRUE))
```

```{r}
all_tops_raw <- read_csv(proc_path("2025_02_13_all_tops_raw.csv"))

gen_df_a <- generalizable_features(all_tops_raw, compare_fn_a, 0.2)
gen_df_b <- generalizable_features(all_tops_raw, compare_fn_b)

# The generalizable features appear identical by both means
identical(gen_df_a, gen_df_b)

write_csv(gen_df_a, proc_path("mtbi_gen_fts.csv", TRUE))

mtbi_gen_fts <- data.frame(read_csv(proc_path("2025_02_13_mtbi_gen_fts.csv")))

mtbi_gen_fts_in <- mtbi_gen_fts |>
    dplyr::filter(
        c1v2 %in% c(">", "<") | c1v3 %in% c(">", "<") | c2v3 %in% c(">", "<")
    ) |>
    dplyr::filter(
        !feature %in% outputs
    )

mtbi_gen_fts_out <- mtbi_gen_fts |>
    dplyr::filter(
        c1v2 %in% c(">", "<") | c1v3 %in% c(">", "<") | c2v3 %in% c(">", "<")
    ) |>
    dplyr::filter(
        feature %in% outputs
    )

mtbi_gen_fts_in

write_csv(mtbi_gen_fts_in, proc_path("mtbi_gen_fts_in.csv", TRUE))
write_csv(mtbi_gen_fts_out, proc_path("mtbi_gen_fts_out.csv", TRUE))

mtbi_gen_fts_in <- read_csv(proc_path("2025_02_13_mtbi_gen_fts_in.csv"))
mtbi_gen_fts_out <- read_csv(proc_path("2025_02_13_mtbi_gen_fts_out.csv"))

mtbi_gen_fts_in_long <- mtbi_gen_fts_in |>
    pivot_longer(
        cols = -feature,
        names_to = "comparison",
        values_to = "order"
    )

mtbi_gen_fts_out_long <- mtbi_gen_fts_out |>
    pivot_longer(
        cols = -feature,
        names_to = "comparison",
        values_to = "order"
    )

write_csv(mtbi_gen_fts_in_long, proc_path("mtbi_gen_fts_in_long.csv", TRUE))
write_csv(mtbi_gen_fts_out_long, proc_path("mtbi_gen_fts_out_long.csv", TRUE))

mtbi_gen_fts_in_long <- read_csv(proc_path("2025_02_13_mtbi_gen_fts_in_long.csv"))
mtbi_gen_fts_out_long <- read_csv(proc_path("2025_02_13_mtbi_gen_fts_out_long.csv"))

mtbi_gen_fts_in |>
    knitr::kable(all_tops, format = "markdown", align = "lccc") |>
    writeLines(proc_path("mtbi_gen_fts_in.txt", TRUE))

mtbi_gen_fts_out |>
    knitr::kable(all_tops, format = "markdown", align = "lccc") |>
    writeLines(proc_path("mtbi_gen_fts_out.txt", TRUE))
```


## How would the process go in demographic adjusted data?

The outcomes (and inputs) appear heavily associated with demographic variables pubertal status, sex, income, and race.
How would correcting for those variables influence the meta clustering results?


```{r}
full_data_list_1 <- readRDS(input_path("2025_02_12_mtbi_full_data_list_1.rds"))

full_data_list_1

dl_no_demo <- full_data_list_1[-c(4, 6:9)] 
dl_demo <- full_data_list_1[c(4, 6:9)]

dl_demo

dl_corrected <- linear_adjust(dl_no_demo, dl_demo)
saveRDS(dl_corrected, proc_path("dl_corrected.rds", TRUE))
```

```{r}
# CHECKPOINT
#dl_corrected <- readRDS(proc_path("2025_02_13_dl_corrected.rds"))
dl_corrected <- readRDS(proc_path("2025_03_26_dl_corrected.rds")) # now with age!
```

```{r}
set.seed(42)
corrected_config <- snf_config(
    dl_corrected,
    n_solutions = 1000,
    cnt_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    dsc_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ord_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    use_default_dist_fns = TRUE
)

saveRDS(corrected_config, proc_path("corrected_config.rds", TRUE))

corrected_config <- readRDS(proc_path("2025_03_26_corrected_config.rds"))

demo_adj_sol_df <- batch_snf(
    dl = dl_corrected,
    sc = corrected_config,
    processes = "max"
)
 # Never ran
saveRDS(demo_adj_sol_df, proc_path("demo_adj_sol_df.rds", TRUE))
```

```{r}

# HERE 2025_03_26

# CHECKPOINT
demo_adj_sol_df <- readRDS(proc_path("2025_02_13_demo_adj_sol_df.rds"))
```

```{r}
demo_adj_ari <- calc_aris(demo_adj_sol_df)
saveRDS(demo_adj_ari, proc_path("demo_adj_ari.rds", TRUE))

demo_adj_ari_order <- get_matrix_order(demo_adj_ari)
write_csv(data.frame(demo_adj_ari_order), proc_path("demo_adj_ari_order.csv", TRUE))

```

```{r}
# CHECKPOINT
demo_adj_ari <- readRDS(proc_path("2025_02_14_demo_adj_ari.rds"))
demo_adj_ari_order <- unlist(read_csv(proc_path("2025_02_14_demo_adj_ari_order.csv")))
names(demo_adj_ari_order) <- NULL
```

```{r}
adj_oom_list <- linear_adjust(full_oom_list_1, dl_demo)

saveRDS(adj_oom_list, proc_path("adj_oom_list.rds", TRUE))

adj_oom_list <- readRDS(proc_path("2025_03_17_adj_oom_list.rds"))

# Extend solutions from adjusted inputs to unadjusted outcomes
demo_adj_ext_sol_df <- extend_solutions(
    demo_adj_sol_df,
    dl = dl_corrected,
    target_dl = full_oom_list_1,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(demo_adj_ext_sol_df, proc_path("demo_adj_ext_sol_df.rds", TRUE))

# Extend solutions from adjusted inputs to adjusted outcomes
demo_double_adj_ext_sol_df <- extend_solutions(
    demo_adj_sol_df,
    dl = dl_corrected,
    target_dl = adj_oom_list,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(demo_double_adj_ext_sol_df, proc_path("demo_double_adj_ext_sol_df.rds", TRUE))
```

```{r}
demo_adj_ext_sol_df <- readRDS(proc_path("2025_02_14_demo_adj_ext_sol_df.rds"))
demo_double_adj_ext_sol_df <- readRDS(proc_path("2025_02_14_demo_double_adj_ext_sol_df.rds"))

base_adj_ari_hm <- meta_cluster_heatmap(
    demo_adj_ari,
    order = demo_adj_ari_order
)

shiny_annotator(base_adj_ari_hm)

demo_adj_esdf <- as.data.frame(demo_adj_ext_sol_df)
demo_adj_esdf$"impairment_separation" <- -log10(demo_adj_esdf$"mean_pval")

demo_double_adj_esdf <- as.data.frame(demo_double_adj_ext_sol_df)
demo_double_adj_esdf$"impairment_separation" <- -log10(demo_double_adj_esdf$"mean_pval")

demo_adj_split_vec <- c(
    50,
    74,
    127,
    297,
    490,
    642,
    755
)

write_csv(data.frame(demo_adj_split_vec), proc_path("demo_adj_split_vec.csv", TRUE))

demo_adj_split_vec <- read_csv(proc_path("2025_02_14_demo_adj_split_vec.csv")) |>
    unlist() |>
    as.numeric()

full_demo_adj_ari_hm <- meta_cluster_heatmap(
    aris = demo_adj_ari,
    order = demo_adj_ari_order,
    data = demo_adj_esdf,
    min_colour = "black",
    split_vector = demo_adj_split_vec,
    top_hm = list(
        "Impairment Separation" = "impairment_separation"
    ),
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    annotation_colours = list(
        "Impairment Separation" = colour_scale(
            demo_adj_esdf$"impairment_separation",
            min_colour = "gray7",
            max_colour = "limegreen"
        )
    )
)
full_demo_adj_ari_hm

# The double adjustment does not yield and interesting meta clusters
full_demo_double_adj_ari_hm <- meta_cluster_heatmap(
    aris = demo_adj_ari,
    order = demo_adj_ari_order,
    data = demo_double_adj_esdf,
    min_colour = "black",
    split_vector = demo_adj_split_vec,
    top_hm = list(
        "Impairment Separation" = "impairment_separation"
    ),
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    annotation_colours = list(
        "Impairment Separation" = colour_scale(
            demo_double_adj_esdf$"impairment_separation",
            min_colour = "gray7",
            max_colour = "limegreen"
        )
    )
)
full_demo_double_adj_ari_hm

save_heatmap(
    heatmap = full_demo_double_adj_ari_hm,
    path = fig_path("full_demo_double_adj_ari_hm.png", TRUE),
    width = 950,
    height = 900,
    res = 100
)

demo_adj_mc_sol_df <- label_meta_clusters(
    demo_adj_ext_sol_df,
    order = demo_adj_ari_order,
    split_vector = demo_adj_split_vec
)

demo_adj_rep_solutions <- get_representative_solutions(
    demo_adj_ari,
    demo_adj_mc_sol_df
)

demo_adj_rep_solutions

demo_adj_top_solution <- demo_adj_rep_solutions |>
    dplyr::filter(mc == "E")

saveRDS(demo_adj_top_solution, proc_path("demo_adj_top_solution.rds", TRUE))

demo_adj_top_solution <- readRDS(proc_path("2025_02_14_demo_adj_top_solution.rds"))

demo_adj_plot_list <- auto_plot(
    demo_adj_top_solution,
    dl = c(dl_corrected, dl_demo, full_oom_list_1)
)

demo_adj_plot_list$"cortical_sa"

demo_adj_pl_ranked <- demo_adj_plot_list[sorted_in_and_out]

demo_adj_p_ranked <- wrap_plots(demo_adj_pl_ranked)

ggsave(
    fig_path("demo_adj_ranked_plots.png", TRUE),
    demo_adj_p_ranked,
    width = 45,
    height = 30,
    dpi = 50
)

demo_adj_plot_df <- auto_plot(
    demo_adj_top_solution,
    dl = c(dl_corrected, dl_demo, full_oom_list_1),
    return_plots = FALSE
)

demo_adj_plot_df |>
    ggplot(
        aes(x = cluster, y = fmri_cort_subcort_cors)
    ) +
    geom_point()

```

```{r}
full_data_list_1 <- readRDS(input_path("2025_02_12_mtbi_full_data_list_1.rds"))

mtbi_age_distribution <- full_data_list_1[[5]]$"data" |>
    dplyr::mutate(
        age = mtbi_age / 12
    ) |>
    ggplot(aes(x = age)) +
    geom_histogram(binwidth = 1, fill = "grey", color = "black") +
    labs(x = "mTBI Age (Years)", y = "Count") +
    theme_minimal() +
    theme(text = element_text(size = 20))

ggsave(
    fig_path("mtbi_age_distribution.png", TRUE),
    mtbi_age_distribution,
    width = 7,
    height = 5,
    dpi = 60
)
```
