# Characterization of identified meta clusters

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)
library(MatchIt)
library(ggplot2)
library(patchwork)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subjects <- read_csv(sub_path("2023_11_07_mtbi_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2023_11_07_uninjured_subjects.csv"))
matched_uninjured <- read_csv(sub_path("2024_01_15_matched_uninjured.csv"))
```
## Loading data and out of model lists

```{r}
data_list_m1 <- list.load(input_path("2024_01_15_data_list_m1.rds"))
data_list_m2 <- list.load(input_path("2024_01_15_data_list_m2.rds"))
data_list_m3 <- list.load(input_path("2024_01_15_data_list_m3.rds"))
data_list_m4 <- list.load(input_path("2024_01_15_data_list_m4.rds"))
data_list_m5 <- list.load(input_path("2024_01_15_data_list_m5.rds"))
data_list_pm1 <- list.load(input_path("2024_01_15_data_list_pm1.rds"))
data_list_pm2 <- list.load(input_path("2024_01_15_data_list_pm2.rds"))
data_list_pm3 <- list.load(input_path("2024_01_15_data_list_pm3.rds"))
data_list_pm4 <- list.load(input_path("2024_01_15_data_list_pm4.rds"))
data_list_pm5 <- list.load(input_path("2024_01_15_data_list_pm5.rds"))
oom_list_m1 <- list.load(input_path("2024_01_15_oom_list_m1.rds"))
oom_list_m2 <- list.load(input_path("2024_01_15_oom_list_m2.rds"))
oom_list_m3 <- list.load(input_path("2024_01_15_oom_list_m3.rds"))
oom_list_m4 <- list.load(input_path("2024_01_15_oom_list_m4.rds"))
oom_list_m5 <- list.load(input_path("2024_01_15_oom_list_m5.rds"))
oom_list_pm1 <- list.load(input_path("2024_01_15_oom_list_pm1.rds"))
oom_list_pm2 <- list.load(input_path("2024_01_15_oom_list_pm2.rds"))
oom_list_pm3 <- list.load(input_path("2024_01_15_oom_list_pm3.rds"))
oom_list_pm4 <- list.load(input_path("2024_01_15_oom_list_pm4.rds"))
oom_list_pm5 <- list.load(input_path("2024_01_15_oom_list_pm5.rds"))

data_list_mu1 <- list.load(input_path("2024_01_15_data_list_mu1.rds"))
data_list_mu2 <- list.load(input_path("2024_01_15_data_list_mu2.rds"))
data_list_mu3 <- list.load(input_path("2024_01_15_data_list_mu3.rds"))
data_list_mu4 <- list.load(input_path("2024_01_15_data_list_mu4.rds"))
data_list_mu5 <- list.load(input_path("2024_01_15_data_list_mu5.rds"))
data_list_mpu1 <- list.load(input_path("2024_01_15_data_list_mpu1.rds"))
data_list_mpu2 <- list.load(input_path("2024_01_15_data_list_mpu2.rds"))
data_list_mpu3 <- list.load(input_path("2024_01_15_data_list_mpu3.rds"))
data_list_mpu4 <- list.load(input_path("2024_01_15_data_list_mpu4.rds"))
data_list_mpu5 <- list.load(input_path("2024_01_15_data_list_mpu5.rds"))
oom_list_mu1 <- list.load(input_path("2024_01_15_oom_list_mu1.rds"))
oom_list_mu2 <- list.load(input_path("2024_01_15_oom_list_mu2.rds"))
oom_list_mu3 <- list.load(input_path("2024_01_15_oom_list_mu3.rds"))
oom_list_mu4 <- list.load(input_path("2024_01_15_oom_list_mu4.rds"))
oom_list_mu5 <- list.load(input_path("2024_01_15_oom_list_mu5.rds"))
oom_list_mpu1 <- list.load(input_path("2024_01_15_oom_list_mpu1.rds"))
oom_list_mpu2 <- list.load(input_path("2024_01_15_oom_list_mpu2.rds"))
oom_list_mpu3 <- list.load(input_path("2024_01_15_oom_list_mpu3.rds"))
oom_list_mpu4 <- list.load(input_path("2024_01_15_oom_list_mpu4.rds"))
oom_list_mpu5 <- list.load(input_path("2024_01_15_oom_list_mpu5.rds"))
```

## mTBI meta clusters

Meta-cluster B of the mTBI subjects are the ones that are of greatest interest to us.
That meta-cluster describes 3-cluster solutions that strongly separate the behavioural impairments and that exist across both solo and pooled imputations.

MCs A and C appear to be close variations of B.
D and E appear to be quite unique and are only found in the solo and pooled imputations respectively.

The tight clusters within F include F-A, F-C, F-D, F-E, and F-J.
Clusters such as F-A, F-B, F-E, F-F, and F-H show strong separation across some of those mTBI-specific variables. 


```{r}
full_extended_solutions_matrix <- read_csv(
    proc_path("2024_01_15_full_mtbi_extended_solutions_matrix.csv")
)

full_extended_solutions_matrix

full_oom_pvals <- pval_select(
    full_extended_solutions_matrix,
    negative_log = TRUE
)

full_extended_solutions_matrix$"mean_neglog_p" <- full_oom_pvals$"mean_neglog_p"

full_extended_solutions_matrix

sm_order <- unlist(
    read_csv(proc_path("2024_01_15_aris_all_mtbi_imputations_order.csv"))
)
names(sm_order) <- NULL

sorted_solutions_matrix <- full_extended_solutions_matrix[sm_order, ]

mc_b_solutions <- sorted_solutions_matrix[501:806, ]

```

### MC B

```{r}

all_data_list_m1 <- c(data_list_m1, oom_list_m1)

top_mc_b_solution <- mc_b_solutions[
    which(
        mc_b_solutions$"mean_neglog_p" == max(mc_b_solutions$"mean_neglog_p")
    ), 
]

title_case <- function(string) {
    words <- strsplit(string, "_")[[1]]
    words <- sapply(
        words,
        function(x) {
            paste0(toupper(substr(x, 1, 1)), substr(x, 2, nchar(x)))
        }
    )
    result <- paste(words, collapse = " ")
    result <- gsub("Mtbi", "mTBI", result)
    result <- gsub("Loc", "LOC", result)
    return(result)
}

scatter_plot <- function(df, feature) {
    df <- df |> dplyr::rename("keycol" = !!feature)
    plot <- df |>
        dplyr::select(
            cluster,
            keycol,
        ) |>
        ggplot(
            aes(
                x = cluster,
                y = keycol,
                colour = cluster
            )
        ) + 
        geom_violin(
            alpha = 0.4
        ) +
        geom_jitter(
            height = 0,
            width = 0.1,
            alpha = 0.8,
            size = 3,
        ) +
        stat_summary(
            fun = "mean",
            geom = "point",
            colour = "black",
            size = 5
        ) +
        labs(
            x = "Cluster",
            y = title_case(feature),
            color = "Cluster"
        ) +
        theme_bw() +
        theme(
            text = element_text(size = 20),
            legend.position = "none"
        )
    return(plot)
}

bar_plot <- function(df, feature) {
    df <- df |>
        dplyr::rename("keycol" = !!feature) |>
        dplyr::select(cluster, keycol) |>
        dplyr::group_by(cluster) |>
        dplyr::count(keycol) |>
        dplyr::mutate(percent = n / sum(n) * 100)
    print(str(df))
    df$"keycol" <- factor(df$"keycol")
    plot <- df |>
        ggplot(
            aes(
                x = cluster,
                y = percent,
                fill = keycol
            )
        ) + 
        geom_bar(
            stat = "identity" ,
            position = ggplot2::position_stack()
        ) +
        geom_text(
            aes(
                label = n,
                y = percent
            ),
            size = 6,
            position = position_stack(vjust = 0.5)
        ) +
        labs(
            x = "Cluster",
            y = "%",
            fill = title_case(feature)
        ) +
        theme_bw() + 
        theme(text = element_text(size = 20))
    return(plot)
}

jitter_plot <- function(df, feature) {
    df <- df |> dplyr::rename("keycol" = !!feature)
    plot <- df |>
        dplyr::select(
            cluster,
            keycol
        ) |>
        ggplot(
            aes(
                x = cluster,
                y = keycol,
                color = cluster
            )
        ) + 
        geom_violin(
            alpha = 0.4
        ) +
        geom_jitter(
            height = 0.1,
            width = 0.2,
            alpha = 0.8,
            size = 3
        ) +
        stat_summary(
            fun = "mean",
            geom = "point",
            colour = "black",
            size = 5
        ) +
        labs(
            x = "Cluster",
            y = title_case(feature),
            color = "Cluster"
        ) +
        theme_bw() +
        theme(
            text = element_text(size = 20),
            legend.position = "none"
        )
    return(plot)
}

# HERE I AM - exporting the plots

characterize_solution <- function(solution, data_list, plotname) {
    # Generating the required full dataframe
    cluster_df <- get_cluster_df(solution)
    data_df <- collapse_dl(data_list)
    full_data <- dplyr::inner_join(cluster_df, data_df, by = "subjectkey")
    full_data$"cluster" <- factor(full_data$"cluster")
    # Re-coding variables
    full_data$"sex"[full_data$"sex" == 0] <- "F"
    full_data$"sex"[full_data$"sex" == 1] <- "M"
    full_data$"race"[full_data$"race" == 0] <- "White"
    full_data$"race"[full_data$"race" == 1] <- "Non-White"
    # Identifying features to plot 
    features <- colnames(full_data)[3:length(colnames(full_data))]
    plot_list <- list()
    for (i in 1:length(features)) {
        feature <- features[[i]]
        feature_col <- full_data[, feature]
        nvals <- length(unique(feature_col))
        if (is.numeric(feature_col)) {
            plot <- jitter_plot(full_data, feature)
        } else {
            plot <- bar_plot(full_data, feature)
        }
        ggsave(
            plot = plot,
            fig_path(
                paste0(
                    plotname
                    "_",
                    feature,
                    ".png"
                ),
                TRUE
            )
        )
        plot_list[[i]] <- plot
    }
    return(plot_list)
}
all_plots <- characterize_solution(
    top_mc_b_solution,
    all_data_list_m1
)

all_plots_pw <- wrap_plots(all_plots)

ggsave(
    plot = all_plots_pw,
    fig_path("mtbi_mc_b_plots.png", TRUE)
)




bar_plot(z, "cbcl_anxdep")

bar_plot(z, "mtbi_mechanism")

jitter_plot(z, "cbcl_anxdep")

scatter_plot(z, "parent_hyperactive")


```


