# Characterization of identified meta clusters

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)
library(MatchIt)
library(ggplot2)
library(patchwork)
library(ggsignif)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subjects <- read_csv(sub_path("2023_11_07_mtbi_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2023_11_07_uninjured_subjects.csv"))
matched_uninjured <- read_csv(sub_path("2024_01_15_matched_uninjured.csv"))
```
## Loading data and out of model lists

```{r}
data_list_m1 <- list.load(input_path("2024_01_15_data_list_m1.rds"))
data_list_m2 <- list.load(input_path("2024_01_15_data_list_m2.rds"))
data_list_m3 <- list.load(input_path("2024_01_15_data_list_m3.rds"))
data_list_m4 <- list.load(input_path("2024_01_15_data_list_m4.rds"))
data_list_m5 <- list.load(input_path("2024_01_15_data_list_m5.rds"))
data_list_pm1 <- list.load(input_path("2024_01_15_data_list_pm1.rds"))
data_list_pm2 <- list.load(input_path("2024_01_15_data_list_pm2.rds"))
data_list_pm3 <- list.load(input_path("2024_01_15_data_list_pm3.rds"))
data_list_pm4 <- list.load(input_path("2024_01_15_data_list_pm4.rds"))
data_list_pm5 <- list.load(input_path("2024_01_15_data_list_pm5.rds"))
oom_list_m1 <- list.load(input_path("2024_01_15_oom_list_m1.rds"))
oom_list_m2 <- list.load(input_path("2024_01_15_oom_list_m2.rds"))
oom_list_m3 <- list.load(input_path("2024_01_15_oom_list_m3.rds"))
oom_list_m4 <- list.load(input_path("2024_01_15_oom_list_m4.rds"))
oom_list_m5 <- list.load(input_path("2024_01_15_oom_list_m5.rds"))
oom_list_pm1 <- list.load(input_path("2024_01_15_oom_list_pm1.rds"))
oom_list_pm2 <- list.load(input_path("2024_01_15_oom_list_pm2.rds"))
oom_list_pm3 <- list.load(input_path("2024_01_15_oom_list_pm3.rds"))
oom_list_pm4 <- list.load(input_path("2024_01_15_oom_list_pm4.rds"))
oom_list_pm5 <- list.load(input_path("2024_01_15_oom_list_pm5.rds"))

data_list_mu1 <- list.load(input_path("2024_01_15_data_list_mu1.rds"))
data_list_mu2 <- list.load(input_path("2024_01_15_data_list_mu2.rds"))
data_list_mu3 <- list.load(input_path("2024_01_15_data_list_mu3.rds"))
data_list_mu4 <- list.load(input_path("2024_01_15_data_list_mu4.rds"))
data_list_mu5 <- list.load(input_path("2024_01_15_data_list_mu5.rds"))
data_list_mpu1 <- list.load(input_path("2024_01_15_data_list_mpu1.rds"))
data_list_mpu2 <- list.load(input_path("2024_01_15_data_list_mpu2.rds"))
data_list_mpu3 <- list.load(input_path("2024_01_15_data_list_mpu3.rds"))
data_list_mpu4 <- list.load(input_path("2024_01_15_data_list_mpu4.rds"))
data_list_mpu5 <- list.load(input_path("2024_01_15_data_list_mpu5.rds"))
oom_list_mu1 <- list.load(input_path("2024_01_15_oom_list_mu1.rds"))
oom_list_mu2 <- list.load(input_path("2024_01_15_oom_list_mu2.rds"))
oom_list_mu3 <- list.load(input_path("2024_01_15_oom_list_mu3.rds"))
oom_list_mu4 <- list.load(input_path("2024_01_15_oom_list_mu4.rds"))
oom_list_mu5 <- list.load(input_path("2024_01_15_oom_list_mu5.rds"))
oom_list_mpu1 <- list.load(input_path("2024_01_15_oom_list_mpu1.rds"))
oom_list_mpu2 <- list.load(input_path("2024_01_15_oom_list_mpu2.rds"))
oom_list_mpu3 <- list.load(input_path("2024_01_15_oom_list_mpu3.rds"))
oom_list_mpu4 <- list.load(input_path("2024_01_15_oom_list_mpu4.rds"))
oom_list_mpu5 <- list.load(input_path("2024_01_15_oom_list_mpu5.rds"))
```

## mTBI meta clusters

Meta-cluster B of the mTBI subjects are the ones that are of greatest interest to us.
That meta-cluster describes 3-cluster solutions that strongly separate the behavioural impairments and that exist across both solo and pooled imputations.

MCs A and C appear to be close variations of B.
D and E appear to be quite unique and are only found in the solo and pooled imputations respectively.

The tight clusters within F include F-A, F-C, F-D, F-E, and F-J.
Clusters such as F-A, F-B, F-E, F-F, and F-H show strong separation across some of those mTBI-specific variables. 


```{r}
full_extended_solutions_matrix <- read_csv(
    proc_path("2024_01_15_full_mtbi_extended_solutions_matrix.csv")
)

full_extended_solutions_matrix

full_oom_pvals <- pval_select(
    full_extended_solutions_matrix,
    negative_log = TRUE
)

full_extended_solutions_matrix$"mean_neglog_p" <- full_oom_pvals$"mean_neglog_p"

full_extended_solutions_matrix

sm_order <- unlist(
    read_csv(proc_path("2024_01_15_aris_all_mtbi_imputations_order.csv"))
)
names(sm_order) <- NULL

sorted_solutions_matrix <- full_extended_solutions_matrix[sm_order, ]

mc_b_solutions <- sorted_solutions_matrix[501:806, ]

```

### mTBI MC B

```{r}
all_data_list_m1 <- c(data_list_m1, oom_list_m1)

top_mc_b_solution <- mc_b_solutions[
    which(
        mc_b_solutions$"mean_neglog_p" == max(mc_b_solutions$"mean_neglog_p")
    ), 
]

mc_b_plots <- characterize_solution(
    top_mc_b_solution,
    all_data_list_m1,
    "mtbi_mc_b"
)

save_plot_list(mc_b_plots, "mtbi_mc_b")

mc_b_main_plots <- list(
    mc_b_plots$"pubertal_status",
    mc_b_plots$"brain_volume",
    mc_b_plots$"sex",
    mc_b_plots$"weekday_screentime",
    mc_b_plots$"household_income",
    mc_b_plots$"race",
    mc_b_plots$"family_fight",
    mc_b_plots$"headache_history",
    mc_b_plots$"mtbi_loc"
) |> wrap_plots()
mc_b_main_plots
```

Based on the plots, MC B can be characterized as follows:

- 3 cluster solution

- Cluster 1:
    - Much lower income
    - Much higher fraction of non-white
    - Middle level of pubertal status
    - Most screen time
    - Least participation in extracurriculars
    - Rated not considerate
    - Worst family environment
    - Worst parent psychopathology
    - Strong impairments
- Cluster 2:
    - More memory loss / feeling dazed
    - More loss of consciousness
    - Lowest pubertal status
    - Highest brain volume and SA
- Cluster 3:
    - Highest pubertal status
    - Lowest history of headaches
    - Lowest brain volume and SA
    - Mostly female

Particularly notable is that the high impairment group was particulary imbalanced across the sexes.

The closest candidate within the uninjured group appeared to be MC D-A, which was tight, small but reproducible across unpooled and pooled imputations, and also exhibited a 3 cluster solution with faint separation across impairment measures.

Is it really the case that the CBCL scores are worse in females?

```{r}

top_mc_b_solution

mc_b_data <- characterize_solution(
    top_mc_b_solution,
    all_data_list_m1,
    "mtbi_mc_b",
    return_plot = FALSE
)

mc_b_data

mc_b_data |>
    ggplot(
        aes(
            x = cluster,
            y = cbcl_withdep
        )
    ) + 
    geom_violin() +
    geom_jitter(
        aes(
            x = cluster,
            y = cbcl_aggressive,
            colour = sex
        ),
        height = 0.05,
        size = 3,
        alpha = 0.5
    )

mc_b_data |>
    ggplot(
        aes(
            x = sex,
            y = cbcl_aggressive
        )
    ) + 
    geom_violin() +
    geom_jitter(
        height = 0.05,
        size = 3,
        alpha = 0.5
    )


```


### Uninjured MC D-A

```{r}
mu_extended_solutions_matrix <- read_csv(
    proc_path("2024_01_20_full_uninjured_extended_solutions_matrix.csv")
)

mu_extended_solutions_matrix

mu_oom_pvals <- pval_select(
    mu_extended_solutions_matrix,
    negative_log = TRUE
)

mu_extended_solutions_matrix$"mean_neglog_p" <- mu_oom_pvals$"mean_neglog_p"

mu_extended_solutions_matrix

mu_sm_order <- unlist(
    read_csv(proc_path("2024_01_20_aris_all_uninjured_imputations_order.csv"))
)
names(mu_sm_order) <- NULL

mu_sorted_solutions_matrix <- mu_extended_solutions_matrix[mu_sm_order, ]

mu_mc_da_solutions <- mu_sorted_solutions_matrix[1466:(1466 + 89), ]

# Stick to the 3 cluster solutions
mu_mc_da_solutions <- mu_mc_da_solutions |>
    dplyr::filter(nclust == 3)

all_data_list_mu1 <- c(data_list_mu1, oom_list_mu1)

top_mu_mc_da_solution <- mu_mc_da_solutions[
    which(
        mu_mc_da_solutions$"mean_neglog_p" == max(mu_mc_da_solutions$"mean_neglog_p")
    ), 
]

mu_mc_da_plots <- characterize_solution(
    top_mu_mc_da_solution,
    all_data_list_mu1,
    "uninjured_mc_da"
)

save_plot_list(mu_mc_da_plots, "uninjured_mc_da")

mc_b_main_plots <- list(
    mc_b_plots$"pubertal_status",
    mc_b_plots$"brain_volume",
    mc_b_plots$"sex",
    mc_b_plots$"weekday_screentime",
    mc_b_plots$"household_income",
    mc_b_plots$"race",
    mc_b_plots$"family_fight",
    mc_b_plots$"headache_history",
    mc_b_plots$"mtbi_loc"
) |> wrap_plots()
mc_b_main_plots

```

That solution ended up being quite meaningless.
Indiscriminantly looking for the best 3 cluster solution amongst the uninjured data we get:

### Top uninjured 3 cluster solution

```{r}

uninjured_3c_solutions <- mu_sorted_solutions_matrix |>
    dplyr::filter(nclust == 3)

uninjured_3c_top_solution <- uninjured_3c_solutions |>
    dplyr::filter(mean_neglog_p == max(uninjured_3c_solutions$"mean_neglog_p"))

mu_top_3c_plots <- characterize_solution(
    uninjured_3c_top_solution,
    all_data_list_mu1,
    "uninjured_top_3c"
)

save_plot_list(mu_top_3c_plots, "uninjured_top_3c")

```

Not very similar to the 3c group.
In the following chapters, an alternative matched uninjured group is explored.


