# Characterization of identified meta clusters

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)
library(MatchIt)
library(ggplot2)
library(patchwork)
library(ggsignif)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subjects <- read_csv(sub_path("2023_11_07_mtbi_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2023_11_07_uninjured_subjects.csv"))
matched_uninjured <- read_csv(sub_path("2024_01_15_matched_uninjured.csv"))
```
## Loading data and out of model lists

```{r}
data_list_m1 <- list.load(input_path("2024_01_15_data_list_m1.rds"))
data_list_m2 <- list.load(input_path("2024_01_15_data_list_m2.rds"))
data_list_m3 <- list.load(input_path("2024_01_15_data_list_m3.rds"))
data_list_m4 <- list.load(input_path("2024_01_15_data_list_m4.rds"))
data_list_m5 <- list.load(input_path("2024_01_15_data_list_m5.rds"))
data_list_pm1 <- list.load(input_path("2024_01_15_data_list_pm1.rds"))
data_list_pm2 <- list.load(input_path("2024_01_15_data_list_pm2.rds"))
data_list_pm3 <- list.load(input_path("2024_01_15_data_list_pm3.rds"))
data_list_pm4 <- list.load(input_path("2024_01_15_data_list_pm4.rds"))
data_list_pm5 <- list.load(input_path("2024_01_15_data_list_pm5.rds"))
oom_list_m1 <- list.load(input_path("2024_01_15_oom_list_m1.rds"))
oom_list_m2 <- list.load(input_path("2024_01_15_oom_list_m2.rds"))
oom_list_m3 <- list.load(input_path("2024_01_15_oom_list_m3.rds"))
oom_list_m4 <- list.load(input_path("2024_01_15_oom_list_m4.rds"))
oom_list_m5 <- list.load(input_path("2024_01_15_oom_list_m5.rds"))
oom_list_pm1 <- list.load(input_path("2024_01_15_oom_list_pm1.rds"))
oom_list_pm2 <- list.load(input_path("2024_01_15_oom_list_pm2.rds"))
oom_list_pm3 <- list.load(input_path("2024_01_15_oom_list_pm3.rds"))
oom_list_pm4 <- list.load(input_path("2024_01_15_oom_list_pm4.rds"))
oom_list_pm5 <- list.load(input_path("2024_01_15_oom_list_pm5.rds"))

data_list_mu1 <- list.load(input_path("2024_01_15_data_list_mu1.rds"))
data_list_mu2 <- list.load(input_path("2024_01_15_data_list_mu2.rds"))
data_list_mu3 <- list.load(input_path("2024_01_15_data_list_mu3.rds"))
data_list_mu4 <- list.load(input_path("2024_01_15_data_list_mu4.rds"))
data_list_mu5 <- list.load(input_path("2024_01_15_data_list_mu5.rds"))
data_list_mpu1 <- list.load(input_path("2024_01_15_data_list_mpu1.rds"))
data_list_mpu2 <- list.load(input_path("2024_01_15_data_list_mpu2.rds"))
data_list_mpu3 <- list.load(input_path("2024_01_15_data_list_mpu3.rds"))
data_list_mpu4 <- list.load(input_path("2024_01_15_data_list_mpu4.rds"))
data_list_mpu5 <- list.load(input_path("2024_01_15_data_list_mpu5.rds"))
oom_list_mu1 <- list.load(input_path("2024_01_15_oom_list_mu1.rds"))
oom_list_mu2 <- list.load(input_path("2024_01_15_oom_list_mu2.rds"))
oom_list_mu3 <- list.load(input_path("2024_01_15_oom_list_mu3.rds"))
oom_list_mu4 <- list.load(input_path("2024_01_15_oom_list_mu4.rds"))
oom_list_mu5 <- list.load(input_path("2024_01_15_oom_list_mu5.rds"))
oom_list_mpu1 <- list.load(input_path("2024_01_15_oom_list_mpu1.rds"))
oom_list_mpu2 <- list.load(input_path("2024_01_15_oom_list_mpu2.rds"))
oom_list_mpu3 <- list.load(input_path("2024_01_15_oom_list_mpu3.rds"))
oom_list_mpu4 <- list.load(input_path("2024_01_15_oom_list_mpu4.rds"))
oom_list_mpu5 <- list.load(input_path("2024_01_15_oom_list_mpu5.rds"))
```

## mTBI meta clusters

Meta-cluster B of the mTBI subjects are the ones that are of greatest interest to us.
That meta-cluster describes 3-cluster solutions that strongly separate the behavioural impairments and that exist across both solo and pooled imputations.

MCs A and C appear to be close variations of B.
D and E appear to be quite unique and are only found in the solo and pooled imputations respectively.

The tight clusters within F include F-A, F-C, F-D, F-E, and F-J.
Clusters such as F-A, F-B, F-E, F-F, and F-H show strong separation across some of those mTBI-specific variables. 


```{r}
full_extended_solutions_matrix <- read_csv(
    proc_path("2024_01_15_full_mtbi_extended_solutions_matrix.csv")
)

full_extended_solutions_matrix

full_oom_pvals <- pval_select(
    full_extended_solutions_matrix,
    negative_log = TRUE
)

full_extended_solutions_matrix$"mean_neglog_p" <- full_oom_pvals$"mean_neglog_p"

full_extended_solutions_matrix

sm_order <- unlist(
    read_csv(proc_path("2024_01_15_aris_all_mtbi_imputations_order.csv"))
)
names(sm_order) <- NULL

sorted_solutions_matrix <- full_extended_solutions_matrix[sm_order, ]

mc_b_solutions <- sorted_solutions_matrix[501:806, ]

```

### MC B

```{r}

all_data_list_m1 <- c(data_list_m1, oom_list_m1)

top_mc_b_solution <- mc_b_solutions[
    which(
        mc_b_solutions$"mean_neglog_p" == max(mc_b_solutions$"mean_neglog_p")
    ), 
]

title_case <- function(string) {
    words <- strsplit(string, "_")[[1]]
    words <- sapply(
        words,
        function(x) {
            paste0(toupper(substr(x, 1, 1)), substr(x, 2, nchar(x)))
        }
    )
    result <- paste(words, collapse = " ")
    result <- gsub("Mtbi", "mTBI", result)
    result <- gsub("Loc", "LOC", result)
    result <- gsub("Cbcl", "CBCL", result)
    result <- gsub("Sds", "SDS", result)
    result <- gsub("Cortical Sa", "Cortical SA (mm2)", result)
    result <- gsub("Volume", "Volume (mm3)", result)
    return(result)
}

scatter_plot <- function(df, feature) {
    df <- df |> dplyr::rename("keycol" = !!feature)
    plot <- df |>
        dplyr::select(
            cluster,
            keycol,
        ) |>
        ggplot(
            aes(
                x = cluster,
                y = keycol,
                colour = cluster
            )
        ) + 
        geom_violin(
            alpha = 0.4
        ) +
        geom_jitter(
            height = 0,
            width = 0.1,
            alpha = 0.8,
            size = 3,
        ) +
        stat_summary(
            fun = "mean",
            geom = "point",
            colour = "black",
            size = 5
        ) +
        labs(
            x = "Cluster",
            y = title_case(feature),
            color = "Cluster"
        ) +
        theme_bw() +
        theme(
            text = element_text(size = 20),
            legend.position = "none",
            panel.grid.major.x = element_blank()
        )
    return(plot)
}

jitter_plot <- function(df, feature) {
    df <- df |> dplyr::rename("keycol" = !!feature)
    plot <- df |>
        dplyr::select(
            cluster,
            keycol
        ) |>
        ggplot(
            aes(
                x = cluster,
                y = keycol,
                color = cluster
            )
        ) + 
        geom_violin(
            alpha = 0.4
        ) +
        geom_jitter(
            height = 0.1,
            width = 0.2,
            alpha = 0.8,
            size = 3
        ) +
        stat_summary(
            fun = "mean",
            geom = "point",
            colour = "black",
            size = 5
        ) +
        labs(
            x = "Cluster",
            y = title_case(feature),
            color = "Cluster"
        ) +
        theme_bw() +
        theme(
            text = element_text(size = 20),
            legend.position = "none",
            panel.grid.major.x = element_blank()
        )
    return(plot)
}

bar_plot <- function(df, feature) {
    df <- df |>
        dplyr::rename("keycol" = !!feature) |>
        dplyr::select(cluster, keycol) |>
        dplyr::group_by(cluster) |>
        dplyr::count(keycol) |>
        dplyr::mutate(percent = n / sum(n) * 100)
    df$"keycol" <- factor(df$"keycol")
    plot <- df |>
        ggplot(
            aes(
                x = cluster,
                y = percent,
                fill = keycol
            )
        ) + 
        geom_bar(
            stat = "identity" ,
            position = ggplot2::position_stack()
        ) +
        geom_text(
            aes(
                label = n,
                y = percent
            ),
            size = 6,
            position = position_stack(vjust = 0.5)
        ) +
        labs(
            x = "Cluster",
            y = "%",
            fill = title_case(feature)
        ) +
        theme_bw() + 
        theme(
            text = element_text(size = 20),
            panel.grid.major.x = element_blank()
        )
    return(plot)
}

characterize_solution <- function(solution, data_list, plotname) {
    # Generating the required full dataframe
    cluster_df <- get_cluster_df(solution)
    data_df <- collapse_dl(data_list)
    full_data <- dplyr::inner_join(cluster_df, data_df, by = "subjectkey")
    full_data$"cluster" <- factor(full_data$"cluster")
    # Re-coding variables
    full_data$"sex"[full_data$"sex" == 0] <- "F"
    full_data$"sex"[full_data$"sex" == 1] <- "M"
    full_data$"race"[full_data$"race" == 0] <- "White"
    full_data$"race"[full_data$"race" == 1] <- "Non-White"
    # Identifying features to plot 
    features <- colnames(full_data)[3:length(colnames(full_data))]
    plot_list <- list()
    for (i in 1:length(features)) {
        feature <- features[[i]]
        feature_col <- full_data[, feature]
        nvals <- length(unique(feature_col))
        if (is.numeric(feature_col)) {
            plot <- jitter_plot(full_data, feature)
        } else {
            plot <- bar_plot(full_data, feature)
        }
        #ggsave(
        #    plot = plot,
        #    fig_path(
        #        paste0(
        #            plotname,
        #            "_",
        #            feature,
        #            ".png"
        #        ),
        #        TRUE
        #    ),
        #    width = 7,
        #    height = 7
        #)
        plot_list[[i]] <- plot
        names(plot_list)[[i]] <- feature
    }
    return(plot_list)
}

mc_b_plots <- characterize_solution(
    top_mc_b_solution,
    all_data_list_m1,
    "mtbi_mc_b"
)

outcome_plots <- function(plot_list) {
    pw <- list(
        #plot_list$"mtbi_mem_daze",
        #plot_list$"mtbi_loc",
        #plot_list$"age",
        #plot_list$"mtbi_age",
        #plot_list$"household_income",
        #plot_list$"pubertal_status",
        #plot_list$"headache_history",
        #plot_list$"sex",
        #plot_list$"previous_mtbis",
        #plot_list$"brain_volume",
        #plot_list$"cortical_thickness",
        #plot_list$"cortical_sa",
        #plot_list$"major_wm_ndi",
        #plot_list$"pericortical_wm_ndi",
        #plot_list$"fmri_cort_cors",
        #plot_list$"race",
        #plot_list$"fmri_cort_subcort_cors",
        #plot_list$"same_sex_friend",
        #plot_list$"opp_sex_friend",
        #plot_list$"same_sex_close_friend",
        #plot_list$"opp_sex_close_friend",
        #plot_list$"weekend_screentime",
        #plot_list$"weekday_screentime",
        #plot_list$"mtbi_mechanism",
        #plot_list$"school_programs",
        #plot_list$"non_school_programs",
        #plot_list$"private_instruction",
        #plot_list$"programs_this_year",
        #plot_list$"exercise_time",
        #plot_list$"prosocial_considerate",
        #plot_list$"prosocial_helps_hurt",
        #plot_list$"prosocial_helpful",
        #plot_list$"family_fight",
        #plot_list$"family_angry",
        #plot_list$"family_throw",
        #plot_list$"family_temper",
        #plot_list$"family_criticize",
        #plot_list$"family_hit",
        #plot_list$"family_peaceful",
        #plot_list$"family_outdo",
        #plot_list$"family_yell",
        #plot_list$"parent_perstr",
        #plot_list$"parent_anxdep",
        #plot_list$"parent_withdrawn",
        #plot_list$"parent_somatic",
        #plot_list$"parent_thought",
        #plot_list$"parent_attention",
        #plot_list$"parent_aggressive",
        #plot_list$"parent_intrusive",
        #plot_list$"parent_depress",
        #plot_list$"parent_anxdisord",
        #plot_list$"parent_avoidant",
        #plot_list$"parent_antisocial",
        #plot_list$"parent_hyperactive",
        plot_list$"cbcl_anxdep",
        plot_list$"cbcl_withdep",
        plot_list$"cbcl_somatic",
        plot_list$"cbcl_social",
        plot_list$"cbcl_thought",
        plot_list$"cbcl_attention",
        plot_list$"cbcl_rulebreak",
        plot_list$"cbcl_aggressive",
        plot_list$"sds_sleep"
    ) |> wrap_plots()
    pw
}

mc_b_outcome_plots <- outcome_plots(mc_b_plots)

mc_b_outcome_plots


input_plots <- function(plot_list) {
    pw <- list(
        plot_list$"mtbi_mem_daze",
        plot_list$"mtbi_loc",
        plot_list$"age",
        plot_list$"mtbi_age",
        plot_list$"household_income",
        plot_list$"pubertal_status",
        plot_list$"headache_history",
        plot_list$"sex",
        plot_list$"previous_mtbis",
        plot_list$"brain_volume",
        plot_list$"cortical_thickness",
        plot_list$"cortical_sa",
        plot_list$"major_wm_ndi",
        plot_list$"pericortical_wm_ndi",
        plot_list$"fmri_cort_cors",
        plot_list$"race",
        plot_list$"fmri_cort_subcort_cors",
        plot_list$"same_sex_friend",
        plot_list$"opp_sex_friend",
        plot_list$"same_sex_close_friend",
        plot_list$"opp_sex_close_friend",
        plot_list$"weekend_screentime",
        plot_list$"weekday_screentime",
        plot_list$"mtbi_mechanism",
        plot_list$"school_programs",
        plot_list$"non_school_programs",
        plot_list$"private_instruction",
        plot_list$"programs_this_year",
        plot_list$"exercise_time",
        plot_list$"prosocial_considerate",
        plot_list$"prosocial_helps_hurt",
        plot_list$"prosocial_helpful",
        plot_list$"family_fight",
        plot_list$"family_angry",
        plot_list$"family_throw",
        plot_list$"family_temper",
        plot_list$"family_criticize",
        plot_list$"family_hit",
        plot_list$"family_peaceful",
        plot_list$"family_outdo",
        plot_list$"family_yell",
        plot_list$"parent_perstr",
        plot_list$"parent_anxdep",
        plot_list$"parent_withdrawn",
        plot_list$"parent_somatic",
        plot_list$"parent_thought",
        plot_list$"parent_attention",
        plot_list$"parent_aggressive",
        plot_list$"parent_intrusive",
        plot_list$"parent_depress",
        plot_list$"parent_anxdisord",
        plot_list$"parent_avoidant",
        plot_list$"parent_antisocial",
        plot_list$"parent_hyperactive"
    ) |> wrap_plots()
    pw
}

mc_b_input_plots <- input_plots(mc_b_plots)
mc_b_input_plots




mc_b_all_plots <- mtbi_plot_layout(mc_b_plots)
mc_b_all_plots

ggsave(
    plot = mc_b_all_plots,
    fig_path("mc_b_all_plots.png", TRUE),
    width = 35,
    height = 25
)

mc_b_main_plots <- list(
    mc_b_plots$"pubertal_status",
    mc_b_plots$"brain_volume",
    mc_b_plots$"sex",
    mc_b_plots$"weekday_screentime",
    mc_b_plots$"household_income",
    mc_b_plots$"race",
    mc_b_plots$"family_fight",
    mc_b_plots$"headache_history",
    mc_b_plots$"mtbi_loc"
) |> wrap_plots()

mc_b_main_plots

stars <- function(comparisons) {
    pairs <- strsplit(comparisons, ", ")[[1]]
    comparisons <- lapply(
        pairs,
        function(pair) {
            strsplit(pair, "-")[[1]]
        }
    )
    geom_signif(
        comparisons = comparisons,
        map_signif_level = TRUE,
        step_increase = 0.1,
        vjust = 0.5,
        colour = "black",
        size = 1,
        textsize = 10
    )
}

mc_b_plots$"headache_history" + stars("1-3, 2-3")


# Now the same plot, but with bigger stars:

names(mc_b_plots)

mc_b_plots_pw <- wrap_plots(mc_b_plots)

ggsave(
    plot = mc_b_plots_pw,
    fig_path("mtbi_mc_b_plots.png", TRUE)
)




bar_plot(z, "cbcl_anxdep")

bar_plot(z, "mtbi_mechanism")

jitter_plot(z, "cbcl_anxdep")

scatter_plot(z, "parent_hyperactive")


fit <- aov(mpg ~ gear, data = mtcars)
summary(fit)
p <- ggplot(mtcars, aes(x = factor(gear), y = mpg, fill = factor(gear))) +
  geom_boxplot() +
  theme_minimal()

p + stat_compare_means(comparisons = list(c("3", "4"), c("3", "5"), c("4", "5")), method = "anova")



ggplot(
    iris,
    aes(x=Species, y=Sepal.Length)) + geom_boxplot() +
    geom_signif(comparisons = list(c("versicolor", "virginica")), map_signif_level=TRUE)





```


