# Imputation, QCing, and CBCL thresholding

To keep things simple, I keep the longitudinal imputation separate from the baseline imputation.
In some ways, the longitudinal analyses are validating steps to the clustering.
That provides some further rationale for keeping them separate.

Questions I'm trying to answer with the longitudinal data:

1. Was the baseline clustering informative for long-term outcomes?
2. Do matched unij subjects to the mTBI group experience more mTBIs by T2 than the other unij subjects?
3. Is the clustering of the longitudinal sample using their baseline (pre-injury) equally informative as using their longitudinal (post-injury) data?

## Loading in data

```{r}
library(abcdutils)
library(here)
library(readr)
library(metasnf)
library(mice)
library(rlist)
library(visdat)

# The path_maker function helps with managing and date stamping long paths. The
# functions are just used here to help with reading and writing data. See
# ?path_maker for more information.
input_path <- path_maker(here(paste0("data/abcd/inputs")))
core_path <- path_maker(here(paste0("data/abcd/core")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))

source("abcd/helper_functions.R")

iread <- function(path) {
    return(read_csv(input_path(path)))
}

iwrite <- function(data, path) {
    write_csv(data, input_path(path, date = TRUE))
}
```

```{r}
# CHECKPOINT
lmtb_subs_wt2 <- readRDS(sub_path("2025_09_15_lmtb_subs_wt2.rds"))
lunj_subs_wt2 <- readRDS(sub_path("2025_09_15_lunj_subs_wt2.rds"))
mtbi_subs_wt2 <- readRDS(sub_path("2025_09_15_mtbi_subs_wt2.rds"))
unij_subs_wt2 <- readRDS(sub_path("2025_09_15_unij_subs_wt2.rds"))
```

```{r}
# Just use 1st imputation.
all_dls_h_ns <- readRDS(proc_path("2025_09_11_all_dls_h_no_sibs.rds"))

# Baseline data
unij_dl <- all_dls_h_ns$"unij_all_u_dls"$"imp_1"
mtbi_dl <- merge(
    all_dls_h_ns$"mtbi_der_u_dls"$"imp_4",
    all_dls_h_ns$"mtbi_val_u_dls"$"imp_1"
)
```

```{r}
strip_sub_prefix <- function(df) {
    df <- df |>
        dplyr::mutate(uid = gsub("uid_", "", uid)) |>
        dplyr::rename("subjectkey" = "uid") |>
        tibble::tibble()
    return(tibble::tibble(df))
}

# LONG MTBI 0
# as_loc not existent
# as_mechanism not existent
# as_mem_daze not existent
# mtbi_age not existent
# mtbi_count not existent
lmtb_cbcl_0              <- iread("2025_09_15_lmtb_cbcl_0.csv")
lmtb_d_income_0          <- iread("2025_09_15_lmtb_d_income_0.csv")
lmtb_d_interview_age_0   <- iread("2025_09_15_lmtb_d_interview_age_0.csv")
lmtb_d_pubertal_status_0 <- iread("2025_09_15_lmtb_d_pubertal_status_0.csv")
lmtb_d_race_0            <- iread("2025_09_15_lmtb_d_race_0.csv")
lmtb_d_sex_0             <- iread("2025_09_15_lmtb_d_sex_0.csv")
lmtb_dm_wmnd_0           <- iread("2025_09_15_lmtb_dm_wmnd_0.csv")
lmtb_mh_headaches_0      <- iread("2025_09_15_lmtb_mh_headaches_0.csv")
lmtb_p_exercise_0        <- iread("2025_09_15_lmtb_p_exercise_0.csv")
lmtb_p_fam_fn_0          <- iread("2025_09_15_lmtb_p_fam_fn_0.csv")
lmtb_p_friends_0         <- iread("2025_09_15_lmtb_p_friends_0.csv")
lmtb_p_parent_psych_0    <- iread("2025_09_15_lmtb_p_parent_psych_0.csv")
lmtb_p_prosocial_0       <- iread("2025_09_15_lmtb_p_prosocial_0.csv")
lmtb_p_screen_time_0     <- iread("2025_09_15_lmtb_p_screen_time_0.csv")
lmtb_p_sports_0          <- iread("2025_09_15_lmtb_p_sports_0.csv")
lmtb_rm_gord_cor_0       <- iread("2025_09_15_lmtb_rm_gord_cor_0.csv")
lmtb_rm_subc_cor_0       <- iread("2025_09_15_lmtb_rm_subc_cor_0.csv")
lmtb_sds_0               <- iread("2025_09_15_lmtb_sds_0.csv")
lmtb_sm_cort_sa_0        <- iread("2025_09_15_lmtb_sm_cort_sa_0.csv")
lmtb_sm_cort_t_0         <- iread("2025_09_15_lmtb_sm_cort_t_0.csv")
lmtb_sm_subc_v_0         <- iread("2025_09_15_lmtb_sm_subc_v_0.csv")
lmtb_family              <- iread("2025_09_15_lmtb_family.csv")
lmtb_scanner_0           <- iread("2025_09_15_lmtb_scanner_0.csv")
lmtb_site_0              <- iread("2025_09_15_lmtb_site_0.csv")


# LONG MTBI L
lmtb_as_loc_l            <- iread("2025_09_15_lmtb_as_loc_l.csv")
lmtb_as_mechanism_l      <- iread("2025_09_15_lmtb_as_mechanism_l.csv")
lmtb_as_mem_daze_l       <- iread("2025_09_15_lmtb_as_mem_daze_l.csv")
lmtb_cbcl_l              <- iread("2025_09_15_lmtb_cbcl_l.csv")
lmtb_d_income_l          <- iread("2025_09_15_lmtb_d_income_l.csv")
lmtb_d_interview_age_l   <- iread("2025_09_15_lmtb_d_interview_age_l.csv")
lmtb_d_mtbi_age_l        <- iread("2025_09_15_lmtb_d_mtbi_age_l.csv")
lmtb_d_pubertal_status_l <- iread("2025_09_15_lmtb_d_pubertal_status_l.csv")
lmtb_d_race_l            <- iread("2025_09_15_lmtb_d_race_0.csv")
lmtb_d_sex_l             <- iread("2025_09_15_lmtb_d_sex_0.csv")
lmtb_dm_wmnd_l           <- iread("2025_09_15_lmtb_dm_wmnd_l.csv")
lmtb_mh_headaches_l      <- iread("2025_09_15_lmtb_mh_headaches_l.csv")
lmtb_mh_mtbi_count_l     <- iread("2025_09_15_lmtb_mh_mtbi_count_l.csv")
lmtb_p_exercise_l        <- iread("2025_09_15_lmtb_p_exercise_l.csv")
lmtb_p_fam_fn_l          <- iread("2025_09_15_lmtb_p_fam_fn_l.csv")
lmtb_p_friends_l         <- iread("2025_09_15_lmtb_p_friends_l.csv")
lmtb_p_parent_psych_l    <- iread("2025_09_15_lmtb_p_parent_psych_l.csv")
lmtb_p_prosocial_l       <- iread("2025_09_15_lmtb_p_prosocial_l.csv")
lmtb_p_screen_time_l     <- iread("2025_09_15_lmtb_p_screen_time_l.csv")
lmtb_p_sports_l          <- iread("2025_09_15_lmtb_p_sports_l.csv")
lmtb_rm_gord_cor_l       <- iread("2025_09_15_lmtb_rm_gord_cor_l.csv")
lmtb_rm_subc_cor_l       <- iread("2025_09_15_lmtb_rm_subc_cor_l.csv")
lmtb_sds_l               <- iread("2025_09_15_lmtb_sds_l.csv")
lmtb_sm_cort_sa_l        <- iread("2025_09_15_lmtb_sm_cort_sa_l.csv")
lmtb_sm_cort_t_l         <- iread("2025_09_15_lmtb_sm_cort_t_l.csv")
lmtb_sm_subc_v_l         <- iread("2025_09_15_lmtb_sm_subc_v_l.csv")
lmtb_scanner_l           <- iread("2025_09_15_lmtb_scanner_l.csv")
lmtb_site_l              <- iread("2025_09_15_lmtb_site_l.csv")

# BASE MTBI L
# as_loc not extracted
# as_mechanism not extracted
# as_mem_daze not extracted
# mtbi_age not extracted
# mtbi_count not extracted
mtbi_cbcl_l              <- iread("2025_09_15_mtbi_cbcl_l.csv")
mtbi_d_income_l          <- iread("2025_09_15_mtbi_d_income_l.csv")
mtbi_d_interview_age_l   <- iread("2025_09_15_mtbi_d_interview_age_l.csv")
mtbi_d_pubertal_status_l <- iread("2025_09_15_mtbi_d_pubertal_status_l.csv")
mtbi_dm_wmnd_l           <- iread("2025_09_15_mtbi_dm_wmnd_l.csv")
mtbi_mh_headaches_l      <- iread("2025_09_15_mtbi_mh_headaches_l.csv")
mtbi_p_exercise_l        <- iread("2025_09_15_mtbi_p_exercise_l.csv")
mtbi_p_fam_fn_l          <- iread("2025_09_15_mtbi_p_fam_fn_l.csv")
mtbi_p_friends_l         <- iread("2025_09_15_mtbi_p_friends_l.csv")
mtbi_p_parent_psych_l    <- iread("2025_09_15_mtbi_p_parent_psych_l.csv")
mtbi_p_prosocial_l       <- iread("2025_09_15_mtbi_p_prosocial_l.csv")
mtbi_p_screen_time_l     <- iread("2025_09_15_mtbi_p_screen_time_l.csv")
mtbi_p_sports_l          <- iread("2025_09_15_mtbi_p_sports_l.csv")
mtbi_rm_gord_cor_l       <- iread("2025_09_15_mtbi_rm_gord_cor_l.csv")
mtbi_rm_subc_cor_l       <- iread("2025_09_15_mtbi_rm_subc_cor_l.csv")
mtbi_sds_l               <- iread("2025_09_15_mtbi_sds_l.csv")
mtbi_sm_cort_sa_l        <- iread("2025_09_15_mtbi_sm_cort_sa_l.csv")
mtbi_sm_cort_t_l         <- iread("2025_09_15_mtbi_sm_cort_t_l.csv")
mtbi_sm_subc_v_l         <- iread("2025_09_15_mtbi_sm_subc_v_l.csv")
mtbi_scanner_l           <- iread("2025_09_15_mtbi_scanner_l.csv")
mtbi_site_l              <- iread("2025_09_15_mtbi_site_l.csv")

# BASE unij L
# as_loc not existent
# as_mechanism not existent
# as_mem_daze not existent
# mtbi_age not existent
# mtbi_count not existent
unij_cbcl_l              <- iread("2025_09_15_unij_cbcl_l.csv")
unij_d_income_l          <- iread("2025_09_15_unij_d_income_l.csv")
unij_d_interview_age_l   <- iread("2025_09_15_unij_d_interview_age_l.csv")
unij_d_pubertal_status_l <- iread("2025_09_15_unij_d_pubertal_status_l.csv")
unij_dm_wmnd_l           <- iread("2025_09_15_unij_dm_wmnd_l.csv")
unij_mh_headaches_l      <- iread("2025_09_15_unij_mh_headaches_l.csv")
unij_p_exercise_l        <- iread("2025_09_15_unij_p_exercise_l.csv")
unij_p_fam_fn_l          <- iread("2025_09_15_unij_p_fam_fn_l.csv")
unij_p_friends_l         <- iread("2025_09_15_unij_p_friends_l.csv")
unij_p_parent_psych_l    <- iread("2025_09_15_unij_p_parent_psych_l.csv")
unij_p_prosocial_l       <- iread("2025_09_15_unij_p_prosocial_l.csv")
unij_p_screen_time_l     <- iread("2025_09_15_unij_p_screen_time_l.csv")
unij_p_sports_l          <- iread("2025_09_15_unij_p_sports_l.csv")
unij_rm_gord_cor_l       <- iread("2025_09_15_unij_rm_gord_cor_l.csv")
unij_rm_subc_cor_l       <- iread("2025_09_15_unij_rm_subc_cor_l.csv")
unij_sds_l               <- iread("2025_09_15_unij_sds_l.csv")
unij_sm_cort_sa_l        <- iread("2025_09_15_unij_sm_cort_sa_l.csv")
unij_sm_cort_t_l         <- iread("2025_09_15_unij_sm_cort_t_l.csv")
unij_sm_subc_v_l         <- iread("2025_09_15_unij_sm_subc_v_l.csv")
unij_scanner_l           <- iread("2025_09_15_unij_scanner_l.csv")
unij_site_l              <- iread("2025_09_15_unij_site_l.csv")

# Race and sex are extracted from pre-imputed data
mtbi_d_race_l <- strip_sub_prefix(mtbi_dl$"d_race"$"data")
mtbi_d_sex_l  <- strip_sub_prefix(mtbi_dl$"d_sex"$"data")
unij_d_race_l <- strip_sub_prefix(unij_dl$"d_race"$"data")
unij_d_sex_l  <- strip_sub_prefix(unij_dl$"d_sex"$"data")

mtbi_d_race_l <- dplyr::filter(mtbi_d_race_l, subjectkey %in% mtbi_subs_wt2)
mtbi_d_sex_l <- dplyr::filter(mtbi_d_sex_l, subjectkey %in% mtbi_subs_wt2)
unij_d_race_l <- dplyr::filter(unij_d_race_l, subjectkey %in% unij_subs_wt2)
unij_d_sex_l <- dplyr::filter(unij_d_sex_l, subjectkey %in% unij_subs_wt2)
```

# QC

```{r}
# QC data
mri_y_qc_incl <- abcd_load(core_path("imaging/mri_y_qc_incl.csv"))
```

```{r}
lmtb_smri_pass_0 <- get_qc_data(
    mri_y_qc_incl,
    t = 0,
    subjects = lmtb_subs_wt2,
    type = "t1w"
)$"pass"

lmtb_smri_pass_l <- get_qc_data(
    mri_y_qc_incl,
    t = 2,
    subjects = lmtb_subs_wt2,
    type = "t1w"
)$"pass"

mtbi_smri_pass_l <- get_qc_data(
    mri_y_qc_incl,
    t = 2,
    subjects = mtbi_subs_wt2,
    type = "t1w"
)$"pass"

unij_smri_pass_l <- get_qc_data(
    mri_y_qc_incl,
    t = 2,
    subjects = unij_subs_wt2,
    type = "t1w"
)$"pass"

lmtb_dmri_pass_0 <- get_qc_data(
    mri_y_qc_incl,
    t = 0,
    subjects = lmtb_subs_wt2,
    type = "dmri"
)$"pass"

lmtb_dmri_pass_l <- get_qc_data(
    mri_y_qc_incl,
    t = 2,
    subjects = lmtb_subs_wt2,
    type = "dmri"
)$"pass"

mtbi_dmri_pass_l <- get_qc_data(
    mri_y_qc_incl,
    t = 2,
    subjects = mtbi_subs_wt2,
    type = "dmri"
)$"pass"

unij_dmri_pass_l <- get_qc_data(
    mri_y_qc_incl,
    t = 2,
    subjects = unij_subs_wt2,
    type = "dmri"
)$"pass"

lmtb_rmri_pass_0 <- get_qc_data(
    mri_y_qc_incl,
    t = 0,
    subjects = lmtb_subs_wt2,
    type = "rsfmri"
)$"pass"

lmtb_rmri_pass_l <- get_qc_data(
    mri_y_qc_incl,
    t = 2,
    subjects = lmtb_subs_wt2,
    type = "rsfmri"
)$"pass"

mtbi_rmri_pass_l <- get_qc_data(
    mri_y_qc_incl,
    t = 2,
    subjects = mtbi_subs_wt2,
    type = "rsfmri"
)$"pass"

unij_rmri_pass_l <- get_qc_data(
    mri_y_qc_incl,
    t = 2,
    subjects = unij_subs_wt2,
    type = "rsfmri"
)$"pass"

# rs-fMRI
lmtb_sm_subc_v_qc_0   <- filter(lmtb_sm_subc_v_0,   subjectkey %in% lmtb_smri_pass_0)
lmtb_sm_cort_t_qc_0   <- filter(lmtb_sm_cort_t_0,   subjectkey %in% lmtb_smri_pass_0)
lmtb_sm_cort_sa_qc_0  <- filter(lmtb_sm_cort_sa_0,  subjectkey %in% lmtb_smri_pass_0)
lmtb_dm_wmnd_qc_0     <- filter(lmtb_dm_wmnd_0,     subjectkey %in% lmtb_dmri_pass_0)
lmtb_rm_gord_cor_qc_0 <- filter(lmtb_rm_gord_cor_0, subjectkey %in% lmtb_rmri_pass_0)
lmtb_rm_subc_cor_qc_0 <- filter(lmtb_rm_subc_cor_0, subjectkey %in% lmtb_rmri_pass_0)
#
lmtb_sm_subc_v_qc_l   <- filter(lmtb_sm_subc_v_l,   subjectkey %in% lmtb_smri_pass_l)
lmtb_sm_cort_t_qc_l   <- filter(lmtb_sm_cort_t_l,   subjectkey %in% lmtb_smri_pass_l)
lmtb_sm_cort_sa_qc_l  <- filter(lmtb_sm_cort_sa_l,  subjectkey %in% lmtb_smri_pass_l)
lmtb_dm_wmnd_qc_l     <- filter(lmtb_dm_wmnd_l,     subjectkey %in% lmtb_dmri_pass_l)
lmtb_rm_gord_cor_qc_l <- filter(lmtb_rm_gord_cor_l, subjectkey %in% lmtb_rmri_pass_l)
lmtb_rm_subc_cor_qc_l <- filter(lmtb_rm_subc_cor_l, subjectkey %in% lmtb_rmri_pass_l)
#
mtbi_sm_subc_v_qc_l   <- filter(mtbi_sm_subc_v_l,   subjectkey %in% mtbi_smri_pass_l)
mtbi_sm_cort_t_qc_l   <- filter(mtbi_sm_cort_t_l,   subjectkey %in% mtbi_smri_pass_l)
mtbi_sm_cort_sa_qc_l  <- filter(mtbi_sm_cort_sa_l,  subjectkey %in% mtbi_smri_pass_l)
mtbi_dm_wmnd_qc_l     <- filter(mtbi_dm_wmnd_l,     subjectkey %in% mtbi_dmri_pass_l)
mtbi_rm_gord_cor_qc_l <- filter(mtbi_rm_gord_cor_l, subjectkey %in% mtbi_rmri_pass_l)
mtbi_rm_subc_cor_qc_l <- filter(mtbi_rm_subc_cor_l, subjectkey %in% mtbi_rmri_pass_l)
#
unij_sm_subc_v_qc_l   <- filter(unij_sm_subc_v_l,   subjectkey %in% unij_smri_pass_l)
unij_sm_cort_t_qc_l   <- filter(unij_sm_cort_t_l,   subjectkey %in% unij_smri_pass_l)
unij_sm_cort_sa_qc_l  <- filter(unij_sm_cort_sa_l,  subjectkey %in% unij_smri_pass_l)
unij_dm_wmnd_qc_l     <- filter(unij_dm_wmnd_l,     subjectkey %in% unij_dmri_pass_l)
unij_rm_gord_cor_qc_l <- filter(unij_rm_gord_cor_l, subjectkey %in% unij_rmri_pass_l)
unij_rm_subc_cor_qc_l <- filter(unij_rm_subc_cor_l, subjectkey %in% unij_rmri_pass_l)

iwrite(lmtb_sm_subc_v_qc_0,   "lmtb_sm_subc_v_qc_0.csv")
iwrite(lmtb_sm_cort_t_qc_0,   "lmtb_sm_cort_t_qc_0.csv")
iwrite(lmtb_sm_cort_sa_qc_0,  "lmtb_sm_cort_sa_qc_0.csv")
iwrite(lmtb_dm_wmnd_qc_0,     "lmtb_dm_wmnd_qc_0.csv")
iwrite(lmtb_rm_gord_cor_qc_0, "lmtb_rm_gord_cor_qc_0.csv")
iwrite(lmtb_rm_subc_cor_qc_0, "lmtb_rm_subc_cor_qc_0.csv")
#
iwrite(lmtb_sm_subc_v_qc_l,   "lmtb_sm_subc_v_qc_l.csv")
iwrite(lmtb_sm_cort_t_qc_l,   "lmtb_sm_cort_t_qc_l.csv")
iwrite(lmtb_sm_cort_sa_qc_l,  "lmtb_sm_cort_sa_qc_l.csv")
iwrite(lmtb_dm_wmnd_qc_l,     "lmtb_dm_wmnd_qc_l.csv")
iwrite(lmtb_rm_gord_cor_qc_l, "lmtb_rm_gord_cor_qc_l.csv")
iwrite(lmtb_rm_subc_cor_qc_l, "lmtb_rm_subc_cor_qc_l.csv")
#
iwrite(mtbi_sm_subc_v_qc_l,   "mtbi_sm_subc_v_qc_l.csv")
iwrite(mtbi_sm_cort_t_qc_l,   "mtbi_sm_cort_t_qc_l.csv")
iwrite(mtbi_sm_cort_sa_qc_l,  "mtbi_sm_cort_sa_qc_l.csv")
iwrite(mtbi_dm_wmnd_qc_l,     "mtbi_dm_wmnd_qc_l.csv")
iwrite(mtbi_rm_gord_cor_qc_l, "mtbi_rm_gord_cor_qc_l.csv")
iwrite(mtbi_rm_subc_cor_qc_l, "mtbi_rm_subc_cor_qc_l.csv")
#
iwrite(unij_sm_subc_v_qc_l,   "unij_sm_subc_v_qc_l.csv")
iwrite(unij_sm_cort_t_qc_l,   "unij_sm_cort_t_qc_l.csv")
iwrite(unij_sm_cort_sa_qc_l,  "unij_sm_cort_sa_qc_l.csv")
iwrite(unij_dm_wmnd_qc_l,     "unij_dm_wmnd_qc_l.csv")
iwrite(unij_rm_gord_cor_qc_l, "unij_rm_gord_cor_qc_l.csv")
iwrite(unij_rm_subc_cor_qc_l, "unij_rm_subc_cor_qc_l.csv")
```

```{r}
lmtb_sm_subc_v_qc_0   <- iread("2025_09_15_lmtb_sm_subc_v_qc_0.csv")
lmtb_sm_cort_t_qc_0   <- iread("2025_09_15_lmtb_sm_cort_t_qc_0.csv")
lmtb_sm_cort_sa_qc_0  <- iread("2025_09_15_lmtb_sm_cort_sa_qc_0.csv")
lmtb_dm_wmnd_qc_0     <- iread("2025_09_15_lmtb_dm_wmnd_qc_0.csv")
lmtb_rm_gord_cor_qc_0 <- iread("2025_09_15_lmtb_rm_gord_cor_qc_0.csv")
lmtb_rm_subc_cor_qc_0 <- iread("2025_09_15_lmtb_rm_subc_cor_qc_0.csv")

lmtb_sm_subc_v_qc_l   <- iread("2025_09_15_lmtb_sm_subc_v_qc_l.csv")
lmtb_sm_cort_t_qc_l   <- iread("2025_09_15_lmtb_sm_cort_t_qc_l.csv")
lmtb_sm_cort_sa_qc_l  <- iread("2025_09_15_lmtb_sm_cort_sa_qc_l.csv")
lmtb_dm_wmnd_qc_l     <- iread("2025_09_15_lmtb_dm_wmnd_qc_l.csv")
lmtb_rm_gord_cor_qc_l <- iread("2025_09_15_lmtb_rm_gord_cor_qc_l.csv")
lmtb_rm_subc_cor_qc_l <- iread("2025_09_15_lmtb_rm_subc_cor_qc_l.csv")

mtbi_sm_subc_v_qc_l   <- iread("2025_09_15_mtbi_sm_subc_v_qc_l.csv")
mtbi_sm_cort_t_qc_l   <- iread("2025_09_15_mtbi_sm_cort_t_qc_l.csv")
mtbi_sm_cort_sa_qc_l  <- iread("2025_09_15_mtbi_sm_cort_sa_qc_l.csv")
mtbi_dm_wmnd_qc_l     <- iread("2025_09_15_mtbi_dm_wmnd_qc_l.csv")
mtbi_rm_gord_cor_qc_l <- iread("2025_09_15_mtbi_rm_gord_cor_qc_l.csv")
mtbi_rm_subc_cor_qc_l <- iread("2025_09_15_mtbi_rm_subc_cor_qc_l.csv")

unij_sm_subc_v_qc_l   <- iread("2025_09_15_unij_sm_subc_v_qc_l.csv")
unij_sm_cort_t_qc_l   <- iread("2025_09_15_unij_sm_cort_t_qc_l.csv")
unij_sm_cort_sa_qc_l  <- iread("2025_09_15_unij_sm_cort_sa_qc_l.csv")
unij_dm_wmnd_qc_l     <- iread("2025_09_15_unij_dm_wmnd_qc_l.csv")
unij_rm_gord_cor_qc_l <- iread("2025_09_15_unij_rm_gord_cor_qc_l.csv")
unij_rm_subc_cor_qc_l <- iread("2025_09_15_unij_rm_subc_cor_qc_l.csv")
```

Building dataframes for imputation:

```{r}
lmtb_0_list <- list(
    "lmtb_cbcl"              = lmtb_cbcl_0,
    "lmtb_d_income"          = lmtb_d_income_0,
    "lmtb_d_interview_age"   = lmtb_d_interview_age_0,
    "lmtb_d_pubertal_status" = lmtb_d_pubertal_status_0,
    "lmtb_d_race"            = lmtb_d_race_0,
    "lmtb_d_sex"             = lmtb_d_sex_0,
    "lmtb_dm_wmnd_qc"        = lmtb_dm_wmnd_qc_0,
    "lmtb_mh_headaches"      = lmtb_mh_headaches_0,
    "lmtb_p_exercise"        = lmtb_p_exercise_0,
    "lmtb_p_fam_fn"          = lmtb_p_fam_fn_0,
    "lmtb_p_friends"         = lmtb_p_friends_0,
    "lmtb_p_parent_psych"    = lmtb_p_parent_psych_0,
    "lmtb_p_prosocial"       = lmtb_p_prosocial_0,
    "lmtb_p_screen_time"     = lmtb_p_screen_time_0,
    "lmtb_p_sports"          = lmtb_p_sports_0,
    "lmtb_rm_gord_cor_qc"    = lmtb_rm_gord_cor_qc_0,
    "lmtb_rm_subc_cor_qc"    = lmtb_rm_subc_cor_qc_0,
    "lmtb_scanner"           = lmtb_scanner_0,
    "lmtb_sds"               = lmtb_sds_0,
    "lmtb_sm_cort_sa_qc"     = lmtb_sm_cort_sa_qc_0,
    "lmtb_sm_cort_t_qc"      = lmtb_sm_cort_t_qc_0,
    "lmtb_sm_subc_v_qc"      = lmtb_sm_subc_v_qc_0
)
lmtb_0_df <- merge_df_list(lmtb_0_list, join = "full", uid = "subjectkey")
lmtb_0_df

lmtb_l_list <- list(
    "lmtb_as_loc"            = lmtb_as_loc_l,
    "lmtb_as_mechanism"      = lmtb_as_mechanism_l,
    "lmtb_as_mem_daze"       = lmtb_as_mem_daze_l,
    "lmtb_cbcl"              = lmtb_cbcl_l,
    "lmtb_d_income"          = lmtb_d_income_l,
    "lmtb_d_interview_age"   = lmtb_d_interview_age_l,
    "lmtb_d_mtbi_age"        = lmtb_d_mtbi_age_l,
    "lmtb_d_pubertal_status" = lmtb_d_pubertal_status_l,
    "lmtb_d_race"            = lmtb_d_race_l,
    "lmtb_d_sex"             = lmtb_d_sex_l,
    "lmtb_dm_wmnd_qc"        = lmtb_dm_wmnd_qc_l,
    "lmtb_mh_headaches"      = lmtb_mh_headaches_l,
    "lmtb_mh_mtbi_count"     = lmtb_mh_mtbi_count_l,
    "lmtb_p_exercise"        = lmtb_p_exercise_l,
    "lmtb_p_fam_fn"          = lmtb_p_fam_fn_l,
    "lmtb_p_friends"         = lmtb_p_friends_l,
    "lmtb_p_parent_psych"    = lmtb_p_parent_psych_l,
    "lmtb_p_prosocial"       = lmtb_p_prosocial_l,
    "lmtb_p_screen_time"     = lmtb_p_screen_time_l,
    "lmtb_p_sports"          = lmtb_p_sports_l,
    "lmtb_rm_gord_cor_qc"    = lmtb_rm_gord_cor_qc_l,
    "lmtb_rm_subc_cor_qc"    = lmtb_rm_subc_cor_qc_l,
    "lmtb_scanner"           = lmtb_scanner_l,
    "lmtb_sds"               = lmtb_sds_l,
    "lmtb_sm_cort_sa_qc"     = lmtb_sm_cort_sa_qc_l,
    "lmtb_sm_cort_t_qc"      = lmtb_sm_cort_t_qc_l,
    "lmtb_sm_subc_v_qc"      = lmtb_sm_subc_v_qc_l
)
lmtb_l_df <- merge_df_list(lmtb_l_list, join = "full", uid = "subjectkey")
lmtb_l_df

mtbi_l_list <- list(
    "mtbi_cbcl"              = mtbi_cbcl_l,
    "mtbi_d_income"          = mtbi_d_income_l,
    "mtbi_d_interview_age"   = mtbi_d_interview_age_l,
    "mtbi_d_pubertal_status" = mtbi_d_pubertal_status_l,
    "mtbi_d_race"            = mtbi_d_race_l,
    "mtbi_d_sex"             = mtbi_d_sex_l,
    "mtbi_dm_wmnd_qc"        = mtbi_dm_wmnd_qc_l,
    "mtbi_mh_headaches"      = mtbi_mh_headaches_l,
    "mtbi_p_exercise"        = mtbi_p_exercise_l,
    "mtbi_p_fam_fn"          = mtbi_p_fam_fn_l,
    "mtbi_p_friends"         = mtbi_p_friends_l,
    "mtbi_p_parent_psych"    = mtbi_p_parent_psych_l,
    "mtbi_p_prosocial"       = mtbi_p_prosocial_l,
    "mtbi_p_screen_time"     = mtbi_p_screen_time_l,
    "mtbi_p_sports"          = mtbi_p_sports_l,
    "mtbi_rm_gord_cor_qc"    = mtbi_rm_gord_cor_qc_l,
    "mtbi_rm_subc_cor_qc"    = mtbi_rm_subc_cor_qc_l,
    "mtbi_scanner"           = mtbi_scanner_l,
    "mtbi_sds"               = mtbi_sds_l,
    "mtbi_sm_cort_sa_qc"     = mtbi_sm_cort_sa_qc_l,
    "mtbi_sm_cort_t_qc"      = mtbi_sm_cort_t_qc_l,
    "mtbi_sm_subc_v_qc"      = mtbi_sm_subc_v_qc_l
)
mtbi_l_df <- merge_df_list(mtbi_l_list, join = "full", uid = "subjectkey")
mtbi_l_df

unij_l_list <- list(
    "unij_cbcl"              = unij_cbcl_l,
    "unij_d_income"          = unij_d_income_l,
    "unij_d_interview_age"   = unij_d_interview_age_l,
    "unij_d_pubertal_status" = unij_d_pubertal_status_l,
    "unij_d_race"            = unij_d_race_l,
    "unij_d_sex"             = unij_d_sex_l,
    "unij_dm_wmnd_qc"        = unij_dm_wmnd_qc_l,
    "unij_mh_headaches"      = unij_mh_headaches_l,
    "unij_p_exercise"        = unij_p_exercise_l,
    "unij_p_fam_fn"          = unij_p_fam_fn_l,
    "unij_p_friends"         = unij_p_friends_l,
    "unij_p_parent_psych"    = unij_p_parent_psych_l,
    "unij_p_prosocial"       = unij_p_prosocial_l,
    "unij_p_screen_time"     = unij_p_screen_time_l,
    "unij_p_sports"          = unij_p_sports_l,
    "unij_rm_gord_cor_qc"    = unij_rm_gord_cor_qc_l,
    "unij_rm_subc_cor_qc"    = unij_rm_subc_cor_qc_l,
    "unij_scanner"           = unij_scanner_l,
    "unij_sds"               = unij_sds_l,
    "unij_sm_cort_sa_qc"     = unij_sm_cort_sa_qc_l,
    "unij_sm_cort_t_qc"      = unij_sm_cort_t_qc_l,
    "unij_sm_subc_v_qc"      = unij_sm_subc_v_qc_l
)
unij_l_df <- merge_df_list(unij_l_list, join = "full", uid = "subjectkey")
unij_l_df

iwrite(lmtb_0_df, "lmtb_0_df.csv")
iwrite(lmtb_l_df, "lmtb_l_df.csv")
iwrite(mtbi_l_df, "mtbi_l_df.csv")
iwrite(unij_l_df, "unij_l_df.csv")
```

```{r}
# CHECKPOINT
lmtb_0_df <- data.frame(iread("2025_09_15_lmtb_0_df.csv"))
lmtb_l_df <- data.frame(iread("2025_09_15_lmtb_l_df.csv"))
mtbi_l_df <- data.frame(iread("2025_09_15_mtbi_l_df.csv"))
unij_l_df <- data.frame(iread("2025_09_15_unij_l_df.csv"))
```

Imputation functions from ch02.

```{r}
set.seed(42)
lmtb_imputed_0 <- run_imputation(lmtb_0_df, 1)
saveRDS(lmtb_imputed_0, proc_path("lmtb_imputed_0.rds", TRUE))
complete(lmtb_imputed_0$"imputed", action = "long", include = FALSE) |>
    missing_columns()

set.seed(42)
lmtb_imputed_l <- run_imputation(lmtb_l_df, 1)
saveRDS(lmtb_imputed_l, proc_path("lmtb_imputed_l.rds", TRUE))
complete(lmtb_imputed_l$"imputed", action = "long", include = FALSE) |>
    missing_columns()

set.seed(42)
mtbi_imputed_l <- run_imputation(mtbi_l_df, 1)
saveRDS(mtbi_imputed_l, proc_path("mtbi_imputed_l.rds", TRUE))
complete(mtbi_imputed_l$"imputed", action = "long", include = FALSE) |>
    missing_columns()

set.seed(42)
unij_imputed_l <- run_imputation(unij_l_df, 1)
saveRDS(unij_imputed_l, proc_path("unij_imputed_l.rds", TRUE))
complete(unij_imputed_l$"imputed", action = "long", include = FALSE) |>
    missing_columns()
```

```{r}
# CHECKPOINT
lmtb_imputed_0 <- readRDS(proc_path("2025_09_15_lmtb_imputed_0.rds"))
lmtb_imputed_l <- readRDS(proc_path("2025_09_15_lmtb_imputed_l.rds"))
mtbi_imputed_l <- readRDS(proc_path("2025_09_15_mtbi_imputed_l.rds"))
unij_imputed_l <- readRDS(proc_path("2025_09_15_unij_imputed_l.rds"))
```

```{r}
save_density_plots(
    missing_columns(lmtb_0_df),
    lmtb_imputed_0$"imputed",
    "lmtb_0_"
)

save_density_plots(
    missing_columns(lmtb_l_df),
    lmtb_imputed_l$"imputed",
    "lmtb_l_"
)

save_density_plots(
    missing_columns(mtbi_l_df),
    mtbi_imputed_l$"imputed",
    "mtbi_l_"
)

save_density_plots(
    missing_columns(unij_l_df),
    unij_imputed_l$"imputed",
    "unij_l_"
)
```


```{r}
complete_lmtb_0 <- complete(
    lmtb_imputed_0$"imputed",
    action = "long",
    include = TRUE
) |>
    dplyr::mutate("subjectkey" = rep(lmtb_subs_wt2, 6))

complete_lmtb_l <- complete(
    lmtb_imputed_l$"imputed",
    action = "long",
    include = TRUE
) |>
    dplyr::mutate("subjectkey" = rep(lmtb_subs_wt2, 6))

complete_mtbi_l <- complete(
    mtbi_imputed_l$"imputed",
    action = "long",
    include = TRUE
) |>
    dplyr::mutate("subjectkey" = rep(mtbi_subs_wt2, 6))

complete_unij_l <- complete(
    unij_imputed_l$"imputed",
    action = "long",
    include = TRUE
) |>
    dplyr::mutate("subjectkey" = rep(unij_subs_wt2, 6))

write_csv(complete_lmtb_0, input_path("complete_lmtb_0.csv", TRUE))
write_csv(complete_lmtb_l, input_path("complete_lmtb_l.csv", TRUE))
write_csv(complete_mtbi_l, input_path("complete_mtbi_l.csv", TRUE))
write_csv(complete_unij_l, input_path("complete_unij_l.csv", TRUE))
```

```{r}
# CHECKPOINT
complete_lmtb_0 <- read_csv(input_path("2025_09_15_complete_lmtb_0.csv"))
complete_lmtb_l <- read_csv(input_path("2025_09_15_complete_lmtb_l.csv"))
complete_mtbi_l <- read_csv(input_path("2025_09_15_complete_mtbi_l.csv"))
complete_unij_l <- read_csv(input_path("2025_09_15_complete_unij_l.csv"))
```

# mTBI subsetting

```{r}
extract_imputed <- function(original_df, imputed_df, partition) {
    return(imputed_df[imputed_df$".imp" == partition, colnames(original_df)])
}

parse_imputations <- function(original_df_list, complete_imputed_df, imps) {
    parsed_imputations <- original_df_list |>
        lapply(
            function(x) {
                imputations <- list()
                for (i in seq_len(imps)) {
                    imputations[[i]] <- extract_imputed(
                        x,
                        complete_imputed_df,
                        i - 1
                    )
                }
                names(imputations) <- paste0("imp_", seq_len(imps) - 1)
                return(imputations)
            }
        )
    names(parsed_imputations) <- gsub("_mtbi$", "", names(parsed_imputations))
    names(parsed_imputations) <- gsub("_unij$", "", names(parsed_imputations))
    return(parsed_imputations)
}

lmtb_0_pi <- parse_imputations(lmtb_0_list, complete_lmtb_0, 6)
lmtb_l_pi <- parse_imputations(lmtb_l_list, complete_lmtb_l, 6)
mtbi_l_pi <- parse_imputations(mtbi_l_list, complete_mtbi_l, 6)
unij_l_pi <- parse_imputations(unij_l_list, complete_unij_l, 6)

names(lmtb_0_pi) <- gsub("lmtb_", "", names(lmtb_0_pi))
names(lmtb_l_pi) <- gsub("lmtb_", "", names(lmtb_l_pi))
names(mtbi_l_pi) <- gsub("mtbi_", "", names(mtbi_l_pi))
names(unij_l_pi) <- gsub("unij_", "", names(unij_l_pi))

list.save(lmtb_0_pi, input_path("lmtb_0_pi.rds", TRUE))
list.save(lmtb_l_pi, input_path("lmtb_l_pi.rds", TRUE))
list.save(mtbi_l_pi, input_path("mtbi_l_pi.rds", TRUE))
list.save(unij_l_pi, input_path("unij_l_pi.rds", TRUE))
```

Re-reading:

```{r}
lmtb_0_pi <- list.load(input_path("2025_09_15_lmtb_0_pi.rds"))
lmtb_l_pi <- list.load(input_path("2025_09_15_lmtb_l_pi.rds"))
mtbi_l_pi <- list.load(input_path("2025_09_15_mtbi_l_pi.rds"))
unij_l_pi <- list.load(input_path("2025_09_15_unij_l_pi.rds"))
```

## Constructing data_lists

```{r}
mtbi_l_dls <- build_unij_dls(mtbi_l_pi)
mtbi_l_ols <- build_ols(mtbi_l_pi)

unij_l_dls <- build_unij_dls(unij_l_pi)
unij_l_ols <- build_ols(unij_l_pi)

lmtb_0_dls <- build_unij_dls(lmtb_0_pi)
lmtb_0_ols <- build_ols(lmtb_0_pi)

lmtb_l_dls <- build_mtbi_dls(lmtb_l_pi)
lmtb_l_ols <- build_ols(lmtb_l_pi)

all_long_dls <- list(
    "lmtb_0_dls" = lmtb_0_dls,
    "lmtb_l_dls" = lmtb_l_dls,
    "mtbi_l_dls" = mtbi_l_dls,
    "unij_l_dls" = unij_l_dls,
    "lmtb_0_ols" = lmtb_0_ols,
    "lmtb_l_ols" = lmtb_l_ols,
    "mtbi_l_ols" = mtbi_l_ols,
    "unij_l_ols" = unij_l_ols
)
```

## Renaming the initial data

```{r}
name_changes <- c(
    "age"                   = "interview_age",
    "brain_volume"          = "smri_vol_scs_wholeb",
    "cbcl_aggressive"       = "cbcl_scr_syn_aggressive_r",
    "cbcl_anxdep"           = "cbcl_scr_syn_anxdep_r",
    "cbcl_attention"        = "cbcl_scr_syn_attention_r",
    "cbcl_rulebreak"        = "cbcl_scr_syn_rulebreak_r",
    "cbcl_social"           = "cbcl_scr_syn_social_r",
    "cbcl_somatic"          = "cbcl_scr_syn_somatic_r",
    "cbcl_thought"          = "cbcl_scr_syn_thought_r",
    "cbcl_withdep"          = "cbcl_scr_syn_withdep_r",
    "cortical_sa"           = "smri_area_cdk_total",
    "cortical_t"            = "smri_thick_cdk_mean",
    "family_angry_p"        = "q2_angry_p",
    "family_angry_y"        = "q2_angry_y",
    "family_criticize_p"    = "q5_criticize_p",
    "family_criticize_y"    = "q5_criticize_y",
    "family_fight_p"        = "q1_fight_p",
    "family_fight_y"        = "q1_fight_y",
    "family_hit_p"          = "q6_hit_p",
    "family_hit_y"          = "q6_hit_y",
    "family_outdo_p"        = "q8_outdo_p",
    "family_outdo_y"        = "q8_outdo_y",
    "family_peaceful_p"     = "q7_peaceful_p",
    "family_peaceful_y"     = "q7_peaceful_y",
    "family_temper_p"       = "q4_temper_p",
    "family_temper_y"       = "q4_temper_y",
    "family_throw_p"        = "q3_throw_p",
    "family_throw_y"        = "q3_throw_y",
    "family_yell_p"         = "q9_yell_p",
    "family_yell_y"         = "q9_yell_y",
    "fmri_dan_within_cor"   = "rsfmri_c_ngd_dla_ngd_dla",
    "fmri_dmn_fpn_cor"      = "rsfmri_c_ngd_dt_ngd_fo",
    "fmri_dmn_within_cor"   = "rsfmri_c_ngd_dt_ngd_dt",
    "fmri_fpn_lamyg_cor"    = "rsfmri_cor_ngd_fopa_scs_aglh",
    "fmri_fpn_ramyg_cor"    = "rsfmri_cor_ngd_fopa_scs_agrh",
    "fmri_fpn_within_cor"   = "rsfmri_c_ngd_fo_ngd_fo",
    "fmri_san_within_cor"   = "rsfmri_c_ngd_sa_ngd_sa",
    "headache_history"      = "headache",
    "major_wm_ndi"          = "dmri_rsirnd_fib_allfib",
    "mtbi_age"              = "latest_mtbi_age",
    "mtbi_loc"              = "latest_mtbi_loc",
    "mtbi_mechanism"        = "latest_mtbi_mechanism",
    "mtbi_mem_daze"         = "latest_mtbi_mem_daze",
    "opp_sex_close_friend"  = "os_close_friend",
    "opp_sex_friend"        = "os_friend",
    "parent_aggressive"     = "asr_scr_aggressive_r",
    "parent_antisocial"     = "asr_scr_antisocial_r",
    "parent_anxdep"         = "asr_scr_anxdep_r",
    "parent_anxdisord"      = "asr_scr_anxdisord_r",
    "parent_attention"      = "asr_scr_attention_r",
    "parent_avoidant"       = "asr_scr_avoidant_r",
    "parent_depress"        = "asr_scr_depress_r",
    "parent_hyperactive"    = "asr_scr_hyperactive_r",
    "parent_intrusive"      = "asr_scr_intrusive_r",
    "parent_perstr"         = "asr_scr_perstr_r",
    "parent_somatic"        = "asr_scr_somatic_r",
    "parent_thought"        = "asr_scr_thought_r",
    "parent_withdrawn"      = "asr_scr_withdrawn_r",
    "pericortical_wm_ndi"   = "dmri_rsirndwm_cdk_mean",
    "previous_mtbis"        = "mtbi_count",
    "same_sex_close_friend" = "ss_close_friend",
    "same_sex_friend"       = "ss_friend",
    "sds_sleep"             = "sds_p_ss_total",
    "weekday_screentime"    = "screentime_wkday_hrs",
    "weekend_screentime"    = "screentime_wknd_hrs"
)

all_long_dls <- all_long_dls |>
    lapply(
        function(data_lists_of_group) {
            lapply(
                data_lists_of_group,
                function(data_list) {
                    data_list <- as_data_list(rename_dl(data_list, name_changes))
                }
            )
        }
    )

# 2025-09-29
saveRDS(all_long_dls, input_path("all_long_dls.rds", TRUE))
```

```{r}
all_long_dls <- readRDS(input_path("2025_09_29_all_long_dls.rds"))
```

# Combat harmonization

```{r echo = FALSE}
library(neuroCombat)

combat_dl <- function(dl, ol, site_df, mean.only = FALSE) {
    neuro_components <- c(
        "n_subc_v",
        "n_cort_t",
        "n_cort_sa",
        "n_wmnd",
        "n_gord_cor",
        "n_subc_cor"
    )
    covariate_components <- c(
        "d_age",
        "d_sex",
        "d_income",
        "d_race",
        "d_pubertal"
    )
    neuro_fts <- c(
        "brain_volume",
        "cortical_t",
        "cortical_sa",
        "major_wm_ndi",
        "pericortical_wm_ndi",
        "fmri_dmn_within_cor",
        "fmri_dan_within_cor",
        "fmri_fpn_within_cor",
        "fmri_san_within_cor",
        "fmri_dmn_fpn_cor",
        "fmri_fpn_lamyg_cor",
        "fmri_fpn_ramyg_cor"
    )
    neuroimaging_df <- as.data.frame(dl[neuro_components])
    covariate_df <- as.data.frame(c(dl[covariate_components], ol))
    site_df <- site_df |>
        dplyr::mutate(
            uid = paste0("uid_", subjectkey)
        ) |>
        dplyr::select(
            -subjectkey
        )
    all_data <- dplyr::inner_join(neuroimaging_df, covariate_df, by = "uid")
    all_data <- dplyr::inner_join(all_data, site_df, by = "uid")
    # 1. data to be harmonized (dat param)
    # 3. covariates
    my_mod <- dplyr::select(all_data[, colnames(covariate_df)], -uid)
    data_harmonized <- neuroCombat(
        dat = t(
            as.matrix(all_data[, neuro_fts])
        ),
        batch = all_data$"site_id",
        mod = model.matrix(
            ~ .,
            data = my_mod
        ),
        mean.only = mean.only
    )
    data_harmonized <- data.frame(t(data_harmonized$"dat.combat"))
    data_harmonized$"uid" <- all_data$"uid"
    #--------------------------------------------------------------------------
    # Updating data list
    harmonized_dl <- dlapply(
        dl,
        function(x) {
            if (any(neuro_fts %in% colnames(x$"data"))) {
                neuro_idx <- which(neuro_fts %in% colnames(x$"data")) 
                neuro_fts_in_x <- neuro_fts[neuro_idx]
                x$"data"[, neuro_fts_in_x] <- data_harmonized[, neuro_fts_in_x]
            }
            return(x)
        }
    )
    return(harmonized_dl)
}

visualize_combat <- function(initial_dl, harmonized_dl, site_df) {
    site_df <- site_df |>
        dplyr::mutate(uid = paste0("uid_", subjectkey)) |>
        dplyr::select(-subjectkey)
    neuro_fts <- c(
        "brain_volume",
        "cortical_t",
        "cortical_sa",
        "major_wm_ndi",
        "pericortical_wm_ndi",
        "fmri_cort_cors",
        "fmri_cort_subcort_cors"
    )
    initial_df <- as.data.frame(initial_dl)
    harmonized_df <- as.data.frame(harmonized_dl)
    if (!all(initial_df$"uid" == harmonized_dl$"uid")) {
        stop("Mismatched UIDs.")
    }
    initial_df$"group" <- "initial"
    initial_df <- dplyr::inner_join(initial_df, site_df, by = "uid")
    harmonized_df$"group" <- "harmonized"
    harmonized_df <- dplyr::inner_join(harmonized_df, site_df, by = "uid")
    df <- dplyr::bind_rows(initial_df, harmonized_df)
    plot_list <- vector("list", length = length(neuro_fts))
    for (i in seq_along(neuro_fts)) {
        ft <- neuro_fts[i]
        plot <- df |>
            ggplot(
                aes(
                    x = .data[["site_id"]],
                    y = .data[[ft]],
                    color = .data[["group"]]
                )
            ) + 
            geom_boxplot(
                outlier.shape = NA,
                position = position_dodge(width = 0.8)
            ) +
            geom_point(
                position = position_dodge(width = 0.8),
                alpha = 0.6,
                size = 1.5
            ) +
            labs(
                x = "Site ID",
                color = "Group"
            ) +
            theme_minimal()
        plot_list[[i]] <- plot
    }
    return(plot_list)
} 

all_long_dls$"lmtb_0_dls"$"imp_1" <- combat_dl(all_long_dls$"lmtb_0_dls"$"imp_1", all_long_dls$"lmtb_0_ols"$"imp_1", lmtb_site_0)
all_long_dls$"lmtb_0_dls"$"imp_2" <- combat_dl(all_long_dls$"lmtb_0_dls"$"imp_2", all_long_dls$"lmtb_0_ols"$"imp_2", lmtb_site_0)
all_long_dls$"lmtb_0_dls"$"imp_3" <- combat_dl(all_long_dls$"lmtb_0_dls"$"imp_3", all_long_dls$"lmtb_0_ols"$"imp_3", lmtb_site_0)
all_long_dls$"lmtb_0_dls"$"imp_4" <- combat_dl(all_long_dls$"lmtb_0_dls"$"imp_4", all_long_dls$"lmtb_0_ols"$"imp_4", lmtb_site_0)
all_long_dls$"lmtb_0_dls"$"imp_5" <- combat_dl(all_long_dls$"lmtb_0_dls"$"imp_5", all_long_dls$"lmtb_0_ols"$"imp_5", lmtb_site_0)

all_long_dls$"lmtb_l_dls"$"imp_1" <- combat_dl(all_long_dls$"lmtb_l_dls"$"imp_1", all_long_dls$"lmtb_l_ols"$"imp_1", lmtb_site_l)
all_long_dls$"lmtb_l_dls"$"imp_2" <- combat_dl(all_long_dls$"lmtb_l_dls"$"imp_2", all_long_dls$"lmtb_l_ols"$"imp_2", lmtb_site_l)
all_long_dls$"lmtb_l_dls"$"imp_3" <- combat_dl(all_long_dls$"lmtb_l_dls"$"imp_3", all_long_dls$"lmtb_l_ols"$"imp_3", lmtb_site_l)
all_long_dls$"lmtb_l_dls"$"imp_4" <- combat_dl(all_long_dls$"lmtb_l_dls"$"imp_4", all_long_dls$"lmtb_l_ols"$"imp_4", lmtb_site_l)
all_long_dls$"lmtb_l_dls"$"imp_5" <- combat_dl(all_long_dls$"lmtb_l_dls"$"imp_5", all_long_dls$"lmtb_l_ols"$"imp_5", lmtb_site_l)

all_long_dls$"mtbi_l_dls"$"imp_1" <- combat_dl(all_long_dls$"mtbi_l_dls"$"imp_1", all_long_dls$"mtbi_l_ols"$"imp_1", mtbi_site_l)
all_long_dls$"mtbi_l_dls"$"imp_2" <- combat_dl(all_long_dls$"mtbi_l_dls"$"imp_2", all_long_dls$"mtbi_l_ols"$"imp_2", mtbi_site_l)
all_long_dls$"mtbi_l_dls"$"imp_3" <- combat_dl(all_long_dls$"mtbi_l_dls"$"imp_3", all_long_dls$"mtbi_l_ols"$"imp_3", mtbi_site_l)
all_long_dls$"mtbi_l_dls"$"imp_4" <- combat_dl(all_long_dls$"mtbi_l_dls"$"imp_4", all_long_dls$"mtbi_l_ols"$"imp_4", mtbi_site_l)
all_long_dls$"mtbi_l_dls"$"imp_5" <- combat_dl(all_long_dls$"mtbi_l_dls"$"imp_5", all_long_dls$"mtbi_l_ols"$"imp_5", mtbi_site_l)

all_long_dls$"unij_l_dls"$"imp_1" <- combat_dl(all_long_dls$"unij_l_dls"$"imp_1", all_long_dls$"unij_l_ols"$"imp_1", unij_site_l)
all_long_dls$"unij_l_dls"$"imp_2" <- combat_dl(all_long_dls$"unij_l_dls"$"imp_2", all_long_dls$"unij_l_ols"$"imp_2", unij_site_l)
all_long_dls$"unij_l_dls"$"imp_3" <- combat_dl(all_long_dls$"unij_l_dls"$"imp_3", all_long_dls$"unij_l_ols"$"imp_3", unij_site_l)
all_long_dls$"unij_l_dls"$"imp_4" <- combat_dl(all_long_dls$"unij_l_dls"$"imp_4", all_long_dls$"unij_l_ols"$"imp_4", unij_site_l)
all_long_dls$"unij_l_dls"$"imp_5" <- combat_dl(all_long_dls$"unij_l_dls"$"imp_5", all_long_dls$"unij_l_ols"$"imp_5", unij_site_l)

all_long_dls_h <- all_long_dls

names(all_long_dls_h) <- c(
    "lmtb_0_dls",
    "lmtb_l_dls",
    "mtbi_l_dls",
    "unij_l_dls",
    "lmtb_0_ols",
    "lmtb_l_ols",
    "mtbi_l_ols",
    "unij_l_ols"
)

saveRDS(all_long_dls_h, proc_path("all_long_dls_h.rds", TRUE))

all_long_dls_h <- readRDS(proc_path("2025_09_29_all_long_dls_h.rds"))
```

# Siblings drop

```{r}
import <- function(path) {
    return(abcdutils::abcd_load(core_path(path)))
}

abcd_y_lt <- import("abcd-general/abcd_y_lt.csv")

drop_random_siblings <- function(abcd_y_lt, subjects) {
    sibling_df <- abcd_y_lt |>
        filter_timepoint(t = 0) |>
        dplyr::select(subjectkey, rel_family_id) |>
        filter_subjects(subjects)
    sibling_df <- sibling_df[sample(nrow(sibling_df)), ]
    is_dup_family <- duplicated(sibling_df$"rel_family_id")
    siblings_removed <- sibling_df[!is_dup_family, ]
    return(siblings_removed$"subjectkey")
}

set.seed(42)
lmtb_subs_wt2_ns <- drop_random_siblings(abcd_y_lt, lmtb_subs_wt2)
length(lmtb_subs_wt2)    # 218
length(lmtb_subs_wt2_ns) # 218

set.seed(42)
lunj_subs_wt2_ns <- drop_random_siblings(abcd_y_lt, lunj_subs_wt2)
length(lunj_subs_wt2)    # 7610
length(lunj_subs_wt2_ns) # 6512

set.seed(42)
mtbi_subs_wt2_ns <- drop_random_siblings(abcd_y_lt, mtbi_subs_wt2)
length(mtbi_subs_wt2)     # 407
length(mtbi_subs_wt2_ns)  # 403

set.seed(42)
unij_subs_wt2_ns <- drop_random_siblings(abcd_y_lt, unij_subs_wt2)
length(unij_subs_wt2)     # 8572
length(unij_subs_wt2_ns)  # 7278

saveRDS(lmtb_subs_wt2_ns, sub_path("lmtb_subs_wt2_ns.rds", TRUE))
saveRDS(lunj_subs_wt2_ns, sub_path("lunj_subs_wt2_ns.rds", TRUE))
saveRDS(mtbi_subs_wt2_ns, sub_path("mtbi_subs_wt2_ns.rds", TRUE))
saveRDS(unij_subs_wt2_ns, sub_path("unij_subs_wt2_ns.rds", TRUE))
```

```{r}
lmtb_subs_wt2_ns <- readRDS(sub_path("2025_09_15_lmtb_subs_wt2_ns.rds"))
lunj_subs_wt2_ns <- readRDS(sub_path("2025_09_15_lunj_subs_wt2_ns.rds"))
mtbi_subs_wt2_ns <- readRDS(sub_path("2025_09_15_mtbi_subs_wt2_ns.rds"))
unij_subs_wt2_ns <- readRDS(sub_path("2025_09_15_unij_subs_wt2_ns.rds"))

names(all_long_dls_h)

batch_uid_replace <- function(list_of_dls, uids) {
    uids <- paste0("uid_", uids)
    list_of_dls_new <- lapply(
        list_of_dls,
        function(dl) {
            new_dl <- dlapply(
                dl,
                function(x) {
                    x$"data" <- x$"data"[x$"data"$"uid" %in% uids, ]
                    return(x)
                }
            )
            return(new_dl)
        }
    )
    return(list_of_dls_new)
}

all_long_dls_h_ns <- all_long_dls_h

all_long_dls_h_ns[["lmtb_0_dls"]] <- batch_uid_replace(all_long_dls_h_ns[["lmtb_0_dls"]], lmtb_subs_wt2_ns)
all_long_dls_h_ns[["lmtb_l_dls"]] <- batch_uid_replace(all_long_dls_h_ns[["lmtb_l_dls"]], lmtb_subs_wt2_ns)
all_long_dls_h_ns[["mtbi_l_dls"]] <- batch_uid_replace(all_long_dls_h_ns[["mtbi_l_dls"]], mtbi_subs_wt2_ns)
all_long_dls_h_ns[["unij_l_dls"]] <- batch_uid_replace(all_long_dls_h_ns[["unij_l_dls"]], unij_subs_wt2_ns)
all_long_dls_h_ns[["lmtb_0_ols"]] <- batch_uid_replace(all_long_dls_h_ns[["lmtb_0_ols"]], lmtb_subs_wt2_ns)
all_long_dls_h_ns[["lmtb_l_ols"]] <- batch_uid_replace(all_long_dls_h_ns[["lmtb_l_ols"]], lmtb_subs_wt2_ns)
all_long_dls_h_ns[["mtbi_l_ols"]] <- batch_uid_replace(all_long_dls_h_ns[["mtbi_l_ols"]], mtbi_subs_wt2_ns)
all_long_dls_h_ns[["unij_l_ols"]] <- batch_uid_replace(all_long_dls_h_ns[["unij_l_ols"]], unij_subs_wt2_ns)

# 2025-09-26
saveRDS(all_long_dls_h_ns, proc_path("all_long_dls_h_ns.rds", TRUE))

# Fixing name of cortical_thickness -> cortical_t
all_long_dls_h_ns <- readRDS(proc_path("2025_09_26_all_long_dls_h_ns.rds"))

names(all_long_dls_h_ns[[1]][[1]])

names(all_long_dls_h_ns[[1]])

names(all_long_dls_h_ns)

all_long_dls_h_ns$"lmtb_0_dls"$"imp_1"$"n_cort_t"$"data" <- dplyr::rename(all_long_dls_h_ns$"lmtb_0_dls"$"imp_1"$"n_cort_t"$"data", "cortical_t" = "cortical_thickness")
all_long_dls_h_ns$"lmtb_0_dls"$"imp_2"$"n_cort_t"$"data" <- dplyr::rename(all_long_dls_h_ns$"lmtb_0_dls"$"imp_2"$"n_cort_t"$"data", "cortical_t" = "cortical_thickness")
all_long_dls_h_ns$"lmtb_0_dls"$"imp_3"$"n_cort_t"$"data" <- dplyr::rename(all_long_dls_h_ns$"lmtb_0_dls"$"imp_3"$"n_cort_t"$"data", "cortical_t" = "cortical_thickness")
all_long_dls_h_ns$"lmtb_0_dls"$"imp_4"$"n_cort_t"$"data" <- dplyr::rename(all_long_dls_h_ns$"lmtb_0_dls"$"imp_4"$"n_cort_t"$"data", "cortical_t" = "cortical_thickness")
all_long_dls_h_ns$"lmtb_0_dls"$"imp_5"$"n_cort_t"$"data" <- dplyr::rename(all_long_dls_h_ns$"lmtb_0_dls"$"imp_5"$"n_cort_t"$"data", "cortical_t" = "cortical_thickness")
all_long_dls_h_ns$"lmtb_l_dls"$"imp_1"$"n_cort_t"$"data" <- dplyr::rename(all_long_dls_h_ns$"lmtb_l_dls"$"imp_1"$"n_cort_t"$"data", "cortical_t" = "cortical_thickness")
all_long_dls_h_ns$"lmtb_l_dls"$"imp_2"$"n_cort_t"$"data" <- dplyr::rename(all_long_dls_h_ns$"lmtb_l_dls"$"imp_2"$"n_cort_t"$"data", "cortical_t" = "cortical_thickness")
all_long_dls_h_ns$"lmtb_l_dls"$"imp_3"$"n_cort_t"$"data" <- dplyr::rename(all_long_dls_h_ns$"lmtb_l_dls"$"imp_3"$"n_cort_t"$"data", "cortical_t" = "cortical_thickness")
all_long_dls_h_ns$"lmtb_l_dls"$"imp_4"$"n_cort_t"$"data" <- dplyr::rename(all_long_dls_h_ns$"lmtb_l_dls"$"imp_4"$"n_cort_t"$"data", "cortical_t" = "cortical_thickness")
all_long_dls_h_ns$"lmtb_l_dls"$"imp_5"$"n_cort_t"$"data" <- dplyr::rename(all_long_dls_h_ns$"lmtb_l_dls"$"imp_5"$"n_cort_t"$"data", "cortical_t" = "cortical_thickness")
all_long_dls_h_ns$"mtbi_l_dls"$"imp_1"$"n_cort_t"$"data" <- dplyr::rename(all_long_dls_h_ns$"mtbi_l_dls"$"imp_1"$"n_cort_t"$"data", "cortical_t" = "cortical_thickness")
all_long_dls_h_ns$"mtbi_l_dls"$"imp_2"$"n_cort_t"$"data" <- dplyr::rename(all_long_dls_h_ns$"mtbi_l_dls"$"imp_2"$"n_cort_t"$"data", "cortical_t" = "cortical_thickness")
all_long_dls_h_ns$"mtbi_l_dls"$"imp_3"$"n_cort_t"$"data" <- dplyr::rename(all_long_dls_h_ns$"mtbi_l_dls"$"imp_3"$"n_cort_t"$"data", "cortical_t" = "cortical_thickness")
all_long_dls_h_ns$"mtbi_l_dls"$"imp_4"$"n_cort_t"$"data" <- dplyr::rename(all_long_dls_h_ns$"mtbi_l_dls"$"imp_4"$"n_cort_t"$"data", "cortical_t" = "cortical_thickness")
all_long_dls_h_ns$"mtbi_l_dls"$"imp_5"$"n_cort_t"$"data" <- dplyr::rename(all_long_dls_h_ns$"mtbi_l_dls"$"imp_5"$"n_cort_t"$"data", "cortical_t" = "cortical_thickness")
all_long_dls_h_ns$"unij_l_dls"$"imp_1"$"n_cort_t"$"data" <- dplyr::rename(all_long_dls_h_ns$"unij_l_dls"$"imp_1"$"n_cort_t"$"data", "cortical_t" = "cortical_thickness")
all_long_dls_h_ns$"unij_l_dls"$"imp_2"$"n_cort_t"$"data" <- dplyr::rename(all_long_dls_h_ns$"unij_l_dls"$"imp_2"$"n_cort_t"$"data", "cortical_t" = "cortical_thickness")
all_long_dls_h_ns$"unij_l_dls"$"imp_3"$"n_cort_t"$"data" <- dplyr::rename(all_long_dls_h_ns$"unij_l_dls"$"imp_3"$"n_cort_t"$"data", "cortical_t" = "cortical_thickness")
all_long_dls_h_ns$"unij_l_dls"$"imp_4"$"n_cort_t"$"data" <- dplyr::rename(all_long_dls_h_ns$"unij_l_dls"$"imp_4"$"n_cort_t"$"data", "cortical_t" = "cortical_thickness")
all_long_dls_h_ns$"unij_l_dls"$"imp_5"$"n_cort_t"$"data" <- dplyr::rename(all_long_dls_h_ns$"unij_l_dls"$"imp_5"$"n_cort_t"$"data", "cortical_t" = "cortical_thickness")

# 2025-09-30
saveRDS(all_long_dls_h_ns, proc_path("all_long_dls_h_ns.rds", TRUE))
```
