# Imputation, QCing, and CBCL thresholding

## Loading in data

```{r}
library(abcdutils)
library(here)
library(readr)
library(metasnf)
library(mice)
library(rlist)

source("abcd/helper_functions.R")

# The path_maker function helps with managing and date stamping long paths. The
#  functions are just used here to help with reading and writing data. See
#  ?path_maker for more information.
input_path <- path_maker(here(paste0("data/abcd/inputs")))
raw_path <- path_maker(here(paste0("data/abcd/raw")))
core_path <- path_maker(here(paste0("data/abcd/core")))
misc_path <- path_maker(here(paste0("data/abcd/misc")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))

import <- function(path) {
    return(read_csv(input_path(path)))
}

# Subjects
mtbi_subjects_0_to_2 <- read_subjects(
    sub_path("2024_05_06_mtbi_subjects_0_to_2.csv")
)

uninjured_subjects_0_to_2 <- read_subjects(
    sub_path("2024_05_06_uninjured_subjects_0_to_2.csv")
)
```

```{r}
# mTBI data
as_mem_daze_mtbi_l <- import("2024_06_14_as_mem_daze_mtbi_l.csv")
as_mechanism_mtbi_l <- import("2024_06_14_as_mechanism_mtbi_l.csv")
as_loc_mtbi_l <- import("2024_06_14_as_loc_mtbi_l.csv")
d_interview_age_mtbi_l0 <- import("2024_06_14_d_interview_age_mtbi_l0.csv")
d_interview_age_mtbi_l2 <- import("2024_06_14_d_interview_age_mtbi_l2.csv")
d_mtbi_age_mtbi_l <- import("2024_06_14_d_mtbi_age_mtbi_l.csv")
d_sex_mtbi_l0 <- import("2024_06_14_d_sex_mtbi_l0.csv")
d_income_mtbi_l0 <- import("2024_06_14_d_income_mtbi_l0.csv")
d_race_mtbi_l0 <- import("2024_06_14_d_race_mtbi_l0.csv")
d_pubertal_status_mtbi_l0 <- import("2024_06_14_d_pubertal_status_mtbi_l0.csv")
d_pubertal_status_mtbi_l2 <- import("2024_06_14_d_pubertal_status_mtbi_l2.csv")
mh_headaches_mtbi_l0 <- import("2024_06_14_mh_headaches_mtbi_l0.csv")
mh_mtbi_count_mtbi_l2 <- import("2024_06_14_mh_mtbi_count_mtbi_l2.csv")
sm_subc_v_mtbi_l0 <- import("2024_06_14_sm_subc_v_mtbi_l0.csv")
sm_subc_v_mtbi_l2 <- import("2024_06_14_sm_subc_v_mtbi_l2.csv")
sm_cort_t_mtbi_l0 <- import("2024_06_14_sm_cort_t_mtbi_l0.csv")
sm_cort_t_mtbi_l2 <- import("2024_06_14_sm_cort_t_mtbi_l2.csv")
sm_cort_sa_mtbi_l0 <- import("2024_06_14_sm_cort_sa_mtbi_l0.csv")
sm_cort_sa_mtbi_l2 <- import("2024_06_14_sm_cort_sa_mtbi_l2.csv")
dm_all_wmnd_mtbi_l0 <- import("2024_06_14_dm_all_wmnd_mtbi_l0.csv")
dm_all_wmnd_mtbi_l2 <- import("2024_06_14_dm_all_wmnd_mtbi_l2.csv")
rm_gord_cor_mtbi_l0 <- import("2024_06_14_rm_gord_cor_mtbi_l0.csv")
rm_gord_cor_mtbi_l2 <- import("2024_06_14_rm_gord_cor_mtbi_l2.csv")
rm_subc_cor_mtbi_l0 <- import("2024_06_14_rm_subc_cor_mtbi_l0.csv")
rm_subc_cor_mtbi_l2 <- import("2024_06_14_rm_subc_cor_mtbi_l2.csv")
p_loneliness_mtbi_l0 <- import("2024_06_14_p_loneliness_mtbi_l0.csv")
p_screen_time_mtbi_l0 <- import("2024_06_14_p_screen_time_mtbi_l0.csv")
p_sports_mtbi_l0 <- import("2024_06_14_p_sports_mtbi_l0.csv")
p_sports_mtbi_l2 <- import("2024_06_14_p_sports_mtbi_l2.csv")
p_exercise_mtbi_l0 <- import("2024_06_14_p_exercise_mtbi_l0.csv")
p_exercise_mtbi_l2 <- import("2024_06_14_p_exercise_mtbi_l2.csv")
p_prosocial_mtbi_l0 <- import("2024_06_14_p_prosocial_mtbi_l0.csv")
p_prosocial_mtbi_l2 <- import("2024_06_14_p_prosocial_mtbi_l2.csv")
p_fam_fn_mtbi_l0 <- import("2024_06_14_p_fam_fn_mtbi_l0.csv")
p_fam_fn_mtbi_l2 <- import("2024_06_14_p_fam_fn_mtbi_l2.csv")
p_parent_psych_mtbi_l0 <- import("2024_06_14_p_parent_psych_mtbi_l0.csv")
p_parent_psych_mtbi_l2 <- import("2024_06_14_p_parent_psych_mtbi_l2.csv")
cbcl_anxdep_mtbi_l0 <- import("2024_06_14_cbcl_anxdep_mtbi_l0.csv")
cbcl_anxdep_mtbi_l2 <- import("2024_06_14_cbcl_anxdep_mtbi_l2.csv")
cbcl_withdep_mtbi_l0 <- import("2024_06_14_cbcl_withdep_mtbi_l0.csv")
cbcl_withdep_mtbi_l2 <- import("2024_06_14_cbcl_withdep_mtbi_l2.csv")
cbcl_somatic_mtbi_l0 <- import("2024_06_14_cbcl_somatic_mtbi_l0.csv")
cbcl_somatic_mtbi_l2 <- import("2024_06_14_cbcl_somatic_mtbi_l2.csv")
cbcl_social_mtbi_l0 <- import("2024_06_14_cbcl_social_mtbi_l0.csv")
cbcl_social_mtbi_l2 <- import("2024_06_14_cbcl_social_mtbi_l2.csv")
cbcl_thought_mtbi_l0 <- import("2024_06_14_cbcl_thought_mtbi_l0.csv")
cbcl_thought_mtbi_l2 <- import("2024_06_14_cbcl_thought_mtbi_l2.csv")
cbcl_attention_mtbi_l0 <- import("2024_06_14_cbcl_attention_mtbi_l0.csv")
cbcl_attention_mtbi_l2 <- import("2024_06_14_cbcl_attention_mtbi_l2.csv")
cbcl_rulebreak_mtbi_l0 <- import("2024_06_14_cbcl_rulebreak_mtbi_l0.csv")
cbcl_rulebreak_mtbi_l2 <- import("2024_06_14_cbcl_rulebreak_mtbi_l2.csv")
cbcl_aggressive_mtbi_l0 <- import("2024_06_14_cbcl_aggressive_mtbi_l0.csv")
cbcl_aggressive_mtbi_l2 <- import("2024_06_14_cbcl_aggressive_mtbi_l2.csv")
sds_total_probs_mtbi_l0 <- import("2024_06_14_sds_total_probs_mtbi_l0.csv")
sds_total_probs_mtbi_l2 <- import("2024_06_14_sds_total_probs_mtbi_l2.csv")

# Uninjured subjects
d_interview_age_uninj_l0 <- import("2024_06_14_d_interview_age_uninj_l0.csv")
d_interview_age_uninj_l2 <- import("2024_06_14_d_interview_age_uninj_l2.csv")
d_sex_uninj_l0 <- import("2024_06_14_d_sex_uninj_l0.csv")
d_income_uninj_l0 <- import("2024_06_14_d_income_uninj_l0.csv")
d_race_uninj_l0 <- import("2024_06_14_d_race_uninj_l0.csv")
d_pubertal_status_uninj_l0 <- import("2024_06_14_d_pubertal_status_uninj_l0.csv")
d_pubertal_status_uninj_l2 <- import("2024_06_14_d_pubertal_status_uninj_l2.csv")
mh_headaches_uninj_l0 <- import("2024_06_14_mh_headaches_uninj_l0.csv")
sm_subc_v_uninj_l0 <- import("2024_06_14_sm_subc_v_uninj_l0.csv")
sm_subc_v_uninj_l2 <- import("2024_06_14_sm_subc_v_uninj_l2.csv")
sm_cort_t_uninj_l0 <- import("2024_06_14_sm_cort_t_uninj_l0.csv")
sm_cort_t_uninj_l2 <- import("2024_06_14_sm_cort_t_uninj_l2.csv")
sm_cort_sa_uninj_l0 <- import("2024_06_14_sm_cort_sa_uninj_l0.csv")
sm_cort_sa_uninj_l2 <- import("2024_06_14_sm_cort_sa_uninj_l2.csv")
dm_all_wmnd_uninj_l0 <- import("2024_06_14_dm_all_wmnd_uninj_l0.csv")
dm_all_wmnd_uninj_l2 <- import("2024_06_14_dm_all_wmnd_uninj_l2.csv")
rm_gord_cor_uninj_l0 <- import("2024_06_14_rm_gord_cor_uninj_l0.csv")
rm_gord_cor_uninj_l2 <- import("2024_06_14_rm_gord_cor_uninj_l2.csv")
rm_subc_cor_uninj_l0 <- import("2024_06_14_rm_subc_cor_uninj_l0.csv")
rm_subc_cor_uninj_l2 <- import("2024_06_14_rm_subc_cor_uninj_l2.csv")
p_loneliness_uninj_l0 <- import("2024_06_14_p_loneliness_uninj_l0.csv")
p_screen_time_uninj_l0 <- import("2024_06_14_p_screen_time_uninj_l0.csv")
p_sports_uninj_l0 <- import("2024_06_14_p_sports_uninj_l0.csv")
p_sports_uninj_l2 <- import("2024_06_14_p_sports_uninj_l2.csv")
p_exercise_uninj_l0 <- import("2024_06_14_p_exercise_uninj_l0.csv")
p_exercise_uninj_l2 <- import("2024_06_14_p_exercise_uninj_l2.csv")
p_prosocial_uninj_l0 <- import("2024_06_14_p_prosocial_uninj_l0.csv")
p_prosocial_uninj_l2 <- import("2024_06_14_p_prosocial_uninj_l2.csv")
p_fam_fn_uninj_l0 <- import("2024_06_14_p_fam_fn_uninj_l0.csv")
p_fam_fn_uninj_l2 <- import("2024_06_14_p_fam_fn_uninj_l2.csv")
p_parent_psych_uninj_l0 <- import("2024_06_14_p_parent_psych_uninj_l0.csv")
p_parent_psych_uninj_l2 <- import("2024_06_14_p_parent_psych_uninj_l2.csv")
cbcl_anxdep_uninj_l0 <- import("2024_06_14_cbcl_anxdep_uninj_l0.csv")
cbcl_anxdep_uninj_l2 <- import("2024_06_14_cbcl_anxdep_uninj_l2.csv")
cbcl_withdep_uninj_l0 <- import("2024_06_14_cbcl_withdep_uninj_l0.csv")
cbcl_withdep_uninj_l2 <- import("2024_06_14_cbcl_withdep_uninj_l2.csv")
cbcl_somatic_uninj_l0 <- import("2024_06_14_cbcl_somatic_uninj_l0.csv")
cbcl_somatic_uninj_l2 <- import("2024_06_14_cbcl_somatic_uninj_l2.csv")
cbcl_social_uninj_l0 <- import("2024_06_14_cbcl_social_uninj_l0.csv")
cbcl_social_uninj_l2 <- import("2024_06_14_cbcl_social_uninj_l2.csv")
cbcl_thought_uninj_l0 <- import("2024_06_14_cbcl_thought_uninj_l0.csv")
cbcl_thought_uninj_l2 <- import("2024_06_14_cbcl_thought_uninj_l2.csv")
cbcl_attention_uninj_l0 <- import("2024_06_14_cbcl_attention_uninj_l0.csv")
cbcl_attention_uninj_l2 <- import("2024_06_14_cbcl_attention_uninj_l2.csv")
cbcl_rulebreak_uninj_l0 <- import("2024_06_14_cbcl_rulebreak_uninj_l0.csv")
cbcl_rulebreak_uninj_l2 <- import("2024_06_14_cbcl_rulebreak_uninj_l2.csv")
cbcl_aggressive_uninj_l0 <- import("2024_06_14_cbcl_aggressive_uninj_l0.csv")
cbcl_aggressive_uninj_l2 <- import("2024_06_14_cbcl_aggressive_uninj_l2.csv")
sds_total_probs_uninj_l0 <- import("2024_06_14_sds_total_probs_uninj_l0.csv")
sds_total_probs_uninj_l2 <- import("2024_06_14_sds_total_probs_uninj_l2.csv")
```

```{r}
###############################################################################
# Storing into lists for bulk preprocessing
###############################################################################
mtbi_l0_dfs <- list(
    "d_interview_age_mtbi_l0" = d_interview_age_mtbi_l0,
    "d_sex_mtbi_l0" = d_sex_mtbi_l0,
    "d_income_mtbi_l0" = d_income_mtbi_l0,
    "d_race_mtbi_l0" = d_race_mtbi_l0,
    "d_pubertal_status_mtbi_l0" = d_pubertal_status_mtbi_l0,
    "mh_headaches_mtbi_l0" = mh_headaches_mtbi_l0,
    "sm_subc_v_mtbi_l0" = sm_subc_v_mtbi_l0,
    "sm_cort_t_mtbi_l0" = sm_cort_t_mtbi_l0,
    "sm_cort_sa_mtbi_l0" = sm_cort_sa_mtbi_l0,
    "dm_all_wmnd_mtbi_l0" = dm_all_wmnd_mtbi_l0,
    "rm_gord_cor_mtbi_l0" = rm_gord_cor_mtbi_l0,
    "rm_subc_cor_mtbi_l0" = rm_subc_cor_mtbi_l0,
    "p_loneliness_mtbi_l0" = p_loneliness_mtbi_l0,
    "p_screen_time_mtbi_l0" = p_screen_time_mtbi_l0,
    "p_sports_mtbi_l0" = p_sports_mtbi_l0,
    "p_exercise_mtbi_l0" = p_exercise_mtbi_l0,
    "p_prosocial_mtbi_l0" = p_prosocial_mtbi_l0,
    "p_fam_fn_mtbi_l0" = p_fam_fn_mtbi_l0,
    "p_parent_psych_mtbi_l0" = p_parent_psych_mtbi_l0,
    "cbcl_anxdep_mtbi_l0" = cbcl_anxdep_mtbi_l0,
    "cbcl_withdep_mtbi_l0" = cbcl_withdep_mtbi_l0,
    "cbcl_somatic_mtbi_l0" = cbcl_somatic_mtbi_l0,
    "cbcl_social_mtbi_l0" = cbcl_social_mtbi_l0,
    "cbcl_thought_mtbi_l0" = cbcl_thought_mtbi_l0,
    "cbcl_attention_mtbi_l0" = cbcl_attention_mtbi_l0,
    "cbcl_rulebreak_mtbi_l0" = cbcl_rulebreak_mtbi_l0,
    "cbcl_aggressive_mtbi_l0" = cbcl_aggressive_mtbi_l0,
    "sds_total_probs_mtbi_l0" = sds_total_probs_mtbi_l0
)

mtbi_l2_dfs <- list(
    "as_mem_daze_mtbi_l" = as_mem_daze_mtbi_l,
    "as_mechanism_mtbi_l" = as_mechanism_mtbi_l,
    "as_loc_mtbi_l" = as_loc_mtbi_l,
    "d_interview_age_mtbi_l2" = d_interview_age_mtbi_l2,
    "d_mtbi_age_mtbi_l" = d_mtbi_age_mtbi_l,
    "d_sex_mtbi_l0" = d_sex_mtbi_l0,
    "d_income_mtbi_l0" = d_income_mtbi_l0,
    "d_race_mtbi_l0" = d_race_mtbi_l0,
    "d_pubertal_status_mtbi_l2" = d_pubertal_status_mtbi_l2,
    "mh_headaches_mtbi_l0" = mh_headaches_mtbi_l0,
    "mh_mtbi_count_mtbi_l2" = mh_mtbi_count_mtbi_l2,
    "sm_subc_v_mtbi_l2" = sm_subc_v_mtbi_l2,
    "sm_cort_t_mtbi_l2" = sm_cort_t_mtbi_l2,
    "sm_cort_sa_mtbi_l2" = sm_cort_sa_mtbi_l2,
    "dm_all_wmnd_mtbi_l2" = dm_all_wmnd_mtbi_l2,
    "rm_gord_cor_mtbi_l2" = rm_gord_cor_mtbi_l2,
    "rm_subc_cor_mtbi_l2" = rm_subc_cor_mtbi_l2,
    "p_loneliness_mtbi_l0" = p_loneliness_mtbi_l0,
    "p_screen_time_mtbi_l0" = p_screen_time_mtbi_l0,
    "p_sports_mtbi_l2" = p_sports_mtbi_l2,
    "p_exercise_mtbi_l2" = p_exercise_mtbi_l2,
    "p_prosocial_mtbi_l2" = p_prosocial_mtbi_l2,
    "p_fam_fn_mtbi_l2" = p_fam_fn_mtbi_l2,
    "p_parent_psych_mtbi_l2" = p_parent_psych_mtbi_l2,
    "cbcl_anxdep_mtbi_l2" = cbcl_anxdep_mtbi_l2,
    "cbcl_withdep_mtbi_l2" = cbcl_withdep_mtbi_l2,
    "cbcl_somatic_mtbi_l2" = cbcl_somatic_mtbi_l2,
    "cbcl_social_mtbi_l2" = cbcl_social_mtbi_l2,
    "cbcl_thought_mtbi_l2" = cbcl_thought_mtbi_l2,
    "cbcl_attention_mtbi_l2" = cbcl_attention_mtbi_l2,
    "cbcl_rulebreak_mtbi_l2" = cbcl_rulebreak_mtbi_l2,
    "cbcl_aggressive_mtbi_l2" = cbcl_aggressive_mtbi_l2,
    "sds_total_probs_mtbi_l2" = sds_total_probs_mtbi_l2
)

uninj_l0_dfs <- list(
    "d_interview_age_uninj_l0" = d_interview_age_uninj_l0,
    "d_sex_uninj_l0" = d_sex_uninj_l0,
    "d_income_uninj_l0" = d_income_uninj_l0,
    "d_race_uninj_l0" = d_race_uninj_l0,
    "d_pubertal_status_uninj_l0" = d_pubertal_status_uninj_l0,
    "mh_headaches_uninj_l0" = mh_headaches_uninj_l0,
    "sm_subc_v_uninj_l0" = sm_subc_v_uninj_l0,
    "sm_cort_t_uninj_l0" = sm_cort_t_uninj_l0,
    "sm_cort_sa_uninj_l0" = sm_cort_sa_uninj_l0,
    "dm_all_wmnd_uninj_l0" = dm_all_wmnd_uninj_l0,
    "rm_gord_cor_uninj_l0" = rm_gord_cor_uninj_l0,
    "rm_subc_cor_uninj_l0" = rm_subc_cor_uninj_l0,
    "p_loneliness_uninj_l0" = p_loneliness_uninj_l0,
    "p_screen_time_uninj_l0" = p_screen_time_uninj_l0,
    "p_sports_uninj_l0" = p_sports_uninj_l0,
    "p_exercise_uninj_l0" = p_exercise_uninj_l0,
    "p_prosocial_uninj_l0" = p_prosocial_uninj_l0,
    "p_fam_fn_uninj_l0" = p_fam_fn_uninj_l0,
    "p_parent_psych_uninj_l0" = p_parent_psych_uninj_l0,
    "cbcl_anxdep_uninj_l0" = cbcl_anxdep_uninj_l0,
    "cbcl_withdep_uninj_l0" = cbcl_withdep_uninj_l0,
    "cbcl_somatic_uninj_l0" = cbcl_somatic_uninj_l0,
    "cbcl_social_uninj_l0" = cbcl_social_uninj_l0,
    "cbcl_thought_uninj_l0" = cbcl_thought_uninj_l0,
    "cbcl_attention_uninj_l0" = cbcl_attention_uninj_l0,
    "cbcl_rulebreak_uninj_l0" = cbcl_rulebreak_uninj_l0,
    "cbcl_aggressive_uninj_l0" = cbcl_aggressive_uninj_l0,
    "sds_total_probs_uninj_l0" = sds_total_probs_uninj_l0
)

uninj_l2_dfs <- list(
    "d_interview_age_uninj_l2" = d_interview_age_uninj_l2,
    "d_sex_uninj_l0" = d_sex_uninj_l0,
    "d_income_uninj_l0" = d_income_uninj_l0,
    "d_race_uninj_l0" = d_race_uninj_l0,
    "d_pubertal_status_uninj_l2" = d_pubertal_status_uninj_l2,
    "mh_headaches_uninj_l0" = mh_headaches_uninj_l0,
    "sm_subc_v_uninj_l2" = sm_subc_v_uninj_l2,
    "sm_cort_t_uninj_l2" = sm_cort_t_uninj_l2,
    "sm_cort_sa_uninj_l2" = sm_cort_sa_uninj_l2,
    "dm_all_wmnd_uninj_l2" = dm_all_wmnd_uninj_l2,
    "rm_gord_cor_uninj_l2" = rm_gord_cor_uninj_l2,
    "rm_subc_cor_uninj_l2" = rm_subc_cor_uninj_l2,
    "p_loneliness_uninj_l0" = p_loneliness_uninj_l0,
    "p_screen_time_uninj_l0" = p_screen_time_uninj_l0,
    "p_sports_uninj_l2" = p_sports_uninj_l2,
    "p_exercise_uninj_l2" = p_exercise_uninj_l2,
    "p_prosocial_uninj_l2" = p_prosocial_uninj_l2,
    "p_fam_fn_uninj_l2" = p_fam_fn_uninj_l2,
    "p_parent_psych_uninj_l2" = p_parent_psych_uninj_l2,
    "cbcl_anxdep_uninj_l2" = cbcl_anxdep_uninj_l2,
    "cbcl_withdep_uninj_l2" = cbcl_withdep_uninj_l2,
    "cbcl_somatic_uninj_l2" = cbcl_somatic_uninj_l2,
    "cbcl_social_uninj_l2" = cbcl_social_uninj_l2,
    "cbcl_thought_uninj_l2" = cbcl_thought_uninj_l2,
    "cbcl_attention_uninj_l2" = cbcl_attention_uninj_l2,
    "cbcl_rulebreak_uninj_l2" = cbcl_rulebreak_uninj_l2,
    "cbcl_aggressive_uninj_l2" = cbcl_aggressive_uninj_l2,
    "sds_total_probs_uninj_l2" = sds_total_probs_uninj_l2
)

###############################################################################
# Make sure everybody has the full set of subjects
###############################################################################
fix_subjects <- function(df_list, subjects) {
    subject_df <- data.frame(subjectkey = subjects)
    df_list <- df_list |>
        lapply(
            function(x) {
                x <- dplyr::full_join(x, subject_df, by = "subjectkey")
            }
        )
    df_list_nsubs <- lapply(
        df_list,
        nrow
    ) |>
        unlist() |>
        unique()
    print(identical(df_list_nsubs, length(subjects)))
    return(df_list)
}

mtbi_l0_dfs_2 <- fix_subjects(mtbi_l0_dfs, mtbi_subjects_0_to_2)
mtbi_l2_dfs_2 <- fix_subjects(mtbi_l2_dfs, mtbi_subjects_0_to_2)
uninj_l0_dfs_2 <- fix_subjects(uninj_l0_dfs, uninjured_subjects_0_to_2)
uninj_l2_dfs_2 <- fix_subjects(uninj_l2_dfs, uninjured_subjects_0_to_2)
```

## Neuroimaging quality control

First identify which subjects have valid neuroimaging data.

```{r}
mri_y_qc_raw_smr_t1 <- abcd_load(core_path("imaging/mri_y_qc_raw_smr_t1.csv"))
mri_y_qc_raw_smr_t2 <- abcd_load(core_path("imaging/mri_y_qc_raw_smr_t2.csv"))
mri_y_qc_raw_rsfmr <- abcd_load(core_path("imaging/mri_y_qc_raw_rsfmr.csv"))
mri_y_qc_raw_dmr <- abcd_load(core_path("imaging/mri_y_qc_raw_dmr.csv"))

mtbi_l0_neuro_dfs <- mtbi_l0_dfs_2[
    c(
        "sm_subc_v_mtbi_l0",
        "sm_cort_t_mtbi_l0",
        "sm_cort_sa_mtbi_l0",
        "dm_all_wmnd_mtbi_l0",
        "rm_gord_cor_mtbi_l0",
        "rm_subc_cor_mtbi_l0"
    )
]

mtbi_l2_neuro_dfs <- mtbi_l2_dfs_2[
    c(
        "sm_subc_v_mtbi_l2",
        "sm_cort_t_mtbi_l2",
        "sm_cort_sa_mtbi_l2",
        "dm_all_wmnd_mtbi_l2",
        "rm_gord_cor_mtbi_l2",
        "rm_subc_cor_mtbi_l2"
    )
]

uninj_l0_neuro_dfs <- uninj_l0_dfs_2[
    c(
        "sm_subc_v_uninj_l0",
        "sm_cort_t_uninj_l0",
        "sm_cort_sa_uninj_l0",
        "dm_all_wmnd_uninj_l0",
        "rm_gord_cor_uninj_l0",
        "rm_subc_cor_uninj_l0"
    )
]

uninj_l2_neuro_dfs <- uninj_l2_dfs_2[
    c(
        "sm_subc_v_uninj_l2",
        "sm_cort_t_uninj_l2",
        "sm_cort_sa_uninj_l2",
        "dm_all_wmnd_uninj_l2",
        "rm_gord_cor_uninj_l2",
        "rm_subc_cor_uninj_l2"
    )
]

# Obtaining the QC'd subjects with complete neuroimaging data
apply_qc <- function(df_list, sqc, dqc, rqc, tp) {
    subjectkeys <- df_list[[1]]$"subjectkey"
    smri_qc <- qc_smri(
        sqc,
        t = tp,
        subjects = subjectkeys,
        metric = "qc"
    )
    smri_pc <- qc_smri(
        sqc,
        t = tp,
        subjects = subjectkeys,
        metric = "pc"
    )
    dmri_qc <- qc_dmri(
        dqc,
        t = tp,
        subjects = subjectkeys,
        metric = "qc"
    )
    dmri_pc <- qc_dmri(
        dqc,
        t = tp,
        subjects = subjectkeys,
        metric = "pc"
    )
    rsfmri_qc <- qc_rsfmri(
        rqc,
        t = tp,
        subjects = subjectkeys,
        metric = "qc"
    )
    rsfmri_pc <- qc_rsfmri(
        rqc,
        t = tp,
        subjects = subjectkeys,
        metric = "pc"
    )
    ###########################################################################
    smri_pass <- intersect(smri_qc$"pass", smri_pc$"pass")
    dmri_pass <- intersect(dmri_qc$"pass", dmri_pc$"pass")
    rsfmri_pass <- intersect(rsfmri_qc$"pass", rsfmri_pc$"pass")
    ###########################################################################
    qc_df_list <- lapply(
        names(df_list),
        function(x) {
            if (startsWith(x, "sm")) {
                qc_df <- dplyr::filter(
                    df_list[[x]],
                    df_list[[x]]$"subjectkey" %in% smri_pass
                )
                return(qc_df)
            } else if (startsWith(x, "d")) {
                qc_df <- dplyr::filter(
                    df_list[[x]],
                    df_list[[x]]$"subjectkey" %in% dmri_pass
                )
                return(qc_df)
            } else {
                qc_df <- dplyr::filter(
                    df_list[[x]],
                    df_list[[x]]$"subjectkey" %in% rsfmri_pass
                )
                return(qc_df)
            }
        }
    )
    names(qc_df_list) <- names(df_list)
    return(qc_df_list)
}

mtbi_l0_qc_neuro_dfs <- apply_qc(
    mtbi_l0_neuro_dfs,
    sqc = mri_y_qc_raw_smr_t1,
    dqc = mri_y_qc_raw_dmr,
    rqc = mri_y_qc_raw_rsfmr,
    tp = 0
) |>
    fix_subjects(mtbi_subjects_0_to_2)

mtbi_l2_qc_neuro_dfs <- apply_qc(
    mtbi_l2_neuro_dfs,
    sqc = mri_y_qc_raw_smr_t1,
    dqc = mri_y_qc_raw_dmr,
    rqc = mri_y_qc_raw_rsfmr,
    tp = 2
) |>
    fix_subjects(mtbi_subjects_0_to_2)

uninj_l0_qc_neuro_dfs <- apply_qc(
    uninj_l0_neuro_dfs,
    sqc = mri_y_qc_raw_smr_t1,
    dqc = mri_y_qc_raw_dmr,
    rqc = mri_y_qc_raw_rsfmr,
    tp = 0
) |>
    fix_subjects(uninjured_subjects_0_to_2)

uninj_l2_qc_neuro_dfs <- apply_qc(
    uninj_l2_neuro_dfs,
    sqc = mri_y_qc_raw_smr_t1,
    dqc = mri_y_qc_raw_dmr,
    rqc = mri_y_qc_raw_rsfmr,
    tp = 2
) |>
    fix_subjects(uninjured_subjects_0_to_2)

###############################################################################
# Merge back in with other DFs
###############################################################################
n_names <- c(
    names(mtbi_l0_qc_neuro_dfs),
    names(mtbi_l2_qc_neuro_dfs),
    names(uninj_l0_qc_neuro_dfs),
    names(uninj_l2_qc_neuro_dfs)
)

mtbi_l0_no_neuro_dfs <- mtbi_l0_dfs_2[!names(mtbi_l0_dfs_2) %in% n_names]
mtbi_l2_no_neuro_dfs <- mtbi_l2_dfs_2[!names(mtbi_l2_dfs_2) %in% n_names]
uninj_l0_no_neuro_dfs <- uninj_l0_dfs_2[!names(uninj_l0_dfs_2) %in% n_names]
uninj_l2_no_neuro_dfs <- uninj_l2_dfs_2[!names(uninj_l2_dfs_2) %in% n_names]

mtbi_l0_dfs_3 <- c(mtbi_l0_no_neuro_dfs, mtbi_l0_qc_neuro_dfs)
mtbi_l2_dfs_3 <- c(mtbi_l2_no_neuro_dfs, mtbi_l2_qc_neuro_dfs)
uninj_l0_dfs_3 <- c(uninj_l0_no_neuro_dfs, uninj_l0_qc_neuro_dfs)
uninj_l2_dfs_3 <- c(uninj_l2_no_neuro_dfs, uninj_l2_qc_neuro_dfs)
```

# Imputation

- 5 imputations of mTBI data alone
- 5 imputations of uninjured data alone

# Imputing missing data

```{r}
mtbi_l0_df <- data.frame(merge_df_list(mtbi_l0_dfs_3, join = "full"))
mtbi_l2_df <- data.frame(merge_df_list(mtbi_l2_dfs_3, join = "full"))
uninj_l0_df <- data.frame(merge_df_list(uninj_l0_dfs_3, join = "full"))
uninj_l2_df <- data.frame(merge_df_list(uninj_l2_dfs_3, join = "full"))

# Remove the subjectkey variable
mtbi_l0_df_no_subs <- char_to_fac(mtbi_l0_df[, -1])
mtbi_l2_df_no_subs <- char_to_fac(mtbi_l2_df[, -1])
uninj_l0_df_no_subs <- char_to_fac(uninj_l0_df[, -1])
uninj_l2_df_no_subs <- char_to_fac(uninj_l2_df[, -1])

# Check to see if any columns have 0 variance
no_var_column_checker <- function(df) {
    no_var_cols <- list()
    for (col in colnames(df)) {
        single_val <- df[, col] |>
            na.omit() |>
            unique() |>
            length() |>
            all.equal(1) |>
            isTRUE()
        if (single_val) {
            no_var_cols <- c(no_var_cols, col)
        }
    }
    if (length(no_var_cols) > 0) {
        return(unlist(no_var_cols))
    }
}

# Good
no_var_column_checker(mtbi_l0_df_no_subs)

# Not good
mtbi_l2_zv <- no_var_column_checker(mtbi_l2_df_no_subs)

# No zero variance vars
mtbi_l2_df_no_subs_no_zv <- mtbi_l2_df_no_subs |>
    dplyr::select(-all_of(mtbi_l2_zv))

# Good
no_var_column_checker(uninj_l0_df_no_subs)

# Not good
uninj_l2_zv <- no_var_column_checker(uninj_l2_df_no_subs)
uninj_l2_df_no_subs_no_zv <- uninj_l2_df_no_subs |>
    dplyr::select(-all_of(uninj_l2_zv))

# Function that checks which variables have the biggest correlations
pairwise_correlations <- function(df, threshold = 0) {
    # Remove missing data to help calculate correlations
    df <- na.omit(df)
    # Remove non-numeric columns
    non_numeric_cols <- sapply(df, function(x) !is.numeric(x))
    df <- df[, !non_numeric_cols]
    # Calculate correlations
    correlations <- cor(df)
    # Ignore self-correlations
    diag(correlations) <- 0
    # Take absolute value of the correlations, as strong anti-correlations also
    # lead to strong linear dependence
    abs_cor <- abs(correlations)
    # Create dataframe of all pairs of correlations
    pairs <- t(combn(colnames(abs_cor), 2))
    paired_cors <- data.frame(pairs, cor = abs_cor[pairs])
    # Filter to only correlations bigger than a specified threshold
    paired_cors <- paired_cors[paired_cors$"cor" > threshold, ]
    return(paired_cors)
}

# Function to help sort variables by pairwise correlations
top_correlating_vars <- function(df, threshold = 0) {
    df <- pairwise_correlations(df, threshold)
    # Why are there NAs here?
    df <- na.omit(df)
    # Why are there NAs here?
    max_cor_df <- data.frame(
        variable = as.character(),
        max_cor = as.numeric()
    )
    i <- 0
    while (nrow(df) > 0) {
        i <- i + 1
        row_with_max_cor <- which(df$"cor" == max(df$"cor"))[1]
        var_with_max_cor <- df[row_with_max_cor, "X1"]
        max_cor <- df[row_with_max_cor, "cor"]
        max_cor_df <- rbind(
            max_cor_df,
            data.frame(
                variable = var_with_max_cor,
                max_cor = max_cor
            )
        )
        df <- dplyr::filter(
            df,
            df$"X1" != var_with_max_cor & df$"X2" != var_with_max_cor
        )
    }
    return(max_cor_df)
}
# Prediction matrix construction
build_pred_mat <- function(df, n_predictors = 1) {
    pred_mat <- matrix(
        nrow = ncol(df),
        ncol = ncol(df),
        data = 1
    )
    colnames(pred_mat) <- colnames(df)
    rownames(pred_mat) <- colnames(df)
    diag(pred_mat) <- 0
    pred_mat_vars <- top_correlating_vars(df)
    vars_to_drop <- pred_mat_vars$"variable"[seq_len(n_predictors)]
    print(paste0("Dropping: ", paste(vars_to_drop, collapse = ", ")))
    pred_mat[, vars_to_drop] <- 0
    return(pred_mat)
}

###############################################################################
# Imputation: mtbi l0
###############################################################################
# Doesn't run
imputed_mtbi_l0 <- futuremice(
    mtbi_l0_df_no_subs,
    m = 5,
    maxit = 10,
    parallelseed = 42
)

mtbi_l0_pred_mat <- build_pred_mat(mtbi_l0_df_no_subs, 1)

# Write and recover
write.table(mtbi_l0_pred_mat, proc_path("mtbi_l0_pred_mat.txt", TRUE))

mtbi_l0_pred_mat <- as.matrix(
    read.table(proc_path("2024_06_17_mtbi_l0_pred_mat.txt"))
)
storage.mode(mtbi_l0_pred_mat) <- "double"

imputed_mtbi_l0 <- futuremice(
    mtbi_l0_df_no_subs,
    m = 5,
    n.core = 5,
    maxit = 10,
    parallelseed = 42,
    predictorMatrix = mtbi_l0_pred_mat
)

five_imputed_mtbi_l0 <- complete(
    imputed_mtbi_l0,
    action = "long",
    include = TRUE
)

# Write and recover
write_csv(five_imputed_mtbi_l0, input_path("five_imputed_mtbi_l0.csv", TRUE))

###############################################################################
# Imputation: mtbi l2
###############################################################################
# Doesn't run
imputed_mtbi_l2 <- futuremice(
    mtbi_l2_df_no_subs_no_zv,
    m = 5,
    maxit = 10,
    parallelseed = 42
)

mtbi_l2_pred_mat <- build_pred_mat(mtbi_l2_df_no_subs_no_zv, 6)

# Pubertal status has an extremely high NA fraction
mtbi_l2_pred_mat[, "pubertal_status"] <- 0

sapply(mtbi_l2_df_no_subs_no_zv, function(x) sum(is.na(x)))


calc_comissingness <- function(df) {
    comissing_df <- NULL
    features <- colnames(df)
    pairwise_features <- combn(features, 2)
    for (i in seq_len(ncol(pairwise_features))) {
        feature1 <- pairwise_features[1, i]
        feature2 <- pairwise_features[2, i]
        missing_together <- sum(
            is.na(df[, feature1]) & is.na(df[, feature2])
        )
        missing_at_all <- sum(
            is.na(df[, feature1]) | is.na(df[, feature2])
        )
        comissingness <- 100 * missing_together / missing_at_all
        this_df <- data.frame(
            var1 = feature1,
            var2 = feature2,
            comissingness = comissingness
        )
        if (is.null(comissing_df)) {
            comissing_df <- this_df
        } else {
            comissing_df <- rbind(comissing_df, this_df)
        }
    }
    return(comissing_df)
}

###############################################################################
# good stuff
###############################################################################
z <- calc_comissingness(mtbi_l2_df_no_subs_no_zv)

z



library(ComplexHeatmap)

Heatmap(mtbi_l2_pred_mat, cluster_rows = FALSE, cluster_columns = FALSE)


#
# Write and recover
write.table(mtbi_l2_pred_mat, proc_path("mtbi_l2_pred_mat.txt", TRUE))
mtbi_l2_pred_mat <- as.matrix(
    read.table(proc_path("2024_06_17_mtbi_l2_pred_mat.txt"))
)
storage.mode(mtbi_l2_pred_mat) <- "double"
#
imputed_mtbi_l2 <- futuremice(
    mtbi_l2_df_no_subs_no_zv,
    m = 5,
    n.core = 5,
    maxit = 10,
    parallelseed = 42,
    predictorMatrix = mtbi_l2_pred_mat
)

five_imputed_mtbi_l2 <- complete(
    imputed_mtbi_l2,
    action = "long",
    include = TRUE
)

# Write and recover
write_csv(five_imputed_mtbi_l2, input_path("five_imputed_mtbi_l2.csv", TRUE))

###############################################################################
# Imputation: uninj l0
###############################################################################
# Doesn't run
imputed_uninj_l0 <- futuremice(
    uninj_l0_df_no_subs,
    m = 5,
    maxit = 10,
    parallelseed = 42
)

uninj_l0_pred_mat <- build_pred_mat(uninj_l0_df_no_subs, 1)

# Write and recover
write.table(uninj_l0_pred_mat, proc_path("uninj_l0_pred_mat.txt", TRUE))

uninj_l0_pred_mat <- as.matrix(
    read.table(proc_path("2024_06_17_uninj_l0_pred_mat.txt"))
)
storage.mode(uninj_l0_pred_mat) <- "double"

imputed_uninj_l0 <- futuremice(
    uninj_l0_df_no_subs,
    m = 5,
    n.core = 5,
    maxit = 10,
    parallelseed = 42,
    predictorMatrix = uninj_l0_pred_mat
)

five_imputed_uninj_l0 <- complete(
    imputed_uninj_l0,
    action = "long",
    include = TRUE
)

# Write and recover
write_csv(five_imputed_uninj_l0, input_path("five_imputed_uninj_l0.csv", TRUE))

###############################################################################
# Imputation: uninj l2
###############################################################################
# Doesn't run
imputed_uninj_l2 <- futuremice(
    uninj_l2_df_no_subs,
    m = 5,
    maxit = 10,
    parallelseed = 42
)

uninj_l2_pred_mat <- build_pred_mat(uninj_l2_df_no_subs, 1)

# Write and recover
write.table(uninj_l2_pred_mat, proc_path("uninj_l2_pred_mat.txt", TRUE))
uninj_l2_pred_mat <- as.matrix(
    read.table(proc_path("2024_06_17_uninj_l2_pred_mat.txt"))
)
storage.mode(uninj_l2_pred_mat) <- "double"

imputed_uninj_l2 <- futuremice(
    uninj_l2_df_no_subs,
    m = 5,
    n.core = 5,
    maxit = 10,
    parallelseed = 42,
    predictorMatrix = uninj_l2_pred_mat
)

five_imputed_uninj_l2 <- complete(
    imputed_uninj_l2,
    action = "long",
    include = TRUE
)

# Write and recover
write_csv(five_imputed_uninj_l2, input_path("five_imputed_uninj_l2.csv", TRUE))
```

```{r}
five_imputed_mtbi_l0 <- import("2024_06_14_five_imputed_mtbi_l0.csv")
five_imputed_mtbi_l2 <- import("2024_06_17_five_imputed_mtbi_l2.csv")
five_imputed_uninj_l0 <- import("2024_06_17_five_imputed_uninj_l0.csv")
five_imputed_uninj_l2 <- import("2024_06_17_five_imputed_uninj_l2.csv")
```

Formatting the imputed data:

```{r}

five_imputed_mtbi_l0$"subjectkey" <- rep(mtbi_l0_df$"subjectkey", 6)
five_imputed_mtbi_l2$"subjectkey" <- rep(mtbi_l2_df$"subjectkey", 6)
five_imputed_uninj_l0$"subjectkey" <- rep(uninj_l0_df$"subjectkey", 6)
five_imputed_uninj_l2$"subjectkey" <- rep(uninj_l2_df$"subjectkey", 6)

write_csv(
    five_imputed_mtbi_l0, input_path("five_imputed_mtbi_l0_named.csv", TRUE)
)
write_csv(
    five_imputed_mtbi_l2, input_path("five_imputed_mtbi_l2_named.csv", TRUE)
)
write_csv(
    five_imputed_uninj_l0, input_path("five_imputed_uninj_l0_named.csv", TRUE)
)
write_csv(
    five_imputed_uninj_l2, input_path("five_imputed_uninj_l2_named.csv", TRUE)
)
```

```{r}
five_imputed_mtbi_l0 <- import("2024_06_17_five_imputed_mtbi_l0_named.csv")
five_imputed_mtbi_l2 <- import("2024_06_17_five_imputed_mtbi_l2_named.csv")
five_imputed_uninj_l0 <- import("2024_06_17_five_imputed_uninj_l0_named.csv")
five_imputed_uninj_l2 <- import("2024_06_17_five_imputed_uninj_l2_named.csv")
```

# mTBI subsetting

```{r}

mtbi_l0_parsed_imps <- parse_imputations(
    mtbi_l0_dfs,
    five_imputed_mtbi_l0,
    6
)
mtbi_l2_parsed_imps <- parse_imputations(
    mtbi_l2_dfs,
    five_imputed_mtbi_l2,
    6
)
uninj_l0_parsed_imps <- parse_imputations(
    uninj_l0_dfs,
    five_imputed_uninj_l0,
    6
)
uninj_l2_parsed_imps <- parse_imputations(
    uninj_l2_dfs,
    five_imputed_uninj_l2,
    6
)

list.save(
    mtbi_l0_parsed_imps,
    input_path("mtbi_l0_parsed_imps.rds", TRUE)
)
list.save(
    mtbi_l2_parsed_imps,
    input_path("mtbi_l2_parsed_imps.rds", TRUE)
)
list.save(
    uninj_l0_parsed_imps,
    input_path("uninj_l0_parsed_imps.rds", TRUE)
)
list.save(
    uninj_l2_parsed_imps,
    input_path("uninj_l2_parsed_imps.rds", TRUE)
)
```


Re-reading:


## Importing imputed data

```{r}
mtbi_l0_parsed_imps <- list.load(
    input_path("2024_06_17_mtbi_l0_parsed_imps.rds")
)
mtbi_l2_parsed_imps <- list.load(
    input_path("2024_06_17_mtbi_l2_parsed_imps.rds")
)
uninj_l0_parsed_imps <- list.load(
    input_path("2024_06_17_uninj_l0_parsed_imps.rds")
)
uninj_l2_parsed_imps <- list.load(
    input_path("2024_06_17_uninj_l2_parsed_imps.rds")
)
```

## Constructing data_lists

* m = mTBI
* u = uninjured
* p = pooled
* 0 = original (unimputed)
* 1-5 = imputed dataset number

```{r}

mtbi_l0_data_lists <- build_dls(mtbi_l0_parsed_imps)
mtbi_l0_oom_lists <- build_ols(mtbi_l0_parsed_imps)
mtbi_l2_data_lists <- build_dls(mtbi_l2_parsed_imps)
mtbi_l2_oom_lists <- build_ols(mtbi_l2_parsed_imps)
uninj_l0_data_lists <- build_dls(uninj_l0_parsed_imps)
uninj_l0_oom_lists <- build_ols(uninj_l0_parsed_imps)
uninj_l2_data_lists <- build_dls(uninj_l2_parsed_imps)
uninj_l2_oom_lists <- build_ols(uninj_l2_parsed_imps)

na.omit(mtbi_l2_parsed_imps[[2]][[1]]) |> nrow()


length(mtbi_l2_parsed_imps)

for (i in mtbi_l2_parsed_imps) {
    if (nrow(na.omit(i[[3]])) == 216) {
        print(na.omit(i[[1]]))
    }
}

lapply(
    mtbi_l2_parsed_imps,
    function(x) {
        z <- lapply(
            x,
            function(y) {
                if (nrow(na.omit(y)) == 216) {
                    return(colnames(y))
                }
            }
        )
        return(as.character(unlist(z)))
    }
)

mtbi_l2_data_lists |>
    lapply(
        function(x) {
            nrow(na.omit(collapse_dl(x)))
        }
    )

all_dls <- list(
    "mtbi_l0_data_lists" = mtbi_l0_data_lists,
    "mtbi_l0_oom_lists" = mtbi_l0_oom_lists,
    "mtbi_l2_data_lists" = mtbi_l2_data_lists,
    "mtbi_l2_oom_lists" = mtbi_l2_oom_lists,
    "uninj_l0_data_lists" = uninj_l0_data_lists,
    "uninj_l0_oom_lists" = uninj_l0_oom_lists,
    "uninj_l2_data_lists" = uninj_l2_data_lists,
    "uninj_l2_oom_lists" = uninj_l2_oom_lists
)

```

## Renaming the initial data

```{r}
name_changes <- c(
    "mtbi_mechanism" = "latest_mtbi_mechanism",
    "mtbi_mem_daze" = "latest_mtbi_mem_daze",
    "mtbi_loc" = "latest_mtbi_loc",
    "mtbi_age" = "latest_mtbi_age",
    "age" = "interview_age",
    "parent_thought" = "asr_scr_thought_t",
    "parent_aggressive" = "asr_scr_aggressive_t",
    "parent_antisocial" = "asr_scr_antisocial_t",
    "parent_hyperactive" = "asr_scr_hyperactive_t",
    "parent_attention" = "asr_scr_attention_t",
    "parent_anxdep" = "asr_scr_anxdep_t",
    "parent_depress" = "asr_scr_depress_t",
    "parent_withdrawn" = "asr_scr_withdrawn_t",
    "parent_avoidant" = "asr_scr_avoidant_t",
    "parent_anxdisord" = "asr_scr_anxdisord_t",
    "parent_somatic" = "asr_scr_somatic_t",
    "parent_intrusive" = "asr_scr_intrusive_t",
    "parent_perstr" = "asr_scr_perstr_t",
    "sds_sleep" = "sds_p_ss_total",
    "cbcl_somatic" = "cbcl_scr_syn_somatic_t",
    "cbcl_social" = "cbcl_scr_syn_social_t",
    "cbcl_anxdep" = "cbcl_scr_syn_anxdep_t",
    "cbcl_thought" = "cbcl_scr_syn_thought_t",
    "cbcl_attention" = "cbcl_scr_syn_attention_t",
    "cbcl_withdep" = "cbcl_scr_syn_withdep_t",
    "cbcl_aggressive" = "cbcl_scr_syn_aggressive_t",
    "cbcl_rulebreak" = "cbcl_scr_syn_rulebreak_t",
    "family_fight" = "q1_fight",
    "family_angry" = "q2_angry",
    "family_throw" = "q3_throw",
    "family_temper" = "q4_temper",
    "family_criticize" = "q5_criticize",
    "family_hit" = "q6_hit",
    "family_peaceful" = "q7_peaceful",
    "family_outdo" = "q8_outdo",
    "family_yell" = "q9_yell",
    "prosocial_considerate" = "q1",
    "prosocial_helps_hurt" = "q2",
    "prosocial_helpful" = "q3",
    "headache_history" = "headache",
    "previous_mtbis" = "mtbi_count",
    "brain_volume" = "smri_vol_scs_wholeb",
    "cortical_thickness" = "smri_thick_cdk_mean",
    "cortical_sa" = "smri_area_cdk_total",
    "major_wm_ndi" = "dmri_rsirnd_fib_allfib",
    "pericortical_wm_ndi" = "dmri_rsirndwm_cdk_mean",
    "fmri_cort_cors" = "avg_gord_cor",
    "fmri_cort_subcort_cors" = "avg_subc_cor",
    "same_sex_friend" = "ss_friend",
    "opp_sex_friend" = "os_friend",
    "same_sex_close_friend" = "ss_close_friend",
    "opp_sex_close_friend" = "os_close_friend",
    "weekend_screentime" = "screentime_wknd_hrs",
    "weekday_screentime" = "screentime_wkday_hrs",
    "school_programs" = "organized_school_activities",
    "non_school_programs" = "organized_outside_activities",
    "private_instruction" = "private_instruction_activities",
    "programs_this_year" = "p12_activities",
    "exercise_time" = "physical_activity"
)

all_dls <- all_dls |>
    lapply(
        function(data_lists_of_group) {
            lapply(
                data_lists_of_group,
                function(data_list) {
                    data_list <- rename_dl(data_list, name_changes)
                }
            )
        }
    )

list.save(all_dls, input_path("all_dls_l.rds", TRUE))

# Subs NDAR_INV56J3P7WJ, NDAR_INVT0056CXX, NDAR_INVUZBAVXHW

```
