# Matching with demographics, family environment, and parent psychopathology

Our previous matched sample showed significantly lower CBCL and SDS impairment levels.
Here we examine another uninjured matched group that includes these outcomes as matching variables.

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)
library(MatchIt)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subjects <- read_csv(sub_path("2024_04_17_mtbi_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2024_04_17_uninjured_subjects.csv"))

source("abcd/functions.R")
```

## Matching

Finding matched uninjured controls for each mtbi subject based on demographic variables.

```{r}

all_dls <- list.load(input_path("2024_04_19_all_dls.rds"))

mtbi_matching_dl <- all_dls$"mtbi_train_data_lists"$"imp_1"
uninj_matching_dl <- all_dls$"uninj_data_lists"$"imp_1"

names(mtbi_matching_dl) <- summarize_dl(mtbi_matching_dl)$"name"
names(uninj_matching_dl) <- summarize_dl(uninj_matching_dl)$"name"

mtbi_matching_dl$"p_fam_fn"$"data" <- tibble::tibble(
    subjectkey = mtbi_matching_dl$"p_fam_fn"$"data"$"subjectkey",
    family_function = rowSums(mtbi_matching_dl$"p_fam_fn"$"data"[, -1])
)

uninj_matching_dl$"p_fam_fn"$"data" <- tibble::tibble(
    subjectkey = uninj_matching_dl$"p_fam_fn"$"data"$"subjectkey",
    family_function = rowSums(uninj_matching_dl$"p_fam_fn"$"data"[, -1])
)

mtbi_matching_dl$"p_parent_psych"$"data" <- tibble::tibble(
    subjectkey = mtbi_matching_dl$"p_parent_psych"$"data"$"subjectkey",
    parent_psych = rowSums(mtbi_matching_dl$"p_parent_psych"$"data"[, -1])
)

uninj_matching_dl$"p_parent_psych"$"data" <- tibble::tibble(
    subjectkey = uninj_matching_dl$"p_parent_psych"$"data"$"subjectkey",
    parent_psych = rowSums(uninj_matching_dl$"p_parent_psych"$"data"[, -1])
)

dfp_matching_vars <- c(
    "d_age",
    "d_sex",
    "d_income",
    "d_race",
    "p_fam_fn",
    "p_parent_psych"
)

d_matching_vars <- c(
    "d_age",
    "d_sex",
    "d_income",
    "d_race"
)

f_matching_vars <- c(
    "p_fam_fn"
)

p_matching_vars <- c(
    "p_parent_psych"
)

# Demographics, family function, and parent psych
mtbi_dfp_matching_dl <- mtbi_matching_dl[dfp_matching_vars]
uninj_dfp_matching_dl <- uninj_matching_dl[dfp_matching_vars]

# Just demographics
mtbi_d_matching_dl <- mtbi_matching_dl[d_matching_vars]
uninj_d_matching_dl <- uninj_matching_dl[d_matching_vars]

# Just family function
mtbi_f_matching_dl <- mtbi_matching_dl[f_matching_vars]
uninj_f_matching_dl <- uninj_matching_dl[f_matching_vars]

# Just parent psych
mtbi_p_matching_dl <- mtbi_matching_dl[p_matching_vars]
uninj_p_matching_dl <- uninj_matching_dl[p_matching_vars]

###############################################################################

# Demographics, family function, and parent psych
mtbi_dfp_matching_df <- collapse_dl(mtbi_dfp_matching_dl)
uninj_dfp_matching_df <- collapse_dl(uninj_dfp_matching_dl)

# Just demographics
mtbi_d_matching_df <- collapse_dl(mtbi_d_matching_dl)
uninj_d_matching_df <- collapse_dl(uninj_d_matching_dl)

# Just family function
mtbi_f_matching_df <- collapse_dl(mtbi_f_matching_dl)
uninj_f_matching_df <- collapse_dl(uninj_f_matching_dl)

# Just parent psych
mtbi_p_matching_df <- collapse_dl(mtbi_p_matching_dl)
uninj_p_matching_df <- collapse_dl(uninj_p_matching_dl)

###############################################################################

mtbi_dfp_matching_df$"mtbi" <- 1
uninj_dfp_matching_df$"mtbi" <- 0

mtbi_d_matching_df$"mtbi" <- 1
uninj_d_matching_df$"mtbi" <- 0

mtbi_f_matching_df$"mtbi" <- 1
uninj_f_matching_df$"mtbi" <- 0

mtbi_p_matching_df$"mtbi" <- 1
uninj_p_matching_df$"mtbi" <- 0

###############################################################################

dfp_matching_df <- rbind(mtbi_dfp_matching_df, uninj_dfp_matching_df)
d_matching_df <- rbind(mtbi_d_matching_df, uninj_d_matching_df)
f_matching_df <- rbind(mtbi_f_matching_df, uninj_f_matching_df)
p_matching_df <- rbind(mtbi_p_matching_df, uninj_p_matching_df)

dfp_matching_results <- matchit(
    formula(
        mtbi ~ household_income +
            race +
            age +
            sex +
            parent_psych +
            family_function
    ),
    data = dfp_matching_df,
    method = "nearest"
)

d_matching_results <- matchit(
    formula(mtbi ~ household_income + race + age + sex),
    data = d_matching_df,
    method = "nearest"
)

f_matching_results <- matchit(
    formula(mtbi ~ family_function),
    data = f_matching_df,
    method = "nearest"
)

p_matching_results <- matchit(
    formula(mtbi ~ parent_psych),
    data = p_matching_df,
    method = "nearest"
)

# Print summary information about the matching
summary(dfp_matching_results)

summary(d_matching_results)

summary(f_matching_results)

summary(p_matching_results)

###############################################################################

grDevices::png(
    filename = fig_path("dfp_matching_summary.png", TRUE),
    width = 1000,
    height = 500,
    res = 120
)
plot(summary(dfp_matching_results), position = "right")
grDevices::dev.off()

grDevices::png(
    filename = fig_path("d_matching_summary.png", TRUE),
    width = 1000,
    height = 500,
    res = 120
)
plot(summary(d_matching_results), position = "right")
grDevices::dev.off()

grDevices::png(
    filename = fig_path("f_matching_summary.png", TRUE),
    width = 1000,
    height = 500,
    res = 120
)
plot(summary(f_matching_results), position = "right")
grDevices::dev.off()

grDevices::png(
    filename = fig_path("p_matching_summary.png", TRUE),
    width = 1000,
    height = 500,
    res = 120
)
plot(summary(p_matching_results), position = "right")
grDevices::dev.off()

# Obtain the matched data
dfp_matched_data <- match.data(dfp_matching_results)
d_matched_data <- match.data(d_matching_results)
f_matched_data <- match.data(f_matching_results)
p_matched_data <- match.data(p_matching_results)

# Extract the control group from the matched data
dfp_matched_uninjured <- dfp_matched_data |>
    dplyr::filter(mtbi == 0) |>
    dplyr::select(subjectkey)
d_matched_uninjured <- d_matched_data |>
    dplyr::filter(mtbi == 0) |>
    dplyr::select(subjectkey)
f_matched_uninjured <- f_matched_data |>
    dplyr::filter(mtbi == 0) |>
    dplyr::select(subjectkey)
p_matched_uninjured <- p_matched_data |>
    dplyr::filter(mtbi == 0) |>
    dplyr::select(subjectkey)

dfp_matched_uninjured$"subjectkey" <- gsub(
    "subject_",
    "",
    dfp_matched_uninjured$"subjectkey"
)
d_matched_uninjured$"subjectkey" <- gsub(
    "subject_",
    "",
    d_matched_uninjured$"subjectkey"
)
f_matched_uninjured$"subjectkey" <- gsub(
    "subject_",
    "",
    f_matched_uninjured$"subjectkey"
)
p_matched_uninjured$"subjectkey" <- gsub(
    "subject_",
    "",
    p_matched_uninjured$"subjectkey"
)

write_csv(dfp_matched_uninjured, sub_path("dfp_matched_subjects.csv", TRUE))
write_csv(d_matched_uninjured, sub_path("d_matched_subjects.csv", TRUE))
write_csv(f_matched_uninjured, sub_path("f_matched_subjects.csv", TRUE))
write_csv(p_matched_uninjured, sub_path("p_matched_subjects.csv", TRUE))
```

## Loading data and out of model lists

```{r}

dfp_uninj_subs <- read_subjects(sub_path("2024_04_23_dfp_matched_subjects.csv"))
d_uninj_subs <- read_subjects(sub_path("2024_04_23_d_matched_subjects.csv"))
f_uninj_subs <- read_subjects(sub_path("2024_04_23_f_matched_subjects.csv"))
p_uninj_subs <- read_subjects(sub_path("2024_04_23_p_matched_subjects.csv"))

all_dls |> names()

uninj_dls_ol_names <- c(
    "uninj_data_lists",
    "uninj_pooled_data_lists",
    "uninj_oom_lists",
    "uninj_pooled_oom_lists"
)

uninj_dls_ols <- all_dls[uninj_dls_ol_names]

subject_filter_dl <- function(data_list, subject_vector) {
    subject_vector <- paste0("subject_", subject_vector)
    data_list <- data_list |>
        lapply(
            function(x) {
                unfiltered_subjects <- x$"data"$"subjectkey"
                x$"data" <- x$"data"[unfiltered_subjects %in% subject_vector, ]
                return(x)
            }
        )
    return(data_list)
}

dfp_dls_ols <- lapply(
    uninj_dls_ols,
    function(dl_list) {
        lapply(
            dl_list,
            function(dl) {
                subject_filter_dl(dl, dfp_uninj_subs)
            }
        )
    }
)

d_dls_ols <- lapply(
    uninj_dls_ols,
    function(dl_list) {
        lapply(
            dl_list,
            function(dl) {
                subject_filter_dl(dl, d_uninj_subs)
            }
        )
    }
)

f_dls_ols <- lapply(
    uninj_dls_ols,
    function(dl_list) {
        lapply(
            dl_list,
            function(dl) {
                subject_filter_dl(dl, f_uninj_subs)
            }
        )
    }
)

p_dls_ols <- lapply(
    uninj_dls_ols,
    function(dl_list) {
        lapply(
            dl_list,
            function(dl) {
                subject_filter_dl(dl, p_uninj_subs)
            }
        )
    }
)

list.save(dfp_dls_ols, input_path("dfp_dls_ols.rds", TRUE))
list.save(d_dls_ols, input_path("d_dls_ols.rds", TRUE))
list.save(f_dls_ols, input_path("f_dls_ols.rds", TRUE))
list.save(p_dls_ols, input_path("p_dls_ols.rds", TRUE))
```
