# Matching with CBCL

Our previous matched sample showed significantly lower CBCL and SDS impairment levels.
Here we examine another uninjured matched group that includes these outcomes as matching variables.

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)
library(MatchIt)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subjects <- read_csv(sub_path("2024_03_12_mtbi_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2024_03_12_uninjured_subjects.csv"))

source("abcd/functions.R")
```

## Matching

Finding matched uninjured controls for each mtbi subject based on demographic variables.

```{r}

d_interview_age_mtbi_train_imp_1 <- read_csv(input_path("2024_03_12_d_interview_age_mtbi_train_imp_1.csv"))
d_sex_mtbi_train_imp_1 <- read_csv(input_path("2024_03_12_d_sex_mtbi_train_imp_1.csv"))
d_income_mtbi_train_imp_1 <- read_csv(input_path("2024_03_12_d_income_mtbi_train_imp_1.csv"))
d_race_mtbi_train_imp_1 <- read_csv(input_path("2024_03_12_d_race_mtbi_train_imp_1.csv"))
cbcl_anxdep_mtbi_train_imp_1 <- read_csv(input_path("2024_03_12_cbcl_anxdep_mtbi_train_imp_1.csv"))
cbcl_withdep_mtbi_train_imp_1 <- read_csv(input_path("2024_03_12_cbcl_withdep_mtbi_train_imp_1.csv"))
cbcl_somatic_mtbi_train_imp_1 <- read_csv(input_path("2024_03_12_cbcl_somatic_mtbi_train_imp_1.csv"))
cbcl_social_mtbi_train_imp_1 <- read_csv(input_path("2024_03_12_cbcl_social_mtbi_train_imp_1.csv"))
cbcl_thought_mtbi_train_imp_1 <- read_csv(input_path("2024_03_12_cbcl_thought_mtbi_train_imp_1.csv"))
cbcl_attention_mtbi_train_imp_1 <- read_csv(input_path("2024_03_12_cbcl_attention_mtbi_train_imp_1.csv"))
cbcl_rulebreak_mtbi_train_imp_1 <- read_csv(input_path("2024_03_12_cbcl_rulebreak_mtbi_train_imp_1.csv"))
cbcl_aggressive_mtbi_train_imp_1 <- read_csv(input_path("2024_03_12_cbcl_aggressive_mtbi_train_imp_1.csv"))
sds_total_probs_mtbi_train_imp_1 <- read_csv(input_path("2024_03_12_sds_total_probs_mtbi_train_imp_1.csv"))

d_interview_age_uninj_imp_1 <- read_csv(input_path("2024_03_12_d_interview_age_uninj_imp_1.csv"))
d_sex_uninj_imp_1 <- read_csv(input_path("2024_03_12_d_sex_uninj_imp_1.csv"))
d_income_uninj_imp_1 <- read_csv(input_path("2024_03_12_d_income_uninj_imp_1.csv"))
d_race_uninj_imp_1 <- read_csv(input_path("2024_03_12_d_race_uninj_imp_1.csv"))
cbcl_anxdep_uninj_imp_1 <- read_csv(input_path("2024_03_12_cbcl_anxdep_uninj_imp_1.csv"))
cbcl_withdep_uninj_imp_1 <- read_csv(input_path("2024_03_12_cbcl_withdep_uninj_imp_1.csv"))
cbcl_somatic_uninj_imp_1 <- read_csv(input_path("2024_03_12_cbcl_somatic_uninj_imp_1.csv"))
cbcl_social_uninj_imp_1 <- read_csv(input_path("2024_03_12_cbcl_social_uninj_imp_1.csv"))
cbcl_thought_uninj_imp_1 <- read_csv(input_path("2024_03_12_cbcl_thought_uninj_imp_1.csv"))
cbcl_attention_uninj_imp_1 <- read_csv(input_path("2024_03_12_cbcl_attention_uninj_imp_1.csv"))
cbcl_rulebreak_uninj_imp_1 <- read_csv(input_path("2024_03_12_cbcl_rulebreak_uninj_imp_1.csv"))
cbcl_aggressive_uninj_imp_1 <- read_csv(input_path("2024_03_12_cbcl_aggressive_uninj_imp_1.csv"))
sds_total_probs_uninj_imp_1 <- read_csv(input_path("2024_03_12_sds_total_probs_uninj_imp_1.csv"))

mtbi_matching_df <- list(
    d_interview_age_mtbi_train_imp_1,
    d_sex_mtbi_train_imp_1,
    d_income_mtbi_train_imp_1,
    d_race_mtbi_train_imp_1,
    cbcl_anxdep_mtbi_train_imp_1,
    cbcl_withdep_mtbi_train_imp_1,
    cbcl_somatic_mtbi_train_imp_1,
    cbcl_social_mtbi_train_imp_1,
    cbcl_thought_mtbi_train_imp_1,
    cbcl_attention_mtbi_train_imp_1,
    cbcl_rulebreak_mtbi_train_imp_1,
    cbcl_aggressive_mtbi_train_imp_1,
    sds_total_probs_mtbi_train_imp_1
) |> merge_df_list()

mtbi_matching_df$"mtbi" <- 1

uninjured_matching_df <- list(
    d_interview_age_uninj_imp_1,
    d_sex_uninj_imp_1,
    d_income_uninj_imp_1,
    d_race_uninj_imp_1,
    cbcl_anxdep_uninj_imp_1,
    cbcl_withdep_uninj_imp_1,
    cbcl_somatic_uninj_imp_1,
    cbcl_social_uninj_imp_1,
    cbcl_thought_uninj_imp_1,
    cbcl_attention_uninj_imp_1,
    cbcl_rulebreak_uninj_imp_1,
    cbcl_aggressive_uninj_imp_1,
    sds_total_probs_uninj_imp_1
) |> merge_df_list()

uninjured_matching_df$"mtbi" <- 0

matching_df <- rbind(mtbi_matching_df, uninjured_matching_df)

matching_df <- matching_df |> dplyr::mutate(
    cbcl_total = cbcl_scr_syn_anxdep_t +
        cbcl_scr_syn_withdep_t +
        cbcl_scr_syn_somatic_t +
        cbcl_scr_syn_social_t +
        cbcl_scr_syn_thought_t +
        cbcl_scr_syn_attention_t +
        cbcl_scr_syn_rulebreak_t +
        cbcl_scr_syn_aggressive_t
)

matching_results <- matchit(
    formula(
        mtbi ~ household_income +
            race +
            interview_age +
            sex +
            cbcl_total +
            sds_p_ss_total
    ),
    data = matching_df,
    method = "nearest"
)

# Print summary information about the matching
summary(matching_results)

grDevices::png(
    filename = fig_path("cmu_matching_summary.png", TRUE),
    width = 500,
    height = 300,
    res = 72
)
plot(summary(matching_results))
grDevices::dev.off()

# Obtain the matched data
matched_data <- match.data(matching_results)

# Extract the control group from the matched data
matched_uninjured <- matched_data |>
    dplyr::filter(mtbi == 0) |>
    dplyr::select(subjectkey)

write_csv(matched_uninjured, sub_path("cbcl_matched_uninjured.csv", TRUE))

```

## Loading data and out of model lists

```{r}
cbcl_matched_uninjured <- read_csv(sub_path("2024_03_18_cbcl_matched_uninjured.csv"))

data_list_u1 <- list.load(input_path("2024_03_12_data_list_u1.rds"))
data_list_u2 <- list.load(input_path("2024_03_12_data_list_u2.rds"))
data_list_u3 <- list.load(input_path("2024_03_12_data_list_u3.rds"))
data_list_u4 <- list.load(input_path("2024_03_12_data_list_u4.rds"))
data_list_u5 <- list.load(input_path("2024_03_12_data_list_u5.rds"))
data_list_pu1 <- list.load(input_path("2024_03_12_data_list_pu1.rds"))
data_list_pu2 <- list.load(input_path("2024_03_12_data_list_pu2.rds"))
data_list_pu3 <- list.load(input_path("2024_03_12_data_list_pu3.rds"))
data_list_pu4 <- list.load(input_path("2024_03_12_data_list_pu4.rds"))
data_list_pu5 <- list.load(input_path("2024_03_12_data_list_pu5.rds"))
oom_list_u1 <- list.load(input_path("2024_03_17_oom_list_u1.rds"))
oom_list_u2 <- list.load(input_path("2024_03_17_oom_list_u2.rds"))
oom_list_u3 <- list.load(input_path("2024_03_17_oom_list_u3.rds"))
oom_list_u4 <- list.load(input_path("2024_03_17_oom_list_u4.rds"))
oom_list_u5 <- list.load(input_path("2024_03_17_oom_list_u5.rds"))
oom_list_pu1 <- list.load(input_path("2024_03_17_oom_list_pu1.rds"))
oom_list_pu2 <- list.load(input_path("2024_03_17_oom_list_pu2.rds"))
oom_list_pu3 <- list.load(input_path("2024_03_17_oom_list_pu3.rds"))
oom_list_pu4 <- list.load(input_path("2024_03_17_oom_list_pu4.rds"))
oom_list_pu5 <- list.load(input_path("2024_03_17_oom_list_pu5.rds"))

subject_filter_dl <- function(data_list, subject_vector) {
    subject_vector <- paste0("subject_", subject_vector)
    data_list <- data_list |>
        lapply(
            function(x) {
                x$"data" <- x$"data"[x$"data"$"subjectkey" %in% subject_vector, ]
                return(x)
            }
        )
    return(data_list)
}

# The matched data lists
data_list_cmu1 <- data_list_u1 |> subject_filter_dl(cbcl_matched_uninjured$"subjectkey")
data_list_cmu2 <- data_list_u2 |> subject_filter_dl(cbcl_matched_uninjured$"subjectkey")
data_list_cmu3 <- data_list_u3 |> subject_filter_dl(cbcl_matched_uninjured$"subjectkey")
data_list_cmu4 <- data_list_u4 |> subject_filter_dl(cbcl_matched_uninjured$"subjectkey")
data_list_cmu5 <- data_list_u5 |> subject_filter_dl(cbcl_matched_uninjured$"subjectkey")
data_list_cmpu1 <- data_list_pu1 |> subject_filter_dl(cbcl_matched_uninjured$"subjectkey")
data_list_cmpu2 <- data_list_pu2 |> subject_filter_dl(cbcl_matched_uninjured$"subjectkey")
data_list_cmpu3 <- data_list_pu3 |> subject_filter_dl(cbcl_matched_uninjured$"subjectkey")
data_list_cmpu4 <- data_list_pu4 |> subject_filter_dl(cbcl_matched_uninjured$"subjectkey")
data_list_cmpu5 <- data_list_pu5 |> subject_filter_dl(cbcl_matched_uninjured$"subjectkey")
oom_list_cmu1 <- oom_list_u1 |> subject_filter_dl(cbcl_matched_uninjured$"subjectkey")
oom_list_cmu2 <- oom_list_u2 |> subject_filter_dl(cbcl_matched_uninjured$"subjectkey")
oom_list_cmu3 <- oom_list_u3 |> subject_filter_dl(cbcl_matched_uninjured$"subjectkey")
oom_list_cmu4 <- oom_list_u4 |> subject_filter_dl(cbcl_matched_uninjured$"subjectkey")
oom_list_cmu5 <- oom_list_u5 |> subject_filter_dl(cbcl_matched_uninjured$"subjectkey")
oom_list_cmpu1 <- oom_list_pu1 |> subject_filter_dl(cbcl_matched_uninjured$"subjectkey")
oom_list_cmpu2 <- oom_list_pu2 |> subject_filter_dl(cbcl_matched_uninjured$"subjectkey")
oom_list_cmpu3 <- oom_list_pu3 |> subject_filter_dl(cbcl_matched_uninjured$"subjectkey")
oom_list_cmpu4 <- oom_list_pu4 |> subject_filter_dl(cbcl_matched_uninjured$"subjectkey")
oom_list_cmpu5 <- oom_list_pu5 |> subject_filter_dl(cbcl_matched_uninjured$"subjectkey")

list.save(data_list_cmu1, input_path("data_list_cmu1.rds", TRUE))
list.save(data_list_cmu2, input_path("data_list_cmu2.rds", TRUE))
list.save(data_list_cmu3, input_path("data_list_cmu3.rds", TRUE))
list.save(data_list_cmu4, input_path("data_list_cmu4.rds", TRUE))
list.save(data_list_cmu5, input_path("data_list_cmu5.rds", TRUE))
list.save(data_list_cmpu1, input_path("data_list_cmpu1.rds", TRUE))
list.save(data_list_cmpu2, input_path("data_list_cmpu2.rds", TRUE))
list.save(data_list_cmpu3, input_path("data_list_cmpu3.rds", TRUE))
list.save(data_list_cmpu4, input_path("data_list_cmpu4.rds", TRUE))
list.save(data_list_cmpu5, input_path("data_list_cmpu5.rds", TRUE))
list.save(oom_list_cmu1, input_path("oom_list_cmu1.rds", TRUE))
list.save(oom_list_cmu2, input_path("oom_list_cmu2.rds", TRUE))
list.save(oom_list_cmu3, input_path("oom_list_cmu3.rds", TRUE))
list.save(oom_list_cmu4, input_path("oom_list_cmu4.rds", TRUE))
list.save(oom_list_cmu5, input_path("oom_list_cmu5.rds", TRUE))
list.save(oom_list_cmpu1, input_path("oom_list_cmpu1.rds", TRUE))
list.save(oom_list_cmpu2, input_path("oom_list_cmpu2.rds", TRUE))
list.save(oom_list_cmpu3, input_path("oom_list_cmpu3.rds", TRUE))
list.save(oom_list_cmpu4, input_path("oom_list_cmpu4.rds", TRUE))
list.save(oom_list_cmpu5, input_path("oom_list_cmpu5.rds", TRUE))
```
