# Building a Classifier

## Importing packages and establishing file paths

```{r}
library(readr)
library(here)
library(abcdutils)
library(dplyr)
library(caret)
library(xgboost)
library(randomForest)
library(fastDummies)
library(skimr)
library(doParallel)
library(future)
library(future.apply)
library(progressr)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
model_path <- path_maker(here(paste0("data/abcd/results/models")))
```

## Preprocessing

```{r}
# Data to build classifier from
mtbi_ful_df <- read_csv(proc_path("2024_11_07_mtbi_ful_df.csv"))
```

So we'll only want to use features that were both considered generalizable and that are present in uninjured children.
These features are the same as those that were characterized in the matched uninjured group.

```{r}
mtbi_gen_fts_in <- read_csv(proc_path("2024_11_07_mtbi_gen_fts_in.csv"))
classifier_fts <- unique(mtbi_gen_fts_in_long$feature) 
classifier_fts <- classifier_fts[!grepl("mtbi", classifier_fts)]
classifier_fts[grepl("race_", classifier_fts)] <- "race"
classifier_fts <- unique(classifier_fts)

write_csv(data.frame(classifier_fts), proc_path("classifier_fts.csv", TRUE))
```

```{r}
classifier_fts <- read_csv(proc_path("2024_11_07_classifier_fts.csv"))$"classifier_fts"

mtbi_classification_df <- dplyr::select(
    mtbi_ful_df,
    subjectkey,
    cluster,
    all_of(classifier_fts)
)

mtbi_classification_df <- mtbi_classification_df |>
    relocate(cluster, .after = last_col())

write_csv(mtbi_classification_df, proc_path("mtbi_classification_df.csv", TRUE))
```

```{r}
mtbi_classification_df <- read_csv(proc_path("2024_11_07_mtbi_classification_df.csv"))
```


```{r}
# Train/test split
set.seed(1111)
shuffled_df <- mtbi_classification_df[sample(nrow(mtbi_classification_df)), ]

nrow(mtbi_classification_df) * 0.8

train_classification_df <- shuffled_df[1:352, ]
test_classification_df <- shuffled_df[352: 440, ]

write_csv(train_classification_df, proc_path("train_classification_df.csv", TRUE))
write_csv(test_classification_df, proc_path("test_classification_df.csv", TRUE))
```

```{r}
# checkpoint
train_classification_df <- read_csv(proc_path("2024_11_07_train_classification_df.csv"))
test_classification_df <- read_csv(proc_path("2024_11_07_test_classification_df.csv"))
```

## Function to prep training data

```{r}
# checkpoint
prep_data <- function(df, standardize = FALSE) {
    df <- dplyr::select(df, -"subjectkey")
    df <- dummy_cols(
        df,
        select_columns = "race",
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = TRUE
    )
    ordered_factors <- c(
        "sex",
        "household_income",
        "pubertal_status_p",
        "family_fight_p",
        "family_outdo_p",
        "helps_hurt_p",
        "helpful_y",
        "considerate_y",
        "helps_hurt_y",
        "family_criticize_p",
        "family_outdo_y",
        "family_angry_p",
        "helpful_p",
        "family_throw_p",
        "family_hit_p",
        "family_peaceful_y",
        "family_throw_y",
        "race_black",
        "race_hispanic",
        "race_other" 
    )
    df[ordered_factors] <- lapply(df[ordered_factors], as.ordered)
    if (standardize) {
        df[] <- lapply(df, as.numeric)
        df <- as.data.frame(scale(df))
    }
    df$"cluster" <- as.factor(df$"cluster")
    return(df)
}

unregister_dopar <- function() {
  env <- foreach:::.foreachGlobals
  rm(list=ls(name=env), pos=env)
}
```

## Caret CV

```{r}
# checkpoint
train_control <- caret::trainControl(
    method = "cv",             # Cross-validation
    number = 5,                # 5-fold CV
    search = "grid",           # Grid search
    verboseIter = TRUE
)
```

## Hyperparameter tuning

### Random forest

Each model is trained with a nested-CV like process:

1. training subset of the data: hyperparameter grid search over CV to find the best hyperparameters
2. full subset of the data: fixed hyperparameter CV to get an estimate of model performance
3. full subset of the data again: fit the inner nested hyperparameters for final model

For random forest, I vary the following hyperparameters:

- Number of trees
- number of attributes that are randomly selected for the split search when constructing each tree
- limits on the tree depth (for each tree)

```{r}
set.seed(42)

training_data <- prep_data(train_classification_df)

# Hyperparameters
tune_grid <- expand.grid(mtry = c(1:20))

time <- Sys.time()
cl <- makePSOCKcluster(64)
registerDoParallel(cl)
trained_models <- list()
counter <- 0
for (maxnodes in c(5, 10, 15)) {
    for (nodesize in c(1:5)) {
        for (ntree in c(100, 1000, 2000, 3000)) {
            rf_model <- train(
                cluster ~ .,
                data = training_data,
                method = "rf",
                trControl = train_control,
                tuneGrid = tune_grid,
                ntree = ntree,
                maxnodes = maxnodes,
                nodesize = nodesize
            )
            trained_models[[length(trained_models) + 1]] <- rf_model
            names(trained_models)[[length(trained_models)]] <- paste0(
                "maxnodes_", maxnodes,
                "nodesize_", nodesize,
                "ntree_", ntree
            )
            counter <- counter + 1
            print(paste0(round(counter / (3*5*4) * 100, 2), "% complete..."))
        }
    }
}
stopCluster(cl)

unregister_dopar()

print(Sys.time() - time)

saveRDS(trained_models, model_path("rf_models.rds", TRUE))
rf_models <- readRDS(model_path("2024_11_11_rf_models.rds"))


rf_models[[1]]$results$"Accuracy" |> max()

# About 77.85% max
rf_accuracies <- lapply(
    rf_models,
    function(x) {
        max(x$"results"$"Accuracy")
    }
)

max(as.numeric(rf_accuracies))
```

### SVM


```{r}
set.seed(42)

svm_tune_grid_1 <- expand.grid(
    sigma = c(0.001, 0.01, 0.1, 0.5, 1),
    C = c(0.1, 1, 10, 100, 1000)
)

svm_model <- train(
  cluster ~ .,                # Formula for the model
  data = prep_data(train_classification_df, TRUE),                # Your dataset
  method = "svmRadial",       # Using radial kernel
  trControl = train_control,  # Cross-validation settings
  tuneGrid = svm_tune_grid_1        # Hyperparameter grid to tune
)

print(svm_model)

svm_tune_grid_2 <- expand.grid(
    sigma = c(0.01, 0.05, 0.1, 0.25, 0.5, 0.75, 1),
    C = c(0.1, 0.5, 1, 2, 5, 10, 25, 50, 100, 200, 400, 600, 750, 1000)
)

svm_model2 <- train(
  cluster ~ .,                # Formula for the model
  data = prep_data(train_classification_df, TRUE),                # Your dataset
  method = "svmRadial",       # Using radial kernel
  trControl = train_control,  # Cross-validation settings
  tuneGrid = svm_tune_grid_2        # Hyperparameter grid to tune
)


svm_tune_grid_2 <- expand.grid(
    sigma = c(0.01, 0.05, 0.1, 0.25, 0.5, 0.75, 1),
    C = c(0.1, 0.5, 1, 2, 5, 10, 25, 50, 100, 200, 400, 600, 750, 1000)
)

svm_model2 <- train(
  cluster ~ .,                # Formula for the model
  data = prep_data(train_classification_df, TRUE),                # Your dataset
  method = "svmRadial",       # Using radial kernel
  trControl = train_control,  # Cross-validation settings
  tuneGrid = svm_tune_grid_2        # Hyperparameter grid to tune
)

saveRDS(svm_model2, model_path("svm_model.rds", TRUE))
svm_model <- readRDS(model_path("2024_11_11_svm_model.rds"))
```

### XGBoost

```{r}
xgb_tune_grid <- expand.grid(
  nrounds = c(50, 100, 200),
  max_depth = c(4, 6, 8),
  eta = c(0.01, 0.1, 0.2),
  gamma = c(0, 0.25, 0.5),
  colsample_bytree = c(0.6, 0.8, 1),
  min_child_weight = c(1, 5),
  subsample = c(0.5, 0.75, 1)
)

xgb_model <- train(
    cluster ~ .,
    data = prep_data(train_classification_df),
    method = "xgbTree",
    trControl = train_control,
    tuneGrid = xgb_tune_grid
)
stopCluster(cl)
unregister_dopar()




xgb_model$results

xgb_model

training_data <- prep_data(train_classification_df)

future::plan(future::multisession, workers = 64)

xgboost_iter <- function(tune_grid) {
    p <- progressor(nrow(tune_grid))
    models <- future_apply(
        tune_grid,
        1,
        function(x) {
            p()
            cnames <- names(x)
            grid <- data.frame(t(x))
            colnames(grid) <- cnames
            xgb_model <- train(
                cluster ~ .,
                data = training_data,
                method = "xgbTree",
                trControl = train_control,
                tuneGrid = grid
            )
            xgb_model
        }
    )
    return(models)
}

xgb_models <- with_progress(xgboost_iter(mini_grid))

q[[1]]$"results"

z <- data.frame()

do.call(rbind, lapply(q, function(x) x$"results"))

###############################################################################
prog <- progressr::progressor(steps = nrow(mini_grid))

xgb_model <- future.apply::future_apply(
    settings_and_weights_df,
    1,
    batch_row_function
)


###############################################################################

time <- Sys.time()
cl <- makePSOCKcluster(64)
registerDoParallel(cl)

xgb_model <- train(
    cluster ~ .,
    data = prep_data(train_classification_df),
    method = "xgbTree",
    trControl = train_control,
    tuneGrid = xgb_tune_grid,
    allowParallel = TRUE
)


print(Sys.time() - time)


print(xgb_model$bestTune)

saveRDS(xgb_model, model_path("xgb_subtype_classifier_1.rds", TRUE))
xgb_model <- readRDS(model_path("2024_11_07_xgb_subtype_classifier_1.rds"))

saveRDS(rf_model, model_path("rf_subtype_classifier_1.rds", TRUE))
rf_model <- readRDS(model_path("2024_11_07_rf_subtype_classifier_1.rds"))
```

```{r}
# Train the xgboost model with cross-validation
xgb_model_2 <- train(
  cluster ~ ., 
  data = df_no_id, 
  method = "xgbTree", 
  trControl = train_control, 
  tuneGrid = tune_grid
)

saveRDS(xgb_model_2, model_path("xgb_subtype_classifier_2.rds", TRUE))
xgb_model_2 <- readRDS(model_path("2024_11_07_xgb_subtype_classifier_2.rds"))
```


```{r}
# Train the KNN model
knn_model <- train(
  cluster ~ ., 
  data = df_no_id, 
  method = "knn", 
  trControl = train_control, 
  tuneLength = 130  # Tuning k (number of neighbors)
)

saveRDS(knn_model, model_path("knn_subtype_classifier_1.rds", TRUE))
knn_model <- readRDS(model_path("2024_11_07_knn_subtype_classifier_1.rds"))
```

```{r}

xgb_model_2 <- readRDS(model_path("2024_11_07_xgb_subtype_classifier_2.rds"))
knn_model <- readRDS(model_path("2024_11_07_knn_subtype_classifier_1.rds"))
xgb_model <- readRDS(model_path("2024_11_07_xgb_subtype_classifier_1.rds"))
rf_model <- readRDS(model_path("2024_11_07_rf_subtype_classifier_1.rds"))

xgb_model_2 |> head()

resamples(
    list(
        "xgb" = xgb_model,
        "xgb2" = xgb_model_2,
        "rf" = rf_model,
        "knn" = knn_model
    )
) |> dotplot()

```

Learning curves?


```{r}

# Load caret library
library(caret)

# Example dataset
data(iris)

# Set up training control with cross-validation
fitControl <- trainControl(method = "cv", number = 5)

# Define the grid for hyperparameters
tuneGrid <- expand.grid(
  mtry = c(1, 2, 3),             # Number of attributes randomly selected for each split
  maxnodes = c(5, 10, 15),       # Max nodes (proxy for tree depth)
  ntree = c(50, 100, 150)        # Number of trees
)

# Train model with caret
model <- train(
  Species ~ ., data = iris,
  method = "rf",
  trControl = fitControl,
  tuneGrid = tuneGrid,
  ntree = tuneGrid$ntree,          # Pass the number of trees directly
  maxnodes = tuneGrid$maxnodes     # Pass maxnodes directly if supported
)

# View the results
print(model)

```
