## Importing packages and establishing file paths

```{r}
library(readr)
library(here)
library(abcdutils)
library(dplyr)
#library(metasnf)
#library(rlist)
#library(tibble)
#library(ggplot2)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
```

```{r}
mtbi_full_df <- read_csv(proc_path("2024_09_18_mtbi_full_df.csv"))
```

# Building a Classifier

I'll ideally be able to create a classifier that doesn't rely on the mTBI-related subjects.
So we'll only want to use features that were both considered generalizable and that are present in uninjured children.
These features are the same as those that were characterized in the matched uninjured group.

```{r}
mtbi_gen_fts_in_long <- read_csv(proc_path("2024_09_23_mtbi_gen_fts_in_long.csv"))

classifier_fts <- unique(mtbi_gen_fts_in_long$feature) 
classifier_fts <- classifier_fts[!grepl("mtbi", classifier_fts)]
classifier_fts[grepl("race_", classifier_fts)] <- "race"
classifier_fts <- unique(classifier_fts)

write_csv(data.frame(classifier_fts), proc_path("classifier_fts.csv", TRUE))
```

```{r}
classifier_fts <- read_csv(proc_path("2024_09_25_classifier_fts.csv"))$"classifier_fts"

colnames(mtbi_full_df)

mtbi_classification_df <- dplyr::select(
    mtbi_full_df,
    subjectkey,
    cluster,
    all_of(classifier_fts)
)

mtbi_classification_df <- mtbi_classification_df |>
    relocate(cluster, .after = last_col())

write_csv(mtbi_classification_df, proc_path("mtbi_classification_df.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_classification_df <- read_csv(proc_path("2024_09_25_mtbi_classification_df.csv"))
```
