# Label propagation of Longitudinal mTBI subjects

## 1. Baseline vs. Longitudinal data of longitudinal mTBI subjects

We are interested in knowing, how effective is our baseline cluster solution at explaining CBCL levels within our longitudinal sample?
If our clustering is primarily informing us about risk-factors, we should expect that the baseline (pre-injury) data of the longitudinal mTBI subjects will be highly informative of their behaviour separations.
On the other hand, if our cluster solution is primarily driven by the injury, we should expect that the longitudinal data will be more informative of the behaviour separations.

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)
library(ggplot2)
library(patchwork)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
```

```{r}
# The longitudinal subject data
all_dls_l <- list.load(input_path("2024_06_18_all_dls_l.rds"))

# The baseline subject data
all_dls_b <- list.load(input_path("2024_04_19_all_dls.rds"))

# The baseline solution
mtbi_mc_d_esm <- read_csv(proc_path("2024_05_30_mtbi_mc_d_esm.csv"))
```

I will check to see how good of a fit the baseline data of the longitudinal subjects is to the baseline solution.

```{r}
mtbi_l0_data_lists <- all_dls_l$"mtbi_l0_data_lists"
mtbi_l2_data_lists <- all_dls_l$"mtbi_l2_data_lists"
mtbi_l0_oom_lists <- all_dls_l$"mtbi_l0_oom_lists"
mtbi_l2_oom_lists <- all_dls_l$"mtbi_l2_oom_lists"
uninj_l0_data_lists <- all_dls_l$"uninj_l0_data_lists"
uninj_l2_data_lists <- all_dls_l$"uninj_l2_data_lists"
uninj_l0_oom_lists <- all_dls_l$"uninj_l0_oom_lists"
uninj_l2_oom_lists <- all_dls_l$"uninj_l2_oom_lists"
```

Quick plot of a couple of CBCL variables:

```{r}
mtbi_l0_oom_df_1 <- mtbi_l0_oom_lists$"imp_1" |> collapse_dl()
mtbi_l2_oom_df_1 <- mtbi_l2_oom_lists$"imp_1" |> collapse_dl()

uninj_l0_oom_df_1 <- uninj_l0_oom_lists$"imp_1" |> collapse_dl()
uninj_l2_oom_df_1 <- uninj_l2_oom_lists$"imp_1" |> collapse_dl()

mtbi_l0_oom_df_1$"cluster" <- "mtbi_l_t0"
mtbi_l2_oom_df_1$"cluster" <- "mtbi_l_t2"
uninj_l0_oom_df_1$"cluster" <- "uninj_l_t0"
uninj_l2_oom_df_1$"cluster" <- "uninj_l_t2"

mtbi_l_oom_df_1 <- rbind(mtbi_l0_oom_df_1, mtbi_l2_oom_df_1)
uninj_l_oom_df_1 <- rbind(uninj_l0_oom_df_1, uninj_l2_oom_df_1)
l_oom_df_1 <- rbind(mtbi_l_oom_df_1, uninj_l_oom_df_1)

outcomes <- dl_variable_summary(mtbi_l0_oom_lists[[1]])$"name"


outcome_plot_list <- list()
for (outcome in outcomes) {
    plot <- jitter_plot(l_oom_df_1, outcome)
    outcome_plot_list[[length(outcome_plot_list) + 1]] <- plot
}

library(patchwork)

outcome_plot_list <- lapply(
    outcome_plot_list,
    function(x) {
        x <- x +
            ggplot2::stat_summary(
                fun = "mean",
                geom = "crossbar",
                colour = "black",
                size = 2
            ) +
            ggplot2::stat_summary(
                fun = "mean", colour = "white", size = 4,
                geom = "text", aes(label = round(after_stat(y), 2)),
                position = position_nudge(y = 0)
            )
    }
)

outcome_plot_wrap <- wrap_plots(outcome_plot_list)

ggsave(
    plot = outcome_plot_wrap,
    file = fig_path("quick_outcome_inj_v_t.png", TRUE),
    dpi = 100,
    width = 20,
    height = 20
)
```

Here I check how the longitudinal subjects map onto our initial baseline mTBI solution.

```{r}
mtbi_b_data_list <- all_dls_b$"mtbi_train_data_lists"$"imp_3"

mtbi_l0_data_list_imp_1 <- mtbi_l0_data_lists$"imp_1"
mtbi_l0_data_list_imp_2 <- mtbi_l0_data_lists$"imp_2"
mtbi_l0_data_list_imp_3 <- mtbi_l0_data_lists$"imp_3"
mtbi_l0_data_list_imp_4 <- mtbi_l0_data_lists$"imp_4"
mtbi_l0_data_list_imp_5 <- mtbi_l0_data_lists$"imp_5"
mtbi_l0_oom_list_imp_1 <- mtbi_l0_oom_lists$"imp_1"
mtbi_l0_oom_list_imp_2 <- mtbi_l0_oom_lists$"imp_2"
mtbi_l0_oom_list_imp_3 <- mtbi_l0_oom_lists$"imp_3"
mtbi_l0_oom_list_imp_4 <- mtbi_l0_oom_lists$"imp_4"
mtbi_l0_oom_list_imp_5 <- mtbi_l0_oom_lists$"imp_5"

# Remove injury variables from baseline data list
preinjury_components <- summarize_dl(mtbi_l0_data_list_imp_1)$"name"
mtbi_b_components <- summarize_dl(mtbi_b_data_list)$"name"
keep_components <- mtbi_b_components %in% preinjury_components

mtbi_b_data_list_no_mtbi <- mtbi_b_data_list[keep_components]

# Remove inclusion injury variables from baseline solutions matrix
mtbi_mc_d_esm_no_mtbi <- mtbi_mc_d_esm |>
    dplyr::select(
        -dplyr::contains(
            c(
                "mtbi_mem_daze",
                "mtbi_mechanism",
                "mtbi_loc",
                "mtbi_age",
                "previous_mtbis"
            )
        )
    )

summarize_dl(mtbi_l0_data_list_imp_1)

summarize_dl(mtbi_b_data_list_no_mtbi)

mtbi_b_l0_imp_1_dl <- merge_data_lists(
    mtbi_b_data_list_no_mtbi,
    mtbi_l0_data_list_imp_1
)

mtbi_b_l0_imp_2_dl <- merge_data_lists(
    mtbi_b_data_list_no_mtbi,
    mtbi_l0_data_list_imp_2
)

mtbi_b_l0_imp_3_dl <- merge_data_lists(
    mtbi_b_data_list_no_mtbi,
    mtbi_l0_data_list_imp_3
)

mtbi_b_l0_imp_4_dl <- merge_data_lists(
    mtbi_b_data_list_no_mtbi,
    mtbi_l0_data_list_imp_4
)

mtbi_b_l0_imp_5_dl <- merge_data_lists(
    mtbi_b_data_list_no_mtbi,
    mtbi_l0_data_list_imp_5
)

list.save(mtbi_b_l0_imp_1_dl, proc_path("mtbi_b_l0_imp_1_dl.rds", TRUE))
list.save(mtbi_b_l0_imp_2_dl, proc_path("mtbi_b_l0_imp_2_dl.rds", TRUE))
list.save(mtbi_b_l0_imp_3_dl, proc_path("mtbi_b_l0_imp_3_dl.rds", TRUE))
list.save(mtbi_b_l0_imp_4_dl, proc_path("mtbi_b_l0_imp_4_dl.rds", TRUE))
list.save(mtbi_b_l0_imp_5_dl, proc_path("mtbi_b_l0_imp_5_dl.rds", TRUE))
```

```{r}
mtbi_b_l0_imp_1_dl <- list.load(proc_path("2024_06_21_mtbi_b_l0_imp_1_dl.rds"))
mtbi_b_l0_imp_2_dl <- list.load(proc_path("2024_06_21_mtbi_b_l0_imp_2_dl.rds"))
mtbi_b_l0_imp_3_dl <- list.load(proc_path("2024_06_21_mtbi_b_l0_imp_3_dl.rds"))
mtbi_b_l0_imp_4_dl <- list.load(proc_path("2024_06_21_mtbi_b_l0_imp_4_dl.rds"))
mtbi_b_l0_imp_5_dl <- list.load(proc_path("2024_06_21_mtbi_b_l0_imp_5_dl.rds"))

my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

###############################################################################
# Label propagation
###############################################################################
mtbi_b_l0_imp_1_lp <- lp_solutions_matrix(
    mtbi_mc_d_esm_no_mtbi,
    mtbi_b_l0_imp_1_dl,
    distance_metrics_list = my_distance_metrics
)
write_csv(mtbi_b_l0_imp_1_lp, proc_path("mtbi_b_l0_imp_1_lp.csv", TRUE))

mtbi_b_l0_imp_2_lp <- lp_solutions_matrix(
    mtbi_mc_d_esm_no_mtbi,
    mtbi_b_l0_imp_2_dl,
    distance_metrics_list = my_distance_metrics
)
write_csv(mtbi_b_l0_imp_2_lp, proc_path("mtbi_b_l0_imp_2_lp.csv", TRUE))

mtbi_b_l0_imp_3_lp <- lp_solutions_matrix(
    mtbi_mc_d_esm_no_mtbi,
    mtbi_b_l0_imp_3_dl,
    distance_metrics_list = my_distance_metrics
)
write_csv(mtbi_b_l0_imp_3_lp, proc_path("mtbi_b_l0_imp_3_lp.csv", TRUE))

mtbi_b_l0_imp_4_lp <- lp_solutions_matrix(
    mtbi_mc_d_esm_no_mtbi,
    mtbi_b_l0_imp_4_dl,
    distance_metrics_list = my_distance_metrics
)
write_csv(mtbi_b_l0_imp_4_lp, proc_path("mtbi_b_l0_imp_4_lp.csv", TRUE))

mtbi_b_l0_imp_5_lp <- lp_solutions_matrix(
    mtbi_mc_d_esm_no_mtbi,
    mtbi_b_l0_imp_5_dl,
    distance_metrics_list = my_distance_metrics
)
write_csv(mtbi_b_l0_imp_5_lp, proc_path("mtbi_b_l0_imp_5_lp.csv", TRUE))
```

```{r}
mtbi_b_l0_imp_1_lp <- read_csv(proc_path("2024_06_20_mtbi_b_l0_imp_1_lp.csv"))
mtbi_b_l0_imp_2_lp <- read_csv(proc_path("2024_06_20_mtbi_b_l0_imp_2_lp.csv"))
mtbi_b_l0_imp_3_lp <- read_csv(proc_path("2024_06_20_mtbi_b_l0_imp_3_lp.csv"))
mtbi_b_l0_imp_4_lp <- read_csv(proc_path("2024_06_20_mtbi_b_l0_imp_4_lp.csv"))
mtbi_b_l0_imp_5_lp <- read_csv(proc_path("2024_06_20_mtbi_b_l0_imp_5_lp.csv"))

mtbi_l0_imp_1_lp <- mtbi_b_l0_imp_1_lp |>
    dplyr::filter(group == "test") |>
    dplyr::select(-group)

mtbi_l0_imp_2_lp <- mtbi_b_l0_imp_2_lp |>
    dplyr::filter(group == "test") |>
    dplyr::select(-group)

mtbi_l0_imp_3_lp <- mtbi_b_l0_imp_3_lp |>
    dplyr::filter(group == "test") |>
    dplyr::select(-group)

mtbi_l0_imp_4_lp <- mtbi_b_l0_imp_4_lp |>
    dplyr::filter(group == "test") |>
    dplyr::select(-group)

mtbi_l0_imp_5_lp <- mtbi_b_l0_imp_5_lp |>
    dplyr::filter(group == "test") |>
    dplyr::select(-group)

colnames(mtbi_l0_imp_1_lp) <- c("subjectkey", "cluster")
colnames(mtbi_l0_imp_2_lp) <- c("subjectkey", "cluster")
colnames(mtbi_l0_imp_3_lp) <- c("subjectkey", "cluster")
colnames(mtbi_l0_imp_4_lp) <- c("subjectkey", "cluster")
colnames(mtbi_l0_imp_5_lp) <- c("subjectkey", "cluster")

write_csv(mtbi_l0_imp_1_lp, proc_path("mtbi_l0_imp_1_lp.csv", TRUE))
write_csv(mtbi_l0_imp_2_lp, proc_path("mtbi_l0_imp_2_lp.csv", TRUE))
write_csv(mtbi_l0_imp_3_lp, proc_path("mtbi_l0_imp_3_lp.csv", TRUE))
write_csv(mtbi_l0_imp_4_lp, proc_path("mtbi_l0_imp_4_lp.csv", TRUE))
write_csv(mtbi_l0_imp_5_lp, proc_path("mtbi_l0_imp_5_lp.csv", TRUE))
```

```{r}
mtbi_l0_imp_1_lp <- read_csv(proc_path("2024_06_20_mtbi_l0_imp_1_lp.csv"))
mtbi_l0_imp_2_lp <- read_csv(proc_path("2024_06_20_mtbi_l0_imp_2_lp.csv"))
mtbi_l0_imp_3_lp <- read_csv(proc_path("2024_06_20_mtbi_l0_imp_3_lp.csv"))
mtbi_l0_imp_4_lp <- read_csv(proc_path("2024_06_20_mtbi_l0_imp_4_lp.csv"))
mtbi_l0_imp_5_lp <- read_csv(proc_path("2024_06_20_mtbi_l0_imp_5_lp.csv"))

mtbi_l0_imp_1_lp_plots <- auto_plot(
    cluster_df = mtbi_l0_imp_1_lp,
    data_list = mtbi_l0_data_list_imp_1,
    target_list = mtbi_l0_oom_list_imp_1,
    save = fig_path("mtbi_l0_imp_1_lp", TRUE)
)

mtbi_l0_imp_2_lp_plots <- auto_plot(
    cluster_df = mtbi_l0_imp_2_lp,
    data_list = mtbi_l0_data_list_imp_2,
    target_list = mtbi_l0_oom_list_imp_2,
    save = fig_path("mtbi_l0_imp_2_lp", TRUE)
)

mtbi_l0_imp_3_lp_plots <- auto_plot(
    cluster_df = mtbi_l0_imp_3_lp,
    data_list = mtbi_l0_data_list_imp_3,
    target_list = mtbi_l0_oom_list_imp_3,
    save = fig_path("mtbi_l0_imp_3_lp", TRUE)
)
#
mtbi_l0_imp_4_lp_plots <- auto_plot(
    cluster_df = mtbi_l0_imp_4_lp,
    data_list = mtbi_l0_data_list_imp_4,
    target_list = mtbi_l0_oom_list_imp_4,
    save = fig_path("mtbi_l0_imp_4_lp", TRUE)
)
#
mtbi_l0_imp_5_lp_plots <- auto_plot(
    cluster_df = mtbi_l0_imp_5_lp,
    data_list = mtbi_l0_data_list_imp_5,
    target_list = mtbi_l0_oom_list_imp_5,
    save = fig_path("mtbi_l0_imp_5_lp", TRUE)
)

saveRDS(
    object = mtbi_l0_imp_1_lp_plots,
    file = fig_path("mtbi_l0_imp_1_lp_plots.rds", TRUE)
)
saveRDS(
    object = mtbi_l0_imp_2_lp_plots,
    file = fig_path("mtbi_l0_imp_2_lp_plots.rds", TRUE)
)
saveRDS(
    object = mtbi_l0_imp_3_lp_plots,
    file = fig_path("mtbi_l0_imp_3_lp_plots.rds", TRUE)
)
saveRDS(
    object = mtbi_l0_imp_4_lp_plots,
    file = fig_path("mtbi_l0_imp_4_lp_plots.rds", TRUE)
)
saveRDS(
    object = mtbi_l0_imp_5_lp_plots,
    file = fig_path("mtbi_l0_imp_5_lp_plots.rds", TRUE)
)
```

```{r}
mtbi_l0_imp_1_lp_plots <- readRDS(
    fig_path("2024_06_20_mtbi_l0_imp_1_lp_plots.rds")
)

mtbi_l0_imp_1_lp_all_plots <- wrap_plots(mtbi_l0_imp_1_lp_plots)

ggsave(
    fig_path("mtbi_l0_imp_1_lp_all_plots.png", TRUE),
    mtbi_l0_imp_1_lp_all_plots,
    width = 30,
    height = 20
)
```

A comparison of the topologies of the original solution (baseline subjects, baseline data) and the new solution (longitudinal subjects, longitudinal data):

[o] means match, [x] means no match, [~] means pretty close

- [o] brain_volume: 2 >> 1 > 3
- [o] considerate: 1 < 2 < 3
- [o] cortical_sa: 2 >> 1 > 3
- [~] family_angry: 1 > 2 = 3
- [o] family_criticize: 1 > 2 = 3
- [o] family_fight: 1 > 2 = 3
- [~] family_outdo: 1 > 2 = 3
- [x] family_peaceful: 1 > 2 > 3
- [~] family_temper: 1 > 2 = 3
- [o] fmri_cort_cors: 1 = 2 = 3
- [x] fmri_cort_subcort_cors: 1 < 3 < 2
- [x] helps_hurt: 3 > 1 = 2
- [~] household_income: 1 << 2 = 3
- [~] non_school_programs: 1 << 2 = 3
- parent_aggressive: 1 > 2 = 3
- parent_antisocial
- parent_anxdep
- parent_anxdisord
- parent_attention
- parent_avoidant
- parent_depress
- parent_hyperactive
- [x] parent_intrusive: 1 > 2 = 3
- parent_perstr
- parent_somatic
- parent_thought
- parent_withdrawn
- private_instruction
- programs_this_year
- [o] pubertal_status: 2 < 1 = 3
- race
- [x] same_sex_close_friend: 3 >> 2 > 1
- [o] sex (n_female): 3 >> 1 > 2
- weekday_screentime
- weekend_screentime

Long story short, the solution fits quite well.

Next we will compare the effect size of the outcome measures across clusters vs. the effect size based on pre/post injury.

```{r}
lp_dfs <- list(
    mtbi_l0_imp_1_lp,
    mtbi_l0_imp_2_lp,
    mtbi_l0_imp_3_lp,
    mtbi_l0_imp_4_lp,
    mtbi_l0_imp_5_lp
)

pairwise_combinations <- combn(5, 2)

ari_mat <- matrix(ncol = 5, nrow = 5)
diag(ari_mat) <- 1
colnames(ari_mat) <- paste0("imp_", 1:5)
rownames(ari_mat) <- paste0("imp_", 1:5)
for (i in seq_len(ncol(pairwise_combinations))) {
    imp_a <- pairwise_combinations[1, i]
    imp_b <- pairwise_combinations[2, i]
    ari <- mclust::adjustedRandIndex(
        lp_dfs[[imp_a]]$"cluster",
        lp_dfs[[imp_b]]$"cluster"
    )
    ari_mat[imp_a, imp_b] <- ari
    ari_mat[imp_b, imp_a] <- ari
}

library(ComplexHeatmap)

imp_ari_mat <- adjusted_rand_index_heatmap(
    ari_mat,
    show_column_names = TRUE,
    show_row_names = TRUE
)

# Demonstrates how tight the different imputations are to each other
save_heatmap(
    imp_ari_mat,
    fig_path("mtbi_l0_lp_imp_ari_mat.png", TRUE),
    width = 320,
    height = 250,
    res = 100
)

identical(mtbi_l0_oom_lists[[1]], mtbi_l0_oom_lists[[2]])

mtbi_l0_oom_dfs <- lapply(
    seq_along(mtbi_l0_oom_lists),
    function(x) {
        dl <- mtbi_l0_oom_lists[[x]]
        df <- collapse_dl(dl)
        df$"imputation" <- x
        df$"tp" <- 0
        return(df)
    }
)

mtbi_l2_oom_dfs <- lapply(
    seq_along(mtbi_l2_oom_lists),
    function(x) {
        dl <- mtbi_l2_oom_lists[[x]]
        df <- collapse_dl(dl)
        df$"imputation" <- x
        df$"tp" <- 2
        return(df)
    }
)

mtbi_l0_oom_long_dfs <- lapply(
    mtbi_l0_oom_dfs,
    function(x) {
        x <- tidyr::pivot_longer(
            x,
            cols = matches("^(cbcl|sds)_"),
            names_to = "outcome",
            values_to = "value"
        )
        return(x)
    }
)

mtbi_l2_oom_long_dfs <- lapply(
    mtbi_l2_oom_dfs,
    function(x) {
        x <- tidyr::pivot_longer(
            x,
            cols = matches("^(cbcl|sds)_"),
            names_to = "outcome",
            values_to = "value"
        )
        return(x)
    }
)

mtbi_l0_oom_long_dfs[[1]]

mtbi_l0_oom_long_dfs[[2]]

mtbi_l0_oom_long_df <- do.call(rbind, mtbi_l0_oom_long_dfs)
mtbi_l2_oom_long_df <- do.call(rbind, mtbi_l2_oom_long_dfs)
mtbi_oom_long_df <- rbind(mtbi_l0_oom_long_df, mtbi_l2_oom_long_df)
mtbi_oom_long_df$"tp" <- factor(mtbi_oom_long_df$"tp")

mtbi_oom_long_df |>
    dplyr::filter(outcome != "sds_sleep") |>
    ggplot(
        aes(x = outcome, y = value, colour = tp),
        group = tp
    ) +
    geom_violin() +
    geom_point(
        position = position_jitterdodge(
            jitter.width = 0.2,
            jitter.height = 0.3
        ),
        size = 3,
        alpha = 0.3
    ) + theme_bw() +
    facet_wrap(~imputation)


#df_long_t0 <- mtbi_l0_oom_dfs[[2]] |>
#    tidyr::pivot_longer(
#        cols = matches("^(cbcl|sds)_"),
#        names_to = "outcome",
#        values_to = "value"
#    )
#
#df_long_t2 <- mtbi_l2_oom_dfs[[2]] |>
#    tidyr::pivot_longer(
#        cols = matches("^(cbcl|sds)_"),
#        names_to = "outcome",
#        values_to = "value"
#    )
#
#df_long <- rbind(df_long_t0, df_long_t2)
#df_long$"tp" <- as.factor(df_long$"tp")
#
#df_long |>
#    ggplot(
#        aes(x = outcome, y = value, fill = tp)
#    ) +
#    geom_bar(
#        stat = "identity",
#        position = position_dodge()
#    )
#
#df_long |>
#    dplyr::filter(outcome != "sds_sleep") |>
#    ggplot(
#        aes(x = outcome, y = value, colour = tp),
#        group = tp
#    ) +
#    geom_violin() +
#    geom_point(
#        position = position_jitterdodge(
#            jitter.width = 0.2,
#            jitter.height = 0.3
#        ),
#        size = 3,
#        alpha = 0.3
#    ) + theme_bw() +
#    facet_wrap(~imputation)
#
#df_long |>
#    dplyr::filter(outcome == "sds_sleep") |>
#    ggplot(
#        aes(x = tp, y = value, colour = tp),
#        group = tp
#    ) +
#    geom_violin() +
#    geom_point(
#        position = position_jitterdodge(
#            jitter.width = 0.2,
#            jitter.height = 0.2
#        ),
#        size = 3,
#        alpha = 0.3
#    ) + theme_bw()
#



rbind(mtbi_l0_oom_dfs[[1]], mtbi_l2_oom_dfs[[1]]) |>
    ggplot(aes(x = factor(tp), y = cbcl_anxdep)) +
    geom_point(aes(colour = factor(tp)), size = 5) +
    geom_line(aes(group = subjectkey))

mtbi_l0_oom_dfs

outcome_vars <- dl_variable_summary(mtbi_l0_oom_lists[[1]])$"name"

mtbi_l0_oom_dfs[[1]]

for (i in mtbi_l0_oom_dfs) {
    for (j in mtbi_l2_oom_dfs) {
        merged_df <- dplyr::inner_join(i, j, by = "subjectkey")
        for (var in outcome_vars) {
            v0 <- merged_df[, paste0(var, "_t0")]
            v2 <- merged_df[, paste0(var, "_t2")]
            merged_df[, paste0(var, "_delta")] <- v2 - v0
        }
    }
}


# Good for individual scores, but not particularly relevant
for (i in mtbi_l0_oom_dfs) {
    for (j in mtbi_l2_oom_dfs) {
        merged_df <- dplyr::inner_join(i, j, by = "subjectkey")
        for (var in outcome_vars) {
            v0 <- merged_df[, paste0(var, "_t0")]
            v2 <- merged_df[, paste0(var, "_t2")]
            merged_df[, paste0(var, "_delta")] <- v2 - v0
        }
    }
}
```

Effect size prep

```{r}
effect_size_raw <- function(x1, x2) {
    n1 <- length(x1)
    n2 <- length(x2)
    s1 <- sd(x1)
    s2 <- sd(x2)
    s <- pooled_sd(n1, s1, n2, s2)
    mean1 <- mean(x1)
    mean2 <- mean(x2)
    d <- cohens_d(mean1, mean2, s)
    return(d)
}

pooled_sd <- function(n1, s1, n2, s2) {
    numerator <- ((n1 - 1) * (s1^2)) + ((n2 - 1) * (s2^2))
    denominator <- n1 + n2 - 2
    s <- sqrt(numerator / denominator)
    return(s)
}

cohens_d <- function(mean1, mean2, pooled_sd) {
    d <- (mean1 - mean2) / pooled_sd
    return(d)
}

tstat <- function(d, n1, n2) {
    t <- d * sqrt((n1 * n2) / (n1 + n2))
    return(t)
}

es_bound <- function(d, n1, n2) {
    t <- tstat(d, n1, n2)
    es_data <- compute.es::tes(
        t = t,
        n.1 = n1,
        n.2 = n2,
        verbose = FALSE
    )
    return(
        list(
            "lower" = es_data$"l.d",
            "upper" = es_data$"u.d"
        )
    )
}
```

Effect size 1: Pre-injury vs. Post-injury


Effect size 2: Pre-injury Group 0 vs Group 1/2

Effect size 3: Pre-injury Group 0 vs Post-injury Group 0
