# metaSNF of Longitudinal mTBI subjects

## 1. Baseline vs. Longitudinal data of longitudinal mTBI subjects

We are interested in knowing, how effective is our baseline cluster solution at explaining CBCL levels within our longitudinal sample?
If our clustering is primarily informing us about risk-factors, we should expect that the baseline (pre-injury) data of the longitudinal mTBI subjects will be highly informative of their behaviour separations.
On the other hand, if our cluster solution is primarily driven by the injury, we should expect that the longitudinal data will be more informative of the behaviour separations.

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)
library(ggplot2)
library(patchwork)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
```

```{r}
# The longitudinal subject data
all_dls_l <- list.load(input_path("2024_06_17_all_dls_l.rds"))

# The baseline subject data
all_dls_b <- list.load(input_path("2024_04_19_all_dls.rds"))

# The baseline solution
mtbi_mc_d_esm <- read_csv(proc_path("2024_05_30_mtbi_mc_d_esm.csv"))
```

There's a few approaches that I could take here.

One is to try running SNF from scratch on the two sets.
The other is to just try using label propagation.
The label propagation approach seems reasonable enough.

```{r}
mtbi_l0_data_lists <- all_dls_l$"mtbi_l0_data_lists"
mtbi_l2_data_lists <- all_dls_l$"mtbi_l2_data_lists"
mtbi_l0_oom_lists <- all_dls_l$"mtbi_l0_oom_lists"
mtbi_l2_oom_lists <- all_dls_l$"mtbi_l2_oom_lists"
uninj_l0_data_lists <- all_dls_l$"uninj_l0_data_lists"
uninj_l2_data_lists <- all_dls_l$"uninj_l2_data_lists"
uninj_l0_oom_lists <- all_dls_l$"uninj_l0_oom_lists"
uninj_l2_oom_lists <- all_dls_l$"uninj_l2_oom_lists"

mtbi_l0_oom_df_1 <- mtbi_l0_oom_lists$"imp_1" |> collapse_dl()
mtbi_l2_oom_df_1 <- mtbi_l2_oom_lists$"imp_1" |> collapse_dl()

uninj_l0_oom_df_1 <- uninj_l0_oom_lists$"imp_1" |> collapse_dl()
uninj_l2_oom_df_1 <- uninj_l2_oom_lists$"imp_1" |> collapse_dl()

mtbi_l0_oom_df_1$"cluster" <- "mtbi_l_t0"
mtbi_l2_oom_df_1$"cluster" <- "mtbi_l_t2"
uninj_l0_oom_df_1$"cluster" <- "uninj_l_t0"
uninj_l2_oom_df_1$"cluster" <- "uninj_l_t2"

mtbi_l_oom_df_1 <- rbind(mtbi_l0_oom_df_1, mtbi_l2_oom_df_1)
uninj_l_oom_df_1 <- rbind(uninj_l0_oom_df_1, uninj_l2_oom_df_1)
l_oom_df_1 <- rbind(mtbi_l_oom_df_1, uninj_l_oom_df_1)

jitter_plot(l_oom_df_1, "cbcl_anxdep")
jitter_plot(l_oom_df_1, "sds_sleep")
```

It is clear from these plots that the outcome measures were considerably higher in the mTBI group even before they sustained an mTBI.

Let's see how the two propagate onto the baseline solution.

```{r}

mtbi_b_data_list <- all_dls_b$"mtbi_train_data_lists"$"imp_3"
names(mtbi_b_data_list) <- summarize_dl(mtbi_b_data_list)$"name"

mtbi_l0_data_list_1 <- mtbi_l0_data_lists$"imp_1"
names(mtbi_l0_data_list_1) <- summarize_dl(mtbi_l0_data_list_1)$"name"

# Remove injury variables from baseline data list
preinjury_components <- names(mtbi_l0_data_list_1)
mtbi_b_data_list_no_mtbi <- mtbi_b_data_list[preinjury_components]

# Remove injury variables from baseline solutions matrix
mtbi_mc_d_esm_no_mtbi <- mtbi_mc_d_esm |>
    dplyr::select(
        -dplyr::contains(
            c(
                "mtbi_mem_daze",
                "mtbi_mechanism",
                "mtbi_loc",
                "mtbi_age",
                "previous_mtbis"
            )
        )
    )

merge_data_lists()

```
