# Longitudinal analyses

This chapter addresses the following four questions:

1. Was the baseline clustering informative for long-term outcomes?

2. Did the matched uninjured subjects experience more mTBIs by T2 than the other uninjured subjects?

3. Clustering of the longitudinal sample with their baseline vs. their longitudinal data: both equally informative?

4. Classifier built from baseline mTBI data: informative?

## Package loading

```{r}
library(abcdutils)
library(here)
library(dplyr)
library(readr)
library(metasnf)
library(visdat)
library(ggplot2)
library(mice)
library(ggsignif)
library(fastDummies)
library(randomForest)
library(patchwork)
library(tidyr)
library(ComplexHeatmap)

source("helper_functions.R")
```

## Establishing file paths

```{r}
input_path <- path_maker(here(paste0("data/abcd/inputs")))
core_path <- path_maker(here(paste0("data/abcd/core")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
model_path <- path_maker(here(paste0("data/abcd/results/models")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))

read <- function(path) {
    return(read_csv(input_path(path)))
}
```

```{r}
mtbi_ful_df <- readRDS(proc_path("2025_09_16_mtbi_ful_df.rds"))
all_long_dls_h_ns <- readRDS(proc_path("2026_01_19_all_long_dls_h_ns.rds"))
all_long_dls_h <- readRDS(proc_path("2026_01_19_all_long_dls_h.rds"))
all_dls_h_ns <- readRDS(proc_path("2025_09_11_all_dls_h_no_sibs.rds"))
all_dls_h <- readRDS(proc_path("2025_09_11_all_dls_h.rds"))
```

## Q1: Was the baseline clustering informative for LT outcomes?

```{r}
names(all_long_dls_h_ns)

mtbi_l_dls <- all_long_dls_h_ns$"mtbi_l_dls"
mtbi_l_ols <- all_long_dls_h_ns$"mtbi_l_ols"

# Convert list of data lists into list of data frames for plotting
mtbi_l_dl_dfs <- lapply(mtbi_l_dls, as.data.frame)
mtbi_l_ol_dfs <- lapply(mtbi_l_ols, as.data.frame)

# Tag each data frame with its originating imputation
mtbi_l_dl_dfs <- lapply(
    1:5,
    function(x) {
        mtbi_l_dl_dfs[[x]]$"imputation" <- x
        mtbi_l_dl_dfs[[x]]
    }
)

mtbi_l_ol_dfs <- lapply(
    1:5,
    function(x) {
        mtbi_l_ol_dfs[[x]]$"imputation" <- x
        mtbi_l_ol_dfs[[x]]
    }
)

# Horizontally merge list of data frames
mtbi_l_ol_df <- do.call(rbind, mtbi_l_ol_dfs)
mtbi_l_dl_df <- do.call(rbind, mtbi_l_dl_dfs)
mtbi_l_df <- dplyr::full_join(
    mtbi_l_ol_df,
    mtbi_l_dl_df,
    by = c("uid", "imputation")
)

mtbi_l_wt2_ns <- intersect(unique(mtbi_l_df$"uid"), mtbi_ful_df$"uid")
mtbi_l_wt2_ns

# Keep track of baseline data before attaching to longitudinal data
mtbi_ful_df_0 <- mtbi_ful_df
colnames(mtbi_ful_df_0) <- paste0(colnames(mtbi_ful_df_0), "_0")
colnames(mtbi_ful_df_0)

mtbi_ful_df_0 <- mtbi_ful_df_0 |>
    dplyr::rename(
        "uid" = "uid_0",
        "cluster" = "cluster_0",
        "sex" = "sex_0",
        "race" = "race_0"
    )

colnames(mtbi_l_df) <- paste0(colnames(mtbi_l_df), "_l")
mtbi_l_df <- mtbi_l_df |>
    dplyr::rename(
        "uid" = "uid_l",
        "imputation" = "imputation_l"
    )

mtbi_ful_df_0 <- dplyr::filter(
     mtbi_ful_df_0,
     uid %in% mtbi_l_wt2_ns
)
mtbi_l_df <- dplyr::filter(
     mtbi_l_df,
     uid %in% mtbi_l_wt2_ns
)

mtbi_long_changes <- dplyr::full_join(
    mtbi_ful_df_0,
    mtbi_l_df,
    by = "uid"
)

original_names <- gsub("_0", "", colnames(mtbi_ful_df_0)[-c(1:2)])
original_names <- original_names[!grepl("mtbi", original_names)]
replace_names <- original_names[!grepl("race", original_names)]
replace_names <- replace_names[!grepl("sex", replace_names)]

print(colnames(mtbi_long_changes))

i <- 0

mtbi_long_changes |> colnames()

for (name in replace_names) {
    i <- i + 1
    print(i)
    print(name)
    long_val <- mtbi_long_changes[[paste0(name, "_l")]]
    base_val <- mtbi_long_changes[[paste0(name, "_0")]]
    mtbi_long_changes[[paste0(name, "_d")]] <- long_val - base_val
}

mtbi_long_changes$"cluster" <- as.factor(mtbi_long_changes$"cluster")

saveRDS(mtbi_long_changes, proc_path("mtbi_long_changes.rds", TRUE))

mtbi_long_changes <- readRDS(proc_path("2026_01_19_mtbi_long_changes.rds"))
```

```{r}
gg_long_cor <- function(df, feature, long = TRUE) {
    df <- dplyr::filter(df, imputation == 1)
    f1 <- paste0(feature, "_0")
    if (long) {
        f2 <- paste0(feature, "_l")
    } else {
        f2 <- paste0(feature, "_d")
    }
    plot <- ggplot(
        df,
        aes(
            x = .data[[f1]],
            y = .data[[f2]],
            colour = as.factor(cluster)
        )
    ) +
        geom_jitter(alpha = 0.5, height = 0.1, width = 0.1) +
        geom_smooth(method = "lm") +
        theme_bw() +
        labs(colour = "C")
    return(plot)
}

#pubertal_status_y_plot <- gg_long_cor(mtbi_long_changes, "pubertal_status_y")
#household_income_plot <- gg_long_cor(mtbi_long_changes, "household_income")
#extracurriculars_plot <- gg_long_cor(mtbi_long_changes, "extracurriculars")
#parent_perstr_plot <- gg_long_cor(mtbi_long_changes, "parent_perstr")
#activities_last_year_plot <- gg_long_cor(mtbi_long_changes, "activities_last_year")
#considerate_y_plot <- gg_long_cor(mtbi_long_changes, "considerate_y")
## looks kind of like an interaction?
#school_activities_plot <- gg_long_cor(mtbi_long_changes, "school_activities")
#weekend_screentime_plot <- gg_long_cor(mtbi_long_changes, "weekend_screentime")
#family_throw_y_plot <- gg_long_cor(mtbi_long_changes, "family_throw_y")
#
#significant_long_cor_plot <- pubertal_status_y_plot +
#household_income_plot +
#extracurriculars_plot +
#parent_perstr_plot +
#activities_last_year_plot +
#considerate_y_plot +
#school_activities_plot +
#weekend_screentime_plot +
#family_throw_y_plot
#
#significant_long_cor_plot
#
#ggsave(
#    fig_path("significant_long_cor_plot.png", TRUE),
#    significant_long_cor_plot,
#    width = 15,
#    height = 10
#)

cbcl_anxdep_plot <- gg_long_cor(mtbi_long_changes, "cbcl_anxdep", 0)
cbcl_withdep_plot <- gg_long_cor(mtbi_long_changes, "cbcl_withdep", 0)
cbcl_somatic_plot <- gg_long_cor(mtbi_long_changes, "cbcl_somatic", 0)
cbcl_social_plot <- gg_long_cor(mtbi_long_changes, "cbcl_social", 0)
cbcl_thought_plot <- gg_long_cor(mtbi_long_changes, "cbcl_thought", 0)
cbcl_attention_plot <- gg_long_cor(mtbi_long_changes, "cbcl_attention", 0)
cbcl_rulebreak_plot <- gg_long_cor(mtbi_long_changes, "cbcl_rulebreak", 0)
cbcl_aggressive_plot <- gg_long_cor(mtbi_long_changes, "cbcl_aggressive", 0)
sds_sleep_plot <- gg_long_cor(mtbi_long_changes, "sds_sleep", 0)

outcome_long_cor_plots <- wrap_plots(
    list(
        cbcl_anxdep_plot,
        cbcl_withdep_plot,
        cbcl_somatic_plot,
        cbcl_social_plot,
        cbcl_thought_plot,
        cbcl_attention_plot,
        cbcl_rulebreak_plot,
        cbcl_aggressive_plot,
        sds_sleep_plot
    )
)

outcome_long_cor_plots

ggsave(
    fig_path("outcome_long_cor_plots.png", TRUE),
    outcome_long_cor_plots,
    width = 15,
    height = 10
)

cbcl_anxdep_plot2 <- gg_long_cor(mtbi_long_changes, "cbcl_anxdep")
cbcl_withdep_plot2 <- gg_long_cor(mtbi_long_changes, "cbcl_withdep")
cbcl_somatic_plot2 <- gg_long_cor(mtbi_long_changes, "cbcl_somatic")
cbcl_social_plot2 <- gg_long_cor(mtbi_long_changes, "cbcl_social")
cbcl_thought_plot2 <- gg_long_cor(mtbi_long_changes, "cbcl_thought")
cbcl_attention_plot2 <- gg_long_cor(mtbi_long_changes, "cbcl_attention")
cbcl_rulebreak_plot2 <- gg_long_cor(mtbi_long_changes, "cbcl_rulebreak")
cbcl_aggressive_plot2 <- gg_long_cor(mtbi_long_changes, "cbcl_aggressive")

sds_sleep_plot2 <- gg_long_cor(mtbi_long_changes, "sds_sleep")

outcome_long_cor_plots_2 <- wrap_plots(
    list(
        cbcl_anxdep_plot2,
        cbcl_withdep_plot2,
        cbcl_somatic_plot2,
        cbcl_social_plot2,
        cbcl_thought_plot2,
        cbcl_attention_plot2,
        cbcl_rulebreak_plot2,
        cbcl_aggressive_plot2,
        sds_sleep_plot2
    )
)

outcome_long_cor_plots_2

ggsave(
    fig_path("outcome_long_cor_plots_2.png", TRUE),
    outcome_long_cor_plots_2,
    width = 15,
    height = 10
)


gg_long_cor(mtbi_long_changes, "cbcl_anxdep", 0)

gg_long_cor(mtbi_long_changes, "cbcl_withdep")

gg_long_cor(mtbi_long_changes, "cbcl_somatic")

gg_long_cor(mtbi_long_changes, "cbcl_anxdep")

gg_long_cor(mtbi_long_changes, "cbcl_withdep")

gg_long_cor(mtbi_long_changes, "cbcl_somatic")

gg_long_cor(mtbi_long_changes, "cbcl_social")

gg_long_cor(mtbi_long_changes, "cbcl_thought")

gg_long_cor(mtbi_long_changes, "cbcl_attention")

gg_long_cor(mtbi_long_changes, "cbcl_rulebreak")

gg_long_cor(mtbi_long_changes, "cbcl_aggressive")

gg_long_cor(mtbi_long_changes, "sds_sleep")

gg_long_cor(mtbi_long_changes, "cbcl_withdep", 0)

gg_long_cor(mtbi_long_changes, "cbcl_somatic", 0)

gg_long_cor(mtbi_long_changes, "cbcl_anxdep", 0)

gg_long_cor(mtbi_long_changes, "cbcl_withdep", 0)

gg_long_cor(mtbi_long_changes, "cbcl_somatic", 0)

gg_long_cor(mtbi_long_changes, "cbcl_social", 0)

gg_long_cor(mtbi_long_changes, "cbcl_thought", 0)

gg_long_cor(mtbi_long_changes, "cbcl_attention", 0)

gg_long_cor(mtbi_long_changes, "cbcl_rulebreak", 0)

gg_long_cor(mtbi_long_changes, "cbcl_aggressive", 0)

gg_long_cor(mtbi_long_changes, "sds_sleep", 0)

gg_long_cor(mtbi_long_changes, "parent_perstr", 0)

gg_long_cor(mtbi_long_changes, "activities_last_year")

gg_long_cor(mtbi_long_changes, "pubertal_status_y")

gg_long_cor(mtbi_long_changes, "pubertal_status_p")

gg_long_cor(mtbi_long_changes, "school_activities")

gg_long_cor(mtbi_long_changes, "weekend_screentime")

gg_long_cor(mtbi_long_changes, "household_income")

colnames(mtbi_long_changes)

cor_mat <- mtbi_long_changes |>
    dplyr::select(-uid, -mtbi_mechanism_0, -race_l) |>
    dplyr::mutate(cluster = as.numeric(cluster)) |>
    dummy_cols(
        select_columns = "race",
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = TRUE
    ) |>
    cor()

cor_mat[!grepl("_d$|_l$", colnames(cor_mat)), grepl("_d$", colnames(cor_mat))] |>
    Heatmap()

cor_mat["cluster", grepl("_d$", colnames(cor_mat))] |>
    Heatmap()

lm_long_fit <- function(df, feature) {
    models <- list(
      lm(as.formula(paste0(feature, "_l ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 1)),
      lm(as.formula(paste0(feature, "_l ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 2)),
      lm(as.formula(paste0(feature, "_l ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 3)),
      lm(as.formula(paste0(feature, "_l ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 4)),
      lm(as.formula(paste0(feature, "_l ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 5))
    )
    pooled_results <- pool(as.mira(models))
    return(summary(pooled_results))
}

pval_df <- data.frame()
for (feature in replace_names) {
    model <- lm_long_fit(mtbi_long_changes, feature)
    pval_df <- rbind(
        pval_df,
        data.frame(
            feature = c(feature, feature),
            compare = c("c1_vs_c2", "c1_vs_c3"),
            p = c(model$"p.value"[3], model$"p.value"[4])
        )
    )
    if (min(model$"p.value"[3]) < 0.05) {
        cat("\n", feature, signif(model$"p.value"[3], 2), "\n")
        print(model)
    }
}
pval_df$"padj" <- p.adjust(pval_df$"p", method = "fdr")

pval_df |>
    dplyr::filter(padj < 0.05) |>
    dplyr::select(-p) |>
    dplyr::mutate(padj = format(padj, scientific = FALSE, digits = 2)) |>
    dplyr::arrange(padj)

# None are significant
cbcl_anxdep_p <- lm_long_fit(mtbi_long_changes, "cbcl_anxdep")
cbcl_withdep_p <- lm_long_fit(mtbi_long_changes, "cbcl_withdep")
cbcl_somatic_p <- lm_long_fit(mtbi_long_changes, "cbcl_somatic")
cbcl_social_p <- lm_long_fit(mtbi_long_changes, "cbcl_social")
cbcl_thought_p <- lm_long_fit(mtbi_long_changes, "cbcl_thought")
cbcl_attention_p <- lm_long_fit(mtbi_long_changes, "cbcl_attention")
cbcl_rulebreak_p <- lm_long_fit(mtbi_long_changes, "cbcl_rulebreak")
cbcl_aggressive_p <- lm_long_fit(mtbi_long_changes, "cbcl_aggressive")
sds_sleep_p <- lm_long_fit(mtbi_long_changes, "sds_sleep")

p_list <- list(
    "cbcl_anxdep" = cbcl_anxdep_p,
    "cbcl_withdep" = cbcl_withdep_p,
    "cbcl_somatic" = cbcl_somatic_p,
    "cbcl_social" = cbcl_social_p,
    "cbcl_thought" = cbcl_thought_p,
    "cbcl_attention" = cbcl_attention_p,
    "cbcl_rulebreak" = cbcl_rulebreak_p,
    "cbcl_aggressive" = cbcl_aggressive_p,
    "sds_sleep" = sds_sleep_p
)

sds_sleep_p

p_list_short <- lapply(
    names(p_list),
    function(x) {
        p_list[[x]] <- dplyr::select(p_list[[x]], term, p.value)
        colnames(p_list[[x]]) <- c("term", x)
        p_list[[x]][3:4, ]
    }
)
p_df <- as.data.frame(t(merge_df_list(p_list_short, uid = "term")))
p_df$"term" <- rownames(p_df)
rownames(p_df) <- NULL
p_df <- p_df[-1, ]
colnames(p_df) <- c("cluster_2_p", "cluster_3_p", "term")
p_df <- dplyr::select(p_df, term, everything())
p_df$"cluster_2_p" <- as.numeric(p_df$"cluster_2_p")
p_df$"cluster_3_p" <- as.numeric(p_df$"cluster_3_p")
p_df |>
    knitr::kable(format = "markdown", digits = 2) |>
    writeLines(proc_path("p_values_of_cluster.txt", TRUE))

# An LRT-based approach
lm_long_lrt_fit <- function(df, feature) {
    base_model <- lm(as.formula(paste0(feature, "_l ~ ", feature, "_0")), data = filter(df, imputation == 1))
    full_model <- lm(as.formula(paste0(feature, "_l ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 1))
    return(anova(base_model, full_model))
}

lm_long_lrt_fit(mtbi_long_changes, "cbcl_anxdep")
```

Cluster is never a significant feature in predicting longitudinal outcome given baseline outcome.


## Longitudinal trajectory check 1

In this section, I first adjust CBCL values by age and sex, bin them according to their quantiles within the entire ABCD dataset, and then check to see how profiles based on those bins differ across the clusters.

```{r}
mtbi_long_changes <- readRDS(proc_path("2026_01_19_mtbi_long_changes.rds"))

# Separating by time
df0 <- mtbi_long_changes |>
    dplyr::select(
        uid,
        cluster,
        imputation,
        dplyr::starts_with("cbcl"),
        dplyr::starts_with("sds")
    ) |>
    dplyr::select(
        uid,
        cluster,
        imputation,
        dplyr::ends_with("0")
    ) |>
    dplyr::mutate(t = "0")
colnames(df0) <- gsub("_0", "", colnames(df0))

dfl <- mtbi_long_changes |>
    dplyr::select(
        uid,
        cluster,
        imputation,
        dplyr::starts_with("cbcl"),
        dplyr::starts_with("sds")
    ) |>
    dplyr::select(
        uid,
        cluster,
        imputation,
        dplyr::ends_with("l")    
    ) |>
    dplyr::mutate(t = "2")
colnames(dfl) <- gsub("_l", "", colnames(dfl))

import <- function(path) {
    return(abcdutils::abcd_load(core_path(path)))
}

mh_p_cbcl <- import("mental-health/mh_p_cbcl.csv")
gish_p_gi <- import("gender-identity-sexual-health/gish_p_gi.csv")
abcd_y_lt <- import("abcd-general/abcd_y_lt.csv")
ph_p_sds <- import("physical-health/ph_p_sds.csv")

all_sex_0 <- get_sex(gish_p_gi, t = 0) |>
    dplyr::mutate(uid = paste0("uid_", subjectkey)) |>
    dplyr::select(-subjectkey)
all_cbcl_0 <- get_cbcl_syndrome_scale(mh_p_cbcl, t = 0) |>
    dplyr::mutate(uid = paste0("uid_", subjectkey)) |>
    dplyr::select(-subjectkey)
all_sds_0 <- get_sleep_disturbance(ph_p_sds, t = 0) |>
    dplyr::mutate(uid = paste0("uid_", subjectkey)) |>
    dplyr::select(-subjectkey)
all_age_0 <- get_interview_age(abcd_y_lt = abcd_y_lt, t = 0, as_years = FALSE) |>
    dplyr::mutate(uid = paste0("uid_", subjectkey)) |>
    dplyr::rename("age" = "interview_age") |>
    dplyr::select(-subjectkey)

all_sex_l <- all_sex_0
all_cbcl_l <- get_cbcl_syndrome_scale(mh_p_cbcl, t = 2) |>
    dplyr::mutate(uid = paste0("uid_", subjectkey)) |>
    dplyr::select(-subjectkey)
all_sds_l <- get_sleep_disturbance(ph_p_sds, t = 2) |>
    dplyr::mutate(uid = paste0("uid_", subjectkey)) |>
    dplyr::select(-subjectkey)
all_age_l <- get_interview_age(abcd_y_lt = abcd_y_lt, t = 2, as_years = FALSE) |>
    dplyr::mutate(uid = paste0("uid_", subjectkey)) |>
    dplyr::rename("age" = "interview_age") |>
    dplyr::select(-subjectkey)

source("abcd/helper_functions.R")

all_out_0 <- dplyr::inner_join(
    all_sex_0,
    all_cbcl_0,
    by = "uid"
) |>
    dplyr::inner_join(
        all_age_0,
        by = "uid"
    ) |>
    dplyr::inner_join(
        all_sds_0,
        by = "uid"
    ) |>
    na.omit() |>
    dplyr::filter(sex %in% c("F", "M")) |>
    dplyr::rename(
        "cbcl_anxdep" = "cbcl_scr_syn_anxdep_r",
        "cbcl_withdep" = "cbcl_scr_syn_withdep_r",
        "cbcl_somatic" = "cbcl_scr_syn_somatic_r",
        "cbcl_social" = "cbcl_scr_syn_social_r",
        "cbcl_thought" = "cbcl_scr_syn_thought_r",
        "cbcl_attention" = "cbcl_scr_syn_attention_r",
        "cbcl_rulebreak" = "cbcl_scr_syn_rulebreak_r",
        "cbcl_aggressive" = "cbcl_scr_syn_aggressive_r",
        "sds_sleep" = "sds_p_ss_total"
    ) |>
    dplyr::mutate(cluster = sex)

all_out_l <- dplyr::inner_join(
    all_sex_l,
    all_cbcl_l,
    by = "uid"
) |>
    dplyr::inner_join(
        all_age_l,
        by = "uid"
    ) |>
    dplyr::inner_join(
        all_sds_l,
        by = "uid"
    ) |>
    na.omit() |>
    dplyr::filter(sex %in% c("F", "M")) |>
    dplyr::rename(
        "cbcl_anxdep" = "cbcl_scr_syn_anxdep_r",
        "cbcl_withdep" = "cbcl_scr_syn_withdep_r",
        "cbcl_somatic" = "cbcl_scr_syn_somatic_r",
        "cbcl_social" = "cbcl_scr_syn_social_r",
        "cbcl_thought" = "cbcl_scr_syn_thought_r",
        "cbcl_attention" = "cbcl_scr_syn_attention_r",
        "cbcl_rulebreak" = "cbcl_scr_syn_rulebreak_r",
        "cbcl_aggressive" = "cbcl_scr_syn_aggressive_r",
        "sds_sleep" = "sds_p_ss_total"
    ) |>
    dplyr::mutate(cluster = sex)

# top, bottom, mid quantiles - do profiles shift?

# Constructing adjustment models for each outcome for each timepoint
out_cols <- grep("^(cbcl|sds)", names(all_out_0), value = TRUE)

all_out_0$"t" <- 0
all_out_l$"t" <- 2

all_out <- rbind(all_out_0, all_out_l)

models <- lapply(
    out_cols,
    function(col) {
        formula <- as.formula(paste(col, "~ age + sex + t"))
        lm(formula, data = all_out)
    }
)
names(models) <- out_cols

#models_0 <- lapply(
#    out_cols,
#    function(col) {
#        formula <- as.formula(paste(col, "~ age + sex"))
#        lm(formula, data = all_out_0)
#    }
#)
#names(models_0) <- out_cols
#
#models_l <- lapply(
#    out_cols,
#    function(col) {
#        formula <- as.formula(paste(col, "~ age + sex"))
#        lm(formula, data = all_out_l)
#    }
#)
#names(models_l) <- out_cols

df0_w_covs <- df0 |>
    as.data.frame() |>
    dplyr::inner_join(all_sex_0) |>
    dplyr::inner_join(all_age_0)

dfl_w_covs <- dfl |>
    as.data.frame() |>
    dplyr::inner_join(all_sex_l) |>
    dplyr::inner_join(all_age_l)

df_w_covs <- rbind(df0_w_covs, dfl_w_covs)

df_w_covs$"t" <- as.numeric(df_w_covs$"t")

#df0_w_covs

#df0_w_covs_adj <- df0_w_covs
#dfl_w_covs_adj <- dfl_w_covs

#dfl_w_covs_adj |> head()
#
dfl_w_covs |> head()

#for (col in out_cols) {
#  # Predicted values based on reference model
#  predicted <- predict(models_0[[col]], newdata = df0_w_covs)
#  # Residuals: actual - predicted
#  df0_w_covs_adj[[paste0("adj_", col)]] <- df0_w_covs[[col]] - predicted
#}
#
#for (col in out_cols) {
#  # Predicted values based on reference model
#  predicted <- predict(models_l[[col]], newdata = dfl_w_covs)
#  # Residuals: actual - predicted
#  dfl_w_covs_adj[[paste0("adj_", col)]] <- dfl_w_covs[[col]] - predicted
#}

#for (col in out_cols) {
#  # Predicted values based on reference model
#  predicted <- predict(models_l[[col]], newdata = dfl_w_covs)
#  # Residuals: actual - predicted
#  dfl_w_covs_adj[[paste0("adj_", col)]] <- dfl_w_covs[[col]] - predicted
#}

#df_adj <- rbind(df0_w_covs_adj, dfl_w_covs_adj)

#saveRDS(df0_w_covs_adj, proc_path("df0_w_covs_adj.rds", TRUE))
#saveRDS(dfl_w_covs_adj, proc_path("dfl_w_covs_adj.rds", TRUE))

#saveRDS(df_adj, proc_path("df_adj.rds", TRUE))

# Storing the quantiles

#all_out_0_adj <- all_out_0
#all_out_l_adj <- all_out_l

#for (col in out_cols) {
#  # Predicted values based on reference model
#  predicted <- predict(models_0[[col]], newdata = all_out_0)
#  # Residuals: actual - predicted
#  all_out_0_adj[[paste0("adj_", col)]] <- all_out_0[[col]] - predicted
#}
#
#for (col in out_cols) {
#  # Predicted values based on reference model
#  predicted <- predict(models_l[[col]], newdata = all_out_l)
#  # Residuals: actual - predicted
#  all_out_l_adj[[paste0("adj_", col)]] <- all_out_l[[col]] - predicted
#}

all_out_adj <- all_out

for (col in out_cols) {
  # Predicted values based on reference model
  predicted <- predict(models[[col]], newdata = all_out)
  # Residuals: actual - predicted
  all_out_adj[[paste0("adj_", col)]] <- all_out[[col]] - predicted
}

# all out adj is residualized against age, sex, and timepoint
# enables quantile comparisons across timepoints as well
quantile(all_out_adj$"adj_sds_sleep", c(0, 0.33, 0.66, 1))

adj_df_w_covs <- df_w_covs

for (col in out_cols) {
  # Predicted values based on reference model
  predicted <- predict(models[[col]], newdata = df_w_covs)
  # Residuals: actual - predicted
  adj_df_w_covs[[paste0("adj_", col)]] <- df_w_covs[[col]] - predicted
}

# Reference adjusted data for quantiles
saveRDS(all_out_adj, proc_path("all_out_adj.rds", TRUE))

# Actual mTBI data
saveRDS(adj_df_w_covs, proc_path("df_w_covs_adj.rds", TRUE))
```

```{r}
all_out_adj <- readRDS(proc_path("2026_01_19_all_out_adj.rds"))
adj_df_w_covs <- readRDS(proc_path("2026_01_19_df_w_covs_adj.rds"))

all_out_adj |> colnames()


#df0_adj <- readRDS(proc_path("2025_07_08_df0_w_covs_adj.rds"))
#dfl_adj <- readRDS(proc_path("2025_07_08_dfl_w_covs_adj.rds"))
#
#df_adj <- readRDS(proc_path("2025_07_08_df_adj.rds"))

out_cols
#------------------------------------------------------------------------------
#library(dplyr)
library(purrr)

# 1. Vector of CBCL columns
cbcl_cols <- paste0("adj_", out_cols[1:8])
sds_cols <- "adj_sds_sleep"

quantile_cbcl <- map(
    cbcl_cols,
    function(col) {
        data <- all_out_adj[[col]]
        list(
            high = quantile(data, 0.93)
        )
    }
) |>
    set_names(cbcl_cols)

quantile_sds <- list(
    high = quantile(all_out_adj$"adj_sds_sleep", 0.75)
)

cbcl_bin_with_thresholds <- function(x, thresholds) {
  case_when(
    x >= thresholds$high ~ "high",
    x <  thresholds$high ~ "low",
    TRUE ~ NA_character_
  )
}

sds_bin_with_thresholds <- function(x, thresholds) {
  case_when(
    x >= thresholds$high ~ "high",
    x <  thresholds$high ~ "low",
    TRUE ~ NA_character_
  )
}

t0_data <- adj_df_w_covs |> dplyr::filter(t == 0)
t2_data <- adj_df_w_covs |> dplyr::filter(t == 2)

for (col in cbcl_cols) {
    new_col <- paste0(col, "_bin")
    t0_data[[paste0(new_col, "_t0")]] <- cbcl_bin_with_thresholds(
        t0_data[[col]],
        quantile_cbcl[[col]]
    )
    t2_data[[paste0(new_col, "_t2")]] <- cbcl_bin_with_thresholds(
        t2_data[[col]],
        quantile_cbcl[[col]]
    )
}
for (col in sds_cols) {
    new_col <- paste0(col, "_bin")
    t0_data[[paste0(new_col, "_t0")]] <- sds_bin_with_thresholds(
        t0_data[[col]],
        quantile_sds
    )
    t2_data[[paste0(new_col, "_t2")]] <- sds_bin_with_thresholds(
        t2_data[[col]],
        quantile_sds
    )
}

t0_bin_cols <- t0_data |> dplyr::select(uid, cluster, imputation, dplyr::ends_with("bin_t0"))
t2_bin_cols <- t2_data |> dplyr::select(uid, cluster, imputation, dplyr::ends_with("bin_t2"))

all_bin_df <- dplyr::full_join(
    t0_bin_cols,
    t2_bin_cols, by = c("uid", "cluster", "imputation")
)

cat_df <- all_bin_df |>
    dplyr::mutate(
        cbcl_anxdep_cat = paste0(adj_cbcl_anxdep_bin_t0, "_", adj_cbcl_anxdep_bin_t2),
        cbcl_withdep_cat = paste0(adj_cbcl_withdep_bin_t0, "_", adj_cbcl_withdep_bin_t2),
        cbcl_somatic_cat = paste0(adj_cbcl_somatic_bin_t0, "_", adj_cbcl_somatic_bin_t2),
        cbcl_social_cat = paste0(adj_cbcl_social_bin_t0, "_", adj_cbcl_social_bin_t2),
        cbcl_thought_cat = paste0(adj_cbcl_thought_bin_t0, "_", adj_cbcl_thought_bin_t2),
        cbcl_attention_cat = paste0(adj_cbcl_attention_bin_t0, "_", adj_cbcl_attention_bin_t2),
        cbcl_rulebreak_cat = paste0(adj_cbcl_rulebreak_bin_t0, "_", adj_cbcl_rulebreak_bin_t2),
        cbcl_aggressive_cat = paste0(adj_cbcl_aggressive_bin_t0, "_", adj_cbcl_aggressive_bin_t2),
        sds_sleep_cat = paste0(adj_sds_sleep_bin_t0, "_", adj_sds_sleep_bin_t2)
    ) |>
    dplyr::select(uid, cluster, imputation, dplyr::ends_with("cat"))

adj_df_cat_annotated <- dplyr::full_join(
    adj_df_w_covs,
    cat_df,
    by = c("uid", "cluster", "imputation")
)

saveRDS(
    adj_df_cat_annotated,
    proc_path("adj_df_cat_annotated.rds", TRUE)
)

adj_df_cat_annotated <- readRDS(proc_path("2026_01_19_adj_df_cat_annotated.rds"))

colnames(adj_df_cat_annotated)

adj_out_cols <- paste0("adj_", out_cols)

colnames(adj_df_cat_annotated)

out_cols

quantile_plot <- function(df, feature, ref_df, probs, mode = "high") {
    if (mode == "high") {
        vec <- c("high_high", "high_low")
        custom_scale <- scale_colour_manual(
            values = c("high_high" = "#5D3A9B", "high_low" = "#E66100"),
            labels = c("high_high" = "High to High", "high_low" = "High to Low")
        )
    } else {
        vec <- c("low_high", "low_low")
        custom_scale <- scale_colour_manual(
            values = c("low_high" = "#F8766D", "low_low" = "#00BFC4"),
            labels = c("low_high" = "Low to High", "low_low" = "Low to Low")
        )
    }
    pd <- position_dodge(width = 0.2)
    quantiles <- quantile(ref_df[[feature]], probs = probs)
    cat_name <- paste0(gsub("adj_", "", feature), "_cat")
    yvals <- as.numeric(quantiles)
    tidy_ft_name <- gsub("adj_", "", feature)
    tidy_ft_name <- gsub("cbcl_", "CBCL ", tidy_ft_name)
    tidy_ft_name <- gsub("anxdep", "Anxious/Depressed", tidy_ft_name)
    tidy_ft_name <- gsub("withdep", "Withdrawn/Depressed", tidy_ft_name)
    tidy_ft_name <- gsub("somatic", "Somatic ", tidy_ft_name)
    tidy_ft_name <- gsub("social", "Social Problems", tidy_ft_name)
    tidy_ft_name <- gsub("thought", "Thought Problems", tidy_ft_name)
    tidy_ft_name <- gsub("attention", "Attention Problems", tidy_ft_name)
    tidy_ft_name <- gsub("rulebreak", "Rule-Breaking Behavior", tidy_ft_name)
    tidy_ft_name <- gsub("aggressive", "Aggressive Behavior", tidy_ft_name)
    tidy_ft_name <- gsub("sds_sleep", "Sleep Disturbance", tidy_ft_name)
    # Data analysis 
    df |>
        dplyr::filter(imputation == 1) |>
        dplyr::filter(.data[[cat_name]] %in% vec) |>
        ggplot(
            aes(
                x = factor(t),
                y = .data[[feature]],
                group = uid,
                colour = .data[[cat_name]],
            ),
        ) +
        geom_point(size = 3, position = pd, alpha = 0.5) +
        geom_line(position = pd, alpha = 0.5) +
        geom_hline(
            yintercept = yvals,
            colour = "black"
        ) +
        labs(x = "Time", y = tidy_ft_name, colour = "Transition") + 
        facet_wrap(~ cluster) +
        theme_classic() + 
        custom_scale
}
```


```{r}
library(multcomp)

check_cat <- function(df, feature, imp) {
    cat_name <- paste0(gsub("adj_", "", feature), "_cat")
    df_low <- df |>
        dplyr::filter(
            imputation == imp,
            t == 0,
            .data[[cat_name]] %in% c("low_low", "low_high")
        ) |>
        dplyr::mutate(
            stayed_low = ifelse(.data[[cat_name]] == "low_low", 1, 0)
        )
    df_high <- df |>
        dplyr::filter(
            imputation == imp,
            t == 0,
            .data[[cat_name]] %in% c("high_low", "high_high")
        ) |>
        dplyr::mutate(
            stayed_high = ifelse(.data[[cat_name]] == "high_high", 1, 0)
        )
    glm_low <- glm(stayed_low ~ factor(cluster), data = df_low, family = "binomial")
    glm_high <- glm(stayed_high ~ factor(cluster), data = df_high, family = "binomial")
    p_stayed_low <- summary(glht(glm_low, linfct = mcp(`factor(cluster)` = "Tukey")), test = adjusted("none"))$"test"$"pvalues"
    p_stayed_high <- summary(glht(glm_high, linfct = mcp(`factor(cluster)` = "Tukey")), test = adjusted("none"))$"test"$"pvalues"
    low_p_df <- dplyr::rename(as.data.frame(p_stayed_low), "p" = "p_stayed_low")
    low_p_df$"comparison" <- rownames(low_p_df)
    low_p_df$"type" <- "stayed_low"
    low_p_df$"feature" <- gsub("adj_", "", feature)
    rownames(low_p_df) <- NULL
    high_p_df <- dplyr::rename(as.data.frame(p_stayed_high), "p" = "p_stayed_high")
    high_p_df$"comparison" <- rownames(high_p_df)
    high_p_df$"type" <- "stayed_high"
    high_p_df$"feature" <- gsub("adj_", "", feature)
    rownames(high_p_df) <- NULL
    p_df <- rbind(low_p_df, high_p_df)
    stayed_low_plot <- df_low |>
        count(cluster, .data[[cat_name]]) |>
        group_by(cluster) |>
        mutate(prop = n / sum(n)) |>
        ggplot(aes(x = cluster, y = prop, fill = .data[[cat_name]])) +
        geom_col(position = "fill") +  # stacked proportion bars
        theme_classic() +
        labs(y = "Proportion", x = "Cluster", fill = "Transition") +
        scale_fill_manual(
            values = c("low_high" = "#F8766D", "low_low" = "#00BFC4"),
            labels = c("low_high" = "Low to High", "low_low" = "Low to Low")
        )
    stayed_high_plot <- df_high |>
        count(cluster, .data[[cat_name]]) |>
        group_by(cluster) |>
        mutate(prop = n / sum(n)) |>
        ggplot(aes(x = cluster, y = prop, fill = .data[[cat_name]])) +
        geom_col(position = "fill") +  # stacked proportion bars
        theme_classic() +
        labs(y = "Proportion", x = "Cluster", fill = "Transition") +
        scale_fill_manual(
            values = c("high_high" = "#5D3A9B", "high_low" = "#E66100"),
            labels = c("high_high" = "High to High", "high_low" = "High to Low")
        )
    return(list(stayed_low_plot, stayed_high_plot, p_df))
}

p_df <- data.frame()
pl <- list()
for (x in 1:9) {
    prop <- check_cat(adj_df_cat_annotated, adj_out_cols[[x]], 1)
    p_df <- rbind(p_df, dplyr::mutate(prop[[3]], x = x))
    thresh <- if (x < 9) (0.93) else (0.75)
    low <- quantile_plot(adj_df_cat_annotated, adj_out_cols[[x]], all_out_adj, thresh, "low")
    high <- quantile_plot(adj_df_cat_annotated, adj_out_cols[[x]], all_out_adj, thresh, "high")
    pl[[x]] <- wrap_plots(list(low, high, prop[[1]], prop[[2]]))
    print(adj_out_cols[[x]])
    ggsave(
        plot = pl[[x]],
        filename = fig_path(
            paste0(
                gsub("adj_", "", adj_out_cols[[x]]),
                "_transition_plot.png"
            ),
            TRUE
        ),
        width = 7,
        height = 4,
        dpi = 150
    )
}
p_df$"p_adj" <- p.adjust(p_df$p, method = "fdr")

p_df |>
    dplyr::arrange(p)

saveRDS(p_df, proc_path("outcome_transition_pvals.rds", TRUE))
saveRDS(pl, proc_path("outcome_transition_plots.rds", TRUE))

p_df <- readRDS(proc_path("2026_01_19_outcome_transition_pvals.rds"))
pl <- readRDS(proc_path("2026_01_19_outcome_transition_plots.rds"))

pl[[1]]

# "Diagnostic accuracy (AUC = 0.9 1) and that the cut-off score
# with the best diagnostic confidence, as determined by the
# intersect point of sensitivity and specificity, was 39 (which
# corresponded to the upper quartile of the control group's SDSC
# total score); this cut-off point gave a sensitivity of 0.89 and a
# specificity of 0.74. This score correctly identified 73.4% of th" - bruni
```


# Longitudinal trajectory check 2

Checking again, but now rather than high-high/high-low, examining if there is differences in high that went down vs. high that stayed same or went up.

```{r}
adj_df_cat_annotated <- readRDS(proc_path("2026_01_19_adj_df_cat_annotated.rds"))
t0_df <- adj_df_cat_annotated |>
    dplyr::filter(t == 0)
t2_df <- adj_df_cat_annotated |>
    dplyr::filter(t == 2)
colnames(t0_df) <- paste0(colnames(t0_df), "_t0")
colnames(t2_df) <- paste0(colnames(t2_df), "_t2")
t0_df <- dplyr::rename(t0_df, "uid" = "uid_t0", "imputation" = "imputation_t0")
t2_df <- dplyr::rename(t2_df, "uid" = "uid_t2", "imputation" = "imputation_t2")

merged_df <- dplyr::inner_join(t0_df, t2_df, by = c("uid", "imputation"))

outcome_fts <- c(
    "cbcl_anxdep",
    "cbcl_withdep",
    "cbcl_somatic",
    "cbcl_social",
    "cbcl_thought",
    "cbcl_attention",
    "cbcl_rulebreak",
    "cbcl_aggressive",
    "sds_sleep"
)

library(ggplot2)
library(multcomp)
library(patchwork)

pretty_features <- c(
    "cbcl_anxdep"     = "CBCL Anxious-Depressed",
    "cbcl_withdep"    = "CBCL Withdrawn-Depressed",
    "cbcl_somatic"    = "CBCL Somatic",
    "cbcl_social"     = "CBCL Social",
    "cbcl_thought"    = "CBCL Thought",
    "cbcl_attention"  = "CBCL Attention",
    "cbcl_rulebreak"  = "CBCL Rule-breaking",
    "cbcl_aggressive" = "CBCL Aggressive",
    "sds_sleep"       = "SDS Sleep"
)

calc_fisher_p <- function(df, f1, f2) {
    tab <- table(df[, f1], df[, f2])
    result <- tryCatch(
        {
            fisher.test(tab)$"p.value"
        }, error = function(e) {
            999
        }
    )
    return(result)
}

plot_change <- function(df, feature, sex_pval_df, mode = "high") {
    # formatting feature names
    pretty_feature <- gsub("cbcl_", "CBCL ", feature)
    category_name <- paste0(feature, "_cat_t0")
    name_t0 <- paste0("adj_", feature, "_t0")
    name_t2 <- paste0("adj_", feature, "_t2")
    name <- paste0("adj_", feature)
    # identifying rows that went maintained a high level or improved
    if (mode == "high") {
        df_labeled <- df |>
            dplyr::filter(
                .data[[category_name]] %in% c("high_high", "high_low")
            ) |>
            dplyr::mutate(
                diff_cat = dplyr::case_when(
                    .data[[name_t2]] < .data[[name_t0]] ~ "improved",
                    TRUE ~ "not_improved"
                )
            ) |>
            dplyr::select(
                uid,
                diff_cat,
                dplyr::contains(c("cluster", "imputation", "t", feature))
            )
    } else if (mode == "low") {
        df_labeled <- df |>
            dplyr::filter(
                .data[[category_name]] %in% c("low_low", "low_high")
            ) |>
            dplyr::mutate(
                diff_cat = dplyr::case_when(
                    .data[[name_t2]] > .data[[name_t0]] ~ "worsened",
                    TRUE ~ "not_worsened"
                )
            ) |>
            dplyr::select(
                uid,
                diff_cat,
                dplyr::contains(c("cluster", "imputation", "t", feature))
            )
    }
    df_0 <- df_labeled |>
        dplyr::select(
            uid,
            imputation,
            diff_cat,
            dplyr::ends_with("_t0")
        )
    df_2 <- df_labeled |>
        dplyr::select(
            uid,
            imputation,
            diff_cat,
            dplyr::ends_with("_t2")
        )
    colnames(df_0) <- gsub("_t0$", "", colnames(df_0))
    colnames(df_2) <- gsub("_t2$", "", colnames(df_2))
    stacked_df <- rbind(df_0, df_2)
    pd <- position_dodge(width = 0.2)
    if (mode == "high") {
        stacked_df_analysis <- stacked_df |>
            dplyr::filter(t == 0) |>
            dplyr::mutate(
                diff_cat_bin = dplyr::case_when(
                    diff_cat == "improved" ~ 1,
                    diff_cat == "not_improved" ~ 0
                )
            )
    } else if (mode == "low") {
        stacked_df_analysis <- stacked_df |>
            dplyr::filter(t == 0) |>
            dplyr::mutate(
                diff_cat_bin = dplyr::case_when(
                    diff_cat == "worsened" ~ 1,
                    diff_cat == "not_worsened" ~ 0
                )
            )
    }
    fisher_p_value <- calc_fisher_p(stacked_df_analysis, "diff_cat_bin", "cluster")
    #------------------------------------------------------------------------------
    # side analysis examining sex
    stacked_df_analysis1  <- stacked_df_analysis |> filter(cluster == 1)
    stacked_df_analysis2  <- stacked_df_analysis |> filter(cluster == 2)
    stacked_df_analysis3  <- stacked_df_analysis |> filter(cluster == 3)
    stacked_df_analysism  <- stacked_df_analysis |> filter(sex == "M")
    stacked_df_analysisf  <- stacked_df_analysis |> filter(sex == "F")
    stacked_df_analysis1m <- stacked_df_analysis |> filter(cluster == 1, sex == "M")
    stacked_df_analysis2m <- stacked_df_analysis |> filter(cluster == 2, sex == "M")
    stacked_df_analysis3m <- stacked_df_analysis |> filter(cluster == 3, sex == "M")
    stacked_df_analysis1f <- stacked_df_analysis |> filter(cluster == 1, sex == "F")
    stacked_df_analysis2f <- stacked_df_analysis |> filter(cluster == 2, sex == "F")
    stacked_df_analysis3f <- stacked_df_analysis |> filter(cluster == 3, sex == "F")
    cor <- calc_propes_wp(
        stacked_df_analysism$"diff_cat_bin",
        stacked_df_analysisf$"diff_cat_bin"
    )
    c1or <- calc_propes_wp(
        stacked_df_analysis1m$"diff_cat_bin",
        stacked_df_analysis1f$"diff_cat_bin"
    )
    c2or <- calc_propes_wp(
        stacked_df_analysis2m$"diff_cat_bin",
        stacked_df_analysis2f$"diff_cat_bin"
    )
    c3or <- calc_propes_wp(
        stacked_df_analysis3m$"diff_cat_bin",
        stacked_df_analysis3f$"diff_cat_bin"
    )
    sex_p <-  calc_fisher_p(stacked_df_analysis, "diff_cat_bin", "sex")
    sex_p1 <- calc_fisher_p(stacked_df_analysis1, "diff_cat_bin", "sex")
    sex_p2 <- calc_fisher_p(stacked_df_analysis2, "diff_cat_bin", "sex")
    sex_p3 <- calc_fisher_p(stacked_df_analysis3, "diff_cat_bin", "sex")
    sex_pval_df <- rbind(
        sex_pval_df,
        data.frame(
            feature = c(feature, feature, feature, feature),
            group = c("all", "1", "2", "3"),
            or = c(cor$"es", c1or$"es", c2or$"es", c3or$"es"),
            l = c(cor$"l", c1or$"l", c2or$"l", c3or$"l"),
            u = c(cor$"u", c1or$"u", c2or$"u", c3or$"u"),
            p_fisher = c(sex_p, sex_p1, sex_p2, sex_p3),
            m_mean = c(
                mean(stacked_df_analysism$"diff_cat_bin"),
                mean(stacked_df_analysis1m$"diff_cat_bin"),
                mean(stacked_df_analysis2m$"diff_cat_bin"),
                mean(stacked_df_analysis3m$"diff_cat_bin")
            ),
            f_mean = c(
                mean(stacked_df_analysisf$"diff_cat_bin"),
                mean(stacked_df_analysis1f$"diff_cat_bin"),
                mean(stacked_df_analysis2f$"diff_cat_bin"),
                mean(stacked_df_analysis3f$"diff_cat_bin")
            )
        )
    )
    #------------------------------------------------------------------------------
    # analyses checking if the clusters significantly differed
    df_12 <- stacked_df_analysis |> dplyr::filter(cluster != 3)
    df_13 <- stacked_df_analysis |> dplyr::filter(cluster != 2)
    df_23 <- stacked_df_analysis |> dplyr::filter(cluster != 1)
    ft_12 <- fisher.test(table(df_12$"diff_cat_bin", as.factor(as.character(df_12$"cluster"))))
    ft_13 <- fisher.test(table(df_13$"diff_cat_bin", as.factor(as.character(df_13$"cluster"))))
    ft_23 <- fisher.test(table(df_23$"diff_cat_bin", as.factor(as.character(df_23$"cluster"))))
    pairwise_df <- data.frame(
        comparison = c("12", "13", "23"),
        p = c(ft_12$p.value, ft_13$p.value, ft_23$p.value),
        estimate = c(ft_12$estimate, ft_13$estimate, ft_23$estimate),
        conf_int_low = c(ft_12$conf.int[1], ft_13$conf.int[1], ft_23$conf.int[1]),
        conf_int_high = c(ft_12$conf.int[2], ft_13$conf.int[2], ft_23$conf.int[2]),
        feature = feature
    )
    p_df <- data.frame(
        p_fisher = fisher_p_value,
        feature = feature
    )
    if (mode == "high") {
        vals <- c("improved" = "darkgreen", "not_improved" = "firebrick")
        labs <- c("improved" = "Improved", "not_improved" = "Not Improved")
    } else if (mode == "low") {
        vals = c("not_worsened" = "darkgreen", "worsened" = "firebrick")
        labs = c("not_worsened" = "Improved", "worsened" = "Not Improved")
    }
    point_plot <- stacked_df |>
        dplyr::filter(imputation == 1) |>
        ggplot(
            aes(
                x = factor(t),
                y = .data[[name]],
                group = uid,
                colour = diff_cat
            )
        ) +
        geom_point(size = 3, position = pd, alpha = 0.5) +
        geom_line(position = pd, alpha = 0.5) +
        facet_wrap(~ cluster) +
        theme_bw() +
        scale_colour_manual(
            values = vals,
            labels = labs
        ) +
        labs(colour = "Transition", title = pretty_features[[feature]], x = "Time point", y = NULL)
    prop_plot <- stacked_df |>
        count(cluster, diff_cat) |>
        group_by(cluster) |>
        mutate(prop = n / sum(n)) |>
        ggplot(aes(x = cluster, y = prop, fill = diff_cat)) +
        geom_col(position = "fill") +  # stacked proportion bars
        theme_classic() + 
        labs(y = "Proportion", x = "Cluster", fill = "Transition") +
        scale_fill_manual(
            values = vals,
            labels = labs
        )
    return(
        list(point_plot,  prop_plot, p_df, pairwise_df, sex_pval_df)
    )
}

#sex_pval_df <- data.frame()
#p_df <- data.frame()
#pairwise_df <- data.frame()
#pl <- list()
#pl_2 <- list()
#for (i in 1:9) {
#    print(i)
#    high_change_results <- plot_change(merged_df, outcome_fts[[i]], sex_pval_df, mode = "high")
#    pl[[i]]   <- high_change_results[[1]]
#    pl_2[[i]] <- high_change_results[[2]]
#    p_df <- rbind(p_df, high_change_results[[3]])
#    pairwise_df <- rbind(pairwise_df, high_change_results[[4]])
#    sex_pval_df <- high_change_results[[5]]
#}

all_change_plots <- function(mode = "high") {
    sex_p_df <- data.frame()
    overall_p_df <- data.frame()
    pairwise_p_df <- data.frame()
    pl_pnt <- list()
    pl_bar <- list()
    for (i in 1:9) {
        print(i)
        change_results <- plot_change(merged_df, outcome_fts[[i]], sex_p_df, mode = mode)
        pl_pnt[[i]]   <- change_results[[1]]
        pl_bar[[i]] <- change_results[[2]]
        overall_p_df <- rbind(overall_p_df, change_results[[3]])
        pairwise_p_df <- rbind(pairwise_p_df, change_results[[4]])
        sex_p_df <- change_results[[5]]
    }
    sex_p_df$"p_adj" <- p.adjust(sex_p_df$"p_fisher", method = "fdr")

In the high_data group, a higher mean indicates higher proportion improved.
In the low_data group, a higher mean indicates higher proportion worsened.
    if (mode == "high") {
        sex_p_df <- sex_p_df |>
            dplyr::mutate()
    }
    return(
        list(
            "pl_pnt" = pl_pnt,
            "pl_bar" = pl_bar,
            "overall_p_df" = overall_p_df,
            "pairwise_p_df" = pairwise_p_df,
            "sex_p_df" = sex_p_df
        )
    )
}

high_data <- all_change_plots(mode = "high")

low_data <- all_change_plots(mode = "low")

options(width = 200)

# those who started high and became normal
high_data$"sex_p_df" |> dplyr::filter(p_adj < 0.05)

# those who started normal and became high
low_data$"sex_p_df" |> dplyr::filter(p_adj < 0.05)

stacked_df_analysis

nrow(stacked_df)


```

In the high_data group, a higher mean indicates higher proportion improved.
In the low_data group, a higher mean indicates higher proportion worsened.


separate sex analysis:

```{r}
sex_pval_df$"p_fisher_adj" <- p.adjust(sex_pval_df$"p_fisher", method = "fdr")
sex_pval_df <- sex_pval_df |>
    dplyr::mutate(
        better = dplyr::case_when(
            m_mean > f_mean ~ "M",
            f_mean > m_mean ~ "F",
            TRUE ~ NA
        )
    )
sex_pval_df |>
    dplyr::filter(p_fisher_adj < 0.05) |>
    nrow()


sex_pval_df |>
    dplyr::filter(p_fisher_adj < 0.05) |>
    dplyr::select(-p_fisher) |>
    dplyr::rename("p" = "p_fisher_adj") |>
    arrange(better) |>
    print(digits = 3)

```

*F better*:

2 cbcl_attention   all    0.426  0.2256 8.05e-01  0.694  0.842 3.86e-02      F
7   cbcl_thought   all    2.833  1.4266 5.63e+00  0.919  0.800 2.17e-02      M

         feature group       or       l        u m_mean f_mean        p better
1   cbcl_somatic     1    0.225  0.0780 6.49e-01  0.474  0.800 2.17e-02      F
3 cbcl_attention     3    0.100  0.0281 3.56e-01  0.333  0.833 5.55e-03      F
4      sds_sleep     3    0.287  0.1276 6.47e-01  0.333  0.635 2.17e-02      F

*M better:*

         feature group       or       l        u m_mean f_mean        p better
6   cbcl_somatic     2 1441.000 25.9911 7.99e+04  1.000  0.000 2.97e-06      M
8 cbcl_rulebreak     2   41.000  1.9530 8.61e+02  0.800  0.000 2.12e-02      M
5    cbcl_anxdep     3   14.830  0.8649 2.54e+02  1.000  0.737 3.24e-02      M

The means in those tables correspond to improvement.

Groups with higher mean scores had a higher proportion of children who improved out of that category.


Another check examining low-low to low-high

```{r}
sex_pval_df <- data.frame()
p_df <- data.frame()
pairwise_df <- data.frame()
pl <- list()
pl_2 <- list()
for (i in 1:9) {
    high_change_results <- plot_change(merged_df, outcome_fts[[i]], sex_pval_df, mode = "low")
    pl[[i]] <- high_change_results[[1]]
    pl_2[[i]] <- high_change_results[[2]]
    p_df <- rbind(p_df, high_change_results[[3]])
    pairwise_df <- rbind(pairwise_df, high_change_results[[4]])
    sex_pval_df <- high_change_results[[5]]
}
print(sex_pval_df)
```

separate sex analysis:

```{r}
sex_pval_df$"p_fisher_adj" <- p.adjust(sex_pval_df$"p_fisher", method = "fdr")
sex_pval_df <- sex_pval_df |>
    dplyr::mutate(
        better = dplyr::case_when(
            m_mean > f_mean ~ "F",
            f_mean > m_mean ~ "M",
            TRUE ~ NA
        )
    )
sex_pval_df |>
    dplyr::filter(p_fisher_adj < 0.05) |>
    dplyr::select(-p_fisher) |>
    dplyr::rename("p" = "p_fisher_adj") |>
    arrange(better) |>
    print(digits = 3)
```



```{r}
names(pl) <- outcome_fts
names(pl_2) <- outcome_fts
p_df$"p_fisher_adj" <- p.adjust(p_df$"p_fisher", method = "fdr")

p_df

pl_annotated <- lapply(
    1:9,
    function(i) {
        pl_2[[i]] +
            annotate(
                "text",
                x = 2,
                y = 1.13,
                label = paste0(
                    "\nFDR Fisher p: ", signif(p_df$"p_fisher_adj"[[i]], 3)
                ),
                colour = "black",
                size = 3
            ) +
             coord_cartesian(ylim = c(0, 1.2))
    }
)

p_df |>
    dplyr::arrange(p_fisher_adj) |>
    dplyr::rename("Adjusted p-value" = "p_fisher_adj", "Feature" = "feature") |>
    dplyr::select(-p_fisher) |>
    knitr::kable(format = "markdown", digits = 6)

sig_fts <- p_df |>
    dplyr::filter(p_fisher_adj < 0.05) |>
    dplyr::pull(feature) |>

pairwise_df_sig <- pairwise_df |>
    dplyr::filter(feature %in% sig_fts)

pairwise_df_sig$"p_adj" <- p.adjust(pairwise_df_sig$p, method = "fdr")

pairwise_df_sig |>
    dplyr::mutate(es = paste0(
        round(estimate, 2),
        " [", round(conf_int_low, 2), ", ", round(conf_int_high, 2), "]"
    )) |>
    dplyr::select(comparison, feature, p_adj, es) |>
    dplyr::arrange(comparison, p_adj) |>
    dplyr::rename(
        "Comparison" = "comparison",
        "Feature" = "feature",
        "Adjusted p-value" = "p_adj",
        "Effect size (95% CI)" = "es"
    ) |>
    dplyr::mutate(
        Comparison = gsub("12", "1 vs 2", Comparison),
        Comparison = gsub("13", "1 vs 3", Comparison),
        Comparison = gsub("23", "2 vs 3", Comparison)
    ) |>
    knitr::kable(format = "markdown", digits = 5)

sig_plots <- lapply(
    c("cbcl_thought", "cbcl_somatic"),
    function(x) {
        (pl[[x]] | pl_2[[x]]) + plot_layout(widths = c(2, 1))
    }
)

my_sig <- function(comparisons, annotations, y_position) {
    geom_signif(
        comparisons = comparisons,
        annotations = annotations,
        y_position = y_position,
        textsize = 5,
        tip_length = 0,
        vjust = 0.3
    )
}

annotations <- list(
    "thought"   = my_sig(list(c("1", "2"), c("2", "3")), c("***", "***"), c(1.02, 1.16)),
    "somatic"   = my_sig(list(c("1", "2"), c("2", "3")), c("***", "***"), c(1.02, 1.16))
)
sig_plots2 <- lapply(
    seq_along(annotations),
    function(x) {
        if (x != 3) {
            sig_plots[[x]][[2]] <- sig_plots[[x]][[2]] + theme(legend.position = "none")
            sig_plots[[x]][[2]] <- sig_plots[[x]][[2]] + labs(y = NULL)
        }
        sig_plots[[x]][[1]] <- sig_plots[[x]][[1]] + theme(legend.position = "none")
        sig_plots[[x]][[1]] <- sig_plots[[x]][[1]] + labs(y = "Adjusted Score")
        sig_plots[[x]][[2]] <- sig_plots[[x]][[2]] +
            annotations[[x]] +
            coord_cartesian(ylim = c(0, 1.35)) +
            scale_y_continuous(breaks = seq(0, 1, by = 0.25))
        sig_plots[[x]]
    }
)

change_plot <- wrap_plots(sig_plots2, ncol = 1)

change_plot

ggsave(
    filename = fig_path("high_change_plot_clean2.png", TRUE),
    plot = change_plot,
    height = 5,
    width = 6
)
```

|Feature         | Adjusted p-value|
|:---------------|----------------:|
|cbcl_somatic    |         0.000000|
|cbcl_thought    |         0.000036|
|cbcl_withdep    |         0.091976|
|sds_sleep       |         0.091976|
|cbcl_social     |         0.336959|
|cbcl_anxdep     |         0.456565|
|cbcl_aggressive |         0.640358|
|cbcl_attention  |         0.782927|
|cbcl_rulebreak  |         0.782927|

Question: where there worse outcomes for girls or boys?

```{r}
"sex_t0" %in% colnames(merged_df)

merged_df |>

check_prop_high <- function(df, feature) {
    category_name <- paste0(feature, "_cat_t0")
    name_t0 <- paste0("adj_", feature, "_t0")
    name_t2 <- paste0("adj_", feature, "_t2")
    df_labeled <- df |>
        dplyr::filter(
            .data[[category_name]] %in% c("high_high", "high_low")
        ) |>
        dplyr::mutate(
            diff_improved = dplyr::case_when(
                .data[[name_t2]] < .data[[name_t0]] ~ 1,
                TRUE ~ 0
            )
        )
    df_labeled
}

z <- check_prop_high(merged_df, "cbcl_anxdep")

zm <- z |> dplyr::filter(sex_t0 == "M")
zf <- z |> dplyr::filter(sex_t0 == "F")



```


```{r}
pl$"cbcl_somatic"
pl_2$"cbcl_thought"
#
#pl <- readRDS(fig_path("2025_07_14_high_change_figs_pl.rds"))
#p_df <- readRDS(proc_path("2025_07_14_high_change_p_df.rds"))
#
#ggsave(
#    filename = fig_path("high_change_plot.png", TRUE),
#    wrap_plots(pl),
#    width = 20,
#    height = 7
#)
#
#p_df |>
#    knitr::kable(format = "markdown", digits = 5)
```

## Q2. Did the matched uninjured subjects experience more mTBIs by T2 than the other uninjured subjects?

(Old analysis - not yet re-run)

```{r}
matched_unij_nearest_esdf <- readRDS(proc_path("2025_02_16_matched_unij_nearest_esdf.rds"))

# Those who exhibited heterogeneity most similar to the baseline mTBI group
matched_subs <- uids(matched_unij_nearest_esdf)
matched_subs <- gsub("uid_", "", matched_subs)

# Those who never sustained a head injury prior to T2
# N = 7678
long_unij_subs <- read_subjects(sub_path("2025_02_07_unij_subs_0_to_2.csv"))

# Those who sustained a head injury between 0 and T2
# N = 220
long_mtbi_subs <- read_subjects(sub_path("2025_02_07_mtbi_subs_0_to_2.csv"))

# The pool of all baseline uninjured subjects
# N = 9349
base_unij_subs <- read_subjects(sub_path("2025_02_07_unij_subs.csv"))

non_matched_subs <- setdiff(base_unij_subs, matched_subs)

base_mtbi_subs <- read_subjects(sub_path("2025_02_07_mtbi_subs.csv"))
```

Let's consider being in the matched group vs. not being in the matched group as exposed vs. unexposed, and ending up in the mTBI sample as outcome vs. no outcome.
Then I calculate the odds ratio and 95% CI of being in the mTBI sample based on being in the matched group.

```{r}
# Calculation 1: Explicitly looking for people that ended up in mTBI sample
matched_that_became_mtbi <- sum(matched_subs %in% long_mtbi_subs)
unmatched_that_became_mtbi <- sum(non_matched_subs %in% long_mtbi_subs)
matched_that_remained_unij <- sum(!matched_subs %in% long_mtbi_subs)
unmatched_that_remained_unij <- sum(!non_matched_subs %in% long_mtbi_subs)

odds_ratio <- function(de, he, dn, hn) {
    numerator <- de / he
    denominator <- dn / hn
    or <- numerator / denominator
    se_log_or <- sqrt(1/de + 1/he + 1/dn + 1/hn)
    log_or <- log(or)
    ci_lower <- exp(log_or - 1.96 * se_log_or)
    ci_upper <- exp(log_or + 1.96 * se_log_or)
    return(list(
        or = or,
        ci_lower = ci_lower,
        ci_upper = ci_upper
    ))
}

# (D)isease = mTBI, (H)ealthy = unij , (E)xposure = match
# 0.83 [0.36, 1.89]
odds_ratio(
    de = matched_that_became_mtbi,
    he = matched_that_remained_unij,
    dn = unmatched_that_became_mtbi,
    hn = unmatched_that_remained_unij
)
```

No significant difference in the proportion of matched uninjured subjects to unmatched uninjured subjects that ended up in the longitudinal mTBI group (1.3% vs. 1.6%, uncorrected Chi-squared test p-value = 0.6565).

### Extra: Correlations with membership in longitudinal mTBI sample

Now I'll double check to see if there were any attributes of subjects that were particularly closely associated with membership in the longitudinal mTBI sample.

```{r}
long_mtbi_0_dl <- all_long_dls$"long_mtbi_0_dls"[[1]]

base_unij_0_dl <- all_dls$"unij_pooled_data_lists"[[1]]

long_unij_0_dl <- base_unij_0_dl |>
    dlapply(
        function(x) {
            x$"data" <- dplyr::filter(x$"data", uid %in% paste0("uid_", long_unij_subs))
            return(x)
        }
    )

long_unij_df <- as.data.frame(long_unij_0_dl)
long_mtbi_df <- as.data.frame(long_mtbi_0_dl)
base_unij_df <- as.data.frame(base_unij_0_dl)

long_unij_df$"mtbi" <- 0
long_mtbi_df$"mtbi" <- 1

long_corr_df <- rbind(long_unij_df, long_mtbi_df)

saveRDS(long_corr_df, proc_path("long_corr_df.rds", TRUE))

long_corr_df <- readRDS(proc_path("2025_05_01_long_corr_df.rds"))

# Correlation matrix examining how correlated each feature is with being assigned to mTBI group
prepped_long_corr_df <- long_corr_df |>
    dplyr::select(-uid) |>
    dummy_cols(
        select_columns = "race",
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = TRUE
    )

# Setup parallel plan
future::plan("multisession")
kendall_row <- function(i, data) {
  sapply(i:ncol(data), function(j) cor(data[[i]], data[[j]], method = "kendall"))
}
n <- ncol(prepped_long_corr_df)
kendall_mat <- matrix(NA, n, n)
colnames(kendall_mat) <- rownames(kendall_mat) <- colnames(prepped_long_corr_df)
results <- pbapply::pblapply(1:n, function(i) kendall_row(i, prepped_long_corr_df), cl = future::availableCores())
for (i in 1:n) {
  kendall_mat[i, i:n] <- results[[i]]
  kendall_mat[i:n, i] <- results[[i]]
}

saveRDS(kendall_mat, proc_path("long_corr_mat_kendall.rds", TRUE))

# Setup parallel plan
spearman_row <- function(i, data) {
    sapply(i:ncol(data), function(j) cor(data[[i]], data[[j]], method = "spearman"))
}
n <- ncol(prepped_long_corr_df)
spearman_mat <- matrix(NA, n, n)
colnames(spearman_mat) <- rownames(spearman_mat) <- colnames(prepped_long_corr_df)
results <- pbapply::pblapply(1:n, function(i) spearman_row(i, prepped_long_corr_df), cl = future::availableCores())
for (i in 1:n) {
  spearman_mat[i, i:n] <- results[[i]]
  spearman_mat[i:n, i] <- results[[i]]
}

saveRDS(spearman_mat, proc_path("long_corr_mat_spearman.rds", TRUE))

pearson_mat <- cor(prepped_long_corr_df, method = "pearson")

saveRDS(pearson_mat, proc_path("long_corr_mat_pearson.rds", TRUE))
```

```{r}
kendall_mat <- readRDS(proc_path("2025_05_01_long_corr_mat_kendall.rds"))
spearman_mat <- readRDS(proc_path("2025_05_01_long_corr_mat_spearman.rds"))
pearson_mat <- readRDS(proc_path("2025_05_01_long_corr_mat_pearson.rds"))

kendall_mat[setdiff(rownames(kendall_mat), "mtbi"), "mtbi"]
spearman_mat[setdiff(rownames(spearman_mat), "mtbi"), "mtbi"]
pearson_mat[setdiff(rownames(pearson_mat), "mtbi"), "mtbi"]

ComplexHeatmap::Heatmap(kendall_mat[setdiff(rownames(kendall_mat), "mtbi"), "mtbi"])

ComplexHeatmap::Heatmap(spearman_mat[setdiff(rownames(spearman_mat), "mtbi"), "mtbi"])

ComplexHeatmap::Heatmap(pearson_mat[setdiff(rownames(pearson_mat), "mtbi"), "mtbi"])

kendall_mat[names(sort(-abs(kendall_mat[setdiff(rownames(kendall_mat), "mtbi"), "mtbi"]))), "mtbi"] |> ComplexHeatmap::Heatmap(cluster_rows = FALSE)


spearman_mat[names(sort(-abs(spearman_mat[setdiff(rownames(spearman_mat), "mtbi"), "mtbi"]))), "mtbi"] |> ComplexHeatmap::Heatmap(cluster_rows = FALSE)

pearson_mat[names(sort(-abs(pearson_mat[setdiff(rownames(pearson_mat), "mtbi"), "mtbi"]))), "mtbi"] |> ComplexHeatmap::Heatmap(cluster_rows = FALSE)

ComplexHeatmap::Heatmap(z3)

z3 <- long_corr_df |>
    dplyr::select(-uid) |>
    dummy_cols(
        select_columns = "race",
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = TRUE
    ) |>
    cor(method = "kendll")

# Only looking at correlations
mtbi_corr_mat <- long_corr_mat[rownames(long_corr_mat) != "mtbi", "mtbi", drop = FALSE]

mtbi_corr_mat |>
    ComplexHeatmap::Heatmap()

mtbi_corr_mat |>
    as.data.frame() |>
    dplyr::arrange(mtbi)

long_corr_df |>
    ggplot(aes(x = factor(mtbi), y = major_wm_ndi)) +
    geom_jitter() +
    theme_bw()


long_corr_clean_df <- long_corr_df |>
    dplyr::select(-uid) |>
    dummy_cols(
        select_columns = "race",
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = TRUE
    )

pvalue_df <- data.frame()
for (col in colnames(long_corr_clean_df)) {
    test_results <- cor.test(long_corr_clean_df$"mtbi", long_corr_clean_df[[col]])
    pval <- test_results$"p.value"
    est <- test_results$"estimate"
    l <- test_results$"conf.int"[1]
    u <- test_results$"conf.int"[2]
    pvalue_df <- rbind(
        pvalue_df,
        data.frame(
            feature = col,
            pval = pval,
            est = est,
            l = l,
            u = u
        )
    )
}
rownames(pvalue_df) <- NULL
p_values_bonferroni <- p.adjust(pvalue_df$"pval", method = "bonferroni")
p_values_fdr <- p.adjust(pvalue_df$"pval", method = "fdr")
pvalue_df$"pval_bon" <- p_values_bonferroni
pvalue_df$"pval_fdr" <- p_values_fdr
pvalue_df <- pvalue_df |>
    dplyr::arrange(pval) |>
    dplyr::filter(feature != "mtbi") |>
    dplyr::select(feature, pval, pval_bon, pval_fdr, est, l, u)

write_csv(pvalue_df, proc_path("pvalue_df.csv", TRUE))
pvalue_df <- read_csv(proc_path("2025_02_16_pvalue_df.csv"))
```

Quite a few features there that remain significant even after bonferroni correction.
There certainly seem to be factors that increase a child's risk of sustaining an mTBI.
These are all taken from the same data collection period as well!


## Q3. Clustering of the longitudinal sample with their baseline vs. their longitudinal data: both equally informative? 

```{r}
lmtb_0_dls <- all_long_dls_h_ns$"lmtb_0_dls"
lmtb_0_ols <- all_long_dls_h_ns$"lmtb_0_ols"
lmtb_l_dls <- all_long_dls_h_ns$"lmtb_l_dls"
lmtb_l_ols <- all_long_dls_h_ns$"lmtb_l_ols"
```

```{r}
lmtb_config <- snf_config(
    lmtb_0_dls[[1]],
    n_solutions = 200,
    cnt_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    dsc_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ord_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    use_default_dist_fns = TRUE
)

saveRDS(lmtb_config, proc_path("lmtb_config.rds", TRUE))
```


```{r}
# CHECKPOINT
lmtb_config <- readRDS(proc_path("2025_10_01_lmtb_config.rds"))
```


```{r}
lmtb_0_sol_df_u1 <- batch_snf(dl = lmtb_0_dls[[1]], sc = lmtb_config, processes = 48)
saveRDS(lmtb_0_sol_df_u1, proc_path("lmtb_0_sol_df_u1.rds", TRUE))
lmtb_0_sol_df_u2 <- batch_snf(dl = lmtb_0_dls[[2]], sc = lmtb_config, processes = 48)
saveRDS(lmtb_0_sol_df_u2, proc_path("lmtb_0_sol_df_u2.rds", TRUE))
lmtb_0_sol_df_u3 <- batch_snf(dl = lmtb_0_dls[[3]], sc = lmtb_config, processes = 48)
saveRDS(lmtb_0_sol_df_u3, proc_path("lmtb_0_sol_df_u3.rds", TRUE))
lmtb_0_sol_df_u4 <- batch_snf(dl = lmtb_0_dls[[4]], sc = lmtb_config, processes = 48)
saveRDS(lmtb_0_sol_df_u4, proc_path("lmtb_0_sol_df_u4.rds", TRUE))
lmtb_0_sol_df_u5 <- batch_snf(dl = lmtb_0_dls[[5]], sc = lmtb_config, processes = 48)
saveRDS(lmtb_0_sol_df_u5, proc_path("lmtb_0_sol_df_u5.rds", TRUE))
lmtb_l_sol_df_u1 <- batch_snf(dl = lmtb_l_dls[[1]], sc = lmtb_config, processes = 48)
saveRDS(lmtb_l_sol_df_u1, proc_path("lmtb_l_sol_df_u1.rds", TRUE))
lmtb_l_sol_df_u2 <- batch_snf(dl = lmtb_l_dls[[2]], sc = lmtb_config, processes = 48)
saveRDS(lmtb_l_sol_df_u2, proc_path("lmtb_l_sol_df_u2.rds", TRUE))
lmtb_l_sol_df_u3 <- batch_snf(dl = lmtb_l_dls[[3]], sc = lmtb_config, processes = 48)
saveRDS(lmtb_l_sol_df_u3, proc_path("lmtb_l_sol_df_u3.rds", TRUE))
lmtb_l_sol_df_u4 <- batch_snf(dl = lmtb_l_dls[[4]], sc = lmtb_config, processes = 48)
saveRDS(lmtb_l_sol_df_u4, proc_path("lmtb_l_sol_df_u4.rds", TRUE))
lmtb_l_sol_df_u5 <- batch_snf(dl = lmtb_l_dls[[5]], sc = lmtb_config, processes = 48)
saveRDS(lmtb_l_sol_df_u5, proc_path("lmtb_l_sol_df_u5.rds", TRUE))
```

```{r}
lmtb_0_sol_df_u1 <- readRDS(proc_path("2026_01_20_lmtb_0_sol_df_u1.rds"))
lmtb_0_sol_df_u2 <- readRDS(proc_path("2026_01_20_lmtb_0_sol_df_u2.rds"))
lmtb_0_sol_df_u3 <- readRDS(proc_path("2026_01_20_lmtb_0_sol_df_u3.rds"))
lmtb_0_sol_df_u4 <- readRDS(proc_path("2026_01_20_lmtb_0_sol_df_u4.rds"))
lmtb_0_sol_df_u5 <- readRDS(proc_path("2026_01_20_lmtb_0_sol_df_u5.rds"))

lmtb_0_sol_df <- do.call(
    "rbind",
    c(
        list(
            lmtb_0_sol_df_u1,
            lmtb_0_sol_df_u2,
            lmtb_0_sol_df_u3,
            lmtb_0_sol_df_u4,
            lmtb_0_sol_df_u5
        ),
        list(reset_indices = TRUE)
    )
)
saveRDS(lmtb_0_sol_df, proc_path("lmtb_0_sol_df.rds", TRUE))
```

```{r}
lmtb_l_sol_df_u1 <- readRDS(proc_path("2026_01_20_lmtb_l_sol_df_u1.rds"))
lmtb_l_sol_df_u2 <- readRDS(proc_path("2026_01_20_lmtb_l_sol_df_u2.rds"))
lmtb_l_sol_df_u3 <- readRDS(proc_path("2026_01_20_lmtb_l_sol_df_u3.rds"))
lmtb_l_sol_df_u4 <- readRDS(proc_path("2026_01_20_lmtb_l_sol_df_u4.rds"))
lmtb_l_sol_df_u5 <- readRDS(proc_path("2026_01_20_lmtb_l_sol_df_u5.rds"))

lmtb_l_sol_df <- do.call(
    "rbind",
    c(
        list(
            lmtb_l_sol_df_u1,
            lmtb_l_sol_df_u2,
            lmtb_l_sol_df_u3,
            lmtb_l_sol_df_u4,
            lmtb_l_sol_df_u5
        ),
        list(reset_indices = TRUE)
    )
)
saveRDS(lmtb_l_sol_df, proc_path("lmtb_l_sol_df.rds", TRUE))
```

```{r}
lmtb_0_sol_df <- readRDS(proc_path("2026_01_20_lmtb_0_sol_df.rds"))
lmtb_l_sol_df <- readRDS(proc_path("2026_01_20_lmtb_l_sol_df.rds"))
```

```{r}
concordance_w_mtbi_quick <- function(data_df, n = NULL, iters = 10, procs = 1, mtbi_data) {
    tops_df <- topologizer(data_df)
    info_table <- data_df |>
        dplyr::group_by(cluster) |>
        dplyr::summarize(
            income = mean(household_income),
            sex = mean(sex)
        ) |>
        dplyr::mutate(combo = income - sex) |> # sort by low income and high M
        dplyr::arrange(combo)
    swap_key <- paste0(info_table$"cluster", collapse = "")
    swap_list <- list(
        "123" = list(),                 # swap nothing
        "132" = list(c(2, 3)),          # swap 2<->3
        "213" = list(c(1, 2)),          # swap 1<->2
        "231" = list(c(1, 2), c(2, 3)), # swap 1<->2 then 2<->3
        "312" = list(c(1, 3), c(2, 3)), # swap 1<->3 then 2<->3
        "321" = list(c(1, 3))           # swap 1<->3
    )
    swap_instructions <- swap_list[[swap_key]]
    for (instruction in swap_instructions) {
        data_df <- data_df |>
            dplyr::mutate(
                cluster = dplyr::case_when(
                    cluster == instruction[1] ~ factor(instruction[2]),
                    cluster == instruction[2] ~ factor(instruction[1]),
                    TRUE ~ cluster
                )
            )
    }
    info_table <- data_df |>
        dplyr::group_by(cluster) |>
        dplyr::summarize(
            income = mean(household_income),
            sex = mean(sex)
        ) |>
        dplyr::mutate(combo = income - sex) |> # sort by low income and high M
        dplyr::arrange(combo)
    swap_key <- paste0(info_table$"cluster", collapse = "")
    gen_tops_df <- generalizable_features(tops_df, compare_fn_a)
    gen_tops_df_long <- gen_tops_df |>
        pivot_longer(
            cols = -feature,
            names_to = "comparison",
            values_to = "order_sample"
        )
    joint_df <- dplyr::left_join(
        mtbi_data, # reference data frame
        gen_tops_df_long, # sampled data frame
        by = c("feature", "comparison")
    ) |>
        dplyr::mutate(
            match = ifelse(order_sample == order, 1, 0)
        ) |>
        dplyr::filter(!grepl("mtbi", feature))
        joint_df <- joint_df |> dplyr::select(match) |> na.omit()
        print(paste0("nrow: ", nrow(joint_df)))
    concordance <- sum(joint_df$"match", na.rm = TRUE) / nrow(joint_df)
    return(concordance)
}

mtbi_gen_fts_table_hits_t <- read_csv(proc_path("2025_09_22_mtbi_gen_fts_table_hits_t.csv"))
mtbi_gen_long <- na.omit(mtbi_gen_fts_table_hits_t)

dl_idx <- c(rep(1, 200), rep(2, 200), rep(3, 200), rep(4, 200), rep(5, 200))

set.seed(42)
conc_df <- data.frame()
for (i in 1:1000) {
    print(i)
    idx <- dl_idx[[i]]
    if (lmtb_0_sol_df[i, ]$"nclust" == 3) {
        lmtb_0_pl_df <- auto_plot(
            lmtb_0_sol_df[i, ],
            dl = c(lmtb_0_dls[[idx]], lmtb_0_ols[[idx]]),
            return_plots = FALSE
        )
        conc <- concordance_w_mtbi_quick(
            lmtb_0_pl_df,
            mtbi_data = mtbi_gen_long
        )
        conc_df <- rbind(
            conc_df,
            data.frame(
                solution = i,
                dl = idx,
                concordance = conc
            )
        )
    }
}
saveRDS(conc_df, proc_path("lmtb_0_concordance_df.rds", TRUE))
lmtb_l_dls |> length()
conc_df <- data.frame()
for (i in 1:1000) {
    print(i)
    idx <- dl_idx[[i]]
    if (lmtb_l_sol_df[i, ]$"nclust" == 3) {
        lmtb_l_pl_df <- auto_plot(
            lmtb_l_sol_df[i, ],
            dl = c(lmtb_l_dls[[idx]], lmtb_l_ols[[idx]]),
            return_plots = FALSE
        )
        conc <- concordance_w_mtbi_quick(
            lmtb_l_pl_df,
            mtbi_data = mtbi_gen_long
        )
        conc_df <- rbind(
            conc_df,
            data.frame(
                solution = i,
                dl = idx,
                concordance = conc
            )
        )
    }
}
saveRDS(conc_df, proc_path("lmtb_l_concordance_df.rds", TRUE))

lmtb_0_conc_df <- readRDS(proc_path("2026_01_20_lmtb_0_concordance_df.rds"))
lmtb_l_conc_df <- readRDS(proc_path("2026_01_20_lmtb_l_concordance_df.rds"))

# max is 87.3%
#lmtb_0_conc_df |>
lmtb_0_conc_df |>
    arrange(-concordance)

lmtb_0_conc_df$"concordance"

mean(lmtb_0_conc_df$"concordance")

# 44 3 cluster solutions
nrow(lmtb_0_conc_df)

# max is 75.4%
lmtb_l_conc_df |>
    arrange(-concordance) |>
    head()

lmtb_0_conc_df$"group" <- "Pre-injury"
lmtb_l_conc_df$"group" <- "Post-injury"

conc_hist <- rbind(lmtb_0_conc_df, lmtb_l_conc_df) |>
    dplyr::mutate(concordance = 100 * concordance) |>
    ggplot(aes(x = concordance)) +
    geom_histogram(binwidth = 1, colour = "black", fill = "grey") +
    labs(x = "Concordance (%)", y = "Count") +
    facet_wrap(~group) +
    scale_y_continuous(
        limits = c(0, 10),
        breaks = seq(0, 10, by = 1),
        minor_breaks = NULL) +
    theme_bw() +
    theme(text = element_text(size = 14))

ggsave(
    fig_path("lmtb_conc_hist.png", TRUE),
    conc_hist,
    width = 10,
    height = 4
)

# 75 3 cluster solutions
nrow(lmtb_l_conc_df)
```

```{r}
# What is different about the longitudinal dataset?
z0 <- as.data.frame(lmtb_0_dls[[1]])
z1 <- as.data.frame(lmtb_l_dls[[1]])

z0s <- z0 |>
    skimr::skim_without_charts() |>
    dplyr::select(skim_variable, numeric.mean) |>
    data.frame()
z1s <- z1 |>
    skimr::skim_without_charts() |>
    dplyr::select(skim_variable, numeric.mean) |>
    data.frame()
colnames(z0s) <- c("var", "m1")
colnames(z1s) <- c("var", "m2")
joined <- na.omit(dplyr::inner_join(z0s, z1s))
rownames(joined) <- joined$"var"
joined <- log(as.matrix(joined[, -1]))
joined <- data.frame(joined)
joined[, "m3"] <- joined[, "m2"] - joined[, "m1"]
joined <- as.matrix(joined)
ComplexHeatmap::Heatmap(joined[, -c(1, 2)])

# This heatmap suggests it is largely different by pubertal status and screen time
```

## Q4. Classifier built from baseline mTBI data: informative?

Assigning predicted clusters to the following 5 groups:

1. Longitudinal mTBI, pre-injury data (N = 220): lmtb_0
2. Longitudinal mTBI, post-injury data (the same N = 220): lmtb_l
3. Baseline uninjured group at T0: unij_0
4. Longitudinal uninjured group at T0: lunj_0
5. Longitudinal uninjured group at T2: lunj_l

The baseline uninjured sample here is a little bit complicated.
For the longitudinal time point of the baseline uninjured sample, we must use the N = 7278 subjects that were calculated in CH6.
These were uninjured subjects that had T2 data and were sibling dropped.
To pull them out in the baseline sample, we need to use the PRE-sibling drop data lists.

```{r}
library(caret)
library(randomForest)
```

```{r}
lunj_subs_wt2_ns <- readRDS(sub_path("2026_01_19_lunj_subs_wt2_ns.rds"))
lunj_subs_wt2_ns <- paste0("uid_", lunj_subs_wt2_ns)
unij_subs_wt2_ns <- readRDS(sub_path("2026_01_19_unij_subs_wt2_ns.rds"))
unij_subs_wt2_ns <- paste0("uid_", unij_subs_wt2_ns)

# Classifying data using baseline as well as longitudinal features
lmtb_0_dl <- all_long_dls_h_ns$"lmtb_0_dls"[[1]]
lmtb_0_ol <- all_long_dls_h_ns$"lmtb_0_ols"[[1]]

lmtb_l_dl <- all_long_dls_h_ns$"lmtb_l_dls"[[1]]
lmtb_l_ol <- all_long_dls_h_ns$"lmtb_l_ols"[[1]]

unij_0_dl <- all_dls_h$"unij_all_p_dls"[[1]]
unij_0_ol <- all_dls_h$"unij_all_p_ols"[[1]]

unij_l_dl <- all_long_dls_h$"unij_l_dls"[[1]]
unij_l_ol <- all_long_dls_h$"unij_l_ols"[[1]]
```

```{r}
# Converting the sets of data lists into sets of data frames
lmtb_0_dl_df_wt2_ns <- as.data.frame(lmtb_0_dl)
lmtb_0_ol_df_wt2_ns <- as.data.frame(lmtb_0_ol)
nrow(lmtb_0_dl_df_wt2_ns) # N = 217

lmtb_l_dl_df_wt2_ns <- as.data.frame(lmtb_l_dl)
lmtb_l_ol_df_wt2_ns <- as.data.frame(lmtb_l_ol)
nrow(lmtb_l_dl_df_wt2_ns) # N = 217

unij_0_dl_df <- as.data.frame(unij_0_dl)
unij_0_ol_df <- as.data.frame(unij_0_ol)
nrow(unij_0_dl_df) # N = 9302

unij_l_dl_df <- as.data.frame(unij_l_dl)
unij_l_ol_df <- as.data.frame(unij_l_ol)
nrow(unij_l_dl_df) # N = 8572

# wt2 drop, NS drop
# Baseline uninjured sample that has T2 data, baseline data
unij_0_dl_df_wt2_ns <- unij_0_dl_df |> dplyr::filter(uid %in% unij_subs_wt2_ns)
nrow(unij_0_dl_df_wt2_ns) # 7278
unij_0_ol_df_wt2_ns <- unij_0_ol_df |> dplyr::filter(uid %in% unij_subs_wt2_ns)
nrow(unij_0_ol_df_wt2_ns) # 7278

# Baseline uninjured sample that has T2 data, long data
unij_l_dl_df_wt2_ns <- unij_l_dl_df |> dplyr::filter(uid %in% unij_subs_wt2_ns)
nrow(unij_l_dl_df_wt2_ns) # 7278
unij_l_ol_df_wt2_ns <- unij_l_ol_df |> dplyr::filter(uid %in% unij_subs_wt2_ns)
nrow(unij_l_ol_df_wt2_ns) # 7278

# wt2 drop, NS drop
# Long uninjured sample that has T2 data, baseline data
lunj_0_dl_df_wt2_ns <- unij_0_dl_df |> dplyr::filter(uid %in% lunj_subs_wt2_ns)
nrow(lunj_0_dl_df_wt2_ns) # 6512
lunj_0_ol_df_wt2_ns <- unij_0_ol_df |> dplyr::filter(uid %in% lunj_subs_wt2_ns)
nrow(lunj_0_ol_df_wt2_ns) # 6512

# Long uninjured sample that has T2 data, long data
lunj_l_dl_df_wt2_ns <- unij_l_dl_df |> dplyr::filter(uid %in% lunj_subs_wt2_ns)
nrow(lunj_l_dl_df_wt2_ns) # 6512
lunj_l_ol_df_wt2_ns <- unij_l_ol_df |> dplyr::filter(uid %in% lunj_subs_wt2_ns)
nrow(lunj_l_ol_df_wt2_ns) # 6512

comparison_dl_dfs <- list(
    "lmtb_0_dl_df" = lmtb_0_dl_df_wt2_ns,
    "lmtb_l_dl_df" = lmtb_l_dl_df_wt2_ns,
    "unij_0_dl_df" = unij_0_dl_df_wt2_ns,
    "unij_l_dl_df" = unij_l_dl_df_wt2_ns,
    "lunj_0_dl_df" = lunj_0_dl_df_wt2_ns,
    "lunj_l_dl_df" = lunj_l_dl_df_wt2_ns
)

comparison_ol_dfs <- list(
    "lmtb_0_ol_df" = lmtb_0_ol_df_wt2_ns,
    "lmtb_l_ol_df" = lmtb_l_ol_df_wt2_ns,
    "unij_0_ol_df" = unij_0_ol_df_wt2_ns,
    "unij_l_ol_df" = unij_l_ol_df_wt2_ns,
    "lunj_0_ol_df" = lunj_0_ol_df_wt2_ns,
    "lunj_l_ol_df" = lunj_l_ol_df_wt2_ns
)

saveRDS(comparison_dl_dfs, proc_path("comparison_dl_dfs.rds", TRUE))
saveRDS(comparison_ol_dfs, proc_path("comparison_ol_dfs.rds", TRUE))
```

```{r}
comparison_dl_dfs <- readRDS(proc_path("2026_01_21_comparison_dl_dfs.rds"))
comparison_ol_dfs <- readRDS(proc_path("2026_01_21_comparison_ol_dfs.rds"))
```

```{r}
classifier_ifts <- readRDS(proc_path("2025_09_23_classifier_ifts.rds"))

classifier_ft_dl_dfs <- lapply(
    comparison_dl_dfs,
    function(x) {
        x[, classifier_ifts]
    }
)

```

```{r}
# Extracted temporally sensitive features for all ABCD subjects at T0 and T2
temporal_df0 <- readRDS(proc_path("2025_09_25_temporal_df.rds"))
temporal_df2 <- readRDS(proc_path("2025_09_25_temporal_df2.rds"))

subtype_classifier <- readRDS(model_path("2025_09_25_subtype_classifier.rds"))
```

The scaling process that occurs below is described as follows.
Consider the data frame `lmtb_0_df`, which contains feature values for the longitudinal mTBI sample at baseline data collection timepoint.
A subset of the columns in `lmtb_0_df` are identified as temporally sensitive.

Our goal is to re-scale these columns within `lmtb_0_df` based on the entire set of ABCD values of that feature for that time point.
The raw extracted set of ABCD values for those temporally sensitive features are found in `temporal_df0` (for T0 values), and `temporal_df2` (for T2 values).
However, scaling those data frames alone is insufficient, as we would not be making use of the missing values that we have imputed.
To account for this, we start by replacing the temporally sensitive features in `temporal_0_df` for the observations in `lmtb_0_df` with the values in `long_mtbi_0_df`.
That is, we inject our cleaned, imputed values for those temporally sensitive features and overwrite the raw extracted ones.
Then, we scale `temporal_df0`.
Finally, we extract our scaled values back into the original `lmtb_0_df`.
This process is made slightly more complicated by doing this process for all the baseline concussion and uninjured sampes simultaneously.

```{r}
# Cleaning up the UID column of the temporally sensitive feature data frames
temporal_df0$"uid" <- gsub("uid_", "", temporal_df0$"uid")
temporal_df2$"uid" <- gsub("uid_", "", temporal_df2$"uid")

# Remove the UID column
temporal_cols <- colnames(temporal_df0)
```

There is notably some overlap between the long_mtbi group and the base_unij group.
As such, we handle the sub-in and scale for the different groups here separately.

```{r}
swap_with_scaled <- function(reference_df, df_to_scale, scaling_cols) {
    reference_df <- reference_df |>
        dplyr::filter(!uid %in% df_to_scale$"uid")
    scaling_fts <- setdiff(scaling_cols, "uid")
    stacked_df <- rbind(
        reference_df,
        df_to_scale[, scaling_cols]
    )
    stacked_df[scaling_fts] <- sapply(stacked_df[scaling_fts], scale)
    rescaled_df <- df_to_scale |>
        dplyr::select(-dplyr::all_of(scaling_fts)) |>
        dplyr::inner_join(stacked_df, by = "uid") |>
        data.frame()
    return(rescaled_df)
}

unij_0_time_scaled <- swap_with_scaled(
    temporal_df0,
    comparison_dl_dfs$"unij_0_dl_df",
    temporal_cols
)
lmtb_0_time_scaled <- swap_with_scaled(
    temporal_df0,
    comparison_dl_dfs$"lmtb_0_dl_df",
    temporal_cols
)
lunj_0_time_scaled <- swap_with_scaled(
    temporal_df0,
    comparison_dl_dfs$"lunj_0_dl_df",
    temporal_cols
)
unij_l_time_scaled <- swap_with_scaled(
    temporal_df2,
    comparison_dl_dfs$"unij_l_dl_df",
    temporal_cols
)
lmtb_l_time_scaled <- swap_with_scaled(
    temporal_df2,
    comparison_dl_dfs$"lmtb_l_dl_df",
    temporal_cols
)
lunj_l_time_scaled <- swap_with_scaled(
    temporal_df2,
    comparison_dl_dfs$"lunj_l_dl_df",
    temporal_cols
)

saveRDS(unij_0_time_scaled, proc_path("unij_0_time_scaled.rds", TRUE))
saveRDS(lmtb_0_time_scaled, proc_path("lmtb_0_time_scaled.rds", TRUE))
saveRDS(lunj_0_time_scaled, proc_path("lunj_0_time_scaled.rds", TRUE))
saveRDS(unij_l_time_scaled, proc_path("unij_l_time_scaled.rds", TRUE))
saveRDS(lmtb_l_time_scaled, proc_path("lmtb_l_time_scaled.rds", TRUE))
saveRDS(lunj_l_time_scaled, proc_path("lunj_l_time_scaled.rds", TRUE))
```

At this point the temporally sensitive variables has been appropriately time scaled for all data frames.


```{r}
unij_0_time_scaled <- readRDS(proc_path("2026_01_21_unij_0_time_scaled.rds"))
lmtb_0_time_scaled <- readRDS(proc_path("2026_01_21_lmtb_0_time_scaled.rds"))
lunj_0_time_scaled <- readRDS(proc_path("2026_01_21_lunj_0_time_scaled.rds"))
unij_l_time_scaled <- readRDS(proc_path("2026_01_21_unij_l_time_scaled.rds"))
lmtb_l_time_scaled <- readRDS(proc_path("2026_01_21_lmtb_l_time_scaled.rds"))
lunj_l_time_scaled <- readRDS(proc_path("2026_01_21_lunj_l_time_scaled.rds"))
```

```{r}
make_pred_df <- function(df) {
    # prep data is function from chapter 8
    clean_df <- prep_data(df)
    df$"cluster" <- predict(subtype_classifier, newdata = clean_df)
    return(df)
}

unij_0_pred_df <- make_pred_df(unij_0_time_scaled)
lmtb_0_pred_df <- make_pred_df(lmtb_0_time_scaled)
lunj_0_pred_df <- make_pred_df(lunj_0_time_scaled)
unij_l_pred_df <- make_pred_df(unij_l_time_scaled)
lmtb_l_pred_df <- make_pred_df(lmtb_l_time_scaled)
lunj_l_pred_df <- make_pred_df(lunj_l_time_scaled)

write_csv(unij_0_pred_df, proc_path("unij_0_pred_df.csv", TRUE))
write_csv(lmtb_0_pred_df, proc_path("lmtb_0_pred_df.csv", TRUE))
write_csv(lunj_0_pred_df, proc_path("lunj_0_pred_df.csv", TRUE))
write_csv(unij_l_pred_df, proc_path("unij_l_pred_df.csv", TRUE))
write_csv(lmtb_l_pred_df, proc_path("lmtb_l_pred_df.csv", TRUE))
write_csv(lunj_l_pred_df, proc_path("lunj_l_pred_df.csv", TRUE))
```

```{r}
# CHECKPOINT
unij_0_pred_df <- read_csv(proc_path("2026_01_21_unij_0_pred_df.csv"))
lmtb_0_pred_df <- read_csv(proc_path("2026_01_21_lmtb_0_pred_df.csv"))
lunj_0_pred_df <- read_csv(proc_path("2026_01_21_lunj_0_pred_df.csv"))
unij_l_pred_df <- read_csv(proc_path("2026_01_21_unij_l_pred_df.csv"))
lmtb_l_pred_df <- read_csv(proc_path("2026_01_21_lmtb_l_pred_df.csv"))
lunj_l_pred_df <- read_csv(proc_path("2026_01_21_lunj_l_pred_df.csv"))
```

```{r}
unij_0_cluster_df <- dplyr::select(unij_0_pred_df, uid, cluster)
lmtb_0_cluster_df <- dplyr::select(lmtb_0_pred_df, uid, cluster)
lunj_0_cluster_df <- dplyr::select(lunj_0_pred_df, uid, cluster)
unij_l_cluster_df <- dplyr::select(unij_l_pred_df, uid, cluster)
lmtb_l_cluster_df <- dplyr::select(lmtb_l_pred_df, uid, cluster)
lunj_l_cluster_df <- dplyr::select(lunj_l_pred_df, uid, cluster)
```

```{r}
# Proportion of each cluster in the data frame
cluster_props <- function(cluster_df) {
    cluster_df$"cluster" |>
    table() |>
    prop.table() |>
    (\(x) 100 * x)()
}

cluster_props(unij_0_cluster_df) # 22.4, 37.4, 40.2

cluster_props(unij_l_cluster_df) # 21.0, 35.2, 43.8

cluster_props(lunj_0_cluster_df) # 22.0, 37.5, 40.5

cluster_props(lunj_l_cluster_df) # 20.3, 35.4, 44.3

cluster_props(lmtb_0_cluster_df) # 13.4, 53.5, 33.2
cluster_props(lmtb_l_cluster_df) # 14.3, 49.3, 36.4

# Compare with the original full solution proportions
mtbi_ful_df <- readRDS(proc_path("2025_09_16_mtbi_ful_df.rds"))

cluster_props(mtbi_ful_df) # 28.1, 41.6, 30.4
```

```{r}
classifier_ifts <- readRDS(proc_path("2025_09_23_classifier_ifts.rds"))
ofts <- readRDS(proc_path("2025_09_15_ofts.rds"))
relevant_fts <- c(classifier_ifts, ofts)

export_wrapped_plots <- function(df,
                                 dl,
                                 ol,
                                 name,
                                 feature_set = NULL,
                                 w = 45,
                                 h = 30,
                                 rows = NULL,
                                 cols = NULL,
                                 dpi = 100,
                                 export = TRUE) {
    plot_list <- auto_plot(
        cluster_df = data.frame(df),
        dl = c(dl, ol)
    )
    wrapped_plots <- wrap_plots(
        plot_list[feature_set],
        nrow = rows,
        ncol = cols,
    )
    if (export) {
        ggsave(
            fig_path(name, TRUE),
            width = w,
            height = h,
            dpi = dpi
        )
    } else {
        return(plot_list[feature_set])
    }
}

export_wrapped_plots(
    df = lmtb_0_cluster_df,
    dl = lmtb_0_dl,
    ol = lmtb_0_ol,
    feature_set = relevant_fts,
    name = "lmtb_0_pred_scaled_plot.png"
)

export_wrapped_plots(
    df = lmtb_l_cluster_df,
    dl = lmtb_l_dl,
    ol = lmtb_l_ol,
    feature_set = relevant_fts,
    name = "lmtb_l_pred_scaled_plot.png"
)

export_wrapped_plots(
    df = unij_0_cluster_df,
    dl = dlapply(
        unij_0_dl,
        function(x) {
            x$"data" <- dplyr::filter(x$"data", uid %in% unij_0_cluster_df$"uid")
            x
        }
    ),
    ol = dlapply(
        unij_0_ol,
        function(x) {
            x$"data" <- dplyr::filter(x$"data", uid %in% unij_0_cluster_df$"uid")
            x
        }
    ),
    feature_set = relevant_fts,
    name = "unij_0_pred_scaled_plot.png"
)

export_wrapped_plots(
    df = unij_l_cluster_df,
    dl = dlapply(
        unij_l_dl,
        function(x) {
            x$"data" <- dplyr::filter(x$"data", uid %in% unij_l_cluster_df$"uid")
            x
        }
    ),
    ol = dlapply(
        unij_l_ol,
        function(x) {
            x$"data" <- dplyr::filter(x$"data", uid %in% unij_l_cluster_df$"uid")
            x
        }
    ),
    feature_set = relevant_fts,
    name = "unij_l_pred_scaled_plot.png"
)

# Just top 10 features
sorted_inputs <- readRDS(proc_path("2025_09_15_ifts.rds"))
outcome_fts <- readRDS(proc_path("2025_09_15_ofts.rds"))
top_fts <- intersect(
    c(sorted_inputs[1:10], outcome_fts),
    relevant_fts
)

export_wrapped_plots(
    df = lmtb_0_cluster_df,
    dl = lmtb_0_dl,
    ol = lmtb_0_ol,
    feature_set = top_fts,
    rows = 2,
    w = 30,
    h = 7,
    name = "lmtb_0_pred_scaled_plot_top_fts.png"
)

export_wrapped_plots(
    df = lmtb_l_cluster_df,
    dl = lmtb_l_dl,
    ol = lmtb_l_ol,
    feature_set = top_fts,
    rows = 2,
    w = 30,
    h = 7,
    name = "lmtb_l_pred_scaled_plot_top_fts.png"
)

export_wrapped_plots(
    df = unij_0_cluster_df,
    dl = dlapply(
        unij_0_dl,
        function(x) {
            x$"data" <- dplyr::filter(x$"data", uid %in% unij_0_cluster_df$"uid")
            x
        }
    ),
    ol = dlapply(
        unij_0_ol,
        function(x) {
            x$"data" <- dplyr::filter(x$"data", uid %in% unij_0_cluster_df$"uid")
            x
        }
    ),
    feature_set = top_fts,
    rows = 2,
    w = 30,
    h = 7,
    name = "unij_0_pred_scaled_plot_top_fts.png"
)

export_wrapped_plots(
    df = unij_l_cluster_df,
    dl = dlapply(
        unij_l_dl,
        function(x) {
            x$"data" <- dplyr::filter(x$"data", uid %in% unij_l_cluster_df$"uid")
            x
        }
    ),
    ol = dlapply(
        unij_l_ol,
        function(x) {
            x$"data" <- dplyr::filter(x$"data", uid %in% unij_l_cluster_df$"uid")
            x
        }
    ),
    feature_set = top_fts,
    rows = 2,
    w = 30,
    h = 7,
    name = "unij_l_pred_scaled_plot_top_fts.png"
)

lunj_0_dl <- unij_0_dl |>
    dlapply(
        function(x) {
            x$"data" <- dplyr::filter(x$"data", uid %in% lunj_subs_wt2_ns)
            return(x)
        }
    )
lunj_0_ol <- unij_0_ol |>
    dlapply(
        function(x) {
            x$"data" <- dplyr::filter(x$"data", uid %in% lunj_subs_wt2_ns)
            return(x)
        }
    )
lunj_l_dl <- unij_l_dl |>
    dlapply(
        function(x) {
            x$"data" <- dplyr::filter(x$"data", uid %in% lunj_subs_wt2_ns)
            return(x)
        }
    )
lunj_l_ol <- unij_l_ol |>
    dlapply(
        function(x) {
            x$"data" <- dplyr::filter(x$"data", uid %in% lunj_subs_wt2_ns)
            return(x)
        }
    )

export_wrapped_plots(
    df = lunj_0_cluster_df,
    dl = lunj_0_dl,
    ol = lunj_0_ol,
    feature_set = relevant_fts,
    name = "lunj_0_pred_scaled_plot.png"
)

export_wrapped_plots(
    df = lunj_l_cluster_df,
    dl = lunj_l_dl,
    ol = lunj_l_ol,
    feature_set = relevant_fts,
    name = "lunj_l_pred_scaled_plot.png"
)
```

Just inputs:

```{r}
light_fts <- c(
    "sex", # 1 (cat)
    "brain_volume", # 2
    "household_income",
    "race", # 6 (cat)
    "parent_antisocial",
    "weekday_screentime",
    "activities_last_year",
    "cbcl_aggressive",
    "sds_sleep"
)

lmtb_0_pl <- export_wrapped_plots(
    df = lmtb_0_cluster_df,
    dl = lmtb_0_dl,
    ol = lmtb_0_ol,
    feature_set = light_fts,
    cols = 1,
    h = 22,
    w = 5,
    dpi = 80,
    name = "lmtb_0_pred_scaled_plot_top_ins.png",
    export = FALSE
)
lapply(
    seq_along(lmtb_0_pl),
    function(x) {
        lmtb_0_pl[[x]] <- lmtb_0_pl[[x]] + theme(
            legend.title = element_text(size = 14),
            legend.text = element_text(size = 14),
            axis.title.y = element_text(size = 14),
            axis.title.x = element_blank()
        )
        if (x %in% c(2, 3, 5, 6, 7, 8, 9)) {
            # Categorical features
            lmtb_0_pl[[x]]$"layers"[[3]]$"aes_params"$"size" <- 3
        }
        if (x %in% c(1, 4)) {
            # Continuous / numeric features
            lmtb_0_pl[[x]]$"layers"[[2]]$"aes_params"$"size" <- 5
        }
        if (x == 2) {
            lmtb_0_pl[[x]] <- lmtb_0_pl[[x]] +
                scale_y_continuous(labels = function(y) y / 1000) +
                labs(y = "brain volume\n(cm³)")
        }
        if (x == 3) {
            lmtb_0_pl[[x]] <- lmtb_0_pl[[x]] +
                labs(y = "household\nincome")
        }
        if (x == 4) {
            lmtb_0_pl[[x]] <- lmtb_0_pl[[x]] +
                labs(y = "parent\nantisocial")
        }
        if (x == 5) {
            lmtb_0_pl[[x]] <- lmtb_0_pl[[x]] +
                labs(y = "weekday\nscreentime")
        }
        if (x == 6) {
            lmtb_0_pl[[x]] <- lmtb_0_pl[[x]] +
                labs(y = "activities\nlast year")
        }
        if (x == 7) {
            lmtb_0_pl[[x]] <- lmtb_0_pl[[x]] +
                labs(y = "cbcl\naggressive")
        }
        if (x == 8) {
            lmtb_0_pl[[x]] <- lmtb_0_pl[[x]] +
                labs(y = "sds\nsleep")
        }
        lmtb_0_pl[[x]]
    }
) |>
    wrap_plots(ncol = 1) |>
    ggsave(
        filename = fig_path("lmtb_0_pred_scaled_plot_top_ins.png", TRUE),
        width = 4,
        height = 15,
        dpi = 80
    )

lmtb_l_pl <- export_wrapped_plots(
    df = lmtb_l_cluster_df,
    dl = lmtb_l_dl,
    ol = lmtb_l_ol,
    feature_set = light_fts,
    cols = 1,
    h = 22,
    w = 5,
    dpi = 80,
    name = "lmtb_l_pred_scaled_plot_top_ins.png",
    export = FALSE
)
lapply(
    seq_along(lmtb_l_pl),
    function(x) {
        lmtb_l_pl[[x]] <- lmtb_l_pl[[x]] + theme(
            legend.title = element_text(size = 14),
            legend.text = element_text(size = 14),
            axis.title.y = element_text(size = 14),
            axis.title.x = element_blank()
        )
        if (x %in% c(2, 3, 5, 6, 7, 8, 9)) {
            # Categorical features
            lmtb_l_pl[[x]]$"layers"[[3]]$"aes_params"$"size" <- 3
        }
        if (x %in% c(1, 4)) {
            # Continuous / numeric features
            lmtb_l_pl[[x]]$"layers"[[2]]$"aes_params"$"size" <- 5
        }
        if (x == 2) {
            lmtb_l_pl[[x]] <- lmtb_l_pl[[x]] +
                scale_y_continuous(labels = function(y) y / 1000) +
                labs(y = "brain volume\n(cm³)")
        }
        if (x == 3) {
            lmtb_l_pl[[x]] <- lmtb_l_pl[[x]] +
                labs(y = "household\nincome")
        }
        if (x == 4) {
            lmtb_l_pl[[x]] <- lmtb_l_pl[[x]] +
                labs(y = "parent\nantisocial")
        }
        if (x == 5) {
            lmtb_l_pl[[x]] <- lmtb_l_pl[[x]] +
                labs(y = "weekday\nscreentime")
        }
        if (x == 6) {
            lmtb_l_pl[[x]] <- lmtb_l_pl[[x]] +
                labs(y = "activities\nlast year")
        }
        if (x == 7) {
            lmtb_l_pl[[x]] <- lmtb_l_pl[[x]] +
                labs(y = "cbcl\naggressive")
        }
        if (x == 8) {
            lmtb_l_pl[[x]] <- lmtb_l_pl[[x]] +
                labs(y = "sds\nsleep")
        }
        lmtb_l_pl[[x]]
    }
) |>
    wrap_plots(ncol = 1) |>
    ggsave(
        filename = fig_path("lmtb_l_pred_scaled_plot_top_ins.png", TRUE),
        width = 4,
        height = 15,
        dpi = 80
    )

unij_0_pl <- export_wrapped_plots(
    df = unij_0_cluster_df,
    dl = dlapply(
        unij_0_dl,
        function(x) {
            x$"data" <- dplyr::filter(x$"data", uid %in% unij_0_cluster_df$"uid")
            x
        }
    ),
    ol = dlapply(
        unij_0_ol,
        function(x) {
            x$"data" <- dplyr::filter(x$"data", uid %in% unij_0_cluster_df$"uid")
            x
        }
    ),
    feature_set = light_fts,
    cols = 1,
    h = 22,
    w = 5,
    dpi = 80,
    name = "unij_0_pred_scaled_plot_top_ins.png",
    export = FALSE
)
lapply(
    seq_along(unij_0_pl),
    function(x) {
        unij_0_pl[[x]] <- unij_0_pl[[x]] + theme(
            legend.title = element_text(size = 14),
            legend.text = element_text(size = 14),
            axis.title.y = element_text(size = 14),
            axis.title.x = element_blank()
        )
        if (x %in% c(2, 3, 5, 6, 7, 8, 9)) {
            # Categorical features
            unij_0_pl[[x]]$"layers"[[3]]$"aes_params"$"size" <- 3
        }
        if (x %in% c(1, 4)) {
            # Continuous / numeric features
            unij_0_pl[[x]]$"layers"[[2]]$"aes_params"$"size" <- 5
        }
        if (x == 2) {
            unij_0_pl[[x]] <- unij_0_pl[[x]] +
                scale_y_continuous(labels = function(y) y / 1000) +
                labs(y = "brain volume\n(cm³)")
        }
        if (x == 3) {
            unij_0_pl[[x]] <- unij_0_pl[[x]] +
                labs(y = "household\nincome")
        }
        if (x == 4) {
            unij_0_pl[[x]] <- unij_0_pl[[x]] +
                labs(y = "parent\nantisocial")
        }
        if (x == 5) {
            unij_0_pl[[x]] <- unij_0_pl[[x]] +
                labs(y = "weekday\nscreentime")
        }
        if (x == 6) {
            unij_0_pl[[x]] <- unij_0_pl[[x]] +
                labs(y = "activities\nlast year")
        }
        if (x == 7) {
            unij_0_pl[[x]] <- unij_0_pl[[x]] +
                labs(y = "cbcl\naggressive")
        }
        if (x == 8) {
            unij_0_pl[[x]] <- unij_0_pl[[x]] +
                labs(y = "sds\nsleep")
        }
        unij_0_pl[[x]]
    }
) |>
    wrap_plots(ncol = 1) |>
    ggsave(
        filename = fig_path("unij_0_pred_scaled_plot_top_ins.png", TRUE),
        width = 4,
        height = 15,
        dpi = 80
    )

unij_l_pl <- export_wrapped_plots(
    df = unij_l_cluster_df,
    dl = dlapply(
        unij_l_dl,
        function(x) {
            x$"data" <- dplyr::filter(x$"data", uid %in% unij_l_cluster_df$"uid")
            x
        }
    ),
    ol = dlapply(
        unij_l_ol,
        function(x) {
            x$"data" <- dplyr::filter(x$"data", uid %in% unij_l_cluster_df$"uid")
            x
        }
    ),
    feature_set = light_fts,
    cols = 1,
    h = 22,
    w = 5,
    dpi = 80,
    name = "unij_l_pred_scaled_plot_top_ins.png",
    export = FALSE
)
lapply(
    seq_along(unij_l_pl),
    function(x) {
        unij_l_pl[[x]] <- unij_l_pl[[x]] + theme(
            legend.title = element_text(size = 14),
            legend.text = element_text(size = 14),
            axis.title.y = element_text(size = 14),
            axis.title.x = element_blank()
        )
        if (x %in% c(2, 3, 5, 6, 7, 8, 9)) {
            # Categorical features
            unij_l_pl[[x]]$"layers"[[3]]$"aes_params"$"size" <- 3
        }
        if (x %in% c(1, 4)) {
            # Continuous / numeric features
            unij_l_pl[[x]]$"layers"[[2]]$"aes_params"$"size" <- 5
        }
        if (x == 2) {
            unij_l_pl[[x]] <- unij_l_pl[[x]] +
                scale_y_continuous(labels = function(y) y / 1000) +
                labs(y = "brain volume\n(cm³)")
        }
        if (x == 3) {
            unij_l_pl[[x]] <- unij_l_pl[[x]] +
                labs(y = "household\nincome")
        }
        if (x == 4) {
            unij_l_pl[[x]] <- unij_l_pl[[x]] +
                labs(y = "parent\nantisocial")
        }
        if (x == 5) {
            unij_l_pl[[x]] <- unij_l_pl[[x]] +
                labs(y = "weekday\nscreentime")
        }
        if (x == 6) {
            unij_l_pl[[x]] <- unij_l_pl[[x]] +
                labs(y = "activities\nlast year")
        }
        if (x == 7) {
            unij_l_pl[[x]] <- unij_l_pl[[x]] +
                labs(y = "cbcl\naggressive")
        }
        if (x == 8) {
            unij_l_pl[[x]] <- unij_l_pl[[x]] +
                labs(y = "sds\nsleep")
        }
        unij_l_pl[[x]]
    }
) |>
    wrap_plots(ncol = 1) |>
    ggsave(
        filename = fig_path("unij_l_pred_scaled_plot_top_ins.png", TRUE),
        width = 4,
        height = 15,
        dpi = 80
    )

lunj_0_pl <- export_wrapped_plots(
    df = lunj_0_cluster_df,
    dl = lunj_0_dl,
    ol = lunj_0_ol,
    feature_set = light_fts,
    cols = 1,
    h = 22,
    w = 5,
    dpi = 80,
    name = "lunj_0_pred_scaled_plot_top_ins.png",
    export = FALSE
)
lapply(
    seq_along(lunj_0_pl),
    function(x) {
        lunj_0_pl[[x]] <- lunj_0_pl[[x]] + theme(
            legend.title = element_text(size = 14),
            legend.text = element_text(size = 14),
            axis.title.y = element_text(size = 14),
            axis.title.x = element_blank()
        )
        if (x %in% c(2, 3, 5, 6, 7, 8, 9)) {
            # Categorical features
            lunj_0_pl[[x]]$"layers"[[3]]$"aes_params"$"size" <- 3
        }
        if (x %in% c(1, 4)) {
            # Continuous / numeric features
            lunj_0_pl[[x]]$"layers"[[2]]$"aes_params"$"size" <- 5
        }
        if (x == 2) {
            lunj_0_pl[[x]] <- lunj_0_pl[[x]] +
                scale_y_continuous(labels = function(y) y / 1000) +
                labs(y = "brain volume\n(cm³)")
        }
        if (x == 3) {
            lunj_0_pl[[x]] <- lunj_0_pl[[x]] +
                labs(y = "household\nincome")
        }
        if (x == 4) {
            lunj_0_pl[[x]] <- lunj_0_pl[[x]] +
                labs(y = "parent\nantisocial")
        }
        if (x == 5) {
            lunj_0_pl[[x]] <- lunj_0_pl[[x]] +
                labs(y = "weekday\nscreentime")
        }
        if (x == 6) {
            lunj_0_pl[[x]] <- lunj_0_pl[[x]] +
                labs(y = "activities\nlast year")
        }
        if (x == 7) {
            lunj_0_pl[[x]] <- lunj_0_pl[[x]] +
                labs(y = "cbcl\naggressive")
        }
        if (x == 8) {
            lunj_0_pl[[x]] <- lunj_0_pl[[x]] +
                labs(y = "sds\nsleep")
        }
        lunj_0_pl[[x]]
    }
) |>
    wrap_plots(ncol = 1) |>
    ggsave(
        filename = fig_path("lunj_0_pred_scaled_plot_top_ins.png", TRUE),
        width = 4,
        height = 15,
        dpi = 80
    )

lunj_l_pl <- export_wrapped_plots(
    df = lunj_l_cluster_df,
    dl = lunj_l_dl,
    ol = lunj_l_ol,
    feature_set = light_fts,
    cols = 1,
    h = 22,
    w = 5,
    dpi = 80,
    name = "lunj_l_pred_scaled_plot_top_ins.png",
    export = FALSE
)
lapply(
    seq_along(lunj_l_pl),
    function(x) {
        lunj_l_pl[[x]] <- lunj_l_pl[[x]] + theme(
            legend.title = element_text(size = 14),
            legend.text = element_text(size = 14),
            axis.title.y = element_text(size = 14),
            axis.title.x = element_blank()
        )
        if (x %in% c(2, 3, 5, 6, 7, 8, 9)) {
            # Categorical features
            lunj_l_pl[[x]]$"layers"[[3]]$"aes_params"$"size" <- 3
        }
        if (x %in% c(1, 4)) {
            # Continuous / numeric features
            lunj_l_pl[[x]]$"layers"[[2]]$"aes_params"$"size" <- 5
        }
        if (x == 2) {
            lunj_l_pl[[x]] <- lunj_l_pl[[x]] +
                scale_y_continuous(labels = function(y) y / 1000) +
                labs(y = "brain volume\n(cm³)")
        }
        if (x == 3) {
            lunj_l_pl[[x]] <- lunj_l_pl[[x]] +
                labs(y = "household\nincome")
        }
        if (x == 4) {
            lunj_l_pl[[x]] <- lunj_l_pl[[x]] +
                labs(y = "parent\nantisocial")
        }
        if (x == 5) {
            lunj_l_pl[[x]] <- lunj_l_pl[[x]] +
                labs(y = "weekday\nscreentime")
        }
        if (x == 6) {
            lunj_l_pl[[x]] <- lunj_l_pl[[x]] +
                labs(y = "activities\nlast year")
        }
        if (x == 7) {
            lunj_l_pl[[x]] <- lunj_l_pl[[x]] +
                labs(y = "cbcl\naggressive")
        }
        if (x == 8) {
            lunj_l_pl[[x]] <- lunj_l_pl[[x]] +
                labs(y = "sds\nsleep")
        }
        lunj_l_pl[[x]]
    }
) |>
    wrap_plots(ncol = 1) |>
    ggsave(
        filename = fig_path("lunj_l_pred_scaled_plot_top_ins.png", TRUE),
        width = 4,
        height = 15,
        dpi = 80
    )
```

Statistical analysis: bootstrapped similarity to baseline mTBI solution

```{r}
mtbi_gen_fts_table_hits_t <- read_csv(proc_path("2025_09_22_mtbi_gen_fts_table_hits_t.csv"))
mtbi_gen_long <- na.omit(mtbi_gen_fts_table_hits_t)

lmtb_0_data_df <- dplyr::inner_join(
    lmtb_0_cluster_df,
    as.data.frame(c(lmtb_0_dl, lmtb_0_ol)),
    by = "uid"
)
nrow(lmtb_0_data_df)

lmtb_l_data_df <- dplyr::inner_join(
    lmtb_l_cluster_df,
    as.data.frame(c(lmtb_l_dl, lmtb_l_ol)),
    by = "uid"
)
nrow(lmtb_l_data_df)

unij_0_data_df <- dplyr::inner_join(
    unij_0_cluster_df,
    as.data.frame(c(unij_0_dl, unij_0_ol)),
    by = "uid"
)
nrow(unij_0_data_df)

unij_l_data_df <- dplyr::inner_join(
    unij_l_cluster_df,
    as.data.frame(c(unij_l_dl, unij_l_ol)),
    by = "uid"
)
nrow(unij_l_data_df)

saveRDS(lmtb_0_data_df, proc_path("lmtb_0_data_df.rds", TRUE))
saveRDS(lmtb_l_data_df, proc_path("lmtb_l_data_df.rds", TRUE))
saveRDS(unij_0_data_df, proc_path("unij_0_data_df.rds", TRUE))
saveRDS(unij_l_data_df, proc_path("unij_l_data_df.rds", TRUE))
```

```{r}
mtbi_gen_fts_table_hits_t <- read_csv(proc_path("2025_09_22_mtbi_gen_fts_table_hits_t.csv"))
mtbi_gen_long <- na.omit(mtbi_gen_fts_table_hits_t)

lmtb_0_data_df <- readRDS(proc_path("2026_01_21_lmtb_0_data_df.rds"))
lmtb_l_data_df <- readRDS(proc_path("2026_01_21_lmtb_l_data_df.rds"))
unij_0_data_df <- readRDS(proc_path("2026_01_21_unij_0_data_df.rds"))
unij_l_data_df <- readRDS(proc_path("2026_01_21_unij_l_data_df.rds"))
```

```{r}
topologizer <- function(df) {
    df <- data.frame(df)
    df <- metasnf:::numcol_to_numeric(df)
    df <- dummy_non_numeric(dplyr::select(df, -"uid"))
    summary_df <- data.frame(
        "feature" = as.character(),
        "type" = as.character(),
        "summary" = as.character(),
        "c1_mean" = as.numeric(),
        "c2_mean" = as.numeric(),
        "c3_mean" = as.numeric(),
        "c1_c2_es" = as.numeric(),
        "c1_c2_l" = as.numeric(),
        "c1_c2_u" = as.numeric(),
        "c1_c3_es" = as.numeric(),
        "c1_c3_l" = as.numeric(),
        "c1_c3_u" = as.numeric(),
        "c2_c3_es" = as.numeric(),
        "c2_c3_l" = as.numeric(),
        "c2_c3_u" = as.numeric()
    )
    c1 <- df[df$"cluster" == 1, ]
    c2 <- df[df$"cluster" == 2, ]
    c3 <- df[df$"cluster" == 3, ]
    features <- df |>
        dplyr::select(-"cluster") |>
        colnames()
    ###########################################################################
    # Check if features are binary (unique values are 0 and 1) or not
    ###########################################################################
    for (feature in features) {
        f1 <- c1[, feature]
        f2 <- c2[, feature]
        f3 <- c3[, feature]
        means <- c("1" = mean(f1), "2" = mean(f2), "3" = mean(f3))
        full_summary <- paste(
            names(sort(means, decreasing = TRUE)),
            collapse = " > "
        )
        if (is_binary(df[, feature])) {
            sum_1_v_2 <- calc_propes(f1, f2)
            sum_1_v_3 <- calc_propes(f1, f3)
            sum_2_v_3 <- calc_propes(f2, f3)
            type <- "or"
        } else {
            sum_1_v_2 <- calc_des(f1, f2)
            sum_1_v_3 <- calc_des(f1, f3)
            sum_2_v_3 <- calc_des(f2, f3)
            type <- "d"
        }
        summary_df <- rbind(
            summary_df,
            data.frame(
                "feature" = feature,
                "summary" = full_summary,
                "c1" = signif(mean(f1), 3),
                "c2" = signif(mean(f2), 3),
                "c3" = signif(mean(f3), 3),
                "es" = type,
                "c12_es" = sum_1_v_2$"es",
                "c12_l" = sum_1_v_2$"l",
                "c12_u" = sum_1_v_2$"u",
                "c13_es" = sum_1_v_3$"es",
                "c13_l" = sum_1_v_3$"l",
                "c13_u" = sum_1_v_3$"u",
                "c23_es" = sum_2_v_3$"es",
                "c23_l" = sum_2_v_3$"l",
                "c23_u" = sum_2_v_3$"u"
            )
        )
    }
    return(summary_df)
}

concordance_w_mtbi <- function(data_df, n = NULL, iters = 10, procs = 1) {
    if (is.null(n)) {
        n <- nrow(data_df)
    }
    p <- progressr::progressor(steps = iters)
    future::plan(
        future::multisession,
        workers = procs
    )
    res <- future.apply::future_lapply(
        1:iters,
        future.seed = TRUE,
        function(x, p) {
            start <- Sys.time()
            bootstrap_sample <- sample(n, replace = TRUE)
            sampled_df <- data_df[bootstrap_sample, ]
            tops_df <- topologizer(sampled_df)
            gen_tops_df <- generalizable_features(tops_df, compare_fn_a)
            gen_tops_df_long <- gen_tops_df |>
                pivot_longer(
                    cols = -feature,
                    names_to = "comparison",
                    values_to = "order_sample"
                )
            joint_df <- dplyr::left_join(
                mtbi_gen_long, # reference data frame
                gen_tops_df_long, # sampled data frame
                by = c("feature", "comparison")
            ) |>
                dplyr::mutate(
                    match = ifelse(order_sample == order, 1, 0)
                ) |>
                dplyr::filter(!grepl("mtbi", feature))
            p()
            concordance <- sum(joint_df$"match") / nrow(joint_df)
            return(concordance)
        },
        p = p
    )
    future::plan(future::sequential)
    return(unlist(res))
}

concordance_w_mtbi_test <- function(df1, df2, n = NULL, iters = 10, procs = 1) {
    if (is.null(n)) {
        n <- nrow(df1)
    }
    p <- progressr::progressor(steps = iters)
    future::plan(
        future::multisession,
        workers = procs
    )
    res <- future.apply::future_lapply(
        1:iters,
        future.seed = TRUE,
        function(x, p) {
            start <- Sys.time()
            bootstrap_sample <- sample(n, replace = TRUE)
            sampled_df1 <- df1[bootstrap_sample, ]
            sampled_df2 <- df2[bootstrap_sample, ]
            tops_df1 <- topologizer(sampled_df1)
            tops_df2 <- topologizer(sampled_df2)
            gen_tops_df1 <- generalizable_features(tops_df1, compare_fn_a)
            gen_tops_df2 <- generalizable_features(tops_df2, compare_fn_a)
            gen_tops_df_long1 <- gen_tops_df1 |>
                pivot_longer(
                    cols = -feature,
                    names_to = "comparison",
                    values_to = "order_sample"
                )
            gen_tops_df_long2 <- gen_tops_df2 |>
                pivot_longer(
                    cols = -feature,
                    names_to = "comparison",
                    values_to = "order_sample"
                )
            joint_df1 <- dplyr::left_join(
                mtbi_gen_long, # reference data frame
                gen_tops_df_long1, # sampled data frame
                by = c("feature", "comparison")
            ) |>
                dplyr::mutate(
                    match = ifelse(order_sample == order, 1, 0)
                ) |>
                dplyr::filter(!grepl("mtbi", feature))
            joint_df2 <- dplyr::left_join(
                mtbi_gen_long, # reference data frame
                gen_tops_df_long2, # sampled data frame
                by = c("feature", "comparison")
            ) |>
                dplyr::mutate(
                    match = ifelse(order_sample == order, 1, 0)
                ) |>
                dplyr::filter(!grepl("mtbi", feature))
            p()
            concordance1 <- sum(joint_df1$"match") / nrow(joint_df1)
            concordance2 <- sum(joint_df2$"match") / nrow(joint_df2)
            return(concordance2 - concordance1)
        },
        p = p
    )
    future::plan(future::sequential)
    return(unlist(res))
}

set.seed(42)
start <- Sys.time()
progressr::with_progress({
    lmtb_0_pred_conc <- concordance_w_mtbi(lmtb_0_data_df, iters = 1000, procs = 8)
})
lmtb_0_pred_conc
print(Sys.time() - start)
saveRDS(lmtb_0_pred_conc, proc_path("lmtb_0_pred_conc.rds", TRUE))

set.seed(42)
start <- Sys.time()
progressr::with_progress({
    lmtb_l_pred_conc <- concordance_w_mtbi(lmtb_l_data_df, iters = 1000, procs = 8)
})
lmtb_l_pred_conc
print(Sys.time() - start)
saveRDS(lmtb_l_pred_conc, proc_path("lmtb_l_pred_conc.rds", TRUE))
set.seed(42)
start <- Sys.time()
progressr::with_progress({
    unij_0_pred_conc <- concordance_w_mtbi(unij_0_data_df, n = 218, iters = 1000, procs = 8)
})
unij_0_pred_conc
print(Sys.time() - start)
saveRDS(unij_0_pred_conc, proc_path("unij_0_pred_conc.rds", TRUE))
set.seed(42)
start <- Sys.time()
progressr::with_progress({
    unij_l_pred_conc <- concordance_w_mtbi(unij_l_data_df, n = 218, iters = 1000, procs = 8)
})
unij_l_pred_conc
print(Sys.time() - start)
saveRDS(unij_l_pred_conc, proc_path("unij_l_pred_conc.rds", TRUE))
#
# Test style:
set.seed(42)
start <- Sys.time()
progressr::with_progress({
    lmtb_pred_conc_test <- concordance_w_mtbi_test(
        df1 = lmtb_0_data_df, df2 = lmtb_l_data_df,  iters = 1000, procs = 5
    )
})
print(Sys.time() - start)
saveRDS(lmtb_pred_conc_test, proc_path("lmtb_pred_conc_test.rds", TRUE))

lmtb_pred_conc_test <- readRDS(proc_path("2025_10_03_lmtb_pred_conc_test.rds"))

lmtb_pred_conc_test <- readRDS(proc_path("2026_01_21_lmtb_pred_conc_test.rds"))

# [-0.151, 0.111]

# [-15% to 11%]
quantile((100*lmtb_pred_conc_test), c(0.025, 0.975), na.rm = TRUE)

mean(lmtb_pred_conc_test)*100 # -1.6%
```

So we can say that there's no significant difference in how similar the pre-injury/post-injury group is to the baseline mTBI group.

```{r}
lmtb_0_pred_conc <- readRDS(proc_path("2026_01_21_lmtb_0_pred_conc.rds"))
lmtb_l_pred_conc <- readRDS(proc_path("2026_01_21_lmtb_l_pred_conc.rds"))

unij_0_pred_conc <- readRDS(proc_path("2026_01_21_unij_0_pred_conc.rds"))
unij_l_pred_conc <- readRDS(proc_path("2026_01_21_unij_l_pred_conc.rds"))

sims_pre <- na.omit(lmtb_0_pred_conc)
ci_solo_pre <- quantile(sims_pre, probs = c(0.025, 0.975))
round(mean(sims_pre)*100, 1)
round(ci_solo_pre*100, 1)

sims_post <- na.omit(lmtb_l_pred_conc)
ci_solo_post <- quantile(sims_post, probs = c(0.025, 0.975))
round(mean(sims_post)*100, 1)
round(ci_solo_post*100, 1)

mean(na.omit(unij_0_pred_conc)) #69.2
mean(na.omit(unij_l_pred_conc)) #71.0

lmtb_0_conc_data <- data.frame(group = "lmtb_0", x = na.omit(lmtb_0_pred_conc))
lmtb_l_conc_data <- data.frame(group = "lmtb_l", x = na.omit(lmtb_l_pred_conc))
unij_0_conc_data <- data.frame(group = "unij_0", x = na.omit(unij_0_pred_conc))
unij_l_conc_data <- data.frame(group = "unij_l", x = na.omit(unij_l_pred_conc))
```
