# Building a Classifier

## Importing packages

```{r}
library(readr)
library(here)
library(abcdutils)
library(dplyr)
library(caret)
library(xgboost)
library(randomForest)
library(fastDummies)
library(skimr)
library(doParallel)
library(future)
library(future.apply)
library(patchwork)
```

## Establishing file paths

```{r}
input_path <- path_maker(here(paste0("data/abcd/inputs")))
core_path <- path_maker(here(paste0("data/abcd/core")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
model_path <- path_maker(here(paste0("data/abcd/results/models")))

import <- function(path) {
    return(abcd_load(core_path(path)))
}

```

## Preparing baseline concussion sample data for training

### Feature selection

We'll only use features that were both considered generalizable and that are present in uninjured children.
These features are the same as those that were characterized in the matched uninjured group.

```{r}
# Data frame of all features extracted for baseline concussion sample
mtbi_ful_df <- readRDS(proc_path("2025_02_13_mtbi_ful_df.rds"))

# Data frame with generalizable features from baseline solution in long format
mtbi_gen_fts_in_long <- read_csv(
    proc_path("2025_02_13_mtbi_gen_fts_in_long.csv")
)

classifier_fts <- unique(mtbi_gen_fts_in_long$feature) 

# Stripping away mTBI specific features
classifier_fts <- classifier_fts[!grepl("mtbi", classifier_fts)]

# Un-dummying race
classifier_fts[grepl("race_", classifier_fts)] <- "race"

classifier_fts <- unique(classifier_fts)

write_csv(data.frame(classifier_fts), proc_path("classifier_fts.csv", TRUE))
```

The features used for classification are:

1. sex
2. brain_volume
3. cortical_sa
4. household_income
5. pubertal_status_p
6. race
7. activities_last_year
8. private_instruction
9. extracurriculars
10. parent_thought
11. weekday_screentime
12. parent_somatic
13. parent_antisocial
14. parent_withdrawn
15. parent_anxdep
16. parent_aggressive
17. parent_depress
18. parent_anxdisord
19. fmri_cort_subcort_cors
20. parent_hyperactive
21. weekend_screentime
22. parent_avoidant
23. parent_perstr
24. parent_attention
25. family_fight_p
26. family_outdo_p
27. cortical_thickness
28. physical_activity
29. considerate_y
30. same_sex_close_friend
31. family_criticize_p
32. family_throw_p
33. family_hit_p
34. pubertal_status_y
35. helps_hurt_p
36. helps_hurt_y
37. helpful_p
38. family_angry_p
39. school_activities
40. family_peaceful_p
41. family_criticize_y
42. family_peaceful_y
43. age
44. same_sex_friend
45. family_yell_y
46. family_throw_y
47. helpful_y

```{r}
classifier_fts_df <- read_csv(proc_path("2025_02_14_classifier_fts.csv"))

classifier_fts <- classifier_fts_df$"classifier_fts"

# Reducing mtbi_ful_df to only contain the classifier features
mtbi_classification_df <- dplyr::select(
    mtbi_ful_df,
    uid,
    all_of(classifier_fts),
    cluster
)

write_csv(
    mtbi_classification_df,
    proc_path("mtbi_classification_df.csv", TRUE)
)
```

```{r}
# CHECKPOINT
mtbi_classification_df <- read_csv(
    proc_path("2025_02_14_mtbi_classification_df.csv")
)
```

### 80/20 train/test split

```{r}
set.seed(1111)
shuffled_df <- mtbi_classification_df[sample(nrow(mtbi_classification_df)), ]

nrow(mtbi_classification_df) * 0.8

train_classification_df <- shuffled_df[1:349, ]
test_classification_df <- shuffled_df[350:437, ]

write_csv(
    train_classification_df,
    proc_path("train_classification_df.csv", TRUE)
)

write_csv(
    test_classification_df,
    proc_path("test_classification_df.csv", TRUE)
)
```

```{r}
# CHECKPOINT
train_classification_df <- read_csv(
    proc_path("2025_02_17_train_classification_df.csv")
)

test_classification_df <- read_csv(
    proc_path("2025_02_17_test_classification_df.csv")
)
```

### Time-scaling temporally sensitive features

```{r}
# Age
abcd_y_lt <- import("abcd-general/abcd_y_lt.csv")
# Pubertal development scale, youth report
ph_y_pds <- import("physical-health/ph_y_pds.csv")
# Pubertal development scale, parent report
ph_p_pds <- import("physical-health/ph_p_pds.csv")
# Parent report of gender identity
gish_p_gi <- import("gender-identity-sexual-health/gish_p_gi.csv")
# Subcortical volumes (ASEG)
mri_y_smr_vol_aseg <- import("imaging/mri_y_smr_vol_aseg.csv")
# Desikan cortical thicknesses
mri_y_smr_thk_dsk <- import("imaging/mri_y_smr_thk_dsk.csv")
# Desikan cortical surface areas
mri_y_smr_area_dsk <- import("imaging/mri_y_smr_area_dsk.csv")
# Number of friends
mh_y_or <- import("mental-health/mh_y_or.csv")
# Screen time
nt_p_stq <- import("novel-technologies/nt_p_stq.csv")
```

```{r}
train_classification_df <- read_csv(
    proc_path("2025_02_17_train_classification_df.csv")
)

test_classification_df <- read_csv(
    proc_path("2025_02_17_test_classification_df.csv")
)

for (name in colnames(train_classification_df)) {
    print(name)
}

subc_v <- get_subc_v(mri_y_smr_vol_aseg, t = 0)
cort_t <- get_cort_t(mri_y_smr_thk_dsk, t = 0)
cort_sa <- get_cort_sa(mri_y_smr_area_dsk, t = 0)
pubertal_status_p <- get_pubertal_status_p(ph_p_pds, max_value = 3, t = 0)
pubertal_status_y <- get_pubertal_status_y(ph_y_pds, max_value = 3, t = 0)
age <- get_interview_age(abcd_y_lt, t = 0, as_years = FALSE)
screen_time <- get_screen_time(nt_p_stq, t = 0)

subc_v_t2 <- get_subc_v(mri_y_smr_vol_aseg, t = 2)
cort_t_t2 <- get_cort_t(mri_y_smr_thk_dsk, t = 2)
cort_sa_t2 <- get_cort_sa(mri_y_smr_area_dsk, t = 2)
pubertal_status_p_t2 <- get_pubertal_status_p(ph_p_pds, max_value = 4, t = 2)
pubertal_status_y_t2 <- get_pubertal_status_y(ph_y_pds, max_value = 4, t = 2)
age_t2 <- get_interview_age(abcd_y_lt, t = 2, as_years = FALSE)
screen_time_t2 <- get_screen_time(nt_p_stq, t = 2)
```

Temporally sensitive features:

- brain_volume
- cortical_sa
- pubertal_status_p
- age
- weekday_screentime
- weekend_screentime
- cortical_thickness
- pubertal_status_y


```{r}
temporal_df <- metasnf::merge_df_list(
    list(
        subc_v,
        cort_t,
        cort_sa,
        pubertal_status_p,
        pubertal_status_y,
        age,
        screen_time
    ),
    uid = "subjectkey"
)

temporal_df2 <- metasnf::merge_df_list(
    list(
        subc_v_t2,
        cort_t_t2,
        cort_sa_t2,
        pubertal_status_p_t2,
        pubertal_status_y_t2,
        age_t2,
        screen_time_t2
    ),
    uid = "subjectkey"
)

temporal_df <- temporal_df |> dplyr::rename(
    "uid" = "subjectkey",
    "age" = "interview_age",
    "brain_volume" = "smri_vol_scs_wholeb",
    "cortical_thickness" = "smri_thick_cdk_mean",
    "cortical_sa" = "smri_area_cdk_total",
    "weekend_screentime" = "screentime_wknd_hrs",
    "weekday_screentime" = "screentime_wkday_hrs"
)

temporal_df2 <- temporal_df2 |> dplyr::rename(
    "uid" = "subjectkey",
    "age" = "interview_age",
    "brain_volume" = "smri_vol_scs_wholeb",
    "cortical_thickness" = "smri_thick_cdk_mean",
    "cortical_sa" = "smri_area_cdk_total",
    "weekend_screentime" = "screentime_wknd_hrs",
    "weekday_screentime" = "screentime_wkday_hrs"
)

temporal_df$"uid" <- paste0("uid_", temporal_df$"uid")
temporal_df2$"uid" <- paste0("uid_", temporal_df2$"uid")

saveRDS(temporal_df, proc_path("temporal_df.rds", TRUE))
saveRDS(temporal_df2, proc_path("temporal_df2.rds", TRUE))

temporal_df <- readRDS(proc_path("2025_02_17_temporal_df.rds"))

temporal_df <- temporal_df |> 
    dplyr::filter(
        !uid %in% c(
            train_classification_df$"uid",
            test_classification_df$"uid"
        )
    )

scaling_df <- dplyr::bind_rows(
    temporal_df,
    train_classification_df[, colnames(temporal_df)],
    test_classification_df[, colnames(temporal_df)]
)
scale_cols <- colnames(temporal_df)[2:ncol(temporal_df)]
scaling_df[scale_cols] <- sapply(scaling_df[scale_cols], scale)

train_scale_df <- train_classification_df |>
    dplyr::select(-dplyr::all_of(scale_cols)) |>
    dplyr::inner_join(scaling_df, by = "uid") |>
    data.frame()

test_scale_df <- test_classification_df |>
    dplyr::select(-dplyr::all_of(scale_cols)) |>
    dplyr::inner_join(scaling_df, by = "uid") |>
    data.frame()

write_csv(train_scale_df, proc_path("train_scale_df.csv", TRUE))
write_csv(test_scale_df, proc_path("test_scale_df.csv", TRUE))
```

Temporally sensitive features have now been z-scored across all ABCD values for that time point.

```{r}
# CHECKPOINT
train_scale_df <- read_csv(proc_path("2025_02_17_train_scale_df.csv"))
test_scale_df <- read_csv(proc_path("2025_02_17_test_scale_df.csv"))
```

### Final preparatory steps

The `prep_data()` function is used to prepare the data for training by removing the `uid` column, creating dummy variables for the `race` column, and converting certain columns to ordered factors.
The function also standardizes the data if specified.

```{r}
prep_data <- function(df, standardize = FALSE) {
    df <- dplyr::select(df, -"uid")
    df <- dummy_cols(
        df,
        select_columns = "race",
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = TRUE
    )
    ordered_factors <- c(
        "sex",
        "household_income",
        "pubertal_status_p",
        "activities_last_year",
        "private_instruction",
        "extracurriculars",
        "family_fight_p",
        "family_outdo_p",
        "considerate_y",
        "same_sex_close_friend",
        "family_criticize_p",
        "family_throw_p",
        "family_hit_p",
        "pubertal_status_y",
        "helps_hurt_p",
        "helps_hurt_y",
        "helpful_p",
        "family_angry_p",
        "school_activities",
        "family_peaceful_p",
        "family_criticize_y",
        "family_peaceful_y",
        "same_sex_friend",
        "family_yell_y",
        "family_throw_y",
        "helpful_y",
        "race_black",
        "race_hispanic",
        "race_other" 
    )
    df[ordered_factors] <- lapply(df[ordered_factors], as.ordered)
    if (standardize) {
        df[] <- lapply(df, as.numeric)
        df <- as.data.frame(scale(df))
    }
    if ("cluster" %in% colnames(df)) {
        df$"cluster" <- as.factor(df$"cluster")
    }
    return(df)
}
```

## Setting up classifier training

The `unregister_dopar()` function is used to clean up the environment after parallel processing.

```{r}
unregister_dopar <- function() {
  env <- foreach:::.foreachGlobals
  rm(list=ls(name=env), pos=env)
}
```

## Caret CV

`train_control` defines the type of cross-validation (in this case, 5-fold grid-searching) to be used.

```{r}
train_control <- caret::trainControl(
    method = "cv",             # Cross-validation
    number = 5,                # 5-fold CV
    search = "grid",           # Grid search
    verboseIter = TRUE
)
```

## Classifier training

### Random forest

Each model is trained with a nested-CV like process:

1. training subset of the data: hyperparameter grid search over CV to find the best hyperparameters
2. full subset of the data: fixed hyperparameter CV to get an estimate of model performance
3. full subset of the data again: fit the inner nested hyperparameters for final model

For random forest, I vary the following hyperparameters:

- Number of trees
- number of attributes that are randomly selected for the split search when constructing each tree
- limits on the tree depth (for each tree)

```{r}
set.seed(42)

training_data <- prep_data(train_scale_df)

# Hyperparameters
tune_grid <- expand.grid(mtry = c(1:20))
time <- Sys.time()
cl <- makePSOCKcluster(64)
registerDoParallel(cl)
trained_models <- list()
counter <- 0
for (maxnodes in c(5, 10, 15)) {
    for (nodesize in c(1:5)) {
        for (ntree in c(100, 1000, 2000, 3000)) {
            rf_model <- train(
                cluster ~ .,
                data = training_data,
                method = "rf",
                trControl = train_control,
                tuneGrid = tune_grid,
                ntree = ntree,
                maxnodes = maxnodes,
                nodesize = nodesize
            )
            trained_models[[length(trained_models) + 1]] <- rf_model
            names(trained_models)[[length(trained_models)]] <- paste0(
                "maxnodes_", maxnodes,
                "nodesize_", nodesize,
                "ntree_", ntree
            )
            counter <- counter + 1
            print(paste0(round(counter / (3*5*4) * 100, 2), "% complete..."))
        }
    }
}
stopCluster(cl)
unregister_dopar()
print(Sys.time() - time)
saveRDS(trained_models, model_path("rf_models.rds", TRUE))
rf_models <- readRDS(model_path("2025_02_17_rf_models.rds"))
```

### SVM

```{r}
set.seed(42)

svm_tune_grid_1 <- expand.grid(
    sigma = c(0.001, 0.01, 0.1, 0.5, 1),
    C = c(0.1, 1, 10, 100, 1000)
)

svm_model <- train(
  cluster ~ .,                # Formula for the model
  data = prep_data(train_scale_df, TRUE),                # Your dataset
  method = "svmRadial",       # Using radial kernel
  trControl = train_control,  # Cross-validation settings
  tuneGrid = svm_tune_grid_1        # Hyperparameter grid to tune
)

print(svm_model)

svm_tune_grid_2 <- expand.grid(
    sigma = c(0.01, 0.05, 0.1, 0.25, 0.5, 0.75, 1),
    C = c(0.1, 0.5, 1, 2, 5, 10, 25, 50, 100, 200, 400, 600, 750, 1000)
)

svm_model2 <- train(
  cluster ~ .,                # Formula for the model
  data = prep_data(train_scale_df, TRUE),                # Your dataset
  method = "svmRadial",       # Using radial kernel
  trControl = train_control,  # Cross-validation settings
  tuneGrid = svm_tune_grid_2        # Hyperparameter grid to tune
)

svm_tune_grid_2 <- expand.grid(
    sigma = c(0.01, 0.05, 0.1, 0.25, 0.5, 0.75, 1),
    C = c(0.1, 0.5, 1, 2, 5, 10, 25, 50, 100, 200, 400, 600, 750, 1000)
)

svm_model2 <- train(
  cluster ~ .,                # Formula for the model
  data = prep_data(train_scale_df, TRUE),                # Your dataset
  method = "svmRadial",       # Using radial kernel
  trControl = train_control,  # Cross-validation settings
  tuneGrid = svm_tune_grid_2        # Hyperparameter grid to tune
)

saveRDS(svm_model2, model_path("svm_model.rds", TRUE))
svm_model <- readRDS(model_path("2025_02_17_svm_model.rds"))
```

### K-NN

```{r}
# Train the KNN model
knn_model <- train(
  cluster ~ ., 
  data = prep_data(train_scale_df, TRUE), 
  method = "knn", 
  trControl = train_control, 
  tuneLength = 130  # Tuning k (number of neighbors)
)

saveRDS(knn_model, model_path("knn_subtype_classifier_1.rds", TRUE))
knn_model <- readRDS(model_path("2025_02_17_knn_subtype_classifier_1.rds"))
```

### Comparisons

```{r}
knn_model <- readRDS(model_path("2025_02_17_knn_subtype_classifier_1.rds"))
rf_models <- readRDS(model_path("2025_02_17_rf_models.rds"))
svm_model <- readRDS(model_path("2025_02_17_svm_model.rds"))

classifier_list <- rf_models
classifier_list[[61]] <- svm_model
classifier_list[[62]] <- knn_model

names(classifier_list)[[61]] <- "svm"
names(classifier_list)[[62]] <- "knn"

png(
    filename = fig_path("resampled_classifier_models_round_1.png", TRUE),
    width = 800,
    height = 1500,
    res = 100
)
print(dotplot(resamples(classifier_list)))
dev.off()

# About 72% max
rf_accuracies <- lapply(
    rf_models,
    function(x) {
        max(x$"results"$"Accuracy")
    }
) |> unlist()

max(rf_accuracies)

rf_accuracy_dfs <- lapply(
    names(rf_models),
    function(x) {
        hyperparameters <- as.numeric(unlist(regmatches(x, gregexpr("\\d+", x))))
        results <- rf_models[[x]]$results
        results$"max_nodes" <- hyperparameters[[1]]
        results$"node_size" <- hyperparameters[[2]]
        results$"n_trees" <- hyperparameters[[3]]
        results$"uid" <- x
        return(results)
    }
)

rf_accuracy_df <- do.call(rbind, rf_accuracy_dfs)

tuning_plot <- function(df, param) {
    plot <- ggplot(
        df,
        aes(x = .data[[param]], y = .data[["Accuracy"]]),
    ) +
    geom_jitter(alpha = 0.2) +
    theme_bw()
    return(plot)
}

set.seed(42)
n_trees_plot <- tuning_plot(rf_accuracy_df, "n_trees")
max_nodes_plot <- tuning_plot(rf_accuracy_df, "max_nodes")
node_size_plot <- tuning_plot(rf_accuracy_df, "node_size")
mtry_plot <- tuning_plot(rf_accuracy_df, "mtry")

tuning_plots <- wrap_plots(
    list(n_trees_plot, max_nodes_plot, node_size_plot, mtry_plot),
    ncol = 2
)

tuning_plots

ggsave(
    fig_path("tuning_plots.png", TRUE),
    tuning_plots,
    width = 10,
    height = 10,
    dpi = 300
)
```

Initial examinations show random forest as the top performing model.
Tuning plots suggest there is room for further improvement.

### Random forest - Second round of training

```{r}
set.seed(42)

training_data <- prep_data(train_scale_df)

# Hyperparameters
tune_grid <- expand.grid(mtry = c(1:10))
time <- Sys.time()
cl <- makePSOCKcluster(64)
registerDoParallel(cl)
trained_models <- list()
counter <- 0
for (maxnodes in c(15, 25, 30, 35, 40, 50)) {
    for (nodesize in c(1:5)) {
        for (ntree in c(100, 1000, 2000, 3000)) {
            rf_model <- train(
                cluster ~ .,
                data = training_data,
                method = "rf",
                trControl = train_control,
                tuneGrid = tune_grid,
                ntree = ntree,
                maxnodes = maxnodes,
                nodesize = nodesize
            )
            trained_models[[length(trained_models) + 1]] <- rf_model
            names(trained_models)[[length(trained_models)]] <- paste0(
                "maxnodes_", maxnodes,
                "nodesize_", nodesize,
                "ntree_", ntree
            )
            counter <- counter + 1
            print(paste0(round(counter / (4*5*4) * 100, 2), "% complete..."))
        }
    }
}
stopCluster(cl)
unregister_dopar()
print(Sys.time() - time)

saveRDS(trained_models, model_path("rf_models_2.rds", TRUE))

rf_models_2 <- readRDS(model_path("2025_02_17_rf_models_2.rds"))

rf_accuracy_dfs2 <- lapply(
    names(rf_models_2),
    function(x) {
        hyperparameters <- as.numeric(unlist(regmatches(x, gregexpr("\\d+", x))))
        results <- rf_models_2[[x]]$results
        results$"max_nodes" <- hyperparameters[[1]]
        results$"node_size" <- hyperparameters[[2]]
        results$"n_trees" <- hyperparameters[[3]]
        results$"uid" <- x
        return(results)
    }
)

rf_accuracy_df2 <- do.call(rbind, rf_accuracy_dfs2)

n_trees_plot2 <- tuning_plot(rf_accuracy_df2, "n_trees")
max_nodes_plot2 <- tuning_plot(rf_accuracy_df2, "max_nodes")
node_size_plot2 <- tuning_plot(rf_accuracy_df2, "node_size")
mtry_plot2 <- tuning_plot(rf_accuracy_df2, "mtry")

tuning_plots2 <- wrap_plots(
    list(n_trees_plot2, max_nodes_plot2, node_size_plot2, mtry_plot2),
    ncol = 2
)

tuning_plots2

rf_models_2_accs <- rf_models_2 |> lapply(
    function(x) max(x$results$Accuracy)
) |> unlist()

rf_models_2_accs[rf_models_2_accs == max(rf_models_2_accs)]

rf_sorted <- rf_accuracy_df2 |> 
    dplyr::select(-Kappa, -KappaSD) |>
    dplyr::arrange(-Accuracy)

rf_sorted[3, ]

rf_models_2$"maxnodes_35nodesize_4ntree_1000"$"finalModel"
```

Best model seemed to have mtry 9, max nodes 25, node size 1, n trees 1000.
But to be safe, I'll lean on one witha slightly larger node size that is still 72% acc (just as the top one is):
mtry of 8, max nodes of 35, node size of 4, n tree of 1000.

        OOB estimate of  error rate: 31.52%
Confusion matrix:
   1  2  3 class.error
1 70 23 21   0.3859649
2  9 98 16   0.2032520
3 16 25 71   0.3660714

### Training on full data set

```{r}
set.seed(42)

model <- randomForest(
    cluster ~ .,
    data = prep_data(train_scale_df),
    mtry = 8,
    ntree = 1000,
    maxnodes = 35,
    nodesize = 4
)

saveRDS(model, model_path("rf_training_subtype_classifier.rds", TRUE))

rf_training_subtype_classifier <- readRDS(model_path("2025_02_17_rf_training_subtype_classifier.rds"))

predictions <- predict(
    rf_training_subtype_classifier,
    newdata = prep_data(test_scale_df)
)

# Model acc on test data: 76.1%
mean(predictions == prep_data(test_scale_df)$cluster)

confusionMatrix(predictions, prep_data(test_scale_df)$"cluster")
```

          Reference
Prediction  1  2  3
         1 17  3  0
         2  7 29  2
         3  7  2 21

Overall Statistics

               Accuracy : 0.7614
                 95% CI : (0.6586, 0.8458)
    No Information Rate : 0.3864
    P-Value [Acc > NIR] : 9.232e-13

                  Kappa : 0.6406

 Mcnemar's Test P-Value : 0.03511

```{r}
set.seed(42)
full_classification_df <- rbind(train_scale_df, test_scale_df)

full_model <- randomForest(
    cluster ~ .,
    data = prep_data(full_classification_df),
    mtry = 8,
    ntree = 1000,
    maxnodes = 35,
    nodesize = 4
)

saveRDS(full_model, model_path("subtype_classifier.rds", TRUE))
subtype_classifier <- readRDS(model_path("2025_02_17_subtype_classifier.rds"))
```

### Variable importances

```{r}
var_imp_df <- as.data.frame(importance(subtype_classifier))
var_imp_df$"feature" <- rownames(var_imp_df)
write_csv(var_imp_df, proc_path("var_imp_df.csv", TRUE))
var_imp_df <- read_csv(proc_path("2025_02_17_var_imp_df.csv"))

var_imp_df

# Create a ggplot for variable importance
var_imp_plot <- ggplot(
    var_imp_df,
    aes(
        x = reorder(feature, -MeanDecreaseGini),
        y = MeanDecreaseGini
    )
) +
    geom_bar(stat = "identity", fill = "darkgray") +
    labs(
        title = "Variable Importance Plot",
        x = "Variables",
        y = "Mean Decrease in Gini"
    ) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))

var_imp_plot

ggsave(
    plot = var_imp_plot,
    fig_path("var_imp_plot.png", TRUE),
    width = 7,
    height = 4
)
```
