# Building a Classifier

## Importing packages and establishing file paths

```{r}
library(readr)
library(here)
library(abcdutils)
library(dplyr)
library(caret)
library(xgboost)
library(randomForest)
library(fastDummies)
library(skimr)
library(doParallel)
library(future)
library(future.apply)
library(progressr)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
model_path <- path_maker(here(paste0("data/abcd/results/models")))
```

## Preprocessing

```{r}
# Data to build classifier from
mtbi_ful_df <- readRDS(proc_path("2025_02_13_mtbi_ful_df.rds"))
```

So we'll only want to use features that were both considered generalizable and that are present in uninjured children.
These features are the same as those that were characterized in the matched uninjured group.

```{r}
#mtbi_gen_fts_in <- read_csv(proc_path("2024_11_07_mtbi_gen_fts_in.csv"))

mtbi_gen_fts_in <- read_csv(proc_path("2025_02_13_mtbi_gen_fts_in.csv"))
mtbi_gen_fts_in_long <- read_csv(proc_path("2025_02_13_mtbi_gen_fts_in_long.csv"))

classifier_fts <- unique(mtbi_gen_fts_in_long$feature) 
classifier_fts <- classifier_fts[!grepl("mtbi", classifier_fts)]
classifier_fts[grepl("race_", classifier_fts)] <- "race"
classifier_fts <- unique(classifier_fts)

write_csv(data.frame(classifier_fts), proc_path("classifier_fts.csv", TRUE))
```

```{r}
classifier_fts <- read_csv(proc_path("2025_02_14_classifier_fts.csv"))$"classifier_fts"

mtbi_classification_df <- dplyr::select(
    mtbi_ful_df,
    uid,
    cluster,
    all_of(classifier_fts)
)

mtbi_classification_df <- mtbi_classification_df |>
    relocate(cluster, .after = last_col())

write_csv(mtbi_classification_df, proc_path("mtbi_classification_df.csv", TRUE))
```

```{r}
mtbi_classification_df <- read_csv(proc_path("2025_02_14_mtbi_classification_df.csv"))
```


```{r}
# Train/test split
set.seed(1111)
shuffled_df <- mtbi_classification_df[sample(nrow(mtbi_classification_df)), ]

nrow(mtbi_classification_df) * 0.8

train_classification_df <- shuffled_df[1:349, ]
test_classification_df <- shuffled_df[349: 437, ]

write_csv(train_classification_df, proc_path("train_classification_df.csv", TRUE))
write_csv(test_classification_df, proc_path("test_classification_df.csv", TRUE))
```

```{r}
# checkpoint
train_classification_df <- read_csv(proc_path("2025_02_14_train_classification_df.csv"))
test_classification_df <- read_csv(proc_path("2025_02_14_test_classification_df.csv"))
```

## Function to prep training data

```{r}
# checkpoint
prep_data <- function(df, standardize = FALSE) {
    df <- dplyr::select(df, -"uid")
    df <- dummy_cols(
        df,
        select_columns = "race",
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = TRUE
    )
    ordered_factors <- c(
        "sex",
        "household_income",
        "pubertal_status_p",
        "activities_last_year",
        "private_instruction",
        "extracurriculars",
        "family_fight_p",
        "family_outdo_p",
        "considerate_y",
        "same_sex_close_friend",
        "family_criticize_p",
        "family_throw_p",
        "family_hit_p",
        "pubertal_status_y",
        "helps_hurt_p",
        "helps_hurt_y",
        "helpful_p",
        "family_angry_p",
        "school_activities",
        "family_peaceful_p",
        "family_criticize_y",
        "family_peaceful_y",
        "same_sex_friend",
        "family_yell_y",
        "family_throw_y",
        "helpful_y",
        "race_black",
        "race_hispanic",
        "race_other" 
    )
    df[ordered_factors] <- lapply(df[ordered_factors], as.ordered)
    if (standardize) {
        df[] <- lapply(df, as.numeric)
        df <- as.data.frame(scale(df))
    }
    if ("cluster" %in% colnames(df)) {
        df$"cluster" <- as.factor(df$"cluster")
    }
    return(df)
}

unregister_dopar <- function() {
  env <- foreach:::.foreachGlobals
  rm(list=ls(name=env), pos=env)
}
```

## Caret CV

```{r}
# checkpoint
train_control <- caret::trainControl(
    method = "cv",             # Cross-validation
    number = 5,                # 5-fold CV
    search = "grid",           # Grid search
    verboseIter = TRUE
)
```

## Hyperparameter tuning

### Random forest

Each model is trained with a nested-CV like process:

1. training subset of the data: hyperparameter grid search over CV to find the best hyperparameters
2. full subset of the data: fixed hyperparameter CV to get an estimate of model performance
3. full subset of the data again: fit the inner nested hyperparameters for final model

For random forest, I vary the following hyperparameters:

- Number of trees
- number of attributes that are randomly selected for the split search when constructing each tree
- limits on the tree depth (for each tree)

```{r}
set.seed(42)

training_data <- prep_data(train_classification_df)

# Hyperparameters
tune_grid <- expand.grid(mtry = c(1:20))
time <- Sys.time()
cl <- makePSOCKcluster(64)
registerDoParallel(cl)
trained_models <- list()
counter <- 0
for (maxnodes in c(5, 10, 15)) {
    for (nodesize in c(1:5)) {
        for (ntree in c(100, 1000, 2000, 3000)) {
            rf_model <- train(
                cluster ~ .,
                data = training_data,
                method = "rf",
                trControl = train_control,
                tuneGrid = tune_grid,
                ntree = ntree,
                maxnodes = maxnodes,
                nodesize = nodesize
            )
            trained_models[[length(trained_models) + 1]] <- rf_model
            names(trained_models)[[length(trained_models)]] <- paste0(
                "maxnodes_", maxnodes,
                "nodesize_", nodesize,
                "ntree_", ntree
            )
            counter <- counter + 1
            print(paste0(round(counter / (3*5*4) * 100, 2), "% complete..."))
        }
    }
}
stopCluster(cl)
unregister_dopar()
print(Sys.time() - time)
saveRDS(trained_models, model_path("rf_models.rds", TRUE))
rf_models <- readRDS(model_path("2025_02_14_rf_models.rds"))
```

### SVM

```{r}
set.seed(42)

svm_tune_grid_1 <- expand.grid(
    sigma = c(0.001, 0.01, 0.1, 0.5, 1),
    C = c(0.1, 1, 10, 100, 1000)
)

svm_model <- train(
  cluster ~ .,                # Formula for the model
  data = prep_data(train_classification_df, TRUE),                # Your dataset
  method = "svmRadial",       # Using radial kernel
  trControl = train_control,  # Cross-validation settings
  tuneGrid = svm_tune_grid_1        # Hyperparameter grid to tune
)

print(svm_model)

svm_tune_grid_2 <- expand.grid(
    sigma = c(0.01, 0.05, 0.1, 0.25, 0.5, 0.75, 1),
    C = c(0.1, 0.5, 1, 2, 5, 10, 25, 50, 100, 200, 400, 600, 750, 1000)
)

svm_model2 <- train(
  cluster ~ .,                # Formula for the model
  data = prep_data(train_classification_df, TRUE),                # Your dataset
  method = "svmRadial",       # Using radial kernel
  trControl = train_control,  # Cross-validation settings
  tuneGrid = svm_tune_grid_2        # Hyperparameter grid to tune
)


svm_tune_grid_2 <- expand.grid(
    sigma = c(0.01, 0.05, 0.1, 0.25, 0.5, 0.75, 1),
    C = c(0.1, 0.5, 1, 2, 5, 10, 25, 50, 100, 200, 400, 600, 750, 1000)
)

svm_model2 <- train(
  cluster ~ .,                # Formula for the model
  data = prep_data(train_classification_df, TRUE),                # Your dataset
  method = "svmRadial",       # Using radial kernel
  trControl = train_control,  # Cross-validation settings
  tuneGrid = svm_tune_grid_2        # Hyperparameter grid to tune
)

saveRDS(svm_model2, model_path("svm_model.rds", TRUE))
svm_model <- readRDS(model_path("2025_02_14_svm_model.rds"))
```

### XGBoost

```{r}
#xgb_tune_grid <- expand.grid(
#  nrounds = c(50, 100, 200),
#  max_depth = c(4, 6, 8),
#  eta = c(0.01, 0.1, 0.2),
#  gamma = c(0, 0.25, 0.5),
#  colsample_bytree = c(0.6, 0.8, 1),
#  min_child_weight = c(1, 5),
#  subsample = c(0.5, 0.75, 1)
#)
#
#xgb_model <- train(
#    cluster ~ .,
#    data = prep_data(train_classification_df),
#    method = "xgbTree",
#    trControl = train_control,
#    tuneGrid = xgb_tune_grid
#)
#
#saveRDS(xgb_model, model_path("xgb_subtype_classifier_1.rds", TRUE))
#xgb_model <- readRDS(model_path("2024_11_11_xgb_subtype_classifier_1.rds"))
```

### K-NN

```{r}
# Train the KNN model
knn_model <- train(
  cluster ~ ., 
  data = prep_data(train_classification_df, TRUE), 
  method = "knn", 
  trControl = train_control, 
  tuneLength = 130  # Tuning k (number of neighbors)
)

saveRDS(knn_model, model_path("knn_subtype_classifier_1.rds", TRUE))
knn_model <- readRDS(model_path("2025_02_14_knn_subtype_classifier_1.rds"))
```

### Comparisons

```{r}
#xgb_model <- readRDS(model_path("2024_11_11_xgb_subtype_classifier_1.rds"))
knn_model <- readRDS(model_path("2025_02_14_knn_subtype_classifier_1.rds"))
rf_models <- readRDS(model_path("2025_02_14_rf_models.rds"))
svm_model <- readRDS(model_path("2025_02_14_svm_model.rds"))

classifier_list <- rf_models
classifier_list[[61]] <- svm_model
classifier_list[[62]] <- knn_model

names(classifier_list)[[61]] <- "svm"
names(classifier_list)[[62]] <- "knn"

# HERE - 2025 -  02 - 14
dotplot(resamples(classifier_list))

# About 77.85% max
rf_accuracies <- lapply(
    rf_models,
    function(x) {
        max(x$"results"$"Accuracy")
    }
) |> unlist()

max(rf_accuracies)

rf_maccuracies <- lapply(
    rf_models,
    function(x) {
        mean(x$"results"$"Accuracy")
    }
) |> unlist()

plot(rf_accuracies, rf_maccuracies)

which(rf_accuracies == max(rf_accuracies))
which(rf_maccuracies == max(rf_maccuracies))

rf_accuracy_dfs <- lapply(
    names(rf_models),
    function(x) {
        hyperparameters <- as.numeric(unlist(regmatches(x, gregexpr("\\d+", x))))
        results <- rf_models[[x]]$results
        results$"max_nodes" <- hyperparameters[[1]]
        results$"node_size" <- hyperparameters[[2]]
        results$"n_trees" <- hyperparameters[[3]]
        results$"uid" <- x
        return(results)
    }
)

rf_accuracy_df <- do.call(rbind, rf_accuracy_dfs)

rf_accuracy_df |>
    ggplot(
        aes(x = n_trees, y = Accuracy)
    ) +
    geom_jitter(alpha = 0.2)

# more than 15 seems clearly better
rf_accuracy_df |>
    ggplot(
        aes(x = max_nodes, y = Accuracy)
    ) +
    geom_jitter(alpha = 0.2)

rf_accuracy_df |>
    ggplot(
        aes(x = node_size, y = Accuracy)
    ) +
    geom_jitter(alpha = 0.2)

# Around 5 seems good?
rf_accuracy_df |>
    ggplot(
        aes(x = mtry, y = Accuracy)
    ) +
    geom_jitter(alpha = 0.2)

rf_accuracy_df |>
    ggplot(
        aes(x = n_trees, y = Accuracy, group = uid)
    ) +
    geom_line(alpha = 0.2) +
    geom_ribbon(aes(ymin = Accuracy - AccuracySD, ymax = Accuracy + AccuracySD), alpha = 0.01)

rf_accuracy_df |>
    ggplot(
        aes(x = max_nodes, y = Accuracy, group = uid)
    ) +
    geom_jitter(alpha = 0.2)


arrange(rf_accuracy_df, -Accuracy)[1:20, ]

rf_models[[1]]$results |>
    ggplot(
        aes(x = mtry, y = Accuracy)
    ) +
    geom_line() +
    geom_ribbon(aes(ymin = Accuracy - AccuracySD, ymax = Accuracy + AccuracySD), alpha = 0.1)


max(as.numeric(rf_accuracies))

svm_model

resamples(
    list(
        "xgb" = xgb_model,
        "svm" = svm_model,
        "rf" = rf_models[[1]],
        "knn" = knn_model
    )
) |> dotplot()

```

### Random forest - Second round of training

```{r}
set.seed(42)

training_data <- prep_data(train_classification_df)

# Hyperparameters
tune_grid <- expand.grid(mtry = c(1:10))
time <- Sys.time()
cl <- makePSOCKcluster(64)
registerDoParallel(cl)
trained_models <- list()
counter <- 0
for (maxnodes in c(13, 15, 20, 25)) {
    for (nodesize in c(1:5)) {
        for (ntree in c(100, 1000, 2000, 3000)) {
            rf_model <- train(
                cluster ~ .,
                data = training_data,
                method = "rf",
                trControl = train_control,
                tuneGrid = tune_grid,
                ntree = ntree,
                maxnodes = maxnodes,
                nodesize = nodesize
            )
            trained_models[[length(trained_models) + 1]] <- rf_model
            names(trained_models)[[length(trained_models)]] <- paste0(
                "maxnodes_", maxnodes,
                "nodesize_", nodesize,
                "ntree_", ntree
            )
            counter <- counter + 1
            print(paste0(round(counter / (4*5*4) * 100, 2), "% complete..."))
        }
    }
}
stopCluster(cl)
unregister_dopar()
print(Sys.time() - time)

saveRDS(trained_models, model_path("rf_models_2.rds", TRUE))
#rf_models_2 <- readRDS(model_path("2024_11_12_rf_models_2.rds"))
rf_models_2 <- readRDS(model_path("2025_02_15_rf_models_2.rds"))

rf_models_2_accs <- rf_models_2 |> lapply(
    function(x) max(x$results$Accuracy)
) |> unlist()

rf_models_2_accs[rf_models_2_accs == max(rf_models_2_accs)]

# Still looks like the max maxnodes value (25) gave best results.
# I'll search again now across 30 to 40.

rf_models |> lapply(
    function(x) max(x$results$Accuracy)
) |> unlist() |> max()


# Hyperparameters
tune_grid <- expand.grid(mtry = c(1:10))
time <- Sys.time()
cl <- makePSOCKcluster(64)
registerDoParallel(cl)
trained_models <- list()
counter <- 0
for (maxnodes in c(30, 35, 40)) {
    for (nodesize in c(1:5)) {
        for (ntree in c(100, 1000, 2000, 3000)) {
            rf_model <- train(
                cluster ~ .,
                data = training_data,
                method = "rf",
                trControl = train_control,
                tuneGrid = tune_grid,
                ntree = ntree,
                maxnodes = maxnodes,
                nodesize = nodesize
            )
            trained_models[[length(trained_models) + 1]] <- rf_model
            names(trained_models)[[length(trained_models)]] <- paste0(
                "maxnodes_", maxnodes,
                "nodesize_", nodesize,
                "ntree_", ntree
            )
            counter <- counter + 1
            print(paste0(round(counter / (4*5*4) * 100, 2), "% complete..."))
        }
    }
}
stopCluster(cl)
unregister_dopar()
print(Sys.time() - time)

saveRDS(trained_models, model_path("rf_models_3.rds", TRUE))

rf_models_3 <- readRDS(model_path("2025_02_15_rf_models_3.rds"))

rf_models_3_accs <- rf_models_3 |> lapply(
    function(x) max(x$results$Accuracy)
) |> unlist()

# Best one so far!
rf_models_3_accs[rf_models_3_accs == max(rf_models_3_accs)]
```


### Second round of comparisons

```{r}
rf_models <- readRDS(model_path("2025_02_14_rf_models.rds"))
rf_models_3 <- readRDS(model_path("2025_02_15_rf_models_3.rds"))

rf_models_3 |> resamples() |> dotplot()

rf_accuracy_dfs_3 <- lapply(
    names(rf_models_3),
    function(x) {
        hyperparameters <- as.numeric(unlist(regmatches(x, gregexpr("\\d+", x))))
        results <- rf_models_3[[x]]$results
        results$"max_nodes" <- hyperparameters[[1]]
        results$"node_size" <- hyperparameters[[2]]
        results$"n_trees" <- hyperparameters[[3]]
        results$"uid" <- x
        return(results)
    }
)

rf_accuracy_df <- do.call(rbind, rf_accuracy_dfs_3)

rf_accuracy_df |>
    ggplot(
        aes(x = n_trees, y = Accuracy)
    ) +
    geom_jitter(alpha = 0.8) +
    theme_bw()

rf_accuracy_df |>
    ggplot(
        aes(x = max_nodes, y = Accuracy)
    ) +
    geom_jitter(alpha = 0.8) +
    theme_bw()

rf_accuracy_df |>
    ggplot(
        aes(x = node_size, y = Accuracy)
    ) +
    geom_jitter(alpha = 0.8) +
    theme_bw()

rf_accuracy_df |>
    ggplot(
        aes(x = mtry, y = Accuracy)
    ) +
    geom_jitter(alpha = 0.8) +
    theme_bw()

rf_accuracy_df |>
    arrange(-Accuracy) |>
    head()

rf_models_3$"maxnodes_35nodesize_3ntree_1000"$"finalModel"
```

Best model seemed to have mtry 6, max nodes 40, node size 1, n trees 100.
But I'll pick the best based on also having a decent n_trees and node_size and reduced max_nodes:
mtry of 6, max nodes of 35, node size of 3, n tree of 1000.

        OOB estimate of  error rate: 31.81%
Confusion matrix:
   1  2  3 class.error
1 71 22 21   0.3771930
2 14 96 13   0.2195122
3 15 26 71   0.3660714

### Training on full data set

```{r}
set.seed(42)

model <- randomForest(
    cluster ~ .,
    data = prep_data(train_classification_df),
    mtry = 6,
    ntree = 1000,
    maxnodes = 35,
    nodesize = 3
)

saveRDS(model, model_path("rf_training_subtype_classifier.rds", TRUE))

rf_training_subtype_classifier <- readRDS(model_path("2025_02_16_rf_training_subtype_classifier.rds"))

predictions <- predict(
    rf_training_subtype_classifier,
    newdata = prep_data(test_classification_df)
)

# Model acc on test data: 75.28%
mean(predictions == prep_data(test_classification_df)$cluster)

confusionMatrix(predictions, prep_data(test_classification_df)$"cluster")
```

          Reference
Prediction  1  2  3
         1 16  2  0
         2  9 30  2
         3  7  2 21

Overall Statistics

               Accuracy : 0.7528
                 95% CI : (0.65, 0.8381)
    No Information Rate : 0.382
    P-Value [Acc > NIR] : 1.264e-12

                  Kappa : 0.6278

 Mcnemar's Test P-Value : 0.009506

Statistics by Class:

                     Class: 1 Class: 2 Class: 3
Sensitivity            0.5000   0.8824   0.9130
Specificity            0.9649   0.8000   0.8636
Pos Pred Value         0.8889   0.7317   0.7000
Neg Pred Value         0.7746   0.9167   0.9661
Prevalence             0.3596   0.3820   0.2584
Detection Rate         0.1798   0.3371   0.2360
Detection Prevalence   0.2022   0.4607   0.3371
Balanced Accuracy      0.7325   0.8412   0.8883

```{r}
set.seed(42)
full_classification_df <- rbind(train_classification_df, test_classification_df)

full_model <- randomForest(
    cluster ~ .,
    data = prep_data(full_classification_df),
    mtry = 6,
    ntree = 1000,
    maxnodes = 35,
    nodesize = 3
)

full_model

saveRDS(full_model, model_path("subtype_classifier.rds", TRUE))

subtype_classifier <- readRDS(model_path("2025_02_16_subtype_classifier.rds"))
```

### Variable importances

```{r}
var_imp_df <- as.data.frame(importance(subtype_classifier))
var_imp_df$"feature" <- rownames(var_imp_df)
write_csv(var_imp_df, proc_path("var_imp_df.csv", TRUE))
var_imp_df <- read_csv(proc_path("2025_02_16_var_imp_df.csv"))

var_imp_df

# Create a ggplot for variable importance
var_imp_plot <- ggplot(
    var_imp_df,
    aes(
        x = reorder(feature, MeanDecreaseGini),
        y = MeanDecreaseGini
    )
) +
    geom_bar(stat = "identity", fill = "darkgray") +
    labs(
        title = "Variable Importance Plot",
        x = "Variables",
        y = "Mean Decrease in Gini"
    ) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))

var_imp_plot

ggsave(
    plot = var_imp_plot,
    fig_path("var_imp_plot.png", TRUE),
    width = 7,
    height = 4
)
```
