# Matching

This chapter contains:

1. Derivation of subtypes from a variety of matched uninjured groups
2. Comparison of those subtypes with the mTBI baseline solution

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)
library(MatchIt)
library(tibble)
library(ggplot2)
library(fastDummies)
library(dplyr)
library(tidyr)
library(xtable)
library(patchwork)
library(ComplexHeatmap)

input_path   <- path_maker(here(paste0("data/abcd/inputs")))
proc_path    <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path     <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path     <- path_maker(here(paste0("data/abcd/subjects")))
model_path   <- path_maker(here(paste0("data/abcd/results/models")))
unij_ns_subs <- readRDS(sub_path("2025_09_11_unij_no_sibs_subs.rds"))
```

## Importing data

```{r}
all_dls_h_ns <- readRDS(proc_path("2025_09_11_all_dls_h_no_sibs.rds"))

mtbi_dl_1 <- readRDS(input_path("2025_09_15_mtbi_dl_1.rds"))
mtbi_ol_1 <- readRDS(input_path("2025_09_15_mtbi_ol_1.rds"))
mtbi_top_solution <- readRDS(proc_path("2025_09_16_mtbi_top_solution.rds"))

names(all_dls_h_ns)

unij_dl_u1 <- all_dls_h_ns$"unij_all_u_dls"$"imp_1"
unij_dl_p1 <- all_dls_h_ns$"unij_all_p_dls"$"imp_1"
unij_ol_u1 <- all_dls_h_ns$"unij_all_u_ols"$"imp_1"
unij_ol_p1 <- all_dls_h_ns$"unij_all_p_ols"$"imp_1"
```

## Matching

Finding matched uninjured controls for each mtbi subject based on a variety of variables.
Matching will be done based on the first imputed dataset of the baseline data.

```{r}
# mTBI group, first imputation
mtbi_matching_df <- as.data.frame(c(mtbi_dl_1, mtbi_ol_1))

# Uninjured group, first solo imputation
unij_matching_df_u1 <- as.data.frame(c(unij_dl_u1, unij_ol_u1))

# Uninjured group, first pooled imputation
unij_matching_df_p1 <- as.data.frame(c(unij_dl_p1, unij_ol_p1))

# Labeling if each group was or was not mTBI
mtbi_matching_df$"mtbi" <- 1
unij_matching_df_u1$"mtbi" <- 0
unij_matching_df_p1$"mtbi" <- 0

# Restricting mTBI data frame to only columns shared with uninjured
mtbi_matching_df <- dplyr::select(
    mtbi_matching_df,
    colnames(unij_matching_df_u1)
)

# Concatenating mTBI and uninjured data frames for matching
matching_df_u1 <- rbind(mtbi_matching_df, unij_matching_df_u1)
matching_df_p1 <- rbind(mtbi_matching_df, unij_matching_df_p1)
```


```{r}
# Creating parent psych matching variable
matching_df_u1$"total_parent_psych" <- matching_df_u1 |>
    dplyr::select(dplyr::starts_with("parent")) |>
    rowSums()
matching_df_p1$"total_parent_psych" <- matching_df_p1 |>
    dplyr::select(dplyr::starts_with("parent")) |>
    rowSums()

# Creating outcome matching variable
matching_df_u1$"total_impairments" <- matching_df_u1 |>
    dplyr::select(dplyr::starts_with("cbcl"), dplyr::starts_with("sds")) |>
    rowSums()
matching_df_p1$"total_impairments" <- matching_df_p1 |>
    dplyr::select(dplyr::starts_with("cbcl"), dplyr::starts_with("sds")) |>
    rowSums()
```

I investigate the following matching schemes:

1. Demographic matching (household income, race, sex, parent and youth reports of pubertal status; d)
2. Parent psychosocial matching (total parent psychosocial score; p)
3. Outcome matching (total impairments; o)
4. Demographic and parent psychosocial matching together (dp)
5. Demographic and outcome matching together (do)
6. Parent psychosocial and outcome matching together (op)
7. Demographic, parent psychosocial, and outcome matching together (dpo)

```{r}
# Establishing formulae
d_vars <- paste(
    "household_income",
    "race",
    "sex",
    "age",
    "pubertal_status_p",
    "pubertal_status_y",
    sep = " + "
)
p_vars <- "total_parent_psych"
o_vars <- "total_impairments"
dp_vars <- paste0(d_vars, " + ", p_vars)
do_vars <- paste0(d_vars, " + ", o_vars)
op_vars <- paste0(o_vars, " + ", p_vars)
dpo_vars <- paste0(d_vars, " + ", p_vars, " + ", o_vars)

match_d_results_u <- matchit(
    as.formula(paste0("mtbi ~ ", d_vars)), matching_df_u1, method = "nearest"
)
match_p_results_u <- matchit(
    as.formula(paste0("mtbi ~ ", p_vars)), matching_df_u1, method = "nearest"
)
match_o_results_u <- matchit(
    as.formula(paste0("mtbi ~ ", o_vars)), matching_df_u1, method = "nearest"
)

match_d_results_p <- matchit(
    as.formula(paste0("mtbi ~ ", d_vars)), matching_df_p1, method = "nearest"
)
match_p_results_p <- matchit(
    as.formula(paste0("mtbi ~ ", p_vars)), matching_df_p1, method = "nearest"
)
match_o_results_p <- matchit(
    as.formula(paste0("mtbi ~ ", o_vars)), matching_df_p1, method = "nearest"
)

match_dp_results_u <- matchit(
    as.formula(paste0("mtbi ~ ", dp_vars)), matching_df_u1, method = "nearest"
)
match_do_results_u <- matchit(
    as.formula(paste0("mtbi ~ ", op_vars)), matching_df_u1, method = "nearest"
)
match_op_results_u <- matchit(
    as.formula(paste0("mtbi ~ ", op_vars)), matching_df_u1, method = "nearest"
)

match_dp_results_p <- matchit(
    as.formula(paste0("mtbi ~ ", dp_vars)), matching_df_p1, method = "nearest"
)
match_do_results_p <- matchit(
    as.formula(paste0("mtbi ~ ", op_vars)), matching_df_p1, method = "nearest"
)
match_op_results_p <- matchit(
    as.formula(paste0("mtbi ~ ", op_vars)), matching_df_p1, method = "nearest"
)

match_dpo_results_u <- matchit(
    as.formula(paste0("mtbi ~ ", dp_vars)), matching_df_u1, method = "nearest"
)
match_dpo_results_p <- matchit(
    as.formula(paste0("mtbi ~ ", dp_vars)), matching_df_p1, method = "nearest"
)

# Saving plots
save_matching_plot <- function(matching_results, name) {
    grDevices::png(filename = name, width = 1000, height = 500, res = 100)
    plot(matching_results, type = "density", interactive = FALSE)
    grDevices::dev.off()
}

save_matching_plot(
    match_d_results_u,
    fig_path("match_d_results_u.png", TRUE)
)
save_matching_plot(
    match_p_results_u,
    fig_path("match_p_results_u.png", TRUE)
)
save_matching_plot(
    match_o_results_u,
    fig_path("match_o_results_u.png", TRUE)
)
save_matching_plot(
    match_d_results_p,
    fig_path("match_d_results_p.png", TRUE)
)
save_matching_plot(
    match_p_results_p,
    fig_path("match_p_results_p.png", TRUE)
)
save_matching_plot(
    match_o_results_p,
    fig_path("match_o_results_p.png", TRUE)
)
save_matching_plot(
    match_dp_results_u,
    fig_path("match_dp_results_u.png", TRUE)
)
save_matching_plot(
    match_do_results_u,
    fig_path("match_do_results_u.png", TRUE)
)
save_matching_plot(
    match_op_results_u,
    fig_path("match_op_results_u.png", TRUE)
)
save_matching_plot(
    match_dp_results_p,
    fig_path("match_dp_results_p.png", TRUE)
)
save_matching_plot(
    match_do_results_p,
    fig_path("match_do_results_p.png", TRUE)
)
save_matching_plot(
    match_op_results_p,
    fig_path("match_op_results_p.png", TRUE)
)
save_matching_plot(
    match_dpo_results_u,
    fig_path("match_dpo_results_u.png", TRUE)
)
save_matching_plot(
    match_dpo_results_p,
    fig_path("match_dpo_results_p.png", TRUE)
)
```


```{r}
# These all contain 438 mTBI children + 438 matched uninjured children
# Saving matched results
match_d_u <- match.data(match_d_results_u)
match_p_u <- match.data(match_p_results_u)
match_o_u <- match.data(match_o_results_u)
match_d_p <- match.data(match_d_results_p)
match_p_p <- match.data(match_p_results_p)
match_o_p <- match.data(match_o_results_p)
match_dp_u <- match.data(match_dp_results_u)
match_do_u <- match.data(match_do_results_u)
match_op_u <- match.data(match_op_results_u)
match_dp_p <- match.data(match_dp_results_p)
match_do_p <- match.data(match_do_results_p)
match_op_p <- match.data(match_op_results_p)
match_dpo_u <- match.data(match_dpo_results_u)
match_dpo_p <- match.data(match_dpo_results_p)

saveRDS(match_d_u, proc_path("match_d_u.rds", TRUE))
saveRDS(match_p_u, proc_path("match_p_u.rds", TRUE))
saveRDS(match_o_u, proc_path("match_o_u.rds", TRUE))
saveRDS(match_d_p, proc_path("match_d_p.rds", TRUE))
saveRDS(match_p_p, proc_path("match_p_p.rds", TRUE))
saveRDS(match_o_p, proc_path("match_o_p.rds", TRUE))
saveRDS(match_dp_u, proc_path("match_dp_u.rds", TRUE))
saveRDS(match_do_u, proc_path("match_do_u.rds", TRUE))
saveRDS(match_op_u, proc_path("match_op_u.rds", TRUE))
saveRDS(match_dp_p, proc_path("match_dp_p.rds", TRUE))
saveRDS(match_do_p, proc_path("match_do_p.rds", TRUE))
saveRDS(match_op_p, proc_path("match_op_p.rds", TRUE))
saveRDS(match_dpo_u, proc_path("match_dpo_u.rds", TRUE))
saveRDS(match_dpo_p, proc_path("match_dpo_p.rds", TRUE))
```

```{r}
match_d_u <- readRDS(proc_path("2025_10_01_match_d_u.rds"))
match_p_u <- readRDS(proc_path("2025_10_01_match_p_u.rds"))
match_o_u <- readRDS(proc_path("2025_10_01_match_o_u.rds"))
match_d_p <- readRDS(proc_path("2025_10_01_match_d_p.rds"))
match_p_p <- readRDS(proc_path("2025_10_01_match_p_p.rds"))
match_o_p <- readRDS(proc_path("2025_10_01_match_o_p.rds"))
match_dp_u <- readRDS(proc_path("2025_10_01_match_dp_u.rds"))
match_do_u <- readRDS(proc_path("2025_10_01_match_do_u.rds"))
match_op_u <- readRDS(proc_path("2025_10_01_match_op_u.rds"))
match_dp_p <- readRDS(proc_path("2025_10_01_match_dp_p.rds"))
match_do_p <- readRDS(proc_path("2025_10_01_match_do_p.rds"))
match_op_p <- readRDS(proc_path("2025_10_01_match_op_p.rds"))
match_dpo_u <- readRDS(proc_path("2025_10_01_match_dpo_u.rds"))
match_dpo_p <- readRDS(proc_path("2025_10_01_match_dpo_p.rds"))
```

```{r}
# Extracting the matched uninjured subjects
matched_unij_d_u <- dplyr::filter(match_d_u, mtbi == 0)$"uid"
matched_unij_p_u <- dplyr::filter(match_p_u, mtbi == 0)$"uid"
matched_unij_o_u <- dplyr::filter(match_o_u, mtbi == 0)$"uid"
matched_unij_d_p <- dplyr::filter(match_d_p, mtbi == 0)$"uid"
matched_unij_p_p <- dplyr::filter(match_p_p, mtbi == 0)$"uid"
matched_unij_o_p <- dplyr::filter(match_o_p, mtbi == 0)$"uid"
matched_unij_dp_u <- dplyr::filter(match_dp_u, mtbi == 0)$"uid"
matched_unij_do_u <- dplyr::filter(match_do_u, mtbi == 0)$"uid"
matched_unij_op_u <- dplyr::filter(match_op_u, mtbi == 0)$"uid"
matched_unij_dp_p <- dplyr::filter(match_dp_p, mtbi == 0)$"uid"
matched_unij_do_p <- dplyr::filter(match_do_p, mtbi == 0)$"uid"
matched_unij_op_p <- dplyr::filter(match_op_p, mtbi == 0)$"uid"
matched_unij_dpo_u <- dplyr::filter(match_dpo_u, mtbi == 0)$"uid"
matched_unij_dpo_p <- dplyr::filter(match_dpo_p, mtbi == 0)$"uid"

write_csv(
    data.frame(subjectkey = matched_unij_d_u),
    sub_path("matched_unij_d_u.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_p_u),
    sub_path("matched_unij_p_u.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_o_u),
    sub_path("matched_unij_o_u.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_d_p),
    sub_path("matched_unij_d_p.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_p_p),
    sub_path("matched_unij_p_p.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_o_p),
    sub_path("matched_unij_o_p.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_dp_u),
    sub_path("matched_unij_dp_u.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_do_u),
    sub_path("matched_unij_do_u.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_op_u),
    sub_path("matched_unij_op_u.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_dp_p),
    sub_path("matched_unij_dp_p.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_do_p),
    sub_path("matched_unij_do_p.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_op_p),
    sub_path("matched_unij_op_p.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_dpo_u),
    sub_path("matched_unij_dpo_u.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_dpo_p),
    sub_path("matched_unij_dpo_p.csv", TRUE)
)
```

```{r}
matched_unij_d_u <- read_subjects(
    sub_path("2025_10_01_matched_unij_d_u.csv")
)
matched_unij_p_u <- read_subjects(
    sub_path("2025_10_01_matched_unij_p_u.csv")
)
matched_unij_o_u <- read_subjects(
    sub_path("2025_10_01_matched_unij_o_u.csv")
)
matched_unij_d_p <- read_subjects(
    sub_path("2025_10_01_matched_unij_d_p.csv")
)
matched_unij_p_p <- read_subjects(
    sub_path("2025_10_01_matched_unij_p_p.csv")
)
matched_unij_o_p <- read_subjects(
    sub_path("2025_10_01_matched_unij_o_p.csv")
)
matched_unij_dp_u <- read_subjects(
    sub_path("2025_10_01_matched_unij_dp_u.csv")
)
matched_unij_do_u <- read_subjects(
    sub_path("2025_10_01_matched_unij_do_u.csv")
)
matched_unij_op_u <- read_subjects(
    sub_path("2025_10_01_matched_unij_op_u.csv")
)
matched_unij_dp_p <- read_subjects(
    sub_path("2025_10_01_matched_unij_dp_p.csv")
)
matched_unij_do_p <- read_subjects(
    sub_path("2025_10_01_matched_unij_do_p.csv")
)
matched_unij_op_p <- read_subjects(
    sub_path("2025_10_01_matched_unij_op_p.csv")
)
matched_unij_dpo_u <- read_subjects(
    sub_path("2025_10_01_matched_unij_dpo_u.csv")
)
matched_unij_dpo_p <- read_subjects(
    sub_path("2025_10_01_matched_unij_dpo_p.csv")
)
```

```{r}
matched_subjects <- list(
    "d_u" = matched_unij_d_u,
    "p_u" = matched_unij_p_u,
    "o_u" = matched_unij_o_u,
    "d_p" = matched_unij_d_p,
    "p_p" = matched_unij_p_p,
    "o_p" = matched_unij_o_p,
    "dp_u" = matched_unij_dp_u,
    "do_u" = matched_unij_do_u,
    "op_u" = matched_unij_op_u,
    "dp_p" = matched_unij_dp_p,
    "do_p" = matched_unij_do_p,
    "op_p" = matched_unij_op_p,
    "dpo_u" = matched_unij_dpo_u,
    "dpo_p" = matched_unij_dpo_p
)

intersect(matched_unij_dpo_p, matched_unij_d_u)

match_mat <- matrix(ncol = length(matched_subjects), nrow = length(matched_subjects))
for (i in seq_along(matched_subjects)) {
    for (j in seq_along(matched_subjects)) {
        match_mat[i, j] <- length(intersect(matched_subjects[[i]], matched_subjects[[j]]))
        match_mat[j, i] <- match_mat[i, j]
    }
}
match_mat <- match_mat / 438 * 100

mat_names <- names(matched_subjects)
mat_names <- gsub("_u", " (Unpooled)", mat_names)
mat_names <- gsub("_p", " (Pooled)", mat_names)
mat_names <- gsub("dpo", "D, P, O", mat_names)
mat_names <- gsub("dp", "D, P", mat_names)
mat_names <- gsub("do", "D, O", mat_names)
mat_names <- gsub("op", "O, P", mat_names)
mat_names <- gsub("d \\(", "D (", mat_names)
mat_names <- gsub("o \\(", "O (", mat_names)
mat_names <- gsub("p \\(", "P (", mat_names)
mat_names

rownames(match_mat) <- mat_names
colnames(match_mat) <- mat_names

match_mat_hm <- ComplexHeatmap::Heatmap(
    match_mat,
    heatmap_legend_param = list(
        title = "% Subject\nOverlap"
    ),
    col = circlize::colorRamp2(
        c(min(match_mat), max(match_mat)),
        c("black", "red")
    ),
    rect_gp = gpar(col = "black", lwd = 1)
)
match_mat_hm

save_heatmap(
    heatmap = match_mat_hm,
    path = fig_path("match_mat_hm.png", TRUE),
    width = 550,
    height = 500,
    res = 100
)
```

## Subsetting matched uninjured data and out of model lists

```{r}
# Function reduces a data list to only subjects in the subject vector
subject_filter_dl <- function(data_list, subject_vector) {
    data_list <- data_list |>
        dlapply(
            function(x) {
                keep_subs <- x$"data"$"uid" %in% subject_vector
                x$"data" <- x$"data"[keep_subs, ]
                return(x)
            }
        )
    return(data_list)
}

set.seed(42)
random_unij_subs <- sample(unij_ns_subs, size = 438)

matched_unij_dl_d_u <- subject_filter_dl(unij_dl_u1, matched_unij_d_u)
matched_unij_dl_d_p <- subject_filter_dl(unij_dl_p1, matched_unij_d_p)

matched_unij_dl_p_u <- subject_filter_dl(unij_dl_u1, matched_unij_p_u)
matched_unij_dl_p_p <- subject_filter_dl(unij_dl_p1, matched_unij_p_p)

matched_unij_dl_o_u <- subject_filter_dl(unij_dl_u1, matched_unij_o_u)
matched_unij_dl_o_p <- subject_filter_dl(unij_dl_p1, matched_unij_o_p)

matched_unij_dl_do_u <- subject_filter_dl(unij_dl_u1, matched_unij_do_u)
matched_unij_dl_do_p <- subject_filter_dl(unij_dl_p1, matched_unij_do_p)

matched_unij_dl_dp_u <- subject_filter_dl(unij_dl_u1, matched_unij_dp_u)
matched_unij_dl_dp_p <- subject_filter_dl(unij_dl_p1, matched_unij_dp_p)

matched_unij_dl_op_u <- subject_filter_dl(unij_dl_u1, matched_unij_op_u)
matched_unij_dl_op_p <- subject_filter_dl(unij_dl_p1, matched_unij_op_p)

matched_unij_dl_dpo_p <- subject_filter_dl(unij_dl_p1, matched_unij_dpo_p)
matched_unij_dl_dpo_u <- subject_filter_dl(unij_dl_u1, matched_unij_dpo_u)

random_unij_dl_u1 <- subject_filter_dl(unij_dl_u1, paste0("uid_", random_unij_subs))
random_unij_dl_p1 <- subject_filter_dl(unij_dl_p1, paste0("uid_", random_unij_subs))

matched_unij_ol_d_u <- subject_filter_dl(unij_ol_u1, matched_unij_d_u)
matched_unij_ol_d_p <- subject_filter_dl(unij_ol_p1, matched_unij_d_p)

matched_unij_ol_p_u <- subject_filter_dl(unij_ol_u1, matched_unij_p_u)
matched_unij_ol_p_p <- subject_filter_dl(unij_ol_p1, matched_unij_p_p)

matched_unij_ol_o_u <- subject_filter_dl(unij_ol_u1, matched_unij_o_u)
matched_unij_ol_o_p <- subject_filter_dl(unij_ol_p1, matched_unij_o_p)

matched_unij_ol_do_u <- subject_filter_dl(unij_ol_u1, matched_unij_do_u)
matched_unij_ol_do_p <- subject_filter_dl(unij_ol_p1, matched_unij_do_p)

matched_unij_ol_dp_u <- subject_filter_dl(unij_ol_u1, matched_unij_dp_u)
matched_unij_ol_dp_p <- subject_filter_dl(unij_ol_p1, matched_unij_dp_p)

matched_unij_ol_op_u <- subject_filter_dl(unij_ol_u1, matched_unij_op_u)
matched_unij_ol_op_p <- subject_filter_dl(unij_ol_p1, matched_unij_op_p)

matched_unij_ol_dpo_p <- subject_filter_dl(unij_ol_p1, matched_unij_dpo_p)
matched_unij_ol_dpo_u <- subject_filter_dl(unij_ol_u1, matched_unij_dpo_u)

random_unij_ol_u1 <- subject_filter_dl(unij_ol_u1, paste0("uid_", random_unij_subs))
random_unij_ol_p1 <- subject_filter_dl(unij_ol_p1, paste0("uid_", random_unij_subs))

saveRDS(matched_unij_dl_d_u, proc_path("matched_unij_dl_d_u.rds", TRUE))
saveRDS(matched_unij_dl_p_u, proc_path("matched_unij_dl_p_u.rds", TRUE))
saveRDS(matched_unij_dl_o_u, proc_path("matched_unij_dl_o_u.rds", TRUE))
saveRDS(matched_unij_dl_d_p, proc_path("matched_unij_dl_d_p.rds", TRUE))
saveRDS(matched_unij_dl_p_p, proc_path("matched_unij_dl_p_p.rds", TRUE))
saveRDS(matched_unij_dl_o_p, proc_path("matched_unij_dl_o_p.rds", TRUE))
saveRDS(matched_unij_dl_dp_u, proc_path("matched_unij_dl_dp_u.rds", TRUE))
saveRDS(matched_unij_dl_do_u, proc_path("matched_unij_dl_do_u.rds", TRUE))
saveRDS(matched_unij_dl_op_u, proc_path("matched_unij_dl_op_u.rds", TRUE))
saveRDS(matched_unij_dl_dp_p, proc_path("matched_unij_dl_dp_p.rds", TRUE))
saveRDS(matched_unij_dl_do_p, proc_path("matched_unij_dl_do_p.rds", TRUE))
saveRDS(matched_unij_dl_op_p, proc_path("matched_unij_dl_op_p.rds", TRUE))
saveRDS(matched_unij_dl_dpo_p, proc_path("matched_unij_dl_dpo_p.rds", TRUE))
saveRDS(matched_unij_dl_dpo_u, proc_path("matched_unij_dl_dpo_u.rds", TRUE))
saveRDS(random_unij_dl_u1, proc_path("random_unij_dl_u1.rds", TRUE))
saveRDS(random_unij_dl_p1, proc_path("random_unij_dl_p1.rds", TRUE))

saveRDS(matched_unij_ol_d_u, proc_path("matched_unij_ol_d_u.rds", TRUE))
saveRDS(matched_unij_ol_p_u, proc_path("matched_unij_ol_p_u.rds", TRUE))
saveRDS(matched_unij_ol_o_u, proc_path("matched_unij_ol_o_u.rds", TRUE))
saveRDS(matched_unij_ol_d_p, proc_path("matched_unij_ol_d_p.rds", TRUE))
saveRDS(matched_unij_ol_p_p, proc_path("matched_unij_ol_p_p.rds", TRUE))
saveRDS(matched_unij_ol_o_p, proc_path("matched_unij_ol_o_p.rds", TRUE))
saveRDS(matched_unij_ol_dp_u, proc_path("matched_unij_ol_dp_u.rds", TRUE))
saveRDS(matched_unij_ol_do_u, proc_path("matched_unij_ol_do_u.rds", TRUE))
saveRDS(matched_unij_ol_op_u, proc_path("matched_unij_ol_op_u.rds", TRUE))
saveRDS(matched_unij_ol_dp_p, proc_path("matched_unij_ol_dp_p.rds", TRUE))
saveRDS(matched_unij_ol_do_p, proc_path("matched_unij_ol_do_p.rds", TRUE))
saveRDS(matched_unij_ol_op_p, proc_path("matched_unij_ol_op_p.rds", TRUE))
saveRDS(matched_unij_ol_dpo_p, proc_path("matched_unij_ol_dpo_p.rds", TRUE))
saveRDS(matched_unij_ol_dpo_u, proc_path("matched_unij_ol_dpo_u.rds", TRUE))
saveRDS(random_unij_ol_u1, proc_path("random_unij_ol_u1.rds", TRUE))
saveRDS(random_unij_ol_p1, proc_path("random_unij_ol_p1.rds", TRUE))
```

```{r}
# CHECKPOINT
matched_unij_dl_d_u <- readRDS(proc_path("2025_10_01_matched_unij_dl_d_u.rds"))
matched_unij_dl_p_u <- readRDS(proc_path("2025_10_01_matched_unij_dl_p_u.rds"))
matched_unij_dl_o_u <- readRDS(proc_path("2025_10_01_matched_unij_dl_o_u.rds"))
matched_unij_dl_d_p <- readRDS(proc_path("2025_10_01_matched_unij_dl_d_p.rds"))
matched_unij_dl_p_p <- readRDS(proc_path("2025_10_01_matched_unij_dl_p_p.rds"))
matched_unij_dl_o_p <- readRDS(proc_path("2025_10_01_matched_unij_dl_o_p.rds"))
matched_unij_dl_dp_u <- readRDS(proc_path("2025_10_01_matched_unij_dl_dp_u.rds"))
matched_unij_dl_do_u <- readRDS(proc_path("2025_10_01_matched_unij_dl_do_u.rds"))
matched_unij_dl_op_u <- readRDS(proc_path("2025_10_01_matched_unij_dl_op_u.rds"))
matched_unij_dl_dp_p <- readRDS(proc_path("2025_10_01_matched_unij_dl_dp_p.rds"))
matched_unij_dl_do_p <- readRDS(proc_path("2025_10_01_matched_unij_dl_do_p.rds"))
matched_unij_dl_op_p <- readRDS(proc_path("2025_10_01_matched_unij_dl_op_p.rds"))
matched_unij_dl_dpo_p <- readRDS(proc_path("2025_10_01_matched_unij_dl_dpo_p.rds"))
matched_unij_dl_dpo_u <- readRDS(proc_path("2025_10_01_matched_unij_dl_dpo_u.rds"))
random_unij_dl_u1 <- readRDS(proc_path("2025_10_01_random_unij_dl_u1.rds"))
random_unij_dl_p1 <- readRDS(proc_path("2025_10_01_random_unij_dl_p1.rds"))

matched_unij_ol_d_u <- readRDS(proc_path("2025_10_01_matched_unij_ol_d_u.rds"))
matched_unij_ol_p_u <- readRDS(proc_path("2025_10_01_matched_unij_ol_p_u.rds"))
matched_unij_ol_o_u <- readRDS(proc_path("2025_10_01_matched_unij_ol_o_u.rds"))
matched_unij_ol_d_p <- readRDS(proc_path("2025_10_01_matched_unij_ol_d_p.rds"))
matched_unij_ol_p_p <- readRDS(proc_path("2025_10_01_matched_unij_ol_p_p.rds"))
matched_unij_ol_o_p <- readRDS(proc_path("2025_10_01_matched_unij_ol_o_p.rds"))
matched_unij_ol_dp_u <- readRDS(proc_path("2025_10_01_matched_unij_ol_dp_u.rds"))
matched_unij_ol_do_u <- readRDS(proc_path("2025_10_01_matched_unij_ol_do_u.rds"))
matched_unij_ol_op_u <- readRDS(proc_path("2025_10_01_matched_unij_ol_op_u.rds"))
matched_unij_ol_dp_p <- readRDS(proc_path("2025_10_01_matched_unij_ol_dp_p.rds"))
matched_unij_ol_do_p <- readRDS(proc_path("2025_10_01_matched_unij_ol_do_p.rds"))
matched_unij_ol_op_p <- readRDS(proc_path("2025_10_01_matched_unij_ol_op_p.rds"))
matched_unij_ol_dpo_p <- readRDS(proc_path("2025_10_01_matched_unij_ol_dpo_p.rds"))
matched_unij_ol_dpo_u <- readRDS(proc_path("2025_10_01_matched_unij_ol_dpo_u.rds"))
random_unij_ol_u1 <- readRDS(proc_path("2025_10_01_random_unij_ol_u1.rds"))
random_unij_ol_p1 <- readRDS(proc_path("2025_10_01_random_unij_ol_p1.rds"))
```

## metaSNF

```{r}
set.seed(42)
matched_config <- snf_config(
    matched_unij_dl_d_u,
    n_solutions = 200,
    cnt_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    dsc_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ord_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    use_default_dist_fns = TRUE
)

saveRDS(matched_config, proc_path("matched_config.rds", TRUE))
```

```{r}
# CHECKPOINT
matched_config <- readRDS(proc_path("2025_10_01_matched_config.rds"))
```

```{r}
# SNF
matched_unij_sol_df_d_u <- progressr::with_progress(batch_snf(matched_unij_dl_d_u, matched_config, processes = 48))
saveRDS(matched_unij_sol_df_d_u, proc_path("matched_unij_sol_df_d_u.rds", TRUE))
cat("snf 1 done\n")
matched_unij_sol_df_p_u <- progressr::with_progress(batch_snf(matched_unij_dl_p_u, matched_config, processes = 48))
saveRDS(matched_unij_sol_df_p_u, proc_path("matched_unij_sol_df_p_u.rds", TRUE))
cat("snf 2 done\n")
matched_unij_sol_df_o_u <- progressr::with_progress(batch_snf(matched_unij_dl_o_u, matched_config, processes = 48))
saveRDS(matched_unij_sol_df_o_u, proc_path("matched_unij_sol_df_o_u.rds", TRUE))
cat("snf 3 done\n")
matched_unij_sol_df_d_p <- progressr::with_progress(batch_snf(matched_unij_dl_d_p, matched_config, processes = 48))
saveRDS(matched_unij_sol_df_d_p, proc_path("matched_unij_sol_df_d_p.rds", TRUE))
cat("snf 4 done\n")
matched_unij_sol_df_p_p <- progressr::with_progress(batch_snf(matched_unij_dl_p_p, matched_config, processes = 48))
saveRDS(matched_unij_sol_df_p_p, proc_path("matched_unij_sol_df_p_p.rds", TRUE))
cat("snf 5 done\n")
```

```{r}
matched_unij_sol_df_o_p <- progressr::with_progress(batch_snf(matched_unij_dl_o_p, matched_config, processes = 48))
saveRDS(matched_unij_sol_df_o_p, proc_path("matched_unij_sol_df_o_p.rds", TRUE))
cat("snf 6 done\n")
matched_unij_sol_df_dp_u <- progressr::with_progress(batch_snf(matched_unij_dl_dp_u, matched_config, processes = 48))
saveRDS(matched_unij_sol_df_dp_u, proc_path("matched_unij_sol_df_dp_u.rds", TRUE))
cat("snf 7 done\n")
matched_unij_sol_df_do_u <- progressr::with_progress(batch_snf(matched_unij_dl_do_u, matched_config, processes = 48))
saveRDS(matched_unij_sol_df_do_u, proc_path("matched_unij_sol_df_do_u.rds", TRUE))
cat("snf 8 done\n")
matched_unij_sol_df_op_u <- progressr::with_progress(batch_snf(matched_unij_dl_op_u, matched_config, processes = 48))
saveRDS(matched_unij_sol_df_op_u, proc_path("matched_unij_sol_df_op_u.rds", TRUE))
cat("snf 9 done\n")
matched_unij_sol_df_dp_p <- progressr::with_progress(batch_snf(matched_unij_dl_dp_p, matched_config, processes = 48))
saveRDS(matched_unij_sol_df_dp_p, proc_path("matched_unij_sol_df_dp_p.rds", TRUE))
cat("snf 10 done\n")
```

```{r}
matched_unij_sol_df_do_p <- progressr::with_progress(batch_snf(matched_unij_dl_do_p, matched_config, processes = 48))
saveRDS(matched_unij_sol_df_do_p, proc_path("matched_unij_sol_df_do_p.rds", TRUE))
cat("snf 11 done\n")
matched_unij_sol_df_op_p <- progressr::with_progress(batch_snf(matched_unij_dl_op_p, matched_config, processes = 48))
saveRDS(matched_unij_sol_df_op_p, proc_path("matched_unij_sol_df_op_p.rds", TRUE))
cat("snf 12 done\n")
matched_unij_sol_df_dpo_p <- progressr::with_progress(batch_snf(matched_unij_dl_dpo_p, matched_config, processes = 48))
saveRDS(matched_unij_sol_df_dpo_p, proc_path("matched_unij_sol_df_dpo_p.rds", TRUE))
cat("snf 13 done\n")
matched_unij_sol_df_dpo_u <- progressr::with_progress(batch_snf(matched_unij_dl_dpo_u, matched_config, processes = 48))
saveRDS(matched_unij_sol_df_dpo_u, proc_path("matched_unij_sol_df_dpo_u.rds", TRUE))
cat("snf 14 done\n")
random_unij_sol_df_u1 <- progressr::with_progress(batch_snf(random_unij_dl_u1, matched_config, processes = 48))
saveRDS(random_unij_sol_df_u1, proc_path("random_unij_sol_df_u1.rds", TRUE))
cat("snf 15 done\n")
random_unij_sol_df_p1 <- progressr::with_progress(batch_snf(random_unij_dl_p1, matched_config, processes = 48))
saveRDS(random_unij_sol_df_p1, proc_path("random_unij_sol_df_p1.rds", TRUE))
```

```{r}
matched_unij_sol_df_dpo_u <- readRDS(proc_path("2025_10_01_matched_unij_sol_df_dpo_u.rds"))
matched_unij_sol_df_dpo_p <- readRDS(proc_path("2025_10_01_matched_unij_sol_df_dpo_p.rds"))
matched_unij_sol_df_op_p  <- readRDS(proc_path("2025_10_01_matched_unij_sol_df_op_p.rds"))
matched_unij_sol_df_do_p  <- readRDS(proc_path("2025_10_01_matched_unij_sol_df_do_p.rds"))
matched_unij_sol_df_dp_p  <- readRDS(proc_path("2025_10_01_matched_unij_sol_df_dp_p.rds"))
matched_unij_sol_df_op_u  <- readRDS(proc_path("2025_10_01_matched_unij_sol_df_op_u.rds"))
matched_unij_sol_df_do_u  <- readRDS(proc_path("2025_10_01_matched_unij_sol_df_do_u.rds"))
matched_unij_sol_df_dp_u  <- readRDS(proc_path("2025_10_01_matched_unij_sol_df_dp_u.rds"))
matched_unij_sol_df_o_p   <- readRDS(proc_path("2025_10_01_matched_unij_sol_df_o_p.rds"))
matched_unij_sol_df_p_p   <- readRDS(proc_path("2025_10_01_matched_unij_sol_df_p_p.rds"))
matched_unij_sol_df_d_p   <- readRDS(proc_path("2025_10_01_matched_unij_sol_df_d_p.rds"))
matched_unij_sol_df_o_u   <- readRDS(proc_path("2025_10_01_matched_unij_sol_df_o_u.rds"))
matched_unij_sol_df_p_u   <- readRDS(proc_path("2025_10_01_matched_unij_sol_df_p_u.rds"))
matched_unij_sol_df_d_u   <- readRDS(proc_path("2025_10_01_matched_unij_sol_df_d_u.rds"))
random_unij_sol_df_u1     <- readRDS(proc_path("2025_10_01_random_unij_sol_df_u1.rds"))
random_unij_sol_df_p1     <- readRDS(proc_path("2025_10_01_random_unij_sol_df_p1.rds"))
```

```{r}
matched_unij_ext_sol_df_dpo_u <- extend_solutions(
    matched_unij_sol_df_dpo_u,
    dl = matched_unij_dl_dpo_u,
    target_dl = matched_unij_ol_dpo_u,
    min_pval = 1e-10,
    processes = 4
)
saveRDS(matched_unij_ext_sol_df_dpo_u, proc_path("matched_unij_ext_sol_df_dpo_u.rds", TRUE))
matched_unij_ext_sol_df_dpo_p <- extend_solutions(
    matched_unij_sol_df_dpo_p,
    dl = matched_unij_dl_dpo_p,
    target_dl = matched_unij_ol_dpo_p,
    min_pval = 1e-10,
    processes = 4
)
saveRDS(matched_unij_ext_sol_df_dpo_p, proc_path("matched_unij_ext_sol_df_dpo_p.rds", TRUE))
matched_unij_ext_sol_df_op_p <- extend_solutions(
    matched_unij_sol_df_op_p,
    dl = matched_unij_dl_op_p,
    target_dl = matched_unij_ol_op_p,
    min_pval = 1e-10,
    processes = 4
)
saveRDS(matched_unij_ext_sol_df_op_p, proc_path("matched_unij_ext_sol_df_op_p.rds", TRUE))
matched_unij_ext_sol_df_do_p <- extend_solutions(
    matched_unij_sol_df_do_p,
    dl = matched_unij_dl_do_p,
    target_dl = matched_unij_ol_do_p,
    min_pval = 1e-10,
    processes = 4
)
saveRDS(matched_unij_ext_sol_df_do_p, proc_path("matched_unij_ext_sol_df_do_p.rds", TRUE))
matched_unij_ext_sol_df_dp_p <- extend_solutions(
    matched_unij_sol_df_dp_p,
    dl = matched_unij_dl_dp_p,
    target_dl = matched_unij_ol_dp_p,
    min_pval = 1e-10,
    processes = 4
)
saveRDS(matched_unij_ext_sol_df_dp_p, proc_path("matched_unij_ext_sol_df_dp_p.rds", TRUE))
matched_unij_ext_sol_df_op_u <- extend_solutions(
    matched_unij_sol_df_op_u,
    dl = matched_unij_dl_op_u,
    target_dl = matched_unij_ol_op_u,
    min_pval = 1e-10,
    processes = 4
)
saveRDS(matched_unij_ext_sol_df_op_u, proc_path("matched_unij_ext_sol_df_op_u.rds", TRUE))
matched_unij_ext_sol_df_do_u <- extend_solutions(
    matched_unij_sol_df_do_u,
    dl = matched_unij_dl_do_u,
    target_dl = matched_unij_ol_do_u,
    min_pval = 1e-10,
    processes = 4
)
saveRDS(matched_unij_ext_sol_df_do_u, proc_path("matched_unij_ext_sol_df_do_u.rds", TRUE))
#
matched_unij_ext_sol_df_dp_u <- extend_solutions(
    matched_unij_sol_df_dp_u,
    dl = matched_unij_dl_dp_u,
    target_dl = matched_unij_ol_dp_u,
    min_pval = 1e-10,
    processes = 4
)
saveRDS(matched_unij_ext_sol_df_dp_u, proc_path("matched_unij_ext_sol_df_dp_u.rds", TRUE))
matched_unij_ext_sol_df_o_p <- extend_solutions(
    matched_unij_sol_df_o_p,
    dl = matched_unij_dl_o_p,
    target_dl = matched_unij_ol_o_p,
    min_pval = 1e-10,
    processes = 4
)
saveRDS(matched_unij_ext_sol_df_o_p, proc_path("matched_unij_ext_sol_df_o_p.rds", TRUE))
matched_unij_ext_sol_df_p_p <- extend_solutions(
    matched_unij_sol_df_p_p,
    dl = matched_unij_dl_p_p,
    target_dl = matched_unij_ol_p_p,
    min_pval = 1e-10,
    processes = 4
)
saveRDS(matched_unij_ext_sol_df_p_p, proc_path("matched_unij_ext_sol_df_p_p.rds", TRUE))
matched_unij_ext_sol_df_d_p <- extend_solutions(
    matched_unij_sol_df_d_p,
    dl = matched_unij_dl_d_p,
    target_dl = matched_unij_ol_d_p,
    min_pval = 1e-10,
    processes = 4
)
saveRDS(matched_unij_ext_sol_df_d_p, proc_path("matched_unij_ext_sol_df_d_p.rds", TRUE))
matched_unij_ext_sol_df_o_u <- extend_solutions(
    matched_unij_sol_df_o_u,
    dl = matched_unij_dl_o_u,
    target_dl = matched_unij_ol_o_u,
    min_pval = 1e-10,
    processes = 4
)
saveRDS(matched_unij_ext_sol_df_o_u, proc_path("matched_unij_ext_sol_df_o_u.rds", TRUE))
matched_unij_ext_sol_df_p_u <- extend_solutions(
    matched_unij_sol_df_p_u,
    dl = matched_unij_dl_p_u,
    target_dl = matched_unij_ol_p_u,
    min_pval = 1e-10,
    processes = 4
)
saveRDS(matched_unij_ext_sol_df_p_u, proc_path("matched_unij_ext_sol_df_p_u.rds", TRUE))
matched_unij_ext_sol_df_d_u <- extend_solutions(
    matched_unij_sol_df_d_u,
    dl = matched_unij_dl_d_u,
    target_dl = matched_unij_ol_d_u,
    min_pval = 1e-10,
    processes = 4
)
saveRDS(matched_unij_ext_sol_df_d_u, proc_path("matched_unij_ext_sol_df_d_u.rds", TRUE))
random_unij_ext_sol_df_u1 <- extend_solutions(
    random_unij_sol_df_u1,
    dl = random_unij_dl_u1,
    target_dl = random_unij_ol_u1,
    min_pval = 1e-10,
    processes = 4
)
saveRDS(random_unij_ext_sol_df_u1, proc_path("random_unij_ext_sol_df_u1.rds", TRUE))
random_unij_ext_sol_df_p1 <- extend_solutions(
    random_unij_sol_df_p1,
    dl = random_unij_dl_p1,
    target_dl = random_unij_ol_p1,
    min_pval = 1e-10,
    processes = 4
)
saveRDS(random_unij_ext_sol_df_p1, proc_path("random_unij_ext_sol_df_p1.rds", TRUE))
```

```{r}
# CHECKPOINT - extended solutions data frames
matched_unij_ext_sol_df_d_u <- readRDS(proc_path("2025_10_02_matched_unij_ext_sol_df_d_u.rds"))
matched_unij_ext_sol_df_p_u <- readRDS(proc_path("2025_10_02_matched_unij_ext_sol_df_p_u.rds"))
matched_unij_ext_sol_df_o_u <- readRDS(proc_path("2025_10_02_matched_unij_ext_sol_df_o_u.rds"))
matched_unij_ext_sol_df_d_p <- readRDS(proc_path("2025_10_02_matched_unij_ext_sol_df_d_p.rds"))
matched_unij_ext_sol_df_p_p <- readRDS(proc_path("2025_10_02_matched_unij_ext_sol_df_p_p.rds"))
matched_unij_ext_sol_df_o_p <- readRDS(proc_path("2025_10_02_matched_unij_ext_sol_df_o_p.rds"))
matched_unij_ext_sol_df_dp_u <- readRDS(proc_path("2025_10_02_matched_unij_ext_sol_df_dp_u.rds"))
matched_unij_ext_sol_df_do_u <- readRDS(proc_path("2025_10_02_matched_unij_ext_sol_df_do_u.rds"))
matched_unij_ext_sol_df_op_u <- readRDS(proc_path("2025_10_02_matched_unij_ext_sol_df_op_u.rds"))
matched_unij_ext_sol_df_dp_p <- readRDS(proc_path("2025_10_02_matched_unij_ext_sol_df_dp_p.rds"))
matched_unij_ext_sol_df_do_p <- readRDS(proc_path("2025_10_02_matched_unij_ext_sol_df_do_p.rds"))
matched_unij_ext_sol_df_op_p <- readRDS(proc_path("2025_10_02_matched_unij_ext_sol_df_op_p.rds"))
matched_unij_ext_sol_df_dpo_p <- readRDS(proc_path("2025_10_02_matched_unij_ext_sol_df_dpo_p.rds"))
matched_unij_ext_sol_df_dpo_u <- readRDS(proc_path("2025_10_02_matched_unij_ext_sol_df_dpo_u.rds"))
random_unij_ext_sol_df_u1 <- readRDS(proc_path("2025_10_02_random_unij_ext_sol_df_u1.rds"))
random_unij_ext_sol_df_p1 <- readRDS(proc_path("2025_10_02_random_unij_ext_sol_df_p1.rds"))
```

```{r}
matched_unij_ext_sol_df_list <- list(
    "d_u" = matched_unij_ext_sol_df_d_u,
    "p_u" = matched_unij_ext_sol_df_p_u,
    "o_u" = matched_unij_ext_sol_df_o_u,
    "d_p" = matched_unij_ext_sol_df_d_p,
    "p_p" = matched_unij_ext_sol_df_p_p,
    "o_p" = matched_unij_ext_sol_df_o_p,
    "dp_u" = matched_unij_ext_sol_df_dp_u,
    "do_u" = matched_unij_ext_sol_df_do_u,
    "op_u" = matched_unij_ext_sol_df_op_u,
    "dp_p" = matched_unij_ext_sol_df_dp_p,
    "do_p" = matched_unij_ext_sol_df_do_p,
    "op_p" = matched_unij_ext_sol_df_op_p,
    "dpo_p" = matched_unij_ext_sol_df_dpo_p,
    "dpo_u" = matched_unij_ext_sol_df_dpo_u,
    "random_u" = random_unij_ext_sol_df_u1,
    "random_p" = random_unij_ext_sol_df_p1
)

saveRDS(
    matched_unij_ext_sol_df_list,
    proc_path("matched_unij_ext_sol_df_list.rds", TRUE)
)
```

```{r}
matched_unij_ext_sol_df_list <- readRDS(
    proc_path("2025_10_02_matched_unij_ext_sol_df_list.rds")
)
```

```{r}
duplicated(matched_unij_ext_sol_df_list)

vec <- matched_unij_ext_sol_df_list

dup_indices <- which(duplicated(vec))

dup_indices

for (i in dup_indices) {
    cat(names(vec)[i], " is equal to:\n", sep = "")
    for (j in seq_along(vec)) {
        if (identical(vec[[i]], vec[[j]]) & i != j) {
            cat("    - ", names(vec)[j], "\n")
        }
    }
}

#op_u is equal to:
#    -  do_u
#op_p is equal to:
#    -  do_p
#dpo_p is equal to:
#    -  dp_p
#dpo_u is equal to:
#    -  dp_u

names(matched_unij_ext_sol_df_list[!duplicated(vec)])

matched_unij_ext_sol_df_list_dedup <- matched_unij_ext_sol_df_list[!duplicated(vec)]

# Tight requirement: -log10(pval) > 3
matched_unij_ext_sol_df_3c_list_dedup <- lapply(
    matched_unij_ext_sol_df_list_dedup,
    function(x) {
        x <- x[x$"nclust" == 3 & -log10(x$"mean_pval") > 3, ]
        if (nrow(x) > 0) {
            return(x)
        } 
    }
)

lapply(
    matched_unij_ext_sol_df_list,
    function(x) {
        sum(x$"nclust" == 3 & -log10(x$"mean_pval") > 1)
    }
) |> unlist() |> sum()

# Loose requirement: -log10(pval) > 1
matched_unij_ext_sol_df_3c_list_dedup_loose <- lapply(
    matched_unij_ext_sol_df_list_dedup,
    function(x) {
        x <- x[x$"nclust" == 3 & -log10(x$"mean_pval") > 1, ]
        if (nrow(x) > 0) {
            return(x)
        } 
    }
)

-log10(0.1)

lapply(
    matched_unij_ext_sol_df_list,
    function(x) {
        x <- x[x$"nclust" == 3 & x$"mean_pval" <= 0.001, ]
        return(nrow(x))
    }
) |> unlist() |> sum()

lapply(
    matched_unij_ext_sol_df_list,
    function(x) {
        x <- x[x$"nclust" == 3, ]
        return(x$"mean_pval")
    }
) |>
    unlist() |>
    log10() |>
    as.numeric() |>
    saveRDS(proc_path("matched_unij_pvals.rds", TRUE))

unij_pvals <- readRDS(proc_path("2025_10_02_matched_unij_pvals.rds"))
mc_d_pvals <- readRDS(proc_path("2025_10_02_mtbi_der_mc_d_pvals.rds"))

density_plot <- data.frame(
    mean_pval = c(unij_pvals, mc_d_pvals),
    group = factor(
        c(
            rep("Matched Uninjured", length(unij_pvals)),
            rep("MC D", length(mc_d_pvals))
        )
    )
) |>
    ggplot(
        aes(x = -mean_pval, fill = group, color = group)
    ) +
    geom_density(alpha = 0.5, position = "identity") +
    labs(
        x = "Impairment Separation",
        y = "Density",
        fill = "Solution Set",
    ) +
    guides(colour = "none") +
    theme_bw()
density_plot

ggsave(
    fig_path("mc_d_vs_mu_pvals_density.png", TRUE),
    density_plot,
    width = 5,
    height = 3,
    dpi = 120
)

lapply(matched_unij_ext_sol_df_list_dedup, nrow) |> unlist() |> sum

matched_unij_ext_sol_df_3c_list_dedup_loose[[1]] |> nrow() # 10

matched_unij_ext_sol_df_3c_list_dedup_loose[[2]] |> nrow() # 11

matched_unij_ext_sol_df_3c_list_dedup_loose[[3]] |> nrow() # 18

matched_unij_ext_sol_df_3c_list

unlist(sapply(matched_unij_ext_sol_df_3c_list, function(x) nrow(x) > 0))

# 9 tight matches
sapply(matched_unij_ext_sol_df_3c_list_dedup, nrow) |>
    unlist() |>
    sum()

# 142 loose matches
sapply(matched_unij_ext_sol_df_3c_list_dedup_loose, nrow) |>
    unlist() |>
    sum()

matched_unij_ext_sol_df_3c_list_dedup <- matched_unij_ext_sol_df_3c_list_dedup[sapply(matched_unij_ext_sol_df_3c_list_dedup, function(x) isTRUE(nrow(x) > 0))]
matched_unij_ext_sol_df_3c_list_dedup_loose <- matched_unij_ext_sol_df_3c_list_dedup_loose[sapply(matched_unij_ext_sol_df_3c_list_dedup_loose, function(x) isTRUE(nrow(x) > 0))]

saveRDS(matched_unij_ext_sol_df_3c_list_dedup, proc_path("matched_unij_ext_sol_df_3c_list_dedup.rds", TRUE))
saveRDS(matched_unij_ext_sol_df_3c_list_dedup_loose, proc_path("matched_unij_ext_sol_df_3c_list_dedup_loose.rds", TRUE))

matched_unij_ext_sol_df_3c_list_dedup <- readRDS(proc_path("2025_10_02_matched_unij_ext_sol_df_3c_list_dedup.rds"))
matched_unij_ext_sol_df_3c_list_dedup_loose <- readRDS(proc_path("2025_10_02_matched_unij_ext_sol_df_3c_list_dedup_loose.rds"))
```

```{r}
# Domain colour labels
dcols <- c(
    "AS" = "#85929e",
    "D" = "#bb8fce",
    "N" = "#e59866",
    "MH" = "#7fb3d5",
    "P" = "#52be80",
    "S" = "#d98880",
    "B" = "#ff3131"
)

# o_p, dp_u, dp_p, do_p
names(matched_unij_ext_sol_df_3c_list_dedup)

matched_unij_o_p_manhattan <- mc_manhattan_plot(
    matched_unij_ext_sol_df_3c_list_dedup$"o_p",
    dl = matched_unij_dl_o_p,
    target_dl = matched_unij_ol_o_p,
    domain_colours = dcols
)

matched_unij_dp_u_manhattan <- mc_manhattan_plot(
    matched_unij_ext_sol_df_3c_list_dedup$"dp_u",
    dl = matched_unij_dl_dp_u,
    target_dl = matched_unij_ol_dp_u,
    domain_colours = dcols
)

matched_unij_dp_p_manhattan <- mc_manhattan_plot(
    matched_unij_ext_sol_df_3c_list_dedup$"dp_p",
    dl = matched_unij_dl_dp_p,
    target_dl = matched_unij_ol_dp_p,
    domain_colours = dcols
)

matched_unij_do_p_manhattan <- mc_manhattan_plot(
    matched_unij_ext_sol_df_3c_list_dedup$"do_p",
    dl = matched_unij_dl_do_p,
    target_dl = matched_unij_ol_do_p,
    domain_colours = dcols
)

matched_unij_manhattan_plots <- list(
    "o_p" = matched_unij_o_p_manhattan,
    "dp_u" = matched_unij_dp_u_manhattan,
    "dp_p" = matched_unij_dp_p_manhattan,
    "do_p" = matched_unij_do_p_manhattan
)

saveRDS(matched_unij_manhattan_plots, fig_path("matched_unij_manhattan_plots.rds", TRUE))
```

```{r}
# CHECKPOINT
matched_unij_manhattan_plots <- readRDS(fig_path("2025_10_02_matched_unij_manhattan_plots.rds"))
```

```{r}
# Quick save function
qs2 <- function(plot, path, w = 18, h = 14, d = 120) {    
    path <- paste0("matched_unij_", path, "_manhattan.png")
    ggsave(
        fig_path(path, TRUE),
        plot,
        width = w,
        height = h,
        dpi = d
    )
}

# Small function to calculate how tall each manhattan plot
# should be.
heighter <- function(panes) {
    panes * 4/3 + 10/3
}

matched_unij_manhattan_plots$"o_p" # 1
matched_unij_manhattan_plots$"dp_u" # 5
matched_unij_manhattan_plots$"dp_p" # 2
matched_unij_manhattan_plots$"do_p" # 1

qs2(matched_unij_manhattan_plots$"o_p", "o_p", h = heighter(1))
qs2(matched_unij_manhattan_plots$"dp_u", "dp_u", h = heighter(5))
qs2(matched_unij_manhattan_plots$"dp_p", "dp_p", h = heighter(2))
qs2(matched_unij_manhattan_plots$"do_p", "do_p", h = heighter(1))
```

```{r}
matched_unij_dls <- list(
    "d_u" = matched_unij_dl_d_u,
    "p_u" = matched_unij_dl_p_u,
    "o_u" = matched_unij_dl_o_u,
    "p_p" = matched_unij_dl_p_p,
    "o_p" = matched_unij_dl_o_p,
    "dp_u" = matched_unij_dl_dp_u,
    "do_u" = matched_unij_dl_do_u,
    "op_u" = matched_unij_dl_op_u,
    "dp_p" = matched_unij_dl_dp_p,
    "do_p" = matched_unij_dl_do_p,
    "op_p" = matched_unij_dl_op_p,
    "dpo_p" = matched_unij_dl_dpo_p,
    "dpo_u" = matched_unij_dl_dpo_u,
    "random_u" = random_unij_dl_u1,
    "random_p" = random_unij_dl_p1
)

matched_unij_ols <- list(
    "d_u" = matched_unij_ol_d_u,
    "p_u" = matched_unij_ol_p_u,
    "o_u" = matched_unij_ol_o_u,
    "d_p" = matched_unij_ol_d_p,
    "p_p" = matched_unij_ol_p_p,
    "o_p" = matched_unij_ol_o_p,
    "dp_u" = matched_unij_ol_dp_u,
    "do_u" = matched_unij_ol_do_u,
    "op_u" = matched_unij_ol_op_u,
    "dp_p" = matched_unij_ol_dp_p,
    "do_p" = matched_unij_ol_do_p,
    "op_p" = matched_unij_ol_op_p,
    "dpo_p" = matched_unij_ol_dpo_p,
    "dpo_u" = matched_unij_ol_dpo_u,
    "random_u" = random_unij_ol_u1,
    "random_p" = random_unij_ol_p1
)

saveRDS(matched_unij_dls, proc_path("matched_unij_dls.rds", TRUE))
saveRDS(matched_unij_ols, proc_path("matched_unij_ols.rds", TRUE))
```

```{r}
# CHECKPOINT
matched_unij_dls <- readRDS(proc_path("2025_10_02_matched_unij_dls.rds"))
matched_unij_ols <- readRDS(proc_path("2025_10_02_matched_unij_ols.rds"))
```


```{r}
mtbi_gen_fts_table_hits_t <- read_csv(proc_path("2025_09_22_mtbi_gen_fts_table_hits_t.csv"))
mtbi_gen_long <- na.omit(mtbi_gen_fts_table_hits_t)
```



```{r}
# CHECKPOINT
classifier_ifts <- readRDS(proc_path("2025_09_23_classifier_ifts.rds"))
classifier_ifts
```

Calculating concordance (similarity between matched uninjured solution and baseline mTBI solution topologies) using loose threshold.

```{r}
matched_pl_dfs <- lapply(
    names(matched_unij_ext_sol_df_3c_list_dedup_loose),
    function(match) {
        pl <- list()
        nrows <- nrow(matched_unij_ext_sol_df_3c_list_dedup_loose[[match]])
        for (row in seq_len(nrows)) {
            print(paste0(match, row))
            p <- auto_plot(
                matched_unij_ext_sol_df_3c_list_dedup_loose[[match]][row, ],
                dl = c(matched_unij_dls[[match]], matched_unij_ols[[match]]),
                return_plots = FALSE
            )
            pl[[length(pl) + 1]] <- p
        }
        return(pl)
    }
)

names(matched_pl_dfs) <- names(matched_unij_ext_sol_df_3c_list_dedup_loose)
matched_pl_dfs <- unlist(matched_pl_dfs, recursive = FALSE)

saveRDS(matched_pl_dfs, proc_path("matched_pl_dfs.rds", TRUE))

matched_pl_dfs <- readRDS(proc_path("2025_10_02_matched_pl_dfs.rds"))

source("abcd/helper_functions.R")

matched_pl_tops <- lapply(
    matched_pl_dfs,
    function(x) {
        print(x)
        topologizer(x)
    }
)

saveRDS(matched_pl_tops, proc_path("matched_pl_tops.rds", TRUE))

matched_pl_tops <- readRDS(proc_path("2025_10_02_matched_pl_tops.rds"))

matched_pl_tops |> names()

matched_pl_gen_fts <- lapply(
    matched_pl_tops,
    function(x) {
        generalizable_features(x, compare_fn_a)
    }
)

#matched_pl_gen_fts_long <- lapply(
#    matched_pl_gen_fts,
#    function(x) {
#        long_x <- pivot_longer(
#            x,
#            cols = -feature,
#            names_to = "comparison",
#            values_to = "order_unij"
#        )
#        long_gen_x <- dplyr::left_join(
#            mtbi_gen_long,
#            long_x,
#            by = c("feature", "comparison")
#        ) 
#        long_gen_x <- dplyr::mutate(
#            long_gen_x,
#            match = dplyr::case_when(
#                is.na(order_unij) ~ 0,
#                order != order_unij ~ 0, 
#                order == order_unij ~ 1
#            )
#        )
#        return(long_gen_x)
#    }
#)
#
#matched_pl_gen_fts_long_fair <- lapply(
#    matched_pl_gen_fts_long,
#    function(x) {
#        dplyr::filter(x, !grepl("mtbi", feature))
#    }
#)

concordance_w_mtbi_quick <- function(data_df, n = NULL, iters = 10, procs = 1, mtbi_data) {
    #start <- Sys.time()
    #bootstrap_sample <- sample(n, replace = TRUE)
    #sampled_df <- data_df[bootstrap_sample, ]
    tops_df <- topologizer(data_df)
    info_table <- data_df |>
        dplyr::group_by(cluster) |>
        dplyr::summarize(
            income = mean(household_income),
            sex = mean(sex)
        ) |>
        dplyr::mutate(combo = income - sex) |> # sort by low income and high M
        dplyr::arrange(combo)
    swap_key <- paste0(info_table$"cluster", collapse = "")
    swap_list <- list(
        "123" = list(),                 # swap nothing
        "132" = list(c(2, 3)),          # swap 2<->3
        "213" = list(c(1, 2)),          # swap 1<->2
        "231" = list(c(1, 2), c(2, 3)), # swap 1<->2 then 2<->3
        "312" = list(c(1, 3), c(2, 3)), # swap 1<->3 then 2<->3
        "321" = list(c(1, 3))           # swap 1<->3
    )
    swap_instructions <- swap_list[[swap_key]]
    for (instruction in swap_instructions) {
        data_df <- data_df |>
            dplyr::mutate(
                cluster = dplyr::case_when(
                    cluster == instruction[1] ~ factor(instruction[2]),
                    cluster == instruction[2] ~ factor(instruction[1]),
                    TRUE ~ cluster
                )
            )
    }
    info_table <- data_df |>
        dplyr::group_by(cluster) |>
        dplyr::summarize(
            income = mean(household_income),
            sex = mean(sex)
        ) |>
        dplyr::mutate(combo = income - sex) |> # sort by low income and high M
        dplyr::arrange(combo)
    swap_key <- paste0(info_table$"cluster", collapse = "")
    gen_tops_df <- generalizable_features(tops_df, compare_fn_a)
    gen_tops_df_long <- gen_tops_df |>
        pivot_longer(
            cols = -feature,
            names_to = "comparison",
            values_to = "order_sample"
        )
    joint_df <- dplyr::left_join(
        mtbi_data, # reference data frame
        gen_tops_df_long, # sampled data frame
        by = c("feature", "comparison")
    ) |>
        dplyr::mutate(
            match = ifelse(order_sample == order, 1, 0)
        ) |>
        dplyr::filter(!grepl("mtbi", feature))
    concordance <- sum(joint_df$"match") / nrow(joint_df)
    return(concordance)
}

matched_pl_concordances <- lapply(
    seq_along(matched_pl_dfs),
    function(x) {
        print(x)
        concordance_w_mtbi_quick(matched_pl_dfs[[x]], mtbi_data = mtbi_gen_long)
    }
)
saveRDS(matched_pl_concordances, proc_path("matched_pl_concordances.rds", TRUE))

# HERE
matched_pl_concordances <- readRDS(
    proc_path("2025_10_02_matched_pl_concordances.rds")
)

concordance_df <- data.frame(
    unij_set = names(matched_pl_dfs),
    concordance = unlist(matched_pl_concordances)
) |>
    arrange(desc(concordance))
rownames(concordance_df) <- NULL

concordance_df

write_csv(concordance_df, proc_path("matched_unij_concordance.csv", TRUE))

concordance_df <- read_csv(proc_path("2025_10_02_matched_unij_concordance.csv"))

concordance_df_old <- read_csv(proc_path("2025_07_22_matched_unij_concordance.csv"))

grepl("dp_p", concordance_df$"unij_set")

concordance_df$"unij_set"

concordance_df_summary <- concordance_df |>
    dplyr::mutate(
        match = dplyr::case_when(
            grepl("dp_", unij_set) ~ "D, P",
            grepl("do_", unij_set) ~ "D, O",
            grepl("d_", unij_set) ~ "D",
            grepl("p_", unij_set) ~ "P",
            grepl("o_", unij_set) ~ "O",
            grepl("random_", unij_set) ~ "Random",
            TRUE ~ "other"
        ),
        imp = dplyr::case_when(
            grepl("_p", unij_set) ~ "p",
            grepl("_u", unij_set) ~ "u",
            TRUE ~ "other"
        )
    ) |>
    dplyr::group_by(match, imp) |>
    dplyr::summarize(
        avg_concordance = mean(concordance),
        max_concordance = max(concordance),
        n = n()
    ) |>
    dplyr::arrange(desc(max_concordance))
concordance_df_summary$"Rank" <- 1:nrow(concordance_df_summary)
concordance_df_summary |>
    dplyr::select(Rank, match, imp, max_concordance, avg_concordance, n) |>
    dplyr::mutate(
        imp = dplyr::case_when(
            imp == "u" ~ "No",
            imp == "p" ~ "Yes"
        ),
        avg_concordance = round(100 * avg_concordance, 2),
        max_concordance = round(100 * max_concordance, 2)
    ) |>
    dplyr::rename(
        "Criteria" = "match",
        "Pooled" = "imp",
        "Average Concordance" = "avg_concordance",
        "Max Concordance" = "max_concordance"
    ) |>
    knitr::kable(
        format = "markdown",
        digits = 1
    ) |>
        writeLines(proc_path("matched_unij_concordance_summary.txt", TRUE))
```



```{r}

concordance_df

saveRDS(
    matched_unij_ext_sol_df_3c_list_loose$"dp_p"[13, ],
    proc_path("matched_unij_nearest_esdf.rds", TRUE)
)

matched_unij_nearest_esdf <- readRDS(proc_path("2025_10_02_matched_unij_nearest_esdf.rds"))

classifier_ifts <- readRDS(proc_path("2025_09_23_classifier_ifts.rds"))

top_unij_pl <- auto_plot(
    matched_unij_nearest_esdf,
    dl = c(
        matched_unij_dls$"dp_p",
        matched_unij_ols$"dp_p"
    )
)

light_fts <- c(
    "sex",
    "brain_volume",
    "household_income",
    "race",
    "parent_antisocial",
    "weekday_screentime",
    "activities_last_year",
    "cbcl_aggressive",
    "sds_sleep"
)

all_light_unij_plots[[1]]

all_light_unij_plots <- top_unij_pl[light_fts]
newsize <- 3
all_light_unij_plots <- lapply(
    seq_along(all_light_unij_plots),
    function(x) {
        all_light_unij_plots[[x]] <- all_light_unij_plots[[x]] + theme(
            legend.title = element_text(size = 14),
            legend.text = element_text(size = 14),
            axis.title.x = element_blank()
        )
        if (x %in% c(2, 3, 5, 6, 7, 8, 9)) {
            # Categorical features
            all_light_unij_plots[[x]]$"layers"[[3]]$"aes_params"$"size" <- 3
        }
        if (x %in% c(1, 4)) {
            # Continuous / numeric features
            all_light_unij_plots[[x]]$"layers"[[2]]$"aes_params"$"size" <- 5
        }
        all_light_unij_plots[[x]]
    }
)
names(all_light_unij_plots) <- light_fts
axis_fs <- 14
all_light_unij_plots$"sex" <- all_light_unij_plots$"sex" +
    labs(fill = "Sex", y = "%") +
    scale_fill_discrete(labels = c("F", "M")) +
    theme(axis.title.y = ggplot2::element_text(size = axis_fs, angle = 90), legend.position = "left")
all_light_unij_plots$"brain_volume" <- all_light_unij_plots$"brain_volume" + labs(y = "Brain\nVolume (cm³)") + theme(axis.title.y = ggplot2::element_text(angle = 90, size = axis_fs)) + scale_y_continuous(labels = function(x) x / 1000)
all_light_unij_plots$"household_income" <- all_light_unij_plots$"household_income" + labs(y = "Household\nIncome") + theme(axis.title.y = ggplot2::element_text(angle = 90, size = axis_fs))
all_light_unij_plots$"activities_last_year" <- all_light_unij_plots$"activities_last_year" + labs(y = "Activities Last\nYear (Quartile)") + theme(axis.title.y = ggplot2::element_text(angle = 90, size = axis_fs))
all_light_unij_plots$"parent_antisocial" <- all_light_unij_plots$"parent_antisocial" + labs(y = "Parent\nAntisocial") + theme(axis.title.y = ggplot2::element_text(angle = 90, size = axis_fs))
all_light_unij_plots$"race" <- all_light_unij_plots$"race" + labs(fill = "Race", y = "%") + theme(axis.title.y = ggplot2::element_text(angle = 90, size = axis_fs), legend.position = "left")
all_light_unij_plots$"weekday_screentime" <- all_light_unij_plots$"weekday_screentime" + labs(y = "Weekday\nScreentime\n(hours)") + theme(axis.title.y = ggplot2::element_text(angle = 90, size = axis_fs))
all_light_unij_plots$"cbcl_aggressive" <- all_light_unij_plots$"cbcl_aggressive" + labs(y = "CBCL\nAggressive") + theme(axis.title.y = ggplot2::element_text(angle = 90, size = axis_fs))
all_light_unij_plots$"sds_sleep" <- all_light_unij_plots$"sds_sleep" + labs(y = "Total Sleeping\nProblems") + theme(axis.title.y = ggplot2::element_text(angle = 90, size = axis_fs), legend.position = "none")
all_light_unij_plots$"race" <- all_light_unij_plots$"race" + scale_fill_discrete(labels = c("Black", "Hispanic", "Other", "White"))
all_light_unij_plots |>
    wrap_plots() |>
    ggsave(
        filename = fig_path("unij_top_match_light.png", TRUE),
        w = 10,
        h = 6,
        dpi = 300
    )

afts <- readRDS(proc_path("2025_06_11_afts.rds"))
top_unij_pl_wrapped <- wrap_plots(top_unij_pl[intersect(afts, names(top_unij_pl))])

ggsave(
    fig_path("top_unij_pl_wrapped.png", TRUE),
    top_unij_pl_wrapped,
    width = 45,
    height = 20,
    dpi = 50
)
```
