# Longitudinal analyses

1. Was the baseline clustering informative for long-term outcomes?

2. Did the matched uninjured subjects experience more mTBIs by T2 than the other uninjured subjects?

3. Clustering of the longitudinal sample with their baseline vs. their longitudinal data: both equally informative?

4. Classifier built from baseline mTBI data: informative?

## Data importing

```{r}
library(abcdutils)
library(here)
library(dplyr)
library(readr)
library(metasnf)
library(rlist)
library(visdat)
library(ggplot2)
library(mice)
library(fastDummies)
library(randomForest)
library(patchwork)
library(tidyr)
library(ComplexHeatmap)

# The path_maker function helps with managing and date stamping long paths. The
# functions are just used here to help with reading and writing data. See
# ?path_maker for more information.
input_path <- path_maker(here(paste0("data/abcd/inputs")))
core_path <- path_maker(here(paste0("data/abcd/core")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
model_path <- path_maker(here(paste0("data/abcd/results/models")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))

read <- function(path) {
    return(read_csv(input_path(path)))
}
```

## Q1: Was the baseline clustering informative for LT outcomes?

```{r}
# Import data
mtbi_base_df <- readRDS(proc_path("2025_02_13_mtbi_ful_df.rds"))
all_long_dls <- readRDS(input_path("2025_03_10_all_long_dls.rds"))
all_dls <- readRDS(input_path("2025_02_10_all_dls.rds"))
```

```{r}
base_mtbi_l_ols <- all_long_dls$"base_mtbi_l_ols"
base_mtbi_l_dls <- all_long_dls$"base_mtbi_l_dls"

# Convert list of data lists into list of data frames for plotting
base_mtbi_l_ol_dfs <- lapply(base_mtbi_l_ols, as.data.frame)
base_mtbi_l_dl_dfs <- lapply(base_mtbi_l_dls, as.data.frame)

# Tag each data frame with its originating imputation
base_mtbi_l_ol_dfs <- lapply(
    1:5,
    function(x) {
        base_mtbi_l_ol_dfs[[x]]$"imputation" <- x
        base_mtbi_l_ol_dfs[[x]]
    }
)

base_mtbi_l_dl_dfs <- lapply(
    1:5,
    function(x) {
        base_mtbi_l_dl_dfs[[x]]$"imputation" <- x
        base_mtbi_l_dl_dfs[[x]]
    }
)

# Horizontally merge list of data frames
base_mtbi_l_ol_df <- do.call(rbind, base_mtbi_l_ol_dfs)
base_mtbi_l_dl_df <- do.call(rbind, base_mtbi_l_dl_dfs)

mtbi_base_df2 <- mtbi_base_df |>
    dplyr::select(uid, cluster, dplyr::everything())
# Keep track of baseline data before attaching to longitudinal data
colnames(mtbi_base_df2) <- paste0(colnames(mtbi_base_df2), "_0")
mtbi_base_df2 <- mtbi_base_df2 |>
    dplyr::rename(
        "uid" = "uid_0",
        "cluster" = "cluster_0",
        "sex" = "sex_0",
        "race" = "race_0"
    )

base_mtbi_l_df <- dplyr::full_join(
    base_mtbi_l_ol_df,
    base_mtbi_l_dl_df,
    by = c("uid", "imputation")
)
colnames(base_mtbi_l_df) <- paste0(colnames(base_mtbi_l_df), "_l")
base_mtbi_l_df <- base_mtbi_l_df |>
    dplyr::rename(
        "uid" = "uid_l",
        "imputation" = "imputation_l"
    )
mtbi_long_changes <- dplyr::full_join(
    mtbi_base_df2,
    base_mtbi_l_df,
    by = "uid"
)

original_names <- gsub("_0", "", colnames(mtbi_base_df2)[-c(1:2)])

original_names <- original_names[!grepl("mtbi", original_names)]

replace_names <- original_names[!grepl("race", original_names)]

replace_names <- replace_names[!grepl("sex", replace_names)]

mtbi_long_changes |> colnames()

for (name in replace_names) {
    print(name)
    long_val <- mtbi_long_changes[[paste0(name, "_l")]]
    base_val <- mtbi_long_changes[[paste0(name, "_0")]]
    mtbi_long_changes[[paste0(name, "_d")]] <- long_val - base_val
}
mtbi_long_changes$"cluster" <- as.factor(mtbi_long_changes$"cluster")

saveRDS(mtbi_long_changes, proc_path("mtbi_long_changes.rds", TRUE))
mtbi_long_changes <- readRDS(proc_path("2025_03_25_mtbi_long_changes.rds"))
```

```{r}
# Some plotting functions
gg_long_cor_imp <- function(df, feature, long = TRUE) {
    f1 <- paste0(feature, "_0")
    if (long) {
        f2 <- paste0(feature, "_l")
    } else {
        f2 <- paste0(feature, "_d")
    }
    plot <- ggplot(
        df,
        aes(x = .data[[f1]], y = .data[[f2]])
    ) +
        geom_jitter(alpha = 0.2) +
        facet_wrap(~ imputation) +
        theme_bw()
    return(plot)
}

gg_long_cor <- function(df, feature, long = TRUE) {
    df <- dplyr::filter(df, imputation == 1)
    f1 <- paste0(feature, "_0")
    if (long) {
        f2 <- paste0(feature, "_l")
    } else {
        f2 <- paste0(feature, "_d")
    }
    plot <- ggplot(
        df,
        aes(
            x = .data[[f1]],
            y = .data[[f2]],
            colour = as.factor(cluster)
        )
    ) +
        geom_jitter(alpha = 0.5, height = 0.1, width = 0.1) +
        geom_smooth(method = "lm") +
        theme_bw() +
        labs(colour = "C")
    return(plot)
}


pubertal_status_y_plot <- gg_long_cor(mtbi_long_changes, "pubertal_status_y")
household_income_plot <- gg_long_cor(mtbi_long_changes, "household_income")
extracurriculars_plot <- gg_long_cor(mtbi_long_changes, "extracurriculars")
parent_perstr_plot <- gg_long_cor(mtbi_long_changes, "parent_perstr")
activities_last_year_plot <- gg_long_cor(mtbi_long_changes, "activities_last_year")
considerate_y_plot <- gg_long_cor(mtbi_long_changes, "considerate_y")
# looks kind of like an interaction?
school_activities_plot <- gg_long_cor(mtbi_long_changes, "school_activities")
weekend_screentime_plot <- gg_long_cor(mtbi_long_changes, "weekend_screentime")
family_throw_y_plot <- gg_long_cor(mtbi_long_changes, "family_throw_y")

significant_long_cor_plot <- pubertal_status_y_plot +
household_income_plot +
extracurriculars_plot +
parent_perstr_plot +
activities_last_year_plot +
considerate_y_plot +
school_activities_plot +
weekend_screentime_plot +
family_throw_y_plot

ggsave(
    fig_path("significant_long_cor_plot.png", TRUE),
    significant_long_cor_plot,
    width = 15,
    height = 10
)

cbcl_anxdep_plot <- gg_long_cor(mtbi_long_changes, "cbcl_anxdep", 0)
cbcl_withdep_plot <- gg_long_cor(mtbi_long_changes, "cbcl_withdep", 0)
cbcl_somatic_plot <- gg_long_cor(mtbi_long_changes, "cbcl_somatic", 0)
cbcl_social_plot <- gg_long_cor(mtbi_long_changes, "cbcl_social", 0)
cbcl_thought_plot <- gg_long_cor(mtbi_long_changes, "cbcl_thought", 0)
cbcl_attention_plot <- gg_long_cor(mtbi_long_changes, "cbcl_attention", 0)
cbcl_rulebreak_plot <- gg_long_cor(mtbi_long_changes, "cbcl_rulebreak", 0)
cbcl_aggressive_plot <- gg_long_cor(mtbi_long_changes, "cbcl_aggressive", 0)
sds_sleep_plot <- gg_long_cor(mtbi_long_changes, "sds_sleep", 0)

outcome_long_cor_plot <- cbcl_anxdep_plot +
cbcl_withdep_plot +
cbcl_somatic_plot +
cbcl_social_plot +
cbcl_thought_plot +
cbcl_attention_plot +
cbcl_rulebreak_plot +
cbcl_aggressive_plot +
sds_sleep_plot

ggsave(
    fig_path("outcome_long_cor_plot.png", TRUE),
    outcome_long_cor_plot,
    width = 15,
    height = 10
)

cbcl_anxdep_plot2 <- gg_long_cor(mtbi_long_changes, "cbcl_anxdep")
cbcl_withdep_plot2 <- gg_long_cor(mtbi_long_changes, "cbcl_withdep")
cbcl_somatic_plot2 <- gg_long_cor(mtbi_long_changes, "cbcl_somatic")
cbcl_social_plot2 <- gg_long_cor(mtbi_long_changes, "cbcl_social")
cbcl_thought_plot2 <- gg_long_cor(mtbi_long_changes, "cbcl_thought")
cbcl_attention_plot2 <- gg_long_cor(mtbi_long_changes, "cbcl_attention")
cbcl_rulebreak_plot2 <- gg_long_cor(mtbi_long_changes, "cbcl_rulebreak")
cbcl_aggressive_plot2 <- gg_long_cor(mtbi_long_changes, "cbcl_aggressive")
sds_sleep_plot2 <- gg_long_cor(mtbi_long_changes, "sds_sleep")

outcome_long_cor_plot2 <- cbcl_anxdep_plot2 +
cbcl_withdep_plot2 +
cbcl_somatic_plot2 +
cbcl_social_plot2 +
cbcl_thought_plot2 +
cbcl_attention_plot2 +
cbcl_rulebreak_plot2 +
cbcl_aggressive_plot2 +
sds_sleep_plot2

ggsave(
    fig_path("outcome_long_cor_plot2.png", TRUE),
    outcome_long_cor_plot2,
    width = 15,
    height = 10
)


gg_long_cor(mtbi_long_changes, "cbcl_anxdep", 0)

gg_long_cor(mtbi_long_changes, "cbcl_withdep")

gg_long_cor(mtbi_long_changes, "cbcl_somatic")

gg_long_cor(mtbi_long_changes, "cbcl_anxdep")

gg_long_cor(mtbi_long_changes, "cbcl_withdep")

gg_long_cor(mtbi_long_changes, "cbcl_somatic")

gg_long_cor(mtbi_long_changes, "cbcl_social")

gg_long_cor(mtbi_long_changes, "cbcl_thought")

gg_long_cor(mtbi_long_changes, "cbcl_attention")

gg_long_cor(mtbi_long_changes, "cbcl_rulebreak")

gg_long_cor(mtbi_long_changes, "cbcl_aggressive")

gg_long_cor(mtbi_long_changes, "sds_sleep")

gg_long_cor(mtbi_long_changes, "cbcl_withdep", 0)

gg_long_cor(mtbi_long_changes, "cbcl_somatic", 0)

gg_long_cor(mtbi_long_changes, "cbcl_anxdep", 0)

gg_long_cor(mtbi_long_changes, "cbcl_withdep", 0)

gg_long_cor(mtbi_long_changes, "cbcl_somatic", 0)

gg_long_cor(mtbi_long_changes, "cbcl_social", 0)

gg_long_cor(mtbi_long_changes, "cbcl_thought", 0)

gg_long_cor(mtbi_long_changes, "cbcl_attention", 0)

gg_long_cor(mtbi_long_changes, "cbcl_rulebreak", 0)

gg_long_cor(mtbi_long_changes, "cbcl_aggressive", 0)

gg_long_cor(mtbi_long_changes, "sds_sleep", 0)

gg_long_cor(mtbi_long_changes, "parent_perstr", 0)

gg_long_cor(mtbi_long_changes, "activities_last_year")

gg_long_cor(mtbi_long_changes, "pubertal_status_y")

gg_long_cor(mtbi_long_changes, "pubertal_status_p")

gg_long_cor(mtbi_long_changes, "school_activities")

gg_long_cor(mtbi_long_changes, "weekend_screentime")

gg_long_cor(mtbi_long_changes, "household_income")

cor_mat <- mtbi_long_changes |>
    dplyr::select(-uid, -mtbi_mechanism_0, -race_l) |>
    dplyr::rename("race" = "race_0") |>
    dplyr::mutate(cluster = as.numeric(cluster)) |>
    dummy_cols(
        select_columns = "race",
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = TRUE
    ) |>
    cor()

cor_mat[!grepl("_d$|_l$", colnames(cor_mat)), grepl("_d$", colnames(cor_mat))] |>
    Heatmap()

cor_mat["cluster", grepl("_d$", colnames(cor_mat))] |>
    Heatmap()

lm_long_fit <- function(df, feature) {
    models <- list(
      lm(as.formula(paste0(feature, "_l ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 1)),
      lm(as.formula(paste0(feature, "_l ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 2)),
      lm(as.formula(paste0(feature, "_l ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 3)),
      lm(as.formula(paste0(feature, "_l ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 4)),
      lm(as.formula(paste0(feature, "_l ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 5))
    )
    pooled_results <- pool(as.mira(models))
    return(summary(pooled_results))
}

replace_names

pval_df <- data.frame()
for (feature in replace_names) {
    model <- lm_long_fit(mtbi_long_changes, feature)
    pval_df <- rbind(
        pval_df,
        data.frame(
            feature = c(feature, feature),
            compare = c("c1_vs_c2", "c1_vs_c3"),
            p = c(model$"p.value"[3], model$"p.value"[4])
        )
    )
    if (min(model$"p.value"[3]) < 0.05) {
        cat("\n", feature, signif(model$"p.value"[3], 2), "\n")
        print(model)
    }
}
pval_df$"padj" <- p.adjust(pval_df$"p", method = "fdr")

pval_df |>
    dplyr::filter(padj < 0.05) |>
    dplyr::select(-p) |>
    dplyr::mutate(padj = format(padj, scientific = FALSE, digits = 2)) |>
    dplyr::arrange(padj)



gg_long_cor(mtbi_long_changes, "parent_perstr")

gg_long_cor(mtbi_long_changes, "pubertal_status_y", 0)

cor_mat

# None are significant
lm_long_fit(mtbi_long_changes, "cbcl_anxdep")

lm_long_fit(mtbi_long_changes, "cbcl_withdep")

lm_long_fit(mtbi_long_changes, "cbcl_somatic")

lm_long_fit(mtbi_long_changes, "cbcl_social")

lm_long_fit(mtbi_long_changes, "cbcl_thought")

lm_long_fit(mtbi_long_changes, "cbcl_attention")

lm_long_fit(mtbi_long_changes, "cbcl_rulebreak")

lm_long_fit(mtbi_long_changes, "cbcl_aggressive")

lm_long_fit(mtbi_long_changes, "sds_sleep")


colnames(mtbi_long_changes)


# Checking just in baseline now...
lm_short_fit <- function(df, ft1, ft2) {
    models <- list(
      lm(as.formula(paste0(feature, "_0 ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 1)),
      lm(as.formula(paste0(feature, "_0 ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 2)),
      lm(as.formula(paste0(feature, "_0 ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 3)),
      lm(as.formula(paste0(feature, "_0 ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 4)),
      lm(as.formula(paste0(feature, "_0 ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 5))
    )
    pooled_results <- pool(as.mira(models))
    return(summary(pooled_results))
}
```

Cluster is never a significant feature in predicting longitudinal outcome given baseline outcome.

### Q2. Did the matched uninjured subjects experience more mTBIs by T2 than the other uninjured subjects?

```{r}
matched_unij_nearest_esdf <- readRDS(proc_path("2025_02_16_matched_unij_nearest_esdf.rds"))

# Those who exhibited heterogeneity most similar to the baseline mTBI group
matched_subs <- uids(matched_unij_nearest_esdf)
matched_subs <- gsub("uid_", "", matched_subs)

# Those who never sustained a head injury prior to T2
# N = 7678
long_unij_subs <- read_subjects(sub_path("2025_02_07_unij_subs_0_to_2.csv"))

# Those who sustained a head injury between 0 and T2
# N = 220
long_mtbi_subs <- read_subjects(sub_path("2025_02_07_mtbi_subs_0_to_2.csv"))

# The pool of all baseline uninjured subjects
# N = 9349
base_unij_subs <- read_subjects(sub_path("2025_02_07_unij_subs.csv"))
```

Let's consider being in the matched group vs. not being in the matched group as exposed vs. unexposed, and ending up in the mTBI sample as outcome vs. no outcome.
Then I calculate the odds ratio and 95% CI of being in the mTBI sample based on being in the matched group.

```{r}
# Calculation 1: Explicitly looking for people that ended up in mTBI sample
matched_that_became_mtbi <- sum(matched_subs %in% long_mtbi_subs)
unmatched_that_became_mtbi <- sum(non_matched_subs %in% long_mtbi_subs)
matched_that_remained_unij <- sum(!matched_subs %in% long_mtbi_subs)
unmatched_that_remained_unij <- sum(!non_matched_subs %in% long_mtbi_subs)

data_matrix <- matrix(
    c(
        matched_that_became_mtbi, matched_that_remained_unij,
        unmatched_that_became_mtbi, unmatched_that_remained_unij
    ),
    nrow = 2,
    byrow = TRUE
)
rownames(data_matrix) <- c("Matched", "Unmatched")
colnames(data_matrix) <- c("Injured", "Remained Uninjured")
chi_result <- chisq.test(data_matrix, correct = FALSE)
print(chi_result)

matched_that_became_mtbi_frac <- mean(matched_subs %in% long_mtbi_subs)
unmatched_that_became_mtbi_frac <- mean(non_matched_subs %in% long_mtbi_subs)
matched_that_remained_unij_frac <- mean(!matched_subs %in% long_mtbi_subs)
unmatched_that_remained_unij_frac <- mean(!non_matched_subs %in% long_mtbi_subs)

matched_that_became_mtbi_frac #0.01372998

unmatched_that_became_mtbi_frac #0.01649461
```

No significant difference in the proportion of matched uninjured subjects to unmatched uninjured subjects that ended up in the longitudinal mTBI group (1.3% vs. 1.6%, uncorrected Chi-squared test p-value = 0.6565).

Now I'll double check to see if there were any attributes of subjects that were particularly closely associated with membership in the longitudinal mTBI sample.

```{r}
long_mtbi_0_dl <- all_long_dls$"long_mtbi_0_dls"[[1]]

base_unij_0_dl <- all_dls$"unij_pooled_data_lists"[[1]]

long_unij_0_dl <- base_unij_0_dl |>
    dlapply(
        function(x) {
            x$"data" <- dplyr::filter(x$"data", uid %in% paste0("uid_", long_unij_subs))
            return(x)
        }
    )

long_unij_df <- as.data.frame(long_unij_0_dl)

long_mtbi_df <- as.data.frame(long_mtbi_0_dl)

long_unij_df$"mtbi" <- 0
long_mtbi_df$"mtbi" <- 1

long_corr_df <- rbind(long_unij_df, long_mtbi_df)

saveRDS(long_corr_df, proc_path("long_corr_df.rds", TRUE))

long_corr_df <- readRDS(proc_path("2025_02_16_long_corr_df.rds"))

# Correlation matrix examining how correlated each feature is with being assigned to mTBI group
long_corr_mat <- long_corr_df |>
    dplyr::select(-uid) |>
    dummy_cols(
        select_columns = "race",
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = TRUE
    ) |>
    cor()

mtbi_corr_mat <- long_corr_mat[rownames(mtbi_corr_mat) != "mtbi", "mtbi", drop = FALSE]

mtbi_corr_mat |>
    ComplexHeatmap::Heatmap()

mtbi_corr_mat |>
    as.data.frame() |>
    dplyr::arrange(mtbi)

long_corr_df |>
    ggplot(aes(x = factor(mtbi), y = major_wm_ndi)) +
    geom_jitter() +
    theme_bw()


long_corr_clean_df <- long_corr_df |>
    dplyr::select(-uid) |>
    dummy_cols(
        select_columns = "race",
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = TRUE
    )

pvalue_df <- data.frame()
for (col in colnames(long_corr_clean_df)) {
    test_results <- cor.test(long_corr_clean_df$"mtbi", long_corr_clean_df[[col]])
    pval <- test_results$"p.value"
    est <- test_results$"estimate"
    l <- test_results$"conf.int"[1]
    u <- test_results$"conf.int"[2]
    pvalue_df <- rbind(
        pvalue_df,
        data.frame(
            feature = col,
            pval = pval,
            est = est,
            l = l,
            u = u
        )
    )
}
rownames(pvalue_df) <- NULL
p_values_bonferroni <- p.adjust(pvalue_df$"pval", method = "bonferroni")
p_values_fdr <- p.adjust(pvalue_df$"pval", method = "fdr")
pvalue_df$"pval_bon" <- p_values_bonferroni
pvalue_df$"pval_fdr" <- p_values_fdr
pvalue_df <- pvalue_df |>
    dplyr::arrange(pval) |>
    dplyr::filter(feature != "mtbi") |>
    dplyr::select(feature, pval, pval_bon, pval_fdr, est, l, u)

write_csv(pvalue_df, proc_path("pvalue_df.csv", TRUE))
pvalue_df <- read_csv(proc_path("2025_02_16_pvalue_df.csv"))
```

Quite a few features there that remain significant even after bonferroni correction.
There certainly seem to be factors that increase a child's risk of sustaining an mTBI.
These are all taken from the same data collection period as well!

### Q3. Clustering of the longitudinal sample with their baseline vs. their longitudinal data: both equally informative?

Can perhaps skip this and just make use of the classifier.

```{r}
long_mtbi_0_dls <- all_long_dls$"long_mtbi_0_dls"
long_mtbi_0_ols <- all_long_dls$"long_mtbi_0_ols"

long_mtbi_l_dls <- all_long_dls$"long_mtbi_l_dls"
long_mtbi_l_ols <- all_long_dls$"long_mtbi_l_ols"
```


```{r}
long_config <- snf_config(
    long_mtbi_0_dls[[1]],
    n_solutions = 200,
    cnt_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    dsc_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ord_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    use_default_dist_fns = TRUE
)

saveRDS(long_config, proc_path("long_config.rds", TRUE))
```


```{r}
# CHECKPOINT
long_config <- readRDS(proc_path("2025_04_28_long_config.rds"))
```

```{r}
progressr::with_progress({long_mtbi_0_sol_df_s1 <- batch_snf(dl = long_mtbi_0_dls[[1]], sc = long_config, processes = "max")})
saveRDS(long_mtbi_0_sol_df_s1, proc_path("long_mtbi_0_sol_df_s1.rds", TRUE))
progressr::with_progress({long_mtbi_0_sol_df_s2 <- batch_snf(dl = long_mtbi_0_dls[[2]], sc = long_config, processes = "max")})
saveRDS(long_mtbi_0_sol_df_s2, proc_path("long_mtbi_0_sol_df_s2.rds", TRUE))
progressr::with_progress({long_mtbi_0_sol_df_s3 <- batch_snf(dl = long_mtbi_0_dls[[3]], sc = long_config, processes = "max")})
saveRDS(long_mtbi_0_sol_df_s3, proc_path("long_mtbi_0_sol_df_s3.rds", TRUE))
progressr::with_progress({long_mtbi_0_sol_df_s4 <- batch_snf(dl = long_mtbi_0_dls[[4]], sc = long_config, processes = "max")})
saveRDS(long_mtbi_0_sol_df_s4, proc_path("long_mtbi_0_sol_df_s4.rds", TRUE))
progressr::with_progress({long_mtbi_0_sol_df_s5 <- batch_snf(dl = long_mtbi_0_dls[[5]], sc = long_config, processes = "max")})
saveRDS(long_mtbi_0_sol_df_s5, proc_path("long_mtbi_0_sol_df_s5.rds", TRUE))
progressr::with_progress({long_mtbi_l_sol_df_s1 <- batch_snf(dl = long_mtbi_l_dls[[1]], sc = long_config, processes = "max")})
saveRDS(long_mtbi_l_sol_df_s1, proc_path("long_mtbi_l_sol_df_s1.rds", TRUE))
progressr::with_progress({long_mtbi_l_sol_df_s2 <- batch_snf(dl = long_mtbi_l_dls[[2]], sc = long_config, processes = "max")})
saveRDS(long_mtbi_l_sol_df_s2, proc_path("long_mtbi_l_sol_df_s2.rds", TRUE))
progressr::with_progress({long_mtbi_l_sol_df_s3 <- batch_snf(dl = long_mtbi_l_dls[[3]], sc = long_config, processes = "max")})
saveRDS(long_mtbi_l_sol_df_s3, proc_path("long_mtbi_l_sol_df_s3.rds", TRUE))
progressr::with_progress({long_mtbi_l_sol_df_s4 <- batch_snf(dl = long_mtbi_l_dls[[4]], sc = long_config, processes = "max")})
saveRDS(long_mtbi_l_sol_df_s4, proc_path("long_mtbi_l_sol_df_s4.rds", TRUE))
progressr::with_progress({long_mtbi_l_sol_df_s5 <- batch_snf(dl = long_mtbi_l_dls[[5]], sc = long_config, processes = "max")})
saveRDS(long_mtbi_l_sol_df_s5, proc_path("long_mtbi_l_sol_df_s5.rds", TRUE))
```

```{r}
long_mtbi_0_sol_df_s1 <- readRDS(proc_path("2025_04_28_long_mtbi_0_sol_df_s1.rds"))
long_mtbi_0_sol_df_s2 <- readRDS(proc_path("2025_04_28_long_mtbi_0_sol_df_s2.rds"))
long_mtbi_0_sol_df_s3 <- readRDS(proc_path("2025_04_28_long_mtbi_0_sol_df_s3.rds"))
long_mtbi_0_sol_df_s4 <- readRDS(proc_path("2025_04_28_long_mtbi_0_sol_df_s4.rds"))
long_mtbi_0_sol_df_s5 <- readRDS(proc_path("2025_04_28_long_mtbi_0_sol_df_s5.rds"))

long_mtbi_0_sol_df <- do.call(
    "rbind",
    c(
        list(
            long_mtbi_0_sol_df_s1,
            long_mtbi_0_sol_df_s2,
            long_mtbi_0_sol_df_s3,
            long_mtbi_0_sol_df_s4,
            long_mtbi_0_sol_df_s5
        ),
        list(reset_indices = TRUE)
    )
)
saveRDS(long_mtbi_0_sol_df, proc_path("long_mtbi_0_sol_df.rds", TRUE))
```

```{r}
long_mtbi_0_ari <- calc_aris(long_mtbi_0_sol_df, processes = "max")
saveRDS(long_mtbi_0_ari, proc_path("long_mtbi_0_ari.rds", TRUE))

long_mtbi_0_ari_order <- get_matrix_order(long_mtbi_0_ari)
write_csv(data.frame(long_mtbi_0_ari_order), proc_path("long_mtbi_0_ari_order.csv", TRUE))
```

```{r}
long_mtbi_l_sol_df_s1 <- readRDS(proc_path("2025_02_18_long_mtbi_l_sol_df_s1.rds"))
long_mtbi_l_sol_df_s2 <- readRDS(proc_path("2025_02_18_long_mtbi_l_sol_df_s2.rds"))
long_mtbi_l_sol_df_s3 <- readRDS(proc_path("2025_02_18_long_mtbi_l_sol_df_s3.rds"))
long_mtbi_l_sol_df_s4 <- readRDS(proc_path("2025_02_18_long_mtbi_l_sol_df_s4.rds"))
long_mtbi_l_sol_df_s5 <- readRDS(proc_path("2025_02_18_long_mtbi_l_sol_df_s5.rds"))

long_mtbi_l_sol_df <- do.call(
    "rbind",
    c(
        list(
            long_mtbi_l_sol_df_s1,
            long_mtbi_l_sol_df_s2,
            long_mtbi_l_sol_df_s3,
            long_mtbi_l_sol_df_s4,
            long_mtbi_l_sol_df_s5
        ),
        list(reset_indices = TRUE)
    )
)
saveRDS(long_mtbi_l_sol_df, proc_path("long_mtbi_l_sol_df.rds", TRUE))
long_mtbi_l_ari <- calc_aris(long_mtbi_l_sol_df, processes = "max")
saveRDS(long_mtbi_l_ari, proc_path("long_mtbi_l_ari.rds", TRUE))
long_mtbi_l_ari_order <- get_matrix_order(long_mtbi_l_ari)
write_csv(data.frame(long_mtbi_l_ari_order), proc_path("long_mtbi_l_ari_order.csv", TRUE))
# HERE I AM 2025_04_28
```

```{r}
# CHECKPOINT
long_mtbi_0_sol_df <- readRDS(proc_path("2025_04_28_long_mtbi_0_sol_df.rds"))
long_mtbi_0_ari <- readRDS(proc_path("2025_04_28_long_mtbi_0_ari.rds"))
long_mtbi_0_ari_order <- unlist(read_csv(proc_path("2025_04_28_long_mtbi_0_ari_order.csv")))
names(long_mtbi_0_ari_order) <- NULL

long_mtbi_l_sol_df <- readRDS(proc_path("2025_04_28_long_mtbi_l_sol_df.rds"))
long_mtbi_l_ari <- readRDS(proc_path("2025_04_28_long_mtbi_l_ari.rds"))
long_mtbi_l_ari_order <- unlist(read_csv(proc_path("2025_04_28_long_mtbi_l_ari_order.csv")))
names(long_mtbi_l_ari_order) <- NULL
```

```{r}
# Solo imputation 1
progressr::with_progress({
long_mtbi_0_ext_sol_df_s1 <- extend_solutions(
    long_mtbi_0_sol_df[1:200, ],
    dl = long_mtbi_0_dls[[1]],
    target_dl = long_mtbi_0_ols[[1]],
    min_pval = 1e-10,
    processes = "max"
)
})
saveRDS(long_mtbi_0_ext_sol_df_s1, proc_path("long_mtbi_0_ext_sol_df_s1.rds", TRUE))
# Solo imputation 2
progressr::with_progress({
long_mtbi_0_ext_sol_df_s2 <- extend_solutions(
    long_mtbi_0_sol_df[201:400, ],
    dl = long_mtbi_0_dls[[2]],
    target_dl = long_mtbi_0_ols[[2]],
    min_pval = 1e-10,
    processes = "max"
)
})
saveRDS(long_mtbi_0_ext_sol_df_s2, proc_path("long_mtbi_0_ext_sol_df_s2.rds", TRUE))
# Solo imputation 3
progressr::with_progress({
long_mtbi_0_ext_sol_df_s3 <- extend_solutions(
    long_mtbi_0_sol_df[401:600, ],
    dl = long_mtbi_0_dls[[3]],
    target_dl = long_mtbi_0_ols[[3]],
    min_pval = 1e-10,
    processes = "max"
)
})
saveRDS(long_mtbi_0_ext_sol_df_s3, proc_path("long_mtbi_0_ext_sol_df_s3.rds", TRUE))
# Solo imputation 4
progressr::with_progress({
long_mtbi_0_ext_sol_df_s4 <- extend_solutions(
    long_mtbi_0_sol_df[601:800, ],
    dl = long_mtbi_0_dls[[4]],
    target_dl = long_mtbi_0_ols[[4]],
    min_pval = 1e-10,
    processes = "max"
)
})
saveRDS(long_mtbi_0_ext_sol_df_s4, proc_path("long_mtbi_0_ext_sol_df_s4.rds", TRUE))
# Solo imputation 5
progressr::with_progress({
long_mtbi_0_ext_sol_df_s5 <- extend_solutions(
    long_mtbi_0_sol_df[801:1000, ],
    dl = long_mtbi_0_dls[[5]],
    target_dl = long_mtbi_0_ols[[5]],
    min_pval = 1e-10,
    processes = "max"
)
})
saveRDS(long_mtbi_0_ext_sol_df_s5, proc_path("long_mtbi_0_ext_sol_df_s5.rds", TRUE))
```

```{r}
# Solo imputation 1
long_mtbi_l_ext_sol_df_s1 <- extend_solutions(
    long_mtbi_l_sol_df[1:200, ],
    dl = long_mtbi_l_dls[[1]],
    target_dl = long_mtbi_l_ols[[1]],
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(long_mtbi_l_ext_sol_df_s1, proc_path("long_mtbi_l_ext_sol_df_s1.rds", TRUE))
# Solo imputation 2
long_mtbi_l_ext_sol_df_s2 <- extend_solutions(
    long_mtbi_l_sol_df[201:400, ],
    dl = long_mtbi_l_dls[[2]],
    target_dl = long_mtbi_l_ols[[2]],
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(long_mtbi_l_ext_sol_df_s2, proc_path("long_mtbi_l_ext_sol_df_s2.rds", TRUE))
# Solo imputation 3
long_mtbi_l_ext_sol_df_s3 <- extend_solutions(
    long_mtbi_l_sol_df[401:600, ],
    dl = long_mtbi_l_dls[[3]],
    target_dl = long_mtbi_l_ols[[3]],
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(long_mtbi_l_ext_sol_df_s3, proc_path("long_mtbi_l_ext_sol_df_s3.rds", TRUE))
# Solo imputation 4
long_mtbi_l_ext_sol_df_s4 <- extend_solutions(
    long_mtbi_l_sol_df[601:800, ],
    dl = long_mtbi_l_dls[[4]],
    target_dl = long_mtbi_l_ols[[4]],
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(long_mtbi_l_ext_sol_df_s4, proc_path("long_mtbi_l_ext_sol_df_s4.rds", TRUE))
# Solo imputation 5
long_mtbi_l_ext_sol_df_s5 <- extend_solutions(
    long_mtbi_l_sol_df[801:1000, ],
    dl = long_mtbi_l_dls[[5]],
    target_dl = long_mtbi_l_ols[[5]],
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(long_mtbi_l_ext_sol_df_s5, proc_path("long_mtbi_l_ext_sol_df_s5.rds", TRUE))
```

```{r}
long_mtbi_0_ext_sol_df_s1 <- readRDS(proc_path("2025_02_18_long_mtbi_0_ext_sol_df_s1.rds"))
long_mtbi_0_ext_sol_df_s2 <- readRDS(proc_path("2025_02_18_long_mtbi_0_ext_sol_df_s2.rds"))
long_mtbi_0_ext_sol_df_s3 <- readRDS(proc_path("2025_02_18_long_mtbi_0_ext_sol_df_s3.rds"))
long_mtbi_0_ext_sol_df_s4 <- readRDS(proc_path("2025_02_18_long_mtbi_0_ext_sol_df_s4.rds"))
long_mtbi_0_ext_sol_df_s5 <- readRDS(proc_path("2025_02_18_long_mtbi_0_ext_sol_df_s5.rds"))

long_mtbi_0_ext_sol_df <- do.call(
    "rbind",
    c(
        list(
            long_mtbi_0_ext_sol_df_s1,
            long_mtbi_0_ext_sol_df_s2,
            long_mtbi_0_ext_sol_df_s3,
            long_mtbi_0_ext_sol_df_s4,
            long_mtbi_0_ext_sol_df_s5
        ),
        list(reset_indices = TRUE)
    )
)

long_mtbi_l_ext_sol_df_s1 <- readRDS(proc_path("2025_02_18_long_mtbi_l_ext_sol_df_s1.rds"))
long_mtbi_l_ext_sol_df_s2 <- readRDS(proc_path("2025_02_18_long_mtbi_l_ext_sol_df_s2.rds"))
long_mtbi_l_ext_sol_df_s3 <- readRDS(proc_path("2025_02_18_long_mtbi_l_ext_sol_df_s3.rds"))
long_mtbi_l_ext_sol_df_s4 <- readRDS(proc_path("2025_02_18_long_mtbi_l_ext_sol_df_s4.rds"))
long_mtbi_l_ext_sol_df_s5 <- readRDS(proc_path("2025_02_18_long_mtbi_l_ext_sol_df_s5.rds"))

long_mtbi_l_ext_sol_df <- do.call(
    "rbind",
    c(
        list(
            long_mtbi_l_ext_sol_df_s1,
            long_mtbi_l_ext_sol_df_s2,
            long_mtbi_l_ext_sol_df_s3,
            long_mtbi_l_ext_sol_df_s4,
            long_mtbi_l_ext_sol_df_s5
        ),
        list(reset_indices = TRUE)
    )
)

saveRDS(long_mtbi_0_ext_sol_df, proc_path("long_mtbi_0_ext_sol_df.rds", TRUE))
saveRDS(long_mtbi_l_ext_sol_df, proc_path("long_mtbi_l_ext_sol_df.rds", TRUE))

long_mtbi_0_ext_sol_df <- readRDS(proc_path("2025_02_18_long_mtbi_0_ext_sol_df.rds"))
long_mtbi_l_ext_sol_df <- readRDS(proc_path("2025_02_18_long_mtbi_l_ext_sol_df.rds"))
```

```{r}
long_0_hm <- meta_cluster_heatmap(long_mtbi_0_ari, order = long_mtbi_0_ari_order)
long_l_hm <- meta_cluster_heatmap(long_mtbi_l_ari, order = long_mtbi_l_ari_order)

long_mtbi_0_esdf <- as.data.frame(long_mtbi_0_ext_sol_df)
long_mtbi_l_esdf <- as.data.frame(long_mtbi_l_ext_sol_df)

long_mtbi_0_esdf$"impairment_separation" <- -log10(long_mtbi_0_esdf$"mean_pval")
long_mtbi_l_esdf$"impairment_separation" <- -log10(long_mtbi_l_esdf$"mean_pval")

full_long_mtbi_0_ari_hm <- meta_cluster_heatmap(
    aris = long_mtbi_0_ari,
    order = long_mtbi_0_ari_order,
    data = long_mtbi_0_esdf,
    min_colour = "black",
    split_vector = c(
        569,
        698,
        778
    ),
    top_hm = list(
        "Impairment Separation" = "impairment_separation"
    ),
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    annotation_colours = list(
        "Impairment Separation" = colour_scale(
            long_mtbi_0_esdf$"impairment_separation",
            min_colour = "gray7",
            max_colour = "limegreen"
        )
    )
)
full_long_mtbi_0_ari_hm

full_long_mtbi_l_ari_hm <- meta_cluster_heatmap(
    aris = long_mtbi_l_ari,
    order = long_mtbi_l_ari_order,
    data = long_mtbi_l_esdf,
    min_colour = "black",
    split_vector = c(
        710,
        900
    ),
    top_hm = list(
        "Impairment Separation" = "impairment_separation"
    ),
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    annotation_colours = list(
        "Impairment Separation" = colour_scale(
            long_mtbi_l_esdf$"impairment_separation",
            min_colour = "gray7",
            max_colour = "limegreen"
        )
    )
)
full_long_mtbi_l_ari_hm
```

Neither option resulted in particularly similar cluster solution to the original mTBI sample.
Suggests that there may be something unique to the kids who had their injury at a much earlier timepoint.




### Q4. Classifier built from baseline mTBI data: informative?

```{r}
library(caret)
library(randomForest)

# Classifying data using baseline as well as longitudinal features
long_mtbi_0_dls <- all_long_dls$"long_mtbi_0_dls"
long_mtbi_l_dls <- all_long_dls$"long_mtbi_l_dls"
long_mtbi_0_ols <- all_long_dls$"long_mtbi_0_ols"
long_mtbi_l_ols <- all_long_dls$"long_mtbi_l_ols"

base_unij_l_dls <- all_long_dls$"base_unij_l_dls"
base_unij_l_ols <- all_long_dls$"base_unij_l_ols"

dls_to_dfs <- function(dls) {
    lapply(
        seq_along(dls),
        function(x) {
            as.data.frame(dls[[x]])
        }
    )
}

long_mtbi_0_dfs <- dls_to_dfs(long_mtbi_0_dls)
nrow(long_mtbi_0_dfs[[1]])
long_mtbi_l_dfs <- dls_to_dfs(long_mtbi_l_dls)
nrow(long_mtbi_l_dfs[[1]])
base_unij_l_dfs <- dls_to_dfs(base_unij_l_dls)
nrow(base_unij_l_dfs[[1]])

long_mtbi_0_df <- long_mtbi_0_dfs[[1]]
long_mtbi_l_df <- long_mtbi_l_dfs[[1]]
base_unij_l_df <- base_unij_l_dfs[[1]]

train_scale_df <- read_csv(proc_path("2025_02_17_train_scale_df.csv"))

# T0 temporal DF
temporal_df <- readRDS(proc_path("2025_02_17_temporal_df.rds"))

# T2 temporal DF
temporal_df2 <- readRDS(proc_path("2025_02_17_temporal_df2.rds"))

subtype_classifier <- readRDS(model_path("2025_02_17_subtype_classifier.rds"))
```

Assigning predicted clusters to three groups:

1. Longitudinal mTBI, pre-injury data
2. Longitudinal mTBI, post-injury data
3. Baseline uninjured group, ssimilarly post-injury data for context to see how it divvies up

```{r}
train_scale_df <- train_scale_df |>
    dplyr::select(-cluster)

long_unij_subs <- read_subjects(sub_path("2025_02_07_unij_subs_0_to_2.csv"))
long_unij_subs <- paste0("uid_", long_unij_subs)

long_mtbi_0_df <- long_mtbi_0_df[, colnames(train_scale_df)]
long_mtbi_l_df <- long_mtbi_l_df[, colnames(train_scale_df)]
long_unij_l_df <- base_unij_l_df[, colnames(train_scale_df)] |>
    dplyr::filter(uid %in% long_unij_subs)

temporal_df <- temporal_df |>
    dplyr::filter(!uid %in% long_mtbi_0_df$"uid")
temporal_df2 <- temporal_df2 |>
    dplyr::filter(!uid %in% long_mtbi_l_df$"uid")
temporal_df2 <- temporal_df2 |>
    dplyr::filter(!uid %in% long_unij_l_df$"uid")

scaling_df_0 <- dplyr::bind_rows(
    temporal_df,
    long_mtbi_0_df[, colnames(temporal_df)]
)

scaling_df_2 <- dplyr::bind_rows(
    temporal_df2,
    long_mtbi_l_df[, colnames(temporal_df2)],
    long_unij_l_df[, colnames(temporal_df2)]
)

scale_cols <- colnames(temporal_df)[2:ncol(temporal_df)]
scaling_df_0[scale_cols] <- sapply(scaling_df_0[scale_cols], scale)
scaling_df_2[scale_cols] <- sapply(scaling_df_2[scale_cols], scale)

long_mtbi_0_scaled_df <- long_mtbi_0_df |>
    dplyr::select(-dplyr::all_of(scale_cols)) |>
    dplyr::inner_join(scaling_df_0, by = "uid") |>
    data.frame()

long_mtbi_l_scaled_df <- long_mtbi_l_df |>
    dplyr::select(-dplyr::all_of(scale_cols)) |>
    dplyr::inner_join(scaling_df_2, by = "uid") |>
    data.frame()

long_unij_l_scaled_df <- long_unij_l_df |>
    dplyr::select(-dplyr::all_of(scale_cols)) |>
    dplyr::inner_join(scaling_df_2, by = "uid") |>
    data.frame()

write_csv(long_mtbi_0_scaled_df, proc_path("long_mtbi_0_scaled_df.csv", TRUE))
write_csv(long_mtbi_l_scaled_df, proc_path("long_mtbi_l_scaled_df.csv", TRUE))
write_csv(long_unij_l_scaled_df, proc_path("long_unij_l_scaled_df.csv", TRUE))

long_mtbi_0_scaled_df <- read_csv(proc_path("2025_02_17_long_mtbi_0_scaled_df.csv"))
long_mtbi_l_scaled_df <- read_csv(proc_path("2025_02_17_long_mtbi_l_scaled_df.csv"))
long_unij_l_scaled_df <- read_csv(proc_path("2025_02_17_long_unij_l_scaled_df.csv"))

make_pred_df <- function(df) {
    clean_df <- prep_data(df)
    df$"cluster" <- predict(subtype_classifier, newdata = clean_df)
    return(df)
}

long_mtbi_0_pred_df <- make_pred_df(long_mtbi_0_scaled_df)
long_mtbi_l_pred_df <- make_pred_df(long_mtbi_l_scaled_df)
long_unij_l_pred_df <- make_pred_df(long_unij_l_scaled_df)

write_csv(long_mtbi_0_pred_df, proc_path("long_mtbi_0_pred_df.csv", TRUE))
write_csv(long_mtbi_l_pred_df, proc_path("long_mtbi_l_pred_df.csv", TRUE))
write_csv(long_unij_l_pred_df, proc_path("long_unij_l_pred_df.csv", TRUE))

long_mtbi_0_pred_df <- read_csv(proc_path("2025_02_17_long_mtbi_0_pred_df.csv"))
long_mtbi_l_pred_df <- read_csv(proc_path("2025_02_17_long_mtbi_l_pred_df.csv"))
long_unij_l_pred_df <- read_csv(proc_path("2025_02_17_long_unij_l_pred_df.csv"))

long_mtbi_0_cluster_df <- long_mtbi_0_pred_df |> dplyr::select(uid, cluster)
long_mtbi_l_cluster_df <- long_mtbi_l_pred_df |> dplyr::select(uid, cluster)
long_unij_l_cluster_df <- long_unij_l_pred_df |> dplyr::select(uid, cluster)

# 17, 52, 31
long_mtbi_0_cluster_df$cluster |> table() |> prop.table() |> (\(x) 100 * x)()

# 16, 45, 39
long_mtbi_l_cluster_df$cluster |> table() |> prop.table() |> (\(x) 100 * x)()

# 21, 31, 47
long_unij_l_cluster_df$cluster |> table() |> prop.table() |> (\(x) 100 * x)()

# Compare with the original full solution proportions
mtbi_ful_df <- readRDS(proc_path("2025_02_13_mtbi_ful_df.rds"))

# 33, 36, 31
mtbi_ful_df$"cluster" |> table() |> prop.table() |> (\(x) 100 * x)()

classifier_fts <- read_csv(proc_path("2025_02_14_classifier_fts.csv"))$"classifier_fts"
outcomes <- readRDS(proc_path("2025_02_13_outputs.rds"))

relevant_fts <- c(classifier_fts, outcomes)

long_mtbi_0_plot_list <- auto_plot(
    cluster_df = data.frame(long_mtbi_0_cluster_df),
    dl = c(long_mtbi_0_dls[[1]], long_mtbi_0_ols[[1]])
)
long_mtbi_0_all_plots <- wrap_plots(long_mtbi_0_plot_list[relevant_fts])
ggsave(
    fig_path("long_mtbi_0_pred_scaled_plots.png", TRUE),
    long_mtbi_0_all_plots,
    width = 45,
    height = 30,
    dpi = 50
)

long_mtbi_l_plot_list <- auto_plot(
    cluster_df = data.frame(long_mtbi_l_cluster_df),
    dl = c(long_mtbi_l_dls[[1]], long_mtbi_l_ols[[1]])
)
long_mtbi_l_all_plots <- wrap_plots(long_mtbi_l_plot_list[relevant_fts])
ggsave(
    fig_path("long_mtbi_l_pred_scaled_plots.png", TRUE),
    long_mtbi_l_all_plots,
    width = 45,
    height = 30,
    dpi = 50
)

long_unij_l_dl <- base_unij_l_dls[[1]] |>
    dlapply(
        function(x) {
            x$"data" <- dplyr::filter(x$"data", uid %in% long_unij_subs)
            return(x)
        }
    )

long_unij_l_ol <- base_unij_l_ols[[1]] |>
    dlapply(
        function(x) {
            x$"data" <- dplyr::filter(x$"data", uid %in% long_unij_subs)
            return(x)
        }
    )

long_unij_l_plot_list <- auto_plot(
    cluster_df = data.frame(long_unij_l_cluster_df),
    dl = c(long_unij_l_dl, long_unij_l_ol)
)
long_unij_l_all_plots <- wrap_plots(long_unij_l_plot_list[relevant_fts])
ggsave(
    fig_path("long_unij_l_pred_scaled_plots.png", TRUE),
    long_unij_l_all_plots,
    width = 45,
    height = 30,
    dpi = 50
)
# Looks very similar!
```

Statistical analysis: bootstrapped similarity to baseline mTBI solution

```{r}
mtbi_gen_fts_in_long <- read_csv(proc_path("2025_02_13_mtbi_gen_fts_in_long.csv"))
mtbi_gen_fts_out_long <- read_csv(proc_path("2025_02_13_mtbi_gen_fts_out_long.csv"))
mtbi_gen_long <- rbind(
    mtbi_gen_fts_in_long,
    mtbi_gen_fts_out_long
)
mtbi_gen_long <- na.omit(mtbi_gen_long)

n <- nrow(long_mtbi_0_i1_cluster_df)

long_mtbi_0_data_df <- dplyr::inner_join(
    long_mtbi_0_i1_cluster_df,
    as.data.frame(c(long_mtbi_0_dls[[1]], long_mtbi_0_ols[[1]])),
    by = "uid"
)

long_mtbi_l_data_df <- dplyr::inner_join(
    long_mtbi_l_i1_cluster_df,
    as.data.frame(c(long_mtbi_l_dls[[1]], long_mtbi_l_ols[[1]])),
    by = "uid"
)

base_unij_l_data_df <- dplyr::inner_join(
    base_unij_l_i1_cluster_df,
    as.data.frame(c(base_unij_l_dls[[1]], base_unij_l_ols[[1]])),
    by = "uid"
)

long_mtbi_l_data_df


concordance_w_mtbi <- function(data_df, n = 220) {
    set.seed(42)
    lapply(
        1:10,
        function(x) {
            bootstrap_sample <- sample(n, replace = TRUE)
            sampled_df <- data_df[bootstrap_sample, ]
            tops_df <- topologizer(sampled_df)
            gen_tops_df <- generalizable_features(tops_df, compare_fn_a)
            gen_tops_df_long <- gen_tops_df |>
                pivot_longer(
                    cols = -feature,
                    names_to = "comparison",
                    values_to = "order_sample"
                )
            joint_df <- dplyr::left_join(
                mtbi_gen_long,
                gen_tops_df_long,
                by = c("feature", "comparison")
            ) |>
                dplyr::mutate(
                    match = ifelse(order_sample == order, 1, 0)
                ) |>
                dplyr::filter(!grepl("mtbi", feature))
            concordance <- sum(joint_df$"match") / nrow(joint_df)
            print(concordance)
        }
    )
}

concordance_w_mtbi(long_mtbi_0_data_df)

concordance_w_mtbi(long_mtbi_l_data_df)

concordance_w_mtbi(base_unij_l_data_df)

```

To check concordance between T0 and T2 is simple.

But how about by permutation testing?

Say I am trying to say the concordance is significantly different between T0 and T2.

I'm trying to say that two things are basically the same thing.

```{r}
matched_pls_dfs <- readRDS(proc_path("2025_02_15_matched_pl_dfs.rds"))

concordance_between_dfs <- function(df1, df2, feature_set) {
    tops_df1 <- topologizer(df1)
    tops_df2 <- topologizer(df2)
    gen_tops_df1 <- generalizable_features(tops_df1, compare_fn_a)
    gen_tops_df2 <- generalizable_features(tops_df2, compare_fn_a)
    gen_tops_df_long1 <- gen_tops_df1 |>
        pivot_longer(
            cols = -feature,
            names_to = "comparison",
            values_to = "order"
        )
    gen_tops_df_long2 <- gen_tops_df2 |>
        pivot_longer(
            cols = -feature,
            names_to = "comparison",
            values_to = "order"
        )
    joint_df <- dplyr::left_join(
        gen_tops_df_long1,
        gen_tops_df_long2,
        by = c("feature", "comparison")
    ) |>
        dplyr::filter(feature %in% feature_set) |>
        dplyr::mutate(
            match = ifelse(order.x == order.y, 1, 0)
        )
    concordance <- sum(joint_df$"match") / nrow(joint_df)
    return(concordance)
}

concordance_between_dfs(
    long_mtbi_0_data_df,
    long_mtbi_l_data_df,
    feature_set = relevant_fts
)

concordance_between_time <- function(data_df_t0, data_df_t2, n = 220) {
    set.seed(42)
    lapply(
        1:10,
        function(x) {
            permutation <- sample(n, replace = FALSE)
            t0_picks <- permutation[1:110]
            t2_picks <- permutation[111:220]
            sampled_df_t0 <- data_df_t0[t0_picks, ]
            sampled_df_t2 <- data_df_t2[t2_picks, ]
            sample_df <- rbind(sampled_df_t0, sampled_df_t2)
            tops_df <- topologizer(sampled_df)
            gen_tops_df <- generalizable_features(tops_df, compare_fn_a)
            gen_tops_df_long <- gen_tops_df |>
                pivot_longer(
                    cols = -feature,
                    names_to = "comparison",
                    values_to = "order_sample"
                )
            joint_df <- dplyr::left_join(
                mtbi_gen_long,
                gen_tops_df_long,
                by = c("feature", "comparison")
            ) |>
                dplyr::mutate(
                    match = ifelse(order_sample == order, 1, 0)
                ) |>
                dplyr::filter(!grepl("mtbi", feature))
            concordance <- sum(joint_df$"match") / nrow(joint_df)
            print(concordance)
        }
    )
}

long_mtbi_l_tops_df <- topologizer(long_mtbi_l_data_df)
long_mtbi_l_gen_tops_df <- generalizable_features(long_mtbi_l_tops_df, compare_fn_a)
long_mtbi_l_gen_tops_df_long <- long_mtbi_l_gen_tops_df |>
    pivot_longer(
        cols = -feature,
        names_to = "comparison",
        values_to = "order_sample"
    )

long_gen_x <- dplyr::left_join(
    mtbi_gen_long,
    long_mtbi_l_gen_tops_df_long,
    by = c("feature", "comparison")
) 

long_gen_x

mtbi_gen_long

long_mtbi_0_i1_cluster_df

long_mtbi_l_i1_cluster_df
```

#------------------------------------------------------------------------------

### Meta clustering the longitudinal timepoint for baseline concussion group

```{r}
# CHECKPOINT
base_mtbi_l_dls <- all_long_dls$"base_mtbi_l_dls"
base_mtbi_l_ols <- all_long_dls$"base_mtbi_l_ols"
```

```{r}
set.seed(42)
long_base_mtbi_config <- snf_config(
    base_mtbi_l_dls[[1]],
    n_solutions = 200,
    cnt_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    dsc_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ord_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    use_default_dist_fns = TRUE
)

saveRDS(long_base_mtbi_config, proc_path("long_base_mtbi_config.rds", TRUE))
```

```{r}
# CHECKPOINT
long_base_mtbi_config <- readRDS(proc_path("2025_02_18_long_base_mtbi_config.rds"))
```

```{r}
base_mtbi_l_sol_df_s1 <- batch_snf(
    dl = base_mtbi_l_dls[[1]],
    sc = long_base_mtbi_config,
    processes = "max"
)
saveRDS(base_mtbi_l_sol_df_s1, proc_path("base_mtbi_l_sol_df_s1.rds", TRUE))

base_mtbi_l_sol_df_s2 <- batch_snf(
    dl = base_mtbi_l_dls[[2]],
    sc = long_base_mtbi_config,
    processes = "max"
)
saveRDS(base_mtbi_l_sol_df_s2, proc_path("base_mtbi_l_sol_df_s2.rds", TRUE))

base_mtbi_l_sol_df_s3 <- batch_snf(
    dl = base_mtbi_l_dls[[3]],
    sc = long_base_mtbi_config,
    processes = "max"
)
saveRDS(base_mtbi_l_sol_df_s3, proc_path("base_mtbi_l_sol_df_s3.rds", TRUE))

base_mtbi_l_sol_df_s4 <- batch_snf(
    dl = base_mtbi_l_dls[[4]],
    sc = long_base_mtbi_config,
    processes = "max"
)
saveRDS(base_mtbi_l_sol_df_s4, proc_path("base_mtbi_l_sol_df_s4.rds", TRUE))

base_mtbi_l_sol_df_s5 <- batch_snf(
    dl = base_mtbi_l_dls[[5]],
    sc = long_base_mtbi_config,
    processes = "max"
)
saveRDS(base_mtbi_l_sol_df_s5, proc_path("base_mtbi_l_sol_df_s5.rds", TRUE))
```

```{r}
base_mtbi_l_sol_df_s1 <- readRDS(proc_path("2025_02_18_base_mtbi_l_sol_df_s1.rds"))
base_mtbi_l_sol_df_s2 <- readRDS(proc_path("2025_02_18_base_mtbi_l_sol_df_s2.rds"))
base_mtbi_l_sol_df_s3 <- readRDS(proc_path("2025_02_18_base_mtbi_l_sol_df_s3.rds"))
base_mtbi_l_sol_df_s4 <- readRDS(proc_path("2025_02_18_base_mtbi_l_sol_df_s4.rds"))
base_mtbi_l_sol_df_s5 <- readRDS(proc_path("2025_02_18_base_mtbi_l_sol_df_s5.rds"))

base_mtbi_l_sol_df <- do.call(
    "rbind",
    c(
        list(
            base_mtbi_l_sol_df_s1,
            base_mtbi_l_sol_df_s2,
            base_mtbi_l_sol_df_s3,
            base_mtbi_l_sol_df_s4,
            base_mtbi_l_sol_df_s5
        ),
        list(reset_indices = TRUE)
    )
)
saveRDS(base_mtbi_l_sol_df, proc_path("base_mtbi_l_sol_df.rds", TRUE))

base_mtbi_l_ari <- calc_aris(base_mtbi_l_sol_df, processes = "max")
saveRDS(base_mtbi_l_ari, proc_path("base_mtbi_l_ari.rds", TRUE))

base_mtbi_l_ari_order <- get_matrix_order(base_mtbi_l_ari)
write_csv(data.frame(base_mtbi_l_ari_order), proc_path("base_mtbi_l_ari_order.csv", TRUE))
```

```{r}
# CHECKPOINT
base_mtbi_l_sol_df <- readRDS(proc_path("2025_02_18_base_mtbi_l_sol_df.rds"))
base_mtbi_l_ari <- readRDS(proc_path("2025_02_18_base_mtbi_l_ari.rds"))
base_mtbi_l_ari_order <- unlist(read_csv(proc_path("2025_02_18_base_mtbi_l_ari_order.csv")))
names(base_mtbi_l_ari_order) <- NULL
```

```{r}
# Solo imputation 1
base_mtbi_l_ext_sol_df_s1 <- extend_solutions(
    base_mtbi_l_sol_df[1:200, ],
    dl = base_mtbi_l_dls[[1]],
    target_dl = base_mtbi_l_ols[[1]],
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(base_mtbi_l_ext_sol_df_s1, proc_path("base_mtbi_l_ext_sol_df_s1.rds", TRUE))
# Solo imputation 2
base_mtbi_l_ext_sol_df_s2 <- extend_solutions(
    base_mtbi_l_sol_df[201:400, ],
    dl = base_mtbi_l_dls[[2]],
    target_dl = base_mtbi_l_ols[[2]],
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(base_mtbi_l_ext_sol_df_s2, proc_path("base_mtbi_l_ext_sol_df_s2.rds", TRUE))
# Solo imputation 3
base_mtbi_l_ext_sol_df_s3 <- extend_solutions(
    base_mtbi_l_sol_df[401:600, ],
    dl = base_mtbi_l_dls[[3]],
    target_dl = base_mtbi_l_ols[[3]],
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(base_mtbi_l_ext_sol_df_s3, proc_path("base_mtbi_l_ext_sol_df_s3.rds", TRUE))
# Solo imputation 4
base_mtbi_l_ext_sol_df_s4 <- extend_solutions(
    base_mtbi_l_sol_df[601:800, ],
    dl = base_mtbi_l_dls[[4]],
    target_dl = base_mtbi_l_ols[[4]],
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(base_mtbi_l_ext_sol_df_s4, proc_path("base_mtbi_l_ext_sol_df_s4.rds", TRUE))
# Solo imputation 5
base_mtbi_l_ext_sol_df_s5 <- extend_solutions(
    base_mtbi_l_sol_df[801:1000, ],
    dl = base_mtbi_l_dls[[5]],
    target_dl = base_mtbi_l_ols[[5]],
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(base_mtbi_l_ext_sol_df_s5, proc_path("base_mtbi_l_ext_sol_df_s5.rds", TRUE))
```

```{r}
base_mtbi_l_ext_sol_df_s1 <- readRDS(proc_path("2025_02_18_base_mtbi_l_ext_sol_df_s1.rds"))
base_mtbi_l_ext_sol_df_s2 <- readRDS(proc_path("2025_02_18_base_mtbi_l_ext_sol_df_s2.rds"))
base_mtbi_l_ext_sol_df_s3 <- readRDS(proc_path("2025_02_18_base_mtbi_l_ext_sol_df_s3.rds"))
base_mtbi_l_ext_sol_df_s4 <- readRDS(proc_path("2025_02_18_base_mtbi_l_ext_sol_df_s4.rds"))
base_mtbi_l_ext_sol_df_s5 <- readRDS(proc_path("2025_02_18_base_mtbi_l_ext_sol_df_s5.rds"))

base_mtbi_l_ext_sol_df <- do.call(
    "rbind",
    c(
        list(
            base_mtbi_l_ext_sol_df_s1,
            base_mtbi_l_ext_sol_df_s2,
            base_mtbi_l_ext_sol_df_s3,
            base_mtbi_l_ext_sol_df_s4,
            base_mtbi_l_ext_sol_df_s5
        ),
        list(reset_indices = TRUE)
    )
)

saveRDS(base_mtbi_l_ext_sol_df, proc_path("base_mtbi_l_ext_sol_df.rds", TRUE))

base_mtbi_l_ext_sol_df <- readRDS(proc_path("2025_02_18_base_mtbi_l_ext_sol_df.rds"))
```

```{r}
base_mtbi_l_hm <- meta_cluster_heatmap(base_mtbi_l_ari, order = base_mtbi_l_ari_order)
base_mtbi_l_esdf <- as.data.frame(base_mtbi_l_ext_sol_df)
base_mtbi_l_esdf$"impairment_separation" <- -log10(base_mtbi_l_esdf$"mean_pval")

# It's there!
full_base_mtbi_l_ari_hm <- meta_cluster_heatmap(
    aris = base_mtbi_l_ari,
    order = base_mtbi_l_ari_order,
    data = base_mtbi_l_esdf,
    min_colour = "black",
    top_hm = list(
        "Impairment Separation" = "impairment_separation"
    ),
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    annotation_colours = list(
        "Impairment Separation" = colour_scale(
            base_mtbi_l_esdf$"impairment_separation",
            min_colour = "gray7",
            max_colour = "limegreen"
        )
    )
)
full_base_mtbi_l_ari_hm

save_heatmap(
    heatmap = full_base_mtbi_l_ari_hm,
    path = fig_path("full_base_mtbi_l_ari_hm.png", TRUE),
    width = 950,
    height = 900,
    res = 100
)

```

So the baseline mTBI subjects do seem to have it!


## Moving on: Change in outcomes

If I go back to when I was about to run extend solutions, and instead try to find any meta clusters associated with change in outcome measures, do I find anything interesting?

```{r}
full_dl_0 <- readRDS(input_path("2025_02_12_mtbi_full_data_list_1.rds"))
full_ol_0 <- readRDS(input_path("2025_02_12_mtbi_full_oom_list_1.rds"))

full_ol_2 <- all_long_dls$"base_mtbi_l_ols"[[1]]

full_ol_0_df <- as.data.frame(full_ol_0)
full_ol_2_df <- as.data.frame(full_ol_2)

full_ol_change_df$"cbcl_anxdep" <- full_ol_2_df$"cbcl_anxdep" - full_ol_0_df$"cbcl_anxdep"
full_ol_change_df$"cbcl_withdep" <- full_ol_2_df$"cbcl_withdep" - full_ol_0_df$"cbcl_withdep"
full_ol_change_df$"cbcl_somatic" <- full_ol_2_df$"cbcl_somatic" - full_ol_0_df$"cbcl_somatic"
full_ol_change_df$"cbcl_social" <- full_ol_2_df$"cbcl_social" - full_ol_0_df$"cbcl_social"
full_ol_change_df$"cbcl_thought" <- full_ol_2_df$"cbcl_thought" - full_ol_0_df$"cbcl_thought"
full_ol_change_df$"cbcl_attention" <- full_ol_2_df$"cbcl_attention" - full_ol_0_df$"cbcl_attention"
full_ol_change_df$"cbcl_rulebreak" <- full_ol_2_df$"cbcl_rulebreak" - full_ol_0_df$"cbcl_rulebreak"
full_ol_change_df$"cbcl_aggressive" <- full_ol_2_df$"cbcl_aggressive" - full_ol_0_df$"cbcl_aggressive"
full_ol_change_df$"sds_sleep" <- full_ol_2_df$"sds_sleep" - full_ol_0_df$"sds_sleep"
full_ol_change_df$"uid" <- gsub("uid_", "", full_ol_change_df$"uid")

full_ol_change <- data_list(
    list(dplyr::select(full_ol_change_df, uid, dplyr::starts_with("cbcl")), "cbcl", "B", "discrete"),
    list(dplyr::select(full_ol_change_df, uid, dplyr::starts_with("sds")), "sds", "B", "discrete"),
    uid = "uid"
)

saveRDS(full_ol_change, proc_path("full_ol_change.rds", TRUE))

full_ol_change <- readRDS(proc_path("2025_02_18_full_ol_change.rds"))
mtbi_full_sol_df <- readRDS(proc_path("2025_02_12_mtbi_full_sol_df.rds"))

mtbi_full_change_ext_sol_df <- extend_solutions(
    mtbi_full_sol_df,
    target_dl = full_ol_change,
    min_pval = 1e-10,
    processes = "max"
)

saveRDS(mtbi_full_change_ext_sol_df, proc_path("mtbi_full_change_ext_sol_df.rds", TRUE))

mtbi_full_change_ext_sol_df <- readRDS(proc_path("2025_02_18_mtbi_full_change_ext_sol_df.rds"))

mtbi_full_change_ari <- calc_aris(mtbi_full_change_ext_sol_df)

saveRDS(mtbi_full_change_ari, proc_path("mtbi_full_change_ari.rds", TRUE))
mtbi_full_change_ari <- readRDS(proc_path("2025_02_18_mtbi_full_change_ari.rds"))

full_change_order <- get_matrix_order(mtbi_full_change_ari)

saveRDS(full_change_order, proc_path("full_change_order.rds", TRUE))
full_change_order <- readRDS(proc_path("2025_02_18_full_change_order.rds"))

full_change_esdf <- as.data.frame(mtbi_full_change_ext_sol_df)

full_change_esdf$"impairment_separation" <- -log10(full_change_esdf$"mean_pval")

full_change_mc_hm <- meta_cluster_heatmap(
    aris = mtbi_full_change_ari,
    order = full_change_order,
    data = full_change_esdf,
    split_vector = c(
        48,
        54,
        95,
        136,
        147
    ),
    top_hm = list(
        "Impairment Separation" = "impairment_separation"
    ),
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    annotation_colours = list(
        "Impairment Separation" = colour_scale(
            full_change_esdf$"impairment_separation",
            min_colour = "gray7",
            max_colour = "limegreen"
        )
    )
)

save_heatmap(
    heatmap = full_change_mc_hm,
    path = fig_path("full_change_mc_hm.png", TRUE),
    width = 950,
    height = 900,
    res = 100
)

change_mc_sol_df <- label_meta_clusters(
    mtbi_full_change_ext_sol_df,
    order = full_change_order,
    split_vector = c(
        48,
        54,
        95,
        136,
        147
    )
)

change_rep_solutions <- get_representative_solutions(
    mtbi_full_change_ari,
    change_mc_sol_df
)

top_change_esdf <- change_rep_solutions[2, ]

saveRDS(top_change_esdf, proc_path("top_change_esdf.rds", TRUE))
top_change_esdf <- readRDS(proc_path("2025_02_18_top_change_esdf.rds"))

# Adding in the input features as well
top_change_esdf2 <- extend_solutions(
    mtbi_full_sol_df[54, ],
    dl = full_dl_0,
    target_dl = full_ol_change,
    min_pval = 1e-10,
    processes = "max"
)

top_change_esdf2$"mc" <- "B"

saveRDS(top_change_esdf2, proc_path("top_change_esdf2.rds", TRUE))
top_change_esdf2 <- readRDS(proc_path("2025_02_18_top_change_esdf2.rds"))

top_change_manhattan <- mc_manhattan_plot(
    top_change_esdf2,
    dl = full_dl_0,
    target_dl = full_ol_change,
    domain_colours = c(
        "AS" = "#85929e",
        "D" = "#bb8fce",
        "N" = "#e59866",
        "MH" = "#7fb3d5",
        "P" = "#52be80",
        "S" = "#d98880",
        "B" = "#ff3131"
    )
)

ggsave(
    plot = top_change_manhattan,
    filename = fig_path("top_change_manhattan.png", TRUE),
    width = 18,
    height = 5,
    dpi = 120
)

change_pl <- auto_plot(
    top_change_esdf2,
    dl = c(full_dl_0, full_ol_change),
    verbose = TRUE
)

change_pl_wrapped <- wrap_plots(change_pl)

ggsave(
    fig_path("change_pl_wrapped.png", TRUE),
    change_pl_wrapped,
    width = 45,
    height = 30,
    dpi = 50
)
```

Not all that interesting; kids who had worse scores to begin with have an easier time getting better.
