# Longitudinal analyses

1. Was the baseline clustering informative for long-term outcomes?

2. Did the matched uninjured subjects experience more mTBIs by T2 than the other uninjured subjects?

3. Clustering of the longitudinal sample with their baseline vs. their longitudinal data: both equally informative?

4. Classifier built from baseline mTBI data: informative?

## Data importing

```{r}
library(abcdutils)
library(here)
library(dplyr)
library(readr)
library(metasnf)
library(rlist)
library(visdat)
library(ggplot2)
library(mice)
library(fastDummies)
library(randomForest)
library(patchwork)

# The path_maker function helps with managing and date stamping long paths. The
# functions are just used here to help with reading and writing data. See
# ?path_maker for more information.
input_path <- path_maker(here(paste0("data/abcd/inputs")))
core_path <- path_maker(here(paste0("data/abcd/core")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
model_path <- path_maker(here(paste0("data/abcd/results/models")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))

read <- function(path) {
    return(read_csv(input_path(path)))
}
```

## Q1: Was the baseline clustering informative for LT outcomes?

```{r}
# Import data
mtbi_base_df <- read_csv(proc_path("2024_11_07_mtbi_ful_df.csv"))

all_long_dls <- list.load(input_path("2024_11_13_all_long_dls.rds"))

base_mtbi_l_ols <- all_long_dls$"base_mtbi_l_ols"

# Convert list of data lists into list of data frames for plotting
base_mtbi_l_ol_dfs <- lapply(base_mtbi_l_ols, collapse_dl)

# Tag each data frame with its originating imputation
base_mtbi_l_ol_dfs <- lapply(
    1:5,
    function(x) {
        base_mtbi_l_ol_dfs[[x]]$"imputation" <- x
        base_mtbi_l_ol_dfs[[x]]
    }
)

# Horizontally merge list of data frames
base_mtbi_l_ol_df <- do.call(rbind, base_mtbi_l_ol_dfs)

# Keep track of baseline data before attaching to longitudinal data
colnames(mtbi_base_df) <- paste0(colnames(mtbi_base_df), "_0")
colnames(mtbi_base_df)[1:2] <- c("subjectkey", "cluster")

mtbi_base_outcomes_l <- dplyr::full_join(mtbi_base_df, base_mtbi_l_ol_df, "subjectkey")

mtbi_long_changes <- mtbi_base_outcomes_l |>
    dplyr::rename(
        "cbcl_anxdep_l" = "cbcl_anxdep",
        "cbcl_withdep_l" = "cbcl_withdep",
        "cbcl_somatic_l" = "cbcl_somatic",
        "cbcl_social_l" = "cbcl_social",
        "cbcl_thought_l" = "cbcl_thought",
        "cbcl_attention_l" = "cbcl_attention",
        "cbcl_rulebreak_l" = "cbcl_rulebreak",
        "cbcl_aggressive_l" = "cbcl_aggressive",
        "sds_sleep_l"  = "sds_sleep"
    ) |>
    dplyr::mutate(
        cbcl_anxdep_d = cbcl_anxdep_l - cbcl_anxdep_0,
        cbcl_withdep_d = cbcl_withdep_l - cbcl_withdep_0,
        cbcl_somatic_d = cbcl_somatic_l - cbcl_somatic_0,
        cbcl_social_d = cbcl_social_l - cbcl_social_0,
        cbcl_thought_d = cbcl_thought_l - cbcl_thought_0,
        cbcl_attention_d = cbcl_attention_l - cbcl_attention_0,
        cbcl_rulebreak_d = cbcl_rulebreak_l - cbcl_rulebreak_0,
        cbcl_aggressive_d = cbcl_aggressive_l - cbcl_aggressive_0,
        sds_sleep_d = sds_sleep_l - sds_sleep_0
    )

mtbi_long_changes

gg_long_cor <- function(df, feature, long = TRUE) {
    f1 <- paste0(feature, "_0")
    if (long) {
        f2 <- paste0(feature, "_l")
    } else {
        f2 <- paste0(feature, "_d")
    }
    plot <- ggplot(
        df,
        aes(x = .data[[f1]], y = .data[[f2]])
    ) +
        geom_jitter(alpha = 0.2) +
        facet_wrap(~ imputation) +
        theme_bw()
    return(plot)
}

mtbi_long_changes$"cluster" <- as.factor(mtbi_long_changes$"cluster")

lm_long_fit <- function(df, feature) {
    models <- list(
      lm(as.formula(paste0(feature, "_l ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 1)),
      lm(as.formula(paste0(feature, "_l ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 2)),
      lm(as.formula(paste0(feature, "_l ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 3)),
      lm(as.formula(paste0(feature, "_l ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 4)),
      lm(as.formula(paste0(feature, "_l ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 5))
    )
    pooled_results <- pool(as.mira(models))
    return(summary(pooled_results))
}

gg_long_cor(mtbi_long_changes, "cbcl_anxdep", 0)

gg_long_cor(mtbi_long_changes, "cbcl_withdep")

gg_long_cor(mtbi_long_changes, "cbcl_somatic")

# None are significant
lm_long_fit(mtbi_long_changes, "cbcl_anxdep")
lm_long_fit(mtbi_long_changes, "cbcl_withdep")
lm_long_fit(mtbi_long_changes, "cbcl_somatic")
lm_long_fit(mtbi_long_changes, "cbcl_social")
lm_long_fit(mtbi_long_changes, "cbcl_thought")
lm_long_fit(mtbi_long_changes, "cbcl_attention")
lm_long_fit(mtbi_long_changes, "cbcl_rulebreak")
lm_long_fit(mtbi_long_changes, "cbcl_aggressive")
lm_long_fit(mtbi_long_changes, "sds_sleep")
```

Cluster is never a significant feature in predicting longitudinal outcome given baseline outcome.

### Q2. Did the matched uninjured subjects experience more mTBIs by T2 than the other uninjured subjects?

### Q3. Clustering of the longitudinal sample with their baseline vs. their longitudinal data: both equally informative?

### Q4. Classifier built from baseline mTBI data: informative?

```{r}
names(all_long_dls)

# Classifying data using baseline as well as longitudinal features
long_mtbi_0_dls <- all_long_dls$"long_mtbi_0_dls"
long_mtbi_l_dls <- all_long_dls$"long_mtbi_l_dls"
long_mtbi_0_ols <- all_long_dls$"long_mtbi_0_ols"
long_mtbi_l_ols <- all_long_dls$"long_mtbi_l_ols"

base_uninj_l_dls <- all_long_dls$"base_uninj_l_dls"
base_uninj_l_ols <- all_long_dls$"base_uninj_l_ols"

dls_to_dfs <- function(dls) {
    lapply(
        seq_along(dls),
        function(x) {
            collapse_dl(dls[[x]])
        }
    )
}

long_mtbi_0_dfs <- dls_to_dfs(long_mtbi_0_dls)
long_mtbi_l_dfs <- dls_to_dfs(long_mtbi_l_dls)
base_uninj_l_dfs <- dls_to_dfs(base_uninj_l_dls)

#reduce_to_gen_fts <- function(df_list) {
#    df_list <- lapply(
#        df_list,
#        function(df) {
#            df <- df |> dplyr::select(
#                any_of(
#                    colnames(
#                        train_classification_df
#                    )
#                )
#            )
#            return(df)
#        }
#    )
#    return(df_list)
#}
#
#long_mtbi_0_gen_dfs <- reduce_to_gen_fts(long_mtbi_0_dfs)
#long_mtbi_l_gen_dfs <- reduce_to_gen_fts(long_mtbi_l_dfs)
#base_uninj_l_gen_dfs <- reduce_to_gen_fts(base_uninj_l_dfs)

subtype_classifier <- readRDS(model_path("2024_11_12_subtype_classifier.rds"))

# Just FYI
prep_data <- function(df, standardize = FALSE) {
    df <- dplyr::select(df, -"subjectkey")
    df <- dummy_cols(
        df,
        select_columns = "race",
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = TRUE
    )
    ordered_factors <- c(
        "sex",
        "household_income",
        "pubertal_status_p",
        "family_fight_p",
        "family_outdo_p",
        "helps_hurt_p",
        "helpful_y",
        "considerate_y",
        "helps_hurt_y",
        "family_criticize_p",
        "family_outdo_y",
        "family_angry_p",
        "helpful_p",
        "family_throw_p",
        "family_hit_p",
        "family_peaceful_y",
        "family_throw_y",
        "race_black",
        "race_hispanic",
        "race_other" 
    )
    df[ordered_factors] <- lapply(df[ordered_factors], as.ordered)
    if (standardize) {
        df[] <- lapply(df, as.numeric)
        df <- as.data.frame(scale(df))
    }
    if ("cluster" %in% colnames(df)) {
        df$"cluster" <- as.factor(df$"cluster")
    }
    return(df)
}

long_mtbi_0_pred_dfs <- lapply(
    long_mtbi_0_dfs,
    function(x) {
        clean_df <- prep_data(x)
        predictions <- predict(
            subtype_classifier,
            newdata = clean_df
        )
        x$"cluster" <- predictions
        x
    }
)

long_mtbi_l_pred_dfs <- lapply(
    long_mtbi_l_dfs,
    function(x) {
        clean_df <- prep_data(x)
        predictions <- predict(
            subtype_classifier,
            newdata = clean_df
        )
        x$"cluster" <- predictions
        x
    }
)

base_uninj_l_pred_dfs <- lapply(
    base_uninj_l_dfs,
    function(x) {
        clean_df <- prep_data(x)
        predictions <- predict(
            subtype_classifier,
            newdata = clean_df
        )
        x$"cluster" <- predictions
        x
    }
)

list.save(long_mtbi_0_pred_dfs, proc_path("long_mtbi_0_pred_dfs.rds", TRUE))
list.save(long_mtbi_l_pred_dfs, proc_path("long_mtbi_l_pred_dfs.rds", TRUE))
list.save(base_uninj_l_pred_dfs, proc_path("base_uninj_l_pred_dfs.rds", TRUE))

long_mtbi_0_pred_dfs <- list.load(proc_path("2024_11_15_long_mtbi_0_pred_dfs.rds"))
long_mtbi_l_pred_dfs <- list.load(proc_path("2024_11_15_long_mtbi_l_pred_dfs.rds"))
base_uninj_l_pred_dfs <- list.load(proc_path("2024_11_15_base_uninj_l_pred_dfs.rds"))

long_mtbi_0_i1_cluster_df <- long_mtbi_0_pred_dfs[[1]] |> 
    dplyr::select(subjectkey, cluster)
long_mtbi_l_i1_cluster_df <- long_mtbi_l_pred_dfs[[1]] |> 
    dplyr::select(subjectkey, cluster)
base_uninj_l_i1_cluster_df <- base_uninj_l_pred_dfs[[1]] |> 
    dplyr::select(subjectkey, cluster)

long_mtbi_0_i1_cluster_df$cluster |> table() |> prop.table() |> (\(x) 100 * x)()

long_mtbi_l_i1_cluster_df$cluster |> table() |> prop.table() |> (\(x) 100 * x)()

base_uninj_l_i1_cluster_df$cluster |> table() |> prop.table() |> (\(x) 100 * x)()


long_mtbi_0_plot_list <- auto_plot(
    cluster_df = long_mtbi_0_i1_cluster_df,
    data_list = long_mtbi_0_dls[[1]],
    target_list = long_mtbi_0_ols[[1]]
)
long_mtbi_0_all_plots <- wrap_plots(plot_list)

long_mtbi_l_plot_list <- auto_plot(
    cluster_df = long_mtbi_l_i1_cluster_df,
    data_list = long_mtbi_l_dls[[1]],
    target_list = long_mtbi_l_ols[[1]]
)
long_mtbi_l_all_plots <- wrap_plots(plot_list)

ggsave(
    fig_path("long_mtbi_0_predicted_plots.png", TRUE),
    long_mtbi_0_all_plots,
    width = 45,
    height = 30,
    dpi = 50
)

ggsave(
    fig_path("long_mtbi_l_predicted_plots.png", TRUE),
    long_mtbi_l_all_plots,
    width = 45,
    height = 30,
    dpi = 50
)

# Looks very similar!
```

