# Longitudinal analyses

1. Was the baseline clustering informative for long-term outcomes?

2. Did the matched uninjured subjects experience more mTBIs by T2 than the other uninjured subjects?

3. Clustering of the longitudinal sample with their baseline vs. their longitudinal data: both equally informative?

4. Classifier built from baseline mTBI data: informative?

## Data importing

```{r}
library(abcdutils)
library(here)
library(dplyr)
library(readr)
library(metasnf)
library(rlist)
library(visdat)
library(ggplot2)
library(mice)
library(fastDummies)
library(randomForest)
library(patchwork)

# The path_maker function helps with managing and date stamping long paths. The
# functions are just used here to help with reading and writing data. See
# ?path_maker for more information.
input_path <- path_maker(here(paste0("data/abcd/inputs")))
core_path <- path_maker(here(paste0("data/abcd/core")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
model_path <- path_maker(here(paste0("data/abcd/results/models")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))

read <- function(path) {
    return(read_csv(input_path(path)))
}
```

## Q1: Was the baseline clustering informative for LT outcomes?

```{r}
# Import data
mtbi_base_df <- readRDS(proc_path("2025_02_13_mtbi_ful_df.rds"))

all_long_dls <- readRDS(input_path("2025_02_16_all_long_dls.rds"))

base_mtbi_l_ols <- all_long_dls$"base_mtbi_l_ols"

# Convert list of data lists into list of data frames for plotting
base_mtbi_l_ol_dfs <- lapply(base_mtbi_l_ols, as.data.frame)

# Tag each data frame with its originating imputation
base_mtbi_l_ol_dfs <- lapply(
    1:5,
    function(x) {
        base_mtbi_l_ol_dfs[[x]]$"imputation" <- x
        base_mtbi_l_ol_dfs[[x]]
    }
)

# Horizontally merge list of data frames
base_mtbi_l_ol_df <- do.call(rbind, base_mtbi_l_ol_dfs)


mtbi_base_df <- mtbi_base_df |>
    dplyr::select(uid, cluster, dplyr::everything())

# Keep track of baseline data before attaching to longitudinal data
colnames(mtbi_base_df) <- paste0(colnames(mtbi_base_df), "_0")

colnames(mtbi_base_df)[1:2] <- c("uid", "cluster")

mtbi_base_outcomes_l <- dplyr::full_join(
    mtbi_base_df,
    base_mtbi_l_ol_df,
    by = "uid"
)

mtbi_long_changes <- mtbi_base_outcomes_l |>
    dplyr::rename(
        "cbcl_anxdep_l" = "cbcl_anxdep",
        "cbcl_withdep_l" = "cbcl_withdep",
        "cbcl_somatic_l" = "cbcl_somatic",
        "cbcl_social_l" = "cbcl_social",
        "cbcl_thought_l" = "cbcl_thought",
        "cbcl_attention_l" = "cbcl_attention",
        "cbcl_rulebreak_l" = "cbcl_rulebreak",
        "cbcl_aggressive_l" = "cbcl_aggressive",
        "sds_sleep_l"  = "sds_sleep"
    ) |>
    dplyr::mutate(
        cbcl_anxdep_d = cbcl_anxdep_l - cbcl_anxdep_0,
        cbcl_withdep_d = cbcl_withdep_l - cbcl_withdep_0,
        cbcl_somatic_d = cbcl_somatic_l - cbcl_somatic_0,
        cbcl_social_d = cbcl_social_l - cbcl_social_0,
        cbcl_thought_d = cbcl_thought_l - cbcl_thought_0,
        cbcl_attention_d = cbcl_attention_l - cbcl_attention_0,
        cbcl_rulebreak_d = cbcl_rulebreak_l - cbcl_rulebreak_0,
        cbcl_aggressive_d = cbcl_aggressive_l - cbcl_aggressive_0,
        sds_sleep_d = sds_sleep_l - sds_sleep_0
    )

mtbi_long_changes

gg_long_cor <- function(df, feature, long = TRUE) {
    f1 <- paste0(feature, "_0")
    if (long) {
        f2 <- paste0(feature, "_l")
    } else {
        f2 <- paste0(feature, "_d")
    }
    plot <- ggplot(
        df,
        aes(x = .data[[f1]], y = .data[[f2]])
    ) +
        geom_jitter(alpha = 0.2) +
        facet_wrap(~ imputation) +
        theme_bw()
    return(plot)
}

mtbi_long_changes$"cluster" <- as.factor(mtbi_long_changes$"cluster")

lm_long_fit <- function(df, feature) {
    models <- list(
      lm(as.formula(paste0(feature, "_l ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 1)),
      lm(as.formula(paste0(feature, "_l ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 2)),
      lm(as.formula(paste0(feature, "_l ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 3)),
      lm(as.formula(paste0(feature, "_l ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 4)),
      lm(as.formula(paste0(feature, "_l ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 5))
    )
    pooled_results <- pool(as.mira(models))
    return(summary(pooled_results))
}

anxdep_long_cor_1 <- gg_long_cor(mtbi_long_changes, "cbcl_anxdep", 0)

anxdep_long_cor_2 <- gg_long_cor(mtbi_long_changes, "cbcl_anxdep")

ggsave(plot = anxdep_long_cor_1, fig_path("anxdep_long_cor_1.png", TRUE), height = 10, width = 10)

ggsave(plot = anxdep_long_cor_2, fig_path("anxdep_long_cor_2.png", TRUE), height = 10, width = 10)

gg_long_cor(mtbi_long_changes, "cbcl_withdep")

gg_long_cor(mtbi_long_changes, "cbcl_somatic")

# None are significant
lm_long_fit(mtbi_long_changes, "cbcl_anxdep")
lm_long_fit(mtbi_long_changes, "cbcl_withdep")
lm_long_fit(mtbi_long_changes, "cbcl_somatic")
lm_long_fit(mtbi_long_changes, "cbcl_social")
lm_long_fit(mtbi_long_changes, "cbcl_thought")
lm_long_fit(mtbi_long_changes, "cbcl_attention")
lm_long_fit(mtbi_long_changes, "cbcl_rulebreak")
lm_long_fit(mtbi_long_changes, "cbcl_aggressive")
lm_long_fit(mtbi_long_changes, "sds_sleep")
```

Cluster is never a significant feature in predicting longitudinal outcome given baseline outcome.

### Q2. Did the matched uninjured subjects experience more mTBIs by T2 than the other uninjured subjects?

```{r}

matched_unij_nearest_esdf <- readRDS(proc_path("2025_02_16_matched_unij_nearest_esdf.rds"))

# Those who exhibited heterogeneity most similar to the baseline mTBI group
matched_subs <- uids(matched_unij_nearest_esdf)
matched_subs <- gsub("uid_", "", matched_subs)

# Those who never sustained a head injury prior to T2
long_unij_subs <- read_subjects(sub_path("2025_02_07_unij_subs_0_to_2.csv"))

# Those who sustained a head injury between 0 and T2
long_mtbi_subs <- read_subjects(sub_path("2025_02_07_mtbi_subs_0_to_2.csv"))

# The pool of all baseline uninjured subjects
base_unij_subs <- read_subjects(sub_path("2025_02_07_unij_subs.csv"))

#calc_injured_fractions <- function(subjects, became_injured, remained_uninjured) {
#    frac_became_injured <- sum(subjects %in% became_injured) / length(subjects)
#    frac_remained_uninjured <- sum(subjects %in% remained_uninjured) / length(subjects)
#    cat(
#        "Fraction injured: ", frac_became_injured, "\n",
#        "Fraction uninjured: ", frac_remained_uninjured, "\n",
#        "Fraction present: ", frac_became_injured + frac_remained_uninjured, "\n",
#        sep = ""
#    )
#}
#
#calc_injured_fractions(
#    matched_subs,
#    long_mtbi_subs,
#    long_unij_subs
#)
```

Let's consider being in the matched group vs. not being in the matched group as exposed vs. unexposed, and ending up in the mTBI sample as outcome vs. no outcome.
Then I calculate the odds ratio and 95% CI of being in the mTBI sample based on being in the matched group.

```{r}
# Calculation 1: Explicitly looking for people that ended up in mTBI sample
matched_that_became_mtbi <- sum(matched_subs %in% long_mtbi_subs)
unmatched_that_became_mtbi <- sum(non_matched_subs %in% long_mtbi_subs)
matched_that_remained_unij <- sum(!matched_subs %in% long_mtbi_subs)
unmatched_that_remained_unij <- sum(!non_matched_subs %in% long_mtbi_subs)

data_matrix <- matrix(
    c(
        matched_that_became_mtbi, matched_that_remained_unij,
        unmatched_that_became_mtbi, unmatched_that_remained_unij
    ),
    nrow = 2,
    byrow = TRUE
)
rownames(data_matrix) <- c("Matched", "Unmatched")
colnames(data_matrix) <- c("Injured", "Remained Uninjured")
chi_result <- chisq.test(data_matrix, correct = FALSE)
print(chi_result)

matched_that_became_mtbi_frac <- mean(matched_subs %in% long_mtbi_subs)
unmatched_that_became_mtbi_frac <- mean(non_matched_subs %in% long_mtbi_subs)
matched_that_remained_unij_frac <- mean(!matched_subs %in% long_mtbi_subs)
unmatched_that_remained_unij_frac <- mean(!non_matched_subs %in% long_mtbi_subs)

matched_that_became_mtbi_frac #0.01372998

unmatched_that_became_mtbi_frac #0.01649461
```

No significant difference in the proportion of matched uninjured subjects to unmatched uninjured subjects that ended up in the longitudinal mTBI group (1.3% vs. 1.6%, uncorrected Chi-squared test p-value = 0.6565).

Now I'll double check to see if there were any attributes of subjects that were particularly associated with membership in the longitudinal mTBI sample.



### Q3. Clustering of the longitudinal sample with their baseline vs. their longitudinal data: both equally informative?

### Q4. Classifier built from baseline mTBI data: informative?

```{r}
names(all_long_dls)

# Classifying data using baseline as well as longitudinal features
long_mtbi_0_dls <- all_long_dls$"long_mtbi_0_dls"
long_mtbi_l_dls <- all_long_dls$"long_mtbi_l_dls"
long_mtbi_0_ols <- all_long_dls$"long_mtbi_0_ols"
long_mtbi_l_ols <- all_long_dls$"long_mtbi_l_ols"

base_uninj_l_dls <- all_long_dls$"base_uninj_l_dls"
base_uninj_l_ols <- all_long_dls$"base_uninj_l_ols"

dls_to_dfs <- function(dls) {
    lapply(
        seq_along(dls),
        function(x) {
            collapse_dl(dls[[x]])
        }
    )
}

long_mtbi_0_dfs <- dls_to_dfs(long_mtbi_0_dls)
long_mtbi_l_dfs <- dls_to_dfs(long_mtbi_l_dls)
base_uninj_l_dfs <- dls_to_dfs(base_uninj_l_dls)

#reduce_to_gen_fts <- function(df_list) {
#    df_list <- lapply(
#        df_list,
#        function(df) {
#            df <- df |> dplyr::select(
#                any_of(
#                    colnames(
#                        train_classification_df
#                    )
#                )
#            )
#            return(df)
#        }
#    )
#    return(df_list)
#}
#
#long_mtbi_0_gen_dfs <- reduce_to_gen_fts(long_mtbi_0_dfs)
#long_mtbi_l_gen_dfs <- reduce_to_gen_fts(long_mtbi_l_dfs)
#base_uninj_l_gen_dfs <- reduce_to_gen_fts(base_uninj_l_dfs)

subtype_classifier <- readRDS(model_path("2024_11_12_subtype_classifier.rds"))

# Just FYI
prep_data <- function(df, standardize = FALSE) {
    df <- dplyr::select(df, -"subjectkey")
    df <- dummy_cols(
        df,
        select_columns = "race",
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = TRUE
    )
    ordered_factors <- c(
        "sex",
        "household_income",
        "pubertal_status_p",
        "family_fight_p",
        "family_outdo_p",
        "helps_hurt_p",
        "helpful_y",
        "considerate_y",
        "helps_hurt_y",
        "family_criticize_p",
        "family_outdo_y",
        "family_angry_p",
        "helpful_p",
        "family_throw_p",
        "family_hit_p",
        "family_peaceful_y",
        "family_throw_y",
        "race_black",
        "race_hispanic",
        "race_other" 
    )
    df[ordered_factors] <- lapply(df[ordered_factors], as.ordered)
    if (standardize) {
        df[] <- lapply(df, as.numeric)
        df <- as.data.frame(scale(df))
    }
    if ("cluster" %in% colnames(df)) {
        df$"cluster" <- as.factor(df$"cluster")
    }
    return(df)
}

long_mtbi_0_pred_dfs <- lapply(
    long_mtbi_0_dfs,
    function(x) {
        clean_df <- prep_data(x)
        predictions <- predict(
            subtype_classifier,
            newdata = clean_df
        )
        x$"cluster" <- predictions
        x
    }
)

long_mtbi_l_pred_dfs <- lapply(
    long_mtbi_l_dfs,
    function(x) {
        clean_df <- prep_data(x)
        predictions <- predict(
            subtype_classifier,
            newdata = clean_df
        )
        x$"cluster" <- predictions
        x
    }
)

base_uninj_l_pred_dfs <- lapply(
    base_uninj_l_dfs,
    function(x) {
        clean_df <- prep_data(x)
        predictions <- predict(
            subtype_classifier,
            newdata = clean_df
        )
        x$"cluster" <- predictions
        x
    }
)

list.save(long_mtbi_0_pred_dfs, proc_path("long_mtbi_0_pred_dfs.rds", TRUE))
list.save(long_mtbi_l_pred_dfs, proc_path("long_mtbi_l_pred_dfs.rds", TRUE))
list.save(base_uninj_l_pred_dfs, proc_path("base_uninj_l_pred_dfs.rds", TRUE))

long_mtbi_0_pred_dfs <- list.load(proc_path("2024_11_15_long_mtbi_0_pred_dfs.rds"))
long_mtbi_l_pred_dfs <- list.load(proc_path("2024_11_15_long_mtbi_l_pred_dfs.rds"))
base_uninj_l_pred_dfs <- list.load(proc_path("2024_11_15_base_uninj_l_pred_dfs.rds"))

long_mtbi_0_i1_cluster_df <- long_mtbi_0_pred_dfs[[1]] |> 
    dplyr::select(subjectkey, cluster)
long_mtbi_l_i1_cluster_df <- long_mtbi_l_pred_dfs[[1]] |> 
    dplyr::select(subjectkey, cluster)
base_uninj_l_i1_cluster_df <- base_uninj_l_pred_dfs[[1]] |> 
    dplyr::select(subjectkey, cluster)

long_mtbi_0_i1_cluster_df$cluster |> table() |> prop.table() |> (\(x) 100 * x)()

long_mtbi_l_i1_cluster_df$cluster |> table() |> prop.table() |> (\(x) 100 * x)()

base_uninj_l_i1_cluster_df$cluster |> table() |> prop.table() |> (\(x) 100 * x)()


for_uninj <- c(sorted_features, outcomes)
for_uninj <- for_uninj[for_uninj %in% names(long_mtbi_0_plot_list)]

long_mtbi_0_plot_list <- auto_plot(
    cluster_df = long_mtbi_0_i1_cluster_df,
    data_list = long_mtbi_0_dls[[1]],
    target_list = long_mtbi_0_ols[[1]]
)

long_mtbi_0_all_plots <- wrap_plots(long_mtbi_0_plot_list[for_uninj])

ggsave(
    fig_path("long_mtbi_0_predicted_plots.png", TRUE),
    long_mtbi_0_all_plots,
    width = 45,
    height = 30,
    dpi = 50
)

long_mtbi_l_plot_list <- auto_plot(
    cluster_df = long_mtbi_l_i1_cluster_df,
    data_list = long_mtbi_l_dls[[1]],
    target_list = long_mtbi_l_ols[[1]]
)

long_mtbi_l_all_plots <- wrap_plots(plot_list)

long_mtbi_l_all_plots <- wrap_plots(long_mtbi_l_plot_list[for_uninj])

ggsave(
    fig_path("long_mtbi_l_predicted_plots.png", TRUE),
    long_mtbi_l_all_plots,
    width = 45,
    height = 30,
    dpi = 50
)

# Looks very similar!
```

