# SNF in CBCL Matched Uninjured Controls

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)
library(MatchIt)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subjects <- read_csv(sub_path("2023_11_07_mtbi_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2023_11_07_uninjured_subjects.csv"))
cbcl_matched_uninjured <- read_csv(sub_path("2024_01_23_cbcl_matched_uninjured.csv"))
```

## Loading data and out of model lists

```{r}
data_list_cmu1 <- list.load(input_path("2024_01_23_data_list_cmu1.rds"))
data_list_cmu2 <- list.load(input_path("2024_01_23_data_list_cmu2.rds"))
data_list_cmu3 <- list.load(input_path("2024_01_23_data_list_cmu3.rds"))
data_list_cmu4 <- list.load(input_path("2024_01_23_data_list_cmu4.rds"))
data_list_cmu5 <- list.load(input_path("2024_01_23_data_list_cmu5.rds"))
data_list_cmpu1 <- list.load(input_path("2024_01_23_data_list_cmpu1.rds"))
data_list_cmpu2 <- list.load(input_path("2024_01_23_data_list_cmpu2.rds"))
data_list_cmpu3 <- list.load(input_path("2024_01_23_data_list_cmpu3.rds"))
data_list_cmpu4 <- list.load(input_path("2024_01_23_data_list_cmpu4.rds"))
data_list_cmpu5 <- list.load(input_path("2024_01_23_data_list_cmpu5.rds"))
oom_list_cmu1 <- list.load(input_path("2024_01_23_oom_list_cmu1.rds"))
oom_list_cmu2 <- list.load(input_path("2024_01_23_oom_list_cmu2.rds"))
oom_list_cmu3 <- list.load(input_path("2024_01_23_oom_list_cmu3.rds"))
oom_list_cmu4 <- list.load(input_path("2024_01_23_oom_list_cmu4.rds"))
oom_list_cmu5 <- list.load(input_path("2024_01_23_oom_list_cmu5.rds"))
oom_list_cmpu1 <- list.load(input_path("2024_01_23_oom_list_cmpu1.rds"))
oom_list_cmpu2 <- list.load(input_path("2024_01_23_oom_list_cmpu2.rds"))
oom_list_cmpu3 <- list.load(input_path("2024_01_23_oom_list_cmpu3.rds"))
oom_list_cmpu4 <- list.load(input_path("2024_01_23_oom_list_cmpu4.rds"))
oom_list_cmpu5 <- list.load(input_path("2024_01_23_oom_list_cmpu5.rds"))
```

## Generating custom distance measures

```{r}
my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

summarize_distance_metrics_list(my_distance_metrics)
```

## Re-importing the settings matrix

```{r}
settings_matrix <- read_csv(
    proc_path(
        "2024_01_15_settings_matrix_mu.csv"
    )
)
```

## SNF for each of the imputations

```{r}
# Uninjured only imputed
# Imputation 1
start <- proc.time()
progressr::with_progress({
    solutions_matrix_cmu1 <- batch_snf(
        data_list = data_list_cmu1,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_cmu1, proc_path("solutions_matrix_cmu1.csv", TRUE))
# Imputation 2
start <- proc.time()
progressr::with_progress({
    solutions_matrix_cmu2 <- batch_snf(
        data_list = data_list_cmu2,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_cmu2, proc_path("solutions_matrix_cmu2.csv", TRUE))
# Imputation 3
start <- proc.time()
progressr::with_progress({
    solutions_matrix_cmu3 <- batch_snf(
        data_list = data_list_cmu3,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_cmu3, proc_path("solutions_matrix_cmu3.csv", TRUE))
# Imputation 4
start <- proc.time()
progressr::with_progress({
    solutions_matrix_cmu4 <- batch_snf(
        data_list = data_list_cmu4,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_cmu4, proc_path("solutions_matrix_cmu4.csv", TRUE))
# Imputation 5
start <- proc.time()
progressr::with_progress({
    solutions_matrix_cmu5 <- batch_snf(
        data_list = data_list_cmu5,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_cmu5, proc_path("solutions_matrix_cmu5.csv", TRUE))
#
# Uninjured pooled imputed
# Imputation 1
start <- proc.time()
progressr::with_progress({
    solutions_matrix_cmpu1 <- batch_snf(
        data_list = data_list_cmpu1,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_cmpu1, proc_path("solutions_matrix_cmpu1.csv", TRUE))
# Imputation 2
start <- proc.time()
progressr::with_progress({
    solutions_matrix_cmpu2 <- batch_snf(
        data_list = data_list_cmpu2,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_cmpu2, proc_path("solutions_matrix_cmpu2.csv", TRUE))
# Imputation 3
start <- proc.time()
progressr::with_progress({
    solutions_matrix_cmpu3 <- batch_snf(
        data_list = data_list_cmpu3,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_cmpu3, proc_path("solutions_matrix_cmpu3.csv", TRUE))
# Imputation 4
start <- proc.time()
progressr::with_progress({
    solutions_matrix_cmpu4 <- batch_snf(
        data_list = data_list_cmpu4,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_cmpu4, proc_path("solutions_matrix_cmpu4.csv", TRUE))
# Imputation 5
start <- proc.time()
progressr::with_progress({
    solutions_matrix_cmpu5 <- batch_snf(
        data_list = data_list_cmpu5,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_cmpu5, proc_path("solutions_matrix_cmpu5.csv", TRUE))
```

HERE I AM

## Re-importing the generated solutions

```{r}
solutions_matrix_cmu1 <- read_csv(proc_path("2024_01_23_solutions_matrix_cmu1.csv"))
solutions_matrix_cmu2 <- read_csv(proc_path("2024_01_23_solutions_matrix_cmu2.csv"))
solutions_matrix_cmu3 <- read_csv(proc_path("2024_01_23_solutions_matrix_cmu3.csv"))
solutions_matrix_cmu4 <- read_csv(proc_path("2024_01_23_solutions_matrix_cmu4.csv"))
solutions_matrix_cmu5 <- read_csv(proc_path("2024_01_23_solutions_matrix_cmu5.csv"))
solutions_matrix_cmpu1 <- read_csv(proc_path("2024_01_23_solutions_matrix_cmpu1.csv"))
solutions_matrix_cmpu2 <- read_csv(proc_path("2024_01_23_solutions_matrix_cmpu2.csv"))
solutions_matrix_cmpu3 <- read_csv(proc_path("2024_01_23_solutions_matrix_cmpu3.csv"))
solutions_matrix_cmpu4 <- read_csv(proc_path("2024_01_23_solutions_matrix_cmpu4.csv"))
solutions_matrix_cmpu5 <- read_csv(proc_path("2024_01_23_solutions_matrix_cmpu5.csv"))

all_cmu_imputations <- do.call(
    "rbind",
    list(
        solutions_matrix_cmu1,
        solutions_matrix_cmu2,
        solutions_matrix_cmu3,
        solutions_matrix_cmu4,
        solutions_matrix_cmu5,
        solutions_matrix_cmpu1,
        solutions_matrix_cmpu2,
        solutions_matrix_cmpu3,
        solutions_matrix_cmpu4,
        solutions_matrix_cmpu5
    )
)
```

## Calculating pairwise ARIs

```{r}
# Completed
aris_cmu1 <- calc_om_aris(solutions_matrix_cmu1)
write_csv(data.frame(aris_cmu1), proc_path("aris_cmu1.csv", TRUE))
aris_cmu2 <- calc_om_aris(solutions_matrix_cmu2)
write_csv(data.frame(aris_cmu2), proc_path("aris_cmu2.csv", TRUE))
aris_cmu3 <- calc_om_aris(solutions_matrix_cmu3)
write_csv(data.frame(aris_cmu3), proc_path("aris_cmu3.csv", TRUE))
aris_cmu4 <- calc_om_aris(solutions_matrix_cmu4)
write_csv(data.frame(aris_cmu4), proc_path("aris_cmu4.csv", TRUE))
aris_cmu5 <- calc_om_aris(solutions_matrix_cmu5)
write_csv(data.frame(aris_cmu5), proc_path("aris_cmu5.csv", TRUE))
aris_cmpu1 <- calc_om_aris(solutions_matrix_cmpu1)
write_csv(data.frame(aris_cmpu1), proc_path("aris_cmpu1.csv", TRUE))
aris_cmpu2 <- calc_om_aris(solutions_matrix_cmpu2)
write_csv(data.frame(aris_cmpu2), proc_path("aris_cmpu2.csv", TRUE))
aris_cmpu3 <- calc_om_aris(solutions_matrix_cmpu3)
write_csv(data.frame(aris_cmpu3), proc_path("aris_cmpu3.csv", TRUE))
aris_cmpu4 <- calc_om_aris(solutions_matrix_cmpu4)
write_csv(data.frame(aris_cmpu4), proc_path("aris_cmpu4.csv", TRUE))
aris_cmpu5 <- calc_om_aris(solutions_matrix_cmpu5)
write_csv(data.frame(aris_cmpu5), proc_path("aris_cmpu5.csv", TRUE))
aris_all_cmu_imputations <- calc_om_aris(all_cmu_imputations)
write_csv(
    data.frame(aris_all_cmu_imputations),
    proc_path("aris_all_cmu_imputations.csv", TRUE)
)
```

## Re-importing the ARIs

```{r}
aris_cmu1 <- read_csv(proc_path("2024_01_23_aris_cmu1.csv")) |> as.matrix()
aris_cmu2 <- read_csv(proc_path("2024_01_23_aris_cmu2.csv")) |> as.matrix()
aris_cmu3 <- read_csv(proc_path("2024_01_23_aris_cmu3.csv")) |> as.matrix()
aris_cmu4 <- read_csv(proc_path("2024_01_23_aris_cmu4.csv")) |> as.matrix()
aris_cmu5 <- read_csv(proc_path("2024_01_23_aris_cmu5.csv")) |> as.matrix()
aris_cmpu1 <- read_csv(proc_path("2024_01_23_aris_cmpu1.csv")) |> as.matrix()
aris_cmpu2 <- read_csv(proc_path("2024_01_23_aris_cmpu2.csv")) |> as.matrix()
aris_cmpu3 <- read_csv(proc_path("2024_01_23_aris_cmpu3.csv")) |> as.matrix()
aris_cmpu4 <- read_csv(proc_path("2024_01_23_aris_cmpu4.csv")) |> as.matrix()
aris_cmpu5 <- read_csv(proc_path("2024_01_23_aris_cmpu5.csv")) |> as.matrix()

aris_all_cmu_imputations <- read_csv(
    proc_path("2024_01_23_aris_all_cmu_imputations.csv")
) |>
    as.matrix()
```

## Plotting the ARIs

### Initial plot across all ARIs to extract order

```{r}
aris_all_cmu_imputations_heatmap <- similarity_matrix_heatmap(
    aris_all_cmu_imputations,
    log_graph = FALSE,
    cluster_rows = TRUE,
    cluster_columns = TRUE
)

aris_all_cmu_imputations_heatmap <- ComplexHeatmap::draw(
    aris_all_cmu_imputations_heatmap
)
aris_all_cmu_imputations_order <- ComplexHeatmap::row_order(
    aris_all_cmu_imputations_heatmap
)

write_csv(
    data.frame(aris_all_cmu_imputations_order),
    proc_path("aris_all_cmu_imputations_order.csv", TRUE)
)
```

### Re-importing the order

```{r}
aris_all_cmu_imputations_order <- unlist(
    read_csv(proc_path("2024_01_23_aris_all_cmu_imputations_order.csv"))
)

names(aris_all_cmu_imputations_order) <- NULL
```

## Full imputation meta clustering plot with impairment levels

```{r}
imputation_labels <- data.frame(
    "imputation" = c(
        rep("u1", 200),
        rep("u2", 200),
        rep("u3", 200),
        rep("u4", 200),
        rep("u5", 200),
        rep("pu1", 200),
        rep("pu2", 200),
        rep("pu3", 200),
        rep("pu4", 200),
        rep("pu5", 200)
    ),
    "pooled" = c(
        rep("yes", 1000),
        rep("no", 1000)
    )
)

full_cmu_solutions_matrix <- cbind(all_cmu_imputations, imputation_labels)

full_cmu_solutions_matrix$"nclust2" <- full_cmu_solutions_matrix$"nclust" - 2

full_cmu_extended_solutions_matrix <- extend_solutions(
    full_cmu_solutions_matrix,
    oom_list_cmu1
)

write_csv(
    full_cmu_extended_solutions_matrix,
    proc_path("full_cmu_extended_solutions_matrix.csv", TRUE)
)

full_cmu_extended_solutions_matrix <- read_csv(
    proc_path("2024_01_23_full_cmu_extended_solutions_matrix.csv")
)

pval_select <- function(extended_solutions_matrix,
                        keep_summary = TRUE,
                        negative_log = FALSE,
                        recalculate_summary = TRUE) {
    pval_df <- extended_solutions_matrix |>
        dplyr::select(
            "row_id",
            dplyr::ends_with("_p"),
            dplyr::contains("p_val")
        ) |>
        data.frame() |>
        metasnf::numcol_to_numeric()
    if (!keep_summary) {
        pval_df <- pval_df |>
            dplyr::select(-c("min_p_val", "mean_p_val"))
    }
    if (negative_log) {
        neg_log_pval_df <- -log(pval_df)
        neg_log_pval_df$"row_id" <- pval_df$"row_id"
        pval_df <- neg_log_pval_df
        if (recalculate_summary) {
            mini_df <- pval_df |> dplyr::select(
                dplyr::ends_with("_p")
            )
            pval_df$"mean_neglog_p" <- apply(mini_df, 1, FUN = mean)
            pval_df$"max_neglog_p" <- apply(mini_df, 1, FUN = max)
        }
    }
    return(pval_df)
}

full_cmu_oom_pvals <- pval_select(
    full_cmu_extended_solutions_matrix,
    negative_log = TRUE
)

full_cmu_extended_solutions_matrix$"mean_neglog_p" <-
    full_cmu_oom_pvals$"mean_neglog_p"

divergent_colours <- function(column)  {
    values <- unique(column)
    colours <- RColorBrewer::brewer.pal(n = length(values), name = "Set3")
    names(colours) <- values
    return(colours)
}

hm_colours <- function(data, max_red = TRUE) {
    if (max_red) {
        colours <- circlize::colorRamp2(
            c(min(data), max(data)),
            c("black", "red")
        )
    } else {
        colours <- circlize::colorRamp2(
            c(min(data), max(data)),
            c("red", "black")
        )
    }
    return(colours)
}

aris_all_cmu_imputations_annotated_heatmap <- similarity_matrix_heatmap(
    aris_all_cmu_imputations,
    order = aris_all_cmu_imputations_order,
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    log_graph = FALSE,
    data = data.frame(full_cmu_extended_solutions_matrix),
    top_hm = list(
        "Scheme" = "snf_scheme",
        "Impairment Separation" = "mean_neglog_p"
    ),
    left_hm = list(
        "Pooled" = "pooled",
        "Imputation" = "imputation"
    ),
    top_bar = list(
        "Number of Clusters - 2" = "nclust2"
    ),
    scale_diag = "none",
    heatmap_height = grid::unit(19, "cm"),
    heatmap_width = grid::unit(19, "cm"),
    annotation_colours = list(
        "Pooled" = c(
            "yes" = "orange",
            "no" = "purple"
        ),
        "Imputation" = divergent_colours(
            full_cmu_extended_solutions_matrix$"imputation"
        ),
        "Scheme" = c(
            "1" = "#7FC97F",
            "2" = "#BEAED4",
            "3" = "#FDC086"
        ),
        "Impairment Separation" = hm_colours(
            full_cmu_extended_solutions_matrix$"mean_neglog_p"
        )
    ),
    col = circlize::colorRamp2(
        c(min(aris_all_cmu_imputations), max(aris_all_cmu_imputations)),
        c("navy", "red")
    )
)

aris_all_cmu_imputations_annotated_heatmap

# PNG export
grDevices::png(
    fig_path("aris_all_cmu_imputations_annotated_heatmap.png", TRUE),
    width = 3000,
    height = 2700,
    res = 300
)
aris_all_cmu_imputations_annotated_heatmap
grDevices::dev.off()
```

## Optimal 3-cluster solution

```{r}

cmu_3c_solutions <- full_cmu_extended_solutions_matrix |>
    dplyr::filter(nclust == 3)

top_ind <- cmu_3c_solutions$"mean_neglog_p" == max(cmu_3c_solutions$"mean_neglog_p")

top_cmu_3c_solution <- cmu_3c_solutions[top_ind, ]

top_cmu_3c_solution

all_data_list_cmu1 <- c(data_list_cmu1, oom_list_cmu1)

cmu_3c_plots <- characterize_solution(
    top_cmu_3c_solution,
    all_data_list_cmu1,
    "cmu_top_3c"
)

save_plot_list(cmu_3c_plots, "cmu_top_3c")
```

Looks much closer to the mTBI group.
