# SNF in CBCL Matched Uninjured Controls

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)
library(MatchIt)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subjects <- read_csv(sub_path("2024_02_13_mtbi_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2024_02_13_uninjured_subjects.csv"))
cbcl_matched_uninjured <- read_csv(sub_path("2024_02_14_cbcl_matched_uninjured.csv"))

source("abcd/functions.R")
```

## Loading data and out of model lists

```{r}
data_list_cmu1 <- list.load(input_path("2024_02_14_data_list_cmu1.rds"))
data_list_cmu2 <- list.load(input_path("2024_02_14_data_list_cmu2.rds"))
data_list_cmu3 <- list.load(input_path("2024_02_14_data_list_cmu3.rds"))
data_list_cmu4 <- list.load(input_path("2024_02_14_data_list_cmu4.rds"))
data_list_cmu5 <- list.load(input_path("2024_02_14_data_list_cmu5.rds"))
data_list_cmpu1 <- list.load(input_path("2024_02_14_data_list_cmpu1.rds"))
data_list_cmpu2 <- list.load(input_path("2024_02_14_data_list_cmpu2.rds"))
data_list_cmpu3 <- list.load(input_path("2024_02_14_data_list_cmpu3.rds"))
data_list_cmpu4 <- list.load(input_path("2024_02_14_data_list_cmpu4.rds"))
data_list_cmpu5 <- list.load(input_path("2024_02_14_data_list_cmpu5.rds"))
oom_list_cmu1 <- list.load(input_path("2024_02_14_oom_list_cmu1.rds"))
oom_list_cmu2 <- list.load(input_path("2024_02_14_oom_list_cmu2.rds"))
oom_list_cmu3 <- list.load(input_path("2024_02_14_oom_list_cmu3.rds"))
oom_list_cmu4 <- list.load(input_path("2024_02_14_oom_list_cmu4.rds"))
oom_list_cmu5 <- list.load(input_path("2024_02_14_oom_list_cmu5.rds"))
oom_list_cmpu1 <- list.load(input_path("2024_02_14_oom_list_cmpu1.rds"))
oom_list_cmpu2 <- list.load(input_path("2024_02_14_oom_list_cmpu2.rds"))
oom_list_cmpu3 <- list.load(input_path("2024_02_14_oom_list_cmpu3.rds"))
oom_list_cmpu4 <- list.load(input_path("2024_02_14_oom_list_cmpu4.rds"))
oom_list_cmpu5 <- list.load(input_path("2024_02_14_oom_list_cmpu5.rds"))
```

## Generating custom distance measures

```{r}
my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

summarize_distance_metrics_list(my_distance_metrics)
```

## Re-importing the settings matrix

```{r}
settings_matrix <- read_csv(
    proc_path(
        "2024_02_14_settings_matrix_mu.csv"
    )
)

```

## SNF for each of the imputations

```{r}
# Uninjured only imputed
# Imputation 1
start <- proc.time()
progressr::with_progress({
    solutions_matrix_cmu1 <- batch_snf(
        data_list = data_list_cmu1,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_cmu1, proc_path("solutions_matrix_cmu1.csv", TRUE))
# Imputation 2
start <- proc.time()
progressr::with_progress({
    solutions_matrix_cmu2 <- batch_snf(
        data_list = data_list_cmu2,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_cmu2, proc_path("solutions_matrix_cmu2.csv", TRUE))
# Imputation 3
start <- proc.time()
progressr::with_progress({
    solutions_matrix_cmu3 <- batch_snf(
        data_list = data_list_cmu3,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_cmu3, proc_path("solutions_matrix_cmu3.csv", TRUE))
# Imputation 4
start <- proc.time()
progressr::with_progress({
    solutions_matrix_cmu4 <- batch_snf(
        data_list = data_list_cmu4,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_cmu4, proc_path("solutions_matrix_cmu4.csv", TRUE))
# Imputation 5
start <- proc.time()
progressr::with_progress({
    solutions_matrix_cmu5 <- batch_snf(
        data_list = data_list_cmu5,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_cmu5, proc_path("solutions_matrix_cmu5.csv", TRUE))
#
# Uninjured pooled imputed
# Imputation 1
start <- proc.time()
progressr::with_progress({
    solutions_matrix_cmpu1 <- batch_snf(
        data_list = data_list_cmpu1,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_cmpu1, proc_path("solutions_matrix_cmpu1.csv", TRUE))
# Imputation 2
start <- proc.time()
progressr::with_progress({
    solutions_matrix_cmpu2 <- batch_snf(
        data_list = data_list_cmpu2,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_cmpu2, proc_path("solutions_matrix_cmpu2.csv", TRUE))
# Imputation 3
start <- proc.time()
progressr::with_progress({
    solutions_matrix_cmpu3 <- batch_snf(
        data_list = data_list_cmpu3,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_cmpu3, proc_path("solutions_matrix_cmpu3.csv", TRUE))
# Imputation 4
start <- proc.time()
progressr::with_progress({
    solutions_matrix_cmpu4 <- batch_snf(
        data_list = data_list_cmpu4,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_cmpu4, proc_path("solutions_matrix_cmpu4.csv", TRUE))
# Imputation 5
start <- proc.time()
progressr::with_progress({
    solutions_matrix_cmpu5 <- batch_snf(
        data_list = data_list_cmpu5,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_cmpu5, proc_path("solutions_matrix_cmpu5.csv", TRUE))
```

## Re-importing the generated solutions

```{r}
solutions_matrix_cmu1 <- read_csv(proc_path("2024_02_14_solutions_matrix_cmu1.csv"))
solutions_matrix_cmu2 <- read_csv(proc_path("2024_02_14_solutions_matrix_cmu2.csv"))
solutions_matrix_cmu3 <- read_csv(proc_path("2024_02_14_solutions_matrix_cmu3.csv"))
solutions_matrix_cmu4 <- read_csv(proc_path("2024_02_14_solutions_matrix_cmu4.csv"))
solutions_matrix_cmu5 <- read_csv(proc_path("2024_02_14_solutions_matrix_cmu5.csv"))
solutions_matrix_cmpu1 <- read_csv(proc_path("2024_02_14_solutions_matrix_cmpu1.csv"))
solutions_matrix_cmpu2 <- read_csv(proc_path("2024_02_14_solutions_matrix_cmpu2.csv"))
solutions_matrix_cmpu3 <- read_csv(proc_path("2024_02_14_solutions_matrix_cmpu3.csv"))
solutions_matrix_cmpu4 <- read_csv(proc_path("2024_02_14_solutions_matrix_cmpu4.csv"))
solutions_matrix_cmpu5 <- read_csv(proc_path("2024_02_14_solutions_matrix_cmpu5.csv"))

all_cmu_imputations <- do.call(
    "rbind",
    list(
        solutions_matrix_cmu1,
        solutions_matrix_cmu2,
        solutions_matrix_cmu3,
        solutions_matrix_cmu4,
        solutions_matrix_cmu5,
        solutions_matrix_cmpu1,
        solutions_matrix_cmpu2,
        solutions_matrix_cmpu3,
        solutions_matrix_cmpu4,
        solutions_matrix_cmpu5
    )
)
```

## Calculating pairwise ARIs

```{r}
# Completed
aris_cmu1 <- calc_om_aris(solutions_matrix_cmu1, verbose = TRUE)
write_csv(data.frame(aris_cmu1), proc_path("aris_cmu1.csv", TRUE))
aris_cmu2 <- calc_om_aris(solutions_matrix_cmu2, verbose = TRUE)
write_csv(data.frame(aris_cmu2), proc_path("aris_cmu2.csv", TRUE))
aris_cmu3 <- calc_om_aris(solutions_matrix_cmu3, verbose = TRUE)
write_csv(data.frame(aris_cmu3), proc_path("aris_cmu3.csv", TRUE))
aris_cmu4 <- calc_om_aris(solutions_matrix_cmu4, verbose = TRUE)
write_csv(data.frame(aris_cmu4), proc_path("aris_cmu4.csv", TRUE))
aris_cmu5 <- calc_om_aris(solutions_matrix_cmu5, verbose = TRUE)
write_csv(data.frame(aris_cmu5), proc_path("aris_cmu5.csv", TRUE))
aris_cmpu1 <- calc_om_aris(solutions_matrix_cmpu1, verbose = TRUE)
write_csv(data.frame(aris_cmpu1), proc_path("aris_cmpu1.csv", TRUE))
aris_cmpu2 <- calc_om_aris(solutions_matrix_cmpu2, verbose = TRUE)
write_csv(data.frame(aris_cmpu2), proc_path("aris_cmpu2.csv", TRUE))
aris_cmpu3 <- calc_om_aris(solutions_matrix_cmpu3, verbose = TRUE)
write_csv(data.frame(aris_cmpu3), proc_path("aris_cmpu3.csv", TRUE))
aris_cmpu4 <- calc_om_aris(solutions_matrix_cmpu4, verbose = TRUE)
write_csv(data.frame(aris_cmpu4), proc_path("aris_cmpu4.csv", TRUE))
aris_cmpu5 <- calc_om_aris(solutions_matrix_cmpu5, verbose = TRUE)
write_csv(data.frame(aris_cmpu5), proc_path("aris_cmpu5.csv", TRUE))
aris_all_cmu_imputations <- calc_om_aris(all_cmu_imputations, verbose = TRUE)
write_csv(
    data.frame(aris_all_cmu_imputations),
    proc_path("aris_all_cmu_imputations.csv", TRUE)
)
```

This is presumably done after 02-15? Double check to make sure it all ran fine.

## Re-importing the ARIs

```{r}
aris_cmu1 <- read_csv(proc_path("2024_02_15_aris_cmu1.csv")) |> as.matrix()
aris_cmu2 <- read_csv(proc_path("2024_02_15_aris_cmu2.csv")) |> as.matrix()
aris_cmu3 <- read_csv(proc_path("2024_02_15_aris_cmu3.csv")) |> as.matrix()
aris_cmu4 <- read_csv(proc_path("2024_02_15_aris_cmu4.csv")) |> as.matrix()
aris_cmu5 <- read_csv(proc_path("2024_02_15_aris_cmu5.csv")) |> as.matrix()
aris_cmpu1 <- read_csv(proc_path("2024_02_15_aris_cmpu1.csv")) |> as.matrix()
aris_cmpu2 <- read_csv(proc_path("2024_02_15_aris_cmpu2.csv")) |> as.matrix()
aris_cmpu3 <- read_csv(proc_path("2024_02_15_aris_cmpu3.csv")) |> as.matrix()
aris_cmpu4 <- read_csv(proc_path("2024_02_15_aris_cmpu4.csv")) |> as.matrix()
aris_cmpu5 <- read_csv(proc_path("2024_02_15_aris_cmpu5.csv")) |> as.matrix()

aris_all_cmu_imputations <- read_csv(
    proc_path("2024_02_15_aris_all_cmu_imputations.csv")
) |>
    as.matrix()
```

## Plotting the ARIs

### Initial plot across all ARIs to extract order

```{r}
aris_all_cmu_imputations_heatmap <- similarity_matrix_heatmap(
    aris_all_cmu_imputations,
    log_graph = FALSE,
    cluster_rows = TRUE,
    cluster_columns = TRUE
)

aris_all_cmu_imputations_heatmap <- ComplexHeatmap::draw(
    aris_all_cmu_imputations_heatmap
)
aris_all_cmu_imputations_order <- ComplexHeatmap::row_order(
    aris_all_cmu_imputations_heatmap
)

write_csv(
    data.frame(aris_all_cmu_imputations_order),
    proc_path("aris_all_cmu_imputations_order.csv", TRUE)
)
```

### Re-importing the order

```{r}
aris_all_cmu_imputations_order <- unlist(
    read_csv(proc_path("2024_02_25_aris_all_cmu_imputations_order.csv"))
)

names(aris_all_cmu_imputations_order) <- NULL
```

## Full imputation meta clustering plot with impairment levels

```{r}
imputation_labels <- data.frame(
    "imputation" = c(
        rep("u1", 200),
        rep("u2", 200),
        rep("u3", 200),
        rep("u4", 200),
        rep("u5", 200),
        rep("pu1", 200),
        rep("pu2", 200),
        rep("pu3", 200),
        rep("pu4", 200),
        rep("pu5", 200)
    ),
    "pooled" = c(
        rep("yes", 1000),
        rep("no", 1000)
    )
)

full_cmu_solutions_matrix <- cbind(all_cmu_imputations, imputation_labels)
full_cmu_solutions_matrix$"nclust2" <- full_cmu_solutions_matrix$"nclust" - 2

full_cmu_o_extended_solutions_matrix <- extend_solutions(
    full_cmu_solutions_matrix,
    oom_list_cmu1,
    verbose = TRUE,
    min_pval = 1e-10
)
write_csv(
    full_cmu_o_extended_solutions_matrix,
    proc_path("full_cmu_o_extended_solutions_matrix.csv", TRUE)
)
full_cmu_io_extended_solutions_matrix <- extend_solutions(
    full_cmu_solutions_matrix,
    target_list = c(data_list_cmu1, oom_list_cmu1),
    verbose = TRUE,
    min_pval = 1e-10
)
write_csv(
    full_cmu_io_extended_solutions_matrix,
    proc_path("full_cmu_io_extended_solutions_matrix.csv", TRUE)
)
```

```{r}
full_cmu_o_extended_solutions_matrix <- read_csv(
    proc_path("2024_02_25_full_cmu_o_extended_solutions_matrix.csv")
)

full_cmu_io_extended_solutions_matrix <- read_csv(
    proc_path("2024_02_25_full_cmu_io_extended_solutions_matrix.csv")
)
```

```{r}

split_vec <- c(
    690,
    1160,
    1330,
    1395,
    1440,
    1780
)

cmu_mc_heatmap <- my_similarity_matrix_heatmap(
    aris = aris_all_cmu_imputations,
    aris_order = aris_all_cmu_imputations_order,
    extended_solutions = full_cmu_o_extended_solutions_matrix,
    split_vector = split_vec
)
cmu_mc_heatmap


# PNG export
grDevices::png(
    fig_path("cmu_mc_heatmap.png", TRUE),
    width = 3000,
    height = 3000,
    res = 300
)
cmu_mc_heatmap
grDevices::dev.off()
```

## One-MC-at-a-time

```{r}

cmu_manhattan <- my_manhattan_plot(
    solutions_matrix = full_cmu_io_extended_solutions_matrix,
    aris_order = aris_all_cmu_imputations_order,
    split_vector = split_vec,
    data_list = data_list_cmu1,
    target_list = oom_list_cmu1,
    colours = c(
        "I-AS" = "#1B9E77",
        "I-D" = "#D95F02",
        "I-N" = "#7570B3",
        "I-MH" = "#E7298A",
        "I-P" = "#66A61E",
        "O-S" = "#E6AB02",
        "O-B" = "#A6761D"
    )
)
cmu_manhattan

ggsave(
    plot = cmu_manhattan,
    fig_path("cmu_manhattan.png", TRUE),
    width = 15,
    height = 12
)

# Bulk export each MC individually
for (mc in split_letters(split_vec)) {
    print(mc)
    mc_plot <- my_manhattan_plot(
        solutions_matrix = full_cmu_io_extended_solutions_matrix,
        aris_order = aris_all_cmu_imputations_order,
        split_vector = split_vec,
        mcs = mc,
        data_list = data_list_cmu1,
        target_list = oom_list_cmu1,
        colours = c(
            "I-D" = "#D95F02",
            "I-N" = "#7570B3",
            "I-MH" = "#E7298A",
            "I-P" = "#66A61E",
            "O-S" = "#E6AB02",
            "O-B" = "#A6761D"
        )
    )
    mc_path <- paste0(
        "cmu_mc_",
        gsub("-", "_", tolower(mc)),
        "_manhattan.png"
    )
    ggsave(
        plot = mc_plot,
        fig_path(mc_path, TRUE),
        width = 15,
        height = 6
    )
}

```

## Replication in demographic-corrected data

```{r}

data_list_cmu1 <- list.load(input_path("2024_02_14_data_list_cmu1.rds"))
data_list_cmu2 <- list.load(input_path("2024_02_14_data_list_cmu2.rds"))
data_list_cmu3 <- list.load(input_path("2024_02_14_data_list_cmu3.rds"))
data_list_cmu4 <- list.load(input_path("2024_02_14_data_list_cmu4.rds"))
data_list_cmu5 <- list.load(input_path("2024_02_14_data_list_cmu5.rds"))
data_list_cmpu1 <- list.load(input_path("2024_02_14_data_list_cmpu1.rds"))
data_list_cmpu2 <- list.load(input_path("2024_02_14_data_list_cmpu2.rds"))
data_list_cmpu3 <- list.load(input_path("2024_02_14_data_list_cmpu3.rds"))
data_list_cmpu4 <- list.load(input_path("2024_02_14_data_list_cmpu4.rds"))
data_list_cmpu5 <- list.load(input_path("2024_02_14_data_list_cmpu5.rds"))
oom_list_cmu1 <- list.load(input_path("2024_02_14_oom_list_cmu1.rds"))
oom_list_cmu2 <- list.load(input_path("2024_02_14_oom_list_cmu2.rds"))
oom_list_cmu3 <- list.load(input_path("2024_02_14_oom_list_cmu3.rds"))
oom_list_cmu4 <- list.load(input_path("2024_02_14_oom_list_cmu4.rds"))
oom_list_cmu5 <- list.load(input_path("2024_02_14_oom_list_cmu5.rds"))
oom_list_cmpu1 <- list.load(input_path("2024_02_14_oom_list_cmpu1.rds"))
oom_list_cmpu2 <- list.load(input_path("2024_02_14_oom_list_cmpu2.rds"))
oom_list_cmpu3 <- list.load(input_path("2024_02_14_oom_list_cmpu3.rds"))
oom_list_cmpu4 <- list.load(input_path("2024_02_14_oom_list_cmpu4.rds"))
oom_list_cmpu5 <- list.load(input_path("2024_02_14_oom_list_cmpu5.rds"))

data_list_no_demo_cmu1 <- data_list_cmu1
data_list_no_demo_cmu2 <- data_list_cmu2
data_list_no_demo_cmu3 <- data_list_cmu3
data_list_no_demo_cmu4 <- data_list_cmu4
data_list_no_demo_cmu5 <- data_list_cmu5
data_list_no_demo_cmpu1 <- data_list_cmpu1
data_list_no_demo_cmpu2 <- data_list_cmpu2
data_list_no_demo_cmpu3 <- data_list_cmpu3
data_list_no_demo_cmpu4 <- data_list_cmpu4
data_list_no_demo_cmpu5 <- data_list_cmpu5
oom_list_no_demo_cmu1 <- oom_list_cmu1
oom_list_no_demo_cmu2 <- oom_list_cmu2
oom_list_no_demo_cmu3 <- oom_list_cmu3
oom_list_no_demo_cmu4 <- oom_list_cmu4
oom_list_no_demo_cmu5 <- oom_list_cmu5
oom_list_no_demo_cmpu1 <- oom_list_cmpu1
oom_list_no_demo_cmpu2 <- oom_list_cmpu2
oom_list_no_demo_cmpu3 <- oom_list_cmpu3
oom_list_no_demo_cmpu4 <- oom_list_cmpu4
oom_list_no_demo_cmpu5 <- oom_list_cmpu5

demo_list_cmu1 <- data_list_no_demo_cmu1[c(1, 2, 3, 4)]
demo_list_cmu2 <- data_list_no_demo_cmu2[c(1, 2, 3, 4)]
demo_list_cmu3 <- data_list_no_demo_cmu3[c(1, 2, 3, 4)]
demo_list_cmu4 <- data_list_no_demo_cmu4[c(1, 2, 3, 4)]
demo_list_cmu5 <- data_list_no_demo_cmu5[c(1, 2, 3, 4)]
demo_list_cmpu1 <- data_list_no_demo_cmpu1[c(1, 2, 3, 4)]
demo_list_cmpu2 <- data_list_no_demo_cmpu2[c(1, 2, 3, 4)]
demo_list_cmpu3 <- data_list_no_demo_cmpu3[c(1, 2, 3, 4)]
demo_list_cmpu4 <- data_list_no_demo_cmpu4[c(1, 2, 3, 4)]
demo_list_cmpu5 <- data_list_no_demo_cmpu5[c(1, 2, 3, 4)]
data_list_no_demo_cmu1[c(1, 2, 3, 4)] <- NULL
data_list_no_demo_cmu2[c(1, 2, 3, 4)] <- NULL
data_list_no_demo_cmu3[c(1, 2, 3, 4)] <- NULL
data_list_no_demo_cmu4[c(1, 2, 3, 4)] <- NULL
data_list_no_demo_cmu5[c(1, 2, 3, 4)] <- NULL
data_list_no_demo_cmpu1[c(1, 2, 3, 4)] <- NULL
data_list_no_demo_cmpu2[c(1, 2, 3, 4)] <- NULL
data_list_no_demo_cmpu3[c(1, 2, 3, 4)] <- NULL
data_list_no_demo_cmpu4[c(1, 2, 3, 4)] <- NULL
data_list_no_demo_cmpu5[c(1, 2, 3, 4)] <- NULL

data_list_no_demo_cmu1 <- remove_signal(data_list_no_demo_cmu1, demo_list_cmu1)
data_list_no_demo_cmu2 <- remove_signal(data_list_no_demo_cmu2, demo_list_cmu2)
data_list_no_demo_cmu3 <- remove_signal(data_list_no_demo_cmu3, demo_list_cmu3)
data_list_no_demo_cmu4 <- remove_signal(data_list_no_demo_cmu4, demo_list_cmu4)
data_list_no_demo_cmu5 <- remove_signal(data_list_no_demo_cmu5, demo_list_cmu5)
data_list_no_demo_cmpu1 <- remove_signal(data_list_no_demo_cmpu1, demo_list_cmpu1)
data_list_no_demo_cmpu2 <- remove_signal(data_list_no_demo_cmpu2, demo_list_cmpu2)
data_list_no_demo_cmpu3 <- remove_signal(data_list_no_demo_cmpu3, demo_list_cmpu3)
data_list_no_demo_cmpu4 <- remove_signal(data_list_no_demo_cmpu4, demo_list_cmpu4)
data_list_no_demo_cmpu5 <- remove_signal(data_list_no_demo_cmpu5, demo_list_cmpu5)
oom_list_no_demo_cmu1 <- remove_signal(oom_list_no_demo_cmu1, demo_list_cmu1)
oom_list_no_demo_cmu2 <- remove_signal(oom_list_no_demo_cmu2, demo_list_cmu2)
oom_list_no_demo_cmu3 <- remove_signal(oom_list_no_demo_cmu3, demo_list_cmu3)
oom_list_no_demo_cmu4 <- remove_signal(oom_list_no_demo_cmu4, demo_list_cmu4)
oom_list_no_demo_cmu5 <- remove_signal(oom_list_no_demo_cmu5, demo_list_cmu5)
oom_list_no_demo_cmpu1 <- remove_signal(oom_list_no_demo_cmpu1, demo_list_cmpu1)
oom_list_no_demo_cmpu2 <- remove_signal(oom_list_no_demo_cmpu2, demo_list_cmpu2)
oom_list_no_demo_cmpu3 <- remove_signal(oom_list_no_demo_cmpu3, demo_list_cmpu3)
oom_list_no_demo_cmpu4 <- remove_signal(oom_list_no_demo_cmpu4, demo_list_cmpu4)
oom_list_no_demo_cmpu5 <- remove_signal(oom_list_no_demo_cmpu5, demo_list_cmpu5)

# Adding back the demographic variables post-correction
data_list_re_demo_cmu1 <- c(data_list_no_demo_cmu1, demo_list_cmu1)
data_list_re_demo_cmu2 <- c(data_list_no_demo_cmu2, demo_list_cmu2)
data_list_re_demo_cmu3 <- c(data_list_no_demo_cmu3, demo_list_cmu3)
data_list_re_demo_cmu4 <- c(data_list_no_demo_cmu4, demo_list_cmu4)
data_list_re_demo_cmu5 <- c(data_list_no_demo_cmu5, demo_list_cmu5)
data_list_re_demo_cmpu1 <- c(data_list_no_demo_cmpu1, demo_list_cmpu1)
data_list_re_demo_cmpu2 <- c(data_list_no_demo_cmpu2, demo_list_cmpu2)
data_list_re_demo_cmpu3 <- c(data_list_no_demo_cmpu3, demo_list_cmpu3)
data_list_re_demo_cmpu4 <- c(data_list_no_demo_cmpu4, demo_list_cmpu4)
data_list_re_demo_cmpu5 <- c(data_list_no_demo_cmpu5, demo_list_cmpu5)

list.save(data_list_no_demo_cmu1, input_path("data_list_no_demo_cmu1.rds", TRUE))
list.save(data_list_no_demo_cmu2, input_path("data_list_no_demo_cmu2.rds", TRUE))
list.save(data_list_no_demo_cmu3, input_path("data_list_no_demo_cmu3.rds", TRUE))
list.save(data_list_no_demo_cmu4, input_path("data_list_no_demo_cmu4.rds", TRUE))
list.save(data_list_no_demo_cmu5, input_path("data_list_no_demo_cmu5.rds", TRUE))
list.save(data_list_no_demo_cmpu1,
    input_path("data_list_no_demo_cmpu1.rds", TRUE)
)
list.save(
    data_list_no_demo_cmpu2,
    input_path("data_list_no_demo_cmpu2.rds", TRUE)
)
list.save(
    data_list_no_demo_cmpu3,
    input_path("data_list_no_demo_cmpu3.rds", TRUE)
)
list.save(
    data_list_no_demo_cmpu4,
    input_path("data_list_no_demo_cmpu4.rds", TRUE)
)
list.save(
    data_list_no_demo_cmpu5,
    input_path("data_list_no_demo_cmpu5.rds", TRUE)
)

list.save(data_list_re_demo_cmu1, input_path("data_list_re_demo_cmu1.rds", TRUE))
list.save(data_list_re_demo_cmu2, input_path("data_list_re_demo_cmu2.rds", TRUE))
list.save(data_list_re_demo_cmu3, input_path("data_list_re_demo_cmu3.rds", TRUE))
list.save(data_list_re_demo_cmu4, input_path("data_list_re_demo_cmu4.rds", TRUE))
list.save(data_list_re_demo_cmu5, input_path("data_list_re_demo_cmu5.rds", TRUE))
list.save(data_list_re_demo_cmpu1,
    input_path("data_list_re_demo_cmpu1.rds", TRUE)
)
list.save(
    data_list_re_demo_cmpu2,
    input_path("data_list_re_demo_cmpu2.rds", TRUE)
)
list.save(
    data_list_re_demo_cmpu3,
    input_path("data_list_re_demo_cmpu3.rds", TRUE)
)
list.save(
    data_list_re_demo_cmpu4,
    input_path("data_list_re_demo_cmpu4.rds", TRUE)
)
list.save(
    data_list_re_demo_cmpu5,
    input_path("data_list_re_demo_cmpu5.rds", TRUE)
)

list.save(oom_list_no_demo_cmu1, input_path("oom_list_no_demo_cmu1.rds", TRUE))
list.save(oom_list_no_demo_cmu2, input_path("oom_list_no_demo_cmu2.rds", TRUE))
list.save(oom_list_no_demo_cmu3, input_path("oom_list_no_demo_cmu3.rds", TRUE))
list.save(oom_list_no_demo_cmu4, input_path("oom_list_no_demo_cmu4.rds", TRUE))
list.save(oom_list_no_demo_cmu5, input_path("oom_list_no_demo_cmu5.rds", TRUE))
list.save(oom_list_no_demo_cmpu1, input_path("oom_list_no_demo_cmpu1.rds", TRUE))
list.save(oom_list_no_demo_cmpu2, input_path("oom_list_no_demo_cmpu2.rds", TRUE))
list.save(oom_list_no_demo_cmpu3, input_path("oom_list_no_demo_cmpu3.rds", TRUE))
list.save(oom_list_no_demo_cmpu4, input_path("oom_list_no_demo_cmpu4.rds", TRUE))
list.save(oom_list_no_demo_cmpu5, input_path("oom_list_no_demo_cmpu5.rds", TRUE))

data_list_no_demo_cmu1 <- list.load(
    input_path(
        "2024_02_25_data_list_no_demo_cmu1.rds"
    )
)
data_list_no_demo_cmu2 <- list.load(
    input_path(
        "2024_02_25_data_list_no_demo_cmu2.rds"
    )
)
data_list_no_demo_cmu3 <- list.load(
    input_path(
        "2024_02_25_data_list_no_demo_cmu3.rds"
    )
)
data_list_no_demo_cmu4 <- list.load(
    input_path(
        "2024_02_25_data_list_no_demo_cmu4.rds"
    )
)
data_list_no_demo_cmu5 <- list.load(
    input_path(
        "2024_02_25_data_list_no_demo_cmu5.rds"
    )
)
data_list_no_demo_cmpu1 <- list.load(
    input_path(
        "2024_02_25_data_list_no_demo_cmpu1.rds"
    )
)
data_list_no_demo_cmpu2 <- list.load(
    input_path(
        "2024_02_25_data_list_no_demo_cmpu2.rds"
    )
)
data_list_no_demo_cmpu3 <- list.load(
    input_path(
        "2024_02_25_data_list_no_demo_cmpu3.rds"
    )
)
data_list_no_demo_cmpu4 <- list.load(
    input_path(
        "2024_02_25_data_list_no_demo_cmpu4.rds"
    )
)
data_list_no_demo_cmpu5 <- list.load(
    input_path(
        "2024_02_25_data_list_no_demo_cmpu5.rds"
    )
)

data_list_re_demo_cmu1 <- list.load(
    input_path(
        "2024_02_27_data_list_re_demo_cmu1.rds"
    )
)
data_list_re_demo_cmu2 <- list.load(
    input_path(
        "2024_02_27_data_list_re_demo_cmu2.rds"
    )
)
data_list_re_demo_cmu3 <- list.load(
    input_path(
        "2024_02_27_data_list_re_demo_cmu3.rds"
    )
)
data_list_re_demo_cmu4 <- list.load(
    input_path(
        "2024_02_27_data_list_re_demo_cmu4.rds"
    )
)
data_list_re_demo_cmu5 <- list.load(
    input_path(
        "2024_02_27_data_list_re_demo_cmu5.rds"
    )
)
data_list_re_demo_cmpu1 <- list.load(
    input_path(
        "2024_02_27_data_list_re_demo_cmpu1.rds"
    )
)
data_list_re_demo_cmpu2 <- list.load(
    input_path(
        "2024_02_27_data_list_re_demo_cmpu2.rds"
    )
)
data_list_re_demo_cmpu3 <- list.load(
    input_path(
        "2024_02_27_data_list_re_demo_cmpu3.rds"
    )
)
data_list_re_demo_cmpu4 <- list.load(
    input_path(
        "2024_02_27_data_list_re_demo_cmpu4.rds"
    )
)
data_list_re_demo_cmpu5 <- list.load(
    input_path(
        "2024_02_27_data_list_re_demo_cmpu5.rds"
    )
)

oom_list_no_demo_cmu1 <- list.load(
    input_path(
        "2024_02_27_oom_list_no_demo_cmu1.rds"
    )
)
oom_list_no_demo_cmu2 <- list.load(
    input_path(
        "2024_02_27_oom_list_no_demo_cmu2.rds"
    )
)
oom_list_no_demo_cmu3 <- list.load(
    input_path(
        "2024_02_27_oom_list_no_demo_cmu3.rds"
    )
)
oom_list_no_demo_cmu4 <- list.load(
    input_path(
        "2024_02_27_oom_list_no_demo_cmu4.rds"
    )
)
oom_list_no_demo_cmu5 <- list.load(
    input_path(
        "2024_02_27_oom_list_no_demo_cmu5.rds"
    )
)
oom_list_no_demo_cmpu1 <- list.load(
    input_path(
        "2024_02_27_oom_list_no_demo_cmpu1.rds"
    )
)
oom_list_no_demo_cmpu2 <- list.load(
    input_path(
        "2024_02_27_oom_list_no_demo_cmpu2.rds"
    )
)
oom_list_no_demo_cmpu3 <- list.load(
    input_path(
        "2024_02_27_oom_list_no_demo_cmpu3.rds"
    )
)
oom_list_no_demo_cmpu4 <- list.load(
    input_path(
        "2024_02_27_oom_list_no_demo_cmpu4.rds"
    )
)
oom_list_no_demo_cmpu5 <- list.load(
    input_path(
        "2024_02_27_oom_list_no_demo_cmpu5.rds"
    )
)
```

Quick visualization of correlations between variables

```{r}

corr_order <- read_csv(proc_path("2024_02_27_mtbi_corr_order.csv"))

cmu_corr <- my_corr_plot(
    data_list_cmu1,
    oom_list_cmu1,
    order = corr_order
)

cmu_nd_corr <- my_corr_plot(
    data_list_re_demo_cmu1,
    oom_list_no_demo_cmu1,
    order = corr_order
)

save_png(
    cmu_corr$"heatmap",
    fig_path("cmu_corr_heatmap.png", TRUE),
    width = 3500,
    height = 3500
)

save_png(
    cmu_nd_corr$"heatmap",
    fig_path("cmu_nd_corr_heatmap.png", TRUE),
    width = 3500,
    height = 3500
)

```


```{r}
settings_matrix_no_demo_cmu1 <- generate_settings_matrix(
    data_list_no_demo_cmu1,
    nrow = 200,
    seed = 42,
    distance_metrics_list = my_distance_metrics
)

write_csv(
    settings_matrix_no_demo_cmu1,
    proc_path("settings_matrix_no_demo_cmu1.csv", TRUE)
)

settings_matrix_no_demo_cmu1 <- read_csv(
    proc_path("2024_02_25_settings_matrix_no_demo_cmu1.csv")
)

###############################################################################
# SNF!
###############################################################################

# Uninjured only imputed
# Imputation 1
start <- proc.time()
progressr::with_progress({
    solutions_matrix_no_demo_cmu1 <- batch_snf(
        data_list = data_list_no_demo_cmu1,
        settings_matrix = settings_matrix_no_demo_cmu1,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_no_demo_cmu1,
    proc_path("solutions_matrix_no_demo_cmu1.csv", TRUE)
)
# Imputation 2
start <- proc.time()
progressr::with_progress({
    solutions_matrix_no_demo_cmu2 <- batch_snf(
        data_list = data_list_no_demo_cmu2,
        settings_matrix = settings_matrix_no_demo_cmu1,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_no_demo_cmu2,
    proc_path("solutions_matrix_no_demo_cmu2.csv", TRUE)
)
# Imputation 3
start <- proc.time()
progressr::with_progress({
    solutions_matrix_no_demo_cmu3 <- batch_snf(
        data_list = data_list_no_demo_cmu3,
        settings_matrix = settings_matrix_no_demo_cmu1,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_no_demo_cmu3,
    proc_path("solutions_matrix_no_demo_cmu3.csv", TRUE)
)
# Imputation 4
start <- proc.time()
progressr::with_progress({
    solutions_matrix_no_demo_cmu4 <- batch_snf(
        data_list = data_list_no_demo_cmu4,
        settings_matrix = settings_matrix_no_demo_cmu1,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_no_demo_cmu4,
    proc_path("solutions_matrix_no_demo_cmu4.csv", TRUE)
)
# Imputation 5
start <- proc.time()
progressr::with_progress({
    solutions_matrix_no_demo_cmu5 <- batch_snf(
        data_list = data_list_no_demo_cmu5,
        settings_matrix = settings_matrix_no_demo_cmu1,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_no_demo_cmu5,
    proc_path("solutions_matrix_no_demo_cmu5.csv", TRUE)
)
# mTBI and uninjured pooled imputed
# Imputation 1
start <- proc.time()
progressr::with_progress({
    solutions_matrix_no_demo_cmpu1 <- batch_snf(
        data_list = data_list_no_demo_cmpu1,
        settings_matrix = settings_matrix_no_demo_cmu1,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_no_demo_cmpu1,
    proc_path("solutions_matrix_no_demo_cmpu1.csv", TRUE)
)
# Imputation 2
start <- proc.time()
progressr::with_progress({
    solutions_matrix_no_demo_cmpu2 <- batch_snf(
        data_list = data_list_no_demo_cmpu2,
        settings_matrix = settings_matrix_no_demo_cmu1,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_no_demo_cmpu2,
    proc_path("solutions_matrix_no_demo_cmpu2.csv", TRUE)
)
# Imputation 3
start <- proc.time()
progressr::with_progress({
    solutions_matrix_no_demo_cmpu3 <- batch_snf(
        data_list = data_list_no_demo_cmpu3,
        settings_matrix = settings_matrix_no_demo_cmu1,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_no_demo_cmpu3,
    proc_path("solutions_matrix_no_demo_cmpu3.csv", TRUE)
)
# Imputation 4
start <- proc.time()
progressr::with_progress({
    solutions_matrix_no_demo_cmpu4 <- batch_snf(
        data_list = data_list_no_demo_cmpu4,
        settings_matrix = settings_matrix_no_demo_cmu1,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_no_demo_cmpu4,
    proc_path("solutions_matrix_no_demo_cmpu4.csv", TRUE)
)
# Imputation 5
start <- proc.time()
progressr::with_progress({
    solutions_matrix_no_demo_cmpu5 <- batch_snf(
        data_list = data_list_no_demo_cmpu5,
        settings_matrix = settings_matrix_no_demo_cmu1,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(
    solutions_matrix_no_demo_cmpu5,
    proc_path("solutions_matrix_no_demo_cmpu5.csv", TRUE)
)

solutions_matrix_no_demo_cmu1 <- read_csv(
    proc_path("2024_02_25_solutions_matrix_no_demo_cmu1.csv")
)
solutions_matrix_no_demo_cmu2 <- read_csv(
    proc_path("2024_02_25_solutions_matrix_no_demo_cmu2.csv")
)
solutions_matrix_no_demo_cmu3 <- read_csv(
    proc_path("2024_02_25_solutions_matrix_no_demo_cmu3.csv")
)
solutions_matrix_no_demo_cmu4 <- read_csv(
    proc_path("2024_02_25_solutions_matrix_no_demo_cmu4.csv")
)
solutions_matrix_no_demo_cmu5 <- read_csv(
    proc_path("2024_02_25_solutions_matrix_no_demo_cmu5.csv")
)
solutions_matrix_no_demo_cmpu1 <- read_csv(
    proc_path("2024_02_25_solutions_matrix_no_demo_cmpu1.csv")
)
solutions_matrix_no_demo_cmpu2 <- read_csv(
    proc_path("2024_02_25_solutions_matrix_no_demo_cmpu2.csv")
)
solutions_matrix_no_demo_cmpu3 <- read_csv(
    proc_path("2024_02_25_solutions_matrix_no_demo_cmpu3.csv")
)
solutions_matrix_no_demo_cmpu4 <- read_csv(
    proc_path("2024_02_25_solutions_matrix_no_demo_cmpu4.csv")
)
solutions_matrix_no_demo_cmpu5 <- read_csv(
    proc_path("2024_02_25_solutions_matrix_no_demo_cmpu5.csv")
)

all_cmu_imputations_no_demo <- do.call(
    "rbind",
    list(
        solutions_matrix_no_demo_cmu1,
        solutions_matrix_no_demo_cmu2,
        solutions_matrix_no_demo_cmu3,
        solutions_matrix_no_demo_cmu4,
        solutions_matrix_no_demo_cmu5,
        solutions_matrix_no_demo_cmpu1,
        solutions_matrix_no_demo_cmpu2,
        solutions_matrix_no_demo_cmpu3,
        solutions_matrix_no_demo_cmpu4,
        solutions_matrix_no_demo_cmpu5
    )
)

aris_cmu1_no_demo <- calc_om_aris(solutions_matrix_no_demo_cmu1, verbose = TRUE)
write_csv(data.frame(aris_cmu1_no_demo), proc_path("aris_cmu1_no_demo.csv", TRUE))
aris_cmu2_no_demo <- calc_om_aris(solutions_matrix_no_demo_cmu2, verbose = TRUE)
write_csv(data.frame(aris_cmu2_no_demo), proc_path("aris_cmu2_no_demo.csv", TRUE))
aris_cmu3_no_demo <- calc_om_aris(solutions_matrix_no_demo_cmu3, verbose = TRUE)
write_csv(data.frame(aris_cmu3_no_demo), proc_path("aris_cmu3_no_demo.csv", TRUE))
aris_cmu4_no_demo <- calc_om_aris(solutions_matrix_no_demo_cmu4, verbose = TRUE)
write_csv(data.frame(aris_cmu4_no_demo), proc_path("aris_cmu4_no_demo.csv", TRUE))
aris_cmu5_no_demo <- calc_om_aris(solutions_matrix_no_demo_cmu5, verbose = TRUE)
write_csv(data.frame(aris_cmu5_no_demo), proc_path("aris_cmu5_no_demo.csv", TRUE))
aris_cmpu1_no_demo <- calc_om_aris(solutions_matrix_no_demo_cmpu1, verbose = TRUE)
write_csv(data.frame(aris_cmpu1_no_demo), proc_path("aris_cmpu1_no_demo.csv", TRUE))
aris_cmpu2_no_demo <- calc_om_aris(solutions_matrix_no_demo_cmpu2, verbose = TRUE)
write_csv(data.frame(aris_cmpu2_no_demo), proc_path("aris_cmpu2_no_demo.csv", TRUE))
aris_cmpu3_no_demo <- calc_om_aris(solutions_matrix_no_demo_cmpu3, verbose = TRUE)
write_csv(data.frame(aris_cmpu3_no_demo), proc_path("aris_cmpu3_no_demo.csv", TRUE))
aris_cmpu4_no_demo <- calc_om_aris(solutions_matrix_no_demo_cmpu4, verbose = TRUE)
write_csv(data.frame(aris_cmpu4_no_demo), proc_path("aris_cmpu4_no_demo.csv", TRUE))
aris_cmpu5_no_demo <- calc_om_aris(solutions_matrix_no_demo_cmpu5, verbose = TRUE)
write_csv(data.frame(aris_cmpu5_no_demo), proc_path("aris_cmpu5_no_demo.csv", TRUE))
aris_all_cmu_imputations_no_demo <- calc_om_aris(
    all_cmu_imputations_no_demo,
    verbose = TRUE
)
write_csv(
    data.frame(aris_all_cmu_imputations_no_demo),
    proc_path("aris_all_cmu_imputations_no_demo.csv", TRUE)
)

```

## Re-importing the ARIs

```{r}
aris_cmu1_no_demo <- read_csv(proc_path("2024_02_25_aris_cmu1_no_demo.csv")) |>
    as.matrix()
aris_cmu2_no_demo <- read_csv(proc_path("2024_02_25_aris_cmu2_no_demo.csv")) |>
    as.matrix()
aris_cmu3_no_demo <- read_csv(proc_path("2024_02_25_aris_cmu3_no_demo.csv")) |>
    as.matrix()
aris_cmu4_no_demo <- read_csv(proc_path("2024_02_25_aris_cmu4_no_demo.csv")) |>
    as.matrix()
aris_cmu5_no_demo <- read_csv(proc_path("2024_02_25_aris_cmu5_no_demo.csv")) |>
    as.matrix()
aris_cmpu1_no_demo <- read_csv(proc_path("2024_02_25_aris_cmpu1_no_demo.csv")) |>
    as.matrix()
aris_cmpu2_no_demo <- read_csv(proc_path("2024_02_25_aris_cmpu2_no_demo.csv")) |>
    as.matrix()
aris_cmpu3_no_demo <- read_csv(proc_path("2024_02_25_aris_cmpu3_no_demo.csv")) |>
    as.matrix()
aris_cmpu4_no_demo <- read_csv(proc_path("2024_02_25_aris_cmpu4_no_demo.csv")) |>
    as.matrix()
aris_cmpu5_no_demo <- read_csv(proc_path("2024_02_25_aris_cmpu5_no_demo.csv")) |>
    as.matrix()
aris_all_cmu_imputations_no_demo <- read_csv(
    proc_path("2024_02_25_aris_all_cmu_imputations_no_demo.csv")
) |>
    as.matrix()
```


## Plotting the ARIs

### Initial plot across all ARIs to extract order

```{r}
aris_all_cmu_imputations_no_demo_heatmap <- similarity_matrix_heatmap(
    aris_all_cmu_imputations_no_demo,
    log_graph = FALSE,
    cluster_rows = TRUE,
    cluster_columns = TRUE
)

aris_all_cmu_imputations_no_demo_heatmap <- ComplexHeatmap::draw(
    aris_all_cmu_imputations_no_demo_heatmap
)
aris_all_cmu_imputations_order_no_demo <- ComplexHeatmap::row_order(
    aris_all_cmu_imputations_no_demo_heatmap
)

write_csv(
    data.frame(aris_all_cmu_imputations_order_no_demo),
    proc_path("aris_all_cmu_imputations_order_no_demo.csv", TRUE)
)
```

### Re-importing the order

```{r}
aris_all_cmu_imputations_order_no_demo <- unlist(
    read_csv(
        proc_path(
            "2024_02_25_aris_all_cmu_imputations_order_no_demo.csv"
        )
    )
)

names(aris_all_cmu_imputations_order_no_demo) <- NULL
```

## Full imputation meta clustering plot with impairment levels

```{r}
imputation_labels <- data.frame(
    "imputation" = c(
        rep("mu1", 200),
        rep("mu2", 200),
        rep("mu3", 200),
        rep("mu4", 200),
        rep("mu5", 200),
        rep("mpu1", 200),
        rep("mpu2", 200),
        rep("mpu3", 200),
        rep("mpu4", 200),
        rep("mpu5", 200)
    ),
    "pooled" = c(
        rep("yes", 1000),
        rep("no", 1000)
    )
)

full_solutions_matrix_no_demo <- cbind(
    all_cmu_imputations_no_demo,
    imputation_labels
)

#full_solutions_matrix_no_demo$"nclust2" <-
#    full_solutions_matrix_no_demo$"nclust" - 2

full_cmu_o_extended_solutions_matrix_no_demo <- extend_solutions(
    full_solutions_matrix_no_demo,
    oom_list_no_demo_cmu1,
    verbose = TRUE,
    min_pval = 1e-10
)
write_csv(
    full_cmu_o_extended_solutions_matrix_no_demo,
    proc_path("full_cmu_o_extended_solutions_matrix_no_demo.csv", TRUE)
)

full_cmu_io_extended_solutions_matrix_no_demo <- extend_solutions(
    full_solutions_matrix_no_demo,
    target_list = c(data_list_no_demo_cmu1, oom_list_no_demo_cmu1),
    verbose = TRUE,
    min_pval = 1e-10
)
write_csv(
    full_cmu_io_extended_solutions_matrix_no_demo,
    proc_path("full_cmu_io_extended_solutions_matrix_no_demo.csv", TRUE)
)

```

```{r}

full_cmu_o_extended_solutions_matrix_no_demo <- read_csv(
    proc_path("2024_02_27_full_cmu_o_extended_solutions_matrix_no_demo.csv")
)

full_cmu_io_extended_solutions_matrix_no_demo <- read_csv(
    proc_path("2024_02_25_full_cmu_io_extended_solutions_matrix_no_demo.csv")
)

cmu_nd_o_esm <- read_csv(
    proc_path("2024_02_27_full_cmu_o_extended_solutions_matrix_no_demo.csv")
)

cmu_nd_io_esm <- read_csv(
    proc_path("2024_02_25_full_cmu_io_extended_solutions_matrix_no_demo.csv")
)

cmu_nd_io_esm$"cbcl_anxdep_p" <- cmu_nd_o_esm$"cbcl_anxdep_p"
cmu_nd_io_esm$"cbcl_withdep_p" <- cmu_nd_o_esm$"cbcl_withdep_p"
cmu_nd_io_esm$"cbcl_somatic_p" <- cmu_nd_o_esm$"cbcl_somatic_p"
cmu_nd_io_esm$"cbcl_social_p" <- cmu_nd_o_esm$"cbcl_social_p"
cmu_nd_io_esm$"cbcl_thought_p" <- cmu_nd_o_esm$"cbcl_thought_p"
cmu_nd_io_esm$"cbcl_attention_p" <- cmu_nd_o_esm$"cbcl_attention_p"
cmu_nd_io_esm$"cbcl_rulebreak_p" <- cmu_nd_o_esm$"cbcl_rulebreak_p"
cmu_nd_io_esm$"cbcl_aggressive_p" <- cmu_nd_o_esm$"cbcl_aggressive_p"

write_csv(cmu_nd_o_esm, proc_path("cmu_nd_o_esm.csv", TRUE))
write_csv(cmu_nd_io_esm, proc_path("cmu_nd_io_esm.csv", TRUE))

```

```{r}
cmu_nd_o_esm <- read_csv(proc_path("2024_02_27_cmu_nd_o_esm.csv"))
cmu_nd_io_esm <- read_csv(proc_path("2024_02_27_cmu_nd_io_esm.csv"))
```

```{r}

split_vec = c(
    295,
    395,
    590,
    705,
    805,
    915,
    1020,
    1255,
    1345,
    1405,
    1500
)
cmu_nd_mc_heatmap <- my_similarity_matrix_heatmap(
    aris = aris_all_cmu_imputations_no_demo,
    aris_order = aris_all_cmu_imputations_order_no_demo,
    extended_solutions = cmu_nd_o_esm,
    split_vector = split_vec
)
cmu_nd_mc_heatmap

# PNG export
grDevices::png(
    fig_path("cmu_nd_mc_heatmap.png", TRUE),
    width = 3000,
    height = 3000,
    res = 300
)
cmu_nd_mc_heatmap
grDevices::dev.off()



```

## One-MC-at-a-time

Candidate clusters here are A, B, D, F, and H

```{r}

cmu_nd_manhattan <- my_manhattan_plot(
    solutions_matrix = cmu_nd_io_esm,
    aris_order = aris_all_cmu_imputations_order_no_demo,
    split_vector = split_vec,
    data_list = data_list_re_demo_cmu1,
    target_list = oom_list_no_demo_cmu1,
    colours = c(
        "I-AS" = "#1B9E77",
        "I-D" = "#D95F02",
        "I-N" = "#7570B3",
        "I-MH" = "#E7298A",
        "I-P" = "#66A61E",
        "O-S" = "#E6AB02",
        "O-B" = "#A6761D"
    )
)
cmu_nd_manhattan

#F looks pretty good!
ggsave(
    plot = cmu_nd_manhattan,
    fig_path("cmu_nd_manhattan.png", TRUE),
    width = 15,
    height = 12*2.5
)

# Bulk export each MC individually
for (mc in split_letters(split_vec)) {
    print(mc)
    mc_plot <- my_manhattan_plot(
        solutions_matrix = cmu_nd_io_esm,
        aris_order = aris_all_cmu_imputations_order_no_demo,
        split_vector = split_vec,
        data_list = data_list_re_demo_cmu1,
        target_list = oom_list_no_demo_cmu1,
        mcs = mc,
        colours = c(
            "I-AS" = "#1B9E77",
            "I-D" = "#D95F02",
            "I-N" = "#7570B3",
            "I-MH" = "#E7298A",
            "I-P" = "#66A61E",
            "O-S" = "#E6AB02",
            "O-B" = "#A6761D"
        )
    )
    mc_path <- paste0(
        "cmu_nd_mc_",
        gsub("-", "_", tolower(mc)),
        "_manhattan.png"
    )
    ggsave(
        plot = mc_plot,
        fig_path(mc_path, TRUE),
        width = 15,
        height = 5
    )
}

```









###############################################################################

## Characterization

```{r}
full_cmu_extended_solutions_matrix <- read_csv(
    proc_path("2024_02_14_full_cmu_extended_solutions_matrix.csv")
)

full_cmu_oom_pvals <- pval_select(
    full_cmu_extended_solutions_matrix,
    negative_log = TRUE
)

full_cmu_extended_solutions_matrix$"mean_neglog_p" <- full_cmu_oom_pvals$"mean_neglog_p"

cmu_sm_order <- unlist(
    read_csv(proc_path("2024_02_14_aris_all_cmu_imputations_order.csv"))
)

names(cmu_sm_order) <- NULL

cmu_sorted_solutions_matrix <- full_cmu_extended_solutions_matrix[cmu_sm_order, ]

cmu_mc_a_solutions <- cmu_sorted_solutions_matrix[1:435, ]
cmu_mc_b_solutions <- cmu_sorted_solutions_matrix[436:820, ]
cmu_mc_c_solutions <- cmu_sorted_solutions_matrix[821:1025, ]
cmu_mc_d_solutions <- cmu_sorted_solutions_matrix[1026:1400, ]
cmu_mc_e_solutions <- cmu_sorted_solutions_matrix[1401:1833, ]
cmu_mc_f_solutions <- cmu_sorted_solutions_matrix[1834:2000, ]

which(cmu_sorted_solutions_matrix$"row_id" == 85 & cmu_sorted_solutions_matrix$"imputation" == "u3")

```

### Setting up total data lists

```{r}
all_data_list_cmu1 <- c(data_list_cmu1, oom_list_cmu1)
all_data_list_cmu2 <- c(data_list_cmu2, oom_list_cmu2)
all_data_list_cmu3 <- c(data_list_cmu3, oom_list_cmu3)
all_data_list_cmu4 <- c(data_list_cmu4, oom_list_cmu4)
all_data_list_cmu5 <- c(data_list_cmu5, oom_list_cmu5)

all_data_list_cmpu1 <- c(data_list_cmpu1, oom_list_cmpu1)
all_data_list_cmpu2 <- c(data_list_cmpu2, oom_list_cmpu2)
all_data_list_cmpu3 <- c(data_list_cmpu3, oom_list_cmpu3)
all_data_list_cmpu4 <- c(data_list_cmpu4, oom_list_cmpu4)
all_data_list_cmpu5 <- c(data_list_cmpu5, oom_list_cmpu5)
```

### Matched control MC C

```{r}

row <- nrow(cmu_mc_c_solutions) %/% 2
cmu_mc_c_solution <- cmu_mc_c_solutions[row, ]
cmu_mc_c_solution$"imputation"

cmu_mc_c_plots <- characterize_solution(
    cmu_mc_c_solution,
    all_data_list_cmu5,
    "cmu_mc_c"
)
save_plot_list_uninj(cmu_mc_c_plots, "cmu_mc_c")

```

## Optimal 3-cluster solution

This solution is also from MC C

```{r}

cmu_3c_solutions <- full_cmu_extended_solutions_matrix |>
    dplyr::filter(nclust == 3)
top_ind <- cmu_3c_solutions$"mean_neglog_p" == max(cmu_3c_solutions$"mean_neglog_p")
top_cmu_3c_solution <- cmu_3c_solutions[top_ind, ]
row <- nrow(top_cmu_3c_solution) %/% 2
top_cmu_3c_solution <- top_cmu_3c_solution[row, ]
top_cmu_3c_solution$"imputation"
top_cmu_3c_solution$"row_id" #85

write_csv(top_cmu_3c_solution, proc_path("top_cmu_3c_solution", TRUE))

get_clusters(top_cmu_3c_solution)

# Restructuring so that the cluster label is the same

for (i in 1:ncol(top_cmu_3c_solution)) {
    cname <- colnames(top_cmu_3c_solution)[i]
    if (grepl("subject_", cname)) {
        if (top_cmu_3c_solution[1, cname] == 1) {
            top_cmu_3c_solution[1, cname] <- 2
        } else if (top_cmu_3c_solution[1, cname] == 2) {
            top_cmu_3c_solution[1, cname] <- 3
        } else if (top_cmu_3c_solution[1, cname] == 3) {
            top_cmu_3c_solution[1, cname] <- 1
        }
    }
}

get_clusters(top_cmu_3c_solution)

cmu_3c_plots <- characterize_solution(
    top_cmu_3c_solution,
    all_data_list_cmu3,
    "cmu_top_3c"
)
save_plot_list_uninj(cmu_3c_plots, "cmu_top_3c")


cmu_3c_characterization <- extend_solutions(
    top_cmu_3c_solution,
    data_list_cmu3
)
cmu_3c_pvals <- p_val_select(cmu_3c_characterization)
cmu_3c_pvals$"row_id" <- top_cmu_3c_solution$"row_id"
cmu_3c_pvals$"mc_label" <- "CMU-C"

cmu_3c_pvals <- cmu_3c_pvals |>
    dplyr::select(
        -dplyr::starts_with("cbcl"),
        -dplyr::starts_with("sds"),
        -dplyr::starts_with("mean")
    )

cmu_3c_associations <- manhattan_plot(
    cmu_3c_pvals,
    threshold = 0.05,
    bonferroni_line = FALSE,
    data_list = data_list_cmu3,
    colours = c("#A3A500", "#00BF7D", "#00B0F6", "#E76BF3")
)

cmu_3c_associations

ggsave(
    plot = cmu_3c_associations,
    fig_path("top_cmu_3c_associations.png", TRUE),
    width = 10,
    height = 3
)

```

Looks much closer to the mTBI group.
I can follow this up with some permutation testing to examine differences between the two groups.
