# Building a Classifier

## Importing packages

```{r}
library(readr)
library(here)
library(abcdutils)
library(dplyr)
library(caret)
library(xgboost)
library(randomForest)
library(fastDummies)
library(skimr)
library(doParallel)
library(future)
library(future.apply)
library(patchwork)
```

## Establishing file paths

```{r}
input_path <- path_maker(here(paste0("data/abcd/inputs")))
core_path <- path_maker(here(paste0("data/abcd/core")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
model_path <- path_maker(here(paste0("data/abcd/results/models")))

import <- function(path) {
    return(abcd_load(core_path(path)))
}

```

## Preparing baseline concussion sample data for training

### Feature selection

We'll only use features that were both considered generalizable and that are present in uninjured children.
These features are the same as those that were characterized in the matched uninjured group.

```{r}
# Data frame of all features extracted for baseline concussion sample
mtbi_ful_df <- readRDS(proc_path("2025_06_11_mtbi_ful_df.rds"))

# Data frame with generalizable features from baseline solution in long format
mtbi_gen_fts_table_hits <- read_csv(proc_path("2025_06_13_mtbi_gen_fts_table_hits.csv"))

mtbi

# Undummying
classifier_fts <- mtbi_gen_fts_table_hits$feature
classifier_fts <- gsub("race_.+", "race", classifier_fts)
classifier_fts <- gsub("mtbi_mechanism_.+", "mtbi_mechanism", classifier_fts)
classifier_fts <- unique(classifier_fts)
# Stripping away mTBI specific features - generally weren't that high (position 51 and 55 to 58)
classifier_fts <- classifier_fts[!grepl("mtbi", classifier_fts)]

saveRDS(classifier_fts, proc_path("classifier_fts.rds", TRUE))
```

```{r}
classifier_fts <- readRDS(proc_path("2025_06_13_classifier_fts.rds"))
ifts <- readRDS(proc_path("2025_06_11_ifts.rds"))

classifier_ifts <- classifier_fts[classifier_fts %in% ifts]

saveRDS(classifier_ifts, proc_path("classifier_ifts.rds", TRUE))

classifier_ifts <- readRDS(proc_path("2025_06_13_classifier_ifts.rds"))

for (ft in classifier_ifts) {
    print(ft)
}
```

The features used for classification are:

1. sex
2. brain_volume
3. cortical_sa
4. household_income
5. pubertal_status_p
6. activities_last_year
7. extracurriculars
8. parent_somatic
9. parent_thought
10. private_instruction
11. parent_depress
12. weekday_screentime
13. fmri_cort_cors
14. parent_anxdisord
15. parent_antisocial
16. parent_aggressive
17. parent_anxdep
18. race
19. parent_withdrawn
20. parent_attention
21. parent_hyperactive
22. parent_avoidant
23. parent_perstr
24. family_fight_p
25. considerate_y
26. weekend_screentime
27. physical_activity
28. family_criticize_p
29. fmri_cort_subcort_cors
30. school_activities
31. helps_hurt_p
32. headache_history
33. considerate_p
34. family_outdo_p
35. family_criticize_y
36. cortical_thickness
37. pericortical_wm_ndi
38. family_throw_p
39. same_sex_close_friend
40. family_hit_p
41. age
42. same_sex_friend
43. family_angry_p
44. pubertal_status_y
45. family_outdo_y
46. helpful_p
47. family_peaceful_y
48. family_yell_y
49. helps_hurt_y
50. helpful_y
51. family_throw_y
52. family_fight_y

```{r}
# Reducing mtbi_ful_df to only contain the classifier features
mtbi_classification_df <- dplyr::select(
    mtbi_ful_df,
    uid,
    all_of(classifier_ifts),
    cluster
)

write_csv(mtbi_classification_df, proc_path("mtbi_classification_df.csv", TRUE))
```

```{r}
# CHECKPOINT
mtbi_classification_df <- read_csv(proc_path("2025_06_13_mtbi_classification_df.csv"))
```

### 80/20 train/test split

```{r}
# These observations were previously shuffled with seed 42
set.seed(1111)
shuffled_df <- mtbi_classification_df[sample(nrow(mtbi_classification_df)), ]

nrow(mtbi_classification_df) * 0.8

train_classification_df <- shuffled_df[1:347, ]
test_classification_df <- shuffled_df[347:434, ]

write_csv(
    train_classification_df,
    proc_path("train_classification_df.csv", TRUE)
)

write_csv(
    test_classification_df,
    proc_path("test_classification_df.csv", TRUE)
)
```

```{r}
# CHECKPOINT
train_classification_df <- read_csv(
    proc_path("2025_06_13_train_classification_df.csv")
)

test_classification_df <- read_csv(
    proc_path("2025_06_13_test_classification_df.csv")
)
```

### Time-scaling temporally sensitive features

```{r}
# Age
abcd_y_lt <- import("abcd-general/abcd_y_lt.csv")
# Pubertal development scale, youth report
ph_y_pds <- import("physical-health/ph_y_pds.csv")
# Pubertal development scale, parent report
ph_p_pds <- import("physical-health/ph_p_pds.csv")
# Parent report of gender identity
gish_p_gi <- import("gender-identity-sexual-health/gish_p_gi.csv")
# Subcortical volumes (ASEG)
mri_y_smr_vol_aseg <- import("imaging/mri_y_smr_vol_aseg.csv")
# Desikan cortical thicknesses
mri_y_smr_thk_dsk <- import("imaging/mri_y_smr_thk_dsk.csv")
# Desikan cortical surface areas
mri_y_smr_area_dsk <- import("imaging/mri_y_smr_area_dsk.csv")
# Number of friends
mh_y_or <- import("mental-health/mh_y_or.csv")
# Screen time
nt_p_stq <- import("novel-technologies/nt_p_stq.csv")
```

```{r}
train_classification_df <- read_csv(
    proc_path("2025_06_13_train_classification_df.csv")
)

test_classification_df <- read_csv(
    proc_path("2025_06_13_test_classification_df.csv")
)

for (name in colnames(train_classification_df)) {
    print(name)
}

subc_v <- get_subc_v(mri_y_smr_vol_aseg, t = 0)
cort_t <- get_cort_t(mri_y_smr_thk_dsk, t = 0)
cort_sa <- get_cort_sa(mri_y_smr_area_dsk, t = 0)
pubertal_status_p <- get_pubertal_status_p(ph_p_pds, max_value = 3, t = 0)
pubertal_status_y <- get_pubertal_status_y(ph_y_pds, max_value = 3, t = 0)
age <- get_interview_age(abcd_y_lt, t = 0, as_years = FALSE)
screen_time <- get_screen_time(nt_p_stq, t = 0)

subc_v_t2 <- get_subc_v(mri_y_smr_vol_aseg, t = 2)
cort_t_t2 <- get_cort_t(mri_y_smr_thk_dsk, t = 2)
cort_sa_t2 <- get_cort_sa(mri_y_smr_area_dsk, t = 2)
pubertal_status_p_t2 <- get_pubertal_status_p(ph_p_pds, max_value = 4, t = 2)
pubertal_status_y_t2 <- get_pubertal_status_y(ph_y_pds, max_value = 4, t = 2)
age_t2 <- get_interview_age(abcd_y_lt, t = 2, as_years = FALSE)
screen_time_t2 <- get_screen_time(nt_p_stq, t = 2)
```

Temporally sensitive features:

- brain_volume
- cortical_sa
- pubertal_status_p
- age
- weekday_screentime
- weekend_screentime
- cortical_thickness
- pubertal_status_y


```{r}
temporal_df <- metasnf::merge_df_list(
    list(
        subc_v,
        cort_t,
        cort_sa,
        pubertal_status_p,
        pubertal_status_y,
        age,
        screen_time
    ),
    uid = "subjectkey"
)

temporal_df2 <- metasnf::merge_df_list(
    list(
        subc_v_t2,
        cort_t_t2,
        cort_sa_t2,
        pubertal_status_p_t2,
        pubertal_status_y_t2,
        age_t2,
        screen_time_t2
    ),
    uid = "subjectkey"
)

temporal_df <- temporal_df |> dplyr::rename(
    "uid" = "subjectkey",
    "age" = "interview_age",
    "brain_volume" = "smri_vol_scs_wholeb",
    "cortical_thickness" = "smri_thick_cdk_mean",
    "cortical_sa" = "smri_area_cdk_total",
    "weekend_screentime" = "screentime_wknd_hrs",
    "weekday_screentime" = "screentime_wkday_hrs"
)

temporal_df2 <- temporal_df2 |> dplyr::rename(
    "uid" = "subjectkey",
    "age" = "interview_age",
    "brain_volume" = "smri_vol_scs_wholeb",
    "cortical_thickness" = "smri_thick_cdk_mean",
    "cortical_sa" = "smri_area_cdk_total",
    "weekend_screentime" = "screentime_wknd_hrs",
    "weekday_screentime" = "screentime_wkday_hrs"
)

temporal_df$"uid" <- paste0("uid_", temporal_df$"uid")
temporal_df2$"uid" <- paste0("uid_", temporal_df2$"uid")

saveRDS(temporal_df, proc_path("temporal_df.rds", TRUE))
saveRDS(temporal_df2, proc_path("temporal_df2.rds", TRUE))

temporal_df <- readRDS(proc_path("2025_06_13_temporal_df.rds"))

temporal_df <- temporal_df |> 
    dplyr::filter(
        !uid %in% c(
            train_classification_df$"uid",
            test_classification_df$"uid"
        )
    )

scaling_df <- dplyr::bind_rows(
    temporal_df,
    train_classification_df[, colnames(temporal_df)],
    test_classification_df[, colnames(temporal_df)]
)
scale_cols <- colnames(temporal_df)[2:ncol(temporal_df)]
scaling_df[scale_cols] <- sapply(scaling_df[scale_cols], scale)

train_scale_df <- train_classification_df |>
    dplyr::select(-dplyr::all_of(scale_cols)) |>
    dplyr::inner_join(scaling_df, by = "uid") |>
    data.frame()

test_scale_df <- test_classification_df |>
    dplyr::select(-dplyr::all_of(scale_cols)) |>
    dplyr::inner_join(scaling_df, by = "uid") |>
    data.frame()

write_csv(train_scale_df, proc_path("train_scale_df.csv", TRUE))
write_csv(test_scale_df, proc_path("test_scale_df.csv", TRUE))
```

Temporally sensitive features have now been z-scored across all ABCD values for that time point.

```{r}
# CHECKPOINT
train_scale_df <- read_csv(proc_path("2025_06_13_train_scale_df.csv"))
test_scale_df <- read_csv(proc_path("2025_06_13_test_scale_df.csv"))
```

### Final preparatory steps

The `prep_data()` function is used to prepare the data for training by removing the `uid` column, creating dummy variables for the `race` column, and converting certain columns to ordered factors.
The function also standardizes the data if specified.

```{r}
prep_data <- function(df, standardize = FALSE) {
    df <- dplyr::select(df, -"uid")
    df <- dummy_cols(
        df,
        select_columns = "race",
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = TRUE
    )
    # This can be built by calling skim(df[, sort(colnames(df))])
    ordered_factors <- c(
        "activities_last_year",
        "considerate_y",
        "considerate_p",
        "extracurriculars",
        "family_angry_p",
        "family_angry_y",
        "family_criticize_p",
        "family_criticize_y",
        "family_fight_p",
        "family_fight_y",
        "family_hit_p",
        "family_hit_y",
        "family_outdo_p",
        "family_outdo_y",
        "family_peaceful_p",
        "family_peaceful_y",
        "family_throw_p",
        "family_throw_y",
        "family_yell_p",
        "family_yell_y",
        "helpful_p",
        "helpful_y",
        "helps_hurt_p",
        "helps_hurt_y",
        "household_income",
        "private_instruction",
        "pubertal_status_p",
        "pubertal_status_y",
        "race_black",
        "race_hispanic",
        "race_other",
        "same_sex_close_friend",
        "same_sex_friend",
        "school_activities",
        "sex"
    )
    ordered_factors <- ordered_factors[ordered_factors %in% colnames(df)]
    df[ordered_factors] <- lapply(df[ordered_factors], as.ordered)
    if (standardize) {
        df[] <- lapply(df, as.numeric)
        df <- as.data.frame(scale(df))
    }
    if ("cluster" %in% colnames(df)) {
        df$"cluster" <- as.factor(df$"cluster")
    }
    return(df)
}
```

## Setting up classifier training

The `unregister_dopar()` function is used to clean up the environment after parallel processing.

```{r}
unregister_dopar <- function() {
  env <- foreach:::.foreachGlobals
  rm(list=ls(name=env), pos=env)
}
```

## Caret CV

`train_control` defines the type of cross-validation (in this case, 5-fold grid-searching) to be used.

```{r}
train_control <- caret::trainControl(
    method = "cv",             # Cross-validation
    number = 5,                # 5-fold CV
    search = "grid",           # Grid search
    verboseIter = TRUE
)
```

## Classifier training

### Random forest

Each model is trained with a nested-CV like process:

1. training subset of the data: hyperparameter grid search over CV to find the best hyperparameters
2. full subset of the data: fixed hyperparameter CV to get an estimate of model performance
3. full subset of the data again: fit the inner nested hyperparameters for final model

For random forest, I vary the following hyperparameters:

- Number of trees
- number of attributes that are randomly selected for the split search when constructing each tree
- limits on the tree depth (for each tree)

```{r}
set.seed(42)
training_data <- prep_data(train_scale_df)
```

```{r}
# Hyperparameters
mtrys <- seq(0, 20, by = 2)
mtrys[1] <- 1
tune_grid <- data.frame(mtry = mtrys)
#tune_grid <- expand.grid(mtry = c(1:15))
time <- Sys.time()
cl <- makePSOCKcluster(100)
registerDoParallel(cl)
trained_models <- list()
counter <- 0
for (maxnodes in c(10, 20, 30, 40, 50)) {
    for (nodesize in c(1:5)) {
        for (ntree in c(100, 1000, 2000, 3000)) {
            rf_model <- train(
                cluster ~ .,
                data = training_data,
                method = "rf",
                trControl = train_control,
                tuneGrid = tune_grid,
                ntree = ntree,
                maxnodes = maxnodes,
                nodesize = nodesize
            )
            trained_models[[length(trained_models) + 1]] <- rf_model
            names(trained_models)[[length(trained_models)]] <- paste0(
                "maxnodes_", maxnodes,
                "nodesize_", nodesize,
                "ntree_", ntree
            )
            counter <- counter + 1
            print(paste0(round(counter / (5*5*4) * 100, 2), "% complete..."))
        }
    }
}
saveRDS(trained_models, model_path("rf_models.rds", TRUE))
stopCluster(cl)
unregister_dopar()
print(Sys.time() - time)
# rf_models <- readRDS(model_path("2025_06_13_rf_models.rds"))
```

### SVM

```{r}
set.seed(42)
svm_tune_grid_1 <- expand.grid(
    sigma = c(0.001, 0.01, 0.1, 0.5, 1),
    C = c(0.1, 1, 10, 100, 1000)
)

svm_model <- train(
  cluster ~ .,                # Formula for the model
  data = prep_data(train_scale_df, TRUE),                # Your dataset
  method = "svmRadial",       # Using radial kernel
  trControl = train_control,  # Cross-validation settings
  tuneGrid = svm_tune_grid_1        # Hyperparameter grid to tune
)

print(svm_model)

svm_tune_grid_2 <- expand.grid(
    sigma = c(0.001, 0.01, 0.05, 0.1, 0.25, 0.5),
    C = c(0.1, 0.5, 1, 2, 5, 10, 25, 50, 100, 200, 400, 600, 750, 1000)
)

svm_model2 <- train(
  cluster ~ .,                # Formula for the model
  data = prep_data(train_scale_df, TRUE),                # Your dataset
  method = "svmRadial",       # Using radial kernel
  trControl = train_control,  # Cross-validation settings
  tuneGrid = svm_tune_grid_2        # Hyperparameter grid to tune
)

print(svm_model2)

svm_model2$"results" |>
    ggplot(aes(x = C, y = sigma, color = Accuracy, size = Accuracy)) +
    geom_jitter() +
    theme_bw()


svm_tune_grid_3 <- expand.grid(
    sigma = c(1e-6, 0.0001, 0.001, 0.01, 0.05),
    C = c(0.1, 0.5, 1, 10, 50, 100, 200, 500)
)

svm_model3 <- train(
  cluster ~ .,                # Formula for the model
  data = prep_data(train_scale_df, TRUE),                # Your dataset
  method = "svmRadial",       # Using radial kernel
  trControl = train_control,  # Cross-validation settings
  tuneGrid = svm_tune_grid_3        # Hyperparameter grid to tune
)

# sigma at 1e-4 to 1e-2 seems good
svm_tune_sigma <- svm_model3$"results" |>
    ggplot(aes(x = sigma, y = Accuracy, color = log(C))) +
    geom_jitter(size = 3) +
    theme_bw() +
    scale_x_log10()
# C at ~10 - 100 seems good
svm_tune_c <- svm_model3$"results" |>
    ggplot(aes(x = C, y = Accuracy, color = log(sigma))) +
    geom_point(size = 3) +
    theme_bw()
svm_tuning_plots <- wrap_plots(list(svm_tune_sigma, svm_tune_c), ncol = 2)

ggsave(
    fig_path("svm_tuning_plots.png", TRUE),
    svm_tuning_plots,
    width = 10,
    height = 4,
    dpi = 100
)

saveRDS(svm_model3, model_path("svm_model.rds", TRUE))
svm_model <- readRDS(model_path("2025_06_13_svm_model.rds"))
```

### K-NN

```{r}
# Train the KNN model
knn_model <- train(
  cluster ~ ., 
  data = prep_data(train_scale_df, TRUE), 
  method = "knn", 
  trControl = train_control, 
  tuneLength = 130  # Tuning k (number of neighbors)
)

saveRDS(knn_model, model_path("knn_model.rds", TRUE))

knn_model <- readRDS(model_path("2025_06_13_knn_model.rds"))
```

### Comparisons

```{r}
knn_model <- readRDS(model_path("2025_06_13_knn_model.rds"))
rf_models <- readRDS(model_path("2025_06_13_rf_models.rds"))
svm_model <- readRDS(model_path("2025_06_13_svm_model.rds"))

classifier_list <- rf_models
classifier_list[[length(classifier_list) + 1]] <- svm_model
classifier_list[[length(classifier_list) + 1]] <- knn_model
names(classifier_list)[[length(classifier_list) - 1]] <- "svm"
names(classifier_list)[[length(classifier_list)]] <- "knn"

#png(
#    filename = fig_path("resampled_classifiers_r1.png", TRUE),
#    width = 800,
#    height = 1500,
#    res = 100
#)
print(dotplot(resamples(classifier_list)))
#dev.off()

# About 86% max
rf_accuracies <- lapply(
    rf_models,
    function(x) {
        max(x$"results"$"Accuracy")
    }
) |> unlist()
#
max(rf_accuracies)
#
rf_accuracy_dfs <- lapply(
    names(rf_models),
    function(x) {
        hyperparameters <- as.numeric(unlist(regmatches(x, gregexpr("\\d+", x))))
        results <- rf_models[[x]]$results
        results$"max_nodes" <- hyperparameters[[1]]
        results$"node_size" <- hyperparameters[[2]]
        results$"n_trees" <- hyperparameters[[3]]
        results$"uid" <- x
        return(results)
    }
)
#
rf_accuracy_df <- do.call(rbind, rf_accuracy_dfs)
#
tuning_plot <- function(df, param) {
    plot <- ggplot(
        df,
        aes(x = factor(.data[[param]]), y = .data[["Accuracy"]]),
    ) +
    geom_jitter(alpha = 0.2, height = 0) +
    geom_boxplot(alpha = 0.8) +
    theme_bw()
    return(plot)
}
#
set.seed(42)
n_trees_plot <- tuning_plot(rf_accuracy_df, "n_trees")
max_nodes_plot <- tuning_plot(rf_accuracy_df, "max_nodes")
node_size_plot <- tuning_plot(rf_accuracy_df, "node_size")
mtry_plot <- tuning_plot(rf_accuracy_df, "mtry")
#
tuning_plots <- wrap_plots(
    list(n_trees_plot, max_nodes_plot, node_size_plot, mtry_plot),
    ncol = 2
)
#
# Max nodes could definitely improve
tuning_plots

ggsave(
    fig_path("tuning_plots.png", TRUE),
    tuning_plots,
    width = 10,
    height = 10,
    dpi = 300
)
```

Initial examinations show random forest as the top performing model.
Tuning plots suggest there is room for further improvement.

```{r}
rf_models_accs <- rf_models |> lapply(
    function(x) max(x$results$Accuracy)
) |> unlist()

rf_models_accs[rf_models_accs == max(rf_models_accs)]

rf_sorted <- rf_accuracy_df |> 
    dplyr::select(-Kappa, -KappaSD) |>
    dplyr::arrange(-Accuracy)

head(rf_sorted)

rf_models$"maxnodes_40nodesize_4ntree_3000"$"bestTune"

```

Best model seemed to have mtry 2, max nodes 50, node size 5, n trees 3000 with 86.2% accuracy and 0.034% accuracy SD.
But to be safe, I'll lean on one witha slightly fewer node size (4), fewer max nodes (40), and lower accuracy SD (0.018%) that is still 85.6% acc.

        OOB estimate of  error rate: 19.83%
Confusion matrix:
   1   2  3 class.error
1 83  17  4  0.20192308
2  8 118  3  0.08527132
3 15  22 78  0.32173913

### Training on full data set

```{r}
set.seed(42)

model <- randomForest(
    cluster ~ .,
    data = prep_data(train_scale_df),
    mtry = 2,
    ntree = 3000,
    maxnodes = 40,
    nodesize = 4
)

saveRDS(model, model_path("rf_training_subtype_classifier.rds", TRUE))

rf_training_subtype_classifier <- readRDS(model_path("2025_06_13_rf_training_subtype_classifier.rds"))

predictions <- predict(
    rf_training_subtype_classifier,
    newdata = prep_data(test_scale_df)
)

# Model acc on test data: 82.0%%
mean(predictions == prep_data(test_scale_df)$cluster)

confusionMatrix(predictions, prep_data(test_scale_df)$"cluster")

c(test_scale_df$"cluster", train_scale_df$"cluster") |> table()
# N = 140, 155, and 142 btw - quite balanced
```

          Reference
Prediction  1  2  3
         1 24  0  1
         2 11 26  3
         3  1  0 23

Overall Statistics

               Accuracy : 0.8202
                 95% CI : (0.7245, 0.8936)
    No Information Rate : 0.4045
    P-Value [Acc > NIR] : 1.041e-15

                  Kappa : 0.733

 Mcnemar's Test P-Value : 0.002905

```{r}
set.seed(42)
full_classification_df <- rbind(train_scale_df, test_scale_df)

full_model <- randomForest(
    cluster ~ .,
    data = prep_data(full_classification_df),
    mtry = 2,
    ntree = 3000,
    maxnodes = 40,
    nodesize = 4
)

saveRDS(full_model, model_path("subtype_classifier.rds", TRUE))
subtype_classifier <- readRDS(model_path("2025_06_13_subtype_classifier.rds"))
```

### Variable importances

```{r}
var_imp_df <- as.data.frame(importance(subtype_classifier))
var_imp_df$"feature" <- rownames(var_imp_df)
write_csv(var_imp_df, proc_path("var_imp_df.csv", TRUE))
var_imp_df <- read_csv(proc_path("2025_06_13_var_imp_df.csv"))

var_imp_df

# Create a ggplot for variable importance
var_imp_plot <- ggplot(
    var_imp_df,
    aes(
        x = reorder(feature, -MeanDecreaseGini),
        y = MeanDecreaseGini
    )
) +
    geom_bar(stat = "identity", fill = "darkgray") +
    labs(
        title = "Variable Importance Plot",
        x = "Variables",
        y = "Mean Decrease in Gini"
    ) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))

var_imp_plot

ggsave(
    plot = var_imp_plot,
    fig_path("var_imp_plot.png", TRUE),
    width = 7,
    height = 4
)
```
