# SNF in CBCL Matched Uninjured Controls

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)
library(MatchIt)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subjects <- read_csv(sub_path("2024_01_28_mtbi_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2024_01_28_uninjured_subjects.csv"))
cbcl_matched_uninjured <- read_csv(sub_path("2024_01_29_cbcl_matched_uninjured.csv"))
```

## Loading data and out of model lists

```{r}
data_list_cmu1 <- list.load(input_path("2024_01_29_data_list_cmu1.rds"))
data_list_cmu2 <- list.load(input_path("2024_01_29_data_list_cmu2.rds"))
data_list_cmu3 <- list.load(input_path("2024_01_29_data_list_cmu3.rds"))
data_list_cmu4 <- list.load(input_path("2024_01_29_data_list_cmu4.rds"))
data_list_cmu5 <- list.load(input_path("2024_01_29_data_list_cmu5.rds"))
data_list_cmpu1 <- list.load(input_path("2024_01_29_data_list_cmpu1.rds"))
data_list_cmpu2 <- list.load(input_path("2024_01_29_data_list_cmpu2.rds"))
data_list_cmpu3 <- list.load(input_path("2024_01_29_data_list_cmpu3.rds"))
data_list_cmpu4 <- list.load(input_path("2024_01_29_data_list_cmpu4.rds"))
data_list_cmpu5 <- list.load(input_path("2024_01_29_data_list_cmpu5.rds"))
oom_list_cmu1 <- list.load(input_path("2024_01_29_oom_list_cmu1.rds"))
oom_list_cmu2 <- list.load(input_path("2024_01_29_oom_list_cmu2.rds"))
oom_list_cmu3 <- list.load(input_path("2024_01_29_oom_list_cmu3.rds"))
oom_list_cmu4 <- list.load(input_path("2024_01_29_oom_list_cmu4.rds"))
oom_list_cmu5 <- list.load(input_path("2024_01_29_oom_list_cmu5.rds"))
oom_list_cmpu1 <- list.load(input_path("2024_01_29_oom_list_cmpu1.rds"))
oom_list_cmpu2 <- list.load(input_path("2024_01_29_oom_list_cmpu2.rds"))
oom_list_cmpu3 <- list.load(input_path("2024_01_29_oom_list_cmpu3.rds"))
oom_list_cmpu4 <- list.load(input_path("2024_01_29_oom_list_cmpu4.rds"))
oom_list_cmpu5 <- list.load(input_path("2024_01_29_oom_list_cmpu5.rds"))
```

## Generating custom distance measures

```{r}
my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

summarize_distance_metrics_list(my_distance_metrics)
```

## Re-importing the settings matrix

```{r}

settings_matrix <- read_csv(
    proc_path(
        "2024_01_29_settings_matrix_mu.csv"
    )
)

```

## SNF for each of the imputations

```{r}

# Uninjured only imputed
# Imputation 1
start <- proc.time()
progressr::with_progress({
    solutions_matrix_cmu1 <- batch_snf(
        data_list = data_list_cmu1,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_cmu1, proc_path("solutions_matrix_cmu1.csv", TRUE))
# Imputation 2
start <- proc.time()
progressr::with_progress({
    solutions_matrix_cmu2 <- batch_snf(
        data_list = data_list_cmu2,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_cmu2, proc_path("solutions_matrix_cmu2.csv", TRUE))
# Imputation 3
start <- proc.time()
progressr::with_progress({
    solutions_matrix_cmu3 <- batch_snf(
        data_list = data_list_cmu3,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_cmu3, proc_path("solutions_matrix_cmu3.csv", TRUE))
# Imputation 4
start <- proc.time()
progressr::with_progress({
    solutions_matrix_cmu4 <- batch_snf(
        data_list = data_list_cmu4,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_cmu4, proc_path("solutions_matrix_cmu4.csv", TRUE))
# Imputation 5
start <- proc.time()
progressr::with_progress({
    solutions_matrix_cmu5 <- batch_snf(
        data_list = data_list_cmu5,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_cmu5, proc_path("solutions_matrix_cmu5.csv", TRUE))
#
# Uninjured pooled imputed
# Imputation 1
start <- proc.time()
progressr::with_progress({
    solutions_matrix_cmpu1 <- batch_snf(
        data_list = data_list_cmpu1,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_cmpu1, proc_path("solutions_matrix_cmpu1.csv", TRUE))
# Imputation 2
start <- proc.time()
progressr::with_progress({
    solutions_matrix_cmpu2 <- batch_snf(
        data_list = data_list_cmpu2,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_cmpu2, proc_path("solutions_matrix_cmpu2.csv", TRUE))
# Imputation 3
start <- proc.time()
progressr::with_progress({
    solutions_matrix_cmpu3 <- batch_snf(
        data_list = data_list_cmpu3,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_cmpu3, proc_path("solutions_matrix_cmpu3.csv", TRUE))
# Imputation 4
start <- proc.time()
progressr::with_progress({
    solutions_matrix_cmpu4 <- batch_snf(
        data_list = data_list_cmpu4,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_cmpu4, proc_path("solutions_matrix_cmpu4.csv", TRUE))
# Imputation 5
start <- proc.time()
progressr::with_progress({
    solutions_matrix_cmpu5 <- batch_snf(
        data_list = data_list_cmpu5,
        settings_matrix = settings_matrix,
        distance_metrics_list = my_distance_metrics,
        processes = "max"
    )
})
proc.time() - start
write_csv(solutions_matrix_cmpu5, proc_path("solutions_matrix_cmpu5.csv", TRUE))

```

## Re-importing the generated solutions

```{r}
solutions_matrix_cmu1 <- read_csv(proc_path("2024_01_29_solutions_matrix_cmu1.csv"))
solutions_matrix_cmu2 <- read_csv(proc_path("2024_01_29_solutions_matrix_cmu2.csv"))
solutions_matrix_cmu3 <- read_csv(proc_path("2024_01_29_solutions_matrix_cmu3.csv"))
solutions_matrix_cmu4 <- read_csv(proc_path("2024_01_29_solutions_matrix_cmu4.csv"))
solutions_matrix_cmu5 <- read_csv(proc_path("2024_01_29_solutions_matrix_cmu5.csv"))
solutions_matrix_cmpu1 <- read_csv(proc_path("2024_01_29_solutions_matrix_cmpu1.csv"))
solutions_matrix_cmpu2 <- read_csv(proc_path("2024_01_29_solutions_matrix_cmpu2.csv"))
solutions_matrix_cmpu3 <- read_csv(proc_path("2024_01_29_solutions_matrix_cmpu3.csv"))
solutions_matrix_cmpu4 <- read_csv(proc_path("2024_01_29_solutions_matrix_cmpu4.csv"))
solutions_matrix_cmpu5 <- read_csv(proc_path("2024_01_29_solutions_matrix_cmpu5.csv"))

all_cmu_imputations <- do.call(
    "rbind",
    list(
        solutions_matrix_cmu1,
        solutions_matrix_cmu2,
        solutions_matrix_cmu3,
        solutions_matrix_cmu4,
        solutions_matrix_cmu5,
        solutions_matrix_cmpu1,
        solutions_matrix_cmpu2,
        solutions_matrix_cmpu3,
        solutions_matrix_cmpu4,
        solutions_matrix_cmpu5
    )
)
```

## Calculating pairwise ARIs

```{r}
# Completed
aris_cmu1 <- calc_om_aris(solutions_matrix_cmu1)
write_csv(data.frame(aris_cmu1), proc_path("aris_cmu1.csv", TRUE))
aris_cmu2 <- calc_om_aris(solutions_matrix_cmu2)
write_csv(data.frame(aris_cmu2), proc_path("aris_cmu2.csv", TRUE))
aris_cmu3 <- calc_om_aris(solutions_matrix_cmu3)
write_csv(data.frame(aris_cmu3), proc_path("aris_cmu3.csv", TRUE))
aris_cmu4 <- calc_om_aris(solutions_matrix_cmu4)
write_csv(data.frame(aris_cmu4), proc_path("aris_cmu4.csv", TRUE))
aris_cmu5 <- calc_om_aris(solutions_matrix_cmu5)
write_csv(data.frame(aris_cmu5), proc_path("aris_cmu5.csv", TRUE))
aris_cmpu1 <- calc_om_aris(solutions_matrix_cmpu1)
write_csv(data.frame(aris_cmpu1), proc_path("aris_cmpu1.csv", TRUE))
aris_cmpu2 <- calc_om_aris(solutions_matrix_cmpu2)
write_csv(data.frame(aris_cmpu2), proc_path("aris_cmpu2.csv", TRUE))
aris_cmpu3 <- calc_om_aris(solutions_matrix_cmpu3)
write_csv(data.frame(aris_cmpu3), proc_path("aris_cmpu3.csv", TRUE))
aris_cmpu4 <- calc_om_aris(solutions_matrix_cmpu4)
write_csv(data.frame(aris_cmpu4), proc_path("aris_cmpu4.csv", TRUE))
aris_cmpu5 <- calc_om_aris(solutions_matrix_cmpu5)
write_csv(data.frame(aris_cmpu5), proc_path("aris_cmpu5.csv", TRUE))
aris_all_cmu_imputations <- calc_om_aris(all_cmu_imputations)
write_csv(
    data.frame(aris_all_cmu_imputations),
    proc_path("aris_all_cmu_imputations.csv", TRUE)
)
```

## Re-importing the ARIs

```{r}
aris_cmu1 <- read_csv(proc_path("2024_01_29_aris_cmu1.csv")) |> as.matrix()
aris_cmu2 <- read_csv(proc_path("2024_01_29_aris_cmu2.csv")) |> as.matrix()
aris_cmu3 <- read_csv(proc_path("2024_01_29_aris_cmu3.csv")) |> as.matrix()
aris_cmu4 <- read_csv(proc_path("2024_01_29_aris_cmu4.csv")) |> as.matrix()
aris_cmu5 <- read_csv(proc_path("2024_01_29_aris_cmu5.csv")) |> as.matrix()
aris_cmpu1 <- read_csv(proc_path("2024_01_29_aris_cmpu1.csv")) |> as.matrix()
aris_cmpu2 <- read_csv(proc_path("2024_01_29_aris_cmpu2.csv")) |> as.matrix()
aris_cmpu3 <- read_csv(proc_path("2024_01_29_aris_cmpu3.csv")) |> as.matrix()
aris_cmpu4 <- read_csv(proc_path("2024_01_29_aris_cmpu4.csv")) |> as.matrix()
aris_cmpu5 <- read_csv(proc_path("2024_01_29_aris_cmpu5.csv")) |> as.matrix()

aris_all_cmu_imputations <- read_csv(
    proc_path("2024_01_29_aris_all_cmu_imputations.csv")
) |>
    as.matrix()
```

## Plotting the ARIs

### Initial plot across all ARIs to extract order

```{r}
aris_all_cmu_imputations_heatmap <- similarity_matrix_heatmap(
    aris_all_cmu_imputations,
    log_graph = FALSE,
    cluster_rows = TRUE,
    cluster_columns = TRUE
)

aris_all_cmu_imputations_heatmap <- ComplexHeatmap::draw(
    aris_all_cmu_imputations_heatmap
)
aris_all_cmu_imputations_order <- ComplexHeatmap::row_order(
    aris_all_cmu_imputations_heatmap
)

write_csv(
    data.frame(aris_all_cmu_imputations_order),
    proc_path("aris_all_cmu_imputations_order.csv", TRUE)
)
```

### Re-importing the order

```{r}
aris_all_cmu_imputations_order <- unlist(
    read_csv(proc_path("2024_01_30_aris_all_cmu_imputations_order.csv"))
)

names(aris_all_cmu_imputations_order) <- NULL
```

## Full imputation meta clustering plot with impairment levels

```{r}
imputation_labels <- data.frame(
    "imputation" = c(
        rep("u1", 200),
        rep("u2", 200),
        rep("u3", 200),
        rep("u4", 200),
        rep("u5", 200),
        rep("pu1", 200),
        rep("pu2", 200),
        rep("pu3", 200),
        rep("pu4", 200),
        rep("pu5", 200)
    ),
    "pooled" = c(
        rep("yes", 1000),
        rep("no", 1000)
    )
)

full_cmu_solutions_matrix <- cbind(all_cmu_imputations, imputation_labels)

full_cmu_solutions_matrix$"nclust2" <- full_cmu_solutions_matrix$"nclust" - 2

full_cmu_extended_solutions_matrix <- extend_solutions(
    full_cmu_solutions_matrix,
    oom_list_cmu1
)

write_csv(
    full_cmu_extended_solutions_matrix,
    proc_path("full_cmu_extended_solutions_matrix.csv", TRUE)
)

full_cmu_extended_solutions_matrix <- read_csv(
    proc_path("2024_01_30_full_cmu_extended_solutions_matrix.csv")
)

full_cmu_oom_pvals <- pval_select(
    full_cmu_extended_solutions_matrix,
    negative_log = TRUE
)

full_cmu_extended_solutions_matrix$"mean_neglog_p" <-
    full_cmu_oom_pvals$"mean_neglog_p"

aris_all_cmu_imputations_annotated_heatmap <- similarity_matrix_heatmap(
    aris_all_cmu_imputations,
    order = aris_all_cmu_imputations_order,
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    log_graph = FALSE,
    data = data.frame(full_cmu_extended_solutions_matrix),
    top_hm = list(
        "Scheme" = "snf_scheme",
        "Impairment Separation" = "mean_neglog_p"
    ),
    left_hm = list(
        "Pooled" = "pooled",
        "Imputation" = "imputation"
    ),
    top_bar = list(
        "Number of Clusters - 2" = "nclust2"
    ),
    scale_diag = "none",
    heatmap_height = grid::unit(19, "cm"),
    heatmap_width = grid::unit(19, "cm"),
    annotation_colours = list(
        "Pooled" = c(
            "yes" = "orange",
            "no" = "purple"
        ),
        "Imputation" = divergent_colours(
            full_cmu_extended_solutions_matrix$"imputation"
        ),
        "Scheme" = c(
            "1" = "#7FC97F",
            "2" = "#BEAED4",
            "3" = "#FDC086"
        ),
        "Impairment Separation" = hm_colours(
            full_cmu_extended_solutions_matrix$"mean_neglog_p"
        )
    ),
    col = circlize::colorRamp2(
        c(min(aris_all_cmu_imputations), max(aris_all_cmu_imputations)),
        c("navy", "red")
    )
)

aris_all_cmu_imputations_annotated_heatmap

# PNG export
grDevices::png(
    fig_path("aris_all_cmu_imputations_annotated_heatmap.png", TRUE),
    width = 3000,
    height = 3000,
    res = 300
)
aris_all_cmu_imputations_annotated_heatmap
grDevices::dev.off()

```

## Identifying meta clusters

```{r}

split_vector <- c(
    435,
    820,
    1025,
    1400,
    1833
)

aris_all_cmu_imputations_chopped_heatmap <- similarity_matrix_heatmap(
    aris_all_cmu_imputations,
    order = aris_all_cmu_imputations_order,
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    log_graph = FALSE,
    data = full_cmu_extended_solutions_matrix,
    top_hm = list(
        "Scheme" = "snf_scheme",
        "Impairment Separation" = "mean_neglog_p"
    ),
    left_hm = list(
        "Pooled" = "pooled",
        "Imputation" = "imputation"
    ),
    top_bar = list(
        "Number of Clusters - 2" = "nclust2"
    ),
    scale_diag = "none",
    heatmap_height = grid::unit(19, "cm"),
    heatmap_width = grid::unit(19, "cm"),
    annotation_colours = list(
        "Pooled" = c(
            "yes" = "orange",
            "no" = "purple"
        ),
        "Imputation" = divergent_colours(full_cmu_extended_solutions_matrix$"imputation"),
        "Scheme" = c(
            "1" = "#7FC97F",
            "2" = "#BEAED4",
            "3" = "#FDC086"
        ),
        "Impairment Separation" = hm_colours(full_cmu_extended_solutions_matrix$"mean_neglog_p")
    ),
    col = circlize::colorRamp2(
        c(min(aris_all_cmu_imputations), max(aris_all_cmu_imputations)),
        c("navy", "red")
    ),
    row_split = split_at(
        vector = split_vector,
        nrow = 2000
    ),
    column_split = split_at(
        vector = split_vector,
        nrow = 2000
    )
)
aris_all_cmu_imputations_chopped_heatmap

# PNG export
grDevices::png(
    fig_path("aris_all_cmu_imputations_chopped_heatmap.png", TRUE),
    width = 3000,
    height = 3000,
    res = 300
)
aris_all_cmu_imputations_chopped_heatmap
grDevices::dev.off()
```

## One-MC-at-a-time

```{r}

# Indices as they appear in the plots
mc_reordered_indices <- list(
    "A" = c(1, 435),
    "B" = c(436, 820),
    "C" = c(821, 1025),
    "D" = c(1026, 1400),
    "E" = c(1401, 1833),
    "E" = c(1834, 2000)
)

mc_reordered_labels <- split_at(
    c(
        435,
        820,
        1025,
        1400,
        1833,
        1686
    ),
    2000
)

names(aris_all_cmu_imputations_order) <- mc_reordered_labels

cmu_sorted_mc_labels <- sort(aris_all_cmu_imputations_order)

full_input_characterization_cmu1 <- extend_solutions(
    full_cmu_solutions_matrix,
    data_list_cmu1
)

write_csv(
    full_input_characterization_cmu1,
    proc_path("full_input_characterization_cmu1.csv", TRUE)
)

full_input_characterization_cmu1 <- read_csv(
    proc_path(
        "2024_01_30_full_input_characterization_cmu1.csv"
    )
)

cmu_target_pvals <- full_input_characterization_cmu1 |>
    p_val_select()
cmu_target_pvals$"mc_label" <- names(cmu_sorted_mc_labels)

# We are missing the acute symptoms here, but still want to match the colours
# of the other plots
gg_color_hue <- function(n) {
  hues = seq(15, 375, length = n + 1)
  hcl(h = hues, l = 65, c = 100)[1:n]
}
gg_color_hue(5)

manhattan_plot <- function(data,
                           key_mode = FALSE,
                           threshold = NULL,
                           bonferroni_line = FALSE,
                           data_list,
                           mc_labels = NULL) {
    row_id <- ""
    variable <- ""
    pval <- ""
    var_cols <- colnames(data)[endsWith(colnames(data), "_p")]
    data[, var_cols] <- data[, var_cols] |>
        apply(
            MARGIN = 2,
            FUN = function(x) {
                -log10(x)
                raw_p <- -log10(x)
                new_x <- dplyr::case_when(
                    raw_p > 5 ~ 5,
                    raw_p > 4 ~ 4,
                    raw_p > 3 ~ 3,
                    raw_p > 2 ~ 2,
                    raw_p > 1 ~ 1,
                    raw_p > 0 ~ 0,
                )
                new_x
            }
        )
    data$"row_id" <- factor(data$"row_id")
    data$"mc_label" <- factor(data$"mc_label")
    data <- data |>
        tidyr::pivot_longer(
            !(c(row_id, mc_label)),
            names_to = "variable",
            values_to = "pval"
        ) |>
        data.frame()
    summary_data <- data |>
        dplyr::group_by(
            mc_label,
            variable
        ) |>
        dplyr::summarize(
            mean_p = mean(pval),
            sd_p = sd(pval),
            se_p = sd_p / sqrt(dplyr::n()),
            .groups = "drop"
        )
    summary_data$"variable" <- sub("_p$", "", summary_data$"variable")
    ###########################################################################
    # Merge the summmary plot with domain information from the data_list
    ###########################################################################
    dl_metadata <- data_list_metadata(data_list) |> dplyr::select(-"type")
    summary_data <- merge(
        summary_data,
        dl_metadata,
        by.x = "variable",
        by.y = "name",
        all.x = TRUE
    )
    summary_data <- summary_data |> dplyr::arrange(domain)
    summary_data$"variable" <- factor(
        summary_data$"variable",
        levels = unique(summary_data$"variable")
    )
    if (!is.null(mc_labels)) {
        summary_data <- summary_data[summary_data$"mc_label" %in% mc_labels, ]
        summary_data$"mc_label" <- factor(
            summary_data$"mc_label",
            levels = mc_labels
        )
    }
    plot <- summary_data |>
        ggplot2::ggplot(ggplot2::aes(x = domain, y = mean_p)) +
        ggplot2::geom_jitter(
            mapping = ggplot2::aes(
                group = domain,
                x = variable,
                y = mean_p,
                colour = domain
            ),
            height = 0,
            width = 0,
            size = 5
        ) +
        ggplot2::labs(
            x = "Variable",
            y = expression("-log"[10]*"(p)"),
            colour = "Domain"
        ) +
        ggplot2::ylim(-log10(0.05), 5) +
        ggplot2::theme_bw() +
        ggplot2::labs(y = "Discretized -log10(p)") +
        ggplot2::scale_color_manual(
            values = c("#A3A500", "#00BF7D", "#00B0F6", "#E76BF3")
        ) +
        ggplot2::theme(
            axis.text.x = ggplot2::element_text(
                angle = 90,
                vjust = 0.5,
                hjust = 1
            ),
            plot.title = ggplot2::element_text(hjust = 0.5)
        )
    plot <- plot + ggplot2::facet_grid(mc_label ~ .)
    if (!is.null(threshold)) {
        plot <- plot + ggplot2::geom_hline(
            yintercept = -log10(threshold),
            linetype = "dashed",
            colour = "red"
        )
        if (bonferroni_line) {
            plot <- plot + ggplot2::geom_hline(
                yintercept = -log10(threshold / nrow(data)),
                linetype = "dashed",
                colour = "black"
            )
        }
    } else if (bonferroni_line) {
        stop(
            "Please specify threshold p-value which will be used",
            " for calculting the Bonferroni-corrected line."
        )
    }
    return(plot)
}

library(ggplot2)
# Here I am

all_cmu_imputations_mc_associations <- manhattan_plot(
    target_pvals,
    threshold = 0.05,
    bonferroni_line = FALSE,
    data_list = data_list_cmu1,
    mc_labels = c("A", "B", "C", "E")
)

all_cmu_imputations_mc_associations

ggsave(
    plot = all_cmu_imputations_mc_associations,
    fig_path("all_cmu_imputations_mc_associations.png", TRUE),
    width = 8,
    height = 7
)

# Bulk export each MC individually
for (mc in names(mc_reordered_indices)) {
    mc_plot <- manhattan_plot(
        target_pvals,
        threshold = 0.05,
        bonferroni_line = FALSE,
        data_list = data_list_cmu1,
        mc_label = mc
    )
    mc_path <- paste0(
        "all_cmu_imputations_mc_",
        gsub("-", "_", tolower(mc)),
        "_associations.png"
    )
    ggsave(
        plot = mc_plot,
        fig_path(mc_path, TRUE),
        width = 10,
        height = 3
    )
}
```

## Characterization

```{r}
full_cmu_extended_solutions_matrix <- read_csv(
    proc_path("2024_01_30_full_cmu_extended_solutions_matrix.csv")
)

full_cmu_oom_pvals <- pval_select(
    full_cmu_extended_solutions_matrix,
    negative_log = TRUE
)

full_cmu_extended_solutions_matrix$"mean_neglog_p" <- full_cmu_oom_pvals$"mean_neglog_p"

cmu_sm_order <- unlist(
    read_csv(proc_path("2024_01_30_aris_all_cmu_imputations_order.csv"))
)

names(cmu_sm_order) <- NULL

cmu_sorted_solutions_matrix <- full_cmu_extended_solutions_matrix[cmu_sm_order, ]

cmu_mc_a_solutions <- cmu_sorted_solutions_matrix[1:435, ]
cmu_mc_b_solutions <- cmu_sorted_solutions_matrix[436:820, ]
cmu_mc_c_solutions <- cmu_sorted_solutions_matrix[821:1025, ]
cmu_mc_d_solutions <- cmu_sorted_solutions_matrix[1026:1400, ]
cmu_mc_e_solutions <- cmu_sorted_solutions_matrix[1401:1833, ]
cmu_mc_f_solutions <- cmu_sorted_solutions_matrix[1834:2000, ]

which(cmu_sorted_solutions_matrix$"row_id" == 85 & cmu_sorted_solutions_matrix$"imputation" == "u3")

```

### Setting up total data lists

```{r}
all_data_list_cmu1 <- c(data_list_cmu1, oom_list_cmu1)
all_data_list_cmu2 <- c(data_list_cmu2, oom_list_cmu2)
all_data_list_cmu3 <- c(data_list_cmu3, oom_list_cmu3)
all_data_list_cmu4 <- c(data_list_cmu4, oom_list_cmu4)
all_data_list_cmu5 <- c(data_list_cmu5, oom_list_cmu5)

all_data_list_cmpu1 <- c(data_list_cmpu1, oom_list_cmpu1)
all_data_list_cmpu2 <- c(data_list_cmpu2, oom_list_cmpu2)
all_data_list_cmpu3 <- c(data_list_cmpu3, oom_list_cmpu3)
all_data_list_cmpu4 <- c(data_list_cmpu4, oom_list_cmpu4)
all_data_list_cmpu5 <- c(data_list_cmpu5, oom_list_cmpu5)
```

### Matched control MC C

```{r}

row <- nrow(cmu_mc_c_solutions) %/% 2
cmu_mc_c_solution <- cmu_mc_c_solutions[row, ]
cmu_mc_c_solution$"imputation"

cmu_mc_c_plots <- characterize_solution(
    cmu_mc_c_solution,
    all_data_list_cmu5,
    "cmu_mc_c"
)
save_plot_list_uninj(cmu_mc_c_plots, "cmu_mc_c")

```

## Optimal 3-cluster solution

This solution is also from MC C

```{r}

cmu_3c_solutions <- full_cmu_extended_solutions_matrix |>
    dplyr::filter(nclust == 3)
top_ind <- cmu_3c_solutions$"mean_neglog_p" == max(cmu_3c_solutions$"mean_neglog_p")
top_cmu_3c_solution <- cmu_3c_solutions[top_ind, ]
row <- nrow(top_cmu_3c_solution) %/% 2
top_cmu_3c_solution <- top_cmu_3c_solution[row, ]
top_cmu_3c_solution$"imputation"
top_cmu_3c_solution$"row_id" #85

write_csv(top_cmu_3c_solution, proc_path("top_cmu_3c_solution", TRUE))

get_clusters(top_cmu_3c_solution)

# Restructuring so that the cluster label is the same 

for (i in 1:ncol(top_cmu_3c_solution)) {
    cname <- colnames(top_cmu_3c_solution)[i]
    if (grepl("subject_", cname)) {
        if (top_cmu_3c_solution[1, cname] == 1) {
            top_cmu_3c_solution[1, cname] <- 2
        } else if (top_cmu_3c_solution[1, cname] == 2) {
            top_cmu_3c_solution[1, cname] <- 3
        } else if (top_cmu_3c_solution[1, cname] == 3) {
            top_cmu_3c_solution[1, cname] <- 1
        }
    }
}

get_clusters(top_cmu_3c_solution)

cmu_3c_plots <- characterize_solution(
    top_cmu_3c_solution,
    all_data_list_cmu3,
    "cmu_top_3c"
)
save_plot_list_uninj(cmu_3c_plots, "cmu_top_3c")


cmu_3c_characterization <- extend_solutions(
    top_cmu_3c_solution,
    data_list_cmu3
)
cmu_3c_pvals <- p_val_select(cmu_3c_characterization)
cmu_3c_pvals$"row_id" <- top_cmu_3c_solution$"row_id"
cmu_3c_pvals$"mc_label" <- "CMU-C"

cmu_3c_pvals <- cmu_3c_pvals |>
    dplyr::select(
        -dplyr::starts_with("cbcl"),
        -dplyr::starts_with("sds"),
        -dplyr::starts_with("mean")
    )

cmu_3c_associations <- manhattan_plot(
    cmu_3c_pvals,
    threshold = 0.05,
    bonferroni_line = FALSE,
    data_list = data_list_cmu3,
    colours = c("#A3A500", "#00BF7D", "#00B0F6", "#E76BF3")
)

cmu_3c_associations

ggsave(
    plot = cmu_3c_associations,
    fig_path("top_cmu_3c_associations.png", TRUE),
    width = 10,
    height = 3
)

```

Looks much closer to the mTBI group.
I can follow this up with some permutation testing to examine differences between the two groups.
