# Matching

This chapter contains:

1. Derivation of subtypes from a variety of matched uninjured groups
2. Comparison of those subtypes with the mTBI baseline solution

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)
library(MatchIt)
library(tibble)
library(ggplot2)
library(fastDummies)
library(dplyr)
library(tidyr)
library(xtable)
library(patchwork)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
model_path <- path_maker(here(paste0("data/abcd/results/models")))

mtbi_subs <- read_subjects(sub_path("2025_02_07_mtbi_subs.csv"))
unij_subs <- read_subjects(sub_path("2025_02_07_unij_subs.csv"))
```

## Importing data

```{r}
all_dls <- readRDS(input_path("2025_02_10_all_dls.rds"))

mtbi_full_data_list_1 <- readRDS(input_path("2025_02_12_mtbi_full_data_list_1.rds"))
mtbi_full_oom_list_1 <- readRDS(input_path("2025_02_12_mtbi_full_oom_list_1.rds"))
mtbi_full_top_3c <- readRDS(proc_path("2025_02_13_mtbi_full_top_3c.rds"))

unij_dl_s1 <- all_dls$"unij_data_lists"$"imp_1"
unij_dl_p1 <- all_dls$"unij_pooled_data_lists"$"imp_1"
unij_ol_s1 <- all_dls$"unij_oom_lists"$"imp_1"
unij_ol_p1 <- all_dls$"unij_pooled_oom_lists"$"imp_1"
```

## Matching

Finding matched uninjured controls for each mtbi subject based on a variety of variables.
Matching will be done based on the first imputed dataset of the baseline data.

```{r}
mtbi_matching_df <- c(mtbi_full_data_list_1, mtbi_full_oom_list_1) |> as.data.frame()
unij_matching_df_s1 <- c(unij_dl_s1, unij_ol_s1) |> as.data.frame()
unij_matching_df_s1 <- c(unij_dl_s1, unij_ol_s1) |> as.data.frame()
unij_matching_df_p1 <- c(unij_dl_p1, unij_ol_p1) |> as.data.frame()

mtbi_matching_df$"mtbi" <- 1
unij_matching_df_s1$"mtbi" <- 0
unij_matching_df_p1$"mtbi" <- 0

mtbi_matching_df <- dplyr::select(
    mtbi_matching_df,
    colnames(unij_matching_df_s1)
)

matching_df_s1 <- rbind(mtbi_matching_df, unij_matching_df_s1)
matching_df_p1 <- rbind(mtbi_matching_df, unij_matching_df_p1)
```


```{r}
# Total parent psych
matching_df_s1$"total_parent_psych" <- matching_df_s1 |> dplyr::select(dplyr::starts_with("parent")) |> rowSums()
matching_df_p1$"total_parent_psych" <- matching_df_p1 |> dplyr::select(dplyr::starts_with("parent")) |> rowSums()

# Total CBCL
matching_df_s1$"total_impairments" <- matching_df_s1 |> dplyr::select(dplyr::starts_with("cbcl"), dplyr::starts_with("sds")) |> rowSums()
matching_df_p1$"total_impairments" <- matching_df_p1 |> dplyr::select(dplyr::starts_with("cbcl"), dplyr::starts_with("sds")) |> rowSums()
```

We'll try a few different matching schemes:

```{r}
# Establishing formulae
d_vars <- "household_income + race + sex + pubertal_status_p + pubertal_status_y"
p_vars <- "total_parent_psych"
o_vars <- "total_impairments"
dp_vars <- paste0(d_vars, " + ", p_vars)
do_vars <- paste0(d_vars, " + ", o_vars)
op_vars <- paste0(o_vars, " + ", p_vars)
dpo_vars <- paste0(d_vars, " + ", p_vars, " + ", o_vars)

match_d_results_s <- matchit(as.formula(paste0("mtbi ~ ", d_vars)), matching_df_s1, method = "nearest")
match_p_results_s <- matchit(as.formula(paste0("mtbi ~ ", p_vars)), matching_df_s1, method = "nearest")
match_o_results_s <- matchit(as.formula(paste0("mtbi ~ ", o_vars)), matching_df_s1, method = "nearest")
match_d_results_p <- matchit(as.formula(paste0("mtbi ~ ", d_vars)), matching_df_p1, method = "nearest")
match_p_results_p <- matchit(as.formula(paste0("mtbi ~ ", p_vars)), matching_df_p1, method = "nearest")
match_o_results_p <- matchit(as.formula(paste0("mtbi ~ ", o_vars)), matching_df_p1, method = "nearest")
match_dp_results_s <- matchit(as.formula(paste0("mtbi ~ ", dp_vars)), matching_df_s1, method = "nearest")
match_do_results_s <- matchit(as.formula(paste0("mtbi ~ ", op_vars)), matching_df_s1, method = "nearest")
match_op_results_s <- matchit(as.formula(paste0("mtbi ~ ", op_vars)), matching_df_s1, method = "nearest")
match_dp_results_p <- matchit(as.formula(paste0("mtbi ~ ", dp_vars)), matching_df_p1, method = "nearest")
match_do_results_p <- matchit(as.formula(paste0("mtbi ~ ", op_vars)), matching_df_p1, method = "nearest")
match_op_results_p <- matchit(as.formula(paste0("mtbi ~ ", op_vars)), matching_df_p1, method = "nearest")
match_dpo_results_s <- matchit(as.formula(paste0("mtbi ~ ", dp_vars)), matching_df_s1, method = "nearest")
match_dpo_results_p <- matchit(as.formula(paste0("mtbi ~ ", dp_vars)), matching_df_p1, method = "nearest")

# Saving plots
save_matching_plot <- function(matching_results, name) {
    grDevices::png(filename = name, width = 1000, height = 500, res = 100)
    plot(matching_results, type = "density", interactive = FALSE)
    grDevices::dev.off()
}

save_matching_plot(match_d_results_s, fig_path("match_d_results_s.png", TRUE))
save_matching_plot(match_p_results_s, fig_path("match_p_results_s.png", TRUE))
save_matching_plot(match_o_results_s, fig_path("match_o_results_s.png", TRUE))
save_matching_plot(match_d_results_p, fig_path("match_d_results_p.png", TRUE))
save_matching_plot(match_p_results_p, fig_path("match_p_results_p.png", TRUE))
save_matching_plot(match_o_results_p, fig_path("match_o_results_p.png", TRUE))
save_matching_plot(match_dp_results_s, fig_path("match_dp_results_s.png", TRUE))
save_matching_plot(match_do_results_s, fig_path("match_do_results_s.png", TRUE))
save_matching_plot(match_op_results_s, fig_path("match_op_results_s.png", TRUE))
save_matching_plot(match_dp_results_p, fig_path("match_dp_results_p.png", TRUE))
save_matching_plot(match_do_results_p, fig_path("match_do_results_p.png", TRUE))
save_matching_plot(match_op_results_p, fig_path("match_op_results_p.png", TRUE))
save_matching_plot(match_dpo_results_s, fig_path("match_dpo_results_s.png", TRUE))
save_matching_plot(match_dpo_results_p, fig_path("match_dpo_results_p.png", TRUE))
```


```{r}
# Saving matched results
match_d_s <- match.data(match_d_results_s)
match_p_s <- match.data(match_p_results_s)
match_o_s <- match.data(match_o_results_s)
match_d_p <- match.data(match_d_results_p)
match_p_p <- match.data(match_p_results_p)
match_o_p <- match.data(match_o_results_p)
match_dp_s <- match.data(match_dp_results_s)
match_do_s <- match.data(match_do_results_s)
match_op_s <- match.data(match_op_results_s)
match_dp_p <- match.data(match_dp_results_p)
match_do_p <- match.data(match_do_results_p)
match_op_p <- match.data(match_op_results_p)
match_dpo_s <- match.data(match_dpo_results_s)
match_dpo_p <- match.data(match_dpo_results_p)

saveRDS(match_d_s, proc_path("match_d_s.rds", TRUE))
saveRDS(match_p_s, proc_path("match_p_s.rds", TRUE))
saveRDS(match_o_s, proc_path("match_o_s.rds", TRUE))
saveRDS(match_d_p, proc_path("match_d_p.rds", TRUE))
saveRDS(match_p_p, proc_path("match_p_p.rds", TRUE))
saveRDS(match_o_p, proc_path("match_o_p.rds", TRUE))
saveRDS(match_dp_s, proc_path("match_dp_s.rds", TRUE))
saveRDS(match_do_s, proc_path("match_do_s.rds", TRUE))
saveRDS(match_op_s, proc_path("match_op_s.rds", TRUE))
saveRDS(match_dp_p, proc_path("match_dp_p.rds", TRUE))
saveRDS(match_do_p, proc_path("match_do_p.rds", TRUE))
saveRDS(match_op_p, proc_path("match_op_p.rds", TRUE))
saveRDS(match_dpo_s, proc_path("match_dpo_s.rds", TRUE))
saveRDS(match_dpo_p, proc_path("match_dpo_p.rds", TRUE))
```

```{r}
match_d_s <- readRDS(proc_path("2025_02_14_match_d_s.rds"))
match_p_s <- readRDS(proc_path("2025_02_14_match_p_s.rds"))
match_o_s <- readRDS(proc_path("2025_02_14_match_o_s.rds"))
match_d_p <- readRDS(proc_path("2025_02_14_match_d_p.rds"))
match_p_p <- readRDS(proc_path("2025_02_14_match_p_p.rds"))
match_o_p <- readRDS(proc_path("2025_02_14_match_o_p.rds"))
match_dp_s <- readRDS(proc_path("2025_02_14_match_dp_s.rds"))
match_do_s <- readRDS(proc_path("2025_02_14_match_do_s.rds"))
match_op_s <- readRDS(proc_path("2025_02_14_match_op_s.rds"))
match_dp_p <- readRDS(proc_path("2025_02_14_match_dp_p.rds"))
match_do_p <- readRDS(proc_path("2025_02_14_match_do_p.rds"))
match_op_p <- readRDS(proc_path("2025_02_14_match_op_p.rds"))
match_dpo_s <- readRDS(proc_path("2025_02_14_match_dpo_s.rds"))
match_dpo_p <- readRDS(proc_path("2025_02_14_match_dpo_p.rds"))
```

```{r}
matched_unij_d_s <- dplyr::filter(match_d_s, mtbi == 0)$"uid"
matched_unij_p_s <- dplyr::filter(match_p_s, mtbi == 0)$"uid"
matched_unij_o_s <- dplyr::filter(match_o_s, mtbi == 0)$"uid"
matched_unij_d_p <- dplyr::filter(match_d_p, mtbi == 0)$"uid"
matched_unij_p_p <- dplyr::filter(match_p_p, mtbi == 0)$"uid"
matched_unij_o_p <- dplyr::filter(match_o_p, mtbi == 0)$"uid"
matched_unij_dp_s <- dplyr::filter(match_dp_s, mtbi == 0)$"uid"
matched_unij_do_s <- dplyr::filter(match_do_s, mtbi == 0)$"uid"
matched_unij_op_s <- dplyr::filter(match_op_s, mtbi == 0)$"uid"
matched_unij_dp_p <- dplyr::filter(match_dp_p, mtbi == 0)$"uid"
matched_unij_do_p <- dplyr::filter(match_do_p, mtbi == 0)$"uid"
matched_unij_op_p <- dplyr::filter(match_op_p, mtbi == 0)$"uid"
matched_unij_dpo_s <- dplyr::filter(match_dpo_s, mtbi == 0)$"uid"
matched_unij_dpo_p <- dplyr::filter(match_dpo_p, mtbi == 0)$"uid"

write_csv(data.frame(subjectkey = matched_unij_d_s), sub_path("matched_unij_d_s.csv", TRUE))
write_csv(data.frame(subjectkey = matched_unij_p_s), sub_path("matched_unij_p_s.csv", TRUE))
write_csv(data.frame(subjectkey = matched_unij_o_s), sub_path("matched_unij_o_s.csv", TRUE))
write_csv(data.frame(subjectkey = matched_unij_d_p), sub_path("matched_unij_d_p.csv", TRUE))
write_csv(data.frame(subjectkey = matched_unij_p_p), sub_path("matched_unij_p_p.csv", TRUE))
write_csv(data.frame(subjectkey = matched_unij_o_p), sub_path("matched_unij_o_p.csv", TRUE))
write_csv(data.frame(subjectkey = matched_unij_dp_s), sub_path("matched_unij_dp_s.csv", TRUE))
write_csv(data.frame(subjectkey = matched_unij_do_s), sub_path("matched_unij_do_s.csv", TRUE))
write_csv(data.frame(subjectkey = matched_unij_op_s), sub_path("matched_unij_op_s.csv", TRUE))
write_csv(data.frame(subjectkey = matched_unij_dp_p), sub_path("matched_unij_dp_p.csv", TRUE))
write_csv(data.frame(subjectkey = matched_unij_do_p), sub_path("matched_unij_do_p.csv", TRUE))
write_csv(data.frame(subjectkey = matched_unij_op_p), sub_path("matched_unij_op_p.csv", TRUE))
write_csv(data.frame(subjectkey = matched_unij_dpo_s), sub_path("matched_unij_dpo_s.csv", TRUE))
write_csv(data.frame(subjectkey = matched_unij_dpo_p), sub_path("matched_unij_dpo_p.csv", TRUE))
```

```{r}
matched_unij_d_s <- read_subjects(sub_path("2025_02_14_matched_unij_d_s.csv"))
matched_unij_p_s <- read_subjects(sub_path("2025_02_14_matched_unij_p_s.csv"))
matched_unij_o_s <- read_subjects(sub_path("2025_02_14_matched_unij_o_s.csv"))
matched_unij_d_p <- read_subjects(sub_path("2025_02_14_matched_unij_d_p.csv"))
matched_unij_p_p <- read_subjects(sub_path("2025_02_14_matched_unij_p_p.csv"))
matched_unij_o_p <- read_subjects(sub_path("2025_02_14_matched_unij_o_p.csv"))
matched_unij_dp_s <- read_subjects(sub_path("2025_02_14_matched_unij_dp_s.csv"))
matched_unij_do_s <- read_subjects(sub_path("2025_02_14_matched_unij_do_s.csv"))
matched_unij_op_s <- read_subjects(sub_path("2025_02_14_matched_unij_op_s.csv"))
matched_unij_dp_p <- read_subjects(sub_path("2025_02_14_matched_unij_dp_p.csv"))
matched_unij_do_p <- read_subjects(sub_path("2025_02_14_matched_unij_do_p.csv"))
matched_unij_op_p <- read_subjects(sub_path("2025_02_14_matched_unij_op_p.csv"))
matched_unij_dpo_s <- read_subjects(sub_path("2025_02_14_matched_unij_dpo_s.csv"))
matched_unij_dpo_p <- read_subjects(sub_path("2025_02_14_matched_unij_dpo_p.csv"))
```

## Subsetting matched unijured data and out of model lists

```{r}
subject_filter_dl <- function(data_list, subject_vector) {
    data_list <- data_list |>
        dlapply(
            function(x) {
                keep_subs <- x$"data"$"uid" %in% subject_vector
                x$"data" <- x$"data"[keep_subs, ]
                return(x)
            }
        )
    return(data_list)
}

set.seed(42)
random_unij_subs <- sample(unij_subs, size = 437)

matched_unij_dl_d_s <- subject_filter_dl(unij_dl_s1, matched_unij_d_s)
matched_unij_dl_d_p <- subject_filter_dl(unij_dl_p1, matched_unij_d_p)

matched_unij_dl_p_s <- subject_filter_dl(unij_dl_s1, matched_unij_p_s)
matched_unij_dl_p_p <- subject_filter_dl(unij_dl_p1, matched_unij_p_p)

matched_unij_dl_o_s <- subject_filter_dl(unij_dl_s1, matched_unij_o_s)
matched_unij_dl_o_p <- subject_filter_dl(unij_dl_p1, matched_unij_o_p)

matched_unij_dl_do_s <- subject_filter_dl(unij_dl_s1, matched_unij_do_s)
matched_unij_dl_do_p <- subject_filter_dl(unij_dl_p1, matched_unij_do_p)

matched_unij_dl_dp_s <- subject_filter_dl(unij_dl_s1, matched_unij_dp_s)
matched_unij_dl_dp_p <- subject_filter_dl(unij_dl_p1, matched_unij_dp_p)

matched_unij_dl_op_s <- subject_filter_dl(unij_dl_s1, matched_unij_op_s)
matched_unij_dl_op_p <- subject_filter_dl(unij_dl_p1, matched_unij_op_p)

matched_unij_dl_dpo_p <- subject_filter_dl(unij_dl_p1, matched_unij_dpo_p)
matched_unij_dl_dpo_s <- subject_filter_dl(unij_dl_s1, matched_unij_dpo_s)

random_unij_dl_s1 <- subject_filter_dl(unij_dl_s1, paste0("uid_", random_unij_subs))
random_unij_dl_p1 <- subject_filter_dl(unij_dl_p1, paste0("uid_", random_unij_subs))

matched_unij_ol_d_s <- subject_filter_dl(unij_ol_s1, matched_unij_d_s)
matched_unij_ol_d_p <- subject_filter_dl(unij_ol_p1, matched_unij_d_p)

matched_unij_ol_p_s <- subject_filter_dl(unij_ol_s1, matched_unij_p_s)
matched_unij_ol_p_p <- subject_filter_dl(unij_ol_p1, matched_unij_p_p)

matched_unij_ol_o_s <- subject_filter_dl(unij_ol_s1, matched_unij_o_s)
matched_unij_ol_o_p <- subject_filter_dl(unij_ol_p1, matched_unij_o_p)

matched_unij_ol_do_s <- subject_filter_dl(unij_ol_s1, matched_unij_do_s)
matched_unij_ol_do_p <- subject_filter_dl(unij_ol_p1, matched_unij_do_p)

matched_unij_ol_dp_s <- subject_filter_dl(unij_ol_s1, matched_unij_dp_s)
matched_unij_ol_dp_p <- subject_filter_dl(unij_ol_p1, matched_unij_dp_p)

matched_unij_ol_op_s <- subject_filter_dl(unij_ol_s1, matched_unij_op_s)
matched_unij_ol_op_p <- subject_filter_dl(unij_ol_p1, matched_unij_op_p)

matched_unij_ol_dpo_p <- subject_filter_dl(unij_ol_p1, matched_unij_dpo_p)
matched_unij_ol_dpo_s <- subject_filter_dl(unij_ol_s1, matched_unij_dpo_s)

random_unij_ol_s1 <- subject_filter_dl(unij_ol_s1, paste0("uid_", random_unij_subs))
random_unij_ol_p1 <- subject_filter_dl(unij_ol_p1, paste0("uid_", random_unij_subs))


saveRDS(matched_unij_dl_d_s, proc_path("matched_unij_dl_d_s.rds", TRUE))
saveRDS(matched_unij_dl_p_s, proc_path("matched_unij_dl_p_s.rds", TRUE))
saveRDS(matched_unij_dl_o_s, proc_path("matched_unij_dl_o_s.rds", TRUE))
saveRDS(matched_unij_dl_d_p, proc_path("matched_unij_dl_d_p.rds", TRUE))
saveRDS(matched_unij_dl_p_p, proc_path("matched_unij_dl_p_p.rds", TRUE))
saveRDS(matched_unij_dl_o_p, proc_path("matched_unij_dl_o_p.rds", TRUE))
saveRDS(matched_unij_dl_dp_s, proc_path("matched_unij_dl_dp_s.rds", TRUE))
saveRDS(matched_unij_dl_do_s, proc_path("matched_unij_dl_do_s.rds", TRUE))
saveRDS(matched_unij_dl_op_s, proc_path("matched_unij_dl_op_s.rds", TRUE))
saveRDS(matched_unij_dl_dp_p, proc_path("matched_unij_dl_dp_p.rds", TRUE))
saveRDS(matched_unij_dl_do_p, proc_path("matched_unij_dl_do_p.rds", TRUE))
saveRDS(matched_unij_dl_op_p, proc_path("matched_unij_dl_op_p.rds", TRUE))
saveRDS(matched_unij_dl_dpo_p, proc_path("matched_unij_dl_dpo_p.rds", TRUE))
saveRDS(matched_unij_dl_dpo_s, proc_path("matched_unij_dl_dpo_s.rds", TRUE))
saveRDS(random_unij_dl_s1, proc_path("random_unij_dl_s1.rds", TRUE))
saveRDS(random_unij_dl_p1, proc_path("random_unij_dl_p1.rds", TRUE))

saveRDS(matched_unij_ol_d_s, proc_path("matched_unij_ol_d_s.rds", TRUE))
saveRDS(matched_unij_ol_p_s, proc_path("matched_unij_ol_p_s.rds", TRUE))
saveRDS(matched_unij_ol_o_s, proc_path("matched_unij_ol_o_s.rds", TRUE))
saveRDS(matched_unij_ol_d_p, proc_path("matched_unij_ol_d_p.rds", TRUE))
saveRDS(matched_unij_ol_p_p, proc_path("matched_unij_ol_p_p.rds", TRUE))
saveRDS(matched_unij_ol_o_p, proc_path("matched_unij_ol_o_p.rds", TRUE))
saveRDS(matched_unij_ol_dp_s, proc_path("matched_unij_ol_dp_s.rds", TRUE))
saveRDS(matched_unij_ol_do_s, proc_path("matched_unij_ol_do_s.rds", TRUE))
saveRDS(matched_unij_ol_op_s, proc_path("matched_unij_ol_op_s.rds", TRUE))
saveRDS(matched_unij_ol_dp_p, proc_path("matched_unij_ol_dp_p.rds", TRUE))
saveRDS(matched_unij_ol_do_p, proc_path("matched_unij_ol_do_p.rds", TRUE))
saveRDS(matched_unij_ol_op_p, proc_path("matched_unij_ol_op_p.rds", TRUE))
saveRDS(matched_unij_ol_dpo_p, proc_path("matched_unij_ol_dpo_p.rds", TRUE))
saveRDS(matched_unij_ol_dpo_s, proc_path("matched_unij_ol_dpo_s.rds", TRUE))
saveRDS(random_unij_ol_s1, proc_path("random_unij_ol_s1.rds", TRUE))
saveRDS(random_unij_ol_p1, proc_path("random_unij_ol_p1.rds", TRUE))
```

```{r}
# CHECKPOINT
matched_unij_dl_d_s <- readRDS(proc_path("2025_02_14_matched_unij_dl_d_s.rds"))
matched_unij_dl_p_s <- readRDS(proc_path("2025_02_14_matched_unij_dl_p_s.rds"))
matched_unij_dl_o_s <- readRDS(proc_path("2025_02_14_matched_unij_dl_o_s.rds"))
matched_unij_dl_d_p <- readRDS(proc_path("2025_02_14_matched_unij_dl_d_p.rds"))
matched_unij_dl_p_p <- readRDS(proc_path("2025_02_14_matched_unij_dl_p_p.rds"))
matched_unij_dl_o_p <- readRDS(proc_path("2025_02_14_matched_unij_dl_o_p.rds"))
matched_unij_dl_dp_s <- readRDS(proc_path("2025_02_14_matched_unij_dl_dp_s.rds"))
matched_unij_dl_do_s <- readRDS(proc_path("2025_02_14_matched_unij_dl_do_s.rds"))
matched_unij_dl_op_s <- readRDS(proc_path("2025_02_14_matched_unij_dl_op_s.rds"))
matched_unij_dl_dp_p <- readRDS(proc_path("2025_02_14_matched_unij_dl_dp_p.rds"))
matched_unij_dl_do_p <- readRDS(proc_path("2025_02_14_matched_unij_dl_do_p.rds"))
matched_unij_dl_op_p <- readRDS(proc_path("2025_02_14_matched_unij_dl_op_p.rds"))
matched_unij_dl_dpo_p <- readRDS(proc_path("2025_02_14_matched_unij_dl_dpo_p.rds"))
matched_unij_dl_dpo_s <- readRDS(proc_path("2025_02_14_matched_unij_dl_dpo_s.rds"))
random_unij_dl_s1 <- readRDS(proc_path("2025_02_14_random_unij_dl_s1.rds"))
random_unij_dl_p1 <- readRDS(proc_path("2025_02_14_random_unij_dl_p1.rds"))

matched_unij_ol_d_s <- readRDS(proc_path("2025_02_14_matched_unij_ol_d_s.rds"))
matched_unij_ol_p_s <- readRDS(proc_path("2025_02_14_matched_unij_ol_p_s.rds"))
matched_unij_ol_o_s <- readRDS(proc_path("2025_02_14_matched_unij_ol_o_s.rds"))
matched_unij_ol_d_p <- readRDS(proc_path("2025_02_14_matched_unij_ol_d_p.rds"))
matched_unij_ol_p_p <- readRDS(proc_path("2025_02_14_matched_unij_ol_p_p.rds"))
matched_unij_ol_o_p <- readRDS(proc_path("2025_02_14_matched_unij_ol_o_p.rds"))
matched_unij_ol_dp_s <- readRDS(proc_path("2025_02_14_matched_unij_ol_dp_s.rds"))
matched_unij_ol_do_s <- readRDS(proc_path("2025_02_14_matched_unij_ol_do_s.rds"))
matched_unij_ol_op_s <- readRDS(proc_path("2025_02_14_matched_unij_ol_op_s.rds"))
matched_unij_ol_dp_p <- readRDS(proc_path("2025_02_14_matched_unij_ol_dp_p.rds"))
matched_unij_ol_do_p <- readRDS(proc_path("2025_02_14_matched_unij_ol_do_p.rds"))
matched_unij_ol_op_p <- readRDS(proc_path("2025_02_14_matched_unij_ol_op_p.rds"))
matched_unij_ol_dpo_p <- readRDS(proc_path("2025_02_14_matched_unij_ol_dpo_p.rds"))
matched_unij_ol_dpo_s <- readRDS(proc_path("2025_02_14_matched_unij_ol_dpo_s.rds"))
random_unij_ol_s1 <- readRDS(proc_path("2025_02_14_random_unij_ol_s1.rds"))
random_unij_ol_p1 <- readRDS(proc_path("2025_02_14_random_unij_ol_p1.rds"))
```

## metaSNF

```{r}
set.seed(42)
matched_config <- snf_config(
    matched_unij_dl_d_s,
    n_solutions = 200,
    cnt_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    dsc_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ord_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    use_default_dist_fns = TRUE
)

saveRDS(matched_config, proc_path("matched_config.rds", TRUE))
```

```{r}
# CHECKPOINT
matched_config <- readRDS(proc_path("2025_02_15_matched_config.rds"))
```

```{r}
# SNF
matched_unij_sm_d_s <- batch_snf(matched_unij_dl_d_s, matched_config, processes = "max")
saveRDS(matched_unij_sm_d_s, proc_path("matched_unij_sm_d_s.rds", TRUE))
cat("snf 1 done\n")
matched_unij_sm_p_s <- batch_snf(matched_unij_dl_p_s, matched_config, processes = "max")
saveRDS(matched_unij_sm_p_s, proc_path("matched_unij_sm_p_s.rds", TRUE))
cat("snf 2 done\n")
matched_unij_sm_o_s <- batch_snf(matched_unij_dl_o_s, matched_config, processes = "max")
saveRDS(matched_unij_sm_o_s, proc_path("matched_unij_sm_o_s.rds", TRUE))
cat("snf 3 done\n")
matched_unij_sm_d_p <- batch_snf(matched_unij_dl_d_p, matched_config, processes = "max")
saveRDS(matched_unij_sm_d_p, proc_path("matched_unij_sm_d_p.rds", TRUE))
cat("snf 4 done\n")
matched_unij_sm_p_p <- batch_snf(matched_unij_dl_p_p, matched_config, processes = "max")
saveRDS(matched_unij_sm_p_p, proc_path("matched_unij_sm_p_p.rds", TRUE))
cat("snf 5 done\n")
matched_unij_sm_o_p <- batch_snf(matched_unij_dl_o_p, matched_config, processes = "max")
saveRDS(matched_unij_sm_o_p, proc_path("matched_unij_sm_o_p.rds", TRUE))
cat("snf 6 done\n")
matched_unij_sm_dp_s <- batch_snf(matched_unij_dl_dp_s, matched_config, processes = "max")
saveRDS(matched_unij_sm_dp_s, proc_path("matched_unij_sm_dp_s.rds", TRUE))
cat("snf 7 done\n")
matched_unij_sm_do_s <- batch_snf(matched_unij_dl_do_s, matched_config, processes = "max")
saveRDS(matched_unij_sm_do_s, proc_path("matched_unij_sm_do_s.rds", TRUE))
cat("snf 8 done\n")
matched_unij_sm_op_s <- batch_snf(matched_unij_dl_op_s, matched_config, processes = "max")
saveRDS(matched_unij_sm_op_s, proc_path("matched_unij_sm_op_s.rds", TRUE))
cat("snf 9 done\n")
matched_unij_sm_dp_p <- batch_snf(matched_unij_dl_dp_p, matched_config, processes = "max")
saveRDS(matched_unij_sm_dp_p, proc_path("matched_unij_sm_dp_p.rds", TRUE))
cat("snf 10 done\n")
matched_unij_sm_do_p <- batch_snf(matched_unij_dl_do_p, matched_config, processes = "max")
saveRDS(matched_unij_sm_do_p, proc_path("matched_unij_sm_do_p.rds", TRUE))
cat("snf 11 done\n")
matched_unij_sm_op_p <- batch_snf(matched_unij_dl_op_p, matched_config, processes = "max")
saveRDS(matched_unij_sm_op_p, proc_path("matched_unij_sm_op_p.rds", TRUE))
cat("snf 12 done\n")
matched_unij_sm_dpo_p <- batch_snf(matched_unij_dl_dpo_p, matched_config, processes = "max")
saveRDS(matched_unij_sm_dpo_p, proc_path("matched_unij_sm_dpo_p.rds", TRUE))
cat("snf 13 done\n")
matched_unij_sm_dpo_s <- batch_snf(matched_unij_dl_dpo_s, matched_config, processes = "max")
saveRDS(matched_unij_sm_dpo_s, proc_path("matched_unij_sm_dpo_s.rds", TRUE))
cat("snf 14 done\n")
random_unij_sm_s1 <- batch_snf(random_unij_dl_s1, matched_config, processes = "max")
saveRDS(random_unij_sm_s1, proc_path("random_unij_sm_s1.rds", TRUE))
cat("snf 15 done\n")
random_unij_sm_p1 <- batch_snf(random_unij_dl_p1, matched_config, processes = "max")
saveRDS(random_unij_sm_p1, proc_path("random_unij_sm_p1.rds", TRUE))
```

```{r}
matched_unij_sm_dpo_s <- readRDS(proc_path("2025_02_15_matched_unij_sm_dpo_s.rds"))
matched_unij_sm_dpo_p <- readRDS(proc_path("2025_02_15_matched_unij_sm_dpo_p.rds"))
matched_unij_sm_op_p <- readRDS(proc_path("2025_02_15_matched_unij_sm_op_p.rds"))
matched_unij_sm_do_p <- readRDS(proc_path("2025_02_15_matched_unij_sm_do_p.rds"))
matched_unij_sm_dp_p <- readRDS(proc_path("2025_02_15_matched_unij_sm_dp_p.rds"))
matched_unij_sm_op_s <- readRDS(proc_path("2025_02_15_matched_unij_sm_op_s.rds"))
matched_unij_sm_do_s <- readRDS(proc_path("2025_02_15_matched_unij_sm_do_s.rds"))
matched_unij_sm_dp_s <- readRDS(proc_path("2025_02_15_matched_unij_sm_dp_s.rds"))
matched_unij_sm_o_p <- readRDS(proc_path("2025_02_15_matched_unij_sm_o_p.rds"))
matched_unij_sm_p_p <- readRDS(proc_path("2025_02_15_matched_unij_sm_p_p.rds"))
matched_unij_sm_d_p <- readRDS(proc_path("2025_02_15_matched_unij_sm_d_p.rds"))
matched_unij_sm_o_s <- readRDS(proc_path("2025_02_15_matched_unij_sm_o_s.rds"))
matched_unij_sm_p_s <- readRDS(proc_path("2025_02_15_matched_unij_sm_p_s.rds"))
matched_unij_sm_d_s <- readRDS(proc_path("2025_02_15_matched_unij_sm_d_s.rds"))
random_unij_sm_s1 <- readRDS(proc_path("2025_02_15_random_unij_sm_s1.rds"))
random_unij_sm_p1 <- readRDS(proc_path("2025_02_15_random_unij_sm_p1.rds"))
```



```{r}
matched_unij_esm_dpo_s <- extend_solutions(matched_unij_sm_dpo_s, dl = matched_unij_dl_dpo_s, target_dl = matched_unij_ol_dpo_s, min_pval = 1e-10, processes = "max")
saveRDS(matched_unij_esm_dpo_s, proc_path("matched_unij_esm_dpo_s.rds", TRUE))
matched_unij_esm_dpo_p <- extend_solutions(matched_unij_sm_dpo_p, dl = matched_unij_dl_dpo_p, target_dl = matched_unij_ol_dpo_p, min_pval = 1e-10, processes = "max")
saveRDS(matched_unij_esm_dpo_p, proc_path("matched_unij_esm_dpo_p.rds", TRUE))
matched_unij_esm_op_p <- extend_solutions(matched_unij_sm_op_p, dl = matched_unij_dl_op_p, target_dl = matched_unij_ol_op_p, min_pval = 1e-10, processes = "max")
saveRDS(matched_unij_esm_op_p, proc_path("matched_unij_esm_op_p.rds", TRUE))
matched_unij_esm_do_p <- extend_solutions(matched_unij_sm_do_p, dl = matched_unij_dl_do_p, target_dl = matched_unij_ol_do_p, min_pval = 1e-10, processes = "max")
saveRDS(matched_unij_esm_do_p, proc_path("matched_unij_esm_do_p.rds", TRUE))
matched_unij_esm_dp_p <- extend_solutions(matched_unij_sm_dp_p, dl = matched_unij_dl_dp_p, target_dl = matched_unij_ol_dp_p, min_pval = 1e-10, processes = "max")
saveRDS(matched_unij_esm_dp_p, proc_path("matched_unij_esm_dp_p.rds", TRUE))
matched_unij_esm_op_s <- extend_solutions(matched_unij_sm_op_s, dl = matched_unij_dl_op_s, target_dl = matched_unij_ol_op_s, min_pval = 1e-10, processes = "max")
saveRDS(matched_unij_esm_op_s, proc_path("matched_unij_esm_op_s.rds", TRUE))
matched_unij_esm_do_s <- extend_solutions(matched_unij_sm_do_s, dl = matched_unij_dl_do_s, target_dl = matched_unij_ol_do_s, min_pval = 1e-10, processes = "max")
saveRDS(matched_unij_esm_do_s, proc_path("matched_unij_esm_do_s.rds", TRUE))
#
matched_unij_esm_dp_s <- extend_solutions(matched_unij_sm_dp_s, dl = matched_unij_dl_dp_s, target_dl = matched_unij_ol_dp_s, min_pval = 1e-10, processes = "max")
saveRDS(matched_unij_esm_dp_s, proc_path("matched_unij_esm_dp_s.rds", TRUE))
matched_unij_esm_o_p <- extend_solutions(matched_unij_sm_o_p, dl = matched_unij_dl_o_p, target_dl = matched_unij_ol_o_p, min_pval = 1e-10, processes = "max")
saveRDS(matched_unij_esm_o_p, proc_path("matched_unij_esm_o_p.rds", TRUE))
matched_unij_esm_p_p <- extend_solutions(matched_unij_sm_p_p, dl = matched_unij_dl_p_p, target_dl = matched_unij_ol_p_p, min_pval = 1e-10, processes = "max")
saveRDS(matched_unij_esm_p_p, proc_path("matched_unij_esm_p_p.rds", TRUE))
matched_unij_esm_d_p <- extend_solutions(matched_unij_sm_d_p, dl = matched_unij_dl_d_p, target_dl = matched_unij_ol_d_p, min_pval = 1e-10, processes = "max")
saveRDS(matched_unij_esm_d_p, proc_path("matched_unij_esm_d_p.rds", TRUE))
matched_unij_esm_o_s <- extend_solutions(matched_unij_sm_o_s, dl = matched_unij_dl_o_s, target_dl = matched_unij_ol_o_s, min_pval = 1e-10, processes = "max")
saveRDS(matched_unij_esm_o_s, proc_path("matched_unij_esm_o_s.rds", TRUE))
matched_unij_esm_p_s <- extend_solutions(matched_unij_sm_p_s, dl = matched_unij_dl_p_s, target_dl = matched_unij_ol_p_s, min_pval = 1e-10, processes = "max")
saveRDS(matched_unij_esm_p_s, proc_path("matched_unij_esm_p_s.rds", TRUE))
matched_unij_esm_d_s <- extend_solutions(matched_unij_sm_d_s, dl = matched_unij_dl_d_s, target_dl = matched_unij_ol_d_s, min_pval = 1e-10, processes = "max")
saveRDS(matched_unij_esm_d_s, proc_path("matched_unij_esm_d_s.rds", TRUE))
random_unij_esm_s1 <- extend_solutions(random_unij_sm_s1, dl = random_unij_dl_s1, target_dl = random_unij_ol_s1, min_pval = 1e-10, processes = "max")
saveRDS(random_unij_esm_s1, proc_path("random_unij_esm_s1.rds", TRUE))
random_unij_esm_p1 <- extend_solutions(random_unij_sm_p1, dl = random_unij_dl_p1, target_dl = random_unij_ol_p1, min_pval = 1e-10, processes = "max")
saveRDS(random_unij_esm_p1, proc_path("random_unij_esm_p1.rds", TRUE))
```

```{r}
matched_unij_esm_d_s <- readRDS(proc_path("2025_02_15_matched_unij_esm_d_s.rds"))
matched_unij_esm_p_s <- readRDS(proc_path("2025_02_15_matched_unij_esm_p_s.rds"))
matched_unij_esm_o_s <- readRDS(proc_path("2025_02_15_matched_unij_esm_o_s.rds"))
matched_unij_esm_d_p <- readRDS(proc_path("2025_02_15_matched_unij_esm_d_p.rds"))
matched_unij_esm_p_p <- readRDS(proc_path("2025_02_15_matched_unij_esm_p_p.rds"))
matched_unij_esm_o_p <- readRDS(proc_path("2025_02_15_matched_unij_esm_o_p.rds"))
matched_unij_esm_dp_s <- readRDS(proc_path("2025_02_15_matched_unij_esm_dp_s.rds"))
matched_unij_esm_do_s <- readRDS(proc_path("2025_02_15_matched_unij_esm_do_s.rds"))
matched_unij_esm_op_s <- readRDS(proc_path("2025_02_15_matched_unij_esm_op_s.rds"))
matched_unij_esm_dp_p <- readRDS(proc_path("2025_02_15_matched_unij_esm_dp_p.rds"))
matched_unij_esm_do_p <- readRDS(proc_path("2025_02_15_matched_unij_esm_do_p.rds"))
matched_unij_esm_op_p <- readRDS(proc_path("2025_02_15_matched_unij_esm_op_p.rds"))
matched_unij_esm_dpo_p <- readRDS(proc_path("2025_02_15_matched_unij_esm_dpo_p.rds"))
matched_unij_esm_dpo_s <- readRDS(proc_path("2025_02_15_matched_unij_esm_dpo_s.rds"))
random_unij_esm_s1 <- readRDS(proc_path("2025_02_15_random_unij_esm_s1.rds"))
random_unij_esm_p1 <- readRDS(proc_path("2025_02_15_random_unij_esm_p1.rds"))
```

```{r}
matched_unij_esm_list <- list(
    "d_s" = matched_unij_esm_d_s,
    "p_s" = matched_unij_esm_p_s,
    "o_s" = matched_unij_esm_o_s,
    "d_p" = matched_unij_esm_d_p,
    "p_p" = matched_unij_esm_p_p,
    "o_p" = matched_unij_esm_o_p,
    "dp_s" = matched_unij_esm_dp_s,
    "do_s" = matched_unij_esm_do_s,
    "op_s" = matched_unij_esm_op_s,
    "dp_p" = matched_unij_esm_dp_p,
    "do_p" = matched_unij_esm_do_p,
    "op_p" = matched_unij_esm_op_p,
    "dpo_p" = matched_unij_esm_dpo_p,
    "dpo_s" = matched_unij_esm_dpo_s,
    "random_s" = random_unij_esm_s1,
    "random_p" = random_unij_esm_p1
)

saveRDS(matched_unij_esm_list, proc_path("matched_unij_esm_list.rds", TRUE))
```

```{r}
matched_unij_esm_list <- readRDS(proc_path("2025_02_15_matched_unij_esm_list.rds"))
```

```{r}
# Tight requirement: -log10(pval) > 4
matched_unij_esm_3c_list <- lapply(
    matched_unij_esm_list,
    function(x) {
        x <- dplyr::filter(x, nclust == 3, -log10(mean_pval) > 4)
        return(x)
    }
)

# Loose requirement: -log10(pval) > 1
matched_unij_esm_3c_list_loose <- lapply(
    matched_unij_esm_list,
    function(x) {
        x <- dplyr::filter(x, nclust == 3, -log10(mean_pval) > 1)
        return(x)
    }
)

matched_unij_esm_3c_list <- matched_unij_esm_3c_list[sapply(matched_unij_esm_3c_list, function(x) nrow(x) > 0)]
matched_unij_esm_3c_list_loose <- matched_unij_esm_3c_list_loose[sapply(matched_unij_esm_3c_list_loose, function(x) nrow(x) > 0)]

saveRDS(matched_unij_esm_3c_list, proc_path("matched_unij_esm_3c_list.rds", TRUE))
saveRDS(matched_unij_esm_3c_list_loose, proc_path("matched_unij_esm_3c_list_loose.rds", TRUE))

matched_unij_esm_3c_list <- readRDS(proc_path("2025_02_15_matched_unij_esm_3c_list.rds"))
matched_unij_esm_3c_list_loose <- readRDS(proc_path("2025_02_15_matched_unij_esm_3c_list_loose.rds"))
```

```{r}
dcols <- c(
    "AS" = "#85929e",
    "D" = "#bb8fce",
    "N" = "#e59866",
    "MH" = "#7fb3d5",
    "P" = "#52be80",
    "S" = "#d98880",
    "B" = "#ff3131"
)

names(matched_unij_esm_3c_list)

matched_unij_do_s <- mc_manhattan_plot(
    matched_unij_esm_3c_list$"do_s",
    dl = matched_unij_dl_do_s,
    target_dl = matched_unij_ol_do_s,
    domain_colours = dcols
)

matched_unij_do_p <- mc_manhattan_plot(
    matched_unij_esm_3c_list$"do_p",
    dl = matched_unij_dl_do_p,
    target_dl = matched_unij_ol_do_p,
    domain_colours = dcols
)

matched_unij_op_s <- mc_manhattan_plot(
    matched_unij_esm_3c_list$"op_s",
    dl = matched_unij_dl_op_s,
    target_dl = matched_unij_ol_op_s,
    domain_colours = dcols
)

matched_unij_op_p <- mc_manhattan_plot(
    matched_unij_esm_3c_list$"op_p",
    dl = matched_unij_dl_op_p,
    target_dl = matched_unij_ol_op_p,
    domain_colours = dcols
)

matched_unij_manhattan_plots <- list(
    "do_s" = matched_unij_do_s,
    "do_p" = matched_unij_do_p,
    "op_s" = matched_unij_op_s,
    "op_p" = matched_unij_op_p
)

saveRDS(matched_unij_manhattan_plots, fig_path("matched_unij_manhattan_plots.rds", TRUE))
```

```{r}
# CHECKPOINT
matched_unij_manhattan_plots <- readRDS(fig_path("2025_02_15_matched_unij_manhattan_plots.rds"))
```

So we know that only a couple of combinations lead to somewhat similar cluster solutions in terms of the mean p-values on outcomes.

```{r}
qs2 <- function(plot, path, w = 18, h = 14, d = 120) {    
    path <- paste0("matched_unij_", path, "_manhattan.png")
    ggsave(
        fig_path(path, TRUE),
        plot,
        width = w,
        height = h,
        dpi = d
    )
}

# Small function to calculate how tall each manhattan plot
# should be.
heighter <- function(panes) {
    panes * 4/3 + 10/3
}

qs2(matched_unij_manhattan_plots$"do_s", "do_s", h = 4.67)
qs2(matched_unij_manhattan_plots$"do_p", "do_p", h = 6)
qs2(matched_unij_manhattan_plots$"op_s", "op_s", h = 4.67)
qs2(matched_unij_manhattan_plots$"op_p", "op_p", h = 6)
```

```{r}
matched_unij_dls <- list(
    "d_s" = matched_unij_dl_d_s,
    "p_s" = matched_unij_dl_p_s,
    "o_s" = matched_unij_dl_o_s,
    "d_p" = matched_unij_dl_d_p,
    "p_p" = matched_unij_dl_p_p,
    "o_p" = matched_unij_dl_o_p,
    "dp_s" = matched_unij_dl_dp_s,
    "do_s" = matched_unij_dl_do_s,
    "op_s" = matched_unij_dl_op_s,
    "dp_p" = matched_unij_dl_dp_p,
    "do_p" = matched_unij_dl_do_p,
    "op_p" = matched_unij_dl_op_p,
    "dpo_p" = matched_unij_dl_dpo_p,
    "dpo_s" = matched_unij_dl_dpo_s,
    "random_s" = random_unij_dl_s1,
    "random_p" = random_unij_dl_p1
)

matched_unij_ols <- list(
    "d_s" = matched_unij_ol_d_s,
    "p_s" = matched_unij_ol_p_s,
    "o_s" = matched_unij_ol_o_s,
    "d_p" = matched_unij_ol_d_p,
    "p_p" = matched_unij_ol_p_p,
    "o_p" = matched_unij_ol_o_p,
    "dp_s" = matched_unij_ol_dp_s,
    "do_s" = matched_unij_ol_do_s,
    "op_s" = matched_unij_ol_op_s,
    "dp_p" = matched_unij_ol_dp_p,
    "do_p" = matched_unij_ol_do_p,
    "op_p" = matched_unij_ol_op_p,
    "dpo_p" = matched_unij_ol_dpo_p,
    "dpo_s" = matched_unij_ol_dpo_s,
    "random_s" = random_unij_ol_s1,
    "random_p" = random_unij_ol_p1
)

saveRDS(matched_unij_dls, proc_path("matched_unij_dls.rds", TRUE))
saveRDS(matched_unij_ols, proc_path("matched_unij_ols.rds", TRUE))
```

```{r}
# CHECKPOINT
matched_unij_dls <- readRDS(proc_path("2025_02_15_matched_unij_dls.rds"))
matched_unij_ols <- readRDS(proc_path("2025_02_15_matched_unij_ols.rds"))
```

```{r}
#matched_unij_esm_3c_list <- matched_unij_esm_3c_list[
#    c(
#        "a_s1",
#        "a_p1",
#        "b_s1",
#        "b_p1",
#        "c_s1",
#        "c_p1",
#        "d_p1"
#    )
#]
#
#matched_pls <- lapply(
#    names(matched_unij_esm_3c_list),
#    function(match) {
#        pl <- list()
#        nrows <- nrow(matched_unij_esm_3c_list[[match]])
#        for (row in seq_len(nrows)) {
#            p <- auto_plot(
#                matched_unij_esm_3c_list[[match]][row, ],
#                data_list = matched_unij_dls[[match]],
#                target_list = matched_unij_ols[[match]]
#            )
#            pl[[length(pl) + 1]] <- p
#        }
#        names(pl) <- paste0("row_", seq_len(nrows))
#        return(pl)
#    }
#)
#names(matched_pls) <- names(matched_unij_esm_3c_list)
#
#list.save(matched_pls, fig_path("matched_pls.rds", TRUE))
```

```{r}
# CHECKPOINT
#matched_pls <- list.load(fig_path("2024_11_28_matched_pls.rds"))
mtbi_gen_fts_in_long <- read_csv(proc_path("2025_02_13_mtbi_gen_fts_in_long.csv"))
mtbi_gen_fts_out_long <- read_csv(proc_path("2025_02_13_mtbi_gen_fts_out_long.csv"))

classifier_fts <- read_csv(proc_path("2025_02_14_classifier_fts.csv"))$"classifier_fts"
```

Calculating concordance (similarity between matched uninjured solution and baseline mTBI solution topologies) using loose threshold.

```{r}
matched_pl_dfs <- lapply(
    names(matched_unij_esm_3c_list_loose),
    function(match) {
        pl <- list()
        nrows <- nrow(matched_unij_esm_3c_list_loose[[match]])
        for (row in seq_len(nrows)) {
            p <- auto_plot(
                matched_unij_esm_3c_list_loose[[match]][row, ],
                dl = c(matched_unij_dls[[match]], matched_unij_ols[[match]]),
                return_plots = FALSE
            )
            pl[[length(pl) + 1]] <- p
        }
        #names(pl) <- paste0("row_", seq_len(nrows))
        return(pl)
    }
)

matched_unij_esm_3c_list_loose$"op_p" |> nrow()

matched_pl_dfs

names(matched_pl_dfs) <- names(matched_unij_esm_3c_list_loose)
matched_pl_dfs <- unlist(matched_pl_dfs, recursive = FALSE)

saveRDS(matched_pl_dfs, proc_path("matched_pl_dfs.rds", TRUE))
matched_pls_dfs <- readRDS(proc_path("2025_02_15_matched_pl_dfs.rds"))

matched_pl_tops <- lapply(
    matched_pl_dfs,
    function(x) {
        topologizer(x)
    }
)

saveRDS(matched_pl_tops, proc_path("matched_pl_tops.rds", TRUE))
matched_pl_tops <- readRDS(proc_path("2025_02_15_matched_pl_tops.rds"))

matched_pl_gen_fts <- lapply(
    matched_pl_tops,
    function(x) {
        generalizable_features(x, compare_fn_a)
    }
)

mtbi_gen_long <- rbind(
    mtbi_gen_fts_in_long,
    mtbi_gen_fts_out_long
)
mtbi_gen_long <- na.omit(mtbi_gen_long)

matched_pl_gen_fts_long <- lapply(
    matched_pl_gen_fts,
    function(x) {
        long_x <- pivot_longer(
            x,
            cols = -feature,
            names_to = "comparison",
            values_to = "order_unij"
        )
        long_gen_x <- dplyr::left_join(
            mtbi_gen_long,
            long_x,
            by = c("feature", "comparison")
        ) 
        long_gen_x <- dplyr::mutate(
            long_gen_x,
            match = dplyr::case_when(
                is.na(order_unij) ~ 0,
                order != order_unij ~ 0, 
                order == order_unij ~ 1
            )
        )
        return(long_gen_x)
    }
)

matched_pl_gen_fts_long_fair <- lapply(
    matched_pl_gen_fts_long,
    function(x) {
        dplyr::filter(x, !grepl("mtbi", feature))
    }
)

concordance_list <- lapply(
    matched_pl_gen_fts_long_fair,
    function(x) {
        100 * sum(x$"match") / nrow(x)
    }
)

concordance_df <- data.frame(
    unij_set = names(concordance_list),
    concordance = unlist(concordance_list)
) |>
    arrange(desc(concordance))
rownames(concordance_df) <- NULL

concordance_df

write_csv(concordance_df, proc_path("matched_unij_concordance.csv", TRUE))

concordance_df <- read_csv(proc_path("2025_02_15_matched_unij_concordance.csv"))

xtable(concordance_df)

knitr::kable(concordance_df, format = "markdown", digits = 3, format.args = list(scientific = FALSE)) |>
    writeLines(proc_path("matched_unij_concordance.txt", TRUE))

concordance_df

```

Matching by D+O and O+P seem to be best.
The D+O and O+P matching yielded identical sets of matched uninjured subjects.

```{r}

matched_unij_esm_3c_list_loose$"do_p"[11, ],
matched_unij_esm_3c_list_loose$"op_p"[11, ]

matched_pls

matched_unij_dls |> names()

top_unij_pl <- auto_plot(
    matched_unij_esm_3c_list_loose$"do_p"[11, ],
    dl = c(
        matched_unij_dls$"do_p",
        matched_unij_ols$"do_p"
    )
)

gen_in_fts <- unique(mtbi_gen_fts_in_long$"feature")
gen_in_fts[startsWith(gen_in_fts, "race_")] <- "race"
gen_in_fts[startsWith(gen_in_fts, "mtbi_mechanism_")] <- "mtbi_mechanism"
gen_in_fts <- unique(gen_in_fts)
gen_out_fts <- unique(mtbi_gen_fts_out_long$"feature")

gen_in_fts

top_unij_input_plots <- top_unij_pl[gen_in_fts]
top_unij_outcome_plots <- top_unij_pl[gen_out_fts]
top_unij_plots <- top_unij_pl[c(gen_in_fts, gen_out_fts)]

saveRDS(top_unij_input_plots, proc_path("top_unij_input_plots.rds", TRUE))
saveRDS(top_unij_outcome_plots, proc_path("top_unij_outcome_plots.rds", TRUE))

top_unij_input_plots <- readRDS(proc_path("2025_02_15_top_unij_input_plots.rds"))
top_unij_outcome_plots <- readRDS(proc_path("2025_02_15_top_unij_outcome_plots.rds"))
top_unij_plots <- readRDS(proc_path("2025_02_15_top_unij_plots.rds"))

top_unij_plots <- top_unij_plots[!is.na(names(top_unij_plots))]

top_unij_wrapped_plots <- wrap_plots(top_unij_plots)

top_unij_wrapped_plots

ggsave(
    fig_path("top_unij_wrapped_plots.png", TRUE),
    top_unij_wrapped_plots,
    width = 45,
    height = 30,
    dpi = 50
)

#------------------------------------------------------------------------------

## qs2 image export helper function
#qs2 <- function(plot, path, w = 4, h = 4) {
#    path <- paste0("unij_a_s4_", path, ".png")
#    ggsave(fig_path(path, TRUE), plot, width = w, height = h)
#}
#
## uni-plot helper function# {{{
#uni_plot <- function(plot,
#                     ft_name,
#                     scale_fill_labels = NULL,
#                     ylims = NULL) {
#    ###########################################################################
#    plot <- plot +
#        theme(axis.title.y = element_text(size = 16))
#    ###########################################################################
#    if (class(plot$layers[[1]]$geom)[[1]] == "GeomBar") {
#        plot <- plot + labs(fill = ft_name)
#    } else {
#        plot <- plot + labs(y = ft_name)
#    }
#    if (!is.null(scale_fill_labels)) {
#        plot <- plot + scale_fill_discrete(labels = scale_fill_labels)
#    }
#    if (!is.null(ylims)) {
#        plot <- plot + ylim(ylims[[1]], ylims[[2]])
#    }
#    ###########################################################################
#    plot <- plot + labs(x = "Cluster") + theme(text = element_text(size = 16))
#    return(plot)
#}
## }}}
#
## Matched unij Input Plots
## Brain volumes
#brain_volume_plot <- uni_plot(top_unij_input_plots$"brain_volume", expression("Brain Volume "(mm^3)))
#brain_volume_plot
#qs2(brain_volume_plot, "brain_volume")
#
## Sex
#sex_plot <- uni_plot(top_unij_input_plots$"sex", "Sex", c("F", "M"))
#sex_plot
#qs2(sex_plot, "sex")
#
## cort sa
#cort_sa_plot <- uni_plot(top_unij_input_plots$"cortical_sa", expression("Cortical Surface Area "(mm^2)))
#cort_sa_plot
#qs2(cort_sa_plot, "cort_sa")
#
## Income
#household_income_plot <- uni_plot(top_unij_input_plots$"household_income", "Household Income")
#household_income_plot
#qs2(household_income_plot, "household_income")
#
## Pubertal Status - Parent Report
#pubertal_status_p_plot <- uni_plot(top_unij_input_plots$"pubertal_status_p", "Pubertal Status\n(Parent Report)")
#pubertal_status_p_plot
#qs2(pubertal_status_p_plot, "pubertal_status_p")
#
## Programs this year
#programs_this_year_plot <- uni_plot(top_unij_input_plots$"programs_this_year", "Programs This Year")
#programs_this_year_plot
#qs2(programs_this_year_plot, "programs_this_year")
#
## Non school programs
#non_school_programs_plot <- uni_plot(top_unij_input_plots$"non_school_programs", "Non-School Programs This Year", ylims= c(-0.5, 12))
#non_school_programs_plot
#qs2(non_school_programs_plot, "non_school_programs")
#
## parent_thought
#parent_thought_plot <- uni_plot(top_unij_input_plots$"parent_thought", "Parent Thought", ylims = c(-0.5, 13.5))
#parent_thought_plot
#qs2(parent_thought_plot, "parent_thought")
#
## Parent Somatic
#parent_somatic_plot <- uni_plot(top_unij_input_plots$"parent_somatic", "Parent Somatic", ylims = c(-0.5, 28))
#parent_somatic_plot
#qs2(parent_somatic_plot, "parent_somatic")
#
## Weekday screentime
#weekday_screentime_plot <- uni_plot(top_unij_input_plots$"weekday_screentime", "Weekday Screentime (hours)", ylims = c(-0.5, 21))
#weekday_screentime_plot
#qs2(weekday_screentime_plot, "weekday_screentime")
#
## parent_antisocial
#parent_antisocial_plot <- uni_plot(top_unij_input_plots$"parent_antisocial", "Parent Antisocial")
#parent_antisocial_plot
#qs2(parent_antisocial_plot, "parent_antisocial")
#
## parent_aggressive
#parent_aggressive_plot <- uni_plot(top_unij_input_plots$"parent_aggressive", "Parent Aggressive")
#parent_aggressive_plot
#qs2(parent_aggressive_plot, "parent_aggressive")
#
## Parent depress
#parent_depress_plot <- uni_plot(top_unij_input_plots$"parent_depress", "Parent Depress", ylims = c(-0.5, 28))
#parent_depress_plot
#qs2(parent_depress_plot, "parent_depress")
#
## parent_anxdep
#parent_anxdep_plot <- uni_plot(top_unij_input_plots$"parent_anxdep", "Parent Anxious-Depressed")
#parent_anxdep_plot
#qs2(parent_anxdep_plot, "parent_anxdep")
#
## Race
#race_plot <- uni_plot(top_unij_input_plots$"race", "Race", scale_fill_labels = c("Black", "Hispanic", "Other", "White"))
#race_plot
#qs2(race_plot, "race")
#
## parent_anxdisord
#parent_anxdisord_plot <- uni_plot(top_unij_input_plots$"parent_anxdisord", "Parent Anxious", ylims = c(-0.5, 13))
#parent_anxdisord_plot
#qs2(parent_anxdisord_plot, "parent_anxdisord")
#
## private_instruction
#private_instruction_plot <- uni_plot(top_unij_input_plots$"private_instruction", "Private Activities", ylims = c(-0.5, 9.5))
#private_instruction_plot
#qs2(private_instruction_plot, "private_instruction")
#
## weekend_screentime
#weekend_screentime_plot <- uni_plot(top_unij_input_plots$"weekend_screentime", "Weekend Screentime (hours)", ylims = c(-0.5, 21))
#weekend_screentime_plot
#qs2(weekend_screentime_plot, "weekend_screentime")
#
## parent_withdrawn
#parent_withdrawn_plot <- uni_plot(top_unij_input_plots$"parent_withdrawn", "Parent Withdrawn", ylims = c(-0.5, 17))
#parent_withdrawn_plot
#qs2(parent_withdrawn_plot, "parent_withdrawn")
#
## parent_avoidant
#parent_avoidant_plot <- uni_plot(top_unij_input_plots$"parent_avoidant", "Parent Avoidant", ylims = c(-0.5, 13))
#parent_avoidant_plot
#qs2(parent_avoidant_plot, "parent_avoidant")
#
## parent_hyperactive
#parent_hyperactive_plot <- uni_plot(top_unij_input_plots$"parent_hyperactive", "Parent Hyperactive", ylims = c(-0.5, 12))
#parent_hyperactive_plot
#qs2(parent_hyperactive_plot, "parent_hyperactive")
#
## fmri_cort_subcort_cors
#fmri_cort_subcort_cors_plot <- uni_plot(top_unij_input_plots$"fmri_cort_subcort_cors", "fMRI Cort-Subcort Corrs", ylims = c(-0.15, 0.2))
#fmri_cort_subcort_cors_plot
#qs2(fmri_cort_subcort_cors_plot, "fmri_cort_subcort_cors")
#
## Parent attention
#parent_attention_plot <- uni_plot(top_unij_input_plots$"parent_attention", "Parent Attention")
#parent_attention_plot
#qs2(parent_attention_plot, "parent_attention")
#
## parent_perstr
#parent_perstr_plot <- uni_plot(top_unij_input_plots$"parent_perstr", "Parent Personal Strength")
#parent_perstr_plot
#qs2(parent_perstr_plot, "parent_perstr")
#
## parent_intrusive
#parent_intrusive_plot <- uni_plot(top_unij_input_plots$"parent_intrusive", "Parent Intrusive", ylims = c(-0.5, 12))
#parent_intrusive_plot
#qs2(parent_intrusive_plot, "parent_intrusive")
#
## family_fight_p
#family_fight_p_plot <- uni_plot(top_unij_input_plots$"family_fight_p", "Family Fights\n(Parent Report)", scale_fill_labels = c("No", "Yes"))
#family_fight_p_plot
#qs2(family_fight_p_plot, "family_fight_p")
#
## headache_history
#headache_history_plot <- uni_plot(top_unij_input_plots$"headache_history", "Headache\nHistory", c("No", "Yes"))
#headache_history_plot
#qs2(headache_history_plot, "headache_history")
#
## exercise_time
#exercise_time_plot <- uni_plot(top_unij_input_plots$"exercise_time", "Exercise Score", ylims = c(0, 1.1))
#exercise_time_plot
#qs2(exercise_time_plot, "exercise_time")
#
## considerate_y
#considerate_y_plot <- uni_plot(top_unij_input_plots$"considerate_y", "Considerate\n(Youth Report)", c("No", "Yes"))
#considerate_y_plot
#qs2(considerate_y_plot, "considerate_y")
#
## family_temper_p
#family_temper_p_plot <- uni_plot(top_unij_input_plots$"family_temper_p", "Family Temper\n(Parent Report)", scale_fill_labels = c("No", "Yes"))
#family_temper_p_plot
#qs2(family_temper_p_plot, "family_temper_p")
#
## family_outdo_p
#family_outdo_p_plot <- uni_plot(top_unij_input_plots$"family_outdo_p", "Family Outdo\n(Parent Report)", c("No", "Yes"))
#family_outdo_p_plot
#qs2(family_outdo_p_plot, "family_outdo_p")
#
## cortical_thickness
#cortical_thickness_plot <- uni_plot(top_unij_input_plots$"cortical_thickness", "Cortical Thickness (mm)", ylims = c(2.3, 3.1))
#cortical_thickness_plot
#qs2(cortical_thickness_plot, "cortical_thickness")
#
## helps_hurt_p
#helps_hurt_p_plot <- uni_plot(top_unij_input_plots$"helps_hurt_p", "Helps Hurt\n(Parent Report)", c("No", "Yes"))
#helps_hurt_p_plot
#qs2(helps_hurt_p_plot, "helps_hurt_p")
#
## family_peaceful_p
#family_peaceful_p_plot <- uni_plot(top_unij_input_plots$"family_peaceful_p", "Family Peaceful\n(Parent Report)", c("No", "Yes"))
#family_peaceful_p_plot
#qs2(family_peaceful_p_plot, "family_peaceful_p")
#
## family_hit_p
#family_hit_p_plot <- uni_plot(top_unij_input_plots$"family_hit_p", "Family Hitting\n(Parent Report)", c("No", "Yes"))
#family_hit_p_plot
#qs2(family_hit_p_plot, "family_hit_p")
#
## family_angry_p
#family_angry_p_plot <- uni_plot(top_unij_input_plots$"family_angry_p", "Family Angry\n(Parent Report)", c("No", "Yes"))
#family_angry_p_plot
#qs2(family_angry_p_plot, "family_angry_p")
#
## family_yell_y
#family_yell_y_plot <- uni_plot(top_unij_input_plots$"family_yell_y", "Family Yells\n(Youth Report)", c("No", "Yes"))
#family_yell_y_plot
#qs2(family_yell_y_plot, "family_yell_y")
#
## pubertal_status_y
#pubertal_status_y_plot <- uni_plot(top_unij_input_plots$"pubertal_status_y", "Pubertal Status (Youth Report)")
#pubertal_status_y_plot
#qs2(pubertal_status_y_plot, "pubertal_status_y")
#
## helps_hurt_y
#helps_hurt_y_plot <- uni_plot(top_unij_input_plots$"helps_hurt_y", "Helps Hurt\n(Youth Report)", c("No", "Yes"))
#helps_hurt_y_plot
#qs2(helps_hurt_y_plot, "helps_hurt_y")
#
## family_throw_p
#family_throw_p_plot <- uni_plot(top_unij_input_plots$"family_throw_p", "Family Throwing\n(Parent Report)", c("No", "Yes"))
#family_throw_p_plot
#qs2(family_throw_p_plot, "family_throw_p")
#
#
#cbcl_anxdep_plot <- uni_plot(top_unij_outcome_plots$"cbcl_anxdep", "Anxious-Depressed", ylims = c(-0.5, 30))
#cbcl_withdep_plot <- uni_plot(top_unij_outcome_plots$"cbcl_withdep", "Withdrawn-Depressed", ylims = c(-0.5, 15))
#cbcl_somatic_plot <- uni_plot(top_unij_outcome_plots$"cbcl_somatic", "Somatic Problems", ylims = c(-0.5, 17))
#cbcl_social_plot <- uni_plot(top_unij_outcome_plots$"cbcl_social", "Social Problems", ylims = c(-0.5, 20))
#cbcl_thought_plot <- uni_plot(top_unij_outcome_plots$"cbcl_thought", "Thought Problems", ylims = c(-0.5, 20))
#cbcl_attention_plot <- uni_plot(top_unij_outcome_plots$"cbcl_attention", "Attention Problems", ylims = c(-0.5, 22))
#cbcl_rulebreak_plot <- uni_plot(top_unij_outcome_plots$"cbcl_rulebreak", "Rule-Breaking Problems", ylims = c(-0.5, 22))
#cbcl_aggressive_plot <- uni_plot(top_unij_outcome_plots$"cbcl_aggressive", "Aggression Problems", ylims = c(-0.5, 32))
#sds_sleep_plot <- uni_plot(top_unij_outcome_plots$"sds_sleep", "Total Sleep Problems", ylims = c(20, 100))
#
#matched_gen_in_plots <- list(
#    "brain_volume" = brain_volume_plot,
#    "sex" = sex_plot,
#    "cort_sa" = cort_sa_plot,
#    "household_income" = household_income_plot,
#    "pubertal_status_p" = pubertal_status_p_plot,
#    "programs_this_year" = programs_this_year_plot,
#    "non_school_programs" = non_school_programs_plot,
#    "parent_thought" = parent_thought_plot,
#    "parent_somatic" = parent_somatic_plot,
#    "weekday_screentime" = weekday_screentime_plot,
#    "parent_antisocial" = parent_antisocial_plot,
#    "parent_aggressive" = parent_aggressive_plot,
#    "parent_depress" = parent_depress_plot,
#    "parent_anxdep" = parent_anxdep_plot,
#    "race" = race_plot,
#    "parent_anxdisord" = parent_anxdisord_plot,
#    "private_instruction" = private_instruction_plot,
#    "weekend_screentime" = weekend_screentime_plot,
#    "parent_withdrawn" = parent_withdrawn_plot,
#    "parent_avoidant" = parent_avoidant_plot,
#    "parent_hyperactive" = parent_hyperactive_plot,
#    "fmri_cort_subcort_cors" = fmri_cort_subcort_cors_plot,
#    "parent_attention" = parent_attention_plot,
#    "parent_perstr" = parent_perstr_plot,
#    "parent_intrusive" = parent_intrusive_plot,
#    "family_fight_p" = family_fight_p_plot,
#    "headache_history" = headache_history_plot,
#    "exercise_time" = exercise_time_plot,
#    "considerate_y" = considerate_y_plot,
#    "family_temper_p" = family_temper_p_plot,
#    "family_outdo_p" = family_outdo_p_plot,
#    "cortical_thickness" = cortical_thickness_plot,
#    "helps_hurt_p" = helps_hurt_p_plot,
#    "family_peaceful_p" = family_peaceful_p_plot,
#    "family_hit_p" = family_hit_p_plot,
#    "family_angry_p" = family_angry_p_plot,
#    "family_yell_y" = family_yell_y_plot,
#    "pubertal_status_y" = pubertal_status_y_plot,
#    "helps_hurt_y" = helps_hurt_y_plot,
#    "family_throw_p" = family_throw_p_plot
#)
#
#matched_gen_out_plots <- list(
#    "cbcl_anxdep" = cbcl_anxdep_plot,
#    "cbcl_withdep" = cbcl_withdep_plot,
#    "cbcl_somatic" = cbcl_somatic_plot,
#    "cbcl_social" = cbcl_social_plot,
#    "cbcl_thought" = cbcl_thought_plot,
#    "cbcl_attention" = cbcl_attention_plot,
#    "cbcl_rulebreak" = cbcl_rulebreak_plot,
#    "cbcl_aggressive" = cbcl_aggressive_plot,
#    "sds_sleep" = sds_sleep_plot
#)
#
#list.save(matched_gen_in_plots, proc_path("matched_gen_in_plots.rds", TRUE))
#list.save(matched_gen_out_plots, proc_path("matched_gen_out_plots.rds", TRUE))
```

```{r}
#matched_gen_in_plots <- list.load(proc_path("2024_11_28_matched_gen_in_plots.rds"))
#matched_gen_out_plots <- list.load(proc_path("2024_11_28_matched_gen_out_plots.rds"))
```

## How does the classifier do?

Can always check this later

```{r}
#subtype_classifier <- readRDS(model_path("2024_11_28_subtype_classifier.rds"))
#
## Just FYI
#prep_data <- function(df, standardize = FALSE) {
#    df <- dplyr::select(df, -"subjectkey")
#    df <- dummy_cols(
#        df,
#        select_columns = "race",
#        remove_selected_columns = TRUE,
#        remove_most_frequent_dummy = TRUE
#    )
#    ordered_factors <- c(
#        "sex",
#        "household_income",
#        "pubertal_status_p",
#        "family_fight_p",
#        "family_outdo_p",
#        "helps_hurt_p",
#        "helpful_y",
#        "considerate_y",
#        "helps_hurt_y",
#        "family_criticize_p",
#        "family_outdo_y",
#        "family_angry_p",
#        "helpful_p",
#        "family_throw_p",
#        "family_hit_p",
#        "family_peaceful_y",
#        "family_throw_y",
#        "race_black",
#        "race_hispanic",
#        "race_other" 
#    )
#    df[ordered_factors] <- lapply(df[ordered_factors], as.ordered)
#    if (standardize) {
#        df[] <- lapply(df, as.numeric)
#        df <- as.data.frame(scale(df))
#    }
#    if ("cluster" %in% colnames(df)) {
#        df$"cluster" <- as.factor(df$"cluster")
#    }
#    return(df)
#}
#
##mini_df <- unij_matching_df_s1[1:200, ]
#
#library(randomForest)
#library(fastDummies)
#
#unij_pred_df_s1 <- unij_matching_df_s1 |> 
#    dplyr::mutate(
#        cluster = predict(
#            subtype_classifier,
#            newdata = prep_data(unij_matching_df_s1)
#        )
#    )
#
#unij_pred_df_s1$cluster |> table() |> prop.table()
#
#unij_pred_cluster_df <- unij_pred_df_s1 |> dplyr::select(subjectkey, cluster)
#
#unij_pred_plot_list <- auto_plot(
#    cluster_df = unij_pred_cluster_df,
#    data_list = unij_dl_s1,
#    target_list = unij_ol_s1 
#)
#
#unij_pred_plot_list[for_unij]
#
#unij_pred_all_plots <- wrap_plots(unij_pred_plot_list[for_unij])
#
#ggsave(
#    fig_path("unij_pred_all_plots.png", TRUE),
#    unij_pred_all_plots,
#    width = 45,
#    height = 30,
#    dpi = 50
#)
#
#unij_pred_cluster_df$"cluster" |> table() |> prop.table()
#
#get_cluster_df(mtbi_full_top_3c)$"cluster" |> table() |> prop.table()
#
#rbind(
#    unij_pred_cluster_df$"cluster" |> table(),
#    get_cluster_df(mtbi_full_top_3c)$"cluster" |> table()
#) |> chisq.test()
```
