# Matching

This chapter contains:

1. Derivation of subtypes from a variety of matched uninjured groups
2. Comparison of those subtypes with the mTBI baseline solution

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)
library(MatchIt)
library(tibble)
library(ggplot2)
library(fastDummies)
library(dplyr)
library(tidyr)
library(xtable)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
model_path <- path_maker(here(paste0("data/abcd/results/models")))

mtbi_subs <- read_subjects(sub_path("2024_11_18_mtbi_subs.csv"))
unij_subs <- read_subjects(sub_path("2024_11_18_unij_subs.csv"))
```

## Importing data

```{r}
all_dls <- list.load(input_path("2024_11_18_all_dls.rds"))

mtbi_full_data_list_1 <- list.load(input_path("2024_11_26_mtbi_full_data_list_1.rds"))
mtbi_full_oom_list_1 <- list.load(input_path("2024_11_26_mtbi_full_oom_list_1.rds"))
mtbi_full_top_3c <- read_csv(proc_path("2024_11_26_mtbi_full_top_3c.csv"))

###############################################################################
unij_dl_s1 <- all_dls$"unij_data_lists"$"imp_1"
unij_dl_p1 <- all_dls$"unij_pooled_data_lists"$"imp_1"
unij_ol_s1 <- all_dls$"unij_oom_lists"$"imp_1"
unij_ol_p1 <- all_dls$"unij_pooled_oom_lists"$"imp_1"
```

## Matching

Finding matched uninjured controls for each mtbi subject based on a variety of variables.
Matching will be done based on the first imputed dataset of the baseline data.

```{r}
mtbi_matching_df <- c(mtbi_full_data_list_1, mtbi_full_oom_list_1) |> collapse_dl()
unij_matching_df_s1 <- c(unij_dl_s1, unij_ol_s1) |> collapse_dl()
unij_matching_df_s1 <- c(unij_dl_s1, unij_ol_s1) |> collapse_dl()
unij_matching_df_p1 <- c(unij_dl_p1, unij_ol_p1) |> collapse_dl()

mtbi_matching_df$"mtbi" <- 1
unij_matching_df_s1$"mtbi" <- 0
unij_matching_df_p1$"mtbi" <- 0

mtbi_matching_df <- dplyr::select(
    mtbi_matching_df,
    colnames(unij_matching_df_s1)
)

matching_df_s1 <- rbind(mtbi_matching_df, unij_matching_df_s1)
matching_df_p1 <- rbind(mtbi_matching_df, unij_matching_df_p1)
```


```{r}
# Total parent psych
matching_df_s1$"total_parent_psych" <- matching_df_s1 |> dplyr::select(dplyr::starts_with("parent")) |> rowSums()
matching_df_p1$"total_parent_psych" <- matching_df_p1 |> dplyr::select(dplyr::starts_with("parent")) |> rowSums()

# Total CBCL
matching_df_s1$"total_impairments" <- matching_df_s1 |> dplyr::select(dplyr::starts_with("cbcl"), dplyr::starts_with("sds")) |> rowSums()
matching_df_p1$"total_impairments" <- matching_df_p1 |> dplyr::select(dplyr::starts_with("cbcl"), dplyr::starts_with("sds")) |> rowSums()
```

We'll try a few different matching schemes:

```{r}
d_vars <- "household_income + race + sex + pubertal_status_p + pubertal_status_y"
p_vars <- "total_parent_psych"
o_vars <- "total_impairments"

dp_vars <- paste0(d_vars, " + ", p_vars)
do_vars <- paste0(d_vars, " + ", o_vars)
op_vars <- paste0(o_vars, " + ", p_vars)

dpo_vars <- paste0(d_vars, " + ", p_vars, " + ", o_vars)

formula_d <- "mtbi ~ household_income + race + sex + pubertal_status_p + pubertal_status_y"
formula_p <- "mtbi ~ total_parent_psych"
formula_o <- "mtbi ~ total_impairments"

###############################################################################
# Matching by demographic variables
###############################################################################
matching_results_b_s1 <- matchit(formula(mtbi ~ household_income + race + sex + pubertal_status_p + pubertal_status_y), data = matching_df_s1, method = "nearest")
matching_results_b_p1 <- matchit(formula(mtbi ~ household_income + race + sex + pubertal_status_p + pubertal_status_y), data = matching_df_p1, method = "nearest")
matching_summary_b_s1 <- capture.output(print(summary(matching_results_b_s1)))
matching_summary_b_p1 <- capture.output(print(summary(matching_results_b_p1)))
matched_data_b_s1 <- match.data(matching_results_b_s1)
matched_data_b_p1 <- match.data(matching_results_b_p1)

###############################################################################
# Matching by parent psych alone
###############################################################################
matching_results_c_s1 <- matchit(formula(mtbi ~ total_parent_psych), data = matching_df_s1, method = "nearest")
matching_results_c_p1 <- matchit(formula(mtbi ~ total_parent_psych), data = matching_df_p1, method = "nearest")
matching_summary_c_s1 <- capture.output(print(summary(matching_results_c_s1)))
matching_summary_c_p1 <- capture.output(print(summary(matching_results_c_p1)))
matched_data_c_s1 <- match.data(matching_results_c_s1)
matched_data_c_p1 <- match.data(matching_results_c_p1)

###############################################################################
# Matching by CBCL alone
###############################################################################
matching_results_d_s1 <- matchit(formula(mtbi ~ total_impairments), data = matching_df_s1, method = "nearest")
matching_results_d_p1 <- matchit(formula(mtbi ~ total_impairments), data = matching_df_p1, method = "nearest")
matching_summary_d_s1 <- capture.output(print(summary(matching_results_d_s1)))
matching_summary_d_p1 <- capture.output(print(summary(matching_results_d_p1)))
matched_data_d_s1 <- match.data(matching_results_d_s1)
matched_data_d_p1 <- match.data(matching_results_d_p1)

saveRDS(matching_results_a_s1, proc_path("matching_results_a_s1.rds", TRUE))
saveRDS(matching_results_a_p1, proc_path("matching_results_a_p1.rds", TRUE))
saveRDS(matching_results_b_s1, proc_path("matching_results_b_s1.rds", TRUE))
saveRDS(matching_results_b_p1, proc_path("matching_results_b_p1.rds", TRUE))
saveRDS(matching_results_c_s1, proc_path("matching_results_c_s1.rds", TRUE))
saveRDS(matching_results_c_p1, proc_path("matching_results_c_p1.rds", TRUE))
saveRDS(matching_results_d_s1, proc_path("matching_results_d_s1.rds", TRUE))
saveRDS(matching_results_d_p1, proc_path("matching_results_d_p1.rds", TRUE))

saveRDS(matching_summary_a_s1, proc_path("matching_summary_a_s1.rds", TRUE))
saveRDS(matching_summary_a_p1, proc_path("matching_summary_a_p1.rds", TRUE))
saveRDS(matching_summary_b_s1, proc_path("matching_summary_b_s1.rds", TRUE))
saveRDS(matching_summary_b_p1, proc_path("matching_summary_b_p1.rds", TRUE))
saveRDS(matching_summary_c_s1, proc_path("matching_summary_c_s1.rds", TRUE))
saveRDS(matching_summary_c_p1, proc_path("matching_summary_c_p1.rds", TRUE))
saveRDS(matching_summary_d_s1, proc_path("matching_summary_d_s1.rds", TRUE))
saveRDS(matching_summary_d_p1, proc_path("matching_summary_d_p1.rds", TRUE))

saveRDS(matched_data_a_s1, proc_path("matched_data_a_s1.rds", TRUE))
saveRDS(matched_data_a_p1, proc_path("matched_data_a_p1.rds", TRUE))
saveRDS(matched_data_b_s1, proc_path("matched_data_b_s1.rds", TRUE))
saveRDS(matched_data_b_p1, proc_path("matched_data_b_p1.rds", TRUE))
saveRDS(matched_data_c_s1, proc_path("matched_data_c_s1.rds", TRUE))
saveRDS(matched_data_c_p1, proc_path("matched_data_c_p1.rds", TRUE))
saveRDS(matched_data_d_s1, proc_path("matched_data_d_s1.rds", TRUE))
saveRDS(matched_data_d_p1, proc_path("matched_data_d_p1.rds", TRUE))

## Matching by income, race, parent psych
#matching_results_a_s1 <- matchit(formula(mtbi ~ household_income + race + total_parent_psych), data = matching_df_s1, method = "nearest")
#matching_results_a_p1 <- matchit(formula(mtbi ~ household_income + race + total_parent_psych), data = matching_df_p1, method = "nearest")
#matching_summary_a_s1 <- capture.output(print(summary(matching_results_a_s1)))
#matching_summary_a_p1 <- capture.output(print(summary(matching_results_a_p1)))
#matched_data_a_s1 <- match.data(matching_results_a_s1)
#matched_data_a_p1 <- match.data(matching_results_a_p1)


```

```{r}
# CHECKPOINT
matching_summary_a_s1 <- readRDS(proc_path("2024_11_28_matching_summary_a_s1.rds"))
matching_summary_a_p1 <- readRDS(proc_path("2024_11_28_matching_summary_a_p1.rds"))
matching_summary_b_s1 <- readRDS(proc_path("2024_11_28_matching_summary_b_s1.rds"))
matching_summary_b_p1 <- readRDS(proc_path("2024_11_28_matching_summary_b_p1.rds"))
matching_summary_c_s1 <- readRDS(proc_path("2024_11_28_matching_summary_c_s1.rds"))
matching_summary_c_p1 <- readRDS(proc_path("2024_11_28_matching_summary_c_p1.rds"))
matching_summary_d_s1 <- readRDS(proc_path("2024_11_28_matching_summary_d_s1.rds"))
matching_summary_d_p1 <- readRDS(proc_path("2024_11_28_matching_summary_d_p1.rds"))

matching_results_a_s1 <- readRDS(proc_path("2024_11_28_matching_results_a_s1.rds"))
matching_results_a_p1 <- readRDS(proc_path("2024_11_28_matching_results_a_p1.rds"))
matching_results_b_s1 <- readRDS(proc_path("2024_11_28_matching_results_b_s1.rds"))
matching_results_b_p1 <- readRDS(proc_path("2024_11_28_matching_results_b_p1.rds"))
matching_results_c_s1 <- readRDS(proc_path("2024_11_28_matching_results_c_s1.rds"))
matching_results_c_p1 <- readRDS(proc_path("2024_11_28_matching_results_c_p1.rds"))
matching_results_d_s1 <- readRDS(proc_path("2024_11_28_matching_results_d_s1.rds"))
matching_results_d_p1 <- readRDS(proc_path("2024_11_28_matching_results_d_p1.rds"))

matched_data_a_s1 <- readRDS(proc_path("2024_11_28_matched_data_a_s1.rds"))
matched_data_a_p1 <- readRDS(proc_path("2024_11_28_matched_data_a_p1.rds"))
matched_data_b_s1 <- readRDS(proc_path("2024_11_28_matched_data_b_s1.rds"))
matched_data_b_p1 <- readRDS(proc_path("2024_11_28_matched_data_b_p1.rds"))
matched_data_c_s1 <- readRDS(proc_path("2024_11_28_matched_data_c_s1.rds"))
matched_data_c_p1 <- readRDS(proc_path("2024_11_28_matched_data_c_p1.rds"))
matched_data_d_s1 <- readRDS(proc_path("2024_11_28_matched_data_d_s1.rds"))
matched_data_d_p1 <- readRDS(proc_path("2024_11_28_matched_data_d_p1.rds"))
```

```{r}
save_matching_plot <- function(matching_results, name) {
    grDevices::png(filename = name, width = 1000, height = 500, res = 100)
    plot(matching_results, type = "density", interactive = FALSE)
    grDevices::dev.off()
}

grDevices::png(filename = fig_path("matching_results_a_s1.png", TRUE), width = 1000, height = 500, res = 100)
plot(matching_results_a_s1, type = "density", interactive = FALSE)
grDevices::dev.off()
grDevices::png(filename = fig_path("matching_results_a_p1.png", TRUE), width = 1000, height = 500, res = 100)
plot(matching_results_a_p1, type = "density", interactive = FALSE)
grDevices::dev.off()
grDevices::png(filename = fig_path("matching_results_b_s1.png", TRUE), width = 1000, height = 500, res = 100)
plot(matching_results_b_s1, type = "density", interactive = FALSE)
grDevices::dev.off()
grDevices::png(filename = fig_path("matching_results_b_p1.png", TRUE), width = 1000, height = 500, res = 100)
plot(matching_results_b_p1, type = "density", interactive = FALSE)
grDevices::dev.off()
grDevices::png(filename = fig_path("matching_results_c_s1.png", TRUE), width = 1000, height = 500, res = 100)
plot(matching_results_c_s1, type = "density", interactive = FALSE)
grDevices::dev.off()
grDevices::png(filename = fig_path("matching_results_c_p1.png", TRUE), width = 1000, height = 500, res = 100)
plot(matching_results_c_p1, type = "density", interactive = FALSE)
grDevices::dev.off()
grDevices::png(filename = fig_path("matching_results_d_s1.png", TRUE), width = 1000, height = 500, res = 100)
plot(matching_results_d_s1, type = "density", interactive = FALSE)
grDevices::dev.off()
grDevices::png(filename = fig_path("matching_results_d_p1.png", TRUE), width = 1000, height = 500, res = 100)
plot(matching_results_d_p1, type = "density", interactive = FALSE)
grDevices::dev.off()
```

```{r}
matched_unij_a_s1 <- dplyr::filter(matched_data_a_s1, mtbi == 0)$"subjectkey"
matched_unij_a_p1 <- dplyr::filter(matched_data_a_p1, mtbi == 0)$"subjectkey"
matched_unij_b_s1 <- dplyr::filter(matched_data_b_s1, mtbi == 0)$"subjectkey"
matched_unij_b_p1 <- dplyr::filter(matched_data_b_p1, mtbi == 0)$"subjectkey"
matched_unij_c_s1 <- dplyr::filter(matched_data_c_s1, mtbi == 0)$"subjectkey"
matched_unij_c_p1 <- dplyr::filter(matched_data_c_p1, mtbi == 0)$"subjectkey"
matched_unij_d_s1 <- dplyr::filter(matched_data_d_s1, mtbi == 0)$"subjectkey"
matched_unij_d_p1 <- dplyr::filter(matched_data_d_p1, mtbi == 0)$"subjectkey"

# Extract the control group from the matched data
write_csv(data.frame(subjectkey = matched_unij_a_s1), sub_path("matched_unij_a_s1.csv", TRUE))
write_csv(data.frame(subjectkey = matched_unij_a_p1), sub_path("matched_unij_a_p1.csv", TRUE))
write_csv(data.frame(subjectkey = matched_unij_b_s1), sub_path("matched_unij_b_s1.csv", TRUE))
write_csv(data.frame(subjectkey = matched_unij_b_p1), sub_path("matched_unij_b_p1.csv", TRUE))
write_csv(data.frame(subjectkey = matched_unij_c_s1), sub_path("matched_unij_c_s1.csv", TRUE))
write_csv(data.frame(subjectkey = matched_unij_c_p1), sub_path("matched_unij_c_p1.csv", TRUE))
write_csv(data.frame(subjectkey = matched_unij_d_s1), sub_path("matched_unij_d_s1.csv", TRUE))
write_csv(data.frame(subjectkey = matched_unij_d_p1), sub_path("matched_unij_d_p1.csv", TRUE))
```

```{r}
matched_unij_a_s1 <- read_subjects(sub_path("2024_11_28_matched_unij_a_s1.csv"))
matched_unij_a_p1 <- read_subjects(sub_path("2024_11_28_matched_unij_a_p1.csv"))
matched_unij_b_s1 <- read_subjects(sub_path("2024_11_28_matched_unij_b_s1.csv"))
matched_unij_b_p1 <- read_subjects(sub_path("2024_11_28_matched_unij_b_p1.csv"))
matched_unij_c_s1 <- read_subjects(sub_path("2024_11_28_matched_unij_c_s1.csv"))
matched_unij_c_p1 <- read_subjects(sub_path("2024_11_28_matched_unij_c_p1.csv"))
matched_unij_d_s1 <- read_subjects(sub_path("2024_11_28_matched_unij_d_s1.csv"))
matched_unij_d_p1 <- read_subjects(sub_path("2024_11_28_matched_unij_d_p1.csv"))

sub_list <- list(
    "a_s1" = matched_unij_a_s1,
    "a_p1" = matched_unij_a_p1,
    "b_s1" = matched_unij_b_s1,
    "b_p1" = matched_unij_b_p1,
    "c_s1" = matched_unij_c_s1,
    "c_p1" = matched_unij_c_p1,
    "d_s1" = matched_unij_d_s1,
    "d_p1" = matched_unij_d_p1
)
```

## Subsetting matched unijured data and out of model lists

```{r}
subject_filter_dl <- function(data_list, subject_vector) {
    data_list <- data_list |>
        lapply(
            function(x) {
                keep_subs <- x$"data"$"subjectkey" %in% subject_vector
                x$"data" <- x$"data"[keep_subs, ]
                return(x)
            }
        )
    return(data_list)
}

set.seed(42)
random_unij_subs <- sample(unij_subs, size = 440)

matched_unij_dl_a_s1 <- subject_filter_dl(unij_dl_s1, matched_unij_a_s1)
matched_unij_dl_a_p1 <- subject_filter_dl(unij_dl_p1, matched_unij_a_p1)
matched_unij_ol_a_s1 <- subject_filter_dl(unij_ol_s1, matched_unij_a_s1)
matched_unij_ol_a_p1 <- subject_filter_dl(unij_ol_p1, matched_unij_a_p1)

matched_unij_dl_b_s1 <- subject_filter_dl(unij_dl_s1, matched_unij_b_s1)
matched_unij_dl_b_p1 <- subject_filter_dl(unij_dl_p1, matched_unij_b_p1)
matched_unij_ol_b_s1 <- subject_filter_dl(unij_ol_s1, matched_unij_b_s1)
matched_unij_ol_b_p1 <- subject_filter_dl(unij_ol_p1, matched_unij_b_p1)

matched_unij_dl_c_s1 <- subject_filter_dl(unij_dl_s1, matched_unij_c_s1)
matched_unij_dl_c_p1 <- subject_filter_dl(unij_dl_p1, matched_unij_c_p1)
matched_unij_ol_c_s1 <- subject_filter_dl(unij_ol_s1, matched_unij_c_s1)
matched_unij_ol_c_p1 <- subject_filter_dl(unij_ol_p1, matched_unij_c_p1)

matched_unij_dl_d_s1 <- subject_filter_dl(unij_dl_s1, matched_unij_d_s1)
matched_unij_dl_d_p1 <- subject_filter_dl(unij_dl_p1, matched_unij_d_p1)
matched_unij_ol_d_s1 <- subject_filter_dl(unij_ol_s1, matched_unij_d_s1)
matched_unij_ol_d_p1 <- subject_filter_dl(unij_ol_p1, matched_unij_d_p1)

random_unij_dl_s1 <- subject_filter_dl(unij_dl_s1, paste0("subject_", random_unij_subs))
random_unij_dl_p1 <- subject_filter_dl(unij_dl_p1, paste0("subject_", random_unij_subs))
random_unij_ol_s1 <- subject_filter_dl(unij_ol_s1, paste0("subject_", random_unij_subs))
random_unij_ol_p1 <- subject_filter_dl(unij_ol_p1, paste0("subject_", random_unij_subs))

list.save(matched_unij_dl_a_s1, proc_path("matched_unij_dl_a_s1.rds", TRUE))
list.save(matched_unij_dl_a_p1, proc_path("matched_unij_dl_a_p1.rds", TRUE))
list.save(matched_unij_ol_a_s1, proc_path("matched_unij_ol_a_s1.rds", TRUE))
list.save(matched_unij_ol_a_p1, proc_path("matched_unij_ol_a_p1.rds", TRUE))
list.save(matched_unij_dl_b_s1, proc_path("matched_unij_dl_b_s1.rds", TRUE))
list.save(matched_unij_dl_b_p1, proc_path("matched_unij_dl_b_p1.rds", TRUE))
list.save(matched_unij_ol_b_s1, proc_path("matched_unij_ol_b_s1.rds", TRUE))
list.save(matched_unij_ol_b_p1, proc_path("matched_unij_ol_b_p1.rds", TRUE))
list.save(matched_unij_dl_c_s1, proc_path("matched_unij_dl_c_s1.rds", TRUE))
list.save(matched_unij_dl_c_p1, proc_path("matched_unij_dl_c_p1.rds", TRUE))
list.save(matched_unij_ol_c_s1, proc_path("matched_unij_ol_c_s1.rds", TRUE))
list.save(matched_unij_ol_c_p1, proc_path("matched_unij_ol_c_p1.rds", TRUE))
list.save(matched_unij_dl_d_s1, proc_path("matched_unij_dl_d_s1.rds", TRUE))
list.save(matched_unij_dl_d_p1, proc_path("matched_unij_dl_d_p1.rds", TRUE))
list.save(matched_unij_ol_d_s1, proc_path("matched_unij_ol_d_s1.rds", TRUE))
list.save(matched_unij_ol_d_p1, proc_path("matched_unij_ol_d_p1.rds", TRUE))

list.save(random_unij_dl_s1, proc_path("random_unij_dl_s1.rds", TRUE))
list.save(random_unij_dl_p1, proc_path("random_unij_dl_p1.rds", TRUE))
list.save(random_unij_ol_s1, proc_path("random_unij_ol_s1.rds", TRUE))
list.save(random_unij_ol_p1, proc_path("random_unij_ol_p1.rds", TRUE))
```

```{r}
# CHECKPOINT
matched_unij_dl_a_s1 <- list.load(proc_path("2024_11_28_matched_unij_dl_a_s1.rds"))
matched_unij_dl_a_p1 <- list.load(proc_path("2024_11_28_matched_unij_dl_a_p1.rds"))
matched_unij_ol_a_s1 <- list.load(proc_path("2024_11_28_matched_unij_ol_a_s1.rds"))
matched_unij_ol_a_p1 <- list.load(proc_path("2024_11_28_matched_unij_ol_a_p1.rds"))
matched_unij_dl_b_s1 <- list.load(proc_path("2024_11_28_matched_unij_dl_b_s1.rds"))
matched_unij_dl_b_p1 <- list.load(proc_path("2024_11_28_matched_unij_dl_b_p1.rds"))
matched_unij_ol_b_s1 <- list.load(proc_path("2024_11_28_matched_unij_ol_b_s1.rds"))
matched_unij_ol_b_p1 <- list.load(proc_path("2024_11_28_matched_unij_ol_b_p1.rds"))
matched_unij_dl_c_s1 <- list.load(proc_path("2024_11_28_matched_unij_dl_c_s1.rds"))
matched_unij_dl_c_p1 <- list.load(proc_path("2024_11_28_matched_unij_dl_c_p1.rds"))
matched_unij_ol_c_s1 <- list.load(proc_path("2024_11_28_matched_unij_ol_c_s1.rds"))
matched_unij_ol_c_p1 <- list.load(proc_path("2024_11_28_matched_unij_ol_c_p1.rds"))
matched_unij_dl_d_s1 <- list.load(proc_path("2024_11_28_matched_unij_dl_d_s1.rds"))
matched_unij_dl_d_p1 <- list.load(proc_path("2024_11_28_matched_unij_dl_d_p1.rds"))
matched_unij_ol_d_s1 <- list.load(proc_path("2024_11_28_matched_unij_ol_d_s1.rds"))
matched_unij_ol_d_p1 <- list.load(proc_path("2024_11_28_matched_unij_ol_d_p1.rds"))

random_unij_dl_s1 <- list.load(proc_path("2024_12_02_random_unij_dl_s1.rds"))
random_unij_dl_p1 <- list.load(proc_path("2024_12_02_random_unij_dl_p1.rds"))
random_unij_ol_s1 <- list.load(proc_path("2024_12_02_random_unij_ol_s1.rds"))
random_unij_ol_p1 <- list.load(proc_path("2024_12_02_random_unij_ol_p1.rds"))
```

## metaSNF

```{r}
my_distance_metrics <- generate_distance_metrics_list(
    continuous_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    discrete_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ordinal_distances = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
)

set.seed(42)
matched_settings_matrix <- generate_settings_matrix(
    matched_unij_dl_a_s1,
    nrow = 200,
    distance_metrics_list = my_distance_metrics
)

write_csv(matched_settings_matrix, proc_path("matched_settings_matrix.csv", TRUE))
```

```{r}
# CHECKPOINT
matched_settings_matrix <- read_csv(proc_path("2024_11_28_matched_settings_matrix.csv"))
```

The goal now is to actually run the SNF.

I have 4 different "sets" of data list / oom list combinations.

Consider just the first set.

This covers 10 different imputed datasets (right?) the 5 pooled and 5 solo unijured.
So, I'll create 2000 SNF solutions using all of those 10 sets.

Then, repeat that process 4x.

```{r}
unij_sm_a_s1 <- batch_snf(matched_unij_dl_a_s1, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(unij_sm_a_s1, proc_path("unij_sm_a_s1.csv", TRUE))
unij_sm_a_p1 <- batch_snf(matched_unij_dl_a_p1, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(unij_sm_a_p1, proc_path("unij_sm_a_p1.csv", TRUE))
unij_sm_b_s1 <- batch_snf(matched_unij_dl_b_s1, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(unij_sm_b_s1, proc_path("unij_sm_b_s1.csv", TRUE))
unij_sm_b_p1 <- batch_snf(matched_unij_dl_b_p1, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(unij_sm_b_p1, proc_path("unij_sm_b_p1.csv", TRUE))
unij_sm_c_s1 <- batch_snf(matched_unij_dl_c_s1, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(unij_sm_c_s1, proc_path("unij_sm_c_s1.csv", TRUE))
unij_sm_c_p1 <- batch_snf(matched_unij_dl_c_p1, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(unij_sm_c_p1, proc_path("unij_sm_c_p1.csv", TRUE))
unij_sm_d_s1 <- batch_snf(matched_unij_dl_d_s1, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(unij_sm_d_s1, proc_path("unij_sm_d_s1.csv", TRUE))
unij_sm_d_p1 <- batch_snf(matched_unij_dl_d_p1, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(unij_sm_d_p1, proc_path("unij_sm_d_p1.csv", TRUE))
```

```{r}
unij_sm_a_s1 <- read_csv(proc_path("2024_11_28_unij_sm_a_s1.csv"))
unij_sm_a_p1 <- read_csv(proc_path("2024_11_28_unij_sm_a_p1.csv"))
unij_sm_b_s1 <- read_csv(proc_path("2024_11_28_unij_sm_b_s1.csv"))
unij_sm_b_p1 <- read_csv(proc_path("2024_11_28_unij_sm_b_p1.csv"))
unij_sm_c_s1 <- read_csv(proc_path("2024_11_28_unij_sm_c_s1.csv"))
unij_sm_c_p1 <- read_csv(proc_path("2024_11_28_unij_sm_c_p1.csv"))
unij_sm_d_s1 <- read_csv(proc_path("2024_11_28_unij_sm_d_s1.csv"))
unij_sm_d_p1 <- read_csv(proc_path("2024_11_28_unij_sm_d_p1.csv"))
```

```{r}
matched_unij_esm_a_s1 <- extend_solutions(unij_sm_a_s1, data_list = matched_unij_dl_a_s1, target_list = matched_unij_ol_a_s1, min_pval = 1e-10, processes = "max")
write_csv(matched_unij_esm_a_s1, proc_path("matched_unij_esm_a_s1.csv", TRUE))
matched_unij_esm_a_p1 <- extend_solutions(unij_sm_a_p1, data_list = matched_unij_dl_a_p1, target_list = matched_unij_ol_a_p1, min_pval = 1e-10, processes = "max")
write_csv(matched_unij_esm_a_p1, proc_path("matched_unij_esm_a_p1.csv", TRUE))
matched_unij_esm_b_s1 <- extend_solutions(unij_sm_b_s1, data_list = matched_unij_dl_b_s1, target_list = matched_unij_ol_b_s1, min_pval = 1e-10, processes = "max")
write_csv(matched_unij_esm_b_s1, proc_path("matched_unij_esm_b_s1.csv", TRUE))
matched_unij_esm_b_p1 <- extend_solutions(unij_sm_b_p1, data_list = matched_unij_dl_b_p1, target_list = matched_unij_ol_b_p1, min_pval = 1e-10, processes = "max")
write_csv(matched_unij_esm_b_p1, proc_path("matched_unij_esm_b_p1.csv", TRUE))
matched_unij_esm_c_s1 <- extend_solutions(unij_sm_c_s1, data_list = matched_unij_dl_c_s1, target_list = matched_unij_ol_c_s1, min_pval = 1e-10, processes = "max")
write_csv(matched_unij_esm_c_s1, proc_path("matched_unij_esm_c_s1.csv", TRUE))
matched_unij_esm_c_p1 <- extend_solutions(unij_sm_c_p1, data_list = matched_unij_dl_c_p1, target_list = matched_unij_ol_c_p1, min_pval = 1e-10, processes = "max")
write_csv(matched_unij_esm_c_p1, proc_path("matched_unij_esm_c_p1.csv", TRUE))
matched_unij_esm_d_s1 <- extend_solutions(unij_sm_d_s1, data_list = matched_unij_dl_d_s1, target_list = matched_unij_ol_d_s1, min_pval = 1e-10, processes = "max")
write_csv(matched_unij_esm_d_s1, proc_path("matched_unij_esm_d_s1.csv", TRUE))
matched_unij_esm_d_p1 <- extend_solutions(unij_sm_d_p1, data_list = matched_unij_dl_d_p1, target_list = matched_unij_ol_d_p1, min_pval = 1e-10, processes = "max")
write_csv(matched_unij_esm_d_p1, proc_path("matched_unij_esm_d_p1.csv", TRUE))
```



```{r}
# Random uninjured for context
random_unij_sm_s1 <- batch_snf(random_unij_dl_s1, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(random_unij_sm_s1, proc_path("random_unij_sm_s1.csv", TRUE))

random_unij_sm_p1 <- batch_snf(random_unij_dl_p1, matched_settings_matrix, processes = "max", distance_metrics_list = my_distance_metrics)
write_csv(random_unij_sm_p1, proc_path("random_unij_sm_p1.csv", TRUE))

random_unij_sm_s1 <- read_csv(proc_path("2024_12_02_random_unij_sm_s1.csv"))
random_unij_sm_p1 <- read_csv(proc_path("2024_12_02_random_unij_sm_p1.csv"))

random_unij_esm_s1 <- extend_solutions(unij_sm_s1, data_list = random_unij_dl_s1, target_list = random_unij_ol_s1, min_pval = 1e-10, processes = "max")
write_csv(random_unij_esm_s1, proc_path("random_unij_esm_s1.csv", TRUE))

random_unij_esm_p1 <- extend_solutions(unij_sm_p1, data_list = random_unij_dl_p1, target_list = random_unij_ol_p1, min_pval = 1e-10, processes = "max")
write_csv(random_unij_esm_p1, proc_path("random_unij_esm_p1.csv", TRUE))
```


```{r}
matched_unij_esm_a_s1 <- read_csv(proc_path("2024_11_28_matched_unij_esm_a_s1.csv"))
matched_unij_esm_a_p1 <- read_csv(proc_path("2024_11_28_matched_unij_esm_a_p1.csv"))
matched_unij_esm_b_s1 <- read_csv(proc_path("2024_11_28_matched_unij_esm_b_s1.csv"))
matched_unij_esm_b_p1 <- read_csv(proc_path("2024_11_28_matched_unij_esm_b_p1.csv"))
matched_unij_esm_c_s1 <- read_csv(proc_path("2024_11_28_matched_unij_esm_c_s1.csv"))
matched_unij_esm_c_p1 <- read_csv(proc_path("2024_11_28_matched_unij_esm_c_p1.csv"))
matched_unij_esm_d_s1 <- read_csv(proc_path("2024_11_28_matched_unij_esm_d_s1.csv"))
matched_unij_esm_d_p1 <- read_csv(proc_path("2024_11_28_matched_unij_esm_d_p1.csv"))

matched_unij_esm_list <- list(
    "a_s1" = matched_unij_esm_a_s1,
    "a_p1" = matched_unij_esm_a_p1,
    "b_s1" = matched_unij_esm_b_s1,
    "b_p1" = matched_unij_esm_b_p1,
    "c_s1" = matched_unij_esm_c_s1,
    "c_p1" = matched_unij_esm_c_p1,
    "d_s1" = matched_unij_esm_d_s1,
    "d_p1" = matched_unij_esm_d_p1
)

names(matched_unij_esm_list)  <- c(
    "a_s1",
    "a_p1",
    "b_s1",
    "b_p1",
    "c_s1",
    "c_p1",
    "d_s1",
    "d_p1"
)

list.save(matched_unij_esm_list, proc_path("matched_unij_esm_list.rds", TRUE))
```

```{r}
matched_unij_esm_list <- list.load(proc_path("2024_11_28_matched_unij_esm_list.rds"))
```

```{r}
matched_unij_esm_3c_list <- lapply(
    matched_unij_esm_list,
    function(x) {
        x$"impairment_separation" <- -log10(x$"mean_pval")
        x <- dplyr::filter(x, nclust == 3, impairment_separation > 1)
        return(x)
    }
)
matched_unij_esm_3c_list |> lapply(nrow)


list.save(
    matched_unij_esm_3c_list,
    proc_path("matched_unij_esm_3c_list.rds", TRUE)
)

```

```{r}
# CHECKPOINT
matched_unij_esm_3c_list <- list.load(
    proc_path("2024_11_28_matched_unij_esm_3c_list.rds")
)
```

```{r}

# Pretty small impairment separations except on "a_p1" and somewhat on "a_s1"
lapply( 
    matched_unij_esm_3c_list,
    function(x) {
        x$"impairment_separation"
    }
)

dcols <- c(
    "AS" = "#85929e",
    "D" = "#bb8fce",
    "N" = "#e59866",
    "MH" = "#7fb3d5",
    "P" = "#52be80",
    "S" = "#d98880",
    "B" = "#ff3131"
)

matched_unij_a_s1 <- mc_manhattan_plot(
    matched_unij_esm_3c_list$"a_s1",
    data_list = matched_unij_dl_a_s1,
    target_list = matched_unij_ol_a_s1,
    domain_colours = dcols
)

matched_unij_a_p1 <- mc_manhattan_plot(
    matched_unij_esm_3c_list$"a_p1",
    data_list = matched_unij_dl_a_p1,
    target_list = matched_unij_ol_a_p1,
    domain_colours = dcols
)

matched_unij_b_s1 <- mc_manhattan_plot(
    matched_unij_esm_3c_list$"b_s1",
    data_list = matched_unij_dl_b_s1,
    target_list = matched_unij_ol_b_s1,
    domain_colours = dcols
)

matched_unij_b_p1 <- mc_manhattan_plot(
    matched_unij_esm_3c_list$"b_p1",
    data_list = matched_unij_dl_b_p1,
    target_list = matched_unij_ol_b_p1,
    domain_colours = dcols
)

matched_unij_c_s1 <- mc_manhattan_plot(
    matched_unij_esm_3c_list$"c_s1",
    data_list = matched_unij_dl_c_s1,
    target_list = matched_unij_ol_c_s1,
    domain_colours = dcols
)

matched_unij_c_p1 <- mc_manhattan_plot(
    matched_unij_esm_3c_list$"c_p1",
    data_list = matched_unij_dl_c_p1,
    target_list = matched_unij_ol_c_p1,
    domain_colours = dcols
)

matched_unij_d_p1 <- mc_manhattan_plot(
    matched_unij_esm_3c_list$"d_p1",
    data_list = matched_unij_dl_d_p1,
    target_list = matched_unij_ol_d_p1,
    domain_colours = dcols
)

# Good rows 1, 4, 5, 6?
matched_unij_a_s1

# Good row 1
matched_unij_a_p1

# Bad
matched_unij_b_s1

# Bad
matched_unij_b_p1

# Bad
matched_unij_c_s1

# Bad
matched_unij_c_p1

# Bad
matched_unij_d_p1

matched_unij_manhattan_plots <- list(
    matched_unij_a_s1,
    matched_unij_a_p1,
    matched_unij_b_s1,
    matched_unij_b_p1,
    matched_unij_c_s1,
    matched_unij_c_p1,
    matched_unij_d_p1
)

names(matched_unij_manhattan_plots) <- c(
    "a_s1",
    "a_p1",
    "b_s1",
    "b_p1",
    "c_s1",
    "c_p1",
    "d_p1"
)

list.save(
    matched_unij_manhattan_plots,
    fig_path("matched_unij_manhattan_plots.rds", TRUE)
)
```

```{r}
# CHECKPOINT
matched_unij_manhattan_plots <- list.load(
    fig_path("2024_11_28_matched_unij_manhattan_plots.rds")
)
```

Exporting the manhattan plots

```{r}

qs2 <- function(plot, path, w = 18, h = 14, d = 120) {    
    path <- paste0("matched_unij_", path, "_manhattan.png")
    ggsave(
        fig_path(path, TRUE),
        plot,
        width = w,
        height = h,
        dpi = d
    )
}


# Small function to calculate how tall each manhattan plot
# should be.
heighter <- function(panes) {
    panes * 4/3 + 10/3
}

qs2(matched_unij_manhattan_plots$"a_s1", "a_s1", h = 14, w = 18)
qs2(matched_unij_manhattan_plots$"a_p1", "a_p1", h = 18, w = 18)
qs2(matched_unij_manhattan_plots$"b_s1", "b_s1", h = 4.67)
qs2(matched_unij_manhattan_plots$"b_p1", "b_p1", h = 6)
qs2(matched_unij_manhattan_plots$"c_s1", "c_s1", h = 14)
qs2(matched_unij_manhattan_plots$"c_p1", "c_p1", h = 12.67)
qs2(matched_unij_manhattan_plots$"d_p1", "d_p1", h = 4.67)

```

```{r}
matched_unij_dls <- list(
    "a_s1" = matched_unij_dl_a_s1,
    "a_p1" = matched_unij_dl_a_p1,
    "b_s1" = matched_unij_dl_b_s1,
    "b_p1" = matched_unij_dl_b_p1,
    "c_s1" = matched_unij_dl_c_s1,
    "c_p1" = matched_unij_dl_c_p1,
    "d_p1" = matched_unij_dl_d_p1
)

matched_unij_ols <- list(
    "a_s1" = matched_unij_ol_a_s1,
    "a_p1" = matched_unij_ol_a_p1,
    "b_s1" = matched_unij_ol_b_s1,
    "b_p1" = matched_unij_ol_b_p1,
    "c_s1" = matched_unij_ol_c_s1,
    "c_p1" = matched_unij_ol_c_p1,
    "d_p1" = matched_unij_ol_d_p1
)

list.save(matched_unij_dls, proc_path("matched_unij_dls.rds", TRUE))
list.save(matched_unij_ols, proc_path("matched_unij_ols.rds", TRUE))
```

```{r}
# CHECKPOINT
matched_unij_dls <- list.load(proc_path("2024_12_02_matched_unij_dls.rds"))
matched_unij_ols <- list.load(proc_path("2024_12_02_matched_unij_ols.rds"))
```

```{r}
matched_unij_esm_3c_list <- matched_unij_esm_3c_list[
    c(
        "a_s1",
        "a_p1",
        "b_s1",
        "b_p1",
        "c_s1",
        "c_p1",
        "d_p1"
    )
]

matched_pls <- lapply(
    names(matched_unij_esm_3c_list),
    function(match) {
        pl <- list()
        nrows <- nrow(matched_unij_esm_3c_list[[match]])
        for (row in seq_len(nrows)) {
            p <- auto_plot(
                matched_unij_esm_3c_list[[match]][row, ],
                data_list = matched_unij_dls[[match]],
                target_list = matched_unij_ols[[match]]
            )
            pl[[length(pl) + 1]] <- p
        }
        names(pl) <- paste0("row_", seq_len(nrows))
        return(pl)
    }
)
names(matched_pls) <- names(matched_unij_esm_3c_list)

list.save(matched_pls, fig_path("matched_pls.rds", TRUE))
```

```{r}
# CHECKPOINT
matched_pls <- list.load(fig_path("2024_11_28_matched_pls.rds"))

mtbi_gen_fts_in_long <- read_csv(proc_path("2024_11_26_mtbi_gen_fts_in_long.csv"))
mtbi_gen_fts_out_long <- read_csv(proc_path("2024_11_26_mtbi_gen_fts_out_long.csv"))
```

```{r}
matched_pl_dfs <- lapply(
    names(matched_unij_esm_3c_list),
    function(match) {
        pl <- list()
        nrows <- nrow(matched_unij_esm_3c_list[[match]])
        for (row in seq_len(nrows)) {
            p <- auto_plot(
                matched_unij_esm_3c_list[[match]][row, ],
                data_list = matched_unij_dls[[match]],
                target_list = matched_unij_ols[[match]],
                return_plots = FALSE
            )
            pl[[length(pl) + 1]] <- p
        }
        names(pl) <- paste0("row_", seq_len(nrows))
        return(pl)
    }
)
names(matched_pl_dfs) <- names(matched_pls)
matched_pl_dfs <- unlist(matched_pl_dfs, recursive = FALSE)

matched_pl_tops <- lapply(
    matched_pl_dfs,
    function(x) {
        topologizer(x)
    }
)

matched_pl_gen_fts <- lapply(
    matched_pl_tops,
    function(x) {
        generalizable_features(x, compare_fn_a)
    }
)

mtbi_gen_long <- rbind(
    mtbi_gen_fts_in_long,
    mtbi_gen_fts_out_long
)
mtbi_gen_long <- na.omit(mtbi_gen_long)

matched_pl_gen_fts_long <- lapply(
    matched_pl_gen_fts,
    function(x) {
        long_x <- pivot_longer(
            x,
            cols = -feature,
            names_to = "comparison",
            values_to = "order_unij"
        )
        long_gen_x <- dplyr::left_join(
            mtbi_gen_long,
            long_x,
            by = c("feature", "comparison")
        ) 
        long_gen_x <- dplyr::mutate(
            long_gen_x,
            match = dplyr::case_when(
                is.na(order_unij) ~ 0,
                order != order_unij ~ 0, 
                order == order_unij ~ 1
            )
        )
        return(long_gen_x)
    }
)

matched_pl_gen_fts_long_fair <- lapply(
    matched_pl_gen_fts_long,
    function(x) {
        dplyr::filter(x, !grepl("mtbi", feature))
    }
)

concordance_list <- lapply(
    matched_pl_gen_fts_long_fair,
    function(x) {
        100 * sum(x$"match") / nrow(x)
    }
)

concordance_df <- data.frame(
    unij_set = names(concordance_list),
    concordance = unlist(concordance_list)
) |>
    arrange(desc(concordance))
rownames(concordance_df) <- NULL

write_csv(concordance_df, proc_path("matched_unij_concordance.csv", TRUE))

concordance_df <- read_csv(proc_path("2024_12_02_matched_unij_concordance.csv"))
xtable(concordance_df)

matched_pl_gen_fts
```

Matching by A seemed to be the best one.

```{r}
gen_in_fts <- unique(mtbi_gen_fts_in_long$"feature")
gen_in_fts[startsWith(gen_in_fts, "race_")] <- "race"
gen_in_fts[startsWith(gen_in_fts, "mtbi_mechanism_")] <- "mtbi_mechanism"
gen_in_fts <- unique(gen_in_fts)
gen_out_fts <- unique(mtbi_gen_fts_out_long$"feature")

top_unij_pl <- matched_pls$"a_s1"$"row_2"

top_unij_input_plots <- top_unij_pl[gen_in_fts]
top_unij_outcome_plots <- top_unij_pl[gen_out_fts]

list.save(top_unij_input_plots, proc_path("top_unij_input_plots.rds", TRUE))
list.save(top_unij_outcome_plots, proc_path("top_unij_outcome_plots.rds", TRUE))

###############################################################################

top_unij_input_plots <- list.load(proc_path("2024_12_02_top_unij_input_plots.rds"))
top_unij_outcome_plots <- list.load(proc_path("2024_12_02_top_unij_outcome_plots.rds"))

# qs2 image export helper function
qs2 <- function(plot, path, w = 4, h = 4) {
    path <- paste0("unij_a_s4_", path, ".png")
    ggsave(fig_path(path, TRUE), plot, width = w, height = h)
}

# uni-plot helper function# {{{
uni_plot <- function(plot,
                     ft_name,
                     scale_fill_labels = NULL,
                     ylims = NULL) {
    ###########################################################################
    plot <- plot +
        theme(axis.title.y = element_text(size = 16))
    ###########################################################################
    if (class(plot$layers[[1]]$geom)[[1]] == "GeomBar") {
        plot <- plot + labs(fill = ft_name)
    } else {
        plot <- plot + labs(y = ft_name)
    }
    if (!is.null(scale_fill_labels)) {
        plot <- plot + scale_fill_discrete(labels = scale_fill_labels)
    }
    if (!is.null(ylims)) {
        plot <- plot + ylim(ylims[[1]], ylims[[2]])
    }
    ###########################################################################
    plot <- plot + labs(x = "Cluster") + theme(text = element_text(size = 16))
    return(plot)
}
# }}}

# Matched unij Input Plots
# Brain volumes
brain_volume_plot <- uni_plot(top_unij_input_plots$"brain_volume", expression("Brain Volume "(mm^3)))
brain_volume_plot
qs2(brain_volume_plot, "brain_volume")

# Sex
sex_plot <- uni_plot(top_unij_input_plots$"sex", "Sex", c("F", "M"))
sex_plot
qs2(sex_plot, "sex")

# cort sa
cort_sa_plot <- uni_plot(top_unij_input_plots$"cortical_sa", expression("Cortical Surface Area "(mm^2)))
cort_sa_plot
qs2(cort_sa_plot, "cort_sa")

# Income
household_income_plot <- uni_plot(top_unij_input_plots$"household_income", "Household Income")
household_income_plot
qs2(household_income_plot, "household_income")

# Pubertal Status - Parent Report
pubertal_status_p_plot <- uni_plot(top_unij_input_plots$"pubertal_status_p", "Pubertal Status\n(Parent Report)")
pubertal_status_p_plot
qs2(pubertal_status_p_plot, "pubertal_status_p")

# Programs this year
programs_this_year_plot <- uni_plot(top_unij_input_plots$"programs_this_year", "Programs This Year")
programs_this_year_plot
qs2(programs_this_year_plot, "programs_this_year")

# Non school programs
non_school_programs_plot <- uni_plot(top_unij_input_plots$"non_school_programs", "Non-School Programs This Year", ylims= c(-0.5, 12))
non_school_programs_plot
qs2(non_school_programs_plot, "non_school_programs")

# parent_thought
parent_thought_plot <- uni_plot(top_unij_input_plots$"parent_thought", "Parent Thought", ylims = c(-0.5, 13.5))
parent_thought_plot
qs2(parent_thought_plot, "parent_thought")

# Parent Somatic
parent_somatic_plot <- uni_plot(top_unij_input_plots$"parent_somatic", "Parent Somatic", ylims = c(-0.5, 28))
parent_somatic_plot
qs2(parent_somatic_plot, "parent_somatic")

# Weekday screentime
weekday_screentime_plot <- uni_plot(top_unij_input_plots$"weekday_screentime", "Weekday Screentime (hours)", ylims = c(-0.5, 21))
weekday_screentime_plot
qs2(weekday_screentime_plot, "weekday_screentime")

# parent_antisocial
parent_antisocial_plot <- uni_plot(top_unij_input_plots$"parent_antisocial", "Parent Antisocial")
parent_antisocial_plot
qs2(parent_antisocial_plot, "parent_antisocial")

# parent_aggressive
parent_aggressive_plot <- uni_plot(top_unij_input_plots$"parent_aggressive", "Parent Aggressive")
parent_aggressive_plot
qs2(parent_aggressive_plot, "parent_aggressive")

# Parent depress
parent_depress_plot <- uni_plot(top_unij_input_plots$"parent_depress", "Parent Depress", ylims = c(-0.5, 28))
parent_depress_plot
qs2(parent_depress_plot, "parent_depress")

# parent_anxdep
parent_anxdep_plot <- uni_plot(top_unij_input_plots$"parent_anxdep", "Parent Anxious-Depressed")
parent_anxdep_plot
qs2(parent_anxdep_plot, "parent_anxdep")

# Race
race_plot <- uni_plot(top_unij_input_plots$"race", "Race", scale_fill_labels = c("Black", "Hispanic", "Other", "White"))
race_plot
qs2(race_plot, "race")

# parent_anxdisord
parent_anxdisord_plot <- uni_plot(top_unij_input_plots$"parent_anxdisord", "Parent Anxious", ylims = c(-0.5, 13))
parent_anxdisord_plot
qs2(parent_anxdisord_plot, "parent_anxdisord")

# private_instruction
private_instruction_plot <- uni_plot(top_unij_input_plots$"private_instruction", "Private Activities", ylims = c(-0.5, 9.5))
private_instruction_plot
qs2(private_instruction_plot, "private_instruction")

# weekend_screentime
weekend_screentime_plot <- uni_plot(top_unij_input_plots$"weekend_screentime", "Weekend Screentime (hours)", ylims = c(-0.5, 21))
weekend_screentime_plot
qs2(weekend_screentime_plot, "weekend_screentime")

# parent_withdrawn
parent_withdrawn_plot <- uni_plot(top_unij_input_plots$"parent_withdrawn", "Parent Withdrawn", ylims = c(-0.5, 17))
parent_withdrawn_plot
qs2(parent_withdrawn_plot, "parent_withdrawn")

# parent_avoidant
parent_avoidant_plot <- uni_plot(top_unij_input_plots$"parent_avoidant", "Parent Avoidant", ylims = c(-0.5, 13))
parent_avoidant_plot
qs2(parent_avoidant_plot, "parent_avoidant")

# parent_hyperactive
parent_hyperactive_plot <- uni_plot(top_unij_input_plots$"parent_hyperactive", "Parent Hyperactive", ylims = c(-0.5, 12))
parent_hyperactive_plot
qs2(parent_hyperactive_plot, "parent_hyperactive")

# fmri_cort_subcort_cors
fmri_cort_subcort_cors_plot <- uni_plot(top_unij_input_plots$"fmri_cort_subcort_cors", "fMRI Cort-Subcort Corrs", ylims = c(-0.15, 0.2))
fmri_cort_subcort_cors_plot
qs2(fmri_cort_subcort_cors_plot, "fmri_cort_subcort_cors")

# Parent attention
parent_attention_plot <- uni_plot(top_unij_input_plots$"parent_attention", "Parent Attention")
parent_attention_plot
qs2(parent_attention_plot, "parent_attention")

# parent_perstr
parent_perstr_plot <- uni_plot(top_unij_input_plots$"parent_perstr", "Parent Personal Strength")
parent_perstr_plot
qs2(parent_perstr_plot, "parent_perstr")

# parent_intrusive
parent_intrusive_plot <- uni_plot(top_unij_input_plots$"parent_intrusive", "Parent Intrusive", ylims = c(-0.5, 12))
parent_intrusive_plot
qs2(parent_intrusive_plot, "parent_intrusive")

# family_fight_p
family_fight_p_plot <- uni_plot(top_unij_input_plots$"family_fight_p", "Family Fights\n(Parent Report)", scale_fill_labels = c("No", "Yes"))
family_fight_p_plot
qs2(family_fight_p_plot, "family_fight_p")

# headache_history
headache_history_plot <- uni_plot(top_unij_input_plots$"headache_history", "Headache\nHistory", c("No", "Yes"))
headache_history_plot
qs2(headache_history_plot, "headache_history")

# exercise_time
exercise_time_plot <- uni_plot(top_unij_input_plots$"exercise_time", "Exercise Score", ylims = c(0, 1.1))
exercise_time_plot
qs2(exercise_time_plot, "exercise_time")

# considerate_y
considerate_y_plot <- uni_plot(top_unij_input_plots$"considerate_y", "Considerate\n(Youth Report)", c("No", "Yes"))
considerate_y_plot
qs2(considerate_y_plot, "considerate_y")

# family_temper_p
family_temper_p_plot <- uni_plot(top_unij_input_plots$"family_temper_p", "Family Temper\n(Parent Report)", scale_fill_labels = c("No", "Yes"))
family_temper_p_plot
qs2(family_temper_p_plot, "family_temper_p")

# family_outdo_p
family_outdo_p_plot <- uni_plot(top_unij_input_plots$"family_outdo_p", "Family Outdo\n(Parent Report)", c("No", "Yes"))
family_outdo_p_plot
qs2(family_outdo_p_plot, "family_outdo_p")

# cortical_thickness
cortical_thickness_plot <- uni_plot(top_unij_input_plots$"cortical_thickness", "Cortical Thickness (mm)", ylims = c(2.3, 3.1))
cortical_thickness_plot
qs2(cortical_thickness_plot, "cortical_thickness")

# helps_hurt_p
helps_hurt_p_plot <- uni_plot(top_unij_input_plots$"helps_hurt_p", "Helps Hurt\n(Parent Report)", c("No", "Yes"))
helps_hurt_p_plot
qs2(helps_hurt_p_plot, "helps_hurt_p")

# family_peaceful_p
family_peaceful_p_plot <- uni_plot(top_unij_input_plots$"family_peaceful_p", "Family Peaceful\n(Parent Report)", c("No", "Yes"))
family_peaceful_p_plot
qs2(family_peaceful_p_plot, "family_peaceful_p")

# family_hit_p
family_hit_p_plot <- uni_plot(top_unij_input_plots$"family_hit_p", "Family Hitting\n(Parent Report)", c("No", "Yes"))
family_hit_p_plot
qs2(family_hit_p_plot, "family_hit_p")

# family_angry_p
family_angry_p_plot <- uni_plot(top_unij_input_plots$"family_angry_p", "Family Angry\n(Parent Report)", c("No", "Yes"))
family_angry_p_plot
qs2(family_angry_p_plot, "family_angry_p")

# family_yell_y
family_yell_y_plot <- uni_plot(top_unij_input_plots$"family_yell_y", "Family Yells\n(Youth Report)", c("No", "Yes"))
family_yell_y_plot
qs2(family_yell_y_plot, "family_yell_y")

# pubertal_status_y
pubertal_status_y_plot <- uni_plot(top_unij_input_plots$"pubertal_status_y", "Pubertal Status (Youth Report)")
pubertal_status_y_plot
qs2(pubertal_status_y_plot, "pubertal_status_y")

# helps_hurt_y
helps_hurt_y_plot <- uni_plot(top_unij_input_plots$"helps_hurt_y", "Helps Hurt\n(Youth Report)", c("No", "Yes"))
helps_hurt_y_plot
qs2(helps_hurt_y_plot, "helps_hurt_y")

# family_throw_p
family_throw_p_plot <- uni_plot(top_unij_input_plots$"family_throw_p", "Family Throwing\n(Parent Report)", c("No", "Yes"))
family_throw_p_plot
qs2(family_throw_p_plot, "family_throw_p")


cbcl_anxdep_plot <- uni_plot(top_unij_outcome_plots$"cbcl_anxdep", "Anxious-Depressed", ylims = c(-0.5, 30))
cbcl_withdep_plot <- uni_plot(top_unij_outcome_plots$"cbcl_withdep", "Withdrawn-Depressed", ylims = c(-0.5, 15))
cbcl_somatic_plot <- uni_plot(top_unij_outcome_plots$"cbcl_somatic", "Somatic Problems", ylims = c(-0.5, 17))
cbcl_social_plot <- uni_plot(top_unij_outcome_plots$"cbcl_social", "Social Problems", ylims = c(-0.5, 20))
cbcl_thought_plot <- uni_plot(top_unij_outcome_plots$"cbcl_thought", "Thought Problems", ylims = c(-0.5, 20))
cbcl_attention_plot <- uni_plot(top_unij_outcome_plots$"cbcl_attention", "Attention Problems", ylims = c(-0.5, 22))
cbcl_rulebreak_plot <- uni_plot(top_unij_outcome_plots$"cbcl_rulebreak", "Rule-Breaking Problems", ylims = c(-0.5, 22))
cbcl_aggressive_plot <- uni_plot(top_unij_outcome_plots$"cbcl_aggressive", "Aggression Problems", ylims = c(-0.5, 32))
sds_sleep_plot <- uni_plot(top_unij_outcome_plots$"sds_sleep", "Total Sleep Problems", ylims = c(20, 100))

matched_gen_in_plots <- list(
    "brain_volume" = brain_volume_plot,
    "sex" = sex_plot,
    "cort_sa" = cort_sa_plot,
    "household_income" = household_income_plot,
    "pubertal_status_p" = pubertal_status_p_plot,
    "programs_this_year" = programs_this_year_plot,
    "non_school_programs" = non_school_programs_plot,
    "parent_thought" = parent_thought_plot,
    "parent_somatic" = parent_somatic_plot,
    "weekday_screentime" = weekday_screentime_plot,
    "parent_antisocial" = parent_antisocial_plot,
    "parent_aggressive" = parent_aggressive_plot,
    "parent_depress" = parent_depress_plot,
    "parent_anxdep" = parent_anxdep_plot,
    "race" = race_plot,
    "parent_anxdisord" = parent_anxdisord_plot,
    "private_instruction" = private_instruction_plot,
    "weekend_screentime" = weekend_screentime_plot,
    "parent_withdrawn" = parent_withdrawn_plot,
    "parent_avoidant" = parent_avoidant_plot,
    "parent_hyperactive" = parent_hyperactive_plot,
    "fmri_cort_subcort_cors" = fmri_cort_subcort_cors_plot,
    "parent_attention" = parent_attention_plot,
    "parent_perstr" = parent_perstr_plot,
    "parent_intrusive" = parent_intrusive_plot,
    "family_fight_p" = family_fight_p_plot,
    "headache_history" = headache_history_plot,
    "exercise_time" = exercise_time_plot,
    "considerate_y" = considerate_y_plot,
    "family_temper_p" = family_temper_p_plot,
    "family_outdo_p" = family_outdo_p_plot,
    "cortical_thickness" = cortical_thickness_plot,
    "helps_hurt_p" = helps_hurt_p_plot,
    "family_peaceful_p" = family_peaceful_p_plot,
    "family_hit_p" = family_hit_p_plot,
    "family_angry_p" = family_angry_p_plot,
    "family_yell_y" = family_yell_y_plot,
    "pubertal_status_y" = pubertal_status_y_plot,
    "helps_hurt_y" = helps_hurt_y_plot,
    "family_throw_p" = family_throw_p_plot
)

matched_gen_out_plots <- list(
    "cbcl_anxdep" = cbcl_anxdep_plot,
    "cbcl_withdep" = cbcl_withdep_plot,
    "cbcl_somatic" = cbcl_somatic_plot,
    "cbcl_social" = cbcl_social_plot,
    "cbcl_thought" = cbcl_thought_plot,
    "cbcl_attention" = cbcl_attention_plot,
    "cbcl_rulebreak" = cbcl_rulebreak_plot,
    "cbcl_aggressive" = cbcl_aggressive_plot,
    "sds_sleep" = sds_sleep_plot
)

list.save(matched_gen_in_plots, proc_path("matched_gen_in_plots.rds", TRUE))
list.save(matched_gen_out_plots, proc_path("matched_gen_out_plots.rds", TRUE))
```

# Export them then can move on to supervised learning for goodness sake!

```{r}
matched_gen_in_plots <- list.load(proc_path("2024_11_28_matched_gen_in_plots.rds"))
matched_gen_out_plots <- list.load(proc_path("2024_11_28_matched_gen_out_plots.rds"))
```



















## How does the classifier do?

```{r}
subtype_classifier <- readRDS(model_path("2024_11_28_subtype_classifier.rds"))

# Just FYI
prep_data <- function(df, standardize = FALSE) {
    df <- dplyr::select(df, -"subjectkey")
    df <- dummy_cols(
        df,
        select_columns = "race",
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = TRUE
    )
    ordered_factors <- c(
        "sex",
        "household_income",
        "pubertal_status_p",
        "family_fight_p",
        "family_outdo_p",
        "helps_hurt_p",
        "helpful_y",
        "considerate_y",
        "helps_hurt_y",
        "family_criticize_p",
        "family_outdo_y",
        "family_angry_p",
        "helpful_p",
        "family_throw_p",
        "family_hit_p",
        "family_peaceful_y",
        "family_throw_y",
        "race_black",
        "race_hispanic",
        "race_other" 
    )
    df[ordered_factors] <- lapply(df[ordered_factors], as.ordered)
    if (standardize) {
        df[] <- lapply(df, as.numeric)
        df <- as.data.frame(scale(df))
    }
    if ("cluster" %in% colnames(df)) {
        df$"cluster" <- as.factor(df$"cluster")
    }
    return(df)
}

#mini_df <- unij_matching_df_s1[1:200, ]

library(randomForest)
library(fastDummies)

unij_pred_df_s1 <- unij_matching_df_s1 |> 
    dplyr::mutate(
        cluster = predict(
            subtype_classifier,
            newdata = prep_data(unij_matching_df_s1)
        )
    )

unij_pred_df_s1$cluster |> table() |> prop.table()

unij_pred_cluster_df <- unij_pred_df_s1 |> dplyr::select(subjectkey, cluster)

unij_pred_plot_list <- auto_plot(
    cluster_df = unij_pred_cluster_df,
    data_list = unij_dl_s1,
    target_list = unij_ol_s1 
)

unij_pred_plot_list[for_unij]

unij_pred_all_plots <- wrap_plots(unij_pred_plot_list[for_unij])

ggsave(
    fig_path("unij_pred_all_plots.png", TRUE),
    unij_pred_all_plots,
    width = 45,
    height = 30,
    dpi = 50
)

unij_pred_cluster_df$"cluster" |> table() |> prop.table()

get_cluster_df(mtbi_full_top_3c)$"cluster" |> table() |> prop.table()

rbind(
    unij_pred_cluster_df$"cluster" |> table(),
    get_cluster_df(mtbi_full_top_3c)$"cluster" |> table()
) |> chisq.test()

```


