# Longitudinal analyses

This chapter addresses the following four questions:

1. Was the baseline clustering informative for long-term outcomes?

2. Did the matched uninjured subjects experience more mTBIs by T2 than the other uninjured subjects?

3. Clustering of the longitudinal sample with their baseline vs. their longitudinal data: both equally informative?

4. Classifier built from baseline mTBI data: informative?

## Package loading

```{r}
library(abcdutils)
library(here)
library(dplyr)
library(readr)
library(metasnf)
library(visdat)
library(ggplot2)
library(mice)
library(fastDummies)
library(randomForest)
library(patchwork)
library(tidyr)
library(ComplexHeatmap)

source("abcd/helper_functions.R")
```

## Establishing file paths

```{r}
input_path <- path_maker(here(paste0("data/abcd/inputs")))
core_path <- path_maker(here(paste0("data/abcd/core")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
model_path <- path_maker(here(paste0("data/abcd/results/models")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))

read <- function(path) {
    return(read_csv(input_path(path)))
}

```

```{r}
mtbi_ful_df <- readRDS(proc_path("2025_06_11_mtbi_ful_df.rds"))
all_long_dls_h_ns <- readRDS(proc_path("2025_06_13_all_long_dls_h_ns.rds"))
all_long_dls_h <- readRDS(proc_path("2025_06_12_all_long_dls_h.rds"))
all_dls_h_ns <- readRDS(proc_path("2025_06_11_all_dls_h_no_sibs.rds"))
all_dls_h <- readRDS(proc_path("2025_06_11_all_dls_h.rds"))
```

## Q1: Was the baseline clustering informative for LT outcomes? (Done, June 15)<!-- {{{ -->

```{r}
# Import data
#mtbi_base_df <- readRDS(proc_path("2025_02_13_mtbi_ful_df.rds"))
#all_long_dls <- readRDS(input_path("2025_03_10_all_long_dls.rds"))
#all_dls <- readRDS(input_path("2025_02_10_all_dls.rds"))

mtbi_ful_df <- readRDS(proc_path("2025_06_11_mtbi_ful_df.rds"))
all_long_dls_h_ns <- readRDS(proc_path("2025_06_13_all_long_dls_h_ns.rds"))
all_dls_h_ns <- readRDS(proc_path("2025_06_11_all_dls_h_no_sibs.rds"))
```

```{r}
names(all_long_dls_h_ns)

mtbi_l_dls <- all_long_dls_h_ns$"mtbi_l_dls"
mtbi_l_ols <- all_long_dls_h_ns$"mtbi_l_ols"

# Convert list of data lists into list of data frames for plotting
mtbi_l_dl_dfs <- lapply(mtbi_l_dls, as.data.frame)
mtbi_l_ol_dfs <- lapply(mtbi_l_ols, as.data.frame)

# Tag each data frame with its originating imputation
mtbi_l_dl_dfs <- lapply(
    1:5,
    function(x) {
        mtbi_l_dl_dfs[[x]]$"imputation" <- x
        mtbi_l_dl_dfs[[x]]
    }
)

mtbi_l_ol_dfs <- lapply(
    1:5,
    function(x) {
        mtbi_l_ol_dfs[[x]]$"imputation" <- x
        mtbi_l_ol_dfs[[x]]
    }
)

# Horizontally merge list of data frames
mtbi_l_ol_df <- do.call(rbind, mtbi_l_ol_dfs)
mtbi_l_dl_df <- do.call(rbind, mtbi_l_dl_dfs)
mtbi_l_df <- dplyr::full_join(
    mtbi_l_ol_df,
    mtbi_l_dl_df,
    by = c("uid", "imputation")
)

mtbi_l_wt2_ns <- intersect(unique(mtbi_l_df$"uid"), mtbi_ful_df2$"uid")
mtbi_l_wt2_ns


# Keep track of baseline data before attaching to longitudinal data
colnames(mtbi_ful_df2) <- paste0(colnames(mtbi_ful_df2), "_0")

mtbi_ful_df2 <- mtbi_ful_df2 |>
    dplyr::rename(
        "uid" = "uid_0",
        "cluster" = "cluster_0",
        "sex" = "sex_0",
        "race" = "race_0"
    )
colnames(mtbi_l_df) <- paste0(colnames(mtbi_l_df), "_l")
mtbi_l_df <- mtbi_l_df |>
    dplyr::rename(
        "uid" = "uid_l",
        "imputation" = "imputation_l"
    )

mtbi_ful_df2 <- dplyr::filter(
     mtbi_ful_df2,
     uid %in% mtbi_l_wt2_ns
)
mtbi_l_df <- dplyr::filter(
     mtbi_l_df,
     uid %in% mtbi_l_wt2_ns
)

mtbi_long_changes <- dplyr::full_join(
    mtbi_ful_df2,
    mtbi_l_df,
    by = "uid"
)

original_names <- gsub("_0", "", colnames(mtbi_ful_df2)[-c(1:2)])
original_names <- original_names[!grepl("mtbi", original_names)]
replace_names <- original_names[!grepl("race", original_names)]
replace_names <- replace_names[!grepl("sex", replace_names)]
for (name in replace_names) {
    print(name)
    long_val <- mtbi_long_changes[[paste0(name, "_l")]]
    base_val <- mtbi_long_changes[[paste0(name, "_0")]]
    mtbi_long_changes[[paste0(name, "_d")]] <- long_val - base_val
}
mtbi_long_changes$"cluster" <- as.factor(mtbi_long_changes$"cluster")

saveRDS(mtbi_long_changes, proc_path("mtbi_long_changes.rds", TRUE))

mtbi_long_changes <- readRDS(proc_path("2025_06_13_mtbi_long_changes.rds"))
```

```{r}
# Some plotting functions
gg_long_cor_imp <- function(df, feature, long = TRUE) {
    f1 <- paste0(feature, "_0")
    if (long) {
        f2 <- paste0(feature, "_l")
    } else {
        f2 <- paste0(feature, "_d")
    }
    plot <- ggplot(
        df,
        aes(x = .data[[f1]], y = .data[[f2]])
    ) +
        geom_jitter(alpha = 0.2) +
        facet_wrap(~ imputation) +
        theme_bw()
    return(plot)
}

gg_long_cor <- function(df, feature, long = TRUE) {
    df <- dplyr::filter(df, imputation == 1)
    f1 <- paste0(feature, "_0")
    if (long) {
        f2 <- paste0(feature, "_l")
    } else {
        f2 <- paste0(feature, "_d")
    }
    plot <- ggplot(
        df,
        aes(
            x = .data[[f1]],
            y = .data[[f2]],
            colour = as.factor(cluster)
        )
    ) +
        geom_jitter(alpha = 0.5, height = 0.1, width = 0.1) +
        geom_smooth(method = "lm") +
        theme_bw() +
        labs(colour = "C")
    return(plot)
}

#pubertal_status_y_plot <- gg_long_cor(mtbi_long_changes, "pubertal_status_y")
#household_income_plot <- gg_long_cor(mtbi_long_changes, "household_income")
#extracurriculars_plot <- gg_long_cor(mtbi_long_changes, "extracurriculars")
#parent_perstr_plot <- gg_long_cor(mtbi_long_changes, "parent_perstr")
#activities_last_year_plot <- gg_long_cor(mtbi_long_changes, "activities_last_year")
#considerate_y_plot <- gg_long_cor(mtbi_long_changes, "considerate_y")
## looks kind of like an interaction?
#school_activities_plot <- gg_long_cor(mtbi_long_changes, "school_activities")
#weekend_screentime_plot <- gg_long_cor(mtbi_long_changes, "weekend_screentime")
#family_throw_y_plot <- gg_long_cor(mtbi_long_changes, "family_throw_y")
#
#significant_long_cor_plot <- pubertal_status_y_plot +
#household_income_plot +
#extracurriculars_plot +
#parent_perstr_plot +
#activities_last_year_plot +
#considerate_y_plot +
#school_activities_plot +
#weekend_screentime_plot +
#family_throw_y_plot
#
#significant_long_cor_plot
#
#ggsave(
#    fig_path("significant_long_cor_plot.png", TRUE),
#    significant_long_cor_plot,
#    width = 15,
#    height = 10
#)

cbcl_anxdep_plot <- gg_long_cor(mtbi_long_changes, "cbcl_anxdep", 0)
cbcl_withdep_plot <- gg_long_cor(mtbi_long_changes, "cbcl_withdep", 0)
cbcl_somatic_plot <- gg_long_cor(mtbi_long_changes, "cbcl_somatic", 0)
cbcl_social_plot <- gg_long_cor(mtbi_long_changes, "cbcl_social", 0)
cbcl_thought_plot <- gg_long_cor(mtbi_long_changes, "cbcl_thought", 0)
cbcl_attention_plot <- gg_long_cor(mtbi_long_changes, "cbcl_attention", 0)
cbcl_rulebreak_plot <- gg_long_cor(mtbi_long_changes, "cbcl_rulebreak", 0)
cbcl_aggressive_plot <- gg_long_cor(mtbi_long_changes, "cbcl_aggressive", 0)
sds_sleep_plot <- gg_long_cor(mtbi_long_changes, "sds_sleep", 0)

outcome_long_cor_plots <- wrap_plots(
    list(
        cbcl_anxdep_plot,
        cbcl_withdep_plot,
        cbcl_somatic_plot,
        cbcl_social_plot,
        cbcl_thought_plot,
        cbcl_attention_plot,
        cbcl_rulebreak_plot,
        cbcl_aggressive_plot,
        sds_sleep_plot
    )
)

outcome_long_cor_plots

ggsave(
    fig_path("outcome_long_cor_plots.png", TRUE),
    outcome_long_cor_plots,
    width = 15,
    height = 10
)

cbcl_anxdep_plot2 <- gg_long_cor(mtbi_long_changes, "cbcl_anxdep")
cbcl_withdep_plot2 <- gg_long_cor(mtbi_long_changes, "cbcl_withdep")
cbcl_somatic_plot2 <- gg_long_cor(mtbi_long_changes, "cbcl_somatic")
cbcl_social_plot2 <- gg_long_cor(mtbi_long_changes, "cbcl_social")
cbcl_thought_plot2 <- gg_long_cor(mtbi_long_changes, "cbcl_thought")
cbcl_attention_plot2 <- gg_long_cor(mtbi_long_changes, "cbcl_attention")
cbcl_rulebreak_plot2 <- gg_long_cor(mtbi_long_changes, "cbcl_rulebreak")
cbcl_aggressive_plot2 <- gg_long_cor(mtbi_long_changes, "cbcl_aggressive")

sds_sleep_plot2 <- gg_long_cor(mtbi_long_changes, "sds_sleep")

outcome_long_cor_plots_2 <- wrap_plots(
    list(
        cbcl_anxdep_plot2,
        cbcl_withdep_plot2,
        cbcl_somatic_plot2,
        cbcl_social_plot2,
        cbcl_thought_plot2,
        cbcl_attention_plot2,
        cbcl_rulebreak_plot2,
        cbcl_aggressive_plot2,
        sds_sleep_plot2
    )
)

outcome_long_cor_plots_2

ggsave(
    fig_path("outcome_long_cor_plots_2.png", TRUE),
    outcome_long_cor_plots_2,
    width = 15,
    height = 10
)


gg_long_cor(mtbi_long_changes, "cbcl_anxdep", 0)

gg_long_cor(mtbi_long_changes, "cbcl_withdep")

gg_long_cor(mtbi_long_changes, "cbcl_somatic")

gg_long_cor(mtbi_long_changes, "cbcl_anxdep")

gg_long_cor(mtbi_long_changes, "cbcl_withdep")

gg_long_cor(mtbi_long_changes, "cbcl_somatic")

gg_long_cor(mtbi_long_changes, "cbcl_social")

gg_long_cor(mtbi_long_changes, "cbcl_thought")

gg_long_cor(mtbi_long_changes, "cbcl_attention")

gg_long_cor(mtbi_long_changes, "cbcl_rulebreak")

gg_long_cor(mtbi_long_changes, "cbcl_aggressive")

gg_long_cor(mtbi_long_changes, "sds_sleep")

gg_long_cor(mtbi_long_changes, "cbcl_withdep", 0)

gg_long_cor(mtbi_long_changes, "cbcl_somatic", 0)

gg_long_cor(mtbi_long_changes, "cbcl_anxdep", 0)

gg_long_cor(mtbi_long_changes, "cbcl_withdep", 0)

gg_long_cor(mtbi_long_changes, "cbcl_somatic", 0)

gg_long_cor(mtbi_long_changes, "cbcl_social", 0)

gg_long_cor(mtbi_long_changes, "cbcl_thought", 0)

gg_long_cor(mtbi_long_changes, "cbcl_attention", 0)

gg_long_cor(mtbi_long_changes, "cbcl_rulebreak", 0)

gg_long_cor(mtbi_long_changes, "cbcl_aggressive", 0)

gg_long_cor(mtbi_long_changes, "sds_sleep", 0)

gg_long_cor(mtbi_long_changes, "parent_perstr", 0)

gg_long_cor(mtbi_long_changes, "activities_last_year")

gg_long_cor(mtbi_long_changes, "pubertal_status_y")

gg_long_cor(mtbi_long_changes, "pubertal_status_p")

gg_long_cor(mtbi_long_changes, "school_activities")

gg_long_cor(mtbi_long_changes, "weekend_screentime")

gg_long_cor(mtbi_long_changes, "household_income")

cor_mat <- mtbi_long_changes |>
    dplyr::select(-uid, -mtbi_mechanism_0, -race_l) |>
    dplyr::rename("race" = "race_0") |>
    dplyr::mutate(cluster = as.numeric(cluster)) |>
    dummy_cols(
        select_columns = "race",
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = TRUE
    ) |>
    cor()

cor_mat[!grepl("_d$|_l$", colnames(cor_mat)), grepl("_d$", colnames(cor_mat))] |>
    Heatmap()

cor_mat["cluster", grepl("_d$", colnames(cor_mat))] |>
    Heatmap()

lm_long_fit <- function(df, feature) {
    models <- list(
      lm(as.formula(paste0(feature, "_l ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 1)),
      lm(as.formula(paste0(feature, "_l ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 2)),
      lm(as.formula(paste0(feature, "_l ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 3)),
      lm(as.formula(paste0(feature, "_l ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 4)),
      lm(as.formula(paste0(feature, "_l ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 5))
    )
    pooled_results <- pool(as.mira(models))
    return(summary(pooled_results))
}

replace_names

pval_df <- data.frame()
for (feature in replace_names) {
    model <- lm_long_fit(mtbi_long_changes, feature)
    pval_df <- rbind(
        pval_df,
        data.frame(
            feature = c(feature, feature),
            compare = c("c1_vs_c2", "c1_vs_c3"),
            p = c(model$"p.value"[3], model$"p.value"[4])
        )
    )
    if (min(model$"p.value"[3]) < 0.05) {
        cat("\n", feature, signif(model$"p.value"[3], 2), "\n")
        print(model)
    }
}
pval_df$"padj" <- p.adjust(pval_df$"p", method = "fdr")

pval_df |>
    dplyr::filter(padj < 0.05) |>
    dplyr::select(-p) |>
    dplyr::mutate(padj = format(padj, scientific = FALSE, digits = 2)) |>
    dplyr::arrange(padj)

# None are significant
cbcl_anxdep_p <- lm_long_fit(mtbi_long_changes, "cbcl_anxdep")
cbcl_withdep_p <- lm_long_fit(mtbi_long_changes, "cbcl_withdep")
cbcl_somatic_p <- lm_long_fit(mtbi_long_changes, "cbcl_somatic")
cbcl_social_p <- lm_long_fit(mtbi_long_changes, "cbcl_social")
cbcl_thought_p <- lm_long_fit(mtbi_long_changes, "cbcl_thought")
cbcl_attention_p <- lm_long_fit(mtbi_long_changes, "cbcl_attention")
cbcl_rulebreak_p <- lm_long_fit(mtbi_long_changes, "cbcl_rulebreak")
cbcl_aggressive_p <- lm_long_fit(mtbi_long_changes, "cbcl_aggressive")
sds_sleep_p <- lm_long_fit(mtbi_long_changes, "sds_sleep")

p_list <- list(
    "cbcl_anxdep" = cbcl_anxdep_p,
    "cbcl_withdep" = cbcl_withdep_p,
    "cbcl_somatic" = cbcl_somatic_p,
    "cbcl_social" = cbcl_social_p,
    "cbcl_thought" = cbcl_thought_p,
    "cbcl_attention" = cbcl_attention_p,
    "cbcl_rulebreak" = cbcl_rulebreak_p,
    "cbcl_aggressive" = cbcl_aggressive_p,
    "sds_sleep" = sds_sleep_p
)

sds_sleep_p

p_list_short <- lapply(
    names(p_list),
    function(x) {
        p_list[[x]] <- dplyr::select(p_list[[x]], term, p.value)
        colnames(p_list[[x]]) <- c("term", x)
        p_list[[x]][3:4, ]
    }
)
p_df <- as.data.frame(t(merge_df_list(p_list_short, uid = "term")))
p_df$"term" <- rownames(p_df)
rownames(p_df) <- NULL
p_df <- p_df[-1, ]
colnames(p_df) <- c("cluster_2_p", "cluster_3_p", "term")
p_df <- dplyr::select(p_df, term, everything())
p_df$"cluster_2_p" <- as.numeric(p_df$"cluster_2_p")
p_df$"cluster_3_p" <- as.numeric(p_df$"cluster_3_p")
p_df |>
    knitr::kable(format = "markdown", digits = 2) |>
    writeLines(proc_path("p_values_of_cluster.txt", TRUE))

# An LRT-based approach
lm_long_lrt_fit <- function(df, feature) {
    base_model <- lm(as.formula(paste0(feature, "_l ~ ", feature, "_0")), data = filter(df, imputation == 1))
    full_model <- lm(as.formula(paste0(feature, "_l ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 1))
    return(anova(base_model, full_model))
}

lm_long_lrt_fit(mtbi_long_changes, "cbcl_anxdep")
```

Cluster is never a significant feature in predicting longitudinal outcome given baseline outcome.
<!-- }}} -->

## Longitudinal trajectory check 1<!-- {{{ -->

In this section, I first adjust CBCL values by age and sex, bin them according to their quantiles within the entire ABCD dataset, and then check to see how profiles based on those bins differ across the clusters.

```{r}
mtbi_long_changes <- readRDS(proc_path("2025_06_13_mtbi_long_changes.rds"))

# Separating by time
df0 <- mtbi_long_changes |>
    dplyr::select(
        uid,
        cluster,
        imputation,
        dplyr::starts_with("cbcl"),
        dplyr::starts_with("sds")
    ) |>
    dplyr::select(
        uid,
        cluster,
        imputation,
        dplyr::ends_with("0")
    ) |>
    dplyr::mutate(t = "0")
colnames(df0) <- gsub("_0", "", colnames(df0))

dfl <- mtbi_long_changes |>
    dplyr::select(
        uid,
        cluster,
        imputation,
        dplyr::starts_with("cbcl"),
        dplyr::starts_with("sds")
    ) |>
    dplyr::select(
        uid,
        cluster,
        imputation,
        dplyr::ends_with("l")    
    ) |>
    dplyr::mutate(t = "2")
colnames(dfl) <- gsub("_l", "", colnames(dfl))

import <- function(path) {
    return(abcdutils::abcd_load(core_path(path)))
}

mh_p_cbcl <- import("mental-health/mh_p_cbcl.csv")
gish_p_gi <- import("gender-identity-sexual-health/gish_p_gi.csv")
abcd_y_lt <- import("abcd-general/abcd_y_lt.csv")
ph_p_sds <- import("physical-health/ph_p_sds.csv")

all_sex_0 <- get_sex(gish_p_gi, t = 0) |>
    dplyr::mutate(uid = paste0("uid_", subjectkey)) |>
    dplyr::select(-subjectkey)
all_cbcl_0 <- get_cbcl_syndrome_scale(mh_p_cbcl, t = 0) |>
    dplyr::mutate(uid = paste0("uid_", subjectkey)) |>
    dplyr::select(-subjectkey)
all_sds_0 <- get_sleep_disturbance(ph_p_sds, t = 0) |>
    dplyr::mutate(uid = paste0("uid_", subjectkey)) |>
    dplyr::select(-subjectkey)
all_age_0 <- get_interview_age(abcd_y_lt = abcd_y_lt, t = 0, as_years = FALSE) |>
    dplyr::mutate(uid = paste0("uid_", subjectkey)) |>
    dplyr::rename("age" = "interview_age") |>
    dplyr::select(-subjectkey)

all_sex_l <- all_sex_0
all_cbcl_l <- get_cbcl_syndrome_scale(mh_p_cbcl, t = 2) |>
    dplyr::mutate(uid = paste0("uid_", subjectkey)) |>
    dplyr::select(-subjectkey)
all_sds_l <- get_sleep_disturbance(ph_p_sds, t = 2) |>
    dplyr::mutate(uid = paste0("uid_", subjectkey)) |>
    dplyr::select(-subjectkey)
all_age_l <- get_interview_age(abcd_y_lt = abcd_y_lt, t = 2, as_years = FALSE) |>
    dplyr::mutate(uid = paste0("uid_", subjectkey)) |>
    dplyr::rename("age" = "interview_age") |>
    dplyr::select(-subjectkey)

source("abcd/helper_functions.R")

all_out_0 <- dplyr::inner_join(
    all_sex_0,
    all_cbcl_0,
    by = "uid"
) |>
    dplyr::inner_join(
        all_age_0,
        by = "uid"
    ) |>
    dplyr::inner_join(
        all_sds_0,
        by = "uid"
    ) |>
    na.omit() |>
    dplyr::filter(sex %in% c("F", "M")) |>
    dplyr::rename(
        "cbcl_anxdep" = "cbcl_scr_syn_anxdep_r",
        "cbcl_withdep" = "cbcl_scr_syn_withdep_r",
        "cbcl_somatic" = "cbcl_scr_syn_somatic_r",
        "cbcl_social" = "cbcl_scr_syn_social_r",
        "cbcl_thought" = "cbcl_scr_syn_thought_r",
        "cbcl_attention" = "cbcl_scr_syn_attention_r",
        "cbcl_rulebreak" = "cbcl_scr_syn_rulebreak_r",
        "cbcl_aggressive" = "cbcl_scr_syn_aggressive_r",
        "sds_sleep" = "sds_p_ss_total"
    ) |>
    dplyr::mutate(cluster = sex)

all_out_l <- dplyr::inner_join(
    all_sex_l,
    all_cbcl_l,
    by = "uid"
) |>
    dplyr::inner_join(
        all_age_l,
        by = "uid"
    ) |>
    dplyr::inner_join(
        all_sds_l,
        by = "uid"
    ) |>
    na.omit() |>
    dplyr::filter(sex %in% c("F", "M")) |>
    dplyr::rename(
        "cbcl_anxdep" = "cbcl_scr_syn_anxdep_r",
        "cbcl_withdep" = "cbcl_scr_syn_withdep_r",
        "cbcl_somatic" = "cbcl_scr_syn_somatic_r",
        "cbcl_social" = "cbcl_scr_syn_social_r",
        "cbcl_thought" = "cbcl_scr_syn_thought_r",
        "cbcl_attention" = "cbcl_scr_syn_attention_r",
        "cbcl_rulebreak" = "cbcl_scr_syn_rulebreak_r",
        "cbcl_aggressive" = "cbcl_scr_syn_aggressive_r",
        "sds_sleep" = "sds_p_ss_total"
    ) |>
    dplyr::mutate(cluster = sex)

# top, bottom, mid quantiles - do profiles shift?

# Constructing adjustment models for each outcome for each timepoint
out_cols <- grep("^(cbcl|sds)", names(all_out_0), value = TRUE)

all_out_0$"t" <- 0
all_out_l$"t" <- 2

all_out <- rbind(all_out_0, all_out_l)

models <- lapply(
    out_cols,
    function(col) {
        formula <- as.formula(paste(col, "~ age + sex + t"))
        lm(formula, data = all_out)
    }
)
names(models) <- out_cols

#models_0 <- lapply(
#    out_cols,
#    function(col) {
#        formula <- as.formula(paste(col, "~ age + sex"))
#        lm(formula, data = all_out_0)
#    }
#)
#names(models_0) <- out_cols
#
#models_l <- lapply(
#    out_cols,
#    function(col) {
#        formula <- as.formula(paste(col, "~ age + sex"))
#        lm(formula, data = all_out_l)
#    }
#)
#names(models_l) <- out_cols

df0_w_covs <- df0 |>
    as.data.frame() |>
    dplyr::inner_join(all_sex_0) |>
    dplyr::inner_join(all_age_0)

dfl_w_covs <- dfl |>
    as.data.frame() |>
    dplyr::inner_join(all_sex_l) |>
    dplyr::inner_join(all_age_l)

df_w_covs <- rbind(df0_w_covs, dfl_w_covs)

df_w_covs$"t" <- as.numeric(df_w_covs$"t")

#df0_w_covs

#df0_w_covs_adj <- df0_w_covs
#dfl_w_covs_adj <- dfl_w_covs

#dfl_w_covs_adj |> head()
#
dfl_w_covs |> head()

#for (col in out_cols) {
#  # Predicted values based on reference model
#  predicted <- predict(models_0[[col]], newdata = df0_w_covs)
#  # Residuals: actual - predicted
#  df0_w_covs_adj[[paste0("adj_", col)]] <- df0_w_covs[[col]] - predicted
#}
#
#for (col in out_cols) {
#  # Predicted values based on reference model
#  predicted <- predict(models_l[[col]], newdata = dfl_w_covs)
#  # Residuals: actual - predicted
#  dfl_w_covs_adj[[paste0("adj_", col)]] <- dfl_w_covs[[col]] - predicted
#}

#for (col in out_cols) {
#  # Predicted values based on reference model
#  predicted <- predict(models_l[[col]], newdata = dfl_w_covs)
#  # Residuals: actual - predicted
#  dfl_w_covs_adj[[paste0("adj_", col)]] <- dfl_w_covs[[col]] - predicted
#}

#df_adj <- rbind(df0_w_covs_adj, dfl_w_covs_adj)

#saveRDS(df0_w_covs_adj, proc_path("df0_w_covs_adj.rds", TRUE))
#saveRDS(dfl_w_covs_adj, proc_path("dfl_w_covs_adj.rds", TRUE))

#saveRDS(df_adj, proc_path("df_adj.rds", TRUE))

# Storing the quantiles

#all_out_0_adj <- all_out_0
#all_out_l_adj <- all_out_l

#for (col in out_cols) {
#  # Predicted values based on reference model
#  predicted <- predict(models_0[[col]], newdata = all_out_0)
#  # Residuals: actual - predicted
#  all_out_0_adj[[paste0("adj_", col)]] <- all_out_0[[col]] - predicted
#}
#
#for (col in out_cols) {
#  # Predicted values based on reference model
#  predicted <- predict(models_l[[col]], newdata = all_out_l)
#  # Residuals: actual - predicted
#  all_out_l_adj[[paste0("adj_", col)]] <- all_out_l[[col]] - predicted
#}

all_out_adj <- all_out

for (col in out_cols) {
  # Predicted values based on reference model
  predicted <- predict(models[[col]], newdata = all_out)
  # Residuals: actual - predicted
  all_out_adj[[paste0("adj_", col)]] <- all_out[[col]] - predicted
}

# all out adj is residualized against age, sex, and timepoint
# enables quantile comparisons across timepoints as well
quantile(all_out_adj$"adj_sds_sleep", c(0, 0.33, 0.66, 1))

adj_df_w_covs <- df_w_covs

for (col in out_cols) {
  # Predicted values based on reference model
  predicted <- predict(models[[col]], newdata = df_w_covs)
  # Residuals: actual - predicted
  adj_df_w_covs[[paste0("adj_", col)]] <- df_w_covs[[col]] - predicted
}

# Reference adjusted data for quantiles
saveRDS(all_out_adj, proc_path("all_out_adj.rds", TRUE))

# Actual mTBI data
saveRDS(adj_df_w_covs, proc_path("df_w_covs_adj.rds", TRUE))
```

```{r}

all_out_adj <- readRDS(proc_path("2025_07_08_all_out_adj.rds"))

adj_df_w_covs <- readRDS(proc_path("2025_07_08_df_w_covs_adj.rds"))

all_out_adj |> colnames()


#df0_adj <- readRDS(proc_path("2025_07_08_df0_w_covs_adj.rds"))
#dfl_adj <- readRDS(proc_path("2025_07_08_dfl_w_covs_adj.rds"))
#
#df_adj <- readRDS(proc_path("2025_07_08_df_adj.rds"))

out_cols
#------------------------------------------------------------------------------
#library(dplyr)
library(purrr)

# 1. Vector of CBCL columns
cbcl_cols <- paste0("adj_", out_cols[1:8])
sds_cols <- "adj_sds_sleep"

quantile_cbcl <- map(
    cbcl_cols,
    function(col) {
        data <- all_out_adj[[col]]
        list(
            high = quantile(data, 0.93)
        )
    }
) |>
    set_names(cbcl_cols)

quantile_sds <- list(
    high = quantile(all_out_adj$"adj_sds_sleep", 0.75)
)

cbcl_bin_with_thresholds <- function(x, thresholds) {
  case_when(
    x >= thresholds$high ~ "high",
    x <  thresholds$high ~ "low",
    TRUE ~ NA_character_
  )
}

sds_bin_with_thresholds <- function(x, thresholds) {
  case_when(
    x >= thresholds$high ~ "high",
    x <  thresholds$high ~ "low",
    TRUE ~ NA_character_
  )
}

t0_data <- adj_df_w_covs |> dplyr::filter(t == 0)
t2_data <- adj_df_w_covs |> dplyr::filter(t == 2)

for (col in cbcl_cols) {
    new_col <- paste0(col, "_bin")
    t0_data[[paste0(new_col, "_t0")]] <- cbcl_bin_with_thresholds(
        t0_data[[col]],
        quantile_cbcl[[col]]
    )
    t2_data[[paste0(new_col, "_t2")]] <- cbcl_bin_with_thresholds(
        t2_data[[col]],
        quantile_cbcl[[col]]
    )
}
for (col in sds_cols) {
    new_col <- paste0(col, "_bin")
    t0_data[[paste0(new_col, "_t0")]] <- sds_bin_with_thresholds(
        t0_data[[col]],
        quantile_sds
    )
    t2_data[[paste0(new_col, "_t2")]] <- sds_bin_with_thresholds(
        t2_data[[col]],
        quantile_sds
    )
}

t0_bin_cols <- t0_data |> dplyr::select(uid, cluster, imputation, dplyr::ends_with("bin_t0"))
t2_bin_cols <- t2_data |> dplyr::select(uid, cluster, imputation, dplyr::ends_with("bin_t2"))

all_bin_df <- dplyr::full_join(
    t0_bin_cols,
    t2_bin_cols, by = c("uid", "cluster", "imputation")
)

out_cols

cat_df <- all_bin_df |>
    dplyr::mutate(
        cbcl_anxdep_cat = paste0(adj_cbcl_anxdep_bin_t0, "_", adj_cbcl_anxdep_bin_t2),
        cbcl_withdep_cat = paste0(adj_cbcl_withdep_bin_t0, "_", adj_cbcl_withdep_bin_t2),
        cbcl_somatic_cat = paste0(adj_cbcl_somatic_bin_t0, "_", adj_cbcl_somatic_bin_t2),
        cbcl_social_cat = paste0(adj_cbcl_social_bin_t0, "_", adj_cbcl_social_bin_t2),
        cbcl_thought_cat = paste0(adj_cbcl_thought_bin_t0, "_", adj_cbcl_thought_bin_t2),
        cbcl_attention_cat = paste0(adj_cbcl_attention_bin_t0, "_", adj_cbcl_attention_bin_t2),
        cbcl_rulebreak_cat = paste0(adj_cbcl_rulebreak_bin_t0, "_", adj_cbcl_rulebreak_bin_t2),
        cbcl_aggressive_cat = paste0(adj_cbcl_aggressive_bin_t0, "_", adj_cbcl_aggressive_bin_t2),
        sds_sleep_cat = paste0(adj_sds_sleep_bin_t0, "_", adj_sds_sleep_bin_t2)
    ) |>
    dplyr::select(uid, cluster, imputation, dplyr::ends_with("cat"))

adj_df_cat_annotated <- dplyr::full_join(
    adj_df_w_covs,
    cat_df,
    by = c("uid", "cluster", "imputation")
)

saveRDS(
    adj_df_cat_annotated,
    proc_path("adj_df_cat_annotated.rds", TRUE)
)

adj_df_cat_annotated <- readRDS(proc_path("2025_07_08_adj_df_cat_annotated.rds"))

colnames(adj_df_cat_annotated)

adj_out_cols <- paste0("adj_", out_cols)

colnames(adj_df_cat_annotated)

out_cols

quantile_plot <- function(df, feature, ref_df, probs, mode = "high") {
    if (mode == "high") {
        vec <- c("high_high", "high_low")
        custom_scale <- scale_colour_manual(
            values = c("high_high" = "#5D3A9B", "high_low" = "#E66100"),
            labels = c("high_high" = "High to High", "high_low" = "High to Low")
        )
    } else {
        vec <- c("low_high", "low_low")
        custom_scale <- scale_colour_manual(
            values = c("low_high" = "#F8766D", "low_low" = "#00BFC4"),
            labels = c("low_high" = "Low to High", "low_low" = "Low to Low")
        )
    }
    pd <- position_dodge(width = 0.2)
    quantiles <- quantile(ref_df[[feature]], probs = probs)
    cat_name <- paste0(gsub("adj_", "", feature), "_cat")
    yvals <- as.numeric(quantiles)
    tidy_ft_name <- gsub("adj_", "", feature)
    tidy_ft_name <- gsub("cbcl_", "CBCL ", tidy_ft_name)
    tidy_ft_name <- gsub("anxdep", "Anxious/Depressed", tidy_ft_name)
    tidy_ft_name <- gsub("withdep", "Withdrawn/Depressed", tidy_ft_name)
    tidy_ft_name <- gsub("somatic", "Somatic ", tidy_ft_name)
    tidy_ft_name <- gsub("social", "Social Problems", tidy_ft_name)
    tidy_ft_name <- gsub("thought", "Thought Problems", tidy_ft_name)
    tidy_ft_name <- gsub("attention", "Attention Problems", tidy_ft_name)
    tidy_ft_name <- gsub("rulebreak", "Rule-Breaking Behavior", tidy_ft_name)
    tidy_ft_name <- gsub("aggressive", "Aggressive Behavior", tidy_ft_name)
    tidy_ft_name <- gsub("sds_sleep", "Sleep Disturbance", tidy_ft_name)
    # Data analysis 
    df |>
        dplyr::filter(imputation == 1) |>
        dplyr::filter(.data[[cat_name]] %in% vec) |>
        ggplot(
            aes(
                x = factor(t),
                y = .data[[feature]],
                group = uid,
                colour = .data[[cat_name]],
            ),
        ) +
        geom_point(size = 3, position = pd, alpha = 0.5) +
        geom_line(position = pd, alpha = 0.5) +
        geom_hline(
            yintercept = yvals,
            colour = "black"
        ) +
        labs(x = "Time", y = tidy_ft_name, colour = "Transition") + 
        facet_wrap(~ cluster) +
        theme_classic() + 
        custom_scale
}

```


```{r}
library(multcomp)

check_cat <- function(df, feature, imp) {
    cat_name <- paste0(gsub("adj_", "", feature), "_cat")
    df_low <- df |>
        dplyr::filter(
            imputation == imp,
            t == 0,
            .data[[cat_name]] %in% c("low_low", "low_high")
        ) |>
        dplyr::mutate(
            stayed_low = ifelse(.data[[cat_name]] == "low_low", 1, 0)
        )
    df_high <- df |>
        dplyr::filter(
            imputation == imp,
            t == 0,
            .data[[cat_name]] %in% c("high_low", "high_high")
        ) |>
        dplyr::mutate(
            stayed_high = ifelse(.data[[cat_name]] == "high_high", 1, 0)
        )
    glm_low <- glm(stayed_low ~ factor(cluster), data = df_low, family = "binomial")
    glm_high <- glm(stayed_high ~ factor(cluster), data = df_high, family = "binomial")
    p_stayed_low <- summary(glht(glm_low, linfct = mcp(`factor(cluster)` = "Tukey")), test = adjusted("none"))$"test"$"pvalues"
    p_stayed_high <- summary(glht(glm_high, linfct = mcp(`factor(cluster)` = "Tukey")), test = adjusted("none"))$"test"$"pvalues"
    low_p_df <- dplyr::rename(as.data.frame(p_stayed_low), "p" = "p_stayed_low")
    low_p_df$"comparison" <- rownames(low_p_df)
    low_p_df$"type" <- "stayed_low"
    low_p_df$"feature" <- gsub("adj_", "", feature)
    rownames(low_p_df) <- NULL
    high_p_df <- dplyr::rename(as.data.frame(p_stayed_high), "p" = "p_stayed_high")
    high_p_df$"comparison" <- rownames(high_p_df)
    high_p_df$"type" <- "stayed_high"
    high_p_df$"feature" <- gsub("adj_", "", feature)
    rownames(high_p_df) <- NULL
    p_df <- rbind(low_p_df, high_p_df)
    stayed_low_plot <- df_low |>
        count(cluster, .data[[cat_name]]) |>
        group_by(cluster) |>
        mutate(prop = n / sum(n)) |>
        ggplot(aes(x = cluster, y = prop, fill = .data[[cat_name]])) +
        geom_col(position = "fill") +  # stacked proportion bars
        theme_classic() +
        labs(y = "Proportion", x = "Cluster", fill = "Transition") +
        scale_fill_manual(
            values = c("low_high" = "#F8766D", "low_low" = "#00BFC4"),
            labels = c("low_high" = "Low to High", "low_low" = "Low to Low")
        )
    stayed_high_plot <- df_high |>
        count(cluster, .data[[cat_name]]) |>
        group_by(cluster) |>
        mutate(prop = n / sum(n)) |>
        ggplot(aes(x = cluster, y = prop, fill = .data[[cat_name]])) +
        geom_col(position = "fill") +  # stacked proportion bars
        theme_classic() +
        labs(y = "Proportion", x = "Cluster", fill = "Transition") +
        scale_fill_manual(
            values = c("high_high" = "#5D3A9B", "high_low" = "#E66100"),
            labels = c("high_high" = "High to High", "high_low" = "High to Low")
        )
    return(list(stayed_low_plot, stayed_high_plot, p_df))
}

p_df <- data.frame()
pl <- list()
for (x in 1:9) {
    prop <- check_cat(adj_df_cat_annotated, adj_out_cols[[x]], 1)
    p_df <- rbind(p_df, dplyr::mutate(prop[[3]], x = x))
    thresh <- if (x < 9) (0.93) else (0.75)
    low <- quantile_plot(adj_df_cat_annotated, adj_out_cols[[x]], all_out_adj, thresh, "low")
    high <- quantile_plot(adj_df_cat_annotated, adj_out_cols[[x]], all_out_adj, thresh, "high")
    pl[[x]] <- wrap_plots(list(low, high, prop[[1]], prop[[2]]))
    print(adj_out_cols[[x]])
    ggsave(
        plot = pl[[x]],
        filename = fig_path(
            paste0(
                gsub("adj_", "", adj_out_cols[[x]]),
                "_transition_plot.png"
            ),
            TRUE
        ),
        width = 7,
        height = 4,
        dpi = 150
    )
}
p_df$"p_adj" <- p.adjust(p_df$p, method = "fdr")

p_df |>
    dplyr::arrange(p)

saveRDS(p_df, proc_path("outcome_transition_pvals.rds", TRUE))
saveRDS(pl, proc_path("outcome_transition_plots.rds", TRUE))

p_df <- readRDS(proc_path("2025_07_08_outcome_transition_pvals.rds"))
pl <- readRDS(proc_path("2025_07_08_outcome_transition_plots.rds"))

pl[[1]]

# HERE 2025-07-08

# "Diagnostic accuracy (AUC = 0.9 1) and that the cut-off score
# with the best diagnostic confidence, as determined by the
# intersect point of sensitivity and specificity, was 39 (which
# corresponded to the upper quartile of the control group's SDSC
# total score); this cut-off point gave a sensitivity of 0.89 and a
# specificity of 0.74. This score correctly identified 73.4% of th" - bruni
```
<!-- }}} -->

# Longitudinal trajectory check 2

Checking again, but now rather than high-high/high-low, examining if there is differences in high that went down vs. high that stayed same or went up.

```{r}
adj_df_cat_annotated <- readRDS(proc_path("2025_07_08_adj_df_cat_annotated.rds"))

t0_df <- adj_df_cat_annotated |>
    dplyr::filter(t == 0)
t2_df <- adj_df_cat_annotated |>
    dplyr::filter(t == 2)
colnames(t0_df) <- paste0(colnames(t0_df), "_t0")
colnames(t2_df) <- paste0(colnames(t2_df), "_t2")
t0_df <- dplyr::rename(t0_df, "uid" = "uid_t0", "imputation" = "imputation_t0")
t2_df <- dplyr::rename(t2_df, "uid" = "uid_t2", "imputation" = "imputation_t2")

merged_df <- dplyr::inner_join(t0_df, t2_df, by = c("uid", "imputation"))

outcome_fts <- c(
    "cbcl_anxdep",
    "cbcl_withdep",
    "cbcl_somatic",
    "cbcl_social",
    "cbcl_thought",
    "cbcl_attention",
    "cbcl_rulebreak",
    "cbcl_aggressive",
    "sds_sleep"
)

library(ggplot2)
library(multcomp)
library(patchwork)

pretty_features <- c(
    "cbcl_anxdep"     = "CBCL Anxious-Depressed",
    "cbcl_withdep"    = "CBCL Withdrawn-Depressed",
    "cbcl_somatic"    = "CBCL Somatic",
    "cbcl_social"     = "CBCL Social",
    "cbcl_thought"    = "CBCL Thought",
    "cbcl_attention"  = "CBCL Attention",
    "cbcl_rulebreak"  = "CBCL Rule-breaking",
    "cbcl_aggressive" = "CBCL Aggressive",
    "sds_sleep"       = "SDS Sleep"
)

plot_high_change <- function(df, feature) {
    pretty_feature <- gsub("cbcl_", "CBCL ", feature)
    category_name <- paste0(feature, "_cat_t0")
    name_t0 <- paste0("adj_", feature, "_t0")
    name_t2 <- paste0("adj_", feature, "_t2")
    name <- paste0("adj_", feature)
    df_labeled <- df |>
        dplyr::filter(
            .data[[category_name]] %in% c("high_high", "high_low")
        ) |>
        dplyr::mutate(
            diff_cat = dplyr::case_when(
                .data[[name_t2]] < .data[[name_t0]] ~ "improved",
                TRUE ~ "not_improved"
            )
        ) |>
        dplyr::select(
            uid,
            diff_cat,
            dplyr::contains(c("cluster", "imputation", "t", feature))
        )
    df_0 <- df_labeled |>
        dplyr::select(
            uid,
            imputation,
            diff_cat,
            dplyr::ends_with("_t0")
        )
    df_2 <- df_labeled |>
        dplyr::select(
            uid,
            imputation,
            diff_cat,
            dplyr::ends_with("_t2")
        )
    colnames(df_0) <- gsub("_t0$", "", colnames(df_0))
    colnames(df_2) <- gsub("_t2$", "", colnames(df_2))
    stacked_df <- rbind(df_0, df_2)
    pd <- position_dodge(width = 0.2)
    stacked_df_analysis <- stacked_df |>
        dplyr::filter(t == 0) |>
        dplyr::mutate(
            diff_cat_bin = dplyr::case_when(
                diff_cat == "improved" ~ 1,
                diff_cat == "not_improved" ~ 0
            )
        )
    fisher_p_value <- fisher.test(table(stacked_df_analysis$diff_cat_bin, stacked_df_analysis$cluster))$"p.value"
    df_12 <- stacked_df_analysis |>
        dplyr::filter(cluster != 3)
    df_13 <- stacked_df_analysis |>
        dplyr::filter(cluster != 2)
    df_23 <- stacked_df_analysis |>
        dplyr::filter(cluster != 1)
    ft_12 <- fisher.test(table(df_12$"diff_cat_bin", as.factor(as.character(df_12$"cluster"))))
    ft_13 <- fisher.test(table(df_13$"diff_cat_bin", as.factor(as.character(df_13$"cluster"))))
    ft_23 <- fisher.test(table(df_23$"diff_cat_bin", as.factor(as.character(df_23$"cluster"))))
    pairwise_df <- data.frame(
        comparison = c("12", "13", "23"),
        p = c(ft_12$p.value, ft_13$p.value, ft_23$p.value),
        estimate = c(ft_12$estimate, ft_13$estimate, ft_23$estimate),
        conf_int_low = c(ft_12$conf.int[1], ft_13$conf.int[1], ft_23$conf.int[1]),
        conf_int_high = c(ft_12$conf.int[2], ft_13$conf.int[2], ft_23$conf.int[2]),
        feature = feature
    )
    p_df <- data.frame(
        p_fisher = fisher_p_value,
        feature = feature
    )
    point_plot <- stacked_df |>
        dplyr::filter(imputation == 1) |>
        ggplot(
            aes(
                x = factor(t),
                y = .data[[name]],
                group = uid,
                colour = diff_cat
            )
        ) +
        geom_point(size = 3, position = pd, alpha = 0.5) +
        geom_line(position = pd, alpha = 0.5) +
        facet_wrap(~ cluster) +
        theme_bw() +
        scale_colour_manual(
            values = c("improved" = "darkgreen", "not_improved" = "firebrick"),
            labels = c("improved" = "Improved", "not_improved" = "Not Improved")
        ) +
        labs(colour = "Transition", title = pretty_features[[feature]], x = "Time point", y = NULL)
    prop_plot <- stacked_df |>
        count(cluster, diff_cat) |>
        group_by(cluster) |>
        mutate(prop = n / sum(n)) |>
        ggplot(aes(x = cluster, y = prop, fill = diff_cat)) +
        geom_col(position = "fill") +  # stacked proportion bars
        theme_classic() + 
        labs(y = "Proportion", x = "Cluster", fill = "Transition") +
        scale_fill_manual(
            values = c("improved" = "darkgreen", "not_improved" = "firebrick"),
            labels = c("improved" = "Improved", "not_improved" = "Not Improved")
        )
    return(
        list(point_plot,  prop_plot, p_df, pairwise_df)
    )
}

p_df <- data.frame()
pairwise_df <- data.frame()
pl <- list()
pl_2 <- list()
for (i in 1:9) {
    print(i)
    high_change_results <- plot_high_change(merged_df, outcome_fts[[i]])
    pl[[i]] <- high_change_results[[1]]
    pl_2[[i]] <- high_change_results[[2]]
    p_df <- rbind(p_df, high_change_results[[3]])
    pairwise_df <- rbind(pairwise_df, high_change_results[[4]])
}
names(pl) <- outcome_fts
names(pl_2) <- outcome_fts
p_df$"p_fisher_adj" <- p.adjust(p_df$"p_fisher", method = "fdr")
pl_annotated <- lapply(
    1:9,
    function(i) {
        pl_2[[i]] +
            annotate(
                "text",
                x = 2,
                y = 1.13,
                label = paste0(
                    "\nFDR Fisher p: ", signif(p_df$"p_fisher_adj"[[i]], 3)
                ),
                colour = "black",
                size = 3
            ) +
             coord_cartesian(ylim = c(0, 1.2))
    }
)
#merged_plots <- wrap_plots(pl, ncol = 1) | wrap_plots(pl_annotated, ncol = 1)
#merged_plots <- merged_plots + plot_layout(widths = c(2, 1))
#saveRDS(merged_plots, fig_path("high_change_figs_pl.rds", TRUE))
#ggsave(
#    filename = fig_path("high_change_plot.png", TRUE),
#    plot = merged_plots,
#    height = 20,
#    width = 10
#)
#p_df <- p_df |>
#    arrange(p_adj) |>
#    dplyr::select(feature, comparison, p, p_adj)
#
#saveRDS(pl, fig_path("high_change_figs_pl.rds", TRUE))
#saveRDS(pl_2, fig_path("high_change_figs_pl_2.rds", TRUE))
#saveRDS(p_df, proc_path("high_change_p_df.rds", TRUE))
#saveRDS(p_df_2, proc_path("high_change_p_df_2.rds", TRUE))
#
#pl <- readRDS(fig_path("2025_07_17_high_change_figs_pl.rds"))
#pl_2 <- readRDS(fig_path("2025_07_17_high_change_figs_pl_2.rds"))
#p_df <- readRDS(proc_path("2025_07_17_high_change_p_df.rds"))
#p_df_2 <- readRDS(proc_path("2025_07_17_high_change_p_df_2.rds"))

p_df |>
    dplyr::arrange(p_fisher_adj) |>
    dplyr::rename("Adjusted p-value" = "p_fisher_adj", "Feature" = "feature") |>
    dplyr::select(-p_fisher) |>
    knitr::kable(format = "markdown", digits = 6)
sig_fts <- p_df |>
    dplyr::filter(p_fisher_adj < 0.05) |>
    dplyr::select(feature) |>
    unlist() |>
    as.character()
pairwise_df_sig <- pairwise_df |>
    dplyr::filter(feature %in% sig_fts)
pairwise_df_sig$"p_adj" <- p.adjust(pairwise_df_sig$p, method = "fdr")
pairwise_df_sig |>
    dplyr::mutate(es = paste0(
        round(estimate, 2),
        " [", round(conf_int_low, 2), ", ", round(conf_int_high, 2), "]"
    )) |>
    dplyr::select(comparison, feature, p_adj, es) |>
    dplyr::arrange(comparison, p_adj) |>
    dplyr::rename(
        "Comparison" = "comparison",
        "Feature" = "feature",
        "Adjusted p-value" = "p_adj",
        "Effect size (95% CI)" = "es"
    ) |>
    dplyr::mutate(
        Comparison = gsub("12", "1 vs 2", Comparison),
        Comparison = gsub("13", "1 vs 3", Comparison),
        Comparison = gsub("23", "2 vs 3", Comparison)
    ) |>
    knitr::kable(format = "markdown", digits = 5)

sig_plots <- lapply(
    c(
        "cbcl_withdep",
        "cbcl_thought",
        "cbcl_somatic",
        "cbcl_rulebreak",
        "cbcl_social"
    ),
    function(x) {
        (pl[[x]] | pl_2[[x]]) + plot_layout(widths = c(2, 1))
    }
)
my_sig <- function(comparisons, annotations, y_position) {
    geom_signif(
        comparisons = comparisons,
        annotations = annotations,
        y_position = y_position,
        textsize = 5,
        tip_length = 0,
        vjust = 0.3
    )
}
annotations <- list(
    "withdep"   = my_sig(list(c("1", "2"), c("1", "3"), c("2", "3")), c("*", "*", "***"), c(1.02, 1.25, 1.12)),
    "thought"   = my_sig(list(c("1", "3")), c("***"), 1.02),
    "somatic"   = my_sig(list(c("2", "3"), c("1", "3")), c("**", "*"), c(1.02, 1.16)),
    "rulebreak" = my_sig(list(c("1", "2"), c("2", "3")), c("**", "*"), c(1.02, 1.12)),
    "social"    = my_sig(list(c("2", "3")), c("**"), 1.02)
)
sig_plots2 <- lapply(
    1:5,
    function(x) {
        if (x != 3) {
            sig_plots[[x]][[2]] <- sig_plots[[x]][[2]] + theme(legend.position = "none")
            sig_plots[[x]][[2]] <- sig_plots[[x]][[2]] + labs(y = NULL)
        }
        sig_plots[[x]][[1]] <- sig_plots[[x]][[1]] + theme(legend.position = "none")
        sig_plots[[x]][[1]] <- sig_plots[[x]][[1]] + labs(y = "Adjusted Score")
        sig_plots[[x]][[2]] <- sig_plots[[x]][[2]] +
            annotations[[x]] +
            coord_cartesian(ylim = c(0, 1.35)) +
            scale_y_continuous(breaks = seq(0, 1, by = 0.25))
        sig_plots[[x]]
    }
)
change_plot <- wrap_plots(sig_plots2, ncol = 1)
ggsave(
    filename = fig_path("high_change_plot_clean2.png", TRUE),
    plot = change_plot,
    height = 13,
    width = 8
)


```

|Feature         | Adjusted p-value|
|:---------------|----------------:|
|cbcl_withdep    |         0.000133|
|cbcl_thought    |         0.000133|
|cbcl_somatic    |         0.008305|
|cbcl_rulebreak  |         0.008305|
|cbcl_social     |         0.008902|
|cbcl_attention  |         0.299846|
|sds_sleep       |         0.628342|
|cbcl_anxdep     |         0.914292|
|cbcl_aggressive |         0.914292|

```{r}

pl$"cbcl_somatic"
pl_2$"cbcl_thought"

#
#pl <- readRDS(fig_path("2025_07_14_high_change_figs_pl.rds"))
#p_df <- readRDS(proc_path("2025_07_14_high_change_p_df.rds"))
#
#ggsave(
#    filename = fig_path("high_change_plot.png", TRUE),
#    wrap_plots(pl),
#    width = 20,
#    height = 7
#)
#
#p_df |>
#    knitr::kable(format = "markdown", digits = 5)

    
```

## Q2. Did the matched uninjured subjects experience more mTBIs by T2 than the other uninjured subjects?<!-- {{{ -->

```{r}
matched_unij_nearest_esdf <- readRDS(proc_path("2025_02_16_matched_unij_nearest_esdf.rds"))

# Those who exhibited heterogeneity most similar to the baseline mTBI group
matched_subs <- uids(matched_unij_nearest_esdf)
matched_subs <- gsub("uid_", "", matched_subs)

# Those who never sustained a head injury prior to T2
# N = 7678
long_unij_subs <- read_subjects(sub_path("2025_02_07_unij_subs_0_to_2.csv"))

# Those who sustained a head injury between 0 and T2
# N = 220
long_mtbi_subs <- read_subjects(sub_path("2025_02_07_mtbi_subs_0_to_2.csv"))

# The pool of all baseline uninjured subjects
# N = 9349
base_unij_subs <- read_subjects(sub_path("2025_02_07_unij_subs.csv"))

non_matched_subs <- setdiff(base_unij_subs, matched_subs)

base_mtbi_subs <- read_subjects(sub_path("2025_02_07_mtbi_subs.csv"))
```

Let's consider being in the matched group vs. not being in the matched group as exposed vs. unexposed, and ending up in the mTBI sample as outcome vs. no outcome.
Then I calculate the odds ratio and 95% CI of being in the mTBI sample based on being in the matched group.

```{r}
# Calculation 1: Explicitly looking for people that ended up in mTBI sample
matched_that_became_mtbi <- sum(matched_subs %in% long_mtbi_subs)
unmatched_that_became_mtbi <- sum(non_matched_subs %in% long_mtbi_subs)
matched_that_remained_unij <- sum(!matched_subs %in% long_mtbi_subs)
unmatched_that_remained_unij <- sum(!non_matched_subs %in% long_mtbi_subs)

odds_ratio <- function(de, he, dn, hn) {
    numerator <- de / he
    denominator <- dn / hn
    or <- numerator / denominator
    se_log_or <- sqrt(1/de + 1/he + 1/dn + 1/hn)
    log_or <- log(or)
    ci_lower <- exp(log_or - 1.96 * se_log_or)
    ci_upper <- exp(log_or + 1.96 * se_log_or)
    return(list(
        or = or,
        ci_lower = ci_lower,
        ci_upper = ci_upper
    ))
}

# (D)isease = mTBI, (H)ealthy = unij , (E)xposure = match
# 0.83 [0.36, 1.89]
odds_ratio(
    de = matched_that_became_mtbi,
    he = matched_that_remained_unij,
    dn = unmatched_that_became_mtbi,
    hn = unmatched_that_remained_unij
)
```

No significant difference in the proportion of matched uninjured subjects to unmatched uninjured subjects that ended up in the longitudinal mTBI group (1.3% vs. 1.6%, uncorrected Chi-squared test p-value = 0.6565).

### Extra: Correlations with membership in longitudinal mTBI sample

Now I'll double check to see if there were any attributes of subjects that were particularly closely associated with membership in the longitudinal mTBI sample.

```{r}
long_mtbi_0_dl <- all_long_dls$"long_mtbi_0_dls"[[1]]

base_unij_0_dl <- all_dls$"unij_pooled_data_lists"[[1]]

long_unij_0_dl <- base_unij_0_dl |>
    dlapply(
        function(x) {
            x$"data" <- dplyr::filter(x$"data", uid %in% paste0("uid_", long_unij_subs))
            return(x)
        }
    )

long_unij_df <- as.data.frame(long_unij_0_dl)
long_mtbi_df <- as.data.frame(long_mtbi_0_dl)
base_unij_df <- as.data.frame(base_unij_0_dl)

long_unij_df$"mtbi" <- 0
long_mtbi_df$"mtbi" <- 1

long_corr_df <- rbind(long_unij_df, long_mtbi_df)

saveRDS(long_corr_df, proc_path("long_corr_df.rds", TRUE))

long_corr_df <- readRDS(proc_path("2025_05_01_long_corr_df.rds"))

# Correlation matrix examining how correlated each feature is with being assigned to mTBI group
prepped_long_corr_df <- long_corr_df |>
    dplyr::select(-uid) |>
    dummy_cols(
        select_columns = "race",
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = TRUE
    )

# Setup parallel plan
future::plan("multisession")
kendall_row <- function(i, data) {
  sapply(i:ncol(data), function(j) cor(data[[i]], data[[j]], method = "kendall"))
}
n <- ncol(prepped_long_corr_df)
kendall_mat <- matrix(NA, n, n)
colnames(kendall_mat) <- rownames(kendall_mat) <- colnames(prepped_long_corr_df)
results <- pbapply::pblapply(1:n, function(i) kendall_row(i, prepped_long_corr_df), cl = future::availableCores())
for (i in 1:n) {
  kendall_mat[i, i:n] <- results[[i]]
  kendall_mat[i:n, i] <- results[[i]]
}

saveRDS(kendall_mat, proc_path("long_corr_mat_kendall.rds", TRUE))

# Setup parallel plan
spearman_row <- function(i, data) {
    sapply(i:ncol(data), function(j) cor(data[[i]], data[[j]], method = "spearman"))
}
n <- ncol(prepped_long_corr_df)
spearman_mat <- matrix(NA, n, n)
colnames(spearman_mat) <- rownames(spearman_mat) <- colnames(prepped_long_corr_df)
results <- pbapply::pblapply(1:n, function(i) spearman_row(i, prepped_long_corr_df), cl = future::availableCores())
for (i in 1:n) {
  spearman_mat[i, i:n] <- results[[i]]
  spearman_mat[i:n, i] <- results[[i]]
}

saveRDS(spearman_mat, proc_path("long_corr_mat_spearman.rds", TRUE))

pearson_mat <- cor(prepped_long_corr_df, method = "pearson")

saveRDS(pearson_mat, proc_path("long_corr_mat_pearson.rds", TRUE))
```

```{r}
kendall_mat <- readRDS(proc_path("2025_05_01_long_corr_mat_kendall.rds"))
spearman_mat <- readRDS(proc_path("2025_05_01_long_corr_mat_spearman.rds"))
pearson_mat <- readRDS(proc_path("2025_05_01_long_corr_mat_pearson.rds"))

kendall_mat[setdiff(rownames(kendall_mat), "mtbi"), "mtbi"]
spearman_mat[setdiff(rownames(spearman_mat), "mtbi"), "mtbi"]
pearson_mat[setdiff(rownames(pearson_mat), "mtbi"), "mtbi"]

ComplexHeatmap::Heatmap(kendall_mat[setdiff(rownames(kendall_mat), "mtbi"), "mtbi"])

ComplexHeatmap::Heatmap(spearman_mat[setdiff(rownames(spearman_mat), "mtbi"), "mtbi"])

ComplexHeatmap::Heatmap(pearson_mat[setdiff(rownames(pearson_mat), "mtbi"), "mtbi"])

kendall_mat[names(sort(-abs(kendall_mat[setdiff(rownames(kendall_mat), "mtbi"), "mtbi"]))), "mtbi"] |> ComplexHeatmap::Heatmap(cluster_rows = FALSE)


spearman_mat[names(sort(-abs(spearman_mat[setdiff(rownames(spearman_mat), "mtbi"), "mtbi"]))), "mtbi"] |> ComplexHeatmap::Heatmap(cluster_rows = FALSE)

pearson_mat[names(sort(-abs(pearson_mat[setdiff(rownames(pearson_mat), "mtbi"), "mtbi"]))), "mtbi"] |> ComplexHeatmap::Heatmap(cluster_rows = FALSE)

ComplexHeatmap::Heatmap(z3)

z3 <- long_corr_df |>
    dplyr::select(-uid) |>
    dummy_cols(
        select_columns = "race",
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = TRUE
    ) |>
    cor(method = "kendll")

# Only looking at correlations
mtbi_corr_mat <- long_corr_mat[rownames(long_corr_mat) != "mtbi", "mtbi", drop = FALSE]

mtbi_corr_mat |>
    ComplexHeatmap::Heatmap()

mtbi_corr_mat |>
    as.data.frame() |>
    dplyr::arrange(mtbi)

long_corr_df |>
    ggplot(aes(x = factor(mtbi), y = major_wm_ndi)) +
    geom_jitter() +
    theme_bw()


long_corr_clean_df <- long_corr_df |>
    dplyr::select(-uid) |>
    dummy_cols(
        select_columns = "race",
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = TRUE
    )

pvalue_df <- data.frame()
for (col in colnames(long_corr_clean_df)) {
    test_results <- cor.test(long_corr_clean_df$"mtbi", long_corr_clean_df[[col]])
    pval <- test_results$"p.value"
    est <- test_results$"estimate"
    l <- test_results$"conf.int"[1]
    u <- test_results$"conf.int"[2]
    pvalue_df <- rbind(
        pvalue_df,
        data.frame(
            feature = col,
            pval = pval,
            est = est,
            l = l,
            u = u
        )
    )
}
rownames(pvalue_df) <- NULL
p_values_bonferroni <- p.adjust(pvalue_df$"pval", method = "bonferroni")
p_values_fdr <- p.adjust(pvalue_df$"pval", method = "fdr")
pvalue_df$"pval_bon" <- p_values_bonferroni
pvalue_df$"pval_fdr" <- p_values_fdr
pvalue_df <- pvalue_df |>
    dplyr::arrange(pval) |>
    dplyr::filter(feature != "mtbi") |>
    dplyr::select(feature, pval, pval_bon, pval_fdr, est, l, u)

write_csv(pvalue_df, proc_path("pvalue_df.csv", TRUE))
pvalue_df <- read_csv(proc_path("2025_02_16_pvalue_df.csv"))
```

Quite a few features there that remain significant even after bonferroni correction.
There certainly seem to be factors that increase a child's risk of sustaining an mTBI.
These are all taken from the same data collection period as well!
<!-- }}} -->

## Q3. Clustering of the longitudinal sample with their baseline vs. their longitudinal data: both equally informative? (Done, June 16) <!-- {{{ -->

Can perhaps skip this and just make use of the classifier.

```{r}
lmtb_0_dls <- all_long_dls_h_ns$"lmtb_0_dls"
lmtb_0_ols <- all_long_dls_h_ns$"lmtb_0_ols"
lmtb_l_dls <- all_long_dls_h_ns$"lmtb_l_dls"
lmtb_l_ols <- all_long_dls_h_ns$"lmtb_l_ols"
```

```{r}
lmtb_config <- snf_config(
    lmtb_0_dls[[1]],
    n_solutions = 200,
    cnt_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    dsc_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ord_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    use_default_dist_fns = TRUE
)

saveRDS(lmtb_config, proc_path("lmtb_config.rds", TRUE))
```


```{r}
# CHECKPOINT
lmtb_config <- readRDS(proc_path("2025_06_15_lmtb_config.rds"))
```

```{r}
lmtb_0_sol_df_u1 <- batch_snf(dl = lmtb_0_dls[[1]], sc = lmtb_config, processes = "max")
saveRDS(lmtb_0_sol_df_u1, proc_path("lmtb_0_sol_df_u1.rds", TRUE))
lmtb_0_sol_df_u2 <- batch_snf(dl = lmtb_0_dls[[2]], sc = lmtb_config, processes = "max")
saveRDS(lmtb_0_sol_df_u2, proc_path("lmtb_0_sol_df_u2.rds", TRUE))
lmtb_0_sol_df_u3 <- batch_snf(dl = lmtb_0_dls[[3]], sc = lmtb_config, processes = "max")
saveRDS(lmtb_0_sol_df_u3, proc_path("lmtb_0_sol_df_u3.rds", TRUE))
lmtb_0_sol_df_u4 <- batch_snf(dl = lmtb_0_dls[[4]], sc = lmtb_config, processes = "max")
saveRDS(lmtb_0_sol_df_u4, proc_path("lmtb_0_sol_df_u4.rds", TRUE))
lmtb_0_sol_df_u5 <- batch_snf(dl = lmtb_0_dls[[5]], sc = lmtb_config, processes = "max")
saveRDS(lmtb_0_sol_df_u5, proc_path("lmtb_0_sol_df_u5.rds", TRUE))

lmtb_l_sol_df_u1 <- batch_snf(dl = lmtb_l_dls[[1]], sc = lmtb_config, processes = "max")
saveRDS(lmtb_l_sol_df_u1, proc_path("lmtb_l_sol_df_u1.rds", TRUE))
lmtb_l_sol_df_u2 <- batch_snf(dl = lmtb_l_dls[[2]], sc = lmtb_config, processes = "max")
saveRDS(lmtb_l_sol_df_u2, proc_path("lmtb_l_sol_df_u2.rds", TRUE))
lmtb_l_sol_df_u3 <- batch_snf(dl = lmtb_l_dls[[3]], sc = lmtb_config, processes = "max")
saveRDS(lmtb_l_sol_df_u3, proc_path("lmtb_l_sol_df_u3.rds", TRUE))
lmtb_l_sol_df_u4 <- batch_snf(dl = lmtb_l_dls[[4]], sc = lmtb_config, processes = "max")
saveRDS(lmtb_l_sol_df_u4, proc_path("lmtb_l_sol_df_u4.rds", TRUE))
lmtb_l_sol_df_u5 <- batch_snf(dl = lmtb_l_dls[[5]], sc = lmtb_config, processes = "max")
saveRDS(lmtb_l_sol_df_u5, proc_path("lmtb_l_sol_df_u5.rds", TRUE))
```

```{r}
lmtb_0_sol_df_u1 <- readRDS(proc_path("2025_06_15_lmtb_0_sol_df_u1.rds"))
lmtb_0_sol_df_u2 <- readRDS(proc_path("2025_06_15_lmtb_0_sol_df_u2.rds"))
lmtb_0_sol_df_u3 <- readRDS(proc_path("2025_06_15_lmtb_0_sol_df_u3.rds"))
lmtb_0_sol_df_u4 <- readRDS(proc_path("2025_06_15_lmtb_0_sol_df_u4.rds"))
lmtb_0_sol_df_u5 <- readRDS(proc_path("2025_06_15_lmtb_0_sol_df_u5.rds"))

lmtb_0_sol_df <- do.call(
    "rbind",
    c(
        list(
            lmtb_0_sol_df_u1,
            lmtb_0_sol_df_u2,
            lmtb_0_sol_df_u3,
            lmtb_0_sol_df_u4,
            lmtb_0_sol_df_u5
        ),
        list(reset_indices = TRUE)
    )
)
saveRDS(lmtb_0_sol_df, proc_path("lmtb_0_sol_df.rds", TRUE))
```

```{r}
lmtb_0_ari <- calc_aris(lmtb_0_sol_df, processes = "max")
saveRDS(lmtb_0_ari, proc_path("lmtb_0_ari.rds", TRUE))

lmtb_0_ari_order <- get_matrix_order(lmtb_0_ari)
write_csv(data.frame(lmtb_0_ari_order), proc_path("lmtb_0_ari_order.csv", TRUE))
```

```{r}
lmtb_l_sol_df_u1 <- readRDS(proc_path("2025_06_15_lmtb_l_sol_df_u1.rds"))
lmtb_l_sol_df_u2 <- readRDS(proc_path("2025_06_15_lmtb_l_sol_df_u2.rds"))
lmtb_l_sol_df_u3 <- readRDS(proc_path("2025_06_15_lmtb_l_sol_df_u3.rds"))
lmtb_l_sol_df_u4 <- readRDS(proc_path("2025_06_15_lmtb_l_sol_df_u4.rds"))
lmtb_l_sol_df_u5 <- readRDS(proc_path("2025_06_15_lmtb_l_sol_df_u5.rds"))

lmtb_l_sol_df <- do.call(
    "rbind",
    c(
        list(
            lmtb_l_sol_df_u1,
            lmtb_l_sol_df_u2,
            lmtb_l_sol_df_u3,
            lmtb_l_sol_df_u4,
            lmtb_l_sol_df_u5
        ),
        list(reset_indices = TRUE)
    )
)
saveRDS(lmtb_l_sol_df, proc_path("lmtb_l_sol_df.rds", TRUE))
lmtb_l_ari <- calc_aris(lmtb_l_sol_df, processes = "max")
saveRDS(lmtb_l_ari, proc_path("lmtb_l_ari.rds", TRUE))
lmtb_l_ari_order <- get_matrix_order(lmtb_l_ari)
write_csv(data.frame(lmtb_l_ari_order), proc_path("lmtb_l_ari_order.csv", TRUE))
```

```{r}
# CHECKPOINT
lmtb_0_sol_df <- readRDS(proc_path("2025_06_16_lmtb_0_sol_df.rds"))
lmtb_0_ari <- readRDS(proc_path("2025_06_16_lmtb_0_ari.rds"))
lmtb_0_ari_order <- unlist(read_csv(proc_path("2025_06_16_lmtb_0_ari_order.csv")))
names(lmtb_0_ari_order) <- NULL

lmtb_l_sol_df <- readRDS(proc_path("2025_06_16_lmtb_l_sol_df.rds"))
lmtb_l_ari <- readRDS(proc_path("2025_06_16_lmtb_l_ari.rds"))
lmtb_l_ari_order <- unlist(read_csv(proc_path("2025_06_16_lmtb_l_ari_order.csv")))
names(lmtb_l_ari_order) <- NULL
```

```{r}
# Solo imputation 1
lmtb_0_ext_sol_df_u1 <- extend_solutions(
    lmtb_0_sol_df[1:200, ],
    dl = lmtb_0_dls[[1]],
    target_dl = lmtb_0_ols[[1]],
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(lmtb_0_ext_sol_df_u1, proc_path("lmtb_0_ext_sol_df_u1.rds", TRUE))
# Solo imputation 2
lmtb_0_ext_sol_df_u2 <- extend_solutions(
    lmtb_0_sol_df[201:400, ],
    dl = lmtb_0_dls[[2]],
    target_dl = lmtb_0_ols[[2]],
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(lmtb_0_ext_sol_df_u2, proc_path("lmtb_0_ext_sol_df_u2.rds", TRUE))
# Solo imputation 3
lmtb_0_ext_sol_df_u3 <- extend_solutions(
    lmtb_0_sol_df[401:600, ],
    dl = lmtb_0_dls[[3]],
    target_dl = lmtb_0_ols[[3]],
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(lmtb_0_ext_sol_df_u3, proc_path("lmtb_0_ext_sol_df_u3.rds", TRUE))
# Solo imputation 4
lmtb_0_ext_sol_df_u4 <- extend_solutions(
    lmtb_0_sol_df[601:800, ],
    dl = lmtb_0_dls[[4]],
    target_dl = lmtb_0_ols[[4]],
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(lmtb_0_ext_sol_df_u4, proc_path("lmtb_0_ext_sol_df_u4.rds", TRUE))
# Solo imputation 5
lmtb_0_ext_sol_df_u5 <- extend_solutions(
    lmtb_0_sol_df[801:1000, ],
    dl = lmtb_0_dls[[5]],
    target_dl = lmtb_0_ols[[5]],
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(lmtb_0_ext_sol_df_u5, proc_path("lmtb_0_ext_sol_df_u5.rds", TRUE))
```

```{r}
# Solo imputation 1
lmtb_l_ext_sol_df_u1 <- extend_solutions(
    lmtb_l_sol_df[1:200, ],
    dl = lmtb_l_dls[[1]],
    target_dl = lmtb_l_ols[[1]],
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(lmtb_l_ext_sol_df_u1, proc_path("lmtb_l_ext_sol_df_u1.rds", TRUE))
# Solo imputation 2
lmtb_l_ext_sol_df_u2 <- extend_solutions(
    lmtb_l_sol_df[201:400, ],
    dl = lmtb_l_dls[[2]],
    target_dl = lmtb_l_ols[[2]],
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(lmtb_l_ext_sol_df_u2, proc_path("lmtb_l_ext_sol_df_u2.rds", TRUE))
# Solo imputation 3
lmtb_l_ext_sol_df_u3 <- extend_solutions(
    lmtb_l_sol_df[401:600, ],
    dl = lmtb_l_dls[[3]],
    target_dl = lmtb_l_ols[[3]],
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(lmtb_l_ext_sol_df_u3, proc_path("lmtb_l_ext_sol_df_u3.rds", TRUE))
# Solo imputation 4
lmtb_l_ext_sol_df_u4 <- extend_solutions(
    lmtb_l_sol_df[601:800, ],
    dl = lmtb_l_dls[[4]],
    target_dl = lmtb_l_ols[[4]],
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(lmtb_l_ext_sol_df_u4, proc_path("lmtb_l_ext_sol_df_u4.rds", TRUE))
# Solo imputation 5
lmtb_l_ext_sol_df_u5 <- extend_solutions(
    lmtb_l_sol_df[801:1000, ],
    dl = lmtb_l_dls[[5]],
    target_dl = lmtb_l_ols[[5]],
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(lmtb_l_ext_sol_df_u5, proc_path("lmtb_l_ext_sol_df_u5.rds", TRUE))
```

```{r}
lmtb_0_ext_sol_df_u1 <- readRDS(proc_path("2025_06_16_lmtb_0_ext_sol_df_u1.rds"))
lmtb_0_ext_sol_df_u2 <- readRDS(proc_path("2025_06_16_lmtb_0_ext_sol_df_u2.rds"))
lmtb_0_ext_sol_df_u3 <- readRDS(proc_path("2025_06_16_lmtb_0_ext_sol_df_u3.rds"))
lmtb_0_ext_sol_df_u4 <- readRDS(proc_path("2025_06_16_lmtb_0_ext_sol_df_u4.rds"))
lmtb_0_ext_sol_df_u5 <- readRDS(proc_path("2025_06_16_lmtb_0_ext_sol_df_u5.rds"))

lmtb_0_ext_sol_df <- do.call(
    "rbind",
    c(
        list(
            lmtb_0_ext_sol_df_u1,
            lmtb_0_ext_sol_df_u2,
            lmtb_0_ext_sol_df_u3,
            lmtb_0_ext_sol_df_u4,
            lmtb_0_ext_sol_df_u5
        ),
        list(reset_indices = TRUE)
    )
)

lmtb_l_ext_sol_df_u1 <- readRDS(proc_path("2025_06_16_lmtb_l_ext_sol_df_u1.rds"))
lmtb_l_ext_sol_df_u2 <- readRDS(proc_path("2025_06_16_lmtb_l_ext_sol_df_u2.rds"))
lmtb_l_ext_sol_df_u3 <- readRDS(proc_path("2025_06_16_lmtb_l_ext_sol_df_u3.rds"))
lmtb_l_ext_sol_df_u4 <- readRDS(proc_path("2025_06_16_lmtb_l_ext_sol_df_u4.rds"))
lmtb_l_ext_sol_df_u5 <- readRDS(proc_path("2025_06_16_lmtb_l_ext_sol_df_u5.rds"))

lmtb_l_ext_sol_df <- do.call(
    "rbind",
    c(
        list(
            lmtb_l_ext_sol_df_u1,
            lmtb_l_ext_sol_df_u2,
            lmtb_l_ext_sol_df_u3,
            lmtb_l_ext_sol_df_u4,
            lmtb_l_ext_sol_df_u5
        ),
        list(reset_indices = TRUE)
    )
)

saveRDS(lmtb_0_ext_sol_df, proc_path("lmtb_0_ext_sol_df.rds", TRUE))
saveRDS(lmtb_l_ext_sol_df, proc_path("lmtb_l_ext_sol_df.rds", TRUE))

lmtb_0_ext_sol_df <- readRDS(proc_path("2025_06_16_lmtb_0_ext_sol_df.rds"))
lmtb_l_ext_sol_df <- readRDS(proc_path("2025_06_16_lmtb_l_ext_sol_df.rds"))
```

```{r}
lmtb_0_hm <- meta_cluster_heatmap(lmtb_0_ari, order = lmtb_0_ari_order)
lmtb_l_hm <- meta_cluster_heatmap(lmtb_l_ari, order = lmtb_l_ari_order)

lmtb_0_esdf <- as.data.frame(lmtb_0_ext_sol_df)
lmtb_l_esdf <- as.data.frame(lmtb_l_ext_sol_df)

lmtb_0_esdf$"impairment_separation" <- -log10(lmtb_0_esdf$"mean_pval")
lmtb_l_esdf$"impairment_separation" <- -log10(lmtb_l_esdf$"mean_pval")



full_lmtb_0_ari_hm <- meta_cluster_heatmap(
    x = lmtb_0_ari,
    order = lmtb_0_ari_order,
    data = lmtb_0_esdf,
    min_colour = "black",
    split_vector = c(
        238,
        558,
        855
    ),
    top_hm = list(
        "Impairment\nSeparation" = "impairment_separation"
    ),
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    annotation_colours = list(
        "Impairment\nSeparation" = colour_scale(
            lmtb_0_esdf$"impairment_separation",
            min_colour = "gray7",
            max_colour = "limegreen"
        )
    )
)

full_lmtb_l_ari_hm <- meta_cluster_heatmap(
    x = lmtb_l_ari,
    order = lmtb_l_ari_order,
    data = lmtb_l_esdf,
    min_colour = "black",
    split_vector = c(
        130,
        185,
        810
    ),
    top_hm = list(
        "Impairment\nSeparation" = "impairment_separation"
    ),
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    annotation_colours = list(
        "Impairment\nSeparation" = colour_scale(
            lmtb_l_esdf$"impairment_separation",
            min_colour = "gray7",
            max_colour = "limegreen"
        )
    )
)
full_lmtb_l_ari_hm

save_heatmap(
    heatmap = full_lmtb_0_ari_hm,
    path = fig_path("full_lmtb_0_ari_hm.png", TRUE),
    width = 950,
    height = 800,
    res = 100
)

save_heatmap(
    heatmap = full_lmtb_l_ari_hm,
    path = fig_path("full_lmtb_l_ari_hm.png", TRUE),
    width = 950,
    height = 800,
    res = 100
)

concordance_w_mtbi_quick <- function(data_df, n = NULL, iters = 10, procs = 1, mtbi_data) {
    tops_df <- topologizer(data_df)
    info_table <- data_df |>
        dplyr::group_by(cluster) |>
        dplyr::summarize(
            income = mean(household_income),
            sex = mean(sex)
        ) |>
        dplyr::mutate(combo = income - sex) |> # sort by low income and high M
        dplyr::arrange(combo)
    swap_key <- paste0(info_table$"cluster", collapse = "")
    swap_list <- list(
        "123" = list(),                 # swap nothing
        "132" = list(c(2, 3)),          # swap 2<->3
        "213" = list(c(1, 2)),          # swap 1<->2
        "231" = list(c(1, 2), c(2, 3)), # swap 1<->2 then 2<->3
        "312" = list(c(1, 3), c(2, 3)), # swap 1<->3 then 2<->3
        "321" = list(c(1, 3))           # swap 1<->3
    )
    swap_instructions <- swap_list[[swap_key]]
    for (instruction in swap_instructions) {
        data_df <- data_df |>
            dplyr::mutate(
                cluster = dplyr::case_when(
                    cluster == instruction[1] ~ factor(instruction[2]),
                    cluster == instruction[2] ~ factor(instruction[1]),
                    TRUE ~ cluster
                )
            )
    }
    info_table <- data_df |>
        dplyr::group_by(cluster) |>
        dplyr::summarize(
            income = mean(household_income),
            sex = mean(sex)
        ) |>
        dplyr::mutate(combo = income - sex) |> # sort by low income and high M
        dplyr::arrange(combo)
    swap_key <- paste0(info_table$"cluster", collapse = "")
    gen_tops_df <- generalizable_features(tops_df, compare_fn_a)
    gen_tops_df_long <- gen_tops_df |>
        pivot_longer(
            cols = -feature,
            names_to = "comparison",
            values_to = "order_sample"
        )
    joint_df <- dplyr::left_join(
        mtbi_data, # reference data frame
        gen_tops_df_long, # sampled data frame
        by = c("feature", "comparison")
    ) |>
        dplyr::mutate(
            match = ifelse(order_sample == order, 1, 0)
        ) |>
        dplyr::filter(!grepl("mtbi", feature))
        joint_df <- joint_df |> dplyr::select(match) |> na.omit()
        print(paste0("nrow: ", nrow(joint_df)))
    concordance <- sum(joint_df$"match", na.rm = TRUE) / nrow(joint_df)
    return(concordance)
}

mtbi_gen_fts_table_hits_t <- read_csv(proc_path("2025_06_13_mtbi_gen_fts_table_hits_t.csv"))
mtbi_gen_long <- na.omit(mtbi_gen_fts_table_hits_t)

z1 <- auto_plot(
    lmtb_0_ext_sol_df[1, ],
    dl = c(lmtb_0_dls[[1]], lmtb_0_ols[[1]]),
    return_plots = FALSE
)

z2 <- auto_plot(
    lmtb_0_ext_sol_df[1:200, ],
    dl = c(lmtb_0_dls[[1]], lmtb_0_ols[[1]]),
    return_plots = FALSE
)

dl_idx <- c(
    rep(1, 200),
    rep(2, 200),
    rep(3, 200),
    rep(4, 200),
    rep(5, 200)
)

conc_df <- data.frame()
for (i in 1:1000) {
    print(i)
    idx <- dl_idx[[i]]
    if (lmtb_0_ext_sol_df[i, ]$"nclust" == 3) {
        lmtb_0_pl_df <- auto_plot(
            lmtb_0_ext_sol_df[i, ],
            dl = c(lmtb_0_dls[[idx]], lmtb_0_ols[[idx]]),
            return_plots = FALSE
        )
        conc <- concordance_w_mtbi_quick(lmtb_0_pl_df, mtbi_data = mtbi_gen_long)
        conc_df <- rbind(
            conc_df,
            data.frame(
                solution = i,
                dl = idx,
                concordance = conc
            )
        )
    }
}
saveRDS(conc_df, proc_path("lmtb_0_concordance_df.rds", TRUE))

conc_df <- data.frame()
for (i in 1:1000) {
    print(i)
    idx <- dl_idx[[i]]
    if (lmtb_l_ext_sol_df[i, ]$"nclust" == 3) {
        lmtb_l_pl_df <- auto_plot(
            lmtb_l_ext_sol_df[i, ],
            dl = c(lmtb_l_dls[[idx]], lmtb_l_ols[[idx]]),
            return_plots = FALSE
        )
        conc <- concordance_w_mtbi_quick(lmtb_l_pl_df, mtbi_data = mtbi_gen_long)
        conc_df <- rbind(
            conc_df,
            data.frame(
                solution = i,
                dl = idx,
                concordance = conc
            )
        )
    }
}
saveRDS(conc_df, proc_path("lmtb_l_concordance_df.rds", TRUE))

lmtb_0_conc_df <- readRDS(proc_path("2025_07_23_lmtb_0_concordance_df.rds"))

lmtb_l_conc_df <- readRDS(proc_path("2025_07_23_lmtb_l_concordance_df.rds"))

# max is 56.6%
lmtb_0_conc_df |>
    arrange(-concordance) |>
    head(5)

# 31 3 cluster solutions
nrow(lmtb_0_conc_df)

# max is 66.4%
lmtb_l_conc_df |>
    arrange(-concordance) |>
    head(5)

# 125 3 cluster solutions
nrow(lmtb_l_conc_df)
```

Neither option resulted in particularly similar cluster solution to the original mTBI sample.
Suggests that there may be something unique to the kids who had their injury at a much earlier timepoint.
<!-- }}} -->

## Q4. Classifier built from baseline mTBI data: informative?

Assigning predicted clusters to the following 5 groups:

1. Longitudinal mTBI, pre-injury data (N = 220)
2. Longitudinal mTBI, post-injury data (the same N = 220)
3. Baseline uninjured group at T0  (N = 9349)
4. Longitudinal uninjured group at T0 (A subset of 3., N = 7678)
5. Longitudinal uninjured group at T2 (the same N = 7678)

```{r}
library(caret)
library(randomForest)
```

```{r}
lunj_subs_wt2_ns <- readRDS(sub_path("2025_06_12_lunj_subs_wt2_ns.rds"))
lunj_subs_wt2_ns <- paste0("uid_", lunj_subs_wt2_ns)

unij_subs_wt2_ns <- readRDS(sub_path("2025_06_12_unij_subs_wt2_ns.rds"))
unij_subs_wt2_ns <- paste0("uid_", unij_subs_wt2_ns)

# Classifying data using baseline as well as longitudinal features
lmtb_0_dl <- all_long_dls_h_ns$"lmtb_0_dls"[[1]]
lmtb_0_ol <- all_long_dls_h_ns$"lmtb_0_ols"[[1]]

lmtb_l_dl <- all_long_dls_h_ns$"lmtb_l_dls"[[1]]
lmtb_l_ol <- all_long_dls_h_ns$"lmtb_l_ols"[[1]]

unij_0_dl <- all_dls_h$"unij_all_p_dls"[[1]]
unij_0_ol <- all_dls_h$"unij_all_p_ols"[[1]]

# These are not all necessary unij still!
unij_l_dl <- all_long_dls_h$"unij_l_dls"[[1]]
unij_l_ol <- all_long_dls_h$"unij_l_ols"[[1]]
```

```{r}
# Converting the sets of data lists into sets of data frames
lmtb_0_dl_df_wt2_ns <- as.data.frame(lmtb_0_dl)
lmtb_0_ol_df_wt2_ns <- as.data.frame(lmtb_0_ol)
nrow(lmtb_0_dl_df_wt2_ns) # N = 218

lmtb_l_dl_df_wt2_ns <- as.data.frame(lmtb_l_dl)
lmtb_l_ol_df_wt2_ns <- as.data.frame(lmtb_l_ol)
nrow(lmtb_l_dl_df_wt2_ns) # N = 218

unij_0_dl_df <- as.data.frame(unij_0_dl)
unij_0_ol_df <- as.data.frame(unij_0_ol)
nrow(unij_0_dl_df) # N = 7944

unij_l_dl_df <- as.data.frame(unij_l_dl)
unij_l_ol_df <- as.data.frame(unij_l_ol)
nrow(unij_l_dl_df) # N = 8615

# wt2 drop, NS drop
unij_0_dl_df_wt2_ns <- unij_0_dl_df |> dplyr::filter(uid %in% unij_subs_wt2_ns)
nrow(unij_0_dl_df_wt2_ns) # 7313
unij_0_ol_df_wt2_ns <- unij_0_ol_df |> dplyr::filter(uid %in% unij_subs_wt2_ns)
nrow(unij_0_ol_df_wt2_ns) # 7313

unij_l_dl_df_wt2_ns <- unij_l_dl_df |> dplyr::filter(uid %in% unij_subs_wt2_ns)
nrow(unij_l_dl_df_wt2_ns) # 7313
unij_l_ol_df_wt2_ns <- unij_l_ol_df |> dplyr::filter(uid %in% unij_subs_wt2_ns)
nrow(unij_l_ol_df_wt2_ns) # 7313

# wt2 drop, NS drop
lunj_0_dl_df_wt2_ns <- unij_0_dl_df |> dplyr::filter(uid %in% lunj_subs_wt2_ns)
nrow(lunj_0_dl_df_wt2_ns)
lunj_0_ol_df_wt2_ns <- unij_0_ol_df |> dplyr::filter(uid %in% lunj_subs_wt2_ns)
nrow(lunj_0_ol_df_wt2_ns)

lunj_l_dl_df_wt2_ns <- unij_l_dl_df |> dplyr::filter(uid %in% lunj_subs_wt2_ns)
nrow(lunj_l_dl_df_wt2_ns)
lunj_l_ol_df_wt2_ns <- unij_l_ol_df |> dplyr::filter(uid %in% lunj_subs_wt2_ns)
nrow(lunj_l_ol_df_wt2_ns)

comparison_dl_dfs <- list(
    "lmtb_0_dl_df" = lmtb_0_dl_df_wt2_ns,
    "lmtb_l_dl_df" = lmtb_l_dl_df_wt2_ns,
    "unij_0_dl_df" = unij_0_dl_df_wt2_ns,
    "unij_l_dl_df" = unij_l_dl_df_wt2_ns,
    "lunj_0_dl_df" = lunj_0_dl_df_wt2_ns,
    "lunj_l_dl_df" = lunj_l_dl_df_wt2_ns
)

comparison_ol_dfs <- list(
    "lmtb_0_ol_df" = lmtb_0_ol_df_wt2_ns,
    "lmtb_l_ol_df" = lmtb_l_ol_df_wt2_ns,
    "unij_0_ol_df" = unij_0_ol_df_wt2_ns,
    "unij_l_ol_df" = unij_l_ol_df_wt2_ns,
    "lunj_0_ol_df" = lunj_0_ol_df_wt2_ns,
    "lunj_l_ol_df" = lunj_l_ol_df_wt2_ns
)

saveRDS(comparison_dl_dfs, proc_path("comparison_dl_dfs.rds", TRUE))
saveRDS(comparison_ol_dfs, proc_path("comparison_ol_dfs.rds", TRUE))
```

```{r}
comparison_dl_dfs <- readRDS(proc_path("2025_06_16_comparison_dl_dfs.rds"))
comparison_ol_dfs <- readRDS(proc_path("2025_06_16_comparison_ol_dfs.rds"))
```

```{r}
classifier_ifts <- readRDS(proc_path("2025_06_13_classifier_ifts.rds"))

classifier_ft_dl_dfs <- lapply(
    comparison_dl_dfs,
    function(x) {
        x[, classifier_ifts]
    }
)
```

```{r}
# Extracted temporally sensitive features for all ABCD subjects at T0 and T2
temporal_df0 <- readRDS(proc_path("2025_06_13_temporal_df.rds"))
temporal_df2 <- readRDS(proc_path("2025_06_13_temporal_df2.rds"))

subtype_classifier <- readRDS(model_path("2025_06_13_subtype_classifier.rds"))
```

The scaling process that occurs below is described as follows.
Consider the data frame `lmtb_0_df`, which contains feature values for the longitudinal mTBI sample at baseline data collection timepoint.
A subset of the columns in `lmtb_0_df` are identified as temporally sensitive:

- brain_volume
- cortical_thickness
- cortical_sa
- pubertal_status_p
- pubertal_status_y
- age
- weekend_screentime
- weekday_screentime

Our goal is to re-scale these columns within `lmtb_0_df` based on the entire set of ABCD values of that feature for that time point.
The raw extracted set of ABCD values for those temporally sensitive features are found in `temporal_df0` (for T0 values), and `temporal_df2` (for T2 values).
However, scaling those data frames alone is insufficient, as we would not be making use of the missing values that we have imputed.
To account for this, we start by replacing the temporally sensitive features in `temporal_0_df` for the observations in `lmtb_0_df` with the values in `long_mtbi_0_df`.
That is, we inject our cleaned, imputed values for those temporally sensitive features and overwrite the raw extracted ones.
Then, we scale `temporal_df0`.
Finally, we extract our scaled values back into the original `lmtb_0_df`.
This process is made slightly more complicated by doing this process for all the baseline concussion and uninjured sampes simultaneously.

```{r}
# Cleaning up the UID column of the temporally sensitive feature data frames
temporal_df0$"uid" <- gsub("uid_", "", temporal_df0$"uid")
temporal_df2$"uid" <- gsub("uid_", "", temporal_df2$"uid")

# Remove the UID column
temporal_cols <- colnames(temporal_df0)

#"lmtb_0_dl_df" = lmtb_0_dl_df,
#"lmtb_l_dl_df" = lmtb_l_dl_df,
#"unij_0_dl_df" = unij_0_dl_df,
#"unij_l_dl_df" = unij_l_dl_df,
#"lunj_0_dl_df" = lunj_0_dl_df,
#"lunj_l_dl_df" = lunj_l_dl_df
#
#long_mtbi_subs
#
#base_unij_subs # <- A superset of long_unij_subs
#
#long_unij_subs
```

There is notably some overlap between the long_mtbi group and the base_unij group.
As such, we handle the sub-in and scale for the different groups here separately.

```{r}
swap_with_scaled <- function(reference_df, df_to_scale, scaling_cols) {
    reference_df <- reference_df |>
        dplyr::filter(!uid %in% df_to_scale$"uid")
    scaling_fts <- setdiff(scaling_cols, "uid")
    stacked_df <- rbind(
        reference_df,
        df_to_scale[, scaling_cols]
    )
    stacked_df[scaling_fts] <- sapply(stacked_df[scaling_fts], scale)
    rescaled_df <- df_to_scale |>
        dplyr::select(-dplyr::all_of(scaling_fts)) |>
        dplyr::inner_join(stacked_df, by = "uid") |>
        data.frame()
    return(rescaled_df)
}

unij_0_time_scaled <- swap_with_scaled(
    temporal_df0,
    comparison_dl_dfs$"unij_0_dl_df",
    temporal_cols
)
lmtb_0_time_scaled <- swap_with_scaled(
    temporal_df0,
    comparison_dl_dfs$"lmtb_0_dl_df",
    temporal_cols
)
lunj_0_time_scaled <- swap_with_scaled(
    temporal_df0,
    comparison_dl_dfs$"lunj_0_dl_df",
    temporal_cols
)
unij_l_time_scaled <- swap_with_scaled(
    temporal_df2,
    comparison_dl_dfs$"unij_l_dl_df",
    temporal_cols
)
lmtb_l_time_scaled <- swap_with_scaled(
    temporal_df2,
    comparison_dl_dfs$"lmtb_l_dl_df",
    temporal_cols
)
lunj_l_time_scaled <- swap_with_scaled(
    temporal_df2,
    comparison_dl_dfs$"lunj_l_dl_df",
    temporal_cols
)

saveRDS(unij_0_time_scaled, proc_path("unij_0_time_scaled.rds", TRUE))
saveRDS(lmtb_0_time_scaled, proc_path("lmtb_0_time_scaled.rds", TRUE))
saveRDS(lunj_0_time_scaled, proc_path("lunj_0_time_scaled.rds", TRUE))
saveRDS(unij_l_time_scaled, proc_path("unij_l_time_scaled.rds", TRUE))
saveRDS(lmtb_l_time_scaled, proc_path("lmtb_l_time_scaled.rds", TRUE))
saveRDS(lunj_l_time_scaled, proc_path("lunj_l_time_scaled.rds", TRUE))
```

At this point the temporally sensitive variables has been appropriately time scaled for all data frames.


```{r}
unij_0_time_scaled <- readRDS(proc_path("2025_06_16_unij_0_time_scaled.rds"))
lmtb_0_time_scaled <- readRDS(proc_path("2025_06_16_lmtb_0_time_scaled.rds"))
lunj_0_time_scaled <- readRDS(proc_path("2025_06_16_lunj_0_time_scaled.rds"))
unij_l_time_scaled <- readRDS(proc_path("2025_06_16_unij_l_time_scaled.rds"))
lmtb_l_time_scaled <- readRDS(proc_path("2025_06_16_lmtb_l_time_scaled.rds"))
lunj_l_time_scaled <- readRDS(proc_path("2025_06_16_lunj_l_time_scaled.rds"))
```

```{r}
make_pred_df <- function(df) {
    clean_df <- prep_data(df)
    df$"cluster" <- predict(subtype_classifier, newdata = clean_df)
    return(df)
}

unij_0_pred_df <- make_pred_df(unij_0_time_scaled)
lmtb_0_pred_df <- make_pred_df(lmtb_0_time_scaled)
lunj_0_pred_df <- make_pred_df(lunj_0_time_scaled)
unij_l_pred_df <- make_pred_df(unij_l_time_scaled)
lmtb_l_pred_df <- make_pred_df(lmtb_l_time_scaled)
lunj_l_pred_df <- make_pred_df(lunj_l_time_scaled)

write_csv(unij_0_pred_df, proc_path("unij_0_pred_df.csv", TRUE))
write_csv(lmtb_0_pred_df, proc_path("lmtb_0_pred_df.csv", TRUE))
write_csv(lunj_0_pred_df, proc_path("lunj_0_pred_df.csv", TRUE))
write_csv(unij_l_pred_df, proc_path("unij_l_pred_df.csv", TRUE))
write_csv(lmtb_l_pred_df, proc_path("lmtb_l_pred_df.csv", TRUE))
write_csv(lunj_l_pred_df, proc_path("lunj_l_pred_df.csv", TRUE))
```

```{r}
# CHECKPOINT
unij_0_pred_df <- read_csv(proc_path("2025_06_16_unij_0_pred_df.csv"))
lmtb_0_pred_df <- read_csv(proc_path("2025_06_16_lmtb_0_pred_df.csv"))
lunj_0_pred_df <- read_csv(proc_path("2025_06_16_lunj_0_pred_df.csv"))
unij_l_pred_df <- read_csv(proc_path("2025_06_16_unij_l_pred_df.csv"))
lmtb_l_pred_df <- read_csv(proc_path("2025_06_16_lmtb_l_pred_df.csv"))
lunj_l_pred_df <- read_csv(proc_path("2025_06_16_lunj_l_pred_df.csv"))
```

```{r}
unij_0_cluster_df <- dplyr::select(unij_0_pred_df, uid, cluster)
lmtb_0_cluster_df <- dplyr::select(lmtb_0_pred_df, uid, cluster)
lunj_0_cluster_df <- dplyr::select(lunj_0_pred_df, uid, cluster)
unij_l_cluster_df <- dplyr::select(unij_l_pred_df, uid, cluster)
lmtb_l_cluster_df <- dplyr::select(lmtb_l_pred_df, uid, cluster)
lunj_l_cluster_df <- dplyr::select(lunj_l_pred_df, uid, cluster)
```

```{r}
# Proportion of each cluster in the data frame
cluster_props <- function(cluster_df) {
    cluster_df$"cluster" |>
    table() |>
    prop.table() |>
    (\(x) 100 * x)()
}

cluster_props(unij_0_cluster_df) # 22.5, 40.4, 37.0

cluster_props(unij_l_cluster_df) # 15.5, 35.6, 48.9

cluster_props(lunj_0_cluster_df) # 21.9 40.3, 37.7

cluster_props(lunj_l_cluster_df) # 15.2, 35.4, 49.3

cluster_props(lmtb_0_cluster_df) # 15.6, 57.3, 27.0

cluster_props(lmtb_l_cluster_df) # 9.6, 51.4, 39.0

# Compare with the original full solution proportions
mtbi_ful_df <- readRDS(proc_path("2025_06_11_mtbi_ful_df.rds"))

cluster_props(mtbi_ful_df) # 32.3, 35.7, 32.0
```

```{r}
classifier_ifts <- readRDS(proc_path("2025_06_13_classifier_ifts.rds"))
ofts <- readRDS(proc_path("2025_06_11_ofts.rds"))
relevant_fts <- c(classifier_ifts, ofts)

export_wrapped_plots <- function(df,
                                 dl,
                                 ol,
                                 name,
                                 feature_set = NULL,
                                 w = 45,
                                 h = 30,
                                 rows = NULL,
                                 cols = NULL,
                                 dpi = 100,
                                 export = TRUE) {
    plot_list <- auto_plot(
        cluster_df = data.frame(df),
        dl = c(dl, ol)
    )
    wrapped_plots <- wrap_plots(
        plot_list[feature_set],
        nrow = rows,
        ncol = cols,
    )
    if (export) {
        ggsave(
            fig_path(name, TRUE),
            width = w,
            height = h,
            dpi = dpi
        )
    } else {
        return(plot_list)
    }
}

export_wrapped_plots(
    df = lmtb_0_cluster_df,
    dl = lmtb_0_dl,
    ol = lmtb_0_ol,
    feature_set = relevant_fts,
    name = "lmtb_0_pred_scaled_plot.png"
)
export_wrapped_plots(
    df = lmtb_l_cluster_df,
    dl = lmtb_l_dl,
    ol = lmtb_l_ol,
    feature_set = relevant_fts,
    name = "lmtb_l_pred_scaled_plot.png"
)

export_wrapped_plots(
    df = unij_0_cluster_df,
    dl = unij_0_dl,
    ol = unij_0_ol,
    feature_set = relevant_fts,
    name = "unij_0_pred_scaled_plot.png"
)

export_wrapped_plots(
    df = unij_l_cluster_df,
    dl = unij_l_dl,
    ol = unij_l_ol,
    feature_set = relevant_fts,
    name = "unij_l_pred_scaled_plot.png"
)

## Just top 10 features
#sorted_inputs <- readRDS(proc_path("2025_02_12_sorted_inputs.rds"))
#top_fts <- intersect(
#    c(sorted_inputs[1:10], outcome_fts),
#    relevant_fts
#)
#
#saveRDS(top_fts, proc_path("top_fts.rds", TRUE))
#top_fts <- readRDS(proc_path("2025_05_12_top_fts.rds"))

export_wrapped_plots(
    df = lmtb_0_cluster_df,
    dl = lmtb_0_dl,
    ol = lmtb_0_ol,
    feature_set = top_fts,
    rows = 2,
    w = 30,
    h = 7,
    name = "lmtb_0_pred_scaled_plot_top_fts.png"
)
export_wrapped_plots(
    df = lmtb_l_cluster_df,
    dl = lmtb_l_dl,
    ol = lmtb_l_ol,
    feature_set = top_fts,
    rows = 2,
    w = 30,
    h = 7,
    name = "lmtb_l_pred_scaled_plot_top_fts.png"
)
export_wrapped_plots(
    df = unij_0_cluster_df,
    dl = unij_0_dl,
    ol = unij_0_ol,
    feature_set = top_fts,
    rows = 2,
    w = 30,
    h = 7,
    name = "unij_0_pred_scaled_plot_top_fts.png"
)

export_wrapped_plots(
    df = unij_l_cluster_df,
    dl = unij_l_dl,
    ol = unij_l_ol,
    feature_set = top_fts,
    rows = 2,
    w = 30,
    h = 7,
    name = "unij_l_pred_scaled_plot_top_fts.png"
)

lunj_0_dl <- unij_0_dl |>
    dlapply(
        function(x) {
            x$"data" <- dplyr::filter(x$"data", uid %in% lunj_subs)
            return(x)
        }
    )
lunj_0_ol <- unij_0_ol |>
    dlapply(
        function(x) {
            x$"data" <- dplyr::filter(x$"data", uid %in% lunj_subs)
            return(x)
        }
    )
lunj_l_dl <- unij_l_dl |>
    dlapply(
        function(x) {
            x$"data" <- dplyr::filter(x$"data", uid %in% lunj_subs)
            return(x)
        }
    )
lunj_l_ol <- unij_l_ol |>
    dlapply(
        function(x) {
            x$"data" <- dplyr::filter(x$"data", uid %in% lunj_subs)
            return(x)
        }
    )

export_wrapped_plots(
    df = lunj_0_cluster_df,
    dl = lunj_0_dl,
    ol = lunj_0_ol,
    name = "lunj_0_pred_scaled_plot.png"
)

export_wrapped_plots(
    df = lunj_l_cluster_df,
    dl = lunj_l_dl,
    ol = lunj_l_ol,
    name = "lunj_l_pred_scaled_plot.png"
)

export_wrapped_plots(
    df = lunj_0_cluster_df,
    dl = lunj_0_dl,
    ol = lunj_0_ol,
    feature_set = top_fts,
    rows = 2,
    w = 30,
    h = 7,
    name = "lunj_0_pred_scaled_plot_top_fts.png"
)

export_wrapped_plots(
    df = lunj_l_cluster_df,
    dl = lunj_l_dl,
    ol = lunj_l_ol,
    feature_set = top_fts,
    rows = 2,
    w = 30,
    h = 7,
    name = "lunj_l_pred_scaled_plot_top_fts.png"
)
```

Just inputs:

```{r}

top_ins <- sorted_inputs[1:10]

export_wrapped_plots(
    df = long_mtbi_0_cluster_df,
    dl = long_mtbi_0_dl,
    ol = long_mtbi_0_ol,
    feature_set = top_ins,
    cols = 1,
    h = 27,
    w = 5,
    dpi = 80,
    name = "long_mtbi_0_pred_scaled_plot_top_ins.png"
)
export_wrapped_plots(
    df = long_mtbi_l_cluster_df,
    dl = long_mtbi_l_dl,
    ol = long_mtbi_l_ol,
    feature_set = top_ins,
    cols = 1,
    h = 27,
    w = 5,
    dpi = 80,
    name = "long_mtbi_l_pred_scaled_plot_top_ins.png"
)
export_wrapped_plots(
    df = base_unij_0_cluster_df,
    dl = base_unij_0_dl,
    ol = base_unij_0_ol,
    feature_set = top_ins,
    cols = 1,
    h = 27,
    w = 5,
    dpi = 80,
    name = "base_unij_0_pred_scaled_plot_top_ins.png"
)
export_wrapped_plots(
    df = base_unij_l_cluster_df,
    dl = base_unij_l_dl,
    ol = base_unij_l_ol,
    feature_set = top_ins,
    cols = 1,
    h = 27,
    w = 5,
    dpi = 80,
    name = "base_unij_l_pred_scaled_plot_top_ins.png"
)
export_wrapped_plots(
    df = long_unij_0_cluster_df,
    dl = long_unij_0_dl,
    ol = long_unij_0_ol,
    feature_set = top_ins,
    cols = 1,
    h = 27,
    w = 5,
    dpi = 80,
    name = "long_unij_0_pred_scaled_plot_top_ins.png"
)
export_wrapped_plots(
    df = long_unij_l_cluster_df,
    dl = long_unij_l_dl,
    ol = long_unij_l_ol,
    feature_set = top_ins,
    cols = 1,
    h = 27,
    w = 5,
    dpi = 80,
    name = "long_unij_l_pred_scaled_plot_top_ins.png"
)
```

Just outputs:

```{r}
export_wrapped_plots(
    df = long_mtbi_0_cluster_df,
    dl = long_mtbi_0_dl,
    ol = long_mtbi_0_ol,
    feature_set = outcome_fts,
    cols = 1,
    h = 24,
    w = 3,
    dpi = 80,
    name = "long_mtbi_0_pred_scaled_plot_outcome_fts.png"
)
export_wrapped_plots(
    df = long_mtbi_l_cluster_df,
    dl = long_mtbi_l_dl,
    ol = long_mtbi_l_ol,
    feature_set = outcome_fts,
    cols = 1,
    h = 24,
    w = 3,
    dpi = 80,
    name = "long_mtbi_l_pred_scaled_plot_outcome_fts.png"
)
export_wrapped_plots(
    df = base_unij_0_cluster_df,
    dl = base_unij_0_dl,
    ol = base_unij_0_ol,
    feature_set = outcome_fts,
    cols = 1,
    h = 24,
    w = 3,
    dpi = 80,
    name = "base_unij_0_pred_scaled_plot_outcome_fts.png"
)
export_wrapped_plots(
    df = base_unij_l_cluster_df,
    dl = base_unij_l_dl,
    ol = base_unij_l_ol,
    feature_set = outcome_fts,
    cols = 1,
    h = 24,
    w = 3,
    dpi = 80,
    name = "base_unij_l_pred_scaled_plot_outcome_fts.png"
)
export_wrapped_plots(
    df = long_unij_0_cluster_df,
    dl = long_unij_0_dl,
    ol = long_unij_0_ol,
    feature_set = outcome_fts,
    cols = 1,
    h = 24,
    w = 3,
    dpi = 80,
    name = "long_unij_0_pred_scaled_plot_outcome_fts.png"
)
export_wrapped_plots(
    df = long_unij_l_cluster_df,
    dl = long_unij_l_dl,
    ol = long_unij_l_ol,
    feature_set = outcome_fts,
    cols = 1,
    h = 24,
    w = 3,
    dpi = 80,
    name = "long_unij_l_pred_scaled_plot_outcome_fts.png"
)
```

Statistical analysis: bootstrapped similarity to baseline mTBI solution

```{r}
mtbi_gen_fts_table_hits_t <- read_csv(proc_path("2025_06_13_mtbi_gen_fts_table_hits_t.csv"))
mtbi_gen_long <- na.omit(mtbi_gen_fts_table_hits_t)

lmtb_0_data_df <- dplyr::inner_join(
    lmtb_0_cluster_df,
    as.data.frame(c(lmtb_0_dl, lmtb_0_ol)),
    by = "uid"
)

lmtb_l_data_df <- dplyr::inner_join(
    lmtb_l_cluster_df,
    as.data.frame(c(lmtb_l_dl, lmtb_l_ol)),
    by = "uid"
)

unij_0_data_df <- dplyr::inner_join(
    unij_0_cluster_df,
    as.data.frame(c(unij_0_dl, unij_0_ol)),
    by = "uid"
)

unij_l_data_df <- dplyr::inner_join(
    unij_l_cluster_df,
    as.data.frame(c(unij_l_dl, unij_l_ol)),
    by = "uid"
)

saveRDS(lmtb_0_data_df, proc_path("lmtb_0_data_df.rds", TRUE))
saveRDS(lmtb_l_data_df, proc_path("lmtb_l_data_df.rds", TRUE))
saveRDS(unij_0_data_df, proc_path("unij_0_data_df.rds", TRUE))
saveRDS(unij_l_data_df, proc_path("unij_l_data_df.rds", TRUE))
```

```{r}
mtbi_gen_fts_table_hits_t <- read_csv(proc_path("2025_06_13_mtbi_gen_fts_table_hits_t.csv"))
mtbi_gen_long <- na.omit(mtbi_gen_fts_table_hits_t)

lmtb_0_data_df <- readRDS(proc_path("2025_06_17_lmtb_0_data_df.rds"))
lmtb_l_data_df <- readRDS(proc_path("2025_06_17_lmtb_l_data_df.rds"))
unij_0_data_df <- readRDS(proc_path("2025_06_17_unij_0_data_df.rds"))
unij_l_data_df <- readRDS(proc_path("2025_06_17_unij_l_data_df.rds"))
```

```{r}
topologizer <- function(df) {
    df <- data.frame(df)
    df <- metasnf:::numcol_to_numeric(df)
    df <- dummy_non_numeric(dplyr::select(df, -"uid"))
    summary_df <- data.frame(
        "feature" = as.character(),
        "type" = as.character(),
        "summary" = as.character(),
        "c1_mean" = as.numeric(),
        "c2_mean" = as.numeric(),
        "c3_mean" = as.numeric(),
        "c1_c2_es" = as.numeric(),
        "c1_c2_l" = as.numeric(),
        "c1_c2_u" = as.numeric(),
        "c1_c3_es" = as.numeric(),
        "c1_c3_l" = as.numeric(),
        "c1_c3_u" = as.numeric(),
        "c2_c3_es" = as.numeric(),
        "c2_c3_l" = as.numeric(),
        "c2_c3_u" = as.numeric()
    )
    c1 <- df[df$"cluster" == 1, ]
    c2 <- df[df$"cluster" == 2, ]
    c3 <- df[df$"cluster" == 3, ]
    features <- df |>
        dplyr::select(-"cluster") |>
        colnames()
    ###########################################################################
    # Check if features are binary (unique values are 0 and 1) or not
    ###########################################################################
    for (feature in features) {
        f1 <- c1[, feature]
        f2 <- c2[, feature]
        f3 <- c3[, feature]
        means <- c("1" = mean(f1), "2" = mean(f2), "3" = mean(f3))
        full_summary <- paste(
            names(sort(means, decreasing = TRUE)),
            collapse = " > "
        )
        if (is_binary(df[, feature])) {
            sum_1_v_2 <- calc_propes(f1, f2)
            sum_1_v_3 <- calc_propes(f1, f3)
            sum_2_v_3 <- calc_propes(f2, f3)
            type <- "or"
        } else {
            sum_1_v_2 <- calc_des(f1, f2)
            sum_1_v_3 <- calc_des(f1, f3)
            sum_2_v_3 <- calc_des(f2, f3)
            type <- "d"
        }
        summary_df <- rbind(
            summary_df,
            data.frame(
                "feature" = feature,
                "summary" = full_summary,
                "c1" = signif(mean(f1), 3),
                "c2" = signif(mean(f2), 3),
                "c3" = signif(mean(f3), 3),
                "es" = type,
                "c12_es" = sum_1_v_2$"es",
                "c12_l" = sum_1_v_2$"l",
                "c12_u" = sum_1_v_2$"u",
                "c13_es" = sum_1_v_3$"es",
                "c13_l" = sum_1_v_3$"l",
                "c13_u" = sum_1_v_3$"u",
                "c23_es" = sum_2_v_3$"es",
                "c23_l" = sum_2_v_3$"l",
                "c23_u" = sum_2_v_3$"u"
            )
        )
    }
    return(summary_df)
}

concordance_w_mtbi <- function(data_df, n = NULL, iters = 10, procs = 1) {
    if (is.null(n)) {
        n <- nrow(data_df)
    }
    p <- progressr::progressor(steps = iters)
    future::plan(
        future::multisession,
        workers = procs
    )
    res <- future.apply::future_lapply(
        1:iters,
        future.seed = TRUE,
        function(x, p) {
            start <- Sys.time()
            bootstrap_sample <- sample(n, replace = TRUE)
            sampled_df <- data_df[bootstrap_sample, ]
            tops_df <- topologizer(sampled_df)
            gen_tops_df <- generalizable_features(tops_df, compare_fn_a)
            gen_tops_df_long <- gen_tops_df |>
                pivot_longer(
                    cols = -feature,
                    names_to = "comparison",
                    values_to = "order_sample"
                )
            joint_df <- dplyr::left_join(
                mtbi_gen_long, # reference data frame
                gen_tops_df_long, # sampled data frame
                by = c("feature", "comparison")
            ) |>
                dplyr::mutate(
                    match = ifelse(order_sample == order, 1, 0)
                ) |>
                dplyr::filter(!grepl("mtbi", feature))
            p()
            concordance <- sum(joint_df$"match") / nrow(joint_df)
            return(concordance)
        },
        p = p
    )
    future::plan(future::sequential)
    return(unlist(res))
}

concordance_w_mtbi_test <- function(df1, df2, n = NULL, iters = 10, procs = 1) {
    if (is.null(n)) {
        n <- nrow(df1)
    }
    p <- progressr::progressor(steps = iters)
    future::plan(
        future::multisession,
        workers = procs
    )
    res <- future.apply::future_lapply(
        1:iters,
        future.seed = TRUE,
        function(x, p) {
            start <- Sys.time()
            bootstrap_sample <- sample(n, replace = TRUE)
            sampled_df1 <- df1[bootstrap_sample, ]
            sampled_df2 <- df2[bootstrap_sample, ]
            tops_df1 <- topologizer(sampled_df1)
            tops_df2 <- topologizer(sampled_df2)
            gen_tops_df1 <- generalizable_features(tops_df1, compare_fn_a)
            gen_tops_df2 <- generalizable_features(tops_df2, compare_fn_a)
            gen_tops_df_long1 <- gen_tops_df1 |>
                pivot_longer(
                    cols = -feature,
                    names_to = "comparison",
                    values_to = "order_sample"
                )
            gen_tops_df_long2 <- gen_tops_df2 |>
                pivot_longer(
                    cols = -feature,
                    names_to = "comparison",
                    values_to = "order_sample"
                )
            joint_df1 <- dplyr::left_join(
                mtbi_gen_long, # reference data frame
                gen_tops_df_long1, # sampled data frame
                by = c("feature", "comparison")
            ) |>
                dplyr::mutate(
                    match = ifelse(order_sample == order, 1, 0)
                ) |>
                dplyr::filter(!grepl("mtbi", feature))
            joint_df2 <- dplyr::left_join(
                mtbi_gen_long, # reference data frame
                gen_tops_df_long2, # sampled data frame
                by = c("feature", "comparison")
            ) |>
                dplyr::mutate(
                    match = ifelse(order_sample == order, 1, 0)
                ) |>
                dplyr::filter(!grepl("mtbi", feature))
            p()
            concordance1 <- sum(joint_df1$"match") / nrow(joint_df1)
            concordance2 <- sum(joint_df2$"match") / nrow(joint_df2)
            return(concordance2 - concordance1)
        },
        p = p
    )
    future::plan(future::sequential)
    return(unlist(res))
}


# HERE
set.seed(42)
start <- Sys.time()
progressr::with_progress({
    lmtb_0_pred_conc <- concordance_w_mtbi(lmtb_0_data_df, iters = 1000, procs = 8)
})
lmtb_0_pred_conc
print(Sys.time() - start)
saveRDS(lmtb_0_pred_conc, proc_path("lmtb_0_pred_conc.rds", TRUE))

set.seed(42)
start <- Sys.time()
progressr::with_progress({
    lmtb_l_pred_conc <- concordance_w_mtbi(lmtb_l_data_df, iters = 1000, procs = 8)
})
lmtb_l_pred_conc
print(Sys.time() - start)
saveRDS(lmtb_l_pred_conc, proc_path("lmtb_l_pred_conc.rds", TRUE))

set.seed(42)
start <- Sys.time()
progressr::with_progress({
    unij_0_pred_conc <- concordance_w_mtbi(unij_0_data_df, n = 218, iters = 1000, procs = 8)
})
unij_0_pred_conc
print(Sys.time() - start)
saveRDS(unij_0_pred_conc, proc_path("unij_0_pred_conc.rds", TRUE))
set.seed(42)
start <- Sys.time()
progressr::with_progress({
    unij_l_pred_conc <- concordance_w_mtbi(unij_l_data_df, n = 218, iters = 1000, procs = 8)
})
unij_l_pred_conc
print(Sys.time() - start)
saveRDS(unij_l_pred_conc, proc_path("unij_l_pred_conc.rds", TRUE))

# Test style:
set.seed(42)
start <- Sys.time()
progressr::with_progress({
    lmtb_pred_conc_test <- concordance_w_mtbi_test(
        df1 = lmtb_0_data_df, df2 = lmtb_l_data_df,  iters = 1000, procs = 5
    )
})
print(Sys.time() - start)

saveRDS(lmtb_pred_conc_test, proc_path("lmtb_pred_conc_test.rds", TRUE))

lmtb_pred_conc_test <- readRDS(proc_path("2025_06_17_lmtb_pred_conc_test.rds"))

# [-0.080, 0.117]
quantile(lmtb_pred_conc_test, c(0.025, 0.975), na.rm = TRUE)
```

So we can say that there's no significant difference in how similar the pre-injury/post-injury group is to the baseline mTBI group.

```{r}
lmtb_0_pred_conc <- readRDS(proc_path("2025_06_17_lmtb_0_pred_conc.rds"))
lmtb_l_pred_conc <- readRDS(proc_path("2025_06_17_lmtb_l_pred_conc.rds"))

unij_0_pred_conc <- readRDS(proc_path("2025_06_17_unij_0_pred_conc.rds"))
unij_l_pred_conc <- readRDS(proc_path("2025_06_17_unij_l_pred_conc.rds"))

mean(na.omit(lmtb_0_pred_conc))
mean(na.omit(lmtb_l_pred_conc))

mean(na.omit(unij_0_pred_conc))
mean(na.omit(unij_l_pred_conc))

sims_pre <- na.omit(lmtb_0_pred_conc)
sims_post <- na.omit(lmtb_l_pred_conc)

ci_solo_pre <- quantile(sims_pre, probs = c(0.025, 0.975))
mean(sims_pre) # 0.7791422
ci_solo_pre # 0.7153285, 0.8394161

ci_solo_post <- quantile(sims_post, probs = c(0.025, 0.975))
mean(sims_post) # 0.7964491
ci_solo_post #0.7299270, 0.8540146

lmtb_0_conc_data <- data.frame(group = "lmtb_0", x = na.omit(lmtb_0_pred_conc))
lmtb_l_conc_data <- data.frame(group = "lmtb_l", x = na.omit(lmtb_l_pred_conc))
unij_0_conc_data <- data.frame(group = "unij_0", x = na.omit(unij_0_pred_conc))
unij_l_conc_data <- data.frame(group = "unij_l", x = na.omit(unij_l_pred_conc))
```

### Meta clustering the longitudinal timepoint for baseline concussion group# {{{

```{r}
## CHECKPOINT
#base_mtbi_l_dls <- all_long_dls$"base_mtbi_l_dls"
#base_mtbi_l_ols <- all_long_dls$"base_mtbi_l_ols"
#
#set.seed(42)
#long_base_mtbi_config <- snf_config(
#    base_mtbi_l_dls[[1]],
#    n_solutions = 200,
#    cnt_dist_fns = list(
#        "standard_norm_euclidean" = sn_euclidean_distance
#    ),
#    dsc_dist_fns = list(
#        "standard_norm_euclidean" = sn_euclidean_distance
#    ),
#    ord_dist_fns = list(
#        "standard_norm_euclidean" = sn_euclidean_distance
#    ),
#    use_default_dist_fns = TRUE
#)
#
#saveRDS(long_base_mtbi_config, proc_path("long_base_mtbi_config.rds", TRUE))
#
## CHECKPOINT
#long_base_mtbi_config <- readRDS(proc_path("2025_02_18_long_base_mtbi_config.rds"))

#base_mtbi_l_sol_df_s1 <- batch_snf(
#    dl = base_mtbi_l_dls[[1]],
#    sc = long_base_mtbi_config,
#    processes = "max"
#)
#saveRDS(base_mtbi_l_sol_df_s1, proc_path("base_mtbi_l_sol_df_s1.rds", TRUE))
#
#base_mtbi_l_sol_df_s2 <- batch_snf(
#    dl = base_mtbi_l_dls[[2]],
#    sc = long_base_mtbi_config,
#    processes = "max"
#)
#saveRDS(base_mtbi_l_sol_df_s2, proc_path("base_mtbi_l_sol_df_s2.rds", TRUE))
#
#base_mtbi_l_sol_df_s3 <- batch_snf(
#    dl = base_mtbi_l_dls[[3]],
#    sc = long_base_mtbi_config,
#    processes = "max"
#)
#saveRDS(base_mtbi_l_sol_df_s3, proc_path("base_mtbi_l_sol_df_s3.rds", TRUE))
#
#base_mtbi_l_sol_df_s4 <- batch_snf(
#    dl = base_mtbi_l_dls[[4]],
#    sc = long_base_mtbi_config,
#    processes = "max"
#)
#saveRDS(base_mtbi_l_sol_df_s4, proc_path("base_mtbi_l_sol_df_s4.rds", TRUE))
#
#base_mtbi_l_sol_df_s5 <- batch_snf(
#    dl = base_mtbi_l_dls[[5]],
#    sc = long_base_mtbi_config,
#    processes = "max"
#)
#saveRDS(base_mtbi_l_sol_df_s5, proc_path("base_mtbi_l_sol_df_s5.rds", TRUE))

#base_mtbi_l_sol_df_s1 <- readRDS(proc_path("2025_02_18_base_mtbi_l_sol_df_s1.rds"))
#base_mtbi_l_sol_df_s2 <- readRDS(proc_path("2025_02_18_base_mtbi_l_sol_df_s2.rds"))
#base_mtbi_l_sol_df_s3 <- readRDS(proc_path("2025_02_18_base_mtbi_l_sol_df_s3.rds"))
#base_mtbi_l_sol_df_s4 <- readRDS(proc_path("2025_02_18_base_mtbi_l_sol_df_s4.rds"))
#base_mtbi_l_sol_df_s5 <- readRDS(proc_path("2025_02_18_base_mtbi_l_sol_df_s5.rds"))
#
#base_mtbi_l_sol_df <- do.call(
#    "rbind",
#    c(
#        list(
#            base_mtbi_l_sol_df_s1,
#            base_mtbi_l_sol_df_s2,
#            base_mtbi_l_sol_df_s3,
#            base_mtbi_l_sol_df_s4,
#            base_mtbi_l_sol_df_s5
#        ),
#        list(reset_indices = TRUE)
#    )
#)
#saveRDS(base_mtbi_l_sol_df, proc_path("base_mtbi_l_sol_df.rds", TRUE))
#
#base_mtbi_l_ari <- calc_aris(base_mtbi_l_sol_df, processes = "max")
#saveRDS(base_mtbi_l_ari, proc_path("base_mtbi_l_ari.rds", TRUE))
#
#base_mtbi_l_ari_order <- get_matrix_order(base_mtbi_l_ari)
#write_csv(data.frame(base_mtbi_l_ari_order), proc_path("base_mtbi_l_ari_order.csv", TRUE))

## CHECKPOINT
#base_mtbi_l_sol_df <- readRDS(proc_path("2025_02_18_base_mtbi_l_sol_df.rds"))
#base_mtbi_l_ari <- readRDS(proc_path("2025_02_18_base_mtbi_l_ari.rds"))
#base_mtbi_l_ari_order <- unlist(read_csv(proc_path("2025_02_18_base_mtbi_l_ari_order.csv")))
#names(base_mtbi_l_ari_order) <- NULL

## Solo imputation 1
#base_mtbi_l_ext_sol_df_s1 <- extend_solutions(
#    base_mtbi_l_sol_df[1:200, ],
#    dl = base_mtbi_l_dls[[1]],
#    target_dl = base_mtbi_l_ols[[1]],
#    min_pval = 1e-10,
#    processes = "max"
#)
#saveRDS(base_mtbi_l_ext_sol_df_s1, proc_path("base_mtbi_l_ext_sol_df_s1.rds", TRUE))
## Solo imputation 2
#base_mtbi_l_ext_sol_df_s2 <- extend_solutions(
#    base_mtbi_l_sol_df[201:400, ],
#    dl = base_mtbi_l_dls[[2]],
#    target_dl = base_mtbi_l_ols[[2]],
#    min_pval = 1e-10,
#    processes = "max"
#)
#saveRDS(base_mtbi_l_ext_sol_df_s2, proc_path("base_mtbi_l_ext_sol_df_s2.rds", TRUE))
## Solo imputation 3
#base_mtbi_l_ext_sol_df_s3 <- extend_solutions(
#    base_mtbi_l_sol_df[401:600, ],
#    dl = base_mtbi_l_dls[[3]],
#    target_dl = base_mtbi_l_ols[[3]],
#    min_pval = 1e-10,
#    processes = "max"
#)
#saveRDS(base_mtbi_l_ext_sol_df_s3, proc_path("base_mtbi_l_ext_sol_df_s3.rds", TRUE))
## Solo imputation 4
#base_mtbi_l_ext_sol_df_s4 <- extend_solutions(
#    base_mtbi_l_sol_df[601:800, ],
#    dl = base_mtbi_l_dls[[4]],
#    target_dl = base_mtbi_l_ols[[4]],
#    min_pval = 1e-10,
#    processes = "max"
#)
#saveRDS(base_mtbi_l_ext_sol_df_s4, proc_path("base_mtbi_l_ext_sol_df_s4.rds", TRUE))
## Solo imputation 5
#base_mtbi_l_ext_sol_df_s5 <- extend_solutions(
#    base_mtbi_l_sol_df[801:1000, ],
#    dl = base_mtbi_l_dls[[5]],
#    target_dl = base_mtbi_l_ols[[5]],
#    min_pval = 1e-10,
#    processes = "max"
#)
#saveRDS(base_mtbi_l_ext_sol_df_s5, proc_path("base_mtbi_l_ext_sol_df_s5.rds", TRUE))

#base_mtbi_l_ext_sol_df_s1 <- readRDS(proc_path("2025_02_18_base_mtbi_l_ext_sol_df_s1.rds"))
#base_mtbi_l_ext_sol_df_s2 <- readRDS(proc_path("2025_02_18_base_mtbi_l_ext_sol_df_s2.rds"))
#base_mtbi_l_ext_sol_df_s3 <- readRDS(proc_path("2025_02_18_base_mtbi_l_ext_sol_df_s3.rds"))
#base_mtbi_l_ext_sol_df_s4 <- readRDS(proc_path("2025_02_18_base_mtbi_l_ext_sol_df_s4.rds"))
#base_mtbi_l_ext_sol_df_s5 <- readRDS(proc_path("2025_02_18_base_mtbi_l_ext_sol_df_s5.rds"))
#
#base_mtbi_l_ext_sol_df <- do.call(
#    "rbind",
#    c(
#        list(
#            base_mtbi_l_ext_sol_df_s1,
#            base_mtbi_l_ext_sol_df_s2,
#            base_mtbi_l_ext_sol_df_s3,
#            base_mtbi_l_ext_sol_df_s4,
#            base_mtbi_l_ext_sol_df_s5
#        ),
#        list(reset_indices = TRUE)
#    )
#)
#
#saveRDS(base_mtbi_l_ext_sol_df, proc_path("base_mtbi_l_ext_sol_df.rds", TRUE))
#
#base_mtbi_l_ext_sol_df <- readRDS(proc_path("2025_02_18_base_mtbi_l_ext_sol_df.rds"))

#base_mtbi_l_hm <- meta_cluster_heatmap(base_mtbi_l_ari, order = base_mtbi_l_ari_order)
#base_mtbi_l_esdf <- as.data.frame(base_mtbi_l_ext_sol_df)
#base_mtbi_l_esdf$"impairment_separation" <- -log10(base_mtbi_l_esdf$"mean_pval")
#
## It's there!
#full_base_mtbi_l_ari_hm <- meta_cluster_heatmap(
#    aris = base_mtbi_l_ari,
#    order = base_mtbi_l_ari_order,
#    data = base_mtbi_l_esdf,
#    min_colour = "black",
#    top_hm = list(
#        "Impairment Separation" = "impairment_separation"
#    ),
#    top_bar = list(
#        "Number of Clusters" = "nclust"
#    ),
#    annotation_colours = list(
#        "Impairment Separation" = colour_scale(
#            base_mtbi_l_esdf$"impairment_separation",
#            min_colour = "gray7",
#            max_colour = "limegreen"
#        )
#    )
#)
#full_base_mtbi_l_ari_hm
#
#save_heatmap(
#    heatmap = full_base_mtbi_l_ari_hm,
#    path = fig_path("full_base_mtbi_l_ari_hm.png", TRUE),
#    width = 950,
#    height = 900,
#    res = 100
#)
#
```

So the baseline mTBI subjects do seem to have it!


## Moving on: Change in outcomes

If I go back to when I was about to run extend solutions, and instead try to find any meta clusters associated with change in outcome measures, do I find anything interesting?

```{r}
#full_dl_0 <- readRDS(input_path("2025_02_12_mtbi_full_data_list_1.rds"))
#full_ol_0 <- readRDS(input_path("2025_02_12_mtbi_full_oom_list_1.rds"))
#
#full_ol_2 <- all_long_dls$"base_mtbi_l_ols"[[1]]
#
#full_ol_0_df <- as.data.frame(full_ol_0)
#full_ol_2_df <- as.data.frame(full_ol_2)
#
#full_ol_change_df$"cbcl_anxdep" <- full_ol_2_df$"cbcl_anxdep" - full_ol_0_df$"cbcl_anxdep"
#full_ol_change_df$"cbcl_withdep" <- full_ol_2_df$"cbcl_withdep" - full_ol_0_df$"cbcl_withdep"
#full_ol_change_df$"cbcl_somatic" <- full_ol_2_df$"cbcl_somatic" - full_ol_0_df$"cbcl_somatic"
#full_ol_change_df$"cbcl_social" <- full_ol_2_df$"cbcl_social" - full_ol_0_df$"cbcl_social"
#full_ol_change_df$"cbcl_thought" <- full_ol_2_df$"cbcl_thought" - full_ol_0_df$"cbcl_thought"
#full_ol_change_df$"cbcl_attention" <- full_ol_2_df$"cbcl_attention" - full_ol_0_df$"cbcl_attention"
#full_ol_change_df$"cbcl_rulebreak" <- full_ol_2_df$"cbcl_rulebreak" - full_ol_0_df$"cbcl_rulebreak"
#full_ol_change_df$"cbcl_aggressive" <- full_ol_2_df$"cbcl_aggressive" - full_ol_0_df$"cbcl_aggressive"
#full_ol_change_df$"sds_sleep" <- full_ol_2_df$"sds_sleep" - full_ol_0_df$"sds_sleep"
#full_ol_change_df$"uid" <- gsub("uid_", "", full_ol_change_df$"uid")
#
#full_ol_change <- data_list(
#    list(dplyr::select(full_ol_change_df, uid, dplyr::starts_with("cbcl")), "cbcl", "B", "discrete"),
#    list(dplyr::select(full_ol_change_df, uid, dplyr::starts_with("sds")), "sds", "B", "discrete"),
#    uid = "uid"
#)
#
#saveRDS(full_ol_change, proc_path("full_ol_change.rds", TRUE))
#
#full_ol_change <- readRDS(proc_path("2025_02_18_full_ol_change.rds"))
#mtbi_full_sol_df <- readRDS(proc_path("2025_02_12_mtbi_full_sol_df.rds"))
#
#mtbi_full_change_ext_sol_df <- extend_solutions(
#    mtbi_full_sol_df,
#    target_dl = full_ol_change,
#    min_pval = 1e-10,
#    processes = "max"
#)
#
#saveRDS(mtbi_full_change_ext_sol_df, proc_path("mtbi_full_change_ext_sol_df.rds", TRUE))
#
#mtbi_full_change_ext_sol_df <- readRDS(proc_path("2025_02_18_mtbi_full_change_ext_sol_df.rds"))
#
#mtbi_full_change_ari <- calc_aris(mtbi_full_change_ext_sol_df)
#
#saveRDS(mtbi_full_change_ari, proc_path("mtbi_full_change_ari.rds", TRUE))
#mtbi_full_change_ari <- readRDS(proc_path("2025_02_18_mtbi_full_change_ari.rds"))
#
#full_change_order <- get_matrix_order(mtbi_full_change_ari)
#
#saveRDS(full_change_order, proc_path("full_change_order.rds", TRUE))
#full_change_order <- readRDS(proc_path("2025_02_18_full_change_order.rds"))
#
#full_change_esdf <- as.data.frame(mtbi_full_change_ext_sol_df)
#
#full_change_esdf$"impairment_separation" <- -log10(full_change_esdf$"mean_pval")
#
#full_change_mc_hm <- meta_cluster_heatmap(
#    aris = mtbi_full_change_ari,
#    order = full_change_order,
#    data = full_change_esdf,
#    split_vector = c(
#        48,
#        54,
#        95,
#        136,
#        147
#    ),
#    top_hm = list(
#        "Impairment Separation" = "impairment_separation"
#    ),
#    top_bar = list(
#        "Number of Clusters" = "nclust"
#    ),
#    annotation_colours = list(
#        "Impairment Separation" = colour_scale(
#            full_change_esdf$"impairment_separation",
#            min_colour = "gray7",
#            max_colour = "limegreen"
#        )
#    )
#)
#
#save_heatmap(
#    heatmap = full_change_mc_hm,
#    path = fig_path("full_change_mc_hm.png", TRUE),
#    width = 950,
#    height = 900,
#    res = 100
#)
#
#change_mc_sol_df <- label_meta_clusters(
#    mtbi_full_change_ext_sol_df,
#    order = full_change_order,
#    split_vector = c(
#        48,
#        54,
#        95,
#        136,
#        147
#    )
#)
#
#change_rep_solutions <- get_representative_solutions(
#    mtbi_full_change_ari,
#    change_mc_sol_df
#)
#
#top_change_esdf <- change_rep_solutions[2, ]
#
#saveRDS(top_change_esdf, proc_path("top_change_esdf.rds", TRUE))
#top_change_esdf <- readRDS(proc_path("2025_02_18_top_change_esdf.rds"))
#
## Adding in the input features as well
#top_change_esdf2 <- extend_solutions(
#    mtbi_full_sol_df[54, ],
#    dl = full_dl_0,
#    target_dl = full_ol_change,
#    min_pval = 1e-10,
#    processes = "max"
#)
#
#top_change_esdf2$"mc" <- "B"
#
#saveRDS(top_change_esdf2, proc_path("top_change_esdf2.rds", TRUE))
#top_change_esdf2 <- readRDS(proc_path("2025_02_18_top_change_esdf2.rds"))
#
#top_change_manhattan <- mc_manhattan_plot(
#    top_change_esdf2,
#    dl = full_dl_0,
#    target_dl = full_ol_change,
#    domain_colours = c(
#        "AS" = "#85929e",
#        "D" = "#bb8fce",
#        "N" = "#e59866",
#        "MH" = "#7fb3d5",
#        "P" = "#52be80",
#        "S" = "#d98880",
#        "B" = "#ff3131"
#    )
#)
#
#ggsave(
#    plot = top_change_manhattan,
#    filename = fig_path("top_change_manhattan.png", TRUE),
#    width = 18,
#    height = 5,
#    dpi = 120
#)
#
#change_pl <- auto_plot(
#    top_change_esdf2,
#    dl = c(full_dl_0, full_ol_change),
#    verbose = TRUE
#)
#
#change_pl_wrapped <- wrap_plots(change_pl)
#
#ggsave(
#    fig_path("change_pl_wrapped.png", TRUE),
#    change_pl_wrapped,
#    width = 45,
#    height = 30,
#    dpi = 50
#)
```

Not all that interesting; kids who had worse scores to begin with have an easier time getting better.# }}}
