# Matching

This chapter contains:

1. Derivation of subtypes from a variety of matched uninjured groups
2. Comparison of those subtypes with the mTBI baseline solution

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)
library(MatchIt)
library(tibble)
library(ggplot2)
library(fastDummies)
library(dplyr)
library(tidyr)
library(xtable)
library(patchwork)

input_path   <- path_maker(here(paste0("data/abcd/inputs")))
proc_path    <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path     <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path     <- path_maker(here(paste0("data/abcd/subjects")))
model_path   <- path_maker(here(paste0("data/abcd/results/models")))
unij_ns_subs <- readRDS(sub_path("2025_06_11_unij_no_sibs_subs.rds"))
```

## Importing data

```{r}
all_dls_h_ns <- readRDS(proc_path("2025_06_11_all_dls_h_no_sibs.rds"))

#mtbi_full_data_list_1 <- readRDS(input_path("2025_02_12_mtbi_full_data_list_1.rds"))
#mtbi_full_oom_list_1 <- readRDS(input_path("2025_02_12_mtbi_full_oom_list_1.rds"))
#mtbi_full_top_3c <- readRDS(proc_path("2025_02_13_mtbi_full_top_3c.rds"))

mtbi_dl_1 <- readRDS(input_path("2025_06_11_mtbi_dl_1.rds"))
mtbi_ol_1 <- readRDS(input_path("2025_06_11_mtbi_ol_1.rds"))
mtbi_top_solution <- readRDS(proc_path("2025_06_11_mtbi_top_solution.rds"))

names(all_dls_h_ns)

unij_dl_u1 <- all_dls_h_ns$"unij_all_u_dls"$"imp_1"
unij_dl_p1 <- all_dls_h_ns$"unij_all_p_dls"$"imp_1"
unij_ol_u1 <- all_dls_h_ns$"unij_all_u_ols"$"imp_1"
unij_ol_p1 <- all_dls_h_ns$"unij_all_p_ols"$"imp_1"
```

## Matching

Finding matched uninjured controls for each mtbi subject based on a variety of variables.
Matching will be done based on the first imputed dataset of the baseline data.

```{r}
# mTBI group, first imputation
mtbi_matching_df <- as.data.frame(c(mtbi_dl_1, mtbi_ol_1))

# Uninjured group, first solo imputation
unij_matching_df_u1 <- as.data.frame(c(unij_dl_u1, unij_ol_u1))

# Uninjured group, first pooled imputation
unij_matching_df_p1 <- as.data.frame(c(unij_dl_p1, unij_ol_p1))

# Labeling if each group was or was not mTBI
mtbi_matching_df$"mtbi" <- 1
unij_matching_df_u1$"mtbi" <- 0
unij_matching_df_p1$"mtbi" <- 0

# Restricting mTBI data frame to only columns shared with uninjured
mtbi_matching_df <- dplyr::select(
    mtbi_matching_df,
    colnames(unij_matching_df_u1)
)

# Concatenating mTBI and uninjured data frames for matching
matching_df_u1 <- rbind(mtbi_matching_df, unij_matching_df_u1)
matching_df_p1 <- rbind(mtbi_matching_df, unij_matching_df_p1)
```


```{r}
# Creating parent psych matching variable
matching_df_u1$"total_parent_psych" <- matching_df_u1 |>
    dplyr::select(dplyr::starts_with("parent")) |>
    rowSums()
matching_df_p1$"total_parent_psych" <- matching_df_p1 |>
    dplyr::select(dplyr::starts_with("parent")) |>
    rowSums()

# Creating outcome matching variable
matching_df_u1$"total_impairments" <- matching_df_u1 |>
    dplyr::select(dplyr::starts_with("cbcl"), dplyr::starts_with("sds")) |>
    rowSums()
matching_df_p1$"total_impairments" <- matching_df_p1 |>
    dplyr::select(dplyr::starts_with("cbcl"), dplyr::starts_with("sds")) |>
    rowSums()
```

I investigate the following matching schemes:

1. Demographic matching (household income, race, sex, parent and youth reports of pubertal status; d)
2. Parent psychosocial matching (total parent psychosocial score; p)
3. Outcome matching (total impairments; o)
4. Demographic and parent psychosocial matching together (dp)
5. Demographic and outcome matching together (do)
6. Parent psychosocial and outcome matching together (op)
7. Demographic, parent psychosocial, and outcome matching together (dpo)

```{r}
# Establishing formulae
d_vars <- paste(
    "household_income",
    "race",
    "sex",
    "age",
    "pubertal_status_p",
    "pubertal_status_y",
    sep = " + "
)
p_vars <- "total_parent_psych"
o_vars <- "total_impairments"
dp_vars <- paste0(d_vars, " + ", p_vars)
do_vars <- paste0(d_vars, " + ", o_vars)
op_vars <- paste0(o_vars, " + ", p_vars)
dpo_vars <- paste0(d_vars, " + ", p_vars, " + ", o_vars)

match_d_results_u <- matchit(
    as.formula(paste0("mtbi ~ ", d_vars)), matching_df_u1, method = "nearest"
)
match_p_results_u <- matchit(
    as.formula(paste0("mtbi ~ ", p_vars)), matching_df_u1, method = "nearest"
)
match_o_results_u <- matchit(
    as.formula(paste0("mtbi ~ ", o_vars)), matching_df_u1, method = "nearest"
)

match_d_results_p <- matchit(
    as.formula(paste0("mtbi ~ ", d_vars)), matching_df_p1, method = "nearest"
)
match_p_results_p <- matchit(
    as.formula(paste0("mtbi ~ ", p_vars)), matching_df_p1, method = "nearest"
)
match_o_results_p <- matchit(
    as.formula(paste0("mtbi ~ ", o_vars)), matching_df_p1, method = "nearest"
)

match_dp_results_u <- matchit(
    as.formula(paste0("mtbi ~ ", dp_vars)), matching_df_u1, method = "nearest"
)
match_do_results_u <- matchit(
    as.formula(paste0("mtbi ~ ", op_vars)), matching_df_u1, method = "nearest"
)
match_op_results_u <- matchit(
    as.formula(paste0("mtbi ~ ", op_vars)), matching_df_u1, method = "nearest"
)

match_dp_results_p <- matchit(
    as.formula(paste0("mtbi ~ ", dp_vars)), matching_df_p1, method = "nearest"
)
match_do_results_p <- matchit(
    as.formula(paste0("mtbi ~ ", op_vars)), matching_df_p1, method = "nearest"
)
match_op_results_p <- matchit(
    as.formula(paste0("mtbi ~ ", op_vars)), matching_df_p1, method = "nearest"
)

match_dpo_results_u <- matchit(
    as.formula(paste0("mtbi ~ ", dp_vars)), matching_df_u1, method = "nearest"
)
match_dpo_results_p <- matchit(
    as.formula(paste0("mtbi ~ ", dp_vars)), matching_df_p1, method = "nearest"
)

# Saving plots
save_matching_plot <- function(matching_results, name) {
    grDevices::png(filename = name, width = 1000, height = 500, res = 100)
    plot(matching_results, type = "density", interactive = FALSE)
    grDevices::dev.off()
}

save_matching_plot(
    match_d_results_u,
    fig_path("match_d_results_u.png", TRUE)
)
save_matching_plot(
    match_p_results_u,
    fig_path("match_p_results_u.png", TRUE)
)
save_matching_plot(
    match_o_results_u,
    fig_path("match_o_results_u.png", TRUE)
)
save_matching_plot(
    match_d_results_p,
    fig_path("match_d_results_p.png", TRUE)
)
save_matching_plot(
    match_p_results_p,
    fig_path("match_p_results_p.png", TRUE)
)
save_matching_plot(
    match_o_results_p,
    fig_path("match_o_results_p.png", TRUE)
)
save_matching_plot(
    match_dp_results_u,
    fig_path("match_dp_results_u.png", TRUE)
)
save_matching_plot(
    match_do_results_u,
    fig_path("match_do_results_u.png", TRUE)
)
save_matching_plot(
    match_op_results_u,
    fig_path("match_op_results_u.png", TRUE)
)
save_matching_plot(
    match_dp_results_p,
    fig_path("match_dp_results_p.png", TRUE)
)
save_matching_plot(
    match_do_results_p,
    fig_path("match_do_results_p.png", TRUE)
)
save_matching_plot(
    match_op_results_p,
    fig_path("match_op_results_p.png", TRUE)
)
save_matching_plot(
    match_dpo_results_u,
    fig_path("match_dpo_results_u.png", TRUE)
)
save_matching_plot(
    match_dpo_results_p,
    fig_path("match_dpo_results_p.png", TRUE)
)
```


```{r}
# Saving matched results
match_d_u <- match.data(match_d_results_u)
match_p_u <- match.data(match_p_results_u)
match_o_u <- match.data(match_o_results_u)
match_d_p <- match.data(match_d_results_p)
match_p_p <- match.data(match_p_results_p)
match_o_p <- match.data(match_o_results_p)
match_dp_u <- match.data(match_dp_results_u)
match_do_u <- match.data(match_do_results_u)
match_op_u <- match.data(match_op_results_u)
match_dp_p <- match.data(match_dp_results_p)
match_do_p <- match.data(match_do_results_p)
match_op_p <- match.data(match_op_results_p)
match_dpo_u <- match.data(match_dpo_results_u)
match_dpo_p <- match.data(match_dpo_results_p)

saveRDS(match_d_u, proc_path("match_d_u.rds", TRUE))
saveRDS(match_p_u, proc_path("match_p_u.rds", TRUE))
saveRDS(match_o_u, proc_path("match_o_u.rds", TRUE))
saveRDS(match_d_p, proc_path("match_d_p.rds", TRUE))
saveRDS(match_p_p, proc_path("match_p_p.rds", TRUE))
saveRDS(match_o_p, proc_path("match_o_p.rds", TRUE))
saveRDS(match_dp_u, proc_path("match_dp_u.rds", TRUE))
saveRDS(match_do_u, proc_path("match_do_u.rds", TRUE))
saveRDS(match_op_u, proc_path("match_op_u.rds", TRUE))
saveRDS(match_dp_p, proc_path("match_dp_p.rds", TRUE))
saveRDS(match_do_p, proc_path("match_do_p.rds", TRUE))
saveRDS(match_op_p, proc_path("match_op_p.rds", TRUE))
saveRDS(match_dpo_u, proc_path("match_dpo_u.rds", TRUE))
saveRDS(match_dpo_p, proc_path("match_dpo_p.rds", TRUE))
```

```{r}
match_d_u <- readRDS(proc_path("2025_06_15_match_d_u.rds"))
match_p_u <- readRDS(proc_path("2025_06_15_match_p_u.rds"))
match_o_u <- readRDS(proc_path("2025_06_15_match_o_u.rds"))
match_d_p <- readRDS(proc_path("2025_06_15_match_d_p.rds"))
match_p_p <- readRDS(proc_path("2025_06_15_match_p_p.rds"))
match_o_p <- readRDS(proc_path("2025_06_15_match_o_p.rds"))
match_dp_u <- readRDS(proc_path("2025_06_15_match_dp_u.rds"))
match_do_u <- readRDS(proc_path("2025_06_15_match_do_u.rds"))
match_op_u <- readRDS(proc_path("2025_06_15_match_op_u.rds"))
match_dp_p <- readRDS(proc_path("2025_06_15_match_dp_p.rds"))
match_do_p <- readRDS(proc_path("2025_06_15_match_do_p.rds"))
match_op_p <- readRDS(proc_path("2025_06_15_match_op_p.rds"))
match_dpo_u <- readRDS(proc_path("2025_06_15_match_dpo_u.rds"))
match_dpo_p <- readRDS(proc_path("2025_06_15_match_dpo_p.rds"))
```

```{r}
# Extracting the matched uninjured subjects
matched_unij_d_u <- dplyr::filter(match_d_u, mtbi == 0)$"uid"
matched_unij_p_u <- dplyr::filter(match_p_u, mtbi == 0)$"uid"
matched_unij_o_u <- dplyr::filter(match_o_u, mtbi == 0)$"uid"
matched_unij_d_p <- dplyr::filter(match_d_p, mtbi == 0)$"uid"
matched_unij_p_p <- dplyr::filter(match_p_p, mtbi == 0)$"uid"
matched_unij_o_p <- dplyr::filter(match_o_p, mtbi == 0)$"uid"
matched_unij_dp_u <- dplyr::filter(match_dp_u, mtbi == 0)$"uid"
matched_unij_do_u <- dplyr::filter(match_do_u, mtbi == 0)$"uid"
matched_unij_op_u <- dplyr::filter(match_op_u, mtbi == 0)$"uid"
matched_unij_dp_p <- dplyr::filter(match_dp_p, mtbi == 0)$"uid"
matched_unij_do_p <- dplyr::filter(match_do_p, mtbi == 0)$"uid"
matched_unij_op_p <- dplyr::filter(match_op_p, mtbi == 0)$"uid"
matched_unij_dpo_u <- dplyr::filter(match_dpo_u, mtbi == 0)$"uid"
matched_unij_dpo_p <- dplyr::filter(match_dpo_p, mtbi == 0)$"uid"

write_csv(
    data.frame(subjectkey = matched_unij_d_u),
    sub_path("matched_unij_d_u.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_p_u),
    sub_path("matched_unij_p_u.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_o_u),
    sub_path("matched_unij_o_u.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_d_p),
    sub_path("matched_unij_d_p.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_p_p),
    sub_path("matched_unij_p_p.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_o_p),
    sub_path("matched_unij_o_p.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_dp_u),
    sub_path("matched_unij_dp_u.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_do_u),
    sub_path("matched_unij_do_u.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_op_u),
    sub_path("matched_unij_op_u.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_dp_p),
    sub_path("matched_unij_dp_p.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_do_p),
    sub_path("matched_unij_do_p.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_op_p),
    sub_path("matched_unij_op_p.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_dpo_u),
    sub_path("matched_unij_dpo_u.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_dpo_p),
    sub_path("matched_unij_dpo_p.csv", TRUE)
)
```

```{r}
matched_unij_d_u <- read_subjects(
    sub_path("2025_06_15_matched_unij_d_u.csv")
)
matched_unij_p_u <- read_subjects(
    sub_path("2025_06_15_matched_unij_p_u.csv")
)
matched_unij_o_u <- read_subjects(
    sub_path("2025_06_15_matched_unij_o_u.csv")
)
matched_unij_d_p <- read_subjects(
    sub_path("2025_06_15_matched_unij_d_p.csv")
)
matched_unij_p_p <- read_subjects(
    sub_path("2025_06_15_matched_unij_p_p.csv")
)
matched_unij_o_p <- read_subjects(
    sub_path("2025_06_15_matched_unij_o_p.csv")
)
matched_unij_dp_u <- read_subjects(
    sub_path("2025_06_15_matched_unij_dp_u.csv")
)
matched_unij_do_u <- read_subjects(
    sub_path("2025_06_15_matched_unij_do_u.csv")
)
matched_unij_op_u <- read_subjects(
    sub_path("2025_06_15_matched_unij_op_u.csv")
)
matched_unij_dp_p <- read_subjects(
    sub_path("2025_06_15_matched_unij_dp_p.csv")
)
matched_unij_do_p <- read_subjects(
    sub_path("2025_06_15_matched_unij_do_p.csv")
)
matched_unij_op_p <- read_subjects(
    sub_path("2025_06_15_matched_unij_op_p.csv")
)
matched_unij_dpo_u <- read_subjects(
    sub_path("2025_06_15_matched_unij_dpo_u.csv")
)
matched_unij_dpo_p <- read_subjects(
    sub_path("2025_06_15_matched_unij_dpo_p.csv")
)
```

```{r}
matched_subjects <- list(
    "d_u" = matched_unij_d_u,
    "p_u" = matched_unij_p_u,
    "o_u" = matched_unij_o_u,
    "d_p" = matched_unij_d_p,
    "p_p" = matched_unij_p_p,
    "o_p" = matched_unij_o_p,
    "dp_u" = matched_unij_dp_u,
    "do_u" = matched_unij_do_u,
    "op_u" = matched_unij_op_u,
    "dp_p" = matched_unij_dp_p,
    "do_p" = matched_unij_do_p,
    "op_p" = matched_unij_op_p,
    "dpo_u" = matched_unij_dpo_u,
    "dpo_p" = matched_unij_dpo_p
)

intersect(matched_unij_dpo_p, matched_unij_d_u)

match_mat <- matrix(ncol = length(matched_subjects), nrow = length(matched_subjects))
for (i in seq_along(matched_subjects)) {
    for (j in seq_along(matched_subjects)) {
        match_mat[i, j] <- length(intersect(matched_subjects[[i]], matched_subjects[[j]]))
        match_mat[j, i] <- match_mat[i, j]
    }
}
match_mat <- match_mat / 434 * 100

mat_names <- names(matched_subjects)
mat_names <- gsub("_u", " (Unpooled)", mat_names)
mat_names <- gsub("_p", " (Pooled)", mat_names)
mat_names <- gsub("dpo", "D, P, O", mat_names)
mat_names <- gsub("dp", "D, P", mat_names)
mat_names <- gsub("do", "D, O", mat_names)
mat_names <- gsub("op", "O, P", mat_names)
mat_names <- gsub("d \\(", "D (", mat_names)
mat_names <- gsub("o \\(", "O (", mat_names)
mat_names <- gsub("p \\(", "P (", mat_names)
mat_names

rownames(match_mat) <- mat_names
colnames(match_mat) <- mat_names

match_mat_hm <- ComplexHeatmap::Heatmap(
    match_mat,
    heatmap_legend_param = list(
        title = "% Subject\nOverlap"
    ),
    col = circlize::colorRamp2(
        c(min(match_mat), max(match_mat)),
        c("black", "red")
    ),
    rect_gp = gpar(col = "black", lwd = 1)
)
match_mat_hm

save_heatmap(
    heatmap = match_mat_hm,
    path = fig_path("match_mat_hm.png", TRUE),
    width = 550,
    height = 500,
    res = 100
)
```

## Subsetting matched uninjured data and out of model lists

```{r}
# Function reduces a data list to only subjects in the subject vector
subject_filter_dl <- function(data_list, subject_vector) {
    data_list <- data_list |>
        dlapply(
            function(x) {
                keep_subs <- x$"data"$"uid" %in% subject_vector
                x$"data" <- x$"data"[keep_subs, ]
                return(x)
            }
        )
    return(data_list)
}

set.seed(42)
random_unij_subs <- sample(unij_ns_subs, size = 434)

matched_unij_dl_d_u <- subject_filter_dl(unij_dl_u1, matched_unij_d_u)
matched_unij_dl_d_p <- subject_filter_dl(unij_dl_p1, matched_unij_d_p)

matched_unij_dl_p_u <- subject_filter_dl(unij_dl_u1, matched_unij_p_u)
matched_unij_dl_p_p <- subject_filter_dl(unij_dl_p1, matched_unij_p_p)

matched_unij_dl_o_u <- subject_filter_dl(unij_dl_u1, matched_unij_o_u)
matched_unij_dl_o_p <- subject_filter_dl(unij_dl_p1, matched_unij_o_p)

matched_unij_dl_do_u <- subject_filter_dl(unij_dl_u1, matched_unij_do_u)
matched_unij_dl_do_p <- subject_filter_dl(unij_dl_p1, matched_unij_do_p)

matched_unij_dl_dp_u <- subject_filter_dl(unij_dl_u1, matched_unij_dp_u)
matched_unij_dl_dp_p <- subject_filter_dl(unij_dl_p1, matched_unij_dp_p)

matched_unij_dl_op_u <- subject_filter_dl(unij_dl_u1, matched_unij_op_u)
matched_unij_dl_op_p <- subject_filter_dl(unij_dl_p1, matched_unij_op_p)

matched_unij_dl_dpo_p <- subject_filter_dl(unij_dl_p1, matched_unij_dpo_p)
matched_unij_dl_dpo_u <- subject_filter_dl(unij_dl_u1, matched_unij_dpo_u)

random_unij_dl_u1 <- subject_filter_dl(unij_dl_u1, paste0("uid_", random_unij_subs))
random_unij_dl_p1 <- subject_filter_dl(unij_dl_p1, paste0("uid_", random_unij_subs))

matched_unij_ol_d_u <- subject_filter_dl(unij_ol_u1, matched_unij_d_u)
matched_unij_ol_d_p <- subject_filter_dl(unij_ol_p1, matched_unij_d_p)

matched_unij_ol_p_u <- subject_filter_dl(unij_ol_u1, matched_unij_p_u)
matched_unij_ol_p_p <- subject_filter_dl(unij_ol_p1, matched_unij_p_p)

matched_unij_ol_o_u <- subject_filter_dl(unij_ol_u1, matched_unij_o_u)
matched_unij_ol_o_p <- subject_filter_dl(unij_ol_p1, matched_unij_o_p)

matched_unij_ol_do_u <- subject_filter_dl(unij_ol_u1, matched_unij_do_u)
matched_unij_ol_do_p <- subject_filter_dl(unij_ol_p1, matched_unij_do_p)

matched_unij_ol_dp_u <- subject_filter_dl(unij_ol_u1, matched_unij_dp_u)
matched_unij_ol_dp_p <- subject_filter_dl(unij_ol_p1, matched_unij_dp_p)

matched_unij_ol_op_u <- subject_filter_dl(unij_ol_u1, matched_unij_op_u)
matched_unij_ol_op_p <- subject_filter_dl(unij_ol_p1, matched_unij_op_p)

matched_unij_ol_dpo_p <- subject_filter_dl(unij_ol_p1, matched_unij_dpo_p)
matched_unij_ol_dpo_u <- subject_filter_dl(unij_ol_u1, matched_unij_dpo_u)

random_unij_ol_u1 <- subject_filter_dl(unij_ol_u1, paste0("uid_", random_unij_subs))
random_unij_ol_p1 <- subject_filter_dl(unij_ol_p1, paste0("uid_", random_unij_subs))

saveRDS(matched_unij_dl_d_u, proc_path("matched_unij_dl_d_u.rds", TRUE))
saveRDS(matched_unij_dl_p_u, proc_path("matched_unij_dl_p_u.rds", TRUE))
saveRDS(matched_unij_dl_o_u, proc_path("matched_unij_dl_o_u.rds", TRUE))
saveRDS(matched_unij_dl_d_p, proc_path("matched_unij_dl_d_p.rds", TRUE))
saveRDS(matched_unij_dl_p_p, proc_path("matched_unij_dl_p_p.rds", TRUE))
saveRDS(matched_unij_dl_o_p, proc_path("matched_unij_dl_o_p.rds", TRUE))
saveRDS(matched_unij_dl_dp_u, proc_path("matched_unij_dl_dp_u.rds", TRUE))
saveRDS(matched_unij_dl_do_u, proc_path("matched_unij_dl_do_u.rds", TRUE))
saveRDS(matched_unij_dl_op_u, proc_path("matched_unij_dl_op_u.rds", TRUE))
saveRDS(matched_unij_dl_dp_p, proc_path("matched_unij_dl_dp_p.rds", TRUE))
saveRDS(matched_unij_dl_do_p, proc_path("matched_unij_dl_do_p.rds", TRUE))
saveRDS(matched_unij_dl_op_p, proc_path("matched_unij_dl_op_p.rds", TRUE))
saveRDS(matched_unij_dl_dpo_p, proc_path("matched_unij_dl_dpo_p.rds", TRUE))
saveRDS(matched_unij_dl_dpo_u, proc_path("matched_unij_dl_dpo_u.rds", TRUE))
saveRDS(random_unij_dl_u1, proc_path("random_unij_dl_u1.rds", TRUE))
saveRDS(random_unij_dl_p1, proc_path("random_unij_dl_p1.rds", TRUE))

saveRDS(matched_unij_ol_d_u, proc_path("matched_unij_ol_d_u.rds", TRUE))
saveRDS(matched_unij_ol_p_u, proc_path("matched_unij_ol_p_u.rds", TRUE))
saveRDS(matched_unij_ol_o_u, proc_path("matched_unij_ol_o_u.rds", TRUE))
saveRDS(matched_unij_ol_d_p, proc_path("matched_unij_ol_d_p.rds", TRUE))
saveRDS(matched_unij_ol_p_p, proc_path("matched_unij_ol_p_p.rds", TRUE))
saveRDS(matched_unij_ol_o_p, proc_path("matched_unij_ol_o_p.rds", TRUE))
saveRDS(matched_unij_ol_dp_u, proc_path("matched_unij_ol_dp_u.rds", TRUE))
saveRDS(matched_unij_ol_do_u, proc_path("matched_unij_ol_do_u.rds", TRUE))
saveRDS(matched_unij_ol_op_u, proc_path("matched_unij_ol_op_u.rds", TRUE))
saveRDS(matched_unij_ol_dp_p, proc_path("matched_unij_ol_dp_p.rds", TRUE))
saveRDS(matched_unij_ol_do_p, proc_path("matched_unij_ol_do_p.rds", TRUE))
saveRDS(matched_unij_ol_op_p, proc_path("matched_unij_ol_op_p.rds", TRUE))
saveRDS(matched_unij_ol_dpo_p, proc_path("matched_unij_ol_dpo_p.rds", TRUE))
saveRDS(matched_unij_ol_dpo_u, proc_path("matched_unij_ol_dpo_u.rds", TRUE))
saveRDS(random_unij_ol_u1, proc_path("random_unij_ol_u1.rds", TRUE))
saveRDS(random_unij_ol_p1, proc_path("random_unij_ol_p1.rds", TRUE))
```

```{r}
# CHECKPOINT
matched_unij_dl_d_u <- readRDS(proc_path("2025_06_15_matched_unij_dl_d_u.rds"))
matched_unij_dl_p_u <- readRDS(proc_path("2025_06_15_matched_unij_dl_p_u.rds"))
matched_unij_dl_o_u <- readRDS(proc_path("2025_06_15_matched_unij_dl_o_u.rds"))
matched_unij_dl_d_p <- readRDS(proc_path("2025_06_15_matched_unij_dl_d_p.rds"))
matched_unij_dl_p_p <- readRDS(proc_path("2025_06_15_matched_unij_dl_p_p.rds"))
matched_unij_dl_o_p <- readRDS(proc_path("2025_06_15_matched_unij_dl_o_p.rds"))
matched_unij_dl_dp_u <- readRDS(proc_path("2025_06_15_matched_unij_dl_dp_u.rds"))
matched_unij_dl_do_u <- readRDS(proc_path("2025_06_15_matched_unij_dl_do_u.rds"))
matched_unij_dl_op_u <- readRDS(proc_path("2025_06_15_matched_unij_dl_op_u.rds"))
matched_unij_dl_dp_p <- readRDS(proc_path("2025_06_15_matched_unij_dl_dp_p.rds"))
matched_unij_dl_do_p <- readRDS(proc_path("2025_06_15_matched_unij_dl_do_p.rds"))
matched_unij_dl_op_p <- readRDS(proc_path("2025_06_15_matched_unij_dl_op_p.rds"))
matched_unij_dl_dpo_p <- readRDS(proc_path("2025_06_15_matched_unij_dl_dpo_p.rds"))
matched_unij_dl_dpo_u <- readRDS(proc_path("2025_06_15_matched_unij_dl_dpo_u.rds"))
random_unij_dl_u1 <- readRDS(proc_path("2025_06_15_random_unij_dl_u1.rds"))
random_unij_dl_p1 <- readRDS(proc_path("2025_06_15_random_unij_dl_p1.rds"))

matched_unij_ol_d_u <- readRDS(proc_path("2025_06_15_matched_unij_ol_d_u.rds"))
matched_unij_ol_p_u <- readRDS(proc_path("2025_06_15_matched_unij_ol_p_u.rds"))
matched_unij_ol_o_u <- readRDS(proc_path("2025_06_15_matched_unij_ol_o_u.rds"))
matched_unij_ol_d_p <- readRDS(proc_path("2025_06_15_matched_unij_ol_d_p.rds"))
matched_unij_ol_p_p <- readRDS(proc_path("2025_06_15_matched_unij_ol_p_p.rds"))
matched_unij_ol_o_p <- readRDS(proc_path("2025_06_15_matched_unij_ol_o_p.rds"))
matched_unij_ol_dp_u <- readRDS(proc_path("2025_06_15_matched_unij_ol_dp_u.rds"))
matched_unij_ol_do_u <- readRDS(proc_path("2025_06_15_matched_unij_ol_do_u.rds"))
matched_unij_ol_op_u <- readRDS(proc_path("2025_06_15_matched_unij_ol_op_u.rds"))
matched_unij_ol_dp_p <- readRDS(proc_path("2025_06_15_matched_unij_ol_dp_p.rds"))
matched_unij_ol_do_p <- readRDS(proc_path("2025_06_15_matched_unij_ol_do_p.rds"))
matched_unij_ol_op_p <- readRDS(proc_path("2025_06_15_matched_unij_ol_op_p.rds"))
matched_unij_ol_dpo_p <- readRDS(proc_path("2025_06_15_matched_unij_ol_dpo_p.rds"))
matched_unij_ol_dpo_u <- readRDS(proc_path("2025_06_15_matched_unij_ol_dpo_u.rds"))
random_unij_ol_u1 <- readRDS(proc_path("2025_06_15_random_unij_ol_u1.rds"))
random_unij_ol_p1 <- readRDS(proc_path("2025_06_15_random_unij_ol_p1.rds"))
```

## metaSNF

```{r}
set.seed(42)
matched_config <- snf_config(
    matched_unij_dl_d_u,
    n_solutions = 200,
    cnt_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    dsc_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ord_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    use_default_dist_fns = TRUE
)

saveRDS(matched_config, proc_path("matched_config.rds", TRUE))
```

```{r}
# CHECKPOINT
matched_config <- readRDS(proc_path("2025_06_15_matched_config.rds"))
```

```{r}
# SNF
matched_unij_sol_df_d_u <- progressr::with_progress(batch_snf(matched_unij_dl_d_u, matched_config, processes = "max"))
saveRDS(matched_unij_sol_df_d_u, proc_path("matched_unij_sol_df_d_u.rds", TRUE))
cat("snf 1 done\n")
matched_unij_sol_df_p_u <- progressr::with_progress(batch_snf(matched_unij_dl_p_u, matched_config, processes = "max"))
saveRDS(matched_unij_sol_df_p_u, proc_path("matched_unij_sol_df_p_u.rds", TRUE))
cat("snf 2 done\n")
matched_unij_sol_df_o_u <- progressr::with_progress(batch_snf(matched_unij_dl_o_u, matched_config, processes = "max"))
saveRDS(matched_unij_sol_df_o_u, proc_path("matched_unij_sol_df_o_u.rds", TRUE))
cat("snf 3 done\n")
matched_unij_sol_df_d_p <- progressr::with_progress(batch_snf(matched_unij_dl_d_p, matched_config, processes = "max"))
saveRDS(matched_unij_sol_df_d_p, proc_path("matched_unij_sol_df_d_p.rds", TRUE))
cat("snf 4 done\n")
matched_unij_sol_df_p_p <- progressr::with_progress(batch_snf(matched_unij_dl_p_p, matched_config, processes = "max"))
saveRDS(matched_unij_sol_df_p_p, proc_path("matched_unij_sol_df_p_p.rds", TRUE))
cat("snf 5 done\n")
```

```{r}
matched_unij_sol_df_o_p <- progressr::with_progress(batch_snf(matched_unij_dl_o_p, matched_config, processes = "max"))
saveRDS(matched_unij_sol_df_o_p, proc_path("matched_unij_sol_df_o_p.rds", TRUE))
cat("snf 6 done\n")
matched_unij_sol_df_dp_u <- progressr::with_progress(batch_snf(matched_unij_dl_dp_u, matched_config, processes = "max"))
saveRDS(matched_unij_sol_df_dp_u, proc_path("matched_unij_sol_df_dp_u.rds", TRUE))
cat("snf 7 done\n")
matched_unij_sol_df_do_u <- progressr::with_progress(batch_snf(matched_unij_dl_do_u, matched_config, processes = "max"))
saveRDS(matched_unij_sol_df_do_u, proc_path("matched_unij_sol_df_do_u.rds", TRUE))
cat("snf 8 done\n")
matched_unij_sol_df_op_u <- progressr::with_progress(batch_snf(matched_unij_dl_op_u, matched_config, processes = "max"))
saveRDS(matched_unij_sol_df_op_u, proc_path("matched_unij_sol_df_op_u.rds", TRUE))
cat("snf 9 done\n")
matched_unij_sol_df_dp_p <- progressr::with_progress(batch_snf(matched_unij_dl_dp_p, matched_config, processes = "max"))
saveRDS(matched_unij_sol_df_dp_p, proc_path("matched_unij_sol_df_dp_p.rds", TRUE))
cat("snf 10 done\n")
```

```{r}
matched_unij_sol_df_do_p <- progressr::with_progress(batch_snf(matched_unij_dl_do_p, matched_config, processes = "max"))
saveRDS(matched_unij_sol_df_do_p, proc_path("matched_unij_sol_df_do_p.rds", TRUE))
cat("snf 11 done\n")
matched_unij_sol_df_op_p <- progressr::with_progress(batch_snf(matched_unij_dl_op_p, matched_config, processes = "max"))
saveRDS(matched_unij_sol_df_op_p, proc_path("matched_unij_sol_df_op_p.rds", TRUE))
cat("snf 12 done\n")
matched_unij_sol_df_dpo_p <- progressr::with_progress(batch_snf(matched_unij_dl_dpo_p, matched_config, processes = "max"))
saveRDS(matched_unij_sol_df_dpo_p, proc_path("matched_unij_sol_df_dpo_p.rds", TRUE))
cat("snf 13 done\n")
matched_unij_sol_df_dpo_u <- progressr::with_progress(batch_snf(matched_unij_dl_dpo_u, matched_config, processes = "max"))
saveRDS(matched_unij_sol_df_dpo_u, proc_path("matched_unij_sol_df_dpo_u.rds", TRUE))
cat("snf 14 done\n")

random_unij_sol_df_u1 <- progressr::with_progress(batch_snf(random_unij_dl_u1, matched_config, processes = "max"))
saveRDS(random_unij_sol_df_u1, proc_path("random_unij_sol_df_u1.rds", TRUE))
cat("snf 15 done\n")
random_unij_sol_df_p1 <- progressr::with_progress(batch_snf(random_unij_dl_p1, matched_config, processes = "max"))
saveRDS(random_unij_sol_df_p1, proc_path("random_unij_sol_df_p1.rds", TRUE))
```

```{r}
# HERE 2025-06-15
matched_unij_sol_df_dpo_u <- readRDS(proc_path("2025_06_15_matched_unij_sol_df_dpo_u.rds"))
matched_unij_sol_df_dpo_p <- readRDS(proc_path("2025_06_15_matched_unij_sol_df_dpo_p.rds"))
matched_unij_sol_df_op_p  <- readRDS(proc_path("2025_06_15_matched_unij_sol_df_op_p.rds"))
matched_unij_sol_df_do_p  <- readRDS(proc_path("2025_06_15_matched_unij_sol_df_do_p.rds"))
matched_unij_sol_df_dp_p  <- readRDS(proc_path("2025_06_15_matched_unij_sol_df_dp_p.rds"))
matched_unij_sol_df_op_u  <- readRDS(proc_path("2025_06_15_matched_unij_sol_df_op_u.rds"))
matched_unij_sol_df_do_u  <- readRDS(proc_path("2025_06_15_matched_unij_sol_df_do_u.rds"))
matched_unij_sol_df_dp_u  <- readRDS(proc_path("2025_06_15_matched_unij_sol_df_dp_u.rds"))
matched_unij_sol_df_o_p   <- readRDS(proc_path("2025_06_15_matched_unij_sol_df_o_p.rds"))
matched_unij_sol_df_p_p   <- readRDS(proc_path("2025_06_15_matched_unij_sol_df_p_p.rds"))
matched_unij_sol_df_d_p   <- readRDS(proc_path("2025_06_15_matched_unij_sol_df_d_p.rds"))
matched_unij_sol_df_o_u   <- readRDS(proc_path("2025_06_15_matched_unij_sol_df_o_u.rds"))
matched_unij_sol_df_p_u   <- readRDS(proc_path("2025_06_15_matched_unij_sol_df_p_u.rds"))
matched_unij_sol_df_d_u   <- readRDS(proc_path("2025_06_15_matched_unij_sol_df_d_u.rds"))

random_unij_sol_df_u1     <- readRDS(proc_path("2025_06_17_random_unij_sol_df_u1.rds"))
random_unij_sol_df_p1     <- readRDS(proc_path("2025_06_17_random_unij_sol_df_p1.rds"))
```

```{r}
matched_unij_ext_sol_df_dpo_u <- extend_solutions(
    matched_unij_sol_df_dpo_u,
    dl = matched_unij_dl_dpo_u,
    target_dl = matched_unij_ol_dpo_u,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(matched_unij_ext_sol_df_dpo_u, proc_path("matched_unij_ext_sol_df_dpo_u.rds", TRUE))

matched_unij_ext_sol_df_dpo_p <- extend_solutions(
    matched_unij_sol_df_dpo_p,
    dl = matched_unij_dl_dpo_p,
    target_dl = matched_unij_ol_dpo_p,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(matched_unij_ext_sol_df_dpo_p, proc_path("matched_unij_ext_sol_df_dpo_p.rds", TRUE))

matched_unij_ext_sol_df_op_p <- extend_solutions(
    matched_unij_sol_df_op_p,
    dl = matched_unij_dl_op_p,
    target_dl = matched_unij_ol_op_p,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(matched_unij_ext_sol_df_op_p, proc_path("matched_unij_ext_sol_df_op_p.rds", TRUE))
matched_unij_ext_sol_df_do_p <- extend_solutions(
    matched_unij_sol_df_do_p,
    dl = matched_unij_dl_do_p,
    target_dl = matched_unij_ol_do_p,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(matched_unij_ext_sol_df_do_p, proc_path("matched_unij_ext_sol_df_do_p.rds", TRUE))
matched_unij_ext_sol_df_dp_p <- extend_solutions(
    matched_unij_sol_df_dp_p,
    dl = matched_unij_dl_dp_p,
    target_dl = matched_unij_ol_dp_p,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(matched_unij_ext_sol_df_dp_p, proc_path("matched_unij_ext_sol_df_dp_p.rds", TRUE))
matched_unij_ext_sol_df_op_u <- extend_solutions(
    matched_unij_sol_df_op_u,
    dl = matched_unij_dl_op_u,
    target_dl = matched_unij_ol_op_u,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(matched_unij_ext_sol_df_op_u, proc_path("matched_unij_ext_sol_df_op_u.rds", TRUE))
matched_unij_ext_sol_df_do_u <- extend_solutions(
    matched_unij_sol_df_do_u,
    dl = matched_unij_dl_do_u,
    target_dl = matched_unij_ol_do_u,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(matched_unij_ext_sol_df_do_u, proc_path("matched_unij_ext_sol_df_do_u.rds", TRUE))
#
matched_unij_ext_sol_df_dp_u <- extend_solutions(
    matched_unij_sol_df_dp_u,
    dl = matched_unij_dl_dp_u,
    target_dl = matched_unij_ol_dp_u,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(matched_unij_ext_sol_df_dp_u, proc_path("matched_unij_ext_sol_df_dp_u.rds", TRUE))
matched_unij_ext_sol_df_o_p <- extend_solutions(
    matched_unij_sol_df_o_p,
    dl = matched_unij_dl_o_p,
    target_dl = matched_unij_ol_o_p,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(matched_unij_ext_sol_df_o_p, proc_path("matched_unij_ext_sol_df_o_p.rds", TRUE))
matched_unij_ext_sol_df_p_p <- extend_solutions(
    matched_unij_sol_df_p_p,
    dl = matched_unij_dl_p_p,
    target_dl = matched_unij_ol_p_p,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(matched_unij_ext_sol_df_p_p, proc_path("matched_unij_ext_sol_df_p_p.rds", TRUE))
matched_unij_ext_sol_df_d_p <- extend_solutions(
    matched_unij_sol_df_d_p,
    dl = matched_unij_dl_d_p,
    target_dl = matched_unij_ol_d_p,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(matched_unij_ext_sol_df_d_p, proc_path("matched_unij_ext_sol_df_d_p.rds", TRUE))
matched_unij_ext_sol_df_o_u <- extend_solutions(
    matched_unij_sol_df_o_u,
    dl = matched_unij_dl_o_u,
    target_dl = matched_unij_ol_o_u,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(matched_unij_ext_sol_df_o_u, proc_path("matched_unij_ext_sol_df_o_u.rds", TRUE))
matched_unij_ext_sol_df_p_u <- extend_solutions(
    matched_unij_sol_df_p_u,
    dl = matched_unij_dl_p_u,
    target_dl = matched_unij_ol_p_u,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(matched_unij_ext_sol_df_p_u, proc_path("matched_unij_ext_sol_df_p_u.rds", TRUE))
matched_unij_ext_sol_df_d_u <- extend_solutions(
    matched_unij_sol_df_d_u,
    dl = matched_unij_dl_d_u,
    target_dl = matched_unij_ol_d_u,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(matched_unij_ext_sol_df_d_u, proc_path("matched_unij_ext_sol_df_d_u.rds", TRUE))
random_unij_ext_sol_df_u1 <- extend_solutions(
    random_unij_sol_df_u1,
    dl = random_unij_dl_u1,
    target_dl = random_unij_ol_u1,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(random_unij_ext_sol_df_u1, proc_path("random_unij_ext_sol_df_u1.rds", TRUE))
random_unij_ext_sol_df_p1 <- extend_solutions(
    random_unij_sol_df_p1,
    dl = random_unij_dl_p1,
    target_dl = random_unij_ol_p1,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(random_unij_ext_sol_df_p1, proc_path("random_unij_ext_sol_df_p1.rds", TRUE))
```

```{r}
# CHECKPOINT - extended solutions data frames
matched_unij_ext_sol_df_d_u <- readRDS(proc_path("2025_06_17_matched_unij_ext_sol_df_d_u.rds"))
matched_unij_ext_sol_df_p_u <- readRDS(proc_path("2025_06_17_matched_unij_ext_sol_df_p_u.rds"))
matched_unij_ext_sol_df_o_u <- readRDS(proc_path("2025_06_17_matched_unij_ext_sol_df_o_u.rds"))
matched_unij_ext_sol_df_d_p <- readRDS(proc_path("2025_06_17_matched_unij_ext_sol_df_d_p.rds"))
matched_unij_ext_sol_df_p_p <- readRDS(proc_path("2025_06_17_matched_unij_ext_sol_df_p_p.rds"))
matched_unij_ext_sol_df_o_p <- readRDS(proc_path("2025_06_17_matched_unij_ext_sol_df_o_p.rds"))
matched_unij_ext_sol_df_dp_u <- readRDS(proc_path("2025_06_17_matched_unij_ext_sol_df_dp_u.rds"))
matched_unij_ext_sol_df_do_u <- readRDS(proc_path("2025_06_17_matched_unij_ext_sol_df_do_u.rds"))
matched_unij_ext_sol_df_op_u <- readRDS(proc_path("2025_06_17_matched_unij_ext_sol_df_op_u.rds"))
matched_unij_ext_sol_df_dp_p <- readRDS(proc_path("2025_06_17_matched_unij_ext_sol_df_dp_p.rds"))
matched_unij_ext_sol_df_do_p <- readRDS(proc_path("2025_06_17_matched_unij_ext_sol_df_do_p.rds"))
matched_unij_ext_sol_df_op_p <- readRDS(proc_path("2025_06_17_matched_unij_ext_sol_df_op_p.rds"))
matched_unij_ext_sol_df_dpo_p <- readRDS(proc_path("2025_06_17_matched_unij_ext_sol_df_dpo_p.rds"))
matched_unij_ext_sol_df_dpo_u <- readRDS(proc_path("2025_06_17_matched_unij_ext_sol_df_dpo_u.rds"))
random_unij_ext_sol_df_u1 <- readRDS(proc_path("2025_06_17_random_unij_ext_sol_df_u1.rds"))
random_unij_ext_sol_df_p1 <- readRDS(proc_path("2025_06_17_random_unij_ext_sol_df_p1.rds"))
```

```{r}

matched_unij_ext_sol_df_list <- list(
    "d_u" = matched_unij_ext_sol_df_d_u,
    "p_u" = matched_unij_ext_sol_df_p_u,
    "o_u" = matched_unij_ext_sol_df_o_u,
    "d_p" = matched_unij_ext_sol_df_d_p,
    "p_p" = matched_unij_ext_sol_df_p_p,
    "o_p" = matched_unij_ext_sol_df_o_p,
    "dp_u" = matched_unij_ext_sol_df_dp_u,
    "do_u" = matched_unij_ext_sol_df_do_u,
    "op_u" = matched_unij_ext_sol_df_op_u,
    "dp_p" = matched_unij_ext_sol_df_dp_p,
    "do_p" = matched_unij_ext_sol_df_do_p,
    "op_p" = matched_unij_ext_sol_df_op_p,
    "dpo_p" = matched_unij_ext_sol_df_dpo_p,
    "dpo_u" = matched_unij_ext_sol_df_dpo_u,
    "random_u" = random_unij_ext_sol_df_u1,
    "random_p" = random_unij_ext_sol_df_p1
)

saveRDS(
    matched_unij_ext_sol_df_list,
    proc_path("matched_unij_ext_sol_df_list.rds", TRUE)
)
```

```{r}
matched_unij_ext_sol_df_list <- readRDS(
    proc_path("2025_06_18_matched_unij_ext_sol_df_list.rds")
)
```

```{r}
duplicated(matched_unij_ext_sol_df_list)

vec <- matched_unij_ext_sol_df_list

dup_indices <- which(duplicated(vec))

dup_indices

for (i in dup_indices) {
    cat(names(vec)[i], " is equal to:\n", sep = "")
    for (j in seq_along(vec)) {
        if (identical(vec[[i]], vec[[j]]) & i != j) {
            cat("    - ", names(vec)[j], "\n")
        }
    }
}

#op_u is equal to:
#    -  do_u
#op_p is equal to:
#    -  do_p
#dpo_p is equal to:
#    -  dp_p
#dpo_u is equal to:
#    -  dp_u

matched_unij_ext_sol_df_list |> length()

# Tight requirement: -log10(pval) > 4
matched_unij_ext_sol_df_3c_list <- lapply(
    matched_unij_ext_sol_df_list,
    function(x) {
        x <- x[x$"nclust" == 3 & -log10(x$"mean_pval") > 4, ]
        if (nrow(x) > 0) {
            return(x)
        } 
    }
)

# Loose requirement: -log10(pval) > 1
matched_unij_ext_sol_df_3c_list_loose <- lapply(
    matched_unij_ext_sol_df_list,
    function(x) {
        x <- x[x$"nclust" == 3 & -log10(x$"mean_pval") > 1, ]
        if (nrow(x) > 0) {
            return(x)
        } 
    }
)


matched_unij_ext_sol_df_3c_list_loose[[1]] |> nrow() # 4

matched_unij_ext_sol_df_3c_list_loose[[2]] |> nrow() # 7

matched_unij_ext_sol_df_3c_list_loose[[3]] |> nrow() # 18

unlist(sapply(matched_unij_ext_sol_df_3c_list, function(x) nrow(x) > 0))

# 8 tight matches
sapply(matched_unij_ext_sol_df_3c_list, nrow) |>
    unlist() |>
    sum()

# 171 loose matches
sapply(matched_unij_ext_sol_df_3c_list_loose, nrow) |>
    unlist() |>
    sum()

class(matched_unij_ext_sol_df_3c_list)

sapply(matched_unij_ext_sol_df_3c_list, function(x) nrow(x) > 0)

matched_unij_ext_sol_df_3c_list <- matched_unij_ext_sol_df_3c_list[sapply(matched_unij_ext_sol_df_3c_list, function(x) isTRUE(nrow(x) > 0))]
matched_unij_ext_sol_df_3c_list_loose <- matched_unij_ext_sol_df_3c_list_loose[sapply(matched_unij_ext_sol_df_3c_list_loose, function(x) isTRUE(nrow(x) > 0))]

saveRDS(matched_unij_ext_sol_df_3c_list, proc_path("matched_unij_ext_sol_df_3c_list.rds", TRUE))
saveRDS(matched_unij_ext_sol_df_3c_list_loose, proc_path("matched_unij_ext_sol_df_3c_list_loose.rds", TRUE))

matched_unij_ext_sol_df_3c_list <- readRDS(proc_path("2025_06_18_matched_unij_ext_sol_df_3c_list.rds"))

matched_unij_ext_sol_df_3c_list_loose <- readRDS(proc_path("2025_06_18_matched_unij_ext_sol_df_3c_list_loose.rds"))
```

```{r}
# Domain colour labels
dcols <- c(
    "AS" = "#85929e",
    "D" = "#bb8fce",
    "N" = "#e59866",
    "MH" = "#7fb3d5",
    "P" = "#52be80",
    "S" = "#d98880",
    "B" = "#ff3131"
)

# dp_u, dpo_u
names(matched_unij_ext_sol_df_3c_list)

matched_unij_dp_u <- mc_manhattan_plot(
    matched_unij_ext_sol_df_3c_list$"dp_u",
    dl = matched_unij_dl_dp_u,
    target_dl = matched_unij_ol_dp_u,
    domain_colours = dcols
)

matched_unij_dpo_u <- mc_manhattan_plot(
    matched_unij_ext_sol_df_3c_list$"dpo_u",
    dl = matched_unij_dl_dpo_u,
    target_dl = matched_unij_ol_dpo_u,
    domain_colours = dcols
)

matched_unij_manhattan_plots <- list(
    "dp_u" = matched_unij_dp_u,
    "dpo_u" = matched_unij_dpo_u
)

saveRDS(matched_unij_manhattan_plots, fig_path("matched_unij_manhattan_plots.rds", TRUE))
```

```{r}
# CHECKPOINT
matched_unij_manhattan_plots <- readRDS(fig_path("2025_06_18_matched_unij_manhattan_plots.rds"))
```

So we know that only a couple of combinations lead to somewhat similar cluster solutions in terms of the mean p-values on outcomes.

```{r}
# Quick save function
qs2 <- function(plot, path, w = 18, h = 14, d = 120) {    
    path <- paste0("matched_unij_", path, "_manhattan.png")
    ggsave(
        fig_path(path, TRUE),
        plot,
        width = w,
        height = h,
        dpi = d
    )
}

# Small function to calculate how tall each manhattan plot
# should be.
heighter <- function(panes) {
    panes * 4/3 + 10/3
}

matched_unij_manhattan_plots$"dp_u" # 4 panes

heighter(4)

heighter(4)

qs2(matched_unij_manhattan_plots$"dp_u", "dp_u", h = heighter(4))
qs2(matched_unij_manhattan_plots$"dpo_u", "dpo_u", h = heighter(4))
```

```{r}
matched_unij_dls <- list(
    "d_u" = matched_unij_dl_d_u,
    "p_u" = matched_unij_dl_p_u,
    "o_u" = matched_unij_dl_o_u,
    "d_p" = matched_unij_dl_d_p,
    "p_p" = matched_unij_dl_p_p,
    "o_p" = matched_unij_dl_o_p,
    "dp_u" = matched_unij_dl_dp_u,
    "do_u" = matched_unij_dl_do_u,
    "op_u" = matched_unij_dl_op_u,
    "dp_p" = matched_unij_dl_dp_p,
    "do_p" = matched_unij_dl_do_p,
    "op_p" = matched_unij_dl_op_p,
    "dpo_p" = matched_unij_dl_dpo_p,
    "dpo_u" = matched_unij_dl_dpo_u,
    "random_u" = random_unij_dl_u1,
    "random_p" = random_unij_dl_p1
)

matched_unij_ols <- list(
    "d_u" = matched_unij_ol_d_u,
    "p_u" = matched_unij_ol_p_u,
    "o_u" = matched_unij_ol_o_u,
    "d_p" = matched_unij_ol_d_p,
    "p_p" = matched_unij_ol_p_p,
    "o_p" = matched_unij_ol_o_p,
    "dp_u" = matched_unij_ol_dp_u,
    "do_u" = matched_unij_ol_do_u,
    "op_u" = matched_unij_ol_op_u,
    "dp_p" = matched_unij_ol_dp_p,
    "do_p" = matched_unij_ol_do_p,
    "op_p" = matched_unij_ol_op_p,
    "dpo_p" = matched_unij_ol_dpo_p,
    "dpo_u" = matched_unij_ol_dpo_u,
    "random_u" = random_unij_ol_u1,
    "random_p" = random_unij_ol_p1
)

saveRDS(matched_unij_dls, proc_path("matched_unij_dls.rds", TRUE))
saveRDS(matched_unij_ols, proc_path("matched_unij_ols.rds", TRUE))
```

```{r}
# CHECKPOINT
matched_unij_dls <- readRDS(proc_path("2025_06_18_matched_unij_dls.rds"))
matched_unij_ols <- readRDS(proc_path("2025_06_18_matched_unij_ols.rds"))
```


```{r}

mtbi_gen_fts_table_hits_t <- read_csv(proc_path("2025_06_13_mtbi_gen_fts_table_hits_t.csv"))
mtbi_gen_long <- na.omit(mtbi_gen_fts_table_hits_t)

```



```{r}
# CHECKPOINT
mtbi_gen_fts_in_long <- read_csv(
    proc_path("2025_02_13_mtbi_gen_fts_in_long.csv")
)
mtbi_gen_fts_out_long <- read_csv(
    proc_path("2025_02_13_mtbi_gen_fts_out_long.csv")
)

classifier_fts <- read_csv(proc_path("2025_02_14_classifier_fts.csv"))
classifier_fts <- classifier_fts$"classifier_fts"
```

Calculating concordance (similarity between matched uninjured solution and baseline mTBI solution topologies) using loose threshold.

```{r}
matched_pl_dfs <- lapply(
    names(matched_unij_ext_sol_df_3c_list_loose),
    function(match) {
        pl <- list()
        nrows <- nrow(matched_unij_ext_sol_df_3c_list_loose[[match]])
        for (row in seq_len(nrows)) {
            print(paste0(match, row))
            p <- auto_plot(
                matched_unij_ext_sol_df_3c_list_loose[[match]][row, ],
                dl = c(matched_unij_dls[[match]], matched_unij_ols[[match]]),
                return_plots = FALSE
            )
            pl[[length(pl) + 1]] <- p
        }
        return(pl)
    }
)

names(matched_pl_dfs) <- names(matched_unij_ext_sol_df_3c_list_loose)
matched_pl_dfs <- unlist(matched_pl_dfs, recursive = FALSE)

saveRDS(matched_pl_dfs, proc_path("matched_pl_dfs.rds", TRUE))

matched_pl_dfs <- readRDS(proc_path("2025_06_18_matched_pl_dfs.rds"))

duplicated(matched_pl_dfs)

names(matched_pl_dfs)

matched_pl_dfs_no_dups <- matched_pl_dfs[!duplicated(matched_pl_dfs)]

matched_pl_dfs_no_dups |> length()

matched_pl_tops <- lapply(
    matched_pl_dfs_no_dups,
    function(x) {
        print(x)
        topologizer(x)
    }
)

saveRDS(matched_pl_tops, proc_path("matched_pl_tops.rds", TRUE))

matched_pl_tops <- readRDS(proc_path("2025_06_18_matched_pl_tops.rds"))

matched_pl_tops |> names()

matched_pl_gen_fts <- lapply(
    matched_pl_tops,
    function(x) {
        generalizable_features(x, compare_fn_a)
    }
)

#matched_pl_gen_fts_long <- lapply(
#    matched_pl_gen_fts,
#    function(x) {
#        long_x <- pivot_longer(
#            x,
#            cols = -feature,
#            names_to = "comparison",
#            values_to = "order_unij"
#        )
#        long_gen_x <- dplyr::left_join(
#            mtbi_gen_long,
#            long_x,
#            by = c("feature", "comparison")
#        ) 
#        long_gen_x <- dplyr::mutate(
#            long_gen_x,
#            match = dplyr::case_when(
#                is.na(order_unij) ~ 0,
#                order != order_unij ~ 0, 
#                order == order_unij ~ 1
#            )
#        )
#        return(long_gen_x)
#    }
#)
#
#matched_pl_gen_fts_long_fair <- lapply(
#    matched_pl_gen_fts_long,
#    function(x) {
#        dplyr::filter(x, !grepl("mtbi", feature))
#    }
#)

saveRDS(matched_pl_dfs_no_dups, proc_path("matched_pl_dfs_no_dups.rds", TRUE))

matched_pl_dfs_no_dups <- readRDS(proc_path("2025_06_18_matched_pl_dfs_no_dups.rds"))

matched_pl_dfs_no_dups[[1]] |> colnames()

concordance_w_mtbi_quick <- function(data_df, n = NULL, iters = 10, procs = 1, mtbi_data) {
    #start <- Sys.time()
    #bootstrap_sample <- sample(n, replace = TRUE)
    #sampled_df <- data_df[bootstrap_sample, ]
    tops_df <- topologizer(data_df)
    info_table <- data_df |>
        dplyr::group_by(cluster) |>
        dplyr::summarize(
            income = mean(household_income),
            sex = mean(sex)
        ) |>
        dplyr::mutate(combo = income - sex) |> # sort by low income and high M
        dplyr::arrange(combo)
    swap_key <- paste0(info_table$"cluster", collapse = "")
    swap_list <- list(
        "123" = list(),                 # swap nothing
        "132" = list(c(2, 3)),          # swap 2<->3
        "213" = list(c(1, 2)),          # swap 1<->2
        "231" = list(c(1, 2), c(2, 3)), # swap 1<->2 then 2<->3
        "312" = list(c(1, 3), c(2, 3)), # swap 1<->3 then 2<->3
        "321" = list(c(1, 3))           # swap 1<->3
    )
    swap_instructions <- swap_list[[swap_key]]
    for (instruction in swap_instructions) {
        data_df <- data_df |>
            dplyr::mutate(
                cluster = dplyr::case_when(
                    cluster == instruction[1] ~ factor(instruction[2]),
                    cluster == instruction[2] ~ factor(instruction[1]),
                    TRUE ~ cluster
                )
            )
    }
    info_table <- data_df |>
        dplyr::group_by(cluster) |>
        dplyr::summarize(
            income = mean(household_income),
            sex = mean(sex)
        ) |>
        dplyr::mutate(combo = income - sex) |> # sort by low income and high M
        dplyr::arrange(combo)
    swap_key <- paste0(info_table$"cluster", collapse = "")
    gen_tops_df <- generalizable_features(tops_df, compare_fn_a)
    gen_tops_df_long <- gen_tops_df |>
        pivot_longer(
            cols = -feature,
            names_to = "comparison",
            values_to = "order_sample"
        )
    joint_df <- dplyr::left_join(
        mtbi_data, # reference data frame
        gen_tops_df_long, # sampled data frame
        by = c("feature", "comparison")
    ) |>
        dplyr::mutate(
            match = ifelse(order_sample == order, 1, 0)
        ) |>
        dplyr::filter(!grepl("mtbi", feature))
    concordance <- sum(joint_df$"match") / nrow(joint_df)
    return(concordance)
}

matched_pl_concordances <- lapply(
    seq_along(matched_pl_dfs_no_dups),
    function(x) {
        print(x)
        concordance_w_mtbi_quick(matched_pl_dfs[[x]], mtbi_data = mtbi_gen_long)
    }
)
saveRDS(matched_pl_concordances, proc_path("matched_pl_concordances.rds", TRUE))

matched_pl_concordances <- readRDS(
    proc_path("2025_06_18_matched_pl_concordances.rds")
)

concordance_df <- data.frame(
    unij_set = names(matched_pl_dfs_no_dups),
    concordance = unlist(matched_pl_concordances)
) |>
    arrange(desc(concordance))
rownames(concordance_df) <- NULL

concordance_df

write_csv(concordance_df, proc_path("matched_unij_concordance.csv", TRUE))

concordance_df <- read_csv(proc_path("2025_07_22_matched_unij_concordance.csv"))

concordance_df

xtable(concordance_df)

knitr::kable(
    concordance_df,
    format = "markdown",
    digits = 3,
    format.args = list(scientific = FALSE)
) |>
    writeLines(proc_path("matched_unij_concordance.txt", TRUE))

concordance_df
```

Matching by D+O and D+P seem to be best.

```{r}
saveRDS(
    matched_unij_ext_sol_df_3c_list_loose$"do_u"[14, ],
    proc_path("matched_unij_nearest_esdf.rds", TRUE)
)

matched_unij_nearest_esdf <- readRDS(proc_path("2025_06_18_matched_unij_nearest_esdf.rds"))

classifier_fts <- readRDS(proc_path("2025_06_13_classifier_fts.rds"))

top_unij_pl <- auto_plot(
    matched_unij_nearest_esdf,
    dl = c(
        matched_unij_dls$"do_u",
        matched_unij_ols$"do_u"
    )
)


light_fts <- c(
    "sex",
    "brain_volume",
    "household_income",
    "family_fight_p",
    "extracurriculars",
    "parent_somatic",
    "race",
    "weekday_screentime",
    "cbcl_attention"
)

top_unij_pl

all_light_unij_plots <- top_unij_pl[light_fts]
all_light_unij_plots

all_light_unij_plots$"sex" <- all_light_unij_plots$"sex" + labs(fill = "", y = "Sex") + theme(axis.title.y = ggplot2::element_text(size = 16, angle = 90), legend.position = "left")
all_light_unij_plots$"brain_volume" <- all_light_unij_plots$"brain_volume" + labs(y = "Brain\nVolume (cm³)") + theme(axis.title.y = ggplot2::element_text(angle = 90, size = 16)) + 
scale_y_continuous(
    labels = function(x) x / 1000
  )
all_light_unij_plots$"household_income" <- all_light_unij_plots$"household_income" + labs(y = "Household\nIncome") + theme(axis.title.y = ggplot2::element_text(angle = 90, size = 16))
all_light_unij_plots[[4]] <- all_light_unij_plots[[4]] + labs(fill = "", y = "Family Fights\n(Parent Report)") + theme(axis.title.y = ggplot2::element_text(angle = 90, size = 16), legend.position = "left")
all_light_unij_plots[[5]] <- all_light_unij_plots[[5]] + labs(y = "Extracurriculars\n(Quartile)") + theme(axis.title.y = ggplot2::element_text(angle = 90, size = 16))
all_light_unij_plots[[6]] <- all_light_unij_plots[[6]] + labs(y = "Parent\nSomatic") + theme(axis.title.y = ggplot2::element_text(angle = 90, size = 16))
all_light_unij_plots[[7]] <- all_light_unij_plots[[7]] + labs(fill = "", y = "Race") + theme(axis.title.y = ggplot2::element_text(angle = 90, size = 16), legend.position = "left")
all_light_unij_plots[[8]] <- all_light_unij_plots[[8]] + labs(y = "Weekday\nScreentime\n(hours)") + theme(axis.title.y = ggplot2::element_text(angle = 90, size = 16))
all_light_unij_plots[[9]] <- all_light_unij_plots[[9]] + labs(y = "CBCL\nAttention") + theme(axis.title.y = ggplot2::element_text(angle = 90, size = 16))
all_light_unij_plots <- all_light_unij_plots |>
    lapply(
        function(x) {
            x <- x + theme(
                axis.title.x = element_blank(),
                legend.title = element_text(size = 14),
                legend.text = element_text(size = 14)
            )
        }
    )
all_light_unij_plots[[7]] <- all_light_unij_plots[[7]] + scale_fill_discrete(labels = c("Black", "Hispanic", "Other", "White"))
all_light_unij_plots |>
    wrap_plots() |>
    ggsave(
        filename = fig_path("unij_top_match_light.png", TRUE),
        w = 10,
        h = 6,
        dpi = 300
    )


afts <- readRDS(proc_path("2025_06_11_afts.rds"))

top_unij_pl_wrapped <- wrap_plots(top_unij_pl[intersect(afts, names(top_unij_pl))])

ggsave(
    fig_path("top_unij_pl_wrapped.png", TRUE),
    top_unij_pl_wrapped,
    width = 45,
    height = 20,
    dpi = 50
)
```
