# Matching

This chapter contains:

1. Derivation of subtypes from a variety of matched uninjured groups
2. Comparison of those subtypes with the mTBI baseline solution

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)
library(MatchIt)
library(tibble)
library(ggplot2)
library(fastDummies)
library(dplyr)
library(tidyr)
library(xtable)
library(patchwork)

input_path   <- path_maker(here(paste0("data/abcd/inputs")))
proc_path    <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path     <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path     <- path_maker(here(paste0("data/abcd/subjects")))
model_path   <- path_maker(here(paste0("data/abcd/results/models")))
unij_ns_subs <- readRDS(sub_path("2025_06_11_unij_no_sibs_subs.rds"))
```

## Importing data

```{r}
all_dls_h_ns <- readRDS(proc_path("2025_06_11_all_dls_h_no_sibs.rds"))

#mtbi_full_data_list_1 <- readRDS(input_path("2025_02_12_mtbi_full_data_list_1.rds"))
#mtbi_full_oom_list_1 <- readRDS(input_path("2025_02_12_mtbi_full_oom_list_1.rds"))
#mtbi_full_top_3c <- readRDS(proc_path("2025_02_13_mtbi_full_top_3c.rds"))

mtbi_dl_1 <- readRDS(input_path("2025_06_11_mtbi_dl_1.rds"))
mtbi_ol_1 <- readRDS(input_path("2025_06_11_mtbi_ol_1.rds"))
mtbi_top_solution <- readRDS(proc_path("2025_06_11_mtbi_top_solution.rds"))

names(all_dls_h_ns)

unij_dl_u1 <- all_dls_h_ns$"unij_all_u_dls"$"imp_1"
unij_dl_p1 <- all_dls_h_ns$"unij_all_p_dls"$"imp_1"
unij_ol_u1 <- all_dls_h_ns$"unij_all_u_ols"$"imp_1"
unij_ol_p1 <- all_dls_h_ns$"unij_all_p_ols"$"imp_1"
```

## Matching

Finding matched uninjured controls for each mtbi subject based on a variety of variables.
Matching will be done based on the first imputed dataset of the baseline data.

```{r}
# mTBI group, first imputation
mtbi_matching_df <- as.data.frame(c(mtbi_dl_1, mtbi_ol_1))

# Uninjured group, first solo imputation
unij_matching_df_u1 <- as.data.frame(c(unij_dl_u1, unij_ol_u1))

# Uninjured group, first pooled imputation
unij_matching_df_p1 <- as.data.frame(c(unij_dl_p1, unij_ol_p1))

# Labeling if each group was or was not mTBI
mtbi_matching_df$"mtbi" <- 1
unij_matching_df_u1$"mtbi" <- 0
unij_matching_df_p1$"mtbi" <- 0

# Restricting mTBI data frame to only columns shared with uninjured
mtbi_matching_df <- dplyr::select(
    mtbi_matching_df,
    colnames(unij_matching_df_u1)
)

# Concatenating mTBI and uninjured data frames for matching
matching_df_u1 <- rbind(mtbi_matching_df, unij_matching_df_u1)
matching_df_p1 <- rbind(mtbi_matching_df, unij_matching_df_p1)
```


```{r}
# Creating parent psych matching variable
matching_df_u1$"total_parent_psych" <- matching_df_u1 |>
    dplyr::select(dplyr::starts_with("parent")) |>
    rowSums()
matching_df_p1$"total_parent_psych" <- matching_df_p1 |>
    dplyr::select(dplyr::starts_with("parent")) |>
    rowSums()

# Creating outcome matching variable
matching_df_u1$"total_impairments" <- matching_df_u1 |>
    dplyr::select(dplyr::starts_with("cbcl"), dplyr::starts_with("sds")) |>
    rowSums()
matching_df_p1$"total_impairments" <- matching_df_p1 |>
    dplyr::select(dplyr::starts_with("cbcl"), dplyr::starts_with("sds")) |>
    rowSums()
```

I investigate the following matching schemes:

1. Demographic matching (household income, race, sex, parent and youth reports of pubertal status; d)
2. Parent psychosocial matching (total parent psychosocial score; p)
3. Outcome matching (total impairments; o)
4. Demographic and parent psychosocial matching together (dp)
5. Demographic and outcome matching together (do)
6. Parent psychosocial and outcome matching together (op)
7. Demographic, parent psychosocial, and outcome matching together (dpo)

```{r}
# Establishing formulae
d_vars <- paste(
    "household_income",
    "race",
    "sex",
    "age",
    "pubertal_status_p",
    "pubertal_status_y",
    sep = " + "
)
p_vars <- "total_parent_psych"
o_vars <- "total_impairments"
dp_vars <- paste0(d_vars, " + ", p_vars)
do_vars <- paste0(d_vars, " + ", o_vars)
op_vars <- paste0(o_vars, " + ", p_vars)
dpo_vars <- paste0(d_vars, " + ", p_vars, " + ", o_vars)

match_d_results_u <- matchit(
    as.formula(paste0("mtbi ~ ", d_vars)), matching_df_u1, method = "nearest"
)
match_p_results_u <- matchit(
    as.formula(paste0("mtbi ~ ", p_vars)), matching_df_u1, method = "nearest"
)
match_o_results_u <- matchit(
    as.formula(paste0("mtbi ~ ", o_vars)), matching_df_u1, method = "nearest"
)

match_d_results_p <- matchit(
    as.formula(paste0("mtbi ~ ", d_vars)), matching_df_p1, method = "nearest"
)
match_p_results_p <- matchit(
    as.formula(paste0("mtbi ~ ", p_vars)), matching_df_p1, method = "nearest"
)
match_o_results_p <- matchit(
    as.formula(paste0("mtbi ~ ", o_vars)), matching_df_p1, method = "nearest"
)

match_dp_results_u <- matchit(
    as.formula(paste0("mtbi ~ ", dp_vars)), matching_df_u1, method = "nearest"
)
match_do_results_u <- matchit(
    as.formula(paste0("mtbi ~ ", op_vars)), matching_df_u1, method = "nearest"
)
match_op_results_u <- matchit(
    as.formula(paste0("mtbi ~ ", op_vars)), matching_df_u1, method = "nearest"
)

match_dp_results_p <- matchit(
    as.formula(paste0("mtbi ~ ", dp_vars)), matching_df_p1, method = "nearest"
)
match_do_results_p <- matchit(
    as.formula(paste0("mtbi ~ ", op_vars)), matching_df_p1, method = "nearest"
)
match_op_results_p <- matchit(
    as.formula(paste0("mtbi ~ ", op_vars)), matching_df_p1, method = "nearest"
)

match_dpo_results_u <- matchit(
    as.formula(paste0("mtbi ~ ", dp_vars)), matching_df_u1, method = "nearest"
)
match_dpo_results_p <- matchit(
    as.formula(paste0("mtbi ~ ", dp_vars)), matching_df_p1, method = "nearest"
)

# Saving plots
save_matching_plot <- function(matching_results, name) {
    grDevices::png(filename = name, width = 1000, height = 500, res = 100)
    plot(matching_results, type = "density", interactive = FALSE)
    grDevices::dev.off()
}

save_matching_plot(
    match_d_results_u,
    fig_path("match_d_results_u.png", TRUE)
)
save_matching_plot(
    match_p_results_u,
    fig_path("match_p_results_u.png", TRUE)
)
save_matching_plot(
    match_o_results_u,
    fig_path("match_o_results_u.png", TRUE)
)
save_matching_plot(
    match_d_results_p,
    fig_path("match_d_results_p.png", TRUE)
)
save_matching_plot(
    match_p_results_p,
    fig_path("match_p_results_p.png", TRUE)
)
save_matching_plot(
    match_o_results_p,
    fig_path("match_o_results_p.png", TRUE)
)
save_matching_plot(
    match_dp_results_u,
    fig_path("match_dp_results_u.png", TRUE)
)
save_matching_plot(
    match_do_results_u,
    fig_path("match_do_results_u.png", TRUE)
)
save_matching_plot(
    match_op_results_u,
    fig_path("match_op_results_u.png", TRUE)
)
save_matching_plot(
    match_dp_results_p,
    fig_path("match_dp_results_p.png", TRUE)
)
save_matching_plot(
    match_do_results_p,
    fig_path("match_do_results_p.png", TRUE)
)
save_matching_plot(
    match_op_results_p,
    fig_path("match_op_results_p.png", TRUE)
)
save_matching_plot(
    match_dpo_results_u,
    fig_path("match_dpo_results_u.png", TRUE)
)
save_matching_plot(
    match_dpo_results_p,
    fig_path("match_dpo_results_p.png", TRUE)
)
```


```{r}
# Saving matched results
match_d_u <- match.data(match_d_results_u)
match_p_u <- match.data(match_p_results_u)
match_o_u <- match.data(match_o_results_u)
match_d_p <- match.data(match_d_results_p)
match_p_p <- match.data(match_p_results_p)
match_o_p <- match.data(match_o_results_p)
match_dp_u <- match.data(match_dp_results_u)
match_do_u <- match.data(match_do_results_u)
match_op_u <- match.data(match_op_results_u)
match_dp_p <- match.data(match_dp_results_p)
match_do_p <- match.data(match_do_results_p)
match_op_p <- match.data(match_op_results_p)
match_dpo_u <- match.data(match_dpo_results_u)
match_dpo_p <- match.data(match_dpo_results_p)

saveRDS(match_d_u, proc_path("match_d_u.rds", TRUE))
saveRDS(match_p_u, proc_path("match_p_u.rds", TRUE))
saveRDS(match_o_u, proc_path("match_o_u.rds", TRUE))
saveRDS(match_d_p, proc_path("match_d_p.rds", TRUE))
saveRDS(match_p_p, proc_path("match_p_p.rds", TRUE))
saveRDS(match_o_p, proc_path("match_o_p.rds", TRUE))
saveRDS(match_dp_u, proc_path("match_dp_u.rds", TRUE))
saveRDS(match_do_u, proc_path("match_do_u.rds", TRUE))
saveRDS(match_op_u, proc_path("match_op_u.rds", TRUE))
saveRDS(match_dp_p, proc_path("match_dp_p.rds", TRUE))
saveRDS(match_do_p, proc_path("match_do_p.rds", TRUE))
saveRDS(match_op_p, proc_path("match_op_p.rds", TRUE))
saveRDS(match_dpo_u, proc_path("match_dpo_u.rds", TRUE))
saveRDS(match_dpo_p, proc_path("match_dpo_p.rds", TRUE))
```

```{r}
match_d_u <- readRDS(proc_path("2025_06_15_match_d_u.rds"))
match_p_u <- readRDS(proc_path("2025_06_15_match_p_u.rds"))
match_o_u <- readRDS(proc_path("2025_06_15_match_o_u.rds"))
match_d_p <- readRDS(proc_path("2025_06_15_match_d_p.rds"))
match_p_p <- readRDS(proc_path("2025_06_15_match_p_p.rds"))
match_o_p <- readRDS(proc_path("2025_06_15_match_o_p.rds"))
match_dp_u <- readRDS(proc_path("2025_06_15_match_dp_u.rds"))
match_do_u <- readRDS(proc_path("2025_06_15_match_do_u.rds"))
match_op_u <- readRDS(proc_path("2025_06_15_match_op_u.rds"))
match_dp_p <- readRDS(proc_path("2025_06_15_match_dp_p.rds"))
match_do_p <- readRDS(proc_path("2025_06_15_match_do_p.rds"))
match_op_p <- readRDS(proc_path("2025_06_15_match_op_p.rds"))
match_dpo_u <- readRDS(proc_path("2025_06_15_match_dpo_u.rds"))
match_dpo_p <- readRDS(proc_path("2025_06_15_match_dpo_p.rds"))
```

```{r}
# Extracting the matched uninjured subjects
matched_unij_d_u <- dplyr::filter(match_d_u, mtbi == 0)$"uid"
matched_unij_p_u <- dplyr::filter(match_p_u, mtbi == 0)$"uid"
matched_unij_o_u <- dplyr::filter(match_o_u, mtbi == 0)$"uid"
matched_unij_d_p <- dplyr::filter(match_d_p, mtbi == 0)$"uid"
matched_unij_p_p <- dplyr::filter(match_p_p, mtbi == 0)$"uid"
matched_unij_o_p <- dplyr::filter(match_o_p, mtbi == 0)$"uid"
matched_unij_dp_u <- dplyr::filter(match_dp_u, mtbi == 0)$"uid"
matched_unij_do_u <- dplyr::filter(match_do_u, mtbi == 0)$"uid"
matched_unij_op_u <- dplyr::filter(match_op_u, mtbi == 0)$"uid"
matched_unij_dp_p <- dplyr::filter(match_dp_p, mtbi == 0)$"uid"
matched_unij_do_p <- dplyr::filter(match_do_p, mtbi == 0)$"uid"
matched_unij_op_p <- dplyr::filter(match_op_p, mtbi == 0)$"uid"
matched_unij_dpo_u <- dplyr::filter(match_dpo_u, mtbi == 0)$"uid"
matched_unij_dpo_p <- dplyr::filter(match_dpo_p, mtbi == 0)$"uid"

write_csv(
    data.frame(subjectkey = matched_unij_d_u),
    sub_path("matched_unij_d_u.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_p_u),
    sub_path("matched_unij_p_u.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_o_u),
    sub_path("matched_unij_o_u.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_d_p),
    sub_path("matched_unij_d_p.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_p_p),
    sub_path("matched_unij_p_p.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_o_p),
    sub_path("matched_unij_o_p.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_dp_u),
    sub_path("matched_unij_dp_u.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_do_u),
    sub_path("matched_unij_do_u.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_op_u),
    sub_path("matched_unij_op_u.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_dp_p),
    sub_path("matched_unij_dp_p.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_do_p),
    sub_path("matched_unij_do_p.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_op_p),
    sub_path("matched_unij_op_p.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_dpo_u),
    sub_path("matched_unij_dpo_u.csv", TRUE)
)
write_csv(
    data.frame(subjectkey = matched_unij_dpo_p),
    sub_path("matched_unij_dpo_p.csv", TRUE)
)
```

```{r}
matched_unij_d_u <- read_subjects(
    sub_path("2025_06_15_matched_unij_d_u.csv")
)
matched_unij_p_u <- read_subjects(
    sub_path("2025_06_15_matched_unij_p_u.csv")
)
matched_unij_o_u <- read_subjects(
    sub_path("2025_06_15_matched_unij_o_u.csv")
)
matched_unij_d_p <- read_subjects(
    sub_path("2025_06_15_matched_unij_d_p.csv")
)
matched_unij_p_p <- read_subjects(
    sub_path("2025_06_15_matched_unij_p_p.csv")
)
matched_unij_o_p <- read_subjects(
    sub_path("2025_06_15_matched_unij_o_p.csv")
)
matched_unij_dp_u <- read_subjects(
    sub_path("2025_06_15_matched_unij_dp_u.csv")
)
matched_unij_do_u <- read_subjects(
    sub_path("2025_06_15_matched_unij_do_u.csv")
)
matched_unij_op_u <- read_subjects(
    sub_path("2025_06_15_matched_unij_op_u.csv")
)
matched_unij_dp_p <- read_subjects(
    sub_path("2025_06_15_matched_unij_dp_p.csv")
)
matched_unij_do_p <- read_subjects(
    sub_path("2025_06_15_matched_unij_do_p.csv")
)
matched_unij_op_p <- read_subjects(
    sub_path("2025_06_15_matched_unij_op_p.csv")
)
matched_unij_dpo_u <- read_subjects(
    sub_path("2025_06_15_matched_unij_dpo_u.csv")
)
matched_unij_dpo_p <- read_subjects(
    sub_path("2025_06_15_matched_unij_dpo_p.csv")
)
```

```{r}

matched_uubjects <- list(
    "d_u" = matched_unij_d_u,
    "p_u" = matched_unij_p_u,
    "o_u" = matched_unij_o_u,
    "d_p" = matched_unij_d_p,
    "p_p" = matched_unij_p_p,
    "o_p" = matched_unij_o_p,
    "dp_u" = matched_unij_dp_u,
    "do_u" = matched_unij_do_u,
    "op_u" = matched_unij_op_u,
    "dp_p" = matched_unij_dp_p,
    "do_p" = matched_unij_do_p,
    "op_p" = matched_unij_op_p,
    "dpo_u" = matched_unij_dpo_u,
    "dpo_p" = matched_unij_dpo_p
)

intersect(matched_unij_dpo_p, matched_unij_d_u)

match_mat <- matrix(ncol = length(matched_subjects), nrow = length(matched_subjects))
for (i in seq_along(matched_subjects)) {
    for (j in seq_along(matched_subjects)) {
        match_mat[i, j] <- length(intersect(matched_subjects[[i]], matched_subjects[[j]]))
        match_mat[j, i] <- match_mat[i, j]
    }
}
match_mat <- match_mat / 434 * 100

mat_names <- names(matched_subjects)
mat_names <- gsub("_u", " (Unpooled)", mat_names)
mat_names <- gsub("_p", " (Pooled)", mat_names)
mat_names <- gsub("dpo", "D, P, O", mat_names)
mat_names <- gsub("dp", "D, P", mat_names)
mat_names <- gsub("do", "D, O", mat_names)
mat_names <- gsub("op", "O, P", mat_names)
mat_names <- gsub("d \\(", "D (", mat_names)
mat_names <- gsub("o \\(", "O (", mat_names)
mat_names <- gsub("p \\(", "P (", mat_names)
mat_names

rownames(match_mat) <- mat_names
colnames(match_mat) <- mat_names

match_mat_hm <- ComplexHeatmap::Heatmap(
    match_mat,
    heatmap_legend_param = list(
        title = "% Subject\nOverlap"
    )
)

save_heatmap(
    heatmap = match_mat_hm,
    path = fig_path("match_mat_hm.png", TRUE),
    width = 550,
    height = 500,
    res = 100
)
```

## Subsetting matched unijured data and out of model lists

```{r}
# Function reduces a data list to only subjects in the subject vector
subject_filter_dl <- function(data_list, subject_vector) {
    data_list <- data_list |>
        dlapply(
            function(x) {
                keep_subs <- x$"data"$"uid" %in% subject_vector
                x$"data" <- x$"data"[keep_subs, ]
                return(x)
            }
        )
    return(data_list)
}

set.seed(42)
random_unij_subs <- sample(unij_ns_subs, size = 434)

matched_unij_dl_d_u <- subject_filter_dl(unij_dl_u1, matched_unij_d_u)
matched_unij_dl_d_p <- subject_filter_dl(unij_dl_p1, matched_unij_d_p)

matched_unij_dl_p_u <- subject_filter_dl(unij_dl_u1, matched_unij_p_u)
matched_unij_dl_p_p <- subject_filter_dl(unij_dl_p1, matched_unij_p_p)

matched_unij_dl_o_u <- subject_filter_dl(unij_dl_u1, matched_unij_o_u)
matched_unij_dl_o_p <- subject_filter_dl(unij_dl_p1, matched_unij_o_p)

matched_unij_dl_do_u <- subject_filter_dl(unij_dl_u1, matched_unij_do_u)
matched_unij_dl_do_p <- subject_filter_dl(unij_dl_p1, matched_unij_do_p)

matched_unij_dl_dp_u <- subject_filter_dl(unij_dl_u1, matched_unij_dp_u)
matched_unij_dl_dp_p <- subject_filter_dl(unij_dl_p1, matched_unij_dp_p)

matched_unij_dl_op_u <- subject_filter_dl(unij_dl_u1, matched_unij_op_u)
matched_unij_dl_op_p <- subject_filter_dl(unij_dl_p1, matched_unij_op_p)

matched_unij_dl_dpo_p <- subject_filter_dl(unij_dl_p1, matched_unij_dpo_p)
matched_unij_dl_dpo_u <- subject_filter_dl(unij_dl_u1, matched_unij_dpo_u)

random_unij_dl_u1 <- subject_filter_dl(unij_dl_u1, paste0("uid_", random_unij_subs))
random_unij_dl_p1 <- subject_filter_dl(unij_dl_p1, paste0("uid_", random_unij_subs))

matched_unij_ol_d_u <- subject_filter_dl(unij_ol_u1, matched_unij_d_u)
matched_unij_ol_d_p <- subject_filter_dl(unij_ol_p1, matched_unij_d_p)

matched_unij_ol_p_u <- subject_filter_dl(unij_ol_u1, matched_unij_p_u)
matched_unij_ol_p_p <- subject_filter_dl(unij_ol_p1, matched_unij_p_p)

matched_unij_ol_o_u <- subject_filter_dl(unij_ol_u1, matched_unij_o_u)
matched_unij_ol_o_p <- subject_filter_dl(unij_ol_p1, matched_unij_o_p)

matched_unij_ol_do_u <- subject_filter_dl(unij_ol_u1, matched_unij_do_u)
matched_unij_ol_do_p <- subject_filter_dl(unij_ol_p1, matched_unij_do_p)

matched_unij_ol_dp_u <- subject_filter_dl(unij_ol_u1, matched_unij_dp_u)
matched_unij_ol_dp_p <- subject_filter_dl(unij_ol_p1, matched_unij_dp_p)

matched_unij_ol_op_u <- subject_filter_dl(unij_ol_u1, matched_unij_op_u)
matched_unij_ol_op_p <- subject_filter_dl(unij_ol_p1, matched_unij_op_p)

matched_unij_ol_dpo_p <- subject_filter_dl(unij_ol_p1, matched_unij_dpo_p)
matched_unij_ol_dpo_u <- subject_filter_dl(unij_ol_u1, matched_unij_dpo_u)

random_unij_ol_u1 <- subject_filter_dl(unij_ol_u1, paste0("uid_", random_unij_subs))
random_unij_ol_p1 <- subject_filter_dl(unij_ol_p1, paste0("uid_", random_unij_subs))

saveRDS(matched_unij_dl_d_u, proc_path("matched_unij_dl_d_u.rds", TRUE))
saveRDS(matched_unij_dl_p_u, proc_path("matched_unij_dl_p_u.rds", TRUE))
saveRDS(matched_unij_dl_o_u, proc_path("matched_unij_dl_o_u.rds", TRUE))
saveRDS(matched_unij_dl_d_p, proc_path("matched_unij_dl_d_p.rds", TRUE))
saveRDS(matched_unij_dl_p_p, proc_path("matched_unij_dl_p_p.rds", TRUE))
saveRDS(matched_unij_dl_o_p, proc_path("matched_unij_dl_o_p.rds", TRUE))
saveRDS(matched_unij_dl_dp_u, proc_path("matched_unij_dl_dp_u.rds", TRUE))
saveRDS(matched_unij_dl_do_u, proc_path("matched_unij_dl_do_u.rds", TRUE))
saveRDS(matched_unij_dl_op_u, proc_path("matched_unij_dl_op_u.rds", TRUE))
saveRDS(matched_unij_dl_dp_p, proc_path("matched_unij_dl_dp_p.rds", TRUE))
saveRDS(matched_unij_dl_do_p, proc_path("matched_unij_dl_do_p.rds", TRUE))
saveRDS(matched_unij_dl_op_p, proc_path("matched_unij_dl_op_p.rds", TRUE))
saveRDS(matched_unij_dl_dpo_p, proc_path("matched_unij_dl_dpo_p.rds", TRUE))
saveRDS(matched_unij_dl_dpo_u, proc_path("matched_unij_dl_dpo_u.rds", TRUE))
saveRDS(random_unij_dl_u1, proc_path("random_unij_dl_u1.rds", TRUE))
saveRDS(random_unij_dl_p1, proc_path("random_unij_dl_p1.rds", TRUE))

saveRDS(matched_unij_ol_d_u, proc_path("matched_unij_ol_d_u.rds", TRUE))
saveRDS(matched_unij_ol_p_u, proc_path("matched_unij_ol_p_u.rds", TRUE))
saveRDS(matched_unij_ol_o_u, proc_path("matched_unij_ol_o_u.rds", TRUE))
saveRDS(matched_unij_ol_d_p, proc_path("matched_unij_ol_d_p.rds", TRUE))
saveRDS(matched_unij_ol_p_p, proc_path("matched_unij_ol_p_p.rds", TRUE))
saveRDS(matched_unij_ol_o_p, proc_path("matched_unij_ol_o_p.rds", TRUE))
saveRDS(matched_unij_ol_dp_u, proc_path("matched_unij_ol_dp_u.rds", TRUE))
saveRDS(matched_unij_ol_do_u, proc_path("matched_unij_ol_do_u.rds", TRUE))
saveRDS(matched_unij_ol_op_u, proc_path("matched_unij_ol_op_u.rds", TRUE))
saveRDS(matched_unij_ol_dp_p, proc_path("matched_unij_ol_dp_p.rds", TRUE))
saveRDS(matched_unij_ol_do_p, proc_path("matched_unij_ol_do_p.rds", TRUE))
saveRDS(matched_unij_ol_op_p, proc_path("matched_unij_ol_op_p.rds", TRUE))
saveRDS(matched_unij_ol_dpo_p, proc_path("matched_unij_ol_dpo_p.rds", TRUE))
saveRDS(matched_unij_ol_dpo_u, proc_path("matched_unij_ol_dpo_u.rds", TRUE))
saveRDS(random_unij_ol_u1, proc_path("random_unij_ol_u1.rds", TRUE))
saveRDS(random_unij_ol_p1, proc_path("random_unij_ol_p1.rds", TRUE))
```

```{r}
# CHECKPOINT
matched_unij_dl_d_u <- readRDS(proc_path("2025_06_15_matched_unij_dl_d_u.rds"))
matched_unij_dl_p_u <- readRDS(proc_path("2025_06_15_matched_unij_dl_p_u.rds"))
matched_unij_dl_o_u <- readRDS(proc_path("2025_06_15_matched_unij_dl_o_u.rds"))
matched_unij_dl_d_p <- readRDS(proc_path("2025_06_15_matched_unij_dl_d_p.rds"))
matched_unij_dl_p_p <- readRDS(proc_path("2025_06_15_matched_unij_dl_p_p.rds"))
matched_unij_dl_o_p <- readRDS(proc_path("2025_06_15_matched_unij_dl_o_p.rds"))
matched_unij_dl_dp_u <- readRDS(proc_path("2025_06_15_matched_unij_dl_dp_u.rds"))
matched_unij_dl_do_u <- readRDS(proc_path("2025_06_15_matched_unij_dl_do_u.rds"))
matched_unij_dl_op_u <- readRDS(proc_path("2025_06_15_matched_unij_dl_op_u.rds"))
matched_unij_dl_dp_p <- readRDS(proc_path("2025_06_15_matched_unij_dl_dp_p.rds"))
matched_unij_dl_do_p <- readRDS(proc_path("2025_06_15_matched_unij_dl_do_p.rds"))
matched_unij_dl_op_p <- readRDS(proc_path("2025_06_15_matched_unij_dl_op_p.rds"))
matched_unij_dl_dpo_p <- readRDS(proc_path("2025_06_15_matched_unij_dl_dpo_p.rds"))
matched_unij_dl_dpo_u <- readRDS(proc_path("2025_06_15_matched_unij_dl_dpo_u.rds"))
random_unij_dl_u1 <- readRDS(proc_path("2025_06_15_random_unij_dl_u1.rds"))
random_unij_dl_p1 <- readRDS(proc_path("2025_06_15_random_unij_dl_p1.rds"))

matched_unij_ol_d_u <- readRDS(proc_path("2025_06_15_matched_unij_ol_d_u.rds"))
matched_unij_ol_p_u <- readRDS(proc_path("2025_06_15_matched_unij_ol_p_u.rds"))
matched_unij_ol_o_u <- readRDS(proc_path("2025_06_15_matched_unij_ol_o_u.rds"))
matched_unij_ol_d_p <- readRDS(proc_path("2025_06_15_matched_unij_ol_d_p.rds"))
matched_unij_ol_p_p <- readRDS(proc_path("2025_06_15_matched_unij_ol_p_p.rds"))
matched_unij_ol_o_p <- readRDS(proc_path("2025_06_15_matched_unij_ol_o_p.rds"))
matched_unij_ol_dp_u <- readRDS(proc_path("2025_06_15_matched_unij_ol_dp_u.rds"))
matched_unij_ol_do_u <- readRDS(proc_path("2025_06_15_matched_unij_ol_do_u.rds"))
matched_unij_ol_op_u <- readRDS(proc_path("2025_06_15_matched_unij_ol_op_u.rds"))
matched_unij_ol_dp_p <- readRDS(proc_path("2025_06_15_matched_unij_ol_dp_p.rds"))
matched_unij_ol_do_p <- readRDS(proc_path("2025_06_15_matched_unij_ol_do_p.rds"))
matched_unij_ol_op_p <- readRDS(proc_path("2025_06_15_matched_unij_ol_op_p.rds"))
matched_unij_ol_dpo_p <- readRDS(proc_path("2025_06_15_matched_unij_ol_dpo_p.rds"))
matched_unij_ol_dpo_u <- readRDS(proc_path("2025_06_15_matched_unij_ol_dpo_u.rds"))
random_unij_ol_u1 <- readRDS(proc_path("2025_06_15_random_unij_ol_u1.rds"))
random_unij_ol_p1 <- readRDS(proc_path("2025_06_15_random_unij_ol_p1.rds"))
```

## metaSNF

```{r}
set.seed(42)
matched_config <- snf_config(
    matched_unij_dl_d_u,
    n_solutions = 200,
    cnt_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    dsc_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ord_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    use_default_dist_fns = TRUE
)

saveRDS(matched_config, proc_path("matched_config.rds", TRUE))
```

```{r}
# CHECKPOINT
matched_config <- readRDS(proc_path("2025_06_15_matched_config.rds"))
```

```{r}
# SNF
matched_unij_sol_df_d_u <- progressr::with_progress(batch_snf(matched_unij_dl_d_u, matched_config, processes = "max"))
saveRDS(matched_unij_sol_df_d_u, proc_path("matched_unij_sol_df_d_u.rds", TRUE))
cat("snf 1 done\n")
matched_unij_sol_df_p_u <- progressr::with_progress(batch_snf(matched_unij_dl_p_u, matched_config, processes = "max"))
saveRDS(matched_unij_sol_df_p_u, proc_path("matched_unij_sol_df_p_u.rds", TRUE))
cat("snf 2 done\n")
matched_unij_sol_df_o_u <- progressr::with_progress(batch_snf(matched_unij_dl_o_u, matched_config, processes = "max"))
saveRDS(matched_unij_sol_df_o_u, proc_path("matched_unij_sol_df_o_u.rds", TRUE))
cat("snf 3 done\n")
matched_unij_sol_df_d_p <- progressr::with_progress(batch_snf(matched_unij_dl_d_p, matched_config, processes = "max"))
saveRDS(matched_unij_sol_df_d_p, proc_path("matched_unij_sol_df_d_p.rds", TRUE))
cat("snf 4 done\n")
matched_unij_sol_df_p_p <- progressr::with_progress(batch_snf(matched_unij_dl_p_p, matched_config, processes = "max"))
saveRDS(matched_unij_sol_df_p_p, proc_path("matched_unij_sol_df_p_p.rds", TRUE))
cat("snf 5 done\n")
```

```{r}
matched_unij_sol_df_o_p <- progressr::with_progress(batch_snf(matched_unij_dl_o_p, matched_config, processes = "max"))
saveRDS(matched_unij_sol_df_o_p, proc_path("matched_unij_sol_df_o_p.rds", TRUE))
cat("snf 6 done\n")
matched_unij_sol_df_dp_u <- progressr::with_progress(batch_snf(matched_unij_dl_dp_u, matched_config, processes = "max"))
saveRDS(matched_unij_sol_df_dp_u, proc_path("matched_unij_sol_df_dp_u.rds", TRUE))
cat("snf 7 done\n")
matched_unij_sol_df_do_u <- progressr::with_progress(batch_snf(matched_unij_dl_do_u, matched_config, processes = "max"))
saveRDS(matched_unij_sol_df_do_u, proc_path("matched_unij_sol_df_do_u.rds", TRUE))
cat("snf 8 done\n")
matched_unij_sol_df_op_u <- progressr::with_progress(batch_snf(matched_unij_dl_op_u, matched_config, processes = "max"))
saveRDS(matched_unij_sol_df_op_u, proc_path("matched_unij_sol_df_op_u.rds", TRUE))
cat("snf 9 done\n")
matched_unij_sol_df_dp_p <- progressr::with_progress(batch_snf(matched_unij_dl_dp_p, matched_config, processes = "max"))
saveRDS(matched_unij_sol_df_dp_p, proc_path("matched_unij_sol_df_dp_p.rds", TRUE))
cat("snf 10 done\n")
```

```{r}
matched_unij_sol_df_do_p <- progressr::with_progress(batch_snf(matched_unij_dl_do_p, matched_config, processes = "max"))
saveRDS(matched_unij_sol_df_do_p, proc_path("matched_unij_sol_df_do_p.rds", TRUE))
cat("snf 11 done\n")
matched_unij_sol_df_op_p <- progressr::with_progress(batch_snf(matched_unij_dl_op_p, matched_config, processes = "max"))
saveRDS(matched_unij_sol_df_op_p, proc_path("matched_unij_sol_df_op_p.rds", TRUE))
cat("snf 12 done\n")
matched_unij_sol_df_dpo_p <- progressr::with_progress(batch_snf(matched_unij_dl_dpo_p, matched_config, processes = "max"))
saveRDS(matched_unij_sol_df_dpo_p, proc_path("matched_unij_sol_df_dpo_p.rds", TRUE))
cat("snf 13 done\n")
matched_unij_sol_df_dpo_u <- progressr::with_progress(batch_snf(matched_unij_dl_dpo_u, matched_config, processes = "max"))
saveRDS(matched_unij_sol_df_dpo_u, proc_path("matched_unij_sol_df_dpo_u.rds", TRUE))
cat("snf 14 done\n")

random_unij_sol_df_u1 <- progressr::with_progress(batch_snf(random_unij_dl_u1, matched_config, processes = "max"))
saveRDS(random_unij_sol_df_u1, proc_path("random_unij_sol_df_u1.rds", TRUE))
cat("snf 15 done\n")
random_unij_sol_df_p1 <- progressr::with_progress(batch_snf(random_unij_dl_p1, matched_config, processes = "max"))
saveRDS(random_unij_sol_df_p1, proc_path("random_unij_sol_df_p1.rds", TRUE))
```

```{r}
# HERE 2025-06-15
matched_unij_sol_df_dpo_u <- readRDS(proc_path("2025_06_15_matched_unij_sol_df_dpo_u.rds"))
matched_unij_sol_df_dpo_p <- readRDS(proc_path("2025_06_15_matched_unij_sol_df_dpo_p.rds"))
matched_unij_sol_df_op_p  <- readRDS(proc_path("2025_06_15_matched_unij_sol_df_op_p.rds"))
matched_unij_sol_df_do_p  <- readRDS(proc_path("2025_06_15_matched_unij_sol_df_do_p.rds"))
matched_unij_sol_df_dp_p  <- readRDS(proc_path("2025_06_15_matched_unij_sol_df_dp_p.rds"))
matched_unij_sol_df_op_u  <- readRDS(proc_path("2025_06_15_matched_unij_sol_df_op_u.rds"))
matched_unij_sol_df_do_u  <- readRDS(proc_path("2025_06_15_matched_unij_sol_df_do_u.rds"))
matched_unij_sol_df_dp_u  <- readRDS(proc_path("2025_06_15_matched_unij_sol_df_dp_u.rds"))
matched_unij_sol_df_o_p   <- readRDS(proc_path("2025_06_15_matched_unij_sol_df_o_p.rds"))
matched_unij_sol_df_p_p   <- readRDS(proc_path("2025_06_15_matched_unij_sol_df_p_p.rds"))
matched_unij_sol_df_d_p   <- readRDS(proc_path("2025_06_15_matched_unij_sol_df_d_p.rds"))
matched_unij_sol_df_o_u   <- readRDS(proc_path("2025_06_15_matched_unij_sol_df_o_u.rds"))
matched_unij_sol_df_p_u   <- readRDS(proc_path("2025_06_15_matched_unij_sol_df_p_u.rds"))
matched_unij_sol_df_d_u   <- readRDS(proc_path("2025_06_15_matched_unij_sol_df_d_u.rds"))

random_unij_sol_df_u1     <- readRDS(proc_path("2025_06_17_random_unij_sol_df_u1.rds"))
random_unij_sol_df_p1     <- readRDS(proc_path("2025_06_17_random_unij_sol_df_p1.rds"))
```

```{r}
matched_unij_ext_sol_df_dpo_u <- extend_solutions(
    matched_unij_sol_df_dpo_u,
    dl = matched_unij_dl_dpo_u,
    target_dl = matched_unij_ol_dpo_u,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(matched_unij_ext_sol_df_dpo_u, proc_path("matched_unij_ext_sol_df_dpo_u.rds", TRUE))

matched_unij_ext_sol_df_dpo_p <- extend_solutions(
    matched_unij_sol_df_dpo_p,
    dl = matched_unij_dl_dpo_p,
    target_dl = matched_unij_ol_dpo_p,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(matched_unij_ext_sol_df_dpo_p, proc_path("matched_unij_ext_sol_df_dpo_p.rds", TRUE))

matched_unij_ext_sol_df_op_p <- extend_solutions(
    matched_unij_sol_df_op_p,
    dl = matched_unij_dl_op_p,
    target_dl = matched_unij_ol_op_p,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(matched_unij_ext_sol_df_op_p, proc_path("matched_unij_ext_sol_df_op_p.rds", TRUE))
matched_unij_ext_sol_df_do_p <- extend_solutions(
    matched_unij_sol_df_do_p,
    dl = matched_unij_dl_do_p,
    target_dl = matched_unij_ol_do_p,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(matched_unij_ext_sol_df_do_p, proc_path("matched_unij_ext_sol_df_do_p.rds", TRUE))
matched_unij_ext_sol_df_dp_p <- extend_solutions(
    matched_unij_sol_df_dp_p,
    dl = matched_unij_dl_dp_p,
    target_dl = matched_unij_ol_dp_p,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(matched_unij_ext_sol_df_dp_p, proc_path("matched_unij_ext_sol_df_dp_p.rds", TRUE))
matched_unij_ext_sol_df_op_u <- extend_solutions(
    matched_unij_sol_df_op_u,
    dl = matched_unij_dl_op_u,
    target_dl = matched_unij_ol_op_u,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(matched_unij_ext_sol_df_op_u, proc_path("matched_unij_ext_sol_df_op_u.rds", TRUE))
matched_unij_ext_sol_df_do_u <- extend_solutions(
    matched_unij_sol_df_do_u,
    dl = matched_unij_dl_do_u,
    target_dl = matched_unij_ol_do_u,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(matched_unij_ext_sol_df_do_u, proc_path("matched_unij_ext_sol_df_do_u.rds", TRUE))
#
matched_unij_ext_sol_df_dp_u <- extend_solutions(
    matched_unij_sol_df_dp_u,
    dl = matched_unij_dl_dp_u,
    target_dl = matched_unij_ol_dp_u,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(matched_unij_ext_sol_df_dp_u, proc_path("matched_unij_ext_sol_df_dp_u.rds", TRUE))
matched_unij_ext_sol_df_o_p <- extend_solutions(
    matched_unij_sol_df_o_p,
    dl = matched_unij_dl_o_p,
    target_dl = matched_unij_ol_o_p,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(matched_unij_ext_sol_df_o_p, proc_path("matched_unij_ext_sol_df_o_p.rds", TRUE))
matched_unij_ext_sol_df_p_p <- extend_solutions(
    matched_unij_sol_df_p_p,
    dl = matched_unij_dl_p_p,
    target_dl = matched_unij_ol_p_p,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(matched_unij_ext_sol_df_p_p, proc_path("matched_unij_ext_sol_df_p_p.rds", TRUE))
matched_unij_ext_sol_df_d_p <- extend_solutions(
    matched_unij_sol_df_d_p,
    dl = matched_unij_dl_d_p,
    target_dl = matched_unij_ol_d_p,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(matched_unij_ext_sol_df_d_p, proc_path("matched_unij_ext_sol_df_d_p.rds", TRUE))
matched_unij_ext_sol_df_o_u <- extend_solutions(
    matched_unij_sol_df_o_u,
    dl = matched_unij_dl_o_u,
    target_dl = matched_unij_ol_o_u,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(matched_unij_ext_sol_df_o_u, proc_path("matched_unij_ext_sol_df_o_u.rds", TRUE))
matched_unij_ext_sol_df_p_u <- extend_solutions(
    matched_unij_sol_df_p_u,
    dl = matched_unij_dl_p_u,
    target_dl = matched_unij_ol_p_u,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(matched_unij_ext_sol_df_p_u, proc_path("matched_unij_ext_sol_df_p_u.rds", TRUE))
matched_unij_ext_sol_df_d_u <- extend_solutions(
    matched_unij_sol_df_d_u,
    dl = matched_unij_dl_d_u,
    target_dl = matched_unij_ol_d_u,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(matched_unij_ext_sol_df_d_u, proc_path("matched_unij_ext_sol_df_d_u.rds", TRUE))
random_unij_ext_sol_df_u1 <- extend_solutions(
    random_unij_sol_df_u1,
    dl = random_unij_dl_u1,
    target_dl = random_unij_ol_u1,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(random_unij_ext_sol_df_u1, proc_path("random_unij_ext_sol_df_u1.rds", TRUE))
random_unij_ext_sol_df_p1 <- extend_solutions(
    random_unij_sol_df_p1,
    dl = random_unij_dl_p1,
    target_dl = random_unij_ol_p1,
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(random_unij_ext_sol_df_p1, proc_path("random_unij_ext_sol_df_p1.rds", TRUE))
```

```{r}
# CHECKPOINT - extended solutions data frames
matched_unij_ext_sol_df_d_u <- readRDS(proc_path("2025_06_17_matched_unij_ext_sol_df_d_u.rds"))
matched_unij_ext_sol_df_p_u <- readRDS(proc_path("2025_06_17_matched_unij_ext_sol_df_p_u.rds"))
matched_unij_ext_sol_df_o_u <- readRDS(proc_path("2025_06_17_matched_unij_ext_sol_df_o_u.rds"))
matched_unij_ext_sol_df_d_p <- readRDS(proc_path("2025_06_17_matched_unij_ext_sol_df_d_p.rds"))
matched_unij_ext_sol_df_p_p <- readRDS(proc_path("2025_06_17_matched_unij_ext_sol_df_p_p.rds"))
matched_unij_ext_sol_df_o_p <- readRDS(proc_path("2025_06_17_matched_unij_ext_sol_df_o_p.rds"))
matched_unij_ext_sol_df_dp_u <- readRDS(proc_path("2025_06_17_matched_unij_ext_sol_df_dp_u.rds"))
matched_unij_ext_sol_df_do_u <- readRDS(proc_path("2025_06_17_matched_unij_ext_sol_df_do_u.rds"))
matched_unij_ext_sol_df_op_u <- readRDS(proc_path("2025_06_17_matched_unij_ext_sol_df_op_u.rds"))
matched_unij_ext_sol_df_dp_p <- readRDS(proc_path("2025_06_17_matched_unij_ext_sol_df_dp_p.rds"))
matched_unij_ext_sol_df_do_p <- readRDS(proc_path("2025_06_17_matched_unij_ext_sol_df_do_p.rds"))
matched_unij_ext_sol_df_op_p <- readRDS(proc_path("2025_06_17_matched_unij_ext_sol_df_op_p.rds"))
matched_unij_ext_sol_df_dpo_p <- readRDS(proc_path("2025_06_17_matched_unij_ext_sol_df_dpo_p.rds"))
matched_unij_ext_sol_df_dpo_u <- readRDS(proc_path("2025_06_17_matched_unij_ext_sol_df_dpo_u.rds"))
random_unij_ext_sol_df_u1 <- readRDS(proc_path("2025_06_17_random_unij_ext_sol_df_u1.rds"))
random_unij_ext_sol_df_p1 <- readRDS(proc_path("2025_06_17_random_unij_ext_sol_df_p1.rds"))
```

```{r}
matched_unij_esm_list <- list(
    "d_s" = matched_unij_esm_d_s,
    "p_s" = matched_unij_esm_p_s,
    "o_s" = matched_unij_esm_o_s,
    "d_p" = matched_unij_esm_d_p,
    "p_p" = matched_unij_esm_p_p,
    "o_p" = matched_unij_esm_o_p,
    "dp_s" = matched_unij_esm_dp_s,
    "do_s" = matched_unij_esm_do_s,
    "op_s" = matched_unij_esm_op_s,
    "dp_p" = matched_unij_esm_dp_p,
    "do_p" = matched_unij_esm_do_p,
    "op_p" = matched_unij_esm_op_p,
    "dpo_p" = matched_unij_esm_dpo_p,
    "dpo_s" = matched_unij_esm_dpo_s,
    "random_s" = random_unij_esm_s1,
    "random_p" = random_unij_esm_p1
)

saveRDS(matched_unij_esm_list, proc_path("matched_unij_esm_list.rds", TRUE))
```

```{r}
matched_unij_esm_list <- readRDS(
    proc_path("2025_02_15_matched_unij_esm_list.rds")
)
```

```{r}

duplicated(matched_unij_esm_list)

vec <- matched_unij_esm_list

dup_indices <- which(duplicated(vec))

dup_indices

for (i in dup_indices) {
    cat(names(vec)[i], " is equal to:\n", sep = "")
    for (j in seq_along(vec)) {
        if (identical(vec[[i]], vec[[j]]) & i != j) {
            cat("    - ", names(vec)[j], "\n")
        }
    }
}

for (i in seq_along(vec)) {
    for (j in seq_along(vec)) {

    }
}


intersect(vec, vec)

intersect(c(1, 2, 3), c(2, 3, 4))


# Tight requirement: -log10(pval) > 4
matched_unij_esm_3c_list <- lapply(
    matched_unij_esm_list,
    function(x) {
        x <- x[x$"nclust" == 3 & -log10(x$"mean_pval") > 4, ]
        if (nrow(x) > 0) {
            return(x)
        } 
    }
)

# Loose requirement: -log10(pval) > 1
matched_unij_esm_3c_list_loose <- lapply(
    matched_unij_esm_list,
    function(x) {
        x <- x[x$"nclust" == 3 & -log10(x$"mean_pval") > 1, ]
        if (nrow(x) > 0) {
            return(x)
        } 
    }
)

# 6 tight matches
sapply(matched_unij_esm_3c_list, nrow) |>
    unlist() |>
    sum()

# 82 loose matches
sapply(matched_unij_esm_3c_list_loose, nrow) |>
    unlist() |>
    sum()

matched_unij_esm_3c_list <- matched_unij_esm_3c_list[sapply(matched_unij_esm_3c_list, function(x) nrow(x) > 0)]
matched_unij_esm_3c_list_loose <- matched_unij_esm_3c_list_loose[sapply(matched_unij_esm_3c_list_loose, function(x) nrow(x) > 0)]

saveRDS(matched_unij_esm_3c_list, proc_path("matched_unij_esm_3c_list.rds", TRUE))
saveRDS(matched_unij_esm_3c_list_loose, proc_path("matched_unij_esm_3c_list_loose.rds", TRUE))

matched_unij_esm_3c_list <- readRDS(proc_path("2025_02_15_matched_unij_esm_3c_list.rds"))
matched_unij_esm_3c_list_loose <- readRDS(proc_path("2025_02_15_matched_unij_esm_3c_list_loose.rds"))
```

```{r}
# Domain colour labels
dcols <- c(
    "AS" = "#85929e",
    "D" = "#bb8fce",
    "N" = "#e59866",
    "MH" = "#7fb3d5",
    "P" = "#52be80",
    "S" = "#d98880",
    "B" = "#ff3131"
)

# do_s, do_p, op_s, op_p
names(matched_unij_esm_3c_list)

matched_unij_do_s <- mc_manhattan_plot(
    matched_unij_esm_3c_list$"do_s",
    dl = matched_unij_dl_do_s,
    target_dl = matched_unij_ol_do_s,
    domain_colours = dcols
)

matched_unij_do_p <- mc_manhattan_plot(
    matched_unij_esm_3c_list$"do_p",
    dl = matched_unij_dl_do_p,
    target_dl = matched_unij_ol_do_p,
    domain_colours = dcols
)

matched_unij_op_s <- mc_manhattan_plot(
    matched_unij_esm_3c_list$"op_s",
    dl = matched_unij_dl_op_s,
    target_dl = matched_unij_ol_op_s,
    domain_colours = dcols
)

matched_unij_op_p <- mc_manhattan_plot(
    matched_unij_esm_3c_list$"op_p",
    dl = matched_unij_dl_op_p,
    target_dl = matched_unij_ol_op_p,
    domain_colours = dcols
)

matched_unij_manhattan_plots <- list(
    "do_s" = matched_unij_do_s,
    "do_p" = matched_unij_do_p,
    "op_s" = matched_unij_op_s,
    "op_p" = matched_unij_op_p
)

saveRDS(matched_unij_manhattan_plots, fig_path("matched_unij_manhattan_plots.rds", TRUE))
```

```{r}
# CHECKPOINT
matched_unij_manhattan_plots <- readRDS(fig_path("2025_02_15_matched_unij_manhattan_plots.rds"))
```

So we know that only a couple of combinations lead to somewhat similar cluster solutions in terms of the mean p-values on outcomes.

```{r}
# Quick save function
qs2 <- function(plot, path, w = 18, h = 14, d = 120) {    
    path <- paste0("matched_unij_", path, "_manhattan.png")
    ggsave(
        fig_path(path, TRUE),
        plot,
        width = w,
        height = h,
        dpi = d
    )
}

# Small function to calculate how tall each manhattan plot
# should be.
heighter <- function(panes) {
    panes * 4/3 + 10/3
}

qs2(matched_unij_manhattan_plots$"do_s", "do_s", h = 4.67)
qs2(matched_unij_manhattan_plots$"do_p", "do_p", h = 6)
qs2(matched_unij_manhattan_plots$"op_s", "op_s", h = 4.67)
qs2(matched_unij_manhattan_plots$"op_p", "op_p", h = 6)
```

```{r}
matched_unij_dls <- list(
    "d_s" = matched_unij_dl_d_s,
    "p_s" = matched_unij_dl_p_s,
    "o_s" = matched_unij_dl_o_s,
    "d_p" = matched_unij_dl_d_p,
    "p_p" = matched_unij_dl_p_p,
    "o_p" = matched_unij_dl_o_p,
    "dp_s" = matched_unij_dl_dp_s,
    "do_s" = matched_unij_dl_do_s,
    "op_s" = matched_unij_dl_op_s,
    "dp_p" = matched_unij_dl_dp_p,
    "do_p" = matched_unij_dl_do_p,
    "op_p" = matched_unij_dl_op_p,
    "dpo_p" = matched_unij_dl_dpo_p,
    "dpo_s" = matched_unij_dl_dpo_s,
    "random_s" = random_unij_dl_s1,
    "random_p" = random_unij_dl_p1
)

matched_unij_ols <- list(
    "d_s" = matched_unij_ol_d_s,
    "p_s" = matched_unij_ol_p_s,
    "o_s" = matched_unij_ol_o_s,
    "d_p" = matched_unij_ol_d_p,
    "p_p" = matched_unij_ol_p_p,
    "o_p" = matched_unij_ol_o_p,
    "dp_s" = matched_unij_ol_dp_s,
    "do_s" = matched_unij_ol_do_s,
    "op_s" = matched_unij_ol_op_s,
    "dp_p" = matched_unij_ol_dp_p,
    "do_p" = matched_unij_ol_do_p,
    "op_p" = matched_unij_ol_op_p,
    "dpo_p" = matched_unij_ol_dpo_p,
    "dpo_s" = matched_unij_ol_dpo_s,
    "random_s" = random_unij_ol_s1,
    "random_p" = random_unij_ol_p1
)

saveRDS(matched_unij_dls, proc_path("matched_unij_dls.rds", TRUE))
saveRDS(matched_unij_ols, proc_path("matched_unij_ols.rds", TRUE))
```

```{r}
# CHECKPOINT
matched_unij_dls <- readRDS(proc_path("2025_02_15_matched_unij_dls.rds"))
matched_unij_ols <- readRDS(proc_path("2025_02_15_matched_unij_ols.rds"))
```

```{r}
# CHECKPOINT
mtbi_gen_fts_in_long <- read_csv(
    proc_path("2025_02_13_mtbi_gen_fts_in_long.csv")
)
mtbi_gen_fts_out_long <- read_csv(
    proc_path("2025_02_13_mtbi_gen_fts_out_long.csv")
)

classifier_fts <- read_csv(proc_path("2025_02_14_classifier_fts.csv"))
classifier_fts <- classifier_fts$"classifier_fts"
```

Calculating concordance (similarity between matched uninjured solution and baseline mTBI solution topologies) using loose threshold.

```{r}
matched_pl_dfs <- lapply(
    names(matched_unij_esm_3c_list_loose),
    function(match) {
        pl <- list()
        nrows <- nrow(matched_unij_esm_3c_list_loose[[match]])
        for (row in seq_len(nrows)) {
            p <- auto_plot(
                matched_unij_esm_3c_list_loose[[match]][row, ],
                dl = c(matched_unij_dls[[match]], matched_unij_ols[[match]]),
                return_plots = FALSE
            )
            pl[[length(pl) + 1]] <- p
        }
        return(pl)
    }
)

matched_unij_esm_3c_list_loose$"op_p" |> nrow()

matched_pl_dfs

names(matched_pl_dfs) <- names(matched_unij_esm_3c_list_loose)
matched_pl_dfs <- unlist(matched_pl_dfs, recursive = FALSE)

saveRDS(matched_pl_dfs, proc_path("matched_pl_dfs.rds", TRUE))
matched_pls_dfs <- readRDS(proc_path("2025_02_15_matched_pl_dfs.rds"))

matched_pl_tops <- lapply(
    matched_pl_dfs,
    function(x) {
        topologizer(x)
    }
)

saveRDS(matched_pl_tops, proc_path("matched_pl_tops.rds", TRUE))
matched_pl_tops <- readRDS(proc_path("2025_02_15_matched_pl_tops.rds"))

matched_pl_gen_fts <- lapply(
    matched_pl_tops,
    function(x) {
        generalizable_features(x, compare_fn_a)
    }
)

mtbi_gen_long <- rbind(
    mtbi_gen_fts_in_long,
    mtbi_gen_fts_out_long
)
mtbi_gen_long <- na.omit(mtbi_gen_long)

matched_pl_gen_fts_long <- lapply(
    matched_pl_gen_fts,
    function(x) {
        long_x <- pivot_longer(
            x,
            cols = -feature,
            names_to = "comparison",
            values_to = "order_unij"
        )
        long_gen_x <- dplyr::left_join(
            mtbi_gen_long,
            long_x,
            by = c("feature", "comparison")
        ) 
        long_gen_x <- dplyr::mutate(
            long_gen_x,
            match = dplyr::case_when(
                is.na(order_unij) ~ 0,
                order != order_unij ~ 0, 
                order == order_unij ~ 1
            )
        )
        return(long_gen_x)
    }
)

matched_pl_gen_fts_long_fair <- lapply(
    matched_pl_gen_fts_long,
    function(x) {
        dplyr::filter(x, !grepl("mtbi", feature))
    }
)

concordance_list <- lapply(
    matched_pl_gen_fts_long_fair,
    function(x) {
        100 * sum(x$"match") / nrow(x)
    }
)

concordance_df <- data.frame(
    unij_set = names(concordance_list),
    concordance = unlist(concordance_list)
) |>
    arrange(desc(concordance))
rownames(concordance_df) <- NULL

write_csv(concordance_df, proc_path("matched_unij_concordance.csv", TRUE))

concordance_df <- read_csv(proc_path("2025_02_15_matched_unij_concordance.csv"))

xtable(concordance_df)

knitr::kable(
    concordance_df,
    format = "markdown",
    digits = 3,
    format.args = list(scientific = FALSE)
) |>
    writeLines(proc_path("matched_unij_concordance.txt", TRUE))

concordance_df
```

Matching by D+O and O+P seem to be best.
The D+O and O+P matching yielded identical sets of matched uninjured subjects.

```{r}
saveRDS(
    matched_unij_esm_3c_list_loose$"op_p"[11, ],
    proc_path("matched_unij_nearest_esdf.rds", TRUE)
)

top_unij_pl <- auto_plot(
    matched_unij_esm_3c_list_loose$"do_p"[11, ],
    dl = c(
        matched_unij_dls$"do_p",
        matched_unij_ols$"do_p"
    )
)

gen_in_fts <- unique(mtbi_gen_fts_in_long$"feature")
gen_in_fts[startsWith(gen_in_fts, "race_")] <- "race"
gen_in_fts[startsWith(gen_in_fts, "mtbi_mechanism_")] <- "mtbi_mechanism"
gen_in_fts <- unique(gen_in_fts)
gen_out_fts <- unique(mtbi_gen_fts_out_long$"feature")

gen_in_fts

top_unij_input_plots <- top_unij_pl[gen_in_fts]
top_unij_outcome_plots <- top_unij_pl[gen_out_fts]
top_unij_plots <- c(top_unij_input_plots, top_unij_outcome_plots)

saveRDS(top_unij_input_plots, proc_path("top_unij_input_plots.rds", TRUE))
saveRDS(top_unij_outcome_plots, proc_path("top_unij_outcome_plots.rds", TRUE))
saveRDS(top_unij_plots, proc_path("top_unij_plots.rds", TRUE))

top_unij_input_plots <- readRDS(
    proc_path("2025_02_15_top_unij_input_plots.rds")
)
top_unij_outcome_plots <- readRDS(
    proc_path("2025_02_15_top_unij_outcome_plots.rds")
)
top_unij_plots <- readRDS(
    proc_path("2025_02_18_top_unij_plots.rds")
)

outcomes <- readRDS(proc_path("2025_02_13_outputs.rds"))
relevant_fts <- c(classifier_fts, outcomes)

top_unij_plots <- top_unij_plots[!is.na(names(top_unij_plots))]

top_unij_wrapped_plots <- wrap_plots(top_unij_plots)

top_unij_wrapped_plots

ggsave(
    fig_path("top_unij_wrapped_plots.png", TRUE),
    top_unij_wrapped_plots,
    width = 45,
    height = 30,
    dpi = 50
)
```

```{r}
#Is the extent of separation significantly different?
matched_unij_nearest_esdf <- readRDS(proc_path("2025_02_16_matched_unij_nearest_esdf.rds"))
matched_unij_dl_do_p <- readRDS(proc_path("2025_02_14_matched_unij_dl_do_p.rds"))
matched_unij_ol_do_p <- readRDS(proc_path("2025_02_14_matched_unij_ol_do_p.rds"))

matched_unij_dl_df <- as.data.frame(c(matched_unij_dl_do_p, matched_unij_ol_do_p))
matched_unij_cluster_df <- t(matched_unij_nearest_esdf)

matched_unij_data_df <- dplyr::inner_join(
    matched_unij_cluster_df,
    matched_unij_dl_df,
    by = "uid"
) |>
    data.frame()
colnames(matched_unij_data_df)[2] <- "cluster"

matched_unij_data_df

saveRDS(matched_unij_data_df, proc_path("nearest_matched_unij_data_df.rds", TRUE))
```

```{r}
matched_unij_data_df <- readRDS(proc_path("2025_02_17_nearest_matched_unij_data_df.rds"))
mtbi_ful_df <- data.frame(readRDS(proc_path("2025_02_13_mtbi_ful_df.rds"))) |>
    dplyr::select(uid, cluster, dplyr::everything())

classifier_fts <- read_csv(proc_path("2025_02_14_classifier_fts.csv"))$"classifier_fts"
outcomes <- readRDS(proc_path("2025_02_13_outputs.rds"))
relevant_fts <- c(classifier_fts, outcomes)

mtbi_ful_df_relevant <- mtbi_ful_df[, c("uid", "cluster", outcomes)]
matched_unij_df_relevant <- matched_unij_data_df[, c("uid", "cluster", outcomes)]

mtbi_ful_df_relevant <- mtbi_ful_df[, c("uid", "cluster", relevant_fts)]
matched_unij_df_relevant <- matched_unij_data_df[, c("uid", "cluster", relevant_fts)]

# Initial comparison
get_mean_d <- function(df) {
    tops_df <- topologizer(df) |>
        dplyr::mutate(
            c12_d = dplyr::case_when(
                es == "d" ~ c12_es,
                es == "or" ~ suppressWarnings(log(c12_es)) * sqrt(3) / pi
            ),
            c23_d = dplyr::case_when(
                es == "d" ~ c23_es,
                es == "or" ~ suppressWarnings(log(c23_es)) * sqrt(3) / pi
            ),
            c13_d = dplyr::case_when(
                es == "d" ~ c13_es,
                es == "or" ~ suppressWarnings(log(c13_es)) * sqrt(3) / pi
            )
        ) |>
        dplyr::select(feature, c12_d, c13_d, c23_d)
    tops_df_long <- tops_df |>
        pivot_longer(
            cols = -feature,
            names_to = "comparison",
            values_to = "d"
        ) |>
        dplyr::mutate(
            d = dplyr::case_when(
                d == Inf | d == -Inf ~ NA,
                TRUE ~ abs(d)
            )
        ) |>
        na.omit()
    return(tops_df_long)
    #return(mean(tops_df_long$"d"))
}

compare_ds <- function(df1, df2) {
    tops_df1 <- topologizer(df1) |>
        dplyr::mutate(
            c12_d = dplyr::case_when(
                es == "d" ~ c12_es,
                es == "or" ~ suppressWarnings(log(c12_es)) * sqrt(3) / pi
            ),
            c23_d = dplyr::case_when(
                es == "d" ~ c23_es,
                es == "or" ~ suppressWarnings(log(c23_es)) * sqrt(3) / pi
            ),
            c13_d = dplyr::case_when(
                es == "d" ~ c13_es,
                es == "or" ~ suppressWarnings(log(c13_es)) * sqrt(3) / pi
            )
        ) |>
        dplyr::select(feature, c12_d, c13_d, c23_d)
    tops_df2 <- topologizer(df2) |>
        dplyr::mutate(
            c12_d = dplyr::case_when(
                es == "d" ~ c12_es,
                es == "or" ~ suppressWarnings(log(c12_es)) * sqrt(3) / pi
            ),
            c23_d = dplyr::case_when(
                es == "d" ~ c23_es,
                es == "or" ~ suppressWarnings(log(c23_es)) * sqrt(3) / pi
            ),
            c13_d = dplyr::case_when(
                es == "d" ~ c13_es,
                es == "or" ~ suppressWarnings(log(c13_es)) * sqrt(3) / pi
            )
        ) |>
        dplyr::select(feature, c12_d, c13_d, c23_d)
    tops_df_long1 <- tops_df1 |>
        pivot_longer(
            cols = -feature,
            names_to = "comparison",
            values_to = "d1"
        )
    tops_df_long2 <- tops_df2 |>
        pivot_longer(
            cols = -feature,
            names_to = "comparison",
            values_to = "d2"
        )
    tops_df_long <- dplyr::inner_join(
        tops_df_long1,
        tops_df_long2,
        by = c("feature", "comparison")
    ) |>
        dplyr::mutate(
            d1 = dplyr::case_when(
                d1 == Inf | d1 == -Inf ~ NA,
                TRUE ~ d1
            ),
            d2 = dplyr::case_when(
                d2 == Inf | d2 == -Inf ~ NA,
                TRUE ~ d2
            )
        ) |>
        na.omit() |>
        dplyr::mutate(
            sse = (d1 - d2)^2
        )
    return(tops_df_long)
}

mtbi_vs_mu_d <- compare_ds(mtbi_ful_df_relevant, matched_unij_df_relevant)

mtbi_vs_mu_d_plot <- mtbi_vs_mu_d |>
    dplyr::filter(feature != "sex") |>
    ggplot(
        aes(x = feature, y = sse)
    ) +
    geom_point() +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
    geom_hline(yintercept = 0.2, color = "red", alpha = 0.5, linewidth = 0.5) +
    facet_wrap(~comparison, nrow = 3)
ggsave(
    fig_path("mtbi_vs_mu_d_plot.png", TRUE),
    mtbi_vs_mu_d_plot,
    width = 9,
    height = 7,
    dpi = 120
)

# Seems to be quite a bit higher.
mtbi_mean_d <- get_mean_d(mtbi_ful_df_relevant) # 0.61
unij_mean_d <- get_mean_d(matched_unij_df_relevant) # 0.53

mtbi_mean_d

unij_mean_d



mtbi_mean_d - unij_mean_d

stacked_df <- rbind(
    mtbi_ful_df_relevant,
    matched_unij_df_relevant
)

set.seed(42)
mean_ds <- c()
for (i in 1:10) {
    print(i)
    random_df <- stacked_df[sample(nrow(stacked_df)), ]
    random_df1 <- random_df[1:427, ]
    random_df2 <- random_df[428:854, ]
    mean_d1 <- get_mean_d(random_df1)
    mean_d2 <- get_mean_d(random_df2)
    mean_ds <- c(mean_ds, (mean_d1 - mean_d2))
}

hist(mean_ds)

#Is the proportion of observations in each cluster significantly different?
#------------------------------------------------------------------------------

## qs2 image export helper function
#qs2 <- function(plot, path, w = 4, h = 4) {
#    path <- paste0("unij_a_s4_", path, ".png")
#    ggsave(fig_path(path, TRUE), plot, width = w, height = h)
#}
#
## uni-plot helper function# {{{
#uni_plot <- function(plot,
#                     ft_name,
#                     scale_fill_labels = NULL,
#                     ylims = NULL) {
#    ###########################################################################
#    plot <- plot +
#        theme(axis.title.y = element_text(size = 16))
#    ###########################################################################
#    if (class(plot$layers[[1]]$geom)[[1]] == "GeomBar") {
#        plot <- plot + labs(fill = ft_name)
#    } else {
#        plot <- plot + labs(y = ft_name)
#    }
#    if (!is.null(scale_fill_labels)) {
#        plot <- plot + scale_fill_discrete(labels = scale_fill_labels)
#    }
#    if (!is.null(ylims)) {
#        plot <- plot + ylim(ylims[[1]], ylims[[2]])
#    }
#    ###########################################################################
#    plot <- plot + labs(x = "Cluster") + theme(text = element_text(size = 16))
#    return(plot)
#}
## }}}
#
## Matched unij Input Plots
## Brain volumes
#brain_volume_plot <- uni_plot(top_unij_input_plots$"brain_volume", expression("Brain Volume "(mm^3)))
#brain_volume_plot
#qs2(brain_volume_plot, "brain_volume")
#
## Sex
#sex_plot <- uni_plot(top_unij_input_plots$"sex", "Sex", c("F", "M"))
#sex_plot
#qs2(sex_plot, "sex")
#
## cort sa
#cort_sa_plot <- uni_plot(top_unij_input_plots$"cortical_sa", expression("Cortical Surface Area "(mm^2)))
#cort_sa_plot
#qs2(cort_sa_plot, "cort_sa")
#
## Income
#household_income_plot <- uni_plot(top_unij_input_plots$"household_income", "Household Income")
#household_income_plot
#qs2(household_income_plot, "household_income")
#
## Pubertal Status - Parent Report
#pubertal_status_p_plot <- uni_plot(top_unij_input_plots$"pubertal_status_p", "Pubertal Status\n(Parent Report)")
#pubertal_status_p_plot
#qs2(pubertal_status_p_plot, "pubertal_status_p")
#
## Programs this year
#programs_this_year_plot <- uni_plot(top_unij_input_plots$"programs_this_year", "Programs This Year")
#programs_this_year_plot
#qs2(programs_this_year_plot, "programs_this_year")
#
## Non school programs
#non_school_programs_plot <- uni_plot(top_unij_input_plots$"non_school_programs", "Non-School Programs This Year", ylims= c(-0.5, 12))
#non_school_programs_plot
#qs2(non_school_programs_plot, "non_school_programs")
#
## parent_thought
#parent_thought_plot <- uni_plot(top_unij_input_plots$"parent_thought", "Parent Thought", ylims = c(-0.5, 13.5))
#parent_thought_plot
#qs2(parent_thought_plot, "parent_thought")
#
## Parent Somatic
#parent_somatic_plot <- uni_plot(top_unij_input_plots$"parent_somatic", "Parent Somatic", ylims = c(-0.5, 28))
#parent_somatic_plot
#qs2(parent_somatic_plot, "parent_somatic")
#
## Weekday screentime
#weekday_screentime_plot <- uni_plot(top_unij_input_plots$"weekday_screentime", "Weekday Screentime (hours)", ylims = c(-0.5, 21))
#weekday_screentime_plot
#qs2(weekday_screentime_plot, "weekday_screentime")
#
## parent_antisocial
#parent_antisocial_plot <- uni_plot(top_unij_input_plots$"parent_antisocial", "Parent Antisocial")
#parent_antisocial_plot
#qs2(parent_antisocial_plot, "parent_antisocial")
#
## parent_aggressive
#parent_aggressive_plot <- uni_plot(top_unij_input_plots$"parent_aggressive", "Parent Aggressive")
#parent_aggressive_plot
#qs2(parent_aggressive_plot, "parent_aggressive")
#
## Parent depress
#parent_depress_plot <- uni_plot(top_unij_input_plots$"parent_depress", "Parent Depress", ylims = c(-0.5, 28))
#parent_depress_plot
#qs2(parent_depress_plot, "parent_depress")
#
## parent_anxdep
#parent_anxdep_plot <- uni_plot(top_unij_input_plots$"parent_anxdep", "Parent Anxious-Depressed")
#parent_anxdep_plot
#qs2(parent_anxdep_plot, "parent_anxdep")
#
## Race
#race_plot <- uni_plot(top_unij_input_plots$"race", "Race", scale_fill_labels = c("Black", "Hispanic", "Other", "White"))
#race_plot
#qs2(race_plot, "race")
#
## parent_anxdisord
#parent_anxdisord_plot <- uni_plot(top_unij_input_plots$"parent_anxdisord", "Parent Anxious", ylims = c(-0.5, 13))
#parent_anxdisord_plot
#qs2(parent_anxdisord_plot, "parent_anxdisord")
#
## private_instruction
#private_instruction_plot <- uni_plot(top_unij_input_plots$"private_instruction", "Private Activities", ylims = c(-0.5, 9.5))
#private_instruction_plot
#qs2(private_instruction_plot, "private_instruction")
#
## weekend_screentime
#weekend_screentime_plot <- uni_plot(top_unij_input_plots$"weekend_screentime", "Weekend Screentime (hours)", ylims = c(-0.5, 21))
#weekend_screentime_plot
#qs2(weekend_screentime_plot, "weekend_screentime")
#
## parent_withdrawn
#parent_withdrawn_plot <- uni_plot(top_unij_input_plots$"parent_withdrawn", "Parent Withdrawn", ylims = c(-0.5, 17))
#parent_withdrawn_plot
#qs2(parent_withdrawn_plot, "parent_withdrawn")
#
## parent_avoidant
#parent_avoidant_plot <- uni_plot(top_unij_input_plots$"parent_avoidant", "Parent Avoidant", ylims = c(-0.5, 13))
#parent_avoidant_plot
#qs2(parent_avoidant_plot, "parent_avoidant")
#
## parent_hyperactive
#parent_hyperactive_plot <- uni_plot(top_unij_input_plots$"parent_hyperactive", "Parent Hyperactive", ylims = c(-0.5, 12))
#parent_hyperactive_plot
#qs2(parent_hyperactive_plot, "parent_hyperactive")
#
## fmri_cort_subcort_cors
#fmri_cort_subcort_cors_plot <- uni_plot(top_unij_input_plots$"fmri_cort_subcort_cors", "fMRI Cort-Subcort Corrs", ylims = c(-0.15, 0.2))
#fmri_cort_subcort_cors_plot
#qs2(fmri_cort_subcort_cors_plot, "fmri_cort_subcort_cors")
#
## Parent attention
#parent_attention_plot <- uni_plot(top_unij_input_plots$"parent_attention", "Parent Attention")
#parent_attention_plot
#qs2(parent_attention_plot, "parent_attention")
#
## parent_perstr
#parent_perstr_plot <- uni_plot(top_unij_input_plots$"parent_perstr", "Parent Personal Strength")
#parent_perstr_plot
#qs2(parent_perstr_plot, "parent_perstr")
#
## parent_intrusive
#parent_intrusive_plot <- uni_plot(top_unij_input_plots$"parent_intrusive", "Parent Intrusive", ylims = c(-0.5, 12))
#parent_intrusive_plot
#qs2(parent_intrusive_plot, "parent_intrusive")
#
## family_fight_p
#family_fight_p_plot <- uni_plot(top_unij_input_plots$"family_fight_p", "Family Fights\n(Parent Report)", scale_fill_labels = c("No", "Yes"))
#family_fight_p_plot
#qs2(family_fight_p_plot, "family_fight_p")
#
## headache_history
#headache_history_plot <- uni_plot(top_unij_input_plots$"headache_history", "Headache\nHistory", c("No", "Yes"))
#headache_history_plot
#qs2(headache_history_plot, "headache_history")
#
## exercise_time
#exercise_time_plot <- uni_plot(top_unij_input_plots$"exercise_time", "Exercise Score", ylims = c(0, 1.1))
#exercise_time_plot
#qs2(exercise_time_plot, "exercise_time")
#
## considerate_y
#considerate_y_plot <- uni_plot(top_unij_input_plots$"considerate_y", "Considerate\n(Youth Report)", c("No", "Yes"))
#considerate_y_plot
#qs2(considerate_y_plot, "considerate_y")
#
## family_temper_p
#family_temper_p_plot <- uni_plot(top_unij_input_plots$"family_temper_p", "Family Temper\n(Parent Report)", scale_fill_labels = c("No", "Yes"))
#family_temper_p_plot
#qs2(family_temper_p_plot, "family_temper_p")
#
## family_outdo_p
#family_outdo_p_plot <- uni_plot(top_unij_input_plots$"family_outdo_p", "Family Outdo\n(Parent Report)", c("No", "Yes"))
#family_outdo_p_plot
#qs2(family_outdo_p_plot, "family_outdo_p")
#
## cortical_thickness
#cortical_thickness_plot <- uni_plot(top_unij_input_plots$"cortical_thickness", "Cortical Thickness (mm)", ylims = c(2.3, 3.1))
#cortical_thickness_plot
#qs2(cortical_thickness_plot, "cortical_thickness")
#
## helps_hurt_p
#helps_hurt_p_plot <- uni_plot(top_unij_input_plots$"helps_hurt_p", "Helps Hurt\n(Parent Report)", c("No", "Yes"))
#helps_hurt_p_plot
#qs2(helps_hurt_p_plot, "helps_hurt_p")
#
## family_peaceful_p
#family_peaceful_p_plot <- uni_plot(top_unij_input_plots$"family_peaceful_p", "Family Peaceful\n(Parent Report)", c("No", "Yes"))
#family_peaceful_p_plot
#qs2(family_peaceful_p_plot, "family_peaceful_p")
#
## family_hit_p
#family_hit_p_plot <- uni_plot(top_unij_input_plots$"family_hit_p", "Family Hitting\n(Parent Report)", c("No", "Yes"))
#family_hit_p_plot
#qs2(family_hit_p_plot, "family_hit_p")
#
## family_angry_p
#family_angry_p_plot <- uni_plot(top_unij_input_plots$"family_angry_p", "Family Angry\n(Parent Report)", c("No", "Yes"))
#family_angry_p_plot
#qs2(family_angry_p_plot, "family_angry_p")
#
## family_yell_y
#family_yell_y_plot <- uni_plot(top_unij_input_plots$"family_yell_y", "Family Yells\n(Youth Report)", c("No", "Yes"))
#family_yell_y_plot
#qs2(family_yell_y_plot, "family_yell_y")
#
## pubertal_status_y
#pubertal_status_y_plot <- uni_plot(top_unij_input_plots$"pubertal_status_y", "Pubertal Status (Youth Report)")
#pubertal_status_y_plot
#qs2(pubertal_status_y_plot, "pubertal_status_y")
#
## helps_hurt_y
#helps_hurt_y_plot <- uni_plot(top_unij_input_plots$"helps_hurt_y", "Helps Hurt\n(Youth Report)", c("No", "Yes"))
#helps_hurt_y_plot
#qs2(helps_hurt_y_plot, "helps_hurt_y")
#
## family_throw_p
#family_throw_p_plot <- uni_plot(top_unij_input_plots$"family_throw_p", "Family Throwing\n(Parent Report)", c("No", "Yes"))
#family_throw_p_plot
#qs2(family_throw_p_plot, "family_throw_p")
#
#
#cbcl_anxdep_plot <- uni_plot(top_unij_outcome_plots$"cbcl_anxdep", "Anxious-Depressed", ylims = c(-0.5, 30))
#cbcl_withdep_plot <- uni_plot(top_unij_outcome_plots$"cbcl_withdep", "Withdrawn-Depressed", ylims = c(-0.5, 15))
#cbcl_somatic_plot <- uni_plot(top_unij_outcome_plots$"cbcl_somatic", "Somatic Problems", ylims = c(-0.5, 17))
#cbcl_social_plot <- uni_plot(top_unij_outcome_plots$"cbcl_social", "Social Problems", ylims = c(-0.5, 20))
#cbcl_thought_plot <- uni_plot(top_unij_outcome_plots$"cbcl_thought", "Thought Problems", ylims = c(-0.5, 20))
#cbcl_attention_plot <- uni_plot(top_unij_outcome_plots$"cbcl_attention", "Attention Problems", ylims = c(-0.5, 22))
#cbcl_rulebreak_plot <- uni_plot(top_unij_outcome_plots$"cbcl_rulebreak", "Rule-Breaking Problems", ylims = c(-0.5, 22))
#cbcl_aggressive_plot <- uni_plot(top_unij_outcome_plots$"cbcl_aggressive", "Aggression Problems", ylims = c(-0.5, 32))
#sds_sleep_plot <- uni_plot(top_unij_outcome_plots$"sds_sleep", "Total Sleep Problems", ylims = c(20, 100))
#
#matched_gen_in_plots <- list(
#    "brain_volume" = brain_volume_plot,
#    "sex" = sex_plot,
#    "cort_sa" = cort_sa_plot,
#    "household_income" = household_income_plot,
#    "pubertal_status_p" = pubertal_status_p_plot,
#    "programs_this_year" = programs_this_year_plot,
#    "non_school_programs" = non_school_programs_plot,
#    "parent_thought" = parent_thought_plot,
#    "parent_somatic" = parent_somatic_plot,
#    "weekday_screentime" = weekday_screentime_plot,
#    "parent_antisocial" = parent_antisocial_plot,
#    "parent_aggressive" = parent_aggressive_plot,
#    "parent_depress" = parent_depress_plot,
#    "parent_anxdep" = parent_anxdep_plot,
#    "race" = race_plot,
#    "parent_anxdisord" = parent_anxdisord_plot,
#    "private_instruction" = private_instruction_plot,
#    "weekend_screentime" = weekend_screentime_plot,
#    "parent_withdrawn" = parent_withdrawn_plot,
#    "parent_avoidant" = parent_avoidant_plot,
#    "parent_hyperactive" = parent_hyperactive_plot,
#    "fmri_cort_subcort_cors" = fmri_cort_subcort_cors_plot,
#    "parent_attention" = parent_attention_plot,
#    "parent_perstr" = parent_perstr_plot,
#    "parent_intrusive" = parent_intrusive_plot,
#    "family_fight_p" = family_fight_p_plot,
#    "headache_history" = headache_history_plot,
#    "exercise_time" = exercise_time_plot,
#    "considerate_y" = considerate_y_plot,
#    "family_temper_p" = family_temper_p_plot,
#    "family_outdo_p" = family_outdo_p_plot,
#    "cortical_thickness" = cortical_thickness_plot,
#    "helps_hurt_p" = helps_hurt_p_plot,
#    "family_peaceful_p" = family_peaceful_p_plot,
#    "family_hit_p" = family_hit_p_plot,
#    "family_angry_p" = family_angry_p_plot,
#    "family_yell_y" = family_yell_y_plot,
#    "pubertal_status_y" = pubertal_status_y_plot,
#    "helps_hurt_y" = helps_hurt_y_plot,
#    "family_throw_p" = family_throw_p_plot
#)
#
#matched_gen_out_plots <- list(
#    "cbcl_anxdep" = cbcl_anxdep_plot,
#    "cbcl_withdep" = cbcl_withdep_plot,
#    "cbcl_somatic" = cbcl_somatic_plot,
#    "cbcl_social" = cbcl_social_plot,
#    "cbcl_thought" = cbcl_thought_plot,
#    "cbcl_attention" = cbcl_attention_plot,
#    "cbcl_rulebreak" = cbcl_rulebreak_plot,
#    "cbcl_aggressive" = cbcl_aggressive_plot,
#    "sds_sleep" = sds_sleep_plot
#)
#
#list.save(matched_gen_in_plots, proc_path("matched_gen_in_plots.rds", TRUE))
#list.save(matched_gen_out_plots, proc_path("matched_gen_out_plots.rds", TRUE))
```

```{r}
#matched_gen_in_plots <- list.load(proc_path("2024_11_28_matched_gen_in_plots.rds"))
#matched_gen_out_plots <- list.load(proc_path("2024_11_28_matched_gen_out_plots.rds"))
```

## How does the classifier do?

Can always check this later

```{r}
#subtype_classifier <- readRDS(model_path("2024_11_28_subtype_classifier.rds"))
#
## Just FYI
#prep_data <- function(df, standardize = FALSE) {
#    df <- dplyr::select(df, -"subjectkey")
#    df <- dummy_cols(
#        df,
#        select_columns = "race",
#        remove_selected_columns = TRUE,
#        remove_most_frequent_dummy = TRUE
#    )
#    ordered_factors <- c(
#        "sex",
#        "household_income",
#        "pubertal_status_p",
#        "family_fight_p",
#        "family_outdo_p",
#        "helps_hurt_p",
#        "helpful_y",
#        "considerate_y",
#        "helps_hurt_y",
#        "family_criticize_p",
#        "family_outdo_y",
#        "family_angry_p",
#        "helpful_p",
#        "family_throw_p",
#        "family_hit_p",
#        "family_peaceful_y",
#        "family_throw_y",
#        "race_black",
#        "race_hispanic",
#        "race_other" 
#    )
#    df[ordered_factors] <- lapply(df[ordered_factors], as.ordered)
#    if (standardize) {
#        df[] <- lapply(df, as.numeric)
#        df <- as.data.frame(scale(df))
#    }
#    if ("cluster" %in% colnames(df)) {
#        df$"cluster" <- as.factor(df$"cluster")
#    }
#    return(df)
#}
#
##mini_df <- unij_matching_df_s1[1:200, ]
#
#library(randomForest)
#library(fastDummies)
#
#unij_pred_df_s1 <- unij_matching_df_s1 |> 
#    dplyr::mutate(
#        cluster = predict(
#            subtype_classifier,
#            newdata = prep_data(unij_matching_df_s1)
#        )
#    )
#
#unij_pred_df_s1$cluster |> table() |> prop.table()
#
#unij_pred_cluster_df <- unij_pred_df_s1 |> dplyr::select(subjectkey, cluster)
#
#unij_pred_plot_list <- auto_plot(
#    cluster_df = unij_pred_cluster_df,
#    data_list = unij_dl_s1,
#    target_list = unij_ol_s1 
#)
#
#unij_pred_plot_list[for_unij]
#
#unij_pred_all_plots <- wrap_plots(unij_pred_plot_list[for_unij])
#
#ggsave(
#    fig_path("unij_pred_all_plots.png", TRUE),
#    unij_pred_all_plots,
#    width = 45,
#    height = 30,
#    dpi = 50
#)
#
#unij_pred_cluster_df$"cluster" |> table() |> prop.table()
#
#get_cluster_df(mtbi_full_top_3c)$"cluster" |> table() |> prop.table()
#
#rbind(
#    unij_pred_cluster_df$"cluster" |> table(),
#    get_cluster_df(mtbi_full_top_3c)$"cluster" |> table()
#) |> chisq.test()
```

## 1. Examining correlation structure between mTBI and matched uninjured

Are the correlations stronger in the mTBI group?

```{r}
mtbi_ful_df <- as.data.frame(readRDS(proc_path("2025_02_13_mtbi_ful_df.rds")))

d_s_df <- as.data.frame(c(matched_unij_dl_d_s, matched_unij_ol_d_s))
p_s_df <- as.data.frame(c(matched_unij_dl_p_s, matched_unij_ol_p_s))
o_s_df <- as.data.frame(c(matched_unij_dl_o_s, matched_unij_ol_o_s))
d_p_df <- as.data.frame(c(matched_unij_dl_d_p, matched_unij_ol_d_p))
p_p_df <- as.data.frame(c(matched_unij_dl_p_p, matched_unij_ol_p_p))
o_p_df <- as.data.frame(c(matched_unij_dl_o_p, matched_unij_ol_o_p))
dp_s_df <- as.data.frame(c(matched_unij_dl_dp_s, matched_unij_ol_dp_s))
do_s_df <- as.data.frame(c(matched_unij_dl_do_s, matched_unij_ol_do_s))
op_s_df <- as.data.frame(c(matched_unij_dl_op_s, matched_unij_ol_op_s))
dp_p_df <- as.data.frame(c(matched_unij_dl_dp_p, matched_unij_ol_dp_p))
do_p_df <- as.data.frame(c(matched_unij_dl_do_p, matched_unij_ol_do_p))
op_p_df <- as.data.frame(c(matched_unij_dl_op_p, matched_unij_ol_op_p))
dpo_p_df <- as.data.frame(c(matched_unij_dl_dpo_p, matched_unij_ol_dpo_p))
dpo_s_df <- as.data.frame(c(matched_unij_dl_dpo_s, matched_unij_ol_dpo_s))
random_s1_df <- as.data.frame(c(random_unij_dl_s1, random_unij_ol_s1))
random_p1_df <- as.data.frame(c(random_unij_dl_p1, random_unij_ol_p1))

matched_unij_dfs <- list(
    "d_s_df" = d_s_df,
    "p_s_df" = p_s_df,
    "o_s_df" = o_s_df,
    "d_p_df" = d_p_df,
    "p_p_df" = p_p_df,
    "o_p_df" = o_p_df,
    "dp_s_df" = dp_s_df,
    "do_s_df" = do_s_df,
    "op_s_df" = op_s_df,
    "dp_p_df" = dp_p_df,
    "do_p_df" = do_p_df,
    "op_p_df" = op_p_df,
    "dpo_p_df" = dpo_p_df,
    "dpo_s_df" = dpo_s_df,
    "random_s1_df" = random_s1_df,
    "random_p1_df" = random_p1_df
)

# No duplicate data frames
matched_unij_dfs2 <- matched_unij_dfs[!duplicated(matched_unij_dfs)]
names(matched_unij_dfs2)
```

```{r}
saveRDS(matched_unij_dfs2, proc_path("matched_unij_dfs2.rds", TRUE))

matched_unij_dfs2 <- readRDS(proc_path("2025_03_25_matched_unij_dfs2.rds"))


# Data frame that only has the uninjured columns
mtbi_compare_df <- mtbi_ful_df[, colnames(d_s_df)]

mean_cor <- function(mat) {
    mat[upper.tri(mat)] |>
        abs() |>
        mean()
}

perm_test <- function(df1, df2, n = 10) {
    mean_cor_diff <- mean_cor(cor(df1)) - mean_cor(cor(df2))
    stacked_df <- rbind(df1, df2)
    diffs <- numeric(n)
    for (i in 1:n) {
        random_df <- stacked_df[sample.int(nrow(stacked_df)), ]
        mean_cor_1 <- mean_cor(cor_fn(random_df[1:437, ]))
        mean_cor_2 <- mean_cor(cor_fn(random_df[438:874, ]))
        diffs[i] <- mean_cor_1 - mean_cor_2
    }
    return(list(
        "observed_diff" = mean_cor_diff,
        "simulated_diffs" = diffs,
        "p_value" = sum(diffs > mean_cor_diff) / n
    ))
}

library(Rcpp)

sourceCpp("abcd/perm_test.cpp")

prep_and_test <- function(df1, df2, n = 10) {
    df1 <- df1 |>
        dplyr::select(-"uid") |>
        dummy_cols(
            select_columns = "race",
            remove_selected_columns = TRUE,
            remove_most_frequent_dummy = TRUE
        ) |>
        as.matrix()
    df2 <- df2 |>
        dplyr::select(-"uid") |>
        dummy_cols(
            select_columns = "race",
            remove_selected_columns = TRUE,
            remove_most_frequent_dummy = TRUE
        ) |>
        as.matrix()
    results <- perm_test_cpp(df1, df2, n = n)
    return(results)
}

matched_unij_dfs2 |> length();

set.seed(42)
matched_perm_test_df <- data.frame()
for (i in seq_along(matched_unij_dfs2)) {
    cat("DF: ", i, "\n")
    p_value <- prep_and_test(
        mtbi_compare_df,
        matched_unij_dfs2[[i]],
        n = 10000
    )$"p_value"
    matched_perm_test_df <- rbind(
        matched_perm_test_df,
        data.frame(
            "match" = names(matched_unij_dfs2)[[i]],
            "p" = p_value
        )
    )
}
write_csv(matched_perm_test_df, proc_path("matched_perm_test_df.csv", TRUE))

matched_perm_test_df <- read_csv(
    proc_path("2025_03_25_matched_perm_test_df.csv")
)

matched_perm_test_df |> arrange(p)

## A tibble: 12 × 2
#   match             p
#   <chr>         <dbl>
# 1 d_s_df       0
# 2 d_p_df       0
# 3 random_s1_df 0
# 4 random_p1_df 0
# 5 p_s_df       0.0022
# 6 p_p_df       0.0037
# 7 do_s_df      0.0407
# 8 do_p_df      0.0618
# 9 dp_s_df      0.0655
#10 dp_p_df      0.120
#11 o_s_df       0.176
#12 o_p_df       0.217
```

## 2. Compare correlations between mTBI C1 and C2

What correlations, if any, are significantly different?
