# Longitudinal analyses

This chapter addresses the following four questions:

1. Was the baseline clustering informative for long-term outcomes?

2. Did the matched uninjured subjects experience more mTBIs by T2 than the other uninjured subjects?

3. Clustering of the longitudinal sample with their baseline vs. their longitudinal data: both equally informative?

4. Classifier built from baseline mTBI data: informative?

## Package loading

```{r}
library(abcdutils)
library(here)
library(dplyr)
library(readr)
library(metasnf)
library(rlist)
library(visdat)
library(ggplot2)
library(mice)
library(fastDummies)
library(randomForest)
library(patchwork)
library(tidyr)
library(ComplexHeatmap)
```

## Establishing file paths

```{r}
input_path <- path_maker(here(paste0("data/abcd/inputs")))
core_path <- path_maker(here(paste0("data/abcd/core")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
model_path <- path_maker(here(paste0("data/abcd/results/models")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))

read <- function(path) {
    return(read_csv(input_path(path)))
}
```

### Q2. Did the matched uninjured subjects experience more mTBIs by T2 than the other uninjured subjects?

```{r}
matched_unij_nearest_esdf <- readRDS(proc_path("2025_02_16_matched_unij_nearest_esdf.rds"))

# Those who exhibited heterogeneity most similar to the baseline mTBI group
matched_subs <- uids(matched_unij_nearest_esdf)
matched_subs <- gsub("uid_", "", matched_subs)

# Those who never sustained a head injury prior to T2
# N = 7678
long_unij_subs <- read_subjects(sub_path("2025_02_07_unij_subs_0_to_2.csv"))

# Those who sustained a head injury between 0 and T2
# N = 220
long_mtbi_subs <- read_subjects(sub_path("2025_02_07_mtbi_subs_0_to_2.csv"))

# The pool of all baseline uninjured subjects
# N = 9349
base_unij_subs <- read_subjects(sub_path("2025_02_07_unij_subs.csv"))

non_matched_subs <- setdiff(base_unij_subs, matched_subs)

base_mtbi_subs <- read_subjects(sub_path("2025_02_07_mtbi_subs.csv"))
```

Let's consider being in the matched group vs. not being in the matched group as exposed vs. unexposed, and ending up in the mTBI sample as outcome vs. no outcome.
Then I calculate the odds ratio and 95% CI of being in the mTBI sample based on being in the matched group.

```{r}
# Calculation 1: Explicitly looking for people that ended up in mTBI sample
matched_that_became_mtbi <- sum(matched_subs %in% long_mtbi_subs)
unmatched_that_became_mtbi <- sum(non_matched_subs %in% long_mtbi_subs)
matched_that_remained_unij <- sum(!matched_subs %in% long_mtbi_subs)
unmatched_that_remained_unij <- sum(!non_matched_subs %in% long_mtbi_subs)

odds_ratio <- function(de, he, dn, hn) {
    numerator <- de / he
    denominator <- dn / hn
    or <- numerator / denominator
    se_log_or <- sqrt(1/de + 1/he + 1/dn + 1/hn)
    log_or <- log(or)
    ci_lower <- exp(log_or - 1.96 * se_log_or)
    ci_upper <- exp(log_or + 1.96 * se_log_or)
    return(list(
        or = or,
        ci_lower = ci_lower,
        ci_upper = ci_upper
    ))
}

# (D)isease = mTBI, (H)ealthy = unij , (E)xposure = match
# 0.83 [0.36, 1.89]
odds_ratio(
    de = matched_that_became_mtbi,
    he = matched_that_remained_unij,
    dn = unmatched_that_became_mtbi,
    hn = unmatched_that_remained_unij
)
```

No significant difference in the proportion of matched uninjured subjects to unmatched uninjured subjects that ended up in the longitudinal mTBI group (1.3% vs. 1.6%, uncorrected Chi-squared test p-value = 0.6565).

### Extra: Correlations with membership in longitudinal mTBI sample

Now I'll double check to see if there were any attributes of subjects that were particularly closely associated with membership in the longitudinal mTBI sample.

```{r}
long_mtbi_0_dl <- all_long_dls$"long_mtbi_0_dls"[[1]]

base_unij_0_dl <- all_dls$"unij_pooled_data_lists"[[1]]

long_unij_0_dl <- base_unij_0_dl |>
    dlapply(
        function(x) {
            x$"data" <- dplyr::filter(x$"data", uid %in% paste0("uid_", long_unij_subs))
            return(x)
        }
    )

long_unij_df <- as.data.frame(long_unij_0_dl)
long_mtbi_df <- as.data.frame(long_mtbi_0_dl)
base_unij_df <- as.data.frame(base_unij_0_dl)

long_unij_df$"mtbi" <- 0
long_mtbi_df$"mtbi" <- 1

long_corr_df <- rbind(long_unij_df, long_mtbi_df)

saveRDS(long_corr_df, proc_path("long_corr_df.rds", TRUE))

long_corr_df <- readRDS(proc_path("2025_05_01_long_corr_df.rds"))

# Correlation matrix examining how correlated each feature is with being assigned to mTBI group
prepped_long_corr_df <- long_corr_df |>
    dplyr::select(-uid) |>
    dummy_cols(
        select_columns = "race",
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = TRUE
    )

# Setup parallel plan
future::plan("multisession")
kendall_row <- function(i, data) {
  sapply(i:ncol(data), function(j) cor(data[[i]], data[[j]], method = "kendall"))
}
n <- ncol(prepped_long_corr_df)
kendall_mat <- matrix(NA, n, n)
colnames(kendall_mat) <- rownames(kendall_mat) <- colnames(prepped_long_corr_df)
results <- pbapply::pblapply(1:n, function(i) kendall_row(i, prepped_long_corr_df), cl = future::availableCores())
for (i in 1:n) {
  kendall_mat[i, i:n] <- results[[i]]
  kendall_mat[i:n, i] <- results[[i]]
}

saveRDS(kendall_mat, proc_path("long_corr_mat_kendall.rds", TRUE))

# Setup parallel plan
spearman_row <- function(i, data) {
    sapply(i:ncol(data), function(j) cor(data[[i]], data[[j]], method = "spearman"))
}
n <- ncol(prepped_long_corr_df)
spearman_mat <- matrix(NA, n, n)
colnames(spearman_mat) <- rownames(spearman_mat) <- colnames(prepped_long_corr_df)
results <- pbapply::pblapply(1:n, function(i) spearman_row(i, prepped_long_corr_df), cl = future::availableCores())
for (i in 1:n) {
  spearman_mat[i, i:n] <- results[[i]]
  spearman_mat[i:n, i] <- results[[i]]
}

saveRDS(spearman_mat, proc_path("long_corr_mat_spearman.rds", TRUE))

pearson_mat <- cor(prepped_long_corr_df, method = "pearson")

saveRDS(pearson_mat, proc_path("long_corr_mat_pearson.rds", TRUE))
```

```{r}
kendall_mat <- readRDS(proc_path("2025_05_01_long_corr_mat_kendall.rds"))
spearman_mat <- readRDS(proc_path("2025_05_01_long_corr_mat_spearman.rds"))
pearson_mat <- readRDS(proc_path("2025_05_01_long_corr_mat_pearson.rds"))

kendall_mat[setdiff(rownames(kendall_mat), "mtbi"), "mtbi"]
spearman_mat[setdiff(rownames(spearman_mat), "mtbi"), "mtbi"]
pearson_mat[setdiff(rownames(pearson_mat), "mtbi"), "mtbi"]

ComplexHeatmap::Heatmap(kendall_mat[setdiff(rownames(kendall_mat), "mtbi"), "mtbi"])

ComplexHeatmap::Heatmap(spearman_mat[setdiff(rownames(spearman_mat), "mtbi"), "mtbi"])

ComplexHeatmap::Heatmap(pearson_mat[setdiff(rownames(pearson_mat), "mtbi"), "mtbi"])

kendall_mat[names(sort(-abs(kendall_mat[setdiff(rownames(kendall_mat), "mtbi"), "mtbi"]))), "mtbi"] |> ComplexHeatmap::Heatmap(cluster_rows = FALSE)


spearman_mat[names(sort(-abs(spearman_mat[setdiff(rownames(spearman_mat), "mtbi"), "mtbi"]))), "mtbi"] |> ComplexHeatmap::Heatmap(cluster_rows = FALSE)

pearson_mat[names(sort(-abs(pearson_mat[setdiff(rownames(pearson_mat), "mtbi"), "mtbi"]))), "mtbi"] |> ComplexHeatmap::Heatmap(cluster_rows = FALSE)

ComplexHeatmap::Heatmap(z3)

z3 <- long_corr_df |>
    dplyr::select(-uid) |>
    dummy_cols(
        select_columns = "race",
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = TRUE
    ) |>
    cor(method = "kendll")

# Only looking at correlations
mtbi_corr_mat <- long_corr_mat[rownames(long_corr_mat) != "mtbi", "mtbi", drop = FALSE]

mtbi_corr_mat |>
    ComplexHeatmap::Heatmap()

mtbi_corr_mat |>
    as.data.frame() |>
    dplyr::arrange(mtbi)

long_corr_df |>
    ggplot(aes(x = factor(mtbi), y = major_wm_ndi)) +
    geom_jitter() +
    theme_bw()


long_corr_clean_df <- long_corr_df |>
    dplyr::select(-uid) |>
    dummy_cols(
        select_columns = "race",
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = TRUE
    )

pvalue_df <- data.frame()
for (col in colnames(long_corr_clean_df)) {
    test_results <- cor.test(long_corr_clean_df$"mtbi", long_corr_clean_df[[col]])
    pval <- test_results$"p.value"
    est <- test_results$"estimate"
    l <- test_results$"conf.int"[1]
    u <- test_results$"conf.int"[2]
    pvalue_df <- rbind(
        pvalue_df,
        data.frame(
            feature = col,
            pval = pval,
            est = est,
            l = l,
            u = u
        )
    )
}
rownames(pvalue_df) <- NULL
p_values_bonferroni <- p.adjust(pvalue_df$"pval", method = "bonferroni")
p_values_fdr <- p.adjust(pvalue_df$"pval", method = "fdr")
pvalue_df$"pval_bon" <- p_values_bonferroni
pvalue_df$"pval_fdr" <- p_values_fdr
pvalue_df <- pvalue_df |>
    dplyr::arrange(pval) |>
    dplyr::filter(feature != "mtbi") |>
    dplyr::select(feature, pval, pval_bon, pval_fdr, est, l, u)

write_csv(pvalue_df, proc_path("pvalue_df.csv", TRUE))
pvalue_df <- read_csv(proc_path("2025_02_16_pvalue_df.csv"))
```

Quite a few features there that remain significant even after bonferroni correction.
There certainly seem to be factors that increase a child's risk of sustaining an mTBI.
These are all taken from the same data collection period as well!



## Q1: Was the baseline clustering informative for LT outcomes?

```{r}
# Import data
mtbi_base_df <- readRDS(proc_path("2025_02_13_mtbi_ful_df.rds"))
all_long_dls <- readRDS(input_path("2025_03_10_all_long_dls.rds"))
all_dls <- readRDS(input_path("2025_02_10_all_dls.rds"))
```

```{r}
base_mtbi_l_ols <- all_long_dls$"base_mtbi_l_ols"
base_mtbi_l_dls <- all_long_dls$"base_mtbi_l_dls"

# Convert list of data lists into list of data frames for plotting
base_mtbi_l_ol_dfs <- lapply(base_mtbi_l_ols, as.data.frame)
base_mtbi_l_dl_dfs <- lapply(base_mtbi_l_dls, as.data.frame)

# Tag each data frame with its originating imputation
base_mtbi_l_ol_dfs <- lapply(
    1:5,
    function(x) {
        base_mtbi_l_ol_dfs[[x]]$"imputation" <- x
        base_mtbi_l_ol_dfs[[x]]
    }
)

base_mtbi_l_dl_dfs <- lapply(
    1:5,
    function(x) {
        base_mtbi_l_dl_dfs[[x]]$"imputation" <- x
        base_mtbi_l_dl_dfs[[x]]
    }
)

# Horizontally merge list of data frames
base_mtbi_l_ol_df <- do.call(rbind, base_mtbi_l_ol_dfs)
base_mtbi_l_dl_df <- do.call(rbind, base_mtbi_l_dl_dfs)

mtbi_base_df2 <- mtbi_base_df |>
    dplyr::select(uid, cluster, dplyr::everything())
# Keep track of baseline data before attaching to longitudinal data
colnames(mtbi_base_df2) <- paste0(colnames(mtbi_base_df2), "_0")
mtbi_base_df2 <- mtbi_base_df2 |>
    dplyr::rename(
        "uid" = "uid_0",
        "cluster" = "cluster_0",
        "sex" = "sex_0",
        "race" = "race_0"
    )

base_mtbi_l_df <- dplyr::full_join(
    base_mtbi_l_ol_df,
    base_mtbi_l_dl_df,
    by = c("uid", "imputation")
)
colnames(base_mtbi_l_df) <- paste0(colnames(base_mtbi_l_df), "_l")
base_mtbi_l_df <- base_mtbi_l_df |>
    dplyr::rename(
        "uid" = "uid_l",
        "imputation" = "imputation_l"
    )
mtbi_long_changes <- dplyr::full_join(
    mtbi_base_df2,
    base_mtbi_l_df,
    by = "uid"
)

original_names <- gsub("_0", "", colnames(mtbi_base_df2)[-c(1:2)])

original_names <- original_names[!grepl("mtbi", original_names)]

replace_names <- original_names[!grepl("race", original_names)]

replace_names <- replace_names[!grepl("sex", replace_names)]

mtbi_long_changes |> colnames()

for (name in replace_names) {
    print(name)
    long_val <- mtbi_long_changes[[paste0(name, "_l")]]
    base_val <- mtbi_long_changes[[paste0(name, "_0")]]
    mtbi_long_changes[[paste0(name, "_d")]] <- long_val - base_val
}
mtbi_long_changes$"cluster" <- as.factor(mtbi_long_changes$"cluster")

saveRDS(mtbi_long_changes, proc_path("mtbi_long_changes.rds", TRUE))
mtbi_long_changes <- readRDS(proc_path("2025_03_25_mtbi_long_changes.rds"))
```

```{r}
# Some plotting functions
gg_long_cor_imp <- function(df, feature, long = TRUE) {
    f1 <- paste0(feature, "_0")
    if (long) {
        f2 <- paste0(feature, "_l")
    } else {
        f2 <- paste0(feature, "_d")
    }
    plot <- ggplot(
        df,
        aes(x = .data[[f1]], y = .data[[f2]])
    ) +
        geom_jitter(alpha = 0.2) +
        facet_wrap(~ imputation) +
        theme_bw()
    return(plot)
}

gg_long_cor <- function(df, feature, long = TRUE) {
    df <- dplyr::filter(df, imputation == 1)
    f1 <- paste0(feature, "_0")
    if (long) {
        f2 <- paste0(feature, "_l")
    } else {
        f2 <- paste0(feature, "_d")
    }
    plot <- ggplot(
        df,
        aes(
            x = .data[[f1]],
            y = .data[[f2]],
            colour = as.factor(cluster)
        )
    ) +
        geom_jitter(alpha = 0.5, height = 0.1, width = 0.1) +
        geom_smooth(method = "lm") +
        theme_bw() +
        labs(colour = "C")
    return(plot)
}


pubertal_status_y_plot <- gg_long_cor(mtbi_long_changes, "pubertal_status_y")
household_income_plot <- gg_long_cor(mtbi_long_changes, "household_income")
extracurriculars_plot <- gg_long_cor(mtbi_long_changes, "extracurriculars")
parent_perstr_plot <- gg_long_cor(mtbi_long_changes, "parent_perstr")
activities_last_year_plot <- gg_long_cor(mtbi_long_changes, "activities_last_year")
considerate_y_plot <- gg_long_cor(mtbi_long_changes, "considerate_y")
# looks kind of like an interaction?
school_activities_plot <- gg_long_cor(mtbi_long_changes, "school_activities")
weekend_screentime_plot <- gg_long_cor(mtbi_long_changes, "weekend_screentime")
family_throw_y_plot <- gg_long_cor(mtbi_long_changes, "family_throw_y")

significant_long_cor_plot <- pubertal_status_y_plot +
household_income_plot +
extracurriculars_plot +
parent_perstr_plot +
activities_last_year_plot +
considerate_y_plot +
school_activities_plot +
weekend_screentime_plot +
family_throw_y_plot

ggsave(
    fig_path("significant_long_cor_plot.png", TRUE),
    significant_long_cor_plot,
    width = 15,
    height = 10
)

cbcl_anxdep_plot <- gg_long_cor(mtbi_long_changes, "cbcl_anxdep", 0)
cbcl_withdep_plot <- gg_long_cor(mtbi_long_changes, "cbcl_withdep", 0)
cbcl_somatic_plot <- gg_long_cor(mtbi_long_changes, "cbcl_somatic", 0)
cbcl_social_plot <- gg_long_cor(mtbi_long_changes, "cbcl_social", 0)
cbcl_thought_plot <- gg_long_cor(mtbi_long_changes, "cbcl_thought", 0)
cbcl_attention_plot <- gg_long_cor(mtbi_long_changes, "cbcl_attention", 0)
cbcl_rulebreak_plot <- gg_long_cor(mtbi_long_changes, "cbcl_rulebreak", 0)
cbcl_aggressive_plot <- gg_long_cor(mtbi_long_changes, "cbcl_aggressive", 0)
sds_sleep_plot <- gg_long_cor(mtbi_long_changes, "sds_sleep", 0)

outcome_long_cor_plot <- cbcl_anxdep_plot +
cbcl_withdep_plot +
cbcl_somatic_plot +
cbcl_social_plot +
cbcl_thought_plot +
cbcl_attention_plot +
cbcl_rulebreak_plot +
cbcl_aggressive_plot +
sds_sleep_plot

ggsave(
    fig_path("outcome_long_cor_plot.png", TRUE),
    outcome_long_cor_plot,
    width = 15,
    height = 10
)

cbcl_anxdep_plot2 <- gg_long_cor(mtbi_long_changes, "cbcl_anxdep")
cbcl_withdep_plot2 <- gg_long_cor(mtbi_long_changes, "cbcl_withdep")
cbcl_somatic_plot2 <- gg_long_cor(mtbi_long_changes, "cbcl_somatic")
cbcl_social_plot2 <- gg_long_cor(mtbi_long_changes, "cbcl_social")
cbcl_thought_plot2 <- gg_long_cor(mtbi_long_changes, "cbcl_thought")
cbcl_attention_plot2 <- gg_long_cor(mtbi_long_changes, "cbcl_attention")
cbcl_rulebreak_plot2 <- gg_long_cor(mtbi_long_changes, "cbcl_rulebreak")
cbcl_aggressive_plot2 <- gg_long_cor(mtbi_long_changes, "cbcl_aggressive")
sds_sleep_plot2 <- gg_long_cor(mtbi_long_changes, "sds_sleep")

outcome_long_cor_plot2 <- cbcl_anxdep_plot2 +
cbcl_withdep_plot2 +
cbcl_somatic_plot2 +
cbcl_social_plot2 +
cbcl_thought_plot2 +
cbcl_attention_plot2 +
cbcl_rulebreak_plot2 +
cbcl_aggressive_plot2 +
sds_sleep_plot2

ggsave(
    fig_path("outcome_long_cor_plot2.png", TRUE),
    outcome_long_cor_plot2,
    width = 15,
    height = 10
)


gg_long_cor(mtbi_long_changes, "cbcl_anxdep", 0)

gg_long_cor(mtbi_long_changes, "cbcl_withdep")

gg_long_cor(mtbi_long_changes, "cbcl_somatic")

gg_long_cor(mtbi_long_changes, "cbcl_anxdep")

gg_long_cor(mtbi_long_changes, "cbcl_withdep")

gg_long_cor(mtbi_long_changes, "cbcl_somatic")

gg_long_cor(mtbi_long_changes, "cbcl_social")

gg_long_cor(mtbi_long_changes, "cbcl_thought")

gg_long_cor(mtbi_long_changes, "cbcl_attention")

gg_long_cor(mtbi_long_changes, "cbcl_rulebreak")

gg_long_cor(mtbi_long_changes, "cbcl_aggressive")

gg_long_cor(mtbi_long_changes, "sds_sleep")

gg_long_cor(mtbi_long_changes, "cbcl_withdep", 0)

gg_long_cor(mtbi_long_changes, "cbcl_somatic", 0)

gg_long_cor(mtbi_long_changes, "cbcl_anxdep", 0)

gg_long_cor(mtbi_long_changes, "cbcl_withdep", 0)

gg_long_cor(mtbi_long_changes, "cbcl_somatic", 0)

gg_long_cor(mtbi_long_changes, "cbcl_social", 0)

gg_long_cor(mtbi_long_changes, "cbcl_thought", 0)

gg_long_cor(mtbi_long_changes, "cbcl_attention", 0)

gg_long_cor(mtbi_long_changes, "cbcl_rulebreak", 0)

gg_long_cor(mtbi_long_changes, "cbcl_aggressive", 0)

gg_long_cor(mtbi_long_changes, "sds_sleep", 0)

gg_long_cor(mtbi_long_changes, "parent_perstr", 0)

gg_long_cor(mtbi_long_changes, "activities_last_year")

gg_long_cor(mtbi_long_changes, "pubertal_status_y")

gg_long_cor(mtbi_long_changes, "pubertal_status_p")

gg_long_cor(mtbi_long_changes, "school_activities")

gg_long_cor(mtbi_long_changes, "weekend_screentime")

gg_long_cor(mtbi_long_changes, "household_income")

cor_mat <- mtbi_long_changes |>
    dplyr::select(-uid, -mtbi_mechanism_0, -race_l) |>
    dplyr::rename("race" = "race_0") |>
    dplyr::mutate(cluster = as.numeric(cluster)) |>
    dummy_cols(
        select_columns = "race",
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = TRUE
    ) |>
    cor()

cor_mat[!grepl("_d$|_l$", colnames(cor_mat)), grepl("_d$", colnames(cor_mat))] |>
    Heatmap()

cor_mat["cluster", grepl("_d$", colnames(cor_mat))] |>
    Heatmap()

lm_long_fit <- function(df, feature) {
    models <- list(
      lm(as.formula(paste0(feature, "_l ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 1)),
      lm(as.formula(paste0(feature, "_l ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 2)),
      lm(as.formula(paste0(feature, "_l ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 3)),
      lm(as.formula(paste0(feature, "_l ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 4)),
      lm(as.formula(paste0(feature, "_l ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 5))
    )
    pooled_results <- pool(as.mira(models))
    return(summary(pooled_results))
}

replace_names

pval_df <- data.frame()
for (feature in replace_names) {
    model <- lm_long_fit(mtbi_long_changes, feature)
    pval_df <- rbind(
        pval_df,
        data.frame(
            feature = c(feature, feature),
            compare = c("c1_vs_c2", "c1_vs_c3"),
            p = c(model$"p.value"[3], model$"p.value"[4])
        )
    )
    if (min(model$"p.value"[3]) < 0.05) {
        cat("\n", feature, signif(model$"p.value"[3], 2), "\n")
        print(model)
    }
}
pval_df$"padj" <- p.adjust(pval_df$"p", method = "fdr")

pval_df |>
    dplyr::filter(padj < 0.05) |>
    dplyr::select(-p) |>
    dplyr::mutate(padj = format(padj, scientific = FALSE, digits = 2)) |>
    dplyr::arrange(padj)



gg_long_cor(mtbi_long_changes, "parent_perstr")

gg_long_cor(mtbi_long_changes, "pubertal_status_y", 0)

cor_mat

# None are significant
lm_long_fit(mtbi_long_changes, "cbcl_anxdep")

lm_long_fit(mtbi_long_changes, "cbcl_withdep")

lm_long_fit(mtbi_long_changes, "cbcl_somatic")

lm_long_fit(mtbi_long_changes, "cbcl_social")

lm_long_fit(mtbi_long_changes, "cbcl_thought")

lm_long_fit(mtbi_long_changes, "cbcl_attention")

lm_long_fit(mtbi_long_changes, "cbcl_rulebreak")

lm_long_fit(mtbi_long_changes, "cbcl_aggressive")

lm_long_fit(mtbi_long_changes, "sds_sleep")

colnames(mtbi_long_changes)

# Checking just in baseline now...
lm_short_fit <- function(df, ft1, ft2) {
    models <- list(
      lm(as.formula(paste0(feature, "_0 ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 1)),
      lm(as.formula(paste0(feature, "_0 ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 2)),
      lm(as.formula(paste0(feature, "_0 ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 3)),
      lm(as.formula(paste0(feature, "_0 ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 4)),
      lm(as.formula(paste0(feature, "_0 ~ ", feature, "_0 + factor(cluster)")), data = filter(df, imputation == 5))
    )
    pooled_results <- pool(as.mira(models))
    return(summary(pooled_results))
}
```

Cluster is never a significant feature in predicting longitudinal outcome given baseline outcome.

### Q3. Clustering of the longitudinal sample with their baseline vs. their longitudinal data: both equally informative?

Can perhaps skip this and just make use of the classifier.

```{r}
long_mtbi_0_dls <- all_long_dls$"long_mtbi_0_dls"
long_mtbi_0_ols <- all_long_dls$"long_mtbi_0_ols"

long_mtbi_l_dls <- all_long_dls$"long_mtbi_l_dls"
long_mtbi_l_ols <- all_long_dls$"long_mtbi_l_ols"
```


```{r}
long_config <- snf_config(
    long_mtbi_0_dls[[1]],
    n_solutions = 200,
    cnt_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    dsc_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ord_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    use_default_dist_fns = TRUE
)

saveRDS(long_config, proc_path("long_config.rds", TRUE))
```


```{r}
# CHECKPOINT
long_config <- readRDS(proc_path("2025_04_28_long_config.rds"))
```

```{r}
progressr::with_progress({long_mtbi_0_sol_df_s1 <- batch_snf(dl = long_mtbi_0_dls[[1]], sc = long_config, processes = "max")})
saveRDS(long_mtbi_0_sol_df_s1, proc_path("long_mtbi_0_sol_df_s1.rds", TRUE))
progressr::with_progress({long_mtbi_0_sol_df_s2 <- batch_snf(dl = long_mtbi_0_dls[[2]], sc = long_config, processes = "max")})
saveRDS(long_mtbi_0_sol_df_s2, proc_path("long_mtbi_0_sol_df_s2.rds", TRUE))
progressr::with_progress({long_mtbi_0_sol_df_s3 <- batch_snf(dl = long_mtbi_0_dls[[3]], sc = long_config, processes = "max")})
saveRDS(long_mtbi_0_sol_df_s3, proc_path("long_mtbi_0_sol_df_s3.rds", TRUE))
progressr::with_progress({long_mtbi_0_sol_df_s4 <- batch_snf(dl = long_mtbi_0_dls[[4]], sc = long_config, processes = "max")})
saveRDS(long_mtbi_0_sol_df_s4, proc_path("long_mtbi_0_sol_df_s4.rds", TRUE))
progressr::with_progress({long_mtbi_0_sol_df_s5 <- batch_snf(dl = long_mtbi_0_dls[[5]], sc = long_config, processes = "max")})
saveRDS(long_mtbi_0_sol_df_s5, proc_path("long_mtbi_0_sol_df_s5.rds", TRUE))
progressr::with_progress({long_mtbi_l_sol_df_s1 <- batch_snf(dl = long_mtbi_l_dls[[1]], sc = long_config, processes = "max")})
saveRDS(long_mtbi_l_sol_df_s1, proc_path("long_mtbi_l_sol_df_s1.rds", TRUE))
progressr::with_progress({long_mtbi_l_sol_df_s2 <- batch_snf(dl = long_mtbi_l_dls[[2]], sc = long_config, processes = "max")})
saveRDS(long_mtbi_l_sol_df_s2, proc_path("long_mtbi_l_sol_df_s2.rds", TRUE))
progressr::with_progress({long_mtbi_l_sol_df_s3 <- batch_snf(dl = long_mtbi_l_dls[[3]], sc = long_config, processes = "max")})
saveRDS(long_mtbi_l_sol_df_s3, proc_path("long_mtbi_l_sol_df_s3.rds", TRUE))
progressr::with_progress({long_mtbi_l_sol_df_s4 <- batch_snf(dl = long_mtbi_l_dls[[4]], sc = long_config, processes = "max")})
saveRDS(long_mtbi_l_sol_df_s4, proc_path("long_mtbi_l_sol_df_s4.rds", TRUE))
progressr::with_progress({long_mtbi_l_sol_df_s5 <- batch_snf(dl = long_mtbi_l_dls[[5]], sc = long_config, processes = "max")})
saveRDS(long_mtbi_l_sol_df_s5, proc_path("long_mtbi_l_sol_df_s5.rds", TRUE))
```

```{r}
long_mtbi_0_sol_df_s1 <- readRDS(proc_path("2025_04_28_long_mtbi_0_sol_df_s1.rds"))
long_mtbi_0_sol_df_s2 <- readRDS(proc_path("2025_04_28_long_mtbi_0_sol_df_s2.rds"))
long_mtbi_0_sol_df_s3 <- readRDS(proc_path("2025_04_28_long_mtbi_0_sol_df_s3.rds"))
long_mtbi_0_sol_df_s4 <- readRDS(proc_path("2025_04_28_long_mtbi_0_sol_df_s4.rds"))
long_mtbi_0_sol_df_s5 <- readRDS(proc_path("2025_04_28_long_mtbi_0_sol_df_s5.rds"))

long_mtbi_0_sol_df <- do.call(
    "rbind",
    c(
        list(
            long_mtbi_0_sol_df_s1,
            long_mtbi_0_sol_df_s2,
            long_mtbi_0_sol_df_s3,
            long_mtbi_0_sol_df_s4,
            long_mtbi_0_sol_df_s5
        ),
        list(reset_indices = TRUE)
    )
)
saveRDS(long_mtbi_0_sol_df, proc_path("long_mtbi_0_sol_df.rds", TRUE))
```

```{r}
long_mtbi_0_ari <- calc_aris(long_mtbi_0_sol_df, processes = "max")
saveRDS(long_mtbi_0_ari, proc_path("long_mtbi_0_ari.rds", TRUE))

long_mtbi_0_ari_order <- get_matrix_order(long_mtbi_0_ari)
write_csv(data.frame(long_mtbi_0_ari_order), proc_path("long_mtbi_0_ari_order.csv", TRUE))
```

```{r}
long_mtbi_l_sol_df_s1 <- readRDS(proc_path("2025_02_18_long_mtbi_l_sol_df_s1.rds"))
long_mtbi_l_sol_df_s2 <- readRDS(proc_path("2025_02_18_long_mtbi_l_sol_df_s2.rds"))
long_mtbi_l_sol_df_s3 <- readRDS(proc_path("2025_02_18_long_mtbi_l_sol_df_s3.rds"))
long_mtbi_l_sol_df_s4 <- readRDS(proc_path("2025_02_18_long_mtbi_l_sol_df_s4.rds"))
long_mtbi_l_sol_df_s5 <- readRDS(proc_path("2025_02_18_long_mtbi_l_sol_df_s5.rds"))

long_mtbi_l_sol_df <- do.call(
    "rbind",
    c(
        list(
            long_mtbi_l_sol_df_s1,
            long_mtbi_l_sol_df_s2,
            long_mtbi_l_sol_df_s3,
            long_mtbi_l_sol_df_s4,
            long_mtbi_l_sol_df_s5
        ),
        list(reset_indices = TRUE)
    )
)
saveRDS(long_mtbi_l_sol_df, proc_path("long_mtbi_l_sol_df.rds", TRUE))
long_mtbi_l_ari <- calc_aris(long_mtbi_l_sol_df, processes = "max")
saveRDS(long_mtbi_l_ari, proc_path("long_mtbi_l_ari.rds", TRUE))
long_mtbi_l_ari_order <- get_matrix_order(long_mtbi_l_ari)
write_csv(data.frame(long_mtbi_l_ari_order), proc_path("long_mtbi_l_ari_order.csv", TRUE))
# HERE I AM 2025_04_28
```

```{r}
# CHECKPOINT
long_mtbi_0_sol_df <- readRDS(proc_path("2025_04_28_long_mtbi_0_sol_df.rds"))
long_mtbi_0_ari <- readRDS(proc_path("2025_04_28_long_mtbi_0_ari.rds"))
long_mtbi_0_ari_order <- unlist(read_csv(proc_path("2025_04_28_long_mtbi_0_ari_order.csv")))
names(long_mtbi_0_ari_order) <- NULL

long_mtbi_l_sol_df <- readRDS(proc_path("2025_04_28_long_mtbi_l_sol_df.rds"))
long_mtbi_l_ari <- readRDS(proc_path("2025_04_28_long_mtbi_l_ari.rds"))
long_mtbi_l_ari_order <- unlist(read_csv(proc_path("2025_04_28_long_mtbi_l_ari_order.csv")))
names(long_mtbi_l_ari_order) <- NULL
```

```{r}
# Solo imputation 1
progressr::with_progress({
long_mtbi_0_ext_sol_df_s1 <- extend_solutions(
    long_mtbi_0_sol_df[1:200, ],
    dl = long_mtbi_0_dls[[1]],
    target_dl = long_mtbi_0_ols[[1]],
    min_pval = 1e-10,
    processes = "max"
)
})
saveRDS(long_mtbi_0_ext_sol_df_s1, proc_path("long_mtbi_0_ext_sol_df_s1.rds", TRUE))
# Solo imputation 2
progressr::with_progress({
long_mtbi_0_ext_sol_df_s2 <- extend_solutions(
    long_mtbi_0_sol_df[201:400, ],
    dl = long_mtbi_0_dls[[2]],
    target_dl = long_mtbi_0_ols[[2]],
    min_pval = 1e-10,
    processes = "max"
)
})
saveRDS(long_mtbi_0_ext_sol_df_s2, proc_path("long_mtbi_0_ext_sol_df_s2.rds", TRUE))
# Solo imputation 3
progressr::with_progress({
long_mtbi_0_ext_sol_df_s3 <- extend_solutions(
    long_mtbi_0_sol_df[401:600, ],
    dl = long_mtbi_0_dls[[3]],
    target_dl = long_mtbi_0_ols[[3]],
    min_pval = 1e-10,
    processes = "max"
)
})
saveRDS(long_mtbi_0_ext_sol_df_s3, proc_path("long_mtbi_0_ext_sol_df_s3.rds", TRUE))
# Solo imputation 4
progressr::with_progress({
long_mtbi_0_ext_sol_df_s4 <- extend_solutions(
    long_mtbi_0_sol_df[601:800, ],
    dl = long_mtbi_0_dls[[4]],
    target_dl = long_mtbi_0_ols[[4]],
    min_pval = 1e-10,
    processes = "max"
)
})
saveRDS(long_mtbi_0_ext_sol_df_s4, proc_path("long_mtbi_0_ext_sol_df_s4.rds", TRUE))
# Solo imputation 5
progressr::with_progress({
long_mtbi_0_ext_sol_df_s5 <- extend_solutions(
    long_mtbi_0_sol_df[801:1000, ],
    dl = long_mtbi_0_dls[[5]],
    target_dl = long_mtbi_0_ols[[5]],
    min_pval = 1e-10,
    processes = "max"
)
})
saveRDS(long_mtbi_0_ext_sol_df_s5, proc_path("long_mtbi_0_ext_sol_df_s5.rds", TRUE))
```

```{r}
# Solo imputation 1
progressr::with_progress({
long_mtbi_l_ext_sol_df_s1 <- extend_solutions(
    long_mtbi_l_sol_df[1:200, ],
    dl = long_mtbi_l_dls[[1]],
    target_dl = long_mtbi_l_ols[[1]],
    min_pval = 1e-10,
    processes = "max"
)
})
saveRDS(long_mtbi_l_ext_sol_df_s1, proc_path("long_mtbi_l_ext_sol_df_s1.rds", TRUE))
# Solo imputation 2
progressr::with_progress({
long_mtbi_l_ext_sol_df_s2 <- extend_solutions(
    long_mtbi_l_sol_df[201:400, ],
    dl = long_mtbi_l_dls[[2]],
    target_dl = long_mtbi_l_ols[[2]],
    min_pval = 1e-10,
    processes = "max"
)
})
saveRDS(long_mtbi_l_ext_sol_df_s2, proc_path("long_mtbi_l_ext_sol_df_s2.rds", TRUE))
# Solo imputation 3
progressr::with_progress({
long_mtbi_l_ext_sol_df_s3 <- extend_solutions(
    long_mtbi_l_sol_df[401:600, ],
    dl = long_mtbi_l_dls[[3]],
    target_dl = long_mtbi_l_ols[[3]],
    min_pval = 1e-10,
    processes = "max"
)
})
saveRDS(long_mtbi_l_ext_sol_df_s3, proc_path("long_mtbi_l_ext_sol_df_s3.rds", TRUE))
# Solo imputation 4
progressr::with_progress({
long_mtbi_l_ext_sol_df_s4 <- extend_solutions(
    long_mtbi_l_sol_df[601:800, ],
    dl = long_mtbi_l_dls[[4]],
    target_dl = long_mtbi_l_ols[[4]],
    min_pval = 1e-10,
    processes = "max"
)
})
saveRDS(long_mtbi_l_ext_sol_df_s4, proc_path("long_mtbi_l_ext_sol_df_s4.rds", TRUE))
# Solo imputation 5
progressr::with_progress({
long_mtbi_l_ext_sol_df_s5 <- extend_solutions(
    long_mtbi_l_sol_df[801:1000, ],
    dl = long_mtbi_l_dls[[5]],
    target_dl = long_mtbi_l_ols[[5]],
    min_pval = 1e-10,
    processes = "max"
)
})
saveRDS(long_mtbi_l_ext_sol_df_s5, proc_path("long_mtbi_l_ext_sol_df_s5.rds", TRUE))
```

```{r}

long_mtbi_0_ext_sol_df_s1 <- readRDS(proc_path("2025_04_29_long_mtbi_0_ext_sol_df_s1.rds"))
long_mtbi_0_ext_sol_df_s2 <- readRDS(proc_path("2025_04_29_long_mtbi_0_ext_sol_df_s2.rds"))
long_mtbi_0_ext_sol_df_s3 <- readRDS(proc_path("2025_04_29_long_mtbi_0_ext_sol_df_s3.rds"))
long_mtbi_0_ext_sol_df_s4 <- readRDS(proc_path("2025_04_29_long_mtbi_0_ext_sol_df_s4.rds"))
long_mtbi_0_ext_sol_df_s5 <- readRDS(proc_path("2025_04_29_long_mtbi_0_ext_sol_df_s5.rds"))

long_mtbi_0_ext_sol_df <- do.call(
    "rbind",
    c(
        list(
            long_mtbi_0_ext_sol_df_s1,
            long_mtbi_0_ext_sol_df_s2,
            long_mtbi_0_ext_sol_df_s3,
            long_mtbi_0_ext_sol_df_s4,
            long_mtbi_0_ext_sol_df_s5
        ),
        list(reset_indices = TRUE)
    )
)

long_mtbi_l_ext_sol_df_s1 <- readRDS(proc_path("2025_04_29_long_mtbi_l_ext_sol_df_s1.rds"))
long_mtbi_l_ext_sol_df_s2 <- readRDS(proc_path("2025_04_29_long_mtbi_l_ext_sol_df_s2.rds"))
long_mtbi_l_ext_sol_df_s3 <- readRDS(proc_path("2025_04_29_long_mtbi_l_ext_sol_df_s3.rds"))
long_mtbi_l_ext_sol_df_s4 <- readRDS(proc_path("2025_04_29_long_mtbi_l_ext_sol_df_s4.rds"))
long_mtbi_l_ext_sol_df_s5 <- readRDS(proc_path("2025_04_29_long_mtbi_l_ext_sol_df_s5.rds"))

long_mtbi_l_ext_sol_df <- do.call(
    "rbind",
    c(
        list(
            long_mtbi_l_ext_sol_df_s1,
            long_mtbi_l_ext_sol_df_s2,
            long_mtbi_l_ext_sol_df_s3,
            long_mtbi_l_ext_sol_df_s4,
            long_mtbi_l_ext_sol_df_s5
        ),
        list(reset_indices = TRUE)
    )
)

saveRDS(long_mtbi_0_ext_sol_df, proc_path("long_mtbi_0_ext_sol_df.rds", TRUE))
saveRDS(long_mtbi_l_ext_sol_df, proc_path("long_mtbi_l_ext_sol_df.rds", TRUE))

long_mtbi_0_ext_sol_df <- readRDS(proc_path("2025_04_29_long_mtbi_0_ext_sol_df.rds"))
long_mtbi_l_ext_sol_df <- readRDS(proc_path("2025_04_29_long_mtbi_l_ext_sol_df.rds"))
```

```{r}
long_0_hm <- meta_cluster_heatmap(long_mtbi_0_ari, order = long_mtbi_0_ari_order)
long_l_hm <- meta_cluster_heatmap(long_mtbi_l_ari, order = long_mtbi_l_ari_order)

long_mtbi_0_esdf <- as.data.frame(long_mtbi_0_ext_sol_df)
long_mtbi_l_esdf <- as.data.frame(long_mtbi_l_ext_sol_df)

long_mtbi_0_esdf$"impairment_separation" <- -log10(long_mtbi_0_esdf$"mean_pval")
long_mtbi_l_esdf$"impairment_separation" <- -log10(long_mtbi_l_esdf$"mean_pval")

full_long_mtbi_0_ari_hm <- meta_cluster_heatmap(
    x = long_mtbi_0_ari,
    order = long_mtbi_0_ari_order,
    data = long_mtbi_0_esdf,
    min_colour = "black",
    split_vector = c(
        75,
        285,
        882
    ),
    top_hm = list(
        "Impairment\nSeparation" = "impairment_separation"
    ),
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    annotation_colours = list(
        "Impairment\nSeparation" = colour_scale(
            long_mtbi_0_esdf$"impairment_separation",
            min_colour = "gray7",
            max_colour = "limegreen"
        )
    )
)
full_long_mtbi_0_ari_hm

full_long_mtbi_l_ari_hm <- meta_cluster_heatmap(
    x = long_mtbi_l_ari,
    order = long_mtbi_l_ari_order,
    data = long_mtbi_l_esdf,
    min_colour = "black",
    split_vector = c(
        692,
        881
    ),
    top_hm = list(
        "Impairment\nSeparation" = "impairment_separation"
    ),
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    annotation_colours = list(
        "Impairment\nSeparation" = colour_scale(
            long_mtbi_l_esdf$"impairment_separation",
            min_colour = "gray7",
            max_colour = "limegreen"
        )
    )
)
full_long_mtbi_l_ari_hm

save_heatmap(
    heatmap = full_long_mtbi_0_ari_hm,
    path = fig_path("full_long_mtbi_0_ari_hm.png", TRUE),
    width = 950,
    height = 800,
    res = 100
)
#
save_heatmap(
    heatmap = full_long_mtbi_l_ari_hm,
    path = fig_path("full_long_mtbi_l_ari_hm.png", TRUE),
    width = 950,
    height = 800,
    res = 100
)
```

Neither option resulted in particularly similar cluster solution to the original mTBI sample.
Suggests that there may be something unique to the kids who had their injury at a much earlier timepoint.

### Q4. Classifier built from baseline mTBI data: informative?

Assigning predicted clusters to the following 5 groups:

1. Longitudinal mTBI, pre-injury data (N = 220)
2. Longitudinal mTBI, post-injury data (the same N = 220)
3. Baseline uninjured group at T0  (N = 9349)
4. Longitudinal uninjured group at T0 (A subset of 3., N = 7678)
5. Longitudinal uninjured group at T2 (the same N = 7678)

```{r}
library(caret)
library(randomForest)
```

```{r}
long_unij_subs <- read_subjects(sub_path("2025_02_07_unij_subs_0_to_2.csv"))
long_unij_subs <- paste0("uid_", long_unij_subs)

# Classifying data using baseline as well as longitudinal features
long_mtbi_0_dl <- all_long_dls$"long_mtbi_0_dls"[[1]]
long_mtbi_0_ol <- all_long_dls$"long_mtbi_0_ols"[[1]]

long_mtbi_l_dl <- all_long_dls$"long_mtbi_l_dls"[[1]]
long_mtbi_l_ol <- all_long_dls$"long_mtbi_l_ols"[[1]]

base_unij_0_dl <- all_dls$"unij_pooled_data_lists"[[1]]
base_unij_0_ol <- all_dls$"unij_pooled_oom_lists"[[1]]

# These are not all necessary unij still!
base_unij_l_dl <- all_long_dls$"base_unij_l_dls"[[1]]
base_unij_l_ol <- all_long_dls$"base_unij_l_ols"[[1]]
```

```{r}
# Converting the sets of data lists into sets of data frames
long_mtbi_0_dl_df <- as.data.frame(long_mtbi_0_dl)
long_mtbi_0_ol_df <- as.data.frame(long_mtbi_0_ol)
nrow(long_mtbi_0_dl_df) # N = 220

long_mtbi_l_dl_df <- as.data.frame(long_mtbi_l_dl)
long_mtbi_l_ol_df <- as.data.frame(long_mtbi_l_ol)
nrow(long_mtbi_l_dl_df) # N = 220

base_unij_0_dl_df <- as.data.frame(base_unij_0_dl)
base_unij_0_ol_df <- as.data.frame(base_unij_0_ol)
nrow(base_unij_0_dl_df) # N = 9349

base_unij_l_dl_df <- as.data.frame(base_unij_l_dl)
base_unij_l_ol_df <- as.data.frame(base_unij_l_ol)
nrow(base_unij_0_dl_df) # N = 9349

long_unij_0_dl_df <- dplyr::filter(base_unij_0_dl_df, uid %in% long_unij_subs)
long_unij_0_ol_df <- dplyr::filter(base_unij_0_ol_df, uid %in% long_unij_subs)
nrow(long_unij_0_dl_df) # N = 9349

long_unij_l_dl_df <- dplyr::filter(base_unij_l_dl_df, uid %in% long_unij_subs)
long_unij_l_ol_df <- dplyr::filter(base_unij_l_ol_df, uid %in% long_unij_subs)
nrow(long_unij_0_dl_df) # N = 9349

comparison_dl_dfs <- list(
    "long_mtbi_0_dl_df" = long_mtbi_0_dl_df,
    "long_mtbi_l_dl_df" = long_mtbi_l_dl_df,
    "base_unij_0_dl_df" = base_unij_0_dl_df,
    "base_unij_l_dl_df" = base_unij_l_dl_df,
    "long_unij_0_dl_df" = long_unij_0_dl_df,
    "long_unij_l_dl_df" = long_unij_l_dl_df
)

comparison_ol_dfs <- list(
    "long_mtbi_0_ol_df" = long_mtbi_0_ol_df,
    "long_mtbi_l_ol_df" = long_mtbi_l_ol_df,
    "base_unij_0_ol_df" = base_unij_0_ol_df,
    "base_unij_l_ol_df" = base_unij_l_ol_df,
    "long_unij_0_ol_df" = long_unij_0_ol_df,
    "long_unij_l_ol_df" = long_unij_l_ol_df
)

saveRDS(comparison_dl_dfs, proc_path("comparison_dl_dfs.rds", TRUE))
saveRDS(comparison_ol_dfs, proc_path("comparison_ol_dfs.rds", TRUE))
```

```{r}
comparison_dl_dfs <- readRDS(proc_path("2025_05_02_comparison_dl_dfs.rds"))
comparison_ol_dfs <- readRDS(proc_path("2025_05_02_comparison_ol_dfs.rds"))
```

```{r}
classifier_fts <- readRDS(proc_path("2025_05_02_classifier_fts.rds"))

classifier_ft_dl_dfs <- lapply(
    comparison_dl_dfs,
    function(x) {
        x[, classifier_fts]
    }
)
```

In earlier chapters, some longitudinal data was reprocessed (date stamp 2025-03-10) to account for a previous extraction error in dMRI longitudinal data. 
That error does not impact the `temporal_df2` object, which was built from directly extracted (no imputed) data in chapter 7.

```{r}
# Extracted temporally sensitive features for all ABCD subjects at T0 and T2
temporal_0_df <- readRDS(proc_path("2025_02_17_temporal_df.rds"))
temporal_2_df <- readRDS(proc_path("2025_02_17_temporal_df2.rds"))

subtype_classifier <- readRDS(model_path("2025_02_17_subtype_classifier.rds"))
```

The scaling process that occurs below is described as follows.
Consider the data frame `long_mtbi_0_df`, which contains feature values for the longitudinal mTBI sample at baseline data collection timepoint.
A subset of the columns in `long_mtbi_0_df` are identified as temporally sensitive:

- brain_volume
- cortical_thickness
- cortical_sa
- pubertal_status_p
- pubertal_status_y
- age
- weekend_screentime
- weekday_screentime

Our goal is to re-scale these columns within `long_mtbi_0_df` based on the entire set of ABCD values of that feature for that time point.
The raw extracted set of ABCD values for those temporally sensitive features are found in `temporal_0_df` (for T0 values), and `temporal_2_df` (for T2 values).
However, scaling those data frames alone is insufficient, as we would not be making use of the missing values that we have imputed.
To account for this, we start by replacing the temporally sensitive features in `temporal_0_df` for the observations in `long_mtbi_0_df` with the values in `long_mtbi_0_df`.
That is, we inject our cleaned, imputed values for those temporally sensitive features and overwrite the raw extracted ones.
Then, we scale `temporal_0_df`.
Finally, we extract our scaled values back into the original `long_mtbi_0_df`.
This process is made slightly more complicated by doing this process for all the baseline concussion and uninjured sampes simultaneously.

```{r}
# Cleaning up the UID column of the temporally sensitive feature data frames
temporal_0_df$"uid" <- gsub("uid_", "", temporal_0_df$"uid")
temporal_2_df$"uid" <- gsub("uid_", "", temporal_2_df$"uid")

# Remove the UID column
temporal_cols <- colnames(temporal_0_df)
                
"long_mtbi_0_dl_df" = long_mtbi_0_dl_df,
"long_mtbi_l_dl_df" = long_mtbi_l_dl_df,
"base_unij_0_dl_df" = base_unij_0_dl_df,
"base_unij_l_dl_df" = base_unij_l_dl_df,
"long_unij_0_dl_df" = long_unij_0_dl_df,
"long_unij_l_dl_df" = long_unij_l_dl_df

long_mtbi_subs

base_unij_subs # <- A superset of long_unij_subs

long_unij_subs
```

There is notably some overlap between the long_mtbi group and the base_unij group.
As such, we handle the sub-in and scale for the different groups here separately.

```{r}
swap_with_scaled <- function(reference_df, df_to_scale, scaling_cols) {
    reference_df <- reference_df |>
        dplyr::filter(!uid %in% df_to_scale$"uid")
    scaling_fts <- setdiff(scaling_cols, "uid")
    stacked_df <- rbind(
        reference_df,
        df_to_scale[, scaling_cols]
    )
    stacked_df[scaling_fts] <- sapply(stacked_df[scaling_fts], scale)
    rescaled_df <- df_to_scale |>
        dplyr::select(-dplyr::all_of(scaling_fts)) |>
        dplyr::inner_join(stacked_df, by = "uid") |>
        data.frame()
    return(rescaled_df)
}

base_unij_0_time_scaled <- swap_with_scaled(
    temporal_0_df,
    comparison_dl_dfs$"base_unij_0_dl_df",
    temporal_cols
)
long_mtbi_0_time_scaled <- swap_with_scaled(
    temporal_0_df,
    comparison_dl_dfs$"long_mtbi_0_dl_df",
    temporal_cols
)
long_unij_0_time_scaled <- swap_with_scaled(
    temporal_0_df,
    comparison_dl_dfs$"long_unij_0_dl_df",
    temporal_cols
)
base_unij_l_time_scaled <- swap_with_scaled(
    temporal_2_df,
    comparison_dl_dfs$"base_unij_l_dl_df",
    temporal_cols
)
long_mtbi_l_time_scaled <- swap_with_scaled(
    temporal_2_df,
    comparison_dl_dfs$"long_mtbi_l_dl_df",
    temporal_cols
)
long_unij_l_time_scaled <- swap_with_scaled(
    temporal_2_df,
    comparison_dl_dfs$"long_unij_l_dl_df",
    temporal_cols
)

saveRDS(base_unij_0_time_scaled, proc_path("base_unij_0_time_scaled.rds", TRUE))
saveRDS(long_mtbi_0_time_scaled, proc_path("long_mtbi_0_time_scaled.rds", TRUE))
saveRDS(long_unij_0_time_scaled, proc_path("long_unij_0_time_scaled.rds", TRUE))
saveRDS(base_unij_l_time_scaled, proc_path("base_unij_l_time_scaled.rds", TRUE))
saveRDS(long_mtbi_l_time_scaled, proc_path("long_mtbi_l_time_scaled.rds", TRUE))
saveRDS(long_unij_l_time_scaled, proc_path("long_unij_l_time_scaled.rds", TRUE))
```

At this point the temporally sensitive variables has been appropriately time scaled for all data frames.

```{r}
base_unij_0_time_scaled <- readRDS(proc_path("2025_05_02_base_unij_0_time_scaled.rds"))
long_mtbi_0_time_scaled <- readRDS(proc_path("2025_05_02_long_mtbi_0_time_scaled.rds"))
long_unij_0_time_scaled <- readRDS(proc_path("2025_05_02_long_unij_0_time_scaled.rds"))
base_unij_l_time_scaled <- readRDS(proc_path("2025_05_02_base_unij_l_time_scaled.rds"))
long_mtbi_l_time_scaled <- readRDS(proc_path("2025_05_02_long_mtbi_l_time_scaled.rds"))
long_unij_l_time_scaled <- readRDS(proc_path("2025_05_02_long_unij_l_time_scaled.rds"))
```

```{r}
make_pred_df <- function(df) {
    clean_df <- prep_data(df)
    df$"cluster" <- predict(subtype_classifier, newdata = clean_df)
    return(df)
}

base_unij_0_pred_df <- make_pred_df(base_unij_0_time_scaled)
long_mtbi_0_pred_df <- make_pred_df(long_mtbi_0_time_scaled)
long_unij_0_pred_df <- make_pred_df(long_unij_0_time_scaled)
base_unij_l_pred_df <- make_pred_df(base_unij_l_time_scaled)
long_mtbi_l_pred_df <- make_pred_df(long_mtbi_l_time_scaled)
long_unij_l_pred_df <- make_pred_df(long_unij_l_time_scaled)

write_csv(base_unij_0_pred_df, proc_path("base_unij_0_pred_df.csv", TRUE))
write_csv(long_mtbi_0_pred_df, proc_path("long_mtbi_0_pred_df.csv", TRUE))
write_csv(long_unij_0_pred_df, proc_path("long_unij_0_pred_df.csv", TRUE))
write_csv(base_unij_l_pred_df, proc_path("base_unij_l_pred_df.csv", TRUE))
write_csv(long_mtbi_l_pred_df, proc_path("long_mtbi_l_pred_df.csv", TRUE))
write_csv(long_unij_l_pred_df, proc_path("long_unij_l_pred_df.csv", TRUE))
# HERE 2025-05-02
```

```{r}
# CHECKPOINT
base_unij_0_pred_df <- read_csv(proc_path("2025_05_02_base_unij_0_pred_df.csv"))
long_mtbi_0_pred_df <- read_csv(proc_path("2025_05_02_long_mtbi_0_pred_df.csv"))
long_unij_0_pred_df <- read_csv(proc_path("2025_05_02_long_unij_0_pred_df.csv"))
base_unij_l_pred_df <- read_csv(proc_path("2025_05_02_base_unij_l_pred_df.csv"))
long_mtbi_l_pred_df <- read_csv(proc_path("2025_05_02_long_mtbi_l_pred_df.csv"))
long_unij_l_pred_df <- read_csv(proc_path("2025_05_02_long_unij_l_pred_df.csv"))
```

```{r}
base_unij_0_cluster_df <- dplyr::select(
    base_unij_0_pred_df,
    uid,
    cluster
)
long_mtbi_0_cluster_df <- dplyr::select(
    long_mtbi_0_pred_df,
    uid,
    cluster
)
long_unij_0_cluster_df <- dplyr::select(
    long_unij_0_pred_df,
    uid,
    cluster
)
base_unij_l_cluster_df <- dplyr::select(
    base_unij_l_pred_df,
    uid,
    cluster
)
long_mtbi_l_cluster_df <- dplyr::select(
    long_mtbi_l_pred_df,
    uid,
    cluster
)
long_unij_l_cluster_df <- dplyr::select(
    long_unij_l_pred_df,
    uid,
    cluster
)
```

```{r}
# Proportion of each cluster in the data frame
cluster_props <- function(cluster_df) {
    cluster_df$"cluster" |>
    table() |>
    prop.table() |>
    (\(x) 100 * x)()
}

cluster_props(base_unij_0_cluster_df) # 24.8, 37.2, 38.0
cluster_props(base_unij_l_cluster_df) # 22.8, 30.4, 46.8

cluster_props(long_unij_0_cluster_df) # 23.7, 38.1, 38.2
cluster_props(long_unij_l_cluster_df) # 21.3, 31.3, 47.4

cluster_props(long_mtbi_0_cluster_df) # 17.3, 50.0, 32.7
cluster_props(long_mtbi_l_cluster_df) # 16.4, 44.1, 39.5

# Compare with the original full solution proportions
mtbi_ful_df <- readRDS(proc_path("2025_02_13_mtbi_ful_df.rds"))

cluster_props(mtbi_ful_df) # 33.2, 35.9, 30.9
```

```{r}
classifier_df <- read_csv(proc_path("2025_02_14_classifier_fts.csv"))
classifier_fts <- classifier_df$"classifier_fts"
outcome_fts <- readRDS(proc_path("2025_02_13_outputs.rds"))
relevant_fts <- c(classifier_fts, outcome_fts)

export_wrapped_plots <- function(df,
                                 dl,
                                 ol,
                                 name,
                                 feature_set = NULL,
                                 w = 45,
                                 h = 30,
                                 rows = NULL,
                                 cols = NULL,
                                 dpi = 100,
                                 export = TRUE) {
    plot_list <- auto_plot(
        cluster_df = data.frame(df),
        dl = c(dl, ol)
    )
    wrapped_plots <- wrap_plots(
        plot_list[feature_set],
        nrow = rows,
        ncol = cols,
    )
    if (export) {
        ggsave(
            fig_path(name, TRUE),
            width = w,
            height = h,
            dpi = dpi
        )
    } else {
        return(plot_list)
    }
}

export_wrapped_plots(
    df = long_mtbi_0_cluster_df,
    dl = long_mtbi_0_dl,
    ol = long_mtbi_0_ol,
    feature_set = relevant_fts,
    name = "long_mtbi_0_pred_scaled_plot.png"
)
export_wrapped_plots(
    df = long_mtbi_l_cluster_df,
    dl = long_mtbi_l_dl,
    ol = long_mtbi_l_ol,
    feature_set = relevant_fts,
    name = "long_mtbi_l_pred_scaled_plot.png"
)
export_wrapped_plots(
    df = base_unij_0_cluster_df,
    dl = base_unij_0_dl,
    ol = base_unij_0_ol,
    feature_set = relevant_fts,
    name = "base_unij_0_pred_scaled_plot.png"
)
export_wrapped_plots(
    df = base_unij_l_cluster_df,
    dl = base_unij_l_dl,
    ol = base_unij_l_ol,
    feature_set = relevant_fts,
    name = "base_unij_l_pred_scaled_plot.png"
)


# Just top 10 features
sorted_inputs <- readRDS(proc_path("2025_02_12_sorted_inputs.rds"))
top_fts <- intersect(
    c(sorted_inputs[1:10], outcome_fts),
    relevant_fts
)

saveRDS(top_fts, proc_path("top_fts.rds", TRUE))
top_fts <- readRDS(proc_path("2025_05_12_top_fts.rds"))

export_wrapped_plots(
    df = long_mtbi_0_cluster_df,
    dl = long_mtbi_0_dl,
    ol = long_mtbi_0_ol,
    feature_set = top_fts,
    rows = 2,
    w = 30,
    h = 7,
    name = "long_mtbi_0_pred_scaled_plot_top_fts.png"
)
export_wrapped_plots(
    df = long_mtbi_l_cluster_df,
    dl = long_mtbi_l_dl,
    ol = long_mtbi_l_ol,
    feature_set = top_fts,
    rows = 2,
    w = 30,
    h = 7,
    name = "long_mtbi_l_pred_scaled_plot_top_fts.png"
)
export_wrapped_plots(
    df = base_unij_0_cluster_df,
    dl = base_unij_0_dl,
    ol = base_unij_0_ol,
    feature_set = top_fts,
    rows = 2,
    w = 30,
    h = 7,
    name = "base_unij_0_pred_scaled_plot_top_fts.png"
)

export_wrapped_plots(
    df = base_unij_l_cluster_df,
    dl = base_unij_l_dl,
    ol = base_unij_l_ol,
    feature_set = top_fts,
    rows = 2,
    w = 30,
    h = 7,
    name = "base_unij_l_pred_scaled_plot_top_fts.png"
)


long_unij_0_dl <- base_unij_0_dl |>
    dlapply(
        function(x) {
            x$"data" <- dplyr::filter(x$"data", uid %in% long_unij_subs)
            return(x)
        }
    )
long_unij_0_ol <- base_unij_0_ol |>
    dlapply(
        function(x) {
            x$"data" <- dplyr::filter(x$"data", uid %in% long_unij_subs)
            return(x)
        }
    )
long_unij_l_dl <- base_unij_l_dl |>
    dlapply(
        function(x) {
            x$"data" <- dplyr::filter(x$"data", uid %in% long_unij_subs)
            return(x)
        }
    )
long_unij_l_ol <- base_unij_l_ol |>
    dlapply(
        function(x) {
            x$"data" <- dplyr::filter(x$"data", uid %in% long_unij_subs)
            return(x)
        }
    )

export_wrapped_plots(
    df = long_unij_0_cluster_df,
    dl = long_unij_0_dl,
    ol = long_unij_0_ol,
    name = "long_unij_0_pred_scaled_plot.png"
)

export_wrapped_plots(
    df = long_unij_l_cluster_df,
    dl = long_unij_l_dl,
    ol = long_unij_l_ol,
    name = "long_unij_l_pred_scaled_plot.png"
)

export_wrapped_plots(
    df = long_unij_0_cluster_df,
    dl = long_unij_0_dl,
    ol = long_unij_0_ol,
    feature_set = top_fts,
    rows = 2,
    w = 30,
    h = 7,
    name = "long_unij_0_pred_scaled_plot_top_fts.png"
)

export_wrapped_plots(
    df = long_unij_l_cluster_df,
    dl = long_unij_l_dl,
    ol = long_unij_l_ol,
    feature_set = top_fts,
    rows = 2,
    w = 30,
    h = 7,
    name = "long_unij_l_pred_scaled_plot_top_fts.png"
)

```

Just inputs:

```{r}

top_ins <- sorted_inputs[1:10]

export_wrapped_plots(
    df = long_mtbi_0_cluster_df,
    dl = long_mtbi_0_dl,
    ol = long_mtbi_0_ol,
    feature_set = top_ins,
    cols = 1,
    h = 27,
    w = 5,
    dpi = 80,
    name = "long_mtbi_0_pred_scaled_plot_top_ins.png"
)
export_wrapped_plots(
    df = long_mtbi_l_cluster_df,
    dl = long_mtbi_l_dl,
    ol = long_mtbi_l_ol,
    feature_set = top_ins,
    cols = 1,
    h = 27,
    w = 5,
    dpi = 80,
    name = "long_mtbi_l_pred_scaled_plot_top_ins.png"
)
export_wrapped_plots(
    df = base_unij_0_cluster_df,
    dl = base_unij_0_dl,
    ol = base_unij_0_ol,
    feature_set = top_ins,
    cols = 1,
    h = 27,
    w = 5,
    dpi = 80,
    name = "base_unij_0_pred_scaled_plot_top_ins.png"
)
export_wrapped_plots(
    df = base_unij_l_cluster_df,
    dl = base_unij_l_dl,
    ol = base_unij_l_ol,
    feature_set = top_ins,
    cols = 1,
    h = 27,
    w = 5,
    dpi = 80,
    name = "base_unij_l_pred_scaled_plot_top_ins.png"
)
export_wrapped_plots(
    df = long_unij_0_cluster_df,
    dl = long_unij_0_dl,
    ol = long_unij_0_ol,
    feature_set = top_ins,
    cols = 1,
    h = 27,
    w = 5,
    dpi = 80,
    name = "long_unij_0_pred_scaled_plot_top_ins.png"
)
export_wrapped_plots(
    df = long_unij_l_cluster_df,
    dl = long_unij_l_dl,
    ol = long_unij_l_ol,
    feature_set = top_ins,
    cols = 1,
    h = 27,
    w = 5,
    dpi = 80,
    name = "long_unij_l_pred_scaled_plot_top_ins.png"
)
```

Just outputs:

```{r}
export_wrapped_plots(
    df = long_mtbi_0_cluster_df,
    dl = long_mtbi_0_dl,
    ol = long_mtbi_0_ol,
    feature_set = outcome_fts,
    cols = 1,
    h = 24,
    w = 3,
    dpi = 80,
    name = "long_mtbi_0_pred_scaled_plot_outcome_fts.png"
)
export_wrapped_plots(
    df = long_mtbi_l_cluster_df,
    dl = long_mtbi_l_dl,
    ol = long_mtbi_l_ol,
    feature_set = outcome_fts,
    cols = 1,
    h = 24,
    w = 3,
    dpi = 80,
    name = "long_mtbi_l_pred_scaled_plot_outcome_fts.png"
)
export_wrapped_plots(
    df = base_unij_0_cluster_df,
    dl = base_unij_0_dl,
    ol = base_unij_0_ol,
    feature_set = outcome_fts,
    cols = 1,
    h = 24,
    w = 3,
    dpi = 80,
    name = "base_unij_0_pred_scaled_plot_outcome_fts.png"
)
export_wrapped_plots(
    df = base_unij_l_cluster_df,
    dl = base_unij_l_dl,
    ol = base_unij_l_ol,
    feature_set = outcome_fts,
    cols = 1,
    h = 24,
    w = 3,
    dpi = 80,
    name = "base_unij_l_pred_scaled_plot_outcome_fts.png"
)
export_wrapped_plots(
    df = long_unij_0_cluster_df,
    dl = long_unij_0_dl,
    ol = long_unij_0_ol,
    feature_set = outcome_fts,
    cols = 1,
    h = 24,
    w = 3,
    dpi = 80,
    name = "long_unij_0_pred_scaled_plot_outcome_fts.png"
)
export_wrapped_plots(
    df = long_unij_l_cluster_df,
    dl = long_unij_l_dl,
    ol = long_unij_l_ol,
    feature_set = outcome_fts,
    cols = 1,
    h = 24,
    w = 3,
    dpi = 80,
    name = "long_unij_l_pred_scaled_plot_outcome_fts.png"
)
```

Statistical analysis: bootstrapped similarity to baseline mTBI solution

```{r}
mtbi_gen_fts_in_long <- read_csv(proc_path("2025_02_13_mtbi_gen_fts_in_long.csv"))
mtbi_gen_fts_out_long <- read_csv(proc_path("2025_02_13_mtbi_gen_fts_out_long.csv"))
mtbi_gen_long <- rbind(
    mtbi_gen_fts_in_long,
    mtbi_gen_fts_out_long
)
mtbi_gen_long <- na.omit(mtbi_gen_long)

long_mtbi_0_data_df <- dplyr::inner_join(
    long_mtbi_0_cluster_df,
    as.data.frame(c(long_mtbi_0_dl, long_mtbi_0_ol)),
    by = "uid"
)

long_mtbi_l_data_df <- dplyr::inner_join(
    long_mtbi_l_cluster_df,
    as.data.frame(c(long_mtbi_l_dl, long_mtbi_l_ol)),
    by = "uid"
)

base_unij_0_data_df <- dplyr::inner_join(
    base_unij_0_cluster_df,
    as.data.frame(c(base_unij_0_dl, base_unij_0_ol)),
    by = "uid"
)

base_unij_l_data_df <- dplyr::inner_join(
    base_unij_l_cluster_df,
    as.data.frame(c(base_unij_l_dl, base_unij_l_ol)),
    by = "uid"
)

topologizer <- function(df) {
    df <- data.frame(df)
    df <- metasnf:::numcol_to_numeric(df)
    df <- dummy_non_numeric(dplyr::select(df, -"uid"))
    summary_df <- data.frame(
        "feature" = as.character(),
        "type" = as.character(),
        "summary" = as.character(),
        "c1_mean" = as.numeric(),
        "c2_mean" = as.numeric(),
        "c3_mean" = as.numeric(),
        "c1_c2_es" = as.numeric(),
        "c1_c2_l" = as.numeric(),
        "c1_c2_u" = as.numeric(),
        "c1_c3_es" = as.numeric(),
        "c1_c3_l" = as.numeric(),
        "c1_c3_u" = as.numeric(),
        "c2_c3_es" = as.numeric(),
        "c2_c3_l" = as.numeric(),
        "c2_c3_u" = as.numeric()
    )
    c1 <- df[df$"cluster" == 1, ]
    c2 <- df[df$"cluster" == 2, ]
    c3 <- df[df$"cluster" == 3, ]
    features <- df |>
        dplyr::select(-"cluster") |>
        colnames()
    ###########################################################################
    # Check if features are binary (unique values are 0 and 1) or not
    ###########################################################################
    for (feature in features) {
        f1 <- c1[, feature]
        f2 <- c2[, feature]
        f3 <- c3[, feature]
        means <- c("1" = mean(f1), "2" = mean(f2), "3" = mean(f3))
        full_summary <- paste(
            names(sort(means, decreasing = TRUE)),
            collapse = " > "
        )
        if (is_binary(df[, feature])) {
            sum_1_v_2 <- calc_propes(f1, f2)
            sum_1_v_3 <- calc_propes(f1, f3)
            sum_2_v_3 <- calc_propes(f2, f3)
            type <- "or"
        } else {
            sum_1_v_2 <- calc_des(f1, f2)
            sum_1_v_3 <- calc_des(f1, f3)
            sum_2_v_3 <- calc_des(f2, f3)
            type <- "d"
        }
        summary_df <- rbind(
            summary_df,
            data.frame(
                "feature" = feature,
                "summary" = full_summary,
                "c1" = signif(mean(f1), 3),
                "c2" = signif(mean(f2), 3),
                "c3" = signif(mean(f3), 3),
                "es" = type,
                "c12_es" = sum_1_v_2$"es",
                "c12_l" = sum_1_v_2$"l",
                "c12_u" = sum_1_v_2$"u",
                "c13_es" = sum_1_v_3$"es",
                "c13_l" = sum_1_v_3$"l",
                "c13_u" = sum_1_v_3$"u",
                "c23_es" = sum_2_v_3$"es",
                "c23_l" = sum_2_v_3$"l",
                "c23_u" = sum_2_v_3$"u"
            )
        )
    }
    return(summary_df)
}

concordance_w_mtbi <- function(data_df, n = NULL, iters = 10, procs = 1) {
    if (is.null(n)) {
        n <- nrow(data_df)
    }
    p <- progressr::progressor(steps = iters)
    future::plan(
        future::multisession,
        workers = procs
    )
    res <- future.apply::future_lapply(
        1:iters,
        future.seed = TRUE,
        function(x, p) {
            start <- Sys.time()
            bootstrap_sample <- sample(n, replace = TRUE)
            sampled_df <- data_df[bootstrap_sample, ]
            tops_df <- topologizer(sampled_df)
            gen_tops_df <- generalizable_features(tops_df, compare_fn_a)
            gen_tops_df_long <- gen_tops_df |>
                pivot_longer(
                    cols = -feature,
                    names_to = "comparison",
                    values_to = "order_sample"
                )
            joint_df <- dplyr::left_join(
                mtbi_gen_long, # reference data frame
                gen_tops_df_long, # sampled data frame
                by = c("feature", "comparison")
            ) |>
                dplyr::mutate(
                    match = ifelse(order_sample == order, 1, 0)
                ) |>
                dplyr::filter(!grepl("mtbi", feature))
            p()
            concordance <- sum(joint_df$"match") / nrow(joint_df)
            return(concordance)
        },
        p = p
    )
    future::plan(future::sequential)
    return(unlist(res))
}

# HERE

set.seed(42)
start <- Sys.time()
progressr::with_progress({
    long_mtbi_0_pred_conc <- concordance_w_mtbi(long_mtbi_0_data_df, iters = 1000, procs = 100)
})
long_mtbi_0_pred_conc
print(Sys.time() - start)
saveRDS(long_mtbi_0_pred_conc, proc_path("long_mtbi_0_pred_conc.rds", TRUE))

set.seed(42)
start <- Sys.time()
progressr::with_progress({
    long_mtbi_l_pred_conc <- concordance_w_mtbi(long_mtbi_l_data_df, iters = 1000, procs = 100)
})
long_mtbi_l_pred_conc
print(Sys.time() - start)
saveRDS(long_mtbi_l_pred_conc, proc_path("long_mtbi_l_pred_conc.rds", TRUE))
```

```{r}
long_mtbi_0_pred_conc <- readRDS(proc_path("2025_05_12_long_mtbi_0_pred_conc.rds"))
long_mtbi_l_pred_conc <- readRDS(proc_path("2025_05_12_long_mtbi_l_pred_conc.rds"))

mean(na.omit(long_mtbi_0_pred_conc))

mean(na.omit(long_mtbi_l_pred_conc))

sims_pre <- na.omit(long_mtbi_0_pred_conc)
sims_post <- na.omit(long_mtbi_l_pred_conc)

ci_solo_pre <- quantile(sims_pre, probs = c(0.025, 0.975))
mean(sims_pre) # 0.7797065
ci_solo_pre # 0.7073171, 0.8455285

ci_solo_post <- quantile(sims_post, probs = c(0.025, 0.975))
mean(sims_post) # 0.829507
ci_solo_post #0 .7623984, 0.8861789



set.seed(42)
bootstrapped_diffs <- lapply(
    1:10000,
    function(x) {
        sampled_sim_post <- sample(sims_post, size = 1)
        sampled_sim_pre <- sample(sims_pre, size = 1)
        sampled_sim_post - sampled_sim_pre
    }
)
mean_diff <- mean(unlist(bootstrapped_diffs))
ci <- quantile(unlist(bootstrapped_diffs), probs = c(0.025, 0.975))
mean_diff * 100 # 5.03
ci * 100 # [-0.04878049, 0.14634146]

```












### Meta clustering the longitudinal timepoint for baseline concussion group

```{r}
# CHECKPOINT
base_mtbi_l_dls <- all_long_dls$"base_mtbi_l_dls"
base_mtbi_l_ols <- all_long_dls$"base_mtbi_l_ols"
```

```{r}
set.seed(42)
long_base_mtbi_config <- snf_config(
    base_mtbi_l_dls[[1]],
    n_solutions = 200,
    cnt_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    dsc_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ord_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    use_default_dist_fns = TRUE
)

saveRDS(long_base_mtbi_config, proc_path("long_base_mtbi_config.rds", TRUE))
```

```{r}
# CHECKPOINT
long_base_mtbi_config <- readRDS(proc_path("2025_02_18_long_base_mtbi_config.rds"))
```

```{r}
base_mtbi_l_sol_df_s1 <- batch_snf(
    dl = base_mtbi_l_dls[[1]],
    sc = long_base_mtbi_config,
    processes = "max"
)
saveRDS(base_mtbi_l_sol_df_s1, proc_path("base_mtbi_l_sol_df_s1.rds", TRUE))

base_mtbi_l_sol_df_s2 <- batch_snf(
    dl = base_mtbi_l_dls[[2]],
    sc = long_base_mtbi_config,
    processes = "max"
)
saveRDS(base_mtbi_l_sol_df_s2, proc_path("base_mtbi_l_sol_df_s2.rds", TRUE))

base_mtbi_l_sol_df_s3 <- batch_snf(
    dl = base_mtbi_l_dls[[3]],
    sc = long_base_mtbi_config,
    processes = "max"
)
saveRDS(base_mtbi_l_sol_df_s3, proc_path("base_mtbi_l_sol_df_s3.rds", TRUE))

base_mtbi_l_sol_df_s4 <- batch_snf(
    dl = base_mtbi_l_dls[[4]],
    sc = long_base_mtbi_config,
    processes = "max"
)
saveRDS(base_mtbi_l_sol_df_s4, proc_path("base_mtbi_l_sol_df_s4.rds", TRUE))

base_mtbi_l_sol_df_s5 <- batch_snf(
    dl = base_mtbi_l_dls[[5]],
    sc = long_base_mtbi_config,
    processes = "max"
)
saveRDS(base_mtbi_l_sol_df_s5, proc_path("base_mtbi_l_sol_df_s5.rds", TRUE))
```

```{r}
base_mtbi_l_sol_df_s1 <- readRDS(proc_path("2025_02_18_base_mtbi_l_sol_df_s1.rds"))
base_mtbi_l_sol_df_s2 <- readRDS(proc_path("2025_02_18_base_mtbi_l_sol_df_s2.rds"))
base_mtbi_l_sol_df_s3 <- readRDS(proc_path("2025_02_18_base_mtbi_l_sol_df_s3.rds"))
base_mtbi_l_sol_df_s4 <- readRDS(proc_path("2025_02_18_base_mtbi_l_sol_df_s4.rds"))
base_mtbi_l_sol_df_s5 <- readRDS(proc_path("2025_02_18_base_mtbi_l_sol_df_s5.rds"))

base_mtbi_l_sol_df <- do.call(
    "rbind",
    c(
        list(
            base_mtbi_l_sol_df_s1,
            base_mtbi_l_sol_df_s2,
            base_mtbi_l_sol_df_s3,
            base_mtbi_l_sol_df_s4,
            base_mtbi_l_sol_df_s5
        ),
        list(reset_indices = TRUE)
    )
)
saveRDS(base_mtbi_l_sol_df, proc_path("base_mtbi_l_sol_df.rds", TRUE))

base_mtbi_l_ari <- calc_aris(base_mtbi_l_sol_df, processes = "max")
saveRDS(base_mtbi_l_ari, proc_path("base_mtbi_l_ari.rds", TRUE))

base_mtbi_l_ari_order <- get_matrix_order(base_mtbi_l_ari)
write_csv(data.frame(base_mtbi_l_ari_order), proc_path("base_mtbi_l_ari_order.csv", TRUE))
```

```{r}
# CHECKPOINT
base_mtbi_l_sol_df <- readRDS(proc_path("2025_02_18_base_mtbi_l_sol_df.rds"))
base_mtbi_l_ari <- readRDS(proc_path("2025_02_18_base_mtbi_l_ari.rds"))
base_mtbi_l_ari_order <- unlist(read_csv(proc_path("2025_02_18_base_mtbi_l_ari_order.csv")))
names(base_mtbi_l_ari_order) <- NULL
```

```{r}
# Solo imputation 1
base_mtbi_l_ext_sol_df_s1 <- extend_solutions(
    base_mtbi_l_sol_df[1:200, ],
    dl = base_mtbi_l_dls[[1]],
    target_dl = base_mtbi_l_ols[[1]],
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(base_mtbi_l_ext_sol_df_s1, proc_path("base_mtbi_l_ext_sol_df_s1.rds", TRUE))
# Solo imputation 2
base_mtbi_l_ext_sol_df_s2 <- extend_solutions(
    base_mtbi_l_sol_df[201:400, ],
    dl = base_mtbi_l_dls[[2]],
    target_dl = base_mtbi_l_ols[[2]],
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(base_mtbi_l_ext_sol_df_s2, proc_path("base_mtbi_l_ext_sol_df_s2.rds", TRUE))
# Solo imputation 3
base_mtbi_l_ext_sol_df_s3 <- extend_solutions(
    base_mtbi_l_sol_df[401:600, ],
    dl = base_mtbi_l_dls[[3]],
    target_dl = base_mtbi_l_ols[[3]],
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(base_mtbi_l_ext_sol_df_s3, proc_path("base_mtbi_l_ext_sol_df_s3.rds", TRUE))
# Solo imputation 4
base_mtbi_l_ext_sol_df_s4 <- extend_solutions(
    base_mtbi_l_sol_df[601:800, ],
    dl = base_mtbi_l_dls[[4]],
    target_dl = base_mtbi_l_ols[[4]],
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(base_mtbi_l_ext_sol_df_s4, proc_path("base_mtbi_l_ext_sol_df_s4.rds", TRUE))
# Solo imputation 5
base_mtbi_l_ext_sol_df_s5 <- extend_solutions(
    base_mtbi_l_sol_df[801:1000, ],
    dl = base_mtbi_l_dls[[5]],
    target_dl = base_mtbi_l_ols[[5]],
    min_pval = 1e-10,
    processes = "max"
)
saveRDS(base_mtbi_l_ext_sol_df_s5, proc_path("base_mtbi_l_ext_sol_df_s5.rds", TRUE))
```

```{r}
base_mtbi_l_ext_sol_df_s1 <- readRDS(proc_path("2025_02_18_base_mtbi_l_ext_sol_df_s1.rds"))
base_mtbi_l_ext_sol_df_s2 <- readRDS(proc_path("2025_02_18_base_mtbi_l_ext_sol_df_s2.rds"))
base_mtbi_l_ext_sol_df_s3 <- readRDS(proc_path("2025_02_18_base_mtbi_l_ext_sol_df_s3.rds"))
base_mtbi_l_ext_sol_df_s4 <- readRDS(proc_path("2025_02_18_base_mtbi_l_ext_sol_df_s4.rds"))
base_mtbi_l_ext_sol_df_s5 <- readRDS(proc_path("2025_02_18_base_mtbi_l_ext_sol_df_s5.rds"))

base_mtbi_l_ext_sol_df <- do.call(
    "rbind",
    c(
        list(
            base_mtbi_l_ext_sol_df_s1,
            base_mtbi_l_ext_sol_df_s2,
            base_mtbi_l_ext_sol_df_s3,
            base_mtbi_l_ext_sol_df_s4,
            base_mtbi_l_ext_sol_df_s5
        ),
        list(reset_indices = TRUE)
    )
)

saveRDS(base_mtbi_l_ext_sol_df, proc_path("base_mtbi_l_ext_sol_df.rds", TRUE))

base_mtbi_l_ext_sol_df <- readRDS(proc_path("2025_02_18_base_mtbi_l_ext_sol_df.rds"))
```

```{r}
base_mtbi_l_hm <- meta_cluster_heatmap(base_mtbi_l_ari, order = base_mtbi_l_ari_order)
base_mtbi_l_esdf <- as.data.frame(base_mtbi_l_ext_sol_df)
base_mtbi_l_esdf$"impairment_separation" <- -log10(base_mtbi_l_esdf$"mean_pval")

# It's there!
full_base_mtbi_l_ari_hm <- meta_cluster_heatmap(
    aris = base_mtbi_l_ari,
    order = base_mtbi_l_ari_order,
    data = base_mtbi_l_esdf,
    min_colour = "black",
    top_hm = list(
        "Impairment Separation" = "impairment_separation"
    ),
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    annotation_colours = list(
        "Impairment Separation" = colour_scale(
            base_mtbi_l_esdf$"impairment_separation",
            min_colour = "gray7",
            max_colour = "limegreen"
        )
    )
)
full_base_mtbi_l_ari_hm

save_heatmap(
    heatmap = full_base_mtbi_l_ari_hm,
    path = fig_path("full_base_mtbi_l_ari_hm.png", TRUE),
    width = 950,
    height = 900,
    res = 100
)

```

So the baseline mTBI subjects do seem to have it!


## Moving on: Change in outcomes

If I go back to when I was about to run extend solutions, and instead try to find any meta clusters associated with change in outcome measures, do I find anything interesting?

```{r}
full_dl_0 <- readRDS(input_path("2025_02_12_mtbi_full_data_list_1.rds"))
full_ol_0 <- readRDS(input_path("2025_02_12_mtbi_full_oom_list_1.rds"))

full_ol_2 <- all_long_dls$"base_mtbi_l_ols"[[1]]

full_ol_0_df <- as.data.frame(full_ol_0)
full_ol_2_df <- as.data.frame(full_ol_2)

full_ol_change_df$"cbcl_anxdep" <- full_ol_2_df$"cbcl_anxdep" - full_ol_0_df$"cbcl_anxdep"
full_ol_change_df$"cbcl_withdep" <- full_ol_2_df$"cbcl_withdep" - full_ol_0_df$"cbcl_withdep"
full_ol_change_df$"cbcl_somatic" <- full_ol_2_df$"cbcl_somatic" - full_ol_0_df$"cbcl_somatic"
full_ol_change_df$"cbcl_social" <- full_ol_2_df$"cbcl_social" - full_ol_0_df$"cbcl_social"
full_ol_change_df$"cbcl_thought" <- full_ol_2_df$"cbcl_thought" - full_ol_0_df$"cbcl_thought"
full_ol_change_df$"cbcl_attention" <- full_ol_2_df$"cbcl_attention" - full_ol_0_df$"cbcl_attention"
full_ol_change_df$"cbcl_rulebreak" <- full_ol_2_df$"cbcl_rulebreak" - full_ol_0_df$"cbcl_rulebreak"
full_ol_change_df$"cbcl_aggressive" <- full_ol_2_df$"cbcl_aggressive" - full_ol_0_df$"cbcl_aggressive"
full_ol_change_df$"sds_sleep" <- full_ol_2_df$"sds_sleep" - full_ol_0_df$"sds_sleep"
full_ol_change_df$"uid" <- gsub("uid_", "", full_ol_change_df$"uid")

full_ol_change <- data_list(
    list(dplyr::select(full_ol_change_df, uid, dplyr::starts_with("cbcl")), "cbcl", "B", "discrete"),
    list(dplyr::select(full_ol_change_df, uid, dplyr::starts_with("sds")), "sds", "B", "discrete"),
    uid = "uid"
)

saveRDS(full_ol_change, proc_path("full_ol_change.rds", TRUE))

full_ol_change <- readRDS(proc_path("2025_02_18_full_ol_change.rds"))
mtbi_full_sol_df <- readRDS(proc_path("2025_02_12_mtbi_full_sol_df.rds"))

mtbi_full_change_ext_sol_df <- extend_solutions(
    mtbi_full_sol_df,
    target_dl = full_ol_change,
    min_pval = 1e-10,
    processes = "max"
)

saveRDS(mtbi_full_change_ext_sol_df, proc_path("mtbi_full_change_ext_sol_df.rds", TRUE))

mtbi_full_change_ext_sol_df <- readRDS(proc_path("2025_02_18_mtbi_full_change_ext_sol_df.rds"))

mtbi_full_change_ari <- calc_aris(mtbi_full_change_ext_sol_df)

saveRDS(mtbi_full_change_ari, proc_path("mtbi_full_change_ari.rds", TRUE))
mtbi_full_change_ari <- readRDS(proc_path("2025_02_18_mtbi_full_change_ari.rds"))

full_change_order <- get_matrix_order(mtbi_full_change_ari)

saveRDS(full_change_order, proc_path("full_change_order.rds", TRUE))
full_change_order <- readRDS(proc_path("2025_02_18_full_change_order.rds"))

full_change_esdf <- as.data.frame(mtbi_full_change_ext_sol_df)

full_change_esdf$"impairment_separation" <- -log10(full_change_esdf$"mean_pval")

full_change_mc_hm <- meta_cluster_heatmap(
    aris = mtbi_full_change_ari,
    order = full_change_order,
    data = full_change_esdf,
    split_vector = c(
        48,
        54,
        95,
        136,
        147
    ),
    top_hm = list(
        "Impairment Separation" = "impairment_separation"
    ),
    top_bar = list(
        "Number of Clusters" = "nclust"
    ),
    annotation_colours = list(
        "Impairment Separation" = colour_scale(
            full_change_esdf$"impairment_separation",
            min_colour = "gray7",
            max_colour = "limegreen"
        )
    )
)

save_heatmap(
    heatmap = full_change_mc_hm,
    path = fig_path("full_change_mc_hm.png", TRUE),
    width = 950,
    height = 900,
    res = 100
)

change_mc_sol_df <- label_meta_clusters(
    mtbi_full_change_ext_sol_df,
    order = full_change_order,
    split_vector = c(
        48,
        54,
        95,
        136,
        147
    )
)

change_rep_solutions <- get_representative_solutions(
    mtbi_full_change_ari,
    change_mc_sol_df
)

top_change_esdf <- change_rep_solutions[2, ]

saveRDS(top_change_esdf, proc_path("top_change_esdf.rds", TRUE))
top_change_esdf <- readRDS(proc_path("2025_02_18_top_change_esdf.rds"))

# Adding in the input features as well
top_change_esdf2 <- extend_solutions(
    mtbi_full_sol_df[54, ],
    dl = full_dl_0,
    target_dl = full_ol_change,
    min_pval = 1e-10,
    processes = "max"
)

top_change_esdf2$"mc" <- "B"

saveRDS(top_change_esdf2, proc_path("top_change_esdf2.rds", TRUE))
top_change_esdf2 <- readRDS(proc_path("2025_02_18_top_change_esdf2.rds"))

top_change_manhattan <- mc_manhattan_plot(
    top_change_esdf2,
    dl = full_dl_0,
    target_dl = full_ol_change,
    domain_colours = c(
        "AS" = "#85929e",
        "D" = "#bb8fce",
        "N" = "#e59866",
        "MH" = "#7fb3d5",
        "P" = "#52be80",
        "S" = "#d98880",
        "B" = "#ff3131"
    )
)

ggsave(
    plot = top_change_manhattan,
    filename = fig_path("top_change_manhattan.png", TRUE),
    width = 18,
    height = 5,
    dpi = 120
)

change_pl <- auto_plot(
    top_change_esdf2,
    dl = c(full_dl_0, full_ol_change),
    verbose = TRUE
)

change_pl_wrapped <- wrap_plots(change_pl)

ggsave(
    fig_path("change_pl_wrapped.png", TRUE),
    change_pl_wrapped,
    width = 45,
    height = 30,
    dpi = 50
)
```

Not all that interesting; kids who had worse scores to begin with have an easier time getting better.
