```{r}
library(abcdutils)
library(here)
library(dplyr)
library(readr)
library(metasnf)
library(fastDummies)
library(patchwork)
library(tidyr)
library(ggplot2)

source("helper_functions.R")

input_path <- path_maker(here("data/abcd/inputs"))
core_path <- path_maker(here("data/abcd/core"))
sub_path <- path_maker(here("data/abcd/subjects"))
fig_path <- path_maker(here("data/abcd/results/figures"))
proc_path <- path_maker(here("data/abcd/results/processed"))
```

```{r}
# baseline concussion sample pre-imputation
mtbi_train_df <- data.frame(read_csv(proc_path("2025_09_11_mtbi_train_df.csv")))
mtbi_test_df <- data.frame(read_csv(proc_path("2025_09_11_mtbi_test_df.csv")))

# baseline uninjured sample pre-imputation
unij_df <- data.frame(read_csv(proc_path("2025_09_11_unij_df.csv")))

# baseline concussion sample post-imputation
# baseline uninjured sample post-imputation
all_dls <- readRDS(input_path("2025_09_11_all_dls.rds"))

# baseline concussion sample post-imputation, post-harmonization
# baseline uninjured sample post-imputation, post-harmonization
all_dls_h <- readRDS(proc_path("2025_09_11_all_dls_h.rds"))

all_dls_h_ns <- readRDS(proc_path("2025_09_11_all_dls_h_no_sibs.rds"))

iread <- function(path) {
    return(read_csv(input_path(path)))
}

# longitudinal data frames, pre-imputation
lmtb_0_df <- data.frame(iread("2026_01_19_lmtb_0_df.csv"))
lmtb_l_df <- data.frame(iread("2026_01_19_lmtb_l_df.csv"))
mtbi_l_df <- data.frame(iread("2025_09_15_mtbi_l_df.csv"))
unij_l_df <- data.frame(iread("2025_09_15_unij_l_df.csv"))

# longitudinal data frames, post-impotation, post-harmonization
all_long_dls_h_ns <- readRDS(proc_path("2026_01_19_all_long_dls_h_ns.rds"))
```


```{r}
mtbi_der_u1 <- as.data.frame(c(all_dls_h_ns$"mtbi_der_u_dls"[[1]], all_dls_h_ns$"mtbi_der_u_ols"[[1]]))
mtbi_der_u2 <- as.data.frame(c(all_dls_h_ns$"mtbi_der_u_dls"[[2]], all_dls_h_ns$"mtbi_der_u_ols"[[2]]))
mtbi_der_u3 <- as.data.frame(c(all_dls_h_ns$"mtbi_der_u_dls"[[3]], all_dls_h_ns$"mtbi_der_u_ols"[[3]]))
mtbi_der_u4 <- as.data.frame(c(all_dls_h_ns$"mtbi_der_u_dls"[[4]], all_dls_h_ns$"mtbi_der_u_ols"[[4]]))
mtbi_der_u5 <- as.data.frame(c(all_dls_h_ns$"mtbi_der_u_dls"[[5]], all_dls_h_ns$"mtbi_der_u_ols"[[5]]))
mtbi_val_u1 <- as.data.frame(c(all_dls_h_ns$"mtbi_val_u_dls"[[1]], all_dls_h_ns$"mtbi_val_u_ols"[[1]]))
mtbi_val_u2 <- as.data.frame(c(all_dls_h_ns$"mtbi_val_u_dls"[[2]], all_dls_h_ns$"mtbi_val_u_ols"[[2]]))
mtbi_val_u3 <- as.data.frame(c(all_dls_h_ns$"mtbi_val_u_dls"[[3]], all_dls_h_ns$"mtbi_val_u_ols"[[3]]))
mtbi_val_u4 <- as.data.frame(c(all_dls_h_ns$"mtbi_val_u_dls"[[4]], all_dls_h_ns$"mtbi_val_u_ols"[[4]]))
mtbi_val_u5 <- as.data.frame(c(all_dls_h_ns$"mtbi_val_u_dls"[[5]], all_dls_h_ns$"mtbi_val_u_ols"[[5]]))

mtbi_der_p1 <- as.data.frame(c(all_dls_h_ns$"mtbi_der_p_dls"[[1]], all_dls_h_ns$"mtbi_der_p_ols"[[1]]))
mtbi_der_p2 <- as.data.frame(c(all_dls_h_ns$"mtbi_der_p_dls"[[2]], all_dls_h_ns$"mtbi_der_p_ols"[[2]]))
mtbi_der_p3 <- as.data.frame(c(all_dls_h_ns$"mtbi_der_p_dls"[[3]], all_dls_h_ns$"mtbi_der_p_ols"[[3]]))
mtbi_der_p4 <- as.data.frame(c(all_dls_h_ns$"mtbi_der_p_dls"[[4]], all_dls_h_ns$"mtbi_der_p_ols"[[4]]))
mtbi_der_p5 <- as.data.frame(c(all_dls_h_ns$"mtbi_der_p_dls"[[5]], all_dls_h_ns$"mtbi_der_p_ols"[[5]]))
mtbi_val_p1 <- as.data.frame(c(all_dls_h_ns$"mtbi_val_p_dls"[[1]], all_dls_h_ns$"mtbi_val_p_ols"[[1]]))
mtbi_val_p2 <- as.data.frame(c(all_dls_h_ns$"mtbi_val_p_dls"[[2]], all_dls_h_ns$"mtbi_val_p_ols"[[2]]))
mtbi_val_p3 <- as.data.frame(c(all_dls_h_ns$"mtbi_val_p_dls"[[3]], all_dls_h_ns$"mtbi_val_p_ols"[[3]]))
mtbi_val_p4 <- as.data.frame(c(all_dls_h_ns$"mtbi_val_p_dls"[[4]], all_dls_h_ns$"mtbi_val_p_ols"[[4]]))
mtbi_val_p5 <- as.data.frame(c(all_dls_h_ns$"mtbi_val_p_dls"[[5]], all_dls_h_ns$"mtbi_val_p_ols"[[5]]))

names(all_dls_h_ns)

mtbi_u1 <- rbind(mtbi_der_u1, mtbi_val_u1)
mtbi_u2 <- rbind(mtbi_der_u2, mtbi_val_u2)
mtbi_u3 <- rbind(mtbi_der_u3, mtbi_val_u3)
mtbi_u4 <- rbind(mtbi_der_u4, mtbi_val_u4)
mtbi_u5 <- rbind(mtbi_der_u5, mtbi_val_u5)
mtbi_p1 <- rbind(mtbi_der_p1, mtbi_val_p1)
mtbi_p2 <- rbind(mtbi_der_p2, mtbi_val_p2)
mtbi_p3 <- rbind(mtbi_der_p3, mtbi_val_p3)
mtbi_p4 <- rbind(mtbi_der_p4, mtbi_val_p4)
mtbi_p5 <- rbind(mtbi_der_p5, mtbi_val_p5)

unij_u_df <- data.frame(
    c(all_dls_h_ns$"unij_all_u_dls"[[1]], all_dls_h_ns$"unij_all_u_ols"[[1]])
)
unij_p_df <- data.frame(
    c(all_dls_h_ns$"unij_all_p_dls"[[1]], all_dls_h_ns$"unij_all_p_ols"[[1]])
)

lmtb_0_df_imp <- c(all_long_dls_h_ns$"lmtb_0_dls"[[1]], all_long_dls_h_ns$"lmtb_0_ols"[[1]]) |> as.data.frame()
lmtb_l_df_imp <- c(all_long_dls_h_ns$"lmtb_l_dls"[[1]], all_long_dls_h_ns$"lmtb_l_ols"[[1]]) |> as.data.frame()
```

```{r}
# Complex helper function to produce summary tables
characterize_feature_prop <- function(df, ft_name, clean, missing = "") {
    if ("latest_mtbi_mechanism" %in% colnames(df)) {
        df$"mtbi_mechanism" <- df$"latest_mtbi_mechanism"
        df$"mtbi_loc" <- df$"latest_mtbi_loc"
        df$"mtbi_mem_daze" <- df$"latest_mtbi_mem_daze"
    }
    if (!"mtbi_mechanism" %in% colnames(df)) {
        df$"mtbi_mechanism" <- "Missing mechanism"
        df$"mtbi_loc" <- "Missing LOC"
    }
    if (ft_name == "household_income") {
        df <- df |>
            dplyr::mutate(
                household_income = dplyr::case_when(
                    household_income == 1 ~ "<$50,000",
                    household_income == 2 ~ "$50,000-$100,000",
                    household_income == 3 ~ ">$100,000",
                    is.na(household_income) ~ "Missing income",
                    TRUE ~ NA
                )
            )
        df$"household_income" <- factor(df$"household_income", levels = c("<$50,000", "$50,000-$100,000", ">$100,000", "Missing income"))
    }
    if (ft_name == "sex") {
        df$"sex"[is.na(df$"sex")] <- "Missing sex"
    }
    ft <- df[[ft_name]]
    count <- table(ft)
    props <- prop.table(count)
    df <- dplyr::inner_join(data.frame(count), data.frame(props), by = "ft") |>
        dplyr::mutate(
            "Frequency" = paste0(Freq.x, " (", round(Freq.y, 2)*100, "%)"),
            .keep = "unused"
        )
    colnames(df)[1] <- clean
    if (ft_name == "sex") {
        df <- df |>
            dplyr::mutate(
                "*Sex*" = dplyr::case_when(
                    `*Sex*` == 0 ~ "F",
                    `*Sex*` == 1 ~ "M",
                    is.na(`*Sex*`) ~ "Missing sex",
                    TRUE ~ `*Sex*`
                )
            )
    }
    if (is.character(ft)) {
        df[[clean]] <- stringr::str_to_sentence(df[[clean]])
        df[[clean]] <- gsub("_loc", " LOC", df[[clean]])
        df[[clean]] <- gsub("Missing loc", "Missing LOC", df[[clean]])
        df[[clean]] <- gsub("Fall_hit", "Fall/hit", df[[clean]])
        df[[clean]] <- gsub("Hosp_er", "Hosp/ER", df[[clean]])
    }
    if (ft_name == "sex") {
        demo_df <- data.frame(
            v1 = c("F", "M", "Missing sex"),
            v2 = c("0 (0%)", "0 (0%)", "0 (0%)")
        )
        colnames(demo_df) <- colnames(df)
        df_vals <- df[, 1]
        demo_df <- demo_df[!demo_df[, 1] %in% df[, 1], ]
        # Move missing row to bottom
        df <- rbind(df, demo_df) %>%
            dplyr::arrange(.[[1]] == "Missing sex")
    }
    if (ft_name == "pubertal_status_p" | ft_name == "pubertal_status_y") {
        demo_df <- data.frame(
            v1 = c("1", "2", "3", "4"),
            v2 = c("0 (0%)", "0 (0%)", "0 (0%)", "0 (0%)")
        )
        colnames(demo_df) <- colnames(df)
        df_vals <- df[, 1]
        demo_df <- demo_df[!demo_df[, 1] %in% df[, 1], ]
        # Move missing row to bottom
        df <- rbind(df, demo_df) %>%
            dplyr::arrange(.[[1]] == "Missing LOC")
    }
    if (ft_name == "mtbi_loc") {
        demo_df <- data.frame(
            v1 = c("0", "1", "Missing LOC"),
            v2 = c("0 (0%)", "0 (0%)", "0 (0%)")
        )
        colnames(demo_df) <- colnames(df)
        df_vals <- df[, 1]
        demo_df <- demo_df[!demo_df[, 1] %in% df[, 1], ]
        # Move missing row to bottom
        df <- rbind(df, demo_df) %>%
            dplyr::arrange(.[[1]] == "Missing LOC")
    }
    if (ft_name == "mtbi_mechanism") {
        demo_df <- data.frame(
            v1 = c("Fall/hit", "Hosp/ER", "Multi", "Other LOC", "Vehicle", "Violent", "Missing mechanism"),
            v2 = c("0 (0%)", "0 (0%)", "0 (0%)", "0 (0%)", "0 (0%)", "0 (0%)", "0 (0%)")
        )
        colnames(demo_df) <- colnames(df)
        df_vals <- df[, 1]
        demo_df <- demo_df[!demo_df[, 1] %in% df[, 1], ]
        # Move missing row to bottom
        df <- rbind(df, demo_df) %>%
            dplyr::arrange(.[[1]] == "Missing mechanism")
    }
    return(
        data.frame(
            label = c(clean, as.character(df[[clean]])),
            value = c("<", df$"Frequency")
        )
    )
}

characterize_feature_mean <- function(df, ft_name, clean, missing = "") {
    if ("previous_mtbis" %in% colnames(df)) {
        df$"mtbi_count" <- df$"previous_mtbis"
    } else {
        if (!"mtbi_count" %in% colnames(df)) {
            df$"mtbi_count" <- 0
            df$"mtbi_age" <- 0
        }
    }
    if ("latest_mtbi_age" %in% colnames(df)) {
        df$"mtbi_age" <- df$"latest_mtbi_age"
    }
    df$"total_impairments" <- df |>
        dplyr::select(dplyr::starts_with("cbcl"), dplyr::starts_with("sds")) |>
        rowSums()
    df$"total_parent_psych" <- df |>
        dplyr::select(dplyr::starts_with("parent")) |>
        rowSums()
    if (ft_name == "age") {
        if ("interview_age" %in% colnames(df)) {
            ft <- df$"interview_age"
        } else {
            ft <- df$"age"
        }
    } else {
        ft <- df[[ft_name]]
    }
    n_missing <- sum(is.na(ft))
    ft <- na.omit(ft)
    x <- signif(mean(ft, na.rm = FALSE), 3)
    s <- signif(sd(ft, na.rm = FALSE), 3)
    l <- min(ft, na.rm = FALSE)
    u <- max(ft, na.rm = FALSE) 
    if (is.character(ft)) {
        df[[clean]] <- gsub("_", " ", df[[clean]])
    }
    df <- data.frame(
            label = c(clean, "Mean (SD)", "Range", paste0("Missing", missing)),
            value = c(
                "<",
                paste0(x, " (", s, ")"),
                paste0(l, " - ", u),
                n_missing
            )
        )
    return(df)
}

sample_characterize <- function(df, name) {
    sex_df <- characterize_feature_prop(df, "sex", "*Sex*")
    age_df <- characterize_feature_mean(df, "age", "*Age (months)*", " age")
    pdy_df <- characterize_feature_prop(df, "pubertal_status_y", "*Pubertal status - YR*")
    pdp_df <- characterize_feature_prop(df, "pubertal_status_p", "*Pubertal status - PR*")
    inc_df <- characterize_feature_prop(df, "household_income", "*Household income*")
    rac_df <- characterize_feature_prop(df, "race", "*Race*")
    cnt_df <- characterize_feature_mean(df, "mtbi_count", "*Prior concussions*", " prior concussions")
    mag_df <- characterize_feature_mean(df, "mtbi_age", "*Age at last injury*", " injury age")
    loc_df <- characterize_feature_prop(df, "mtbi_loc", "*LOC*")
    mec_df <- characterize_feature_prop(df, "mtbi_mechanism", "*Mechanism of injury*", " mechanism")
    #imp_df <- characterize_feature_mean(df, "total_impairments", "*Total CBCL/SDS*", " CBCL/SDS")
    cb1_df <- characterize_feature_mean(df, "cbcl_anxdep", "CBCL Anxious-Depressed")
    cb2_df <- characterize_feature_mean(df, "cbcl_withdep", "CBCL Withdrawn-Depressed")
    cb3_df <- characterize_feature_mean(df, "cbcl_somatic", "CBCL Somatic")
    cb4_df <- characterize_feature_mean(df, "cbcl_social", "CBCL Social")
    cb5_df <- characterize_feature_mean(df, "cbcl_thought", "CBCL Thought")
    cb6_df <- characterize_feature_mean(df, "cbcl_attention", "CBCL Attention")
    cb7_df <- characterize_feature_mean(df, "cbcl_rulebreak", "CBCL Rule-breaking")
    cb8_df <- characterize_feature_mean(df, "cbcl_aggressive", "CBCL Aggressive")
    sds_df <- characterize_feature_mean(df, "sds_sleep", "SDS Total Sleep Problems")
    n_df <- data.frame(
        label = "*N*",
        value = nrow(df)
    )
    new_df <- list(
            n_df,
            sex_df,
            age_df,
            pdy_df,
            pdp_df,
            inc_df,
            rac_df,
            cnt_df,
            mag_df,
            loc_df,
            mec_df,
            cb1_df,
            cb2_df,
            cb3_df,
            cb4_df,
            cb5_df,
            cb6_df,
            cb7_df,
            cb8_df,
            sds_df
        ) |>
        do.call(what = rbind)
    colnames(new_df) <- c("", name)
    return(new_df)
}
```

```{r}
mtbi_0_df <- rbind(mtbi_der_u1, mtbi_val_u1)
mtbi_l_df <- data.frame(
    c(
        all_long_dls_h_ns$"mtbi_l_dls"[[1]],
        all_long_dls_h_ns$"mtbi_l_ols"[[1]]
    )
)

best_matched_uninjured_df <- readRDS(proc_path("2025_10_03_best_matched_uninjured_df.rds"))
random_unij_1_df <- readRDS(proc_path("2025_10_03_random_unij_1_df.rds"))
```

```{r}
mtbi_0_characterized <- sample_characterize(mtbi_0_df, "BC T0")
mtbi_l_characterized <- sample_characterize(mtbi_l_df, "BC T2")
unij_0_characterized <- sample_characterize(unij_u_df, "BU T0")
lmtb_0_characterized <- sample_characterize(lmtb_0_df_imp, "LC T0")
lmtb_l_characterized <- sample_characterize(lmtb_l_df_imp, "LC T2")
bunj_0_characterized <- sample_characterize(best_matched_uninjured_df, "BMU T0")
runj_0_characterized <- sample_characterize(random_unij_1_df, "RMU T0")

merged <- cbind(
    mtbi_0_characterized,
    mtbi_l_characterized[, 2],
    unij_0_characterized[, 2],
    bunj_0_characterized[, 2],
    runj_0_characterized[, 2],
    lmtb_0_characterized[, 2],
    lmtb_l_characterized[, 2]
)
colnames(merged) <- c("Feature", "BC T0", "BC T2", "BU T0", "BMU T0", "RMU T0", "LC T0", "LC T2")

merged |>
    knitr::kable(format = "markdown")
 
options(width = 200)
```

|Feature                   |BC T0        |BC T2       |BU T0        |BMU T0      |RMU T0      |LC T0        |LC T2        |
|:-------------------------|:------------|:-----------|:------------|:-----------|:-----------|:------------|:------------|
|*N*                       |438          |403         |7905         |438         |438         |217          |217          |
|*Sex*                     |<            |<           |<            |<           |<           |<            |<            |
|F                         |171 (39%)    |162 (40%)   |3949 (50%)   |168 (38%)   |229 (52%)   |85 (39%)     |85 (39%)     |
|M                         |267 (61%)    |241 (60%)   |3956 (50%)   |270 (62%)   |209 (48%)   |132 (61%)    |132 (61%)    |
|*Age (months)*            |<            |<           |<            |<           |<           |<            |<            |
|Mean (SD)                 |120 (7.47)   |145 (8.06)  |119 (7.44)   |120 (7.5)   |118 (7.34)  |120 (7.51)   |145 (7.81)   |
|Range                     |107 - 132    |127 - 165   |107 - 133    |107 - 133   |107 - 132   |107 - 131    |129 - 166    |
|*Pubertal status - YR*    |<            |<           |<            |<           |<           |<            |<            |
|1                         |136 (31%)    |55 (14%)    |2203 (28%)   |132 (30%)   |130 (30%)   |66 (30%)     |30 (14%)     |
|2                         |169 (39%)    |113 (28%)   |2961 (37%)   |166 (38%)   |167 (38%)   |81 (37%)     |68 (31%)     |
|3                         |133 (30%)    |156 (39%)   |2741 (35%)   |140 (32%)   |141 (32%)   |70 (32%)     |80 (37%)     |
|4                         |0 (0%)       |79 (20%)    |0 (0%)       |0 (0%)      |0 (0%)      |0 (0%)       |39 (18%)     |
|*Pubertal status - PR*    |<            |<           |<            |<           |<           |<            |<            |
|1                         |231 (53%)    |86 (21%)    |3853 (49%)   |231 (53%)   |216 (49%)   |129 (59%)    |43 (20%)     |
|2                         |108 (25%)    |94 (23%)    |1890 (24%)   |105 (24%)   |111 (25%)   |49 (23%)     |62 (29%)     |
|3                         |99 (23%)     |135 (33%)   |2162 (27%)   |102 (23%)   |111 (25%)   |39 (18%)     |69 (32%)     |
|4                         |0 (0%)       |88 (22%)    |0 (0%)       |0 (0%)      |0 (0%)      |0 (0%)       |43 (20%)     |
|*Household income*        |<            |<           |<            |<           |<           |<            |<            |
|<$50,000                  |102 (23%)    |82 (20%)    |2631 (33%)   |99 (23%)    |162 (37%)   |35 (16%)     |38 (18%)     |
|$50,000-$100,000          |122 (28%)    |102 (25%)   |2203 (28%)   |122 (28%)   |108 (25%)   |70 (32%)     |47 (22%)     |
|>$100,000                 |214 (49%)    |219 (54%)   |3071 (39%)   |217 (50%)   |168 (38%)   |112 (52%)    |132 (61%)    |
|*Race*                    |<            |<           |<            |<           |<           |<            |<            |
|Black                     |38 (9%)      |30 (7%)     |1307 (17%)   |36 (8%)     |79 (18%)    |18 (8%)      |18 (8%)      |
|Hispanic                  |70 (16%)     |63 (16%)    |1714 (22%)   |68 (16%)    |97 (22%)    |30 (14%)     |30 (14%)     |
|Other                     |50 (11%)     |47 (12%)    |1008 (13%)   |47 (11%)    |52 (12%)    |30 (14%)     |30 (14%)     |
|White                     |280 (64%)    |263 (65%)   |3876 (49%)   |287 (66%)   |210 (48%)   |139 (64%)    |139 (64%)    |
|*Prior concussions*       |<            |<           |<            |<           |<           |<            |<            |
|Mean (SD)                 |1.32 (0.508) |0 (0)       |0 (0)        |0 (0)       |0 (0)       |0 (0)        |1.37 (0.588) |
|Range                     |1 - 3        |0 - 0       |0 - 0        |0 - 0       |0 - 0       |0 - 0        |1 - 4        |
|*Age at last injury*      |<            |<           |<            |<           |<           |<            |<            |
|Mean (SD)                 |74.1 (32.7)  |0 (0)       |0 (0)        |0 (0)       |0 (0)       |0 (0)        |129 (10.7)   |
|Range                     |0 - 120      |0 - 0       |0 - 0        |0 - 0       |0 - 0       |0 - 0        |108 - 156    |
|*LOC*                     |<            |<           |<            |<           |<           |<            |<            |
|0                         |316 (72%)    |0 (0%)      |0 (0%)       |0 (0%)      |0 (0%)      |0 (0%)       |164 (76%)    |
|1                         |122 (28%)    |0 (0%)      |0 (0%)       |0 (0%)      |0 (0%)      |0 (0%)       |53 (24%)     |
|Missing LOC               |0 (0%)       |403 (100%)  |7905 (100%)  |438 (100%)  |438 (100%)  |217 (100%)   |0 (0%)       |
|*Mechanism of injury*     |<            |<           |<            |<           |<           |<            |<            |
|Fall/hit                  |135 (31%)    |0 (0%)      |0 (0%)       |0 (0%)      |0 (0%)      |0 (0%)       |89 (41%)     |
|Hosp/ER                   |273 (62%)    |0 (0%)      |0 (0%)       |0 (0%)      |0 (0%)      |0 (0%)       |103 (47%)    |
|Multi                     |3 (1%)       |0 (0%)      |0 (0%)       |0 (0%)      |0 (0%)      |0 (0%)       |9 (4%)       |
|Other LOC                 |6 (1%)       |0 (0%)      |0 (0%)       |0 (0%)      |0 (0%)      |0 (0%)       |13 (6%)      |
|Vehicle                   |16 (4%)      |0 (0%)      |0 (0%)       |0 (0%)      |0 (0%)      |0 (0%)       |3 (1%)       |
|Violent                   |5 (1%)       |0 (0%)      |0 (0%)       |0 (0%)      |0 (0%)      |0 (0%)       |0 (0%)       |
|Missing mechanism         |0 (0%)       |403 (100%)  |7905 (100%)  |438 (100%)  |438 (100%)  |217 (100%)   |0 (0%)       |
|CBCL Anxious-Depressed    |<            |<           |<            |<           |<           |<            |<            |
|Mean (SD)                 |3.45 (3.77)  |2.94 (3.7)  |2.39 (2.96)  |3 (3.29)    |2.45 (3.14) |2.95 (3.3)   |3.12 (3.71)  |
|Range                     |0 - 26       |0 - 21      |0 - 25       |0 - 17      |0 - 25      |0 - 22       |0 - 21       |
|CBCL Withdrawn-Depressed  |<            |<           |<            |<           |<           |<            |<            |
|Mean (SD)                 |1.41 (2.16)  |1.43 (2.33) |0.999 (1.66) |1.21 (1.75) |1.05 (1.87) |0.871 (1.56) |1.2 (1.91)   |
|Range                     |0 - 14       |0 - 13      |0 - 15       |0 - 11      |0 - 13      |0 - 10       |0 - 11       |
|CBCL Somatic              |<            |<           |<            |<           |<           |<            |<            |
|Mean (SD)                 |2.28 (2.5)   |2.04 (2.46) |1.42 (1.88)  |1.66 (2.02) |1.29 (1.79) |1.78 (2.08)  |1.74 (2.14)  |
|Range                     |0 - 15       |0 - 12      |0 - 16       |0 - 11      |0 - 13      |0 - 11       |0 - 13       |
|CBCL Social               |<            |<           |<            |<           |<           |<            |<            |
|Mean (SD)                 |2.51 (3.21)  |1.75 (2.52) |1.52 (2.16)  |1.87 (2.44) |1.66 (2.34) |1.66 (2.24)  |1.81 (2.47)  |
|Range                     |0 - 18       |0 - 15      |0 - 17       |0 - 12      |0 - 14      |0 - 11       |0 - 17       |
|CBCL Thought              |<            |<           |<            |<           |<           |<            |<            |
|Mean (SD)                 |2.51 (3.03)  |1.91 (2.36) |1.52 (2.08)  |1.99 (2.45) |1.44 (1.99) |1.89 (2.19)  |1.75 (2.35)  |
|Range                     |0 - 18       |0 - 13      |0 - 17       |0 - 17      |0 - 13      |0 - 10       |0 - 15       |
|CBCL Attention            |<            |<           |<            |<           |<           |<            |<            |
|Mean (SD)                 |4.18 (4.37)  |3.63 (3.85) |2.86 (3.38)  |3.51 (3.64) |2.81 (3.5)  |2.98 (3.22)  |2.93 (3.49)  |
|Range                     |0 - 20       |0 - 19      |0 - 19       |0 - 19      |0 - 17      |0 - 15       |0 - 14       |
|CBCL Rule-breaking        |<            |<           |<            |<           |<           |<            |<            |
|Mean (SD)                 |1.66 (2.45)  |1.4 (2.28)  |1.13 (1.77)  |1.43 (2.02) |1.15 (1.92) |1.21 (1.76)  |1.32 (1.88)  |
|Range                     |0 - 20       |0 - 23      |0 - 17       |0 - 14      |0 - 13      |0 - 11       |0 - 9        |
|CBCL Aggressive           |<            |<           |<            |<           |<           |<            |<            |
|Mean (SD)                 |4.87 (5.73)  |3.78 (4.68) |3.02 (4.08)  |3.72 (4.82) |3.15 (4.42) |3.36 (3.87)  |3.39 (4.2)   |
|Range                     |0 - 26       |0 - 26      |0 - 36       |0 - 32      |0 - 25      |0 - 19       |0 - 23       |
|SDS Total Sleep Problems  |<            |<           |<            |<           |<           |<            |<            |
|Mean (SD)                 |39.4 (9.81)  |38.7 (10)   |36.3 (8.05)  |37.5 (8.44) |36.3 (7.67) |37.7 (7.74)  |38.3 (8.08)  |
|Range                     |26 - 95      |26 - 103    |26 - 126     |26 - 85     |26 - 76     |26 - 66      |26 - 65      |

Stats comparing baseline concussion sample with baseline uninjured sample:

```{r}
colnames(mtbi_0_df)
colnames(unij_u_df)

sum(mtbi_0_df$"sex")
sum(unij_u_df$"sex")

run_stats <- function(df1, df2) {
    sex_stats <- calc_propes(df1$"sex", df2$"sex")
    cat(
        "\nSex (> 1 means df1 has more males):",
        "\n    OR: ", sex_stats$"es", " [", sex_stats$"l", ", ", sex_stats$"u", "]\n",
        sep = ""
    )
    # D 0.14 [0.04, 0.23] p = 0.01
    age_stats <- calc_des_wp(df1$"age", df2$"age")
    cat(
        "\nage (+d means df1 is older):",
        "\n    d: ", age_stats$"es", " [", age_stats$"l", ", ", age_stats$"u", "]",
        "\n    p: ", age_stats$"p", "\n",
        sep = ""
    )
    # D -0.1 [-0.19, 0] p = 0.05 (n.s.)
    pds_stats <- calc_des_wp(df1$"pubertal_status_y", df2$"pubertal_status_y")
    cat(
        "\npds (+d means df1 is higher pds):",
        "\n    d: ", pds_stats$"es", " [", pds_stats$"l", ", ", pds_stats$"u", "]",
        "\n    p: ", pds_stats$"p", "\n",
        sep = ""
    )
    # D 0.24 [0.14, 0.33] p < 0.01
    # positive D means first sample higher
    income_stats <- calc_des_wp(df1$"household_income", df2$"household_income")
    cat(
        "\nincome (+d means df1 is higher income):",
        "\n    d: ", income_stats$"es", " [", income_stats$"l", ", ", income_stats$"u", "]",
        "\n    p: ", income_stats$"p", "\n",
        sep = ""
    )
    # OR 1.84 [1.51, 2.25]
    race_white_stats <- calc_propes(
        pull(dummy_cols(df1, select_columns = "race"), race_white),
        pull(dummy_cols(df2, select_columns = "race"), race_white)
    )
    cat(
        "\n% white (> 1 means df1 has more % white):",
        "\n    OR: ", race_white_stats$"es", " [", race_white_stats$"l", ", ", race_white_stats$"u", "]\n",
        sep = ""
    )
    # OR 0.48 [0.34, 0.67]
    race_black_stats <- calc_propes(
        pull(dummy_cols(df1, select_columns = "race"), race_black),
        pull(dummy_cols(df2, select_columns = "race"), race_black)
    )
    cat(
        "\n% black (> 1 means df1 has more % black):",
        "\n    OR: ", race_black_stats$"es", " [", race_black_stats$"l", ", ", race_black_stats$"u", "]\n",
        sep = ""
    )
    # OR 0.69 [0.53, 0.89]
    race_hispanic_stats <- calc_propes(
        pull(dummy_cols(df1, select_columns = "race"), race_hispanic),
        pull(dummy_cols(df2, select_columns = "race"), race_hispanic)
    )
    cat(
        "\n% hispanic (> 1 means df1 has more % hispanic):",
        "\n    OR: ", race_hispanic_stats$"es", " [", race_hispanic_stats$"l", ", ", race_hispanic_stats$"u", "]\n",
        sep = ""
    )
    # OR 0.88 [0.65, 1.19] n.s.
    race_other_stats <- calc_propes(
        pull(dummy_cols(df1, select_columns = "race"), race_other),
        pull(dummy_cols(df2, select_columns = "race"), race_other)
    )
    cat(
        "\n% other (> 1 means df1 has more % other):",
        "\n    OR: ", race_other_stats$"es", " [", race_other_stats$"l", ", ", race_other_stats$"u", "]\n",
        sep = ""
    )
    # 0.51 [0.42, 0.61], p < 0.01
    impairment_stats <- calc_des_wp(
        rowSums(dplyr::select(df1, dplyr::starts_with("cbcl"), dplyr::starts_with("sds"))),
        rowSums(dplyr::select(df2, dplyr::starts_with("cbcl"), dplyr::starts_with("sds")))
    )
    cat(
        "\nimpairment (+d means df1 is higher impairment):",
        "\n    d: ", impairment_stats$"es", " [", impairment_stats$"l", ", ", impairment_stats$"u", "]",
        "\n    p: ", impairment_stats$"p", "\n",
        sep = ""
    )
}

# mTBI vs. unij:
run_stats(mtbi_0_df, unij_u_df)

mtbi_m <- dplyr::filter(mtbi_0_df, sex == 1)
mtbi_f <- dplyr::filter(mtbi_0_df, sex == 0)
unij_m <- dplyr::filter(unij_u_df, sex == 1)
unij_f <- dplyr::filter(unij_u_df, sex == 0)

# d: 0.1 [-0.09, 0.3], p = 0.29
run_stats(mtbi_m, mtbi_f)

# d: 0.15 [0.11, 0.19], p < 0.01
run_stats(unij_m, unij_f)

n_mtbi_m <- nrow(mtbi_m)
n_mtbi_f <- nrow(mtbi_m)
n_unij_m <- nrow(unij_m)
n_unij_f <- nrow(unij_m)

set.seed(42)
perm_diffs <- vector(mode = "numeric", length = 1000)
mtbi_m_x <- rowSums(dplyr::select(mtbi_m, dplyr::starts_with("cbcl"), dplyr::starts_with("sds")))
mtbi_f_x <- rowSums(dplyr::select(mtbi_f, dplyr::starts_with("cbcl"), dplyr::starts_with("sds")))
unij_m_x <- rowSums(dplyr::select(unij_m, dplyr::starts_with("cbcl"), dplyr::starts_with("sds")))
unij_f_x <- rowSums(dplyr::select(unij_f, dplyr::starts_with("cbcl"), dplyr::starts_with("sds")))
m_pool <- c(mtbi_m_x, unij_m_x)
f_pool <- c(mtbi_f_x, unij_f_x)
for (i in 1:1000) {
    m_perm <- sample(m_pool)
    f_perm <- sample(f_pool)
    mock_mtbi_m <- m_perm[1:n_mtbi_m]
    mock_mtbi_f <- f_perm[1:n_mtbi_f]
    mock_unij_m <- m_perm[(1 + n_mtbi_m):length(m_perm)]
    mock_unij_f <- f_perm[(1 + n_mtbi_f):length(f_perm)]
    mtbi_m_worse <- calc_des_wp(mock_mtbi_m, mock_mtbi_f)$"es" # positive means m worse
    unij_m_worse <- calc_des_wp(mock_unij_m, mock_unij_f)$"es" # positive means m worse
    diff <- unij_m_worse - mtbi_m_worse # positive means m more worse in unij
    perm_diffs[i] <- diff
}
mtbi_m_worse <- calc_des_wp(mtbi_m_x, mtbi_f_x)$"es"
unij_m_worse <- calc_des_wp(unij_m_x, unij_f_x)$"es"
observed_diff <- unij_m_worse - mtbi_m_worse
print(out)
print(mean(observed_diff < perm_diffs)) # 0.307
```

So it's not significantly different.

What about for individual features?

```{r}
outs <- colnames(dplyr::select(mtbi_m, dplyr::starts_with("cbcl"), dplyr::starts_with("sds")))
outs
# check individual features
out_df <- data.frame()
for (out in outs) {
    mtbi_m_x <- rowSums(dplyr::select(mtbi_m, all_of(out)))
    mtbi_f_x <- rowSums(dplyr::select(mtbi_f, all_of(out)))
    unij_m_x <- rowSums(dplyr::select(unij_m, all_of(out)))
    unij_f_x <- rowSums(dplyr::select(unij_f, all_of(out)))
    m_pool <- c(mtbi_m_x, unij_m_x)
    f_pool <- c(mtbi_f_x, unij_f_x)
    for (i in 1:1000) {
        m_perm <- sample(m_pool)
        f_perm <- sample(f_pool)
        mock_mtbi_m <- m_perm[1:n_mtbi_m]
        mock_mtbi_f <- f_perm[1:n_mtbi_f]
        mock_unij_m <- m_perm[(1 + n_mtbi_m):length(m_perm)]
        mock_unij_f <- f_perm[(1 + n_mtbi_f):length(f_perm)]
        mtbi_m_worse <- calc_des_wp(mock_mtbi_m, mock_mtbi_f)$"es" # positive means m worse
        unij_m_worse <- calc_des_wp(mock_unij_m, mock_unij_f)$"es" # positive means m worse
        diff <- unij_m_worse - mtbi_m_worse # positive means m more worse in unij
        perm_diffs[i] <- diff
    }
    mtbi_m_worse <- calc_des_wp(mtbi_m_x, mtbi_f_x)$"es"
    unij_m_worse <- calc_des_wp(unij_m_x, unij_f_x)$"es"
    observed_diff <- unij_m_worse - mtbi_m_worse
    print(out)
    print(mean(observed_diff < perm_diffs))
    print("----")
    out_df <- rbind(out_df, data.frame(outcome = out, p = mean(observed_diff < perm_diffs)))
}
```

Maybe need to adjust for race?

```{r}

mtbi_0_df$"group" <- "mtbi"
unij_u_df$"group" <- "unij"

joint_df <- rbind(mtbi_0_df[, colnames(unij_u_df)], unij_u_df)

joint_df$"race" <- factor(joint_df$"race")

model <- lm(outs[1] ~ race, data = joint_df)

for (out in outs) {
    model <- lm(as.formula(paste0(out, " ~ race")), data = joint_df)
    joint_df[, out] <- resid(model)
}

mtbi_m_adj <- dplyr::filter(joint_df, sex == 1, group == "mtbi")
mtbi_f_adj <- dplyr::filter(joint_df, sex == 0, group == "mtbi")
unij_m_adj <- dplyr::filter(joint_df, sex == 1, group == "unij")
unij_f_adj <- dplyr::filter(joint_df, sex == 0, group == "unij")

n_mtbi_m <- nrow(mtbi_m)
n_mtbi_f <- nrow(mtbi_m)
n_unij_m <- nrow(unij_m)
n_unij_f <- nrow(unij_m)

set.seed(42)
perm_diffs_adj <- vector(mode = "numeric", length = 1000)
mtbi_m_x_adj <- rowSums(dplyr::select(mtbi_m_adj, dplyr::starts_with("cbcl"), dplyr::starts_with("sds")))
mtbi_f_x_adj <- rowSums(dplyr::select(mtbi_f_adj, dplyr::starts_with("cbcl"), dplyr::starts_with("sds")))
unij_m_x_adj <- rowSums(dplyr::select(unij_m_adj, dplyr::starts_with("cbcl"), dplyr::starts_with("sds")))
unij_f_x_adj <- rowSums(dplyr::select(unij_f_adj, dplyr::starts_with("cbcl"), dplyr::starts_with("sds")))
m_pool_adj <- c(mtbi_m_x_adj, unij_m_x_adj)
f_pool_adj <- c(mtbi_f_x_adj, unij_f_x_adj)
for (i in 1:1000) {
    m_perm_adj <- sample(m_pool_adj)
    f_perm_adj <- sample(f_pool_adj)
    mock_mtbi_m_adj <- m_perm_adj[1:n_mtbi_m]
    mock_mtbi_f_adj <- f_perm_adj[1:n_mtbi_f]
    mock_unij_m_adj <- m_perm_adj[(1 + n_mtbi_m):length(m_perm_adj)]
    mock_unij_f_adj <- f_perm_adj[(1 + n_mtbi_f):length(f_perm_adj)]
    mtbi_m_worse_adj <- calc_des_wp(mock_mtbi_m_adj, mock_mtbi_f_adj)$"es" # positive means m worse
    unij_m_worse_adj <- calc_des_wp(mock_unij_m_adj, mock_unij_f_adj)$"es" # positive means m worse
    diff_adj <- unij_m_worse_adj - mtbi_m_worse_adj # positive means m more worse in unij
    perm_diffs_adj[i] <- diff_adj
}
mtbi_m_worse_adj <- calc_des_wp(mtbi_m_x_adj, mtbi_f_x_adj)$"es"
unij_m_worse_adj <- calc_des_wp(unij_m_x_adj, unij_f_x_adj)$"es"
observed_diff_adj <- unij_m_worse_adj - mtbi_m_worse_adj
print(mean(observed_diff_adj < perm_diffs_adj))

m_pool_adj |> mean()
f_pool_adj |> mean()

observed_diff_adj # 0.292
```

These analyses indicate that the M vs. F overall outcome measures at baseline are worse in M than F regardless of mTBI or uninjured status, and that this gap is not bigger in the injured group than the uninjured group.


Validating the sentence:

"the differences between the subtypes across outcome measures far exceeds ABCD-wide effects of sex, suggesting that sex at birth alone does not nearly fully explain the inter-subtype variation in outcomes."


```{r}
import <- function(path) {
    return(abcd_load(core_path(path)))
}
```

```{r}
mh_p_cbcl <- import("mental-health/mh_p_cbcl.csv")
ph_p_sds <- import("physical-health/ph_p_sds.csv")
gish_p_gi <- import("gender-identity-sexual-health/gish_p_gi.csv")


cbcl <- get_cbcl_syndrome_scale(mh_p_cbcl, raw = TRUE, t = 0)
sds <- get_sleep_disturbance(ph_p_sds, t = 0)
sex <- get_sex(gish_p_gi, t = 0, as_numeric = TRUE, only_m_f = TRUE)

my_df <- dplyr::inner_join(cbcl, sds, by = "subjectkey") |>
    dplyr::inner_join(sex, by = "subjectkey") |>
    na.omit()

m_df <- dplyr::filter(my_df, sex == 1)
f_df <- dplyr::filter(my_df, sex == 0)

colnames(my_df)

nrow(my_df)

calc_des_wp(m_df$"sds_p_ss_total", f_df$"sds_p_ss_total")

for (i in colnames(my_df)[2:10]) {
    print(paste0(i, " - ", calc_des_wp(m_df[, i], f_df[, i])$"es"))
}

calc_des_wp(m_df$"cbcl_scr_syn_aggressive_r", f_df$"cbcl_scr_syn_aggressive_r")

mean(m_df$"cbcl_scr_syn_attention_r")

mean(f_df$"cbcl_scr_syn_attention_r")
```
