
Is there something in the correlation structure of these samples that determines whether or not cluster analysis can find the baseline concussion solution?

```{r}
library(abcdutils)
library(circlize)
library(ComplexHeatmap)
library(dplyr)
library(fastDummies)
library(ggplot2)
library(here)
library(metasnf)
library(mice)
library(patchwork)
library(randomForest)
library(readr)
library(rlist)
library(tidyr)
library(visdat)

core_path <- path_maker(here(paste0("data/abcd/core")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
input_path <- path_maker(here(paste0("data/abcd/inputs")))
model_path <- path_maker(here(paste0("data/abcd/results/models")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
```

```{r}
calculate_cor_mat <- function(df, method, fisher_z = FALSE) {
    df <- df |>
    data.frame() |>
    dplyr::select(-uid) |>
    dummy_cols(
        select_columns = c("race"),
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = TRUE
    )
    if (method == "spearman") {
        future::plan("multisession")
        n <- ncol(df)
        spearman_mat <- matrix(NA, n, n)
        colnames(spearman_mat) <- rownames(spearman_mat) <- colnames(df)
        results <- pbapply::pblapply(
            1:n,
            function(i) {
                sapply(
                    i:ncol(df),
                    function(j) {
                        cor(df[[i]], df[[j]], method = "spearman")
                    }
                )
            },
            cl = future::availableCores()
        )
        for (i in 1:n) {
            spearman_mat[i, i:n] <- results[[i]]
            spearman_mat[i:n, i] <- results[[i]]
        }
        mat <- spearman_mat
        future::plan("sequential")
    } else if (method == "pearson") {
        mat <- cor(df, method = "pearson")
    }
    if (fisher_z) {
        mat <- atanh(mat) 
    }
    diag(mat) <- NA
    return(mat)
}

permutation_test_corrs <- function(df1, df2, method, fisher_z, perms) {
    cor1 <- calculate_cor_mat(df1, method, fisher_z)
    nofts <- colnames(cor1)[!colnames(cor1) %in% ofts]
    cor1 <- cor1[ofts, nofts]
    cor2 <- calculate_cor_mat(df2, method, fisher_z)[ofts, nofts]
    observed_diff <- mean(abs(cor1 - cor2), na.rm = TRUE)
    perm_diffs <- numeric(perms)
    n1 <- nrow(df1)
    n2 <- nrow(df2)
    n <- n1 + n2
    for (i in 1:perms) {
        merged_df <- rbind(df1, df2)[sample(n), ]
        perm_cor1 <- calculate_cor_mat(merged_df[1:n1, ], method, fisher_z)[ofts, nofts]
        perm_cor2 <- calculate_cor_mat(merged_df[(n1+1):n, ], method, fisher_z)[ofts, nofts]
        perm_diffs[i] <- mean(abs(perm_cor1 - perm_cor2), na.rm = TRUE)
    }
    p_value <- mean(perm_diffs >= observed_diff)
    return(
        list(
            observed_diff = observed_diff,
            p_value = p_value,
            perm_diffs = perm_diffs
        )
    )
}


permutation_test_corrs2 <- function(df1, df2, method, fisher_z, perms) {
    cor1 <- calculate_cor_mat(df1, method, fisher_z)
    nofts <- colnames(cor1)[!colnames(cor1) %in% ofts]
    cor1 <- cor1[ofts, nofts]
    cor2 <- calculate_cor_mat(df2, method, fisher_z)[ofts, nofts]
    observed_diff <- mean(abs(cor1 - cor2), na.rm = TRUE)
    n1 <- nrow(df1)
    n2 <- nrow(df2)
    n <- n1 + n2
    future::plan(future::multisession, workers = future::availableCores())
    perm_diffs <- future.apply::future_lapply(
        seq_len(perms),
        future.seed = TRUE,
        function(i) {
            merged_df <- rbind(df1, df2)[sample(n), ]
            perm_cor1 <- calculate_cor_mat(merged_df[1:n1, ], method, fisher_z)[ofts, nofts]
            perm_cor2 <- calculate_cor_mat(merged_df[(n1+1):n, ], method, fisher_z)[ofts, nofts]
            return(mean(abs(perm_cor1 - perm_cor2), na.rm = TRUE))
        }
    ) |> unlist()
    future::plan("sequential")
    p_value <- mean(perm_diffs >= observed_diff)
    return(
        list(
            observed_diff = observed_diff,
            p_value = p_value,
            perm_diffs = perm_diffs
        )
    )
}

plot_cor_mat_diffs <- function(cmat1, cmat2) {
    cor_mat <- abs(cmat1 - cmat2)
    diag(cor_mat) <- 0
    col_fn <- colorRamp2(c(0, max(cor_mat, na.rm = TRUE)), c("white", "red"))
    no_fts <- colnames(cor_mat)[!colnames(cor_mat) %in% ofts]
    cor_mat <- cor_mat[no_fts, ofts]
    cor_mat <- cor_mat[names(sort(-rowSums(cor_mat))), ]
    return(
        list(
            plot = ComplexHeatmap::Heatmap(
                cor_mat,
                cluster_rows = FALSE,
                cluster_columns = FALSE,
                col = col_fn
            ),
            mat = cor_mat
        )
    )
}
```

I'll try to compare matrices under the following schemes:

- baseline concussion data vs...
    - A. 10 random uninjured samples
    - B. the best matched uninjured sample
    - C. the pre-injury sample data
    - D. the post-injury sample data

I'll do the comparisons the following ways:

- permutation testing mean absolute difference in spearman correlations
- permutation testing mean absolute difference in pearson correlations
- permutation testing mean absolute difference in z-transformed pearson correlations

```{r}
# Data
random_unij_dl_u1 <- readRDS(proc_path("2025_06_15_random_unij_dl_u1.rds"))
all_dls_h_ns <- readRDS(proc_path("2025_06_11_all_dls_h_no_sibs.rds"))
unij_dl_u1 <- all_dls_h_ns$"unij_all_u_dls"$"imp_1"
unij_ol_u1 <- all_dls_h_ns$"unij_all_u_ols"$"imp_1"
matched_unij_dl_do_u <- readRDS(proc_path("2025_06_15_matched_unij_dl_do_u.rds"))
matched_unij_ol_do_u <- readRDS(proc_path("2025_06_15_matched_unij_ol_do_u.rds"))
all_long_dls_h_ns <- readRDS(proc_path("2025_06_13_all_long_dls_h_ns.rds"))

subject_filter_dl <- function(data_list, subject_vector) {
    data_list <- data_list |>
        dlapply(
            function(x) {
                keep_subs <- x$"data"$"uid" %in% subject_vector
                x$"data" <- x$"data"[keep_subs, ]
                return(x)
            }
        )
    return(data_list)
}

# A
set.seed(42)
random_unij_subs_01 <- sample(uids(unij_dl_u1))[1:434]
random_unij_subs_02 <- sample(uids(unij_dl_u1))[1:434]
random_unij_subs_03 <- sample(uids(unij_dl_u1))[1:434]
random_unij_subs_04 <- sample(uids(unij_dl_u1))[1:434]
random_unij_subs_05 <- sample(uids(unij_dl_u1))[1:434]
random_unij_subs_06 <- sample(uids(unij_dl_u1))[1:434]
random_unij_subs_07 <- sample(uids(unij_dl_u1))[1:434]
random_unij_subs_08 <- sample(uids(unij_dl_u1))[1:434]
random_unij_subs_09 <- sample(uids(unij_dl_u1))[1:434]
random_unij_subs_10 <- sample(uids(unij_dl_u1))[1:434]

random_unij_1 <- subject_filter_dl(c(unij_dl_u1, unij_ol_u1), random_unij_subs_01)
random_unij_2 <- subject_filter_dl(c(unij_dl_u1, unij_ol_u1), random_unij_subs_02)
random_unij_3 <- subject_filter_dl(c(unij_dl_u1, unij_ol_u1), random_unij_subs_03)
random_unij_4 <- subject_filter_dl(c(unij_dl_u1, unij_ol_u1), random_unij_subs_04)
random_unij_5 <- subject_filter_dl(c(unij_dl_u1, unij_ol_u1), random_unij_subs_05)
random_unij_6 <- subject_filter_dl(c(unij_dl_u1, unij_ol_u1), random_unij_subs_06)
random_unij_7 <- subject_filter_dl(c(unij_dl_u1, unij_ol_u1), random_unij_subs_07)
random_unij_8 <- subject_filter_dl(c(unij_dl_u1, unij_ol_u1), random_unij_subs_08)
random_unij_9 <- subject_filter_dl(c(unij_dl_u1, unij_ol_u1), random_unij_subs_09)
random_unij_10 <- subject_filter_dl(c(unij_dl_u1, unij_ol_u1), random_unij_subs_10)

random_unij_1_df <- as.data.frame(random_unij_1)
random_unij_2_df <- as.data.frame(random_unij_2)
random_unij_3_df <- as.data.frame(random_unij_3)
random_unij_4_df <- as.data.frame(random_unij_4)
random_unij_5_df <- as.data.frame(random_unij_5)
random_unij_6_df <- as.data.frame(random_unij_6)
random_unij_7_df <- as.data.frame(random_unij_7)
random_unij_8_df <- as.data.frame(random_unij_8)
random_unij_9_df <- as.data.frame(random_unij_9)
random_unij_10_df <- as.data.frame(random_unij_10)

saveRDS(random_unij_1_df, proc_path("random_unij_1_df.rds", TRUE))
saveRDS(random_unij_2_df, proc_path("random_unij_2_df.rds", TRUE))
saveRDS(random_unij_3_df, proc_path("random_unij_3_df.rds", TRUE))
saveRDS(random_unij_4_df, proc_path("random_unij_4_df.rds", TRUE))
saveRDS(random_unij_5_df, proc_path("random_unij_5_df.rds", TRUE))
saveRDS(random_unij_6_df, proc_path("random_unij_6_df.rds", TRUE))
saveRDS(random_unij_7_df, proc_path("random_unij_7_df.rds", TRUE))
saveRDS(random_unij_8_df, proc_path("random_unij_8_df.rds", TRUE))
saveRDS(random_unij_9_df, proc_path("random_unij_9_df.rds", TRUE))
saveRDS(random_unij_10_df, proc_path("random_unij_10_df.rds", TRUE))

# B
best_matched_uninjured_df <- as.data.frame(
    c(matched_unij_dl_do_u, matched_unij_ol_do_u)
)
saveRDS(best_matched_uninjured_df, proc_path("best_matched_uninjured_df.rds", TRUE))

# C
saveRDS(
    as.data.frame(
        c(
            all_long_dls_h_ns$"lmtb_0_dls"[[1]],
            all_long_dls_h_ns$"lmtb_0_ols"[[1]]
        )
    ),
    proc_path("lmtb_0_df.rds", TRUE)
)

# D
saveRDS(
    as.data.frame(
        c(
            all_long_dls_h_ns$"lmtb_l_dls"[[1]],
            all_long_dls_h_ns$"lmtb_l_ols"[[1]]
        )
    ),
    proc_path("lmtb_l_df.rds", TRUE)
)

```

```{r}
# Reference
mtbi_ful_df <- readRDS(proc_path("2025_06_11_mtbi_ful_df.rds"))

# A
random_unij_1_df <- readRDS(proc_path("2025_06_19_random_unij_1_df.rds"))
random_unij_2_df <- readRDS(proc_path("2025_06_19_random_unij_2_df.rds"))
random_unij_3_df <- readRDS(proc_path("2025_06_19_random_unij_3_df.rds"))
random_unij_4_df <- readRDS(proc_path("2025_06_19_random_unij_4_df.rds"))
random_unij_5_df <- readRDS(proc_path("2025_06_19_random_unij_5_df.rds"))
random_unij_6_df <- readRDS(proc_path("2025_06_19_random_unij_6_df.rds"))
random_unij_7_df <- readRDS(proc_path("2025_06_19_random_unij_7_df.rds"))
random_unij_8_df <- readRDS(proc_path("2025_06_19_random_unij_8_df.rds"))
random_unij_9_df <- readRDS(proc_path("2025_06_19_random_unij_9_df.rds"))
random_unij_10_df <- readRDS(proc_path("2025_06_19_random_unij_10_df.rds"))

# B
best_matched_uninjured_df <- readRDS(proc_path("2025_06_18_best_matched_uninjured_df.rds"))

# C
preinjury_df <- readRDS(proc_path("2025_06_18_lmtb_0_df.rds"))

# D
postinjury_df <- readRDS(proc_path("2025_06_18_lmtb_l_df.rds"))

df_list <- list(
    "mtbi_ful_df"               = mtbi_ful_df,
    "random_unij_1_df"          = random_unij_1_df,
    "random_unij_2_df"          = random_unij_2_df,
    "random_unij_3_df"          = random_unij_3_df,
    "random_unij_4_df"          = random_unij_4_df,
    "random_unij_5_df"          = random_unij_5_df,
    "random_unij_6_df"          = random_unij_6_df,
    "random_unij_7_df"          = random_unij_7_df,
    "random_unij_8_df"          = random_unij_8_df,
    "random_unij_9_df"          = random_unij_9_df,
    "random_unij_10_df"         = random_unij_10_df,
    "best_matched_uninjured_df" = best_matched_uninjured_df,
    "preinjury_df"              = preinjury_df,
    "postinjury_df"             = postinjury_df
)

# How to use the intersect-Reduce approach:
intersect_reduce <- function(df_list) {
    common_cols <- Reduce(intersect, lapply(df_list, colnames))
    reduced_dfs <- lapply(df_list, function(df) as.data.frame(df)[, common_cols, drop = FALSE])
    return(reduced_dfs)
}


reduced_dfs <- intersect_reduce(df_list)

saveRDS(reduced_dfs, proc_path("reduced_dfs.rds", TRUE))
```

```{r}
# CHECKPOINT
reduced_dfs <- readRDS(proc_path("2025_06_19_reduced_dfs.rds"))
ofts <- readRDS(proc_path("2025_06_11_ofts.rds"))
```

## 1. Check if the extent of the correlations are significantly different

```{r}
set.seed(42)
start <- Sys.time()
perm_diffs_cor_v_mtbi <- lapply(
    2:length(reduced_dfs),
    function(x) {
        permutation_test_corrs2(reduced_dfs[[1]], reduced_dfs[[x]], "pearson", TRUE, 5000)
    }
)
print(Sys.time() - start)

names(perm_diffs_cor_v_mtbi) <- names(reduced_dfs)[2:length(reduced_dfs)]

saveRDS(perm_diffs_cor_v_mtbi, proc_path("perm_diffs_cor_v_mtbi_fisherz_5000.rds", TRUE))
```

```{r}
perm_diffs_cor_v_mtbi <- readRDS(proc_path("2025_06_20_perm_diffs_cor_v_mtbi_fisherz_5000.rds"))

lapply(
    names(perm_diffs_cor_v_mtbi),
    function(x) {
        paste0(x, ": ", min(1, 14*perm_diffs_cor_v_mtbi[[x]]$"p_value"))
    }
) |> unlist()

z <- p.adjust(
    c(1, 0.0308, 0.2128, 0.0056, 0, 0.0336, 0.0112, 0.1652, 0.378, 0.0224, 1, 1, 1),
    method = "fdr"
)

for (i in z) {
    print(i)
}
```

Random unij dfs (6/10 significantly different after multiple comparisons corrections):
- 1
- *0.0308*
- 0.2128
- *0.0056*
- *0*
- *0.0336*
- *0.0112*
- 0.1652
- 0.378
- *0.0224*

best_matched_uninjured_df: 1

preinjury_df: 1

postinjury_df: 1

## 2. If not a generic increase in strength, what is significantly different?

- Focus on correlations between outcome measures and top 20 most important features for clustering solution only

```{r}
# Adding in dummy race variable
ifts <- readRDS(proc_path("2025_06_11_ifts.rds"))
ifts_expand <- unlist(append(ifts, list("race_black", "race_hispanic", "race_other"), after = which(ifts == "race")))
ifts_expand <- ifts_expand[-18]
ifts_expand <- ifts_expand[1:20]

ofts <- readRDS(proc_path("2025_06_11_ofts.rds"))
```

```{r}

permutation_test_corrs3 <- function(df1,
                                    df2,
                                    method = "pearson",
                                    fisher_z = TRUE,
                                    perms,
                                    procs = future::availableCores(),
                                    style = "loop") {
    cor1 <- calculate_cor_mat(df1, method, fisher_z)[ifts_expand, ofts]
    cor2 <- calculate_cor_mat(df2, method, fisher_z)[ifts_expand, ofts]
    obs_diff <- cor1 - cor2
    n1 <- nrow(df1)
    n2 <- nrow(df2)
    n <- n1 + n2
    if (style == "lapply") {
        future::plan(future::multisession, workers = procs)
        perm_mat_diffs <- future.apply::future_lapply(
            seq_len(perms),
            future.seed = TRUE,
            function(i) {
                merged_df <- rbind(df1, df2)[sample(n), ]
                perm_cor1 <- calculate_cor_mat(merged_df[1:n1, ], method, fisher_z)[ifts_expand, ofts]
                perm_cor2 <- calculate_cor_mat(merged_df[(n1+1):n, ], method, fisher_z)[ifts_expand, ofts]
                return(perm_cor1 - perm_cor2)
            }
        )
        future::plan("sequential")
    }
    if (style == "loop") {
        perm_mat_diffs <- vector("list", perms)
        for (i in seq_len(perms)) {
            merged_df <- rbind(df1, df2)[sample(n), ]
            perm_cor1 <- calculate_cor_mat(merged_df[1:n1, ], method, fisher_z)[ifts_expand, ofts]
            perm_cor2 <- calculate_cor_mat(merged_df[(n1+1):n, ], method, fisher_z)[ifts_expand, ofts]
            perm_mat_diffs[[i]] <- perm_cor1 - perm_cor2
        }
    }
    perm_mat_diffs <- append(perm_mat_diffs, list(obs_diff) , after = 0)
    return(
        list(
            cor1 = cor1,
            cor2 = cor2,
            obs_diff = cor1 - cor2,
            perm_mat_diffs = perm_mat_diffs
        )
    )
}


set.seed(42)
start <- Sys.time()
perm_ele_wise_corrs_v_mtbi_lapply <- lapply(
    2:length(reduced_dfs),
    function(x) {
        permutation_test_corrs3(
            df1 = reduced_dfs[[1]],
            df2 = reduced_dfs[[x]],
            method = "pearson",
            fisher_z = TRUE,
            perms = 5000,
            style = "lapply"
        )
    }
)
print(Sys.time() - start)
saveRDS(
    perm_ele_wise_corrs_v_mtbi_lapply,
    proc_path(
        "perm_ele_wise_corrs_v_mtbi_lapply_fisherz_5000.rds",
        TRUE
    )
)

flatten_mats <- function(perm_results) {
    mat_list <- perm_results$"perm_mat_diffs"
    flattened_mats <- lapply(
        1:length(mat_list[[1]]),
        function(element) {
            lapply(
                mat_list,
                function(mat) {
                    mat[element]
                }
            ) |> unlist()
        }
    )
    flattened_mats <- setNames(
        flattened_mats,
        as.vector(
            outer(
                rownames(perm_results$"perm_mat_diffs"[[1]]),
                colnames(perm_results$"perm_mat_diffs"[[1]]),
                paste,
                sep = "_vs_"
            )
        )
    )
    return(flattened_mats)
}

perm_ele_flat <- lapply(
    perm_ele_wise_corrs_v_mtbi_lapply,
    function(x) {
        flatten_mats(x)
    }
)

perm_ele_flat[[1]][[1]][1] > perm_ele_flat[[1]][[1]][-1]

# this object is a list of 13 sets of group comparisons
# each set of comparison is a list of 180 pairwise correlations
# each pairwise correlation si a vector of 5001 values

saveRDS(
    perm_ele_flat,
    proc_path("perm_ele_flat_v_mtbi_fisherz_5000.rds", TRUE)
)

perm_p_values <- lapply(
    perm_ele_flat,
    function(group_comparison) {
        lapply(
            group_comparison,
            function(perm_vector) {
                # base the comparison on sign of the first element
                # which is the actual observed difference
                if (perm_vector[1] >= 0) {
                    return(mean(perm_vector[-1] >= perm_vector[1]))
                } else {
                    return(mean(perm_vector[-1] <= perm_vector[1]))
                }
            }
        ) |> unlist()
    }
)

saveRDS(
    perm_p_values,
    proc_path("perm_p_values_v_mtbi_fisherz_5000.rds", TRUE)
)


perm_p_dfs <- lapply(
    perm_p_values,
    function(x) {
        df <- data.frame(
            "feature" = names(x),
            "p_value" = x
        )
        rownames(df) <- NULL
        df
    }
)

names(perm_p_dfs) <- names(reduced_dfs)[2:length(reduced_dfs)]

perm_p_dfs_clean <- lapply(
    names(perm_p_dfs),
    function(name) {
        perm_p_dfs[[name]]$"set" <- name
        if (isTRUE(as.logical(grep("random_unij", name)))) {
            perm_p_dfs[[name]]$"set_type" <- "random_unij"
        } else {
            perm_p_dfs[[name]]$"set_type" <- name
        }
        #perm_p_dfs[[name]]$"input" <- strsplit(perm_p_dfs[[name]]$"feature", "_vs_")[[1]][[1]]
        #perm_p_dfs[[name]]$"output" <- strsplit(perm_p_dfs[[name]]$"feature", "_vs_")[[1]][[2]]
        perm_p_dfs[[name]]$"input" <- unlist(lapply(strsplit(perm_p_dfs[[name]]$"feature", "_vs_"), function(x) x[1]))
        perm_p_dfs[[name]]$"output" <- unlist(lapply(strsplit(perm_p_dfs[[name]]$"feature", "_vs_"), function(x) x[2]))
        perm_p_dfs[[name]]
    }
)
perm_p_df <- do.call(
    rbind,
    perm_p_dfs_clean
)
perm_p_df$"fdr_p" <- p.adjust(perm_p_df$"p_value", method = "fdr") 

saveRDS(perm_p_df, proc_path("perm_p_df.rds", TRUE))

perm_p_df <- readRDS(proc_path("2025_06_20_perm_p_df.rds"))

perm_p_df
```

1/5001

```{r}
# Everything

for (i in unique(perm_p_df$"set_type")) {
    mini_df <- perm_p_df |> dplyr::filter(set_type == i)
    mini_df |>
        dplyr::group_by(feature, input, output, set_type) |>
        dplyr::summarize(mean = mean(fdr_p)) |>
        dplyr::arrange(mean) |>
        dplyr::filter(mean < 0.05) |>
        dplyr::ungroup() |>
        dplyr::select(-feature) |>
        data.frame() |>
        dplyr::select(set_type, dplyr::everything()) |>
        dplyr::rename(
            "*Group*" = "set_type",
            "*Input Feature*" = "input",
            "*Outcome Feature*" = "output",
            "*p-value*" = "mean"
        ) |>
        knitr::kable(format = "markdown", digits = 4) |>
        print()
}

perm_p_df |>
    dplyr::group_by(feature, input, output, set_type) |>
    dplyr::summarize(mean = mean(fdr_p)) |>
    dplyr::arrange(mean) |>
    dplyr::filter(mean < 0.05) |>
    dplyr::ungroup() |>
    dplyr::select(-feature) |>
    data.frame() |>
    knitr::kable(format = "markdown", digits = 4)

perm_p_df |>
    dplyr::group_by(feature, input, output, set_type) |>
    dplyr::summarize(mean = mean(fdr_p)) |>
    dplyr::arrange(mean) |>
    dplyr::filter(mean < 0.05) |>
    dplyr::ungroup() |>
    dplyr::select(-feature) |>
    data.frame() |>
    dplyr::filter(set_type == "random_unij") |>
    dplyr::arrange(input)

```

                  input          output                  set_type        mean
1        parent_somatic    cbcl_withdep              preinjury_df 0.000000000
2   private_instruction cbcl_aggressive              preinjury_df 0.000000000
3      extracurriculars cbcl_aggressive              preinjury_df 0.005318182
4      household_income    cbcl_withdep              preinjury_df 0.005318182
5   private_instruction cbcl_aggressive best_matched_uninjured_df 0.005318182
6   private_instruction  cbcl_rulebreak              preinjury_df 0.005318182
7      extracurriculars cbcl_aggressive               random_unij 0.006433632
8      household_income    cbcl_thought               random_unij 0.007816359
9      household_income cbcl_aggressive               random_unij 0.008879989
10 activities_last_year cbcl_aggressive               random_unij 0.009327785
11  private_instruction    cbcl_withdep             postinjury_df 0.011700000
12 activities_last_year cbcl_aggressive best_matched_uninjured_df 0.013664234
13 activities_last_year cbcl_aggressive             postinjury_df 0.013664234
14     extracurriculars    cbcl_somatic             postinjury_df 0.013664234
15  private_instruction    cbcl_withdep best_matched_uninjured_df 0.013664234
16     household_income     cbcl_anxdep               random_unij 0.017178958
17 activities_last_year cbcl_aggressive              preinjury_df 0.017550000
18  private_instruction cbcl_aggressive               random_unij 0.019172319
19 activities_last_year     cbcl_social best_matched_uninjured_df 0.019384615
20     extracurriculars cbcl_aggressive best_matched_uninjured_df 0.019384615
21  private_instruction    cbcl_withdep              preinjury_df 0.021517241
22  private_instruction  cbcl_rulebreak best_matched_uninjured_df 0.023142857
23     household_income    cbcl_withdep               random_unij 0.023790351
24     household_income  cbcl_attention               random_unij 0.023911780
25  private_instruction  cbcl_rulebreak               random_unij 0.024018424
26     extracurriculars cbcl_aggressive             postinjury_df 0.024502618
27     extracurriculars    cbcl_withdep best_matched_uninjured_df 0.025485149
28     extracurriculars  cbcl_rulebreak               random_unij 0.027664824
29     household_income     cbcl_social               random_unij 0.032231645
30 activities_last_year     cbcl_social             postinjury_df 0.036310345
31  private_instruction cbcl_aggressive             postinjury_df 0.036310345
32     extracurriculars     cbcl_social best_matched_uninjured_df 0.040114286
33     household_income    cbcl_withdep best_matched_uninjured_df 0.040114286
34     household_income    cbcl_withdep             postinjury_df 0.040695652
35         brain_volume     cbcl_anxdep              preinjury_df 0.042046875
36 activities_last_year    cbcl_thought               random_unij 0.042116119
37     parent_anxdisord    cbcl_withdep              preinjury_df 0.044150943
38     household_income       sds_sleep               random_unij 0.044587490
39 activities_last_year    cbcl_withdep best_matched_uninjured_df 0.045234201

```{r}
# Distribution of inputs
perm_p_df |>
    dplyr::group_by(feature, input, output, set_type) |>
    dplyr::summarize(mean = mean(fdr_p)) |>
    dplyr::arrange(mean) |>
    dplyr::filter(mean < 0.05) |>
    dplyr::ungroup() |>
    dplyr::select(-feature) |>
    data.frame() |>
    dplyr::select(input) |> table()
```

activities_last_year         brain_volume     extracurriculars
                   8                    1                    8
    household_income     parent_anxdisord       parent_somatic
                  10                    1                    1
 private_instruction
                  10


```{r}
# In just pre-injury / post-injry
perm_p_df |>
    dplyr::filter(set_type %in% c("preinjury_df")) |>
    dplyr::group_by(feature, input, output, set_type) |>
    dplyr::summarize(mean = mean(fdr_p)) |>
    dplyr::arrange(mean) |>
    dplyr::filter(mean < 0.05) |>
    dplyr::ungroup() |>
    dplyr::select(-feature) |>
    data.frame()

perm_p_df |>
    dplyr::filter(set_type %in% c("postinjury_df")) |>
    dplyr::group_by(feature, input, output, set_type) |>
    dplyr::summarize(mean = mean(fdr_p)) |>
    dplyr::arrange(mean) |>
    dplyr::filter(mean < 0.05) |>
    dplyr::ungroup() |>
    dplyr::select(-feature) |>
    data.frame()

```
                 input          output     set_type        mean
1       parent_somatic    cbcl_withdep preinjury_df 0.000000000
2  private_instruction cbcl_aggressive preinjury_df 0.000000000
3     extracurriculars cbcl_aggressive preinjury_df 0.005318182
4     household_income    cbcl_withdep preinjury_df 0.005318182
5  private_instruction  cbcl_rulebreak preinjury_df 0.005318182
6 activities_last_year cbcl_aggressive preinjury_df 0.017550000
7  private_instruction    cbcl_withdep preinjury_df 0.021517241
8         brain_volume     cbcl_anxdep preinjury_df 0.042046875
9     parent_anxdisord    cbcl_withdep preinjury_df 0.044150943

                 input          output      set_type       mean
1  private_instruction    cbcl_withdep postinjury_df 0.01170000
2 activities_last_year cbcl_aggressive postinjury_df 0.01366423
3     extracurriculars    cbcl_somatic postinjury_df 0.01366423
4     extracurriculars cbcl_aggressive postinjury_df 0.02450262
5 activities_last_year     cbcl_social postinjury_df 0.03631034
6  private_instruction cbcl_aggressive postinjury_df 0.03631034
7     household_income    cbcl_withdep postinjury_df 0.04069565

```{r}
# A quick check of pre vs post

names(reduced_dfs)

pre_v_post_ele_perm <- permutation_test_corrs3(
    df1 = reduced_dfs[["preinjury_df"]],
    df2 = reduced_dfs[["postinjury_df"]],
    method = "pearson",
    fisher_z = TRUE,
    perms = 5000,
    style = "lapply"
)

pre_v_post_flat <- flatten_mats(pre_v_post_ele_perm)

names(pre_v_post_flat)

pre_v_post_p_values <- lapply(
    pre_v_post_flat,
    function(perm_vector) {
        # base the comparison on sign of the first element
        # which is the actual observed difference
        if (perm_vector[1] >= 0) {
            return(mean(perm_vector[-1] >= perm_vector[1]))
        } else {
            return(mean(perm_vector[-1] <= perm_vector[1]))
        }
    }
) |> unlist()

pre_v_post_df <- data.frame(
    "feature" = names(pre_v_post_p_values),
    "p_value" = pre_v_post_p_values
)
pre_v_post_df$"input" <- unlist(lapply(strsplit(pre_v_post_df$"feature", "_vs_"), function(x) x[1]))
pre_v_post_df$"output" <- unlist(lapply(strsplit(pre_v_post_df$"feature", "_vs_"), function(x) x[2]))
rownames(pre_v_post_df) <- NULL
pre_v_post_df <- pre_v_post_df |> dplyr::select(-feature)
pre_v_post_df$"fdr_p" <- p.adjust(pre_v_post_df$"p_value", method = "fdr")

saveRDS(pre_v_post_df, proc_path("pre_v_post_df.rds", TRUE))

pre_v_post_df <- readRDS(proc_path("2025_06_20_pre_v_post_df.rds"))

pre_v_post_df |>
    dplyr::arrange(p_value)

```

Nothing remained significant following FDR multiple comparisons corrections.


Checking our main results with some plots:

```{r}

names(reduced_dfs)

# significant!!!
plot_df <- function(group1, group2) {
    df <- rbind(
        dplyr::mutate(reduced_dfs[[group1]], group = names(reduced_dfs)[group1]),
        dplyr::mutate(reduced_dfs[[group2]], group = names(reduced_dfs)[group2])
    )
    print(
        summary(
            lm(cbcl_aggressive ~ household_income * group, data = df)
        )
    )
    df |>
        ggplot(
            aes(
                x = household_income,
                y = cbcl_aggressive,
                colour = group
            )
        ) +
        geom_jitter(height = 0.1, width = 0.1, alpha = 0.5) +
        geom_smooth(method = "lm", se = FALSE) +
        theme_bw()
}
z1 <- plot_df(1, 13)
z2 <- plot_df(1, 14)

ggsave(
    fig_path("income_vs_aggressive_cor_mtbi_vs_lmtb.png", TRUE),
    wrap_plots(list(z1, z2)),
    width = 10,
    height = 4
)



```
