
Is there something in the correlation structure of these samples that determines whether or not cluster analysis can find the baseline concussion solution?

```{r}
library(abcdutils)
library(here)
library(dplyr)
library(readr)
library(metasnf)
library(rlist)
library(visdat)
library(ggplot2)
library(mice)
library(fastDummies)
library(randomForest)
library(patchwork)
library(tidyr)
library(ComplexHeatmap)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
core_path <- path_maker(here(paste0("data/abcd/core")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
model_path <- path_maker(here(paste0("data/abcd/results/models")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
```

```{r}
mtbi_ful_df <- readRDS(proc_path("2025_06_11_mtbi_ful_df.rds"))

mtbi_ful_df

calculate_cor_mat <- function(df, method, fisher_z = FALSE) {
    df <- df |>
    data.frame() |>
    dplyr::select(-uid, -cluster) |>
    dummy_cols(
        select_columns = c("race", "mtbi_mechanism"),
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = TRUE
    )
    if (method == "spearman") {
        future::plan("multisession")
        n <- ncol(df)
        spearman_mat <- matrix(NA, n, n)
        colnames(spearman_mat) <- rownames(spearman_mat) <- colnames(df)
        results <- pbapply::pblapply(
            1:n,
            function(i) {
                sapply(
                    i:ncol(df),
                    function(j) {
                        cor(df[[i]], df[[j]], method = "spearman")
                    }
                )
            },
            cl = future::availableCores()
        )
        for (i in 1:n) {
            spearman_mat[i, i:n] <- results[[i]]
            spearman_mat[i:n, i] <- results[[i]]
        }
        mat <- spearman_mat
    } else if (method == "pearson") {
        mat <- cor(df, method = "pearson")
    }
    if (fisher_z) {
        mat <- atanh(mat) 
    }
}
```

I'll try to compare matrices under the following schemes:

- baseline concussion data vs...
    - A. 10 random uninjured samples
    - B. the best matched uninjured sample
    - C. the pre-injury sample data
    - D. the post-injury sample data

I'll do the comparisons the following ways:

- permutation testing mean absolute difference in spearman correlations
- permutation testing mean absolute difference in pearson correlations
- permutation testing mean absolute difference in z-transformed pearson correlations

```{r}
# Data
random_unij_dl_u1 <- readRDS(proc_path("2025_06_15_random_unij_dl_u1.rds"))
all_dls_h_ns <- readRDS(proc_path("2025_06_11_all_dls_h_no_sibs.rds"))
unij_dl_u1 <- all_dls_h_ns$"unij_all_u_dls"$"imp_1"
matched_unij_dl_do_u <- readRDS(proc_path("2025_06_15_matched_unij_dl_do_u.rds"))
matched_unij_ol_do_u <- readRDS(proc_path("2025_06_15_matched_unij_ol_do_u.rds"))
all_long_dls_h_ns <- readRDS(proc_path("2025_06_13_all_long_dls_h_ns.rds"))

subject_filter_dl <- function(data_list, subject_vector) {
    data_list <- data_list |>
        dlapply(
            function(x) {
                keep_subs <- x$"data"$"uid" %in% subject_vector
                x$"data" <- x$"data"[keep_subs, ]
                return(x)
            }
        )
    return(data_list)
}

# A
set.seed(42)
random_unij_subs_01 <- sample(uids(unij_dl_u1))[1:434]
random_unij_subs_02 <- sample(uids(unij_dl_u1))[1:434]
random_unij_subs_03 <- sample(uids(unij_dl_u1))[1:434]
random_unij_subs_04 <- sample(uids(unij_dl_u1))[1:434]
random_unij_subs_05 <- sample(uids(unij_dl_u1))[1:434]
random_unij_subs_06 <- sample(uids(unij_dl_u1))[1:434]
random_unij_subs_07 <- sample(uids(unij_dl_u1))[1:434]
random_unij_subs_08 <- sample(uids(unij_dl_u1))[1:434]
random_unij_subs_09 <- sample(uids(unij_dl_u1))[1:434]
random_unij_subs_10 <- sample(uids(unij_dl_u1))[1:434]

random_unij_1 <- subject_filter_dl(unij_dl_u1, random_unij_subs_01)
random_unij_2 <- subject_filter_dl(unij_dl_u1, random_unij_subs_02)
random_unij_3 <- subject_filter_dl(unij_dl_u1, random_unij_subs_03)
random_unij_4 <- subject_filter_dl(unij_dl_u1, random_unij_subs_04)
random_unij_5 <- subject_filter_dl(unij_dl_u1, random_unij_subs_05)
random_unij_6 <- subject_filter_dl(unij_dl_u1, random_unij_subs_06)
random_unij_7 <- subject_filter_dl(unij_dl_u1, random_unij_subs_07)
random_unij_8 <- subject_filter_dl(unij_dl_u1, random_unij_subs_08)
random_unij_9 <- subject_filter_dl(unij_dl_u1, random_unij_subs_09)
random_unij_10 <- subject_filter_dl(unij_dl_u1, random_unij_subs_10)

random_unij_1_df <- as.data.frame(random_unij_1)
random_unij_2_df <- as.data.frame(random_unij_2)
random_unij_3_df <- as.data.frame(random_unij_3)
random_unij_4_df <- as.data.frame(random_unij_4)
random_unij_5_df <- as.data.frame(random_unij_5)
random_unij_6_df <- as.data.frame(random_unij_6)
random_unij_7_df <- as.data.frame(random_unij_7)
random_unij_8_df <- as.data.frame(random_unij_8)
random_unij_9_df <- as.data.frame(random_unij_9)
random_unij_10_df <- as.data.frame(random_unij_10)

saveRDS(random_unij_1_df, proc_path("random_unij_1_df.rds", TRUE))
saveRDS(random_unij_2_df, proc_path("random_unij_2_df.rds", TRUE))
saveRDS(random_unij_3_df, proc_path("random_unij_3_df.rds", TRUE))
saveRDS(random_unij_4_df, proc_path("random_unij_4_df.rds", TRUE))
saveRDS(random_unij_5_df, proc_path("random_unij_5_df.rds", TRUE))
saveRDS(random_unij_6_df, proc_path("random_unij_6_df.rds", TRUE))
saveRDS(random_unij_7_df, proc_path("random_unij_7_df.rds", TRUE))
saveRDS(random_unij_8_df, proc_path("random_unij_8_df.rds", TRUE))
saveRDS(random_unij_9_df, proc_path("random_unij_9_df.rds", TRUE))
saveRDS(random_unij_10_df, proc_path("random_unij_10_df.rds", TRUE))

# B
best_matched_uninjured_df <- as.data.frame(
    c(matched_unij_dl_do_u, matched_unij_ol_do_u)
)
saveRDS(best_matched_uninjured_df, proc_path("best_matched_uninjured_df.rds", TRUE))

# C
saveRDS(
    as.data.frame(
        c(
            all_long_dls_h_ns$"lmtb_0_dls"[[1]],
            all_long_dls_h_ns$"lmtb_0_ols"[[1]]
        )
    ),
    proc_path("lmtb_0_df.rds", TRUE)
)

# D
saveRDS(
    as.data.frame(
        c(
            all_long_dls_h_ns$"lmtb_l_dls"[[1]],
            all_long_dls_h_ns$"lmtb_l_ols"[[1]]
        )
    ),
    proc_path("lmtb_l_df.rds", TRUE)
)

```

```{r}
# A
random_unij_1_df <- readRDS(proc_path("2025_06_18_random_unij_1_df.rds"))
random_unij_2_df <- readRDS(proc_path("2025_06_18_random_unij_2_df.rds"))
random_unij_3_df <- readRDS(proc_path("2025_06_18_random_unij_3_df.rds"))
random_unij_4_df <- readRDS(proc_path("2025_06_18_random_unij_4_df.rds"))
random_unij_5_df <- readRDS(proc_path("2025_06_18_random_unij_5_df.rds"))
random_unij_6_df <- readRDS(proc_path("2025_06_18_random_unij_6_df.rds"))
random_unij_7_df <- readRDS(proc_path("2025_06_18_random_unij_7_df.rds"))
random_unij_8_df <- readRDS(proc_path("2025_06_18_random_unij_8_df.rds"))
random_unij_9_df <- readRDS(proc_path("2025_06_18_random_unij_9_df.rds"))
random_unij_10_df <- readRDS(proc_path("2025_06_18_random_unij_10_df.rds"))

# B
best_matched_uninjured_df <- readRDS(proc_path("2025_06_18_best_matched_uninjured_df.rds"))

# C
preinjury_df <- readRDS(proc_path("2025_06_18_lmtb_0_df.rds"))

# D
postinjury_df <- readRDS(proc_path("2025_06_18_lmtb_l_df.rds"))


permutation_test_corrs <- function(df1, df2, method, fisher_z, perms) {
    cor1 <- calculate_cor_mat(df1, method, fisher_z)
    cor2 <- calculate_cor_mat(df2, method, fisher_z)
    observed_diff <- mean(abs(cor1 - cor2), na.rm = TRUE)
    perm_diffs <- numeric(perms)
    n1 <- nrow(df1)
    n2 <- nrow(df2)
    n <- n1 + n2
    for (i in 1:perms) {
        merged_df <- rbind(df1, df2)[sample(n), ]
        perm_cor1 <- calculate_cor_mat(merged_df[1:n1, ], method, fisher_z)
        perm_cor2 <- calculate_cor_mat(merged_df[(n1+1):n, ], method, fisher_z)
        perm_diffs[i] <- mean(abs(perm_cor1 - perm_cor2), na.rm = TRUE)
    }
    p_value <- mean(perm_diffs >= observed_diff)
    return(list(observed_diff = observed_diff, p_value = p_value))
}

permutation_test_corrs(mtbi_ful_df, best_matched_uninjured_df, "pearson", FALSE, 10)



#permutation testing mean absolute difference in spearman correlations
#permutation testing mean absolute difference in pearson correlations
#permutation testing mean absolute difference in z-transformed pearson correlations







```
