# Data Exploration

## Establishing paths

```{r}
library(ggplot2)
library(readr)
library(dplyr)
library(here)
library(abcdutils)
library(fastDummies)
library(patchwork)
library(visdat)
library(mice)
library(circlize)
library(ComplexHeatmap)
library(metasnf)

core_path <- path_maker(here(paste0("data/abcd/core")))
input_path <- path_maker(here(paste0("data/abcd/inputs")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))

read <- function(path) {
    read_csv(input_path(path))
}
```

## Importing baseline data

```{r}
# Post imputation and harmonization
all_dls_h <- readRDS(proc_path("2025_09_11_all_dls_h.rds"))
# Post imputation and harmonization, siblings dropped
all_dls_h_ns <- readRDS(proc_path("2025_09_11_all_dls_h_no_sibs.rds"))

c(all_dls_h_ns$"mtbi_der_u_dls"[[1]], all_dls_h_ns$"mtbi_der_u_ols"[[1]]) 

c(all_dls_h_ns$"mtbi_val_u_dls"[[1]], all_dls_h_ns$"mtbi_val_u_ols"[[1]]) 

# Pre-imputation
mtbi_train_df <- data.frame(read_csv(proc_path("2025_09_11_mtbi_train_df.csv")))
mtbi_test_df <- data.frame(read_csv(proc_path("2025_09_11_mtbi_test_df.csv")))
unij_df <- data.frame(read_csv(proc_path("2025_09_11_unij_df.csv")))
mtbi_df <- rbind(mtbi_train_df, mtbi_test_df)

# Post-imputation
mtbi_train_imputed <- readRDS(proc_path("2025_09_11_mtbi_train_imputed.rds"))
mtbi_test_imputed <- readRDS(proc_path("2025_09_11_mtbi_test_imputed.rds"))
unij_imputed <- readRDS(proc_path("2025_09_11_unij_imputed.rds"))
pool_imputed <- readRDS(proc_path("2025_09_11_pool_imputed.rds"))

# All the baseline subjects
mtbi_ful_df <- readRDS(proc_path("2025_09_16_mtbi_ful_df.rds"))

mtbi_ful_df |> colnames()

all_long_dls_h_ns <- readRDS(proc_path("2025_10_03_all_long_dls_h_ns.rds"))
all_long_dls_h <- readRDS(proc_path("2025_09_29_all_long_dls_h.rds"))

```

This chunk examines the % of missingness in the original mTBI and uninjured sample

```{r}
mtbi_missingness_plot <- mtbi_df |>
    dplyr::select(order(colnames(mtbi_df))) |>
    dplyr::select(-subjectkey) |>
    visdat::vis_miss() + theme(
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 0)
  )

unij_missingness_plot <- unij_df |>
    dplyr::select(order(colnames(unij_df))) |>
    dplyr::select(-subjectkey) |>
    visdat::vis_miss() + theme(
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 0)
  )

mtbi_missingness_plot


ggsave(
    fig_path("mtbi_missingness_plot.png", TRUE),
    plot = mtbi_missingness_plot,
    width = 10,
    height = 6
)

ggsave(
    fig_path("unij_missingness_plot.png", TRUE),
    plot = unij_missingness_plot,
    width = 10,
    height = 6
)

```

## Sample characteristics

```{r}
sample_characterize <- function(data) {
    if (inherits(data, "data_list")) {
        data <- as.data.frame(data)
    }
    # 1. Sex
    sex_df <- data.frame(table(data$"sex")) |>
        dplyr::mutate(
            Var1 = c("F", "M"),
            Freq = paste0(Freq, " (", signif(100 * Freq / nrow(data), 3), "%)")
        ) |>
        dplyr::rename("label" = "Var1", "value" = "Freq")
    sex_df <- rbind(
        data.frame("label" = "*Sex*", value = ""),
        sex_df
    )
    # 2. Age
    age_df <- data.frame(
        label = c("*Age*", "Mean (SD)"),
        value = c("", paste0(signif(mean(data$"age"), 3), " (", signif(sd(data$"age"), 2), ")"))
    )
    # 3. Pubertal status
    # 4. Income
    income_df <- data.frame(table(data$"household_income")) |>
        dplyr::mutate(
            Var1 = dplyr::case_when(
                Var1 == 1 ~ "<$50,000",
                Var1 == 2 ~ "$50,000-$100,000",
                Var1 == 3 ~ ">$100,000",
                TRUE ~ NA
            ),
            Freq = paste0(Freq, " (", signif(100 * Freq / nrow(data), 3), "%)")
        ) |>
        dplyr::rename("label" = "Var1", "value" = "Freq")
    income_df <- rbind(
        data.frame("label" = "*Income*", value = ""),
        income_df
    )
    # 5. Race 
    race_names <- names(table(data$"race"))
    race_counts <- as.numeric(table(data$"race"))
    race_pcts <- race_counts / nrow(data) * 100
    race_df <- lapply(
        1:length(race_pcts),
        function(x) {
            data.frame(
                label = race_names[x],
                value = paste0(race_counts[x], " (", signif(race_pcts[x], 3), "%)")
            )
        }
    ) |> do.call(what = rbind)
    race_df <- rbind(
        data.frame("label" = "*Race*", value = ""),
        race_df
    )
    return(
        list(
            sex_df,
            age_df,
            income_df,
            race_df
        ) |>
        do.call(what = rbind)
    )
}

mtbi_samp_char <- rbind(
    as.data.frame(all_dls_h_ns$"mtbi_der_u_dls"$"imp_1"),
    as.data.frame(all_dls_h_ns$"mtbi_val_u_dls"$"imp_1")
) |> sample_characterize()

mtbi_samp_char



unij_samp_char <- as.data.frame(all_dls_h_ns$"unij_all_u_dls"$"imp_1") |> sample_characterize()

cbind(mtbi_samp_char, dplyr::select(unij_samp_char, -label)) |>
    knitr::kable(format = "markdown", digits = 2)

#|label            |value       |value        |
#|:----------------|:-----------|:------------|
#|*Sex*            |            |             |
#|F                |171 (39%)   |3949 (50%)   |
#|M                |267 (61%)   |3956 (50%)   |
#|*Age*            |            |             |
#|Mean (SD)        |120 (7.5)   |119 (7.4)    |
#|*Income*         |            |             |
#|<$50,000         |102 (23.3%) |2631 (33.3%) |
#|$50,000-$100,000 |122 (27.9%) |2203 (27.9%) |
#|>$100,000        |214 (48.9%) |3071 (38.8%) |
#|*Race*           |            |             |
#|black            |38 (8.68%)  |1307 (16.5%) |
#|hispanic         |70 (16%)    |1714 (21.7%) |
#|other            |50 (11.4%)  |1008 (12.8%) |
#|white            |280 (63.9%) |3876 (49%)   |
```


<!-- -->-----------------------------------------------------------------------
## Who failed QC?

```{r}
# Function that will be used to compare subjects missing data in a list of
# pre-QC data frames to those in a list of post-QC data frames.
qc_fails <- function(df_list_1, df_list_2) {
    df_1 <- merge_df_list(df_list_1)
    df_2 <- merge_df_list(df_list_2)
    subs_1 <- na.omit(df_1)$"subjectkey"
    subs_2 <- na.omit(df_2)$"subjectkey"
    return(subs_1[which(!subs_1 %in% subs_2)])
}

###############################################################################
# Baseline mTBI, T = 0
###############################################################################
base_mtbi_0_s_qcf <- qc_fails(
    list(sm_subc_v_mtbi, sm_cort_t_mtbi, sm_cort_sa_mtbi),
    list(sm_cort_sa_qc_mtbi, sm_cort_t_qc_mtbi, sm_subc_v_qc_mtbi)
)
base_mtbi_0_s_qcf

base_mtbi_0_d_qcf <- qc_fails(
    list(dm_all_wmnd_mtbi),
    list(dm_all_wmnd_qc_mtbi)
)
base_mtbi_0_d_qcf

base_mtbi_0_r_qcf <- qc_fails(
    list(rm_gord_cor_mtbi),
    list(rm_gord_cor_qc_mtbi)
)
base_mtbi_0_r_qcf

###############################################################################
# Baseline unij, T = 0
###############################################################################
base_unij_0_s_qcf <- qc_fails(
    list(sm_subc_v_unij, sm_cort_t_unij, sm_cort_sa_unij),
    list(sm_cort_sa_qc_unij, sm_cort_t_qc_unij, sm_subc_v_qc_unij)
)
base_unij_0_s_qcf

base_unij_0_d_qcf <- qc_fails(
    list(dm_all_wmnd_unij),
    list(dm_all_wmnd_qc_unij)
)
base_unij_0_d_qcf

base_unij_0_r_qcf <- qc_fails(
    list(rm_gord_cor_unij),
    list(rm_gord_cor_qc_unij)
)
base_unij_0_r_qcf

###############################################################################
# Baseline mtbi, T = 2
###############################################################################
base_mtbi_l_s_qcf <- qc_fails(
    list(sm_subc_v_base_mtbi_l, sm_cort_t_base_mtbi_l, sm_cort_sa_base_mtbi_l),
    list(sm_cort_sa_qc_base_mtbi_l, sm_cort_t_qc_base_mtbi_l, sm_subc_v_qc_base_mtbi_l)
)
base_mtbi_l_s_qcf

base_mtbi_l_d_qcf <- qc_fails(
    list(dm_all_wmnd_base_mtbi_l),
    list(dm_all_wmnd_qc_base_mtbi_l)
)
base_mtbi_l_d_qcf

base_mtbi_l_r_qcf <- qc_fails(
    list(rm_gord_cor_base_mtbi_l),
    list(rm_gord_cor_qc_base_mtbi_l)
)
base_mtbi_l_r_qcf

###############################################################################
# Baseline unij, T = 2
###############################################################################
base_unij_l_s_qcf <- qc_fails(
    list(sm_subc_v_base_unij_l, sm_cort_t_base_unij_l, sm_cort_sa_base_unij_l),
    list(sm_cort_sa_qc_base_unij_l, sm_cort_t_qc_base_unij_l, sm_subc_v_qc_base_unij_l)
)
base_unij_l_s_qcf

base_unij_l_d_qcf <- qc_fails(
    list(dm_all_wmnd_base_unij_l),
    list(dm_all_wmnd_qc_base_unij_l)
)
base_unij_l_d_qcf

base_unij_l_r_qcf <- qc_fails(
    list(rm_gord_cor_base_unij_l),
    list(rm_gord_cor_qc_base_unij_l)
)
base_unij_l_r_qcf

###############################################################################
# Longitudinal mtbi, T = 0
###############################################################################
long_mtbi_0_s_qcf <- qc_fails(
    list(sm_subc_v_long_mtbi_0, sm_cort_t_long_mtbi_0, sm_cort_sa_long_mtbi_0),
    list(sm_cort_sa_qc_long_mtbi_0, sm_cort_t_qc_long_mtbi_0, sm_subc_v_qc_long_mtbi_0)
)
long_mtbi_0_s_qcf

long_mtbi_0_d_qcf <- qc_fails(
    list(dm_all_wmnd_long_mtbi_0),
    list(dm_all_wmnd_qc_long_mtbi_0)
)
long_mtbi_0_d_qcf

long_mtbi_0_r_qcf <- qc_fails(
    list(rm_gord_cor_long_mtbi_0),
    list(rm_gord_cor_qc_long_mtbi_0)
)
long_mtbi_0_r_qcf

###############################################################################
# Longitudinal mtbi, T = 2
###############################################################################
long_mtbi_l_s_qcf <- qc_fails(
    list(sm_subc_v_long_mtbi_l, sm_cort_t_long_mtbi_l, sm_cort_sa_long_mtbi_l),
    list(sm_cort_sa_qc_long_mtbi_l, sm_cort_t_qc_long_mtbi_l, sm_subc_v_qc_long_mtbi_l)
)
long_mtbi_l_s_qcf

long_mtbi_l_d_qcf <- qc_fails(
    list(dm_all_wmnd_long_mtbi_l),
    list(dm_all_wmnd_qc_long_mtbi_l)
)
long_mtbi_l_d_qcf

long_mtbi_l_r_qcf <- qc_fails(
    list(rm_gord_cor_long_mtbi_l),
    list(rm_gord_cor_qc_long_mtbi_l)
)
long_mtbi_l_r_qcf


# These are the subjects that were dropped due to QC. 
# Can pull from this list to check correlations with any other features.
failed_qc_subjects <- list(
    "base_mtbi_0_s_qcf" = base_mtbi_0_s_qcf,
    "base_mtbi_0_d_qcf" = base_mtbi_0_d_qcf,
    "base_mtbi_0_r_qcf" = base_mtbi_0_r_qcf,
    "base_unij_0_s_qcf" = base_unij_0_s_qcf,
    "base_unij_0_d_qcf" = base_unij_0_d_qcf,
    "base_unij_0_r_qcf" = base_unij_0_r_qcf,
    "base_mtbi_l_s_qcf" = base_mtbi_l_s_qcf,
    "base_mtbi_l_d_qcf" = base_mtbi_l_d_qcf,
    "base_mtbi_l_r_qcf" = base_mtbi_l_r_qcf,
    "base_unij_l_s_qcf" = base_unij_l_s_qcf,
    "base_unij_l_d_qcf" = base_unij_l_d_qcf,
    "base_unij_l_r_qcf" = base_unij_l_r_qcf,
    "long_mtbi_0_s_qcf" = long_mtbi_0_s_qcf,
    "long_mtbi_0_d_qcf" = long_mtbi_0_d_qcf,
    "long_mtbi_0_r_qcf" = long_mtbi_0_r_qcf,
    "long_mtbi_l_s_qcf" = long_mtbi_l_s_qcf,
    "long_mtbi_l_d_qcf" = long_mtbi_l_d_qcf,
    "long_mtbi_l_r_qcf" = long_mtbi_l_r_qcf
)

saveRDS(failed_qc_subjects, proc_path("failed_qc_subjects.rds", TRUE))
failed_qc_subjects <- readRDS(proc_path("2025_03_17_failed_qc_subjects.rds"))
```

## MAR/MCAR check

```{r}
# This function will create new X_* columns in a data frame to keep track of
# missing values 
flag_missing <- function(df) {
    for (col in colnames(df)) {
        if (any(is.na(df[, col]))) {
            newcol <- paste0("X_", col)
            df <- df |>
                dplyr::mutate(
                    newcol = as.numeric(is.na(.data[[col]]))
                )
            colnames(df)[ncol(df)] <- newcol
        }
    }
    return(df)
}
```

```{r}
mtbi_df$"group" <- "base_mtbi"
mtbi_df$"t" <- 0

unij_df$"group" <- "base_unij"
unij_df$"t" <- 0

long_mtbi_0_df$"group" <- "long_mtbi"
long_mtbi_0_df$"t" <- 0

long_mtbi_l_df$"group" <- "long_mtbi"
long_mtbi_l_df$"t" <- 2

base_mtbi_l_df$"group" <- "base_mtbi"
base_mtbi_l_df$"t" <- 2

base_unij_l_df$"group" <- "base_unij"
base_unij_l_df$"t" <- 2

pre_imputation_df <- bind_rows(
    mtbi_df,
    unij_df,
    long_mtbi_0_df,
    long_mtbi_l_df,
    base_mtbi_l_df,
    base_unij_l_df
)

pre_imputation_df <- pre_imputation_df |>
    dplyr::mutate(
        X_s_qc = dplyr::case_when(
            t == 0 & group == "base_mtbi" & subjectkey %in% base_mtbi_0_s_qcf ~ 1,
            t == 2 & group == "base_mtbi" & subjectkey %in% base_mtbi_l_s_qcf ~ 1,
            t == 0 & group == "base_unij" & subjectkey %in% base_unij_0_s_qcf ~ 1,
            t == 2 & group == "base_unij" & subjectkey %in% base_unij_l_s_qcf ~ 1,
            t == 0 & group == "long_mtbi" & subjectkey %in% long_mtbi_0_s_qcf ~ 1,
            t == 2 & group == "long_mtbi" & subjectkey %in% long_mtbi_l_s_qcf ~ 1,
            TRUE ~ 0
        ),
        X_d_qc = dplyr::case_when(
            t == 0 & group == "base_mtbi" & subjectkey %in% base_mtbi_0_d_qcf ~ 1,
            t == 2 & group == "base_mtbi" & subjectkey %in% base_mtbi_l_d_qcf ~ 1,
            t == 0 & group == "base_unij" & subjectkey %in% base_unij_0_d_qcf ~ 1,
            t == 2 & group == "base_unij" & subjectkey %in% base_unij_l_d_qcf ~ 1,
            t == 0 & group == "long_mtbi" & subjectkey %in% long_mtbi_0_d_qcf ~ 1,
            t == 2 & group == "long_mtbi" & subjectkey %in% long_mtbi_l_d_qcf ~ 1,
            TRUE ~ 0
        ),
        X_r_qc = dplyr::case_when(
            t == 0 & group == "base_mtbi" & subjectkey %in% base_mtbi_0_r_qcf ~ 1,
            t == 2 & group == "base_mtbi" & subjectkey %in% base_mtbi_l_r_qcf ~ 1,
            t == 0 & group == "base_unij" & subjectkey %in% base_unij_0_r_qcf ~ 1,
            t == 2 & group == "base_unij" & subjectkey %in% base_unij_l_r_qcf ~ 1,
            t == 0 & group == "long_mtbi" & subjectkey %in% long_mtbi_0_r_qcf ~ 1,
            t == 2 & group == "long_mtbi" & subjectkey %in% long_mtbi_l_r_qcf ~ 1,
            TRUE ~ 0
        ) 
    )

pre_imputation_df <- pre_imputation_df |>
    dummy_cols(
        select_columns = c("latest_mtbi_mechanism", "race"),
        remove_most_frequent_dummy = TRUE,
        remove_selected_columns = TRUE
    )

pre_imputation_df <- flag_missing(pre_imputation_df)

# This data frame has X_* columns to keep track of missingness generally or by
# the result of neuroimaging QC
colnames(pre_imputation_df)

write_csv(pre_imputation_df, proc_path("pre_imputation_df.csv", TRUE))

pre_imputation_df <- read_csv(proc_path("2025_02_13_pre_imputation_df.csv"))
```


```{r}
# This matrix contains the correlations across all regular and missing-based
# columns.
missing_mat <- pre_imputation_df |>
    dplyr::select(-subjectkey, -group, -t) |>
    cor(use = "pairwise.complete.obs") |>
    as.matrix()

saveRDS(missing_mat, proc_path("missing_mat.rds", TRUE))
```

```{r}
# CHECKPOINT
missing_mat <- readRDS(proc_path("2025_02_13_missing_mat.rds"))
```

```{r}
missing_indicator_cols <- grepl("X_", colnames(missing_mat))

# For checking MCAR vs. MAR
missing_cor_mat_1 <- missing_mat[missing_indicator_cols, !missing_indicator_cols]

# For checking patterns of missingness
missing_cor_mat_2 <- missing_mat[missing_indicator_cols, missing_indicator_cols]

x_map <- matrix(
    c(
        "X_s_qc", "N",
        "X_d_qc", "N",
        "X_r_qc", "N",
        "X_latest_mtbi_mem_daze", "AS",
        "X_latest_mtbi_loc", "AS",
        "X_interview_age", "D",
        "X_latest_mtbi_age", "AS",
        "X_sex", "D",
        "X_household_income", "D",
        "X_pubertal_status_p", "D",
        "X_pubertal_status_y", "D",
        "X_headache", "MH",
        "X_mtbi_count", "MH",
        "X_smri_vol_scs_wholeb", "N",
        "X_smri_thick_cdk_mean", "N",
        "X_smri_area_cdk_total", "N",
        "X_dmri_rsirnd_fib_allfib", "N",
        "X_dmri_rsirndwm_cdk_mean", "N",
        "X_avg_gord_cor", "N",
        "X_avg_subc_cor", "N",
        "X_ss_friend", "P",
        "X_os_friend", "P",
        "X_ss_close_friend", "P",
        "X_os_close_friend", "P",
        "X_screentime_wknd_hrs", "P",
        "X_screentime_wkday_hrs", "P",
        "X_physical_activity", "P",
        "X_considerate_y", "P",
        "X_helps_hurt_y", "P",
        "X_helpful_y", "P",
        "X_considerate_p", "P",
        "X_helps_hurt_p", "P",
        "X_helpful_p", "P",
        "X_q1_fight_y", "P",
        "X_q2_angry_y", "P",
        "X_q3_throw_y", "P",
        "X_q4_temper_y", "P",
        "X_q5_criticize_y", "P",
        "X_q6_hit_y", "P",
        "X_q7_peaceful_y", "P",
        "X_q8_outdo_y", "P",
        "X_q9_yell_y", "P",
        "X_q1_fight_p", "P",
        "X_q2_angry_p", "P",
        "X_q3_throw_p", "P",
        "X_q4_temper_p", "P",
        "X_q5_criticize_p", "P",
        "X_q6_hit_p", "P",
        "X_q7_peaceful_p", "P",
        "X_q8_outdo_p", "P",
        "X_q9_yell_p", "P",
        "X_asr_scr_perstr_r", "P",
        "X_asr_scr_anxdep_r", "P",
        "X_asr_scr_withdrawn_r", "P",
        "X_asr_scr_somatic_r", "P",
        "X_asr_scr_thought_r", "P",
        "X_asr_scr_attention_r", "P",
        "X_asr_scr_aggressive_r", "P",
        "X_asr_scr_intrusive_r", "P",
        "X_asr_scr_depress_r", "P",
        "X_asr_scr_anxdisord_r", "P",
        "X_asr_scr_avoidant_r", "P",
        "X_asr_scr_antisocial_r", "P",
        "X_asr_scr_hyperactive_r", "P",
        "X_cbcl_scr_syn_anxdep_r", "B",
        "X_cbcl_scr_syn_withdep_r", "B",
        "X_cbcl_scr_syn_somatic_r", "B",
        "X_cbcl_scr_syn_social_r", "B",
        "X_cbcl_scr_syn_thought_r", "B",
        "X_cbcl_scr_syn_attention_r", "B",
        "X_cbcl_scr_syn_rulebreak_r", "B",
        "X_cbcl_scr_syn_aggressive_r", "B",
        "X_sds_p_ss_total", "B",
        "X_latest_mtbi_mechanism_fall_hit", "AS",
        "X_latest_mtbi_mechanism_multi", "AS",
        "X_latest_mtbi_mechanism_other_loc", "AS",
        "X_latest_mtbi_mechanism_vehicle", "AS",
        "X_latest_mtbi_mechanism_violent", "AS",
        "X_race_black", "D",
        "X_race_hispanic", "D",
        "X_race_other", "D"
    ),
    ncol = 2,
    byrow = TRUE
)

non_x_map <- matrix(
    c(
        "latest_mtbi_mem_daze", "AS",
        "latest_mtbi_loc", "AS",
        "interview_age", "D",
        "latest_mtbi_age", "AS",
        "sex", "D",
        "household_income", "D",
        "pubertal_status_p", "D",
        "pubertal_status_y", "D",
        "headache", "MH",
        "mtbi_count", "MH",
        "smri_vol_scs_wholeb", "N",
        "smri_thick_cdk_mean", "N",
        "smri_area_cdk_total", "N",
        "dmri_rsirnd_fib_allfib", "N",
        "dmri_rsirndwm_cdk_mean", "N",
        "avg_gord_cor", "N",
        "avg_subc_cor", "N",
        "ss_friend", "P",
        "os_friend", "P",
        "ss_close_friend", "P",
        "os_close_friend", "P",
        "screentime_wknd_hrs", "P",
        "screentime_wkday_hrs", "P",
        "school_activities", "P",
        "extracurriculars", "P",
        "private_instruction", "P",
        "activities_last_year", "P",
        "physical_activity", "P",
        "considerate_y", "P",
        "helps_hurt_y", "P",
        "helpful_y", "P",
        "considerate_p", "P",
        "helps_hurt_p", "P",
        "helpful_p", "P",
        "q1_fight_y", "P",
        "q2_angry_y", "P",
        "q3_throw_y", "P",
        "q4_temper_y", "P",
        "q5_criticize_y", "P",
        "q6_hit_y", "P",
        "q7_peaceful_y", "P",
        "q8_outdo_y", "P",
        "q9_yell_y", "P",
        "q1_fight_p", "P",
        "q2_angry_p", "P",
        "q3_throw_p", "P",
        "q4_temper_p", "P",
        "q5_criticize_p", "P",
        "q6_hit_p", "P",
        "q7_peaceful_p", "P",
        "q8_outdo_p", "P",
        "q9_yell_p", "P",
        "asr_scr_perstr_r", "P",
        "asr_scr_anxdep_r", "P",
        "asr_scr_withdrawn_r", "P",
        "asr_scr_somatic_r", "P",
        "asr_scr_thought_r", "P",
        "asr_scr_attention_r", "P",
        "asr_scr_aggressive_r", "P",
        "asr_scr_intrusive_r", "P",
        "asr_scr_depress_r", "P",
        "asr_scr_anxdisord_r", "P",
        "asr_scr_avoidant_r", "P",
        "asr_scr_antisocial_r", "P",
        "asr_scr_hyperactive_r", "P",
        "cbcl_scr_syn_anxdep_r", "B",
        "cbcl_scr_syn_withdep_r", "B",
        "cbcl_scr_syn_somatic_r", "B",
        "cbcl_scr_syn_social_r", "B",
        "cbcl_scr_syn_thought_r", "B",
        "cbcl_scr_syn_attention_r", "B",
        "cbcl_scr_syn_rulebreak_r", "B",
        "cbcl_scr_syn_aggressive_r", "B",
        "sds_p_ss_total", "B",
        "latest_mtbi_mechanism_fall_hit", "AS",
        "latest_mtbi_mechanism_multi", "AS",
        "latest_mtbi_mechanism_other_loc", "AS",
        "latest_mtbi_mechanism_vehicle", "AS",
        "latest_mtbi_mechanism_violent", "AS",
        "race_black", "D",
        "race_hispanic", "D",
        "race_other", "D"
    ),
    ncol = 2,
    byrow = TRUE
)

# Here i am! - Interesting missingness plots
overall_missing_cor_hm_1 <- ComplexHeatmap::Heatmap(
    missing_cor_mat_1,
    cluster_rows = TRUE,
    cluster_columns = TRUE,
    heatmap_legend_param = list(
        title = "Corr"
    ),
    column_names_gp = gpar(fontsize = 6),
    row_names_gp = gpar(fontsize = 6),
    column_split = non_x_map[, 2],
    row_split = x_map[, 2]
)

overall_missing_cor_hm_2 <- ComplexHeatmap::Heatmap(
    missing_cor_mat_2,
    cluster_rows = TRUE,
    cluster_columns = TRUE,
    heatmap_legend_param = list(
        title = "Corr"
    ),
    col = circlize::colorRamp2(
        c(-1, 0, 1),
        c("blue", "white", "red")
    ),
    column_names_gp = gpar(fontsize = 6),
    row_names_gp = gpar(fontsize = 6),
    column_split = x_map[, 2],
    row_split = x_map[, 2]
)

# Missingness vs. feature values
save_heatmap(
    heatmap = overall_missing_cor_hm_1,
    path = fig_path("overall_missing_cor_hm_1.png", TRUE),
    width = 1200,
    height = 1000,
    res = 100
)

# Missingness vs. missingness
save_heatmap(
    heatmap = overall_missing_cor_hm_2,
    path = fig_path("overall_missing_cor_hm_2.png", TRUE),
    width = 950,
    height = 900,
    res = 100
)
```

## Sex and Gender

The purpose of this subsection is to examine the distribution of children by their parent-reported genders and sexes at baseline with their own self-reported genders and sexes at the 3-year follow-up timepoint.

```{r}
gish_p_gi <- import("gender-identity-sexual-health/gish_p_gi.csv")
gish_y_gi <- import("gender-identity-sexual-health/gish_y_gi.csv")

mtbi_y_sex <- gish_y_gi |>
    filter_subjects(mtbi_subjects) |>
    filter_timepoint(t = 3) |>
    dplyr::select(
        subjectkey,
        kbi_sex_assigned_at_birth
    ) |>
    dplyr::rename(
        "y_sex" = "kbi_sex_assigned_at_birth"
    ) |>
    dplyr::mutate(group = "mtbi", t = 3) |>
    dplyr::mutate(
        y_sex = dplyr::case_when(
            y_sex == 1 ~ "M",
            y_sex == 2 ~ "F",
            TRUE ~ NA
        )
    )

uninj_y_sex <- gish_y_gi |>
    filter_subjects(uninjured_subjects) |>
    filter_timepoint(t = 3) |>
    dplyr::select(
        subjectkey,
        kbi_sex_assigned_at_birth
    ) |>
    dplyr::rename(
        "y_sex" = "kbi_sex_assigned_at_birth"
    ) |>
    dplyr::mutate(group = "uninj", t = 3) |>
    dplyr::mutate(
        y_sex = dplyr::case_when(
            y_sex == 1 ~ "M",
            y_sex == 2 ~ "F",
            TRUE ~ NA
        )
    )

mtbi_p_sex <- get_sex(
    gish_p_gi,
    mtbi_subjects,
    t = 0,
    as_numeric = FALSE,
    only_m_f = FALSE
) |>
    dplyr::mutate(group = "mtbi", t = 0)

uninj_p_sex <- get_sex(
    gish_p_gi,
    uninjured_subjects,
    t = 0,
    as_numeric = FALSE,
    only_m_f = FALSE
) |>
    dplyr::mutate(group = "uninj", t = 0)

mtbi_y_gender <- get_y_gender(
    gish_y_gi,
    mtbi_subjects,
    t = 3
) |>
    dplyr::mutate(group = "mtbi", t = 3)

uninj_y_gender <- get_y_gender(
    gish_y_gi,
    uninjured_subjects,
    t = 3
) |>
    dplyr::mutate(group = "uninj", t = 3)

mtbi_p_gender <- get_p_gender(
    gish_p_gi,
    mtbi_subjects,
    t = 0,
    match_y_report = TRUE
) |>
    dplyr::mutate(group = "mtbi", t = 0)

uninj_p_gender <- get_p_gender(
    gish_p_gi,
    uninjured_subjects,
    t = 0,
    match_y_report = TRUE
) |>
    dplyr::mutate(group = "uninj", t = 0)

y_sex <- rbind(mtbi_y_sex, uninj_y_sex)
y_gender <- rbind(mtbi_y_gender, uninj_y_gender)
p_sex <- rbind(mtbi_p_sex, uninj_p_sex)
p_gender <- rbind(mtbi_p_gender, uninj_p_gender)

y_report <- dplyr::full_join(y_sex, y_gender) |>
    dplyr::select(-t)

p_report <- dplyr::full_join(p_sex, p_gender) |>
    dplyr::rename("p_sex" = "sex") |>
    dplyr::select(-t)

sex_and_gender <- dplyr::full_join(
    y_report,
    p_report
)

sex_and_gender[is.na(sex_and_gender)] <- "NA"

sex_and_gender <- sex_and_gender |>
    dummy_cols(
        select_columns = c("y_sex", "y_gender", "p_sex", "p_gender"),
        remove_selected_columns = TRUE
    ) |>
    tibble()

sex_and_gender_mtbi <- sex_and_gender |>
    dplyr::filter(group == "mtbi")  |>
    dplyr::select(-group)

sex_and_gender_uninj <- sex_and_gender |>
    dplyr::filter(group == "uninj")  |>
    dplyr::select(-group)
```

### Gender Upset Plots

```{r}
gender_sets <- c(
    "p_gender_NB",
    "p_gender_NA",
    "y_gender_NB",
    "y_gender_NA",
    "y_gender_F",
    "y_gender_M",
    "p_gender_F",
    "p_gender_M"
)

gender_ints <- list(
    c("p_gender_M", "y_gender_M"),
    c("p_gender_F", "y_gender_F"),
    c("p_gender_F", "y_gender_NA"),
    c("p_gender_M", "y_gender_NA"),
    c("p_gender_F", "y_gender_NB"),
    c("p_gender_F", "y_gender_M"),
    c("p_gender_M", "y_gender_NB"),
    c("p_gender_M", "y_gender_F"),
    c("p_gender_NA", "y_gender_F"),
    c("p_gender_NA", "y_gender_M"),
    c("p_gender_NA", "y_gender_NB"),
    c("p_gender_NA", "y_gender_NA"),
    c("p_gender_NB", "y_gender_F"),
    c("p_gender_NB", "y_gender_NA"),
    c("p_gender_NB", "y_gender_NB")
)

uninj_gender_upset <- upset(
    sex_and_gender_uninj,
    gender_sets,
    intersections = gender_ints,
    name = "",
    sort_sets = FALSE,
    sort_intersections = FALSE
) +
    ggtitle("Uninjured") +
    theme(text = element_text(size = 14))

mtbi_gender_upset <- upset(
    sex_and_gender_mtbi,
    gender_sets,
    intersections = gender_ints,
    name = "Gender Identity",
    sort_sets = FALSE,
    sort_intersections = FALSE
) +
    ggtitle("mTBI") +
    theme(text = element_text(size = 14))

gender_upset_plots <- uninj_gender_upset / mtbi_gender_upset

gender_upset_plots

pdf(fig_path("gender_upset_plots.pdf", TRUE), width = 10, height = 10)
print(gender_upset_plots)
dev.off()
```

### Sex Upset Plots

```{r}
sex_sets <- c(
    "p_sex_IM",
    "y_sex_NA",
    "y_sex_F",
    "y_sex_M",
    "p_sex_F",
    "p_sex_M"
)

sex_ints <- list(
    c("p_sex_M", "y_sex_M"),
    c("p_sex_F", "y_sex_F"),
    c("p_sex_M", "y_sex_NA"),
    c("p_sex_F", "y_sex_NA"),
    c("p_sex_M", "y_sex_F"),
    c("p_sex_F", "y_sex_M"),
    c("y_sex_M", "p_sex_IM")
)

mtbi_sex_upset <- upset(
    sex_and_gender_mtbi,
    sex_sets,
    intersections = sex_ints,
    name = "Sex at Birth",
    sort_sets = FALSE,
    sort_intersections = FALSE
) +
    ggtitle("mTBI") +
    theme(text = element_text(size = 14))
uninj_sex_upset <- upset(
    sex_and_gender_uninj,
    sex_sets,
    intersections = sex_ints,
    name = "Sex at Birth",
    sort_sets = FALSE,
    sort_intersections = FALSE
) +
    ggtitle("Uninjured") +
    theme(text = element_text(size = 14))
sex_upset_plots <- uninj_sex_upset / mtbi_sex_upset

sex_upset_plots

pdf(fig_path("sex_upset_plots.pdf", TRUE), width = 10, height = 10)
print(sex_upset_plots)
dev.off()
```

### Parent Report Upset Plots

```{r}

parent_sets <- c(
    "p_gender_NB",
    "p_gender_NA",
    "p_gender_F",
    "p_gender_M",
    "p_sex_IM",
    "p_sex_F",
    "p_sex_M"
)

parent_ints <- list(
    c("p_sex_M", "p_gender_M"),
    c("p_sex_F", "p_gender_F"),
    c("p_sex_F", "p_gender_NA"),
    c("p_sex_M", "p_gender_NB"),
    c("p_sex_F", "p_gender_NB"),
    c("p_gender_M", "p_sex_IM"),
    c("p_sex_M", "p_gender_F"), 
    c("p_sex_M", "p_gender_NA"), 
    c("p_gender_M", "p_sex_F")
)

mtbi_parent_sag <- upset(
    sex_and_gender_mtbi,
    intersect = parent_sets,
    intersections = parent_ints,
    set_sizes = FALSE,
    sort_sets = FALSE,
    sort_intersections = FALSE
) +
    ggtitle("mTBI") +
    theme(text = element_text(size = 14))

uninj_parent_sag <- upset(
    sex_and_gender_uninj,
    intersect = parent_sets,
    intersections = parent_ints,
    set_sizes = FALSE,
    sort_sets = FALSE,
    sort_intersections = FALSE
) +
    ggtitle("Uninjured") +
    theme(text = element_text(size = 14))

parent_sag <- wrap_plots(
    list(
        uninj_parent_sag,
        mtbi_parent_sag
    ),
    ncol = 1
)

pdf(fig_path("parent_sag", TRUE), width = 10, height = 10)
print(parent_sag)
dev.off()

```

```{r}

youth_sets <- c(
    "y_gender_NB",
    "y_gender_NA",
    "y_gender_F",
    "y_gender_M",
    "y_sex_NA",
    "y_sex_F",
    "y_sex_M"
)

youth_ints <- list(
    c("y_sex_M", "y_gender_M"),
    c("y_sex_F", "y_gender_F"),
    c("y_sex_NA", "y_gender_NA"), 
    c("y_sex_F", "y_gender_NB"),
    c("y_gender_M", "y_sex_NA"),
    c("y_gender_F", "y_sex_NA"),
    c("y_sex_F", "y_gender_NA"),
    c("y_gender_M", "y_sex_F"),
    c("y_sex_M", "y_gender_NA"),
    c("y_sex_M", "y_gender_NB"),
    c("y_sex_M", "y_gender_F")
)

mtbi_youth_sag <- upset(
    sex_and_gender_mtbi,
    intersect = youth_sets,
    intersections = youth_ints,
    set_sizes = FALSE,
    sort_sets = FALSE,
    sort_intersections = FALSE
) +
    ggtitle("mTBI") +
    theme(text = element_text(size = 14))

uninj_youth_sag <- upset(
    sex_and_gender_uninj,
    intersect = youth_sets,
    intersections = youth_ints,
    set_sizes = FALSE,
    sort_sets = FALSE,
    sort_intersections = FALSE
) +
    ggtitle("Uninjured") +
    theme(text = element_text(size = 14))

youth_sag <- wrap_plots(
    list(
        uninj_youth_sag,
        mtbi_youth_sag
    ),
    ncol = 1
)

age_split_sag <- wrap_plots(
    list(parent_sag, youth_sag),
    nrow = 2, ncol = 2
)

pdf(fig_path("age_split_sag.pdf", TRUE), width = 20, height = 20)
print(age_split_sag)
dev.off()
```

## Other features

```{r}
as_mem_daze_mtbi <- read("2024_07_31_as_mem_daze_mtbi.csv")
as_mechanism_mtbi <- read("2024_07_31_as_mechanism_mtbi.csv")
as_loc_mtbi <- read("2024_07_31_as_loc_mtbi.csv")
d_interview_age_mtbi <- read("2024_07_31_d_interview_age_mtbi.csv")
d_mtbi_age_mtbi <- read("2024_07_31_d_mtbi_age_mtbi.csv")
d_sex_mtbi <- read("2024_07_31_d_sex_mtbi.csv")
d_income_mtbi <- read("2024_07_31_d_income_mtbi.csv")
d_race_mtbi <- read("2024_07_31_d_race_mtbi.csv")
d_pubertal_status_mtbi <- read("2024_07_31_d_pubertal_status_mtbi.csv")
mh_headaches_mtbi <- read("2024_07_31_mh_headaches_mtbi.csv")
mh_mtbi_count_mtbi <- read("2024_07_31_mh_mtbi_count_mtbi.csv")
sm_subc_v_mtbi <- read("2024_07_31_sm_subc_v_mtbi.csv")
sm_cort_t_mtbi <- read("2024_07_31_sm_cort_t_mtbi.csv")
sm_cort_sa_mtbi <- read("2024_07_31_sm_cort_sa_mtbi.csv")
dm_all_wmnd_mtbi <- read("2024_07_31_dm_all_wmnd_mtbi.csv")
rm_gord_cor_mtbi <- read("2024_07_31_rm_gord_cor_mtbi.csv")
rm_subc_cor_mtbi <- read("2024_07_31_rm_subc_cor_mtbi.csv")
p_loneliness_mtbi <- read("2024_07_31_p_loneliness_mtbi.csv")
p_screen_time_mtbi <- read("2024_07_31_p_screen_time_mtbi.csv")
p_sports_mtbi <- read("2024_07_31_p_sports_mtbi.csv")
p_exercise_mtbi <- read("2024_07_31_p_exercise_mtbi.csv")
p_prosocial_mtbi <- read("2024_07_31_p_prosocial_mtbi.csv")
p_fam_fn_mtbi <- read("2024_07_31_p_fam_fn_mtbi.csv")
p_parent_psych_mtbi <- read("2024_07_31_p_parent_psych_mtbi.csv")
cbcl_anxdep_mtbi <- read("2024_07_31_cbcl_anxdep_mtbi.csv")
cbcl_withdep_mtbi <- read("2024_07_31_cbcl_withdep_mtbi.csv")
cbcl_somatic_mtbi <- read("2024_07_31_cbcl_somatic_mtbi.csv")
cbcl_social_mtbi <- read("2024_07_31_cbcl_social_mtbi.csv")
cbcl_thought_mtbi <- read("2024_07_31_cbcl_thought_mtbi.csv")
cbcl_attention_mtbi <- read("2024_07_31_cbcl_attention_mtbi.csv")
cbcl_rulebreak_mtbi <- read("2024_07_31_cbcl_rulebreak_mtbi.csv")
cbcl_aggressive_mtbi <- read("2024_07_31_cbcl_aggressive_mtbi.csv")
sds_total_probs_mtbi <- read("2024_07_31_sds_total_probs_mtbi.csv")

# Uninjured subjects
d_interview_age_uninj <- read("2024_07_31_d_interview_age_uninj.csv")
d_sex_uninj <- read("2024_07_31_d_sex_uninj.csv")
d_income_uninj <- read("2024_07_31_d_income_uninj.csv")
d_race_uninj <- read("2024_07_31_d_race_uninj.csv")
d_pubertal_status_uninj <- read("2024_07_31_d_pubertal_status_uninj.csv")
mh_headaches_uninj <- read("2024_07_31_mh_headaches_uninj.csv")
sm_subc_v_uninj <- read("2024_07_31_sm_subc_v_uninj.csv")
sm_cort_t_uninj <- read("2024_07_31_sm_cort_t_uninj.csv")
sm_cort_sa_uninj <- read("2024_07_31_sm_cort_sa_uninj.csv")
dm_all_wmnd_uninj <- read("2024_07_31_dm_all_wmnd_uninj.csv")
rm_gord_cor_uninj <- read("2024_07_31_rm_gord_cor_uninj.csv")
rm_subc_cor_uninj <- read("2024_07_31_rm_subc_cor_uninj.csv")
p_loneliness_uninj <- read("2024_07_31_p_loneliness_uninj.csv")
p_screen_time_uninj <- read("2024_07_31_p_screen_time_uninj.csv")
p_sports_uninj <- read("2024_07_31_p_sports_uninj.csv")
p_exercise_uninj <- read("2024_07_31_p_exercise_uninj.csv")
p_prosocial_uninj <- read("2024_07_31_p_prosocial_uninj.csv")
p_fam_fn_uninj <- read("2024_07_31_p_fam_fn_uninj.csv")
p_parent_psych_uninj <- read("2024_07_31_p_parent_psych_uninj.csv")
cbcl_anxdep_uninj <- read("2024_07_31_cbcl_anxdep_uninj.csv")
cbcl_withdep_uninj <- read("2024_07_31_cbcl_withdep_uninj.csv")
cbcl_somatic_uninj <- read("2024_07_31_cbcl_somatic_uninj.csv")
cbcl_social_uninj <- read("2024_07_31_cbcl_social_uninj.csv")
cbcl_thought_uninj <- read("2024_07_31_cbcl_thought_uninj.csv")
cbcl_attention_uninj <- read("2024_07_31_cbcl_attention_uninj.csv")
cbcl_rulebreak_uninj <- read("2024_07_31_cbcl_rulebreak_uninj.csv")
cbcl_aggressive_uninj <- read("2024_07_31_cbcl_aggressive_uninj.csv")
sds_total_probs_uninj <- read("2024_07_31_sds_total_probs_uninj.csv")
```

## mTBI vs. Uninj Initial Comparisons

```{r}
mtbi_initial_df_list <- list(
    as_mem_daze_mtbi,
    as_mechanism_mtbi,
    as_loc_mtbi,
    d_interview_age_mtbi,
    d_mtbi_age_mtbi,
    d_sex_mtbi,
    d_income_mtbi,
    d_race_mtbi,
    d_pubertal_status_mtbi,
    mh_headaches_mtbi,
    mh_mtbi_count_mtbi,
    sm_subc_v_mtbi,
    sm_cort_t_mtbi,
    sm_cort_sa_mtbi,
    dm_all_wmnd_mtbi,
    rm_gord_cor_mtbi,
    rm_subc_cor_mtbi,
    p_loneliness_mtbi,
    p_screen_time_mtbi,
    p_sports_mtbi,
    p_exercise_mtbi,
    p_prosocial_mtbi,
    p_fam_fn_mtbi,
    p_parent_psych_mtbi,
    cbcl_anxdep_mtbi,
    cbcl_withdep_mtbi,
    cbcl_somatic_mtbi,
    cbcl_social_mtbi,
    cbcl_thought_mtbi,
    cbcl_attention_mtbi,
    cbcl_rulebreak_mtbi,
    cbcl_aggressive_mtbi,
    sds_total_probs_mtbi
)

uninj_initial_df_list <- list(
    d_interview_age_uninj,
    d_sex_uninj,
    d_income_uninj,
    d_race_uninj,
    d_pubertal_status_uninj,
    mh_headaches_uninj,
    sm_subc_v_uninj,
    sm_cort_t_uninj,
    sm_cort_sa_uninj,
    dm_all_wmnd_uninj,
    rm_gord_cor_uninj,
    rm_subc_cor_uninj,
    p_loneliness_uninj,
    p_screen_time_uninj,
    p_sports_uninj,
    p_exercise_uninj,
    p_prosocial_uninj,
    p_fam_fn_uninj,
    p_parent_psych_uninj,
    cbcl_anxdep_uninj,
    cbcl_withdep_uninj,
    cbcl_somatic_uninj,
    cbcl_social_uninj,
    cbcl_thought_uninj,
    cbcl_attention_uninj,
    cbcl_rulebreak_uninj,
    cbcl_aggressive_uninj,
    sds_total_probs_uninj
)

mtbi_initial_df <- merge_df_list(mtbi_initial_df_list, join = "full")
uninj_initial_df <- merge_df_list(uninj_initial_df_list, join = "full")

nrow(mtbi_initial_df)

baseline_initial_df <- bind_rows(mtbi_initial_df, uninj_initial_df)

expect it is all diffuse global is fine
```

## Correlation analyse

```{r}
all_dls <- readRDS(input_path("2025_02_10_all_dls.rds"))

mtbi_train_dl_s1 <- c(all_dls$"mtbi_train_data_lists"[[1]], all_dls$"mtbi_train_oom_lists"[[1]])

mtbi_train_dl_s2 <- c(all_dls$"mtbi_train_data_lists"[[2]], all_dls$"mtbi_train_oom_lists"[[2]])
mtbi_train_dl_s3 <- c(all_dls$"mtbi_train_data_lists"[[3]], all_dls$"mtbi_train_oom_lists"[[3]])
mtbi_train_dl_s4 <- c(all_dls$"mtbi_train_data_lists"[[4]], all_dls$"mtbi_train_oom_lists"[[4]])
mtbi_train_dl_s5 <- c(all_dls$"mtbi_train_data_lists"[[5]], all_dls$"mtbi_train_oom_lists"[[5]])

mtbi_test_dl_s1 <- c(all_dls$"mtbi_test_data_lists"[[1]], all_dls$"mtbi_test_oom_lists"[[1]])
mtbi_test_dl_s2 <- c(all_dls$"mtbi_test_data_lists"[[2]], all_dls$"mtbi_test_oom_lists"[[2]])
mtbi_test_dl_s3 <- c(all_dls$"mtbi_test_data_lists"[[3]], all_dls$"mtbi_test_oom_lists"[[3]])
mtbi_test_dl_s4 <- c(all_dls$"mtbi_test_data_lists"[[4]], all_dls$"mtbi_test_oom_lists"[[4]])
mtbi_test_dl_s5 <- c(all_dls$"mtbi_test_data_lists"[[5]], all_dls$"mtbi_test_oom_lists"[[5]])

mtbi_pooled_dl_s1 <- c(all_dls$"mtbi_pooled_data_lists"[[1]], all_dls$"mtbi_pooled_oom_lists"[[1]])
mtbi_pooled_dl_s2 <- c(all_dls$"mtbi_pooled_data_lists"[[2]], all_dls$"mtbi_pooled_oom_lists"[[2]])
mtbi_pooled_dl_s3 <- c(all_dls$"mtbi_pooled_data_lists"[[3]], all_dls$"mtbi_pooled_oom_lists"[[3]])
mtbi_pooled_dl_s4 <- c(all_dls$"mtbi_pooled_data_lists"[[4]], all_dls$"mtbi_pooled_oom_lists"[[4]])
mtbi_pooled_dl_s5 <- c(all_dls$"mtbi_pooled_data_lists"[[5]], all_dls$"mtbi_pooled_oom_lists"[[5]])

unij_dl_s1 <- c(all_dls$"unij_data_lists"[[1]], all_dls$"unij_oom_lists"[[1]])

unij_dl_s2 <- c(all_dls$"unij_data_lists"[[2]], all_dls$"unij_oom_lists"[[2]])
unij_dl_s3 <- c(all_dls$"unij_data_lists"[[3]], all_dls$"unij_oom_lists"[[3]])
unij_dl_s4 <- c(all_dls$"unij_data_lists"[[4]], all_dls$"unij_oom_lists"[[4]])
unij_dl_s5 <- c(all_dls$"unij_data_lists"[[5]], all_dls$"unij_oom_lists"[[5]])
unij_pooled_dl_s1 <- c(all_dls$"unij_pooled_data_lists"[[1]], all_dls$"unij_pooled_oom_lists"[[1]])
unij_pooled_dl_s2 <- c(all_dls$"unij_pooled_data_lists"[[2]], all_dls$"unij_pooled_oom_lists"[[2]])
unij_pooled_dl_s3 <- c(all_dls$"unij_pooled_data_lists"[[3]], all_dls$"unij_pooled_oom_lists"[[3]])
unij_pooled_dl_s4 <- c(all_dls$"unij_pooled_data_lists"[[4]], all_dls$"unij_pooled_oom_lists"[[4]])
unij_pooled_dl_s5 <- c(all_dls$"unij_pooled_data_lists"[[5]], all_dls$"unij_pooled_oom_lists"[[5]])
```

```{r}
dls <- list(
    "mtbi_train_dl_s1" = mtbi_train_dl_s1,
    "mtbi_train_dl_s2" = mtbi_train_dl_s2,
    "mtbi_train_dl_s3" = mtbi_train_dl_s3,
    "mtbi_train_dl_s4" = mtbi_train_dl_s4,
    "mtbi_train_dl_s5" = mtbi_train_dl_s5,
    "mtbi_pooled_dl_s1" = mtbi_pooled_dl_s1,
    "mtbi_pooled_dl_s2" = mtbi_pooled_dl_s2,
    "mtbi_pooled_dl_s3" = mtbi_pooled_dl_s3,
    "mtbi_pooled_dl_s4" = mtbi_pooled_dl_s4,
    "mtbi_pooled_dl_s5" = mtbi_pooled_dl_s5,
    "unij_dl_s1" = unij_dl_s1,
    "unij_dl_s2" = unij_dl_s2,
    "unij_dl_s3" = unij_dl_s3,
    "unij_dl_s4" = unij_dl_s4,
    "unij_dl_s5" = unij_dl_s5,
    "unij_pooled_dl_s1" = unij_pooled_dl_s1,
    "unij_pooled_dl_s2" = unij_pooled_dl_s2,
    "unij_pooled_dl_s3" = unij_pooled_dl_s3,
    "unij_pooled_dl_s4" = unij_pooled_dl_s4,
    "unij_pooled_dl_s5" = unij_pooled_dl_s5
)

mtbi_train_dl_s1 |>
    as.data.frame() |>
    dplyr::select(-uid, -dplyr::starts_with("mtbi")) |>
    dummy_cols(
        select_columns = "race",
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = TRUE
    ) |>
    cor() |>
    ComplexHeatmap::Heatmap()

cor_mats <- lapply(
    dls,
    function(x) {
        x |>
        as.data.frame() |>
        dplyr::select(-uid, -dplyr::contains("mtbi")) |>
        dummy_cols(
            select_columns = "race",
            remove_selected_columns = TRUE,
            remove_most_frequent_dummy = TRUE
        ) |>
        cor()
    }
)

order <- get_matrix_order(cor_mats[[1]])

cor_mats <- lapply(
    cor_mats,
    function(x) {
        x[order, order]
    }
)

saveRDS(cor_mats, proc_path("baseline_cor_mats.rds", TRUE))

cor_mats <- readRDS(proc_path("2025_02_18_baseline_cor_mats.rds"))

make_and_save_heatmap <- function(mat, filename = NULL, save = TRUE) {
    hm <- ComplexHeatmap::Heatmap(
        mat,
        cluster_rows = FALSE,
        cluster_columns = FALSE,
        heatmap_legend_param = list(
            title = "Corr"
        ),
        column_names_gp = gpar(fontsize = 8),
        row_names_gp = gpar(fontsize = 8)
    )
    if (save) {
        save_heatmap(
            heatmap = hm,
            path = fig_path(filename, TRUE),
            width = 1000,
            height = 900,
            res = 100
        )
    } else {
        return(hm)
    }
}

# Imputation variations are minor, but uninjured to injured has a notable difference
make_and_save_heatmap(cor_mats[[1]], "baseline_cor_mat_s1.png")
make_and_save_heatmap(cor_mats[[2]], "baseline_cor_mat_s2.png")
make_and_save_heatmap(cor_mats[[3]], "baseline_cor_mat_s3.png")
make_and_save_heatmap(cor_mats[[4]], "baseline_cor_mat_s4.png")
make_and_save_heatmap(cor_mats[[5]], "baseline_cor_mat_s5.png")
make_and_save_heatmap(cor_mats[[6]], "baseline_cor_mat_p1.png")
make_and_save_heatmap(cor_mats[[7]], "baseline_cor_mat_p2.png")
make_and_save_heatmap(cor_mats[[8]], "baseline_cor_mat_p3.png")
make_and_save_heatmap(cor_mats[[9]], "baseline_cor_mat_p4.png")
make_and_save_heatmap(cor_mats[[10]], "baseline_cor_mat_p5.png")
make_and_save_heatmap(cor_mats[[11]], "baseline_cor_mat_u1.png")
make_and_save_heatmap(cor_mats[[12]], "baseline_cor_mat_u2.png")
make_and_save_heatmap(cor_mats[[13]], "baseline_cor_mat_u3.png")
make_and_save_heatmap(cor_mats[[14]], "baseline_cor_mat_u4.png")
make_and_save_heatmap(cor_mats[[15]], "baseline_cor_mat_u5.png")
make_and_save_heatmap(cor_mats[[16]], "baseline_cor_mat_up1.png")
make_and_save_heatmap(cor_mats[[17]], "baseline_cor_mat_up2.png")
make_and_save_heatmap(cor_mats[[18]], "baseline_cor_mat_up3.png")
make_and_save_heatmap(cor_mats[[19]], "baseline_cor_mat_up4.png")
make_and_save_heatmap(cor_mats[[20]], "baseline_cor_mat_up5.png")
```

These are taken from chapter 8 - longitudinal analyses.

The pre and post injury data lists for the longitudinal mTBI sample.


```{r}

long_mtbi_0_dls <- all_long_dls$"long_mtbi_0_dls"
long_mtbi_l_dls <- all_long_dls$"long_mtbi_l_dls"
long_mtbi_0_ols <- all_long_dls$"long_mtbi_0_ols"
long_mtbi_l_ols <- all_long_dls$"long_mtbi_l_ols"

long_mtbi_0_all_dls <- lapply(
    1:5,
    function(x) {
        c(long_mtbi_0_dls[[x]], long_mtbi_0_ols[[x]])
    }
)

long_mtbi_l_all_dls <- lapply(
    1:5,
    function(x) {
        c(long_mtbi_l_dls[[x]], long_mtbi_l_ols[[x]])
    }
)

long_dls <- c(long_mtbi_0_all_dls, long_mtbi_l_all_dls)

cor_mats_long <- lapply(
    long_dls,
    function(x) {
        x |>
        as.data.frame() |>
        dplyr::select(-uid, -dplyr::contains("mtbi")) |>
        dummy_cols(
            select_columns = "race",
            remove_selected_columns = TRUE,
            remove_most_frequent_dummy = TRUE
        ) |>
        cor()
    }
)

cor_mat_names <- colnames(cor_mats[[1]])

saveRDS(cor_mat_names, proc_path("cor_mat_names.rds", TRUE))
```

```{r}
cor_mat_names <- readRDS(proc_path("2025_02_26_cor_mat_names.rds"))

cor_mats_long <- lapply(
    cor_mats_long,
    function(x) {
        x[colnames(cor_mats[[1]]), colnames(cor_mats[[1]])]
    }
)

saveRDS(cor_mats_long, proc_path("longitudinal_cor_mats_long.rds", TRUE))

cor_mats_long <- readRDS(proc_path("2025_02_18_longitudinal_cor_mats_long.rds"))

make_and_save_heatmap(cor_mats_long[[1]], "long_cor_mat_preinj_1.png")
make_and_save_heatmap(cor_mats_long[[2]], "long_cor_mat_preinj_2.png")
make_and_save_heatmap(cor_mats_long[[3]], "long_cor_mat_preinj_3.png")
make_and_save_heatmap(cor_mats_long[[4]], "long_cor_mat_preinj_4.png")
make_and_save_heatmap(cor_mats_long[[5]], "long_cor_mat_preinj_5.png")
make_and_save_heatmap(cor_mats_long[[6]], "long_cor_mat_postinj_1.png")
make_and_save_heatmap(cor_mats_long[[7]], "long_cor_mat_postinj_2.png")
make_and_save_heatmap(cor_mats_long[[8]], "long_cor_mat_postinj_3.png")
make_and_save_heatmap(cor_mats_long[[9]], "long_cor_mat_postinj_4.png")
make_and_save_heatmap(cor_mats_long[[10]], "long_cor_mat_postinj_5.png")
```

```{r}
# Baseline mTBI
base_mtbi_avg_cors <- lapply(
    1:10,
    function(x) {
        mean(abs(cor_mats[[x]]))
    }
) |> unlist()

# Baseline uninjured
base_unij_avg_cors <- lapply(
    11:20,
    function(x) {
        mean(abs(cor_mats[[x]]))
    }
) |> unlist()

# Long mTBI preinjury
long_mtbi_0_avg_cors <- lapply(
    1:5,
    function(x) {
        mean(abs(cor_mats_long[[x]]))
    }
) |> unlist()

# Long mTBI postinjury
long_mtbi_1_avg_cors <- lapply(
    6:10,
    function(x) {
        mean(abs(cor_mats_long[[x]]))
    }
) |> unlist()

avg_cor_plot <- data.frame(
    group = c(
        rep("Baseline mTBI", 10),
        rep("Baseline uninjured", 10),
        rep("Longitudinal mTBI, pre-injury", 5),
        rep("Longitudinal mTBI, post-injury", 5)
    ),
    avg_cor = c(
        base_mtbi_avg_cors,
        base_unij_avg_cors,
        long_mtbi_0_avg_cors,
        long_mtbi_1_avg_cors
    )
) |>
    ggplot(aes(x = group, y = avg_cor)) +
    geom_jitter(width = 0.1, height = 0, alpha = 0.5) +
    labs(
        y = "Mean Absolute Correlation",
        x = "Group"
    ) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
ggsave(
    fig_path("avg_cor_plot.png", TRUE),
    avg_cor_plot,
    width = 5,
    height = 5,
    dpi = 120
)
```

Getting more specific

```{r}

# Baseline mTBI
base_mtbi_avg_cors2 <- c(
    mean(abs(cor_mats[[1]][1:33, 1:33])),
    mean(abs(cor_mats[[2]][1:33, 1:33])),
    mean(abs(cor_mats[[3]][1:33, 1:33])),
    mean(abs(cor_mats[[4]][1:33, 1:33])),
    mean(abs(cor_mats[[5]][1:33, 1:33])),
    mean(abs(cor_mats[[6]][1:33, 1:33])),
    mean(abs(cor_mats[[7]][1:33, 1:33])),
    mean(abs(cor_mats[[8]][1:33, 1:33])),
    mean(abs(cor_mats[[9]][1:33, 1:33])),
    mean(abs(cor_mats[[10]][1:33, 1:33]))
)

# Baseline unij
base_unij_avg_cors2 <- c(
    mean(abs(cor_mats[[11]][1:33, 1:33])),
    mean(abs(cor_mats[[12]][1:33, 1:33])),
    mean(abs(cor_mats[[13]][1:33, 1:33])),
    mean(abs(cor_mats[[14]][1:33, 1:33])),
    mean(abs(cor_mats[[15]][1:33, 1:33])),
    mean(abs(cor_mats[[16]][1:33, 1:33])),
    mean(abs(cor_mats[[17]][1:33, 1:33])),
    mean(abs(cor_mats[[18]][1:33, 1:33])),
    mean(abs(cor_mats[[19]][1:33, 1:33])),
    mean(abs(cor_mats[[20]][1:33, 1:33]))
)

# Pre-injury
long_mtbi_0_avg_cors2 <- c(
    mean(abs(cor_mats_long[[1]][1:33, 1:33])),
    mean(abs(cor_mats_long[[2]][1:33, 1:33])),
    mean(abs(cor_mats_long[[3]][1:33, 1:33])),
    mean(abs(cor_mats_long[[4]][1:33, 1:33])),
    mean(abs(cor_mats_long[[5]][1:33, 1:33]))
)

# Post-injury
long_mtbi_1_avg_cors2 <- c(
    mean(abs(cor_mats_long[[6]][1:33, 1:33])),
    mean(abs(cor_mats_long[[7]][1:33, 1:33])),
    mean(abs(cor_mats_long[[8]][1:33, 1:33])),
    mean(abs(cor_mats_long[[9]][1:33, 1:33])),
    mean(abs(cor_mats_long[[10]][1:33, 1:33]))
)

avg_cor_plot2 <- data.frame(
    group = c(
        rep("Baseline mTBI", 10),
        rep("Baseline uninjured", 10),
        rep("Longitudinal mTBI, pre-injury", 5),
        rep("Longitudinal mTBI, post-injury", 5)
    ),
    avg_cor = c(
        base_mtbi_avg_cors2,
        base_unij_avg_cors2,
        long_mtbi_0_avg_cors2,
        long_mtbi_1_avg_cors2
    )
) |>
    ggplot(aes(x = group, y = avg_cor)) +
    geom_jitter(width = 0.1, height = 0, alpha = 0.5) +
    labs(
        y = "Mean Absolute Correlation",
        x = "Group"
    ) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

avg_cor_plot2

ggsave(
    fig_path("avg_cor_plot2.png", TRUE),
    avg_cor_plot2,
    width = 5,
    height = 5,
    dpi = 120
)


#make_and_save_heatmap(cor_mats[[1]][1:21, 1:33], save = FALSE)

```

## Permutation testing correlation comparisons

First, a simple permutation test comparing the first mTBI correlation sample with the first uninjured correlation sample.

```{r}
mtbi_full_train_dl_1 <- merge(mtbi_train_dl_s1, mtbi_test_dl_s1)

mtbi_df_1 <- mtbi_full_train_dl_1 |>
    as.data.frame() |>
    dplyr::select(-uid, -dplyr::contains("mtbi")) |>
    dummy_cols(
        select_columns = "race",
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = TRUE
    )

unij_df_1 <- unij_dl_s1 |>
    as.data.frame() |>
    dplyr::select(-uid, -dplyr::contains("mtbi")) |>
    dummy_cols(
        select_columns = "race",
        remove_selected_columns = TRUE,
        remove_most_frequent_dummy = TRUE
    )

cor_mat_names <- readRDS(proc_path("2025_02_26_cor_mat_names.rds"))

# Effect of sample size on correlation
sample_size_cor_df <- data.frame()
for (i in c(1:50)) {
    for (n in c(50, 100, 250, 500, 1000, 2000, 5000)) {
        print(n)
        cor <- mean(
            abs(
                cor(
                    unij_df_1[sample(nrow(unij_df_1), size = n), ]
                )
            )
        )
        sample_size_cor_df <- rbind(
            sample_size_cor_df,
            data.frame(
                n = n,
                cor = cor
            )
        )
    }
}

sample_size_cor_plot <- sample_size_cor_df |>
    ggplot(
        aes(x = factor(n), y = cor)
    ) +
    geom_jitter(width = 0.1) +
    theme_bw() +
    labs(x = "Sample size", y = "Mean Absolute Correlation") +
    theme(text = element_text(size = 15))
sample_size_cor_plot

ggsave(
    fig_path("sample_size_cor_plot.png", TRUE),
    sample_size_cor_plot,
    width = 5,
    height = 5,
    dpi = 120
)

# Non-Absolute value version
sample_size_non_abs_cor_df <- data.frame()
for (i in c(1:50)) {
    for (n in c(50, 100, 250, 500, 1000, 2000, 5000)) {
        print(n)
        cor <- mean(
            cor(
                unij_df_1[sample(nrow(unij_df_1), size = n), ]
            )
        )
        sample_size_non_abs_cor_df <- rbind(
            sample_size_non_abs_cor_df,
            data.frame(
                n = n,
                cor = cor
            )
        )
    }
}

sample_size_non_abs_cor_plot <- sample_size_non_abs_cor_df |>
    ggplot(
        aes(x = factor(n), y = cor)
    ) +
    geom_jitter(width = 0.1) +
    theme_bw() +
    labs(x = "Sample size", y = "Mean Correlation") +
    theme(text = element_text(size = 15))
sample_size_non_abs_cor_plot

ggsave(
    fig_path("sample_size_non_abs_cor_plot.png", TRUE),
    sample_size_non_abs_cor_plot,
    width = 5,
    height = 5,
    dpi = 120
)

```

After creating a correlation matrix, it is necessary to remove the diagonal values and the lower triangle of the matrix to avoid double counting.

```{r}
upper_tri_cor <- function(df) {
    cor_df <- cor(df)
    return(mean(abs(cor_df[upper.tri(cor_df)])))
}

# Distribution of upper triangle MACs, uninjured sample
set.seed(42)
unij_cor_dist <- c()
for (i in 1:10000) {
    print(i)
    sampled_df <- unij_df_1[sample(nrow(unij_df_1), size = 437), ]
    unij_cor_dist <- c(unij_cor_dist, upper_tri_cor(sampled_df))
}

saveRDS(unij_cor_dist, proc_path("unij_mac_dist.rds", TRUE))

unij_cor_dist <- readRDS(proc_path("2025_02_27_unij_mac_dist.rds"))

unij_mac_hist <- data.frame(mac = unij_cor_dist) |>
    ggplot(
        aes(x = mac)
    ) +
    geom_histogram(color = "gray") +
    theme_bw() +
    labs(x = "Mean Average Correlation", y = "Count") +
    geom_vline(
        aes(
            xintercept = upper_tri_cor(mtbi_df_1)
        ),
        color = "red"
    )

ggsave(
    plot = unij_mac_hist,
    fig_path("unij_mac_hist.png", TRUE),
    width = 5,
    height = 5,
    dpi = 120
)

unij_cor_dist > upper_tri_cor(mtbi_df_1)
```

## Alternative approach

Pick a random sample, then permutation test the difference in MACs.
Repeat for perhaps 100 samples?

```{r}
perm_test <- function(df1, df2, n = 2000) {
    # MAC for DF1
    mac1 <- upper_tri_cor(df1)
    # MAC for random sampled DF2
    observed_df2 <- df2[sample(nrow(df2), size = nrow(df1)), ]
    mac2 <- upper_tri_cor(observed_df2)
    # "Observed difference"
    diff <- mac1 - mac2
    diff_dist <- c()
    for (i in 1:n) {
        full_df <- rbind(df1, observed_df2)
        full_df <- full_df[sample(nrow(full_df)), ]
        diff_dist <- c(
            diff_dist,
            upper_tri_cor(full_df[1:nrow(df1), ]) - upper_tri_cor(full_df[(nrow(df1) + 1):nrow(full_df), ])
        )
    }
    return(sum(diff <= diff_dist))
}
z <- perm_test(mtbi_df_1, unij_df_1, n = 1000)
z

future::plan(future::multisession, workers = 64)

progressr::handlers(global = TRUE)  # Use a global handler to update progress

progressr::with_progress({
p <- progressr::progressor(steps = 1000) 
perm_test_dist <- future.apply::future_lapply(
    1:1000,
    function(x) {
        result <- perm_test(mtbi_df_1, unij_df_1, n = 1000)
        p()      
        return(result)
    },
    future.seed = TRUE
)
})
saveRDS(perm_test_dist, proc_path("perm_test_dist.rds", TRUE))

perm_test_dist <- readRDS(proc_path("2025_02_27_perm_test_dist.rds"))

perm_test_dist_plot <- data.frame(
    p = unlist(perm_test_dist)
) |>
    ggplot(
        aes(x = p)
    ) +
    geom_histogram(fill = "black", binwidth = 0.002) +
    theme_bw() +
    theme(text = element_text(size = 15)) +
    labs(x = "p-value", y = "Count") +
    geom_vline(
        aes(
            xintercept = 0.05
        ),
        color = "red"
    )
ggsave(
    plot = perm_test_dist_plot,
    fig_path("perm_test_dist_plot.png", TRUE),
    width = 5,
    height = 3,
    dpi = 200
)

unlist(perm_test_dist) |> hist()

print(Sys.time() - start)
```

## Repeating both approaches for only the top left set of correlations

```{r}
upper_tri_top_cor <- function(df) {
    cor_df <- cor(df)
    cor_df <- cor_df[cor_mat_names, cor_mat_names]
    cor_df <- cor_df[grepl("^cbcl|^sds", cor_mat_names), !grepl("^cbcl|^sds", cor_mat_names)]
    return(mean(abs(cor_df)))
}

upper_tri_top_cor(mtbi_df_1)

upper_tri_top_cor(unij_df_1)
```
