# Moderate/Severe TBI examination

```{r}
library(ggplot2)
library(readr)
library(dplyr)
library(here)
library(abcdutils)
library(visdat)

core_path <- path_maker(here::here("data/abcd/core"))
input_path <- path_maker(here::here("data/abcd/inputs"))
sub_path <- path_maker(here::here("data/abcd/subjects"))
fig_path <- path_maker(here::here("data/abcd/results/figures"))

core_path <- path_maker(here::here("data/abcd/core"))
import <- function(path) {
    return(abcd_load(core_path(path)))
}
```

## Import raw data

This chunk loads in raw ABCD 5.1 CSVs into data frames.

```{r}
# Ohio TBI screen
ph_p_otbi <- import("physical-health/ph_p_otbi.csv")
# Age, family ID, site ID
abcd_y_lt <- import("abcd-general/abcd_y_lt.csv")
# Pubertal development scale, youth report
ph_y_pds <- import("physical-health/ph_y_pds.csv")
# Pubertal development scale, parent report
ph_p_pds <- import("physical-health/ph_p_pds.csv")
# Parent report of gender identity
gish_p_gi <- import("gender-identity-sexual-health/gish_p_gi.csv")
# Demographic data
abcd_p_demo <- import("abcd-general/abcd_p_demo.csv")
# Medical history
ph_p_mhx <- import("physical-health/ph_p_mhx.csv")
# Subcortical volumes (ASEG)
mri_y_smr_vol_aseg <- import("imaging/mri_y_smr_vol_aseg.csv")
# Desikan cortical thicknesses
mri_y_smr_thk_dsk <- import("imaging/mri_y_smr_thk_dsk.csv")
# Desikan cortical surface areas
mri_y_smr_area_dsk <- import("imaging/mri_y_smr_area_dsk.csv")
# Neurite density (AtlasTrack, all fibers)
mri_y_rsi_rnd_at <- import("imaging/mri_y_rsi_rnd_at.csv")
# Neurite density (Desikan, peri-cortical WM)
mri_y_rsi_rnd_wm_dsk <- import("imaging/mri_y_rsi_rnd_wm_dsk.csv")
# Neurite density (Destriux, peri-cortical WM)
mri_y_rsi_rnd_wm_dst <- import("imaging/mri_y_rsi_rnd_wm_dst.csv")
# rs-fMRI cortical-cortical correlations
mri_y_rsfmr_cor_gp_gp <- import("imaging/mri_y_rsfmr_cor_gp_gp.csv")
# rs-fMRI cortical-subcortical correlations
mri_y_rsfmr_cor_gp_aseg <- import("imaging/mri_y_rsfmr_cor_gp_aseg.csv")
# Number of friends
mh_y_or <- import("mental-health/mh_y_or.csv")
# Screen time
nt_p_stq <- import("novel-technologies/nt_p_stq.csv")
# Participation in sports and activities
ph_p_saiq <- import("physical-health/ph_p_saiq.csv")
# Exercise habits
ph_y_yrb <- import("physical-health/ph_y_yrb.csv")
# Youth report of prosocial behaviour
ce_y_psb <- import("culture-environment/ce_y_psb.csv")
# Parent report of prosocial behaviour
ce_p_psb <- import("culture-environment/ce_p_psb.csv")
# Youth report of family function
ce_y_fes <- import("culture-environment/ce_y_fes.csv")
# Parent report of family function
ce_p_fes <- import("culture-environment/ce_p_fes.csv")
# Parent ASEBA self-report (psychopathology)
mh_p_asr <- import("mental-health/mh_p_asr.csv")
# Parent report of child behaviour (CBCL)
mh_p_cbcl <- import("mental-health/mh_p_cbcl.csv")
# Sleep disturbance scale
ph_p_sds <- import("physical-health/ph_p_sds.csv")
# Scanner ID
mri_y_adm_info <- import("imaging/mri_y_adm_info.csv")
```

## Sample identification

All information required for identifying children following mTBI as of baseline data collection is available in the `ph_p_otbi.csv` file.
The structure of the Ohio State TBI screen as used for ABCD data collection was not completely compatible with the most commonly used definition of mTBI [@blennow_traumatic_2016], which requires at least one of the following:

* Any period of loss of consciousness
* Any loss of memory
* Any alteration in mental state
* Focal neurological deficits

But none of the following:

* LOC over 30 minutes
* A Glasgow Coma Scale score below 13
* Post-traumatic amnesia (PTA) greater than 24 hours

A few aspects of the data collection process in the ABCD study precluded the usage of this definition:

* No information was collected regarding the GCS
* Feeling dazed and PTA were combined into a single variable, making it unclear which combination of symptoms was present
* No information was collected regarding the duration of feeling dazed or experiencing PTA

Consequently, I defined mTBI as any injury that resulted in **either**:

1. LOC for less than 30 minutes (including 0 minutes) **AND** any duration of memory loss / feeling dazed
2. LOC for less than 30 minutes but greater than 0 minutes

The fixed nature of the questionnaire also meant that some information about multiple mTBIs sustained in the same way or about a very large number of mTBIs throughout a child's life could have been lost (see the previous section on identifying children with a history of mTBI).
For my analyses, I assume these edge cases are not common enough to meaningfully change any obtained conclusions.

```{r}
# 11864 total children included in baseline TBI data
ph_p_otbi |>
    filter_timepoint(0) |>
    nrow()

detail_mtbi(ph_p_otbi, abcd_y_lt) |>
    dplyr::filter(moderate_tbi | severe_tbi)
```

There are only 7 children with moderate and/or severe TBI as of baseline.
