Is there something in the correlation structure of these samples that determines whether or not cluster analysis can find the baseline concussion solution?

```{r}
library(abcdutils)
library(circlize)
library(ComplexHeatmap)
library(dplyr)
library(fastDummies)
library(ggplot2)
library(here)
library(metasnf)
library(mice)
library(patchwork)
library(randomForest)
library(readr)
library(rlist)
library(tidyr)
library(visdat)

core_path <- path_maker(here(paste0("data/abcd/core")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
input_path <- path_maker(here(paste0("data/abcd/inputs")))
model_path <- path_maker(here(paste0("data/abcd/results/models")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
```

```{r}
calculate_cor_mat <- function(df, method, fisher_z = FALSE) {
    if ("race" %in% colnames(df)) {
        df <- df |>
        data.frame() |>
        dplyr::select(-uid) |>
        dummy_cols(
            select_columns = c("race"),
            remove_selected_columns = TRUE,
            remove_most_frequent_dummy = TRUE
        )
    } else {
        df <- df |>
        data.frame() |>
        dplyr::select(-uid)
    }
    if (method == "spearman") {
        future::plan("multisession")
        n <- ncol(df)
        spearman_mat <- matrix(NA, n, n)
        colnames(spearman_mat) <- rownames(spearman_mat) <- colnames(df)
        results <- pbapply::pblapply(
            1:n,
            function(i) {
                sapply(
                    i:ncol(df),
                    function(j) {
                        cor(df[[i]], df[[j]], method = "spearman")
                    }
                )
            },
            cl = future::availableCores()
        )
        for (i in 1:n) {
            spearman_mat[i, i:n] <- results[[i]]
            spearman_mat[i:n, i] <- results[[i]]
        }
        mat <- spearman_mat
        future::plan("sequential")
    } else if (method == "pearson") {
        mat <- cor(df, method = "pearson")
    }
    if (fisher_z) {
        mat <- atanh(mat) 
    }
    diag(mat) <- NA
    return(mat)
}

permutation_test_corrs <- function(df1, df2, method, fisher_z, perms) {
    cor1 <- calculate_cor_mat(df1, method, fisher_z)
    nofts <- colnames(cor1)[!colnames(cor1) %in% ofts]
    cor1 <- cor1[ofts, nofts]
    cor2 <- calculate_cor_mat(df2, method, fisher_z)[ofts, nofts]
    observed_diff <- mean(abs(cor1 - cor2), na.rm = TRUE)
    n1 <- nrow(df1)
    n2 <- nrow(df2)
    n <- n1 + n2
    future::plan(future::multisession, workers = future::availableCores())
    perm_diffs <- future.apply::future_lapply(
        seq_len(perms),
        future.seed = TRUE,
        function(i) {
            merged_df <- rbind(df1, df2)[sample(n), ]
            perm_cor1 <- calculate_cor_mat(merged_df[1:n1, ], method, fisher_z)[ofts, nofts]
            perm_cor2 <- calculate_cor_mat(merged_df[(n1+1):n, ], method, fisher_z)[ofts, nofts]
            return(mean(abs(perm_cor1 - perm_cor2), na.rm = TRUE))
        }
    ) |> unlist()
    future::plan("sequential")
    p_value <- mean(perm_diffs >= observed_diff)
    return(
        list(
            observed_diff = observed_diff,
            p_value = p_value,
            perm_diffs = perm_diffs
        )
    )
}

plot_cor_mat_diffs <- function(cmat1, cmat2) {
    cor_mat <- abs(cmat1 - cmat2)
    diag(cor_mat) <- 0
    col_fn <- colorRamp2(c(0, max(cor_mat, na.rm = TRUE)), c("white", "red"))
    no_fts <- colnames(cor_mat)[!colnames(cor_mat) %in% ofts]
    cor_mat <- cor_mat[no_fts, ofts]
    cor_mat <- cor_mat[names(sort(-rowSums(cor_mat))), ]
    return(
        list(
            plot = ComplexHeatmap::Heatmap(
                cor_mat,
                cluster_rows = FALSE,
                cluster_columns = FALSE,
                col = col_fn
            ),
            mat = cor_mat
        )
    )
}
```

- baseline concussion data vs...
    - A. 10 random uninjured samples
    - B. the best matched uninjured sample
    - C. the pre-injury sample data
    - D. the post-injury sample data

```{r}
# Data
random_unij_dl_u1 <- readRDS(proc_path("2025_10_01_random_unij_dl_u1.rds"))
all_dls_h_ns <- readRDS(proc_path("2025_09_11_all_dls_h_no_sibs.rds"))
unij_dl_u1 <- all_dls_h_ns$"unij_all_u_dls"$"imp_1"
unij_ol_u1 <- all_dls_h_ns$"unij_all_u_ols"$"imp_1"
matched_unij_dl_dp_p <- readRDS(proc_path("2025_10_01_matched_unij_dl_dp_p.rds"))
matched_unij_ol_dp_p <- readRDS(proc_path("2025_10_01_matched_unij_ol_dp_p.rds"))
all_long_dls_h_ns <- readRDS(proc_path("2026_01_19_all_long_dls_h_ns.rds"))
```

```{r}
subject_filter_dl <- function(data_list, subject_vector) {
    data_list <- data_list |>
        dlapply(
            function(x) {
                keep_subs <- x$"data"$"uid" %in% subject_vector
                x$"data" <- x$"data"[keep_subs, ]
                return(x)
            }
        )
    return(data_list)
}

# A
set.seed(42)
random_unij_subs_01 <- sample(uids(unij_dl_u1))[1:438]
random_unij_subs_02 <- sample(uids(unij_dl_u1))[1:438]
random_unij_subs_03 <- sample(uids(unij_dl_u1))[1:438]
random_unij_subs_04 <- sample(uids(unij_dl_u1))[1:438]
random_unij_subs_05 <- sample(uids(unij_dl_u1))[1:438]
random_unij_subs_06 <- sample(uids(unij_dl_u1))[1:438]
random_unij_subs_07 <- sample(uids(unij_dl_u1))[1:438]
random_unij_subs_08 <- sample(uids(unij_dl_u1))[1:438]
random_unij_subs_09 <- sample(uids(unij_dl_u1))[1:438]
random_unij_subs_10 <- sample(uids(unij_dl_u1))[1:438]

random_unij_1 <- subject_filter_dl(c(unij_dl_u1, unij_ol_u1), random_unij_subs_01)
random_unij_2 <- subject_filter_dl(c(unij_dl_u1, unij_ol_u1), random_unij_subs_02)
random_unij_3 <- subject_filter_dl(c(unij_dl_u1, unij_ol_u1), random_unij_subs_03)
random_unij_4 <- subject_filter_dl(c(unij_dl_u1, unij_ol_u1), random_unij_subs_04)
random_unij_5 <- subject_filter_dl(c(unij_dl_u1, unij_ol_u1), random_unij_subs_05)
random_unij_6 <- subject_filter_dl(c(unij_dl_u1, unij_ol_u1), random_unij_subs_06)
random_unij_7 <- subject_filter_dl(c(unij_dl_u1, unij_ol_u1), random_unij_subs_07)
random_unij_8 <- subject_filter_dl(c(unij_dl_u1, unij_ol_u1), random_unij_subs_08)
random_unij_9 <- subject_filter_dl(c(unij_dl_u1, unij_ol_u1), random_unij_subs_09)
random_unij_10 <- subject_filter_dl(c(unij_dl_u1, unij_ol_u1), random_unij_subs_10)

random_unij_1_df <- as.data.frame(random_unij_1)
random_unij_2_df <- as.data.frame(random_unij_2)
random_unij_3_df <- as.data.frame(random_unij_3)
random_unij_4_df <- as.data.frame(random_unij_4)
random_unij_5_df <- as.data.frame(random_unij_5)
random_unij_6_df <- as.data.frame(random_unij_6)
random_unij_7_df <- as.data.frame(random_unij_7)
random_unij_8_df <- as.data.frame(random_unij_8)
random_unij_9_df <- as.data.frame(random_unij_9)
random_unij_10_df <- as.data.frame(random_unij_10)

saveRDS(random_unij_1_df, proc_path("random_unij_1_df.rds", TRUE))
saveRDS(random_unij_2_df, proc_path("random_unij_2_df.rds", TRUE))
saveRDS(random_unij_3_df, proc_path("random_unij_3_df.rds", TRUE))
saveRDS(random_unij_4_df, proc_path("random_unij_4_df.rds", TRUE))
saveRDS(random_unij_5_df, proc_path("random_unij_5_df.rds", TRUE))
saveRDS(random_unij_6_df, proc_path("random_unij_6_df.rds", TRUE))
saveRDS(random_unij_7_df, proc_path("random_unij_7_df.rds", TRUE))
saveRDS(random_unij_8_df, proc_path("random_unij_8_df.rds", TRUE))
saveRDS(random_unij_9_df, proc_path("random_unij_9_df.rds", TRUE))
saveRDS(random_unij_10_df, proc_path("random_unij_10_df.rds", TRUE))

# B
best_matched_uninjured_df <- as.data.frame(
    c(matched_unij_dl_dp_p, matched_unij_ol_dp_p)
)
saveRDS(best_matched_uninjured_df, proc_path("best_matched_uninjured_df.rds", TRUE))

# C
saveRDS(
    as.data.frame(
        c(
            all_long_dls_h_ns$"lmtb_0_dls"[[1]],
            all_long_dls_h_ns$"lmtb_0_ols"[[1]]
        )
    ),
    proc_path("lmtb_0_df.rds", TRUE)
)

# D
saveRDS(
    as.data.frame(
        c(
            all_long_dls_h_ns$"lmtb_l_dls"[[1]],
            all_long_dls_h_ns$"lmtb_l_ols"[[1]]
        )
    ),
    proc_path("lmtb_l_df.rds", TRUE)
)
```

```{r}
# Reference
mtbi_ful_df <- readRDS(proc_path("2025_09_16_mtbi_ful_df.rds"))

# A
random_unij_1_df <- readRDS(proc_path("2025_10_03_random_unij_1_df.rds"))
random_unij_2_df <- readRDS(proc_path("2025_10_03_random_unij_2_df.rds"))
random_unij_3_df <- readRDS(proc_path("2025_10_03_random_unij_3_df.rds"))
random_unij_4_df <- readRDS(proc_path("2025_10_03_random_unij_4_df.rds"))
random_unij_5_df <- readRDS(proc_path("2025_10_03_random_unij_5_df.rds"))
random_unij_6_df <- readRDS(proc_path("2025_10_03_random_unij_6_df.rds"))
random_unij_7_df <- readRDS(proc_path("2025_10_03_random_unij_7_df.rds"))
random_unij_8_df <- readRDS(proc_path("2025_10_03_random_unij_8_df.rds"))
random_unij_9_df <- readRDS(proc_path("2025_10_03_random_unij_9_df.rds"))
random_unij_10_df <- readRDS(proc_path("2025_10_03_random_unij_10_df.rds"))

# B
best_matched_uninjured_df <- readRDS(proc_path("2025_10_03_best_matched_uninjured_df.rds"))

# C
preinjury_df <- readRDS(proc_path("2026_01_21_lmtb_0_df.rds"))

# D
postinjury_df <- readRDS(proc_path("2026_01_21_lmtb_l_df.rds"))

df_list <- list(
    "mtbi_ful_df"               = mtbi_ful_df,
    "random_unij_1_df"          = random_unij_1_df,
    "random_unij_2_df"          = random_unij_2_df,
    "random_unij_3_df"          = random_unij_3_df,
    "random_unij_4_df"          = random_unij_4_df,
    "random_unij_5_df"          = random_unij_5_df,
    "random_unij_6_df"          = random_unij_6_df,
    "random_unij_7_df"          = random_unij_7_df,
    "random_unij_8_df"          = random_unij_8_df,
    "random_unij_9_df"          = random_unij_9_df,
    "random_unij_10_df"         = random_unij_10_df,
    "best_matched_uninjured_df" = best_matched_uninjured_df,
    "preinjury_df"              = preinjury_df,
    "postinjury_df"             = postinjury_df
)

# How to use the intersect-Reduce approach:
intersect_reduce <- function(df_list) {
    common_cols <- Reduce(intersect, lapply(df_list, colnames))
    reduced_dfs <- lapply(df_list, function(df) as.data.frame(df)[, common_cols, drop = FALSE])
    return(reduced_dfs)
}

reduced_dfs <- intersect_reduce(df_list)

saveRDS(reduced_dfs, proc_path("reduced_dfs.rds", TRUE))

reduced_dfs_in <- lapply(
    reduced_dfs,
    function(x) {
        x <- x |>
            dplyr::select(-dplyr::starts_with("cbcl"), -sds_sleep)
        x
    }
)

saveRDS(reduced_dfs_in, proc_path("reduced_dfs_in.rds", TRUE))
```

```{r}
# CHECKPOINT
reduced_dfs <- readRDS(proc_path("2026_01_21_reduced_dfs.rds"))
reduced_dfs_in <- readRDS(proc_path("2026_01_21_reduced_dfs_in.rds")) # could follow up
ofts <- readRDS(proc_path("2025_09_15_ofts.rds"))
```

## 1. Check if the extent of the correlations are significantly different

In this chunk, I compare the average overall strength of correlations.
The `permutation_test_corrs()` function subtracts two correlation matrices and calculates the mean of the absolute difference across all elements.
It reveals if the difference in the average strength of correlations in the two compared matrices is significant.

```{r}
set.seed(42)
start <- Sys.time()
perm_diffs_cor_v_mtbi <- lapply(
    2:length(reduced_dfs),
    function(x) {
        permutation_test_corrs(reduced_dfs[[1]], reduced_dfs[[x]], "pearson", TRUE, 5000)
    }
)
print(Sys.time() - start)
names(perm_diffs_cor_v_mtbi) <- names(reduced_dfs)[2:length(reduced_dfs)]
saveRDS(perm_diffs_cor_v_mtbi, proc_path("perm_diffs_cor_v_mtbi_fisherz_5000.rds", TRUE))
```

```{r}
perm_diffs_cor_v_mtbi <- readRDS(proc_path("2026_01_21_perm_diffs_cor_v_mtbi_fisherz_5000.rds"))

length(perm_diffs_cor_v_mtbi)

perm_diffs_cor_v_mtbi |> names()

# uncorrected p-values
uncorrected_pvals <- lapply(
    names(perm_diffs_cor_v_mtbi),
    function(x) {
        min(1, perm_diffs_cor_v_mtbi[[x]]$"p_value")
    }
) |> unlist()

clean_names <- names(perm_diffs_cor_v_mtbi)
clean_names <- gsub("_df", "", clean_names)
clean_names <- gsub("random_unij_", "Random Uninjured Sample ", clean_names)
clean_names <- gsub("best_matched_uninjured", "Closest Matched Uninjured Sample", clean_names)
clean_names <- gsub("preinjury", "Longitudinal Concussion Sample, Pre-injury Data", clean_names)
clean_names <- gsub("postinjury", "Longitudinal Concussion Sample, Post-injury Data", clean_names)
clean_names

data.frame(
    Sample = clean_names,
    p = uncorrected_pvals
) |>
    arrange(-p) |>
    knitr::kable(format = "markdown")
```

|Sample                                           |      p|
|:------------------------------------------------|------:|
|Longitudinal Concussion Sample, Pre-injury Data  | 0.3122|
|Longitudinal Concussion Sample, Post-injury Data | 0.2422|
|Closest Matched Uninjured Sample                 | 0.1188|
|Random Uninjured Sample 1                        | 0.0232|
|Random Uninjured Sample 4                        | 0.0082|
|Random Uninjured Sample 3                        | 0.0062|
|Random Uninjured Sample 5                        | 0.0024|
|Random Uninjured Sample 7                        | 0.0018|
|Random Uninjured Sample 10                       | 0.0014|
|Random Uninjured Sample 9                        | 0.0010|
|Random Uninjured Sample 8                        | 0.0008|
|Random Uninjured Sample 6                        | 0.0006|
|Random Uninjured Sample 2                        | 0.0002|

```{r}
lapply(perm_diffs_cor_v_mtbi, function(x) x$"p_value")

fdr_adjusted_pvals <- lapply(
    perm_diffs_cor_v_mtbi,
    function(x) {
        x$"p_value"
    }
) |>
    p.adjust(method = "fdr") |>
    round(4)

for (p in fdr_adjusted_pvals) {
    print(p)
}
```

Random unij dfs (10/10 significantly different after multiple comparisons corrections):

1. 0.0302
2. 0.0026
3. 0.0101
4. 0.0118
5. 0.0045
6. 0.0033
7. 0.0039
8. 0.0033
9. 0.0033
10. 0.0036

[1] 0.1404
[1] 0.3122
[1] 0.2624

best_matched_uninjured_df: 1
preinjury_df: 1
postinjury_df: 1

## 2. What is significantly different?

- Focus on correlations between outcome measures and top 20 most important features for clustering solution only

```{r}
# Adding in dummy race variable
ifts <- readRDS(proc_path("2025_09_15_ifts.rds"))
ifts_expand <- ifts[1:10]
ifts_expand <- unlist(append(ifts_expand, list("race_black", "race_hispanic", "race_other"), after = which(ifts_expand == "race")))
ifts_expand <- ifts_expand[-which(ifts_expand == "race")]
ifts_expand

ofts <- readRDS(proc_path("2025_09_15_ofts.rds"))
```

```{r}
permutation_test_corrs2 <- function(df1,
                                    df2,
                                    method = "pearson",
                                    fisher_z = TRUE,
                                    perms,
                                    procs = 8,
                                    style = "loop") {
    cor1 <- calculate_cor_mat(df1, method, fisher_z)[ifts_expand, ofts]
    cor2 <- calculate_cor_mat(df2, method, fisher_z)[ifts_expand, ofts]
    obs_diff <- cor1 - cor2
    n1 <- nrow(df1)
    n2 <- nrow(df2)
    n <- n1 + n2
    if (style == "lapply") {
        future::plan(future::multisession, workers = procs)
        perm_mat_diffs <- future.apply::future_lapply(
            seq_len(perms),
            future.seed = TRUE,
            function(i) {
                merged_df <- rbind(df1, df2)[sample(n), ]
                perm_cor1 <- calculate_cor_mat(merged_df[1:n1, ], method, fisher_z)[ifts_expand, ofts]
                perm_cor2 <- calculate_cor_mat(merged_df[(n1+1):n, ], method, fisher_z)[ifts_expand, ofts]
                return(perm_cor1 - perm_cor2)
            }
        )
        future::plan("sequential")
    }
    if (style == "loop") {
        perm_mat_diffs <- vector("list", perms)
        for (i in seq_len(perms)) {
            merged_df <- rbind(df1, df2)[sample(n), ]
            perm_cor1 <- calculate_cor_mat(merged_df[1:n1, ], method, fisher_z)[ifts_expand, ofts]
            perm_cor2 <- calculate_cor_mat(merged_df[(n1+1):n, ], method, fisher_z)[ifts_expand, ofts]
            perm_mat_diffs[[i]] <- perm_cor1 - perm_cor2
        }
    }
    perm_mat_diffs <- append(perm_mat_diffs, list(obs_diff) , after = 0)
    return(
        list(
            cor1 = cor1,
            cor2 = cor2,
            obs_diff = cor1 - cor2,
            perm_mat_diffs = perm_mat_diffs
        )
    )
}

set.seed(42)
start <- Sys.time()
perm_ele_wise_corrs_v_mtbi_lapply <- lapply(
    2:length(reduced_dfs),
    function(x) {
        permutation_test_corrs2(
            df1 = reduced_dfs[[1]],
            df2 = reduced_dfs[[x]],
            method = "pearson",
            fisher_z = TRUE,
            perms = 5000,
            style = "lapply"
        )
    }
)
print(Sys.time() - start)
saveRDS(
    perm_ele_wise_corrs_v_mtbi_lapply,
    proc_path(
        "perm_ele_wise_corrs_v_mtbi_lapply_fisherz_5000.rds",
        TRUE
    )
)

perm_ele_wise_corrs_v_mtbi_lapply[[1]]$"obs_diff"

cor_mat_list <- lapply(
    reduced_dfs,
    function(x) {
        calculate_cor_mat(x, "pearson", TRUE)[ifts_expand, ofts]
    }
)

saveRDS(cor_mat_list, proc_path("cor_mat_list.rds", TRUE))

cor_mat_list <- readRDS(proc_path("2026_01_21_cor_mat_list.rds"))
```

```{r}
flatten_mats <- function(perm_results) {
    mat_list <- perm_results$"perm_mat_diffs"
    flattened_mats <- lapply(
        1:length(mat_list[[1]]),
        function(element) {
            lapply(
                mat_list,
                function(mat) {
                    mat[element]
                }
            ) |> unlist()
        }
    )
    flattened_mats <- setNames(
        flattened_mats,
        as.vector(
            outer(
                rownames(perm_results$"perm_mat_diffs"[[1]]),
                colnames(perm_results$"perm_mat_diffs"[[1]]),
                paste,
                sep = "_vs_"
            )
        )
    )
    return(flattened_mats)
}

perm_ele_flat <- lapply(
    perm_ele_wise_corrs_v_mtbi_lapply,
    function(x) {
        flatten_mats(x)
    }
)

# this object is a list of 13 sets of group comparisons
# each set of comparison is a list of 180 pairwise correlations
# each pairwise correlation si a vector of 5001 values

saveRDS(
    perm_ele_flat,
    proc_path("perm_ele_flat_v_mtbi_fisherz_5000.rds", TRUE)
)

perm_p_values <- lapply(
    perm_ele_flat,
    function(group_comparison) {
        lapply(
            group_comparison,
            function(perm_vector) {
                # base the comparison on sign of the first element
                # which is the actual observed difference
                if (perm_vector[1] >= 0) {
                    return(mean(perm_vector[-1] >= perm_vector[1]))
                } else {
                    return(mean(perm_vector[-1] <= perm_vector[1]))
                }
            }
        ) |> unlist()
    }
)

saveRDS(
    perm_p_values,
    proc_path("perm_p_values_v_mtbi_fisherz_5000.rds", TRUE)
)

perm_p_dfs <- lapply(
    perm_p_values,
    function(x) {
        df <- data.frame("feature" = names(x), "p_value" = x)
        rownames(df) <- NULL
        df
    }
)

names(perm_p_dfs) <- names(reduced_dfs)[2:length(reduced_dfs)]

saveRDS(perm_p_dfs, proc_path("perm_p_dfs.rds", TRUE))
```

```{r}
perm_p_dfs <- readRDS(proc_path("2026_01_21_perm_p_dfs.rds"))

perm_p_dfs <- lapply(
    perm_p_dfs,
    function(x) {
        x$"fdr_p" <- p.adjust(x$"p_value", method = "fdr") 
        x
    }
)

perm_p_dfs_clean2 <- lapply(
    perm_p_dfs,
    function(x) {
        x |>
            separate(feature, into = c("input", "outcome"), sep = "_vs_") |>
            filter(fdr_p <= 0.05) |>
            arrange(fdr_p) |>
            dplyr::select(-p_value) |>
            dplyr::rename("p" = "fdr_p")
    }
)

check_strength <- function(idx) {
    other_cor_df <- perm_p_dfs_clean2[[idx]]
    vals <- c()
    mtbi_cors <- c()
    other_cors <- c()
    for (i in seq_len(nrow(other_cor_df))) {
        input <- other_cor_df$"input"[i]
        outcome <- other_cor_df$"outcome"[i]
        mtbi_cor <- cor_mat_list$"mtbi_ful_df"[input, outcome]
        other_cor_mat <- cor_mat_list[[idx + 1]]
        other_cor <- other_cor_mat[input, outcome]
        if (mtbi_cor > other_cor) {
            val <- "M > U"
        } else {
            val <- "M < U"
        }
        vals <- c(vals, val)
        mtbi_cors <- c(mtbi_cors, mtbi_cor)
        other_cors <- c(other_cors, other_cor)
    }
    other_cor_df$"mtbi_cor" <- mtbi_cors
    other_cor_df$"other_cor" <- other_cors
    other_cor_df$"summary" <- vals
    return(other_cor_df)
}

reference_dfs <- lapply(
    seq_along(perm_p_dfs_clean2),
    function(x) {
        check_strength(x) |>
        arrange(input)
    }
)
names(reference_dfs) <- names(perm_p_dfs_clean2)

populated_dfs <- reference_dfs[unlist(lapply(reference_dfs, function(x) nrow(x) > 0))]

populated_dfs_clean <- names(populated_dfs) |>
    lapply(
        function(x) {
            df <- populated_dfs[[x]]
            x <- gsub("random_unij_", "Random Uninjured ", x)
            x <- gsub("_df", "", x)
            x <- gsub("preinjury", "Longitudinal Concussion, Pre-injury", x)
            df$"*Sample*" <- x
            df |>
                dplyr::rename(
                    "*Input*" = "input",
                    "*Outcome*" = "outcome",
                    "*p-value*" = "p",
                    "*Baseline Concussion Corr.*" = "mtbi_cor",
                    "*Sample Corr.*" = "other_cor",
                ) |>
                dplyr::select("*Sample*", dplyr::everything())
        }
    )

do.call("rbind", populated_dfs_clean) |>
    knitr::kable(format = "markdown", digits = 3)
```
    
|*Sample*                            |*Input*              |*Outcome*       | *p-value*| *Baseline Concussion Corr.*| *Sample Corr.*|summary |
|:-----------------------------------|:--------------------|:---------------|---------:|---------------------------:|--------------:|:-------|
|Random Uninjured 1                  |activities_last_year |cbcl_somatic    |     0.022|                      -0.155|          0.059|M < U   |
|Random Uninjured 1                  |activities_last_year |cbcl_social     |     0.030|                      -0.254|         -0.058|M < U   |
|Random Uninjured 1                  |activities_last_year |cbcl_thought    |     0.030|                      -0.190|         -0.009|M < U   |
|Random Uninjured 1                  |activities_last_year |cbcl_aggressive |     0.030|                      -0.284|         -0.083|M < U   |
|Random Uninjured 1                  |activities_last_year |cbcl_withdep    |     0.037|                      -0.206|         -0.033|M < U   |
|Random Uninjured 1                  |household_income     |cbcl_rulebreak  |     0.000|                      -0.368|         -0.131|M < U   |
|Random Uninjured 1                  |household_income     |cbcl_anxdep     |     0.032|                      -0.205|         -0.006|M < U   |
|Random Uninjured 1                  |household_income     |cbcl_aggressive |     0.046|                      -0.343|         -0.148|M < U   |
|Random Uninjured 2                  |activities_last_year |cbcl_aggressive |     0.008|                      -0.284|         -0.088|M < U   |
|Random Uninjured 2                  |activities_last_year |cbcl_attention  |     0.012|                      -0.246|         -0.059|M < U   |
|Random Uninjured 2                  |activities_last_year |cbcl_withdep    |     0.020|                      -0.206|         -0.028|M < U   |
|Random Uninjured 2                  |activities_last_year |cbcl_thought    |     0.026|                      -0.190|         -0.037|M < U   |
|Random Uninjured 2                  |activities_last_year |cbcl_somatic    |     0.041|                      -0.155|          0.010|M < U   |
|Random Uninjured 2                  |household_income     |cbcl_withdep    |     0.008|                      -0.304|         -0.067|M < U   |
|Random Uninjured 2                  |household_income     |cbcl_aggressive |     0.008|                      -0.343|         -0.091|M < U   |
|Random Uninjured 2                  |household_income     |cbcl_thought    |     0.009|                      -0.220|          0.000|M < U   |
|Random Uninjured 2                  |household_income     |cbcl_rulebreak  |     0.012|                      -0.368|         -0.155|M < U   |
|Random Uninjured 2                  |household_income     |cbcl_anxdep     |     0.020|                      -0.205|         -0.028|M < U   |
|Random Uninjured 2                  |household_income     |cbcl_attention  |     0.020|                      -0.259|         -0.064|M < U   |
|Random Uninjured 2                  |household_income     |cbcl_social     |     0.025|                      -0.316|         -0.131|M < U   |
|Random Uninjured 2                  |household_income     |cbcl_somatic    |     0.026|                      -0.228|         -0.048|M < U   |
|Random Uninjured 2                  |parent_somatic       |cbcl_aggressive |     0.000|                       0.524|          0.204|M > U   |
|Random Uninjured 2                  |parent_somatic       |cbcl_social     |     0.008|                       0.491|          0.217|M > U   |
|Random Uninjured 2                  |parent_somatic       |cbcl_attention  |     0.020|                       0.366|          0.150|M > U   |
|Random Uninjured 2                  |parent_somatic       |cbcl_withdep    |     0.026|                       0.489|          0.279|M > U   |
|Random Uninjured 2                  |parent_somatic       |cbcl_anxdep     |     0.049|                       0.424|          0.238|M > U   |
|Random Uninjured 2                  |race_black           |cbcl_anxdep     |     0.008|                       0.108|         -0.136|M > U   |
|Random Uninjured 2                  |race_black           |cbcl_withdep    |     0.008|                       0.123|         -0.103|M > U   |
|Random Uninjured 2                  |race_black           |cbcl_aggressive |     0.008|                       0.179|         -0.067|M > U   |
|Random Uninjured 2                  |race_black           |cbcl_somatic    |     0.009|                       0.145|         -0.074|M > U   |
|Random Uninjured 2                  |race_black           |cbcl_social     |     0.025|                       0.231|          0.016|M > U   |
|Random Uninjured 2                  |race_black           |cbcl_thought    |     0.042|                       0.107|         -0.066|M > U   |
|Random Uninjured 2                  |weekday_screentime   |cbcl_anxdep     |     0.010|                       0.155|         -0.057|M > U   |
|Random Uninjured 2                  |weekday_screentime   |cbcl_withdep    |     0.020|                       0.138|         -0.029|M > U   |
|Random Uninjured 2                  |weekday_screentime   |cbcl_thought    |     0.025|                       0.186|          0.013|M > U   |
|Random Uninjured 2                  |weekday_screentime   |cbcl_aggressive |     0.025|                       0.276|          0.052|M > U   |
|Random Uninjured 2                  |weekday_screentime   |cbcl_attention  |     0.033|                       0.157|         -0.003|M > U   |
|Random Uninjured 2                  |weekday_screentime   |sds_sleep       |     0.042|                       0.177|          0.024|M > U   |
|Random Uninjured 2                  |weekday_screentime   |cbcl_social     |     0.043|                       0.174|          0.010|M > U   |
|Random Uninjured 2                  |weekend_screentime   |cbcl_withdep    |     0.042|                       0.094|         -0.036|M > U   |
|Random Uninjured 3                  |activities_last_year |cbcl_thought    |     0.000|                      -0.190|          0.066|M < U   |
|Random Uninjured 3                  |activities_last_year |cbcl_aggressive |     0.000|                      -0.284|         -0.022|M < U   |
|Random Uninjured 3                  |activities_last_year |cbcl_social     |     0.007|                      -0.254|         -0.015|M < U   |
|Random Uninjured 3                  |activities_last_year |cbcl_attention  |     0.011|                      -0.246|         -0.030|M < U   |
|Random Uninjured 3                  |activities_last_year |cbcl_withdep    |     0.015|                      -0.206|         -0.003|M < U   |
|Random Uninjured 3                  |activities_last_year |cbcl_rulebreak  |     0.015|                      -0.240|         -0.049|M < U   |
|Random Uninjured 3                  |activities_last_year |cbcl_anxdep     |     0.016|                      -0.136|          0.058|M < U   |
|Random Uninjured 3                  |activities_last_year |cbcl_somatic    |     0.022|                      -0.155|          0.031|M < U   |
|Random Uninjured 3                  |household_income     |cbcl_rulebreak  |     0.015|                      -0.368|         -0.173|M < U   |
|Random Uninjured 3                  |household_income     |cbcl_aggressive |     0.016|                      -0.343|         -0.136|M < U   |
|Random Uninjured 3                  |household_income     |cbcl_attention  |     0.020|                      -0.259|         -0.068|M < U   |
|Random Uninjured 3                  |household_income     |cbcl_withdep    |     0.028|                      -0.304|         -0.120|M < U   |
|Random Uninjured 3                  |household_income     |cbcl_thought    |     0.028|                      -0.220|         -0.034|M < U   |
|Random Uninjured 3                  |race_black           |cbcl_social     |     0.011|                       0.231|         -0.017|M > U   |
|Random Uninjured 3                  |race_black           |cbcl_attention  |     0.011|                       0.210|         -0.061|M > U   |
|Random Uninjured 3                  |race_black           |cbcl_anxdep     |     0.015|                       0.108|         -0.097|M > U   |
|Random Uninjured 4                  |activities_last_year |cbcl_aggressive |     0.000|                      -0.284|         -0.084|M < U   |
|Random Uninjured 4                  |household_income     |cbcl_rulebreak  |     0.011|                      -0.368|         -0.132|M < U   |
|Random Uninjured 4                  |household_income     |cbcl_aggressive |     0.014|                      -0.343|         -0.112|M < U   |
|Random Uninjured 4                  |household_income     |cbcl_anxdep     |     0.043|                      -0.205|         -0.005|M < U   |
|Random Uninjured 4                  |parent_somatic       |cbcl_aggressive |     0.049|                       0.524|          0.295|M > U   |
|Random Uninjured 4                  |race_black           |cbcl_somatic    |     0.030|                       0.145|         -0.058|M > U   |
|Random Uninjured 4                  |weekday_screentime   |cbcl_aggressive |     0.027|                       0.276|          0.036|M > U   |
|Random Uninjured 6                  |activities_last_year |cbcl_thought    |     0.000|                      -0.190|          0.044|M < U   |
|Random Uninjured 6                  |activities_last_year |cbcl_rulebreak  |     0.012|                      -0.240|         -0.044|M < U   |
|Random Uninjured 6                  |activities_last_year |cbcl_social     |     0.014|                      -0.254|         -0.057|M < U   |
|Random Uninjured 6                  |activities_last_year |cbcl_withdep    |     0.022|                      -0.206|         -0.038|M < U   |
|Random Uninjured 6                  |activities_last_year |cbcl_anxdep     |     0.024|                      -0.136|          0.039|M < U   |
|Random Uninjured 6                  |activities_last_year |cbcl_somatic    |     0.024|                      -0.155|          0.024|M < U   |
|Random Uninjured 6                  |activities_last_year |cbcl_aggressive |     0.024|                      -0.284|         -0.115|M < U   |
|Random Uninjured 6                  |activities_last_year |cbcl_attention  |     0.047|                      -0.246|         -0.096|M < U   |
|Random Uninjured 6                  |household_income     |cbcl_anxdep     |     0.000|                      -0.205|          0.128|M < U   |
|Random Uninjured 6                  |household_income     |cbcl_thought    |     0.000|                      -0.220|          0.015|M < U   |
|Random Uninjured 6                  |household_income     |cbcl_withdep    |     0.004|                      -0.304|         -0.039|M < U   |
|Random Uninjured 6                  |household_income     |cbcl_aggressive |     0.004|                      -0.343|         -0.099|M < U   |
|Random Uninjured 6                  |household_income     |cbcl_rulebreak  |     0.006|                      -0.368|         -0.158|M < U   |
|Random Uninjured 6                  |household_income     |cbcl_attention  |     0.013|                      -0.259|         -0.053|M < U   |
|Random Uninjured 6                  |household_income     |cbcl_social     |     0.022|                      -0.316|         -0.123|M < U   |
|Random Uninjured 6                  |household_income     |sds_sleep       |     0.025|                      -0.230|         -0.050|M < U   |
|Random Uninjured 6                  |household_income     |cbcl_somatic    |     0.034|                      -0.228|         -0.044|M < U   |
|Random Uninjured 6                  |parent_somatic       |cbcl_aggressive |     0.034|                       0.524|          0.311|M > U   |
|Random Uninjured 6                  |parent_somatic       |cbcl_withdep    |     0.047|                       0.489|          0.294|M > U   |
|Random Uninjured 6                  |race_black           |cbcl_anxdep     |     0.000|                       0.108|         -0.161|M > U   |
|Random Uninjured 6                  |race_black           |cbcl_somatic    |     0.012|                       0.145|         -0.073|M > U   |
|Random Uninjured 6                  |race_black           |cbcl_attention  |     0.014|                       0.210|         -0.005|M > U   |
|Random Uninjured 6                  |race_black           |cbcl_social     |     0.022|                       0.231|          0.028|M > U   |
|Random Uninjured 6                  |race_black           |cbcl_thought    |     0.034|                       0.107|         -0.068|M > U   |
|Random Uninjured 7                  |activities_last_year |cbcl_thought    |     0.026|                      -0.190|          0.001|M < U   |
|Random Uninjured 7                  |activities_last_year |cbcl_attention  |     0.031|                      -0.246|         -0.059|M < U   |
|Random Uninjured 7                  |activities_last_year |cbcl_aggressive |     0.031|                      -0.284|         -0.102|M < U   |
|Random Uninjured 7                  |household_income     |cbcl_attention  |     0.011|                      -0.259|         -0.004|M < U   |
|Random Uninjured 7                  |household_income     |cbcl_aggressive |     0.022|                      -0.343|         -0.112|M < U   |
|Random Uninjured 7                  |household_income     |cbcl_social     |     0.026|                      -0.316|         -0.108|M < U   |
|Random Uninjured 7                  |household_income     |cbcl_anxdep     |     0.031|                      -0.205|         -0.011|M < U   |
|Random Uninjured 7                  |household_income     |cbcl_rulebreak  |     0.031|                      -0.368|         -0.199|M < U   |
|Random Uninjured 7                  |household_income     |cbcl_thought    |     0.034|                      -0.220|         -0.041|M < U   |
|Random Uninjured 7                  |household_income     |cbcl_somatic    |     0.049|                      -0.228|         -0.045|M < U   |
|Random Uninjured 7                  |race_black           |cbcl_somatic    |     0.011|                       0.145|         -0.075|M > U   |
|Random Uninjured 7                  |race_black           |cbcl_anxdep     |     0.031|                       0.108|         -0.090|M > U   |
|Random Uninjured 7                  |race_black           |cbcl_social     |     0.031|                       0.231|          0.012|M > U   |
|Random Uninjured 7                  |race_black           |cbcl_attention  |     0.049|                       0.210|          0.030|M > U   |
|Random Uninjured 8                  |activities_last_year |cbcl_social     |     0.000|                      -0.254|         -0.036|M < U   |
|Random Uninjured 8                  |activities_last_year |cbcl_thought    |     0.000|                      -0.190|          0.053|M < U   |
|Random Uninjured 8                  |activities_last_year |cbcl_aggressive |     0.003|                      -0.284|         -0.057|M < U   |
|Random Uninjured 8                  |activities_last_year |cbcl_rulebreak  |     0.010|                      -0.240|         -0.050|M < U   |
|Random Uninjured 8                  |activities_last_year |cbcl_withdep    |     0.013|                      -0.206|         -0.024|M < U   |
|Random Uninjured 8                  |activities_last_year |cbcl_somatic    |     0.019|                      -0.155|          0.029|M < U   |
|Random Uninjured 8                  |activities_last_year |cbcl_attention  |     0.031|                      -0.246|         -0.074|M < U   |
|Random Uninjured 8                  |brain_volume         |cbcl_attention  |     0.020|                      -0.049|          0.129|M < U   |
|Random Uninjured 8                  |household_income     |cbcl_thought    |     0.003|                      -0.220|          0.020|M < U   |
|Random Uninjured 8                  |household_income     |cbcl_attention  |     0.010|                      -0.259|         -0.051|M < U   |
|Random Uninjured 8                  |household_income     |cbcl_withdep    |     0.010|                      -0.304|         -0.089|M < U   |
|Random Uninjured 8                  |household_income     |cbcl_aggressive |     0.032|                      -0.343|         -0.159|M < U   |
|Random Uninjured 8                  |household_income     |cbcl_rulebreak  |     0.048|                      -0.368|         -0.209|M < U   |
|Random Uninjured 8                  |parent_somatic       |cbcl_withdep    |     0.003|                       0.489|          0.222|M > U   |
|Random Uninjured 8                  |parent_somatic       |cbcl_aggressive |     0.017|                       0.524|          0.264|M > U   |
|Random Uninjured 8                  |parent_somatic       |cbcl_thought    |     0.029|                       0.390|          0.172|M > U   |
|Random Uninjured 8                  |parent_somatic       |cbcl_social     |     0.032|                       0.491|          0.269|M > U   |
|Random Uninjured 8                  |parent_somatic       |cbcl_attention  |     0.048|                       0.366|          0.194|M > U   |
|Random Uninjured 8                  |race_black           |cbcl_social     |     0.003|                       0.231|         -0.022|M > U   |
|Random Uninjured 8                  |race_black           |cbcl_attention  |     0.003|                       0.210|         -0.031|M > U   |
|Random Uninjured 8                  |race_black           |cbcl_thought    |     0.005|                       0.107|         -0.141|M > U   |
|Random Uninjured 8                  |race_black           |cbcl_anxdep     |     0.019|                       0.108|         -0.098|M > U   |
|Random Uninjured 8                  |race_black           |cbcl_aggressive |     0.036|                       0.179|         -0.006|M > U   |
|Random Uninjured 8                  |race_black           |cbcl_withdep    |     0.048|                       0.123|         -0.038|M > U   |
|Random Uninjured 9                  |activities_last_year |cbcl_aggressive |     0.016|                      -0.284|         -0.071|M < U   |
|Random Uninjured 9                  |activities_last_year |cbcl_rulebreak  |     0.049|                      -0.240|         -0.077|M < U   |
|Random Uninjured 9                  |household_income     |cbcl_rulebreak  |     0.018|                      -0.368|         -0.150|M < U   |
|Random Uninjured 9                  |household_income     |cbcl_attention  |     0.028|                      -0.259|         -0.069|M < U   |
|Random Uninjured 9                  |parent_somatic       |cbcl_aggressive |     0.026|                       0.524|          0.277|M > U   |
|Random Uninjured 9                  |race_black           |cbcl_somatic    |     0.000|                       0.145|         -0.081|M > U   |
|Random Uninjured 9                  |race_black           |cbcl_anxdep     |     0.018|                       0.108|         -0.108|M > U   |
|Random Uninjured 9                  |weekday_screentime   |cbcl_thought    |     0.000|                       0.186|         -0.061|M > U   |
|Random Uninjured 9                  |weekday_screentime   |cbcl_aggressive |     0.007|                       0.276|          0.018|M > U   |
|Random Uninjured 9                  |weekday_screentime   |cbcl_anxdep     |     0.026|                       0.155|         -0.042|M > U   |
|Random Uninjured 9                  |weekday_screentime   |sds_sleep       |     0.026|                       0.177|         -0.020|M > U   |
|Random Uninjured 9                  |weekday_screentime   |cbcl_attention  |     0.047|                       0.157|         -0.008|M > U   |
|Random Uninjured 10                 |activities_last_year |cbcl_aggressive |     0.000|                      -0.284|         -0.063|M < U   |
|Random Uninjured 10                 |activities_last_year |cbcl_thought    |     0.007|                      -0.190|          0.016|M < U   |
|Random Uninjured 10                 |activities_last_year |cbcl_attention  |     0.031|                      -0.246|         -0.059|M < U   |
|Random Uninjured 10                 |activities_last_year |cbcl_somatic    |     0.038|                      -0.155|          0.030|M < U   |
|Random Uninjured 10                 |household_income     |cbcl_aggressive |     0.000|                      -0.343|         -0.076|M < U   |
|Random Uninjured 10                 |household_income     |cbcl_withdep    |     0.025|                      -0.304|         -0.089|M < U   |
|Random Uninjured 10                 |household_income     |cbcl_attention  |     0.025|                      -0.259|         -0.056|M < U   |
|Random Uninjured 10                 |household_income     |cbcl_somatic    |     0.037|                      -0.228|         -0.032|M < U   |
|Random Uninjured 10                 |household_income     |cbcl_rulebreak  |     0.037|                      -0.368|         -0.191|M < U   |
|Random Uninjured 10                 |parent_somatic       |cbcl_social     |     0.016|                       0.491|          0.238|M > U   |
|Random Uninjured 10                 |parent_somatic       |cbcl_aggressive |     0.037|                       0.524|          0.297|M > U   |
|Random Uninjured 10                 |parent_somatic       |sds_sleep       |     0.040|                       0.446|          0.260|M > U   |
|Random Uninjured 10                 |race_black           |cbcl_somatic    |     0.040|                       0.145|         -0.028|M > U   |
|Random Uninjured 10                 |race_black           |cbcl_attention  |     0.040|                       0.210|          0.021|M > U   |
|Random Uninjured 10                 |race_hispanic        |cbcl_aggressive |     0.035|                       0.080|         -0.104|M > U   |
|Random Uninjured 10                 |race_hispanic        |cbcl_rulebreak  |     0.038|                       0.055|         -0.114|M > U   |
|Longitudinal Concussion, Pre-injury |household_income     |cbcl_withdep    |     0.043|                      -0.304|         -0.016|M < U   |
|Longitudinal Concussion, Pre-injury |parent_somatic       |cbcl_withdep    |     0.000|                       0.489|          0.089|M > U   |

```{r}
do.call("rbind", populated_dfs[1:9]) |>
    dplyr::group_by(input, outcome, summary) |>
    summarize(n = n()) |>
    arrange(-n) |>
    data.frame() |>
    dplyr::rename(
        "*Input*" = "input",
        "*Outcome*" = "outcome",
        "*Summary*" = "summary",
        "*n*" = "n"
    ) |>
    knitr::kable(format = "markdown")

```

|*Input*              |*Outcome*       |*Summary* | *n*|
|:--------------------|:---------------|:---------|---:|
|activities_last_year |cbcl_aggressive |M < U     |   9|
|household_income     |cbcl_rulebreak  |M < U     |   9|
|household_income     |cbcl_aggressive |M < U     |   8|
|activities_last_year |cbcl_thought    |M < U     |   7|
|household_income     |cbcl_attention  |M < U     |   7|
|activities_last_year |cbcl_attention  |M < U     |   6|
|activities_last_year |cbcl_somatic    |M < U     |   6|
|parent_somatic       |cbcl_aggressive |M > U     |   6|
|race_black           |cbcl_anxdep     |M > U     |   6|
|race_black           |cbcl_somatic    |M > U     |   6|
|activities_last_year |cbcl_withdep    |M < U     |   5|
|household_income     |cbcl_anxdep     |M < U     |   5|
|household_income     |cbcl_thought    |M < U     |   5|
|household_income     |cbcl_withdep    |M < U     |   5|
|race_black           |cbcl_attention  |M > U     |   5|
|race_black           |cbcl_social     |M > U     |   5|
|activities_last_year |cbcl_rulebreak  |M < U     |   4|
|activities_last_year |cbcl_social     |M < U     |   4|
|household_income     |cbcl_somatic    |M < U     |   4|
|household_income     |cbcl_social     |M < U     |   3|
|parent_somatic       |cbcl_social     |M > U     |   3|
|parent_somatic       |cbcl_withdep    |M > U     |   3|
|race_black           |cbcl_thought    |M > U     |   3|
|weekday_screentime   |cbcl_aggressive |M > U     |   3|
|activities_last_year |cbcl_anxdep     |M < U     |   2|
|parent_somatic       |cbcl_attention  |M > U     |   2|
|race_black           |cbcl_aggressive |M > U     |   2|
|race_black           |cbcl_withdep    |M > U     |   2|
|weekday_screentime   |cbcl_anxdep     |M > U     |   2|
|weekday_screentime   |cbcl_attention  |M > U     |   2|
|weekday_screentime   |cbcl_thought    |M > U     |   2|
|weekday_screentime   |sds_sleep       |M > U     |   2|
|brain_volume         |cbcl_attention  |M < U     |   1|
|household_income     |sds_sleep       |M < U     |   1|
|parent_somatic       |cbcl_anxdep     |M > U     |   1|
|parent_somatic       |cbcl_thought    |M > U     |   1|
|parent_somatic       |sds_sleep       |M > U     |   1|
|race_hispanic        |cbcl_aggressive |M > U     |   1|
|race_hispanic        |cbcl_rulebreak  |M > U     |   1|
|weekday_screentime   |cbcl_social     |M > U     |   1|
|weekday_screentime   |cbcl_withdep    |M > U     |   1|
|weekend_screentime   |cbcl_withdep    |M > U     |   1|
