# Cluster characterization

## Load libraries and data

```{r}
library(scabcd)
library(rlist)
library(abcdutils)
library(here)
library(readr)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))

proc_writer <- make_writer(proc_path)
proc_reader <- make_reader(proc_path)
input_reader <- make_reader(input_path)

#data_list_train <- list.load(proc_path("2023_03_15_data_list_train.rdata"))
#data_list_test <- list.load(proc_path("2023_03_21_data_list_test.rdata"))
#cbcl_list_train <- list.load(proc_path("2023_03_15_cbcl_list_train.rdata"))
#data_list_full <- list.load(proc_path("2023_03_15_data_list_full.rdata"))
#cbcl_list_full <- list.load(proc_path("2023_03_15_cbcl_list_full.rdata"))

data_list_train <- list.load(proc_path("2023_03_27_data_list_0_train.rdata"))
data_list_test <- list.load(proc_path("2023_03_27_data_list_0_test.rdata"))
data_list_full <- list.load(proc_path("2023_03_27_data_list_0_full.rdata"))
cbcl_list_train <- list.load(proc_path("2023_03_15_cbcl_list_train.rdata"))
cbcl_list_full <- list.load(proc_path("2023_03_15_cbcl_list_full.rdata"))


nihtbx_pattern <- input_reader("nihtbx_pattern_fc_imp.csv")
nihtbx_list <- input_reader("nihtbx_list_fc_imp.csv")
nihtbx_cardsort <- input_reader("nihtbx_cardsort_fc_imp.csv")
sds_sleep_df <- input_reader("sds_sleep_df.csv")

#top_oms <- read_csv(proc_path("2023_03_09_top_om_rows_all_nclust.csv"))
#propagated_labels <- proc_reader("2023_03_16_top_oms_lp.csv")

top_oms <- read_csv(proc_path("2023_03_27_top_om_rows_all_nclust.csv"))
```


## CBCL plotting in the training subjects

The function below generates a grid of CBCL impairment plots for each cluster solution and saves them using a provided `path_maker` function.

```{r}
om_plot_all_cbcl(top_oms, cbcl_list_train, fig_path)

cbcl_ord_reg_from_om(top_oms[1, ], cbcl_list_train)

cbcl_ord_reg_from_om(top_oms[2, ], cbcl_list_train)

for (row in seq_len(nrow(top_oms))) {
    current_row <- top_oms[row, ]
    print(current_row$"significance")
    print(cbcl_ord_reg_from_om(current_row, cbcl_list_train))
}
```


## NMI calculations

I have found that the `om_to_nmi_df` function can yield different results across different machines.
I believe this is due to to hardware-specific differences in handling floating point arithmetic during the SNFTool package's implementation of spectral clustering.
Moving forward, I use results generated by the machine at SickKids (Intel(R) Core(TM) i5-10400 CPU @ 2.90 GHz).
Some notable file versions are `2023_03_13_nmi_df.csv` (the first run of the `om_to_nmi_df` function, calculated at the SickKids machine) and `2023_03_15_nmi_df.csv` (run from my home machine, yielding distinct results).


```{r}
nmi_df <- om_to_nmi_df(top_oms, data_list_train)

write_csv(nmi_df, proc_path("nmi_df_sk.csv", date = TRUE))

nmi_df <- data.frame(read_csv(proc_path("2023_03_16_nmi_df_sk.csv")))
```


## Label propagation

```{r}
propagated_labels <- lp_om(top_oms, data_list_full)

write_csv(propagated_labels, proc_path("top_oms_lp.csv", date = TRUE))

propagated_labels <- proc_reader("2023_03_27_top_oms_lp.csv")
```

## CBCL plotting in the label propagated group

```{r}
test_labels <- propagated_labels |>
    dplyr::filter(group == "test") |>
    dplyr::select(-"group")

outcomes_and_eval_df <- append(list(test_labels), cbcl_list_full)

test_eval_df <- merge_df_list(outcomes_and_eval_df)

test_plot_all_cbcl <- function(eval_df, full_cbcl_list, fig_path_fn) {
    solutions <- eval_df |>
        dplyr::select(-dplyr::starts_with(c("subject", "cbcl"))) |>
        colnames()
    for (solution in solutions) {
        cluster_df <- eval_df |>
            dplyr::select(!!solution, "subjectkey") |>
            data.frame()
        colnames(cluster_df) <- c("cluster", "subjectkey")
        current_sig <- solution
        plot_all_cbcl(
            cluster_df,
            current_sig,
            full_cbcl_list,
            save = fig_path_fn(paste0(current_sig, "_lp.png"), date = TRUE))
    }
}

test_plot_all_cbcl(test_eval_df, cbcl_list_full, fig_path)
```

## NMI characterization
```{r}
nmi_df

# How NMIs are distributed
plot_nmis(nmi_df, fig_path)
```


## Input variable characterization
```{r}
plot_om_bar <- function(om_row, input_df, feature, featname, save = NULL) {
    if (is.null(input_df)) {
        return(NULL)
    }
    cluster_df <- get_cluster_df(om_row)
    characterization_df <-
        dplyr::inner_join(cluster_df, input_df, by = "subjectkey")
    cluster <- ""
    percent <- ""
    n <- ""
    keycol <- ""
    n_thresh <- ""
    characterization_df <- characterization_df |>
        dplyr::rename("keycol" = !!feature) # wizardry
    summary <- characterization_df |>
        dplyr::group_by(cluster) |>
        dplyr::count(keycol) |>
        dplyr::mutate(percent = round(n / sum(n) * 100))
    if (is.numeric(summary$"keycol")) {
        lvl <- as.character(rev(sort(unique(summary$"keycol"))))
        summary$"keycol" <- factor(summary$"keycol", levels = lvl)
    } else {
        summary$"keycol" <- factor(summary$"keycol")
    }
    summary$"cluster" <- factor(summary$"cluster")
    summary <- summary |>
        dplyr::mutate(n_thresh = dplyr::case_when(
            n < 5 ~ "",
            TRUE ~ as.character(n)))
    print(summary)
    plot <- ggplot2::ggplot(
        summary,
        ggplot2::aes(
            x = cluster,
            y = percent,
            fill = keycol)) +
        ggplot2::geom_bar(
            stat = "identity",
            position = ggplot2::position_stack()) +
        ggplot2::geom_text(
            #data = subset(summary, percent > 10),
            mapping = ggplot2::aes(
                label = n_thresh,
                y = percent),
            size = 8,
            position = ggplot2::position_stack(vjust = 0.5)) +
        ggplot2::scale_y_continuous(
            expand = ggplot2::expansion(mult = c(0, .1))) +
        ggplot2::labs(
            x = "Cluster",
            y = "Percentage",
            fill = featname) +
        ggplot2::theme_bw() +
        ggplot2::theme(
            text = ggplot2::element_text(size = 30),
            plot.margin = ggplot2::margin(l = 0, r = 2, t = 1, b = 1, "cm"))
    if (!is.null(save)) {
        ggplot2::ggsave(file = save, plot, width = 10, height = 10)
    } else {
        return(plot)
    }
}
pheatmap_om_matrix <- function(om_row, input_df, binary = FALSE, save = NULL,
                               main = "", show_row = FALSE, legend = TRUE,
                               cw = 100, ch = 2) {
    if (is.null(input_df)) {
        return(NULL)
    }
    cluster <- ""
    cluster_df <- get_cluster_df(om_row)
    characterization_df <-
        dplyr::inner_join(input_df, cluster_df, by = "subjectkey")
    cluster_names <- characterization_df |>
        dplyr::group_by(cluster) |>
        dplyr::select(-"subjectkey") |>
        dplyr::summarize_all(mean) |>
        dplyr::select("cluster") |>
        unlist() |>
        names()
    cluster_names <- as.character(1:om_row$"nclust")
    matrix <- characterization_df |>
        dplyr::group_by(cluster) |>
        dplyr::select(-"subjectkey") |>
        dplyr::summarize_all(mean) |>
        dplyr::select(-"cluster") |>
        t()
    colnames(matrix) <- cluster_names
    if (binary == TRUE) {
    # This for loop ensures that the lowest value in each row becomes 0
        for (i in seq_len(nrow(matrix))) {
            matrix[i, ] <- matrix[i, ] - min(matrix[i, ])
        }
    }
    # This for loop ensures that the highest value in each row becomes 1
    matrix_row_max <- apply(matrix, 1, max)
    for (i in seq_len(nrow(matrix))) {
        matrix[i, ] <- (matrix[i, ] / matrix_row_max[i])
    }
    if (!(is.null(grDevices::dev.list())) && !(is.null(save))) {
        grDevices::dev.off()
    }
    if (!(is.null(save))) {
        pheatmap::pheatmap(matrix,
                           cluster_cols = FALSE,
                           filename = save,
                           main = main,
                           fontsize = 25,
                           show_rownames = show_row)
    } else {
        return(pheatmap::pheatmap(matrix, cluster_cols = FALSE, main = main,
                                  fontsize = 25,
                                  show_rownames = show_row,
                                  legend = legend,
                                  angle_col = "0",
                                  cellwidth = cw,
                                  cellheight = ch,
                                  border_color = NA))
    }
}
plot_om_cont <- function(om_row, input_df, feature, featname, save = NULL) {
    if (is.null(input_df)) {
        return(NULL)
    }
    cluster_df <- get_cluster_df(om_row)
    cluster <- ""
    keycol <- ""
    characterization_df <-
        dplyr::inner_join(cluster_df, input_df, by = "subjectkey")
    characterization_df <- characterization_df |>
        dplyr::rename("keycol" = !!feature) # wizardry
    characterization_df$"cluster" <- factor(characterization_df$"cluster")
    plot <- ggplot2::ggplot(
        characterization_df,
        ggplot2::aes(
            x = cluster,
            y = keycol,
            fill = cluster,
            color = cluster)) +
        ggplot2::geom_violin(alpha = 0.4) +
        ggplot2::geom_jitter(height = 0, size = 3, alpha = 1) +
        ggplot2::scale_y_continuous(
            expand = ggplot2::expansion(mult = c(0, .1))) +
        ggplot2::labs(
            x = "Cluster",
            y = featname) +
        ggplot2::theme_bw() +
        ggplot2::theme(
            text = ggplot2::element_text(size = 30),
            plot.margin = ggplot2::margin(l = 0, r = 2, t = 1, b = 1, "cm"),
            legend.position = "none")
    if (!is.null(save)) {
        print(save)
        ggplot2::ggsave(file = save, plot, width = 10, height = 10)
    } else {
        return(plot)
    }
}

train_dfs <- lapply(data_list_train, function(x) x$"data")

train_df_names <- lapply(data_list_train, function(x) x$"name") |>
    unlist()


row <- 1

# LOC
plot_om_bar(top_oms[row, ], train_dfs[[1]], "latest_mtbi_loc", "LOC")

# Mechanism
plot_om_bar(top_oms[row, ], train_dfs[[2]], "latest_mtbi_mechanism", "MOI")

# Mem/dazed
plot_om_bar(top_oms[row, ], train_dfs[[3]], "latest_mtbi_mem_daze", "Dazed")

# Income
plot_om_bar(top_oms[row, ], train_dfs[[4]], "household_income", "Income")

# Age at interview
plot_om_cont(top_oms[row, ], train_dfs[[5]], "interview_age", "Interview Age")

# Age at injury
plot_om_cont(top_oms[row, ], train_dfs[[6]], "latest_mtbi_age", "Injury Age")

# Pubertal status
plot_om_cont(top_oms[row, ], train_dfs[[7]], "pubertal_status", "Pubertal")

# Race
plot_om_bar(top_oms[row, ], train_dfs[[8]], "race", "Race")

# Sex
plot_om_bar(top_oms[row, ], train_dfs[[9]], "M", "Male")

# Headaches
plot_om_bar(top_oms[row, ], train_dfs[[10]], "headache", "Headaches")

# Number of injuries
plot_om_cont(top_oms[row, ], train_dfs[[11]], "mtbi_count", "mTBI Count")

# dMRI
pheatmap_om_matrix(top_oms[row, ], train_dfs[[12]], binary = FALSE, main = "Gordon correlations")

# Gord cor
pheatmap_om_matrix(top_oms[row, ], train_dfs[[13]], binary = TRUE)

# Gord var
pheatmap_om_matrix(top_oms[row, ], train_dfs[[14]], binary = FALSE)

# Subc cor
pheatmap_om_matrix(top_oms[row, ], train_dfs[[15]], binary = TRUE)

# Subc var
pheatmap_om_matrix(top_oms[row, ], train_dfs[[16]], binary = FALSE)

# Cort sa
pheatmap_om_matrix(top_oms[row, ], train_dfs[[17]], binary = FALSE)

# Cort t
pheatmap_om_matrix(top_oms[row, ], train_dfs[[18]], binary = FALSE)

# Subc v
pheatmap_om_matrix(top_oms[row, ], train_dfs[[19]], binary = FALSE)

# Loneliness
plot_om_cont(top_oms[row, ], train_dfs[[20]], "ss_friend",
             "Number of Same Sex Friends")

plot_om_cont(top_oms[row, ], train_dfs[[20]], "ss_close_friend",
             "Number of Same Sex Close Friends")

plot_om_cont(top_oms[row, ], train_dfs[[20]], "os_friend",
             "Number of Opposite Sex Friends")

plot_om_cont(top_oms[row, ], train_dfs[[20]], "os_close_friend",
             "Number of Opposite Sex Close Friends")

# Screentime
plot_om_cont(top_oms[row, ], train_dfs[[21]], "screentime_wknd_hrs",
             "Weekend Screentime")

plot_om_cont(top_oms[row, ], train_dfs[[21]], "screentime_wknd_hrs",
             "Weekday Screentime")

# Family function
pheatmap_om_matrix(top_oms[row, ], train_dfs[[22]])

# Sports and Activities
pheatmap_om_matrix(top_oms[row, ], train_dfs[[23]], show_row = TRUE)

plot_om_cont(top_oms[row, ], train_dfs[[23]], "organized_school_activities",
             "Activities organized within school")

plot_om_cont(top_oms[row, ], train_dfs[[23]], "organized_outside_activities",
             "Activities organized outside of school")

plot_om_cont(top_oms[row, ], train_dfs[[23]], "private_instruction_activities",
             "Activities with private instruction")

plot_om_cont(top_oms[row, ], train_dfs[[23]], "p12_activities",
             "Activities in the last year")

# Prosocial behaviour
plot_om_bar(top_oms[row, ], train_dfs[[24]], "q1",
            "Care about \nothers' feelings")

plot_om_bar(top_oms[row, ], train_dfs[[24]], "q2",
            "Help those \nhurt, upset, \nor feeling sick")

plot_om_bar(top_oms[row, ], train_dfs[[24]], "q3",
            "Often offer to help")

# Parent psychopathology
pheatmap_om_matrix(top_oms[row, ], train_dfs[[25]])

# Exercise
plot_om_cont(top_oms[row, ], train_dfs[[26]], "physical_activity1_y",
    "Days with over 60\n mins activity this week")

plot_om_cont(top_oms[row, ], train_dfs[[26]], "physical_activity2_y",
    "Days with strength \nexercise")

plot_om_cont(top_oms[row, ], train_dfs[[26]], "physical_activity5_y",
    "Days of PE class\n per week")

train_dfs[[26]]


# NIHTBX
plot_om_cont(top_oms[row, ], nihtbx_pattern, "nihtbx_pattern_fc", "Pattern")

# NIH Cardsort
plot_om_cont(top_oms[row, ], nihtbx_cardsort, "nihtbx_cardsort_fc", "cardsort")

# NIH List
plot_om_cont(top_oms[row, ], nihtbx_list, "nihtbx_list_fc", "list")
pheatmap_om_matrix(top_oms[row, ], sds_sleep_df)




input_characterization_plots_g <- function(om,
                                         loc = NULL,
                                         mechanism = NULL,
                                         dazed = NULL,
                                         income = NULL,
                                         interview_age = NULL,
                                         mtbi_age = NULL,
                                         pubertal = NULL,
                                         race = NULL,
                                         sex = NULL,
                                         headache = NULL,
                                         mtbi_count = NULL,
                                         wmnd = NULL,
                                         gord_cor = NULL,
                                         gord_var = NULL,
                                         subc_cor = NULL,
                                         subc_var = NULL,
                                         cort_sa = NULL,
                                         cort_t = NULL,
                                         subc_v = NULL,
                                         loneliness = NULL,
                                         screentime = NULL,
                                         fam_fn = NULL,
                                         sports = NULL,
                                         prosocial = NULL,
                                         parent_psych = NULL,
                                         exercise = NULL,
                                         pattern = NULL,
                                         cardsort = NULL,
                                         list = NULL,
                                         general_inp_path,
                                         rsfmri_path,
                                         other_mri_path,
                                         other_heatmap_path) {
    for (i in seq_len(nrow(om))) {
        row_i <- om[i, ]
        sig <- row_i$"significance"
        id <- row_i$"row_id"
        prefix <- paste0("row_", id, "_", sig)
        g_path <- gsub("gen", paste0(prefix, "_gen"), general_inp_path)
        r_path <- gsub("rsfmri", paste0(prefix, "_rsfmri"), rsfmri_path)
        om_path <- gsub("other_mri",
                        paste0(prefix, "_other_mri"), other_mri_path)
        o_path <- gsub("other_in",
                       paste0(prefix, "_other_in"), other_heatmap_path)
        # LOC
        loc_p <- plot_om_bar(row_i, loc, "latest_mtbi_loc", "LOC")
        # Mechanism
        mech_p <- plot_om_bar(row_i, mechanism, "latest_mtbi_mechanism", "MOI")
        # Dazed
        dazed_p <- plot_om_bar(row_i, dazed, "latest_mtbi_mem_daze", "Dazed")
        # Income
        income_p <- plot_om_bar(row_i, income, "household_income", "Income")
        # Age at interview
        interview_age_p <- plot_om_cont(row_i, interview_age, "interview_age",
                               "Interview Age")
        # Age at injury
        injury_age_p <- plot_om_cont(row_i, mtbi_age, "latest_mtbi_age",
                                     "Injury Age")
        # Pubertal status
        pubertal_p <- plot_om_cont(row_i, pubertal, "pubertal_status",
                                   "Pubertal\nStage")
        # Race
        race_p <- plot_om_bar(row_i, race, "race", "Race")
        # Sex
        sex_p <- plot_om_bar(row_i, sex, "M", "Male")
        # Headaches
        headache_p <- plot_om_bar(row_i, headache, "headache", "Headaches")
        # Number of injuries
        mtbi_count_p <- plot_om_bar(row_i, mtbi_count, "mtbi_count",
                                     "mTBI\nCount")
        # Loneliness
        friend_p1 <- plot_om_cont(row_i, loneliness, "ss_friend",
                     "Same Sex\nFriends")
        friend_p2 <- plot_om_cont(row_i, loneliness, "ss_close_friend",
                     "Same Sex\nClose Friends")
        friend_p3 <- plot_om_cont(row_i, loneliness, "os_friend",
                     "Opposite Sex\nFriends")
        friend_p4 <- plot_om_cont(row_i, loneliness, "os_close_friend",
                     "Opposite Sex\nClose Friends")
        # Screentime
        wknd_screen_p <- plot_om_cont(row_i, screentime, "screentime_wknd_hrs",
                     "Weekend\nScreentime")
        wkd_screen_p <- plot_om_cont(row_i, screentime, "screentime_wkday_hrs",
                     "Weekday\nScreentime")
        # Exercise
        exercise_p1 <- plot_om_cont(row_i, exercise, "physical_activity1_y",
            "Days with over 60\n mins activity this week")
        exercise_p2 <- plot_om_cont(row_i, exercise, "physical_activity2_y",
            "Days with\nstrength exercise")
        exercise_p3 <- plot_om_cont(row_i, exercise, "physical_activity5_y",
            "Days of PE class\n per week")
        # NIHTBX
        pattern_p <- plot_om_cont(row_i, pattern, "nihtbx_pattern_fc",
                     "NIHTBX\nPattern Comparison")
        # NIH Cardsort
        card_p <- plot_om_cont(row_i, cardsort, "nihtbx_cardsort_fc",
                     "NIHTBX\nCard Sort")
        # NIH List
        list_p <- plot_om_cont(row_i, list, "nihtbx_list_fc",
                     "NIHTBX\nList Sort")
        ## Sports and Activities
        sa_p1 <- plot_om_cont(row_i, sports, "organized_school_activities",
                     "Activities organized\nwithin school")
        sa_p2 <- plot_om_cont(row_i, sports, "organized_outside_activities",
                     "Activities organized\noutside of school")
        sa_p3 <- plot_om_cont(row_i, sports, "private_instruction_activities",
                     "Activities with\nprivate instruction")
        sa_p4 <- plot_om_cont(row_i, sports, "p12_activities",
                     "Activities in\nthe last year")
        # Prosocial behaviour
        proso_p1 <- plot_om_bar(row_i, prosocial, "q1",
                    "Care about \nothers'\nfeelings")
        proso_p2 <- plot_om_bar(row_i, prosocial, "q2",
                    "Help hurt, upset, \nor sick people")
        proso_p3 <- plot_om_bar(row_i, prosocial, "q3",
                    "Often offer\nto help")
        # rsFMRI
        ## gord_cor
        gord_cor_p <- pheatmap_om_matrix(row_i, gord_cor, binary = TRUE,
            legend = FALSE,
            cw = 50,
            ch = 3,
            main = "Cortical correlations (rs-fMRI)")[[4]]
        ## gord_var
        gord_var_p <- pheatmap_om_matrix(row_i, gord_var,
            legend = FALSE,
            cw = 50,
            ch = 3,
            main = "Cortical variations (rs-fMRI))")[[4]]
        ### subc_cor
        subc_cor_p <- pheatmap_om_matrix(row_i, subc_cor, binary = TRUE,
            legend = FALSE,
            cw = 50,
            ch = 3,
            main = "Subcortical correlations (rs-fMRI)")[[4]]
        ## subc_var
        subc_var_p <- pheatmap_om_matrix(row_i, subc_var,
            legend = FALSE,
            cw = 50,
            ch = 3,
            main = "Subcortical variations (rs-fMRI)")[[4]]
        # Other MRI
        ## dMRI
        wmnd_p <- pheatmap_om_matrix(
            row_i, wmnd, binary = FALSE,
            legend = FALSE,
            cw = 50,
            ch = 3,
            main = "White Matter Neurite Densities")[[4]]
        ## cort_sa
        cort_sa_p <- pheatmap_om_matrix(row_i, cort_sa,
            legend = FALSE,
            cw = 50,
            ch = 3,
            main = "Cortical Surface Area")[[4]]
        ## cort_t
        cort_t_p <- pheatmap_om_matrix(row_i, cort_t,
            legend = FALSE,
            cw = 50,
            ch = 3,
            main = "Cortical Thickness")[[4]]
        ## subc_v
        subc_v_p <- pheatmap_om_matrix(row_i, subc_v,
            legend = FALSE,
            cw = 50,
            ch = 3,
            main = "Subcortical Volume")[[4]]
        # Non-imaging
        ## Family function
        fam_fn_p <- pheatmap_om_matrix(row_i, fam_fn,
            legend = FALSE,
            cw = 50,
            ch = 30,
            show_row = TRUE,
            main = "Family Function")[[4]]
        ## Parent psychopathology
        parent_p <- pheatmap_om_matrix(row_i, parent_psych,
            legend = FALSE,
            cw = 50,
            ch = 30,
            show_row = TRUE,
            main = "Parent Psychopathology")[[4]]
        ## SDS
        sleep_p <- pheatmap_om_matrix(row_i, sds_sleep_df,
            legend = FALSE,
            cw = 50,
            ch = 30,
            show_row = TRUE,
            main = "Sleeping issues")[[4]]
        ## Sports and Activities
        sports_p <- pheatmap_om_matrix(row_i, sports,
            legend = FALSE,
            cw = 50,
            ch = 30,
            show_row = TRUE,
            main = "Sports and Activities")[[4]]
        #
        # Grid creation
        #
        grid_rsfmri <- gridExtra::arrangeGrob(
            gord_var_p,
            subc_cor_p,
            gord_cor_p,
            subc_var_p)
        ggplot2::ggsave(file = r_path,
                        grid_rsfmri,
                        width = 20,
                        height = 30)
        grid_other_mri <- gridExtra::arrangeGrob(
            wmnd_p,
            cort_sa_p,
            cort_t_p,
            subc_v_p)
        ggplot2::ggsave(file = om_path,
                        grid_other_mri,
                        width = 20,
                        height = 20)
        grid_non_imaging <- gridExtra::arrangeGrob(
            fam_fn_p,
            parent_p,
            sleep_p,
            sports_p)
        ggplot2::ggsave(file = o_path,
                        grid_non_imaging,
                        width = 20,
                        height = 30)
        grid <- gridExtra::arrangeGrob(
                abcdutils::clean_plot(loc_p, c("x")),
                abcdutils::clean_plot(mech_p, c("x")),
                abcdutils::clean_plot(dazed_p, c("x")),
                abcdutils::clean_plot(income_p, c("x")),
                abcdutils::clean_plot(race_p, c("x")),
                abcdutils::clean_plot(sex_p, c("x")),
                abcdutils::clean_plot(headache_p, c("x")),
                abcdutils::clean_plot(mtbi_count_p, c("x")),
                abcdutils::clean_plot(proso_p1, c("x")),
                abcdutils::clean_plot(proso_p2, c("x")),
                abcdutils::clean_plot(proso_p3, c("x")),
                abcdutils::clean_plot(sa_p1, c("x")),
                abcdutils::clean_plot(sa_p2, c("x")),
                abcdutils::clean_plot(sa_p3, c("x")),
                abcdutils::clean_plot(sa_p4, c("x")),
                abcdutils::clean_plot(exercise_p1, c("x")),
                abcdutils::clean_plot(exercise_p2, c("x")),
                abcdutils::clean_plot(exercise_p3, c("x")),
                abcdutils::clean_plot(interview_age_p, c("x")),
                abcdutils::clean_plot(injury_age_p, c("x")),
                abcdutils::clean_plot(friend_p1, c("x")),
                abcdutils::clean_plot(friend_p2, c("x")),
                abcdutils::clean_plot(friend_p3, c("x")),
                abcdutils::clean_plot(friend_p4, c("x")),
                abcdutils::clean_plot(wknd_screen_p, c("x")),
                abcdutils::clean_plot(wkd_screen_p, c("x")),
                abcdutils::clean_plot(pattern_p, c("x")),
                abcdutils::clean_plot(card_p, c("x")),
                abcdutils::clean_plot(list_p, c("x")),
                abcdutils::clean_plot(pubertal_p, c("x")))
        ggplot2::ggsave(file = g_path, grid, width = 45, height = 30)
    }
}


input_characterization_plots_g(top_oms,
    loc = train_dfs[[1]],
    mechanism = train_dfs[[2]],
    dazed = train_dfs[[3]],
    income = train_dfs[[4]],
    interview_age = train_dfs[[5]],
    mtbi_age = train_dfs[[6]],
    pubertal = train_dfs[[7]],
    race = train_dfs[[8]],
    sex = train_dfs[[9]],
    headache = train_dfs[[10]],
    mtbi_count = train_dfs[[11]],
    wmnd = train_dfs[[12]],
    gord_cor = train_dfs[[13]],
    gord_var = train_dfs[[14]],
    subc_cor = train_dfs[[15]],
    subc_var = train_dfs[[16]],
    cort_sa = train_dfs[[17]],
    cort_t = train_dfs[[18]],
    subc_v = train_dfs[[19]],
    loneliness = train_dfs[[20]],
    screentime = train_dfs[[21]],
    fam_fn = train_dfs[[22]],
    sports = train_dfs[[23]],
    prosocial = train_dfs[[24]],
    parent_psych = train_dfs[[25]],
    exercise = train_dfs[[26]],
    pattern = nihtbx_pattern,
    cardsort = nihtbx_cardsort,
    list = nihtbx_list,
    general_inp_path = fig_path("general_inputs_train.png", date = TRUE),
    rsfmri_path = fig_path("rsfmri_inputs_train.png", date = TRUE),
    other_mri_path = fig_path("other_mri_train.png", date = TRUE),
    other_heatmap_path = fig_path("other_input_train.png", date = TRUE))



test_dfs <- lapply(data_list_test, function(x) x$"data")

propagated_labels

# Conversion of propagated labels into an om format
propagated_om <- propagated_labels |>
    dplyr::select(-"group") |>
    t()
colnames(propagated_om) <- propagated_om[1, ]
propagated_om <- data.frame(propagated_om[-1, ])
propagated_om$"significance" <- propagated_labels |>
    dplyr::select(-c("subjectkey", "group")) |>
    colnames()
rownames(propagated_om) <- NULL
top_oms$"row_id"
if (all(top_oms$"significance" == propagated_om$"significance")) {
    propagated_om$"row_id" <- top_oms$"row_id"
    propagated_om$"nclust" <- top_oms$"nclust"
}

input_characterization_plots_g(propagated_om,
    loc = test_dfs[[1]],
    mechanism = test_dfs[[2]],
    dazed = test_dfs[[3]],
    income = test_dfs[[4]],
    interview_age = test_dfs[[5]],
    mtbi_age = test_dfs[[6]],
    pubertal = test_dfs[[7]],
    race = test_dfs[[8]],
    sex = test_dfs[[9]],
    headache = test_dfs[[10]],
    mtbi_count = test_dfs[[11]],
    wmnd = test_dfs[[12]],
    gord_cor = test_dfs[[13]],
    gord_var = test_dfs[[14]],
    subc_cor = test_dfs[[15]],
    subc_var = test_dfs[[16]],
    cort_sa = test_dfs[[17]],
    cort_t = test_dfs[[18]],
    subc_v = test_dfs[[19]],
    loneliness = test_dfs[[20]],
    screentime = test_dfs[[21]],
    fam_fn = test_dfs[[22]],
    sports = test_dfs[[23]],
    prosocial = test_dfs[[24]],
    parent_psych = test_dfs[[25]],
    exercise = test_dfs[[26]],
    pattern = nihtbx_pattern,
    cardsort = nihtbx_cardsort,
    list = nihtbx_list,
    general_inp_path = fig_path("general_inputs_test.png", date = TRUE),
    rsfmri_path = fig_path("rsfmri_inputs_test.png", date = TRUE),
    other_mri_path = fig_path("other_mri_test.png", date = TRUE),
    other_heatmap_path = fig_path("other_input_test.png", date = TRUE))

```


