# Cluster characterization

## Load libraries and data

```{r}
library(scabcd)
library(rlist)
library(abcdutils)
library(here)
library(readr)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))

proc_writer <- make_writer(proc_path)
proc_reader <- make_reader(proc_path)

top_oms <- read_csv(proc_path("2023_03_09_top_om_rows_all_nclust.csv"))

data_list_train <- list.load(proc_path("2023_03_15_data_list_train.rdata"))
cbcl_list_train <- list.load(proc_path("2023_03_15_cbcl_list_train.rdata"))
data_list_full <- list.load(proc_path("2023_03_15_data_list_full.rdata"))
cbcl_list_full <- list.load(proc_path("2023_03_15_cbcl_list_full.rdata"))
```


## CBCL plotting in the training subjects

The function below generates a grid of CBCL impairment plots for each cluster solution and saves them using a provided `path_maker` function.

```{r}
om_plot_all_cbcl(top_oms, cbcl_list_train, fig_path)

cbcl_ord_reg_from_om(top_oms[1, ], cbcl_list_train)

cbcl_ord_reg_from_om(top_oms[2, ], cbcl_list_train)

for (row in seq_len(nrow(top_oms))) {
    current_row <- top_oms[row, ]
    print(current_row$"significance")
    print(cbcl_ord_reg_from_om(current_row, cbcl_list_train))
}
```


## NMI calculations

I have found that the `om_to_nmi_df` function can yield different results across different machines.
I believe this is due to to hardware-specific differences in handling floating point arithmetic during the SNFTool package's implementation of spectral clustering.
Moving forward, I use results generated by the machine at SickKids (Intel(R) Core(TM) i5-10400 CPU @ 2.90 GHz).
Some notable file versions are `2023_03_13_nmi_df.csv` (the first run of the `om_to_nmi_df` function, calculated at the SickKids machine) and `2023_03_15_nmi_df.csv` (run from my home machine, yielding distinct results).


```{r}
nmi_df <- om_to_nmi_df(top_oms, data_list_train)

write_csv(nmi_df, proc_path("nmi_df_sk.csv", date = TRUE))

nmi_df <- data.frame(read_csv(proc_path("2023_03_16_nmi_df_sk.csv")))
```


## Label propagation

```{r}
propagated_labels <- lp_om(top_oms, data_list_full)

write_csv(propagated_labels, proc_path("top_oms_lp.csv", date = TRUE))

propagated_labels <- proc_reader("2023_03_16_top_oms_lp.csv")
```

## CBCL plotting in the label propagated group

```{r}
test_labels <- propagated_labels |>
    dplyr::filter(group == "test") |>
    dplyr::select(-"group")

outcomes_and_eval_df <- append(list(test_labels), cbcl_list_full)

test_eval_df <- merge_df_list(outcomes_and_eval_df)

test_plot_all_cbcl <- function(eval_df, full_cbcl_list, fig_path_fn) {
    solutions <- eval_df |>
        dplyr::select(-dplyr::starts_with(c("subject", "cbcl"))) |>
        colnames()
    for (solution in solutions) {
        cluster_df <- eval_df |>
            dplyr::select(!!solution, "subjectkey") |>
            data.frame()
        colnames(cluster_df) <- c("cluster", "subjectkey")
        current_sig <- solution
        plot_all_cbcl(
            cluster_df,
            current_sig,
            full_cbcl_list,
            save = fig_path_fn(paste0(current_sig, "_lp.png"), date = TRUE))
    }
}

test_plot_all_cbcl(test_eval_df, cbcl_list_full, fig_path)
```

## Plotting and assessing inputs
```{r}
nmi_df

# How NMIs are distributed
plot_nmis(nmi_df, fig_path)
```


## Input variable characterization
```{r}

train_dfs <- lapply(data_list_train, function(x) x$"data")

train_df_names <- lapply(data_list_train, function(x) x$"name") |>
    unlist()

subjects_train <- data_list_train[[1]]$"data"$"subjectkey"

subjects_train

top_oms

train_df_names

plot_om_bar <- function(om_row, input_df, feature, featname) {
    cluster_df <- get_cluster_df(om_row)
    characterization_df <-
        dplyr::inner_join(cluster_df, input_df, by = "subjectkey")
    cluster <- ""
    percent <- ""
    n <- ""
    keycol <- ""
    characterization_df <- characterization_df |>
        dplyr::rename("keycol" = !!feature) # wizardry
    summary <- characterization_df |>
        dplyr::group_by(cluster) |>
        dplyr::count(keycol) |>
        dplyr::mutate(percent = round(n / sum(n) * 100))
    if (is.numeric(summary$"keycol")) {
        lvl <- as.character(rev(sort(unique(summary$"keycol"))))
        summary$"keycol" <- factor(summary$"keycol", levels = lvl)
    } else {
        summary$"keycol" <- factor(summary$"keycol")
    }
    summary$"cluster" <- factor(summary$"cluster")
    plot <- ggplot2::ggplot(
        summary,
        ggplot2::aes(
            x = cluster,
            y = percent,
            fill = keycol)) +
        ggplot2::geom_bar(
            stat = "identity",
            position = ggplot2::position_stack()) +
        ggplot2::geom_text(
            mapping = ggplot2::aes(
                label = n,
                y = percent),
            position = ggplot2::position_stack(
                vjust = 0.5)) +
        ggplot2::scale_y_continuous(
            expand = ggplot2::expansion(mult = c(0, .1))) +
        ggplot2::labs(
            x = "Cluster",
            y = "Percentage",
            fill = featname) +
        ggplot2::theme_bw() +
        ggplot2::theme(
            text = ggplot2::element_text(
                size = 20))
    print(plot)
}

plot_om_cont <- function(om_row, input_df, feature, featname) {
    cluster_df <- get_cluster_df(om_row)
    cluster <- ""
    keycol <- ""
    characterization_df <-
        dplyr::inner_join(cluster_df, input_df, by = "subjectkey")
    characterization_df <- characterization_df |>
        dplyr::rename("keycol" = !!feature) # wizardry
    characterization_df$"cluster" <- factor(characterization_df$"cluster")
    plot <- ggplot2::ggplot(
        characterization_df,
        ggplot2::aes(
            x = cluster,
            y = keycol)) +
        ggplot2::geom_boxplot() +
        ggplot2::geom_jitter(height = 0, alpha = 0.2, size = 4) +
        ggplot2::scale_y_continuous(
            expand = ggplot2::expansion(mult = c(0, .1))) +
        ggplot2::labs(
            x = "Cluster",
            y = featname) +
        ggplot2::theme_bw() +
        ggplot2::theme(
            text = ggplot2::element_text(
                size = 20))
    print(plot)
}


row <- 1

# LOC
plot_om_bar(top_oms[row, ], train_dfs[[1]], "latest_mtbi_loc", "LOC")

# Mechanism
plot_om_bar(top_oms[row, ], train_dfs[[2]], "latest_mtbi_mechanism", "MOI")

# Mem/dazed
plot_om_bar(top_oms[row, ], train_dfs[[3]], "latest_mtbi_mem_daze", "Dazed")

# Income
plot_om_cont(top_oms[row, ], train_dfs[[4]], "household_income", "Income")

# Age at interview
plot_om_cont(top_oms[row, ], train_dfs[[5]], "interview_age", "Interview Age")

# Age at injury
plot_om_cont(top_oms[row, ], train_dfs[[6]], "latest_mtbi_age", "Injury Age")

# Pubertal status
plot_om_cont(top_oms[row, ], train_dfs[[7]], "pubertal_status", "Pubertal")

# Race
plot_om_bar(top_oms[row, ], train_dfs[[8]], "race", "Race")

# Sex
plot_om_bar(top_oms[row, ], train_dfs[[9]], "M", "Male")

# Headaches
plot_om_bar(top_oms[row, ], train_dfs[[10]], "headache", "Headaches")

# Number of injuries
plot_om_cont(top_oms[row, ], train_dfs[[11]], "mtbi_count", "mTBI Count")

colnames(train_dfs[[12]])

ndwm <- train_dfs[[12]]

ndwm
cluster_df <- get_cluster_df(top_oms[row, ])

char_df <- dplyr::inner_join(ndwm, cluster_df, by = "subjectkey")

c1_char_df <- char_df |>
    dplyr::filter(cluster == 1) |>
    dplyr::select(-"cluster")

new_df <- char_df |>
    dplyr::group_by(cluster) |>
    dplyr::select(-"subjectkey") |>
    dplyr::summarize_all(mean) |>
    dplyr::select(-"cluster") |>
    t()

new_df

new_df_row_max <- apply(new_df, 1, max)

for (i in seq_len(nrow(new_df))) {
    new_df[i, ] <- (new_df[i, ] / new_df_row_max[i])
}

pheatmap::pheatmap(new_df)

a <- matrix(c(9, 2, 1, 4, 6, 7, 2, 2, 3), 3, 3)
a
b <- apply(a, 1, max)
b
for (i in seq_len(nrow(a))) {
    a[i, ] <- (a[i, ] / b[i])
}

a

i <- 12
colnames(train_dfs[[i]])
train_df_names[i]
```


