# Data organization

This chapter loads the raw and imputed input files and organizes them into the objects that will be used for subsequent analyses.

## Training and testing data splits

```{r eval = FALSE}
library(abcdutils)
library(scabcd)
library(readr)
library(here)


# Functions to import data from carbon
input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))


# Importing data
as_mtbi_loc <- read_csv(input_path("as_mtbi_loc_imp.csv"))
as_mtbi_mechanism <- read_csv(input_path("as_mtbi_mechanism_imp.csv"))
as_mtbi_mem_daze <- read_csv(input_path("as_mtbi_mem_daze_imp.csv"))
d_income <- read_csv(input_path("d_income_imp.csv"))
d_interview_age <- read_csv(input_path("d_interview_age_imp.csv"))
d_mtbi_age <- read_csv(input_path("d_mtbi_age_imp.csv"))
d_pubertal_status <- read_csv(input_path("d_pubertal_status_imp.csv"))
d_race <- read_csv(input_path("d_race_imp.csv"))
d_sex <- read_csv(input_path("d_sex_imp.csv"))
mh_headaches <- read_csv(input_path("mh_headaches_imp.csv"))
mh_mtbi_count <- read_csv(input_path("mh_mtbi_count_imp.csv"))
dm_wmndf_qc <- read_csv(input_path("dm_wmndf_qc.csv"))
rm_gord_cor_qc <- read_csv(input_path("rm_gord_cor_qc.csv"))
rm_gord_var_qc <- read_csv(input_path("rm_gord_var_qc.csv"))
rm_subc_cor_qc <- read_csv(input_path("rm_subc_cor_qc.csv"))
rm_subc_var_qc <- read_csv(input_path("rm_subc_var_qc.csv"))
sm_cort_sa_qc <- read_csv(input_path("sm_cort_sa_qc.csv"))
sm_cort_t_qc <- read_csv(input_path("sm_cort_t_qc.csv"))
sm_subc_v_qc <- read_csv(input_path("sm_subc_v_qc.csv"))
p_loneliness <- read_csv(input_path("p_loneliness_imp.csv"))
p_screen_time <- read_csv(input_path("p_screen_time_imp.csv"))
p_family_function <- read_csv(input_path("p_family_function_imp.csv"))
p_sports <- read_csv(input_path("p_sports_imp.csv"))
p_prosocial <- read_csv(input_path("p_prosocial_imp.csv"))
p_parent_psych <- read_csv(input_path("p_parent_psych_imp.csv"))
p_exercise <- read_csv(input_path("p_exercise_imp.csv"))
cbcl_headaches <- read_csv(input_path("cbcl_headaches_imp.csv"))
cbcl_nausea <- read_csv(input_path("cbcl_nausea_imp.csv"))
cbcl_vomiting <- read_csv(input_path("cbcl_vomiting_imp.csv"))
cbcl_dizzy <- read_csv(input_path("cbcl_dizzy_imp.csv"))
cbcl_overtired <- read_csv(input_path("cbcl_overtired_imp.csv"))
cbcl_sleeping_more <- read_csv(input_path("cbcl_sleeping_more_imp.csv"))
cbcl_sleeping_less <- read_csv(input_path("cbcl_sleeping_less_imp.csv"))
cbcl_depress <- read_csv(input_path("cbcl_depress_imp.csv"))
cbcl_anxiety <- read_csv(input_path("cbcl_anxiety_imp.csv"))
cbcl_attention <- read_csv(input_path("cbcl_attention_imp.csv"))
cbcl_aggressive <- read_csv(input_path("cbcl_aggressive_imp.csv"))
sds_sleep <- read_csv(input_path("sds_sleep_imp.csv"))
nihtbx_list_fc <- read_csv(input_path("nihtbx_list_fc_imp.csv"))
nihtbx_pattern_fc <- read_csv(input_path("nihtbx_pattern_fc_imp.csv"))
nihtbx_cardsort_fc <- read_csv(input_path("nihtbx_cardsort_fc_imp.csv"))


# Filtering to common subjects
common_subs <- common_subjects(list(mtbi_loc = as_mtbi_loc,
    as_mtbi_mechanism,
    as_mtbi_mem_daze,
    d_income,
    d_interview_age,
    d_mtbi_age,
    d_pubertal_status,
    d_race,
    d_sex,
    mh_headaches,
    mh_mtbi_count,
    dm_wmndf_qc,
    rm_gord_cor_qc,
    rm_gord_var_qc,
    rm_subc_cor_qc,
    rm_subc_var_qc,
    sm_cort_sa_qc,
    sm_cort_t_qc,
    sm_subc_v_qc,
    p_loneliness,
    p_screen_time,
    p_family_function,
    p_sports,
    p_prosocial,
    p_parent_psych,
    p_exercise,
    cbcl_headaches,
    cbcl_nausea,
    cbcl_vomiting,
    cbcl_dizzy,
    cbcl_overtired,
    cbcl_sleeping_more,
    cbcl_sleeping_less,
    cbcl_depress,
    cbcl_anxiety,
    cbcl_attention,
    cbcl_aggressive,
    sds_sleep))

# Assigning common subjects into training and testing sets
assigned_df <- train_test_assign(train_frac = 0.8, subjects = common_subs)

# Generate training set
as_mtbi_loc_train <- keep_split(as_mtbi_loc, assigned_df, "train")
as_mtbi_mechanism_train <- keep_split(as_mtbi_mechanism, assigned_df, "train")
as_mtbi_mem_daze_train <- keep_split(as_mtbi_mem_daze, assigned_df, "train")
d_income_train <- keep_split(d_income, assigned_df, "train")
d_interview_age_train <- keep_split(d_interview_age, assigned_df, "train")
d_mtbi_age_train <- keep_split(d_mtbi_age, assigned_df, "train")
d_pubertal_status_train <- keep_split(d_pubertal_status, assigned_df, "train")
d_race_train <- keep_split(d_race, assigned_df, "train")
d_sex_train <- keep_split(d_sex, assigned_df, "train")
mh_headaches_train <- keep_split(mh_headaches, assigned_df, "train")
mh_mtbi_count_train <- keep_split(mh_mtbi_count, assigned_df, "train")
dm_wmndf_qc_train <- keep_split(dm_wmndf_qc, assigned_df, "train")
rm_gord_cor_qc_train <- keep_split(rm_gord_cor_qc, assigned_df, "train")
rm_gord_var_qc_train <- keep_split(rm_gord_var_qc, assigned_df, "train")
rm_subc_cor_qc_train <- keep_split(rm_subc_cor_qc, assigned_df, "train")
rm_subc_var_qc_train <- keep_split(rm_subc_var_qc, assigned_df, "train")
sm_cort_sa_qc_train <- keep_split(sm_cort_sa_qc, assigned_df, "train")
sm_cort_t_qc_train <- keep_split(sm_cort_t_qc, assigned_df, "train")
sm_subc_v_qc_train <- keep_split(sm_subc_v_qc, assigned_df, "train")
p_loneliness_train <- keep_split(p_loneliness, assigned_df, "train")
p_screen_time_train <- keep_split(p_screen_time, assigned_df, "train")
p_family_function_train <- keep_split(p_family_function, assigned_df, "train")
p_sports_train <- keep_split(p_sports, assigned_df, "train")
p_prosocial_train <- keep_split(p_prosocial, assigned_df, "train")
p_parent_psych_train <- keep_split(p_parent_psych, assigned_df, "train")
p_exercise_train <- keep_split(p_exercise, assigned_df, "train")
cbcl_headaches_train <- keep_split(cbcl_headaches, assigned_df, "train")
cbcl_nausea_train <- keep_split(cbcl_nausea, assigned_df, "train")
cbcl_vomiting_train <- keep_split(cbcl_vomiting, assigned_df, "train")
cbcl_dizzy_train <- keep_split(cbcl_dizzy, assigned_df, "train")
cbcl_overtired_train <- keep_split(cbcl_overtired, assigned_df, "train")
cbcl_sleeping_more_train <- keep_split(cbcl_sleeping_more, assigned_df, "train")
cbcl_sleeping_less_train <- keep_split(cbcl_sleeping_less, assigned_df, "train")
cbcl_depress_train <- keep_split(cbcl_depress, assigned_df, "train")
cbcl_anxiety_train <- keep_split(cbcl_anxiety, assigned_df, "train")
cbcl_attention_train <- keep_split(cbcl_attention, assigned_df, "train")
cbcl_aggressive_train <- keep_split(cbcl_aggressive, assigned_df, "train")
sds_sleep_train <- keep_split(sds_sleep, assigned_df, "train")

# Generate testing set
as_mtbi_loc_test <- keep_split(as_mtbi_loc, assigned_df, "test")
as_mtbi_mechanism_test <- keep_split(as_mtbi_mechanism, assigned_df, "test")
as_mtbi_mem_daze_test <- keep_split(as_mtbi_mem_daze, assigned_df, "test")
d_income_test <- keep_split(d_income, assigned_df, "test")
d_interview_age_test <- keep_split(d_interview_age, assigned_df, "test")
d_mtbi_age_test <- keep_split(d_mtbi_age, assigned_df, "test")
d_pubertal_status_test <- keep_split(d_pubertal_status, assigned_df, "test")
d_race_test <- keep_split(d_race, assigned_df, "test")
d_sex_test <- keep_split(d_sex, assigned_df, "test")
mh_headaches_test <- keep_split(mh_headaches, assigned_df, "test")
mh_mtbi_count_test <- keep_split(mh_mtbi_count, assigned_df, "test")
dm_wmndf_qc_test <- keep_split(dm_wmndf_qc, assigned_df, "test")
rm_gord_cor_qc_test <- keep_split(rm_gord_cor_qc, assigned_df, "test")
rm_gord_var_qc_test <- keep_split(rm_gord_var_qc, assigned_df, "test")
rm_subc_cor_qc_test <- keep_split(rm_subc_cor_qc, assigned_df, "test")
rm_subc_var_qc_test <- keep_split(rm_subc_var_qc, assigned_df, "test")
sm_cort_sa_qc_test <- keep_split(sm_cort_sa_qc, assigned_df, "test")
sm_cort_t_qc_test <- keep_split(sm_cort_t_qc, assigned_df, "test")
sm_subc_v_qc_test <- keep_split(sm_subc_v_qc, assigned_df, "test")
p_loneliness_test <- keep_split(p_loneliness, assigned_df, "test")
p_screen_time_test <- keep_split(p_screen_time, assigned_df, "test")
p_family_function_test <- keep_split(p_family_function, assigned_df, "test")
p_sports_test <- keep_split(p_sports, assigned_df, "test")
p_prosocial_test <- keep_split(p_prosocial, assigned_df, "test")
p_parent_psych_test <- keep_split(p_parent_psych, assigned_df, "test")
p_exercise_test <- keep_split(p_exercise, assigned_df, "test")
cbcl_headaches_test <- keep_split(cbcl_headaches, assigned_df, "test")
cbcl_nausea_test <- keep_split(cbcl_nausea, assigned_df, "test")
cbcl_vomiting_test <- keep_split(cbcl_vomiting, assigned_df, "test")
cbcl_dizzy_test <- keep_split(cbcl_dizzy, assigned_df, "test")
cbcl_overtired_test <- keep_split(cbcl_overtired, assigned_df, "test")
cbcl_sleeping_more_test <- keep_split(cbcl_sleeping_more, assigned_df, "test")
cbcl_sleeping_less_test <- keep_split(cbcl_sleeping_less, assigned_df, "test")
cbcl_depress_test <- keep_split(cbcl_depress, assigned_df, "test")
cbcl_anxiety_test <- keep_split(cbcl_anxiety, assigned_df, "test")
cbcl_attention_test <- keep_split(cbcl_attention, assigned_df, "test")
cbcl_aggressive_test <- keep_split(cbcl_aggressive, assigned_df, "test")
sds_sleep_test <- keep_split(sds_sleep, assigned_df, "test")

# Generate full set (note that this is structured specifically in row order of
#  training subjects followed by testing subjects)
as_mtbi_loc_full <- rbind(as_mtbi_loc_train, as_mtbi_loc_test)
as_mtbi_mechanism_full <- rbind(as_mtbi_mechanism_train, as_mtbi_mechanism_test)
as_mtbi_mem_daze_full <- rbind(as_mtbi_mem_daze_train, as_mtbi_mem_daze_test)
d_income_full <- rbind(d_income_train, d_income_test)
d_interview_age_full <- rbind(d_interview_age_train, d_interview_age_test)
d_mtbi_age_full <- rbind(d_mtbi_age_train, d_mtbi_age_test)
d_pubertal_status_full <- rbind(d_pubertal_status_train, d_pubertal_status_test)
d_race_full <- rbind(d_race_train, d_race_test)
d_sex_full <- rbind(d_sex_train, d_sex_test)
mh_headaches_full <- rbind(mh_headaches_train, mh_headaches_test)
mh_mtbi_count_full <- rbind(mh_mtbi_count_train, mh_mtbi_count_test)
dm_wmndf_qc_full <- rbind(dm_wmndf_qc_train, dm_wmndf_qc_test)
rm_gord_cor_qc_full <- rbind(rm_gord_cor_qc_train, rm_gord_cor_qc_test)
rm_gord_var_qc_full <- rbind(rm_gord_var_qc_train, rm_gord_var_qc_test)
rm_subc_cor_qc_full <- rbind(rm_subc_cor_qc_train, rm_subc_cor_qc_test)
rm_subc_var_qc_full <- rbind(rm_subc_var_qc_train, rm_subc_var_qc_test)
sm_cort_sa_qc_full <- rbind(sm_cort_sa_qc_train, sm_cort_sa_qc_test)
sm_cort_t_qc_full <- rbind(sm_cort_t_qc_train, sm_cort_t_qc_test)
sm_subc_v_qc_full <- rbind(sm_subc_v_qc_train, sm_subc_v_qc_test)
p_loneliness_full <- rbind(p_loneliness_train, p_loneliness_test)
p_screen_time_full <- rbind(p_screen_time_train, p_screen_time_test)
p_family_function_full <- rbind(p_family_function_train, p_family_function_test)
p_sports_full <- rbind(p_sports_train, p_sports_test)
p_prosocial_full <- rbind(p_prosocial_train, p_prosocial_test)
p_parent_psych_full <- rbind(p_parent_psych_train, p_parent_psych_test)
p_exercise_full <- rbind(p_exercise_train, p_exercise_test)
cbcl_headaches_full <- rbind(cbcl_headaches_train, cbcl_headaches_test)
cbcl_nausea_full <- rbind(cbcl_nausea_train, cbcl_nausea_test)
cbcl_vomiting_full <- rbind(cbcl_vomiting_train, cbcl_vomiting_test)
cbcl_dizzy_full <- rbind(cbcl_dizzy_train, cbcl_dizzy_test)
cbcl_overtired_full <- rbind(cbcl_overtired_train, cbcl_overtired_test)
cbcl_sleeping_more_full <-
    rbind(cbcl_sleeping_more_train, cbcl_sleeping_more_test)
cbcl_sleeping_less_full <-
    rbind(cbcl_sleeping_less_train, cbcl_sleeping_less_test)
cbcl_depress_full <- rbind(cbcl_depress_train, cbcl_depress_test)
cbcl_anxiety_full <- rbind(cbcl_anxiety_train, cbcl_anxiety_test)
cbcl_attention_full <- rbind(cbcl_attention_train, cbcl_attention_test)
cbcl_aggressive_full <- rbind(cbcl_aggressive_train, cbcl_aggressive_test)


# Export training set
write_csv(as_mtbi_loc_train, proc_path("as_mtbi_loc_train.csv"))
write_csv(as_mtbi_mechanism_train, proc_path("as_mtbi_mechanism_train.csv"))
write_csv(as_mtbi_mem_daze_train, proc_path("as_mtbi_mem_daze_train.csv"))
write_csv(d_income_train, proc_path("d_income_train.csv"))
write_csv(d_interview_age_train, proc_path("d_interview_age_train.csv"))
write_csv(d_mtbi_age_train, proc_path("d_mtbi_age_train.csv"))
write_csv(d_pubertal_status_train, proc_path("d_pubertal_status_train.csv"))
write_csv(d_race_train, proc_path("d_race_train.csv"))
write_csv(d_sex_train, proc_path("d_sex_train.csv"))
write_csv(mh_headaches_train, proc_path("mh_headaches_train.csv"))
write_csv(mh_mtbi_count_train, proc_path("mh_mtbi_count_train.csv"))
write_csv(dm_wmndf_qc_train, proc_path("dm_wmndf_qc_train.csv"))
write_csv(rm_gord_cor_qc_train, proc_path("rm_gord_cor_qc_train.csv"))
write_csv(rm_gord_var_qc_train, proc_path("rm_gord_var_qc_train.csv"))
write_csv(rm_subc_cor_qc_train, proc_path("rm_subc_cor_qc_train.csv"))
write_csv(rm_subc_var_qc_train, proc_path("rm_subc_var_qc_train.csv"))
write_csv(sm_cort_sa_qc_train, proc_path("sm_cort_sa_qc_train.csv"))
write_csv(sm_cort_t_qc_train, proc_path("sm_cort_t_qc_train.csv"))
write_csv(sm_subc_v_qc_train, proc_path("sm_subc_v_qc_train.csv"))
write_csv(p_loneliness_train, proc_path("p_loneliness_train.csv"))
write_csv(p_screen_time_train, proc_path("p_screen_time_train.csv"))
write_csv(p_family_function_train, proc_path("p_family_function_train.csv"))
write_csv(p_sports_train, proc_path("p_sports_train.csv"))
write_csv(p_prosocial_train, proc_path("p_prosocial_train.csv"))
write_csv(p_parent_psych_train, proc_path("p_parent_psych_train.csv"))
write_csv(p_exercise_train, proc_path("p_exercise_train.csv"))
write_csv(cbcl_headaches_train, proc_path("cbcl_headaches_train.csv"))
write_csv(cbcl_nausea_train, proc_path("cbcl_nausea_train.csv"))
write_csv(cbcl_vomiting_train, proc_path("cbcl_vomiting_train.csv"))
write_csv(cbcl_dizzy_train, proc_path("cbcl_dizzy_train.csv"))
write_csv(cbcl_overtired_train, proc_path("cbcl_overtired_train.csv"))
write_csv(cbcl_sleeping_more_train, proc_path("cbcl_sleeping_more_train.csv"))
write_csv(cbcl_sleeping_less_train, proc_path("cbcl_sleeping_less_train.csv"))
write_csv(cbcl_depress_train, proc_path("cbcl_depress_train.csv"))
write_csv(cbcl_anxiety_train, proc_path("cbcl_anxiety_train.csv"))
write_csv(cbcl_attention_train, proc_path("cbcl_attention_train.csv"))
write_csv(cbcl_aggressive_train, proc_path("cbcl_aggressive_train.csv"))
write_csv(sds_sleep_train, proc_path("sds_sleep_train.csv"))

# Export testing set
write_csv(as_mtbi_loc_test, proc_path("as_mtbi_loc_test.csv"))
write_csv(as_mtbi_mechanism_test, proc_path("as_mtbi_mechanism_test.csv"))
write_csv(as_mtbi_mem_daze_test, proc_path("as_mtbi_mem_daze_test.csv"))
write_csv(d_income_test, proc_path("d_income_test.csv"))
write_csv(d_interview_age_test, proc_path("d_interview_age_test.csv"))
write_csv(d_mtbi_age_test, proc_path("d_mtbi_age_test.csv"))
write_csv(d_pubertal_status_test, proc_path("d_pubertal_status_test.csv"))
write_csv(d_race_test, proc_path("d_race_test.csv"))
write_csv(d_sex_test, proc_path("d_sex_test.csv"))
write_csv(mh_headaches_test, proc_path("mh_headaches_test.csv"))
write_csv(mh_mtbi_count_test, proc_path("mh_mtbi_count_test.csv"))
write_csv(dm_wmndf_qc_test, proc_path("dm_wmndf_qc_test.csv"))
write_csv(rm_gord_cor_qc_test, proc_path("rm_gord_cor_qc_test.csv"))
write_csv(rm_gord_var_qc_test, proc_path("rm_gord_var_qc_test.csv"))
write_csv(rm_subc_cor_qc_test, proc_path("rm_subc_cor_qc_test.csv"))
write_csv(rm_subc_var_qc_test, proc_path("rm_subc_var_qc_test.csv"))
write_csv(sm_cort_sa_qc_test, proc_path("sm_cort_sa_qc_test.csv"))
write_csv(sm_cort_t_qc_test, proc_path("sm_cort_t_qc_test.csv"))
write_csv(sm_subc_v_qc_test, proc_path("sm_subc_v_qc_test.csv"))
write_csv(p_loneliness_test, proc_path("p_loneliness_test.csv"))
write_csv(p_screen_time_test, proc_path("p_screen_time_test.csv"))
write_csv(p_family_function_test, proc_path("p_family_function_test.csv"))
write_csv(p_sports_test, proc_path("p_sports_test.csv"))
write_csv(p_prosocial_test, proc_path("p_prosocial_test.csv"))
write_csv(p_parent_psych_test, proc_path("p_parent_psych_test.csv"))
write_csv(p_exercise_test, proc_path("p_exercise_test.csv"))
write_csv(cbcl_headaches_test, proc_path("cbcl_headaches_test.csv"))
write_csv(cbcl_nausea_test, proc_path("cbcl_nausea_test.csv"))
write_csv(cbcl_vomiting_test, proc_path("cbcl_vomiting_test.csv"))
write_csv(cbcl_dizzy_test, proc_path("cbcl_dizzy_test.csv"))
write_csv(cbcl_overtired_test, proc_path("cbcl_overtired_test.csv"))
write_csv(cbcl_sleeping_more_test, proc_path("cbcl_sleeping_more_test.csv"))
write_csv(cbcl_sleeping_less_test, proc_path("cbcl_sleeping_less_test.csv"))
write_csv(cbcl_depress_test, proc_path("cbcl_depress_test.csv"))
write_csv(cbcl_anxiety_test, proc_path("cbcl_anxiety_test.csv"))
write_csv(cbcl_attention_test, proc_path("cbcl_attention_test.csv"))
write_csv(cbcl_aggressive_test, proc_path("cbcl_aggressive_test.csv"))
write_csv(sds_sleep_test, proc_path("sds_sleep_test.csv"))

# Full data
write_csv(as_mtbi_loc_full, proc_path("as_mtbi_loc_full.csv"))
write_csv(as_mtbi_mechanism_full, proc_path("as_mtbi_mechanism_full.csv"))
write_csv(as_mtbi_mem_daze_full, proc_path("as_mtbi_mem_daze_full.csv"))
write_csv(d_income_full, proc_path("d_income_full.csv"))
write_csv(d_interview_age_full, proc_path("d_interview_age_full.csv"))
write_csv(d_mtbi_age_full, proc_path("d_mtbi_age_full.csv"))
write_csv(d_pubertal_status_full, proc_path("d_pubertal_status_full.csv"))
write_csv(d_race_full, proc_path("d_race_full.csv"))
write_csv(d_sex_full, proc_path("d_sex_full.csv"))
write_csv(mh_headaches_full, proc_path("mh_headaches_full.csv"))
write_csv(mh_mtbi_count_full, proc_path("mh_mtbi_count_full.csv"))
write_csv(dm_wmndf_qc_full, proc_path("dm_wmndf_qc_full.csv"))
write_csv(rm_gord_cor_qc_full, proc_path("rm_gord_cor_qc_full.csv"))
write_csv(rm_gord_var_qc_full, proc_path("rm_gord_var_qc_full.csv"))
write_csv(rm_subc_cor_qc_full, proc_path("rm_subc_cor_qc_full.csv"))
write_csv(rm_subc_var_qc_full, proc_path("rm_subc_var_qc_full.csv"))
write_csv(sm_cort_sa_qc_full, proc_path("sm_cort_sa_qc_full.csv"))
write_csv(sm_cort_t_qc_full, proc_path("sm_cort_t_qc_full.csv"))
write_csv(sm_subc_v_qc_full, proc_path("sm_subc_v_qc_full.csv"))
write_csv(p_loneliness_full, proc_path("p_loneliness_full.csv"))
write_csv(p_screen_time_full, proc_path("p_screen_time_full.csv"))
write_csv(p_family_function_full, proc_path("p_family_function_full.csv"))
write_csv(p_sports_full, proc_path("p_sports_full.csv"))
write_csv(p_prosocial_full, proc_path("p_prosocial_full.csv"))
write_csv(p_parent_psych_full, proc_path("p_parent_psych_full.csv"))
write_csv(p_exercise_full, proc_path("p_exercise_full.csv"))
write_csv(cbcl_headaches_full, proc_path("cbcl_headaches_full.csv"))
write_csv(cbcl_nausea_full, proc_path("cbcl_nausea_full.csv"))
write_csv(cbcl_vomiting_full, proc_path("cbcl_vomiting_full.csv"))
write_csv(cbcl_dizzy_full, proc_path("cbcl_dizzy_full.csv"))
write_csv(cbcl_overtired_full, proc_path("cbcl_overtired_full.csv"))
write_csv(cbcl_sleeping_more_full, proc_path("cbcl_sleeping_more_full.csv"))
write_csv(cbcl_sleeping_less_full, proc_path("cbcl_sleeping_less_full.csv"))
write_csv(cbcl_depress_full, proc_path("cbcl_depress_full.csv"))
write_csv(cbcl_anxiety_full, proc_path("cbcl_anxiety_full.csv"))
write_csv(cbcl_attention_full, proc_path("cbcl_attention_full.csv"))
write_csv(cbcl_aggressive_full, proc_path("cbcl_aggressive_full.csv"))
```


## Data and outcome lists

Subsequent analyses make use of custom `data_list` and `outcome_list` objects that store information about all input variables and outcome (CBCL) measures used for SNF and cluster characterization.
I also store make use of a `cbcl_list` object, which is simply a list of cbcl dataframes and does not keep a track of the same amount of metadata as used in the highly nested `outcome_list` object.
Instead of loading each individual file and building these lists, we can build the lists here and export them for later use.

```{r}
library(rlist)

# Training data list
data_list_train <- generate_data_list(
    mtbi_loc = as_mtbi_loc_train,
    mtbi_mechanism = as_mtbi_mechanism_train,
    mtbi_mem_daze = as_mtbi_mem_daze_train,
    income = d_income_train,
    interview_age = d_interview_age_train,
    mtbi_age = d_mtbi_age_train,
    pubertal_status = d_pubertal_status_train,
    race = d_race_train,
    sex = d_sex_train,
    headaches = mh_headaches_train,
    mtbi_count = mh_mtbi_count_train,
    wmndf = dm_wmndf_qc_train,
    gord_cor = rm_gord_cor_qc_train,
    gord_var = rm_gord_var_qc_train,
    subc_cor = rm_subc_cor_qc_train,
    subc_var = rm_subc_var_qc_train,
    cort_sa = sm_cort_sa_qc_train,
    cort_t = sm_cort_t_qc_train,
    subc_v = sm_subc_v_qc_train,
    loneliness = p_loneliness_train,
    screen_time = p_screen_time_train,
    family_function = p_family_function_train,
    sports = p_sports_train,
    prosocial = p_prosocial_train,
    parent_psych = p_parent_psych_train,
    exercise = p_exercise_train)

list.save(data_list_train, proc_path("data_list_train.rdata", date = TRUE))


# Testing data list
data_list_test <- generate_data_list(
    mtbi_loc = as_mtbi_loc_test,
    mtbi_mechanism = as_mtbi_mechanism_test,
    mtbi_mem_daze = as_mtbi_mem_daze_test,
    income = d_income_test,
    interview_age = d_interview_age_test,
    mtbi_age = d_mtbi_age_test,
    pubertal_status = d_pubertal_status_test,
    race = d_race_test,
    sex = d_sex_test,
    headaches = mh_headaches_test,
    mtbi_count = mh_mtbi_count_test,
    wmndf = dm_wmndf_qc_test,
    gord_cor = rm_gord_cor_qc_test,
    gord_var = rm_gord_var_qc_test,
    subc_cor = rm_subc_cor_qc_test,
    subc_var = rm_subc_var_qc_test,
    cort_sa = sm_cort_sa_qc_test,
    cort_t = sm_cort_t_qc_test,
    subc_v = sm_subc_v_qc_test,
    loneliness = p_loneliness_test,
    screen_time = p_screen_time_test,
    family_function = p_family_function_test,
    sports = p_sports_test,
    prosocial = p_prosocial_test,
    parent_psych = p_parent_psych_test,
    exercise = p_exercise_test)

list.save(data_list_test, proc_path("data_list_test.rdata", date = TRUE))


# Full data list
data_list_full <- generate_data_list(
    mtbi_loc = as_mtbi_loc_full,
    mtbi_mechanism = as_mtbi_mechanism_full,
    mtbi_mem_daze = as_mtbi_mem_daze_full,
    income = d_income_full,
    interview_age = d_interview_age_full,
    mtbi_age = d_mtbi_age_full,
    pubertal_status = d_pubertal_status_full,
    race = d_race_full,
    sex = d_sex_full,
    headaches = mh_headaches_full,
    mtbi_count = mh_mtbi_count_full,
    wmndf = dm_wmndf_qc_full,
    gord_cor = rm_gord_cor_qc_full,
    gord_var = rm_gord_var_qc_full,
    subc_cor = rm_subc_cor_qc_full,
    subc_var = rm_subc_var_qc_full,
    cort_sa = sm_cort_sa_qc_full,
    cort_t = sm_cort_t_qc_full,
    subc_v = sm_subc_v_qc_full,
    loneliness = p_loneliness_full,
    screen_time = p_screen_time_full,
    family_function = p_family_function_full,
    sports = p_sports_full,
    prosocial = p_prosocial_full,
    parent_psych = p_parent_psych_full,
    exercise = p_exercise_full)

list.save(data_list_full, proc_path("data_list_full.rdata", date = TRUE))



# Training CBCL list
cbcl_list_train <- list(
    cbcl_nausea_train,
    cbcl_vomiting_train,
    cbcl_dizzy_train,
    cbcl_overtired_train,
    cbcl_sleeping_more_train,
    cbcl_sleeping_less_train,
    cbcl_depress_train,
    cbcl_anxiety_train,
    cbcl_attention_train,
    cbcl_aggressive_train)

list.save(cbcl_list_train, proc_path("cbcl_list_train.rdata", date = TRUE))


cbcl_list_full <- list(
    cbcl_nausea_full,
    cbcl_vomiting_full,
    cbcl_dizzy_full,
    cbcl_overtired_full,
    cbcl_sleeping_more_full,
    cbcl_sleeping_less_full,
    cbcl_depress_full,
    cbcl_anxiety_full,
    cbcl_attention_full,
    cbcl_aggressive_full)

list.save(cbcl_list_full, proc_path("cbcl_list_full.rdata", date = TRUE))


```

