# Extract and transform

## Subjects

All information required for identifying children at a chronic stage following mTBI as of baseline data collection is available in the `abcd_otbi01.txt` file.
To identify subjects at a chronic stage post-mTBI, two intermediate pieces of information must be calculated from the original dataset:

* identifying which head injuries were mTBIs
* identifying the time since the most recent mTBI

The structure of the Ohio State TBI screen as used for ABCD data collection was not completely compatible with the most commonly used definition of mTBI @WYA25C6X#Blennow_Etal_2016, which requires at least one of the following:

* Any period of loss of consciousness
* Any loss of memory
* Any alteration in mental state
* Focal neurological deficits

but none of the following:

* LOC over 30 minutes
* A Glasgow Coma Scale score below 13
* Post-traumatic amnesia (PTA) greater than 24 hours

A few aspects of the data collection process in the ABCD study precluded the usage of this definition:

* No information was collected regarding the GCS
* Feeling dazed and PTA were combined into a single variable, making it unclear which combination of symptoms was present
* No information was collected regarding the duration of feeling dazed or experiencing PTA

Consequently, I defined mTBI as any injury that resulted in **either**:

1. LOC for less than 30 minutes (including 0 minutes) **AND** any duration of memory loss / feeling dazed
2. LOC for less than 30 minutes but greater than 0 minutes
 
The fixed nature of the questionnaire also meant that some information about multiple mTBIs sustained in the same way or about a very large number of mTBIs throughout a child's life could have been lost (see the previous section on identifying children with a history of mTBI).
For my analyses, I assume these edge cases are not common enough to meaningfully change any obtained conclusions.


```{r eval = TRUE}
library(ggplot2)
library(scabcd)
library(readr)
library(dplyr)
library(here)
library(knitr)


# Import baseline TBI dataset
tbi <- read_delim(here("data/abcd/4.0/trauma/abcd_otbi01.txt"))

# Remove data dictionary
tbi_no_dd <- tbi[-1, ]

# Give the dataset meaningful column names (e.g., tbi_5 -> blast_inj)
tbi_renamed <- rename_tbi(tbi_no_dd)

# Add a series of columns required to identify latest mTBI details
tbi_detailed <- tbi_renamed |>
    identify_all_tbi() |> # did subject have an mTBI / mod+ injury?
    identify_mtbi() |> # which injury types were mild?
    identify_mtbi_times() # time since / age at each / latest mTBI

# Identify baseline mtbi subjects at chronic stage post-mTBI (> 3 months)
mtbi_subjects <- get_mtbi_subjects(tbi_detailed, min_latest_mtbi_mpi = 3)
```


```{r eval = FALSE}
data_path <- "data/abcd/processed/prashanth/data/"
write_csv(mtbi_subjects, paste0(data_path, "mtbi_subjects.csv"))
```


A few types of injuries were handled differently from the rest in the above code.
For the `other_loc` injury type, the questionnaire asked for a total number of injuries with LOC as well as a total number of injuries with LOC above 30 minutes.
If their difference was above 0, they were labelled as having had an mTBI.
For the `other_multi` and `other_other_multi` injury types, insufficient information was provided to determine the severity of the associated injuries.

For my analyses, I consider 3 months to be the threshold at which an mTBI patient enters a chronic stage post-injury.


## Input variables

### Acute symptoms

The acute symptom data is found within the TBI dataset.
We are interesed in the following acute symptoms:

* mechanism of injury
* age
* LOC information
* Feeling dazed or having memory loss

A few more intermediate columns need to be added to isolate these variables for the most recent mTBIs of the subjects.

```{r eval = TRUE}
# Subset to just mTBI subjects to be included in analyses
mtbi_df <- inner_join(mtbi_subjects, tbi_detailed, by = "subjectkey")

# Additional columns to aid in extracting acute symptoms
mtbi_detailed <- mtbi_df |>
    identify_latest_mtbi_mechanism() |> # mechanism of latest mTBI
    identify_num_mtbi() |> # number of mTBIs sustained
    identify_latest_mtbi_loc() |> # LOC information for latest mTBI
    identify_latest_mtbi_mem_daze() # mem/daze information for latest mTBI

acute_symptoms <- get_acute_symptoms(mtbi_detailed)
```

```{r eval = FALSE}
write_csv(acute_symptoms, paste0(data_path, "acute_symptoms.csv"))
```


### Demographics

```{r}
# Pubertal status
parent_pubertal_df <-
    read_delim("data/abcd/4.0/med-history/abcd_ssphp01.txt") |>
    remove_dd() |>
    filter_baseline() |>
    filter_subjects(mtbi_subjects)

youth_pubertal_df <-
    read_delim("data/abcd/4.0/med-history/abcd_ssphy01.txt") |>
    remove_dd() |>
    filter_baseline() |>
    filter_subjects(mtbi_subjects)

puberty_df <- get_pubertal_status(youth_pubertal_df, parent_pubertal_df)


# Age
age_df <- youth_pubertal_df |> select("subjectkey", "interview_age")


# Sex
sex_df <- youth_pubertal_df |> select("subjectkey", "sex")

# Parent demographics (income, race)
parent_demographics <-
    read_delim("data/abcd/4.0/demographics/pdem02.txt") |>
    remove_dd() |>
    filter_baseline() |>
    filter_subjects(mtbi_subjects)

# Income
income_df <- get_income(parent_demographics)


# Race
race_df <- get_race(parent_demographics)


# Generate main demographic df
demographic_df <- generate_demographic(
    puberty_df,
    age_df,
    sex_df,
    income_df,
    race_df)
```

Subset and export the demographic input variables:

```{r eval = FALSE}
write_csv(demographic_df, paste0(data_path, "demographics.csv"))
```

### Medical history

```{r eval = TRUE}

medical_df <-
    read_delim("data/abcd/4.0/med-history/abcd_mx01.txt") |>
    remove_dd() |>
    filter_baseline() |>
    filter_subjects(mtbi_subjects)

# Medical history
med_history_df <- get_med_history(medical_df, mtbi_detailed)
```

Subset and export the medical history variables:

```{r eval = FALSE}
write_csv(med_history_df, paste0(data_path, "med_history.csv"))
```

### Neuroimaging

#### Structural MRI

The sMRI variables of interest include subcortical volumes, and cortical thicknesses, and cortical surface areas.


```{r eval = TRUE}
# Subcortical volumes
subc_v_df <- get_subc_v("data/abcd/4.0/evaluated-data/abcd_smrip10201.txt",
                        mtbi_subjects)

# Cortical thickness
cort_t_df <- get_cort_t("data/abcd/4.0/evaluated-data/abcd_mrisdp10201.txt",
                        mtbi_subjects_df)

# Cortical volumes
cort_sa_df <- get_cort_sa("data/abcd/4.0/evaluated-data/abcd_mrisdp10201.txt",
                        mtbi_subjects)
```


#### Diffusion MRI

We are interested in the neurite density measures of white matter regions in the brain.
Previously, these measures were found in variables containing the string "rsindwm_cdk" within the file `mri_rsi_p102.txt`.
A change anounced in the ABCD 4.0 MRI release notes indicates that neurite density is now referred to as "restricted normalized directional" and that the relevant white matter variables contain the string "rsirndwm" within the file `abcd_drsip201.txt`.

```{r}
# White matter neurite densities
wmnd_df <- get_wmnd("data/abcd/4.0/evaluated-data/abcd_drsip201.txt",
                    mtbi_subjects)
```


#### Resting-state functional MRI

We are interested in the following rs-fMRI measures:

- Gordon network (cortical) correlations 
- Subcortical correlations
- Gordon and subcortical temporal variances

```{r}

# CONTINUE FROM HERE!
# Network correlations (cortical parcellations)
gord_cor <- get_gord_cor("", mtbi_subjects)

# Network correlations - subcortical parcellations
subc_cor <- get_subc_cor("", mtbi_subjects)

# Temporal variances
temp_var <-
    read_delim(paste0(input_path, "rsfmri-temp-var/abcd_mrirstv02.txt"),
        col_select = "subjectkey" |
                     "eventname" |
                     contains("rsfmri_var_cortgordon_") |
                     contains("rsfmri_var_scs_"))[-1, ]

# Temporal variances - cortical parcellations
gord_temp_var <- temp_var |>
    select(subjectkey,
           eventname,
           contains("rsfmri_var_cortgordon"))

# Temporal variances - subcortical parcellations
subc_temp_var <- temp_var |>
    select(subjectkey,
           eventname,
           contains("rsfmri_var_scs_"))

```


Some visualizations of the extracted data:

```{r eval = TRUE}
# Breakdown of how many kids had each number of mTBIs
table(mtbi_detailed$mtbi_count)

# Plot of the times since each child had their latest mTBI
scabcd_hist(mtbi_detailed,
            title = "Histogram of times since latest mTBI",
            xval = "latest_mtbi_mpi",
            xlabel = "Time since last mTBI")
```

```{r eval = FALSE, echo = FALSE}
# Export the figure
scabcd_ggsave(path = "data/abcd/processed/prashanth/figures-and-tables/",
              plotname = "time_since_latest_mtbi_full.png")
```

```{r eval = TRUE}
scabcd_hist(df = puberty_df,
            xval = "pubertal_status",
            xlabel = "Pubertal status",
            title = "Distribution of pubertal status reports")
```

```{r eval = FALSE, echo = FALSE}
# Export the figure
scabcd_ggsave(path = "data/abcd/processed/prashanth/figures-and-tables/",
              plotname = "puberty_distributions.png")
```

```{r eval = TRUE}
scabcd_hist(income_df,
            xval = "household_income",
            title = "Household incomes of mTBI subjects",
            xlabel = "Income tier (1 = 0-50k, 2 = 50-100k, 3 = 100k+)")
```

```{r eval = FALSE, echo = FALSE}
# Export the figure
scabcd_ggsave(path = "data/abcd/processed/prashanth/figures-and-tables/",
              plotname = "income_distributions.png")
```

```{r}
# Distribution of subjects by race
count(race_df, race_df$"race")
```

