# Extract and transform

## Subjects

All information required for identifying children at a chronic stage following mTBI as of baseline data collection is available in the `abcd_otbi01.txt` file.
To identify subjects at a chronic stage post-mTBI, two intermediate pieces of information must be calculated from the original dataset:

* identifying which head injuries were mTBIs
* identifying the time since the most recent mTBI

The structure of the Ohio State TBI screen as used for ABCD data collection was not completely compatible with the most commonly used definition of mTBI @WYA25C6X#Blennow_Etal_2016, which requires at least one of the following:

* Any period of loss of consciousness
* Any loss of memory
* Any alteration in mental state
* Focal neurological deficits

but none of the following:

* LOC over 30 minutes
* A Glasgow Coma Scale score below 13
* Post-traumatic amnesia (PTA) greater than 24 hours

A few aspects of the data collection process in the ABCD study precluded the usage of this definition:

* No information was collected regarding the GCS
* Feeling dazed and PTA were combined into a single variable, making it unclear which combination of symptoms was present
* No information was collected regarding the duration of feeling dazed or experiencing PTA

Consequently, I defined mTBI as any injury that resulted in **either**:

1. LOC for less than 30 minutes (including 0 minutes) **AND** any duration of memory loss / feeling dazed
2. LOC for less than 30 minutes but greater than 0 minutes
 
The fixed nature of the questionnaire also meant that some information about multiple mTBIs sustained in the same way or about a very large number of mTBIs throughout a child's life could have been lost (see the previous section on identifying children with a history of mTBI).
For my analyses, I assume these edge cases are not common enough to meaningfully change any obtained conclusions.


```{r eval = TRUE}
library(ggplot2)
library(scabcd)
library(readr)
library(dplyr)
library(here)
library(knitr)

# Location of processed data
input_path <- "data/abcd/processed/prashanth/data/inputs/"
subject_path <- "data/abcd/processed/prashanth/data/subjects/"

# Import baseline TBI dataset
otbi01 <- read_delim(here("data/abcd/4.0/trauma/abcd_otbi01.txt"))

# Identify baseline mtbi subjects at chronic stage post-mTBI (> 3 months)
mtbi_subjects <- get_mtbi_subjects(otbi01, min_latest_mtbi_mpi = 3)
```


```{r eval = FALSE}
write_csv(mtbi_subjects, paste0(subject_path, "mtbi_subjects.csv"))
```


A few types of injuries were handled differently from the rest in the above code.
For the `other_loc` injury type, the questionnaire asked for a total number of injuries with LOC as well as a total number of injuries with LOC above 30 minutes.
If their difference was above 0, they were labelled as having had an mTBI.
For the `other_multi` and `other_other_multi` injury types, insufficient information was provided to determine the severity of the associated injuries.

For my analyses, I consider 3 months to be the threshold at which an mTBI patient enters a chronic stage post-injury.


## Acute symptoms

The acute symptom data is found within the TBI dataset.
We are interesed in the following acute symptoms:

* mechanism of injury
* age
* LOC information
* Feeling dazed or having memory loss

A few more intermediate columns need to be added to isolate these variables for the most recent mTBIs of the subjects.

```{r eval = TRUE}
as_mtbi_mem_daze <- get_mtbi_mem_daze(otbi01, mtbi_subjects)
as_mtbi_mechanism <- get_mtbi_mechanism(otbi01, mtbi_subjects)
as_mtbi_loc <- get_mtbi_loc(otbi01, mtbi_subjects)
as_mtbi_age <- get_mtbi_age(otbi01, mtbi_subjects)
```

```{r eval = FALSE}
write_csv(as_mtbi_mem_daze, paste0(input_path, "as_mtbi_mem_daze.csv"))
write_csv(as_mtbi_mechanism, paste0(input_path, "as_mtbi_mechanism.csv"))
write_csv(as_mtbi_loc, paste0(input_path, "as_mtbi_loc.csv"))
write_csv(as_mtbi_age, paste0(input_path, "as_mtbi_age.csv"))
```


## Demographics

```{r}
# Demographic dataframes
ssphp01 <- read_delim(here("data/abcd/4.0/med-history/abcd_ssphp01.txt"))
ssphy01 <- read_delim(here("data/abcd/4.0/med-history/abcd_ssphy01.txt"))

pdem02 <- read_delim(here("data/abcd/4.0/demographics/pdem02.txt"))

# Pubertal status
d_pubertal_status <- get_pubertal_status(ssphp01, ssphy01, mtbi_subjects)

# Age on interview
d_interview_age <- get_interview_age(otbi01, mtbi_subjects)

# Age on injury
d_mtbi_age <- get_mtbi_age(otbi01, mtbi_subjects)

# Sex
d_sex <- get_sex(otbi01, mtbi_subjects)

# Household income
d_income <- get_income(pdem02, mtbi_subjects)
```

Race/ethnicity is a bit confusing to deal with.
A huge fraction of subjects identify with multiple categories.
While that is no issue for constructing similarity matrices, it is an issue for comparing clusters by race/ethnicity post-subtyping.
Different publications have handled this differently.
I am currently categorizing all subjects as either white, black, or 'mixed/other'.
The rationale for this decision is below:


```{r}
full_race_df <- abcd_import(pdem02, mtbi_subjects) |>
    dplyr::rename("white" = "demo_race_a_p___10",
           "black" = "demo_race_a_p___11",
           "native_american" = "demo_race_a_p___12",
           "native_alaskan" = "demo_race_a_p___13",
           "native_hawaiian" = "demo_race_a_p___14",
           "guamanian" = "demo_race_a_p___15",
           "samoan" = "demo_race_a_p___16",
           "other_pacific_islander" = "demo_race_a_p___17",
           "asian" = "demo_race_a_p___18",
           "chinese" = "demo_race_a_p___19",
           "filipino" = "demo_race_a_p___20",
           "japanese" = "demo_race_a_p___21",
           "korean" = "demo_race_a_p___22",
           "vietnamese" = "demo_race_a_p___23",
           "other_asian" = "demo_race_a_p___24",
           "other" = "demo_race_a_p___25",
           "refuse_to_answer" = "demo_race_a_p___77",
           "dont_know" = "demo_race_a_p___99",
           "hispanic" = "demo_ethn_v2") |>
    dplyr::select("subjectkey",
                  "white":"hispanic",
                  -"demo_race_notes_v2") |>
    dplyr::mutate(
        dplyr::across(
            "white":"hispanic", as.numeric))
    full_race_df <- full_race_df |>
        dplyr::mutate(hispanic =
            dplyr::case_when(full_race_df$"hispanic" == 1 ~ 1, TRUE ~ 0))

colSums(full_race_df |> select(-"subjectkey"))
```

Several categories have less than 10 subjects in them(native alaskan, native hawaiian, guamanian, samoan, other pacific islander, asian, chinese, filipino, japanese, korean, vietnamese, other asian).

In the next chunk, I pool some of them together:

```{r}
full_race_df2 <- full_race_df |>
    dplyr::mutate(asian_other_pi = pmax(
        full_race_df$"asian",
        full_race_df$"filipino",
        full_race_df$"korean",
        full_race_df$"other_asian",
        full_race_df$"chinese",
        full_race_df$"japanese",
        full_race_df$"vietnamese",
        full_race_df$"other_pacific_islander",
        full_race_df$"samoan",
        full_race_df$"guamanian",
        full_race_df$"native_hawaiian",
        full_race_df$"native_alaskan"),
    na = pmax(
        full_race_df$"dont_know",
        full_race_df$"refuse_to_answer")) |>
    dplyr::select("subjectkey",
           "asian_other_pi",
           "native_american",
           "other",
           "na",
           "white",
           "black",
           "hispanic")

colSums(full_race_df2 |> select(-"subjectkey"))
```

These seems like a sensible breakdown, but the main issue is that many subjects belong to more than one of these categories.

```{r}
# How many subjects belong to more than one race category?
sum(rowSums(full_race_df2 |> select(-"subjectkey")) > 1)
```

Quite a large number of subjects are mixed.
In the next chunk, I assign those subjects to their own 'mixed' category and remove them from the individual race categories they previously belonged to.

```{r}
full_race_df3 <- full_race_df2 |>
    dplyr::mutate(mixed = dplyr::case_when(
        full_race_df2$"white" +
        full_race_df2$"black" +
        full_race_df2$"asian_other_pi" +
        full_race_df2$"native_american" +
        full_race_df2$"other" +
        full_race_df2$"hispanic" > 1 ~ 1,
        TRUE ~ 0
        ))
# Remove original race category for those who are mixed
full_race_df4 <- full_race_df3 |>
    dplyr::mutate(
        black = dplyr::case_when(
            full_race_df3$"black" == 1 &
                full_race_df3$"mixed" == 0 ~ 1,
            TRUE ~ 0),
        white = dplyr::case_when(
            full_race_df3$"white" == 1 &
                full_race_df3$"mixed" == 0 ~ 1,
            TRUE ~ 0),
        asian_other_pi = dplyr::case_when(
            full_race_df3$"asian_other_pi" == 1 &
                full_race_df3$"mixed" == 0 ~ 1,
            TRUE ~ 0),
        hispanic = dplyr::case_when(
            full_race_df3$"hispanic" == 1 &
                full_race_df3$"mixed" == 0 ~ 1,
            TRUE ~ 0),
        native_american = dplyr::case_when(
            full_race_df3$"native_american" == 1 &
                full_race_df3$"mixed" == 0 ~ 1,
            TRUE ~ 0))

colSums(full_race_df4 |> select(-"subjectkey"))
```

Now the only categories with more than 5 people are other, white, black, and mixed.

Moving forward, I see two sensible options:

1. Assign one race category per subject, where that category is either white, black, or other/mixed
2. Allow multiple race categories per subject, where those categories are white, black, hispanic, asian/other pacific islander, native american, and other

Easier post-hoc analyses are provided by option 1, but more accurate similarity matrices will be constructed with option 2.
I unfortunately can't think of any concrete reason as to why one of these two options will give better SNF results, so switching between these two types will need to be one of the free parameters in my upcoming SNF iterations.
The function `get_race()` shown below is written to allow the user to specify which format they want their dataframe in:

1. Option #1 dummied ('condensed_dummied'): three columns of white, black, mixed/other
2. Option #1 undummied ('condensed_undummied'): one race column with categories white, black, mixed/other
2. Option #2 dummied ('expanded_dummied'): multiple race columns including asian/other pacific islander, native american, other, white, black, hispanic


# Race
```{r}

# CONTINUE FROM HERE!

# HUGE TO DO: check the PNC associations on a per-cluster basis
# Big to-do: ensure that all the 'get' input functions remove any rows with NA
# Remove the old get_race function
# Move this race demonstration into the appendix
a <- get_race2(pdem02, mtbi_subjects, "condensed_undummied")

unique(na.omit(a$race))



d_race <- get_race(pdem02, mtbi_subjects)

d_race2 <- get_race2(pdem02, mtbi_subjects)

d_race2

count(d_race, d_race$"race")

colnames(pdem02)

```

Subset and export the demographic input variables:

```{r eval = FALSE}
write_csv(d_pubertal_status, paste0(input_path, "d_pubertal_status.csv"))
write_csv(d_interview_age, paste0(input_path, "d_interview_age.csv"))
write_csv(d_mtbi_age, paste0(input_path, "d_mtbi_age.csv"))
write_csv(d_sex, paste0(input_path, "d_sex.csv"))
write_csv(d_income, paste0(input_path, "d_income.csv"))
write_csv(d_race, paste0(input_path, "d_race.csv"))
```

## Medical history

```{r eval = TRUE}
mx01 <- (here("data/abcd/4.0/med-history/abcd_mx01.txt"))

# History of headaches
mh_headaches <- get_headaches(mx01, mtbi_subjects)

# Number of previous mTBIs
mh_mtbi_count <- get_mtbi_count(otbi01, mtbi_subjects)
```

Subset and export the medical history variables:

```{r eval = FALSE}
write_csv(mh_headaches, paste0(input_path, "mh_headaches.csv"))
write_csv(mh_mtbi_count, paste0(input_path, "mh_mtbi_count.csv"))
```

## Neuroimaging

### Structural MRI

The sMRI variables of interest include subcortical volumes, and cortical thicknesses, and cortical surface areas.


```{r eval = TRUE}
# SMRI dataframes
smrip10201 <-
    read_delim(here("data/abcd/4.0/evaluated-data/abcd_smrip10201.txt"))
mrisdp10201 <-
    read_delim(here("data/abcd/4.0/evaluated-data/abcd_mrisdp10201.txt"))

# Subcortical volumes
sm_subc_v <- get_subc_v(smrip10201, mtbi_subjects)

# Cortical thickness
sm_cort_t <- get_cort_t(mrisdp10201, mtbi_subjects)

# Cortical volumes
sm_cort_sa <- get_cort_sa(mrisdp10201, mtbi_subjects)
```

```{r eval = FALSE}
write_csv(sm_subc_v, paste0(input_path, "sm_subc_v.csv"))
write_csv(sm_cort_t, paste0(input_path, "sm_cort_t.csv"))
write_csv(sm_cort_sa, paste0(input_path, "sm_cort_sa.csv"))
```

### Diffusion MRI

We are interested in the neurite density measures of white matter regions in the brain.
Previously, these measures were found in variables containing the string "rsindwm_cdk" within the file `mri_rsi_p102.txt`.
A change anounced in the ABCD 4.0 MRI release notes indicates that neurite density is now referred to as "restricted normalized directional" and that the relevant white matter variables contain the string "rsirndwm" within the file `abcd_drsip201.txt`.

```{r}
# DMRI dataframe
drsip201 <-
    read_delim(here("data/abcd/4.0/evaluated-data/abcd_drsip201.txt"))

# White matter neurite densities
dm_wmndf <- get_wmnd(drsip201, mtbi_subjects)
```

```{r eval = FALSE}
write_csv(dm_wmndf, paste0(input_path, "dm_wmndf.csv"))
```


### Resting-state functional MRI

We are interested in the following rs-fMRI measures:

- Gordon network (cortical) correlations 
- Subcortical correlations
- Gordon and subcortical temporal variances

```{r}
betnet02 <-
    read_delim(here(paste0("data/abcd/2.0/tabular-MRI/rsfMRI-data/",
                           "rsfmri-gord-cor/abcd_betnet02.txt")))
mrirscor02 <-
    read_delim(here(paste0("data/abcd/2.0/tabular-MRI/rsfMRI-data/",
                           "rsfmri-subc-cor/mrirscor02.txt")))
mrirstv02 <-
    read_delim(here(paste0("data/abcd/2.0/tabular-MRI/rsfMRI-data/",
                           "rsfmri-temp-var/abcd_mrirstv02.txt")))


# Cortical parcellation network correlations
rm_gord_cor <- get_gord_cor(betnet02, mtbi_subjects)

# Subcortical parcellation network correlations
rm_subc_cor <- get_subc_cor(mrirscor02, mtbi_subjects)

# Temporal variances - cortical parcellations
rm_gord_var <- get_gord_var(mrirstv02, mtbi_subjects)

# Subcortical temporal variances
rm_subc_var <- get_subc_var(mrirstv02, mtbi_subjects)
```

```{r eval = FALSE}
write_csv(rm_gord_cor, paste0(input_path, "rm_gord_cor.csv"))
write_csv(rm_subc_cor, paste0(input_path, "rm_subc_cor.csv"))
write_csv(rm_subc_var, paste0(input_path, "rm_subc_var"))
write_csv(rm_gord_var, paste0(input_path, "rm_gord_var.csv"))
```


## Psychosocial resilience




Some visualizations of the extracted data:

```{r eval = TRUE}
# Breakdown of how many kids had each number of mTBIs
table(mh_mtbi_count$mtbi_count)


# Plot of the times since each child had their latest mTBI
mtbi_detailed <- detail_mtbi(otbi01, mtbi_subjects)
scabcd_hist(mtbi_detailed,
            title = "Histogram of times since latest mTBI",
            xval = "latest_mtbi_mpi",
            xlabel = "Time since last mTBI")
```

```{r eval = FALSE, echo = FALSE}
# Export the figure
scabcd_ggsave(path = "data/abcd/processed/prashanth/figures-and-tables/",
              plotname = "time_since_latest_mtbi_full.png")
```

```{r eval = TRUE}
scabcd_hist(df = d_pubertal_status,
            xval = "pubertal_status",
            xlabel = "Pubertal status",
            title = "Distribution of pubertal status reports")
```

```{r eval = FALSE, echo = FALSE}
# Export the figure
scabcd_ggsave(path = "data/abcd/processed/prashanth/figures-and-tables/",
              plotname = "puberty_distributions.png")
```

```{r eval = TRUE}
scabcd_hist(d_income,
            xval = "household_income",
            title = "Household incomes of mTBI subjects",
            xlabel = "Income tier (1 = 0-50k, 2 = 50-100k, 3 = 100k+)")
```

```{r eval = FALSE, echo = FALSE}
# Export the figure
scabcd_ggsave(path = "data/abcd/processed/prashanth/figures-and-tables/",
              plotname = "income_distributions.png")
```

```{r}
# Distribution of subjects by race
count(d_race, d_race$"race")
```

