# Imputation, QCing, and CBCL thresholding

This script is used to:

1. Impute missing data for non-neuroimaging input variables
2. Remove neuroimaging data for participants who do not meet ABCD's QC
3. Threshold CBCL behaviour measures (raw scores into normal (0), borderline (1), and clinical (2))


## Loading in data

```{r}
library(mice)
library(dplyr)
library(abcdutils)
library(readr)
library(purrr)
library(here)


# Place the location of your input data here
input_data <- path_maker(here(paste0("data/abcd/inputs")))
raw_data <- path_maker(here(paste0("data/abcd/raw")))


# Inputs
as_mtbi_loc <- read_csv(input_data("as_mtbi_loc.csv"))
as_mtbi_mechanism <- read_csv(input_data("as_mtbi_mechanism.csv"))
as_mtbi_mem_daze <- read_csv(input_data("as_mtbi_mem_daze.csv"))
d_income <- read_csv(input_data("d_income.csv"))
d_interview_age <- read_csv(input_data("d_interview_age.csv"))
d_mtbi_age <- read_csv(input_data("d_mtbi_age.csv"))
d_pubertal_status <- read_csv(input_data("d_pubertal_status.csv"))
d_race <- read_csv(input_data("d_race_cu.csv"))
d_sex <- read_csv(input_data("d_sex.csv"))
mh_headaches <- read_csv(input_data("mh_headaches.csv"))
mh_mtbi_count <- read_csv(input_data("mh_mtbi_count.csv"))

dm_wmndf <- read_csv(input_data("dm_wmndf.csv")) # Just peri-cortical
dm_all_wmnd_0 <- read_csv(input_data("2023_03_27_dm_all_wmnd_0.csv")) # All WM

rm_gord_cor <- read_csv(input_data("rm_gord_cor.csv"))
rm_gord_var <- read_csv(input_data("rm_gord_var.csv"))
rm_subc_cor <- read_csv(input_data("rm_subc_cor.csv"))
rm_subc_var <- read_csv(input_data("rm_subc_var.csv"))
sm_cort_sa <- read_csv(input_data("sm_cort_sa.csv"))
sm_cort_t <- read_csv(input_data("sm_cort_t.csv"))
sm_subc_v <- read_csv(input_data("sm_subc_v.csv"))
p_loneliness <- read_csv(input_data("p_loneliness.csv"))
p_screen_time <- read_csv(input_data("p_screen_time.csv"))
p_family_function <- read_csv(input_data("p_family_function.csv"))
p_sports <- read_csv(input_data("p_sports.csv"))
p_prosocial <- read_csv(input_data("p_prosocial.csv"))
p_parent_psych <- read_csv(input_data("p_parent_psych.csv"))
p_exercise <- read_csv(input_data("p_exercise.csv"))
cbcl_headaches <- read_csv(input_data("cbcl_headaches.csv"))
cbcl_nausea <- read_csv(input_data("cbcl_nausea.csv"))
cbcl_vomiting <- read_csv(input_data("cbcl_vomiting.csv"))
cbcl_dizzy <- read_csv(input_data("cbcl_dizzy.csv"))
cbcl_overtired <- read_csv(input_data("cbcl_overtired.csv"))
cbcl_sleeping_more <- read_csv(input_data("cbcl_sleeping_more.csv"))
cbcl_sleeping_less <- read_csv(input_data("cbcl_sleeping_less.csv"))
cbcl_depress_r <- read_csv(input_data("cbcl_depress_r.csv"))
cbcl_anxiety_r <- read_csv(input_data("cbcl_anxiety_r.csv"))
cbcl_attention_r <- read_csv(input_data("cbcl_attention_r.csv"))
cbcl_aggressive_r <- read_csv(input_data("cbcl_aggressive_r.csv"))
sds_sleep <- read_csv(input_data("sds_sleep_df.csv"))
nihtbx_list_fc <- read_csv(input_data("nihtbx_list_fc.csv"))
nihtbx_pattern_fc <- read_csv(input_data("nihtbx_pattern_fc.csv"))
nihtbx_cardsort_fc <- read_csv(input_data("nihtbx_cardsort_fc.csv"))
```


## Neuroimaging quality control

```{r eval = FALSE}
mriqcrp10301 <- read_delim(raw_data("mriqcrp10301.txt"))


# Obtaining the QC'd subjects with complete neuroimaging data
rm_gord_cor_qc <- qc_rsfmri(rm_gord_cor, mriqcrp10301, t = 0, no_na = TRUE)
rm_gord_var_qc <- qc_rsfmri(rm_gord_var, mriqcrp10301, t = 0, no_na = TRUE)
rm_subc_cor_qc <- qc_rsfmri(rm_subc_cor, mriqcrp10301, t = 0, no_na = TRUE)
rm_subc_var_qc <- qc_rsfmri(rm_subc_var, mriqcrp10301, t = 0, no_na = TRUE)
dm_wmndf_qc <- qc_dmri(dm_wmndf, mriqcrp10301, t = 0, no_na = TRUE)
dm_all_wmnd_0_qc <- qc_dmri(dm_all_wmnd_0, mriqcrp10301, t = 0, no_na = TRUE)
sm_cort_sa_qc <- qc_smri(sm_cort_sa, mriqcrp10301, t = 0, no_na = TRUE)
sm_cort_t_qc <- qc_smri(sm_cort_t, mriqcrp10301, t = 0, no_na = TRUE)
sm_subc_v_qc <- qc_smri(sm_subc_v, mriqcrp10301, t = 0, no_na = TRUE)
```

```{r eval = FALSE}
write_csv(rm_gord_cor_qc, input_data("rm_gord_cor_qc.csv"))
write_csv(rm_gord_var_qc, input_data("rm_gord_var_qc.csv"))
write_csv(rm_subc_cor_qc, input_data("rm_subc_cor_qc.csv"))
write_csv(rm_subc_var_qc, input_data("rm_subc_var_qc.csv"))
write_csv(dm_wmndf_qc, input_data("dm_wmndf_qc.csv"))
write_csv(dm_all_wmnd_0_qc, input_data("dm_all_wmnd_0_qc.csv", date = TRUE))
write_csv(sm_cort_sa_qc, input_data("sm_cort_sa_qc.csv"))
write_csv(sm_cort_t_qc, input_data("sm_cort_t_qc.csv"))
write_csv(sm_subc_v_qc, input_data("sm_subc_v_qc.csv"))
```


## Imputing missing data 

Here, I only impute the non-neuroimaging data.

Code is based on Eman's imputation script.
Thanks Eman!

While this choice was made largely for the sake of time, it was also partially because imputing neuroimaging data doesn't seem to be a common practice.


```{r eval = FALSE}
# put all data frames into a named list
df_list <- list(
    "loss of consciousness" = as_mtbi_loc,
    "mechanism of injury" = as_mtbi_mechanism,
    "memory loss / dazed" = as_mtbi_mem_daze,
    "income" = d_income,
    "interview_age" = d_interview_age,
    "mtbi_age" = d_mtbi_age,
    "pubertal_status" = d_pubertal_status,
    "race" = d_race,
    "sex" = d_sex,
    "headaches" = mh_headaches,
    "mtbi_count" = mh_mtbi_count,
    "wmndf" = dm_wmndf,
    "gord correlations" = rm_gord_cor,
    "gord variances" = rm_gord_var,
    "subc corrrelations" = rm_subc_cor,
    "subc variances" = rm_subc_var,
    "cortical surface area" = sm_cort_sa,
    "cortical thickness" = sm_cort_t,
    "subcortical volume" = sm_subc_v,
    "loneliness" = p_loneliness,
    "screen time" = p_screen_time,
    "family function" = p_family_function,
    "sports" = p_sports,
    "prosocial" = p_prosocial,
    "parent psych" = p_parent_psych,
    "exercise" = p_exercise,
    "cbcl headaches" = cbcl_headaches,
    "cbcl nausea" = cbcl_nausea,
    "cbcl vomiting" = cbcl_vomiting,
    "cbcl dizzy" = cbcl_dizzy,
    "cbcl overtired" = cbcl_overtired,
    "cbcl sleeping more" = cbcl_sleeping_more,
    "cbcl sleeping less" = cbcl_sleeping_less,
    "cbcl depress r" = cbcl_depress_r,
    "cbcl anxiety r" = cbcl_anxiety_r,
    "cbcl attention r" = cbcl_attention_r,
    "cbcl aggressive r" = cbcl_aggressive_r,
    "sds sleep" = sds_sleep,
    "nihtbx list fc" = nihtbx_list_fc,
    "nihtbx pattern fc" = nihtbx_pattern_fc,
    "nihtbx cardsort fc" = nihtbx_cardsort_fc)

vis_missing_by_df(df_list)

df_list_no_neuroimaging <- list(
    "loss of consciousness" = as_mtbi_loc,
    "mechanism of injury" = as_mtbi_mechanism,
    "memory loss / dazed" = as_mtbi_mem_daze,
    "income" = d_income,
    "interview_age" = d_interview_age,
    "mtbi_age" = d_mtbi_age,
    "pubertal_status" = d_pubertal_status,
    "race" = d_race,
    "sex" = d_sex,
    "headaches" = mh_headaches,
    "mtbi_count" = mh_mtbi_count,
    "loneliness" = p_loneliness,
    "screen time" = p_screen_time,
    "family function" = p_family_function,
    "sports" = p_sports,
    "prosocial" = p_prosocial,
    "parent psych" = p_parent_psych,
    "exercise" = p_exercise,
    "cbcl headaches" = cbcl_headaches,
    "cbcl nausea" = cbcl_nausea,
    "cbcl vomiting" = cbcl_vomiting,
    "cbcl dizzy" = cbcl_dizzy,
    "cbcl overtired" = cbcl_overtired,
    "cbcl sleeping more" = cbcl_sleeping_more,
    "cbcl sleeping less" = cbcl_sleeping_less,
    "cbcl depress r" = cbcl_depress_r,
    "cbcl anxiety r" = cbcl_anxiety_r,
    "cbcl attention r" = cbcl_attention_r,
    "cbcl aggressive r" = cbcl_aggressive_r,
    "sds sleep" = sds_sleep,
    "nihtbx list fc" = nihtbx_list_fc,
    "nihtbx pattern fc" = nihtbx_pattern_fc,
    "nihtbx cardsort fc" = nihtbx_cardsort_fc)


full_df <- df_list_no_neuroimaging |>
    purrr::reduce(dplyr::full_join, by = "subjectkey")
full_df$household_income <- as.factor(full_df$household_income)
full_df$race <- as.factor(full_df$race)

# m = 5 and maxit = 10 are default settings
imputed <- mice(full_df, m = 5, maxit = 10, seed = 42)

# View a summary of which variables were added by the imputation
imputed$imp

# Isolate the imputed data
imputed_non_imaging <- complete(imputed)

as_mtbi_loc_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "latest_mtbi_loc")
as_mtbi_mechanism_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "latest_mtbi_mechanism")
as_mtbi_mem_daze_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "latest_mtbi_mem_daze")
d_income_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "household_income")
d_interview_age_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "interview_age")
d_mtbi_age_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "latest_mtbi_age")
d_pubertal_status_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "pubertal_status")
d_race_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "race")
d_sex_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "M")
mh_headaches_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "headache")
mh_mtbi_count_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "mtbi_count")
p_loneliness_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "ss_friend":"os_close_friend")
p_screen_time_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", dplyr::contains("screentime"))
p_family_function_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "q1_fight":"q9_yell")
p_sports_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", dplyr::contains("activities"))
p_prosocial_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "q1":"q3")
p_parent_psych_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", dplyr::contains("asr_scr"))
p_exercise_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", dplyr::contains("physical_activity"))
cbcl_headaches_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "cbcl_headaches")
cbcl_nausea_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "cbcl_nausea")
cbcl_vomiting_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "cbcl_vomiting")
cbcl_dizzy_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "cbcl_dizzy")
cbcl_overtired_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "cbcl_overtired")
cbcl_sleeping_more_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "cbcl_sleeping_more")
cbcl_sleeping_less_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "cbcl_sleeping_less")
cbcl_depress_r_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "cbcl_depress_r")
cbcl_anxiety_r_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "cbcl_anxiety_r")
cbcl_attention_r_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "cbcl_attention_r")
cbcl_aggressive_r_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "cbcl_aggressive_r")
sds_sleep_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", dplyr::starts_with("sleep"))
nihtbx_list_fc_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "nihtbx_list_fc")
nihtbx_pattern_fc_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "nihtbx_pattern_fc")
nihtbx_cardsort_fc_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "nihtbx_cardsort_fc")

write_csv(as_mtbi_loc_imp, input_data("as_mtbi_loc_imp.csv"))
write_csv(as_mtbi_mechanism_imp, input_data("as_mtbi_mechanism_imp.csv"))
write_csv(as_mtbi_mem_daze_imp, input_data("as_mtbi_mem_daze_imp.csv"))
write_csv(d_income_imp, input_data("d_income_imp.csv"))
write_csv(d_interview_age_imp, input_data("d_interview_age_imp.csv"))
write_csv(d_mtbi_age_imp, input_data("d_mtbi_age_imp.csv"))
write_csv(d_pubertal_status_imp, input_data("d_pubertal_status_imp.csv"))
write_csv(d_race_imp, input_data("d_race_imp.csv"))
write_csv(d_sex_imp, input_data("d_sex_imp.csv"))
write_csv(mh_headaches_imp, input_data("mh_headaches_imp.csv"))
write_csv(mh_mtbi_count_imp, input_data("mh_mtbi_count_imp.csv"))
write_csv(p_loneliness_imp, input_data("p_loneliness_imp.csv"))
write_csv(p_screen_time_imp, input_data("p_screen_time_imp.csv"))
write_csv(p_family_function_imp, input_data("p_family_function_imp.csv"))
write_csv(p_sports_imp, input_data("p_sports_imp.csv"))
write_csv(p_prosocial_imp, input_data("p_prosocial_imp.csv"))
write_csv(p_parent_psych_imp, input_data("p_parent_psych_imp.csv"))
write_csv(p_exercise_imp, input_data("p_exercise_imp.csv"))
write_csv(cbcl_headaches_imp, input_data("cbcl_headaches_imp.csv"))
write_csv(cbcl_nausea_imp, input_data("cbcl_nausea_imp.csv"))
write_csv(cbcl_vomiting_imp, input_data("cbcl_vomiting_imp.csv"))
write_csv(cbcl_dizzy_imp, input_data("cbcl_dizzy_imp.csv"))
write_csv(cbcl_overtired_imp, input_data("cbcl_overtired_imp.csv"))
write_csv(cbcl_sleeping_more_imp, input_data("cbcl_sleeping_more_imp.csv"))
write_csv(cbcl_sleeping_less_imp, input_data("cbcl_sleeping_less_imp.csv"))
write_csv(cbcl_depress_r_imp, input_data("cbcl_depress_r_imp.csv"))
write_csv(cbcl_anxiety_r_imp, input_data("cbcl_anxiety_r_imp.csv"))
write_csv(cbcl_attention_r_imp, input_data("cbcl_attention_r_imp.csv"))
write_csv(cbcl_aggressive_r_imp, input_data("cbcl_aggressive_r_imp.csv"))
write_csv(sds_sleep_imp, input_data("sds_sleep_imp.csv"))
write_csv(nihtbx_list_fc_imp, input_data("nihtbx_list_fc_imp.csv"))
write_csv(nihtbx_pattern_fc_imp, input_data("nihtbx_pattern_fc_imp.csv"))
write_csv(nihtbx_cardsort_fc_imp, input_data("nihtbx_cardsort_fc_imp.csv"))
```

## Convert the raw CBCL scores into thresholded ones
```{r}
cbcl_depress_r_imp <- read_csv(input_data("cbcl_depress_r_imp.csv"))
cbcl_anxiety_r_imp <- read_csv(input_data("cbcl_anxiety_r_imp.csv"))
cbcl_attention_r_imp <- read_csv(input_data("cbcl_attention_r_imp.csv"))
cbcl_aggressive_r_imp <- read_csv(input_data("cbcl_aggressive_r_imp.csv"))

cbcl_depress_imp <- cbcl_raw_to_thresh(cbcl_depress_r_imp)
cbcl_anxiety_imp <- cbcl_raw_to_thresh(cbcl_anxiety_r_imp)
cbcl_attention_imp <- cbcl_raw_to_thresh(cbcl_attention_r_imp)
cbcl_aggressive_imp <- cbcl_raw_to_thresh(cbcl_aggressive_r_imp)

write_csv(cbcl_depress_imp, input_data("cbcl_depress_imp.csv"))
write_csv(cbcl_anxiety_imp, input_data("cbcl_anxiety_imp.csv"))
write_csv(cbcl_attention_imp, input_data("cbcl_attention_imp.csv"))
write_csv(cbcl_aggressive_imp, input_data("cbcl_aggressive_imp.csv"))
```
