# Imputation

Missing value imputation.

1. Load all the data and join into a single dataframe.

```{r}
library(mice)
library(dplyr)
library(abcdutils)
library(readr)
library(purrr)
library(here)

# Inputs
as_mtbi_loc <-
    read_csv(here("data/abcd/inputs/pre-imputation/as_mtbi_loc.csv"))
as_mtbi_mechanism <-
    read_csv(here("data/abcd/inputs/pre-imputation/as_mtbi_mechanism.csv"))
as_mtbi_mem_daze <-
    read_csv(here("data/abcd/inputs/pre-imputation/as_mtbi_mem_daze.csv"))
d_income <-
    read_csv(here("data/abcd/inputs/pre-imputation/d_income.csv"))
d_interview_age <-
    read_csv(here("data/abcd/inputs/pre-imputation/d_interview_age.csv"))
d_mtbi_age <-
    read_csv(here("data/abcd/inputs/pre-imputation/d_mtbi_age.csv"))
d_pubertal_status <-
    read_csv(here("data/abcd/inputs/pre-imputation/d_pubertal_status.csv"))
d_race <-
    read_csv(here("data/abcd/inputs/pre-imputation/d_race_cu.csv"))
d_sex <-
    read_csv(here("data/abcd/inputs/pre-imputation/d_sex.csv"))
mh_headaches <-
    read_csv(here("data/abcd/inputs/pre-imputation/mh_headaches.csv"))
mh_mtbi_count <-
    read_csv(here("data/abcd/inputs/pre-imputation/mh_mtbi_count.csv"))
dm_wmndf <-
    read_csv(here("data/abcd/inputs/pre-imputation/dm_wmndf.csv"))
rm_gord_cor <-
    read_csv(here("data/abcd/inputs/pre-imputation/rm_gord_cor.csv"))
rm_gord_var <-
    read_csv(here("data/abcd/inputs/pre-imputation/rm_gord_var.csv"))
rm_subc_cor <-
    read_csv(here("data/abcd/inputs/pre-imputation/rm_subc_cor.csv"))
rm_subc_var <-
    read_csv(here("data/abcd/inputs/pre-imputation/rm_subc_var.csv"))
sm_cort_sa <-
    read_csv(here("data/abcd/inputs/pre-imputation/sm_cort_sa.csv"))
sm_cort_t <-
    read_csv(here("data/abcd/inputs/pre-imputation/sm_cort_t.csv"))
sm_subc_v <-
    read_csv(here("data/abcd/inputs/pre-imputation/sm_subc_v.csv"))
p_loneliness <-
    read_csv(here("data/abcd/inputs/pre-imputation/p_loneliness.csv"))
p_screen_time <-
    read_csv(here("data/abcd/inputs/pre-imputation/p_screen_time.csv"))
p_family_function <-
    read_csv(here("data/abcd/inputs/pre-imputation/p_family_function.csv"))
p_sports <-
    read_csv(here("data/abcd/inputs/pre-imputation/p_sports.csv"))
p_prosocial <-
    read_csv(here("data/abcd/inputs/pre-imputation/p_prosocial.csv"))
p_parent_psych <-
    read_csv(here("data/abcd/inputs/pre-imputation/p_parent_psych.csv"))
p_exercise <-
    read_csv(here("data/abcd/inputs/pre-imputation/p_exercise.csv"))
# Outcomes
cbcl_headaches <-
    read_csv(here("data/abcd/outputs/pre-imputation/cbcl_headaches.csv"))
cbcl_nausea <-
    read_csv(here("data/abcd/outputs/pre-imputation/cbcl_nausea.csv"))
cbcl_vomiting <-
    read_csv(here("data/abcd/outputs/pre-imputation/cbcl_vomiting.csv"))
cbcl_dizzy <-
    read_csv(here("data/abcd/outputs/pre-imputation/cbcl_dizzy.csv"))
cbcl_overtired <-
    read_csv(here("data/abcd/outputs/pre-imputation/cbcl_overtired.csv"))
cbcl_sleeping_more <-
    read_csv(here("data/abcd/outputs/pre-imputation/cbcl_sleeping_more.csv"))
cbcl_sleeping_less <-
    read_csv(here("data/abcd/outputs/pre-imputation/cbcl_sleeping_less.csv"))
cbcl_depress_r <-
    read_csv(here("data/abcd/outputs/pre-imputation/cbcl_depress_r.csv"))
cbcl_anxiety_r <-
    read_csv(here("data/abcd/outputs/pre-imputation/cbcl_anxiety_r.csv"))
cbcl_attention_r <-
    read_csv(here("data/abcd/outputs/pre-imputation/cbcl_attention_r.csv"))
cbcl_aggressive_r <-
    read_csv(here("data/abcd/outputs/pre-imputation/cbcl_aggressive_r.csv"))
sds_sleep <-
    read_csv(here("data/abcd/outputs/pre-imputation/sds_sleep_df.csv"))
nihtbx_list_fc <-
    read_csv(here("data/abcd/outputs/pre-imputation/nihtbx_list_fc.csv"))
nihtbx_pattern_fc <-
    read_csv(here("data/abcd/outputs/pre-imputation/nihtbx_pattern_fc.csv"))
nihtbx_cardsort_fc <-
    read_csv(here("data/abcd/outputs/pre-imputation/nihtbx_cardsort_fc.csv"))
```


## Quality control

```{r eval = FALSE}

mriqcrp10301 <-
    read_delim(here("data/abcd/raw/mriqcrp10301.txt"))

# Obtaining the QC'd subjects with complete neuroimaging data
rm_gord_cor_qc <- qc_rsfmri(rm_gord_cor, mriqcrp10301, t = 0, no_na = TRUE)
rm_gord_var_qc <- qc_rsfmri(rm_gord_var, mriqcrp10301, t = 0, no_na = TRUE)
rm_subc_cor_qc <- qc_rsfmri(rm_subc_cor, mriqcrp10301, t = 0, no_na = TRUE)
rm_subc_var_qc <- qc_rsfmri(rm_subc_var, mriqcrp10301, t = 0, no_na = TRUE)
dm_wmndf_qc <- qc_dmri(dm_wmndf, mriqcrp10301, t = 0, no_na = TRUE)
sm_cort_sa_qc <- qc_smri(sm_cort_sa, mriqcrp10301, t = 0, no_na = TRUE)
sm_cort_t_qc <- qc_smri(sm_cort_t, mriqcrp10301, t = 0, no_na = TRUE)
sm_subc_v_qc <- qc_smri(sm_subc_v, mriqcrp10301, t = 0, no_na = TRUE)
```

```{r eval = FALSE}
write_csv(rm_gord_cor_qc,
    here("data/abcd/inputs/pre-imputation/rm_gord_cor_qc.csv"))
write_csv(rm_gord_var_qc,
    here("data/abcd/inputs/pre-imputation/rm_gord_var_qc.csv"))
write_csv(rm_subc_cor_qc,
    here("data/abcd/inputs/pre-imputation/rm_subc_cor_qc.csv"))
write_csv(rm_subc_var_qc,
    here("data/abcd/inputs/pre-imputation/rm_subc_var_qc.csv"))
write_csv(dm_wmndf_qc,
    here("data/abcd/inputs/pre-imputation/dm_wmndf_qc.csv"))
write_csv(sm_cort_sa_qc,
    here("data/abcd/inputs/pre-imputation/sm_cort_sa_qc.csv"))
write_csv(sm_cort_t_qc,
    here("data/abcd/inputs/pre-imputation/sm_cort_t_qc.csv"))
write_csv(sm_subc_v_qc,
    here("data/abcd/inputs/pre-imputation/sm_subc_v_qc.csv"))
```


## Missing data 

To-do: switch the neuroimaging vars to their QC form

```{r eval = FALSE}
# put all data frames into a named list
df_list <- list(
    "loss of consciousness" = as_mtbi_loc,
    "mechanism of injury" = as_mtbi_mechanism,
    "memory loss / dazed" = as_mtbi_mem_daze,
    "income" = d_income,
    "interview_age" = d_interview_age,
    "mtbi_age" = d_mtbi_age,
    "pubertal_status" = d_pubertal_status,
    "race" = d_race,
    "sex" = d_sex,
    "headaches" = mh_headaches,
    "mtbi_count" = mh_mtbi_count,
    "wmndf" = dm_wmndf,
    "gord correlations" = rm_gord_cor,
    "gord variances" = rm_gord_var,
    "subc corrrelations" = rm_subc_cor,
    "subc variances" = rm_subc_var,
    "cortical surface area" = sm_cort_sa,
    "cortical thickness" = sm_cort_t,
    "subcortical volume" = sm_subc_v,
    "loneliness" = p_loneliness,
    "screen time" = p_screen_time,
    "family function" = p_family_function,
    "sports" = p_sports,
    "prosocial" = p_prosocial,
    "parent psych" = p_parent_psych,
    "exercise" = p_exercise,
    "cbcl headaches" = cbcl_headaches,
    "cbcl nausea" = cbcl_nausea,
    "cbcl vomiting" = cbcl_vomiting,
    "cbcl dizzy" = cbcl_dizzy,
    "cbcl overtired" = cbcl_overtired,
    "cbcl sleeping more" = cbcl_sleeping_more,
    "cbcl sleeping less" = cbcl_sleeping_less,
    "cbcl depress r" = cbcl_depress_r,
    "cbcl anxiety r" = cbcl_anxiety_r,
    "cbcl attention r" = cbcl_attention_r,
    "cbcl aggressive r" = cbcl_aggressive_r,
    "sds sleep" = sds_sleep,
    "nihtbx list fc" = nihtbx_list_fc,
    "nihtbx pattern fc" = nihtbx_pattern_fc,
    "nihtbx cardsort fc" = nihtbx_cardsort_fc)

vis_missing_by_df(df_list)
```


## Imputation

Here, I only impute the non-neuroimaging data.

Code is based on Eman's imputation script.
Thanks Eman!

While this choice was made largely for the sake of time, it was also partially because imputing neuroimaging data doesn't seem to be a common practice.


```{r eval = FALSE}

df_list_no_neuroimaging <- list(
    "loss of consciousness" = as_mtbi_loc,
    "mechanism of injury" = as_mtbi_mechanism,
    "memory loss / dazed" = as_mtbi_mem_daze,
    "income" = d_income,
    "interview_age" = d_interview_age,
    "mtbi_age" = d_mtbi_age,
    "pubertal_status" = d_pubertal_status,
    "race" = d_race,
    "sex" = d_sex,
    "headaches" = mh_headaches,
    "mtbi_count" = mh_mtbi_count,
    "loneliness" = p_loneliness,
    "screen time" = p_screen_time,
    "family function" = p_family_function,
    "sports" = p_sports,
    "prosocial" = p_prosocial,
    "parent psych" = p_parent_psych,
    "exercise" = p_exercise,
    "cbcl headaches" = cbcl_headaches,
    "cbcl nausea" = cbcl_nausea,
    "cbcl vomiting" = cbcl_vomiting,
    "cbcl dizzy" = cbcl_dizzy,
    "cbcl overtired" = cbcl_overtired,
    "cbcl sleeping more" = cbcl_sleeping_more,
    "cbcl sleeping less" = cbcl_sleeping_less,
    "cbcl depress r" = cbcl_depress_r,
    "cbcl anxiety r" = cbcl_anxiety_r,
    "cbcl attention r" = cbcl_attention_r,
    "cbcl aggressive r" = cbcl_aggressive_r,
    "sds sleep" = sds_sleep,
    "nihtbx list fc" = nihtbx_list_fc,
    "nihtbx pattern fc" = nihtbx_pattern_fc,
    "nihtbx cardsort fc" = nihtbx_cardsort_fc)


full_df <- df_list_no_neuroimaging |> purrr::reduce(dplyr::full_join, by = "subjectkey")
full_df$household_income <- as.factor(full_df$household_income)
full_df$race <- as.factor(full_df$race)

# m = 5 and maxit = 10 are default settings
imputed <- mice(full_df, m = 5, maxit = 10, seed = 42)

# View a summary of which variables were added by the imputation
imputed$imp

# Isolate the imputed data
imputed_non_imaging <- complete(imputed)

as_mtbi_loc_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "latest_mtbi_loc")
as_mtbi_mechanism_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "latest_mtbi_mechanism")
as_mtbi_mem_daze_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "latest_mtbi_mem_daze")
d_income_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "household_income")
d_interview_age_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "interview_age")
d_mtbi_age_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "latest_mtbi_age")
d_pubertal_status_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "pubertal_status")
d_race_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "race")
d_sex_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "M")
mh_headaches_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "headache")
mh_mtbi_count_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "mtbi_count")
p_loneliness_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "ss_friend":"os_close_friend")
p_screen_time_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", dplyr::contains("screentime"))
p_family_function_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "q1_fight":"q9_yell")
p_sports_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", dplyr::contains("activities"))
p_prosocial_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "q1":"q3")
p_parent_psych_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", dplyr::contains("asr_scr"))
p_exercise_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", dplyr::contains("physical_activity"))
cbcl_headaches_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "cbcl_headaches")
cbcl_nausea_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "cbcl_nausea")
cbcl_vomiting_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "cbcl_vomiting")
cbcl_dizzy_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "cbcl_dizzy")
cbcl_overtired_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "cbcl_overtired")
cbcl_sleeping_more_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "cbcl_sleeping_more")
cbcl_sleeping_less_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "cbcl_sleeping_less")
cbcl_depress_r_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "cbcl_depress_r")
cbcl_anxiety_r_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "cbcl_anxiety_r")
cbcl_attention_r_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "cbcl_attention_r")
cbcl_aggressive_r_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "cbcl_aggressive_r")
sds_sleep_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", dplyr::starts_with("sleep"))
nihtbx_list_fc_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "nihtbx_list_fc")
nihtbx_pattern_fc_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "nihtbx_pattern_fc")
nihtbx_cardsort_fc_imp <- imputed_non_imaging |>
    dplyr::select("subjectkey", "nihtbx_cardsort_fc")
```

```{r eval = FALSE}
write_csv(as_mtbi_loc_imp,
    here("data/abcd/inputs/post-imputation/as_mtbi_loc_imp.csv"))
write_csv(as_mtbi_mechanism_imp,
    here("data/abcd/inputs/post-imputation/as_mtbi_mechanism_imp.csv"))
write_csv(as_mtbi_mem_daze_imp,
    here("data/abcd/inputs/post-imputation/as_mtbi_mem_daze_imp.csv"))
write_csv(d_income_imp,
    here("data/abcd/inputs/post-imputation/d_income_imp.csv"))
write_csv(d_interview_age_imp,
    here("data/abcd/inputs/post-imputation/d_interview_age_imp.csv"))
write_csv(d_mtbi_age_imp,
    here("data/abcd/inputs/post-imputation/d_mtbi_age_imp.csv"))
write_csv(d_pubertal_status_imp,
    here("data/abcd/inputs/post-imputation/d_pubertal_status_imp.csv"))
write_csv(d_race_imp,
    here("data/abcd/inputs/post-imputation/d_race_imp.csv"))
write_csv(d_sex_imp,
    here("data/abcd/inputs/post-imputation/d_sex_imp.csv"))
write_csv(mh_headaches_imp,
    here("data/abcd/inputs/post-imputation/mh_headaches_imp.csv"))
write_csv(mh_mtbi_count_imp,
    here("data/abcd/inputs/post-imputation/mh_mtbi_count_imp.csv"))
write_csv(p_loneliness_imp,
    here("data/abcd/inputs/post-imputation/p_loneliness_imp.csv"))
write_csv(p_screen_time_imp,
    here("data/abcd/inputs/post-imputation/p_screen_time_imp.csv"))
write_csv(p_family_function_imp,
    here("data/abcd/inputs/post-imputation/p_family_function_imp.csv"))
write_csv(p_sports_imp,
    here("data/abcd/inputs/post-imputation/p_sports_imp.csv"))
write_csv(p_prosocial_imp,
    here("data/abcd/inputs/post-imputation/p_prosocial_imp.csv"))
write_csv(p_parent_psych_imp,
    here("data/abcd/inputs/post-imputation/p_parent_psych_imp.csv"))
write_csv(p_exercise_imp,
    here("data/abcd/inputs/post-imputation/p_exercise_imp.csv"))
write_csv(cbcl_headaches_imp,
    here("data/abcd/outputs/post-imputation/cbcl_headaches_imp.csv"))
write_csv(cbcl_nausea_imp,
    here("data/abcd/outputs/post-imputation/cbcl_nausea_imp.csv"))
write_csv(cbcl_vomiting_imp,
    here("data/abcd/outputs/post-imputation/cbcl_vomiting_imp.csv"))
write_csv(cbcl_dizzy_imp,
    here("data/abcd/outputs/post-imputation/cbcl_dizzy_imp.csv"))
write_csv(cbcl_overtired_imp,
    here("data/abcd/outputs/post-imputation/cbcl_overtired_imp.csv"))
write_csv(cbcl_sleeping_more_imp,
    here("data/abcd/outputs/post-imputation/cbcl_sleeping_more_imp.csv"))
write_csv(cbcl_sleeping_less_imp,
    here("data/abcd/outputs/post-imputation/cbcl_sleeping_less_imp.csv"))
write_csv(cbcl_depress_r_imp,
    here("data/abcd/outputs/post-imputation/cbcl_depress_r_imp.csv"))
write_csv(cbcl_anxiety_r_imp,
    here("data/abcd/outputs/post-imputation/cbcl_anxiety_r_imp.csv"))
write_csv(cbcl_attention_r_imp,
    here("data/abcd/outputs/post-imputation/cbcl_attention_r_imp.csv"))
write_csv(cbcl_aggressive_r_imp,
    here("data/abcd/outputs/post-imputation/cbcl_aggressive_r_imp.csv"))
write_csv(sds_sleep_imp,
    here("data/abcd/outputs/post-imputation/sds_sleep_imp.csv"))
write_csv(nihtbx_list_fc_imp,
    here("data/abcd/outputs/post-imputation/nihtbx_list_fc_imp.csv"))
write_csv(nihtbx_pattern_fc_imp,
    here("data/abcd/outputs/post-imputation/nihtbx_pattern_fc_imp.csv"))
write_csv(nihtbx_cardsort_fc_imp,
    here("data/abcd/outputs/post-imputation/nihtbx_cardsort_fc_imp.csv"))
```

