# Input variables
This chapter outlines the extraction of the input variables that will be included for the clustering analyses.

The inputs are collected across the following domains:

1. Acute symptoms (@sec-inputacutesymptoms)
2. Demographics (@sec-inputdemographics)
3. Medical history (@sec-inputmedicalhistory)
4. Neuroimaging (@sec-inputneuroimaging)
5. Psychosocial factors (@sec-inputpsychosocial)


## Acute symptoms {#sec-inputacutesymptoms}

Acute symptoms of interest include:

1. mechanism of injury
2. age at which injury occurred
3. presence and duration of LOC
4. presence of feeling dazed or having memory loss following the injury


```{r child="../subtyping-mtbi/abcd/get_acute_symptoms.Rmd", eval=TRUE}

```


## Demographics {#sec-inputdemographics}

Demographic variables included in the analyses are:

* Age
* Sex
* Race
* Ethnicity
* Socioeconomic status
* Pubertal development status

Aspects of the NIH Toolbox probe different forms of IQ @7HIU42K2#Zhao_Etal_2022 and are used in this study as an out-of-model outcome measure rather than as an input. 

Age and sex are commonly included in the ABCD study's data files.


```{r child="../subtyping-mtbi/abcd/get_demographics.Rmd", eval=TRUE}

```


## Medical history {#sec-inputmedicalhistory}

Medical history variables of interest include:

1. Number of previous head injuries
    * discrete variable `mtbi_count` from the processed file `abcd_otbi01_detailed.csv`
2. History of headaches 
    * binary variable `medhx_2q` from the file ABCD Parent Medical History Questionnaire (`abcd_mx01.txt`; category Med History; release 2.0)
        * checks if subject has ever gone to doctor for bad headaches

Unfortunately, information on pain (the file `abcd_pq01.txt`), a factor noted as an important covariate by the original A-CAP study (@8VF7JUXL#Yeates_Etal_2017), was not a part of ABCD's baseline data collection.

```{r child="../subtyping-mtbi/abcd/get_med_history.Rmd", eval=TRUE}

```


## Neuroimaging {#sec-inputneuroimaging}

Variables of interest related to brain structure and function include:

* Structural: T1-weighted multishell diffusion-weighted MRI data
* Diffusion: Neurite density (restricted spectrum imaging)
* Functional: resting-state functional MRI data

The 2019 publication by Hagler et al. @UD6THTQZ#Hagler_Etal_2019 outlines the neuroimaging data present in the ABCD dataset in detail.

### Structural imaging

As mentioned in @sec-abcdneuroimaging, this project is interested in three aspects of structural MRI:
* cortical surface areas
* cortical thickness(es)
* subcortical volumes

#### Cortical surface area

The relevant file is abcd_mrisdp10201, which contains the cortical thickness of ~150 regions (variables `mrisdp_*` where * ranges from 303 to 453).

#### Cortical thickness

The relevant file is abcd_mrisdp10201, which contains the cortical thickness of ~150 regions (variables `mrisdp_*` where * ranges from 1 to 151).


```{r child="../subtyping-mtbi/abcd/get_brain_str.Rmd", eval=TRUE}

```

### Diffusion imaging

For this project, I specifically focus on neurite density, a restricted spectrum imaging measure that is interpreted as reflecting the relative density of cellular (neuronal) processes. 


```{r child="../subtyping-mtbi/abcd/get_brain_diffusion.Rmd", eval=TRUE}

```

### Functional imaging

As mentioned in the neuroimaging background of this section, this project is concerned with the following variables resting-state fMRI variables:

- Gordon network (cortical) correlations 
- Subcortical correlations
- Gordon and subcortical temporal variances

The script below collects and exports these variables.

```{r child="../subtyping-mtbi/abcd/get_brain_fn.Rmd", eval=TRUE}

```


## Psychosocial factors {#sec-inputpsychosocial}

Psychosocial factors of interest include:

* family function
* prosocial behaviour
* loneliness
* healthy behaviours
* parent psychopathology

```{r child="../subtyping-mtbi/abcd/get_psych.Rmd", eval=TRUE}

```
