# Extracting input variables

The proposed analyses for this project include the following categories of input variables:

* acute symptoms
* brain structure and function
* demographics
* psychosocial factors
* medical history

Over the next few subsections, I go collect key variables related to these categories from the NDA.


## Acute symptoms

Acute symptoms of interest include:

1. mechanism of injury
2. age at which injury occurred
3. presence and duration of LOC
4. presence of feeling dazed or having memory loss following the injury


```{r child="../subtyping-mtbi/abcd/get_acute_symptoms.Rmd", eval=TRUE}

```


## Structural, functional, and diffusion brain imaging

Variables of interest related to brain structure and function include:

* Structural: T1-weighted multishell diffusion-weighted MRI data
* Functional: resting-state functional MRI data
- Diffusion: Neurite density (restricted spectrum imaging)

The 2019 publication by Hagler et al. @UD6THTQZ#Hagler_Etal_2019 outlines the neuroimaging data present in the ABCD dataset in detail.


### Diffusion imaging

For this project, I speciically focus on neurite density, a restricted spectrum imaging measure that is interpreted as reflecting the relative density of cellular (neuronal) processes. 


```{r child="../subtyping-mtbi/abcd/get_brain_diffusion.Rmd", eval=TRUE}

```

### Functional imaging

As mentioned in the neuroimaging background of this section, this project is concerned with the following variables resting-state fMRI variables:

- Gordon network (cortical) correlations 
- Subcortical correlations
- Gordon and subcortical temporal variances

The script below collects and exports these variables.

```{r child="../subtyping-mtbi/abcd/get_brain_fn.Rmd", eval=TRUE}

```


## Demographics

Demographic variables included in the analyses are:

* Age
* Sex
* Race
* Ethnicity
* Socioeconomic status
* Pubertal development status

Age and sex are commonly included in the ABCD study's data files.


```{r child="../subtyping-mtbi/abcd/get_demographics.Rmd", eval=TRUE}

```


## Psychosocial factors

Psychosocial factors of interest include:

* family function
* prosocial behaviour
* loneliness
* healthy behaviours
* parent psychopathology


## Medical history

Medical history variables of interest include:

1. Number of previous head injuries
    * discrete variable `mtbi_count` from the processed file `abcd_otbi01_detailed.csv`
2. History of headaches 
    * binary variable `medhx_2q` from the file ABCD Parent Medical History Questionnaire (`abcd_mx01.txt`; category Med History; release 2.0)
        * checks if subject has ever gone to doctor for bad headaches


## Handling data types of mixed input

The original similarity network fusion paper @wang_similarity_2014 suggests using a scaled Euclidean distance for continuous variables, chi-squared distance for discrete variables, and agreement-based measure for binary variables.
The paper also indicates that SNF may be used to incorporate arbitrary types of discrete (binary or categorical) data alongside continuous data, and that the compatibility of the selected data sources can be verified using normalized mutual information scores.
This topic is addressed further in the methods section.


## Post-concussion symptoms
