# metaSNF of Baseline mTBI Subjects

This chapter contains:

1. Derivation of baseline mTBI subtypes with metasnf
2. Characterization of those subtypes

## Importing packages and establishing file paths

```{r}
library(metasnf)

# This is a data list
example_dl <- readRDS("example_dl.rds")
```

## metaSNF approach

```{r}
set.seed(42)
mtbi_config <- snf_config(
    example_dl,
    n_solutions = 1,
    cnt_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    dsc_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    ord_dist_fns = list(
        "standard_norm_euclidean" = sn_euclidean_distance
    ),
    possible_snf_schemes = 1, # The only option that matches vanilla SNF
    use_default_dist_fns = TRUE
)

mtbi_config

my_sol_df <- batch_snf(
    dl = example_dl,
    sc = mtbi_config,
    processes = 1,
    return_sim_mats = TRUE
)
```

## Regular SNF approach

```{r}
mtbi_config
```

Within this configuration, the following distance matrices are used:

- Continuous: 1 (euclidean)
- Discrete: 2 (standard_norm_euclidean)
- Ordinal: 1 (euclidean)
- Categorical: 1 (gower)
- Mixed: 1 (gower)

```{r}
feature_weights <- data.frame(mtbi_config$"weights_matrix"[1, , drop = FALSE])
feature_weights

non_dropout_dfs <- c(
    "as_mem_daze",
    "as_mechanism",
    "d_age",
    "d_mtbi_age",
    "d_race",
    "d_pubertal",
    "mh_headaches",
    "mh_mtbi_count",
    "sm_subc_v",
    "sm_cort_sa",
    "p_friends",
    "p_exercise",
    "p_parent_psych"
)

example_dl_dropout <- example_dl[non_dropout_dfs]

list_of_distance_matrices <- lapply(
    example_dl_dropout,
    function(x) {
        if (x$"type" %in% c("continous", "ordinal")) {
            distance_matrix <- euclidean_distance(
                x$"data"[, -1, drop = FALSE],
                feature_weights[, colnames(x$"data"[, -1, drop = FALSE])]
            )
        } else if (x$"type" == "discrete") {
            distance_matrix <- sn_euclidean_distance(
                x$"data"[, -1, drop = FALSE],
                feature_weights[, colnames(x$"data"[, -1, drop = FALSE])]
            )
        } else {
            distance_matrix <- gower_distance(
                x$"data"[, -1, drop = FALSE],
                feature_weights[, colnames(x$"data"[, -1, drop = FALSE])]
            )
        }
    }
)

similarity_matrices <- lapply(
    list_of_distance_matrices,
    function(x) {
        SNFtool::affinityMatrix(x, K = mtbi_config$"settings_df"$"k", sigma = mtbi_config$"settings_df"$"alpha")
    }
)

fused_network <- SNFtool::SNF(Wall = similarity_matrices, K = mtbi_config$"settings_df"$"k", t = 20)

# TRUE
all.equal(sim_mats_list(my_sol_df)[[1]], fused_network, check.attributes = FALSE)
```
