# Standard SNF

In this chapter I work through a typical SNF study pipeline.


## Loading data

```{r eval = FALSE}
library(dplyr)
library(abcdutils)
library(scabcd)
library(readr)
library(here)
library(digest) # For generating hash functions

# Inputs
as_mtbi_loc <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/as_mtbi_loc_imp.csv")))
as_mtbi_mechanism <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/as_mtbi_mechanism_imp.csv")))
as_mtbi_mem_daze <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/as_mtbi_mem_daze_imp.csv")))
d_income <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/d_income_imp.csv")))
d_interview_age <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/d_interview_age_imp.csv")))
d_mtbi_age <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/d_mtbi_age_imp.csv")))
d_pubertal_status <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/d_pubertal_status_imp.csv")))
d_race <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/d_race_imp.csv")))
d_sex <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/d_sex_imp.csv")))
mh_headaches <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/mh_headaches_imp.csv")))
mh_mtbi_count <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/mh_mtbi_count_imp.csv")))
dm_wmndf_qc <-
    stats::na.omit(read_csv(here("data/abcd/inputs/pre-imputation/dm_wmndf_qc.csv")))
rm_gord_cor_qc <-
    stats::na.omit(read_csv(here("data/abcd/inputs/pre-imputation/rm_gord_cor_qc.csv")))
rm_gord_var_qc <-
    stats::na.omit(read_csv(here("data/abcd/inputs/pre-imputation/rm_gord_var_qc.csv")))
rm_subc_cor_qc <-
    stats::na.omit(read_csv(here("data/abcd/inputs/pre-imputation/rm_subc_cor_qc.csv")))
rm_subc_var_qc <-
    stats::na.omit(read_csv(here("data/abcd/inputs/pre-imputation/rm_subc_var_qc.csv")))
sm_cort_sa_qc <-
    stats::na.omit(read_csv(here("data/abcd/inputs/pre-imputation/sm_cort_sa_qc.csv")))
sm_cort_t_qc <-
    stats::na.omit(read_csv(here("data/abcd/inputs/pre-imputation/sm_cort_t_qc.csv")))
sm_subc_v_qc <-
    stats::na.omit(read_csv(here("data/abcd/inputs/pre-imputation/sm_subc_v_qc.csv")))
p_loneliness <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/p_loneliness_imp.csv")))
p_screen_time <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/p_screen_time_imp.csv")))
p_family_function <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/p_family_function_imp.csv")))
p_sports <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/p_sports_imp.csv")))
p_prosocial <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/p_prosocial_imp.csv")))
p_parent_psych <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/p_parent_psych_imp.csv")))
p_exercise <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/p_exercise_imp.csv")))
# Outcomes
cbcl_headaches <-
    stats::na.omit(read_csv(here("data/abcd/outputs/post-imputation/cbcl_headaches_imp.csv")))
cbcl_nausea <-
    stats::na.omit(read_csv(here("data/abcd/outputs/post-imputation/cbcl_nausea_imp.csv")))
cbcl_vomiting <-
    stats::na.omit(read_csv(here("data/abcd/outputs/post-imputation/cbcl_vomiting_imp.csv")))
cbcl_dizzy <-
    stats::na.omit(read_csv(here("data/abcd/outputs/post-imputation/cbcl_dizzy_imp.csv")))
cbcl_overtired <-
    stats::na.omit(read_csv(here("data/abcd/outputs/post-imputation/cbcl_overtired_imp.csv")))
cbcl_sleeping_more <-
    stats::na.omit(read_csv(here("data/abcd/outputs/post-imputation/cbcl_sleeping_more_imp.csv")))
cbcl_sleeping_less <-
    stats::na.omit(read_csv(here("data/abcd/outputs/post-imputation/cbcl_sleeping_less_imp.csv")))
cbcl_depress_r <-
    stats::na.omit(read_csv(here("data/abcd/outputs/post-imputation/cbcl_depress_r_imp.csv")))
cbcl_anxiety_r <-
    stats::na.omit(read_csv(here("data/abcd/outputs/post-imputation/cbcl_anxiety_r_imp.csv")))
cbcl_attention_r <-
    stats::na.omit(read_csv(here("data/abcd/outputs/post-imputation/cbcl_attention_r_imp.csv")))
cbcl_aggressive_r <-
    stats::na.omit(read_csv(here("data/abcd/outputs/post-imputation/cbcl_aggressive_r_imp.csv")))
sds_sleep <-
    stats::na.omit(read_csv(here("data/abcd/outputs/post-imputation/sds_sleep_imp.csv")))
nihtbx_list_fc <-
    stats::na.omit(read_csv(here("data/abcd/outputs/post-imputation/nihtbx_list_fc_imp.csv")))
nihtbx_pattern_fc <-
    stats::na.omit(read_csv(here("data/abcd/outputs/post-imputation/nihtbx_pattern_fc_imp.csv")))
nihtbx_cardsort_fc <-
    stats::na.omit(read_csv(here("data/abcd/outputs/post-imputation/nihtbx_cardsort_fc_imp.csv")))
```


## Filtering to common subjects and separating training/testing splits

This block is used to only keep subjects with complete data (post-imputation)

```{r eval = FALSE}
full_df_list <- list(mtbi_loc = as_mtbi_loc,
    as_mtbi_mechanism,
    as_mtbi_mem_daze,
    d_income,
    d_interview_age,
    d_mtbi_age,
    d_pubertal_status,
    d_race,
    d_sex,
    mh_headaches,
    mh_mtbi_count,
    dm_wmndf_qc,
    rm_gord_cor_qc,
    rm_gord_var_qc,
    rm_subc_cor_qc,
    rm_subc_var_qc,
    sm_cort_sa_qc,
    sm_cort_t_qc,
    sm_subc_v_qc,
    p_loneliness,
    p_screen_time,
    p_family_function,
    p_sports,
    p_prosocial,
    p_parent_psych,
    p_exercise,
    cbcl_headaches,
    cbcl_nausea,
    cbcl_vomiting,
    cbcl_dizzy,
    cbcl_overtired,
    cbcl_sleeping_more,
    cbcl_sleeping_less,
    cbcl_depress_r,
    cbcl_anxiety_r,
    cbcl_attention_r,
    cbcl_aggressive_r,
    sds_sleep)

shared_df <- full_df_list |> purrr::reduce(dplyr::inner_join, by = "subjectkey")

common_subs <- shared_df$subjectkey

training_subs <- train_test_split(0.8, common_subs)$training_set
testing_subs <- train_test_split(0.8, common_subs)$testing_set

as_mtbi_loc <-
    as_mtbi_loc[as_mtbi_loc$subjectkey %in% training_subs, ]
as_mtbi_mechanism <-
    as_mtbi_mechanism[as_mtbi_mechanism$subjectkey %in% training_subs, ]
as_mtbi_mem_daze <-
    as_mtbi_mem_daze[as_mtbi_mem_daze$subjectkey %in% training_subs, ]
d_income <-
    d_income[d_income$subjectkey %in% training_subs, ]
d_interview_age <-
    d_interview_age[d_interview_age$subjectkey %in% training_subs, ]
d_mtbi_age <-
    d_mtbi_age[d_mtbi_age$subjectkey %in% training_subs, ]
d_pubertal_status <-
    d_pubertal_status[d_pubertal_status$subjectkey %in% training_subs, ]
d_race <-
    d_race[d_race$subjectkey %in% training_subs, ]
d_sex <-
    d_sex[d_sex$subjectkey %in% training_subs, ]
mh_headaches <-
    mh_headaches[mh_headaches$subjectkey %in% training_subs, ]
mh_mtbi_count <-
    mh_mtbi_count[mh_mtbi_count$subjectkey %in% training_subs, ]
dm_wmndf_qc <-
    dm_wmndf_qc[dm_wmndf_qc$subjectkey %in% training_subs, ]
rm_gord_cor_qc <-
    rm_gord_cor_qc[rm_gord_cor_qc$subjectkey %in% training_subs, ]
rm_gord_var_qc <-
    rm_gord_var_qc[rm_gord_var_qc$subjectkey %in% training_subs, ]
rm_subc_cor_qc <-
    rm_subc_cor_qc[rm_subc_cor_qc$subjectkey %in% training_subs, ]
rm_subc_var_qc <-
    rm_subc_var_qc[rm_subc_var_qc$subjectkey %in% training_subs, ]
sm_cort_sa_qc <-
    sm_cort_sa_qc[sm_cort_sa_qc$subjectkey %in% training_subs, ]
sm_cort_t_qc <-
    sm_cort_t_qc[sm_cort_t_qc$subjectkey %in% training_subs, ]
sm_subc_v_qc <-
    sm_subc_v_qc[sm_subc_v_qc$subjectkey %in% training_subs, ]
p_loneliness <-
    p_loneliness[p_loneliness$subjectkey %in% training_subs, ]
p_screen_time <-
    p_screen_time[p_screen_time$subjectkey %in% training_subs, ]
p_family_function <-
    p_family_function[p_family_function$subjectkey %in% training_subs, ]
p_sports <-
    p_sports[p_sports$subjectkey %in% training_subs, ]
p_prosocial <-
    p_prosocial[p_prosocial$subjectkey %in% training_subs, ]
p_parent_psych <-
    p_parent_psych[p_parent_psych$subjectkey %in% training_subs, ]
p_exercise <-
    p_exercise[p_exercise$subjectkey %in% training_subs, ]
cbcl_headaches <-
    cbcl_headaches[cbcl_headaches$subjectkey %in% training_subs, ]
cbcl_nausea <-
    cbcl_nausea[cbcl_nausea$subjectkey %in% training_subs, ]
cbcl_vomiting <-
    cbcl_vomiting[cbcl_vomiting$subjectkey %in% training_subs, ]
cbcl_dizzy <-
    cbcl_dizzy[cbcl_dizzy$subjectkey %in% training_subs, ]
cbcl_overtired <-
    cbcl_overtired[cbcl_overtired$subjectkey %in% training_subs, ]
cbcl_sleeping_more <-
    cbcl_sleeping_more[cbcl_sleeping_more$subjectkey %in% training_subs, ]
cbcl_sleeping_less <-
    cbcl_sleeping_less[cbcl_sleeping_less$subjectkey %in% training_subs, ]
cbcl_depress_r <-
    cbcl_depress_r[cbcl_depress_r$subjectkey %in% training_subs, ]
cbcl_anxiety_r <-
    cbcl_anxiety_r[cbcl_anxiety_r$subjectkey %in% training_subs, ]
cbcl_attention_r <-
    cbcl_attention_r[cbcl_attention_r$subjectkey %in% training_subs, ]
cbcl_aggressive_r <-
    cbcl_aggressive_r[cbcl_aggressive_r$subjectkey %in% training_subs, ]
sds_sleep <-
    sds_sleep[sds_sleep$subjectkey %in% training_subs, ]
```


```{r}
# Structure containing all input data
# These data should not contain any NAs, but need not have the same subjects
data_list <- generate_data_list(mtbi_loc = as_mtbi_loc,
                                mtbi_mechanism = as_mtbi_mechanism,
                                mtbi_mem_daze = as_mtbi_mem_daze,
                                income = d_income,
                                interview_age = d_interview_age,
                                mtbi_age = d_mtbi_age,
                                pubertal_status = d_pubertal_status,
                                race = d_race,
                                sex = d_sex,
                                headaches = mh_headaches,
                                mtbi_count = mh_mtbi_count,
                                wmndf = dm_wmndf_qc,
                                gord_cor = rm_gord_cor_qc,
                                gord_var = rm_gord_var_qc,
                                subc_cor = rm_subc_cor_qc,
                                subc_var = rm_subc_var_qc,
                                cort_sa = sm_cort_sa_qc,
                                cort_t = sm_cort_t_qc,
                                subc_v = sm_subc_v_qc,
                                loneliness = p_loneliness,
                                screen_time = p_screen_time,
                                family_function = p_family_function,
                                sports = p_sports,
                                prosocial = p_prosocial,
                                parent_psych = p_parent_psych,
                                exercise = p_exercise)
    

# Structure containing all outcome data
outcome_list <- generate_outcome_list(cbcl_headaches = cbcl_headaches,
                                      cbcl_nausea = cbcl_nausea,
                                      cbcl_vomiting = cbcl_vomiting,
                                      cbcl_dizzy = cbcl_dizzy,
                                      cbcl_overtired = cbcl_overtired,
                                      cbcl_sleeping_more = cbcl_sleeping_more,
                                      cbcl_sleeping_less = cbcl_sleeping_less,
                                      cbcl_depress_r = cbcl_depress_r,
                                      cbcl_anxiety_r = cbcl_anxiety_r,
                                      cbcl_attention_r = cbcl_attention_r,
                                      cbcl_aggressive_r = cbcl_aggressive_r,
                                      sds_sleep = sds_sleep)


# Builds a standard design matrix only exploring SNF hyperparameters
design_matrix <- build_design_matrix_s()

# Assess clustering minimum p-value for an ordinal dependent variable
output_matrix <- execute_design_matrix(data_list, design_matrix, outcome_list)

output_matrix$mean_p_val <- as.numeric(output_matrix$mean_p_val)
output_matrix$min_p_val <- as.numeric(output_matrix$min_p_val)

# write_csv(output_matrix, here("data/abcd/results/processed/standard_scan_om.csv"))

min(output_matrix$min_p_val)
min(output_matrix$mean_p_val)

library(ggplot2)

ggplot(output_matrix, mapping = aes(x = K, y = mean_p_val)) +
    geom_point()

ggplot(output_matrix, mapping = aes(x = K, y = mean_p_val, color = alpha)) +
    geom_point()

# The boring NOOBs way
ggplot(output_matrix, mapping = aes(x = min_p_val, y = mean_p_val, color = alpha)) +
    geom_point()

ggplot(output_matrix, mapping = aes(x = K, y = alpha, size = min_p_val)) +
    geom_point()


colnames(output_matrix)

set.seed(42)
design_matrix_base <- build_design_matrix_base_t()
design_matrix <- add_design_matrix_rows(design_matrix_base, 100)

design_matrix




output_matrix_full <- execute_design_matrix(data_list, design_matrix, outcome_list)

output_matrix_full

# My cool dude way
output_matrix_full$mean_p_val <- as.numeric(output_matrix_full$mean_p_val)
output_matrix_full$min_p_val <- as.numeric(output_matrix_full$min_p_val)

write_csv(output_matrix_full, here("data/abcd/results/processed/full_scan_om.csv"))

min(output_matrix_full$min_p_val)
min(output_matrix_full$mean_p_val)

library(ggplot2)

ggplot(output_matrix_full, mapping = aes(x = K, y = mean_p_val)) +
    geom_point()

ggplot(output_matrix_full, mapping = aes(x = alpha, y = mean_p_val)) +
    geom_point()

ggplot(output_matrix_full, mapping = aes(x = K, y = mean_p_val, color = alpha)) +
    geom_point()

ggplot(output_matrix_full, mapping = aes(x = min_p_val, y = mean_p_val, color = alpha)) +
    geom_point()

ggplot(output_matrix_full, mapping = aes(x = K, y = alpha, size = min_p_val)) +
    geom_point()

which(output_matrix_full$min_p_val == min(output_matrix_full$min_p_val))

output_matrix_full[33, ]

```


## Adjusting the CBCL measures and trying again

Borderline is 93-97th percentile, clinical is 97th percentile or higher
```{r}

abcd_cbcl01 <- read_delim(here("data/abcd/raw/abcd_cbcl01.txt"))
abcd_cbcls01 <- read_delim(here("data/abcd/raw/abcd_cbcls01.txt"))

# The raw scores of all children
cbcl_depress_r_all <- get_cbcl_depress_r(abcd_cbcls01, t = 0)
cbcl_anxiety_r_all <- get_cbcl_anxiety_r(abcd_cbcls01, t = 0)
cbcl_attention_r_all <- get_cbcl_attention_r(abcd_cbcls01, t = 0)
cbcl_aggressive_r_all <- get_cbcl_aggressive_r(abcd_cbcls01, t = 0)

# Converting relevant columns to numeric
cbcl_depress_r_all$cbcl_depress_r <- as.numeric(cbcl_depress_r_all$cbcl_depress_r)
cbcl_anxiety_r_all$cbcl_anxiety_r <- as.numeric(cbcl_anxiety_r_all$cbcl_anxiety_r)
cbcl_attention_r_all$cbcl_attention_r <- as.numeric(cbcl_attention_r_all$cbcl_attention_r)
cbcl_aggressive_r_all$cbcl_aggressive_r <- as.numeric(cbcl_aggressive_r_all$cbcl_aggressive_r)

depress_threshold_borderline <-
    quantile(cbcl_depress_r_all$cbcl_depress_r, probs = c(0.93, 0.97), na.rm = TRUE)[[1]]
depress_threshold_clinical <-
    quantile(cbcl_depress_r_all$cbcl_depress_r, probs = c(0.93, 0.97), na.rm = TRUE)[[2]]
anxiety_threshold_borderline <-
    quantile(cbcl_anxiety_r_all$cbcl_anxiety_r, probs = c(0.93, 0.97), na.rm = TRUE)[[1]]
anxiety_threshold_clinical <-
    quantile(cbcl_anxiety_r_all$cbcl_anxiety_r, probs = c(0.93, 0.97), na.rm = TRUE)[[2]]
attention_threshold_borderline <-
    quantile(cbcl_attention_r_all$cbcl_attention_r, probs = c(0.93, 0.97), na.rm = TRUE)[[1]]
attention_threshold_clinical <-
    quantile(cbcl_attention_r_all$cbcl_attention_r, probs = c(0.93, 0.97), na.rm = TRUE)[[2]]
aggressive_threshold_borderline <-
    quantile(cbcl_aggressive_r_all$cbcl_aggressive_r, probs = c(0.93, 0.97), na.rm = TRUE)[[1]]
aggressive_threshold_clinical <-
    quantile(cbcl_aggressive_r_all$cbcl_aggressive_r, probs = c(0.93, 0.97), na.rm = TRUE)[[2]]

cbcl_depress <- cbcl_depress_r |>
    dplyr::mutate(cbcl_depress = dplyr::case_when(
        cbcl_depress_r < depress_threshold_borderline ~ 0,
        cbcl_depress_r < depress_threshold_clinical ~ 1,
        TRUE ~ 2)) |>
    dplyr::select("subjectkey", "cbcl_depress")

cbcl_anxiety <- cbcl_anxiety_r |>
    dplyr::mutate(cbcl_anxiety = dplyr::case_when(
        cbcl_anxiety_r < anxiety_threshold_borderline ~ 0,
        cbcl_anxiety_r < anxiety_threshold_clinical ~ 1,
        TRUE ~ 2)) |>
    dplyr::select("subjectkey", "cbcl_anxiety")

cbcl_attention <- cbcl_attention_r |>
    dplyr::mutate(cbcl_attention = dplyr::case_when(
        cbcl_attention_r < attention_threshold_borderline ~ 0,
        cbcl_attention_r < attention_threshold_clinical ~ 1,
        TRUE ~ 2)) |>
    dplyr::select("subjectkey", "cbcl_attention")


cbcl_aggressive <- cbcl_aggressive_r |>
    dplyr::mutate(cbcl_aggressive = dplyr::case_when(
        cbcl_aggressive_r < aggressive_threshold_borderline ~ 0,
        cbcl_aggressive_r < aggressive_threshold_clinical ~ 1,
        TRUE ~ 2)) |>
    dplyr::select("subjectkey", "cbcl_aggressive")

data_list <- generate_data_list(mtbi_loc = as_mtbi_loc,
                                mtbi_mechanism = as_mtbi_mechanism,
                                mtbi_mem_daze = as_mtbi_mem_daze,
                                income = d_income,
                                interview_age = d_interview_age,
                                mtbi_age = d_mtbi_age,
                                pubertal_status = d_pubertal_status,
                                race = d_race,
                                sex = d_sex,
                                headaches = mh_headaches,
                                mtbi_count = mh_mtbi_count,
                                wmndf = dm_wmndf_qc,
                                gord_cor = rm_gord_cor_qc,
                                gord_var = rm_gord_var_qc,
                                subc_cor = rm_subc_cor_qc,
                                subc_var = rm_subc_var_qc,
                                cort_sa = sm_cort_sa_qc,
                                cort_t = sm_cort_t_qc,
                                subc_v = sm_subc_v_qc,
                                loneliness = p_loneliness,
                                screen_time = p_screen_time,
                                family_function = p_family_function,
                                sports = p_sports,
                                prosocial = p_prosocial,
                                parent_psych = p_parent_psych,
                                exercise = p_exercise)
    

# Structure containing all outcome data
outcome_list <- generate_outcome_list(cbcl_headaches = cbcl_headaches,
                                      cbcl_nausea = cbcl_nausea,
                                      cbcl_vomiting = cbcl_vomiting,
                                      cbcl_dizzy = cbcl_dizzy,
                                      cbcl_overtired = cbcl_overtired,
                                      cbcl_sleeping_more = cbcl_sleeping_more,
                                      cbcl_sleeping_less = cbcl_sleeping_less,
                                      cbcl_depress = cbcl_depress,
                                      cbcl_anxiety = cbcl_anxiety,
                                      cbcl_attention = cbcl_attention,
                                      cbcl_aggressive = cbcl_aggressive,
                                      sds_sleep = sds_sleep)


# Builds a standard design matrix only exploring SNF hyperparameters
design_matrix <- build_design_matrix_s()

# Assess clustering minimum p-value for an ordinal dependent variable
output_matrix <- execute_design_matrix(data_list, design_matrix, outcome_list)

output_matrix$mean_p_val <- as.numeric(output_matrix$mean_p_val)
output_matrix$min_p_val <- as.numeric(output_matrix$min_p_val)

# Not great
min(output_matrix$min_p_val) # 0.009479592
min(output_matrix$mean_p_val) # 0.2236012

write_csv(output_matrix, here("data/abcd/results/processed/standard_scan_om_adjusted_cbcl.csv"))

ggplot(output_matrix, mapping = aes(x = K, y = mean_p_val)) +
    geom_point()

ggplot(output_matrix, mapping = aes(x = K, y = mean_p_val, color = alpha)) +
    geom_point()

# The boring NOOBs way
ggplot(output_matrix, mapping = aes(x = min_p_val, y = mean_p_val, color = alpha)) +
    geom_point()

ggplot(output_matrix, mapping = aes(x = K, y = alpha, size = min_p_val)) +
    geom_point()

output_matrix


# Now trying within the proper K val range

set.seed(42)
design_matrix_base <- build_design_matrix_base_t()
design_matrix <- add_design_matrix_rows(design_matrix_base, 100)

design_matrix

output_matrix_full <- execute_design_matrix(data_list, design_matrix, outcome_list)

output_matrix_full

write_csv(output_matrix_full, here("data/abcd/results/processed/full_scan_om_adjusted_cbcl.csv"))

output_matrix_full$mean_p_val <- as.numeric(output_matrix_full$mean_p_val)
output_matrix_full$min_p_val <- as.numeric(output_matrix_full$min_p_val)

# Pretty good!
min(output_matrix_full$min_p_val) # 0.000380322511, and that is for both depression and anxiety
min(output_matrix_full$mean_p_val) # 0.12


best <- which(output_matrix_full$min_p_val == min(output_matrix_full$min_p_val))
output_matrix_full[best, ]


```


# Try the base given the psychosocial vars

```{r}
set.seed(42)
design_matrix_base <- build_design_matrix_base_t2()
design_matrix <- add_design_matrix_rows(design_matrix_base, 100)

design_matrix

outcome_list

output_matrix_full2 <- execute_design_matrix(data_list, design_matrix, outcome_list)

#output_matrix_full <- read_delim(here("data/abcd/results/processed/full_scan_om_adjusted_cbcl_inc_psych.csv"))


output_matrix_full$mean_p_val <- as.numeric(output_matrix_full$mean_p_val)
output_matrix_full$min_p_val <- as.numeric(output_matrix_full$min_p_val)

output_matrix_full$min_p_val

min(output_matrix_full$min_p_val)
min(output_matrix_full$mean_p_val)
# These are outstanding p-values

# write_csv(output_matrix_full, here("data/abcd/results/processed/full_scan_om_adjusted_cbcl_inc_psych.csv"))

mc_pvals <- p_val_select(output_matrix_full)

# That looks pretty intense
heatmap_pvals(mc_pvals)

mc_results <- meta_cluster(output_matrix_full)

mc_results


# That is extremely well-separated
pheatmap::pheatmap(mc_results)


output_matrix_full

```

Make sure to remove headaches from the final list of examined outcomes, as it is basically an input


## Figuring out how to characterize the MC results

```{r}

library(pheatmap)

pheatmap(mc_results, border_color = FALSE)

mc_results

pheatmap(design_matrix)

dm_scaled <- design_matrix

# Trying to plot the input design matrix as a heatmap
dm_scaled$row_id <- dm_scaled$row_id / max(dm_scaled$row_id)
dm_scaled$K <- dm_scaled$K / max(dm_scaled$K)
dm_scaled$alpha <- dm_scaled$alpha / max(dm_scaled$alpha)
dm_scaled$snf_scheme <- dm_scaled$snf_scheme / max(dm_scaled$snf_scheme)
dm_scaled$eigen_or_rot <- dm_scaled$eigen_or_rot / max(dm_scaled$eigen_or_rot)

pheatmap(dm_scaled, cluster_rows = FALSE, cluster_columns = FALSE)

mc_results

colnames(mc_results) <- as.character(1:nrow(mc_results))
rownames(mc_results) <- as.character(1:nrow(mc_results))


write_csv(data.frame(mc_results), here("data/abcd/results/processed/full_scan_om_adjusted_cbcl_inc_psych_mc_results.csv"))

mc_results <- as.matrix(read_delim(here("data/abcd/results/processed/full_scan_om_adjusted_cbcl_inc_psych_mc_results.csv")))


identical(mc_results2, mc_results)

out <- pheatmap(mc_results)

dm_scaled_reordered <- dm_scaled[out$tree_row[["order"]], ]

dm_reordered <- design_matrix[out$tree_row[["order"]], ]

dm_reordered

pheatmap(dm_scaled_reordered, cluster_rows = FALSE)

mc_pvals_reordered <- mc_pvals[out$tree_row[["order"]], ]


pheatmap(mc_pvals_reordered, cluster_rows = FALSE)

om_reordered <- output_matrix_full[out$tree_row[["order"]], ]

om_row1 <- om_reordered[1, ]

om_row1
```

## Are the p-values calculated properly?

```{r}
library(ggplot2)

clustered_subjects <- subs(om_reordered[1, ])
clusters <- data.frame(t(clustered_subjects))
clusters$id <- rownames(clusters)
rownames(clusters) <- NULL
colnames(clusters) <- c("cluster", "subjectkey")
clusters <- clusters[2:nrow(clusters), ]
clusters

outcome_list <- list(
    clusters,
    cbcl_headaches,
    cbcl_nausea,
    cbcl_vomiting,
    cbcl_dizzy,
    cbcl_overtired,
    cbcl_sleeping_more,
    cbcl_sleeping_less,
    cbcl_depress,
    cbcl_anxiety,
    cbcl_attention,
    cbcl_aggressive,
    sds_sleep)

comparison_df <- outcome_list |> purrr::reduce(dplyr::inner_join, by = "subjectkey")

comparison_df$cluster <- as.factor(comparison_df$cluster)

colnames(comparison_df)

dim(comparison_df)

# Using ordinal regression, the p-values are very low
9 * ord_reg_p(clusters, cbcl_nausea, "cbcl_nausea") # 0.0001365547
9 * ord_reg_p(clusters, cbcl_dizzy, "cbcl_dizzy")
9 * ord_reg_p(clusters, cbcl_overtired, "cbcl_overtired")
9 * ord_reg_p(clusters, cbcl_sleeping_more, "cbcl_sleeping_more")
9 * ord_reg_p(clusters, cbcl_sleeping_less, "cbcl_sleeping_less")
9 * ord_reg_p(clusters, cbcl_anxiety, "cbcl_anxiety")
9 * ord_reg_p(clusters, cbcl_attention, "cbcl_attention")
9 * ord_reg_p(clusters, cbcl_aggressive, "cbcl_aggressive")


pval_vec <- c(
    9 * ord_reg_p(clusters, cbcl_nausea, "cbcl_nausea"), # 0.0001365547 uncorrected
    9 * ord_reg_p(clusters, cbcl_dizzy, "cbcl_dizzy"),
    9 * ord_reg_p(clusters, cbcl_overtired, "cbcl_overtired"),
    9 * ord_reg_p(clusters, cbcl_sleeping_more, "cbcl_sleeping_more"),
    9 * ord_reg_p(clusters, cbcl_sleeping_less, "cbcl_sleeping_less"),
    9 * ord_reg_p(clusters, cbcl_anxiety, "cbcl_anxiety"),
    9 * ord_reg_p(clusters, cbcl_attention, "cbcl_attention"),
    9 * ord_reg_p(clusters, cbcl_aggressive, "cbcl_aggressive"))

mean(pval_vec)

c1_df <- comparison_df |> dplyr::filter(cluster == 1)
c2_df <- comparison_df |> dplyr::filter(cluster == 2)

colnames(c1_df)

nrow(c1_df) # 114
nrow(c2_df) # 139

# How many borderline/clinical patients in each cluster?
length(which(c1_df$cbcl_nausea > 0))
length(which(c1_df$cbcl_dizzy > 0))
length(which(c1_df$cbcl_overtired > 0))
length(which(c1_df$cbcl_sleeping_more > 0))
length(which(c1_df$cbcl_sleeping_less > 0))
length(which(c1_df$cbcl_depress > 0))
length(which(c1_df$cbcl_anxiety > 0))
length(which(c1_df$cbcl_attention > 0))
length(which(c1_df$cbcl_aggressive > 0))

length(which(c2_df$cbcl_nausea > 0))
length(which(c2_df$cbcl_dizzy > 0))
length(which(c2_df$cbcl_overtired > 0))
length(which(c2_df$cbcl_sleeping_more > 0))
length(which(c2_df$cbcl_sleeping_less > 0))
length(which(c2_df$cbcl_depress > 0))
length(which(c2_df$cbcl_anxiety > 0))
length(which(c2_df$cbcl_attention > 0))
length(which(c2_df$cbcl_aggressive > 0))

# Proportions:
length(which(c1_df$cbcl_nausea > 0)) / nrow(c1_df) * 100
length(which(c1_df$cbcl_dizzy > 0)) / nrow(c1_df) * 100
length(which(c1_df$cbcl_overtired > 0)) / nrow(c1_df) * 100
length(which(c1_df$cbcl_sleeping_more > 0)) / nrow(c1_df) * 100
length(which(c1_df$cbcl_sleeping_less > 0)) / nrow(c1_df) * 100
length(which(c1_df$cbcl_depress > 0)) / nrow(c1_df) * 100
length(which(c1_df$cbcl_anxiety > 0)) / nrow(c1_df) * 100
length(which(c1_df$cbcl_attention > 0)) / nrow(c1_df) * 100
length(which(c1_df$cbcl_aggressive > 0)) / nrow(c1_df) * 100

length(which(c2_df$cbcl_nausea > 0)) / nrow(c2_df) * 100
length(which(c2_df$cbcl_dizzy > 0)) / nrow(c2_df) * 100
length(which(c2_df$cbcl_overtired > 0)) / nrow(c2_df) * 100
length(which(c2_df$cbcl_sleeping_more > 0)) / nrow(c2_df) * 100
length(which(c2_df$cbcl_sleeping_less > 0)) / nrow(c2_df) * 100
length(which(c2_df$cbcl_depress > 0)) / nrow(c2_df) * 100
length(which(c2_df$cbcl_anxiety > 0)) / nrow(c2_df) * 100
length(which(c2_df$cbcl_attention > 0)) / nrow(c2_df) * 100
length(which(c2_df$cbcl_aggressive > 0)) / nrow(c2_df) * 100


```

## Label propagation
```{r}
library(SNFtool)

# Now for my demo version lol
as_mtbi_loc <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/as_mtbi_loc_imp.csv")))
as_mtbi_mechanism <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/as_mtbi_mechanism_imp.csv")))
as_mtbi_mem_daze <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/as_mtbi_mem_daze_imp.csv")))
d_income <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/d_income_imp.csv")))
d_interview_age <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/d_interview_age_imp.csv")))
d_mtbi_age <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/d_mtbi_age_imp.csv")))
d_pubertal_status <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/d_pubertal_status_imp.csv")))
d_race <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/d_race_imp.csv")))
d_sex <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/d_sex_imp.csv")))
mh_headaches <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/mh_headaches_imp.csv")))
mh_mtbi_count <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/mh_mtbi_count_imp.csv")))
dm_wmndf_qc <-
    stats::na.omit(read_csv(here("data/abcd/inputs/pre-imputation/dm_wmndf_qc.csv")))
rm_gord_cor_qc <-
    stats::na.omit(read_csv(here("data/abcd/inputs/pre-imputation/rm_gord_cor_qc.csv")))
rm_gord_var_qc <-
    stats::na.omit(read_csv(here("data/abcd/inputs/pre-imputation/rm_gord_var_qc.csv")))
rm_subc_cor_qc <-
    stats::na.omit(read_csv(here("data/abcd/inputs/pre-imputation/rm_subc_cor_qc.csv")))
rm_subc_var_qc <-
    stats::na.omit(read_csv(here("data/abcd/inputs/pre-imputation/rm_subc_var_qc.csv")))
sm_cort_sa_qc <-
    stats::na.omit(read_csv(here("data/abcd/inputs/pre-imputation/sm_cort_sa_qc.csv")))
sm_cort_t_qc <-
    stats::na.omit(read_csv(here("data/abcd/inputs/pre-imputation/sm_cort_t_qc.csv")))
sm_subc_v_qc <-
    stats::na.omit(read_csv(here("data/abcd/inputs/pre-imputation/sm_subc_v_qc.csv")))
p_loneliness <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/p_loneliness_imp.csv")))
p_screen_time <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/p_screen_time_imp.csv")))
p_family_function <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/p_family_function_imp.csv")))
p_sports <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/p_sports_imp.csv")))
p_prosocial <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/p_prosocial_imp.csv")))
p_parent_psych <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/p_parent_psych_imp.csv")))
p_exercise <-
    stats::na.omit(read_csv(here("data/abcd/inputs/post-imputation/p_exercise_imp.csv")))
# Outcomes
cbcl_headaches <-
    stats::na.omit(read_csv(here("data/abcd/outputs/post-imputation/cbcl_headaches_imp.csv")))
cbcl_nausea <-
    stats::na.omit(read_csv(here("data/abcd/outputs/post-imputation/cbcl_nausea_imp.csv")))
cbcl_vomiting <-
    stats::na.omit(read_csv(here("data/abcd/outputs/post-imputation/cbcl_vomiting_imp.csv")))
cbcl_dizzy <-
    stats::na.omit(read_csv(here("data/abcd/outputs/post-imputation/cbcl_dizzy_imp.csv")))
cbcl_overtired <-
    stats::na.omit(read_csv(here("data/abcd/outputs/post-imputation/cbcl_overtired_imp.csv")))
cbcl_sleeping_more <-
    stats::na.omit(read_csv(here("data/abcd/outputs/post-imputation/cbcl_sleeping_more_imp.csv")))
cbcl_sleeping_less <-
    stats::na.omit(read_csv(here("data/abcd/outputs/post-imputation/cbcl_sleeping_less_imp.csv")))
cbcl_depress_r <-
    stats::na.omit(read_csv(here("data/abcd/outputs/post-imputation/cbcl_depress_r_imp.csv")))
cbcl_anxiety_r <-
    stats::na.omit(read_csv(here("data/abcd/outputs/post-imputation/cbcl_anxiety_r_imp.csv")))
cbcl_attention_r <-
    stats::na.omit(read_csv(here("data/abcd/outputs/post-imputation/cbcl_attention_r_imp.csv")))
cbcl_aggressive_r <-
    stats::na.omit(read_csv(here("data/abcd/outputs/post-imputation/cbcl_aggressive_r_imp.csv")))
sds_sleep <-
    stats::na.omit(read_csv(here("data/abcd/outputs/post-imputation/sds_sleep_imp.csv")))
nihtbx_list_fc <-
    stats::na.omit(read_csv(here("data/abcd/outputs/post-imputation/nihtbx_list_fc_imp.csv")))
nihtbx_pattern_fc <-
    stats::na.omit(read_csv(here("data/abcd/outputs/post-imputation/nihtbx_pattern_fc_imp.csv")))
nihtbx_cardsort_fc <-
    stats::na.omit(read_csv(here("data/abcd/outputs/post-imputation/nihtbx_cardsort_fc_imp.csv")))

cbcl_depress <- cbcl_depress_r |>
    dplyr::mutate(cbcl_depress = dplyr::case_when(
        cbcl_depress_r < depress_threshold_borderline ~ 0,
        cbcl_depress_r < depress_threshold_clinical ~ 1,
        TRUE ~ 2)) |>
    dplyr::select("subjectkey", "cbcl_depress")
cbcl_anxiety <- cbcl_anxiety_r |>
    dplyr::mutate(cbcl_anxiety = dplyr::case_when(
        cbcl_anxiety_r < anxiety_threshold_borderline ~ 0,
        cbcl_anxiety_r < anxiety_threshold_clinical ~ 1,
        TRUE ~ 2)) |>
    dplyr::select("subjectkey", "cbcl_anxiety")
cbcl_attention <- cbcl_attention_r |>
    dplyr::mutate(cbcl_attention = dplyr::case_when(
        cbcl_attention_r < attention_threshold_borderline ~ 0,
        cbcl_attention_r < attention_threshold_clinical ~ 1,
        TRUE ~ 2)) |>
    dplyr::select("subjectkey", "cbcl_attention")
cbcl_aggressive <- cbcl_aggressive_r |>
    dplyr::mutate(cbcl_aggressive = dplyr::case_when(
        cbcl_aggressive_r < aggressive_threshold_borderline ~ 0,
        cbcl_aggressive_r < aggressive_threshold_clinical ~ 1,
        TRUE ~ 2)) |>
    dplyr::select("subjectkey", "cbcl_aggressive")

as_mtbi_loc_test <- as_mtbi_loc[as_mtbi_loc$subjectkey %in% testing_subs, ]
as_mtbi_mechanism_test <- as_mtbi_mechanism[as_mtbi_mechanism$subjectkey %in% testing_subs, ]
as_mtbi_mem_daze_test <- as_mtbi_mem_daze[as_mtbi_mem_daze$subjectkey %in% testing_subs, ]
d_income_test <- d_income[d_income$subjectkey %in% testing_subs, ]
d_interview_age_test <- d_interview_age[d_interview_age$subjectkey %in% testing_subs, ]
d_mtbi_age_test <- d_mtbi_age[d_mtbi_age$subjectkey %in% testing_subs, ]
d_pubertal_status_test <- d_pubertal_status[d_pubertal_status$subjectkey %in% testing_subs, ]
d_race_test <- d_race[d_race$subjectkey %in% testing_subs, ]
mh_headaches_test <- mh_headaches[mh_headaches$subjectkey %in% testing_subs, ]
mh_mtbi_count_test <- mh_mtbi_count[mh_mtbi_count$subjectkey %in% testing_subs, ]
rm_gord_cor_qc_test <- rm_gord_cor_qc[rm_gord_cor_qc$subjectkey %in% testing_subs, ]
rm_gord_var_qc_test <- rm_gord_var_qc[rm_gord_var_qc$subjectkey %in% testing_subs, ]
rm_subc_cor_qc_test <- rm_subc_cor_qc[rm_subc_cor_qc$subjectkey %in% testing_subs, ]
rm_subc_var_qc_test <- rm_subc_var_qc[rm_subc_var_qc$subjectkey %in% testing_subs, ]
sm_cort_sa_qc_test <- sm_cort_sa_qc[sm_cort_sa_qc$subjectkey %in% testing_subs, ]
sm_cort_t_qc_test <- sm_cort_t_qc[sm_cort_t_qc$subjectkey %in% testing_subs, ]
sm_subc_v_qc_test <- sm_subc_v_qc[sm_subc_v_qc$subjectkey %in% testing_subs, ]
p_loneliness_test <- p_loneliness[p_loneliness$subjectkey %in% testing_subs, ]
p_screen_time_test <- p_screen_time[p_screen_time$subjectkey %in% testing_subs, ]
p_family_function_test <- p_family_function[p_family_function$subjectkey %in% testing_subs, ]
p_sports_test <- p_sports[p_sports$subjectkey %in% testing_subs, ]
p_prosocial_test <- p_prosocial[p_prosocial$subjectkey %in% testing_subs, ]
p_parent_psych_test <- p_parent_psych[p_parent_psych$subjectkey %in% testing_subs, ]
p_exercise_test <- p_exercise[p_exercise$subjectkey %in% testing_subs, ]
cbcl_headaches_test <- cbcl_headaches[cbcl_headaches$subjectkey %in% testing_subs, ]
cbcl_nausea_test <- cbcl_nausea[cbcl_nausea$subjectkey %in% testing_subs, ]
cbcl_vomiting_test <- cbcl_vomiting[cbcl_vomiting$subjectkey %in% testing_subs, ]
cbcl_dizzy_test <- cbcl_dizzy[cbcl_dizzy$subjectkey %in% testing_subs, ]
cbcl_overtired_test <- cbcl_overtired[cbcl_overtired$subjectkey %in% testing_subs, ]
cbcl_sleeping_more_test <- cbcl_sleeping_more[cbcl_sleeping_more$subjectkey %in% testing_subs, ]
cbcl_sleeping_less_test <- cbcl_sleeping_less[cbcl_sleeping_less$subjectkey %in% testing_subs, ]
cbcl_depress_r_test <- cbcl_depress_r[cbcl_depress_r$subjectkey %in% testing_subs, ]
cbcl_anxiety_r_test <- cbcl_anxiety_r[cbcl_anxiety_r$subjectkey %in% testing_subs, ]
cbcl_attention_r_test <- cbcl_attention_r[cbcl_attention_r$subjectkey %in% testing_subs, ]
cbcl_aggressive_r_test <- cbcl_aggressive_r[cbcl_aggressive_r$subjectkey %in% testing_subs, ]
sds_sleep_test <- sds_sleep[sds_sleep$subjectkey %in% testing_subs, ]

as_mtbi_loc_train <- as_mtbi_loc[as_mtbi_loc$subjectkey %in% training_subs, ]
as_mtbi_mechanism_train <- as_mtbi_mechanism[as_mtbi_mechanism$subjectkey %in% training_subs, ]
as_mtbi_mem_daze_train <- as_mtbi_mem_daze[as_mtbi_mem_daze$subjectkey %in% training_subs, ]
d_income_train <- d_income[d_income$subjectkey %in% training_subs, ]
d_interview_age_train <- d_interview_age[d_interview_age$subjectkey %in% training_subs, ]
d_mtbi_age_train <- d_mtbi_age[d_mtbi_age$subjectkey %in% training_subs, ]
d_pubertal_status_train <- d_pubertal_status[d_pubertal_status$subjectkey %in% training_subs, ]
d_race_train <- d_race[d_race$subjectkey %in% training_subs, ]
mh_headaches_train <- mh_headaches[mh_headaches$subjectkey %in% training_subs, ]
mh_mtbi_count_train <- mh_mtbi_count[mh_mtbi_count$subjectkey %in% training_subs, ]
rm_gord_cor_qc_train <- rm_gord_cor_qc[rm_gord_cor_qc$subjectkey %in% training_subs, ]
rm_gord_var_qc_train <- rm_gord_var_qc[rm_gord_var_qc$subjectkey %in% training_subs, ]
rm_subc_cor_qc_train <- rm_subc_cor_qc[rm_subc_cor_qc$subjectkey %in% training_subs, ]
rm_subc_var_qc_train <- rm_subc_var_qc[rm_subc_var_qc$subjectkey %in% training_subs, ]
sm_cort_sa_qc_train <- sm_cort_sa_qc[sm_cort_sa_qc$subjectkey %in% training_subs, ]
sm_cort_t_qc_train <- sm_cort_t_qc[sm_cort_t_qc$subjectkey %in% training_subs, ]
sm_subc_v_qc_train <- sm_subc_v_qc[sm_subc_v_qc$subjectkey %in% training_subs, ]
p_loneliness_train <- p_loneliness[p_loneliness$subjectkey %in% training_subs, ]
p_screen_time_train <- p_screen_time[p_screen_time$subjectkey %in% training_subs, ]
p_family_function_train <- p_family_function[p_family_function$subjectkey %in% training_subs, ]
p_sports_train <- p_sports[p_sports$subjectkey %in% training_subs, ]
p_prosocial_train <- p_prosocial[p_prosocial$subjectkey %in% training_subs, ]
p_parent_psych_train <- p_parent_psych[p_parent_psych$subjectkey %in% training_subs, ]
p_exercise_train <- p_exercise[p_exercise$subjectkey %in% training_subs, ]
cbcl_headaches_train <- cbcl_headaches[cbcl_headaches$subjectkey %in% training_subs, ]
cbcl_nausea_train <- cbcl_nausea[cbcl_nausea$subjectkey %in% training_subs, ]
cbcl_vomiting_train <- cbcl_vomiting[cbcl_vomiting$subjectkey %in% training_subs, ]
cbcl_dizzy_train <- cbcl_dizzy[cbcl_dizzy$subjectkey %in% training_subs, ]
cbcl_overtired_train <- cbcl_overtired[cbcl_overtired$subjectkey %in% training_subs, ]
cbcl_sleeping_more_train <- cbcl_sleeping_more[cbcl_sleeping_more$subjectkey %in% training_subs, ]
cbcl_sleeping_less_train <- cbcl_sleeping_less[cbcl_sleeping_less$subjectkey %in% training_subs, ]
cbcl_depress_r_train <- cbcl_depress_r[cbcl_depress_r$subjectkey %in% training_subs, ]
cbcl_anxiety_r_train <- cbcl_anxiety_r[cbcl_anxiety_r$subjectkey %in% training_subs, ]
cbcl_attention_r_train <- cbcl_attention_r[cbcl_attention_r$subjectkey %in% training_subs, ]
cbcl_aggressive_r_train <- cbcl_aggressive_r[cbcl_aggressive_r$subjectkey %in% training_subs, ]
sds_sleep_train <- sds_sleep[sds_sleep$subjectkey %in% training_subs, ]

# Begin label propagation: https://rdrr.io/cran/SNFtool/src/R/groupPredict.r
groups <- clusters$cluster

as_mtbi_loc_full <- rbind(as_mtbi_loc_train, as_mtbi_loc_test)
as_mtbi_mechanism_full <- rbind(as_mtbi_mechanism_train, as_mtbi_mechanism_test)
as_mtbi_mem_daze_full <- rbind(as_mtbi_mem_daze_train, as_mtbi_mem_daze_test)
d_income_full <- rbind(d_income_train, d_income_test)
d_interview_age_full <- rbind(d_interview_age_train, d_interview_age_test)
d_mtbi_age_full <- rbind(d_mtbi_age_train, d_mtbi_age_test)
d_pubertal_status_full <- rbind(d_pubertal_status_train, d_pubertal_status_test)
d_race_full <- rbind(d_race_train, d_race_test)
mh_headaches_full <- rbind(mh_headaches_train, mh_headaches_test)
mh_mtbi_count_full <- rbind(mh_mtbi_count_train, mh_mtbi_count_test)
rm_gord_cor_qc_full <- rbind(rm_gord_cor_qc_train, rm_gord_cor_qc_test)
rm_gord_var_qc_full <- rbind(rm_gord_var_qc_train, rm_gord_var_qc_test)
rm_subc_cor_qc_full <- rbind(rm_subc_cor_qc_train, rm_subc_cor_qc_test)
rm_subc_var_qc_full <- rbind(rm_subc_var_qc_train, rm_subc_var_qc_test)
sm_cort_sa_qc_full <- rbind(sm_cort_sa_qc_train, sm_cort_sa_qc_test)
sm_cort_t_qc_full <- rbind(sm_cort_t_qc_train, sm_cort_t_qc_test)
sm_subc_v_qc_full <- rbind(sm_subc_v_qc_train, sm_subc_v_qc_test)
p_loneliness_full <- rbind(p_loneliness_train, p_loneliness_test)
p_screen_time_full <- rbind(p_screen_time_train, p_screen_time_test)
p_family_function_full <- rbind(p_family_function_train, p_family_function_test)
p_sports_full <- rbind(p_sports_train, p_sports_test)
p_prosocial_full <- rbind(p_prosocial_train, p_prosocial_test)
p_parent_psych_full <- rbind(p_parent_psych_train, p_parent_psych_test)
p_exercise_full <- rbind(p_exercise_train, p_exercise_test)

full_data_list <- generate_data_list(
                                mtbi_loc = as_mtbi_loc_full,
                                mtbi_mechanism = as_mtbi_mechanism_full,
                                mtbi_mem_daze = as_mtbi_mem_daze_full,
                                income = d_income_full,
                                interview_age = d_interview_age_full,
                                mtbi_age = d_mtbi_age_full,
                                pubertal_status = d_pubertal_status_full,
                                race = d_race_full,
                                headaches = mh_headaches_full,
                                mtbi_count = mh_mtbi_count_full,
                                gord_cor = rm_gord_cor_qc_full,
                                gord_var = rm_gord_var_qc_full,
                                subc_cor = rm_subc_cor_qc_full,
                                subc_var = rm_subc_var_qc_full,
                                cort_sa = sm_cort_sa_qc_full,
                                cort_t = sm_cort_t_qc_full,
                                subc_v = sm_subc_v_qc_full,
                                loneliness = p_loneliness_full,
                                screen_time = p_screen_time_full,
                                family_function = p_family_function_full,
                                sports = p_sports_full,
                                prosocial = p_prosocial_full,
                                parent_psych = p_parent_psych_full,
                                exercise = p_exercise_full)
    

sdl(full_data_list)

full_dist_list <- lapply(full_data_list,
    function(x) {
        get_dist_matrix(df = x$"data", input_type = x$"type")
    })

full_sim_list <- lapply(full_dist_list,
    function(x) {
        SNFtool::affinityMatrix(x, K = 19, sigma = 0.8)
    })

full_fused_network <- SNFtool::SNF(full_sim_list, K = 19)

Y0 <- matrix(0, nrow(full_fused_network), max(groups))

for (i in 1:length(groups)){
    Y0[i,groups[i]] <- 1
}


## Need their internal prediction function:
.csPrediction <- function(W,Y0,method){
  ###This function implements the label propagation to predict the label(subtype) for new patients.	
  ### note method is an indicator of which semi-supervised method to use
  # method == 0 indicates to use the local and global consistency method
  # method >0 indicates to use label propagation method.
  alpha=0.9;
  P= W/rowSums(W)
  if(method==0){
    Y= (1-alpha)* solve( diag(dim(P)[1])- alpha*P)%*%Y0;
  } else {
    NLabel=which(rowSums(Y0)==0)[1]-1;
    Y=Y0;
    for (i in 1:1000){
      Y=P%*%Y;
      Y[1:NLabel,]=Y0[1:NLabel,];
    }
  }
  return(Y);
}
### End of their internal function
Y <- .csPrediction(W = full_fused_network,Y0,method = TRUE)

newgroups <- rep(0,nrow(full_fused_network))
for (i in 1:nrow(Y)){
    newgroups[i] <- which(Y[i,] == max(Y[i,]))
}

newgroups

full_clusters <- as_mtbi_loc_full[, "subjectkey"]
full_clusters$cluster <- newgroups

full_clusters

labeled_test <- full_clusters[full_clusters$subjectkey %in% testing_subs, ]

test_evaluation_list <- list(
    labeled_test,
    cbcl_nausea,
    cbcl_vomiting,
    cbcl_dizzy,
    cbcl_overtired,
    cbcl_sleeping_more,
    cbcl_sleeping_less,
    cbcl_depress,
    cbcl_anxiety,
    cbcl_attention,
    cbcl_aggressive)

test_evaluation_df <- test_evaluation_list |>
    purrr::reduce(dplyr::inner_join, by = "subjectkey")

test_evaluation_df$cluster <- as.numeric(test_evaluation_df$cluster)

test_clusters <- test_evaluation_df |>
    dplyr::select("subjectkey", "cluster") |>
    data.frame()



# Using ordinal regression, the p-values are very low
ord_reg_p(test_clusters, cbcl_dizzy, "cbcl_dizzy") # 0.0001365547
ord_reg_p(test_clusters, cbcl_nausea, "cbcl_nausea") # 0.0001365547
ord_reg_p(test_clusters, cbcl_overtired, "cbcl_overtired")
ord_reg_p(test_clusters, cbcl_sleeping_more, "cbcl_sleeping_more")
ord_reg_p(test_clusters, cbcl_sleeping_less, "cbcl_sleeping_less")
ord_reg_p(test_clusters, cbcl_anxiety, "cbcl_anxiety")
ord_reg_p(test_clusters, cbcl_attention, "cbcl_attention")
ord_reg_p(test_clusters, cbcl_aggressive, "cbcl_aggressive")

c1_test_df <- test_evaluation_df |> dplyr::filter(cluster == 1)
c2_test_df <- test_evaluation_df |> dplyr::filter(cluster == 2)

colnames(c1_test_df)

nrow(c1_test_df) # 4
nrow(c2_test_df) # 63

# How many borderline/clinical patients in each cluster?
length(which(c1_test_df$cbcl_nausea > 0))
length(which(c1_test_df$cbcl_dizzy > 0))
length(which(c1_test_df$cbcl_overtired > 0))
length(which(c1_test_df$cbcl_sleeping_more > 0))
length(which(c1_test_df$cbcl_sleeping_less > 0))
length(which(c1_test_df$cbcl_depress > 0))
length(which(c1_test_df$cbcl_anxiety > 0))
length(which(c1_test_df$cbcl_attention > 0))
length(which(c1_test_df$cbcl_aggressive > 0))

length(which(c2_test_df$cbcl_nausea > 0))
length(which(c2_test_df$cbcl_dizzy > 0))
length(which(c2_test_df$cbcl_overtired > 0))
length(which(c2_test_df$cbcl_sleeping_more > 0))
length(which(c2_test_df$cbcl_sleeping_less > 0))
length(which(c2_test_df$cbcl_depress > 0))
length(which(c2_test_df$cbcl_anxiety > 0))
length(which(c2_test_df$cbcl_attention > 0))
length(which(c2_test_df$cbcl_aggressive > 0))

# Hm... I believe it is on to something.

length(which(c1_test_df$cbcl_nausea > 0)) / nrow(c1_test_df) * 100
length(which(c1_test_df$cbcl_dizzy > 0)) / nrow(c1_test_df) * 100
length(which(c1_test_df$cbcl_overtired > 0)) / nrow(c1_test_df) * 100
length(which(c1_test_df$cbcl_sleeping_more > 0)) / nrow(c1_test_df) * 100
length(which(c1_test_df$cbcl_sleeping_less > 0)) / nrow(c1_test_df) * 100
length(which(c1_test_df$cbcl_depress > 0)) / nrow(c1_test_df) * 100
length(which(c1_test_df$cbcl_anxiety > 0)) / nrow(c1_test_df) * 100
length(which(c1_test_df$cbcl_attention > 0)) / nrow(c1_test_df) * 100
length(which(c1_test_df$cbcl_aggressive > 0)) / nrow(c1_test_df) * 100

length(which(c2_test_df$cbcl_nausea > 0)) / nrow(c2_test_df) * 100
length(which(c2_test_df$cbcl_dizzy > 0)) / nrow(c2_test_df) * 100
length(which(c2_test_df$cbcl_overtired > 0)) / nrow(c2_test_df) * 100
length(which(c2_test_df$cbcl_sleeping_more > 0)) / nrow(c2_test_df) * 100
length(which(c2_test_df$cbcl_sleeping_less > 0)) / nrow(c2_test_df) * 100
length(which(c2_test_df$cbcl_depress > 0)) / nrow(c2_test_df) * 100
length(which(c2_test_df$cbcl_anxiety > 0)) / nrow(c2_test_df) * 100
length(which(c2_test_df$cbcl_attention > 0)) / nrow(c2_test_df) * 100
length(which(c2_test_df$cbcl_aggressive > 0)) / nrow(c2_test_df) * 100
# THIS IS WHERE I LEFT OFF ON THURSDAY AT 3 AM


# More rigorous random simulation based testing
c1_test_df
c2_test_df

c1_test_df$cbcl_total <- c1_test_df |>
    dplyr::select(dplyr::contains("cbcl")) |>
    rowSums()

c2_test_df$cbcl_total <- c2_test_df |>
    dplyr::select(dplyr::contains("cbcl")) |>
    rowSums()

c1_impaired_frac <- length(which(c1_test_df$cbcl_total > 0)) / nrow(c1_test_df)
c2_impaired_frac <- length(which(c2_test_df$cbcl_total > 0)) / nrow(c2_test_df)

true_diff <- c1_impaired_frac - c2_impaired_frac

true_diff

test_evaluation_df$cbcl_total <- test_evaluation_df |>
    dplyr::select(dplyr::contains("cbcl")) |>
    rowSums()

test_evaluation_df

# Trying to pull out random splits of the testing data
vector <- c()
set.seed(42)
for (i in 1:10000) {
    number_in_c1 <- sample.int(66, 1)
    c1_indices <- sample(67, size = number_in_c1)
    c2_indices <- which(!(1:67 %in% c1_indices))
    mock_c1_df <- test_evaluation_df[c1_indices, c("cluster", "cbcl_total")]
    mock_c2_df <- test_evaluation_df[c2_indices, c("cluster", "cbcl_total")]
    c1_impaired_frac <- length(which(mock_c1_df$cbcl_total > 0)) / nrow(mock_c1_df)
    c2_impaired_frac <- length(which(mock_c2_df$cbcl_total > 0)) / nrow(mock_c2_df)
    difference <- c1_impaired_frac - c2_impaired_frac
    vector <- c(vector, difference)
    if (is.nan(difference)) {
        print(c1_impaired_frac)
        print(c2_impaired_frac)
        print(number_in_c1)
    }
}
percentile <- ecdf(vector)
1 - percentile(true_diff) # The p-value
# This is an essential plot
hist(vector,col="gray",las=1,main="", breaks=30)
abline(v=true_diff,col="red")


true_diff


data=rnorm(1000)

# Get the density estimate
dens=density(vector)


# Plot y-values scaled by number of observations against x values
plot(dens$x,length(data)*dens$y,type="l",xlab="Value",ylab="Count estimate")


```

## Input variable characterization

```{r}

d_sex_train <- d_sex[d_sex$subjectkey %in% training_subs, ]

train_input_char <- list(clusters,
    as_mtbi_loc_train,
    as_mtbi_mechanism_train,
    as_mtbi_mem_daze_train,
    d_income_train,
    d_interview_age_train,
    d_mtbi_age_train,
    d_pubertal_status_train,
    d_race_train,
    d_sex_train,
    mh_headaches_train,
    mh_mtbi_count_train,
    p_loneliness_train,
    p_screen_time_train,
    p_family_function_train,
    p_sports_train,
    p_prosocial_train,
    p_parent_psych_train,
    p_exercise_train)



input_df <- train_input_char |>
    purrr::reduce(dplyr::inner_join, by = "subjectkey")

colnames(input_df)

c1in <- input_df[input_df$cluster == 1, ]
c2in <- input_df[input_df$cluster == 2, ]

# More females in c1
length(which(c1in$M == 0)) / length(c1in$M) # 46% F
length(which(c2in$M == 0)) / length(c2in$M) # 37% F

# NS
t.test(c1in$interview_age, c2in$interview_age)

# NS
t.test(c1in$latest_mtbi_age, c2in$latest_mtbi_age)

# More LOC in c1
length(which(c1in$latest_mtbi_loc == 1)) / length(c1in$latest_mtbi_loc) # 30%
length(which(c2in$latest_mtbi_loc == 1)) / length(c2in$latest_mtbi_loc) # 19%

# p = 2.06e-07; significantly higher pubertal status in c1
t.test(c1in$pubertal_status, c2in$pubertal_status)
# Note that age is not significantly different, but pubertal status is
# Expected given females go through puberty earlier?

# More concussions in C2? strange
t.test(c1in$mtbi_count, c2in$mtbi_count)


t.test(c1in$mtbi_count, c2in$mtbi_count)

# This is actually fire emoji
pvals <- c(
    t.test(c1in$asr_scr_perstr_r, c2in$asr_scr_perstr_r)$p.value,
    t.test(c1in$asr_scr_anxdep_r, c2in$asr_scr_anxdep_r)$p.value,
    t.test(c1in$asr_scr_withdrawn_r, c2in$asr_scr_withdrawn_r)$p.value,
    t.test(c1in$asr_scr_somatic_r, c2in$asr_scr_somatic_r)$p.value,
    t.test(c1in$asr_scr_thought_r, c2in$asr_scr_thought_r)$p.value,
    t.test(c1in$asr_scr_attention_r, c2in$asr_scr_attention_r)$p.value,
    t.test(c1in$asr_scr_aggressive_r, c2in$asr_scr_aggressive_r)$p.value,
    t.test(c1in$asr_scr_rulebreak_r, c2in$asr_scr_rulebreak_r)$p.value,
    t.test(c1in$asr_scr_intrusive_r, c2in$asr_scr_intrusive_r)$p.value,
    t.test(c1in$asr_scr_internal_r, c2in$asr_scr_internal_r)$p.value,
    t.test(c1in$asr_scr_external_r, c2in$asr_scr_external_r)$p.value,
    t.test(c1in$asr_scr_totprob_r, c2in$asr_scr_totprob_r)$p.value,
    t.test(c1in$asr_scr_depress_r, c2in$asr_scr_depress_r)$p.value,
    t.test(c1in$asr_scr_anxdisord_r, c2in$asr_scr_anxdisord_r)$p.value,
    t.test(c1in$asr_scr_somaticpr_r, c2in$asr_scr_somaticpr_r)$p.value,
    t.test(c1in$asr_scr_avoidant_r, c2in$asr_scr_avoidant_r)$p.value,
    t.test(c1in$asr_scr_adhd_r, c2in$asr_scr_adhd_r)$p.value,
    t.test(c1in$asr_scr_antisocial_r, c2in$asr_scr_antisocial_r)$p.value,
    t.test(c1in$asr_scr_inattention_r, c2in$asr_scr_inattention_r)$p.value,
    t.test(c1in$asr_scr_hyperactive_r, c2in$asr_scr_hyperactive_r)$p.value)

mean(pvals)

physical_activity1_y
physical_activity2_y

```





## NMI
```{r}
# Below is the NMI function I previously redefined
# full_cluster: the spectral clustering results of the full post-SNF graph
# inputs: a list of each dataframe (not affinity or distance matrix) used
# distance measures: a list of distance functions that map to inputs
rankFeaturesByNMI <- function(
    total_clustering, input_list, distance_measure_list, num_clusters,
    k_val, a_val) {
    # Dataframe to store the NMI of each feature from each input
    results_df <- data.frame(
        input = integer(),
        feature = integer(),
        nmi = double(),
        stringsAsFactors=FALSE)
    # Iterate through each feature of each input and calculate NMI
    for (input_num in seq_along(input_list)) {
        for (feature_num in seq_along(input_list[[input_num]])) {
            # Some pretty printing
            cat(paste0(
                "\nCalculating ", "input ", input_num, "/" ,
                length(input_list), ", ", "feature ", feature_num, "/",
                length(input_list[[input_num]]), "..."))
            # NMI calculation
            distance_measure <- distance_measure_list[[input_num]]
            input <- inputs[[input_num]]
            feature <- input[[feature_num]]
            d_matrix <- distance_measure(feature)
            a_matrix <- affinityMatrix(d_matrix, k_val, a_val)
            feature_clustering <- spectralClustering(a_matrix, num_clusters)
            nmi <- calNMI(total_clustering, feature_clustering)
            # Add the results to the output dataframe
            feature_name <- colnames(input_list[[input_num]])[feature_num]
            results_df[nrow(results_df) + 1,] =
                list(
                    input_num,
                    feature_name,
                    nmi)
        }
    }
    ordered_results_df <- results_df |>
        arrange(desc(nmi))
    return(ordered_results_df)
}



```




## Manual sanity check of clustering results

```{r}

dm_reordered[1, ] # A row that should work very effectively

om_reordered[1, ]$mean_p_val
om_reordered[1, ]$min_p_val

sdl(data_list)

# No sex or wmndf
as_mtbi_loc
as_mtbi_mechanism
as_mtbi_mem_daze
d_income
d_interview_age
d_mtbi_age
d_pubertal_status
d_race
mh_headaches
mh_mtbi_count
rm_gord_cor_qc
rm_gord_var_qc
rm_subc_cor_qc
rm_subc_var_qc
sm_cort_sa_qc
sm_cort_t_qc
sm_subc_v_qc
p_loneliness
p_screen_time
p_family_function
p_sports
p_prosocial
p_parent_psych
p_exercise
    

# Structure containing all outcome data
outcome_list <- generate_outcome_list(cbcl_headaches = cbcl_headaches,
                                      cbcl_nausea = cbcl_nausea,
                                      cbcl_vomiting = cbcl_vomiting,
                                      cbcl_dizzy = cbcl_dizzy,
                                      cbcl_overtired = cbcl_overtired,
                                      cbcl_sleeping_more = cbcl_sleeping_more,
                                      cbcl_sleeping_less = cbcl_sleeping_less,
                                      cbcl_depress_r = cbcl_depress,
                                      cbcl_anxiety_r = cbcl_anxiety,
                                      cbcl_attention_r = cbcl_attention,
                                      cbcl_aggressive_r = cbcl_aggressive,
                                      sds_sleep = sds_sleep)


```



