# Loading Data

```{r eval = FALSE}
library(dplyr)# {{{
library(abcdutils)
library(scabcd)
library(readr)
library(here)
library(ggplot2)
library(pheatmap)

# Function to import data from carbon
load_data <- function(filename, type, imputed = TRUE) {
    if (imputed) {
        impute_str <- "post-imputation/"
    } else {
        impute_str <- "pre-imputation/"
    }
    df <- read_csv(here(paste0("data/abcd/", type, "/", impute_str, filename)),
        show_col_types = FALSE)
    return(stats::na.omit(df))
}

abcd_ggsave <- function(filename, saved_plot) {
    filename <- here(paste0("data/abcd/results/figures/", filename))
    print(filename)
    ggsave(filename, saved_plot)
}

abcd_pheatmapsave <- function(filename, matrix) {
    filename <- here(paste0("data/abcd/results/figures/", filename))
    print(filename)
    pheatmap(matrix, filename = filename)
}

img_path <- function(filename) {
    img_folder <- here(paste0("data/abcd/results/figures/"))
    img_path <- paste0(img_folder, filename)
    return(img_path)
}

# The better function
image_path <- function(filename, date = NULL) {
    image_folder <- here(paste0("data/abcd/results/figures/"))
    if (is.null(date)) {
        date <- gsub("-", "_", Sys.Date())
    }
    date <- paste0(date, "_")
    image_path <- paste0(image_folder, date, filename)
    return(image_path)
}

data_path <- function(filename, date = NULL) {
    data_folder <- here(paste0("data/abcd/results/processed/"))
    if (is.null(date)) {
        date <- gsub("-", "_", Sys.Date())
    }
    date <- paste0(date, "_")
    data_path <- paste0(data_folder, date, filename)
    return(data_path)
}



# Importing data
as_mtbi_loc <- load_data("as_mtbi_loc_imp.csv", type = "inputs")
as_mtbi_mechanism <- load_data("as_mtbi_mechanism_imp.csv", type = "inputs")
as_mtbi_mem_daze <- load_data("as_mtbi_mem_daze_imp.csv", type = "inputs")
d_income <- load_data("d_income_imp.csv", type = "inputs")
d_interview_age <- load_data("d_interview_age_imp.csv", type = "inputs")
d_mtbi_age <- load_data("d_mtbi_age_imp.csv", type = "inputs")
d_pubertal_status <- load_data("d_pubertal_status_imp.csv", type = "inputs")
d_race <- load_data("d_race_imp.csv", type = "inputs")
d_sex <- load_data("d_sex_imp.csv", type = "inputs")
mh_headaches <- load_data("mh_headaches_imp.csv", type = "inputs")
mh_mtbi_count <- load_data("mh_mtbi_count_imp.csv", type = "inputs")
dm_wmndf_qc <- load_data("dm_wmndf_qc.csv", imputed = FALSE, type = "inputs")
rm_gord_cor_qc <-
    load_data("rm_gord_cor_qc.csv", imputed = FALSE, type = "inputs")
rm_gord_var_qc <-
    load_data("rm_gord_var_qc.csv", imputed = FALSE, type = "inputs")
rm_subc_cor_qc <-
    load_data("rm_subc_cor_qc.csv", imputed = FALSE, type = "inputs")
rm_subc_var_qc <-
    load_data("rm_subc_var_qc.csv", imputed = FALSE, type = "inputs")
sm_cort_sa_qc <-
    load_data("sm_cort_sa_qc.csv", imputed = FALSE, type = "inputs")
sm_cort_t_qc <-
    load_data("sm_cort_t_qc.csv", imputed = FALSE, type = "inputs")
sm_subc_v_qc <-
    load_data("sm_subc_v_qc.csv", imputed = FALSE, type = "inputs")
p_loneliness <- load_data("p_loneliness_imp.csv", type = "inputs")
p_screen_time <- load_data("p_screen_time_imp.csv", type = "inputs")
p_family_function <- load_data("p_family_function_imp.csv", type = "inputs")
p_sports <- load_data("p_sports_imp.csv", type = "inputs")
p_prosocial <- load_data("p_prosocial_imp.csv", type = "inputs")
p_parent_psych <- load_data("p_parent_psych_imp.csv", type = "inputs")
p_exercise <- load_data("p_exercise_imp.csv", type = "inputs")
# Outcomes
cbcl_headaches <- load_data("cbcl_headaches_imp.csv", type = "outputs")
cbcl_nausea <- load_data("cbcl_nausea_imp.csv", type = "outputs")
cbcl_vomiting <- load_data("cbcl_vomiting_imp.csv", type = "outputs")
cbcl_dizzy <- load_data("cbcl_dizzy_imp.csv", type = "outputs")
cbcl_overtired <- load_data("cbcl_overtired_imp.csv", type = "outputs")
cbcl_sleeping_more <- load_data("cbcl_sleeping_more_imp.csv", type = "outputs")
cbcl_sleeping_less <- load_data("cbcl_sleeping_less_imp.csv", type = "outputs")
cbcl_depress <- load_data("cbcl_depress_imp.csv", type = "outputs")
cbcl_anxiety <- load_data("cbcl_anxiety_imp.csv", type = "outputs")
cbcl_attention <- load_data("cbcl_attention_imp.csv", type = "outputs")
cbcl_aggressive <- load_data("cbcl_aggressive_imp.csv", type = "outputs")
sds_sleep <- load_data("sds_sleep_imp.csv", type = "outputs")
nihtbx_list_fc <- load_data("nihtbx_list_fc_imp.csv", type = "outputs")
nihtbx_pattern_fc <- load_data("nihtbx_pattern_fc_imp.csv", type = "outputs")
nihtbx_cardsort_fc <- load_data("nihtbx_cardsort_fc_imp.csv", type = "outputs")

# Filtering to common subjects
full_df_list <- list(mtbi_loc = as_mtbi_loc,
    as_mtbi_mechanism,
    as_mtbi_mem_daze,
    d_income,
    d_interview_age,
    d_mtbi_age,
    d_pubertal_status,
    d_race,
    d_sex,
    mh_headaches,
    mh_mtbi_count,
    dm_wmndf_qc,
    rm_gord_cor_qc,
    rm_gord_var_qc,
    rm_subc_cor_qc,
    rm_subc_var_qc,
    sm_cort_sa_qc,
    sm_cort_t_qc,
    sm_subc_v_qc,
    p_loneliness,
    p_screen_time,
    p_family_function,
    p_sports,
    p_prosocial,
    p_parent_psych,
    p_exercise,
    cbcl_headaches,
    cbcl_nausea,
    cbcl_vomiting,
    cbcl_dizzy,
    cbcl_overtired,
    cbcl_sleeping_more,
    cbcl_sleeping_less,
    cbcl_depress,
    cbcl_anxiety,
    cbcl_attention,
    cbcl_aggressive,
    sds_sleep)

shared_df <- full_df_list |> purrr::reduce(dplyr::inner_join, by = "subjectkey")

common_subs <- shared_df$subjectkey

# Splitting into training and testing sets
assigned_df <- train_test_assign(train_frac = 0.8, subjects = common_subs)


# Keep only the training set
# TO-DO: rename these to train later
as_mtbi_loc <- keep_split(as_mtbi_loc, assigned_df, "train")
as_mtbi_mechanism <- keep_split(as_mtbi_mechanism, assigned_df, "train")
as_mtbi_mem_daze <- keep_split(as_mtbi_mem_daze, assigned_df, "train")
d_income <- keep_split(d_income, assigned_df, "train")
d_interview_age <- keep_split(d_interview_age, assigned_df, "train")
d_mtbi_age <- keep_split(d_mtbi_age, assigned_df, "train")
d_pubertal_status <- keep_split(d_pubertal_status, assigned_df, "train")
d_race <- keep_split(d_race, assigned_df, "train")
d_sex <- keep_split(d_sex, assigned_df, "train")
mh_headaches <- keep_split(mh_headaches, assigned_df, "train")
mh_mtbi_count <- keep_split(mh_mtbi_count, assigned_df, "train")
dm_wmndf_qc <- keep_split(dm_wmndf_qc, assigned_df, "train")
rm_gord_cor_qc <- keep_split(rm_gord_cor_qc, assigned_df, "train")
rm_gord_var_qc <- keep_split(rm_gord_var_qc, assigned_df, "train")
rm_subc_cor_qc <- keep_split(rm_subc_cor_qc, assigned_df, "train")
rm_subc_var_qc <- keep_split(rm_subc_var_qc, assigned_df, "train")
sm_cort_sa_qc <- keep_split(sm_cort_sa_qc, assigned_df, "train")
sm_cort_t_qc <- keep_split(sm_cort_t_qc, assigned_df, "train")
sm_subc_v_qc <- keep_split(sm_subc_v_qc, assigned_df, "train")
p_loneliness <- keep_split(p_loneliness, assigned_df, "train")
p_screen_time <- keep_split(p_screen_time, assigned_df, "train")
p_family_function <- keep_split(p_family_function, assigned_df, "train")
p_sports <- keep_split(p_sports, assigned_df, "train")
p_prosocial <- keep_split(p_prosocial, assigned_df, "train")
p_parent_psych <- keep_split(p_parent_psych, assigned_df, "train")
p_exercise <- keep_split(p_exercise, assigned_df, "train")
cbcl_headaches <- keep_split(cbcl_headaches, assigned_df, "train")
cbcl_nausea <- keep_split(cbcl_nausea, assigned_df, "train")
cbcl_vomiting <- keep_split(cbcl_vomiting, assigned_df, "train")
cbcl_dizzy <- keep_split(cbcl_dizzy, assigned_df, "train")
cbcl_overtired <- keep_split(cbcl_overtired, assigned_df, "train")
cbcl_sleeping_more <- keep_split(cbcl_sleeping_more, assigned_df, "train")
cbcl_sleeping_less <- keep_split(cbcl_sleeping_less, assigned_df, "train")
cbcl_depress <- keep_split(cbcl_depress, assigned_df, "train")
cbcl_anxiety <- keep_split(cbcl_anxiety, assigned_df, "train")
cbcl_attention <- keep_split(cbcl_attention, assigned_df, "train")
cbcl_aggressive <- keep_split(cbcl_aggressive, assigned_df, "train")
sds_sleep <- keep_split(sds_sleep, assigned_df, "train")}}}
```

# SNF

## Alpha and K

In this section, 'default' settings (i.e., including all variables) are used to iterate through clustering solutions from different values of alpha and K.

```{r}
# Structure containing all input data# {{{
# These data should not contain any NAs, but need not have the same subjects
data_list <- generate_data_list(mtbi_loc = as_mtbi_loc,
                                mtbi_mechanism = as_mtbi_mechanism,
                                mtbi_mem_daze = as_mtbi_mem_daze,
                                income = d_income,
                                interview_age = d_interview_age,
                                mtbi_age = d_mtbi_age,
                                pubertal_status = d_pubertal_status,
                                race = d_race,
                                sex = d_sex,
                                headaches = mh_headaches,
                                mtbi_count = mh_mtbi_count,
                                wmndf = dm_wmndf_qc,
                                gord_cor = rm_gord_cor_qc,
                                gord_var = rm_gord_var_qc,
                                subc_cor = rm_subc_cor_qc,
                                subc_var = rm_subc_var_qc,
                                cort_sa = sm_cort_sa_qc,
                                cort_t = sm_cort_t_qc,
                                subc_v = sm_subc_v_qc,
                                loneliness = p_loneliness,
                                screen_time = p_screen_time,
                                family_function = p_family_function,
                                sports = p_sports,
                                prosocial = p_prosocial,
                                parent_psych = p_parent_psych,
                                exercise = p_exercise)

# Structure containing all outcome data
outcome_list <- generate_outcome_list(cbcl_nausea = cbcl_nausea,
                                      cbcl_vomiting = cbcl_vomiting,
                                      cbcl_dizzy = cbcl_dizzy,
                                      cbcl_overtired = cbcl_overtired,
                                      cbcl_sleeping_more = cbcl_sleeping_more,
                                      cbcl_sleeping_less = cbcl_sleeping_less,
                                      cbcl_depress = cbcl_depress,
                                      cbcl_anxiety = cbcl_anxiety,
                                      cbcl_attention = cbcl_attention,
                                      cbcl_aggressive = cbcl_aggressive)


# Builds a standard design matrix only exploring SNF hyperparameters alpha and K
design_matrix_ak <- build_design_matrix_ak()

# Assess clustering minimum p-value for an ordinal dependent variable
ak_scan_om <- execute_design_matrix(data_list, design_matrix_ak, outcome_list)

write_csv(ak_scan_om,
    here("data/abcd/results/processed/2023_02_17_ak_scan_om.csv"))

# Note that the column types will be different (and more accurate) when going
#  through the read_delim function. Without doing this, you will have a lot of
#  character columns.
ak_scan_om <-
    read_delim(here("data/abcd/results/processed/2023_02_17_ak_scan_om.csv"))

min(ak_scan_om$min_p_val)
min(ak_scan_om$mean_p_val)

ak_scan_om$nclust <- as.factor(ak_scan_om$nclust)

ak_scan_om

# Highlighting the point that used the most default settings
ak_default <- ak_scan_om |>
    dplyr::filter(K == 20, alpha == 0.5)

k_scan_plot <-
    ggplot(ak_scan_om,
        mapping = aes(x = min_p_val,
                      y = mean_p_val,
                      color = nclust,
                      size = K)) +
        geom_point(data = ak_default, colour = "pink", size = 6) +
        geom_point() +
        scale_x_continuous(trans = 'log10') +
        xlab("Minimum p-value") +
        ylab("Mean p-value") +
        theme_bw() +
        theme(text = element_text(size = 20))
k_scan_plot

abcd_ggsave("2023_02_20_k_scan_plot.png", k_scan_plot)

a_scan_plot <-
    ggplot(ak_scan_om,
        mapping = aes(x = min_p_val,
                      y = mean_p_val,
                      color = nclust,
                      size = alpha)) +
        geom_point(data = ak_default, colour = "pink", size = 7) +
        geom_point() +
        scale_x_continuous(trans = 'log10') +
        xlab("Minimum p-value") +
        ylab("Mean p-value") +
        theme_bw() +
        theme(text = element_text(size = 20))
a_scan_plot

abcd_ggsave("2023_02_20_a_scan_plot.png", a_scan_plot)


# Alternative visualizations
# Min-p-values
a_k_matrix_min <- matrix(nrow = length(unique(ak_scan_om$K)),
                     ncol = length(unique(ak_scan_om$alpha)))
colnames(a_k_matrix_min) <- as.character(seq(0.3, 1, by = 0.1))
rownames(a_k_matrix_min) <- as.character(seq(10, 100, by = 10))
for (i in seq_len(nrow(ak_scan_om))) {
    print(i)
   row <- as.character(ak_scan_om[i, "K"])
   col <- as.character(ak_scan_om[i, "alpha"])
   min_p <- as.numeric(ak_scan_om[i, "min_p_val"])
   a_k_matrix_min[row, col] <- min_p
}
pheatmap(a_k_matrix_min, cluster_rows = FALSE, cluster_cols = FALSE)

abcd_pheatmapsave("2023_02_20_a_k_matrix_min.png", a_k_matrix_min)

# Mean p-values
a_k_matrix_mean <- matrix(nrow = length(unique(ak_scan_om$K)),
                          ncol = length(unique(ak_scan_om$alpha)))
colnames(a_k_matrix_mean) <- as.character(seq(0.3, 1, by = 0.1))
rownames(a_k_matrix_mean) <- as.character(seq(10, 100, by = 10))
for (i in seq_len(nrow(ak_scan_om))) {
    print(i)
   row <- as.character(ak_scan_om[i, "K"])
   col <- as.character(ak_scan_om[i, "alpha"])
   mean_p <- as.numeric(ak_scan_om[i, "mean_p_val"])
   a_k_matrix_mean[row, col] <- mean_p
}
pheatmap(a_k_matrix_mean, cluster_rows = FALSE, cluster_cols = FALSE)

abcd_pheatmapsave("2023_02_20_a_k_matrix_mean.png", a_k_matrix_mean)# }}}
```


## Training set

```{r}
set.seed(42)# {{{
design_matrix_base <- build_design_matrix_base()
design_matrix <- add_design_matrix_rows(design_matrix_base, 100)

#write_csv(design_matrix,
#    here(paste0("data/abcd/results/processed/full_design_matrix.csv")))

output_matrix_full <-
    execute_design_matrix(data_list, design_matrix, outcome_list)

write_csv(output_matrix_full,
    here(paste0("data/abcd/results/processed/2023_02_22_om.csv")))

output_matrix_full <-
    read_delim(here(paste0("data/abcd/results/processed/2023_02_22_om.csv")))


min(output_matrix_full$min_p_val) #3.2 e-08
min(output_matrix_full$mean_p_val) #0.00414

mc_results <- meta_cluster(output_matrix_full)

write_csv(data.frame(mc_results), here(paste0("data/abcd/results/processed/",
    "2023_02_22_mc_results.csv")))

mc_results <- as.matrix(read_delim(
    here(paste0("data/abcd/results/processed/",
                "2023_02_22_mc_results.csv"))))

# That is extremely well-separated
colnames(mc_results) <- NULL
rownames(mc_results) <- NULL
pheatmap(mc_results,
    legend_breaks = c(0, 0.5, 1, max(mc_results)),
    main = "",
    legend_labels = c("0", "0.5", "1", "ARI\n\n"),
    legend = TRUE, border_color = FALSE)

# Same thing, but saving the file
colnames(mc_results) <- NULL
rownames(mc_results) <- NULL
pheatmap(mc_results,
    legend_breaks = c(0, 0.5, 1, max(mc_results)),
    main = "",
    legend_labels = c("0", "0.5", "1", "ARI\n\n"),
    legend = TRUE,
    border_color = FALSE,
    filename = img_path("2023_02_22_mc_results.png"),
    cellheight = 6,
    width = 10,
    height = 10)
dev.off()

# Pretty art
pheatmap(mc_results, cluster_rows = FALSE, cluster_cols = FALSE)

# Same thing, but saving the file
pheatmap(mc_results, cluster_rows = FALSE, cluster_cols = FALSE,
    filename = img_path("2023_02_22_mc_pretty.png"))
dev.off()

colnames(mc_results) <- as.character(seq_len(nrow(mc_results)))
rownames(mc_results) <- as.character(seq_len(nrow(mc_results))) # }}}
```

Make sure to remove headaches from the final list of examined outcomes, as it is basically an input


## Meta-clustering

```{r}
# Trying to plot the input design matrix as a heatmap# {{{
dm_scaled <- design_matrix
dm_scaled$row_id <- dm_scaled$row_id / max(dm_scaled$row_id)
dm_scaled$K <- dm_scaled$K / max(dm_scaled$K)
dm_scaled$alpha <- dm_scaled$alpha / max(dm_scaled$alpha)
dm_scaled$snf_scheme <- dm_scaled$snf_scheme / max(dm_scaled$snf_scheme)
dm_scaled$eigen_or_rot <- dm_scaled$eigen_or_rot / max(dm_scaled$eigen_or_rot)

out <- pheatmap(mc_results)

dm_scaled_reordered <- dm_scaled[out$tree_row[["order"]], ]

dm_reordered <- design_matrix[out$tree_row[["order"]], ]

# Heatmap of the design matrix
pheatmap(dm_scaled_reordered,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         labels_row = "",
         legend = FALSE,
         fontsize = 12)

# Same thing but saved to a file
pheatmap(dm_scaled_reordered,
    cluster_rows = FALSE,
    cluster_cols = FALSE,
    labels_row = "",
    legend = FALSE,
    fontsize = 12,
    filename = img_path("2023_02_22_dm.png"))
dev.off()

mc_pvals <- p_val_select(output_matrix_full)
mc_pvals_reordered <- mc_pvals[out$tree_row[["order"]], ]

# This is the actual important graph
pheatmap(mc_pvals_reordered,
    legend_breaks = c(0, 0.2, 0.4, 0.6, 0.8, max(mc_pvals_reordered)),
    main = "",
    color = colorRampPalette(
        RColorBrewer::brewer.pal(n = 7, name = "RdYlBu"))(100),
    legend_labels = c("0", "0.2", "0.4", "0.6", "0.8", "p-value\n\n"),
    cluster_rows = FALSE,
    legend = TRUE)

pheatmap(mc_pvals_reordered,
    legend_breaks = c(0, 0.2, 0.4, 0.6, 0.8, max(mc_pvals_reordered)),
    main = "",
    color = colorRampPalette(
        RColorBrewer::brewer.pal(n = 7, name = "RdYlBu"))(100),
    legend_labels = c("0", "0.2", "0.4", "0.6", "0.8", "p-value\n\n"),
    cluster_rows = FALSE,
    legend = TRUE,
    filename = image_path("mc_pvals.png"))
dev.off()
# }}}
```

## Distribution of cluster assignment

```{r}
# A selection based on the main visual meta cluster and the p-values# {{{
om_reordered <- output_matrix_full[out$tree_row[["order"]], ]
best_mc <- om_reordered[6:41, ]
best_mc_clusters <- as.matrix(subs(best_mc)[, -1])

# Visualization of cluster assignments
pheatmap(best_mc_clusters,
    cluster_rows = FALSE,
    show_rownames = FALSE,
    show_colnames = FALSE,
    legend = FALSE,
    cellwidth = 2.2)

pheatmap(best_mc_clusters,
    cluster_rows = FALSE,
    show_rownames = FALSE,
    show_colnames = FALSE,
    legend = FALSE,
    cellwidth = 2.2,
    filename = img_path("2023_02_22_cluster_assignment_heatmap.png"))
dev.off()

# Alternative visualizations
best_mc_subs <- best_mc |>
    dplyr::select(row_id, dplyr::starts_with("NDAR")) |>
    t()
colnames(best_mc_subs) <- best_mc_subs["row_id", ]
best_mc_subs <- best_mc_subs[2:nrow(best_mc_subs), ]
best_mc_subs <- as.data.frame(best_mc_subs)
best_mc_subs <- sapply(best_mc_subs, as.numeric)
row_means <- apply(X = best_mc_subs, MARGIN = 1, FUN = mean, na.rm = TRUE)
names(row_means) <- colnames(subs(best_mc))[-1]

# Shows how consistently a subject was assigned to a particular cluster
png(img_path("2023_02_22_avg_cluster.png"),
    height = 5,
    width = 5,
    units = "in",
    res = 300)
plot(row_means,
    xlab = "Subject",
    ylab = "Mean assigned cluster")
dev.off()


# Histogram form
png(img_path("2023_02_22_avg_cluster_hist.png"),
    height = 5,
    width = 5,
    units = "in",
    res = 300)
hist(row_means,
    xlab = "Mean assigned cluster",
    main = NULL)
dev.off()# }}}
```

## Choosing top solution

```{r}
om_reordered# {{{

# Next steps are to evaluate a few options:
# A consensus cluster row (nah)
# A row containing everybody
# Consensus cluster row without problematic patients
# A row containing everybody without problematic patients

# Or perhaps:
# 1. The consensus results
# 2. The best results

# Best MC Subs: finding some dm rows to work with
best_mc_df <- data.frame(best_mc_subs)
colnames(best_mc_df) <- colnames(best_mc_subs)
best_mc_df$subjectkey <- rownames(best_mc_df)
rownames(best_mc_df) <- NULL

# Choosing a row to characterize by p-value
best_mc_copy <- best_mc
best_mc_copy$inc_var_count <- best_mc_copy |>
    dplyr::select(dplyr::starts_with("inc")) |>
    rowSums()

ggplot(best_mc_copy,
    aes(x = min_p_val, y = mean_p_val, label = row_id,
        color = (inc_var_count == 25))) +
    geom_point() +
    scale_x_continuous(trans = "log10") +
    scale_y_continuous(trans = "log10") +
    geom_text(hjust = 0, vjust = 0) +
    xlab("Minimum CBCL log(p-value)") +
    ylab("Mean CBCL log(p-value)") +
    labs(color = "All variables included?") +
    theme_bw() +
    theme(text = element_text(size = 15))
# ggsave(img_path("2023_02_22_solutions_by_pvals.png"))

top_om_row <- best_mc[best_mc$row_id == 84, ] # just try this one based on graph
# }}}
```


## Finding the consensus cluster best row - Can do this later {{{

```{r}
# Let me now find the consensus clustering results
best_mc_df$mean_cluster <- best_mc_df |>
    dplyr::select(-subjectkey) |>
    rowMeans()

which(best_mc_df$mean_cluster == 1.5) # subjects 40 and 118 are exactly equally distributed to cluster 1 and 2


# Dataframe to calculate deviation of clustering solns from CC soln
distance_from_cc <- data.frame(row_id = as.character(best_mc$row_id))

best_mc_df

row_distances <- vector()
for (i in seq_len(nrow(distance_from_cc))) {
   dist <- mean((best_mc_df[, i] - best_mc_df$"mean_cluster")^2)
    row_distances <- c(row_distances, dist)
}

distance_from_cc$dist <- row_distances

distance_from_cc

best_mc$dist <- row_distances


ggplot(best_mc, aes(x = min_p_val, y = dist, label = row_id, color = dist)) +
  geom_point() +
  scale_x_continuous(trans = 'log10') +
  geom_text(hjust = 0, vjust = 0) +
  theme_bw()


# row 48 appears to also be the lowest distance from the cc solution
best_mc[which(best_mc$dist == min(row_distances)), ] # row 48

```
}}}

# Cluster characterization

## CBCL measures

```{r}
# Pick a row# {{{


om_row <- 34 # Corresponds to row_id 84, the lowest min/mean p value
best_mc$row_id[om_row] == 84


# DF with row_id and subjects as columns and cluster as rows)
clustered_subjects <- subs(best_mc[om_row, ])

clusters <- data.frame(t(clustered_subjects))
clusters$id <- rownames(clusters)
rownames(clusters) <- NULL
colnames(clusters) <- c("cluster", "subjectkey")
clusters <- clusters[2:nrow(clusters), ]
clusters

groups <- clusters$cluster
groups

outcome_list <- list(
    clusters,
    cbcl_nausea,
    cbcl_vomiting,
    cbcl_dizzy,
    cbcl_overtired,
    cbcl_sleeping_more,
    cbcl_sleeping_less,
    cbcl_depress,
    cbcl_anxiety,
    cbcl_attention,
    cbcl_aggressive)

comparison_df <-
    outcome_list |> purrr::reduce(dplyr::inner_join, by = "subjectkey")

comparison_df$cluster <- as.factor(comparison_df$cluster)

# Using ordinal regression, the p-values are very low
8 * ord_reg_p(clusters, cbcl_nausea, "cbcl_nausea") # 0.0001365547
8 * ord_reg_p(clusters, cbcl_dizzy, "cbcl_dizzy")
8 * ord_reg_p(clusters, cbcl_overtired, "cbcl_overtired")
8 * ord_reg_p(clusters, cbcl_sleeping_more, "cbcl_sleeping_more")
8 * ord_reg_p(clusters, cbcl_sleeping_less, "cbcl_sleeping_less")
8 * ord_reg_p(clusters, cbcl_anxiety, "cbcl_anxiety")
8 * ord_reg_p(clusters, cbcl_attention, "cbcl_attention")
8 * ord_reg_p(clusters, cbcl_aggressive, "cbcl_aggressive")

nausea_summary <- comparison_df |>
    group_by(cluster) |>
    count(cbcl_nausea) |>
    mutate(Percent = round(n / sum(n) * 100, 1))
nausea_summary$cbcl_nausea <-
    factor(nausea_summary$cbcl_nausea, levels = c("2", "1", "0"))
ggplot(nausea_summary,
    aes(x = cluster, y = Percent, fill = cbcl_nausea)) +
    geom_bar(stat = "identity", position = position_stack()) +
    geom_text(aes(label = paste(Percent, "%"), y = Percent),
            position = position_stack(vjust = 0.5)) +
    scale_y_continuous(expand = expansion(mult = c(0, .1))) +
    labs(x = "Cluster", y = "Percentage", fill = "CBCL Nausea Grade") +
    theme_bw() +
    theme(text = element_text(size = 20))
# ggsave(image_path("cbcl_nausea.png"), height = 6, dpi = 300)
# p = 0.015

dizzy_summary <- comparison_df |>
    group_by(cluster) |>
    count(cbcl_dizzy) |>
    mutate(Percent = round(n / sum(n) * 100, 1))
dizzy_summary$cbcl_dizzy <-
    factor(dizzy_summary$cbcl_dizzy, levels = c("2", "1", "0"))
ggplot(dizzy_summary,
    aes(x = cluster, y = Percent, fill = cbcl_dizzy)) +
    geom_bar(stat = "identity", position = position_stack()) +
    geom_text(aes(label = paste(Percent, "%"), y = Percent),
            position = position_stack(vjust = 0.5)) +
    scale_y_continuous(expand = expansion(mult = c(0, .1))) +
    labs(x = "Cluster", y = "Percentage", fill = "CBCL dizzy Grade") +
    theme_bw() +
    theme(text = element_text(size = 20))
ggsave(image_path("cbcl_dizzy.png"), height = 6, dpi = 300)
# p = 0.12 (NS)

overtired_summary <- comparison_df |>
    group_by(cluster) |>
    count(cbcl_overtired) |>
    mutate(Percent = round(n / sum(n) * 100, 1))
overtired_summary$cbcl_overtired <-
    factor(overtired_summary$cbcl_overtired, levels = c("2", "1", "0"))
ggplot(overtired_summary,
    aes(x = cluster, y = Percent, fill = cbcl_overtired)) +
    geom_bar(stat = "identity", position = position_stack()) +
    geom_text(aes(label = paste(Percent, "%"), y = Percent),
            position = position_stack(vjust = 0.5)) +
    scale_y_continuous(expand = expansion(mult = c(0, .1))) +
    labs(x = "Cluster", y = "Percentage", fill = "CBCL overtired Grade") +
    theme_bw() +
    theme(text = element_text(size = 20))
ggsave(image_path("cbcl_overtired.png"), height = 6, dpi = 300)
# p = 0.037

sleeping_more_summary <- comparison_df |>
    group_by(cluster) |>
    count(cbcl_sleeping_more) |>
    mutate(Percent = round(n / sum(n) * 100, 1))
sleeping_more_summary$cbcl_sleeping_more <-
    factor(sleeping_more_summary$cbcl_sleeping_more, levels = c("2", "1", "0"))
ggplot(sleeping_more_summary,
    aes(x = cluster, y = Percent, fill = cbcl_sleeping_more)) +
    geom_bar(stat = "identity", position = position_stack()) +
    geom_text(aes(label = paste(Percent, "%"), y = Percent),
            position = position_stack(vjust = 0.5)) +
    scale_y_continuous(expand = expansion(mult = c(0, .1))) +
    labs(x = "Cluster", y = "Percentage", fill = "CBCL sleeping_more Grade") +
    theme_bw() +
    theme(text = element_text(size = 20))
ggsave(image_path("cbcl_sleeping_more.png"), height = 6, dpi = 300)
# p = 0.024

sleeping_less_summary <- comparison_df |>
    group_by(cluster) |>
    count(cbcl_sleeping_less) |>
    mutate(Percent = round(n / sum(n) * 100, 1))
sleeping_less_summary$cbcl_sleeping_less <-
    factor(sleeping_less_summary$cbcl_sleeping_less, levels = c("2", "1", "0"))
ggplot(sleeping_less_summary,
    aes(x = cluster, y = Percent, fill = cbcl_sleeping_less)) +
    geom_bar(stat = "identity", position = position_stack()) +
    geom_text(aes(label = paste(Percent, "%"), y = Percent),
            position = position_stack(vjust = 0.5)) +
    scale_y_continuous(expand = expansion(mult = c(0, .1))) +
    labs(x = "Cluster", y = "Percentage", fill = "CBCL sleeping_less Grade") +
    theme_bw() +
    theme(text = element_text(size = 20))
ggsave(image_path("cbcl_sleeping_less.png"), height = 6, dpi = 300)
# p = 0.06 (NS)

anxiety_summary <- comparison_df |>
    group_by(cluster) |>
    count(cbcl_anxiety) |>
    mutate(Percent = round(n / sum(n) * 100, 1))
anxiety_summary$cbcl_anxiety <-
    factor(anxiety_summary$cbcl_anxiety, levels = c("2", "1", "0"))
ggplot(anxiety_summary,
    aes(x = cluster, y = Percent, fill = cbcl_anxiety)) +
    geom_bar(stat = "identity", position = position_stack()) +
    geom_text(aes(label = paste(Percent, "%"), y = Percent),
            position = position_stack(vjust = 0.5)) +
    scale_y_continuous(expand = expansion(mult = c(0, .1))) +
    labs(x = "Cluster", y = "Percentage", fill = "CBCL anxiety Grade") +
    theme_bw() +
    theme(text = element_text(size = 20))
ggsave(image_path("cbcl_anxiety.png"), height = 6, dpi = 300)
# p = 0.00025

attention_summary <- comparison_df |>
    group_by(cluster) |>
    count(cbcl_attention) |>
    mutate(Percent = round(n / sum(n) * 100, 1))
attention_summary$cbcl_attention <-
    factor(attention_summary$cbcl_attention, levels = c("2", "1", "0"))
ggplot(attention_summary,
    aes(x = cluster, y = Percent, fill = cbcl_attention)) +
    geom_bar(stat = "identity", position = position_stack()) +
    geom_text(aes(label = paste(Percent, "%"), y = Percent),
            position = position_stack(vjust = 0.5)) +
    scale_y_continuous(expand = expansion(mult = c(0, .1))) +
    labs(x = "Cluster", y = "Percentage", fill = "CBCL attention Grade") +
    theme_bw() +
    theme(text = element_text(size = 20))
ggsave(image_path("cbcl_attention.png"), height = 6, dpi = 300)
# p = 2e-05

aggressive_summary <- comparison_df |>
    group_by(cluster) |>
    count(cbcl_aggressive) |>
    mutate(Percent = round(n / sum(n) * 100, 1))
aggressive_summary$cbcl_aggressive <-
    factor(aggressive_summary$cbcl_aggressive, levels = c("2", "1", "0"))
ggplot(aggressive_summary,
    aes(x = cluster, y = Percent, fill = cbcl_aggressive)) +
    geom_bar(stat = "identity", position = position_stack()) +
    geom_text(aes(label = paste(Percent, "%"), y = Percent),
            position = position_stack(vjust = 0.5)) +
    scale_y_continuous(expand = expansion(mult = c(0, .1))) +
    labs(x = "Cluster", y = "Percentage", fill = "CBCL aggressive Grade") +
    theme_bw() +
    theme(text = element_text(size = 20))
ggsave(image_path("cbcl_aggressive.png"), height = 6, dpi = 300)
# p = 2e-05

depress_summary <- comparison_df |>
    group_by(cluster) |>
    count(cbcl_depress) |>
    mutate(Percent = round(n / sum(n) * 100, 1))
depress_summary$cbcl_depress <-
    factor(depress_summary$cbcl_depress, levels = c("2", "1", "0"))
ggplot(depress_summary,
    aes(x = cluster, y = Percent, fill = cbcl_depress)) +
    geom_bar(stat = "identity", position = position_stack()) +
    geom_text(aes(label = paste(Percent, "%"), y = Percent),
            position = position_stack(vjust = 0.5)) +
    scale_y_continuous(expand = expansion(mult = c(0, .1))) +
    labs(x = "Cluster", y = "Percentage", fill = "CBCL Depress Grade") +
    theme_bw() +
    theme(text = element_text(size = 20))
ggsave(image_path("cbcl_depress.png"), height = 6, dpi = 300)


pval_vec <- c(
    8 * ord_reg_p(clusters, cbcl_nausea, "cbcl_nausea"), # 0.0001365547 raw
    8 * ord_reg_p(clusters, cbcl_dizzy, "cbcl_dizzy"),
    8 * ord_reg_p(clusters, cbcl_overtired, "cbcl_overtired"),
    8 * ord_reg_p(clusters, cbcl_sleeping_more, "cbcl_sleeping_more"),
    8 * ord_reg_p(clusters, cbcl_sleeping_less, "cbcl_sleeping_less"),
    8 * ord_reg_p(clusters, cbcl_anxiety, "cbcl_anxiety"),
    8 * ord_reg_p(clusters, cbcl_attention, "cbcl_attention"),
    8 * ord_reg_p(clusters, cbcl_aggressive, "cbcl_aggressive"))

mean(pval_vec)

c1_df <- comparison_df |> dplyr::filter(cluster == 1)
c2_df <- comparison_df |> dplyr::filter(cluster == 2)

nrow(c1_df) # 111
nrow(c2_df) # 142

# How many borderline/clinical patients in each cluster?
length(which(c1_df$cbcl_nausea > 0))
length(which(c1_df$cbcl_dizzy > 0))
length(which(c1_df$cbcl_overtired > 0))
length(which(c1_df$cbcl_sleeping_more > 0))
length(which(c1_df$cbcl_sleeping_less > 0))
length(which(c1_df$cbcl_depress > 0))
length(which(c1_df$cbcl_anxiety > 0))
length(which(c1_df$cbcl_attention > 0))
length(which(c1_df$cbcl_aggressive > 0))

length(which(c2_df$cbcl_nausea > 0))
length(which(c2_df$cbcl_dizzy > 0))
length(which(c2_df$cbcl_overtired > 0))
length(which(c2_df$cbcl_sleeping_more > 0))
length(which(c2_df$cbcl_sleeping_less > 0))
length(which(c2_df$cbcl_depress > 0))
length(which(c2_df$cbcl_anxiety > 0))
length(which(c2_df$cbcl_attention > 0))
length(which(c2_df$cbcl_aggressive > 0))


# Proportions:
length(which(c1_df$cbcl_nausea > 0)) / nrow(c1_df) * 100
length(which(c1_df$cbcl_dizzy > 0)) / nrow(c1_df) * 100
length(which(c1_df$cbcl_overtired > 0)) / nrow(c1_df) * 100
length(which(c1_df$cbcl_sleeping_more > 0)) / nrow(c1_df) * 100
length(which(c1_df$cbcl_sleeping_less > 0)) / nrow(c1_df) * 100
length(which(c1_df$cbcl_depress > 0)) / nrow(c1_df) * 100
length(which(c1_df$cbcl_anxiety > 0)) / nrow(c1_df) * 100
length(which(c1_df$cbcl_attention > 0)) / nrow(c1_df) * 100
length(which(c1_df$cbcl_aggressive > 0)) / nrow(c1_df) * 100

length(which(c2_df$cbcl_nausea > 0)) / nrow(c2_df) * 100
length(which(c2_df$cbcl_dizzy > 0)) / nrow(c2_df) * 100
length(which(c2_df$cbcl_overtired > 0)) / nrow(c2_df) * 100
length(which(c2_df$cbcl_sleeping_more > 0)) / nrow(c2_df) * 100
length(which(c2_df$cbcl_sleeping_less > 0)) / nrow(c2_df) * 100
length(which(c2_df$cbcl_depress > 0)) / nrow(c2_df) * 100
length(which(c2_df$cbcl_anxiety > 0)) / nrow(c2_df) * 100
length(which(c2_df$cbcl_attention > 0)) / nrow(c2_df) * 100
length(which(c2_df$cbcl_aggressive > 0)) / nrow(c2_df) * 100


c1_df$cbcl_total <- c1_df |>
    dplyr::select(dplyr::contains("cbcl")) |>
    rowSums()

c2_df$cbcl_total <- c2_df |>
    dplyr::select(dplyr::contains("cbcl")) |>
    rowSums()

library("RColorBrewer")

color

# create matrix
colours <- c("#2274e0", "#FFFFBF", "#db0f1d")

# Obtain the heatmap of c1_df so we can extract the right column order
cbcl_pheatmap <- c1_df |>
    dplyr::select(dplyr::starts_with("cbcl"), -cbcl_total) |>
    as.matrix() |>
    pheatmap(cellheight = 3,
             color = colours,
             legend_breaks = c(0, 1, 2),
             cellwidth = 30)

# This is the clustered column order from c1_df
cbcl_outcome_clustering <- cbcl_pheatmap$tree_col[["order"]]

# Prep the two dataframes in matrix form so we don't need the many pipes
c1_df_matrix <- c1_df |>
    dplyr::select(dplyr::starts_with("cbcl"), -cbcl_total) |>
    as.matrix()
c2_df_matrix <- c2_df |>
    dplyr::select(dplyr::starts_with("cbcl"), -cbcl_total) |>
    as.matrix()

# Reorder the matrices to match the column order from the original c1_df
c1_df_matrix <- c1_df_matrix[, cbcl_outcome_clustering]
c2_df_matrix <- c2_df_matrix[, cbcl_outcome_clustering]

# Plots
pheatmap(c1_df_matrix,
    cellheight = 3,
    color = colours,
    legend_breaks = c(0, 1, 2),
    cellwidth = 30,
    cluster_cols = FALSE)

# Same thing, but saved
pheatmap(c1_df_matrix,
    cellheight = 3,
    color = colours,
    legend_breaks = c(0, 1, 2),
    cellwidth = 30,
    cluster_cols = FALSE,
    filename = image_path("cbcl_train_matrix_c1.png"))
dev.off()

pheatmap(c2_df_matrix,
    cellheight = 3,
    color = colours,
    legend_breaks = c(0, 1, 2),
    cellwidth = 30,
    cluster_cols = FALSE)

# Same thing, but saved
pheatmap(c2_df_matrix,
    cellheight = 3,
    color = colours,
    legend_breaks = c(0, 1, 2),
    cellwidth = 30,
    cluster_cols = FALSE,
    filename = image_path("cbcl_train_matrix_c2.png"))
dev.off()


c1_df_total <- c1_df |>
    dplyr::select(subjectkey, cbcl_total)
c2_df_total <- c2_df |>
    dplyr::select(subjectkey, cbcl_total)
c1_df_total$cluster <- 1
c2_df_total$cluster <- 2
train_total_c_df <- rbind(c1_df_total, c2_df_total)
train_total_c_df$cluster <- as.factor(train_total_c_df$cluster)

ggplot(train_total_c_df,
    aes(x = cbcl_total,
        fill = cluster)) +
    scale_y_continuous(expand = expansion(mult = c(0, 0))) +
    geom_density(alpha = 0.6) +
    theme_bw() +
    theme(text = element_text(size = 20))
ggsave(image_path("cbcl_total_problems_train.png"), height = 6, dpi = 300)


# Rather than looking at the sum (which treats 1 and 2 differently,
#  examine the density of whether or not a child is borderline+ (i.e., above 0)
c1_df_no_total <- c1_df |>
    dplyr::select(dplyr::contains("cbcl"), -cbcl_total)
c1_df_no_total[c1_df_no_total == 2] <- 1
c1_df_no_total$total_any <- rowSums(c1_df_no_total)

c2_df_no_total <- c2_df |>
    dplyr::select(dplyr::contains("cbcl"), -cbcl_total)
c2_df_no_total[c2_df_no_total == 2] <- 1
c2_df_no_total$total_any <- rowSums(c2_df_no_total)

c1_df_total_binary <- c1_df_no_total |>
    dplyr::select(total_any)
c2_df_total_binary <- c2_df_no_total |>
    dplyr::select(total_any)
c1_df_total_binary$cluster <- 1
c2_df_total_binary$cluster <- 2

train_total_c_binary_df <- rbind(c1_df_total_binary, c2_df_total_binary)
train_total_c_binary_df$cluster <- as.factor(train_total_c_df$cluster)

ggplot(train_total_c_binary_df,
    aes(x = total_any,
        fill = cluster)) +
    scale_y_continuous(expand = expansion(mult = c(0, 0))) +
    geom_density(alpha = 0.6) +
    theme_bw() +
    theme(text = element_text(size = 20))
# ggsave(image_path("cbcl_any_problems_train.png"), height = 6, dpi = 300)


c1_df$cbcl_total[c1_df$cbcl_total > 0] <- 1
c2_df$cbcl_total[c2_df$cbcl_total > 0] <- 1

# Consider fleshing out these odds ratios more later

# Odds ratio calcs
c1_bad <- length(which(c1_df$cbcl_total > 0))
c1_good <- length(which(c1_df$cbcl_total == 0))
c2_bad <- length(which(c2_df$cbcl_total > 0))
c2_good <- length(which(c2_df$cbcl_total == 0))
# C2 ~ Not exposed
# C1 ~ Exposed
# good ~ Healthy
# bad ~ Diseased
odds_ratio <- function(DE, HE, DN, HN) {
    numerator <- DE / HE
    denominator <- DN / HN
    return(numerator / denominator)
}
true_or <- odds_ratio(DE = c1_bad, HE = c1_good, DN = c2_bad, HN = c2_good)
true_or
ors <- vector()
set.seed(42)
for (i in 1:1000) {
    bootstrap_c1 <- sample(c1_df$cbcl_total, replace = TRUE)
    bootstrap_c2 <- sample(c2_df$cbcl_total, replace = TRUE)
    c1_bad <- length(which(bootstrap_c1 > 0))
    c1_good <- length(which(bootstrap_c1 == 0))
    c2_bad <- length(which(bootstrap_c2 > 0))
    c2_good <- length(which(bootstrap_c2 == 0))
    ors <- c(ors,
             odds_ratio(DE = c1_bad, HE = c1_good, DN = c2_bad, HN = c2_good))
}
ci <- quantile(ors, probs = c(0.05, 0.95))
ci


c1_and_c2_df <- rbind(c1_df, c2_df)
c1_and_c2_df$cluster <- as.factor(c1_and_c2_df$cluster)
c1_and_c2_df$cbcl_total <- as.factor(c1_and_c2_df$cbcl_total)
c1_and_c2_df <- c1_and_c2_df |>
    group_by(cluster) |>
    count(cbcl_total) |>
    mutate(Percent = round(n / sum(n) * 100, 1))
c1_and_c2_df$cbcl_total <-
    factor(c1_and_c2_df$cbcl_total, levels = c("1", "0"))
ggplot(c1_and_c2_df,
    aes(x = cluster, y = Percent, fill = cbcl_total)) +
    geom_bar(stat = "identity", position = position_stack()) +
    geom_text(aes(label = paste(Percent, "%"), y = Percent),
            position = position_stack(vjust = 0.5)) +
    scale_y_continuous(expand = expansion(mult = c(0, .1))) +
    labs(x = "Cluster", y = "Percentage", fill = "Has any CBCL impairment") +
    theme_bw() +
    theme(text = element_text(size = 20))
ggsave(image_path("any_cbcl_impairment.png"), height = 6, dpi = 300)
true_or
ci# }}}
```

# Label propagation
```{r}
# I have to re-import because of the 'keep_split' that happened early in script# {{{
# Once the keep training split data is renamed to end in train, won't need to
#  do this double importing.
as_mtbi_loc <- load_data("as_mtbi_loc_imp.csv", type = "inputs")
as_mtbi_mechanism <- load_data("as_mtbi_mechanism_imp.csv", type = "inputs")
as_mtbi_mem_daze <- load_data("as_mtbi_mem_daze_imp.csv", type = "inputs")
d_income <- load_data("d_income_imp.csv", type = "inputs")
d_interview_age <- load_data("d_interview_age_imp.csv", type = "inputs")
d_mtbi_age <- load_data("d_mtbi_age_imp.csv", type = "inputs")
d_pubertal_status <- load_data("d_pubertal_status_imp.csv", type = "inputs")
d_race <- load_data("d_race_imp.csv", type = "inputs")
d_sex <- load_data("d_sex_imp.csv", type = "inputs")
mh_headaches <- load_data("mh_headaches_imp.csv", type = "inputs")
mh_mtbi_count <- load_data("mh_mtbi_count_imp.csv", type = "inputs")
dm_wmndf_qc <- load_data("dm_wmndf_qc.csv", imputed = FALSE, type = "inputs")
rm_gord_cor_qc <-
    load_data("rm_gord_cor_qc.csv", imputed = FALSE, type = "inputs")
rm_gord_var_qc <-
    load_data("rm_gord_var_qc.csv", imputed = FALSE, type = "inputs")
rm_subc_cor_qc <-
    load_data("rm_subc_cor_qc.csv", imputed = FALSE, type = "inputs")
rm_subc_var_qc <-
    load_data("rm_subc_var_qc.csv", imputed = FALSE, type = "inputs")
sm_cort_sa_qc <-
    load_data("sm_cort_sa_qc.csv", imputed = FALSE, type = "inputs")
sm_cort_t_qc <-
    load_data("sm_cort_t_qc.csv", imputed = FALSE, type = "inputs")
sm_subc_v_qc <-
    load_data("sm_subc_v_qc.csv", imputed = FALSE, type = "inputs")
p_loneliness <- load_data("p_loneliness_imp.csv", type = "inputs")
p_screen_time <- load_data("p_screen_time_imp.csv", type = "inputs")
p_family_function <- load_data("p_family_function_imp.csv", type = "inputs")
p_sports <- load_data("p_sports_imp.csv", type = "inputs")
p_prosocial <- load_data("p_prosocial_imp.csv", type = "inputs")
p_parent_psych <- load_data("p_parent_psych_imp.csv", type = "inputs")
p_exercise <- load_data("p_exercise_imp.csv", type = "inputs")
# Outcomes
cbcl_headaches <- load_data("cbcl_headaches_imp.csv", type = "outputs")
cbcl_nausea <- load_data("cbcl_nausea_imp.csv", type = "outputs")
cbcl_vomiting <- load_data("cbcl_vomiting_imp.csv", type = "outputs")
cbcl_dizzy <- load_data("cbcl_dizzy_imp.csv", type = "outputs")
cbcl_overtired <- load_data("cbcl_overtired_imp.csv", type = "outputs")
cbcl_sleeping_more <- load_data("cbcl_sleeping_more_imp.csv", type = "outputs")
cbcl_sleeping_less <- load_data("cbcl_sleeping_less_imp.csv", type = "outputs")
cbcl_depress <- load_data("cbcl_depress_imp.csv", type = "outputs")
cbcl_anxiety <- load_data("cbcl_anxiety_imp.csv", type = "outputs")
cbcl_attention <- load_data("cbcl_attention_imp.csv", type = "outputs")
cbcl_aggressive <- load_data("cbcl_aggressive_imp.csv", type = "outputs")
sds_sleep <- load_data("sds_sleep_imp.csv", type = "outputs")
nihtbx_list_fc <- load_data("nihtbx_list_fc_imp.csv", type = "outputs")
nihtbx_pattern_fc <- load_data("nihtbx_pattern_fc_imp.csv", type = "outputs")
nihtbx_cardsort_fc <- load_data("nihtbx_cardsort_fc_imp.csv", type = "outputs")

as_mtbi_loc_train <- keep_split(as_mtbi_loc, assigned_df, "train")
as_mtbi_mechanism_train <- keep_split(as_mtbi_mechanism, assigned_df, "train")
as_mtbi_mem_daze_train <- keep_split(as_mtbi_mem_daze, assigned_df, "train")
d_income_train <- keep_split(d_income, assigned_df, "train")
d_interview_age_train <- keep_split(d_interview_age, assigned_df, "train")
d_mtbi_age_train <- keep_split(d_mtbi_age, assigned_df, "train")
d_pubertal_status_train <- keep_split(d_pubertal_status, assigned_df, "train")
d_race_train <- keep_split(d_race, assigned_df, "train")
d_sex_train <- keep_split(d_sex, assigned_df, "train")
mh_headaches_train <- keep_split(mh_headaches, assigned_df, "train")
mh_mtbi_count_train <- keep_split(mh_mtbi_count, assigned_df, "train")
dm_wmndf_qc_train <- keep_split(dm_wmndf_qc, assigned_df, "train")
rm_gord_cor_qc_train <- keep_split(rm_gord_cor_qc, assigned_df, "train")
rm_gord_var_qc_train <- keep_split(rm_gord_var_qc, assigned_df, "train")
rm_subc_cor_qc_train <- keep_split(rm_subc_cor_qc, assigned_df, "train")
rm_subc_var_qc_train <- keep_split(rm_subc_var_qc, assigned_df, "train")
sm_cort_sa_qc_train <- keep_split(sm_cort_sa_qc, assigned_df, "train")
sm_cort_t_qc_train <- keep_split(sm_cort_t_qc, assigned_df, "train")
sm_subc_v_qc_train <- keep_split(sm_subc_v_qc, assigned_df, "train")
p_loneliness_train <- keep_split(p_loneliness, assigned_df, "train")
p_screen_time_train <- keep_split(p_screen_time, assigned_df, "train")
p_family_function_train <- keep_split(p_family_function, assigned_df, "train")
p_sports_train <- keep_split(p_sports, assigned_df, "train")
p_prosocial_train <- keep_split(p_prosocial, assigned_df, "train")
p_parent_psych_train <- keep_split(p_parent_psych, assigned_df, "train")
p_exercise_train <- keep_split(p_exercise, assigned_df, "train")
cbcl_headaches_train <- keep_split(cbcl_headaches, assigned_df, "train")
cbcl_nausea_train <- keep_split(cbcl_nausea, assigned_df, "train")
cbcl_vomiting_train <- keep_split(cbcl_vomiting, assigned_df, "train")
cbcl_dizzy_train <- keep_split(cbcl_dizzy, assigned_df, "train")
cbcl_overtired_train <- keep_split(cbcl_overtired, assigned_df, "train")
cbcl_sleeping_more_train <- keep_split(cbcl_sleeping_more, assigned_df, "train")
cbcl_sleeping_less_train <- keep_split(cbcl_sleeping_less, assigned_df, "train")
cbcl_depress_train <- keep_split(cbcl_depress, assigned_df, "train")
cbcl_anxiety_train <- keep_split(cbcl_anxiety, assigned_df, "train")
cbcl_attention_train <- keep_split(cbcl_attention, assigned_df, "train")
cbcl_aggressive_train <- keep_split(cbcl_aggressive, assigned_df, "train")
sds_sleep_train <- keep_split(sds_sleep, assigned_df, "train")

nihtbx_list_fc_train <- keep_split(nihtbx_list_fc, assigned_df, "train")
nihtbx_pattern_fc_train <- keep_split(nihtbx_pattern_fc, assigned_df, "train")
nihtbx_cardsort_fc_train <- keep_split(nihtbx_cardsort_fc, assigned_df, "train")

as_mtbi_loc_test <- keep_split(as_mtbi_loc, assigned_df, "test")
as_mtbi_mechanism_test <- keep_split(as_mtbi_mechanism, assigned_df, "test")
as_mtbi_mem_daze_test <- keep_split(as_mtbi_mem_daze, assigned_df, "test")
d_income_test <- keep_split(d_income, assigned_df, "test")
d_interview_age_test <- keep_split(d_interview_age, assigned_df, "test")
d_mtbi_age_test <- keep_split(d_mtbi_age, assigned_df, "test")
d_pubertal_status_test <- keep_split(d_pubertal_status, assigned_df, "test")
d_race_test <- keep_split(d_race, assigned_df, "test")
d_sex_test <- keep_split(d_sex, assigned_df, "test")
mh_headaches_test <- keep_split(mh_headaches, assigned_df, "test")
mh_mtbi_count_test <- keep_split(mh_mtbi_count, assigned_df, "test")
dm_wmndf_qc_test <- keep_split(dm_wmndf_qc, assigned_df, "test")
rm_gord_cor_qc_test <- keep_split(rm_gord_cor_qc, assigned_df, "test")
rm_gord_var_qc_test <- keep_split(rm_gord_var_qc, assigned_df, "test")
rm_subc_cor_qc_test <- keep_split(rm_subc_cor_qc, assigned_df, "test")
rm_subc_var_qc_test <- keep_split(rm_subc_var_qc, assigned_df, "test")
sm_cort_sa_qc_test <- keep_split(sm_cort_sa_qc, assigned_df, "test")
sm_cort_t_qc_test <- keep_split(sm_cort_t_qc, assigned_df, "test")
sm_subc_v_qc_test <- keep_split(sm_subc_v_qc, assigned_df, "test")
p_loneliness_test <- keep_split(p_loneliness, assigned_df, "test")
p_screen_time_test <- keep_split(p_screen_time, assigned_df, "test")
p_family_function_test <- keep_split(p_family_function, assigned_df, "test")
p_sports_test <- keep_split(p_sports, assigned_df, "test")
p_prosocial_test <- keep_split(p_prosocial, assigned_df, "test")
p_parent_psych_test <- keep_split(p_parent_psych, assigned_df, "test")
p_exercise_test <- keep_split(p_exercise, assigned_df, "test")
cbcl_headaches_test <- keep_split(cbcl_headaches, assigned_df, "test")
cbcl_nausea_test <- keep_split(cbcl_nausea, assigned_df, "test")
cbcl_vomiting_test <- keep_split(cbcl_vomiting, assigned_df, "test")
cbcl_dizzy_test <- keep_split(cbcl_dizzy, assigned_df, "test")
cbcl_overtired_test <- keep_split(cbcl_overtired, assigned_df, "test")
cbcl_sleeping_more_test <- keep_split(cbcl_sleeping_more, assigned_df, "test")
cbcl_sleeping_less_test <- keep_split(cbcl_sleeping_less, assigned_df, "test")
cbcl_depress_test <- keep_split(cbcl_depress, assigned_df, "test")
cbcl_anxiety_test <- keep_split(cbcl_anxiety, assigned_df, "test")
cbcl_attention_test <- keep_split(cbcl_attention, assigned_df, "test")
cbcl_aggressive_test <- keep_split(cbcl_aggressive, assigned_df, "test")
sds_sleep_test <- keep_split(sds_sleep, assigned_df, "test")

as_mtbi_loc_full <- rbind(as_mtbi_loc_train, as_mtbi_loc_test)
as_mtbi_mechanism_full <- rbind(as_mtbi_mechanism_train, as_mtbi_mechanism_test)
as_mtbi_mem_daze_full <- rbind(as_mtbi_mem_daze_train, as_mtbi_mem_daze_test)
d_income_full <- rbind(d_income_train, d_income_test)
d_interview_age_full <- rbind(d_interview_age_train, d_interview_age_test)
d_mtbi_age_full <- rbind(d_mtbi_age_train, d_mtbi_age_test)
d_pubertal_status_full <- rbind(d_pubertal_status_train, d_pubertal_status_test)
d_race_full <- rbind(d_race_train, d_race_test)
d_sex_full <- rbind(d_sex_train, d_sex_test)
mh_headaches_full <- rbind(mh_headaches_train, mh_headaches_test)
mh_mtbi_count_full <- rbind(mh_mtbi_count_train, mh_mtbi_count_test)
dm_wmndf_qc_full <- rbind(dm_wmndf_qc_train, dm_wmndf_qc_test)
rm_gord_cor_qc_full <- rbind(rm_gord_cor_qc_train, rm_gord_cor_qc_test)
rm_gord_var_qc_full <- rbind(rm_gord_var_qc_train, rm_gord_var_qc_test)
rm_subc_cor_qc_full <- rbind(rm_subc_cor_qc_train, rm_subc_cor_qc_test)
rm_subc_var_qc_full <- rbind(rm_subc_var_qc_train, rm_subc_var_qc_test)
sm_cort_sa_qc_full <- rbind(sm_cort_sa_qc_train, sm_cort_sa_qc_test)
sm_cort_t_qc_full <- rbind(sm_cort_t_qc_train, sm_cort_t_qc_test)
sm_subc_v_qc_full <- rbind(sm_subc_v_qc_train, sm_subc_v_qc_test)
p_loneliness_full <- rbind(p_loneliness_train, p_loneliness_test)
p_screen_time_full <- rbind(p_screen_time_train, p_screen_time_test)
p_family_function_full <- rbind(p_family_function_train, p_family_function_test)
p_sports_full <- rbind(p_sports_train, p_sports_test)
p_prosocial_full <- rbind(p_prosocial_train, p_prosocial_test)
p_parent_psych_full <- rbind(p_parent_psych_train, p_parent_psych_test)
p_exercise_full <- rbind(p_exercise_train, p_exercise_test)
cbcl_headaches_full <- rbind(cbcl_headaches_train, cbcl_headaches_test)
cbcl_nausea_full <- rbind(cbcl_nausea_train, cbcl_nausea_test)
cbcl_vomiting_full <- rbind(cbcl_vomiting_train, cbcl_vomiting_test)
cbcl_dizzy_full <- rbind(cbcl_dizzy_train, cbcl_dizzy_test)
cbcl_overtired_full <- rbind(cbcl_overtired_train, cbcl_overtired_test)
cbcl_sleeping_more_full <-
    rbind(cbcl_sleeping_more_train, cbcl_sleeping_more_test)
cbcl_sleeping_less_full <-
    rbind(cbcl_sleeping_less_train, cbcl_sleeping_less_test)
cbcl_depress_full <- rbind(cbcl_depress_train, cbcl_depress_test)
cbcl_anxiety_full <- rbind(cbcl_anxiety_train, cbcl_anxiety_test)
cbcl_attention_full <- rbind(cbcl_attention_train, cbcl_attention_test)
cbcl_aggressive_full <- rbind(cbcl_aggressive_train, cbcl_aggressive_test)
sds_sleep_full <- rbind(sds_sleep_train, sds_sleep_test)

full_data_list <- generate_data_list(
                                mtbi_loc = as_mtbi_loc_full,
                                mtbi_mechanism = as_mtbi_mechanism_full,
                                mtbi_mem_daze = as_mtbi_mem_daze_full,
                                income = d_income_full,
                                interview_age = d_interview_age_full,
                                mtbi_age = d_mtbi_age_full,
                                pubertal_status = d_pubertal_status_full,
                                sex = d_sex_full,
                                race = d_race_full,
                                headaches = mh_headaches_full,
                                mtbi_count = mh_mtbi_count_full,
                                wmndf = dm_wmndf_qc_full,
                                gord_cor = rm_gord_cor_qc_full,
                                gord_var = rm_gord_var_qc_full,
                                subc_cor = rm_subc_cor_qc_full,
                                subc_var = rm_subc_var_qc_full,
                                cort_sa = sm_cort_sa_qc_full,
                                cort_t = sm_cort_t_qc_full,
                                subc_v = sm_subc_v_qc_full,
                                loneliness = p_loneliness_full,
                                screen_time = p_screen_time_full,
                                family_function = p_family_function_full,
                                sports = p_sports_full,
                                prosocial = p_prosocial_full,
                                parent_psych = p_parent_psych_full,
                                exercise = p_exercise_full)

outcome_list_full <- generate_outcome_list(
    cbcl_nausea = cbcl_nausea_full,
    cbcl_vomiting = cbcl_vomiting_full,
    cbcl_dizzy = cbcl_dizzy_full,
    cbcl_overtired = cbcl_overtired_full,
    cbcl_sleeping_more = cbcl_sleeping_more_full,
    cbcl_sleeping_less = cbcl_sleeping_less_full,
    cbcl_depress = cbcl_depress_full,
    cbcl_anxiety = cbcl_anxiety_full,
    cbcl_attention = cbcl_attention_full,
    cbcl_aggressive = cbcl_aggressive_full)



# Options we've previously collected
# The best row (from the output matrix, which isn't really needed here)
top_om_row

# The best row (from the design matrix)
top_dm_row <- dm_reordered |>
    dplyr::filter(row_id %in% top_om_row$row_id)
top_dm_row

write_csv(top_om_row, data_path("top_om_row.csv"))
write_csv(top_dm_row, data_path("top_dm_row.csv"))

top_om_row <- read_delim(data_path("top_om_row.csv", date = "2023_02_23"))
top_dm_row <- read_delim(data_path("top_dm_row.csv", date = "2023_02_23"))


# This formality is in preparation for looping this chunk through many rows
current_dm_row <- top_dm_row
current_om_row <- top_om_row

current_data_list <- execute_inclusion(full_data_list, current_dm_row)
current_K <- current_dm_row$K
current_alpha <- current_dm_row$alpha

full_fused_network <- snf_step(current_data_list,
                          "individual",
                          K = current_K,
                          alpha = current_alpha)

# Make sure the order between OM and fused network match
clustered_subs <- colnames(subs(current_om_row))[-1]

test_subs <- as_mtbi_loc_test$subjectkey
ordered_subs <- c(clustered_subs, test_subs)
full_fused_network <- full_fused_network[ordered_subs, ordered_subs]

identical(colnames(full_fused_network)[seq_along(clustered_subs)],
          clustered_subs)

clustered_subjects <- subs(current_om_row) # keep row_id and subj cluster info
clusters <- data.frame(t(clustered_subjects))
clusters$id <- rownames(clusters)
rownames(clusters) <- NULL
colnames(clusters) <- c("cluster", "subjectkey")
clusters <- clusters[2:nrow(clusters), ]
clusters # reformatted for label prop

groups <- clusters$cluster
groups

# Another sanity check that everything is in order
identical(colnames(full_fused_network)[seq_along(clustered_subs)],
          clusters$subjectkey)

# Label propagation from SNFtool's source code
Y0 <- matrix(0, nrow(full_fused_network), as.numeric(max(groups)))
Y0
groups <- as.numeric(groups)
for (i in 1:length(groups)){
    Y0[i,groups[i]] <- 1
}
## Need their internal prediction function:
.csPrediction <- function(W,Y0,method){
  alpha=0.9;
  P= W/rowSums(W)
  if(method==0){
    Y= (1-alpha)* solve( diag(dim(P)[1])- alpha*P)%*%Y0;
  } else {
    NLabel=which(rowSums(Y0)==0)[1]-1;
    Y=Y0;
    for (i in 1:1000){
      Y=P%*%Y;
      Y[1:NLabel,]=Y0[1:NLabel,];
    }
  }
  return(Y);
}
### End of their internal function
Y <- .csPrediction(W = full_fused_network,Y0,method = TRUE)
newgroups <- rep(0,nrow(full_fused_network))
for (i in 1:nrow(Y)){
    newgroups[i] <- which(Y[i,] == max(Y[i,]))
}
newgroups
full_clusters <- as_mtbi_loc_full |> dplyr::select("subjectkey")
full_clusters$cluster <- newgroups
testing_subs <- as_mtbi_loc_test$subjectkey
labeled_test <- full_clusters[full_clusters$subjectkey %in% testing_subs, ]
test_evaluation_list <- list(
    labeled_test,
    cbcl_nausea,
    cbcl_vomiting,
    cbcl_dizzy,
    cbcl_overtired,
    cbcl_sleeping_more,
    cbcl_sleeping_less,
    cbcl_depress,
    cbcl_anxiety,
    cbcl_attention,
    cbcl_aggressive)
test_evaluation_df <- test_evaluation_list |>
    purrr::reduce(dplyr::inner_join, by = "subjectkey")
test_evaluation_df$cluster <- as.numeric(test_evaluation_df$cluster)
test_clusters <- test_evaluation_df |>
    dplyr::select("subjectkey", "cluster") |>
    data.frame()
ord_reg_p(test_clusters, cbcl_dizzy, "cbcl_dizzy")
ord_reg_p(test_clusters, cbcl_nausea, "cbcl_nausea")
ord_reg_p(test_clusters, cbcl_overtired, "cbcl_overtired")
ord_reg_p(test_clusters, cbcl_sleeping_more, "cbcl_sleeping_more")
ord_reg_p(test_clusters, cbcl_sleeping_less, "cbcl_sleeping_less")
ord_reg_p(test_clusters, cbcl_anxiety, "cbcl_anxiety")
ord_reg_p(test_clusters, cbcl_attention, "cbcl_attention")
ord_reg_p(test_clusters, cbcl_aggressive, "cbcl_aggressive")
c1_test_df <- test_evaluation_df |> dplyr::filter(cluster == 1)
c2_test_df <- test_evaluation_df |> dplyr::filter(cluster == 2)
nrow(c1_test_df) # 6
nrow(c2_test_df) # 61

# THIS IS WHERE I LEFT OFF! (FEBRUARY 23)

write_csv(c1_test_df, data_path("label_propagated_c1.csv"))
write_csv(c2_test_df, data_path("label_propagated_c2.csv"))
write_csv(test_evaluation_df, data_path("test_evaluation_df.csv"))

c1_test_df <- data.frame(read_delim(data_path("label_propagated_c1.csv",
    date = "2023_02_23")))
c2_test_df <- data.frame(read_delim(data_path("label_propagated_c2.csv",
    date = "2023_02_23")))
test_evaluation_df <- data.frame(read_delim(data_path("test_evaluation_df.csv",
    date = "2023_02_23")))

c1_test_df$cbcl_total <- c1_test_df |>
    dplyr::select(dplyr::contains("cbcl")) |>
    rowSums()
c2_test_df$cbcl_total <- c2_test_df |>
    dplyr::select(dplyr::contains("cbcl")) |>
    rowSums()

# A new thing thrown in for testing
c1_test_df <- c1_test_df |>
    rowwise() |>
    dplyr::mutate(max_impair=max(c_across(cbcl_nausea:cbcl_aggressive)))
c2_test_df <- c2_test_df |>
    rowwise() |>
    dplyr::mutate(max_impair=max(c_across(cbcl_nausea:cbcl_aggressive)))


c1_impaired_frac <- length(which(c1_test_df$max_impair > 1)) / nrow(c1_test_df)
c2_impaired_frac <- length(which(c2_test_df$max_impair > 1)) / nrow(c2_test_df)
true_diff <- c1_impaired_frac - c2_impaired_frac

c1_border_frac <- length(which(c1_test_df$max_impair > 0)) / nrow(c1_test_df)
c2_border_frac <- length(which(c2_test_df$max_impair > 0)) / nrow(c2_test_df)
true_diff_border <- c1_border_frac - c2_border_frac

test_evaluation_df$cbcl_total <- test_evaluation_df |>
    dplyr::select(dplyr::contains("cbcl")) |>
    rowSums()

test_evaluation_df <- test_evaluation_df |>
    rowwise() |>
    dplyr::mutate(max_impair=max(c_across(cbcl_nausea:cbcl_aggressive)))# }}}
```

## Permutation testing

### CBCL proportions

```{r}
# Permutation testing difference in proportion# {{{
vector_uniform <- c()
set.seed(42)
for (i in 1:10000) {
    number_in_c1 <- sample.int(66, 1)
    c1_indices <- sample(67, size = number_in_c1)
    c2_indices <- which(!(1:67 %in% c1_indices))
    mock_c1_df <- test_evaluation_df[c1_indices, c("cluster", "max_impair")]
    mock_c2_df <- test_evaluation_df[c2_indices, c("cluster", "max_impair")]
    c1_impaired_frac <-
        length(which(mock_c1_df$max_impair > 1)) / nrow(mock_c1_df)
    c2_impaired_frac <-
        length(which(mock_c2_df$max_impair > 1)) / nrow(mock_c2_df)
    difference <- c1_impaired_frac - c2_impaired_frac
    print(i)
    vector_uniform <- c(vector_uniform, difference)
    if (is.nan(difference)) {
        print(c1_impaired_frac)
        print(c2_impaired_frac)
        print(number_in_c1)
    }
}
percentile <- ecdf(vector_uniform)
1 - percentile(true_diff) # The p-value

png(img_path("difference_in_proportion_cbcl_uniform_lp.png"),
    height = 5,
    width = 5,
    units = "in",
    res = 300)
# This is an essential plot
hist(vector_uniform,
    col = "gray",
    las = 1,
    main = "",
    breaks = 30,
    xlab = "Difference in proportion of children with clinical CBCL impairment")
abline(v = true_diff,
    col = "red")
axis(1,at=seq(-1,1,by=0.5))
dev.off()# }}}

# Preserving the 6 and 61 split size# {{{
vector_6_61 <- c()
set.seed(42)
for (i in 1:10000) {
    number_in_c1 <- 6
    c1_indices <- sample(67, size = number_in_c1)
    c2_indices <- which(!(1:67 %in% c1_indices))
    mock_c1_df <- test_evaluation_df[c1_indices, c("cluster", "max_impair")]
    mock_c2_df <- test_evaluation_df[c2_indices, c("cluster", "max_impair")]
    c1_impaired_frac <-
        length(which(mock_c1_df$max_impair > 1)) / nrow(mock_c1_df)
    c2_impaired_frac <-
        length(which(mock_c2_df$max_impair > 1)) / nrow(mock_c2_df)
    difference <- c1_impaired_frac - c2_impaired_frac
    print(i)
    vector_6_61 <- c(vector_6_61, difference)
    if (is.nan(difference)) {
        print(c1_impaired_frac)
        print(c2_impaired_frac)
        print(number_in_c1)
    }
}
percentile <- ecdf(vector_6_61)
1 - percentile(true_diff) # The p-value

png(img_path("difference_in_proportion_cbcl_6_61_lp.png"),
    height = 5,
    width = 5,
    units = "in",
    res = 300)
hist(vector_6_61,
    col = "gray",
    las = 1,
    main = "",
    breaks = 30,
    xlab = "Difference in proportion of children with clinical CBCL impairment")
abline(v = true_diff,
    col = "red")
axis(1,at=seq(-1,1,by=0.5))
dev.off()# }}}

# Permutation testing difference in proportion borderline OR clinical# {{{
vector_uniform <- c()
set.seed(42)
for (i in 1:10000) {
    number_in_c1 <- sample.int(66, 1)
    c1_indices <- sample(67, size = number_in_c1)
    c2_indices <- which(!(1:67 %in% c1_indices))
    mock_c1_df <- test_evaluation_df[c1_indices, c("cluster", "max_impair")]
    mock_c2_df <- test_evaluation_df[c2_indices, c("cluster", "max_impair")]
    c1_impaired_frac <-
        length(which(mock_c1_df$max_impair > 0)) / nrow(mock_c1_df)
    c2_impaired_frac <-
        length(which(mock_c2_df$max_impair > 0)) / nrow(mock_c2_df)
    difference <- c1_impaired_frac - c2_impaired_frac
    print(i)
    vector_uniform <- c(vector_uniform, difference)
    if (is.nan(difference)) {
        print(c1_impaired_frac)
        print(c2_impaired_frac)
        print(number_in_c1)
    }
}
percentile <- ecdf(vector_uniform)
1 - percentile(true_diff_border) # The p-value is 0.0341

png(image_path("difference_in_proportion_any_cbcl_uniform_lp.png"),
    height = 5,
    width = 5,
    units = "in",
    res = 300)
# This is an essential plot
hist(vector_uniform,
    col = "gray",
    las = 1,
    main = "",
    breaks = 30,
    xlab = "Difference in proportion of any CBCL impairment")
abline(v = true_diff_border,
    col = "red")
axis(1,at=seq(-1,1,by=0.5))
dev.off()# }}}

# Preserving the 6 and 61 split size# {{{
vector_6_61 <- c()
set.seed(42)
for (i in 1:10000) {
    number_in_c1 <- 6
    c1_indices <- sample(67, size = number_in_c1)
    c2_indices <- which(!(1:67 %in% c1_indices))
    mock_c1_df <- test_evaluation_df[c1_indices, c("cluster", "max_impair")]
    mock_c2_df <- test_evaluation_df[c2_indices, c("cluster", "max_impair")]
    c1_impaired_frac <-
        length(which(mock_c1_df$max_impair > 0)) / nrow(mock_c1_df)
    c2_impaired_frac <-
        length(which(mock_c2_df$max_impair > 0)) / nrow(mock_c2_df)
    difference <- c1_impaired_frac - c2_impaired_frac
    print(i)
    vector_6_61 <- c(vector_6_61, difference)
    if (is.nan(difference)) {
        print(c1_impaired_frac)
        print(c2_impaired_frac)
        print(number_in_c1)
    }
}
percentile <- ecdf(vector_6_61)
1 - percentile(true_diff_border) # The p-value

png(image_path("difference_in_proportion_any_cbcl_6_61_lp.png"),
    height = 5,
    width = 5,
    units = "in",
    res = 300)

hist(vector_6_61,
    col = "gray",
    las = 1,
    main = "",
    breaks = 30,
    xlab = "Difference in proportion of any CBCL impairment")
abline(v = true_diff_border,
    col = "red")

dev.off()# }}}
```

## CBCL relationships

```{r}

c1_df

test_evaluation_df

c1_test_matrix <- c1_test_df |>
    dplyr::select(dplyr::starts_with("cbcl"), -cbcl_total) |>
    as.matrix()
c1_test_matrix <- c1_test_matrix[, cbcl_outcome_clustering]


c2_test_matrix <- c2_test_df |>
    dplyr::select(dplyr::starts_with("cbcl"), -cbcl_total) |>
    as.matrix()
c2_test_matrix <- c2_test_matrix[, cbcl_outcome_clustering]


pheatmap(c1_test_matrix,
    cellheight = 3,
    color = colours,
    legend_breaks = c(0, 1, 2),
    cellwidth = 30,
    cluster_cols = FALSE)

pheatmap(c2_test_matrix,
    cellheight = 3,
    color = colours,
    legend_breaks = c(0, 1, 2),
    cellwidth = 30,
    cluster_cols = FALSE)

pheatmap(c1_test_matrix,
    cellheight = 3,
    color = colours,
    legend_breaks = c(0, 1, 2),
    cellwidth = 30,
    cluster_cols = FALSE,
    filename = image_path("cbcl_test_matrix_c1.png"))
dev.off()

pheatmap(c2_test_matrix,
    cellheight = 3,
    color = colours,
    legend_breaks = c(0, 1, 2),
    cellwidth = 30,
    cluster_cols = FALSE,
    filename = image_path("cbcl_test_matrix_c2.png"))
dev.off()

```



## Odds ratios
```{r}

# Training subjects only
cbcl_outcomes <- list(
    cbcl_nausea,
    cbcl_vomiting,
    cbcl_dizzy,
    cbcl_overtired,
    cbcl_sleeping_more,
    cbcl_sleeping_less,
    cbcl_depress,
    cbcl_anxiety,
    cbcl_attention,
    cbcl_aggressive)

top_om_row


or_om_row <- function(om_row, outcome_list) {
    om_row_subs <- subs(om_row)
    clusters_df <- data.frame(t(om_row_subs))
    clusters_df$cluster <- rownames(clusters_df)
    rownames(clusters_df) <- NULL
    colnames(clusters_df) <- c("cluster", "subjectkey")
    clusters_df <- clusters_df[2:nrow(clusters_df), ]
    clusters_and_outcomes_list <- append(list(clusters_df), outcome_list)
    clusters_and_outcomes_df <- clusters_and_outcomes_list |>
        purrr::reduce(dplyr::inner_join, by = "subjectkey")
    return(clusters_and_outcomes_df)
}
train_evaluation_df <- or_om_row(top_om_row, cbcl_outcomes)

train_evaluation_df


odds_ratio <- function(de, he, dn, hn) {
    numerator <- de / he
    denominator <- dn / hn
    return(numerator / denominator)
}


cbcl_or <- function(evaluation_df) {
    or_df <- data.frame(outcome = as.character(),
                        or = as.numeric(),
                        ci_low = as.numeric(),
                        ci_high = as.numeric())
    outcome_names <- evaluation_df |>
        dplyr::select(dplyr::starts_with("cbcl")) |>
        colnames()
    for (i in seq_along(outcome_names)) {
        current_outcome <- outcome_names[i]
        or_summary <- evaluation_df |>
            group_by(cluster) |>
            count(evaluation_df[, current_outcome] > 0)
        colnames(or_summary) <- c("cluster", "bad_outcome", "n")
        # Calculating odds ratios
        de_bad_c1 <- or_summary |>
            dplyr::filter(cluster == 1 & bad_outcome == TRUE) |>
            dplyr::ungroup() |>
            dplyr::select("n") |>
            as.numeric()
        he_good_c1 <- or_summary |>
            dplyr::filter(cluster == 1 & bad_outcome == FALSE) |>
            dplyr::ungroup() |>
            dplyr::select("n") |>
            as.numeric()
        dn_bad_c2 <- or_summary |>
            dplyr::filter(cluster == 2 & bad_outcome == TRUE) |>
            dplyr::ungroup() |>
            dplyr::select("n") |>
            as.numeric()
        hn_good_c2 <- or_summary |>
            dplyr::filter(cluster == 2 & bad_outcome == FALSE) |>
            dplyr::ungroup() |>
            dplyr::select("n") |>
            as.numeric()
        or <- odds_ratio(de = de_bad_c1,
            he = he_good_c1,
            dn = dn_bad_c2,
            hn = hn_good_c2)
        # Calculating upper and lower bounds
        a_val <- de_bad_c1
        c_val <- dn_bad_c2
        b_val <- he_good_c1
        d_val <- hn_good_c2
        num <- a_val/b_val
        den <- c_val/d_val
        se_ln_or <- sqrt((1/a_val + 1/b_val + 1/c_val + 1/d_val))
        ln_or <- log(num/den)
        lower <- exp(ln_or - 1.96 * se_ln_or)
        upper <- exp(ln_or + 1.96 * se_ln_or)
        current_df <- data.frame(outcome = current_outcome,
                              or = or,
                              ci_low = lower,
                              ci_high = upper)
        or_df <- rbind(or_df, current_df)
    }
    return(or_df)
}

test_evaluation_df <- data.frame(test_evaluation_df)

train_cbcl_ors <- cbcl_or(train_evaluation_df)

test_cbcl_ors <- cbcl_or(test_evaluation_df) |>
    dplyr::filter(!(outcome == "cbcl_total"))


outcome_order <- train_cbcl_ors$outcome[cbcl_outcome_clustering]

train_cbcl_ors <- train_cbcl_ors |>
    arrange(sapply(outcome, function(y) which(y == outcome_order))) |>
    mutate(row = row_number())

test_cbcl_ors <- test_cbcl_ors |>
    arrange(sapply(outcome, function(y) which(y == outcome_order))) |>
    mutate(row = row_number())

test_cbcl_ors

train_cbcl_ors$outcome <- as.factor(train_cbcl_ors$outcome)


ggplot(train_cbcl_ors, aes(y = reorder(outcome, rev(row)),
                          x = or,
                          color = ci_low > 1)) +
    geom_point(shape = 18, size = 10, show.legend = FALSE) +
    geom_errorbarh(aes(xmin = ci_low, xmax = ci_high),
                   height = 0.5, size = 1.5, show.legend = FALSE) +
    geom_vline(xintercept = 1,
             linetype = "dashed",
             cex = 1,
             alpha = 0.5) +
    xlab("Odds Ratio (95% CI)") +
    ylab(" ") +
    scale_x_continuous(trans = 'log10') +
    scale_y_discrete(labels = c("Undersleeping",
                                "Nauseous",
                                "Overtired",
                                "Vomiting",
                                "Dizzy",
                                "Oversleeping",
                                "Anxious",
                                "Depressed",
                                "Aggressive",
                                "Attention issues")) +
    scale_colour_manual(values = "#F8766D") +
    theme_bw() +
    theme(panel.border = element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        axis.text.y = element_text(colour = "black"),
        axis.title.x = element_text(colour = "black",
                                    margin = margin(t = 15,
                                                    r = 20, b = 0, l = 0)),
        axis.text.x.bottom = element_text(colour = "black"),
        text = element_text(size = 30))
#    labs(colour = "Significant OR") +
ggsave(image_path("training_cbcl_ors.png"), height = 6, dpi = 300)

ggplot(test_cbcl_ors, aes(y = reorder(outcome, rev(row)),
                          x = or,
                          color = ci_low > 1)) +
    geom_point(shape = 18, size = 10, show.legend = FALSE) +
    geom_errorbarh(aes(xmin = ci_low, xmax = ci_high),
                   height = 0.5, size = 1.5, show.legend = FALSE) +
    geom_vline(xintercept = 1,
             linetype = "dashed",
             cex = 1,
             alpha = 0.5) +
    xlab("Odds Ratio (95% CI)") +
    ylab(" ") +
    scale_x_continuous(trans = 'log10') +
    scale_y_discrete(labels = c("Undersleeping",
                                "Nauseous",
                                "Overtired",
                                "Vomiting",
                                "Dizzy",
                                "Oversleeping",
                                "Anxious",
                                "Depressed",
                                "Aggressive",
                                "Attention issues")) +
    scale_colour_manual(values = c("darkgray", "#F8766D")) +
    theme_bw() +
    theme(panel.border = element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        axis.text.y = element_text(colour = "black"),
        axis.title.x = element_text(colour = "black",
                                    margin = margin(t = 15,
                                                    r = 20, b = 0, l = 0)),
        axis.text.x.bottom = element_text(colour = "black"),
        text = element_text(size = 30))
#    labs(colour = "Significant OR") +

ggsave(image_path("testing_cbcl_ors.png"), height = 6, dpi = 300)


```


## Individual CBCL measures as bar charts

```{r}
test_comparison_df <- rbind(c1_test_df, c2_test_df) # {{{

test_comparison_df$cluster <- as.factor(test_comparison_df$cluster)

nausea_summary <- test_comparison_df |>
    group_by(cluster) |>
    count(cbcl_nausea) |>
    mutate(Percent = round(n / sum(n) * 100, 1))
nausea_summary$cbcl_nausea <-
    factor(nausea_summary$cbcl_nausea, levels = c("2", "1", "0"))
ggplot(nausea_summary,
    aes(x = cluster, y = Percent, fill = cbcl_nausea)) +
    geom_bar(stat = "identity", position = position_stack()) +
    geom_text(aes(label = paste(Percent, "%"), y = Percent),
            position = position_stack(vjust = 0.5)) +
    scale_y_continuous(expand = expansion(mult = c(0, .1))) +
    labs(x = "Cluster", y = "Percentage", fill = "CBCL Nausea Grade") +
    theme_bw() +
    theme(text = element_text(size = 20))

ggsave(img_path("2023_02_22_cbcl_nausea_lp.png"))

dizzy_summary <- test_comparison_df |>
    group_by(cluster) |>
    count(cbcl_dizzy) |>
    mutate(Percent = round(n / sum(n) * 100, 1))
dizzy_summary$cbcl_dizzy <-
    factor(dizzy_summary$cbcl_dizzy, levels = c("2", "1", "0"))
ggplot(dizzy_summary,
    aes(x = cluster, y = Percent, fill = cbcl_dizzy)) +
    geom_bar(stat = "identity", position = position_stack()) +
    geom_text(aes(label = paste(Percent, "%"), y = Percent),
            position = position_stack(vjust = 0.5)) +
    labs(x = "Cluster", y = "Percentage", fill = "CBCL dizzy Grade") +
    theme_bw() +
    theme(text = element_text(size = 20))

ggsave(img_path("2023_02_22_cbcl_dizzy_lp.png"))

overtired_summary <- test_comparison_df |>
    group_by(cluster) |>
    count(cbcl_overtired) |>
    mutate(Percent = round(n / sum(n) * 100, 1))
overtired_summary$cbcl_overtired <-
    factor(overtired_summary$cbcl_overtired, levels = c("2", "1", "0"))
ggplot(overtired_summary,
    aes(x = cluster, y = Percent, fill = cbcl_overtired)) +
    geom_bar(stat = "identity", position = position_stack()) +
    geom_text(aes(label = paste(Percent, "%"), y = Percent),
            position = position_stack(vjust = 0.5)) +
    labs(x = "Cluster", y = "Percentage", fill = "CBCL overtired Grade") +
    theme_bw() +
    theme(text = element_text(size = 20))

ggsave(img_path("2023_02_22_cbcl_overtired_lp.png"))

sleeping_more_summary <- test_comparison_df |>
    group_by(cluster) |>
    count(cbcl_sleeping_more) |>
    mutate(Percent = round(n / sum(n) * 100, 1))
sleeping_more_summary$cbcl_sleeping_more <-
    factor(sleeping_more_summary$cbcl_sleeping_more, levels = c("2", "1", "0"))
ggplot(sleeping_more_summary,
    aes(x = cluster, y = Percent, fill = cbcl_sleeping_more)) +
    geom_bar(stat = "identity", position = position_stack()) +
    geom_text(aes(label = paste(Percent, "%"), y = Percent),
            position = position_stack(vjust = 0.5)) +
    labs(x = "Cluster", y = "Percentage", fill = "CBCL sleeping_more Grade") +
    theme_bw() +
    theme(text = element_text(size = 20))

ggsave(img_path("2023_02_22_cbcl_sleeping_more_lp.png"))

sleeping_less_summary <- test_comparison_df |>
    group_by(cluster) |>
    count(cbcl_sleeping_less) |>
    mutate(Percent = round(n / sum(n) * 100, 1))
sleeping_less_summary$cbcl_sleeping_less <-
    factor(sleeping_less_summary$cbcl_sleeping_less, levels = c("2", "1", "0"))
ggplot(sleeping_less_summary,
    aes(x = cluster, y = Percent, fill = cbcl_sleeping_less)) +
    geom_bar(stat = "identity", position = position_stack()) +
    geom_text(aes(label = paste(Percent, "%"), y = Percent),
            position = position_stack(vjust = 0.5)) +
    labs(x = "Cluster", y = "Percentage", fill = "CBCL sleeping_less Grade") +
    theme_bw() +
    theme(text = element_text(size = 20))

ggsave(img_path("2023_02_22_cbcl_sleeping_less_lp.png"))

anxiety_summary <- test_comparison_df |>
    group_by(cluster) |>
    count(cbcl_anxiety) |>
    mutate(Percent = round(n / sum(n) * 100, 1))
anxiety_summary$cbcl_anxiety <-
    factor(anxiety_summary$cbcl_anxiety, levels = c("2", "1", "0"))
ggplot(anxiety_summary,
    aes(x = cluster, y = Percent, fill = cbcl_anxiety)) +
    geom_bar(stat = "identity", position = position_stack()) +
    geom_text(aes(label = paste(Percent, "%"), y = Percent),
            position = position_stack(vjust = 0.5)) +
    labs(x = "Cluster", y = "Percentage", fill = "CBCL anxiety Grade") +
    theme_bw() +
    theme(text = element_text(size = 20))

ggsave(img_path("2023_02_22_cbcl_anxiety_lp.png"))

attention_summary <- test_comparison_df |>
    group_by(cluster) |>
    count(cbcl_attention) |>
    mutate(Percent = round(n / sum(n) * 100, 1))
attention_summary$cbcl_attention <-
    factor(attention_summary$cbcl_attention, levels = c("2", "1", "0"))
ggplot(attention_summary,
    aes(x = cluster, y = Percent, fill = cbcl_attention)) +
    geom_bar(stat = "identity", position = position_stack()) +
    geom_text(aes(label = paste(Percent, "%"), y = Percent),
            position = position_stack(vjust = 0.5)) +
    labs(x = "Cluster", y = "Percentage", fill = "CBCL attention Grade") +
    theme_bw() +
    theme(text = element_text(size = 20))

ggsave(img_path("2023_02_22_cbcl_attention_lp.png"))

aggressive_summary <- test_comparison_df |>
    group_by(cluster) |>
    count(cbcl_aggressive) |>
    mutate(Percent = round(n / sum(n) * 100, 1))
aggressive_summary$cbcl_aggressive <-
    factor(aggressive_summary$cbcl_aggressive, levels = c("2", "1", "0"))
ggplot(aggressive_summary,
    aes(x = cluster, y = Percent, fill = cbcl_aggressive)) +
    geom_bar(stat = "identity", position = position_stack()) +
    geom_text(aes(label = paste(Percent, "%"), y = Percent),
            position = position_stack(vjust = 0.5)) +
    labs(x = "Cluster", y = "Percentage", fill = "CBCL aggressive Grade") +
    theme_bw() +
    theme(text = element_text(size = 20))

ggsave(img_path("2023_02_22_cbcl_aggressive_lp.png"))
# }}}
```

## Input variable characterization

```{r}

train_input_char <- list(train_evaluation_df,
    as_mtbi_loc_train,
    as_mtbi_mechanism_train,
    as_mtbi_mem_daze_train,
    d_income_train,
    d_interview_age_train,
    d_mtbi_age_train,
    d_pubertal_status_train,
    d_race_train,
    d_sex_train,
    mh_headaches_train,
    mh_mtbi_count_train,
    p_loneliness_train,
    p_screen_time_train,
    p_family_function_train,
    p_sports_train,
    p_prosocial_train,
    p_parent_psych_train,
    p_exercise_train,
    nihtbx_list_fc,
    nihtbx_pattern_fc,
    nihtbx_cardsort_fc)


test_input_char <- list(test_evaluation_df,
    as_mtbi_loc_test,
    as_mtbi_mechanism_test,
    as_mtbi_mem_daze_test,
    d_income_test,
    d_interview_age_test,
    d_mtbi_age_test,
    d_pubertal_status_test,
    d_race_test,
    d_sex_test,
    mh_headaches_test,
    mh_mtbi_count_test,
    p_loneliness_test,
    p_screen_time_test,
    p_family_function_test,
    p_sports_test,
    p_prosocial_test,
    p_parent_psych_test,
    p_exercise_test)


input_train_df <- train_input_char |>
    purrr::reduce(dplyr::inner_join, by = "subjectkey")

input_test_df <- test_input_char |>
    purrr::reduce(dplyr::inner_join, by = "subjectkey")

input_train_df <- input_train_df |>
    dplyr::mutate(
        F = dplyr::case_when(M == 0 ~ 1, TRUE ~ 0),
        pubertal = dplyr::case_when(pubertal_status > 2 ~ 1, TRUE ~ 0),
        non_white = dplyr::case_when(race != "white" ~ 1, TRUE ~ 0),
        parent_psych = dplyr::case_when(asr_scr_totprob_r > 63 ~ 1, TRUE ~ 0))
input_train_df$cluster <- as.factor(input_train_df$cluster)

# Participants scoring above 63 on the ASR scales are considered to be in the
#  clinical range (Achenbach and Rescorla 2003).
input_test_df <- input_test_df |>
    dplyr::mutate(
        F = dplyr::case_when(M == 0 ~ 1, TRUE ~ 0),
        pubertal = dplyr::case_when(pubertal_status > 2 ~ 1, TRUE ~ 0),
        non_white = dplyr::case_when(race != "white" ~ 1, TRUE ~ 0),
        parent_psych = dplyr::case_when(asr_scr_totprob_r > 63 ~ 1, TRUE ~ 0))
input_test_df$cluster <- as.factor(input_test_df$cluster)

input_train_df$total_family_env <- input_train_df |>
    dplyr::select(cluster, "q1_fight":"q9_yell") |>
    sapply(as.numeric) |>
    rowSums()

input_test_df$total_family_env <- input_test_df |>
    dplyr::select(cluster, "q1_fight":"q9_yell") |>
    sapply(as.numeric) |>
    rowSums()


c1in <- input_train_df[input_train_df$cluster == 1, ]
c2in <- input_train_df[input_train_df$cluster == 2, ]

c1in_test <- input_test_df[input_test_df$cluster == 1, ]
c2in_test <- input_test_df[input_test_df$cluster == 2, ]

# More females in c1
length(which(c1in$M == 0)) / length(c1in$M) # 50% F
length(which(c2in$M == 0)) / length(c2in$M) # 33% F

odds_ratio_and_ci <- function(dataframe, outcome) {
    summary_df <- dataframe |>
        dplyr::group_by_at("cluster") |>
        dplyr::count(dataframe[, outcome])
    colnames(summary_df) <- c("cluster", as.character(outcome), "n")
    a_val <- summary_df$"n"[1]
    c_val <- summary_df$"n"[2]
    b_val <- summary_df$"n"[3]
    d_val <- summary_df$"n"[4]
    summary_df$exposure <- c("exposed", "exposed", "control", "control")
    summary_df$health <- c("healthy", "diseased", "healthy", "diseased")
    print(summary_df)
    or <- odds_ratio(he = a_val, de = c_val, hn = b_val, dn = d_val)
    se_ln_or <- sqrt((1/a_val + 1/b_val + 1/c_val + 1/d_val))
    ln_or <- log(or)
    lower <- exp(ln_or - 1.96 * se_ln_or)
    upper <- exp(ln_or + 1.96 * se_ln_or)
    or_df <- data.frame(outcome = as.character(outcome),
                        or = as.numeric(round(or, 2)),
                        ci_low = as.numeric(round(lower, 2)),
                        ci_high = as.numeric(round(upper, 2)))
    print(or_df)
}


colnames(input_train_df)

# S checks (train)
odds_ratio_and_ci(input_train_df, "F") # S
odds_ratio_and_ci(input_train_df, "non_white") # S
odds_ratio_and_ci(input_train_df, "pubertal") # S
odds_ratio_and_ci(input_train_df, "parent_psych") # S (clinical range parent)
t.test(c1in$screentime_wknd_hrs, c2in$screentime_wknd_hrs)
t.test(c1in$screentime_wkday_hrs, c2in$screentime_wkday_hrs)

t.test(c1in$nihtbx_list_fc, c2in$nihtbx_list_fc)
t.test(c1in$nihtbx_pattern_fc, c2in$nihtbx_pattern_fc)
t.test(c1in$nihtbx_cardsort_fc, c2in$nihtbx_cardsort_fc)


# NS checks (train)
odds_ratio_and_ci(input_train_df, "latest_mtbi_loc")
odds_ratio_and_ci(input_train_df, "latest_mtbi_mem_daze")
t.test(c1in$interview_age, c2in$interview_age)
t.test(c1in$latest_mtbi_age, c2in$latest_mtbi_age)
t.test(c1in$mtbi_count, c2in$mtbi_count)
t.test(c1in$ss_friend, c2in$ss_friend)
t.test(c1in$os_friend, c2in$os_friend)
t.test(c1in$os_close_friend, c2in$os_close_friend)
t.test(c1in$ss_close_friend, c2in$ss_close_friend)

# S checks (test)
odds_ratio_and_ci(input_test_df, "pubertal")
t.test(c1in_test$ss_friend, c2in_test$ss_friend) # Not in original
t.test(c1in_test$latest_mtbi_age, c2in_test$latest_mtbi_age) # not in original


# Trending checks (test)
odds_ratio_and_ci(input_test_df, "non_white")
odds_ratio_and_ci(input_test_df, "parent_psych")

# NS checks (test)
odds_ratio_and_ci(input_test_df, "F") # NS
odds_ratio_and_ci(input_test_df, "latest_mtbi_loc")
odds_ratio_and_ci(input_test_df, "latest_mtbi_mem_daze")


t.test(c1in_test$screentime_wknd_hrs, c2in_test$screentime_wknd_hrs)
t.test(c1in_test$screentime_wkday_hrs, c2in_test$screentime_wkday_hrs)
t.test(c1in_test$interview_age, c2in_test$interview_age)
t.test(c1in_test$mtbi_count, c2in_test$mtbi_count)
t.test(c1in_test$os_friend, c2in_test$os_friend)
t.test(c1in_test$os_close_friend, c2in_test$os_close_friend)
t.test(c1in_test$ss_close_friend, c2in_test$ss_close_friend)


head(input_test_df)

input_train_ors <- do.call("rbind", list(
    train_cbcl_ors[, 1:4],
    odds_ratio_and_ci(input_train_df, "F"),
    odds_ratio_and_ci(input_train_df, "non_white"),
    odds_ratio_and_ci(input_train_df, "pubertal"),
    odds_ratio_and_ci(input_train_df, "parent_psych"),
    odds_ratio_and_ci(input_test_df, "latest_mtbi_loc"),
    odds_ratio_and_ci(input_test_df, "latest_mtbi_mem_daze")))

input_train_ors <- input_train_ors |>
    arrange(sapply(outcome, function(y) which(y == outcome_order))) |>
    mutate(row = row_number())

ggplot(input_train_ors,
        aes(y = reorder(outcome, rev(row)),
            x = or,
            color = ci_low > 1)) +
    geom_point(shape = 18, size = 10, show.legend = FALSE) +
    geom_errorbarh(aes(xmin = ci_low, xmax = ci_high),
                   height = 0.5, size = 1.5, show.legend = FALSE) +
    geom_vline(xintercept = 1,
             linetype = "dashed",
             cex = 1,
             alpha = 0.5) +
    geom_hline(yintercept = 6.5, cex = 0.3) +
    xlab("Odds Ratio (95% CI)") +
    ylab(" ") +
    scale_x_continuous(trans = "log10") +
    theme_bw() +
    theme(panel.border = element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        axis.text.y = element_text(colour = "black"),
        axis.title.x = element_text(colour = "black",
                                    margin = margin(t = 15,
                                                    r = 20, b = 0, l = 0)),
        axis.text.x.bottom = element_text(colour = "black"),
        text = element_text(size = 30))

ggsave(image_path("training_input_ors.png"), height = 6, dpi = 300)


ggplot(input_train_df, mapping = aes(x = cluster, y = screentime_wkday_hrs)) +
    geom_boxplot() +
    geom_jitter(height = 0, width = 0.1, alpha = 0.5)

ggplot(input_train_df, mapping = aes(x = cluster, y = screentime_wknd_hrs)) +
    geom_boxplot() +
    geom_jitter(height = 0, width = 0.1, alpha = 0.5)


# This is actually fire emoji
pvals <- c(
    t.test(c1in$asr_scr_perstr_r, c2in$asr_scr_perstr_r)$p.value,
    t.test(c1in$asr_scr_anxdep_r, c2in$asr_scr_anxdep_r)$p.value,
    t.test(c1in$asr_scr_withdrawn_r, c2in$asr_scr_withdrawn_r)$p.value,
    t.test(c1in$asr_scr_somatic_r, c2in$asr_scr_somatic_r)$p.value,
    t.test(c1in$asr_scr_thought_r, c2in$asr_scr_thought_r)$p.value,
    t.test(c1in$asr_scr_attention_r, c2in$asr_scr_attention_r)$p.value,
    t.test(c1in$asr_scr_aggressive_r, c2in$asr_scr_aggressive_r)$p.value,
    t.test(c1in$asr_scr_rulebreak_r, c2in$asr_scr_rulebreak_r)$p.value,
    t.test(c1in$asr_scr_intrusive_r, c2in$asr_scr_intrusive_r)$p.value,
    t.test(c1in$asr_scr_internal_r, c2in$asr_scr_internal_r)$p.value,
    t.test(c1in$asr_scr_external_r, c2in$asr_scr_external_r)$p.value,
    t.test(c1in$asr_scr_totprob_r, c2in$asr_scr_totprob_r)$p.value,
    t.test(c1in$asr_scr_depress_r, c2in$asr_scr_depress_r)$p.value,
    t.test(c1in$asr_scr_anxdisord_r, c2in$asr_scr_anxdisord_r)$p.value,
    t.test(c1in$asr_scr_somaticpr_r, c2in$asr_scr_somaticpr_r)$p.value,
    t.test(c1in$asr_scr_avoidant_r, c2in$asr_scr_avoidant_r)$p.value,
    t.test(c1in$asr_scr_adhd_r, c2in$asr_scr_adhd_r)$p.value,
    t.test(c1in$asr_scr_antisocial_r, c2in$asr_scr_antisocial_r)$p.value,
    t.test(c1in$asr_scr_inattention_r, c2in$asr_scr_inattention_r)$p.value,
    t.test(c1in$asr_scr_hyperactive_r, c2in$asr_scr_hyperactive_r)$p.value)
mean(pvals)



f_summary <- input_test_df |>
    group_by(cluster) |>
    count(F) |>
    mutate(Percent = round(n / sum(n) * 100, 1))
f_summary$F <- factor(f_summary$F)
ggplot(f_summary,
    aes(x = cluster, y = Percent, fill = F)) +
    geom_bar(stat = "identity", position = position_stack()) +
    geom_text(aes(label = paste(Percent, "%"), y = Percent),
            position = position_stack(vjust = 0.5), size = 6) +
    labs(x = "Cluster", y = "Percentage", fill = "Sex") +
    theme_bw() +
    theme(text = element_text(size = 30)) +
    scale_fill_discrete(labels = c("F", "M"))

ggsave(image_path("test_sex_bar.png"), height = 6, width = 8, dpi = 300)


colnames(input_test_df)

white_summary <- input_test_df |>
    group_by(cluster) |>
    count(non_white) |>
    mutate(Percent = round(n / sum(n) * 100, 1))
white_summary$non_white <- factor(white_summary$non_white, levels = c(1, 0))
ggplot(white_summary,
    aes(x = cluster, y = Percent, fill = non_white)) +
    geom_bar(stat = "identity", position = position_stack()) +
    geom_text(aes(label = paste(Percent, "%"), y = Percent),
            position = position_stack(vjust = 0.5), size = 6) +
    labs(x = "Cluster", y = "Percentage", fill = "Race") +
    theme_bw() +
    theme(text = element_text(size = 30)) +
    scale_fill_discrete(labels = c("Non-white", "White"))
ggsave(image_path("test_white_bar.png"), height = 6, width = 8, dpi = 300)


parent_psych_summary <- input_test_df |>
    group_by(cluster) |>
    count(parent_psych) |>
    mutate(Percent = round(n / sum(n) * 100, 1))
parent_psych_summary$parent_psych <-
    factor(parent_psych_summary$parent_psych, levels = c(1, 0))
ggplot(parent_psych_summary,
    aes(x = cluster, y = Percent, fill = parent_psych)) +
    geom_bar(stat = "identity", position = position_stack()) +
    geom_text(aes(label = paste(Percent, "%"), y = Percent),
            position = position_stack(vjust = 0.5), size = 6) +
    labs(x = "Cluster",
         y = "Percentage",
         fill = "Parent\nPsychopathology\nScore") +
    theme_bw() +
    theme(text = element_text(size = 30)) +
    scale_fill_discrete(labels = c("Clinical", "Normal"))

ggsave(image_path("test_parent_psych_bar.png"), height = 6, dpi = 300)

```


# Permutation testing the inputs again

```{r}
permutation_test <- function(df, param, title, save_plot = FALSE) {
    vals1 <- df[, param][df[, "cluster"] == 1]
    vals2 <- df[, param][df[, "cluster"] == 2]
    true_diff <- mean(vals1) - mean(vals2)
    results <- c()
    all_vals <- c(vals1, vals2)
    set.seed(42)
    for (i in 1:10000) {
        number_in_c1 <- 6
        c1_indices <- sample(67, size = number_in_c1)
        c2_indices <- which(!(1:67 %in% c1_indices))
        mock_c1 <- all_vals[c1_indices]
        mock_c2 <- all_vals[c2_indices]
        mean_difference <- mean(mock_c1) - mean(mock_c2)
        results <- c(results, mean_difference)
    }
    percentile <- ecdf(results)
    print(paste0("The true mean difference: ", signif(true_diff, 2)))
    print("The 5% and 95% percentiles:")
    print(quantile(results, probs = c(0.05, 0.95)))
    p_value <- length(which(results >= true_diff)) / (length(results))
    print(paste0("p-value: ", p_value))
    if (save_plot) {
        png(image_path(paste0("lp_ptest_", param, ".png")),
            height = 5,
            width = 5,
            units = "in",
            res = 300)
        par(mar=c(5,6,4,1)+.1)
        hist(results,
             cex.lab = 2,
             cex.axis = 2,
             cex.main = 2,
             cex.sub = 2,
             xlab = "Mean Difference",
             main = title)
        abline(v = true_diff,
            col = "red")
        dev.off()
    } else {
        par(mar=c(5,6,4,1)+.1)
        hist(results,
             cex.lab = 2,
             cex.axis = 2,
             cex.main = 2,
             cex.sub = 2,
             xlab = "Mean Difference",
             main = title)
        abline(v = true_diff,
            col = "red")
    }
}

permutation_test(input_test_df, "cbcl_nausea", "Nauseous")

permutation_test(input_test_df, "cbcl_vomiting", "Vomiting")

permutation_test(input_test_df, "cbcl_dizzy", "Dizzy")

permutation_test(input_test_df, "cbcl_overtired", "Overtired")

permutation_test(input_test_df, "cbcl_sleeping_less", "Oversleeping")

permutation_test(input_test_df, "cbcl_sleeping_more", "Undersleeping")

permutation_test(input_test_df, "cbcl_depress", "Depressed") # 0.010

permutation_test(input_test_df, "cbcl_anxiety", "Anxious") # 0.0098

permutation_test(input_test_df, "cbcl_attention", "Attention issues") # 0.0013

permutation_test(input_test_df, "cbcl_aggressive", "Aggressive") # 0.0010

permutation_test(input_test_df, "F", "Female") # 0.53

permutation_test(input_test_df, "non_white", "Non-white") # 0.0018

permutation_test(input_test_df, "pubertal", "Pubertal") # 0.014

permutation_test(input_test_df,
                 "parent_psych",
                 "Clinical Parent\nPsychopathology") # 0.25


permutation_test_prop <- function(df, param, title, save_plot = FALSE) {
    vals1 <- df[, param][df[, "cluster"] == 1]
    vals2 <- df[, param][df[, "cluster"] == 2]
    prop1 <- length(which(vals1 > 0)) / length(vals1)
    prop2 <- length(which(vals2 > 0)) / length(vals2)
    prop_diff <- prop1 - prop2
    print(prop_diff)
    results <- c()
    all_vals <- c(vals1, vals2)
    set.seed(42)
    for (i in 1:1000) {
        number_in_c1 <- 6
        c1_indices <- sample(67, size = number_in_c1)
        c2_indices <- which(!(1:67 %in% c1_indices))
        mock_c1 <- all_vals[c1_indices]
        mock_c2 <- all_vals[c2_indices]
        mock_prop1 <- length(which(mock_c1 > 0)) / length(mock_c1)
        mock_prop2 <- length(which(mock_c2 > 0)) / length(mock_c2)
        mock_prop_diff <- mock_prop1 - mock_prop2
        results <- c(results, mock_prop_diff)
    }
    p_value <- length(which(results >= prop_diff)) / (length(results))
    print(p_value)
    if (save_plot) {
        png(image_path(paste0("lp_ptest_", param, ".png")),
            height = 5,
            width = 5,
            units = "in",
            res = 300)
        par(mar=c(5,6,4,1)+.1)
        hist(results,
             cex.lab = 2,
             cex.axis = 2,
             cex.main = 2,
             cex.sub = 2,
             xlab = "Difference in Proportion",
             main = title)
        abline(v = prop_diff,
            col = "red")
        dev.off()
    } else {
        par(mar=c(5,6,4,1)+.1)
        hist(results,
             cex.lab = 2,
             cex.axis = 2,
             cex.main = 2,
             cex.sub = 2,
             xlab = "Difference in Proportion",
             main = title)
        abline(v = prop_diff,
            col = "red")
    }
}

permutation_test_prop(input_test_df, "non_white", "Non-white")

permutation_test_prop(input_test_df, "F", "Female") # 0.53

permutation_test_prop(input_test_df, "non_white", "Non-white") # 0.0018

permutation_test_prop(input_test_df, "pubertal", "Pubertal") # 0.014

permutation_test_prop(input_test_df,
                 "parent_psych",
                 "Clinical Parent\nPsychopathology") # 0.25




permutation_test_prop(input_test_df, "non_white", "Non-white",
                      save_plot = TRUE)

permutation_test_prop(input_test_df, "F", "Female",
                      save_plot = TRUE) # 0.53

permutation_test_prop(input_test_df, "non_white", "Non-white",
                      save_plot = TRUE) # 0.0018

permutation_test_prop(input_test_df, "pubertal", "Pubertal",
                      save_plot = TRUE) # 0.014

permutation_test_prop(input_test_df,
                 "parent_psych",
                 "Clinical Parent\nPsychopathology", save_plot = TRUE) # 0.25

# Function for debugging
permutation_test_d <- function(df, param, title) {
    vals1 <- df[, param][df[, "cluster"] == 1]
    vals2 <- df[, param][df[, "cluster"] == 2]
    prop1 <- length(which(vals1 > 0)) / length(vals1)
    prop2 <- length(which(vals2 > 0)) / length(vals2)
    prop_diff <- prop1 - prop2
    print(prop_diff)
    results <- c()
    all_vals <- c(vals1, vals2)
    set.seed(42)
    for (i in 1:1000) {
        number_in_c1 <- 6
        c1_indices <- sample(67, size = number_in_c1)
        c2_indices <- which(!(1:67 %in% c1_indices))
        mock_c1 <- all_vals[c1_indices]
        mock_c2 <- all_vals[c2_indices]
        mock_prop1 <- length(which(mock_c1 > 0)) / length(mock_c1)
        mock_prop2 <- length(which(mock_c2 > 0)) / length(mock_c2)
        mock_prop_diff <- mock_prop1 - mock_prop2
        results <- c(results, mock_prop_diff)
    }
    p_value <- length(which(results >= prop_diff)) / (length(results))
    print(p_value)
    print(which(results == prop_diff))
}

permutation_test_d(input_test_df, "pubertal", "Pubertal") # 0.014


```

# Cohen's d

```{r}

cohens_d <- function(df, param) {
    vals1 <- df[, param][df[, "cluster"] == 1]
    vals2 <- df[, param][df[, "cluster"] == 2]
    mean1 <- mean(vals1)
    print(mean1)
    mean2 <- mean(vals2)
    print(mean2)
    n1 <- length(vals1)
    n2 <- length(vals2)
    std1 <- sd(vals1)
    std2 <- sd(vals2)
    sdp <- sqrt((std1^2 + std2^2)/2)
    d <- (mean1 - mean2) / sdp
    return(d)
}
cohens_d(input_test_df, "non_white")

```




# Neuroimaging things

```{r}

input_train_df

```




## Normalized mutual information calculations
```{r}
# Below is the NMI function I previously redefined
# full_cluster: the spectral clustering results of the full post-SNF graph
# inputs: a list of each dataframe (not affinity or distance matrix) used
# distance measures: a list of distance functions that map to inputs
rankFeaturesByNMI <- function(
    total_clustering, input_list, distance_measure_list, num_clusters,
    k_val, a_val) {
    # Dataframe to store the NMI of each feature from each input
    results_df <- data.frame(
        input = integer(),
        feature = integer(),
        nmi = double(),
        stringsAsFactors=FALSE)
    # Iterate through each feature of each input and calculate NMI
    for (input_num in seq_along(input_list)) {
        for (feature_num in seq_along(input_list[[input_num]])) {
            # Some pretty printing
            cat(paste0(
                "\nCalculating ", "input ", input_num, "/" ,
                length(input_list), ", ", "feature ", feature_num, "/",
                length(input_list[[input_num]]), "..."))
            # NMI calculation
            distance_measure <- distance_measure_list[[input_num]]
            input <- inputs[[input_num]]
            feature <- input[[feature_num]]
            d_matrix <- distance_measure(feature)
            a_matrix <- affinityMatrix(d_matrix, k_val, a_val)
            feature_clustering <- spectralClustering(a_matrix, num_clusters)
            nmi <- calNMI(total_clustering, feature_clustering)
            # Add the results to the output dataframe
            feature_name <- colnames(input_list[[input_num]])[feature_num]
            results_df[nrow(results_df) + 1,] =
                list(
                    input_num,
                    feature_name,
                    nmi)
        }
    }
    ordered_results_df <- results_df |>
        arrange(desc(nmi))
    return(ordered_results_df)
}
```
