# Clustering

## Loading and prepping data

```{r eval = FALSE}
library(dplyr)
library(abcdutils)
library(scabcd)
library(readr)
library(here)
library(ggplot2)
library(pheatmap)

# Function to import data from carbon
load_data <- function(filename, type, imputed = TRUE) {
    if (imputed) {
        impute_str <- "post-imputation/"
    } else {
        impute_str <- "pre-imputation/"
    }
    df <- read_csv(here(paste0("data/abcd/", type, "/", impute_str, filename)),
        show_col_types = FALSE)
    return(stats::na.omit(df))
}

abcd_ggsave <- function(filename, saved_plot) {
    filename <- here(paste0("data/abcd/results/figures/", filename))
    print(filename)
    ggsave(filename, saved_plot)
}

abcd_pheatmapsave <- function(filename, matrix) {
    filename <- here(paste0("data/abcd/results/figures/", filename))
    print(filename)
    pheatmap(matrix, filename = filename)
}

img_path <- function(filename) {
    img_folder <- here(paste0("data/abcd/results/figures/"))
    img_path <- paste0(img_folder, filename)
    return(img_path)
}

# Importing data
as_mtbi_loc <- load_data("as_mtbi_loc_imp.csv", type = "inputs")
as_mtbi_mechanism <- load_data("as_mtbi_mechanism_imp.csv", type = "inputs")
as_mtbi_mem_daze <- load_data("as_mtbi_mem_daze_imp.csv", type = "inputs")
d_income <- load_data("d_income_imp.csv", type = "inputs")
d_interview_age <- load_data("d_interview_age_imp.csv", type = "inputs")
d_mtbi_age <- load_data("d_mtbi_age_imp.csv", type = "inputs")
d_pubertal_status <- load_data("d_pubertal_status_imp.csv", type = "inputs")
d_race <- load_data("d_race_imp.csv", type = "inputs")
d_sex <- load_data("d_sex_imp.csv", type = "inputs")
mh_headaches <- load_data("mh_headaches_imp.csv", type = "inputs")
mh_mtbi_count <- load_data("mh_mtbi_count_imp.csv", type = "inputs")
dm_wmndf_qc <- load_data("dm_wmndf_qc.csv", imputed = FALSE, type = "inputs")
rm_gord_cor_qc <-
    load_data("rm_gord_cor_qc.csv", imputed = FALSE, type = "inputs")
rm_gord_var_qc <-
    load_data("rm_gord_var_qc.csv", imputed = FALSE, type = "inputs")
rm_subc_cor_qc <-
    load_data("rm_subc_cor_qc.csv", imputed = FALSE, type = "inputs")
rm_subc_var_qc <-
    load_data("rm_subc_var_qc.csv", imputed = FALSE, type = "inputs")
sm_cort_sa_qc <-
    load_data("sm_cort_sa_qc.csv", imputed = FALSE, type = "inputs")
sm_cort_t_qc <-
    load_data("sm_cort_t_qc.csv", imputed = FALSE, type = "inputs")
sm_subc_v_qc <-
    load_data("sm_subc_v_qc.csv", imputed = FALSE, type = "inputs")
p_loneliness <- load_data("p_loneliness_imp.csv", type = "inputs")
p_screen_time <- load_data("p_screen_time_imp.csv", type = "inputs")
p_family_function <- load_data("p_family_function_imp.csv", type = "inputs")
p_sports <- load_data("p_sports_imp.csv", type = "inputs")
p_prosocial <- load_data("p_prosocial_imp.csv", type = "inputs")
p_parent_psych <- load_data("p_parent_psych_imp.csv", type = "inputs")
p_exercise <- load_data("p_exercise_imp.csv", type = "inputs")
# Outcomes
cbcl_headaches <- load_data("cbcl_headaches_imp.csv", type = "outputs")
cbcl_nausea <- load_data("cbcl_nausea_imp.csv", type = "outputs")
cbcl_vomiting <- load_data("cbcl_vomiting_imp.csv", type = "outputs")
cbcl_dizzy <- load_data("cbcl_dizzy_imp.csv", type = "outputs")
cbcl_overtired <- load_data("cbcl_overtired_imp.csv", type = "outputs")
cbcl_sleeping_more <- load_data("cbcl_sleeping_more_imp.csv", type = "outputs")
cbcl_sleeping_less <- load_data("cbcl_sleeping_less_imp.csv", type = "outputs")
cbcl_depress <- load_data("cbcl_depress_imp.csv", type = "outputs")
cbcl_anxiety <- load_data("cbcl_anxiety_imp.csv", type = "outputs")
cbcl_attention <- load_data("cbcl_attention_imp.csv", type = "outputs")
cbcl_aggressive <- load_data("cbcl_aggressive_imp.csv", type = "outputs")
sds_sleep <- load_data("sds_sleep_imp.csv", type = "outputs")
nihtbx_list_fc <- load_data("nihtbx_list_fc_imp.csv", type = "outputs")
nihtbx_pattern_fc <- load_data("nihtbx_pattern_fc_imp.csv", type = "outputs")
nihtbx_cardsort_fc <- load_data("nihtbx_cardsort_fc_imp.csv", type = "outputs")

# Filtering to common subjects
full_df_list <- list(mtbi_loc = as_mtbi_loc,
    as_mtbi_mechanism,
    as_mtbi_mem_daze,
    d_income,
    d_interview_age,
    d_mtbi_age,
    d_pubertal_status,
    d_race,
    d_sex,
    mh_headaches,
    mh_mtbi_count,
    dm_wmndf_qc,
    rm_gord_cor_qc,
    rm_gord_var_qc,
    rm_subc_cor_qc,
    rm_subc_var_qc,
    sm_cort_sa_qc,
    sm_cort_t_qc,
    sm_subc_v_qc,
    p_loneliness,
    p_screen_time,
    p_family_function,
    p_sports,
    p_prosocial,
    p_parent_psych,
    p_exercise,
    cbcl_headaches,
    cbcl_nausea,
    cbcl_vomiting,
    cbcl_dizzy,
    cbcl_overtired,
    cbcl_sleeping_more,
    cbcl_sleeping_less,
    cbcl_depress,
    cbcl_anxiety,
    cbcl_attention,
    cbcl_aggressive,
    sds_sleep)

shared_df <- full_df_list |> purrr::reduce(dplyr::inner_join, by = "subjectkey")

common_subs <- shared_df$subjectkey

# Splitting into training and testing sets
assigned_df <- train_test_assign(train_frac = 0.8, subjects = common_subs)


# Keep only the training set
# TO-DO: rename these to train later
as_mtbi_loc <- keep_split(as_mtbi_loc, assigned_df, "train")
as_mtbi_mechanism <- keep_split(as_mtbi_mechanism, assigned_df, "train")
as_mtbi_mem_daze <- keep_split(as_mtbi_mem_daze, assigned_df, "train")
d_income <- keep_split(d_income, assigned_df, "train")
d_interview_age <- keep_split(d_interview_age, assigned_df, "train")
d_mtbi_age <- keep_split(d_mtbi_age, assigned_df, "train")
d_pubertal_status <- keep_split(d_pubertal_status, assigned_df, "train")
d_race <- keep_split(d_race, assigned_df, "train")
d_sex <- keep_split(d_sex, assigned_df, "train")
mh_headaches <- keep_split(mh_headaches, assigned_df, "train")
mh_mtbi_count <- keep_split(mh_mtbi_count, assigned_df, "train")
dm_wmndf_qc <- keep_split(dm_wmndf_qc, assigned_df, "train")
rm_gord_cor_qc <- keep_split(rm_gord_cor_qc, assigned_df, "train")
rm_gord_var_qc <- keep_split(rm_gord_var_qc, assigned_df, "train")
rm_subc_cor_qc <- keep_split(rm_subc_cor_qc, assigned_df, "train")
rm_subc_var_qc <- keep_split(rm_subc_var_qc, assigned_df, "train")
sm_cort_sa_qc <- keep_split(sm_cort_sa_qc, assigned_df, "train")
sm_cort_t_qc <- keep_split(sm_cort_t_qc, assigned_df, "train")
sm_subc_v_qc <- keep_split(sm_subc_v_qc, assigned_df, "train")
p_loneliness <- keep_split(p_loneliness, assigned_df, "train")
p_screen_time <- keep_split(p_screen_time, assigned_df, "train")
p_family_function <- keep_split(p_family_function, assigned_df, "train")
p_sports <- keep_split(p_sports, assigned_df, "train")
p_prosocial <- keep_split(p_prosocial, assigned_df, "train")
p_parent_psych <- keep_split(p_parent_psych, assigned_df, "train")
p_exercise <- keep_split(p_exercise, assigned_df, "train")
cbcl_headaches <- keep_split(cbcl_headaches, assigned_df, "train")
cbcl_nausea <- keep_split(cbcl_nausea, assigned_df, "train")
cbcl_vomiting <- keep_split(cbcl_vomiting, assigned_df, "train")
cbcl_dizzy <- keep_split(cbcl_dizzy, assigned_df, "train")
cbcl_overtired <- keep_split(cbcl_overtired, assigned_df, "train")
cbcl_sleeping_more <- keep_split(cbcl_sleeping_more, assigned_df, "train")
cbcl_sleeping_less <- keep_split(cbcl_sleeping_less, assigned_df, "train")
cbcl_depress <- keep_split(cbcl_depress, assigned_df, "train")
cbcl_anxiety <- keep_split(cbcl_anxiety, assigned_df, "train")
cbcl_attention <- keep_split(cbcl_attention, assigned_df, "train")
cbcl_aggressive <- keep_split(cbcl_aggressive, assigned_df, "train")
sds_sleep <- keep_split(sds_sleep, assigned_df, "train")
```

## SNF run to find good alpha and K hyperparameters

In this section, 'default' settings (i.e., including all variables) are used to iterate through clustering solutions from different values of alpha and K.

```{r}
# Structure containing all input data
# These data should not contain any NAs, but need not have the same subjects
data_list <- generate_data_list(mtbi_loc = as_mtbi_loc,
                                mtbi_mechanism = as_mtbi_mechanism,
                                mtbi_mem_daze = as_mtbi_mem_daze,
                                income = d_income,
                                interview_age = d_interview_age,
                                mtbi_age = d_mtbi_age,
                                pubertal_status = d_pubertal_status,
                                race = d_race,
                                sex = d_sex,
                                headaches = mh_headaches,
                                mtbi_count = mh_mtbi_count,
                                wmndf = dm_wmndf_qc,
                                gord_cor = rm_gord_cor_qc,
                                gord_var = rm_gord_var_qc,
                                subc_cor = rm_subc_cor_qc,
                                subc_var = rm_subc_var_qc,
                                cort_sa = sm_cort_sa_qc,
                                cort_t = sm_cort_t_qc,
                                subc_v = sm_subc_v_qc,
                                loneliness = p_loneliness,
                                screen_time = p_screen_time,
                                family_function = p_family_function,
                                sports = p_sports,
                                prosocial = p_prosocial,
                                parent_psych = p_parent_psych,
                                exercise = p_exercise)

# Structure containing all outcome data
outcome_list <- generate_outcome_list(cbcl_nausea = cbcl_nausea,
                                      cbcl_vomiting = cbcl_vomiting,
                                      cbcl_dizzy = cbcl_dizzy,
                                      cbcl_overtired = cbcl_overtired,
                                      cbcl_sleeping_more = cbcl_sleeping_more,
                                      cbcl_sleeping_less = cbcl_sleeping_less,
                                      cbcl_depress = cbcl_depress,
                                      cbcl_anxiety = cbcl_anxiety,
                                      cbcl_attention = cbcl_attention,
                                      cbcl_aggressive = cbcl_aggressive)


# Builds a standard design matrix only exploring SNF hyperparameters alpha and K
design_matrix_ak <- build_design_matrix_ak()

# Assess clustering minimum p-value for an ordinal dependent variable
ak_scan_om <- execute_design_matrix(data_list, design_matrix_ak, outcome_list)

write_csv(ak_scan_om,
    here("data/abcd/results/processed/2023_02_17_ak_scan_om.csv"))

# Note that the column types will be different (and more accurate) when going
#  through the read_delim function. Without doing this, you will have a lot of
#  character columns.
ak_scan_om <-
    read_delim(here("data/abcd/results/processed/2023_02_17_ak_scan_om.csv"))

min(ak_scan_om$min_p_val)
min(ak_scan_om$mean_p_val)

ak_scan_om$nclust <- as.factor(ak_scan_om$nclust)

ak_scan_om

# Highlighting the point that used the most default settings
ak_default <- ak_scan_om |>
    dplyr::filter(K == 20, alpha == 0.5)

k_scan_plot <-
    ggplot(ak_scan_om,
        mapping = aes(x = min_p_val,
                      y = mean_p_val,
                      color = nclust,
                      size = K)) +
        geom_point(data = ak_default, colour = "pink", size = 6) +
        geom_point() +
        scale_x_continuous(trans = 'log10') +
        xlab("Minimum p-value") +
        ylab("Mean p-value") +
        theme_bw() +
        theme(text = element_text(size = 20))
k_scan_plot

abcd_ggsave("2023_02_20_k_scan_plot.png", k_scan_plot)

a_scan_plot <-
    ggplot(ak_scan_om,
        mapping = aes(x = min_p_val,
                      y = mean_p_val,
                      color = nclust,
                      size = alpha)) +
        geom_point(data = ak_default, colour = "pink", size = 7) +
        geom_point() +
        scale_x_continuous(trans = 'log10') +
        xlab("Minimum p-value") +
        ylab("Mean p-value") +
        theme_bw() +
        theme(text = element_text(size = 20))
a_scan_plot

abcd_ggsave("2023_02_20_a_scan_plot.png", a_scan_plot)


# Alternative visualizations
# Min-p-values
a_k_matrix_min <- matrix(nrow = length(unique(ak_scan_om$K)),
                     ncol = length(unique(ak_scan_om$alpha)))
colnames(a_k_matrix_min) <- as.character(seq(0.3, 1, by = 0.1))
rownames(a_k_matrix_min) <- as.character(seq(10, 100, by = 10))
for (i in seq_len(nrow(ak_scan_om))) {
    print(i)
   row <- as.character(ak_scan_om[i, "K"])
   col <- as.character(ak_scan_om[i, "alpha"])
   min_p <- as.numeric(ak_scan_om[i, "min_p_val"])
   a_k_matrix_min[row, col] <- min_p
}
pheatmap(a_k_matrix_min, cluster_rows = FALSE, cluster_cols = FALSE)

abcd_pheatmapsave("2023_02_20_a_k_matrix_min.png", a_k_matrix_min)

# Mean p-values
a_k_matrix_mean <- matrix(nrow = length(unique(ak_scan_om$K)),
                          ncol = length(unique(ak_scan_om$alpha)))
colnames(a_k_matrix_mean) <- as.character(seq(0.3, 1, by = 0.1))
rownames(a_k_matrix_mean) <- as.character(seq(10, 100, by = 10))
for (i in seq_len(nrow(ak_scan_om))) {
    print(i)
   row <- as.character(ak_scan_om[i, "K"])
   col <- as.character(ak_scan_om[i, "alpha"])
   mean_p <- as.numeric(ak_scan_om[i, "mean_p_val"])
   a_k_matrix_mean[row, col] <- mean_p
}
pheatmap(a_k_matrix_mean, cluster_rows = FALSE, cluster_cols = FALSE)

abcd_pheatmapsave("2023_02_20_a_k_matrix_mean.png", a_k_matrix_mean)
```


## Full SNF run on training data

```{r}
set.seed(42)
design_matrix_base <- build_design_matrix_base()
design_matrix <- add_design_matrix_rows(design_matrix_base, 100)

#write_csv(design_matrix,
#    here(paste0("data/abcd/results/processed/full_design_matrix.csv")))

output_matrix_full <-
    execute_design_matrix(data_list, design_matrix, outcome_list)

write_csv(output_matrix_full,
    here(paste0("data/abcd/results/processed/2023_02_22_om.csv")))

output_matrix_full <-
    read_delim(here(paste0("data/abcd/results/processed/2023_02_22_om.csv")))


min(output_matrix_full$min_p_val) #3.2 e-08
min(output_matrix_full$mean_p_val) #0.00414

mc_results <- meta_cluster(output_matrix_full)

write_csv(data.frame(mc_results), here(paste0("data/abcd/results/processed/",
    "2023_02_22_mc_results.csv")))

mc_results <- as.matrix(read_delim(
    here(paste0("data/abcd/results/processed/",
                "2023_02_22_mc_results.csv"))))

# That is extremely well-separated
colnames(mc_results) <- NULL
rownames(mc_results) <- NULL
pheatmap(mc_results,
    legend_breaks = c(0, 0.5, 1, max(mc_results)),
    main = "",
    legend_labels = c("0", "0.5", "1", "ARI\n\n"),
    legend = TRUE, border_color = FALSE)

# Same thing, but saving the file
colnames(mc_results) <- NULL
rownames(mc_results) <- NULL
pheatmap(mc_results,
    legend_breaks = c(0, 0.5, 1, max(mc_results)),
    main = "",
    legend_labels = c("0", "0.5", "1", "ARI\n\n"),
    legend = TRUE,
    border_color = FALSE,
    filename = img_path("2023_02_22_mc_results.png"),
    cellheight = 6,
    width = 10,
    height = 10)
dev.off()

# Pretty art
pheatmap(mc_results, cluster_rows = FALSE, cluster_cols = FALSE)

# Same thing, but saving the file
pheatmap(mc_results, cluster_rows = FALSE, cluster_cols = FALSE,
    filename = img_path("2023_02_22_mc_pretty.png"))
dev.off()

colnames(mc_results) <- as.character(seq_len(nrow(mc_results)))
rownames(mc_results) <- as.character(seq_len(nrow(mc_results)))
```

Make sure to remove headaches from the final list of examined outcomes, as it is basically an input


## Characterizing meta-clustering results

```{r}
# Trying to plot the input design matrix as a heatmap
dm_scaled <- design_matrix
dm_scaled$row_id <- dm_scaled$row_id / max(dm_scaled$row_id)
dm_scaled$K <- dm_scaled$K / max(dm_scaled$K)
dm_scaled$alpha <- dm_scaled$alpha / max(dm_scaled$alpha)
dm_scaled$snf_scheme <- dm_scaled$snf_scheme / max(dm_scaled$snf_scheme)
dm_scaled$eigen_or_rot <- dm_scaled$eigen_or_rot / max(dm_scaled$eigen_or_rot)

out <- pheatmap(mc_results)

dm_scaled_reordered <- dm_scaled[out$tree_row[["order"]], ]

dm_reordered <- design_matrix[out$tree_row[["order"]], ]

# Heatmap of the design matrix
pheatmap(dm_scaled_reordered,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         labels_row = "",
         legend = FALSE,
         fontsize = 12)

# Same thing but saved to a file
pheatmap(dm_scaled_reordered,
    cluster_rows = FALSE,
    cluster_cols = FALSE,
    labels_row = "",
    legend = FALSE,
    fontsize = 12,
    filename = img_path("2023_02_22_dm.png"))
dev.off()

mc_pvals <- p_val_select(output_matrix_full)
mc_pvals_reordered <- mc_pvals[out$tree_row[["order"]], ]

# This is the actual important graph
pheatmap(mc_pvals_reordered,
    legend_breaks = c(0, 0.2, 0.4, 0.6, 0.8, max(mc_pvals_reordered)),
    main = "",
    legend_labels = c("0", "0.2", "0.4", "0.6", "0.8", "p-value\n\n"),
    cluster_rows = FALSE,
    legend = TRUE)

# Same one, but saved
pheatmap(mc_pvals_reordered,
    legend_breaks = c(0, 0.2, 0.4, 0.6, 0.8, max(mc_pvals_reordered)),
    main = "",
    legend_labels = c("0", "0.2", "0.4", "0.6", "0.8", "p-value\n\n"),
    cluster_rows = FALSE,
    legend = TRUE,
    filename = img_path("2023_02_22_mc_pvals.png"))
dev.off()

om_reordered <- output_matrix_full[out$tree_row[["order"]], ]

om_reordered
```

# Examining distribution of subjects across the various clustering solutions
```{r}
# A selection based on the main visual meta cluster and the p-values
best_mc <- om_reordered[6:41, ]

best_mc

best_mc_clusters <- as.matrix(subs(best_mc)[, -1])

# Visualization of cluster assignments
pheatmap(best_mc_clusters,
    cluster_rows = FALSE,
    show_rownames = FALSE,
    show_colnames = FALSE,
    legend = FALSE,
    cellwidth = 2.2)

pheatmap(best_mc_clusters,
    cluster_rows = FALSE,
    show_rownames = FALSE,
    show_colnames = FALSE,
    legend = FALSE,
    cellwidth = 2.2,
    filename = img_path("2023_02_22_cluster_assignment_heatmap.png"))
dev.off()

# Alternative visualizations
best_mc_subs <- best_mc |>
    dplyr::select(row_id, dplyr::starts_with("NDAR")) |>
    t()
colnames(best_mc_subs) <- best_mc_subs["row_id", ]
best_mc_subs <- best_mc_subs[2:nrow(best_mc_subs), ]
best_mc_subs <- as.data.frame(best_mc_subs)
best_mc_subs <- sapply(best_mc_subs, as.numeric)
row_means <- apply(X = best_mc_subs, MARGIN = 1, FUN = mean, na.rm = TRUE)
names(row_means) <- colnames(subs(best_mc))[-1]

# Shows how consistently a subject was assigned to a particular cluster
png(img_path("2023_02_22_avg_cluster.png"),
    height = 5,
    width = 5,
    units = "in",
    res = 300)
plot(row_means,
    xlab = "Subject",
    ylab = "Mean assigned cluster")
dev.off()

# Histogram form
png(img_path("2023_02_22_avg_cluster_hist.png"),
    height = 5,
    width = 5,
    units = "in",
    res = 300)
hist(row_means,
    xlab = "Mean assigned cluster",
    main = NULL)
dev.off()
```

# Choosing specific solutions to further characterize

```{r}
om_reordered

# Next steps are to evaluate a few options:
# A consensus cluster row (nah)
# A row containing everybody
# Consensus cluster row without problematic patients
# A row containing everybody without problematic patients

# Or perhaps:
# 1. The consensus results
# 2. The best results

# Best MC Subs: finding some dm rows to work with
best_mc_df <- data.frame(best_mc_subs)
colnames(best_mc_df) <- colnames(best_mc_subs)
best_mc_df$subjectkey <- rownames(best_mc_df)
rownames(best_mc_df) <- NULL

# Choosing a row to characterize by p-value
best_mc_copy <- best_mc
best_mc_copy$inc_var_count <- best_mc_copy |>
    dplyr::select(dplyr::starts_with("inc")) |>
    rowSums()

ggplot(best_mc_copy,
    aes(x = min_p_val, y = mean_p_val, label = row_id,
        color = (inc_var_count == 25))) +
    geom_point() +
    scale_x_continuous(trans = "log10") +
    scale_y_continuous(trans = "log10") +
    geom_text(hjust = 0, vjust = 0) +
    xlab("Minimum CBCL log(p-value)") +
    ylab("Mean CBCL log(p-value)") +
    labs(color = "All variables included?") +
    theme_bw() +
    theme(text = element_text(size = 15))
# ggsave(img_path("2023_02_22_solutions_by_pvals.png"))



# The rows that had the lowest min/mean p values
lowest_p_a <- best_mc[best_mc$row_id == 10, ]
lowest_p_b <- best_mc[best_mc$row_id == 84, ]

# The rows that had the lowest min/mean p-values, given all variables included
inc_all_a <- best_mc[best_mc$row_id == 28, ]
inc_all_b <- best_mc[best_mc$row_id == 48, ]

top_om_rows <-
    do.call("rbind", list(lowest_p_a, lowest_p_b, inc_all_a, inc_all_b))

# They appear to not be that similar to each other
meta_cluster(top_om_rows)

# Let me now find the consensus clustering results

best_mc_df$mean_cluster <- best_mc_df |>
    dplyr::select(-subjectkey) |>
    rowMeans()

which(best_mc_df$mean_cluster == 1.5) # subjects 40 and 118 are exactly equally distributed to cluster 1 and 2


# Dataframe to calculate deviation of clustering solns from CC soln
distance_from_cc <- data.frame(row_id = as.character(best_mc$row_id))

best_mc_df

row_distances <- vector()
for (i in seq_len(nrow(distance_from_cc))) {
   dist <- mean((best_mc_df[, i] - best_mc_df$"mean_cluster")^2)
    row_distances <- c(row_distances, dist)
}

distance_from_cc$dist <- row_distances

distance_from_cc

best_mc$dist <- row_distances


ggplot(best_mc, aes(x = min_p_val, y = dist, label = row_id, color = dist)) +
  geom_point() +
  scale_x_continuous(trans = 'log10') +
  geom_text(hjust = 0, vjust = 0) +
  theme_bw()


# row 48 appears to also be the lowest distance from the cc solution
best_mc[which(best_mc$dist == min(row_distances)), ] # row 48


```



## Are the p-values calculated properly?

```{r}
# Pick a row


om_row <- 35 # Corresponds to row_id 84, the lowest min/mean p value

best_mc


clustered_subjects <- subs(best_mc[om_row, ])
clusters <- data.frame(t(clustered_subjects))
clusters$id <- rownames(clusters)
rownames(clusters) <- NULL
colnames(clusters) <- c("cluster", "subjectkey")
clusters <- clusters[2:nrow(clusters), ]
clusters

groups <- clusters$cluster
groups

outcome_list <- list(
    clusters,
    cbcl_nausea,
    cbcl_vomiting,
    cbcl_dizzy,
    cbcl_overtired,
    cbcl_sleeping_more,
    cbcl_sleeping_less,
    cbcl_depress,
    cbcl_anxiety,
    cbcl_attention,
    cbcl_aggressive)

comparison_df <-
    outcome_list |> purrr::reduce(dplyr::inner_join, by = "subjectkey")

comparison_df$cluster <- as.factor(comparison_df$cluster)


colnames(comparison_df)

dim(comparison_df)

# Using ordinal regression, the p-values are very low
8 * ord_reg_p(clusters, cbcl_nausea, "cbcl_nausea") # 0.0001365547
8 * ord_reg_p(clusters, cbcl_dizzy, "cbcl_dizzy")
8 * ord_reg_p(clusters, cbcl_overtired, "cbcl_overtired")
8 * ord_reg_p(clusters, cbcl_sleeping_more, "cbcl_sleeping_more")
8 * ord_reg_p(clusters, cbcl_sleeping_less, "cbcl_sleeping_less")
8 * ord_reg_p(clusters, cbcl_anxiety, "cbcl_anxiety")
8 * ord_reg_p(clusters, cbcl_attention, "cbcl_attention")
8 * ord_reg_p(clusters, cbcl_aggressive, "cbcl_aggressive")


pval_vec <- c(
    8 * ord_reg_p(clusters, cbcl_nausea, "cbcl_nausea"), # 0.0001365547 raw
    8 * ord_reg_p(clusters, cbcl_dizzy, "cbcl_dizzy"),
    8 * ord_reg_p(clusters, cbcl_overtired, "cbcl_overtired"),
    8 * ord_reg_p(clusters, cbcl_sleeping_more, "cbcl_sleeping_more"),
    8 * ord_reg_p(clusters, cbcl_sleeping_less, "cbcl_sleeping_less"),
    8 * ord_reg_p(clusters, cbcl_anxiety, "cbcl_anxiety"),
    8 * ord_reg_p(clusters, cbcl_attention, "cbcl_attention"),
    8 * ord_reg_p(clusters, cbcl_aggressive, "cbcl_aggressive"))

mean(pval_vec)

c1_df <- comparison_df |> dplyr::filter(cluster == 1)
c2_df <- comparison_df |> dplyr::filter(cluster == 2)

colnames(c1_df)

nrow(c1_df) # 111
nrow(c2_df) # 142

# How many borderline/clinical patients in each cluster?
length(which(c1_df$cbcl_nausea > 0))
length(which(c1_df$cbcl_dizzy > 0))
length(which(c1_df$cbcl_overtired > 0))
length(which(c1_df$cbcl_sleeping_more > 0))
length(which(c1_df$cbcl_sleeping_less > 0))
length(which(c1_df$cbcl_depress > 0))
length(which(c1_df$cbcl_anxiety > 0))
length(which(c1_df$cbcl_attention > 0))
length(which(c1_df$cbcl_aggressive > 0))

length(which(c2_df$cbcl_nausea > 0))
length(which(c2_df$cbcl_dizzy > 0))
length(which(c2_df$cbcl_overtired > 0))
length(which(c2_df$cbcl_sleeping_more > 0))
length(which(c2_df$cbcl_sleeping_less > 0))
length(which(c2_df$cbcl_depress > 0))
length(which(c2_df$cbcl_anxiety > 0))
length(which(c2_df$cbcl_attention > 0))
length(which(c2_df$cbcl_aggressive > 0))

# Proportions:
length(which(c1_df$cbcl_nausea > 0)) / nrow(c1_df) * 100
length(which(c1_df$cbcl_dizzy > 0)) / nrow(c1_df) * 100
length(which(c1_df$cbcl_overtired > 0)) / nrow(c1_df) * 100
length(which(c1_df$cbcl_sleeping_more > 0)) / nrow(c1_df) * 100
length(which(c1_df$cbcl_sleeping_less > 0)) / nrow(c1_df) * 100
length(which(c1_df$cbcl_depress > 0)) / nrow(c1_df) * 100
length(which(c1_df$cbcl_anxiety > 0)) / nrow(c1_df) * 100
length(which(c1_df$cbcl_attention > 0)) / nrow(c1_df) * 100
length(which(c1_df$cbcl_aggressive > 0)) / nrow(c1_df) * 100

length(which(c2_df$cbcl_nausea > 0)) / nrow(c2_df) * 100
length(which(c2_df$cbcl_dizzy > 0)) / nrow(c2_df) * 100
length(which(c2_df$cbcl_overtired > 0)) / nrow(c2_df) * 100
length(which(c2_df$cbcl_sleeping_more > 0)) / nrow(c2_df) * 100
length(which(c2_df$cbcl_sleeping_less > 0)) / nrow(c2_df) * 100
length(which(c2_df$cbcl_depress > 0)) / nrow(c2_df) * 100
length(which(c2_df$cbcl_anxiety > 0)) / nrow(c2_df) * 100
length(which(c2_df$cbcl_attention > 0)) / nrow(c2_df) * 100
length(which(c2_df$cbcl_aggressive > 0)) / nrow(c2_df) * 100


c1_df$cbcl_total <- c1_df |>
    dplyr::select(dplyr::contains("cbcl")) |>
    rowSums()

c2_df$cbcl_total <- c2_df |>
    dplyr::select(dplyr::contains("cbcl")) |>
    rowSums()

c1_df$cbcl_total[c1_df$cbcl_total > 0] <- 1
c2_df$cbcl_total[c2_df$cbcl_total > 0] <- 1

c1_df

# Odds ratio calcs
c1_bad <- length(which(c1_df$cbcl_total > 0))
c1_good <- length(which(c1_df$cbcl_total == 0))
c2_bad <- length(which(c2_df$cbcl_total > 0))
c2_good <- length(which(c2_df$cbcl_total == 0))
# C2 ~ Not exposed
# C1 ~ Exposed
# good ~ Healthy
# bad ~ Diseased
odds_ratio <- function(DE, HE, DN, HN) {
    numerator <- DE / HE
    denominator <- DN / HN
    return(numerator / denominator)
}
odds_ratio(DE = c1_bad, HE = c1_good, DN = c2_bad, HN = c2_good)
ors <- vector()
for (i in 1:1000) {
    bootstrap_c1 <- sample(c1_df$cbcl_total, replace = TRUE)
    bootstrap_c2 <- sample(c2_df$cbcl_total, replace = TRUE)
    c1_bad <- length(which(bootstrap_c1 > 0))
    c1_good <- length(which(bootstrap_c1 == 0))
    c2_bad <- length(which(bootstrap_c2 > 0))
    c2_good <- length(which(bootstrap_c2 == 0))
    ors <- c(ors,
             odds_ratio(DE = c1_bad, HE = c1_good, DN = c2_bad, HN = c2_good))
}
quantile(ors, probs = c(0.05, 0.95))
sample(c1_df$cbcl_total)
```




# See if we can get the label prop results using the design matrix approach
```{r}
# Importing data again
as_mtbi_loc <- load_data("as_mtbi_loc_imp.csv", type = "inputs")
as_mtbi_mechanism <- load_data("as_mtbi_mechanism_imp.csv", type = "inputs")
as_mtbi_mem_daze <- load_data("as_mtbi_mem_daze_imp.csv", type = "inputs")
d_income <- load_data("d_income_imp.csv", type = "inputs")
d_interview_age <- load_data("d_interview_age_imp.csv", type = "inputs")
d_mtbi_age <- load_data("d_mtbi_age_imp.csv", type = "inputs")
d_pubertal_status <- load_data("d_pubertal_status_imp.csv", type = "inputs")
d_race <- load_data("d_race_imp.csv", type = "inputs")
d_sex <- load_data("d_sex_imp.csv", type = "inputs")
mh_headaches <- load_data("mh_headaches_imp.csv", type = "inputs")
mh_mtbi_count <- load_data("mh_mtbi_count_imp.csv", type = "inputs")
dm_wmndf_qc <- load_data("dm_wmndf_qc.csv", imputed = FALSE, type = "inputs")
rm_gord_cor_qc <-
    load_data("rm_gord_cor_qc.csv", imputed = FALSE, type = "inputs")
rm_gord_var_qc <-
    load_data("rm_gord_var_qc.csv", imputed = FALSE, type = "inputs")
rm_subc_cor_qc <-
    load_data("rm_subc_cor_qc.csv", imputed = FALSE, type = "inputs")
rm_subc_var_qc <-
    load_data("rm_subc_var_qc.csv", imputed = FALSE, type = "inputs")
sm_cort_sa_qc <-
    load_data("sm_cort_sa_qc.csv", imputed = FALSE, type = "inputs")
sm_cort_t_qc <-
    load_data("sm_cort_t_qc.csv", imputed = FALSE, type = "inputs")
sm_subc_v_qc <-
    load_data("sm_subc_v_qc.csv", imputed = FALSE, type = "inputs")
p_loneliness <- load_data("p_loneliness_imp.csv", type = "inputs")
p_screen_time <- load_data("p_screen_time_imp.csv", type = "inputs")
p_family_function <- load_data("p_family_function_imp.csv", type = "inputs")
p_sports <- load_data("p_sports_imp.csv", type = "inputs")
p_prosocial <- load_data("p_prosocial_imp.csv", type = "inputs")
p_parent_psych <- load_data("p_parent_psych_imp.csv", type = "inputs")
p_exercise <- load_data("p_exercise_imp.csv", type = "inputs")
# Outcomes
cbcl_headaches <- load_data("cbcl_headaches_imp.csv", type = "outputs")
cbcl_nausea <- load_data("cbcl_nausea_imp.csv", type = "outputs")
cbcl_vomiting <- load_data("cbcl_vomiting_imp.csv", type = "outputs")
cbcl_dizzy <- load_data("cbcl_dizzy_imp.csv", type = "outputs")
cbcl_overtired <- load_data("cbcl_overtired_imp.csv", type = "outputs")
cbcl_sleeping_more <- load_data("cbcl_sleeping_more_imp.csv", type = "outputs")
cbcl_sleeping_less <- load_data("cbcl_sleeping_less_imp.csv", type = "outputs")
cbcl_depress <- load_data("cbcl_depress_imp.csv", type = "outputs")
cbcl_anxiety <- load_data("cbcl_anxiety_imp.csv", type = "outputs")
cbcl_attention <- load_data("cbcl_attention_imp.csv", type = "outputs")
cbcl_aggressive <- load_data("cbcl_aggressive_imp.csv", type = "outputs")
sds_sleep <- load_data("sds_sleep_imp.csv", type = "outputs")
nihtbx_list_fc <- load_data("nihtbx_list_fc_imp.csv", type = "outputs")
nihtbx_pattern_fc <- load_data("nihtbx_pattern_fc_imp.csv", type = "outputs")
nihtbx_cardsort_fc <- load_data("nihtbx_cardsort_fc_imp.csv", type = "outputs")

as_mtbi_loc_train <- keep_split(as_mtbi_loc, assigned_df, "train")
as_mtbi_mechanism_train <- keep_split(as_mtbi_mechanism, assigned_df, "train")
as_mtbi_mem_daze_train <- keep_split(as_mtbi_mem_daze, assigned_df, "train")
d_income_train <- keep_split(d_income, assigned_df, "train")
d_interview_age_train <- keep_split(d_interview_age, assigned_df, "train")
d_mtbi_age_train <- keep_split(d_mtbi_age, assigned_df, "train")
d_pubertal_status_train <- keep_split(d_pubertal_status, assigned_df, "train")
d_race_train <- keep_split(d_race, assigned_df, "train")
d_sex_train <- keep_split(d_sex, assigned_df, "train")
mh_headaches_train <- keep_split(mh_headaches, assigned_df, "train")
mh_mtbi_count_train <- keep_split(mh_mtbi_count, assigned_df, "train")
dm_wmndf_qc_train <- keep_split(dm_wmndf_qc, assigned_df, "train")
rm_gord_cor_qc_train <- keep_split(rm_gord_cor_qc, assigned_df, "train")
rm_gord_var_qc_train <- keep_split(rm_gord_var_qc, assigned_df, "train")
rm_subc_cor_qc_train <- keep_split(rm_subc_cor_qc, assigned_df, "train")
rm_subc_var_qc_train <- keep_split(rm_subc_var_qc, assigned_df, "train")
sm_cort_sa_qc_train <- keep_split(sm_cort_sa_qc, assigned_df, "train")
sm_cort_t_qc_train <- keep_split(sm_cort_t_qc, assigned_df, "train")
sm_subc_v_qc_train <- keep_split(sm_subc_v_qc, assigned_df, "train")
p_loneliness_train <- keep_split(p_loneliness, assigned_df, "train")
p_screen_time_train <- keep_split(p_screen_time, assigned_df, "train")
p_family_function_train <- keep_split(p_family_function, assigned_df, "train")
p_sports_train <- keep_split(p_sports, assigned_df, "train")
p_prosocial_train <- keep_split(p_prosocial, assigned_df, "train")
p_parent_psych_train <- keep_split(p_parent_psych, assigned_df, "train")
p_exercise_train <- keep_split(p_exercise, assigned_df, "train")
cbcl_headaches_train <- keep_split(cbcl_headaches, assigned_df, "train")
cbcl_nausea_train <- keep_split(cbcl_nausea, assigned_df, "train")
cbcl_vomiting_train <- keep_split(cbcl_vomiting, assigned_df, "train")
cbcl_dizzy_train <- keep_split(cbcl_dizzy, assigned_df, "train")
cbcl_overtired_train <- keep_split(cbcl_overtired, assigned_df, "train")
cbcl_sleeping_more_train <- keep_split(cbcl_sleeping_more, assigned_df, "train")
cbcl_sleeping_less_train <- keep_split(cbcl_sleeping_less, assigned_df, "train")
cbcl_depress_train <- keep_split(cbcl_depress, assigned_df, "train")
cbcl_anxiety_train <- keep_split(cbcl_anxiety, assigned_df, "train")
cbcl_attention_train <- keep_split(cbcl_attention, assigned_df, "train")
cbcl_aggressive_train <- keep_split(cbcl_aggressive, assigned_df, "train")
sds_sleep_train <- keep_split(sds_sleep, assigned_df, "train")
as_mtbi_loc_test <- keep_split(as_mtbi_loc, assigned_df, "test")
as_mtbi_mechanism_test <- keep_split(as_mtbi_mechanism, assigned_df, "test")
as_mtbi_mem_daze_test <- keep_split(as_mtbi_mem_daze, assigned_df, "test")
d_income_test <- keep_split(d_income, assigned_df, "test")
d_interview_age_test <- keep_split(d_interview_age, assigned_df, "test")
d_mtbi_age_test <- keep_split(d_mtbi_age, assigned_df, "test")
d_pubertal_status_test <- keep_split(d_pubertal_status, assigned_df, "test")
d_race_test <- keep_split(d_race, assigned_df, "test")
d_sex_test <- keep_split(d_sex, assigned_df, "test")
mh_headaches_test <- keep_split(mh_headaches, assigned_df, "test")
mh_mtbi_count_test <- keep_split(mh_mtbi_count, assigned_df, "test")
dm_wmndf_qc_test <- keep_split(dm_wmndf_qc, assigned_df, "test")
rm_gord_cor_qc_test <- keep_split(rm_gord_cor_qc, assigned_df, "test")
rm_gord_var_qc_test <- keep_split(rm_gord_var_qc, assigned_df, "test")
rm_subc_cor_qc_test <- keep_split(rm_subc_cor_qc, assigned_df, "test")
rm_subc_var_qc_test <- keep_split(rm_subc_var_qc, assigned_df, "test")
sm_cort_sa_qc_test <- keep_split(sm_cort_sa_qc, assigned_df, "test")
sm_cort_t_qc_test <- keep_split(sm_cort_t_qc, assigned_df, "test")
sm_subc_v_qc_test <- keep_split(sm_subc_v_qc, assigned_df, "test")
p_loneliness_test <- keep_split(p_loneliness, assigned_df, "test")
p_screen_time_test <- keep_split(p_screen_time, assigned_df, "test")
p_family_function_test <- keep_split(p_family_function, assigned_df, "test")
p_sports_test <- keep_split(p_sports, assigned_df, "test")
p_prosocial_test <- keep_split(p_prosocial, assigned_df, "test")
p_parent_psych_test <- keep_split(p_parent_psych, assigned_df, "test")
p_exercise_test <- keep_split(p_exercise, assigned_df, "test")
cbcl_headaches_test <- keep_split(cbcl_headaches, assigned_df, "test")
cbcl_nausea_test <- keep_split(cbcl_nausea, assigned_df, "test")
cbcl_vomiting_test <- keep_split(cbcl_vomiting, assigned_df, "test")
cbcl_dizzy_test <- keep_split(cbcl_dizzy, assigned_df, "test")
cbcl_overtired_test <- keep_split(cbcl_overtired, assigned_df, "test")
cbcl_sleeping_more_test <- keep_split(cbcl_sleeping_more, assigned_df, "test")
cbcl_sleeping_less_test <- keep_split(cbcl_sleeping_less, assigned_df, "test")
cbcl_depress_test <- keep_split(cbcl_depress, assigned_df, "test")
cbcl_anxiety_test <- keep_split(cbcl_anxiety, assigned_df, "test")
cbcl_attention_test <- keep_split(cbcl_attention, assigned_df, "test")
cbcl_aggressive_test <- keep_split(cbcl_aggressive, assigned_df, "test")
sds_sleep_test <- keep_split(sds_sleep, assigned_df, "test")
# Begin label propagation: https://rdrr.io/cran/SNFtool/src/R/groupPredict.r


as_mtbi_loc_full <- rbind(as_mtbi_loc_train, as_mtbi_loc_test)
as_mtbi_mechanism_full <- rbind(as_mtbi_mechanism_train, as_mtbi_mechanism_test)
as_mtbi_mem_daze_full <- rbind(as_mtbi_mem_daze_train, as_mtbi_mem_daze_test)
d_income_full <- rbind(d_income_train, d_income_test)
d_interview_age_full <- rbind(d_interview_age_train, d_interview_age_test)
d_mtbi_age_full <- rbind(d_mtbi_age_train, d_mtbi_age_test)
d_pubertal_status_full <- rbind(d_pubertal_status_train, d_pubertal_status_test)
d_race_full <- rbind(d_race_train, d_race_test)
d_sex_full <- rbind(d_sex_train, d_sex_test)
mh_headaches_full <- rbind(mh_headaches_train, mh_headaches_test)
mh_mtbi_count_full <- rbind(mh_mtbi_count_train, mh_mtbi_count_test)
dm_wmndf_qc_full <- rbind(dm_wmndf_qc_train, dm_wmndf_qc_test)
rm_gord_cor_qc_full <- rbind(rm_gord_cor_qc_train, rm_gord_cor_qc_test)
rm_gord_var_qc_full <- rbind(rm_gord_var_qc_train, rm_gord_var_qc_test)
rm_subc_cor_qc_full <- rbind(rm_subc_cor_qc_train, rm_subc_cor_qc_test)
rm_subc_var_qc_full <- rbind(rm_subc_var_qc_train, rm_subc_var_qc_test)
sm_cort_sa_qc_full <- rbind(sm_cort_sa_qc_train, sm_cort_sa_qc_test)
sm_cort_t_qc_full <- rbind(sm_cort_t_qc_train, sm_cort_t_qc_test)
sm_subc_v_qc_full <- rbind(sm_subc_v_qc_train, sm_subc_v_qc_test)
p_loneliness_full <- rbind(p_loneliness_train, p_loneliness_test)
p_screen_time_full <- rbind(p_screen_time_train, p_screen_time_test)
p_family_function_full <- rbind(p_family_function_train, p_family_function_test)
p_sports_full <- rbind(p_sports_train, p_sports_test)
p_prosocial_full <- rbind(p_prosocial_train, p_prosocial_test)
p_parent_psych_full <- rbind(p_parent_psych_train, p_parent_psych_test)
p_exercise_full <- rbind(p_exercise_train, p_exercise_test)

cbcl_headaches_full <- rbind(cbcl_headaches_train, cbcl_headaches_test)
cbcl_nausea_full <- rbind(cbcl_nausea_train, cbcl_nausea_test)
cbcl_vomiting_full <- rbind(cbcl_vomiting_train, cbcl_vomiting_test)
cbcl_dizzy_full <- rbind(cbcl_dizzy_train, cbcl_dizzy_test)
cbcl_overtired_full <- rbind(cbcl_overtired_train, cbcl_overtired_test)
cbcl_sleeping_more_full <-
    rbind(cbcl_sleeping_more_train, cbcl_sleeping_more_test)
cbcl_sleeping_less_full <-
    rbind(cbcl_sleeping_less_train, cbcl_sleeping_less_test)
cbcl_depress_full <- rbind(cbcl_depress_train, cbcl_depress_test)
cbcl_anxiety_full <- rbind(cbcl_anxiety_train, cbcl_anxiety_test)
cbcl_attention_full <- rbind(cbcl_attention_train, cbcl_attention_test)
cbcl_aggressive_full <- rbind(cbcl_aggressive_train, cbcl_aggressive_test)
sds_sleep_full <- rbind(sds_sleep_train, sds_sleep_test)


full_data_list <- generate_data_list(
                                mtbi_loc = as_mtbi_loc_full,
                                mtbi_mechanism = as_mtbi_mechanism_full,
                                mtbi_mem_daze = as_mtbi_mem_daze_full,
                                income = d_income_full,
                                interview_age = d_interview_age_full,
                                mtbi_age = d_mtbi_age_full,
                                pubertal_status = d_pubertal_status_full,
                                sex = d_sex_full,
                                race = d_race_full,
                                headaches = mh_headaches_full,
                                mtbi_count = mh_mtbi_count_full,
                                wmndf = dm_wmndf_qc_full,
                                gord_cor = rm_gord_cor_qc_full,
                                gord_var = rm_gord_var_qc_full,
                                subc_cor = rm_subc_cor_qc_full,
                                subc_var = rm_subc_var_qc_full,
                                cort_sa = sm_cort_sa_qc_full,
                                cort_t = sm_cort_t_qc_full,
                                subc_v = sm_subc_v_qc_full,
                                loneliness = p_loneliness_full,
                                screen_time = p_screen_time_full,
                                family_function = p_family_function_full,
                                sports = p_sports_full,
                                prosocial = p_prosocial_full,
                                parent_psych = p_parent_psych_full,
                                exercise = p_exercise_full)

outcome_list_full <- generate_outcome_list(
    cbcl_nausea = cbcl_nausea_full,
    cbcl_vomiting = cbcl_vomiting_full,
    cbcl_dizzy = cbcl_dizzy_full,
    cbcl_overtired = cbcl_overtired_full,
    cbcl_sleeping_more = cbcl_sleeping_more_full,
    cbcl_sleeping_less = cbcl_sleeping_less_full,
    cbcl_depress = cbcl_depress_full,
    cbcl_anxiety = cbcl_anxiety_full,
    cbcl_attention = cbcl_attention_full,
    cbcl_aggressive = cbcl_aggressive_full)



# Options we've previously collected
# The best rows (from the output matrix, which isn't really needed here)
top_om_rows

# The best rows (from the design matrix)
top_dm_rows <- dm_reordered |>
    dplyr::filter(row_id %in% top_om_rows$row_id)


top_om_rows <- top_om_rows |> dplyr::arrange(by = row_id)

top_dm_rows <- top_dm_rows |> dplyr::arrange(by = row_id)


top_om_rows

top_dm_rows

current_dm_row <- top_dm_rows[1, ]
current_dm_row

current_om_row <- top_om_rows[1, ]

current_data_list <- execute_inclusion(full_data_list, current_dm_row)
current_K <- current_dm_row$K
current_alpha <- current_dm_row$alpha

fused_network <- snf_step(current_data_list,
                          "individual",
                          K = current_K,
                          alpha = current_alpha)

# Need to reorder the fused network

clustered_subs <- colnames(subs(current_om_row))[-1]

test_subs <- as_mtbi_loc_test$subjectkey

ordered_subs <- c(clustered_subs, test_subs)

fused_network <- fused_network[ordered_subs, ordered_subs]

# Looks good
fused_network[1:5, 1:5]
clustered_subs[1:5]


clustered_subjects <- subs(best_mc[om_row, ])

# Ahh.. gotta fix something in here


clustered_subjects <- subs(current_om_row)
clusters <- data.frame(t(clustered_subjects))
clusters$id <- rownames(clusters)
rownames(clusters) <- NULL
colnames(clusters) <- c("cluster", "subjectkey")
clusters <- clusters[2:nrow(clusters), ]
clusters

groups <- clusters$cluster
groups



Y0 <- matrix(0, nrow(fused_network), as.numeric(max(groups)))

Y0
groups <- as.numeric(groups)
for (i in 1:length(groups)){
    Y0[i,groups[i]] <- 1
}
## Need their internal prediction function:
.csPrediction <- function(W,Y0,method){
  alpha=0.9;
  P= W/rowSums(W)
  if(method==0){
    Y= (1-alpha)* solve( diag(dim(P)[1])- alpha*P)%*%Y0;
  } else {
    NLabel=which(rowSums(Y0)==0)[1]-1;
    Y=Y0;
    for (i in 1:1000){
      Y=P%*%Y;
      Y[1:NLabel,]=Y0[1:NLabel,];
    }
  }
  return(Y);
}
### End of their internal function
Y <- .csPrediction(W = full_fused_network,Y0,method = TRUE)
newgroups <- rep(0,nrow(full_fused_network))
for (i in 1:nrow(Y)){
    newgroups[i] <- which(Y[i,] == max(Y[i,]))
}
newgroups
full_clusters <- as_mtbi_loc_full |> dplyr::select("subjectkey")
full_clusters$cluster <- newgroups
testing_subs <- as_mtbi_loc_test$subjectkey
labeled_test <- full_clusters[full_clusters$subjectkey %in% testing_subs, ]
test_evaluation_list <- list(
    labeled_test,
    cbcl_nausea,
    cbcl_vomiting,
    cbcl_dizzy,
    cbcl_overtired,
    cbcl_sleeping_more,
    cbcl_sleeping_less,
    cbcl_depress,
    cbcl_anxiety,
    cbcl_attention,
    cbcl_aggressive)
test_evaluation_df <- test_evaluation_list |>
    purrr::reduce(dplyr::inner_join, by = "subjectkey")
test_evaluation_df$cluster <- as.numeric(test_evaluation_df$cluster)
test_clusters <- test_evaluation_df |>
    dplyr::select("subjectkey", "cluster") |>
    data.frame()
ord_reg_p(test_clusters, cbcl_dizzy, "cbcl_dizzy")
ord_reg_p(test_clusters, cbcl_nausea, "cbcl_nausea")
ord_reg_p(test_clusters, cbcl_overtired, "cbcl_overtired")
ord_reg_p(test_clusters, cbcl_sleeping_more, "cbcl_sleeping_more")
ord_reg_p(test_clusters, cbcl_sleeping_less, "cbcl_sleeping_less")
ord_reg_p(test_clusters, cbcl_anxiety, "cbcl_anxiety")
ord_reg_p(test_clusters, cbcl_attention, "cbcl_attention")
ord_reg_p(test_clusters, cbcl_aggressive, "cbcl_aggressive")
c1_test_df <- test_evaluation_df |> dplyr::filter(cluster == 1)
c2_test_df <- test_evaluation_df |> dplyr::filter(cluster == 2)
nrow(c1_test_df) # 4
nrow(c2_test_df) # 63
# How many borderline/clinical patients in each cluster?
#length(which(c1_test_df$cbcl_nausea > 0))
#length(which(c1_test_df$cbcl_dizzy > 0))
#length(which(c1_test_df$cbcl_overtired > 0))
#length(which(c1_test_df$cbcl_sleeping_more > 0))
#length(which(c1_test_df$cbcl_sleeping_less > 0))
#length(which(c1_test_df$cbcl_depress > 0))
#length(which(c1_test_df$cbcl_anxiety > 0))
#length(which(c1_test_df$cbcl_attention > 0))
#length(which(c1_test_df$cbcl_aggressive > 0))
## C2 counts
#length(which(c2_test_df$cbcl_nausea > 0))
#length(which(c2_test_df$cbcl_dizzy > 0))
#length(which(c2_test_df$cbcl_overtired > 0))
#length(which(c2_test_df$cbcl_sleeping_more > 0))
#length(which(c2_test_df$cbcl_sleeping_less > 0))
#length(which(c2_test_df$cbcl_depress > 0))
#length(which(c2_test_df$cbcl_anxiety > 0))
#length(which(c2_test_df$cbcl_attention > 0))
#length(which(c2_test_df$cbcl_aggressive > 0))
# Hm... I believe it is on to something.
#length(which(c1_test_df$cbcl_nausea > 0)) / nrow(c1_test_df) * 100
#length(which(c1_test_df$cbcl_dizzy > 0)) / nrow(c1_test_df) * 100
#length(which(c1_test_df$cbcl_overtired > 0)) / nrow(c1_test_df) * 100
#length(which(c1_test_df$cbcl_sleeping_more > 0)) / nrow(c1_test_df) * 100
#length(which(c1_test_df$cbcl_sleeping_less > 0)) / nrow(c1_test_df) * 100
#length(which(c1_test_df$cbcl_depress > 0)) / nrow(c1_test_df) * 100
#length(which(c1_test_df$cbcl_anxiety > 0)) / nrow(c1_test_df) * 100
#length(which(c1_test_df$cbcl_attention > 0)) / nrow(c1_test_df) * 100
#length(which(c1_test_df$cbcl_aggressive > 0)) / nrow(c1_test_df) * 100
## c2 proportions
#length(which(c2_test_df$cbcl_nausea > 0)) / nrow(c2_test_df) * 100
#length(which(c2_test_df$cbcl_dizzy > 0)) / nrow(c2_test_df) * 100
#length(which(c2_test_df$cbcl_overtired > 0)) / nrow(c2_test_df) * 100
#length(which(c2_test_df$cbcl_sleeping_more > 0)) / nrow(c2_test_df) * 100
#length(which(c2_test_df$cbcl_sleeping_less > 0)) / nrow(c2_test_df) * 100
#length(which(c2_test_df$cbcl_depress > 0)) / nrow(c2_test_df) * 100
#length(which(c2_test_df$cbcl_anxiety > 0)) / nrow(c2_test_df) * 100
#length(which(c2_test_df$cbcl_attention > 0)) / nrow(c2_test_df) * 100
#length(which(c2_test_df$cbcl_aggressive > 0)) / nrow(c2_test_df) * 100
# More rigorous random simulation based testing
c1_test_df
c2_test_df
c1_test_df$cbcl_total <- c1_test_df |>
    dplyr::select(dplyr::contains("cbcl")) |>
    rowSums()
c2_test_df$cbcl_total <- c2_test_df |>
    dplyr::select(dplyr::contains("cbcl")) |>
    rowSums()

# A new thing thrown in for testing
c1_test_df <- c1_test_df |>
    rowwise() |>
    dplyr::mutate(max_impair=max(c_across(cbcl_nausea:cbcl_aggressive)))
c2_test_df <- c2_test_df |>
    rowwise() |>
    dplyr::mutate(max_impair=max(c_across(cbcl_nausea:cbcl_aggressive)))


c1_impaired_frac <- length(which(c1_test_df$max_impair > 1)) / nrow(c1_test_df)
c2_impaired_frac <- length(which(c2_test_df$max_impair > 1)) / nrow(c2_test_df)
true_diff <- c1_impaired_frac - c2_impaired_frac

test_evaluation_df$cbcl_total <- test_evaluation_df |>
    dplyr::select(dplyr::contains("cbcl")) |>
    rowSums()

test_evaluation_df <- test_evaluation_df |>
    rowwise() |>
    dplyr::mutate(max_impair=max(c_across(cbcl_nausea:cbcl_aggressive)))

# Trying to pull out random splits of the testing data
vector <- c()
set.seed(42)
for (i in 1:10000) {
    number_in_c1 <- sample.int(66, 1)
    c1_indices <- sample(67, size = number_in_c1)
    c2_indices <- which(!(1:67 %in% c1_indices))
    mock_c1_df <- test_evaluation_df[c1_indices, c("cluster", "max_impair")]
    mock_c2_df <- test_evaluation_df[c2_indices, c("cluster", "max_impair")]
    c1_impaired_frac <-
        length(which(mock_c1_df$max_impair > 1)) / nrow(mock_c1_df)
    c2_impaired_frac <-
        length(which(mock_c2_df$max_impair > 1)) / nrow(mock_c2_df)
    difference <- c1_impaired_frac - c2_impaired_frac
    print(i)
    vector <- c(vector, difference)
    if (is.nan(difference)) {
        print(c1_impaired_frac)
        print(c2_impaired_frac)
        print(number_in_c1)
    }
}
percentile <- ecdf(vector)
1 - percentile(true_diff) # The p-value
# This is an essential plot
hist(vector,col="gray",las=1,main="", breaks=30)
abline(v=true_diff,col="red")

# Praise it. PRAISE IT

```









## Input variable characterization

```{r}

d_sex_train <- d_sex[d_sex$subjectkey %in% training_subs, ]

train_input_char <- list(clusters,
    as_mtbi_loc_train,
    as_mtbi_mechanism_train,
    as_mtbi_mem_daze_train,
    d_income_train,
    d_interview_age_train,
    d_mtbi_age_train,
    d_pubertal_status_train,
    d_race_train,
    d_sex_train,
    mh_headaches_train,
    mh_mtbi_count_train,
    p_loneliness_train,
    p_screen_time_train,
    p_family_function_train,
    p_sports_train,
    p_prosocial_train,
    p_parent_psych_train,
    p_exercise_train)



input_df <- train_input_char |>
    purrr::reduce(dplyr::inner_join, by = "subjectkey")

colnames(input_df)

c1in <- input_df[input_df$cluster == 1, ]
c2in <- input_df[input_df$cluster == 2, ]

# More females in c1
length(which(c1in$M == 0)) / length(c1in$M) # 46% F
length(which(c2in$M == 0)) / length(c2in$M) # 37% F

# NS
t.test(c1in$interview_age, c2in$interview_age)

# NS
t.test(c1in$latest_mtbi_age, c2in$latest_mtbi_age)

# More LOC in c1
length(which(c1in$latest_mtbi_loc == 1)) / length(c1in$latest_mtbi_loc) # 30%
length(which(c2in$latest_mtbi_loc == 1)) / length(c2in$latest_mtbi_loc) # 19%



# p = 2.06e-07; significantly higher pubertal status in c1
t.test(c1in$pubertal_status, c2in$pubertal_status)

m1 <- mean(c1in$pubertal_status)
m2 <- mean(c2in$pubertal_status)
sd1 <- sd(c1in$pubertal_status)
sd2 <- sd(c2in$pubertal_status)
n1 <- length(c1in$pubertal_status)
n2 <- length(c2in$pubertal_status)

sdp <- sqrt((sd1^2 + sd2^2)/2)

(m1 - m2)/sdp


unique(c1in$pubertal_status)

unique(c2in$pubertal_status)

# Bit of a strange way to do pubertal status. Anne suggested OR for a pre/post-pubertal cutoff

# Odds ratio calcs


# C2 ~ Not exposed
# C1 ~ Exposed
# good ~ Healthy
# bad ~ Diseased

odds_ratio <- function(DE, HE, DN, HN) {
    numerator <- DE / HE
    denominator <- DN / HN
    return(numerator / denominator)
}

c1_bad <- length(which(c1in$pubertal_status > 1))
c1_good <- length(which(c1in$pubertal_status <= 1))
c2_bad <- length(which(c2in$pubertal_status > 1))
c2_good <- length(which(c2in$pubertal_status <= 1))

odds_ratio(DE = c1_bad, HE = c1_good, DN = c2_bad, HN = c2_good)

ors <- vector()
for (i in 1:1000) {
    bootstrap_c1 <- sample(c1in$pubertal_status, replace = TRUE)
    bootstrap_c2 <- sample(c2in$pubertal_status, replace = TRUE)
    c1_bad <- length(which(bootstrap_c1 > 1))
    c1_good <- length(which(bootstrap_c1 <= 1))
    c2_bad <- length(which(bootstrap_c2 > 1))
    c2_good <- length(which(bootstrap_c2 <= 1))
    ors <- c(ors,
             odds_ratio(DE = c1_bad, HE = c1_good, DN = c2_bad, HN = c2_good))
}

quantile(ors, probs = c(0.05, 0.95))

sample(c1_df$cbcl_total)


# For LOC:
c1_bad <- length(which(c1in$latest_mtbi_loc > 0))
c1_good <- length(which(c1in$latest_mtbi_loc == 0))
c2_bad <- length(which(c2in$latest_mtbi_loc > 0))
c2_good <- length(which(c2in$latest_mtbi_loc == 0))

odds_ratio(DE = c1_bad, HE = c1_good, DN = c2_bad, HN = c2_good) # 1.87

ors <- vector()
for (i in 1:1000) {
    bootstrap_c1 <- sample(c1in$latest_mtbi_loc, replace = TRUE)
    bootstrap_c2 <- sample(c2in$latest_mtbi_loc, replace = TRUE)
    c1_bad <- length(which(bootstrap_c1 > 0))
    c1_good <- length(which(bootstrap_c1 <= 0))
    c2_bad <- length(which(bootstrap_c2 > 0))
    c2_good <- length(which(bootstrap_c2 <= 0))
    ors <- c(ors,
             odds_ratio(DE = c1_bad, HE = c1_good, DN = c2_bad, HN = c2_good))
}

quantile(ors, probs = c(0.05, 0.95))

sample(c1_df$cbcl_total)


# For being female
c1_bad <- length(which(c1in$M == 0))
c1_good <- length(which(c1in$M > 0))
c2_bad <- length(which(c2in$M == 0))
c2_good <- length(which(c2in$M > 0))

odds_ratio(DE = c1_bad, HE = c1_good, DN = c2_bad, HN = c2_good) # 1.87

ors <- vector()
for (i in 1:1000) {
    bootstrap_c1 <- sample(c1in$M, replace = TRUE)
    bootstrap_c2 <- sample(c2in$M, replace = TRUE)
    c1_bad <- length(which(bootstrap_c1 == 0))
    c1_good <- length(which(bootstrap_c1 > 0))
    c2_bad <- length(which(bootstrap_c2 == 0))
    c2_good <- length(which(bootstrap_c2 > 0))
    ors <- c(ors,
             odds_ratio(DE = c1_bad, HE = c1_good, DN = c2_bad, HN = c2_good))
}
quantile(ors, probs = c(0.05, 0.95))

sample(c1_df$cbcl_total)





# Note that age is not significantly different, but pubertal status is
# Expected given females go through puberty earlier?

# More concussions in C2? strange
t.test(c1in$mtbi_count, c2in$mtbi_count)


t.test(c1in$mtbi_count, c2in$mtbi_count)

# This is actually fire emoji
pvals <- c(
    t.test(c1in$asr_scr_perstr_r, c2in$asr_scr_perstr_r)$p.value,
    t.test(c1in$asr_scr_anxdep_r, c2in$asr_scr_anxdep_r)$p.value,
    t.test(c1in$asr_scr_withdrawn_r, c2in$asr_scr_withdrawn_r)$p.value,
    t.test(c1in$asr_scr_somatic_r, c2in$asr_scr_somatic_r)$p.value,
    t.test(c1in$asr_scr_thought_r, c2in$asr_scr_thought_r)$p.value,
    t.test(c1in$asr_scr_attention_r, c2in$asr_scr_attention_r)$p.value,
    t.test(c1in$asr_scr_aggressive_r, c2in$asr_scr_aggressive_r)$p.value,
    t.test(c1in$asr_scr_rulebreak_r, c2in$asr_scr_rulebreak_r)$p.value,
    t.test(c1in$asr_scr_intrusive_r, c2in$asr_scr_intrusive_r)$p.value,
    t.test(c1in$asr_scr_internal_r, c2in$asr_scr_internal_r)$p.value,
    t.test(c1in$asr_scr_external_r, c2in$asr_scr_external_r)$p.value,
    t.test(c1in$asr_scr_totprob_r, c2in$asr_scr_totprob_r)$p.value,
    t.test(c1in$asr_scr_depress_r, c2in$asr_scr_depress_r)$p.value,
    t.test(c1in$asr_scr_anxdisord_r, c2in$asr_scr_anxdisord_r)$p.value,
    t.test(c1in$asr_scr_somaticpr_r, c2in$asr_scr_somaticpr_r)$p.value,
    t.test(c1in$asr_scr_avoidant_r, c2in$asr_scr_avoidant_r)$p.value,
    t.test(c1in$asr_scr_adhd_r, c2in$asr_scr_adhd_r)$p.value,
    t.test(c1in$asr_scr_antisocial_r, c2in$asr_scr_antisocial_r)$p.value,
    t.test(c1in$asr_scr_inattention_r, c2in$asr_scr_inattention_r)$p.value,
    t.test(c1in$asr_scr_hyperactive_r, c2in$asr_scr_hyperactive_r)$p.value)

mean(pvals)

physical_activity1_y
physical_activity2_y



c1in$asr_scr_perstr_r
c1in$asr_scr_anxdep_r
c1in$asr_scr_withdrawn_r
c1in$asr_scr_somatic_r
c1in$asr_scr_thought_r
c1in$asr_scr_attention_r
c1in$asr_scr_aggressive_r
c1in$asr_scr_rulebreak_r
c1in$asr_scr_intrusive_r
c1in$asr_scr_internal_r
c1in$asr_scr_external_r
c1in$asr_scr_totprob_r
c1in$asr_scr_depress_r
c1in$asr_scr_anxdisord_r
c1in$asr_scr_somaticpr_r
c1in$asr_scr_avoidant_r
c1in$asr_scr_adhd_r
c1in$asr_scr_antisocial_r
c1in$asr_scr_inattention_r
c1in$asr_scr_hyperactive_r


c1in$total_parent <- c1in |>
    dplyr::select(dplyr::contains("asr_scr")) |>
    rowSums()

c2in$total_parent <- c2in |>
    dplyr::select(dplyr::contains("asr_scr")) |>
    rowSums()

t.test(c1in$total_parent, c2in$total_parent)

t.test(c1in$total_parent, c2in$total_parent)


m1 <- mean(c1in$total_parent)
m2 <- mean(c2in$total_parent)
sd1 <- sd(c1in$total_parent)
sd2 <- sd(c2in$total_parent)

sdp <- sqrt((sd1^2 + sd2^2)/2)

(m1 - m2)/sdp

```





## Normalized mutual information calculations
```{r}
# Below is the NMI function I previously redefined
# full_cluster: the spectral clustering results of the full post-SNF graph
# inputs: a list of each dataframe (not affinity or distance matrix) used
# distance measures: a list of distance functions that map to inputs
rankFeaturesByNMI <- function(
    total_clustering, input_list, distance_measure_list, num_clusters,
    k_val, a_val) {
    # Dataframe to store the NMI of each feature from each input
    results_df <- data.frame(
        input = integer(),
        feature = integer(),
        nmi = double(),
        stringsAsFactors=FALSE)
    # Iterate through each feature of each input and calculate NMI
    for (input_num in seq_along(input_list)) {
        for (feature_num in seq_along(input_list[[input_num]])) {
            # Some pretty printing
            cat(paste0(
                "\nCalculating ", "input ", input_num, "/" ,
                length(input_list), ", ", "feature ", feature_num, "/",
                length(input_list[[input_num]]), "..."))
            # NMI calculation
            distance_measure <- distance_measure_list[[input_num]]
            input <- inputs[[input_num]]
            feature <- input[[feature_num]]
            d_matrix <- distance_measure(feature)
            a_matrix <- affinityMatrix(d_matrix, k_val, a_val)
            feature_clustering <- spectralClustering(a_matrix, num_clusters)
            nmi <- calNMI(total_clustering, feature_clustering)
            # Add the results to the output dataframe
            feature_name <- colnames(input_list[[input_num]])[feature_num]
            results_df[nrow(results_df) + 1,] =
                list(
                    input_num,
                    feature_name,
                    nmi)
        }
    }
    ordered_results_df <- results_df |>
        arrange(desc(nmi))
    return(ordered_results_df)
}
```




## Manual check of clustering results

Here, I go through the SNF process for one of the design matrix rows "by hand" instead of through the design matrix function.

```{r}
# To-do
dm_reordered[1, ]
```



