# Subtyping

## Identifying subjects

All information required for identifying children at a chronic stage following mTBI as of baseline data collection is available in the `abcd_otbi01.txt` file.
To identify subjects at a chronic stage post-mTBI, two intermediate pieces of information must be calculated from the original dataset:

* identifying which head injuries were mTBIs
* identifying the time since the most recent mTBI

The structure of the Ohio State TBI screen as used for ABCD data collection was not completely compatible with the most commonly used definition of mTBI @WYA25C6X#Blennow_Etal_2016:

At least one of the following:

* Any period of loss of consciousness
* Any loss of memory
* Any alteration in mental state
* Focal neurological deficits

but where the severity does not exceed:

* LOC over 30 minutes
* A Glasgow Coma Scale score below 13
* Post-traumatic amnesia (PTA) greater than 24 hours

A few aspects of the data collection process in the ABCD study precluded the usage of this definition:

* No information was collected regarding the GCS
* Feeling dazed and PTA were combined into a single variable, making it unclear which combination of symptoms was present
* No information was collected regarding the duration of feeling dazed or experiencing PTA

Consequently, I defined mTBI as any injury that resulted in **either**:

1. LOC for less than 30 minutes (including 0 minutes) **AND** any duration of memory loss / feeling dazed
2. LOC for less than 30 minutes but greater than 0 minutes

The fixed nature of the questionnaire also meant that some information about multiple mTBIs sustained in the same way or about a very large number of mTBIs throughout a child's life could have been lost (see the previous section on identifying children with a history of mTBI).
For my analyses, I assume these edge cases are not common enough to meaningfully change any obtained conclusions.

The code below extends the TBI dataset with the following columns:

1. If a subject has experienced an mTBI prior to baseline
2. Which of the reported head injuries were mTBIs
3. The time since a subject's most recent mTBI


```{r eval = FALSE}

library(branchabcd)
library(readr)
library(dplyr)
library(here)

# Import baseline TBI dataset
tbi <- read_delim(here("data/abcd/4.0/trauma/abcd_otbi01.txt"))

# Remove data dictionary
tbi_no_dd <- tbi[-1, ]

# Give the dataset meaningful column names (e.g., tbi_5 -> blast_inj)
tbi_renamed <- rename_tbi(tbi_no_dd)

# Add the following columns:
# mtbi = did the child previously have an mTBI?
# moderate_or_severe_tbi = did the child previously have a moderate/severe TBI?
tbi_labeled <- assign_tbi(tbi_renamed)

# In progress over here!
tbi_labeled <- tbi_labeled |>
    mutate(
        hosp_er_mtbi = case_when((hosp_er_loc < 2 & hosp_er_mem_daze == 1) |
            hosp_er_loc == 1 ~ TRUE, TRUE ~ FALSE),
        vehicle_mtbi = case_when((vehicle_loc < 2 & vehicle_mem_daze == 1) |
            vehicle_loc == 1 ~ TRUE, TRUE ~ FALSE),
        fall_hit_mtbi = case_when((fall_hit_loc < 2 & fall_hit_mem_daze == 1) |
            fall_hit_loc == 1 ~ TRUE, TRUE ~ FALSE),
        violent_hit_mtbi = case_when((violent_hit_loc < 2 & violent_hit_mem_daze == 1) |
            violent_hit_loc == 1 ~ TRUE, TRUE ~ FALSE),
        blast_mtbi = case_when((blast_loc < 2 & blast_mem_daze == 1) |
            blast_loc == 1 ~ TRUE, TRUE ~ FALSE))
    mutate(other_loc_mtbi = case_when(
        (other_loc_num - other_loc_num_over_30) > 0 ~ TRUE,
        TRUE ~ FALSE)) |>
    mutate(multi_mtbi = case_when(
        (multi_loc < 2 & multi_mem_daze == 1) | multi_loc == 1 ~ TRUE,
        TRUE ~ FALSE))



tbi_labeled <- tbi_labeled |>
    mutate(hosp_er_mtbi_mpi =
            case_when(hosp_er_mtbi ~ interview_age - hosp_er_age))
tbi_labeled <- tbi_labeled |>
    mutate(vehicle_mtbi_mpi =
            case_when(vehicle_mtbi ~ interview_age - vehicle_age))
tbi_labeled <- tbi_labeled |>
    mutate(fall_hit_mtbi_mpi =
            case_when(fall_hit_mtbi ~ interview_age - fall_hit_age))
tbi_labeled <- tbi_labeled |>
    mutate(violent_hit_mtbi_mpi =
            case_when(violent_hit_mtbi ~ interview_age - violent_hit_age))
tbi_labeled <- tbi_labeled |>
    mutate(blast_mtbi_mpi =
            case_when(blast_mtbi ~ interview_age - blast_age))
tbi_labeled <- tbi_labeled |>
    mutate(other_loc_mtbi_mpi =
            case_when(other_loc_mtbi ~ interview_age - other_loc_min_age))
tbi_labeled <- tbi_labeled |>
    mutate(multi_mtbi_mpi =
            case_when(multi_mtbi ~ interview_age - multi_effect_end_age))

```



```{r child="../subtyping-mtbi/abcd/detail_otbi01.Rmd", eval=TRUE}

```



A few types of injuries were handled differently from the rest in the above code:

* for `other_loc`, the questionnaire asked for a total number of injuries with LOC as well as a total number of injuries with LOC above 30 minutes.
    * If their difference was above 0, they were labelled as having had an mTBI.
* for `other_multi` and `other_other_multi`, insufficient information was provided to determine the severity of the associated injuries.


## Extracting subjects at a chronic stage post-mTBI


For my analyses, I consider 3 months to be the threshold at which an mTBI patient enters a chronic stage post-injury.

<div class = "moccasin">

---

```{r child="../subtyping-mtbi/abcd/get_baseline_mtbi_subjects.Rmd", eval=TRUE}

```

---

</div>

## Handling twins

To do.
