# Data extraction

## Subjects

All information required for identifying children at a chronic stage following mTBI as of baseline data collection is available in the `abcd_otbi01.txt` file.
To identify subjects at a chronic stage post-mTBI, two intermediate pieces of information must be calculated from the original dataset:

* identifying which head injuries were mTBIs
* identifying the time since the most recent mTBI

The structure of the Ohio State TBI screen as used for ABCD data collection was not completely compatible with the most commonly used definition of mTBI @WYA25C6X#Blennow_Etal_2016, which requires at least one of the following:

* Any period of loss of consciousness
* Any loss of memory
* Any alteration in mental state
* Focal neurological deficits

but none of the following:

* LOC over 30 minutes
* A Glasgow Coma Scale score below 13
* Post-traumatic amnesia (PTA) greater than 24 hours

A few aspects of the data collection process in the ABCD study precluded the usage of this definition:

* No information was collected regarding the GCS
* Feeling dazed and PTA were combined into a single variable, making it unclear which combination of symptoms was present
* No information was collected regarding the duration of feeling dazed or experiencing PTA

Consequently, I defined mTBI as any injury that resulted in **either**:

1. LOC for less than 30 minutes (including 0 minutes) **AND** any duration of memory loss / feeling dazed
2. LOC for less than 30 minutes but greater than 0 minutes
 
The fixed nature of the questionnaire also meant that some information about multiple mTBIs sustained in the same way or about a very large number of mTBIs throughout a child's life could have been lost (see the previous section on identifying children with a history of mTBI).
For my analyses, I assume these edge cases are not common enough to meaningfully change any obtained conclusions.


```{r}
library(ggplot2)
library(readr)
library(dplyr)
library(here)
library(knitr)
library(abcdutils)

raw_path <- path_maker(here(paste0("data/abcd/raw")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

# Import baseline TBI dataset
abcd_otbi01 <- read_delim(raw_path("abcd_otbi01.txt"))
# Longitudinal subjects
abcd_lpohstbi01 <- read_delim(raw_path("abcd_lpohstbi01.txt"))

# Identify baseline mtbi subjects at chronic stage post-mTBI (> 3 months)
mtbi_subjects_0 <- get_mtbi_subjects(abcd_otbi01, min_mpi = 3, t = 0)
mtbi_subjects_1 <- get_mtbi_subjects(abcd_lpohstbi01, min_mpi = 3, t = 1)
mtbi_subjects_2 <- get_mtbi_subjects(abcd_lpohstbi01, min_mpi = 3, t = 2)

# Note that the longitudinal subjects have not been filtered in any way based on
#  whether or not they also had an mTBI at bsaeline or another timepoint

write_csv(mtbi_subjects_0, sub_path("mtbi_subjects_0.csv", date = TRUE))
write_csv(mtbi_subjects_1, sub_path("mtbi_subjects_1.csv", date = TRUE))
write_csv(mtbi_subjects_2, sub_path("mtbi_subjects_2.csv", date = TRUE))

mtbi_subjects_0 <- read_csv(sub_path("2023_03_22_mtbi_subjects_0.csv"))
mtbi_subjects_1 <- read_csv(sub_path("2023_03_22_mtbi_subjects_1.csv"))
mtbi_subjects_2 <- read_csv(sub_path("2023_03_22_mtbi_subjects_2.csv"))

mtbi_subjects_0
mtbi_subjects_1
mtbi_subjects_2

which(mtbi_subjects_0$"subjectkey" %in% mtbi_subjects_1$"subjectkey")

which(mtbi_subjects_0$"subjectkey" %in% mtbi_subjects_2$"subjectkey")

which(mtbi_subjects_1$"subjectkey" %in% mtbi_subjects_2$"subjectkey")

intersect(intersect(mtbi_subjects_0$"subjectkey", mtbi_subjects_1$"subjectkey"),
          mtbi_subjects_2$"subjectkey")

Reduce(intersect, list(mtbi_subjects_0$"subjectkey",
                       mtbi_subjects_1$"subjectkey",
                       mtbi_subjects_2$"subjectkey"))

# Unique to longitudinal
colnames(q)[which(!(colnames(q) %in% colnames(w)))]

# Unique to baseline
colnames(w)[which(!(colnames(w) %in% colnames(q)))]

```


A few types of injuries were handled differently from the rest in the above code.
For the `other_loc` injury type, the questionnaire asked for a total number of injuries with LOC as well as a total number of injuries with LOC above 30 minutes.
If their difference was above 0, they were labelled as having had an mTBI.
For the `other_multi` and `other_other_multi` injury types, insufficient information was provided to determine the severity of the associated injuries.

For my analyses, I consider 3 months to be the threshold at which an mTBI patient enters a chronic stage post-injury.

## Input variables

### Acute symptoms

The acute symptom data is found within the TBI dataset.
We are interesed in the following acute symptoms:

* mechanism of injury
* age
* LOC information
* Feeling dazed or having memory loss

A few more intermediate columns need to be added to isolate these variables for the most recent mTBIs of the subjects.

```{r}
as_mtbi_mem_daze <-
    get_mtbi_mem_daze(abcd_otbi01, mtbi_subjects, t = 0)
as_mtbi_mechanism <-
    get_mtbi_mechanism(abcd_otbi01, mtbi_subjects, t = 0, format = "undummied")
as_mtbi_loc <-
    get_mtbi_loc(abcd_otbi01, mtbi_subjects, t = 0)
```

```{r}
write_csv(as_mtbi_mem_daze,
    here("data/abcd/inputs/as_mtbi_mem_daze.csv"))
write_csv(as_mtbi_mechanism,
    here("data/abcd/inputs/as_mtbi_mechanism.csv"))
write_csv(as_mtbi_loc,
    here("data/abcd/inputs/as_mtbi_loc.csv"))
```


### Demographics

Demographic variables included in the analyses are:

* Age
* Sex
* Race
* Household income
* Pubertal development status

```{r}
## Demographic dataframes
ssphp01 <- read_delim(here("data/abcd/raw/abcd_ssphp01.txt"))
ssphy01 <- read_delim(here("data/abcd/raw/abcd_ssphy01.txt"))
pdem02 <- read_delim(here("data/abcd/raw/pdem02.txt"))

## Pubertal status
d_pubertal_status <- get_pubertal_status(ssphp01, ssphy01, mtbi_subjects, t = 0)

## Age on interview
d_interview_age <- get_interview_age(abcd_otbi01, mtbi_subjects, t = 0)

## Age on injury
d_mtbi_age <- get_mtbi_age(abcd_otbi01, mtbi_subjects, t = 0)

## Sex
d_sex <- get_sex(abcd_otbi01, mtbi_subjects, t = 0)

## Household income
d_income <- get_income(pdem02, mtbi_subjects, t = 0)
```

I will be trying two separate categorizations:

1. White, black, mixed/other
2. White, black, hispanic, asian/other pacific islander, native american

The rationale for this decision can be found at (@sec-racebreakdown).


### Race
```{r}
d_race_condensed <-
    get_race(pdem02, mtbi_subjects, "condensed_dummied", t = 0)
d_race_expanded <-
    get_race(pdem02, mtbi_subjects, "expanded_dummied", t = 0)
d_race_undummied <-
    get_race(pdem02, mtbi_subjects, "condensed_undummied", t = 0)
```

Subset and export the demographic input variables:

```{r}
write_csv(d_pubertal_status,
    here("data/abcd/inputs/d_pubertal_status.csv"))
write_csv(d_interview_age,
    here("data/abcd/inputs/d_interview_age.csv"))
write_csv(d_mtbi_age,
    here("data/abcd/inputs/d_mtbi_age.csv"))
write_csv(d_sex,
    here("data/abcd/inputs/d_sex.csv"))
write_csv(d_income,
    here("data/abcd/inputs/d_income.csv"))
write_csv(d_race_condensed,
    here("data/abcd/inputs/d_race_cd.csv"))
write_csv(d_race_expanded,
    here("data/abcd/inputs/d_race_ed.csv"))
write_csv(d_race_undummied,
    here("data/abcd/inputs/d_race_cu.csv"))
```


### Medical history

Medical history variables of interest include:

1. Number of previous head injuries
    * discrete variable `mtbi_count` from the processed file `abcd_otbi01_detailed.csv`
2. History of headaches 
    * binary variable `medhx_2q` from the file ABCD Parent Medical History Questionnaire (`abcd_mx01.txt`; category Med History; release 2.0)
        * checks if subject has ever gone to doctor for bad headaches

Unfortunately, information on pain (the file `abcd_pq01.txt`), a factor noted as an important covariate by the original A-CAP study (@8VF7JUXL##Yeates_Etal_2017), was not a part of ABCD's baseline data collection.

```{r}
mx01 <- read_delim(here("data/abcd/raw/abcd_mx01.txt"))

## History of headaches
mh_headaches <- get_headaches(mx01, mtbi_subjects, t = 0)

## Number of previous mTBIs
mh_mtbi_count <- get_mtbi_count(abcd_otbi01, mtbi_subjects, t = 0)
```

Subset and export the medical history variables:

```{r}
write_csv(mh_headaches,
    here("data/abcd/inputs/mh_headaches.csv"))
write_csv(mh_mtbi_count,
    here("data/abcd/inputs/mh_mtbi_count.csv"))
```


### Neuroimaging

Variables of interest related to brain structure and function include:

* Structural: T1-weighted multishell diffusion-weighted MRI data
* Diffusion: Neurite density (restricted spectrum imaging)
* Functional: resting-state functional MRI data

The 2019 publication by Hagler et al. @UD6THTQZ##Hagler_Etal_2019 outlines the neuroimaging data present in the ABCD dataset in detail.


#### Structural MRI

The sMRI variables of interest include subcortical volumes, and cortical thicknesses, and cortical surface areas.


```{r}
## SMRI dataframes
smrip10201 <- read_delim(here("data/abcd/raw/abcd_smrip10201.txt"))
mrisdp10201 <- read_delim(here("data/abcd/raw/abcd_mrisdp10201.txt"))

## Subcortical volumes
sm_subc_v <- get_subc_v(smrip10201, mtbi_subjects, t = 0)

## Cortical thickness
sm_cort_t <- get_cort_t(mrisdp10201, mtbi_subjects, t = 0)

## Cortical volumes
sm_cort_sa <- get_cort_sa(mrisdp10201, mtbi_subjects, t = 0)

### Checking for missing subjects
smrip10201_bl <- smrip10201 |> filter_timepoint(0)
which(!(mtbi_subjects$subjectkey %in% smrip10201_bl$subjectkey))
mtbi_subjects$subjectkey[c(24, 327)]
### "NDAR_INV1ZY11ZP0" and "NDAR_INVRV742U1M" have no baseline sMRI

```

```{r}
write_csv(sm_subc_v,
    here("data/abcd/inputs/sm_subc_v.csv"))
write_csv(sm_cort_t,
    here("data/abcd/inputs/sm_cort_t.csv"))
write_csv(sm_cort_sa,
    here("data/abcd/inputs/sm_cort_sa.csv"))
```


#### Diffusion MRI

We are interested in the neurite density measures of white matter regions in the brain.
Previously, these measures were found in variables containing the string "rsindwm_cdk" within the file `mri_rsi_p102.txt`.
A change anounced in the ABCD 4.0 MRI release notes indicates that neurite density is now referred to as "restricted normalized directional" and that the relevant white matter variables contain the string "rsirndwm" within the file `abcd_drsip201.txt`.

```{r}
## DMRI dataframe
drsip201 <- read_delim(here("data/abcd/raw/abcd_drsip201.txt"))

## White matter neurite densities
dm_wmndf <- get_wmnd(drsip201, mtbi_subjects, t = 0)
```

```{r}
write_csv(dm_wmndf,
    here("data/abcd/inputs/dm_wmndf.csv"))
```


#### Resting-state functional MRI

We are interested in the following rs-fMRI measures:

- Gordon network (cortical) correlations 
- Subcortical correlations
- Gordon and subcortical temporal variances

```{r}
betnet02 <- read_delim(here("data/abcd/raw/abcd_betnet02.txt"))
mrirscor02 <- read_delim(here("data/abcd/raw/mrirscor02.txt"))
mrirstv02 <- read_delim(here("data/abcd/raw/abcd_mrirstv02.txt"))


## Cortical parcellation network correlations
rm_gord_cor <- get_gord_cor(betnet02, mtbi_subjects, t = 0)

## Subcortical parcellation network correlations
rm_subc_cor <- get_subc_cor(mrirscor02, mtbi_subjects, t = 0)

## Temporal variances - cortical parcellations
rm_gord_var <- get_gord_var(mrirstv02, mtbi_subjects, t = 0)

## Subcortical temporal variances
rm_subc_var <- get_subc_var(mrirstv02, mtbi_subjects, t = 0)
```

```{r}
write_csv(rm_gord_cor,
    here("data/abcd/inputs/rm_gord_cor.csv"))
write_csv(rm_subc_cor,
    here("data/abcd/inputs/rm_subc_cor.csv"))
write_csv(rm_subc_var,
    here("data/abcd/inputs/rm_subc_var.csv"))
write_csv(rm_gord_var,
    here("data/abcd/inputs/rm_gord_var.csv"))
```


### Psychosocial resilience

Psychosocial factors of interest include:

* loneliness
* healthy behaviours
* family function
* prosocial behaviour
* parent psychopathology

```{r}
abcd_ysr01 <- read_delim(here("data/abcd/raw/abcd_ysr01.txt"))
stq01 <- read_delim(here("data/abcd/raw/stq01.txt"))
fes02 <- read_delim(here("data/abcd/raw/fes02.txt"))
abcd_fes01 <- read_delim(here("data/abcd/raw/abcd_fes01.txt"))
abcd_saiq02 <- read_delim(here("data/abcd/raw/abcd_saiq02.txt"))
psb01 <- read_delim(here("data/abcd/raw/psb01.txt"))
abcd_psb01 <- read_delim(here("data/abcd/raw/abcd_psb01.txt"))
abcd_asrs01 <- read_delim(here("data/abcd/raw/abcd_asrs01.txt"))
abcd_yrb01 <- read_delim(here("data/abcd/raw/abcd_yrb01.txt"))


p_loneliness <- get_loneliness(abcd_ysr01, mtbi_subjects, t = 0)
p_loneliness

p_screen_time <- get_screen_time(stq01, mtbi_subjects, t = 0)
p_screen_time

p_family_function <-
    get_family_function(fes02, abcd_fes01, mtbi_subjects, t = 0)
p_family_function

p_sports <- get_sports_and_activities(abcd_saiq02, mtbi_subjects, t = 0)
p_sports

p_prosocial <- get_prosocial_behaviour(psb01, abcd_psb01, mtbi_subjects, t = 0)
p_prosocial

p_parent_psych <- get_parent_psychopathology(abcd_asrs01, mtbi_subjects, t = 0)
p_parent_psych

p_exercise <- get_exercise(abcd_yrb01, mtbi_subjects, t = 0)
p_exercise
```

Subset and export the psychosocial resilience variables:

```{r}
write_csv(p_loneliness,
    here("data/abcd/inputs/p_loneliness.csv"))
write_csv(p_screen_time,
    here("data/abcd/inputs/p_screen_time.csv"))
write_csv(p_family_function,
    here("data/abcd/inputs/p_family_function.csv"))
write_csv(p_sports,
    here("data/abcd/inputs/p_sports.csv"))
write_csv(p_prosocial,
    here("data/abcd/inputs/p_prosocial.csv"))
write_csv(p_parent_psych,
    here("data/abcd/inputs/p_parent_psych.csv"))
write_csv(p_exercise,
    here("data/abcd/inputs/p_exercise.csv"))
```


## Output variables

### Child behaviour checklist

```{r}
abcd_cbcl01 <- read_delim(here("data/abcd/raw/abcd_cbcl01.txt"))
abcd_cbcls01 <- read_delim(here("data/abcd/raw/abcd_cbcls01.txt"))

cbcl_headaches <- get_cbcl_headaches(abcd_cbcl01, mtbi_subjects, t = 0)
cbcl_nausea <- get_cbcl_nausea(abcd_cbcl01, mtbi_subjects, t = 0)
cbcl_vomiting <- get_cbcl_vomiting(abcd_cbcl01, mtbi_subjects, t = 0)
cbcl_dizzy <- get_cbcl_dizzy(abcd_cbcl01, mtbi_subjects, t = 0)
cbcl_overtired <- get_cbcl_overtired(abcd_cbcl01, mtbi_subjects, t = 0)
cbcl_sleeping_more <- get_cbcl_sleeping_more(abcd_cbcl01, mtbi_subjects, t = 0)
cbcl_sleeping_less <- get_cbcl_sleeping_less(abcd_cbcl01, mtbi_subjects, t = 0)
cbcl_depress_r <- get_cbcl_depress(abcd_cbcls01, mtbi_subjects, t = 0)
cbcl_anxiety_r <- get_cbcl_anxiety(abcd_cbcls01, mtbi_subjects, t = 0)
cbcl_attention_r <- get_cbcl_attention(abcd_cbcls01, mtbi_subjects, t = 0)
cbcl_aggressive_r <- get_cbcl_aggressive(abcd_cbcls01, mtbi_subjects, t = 0)
# Borderline/clinical thresholded instead of raw scores
cbcl_depress <- get_cbcl_depress(abcd_cbcls01, mtbi_subjects, t = 0,
                                 raw = FALSE)
cbcl_anxiety <- get_cbcl_anxiety(abcd_cbcls01, mtbi_subjects, t = 0,
                                 raw = FALSE)
cbcl_attention <- get_cbcl_attention(abcd_cbcls01, mtbi_subjects, t = 0,
                                     raw = FALSE)
cbcl_aggressive <- get_cbcl_aggressive(abcd_cbcls01, mtbi_subjects, t = 0,
                                       raw = FALSE)

```

```{r}
write_csv(cbcl_headaches,
    here("data/abcd/outputs/cbcl_headaches.csv"))
write_csv(cbcl_nausea,
    here("data/abcd/outputs/cbcl_nausea.csv"))
write_csv(cbcl_vomiting,
    here("data/abcd/outputs/cbcl_vomiting.csv"))
write_csv(cbcl_dizzy,
    here("data/abcd/outputs/cbcl_dizzy.csv"))
write_csv(cbcl_overtired,
    here("data/abcd/outputs/cbcl_overtired.csv"))
write_csv(cbcl_sleeping_more,
    here("data/abcd/outputs/cbcl_sleeping_more.csv"))
write_csv(cbcl_sleeping_less,
    here("data/abcd/outputs/cbcl_sleeping_less.csv"))
write_csv(cbcl_depress_r,
    here("data/abcd/outputs/cbcl_depress_r.csv"))
write_csv(cbcl_anxiety_r,
    here("data/abcd/outputs/cbcl_anxiety_r.csv"))
write_csv(cbcl_attention_r,
    here("data/abcd/outputs/cbcl_attention_r.csv"))
write_csv(cbcl_aggressive_r,
    here("data/abcd/outputs/cbcl_aggressive_r.csv"))
write_csv(cbcl_depress,
    here("data/abcd/outputs/cbcl_depress.csv"))
write_csv(cbcl_anxiety,
    here("data/abcd/outputs/cbcl_anxiety.csv"))
write_csv(cbcl_attention,
    here("data/abcd/outputs/cbcl_attention.csv"))
write_csv(cbcl_aggressive,
    here("data/abcd/outputs/cbcl_aggressive.csv"))
```

### NIH Toolbox

```{r}
abcd_tbss01 <- read_delim(here("data/abcd/raw/abcd_tbss01.txt"))

nihtbx_list_fc <- get_nihtbx_list_fc(abcd_tbss01, mtbi_subjects, t = 0)
nihtbx_pattern_fc <- get_nihtbx_pattern_fc(abcd_tbss01, mtbi_subjects, t = 0)
nihtbx_cardsort_fc <- get_nihtbx_cardsort_fc(abcd_tbss01, mtbi_subjects, t = 0)
```

```{r}
write_csv(nihtbx_list_fc,
    here("data/abcd/outputs/nihtbx_list_fc.csv"))
write_csv(nihtbx_pattern_fc,
    here("data/abcd/outputs/nihtbx_pattern_fc.csv"))
write_csv(nihtbx_cardsort_fc,
    here("data/abcd/outputs/nihtbx_cardsort_fc.csv"))
```

### Sleep disturbance scale

```{r}
abcd_sds01 <- read_delim(here("data/abcd/raw/abcd_sds01.txt"))

sds_sleep_df <- get_full_sleep_df(abcd_sds01, mtbi_subjects, t = 0)
```

```{r}
write_csv(sds_sleep_df,
    here("data/abcd/outputs/sds_sleep_df.csv"))
```
