---
format:
  html:
    code-fold: true
    code-tools: true
    embed-resources: true
    toc: true
    number-sections: true
execute:
    warning: false
    message: false
---

```{r}
library(ggplot2)
library(readr)
library(dplyr)
library(here)
library(abcdutils)

acap_path <- path_maker(here(paste0("data/acap/data")))

import_acap <- function(path) {
    return(readr::read_csv(acap_path(path)))
}
```

Important terms:

- anat = T1w
- gt = graph theory
- thr = thresholded (in this case at 0.25)
- "ses" reflects BIDS format for session and not socioeconomic status ("centmat")
- "value" represents raw metrics while "value_h" represents data harmonized using combat

- The `demo` folder includes a demographic dataset with demographic, injury, MRI QA, and clinical symptoms at each timepoint
    - this file is in both wide and long format to accommodate the MRI methodology (i.e., 2 scan sessions)
    - A-CAP Study data dictionary is included for reference in the same directory
- Sample sizes for sequences differ, especially for DTI because of data loss at Ottawa (described in Ashley's longitudinal paper)
- Ashley published harmonized data

```{r}
demo <- import_acap("demo/acap_demo+qa_wide_data-2021-03-05.csv")

cort_t <- import_acap("anat/ants/ants_usable_cortthick_09.14.2023.csv")
cort_v <- import_acap("anat/ants/ants_usable_cortvol_09.14.2023.csv")
subc_v <- import_acap("anat/ants/ants_usable_subcortvol_09.14.2023.csv")

gt_dwi <- import_acap("dwi/gt/gt_usable_b900_09.14.2023.csv")
gt_func <- import_acap("func/gt/gt_usable_thr_25_0_09.14.2023.csv")

# dwi <- ?
# noddi <- ?
```

Note that DWI and NODDI are empty.

```{r}
dfs <- list(
    "demo" = demo,
    "cort_t" = cort_t,
    "cort_v" = cort_v,
    "subc_v" = subc_v,
    "gt_dwi" = gt_dwi,
    "gt_func" = gt_func
)

x <- lapply(
    dfs,
    function(x) {
        cat(length(unique(x$"acapid")), "\n")
    }
)

x <- lapply(
    names(dfs),
    function(x) {
        cat(x)
        out <- utils::capture.output(dplyr::glimpse(dfs[[x]]))
        cat(out, sep = "\n") 
        cat("\n\n")
    }
)

dplyr::glimpse(demo)
```
