# Characterization of identified meta clusters

## Importing packages and establishing file paths

```{r}
library(readr)
library(abcdutils)
library(here)
library(metasnf)
library(progressr)
library(rlist)
library(MatchIt)
library(ggplot2)
library(patchwork)
library(ggsignif)

source(here("abcd/functions.R"))

input_path <- path_maker(here(paste0("data/abcd/inputs")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

mtbi_subjects <- read_csv(sub_path("2024_01_28_mtbi_subjects.csv"))
uninjured_subjects <- read_csv(sub_path("2024_01_28_uninjured_subjects.csv"))
matched_uninjured <- read_csv(sub_path("2024_01_28_matched_uninjured.csv"))
```
## Loading data and out of model lists

```{r}
data_list_m1 <- list.load(input_path("2024_01_28_data_list_m1.rds"))
data_list_m2 <- list.load(input_path("2024_01_28_data_list_m2.rds"))
data_list_m3 <- list.load(input_path("2024_01_28_data_list_m3.rds"))
data_list_m4 <- list.load(input_path("2024_01_28_data_list_m4.rds"))
data_list_m5 <- list.load(input_path("2024_01_28_data_list_m5.rds"))
data_list_pm1 <- list.load(input_path("2024_01_28_data_list_pm1.rds"))
data_list_pm2 <- list.load(input_path("2024_01_28_data_list_pm2.rds"))
data_list_pm3 <- list.load(input_path("2024_01_28_data_list_pm3.rds"))
data_list_pm4 <- list.load(input_path("2024_01_28_data_list_pm4.rds"))
data_list_pm5 <- list.load(input_path("2024_01_28_data_list_pm5.rds"))
oom_list_m1 <- list.load(input_path("2024_01_28_oom_list_m1.rds"))
oom_list_m2 <- list.load(input_path("2024_01_28_oom_list_m2.rds"))
oom_list_m3 <- list.load(input_path("2024_01_28_oom_list_m3.rds"))
oom_list_m4 <- list.load(input_path("2024_01_28_oom_list_m4.rds"))
oom_list_m5 <- list.load(input_path("2024_01_28_oom_list_m5.rds"))
oom_list_pm1 <- list.load(input_path("2024_01_28_oom_list_pm1.rds"))
oom_list_pm2 <- list.load(input_path("2024_01_28_oom_list_pm2.rds"))
oom_list_pm3 <- list.load(input_path("2024_01_28_oom_list_pm3.rds"))
oom_list_pm4 <- list.load(input_path("2024_01_28_oom_list_pm4.rds"))
oom_list_pm5 <- list.load(input_path("2024_01_28_oom_list_pm5.rds"))

data_list_mu1 <- list.load(input_path("2024_01_28_data_list_mu1.rds"))
data_list_mu2 <- list.load(input_path("2024_01_28_data_list_mu2.rds"))
data_list_mu3 <- list.load(input_path("2024_01_28_data_list_mu3.rds"))
data_list_mu4 <- list.load(input_path("2024_01_28_data_list_mu4.rds"))
data_list_mu5 <- list.load(input_path("2024_01_28_data_list_mu5.rds"))
data_list_mpu1 <- list.load(input_path("2024_01_28_data_list_mpu1.rds"))
data_list_mpu2 <- list.load(input_path("2024_01_28_data_list_mpu2.rds"))
data_list_mpu3 <- list.load(input_path("2024_01_28_data_list_mpu3.rds"))
data_list_mpu4 <- list.load(input_path("2024_01_28_data_list_mpu4.rds"))
data_list_mpu5 <- list.load(input_path("2024_01_28_data_list_mpu5.rds"))
oom_list_mu1 <- list.load(input_path("2024_01_28_oom_list_mu1.rds"))
oom_list_mu2 <- list.load(input_path("2024_01_28_oom_list_mu2.rds"))
oom_list_mu3 <- list.load(input_path("2024_01_28_oom_list_mu3.rds"))
oom_list_mu4 <- list.load(input_path("2024_01_28_oom_list_mu4.rds"))
oom_list_mu5 <- list.load(input_path("2024_01_28_oom_list_mu5.rds"))
oom_list_mpu1 <- list.load(input_path("2024_01_28_oom_list_mpu1.rds"))
oom_list_mpu2 <- list.load(input_path("2024_01_28_oom_list_mpu2.rds"))
oom_list_mpu3 <- list.load(input_path("2024_01_28_oom_list_mpu3.rds"))
oom_list_mpu4 <- list.load(input_path("2024_01_28_oom_list_mpu4.rds"))
oom_list_mpu5 <- list.load(input_path("2024_01_28_oom_list_mpu5.rds"))
```

## mTBI meta clusters

Meta-cluster B of the mTBI subjects are the ones that are of greatest interest to us.
That meta-cluster describes 3-cluster solutions that strongly separate the behavioural impairments and that exist across both solo and pooled imputations.

MCs A and C appear to be close variations of B.
D and E appear to be quite unique and are only found in the solo and pooled imputations respectively.

The tight clusters within F include F-A, F-C, F-D, F-E, and F-J.
Clusters such as F-A, F-B, F-E, F-F, and F-H show strong separation across some of those mTBI-specific variables.


```{r}
full_extended_solutions_matrix <- read_csv(
    proc_path("2024_01_29_full_mtbi_extended_solutions_matrix.csv")
)

full_oom_pvals <- pval_select(
    full_extended_solutions_matrix,
    negative_log = TRUE
)

full_extended_solutions_matrix$"mean_neglog_p" <- full_oom_pvals$"mean_neglog_p"

sm_order <- unlist(
    read_csv(proc_path("2024_01_29_aris_all_mtbi_imputations_order.csv"))
)
names(sm_order) <- NULL

sorted_solutions_matrix <- full_extended_solutions_matrix[sm_order, ]

mc_a_solutions <- sorted_solutions_matrix[1:500, ]
mc_b_solutions <- sorted_solutions_matrix[501:806, ]
mc_c_solutions <- sorted_solutions_matrix[807:956, ]
mc_d_solutions <- sorted_solutions_matrix[957:1227, ]
mc_e_solutions <- sorted_solutions_matrix[1228:1441, ]

mc_f_a_solutions <- sorted_solutions_matrix[1442:(1442 + 168), ]
mc_f_b_solutions <- sorted_solutions_matrix[(1442 + 169):(1442 + 336), ]
mc_f_c_solutions <- sorted_solutions_matrix[(1442 + 337):(1442 + 438), ]
mc_f_d_solutions <- sorted_solutions_matrix[(1442 + 439):(1442 + 513), ]
mc_f_e_solutions <- sorted_solutions_matrix[(1442 + 514):2000, ]

```

### Setting up total data lists

```{r}
all_data_list_m1 <- c(data_list_m1, oom_list_m1)
all_data_list_m2 <- c(data_list_m2, oom_list_m2)
all_data_list_m3 <- c(data_list_m3, oom_list_m3)
all_data_list_m4 <- c(data_list_m4, oom_list_m4)
all_data_list_m5 <- c(data_list_m5, oom_list_m5)
all_data_list_pm1 <- c(data_list_pm1, oom_list_pm1)
all_data_list_pm2 <- c(data_list_pm2, oom_list_pm2)
all_data_list_pm3 <- c(data_list_pm3, oom_list_pm3)
all_data_list_pm4 <- c(data_list_pm4, oom_list_pm4)
all_data_list_pm5 <- c(data_list_pm5, oom_list_pm5)
```

### mTBI MC A

```{r}

# Randomly plucking solutions
mc_a_solution <- mc_a_solutions[250, ]
mc_a_solution$"imputation"

mc_a_plots <- characterize_solution(
    solution = mc_a_solution,
    data_list = all_data_list_pm5,
    plotname = "mtbi_mc_a",
    return_plots = FALSE
)

mc_a_plots |> head()

mc_a_plots <- characterize_solution(
    mc_a_solution,
    all_data_list_pm5,
    "mtbi_mc_a"
)

save_plot_list_uninj(mc_a_plots, "mtbi_mc_a")

```


### mTBI MC B

```{r}

top_mc_b_solution <- mc_b_solutions[
    which(
        mc_b_solutions$"mean_neglog_p" == max(mc_b_solutions$"mean_neglog_p")
    ),
]
top_mc_b_solution <- top_mc_b_solution[4, ] # an mTBI solo dataset

write_csv(top_mc_b_solution, proc_path("top_mc_b_solution.csv", TRUE))

top_mc_b_solution <- read_csv(proc_path("2024_01_30_top_mc_b_solution.csv"))

top_mc_b_solution$"imputation"

mc_b_plots <- characterize_solution(
    top_mc_b_solution,
    all_data_list_m1,
    "mtbi_mc_b"
)

save_plot_list(mc_b_plots, "mtbi_mc_b")

mc_b_data <- characterize_solution(
    solution = top_mc_b_solution,
    data_list = all_data_list_m1,
    plotname = "mtbi_mc_b",
    return_plots = FALSE
)

write_csv(mc_b_data, proc_path("top_mc_b_data.csv", TRUE))

mc_b_data <- read_csv(proc_path("2024_01_31_top_mc_b_data.csv"))

mc_b_data$"cluster" |> table()

colnames(mc_b_data)

mc_b_data <- mc_b_data |>
    dplyr::mutate(
        avg_cbcl =
            (cbcl_anxdep +
            cbcl_withdep +
            cbcl_somatic +
            cbcl_social +
            cbcl_thought +
            cbcl_attention +
            cbcl_rulebreak +
            cbcl_aggressive) / 8
    )

mc_b_data <- mc_b_data |>
    dplyr::mutate(
        avg_parent_psych = (
            parent_aggressive +
            parent_perstr +
            parent_anxdep +
            parent_withdrawn +
            parent_somatic +
            parent_thought +
            parent_attention +
            parent_aggressive +
            parent_intrusive +
            parent_depress +
            parent_anxdisord +
            parent_avoidant +
            parent_antisocial +
            parent_hyperactive
        ) / 8
    )


colnames(mc_b_data)[grepl("parent", colnames(mc_b_data))]

cluster_d(mc_b_data, 1, c(2, 3), "total_cbcl")

cluster_d(mc_b_data, 1, c(2, 3), "sds_sleep")

cluster_d(mc_b_data, 1, c(2, 3), "household_income")

cluster_d(mc_b_data, 1, c(2, 3), "avg_parent_psych")



```

Based on the plots, MC B can be characterized as follows:

- 3 cluster solution

- Cluster 1:
    - Much lower income
    - Much higher fraction of non-white
    - Middle level of pubertal status
    - Most screen time
    - Least participation in extracurriculars
    - Rated not considerate
    - Worst family environment
    - Worst parent psychopathology
    - Strong impairments
- Cluster 2:
    - More memory loss / feeling dazed
    - More loss of consciousness
    - Lowest pubertal status
    - Highest brain volume and SA
- Cluster 3:
    - Highest pubertal status
    - Lowest history of headaches
    - Lowest brain volume and SA
    - Mostly female

Particularly notable is that the high impairment group was particulary imbalanced across the sexes.

The closest candidate within the uninjured group appeared to be MC D-A, which was tight, small but reproducible across unpooled and pooled imputations, and also exhibited a 3 cluster solution with faint separation across impairment measures.

Is it really the case that the CBCL scores are worse in males?

```{r}

top_mc_b_solution

mc_b_data <- characterize_solution(
    top_mc_b_solution,
    all_data_list_m1,
    "mtbi_mc_b",
    return_plot = FALSE
)

mc_b_data

mc_b_data |>
    ggplot(
        aes(
            x = cluster,
            y = cbcl_withdep
        )
    ) +
    geom_violin() +
    geom_jitter(
        aes(
            x = cluster,
            y = cbcl_withdep,
            colour = sex
        ),
        height = 0.05,
        size = 3,
        alpha = 0.5
    ) +
    stat_summary(
        fun = "mean",
        geom = "point",
        size = 5
    )

mc_b_data |>
    ggplot(
        aes(
            x = sex,
            y = cbcl_withdep
        )
    ) +
    geom_violin() +
    geom_jitter(
        height = 0.05,
        size = 3,
        alpha = 0.5
    ) +
    stat_summary(
        aes(x = sex, y = cbcl_withdep, colour = sex),
        fun = "mean",
        geom = "point",
        size = 5
    )

```

Looks like yes.


### mTBI MC C

```{r}

# A randomly plucked solution from m3
mc_c_solution <- mc_c_solutions[75, ]
mc_c_solution$"imputation"

all_data_list_m5 <- c(data_list_m5, oom_list_m5)
mc_c_plots <- characterize_solution(
    mc_c_solution,
    all_data_list_m5,
    "mtbi_mc_c"
)

save_plot_list_uninj(mc_c_plots, "mtbi_mc_c")

```

### mTBI MC D

```{r}

# A randomly plucked solution from m3
nrow(mc_d_solutions)

mc_d_solution <- mc_d_solutions[135, ]
mc_d_solution$"imputation"

all_data_list_pm4 <- c(data_list_pm4, oom_list_pm4)
mc_d_plots <- characterize_solution(
    mc_d_solution,
    all_data_list_pm4,
    "mtbi_mc_d"
)
save_plot_list_uninj(mc_d_plots, "mtbi_mc_d")

```

### mTBI MC E

```{r}

# A randomly plucked solution from m3
nrow(mc_e_solutions)

mc_e_solution <- mc_e_solutions[107, ]
mc_e_solution$"imputation"

all_data_list_m4 <- c(data_list_m4, oom_list_m4)
mc_e_plots <- characterize_solution(
    mc_e_solution,
    all_data_list_m4,
    "mtbi_mc_e"
)
save_plot_list(mc_e_plots, "mtbi_mc_e")

```

### Uninjured MCs

```{r}
mu_extended_solutions_matrix <- read_csv(
    proc_path("2024_01_30_full_uninjured_extended_solutions_matrix.csv")
)

mu_extended_solutions_matrix

mu_oom_pvals <- pval_select(
    mu_extended_solutions_matrix,
    negative_log = TRUE
)

mu_extended_solutions_matrix$"mean_neglog_p" <- mu_oom_pvals$"mean_neglog_p"

mu_extended_solutions_matrix

mu_sm_order <- unlist(
    read_csv(proc_path("2024_01_30_aris_all_uninjured_imputations_order.csv"))
)
names(mu_sm_order) <- NULL

mu_sorted_solutions_matrix <- mu_extended_solutions_matrix[mu_sm_order, ]

mu_mc_a_solutions <- mu_sorted_solutions_matrix[1:734, ]
mu_mc_b_solutions <- mu_sorted_solutions_matrix[735:1062, ]
mu_mc_c_solutions <- mu_sorted_solutions_matrix[1063:1178, ]
mu_mc_d_solutions <- mu_sorted_solutions_matrix[1179:1686, ]
mu_mc_e_solutions <- mu_sorted_solutions_matrix[1687:2000, ]
```

### Setting up total data lists

```{r}
all_data_list_mu1 <- c(data_list_mu1, oom_list_mu1)
all_data_list_mu2 <- c(data_list_mu2, oom_list_mu2)
all_data_list_mu3 <- c(data_list_mu3, oom_list_mu3)
all_data_list_mu4 <- c(data_list_mu4, oom_list_mu4)
all_data_list_mu5 <- c(data_list_mu5, oom_list_mu5)
all_data_list_mpu1 <- c(data_list_mpu1, oom_list_mpu1)
all_data_list_mpu2 <- c(data_list_mpu2, oom_list_mpu2)
all_data_list_mpu3 <- c(data_list_mpu3, oom_list_mpu3)
all_data_list_mpu4 <- c(data_list_mpu4, oom_list_mpu4)
all_data_list_mpu5 <- c(data_list_mpu5, oom_list_mpu5)
```


### Uninjured MC A

```{r}

# Randomly plucking solutions
mu_mc_a_solution <- mu_mc_a_solutions[350, ]

mu_mc_a_solution$"imputation"

mu_mc_a_plots <- characterize_solution(
    mu_mc_a_solution,
    all_data_list_mpu4,
    "mtbi_mu_mc_a"
)

save_plot_list_uninj(mu_mc_a_plots, "mtbi_mu_mc_a")

```

### Uninjured MC B

```{r}

row <- nrow(mu_mc_b_solutions) %/% 2
mu_mc_b_solution <- mu_mc_b_solutions[row, ]
mu_mc_b_solution$"imputation"

mu_mc_b_plots <- characterize_solution(
    mu_mc_b_solution,
    all_data_list_mu3,
    "mtbi_mu_mc_b"
)
save_plot_list_uninj(mu_mc_b_plots, "mtbi_mu_mc_b")

```

### Uninjured MC C

This is the solution that may be most similar to the mTBI MC B solution.
It has 3 clusters and occurs across both imputation conditions.

```{r}
# Stick to the 3 cluster solutions
mu_mc_c_solutions <- mu_mc_c_solutions |>
    dplyr::filter(nclust == 3)
top_mu_mc_c_solution <- mu_mc_c_solutions[
    which(
        mu_mc_c_solutions$"mean_neglog_p" == max(mu_mc_c_solutions$"mean_neglog_p")
    ),
]
top_mu_mc_c_solution

mu_mc_c_plots <- characterize_solution(
    top_mu_mc_c_solution,
    all_data_list_mu1,
    "uninjured_mc_c"
)
save_plot_list_uninj(mu_mc_c_plots, "uninjured_mc_c")

```

### Uninjured MC E

```{r}

row <- nrow(mu_mc_e_solutions) %/% 2
mu_mc_e_solution <- mu_mc_e_solutions[row, ]
mu_mc_e_solution$"imputation"

mu_mc_e_plots <- characterize_solution(
    mu_mc_e_solution,
    all_data_list_mu5,
    "mtbi_mu_mc_e"
)
save_plot_list_uninj(mu_mc_e_plots, "mtbi_mu_mc_e")

```

That solution ended up being quite meaningless.
In the following two chapter, an alternative matched uninjured group is explored.
