# Controls

Examining subjects who have not had a concussion will reveal the extent to which our results thus far are specific to children with concussions.

## Matched controls

## Data extraction

```{r}

library(MatchIt)
library(readr)
library(abcdutils)
library(metasnf)
library(here)

core_path <- path_maker(here(paste0("data/abcd/core")))
input_path <- path_maker(here(paste0("data/abcd/inputs")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))

# Loading data
ph_p_otbi <- abcd_load(core_path("physical-health/ph_p_otbi.csv"))
abcd_y_lt <- abcd_load(core_path("abcd-general/abcd_y_lt.csv"))
ph_y_pds <- abcd_load(core_path("physical-health/ph_y_pds.csv"))
ph_p_pds <- abcd_load(core_path("physical-health/ph_p_pds.csv"))
gish_p_gi <- abcd_load(core_path("gender-identity-sexual-health/gish_p_gi.csv"))
gish_y_gi <- abcd_load(core_path("gender-identity-sexual-health/gish_y_gi.csv"))
gish_p_sex <- abcd_load(core_path("gender-identity-sexual-health/gish_p_sex.csv"))
gish_y_sex <- abcd_load(core_path("gender-identity-sexual-health/gish_y_sex.csv"))
abcd_p_demo <- abcd_load(core_path("abcd-general/abcd_p_demo.csv"))
ph_p_mhx <- abcd_load(core_path("physical-health/ph_p_mhx.csv"))
mri_y_smr_vol_aseg <- abcd_load(core_path("imaging/mri_y_smr_vol_aseg.csv"))
mri_y_smr_thk_dst <- abcd_load(core_path("imaging/mri_y_smr_thk_dst.csv"))
mri_y_smr_area_dst <- abcd_load(core_path("imaging/mri_y_smr_area_dst.csv"))
mri_y_rsi_rnd_at <- abcd_load(core_path("imaging/mri_y_rsi_rnd_at.csv"))
mri_y_rsi_rnd_wm_dsk <- abcd_load(core_path("imaging/mri_y_rsi_rnd_wm_dsk.csv"))
mri_y_rsi_rnd_wm_dst <- abcd_load(core_path("imaging/mri_y_rsi_rnd_wm_dst.csv"))
mri_y_rsfmr_cor_gp_gp <- abcd_load(core_path("imaging/mri_y_rsfmr_cor_gp_gp.csv"))
mri_y_rsfmr_cor_gp_aseg <- abcd_load(core_path("imaging/mri_y_rsfmr_cor_gp_aseg.csv"))
mri_y_rsfmr_var_gp <- abcd_load(core_path("imaging/mri_y_rsfmr_var_gp.csv"))
mri_y_rsfmr_var_aseg <- abcd_load(core_path("imaging/mri_y_rsfmr_var_aseg.csv"))
mh_y_or <- abcd_load(core_path("mental-health/mh_y_or.csv"))
nt_p_stq <- abcd_load(core_path("novel-technologies/nt_p_stq.csv"))
ce_y_fes <- abcd_load(core_path("culture-environment/ce_y_fes.csv"))
ce_p_fes <- abcd_load(core_path("culture-environment/ce_p_fes.csv"))
ph_p_saiq <- abcd_load(core_path("physical-health/ph_p_saiq.csv"))
ce_y_psb <- abcd_load(core_path("culture-environment/ce_y_psb.csv"))
ce_p_psb <- abcd_load(core_path("culture-environment/ce_p_psb.csv"))
mh_p_asr <- abcd_load(core_path("mental-health/mh_p_asr.csv"))
ph_y_yrb <- abcd_load(core_path("physical-health/ph_y_yrb.csv"))
mh_p_cbcl <- abcd_load(core_path("mental-health/mh_p_cbcl.csv"))
nc_y_nihtb <- abcd_load(core_path("neurocognition/nc_y_nihtb.csv"))
ph_p_sds <- abcd_load(core_path("physical-health/ph_p_sds.csv"))
mri_y_qc_raw_rsfmr <- abcd_load(core_path("imaging/mri_y_qc_raw_rsfmr.csv"))
mri_y_qc_raw_dmr <- abcd_load(core_path("imaging/mri_y_qc_raw_dmr.csv"))
mri_y_qc_raw_smr_t1 <- abcd_load(core_path("imaging/mri_y_qc_raw_smr_t1.csv"))
mri_y_qc_raw_smr_t2 <- abcd_load(core_path("imaging/mri_y_qc_raw_smr_t2.csv"))

# Subjects
uninjured_subjects <- read_csv(sub_path("2023_07_17_uninjured_subjects.csv"))

```

### Demographics

```{r}

## Pubertal status
(d_pubertal_status_u_0 <-
    get_pubertal_status(ph_p_pds, ph_y_pds, uninjured_subjects, t = 0))

## Age on interview
(d_interview_age_u_0 <- get_interview_age(abcd_y_lt, uninjured_subjects, t = 0))

## Sex assigned at birth
(d_sex_u_0 <- get_sex(gish_p_gi, uninjured_subjects, t = 0))

## Household income
(d_income_u_0 <- get_income(abcd_p_demo, uninjured_subjects, t = 0))

## Race
(d_race_u_0 <-
    get_race(abcd_p_demo, uninjured_subjects, "condensed_undummied", t = 0))

write_csv(d_pubertal_status_u_0, input_path("d_pubertal_status_u_0.csv", TRUE))
write_csv(d_interview_age_u_0, input_path("d_interview_age_u_0.csv", TRUE))
write_csv(d_sex_u_0, input_path("d_sex_u_0.csv", TRUE))
write_csv(d_income_u_0, input_path("d_income_u_0.csv", TRUE))
write_csv(d_race_u_0, input_path("d_race_u_0.csv", TRUE))

```

### Medical history

```{r}

## History of headaches
(mh_headaches_u_0 <- get_headaches(ph_p_mhx, uninjured_subjects, t = 0))

write_csv(mh_headaches_u_0, input_path("mh_headaches_u_0.csv", date = TRUE))

```

### Neuroimaging

#### Structural MRI

```{r}

## Subcortical volumes
sm_subc_v_u_0 <- abcdutils::get_subc_v(mri_y_smr_vol_aseg, uninjured_subjects, t = 0)

## Cortical thickness
sm_cort_t_u_0 <- abcdutils::get_cort_t(mri_y_smr_thk_dst, uninjured_subjects, t = 0)

## Cortical surface areas
sm_cort_sa_u_0 <- abcdutils::get_cort_sa(mri_y_smr_area_dst, uninjured_subjects, t = 0)

write_csv(sm_subc_v_u_0, input_path("sm_subc_v_u_0.csv", date = TRUE))
write_csv(sm_cort_t_u_0, input_path("sm_cort_t_u_0.csv", date = TRUE))
write_csv(sm_cort_sa_u_0, input_path("sm_cort_sa_u_0.csv", date = TRUE))

```

#### Diffusion MRI


```{r}

# White matter neurite densities
dm_all_wmnd_u_0 <- get_all_wmnd(
    mri_y_rsi_rnd_at,
    mri_y_rsi_rnd_wm_dst,
    mri_y_rsi_rnd_wm_dsk,
    subjects = uninjured_subjects,
    t = 0
)

write_csv(dm_all_wmnd_u_0, input_path("dm_all_wmnd_u_0.csv", date = TRUE))

```

#### Resting-state functional MRI

```{r}

## Cortical parcellation network correlations
rm_gord_cor_u_0 <- get_gord_cor(
    mri_y_rsfmr_cor_gp_gp,
    uninjured_subjects,
    t = 0
)

## Subcortical parcellation network correlations
rm_subc_cor_u_0 <- get_subc_cor(
    mri_y_rsfmr_cor_gp_aseg,
    uninjured_subjects,
    t = 0
)

## Temporal variances - cortical parcellations
rm_gord_var_u_0 <- get_gord_var(
    mri_y_rsfmr_var_gp,
    uninjured_subjects,
    t = 0
)

## Subcortical temporal variances
rm_subc_var_u_0 <- get_subc_var(
    mri_y_rsfmr_var_aseg,
    uninjured_subjects,
    t = 0
)

write_csv(rm_gord_cor_u_0, input_path("rm_gord_cor_u_0.csv", date = TRUE))
write_csv(rm_subc_cor_u_0, input_path("rm_subc_cor_u_0.csv", date = TRUE))
write_csv(rm_subc_var_u_0, input_path("rm_subc_var_u_0.csv", date = TRUE))
write_csv(rm_gord_var_u_0, input_path("rm_gord_var_u_0.csv", date = TRUE))

```

### Psychosocial resilience

```{r}

p_loneliness_u_0 <- get_loneliness(
    mh_y_or,
    gish_p_gi,
    uninjured_subjects,
    t = 0
)

p_screen_time_u_0 <-
    get_screen_time(nt_p_stq, uninjured_subjects, t = 0)

p_family_function_u_0 <-
    get_family_function(ce_y_fes, ce_p_fes, uninjured_subjects, t = 0)

p_sports_u_0 <-
    get_sports_and_activities(ph_p_saiq, uninjured_subjects, t = 0)

p_prosocial_u_0 <-
    get_prosocial_behaviour(ce_p_psb, ce_y_psb, uninjured_subjects, t = 0)

p_parent_psych_u_0 <-
    get_parent_psychopathology(mh_p_asr, uninjured_subjects, t = 0)

p_exercise_u_0 <-
    get_exercise(ph_y_yrb, uninjured_subjects, t = 0)

write_csv(p_loneliness_u_0, input_path("p_loneliness_u_0.csv", date = TRUE))
write_csv(p_screen_time_u_0, input_path("p_screen_time_u_0.csv", date = TRUE))
write_csv(p_family_function_u_0,
          input_path("p_family_function_u_0.csv", date = TRUE))
write_csv(p_sports_u_0, input_path("p_sports_u_0.csv", date = TRUE))
write_csv(p_prosocial_u_0, input_path("p_prosocial_u_0.csv", date = TRUE))
write_csv(p_parent_psych_u_0, input_path("p_parent_psych_u_0.csv", date = TRUE))
write_csv(p_exercise_u_0, input_path("p_exercise_u_0.csv", date = TRUE))

```



## Output variables

### Child behaviour checklist

These are needed at both baseline and longitudinal timepoints.

```{r}

# Baseline subjects, baseline time point
cbcl_headaches_u_0 <-
    get_cbcl_headaches(mh_p_cbcl, uninjured_subjects, t = 0)
cbcl_nausea_u_0 <-
    get_cbcl_nausea(mh_p_cbcl, uninjured_subjects, t = 0)
cbcl_vomiting_u_0 <-
    get_cbcl_vomiting(mh_p_cbcl, uninjured_subjects, t = 0)
cbcl_dizzy_u_0 <-
    get_cbcl_dizzy(mh_p_cbcl, uninjured_subjects, t = 0)
cbcl_overtired_u_0 <-
    get_cbcl_overtired(mh_p_cbcl, uninjured_subjects, t = 0)
cbcl_sleeping_more_u_0 <-
    get_cbcl_sleeping_more(mh_p_cbcl, uninjured_subjects, t = 0)
cbcl_sleeping_less_u_0 <-
    get_cbcl_sleeping_less(mh_p_cbcl, uninjured_subjects, t = 0)
cbcl_depress_r_u_0 <-
    get_cbcl_depress(mh_p_cbcl, uninjured_subjects, t = 0)
cbcl_anxiety_r_u_0 <-
    get_cbcl_anxiety(mh_p_cbcl, uninjured_subjects, t = 0)
cbcl_attention_r_u_0 <-
    get_cbcl_attention(mh_p_cbcl, uninjured_subjects, t = 0)
cbcl_aggressive_r_u_0 <-
    get_cbcl_aggressive(mh_p_cbcl, uninjured_subjects, t = 0)

# Borderline/clinical thresholded instead of raw scores
cbcl_depress_u_0 <-
    get_cbcl_depress(mh_p_cbcl, uninjured_subjects, t = 0, raw = FALSE)
cbcl_anxiety_u_0 <-
    get_cbcl_anxiety(mh_p_cbcl, uninjured_subjects, t = 0, raw = FALSE)
cbcl_attention_u_0 <-
    get_cbcl_attention(mh_p_cbcl, uninjured_subjects, t = 0, raw = FALSE)
cbcl_aggressive_u_0 <-
    get_cbcl_aggressive(mh_p_cbcl, uninjured_subjects, t = 0, raw = FALSE)

write_csv(cbcl_headaches_u_0,
    input_path("cbcl_headaches_u_0.csv", date = TRUE))
write_csv(cbcl_nausea_u_0,
    input_path("cbcl_nausea_u_0.csv", date = TRUE))
write_csv(cbcl_vomiting_u_0,
    input_path("cbcl_vomiting_u_0.csv", date = TRUE))
write_csv(cbcl_dizzy_u_0,
    input_path("cbcl_dizzy_u_0.csv", date = TRUE))
write_csv(cbcl_overtired_u_0,
    input_path("cbcl_overtired_u_0.csv", date = TRUE))
write_csv(cbcl_sleeping_more_u_0,
    input_path("cbcl_sleeping_more_u_0.csv", date = TRUE))
write_csv(cbcl_sleeping_less_u_0,
    input_path("cbcl_sleeping_less_u_0.csv", date = TRUE))
write_csv(cbcl_depress_r_u_0,
    input_path("cbcl_depress_r_u_0.csv", date = TRUE))
write_csv(cbcl_anxiety_r_u_0,
    input_path("cbcl_anxiety_r_u_0.csv", date = TRUE))
write_csv(cbcl_attention_r_u_0,
    input_path("cbcl_attention_r_u_0.csv", date = TRUE))
write_csv(cbcl_aggressive_r_u_0,
    input_path("cbcl_aggressive_r_u_0.csv", date = TRUE))
write_csv(cbcl_depress_u_0,
    input_path("cbcl_depress_u_0.csv", date = TRUE))
write_csv(cbcl_anxiety_u_0,
    input_path("cbcl_anxiety_u_0.csv", date = TRUE))
write_csv(cbcl_attention_u_0,
    input_path("cbcl_attention_u_0.csv", date = TRUE))
write_csv(cbcl_aggressive_u_0,
    input_path("cbcl_aggressive_u_0.csv", date = TRUE))

```

### NIH Toolbox

```{r}

# Baseline subjects, baseline data
nihtbx_list_fc_u_0 <-
    get_nihtbx_list_fc(nc_y_nihtb, uninjured_subjects, t = 0)
nihtbx_pattern_fc_u_0 <-
    get_nihtbx_pattern_fc(nc_y_nihtb, uninjured_subjects, t = 0)
nihtbx_cardsort_fc_u_0 <-
    get_nihtbx_cardsort_fc(nc_y_nihtb, uninjured_subjects, t = 0)

write_csv(nihtbx_list_fc_u_0, input_path("nihtbx_list_fc_u_0.csv", 1))
write_csv(nihtbx_pattern_fc_u_0, input_path("nihtbx_pattern_fc_u_0.csv", 1))
write_csv(nihtbx_cardsort_fc_u_0, input_path("nihtbx_cardsort_fc_u_0.csv", 1))

```


### Sleep disturbance scale

```{r}

(sds_sleep_df_u_0 <- get_full_sleep_df(ph_p_sds, uninjured_subjects, t = 0))

write_csv(sds_sleep_df_u_0, input_path("sds_sleep_df_u_0.csv", date = TRUE))


```

## Matching

```{r}

data("lalonde")

head(lalonde)

m.out1 <- matchit(
    treat ~ age + educ + race + nodegree + married + re74 + re75,
    data = lalonde
)

summary(m.out1)

```

