# Assigning borderline and clinical cases to raw CBCL scores


Borderline is 93-97th percentile, clinical is 97th percentile or higher

```{r}
abcd_cbcl01 <- read_delim(here("data/abcd/raw/abcd_cbcl01.txt"))
abcd_cbcls01 <- read_delim(here("data/abcd/raw/abcd_cbcls01.txt"))

# The raw scores of all children
cbcl_depress_r_all <- get_cbcl_depress_r(abcd_cbcls01, t = 0)
cbcl_anxiety_r_all <- get_cbcl_anxiety_r(abcd_cbcls01, t = 0)
cbcl_attention_r_all <- get_cbcl_attention_r(abcd_cbcls01, t = 0)
cbcl_aggressive_r_all <- get_cbcl_aggressive_r(abcd_cbcls01, t = 0)

# Converting relevant columns to numeric
cbcl_depress_r_all$cbcl_depress_r <- as.numeric(cbcl_depress_r_all$cbcl_depress_r)
cbcl_anxiety_r_all$cbcl_anxiety_r <- as.numeric(cbcl_anxiety_r_all$cbcl_anxiety_r)
cbcl_attention_r_all$cbcl_attention_r <- as.numeric(cbcl_attention_r_all$cbcl_attention_r)
cbcl_aggressive_r_all$cbcl_aggressive_r <- as.numeric(cbcl_aggressive_r_all$cbcl_aggressive_r)

depress_threshold_borderline <-
    quantile(cbcl_depress_r_all$cbcl_depress_r,
             probs = c(0.93, 0.97), na.rm = TRUE)[[1]]
depress_threshold_clinical <-
    quantile(cbcl_depress_r_all$cbcl_depress_r,
             probs = c(0.93, 0.97), na.rm = TRUE)[[2]]
anxiety_threshold_borderline <-
    quantile(cbcl_anxiety_r_all$cbcl_anxiety_r,
            probs = c(0.93, 0.97), na.rm = TRUE)[[1]]
anxiety_threshold_clinical <-
    quantile(cbcl_anxiety_r_all$cbcl_anxiety_r,
            probs = c(0.93, 0.97), na.rm = TRUE)[[2]]
attention_threshold_borderline <-
    quantile(cbcl_attention_r_all$cbcl_attention_r,
            probs = c(0.93, 0.97), na.rm = TRUE)[[1]]
attention_threshold_clinical <-
    quantile(cbcl_attention_r_all$cbcl_attention_r,
            probs = c(0.93, 0.97), na.rm = TRUE)[[2]]
aggressive_threshold_borderline <-
    quantile(cbcl_aggressive_r_all$cbcl_aggressive_r,
            probs = c(0.93, 0.97), na.rm = TRUE)[[1]]
aggressive_threshold_clinical <-
    quantile(cbcl_aggressive_r_all$cbcl_aggressive_r,
            probs = c(0.93, 0.97), na.rm = TRUE)[[2]]

depress_threshold_borderline # 5
depress_threshold_clinical # 7
anxiety_threshold_borderline # 6
anxiety_threshold_clinical # 8
attention_threshold_borderline # 9
attention_threshold_clinical # 12
aggressive_threshold_borderline # 11
aggressive_threshold_clinical # 15
```

These thresholds correspond to the 93rd and 97th percentiles of behavioural impairments across all ABCD children, which define the borderline and clinical categories of impairment respectively.

# Exploring all CBCL scores in relation to age and sex

```{r}
library(here)
library(abcdutils)
library(patchwork)
library(ggplot2)
library(readr)

core_path <- path_maker(here(paste0("data/abcd/core")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))

# Parent report of child behaviour (CBCL)
mh_p_cbcl <- abcd_load(core_path("mental-health/mh_p_cbcl.csv"))

# Parent report of sex identity
gish_p_gi <- abcd_load(core_path("gender-identity-sexual-health/gish_p_gi.csv"))
sex <- get_sex(gish_p_gi, t = 0)
sex <- dplyr::filter(sex, sex %in% c("M", "F"))

# Age
abcd_y_lt <- abcd_load(core_path("abcd-general/abcd_y_lt.csv"))
age <- d_interview_age_mtbi <- get_interview_age(abcd_y_lt, t = 0)

scales <- c(
    "anxdep",
    "withdep",
    "somatic",
    "social",
    "thought",
    "attention",
    "rulebreak",
    "aggressive"
)

all_cbcl_dfs <- list()
for (i in 1:length(scales)) {
    scale <- scales[[i]]
    cbcl_df <- get_cbcl_syndrome_scale(
        syndrome = scale,
        mh_p_cbcl,
        raw = TRUE,
        t = 0
    )
    all_cbcl_dfs[[i]] <- cbcl_df
}
all_cbcl <- merge_df_list(all_cbcl_dfs)
all_cbcl <- dplyr::inner_join(all_cbcl, sex)
all_cbcl <- dplyr::inner_join(all_cbcl, age)
all_cbcl <- na.omit(all_cbcl)

colnames(all_cbcl) <- gsub("cbcl_scr_syn_", "", colnames(all_cbcl))


all_cbcl_t_dfs <- list()
for (i in 1:length(scales)) {
    scale <- scales[[i]]
    cbcl_df <- get_cbcl_syndrome_scale(
        syndrome = scale,
        mh_p_cbcl,
        raw = FALSE,
        t = 0
    )
    all_cbcl_t_dfs[[i]] <- cbcl_df
}
all_cbcl_t <- merge_df_list(all_cbcl_t_dfs)
all_cbcl_t <- dplyr::inner_join(all_cbcl_t, sex)
all_cbcl_t <- dplyr::inner_join(all_cbcl_t, age)
all_cbcl_t <- na.omit(all_cbcl_t)
colnames(all_cbcl_t) <- gsub("cbcl_scr_syn_", "", colnames(all_cbcl_t))


nrow(all_cbcl) # n = 11856

# All differences by sex
plot_list <- list()
m_minus_f_df <- data.frame()
for (i in 1:length(scales)) {
    scale <- paste0(scales[[i]], "_r")
    f_mean <- all_cbcl[all_cbcl$"sex" == "F", scale] |> mean()
    m_mean <- all_cbcl[all_cbcl$"sex" == "M", scale] |> mean()
    diff <- round(m_mean - f_mean, 4)
    m_minus_f_df <- rbind(
        m_minus_f_df,
        data.frame(
            symptom = scale,
            m_minus_f = (m_mean - f_mean)
        )
    )
    diff_text <- paste0("M - F = ", diff)
    cbcl_plot <- all_cbcl |>
        ggplot(
            aes(
                x = all_cbcl[, "sex"],
                y = all_cbcl[, !!scale],
                color = sex
            )
        ) +
        geom_jitter(
            height = 0,
            alpha = 0.05
        ) +
        stat_summary(
            fun = "mean",
            geom = "crossbar",
            colour = "black"
        ) +
        labs(
            x = "Sex",
            y = gsub("_r", "", scale)
        ) + 
        annotate(
            "text",
            label = diff_text,
            x = 1.5,
            y = Inf,
            vjust = 3,
            size = 5
        ) +
        theme_bw()
    cbcl_plot <- cbcl_plot + 
        theme(
            legend.position = "none",
            panel.grid.major.x = element_blank()
        )
    plot_list[[i]] <- cbcl_plot
    names(plot_list)[i] <- scale
}
wrap_plots(plot_list, nrow = 2) 

ggsave(
    plot = wrap_plots(plot_list, nrow = 2),
    fig_path("all_baseline_cbcl_by_sex.png", TRUE),
    width = 12,
    height = 5
)

write_csv(m_minus_f_df, proc_path("cbcl_m_minus_f_df.csv", TRUE))

plot_list <- list()
over_age_df <- data.frame()
for (i in 1:length(scales)) {
    scale <- paste0(scales[[i]], "_r")
    lm_fit <- lm(all_cbcl[, scale] ~ all_cbcl[, "interview_age"])
    m <- round(coef(lm_fit)[2], 4)
    b <- round(coef(lm_fit)[1], 4)
    over_age_df <- rbind(
        over_age_df,
        data.frame(
            symptom = scale,
            m = m
        )
    )
    cbcl_plot <- all_cbcl |>
        ggplot(
            aes(
                x = all_cbcl[, "interview_age"],
                y = all_cbcl[, !!scale],
            )
        ) +
        geom_point(
            alpha = 0.01
        ) +
        labs(
            x = "Age",
            y = gsub("_r", "", scale)
        ) + 
        geom_smooth(
            method = "lm",
            se = FALSE
        ) +
        geom_text(
            aes(
                x = Inf,
                y = Inf,
                label = paste("y = ", !!m, "x + ", !!b)
            ),
            hjust = 1,
            vjust = 5,
            size = 4,
            data = data.frame()
        ) +
        theme(
            legend.position = "none",
            text = element_text(family = "Arial", size = 12)
        ) +
        theme_minimal()
    plot_list[[i]] <- cbcl_plot
}
wrap_plots(plot_list, nrow = 2)

ggsave(
    plot = wrap_plots(plot_list, nrow = 2),
    fig_path("all_baseline_cbcl_by_age.png", TRUE),
    width = 15,
    height = 5
)

rownames(over_age_df) <- NULL
write_csv(over_age_df, proc_path("cbcl_over_age_df.csv", TRUE))

m_minus_f_df

```

## Sex and age adjusted CBCL scores

```{r}
library(ggplot2)

all_cbcl |> colnames()
all_cbcl_t |> colnames()

all_cbcl_t_and_r <- dplyr::inner_join(all_cbcl, all_cbcl_t) |>
    na.omit()


all_cbcl_t_and_r |> colnames()

all_cbcl_t_and_r |>
    ggplot(
        aes(
            x = anxdep_r,
            y = anxdep_t
        )
    ) + 
    geom_point(size = 5)
```
