# Assigning borderline and clinical cases to raw CBCL scores


Borderline is 93-97th percentile, clinical is 97th percentile or higher

```{r}

abcd_cbcl01 <- read_delim(here("data/abcd/raw/abcd_cbcl01.txt"))
abcd_cbcls01 <- read_delim(here("data/abcd/raw/abcd_cbcls01.txt"))

# The raw scores of all children
cbcl_depress_r_all <- get_cbcl_depress_r(abcd_cbcls01, t = 0)
cbcl_anxiety_r_all <- get_cbcl_anxiety_r(abcd_cbcls01, t = 0)
cbcl_attention_r_all <- get_cbcl_attention_r(abcd_cbcls01, t = 0)
cbcl_aggressive_r_all <- get_cbcl_aggressive_r(abcd_cbcls01, t = 0)

# Converting relevant columns to numeric
cbcl_depress_r_all$cbcl_depress_r <- as.numeric(cbcl_depress_r_all$cbcl_depress_r)
cbcl_anxiety_r_all$cbcl_anxiety_r <- as.numeric(cbcl_anxiety_r_all$cbcl_anxiety_r)
cbcl_attention_r_all$cbcl_attention_r <- as.numeric(cbcl_attention_r_all$cbcl_attention_r)
cbcl_aggressive_r_all$cbcl_aggressive_r <- as.numeric(cbcl_aggressive_r_all$cbcl_aggressive_r)

depress_threshold_borderline <-
    quantile(cbcl_depress_r_all$cbcl_depress_r,
             probs = c(0.93, 0.97), na.rm = TRUE)[[1]]
depress_threshold_clinical <-
    quantile(cbcl_depress_r_all$cbcl_depress_r,
             probs = c(0.93, 0.97), na.rm = TRUE)[[2]]
anxiety_threshold_borderline <-
    quantile(cbcl_anxiety_r_all$cbcl_anxiety_r,
            probs = c(0.93, 0.97), na.rm = TRUE)[[1]]
anxiety_threshold_clinical <-
    quantile(cbcl_anxiety_r_all$cbcl_anxiety_r,
            probs = c(0.93, 0.97), na.rm = TRUE)[[2]]
attention_threshold_borderline <-
    quantile(cbcl_attention_r_all$cbcl_attention_r,
            probs = c(0.93, 0.97), na.rm = TRUE)[[1]]
attention_threshold_clinical <-
    quantile(cbcl_attention_r_all$cbcl_attention_r,
            probs = c(0.93, 0.97), na.rm = TRUE)[[2]]
aggressive_threshold_borderline <-
    quantile(cbcl_aggressive_r_all$cbcl_aggressive_r,
            probs = c(0.93, 0.97), na.rm = TRUE)[[1]]
aggressive_threshold_clinical <-
    quantile(cbcl_aggressive_r_all$cbcl_aggressive_r,
            probs = c(0.93, 0.97), na.rm = TRUE)[[2]]

depress_threshold_borderline # 5
depress_threshold_clinical # 7
anxiety_threshold_borderline # 6
anxiety_threshold_clinical # 8
attention_threshold_borderline # 9
attention_threshold_clinical # 12
aggressive_threshold_borderline # 11
aggressive_threshold_clinical # 15
```

These thresholds correspond to the 93rd and 97th percentiles of behavioural impairments across all ABCD children, which define the borderline and clinical categories of impairment respectively.

# Exploring all CBCL scores in relation to age and sex

```{r}
core_path <- path_maker(here(paste0("data/abcd/core")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))

# Parent report of child behaviour (CBCL)
mh_p_cbcl <- abcd_load(core_path("mental-health/mh_p_cbcl.csv"))

# Parent report of sex identity
gish_p_gi <- abcd_load(core_path("gender-identity-sexual-health/gish_p_gi.csv"))
sex <- get_sex(gish_p_gi, t = 0)
sex <- dplyr::filter(sex, sex %in% c("M", "F"))

# Age
abcd_y_lt <- abcd_load(core_path("abcd-general/abcd_y_lt.csv"))
age <- d_interview_age_mtbi <- get_interview_age(abcd_y_lt, t = 0)


scales <- c(
    "anxdep",
    "withdep",
    "somatic",
    "social",
    "thought",
    "attention",
    "rulebreak",
    "aggressive"
)

all_cbcl_dfs <- list()
for (i in 1:length(scales)) {
    scale <- scales[[i]]
    cbcl_df <- get_cbcl_syndrome_scale(
        syndrome = scale,
        mh_p_cbcl,
        raw = TRUE,
        t = 0
    )
    all_cbcl_dfs[[i]] <- cbcl_df
}
all_cbcl <- merge_df_list(all_cbcl_dfs)
all_cbcl <- dplyr::inner_join(all_cbcl, sex)
all_cbcl <- dplyr::inner_join(all_cbcl, age)
all_cbcl <- na.omit(all_cbcl)

colnames(all_cbcl) <- gsub("cbcl_scr_syn_", "", colnames(all_cbcl))

###############################################################################

library(patchwork)

# All differences by sex
plot_list <- list()
for (i in 1:length(scales)) {
    scale <- paste0(scales[[i]], "_r")
    cbcl_plot <- all_cbcl |>
        ggplot(
            aes(
                x = all_cbcl[, "sex"],
                y = all_cbcl[, scale],
                color = sex
            )
        ) +
        geom_jitter(
            height = 0.05
        ) +
        stat_summary(
            fun = "mean",
            geom = "crossbar",
            colour = "black"
        ) +
        labs(
            x = "Sex",
            y = scale
        ) + 
        theme(legend.position = "none")
    plot_list[[i]] <- cbcl_plot
}

wrap_plots(plot_list)

plot_list <- list()
for (i in 1:length(scales)) {
    scale <- paste0(scales[[i]], "_r")
    cbcl_plot <- all_cbcl |>
        ggplot(
            aes(
                x = all_cbcl[, "interview_age"],
                y = all_cbcl[, scale],
            )
        ) +
        geom_point() +
        labs(
            x = "Age",
            y = scale
        ) + 
        geom_smooth(
            method = "lm",
            se = FALSE,
            color = "blue"
        ) +
        theme(legend.position = "none")
    plot_list[[i]] <- cbcl_plot
    print(
        cor(
            all_cbcl[, "interview_age"],
            all_cbcl[, scale]
        )
    )
}

wrap_plots(plot_list)


```
