# Coding categorical variables dummies {#sec-codingdummies}

It is often recommended that categorical variables be converted into dummy format for distance matrix calculations.
However, this conversion can make a large impact on the resulting distance matrices should be interpreted.

Consider the following three people:

1. Person 1 is a tall man.
2. Person 2 is a short woman.
3. Person 3 is a medium-height man

Based on these attributes, what should the resulting distance matrix look like?

Person 1 and 2 have nothing in common.

Person 2 and 3 have nothing in common.

Person 1 and 3 are both men.

From this perspective, we should get a distance matrix were 1 and 3 are closer together than 2 and 3 or 1 and 2.


```{r}
library(cluster)

people <- data.frame(
    man = c(1, 0, 1),
    tall = c(1, 0, 0),
    medium = c(0, 0, 1))

people

as.matrix(daisy(people, metric = "gower"))
```

Why is everybody equally similar to each other?

Well, this dummy approach has a couple of issues:

1. There is no accounting for short and tall being closer to medium than they are to each other
2. Positively agreeing on a column (1 and 3 are both men) is equally as valuable as negatively agreeing on a column (1 and 2 are both *not* short, 2 and 3 are both *not* tall).

We can get the distance matrix we were expecting by not doing the dummying:

```{r}
people_no_dum <- data.frame(
    sex = as.factor(c("man", "woman", "man")),
    height = as.factor(c("tall", "short", "medium")))

people_no_dum

as.matrix(daisy(people_no_dum, metric = "gower"))
```

That handles problem #2.
But what about problem #1?


```{r}
people_no_dum <- rbind(people_no_dum, c("man", "short"))

people_no_dum

as.matrix(daisy(people_no_dum, metric = "gower"))
```

Problem #1 is still there! The gaps between persons 3 and 4 and between persons 1 and 3 should be smaller than the gap between persons 1 and 4 (because the differences between medium and short and medium and tall are less than the difference between short and tall).

```{r}
people_no_dum$height <- ordered(people_no_dum$height,
                               levels = c("short", "medium", "tall"))

str(people_no_dum)

as.matrix(daisy(people_no_dum, metric = "gower"))
```

That looks correct!

In some cases you may not want the automatic level management done by the daisy function.
If you believe your ordered categories should not be treated as evenly spaced, you should code your own weights.



