# Destrieux and Desikan Parcellations

The Destrieux and Desikan parcellations can both be used to obtain brain structure information on a region-by-region basis.

This file is by no means an exhaustive comparison of the two parcellations, but briefly outlines their correlation on variables included in this study.

## Libraries, path names, and importing of raw data

```{r}
library(here)
library(abcdutils)
library(ggplot2)

core_path <- path_maker(here(paste0("data/abcd/core")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))

# Desikan cortical thicknesses
mri_y_smr_thk_dsk <- abcd_load(core_path("imaging/mri_y_smr_thk_dsk.csv"))

# Destrieux cortical thicknesses
mri_y_smr_thk_dst <- abcd_load(core_path("imaging/mri_y_smr_thk_dst.csv"))

# Desikan cortical surface areas
mri_y_smr_area_dsk <- abcd_load(core_path("imaging/mri_y_smr_area_dsk.csv"))

# Destrieux cortical surface areas
mri_y_smr_area_dst <- abcd_load(core_path("imaging/mri_y_smr_area_dst.csv"))

# Neurite density (AtlasTrack, all fibers)
mri_y_rsi_rnd_at <- abcd_load(core_path("imaging/mri_y_rsi_rnd_at.csv"))

# Neurite density (Desikan, peri-cortical WM)
mri_y_rsi_rnd_wm_dsk <- abcd_load(core_path("imaging/mri_y_rsi_rnd_wm_dsk.csv"))

# Neurite density (Destriux, peri-cortical WM)
mri_y_rsi_rnd_wm_dst <- abcd_load(core_path("imaging/mri_y_rsi_rnd_wm_dst.csv"))
```

## Cortical thickness

### Missing data counts

```{r}
# Comparison of the two parcellations:
dst_cort_t <- mri_y_smr_thk_dst |>
    dplyr::filter(eventname == "baseline_year_1_arm_1") |>
    dplyr::select("subjectkey", "mrisdp_151")

dsk_cort_t <- mri_y_smr_thk_dsk |>
    dplyr::filter(eventname == "baseline_year_1_arm_1") |>
    dplyr::select("subjectkey", "smri_thick_cdk_mean")

dsk_cort_t |> na.omit() |> dim() # 11728 participants
dst_cort_t |> na.omit() |> dim() # 11715 participants
```

It's close, but it looks like a few more participants have complete data with the Desikan parcellation.

### Correlation

```{r}
cort_t_dfs <- dplyr::inner_join(dst_cort_t, dsk_cort_t, by = "subjectkey") |>
    na.omit()

cort_t_dfs |>
    ggplot(aes(x = mrisdp_151, y = smri_thick_cdk_mean)) +
    geom_point() +
    labs(
        x = "Destrieux parcellation whole brain cortical thickness",
        y = "Desikan parcellation mean brain cortical thickness"
    ) +
    theme_bw() +
    theme(text = element_text(size = 20))

cor(cort_t_dfs$"mrisdp_151", cort_t_dfs$"smri_thick_cdk_mean")

ggsave(fig_path("destrieux_vs_desikan_cort_t.png", date = TRUE))
```

Excluding what looks like negligible noise, they seem to be nearly identical.

## Neurite densities

### Missing data

```{r}
dsk_pc_wm <- mri_y_rsi_rnd_wm_dsk |>
    dplyr::filter(eventname == "baseline_year_1_arm_1") |>
    dplyr::select("subjectkey", "dmri_rsirndwm_cdk_mean")

dst_pc_wm <- mri_y_rsi_rnd_wm_dst |>
    dplyr::filter(eventname == "baseline_year_1_arm_1") |>
    dplyr::select("subjectkey", "dmri_rsirndwm_cdx_mean")

dsk_pc_wm |> na.omit() |> dim()
dst_pc_wm |> na.omit() |> dim()
```

Again it appears that a few more participants have Desikan data.

### Correlation

```{r}
pc_wm_df <- dplyr::inner_join(dst_pc_wm, dsk_pc_wm, by = "subjectkey") |>
    na.omit()

pc_wm_df |>
    ggplot(aes(x = dmri_rsirndwm_cdx_mean, y = dmri_rsirndwm_cdk_mean)) +
    geom_point() +
    labs(
        x = "Destrieux parcellation peri-cortical WM neurite density",
        y = "Desikan parcellation peri-cortical WM neurite density"
    ) +
    theme_bw() +
    theme(text = element_text(size = 20))

cor(pc_wm_df$"dmri_rsirndwm_cdx_mean", pc_wm_df$"dmri_rsirndwm_cdk_mean")

ggsave(fig_path("destrieux_vs_desikan_pericortical_wm_nd.png", date = TRUE))
```
