# RSI Measures in ABCD


## Name and data changes in the 4.0 release

On page 11 of the release file *3a. NDA 4.0 Changes and Known Issues.pdf*, the following is stated regarding neurite density / RSI:

> ...Measures derived from this RSI model fit included restricted normalized isotropic (RNI), restricted normalized directional (RND), restricted normalized total (RNT), hindered normalized isotropic (HNI), hindered normalized directional (HND), and hindered normalized total (HNT), and free normalized isotropic (FNI).
These normalized RSI measures are unitless and range from 0 to 1.
**Note that thes abbreviations differ from those used in previous releases and in Hagler et al., 2019.**
RNI and HNI were previously called N0 and N0_s2, respectively.
**RND and HND were previously called ND and ND_s2.**
RNT and HNT were previously called NT and NT_s2.
FNI was not previously included.
The tabulated data structures for RSI-derived ROI average measures have been replaced for ABCD Release 4.0 (abcd_drsip101, abcd_drsip201, abcd_drsip301, abcd_drsip401, abcd_drsip501, abcd_drsip601, and abcd_drsip701), with each data structure corresponding to one RSI-derived measure for all ROIs.

As well as:

> **[new element names, descriptions, and DEAP aliases for] mri_rsi_p102, mri_rsi_p202, abcd_drsidp101, abcd_drsidp201, and abcd_drsidp301**

In this change it also appears that references to "sub-adjacent white matter" have now changed to "peri_cortical white matter".


## A summary of currently accessible files

The following files appear when searching "dMRI RSI" in the NDA:

| File                                             | Short name            | Summary                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          |
|--------------------------------------------------+-----------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
| ABCD dMRI RSI Destrieux Parcellation Part 1 to 3 | abcd_drsidp101 to 301 | Only in release 2.0 and 3.0. Contained the parameters: F0 divided by T with restricted volume fraction, F0 divided by T with hindered volume fraction, Neurite density (FD divided by T) with restricted volume fraction, Total restricted volume fraction (FT divided by T), Total hindered volume fraction (FT divided by T), and F0 divided by T with restricted volume fraction, F0 divided by T with hindered volume fraction. All parameters were for cortical Destrieux ROIs (or GM-WM boundaries / sub-adjacent WM based on those ROIs). |
| ABCD dMRI RSI Part 1 to 2                        | mri_rsi_p102          | Only in release 2.0 and 3.0. The same RSI parameters as above, but for ASEG (AKA automatic segmentation / Fischl) and Desikan (AKA anatomical parcellation / aparc) ROIs.                                                                                                                                                                                                                                                                                                                                                                                                          |
| ABCD dMRI RSI Part 1 to 7                        | abcd_drsip101 to 701  | Only in release 4.0. This is what I am using. Contains the parameters: restricted normalized isotropic diffusion (file 1), **restricted normalized directional diffusion (file 2)**, restricted normalized total diffusion (file 3), hindered normalized isotropic diffusion (file 4), hindered normalized directional diffusion (file 5), hindered normalized total diffusion (file 6), and free normalized isotropic diffusion (file 7). All parameters were collected for for AtlasTrack, ASEG, Desikan, and Destrieux ROIs. |


## Neurite density data

The bolded file 2 (i.e., abcd_drsip201) contains neurite density data, now referred to as restricted normalized directional data.

| Element name      | Parcellation     | Description                                                                                                                                                          |
|-------------------+------------------+----------------------------------------------------------------------------------------------------------------------------------------------------------------------|
| dmri_rsirnd_fib_* | AtlasTrack       | Major white matter structures (the ones I should use)                                                                                                                |
| dmri_rsirnd_scs_* | ASEG             | Subcortical ROIs                                                                                                                                                     |
| dmri_rsirndwm_*   | Desikan cortical | White matter structures that are "peri-cortical" to ROIs from the Desikan parcellation (the ones I have accidentally exclusively been using prior to March 24th 2023). |
| dmri_rsirndgm_*   | Desikan cortical | Gray matter gyri and sulci                                                                                                                                           |
| dmri_rsirndgwc_*  | Desikan cortical | Gray-white contrast


## Code for data extraction

### The outdated function

The function below was used to pull peri-cortical white matter structures from the NDA file `drsip201.txt`.
It makes use of one non-dplyr function, `abcd_import` from my abcdutils package, which is just used to optionally filter the dataframe by any subject list or data collection timepoint the user specifies.

```{r eval = FALSE}
#' Extract white matter neurite densities
#'
#' @param drsip201 Data file containing neurite density data
#' @param subjects Dataframe containing list of required subjects
#' @param t timepoint for data collection (0: baseline, 1: 1yfu, ... 3: 3yfu)
#'
#' @return wmnd_df Dataframe of white matter neurite densities
#'
#' @export
get_wmnd <- function(drsip201, subjects = NULL, t = NULL) {
    nd_raw <- abcdutils::abcd_import(drsip201, subjects, t = t)
    wmnd_df <- nd_raw |>
        dplyr::select(
            "subjectkey",
            dplyr::contains("rsirndwm")) |>
        dplyr::select(-c( # Not interested in redundant mean ROIs:
            "dmri_rsirndwm_cdx_mean", # overall mean
            "dmri_rsirndwm_cdx_meanlh", # left hemisphere
            "dmri_rsirndwm_cdx_meanrh")) # right hemisphere
    return(wmnd_df)
}
```

### Updated function v1: only keep major white matter tracts

```{r eval = FALSE}
#' Extract white matter neurite densities
#'
#' @param drsip201 Data file containing neurite density data
#' @param subjects Dataframe containing list of required subjects
#' @param t timepoint for data collection (0: baseline, 1: 1yfu, ... 3: 3yfu)
#'
#' @return wmnd_df Dataframe of white matter neurite densities
#'
#' @export
get_wmnd <- function(drsip201, subjects = NULL, t = NULL) {
    nd_raw <- abcdutils::abcd_import(drsip201, subjects, t = t)
    wmnd_df <- nd_raw |>
        dplyr::select(
            "subjectkey",
            dplyr::contains("rsirnd_fib")) |>
        dplyr::select(-c( # Not interested in redundant mean ROIs:
            "dmri_rsirnd_fib_fxcutrh", # Duplicate right fornix without fimbria
            "dmri_rsirnd_fib_fxcutlh", # Duplicate left fornix without fimbria
            "dmri_rsirnd_fib_allfib", # All fibers
            "dmri_rsirnd_fib_afbncrh", # All right hemisphere without CC
            "dmri_rsirnd_fib_afbnclh", # All left hemisphere without CC
            "dmri_rsirnd_fib_allfibrh", # All right hemisphere
            "dmri_rsirnd_fib_allfiblh")) # All left hemisphere
    return(wmnd_df)
}
```

In this updated function version, the WM variables to be used are those containing the string "rsirnd_fib" (major white matter ROIs defined by the AtlasTrack fiber segmentation) excluding redundant (e.g., keeping the right fornix as well as the right fornix without the fimbria) or summary ROIs (e.g., merging all the right hemisphere ROIs into a single ROI).


### Updated function v2: keep major white matter tracts as well as peri-cortical white matter

```{r eval = FALSE}
#' Extract white matter neurite densities
#'
#' @param drsip201 Data file containing neurite density data
#' @param subjects Dataframe containing list of required subjects
#' @param t timepoint for data collection (0: baseline, 1: 1yfu, ... 3: 3yfu)
#'
#' @return wmnd_df Dataframe of white matter neurite densities
#'
#' @export
get_wmnd <- function(drsip201, subjects = NULL, t = NULL) {
    nd_raw <- abcdutils::abcd_import(drsip201, subjects, t = t)
    wmnd_df <- nd_raw |>
        dplyr::select(
            "subjectkey",
            dplyr::contains("rsirnd_fib", "rsirndwm")) |>
        dplyr::select(-c( # Not interested in redundant mean ROIs:
            "dmri_rsirnd_fib_fxcutrh", # Duplicate right fornix without fimbria
            "dmri_rsirnd_fib_fxcutlh", # Duplicate left fornix without fimbria
            "dmri_rsirnd_fib_allfib", # All fibers
            "dmri_rsirnd_fib_afbncrh", # All right hemisphere without CC
            "dmri_rsirnd_fib_afbnclh", # All left hemisphere without CC
            "dmri_rsirnd_fib_allfibrh", # All right hemisphere
            "dmri_rsirnd_fib_allfiblh", # All left hemisphere
            "dmri_rsirndwm_cdx_mean", # overall mean (peri-cortical wm)
            "dmri_rsirndwm_cdx_meanlh", # left hemisphere (peri-cortical wm)
            "dmri_rsirndwm_cdx_meanrh")) # right hemisphere (peri-cortical wm)
    return(wmnd_df)
}
```

In this updated function version, both major white matter tracts defined by AtlasTrack and peri-cortical / sub-adjacent WM structures based on the Desikan cortical parcellation are kept.
I will try re-running the analyses with this version and see if results are significantly changed.
