```{r}
library(ggplot2)
library(readr)
library(dplyr)
library(here)
library(abcdutils)
library(patchwork)
library(ggplot2)
library(visdat)

core_path <- path_maker(here(paste0("data/abcd/core3")))
input_path <- path_maker(here(paste0("data/abcd/inputs")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))

import <- function(path) {
    return(abcd_load(core_path(path)))
}

# Pubertal development scale, youth report
ph_y_pds <- import("physical-health/ph_y_pds.csv")
# Pubertal development scale, parent report
ph_p_pds <- import("physical-health/ph_p_pds.csv")

mtbi_subjects <- read_subjects(sub_path("2024_07_30_mtbi_subjects.csv"))
uninjured_subjects <- read_subjects(sub_path("2024_07_30_uninjured_subjects.csv"))
```


```{r}
d_pubertal_status_mtbi <- get_pubertal_status(
    ph_p_pds,
    ph_y_pds,
    mtbi_subjects,
    max_value = 3,
    t = 0
)
tibble(d_pubertal_status_mtbi)

ph_p_pds |> colnames()

pds_na_check <- function(ph_p_pds, t, subjects, idkna = TRUE) {
    if (idkna) {
        ph_p_pds[ph_p_pds == 999] <- NA
        ph_p_pds[ph_p_pds == 777] <- NA
    }
    pds_check_df <- ph_p_pds |>
        filter_timepoint(t = t) |>
        filter_subjects(subjects = subjects) |>
        dplyr::select(
            "pds_1_p",
            "pds_2_p",
            "pds_3_p",
            "pds_m4_p",
            "pds_m5_p",
            "pds_f4_p",
            "pds_f5b_p",
            "pds_p_ss_female_category",
            "pds_p_ss_male_category",
            "pds_p_ss_female_category_2",
            "pds_p_ss_male_category_2"
        )
    pds_check_df$"pds_4_p" <- rowMeans(
        pds_check_df[, c("pds_m4_p", "pds_f4_p")],
        na.rm = TRUE
    )
    pds_check_df$"pds_5_p" <- rowMeans(
        pds_check_df[, c("pds_m5_p", "pds_f5b_p")],
        na.rm = TRUE
    )
    pds_check_df$"manual_summary" <- rowSums(
        pds_check_df[, c("pds_1_p", "pds_2_p", "pds_3_p", "pds_4_p", "pds_5_p")]
    )
    pds_check_df$"parent_summary" <- rowMeans(
        pds_check_df[, c("pds_p_ss_female_category", "pds_p_ss_male_category")],
        na.rm = TRUE
    )
    pds_check_df$"parent_summary2" <- rowMeans(
        pds_check_df[, c("pds_p_ss_female_category_2", "pds_p_ss_male_category_2")],
        na.rm = TRUE
    )
    pds_check_df$"biorxiv_summary_m" <- pds_check_df$"pds_2_p" +
        pds_check_df$"pds_m4_p" + pds_check_df$"pds_m5_p"
    pds_check_df$"biorxiv_summary_f" <- pds_check_df$"pds_2_p" +
        pds_check_df$"pds_f4_p" + pds_check_df$"pds_f5b_p"
    pds_check_df$"biorxiv_summary" <- rowMeans(
        pds_check_df[, c("biorxiv_summary_f", "biorxiv_summary_m")],
        na.rm = TRUE
    )
    pds_check_df <- pds_check_df |>
        dplyr::select(
            -pds_m4_p,
            -pds_f4_p,
            -pds_m5_p,
            -pds_f5b_p,
            -dplyr::contains("cat"),
            -dplyr::contains("biorxiv_summary_")
        )
    return(pds_check_df)
}

pds_y_na_check <- function(ph_y_pds, t, subjects, idkna = TRUE) {
    if (idkna) {
        ph_y_pds[ph_y_pds == 999] <- NA
        ph_y_pds[ph_y_pds == 777] <- NA
    }
    pds_check_df <- ph_y_pds |>
        filter_timepoint(t = t) |>
        filter_subjects(subjects = subjects) |>
        dplyr::select(
            "pds_ht2_y",
            "pds_bdyhair_y",
            "pds_skin2_y",
            "pds_m4_y",
            "pds_m5_y",
            "pds_f4_2_y",
            "pds_f5_y",
            "pds_y_ss_female_category",
            "pds_y_ss_male_category",
            "pds_y_ss_female_category_2",
            "pds_y_ss_male_cat_2"
        )
    pds_check_df$"pds_4_y" <- rowMeans(
        pds_check_df[, c("pds_m4_y", "pds_f4_2_y")],
        na.rm = TRUE
    )
    pds_check_df$"pds_5_y" <- rowMeans(
        pds_check_df[, c("pds_m5_y", "pds_f5_y")],
        na.rm = TRUE
    )
    pds_check_df$"manual_summary" <- rowSums(
        pds_check_df[, c("pds_ht2_y", "pds_bdyhair_y", "pds_skin2_y", "pds_4_y", "pds_5_y")]
    )
    pds_check_df$"youth_summary" <- rowMeans(
        pds_check_df[, c("pds_y_ss_female_category", "pds_y_ss_male_category")],
        na.rm = TRUE
    )
    pds_check_df$"youth_summary2" <- rowMeans(
        pds_check_df[, c("pds_y_ss_female_category_2", "pds_y_ss_male_cat_2")],
        na.rm = TRUE
    )
    pds_check_df$"biorxiv_summary_m" <- pds_check_df$"pds_bdyhair_y" +
        pds_check_df$"pds_m4_y" + pds_check_df$"pds_m5_y"
    pds_check_df$"biorxiv_summary_f" <- pds_check_df$"pds_bdyhair_y" +
        pds_check_df$"pds_f4_2_y" + pds_check_df$"pds_f5_y"
    pds_check_df$"biorxiv_summary" <- rowMeans(
        pds_check_df[, c("biorxiv_summary_f", "biorxiv_summary_m")],
        na.rm = TRUE
    )
    pds_check_df <- pds_check_df |>
        dplyr::rename(
            "pds_1_y" = "pds_ht2_y",
            "pds_2_y" = "pds_bdyhair_y",
            "pds_3_y" = "pds_skin2_y"
        ) |>
        dplyr::select(
            -pds_m4_y,
            -pds_f4_2_y,
            -pds_m5_y,
            -pds_f5_y,
            -dplyr::contains("cat"),
            -dplyr::contains("biorxiv_summary_")
        )
    return(pds_check_df)
}

p0idkna <- pds_na_check(ph_p_pds, 0, mtbi_subjects)
p1idkna <- pds_na_check(ph_p_pds, 1, mtbi_subjects)
p2idkna <- pds_na_check(ph_p_pds, 2, mtbi_subjects)
p3idkna <- pds_na_check(ph_p_pds, 3, mtbi_subjects)
p4idkna <- pds_na_check(ph_p_pds, 4, mtbi_subjects)

y0idkna <- pds_y_na_check(ph_y_pds, 0, mtbi_subjects)
y1idkna <- pds_y_na_check(ph_y_pds, 1, mtbi_subjects)
y2idkna <- pds_y_na_check(ph_y_pds, 2, mtbi_subjects)
y3idkna <- pds_y_na_check(ph_y_pds, 3, mtbi_subjects)
y4idkna <- pds_y_na_check(ph_y_pds, 4, mtbi_subjects)

parent_reports <- vis_miss(p0idkna) + labs(title = "Parent report, T0") +
    vis_miss(p1idkna) + labs(title = "Parent report, T1") +
    vis_miss(p2idkna) + labs(title = "Parent report, T2") +
    vis_miss(p3idkna) + labs(title = "Parent report, T3") +
    vis_miss(p4idkna) + labs(title = "Parent report, T4")

youth_reports <- vis_miss(y0idkna) + labs(title = "Youth report, T0") +
    vis_miss(y1idkna) + labs(title = "Youth report, T1") +
    vis_miss(y2idkna) + labs(title = "Youth report, T2") +
    vis_miss(y3idkna) + labs(title = "Youth report, T3") +
    vis_miss(y4idkna) + labs(title = "Youth report, T4")
```

Parent category 2 values require question 2, 4, and 5.

Pubertal Developmental Scale Parent:
Female Category - based on sex at birth;

pubertdev_sum_p_f = pubertdev_2_p plus pubertdev_f4_p

1 - prepuberty    - pubertdev_sum_p_f   =  2 and pubertdev_f5b_p = 1
2 - early puberty - pubertdev_sum_p_f   =  3 and pubertdev_f5b_p = 1
3 - mid puberty   - pubertdev_sum_p_f   >  3 and pubertdev_f5b_p = 1
4 - late puberty  - pubertdev_sum_p_f   <= 7 and pubertdev_f5b_p = 4 
5 - post puberty  - pubertdev_sum_p_f   =  8 and pubertdev_f5b_p = 4 

```{r}
pdf(
    fig_path("parent_pds_missingness.pdf", TRUE),
    width = 12,
    height = 10
)
dev.off()

pdf(
    fig_path("youth_pds_missingness.pdf", TRUE),
    width = 12,
    height = 10
)
print(youth_reports)
dev.off()
```
