---
title: "Comparison of PV and EN Subject Lists"
output:
  html_document:
    toc: true
    toc_depth: 2
---

```{r, include=FALSE}
knitr::opts_chunk$set(
    comment = "#>",
    fig.width = 6,
    message = FALSE
)
```


This report explores the subjects included in PV and EN ABCD longitudinal analyses.
Both longitudinal analyses focus on children who have sustained an mTBI between baseline and 2-year follow-up.

## Importing libraries

```{r}
library(ggplot2)
library(readr)
library(dplyr)
library(here)
library(abcdutils)
library(gt)
```

## Importing 5.0 release data

```{r}
core_path <- path_maker(here(paste0("data/abcd/core")))
input_path <- path_maker(here(paste0("data/abcd/inputs")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))

import <- function(path) {
    return(abcd_load(core_path(path)))
}

ph_p_otbi <- import("physical-health/ph_p_otbi.csv")
abcd_y_lt <- import("abcd-general/abcd_y_lt.csv")
```

## PV subject selection

The following extraction uses the `get_mtbi_subjects` function in `abcdutils`.
This function uses another `abcdutils` function, `detail_mtbi`, to first define attributes such as whether or not an Ohio TBI entry should could as no injury, a mild injury, a moderate injury, or a severe injury; what the mechanism of that injury was; when the injury occurred; how many total mTBIs the child has had; and details related to LOC and memory loss / feeling dazed.
After a call to `detail_mtbi`, `get_mtbi_subjects` itself selects those who have had an mTBI but who have not had any moderate or severe TBIs.
The function also removes those who had their injury earlier than a timepoint specified by the `min_mpi` (minimum months post injury) argument.

```{r}

# Subjects who had an mTBI pre-baseline
mtbi_subjects_t0 <- abcdutils::get_mtbi_subjects(
    ph_p_otbi,
    abcd_y_lt,
    min_mpi = 0,
    t = 0
) |>
    dplyr::select(subjectkey) |>
    unlist() |>
    as.character()

# Subjects who had an mTBI between baseline and 1yfu
mtbi_subjects_t1 <- abcdutils::get_mtbi_subjects(
    ph_p_otbi,
    abcd_y_lt,
    min_mpi = 0,
    t = 1
) |>
    dplyr::select(subjectkey) |>
    unlist() |>
    as.character()

# Subjects who had an mTBI between 1yfu and 2yfu
mtbi_subjects_t2 <- abcdutils::get_mtbi_subjects(
    ph_p_otbi,
    abcd_y_lt,
    min_mpi = 0,
    t = 2
) |>
    dplyr::select(subjectkey) |>
    unlist() |>
    as.character()

# mTBI between baseline and 1yfu, but had 0 mTBIs pre-baseline
mtbi_subjects_t1o <- mtbi_subjects_t1[!mtbi_subjects_t1 %in% mtbi_subjects_t0]

# mTBI between 1yfu and 2yfu, but had 0 mTBIs pre-baseline
mtbi_subjects_t2o <- mtbi_subjects_t2[!mtbi_subjects_t2 %in% mtbi_subjects_t0]

# mTBI between baseline and 2yfu, but had 0 mTBIs pre-baseline
mtbi_subjects_0_to_2 <- unique(c(mtbi_subjects_t1o, mtbi_subjects_t2o))

# Exporting the subjects
data.frame(subjectkey = mtbi_subjects_0_to_2) |>
    write_csv(sub_path("mtbi_subjects_0_to_2.csv", date = TRUE))

# Subjects who had 0 mTBIs pre-baseline
uninjured_subjects_t0 <- get_uninjured_subjects(ph_p_otbi, abcd_y_lt, t = 0) |>
    dplyr::select(subjectkey) |>
    unlist() |>
    as.character()

# Subjects who had 0 mTBIs between baseline and 1yfu
uninjured_subjects_t1 <- get_uninjured_subjects(ph_p_otbi, abcd_y_lt, t = 1) |>
    dplyr::select(subjectkey) |>
    unlist() |>
    as.character()

# Subjects who had 0 mTBIs between 1yfu and 2yfu
uninjured_subjects_t2 <- get_uninjured_subjects(ph_p_otbi, abcd_y_lt, t = 2) |>
    dplyr::select(subjectkey) |>
    unlist() |>
    as.character()

# Subjects who had 0 mTBIs at any timepoint prior to 2yfu
uninjured_subjects_0_to_2 <- Reduce(
    intersect,
    list(
        uninjured_subjects_t0,
        uninjured_subjects_t1,
        uninjured_subjects_t2
    )
)

# Exporting those subjects
data.frame(subjectkey = uninjured_subjects_0_to_2) |>
    write_csv(sub_path("uninjured_subjects_0_to_2.csv", date = TRUE))
```

Re-importing the mTBI and control subjects:

```{r}
mtbi_subjects_0_to_2 <- read_csv(
    sub_path("2024_04_02_mtbi_subjects_0_to_2.csv")
)

uninjured_subjects_0_to_2 <- read_csv(
    sub_path("2024_04_02_uninjured_subjects_0_to_2.csv")
)

nrow(mtbi_subjects_0_to_2) # 220

nrow(uninjured_subjects_0_to_2) #10018
```

## Organizing PV mTBI information into a single data.frame

```{r}
injured_as_of_baseline <- data.frame(
    subjectkey = mtbi_subjects_t0,
    pv_mtbi_pre_baseline = TRUE
)

injured_between_0_and_1 <- data.frame(
    subjectkey = mtbi_subjects_t1,
    pv_mtbi_baseline_to_1 = TRUE
)

injured_between_1_and_2 <- data.frame(
    subjectkey = mtbi_subjects_t2,
    pv_mtbi_1_to_2 = TRUE
)

# Dataframe of those who are in PV mTBI group
pv_included <- data.frame(
    subjectkey = mtbi_subjects_0_to_2,
    pv_sample = TRUE
)

# Dataframe of those who are in PV control group
pv_never_injured <- data.frame(
    subjectkey = uninjured_subjects_0_to_2,
    pv_never_injured = TRUE
)

# Combining the above dataframes
pv_injured <- dplyr::full_join(
    injured_as_of_baseline,
    injured_between_0_and_1,
    by = "subjectkey"
)

pv_injured <- dplyr::full_join(
    pv_injured,
    injured_between_1_and_2,
    by = "subjectkey"
)

pv_injured <- dplyr::full_join(
    pv_injured,
    pv_included,
    by = "subjectkey"
)

pv_subjects <- dplyr::full_join(
    pv_injured,
    pv_never_injured,
    by = "subjectkey"
)

head(pv_subjects)
```

## Importing and merging EN subjects

```{r}
# EN mTBI group (used for behaviour)
en_behav <- read_csv(sub_path("1_cbcl_subjectIDs.csv"))
en_behav <- en_behav |>
    dplyr::filter(group == "mTBI") |>
    dplyr::select(subjectkey) |>
    unlist() |>
    as.character() |>
    unique()
en_behav <- data.frame(
    subjectkey = en_behav,
    en_b_sample = TRUE
)

nrow(en_behav) # 239

# EN mTBI group - neuroimaging subset
en_neuro <- read_csv(sub_path("2_rsi_subjectIDs.csv"))
en_neuro <- en_neuro |>
    dplyr::filter(group == "mTBI") |>
    dplyr::select(subjectkey) |>
    unlist() |>
    as.character() |>
    unique()
en_neuro <- data.frame(
    subjectkey = en_neuro,
    en_n_sample = TRUE
)

nrow(en_neuro) # 134

# EN control group
en_uninj <- read_csv(sub_path("1_cbcl_subjectIDs.csv"))
en_uninj <- en_uninj |>
    dplyr::filter(group == "CTRL") |>
    dplyr::select(subjectkey) |>
    unlist() |>
    as.character() |>
    unique()
en_uninj <- data.frame(
    subjectkey = en_uninj,
    en_never_injured = TRUE
)

# Combining EN data into a single dataframe
en_subjects <- dplyr::full_join(en_neuro, en_behav, by = "subjectkey")
en_subjects <- dplyr::full_join(en_subjects, en_uninj, by = "subjectkey")

# Combining PV and EN data
all_subjects <- dplyr::full_join(pv_subjects, en_subjects, by = "subjectkey")
all_subjects <- replace(all_subjects, is.na(all_subjects), FALSE)

head(all_subjects)
```

## Subjects that differ between PV and EN mTBI groups

```{r}
en_in_pv <- en_behav$"subjectkey" %in% mtbi_subjects_0_to_2$"subjectkey"
en_only <- en_behav$"subjectkey"[!en_in_pv]

# 35 subjects in EN sample that are not in PV sample
length(en_only)

pv_in_en <- mtbi_subjects_0_to_2$"subjectkey" %in% en_behav$"subjectkey"
pv_only <- mtbi_subjects_0_to_2$"subjectkey"[!pv_in_en]

# 16 subjects in PV sample that are not in EN sample
length(pv_only)
```

The subsequent chunks seek to explain the 35 subjects that are unique to EN sample and the 16 subjects that are unique to PV sample.

```{r}
summary <- data.frame(
    subjectkey = as.character(),
    sample = as.character(),
    reason = as.character()
)

summary2 <- rbind(
    summary,
    data.frame(
        subjectkey = pv_only,
        sample = "pv_only",
        reason = NA
    )
)

summary3 <- rbind(
    summary2,
    data.frame(
        subjectkey = en_only,
        sample = "en_only",
        reason = NA
    )
)

summary3
```

## Children only in PV sample

```{r}
all_subjects |>
    dplyr::filter(subjectkey %in% pv_only)

all_en_subjects <- read_csv(sub_path("1_cbcl_subjectIDs.csv"))

pv_only %in% all_en_subjects$"subjectkey"
```

The children unique to PV sample are not present in EN mTBI/CTRL subject lists.

### Checking for complete mTBI data in 4.0 release

Checking to see if they are in the 4.0 release at all:

```{r}
abcd_4 <- "/home/prashanth/mnt/wheeler-lab/lab-data/abcd/4.0/trauma/"

abcd_otbi01 <- read_delim(paste0(abcd_4, "abcd_otbi01.txt"))
abcd_lpohstbi01 <- read_delim(paste0(abcd_4, "abcd_lpohstbi01.txt"))

# Subjects are found in baseline data
pv_only %in% abcd_otbi01$"subjectkey"

abcd_lpohstbi01$"eventname" |> unique()

abcd_4_1yfu <- abcd_lpohstbi01 |>
    dplyr::filter(eventname == "1_year_follow_up_y_arm_1")

# Subjects are found in 1yfu data
pv_only %in% abcd_4_1yfu$"subjectkey"

abcd_4_2yfu <- abcd_lpohstbi01 |>
    dplyr::filter(eventname == "2_year_follow_up_y_arm_1")

# Some subjects are missing from 2yfu data
pv_only %in% abcd_4_2yfu$"subjectkey"

pv_only[!pv_only %in% abcd_4_2yfu$"subjectkey"]
```

The following subjects are only in PV sample as they did not have mTBI data collection at 2yfu until the 5.0 release:

1. NDAR_INV56J3P7WJ
2. NDAR_INV619DWVEK
3. NDAR_INVT0056CXX
4. NDAR_INVYVRMB9TW
5. NDAR_INV2358EMKW
6. NDAR_INV6VB0DZ51
7. NDAR_INVAFNHCVUJ
8. NDAR_INVGWGVANWJ


This explains 8/16 of the subjects unique to PV sample.

There are still 8/16 subjects unique to PV that are unexplained and 35/35 subjects unique to EN that are unexplained.

```{r}
no_5 <- pv_only[!pv_only %in% abcd_4_2yfu$"subjectkey"]

summary4 <- summary3

summary4[summary4$"subjectkey" %in% no_5, "reason"] <-
    "(A) 2yfu TBI data missing in 4.0, but present in 5.0."

summary4
```

Here are the remaining 8:

```{r}
pv_only_all_in_4 <- pv_only[pv_only %in% abcd_4_2yfu$"subjectkey"]

pv_only_all_in_4

all_subjects |>
    dplyr::filter(subjectkey %in% pv_only_all_in_4)

```

After checking with Eman, it seems these kids were excluded on the basis of reporting an injury during a longitudinal data collection period where the injury occured at an age prior to the child's age at baseline.
This is an unfortunate source of ambiguity.
It is possible that the parents are recalling an earlier injury that they forgot to mention at baseline data collection.
However, the phrasings of these Ohio TBI questions are specifically worded to ask the parent "Since we last saw you", [has your child had an injury?].
Because ABCD anonymizes ages, I assume that discrepancies where a reported mTBI at 1 or 2yfu that seem to occur pre-baseline are the result of age noising, and are indeed representative of injuries that took place post baseline.

When did those children have their mTBIs?

```{r}
t0_mtbi_df <- detail_mtbi(ph_p_otbi, abcd_y_lt, t = 0)
t1_mtbi_df <- detail_mtbi(ph_p_otbi, abcd_y_lt, t = 1)
t2_mtbi_df <- detail_mtbi(ph_p_otbi, abcd_y_lt, t = 2)

# These kids had no baseline injuries
t0_mtbi_df |>
    dplyr::filter(subjectkey %in% pv_only_all_in_4) |>
    dplyr::select(subjectkey, mtbi_count)

# All of them had injuries between 1yfu and 2yfu
t1_mtbi_df |>
    dplyr::filter(subjectkey %in% pv_only_all_in_4) |>
    dplyr::select(subjectkey, mtbi_count)

# One of them had an mTBI between 1yfu and 2yfu
t2_mtbi_df |>
    dplyr::filter(subjectkey %in% pv_only_all_in_4) |>
    dplyr::select(subjectkey, mtbi_count)
```

Most of them had their injury between baseline and 1 year follow up.

```{r}
long_pre_baseline <- data.frame(
    subjectkey = pv_only_all_in_4
)

baseline_age <- get_interview_age(
    abcd_y_lt,
    t = 0,
    as_years = FALSE
)
colnames(baseline_age) <- c("subjectkey", "baseline_age")

y1_mtbi_age <- get_mtbi_age(
    ph_p_otbi,
    abcd_y_lt,
    t = 1,
    as_years = TRUE
)
colnames(y1_mtbi_age) <- c("subjectkey", "y1fu_age")

age_explain_df <- dplyr::inner_join(long_pre_baseline, baseline_age, by = "subjectkey")
age_explain_df <- dplyr::inner_join(age_explain_df, y1_mtbi_age, by = "subjectkey")
age_explain_df <- age_explain_df |>
    dplyr::mutate(
        upper_1yfu_age_bound = y1fu_age * 12 + 11,
        possible_post_baseline = upper_1yfu_age_bound >= baseline_age
    )

age_explain_df |> gt()

possible_post_baseline <-
    age_explain_df$"subjectkey"[age_explain_df$"possible_post_baseline" == TRUE]

not_possible_post_baseline <-
    age_explain_df$"subjectkey"[age_explain_df$"possible_post_baseline" == FALSE]

not_possible_post_baseline

summary5 <- summary4

summary5[summary5$"subjectkey" %in% possible_post_baseline, "reason"] <-
    paste0(
        "(B) Injury age reported at longitudinal is extremely close to",
        " baseline interview age."
    )

summary5[summary5$"subjectkey" %in% not_possible_post_baseline, "reason"] <-
    paste0(
        "(B2) Injury age reported at longitudinal is pre-baseline.")

summary5
```

## Children only in EN sample

### EN sample that were not a part of PV mTBI or uninjured group

```{r}

# 2 children present in EN sample that are not in PV sample
en_only_sub <- en_behav[!en_behav$"subjectkey" %in% pv_subjects$"subjectkey", ]

en_only_sub$"subjectkey"

```

These two subjects are in EN mTBI sample but not in PV mTBI or uninjured group.
NDAR_INVV9LM0ZAG and NDAR_INVT7YJ84MG.

Why were they excluded from PV sample?

```{r}

all_subjects |>
    dplyr::filter(subjectkey %in% en_only_sub$"subjectkey")

# If they show up in true here, it means they didn't count as having mTBI:
en_only_sub$"subjectkey" %in% mtbi_subjects_t0
en_only_sub$"subjectkey" %in% mtbi_subjects_t1
en_only_sub$"subjectkey" %in% mtbi_subjects_t2

# If they show up as true here, it means they had no injuries:
en_only_sub$"subjectkey" %in% uninjured_subjects_t0
en_only_sub$"subjectkey" %in% uninjured_subjects_t1
en_only_sub$"subjectkey" %in% uninjured_subjects_t2
```

The first subject seems to have had some sort of injury at T1 that didn't count towards mTBI.
Similar situation for the second subject and T2.

```{r}

t1_mtbi_df <- detail_mtbi(ph_p_otbi, abcd_y_lt, t = 1)

t1_mtbi_df_en_only_sub <- t1_mtbi_df |>
    dplyr::filter(subjectkey == "NDAR_INVV9LM0ZAG")

t1_mtbi_df_en_only_sub$"moderate_or_severe_tbi"

t1_mtbi_df_en_only_sub$"other_loc_max_loc_mins"
```

Subject NDAR_INVV9LM0ZAG had a moderate/severe TBI flagged at the 1 year follow up.
This was on the basis that they had 45 minutes of LOC at their T1 injury.
Is this information present in the 4.0 release?

```{r}
abcd_lpohstbi01 |>
    dplyr::filter(subjectkey == "NDAR_INVV9LM0ZAG") |>
    data.frame() |>
    dplyr::select(tbi_6q_l)

search_dd("tbi_6q_l")
```

Yes.

```{r}
summary6 <- summary5

summary6[summary6$"subjectkey" == "NDAR_INVV9LM0ZAG", "reason"] <-
    "(C) Moderate/severe TBI (>30 min LOC) at 1YFU."
```

Now for the other individual, NDAR_INVT7YJ84MG.

```{r}

t2_mtbi_df <- detail_mtbi(ph_p_otbi, abcd_y_lt, t = 2)

t2_mtbi_df_en_only_sub <- t2_mtbi_df |>
    dplyr::filter(subjectkey == "NDAR_INVT7YJ84MG")

t2_mtbi_df_en_only_sub
```

This child also had a moderate severe TBI, this time at the 2yfu period.

```{r}
summary7 <- summary6

summary7[summary7$"subjectkey" == "NDAR_INVT7YJ84MG", "reason"] <-
    "(D) Moderate/severe TBI (>30 min LOC) at 2YFU."
```

### EN sample that were a part of PV mTBI or uninjured group

```{r}

# Subjects that are in both of our sample sets, but only EN's mTBI group.
en_sub_pv_exclude <- en_only[!en_only %in% en_only_sub$"subjectkey"]

all_subjects |>
    dplyr::filter(subjectkey %in% en_sub_pv_exclude)

en_sub_pv_exclude %in% mtbi_subjects_t0
```

These children all had pre-baseline mTBIs.

Here they are based on the 4.0 release data:

```{r}
# Baseline ohio dataframe with superfluous columns removed
baseline_4_tidy <- abcd_otbi01 |>
    dplyr::filter(subjectkey %in% en_sub_pv_exclude) |>
    data.frame() |>
    dplyr::select(
        -c(
            collection_id,
            dataset_id,
            collection_title,
            eventname,
            tbi_select_language___1,
            abcd_otbi01_id,
            src_subject_id,
            interview_date,
            interview_age,
            sex
        )
    )

baseline_4_tidy <-
    baseline_4_tidy[, colSums(is.na(baseline_4_tidy)) < nrow(baseline_4_tidy)]

# The legend:
for (i in seq_along(colnames(baseline_4_tidy))) {
    if (i > 1) {
        print(
            paste0(
                colnames(baseline_4_tidy)[i],
                ": ",
                gsub(
                    " ¿.*",
                    "",
                    as.character(
                        unlist(abcd_otbi01[1, colnames(baseline_4_tidy)[i]])
                    )
                )
            )
        )
    }
}

baseline_4_tidy
```

I don't go into detail here on how each individual person in the above 4.0 data should be assigned an mTBI, but a clearer outline from the 5.0 data is given below:

```{r}
t0_mtbi_df <- detail_mtbi(ph_p_otbi, abcd_y_lt, t = 0)

t0_mtbi_df |>
    dplyr::filter(subjectkey %in% en_sub_pv_exclude)
```

```{r}

summary8 <- summary7

summary8[summary8$"subjectkey" %in% en_sub_pv_exclude, "reason"] <-
    "(E) Had mTBI pre-baseline"

final_summary <- cbind(data.frame(subject = seq_len(nrow(summary8))), summary8)
```

# Final Summary

```{r}
library(kableExtra)

final_summary |> gt()

final_summary$"reason" <- gsub(").*", "", final_summary$"reason")
final_summary$"reason" <- gsub("\\(", "", final_summary$"reason")

final_summary |>
    dplyr::select(
        -c(subject, subjectkey)
    ) |>
    table()

```
