
# Loading in data

```{r}
library(abcdutils)
library(here)
library(readr)
library(metasnf)
library(mice)
library(ComplexHeatmap)
library(naniar)
library(dplyr)

input_path <- path_maker(here(paste0("data/abcd/inputs")))
raw_path <- path_maker(here(paste0("data/abcd/raw")))
core_path <- path_maker(here(paste0("data/abcd/core")))
misc_path <- path_maker(here(paste0("data/abcd/misc")))
sub_path <- path_maker(here(paste0("data/abcd/subjects")))
fig_path <- path_maker(here(paste0("data/abcd/results/figures")))
proc_path <- path_maker(here(paste0("data/abcd/results/processed")))

# Subjects
mtbi_subjects <- read_csv(sub_path("2024_03_12_mtbi_subjects.csv")) # 440
uninjured_subjects <- read_csv(sub_path("2024_03_12_uninjured_subjects.csv")) #11,408

import <- function(path) {
    return(abcd_load(core_path(path)))
}
```

```{r}
source("abcd/functions.R")
```

```{r}
as_mem_daze_mtbi <- read_csv(input_path("2024_03_12_as_mem_daze_mtbi.csv"))
as_mechanism_mtbi <- read_csv(input_path("2024_03_12_as_mechanism_mtbi.csv"))
as_loc_mtbi <- read_csv(input_path("2024_03_12_as_loc_mtbi.csv"))
d_interview_age_mtbi <- read_csv(input_path("2024_03_12_d_interview_age_mtbi.csv"))
d_mtbi_age_mtbi <- read_csv(input_path("2024_03_12_d_mtbi_age_mtbi.csv"))
d_sex_mtbi <- read_csv(input_path("2024_03_12_d_sex_mtbi.csv"))
d_income_mtbi <- read_csv(input_path("2024_03_12_d_income_mtbi.csv"))
d_race_mtbi <- read_csv(input_path("2024_03_12_d_race_mtbi.csv"))
d_pubertal_status_mtbi <- read_csv(input_path("2024_03_12_d_pubertal_status_mtbi.csv"))
mh_headaches_mtbi <- read_csv(input_path("2024_03_12_mh_headaches_mtbi.csv"))
mh_mtbi_count_mtbi <- read_csv(input_path("2024_03_12_mh_mtbi_count_mtbi.csv"))
p_loneliness_mtbi <- read_csv(input_path("2024_03_12_p_loneliness_mtbi.csv"))
p_screen_time_mtbi <- read_csv(input_path("2024_03_12_p_screen_time_mtbi.csv"))
p_sports_mtbi <- read_csv(input_path("2024_03_12_p_sports_mtbi.csv"))
p_exercise_mtbi <- read_csv(input_path("2024_03_12_p_exercise_mtbi.csv"))
p_prosocial_mtbi <- read_csv(input_path("2024_03_12_p_prosocial_mtbi.csv"))
p_fam_fn_mtbi <- read_csv(input_path("2024_03_12_p_fam_fn_mtbi.csv"))
p_parent_psych_mtbi <- read_csv(input_path("2024_03_12_p_parent_psych_mtbi.csv"))
cbcl_anxdep_mtbi <- read_csv(input_path("2024_03_12_cbcl_anxdep_mtbi.csv"))
cbcl_withdep_mtbi <- read_csv(input_path("2024_03_12_cbcl_withdep_mtbi.csv"))
cbcl_somatic_mtbi <- read_csv(input_path("2024_03_12_cbcl_somatic_mtbi.csv"))
cbcl_social_mtbi <- read_csv(input_path("2024_03_12_cbcl_social_mtbi.csv"))
cbcl_thought_mtbi <- read_csv(input_path("2024_03_12_cbcl_thought_mtbi.csv"))
cbcl_attention_mtbi <- read_csv(input_path("2024_03_12_cbcl_attention_mtbi.csv"))
cbcl_rulebreak_mtbi <- read_csv(input_path("2024_03_12_cbcl_rulebreak_mtbi.csv"))
cbcl_aggressive_mtbi <- read_csv(input_path("2024_03_12_cbcl_aggressive_mtbi.csv"))
sds_total_probs_mtbi <- read_csv(input_path("2024_03_12_sds_total_probs_mtbi.csv"))

rm_gord_cor_qc_mtbi <- read_csv(input_path("2024_03_12_rm_gord_cor_qc_mtbi.csv"))
rm_subc_cor_qc_mtbi <- read_csv(input_path("2024_03_12_rm_subc_cor_qc_mtbi.csv"))
dm_all_wmnd_qc_mtbi <- read_csv(input_path("2024_03_12_dm_all_wmnd_qc_mtbi.csv"))
sm_cort_sa_qc_mtbi <- read_csv(input_path("2024_03_12_sm_cort_sa_qc_mtbi.csv"))
sm_cort_t_qc_mtbi <- read_csv(input_path("2024_03_12_sm_cort_t_qc_mtbi.csv"))
sm_subc_v_qc_mtbi <- read_csv(input_path("2024_03_12_sm_subc_v_qc_mtbi.csv"))

rm_gord_cor_mtbi <- read_csv(input_path("2024_03_12_rm_gord_cor_mtbi.csv"))
rm_subc_cor_mtbi <- read_csv(input_path("2024_03_12_rm_subc_cor_mtbi.csv"))
dm_all_wmnd_mtbi <- read_csv(input_path("2024_03_12_dm_all_wmnd_mtbi.csv"))
sm_subc_v_mtbi <- read_csv(input_path("2024_03_12_sm_subc_v_mtbi.csv"))
sm_cort_t_mtbi <- read_csv(input_path("2024_03_12_sm_cort_t_mtbi.csv"))
sm_cort_sa_mtbi <- read_csv(input_path("2024_03_12_sm_cort_sa_mtbi.csv"))
```

## Neuroimaging QC

Should both T1 and T2 be QC'd?

https://www.ncbi.nlm.nih.gov/pmc/articles/PMC8543704/
    - cortical thickness
    - QC for t1 and t2
https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6981278/
    - hagler paper
    - "For most ABCD participants, a single scan of each type (T1w or T2w) is collected. If multiple scans of a given type are obtained, only one is used for processing and analysis. Results of manual quality control (QC) performed prior to the full image processing are used to exclude poor-quality structural scans (refer to the Protocol Compliance and Initial Quality Control section). If there is more than one acceptable scan of a given type, the scan with the fewest issues noted is used. In case of a tie, the final acceptable scan of the session is used."
    - Include protocol compliance? CTRL+F Protocol Compliance and Initial Quality Control
https://jamanetwork.com/journals/jamapediatrics/article-abstract/2756132
    - T1w & T2w

```{r}

mri_y_smr_vol_aseg <- import("imaging/mri_y_smr_vol_aseg.csv")
mri_y_smr_thk_dsk <- import("imaging/mri_y_smr_thk_dsk.csv")
mri_y_smr_area_dsk <- import("imaging/mri_y_smr_area_dsk.csv")
mri_y_rsi_rnd_at <- import("imaging/mri_y_rsi_rnd_at.csv")
mri_y_rsi_rnd_wm_dsk <- import("imaging/mri_y_rsi_rnd_wm_dsk.csv")
mri_y_rsi_rnd_wm_dst <- import("imaging/mri_y_rsi_rnd_wm_dst.csv")
mri_y_rsfmr_cor_gp_gp <- import("imaging/mri_y_rsfmr_cor_gp_gp.csv")
mri_y_rsfmr_cor_gp_aseg <- import("imaging/mri_y_rsfmr_cor_gp_aseg.csv")

mri_y_qc_raw_smr_t1 <- abcd_load(core_path("imaging/mri_y_qc_raw_smr_t1.csv"))
mri_y_qc_raw_smr_t2 <- abcd_load(core_path("imaging/mri_y_qc_raw_smr_t2.csv"))
mri_y_qc_raw_rsfmr <- abcd_load(core_path("imaging/mri_y_qc_raw_rsfmr.csv"))
mri_y_qc_raw_dmr <- abcd_load(core_path("imaging/mri_y_qc_raw_dmr.csv"))


mri_y_qc_raw_smr_t1

j <- smri_t1_qc(
    mri_y_qc_raw_smr_t1,
    subject_list = 
)

j


z <- qc_smri(
    sm_cort_t_mtbi,
    mri_y_qc_raw_smr_t1,
    mri_y_qc_raw_smr_t2,
    t = 0,
    no_na = FALSE
)

vis_miss(z)

na.omit(mri_y_qc_raw_smr_t1$"iqc_t1_1_seriestime") |> length()


search_dd("iqc_t1_1_seriestime")

z

t1_qc <- z |>
    dplyr::select(
        subjectkey,
        matches("t1_._qc")
    )
t1_qc |> head()
t1_qc_pass <- t1_qc |>
    apply(
        1,
        function(x) {
            qc_scores <- as.numeric(x[2:4])
            if (sum(is.na(qc_scores)) == 3) {
                return(NA)
            } else {
                return(min(qc_scores, na.rm = TRUE))
            }
        }
    )
t1_qc$"t1_qc_pass" <- t1_qc_pass

t1_pc <- z |>
    dplyr::select(
        subjectkey,
        matches("t1_._pc")
    )
t1_pc |> head()
t1_pc_pass <- t1_pc |>
    apply(
        1,
        function(x) {
            pc_scores <- as.numeric(x[2:4])
            if (sum(is.na(pc_scores)) == 3) {
                return(NA)
            } else {
                return(min(pc_scores, na.rm = TRUE))
            }
        }
    )
t1_pc$"t1_pc_pass" <- t1_pc_pass



t2_qc <- z |>
    dplyr::select(
        subjectkey,
        matches("t2_._qc")
    )
t2_qc |> head()
t2_qc_pass <- t2_qc |>
    apply(
        1,
        function(x) {
            qc_scores <- as.numeric(x[2:3])
            if (sum(is.na(qc_scores)) == 2) {
                return(NA)
            } else {
                return(min(qc_scores, na.rm = TRUE))
            }
        }
    )
t2_qc$"t2_qc_pass" <- t2_qc_pass

t2_pc <- z |>
    dplyr::select(
        subjectkey,
        matches("t2_._pc")
    )
t2_pc |> head()
t2_pc_pass <- t2_pc |>
    apply(
        1,
        function(x) {
            pc_scores <- as.numeric(x[2:3])
            if (sum(is.na(pc_scores)) == 2) {
                return(NA)
            } else {
                return(min(pc_scores, na.rm = TRUE))
            }
        }
    )
t2_pc$"t2_pc_pass" <- t2_pc_pass

t1_qc_summary <- t1_qc |>
    dplyr::select(subjectkey, t1_qc_pass)

t1_pc_summary <- t1_pc |>
    dplyr::select(subjectkey, t1_pc_pass)

t2_qc_summary <- t2_qc |>
    dplyr::select(subjectkey, t2_qc_pass)

t2_pc_summary <- t2_pc |>
    dplyr::select(subjectkey, t2_pc_pass)

smri_qc <- list(t1_qc_summary, t1_pc_summary, t2_qc_summary, t2_pc_summary) |>
    merge_df_list(join = "full")

any_fails <- smri_qc |>
    apply(
        1,
        function(x) {
            vals <- as.numeric(x[2:5])
            print(vals)
            if (any(is.na(vals))) {
                return(TRUE)
            }
            if (sum(vals) != 4) {
                return(TRUE)
            } else {
                return(FALSE)
            }
        }
    )


smri_qc[any_fails, ] |>
    dplyr::select(-subjectkey) |>
    Heatmap(cluster_columns = FALSE)

any_smri_fails <- smri_qc[any_fails, ]

any_smri_fails[is.na(any_smri_fails)]  <- -1

# Kids who fail T2 QC, but not T1
t2_problems <- any_smri_fails |>
    dplyr::filter(t1_qc_pass == 1) |>
    dplyr::filter(t2_qc_pass != 1) |>
    dplyr::select(subjectkey) |>
    unlist() |>
    as.character()

sm_cort_hl <- sm_cort_t_mtbi |>
    dplyr::mutate(
        t2_fail = dplyr::case_when(
            subjectkey %in% t2_problems ~ TRUE,
            TRUE ~ FALSE
        )
    )

sm_cort_hl |>
    ggplot(aes(x = t2_fail, y = smri_thick_cdk_mean)) +
    geom_point()

```


```{r}
mtbi_df <- list(
    "as_mtbi_mem_daze_mtbi" = as_mem_daze_mtbi,
    "as_mtbi_mechanism_mtbi" = as_mechanism_mtbi,
    "as_mtbi_loc_mtbi" = as_loc_mtbi,
    "d_pubertal_status_mtbi" = d_pubertal_status_mtbi,
    "d_interview_age_mtbi" = d_interview_age_mtbi,
    "d_mtbi_age_mtbi" = d_mtbi_age_mtbi,
    "d_sex_mtbi" = d_sex_mtbi,
    "d_income_mtbi" = d_income_mtbi,
    "d_race_mtbi" = d_race_mtbi,
    "mh_headaches_mtbi" = mh_headaches_mtbi,
    "mh_mtbi_count_mtbi" = mh_mtbi_count_mtbi,
    "sm_subc_v_qc_mtbi" = sm_subc_v_qc_mtbi,
    "sm_cort_t_qc_mtbi" = sm_cort_t_qc_mtbi,
    "sm_cort_sa_qc_mtbi" = sm_cort_sa_qc_mtbi,
    "dm_all_wmnd_qc_mtbi" = dm_all_wmnd_qc_mtbi,
    "rm_gord_cor_qc_mtbi" = rm_gord_cor_qc_mtbi,
    "rm_subc_cor_qc_mtbi" = rm_subc_cor_qc_mtbi,
    "p_loneliness_mtbi" = p_loneliness_mtbi,
    "p_screen_time_mtbi" = p_screen_time_mtbi,
    "p_sports_mtbi" = p_sports_mtbi,
    "p_exercise_mtbi" = p_exercise_mtbi,
    "p_prosocial_mtbi" = p_prosocial_mtbi,
    "p_family_function_mtbi" = p_fam_fn_mtbi,
    "p_parent_psych_mtbi" = p_parent_psych_mtbi,
    "cbcl_anxdep_mtbi" = cbcl_anxdep_mtbi,
    "cbcl_withdep_mtbi" = cbcl_withdep_mtbi,
    "cbcl_somatic_mtbi" = cbcl_somatic_mtbi,
    "cbcl_social_mtbi" = cbcl_social_mtbi,
    "cbcl_thought_mtbi" = cbcl_thought_mtbi,
    "cbcl_attention_mtbi" = cbcl_attention_mtbi,
    "cbcl_rulebreak_mtbi" = cbcl_rulebreak_mtbi,
    "cbcl_aggressive_mtbi" = cbcl_aggressive_mtbi,
    "sds_total_probs_mtbi" = sds_total_probs_mtbi
) |> merge_df_list(join = "full")

mtbi_df_no_qc <- list(
    "as_mtbi_mem_daze_mtbi" = as_mem_daze_mtbi,
    "as_mtbi_mechanism_mtbi" = as_mechanism_mtbi,
    "as_mtbi_loc_mtbi" = as_loc_mtbi,
    "d_pubertal_status_mtbi" = d_pubertal_status_mtbi,
    "d_interview_age_mtbi" = d_interview_age_mtbi,
    "d_mtbi_age_mtbi" = d_mtbi_age_mtbi,
    "d_sex_mtbi" = d_sex_mtbi,
    "d_income_mtbi" = d_income_mtbi,
    "d_race_mtbi" = d_race_mtbi,
    "mh_headaches_mtbi" = mh_headaches_mtbi,
    "mh_mtbi_count_mtbi" = mh_mtbi_count_mtbi,
    "sm_subc_v_mtbi" = sm_subc_v_mtbi,
    "sm_cort_t_mtbi" = sm_cort_t_mtbi,
    "sm_cort_sa_mtbi" = sm_cort_sa_mtbi,
    "dm_all_wmnd_mtbi" = dm_all_wmnd_mtbi,
    "rm_gord_cor_mtbi" = rm_gord_cor_mtbi,
    "rm_subc_cor_mtbi" = rm_subc_cor_mtbi,
    "p_loneliness_mtbi" = p_loneliness_mtbi,
    "p_screen_time_mtbi" = p_screen_time_mtbi,
    "p_sports_mtbi" = p_sports_mtbi,
    "p_exercise_mtbi" = p_exercise_mtbi,
    "p_prosocial_mtbi" = p_prosocial_mtbi,
    "p_family_function_mtbi" = p_fam_fn_mtbi,
    "p_parent_psych_mtbi" = p_parent_psych_mtbi,
    "cbcl_anxdep_mtbi" = cbcl_anxdep_mtbi,
    "cbcl_withdep_mtbi" = cbcl_withdep_mtbi,
    "cbcl_somatic_mtbi" = cbcl_somatic_mtbi,
    "cbcl_social_mtbi" = cbcl_social_mtbi,
    "cbcl_thought_mtbi" = cbcl_thought_mtbi,
    "cbcl_attention_mtbi" = cbcl_attention_mtbi,
    "cbcl_rulebreak_mtbi" = cbcl_rulebreak_mtbi,
    "cbcl_aggressive_mtbi" = cbcl_aggressive_mtbi,
    "sds_total_probs_mtbi" = sds_total_probs_mtbi
) |> merge_df_list(join = "full")

vis_miss(mtbi_df)

colnames(mtbi_df)

# Summarizing
mtbi_df_race5 <- mtbi_df
#mtbi_df_race5 <- mtbi_df_no_qc
mtbi_df_race5$"race" <- NULL
mtbi_df_race5 <- dplyr::full_join(
    mtbi_df_race5,
    d_race_5,
    by = "subjectkey"
)
#any_na_mtbi <- mtbi_df_race5[, colSums(is.na(mtbi_df_race5)) > 0]
any_na_mtbi <- mtbi_df_race5
any_na_mtbi$"race" <- mtbi_df_race5$"race"
mtbi_summary <- any_na_mtbi |>
    group_by(race) |>
    summarize(N = n())
mtbi_summary
missingness_by_race_plot <- any_na_mtbi |>
    gg_miss_var(
        facet = race,
        show_pct = TRUE
    ) +
    geom_text(
        data = mtbi_summary,
        x = ncol(any_na_mtbi) / 2,
        y = 13,
        aes(label = paste0("n = ", N)),
        hjust = 1,
        size = 5
    ) +
    theme(
      text = element_text(size = 10)
    )
missingness_by_race_plot

get_race

import <- function(path) {
    return(abcd_load(core_path(path)))
}
abcd_p_demo <- import("abcd-general/abcd_p_demo.csv")

d_race_5 <- get_race(
    abcd_p_demo,
    mtbi_subjects,
    asian_as_other = FALSE,
    t = 0
)


missingness_by_race_plot <- any_na_mtbi |>
    gg_miss_var(
        facet = race,
        show_pct = TRUE
    ) +
    geom_text(
        data = mtbi_summary,
        x = ncol(mtbi_df) / 2,
        y = 13,
        aes(label = paste0("n = ", N)),
        hjust = 1,
        size = 5
    ) +
    theme(
      text = element_text(size = 10)
    )
missingness_by_race_plot


?gg_miss_var

mtbi_df |>
    ggplot(
        aes(x = race, y = household_income)
    ) +
    geom_miss_point(
        size = 4,
        alpha = 0.5,
        position = "jitter",
        jitter = 0,
        width = 1
    ) +
    theme_bw()


to_missingness <- function(df) {
    df_char <- as.data.frame(apply(df, 2, as.character))
    df_char <- apply(
        df_char,
        2,
        function(x) {
            x[!is.na(x)] <- "1"
            x[is.na(x)] <- "0"
            return(x)
        }
    ) |> as.data.frame()
    df_num <- as.data.frame(apply(df_char, 2, as.numeric))
    return(df_num)
}

mtbi_missing <- to_missingness(mtbi_df)


mtbi_missing |> Heatmap()

cor(mtbi_missing)


complete_mtbi <- na.omit(mtbi_df_list)
```
